
\begin{comment}
\part{The Book Series of \Miith}
\end{comment}
\begin{comment}
% \include{SentinelsMain}
% \include{Utilities/UsePackages}
% \input{Commands}
% \input{Hyphenation}
% \include{Story/DominatorsofMith}
% \include{Story/ArchonsofMith}
% \include{Story/SentinelsofMith}
\end{comment}



\part{Sentinels of \Miith}























\chapter{\CarzainPrequelBook}
This book tells Carzain's back story, before he joined the Runger War. 
It details Carzain's travels, Vizicar's awakening and their joint path to \kenosis. 















\section{Overview}















\section{The Mutiny}
\target{Mutiny}
\target{Mutiny chapter}
Carzain and Nishain were betrayed by mercenaries in Heropond Forest. 
Vizicar awakened (for the first time in Carzain's life) and fought, killing the mutineers. 









\subsection{Old description}
Carzain goes to Martinum with his father. Then back.

It is only autumn as they travel through Heropond, but in the \Wylde it feels almost like winter: Hoarfrost lies on the ground, and cold mist fills the air.

The younger trees hate them and want the intruders out of their forest. Carzain finds an older tree that is indifferent, cold, uncaring\dash it knows that the humanoids will die soon enough anyway. 

(To what extent can Carzain read the thoughts of trees? Much of it is probably just guessing based on vague emotional impressions.)

He also sees the \hr{Moons}{moons} in the forest. They look spectral and spooky. Have some Bal-Sagoth-esque imagery about them.






\subsubsection{Carzain dreams of being nothing}
On the way back to \hr{Redglen}{\Redglen}, Carzain dreams \hr{Ramiel is nothing}{his recurrent nightmare of being nothing}. 

He sees visions of humongous gods: 
\Human-like, \dragons, amoebae with pseudopods\ldots{}





\subsubsection{Betrayed by mercenaries}
On the way back to \hr{Redglen}{\Redglen}, their hired guards mutiny against them. Carzain fights back using magic and suddenly feels a strange ecstasy, a possession. He fights with power he did not know he had and slays the thugs. He is puzzled by the possession experience. 

The magic should be more bloody. I should show how the skin blackens and seethes, let people scream their agony while they boil and burn. They get cramps and spasms and perform a sickly, morbid \quo{dance} before they die from being zapped. 

Maybe fire magic should cause the victim to burn up \emph{from the inside}, instead of just tossing fireballs. Or perhaps tossing fireballs is the beginner's tactic: Easier and cheaper, but less powerful and less accurate. Causing your victim to combust from within is harder, but much more deadly and accurate. It uses the victim's own life force as fuel, burning him to ashes. 

Describe how blisters boil and burst. 





\subsubsection{The Redcor discover the \vertexspike}
A Redcor \matron\dash\Esmerel?\dash is sitting in the Topaz \Chateau, performing divination though \index{aquamancy}. Insert some Bal-Sagoth imagery here. 

\lyricsbs{Bal-Sagoth}{A Black Moon Broods Over Lemuria}{
  And in the dark ethereal mists of winter dreams,\\
  the ebon waters of enlightenment gleam 'neath the Black Moon,\\
  and the Valley of Silent Paths beckons\ldots{}
}

She discovers the \vertexspike{} that is caused by Vizicar's brief awakening, and realizes something has happened. I am not sure how much the Redcor know about \vertices, but she definitely knows something is up. She goes into research, and eventually they determine that very likely a Scion has awakened. 

\Esmerel{} goes off to wander the lands of \Velcad{} in search of the Scion. A year or so later she finds him, in the midst of the Pelidor-Runger war\ldots{}






\subsection{Changes}
The mercenaries have guns (pistols or muskets).

Maybe I should edit the date. 

Carzain and Nishain have not been to the Imetrium, merely some big port city in southern \Scyrum. 
They do not know so much Imetric. 
Nishain only knows a few rudiments, and Carzain none at all. 

When Vizicar fights, he ignores the \hr{Itzach pain}{pain that \Itzach{} brings}. 
\Itzach{} Vaimons have ways of using power economically, thus minimizing the pain and risk. 
Vizicar does not care about this. 
He is groggy and sleepy and his senses are dulled, so he thinks he is completely fresh and healthy and has plenty of bodily energy to spare. 
He does not want to be careful and conservative. 
He wants to be flamboyant and teach these damned peasants a lesson. 

After all, he is \VaimonCaliph. 
He is used to being one of the most powerful and skilled Vaimons in the \caliphate, and a Scion to boot. 
He does not stop to consider that he is out-of-touch with his body, or that his new body is weaker and less trained than his old one. 

Remember to have references to the \hr{Shechinah}{\shechinah}. 

After the battle, Carzain has nasty open wounds caused by drawing too much \qliphah{} power. 
He uses these heroic wounds to score Mirai. 
Then he gets healed by Imetric healers. 

The chapters with \ChyrieEsmerel{} and \LocarPsyrex{} do not happen at all. 
Get rid of them. 
At this point in time, no one knows about the \vertex. 
If they did, that would just cause all sorts of trouble and plot holes. 















\section{Ilcas Northstar}
\target{Ilcas Northstar chapter}
\target{Ilcas introduction}
Carzain and Nishain met Ilcas Northstar in \Bryndwin. 









\subsection{Old description}
Carzain and Nishain go back out of Heropond forest to the town of \Bryndwin.

\Bryndwin has its share of monuments (see section \ref{Monuments}): Poles with flags and lamps on them, carved images of gods, heroes and creatures, meant to scare the \Wylde and intruders away.

They encounter \hs{Telcastora Ilcas}, his two \nycans, Razor and Countess, and a bunch of other Imetrians. 

Remember to describe \hs{Telcastora Ilcas's appearance}.

They see a big \hr{Mulgron}{\mulgron}. Carzain is impressed by how the \mulgron is even bigger than an elephant. 

Remember to \hr{Nycans are frightening}{describe the \nycans as frightening and alien}.

Carzain reaches out his hand and tries to touch Razor's snout. Razor's eyes narrow slighty, and he retracts the hand. 

The two Vaimons hitch a ride back to \Redglen with Telcastora Ilcas and his Imetrians. Carzain befriends Ilcas and his \nycans, Razor and Countess. 

They part ways somewhere in Pelidor. 

Carzain has a wound from his battle with the thugs, but he suppresses the pain, as he doesn't want to show weakness in front on Telcastora Ilcas. I should try to portray him as somewhat over-proud and silly. 

During the trip back, he is treated by an Imetric healer-surgeon. But he retains the scars: One in his leg, one in the side of his stomach. 
The surgeon's treatment is more bloody than the Iquinian healing he is used to, but it is at least as effective. The Imetrians have a scientific approach to medicine, whereas the Redcor repress real science in favour of traditional mysticism. 
This makes Carzain doubt the value of Vaimon tradition.









\subsection{Changes}
Write about Carzain's meditation. 

Replace \quo{resonance} by \quo{\shechinah}.
Add \quo{\shechinah} to the glossary. 

\Bryndwin has a \hr{Wylde border}{\Wylde border} with charms and totem poles. 

Carzain introduces himself to Ilcas: 
\ta{I am \VizicarDurasRespina.} 

Ilcas carries a gun. 

When negotiating with the priest: 
Carzain has no interest in theology, but he is skilled at faking interest, if he does say so himself. 
It is a skill he has honed when picking up women. 

On their first day on the caravan, Carzain talks to Ilcas. 
Ilcas tells stories of his heroic and violent deeds, and of his heroic and violent sword. 
He especially tells of how he has fought against the Imetrium's arch-nemeses, the Rissitics. 
\hr{Rissitics and Runger}{This is important. The Rissitics are important to the story.} 
Make sure to paint the Rissitics as threatening and imposing foes.
Tell of how they wear animal masks and have warrior orders named Order of the \hr{Order of the Crocodile}{Crocodile} and Jackal and Scorpion and \hr{Order of the Hippopotamus}{Hippopotamus} and so on. 

These associations of war makes Carzain see visions of his past, but still very vague, little more than regular daydreams. 

Then Carzain asks to hold the sword. 
Ilcas refuses. 
But he shows him the sword and swings it around a bit himself. 
And tells him about it. 

Carzain scores Mirai faster (already on the first night) and more solidly. 
I need to show the reader how cool he is. 
He pulls off a pick-up comparable to the way Tony Stark scores the reporter girl in the movie \cite{Movie:IronMan}: 
\ta{I'd be willing to lose a few hours of sleep with you.}
She is impressed already after their very first meeting. 

Have more Vizicar in the sex scene with Mirai. 
And after it. 
He talks to Carzain in his head. 
Perhaps from Vizicar's POV. 

The night after sex, he lies awake thinking wildly about what in all of \Iquin and \Itzach is happening to him. 
When he falls asleep, he meets Vizicar in dreams. 

\target{Vizicar drives Carzain to war}
After this night, Vizicar drifts away. 
Carzain feels lost. 
Like something is missing inside him. 
Some important clue in some important mystery. 
Some part of himself. 
He feels like half a man. 

Carzain goes off to war hoping to find Vizicar again.  
He seeks out battle in the hope of provoking more Vizicar action in his head, so he can figure out who Vizicar is and what the deal is. 
Maybe Vizicar subconsciously imparts in him a desire to fight and seek glory. 
















\section{Visions and dreams}
Carzain had visions and dreams. 
As did Vizicar. 

They met in dreams and talked to one another, but neither understood what was going on. 
Both thought the other man was a figment of their own imagination. 

The dreams were triggered by combat and war, or the expectation of it. 









\subsection{Vizicar's motivation}
Vizicar knew he is more than a \human, and he told Carzain this. 
Vizicar wanted to attain \kenosis and regain his body, power and memory. 
Then he wanted to achieve \apotheosis and learn his true nature.
Then he would be a god.












\section{Carzain in the War}
\target{Carzain joins the army}
Pelidor went to war against Beirod. 
A trivial border dispute, but bloody enough. 

At this point, Carzain knew there was something odd going on with him. 
Carzain joined the army because he hoped it would help him find out what was happening to him, who he was and who Vizicar was. 
He could hear Vizicar stirring in his head at the prospect of war and glory: 

\begin{prose}
  \tho{I thought so. 
    It is this sort of thing that brings you out.
    \quo{Vizicar}.
    Whoever you are.
    I will find out what the deal is with you.
    And how I can get rid of you.}
\end{prose}







\subsection{War is Coming}







\subsubsection{Carzain joins the army}
News of the impending war with Runger reaches \Redglen. 

Carzain's parents hate war. Perhaps they have even done stuff to get him to dodge the draft - without his knowledge. Any any rate, Carzain goes to the barracks and signs up. See, Carzain is bored as fuck. He's a big boy in a small town. He has a craving for greatness, fame and power - things he cannot possibly find in \Redglen. He wants to explore and wants something to happen. So he goes off to war. At this point, Carzain is maybe 22. 

In the Pelidorian army, Carzain is welcomed because of his magical knowledge. Pelidor has few mages, since neither the Imetrium nor the Iquinian church support them. He is assigned to serve under Captain Archibald Curwen, the commander of the \ishrah of the Pelidorian army.  
Carzain also learns a lot of combat technique. As he studies combat, he finds all sorts of things coming naturally to him, as if he already knows them but has just forgotten he knew. 

On the way to \Malcur, Carzain calls dibs on a horse\dash a gray stallion named Arrow\dash rather than a \relc. Later, having trouble riding the beast, he ponders his decision. Seeing some of the others getting easily ahead on their \relcs, he realizes that a horse is not necessarily better. It is just that horses are more Vaimon-like. In stories, Vaimons always ride horses, so when he pictures himself in his head as a great Vaimon hero, he sees himself astride a horse, not a \relc or other reptile. Carzain realizes that he is a status-fixated snob. 





\subsubsection{Carzain and the Goldsmiths}
He talks to the Goldsmith brothers. 
He talks of how he is destined for greatness. 
At this point he remembers \hr{Ramiel dreams of being nothing}{his recurring nightmare of being nothing}, and he tries desperately to convince himself that he is not nothing. 
He tells himself that he is big and important, because he fears that dream. 









\subsection{To \Malcur}
Carzain travelled to \Malcur to join the Pelidorian \ishrah.

On the way he met Adrian Testor. 

In \Malcur he met Archibald Curwen. 

Have plenty of Vizicar scenes early on, including before, during and after his signing-up to the army. 
(If \quo{The Mutiny} and \quo{Ilcas Northstar} are kept in \TwilightAngelRememberEmph, then include lots of Vizicar scenes there. Otherwise move them to the prequel story about Carzain.)

Vizicar (when he gained some \kenosis) liked the life of an adventurer. 
It was a refreshing change of pace from the court life he was used to, full of responsibility and chains. 
This was a new kind of freedom, and Vizicar loved it. 





\subsubsection[Carzain meets Delph and Tsekkect]{Carzain meets Delph and \Tsekkect}
\target{Carzain meets Delph}
Carzain meets \hs{Delph} and \hr{Tsekkect}{\Tsekkect}.

They are cheerful guys. 
They befriend Carzain and show him around the barracks, where, among other things, Delph utters his classic line: 
\ta{Life in the army is great. We get food, money, a shot at glory, and the best pussy that money can buy. Well\ldots{} the best pussy that \emph{our} money can buy, anyway.} 

To which Carzain replies: 
\ta{And all they ask in return is that we fight to the death.}






\subsubsection{Carzain's idealism}
At the beginning of the story, \hr{Carzain's idealism}{Carzain is quite idealistic}.





\subsubsection{Vizicar awakens a little bit}
At some time at the beginning of the war, before Carzain's first battle in the army, Vizicar surfaces a little bit. 









\subsection{To battle}
They go to battle the enemy. 





\subsubsection{Carzain and Delph practice with swords}
Carzain and Delph practice their swordsmanship. 

When the two duel, Carzain mostly loses. He knows some technique, taught to him by Sir Guy in \Redglen, and he is taller, which gives him a better reach. But the shorter and cruder Delph is faster and more agile, and he fights dirty. 

Carzain: \ta{You fight dirty, you know that?}

Delph: 
\ta{No, I just fight like a \meccaran. 
  That attitude of yours is just \human{} provincialism.}





\subsubsection{Carzain won't smoke}
Carzain hangs out with some soldiers. The others smoke some kind of strong drug, like hash or marijuana. 

\begin{prose}
  Soldier: \ta{Come on, \Shireyo, get over here and smoke.}
  
  Carzain: \ta{No, I don't touch that. It's filth.}
  
  Soldier: \ta{Why do you say that?}
  
  Carzain: 
    \tho{%
      Why \emph{do} I say that? 
      Because my father told me so, but I am not going to tell them that. Think, Carzain, think! 
      I can't lose face in front of these guys. 
      Say something witty.} 
    \ta{Something witty.} 
    \tho{Phew. Nicely salvaged, Carzain.}
\end{prose}





\subsubsection{Curwen and Carzain eat}
The officers of the Pelidorian army are eating a luxurious meal. This includes the \ishrah. 

Curwen: \ta{Ah, by \nieur, I love food.}

Carzain: \ta{Food is good, but I like sex better.}

Curwen: \ta{Meh. Most women cook better than they fuck.}

Both: \ta{LOL.}









\subsection{The \Caliph Inviolate}
The sortie encounters a small Rungeran force. They fight. 

Carzain fights and kills. 
But he is not as great a warrior as he fancies himself. 
So he gets clobbered and takes wounds. 

He calls out to Curwen-tachi for help. 
They save his ass. 

Then Vizicar awakens. 
It's due to a combination of factors: 

\begin{itemize}
  \item The pure rush of combat. 
  \item The anger and shame over being defeated in combat by such lowly grunts. 
  \item The wounds leave Carzain's own conscious mind weakened, making it easier for Vizicar to take over. 
\end{itemize}


% Recall that Carzain is a Scion, an incarnation of the \Malach{} Ramiel. 
% Occasionally, when he fights and kills, Ramiel awakens in him, and he hears the voice of \VizicarFull, the previous incarnation of Ramiel. (This is inspired by, and similar to, how Rand al'Thor in Wheel of Time hears the voice of Lews Therin Telamon. But where Lews Therin is mad, annoying and even dangerous, Vizicar is sane and a powerful ally.) 

% Anyway, Carzain fights and kills, and Vizicar comes along and takes over. 

Curwen immediately senses something fishy, probably a \vertexspike{}. 

This time there is a struggle between Carzain and Vizicar, as Carzain tries to get back in control of his own body. 

%After the battle, Carzain falls unconscious as Vizicar retreats. The prolonged, unaccustomed possession and the struggle between the two personas was too much for his consciousness to take. 

After the battle Curwen probes, prodding Carzain into telling him stuff. Carzain tells a little of what he knows, but it's not much. 

Carzain's body is in a bad shape. 
Vizicar is a harsh master and takes poor care of it. 
This is because Vizicar is only half-awake. 
He's still in a half-dreamy state, and his senses are weakened. 
He doesn't entirely register the pain, so he just pushes on. 
So after the fight Carzain is a useless wreck, barely conscious. 

Maybe Carzain asks the others: \ta{Did I save the da?} 

The others: 
\tho{Save the day? You crazy fuck, you nearly killed yourself, and maybe us, too.} 
\ta{Um, yeah. Sure. You saved the day.}

Delph is scared by Carzain's weirdness. Maybe insert an inner monologue with Delph about how Carzain is a crazy weirdo: 
\tho{Typically. 
     Finally I meet a guy who seems trustworthy, who might become a true friend, and turns out he is a madman. 
     Or possessed by \mdaemons{}, or whatever. 
     Huh. 
     That'll teach me to trust a sorcerer.}

During the fight, Carzan does something stupid and reckless. 
Perhaps he sees an enemy Vaimon and goes in to capture his sabre. 
Afterwards, Curwen bitchslaps him and scolds him: 
\ta{You crazy fuck, \Shireyo!
    What the fuck were you trying to do?
    You very nearly got yourself and the rest of us killed!}
He grabs Carzain by the collar. 
\ta{Let me tell you something, boy.
    Your insubordination stopped being charming a long time ago. 
    Now either you get in line or I'll have you beaten!}





\subsubsection{Vizicar dreams}
Have another scene that describes the battle from Vizicar's point of view. 










\subsection{Vizicar}
Vizicar fights to gain control of his own body. 

\lyricsbs{Marduk}{Voices From Avignon}{
  Speak through me. Speak through me.\\
  The sin must be washed away with blood.\\
  Dream through me. \\
  Called to a new life through death.\\
  Called to a new life through death.\\
  But what shall you reach for when all \colours fall?\\
  Overwhelmed with maledictions. \\
  Feel the rays of redemption of a brand new Sun.
  
  Choking. Asphyxia. \\
  Inhale the Darkness, lungs filled up. \\
  Asphyxia. Asphyxia. \\
  But who shall you reach for when all \colours fall?\\
  Long-drawn moans and piercing cries \\
  blend with prayers and litanies. \\
  Faces bone dry. Condemned as the river everybody drank of. \\
  Inhale! Inhale!
}

\ta{I will win the power and glory I deserve. 
  Not just as \VaimonCaliph, but higher yet. 
  I am a Scion. 
  I am a \Malach. 
  I will achieve the \apotheosis{} and become one with \Iquin{} and \Itzach.
  That is my purpose as a Scion. 
  
  But first I must gain control of my own body. 
  Right now I live out an ignominious existence as a ghost in a boy's head. 
  I am nothing\ldots{}}

This makes him remember his nightmare of being nothing. 
He drifts away. 

He philosophizes. 

\lyricsbs{Emperor}{Sworn}{
  Four eyes as two in one.\\
  The forward circular view that never ends.\\
  An orbital voyage throughout the endless sphere of all,\\
  where time is lost and everything transcends.
  
  A graceful presence at stolen time
  
  As ghosts to the world.\\
  Ghosts to the world.
  
  For ice, outside, are we apart.\\
  As cold and eerie mist to the hand.\\
  Ever floating on its course\\
  towards the heights of shadowland.\\
  
  Thus appear the truly sworn.
  
  To be seen.\\
  To be feared.\\
  Yet, not to be reached.
}





\subsubsection{Lost in the labyrinth}
He is trapped in the labyrinths of \itzach{}, lost and searching for those precious and ephemeral windows through which he can peer out through Carzain's eyes and affect the world through Carzain's body. 

\lyricsbs{Emperor}{Ensorcelled By Khaos}{
  In an endless maze begotten,\\
  to dead ends led by fools.\\
  I sought a plague for those\\
  who smiled at walls in humble fear.\\
  
  Yet, belligerent ways came to an end.\\
  No war could ease my hunger.\\
  By craving death I was to darkness reborn.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine.
  
  No peace for me. No peace I seek.\\
  My quest goes far beyond.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine.
  
  I hail the greatest fall.\\
  Dark is the spirit of my token.\\
  Dark is my call.
  
  Still craving, still torn.\\
  Hear me, master of this realm\\
  to which I was reborn.
  
  \ta{Bearer of my stigma. Thou art of me.\\
  Yet, claim no gift, but guidance.\\
  For I am the giver of temptation.\\
  Thou art the executor of Thy rewards.}
  
  Dark is the spirit of my token.\\
  Dark is my call.
  
  The cosmic forces driving me,\\
  more noble, more free.
  
  Take me.

  Love and hate and all in between,\\
  I greet them all in ecstasy.\\
  Venus, seduce me.\\
  Mars, possess me.\\
  Tear my soul from sanity.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine and I am thine.
}









\subsection{Reads about Scions and Vizicar}
Maybe Carzain overhears someone (\Esmerel{} and \Racel{}?) talking about Scions. 
Maybe he is half-unconscious and they are standing over him, talking about him, trying to decide his future. 

He asks someone about the story of the Scions. 
Who? 
Perhaps \Racel, but more likely some other mage in the \ishrah. 
Perhaps \Sanyor. 

Anyway, he is told the story of the Scions. Or a version of it. Remember to have many false details, which can be brought into question later. 

Later, he goes into a library in \Forklin{} and reads about \VizicarDurasRespina. 
There isn't a big public library, but there are churches, and they have books. 
He goes into a church, introduces himself as an \ishrah{} mage and pulls a \trope{BavarianFireDrill}{Bavarian Fire Drill}.
He knows he has to use the same body language, frame control and social engineering skills that he masters when picking up women.
It works.
He gets his hands on the writings.

He also finds references to \hr{Vizicar's notes}{Vizicar's notes about \Malachim}, but can find no fragments of the notes themselves. 

He also finds references to \hr{Iolivine's notes}{\ps{\Iolivine} notes}. 
He has heard before that these notes are of exceptionally high quality, but he had been unable to find any copies of them. 
\hr{Redcor bogarted Iolivine's notes}{The Redcor are bogarting the notes}. 
This is one of the reasons he wants to go to \Redce. 

Among other things, he learns that \Belzir{} was an incarnation of an \quo{evil} \malach, and that she caused the \HundredScourges{} with her wicked \malach{} powers. 

More importantly, he learns that he is not mad. 
There are no \qliphoth{} controlling him. 
Instead, he is a Scion! 
He is an \uber-dude! 

He is happy. 









\subsection{Changes}
\begin{changes}
    
  \begin{comment}
  \paragraph{War is Coming}
  \end{comment}
  \changesitem{War is Coming}
    Remember to have references to the \hr{Shechinah}{\shechinah} in Nishain's speculations. 
    
    Rewrite the \quo{I want to fight} section from the officer's POV. 
    
    Mention Carzain's age (\quo{a young man, around 25\ldots{}}). 
    
    Make sure the soldiers notice that Carzain is a bit swarthy (being half Geican). 
    
    This might be the place where Carzain introduces himself:
    \ta{I am \VizicarDurasRespina. No! Wait\ldots{} I am Carzain \Shireyo\ldots{}}

  \begin{comment}
  \paragraph{To \Malcur}
  \end{comment}
  \changesitem{To \Malcur}
    Rewrite the scene where Curwen and Carzain meet, so it is from Curwen's POV. 
    
    Curwen should be smoking his pipe. 
    
    Mention Carzain's age (\quo{a young man, around 25\ldots{}}). 
    
    This might be the place where Carzain introduces himself:
    \ta{I am \VizicarDurasRespina. No! Wait\ldots{} I am Carzain \Shireyo\ldots{}}
  
  \begin{comment}\paragraph{\Forklin}\end{comment}
  \changesitem{\Forklin} 
    Get rid of \Racel. 
    
    Carzain is \hr{Carzain PUA}{a great PUA}. 
    He \emph{does} score in \Forklin.  
  
  \begin{comment}
  \paragraph{The \Caliph Inviolate}
  \end{comment}
  \changesitem{The \Caliph Inviolate}
    Again, Vizicar ignores the \hr{Itzach pain}{pain of \Itzach}, and Carzain gets burnt and wounded as a result. 
    
    Remember the \hr{Itzach pain}{pain of \itzach} when Curwen casts magic. 
    
    Remember to have references to the \hr{Shechinah}{\shechinah}. 
    
    Curwen needs to tell the reader that the \ishrah{} mages are equipped with plate \armour. 
    They just do not wear it when travelling, nor on stealth missions like this. 
    But when the battle comes, he misses it. 
    
    Maybe Vizicar holds back his power and magic. 
    He does not want to arouse suspicion and get caught. 
  
  \begin{comment}\paragraph{\Tsekkect{} and Delph}\end{comment}
  \changesitem{\Tsekkect{} and Delph} 
    Make sure people like \Tsekkect{} and Delph have inner lives of their own and don't spend all their time gaping at Carzain. 
\end{changes}
















\section{Mercenary}
After this short war ended, Carzain left the army and became a mercenary and adventurer.
























\chapter[Twilight Angel, Remember]{\TwilightAngelRemember}
\target{Twilight Angel, Remember}
\input{Story/Sentinels01Notes} 

























\chapter{\TheKenosis}
\section{Overview}
There are three main plot threads in this book. 
Each of them takes place in the dwelling place of one of the three fragments of the \Haskelek{} and deals with the people fighting the \Haskelek. 

\begin{enumerate}
  \item 
    Carzain goes to \Redce{}, trains there, and ultimately goes to fight the \Haskelek{} in \Redce.
  \item
    Lica and Sir James fight the \Haskelek{} in their country.
  \item
    Sentinels and Cabalists battle for control of the Ghost Tower. 
    Ultimately the Sentinels, led by \Nzessuacrith{} and aided by the \Haskelek{} fragment, succeed in driving away the Cabalists, led by \Achsah. 
\end{enumerate}









\subsection{Carzain in \Redce}
Vizicar, at this point, has regained most of his memories from his life as Vizicar. 
He knows he is a Scion, an incarnation of a \malach. 
He knows he is a superhuman badass. 
He is not \human, but something bigger and better. 
Now he wants to break his feeble \human{} shell and reawaken his true potential. 

Early on, he is joined by Shereid. 
She learns that he is a Scion. 
She joins him and supports him, like Mele supporting Rio in \cite{Tokusatsu:Gekiranger}. 
Together they do some research. 
They want to find out how to achieve his \Apotheosis{} and become the Twilight Angel he was meant to be. 
To do this they must work together with the Redcor. 

In the meantime, they discover that something abnormal is afoot in \Redce.
Something evil. 
Or is it? 

The Redcor want Carzain/Vizicar's help to fight this evil. 
(They mostly ignore and discount Shereid.) 
He is reluctant to ally himself with them too closely, but he would like to work with them to learn more. 
So he lets them think he is obeying their orders, all the while manipulating them. 
When he wants to, Carzain can look like a stupid, brash, impulsive boy who is easy to manipulate into doing stuff. 
But Vizicar, who lies and lurks in the back of Carzain's head, is much shrewder and often outsmarts the Redcor. 
(Be careful not to make the Redcor too stupid, though.)





\subsubsection{Carzain is a Sephiroth-type}
Remember that \hr{Carzain is Sephiroth}{Carzain is meant to resemble Sephiroth} from \cite{VideoGame:FinalFantasyVII}. 





\subsubsection{Carzain regains \Tydesmos's memories}
\target{Carzain remembers Tydesmos}
During this book, Carzain gradually regains \Tydesmos's memories, \hr{Carzain cannot remember Tydesmos}{which he had otherwise been unable to remember}. 
\Tydesmos was \hr{Tydesmos power}{a mighty and wise dark mage who possessed much Mythos knowledge}.
As Carzain gains these memories, it drives him a bit more mad. 
\quo{Mad} in the sense that he gains a non-\human perspective and begins thinking more like an immortal. 

Like Sephiroth from \cite{VideoGame:FinalFantasyVII}. 





\subsubsection{Carzain is forced to use violence}
At first, Carzain intends to work inside the system.
He plans to go along with the Redcor while secretly manipulating them to get what he wants. 

Some of the Redcor are nice.
Others are \quo{good} in a somewhat annoying way. 
Yet others are complete assholes and use the rules to bully and oppress people, even Carzain if they can. 
Compare them to Principal Snyder and the Watcher Council in \cite{TV:Buffy}. 

Carzain puts up with it for a while, with all the pride and disdain he can muster.
Eventually, though, he feels forced to resort to violence.
The \hr{Racel dies}{he kills \Racel} in a very Sephiroth-esque scene (\cite{VideoGame:FinalFantasyVII}). 

All the way through the book, Carzain has had a sinister master plan.
This has to do with his \hr{Carzain's Sephiroth epiphany}{Sephiroth epiphany} in \TwilightAngelRememberEmph. 
He has been secretly working towards this dark goal for the whole book, in front of the reader's nose yet behind his back. 
The big surprise comes at the end. 
Carzain shows his true \colours, kills \Racel and a bucketload of other Redcor. 
He unveils what he has been secretly working on the whole time, and does a \trope{FaceHeelTurn}{Face Heel Turn} and goes to join \Belzir. 

Also make him resemble Anakin Skywalker/Darth Vader in \cite{Movie:StarWars:III}. 

Carzain has been contacted by \Belzir. 
She tries to seduce him.
Through this, he learns a little of her plans. 
He tells this to the Redcor. 
Officially, he is horrified by \Belzir's evil and wants to work with the Redcor to stop her. 
Unofficially, he is thinking of defecting to \Belzir's side. 
So he \quo{spies} on \Belzir for the Redcor. 
He tries to figure out what \Belzir is up to.
Whenever he finds out something and explains it to the Redcor, he deliberately misinterprets his data so as to mislead them and cast a smokescreen over himself to cover for his own shady plans and dealings. 









\subsection{Sentinels}
Meanwhile, \Narkiza-tachi are advancing north. 
They have conquered some stuff. 
They want to control more land. 
They need some strategic locations in southeastern \Velcad{} in order to resurrect \Belzir. 

See, the Sentinels have been communing with \Belzir. 
They want her back. 
She has grown to hate the Cabalists.
If she returns, she will want to take revenge on them. 
But they also know that she is a \Mystraacht{} patriot. 
So maybe, if she returns, she will be able to go to \Mystraacht{} and conquer it. 
This will leave a third of the Cabal's strength under the command of a maverick with a giant grudge against the rest of the Cabal. 
The Sentinels want this. 
So they are supporting \ps{\Belzir} \quo{Royalist Faction}, who work to see her restored. 

But, but, but. 
The Sentinels must not be seen as actively supporting \Belzir.
That would be bad. 
Instead, the Sentinels act as if they know nothing of the Royalists and are just pursuing their own gambits.
Then, by sheer chance, they \quo{unwittingly} end up accidentally helping the Royalists achieve their goal. 
The Sentinels obstruct the Cabalists and Redcor who were trying to obstruct the Royalists, and so the Sentinels \quo{unwittingly} end up accidentally helping the Royalists achieve their goal. 

(Oh, yes. 
\ps{\Secherdamon} \trope{XanatosGambit}{Xanatos Gambits} can be complicated.) 

The Sentinels now have \Nithdornazsh{} set up. 
So far, so good. 
This will allow \ps{\Vizsherioch} to spread his \vertex{} influence and become the \hs{Dagger}. 

Meanwhile, the Royalists are abroad. 
They have to solve some Aenigmata in order to free their queen. 
The Sentinels covertly help them do it. 

The Rissitic invasion also drains Cabal and Redcor resources away from \Redce, where a vital piece of \Belzir{} lies. 
This means that when the \Redcean{} Royalist infiltrators strike, there are few Vaimons to oppose them, and mostly weak ones. 
(Obviously this casts no suspicion on the Sentinels. 
 They have plenty of good reasons for wanting more land in \Velcad.
 No one would suspect them of secretly supporting an obscure cult serving a rogue \resphan.) 





\subsection{Royalists}
The Royalists do not have a fixed plan. 
In order to bring \Belzir{} back they need the blood (or, more generally, lifeforce) of a \resphan. 
This is not so easy to come by. 
\Shiaraid{} \hr{Shiaraid unpopular}{does not have many immortal allies}. 
So \quo{lots} of Royalists are out in the world, questing, seeking for a source of high-quality immortal blood or lifeforce. 

One group has the mummy of a powerful \quiljaaran{} king, unearthed from an ancient tomb. 
They think this mummy might contain some magic that will help them, so they are bringing it to their headquarters. 

Then Ramiel appears.
In Pelidor he \hr{Ramiel scares Nzessuacrith}{semi-unconsciously unleashes his \sathariah{} power} and scares \Nzessuacrith. 
\Shiaraid{} immediately detects and recognizes him. 
She knows Ramiel better than any other and can recognize his \vertex{} signature in a moment. 

This is a godsend for \Shiaraid. 
For centuries she has been searching for a way to come back to life. 
Now her old lover is suddenly reborn. 
This is an opportunity she cannot afford to waste. 
She must secure his alliance. 
She then sends some Royalists hunting for Ramiel (including Shereid). 

In addition to Ramiel's help, \Shiaraid{} also needs a strong link to the Midnight Bat \matrix. 
This is where \hr{Sentinels help Shiaraid with Ghost Tower}{the Sentinels can help}. 





\subsection{Shereid}
\hs{Shereid} is the first Royalist to find Ramiel. 

She wants to \quo{recruit} him and make him ally himself with \Belzir{} and the Royalists.
But Shereid cannot reveal her identity too soon. 
If Carzain were to refuse her offer, she would be in danger. 

She and Carzain initiate a subtle dance of evasion. 
He (Vizicar) quickly picks up on the fact that she knows something she is not saying; that she is more than she appears. 
He tries to ferret it out of her. 
But she is a skilled deceiver herself. 
She does not want to tell him before she is sure he is on her side. 

So she tries her best to turn him against the Redcor and get him to like the idea of a Geican revolution, and personal power and glory and sex. 
She talks about how bad the Redcor are and how great it would be to be free of them, to see how he reacts. 
He tentatively agrees, but he is also wary of her and does not tell her too much. 
It is a delicate game of mutual distrust. 

At last she lets slip to him the possibility that \Belzir{} is still sort of alive. 
This makes Vizicar very interested. 
He very much wants to meet this other Scion and exchange knowledge with her. 
He has read some claims that she achieved \apotheosis. 
This idea gives him a boner. 

But he still does not trust Shereid. 
Carzain and Vizicar have an internal dialogue about how they will not let her control them. 
I should also have plenty of scenes where he criticizes her\dash to her face, to others or inside his head. 
This is meant to fool the reader into thinking that he does \emph{not} want to go along with Shereid's ideas. 

But in fact he does. 
He likes Shereid. 
Much better than the Redcor. 
So, in the end, he betrays the Redcor (including \Racel) and goes with Shereid to Geica. 







\subsection{Underground cult in \Redce}
In \Redce{} there is an underground cult of hopeful, gullible youths who worship dark powers and hope for some kind of reward or insight. 
It is very much an ecstasy cult, with sex-orgies. 
The young people get their sexual urges satisfied, and more so, with drugs and dark magic. 
Maybe the dark powers feed on their sex. 

Have sexy priestesses and erotic rituals, including live sacrifice. 
The sacrifices may be unwilling captives, or willing, or mind-controlled. 
It works best, I suppose, if it's sexy girls who willingly let themselves be killed in a sexual ritual of pleasure and pain. 

The sexy priestesses have power, but they ultimately crawl at the feet of the master of the cult. 
The master is a badass gangster, like Lex from the movie \cite{Movie:GargoylesRevenge}. 

\lyricslimbonicart{Twilight Omen}{
  I salute thee, baptizer of my soul.\\
  Dear pagan master, let thy universe unfold.\\
  Show me the sign of the midnight sky.\\
  I will forever follow until dawn's early light.\\
  From the ashes a fire shall be woken.\\
  From the shadows words shall be spoken.\\
  A star constellation, \\
  a burning circle of serpent eyes.\\
  Esoteric mysteries of unknown life.
}

The Cabal actually know about the cult. 
At first, they allowed it to exist.
Back then, it was clear that the cultists were not Sentinels.
The Cabalists did extensive research and found \emph{no} links from the cultists to any Sentinel-aligned \matrices. 
In fact, the cult's magic was not even real, just smoke and mirrors. 

Moreover, the cult serves a useful purpose as an outlet for the people's evil nature. 
The Cabal knows that people have evil lusts. 
The Redcor try their best to suppress those lusts. 
For some people, the internal pressure becomes unbearable and they must have an outlet. 
From the Cabalists point of view, this underground cult is as good an outlet as any. 
So they let the cult exist, but keep it under surveillance. 

(Note that only the Cabal know about the cult. The Redcor know nothing.) 

For a while this went fine for the Cabal. 
But then, unbeknownst to them, \ps{\Shiaraid} Royalists found out about the cult. 
In deepest secrecy, she had her people infiltrate the cult. 
Now she has quite a lot of influence in the cult. 
She does not rule the cult, but she has enough power to use the cult for her purposes, as long as she is crafty. 
She can run her own business in the shadows, and whenever her people are discovered she can frame the cult and have it take the heat for it. 
The cult is not so well-organized, so the cult leaders and the Cabal spies do not have an overview of everything the cult members do. 
\Shiaraid{} herself encouraged this infighting and chaos and division, because she knew that chaos and outlawry would be the perfect milieu in which for her to work her shady schemes. 

The Redcor have no idea that \Shiaraid{} is back. 
To their minds, she is an ancient enemy they defeated millennia ago, and (despite what they may say to frighten children and outsiders) they do not suspect she will come back to haunt them any time soon. 

Under the cover of a \quo{harmless} ecstasy cult, \Shiaraid{} has sent her spies crawling all over the place under the \TopazChateau{}. 
She knew the Redcor had a piece of her soul prison in their keeping. 
Now, after decades of spying and searching, she knows where it is. 
But she cannot get at it. 
She does not have any contacts in the \Chateau{} that are sufficiently high-placed or sufficiently powerful. 

Hence, it is extremely fortunate for her that Carzain is now in \Redce. 
If she can get him converted to her cause, he could help her get her soul-jar thingy from the Redcor. 





\subsubsection{Scenes}
Have erotic scenes, like in \cite{GaryMyers:TheHorrorShow}, where a hot girl is stripped naked, tied up, beaten halfway to death and then sacrificed. 
In the end, she changes her mind and screams and begs for mercy, but in vain, and she is devoured. 
All the while, the cult chant their songs to their dark gods. 







\subsection{Ghost Tower}
\target{Sentinels help Shiaraid with Ghost Tower}
In addition to Ramiel's help, \Shiaraid{} also needs a strong link to the Midnight Bat \matrix, and through it the \Erebean{} \dweomer. 
Ramiel cannot provide this. 
His \kenosis{} weakens his link to the \matrix{} and \dweomer. 

But the Sentinels can. 
The \hs{Ghost Tower} is a link from \Azmith{} to \Nyx, remember. 
\Secherdamon-tachi plan to conquer the Tower, then \cooperate{} with \Shiaraid{} and Ramiel to cast a complex spell that will penetrate through the Tower into \Nyx{} and tap into the Midnight Bat and the \dweomer, then tap the energy and channel it through the Tower, through a complex \quo{series of tubes} devised by \Vizsherioch{} and built with assistance from the Royalist Faction, all the way from Pelidor through the Beyond and into Geica, where \ps{\Belzir} body is. 
This energy, combined with Ramiel's help, will let \Shiaraid{} rise from the dead. 

But there is a problem. 
This could be detected. 
If the Sentinels start siphoning energy from \Nyx, everyone will know. 
And the Sentinels still do not want it known that they are in bed with \Shiaraid. 
So they do something sneaky: 
They make it collide with another long-term plan of theirs, namely that of \hr{Vizsherioch becomes Shaeeroth}{raising \Vizsherioch{} to \shaeeroth{} status}. 
They will perform both \ps{\Vizsherioch} \shaeeroth{} ritual and \ps{\Shiaraid} resurrection ritual at the same time. 
Most of the energy will be consumed by \Vizsherioch, but some of it will be siphoned away and used by \Shiaraid. 
That way, if this is discovered at all, it will look as if some clever Royalists infiltrated the Sentinels and installed a \quo{back door}, stealing some of the Sentinels' energy and siphoning it away to use for their own nefarious purposes. 
No one will ever know. 

Of course, in order for the Sentinels to accomplish any of this, they must first capture the Ghost Tower. 
This is not easy, for the \resphain{} have turned it into a bastion and are fighting to defend it. 






\subsection{Telcastora Ilcas}
\target{Ilcas suspects}
The Imetrium is taking an active interest in \Velcad. 
They are ancient rivals of the Rissitics and do not want the Rissitics to conquer and gain too much power (be it secular or metaphysical power). 

Telcastora Ilcas escorts Carzain-tachi to \Redce. 
Then he turns back to southern \Velcad. 
There he works with other Imetrians and allies to oppose the Rissitic plan. 

He has to deal with the sinister \nagae{} that are the allies of the Imetrium. 
Gradually, he discovers more about the Imetrium's involvement with \nagae{} and other wicked powers. 
He becomes slowly disillusioned with his religion. 
He is learning \hr{The truth about the Imetrium}{the truth about the Imetrium}, and it is a darker truth than he would have liked. 

Gradually he turns away from his commanders, and even his gods. 
But only a little bit. 
He has served the Imetric gods all his life. 
He remains true to the ideals he has always upheld. 
But he becomes more critical and distrustful. 

From the Imetrians' point of view, Ilcas serves an important purpose in this battle. 
His sword, \Telderain, is a powerful \vertex{} in the Imetric \matrix. 
So when they find out he has gone prancing off to \Redce, they quickly send for him and fetch him back to southern \Velcad{} where he is needed to form part of the metaphysical bulwark against \ps{\Secherdamon} Sentinels. 

(Note that the Imetrians are not necessarily opposing \emph{all} Sentinels. But they are certainly opposing \Secherdamon.) 

In the process, Ilcas will encounter \Narkiza. 
They find out they have a lot in common. 
But they are destined to be enemies. 









\subsection{\Mystraacht}
Some of the \Mystraacht{} have learned that Ramiel is alive. 
They want to kill him, \hr{Mystraacht rival goes after Ramiel}{so they hunt him}. 
But \hr{Azraid protects Ramiel}{\Azraid{} protects Ramiel}, as does \Cishiel{}. 

\Cishiel{} should not discover that Ramiel lives until late in the story. 
She and \Dasteron{} need to be introduced before that point. 

In fact, maybe \Cishiel{} should be postponed to the next book. 









\subsection{Rissitics}
We follow \Narkiza{} and his Rissitic army, who are fighting their way through southern \Velcad{} in a campaign of conquest. 

In the \Narkiza chapters, make it clear that the \hs{Rissitics value their lives}. 

Their attack is partially meant as a diversion, drawing Redcor and Cabal attention away from more important matters such as \Nithdornazsh{} and the Royalist Faction's resurrection project. 

But the invasion also serves a useful purpose. 
\Secherdamon{} knows (or suspects) that the final breaking of the Shroud is near. 
He knows \iquin{} has a Hell of a lot of power. 
He wants to try to break that power. 
To this end, he wants to destroy the Redcor. 
He hopes to enlist the help of \ps{\Shiaraid} Royalists. 

The plan is that the Rissitics will move in to attack some Iquinian key strongholds and nations. 
If these fall, it will cause Iquinianism to falter on an \Azmith-wide scale. 

The Redcor know this, so they will set in as many resources as they can to fight off the Rissitics. 
This does not merely mean sending in a bunch of Vaimons. 
It also means calling in favours, pulling strings, drawing deep of the Redcor credit coffers and bullying allied rulers into banding together and fighting the Rissitic menace and defending the Iquinian world.

Meanwhile, the Royalists will resurrect \Shiaraid. 
This will be done in some place relatively close to \Redce. 
\Shiaraid{} will harbour a great hatred against the Redcor and will want to take revenge on them. 
With her \sathariah{} powers, her loyal Royalists and her covert Sentinel backing, she should be able to wreak a lot of havoc on the Redcor, which would seriously harm the Iquinian church. 
(And, with luck, this will not implicate the Sentinels at all and thus not expose \ps{\Secherdamon} long-term plan.)

If the Iquinian church can be destabilized, it will harm the global Shroud of Civilization that the church exerts over \Azmith. 
This will allow \Secherdamon{} to use gain more power in \Azmith{} and use the Realm to complete the forging of his Dagger. 





\subsubsection{\Secherdamon{} and Ramiel}
\Secherdamon{} does not know that Ramiel is back. 
And \Shiaraid{} does not tell him, even though they do communicate every once in a while. 
She keeps Ramiel a secret from \Secherdamon.

\Secherdamon{} discovers the secret near the end of the book, though. 
When someone helps \Shiaraid{} rescue her stuff from \Redce, Ramiel releases some powerful energy. 
\Secherdamon{} has been paying attention to what \Shiaraid{} is up to\dash she is his ally, but he trusts her only as far as he throw her\dash and this sudden burst of new energy interests him. 

\Secherdamon{} sees clear signs of activity in the Midnight Bat \matrix, and he hears some rumours. 
He puts two and two together and deduces that she has an ally who is a \resphan{} in disguise\dash perhaps a Scion. 

\Secherdamon{} or \Vizsherioch{} then talks to \Shiaraid. 
She is mentally unstable and has a hard time concealing her feelings, so \Secherdamon{} begins to suspect that her old lover, Ramiel, is back. 

At last the cat comes out of the bag. 
Ramiel kills \Shiaraid{} during her would-be resurrection. 
He can no longer hide his existence. 

(At this point, Ramiel knows who he is. 
 Maybe he has even taken contact with \Cishiel{}. 
 But maybe not) 

\Secherdamon{} is nonplussed and \hr{Secherdamon wants to off Ramiel}{wants to off Ramiel}. 









\subsection{\Ishnaruchaefir and \Azraid}
\target{Ishnaruchaefir and Azraid plot together, early in TBW}
Have a scene in the beginning of this book or the next.

\Ishnaruchaefir and \Azraid meet (\hr{Ishnaruchaefir and Azraid develop empathy}{as they have done before}). 
Gradually and ever so subtly through \SentinelsofMithEmph, \Ishnaruchaefir becomes convinced that \Azraid is on the level, and he also begins to suspect the general nature of \Azraid's plan. 

So when Azraid finally \hr{Ishnaruchaefir and Azraid plot together, early in TBW}{approaches \Ishnaruchaefir and asks for his cooperation in a secret venture}, \Ishnaruchaefir has expected it. 



















\section{Carzain in \Redce}









\subsection{Carzain is born}
Have a flashback to the day Carzain was born. 
Or, rather, the day he was conceived and became a foetus.

Before his birth, Carzain is a disembodied, barely conscious thing. 
In this state, he is less constricted by the Shroud. 
He can see beyond it.
He is also less afflicted by his usual \malach amnesia.
He knows and remembers his true self (in a semi-conscious way). 

He is an angel.
A god. 
He is the lord of tons of souls (in his \carcer).
He is the king of the world. 
He remembers his power as a \sathariah and a \malach.
Limitless power is at his fingertips. 

He is free of the Shroud. 
He is one with the universe. 
He can see and touch the entire Cosmos.
All bliss and glory is his. 
Everything is beautiful and perfect. 

But then it is torn away. 
He snatched out of his blissful rest. 
He is squeezed and hammered and compressed into a tiny, weak, constricting body. 
He is cut off from his divinity and immortality and power. 
He feels his mind slipping away.
His memories are being taken from him. 
He cannot remember who he is.
He can feel only loss. 
He is bewildered. 
He is afraid.
Desperate. 
His very being is being torn from him, and he can do nothing about it. 

He is blind. 
Mindless. 
Drowning in wet slime. 
He cannot breathe.

Flash forward to his birth.

Carzain is pushed out of his mother's womb. 
And suddenly he feels cold. 
There is blood.
A voice screams.
It is his own. 

Change POV to his parents. 
Nishain comes in. 
The midwife tells him it's a boy. 
Nishain touches his son and speaks his name: 
\ta{\CarzainShireyo.} 









\subsection{Carzain-tachi go to \Redce}
\target{Carzain goes to Redce}
Carzain-tachi go to \Redce. 





\subsubsection{They meet Shereid}
They meet Shereid. 

Carzain notices her \hr{Geican green eyes}{green eyes}. 
He \hr{Carzain wants green eyes}{wishes he had green eyes}. 









\subsection{Alliance with the Redcor}
\target{Carzain with Redcor}
At length, Carzain reaches \Redce{} and joins up with the Redcor. His mother is Redcor-born, and her name, \Deracille, is a Redcor name of the lesser nobility, so Carzain, grudgingly acquiescing to using his mother's last name, is accepted. He is trained as a Gandierre by Lacquasse, whom he comes to like and respect. 

He quickly learns to distrust the Redcor and not submit to them too easily. When his training as a Gandierre apprentice is complete, he is released from his bonds as an apprentice, and it is assumed and expected that he will take his vows as a Gandierre. But Carzain surprises them all by refusing to join the Gandierre. He has studied the Redcor laws and found a loophole, saying once free of apprenticeship, he has no more duties to the Redcor. However, he graciously offers to remain as their ally. The Redcor are less than happy about this, but they have to accept. 





\subsubsection{Carzain as an unwilling ally}
Carzain is unwilling, but somehow circumstances force him to work with the Redcor. 
He struggles to maintain the frame of an independent ally, while they try to turn him into a servant who should rightfully obey. 

I need to make up a good reason for this. 
Perhaps I can use a story similar to that found in the anime \cite{Anime:Dragonaut}, where Kamishina Jin is pulled into the Dragonaut organization without understanding what is going on. 





\subsubsection{Carzain uses his Redcor blood to coerce them}
Carzain uses his Redcor blood to coerce the Redcor into accepting him and thus gain access to stuff in \Redce. 
He exploits their snobbery and nepotism.










\subsection{\Redcean{} climate}
Remember what the \hr{Redce climate}{\Redcean{} climate} is like. 
This will influence the story. 









\subsection{\Esmerel{} has won a victory}
When \Esmerel{} brings Carzain back with her to \Redce{} and can prove that he is a Scion, it is a professional victory over some of her rival scholars.
Many of her colleagues refused to believe her theory that the \spike{} was a Scion. 
There were many other reasonable explanations, after all. 
But \Esmerel{} was a bigger Scion expert than any other, and she was certain her theory was correct. 
Now she has proven it. 

Carzain and Vizicar are not happy to be paraded as her trophy. 









\subsection{Carzain was wrong about \Esmerel}
Carzain sees \Esmerel{} in a new dress: Much lower cut, showing off a bit of cleavage. 

He tells her: 
\ta{\Matron{} \Esmerel, I was wrong about you. 
I understand now that underneath your gruff, arrogant and bitchy exterior, you are actually a real woman\ldots{} with a pair of very nice boobs.}









\subsection{Carzain gains an enemy}
Carzain is placed as a subordinate to a Redcor. She bullies and humiliates him, treating him like a stupid child. He tells her: \ta{You have gained an enemy. You have me outnumbered today, but know this: One day I will kill you.} 









\subsection{Carzain sees the \Morbus{} in \Redce}
\target{Carzain sees the Morbus in Redce}
Carzain walks around in \Redce. He ventures into the slums, where he sees the \hr{Morbus}{\Morbus} at work.







\subsection{Look at the zwongas on that one}
Carzain is in \Redce{} with a friend. 
A girl with very large boobs walks by. 

The friend exclaims: \tho{Look at the zwongas on that one!}

\target{zwonga}
\target{zwongas}
A \quo{zwonga} is actually an oriental fruit, a soft thingy like a very large plum. 
It is also slang for a woman's breasts, because a zwonga feels kind of like a breast. 









\subsection{I have zwongas}
Carzain is at a ball in \Redce. 
A serving girl comes up to him. 

Girl: 
\ta{Good day, sir. 
I have zwongas. 
Very nice. 
Would you like to try one?}

Carzain spewed and, for the next many moments, could only stare at the girl\dash and her zwongas\dash with a dumbfounded grin. 
He later learned that the girl was selling zwongas, which were actually a kind of fruit. 









\subsection{Carzain rescues ungrateful Redcor}
Carzain rescues a Redcor. 
She is a bitch from moment one, trying to order him around. 

Carzain: 
\ta{I haven't rescued you yet. 
If I were in your position, I wouldn't be mouthing off.}








\subsubsection{Carzain watches his language}
Later, she orders him: \ta{Watch your language, boy!}

Carzain: \ta{Fuck you. You can suck my big, sweaty cock until you choke on my cum and die.}







\subsection{Carzain practices archery}
From time to time in \Redce, Carzain practices archery in his spare time. 
He is a sucky archer, rarely ever hitting the target. 

It's a habit he inherited from Vizicar. 
In Vizicar's time they had guns, so archery was a sport, a harmless hobby. 
Vizicar was a sucky archer, too. 







\subsection{Carzain is lazy}
The Redcor try to get Carzain to practice dilligently, but he is lazy and would rather be a \boheme. 

But, from time to time, Carzain has flashes of mastery. This is typically when Vizicar (or an even older incarnation) awakens to help him, or take control. This frustrates the Redcor. 

It also serves as a subversion of the oft-seen \trope{AnAesop}{Aesop} that you must train and practice all the time to achieve greatness: Carzain pulls greatness out of his ass. (But not all the time. That would make him an annoying \trope{MartyStu}{Marty Stu}. Just once in a while.)









\subsection{Someone disbelieves Carzain's talk of monsters}
Carzain talks about monsters. Someone, a Redcor, immediately laughs. \ta{Surely you are imagining things.} Compare to episode 2 of the anime \cite{Anime:Gilgamesh}.

Vizicar immediately sees through the guy. 
\vizicar{%
  Too fast a reaction. He is trying too hard to conceal what he knows, to avoid suspicion. We need to keep an eye on him, Carzain.}









\subsection{Telcastora Ilcas faces off with a Trickster Mentor}
There is an old Redcor woman who tries to play the \trope{TricksterMentor}{Trickster Mentor} and be all hysterical and demanding. She tries to get people to jump through hoops for her before she'll help them. 

Telcastora Ilcas calls her out on it. 
\ta{Listen to me. 
  We are not supplicants begging a favour of you. 
  We come to you as equal allies and call upon you to do your \emph{duty}. 
  No more, no less. 
  And now you wish to hold the future of the world hostage to your own petty desires, your perversions? 
  Kindly explain to me, then, what makes you any whit better than the Rissitics? 
  What makes you any less of an enemy of the world?}

Carzain is impressed by Ilcas' ballsy-ness. 









\subsection{Ilcas comments on worms}
Some people eat food with Durcaci spice. 
They talk about the rumour that \hr{Spice and worms}{the spice is produced by giant sandworms}. 
They ask Ilcas about it, since he has travelled in Durcac. 

He says he \emph{thinks} it is true. 
But he has never seen these worms. 









\subsection{Carzain and Vizicar work together}
Carzain and Vizicar gradually learn each others' strengths and weaknesses and how to best combine them. 

\hs{Carzain is a better lover than Vizicar}. 

Vizicar's practiced diplomacy combined with Carzain's irreverent daring make them a great detective and manipulator, akin to Vlad Taltos from \authorseries{Steven Brust}{Dragaera}. 
(Vizicar on his own is a bit too constricted by principles and etiquette after having spent his whole life at court. Carzain teaches him to loosen up and be more open-minded and undaunted.)







\subsection{Vizicar surprised by map}
At one point Carzain looks at a map. 
Vizicar is in his head, reading along. 

\begin{prose}
  Vizicar: 
  \vizicar{Damn. This looks nothing like the maps I know.}
  
  Carzain: 
  \ta{Huh? Oh, right. Makes sense. 
    You lived before the \Darkfall, after all.}
  
  Vizicar: 
  \vizicar{The what?}
  
  Carzain summarizes what he knows of the \Darkfall. 
  
  Vizicar: 
  \vizicar{Interesting.} 
  
  Vizicar is especially intrigued by this \hr{Belzir}{\Belzir} character. 
\end{prose}







\subsection{Carzain hates the Redcor}
The Redcor are bitches. Carzain puts up with it for a while, but gradually, their arrogance makes him grow to hate them. 

The Redcor know that the Rissitics are up to something. Gradually it turns out that they mean to resurrect a \daemonic{} demigod, a \Haskelek{}. 
%See section \ref{Haskelek story} for details. 
%The \Haskelek{} is an old ally of the Sentinels and a terribly evil \daemon. It was brought to \Miith{} once about 1000 years ago (after Vizicar's reign but before \Belzir's) where it conquered and controlled a kingdom in central \Velcad{}, current day Pelidor and surroundings. But after a prolonged war, the \Haskelek{} was defeated by the Vaimons. 

%Unable to destroy it, the Vaimons imprisoned the \Haskelek{} in his temple, located in the middle of a huge, wild forest south or southeast of Pelidor. There it lay dormant, but its evil seeped out and corrupted the beasts and people in the surrounding area. The forests around its temple became dark, twisted and hostile (even more so than the regular \Miithian{} nature, which can be harsh enough) and the humanoid tribes to become degenerate savages who now worship the \Haskelek, or the memory of it. 

%There might be some planar stuff going on here, with the temple residing in another plane of reality. I should give this more thought. 

%Somehow the Rissitics reach the \Haskelekz{} temple and awaken it. It has grown stronger in the meantime by feeding off the prayers and sacrifices of his primitive worshippers, and is now almost as strong as before its death, but it needs powerful help to break free of its prison. The Rissitics free it. 

%The Redcor now oppose the \Haskelek{} and attempt to destroy it. It comes to a climactic battle, where they weaken \Haskelek{}, forcing it to retreat to its temple to recuperate. Redcor forces, including Carzain\dash and possibly Curwen\dash pursue him there, intending to reactivate the old spell seals and reseal the \Haskelek{} in its old prison\dash or something like that. 





\subsection{The Redcor leaders are incompetent}
The Redcor fight against the Rissitcs and Sentinels and the \Haskelek. But some of their leaders are incompetent fools. So, at times, Telcastora Ilcas or Carzain/Vizicar have to take command and lead their forces to victory. (In case of Carzain/Vizicar, it's more of Vizicar, since he is better versed in the art of war and commanding armies). 

Compare to Jarod Shadowsong in Richard Knaak's \emph{The Sundering}. When he leads the warriors into battle, compare to the king of Hyperborea in \bandsong{Bal-Sagoth}{The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire}. 







\subsection{Carzain runs from battle}
Carzain and some Redcor are in trouble, threatened by enemies. 

A \gandierre: \ta{We must fight! \Honour demands no less!}

Carzain: \ta{I have a better idea: Run like Hell!}

Telcastora Ilcas: \ta{I must agree with \Shireyo. I have my own \honour, but it does not require me to let myself die if I can do more good alive.}

Perhaps this is another instance of Ilcas inspiring Carzain to value his life above that of others\dash which, by utilitarian reasoning, is perfectly justified. 







\subsection{Carzain fails at etiquette}
Carzain gets owned regularly in \Redce{} because he does not know Redcor etiquette, or because he refuses to acknowledge it. 

He bitches and disses the hypocrisy of the Redcor rules and taboos. Perhaps he discusses it with Vizicar. 







\subsection{Carzain discusses philosphy with Shereid}
Carzain discusses \hs{Redcor philosophy} and \hs{Geican philosophy} with Shereid. 








\subsection{Carzain is fencing, no Vizicar}
Carzain is in a sword-fight. He tries to \quo{summon} Vizicar, who is a superior swordsman, and get him to come out and take control. But Vizicar is submerged in dormancy at that moment. 

Carzain is not a good enough swordsman to win on his own, so he flees. The Redcor are nonplussed by his cowardice. 










\subsection{Vizicar takes crazy chances}
Vizicar takes over their shared body and takes some crazy chances that nearly kills them both. 

\begin{prose}
  Carzain: \ta{You crazy fuck, are you trying to kill us?}
  
  Vizicar: 
  \ta{Well, I've already died once. 
    I got better. 
    That puts things into perspective, you know.}
\end{prose}










\subsection{Carzain shows off his game}
\target{Carzain shows off his game}
Carzain wants to prove to Vizicar that \hr{Carzain is a better lover than Vizicar}{he is a better pick-up artist}. 

He walks up to a hot girl. 
Makes eye contact. 
Comes close. 
Kisses her and grabs her breast under her clothes. 
Then he goes, without a word. 
Later that night, she seeks him out. 
They have sex. 

Compare to Satan from the movie \cite{Movie:EndofDays}.

Vizicar is improved. 
\vizicar{Wow. I could not have done that.}









\subsection{Carzain sacrifices himself by fleeing}
Carzain has the choice of rescuing someone\dash\Racel?\dash at great risk to himself, or flee and save himself. Inspired by Telcastora Ilcas's utilitarianism, he chooses the latter. 

\Racel{} survives and later confronts him: \ta{What did you think you were doing? Why did you not come and rescue me? You knew I was in danger! Have you no \honour? As a man, it is your Light-given duty to risk your life to save a woman! Or are you no man at all? Are you truly so selfish, so cowardly, so petty?}

Carzain slaps her up. \ta{Listen to me, you cunt. \emph{I} am the Scion! \emph{I} am the one whom you Redcor rely on to save you. I am the most important person on this expedition. Without me, there is no mission. \emph{I am the mission}. Without me, all that you have fought to accomplish will be for nothing. It follows that my life is worth more than any of yours. My foremost duty, then, is to remain alive, that I may fulfill the mission.

Nay, it is you who are selfish. It is you who are petty. It is you, you Redcor fuck, who don't know the meaning of sacrifice. I would love to save your pretty little ass\dash and with it, it would seem, my \honour and manhood\dash but I know my duty. For that, I am willing to sacrifice my \honour among the Redcor if need be. 

That is one of the many things that separate us: You are a fool, a blind fool, trapped in dogma and hypocrisy. Whereas I am wise enough to know right from wrong without such stupid principles. That is why I am better than you!}







\subsection{Carzain reveals his friend's secret}
Carzain has a Redcor friend who confides a secret to him. He makes Carzain solemnly swear that he will not reveal the secret to anyone. 

Later Carzain suspects that something fishy is going on, and tries to solve it. He works together with some allies\dash possibly Shereid. 
In order to solve this mystery\dash and save humanoid lives and potentially avert disaster\dash he deems it necessary to reveal the friend's secret. 

This is one of the first of Carzain's many broken promises.







\subsection{Carzain's \human{} enemy}
Carzain is standing and hating some enemy, possibly a Redcor. 

A friend of his defends the enemy, saying: \ta{When you look closer at her, she's really very \human{}. Look, she has all these nice qualities and does all these sympathetic, \human{} things\ldots{}}

Carzain: \ta{So? How does that excuse her crimes? In fact, it makes it worse. If she was a piece of shit all the time, then she might have the excuse of stupidity or a bad upbringing or whatnot. But her \quo{\humanity} only shows that she can be worthwhile if she chooses. Alas, she chooses to be a stupid bitch.}







\subsection{Carzain learns to control his souls}
Carzain slowly learns to control the dead souls bound to him, and to channel them as a weapon. (See section \ref{Bound souls as a weapon}.)

Carzain unleashes this power by accident one or more times in the latter half of this story, in a fit of extreme anger, anguish or other emotion. He is horrified by what he has done, as is Vizicar. 

Describe the victim's fear and horror. Inspired by Clive Barker's \emph{Jacqueline Ess: Her Will and Testament}. 

Afterwards, Carzain is like: \tho{What the fuck? That was no \Qliphah, and it sure as fuck wasn't a \Sephirah!}







\subsection{Carzain disgruntled}
After their victory, some of the Redcor are praised for their great worth, but Carzain is neglected and gets no praise, only reprimands. This causes him to resolve to turn on the Redcor. Shereid urges him on in that direction. Ultimately, while out in the wilderness somewhere\dash perhaps on a mission\dash Carzain betrays his \Redcean{} companions and kills at least one Redcor, then flees to Geica with Shereid. 

%The Redcor are bitches. Carzain puts up with it for a while, but eventually, their arrogance has bred such hatred in him that he turns on them. So, while on a mission, he betrays his companions and kills them, including one or more Redcor. 

%that he willingly turns to evil. In his experience, those that call themselves \squo{good} are no better. So, while on a mission, he betrays his companions and kills them, including one or more Redcor. 

%He goes to Geica and learns to channel Nieur like the Geican mages do. When he returns, he is far more powerful than before. 















\section{Carzain and his Dreams}









\subsection{Carzain dreams of \ophidian{} eyes}
Carzain dreams of \ophidian{} eyes. When he wakes he wonders who the \ophidians{} are and how he knows of them. How does he know the name? How did it come to him?

Maybe move this to the next book. 

\lyricsbs{Bal-Sagoth}{
  A Black Moon Broods Over Lemuria
}{
  As a black Moon broods over Lemuria,\\
  ebon witchfire enshrouds the gleaming citadels.\\
  sinistrous shadows rise from the vaults of the dreaming elder gods.\\
  \Ophidian{} eyes glimmer through the icy whispering Moon-mist\ldots{}
}

\lyricsbs{Bal-Sagoth}{
  Enthroned in the Temple of the Serpent Kings
}{
  Storm-borne bride of winter's fire,\\
  serpent-witch of the whispering fens.\\
  Veils of scarlet and sable,\\
  blood spilled in the vault of night,\\
  Frost-garlanded, the mind-binding \\
  glimmer of tear-filled ophidian eyes.\\
  The gleam of winter Moonlight upon black waters.\\
  Nighted spells of the enchantress.
}

\lyricsbs{Bal-Sagoth}{
  Shadows 'Neath the Black Pyramid
}{
  I hearken to the grisly murmur of nameless fiends,\\
  black jaws drooling blasphemy.\\
  Beyond the witch-song, darkly sweet,\\
  The wyrm-horn sounds cross Dagon's mere.\\
  Shadow-gate (portal to the Black Pyramid) yawns wide, beckoning\ldots{}\\
  Spells scrawled in blood and frosty rime.\\
  Squamous god encoils the onyx shrine.\\
  (By the bleeding stone) I am enraptured by \ophidian{} eyes.
}









\subsection{Ramiel's \Kenosis}
Ramiel has undergone the \hr{Kenosis}{\Kenosis} and become a Scion. 
But the \Kenosis{} is imperfect and has split his personality and memories into Carzain and Vizicar. 

Vizicar tells Carzain that before they can hope for \hr{Apotheosis}{\Apotheosis} and regain their true power, they must first master and perfect the \Kenosis. 
They must become one. 









\subsection{Dreaming of \Cuezcan{} Spires}
\target{Dreaming of Cuezcan Spires}
Carzain/Ramiel has amnesia and does not remember his past as a \resphan{} lord. But he remembers scattered pieces and fragments. His memory loss pains him, and he makes it his great quest to discover who he is. 

Carzain falls sick. During this time, he has fevered dreams and visions where hidden presences whisper to him about his purpose, his quest, his destiny of greatness. 

He sees visions of terrible creatures, macabre gods and ancient, ruined cities. 

Later, we have another scene where Carzain/Ramiel broods. He searches his mind for clues about his past and identity. He takes poisonous drugs and uses dangerous magic and meditation to take himself into trance.

\lyricsbs{Bal-Sagoth}{A Black Moon Broods Over Lemuria}{
  Slumbering upon the throne of Moon-caressed ice\\
  I have supped deep the draught of white vapours.\\
  Shimmering upon the gleaming garlanded marble,\\
  a single strand of glimmering gossamer.\\
  In brooding and sombre visions I hear cries. \\
  Enthralling cries 'neath this frost-Moon rising.\\
  The whisperer in crystals speaks in dreams,\\
  of silken shadows and the softest breath of dark enchantment,\\
  of ancient cyclopean temples, raising jewelled spires to the stars.\\
  There is witchcraft in the moon,\\
  and a brooding silence reigns over the woods.\\
  My storm-forged sword,\\
  ensorcelled by eon-veiled incantations.\\
  Dark wizards' spells entwine me in ravening shackles,\\
  and black roses draw my blood with thorns as sharp as serpent's tooth. \\
  I fall into the rapturous embrace of sloe-eyed witches, \\
  the Moon gleaming upon their ivory bosoms,\\
  and descend into the still, icy waters of the lakes.\\
  Beyond the veil of the north-winds\\
  I await the emissaries of the tyrant.\\
  The wind whispering across the everlasting snows.\\
  My slumber is light as a wolf's\ldots{}
}






\subsubsection{Ramiel's dark secrets}
Ramiel has dark secrets and dark dreams. See section \ref{Ramiel dreams}.





\subsubsection{He dreams of \Nyx}
In his dark dreams he sees \Nyx. 

\lyricslimbonicart{Deathtrip to a Mirage Asylum}{
  To the abyss' morbid enigmas.
  
  Far beyond the earthly grave,\\
  the soul betakes to drift astray.\\
  Infinite horizons of pale grey skies.\\
  A still born heart within there lies.
}

He somehow understands and remembers that even though \Nyx{} is scary and horrid, it was once his home, and thus remains his home. 

\lyricslimbonicart{Deathtrip to a Mirage Asylum}{
  The sanctuary that once was lost\\
  is streaming endlessly in holocaust.\\
  The astral corpse is still pulsating,\\
  in a mirage asylum awaiting.
}









\subsection{Carzain gets lost in strange Realms}
Maybe have a scene where Carzain somehow stumbles into another Realm and is led astray. 

He encounters creatures that are sworn to serve his kind, but have been alone and abandoned for centuries or more. Perhaps they are incorporeal, but he imagines them in humanoid form. And because of his power over them, they assume the form the thinks up for them.

Perhaps this is where he finds \Belzir, and she finds him.







\subsection{\Belzir contacts Carzain in dreams}
Carzain is visited in his dreams by a mysterious woman. In his dreams, they have sex. The wraith-woman tempts him with promises of power, glory and revenge upon the Redcor. It turns out that the woman is \Belzir, the last \Calipha of the ancient \VaimonCaliphate and called the Dark Prophet of Nieur by some. She wants him to join her and her servitors, who are working to resurrect her. 

She also approaches Vizicar\dash maybe both at the same time, maybe one at a time. 

She urges them to join her, tempting them with promises of power, glory, sex\ldots{} and, best of all, knowledge. 
She knows he is a Scion, amnesiac and questing to master the \hr{Kenosis}{\Kenosis} and eventually the \hr{Apotheosis}{\Apotheosis}. 
She tells him that she is a Scion herself, the only Scion ever to have attained the \hr{Apotheosis}{\Apotheosis}. 
This gives Carzain and (especially) Vizicar a boner. 
Vizicar very much wants to go to her. 
He does not know of her and has not been indoctrinated to hate her (since he lived before she did), and he doesn't like the Redcor, so he roots for her. 
Carzain is a bit more \skeptical, with his heroic ideals and all. 

\Belzir{} tells him of how she was a rebel against the Vaimons and their oppressive religion. 
This impresses Vizicar. 
He wanted to do the same, but never had the will to actually do something about it. 
He admires her a bit. 

\Belzir claims that she is not evil.
She is working to create a better world. 
It is the Redcor that are the evil ones, with their repressive and bigoted religion. 
They are hypocrites.
She is the real deal. 

Carzain is stuck by the \hr{Belzir's sorrow}{immense sorrow and pain} she radiates. 
He notices the lines of tears under her eyes.

He is also attracted and enraptured by her \hr{Geican green eyes}{emerald green eyes}. 
He can feel the Geican eagle in her. 

When Carzain/Ramiel first encounters \Belzir, he is struck by her commanding, seductive being. 
It fills him with conflicting emotions: 
\begin{itemize}
  \item Sexual lust for her. 
  \item Intimidation; an inclination to submit and obey her. 
  \item A masochistic lust to let her sexually dominate him. 
  \item Shame at his own weakness and unmanliness. 
  \item Anger at her for making him feel shame. 
  \item Desire to punish her. 
  \item Lust to sexually dominate her. 
  \item Excitement at this challenge. 
  \item Respect for her strength, sexiness, seductiveness and boldness for making him feel all of the above. 
\end{itemize}

Later and gradually, he comes to realize this: 
\begin{prose}
\tho{I want to rule, to dominate her.
  Any opposite feelings I may experience are alien, unnatural things she plants in me through her manipulation and wiles, and which I have to combat with the power of my true self. 
  
  But \emph{she} has both: 
  She wants to submit to me, and she wants to enslave me.
  Perhaps both at the same time. 
  
  The last part is a scary thought. 
  Underneath the surface, who is really dominating whom? 
  If one of us pulls the other by a chain, who truly leads and who follows? 
  I am simple, but she is complex. 
  Damnably complex. 
  And that makes her even more dangerous. 
  I must not let down my guard with her.}
\end{prose}







\subsubsection{Sex with \Belzir}
Remember that \Belzir{} is herself a Scion, and she knows a lot about the \Malachim. She uses this knowledge to drop hints to Carzain/Vizicar and lead them on.

The sex scenes with Carzain and \Belzir{} should be Bal-Sagoth-esque: 

\lyricsbs{Bal-Sagoth}{
  Enthroned in the Temple of the Serpent Kings
}{
  Ruby-lipped and midnight-tressed, \\
  eyes as black as raven's wing.\\
  Flesh so pale as dawn-frost gleaming,\\
  nighted spells of the enchantress.
}

Or \Duana-esque (in the following, replace \quo{he} with \quo{she}):

\lyricsduana{nightsong}{Night Song}{
  at night he slips through my window \\
  cool air caressing me like a lover's moist tongue 
  
  I shiver new awakening \\
  moaning a rhapsody of vowels \\
  and consonants like crosses in a row \\
  his lips of bittersweet agony \\
  bruising tender flesh \\
  as I lay impaled by lust \\
  and hear the sound of my heart beating \\
  druming blood through my viens 
  
  his love is wild like wolf-song \\
  howling at the pregnant moon \\
  his voice is smooth as liquid velvet \\
  as he sings his soothing lullaby \\
  hush hush hush my pretty pretty one 
  
  until the dawn bleeds from darkness \\
  tangerine rays grazing my cooling flesh \\
  and he flees like the shadow of a dream \\
  leaving silence in his wake
}

\lyricsbalsagoth{The Hammer of the Emperor}{
  [She Came Bearing Dark Portents (The Foreshadowing):]\\
  Fever-dreams, dark omens and auguries. Prophecy!\\
  Why, when I meet your narcotic sloe-eyed gaze, \\
  does the image of a viper nestling in a bed of blossoms fill my mind's eye?\\
  Why, when you come to me by the pale light of a waning moon, \\
  do I glimpse the sheen of ophidian scales through the veils of sable?\\
  Why, when you enrapture me with your envenomed kisses, \\
  does the flicker of a serpent's tongue score my flesh?\\
  Enthralled by the vitreous lustre of your rubicund lips, \\
  your snow-pale skin musky with the intoxicating scent of night\ldots{} \\
  but such wicket thorns beneath this rose.\\
  Come witch, fly to me!\\
}

Gradually through the book, his sex with \Belzir{} helps him remember fragments of his past life. 

\lyricslimbonicart{Symphony in Moonlight and Nightmares}{
  This night belongs to us,\\
  my dear princess of death.\\
  We have a destiny together\\
  as we meet in hungry caress.
  
  A deadly kiss under moonlit sky,\\
  as I stare into thy dark and hollow eyes.\\
  You take me down where cold silence dwells.\\
  Unconscious darkness realms of demise.
  
  You are born at my grace to serve only me.
  
  Blood paint on the wall is the ancient dream I recall.\\
  Predictions in rainstorm as tears dark red cascaded.\\
  In cryptic depths of imprisoned rage where I succumbed to temptation,\\
  in the laughter of cruel gods, demonic wrath and devastation.
  
  A monstrous enemy demands to be set free.\\
  Frigid evil games. Black art and blasphemy.\\
  Prophecies in blood.\\
  A deadly kiss unto darkened bliss.
  
  We have a gift of shining\\
  by knowing the history\\
  behind obscure mysteries.
  
  The mysterious source of true art and experience.
}





\subsubsection{From \ps{\Belzir}{} perspective}
We see one of the scenes from \ps{\Belzir}{} point of view. 

\lyricsbs{Emperor}{The Ancient Queen}{
  Dark rivers run though me.\\
  Darkness follows everwhere. \\
  Kingdoms falling again and again.
}

In a dreaming state, she flies to him. 

\lyricsduana{thedreaming}{The Dreaming}{
  Midnight wakes beneath a mystic moon \\
  as ominous mists waltz dewy down \\
  the nocturnal dance of mothwings beating \\
  soft staccatos and whispered wind \\
  the spirit of a shape transforming \\
  like a ghost of velvet shadows \\
  through a lattice silently creeping \\
  into a window open to the night \\
  steals between the gauzy drapes \\
  to find the sleeper \\
  lost in slumber \\
  dreaming, dreaming, dreaming. 
  
  She watches as his soul lies hid \\
  slack-jawed and lashes fluttering \\
  lost in the nebulous expanse of dreams \\
  the rise and fall of his shallow breathing \\
  she sighs sweet syllables in his ear \\
  from bloody lips smiling deeply \\
  whispers caress his naked skin \\
  moonpale gooseflesh shivering \\
  his mouth opens to her poisoned kiss \\
  his breath captured as he is waking \\
  eyes open wide to the terrible sight \\
  dreams to night terrors transforming \\
  she drinks his spirit red like wine \\
  as his voice is \\
  screaming, screaming, screaming.
}





\subsubsection{Geican principles}
Carzain believes it's a Geican thing to accept your sexuality and revel in it. 
\hr{Carzain is disappointed in Geica}{He is disappointed} when he gets to Geica\ldots{}





\subsubsection{Shereid}
Carzain hangs out with \hr{Shereid}{Shereid}, a Vaimon woman of \ClanGeican. She is secretly a follower of \Belzir. She and Carzain end up having a sexual relationship.  





\subsubsection{He is scared when he learns \ps{\Belzir}{} identity}
When Carzain first learns \ps{\Belzir}{} true identity he is scared. 
But she convinces him that she is really good, and merely the victim of evil propaganda and lies. 
At this point Carzain doesn't like the Redcor, so he is willing to believe much. 





\subsubsection{\Belzir{} and Vizicar exchange memories}
\Belzir{} and Vizicar exchange memories of life, death and afterlife as \malachim. 

\lyricsbs{Emperor}{The Tongue of Fire}{
  the soul is never silent\\
  but wordless, held imprisoned in a cursed tomb\\
  wherein reflections never fade, never die\\
  slowly maddened by the emptiness
  
  left to perish in the ever-dark coil\\
  yet, always alert it its slumber\\
  scorn by the drops of light\\
  piercing through the surface\\
  and it screams
}

They both long to regain their true and rightful power.

\lyricsbs{Emperor}{The Tongue of Fire}{
  teach me the tongue of fire\\
  so that I may set the world ablaze\\
  for it is cold\\
  and this blindness can no longer give me shelter\\
  teach me the tongue of fire\\
  so that I may cry out loud my wrath\\
  and my passion\\
  or else my coil will blister and decay
}









\subsection{Carzain has evil daydreams}
Carzain's nightmares escalate. He begins to suffer from daymares as well: Daydreams that pop up every now and then, where he sees into the Beyond or into his own imagination. He sees people's true faces, or they are horribly distorted. He sees monsters from the Beyond, or the ghosts that are bound to him, or spectres from his imagination. 

A horrific theme is the blurring of the border between reality and fiction. Or rather, Carzain gradually realizes how blurred the border has always been. Some of the visions he sees in his daydreams are lies, his half-mad subconscious mind twisting the Shroud further to fit its own fears. But some of the visions he sees are truths, with his terrified mind momentarily breaking through the Shroud and gazing into Reality. 

See, when a mind is under great stress, afflicted with powerful, stressful emotions, it may be able to draw upon reserves of primal strength that are otherwise latent and sealed away from the dumb, Shrouded mind. This may sometimes enable the person to penetrate the Shroud. Although sometimes, the stressed mind may be in an exceptionally vulnerable state, and the experience of seeing into true Reality might be extra traumatic. 

In Carzain's case, he is not immediately traumatized. Vizicar helps a lot here, since he has had to live with this for a longer time and knows more of how to deal with it. But Carzain begins to doubt both the reality around him, and his own sanity. And Vizicar's. Because we more and more learn how demented Vizicar is. 

\lyricsbs{Arcane Wisdom}{Symphonia Chaos}{
  Ghastly ghostly presences.  \\
  Insanity takes its place, \\
  while an effigy fades astray \\
  and memories still withstand. 
}









\subsection{Carzain is repulsed, but also attracted}
At first, when Carzain learns of the horrors that fill the universe, he is repulsed. He is swayed by the Redcor's talk of the Light and all that is good, and almost renounces the \quo{black} Geican magic with which he is brought up. 

Vizicar objects to Carzain's idealism, and Carzain lashes back by repressing Vizicar and shutting him out. Compare to Rand in \emph{Wheel of Time} or Gollum in \emph{Lord of the Rings}, who represses his evil side. 

But the longer he stays among the Redcor, the more he is disgusted by them, their hypocrisy and arrogance. When his faith in the Light falters, Vizicar creeps back and whispers in his ear. 

Gradually through the book, Carzain becomes disillusioned and bitter, and more and more fascinated by the dark powers of \nieur{} and other forbidden things. Having to fight against the Redcor's moral principles, he develops a distaste for all morals and comes to enjoy breaking rules and reveling in his power, obeying only his own will and whim. 

This is gradual, tho. Whenever Carzain discovers a new power of his or Vizicar's, he is repulsed and horrified at first, and only later comes to like it. These powers become guilty pleasures to him: They are useful, and he likes the intoxicating rush they give, but he also tries to deny it\dash on the outside, to keep it secret, but also on the inside, because he wants to maintain his own illusion of himself as a principled and righteous hero. 

At the end of this book, of course, he completely abandons and betrays the Redcor and goes to side with Geica. 









\subsection{\Belzir{} awakens}
\Belzir{} slowly awakens. 
She is still groggy and half-delirious from her long slumber\ldots{} and only halfway sane. 
The first times she came to Carzain and had sex with him, she was in a hazy dream, too. 
She doesn't quite understand what is going on herself. 

In dreams, she teaches Carzain secrets. 
She speaks in riddles, because she thinks in riddles. 
It's all still dreamlike and cryptic to her. 
Besides, she's half mad from her millennia in limbo. 

\lyricslimbonicart{Deathtrip to a Mirage Asylum}{
  In limbonic life I've slept,\\
  dreamt that cryptic seals me kept\\
  sheltered from all visual sight\\
  'cause shadows chased every sign of light.
  
  Awakened from an ancient slumber,\\
  recalled to act of strife.\\
  My spirit old and body cold\\
  remain in dark demise.\\
  Immortality beloved am I to dying,\\
  and the whispering of secrets to my soul.\\
  I am born to sing this sorrow.\\
  Evil has no rest in me.
}

She still suffers and has horrible dreams from her time in limbo. 

\lyricslimbonicart{Deathtrip to a Mirage Asylum}{
  The invisible addiction of darkness, emptiness.\\
  And the ghastly silence devours.
  
  Deathtrip to a mirage asylum.
}

\lyricslimbonicart{The Dark Paranormal Calling}{
  The black funeral uniform gives me powers. \\
  I'm catching without warning the dark paranormal calling.\\
  A putrefied shadow that in purgatory dwells,\\
  imprisoned by the cold anxious pits of Hell.
}

She is a \hr{Disembodied souls}{disembodied soul} and hence weak. 
She wants a body back. 
To do this she has to break some spells. 









\subsection{Something inside Carzain mourns his loss}
Something inside Carzain/Vizicar mourns his loss. Perhaps this is a servant or servants (\humans? \resphain?) who willingly let themselves be killed and have their souls bound to him, to serve him as ghosts. But he lost his ability to hear them.

\lyricsbalsagoth{%
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  Can you not remember? \\
  Have you forgotten the magic?\\
  Sing to us your spells once more, \\
  and the ancient forest shall dance to your words\ldots{}
}









\subsection{Carzain dreams of his destiny of greatness}
Carzain dreams of the greatness for which he believes himself destined, namely as Overlord of \Mystraacht{} (although he doesn't understand that yet). 
These dreams are more optimistic, but still dark. 

\lyricsdimmuborgir{Reptile}{
  Black uneartly void. Creatures crawling.\\
  Forbidden, forgotten, fairly underrated.\\
  Bastards in the shape of angels holding my hands,\\
  passing me what is left of the wine.
}

\lyricsbs{Marduk}{Infernal Eternal}{
  As I looked into the mirror, \\
  and saw the creation which was fading, \\
  I sailed the darkened waters of my soul \\
  on the ship of flaming hate\\
  towards the land of the damned.
  
  The cold winds of the darkness blow strongly.\\
  The cemetery glows in the dark.\\
  A thousand times, thousand voices \\
  are screaming in pain from beyond.
  
  A number of faceless shapes \\
  march forth from the darkness within.\\
  Life is slowly passing away, poisoned by guilt and sin.
  
  Embraced in Black I lie,\\
  only waiting to die. 
  
  The greatest of life's events,\\
  and I begin my journey\\
  as hands of greater characters unveil the world.\\
  Plunging through space and time, my prison has now been slain.
  
  The reaper purifies my soul.
  
  Perdition and death. \\
  I was in ages so dark and far away,\\
  and I will always be.
}

\lyricsbs{Emperor}{Cosmic Keys to my Creations and Times}{
  All these landscapes are timeless, \\
  and this is all just a part of cosmos, \\
  (but) all is mine and past and future is yet to discover\ldots{} \\
  Much have been discovered, but tomorrow \\
  I will realise I existed before myself.
  
  I will realise planets ages old, \\
  created by a ruler with a crown of dragon claws, \\
  arrived with a stargate\ldots{} \\
  a king among the wolves in the night\ldots{} \\
  An observer of the stars.
}









\subsection{Dreams of his father}
Carzain/Vizicar dreams of his true father, \hr{Zachirah}{\Zachirah}, who urges him on: 
\ta{\hr{Ramiel can do better}{You can do better!}} 

When he wakens, Carzain talks to Vizicar. 
They discuss who this \quo{father} figure might be.  









\subsection{SM sex with \Belzir}
In dreams, \Belzir/\Shiaraid{} plays her sex-games with Carzain/Vizicar/Ramiel. 
She is a \hr{Shiaraid's sexuality}{sado-masochist}. 

She hopes to achieve one of two things: 
Either coerce Ramiel into submission or provoke him so much that his rage and pride will awaken some of his inner power and let him dominate her. 
Either way, she wins. 

Ramiel has his pride and refuses to submit, because he \hr{Ramiel is nothing}{fears being nothing}. 
He fights with all he has in him. 

She presses him to his limit. 
Her attempts at domination are not merely physical, but also psychological and social. 
She convinces him that he is indebted to her and that he has to serve her and submit to her if he is to keep in her good graces, so she will continue to graciously help him. 
She hints that if he is disobedient or incompetent or otherwise displeases her, she will punish him and make his life miserable (not just physically, but socially). 

At last he explodes in a mighty roar. 
The Shroud is broken, and for a moment she sees him in his true \resphan{} form, black-skinned and winged. 
But only for a moment. 
His \hr{Kenosis}{\Kenosis} once again takes over, and he lapses back into \human{} form. 
But some memories remain. 
She has brought him a great leap closer to \hr{Apotheosis}{\Apotheosis}. 
He has \trope{TookALevelInBadass}{Gained a Level in Badass}. 

Up until this point, \Belzir{} has been quite arrogant and always teased and baited Carzain. 
But now he is Ramiel, and just as strong as she. 
She is exhilarated. 

\begin{prose}
  \Belzir: 
  \ta{You have long said that you would make me pay for my insolence.
    Come and take your revenge then, if you have the strength and the courage for it. 
    Punish me\ldots{} my lord Ramiel!}
\end{prose}

He does. (In dreams.)

Compare with the sex scenes in \authorseries{Jacqueline Carey}{Kushiel's Legacy} with \Phedre{} and Melisande, or with \Phedre{} and Severio Stregazza. 

\lyricsauthorbookpage{Jacqueline Carey}{Kushiel's Chosen}{100}{
  [Severio Stregazza:] \\
  \quo{You\ldots{} will\ldots{} acknowledge\ldots{} my\ldots{} sovereignty!}
}





\subsubsection{\Belzir{} thinks}
Afterwards, Belzir thinks to herself: 

\begin{prose}
  \Belzir:
  \tho{He is good. And evil. I can use him. 
    Yes, he and I will go on to a fruitful and delightful partnership. 
    In bed, and out of it.
    And as for the \quo{acknowledge my sovereignty}, well\ldots{} we will see about that.}
\end{prose}

But later, she has doubts. 
She does not remember everything of her former lives, but she knows there is something \quo{wrong} with her. 
She is \hr{Self-destructive Shiaraid}{self-destructive}. 
It worries her. 

She cannot recall the details, but she remembers one name: 
\Nexagglachel. 
He has cursed her somehow. 
She knows her lusts are dangerous to her. 
\tho{It is madness. But it feels so sweet\ldots{}}











\subsection{Vizicar remembers the \angels}
Vizicar remembers the time of the \VaimonCaliphate, when everyone thought that the \Sephiroth{} and the \angels{} were good and all-powerful, and that evil in the world would soon be defeated. See section \ref{Vaimon Caliphate naivete}.

Later, he is very much shocked to learn that the \resphain{} are evil.







\subsection{Carzain encounters \vorcanths{} again}
Carzain has bad dreams, perhaps even manifesting in the real world. 
And \hr{Moon-Wolves help Ramiel in dreams}{the \vorcanths{} come to help him}. 

The \vorcanths{} actually need his help. 
He owes them favours for their having helped him in the past (distant and \hr{Vorcanth help Ramiel}{near} past alike), so they are \emph{demanding} that he come and help them. 









\subsection{\Belzir{} tempts Carzain}
\Belzir{} tempts Carzain to delve deeper into the darkness. 
This is after he has become embittered with the Redcor. 

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  Return with me, beyond the stars.\\
  Rule with me a thousand worlds.
}

\lyricslimbonicart{Path of Ice}{
  Journey into your darkened secrets.\\
  Feel the burning flame inside.\\
  Admit the ecstacy of the extreme.\\
  Just close the eyes and enjoy the override.\\
  When we adrift through the sensual streams\\
  the enchanted pains are so divine.
  
  There are thorns everywhere,\\
  but along the path of ice rose bloom above.\\
  Blood is the rose of mysterious unions,\\
  the symbol of potency.\\
  A taste of erotic sins of lust.\\
  The entrance of immortality.
  
  There are such sights to see,\\
  Adventures and pleasures to feel.
}

\lyricsdimmuborgir{The Maelstrom Mephisto}{
  Dwell in depths of the darker self, at any shore of infinity,\\
  and watch the relentless paint the soil black.\\
  What is being formed echoes throughout eternity,\\
  as the painter chooses \colour no more.
}

She teaches him some magic. 

\lyricslimbonicart{Path of Ice}{
  The dormant seeds of suffering.\\
  The art of mortal flesh that bleed.\\
  Indulged in desire, the forbidden soul empire.
  
  Path of ice.\\
  The entrance to immortality.
}

He sees glimpses of his past as a mighty \resphan{} warlord, and glimpses of a possible future as a great sorcerer-king with \Belzir{} by his side. 

This also foreshadows the fact that he \emph{is} on a path to greatness. The book ends with Carzain contemplating his path from now on. He is becoming a character like Rio from \JuukenSentaiGekiranger, obsessed with the pursuit of power and greatness.

\lyricslimbonicart{Path of Ice}{
  Cold winds pierce through me\\
  as my dark star unfolds.\\
  I ascend the throne of fantasies\\
  where the beautiful abyss recalls.
}

She tells of how the \quo{pious} Vaimons betrayed her, even though she fought for freedom and enlightenment. 
Therefore she wants him to reject the Redcor, their religion and all conventional morality. 
(The Sun is a symbol of the Redcor and the Iquinian church.) 

\lyricsbs{Monolith Deathcult}{Den Ensomme Nordens Dronning}{
  Curse the Sun and all that's holy. \\
  Turn back. I dwell around. \\
  Come to me as a shadow. \\
  Engrave the Sun and the Blackest Moon shadow. 
}





\subsubsection{She tells him of the \Feud}
\Belzir{} tells Carzain a few secrets about the \feud{} and the master races. 

\Belzir: 
\ta{Mages are so obviously superior to the common people. 
Why, then, do they not rule the world? 
Why have there been no great sorcerer-kings since me, do you think? 

I will tell you: 
\emph{They} fear ones such as us. 
Whenever a mage starts climbing to power, they stab him in the back and take him down. 
}

Carzain: \ta{\quo{They}?}

\Belzir: (Dodges the question.) 






\subsubsection{Carzain sees \Belzir{} as a kindred spirit}
Carzain instinctively recognizes that \Belzir{} is a kindred spirit of sorts. 
This is vague memories from their time as \resphain, where they were both \Mystraacht, close friends and sometime lovers. 

He lets her seduce him and allies with her. 

\lyricsdimmuborgir{United in Unhallowed Grace}{
  We embrace the madness gathered as one.\\
  Mourning dead passion\ldots{} she comes to me.\\
  A fate awaits us in the night.\\
  In the ruins of creation we will unite.
  
  I am smitten by forbidden fruit.\\
  Possessed by moments of dark splendour.\\
  To walk the nightmare terrains forever.\\
  The enigma lies broken.
}

\lyricsbs{Emperor}{The Ancient Queen}{
  Crawl to thee over again. \\
  The Ancient Queen, the darkest woman.\\
  Stepping through her shadow. \\
  She who sees the soul. \\
  Black is her blood. \\
  Keeper of the fury. 
  
  Stepping through her shadow. \\
  Do you see her soul?\\
  Black is her blood. \\
  Keeper of the fury. 
  
  Dark under the shadow. \\
  Thy destiny lies with her. \\
  The Ancient Queen, \\
  ruler of the domain. \\
  Keeper of the fury. \\
  In shadow\ldots{} shadow.
}

It also brings back memories of the time when \hr{Zachirah seduces Ramiel}{\Zachirah{} tempted Ramiel into joining \Mystraacht}. 
This is what \Belzir{} is planning. 
She remembers their time in \Mystraacht{} together (if not perfectly then at least partially), and she knows how powerful and effective those memories are. 















\section{Immortals and the \Feud}









\subsection{\Azraid{} protects Ramiel}
\target{Azraid protects Carzain}
\target{Azraid protects Ramiel}
Ever since \hr{Azraid learns of spike}{\Azraid{} learned the details of the \vertexspike{}}, he has taken on the role of Ramiel's \quo{guardian angel}, subtly pulling threads and protecting him from harm while he grows towards his \apotheosis. 

This is necessary. 
Many forces conspire to kill Ramiel's Scion.







\subsection{Cabalists hold out in the Ghost Tower}
The \hs{Ghost Tower} is the Cabalists' bastion in Pelidor after they lost \Malcur. They use it as a staging area to mount offensives. Due to \hr{Charcoal at the Ghost Tower}{Charcoal's clever spell}, later improved and strengthened by \Achsah, the Tower is easily defensible. 

\Achsah{} and Charcoal hold out in the Tower, command their Cabalist minions, and maybe \hr{Achsah rewards Charcoal}{have sex}.





\subsubsection{\Achsah{} is inherited by a new mistress}
After \ps{\Teshrial} death, \ps{\Achsah} allegiance passes to another \resvil, a \Mystraacht{}, to whom \Teshrial{} was indebted. 

\Mystraacht: 
\ta{%
  You belong to me now.}

The \resphan{} tongue has many words for \quo{belong to} and \quo{have/possess/own}. 
She used one of the more respectful ones, but her tone and body language practically scream: 
\hypota{You are my slave.} 

\Achsah: 
\tho{%
  These \Mystraacht{} have no etiquette. 
  I miss \Teshrial{} already.}

Even so, it's not so bad, because the \Mystraacht{} are less snobbish and don't look down on her so much for her blood. 
They respect her more for her strength and skill. 









\subsection{Charcoal leaves the Ghost Tower}
To begin with, Charcoal is in the Ghost Tower with \Achsah. He helps her fight off the Sentinels, and she rewards him with sex. 

But eventually \Achsah{} sends him away on some mission. 









\subsection{Cabalists oppose the \Haskelek{} fragment in \Redce}
\Redcean{} Cabalists fight against a fragment of the \Haskelek. 
It is difficult, because they have to be covert and work indirectly under the nose of the nosy Redcor. 









\subsection{\Mystraacht{} rival goes after Ramiel}
\target{Mystraacht rival goes after Ramiel}
A \resphan{} of \Mystraacht, allied with a faction that hates Ramiel and does not want him to return, is pulling strings in \Redce. 
Trying to oppose Carzain and get him killed. 

This guy is approached by \Azraid, who asks him to stop. 
\Azraid{} \hr{Azraid protects Carzain}{has his own plans for Ramiel} and does not want this guy to interfere. 

\Azraid{} is very polite, but in a sinister way, with an undertone of threat. 

\begin{prose}
  \Azraid:
  \ta{%
    You are not under my command, of course, so I cannot force you to do anything.
    But I can \emph{request} that you desist and cease interfering with Ramiel.
    I hope you can be persuaded to acquiesce to my request. 
    Otherwise I should be\ldots{} saddened. 
    
    And by desist, I mean desist completely.
    Do not try to pull any strings.
    Do not interfere with him at all.
    
    Please consider my proposal.}
\end{prose}

After this, \Azraid{} figures that his veiled threats are probably not quite enough. 
So he contacts \Cishiel. 
Tells her about the affair. 
She is very interested. 

He sits back and is happy.
He knows \Cishiel{} will help keep Ramiel safe from meddling \Mystraacht{} busibodies. 
\Azraid{} was not confident he could keep them all away. 
But \Cishiel{} is very skilled. 
She has had to become sly and cunning just to survive. 
She has quite some insight into \Mystraacht, and she knows very well who Ramiel's enemies are. 
The two can work together and supply each other with information, which should be enough to keep Ramiel alive and guide him to a path where he can regain his memories and power. 










\subsection{\Vizsherioch{} and \Secherdamon}
Have scenes with \Vizsherioch{} and \Secherdamon{} at home, and show their relationship. 
Perhaps \Vizsherioch{} recommends that his father send him out, after his other minions have failed. This is the first time we see \Vizsherioch. 









\subsection{\Dasteron cleans up \Mystraacht}
\Dasteron does much good work to clean up \Mystraacht.
It had degenerated into a gangster-like den of petty greed and brutality. 
Barbarism.

\Dasteron has a long-term vision.
He unites \Mystraacht and restores it to \honour, glory, dignity and purpose.









\subsection{\Humans{} are special}
Some high-up Cabalist or Sentinel is talking to a \human.

\ta{The old days are gone, and so are the old master races. They may not know it, but their time is up. They had their time and now they are decline. 

Oh, they may still be strong, they may still have raw power. But they are locked in place. They are slaves to their own game, unable to break from it. 

But you \humans\ldots{} you are special. You are unique. You alone possess true freedom of will. And it is this special \human{} quality that, in the end, will decide this war. All the power of the elder races is nothing compared to the gift that is \emph{\humanity}. This is the age of men, and the future lies in \human{} hands.}

Afterwards, he walks away, thinking to himself. \tho{By the \Voidbringer, that was disgusting. I almost feel dirty for spinning such an outrageous lie. I can hardly believe that he bought it. Heh. But that is \humans{} for you, is it not? So easily manipulated, so easily tricked into believing anything you tell them.}

\tho{Hah. \quo{True freedom} indeed. \quo{The gift of \humanity}. Hah.}

\tho{Foolish worms.}









\subsection{A \Haskelek{} fragment possesses a mortal host}
A mortal \scatha{} or \human{} is possessed and used as a host body by one of the fragments of the \Haskelek. 
This might be \hs{Lica}.

The fragment is only half-awake, so the mortal carries it around for a long while. 

The victim is slowly driven mad by the presence of the \Haskelek{} inside her. 
It is alien and terrifying. 
She tries to interpret and put into words those alien thoughts, emotions, images and visions that the \haskelek{} sends into her mind. 
The only recognizable emotion that comes close is\ldots{} hate. 

In the end, the fragment breaks out of her, and her body explodes. 
Compare to the people possessed by Nyak in \authorbook{Stephen Marley}{Spirit Mirror}. 

\lyricslimbonicart{From the Shades of Hatred}{
  A thousand years time dimension \\
  in subconscious incarceration. \\
  My hatred to man, has transformed me \\
  into a habitation for demons. \\
  A devil incarnation. \\
  In the forgotten past, ages ago, \\
  beast became my alter ego.
  
  The god in me, infernal black divinity.\\
  After years of agony and pain \\
  hatred is all that remains.
}









\subsection{\Dzasselid{} explores the Beyond and gains knowledge}
\Dzasselid-tachi are on a mission. He needs more knowledge. 

Have a scene where he casts divination spells, explores the Beyond and gains some kind of enlightenment. See section \ref{The dark universe}.

\lyricslimbonicart{Dynasty of Death}{
  I'm launching into the abysmal universe.\\
  Disembodied I enter the cosmic cataclysm.
  
  I discover stairways to celestial dreamscapes\\
  A dark unknown conjunction within an immoral dimension.
}

Remember that the Rissitic \humans{} are dark-skinned. 
They should remark that \Velcadian{} \humans{} are much paler. 









\subsection{Someone finds a desecrated corpse}
Someone, investigating the strange happenings that have occurred lately in \Redce, finds a corpse that has been killed and desecrated by the underground cult. It is mutilated, perhaps with the skin torn off, and bears clear signs of sexual abuse (perhaps covered in sperm after bukkake). 

Maybe something a la Clive Barker's \emph{The Midnight Meat Train} (from \emph{Books of Blood I}). 









\subsection{\Narkiza{} fights and Belgrim almost dies}
\hr{Narkiza}{\Narkiza} fights in a great battle. \hs{Belgrim} takes grievous wounds and almost dies. But with massive, heroic effort, Belgrim rises again, roars its defiance and fury, then charges and causes immense destruction. He collapses again. 

\Narkiza{} fights off the enemies to keep Belgrim safe. He is not skilled enough to heal him, but he has enough spells to send Belgrim into a deep, ensorcelled sleep, stabilizing his wounds until they can find mages and have him healed. 

Belgrim lives.









\subsection{Raising the \Haskelek}
\target{Raising the Haskelek}
The Sentinels begin raising the \Haskelek. 

There are three parts, called the Hand, the Eye and the Heart. 

The strongest part is the Heart. It is imprisoned in a forgotten temple deep in Heropond forest. It's in the southern part of Heropond, where the forest is thickest. It is the hate, madness and evil of the \Haskelek{} Heart that has corrupted Heropond and made it a dark, haunted place of monsters and diabolist savages. (There might be some planar stuff going on here, with the temple residing in another plane of reality. I should give this more thought.) 

The Hand is in Sumian, buried in a secret, shunned tomb. 

The Eye is in northern Pelidor, near \Forklin. It lies in an enchanted tower which exists in \Nyx{} but can be glimpsed from the physical world. It is called the Ghost Tower, and the locals fear to come within sight of it. 

%Somehow the Rissitics reach the \Haskelekz{} temple and awaken it. 
The \Haskelek{} has grown stronger in the meantime by feeding off the prayers and sacrifices of his primitive worshippers, and each part is now stronger than after its initial defeat at the Vaimons' hands. But still, each part is not strong enough to break its prison, and so they need pwoerful help to escape. In come the Rissitics, who attempt to free it. 
%and is now almost as strong as before its death, but it needs powerful help to break free of its prison. The Rissitics free it. 

The Eye is the first part to be released. Soon after the Rungeran forces conquer \Forklin, the Rissitic mages move in and begin the spells to awaken the Eye. It takes humanoid form\dash a humanoid is sacrificed to it, and it occupies his/her body. 

The Hand is the second part to be released. It happens near the end of the first book. After a long quest, Sir James and Lica fail and are killed. The Sentinels successfully awaken the Hand. They use its power to scour the area of opposition, securing a strong foothold in Sumian. Then the Hand goes to Pelidor to join the Eye. 

Now Carzain and the Redcor come in to stop them. A lot of stuff happens. 

%The Heart is released, but eventually the resurrection process is stopped and the \Haskelek{} returned to sleep. This is not necessarily the end of the \Haskelek{}, but it will take a lot more work to awaken it again. I don't know how this goes on exactly. Perhaps they destroy some artifact that was vital to the process. 

Eventually the Heart is released, but before the three parts can be united as one again, Carzain and the Redcor storm in and attack. They succeed in breaking up the ritual, weakening (some of) the \Haskelek{} parts and forcing them to retreat.
%The Redcor now oppose the \Haskelek{} and attempt to destroy it. It comes to a climactic battle, where they weaken \Haskelek{}, forcing it to retreat to its temple to recuperate. Redcor forces, including Carzain\dash and possibly Curwen\dash pursue him there, intending to reactivate the old spell seals and reseal the \Haskelek{} in its old prison\dash or something like that. 

Ultimately, Redcor forces, including Carzain\dash and possibly Curwen\dash destroy the physical bodies of the Eye and Hand, possibly the Heart, too. This breaks them up.

See, each part is still bound to its tomb, but is able to project its power into a possessed body and thus walk abroad. But if that body is slain, the \Haskelek{} part is sent back to its prison, and a new ritual must be performed to release it again. After the defeat of the Hand and Eye, the Redcor (with Cabal aid) storm the Ghost Tower and/or the Hand's tomb and besiege them, thus preventing the three parts from easily uniting again. The book ends in a victory for the Redcor, but one that leaves Carzain bitter and resentful (see section \ref{Carzain with Redcor}). 















\subsection{\Daggerrain{} knows it all}
Have occasional references to \hr{Daggerrain}{\Daggerrain}, hinting at his status as \trope{TheChessmaster}{Chessmaster}. He pulls all the strings and knows everything. The reader should be kept guessing as to how much of the story was actually orchestrated by \Daggerrain. 

Have Cabalists going: \ta{Yes, \Daggerrain{} predicted that this would happen\ldots{}}

An interesting twist might be to have \Secherdamon{} acting as a counter-Chessmaster, at times eaving pulling \trope{XanatosGambit}{Xanatos Gamits} on \Daggerrain.

Compare him to the Crippled God from \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}. 









\subsection{\Cishiel{} and \Dasteron}
\hr{Cishiel}{\Cishiel} is allied with \hr{Dasteron}{\Dasteron}. 
He wants to be Overlord of \Mystraacht, and she wants to help him. 
They are already lovers and have had plenty of sex. 
Often in public. 
That is \hr{Mystraacht sexuality}{a \Mystraacht{} thing}. 





\subsubsection{Submissive \Cishiel}
The two devise a ploy to gain publicity: 
\Cishiel{} will sexually submit to \Dasteron{} in public. 
This will garner tons of attention and make them both look interesting and cool. 
It will make \Dasteron{} more alpha-male-ish and give him a little bit of \Zachirah-image. 

He invites her to a party at his place, or she invites him. 
As soon as they meet, she kneels down without a word and sucks his dick. 
She swallows, licks it clean, then stays on her knees. 
He grabs her hair and violently pulls her head back. 
She is in pain as she says: 
\quo{Thank you, Lord \Dasteron.}

He remains quiet. 
Throws her down to the floor and walks away. 
She remains on the floor for some seconds. 
Then she rises and meekly follows him. 

Then, at dinner, they both act like it didn't happen;
as if it were the most natural thing in the world. 
(Of course, they also have sex that night.)

Another possibility is to have \Cishiel{} act like a willing slave for \Dasteron. 
During dinner she kneels by his side. 
He caresses her hair and head, at times violently. 
When he is angered (by something else), he grips her hair and yanks her roughly. 
She moans and whimpers in a sexy way. 

Slave-girl \Cishiel{} is dressed in a skimpy bikini. 
Not naked as \hr{Resphan slave livery}{a \Mystraacht{} slave would normally be}, but close enough to naked to invoke associations of slavery. 
And a tight necklace reminiscent of a slave's collar. 
\Dasteron{} tried to make her wear an actual slave collar, but \Cishiel{} drew the line there. 
She was willing to endure much humiliation, but not that much. 

Everyone else knows that it was planned and constructed to make him look cool and give him publicity. 
But it still works. 
\ps{\Dasteron} rivals cannot help but be affected, even though they know it is a ploy. 
And \Dasteron{} knew they would. 

\Cishiel{} is, of course, richly compensated in favours. 
And it also reflects on her standing. 
She gains a certain naughty, erotic allure: 
\ta{Imagine the daring, that she would do such a thing!}
\hr{Resphain are possessive}{\Resphain{} are possessive}, and \Mystraacht{} perhaps more than any.
Now, whenever a \resphan{} sees her he thinks \quo{submissive sex slave} inside his head, and he gets obsessed and must have her. 
This gives her a great deal of power and political influence, and she knows how to use it. 

She muses over it. 
She has broken the rules of sexual conduct. 
In \CiriathSepher{} such an act would leave her branded as a slut with no self-respect. 
But in \Mystraacht{} it has the opposite effect. 
\Mystraacht{} is founded on a spirit of rebellion and anarchy; they hunger for sensations and turmoil. 
Breaking the rules is admired. 
She has been naughty and broken the oppressive \CiriathSepher{} morality, and the \Mystraacht{} love her for it. 





\subsubsection{\Cishiel{} hears rumours about Ramiel}
\Cishiel{} hears rumours that Ramiel is returning. 
She gets excited and goes looking for him. 

\Dasteron{} learns of it. 
It drives a wedge between him and \Cishiel. 
But they still have sex, and they still cooperate. 
It adds some spice, some challenge, some excitement to their relationship. 
They are \resphain{} of \Mystraacht, after all. 
They thrive on conflict. 

They end up enjoying this game, where they both try to extract information and favours from one another. 
They are now rivals. 
They manipulate and distrust but respect each other. 
And they have exciting, dangerous rival sex. 





\subsubsection{\Dasteron{} rapes \Cishiel}
Later, \Dasteron{} suspects \Cishiel{} of having done stuff to harm him behind his back. 
(She knows Ramiel is back. He does not know yet.) 

So \Dasteron{} comes and threatens \Cishiel. 
But she is clever. 
She manipulates him and re-frames his threats as a sex game. 
It ends with him mock-raping her and her mock-pleading for mercy. 

After he is done raping her and has dressed again and is about to leave, he turns around. 
She is still naked and lying on the bed. 
He gives her a long and intense stare. 
He makes her feel even more naked than she is. 
She wants to wrap her wings around her naked body in protection, but she does not want to show such a surrender to him, so she just lies there and lets him stare. 

Without words he tells her: 
\begin{prose}
  \Dasteron: 
  \ta{You tricked me today, \Cishiel. 
    But I will get you. 
    Mark my \quo{words}.}
\end{prose}










\subsection{\Dasteron{} becomes Overlord}
\target{Dasteron becomes Overlord}
\Dasteron{} made himself Overlord by gathering enough support to beat down those who disagreed. 
This had taken more than a thousand years of concentrated work. 

Before \Dasteron becomes Overlord, he has to fight several battles to the death against potential rivals.
Strength in combat is not the only virtue demanded of an Overlord, but it is an important one.
He brings \Cishiel as a spectator to those battles. 
She is dressed to resemble a slave: 
A bikini of brass and a necklace that sort of looks like a slave collar, and otherwise naked.

\target{Dasteron cannot become Apex}
\Dasteron is powerful, but his power and skill is chiefly political, not metaphysical. 
He lacks the \vertex{} strength required to make himself \apex{} of the \Mystraacht{} \matrix. 

At the point when he becomes Overlord, \Cishiel{} has learned of Ramiel's return and is working behind \ps{\Dasteron} back to support her father. 









\subsection{\Vizsherioch{} becomes a \shaeeroth}
\target{Vizsherioch becomes Shaeeroth}
\Vizsherioch{} becomes a \shaeeroth.
This is the culmination of the whole \Nithdornazsh{} gambit. 
\Nithdornazsh{} was a stepping stone for \Vizsherioch, to enable him to contact the \xss{} and harness the power that would make him a \shaeeroth.

No one anticipated this. 
Most people have forgotten that \shaeeroth{} could be created, since \hr{No more Shaeeroth created}{no more had been created} in the last thousands of years. 
Plus, most people do not know \Vizsherioch{} even exists. 

The kind of invocation needed to become a \shaeeroth{} is different from most of the invocations that summon forth monsters or other stuff to do the mage's bidding. 
Therefore, when \Vizsherioch-tachi prepared and performed the deed, it was not seen as such an apocalyptic thing, so the Cabal did not really move out in force against them. 
They did not understand the magnitude of what was happening, because it was so atypical, and it looked relatively benevolent (or, at worst, self-destructive). 

After he becomes a \shaeeroth, he becomes feared by all.
He grows so much in power as to rival Secherdamon and \Ishnaruchaefir. 
He is, after all, (sort of) an incarnation of the \xs. A \xs in draconic form.















\section{Ramiel's Defection}
Ramiel betrays the Redcor and defects to the Royalist Faction. 







\subsection{Carzain sacrifices \Racel} 
\target{Racel dies}
Somehow Carzain and the Redcor, fighting against the evil Royalist cultists, set up a gambit where Carzain poses as a turncoat who wants to join \Belzir. 

He tells the Redcor of his plan. 
\Belzir{} has long tired to seduce him, and he has let himself be seduced to an extent, but he has always defied her in the end. 
(We have seen this.) 
But now, he says, he thinks he can fool her. 
And here is how\ldots{} 

The reader must not know his entire plan. 
Then the genre-savvy reader will know it will fail. 
\trope{UnspokenPlanGuarantee}{Unspoken Plan Guarantee}, remember. 

He sneaks in in order to infiltrate the Royalists so the Redcor can stop them. 
He now has his hands on \hr{Belzir}{\Belzir} soul-jar, which the Redcor had been keeping secret and hidden from everyone. 
He has persuaded them to give it to him because he says he can destroy \Belzir{} with it. 

\Racel{} is with him, for some reason. 

The Royalists do a \trope{ShootYourMate}{Shoot Your Mate}: 
They tell Carzain that if he is with them, he should kill \Racel. 

Carzain walks towards \Racel. 
She is nervous, but knows he would never kill her.
He moves closer.
She becomes afraid.
\tho{What is he planning?}

He kills her by chopping her head off. 

See, Carzain had been playing the Redcor for fools. 
He wanted to get in on their gambits and know as much of their insider knowledge as he could. 
But now he thinks he has learned as much from them as they are willing to let him, so he seeks greener pastures. 
He betrays them and joins \Belzir. 
He knows she can be of tremendous help to him.
He gives her the soul-jar, and she is now almost ready to return to life. 







\subsection{Carzain flees to Geica} 
Carzain flees to Geica, together with Shereid and possibly a few others. 
(Maybe even Ilcas?) 
They meet up with other members of the Royalist Faction (the followers of the Dark Queen), including Senator Hayad. 
From here, the next step is to conquer Geica from within. 
(Geica has a democracy; they mean to seize it by a coup.) 

\emph{New idea:} 
At this point, Carzain is not evil, albeit disillusioned. 
Shereid convinces him that there are forces in Geica that are better than the Redcor. 
She introduces him to Hayad and some others, who make a good impression on him. 
It takes a while before he learns that the one behind it all is \Belzir. 
He balks at this, because he has always been told that \Belzir{} is evil, but they all argue that she was less evil than the stories say, that the Redcor and other wicked folks deliberately blackened her reputation\dash and that it was in fact their rebellion that caused the empire's fall, not \Belzir's just retaliation. 
After a while, Carzain accepts this. 
After all, he hates the Redcor and is willing to believe much bad about them. 
He also balks when he learns that they mean to conquer Geica by a coup, but after spending some time among the Geicans, he is convinced that they are little better than the Redcor. 







\subsection{Carzain allies himself with \Belzir} 
Carzain allies himself with the Dark Queen, and she sends demons to aid him. 
She wants him to help resurrect her, that she may return to \Miith{}. 
To this end, she gives him a magical orb. 
Carzain agrees, but plots against her. 

Carzain joins \Belzir's armies. 
He is equipped with the sabre and the \hs{Archon Ward} that belonged to her son Zacrias (the most powerful of \Belzir's many children, who succeeded her as Lord of \ClanGeican after her death). 
He also gets two antique \hr{Vaimon guns}{Vaimon pistols} (magical and powerful). 

\Belzir{} also summons a Peryton (a hind, whom Carzain names Venom) to serve him. 

\lyricsbs{Emperor}{Witches' Sabbath}{
  Shifting shadows guide my way in the autumn. \\
  From this fell alliance eternal night shall arise. \\
  Hear the scream of the wolves calling again. \\
  Legions are wreaking destruction upon the fortress.
}















\section{Carzain in Geica}
\subsection{Geica is corrupt}
\target{Carzain is disappointed in Geica}
Carzain has been filled with stories of how glorious Geica is. He has heard and read stories of the splendid, enlightened Geica as it looked during the time of the \hr{Vaimon Caliphate}{\VaimonCaliphate}. He sees it as a proud, enlightened, freedom-loving and free-thinking culture where all men are equal and free to achieve their goals and live for their ideals, and also a Mecca of learning and wisdom. 

But he is sorely disappointed. The real Geica is corrupt, a cesspool of hypocrisy, bureaucracy and greed. I need to underline the avarice, pettiness and treacherousness of the Geicans. 

Have a named guild of politicians, lawyers and the like (\quo{\DJOF'ers}\footnote{\quo{\DJOF} is Danish for \quo{Danske Juristers og \O konomers Forbund} (or something like that), the \quo{Danish Lawyers' and Economists' Association}.}), who are made the scapegoats and blamed for the corruption of Geica, by virtue (or vice) of the materialistic world view they spread. 

Compare to the Letherii culture in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}, and especially Chancellor Triban Gnol and Invigilator Karos Invictad. 

Perhaps the Geicans own no slaves, only life-long indentured serfs. Compare to the Indebted in Lether. 

This is a part of Carzain's process of disillusionment with all that is good. 

According to \Belzir, it has been going downhill ever since her death. She represented the pinnacle of Geican civilization, but history has posthumously vilified her. Her son \hs{Zacrias}, who succeeded her, did his best to carry on her legacy. His successors were less dilligent and less faithful. 

Perhaps Geica's decay is a result of being vilified, demonized and hated by the rest of the world, especially the \hs{Redcor}, who blamed the Geicans for \Belzir{} and the \hr{Hundred Scourges}{\HundredScourges}. 

Compare to House Harkonnen in \authorbook{Brian Herbert \& Kevin J. Anderson}{The Battle of Corrin}, who descended into evil after being abandoned by Vorian Atreides. 

After all this corruption and hypocrisy, \ps{\Belzir}{} bloody and violent coup almost seems an improvement. The \hs{Royalist Faction} have ideals of \quo{awakening to life the true Geican soul and legacy} and overthrow the corruption and decadence that has festered like a disease, a vermin infestation, in the absence of the true Geican spirit and way of life. They fight for the true Geica and seek to awaken the people. 

Compare them to Bruthen Trana and his Tiste Edur in \MalazanReapersGale. 





\subsubsection{True ruler is not good}
\ps{\Belzir} brutal coup is intended as a subversion of the \cliche{} of \quo{rightful ruler returns to the throne and all is good}. 





\subsubsection{Limyaael's ideas}
See \href{http://limyaael.insanejournal.com/205202.html}{Limyaael's rant on political systems} for inspiration and ideas on how to flesh out the Geican political system. 

See also \href{http://limyaael.insanejournal.com/205202.html}{Limyaael's rant on \quo{council scenes}} for inspiration regarding political intrigue and debates. 







\subsection{Royalists}
In Geica there is a \quo{Royalist Faction} who support \Belzir{} and want to restore her to life and throne. 
They love their queen and fight fiercely for her. 

Vizicar has similar feelings. 
He believes \Belzir{} is the key to his own goals. 
Besides, his feelings remember their old love for her. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  Through the marshland\\
  And through the rain and mud\\
  Now listen\\
  I march to youm my sleeping beauty\\
  I alone\\
  I cut myself on the moonlight beams\\
  Hordes of wolves follow behind me\\
  I alone\\
  I'm all alone\\
  My face brightens in the flash of the lightning
  
  Through the morning mist\\
  And through the frozen land\\
  I feel your presence\\
  I march to you, my sleeping beauty\\
  You alone\\
  I cut myself on the moonlight beams\\
  So that you can drink from my chest\\
  You alone\\
  The wind gripping my hair\\
  My teeth are grinding\\
  As we meet in the flash of the lightning\\
  It's like a dream
}







\subsection{Vizicar picks up an instrument}
In Geica, Vizicar sees a flute or something lying around. He picks it up. \ta{I can play that.}

He pipes some notes. It sounds horrible. He puts it down. \ta{I didn't say I could play it \emph{well}.}









\subsection{Carzain is drawn by the moon}
Carzain feels somehow that the moons are a key to unlocking the secrets of his past.

\lyricslimbonicart{Enthralled by the Shrine of Silence}{
  Restless days and sleepless nights.\\
  Drawn in the direction of the moon.\\
  Infernal magnet to mysterious destiny,\\
  beyond the grave of doom.
}









\subsection{Carzain goes on a quest to find a \vorcanth}
\target{Carzain dreams of Moon-Wolves}
Carzain is sought out in dreams by the \vorcanths. 

When he finally meets the \vorcanths, he also meets some of their \hr{Aryoth}{\aryoth} companions. 
But it is the \vorcanths{} who lead, not the \aryothim. 

\lyricsbalsagoth{Of Carnage and a Gathering of the Wolves}{
  [VOICE OF THE NIGHT:]\\
  Who are you, wanderer?
  
  [WANDERING SPIRIT:]\\
  I can't remember\ldots{}
  
  [VOICE OF THE NIGHT:]\\
  The wolves are gathering,\\
  the stars are shifting\ldots{}\\
  come, join us in the hunt.
  
  [VOICE OF THE NIGHT:]\\
  Who are you, wanderer?
  
  [WANDERING SPIRIT:]\\
  I have the scent\ldots{}
  
  [VOICE OF THE NIGHT:]\\
  Gaze into the mists\ldots{}\\
  feel the earth thawing beneath your feet.\\
  Come, bring down the prey.
}

Turns out there is a wounded \vorcanth{} who cries out for his help. 
He goes on a quest to find and save it. 
See section \ref{Moon-Wolves help Ramiel in dreams}. 

They guide him, employing occult astrology and \hr{Moon-Wolves and the Moon}{their mystic connection to the moon Visha}.

\lyricsbalsagoth{Of Carnage and a Gathering of the Wolves}{
  [THE SYLVAN ORACLE:]\\
  The wolves are gathering.\\
  The stars are shifting.\\
  This spectre at the feast.\\
  This nectar of the vine.
}

They guide him towards his true identity. He begins to understand his true nature: A terrible creature, cruel yet glorious.

\lyricsbalsagoth{Of Carnage and a Gathering of the Wolves}{
  [VOICE OF THE NIGHT:]\\
  Look at the power you possess\ldots{}\\
  See the might which you wield!\\
  You know who you are, do you not?
  
  [WANDERING SPIRIT:]\\
  Yes, I am the scythe in the field at summer,\\
  I am the thunder that awakens the earth,\\
  I am that which gives the night air its chill.
  
  [VOICE OF THE NIGHT:]\\
  Who are you, wanderer?
  
  [WANDERING SPIRIT:]\\
  I am far beyond the ken of men\ldots{}\\
  my gaze shall make the night tremble!
}

The \vorcanths{} \hr{Moon-Wolves dislike Dragons}{do not like \dragons}, their ancient rivals. They see Ramiel as their saviour.

\lyricsbalsagoth{Of Carnage and a Gathering of the Wolves}{
  He is the scourge, the thanatos, \\
  the cleansing fire, the purifying storm\ldots{}\\
  he is the cataclysm given corporeal form!
}

Later, he remembers that he is on a mission of genocide against the \dragons{} and their spawn.

\lyricsbalsagoth{Of Carnage and a Gathering of the Wolves}{
  [VOICE OF THE NIGHT:]\\
  Who are you, my son?
  
  [WANDERING SPIRIT:]\\
  Father\ldots{} I am annihilation incarnate!
}







\subsection{Someone admits to rationalizing}
Someone, possibly \Ishna, tells about his own history. He portrays himself as the hero and most everyone else as misguided or corrupt. At some point, he confesses that he is subconsciously rationalizing and shining up the story to fit his own desired interpretation. 







\subsection{Fake rebellion is beaten down}
The Geican power holders have caught the scent of the Royalist Faction rebellion. 

So the Royalists stage a fake coup. They are discovered because of information they themselves leaked, and are beaten down. Some of their \quo{leaders} are caught and killed. Apparently the faction is destroyed. The intention is to make the enemy lower their guard, so they can resume their plotting and be more effective for it. 

Compare to the plot of \FLuneNoireVol{5-6}. 

Hayad fights against the rebellion and thus proves himself \quo{loyal} to the government (although, of course, this is just a cover). 

Carzain is unsuspecting and only barely survives thanks to Vizicar's cleverness. \Belzir{} then tells him that it was a test of him somehow. 

Carzain is bitter over having been deceived and almost killed. 

Only Hayad apologizes to Carzain for using him. 







\subsection{Carzain becomes really badass}
During the course of this book, Vizicar awakens some more, and he and Carzain learn to better control their powers. They become more badass, in power and attitude alike. 

He begins to be more of a Dark Knight. Perhaps, at times, his eyes glow with some spectral \colour. 





\subsubsection{He remembers more of Ramiel}
He gradually remembers more and more of his life as Ramiel.

\lyricslimbonicart{Behind the Darkened Walls of Sleep}{
  Behind the darkened walls of sleep, \\
  as body rest and mind goes deep. \\
  A door opens in my heart. \\
  A dark euphoria.
  
  The soul is longing to escape \\
  the tyranny of the body. \\
  Dark winds now embrace \\
  the spiritual entity.
}

He remembers the wars he fought with the legions of \Mystraacht. 

\lyricsbs{Arcane Wisdom}{Maelstroms of Majestic Night}{
  Torrents of blasphemous fire enrage forth, \\
  thus allowing my soul to devour \\
  feeblish souls with sickening power, \\
  as the ancient warcrafts proudly descend from the North. 
  
  Oh the blood of my foes and fiends. \\
  How I beheld thy corpses, \\
  raptur'd by virulent winds. 
}









\subsection{Carzain drinks \ps{\Belzir}{} blood}
Carzain drinks \ps{\Belzir}{} blood during sex. 
It is \hr{Resphan cannibalism}{the greatest rush he's ever tasted}. 
It also brings back a little bit of \resphan{} memories, since it's \sathariah{} \Malach{} blood he's drinking. 

Compare to the movie \cite{Movie:QueenoftheDamned}. 







\subsection{Carzain goes into battle}
Carzain is about to go into battle. He dons his \armour. 

Vizicar complains. 
\vizicar{This is primitive.} 
Vizicar is used to wearing an \hs{Archon Ward}, a magical super-\armour so expensive that pretty much only the \VaimonCaliphs could afford it. 















\section{War Against the Redcor}
\subsection{Carzain has become Ramiel}
During the course of the Geican coup, \hs{Carzain} regains almost all of \hs{Vizicar}'s memories, and much of \hs{Tydesmos}'. 

By the time of the beginning of this book, Carzain and Vizicar have merged enough to be one person, with access to all of their shared memories (or all that they remember of them). (Although they still have their internal dialogue from time to time.)

He now uses the name Ramiel. 

He has become a badass dark lord who wears black \armour and robes. With swords and magic he kills anyone who stands in his way. At times his eyes glow red or some other evil \colour. 

They ally with \hr{Psyrex}{\ps{\Psyrex}} cult and wage war against the Redcor. 

Compare to Wismerhill from \FLuneNoire. It is interesting that Geica's \colours are green and black, like those of the Black Moon.

So the man who puts himself in command of the Geican army is far more than Carzain \Shireyo. He has all the life-long experience of a \VaimonCaliph and an archmage at his disposal. 
Vizicar is a much better general than \Belzir, but she is a far more skilled mage. 

Carzain is sort of like Rio from \emph{\JuukenSentaiGekiranger}. His obsession is not only to become stronger, but also to learn his true identity. 





\subsubsection{Archon Ward and other equipment}
\Belzir{} finally provides an \hs{Archon Ward} for Ramiel. Vizicar is happy. Ramiel also gets a black cape and robe, enforced with metal, to serve as backup \armour. Now, at last, he looks like a true Vaimon dark knight. 

At Vizicar's command they also produce for Ramiel an imperial coronet. It is enchanted and socketed with magical jewels. Perhaps these jewels were previously acquired on a quest.







\subsection{\Belzir controls Geica}
\Belzir{} now controls Geica. She and her associates use a mix of sincerity, propaganda and Shroud-weaving magic to make the people adore them as liberators. 









\subsection{\Belzir's resurrection nears}
\Belzir{} is looking forward to her impending resurrection. 

\lyricslimbonicart{As the Bell of Immolation Calls}{
  In a timeless departure from the flesh,\\
  Drifting the cold ether streams of death.\\
  By the altar of sacrifice, as I call upon the night\\
  to take and give me life beyond the shores of light.
  
  I glorify the hour of blackness\\
  as the bell of immolation calls.
  
  A black heart will adorn\\
  the wings when I'm reborn.\\
  Engraved on my memory\\
  is whom hatred made me.\\
  The ravages of time.\\
  Battles on in my mind.\\
  There are still wounds that bleed\\
  deep in the soul of mine.
}

She is happy to leave behind the horrible limbo.

\lyricslimbonicart{As the Bell of Immolation Calls}{
  A life among the dead and sorrowful,\\
  the endless voids where spirits are mournful.\\
  From the pale of agonising light \\
  I cross the bridge to crystal night,\\
  as the bell of immolation calls.
}







\subsection{Carzain turns against \Belzir} 
It turns out that Ramiel and \Belzir{} were manipulated by \Secherdamon{} and \Psyrex. 

\Belzir becomes more and more irrational and hysterical, like Efrel in \cite{KarlEdwardWagner:DarknessWeaves}. 
Ramiel begins to resent her. 

Ramiel becomes disgruntled. 
Ramiel grows to hate \Belzir{} and desires to usurp her, because she is an insane bitch. He also grows to hate the Sentinels for trying to manipulate him. 

He resents Shereid when he learns that she was part of the plan. He punishes her and means to kill her, but she pleads for her life. She claims that she loves him above all else and swears to serve as his devoted slave. So he lets her live. 

Ramiel's betrayal should be kept secret from the reader until the very end, but subtle hints should be dropped here and there, as he plots, schemes and prepares. The reader should understand that Ramiel is \quo{up to something}, but kept guessing as to what.









\subsection{Overlordship of \Mystraacht}
Ramiel and \Shiaraid{} both covet the throne of the \hs{Overlord} of \Mystraacht. 

\Shiaraid{} is the daughter of \hr{Zachirah}{\Zachirah} and feels that she is the rightful heir and should be Overlord, with Ramiel as her Prince Consort. 
She accidentally lets a suggestion of this slip. 
Ramiel picks up on it. 

He is not happy. 
He wants to rule, over \Mystraacht{} as well as over her. 
\emph{Especially} over her. 

Later she offers him the position of Overlord, with herself as his Consort. 
But by that time he has gotten paranoid and fears her ambition. 
He suspects she will cheat him and try to manipulate him so she can rule behind the throne with him as a marionette. 
She has done it before. 
She is good at exercising power even when she seems submissive. 
He does not trust her. 

\Shiaraid{} feels it is OK to submit to him but still exercise power. 
In her mind, it would be a great arrangement. 
Ramiel has his pride and she has her submissive side, so she is perfectly willing to let him have the fancy title, with her as his nominal inferior. 
But she still sees herself as his equal in worth, so she wants an equal share of the power. 
So in a sense her sado-masochistic way of thinking is more sane and healthy, since she can accept a equal relationship where she is sometimes dominant and sometimes subservient. 

Ramiel does not want to share. 
He has his (almost hysterical) \hr{Ramiel is nothing}{fear of being nothing} and cannot stomach the thought of submitting to anyone. 
He must dominate all the time. 

\hr{Curse}{\NexagglachelsCurse} plays them against each other and makes them suspect and plot against each other. 
They argue and fight and lash out in anger, with words or actual violence. 





\subsubsection{\Belzir{} is a bitch}
I need to make sure that \Belzir, under the influence of the Curse, acts like a real bitch at times. 
She may silently regret it afterwards. 
But she is bad enough that the reader understands Ramiel's growing hate and sympathizes with him (to some extent) when he betrays her. 









\subsection{\Belzir cries out \ps{\Aryal} name}
While having sex with Ramiel, \Belzir{} moans the name of \Aryal. 
Ramiel says nothing, but he is not happy. 
He knows that \Aryal{} was and is the greatest love of her life, and that he will always rank below her.
He does not like the reminder that he stands below someone else in some respect. 
It triggers his trauma about \hr{Ramiel is nothing}{being nothing}. 
It makes him jealous and resentful. 

It also makes him mistrust \Shiaraid. 
He fears she is more loyal to \Aryal{} than she is to him. 

Then he finds out the story of what happened to \Aryal. 
\Shiaraid{} \hr{Silqua dies}{betrayed and killed her}. 
If she would do that to her true love, what would she not do to him? 
The second-rate usurper who \quo{thinks he can take \ps{\Aryal} place in \ps{\Shiaraid} heart}? 

He resolves that he can't trust her and begins to plot against her. 

\Shiaraid{} also thinks about it. 
She knows Ramiel dislikes \Aryal, thinking of her as a coward and a weakling. 
This makes \Shiaraid{} resent Ramiel. 








\subsection{Shereid in distress}
Shereid slowly goes mad. Partially out of her obsessive love for Carzain/Ramiel, but even more so because she learns the cruel truth of \ps{\humanity} history. 

She keeps herself halfway sane by clinging to Ramiel and her love for him. 
They have incredible sex. Ramiel's love confirms to her that her life has a purpose. As long as she can be with him, she can live with the fact that her entire race is created to be the slaves of monstrous aliens. 

Compare her to Mele, with her love for Rio, from \emph{\JuukenSentaiGekiranger}. Come to think of it, Ramiel is also quite like Rio. 









\subsection{Carzain doubts his evil, and finally embraces it}
Throughout the book, Carzain is plagued by the memories of his evil life as Ramiel. At first he is horrified, repelled by what he finds inside him. But in the end, he embraces that legacy as his true self.

\lyricslimbonicart{Sources to Agonies}{
  Through the mirror of the soul\\
  I'm staring deep within\\
  To see what dwell behind the wall,\\
  The beauty of pale skin.
  
  The aura that surrounds me\\
  is not of noble kind.\\
  The blackness of the heart\\
  is all that's left to find.
  
  A dark river runs silent through my life\\
  like a floating nemesis.\\
  A dark shadow of what that used to be\\
  drifts now in lifeless misery.
  
  Live only to witness what I've become.\\
  Midnight is my shallow home.\\
  Soon to enter the last deed of mine.\\
  I'm forced to follow the streaming bloodline.
  
  When the wine of life is shed\\
  and dark cosmic space consumes\\
  I bring the memories back from the dead.\\
  Sources to agonies, a devouring monsoon.
}









\subsection{\Belzir is resurrected}
\Belzir{} is resurrected and has her body back. 
Perhaps she even gets a \resvil{} body. 

But part of her soul is imprisoned and sealed somewhere in \Redce. So they ally with \hr{Psyrex}{\ps{\Psyrex}} cult and conquer \Redce. 

Then they perform a magical ritual to heal \Belzir{} and return her true power to her.
Perhaps this ritual is also meant to restore her memories and her full \Malach{} power. 
But in the end, Carzain betrays \Belzir{} and kills her during the ritual. 

\lyricsbs{Cradle of Filth}{Cruelty Brought Thee Orchids}{
  Maleficent in dusky rose.\\
  Gathered satin lapped Her breasts\\
  like blood upon the snow.\\
  A tourniquet of Topaz\\
  glistened at Her throat.\\
  Awakening, pulled from the tomb,\\
  Her spirit, freed, eclipsed the Moon\\
  that She outshone as a fallen star.\\
  a regal ornament from a far flung nebular.
}







\subsection{\Vizsherioch{} is strengthened}
Have an arcane ritual where \Vizsherioch{} is given more power. 

Compare to \FLuneNoireVol{9}, where Wismerhill becomes the Prince of Negation. 

\lyricsflnv{9}{
  Haazeel Thorn: 
  \ta{%
    Life was truly torn from you, but I have replaced it with something better. In your veins now flows Negation.}
}







\subsection{\Redce{} falls}
Under the onslaught of the \hs{Geican} and \hs{Dark Crescent} armies, \hr{Redce}{\Redce} finally falls. 

In the end, Ramiel has to fight a boss monster: 
\Matriarch{} \hr{Dominice}{\Dominice}, a really badass Redcor mage. 
%, who is a Scion of the \Malach{} \hr{Eryal}{\Eryal}. She is older and more experienced that he, and knows more of her true nature and power. She might not be a \sathariah, but he cannot wield his full \sathariah{} power yet. 
She is far older and more experienced than he, and while a mere \human, she knows a lot about him and knows spells that can counter his \resphan{} powers. 

%She actually defeats Ramiel. But he is not quite dead. She becomes overconfident, and he rises to strike her down. Compare to Wismerhill from \FLuneNoireVol{10-11}. 
Ramiel knowingly holds back and lets \Dominice{} defeat him and \emph{almost} kill him. 
%\Dominice{} defeats Ramiel, almost killing him. 
He contacts \Belzir{} and requests that she use her power to keep him alive. 
She cannot afford to refuse. 

Meanwhile, \Dominice{} has become overconfident. 
He rises to strike her down. 
He kills her, then eats her and absorbs her power. 

Have a bloody scene where he tears out her heart, brain and liver and eat them. 

% He insisted on facing her alone because he wanted to eat her alone. 
% This gives him the strength he needs to face \Belzir{} and betray her. 
% Also, he has forced \Belzir{} to deplete her strength to heal him. A dangerous \trope{XanatosGambit}{Xanatos Gambit}, but Ramiel has always been reckless. 
This was a part of Ramiel's plan: 
He let himself be wounded, thus forcing \Belzir{} to pour her power into him and depleting her own strength to heal him. 
Now \Belzir{} is weakened, while he, having eaten \Dominice, is strong.
A dangerous \trope{XanatosGambit}{Xanatos Gambit}, but Ramiel has always been reckless. 












\subsection{The Resurrection} 
\target{Shiaraid dies}
Ramiel makes Shereid his willing sex slave, and together they plot to usurp the Dark Queen. 
Ramiel is bitter at \Belzir{} for treating him badly. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Ecstasy Arise%
}{
  I've learned to cry and crawl away\\
  But at the closing of our circle you will pay\\
  I see the hope vanish in your eyes\\
  I feel the ecstasy in me arise
}

\Belzir's resurrection is a ritual performed by many mages. 

She must be reborn through a \human{} body. 
So a young, healthy, beautiful Royalist woman (named Shadira or somesuch) willingly sacrifices her body and soul to her beloved queen. 

Carzain and Shereid plan to interrupt the ritual and drain \Belzir's power. 
In order to do this, they must have their own agents participating in the ritual in the key spots. 
So they begin to subvert other members of the Royalist Faction to their cause. 
When the war progresses and the day of the resurrection nears, they take measures to assassinate the mages that have remained loyal to \Belzir, so that they may control the ritual. 

At the end of the story, there is a big ceremony to resurrect the Queen, in which Carzain must channel her power through the orb. 
But he betrays her by smashing the orb, thus keeper her power for himself. 

After this, Carzain sets himself up as \caliph. 
But unbeknownst to him, \Belzir{} is not destroyed. 
After the betrayal, she contacts a group of Royalists in Geica, who (hidden from Carzain) were prepared to take over the ritual if anything should go wrong. 
They succeed, and she is resurrected. Some of the Royalists side with Carzain. 

Hayad and his children are among the Royalists who side with \Belzir. However, after a while Hayad notices that \Belzir{} is becoming dangerously insane. 
One night, she tortures and kills a lover who fails to satisfy her sexually. 
Hayad, fearing that he is next in line, flees to join Carzain. 





\subsubsection{\Shiaraid{} dies}
So Carzain and \Belzir{} clash and fight.
And in the end he is victorious. 
He not only kills her, but also \hr{soul-eating}{consumes her soul}. 

She fights back. 
It is a hard battle. 
Ramiel is in danger, so he has to draw really fucking deep of the power within his \carcer. 
He digs deep into his inner darkness in order to unleash as much as he possibly can of his wicked \sathariah{} power. 
He forces the souls within his \carcer{} to submit and serve him. 
This is tough, because there are immortals in there. 
Even \dragons. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Shadow Self%
}{
  Blood on a legion of nameless shores, I beseech you!\\
  Skill of a thousand nameless whores, I invoke you!\\
  Holding the light away\\
  Twisting in my mind
  
  Love of a legion of begging slaves, I exalt you!\\
  Screams of a thousand burning souls, I unleash you!\\
  Holding the light away\\
  Twisting in my mind\\
  Into the shadow's waking eyes
  
  Power of a legion of nameless lords, I command you!\\
  Locks of a thousand nameless doors, I unlock you!\\
  Lash of the six soul-taking strokes, I will feed you!\\
  Twisting in my mind\\
  Into the shadow's waking eyes
  
  \quo{Spiritus Pervertus Nymph}\\
  \quo{Spiritus Pervertus Femme}\\
  Twisting in my mind
  
  I know he steals, my body is haunted\\
  Wicked voice in my spirit has control\\
  Blinded by the beauty of my darkness\\
  Makes me fly, takes me higher
  
  I invoke thee, blackened lord.\\
  Night begins to crawl the skies\\
  Kneel before your master, shadow self\\
  Taste the pain caressed by chains
}

But in the end, \Shiaraid/\Belzir{} submits and lets him kill her, like \hr{Silqua dies}{\Aryal{} once let \Shiaraid{} kill her}. 
For a number of reasons:
\begin{enumerate}
  \item 
    \Shiaraid{} feels guilty over having killed and eaten her (submissive) lover, \Eryal, so she feels she deserves to have her new (dominant) lover do the same to her. 
  \item 
    \NexagglachelsCurse{} makes her self-destructive and suicidal and emo. 
  \item 
    She is very sad because \Mystraacht{} is in turmoil and has been tearing itself apart from the inside for thousands of years. 
    \Mystraacht{} is her father's legacy, so she is strongly attached to it and wants it to live and be strong. 
    She has almost motherly feelings towards her dynasty and will sacrifice herself for it.
    When she lets Ramiel absorb her power and unify it with his own, \Mystraacht{} will be one step closer to uniting and restoring its former glory. 
    
    After all, \ps{\Zachirah} great strength as a leader derived partially from the fact that \hr{Zachirah's slave Resviel}{his \resviel{} submitted to him}. 
    That made him the ultimate alpha male, respected and envied by all. 
    \Shiaraid{} hopes that if she submits to Ramiel and lets him eat her, it will make him (in some small way) a new \Zachirah. 
\end{enumerate}

She feels she deserves to die for her wicked \sathariah{} lusts.

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  He only will grasp me aright \\
  whose heart holds a wound that is an incurable wound,\\
  Who never, for anything, in any way, would be cured of it\ldots{}\\
  And what man, if so wounded, \\
  would ever be willing to \quo{die} of any other hurt?
}

In the end, she is a little bit happy. 
Now she can be sort of reunited with \hr{Shiaraid and the ghost of Eryal}{the ghost of \Eryal}. 
Previously, \Eryal{} had been locked away in \ps{\Shiaraid} \carcer. 
Now they will both be absorbed into Ramiel's \carcer. 
This is as close as they can come to a reunion. 

She tells herself that by sacrificing herself she has atoned for her crimes against the world, against \Eryal, and even against Ramiel. 
She has done what she thinks \Eryal{} would have wished. 

\begin{prose}
  \Shiaraid:
  \tho{Ramiel is saner than I.
    In all my life I did nothing but harm with my tremendous powers, but now, in Ramiel's hand, my powers can perhaps do some good.}
\end{prose}

She is also happy to be free of the burden of her \carcer, and all the loathsome undead souls haunting her. 
Now it is up to Ramiel to carry that burden. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  When struck I rise\\
  I'm finally free\\
  Mark the bitter tear descending\\
  No more heavy burden\\
  And this is my eternal music
}


Her last words to Ramiel are: 
\begin{prose}
  \ta{%
    Promise me you will reunite \Mystraacht{} and make it strong and mighty again!
    You now have me inside you, and with me the last remnants of \ps{\Zachirah} bloodline.
    That makes you his true heir. 
    And our last \sathariah.
    
    You are the only one!
    \ps{\Mystraacht} future rests on your shoulders, Ramiel.
    \ps{\Zachirah}, \ps{\Nathrach} and mine. 
    We all live on in you now. 
    You are all of us. 
    You carry our hopes, dreams and legacy. 
    You are the soul and heart of \Mystraacht!}
\end{prose}








\subsubsection{\ps{\Shiaraid} tragedy} 
\hr{Shiaraid's tragedy}{\ps{\Shiaraid} tragedy} is \NexagglachelsCurse, which forces her to destroy herself and those she loves. 
For she genuinely loves Ramiel. 

When she finally perishes, it is \ps{\Nexagglachel} revenge. 
She imagines she hears him laughing inside her head, mocking him as she once mocked him in his captivity. 
She hates him, but still some part of her recognizes the justice in it. 





\subsubsection{Ramiel is sad}
\target{Ramiel blames both sides for the tragedy}
Ramiel is victorious, but his victory is bittersweet. 
He is somewhat sad. 
He loved \Shiaraid, and now he has betrayed her. 
He repents. 
He knows it was the Curse that turned them against one another. 

He tries to tell himself it is justice, because \Delphine{} \hr{Silqua dies}{did the same to her beloved \Aryal}, and \Shiaraid{} also \hr{Shiaraid betrays Zachirah}{turned her back on \Zachirah}.
But he cannot convince himself. 

The affair leaves him bitter and disillusioned, and he becomes more evil and brutal. 

He also speculates that maybe it is just and natural for him to kill and eat her. 
After all, it is inherent in the nature and purpose of the \resphain{} to be \hr{Shiaraid betrays Zachirah}{parasitic and consume one another}. 
But that doesn't make it any better. 
He concludes that both sides in the \hs{Feud} are to blame for this tragedy: 
The \banelords{} for having bred the \resphain{} into the destructive things they are, and \Nexagglachel{} and his \dragons{} for having twisted them further. 
He grows to hate both sides more. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Section X%
}{
  Blood on my fingers\\
  Night in my soul\\
  Your breath I will hear no more\\
  I'm slowly growing cold\\
  Your eyes are open\\
  Dead to the light\\
  I hear my soul cry\\
  On the wings of death I ride
}

Eating \Shiaraid{} strikes Ramiel as a hard blow, not just psychologically, but also physically and metaphysically. 
She is a humongous soul: 
\Sathariah{} and \malach, carrying behind a huge \carcer{} of her own. 
It is difficult to gulp her down. 
Her \carcer-souls attack him and haunt him. 
He has to struggle to subdue them. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Section X%
}{
  Hunting the shadows\\
  Knowing they are one\\
  Whispering voices\\
  They stalk me through the dark\\
  My eyes are open\\
  Black, all is black\\
  I am desperately cold\\
  And upon my knees I crawl
}






\subsection{Ramiel is closer to regaining himself}
Ramiel's betraying \Belzir{} and draining her power\dash perhaps even eating her flesh\dash is a key step towards regaining his full power. Remember, \hr{Resphan power and hunger}{a powerful \resphan{} needs to eat}. 

By absorbing her, he is able to \quo{inherit} some of her knowledge. 
He also absorbs her \hr{Fragments of Nexagglachel}{\Nexagglachel{} fragment}, making him \hr{Ramiel is overpowered}{\uber-powerful}. 

\lyricslimbonicart{As the Bell of Immolation Calls}{
  A black heart will adorn\\
  the wings when I'm reborn.\\
  Engraved on my memory\\
  is whom hatred made me.\\
  The ravages of time.\\
  Battles on in my mind.\\
  There are still wounds that bleed\\
  deep in the soul of mine.
  
  I behold the beginnings of sorrow\\
  and predict the omens of cruelty.\\
  In the plague's shadow I follow,\\
  as tormenting winds sweeps\\
  through the cathedral halls,\\
  as the bell of immolation calls.
  
  In embers of infernal greed,\\
  feeding the fires unholy.\\
  Apocalypse was born\\
  when hell brainstormed through me.
}

















\section{Random ideas}









\subsection{Things to remember}
Remember that the books should not be too \human-centered. 
Have more focus on the \scathaese{} societies. 
This book should have lots of focus on the Rissitics and Imetrians. 
Perhaps even with Carzain as a mere subplot. 









\subsection{The \xzaishanns{} and the deepest Chaos}
Remember to have references to the \xzaishanns{} and the deepest recesses of Chaos, from which the \dragons{} draw their power. 

Compare to the First Warren of Starvald Demelain in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}.

Have references to \quo{the blood of the \xzaishanns} and \quo{the power of the \xzaishanns} and \quo{the legacy of the \xzaishanns}. 









\subsection{\Malcur becomes a myth}
After the fall of \Malcur, the city rapidly becomes a myth. Some months later, people have almost forgotten it. 
The talk is that the city has been eaten by the \Wylde{}, but people are forgetting when it existed\dash it's already categorized as \quo{the far past}. 

Soon, people look at you as if you're mad or a liar if you claim to have been there, or even be from the city. 
This is self-enforcing: 
It makes people question their own memories, repress their memories of having been there, until their minds make up a fake past to cover the fact that they're \Malcurian. 









\subsection{A sexy girl}
In this book or in one of the next, maybe I should have as a main character a sexy girl who regularly gets owned, dominated, humiliated and sexually harassed by other characters, villains and heroes alike. 





\subsubsection{Erotic scene with girl being killed}
Have an erotic scene with a girl being stripped naked and killed. As in the movie \emph{House of the Dead}. 










\subsection{Sentinels battle to the death}
Have a scene where Sentinels (\rachyth?), servitors of \Secherdamon{} or \Vizsherioch, fight to the death in ritual combat. This is a ceremonial contest, where the winner will be granted great power and status. 

Inspired by one of the early episodes of the tokusatsu series \emph{Go Go Sentai Boukenger}, where \Ryuuoun{} has some of his \Jaryuu{} Tribe battle to the death for the \honour of being selected and transformed into a \Daijakuryuu, a powerful monster.







\subsection{Expedition to the lost \Dragonland}
Have a short excursion to \Dragonland, the lost realm of \dragons. Perhaps \Nzessuacrith{} or another major \draconian{} character. 







\subsection{Betrayal}
I need to have a character who seems good and nice and dandy, helping out the heroes. But in the end, he betrays them, and it turns out he was evil all along. 

Compare to the priest Father Soren from the movie \cite{Movie:GargoylesRevenge}. 
At the end it becomes apparent that he was actively working to help the gargoyles awaken. 







\subsection{Someone is betrayed and imprisoned}
Someone is betrayed and taken prisoner. By whom? The Redcor? Or the Rissitics?

And who? Perhaps Carzain, but perhaps rather someone else. I have enough Carzain material already. 

Anyway, the prisoner awakens some kind of inner power, perhaps one that had previously lain dormant and hidden. He/she strikes back and causes great destruction. 

Compare to the scene in \authorseries{Robert Jordan}{Wheel of Time} where Rand al'Thor is taken prisoner and stuffed in a chest by the Aes Sedai. Or a scene in volume 2 of \FLuneNoire{} where Wismerhill is captured by a wizard who wants to drink his blood. 







\subsection{A \succubus{} shows people illusions}
\index{\succubus}%
A \hr{Succubus}{\succubus}-like monster, or group of monsters or villains, lurk in the Topaz \Chateau{} in \Redce{} and lures people in, to devour or to capture for later use.







\subsection{\Dzasselid-tachi fight for good}
\Dzasselid{} and \Narkiza{} and the rest still fight for \Nechsain, but they try as best they can to bend it in a good direction, to work for a kind of \quo{Rissitism with a \human{} face}.

Compare to lots of good guys in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}, and maybe \authorseries{Michael Moorcock}{Elric of \Melnibone}, where Elric serves Arioch but tries to subvert him. 







\subsection{Ilcas and \Narkiza}
Telcastora Ilcas and \Narkiza{} meet. 
They criticize each other's countries and religions. 

\begin{prose}
  \Narkiza: 
  \ta{Yous sword drinks blood. (Subtext: That is evil.)}
  
  Ilcas: 
  \ta{I am a warrior. 
    I kill my enemies. But I have never killed an innocent.}
  
  \Narkiza: 
  \ta{Innocent how?}
  
  Ilcas: 
  \ta{Give it up. 
    You are trying to get me to doubt my religion and my cause. 
    That is \emph{not} going to happen.}
\end{prose}








\subsection{Someone is overly philosophical}
Some dude is being overly philosophical and sees symbolism everywhere. A wiser character (\hs{Criseis}{\Criseis}?) calls how down on it. 

\Criseis: \ta{Dude, knock it off. Understand this: The world is not full of symbols. The world is not full of meaning. The vast majority of what goes on in the world is due to chaos, chance, meaninglessness. I have lived twenty thousand years. I know this.}

Lamer: \ta{But I am \emph{giving} it meaning, here in my head!}

\Criseis: \ta{Then let it stay inside your head. And know that the world is infinitely larger than your head, and it cares nothing for how you \quo{interpret} it, how you \quo{give it meaning}.}







\subsection{Cool conversations with \Ishnaruchaefir}
\subsubsection{Immortality}
Someone comments that immortality must suck. 

\hr{Ishnaruchaefir}{\Ishna}, or \hr{Criseis}{\Criseis}, or another immortal: 
\ta{Hell no! If immortality sucked I would have killed myself long ago. Immortality owns ass!}

Subvert the trope \trope{WhoWantsToLiveForever}{Who Wants to Live Forever}.





\subsubsection{Peace with my past}
\Ishnaruchaefir: \ta{I have long since made peace with my past.}

\Criseis: \tho{You lie, my lord. You have never made peace. I see it, deep in your eyes. You merely hide it well and have developed skill at ignoring insults.}





\subsubsection{Fallibility}
\Ishnaruchaefir: \ta{Acknowledge my own fallibility? Ha. I think not. Perhaps in another ten thousand years.}







\subsection{A villain disses the younger races}
A Cabalist or Sentinel is accused of being evil. He does a long rant (perhaps a \trope{HannibalLecture}{Hannibal Lecture}) about how the younger races have not only inherited all of the elder races' evil, but also made it worse through stupidity. 

The elder races were and are cruel, true, but theirs is a cultured cruelty, evil with a purpose, intelligent malice. The evil of the younger races, on the other hand, is petty, vicious and, above all, senseless. Where they act there is more waste, more chaos, more senseless destruction and suffering. 

He recites many examples of how \humans{}, \scathae{} and \meccara{} are capable of horrible crimes, completely on their own initiative. This includes all kinds of people: The downtrodden Shroud slaves, the nobles who are still Shroud slaves, the enlightened who fight in the \secretwar, and those few who try to subvert the \secretwar. All of them commit terrible crimes, for what they believe is right, or for no reason at all.







\subsection{Social interaction sucks}
Someone, perhaps Carzain, or even \Ishna, complains about social interaction and all of the hypocrisy which is a necessary part of it. It stems from Carzain's being tired of running political games in Geica.







\subsection{Someone discusses sorcerer-kings}
Have some high-up villain comment on the subject of \hr{Sorcerer-kings}{sorcerer-kings}, and why there are not more of them. 







\subsection{\Ishnaruchaefir{} berates a whiner}
\Ishnaruchaefir{} is talking to someone who whines. He berates him: 
\ta{Get over it. 
  I have suffered more than you ever will. 
  For ten thousand years. 
  So do not come whining to me.}






\subsection{\Banes{} were not the first invaders}
Someone remarks that the \banes{} were not the first aliens to invade \Miith. 
There have been others. 
The \xss{} were one such invading force. 
They \emph{won} and ruled \Miith{} for millions of years. 
But then they grew sleepy\ldots{}







\subsection{\Ishnaruchaefir{} fights during Nadir}
At some point in the series, I need to have a big, climactic event coincide with \hr{Ishnaruchaefir's Nadir}{\ps{\Ishnaruchaefir} Nadir}. 
He is weak, but forced to fight anyway, and not through a \XanatosGambit{} of his own this time (unlike that time with \Teshrial). 

This new Nadir is much worse than the previous one (during \TwilightAngelRememberEmph). 
The \hs{Nadirs get worse}, remember.








\subsection{A \bane{} talks about viruses}
A \bane, perhaps even \Daggerrain: 
\daggerrain{%
  There exist diseases that spread (like viruses). 
  (\Daggerrain{} knows what a virus is, but the listener would not know, so he has to explain.) 
  You \humans{} are the same in the way you spread all over the world, destroying and enslaving the land around you. And yes, we \banes, too, are the same, only on a \cosmic{} scale.}

Or\ldots{} maybe the \banes{} are not the virus. Maybe everything else, such as the \dragons, is the virus, and the \banes{} are the cosmic antibody, created to scour the infestation of life from the universe. See section \ref{Banes as an antibody}. 







\subsection{\Vizsherioch}
\subsubsection{\Rathyon{} and \Vizsherioch}
\hr{Rathyon}{\Rathyon} meets \hr{Vizsherioch}{\Vizsherioch}. 

\Vizsherioch: \ta{Greetings, nephew.}

\Rathyon: \ta{\quo{Nephew}? Who are you?}

\Vizsherioch: 
\ta{You do not know me? 
  I am \Vizsherioch, son of \Secherdamon.
  I am the \xss{} given flesh!}

\Rathyon: \ta{\quo{\Vizsherioch}? That does not sound like much.}

\Vizsherioch: 
\ta{[Smile.]
  I need to litany of names. \Vizsherioch.
  Speak my name. 
  Hear it.
  Perceive its Aenigma.
  And you will understand.}





\subsubsection{\Ishnaruchaefir{} and \Vizsherioch}
\Ishnaruchaefir{} meets \Vizsherioch{} for the first time. 

\Ishnaruchaefir: 
\ta{Aaah. 
  So \emph{you} are the new \vertex{} I sensed in \ps{\Secherdamon} constellation.}







\subsection{Immortals curse the Shroud}
Some immortals curse the Shroud. 
It makes them stupid and forgetful and \hr{Shroud represses technology}{represses technology}. 






















\chapter{\RamielsAwakeningBook}















\section{Concepts}









\subsection{Ramiel and Hayad}
After Ramiel betrayed \Belzir, Hayad remained his friend. 

But Hayad is Sentinel-allied, and Ramiel goes to join the Cabal. 
How does that work? 

I guess Hayad will die at some point, so Ramiel won't be forced to turn on his friend. 







\subsubsection{The \Bane{} Invasion}
%After defeating \Belzir{}, Carzain fights some Rissitics and some \banes{} sent by Rissit. But eventually, it becomes apparent that the \banes{} have their own agenda. 

After this, Carzain discovers that he and \Belzir{} have been manipulated by the Sentinels. He becomes angry and leaves them. 

Perhaps he travels the world for a while now, fighting for whatever cause catches his fancy. Kind of like Elric of \Melnibone{} in his mercenary years. 

Somehow, he meets the \banes. Perhaps he is taken prisoner by them. They show him how all morality is a lie, how everything in the world revolves around the struggle between \dragons{} and \banes. They convince him that, as a \Malach, he is created by the \banes{} and destined for greatness as a hero on their side. 

At this point, Carzain has encountered several different civilizations and their different moralities, and has found them all lacking\dash{}totalitarian, intolerant and contradictory. He has also read snippets of the Book of Nom, strengthening his growing suspicion that good is futile. He is near to concluding that everyone is a hypocrite, that all morals are false and that the only truth is power. 
After being shown the brutal truth by the \banes, he becomes completely disillusioned and turns to evil completely. (Perhaps it is his already high degree of disillusionment at this point that lets him keep his sanity when confronted with the truth.) 
%Carzain, completely disillusioned, abandons all his former morals and turns to evil completely. 
He abandons the name Carzain \Shireyo{} and becomes Ramiel (his \Malach{} name). 

Later, he learns that the Redcor, or at least some of them, are on the Cabal's side, and that he will have to work with them. He balks until he is reassured that he will not be put under them but beside or above them. 

%The Cabal betrays \Belzir{}, and it turns out that they actually serve the \banes. 

%Late on in the story, Carzain and a party of other heroes go on a quest to destroy some \banes. It comes to a big boss fight, but in the end, one of the heroes betrays the party and turns on them. Carzain dies. %, and the \banes conquer \Velcad{}. 

%The \banes{} conquer \Velcad{}. The Imetrians and Rissitics team up with Irokas to oppose them. I don't know what happens after that. (A nice evil ending might be to have \Tiamat{} awaken and destroy \banes{} and \dragons{} alike\ldots{}) 





\subsubsection{Ramiel's companions}
Maybe Ramiel has a female companion. 
Compare to Mele from \emph{\JuukenSentaiGekiranger}, with Ramiel (of course) being Rio. 

Perhaps he gathers \vorcanths{} and other creatures around him and forms his own \Rinjuuken. 









\subsection{Ramiel's enemies}
\target{Secherdamon wants to off Ramiel}
Ramiel had managed to keep his existence secret from the Sentinels for a while, but no longer. 
After he killed \Shiaraid, he could no longer hide. 

\Secherdamon{} is not happy about this new development. 
He liked \Shiaraid{} because she was so mad. 
She was dangerous to him, true, but he suspected she would be just as dangerous to the Cabal. 
But Ramiel is another matter. 
\Secherdamon{} does not know how \malach-hood and the Curse have affected Ramiel, but he remembers Ramiel as a formidable and competent adversary. 

So \Secherdamon{} decides he wants to off Ramiel. 
Throughout this book, therefore, Ramiel is hounded by Sentinels and Cabalists alike. 

Fortunately, Ramiel has allies: 
\Cishiel, \Azraid{} and the \vorcanths. 





\subsubsection{\Azraid{} helps Ramiel}
\Azraid{} \hr{Azraid protects Carzain}{has his own plans for Ramiel}, so he protects him. 
He also subtly guides Ramiel on his quest and pokes him in the direction of the things he might need to regain his power. 

In this way, \Azraid{} acts as a \trope{StealthMentor}{Stealth Mentor} to Ramiel. 

When Ramiel finally learns of \ps{\Azraid} involvement, he is amused and slightly grateful, but not surprised. 
That is the kind of thing \Azraid{} has always done. 








\subsection{\Sithiyacaan}
Introduce \hr{Sithiyacaan}{\Sithiyacaan}, the last \hr{Kezerad}{\Kezeradi} lord. 







\subsection{The \Feud}
\target{Resphain are winning the Feud}
From the \Shrouding{} and up until this time, the \feud{} had been pretty much a war of attrition. 
And the \resphain{} were winning. 
Their numbers were dwindling, true, but the \dragons{} were dwindling faster. 
Besides, those \resphain{} who survived were the strongest, \hr{Resphain grow stronger}{and they kept growing stronger}. 







\subsection{To break or preserve the Shroud}
\target{To break or preserve the Shroud}
The \dragons{} originally created the Shroud. They did not care for progress. The \resphain{} \emph{do} care for progress, so they want to get rid of the Shroud. But they are afraid that it will give their \draconic{} foes access to more \xsic{} power, so they will not unravel the Shroud before their \matrix{} has control. 

Both \Daggerrain{} and \Secherdamon{} plan to sunder the Shroud and bring in their forces to lay waste to \Miith{} (see section \ref{Daggerrain's master plan}). For both parties, this is \hr{Summoning the XS: A deadly balance}{a delicate balance}.

Our \quo{heroes}\ldots{} wait, who are our heroes? \Narkiza{} and \Dzasselid? Moro \Cornel? \Cuezcans? Imetrians? \Ophidians? Remnants of the Redcor and Geicans?

Anyway, our heroes initially want to destroy the Shroud and free the people of \Miith{} from its cruel oppression and their imprisonment as witless slaves and defenseless victims, easy prey for all the horrors that lurk in the universe.

But towards the end, it becomes apparent that unravelling the Shroud is not a good idea. It will enable \Daggerrain{} or \Secherdamon{} or both to carry out their plan, and whoever wins that struggle in the end, the consequences for \Miith{}'s inhabitants will be cataclysmic. So the heroes realize that, hateful as it may be, if they wish to protect \Miith{} they will have to fight to preserve the Shroud.

\target{Ishnaruchaefir fights to preserve the Shroud}
\Ishnaruchaefir{} helps them, but only in secret at first. Later he openly declares his opposition to \Secherdamon{} and overtly fights against him. Perhaps he becomes a leader of sorts for the opposition, like Elric in Michael Moorcock's \emph{Stormbringer}.

\Ishnaruchaefir: 
\ta{%
  A balance has reigned over the \Matrices{} of the \Feud{} for thousands of years, but it is slipping. 
  The \banes{} are gaining strength. 
  I cannot have that. 
  There are times when I have held a stalemate preferable to any end to the war. 
  But if any side is to win ascendancy, I want it to be my own people.}

The whole picture of alliances is very chaotic at this point, with factions splintering and turning on each other at the drop of a hat.

Remember to have some sad philosophy about how tragic it is that while the Shroud is a wicked abomination that keeps people down as ignorant slaves and hapless victims of the world around them, the same Shroud is still the world's best defense against all-out invasion and another apocalypse. 
The heroes have to fight to keep the world as a prison. 





\subsubsection{Mortals fight against \iquin}
Some mortals have learned the evil purpose behind \iquin. 
They fight to stop it. 

Describe \hr{How it feels to learn Iquin is evil}{how it feels to learn that your religion is really evil}. 









\subsection{The final purpose of the \Sephiroth}
The \hr{Sephiroth}{\Sephiroth} have \hr{Final purpose of the Sephiroth}{a grand purpose}. 
It ties in with the \hs{Morbus} and the \hr{Purpose of Humanity}{purpose of \humanity}. 







\subsection{\Kezerad}
But the \hr{Kezerad}{\Kezeradi} are a danger to the \Sephirah{} project. They could potentially break the project, because they still have a \hr{Kezeradi telepathy}{deep connection to the \Sephiroth}.

By the end, some \Kezeradi{} have become main characters. Or at least one, namely \hr{Sithiyacaan}{\Sithiyacaan}, the last \Kezeradi{} prince. He and his followers work together with \Ishna\dash to some degree at least, although \Ishnaruchaefir{} was never exactly a friend of \Kezerad. 

The Cabal knows that the \Kezeradi{} have the power to fuck up their plan, so they do everything they can to hunt down the survivors.





\subsubsection{An undercover \Kezeradi}
A long-running \resphan, perhaps \Achsah, turns out to be an undercover \Kezeradi. Perhaps she is half \Kezeradi{} and openly condemned her heritage while secretly sympathizing with her people.









\subsection{Epidemies ravage \Azmith}
Epidemies ravage all of \Azmith, now that the \Iquin/\hr{Morbus}{\Morbus} plan is nearing its culmination. 
Entire countries are depopulated and collapse. 

It is a consequence of the life-drain inflicted by \Iquin, and also a side effect of the growing influence of the \banelords and their Entropy.
Disease is a manifestation of Entropy.

\citebandsong{Nile:AmongstheCatacombsofNephrenKa}{Nile}{
  Pestilence and Iniquity:
}{
  Heralds of Pestilence\\
  Blackest Plague Rusheth through the Land\\
  Burning Evil Winds\\
  Carry Sickness\\
  Invoking the Bitter Venom of the Gods

  Loathsome Sickening Stench of the Defiled\\
  A Cesspool Breeding the Unclean\\
  Hordes of Locusts\\
  Fiends of the South Winds\\
  Cleanse the Earth from the Impure

  The Daemon That Siezeth the Body\\
  The Daemon that Rendeth the Body

  Ruthless and Profane\\
  Lord of all Fevers and Plagues\\
  Grinning Dark Angel of the four Wings\\
  Spawn of Eng\\
  Horned God with rotting Genitalia\\
  Pazuzu
}









\subsection{Cataclysmic events}
There should be some apocalyptic events before the last book of \SentinelsofMithEmph where much of \Azmith is devastated and the truth of the \xs, \Iquin and perhaps even the \banes is revealed to the mortal masses. 

Hordes of Chaos and/or Darkness invade \Azmith, like in the \emph{Warhammer} game. 

The surviving mortals suffer.
They know their world has been destroyed and they are now living in a Hell on Earth.

\citebandsong{Nile:FestivalsofAtonement}{Nile}{
  Extinct
}{
  Paradise Lost\\
  Dreaming of Extinction\\
  We wander through the Walls of Sacrifice\\
  Sick winds brush against my Skin

  Power of Extinction\\
  Growth Intelligence No More\\
  Mud Rot Skeletal Earth\\
  Drown thy spirit of Kings

  Society's walls break Down\\
  \Humans Pound Down\\
  Dig I must dig Out\\
  Surviving puts all tools in Place\\
  Only peace comes in Death

  As I sleep I dream of Death\\
  Only Peace comes in Death
}









\subsection{Looming confrontation between Ramiel and \Dasteron}
Throughout the book, the upcoming conflict between Ramiel and \Dasteron looms. 
It is a source of tension. 
Everyone knows it will happen and is waiting for it to erupt. 
Compare to the promised battle between Karsa Orlong and Rhulad in \cite{StevenErikson:ReapersGale}. 














\section{Ramiel's Search}





\subsection{\Vorcanths{} are mad at Ramiel}
The \hr{Vorcanth}{\vorcanths}, previously Ramiel's allies, had grown mad at him. 
They liked \Shiaraid{} and were nonplussed that Ramiel had backstabbed and killed her. 
They demanded he make it up to them and do them some favours before they would help him again. 





\subsection{Ramiel searches moons for answers}
Ramiel searches the moons, hoping to find answers and peace from his inner Chaos (and \hr{Curse}{\NexagglachelsCurse}). 
Especially \hs{Visha}, the moon associated with the \hr{Vorcanth}{\vorcanths}. 

\lyricslimbonicart{Enthralled by the Shrine of Silence}{
  Cold jewel Moon, I found shelter in your shade \\
  as wind and time took me astray. \\
  I'm floating down the river of forgotten names \\
  into a dark and calm water that devours my flame.\\
  There I find rest and glorious peace, \\
  a sanctuary of eternal bliss.
}

\lyricslimbonicart{Seven Doors of Death}{
  Restless days and sleepless nights.\\
  Drawn in the direction of the moon.\\
  Infernal magnet to mysterious destiny,\\
  beyond the grave of doom.
}

He wants to be rid of his frail \human{} body and return to his true form. 

\lyricsbs{Hate Eternal}{I, Monarch}{
  In this being, in flesh, there can be no absolution.\\
  Therefore I must shed my skin, in a world so fabled, so false.\\
  
  In this shell, in flesh, there can be no solitude.\\
  I will not live in this facade, in a world of contradiction.\\
  
  I, Monarch, master of what shall be.\\
  I, Monarch, captor of what I seek.\\
  I, Monarch, victor of all battles.\\
  I, Monarch, sovereign of this domain.
}









\subsection{Ramiel sees through \Iquin}
Ramiel realizes the true nature of \iquin. 
He is himself a \carcer, and his growing self-understanding allows him to understand \iquin{} as well, and see it for the carcer it is. 

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega
}{
  Mass Grave Aesthetics
}{
  The dimension of ethereal totalitarianism discloses itself \\
  And takes possession of the quintessential human soul \\
  Like a nail hammered through most tender flesh \\
  Aeons separate the one \\
  whose eyes have seen through the night of the spirit \\
  The king, the Lord of hosts, draped in terrifying magnificence \\
  From the gleaming clot of trembling vermin
  
  This is you, nourishing \\
  the grand Mass Grave Aesthetics!
}









\subsection{Psychics see portents of the end of the world}
Gradually, as \ps{\Daggerrain}{} master plan unfolds (including the spread of the \hr{Morbus}{\Morbus}), psychics (people who can see through the Shroud) all over \Miith{} see portents of the end of the world: 
Death and emptiness, \hr{Morbus}{disease} and horror, Entropy and torturous decay. 









\subsection{Ramiel and \Ishnaruchaefir}
Ramiel meets \Ishnaruchaefir. 

\begin{prose}
  \Ishnaruchaefir:
  \ta{Ramiel. I hear you destroyed \Shiaraid.}
  (He studies Ramiel's reaction.)
  \ta{You loved her.}
  
  \Ishnaruchaefir{} fingers his glaive.
  He also destroyed his beloved once, remember. 
  A wordless \quo{\trope{NotSoDifferent}{Not So Different}}-conversation passes between them. 
  They go their separate ways with a newfound respect and mutual understanding. 
\end{prose}









\subsection{Ramiel meets \Cishiel}
\target{Ramiel meets Cishiel}
Ramiel is re-united with his long-lost daughter, \hr{Cishiel}{\Cishiel}. 
At first he does not recognize her. 
She was a young girl when he last saw her.
Now she has grown into a mature and very powerful \resvil. 

She has searched for him. 
She wants him back and will support his bid for the throne. 
But she also resents him for abandoning her to fend for herself back when she was a defenseless little girl. 

\target{Ramiel regains guns}
She gives him back \hr{Ramiel's guns}{\Strith{} and \Currah}, the two pistols he once used to wield. 









\subsection{Ramiel journeys to \UltimaThule}
\target{Ramiel journeys to Thule}
Ramiel sails north. 
He journeys to \hr{Thule}{\UltimaThule} in the hope of regaining his memory and power. 
His goal was a particular lost temple city in \UltimaThule that had once been a sorcerous bastion (of some race), but was now abandoned and ruined.
Perhaps this was even a \voyager citadel.

\lyricsbs{Bal-Sagoth}{%
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  For how long have we travelled?\\
  The memory grows dim, lost in the cruel, searing storm-winds.\\
  With the blessings of the Elders we began our journey, \\
  beyond the great veil of shadowed glaciers.\\
  They spoke of a prophecy foretold, an ancient and glorious legacy.\\
  A quest for the realm of legendry, \\
  lost to Man since before even the star-lords descended.
}

He gazes out over the vast, black sea and the darkened, stormy sky, dimly lit by a faint, mystic, spectral luminescence, from the clouds or the northern lights. 

Compare to \bandsong{Bal-Sagoth}{Journey to the Isle of Mists (Over the Sunless Depths of Night-Dark Seas)}. 

\lyricsbalsagoth{Invocations Beyond the Outer-World Night}{
  Seeking answers to the cryptic riddles of the universe,\\
  Secrets of the blackest, most impenetrable deeps of the umbra,\\
  Wreathed in frozen shadow and ice-bound peril,\\
  Subterrene halls of horripilated wonderment\ldots{}
  
  Tatsumaki Maru voyage north, ever north!\\
  Cleave a path through the massing Arctic ice!\\
  Agleam with all the \colours of the aurora,\\
  Far beyond Ny Alesund lies our goal.
  
  Wreathed in frozen shadow and ice-bound peril.\\
  Agleam with all the \colours of the aurora.\\
  The portal to the tenebrous cryptic core \\
  of this world's subterrene inner sanctums.\\
  Quaere verum\ldots{} \\
  Sic itur ad astra!
  
  Invocations and ideograms (dreams of the Xytaxehedron?),\\
  Conjuration of the inner world's (tenebrous) denizens,\\
  And their star-spanning progenitors, \\
  spawned beyond the outer-world night.
}

He feels deep inside him that he is nearing enlightenment. 

\lyricslimbonicart{Beneath the Burial Surface}{
  Water from a thousand tears floats in streams.\\
  The feeling from a thousand years flow over me.\\
  As I once again return to the cemetery gate\\
  I hear the dismal call from the hollow grave.
}






\subsection{I know you are in there somewhere}
In a fight or the like, someone tells Ramiel this: 

\begin{prose}
  Someone: 
  \ta{Carzain! I know you are in there somewhere!}
  
  Ramiel: 
  \ta{%
    Oh, no. You have gotten it mixed up. See, it was never Carzain who was \quo{in there}. Back in the day, Carzain was up-front, and I, Ramiel, was \quo{in there} within him.
  
    You cannot break through to the \quo{real me}. 
    I \emph{am} the real me.
    I am as real as I can get.}
\end{prose}







\subsection{A \resvil{} who loves and hates Ramiel}
Ramiel has an admirer and enemy. A \resvil{} who is in love with him to the point of obsession, but also hates him for his evil and his (in her eyes) betrayal of her people. Is she \Mystraacht{} or from another dynasty?

Perhaps I can merge her with Shereid. 

Have some scenes from her perspective, where she is disgusted with her own obsession. 

In the end, he probably kills her. Perhaps she willingly lets him kill her: Stripping naked for him, kneeling down to first suck his dick, and then letting him run his blade through her breast. 

Compare her to Titus Pettifer from Clive Barker's \emph{Jacqueline Ess: Her Will and Testament} (\emph{Books of Blood II} p.81-84). Or the relationship between Elric and Stormbringer in Michael Moorcock's \emph{Elric of \Melnibone} series\dash and maybe the scenes where Elric slays Zarozinia and Moonglum. 















\section{At the Temple}
\subsection{Ramiel reaches the temple}
\target{Ramiel's awakening at the temple}
\target{Ramiel's awakening in the temple}
Ramiel reaches the temple, far to the north. 





\subsubsection{First impressions of the temple}
It is a \Mystraacht{} citadel, but built in \ophidian{} style, since \Mystraacht{} has conspired with the \ophidians. It is not only a temple, but a cosmic gzateway to the Throne of the \Mystraacht{} Overlord, ensorcelled by \resphan{} and \ophidian{} power alike. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Swathed in Moon-frosts, in icy winds our blazon flying.\\
  Iron gleaming 'neath the stars, black skies ablaze with astral fire.\\
  White wolves (like silent spirits) haunt us, ever northwards.\\
  The ice-gem leads us, glimmering.\\
  Powerful spells entwine the shrine of legendry,\\
  mighty gates of frozen splendour looming.\\
  When the moon and stars shine as one upon the snows, \\
  the ancient ice-gate opens, the prophecy is fulfilled!
}

\lyricslimbonicart{Lycanthropic Tales}{
  As the storm looms over the frozen landscape:\\
  A call from the beginning of time,\\
  out of darkness through the mist.
  
  Requiem in blood and fire.\\
  Symbols of occult desire.\\
  Through the cosmic vortex,\\
  the gate to unknown darkness.\\
  An esoteric voyage to eminent discovery.\\
  I am the deathlike shadow,\\
  architect of black mysteries.
}





\subsubsection{They fight their way in}
He and his companions fight their way to the temple, past its terrible guardians. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Towering, ice-encrusted forms lumber forth from the freezing mist,\\
  their eyes shimmering with a fiendish, eldritch malevolance\ldots{}\\
  Our steel is raised against their weapons of gleaming crystal.\\
  And the virgin snow is rendered crimson by bloodshed 
  in a searing storm of slaughter.\\
  Wounded, dying, my flesh rent by weapons no human ever forged or wielded, \\
  I am beckoned forward by a strange, alluring force \\
  from beyond the veil of swirling mists\ldots{}
}





\subsubsection{They explore it}
He explores the mystic temple. 

\lyricslimbonicart{Infernal Phantom Kingdom}{
  After years of dormancy\\
  in a cosmic mausoleum,\\
  arcane cemetery.\\
  The soil is cursed and sour.\\
  A rotten landscape draped in horror.\\
  Evil has a way of returning.\\
  You can not hide from hell's eye.\\
  It is always burning;\\
  a way of returning.
}

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Shadows, images form \\
  in the glittering rune-carved walls of this glacial chamber,\\
  aecrets frozen within the timeless vaults of eternity.\\
  The throne of the time-lost ice realm, \\
  entwined in the mantle of such searing star-born power.\\
  This frozen, aeon-cloaked seat of immortal majesty,\\
  of an empire forged long before the vast seas rose in devouring fury!
}





\subsubsection{Insight comes}
Here he regains some of his memory. 
He remembers his life as a \resphan{} lord. 
He recalls the march of the \Mystraacht{} \hr{Glorious armies}{armies}, the incounterable legions that once forced the world to its knees. 
Back in those days, the \banes{} were weakened and mostly absent after their great defeat in the \secondbanewar{}, so the \resphain{} were left to their own designs, and they fought among one another. 
\Mystraacht{} was the most powerful dynasty, but they were betrayed, their Overlord assassinated, and they sank into the mire of civil war. 
(See section \ref{Mystraacht betrayed}.)

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  What shimmering swords raised in combat \\
  once sang with the glorious clamour of steel on steel?\\
  What splendid banners, billowing in the icy gales, \\
  once heralded the march of these invincible silver-clad legions \\
  to the blood-swathed embrace of epic battle?\\
  The glory of untold thousands of years past\ldots{} \\
  this ethereal legacy of mighty Ultima Thule.\\
  The frozen eyes of immortal kings watch me\ldots{} such a dark splendour!
}

Perhaps Ramiel reads the story of his people on the walls, like in H.P. Lovecraft's \emph{At the Mountains of Madness}. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  These ancient carvings in a time-veiled tongue,\\ 
  etched into the primeval ice countless aeons ago, \\
  now bathed in diaphonous incandescence \\
  by this storm of lucent stellar power, \\
  their mindsearing meaning at last becomes known to me.\\
  Their cosmic secrets unfold.
}





\subsubsection{Ramiel remembers his past}
Ramiel remembers the bloody wars he fought against other \resphain{} and against \dragons{} and \ophidians. 

He remembers fragments of \Ishna. The two have a history together. They are enemies, but respecting enemies. Almost like friendly rivals. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  And then, enlightenment comes, gleaming down upon my consciousness as the bright moon gazes down upon this auroral vista\ldots{} From my mind is lifted an obscuring veil, a veil induced by sorcerous arts, and I realize I have been merely a vassal of another's twisted will, a pawn in a game which is entwined in treachery and malign aspirations to thresholds of great power. 
  
  Such a traitorous web has been spun! The elders of my kingdom bow in obeisance to the vile priests of Xothan'kur, and it is their diseased machinations which have urged me here, to the very heart of the far-fabled ice realm\ldots{} for they seek to usurp the power of the Conjunction, stealing the vast energies of the Ice-Veiled throne and absorbing them into their own leprous, undead bodies, perpetuating the adoration of their abhorrent liege for countless ages, liberating his vile will and enslaving the realms of the world\ldots{}
}

He invokes \banes, \xss{} and cosmic gods. 

\lyricsbs{Hate Eternal}{Beyond Redemption}{
  Awaken from below I call thee,\\
  thy master pure in darkness,\\
  the one of hate before thy paths\\
  were chose to be forsaken.\\
  From depths of time in portals,\\
  through empty eyes of light,\\
  I searched the texts for knowledge.\\
  Now I bleed the sacrifice.
  
  I am of purest power. \\
  Strengths of a thousand souls.\\
  I hear the voices of\\
  the oldest ones burning within.\\
  Reveal the truth unto me, \\
  for I'll command the worthy.\\
  March through the ruins of diminished tribes.
}

He swears to retake the throne and reclaim power. 

\lyricsbs{Hate Eternal}{Beyond Redemption}{
  I summon winds of fire.\\
  I summon winds of disease.\\
  I summon torture upon\\
  all my rivals who shall bleed.\\
  Confronting all before me\\
  to tempt what I have in store.\\
  Don't tempt my fury for\\
  the flames shall burn eternally.
}







\subsection{\Azraid{} begins stockpiling \Erebean{} power}
\target{Azraid stockpiles Erebean power}
\Azraid{} sees portents (mystic or mundane?) that the \banes{} are reeling and about to be defeated. So he begins stockpiling \Erebean{} power, draining it away from \Erebos{} and the \banelords{} and hoarding it for himself. This is effective, because \Daggerrain{} is not expecting \Azraid{} to betray him. \Azraid{} has always been one of the most loyal \resphain. 

Remember to have subtle references to \ps{\Azraid} evil hand in all \Azraid{} chapters. 







\subsection{Ramiel is still bound}
Even after his enlightenment at the \Mystraacht{} temple, Ramiel is still bound. He is not entirely free of the Shroud, still trapped in a \human{} body, and without access to his full \sathariah{} power. He has a lot of power now, but he does not completely understand it. 

And not only that: He is under the effect of spells that chain his mind. He has enemies who want to manipulate him, use his power as a weapon of their own. They don't want him to awaken completely. Ultimately, they want to use him in their plan, where he is to expend all his power and be destroyed himself. Perhaps they plan to directly usurp his power, absorbing it for themselves and destroying him\ldots{}

No! Better idea: They want to create a new kind of \Sephirah, a more powerful one, but under their control. They want to transform Ramiel into one such. In order for that to work, he must be awake and have access to his full \sathariah{} power\ldots{} but he must awaken while under their control, so that immediately upon his awakening, they can chain and spellbind him and transform him into their new \Sephirah. 

Perhaps this is connected to the destruction of the original \Sephiroth. Perhaps Ramiel is to become the first of a new generation of \Sephiroth{} that will take over once the current ones have served their purpose. 

At any rate, Ramiel learns too much at the temple. Or, rather, he has learned too much before he came to the temple, so he is able to piece together more of the big picture than they expected him to. He suspects their scheme and takes active measures to undermine them, lay traps for them, infiltrate their ranks, so that in the end, he will be stabbing \emph{them} in the back. 







\subsection{Ramiel's enemies}
Ramiel has \hr{Ramiel's enemies}{enemies among the \resphain}. 
Have a Scabandari Bloodeye-like character. 







\subsection{Ramiel is broken down and rebuilt}
\target{Ramiel's final awakening}
He has regained much of his memory, but he is still trapped in the Shroud and must break free and be reconciled with his true self before he can regain his true \resphan{} form and his \sathariah{} power. 

He undergoes several mental torture. I don't know if this is voluntary or if he's trapped and imprisoned. Anyway, his Shrouded personality must be torn apart and broken down before his true self can re-emerge. 

\Cishiel{} and \Gilchad{} help him. 

Ramiel does not like \Gilchad. 
He is an obnoxious, condescending snob. 
He thinks he is smarter than everyone else and does not give Ramiel the respect he thinks he deserves. 

During the process of Apotheosis, Ramiel gradually comes to remember all the bits of cosmic knowledge he has gleaned over his many lives, the many Aenigmata whose Gnosis he has glimpsed. 
Back then he usually understood very little of it, but now, with the full knowledge of his many lives, he is able to see this knowledge from many exciting perspectives, and suddenly it all makes sense.
So immense amounts of horrid, sinister insight crash down upon his mind like a tidal wave.
With his multi-faceted experience he is able to understand much more than he otherwise would.
He attains Gnosis that no \resphan has ever held before him, save perhaps \Azraid.

And it is hard on him,
He screams in terror and anguish and has to fight a desperate and bloody battle against the many inner \daemons of his thoughts and fears to avoid losing his mind entirely.
His sanity is lashed like a vessel on a storm-wracked sea.
\hr{Ramiel is traumatized from awakening}{Afterwards he is traumatized and shaken}. 





\subsubsection{\Cishiel is worried}
\Cishiel is worried.
She fears her father has gone mad, and that his new power will make him even more mad and more dangerous.
But she knows it is too late to turn back.
She has cast in her lot with Ramiel and cannot hope to betray him, even if she would\ldots{} which she would not.
He is still her father and she loves him. 
He saved her from the horrible fate that befell him.
She knows that had he not forbidden her to become a \malach herself, she would have had to undergo the same torture and madness that Ramiel has endured - or she might have been destroyed long ago, or still trapped in the body of an amnesiac human.
No, she owes everything to Ramiel and still has more to repay him.

She feels more anguish for \Dasteron, her other ally, for she fears Ramiel will destroy him.
Ramiel looks terrible in his fury (when he \hr{Ramiel kills a Resphan after awakening}{eats a \resphan}), and \Cishiel fears no one will be able to stand against him, not even the formidable and resourceful \Dasteron.





\subsubsection{Voyage into inner worlds}
Perhaps the awakening process should be presented as a dream-quest, a journey into imaginary worlds that exist/are formed within his mind. 

Compare to Elric's journey beyond the Shadow-Gate in \cite{MichaelMoorcock:ElricofMelnibone}. 





\subsubsection{Facing his fears}
He is confronted with all his fears, sorrows, regrets, shame and pain. He must face, learn and accept the entirety of the brutal truth of his people's cruel nature and monstrous origins, the nature of \humans{} as a slave race, and his own history as a cruel conqueror and betrayer. 

Compare with the \emph{thetalos} cave in \authorbook{Jacqueline Carey}{Kushiel's Chosen} or Chia's caves in \authorbook{Stephen Marley}{Shadow Sisters}. 

Before he begins he promises himself that he will win. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  I smell the gasoline\\
  I smell the fire\\
  I'll make it all so clear\\
  This is my mentor
}

\citebandsong{BeyondTwilight:LurkingFantasia}{Beyond Twilight}{Rage}{
  Trying to face my sanity. \\
  But I'm too afraid to confront with it. \\
  Reaching out. \\
  For what I do not know.\\
  There's no way to explain this Hell I'm in. \\
  Can you? Can you? 
  
  No source of power to take from and wake \\
  from this nightmarish lunacy \\
  Is there a meaning or is this \\
  just a test of destiny? \\
  Creating these monsters for self purposed riches \\
  and glory in the end \\
  Thousands of victims with fresh schizophrenia \\
  isn't out here to pretend.
}

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Godless and Wicked%
}{
  Parts of my memory have been erased.\\
  You've destroyed my files\\
  Oh but I'm getting nearer\\
  It's all getting clearer 
  
  Look for a passage way\\
  Wait for the judgement day\\
  The truth will be told\\
  And my dreams unfold \\
  I'll find a way 
  
  I'm half alive here\\
  But I have no fear\\
  Cause I'll find the light yeah 
  
  Time to changes\\
  Everything re-arranges
  
  I'm getting ready\\
  At the break of dawn \\
  The fight is on 
  
  Godless and wicked\\
  Creepy and cold
}

With all his might he clings to the good memories of grandeur. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Send yourself to get back night\\
  I see women crawl\\
  It's dusty and mid in mind\\
  This is my intention
}

He wants to prove that he is the boss. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  I've seen me set the light\\
  This is the mentor\\
  I met cold on this ride\\
  This is the centre
}

But dangers lurk within his mind. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Don't let it fall\\
  You're not you, you're me\\
  Don't let it get a taste of your blood\\
  Yeah you're feeling small\\
  Don't look at me, don't look at me\\
  You're dancing with the Devil in my hall
}

He almost wanders lost in the dark corridors of his mind. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Now am I lost? Deep in my soul. \\
  There will be no forever.\\
  Through time I'm tossed. A wish without hope. \\
  Into the never.\\
  As time stands still, my spirit grows cold.\\
  I fall into darkness, as black as my soul.

  Now am I lost?\\
  Without hope into the never\\
  Deep in my soul
}

He holds tight. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Crawl for your master\\
  You know I'm in control
}

The whole process takes a long time. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Smell the gasoline\\
  I light the fire inside\\
  Smell the gasoline\\
  I sway all through the night
}

Finally, slowly he awakens. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Ecstasy Arise%
}{
  From dark waters I rise\\
  My once trembling shell conceals a God
  
  Power surging through the void I soar\\
  Intoxicating visions whispering more\\
  In my radiance every \colour seems to fade
  
  I speak only in thought\\
  Life is not forever nothing is forever\\
  In dark waters I find\\
  Beauty beyond oceans of time
  
  In my radiance every \colour will soon fade away\\
  In the emptiness I will no longer stay
}

It is much like \hr{Shaeeroth ritual}{the process that turns a \dragon into a \shaeeroth}. 
Ramiel gains insight into many horrible truths concerning his people, the \banes, their \matrices and their purpose.
This is only possible because of the wisdom he has already attained, and it makes him even wiser and stronger, but also less sane, and it brings him a pain and a despair that will continue to haunt him.

\citebandsong{Nile:Ithyphallic}{Nile}{
  Language of the Shadows
}{
  Abandon hope\\
  And I shall become free\\
  And with freedom acquire emptiness

  With the mind cleansed and empty\\
  There is the void known as despair\\
  A gateway upon an emptiness endless and vast

  In despair the language of the shadows is intelligible\\
  In madness all sounds become articulate

  Terror and despair they guide me\\
  Into nightmares that follow one upon the other\\
  Like windblown grains of sand

  [solo: Dallas]

  I have become as the wastelands\\
  Of unending nothingness\\
  Now shall the night things\\
  Fill me with their whisperings\\
  And the shadows reveal their wisdom
}





\subsubsection{Triumphant}
His traumas, his emotions and all his personality as Carzain, Vizicar and others is broken down. 
He is reconciled with his true nature as a \sathariah{} and his \malach{} \hr{Malachim bind souls}{power of binding souls} (and \hr{Ramiel binding souls}{his \carcer}).  
He embraces the enslaved souls and uses them and their power. 
He becomes the true Ramiel. 

He says to \Cishiel:
\ta{Bring me my sword and my guns.}
She swiftly obeys. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  And so, enrob'd by tendrils of starfire and the raiments of lunar mist, the immortal liege whose sceptred empire is eternity sits enthroned and brooding over his dark realm once more.
  
  Swathed in moon-frosts, in icy winds our blazon flying. \\
  When the moon and stars shine as one upon the snows, \\
  the ice-gate opens, the prophecy is fulfilled!
}

He tears asunder his \human{} guise and strides forth from the Shroud into true Reality, resplendent in all of his \sathariah{} glory. 

He summons his faithful servants, which are wolf-like creatures. See section \ref{Ramiel's wolves}. 





\subsubsection{Stronger than before}
When he awakens, \hr{Ramiel is wiser from walking the earth}{Ramiel is stronger and wiser than ever before}. 










\subsection{Kills a \resphan}
\target{Ramiel kills a Resphan after awakening}
Ramiel wants to test his new powers. 
As a full-fledged \malach he has \hr{Malachim binding souls}{enhanced soul-eating powers}. 
He tests it by attacking an eating a \resphan. 

Ramiel zaps his foe with dark lightning. 
Then shoots him with his pistols.
Then blasts him repeatedly with sorcery and lightning.
Gradually he tears his foe apart and, turning himself into a devouring, hungry vortex, sucks in the victim and devours him body and soul.
It is like witnessing a black hole and its accretion disc.





\subsubsection{Kills \Gilchad}
\target{Ramiel kills Gilchad}
Perhaps the first \resphan that Ramiel kills is \Gilchad. 

\Gilchad{} was responsible for guiding him through the torture process. 
When Ramiel finally awakens and emerges, he tells him: 
\ta{I owe you thanks for helping me regain my memory. 
  But I can tell by looking at you that you enjoyed the process. 
  So, with that in mind, I also owe you \emph{this}\ldots{}} 

And then Ramiel kills \Gilchad. 
And eats him. 

He had wanted to do this for a while, but he needed him. 
Now, for the first time ever in his life, Ramiel has full control over his \Malach{} powers and the associated \carcer. 
This means that he can eat (weak) souls far more easily than any normal \resphan{} or \dragon. 

He also wants to exercise and test that power. 
That is part of the reason for killing \Gilchad. 















\section{Return to \Mystraacht}
\target{Ramiel returns to Mystraacht}
Ramiel returns to \Mystraacht. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  He is the prince of darkness\\
  Returning home to take his kingdom
}

Ramiel is now \hr{Ramiel is overpowered}{immensely powerful}.
When he comes back, others \hr{Ramiel is underestimated after Apotheosis}{underestimate his strength}. 





\subsection{Ramiel and \Dasteron}





\subsubsection{Ramiel hears of \Dasteron}
At first, Ramiel's motivation was just to get his powers and memory back. 

Now that he has achieved that, he spends many days doing research, learning everything about the state of the world from records and from \Cishiel's Cabalist contacts.
He covets power and greatness and feels it is his right by succession to become Overlord.

But not only that.
He also doubts \Dasteron's ability.
He returns to \Mystraacht and studies \Dasteron in person.





\subsubsection{Ramiel gets to know \Dasteron}
Ramiel goes to \Mystraacht and meets \Dasteron.
Ramiel hangs out for a while and learns how thing work nowadays.
He greets \Dasteron with respect (of sorts), but no subservience.
\Dasteron reciprocates. (Ramiel is, after all, a \sathariah, and thus in a sense \Dasteron's superior.)
Ramiel comes to \Mystraacht intent on hating \Dasteron, this pathetic usurper who thinks he can be Overlord.
But Ramiel finds, much to his chagrin, that \Dasteron is a good \resphan, a worthy leader and even a potential friend.
This complicates matters.





\subsubsection{Ramiel must dethrone \Dasteron}
Ramiel learns that \hr{Dasteron cannot become Apex}{\Dasteron{} lacks the \vertex{} strength to ascend to the position of \apex{} of the \Mystraacht{} \matrix}. 
This is no good. 
It is one of the reasons why Ramiel knows he has to dethrone \Dasteron. 
He might be a good leader for a while, but if he cannot become \apex{}, his reign is stillborn and without true prospect. 

Ramiel has learned from his travels, and from the insight he has gathered over his many lifetimes, that something big is coming. 
Some cataclysmic metaphysical event. 
And the \Mystraacht{} \matrix{} has to be strong to deal with it. 
Therefore, a true \apex{} is needed. 
Ramiel feels this \apex{} should be him. 

He becomes convinced that, while \Dasteron is a good leader, he is not good enough.
He is a skilled politician and fighter, but he does not have the cosmic insight or \vertex strenght that \Mystraacht needs.
He finds out that \Dasteron shies away from all the darker writings and fears dealing with the \banes.
\Dasteron tends to obey the \banes quickly and with great fear.
\Dasteron is fearless when it comes to his fellow \resphain, but Ramiel fears \Dasteron is not capable of managing \resphan affairs in a larger cosmos.

This makes up Ramiel's mind.
He must dethrone \Dasteron and take the throne himself.
Only he is strong enough to rule \Mystraacht. 





\subsubsection{Ramiel laments having to kill \Dasteron}
Ramiel grieves. 
He has come to see \Dasteron as almost a friend. 

Ramiel also knows that however good \Dasteron is, Ramiel has to dethrone him.
\Dasteron knows this as well.
Sooner or later, Ramiel will challenge him for the throne.
Here is the real tragedy:
Ramiel knows that if he loses their match, he will not submit to \Dasteron's rule.
He will challenge him again and again until he wins, for Ramiel must win.
He also comes to know \Dasteron well enough to know that \Dasteron will do the same if Ramiel wins.
They are both full of pride.
Each believes that he is the better leader, that only he is worthy and capable of leading \Mystraacht.
\Dasteron believes that Ramiel, for all his brute force, is too insane and unstable and dangerous to have as Overlord.
So they conflict is doomed to continue forever, until one of them perishes.
So Ramiel makes a very hard decision.
He will destroy and eat \Dasteron as soon as he wins (if he can, that is). 
This is tragic.
Ramiel will miss \Dasteron.
He is a great \resphan and a friend.
It will be a great loss for \Mystraacht and for the \resphan race, and for Ramiel, and for \Cishiel.
But it must be done.










\subsection{\Mystraacht{} has degenerated}
In Ramiel's absence, \Mystraacht{} has degenerated into a crowd of decadent barbarians striving for maximal evil and perversity for its own sake, and out of some misguided ideological idea that this is their true nature and the purpose of \Mystraacht. 

Compare to the Dark Eldar of \emph{Warhammer 40,000}.

Ramiel: 
\tho{%
  We of \Mystraacht{} boast of our independence and free thinking.
  But we are just as bound by tradition as the \KiriathSepher.
  We go with the flow just as much as they do.
  Just look at how I followed \Zachirah.}

Ramiel intends to bring order and restore the true \Mystraacht. 
Bring them back on track and introduce meaning in all the madness. 

Ramiel: 
\ta{%
  I am \ps{\Zachirah}{} only son. 
  I alone am heir to his legacy and his designs. 
  I alone comprehend the scope of his original vision. 
  I alone understand \ps{\Mystraacht}{} true purpose.}
\tho{%
  And I alone understand the flaws in my father's vision and know how to correct them.}

The \Mystraacht{} do a lot of eating and binding souls. 
This is the source of \hs{Ramiel's bound souls}. 

\lyricstitle{Warhammer 40,000: Codex Dark Eldar}{
  As the Dark Eldar died, the air was filled with escaping souls. 
  A roiling mass of blackness hovered on the edge of vision, the screams of spirits in eternal torment sounded on the edge of hearing.
  
  \ldots{}
  
  The ebbing and flowing of released souls slithered around the Dracon, drawn to her blood and fear. 
  She could feel their wispy tendrils sliding over her, probing gently into her mind. 
  She felt like screaming, but she gritted her teeth and was silent. 
  
  \ldots{}
  
  The Dark Eldar Lord's eyes glazed over, as he took a long, deep breath. 
  Khirareq felt the spirits around her drifting away, pulled towards the gulf inside the Lord's own soul. 
  The Lord's body twitched spasmodically as he absorbed the freed life essence of his followers. 
  As the spirits of the dead were consumed, Akhara'Keth's spasms increased and a thin dribble of saliva trickled from the corner of his slack lips. 
  With a shuddering sigh, the Lord finished and slumped back in the chair. 
  When he sat forward once more his eyes burned more brightly, his skin was less wrinkled, his hair darker with more lustre. 
  
  \ldots{}
  
  She stared straight back at the Lord, looking deep into the ancient pits of evil that were his eyes. 
  
  \ldots{}
  
  \ta{%
    You need to rule?
    What do you know of needs 
    You are young, the Thirst has a shallow hold on you. 
    I will tell you of need; a deep, unfaltering emptiness that grows larger and more demanding with every passing of the night. 
    You have heard tales of how I consume a hundred souls a day. 
    That number is but the morsel to whet my appetite. 
    A hundred times that number die every day to quench my desire, my need.
    Spirits unnumbered are distilled in agony and torture to the peak of exquisite taste to fill the chasm of my soul. 
    Do not confuse needs with ambitions.}
}









\subsection{Ramiel confronts \Dasteron}
There is an upstart, \hr{Dasteron}{\Dasteron}, who is the closest thing \Mystraacht{} has to a leader these days and thus counts as having usurped Ramiel's place. 

\target{Ramiel uses macho rhetoric against Dasteron}
Ramiel uses traditional \Mystraacht \hr{Mystraacht philosophy}{macho rhetoric}. 
But he is actually \hr{Ramiel is critical of Mystraacht ideology}{critical of the \Mystraacht ideology}. 

\Dasteron{} is taller than Ramiel, and very powerful. 
(You have to be powerful as fuck to aspire to lead \Mystraacht.)

He mocks Ramiel: 
\ta{%
  I believe you will find that things have changed in your absence, Lord Ramiel.}

Ramiel:
\ta{%
  You will find that things are about to change again following my return.}

\Dasteron{}: 
\ta{%
  You have been out of the game for thousands of years, Lord Ramiel.
  You drifted around down there playing \human, 
  while I was devouring souls and waxing strong. 
  I have even devoured \dragons.
  \Dragons, Lord Ramiel!
  Times have overtaken you.
  I am your superior now.}

Ramiel: 
\ta{%
  Then I challenge you.
  I invoke my right of Trial by Combat.}

Remember to compare Ramiel's and \ps{\Dasteron} \hr{Dasteron's appearance}{appearance}. 

The battle itself, despite what they try to show the spectators, is a grim, sad affair.
There is no hate or anger, so there is no enjoyment.
It is just a grim and gritty fight to the bitter end.





\subsubsection{Motivation}
Ramiel knows he has to prove his own worth by defeating \Dasteron. 
He must impress the \Mystraacht{} so they will accept him as their Overlord. 
He has to entertain in order to lay a foundation for his future reign. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Panem et Circenses}{
  Awake, O' serpent of my heart. It is time.\\
  The sun stands high, and unfaithful crowds await thee.\\
  Redemption in their eyes and stone at hand.\\
  The arena hungers for your venom.\\
  Let the games begin.
  
  Bring in the lions. Bring in the beasts.\\
  It is time to confront the masses with their fears.\\
  A sober moment. A shred of truth.\\ 
  To gaze into an honest mirror. \\
  A disturbance of their sleep.
  
  Violent teeth and claws, untamed and fierce, \\
  reaches far and cut deep into the empty eye.\\
  It is time to let the bitter venom flow\\
  through this embodiment of emptiness.
  
  And the blood shall run free like words.\\
  And the bones shall form stairs to the future.
  
  Now, unfaithful spectator. Are you satisfied?\\
  Did you come close enough to feel the lion's breath?\\
  On day soon your shall be the sacrifice.\\
  A nameless grave of the past.
  
  Protagonist!\\
  Your time is now.
}





\subsubsection{Combat}
\target{Dasteron dies}
\target{Dasteron stronger than Ramiel}
\Dasteron{} is more skilled than Ramiel. 
\hr{Dasteron's skill}{Much more skilled}. 
He has faced down \satharioth{} before and knows how to turn an opponent's strength against him. 
Besides, \hr{Dasteron's smithing}{he is a great weaponsmith} and armed with the sword \hr{Scaleron}{\Scaleron} and many other powerful magical items. 

\ps{\Scaleron} design was inspired by \hr{Ascaril}{\Ascaril}, Ramiel's mother's sword. 
\Dasteron{} tells Ramiel this. 

Ramiel is taken unawares when \Dasteron{} displays just \emph{how} skilled he is at all three \hs{Paths}; not only \hr{Path of Light}{Light}, but \hr{Path of Ice}{Ice} and \hr{Path of Darkness}{Darkness} as well. 
This nearly overpowers Ramiel. 
The two combatants are sort of evenly matched at the Path of Light, but \Dasteron{} is far better than Ramiel at Darkness and Ice. 

One reason why \Dasteron{} is stronger than Ramiel is that he has \hr{Dasteron's upbringing}{lived his entire life as a \Mystraacht{} warrior}.  
Ramiel spent his formative years in the wussy and semi-pacifist and effeminate \Merkyrah{}, and then spend thousands of years \trope{WalkingTheEarth}{Walking the Earth} as a Scion.  

Ramiel is \hr{Ramiel is overpowered}{\uber, because he has eaten \Belzir}. 
But even so, he is hard pressed. 
He is not confident he can win. 
So he \emph{cheats}. 

The fight is to the death, but \emph{not} to destruction. 
But after Ramiel wins he breaks the rules and eats his fallen foe's soul, destroying him. 
Dark Eldar style. 

\ta{Stop him!} people around him cry. 
This was not part of the deal.
But no one is brave enough to challenge the \sathariah{} who has just splattered their leader and is now eating his soul and radiating fucking wicked-sick \sathariah{} power in all directions. 

Ramiel: 
\ta{%
  I am Overlord now. That was the prize. I can do whatever I want. That is my right. Will anyone deny me?}

Someone dares call him out on the dishonourable methods he used, both before, during and after the fight: 
\ta{You cheated!}

Ramiel:
\ta{Have you become like the \KiriathSepher{} in my absence?
  Have you become fops and cowards, slaves of etiquette?
  Ruthlessness has always been the \Mystraacht{} credo. 
  I saw my chances, so I took them. 
  Just as I saw my throne and now seize it.}





\subsubsection{Claims \Scaleron}
After slaying \Dasteron, Ramiel claims the sword \Scaleron. 
From that point he wears and uses the sword. 
It is his way of paying tribute to \Dasteron. 
He was, after all, a great and brave man and a worthy opponent. 
A true warrior of \Mystraacht. 

\Scaleron{} is a more than worthy replacement for Ramiel's old weapon, \Ascaril. 









\subsection{Ramiel claims the throne}
Ramiel lays claim to the throne of \Mystraacht. 
At this time he is not only the son of the first and greatest Overlord, but also the last surviving \sathariah{} in \Mystraacht{} (\Shiaraid{}, whom he killed, was the penultimate one). 
So, try as they might, no one can can really deny that he is the best candidate for the throne. 

\begin{prose}
Critic: 
\ta{What gives you the right to claim Overlordship?}

Ramiel: 
\ta{I am Ramiel.} 

(He could list off titles, lineage and accomplishments: 
One of the original discoverers of \Semiza, \sathariah, co-founder of \Mystraacht, sole heir of the last Overlord, and a mega-badass dude. 
But he needs say no more.) 

Critic: 
\ta{I believe you will find, Lord Ramiel, that things have changed in your absence.} 

Ramiel: 
\ta{And I believe you will find, [Critic's name], that things are about to change again.} 
\end{prose}

Perhaps he challenges his rivals by invoking his right of \hr{Mystraacht trial by combat}{trial by combat}, as is a \Mystraacht{} tradition.

\emph{\RamielsAwakeningBook} ends with Ramiel proclaiming his dominion and claiming his ancestral throne, cementing his position as the unchallenged Overlord of \Mystraacht. 

\lyricsbs{Emperor}{Moon Over Kara-Shehr}{
  Master! We ride with the storm \\
  in his name, the sire, wolves' king. \\
  Enter the power coursing \\
  through veins of the night.
  
  Power ripples through me. \\
  Armageddon's thunder will bring others to my side. \\
  The throne is mine. \\
  A blackened storm of evil. 
  
  Master! We ride with the storm to take \\
  revenge in the sky upon the one \\
  who cast thee from his side.
}

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Such power! I am the Chosen. \\
  The secrets of the earth and the stars are unlocked before me.\\
  I am destined to reign forever\ldots{} \\
  to reign from the Ice-Veiled Throne of Ultima Thule!
}



After Ramiel has regained his full \malach powers and become Overlord, he lets himself hail as the saviour and champion of the \resphan race. 
He has mastered his \carcer and the dark powers of the \banes.
He is the ideal of all \resphain who crave power and greatness and perfection.

The new \Thanatzil, even.

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  Churning the Maelstrom
}{
  Hail To He Who Is In The Duat, Who Is Strong\\
  Even Before The Servants of Serpents\\
  He Gathers The Power From Every Pit of Torment\\
  From They Who Hath Burnt in Flames\\
  From Words of Power Uttered By the Darkness Itself

  Hail To He in The Pit, Who Is Strong\\
  Even Before the Terrors of The Abyss\\
  Who Gathers The Power from the Wailing And Lamentations\\
  Of The Shades Chained Therein\\
  From He Who Createth Gods \\
  From The Silence Alone
}





\subsubsection{Ramiel is sad}
After having slain \Dasteron and claimed the throne, Ramiel is very serious and determined and weighed down with responsibility.
Not at all the reckless adventurer he was in his youth.

Compare to William Adama from \cite{TV:BattlestarGalactica}.





\subsubsection{Contacted by \Daggerrain}
At the end (or perhaps at the beginning of the next book), Ramiel is contacted by \Daggerrain. 

\daggerrain{Ramiel. 
  Thou hast united \Mystraacht. 
  That is good. 
  But forget not whom thou servest.}















\section{Sentinel story thread}










\subsection{\Vizsherioch{} versus \Ishnaruchaefir}
\Vizsherioch{} is strong, powerful enough to challenge even \Ishnaruchaefir. Despite his young age. 





\subsubsection{\Vizsherioch{} becomes the Dagger}
\target{Vizsherioch becomes the Dagger}
\index{Dagger, the}%
\Vizsherioch{} finally becomes the \hs{Dagger} and takes his rightful place in the \matrix. 
His confrontation with \Ishnaruchaefir{} (and his \hs{Fulcrum}, \Rystessakhin) was important in this process. 











\subsection{\Secherdamon{} communicates with Tiamat}
\target{Rissit communicates with Tiamat}
\Secherdamon, seeking power and guidance in his war against the \banes, contacts the \firstgendragons. He feels the presence of \Tiamat. She appears as a great mass of swirling Chaos, almost too amorphous to be a person. She seems almost mindless. Compare her to Azathoth from H.P. Lovecraft's stories, such as \emph{The Dream-Quest of Unknown Kadath}.

Of course, \Tiamat{} is not mindless. But she has absorbed so much Chaos power and \xzaishannic{} essence that she has become more like \xzaishann{} than a \dragon. Her mind is so Chaotic as to be completely alien and unknowable, even to \Secherdamon, who is otherwise one of the wisest among the \shaeeroths{} in the arts of Chaos, one of those who knows the most and has done the most research. (For instance, he\dash along with subordinates\dash created the Rissitic magic theory of the Three Worlds.)





\subsubsection{\Secherdamon{} visits \Dathka}
\Secherdamon{} visits the fallen city of \hr{Dathka}{\Dathka}. 

\lyricsbs{Emperor}{Ye Entrancemperium}{
  Drawn towards these lands again.
  Seeking death and sacred soil.
  I ride the longing winds of my blackened soul,
  growing stronger once I enter my empire beyond.
  
  Emperium!
  Behold my coming.
  
  The fullmoon rise above me,
  enlightening my realm in a silvery glow.
  Yet the shadows crawl beneath my storming sky,
  guarding treasures from forbidden light.
}

He remembers \hr{Secherdamon's rise to power}{the time when he became a god}. 

\lyricsbs{Emperor}{Ye Entrancemperium}{
  I still remember,\\
  though ages ago it seems,\\
  the first time I entered the gates,\\
  the revelation of ritual death\\
  by which I became divine.\\
  Sacrifice of the life I had\\
  among the flesh of the light.
  
  And now I enter again.\\
  Even stronger, yet amazed by what I see.\\
  In ecstasy I mock the world.
  
  Suddenly I memorize,\\
  asking what I left behind.\\
  Nothing.
  
  Can I ever comprehend?\\
  Will my longing ever end?\\
  Never.
}





\subsubsection{\Secherdamon{} seeks out \KhothSell}
\Secherdamon{} also hopes to invoke \KhothSell{} and obtain her power of death to wield it against the \sephiroth{} and the \Morbus. 

\lyricsbs{Exmortem}{Death deceiver}{
  Ancient image of death.\\
  The deepest depts of horror.\\
  A diabolic master plan.\\
  Not to succumb to the damned.
  
  Mummified in slumber.\\
  Awaiting to appear.\\
  Death deceiver.\\
  Exmortem.
}







\subsection{\Ishnaruchaefir{} seeks power}
\target{Ishnaruchaefir seeks out cosmic gods}
\Ishnaruchaefir{} fears \ps{\Secherdamon} plotting. 
He plans to go up against his brother, but he is not powerful enough. 
He needs more knowledge and power. 

In order to build and release the \hs{Ark}, \Ishnaruchaefir requires the help of some \hr{Aloof Dragons}{aloof Elder \Dragons} that sleep dormant.

Maybe replace the gods in this scene with Elder \Dragons. 
Or maybe it is \Secherdamon who contacts them.

In the end, a few Elder \Dragons manage to awaken (now that the Shroud is broken) and come to \Ishnaruchaefir's aid.
Not many, though. 
Perhaps 4--6.
10 at the very most. 




\subsubsection{Navel gazing}
He gazes into himself, and into his glaive, \Triestessakhin. 

\lyricsdimmuborgir{The Insight and the Catharsis}{
  Oh, dreadful angel of mine.\\
  Enrich me with the vastness of your being.
  
  Rigid father, teach me to comprehend.\\
  I'll commit myself to understand.\\
  To be the faithful and the instrument,\\
  so that the ones with blindfold can see what I have seen.
}





\subsubsection{\KhothSell}
He seeks out \KhothSell, his \quo{mother}. 
She tells him stuff. 

\lyricsdimmuborgir{The Insight and the Catharsis}{
  What more do you need of proof?\\
  Human hands conforming clooven hooves.\\
  For I know the secrets and lies behind all truths.\\
  Knowlege is power and the power is mine.\\
  It's all mine.
}





\subsubsection{Cosmic gods}
He seeks out some \hr{Cosmic gods}{cosmic gods}, hoping to gain the power and knowledge he needs to thwart his brother. 

Their dark halls are splendid and overwhelming, but also dangerous, filled with mighty guardians that strike even the legendary \Ishnaruchaefir{} with terror. 

\lyricsbalsagoth{Invocations Beyond the Outer-World Night}{
  These stygian pitch-black vaults are filled with batrachian devils,\\
  Dire crystalline watch-dogs of the chasmed deeps,\\
  (For the gleaming jewels of truth are not without their protection\ldots{})\\
  Vril-gorged adamantine fiends of the threshold,\\
  Spawn of the ersatz interior sun.
}

The cosmic gods turn him away. 

\lyricsbalsagoth{
  The Hound of Chaos Transcends the Nebulous Palisades of Z'xulth
}{
  [THEY-WHO-LURK-AND-BREED-IN-LIMBO:]\\
  Silence, godling! \\
  The fact that you stand before us is testimony to your mettle, 
  but your ambitions shall yet outreach your abilities. 
  
  We have long watched thee and your struggles with amusement, Zurra, 
  Sire of Angsaar. But this audience is now at an end. The path you 
  must traverse lies before you, and you must follow it to its 
  ultimate destination.
}

But \Ishnaruchaefir{} is sneaky, and he manages to surprise and out\manoeuvre them, if only for a moment. He successfully gleans enough of their secret knowledge to achieve what he needs. And so, \Ishnaruchaefir{} confronts some of the mightiest creatures in the cosmos, entities who could crush him underfoot with no effort at all, and he \emph{still} comes out looking like a total stud. \trope{Badass}{Badass}.  







\subsection{\Ishnaruchaefir{} laughs}
At some point, \Ishnaruchaefir{} experiences something funny. 
He laughs with sincere mirth for several seconds. 
\Criseis{} (who is with him) laughs along. 
Seeing him enjoying himself is intoxicating. 
She becomes ecstatic and blissfully happy. 
Her entire world lights up, and everything seems good and bright. 

While it lasts. 

Then he gets over it, and his usual brooding, grim, sardonic state-of-mind takes over. 
Suddenly \ps{\Criseis} world again turns dark and brutal and full of war and pain.
She understands that his mirth made him forget his gruesome burden and all his traumata and hate against the world for a brief moment. 
And his feelings rub off on her, who is closer to him than any other. 
And she is more impressionable and vulnerable than he, so it rocks her world more strongly. 





\subsection{Sentinels seeks out \voyagers}
Some Sentinels, perhaps \Ishnaruchaefir, seek out the \hr{Voyagers today}{surviving \voyagers} to gain knowledge useful against the \banes. 








\subsection{\Ishnaruchaefir{} begins to realize what he must do}
\target{Ishnaruchaefir begins to realize what he must do}
\Ishnaruchaefir{} slowly begins to realize \hr{Ishnaruchaefir realizes what he must do}{what he must do} to overcome his own mental blocks and reach the Gnosis he so desperately needs. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  A distant cry arose\\
  from the fathomless well that is my soul.\\
  I can not hear the words,\\
  so I throw my heart in like a coin\\
  and wish that it would sink forever.
}

He realizes that \hr{Mirage Asylum symbolism}{he is hiding}. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  A purpose, a sacrifice,\\
  or merely temptation?\\
  Is my solitude anything but a perversion\\
  of my vanity?
}

He defends/rationalizes his actions to himself. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  I never cared for this weak inclination,\\
  this paranoid tendency to flock.\\
  And in between all the noise, all the guilt,\\
  a silence would carry my spirit away\\
  from diminishing obsessions.\\
  Away from fools and poisonous flies.\\
}

But deep down he knows his rationalizations do not cut it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  The birth of a dreamer.
}









\subsection{\Ishnaruchaefir{} takes a crazy risk too much}
\QuessanthIshnaruchaefir{} is known to be reckless and take crazy risks. 
In this book, he takes one crazy risk too many. 
It goes wrong. 
He fucks up and accidentally leaves a back door open so the \resphain{} can sneak into his Mirage Asylum. 







\subsection{Mirage Asylum destroyed}
\target{Mirage Asylum destroyed}
At some point \ps{\Ishnaruchaefir} \hs{Mirage Asylum} is breached, invaded by \resphain{} and \banes, overrun and destroyed.
 
It had been a living thing, but now it died. 
It bled and felt pain as it died. 
It was horrible for \Criseis to feel it die.
It was her home. 

\Ishnaruchaefir{} now has no safe hiding place. 
He cannot just skulk and let things happen. 
He is forced to take a more active role in the Feud. 
And he does. 
Oh, boy, does he. 
With a vengeance. 
The \resphain{} soon regret provoking him. 

Maybe this is part of \ps{\Azraid} \trope{XanatosGambit}{Xanatos Gambit}. 

The Asylum was protected by the Shroud. 
It was only because the Shroud was \hs{unravelling} that it was possible for the \resphain{} to breach it. 

Make sure to have plenty of story leading up to this, making it plausible that the Asylum could be breached now but not just at any point in the last seven thousand years. 

This is an omen of things to come. 
Soon, the whole world will lose its Mirage Asylum, the Shroud itself. 

Compare to where Chia loses her Black Dragon Valley in \authorbook{Stephen Marley}{Shadow Sisters}. 







\subsection{\Ishnaruchaefir{} confronts \Secherdamon}
\Ishnaruchaefir{} confronts \Secherdamon.

Perhaps, in the distant past, \Ishnaruchaefir{} warred against \Nexagglachel{} in an attempt to bring the \dragons{} together. 
They discuss this.

\begin{prose}
  \Ishnaruchaefir: 
  \ta{That is something you never grasped.}
  
  \Secherdamon: 
  \ta{You think you know so much about me. 
      Yes, I know and understand perfectly, as I always have. 
      But your mission is misaimed (forfejlet?). 
  
      You are so arrogant. 
      You do not understand what I have become; indeed, you never understood what I was. 
      You have power, yes, and you may best me in combat, but in the world I wield power beyond your wildest dreams.%
  }
  
  \Ishnaruchaefir: 
  \ta{Unlike you, I have no wildest dreams\ldots{}}
  
  \Secherdamon: 
  \ta{\ldots{} and that, brother, is your failing. 
      It is why you have become a relic of the past. 
      The future is mine! 
      I am the future!
  
      Heh. 
      Perhaps I ought to thank you and \Nexagglachel. 
      If not for his death, I might still live in his shadow. 
      The events of those days are what have me the push to rise above what I was. 
      And today I am by far the greatest of us three.%
  }
  
  \ldots{}
  
  \Secherdamon: 
  \ta{%
    The Gnosis which \hr{Ishnaruchaefir refuses to tell Secherdamon Gnosis}{thou stole from me}\ldots{}
    I have \hr{Secherdamon gains Gnosis}{reclaimed it} by mine own craft.
    I am ready.
    My plan will come to fruition, and thy hideous work will be undone!}
\end{prose}

They fight a great duel. 
It is savage, murderous business, but cathartic. 
They slash and rip one another apart and let loose all the aggression and hate that they have pent up for one another and left to brood and fester for thousands of years. 

For once, \Ishnaruchaefir{} talks about feelings and motives. 
And he defends his actions, something he has always refused to do. 
He shouts in anger, which helps, because it is what \dragons{} do when they are being candid. 
This open anger is cathartic and brings them closer to each other (even though, between \resphain{} or \humans{} or \scathae, such anger could easily work the other way and drive them further apart). 

They learn to understand each other better, through the words and curses they speak, and through the deeper truths their bodies tell, with claws, weapons and magic. 
They understand each other's Aenigmata. 

They come a step closer to resolving the endless feud between the two brothers. 
They learn to respect each other. 

At the end, \Secherdamon{} admits that he is closer to forgiving \ps{\Ishnaruchaefir} crimes against them all. 
This is hard to say. 
Equally hard, \Ishnaruchaefir{} \emph{accepts} this step towards reconciliation. 
Previously he has responded to the idea of forgiveness with nothing but scorn. 
But this time he accepts and respects it (but wordlessly, not explicitly). 

This makes \Secherdamon{} more ready for his final mission. 
\hr{Secherdamon's sacrifice}{His sacrifice}. 

% They fight. 
% Ultimately, \Ishnaruchaefir{} slays \Secherdamon.









\subsection{\Secherdamon{} dies}
\target{Secherdamon dies}
\Secherdamon{} has two possible deaths: 





\subsubsection{Version 1: \Vizsherioch{} kills him}
Somehow, \Secherdamon{} get into combat and is mortally wounded. \Vizsherioch{} comes to him. 
\Secherdamon{} asks his son to save him, but \Vizsherioch{} instead kills him. 

First, \Vizsherioch{} holds a monologue: 
\ta{Yes, father. 
  You created me to be loyal to you. But more importantly, you created me to be loyal to our quest, our legacy.

  You created me from your own essence. I am part of you, and you are part of me. In the long run, this is a weakness. You must understand this. You made me well, but you have held too much back.
  
  You are fallen. To save you would be\ldots{} inefficient.
  
  I will strike you down, father, and subsume your essence into me. I will absorb your \xzaishannic{} blood, and in doing so I will become greater than any of us.
  
  I will become the ultimate \draecchonosh. I will become the ultimate heir to the \firstgendragons\ldots{} and to the \xzaishanns. I will become\ldots{} \emph{perfect}. And I swear to you this, father: I will filfull our destiny. I will scour \Miith{} of the \Erebean{} infestation and restore the glory of the \draconian{} race.}

\Secherdamon{} understands his son's vision, so he is happy when he dies. 

After this, \Vizsherioch{} becomes the ultimate god. 

He remembers the \quo{his} past as a \xzaishann{}.

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  I was spawned deep beneath the Pre-Cambrian sea, \\
  the scion of a far distant sun\ldots{}\\
  I have traversed the endless stars, \\
  and journeyed to a myriad galaxies\ldots{}\\
  The dimensional gates of the multiverse are mine to voyage effortlessly beyond,\\
  cosmic infinity is naught to one such as I\ldots{} \\
  I am as one with celestial eternity\ldots{}\\
  Clad in gleaming pentlandite \armour, \\
  on a whim I may reshape entire worlds,\\
  or extinguish the blazing light of a sun\ldots{} \\
  and I remain forever enchanted by sylphs\ldots{}
}

He has memories of the \xzaishanns{} beyond anything \Secherdamon{} and even the \firstgendragons{} had achieved, and he also carries within him the stolen essence of the \banelords. 

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  Wielding this Power Cosmic,\\
  the Omniverse is mine to conquer.\\
  I am a god.
  
  Arcane power lances forth from my fingertips,\\
  life withers before my baleful gaze.
}

He remembers the whole civilizations that the \xzaishanns{} once destroyed.

Have some evil flashbacks with the \xzaishanns{} destroying civilizations. 

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  The proud citadels of great antediluvian empires\\
  have been razed to the ground by my zircon blade.
  
  Riding the screaming crest of fettered ions,\\
  I shall bring my crystalline Chaos where order reigns.
}

He looks down at his father's corpse. 
\ta{I'm sorry, father, but I was not telling the whole truth. 
  I am not driven by our legacy or quest, but by the Will to Power.} 
Compare with Friedrich Nietzsche's philosophy.





\subsubsection{Version 2: Heroic sacrifice}
\target{Secherdamon's sacrifice}
\ps{\Secherdamon} death is a heroic sacrifice for his people. 
It has cosmos-spanning metaphysical ramifications and ripples. 

Compare to Anomander Rake's sacrifice in \cite{StevenErikson:TolltheHounds}. 















\section{Random scenes}









\subsection{The power of love}
A \human{} talks to a \resphan{} about how love is the greatest, most important thing in the world. 

\Resphan: \ta{Ah, yes. \quo{Love}. Insertion of dick into cunt, a splash of liquid, followed by cuddling. Believe me, I know what love is. I and my fellows were the ones that created it. We designed your people, programmed your obsession with sex and sexual bonding. Because that it what we need you for. Your \human{} \quo{love} is a pawn on our game, and your idolization of it is a keystone to our \hr{Daggerrain's master plan}{Master Plan}.}









\subsection{The master races did not infiltrate}
A Cabalist or Sentinel talks to a mortal about how his people supposedly infiltrated the kingdoms of mortals.

Big guy: 
\ta{%
  Ha! We never \quo{infiltrated} your world. We \emph{created} it! Your civilization is and was ever our tool. We never conquered you or couped you out. You were created, born and bred as our slaves.}









\subsection{\Criseis{} apologizes for \Ishnaruchaefir}
\Ishnaruchaefir{} has hurt some people. 
\Criseis{} comes in secret and of her own initiative to apologize and ask forgiveness on her master's behalf. 
\hr{Ishnaruchaefir never apologizes}{\Ishnaruchaefir{} never apologizes}. 















\chapter{\ThirdBanewarBook}
\target{Third Banewar}
\target{TBW}
This book details what would later be retroactively called \thirdbanewar, the final showdown with the \banes. 















\section{Overview}









\subsection{The Unravelling brings chaos}
The \hs{Unravelling brings chaos}. 
The world is slowly going mad. 
It will get much worse\ldots{}





\subsubsection{Ghosts escape}
Now, as the \hr{Sephirah plan}{\sephirah{} plan} is approaching fruition, the \carcer{} of \Iquin{} is filled to the bursting. 
Due to the \hs{unravelling}, \Iquin{} has grown unstable and leaking. 
Ghosts seep out and escape into the world, in droves. 

Compare to the ghosts and the Spectres in \cite{PhillipPullman:HisDarkMaterials}. 









\subsection{The world goes mad}
\target{The world goes mad}
Have a longer story where the world goes mad. 
More people discover the truth about \iquin, but by then it is too late, and their souls are too deeply bound to \iquin to break free. 

They also discover that there are even older and more malevolent things in the world than \iquin.
Things perhaps even more inimical to them.
So that even if \iquin is a parasitic soul prison, it is perhaps better than the alternative. 

Compare to the movie \cite{Movie:IntheMouthofMadness}. 

\citeauthorbook[\quo{First Thought in Three Forms}, p.86--100]{%
  BentleyLayton:TheGnosticScriptures%
}{%
  Bentley Layton%
}{%
  The Gnostic Scriptures%
}{
  Now, when the great authorities knew that the time for fulfillment had come\dash as when labor pains are felt by a lying-in woman\dash and that it was near the door, and that just so, destruction had drawn night, all the elements together shook.
  And the foundations of Hades and the ceilings of chaos moved.
  A great fire broke out in their midsts.
  And the rocky cliffs and the earth moved as a reef is moved by the wind. 
}

Seek inspiration in the Book of Revelation in the \emph{Bible} and other religious eschatology. 







\subsection{\Voidbringer must be stopped}
The \dragons{} and other \bane-opponents know that if the Cabal manage to open the portal to \Erebos{} as wide as they did in the \secondbanewar, they will be able to let in millions of \bane{} warriors. 
There is no way in fucking Hell the \Miithians will be able to deal with that many.
They are fewer and weaker than they were last time. 
So they must stop the portal. 








\subsection{Aloof \dragons must be roused}
There were some \hr{Aloof Dragons}{aloof \dragons} who took no part in the \feud.

The aloof ones did not care that \hr{No new Dragons are born}{almost no new \dragons were born} since the \hr{Heart weakened}{weakening of the Heart} began.
The aloof ones were powerful and immortal and had the luxury to wait a few thousands or even tens of thousands of years between procreating. Many of them were over 20,000 years old and saw the war with the \resphain as a temporary nuisance. 

\Ishnaruchaefir and \Secherdamon were similarly old and would likely have thought the same, but the war came horribly close to them when some of their close family members (Nexagglachel and \Ishnaruchaefir's three sons) were destroyed by the \resphain.
Now, in the \thirdbanewar, \Secherdamon or \Ishnaruchaefir had to convince the aloof ones that the war was more than a nuisance and that its conclusion would have great repercussions for all \dragons, even the ones who had fled to \Machai.
Eventually some of the aloof ones became convinced. 
Not all, but enough.

The conclusion of the war WAS important.
The aloof ones could hide in \Machai, but they could not really get away. 
They were still bound by the Heart and would suffer its fate.
Either that, or they would have to evolve, abandoning their Draconic nature entirely and becoming something different.
\Ishnaruchaefir and \Secherdamon knew this might be an option\dash{}to flee to \Machai and abandon \dragonkind\dash{}but it was not a palatable one. 
They both wanted the Draconian race to survive.
\Secherdamon wanted to win the war and was willing to enlist the \xs, with all the associated costs.
\Ishnaruchaefir did not like that idea.
So he looked outward into the universe for other ideas.









\subsection{Ramiel is mad}
Ramiel tries to hide it, but \hr{Ramiel is mad after awakening}{his sanity has suffered badly}. 









\subsection{Clean \humans}
There are some \humans who are \quo{\hr{Clean Humans}{clean}}, in the sense that they have no blood of the \quo{\hs{Men of Light}} and thus do not carry \Lithrim inside them. 
These \humans still have \bane and \resphan blood, but no \Lithrim.
This means that they are unaffected by the Second Advent. 

Some of these \humans are among the heroes. 
They help the immortal heroes.
They accomplish some minor things and manage to make a difference. 
Then they die at the end.
But they die a heroic death, having helped ensure that the Ark could escape. 
















\section{The \Matrices Battle}









\subsection{\ps{\Daggerrain} master plan}
\hr{Daggerrain's master plan}{\ps{\Daggerrain}{} master plan}, planned and orchestrated throughout twenty thousand years, is unfolding. 

\Secherdamon{} and \Ishnaruchaefir{} oppose him. Ramiel ostensibly serves the \banes, but is actually planning yet another betrayal.

\Daggerrain{} intends to sunder the wall to \Erebos{} and allow the \Voidbringer{} unrestricted access to \Miith{}. 

But \hr{Daggerrain's blind spot}{he has a blind spot}\ldots{}

\Secherdamon, on the other hand, wants to open the gate to Chaos and awaken \Tiamat{} and the \firstgendragons. He has communicated with \KhothSell{} or another one of them. She agrees to help him, but only if he can open the way and make it easy for them to help him. (See section \ref{Rissit communicates with Tiamat}.)

But \Iurzmacul{} plots against his fellow \firstgendragons{}. He does not want to see \Tiamat{} and the others return and devastate \Miith{}. Maybe he tells \Ishnaruchaefir{} and guides him. Maybe \Ishnaruchaefir{} is the son of \Iurzmacul.





\subsubsection{\Dragons fear \Voidbringer}
The \dragons{} know that if \Voidbringer{} gains access to \Miith, they will not stand a chance against the feared \baneking. 
If that happens their only recourse will be to follow \ps{\Vizsherioch} lead and appeal to the \xss. 

\Vizsherioch{} will not accept \Ishnaruchaefir{} as an ally. 
He would prefer to kill him. 

\Vizsherioch{} \emph{wants} to see the \banes{} succeed and \Voidbringer{} brought into the world, because then all of \Miith{} will be forced to turn to him as their only saviour. 
He cannot summon the \xss{} alone, but with enough \dragons{} and \quiljaaran{} and other immortals on his side, he can pull it off. 

He relishes the thought of a war between the \xss{} and the \banelords. 
He is willing to risk the destruction of all of \Miith. 
He kind of thinks like a \xss, remember. 
Plus \hr{Immortal Vizsherioch}{he is more immortal than most}. 









\subsection{Ramiel solidifies his power}
I should let a few years pass between the end of the last book and the beginning of (the serious part of) this one. 
Ramiel needs some time to consolidate his rule as Overlord. 
Not everyone swoons and falls down to worship at his feet. 

And even after some years, he still has rivals and has trouble controlling the dynasty. 

\target{Dasteron's cousins oppose Ramiel}
Among his most vehement foes are \hr{Dasteron's cousins}{\ps{\Dasteron} cousins}, \Sargamel and \Themirod. 

\target{Ramiel uses macho rhetoric as Overlord}
Ramiel uses traditional \Mystraacht \hr{Mystraacht philosophy}{macho rhetoric}. 
But he is actually \hr{Ramiel is critical of Mystraacht ideology}{critical of the \Mystraacht ideology}. 

After his return to Overlordship, Ramiel broods over the doings of the \resphan race.
He is disgusted by their stupidity and hypocrisy. 
The \Mystraacht curse the \CiriathSepher for being shallow and dishonest, but the new, wiser Ramiel can now see that the \Mystraacht are no better themselves, with all their shallow machismo and their hollow talk of \honour and bravery and whatnot.

He thinks: 
\tho{There are times when I wish the \banelords would just come and devour everything. Or whatever it is they plan to do.}

Even among the highest tiers of the \resphain who serve them, there is no one who really knows what the \banelords intend to do.
No \resphan understands the mind of a \bane.









\subsection{\Dragons summon \xss}
\Secherdamon-tachi want to awaken the \xss and summon them to \Miith to fight against the \bane menace. 
Maybe this is mostly intended to slow down the \banes. 
The \dragons know they cannot rely on the \xss as allies.
The \xss might decide it is not worth the effort and pull out of \Miith.
But if the \dragons can at least get the \xss to hold off the \banes, they have a chance. 

The \banes have a thousand-year master plan.
The \xss have little interest in \Miith.
They are likely to give up and go home. 
They will not commit many resources to \Miith. 
It is unlikely that they will save it in the long run, but they may save it in the short run. 





\subsubsection{\Vizsherioch seeks out \daemons}
\Vizsherioch{} seeks out some great and mighty \daemons{} who once served the \xzaishanns{} but have lain dormant for thousands if not millions of years. 

He demands that they serve him. They laugh and reject him, for they have been approached by \dragons{} before. But \Vizsherioch{} is more \xzaishann{} than any \dragon{} ever before. When the \daemons{} realize that, they are impressed and overwhelmed. They agree to serve him. 

He also seeks out \hr{Cosmic gods}{cosmic gods}\dash the same ones that \hr{Ishnaruchaefir seeks out cosmic gods}{\Ishnaruchaefir{} sought out}. But they turn him down. He claims that he is a \xzaishann{} reincarnated, and they laugh.

\lyricsbalsagoth{
  The Hound of Chaos Transcends the Nebulous Palisades of Z'xulth
}{
  The Outer Darkness has cast me from its cavernous maw! 
  So be it\ldots{} the final pieces of this great macrocosmic puzzle shall soon fall into place. 
  It has been millennia since I last visited my beloved brother, Zuranthus\ldots{} 
  and this reunion shall most certainly be steeped in ire! 
  
  The annals of eternity shall soon be illumined by the glorious radiance of my deeds, and the searing fire of my long denied vengeance! Woe unto my dogged nemesis and all those who dare aspire to thwart me\ldots{} for my final ascendence is nigh!
}







\subsection{\Ishnaruchaefir invokes dark gods}
\Ishnaruchaefir{} is forced to invoke various dark gods to seek their power and aid. Some of the same forces that \Secherdamon{} originally invoked to gain power (see section \ref{Rissit invokes dark gods}). 

Perhaps these powers originally helped effect the \hr{Shrouding}{\SecondShrouding}, and now \Ishnaruchaefir{} needs their power to defend the Shroud (see section \ref{To break or preserve the Shroud}).

In the end, a few Elder \Dragons manage to awaken (now that the Shroud is broken) and come to \Ishnaruchaefir's aid.









\subsection{\Iquinian Church preaches}
The \Iquinian Church preaches extra hard. 
The advent of \Lithrim{} is nigh, and the Cabalists want to be sure all the myriad Iquinians are kept under tight control. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  A Chore for the Lost
}{
  Every human being not going to the extreme limit \\
  is the servant or the enemy of man \\
  and the accomplice of a nameless obscenity.
}







\subsection{Ramiel accepts \NexagglachelsCurse}
Ramiel is seduced by the blood of \Nexagglachel{} in his veins. 
He is swayed by the \ps{\dragonlord} voice and ultimately agrees to betray the \banelords, in return for peace of mind from the \hr{Madness of the Curse}{madness and dementia that the curse brings}.

\lyricslimbonicart{The Yawning Abyss of Madness}{
  The winds that carry this esoteric call\\
  emerges from the dungeons underneath my soul. \\
  As I cross the bridge to that darkness, \\
  my eyes are filled with so much death.
}







\subsection{\Ishnaruchaefir hears \Nexagglachel would be proud}
\target{Ishnaruchaefir hears Nexagglachel would be proud}
\Ishnaruchaefir{} meets some \sathariah. 
Possibly Ramiel or \Azraid. 
(Maybe when \hr{Ishnaruchaefir and Azraid plot together, late in TBW}{\Azraid{} conspires with \Ishnaruchaefir}.) 

\begin{prose}
  The \sathariah: 
  \ta{I have a piece of your brother inside of me, you know. 
    I know something of his thoughts. 
    And you know what? 
    I think if \Nexagglachel{} knew what you had done, he would be pleased.}
\end{prose}

The above is not well-meant. 
The \sathariah{} hates \Nexagglachel, because \Nexagglachel{} hates him and drives him mad and ruins his life. 
But it is sincere. 

\Ishnaruchaefir{} takes it as a confirmation that he is on the right track. 
This makes him incredibly relieved. 
He has spent millennia brooding over whether he is \hr{Ishnaruchaefir's stewardship}{carrying on \ps{\Nexagglachel} legacy} properly. 
When \Criseis{} next sees him, he is happier than she has seen him in thousands of years. 
He does not show it, but she, who knows him better than any other, can detect it in his smell and his aethereal threads. 
The pall of darkness that always hangs over him has lifted a little. 










\subsection{Ramiel allies with \Baelzerach}
In secret, Ramiel contacts the \Baelzerach{} and forges a hidden alliance between them and \Mystraacht. They will not openly fight side by side, but they will strike at the same enemies and covertly work to achieve the same goals. 

This is especially sneaky because no one expects it. \Mystraacht{} and \Baelzerach{} are traditionally enemies, having fought many and very bloody wars. 









\subsection{The \banes bring a spaceship to \Miith}
The \banelords{} succeed at bringing a titanic and ancient \hr{Bane technology}{\voyager{} spaceship} from \Erebos/\Nyx{} to \Miith{}. 
It will take all of the \psp{\dragons}{} \xsic{} power to destroy it.

Other people see signs of its approach.

\lyricslimbonicart{Nebulous Dawn}{
  Dark atmospheric winds\\
  are striking towards Earth.\\
  Nihilistic cosmic force.\\
  Asteroid curse.
}

The ship arrives. 
It is a massively powerful juggernaut and wreaks tremendous destruction. 

\lyricslimbonicart{Nebulous Dawn}{
  A blazing phenomenon\\
  launching through the skies.\\
  A deadly impact, tempest chaos.\\
  Utterly devoid of life.
  
  Fountains of fire rise from the lava chambers.\\
  Columns of smoke darken the sky\\
  and cover the landscape in ashes.\\
  Storms with the anatomy of disaster.\\
  Immense swirling winds.
}









\subsection{\Erebos \Matrix Ascendant}
The \bane{} \matrix{} is strong and has almost taken over the world. 
Its corrupting, destructive influence can be felt all over \Miith{}. 
The \hr{Morbus}{\Morbus} is but one of its manifestations. 

\lyricslimbonicart{Nebulous Dawn}{
  An epic eclipse of the Sun.\\
  A rebirth of desolation.\\
  When the cold silence reigns,\\
  darkness sweeps the face of Earth\\
  with infesting freezing torments.\\
  Across the desert wastelands.\\
  Cataclysmic events.
}









\subsection{\Rystessakhin is damaged}
\Ishnaruchaefir{} is in battle, wielding his \hs{glaive}. 
Suddenly it goes wrong, and the unthinkable happens: 
The glaive becomes damaged. 
One of the little blades snaps off. 

\Ishnaruchaefir{} is terrified. 
He knew the Shroud was \hs{unravelling} and it was becoming harder for \Rystessakhin{} to keep it in place. 
\hr{Ishnaruchaefir's Nadir}{His own Nadirs} had been growing steadily worse as a result. 
But had never imagined that it would come to this. 

He immediately unsummons the glaive. 
Then he spends all his available energy on fighting his way free and escaping from the fight. 

He realizes that something is catastrophically wrong. 
The Shroud is under attack, and the pressure on poor \Rystessakhin{} has become so great that even her physical form is chipping and falling apart. 
The status quo is crumbling, and he cannot hope to maintain it any longer. 
He needs to change his strategy.
Something drastic must be done. 








\subsection{\Azraid conspires with \Ishnaruchaefir}
\target{Ishnaruchaefir and Azraid plot together, late in TBW}
\Azraid{} conspires with \Ishnaruchaefir. 

They have \hr{Ishnaruchaefir and Azraid develop empathy}{talked before} and have a relationship as friendly rivals. 
They have even \hr{Ishnaruchaefir and Azraid plot together, early in TBW}{plotted together before}. 
They are both philosophers who feel somewhat estranged from their races, so they have a certain mutual understanding. 

Gradually and ever so subtly through \quo{Sentinels of \Miith} \Ishnaruchaefir becomes convinced that Azraid is on the level, and he also begins to suspect the general nature of Azraid's plan. 
So when Azraid finally approaches \Ishnaruchaefir and asks for his cooperation in a secret venture, \Ishnaruchaefir has a bit of a \quo{what took you so long?} attitude, and the whole interaction has a \quo{I know you know I know you know\ldots{}} frame.
The two have each formulated ideas that can be combined into a useful whole.

Now \Azraid{}, for the first time \emph{ever}, comes clean and reveals (part of) his master plan to \Ishnaruchaefir. 
\Ishnaruchaefir{} is the best person he can trust with his plan. 

\Azraid{} also needs Ramiel, but he cannot trust him.
Ramiel is too volatile, too unreliable. 
\Ishnaruchaefir{} \hr{Ishnaruchaefir's impulsiveness}{has spent all his impulsiveness long ago}, so \Azraid{} knows he is dependable.

\Ishnaruchaefir{} agrees to cooperate with his old enemy. 

Perhaps it is here \Azraid{} \hr{Ishnaruchaefir hears Nexagglachel would be proud}{tells \Ishnaruchaefir{} that \Nexagglachel{} would be proud}. 








\subsection{\Ishnaruchaefir realizes what he must do}
\target{Ishnaruchaefir realizes what he must do}
\Ishnaruchaefir{} realizes that if he is to truly make a difference in this war, he will need more power.
(He \hr{Ishnaruchaefir begins to realize what he must do}{began to realize this earlier}.)
He will need true Gnosis of his own Aenigma. 
To do this he has to look deep inside himself and come to terms with himself. 
This means he must overcome a ton of traumata, which have festered inside him ever since he \hr{Ishnaruchaefir slays his beloved}{killed \Rystessakhin} and \hr{Ishnaruchaefir goes into the void}{fled into the void}. 

He must make peace with the memory of \Rystessakhin{}. 
He must save himself before he can hope to save the world. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  As deep cuts of truth.\\
  As a fire that closes the wound.\\
  So is my redemption.
  
  Beyond repentance.\\
  This is the ordeal of fire.
}

It will be hard, expensive and bloody, for both him and the world. 
But it will be worth it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  Come suffering, Apocalypse.\\
  Release the fires of Hell.\\
  I call upon destruction and despair.\\
  Not for vengeance, not for power.\\
  Beneath the ashes I walk.
}

At last he takes a deep breath and prepares to do it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  Behold, an angel of vengeance.\\
  A lion. A sword of fire. \\
  Alas, the burden of my heart\\
  is violence undone\\
  Pain unfulfilled.\\
  Silence.
}

Finally he does it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  When I finally cut \\
  deep into the flesh of guilt,\\
  the un-naked body of shame\\
  and the veins of repentance open wide,\\
  sending rivers of blood into my mouth.
  
  The pain is still mine.
}








\subsection{\Harbeth dies}
\target{Harbeth dies}
\Harbeth dies for some reason. 

Maybe \Zereth also dies. 
Most of the \hr{CS heirs die}{\CiriathSepher{} heirs die}. 















\section{Climactic Battle}
Near the end there is a great, climactic battle between the \bane/\resphan{} forces and some \quo{good guys}. 
There are very few \dragons{} (perhaps only \Ishnaruchaefir{} and his companions), because most \dragons{} support \ps{\Secherdamon} gambit, hoping to utilize the \pps{\banes}{} Shroud-weaving spell to bring the \firstgendragons{} into the world and have them vanquish the \Voidbringer{} and his legions.







\subsection{\HothNrul}
\target{Hoth-Nrul summoned}
\Vizsherioch{} and his cohorts manage to bring a mighty ally to \Miith: 
\hr{Hoth-Nrul}{\HothNrul}, a \xsic{} godling. 
\HothNrul{} is intended to spearhead the coming \xs{} invasion of \Miith. 

Later, \Ishnaruchaefir-tachi communicate with \HothNrul{} and convince the alien god that it is in its interest to attack \Daggerrain.
So \HothNrul{} seeks out the \banelord. 

\HothNrul{} has difficulty attacking \Daggerrain, for he is well-hidden-away. 
But it manages to do some damage. 
When \Daggerrain{} is distracted by the \xs{}, \Azraid{} and Ramiel strike and fuck up \Daggerrain. 

\HothNrul{} \hr{Hoth-Nrul left behind}{ends up the same place where \Daggerrain{} is}. 







\subsection{\Ishnaruchaefir leads \dragons}
\target{Ishnaruchaefir leads Dragons to war in TBW}
\Ishnaruchaefir{} does not believe in this gambit. He has no faith in \Tiamat{} and her brethren and does not think they will come to help. 
So he works to persuade the \dragons{} (including some \hr{Aloof Dragons}{aloof ones}) to fight, to fly with him against \ps{\Daggerrain}{} legions. 

At the last moment, he succeeds. 
Have a massively epic scene where \Ishnaruchaefir{} flies at the head of a massive flight of a \dragons, flanked by hundreds of \rachyths, \drakes{} and \pdaemons, to engage the \bane{} armies and seize victory.
They are awesome to behold as they return to \Miith in full force. 
Dozens of Elder \Dragons, several of them \shaeeroth.

Compare to: 

\begin{itemize}
  \item 
    \bandsong{Bal-Sagoth}{Black Dragons Soar Above the Mountain of Shadows}. 
  \item 
    The scenes in \authorseries{Richard Knaak}{War of the Ancients} where everyone holds their breath for the \dragons{} to come to their aid, and where they finally do come and save the day.
  \item 
    The scenes in \authorbook{Graham McNeill}{Fulgrim} p.472, where the Alpha Legion, Word Bearer, Night Lords and Iron Warriors come to the \quo{rescue}. 
\end{itemize}







\subsection{The advent of \Lithrim}
\target{Lithrim arises}
\Lithrim{} finally arises. 

Mankind is very Shrouded, \naive{} and stupid. 
Not quite as well-meaning and {innocent} as the \scathae, but not all that far from them.
That is why it is so effective when their inner \Erebean{} darkness is finally released in the culmination of the \Morbus{} plan. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Sola Fide
}{
  Some rejoice of the children's innocence and smiles\\
  Others of their shameful defloration \\
  by the ministers of Christ, swollen by arrogance and lust\\
  Jesus spoke words of wisdom: \quo{Let the children come to me}\\
  What's more enthralling indeed \\
  than ruining through them the genesis of life itself?\\
  Dive deep into the blue eyes of the newborn \\
  and thou shalt get a glance of heaven\\
  When this dive reveals despair, \\
  hideous ruins of the glory of Hell\\
  The serving sons of disobedience proclaim \\
  Vengeance belongeth unto Him\ldots{}
}

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Innocence sacrificed and heaven denied\\
  Iniquity divine\dash no repentance\dash over mankind\\
  Mind-raped, self-devoured, empty god-eyed\\
  Transgression coercive, Redemption never to be found

  Under the altar of cannibalism\\
  Man hast (thou) confessed the spiritual schism\\
  And without pride mourned the loss of freedom,\\
  Our blessed Lord have condemned you to martyrdom
  
  Let everything that hath breath praise the Lord, \\
  praise ye the Lord.
}

It is the culmination of that which began with \ps{\Thanatzil} noble sacrifice. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  The advent of Plerosis is the destiny of Man \\
  and shall shatter up to the Heavens,\\
  A savage aperture to the High Mass of the Comforter
}

It is cataclysmic and destructive. 
It unleashes all the wicked, destructive Entropy that, as it turns out, were the building blocks of Man all along. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Instigating manifold quadrants of industrialized death,\\
  An avid Moloch, never satiated, an endless Feast,\\
  Following the principle of reversibility of merits,\\ 
  shattering up the Word\\
  As Pillars of grayish Soulfire spurt out to a bereaved firmament
}

Man instinctively welcomes the advent of \Lithrim.

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  The unreservedly open spirit, \\
  open to death, to torment, to joy,\\
  The open spirit, open and dying,\\
  Suffering and dying and happy, \\
  stands in a certain veiled light:\\
  That light is divine.\\
  And the cry that breaks from a twisted \\
  mouth may perhaps twist him who utters it,\\
  But what he speaks is an immense alleluia, \\
  flung into endless silence, and lost there.
}

But it is also scary. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  From very high above a kind of stillness \\
  swept down upon me and froze me\\
  It was as though I were borne aloft \\
  in a flight of headless and unbodied angels\\
  Shaped from the broad swooping of wings, \\
  but it was simpler than that\\
  I became unhappy and felt painfully forsaken, \\
  as one is when in the presence of God
}

Some \humans{} fight against it. 

\citebandsong{BeyondTwilight:TheEdge}{Beyond Twilight}{Salem}{
  Entombed by the will of the night.\\
  All your thoughts deflowered.\\
  Waived all of your beliefs\\
  in this midnight hour. \\
  Search your past, try and make it back.\\
  All your strength overpowered.\\
  Unknown forces run you through \\
  in the shadow of the black tower.
  
  The witches of Salem hold your fate. 
  
  Relief obtained in sacred mass.\\
  All your sins forgiven. \\
  The ultimate sign of witchery.\\
  The total lack of sanity.
}

\Humans{} lose their individual identity. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  And the victim, blind to the radiating Light of Truth, \\
  stuttering, repeats:\\
  Lamma Sabacthani?\\
  Lamma Sabacthani?\\
  Lamma Sabacthani?
  
  Consummatum est.
}

Mankind becomes a god: \Lithrim. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  I am the son of Man, \\
  and this in erring reason's spite, is my pride\ldots{}\\
  War, be enthroned, a form of divine retribution!\\
  Execution, be sacred, agent of divine Providence!
  
  The stillness of Contemplation \\
  is allowed in billions of woeful cries,\\
  So astonishingly simultaneous and in unison,\\
  Each and every second, \\
  They defuse each other in such a perfect manner,\\
  Equaling the most inscrutable of all silences\\
  Doctrine of Mystical Substitution, Mystical Body, \\
  Sanctorum Communionem,\\
  Celebrate the Sin of one reflecting, \\
  tectonic forces alike, upon the multitude
  
  The purest of all Holocausts shall be perpetrated\\
  By a loving hand, never knowing if it provided felicity\\
  Or the vilest of everlasting torments\\
  No man can see Me and live!
}

When the \humans{} become the fell, abhorrent \Lithrim, they (or the smarter of them) at last realize the purpose of their otherwise empty and wretched lives. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  The act whereby being\dash existence\dash is bestowed upon us\\
  Is an unbearable surpassing of being,\\
  An act no less unbearable than that of dying.\\
  And since, in death, being is taken away from us \\
  at the same time it is given us,\\
  We must seek for it in the feeling of dying,\\
  In those unbearable moments \\
  when it seems to us that we are dying\\
  Because the existence in us,\\
  During these interludes,\\
  Exists through nothing but a sustaining and ruinous excess,\\
  When the fullness of horror and that of joy coincide.
  
  As I waited for annihilation, all that subsisted in me\\
  Seemed to me to be the dross over which man's life tarries\ldots{}
}

But they lose their \humanity{} in the process. 

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega
}{
  Mass Grave Aesthetics
}{
  The black Idol fills the veil of flesh with noxious smoke, \\
  Depicting primal human experiences indifferently, \\
  Contemptuous of moral concerns, dehumanized \\
  The howling of wolves and the destructive sword \\
  are portions of Eternity, \\
  Too great for the eyes of merely a man
}

But they gain new insight as they leave their \human{} forms:

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega
}{
  Mass Grave Aesthetics
}{
  Violence exists I the moment \\
  when the eye turns upwards into the head, \\
  When inversion is complete and total \\
  The darkness of the upturned eye is not the absence of light \\
  But the process of seeing being taken to its limit \\
  That thorough derangement of the senses, \\
  Way beyond the deceptive conflict between darkness and light \\
  Opens perceptions to the tyranny of the Chekhinah
}

\Lithrim{} is a slave under the \psp{\banelords}{} command. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  I can utter no word, O my God, \\
  unless I be permitted by Thee\\
  And can move in no direction \\
  until I obtain Thy sanction\\
  It is Thou, O my God, \\
  who hast called me into being through the power\\
  Of Thy might, and has endued me \\
  with Thy grace to manifest Thy Cause
}

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  Bread of Bitterness
}{
  From a supplication without response, \\
  the essence of man, his ground giving way, \\
  comes illumination by a sun of great evil \\
  that sets aflame the inner core \\
  and enthrones suffocation and the intolerable without respite \\
  as the joyful reward for a million aborted truths.
  
  This silence that among all man has charged with sacred horror, \\
  it becomes sovereign, in repugnant nativity, \\
  and detaches itself from the bonds \\
  which paralyse a vertiginous movement towards the void.
  
  Breathless ecstatic experience,\\
  it opens the horizon a bit more,\\
  this wound of God;\\
  it is the assassination of the abyss of possibilities, \\
  the depths of being left to holy vultures. 
}






\subsection{The portal opens}
\Lithrim{} opens the way for the \Voidbringer. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Perfect Dark%
}{
  Hold the candle\\
  Pass the flame\\
  We're all in this together \\
  Cosmic winds are gathering\\
  Coming your way\\
  Telling you you are only a fragment\\
  A fragment of time 
  
  And it's perfect dark\\
  It's perfect dark here\\
  Hear the angels screaming
}





\subsubsection{People feel the \Voidbringer}
As the Cabal plot nears fruition and they are opening the gate to \Erebos, \Miithians can feel the presence of the \Voidbringer: 
An ever hungry, ever consuming emptiness, completely inhuman. 
The older immortals remember it from the \secondbanewar. 





\subsubsection{\Banes{} slip through}
Many \lesserbanes{} slip through into \Miith. 
Not in the same millions that got through in the \secondbanewar, but still quite a lot. 
But not so many that the combined \dragons{} and \resphain{} cannot deal with them\ldots{} hopefully. 

















\section{Ramiel the Betrayer}
\target{Ramiel betrays Voidbringer}
\target{Ramiel betrays Banes}









\subsection{Summary}
\hs{Ramiel} has decided that he will no longer serve the \banelords. 

\lyricsbs{Dream Theater}{In the Presence of Enemies}{\obeylines%
  My soul grows weaker.\\
  He knows and he waits.\\
  He watches over me,\\
  standing at the infernal gates.\\
  In the hour of darkness,\\
  the moment I feared has passed,\\
  the moment I lost my faith.\\
  Promising salvation.\\
  My soul is my own now.\\
  I do not fight for you,\\
  Dark Master!
}

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Hellfire%
}{
  Before me now I see a dying planet.\\
  Captured souls with microchips implanted.\\
  When warning came you stayed the same.\\
  When warning came you stayed the same.\\
  I am crumbling over the obstacles.\\
  Nothing left to entertain. \\
  The smell of burning corpses. \\
  A new world domain.
  
  Before me now I see a future\\
  A future black\\
  Oh come and save me\\
  I'm under soul attack
  
  I will break out from this madness\\
  There is nothing here but sadness\\
  I'm burning in the hellfire\\
  There must be a way\\
  Waiting for the day\\
  
  Hellfire burns higher\\
  Higher, higher. \\
  Only blood remains\\
  There is nothing more to gain \\
  Take me.
}

He now plans to betray the \banes. 
He intends to siphon energy from the \Voidbringer, thus empowering himself enough to overpower \Daggerrain{} and slay or banish him. 
It is a mad scheme, but Ramiel has always been one for mad schemes. It stems from his sublime arrogance and megalomania (see section \ref{Ramiel's megalomania}). 

It is a good plan, but \Daggerrain{} is too clever. 
The \banelord{} has always known that Ramiel was a loose cannon and could not be trusted, so he had taken precautions. 
When Ramiel finally betrayed the \banes, they were ready for him. 

So Ramiel's plan fails\ldots{}

\ldots{} or would fail, if not for the intervention of \Azraid. 
\Azraid{} had always played the loyal Cabalist, faithful servant of the \banelords, but \hr{Azraid hates Banes}{in secret he has always hated them} and \hr{Azraid plots against Banes}{plotted against them}. 
He anticipated Ramiel's betrayal and planned for it. 
So when Ramiel fails, \hr{Azraid helps Ramiel betray Banes}{\Azraid{} steps in and helps him}. 

\ps{\Azraid} gambit cannot succeed without Ramiel's help. 
But he cannot tell Ramiel about it before the very last minute, because he doesn't trust Ramiel's ability to keep the secret. 
(It is \emph{hard} to keep secrets from \Daggerrain.) 
It is thus something of a \trope{XanatosRoulette}{Xanatos Roulette}. 

So, in the end, it turns out that \Azraid{} was \hr{Daggerrain's blind spot}{\ps{\Daggerrain}{} blind spot}. 





\subsubsection{The Ark}
\target{Ark}
\index{Ark}
The plan (a collaborative effort between \Azraid{} and \Ishnaruchaefir) is to use the wild threads of the collapsing Shroud to \quo{cut} free a chunk of \Miith{}, forming a pocket Realm. 
They then hope to be able to close the way behind them, setting up a makeshift barrier by piecing together fragments of the shattered \CrystalSphere{} and Shroud.

They will then have formed a new mini-Realm, a micro-\Miith{} torn loose. 
This will be their Ark. 
A small population of \Miithians should be able to escape in this Realm. 
The makeshift barrier will keep the \banes{} out for a short while, while the masterminds use their magic to twist the fabric of space around them propel the Ark away through the universe, to a place where the \banes{} cannot easily find them. 

It will be fucked-up difficult, but \Azraid{} is ready. 
He has spent millennia preparing for this day, and he is prepared to sacrifice his life to see it through. 
And he has \ps{\Ishnaruchaefir} awesome Gnosis helping him. 

In the end, \Ishnaruchaefir{} and Ramiel end up on the Ark, while \Azraid{} destroys himself in the process. 

Perhaps the Ark is not a chunk of planet, but a spaceship. 
Perhaps a commandeered \bane/\resphan{} ship. 
If so, it is huge. 
A colony ship. 
A world-ship. 





\subsubsection{It all takes place in the \matrix{} world}
Note that all of this takes place in the world of the \matrices. 
The three may not physically meet at all. 
They simply pull at cosmic strings using their \vertex{} abilities. 
Any any \quo{portals} are not physical portals, but a ubiquitous thinning of the Shroud allowing passage into \Erebos{} or somewhere else. 





\subsubsection{Why they wait so long}
One might think \Azraid{} could have betrayed the \banes{} long ago. 
But that would not have worked. 
He was not confident he could have done enough damage before he was caught, eliminated and replaced. 

No, this is a unique opportunity. 
\ps{\Azraid} betrayal has to happen \emph{after} the advent of \Lithrim. 
See, they need to rely on the Shroud-wide chaos and fluctuations that \Lithrim{} creates, and use them to set the Ark free. 









\subsection{Ramiel drains the \ps{\Voidbringer}{} power}
Ramiel tries to betray the \Voidbringer. 
This is similar to how Astronema betrays Dark Specter and drains his power in \emph{Power Rangers in Space}. 
%It stems from Ramiel's sublime arrogance and megalomania (see section \ref{Ramiel's megalomania}). 

He absorbs some of the \ps{\Voidbringer}{} power. 





\subsubsection{How it feels}
He feels himself swimming adrift in an endless, bleak ocean of dark, Entropic power, feels how it almost devours him and his sanity.

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{
  The ravening black worms of madness 
  are devouring the shredded remnants of sanity 
  as I return to my slumbering steel-clad body\ldots{} \\
  but as the dream-veil lifts, I feel my limbs transform, 
  flesh becoming cold stone\ldots{} \\
  enshrouded by a dark mantle of obsidian. \\
  And the laughter of the Guardians echoes, 
  carries upon the winds of this spectral eve.
}

Actually, he began doing this much earlier, but it takes a while before \Daggerrain{} \quo{discovers} his treachery. 





\subsection{Ramiel fails}
\target{Ramiel as Xanatos Sucker}
\Daggerrain{} is too clever for Ramiel. 
He had anticipated Ramiel's betrayal and easily stops him. 
He is about to kill and destroy Ramiel\ldots{} 

Before his death, Ramiel's life flashes before his eyes. 
He realizes that \Daggerrain{} must have anticipated his every move and planned accordingly. 
He has been playing straight into \ps{\Daggerrain}{} hands the whole time. 

He truly \hr{Ramiel is nothing}{is nothing}\ldots{} 
or so he fears. 

Compare a \hr{Azraid as Xanatos Sucker}{similar scene with \Azraid{} much earlier}. 
Also compare to the scene in \emph{\JuukenSentaiGekiranger} episode 46 (or so) where Rio discovers that his entire life has been masterminded by Long. 

We see inside Ramiel's head as he struggles against \Daggerrain{} and almost dies. 

\lyricsbs{Hate Eternal}{Path to the Eternal Gods}{
  On this journey into death, \\
  I am beside myself in tremendous bliss,\\
  For this allegiance has been made. \\
  Shall my sins be absolved, \\
  washed away by the blood of the sacred lambs? \\ 
  Yet I am not amongst the flock.
  
  The remnants of my life now become my vast illusions,\\
  whilst exiled from your grace. 
  
  With fortitude, with courage, 
  I face all my fears, \\
  on my path to the eternal gods. \\
  With my wrath, with my disdain, 
  I face all my fears, \\
  on my path to the eternal gods.\\
  As I cross over into my final place, 
  I face all my fears, \\
  on my path to the eternal gods.\\
  As I bear trials in my final resting place, 
  I face all my fears, 
  on my path to the eternal gods.\\
}





\subsection{\Azraid helps Ramiel}
\target{Azraid helps Ramiel betray Banes}
At the last moment, before \Daggerrain{} would have destroyed Ramiel, \Azraid{} steps in and backstabs \Daggerrain. 

Ramiel realizes that he had been overreacting before, overestimating \ps{\Daggerrain}{} omniscience and underestimating his own capability. 
Some parts of his plan actually \emph{were} successful, not covered by the \ps{\banelord}{} \trope{XanatosGambit}{Xanatos Gambit}. 
He regains some faith in himself. 

Together, the two \satharioth{} push \Daggerrain{} back. 
% It closes behind him. 
Ramiel now manages to hold \Daggerrain{} occupied while \Azraid{} works his magic and tears the \hs{Ark} loose. 





\subsubsection{Ramiel and \Azraid{} as kindred spirits}
\Azraid{} criticizes Ramiel for being too overt and honest (\hr{Mystraacht philosophy}{and would be expected of a \Mystraacht}), making him predictable. 
In contrast to \Azraid{} himself, who has managed to creep under even \ps{\Daggerrain}{} radar for twenty thousand years. 

But he is also sympathetic, because he recognizes that Ramiel's situation is like a mirror of his own. 
Back when \Daggerrain{} manipulated the young \Azraid{} into betraying and murdering his brother \Damiarch, he was similarly shocked and disillusioned. 
He shares this with Ramiel. 
This is a rare \trope{PetTheDog}{Pet the Dog} moment for \Azraid. 

A new understanding and empathy suddenly exists between the two \resphan{} lords. 
They are now kindred spirits. 
After this battle they part, not as friends, nor allies, but with a deeper mutual respect than previously. 

\begin{prose}
  Ramiel: 
  \ta{\Azraid. Were you among those who betrayed \Zachirah{} and me?}

  \Azraid: 
  \ta{LOL. Ramiel. 
    I have deceived the \banelords{} for thousands of years. 
    I have deceived everyone. 
    Among all the \resphain, there is no greater fraud than I.
    If I were to answer \quo{no}, would you believe me?
    I would not believe me.}
\end{prose}






\subsubsection{Ramiel imagines hearing \ps{\Daggerrain}{} voice}
Ramiel jokingly imagines hearing \ps{\Daggerrain}{} voice in his head: 
\daggerrain{A minor setback. 
I have planned for this contingency. 
It will take us another 3651 years to get out plan back on schedule\ldots{}} 
(The number 3651 is a random one that Ramiel pulls out of his ass, but it sounds like something \Daggerrain{} might say.)








\subsection{\Azraid dies\ldots{} maybe}
\target{Azraid dies}
Maybe \Azraid{} dies. 
He sacrifices himself in order to violently disrupt the \Erebean{} \matrix{}, thus causing it to implode and collapse faster than \Daggerrain{} can restore it to order. 

\ps{\Azraid} death leaves \CiriathSepher{}, its hierarchy and \matrix, in chaos. 
(\hr{CS heirs die}{Not much is left} of the \hr{CS order of succession}{\CiriathSepher{} order of succession} at this time.)
It is now up to Ramiel to pick up the pieces and lead the \resphan{} race, if they are to have a chance of surviving. 

Compare to Anomander Rake's sacrifice in \cite{StevenErikson:TolltheHounds}. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Surrender\\
  Lost in the dark\\
  Without angels to guide me 
  
  Hands of death reaching out for me\\
  I'm longing to rest\\
  I see myself move in need of power
}

He knows the \banes{} better than any other. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  I've looked straight into the eyes of demons rising\\
  So close.\\
  I've had one foot on the other side\\
  For so long. \\
  I've seen evil so evil that all living died\\
  The devil is near.\\
}

He wants to stop the \iquin{} plan. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  You may fool the people, but you can't fool me\\
  No more, not anymore. 
  
  And all the souls turned black\\
  There is no way back
}

He dies. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Stranded with the darkness\\
  It's so cold in here \\
  I feel the rush within me
}

He hopes that \Miith{} (or a fragment of it) now has a future. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Time will mend\\
  Ease the sorrow\\
  Take my hand\\
  There's no tomorrow
}











\subsection{\Daggerrain falls}
\target{Daggerrain falls}
\Daggerrain{} has fallen. 
And the worst part is that the link between \Erebos{} and \Nyx{} fell with him. 
\hr{Daggerrain is the gate}{\Daggerrain{} \emph{was} the link}. Without him, the way is closed permanently. 
Now, the only way for the \banes{} to return from \Erebos{} would be to send spaceships, like they did the first time around. 
That might take millennia, because \Erebos{} and \Miith{} are very distant from each other. 





\subsubsection{\HothNrul{} left behind}
\target{Hoth-Nrul left behind}
\HothNrul{} ends up the same place where \Daggerrain{} is. 
No one knows what becomes of it. 
Perhaps it gets destroyed by \Daggerrain{} and his fellow \banelords\ldots{} if it is even possible to destroy a \xs, which is not known. 
Or perhaps it returns to the \xs{} homeworld. 

Or perhaps it wins. 
It is very difficult to get a clear idea of the balance of power between so \uber-powerful beings as \xss{} and great \banelords. 

The survivors of the war are not sure \HothNrul{} will not return to wreak more havoc on them. 
But they hope not. 















\section{The Fall of the Shroud}
\subsection{\ps{\Ishnaruchaefir} glaive is destroyed}
\target{Ishnaruchaefir's glaive is destroyed}
\target{Glaive is destroyed}
Throughout most of the story, \hr{Ishnaruchaefir fights to preserve the Shroud}{\Ishnaruchaefir{} has fought to preserve the Shroud}. But at the end, he lets himself persuade to assist in unravelling the Shroud. \Triestessakhin{} is the one who persuades him. 

Ultimately, \hr{Ishnaruchaefir's glaive}{\ps{\Ishnaruchaefir} glaive} is destroyed, its Shroud-weaving effect (as a \hs{weaving artifact}) is broken, and the soul of \Triestessakhin{} is released. 
\hr{Glaive must be destroyed}{This had to happen}. 

She is quite insane after these many thousand years inside the sword, but he manages to lead a conversation with her. She is bitter and tries to make him repent. 

\Ishna: 
\ta{%
  I mourn what I have done, and at times I even regret. But I would not change it, and given the chance, I would do the same again.}

Compare to the scene with Lord Soth and his wife at the end of \emph{Spectre of the Black Rose} by James Lowder and Voronica-Whitney Robinson. 



% \subsection{Daggerrain's epilogue}
% In the end, the \banes{} are defeated and the way to \Erebos{} is sealed shut once more. 
% 
% In the very last chapter, \Daggerrain{} holds a monologue, telling his subordinates to get to work. Having planned for this contingency, he has a new plan to reclaim \Miith{}, another four thousand years from now. As he says: \daggerrain{I have waited thirty thousand years. Another four thousand is nothing to me.}







\subsection{\Vizsherioch falls asleep}
\target{Vizsherioch falls asleep}
\Vizsherioch{} \hr{Vizsherioch's XS blood}{has too much \xsic{} blood} and is susceptible to the \hr{XS slumber}{\xsic{} slumber}. He uses his \bane{} blood to draw upon \Erebean{} power to negate this effect. 

But when \hr{Daggerrain falls}{\Daggerrain{} falls}, his connection to \Erebos{} fails and he falls prey to the \xsic{} slumber. 







\subsection{\Miith is once again in \Miithian hands}
\hr{Daggerrain falls}{\Daggerrain{} is gone}. So now the supreme leaders of the \resphain{} are Ramiel and \hr{Azraid}{\Azraid}. There are still \banelords, but they cannot replenish their number, so they will eventually be hunted down and destroyed. 

Similarly, \Vizsherioch{} falls prey to the \xzaishannic{} slumber. The lords of \dragonkind{} are \Ishnaruchaefir{} and some other \uber-dragons. 

The \Erebean{} and \Machaic{} overlords are gone, and only their descendants remain. The future of \Miith{} now once again belongs to \Miithian{} powers. 









\subsection{The Shroud is torn}
In the process of this whole thing, the Shroud has been ripped and torn and now lies greatly weakened. A climax of this was the \hr{Glaive is destroyed}{breaking of the glaive \Triestessakhin}. 

The \charade{} is breaking apart and the old world order is crumbled. 

The \hs{Unravelling brings chaos}. 
The world will descend into chaos and anarchy. 

\lyricstitle{\cite{HPLovecraft:TheCallofCthulhu}}{
  The most merciful thing in the world, I think, is the inability of the human mind to correlate all its contents. We live on a placid island of ignorance in the midst of black seas of infinity, and it was not meant that we should voyage far. The sciences, each straining in its own direction, have hitherto harmed us little; but some day the piecing together of dissociated knowledge will open up such terrifying vistas of reality, and of our frightful position therein, that we shall either go mad from the revelation or flee from the deadly light into the peace and safety of a new dark age.
  
  [\ldots{}]
  
  That cult would never die till the stars came right again, and the secret priests would take great Cthulhu from His tomb to revive His subjects and resume His rule of earth. The time would be easy to know, for then mankind would have become as the Great Old Ones; free and wild and beyond good and evil, with laws and morals thrown aside and all men shouting and killing and revelling in joy. Then the liberated Old Ones would teach them new ways to shout and kill and revel and enjoy themselves, and all the earth would flame with a holocaust of ecstasy and freedom.
}

A new world order will establish itself, although it may take centuries. 

\index{technology}
\Ishnaruchaefir{} predicts that the Shroud will mostly unravel and fade away. With the loss of the Shroud, \hs{technology} will again accelerate. 

A suggestion for an epitaph: 

\lyrics{
  The \charade{} is broken. \\
  The Shroud is sundered. \\
  Now, let the arms race begin.
}

Knowledge will escalate, and so will war. 
In a way, this is \hr{Ishnaruchaefir sees three futures}{\ps{\Ishnaruchaefir} nightmare} come true. 

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\ldots{} 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}





\subsubsection{The Space Age begins}
Both races will now venture into space, looking for new \dweomers{} to consume to feed the dying Heart. 




\subsubsection{The \banes{} still exist}
Make it clear that the \banes{} have only been banished, not destroyed. 
\Daggerrain{} still lives. 
He will be back. 
\Miith{} has gained a reprieve. 
Maybe a thousand years. 
Maybe less.
However long or short it takes, the \banes{} \emph{will} return. 

So all this talk about \quo{evolution towards perfection}, which obsesses both sides in the Feud, is more relevant than ever, if Mith is to prepare itself and be ready to face the \ps{\Voidbringer} attack a \emph{fourth} time. 






\subsubsection{A respite for the Heart}
\target{Respite for the Heart}
The Heart of \Miith{} is finally freed from \hr{Heart weakened}{the scourge of the \sephiroth{} and the \Morbus}. 
The millions upon millions of imprisoned souls finally die and are released back into the Heart. 
This lets the Heart regain some of the stolen lifeforce and thus grow in strength. 

But this is just a temporary respite. 
The menace of the \banes{} is gone, but the remaining two master races (\dragons{} and \resphain) still battle for control of the Heart. 
The two races \emph{cannot} coexist\dash their \matrices{} are inherently incompatible and inimical, ripping and tearing into the Heart\dash and the Heart will continue to be drained and weakened until this war comes to an end. 

So the war for the Heart escalates again (as per the \quo{arms race} above). 
After all, this is what the Heart is: 
Life and death, beauty and ugliness, love and cruelty. 
Nature. 

\Miith{} is a cruel world. 





\subsubsection{Ramiel rules}
The old world order has crumbled. 
Ramiel is now the lord of the \resphain.

\citebandsong{Arcturus:AsperaHiemsSymfonia}{Arcturus}{
  Raudt og Svart
}{
  Deira dagar har m\o rkna\\
  Moder jord meld sitt fraafall\\
  Men sverdet har gaat vidare\\
  Til ein ny b\ae rar
  
  Me er einsomme menn\\
  Me b\ae r fenresulvens muspell\\
  Skoll skal sluka sola
  
  Me er djerve menn\\
  
  Sola svartner\\
  Der fjellvegg ramlar\\
  Naa gjestar sorgen\\
  Paa livets tre \\
  Yggdrasil
  
  For byleits bror farar\\
  Kva er det ikkje Kampfar klarer?
}





\subsubsection{Ramiel and \Ishnaruchaefir}
Ramiel and \Ishnaruchaefir{} are on the Ark and chatting. 

\begin{prose}
  \Ishnaruchaefir:
  \ta{Perhaps the \banelords{} will find us again.
    Perhaps not.
    Perhaps there will one day be peace between our two peoples.
    Perhaps one of our races will become extinct\dash or both.
    Perhaps we will somehow find the means to wage war for all eternity.
    Who knows?}
  
  Ramiel:
  \ta{%
    We \resphain{} have always held that science is one of our greatest weapons and assets.
    We know\dash or believe\dash that we are set in the world to rise above our nature.
    I will take command of the \resphain{} here, and I will see to it that we rise to our fullest potential.
    I am Overlord now\ldots{}}
  
  \Ishnaruchaefir:
  \ta{Overlord of what?
    I doubt any traces of the old world order have survived the exodus of the Ark.
    I doubt that \Mystraacht{} even exists anymore.}
  
  Ramiel:
  \ta{I have seized a throne by force before and I can do it again.
    And know this: 
    My goal is to secure the future of \Mystraacht.
    No one else's. 
    Maybe this road will end in peace.
    But if I must destroy your people\dash or any other\dash so that mine may live, then so be it.}
  
  \Ishnaruchaefir:
  \ta{Heh. So be it.}
\end{prose}

Remember that after the exodus of the Ark, \Mystraacht{} does not really exist anymore. 
So Ramiel is no longer Overlord. 
But:

\begin{prose}
  Ramiel:
  \ta{I have seized a throne by force before and I can do it again.}
\end{prose}







\subsubsection{\Ishnaruchaefir{} looks forward}
The very last scene of the book is with \Ishnaruchaefir{}.
He looks forward the chaos and war that is to come. 
No longer will he hide and huddle in some Asylum. 
He will fight. 
It will be\ldots{} exciting. 

Remember: \emph{End on a dark note!}









\subsection{The cost of the \thirdbanewar}
The \thirdbanewar{} is the most costly and most apocalyptic of the three \banewars. 
It did not kill as many people in absolute numbers as the first two had done, but it killed a larger percentage of the population. 
The population is smaller at this time, remember. 

\Daggerrain{} is now gone, but \Miith{} has paid a terrible price. 
Ahead wait centuries of chaos, blood and war. 














\section{The Future}
After a thousand years or two, a new interstellar civilization centered on \Miith{} will be established, and a \quo{science fantasy} aera will begin. Compare to \emph{Warhammer 40.000} and \bandalbum{Bal-Sagoth}{The Power Cosmic}. 









\subsection{\Resphan/\dragon hybrids}
Perhaps some day in the far future, someone will begin experimenting and trying to create a race of \resphan/\dragon{} hybrids. 
These will try to conquer the races and destroy those who will not join them. 
This is seen as evil, but the intent is good: 
Only a hybrid race can stop the war and let the Heart of \Miith{} live on in peace. 









\subsection{New cosmic empire}
In the far future, after the exodus from \Miith, the \dragons and \resphain ended up ruling each their vast interstellar empire spanning dozens or hundreds of planets. 
They became super-technological and super-magical civilizations close to rivalling the \voyagers in technology, but far surpassing them in aggression and greedy ambition. 
The \voyagers were a peaceful (if decadent) race of scientists and explorers. 
The exiled \Miithians were warriors and conquerors at their very core.

At this time, the \dragons and \resphain had found new \dweomers to sustain them, so they no longer had to fight each other for possession of the Heart of \Miith. 
But they were warriors by nature and instinct, so they still fought one another. 























\chapter{Random Ideas}












\section{\Shilred{} Story Arc}





\subsubsection[Ishnaruchaefir and his fake mission]{\Ishnaruchaefir{} and his fake mission}
\target{Ishnaruchaefir's fake mission}
\Ishnaruchaefir{} is clever. He knows about \hr{Teshrial's creatures}{the \noggyaleth{} in \Malcur}, or at least suspects them. So he \hr{Ishnaruchaefir attacks Teshrial's creature}{goes there to see for himself}. 

\Ishnaruchaefir initially believes \Secherdamon's plan takes place in \Malcur.
Then he falls for the \Forclin decoy when it is unveiled. 
He is impressed to learn that both were decoys. 

He has also seen through \ps{\Secherdamon} plan to resurrect \Nithdornazsh{} in \Malcur. 
He has more Sentinel contacts than most people realize, so he has spies telling him of \ps{\Secherdamon} plans. 
And he is an expert astrologer and \matrix-theorist, so he has picked up subtle clues concerning \Nithdornazsh{} and \Malcur. 

He knows that the \noggyaleth{} may put a stop to the plan. 
He wants to help his brother.
He does not fully approve of \ps{\Secherdamon} plan to resurrect \Nithdornazsh, but he helps out of respect for \hr{Nexagglachel}{\Nexagglachel}, since he still feels guilt and obligation towards him and his memory. 
\Nithd{} was \ps{\Nexagglachel}{} fortress, after all, so it can stand as a monument of sorts to the fallen \dragonking.

\target{Ishnaruchaefir's creatures}
So \Ishnaruchaefir{} plans to free some of his own servitors\dash\pdaemons, \dragons{} or otherwise\dash who are imprisoned in a cave or lost temple somewhere in the eastern \PelidorContinent. 

But he can't just go off and do that. He would be discovered and foiled by \hr{Teshrial}{\Teshrial}, the Cabalist in charge of the area around the cave. 

So \Ishnaruchaefir{} develops a circuitous plan: 
\hr{Ishnaruchaefir recruits Shilred-tachi}{He recruits \Shilred-tachi} and sends them off to fulfill an ill-defined quest for him, in the general area of the cave in question. He tells them to search for a cave or something like that. 

But whatever he alludes that he wants them to do is a lie. The purpose of their entire mission is to look suspicious. \Ishnaruchaefir{} shows up to help them just often enough that the sneaky Cabalists cannot help but notice, yet rarely enough that it still looks like he is trying to lay low. 

What he is actually looking for is another cave, where his servitors are imprisoned. 

The Cabalists in the area where \Shilred-tachi are going are led by \Teshrial{} (see section \ref{Teshrial}). We follow him in several chapters, where he fears \Ishnaruchaefir{} and tries to guess his plan. 






\subsection{Rissitic invasion}
Some time after the Rungerans cross the Pelidorian border, Rissitic fleets sail north to besiege and conquer cities in \Scyrum. 
%march north from Gaznor into Beirod. They besiege and conquer Beirodi cities. 

%Or\ldots{} wait\ldots{} is it Beirod they attack? Or is it \Scyrum? \Scyrum{} might make more sense. 

For the Rissitics, controlling more land in \Velcad{} is nice, but the chief purpose of this attack is to draw the Redcor away. See, in intra-\Velcadian{} wars the Redcor traditionally take little part, acting mostly as negotiators and healers. But in case of a major attack on an Iquinian kingdom by a heathen invader, the Redcor typically offer more direct aid, participating in battles with their magic. So when the Rissitics invade, the Redcor are forced to send Vaimons from the entire region to help oppose them. 
This makes the invasion harder, but it has the nice bonus feature that it leaves \Malcur drained of Redcor, making it easier for the Sentinels to operate there. 

We follow Narkiza on his march north through \Scyrum. 

%Is Geldashad with him, or is he off on a mission of his own?

%What about \Shilred? 

Remember to describe the Rissitic army as \hr{Glorious armies}{magnificent and glorious}.







\subsection{\Shilred-tachi get lost in \Nyx}
\Shilred{}, \Dzasselid{} and \KarsaOrlong{} (see \ref{Karsa Orlong}) take part in the initial attack on a port city in southern \Scyrum. Maybe they are together with Mestos and Semphai. Anyway, during the battle they become separated from the main army and nearly get killed by \banes. %Maybe they even flee out of the mortal Realm and stumble into \Nyx. 

Maybe \Dzasselid{} deliberately takes them into \Nyx. Perhaps he has a back-story as a double agent for the Cabal, and thus knows his way around in \Nyx. Or something like that. He needs some skeletons in his closet, remember?

At any rate, they end up in \Nyx{} and get surrounded by \banes{} or other monsters. 






\subsubsection{\Ishnaruchaefir{} approaches}
Just when \Shilred-tachi are about to be killed, \Ishnaruchaefir{} appears. He appears in humanoid form. Using magic (incl. the spell \quo{\kingstongue{khestni}}) and his mighty glaive (see section \ref{Ishnaruchaefir's glaive}), he slays the monsters and saves them. The monsters should be huge, monstrous and menacing, like in the anime \emph{Devil May Cry}. 

Given that they owe him their lives, he claims them as his own. Perhaps one of the \Gisshorns{} knows who he is and convinces the others to be respectful. Somehow or other, \Ishnaruchaefir{} beats it into their heads that he is a high-ranking ally of Rissit and that they should obey him. 

Maybe \Ishnaruchaefir{} first approaches \Narkiza{}, gives a little help and asks to borrow some of his men. 






\subsubsection{\ps{\Ishnaruchaefir} mission}
\target{Ishnaruchaefir recruits Shilred-tachi}
\Ishnaruchaefir{} sends them on a private, secret mission. He wants them to find a cave somewhere in western \Velcad{}, where they must do fulfill some as-of-yet unspecified task for him. 

\Ishnaruchaefir{} tells them that he cannot go off searching for the cave himself, as he would be detected and attract Cabal attention (and Sentinel attention, for that matter). But he teaches them an invocation that will summon him, to use when they reach the cave or are in dire need of his help. 

\hr{Ishnaruchaefir's fake mission}{The above is actually a lie.}







\subsection{\Shilred-tachi go into the \Wylde}
On their mission for \Ishna, \Shilred-tachi must go into the \Wylde{}. \Ishnaruchaefir{} throws them into some place which has a tenuous link to \Nyx. Perhaps a cave system that was once inhabited, or a ruined castle. It must be something sort of urban area, since \Nyx{} is city-like. 

From there, they go out into the \Wylde{}. They fight their way through monster-infested jungles. 

Maybe they encounter a native tribe. Maybe they help them, like how Karsa Orlong helps the Anibar in \emph{The Bonehunters}. Maybe they just coerce them into accepting them. Maybe they hire native guides, who later die. 

They are chased through the \Wylde{} by savage monsters, maybe zombies or lycanthropes. Monstrous almost-humanoids, at any rate. Occasionally they are harassed by the Cabal. 







\subsection{\Shilred-tachi find a ruined city}
\Shilred-tachi find a ruined city out in the wild, with broken walls, toppled towers, defaced monuments and statues and the like. It is decrepit, dead, moss-grown and spooky. 

Compare to the cemetery in the movie \cite{Movie:HouseoftheDead}. 

Remember to have some references: 
\ta{%
  There are many places of power in the world, places of convergence. Especially out in the \Wylde{}. After all, the \Wylde{} is far vaster than the settled world.}

Remember to have them fight monsters. Have a scene where \Dzasselid{} kicks the butts of loads of monsters. 







\subsection{\Shilred-tachi find a laboratory}
\Shilred-tachi fight past monsters and end up in the laboratory of some necromancer or witch-doctor. It is filled with mutilated corpses and deformed creatures\dash living, dead or undead. Like in the movie \cite{Movie:HouseoftheDead}. 







\subsection{\Shilred-tachi crawl around underground}
\Shilred-tachi find themselves underground in a system of dark, creepy, monster-infested caves. Like in the movie \cite{Movie:HouseoftheDead}. 








\subsection{\Shilred{}-tachi see great monsters in the distance}
%Remember \Shilred{} and her party. They need to do something intelligent. 
\Shilred-tachi, travelling in the \Wylde{}, see some colossal creatures far off in the distance. They need to be at some special place or in special circumstances, being able to see into the Beyond, in order to be able to see them. 

Maybe they see the creatures on a background of \Nyx{} or \Machai{}, or maybe just the great mountains and forests of the Beast Realm (these are larger than the ones that can be seen from within the Shroud). 

Perhaps the creatures are \dragons{} and \banes{} fighting. 

Perhaps, in the end, they see \Ishnaruchaefir{} vs \Teshrial-tachi this way. 

Remember to drop hints along the way about how powerful and terrible \Ishnaruchaefir{} is. Perhaps when they see these monsters, they reflect about \Ishnaruchaefir{} and his awesome power. 







\subsection{\Narkiza{} on the move}
%Early on, we follow \Filshed{} and her party as they invade Fendor. 

We follow \Narkiza{}, first in the port city in \Scyrum, and later as his army pushes north into \Velcad{}. His invasion is one of several \quo{prongs} in the Sentinel scheme.

In \TwilightAngelRememberEmph, only little time is devoted to \Narkiza{} and the other Rissitics. They will be given much more screen time in \emph{\CarzainWithRedcorBook}. 
%in the scheme to awaken the \Haskelek, 

%\Filshed{}, maybe together with the two \Gisshorn, are sent as a second \quo{prong} on covert missions to revive parts of the \Haskelek. 

%A third \quo{prong} are the Rissitics that are with Morgan Runger. 

%There might be a fourth \quo{prong}, consisting of some non-Rissitic Sentinels. They might include \Cryocas{} and her lover, Nisgzarchiev. Or maybe Vlad Racul. 










\subsection{\Shilred-tachi reach the cave}
\target{Shilred-tachi reach the cave}
\Shilred-tachi finally reach their destination. 





\subsubsection{They see fantastic and terrible things}
They near the cave and travel through fantastic, alien Realms (perhaps parts of \hr{Machai}{\Machai}). Compare to \authorbook{Clark Ashton Smith}{The Door to Saturn}. 

They even see glimpses of the \xss. 
\Shilred{}, \hr{Shilred is a nerd}{being something of a nerd}, is amazed by what she sees. And horrified.

\lyricslimbonicart{When Mind and Flesh Depart}{
  I'm captured by the sound of the tempest winds, \\
  and my demonvoice that dwells within.\\
  The ground I walk is sour.\\
  A spectrum shines so genuine.\\
  While the earthquake starts to devour,\\
  I behold the shrine in the ruin.
}

She sees horrors and is disillusioned. 

\lyricslimbonicart{When Mind and Flesh Depart}{
  The human way of life, \\
  an inferior state of mind.
  The third stone from the Sun\\
  had become a stillborn illusion.
  
  I'm under siege of anger and fury.\\
  There is no values, no faith or glory.\\
  Antagonising mortal flesh.\\
  Life on Earth I do oppress\\
  with infernal bleedings of bitterness.
}






\subsubsection{\Teshrial{} moves out}
\Teshrial{} fails in his attempts to guess \ps{\Ishnaruchaefir} thoughts. 
When \Shilred-tachi ostensibly reach their destination\dash the main entrance to the cave\dash they are attacked by \ps{\Teshrial} monsters and must call on \Ishnaruchaefir. 
He appears in humanoid form to fight the monsters. 
\Teshrial{} is now convinced that \Ishnaruchaefir{} means business, so he rushes to his location in person, leading a group of mighty \banes{} and monsters. 





\subsubsection{Epic description of \Ishnaruchaefir{} as a \dragon}
\Ishnaruchaefir{} assumes his true, \draconian{} form. Insert an epic description of the mighty \dragon{} here, a la \bandsong{Bal-Sagoth}{Black Dragons Soar Above the Mountain of Shadows}. 

This is the first time we are shown a \dragon. 
Describe the mortals' awe at the sight. 
\Dzasselid{} might have seen one before, but \Shilred{} sure hasn't. 
She has heard \hs{myths} of \dragons{}, but reality surpasses the myths. 





\subsubsection{\Dzasselid-tachi are sent to the real cave}
\Ishnaruchaefir{} draws out all the Cabal monsters in the area. 

In the meantime, \Criseis{} sees to it that \Dzasselid-tachi are sent to the \emph{real} cave he is after\dash which is now mostly unguarded. 

They encounter some creatures that try to block their way. 
\Criseis{} zaps them.

\lyricsbalsagoth{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire - Part II: The Dark Liege of Chaos is Unleashed at the Ensorcelled Shrine of A'zura-Kai
}{
  [THE KING:]\\
  By the darkling powers of the Shadow-Sword, \\
  I call forth the fury of the storm\\
  to rend the massed legions of Chaos!
  
  [ALTARUS:]\\
  And at the sound of his baleful Words of Power, \\
  the sky split wide in fury, \\
  and searing tendrils of ruinous lightning \\
  lanced inexorably forth from the heavens \\
  to rake and reave the massed hordes of Chaos\ldots{}
}

They find the creatures they are looking for and set them free. Thus \Ishnaruchaefir{} has tricked \Teshrial{}, and his circuitous plan has succeeded. The freed monsters now rush to \Malcur to assist in the summoning of \Nithdornazsh. 

See \hr{Ishnaruchaefir kills Teshrial}{here} for the end of the fight.






\subsubsection{\Shilred{} is left behind near the cave}
\Shilred{} accidentally gets separated from the rest and stays behind near the cave. 
She gets to see the fight between \Ishnaruchaefir{} and \Teshrial{} in all its gory glory. 















\section{Sir James story arc}
Sir James is a \human{} Iquinian knight living somewhere in \Velcad{}. 
It might be in the east, if I want him connected to the king-thing and Vlad Racul, or it might be in the west (Ontephar or \Scyrum) if I want him connected to Telcastora Ilcas. 
I think it's going to be in the east. 

There is also Sir Lawrence, another knight. 
Perhaps Sir James' companion. 

And Prince Alistair, who later becomes King Alistair. 
I think. 

And Vlad Racul, a mysterious sorcerer who is actually the \dragon{} Candrazor (a high-ranking Sentinel) in disguise. 

Sir James discovers a Rissitic plot somewhere. 
The Rissitics work on resurrecting a part of the \Haskelek{} \daemon. 
He goes to the Redcor for help. They set out to thwart the Rissitics. 
It turns into a big quest with all sorts of stuff going on. 
There's an evil Rissitic mastermind (who?) who keeps outsmarting them, but somehow the reader is assured that good will prevail. 
And then, in the end, I assfuck the reader by having the Rissitics win, and Sir James and his party of heroes are killed. 




\subsection{The beginning}
Sir James, as a knight and minor lord of sorts, is approached by the girl Lica, a commoner who's had visions, seen suspicous things. 
His advisors scoff at the girl's fanciful tales and persuade him to dismiss her, but he does so with doubts. 
Later stuff happens to him that convinces him she was right, so he seeks her out and brings her back. 

James or his companion asks Lica: 
\ta{How old are you, girl?}

\ta{I am sixteen, my lord.}

Later, James comments to his companion: 
\ta{She is pretty, though.}

The companion laughs. 
\ta{She is sixteen, James. 
  Even my warty cackling crone of a great-grandmother was pretty when she was sixteen.}

%Turns out that Lica has seen a \bane. The \banes{} are working on some big thing, so they are getting bolder and more careless. (It's for the same reason that Catrian saw a \bane{} earlier.) Or maybe she hasn't seen an actual \bane, but merely a Cabalist working magic. Or maybe some \Nyxian{} monster. 
Turns out that Lica has seen either a Sentinel mage or some \daemon. 
And it's a good thing that Sir James starts to believe her, because it turns out the Sentinels is after her. Assassins come for her and he has to protect her. They flee back to the castle or whatever, and the authorities (Redcor church?) finally believe that something is up. 

Lica is gifted in seeing into the worlds beyond. Since her childhood she has had trouble accepting the illusion that everyone else believes in. She always wanted to see through the lie, doubt what she was told. This has continued to the current day (she is now 16 or so) and lets her see many things that others can't, but it also makes her strange (she is unmarried and unbetrothed, and her parents worry) and affects her sanity. 

Alarmed by Lica's vision, the Redcor send a delegation to investigate. Lica is brought along as a guide of sorts, and Sir James goes as her protector. 









\subsection{Lica sees strange visions}
Lica sees grim and horrid visions. 
She hates this \quo{gift}. 

\lyricslimbonicart{The Supreme Sacrifice}{
  Thought are tyrants that always return\\
  to rape and torment the heart.\\
  As darkness sweeps the face of Earth,\\
  I enter the chambers of bleeding art.
}









\subsection{Lica sees the \Morbus}
Lica sees the \hr{Morbus}{\Morbus} at work. 
She has dreams of its evil consequences. 

She sees visions of \Nyx{} and mistakes them for visions of the future. 
She is scared shitless. 

\lyricsduana{thisistheend}{This is the End}{
  I dream of a host cockroaches \\
  crawling, swarming over charred flesh \\
  up bitter blackend walls \\
  in sewer pipes now purgd \\
  the cries of many amplifd \\
  then swallowd by silence \\
  echoes of a lost world \\
  of a foul smoke that lingers like stale breath \\
  of steel/glass/concrete fusion-statues \\
  rising high in a pale and infinite twilight \\
  shining beacons like bleachd bones 
  
  I see field upon field upon field \\
  of bloatd-cattle-corpses bleeding intestines \\
  staring with sightless opaque eyes \\
  of waves drowning mountains \\
  and the earth's flesh torn with angry fissures \\
  of molten-spewing-spittle \\
  and hot lashing tongues \\
  of a planet roaring/quaking/quivering \\
  with unbound vergence 
  
  shivers erupt through space and time \\
  and images flashing faster faster\ldots{} \\
  until finally all is annihilated 
  
  like a vacuum space sucks the debris \\
  into a black empty hole \\
  and I fall down into the void \\
  this is the end
}









\subsection{Lica suffers}
Lica feels like she is losing her innocence and being corrupted from the inside by the terrible truths she sees.

\lyricslimbonicart{Beneath the Burial Surface}{
  The sky is darkening, soon the night befall.\\
  Righteously angels are weeping for my soul.\\
  All childhood dreams are soon to be lost,\\
  all innocence to be shattered.
  
  I am the fallen from grace.
  
  My face is a river.\\
  See my eyes as they drown in black.
  My sacred doom and nemesis\\
  beneath the burial surface\\
  To the final act of the immortal sin\\
  I am lead by funeral winds.
}









\subsection{Lica can curse people}
Lica discovers at a young age that she can curse people. 
When people are mean to her or refuse to believe her, she can stare at them and hate them and wish them ill\dash and sometimes it happens.
This is a manifestation of her (albeit weak) \vertex{} powers. 




































 

 
