\begin{garbage}
\part{Sentinels of \Miith}























\chapter{Carzain Prequel}
This book tells Carzain's back story, before he joined the Runger War. 
It details Carzain's travels, Vizicar's awakening and their joint path to \kenosis. 















\section{Overview}















\section{The Mutiny}
\target{Mutiny}
\target{Mutiny chapter}
Carzain and Nishain were betrayed by mercenaries in Heropond Forest. 
Vizicar awakened (for the first time in Carzain's life) and fought, killing the mutineers. 









\subsection{Old description}
Carzain goes to Martinum with his father. Then back.

It is only autumn as they travel through Heropond, but in the \Wylde{} it feels almost like winter: Hoarfrost lies on the ground, and cold mist fills the air.

The younger trees hate them and want the intruders out of their forest. Carzain finds an older tree that is indifferent, cold, uncaring\dash it knows that the humanoids will die soon enough anyway. 

(To what extent can Carzain read the thoughts of trees? Much of it is probably just guessing based on vague emotional impressions.)

He also sees the \hr{Moons}{moons} in the forest. They look spectral and spooky. Have some Bal-Sagoth-esque imagery about them.






\subsubsection{Carzain dreams of being nothing}
On the way back to \hs\Redglen, Carzain dreams \hr{Ramiel is nothing}{his recurrent nightmare of being nothing}. 

He sees visions of humongous gods: 
\Human-like, \dragons, amoebae with pseudopods...





\subsubsection{Betrayed by mercenaries}
On the way back to \hs\Redglen, their hired guards mutiny against them. Carzain fights back using magic and suddenly feels a strange ecstasy, a possession. He fights with power he did not know he had and slays the thugs. He is puzzled by the possession experience. 

The magic should be more bloody. I should show how the skin blackens and seethes, let people scream their agony while they boil and burn. They get cramps and spasms and perform a sickly, morbid \quo{dance} before they die from being zapped. 

Maybe fire magic should cause the victim to burn up \emph{from the inside}, instead of just tossing fireballs. Or perhaps tossing fireballs is the beginner's tactic: Easier and cheaper, but less powerful and less accurate. Causing your victim to combust from within is harder, but much more deadly and accurate. It uses the victim's own life force as fuel, burning him to ashes. 

Describe how blisters boil and burst. 





\subsubsection{The Redcor discover the \vertexspike{}}
A Redcor \matron\dash\Esmerel?\dash is sitting in the Topaz \Chateau, performing divination though \index{aquamancy}. Insert some Bal-Sagoth imagery here. 

\lyricsbs{Bal-Sagoth}{A Black Moon Broods Over Lemuria}{
  And in the dark ethereal mists of winter dreams,\\
  the ebon waters of enlightenment gleam 'neath the Black Moon,\\
  and the Valley of Silent Paths beckons...
}

She discovers the \vertexspike{} that is caused by Vizicar's brief awakening, and realizes something has happened. I am not sure how much the Redcor know about \vertices, but she definitely knows something is up. She goes into research, and eventually they determine that very likely a Scion has awakened. 

\Esmerel{} goes off to wander the lands of \Velcad{} in search of the Scion. A year or so later she finds him, in the midst of the Pelidor-Runger war...






\subsection{Changes}
Some of the mercenaries have guns (pistols or muskets).

Maybe I should edit the date. 
Maybe the lapse of time between the Mutiny and the Runger War should be shorter. 

Carzain and Nishain have not been to the Imetrium, merely some big port city in southern \Scyrum. 
They do not know so much Imetric. 
Nishain only knows a few rudiments, and Carzain none at all. 

When Vizicar fights, he ignores the \hr{Itzach pain}{pain that \Itzach{} brings}. 
\Itzach{} Vaimons have ways of using power economically, thus minimizing the pain and risk. 
Vizicar does not care about this. 
He is groggy and sleepy and his senses are dulled, so he thinks he is completely fresh and healthy and has plenty of bodily energy to spare. 
He does not want to be careful and conservative. 
He wants to be flamboyant and teach these damned peasants a lesson. 

After all, he is Vaimon Emperor. 
He is used to being one of the most powerful and skilled Vaimons in the Empire, and a Scion to boot. 
He does not stop to consider that he is out-of-touch with his body, or that his new body is weaker and less trained than his old one. 

Remember to have references to the \hs{\shechinah}. 

After the battle, Carzain has nasty open wounds caused by drawing too much \qliphah{} power. 
He uses these heroic wounds to score Mirai. 
Then he gets healed by Imetric healers. 

The chapters with \ChyrieEsmerel{} and \LocarPsyrex{} do not happen at all. 
Get rid of them. 
At this point in time, no one knows about the \vertex. 
If they did, that would just cause all sorts of trouble and plot holes. 















\section{Ilcas Northstar}
\target{Ilcas Northstar chapter}
\target{Ilcas introduction}
Carzain and Nishain met Ilcas Northstar in \Bryndwin. 









\subsection{Old description}
Carzain and Nishain go back out of Heropond forest to the town of \Bryndwin.

\Bryndwin{} has its share of monuments (see section \ref{Monuments}): Poles with flags and lamps on them, carved images of gods, heroes and creatures, meant to scare the \Wylde{} and intruders away.

They encounter \hs{Telcastora Ilcas}, his two \nycans, Razor and Countess, and a bunch of other Imetrians. 

Remember to describe \hs{Telcastora Ilcas's appearance}.

They see a big \hs{\mulgron}. Carzain is impressed by how the \mulgron{} is even bigger than an elephant. 

Remember to \hyperref[Nycans are frightening]{describe the \nycans{} as frightening and alien}.

Carzain reaches out his hand and tries to touch Razor's snout. Razor's eyes narrow slighty, and he retracts the hand. 

The two Vaimons hitch a ride back to \Redglen{} with Telcastora Ilcas and his Imetrians. Carzain befriends Ilcas and his \nycans, Razor and Countess. 

They part ways somewhere in Pelidor. 

Carzain has a wound from his battle with the thugs, but he suppresses the pain, as he doesn't want to show weakness in front on Telcastora Ilcas. I should try to portray him as somewhat over-proud and silly. 

During the trip back, he is treated by an Imetric healer-surgeon. But he retains the scars: One in his leg, one in the side of his stomach. 
The surgeon's treatment is more bloody than the Iquinian healing he is used to, but it is at least as effective. The Imetrians have a scientific approach to medicine, whereas the Redcor repress real science in favour of traditional mysticism. 
This makes Carzain doubt the value of Vaimon tradition.





\subsubsection{Changes}
Write about Carzain's meditation. 

Replace \quo{resonance} by \quo{\shechinah}.
Add \quo{\shechinah} to the glossary. 

\Bryndwin{} has a \hr{Wylde border}{\Wylde{} border} with charms and totem poles. 

Carzain introduces himself to Ilcas: 
\ta{I am \VizicarDurasRespina.} 

When negotiating with the priest: 
Carzain has no interest in theology, but he is skilled at faking interest, if he does say so himself. 
It is a skill he has honed when picking up women. 

On their first day on the caravan, Carzain talks to Ilcas. 
Ilcas tells stories of his heroic and violent deeds, and of his heroic and violent sword. 
He especially tells of how he has fought against the Imetrium's arch-nemeses, the Rissitics. 
\hr{Rissitics and Runger}{This is important. The Rissitics are important to the story.} 
Make sure to paint the Rissitics as threatening and imposing foes.
Tell of how they wear animal masks and have warrior orders named Order of the \hr{Order of the Crocodile}{Crocodile} and Jackal and Scorpion and \hr{Order of the Hippopotamus}{Hippopotamus} and so on. 

These associations of war makes Carzain see visions of his past, but still very vague, little more than regular daydreams. 

Then Carzain asks to hold the sword. 
Ilcas refuses. 
But he shows him the sword and swings it around a bit himself. 
And tells him about it. 

Carzain scores Mirai faster (already on the first night) and more solidly. 
I need to show the reader how cool he is. 
He pulls off a pick-up comparable to the way Tony Stark scores the reporter girl in the movie \cite{Movie:IronMan}: 
\ta{I'd be willing to lose a few hours of sleep with you.}
She is impressed already after their very first meeting. 

Have more Vizicar in the sex scene with Mirai. 
And after it. 
He talks to Carzain in his head. 
Perhaps from Vizicar's POV. 

The night after sex, he lies awake thinking wildly about what in all of \Iquin{} and \Itzach{} is happening to him. 
When he falls asleep, he meets Vizicar in dreams. 

\target{Vizicar drives Carzain to war}
After this night, Vizicar drifts away. 
Carzain feels lost. 
Like something is missing inside him. 
Some important clue in some important mystery. 
Some part of himself. 
He feels like half a man. 

Carzain goes off to war hoping to find Vizicar again.  
He seeks out battle in the hope of provoking more Vizicar action in his head, so he can figure out who Vizicar is and what the deal is. 
Maybe Vizicar subconsciously imparts in him a desire to fight and seek glory. 
















\section{Visions and dreams}
Carzain had visions and dreams. 
As did Vizicar. 

They met in dreams and talked to one another, but neither understood what was going on. 
Both thought the other man was a figment of their own imagination. 

The dreams were triggered by combat and war, or the expectation of it. 









\subsection{Vizicar's motivation}
Vizicar knew he is more than a \human, and he told Carzain this. 
Vizicar wanted to attain \kenosis{} and regain his body, power and memory. 
Then he wanted to achieve \apotheosis{} and learn his true nature.
Then he would be a god.












\section{Carzain in the War}
\target{Carzain joins the army}
Pelidor went to war against Beirod. 
A trivial border dispute, but bloody enough. 

At this point, Carzain knew there was something odd going on with him. 
Carzain joined the army because he hoped it would help him find out what was happening to him, who he was and who Vizicar was. 
He could hear Vizicar stirring in his head at the prospect of war and glory: 

\begin{prose}
  \tho{I thought so. 
    It is this sort of thing that brings you out.
    \quo{Vizicar}.
    Whoever you are.
    I will find out what the deal is with you.
    And how I can get rid of you.}
\end{prose}







\subsection{War is Coming}







\subsubsection{Carzain joins the army}
News of the impending war with Runger reaches \Redglen. 

Carzain's parents hate war. Perhaps they have even done stuff to get him to dodge the draft - without his knowledge. Any any rate, Carzain goes to the barracks and signs up. See, Carzain is bored as fuck. He's a big boy in a small town. He has a craving for greatness, fame and power - things he cannot possibly find in \Redglen. He wants to explore and wants something to happen. So he goes off to war. At this point, Carzain is maybe 22. 

In the Pelidorian army, Carzain is welcomed because of his magical knowledge. Pelidor has few mages, since neither the Imetrium nor the Iquinian church support them. He is assigned to serve under Captain Archibald Curwen, the commander of the \ishrah{} of the Pelidorian army.  
Carzain also learns a lot of combat technique. As he studies combat, he finds all sorts of things coming naturally to him, as if he already knows them but has just forgotten he knew. 

On the way to Malcur, Carzain calls dibs on a horse\dash a gray stallion named Arrow\dash rather than a \relc. Later, having trouble riding the beast, he ponders his decision. Seeing some of the others getting easily ahead on their \relcs, he realizes that a horse is not necessarily better. It is just that horses are more Vaimon-like. In stories, Vaimons always ride horses, so when he pictures himself in his head as a great Vaimon hero, he sees himself astride a horse, not a \relc{} or other reptile. Carzain realizes that he is a status-fixated snob. 





\subsubsection{Carzain and the Goldsmiths}
He talks to the Goldsmith brothers. 
He talks of how he is destined for greatness. 
At this point he remembers \hr{Ramiel dreams of being nothing}{his recurring nightmare of being nothing}, and he tries desperately to convince himself that he is not nothing. 
He tells himself that he is big and important, because he fears that dream. 









\subsection{To Malcur}
Carzain travelled to Malcur to join the Pelidorian \ishrah{}.

On the way he met Adrian Testor. 

In Malcur he met Archibald Curwen. 

Have plenty of Vizicar scenes early on, including before, during and after his signing-up to the army. 
(If \quo{The Mutiny} and \quo{Ilcas Northstar} are kept in \emph{\TwilightAngelRemember}, then include lots of Vizicar scenes there. Otherwise move them to the prequel story about Carzain.)

Vizicar (when he gained some \kenosis) liked the life of an adventurer. 
It was a refreshing change of pace from the court life he was used to, full of responsibility and chains. 
This was a new kind of freedom, and Vizicar loved it. 





\end{garbage}
\subsubsection{Carzain meets Delph and \Tsekkect}

\target{Carzain meets Delph}
\begin{garbage}
Carzain meets \hs{Delph} and \hs{\Tsekkect}.

They are cheerful guys. 
They befriend Carzain and show him around the barracks, where, among other things, Delph utters his classic line: 
\ta{Life in the army is great. We get food, money, a shot at glory, and the best pussy that money can buy. Well... the best pussy that \emph{our} money can buy, anyway.} 

To which Carzain replies: 
\ta{And all they ask in return is that we fight to the death.}






\subsubsection{Carzain's idealism}
At the beginning of the story, \hr{Carzain's idealism}{Carzain is quite idealistic}.





\subsubsection{Vizicar awakens a little bit}
At some time at the beginning of the war, before Carzain's first battle in the army, Vizicar surfaces a little bit. 









\subsection{To battle}
They go to battle the enemy. 





\subsubsection{Carzain and Delph practice with swords}
Carzain and Delph practice their swordsmanship. 

When the two duel, Carzain mostly loses. He knows some technique, taught to him by Sir Guy in \Redglen, and he is taller, which gives him a better reach. But the shorter and cruder Delph is faster and more agile, and he fights dirty. 

Carzain: \ta{You fight dirty, you know that?}

Delph: 
\ta{No, I just fight like a \meccaran. 
  That attitude of yours is just \human{} provincialism.}





\subsubsection{Carzain won't smoke}
Carzain hangs out with some soldiers. The others smoke some kind of strong drug, like hash or marijuana. 

\begin{prose}
  Soldier: \ta{Come on, \Shireyo, get over here and smoke.}
  
  Carzain: \ta{No, I don't touch that. It's filth.}
  
  Soldier: \ta{Why do you say that?}
  
  Carzain: 
    \tho{%
      Why \emph{do} I say that? 
      Because my father told me so, but I am not going to tell them that. Think, Carzain, think! 
      I can't lose face in front of these guys. 
      Say something witty.} 
    \ta{Something witty.} 
    \tho{Phew. Nicely salvaged, Carzain.}
\end{prose}





\subsubsection{Curwen and Carzain eat}
The officers of the Pelidorian army are eating a luxurious meal. This includes the \ishrah. 

Curwen: \ta{Ah, by \nieur, I love food.}

Carzain: \ta{Food is good, but I like sex better.}

Curwen: \ta{Meh. Most women cook better than they fuck.}

Both: \ta{LOL.}









\subsection{The Emperor Inviolate}
The sortie encounters a small Rungeran force. They fight. 

Carzain fights and kills. 
But he is not as great a warrior as he fancies himself. 
So he gets clobbered and takes wounds. 

He calls out to Curwen-tachi for help. 
They save his ass. 

Then Vizicar awakens. 
It's due to a combination of factors: 

\begin{itemize}
  \item The pure rush of combat. 
  \item The anger and shame over being defeated in combat by such lowly grunts. 
  \item The wounds leave Carzain's own conscious mind weakened, making it easier for Vizicar to take over. 
\end{itemize}


% Recall that Carzain is a Scion, an incarnation of the \Malach{} Ramiel. 
% Occasionally, when he fights and kills, Ramiel awakens in him, and he hears the voice of \VizicarFull, the previous incarnation of Ramiel. (This is inspired by, and similar to, how Rand al'Thor in Wheel of Time hears the voice of Lews Therin Telamon. But where Lews Therin is mad, annoying and even dangerous, Vizicar is sane and a powerful ally.) 

% Anyway, Carzain fights and kills, and Vizicar comes along and takes over. 

Curwen immediately senses something fishy, probably a \vertexspike{}. 

This time there is a struggle between Carzain and Vizicar, as Carzain tries to get back in control of his own body. 

%After the battle, Carzain falls unconscious as Vizicar retreats. The prolonged, unaccustomed possession and the struggle between the two personas was too much for his consciousness to take. 

After the battle Curwen probes, prodding Carzain into telling him stuff. Carzain tells a little of what he knows, but it's not much. 

Carzain's body is in a bad shape. 
Vizicar is a harsh master and takes poor care of it. 
This is because Vizicar is only half-awake. 
He's still in a half-dreamy state, and his senses are weakened. 
He doesn't entirely register the pain, so he just pushes on. 
So after the fight Carzain is a useless wreck, barely conscious. 

Maybe Carzain asks the others: \ta{Did I save the da?} 

The others: 
\tho{Save the day? You crazy fuck, you nearly killed yourself, and maybe us, too.} 
\ta{Um, yeah. Sure. You saved the day.}

Delph is scared by Carzain's weirdness. Maybe insert an inner monologue with Delph about how Carzain is a crazy weirdo: 
\tho{Typically. 
     Finally I meet a guy who seems trustworthy, who might become a true friend, and turns out he is a madman. 
     Or possessed by \mdaemons{}, or whatever. 
     Huh. 
     That'll teach me to trust a sorcerer.}

During the fight, Carzan does something stupid and reckless. 
Perhaps he sees an enemy Vaimon and goes in to capture his sabre. 
Afterwards, Curwen bitchslaps him and scolds him: 
\ta{You crazy fuck, \Shireyo!
    What the fuck were you trying to do?
    You very nearly got yourself and the rest of us killed!}
He grabs Carzain by the collar. 
\ta{Let me tell you something, boy.
    Your insubordination stopped being charming a long time ago. 
    Now either you get in line or I'll have you beaten!}





\subsubsection{Vizicar dreams}
Have another scene that describes the battle from Vizicar's point of view. 









\subsection{Reads about Scions and Vizicar}
Maybe Carzain overhears someone (\Esmerel{} and \Racel{}?) talking about Scions. 
Maybe he is half-unconscious and they are standing over him, talking about him, trying to decide his future. 

He asks someone about the story of the Scions. 
Who? 
Perhaps \Racel, but more likely some other mage in the \ishrah. 
Perhaps \Sanyor. 

Anyway, he is told the story of the Scions. Or a version of it. Remember to have many false details, which can be brought into question later. 

Later, he goes into a library in \Forklin{} and reads about \VizicarDurasRespina. 
There isn't a big public library, but there are churches, and they have books. 
He goes into a church, introduces himself as an \ishrah{} mage and pulls a \trope{BavarianFireDrill}{Bavarian Fire Drill}.
He knows he has to use the same body language, frame control and social engineering skills that he masters when picking up women.
It works.
He gets his hands on the writings.

He also finds references to \hr{Vizicar's notes}{Vizicar's notes about \Malachim}, but can find no fragments of the notes themselves. 

He also finds references to \hr{Iolivine's notes}{\ps{\Iolivine} notes}. 
He has heard before that these notes are of exceptionally high quality, but he had been unable to find any copies of them. 
\hr{Redcor bogarted Iolivine's notes}{The Redcor are bogarting the notes}. 
This is one of the reasons he wants to go to \Redce. 

Among other things, he learns that \Belzir{} was an incarnation of an \quo{evil} \malach, and that she caused the \HundredScourges{} with her wicked \malach{} powers. 

More importantly, he learns that he is not mad. 
There are no \qliphoth{} controlling him. 
Instead, he is a Scion! 
He is an \uber-dude! 

He is happy. 









\subsection{Changes}
\begin{changes}
    
  \begin{comment}
  \paragraph{War is Coming}
  \end{comment}
  \changesitem{War is Coming}
    Remember to have references to the \hs{\shechinah} in Nishain's speculations. 
    
    Rewrite the \quo{I want to fight} section from the officer's POV. 
    
    Mention Carzain's age (\quo{a young man, around 25...}). 
    
    Make sure the soldiers notice that Carzain is a bit swarthy (being half Geican). 
    
    This might be the place where Carzain introduces himself:
    \ta{I am \VizicarDurasRespina. No! Wait... I am Carzain \Shireyo...}

  \begin{comment}
  \paragraph{To Malcur}
  \end{comment}
  \changesitem{To Malcur}
    Rewrite the scene where Curwen and Carzain meet, so it is from Curwen's POV. 
    
    Curwen should be smoking his pipe. 
    
    Mention Carzain's age (\quo{a young man, around 25...}). 
    
    This might be the place where Carzain introduces himself:
    \ta{I am \VizicarDurasRespina. No! Wait... I am Carzain \Shireyo...}
  
  \begin{comment}\paragraph{\Forklin}\end{comment}
  \changesitem{\Forklin} 
    Get rid of \Racel. 
    
    Carzain is \hr{Carzain PUA}{a great PUA}. 
    He \emph{does} score in \Forklin.  
  
  \begin{comment}
  \paragraph{The Emperor Inviolate}
  \end{comment}
  \changesitem{The Emperor Inviolate}
    Again, Vizicar ignores the \hr{Itzach pain}{pain of \Itzach}, and Carzain gets burnt and wounded as a result. 
    
    Remember the \hr{Itzach pain}{pain of \itzach} when Curwen casts magic. 
    
    Remember to have references to the \hs{\shechinah}. 
    
    Curwen needs to tell the reader that the \ishrah{} mages are equipped with plate armour. 
    They just do not wear it when travelling, nor on stealth missions like this. 
    But when the battle comes, he misses it. 
    
    Maybe Vizicar holds back his power and magic. 
    He does not want to arouse suspicion and get caught. 
  
  \begin{comment}\paragraph{\Tsekkect{} and Delph}\end{comment}
  \changesitem{\Tsekkect{} and Delph} 
    Make sure people like \Tsekkect{} and Delph have inner lives of their own and don't spend all their time gaping at Carzain. 
\end{changes}
















\section{Mercenary}
After this short war ended, Carzain left the army and became a mercenary and adventurer. 

























\chapter{\TwilightAngelRemember}
\target{\TwilightAngelRemember}

















\section{Overview}
\input{Sentinels01/Blurb}
\begin{comment}
\input{Sentinels01/DramatisPersonae}
\end{comment}









\subsection{Malcur}
Much of the book is set in or revolves around the city of \hs{Malcur}, the capital city of \hs{Pelidor} and a powerful \hs{\nexus}.





\subsubsection{Sentinel plan}
\target{Secherdamon wants Nithdornazsh}
\target{Ghost Tower ploy}
The \hs{Sentinels} have a plan: \hs{\Secherdamon} wants to resurrect the \draconic{} fortress of \hs{\Nithdornazsh}, and he wants to do it in Malcur. 

The overall plan is this:

First they go for the \hs{Ghost Tower} near \hs{\Forklin}, besiege it and send in their Rissitic agents. 
The Cabalists immediately smell that something nasty is brewing, so they send in agents to stop them. 
They even send \banes. 

It comes to a major confrontation between Rissitic and Cabal agents. 
\hs{\Nzessuacrith}, disguised as \hs{\Takestsha}, is forced to change to \draconic{} form to fend of the \bane{} attack. 

The Cabalists immediately detect the \dragon{} and send loads of reinforcements to the Ghost Tower, bent on fighting off the Rissitics (Sentinels?) at all costs. 

%But this was all part of the Sentinels' plan. Having drained Pelidor of Cabal resources\dash every Cabalist that matters off to defend the Ghost Tower\dash Sentinel agents in Malcur now proceed to the cemetery. 
\target{Rissitics start Haskelek plan}
Now, \Nzessuacrith{} genuinely does want the Ghost Tower, because it contains one of the parts of the \hs{\Haskelek}. But her whole attack is a diversion. She works for, and is unwittingly being manipulated by \Secherdamon, who has his own plans. Having drained Pelidor of Cabal resources\dash every Cabalist that matters off to defend the Ghost Tower\dash his agents in Malcur now commence with their arcane ritual, to achieve the resurrection of the fortress of \hs{\Nithdornazsh}. 





\subsubsection{\ps{\Secherdamon} role}
\Secherdamon{} should be portrayed as a distant, mystic dark lord. 

Keep his name secret for a long time and have people refer to him only by various ominous titles. 

Compare him to Lucifer from \FLuneNoire. 






\subsubsection{The summoning ritual}
%There is a \vertex{} in the Shroud somewhere in Malcur. The Sentinels want to draw a thread through this \vertex{} to form a connection to \Machai{} and pull \Nithdornazsh{} into the world. 
To this end, they need a magical ritual. \ps{\Secherdamon} servitor \hr{Psyrex}{\Psyrex} is responsible for this. He pulls the strings of the \Malcuric{} Sentinels and the criminal underworld in order to set up the ritual. 

The plan utilizes the \hr{Occult geometry}{occult geometry} that was used in the building of Malcur.

The ritual to pull \Nithdornazsh{} from \hs{\Machai} into the \Miith{} requires \quo{beacons} to be set up at strategic locations. 
Each of these beacons must be secured and prepared for the ritual, including humanoids captured and ready to be sacrificed. 
The Sentinel-led mafia, masterminded by \Psyrex, can set up the beacons, but they need help diverting the town guards and the church. 
To do this, \Psyrex{} recruits the Duchess \hs{\Tiroco}. 






\subsubsection{Cabal plan}
\target{Teshrial's creatures}
\target{Teshrial's monsters}
The \hs{Cabal} have their own plans for Malcur. 
\hs\Teshrial, the leader of the Cabal in the Pelidor region, has brought several of the dreaded \hs{\ghobaleth} to Malcur. Perhaps these \ghobaleth{} have been there for thousands of years, or have gradually dug their way to Malcur from Erebos over the course of thousands of years. 

Anyway, since Malcur is a powerful \nexus, \Teshrial{} intends to use the \ghobaleth{} to open a portal to \hs{\Erebos} through Malcur. 

The worms are hiding beneath the city. If the Sentinels try anything major, he is confident that the \ghobaleth{} can handle it. 

The \ghobaleth{} are intrinsically tied to \hr{Ancient history of Malcur}{Malcur's mystic past}.

In the end, of course, the \ghobaleth{} are defeated by the creatures which \Ishnaruchaefir{} and \Shilred-tachi free from their cave in western \PelidorContinent. 






\subsubsection{\Ishnaruchaefir{} and his fake mission}
\target{Ishnaruchaefir's fake mission}
\Ishnaruchaefir{} is clever. He knows about \hyperref[Teshrial's creatures]{the \ghobaleth{} in Malcur}, or at least suspects them. So he \hyperref[Ishnaruchaefir attacks Teshrial's creature]{goes there to see for himself}. 

He has also seen through \ps{\Secherdamon} plan to resurrect \Nithdornazsh{} in Malcur. 
He has more Sentinel contacts than most people realize, so he has spies telling him of \ps{\Secherdamon} plans. 
And he is an expert astrologer and \matrix-theorist, so he has picked up subtle clues concerning \Nithdornazsh{} and Malcur. 

He knows that the \ghobaleth{} may put a stop to the plan. 
He wants to help his brother.
He does not fully approve of \ps{\Secherdamon} plan to resurrect \Nithdornazsh, but he helps out of respect for \hs{\Nexagglachel}, since he still feels guilt and obligation towards him and his memory. 
\Nithd{} was \ps{\Nexagglachel}{} fortress, after all, so it can stand as a monument of sorts to the fallen \dragonking.

\target{Ishnaruchaefir's creatures}
So \Ishnaruchaefir{} plans to free some of his own servitors\dash\pdaemons, \dragons{} or otherwise\dash who are imprisoned in a cave or lost temple somewhere in the eastern \PelidorContinent. 

But he can't just go off and do that. He would be discovered and foiled by \hs{\Teshrial}, the Cabalist in charge of the area around the cave. 

So \Ishnaruchaefir{} develops a circuitous plan: 
\hyperref[Ishnaruchaefir recruits Shilred-tachi]{He recruits \Shilred-tachi} and sends them off to fulfill an ill-defined quest for him, in the general area of the cave in question. He tells them to search for a cave or something like that. 

But whatever he alludes that he wants them to do is a lie. The purpose of their entire mission is to look suspicious. \Ishnaruchaefir{} shows up to help them just often enough that the sneaky Cabalists cannot help but notice, yet rarely enough that it still looks like he is trying to lay low. 

What he is actually looking for is another cave, where his servitors are imprisoned. 

The Cabalists in the area where \Shilred-tachi are going are led by \Teshrial{} (see section \ref{Teshrial}). We follow him in several chapters, where he fears \Ishnaruchaefir{} and tries to guess his plan. 






\subsubsection{\Secherdamon{} versus \ghobaleth}
I am not sure if \hs{\Secherdamon} is aware of the \ghobaleth. 
If not, then \hyperref[Ishnaruchaefir tells Secherdamon of the Ghobaleth]{\Ishnaruchaefir{} tells him at the end} and thus forces \Secherdamon{} to \cooperate{} with him.

If \Secherdamon{} does know, then he must be planning for it. 
He knows that the \ghobaleth{} can fuck up his resurrection ritual. 
They can even use their Shroud-weaving power to take control of the ritual and use it for Cabal purposes\dash but only if \Teshrial, their master, or \Achsah, his servant, is there to guide and control the mindless abominations. 
Thus the \hs{Ghost Tower ploy} to lure \Achsah{} out of Malcur.
Then \LocarPsyrex{} and his Cabalists ought to be able to handle whatever \Teshrial{} can whip up. 

But the \ghobaleth{} are more strongly present than \Secherdamon{} believes. 
They have taken root and entrenched themselves much deeper than he thinks. 
So they can disrupt the spell, with catastrophic consequences for everyone. 
This fucks up \ps{\Secherdamon} plan. 

But \Ishnaruchaefir{} knows this, because only he is crazy and reckless enough to seek out the \ghobaleth{} and fight them in \melee{} combat, which \Secherdamon{} or \LocarPsyrex{} would never dream of doing. 
\Ishnaruchaefir{} finally \hyperref[Ishnaruchaefir tells Secherdamon of the Ghobaleth]{warns \Secherdamon{} about the problem}. 

Then \Ishnaruchaefir{} fights the \ghobaleth{} and holds them off. 
They are not all slain, but held off and weakened enough for \hyperref[Psyrex-tachi invoke the ritual]{\Psyrex-tachi to complete the ritual}. The sorcerers now have enough control of the local Shroud to be able to trap the \ghobaleth, and so turn the worms' Shroud-weaving power against them and their masters and use it to \hyperref[Nith'dornazsh rises]{resurrect \Nithdornazsh}. 

In this interpretation, the \ghobaleth{} are a vital part of the Sentinels' plan as well.






\subsubsection{\ps{\Ishnaruchaefir} stealth}
\target{Exile intersecting with Pyre}
\Ishnaruchaefir{} is stealthy. 
He helps \Secherdamon-tachi, but not too directly. 
He does not combine his powers with theirs in a straightforward manner. 
If he did that, his alliance would be astrologically detectable; astrologers would be able to see in the sky that the \hs{Exile} was intersecting with the \hs{Pyre}. 
He doesn't want that. 
So he merely helps them out without directly aiding them. 

Later \hr{\Azraid{} muses on Exile and Pyre}{\Azraid{} will muse on this}. 





\subsubsection{Twist ending: Evil wins}
At the end, evil wins. 
Malcur falls and \Nithdornazsh{} rises. 

\target{stop the evil}
This must be a surprise for the reader. 
Remember to have tons of references to how the heroes want to \quo{stop the evil}, so the reader thinks they will succeed. 









\subsection{Tantor's journal and \EreshKal}
\target{Tantor's journal}
The Sentinels, who are secretly supporting Runger, have planted a diary (written by Rungeran mage \Jirad{} Tantor) among the possessions of \Ambrose{} \Onatol, a Pelidorian \ishrah{} mage. 

%Tantor relates how he, together with a Rungeran expedition, finds a forgotten temple that appears to be many thousands of years old, built with odd shapes that twist the eye and seem to defy geometry and reason, and adorned with carvings of horrific monsters. 
Tantor relates how he is sent on a secret expedition, led by \Takestsha, King Morgan's new advisor. \Takestsha{} is looking for the lost temple of \Rungertemple, in which is supposedly hidden a vast wealth of mystic knowledge. 

After a harrowing trek through the \Wylde{} they find the temple. It appears to be many thousands of years old, built with odd shapes that twist the eye and seem to defy geometry and reason, and adorned with carvings of horrific monsters. 

In this tower they find a wealth of mystic knowledge: Books, scrolls and artifacts. All in all a tremendous source of magic. They bring it back to the king. 

Not only do they have to hide this knowledge from the Iquinian church, but some mysterious people also appear and try to steal the magic and kill the finders. They use magic, and from their technique and behaviour Charcoal estimates that they are very likely Sentinels. But they are defeated or outmanoeuvred and the magic is brought to the king. Tantor has his reservations, but he follows the leader, a very strong-willed mage and a loyal Rungeran (perhaps a relative of the king). 

Tantor fears that Morgan Runger wants to use this terrible magic to conquer. He warns \Anatoli{}. 

It turns out that the discovery occured a year or a few years ago. Tantor and the other participants were sworn to silence, and he only recently gathered up the courage to write this. 






\subsubsection{The truth} 
The whole story about how Morgan's people discover a cache of magical knowledge is a hoax. It's meant to cover up the fact that the Rungerans are armed with Rissitic/Sentinel-provided magic. The Sentinel-looking characters that try to stop the Rungerans are completely fictional. They are there for the specific purpose to convince a Cabalist reader that the whole thing is \emph{not} a Sentinel plot (which it is). 

%The tower is real, however. Its location and nature are known to both the Sentinels and the Cabal. But it's guarded by nasty things, and the Rungerans were never there. (Or were they?) 
\Rungertemple{} is real, however, and so is the expedition. \Takestsha-tachi really were there and picked up some occult tablets and scrolls, but these are not as valuable as they are eld to believe. The actual mystic knowledge was provided by \Takestsha, who is really the \dragon{} \Nzessuacrith. 

Giles Tantor is a real person and \emph{did} correspond with \Anatoli{}. His account is real, although he was being mind-fucked to some extent by \Nzessuacrith. 
%But this story is not his work. The real Tantor was killed by the Sentinels, and his \quo{journal} was
A few fragments are concocted by the Sentinels and inserted afterwards. Tantor was later killed by the Sentinels, and his edited journal was sent to \Anatoli{} in Malcur, ostensibly to warn him, but in reality it was meant to be leaked to Charcoal. 
Then \Anatoli{} was killed so he wouldn't spill the wrong beans. 

The \EreshKali{} magic is Rissitic magic, but not standard issue. 
It is a new experimental kind. 
\Secherdamon{} intends to kill two birds with one stone by field-testing his new spells and winning the Runger war at the same time. 
Also, the Rungeran mages are much more expendable than precious Rissitic ones. 
\Secherdamon{} loves his own people. 









\subsection{Rissitic invasion}
\target{Rissitics and Runger}
Shortly before the Rungeran attack against Pelidor, the Rissitic Empire launched invasion forces in southern \Galessan. 
They are especially targetting \hs{Sumian}. 
Or maybe \Scyrum. 

This is part of a bigger long-term strategy. 
\Secherdamon{} wants a bigger foothold in the world. 
And it also serves as a diversion, a means to distract the world from the Runger-Pelidor war. 
With Rissitics attacking from the south, they will draw all the eyes to them, and the world will not pay much attention to a little border dispute between two unseeming little kingdoms. 
The Redcor Church and the Imetrium will be far too busy to respond to Pelidor's call for aid. 

But in reality the Runger-Pelidor war is more important than the Rissitic invasion, because it sets the stage for the resurrection of \Nithdornazsh. 

Remember to make it clear that Durcac = Rissitics! 
Write this multiple times! 

And remember to advertise \hr{Narkiza}{\Narkiza}. 
Namedrop him and tell everyone how skilled and feared and powerful and cool he is. 
















\section{The Dreaming Predator}
\subsection{The \SecondShrouding}
Have a flashback to somewhere around the time of the \hs{\SecondShrouding}. 
Probably seen through the eyes of \Nzessuacrith. 

We see her flying over a vast battlefield, strewn with the corpses of mortals, \dragons{}, \cuezcans, \banes{} and \resphain. 

She meets \Secherdamon{} and talks to him. 
He spews his hate for \Ishnaruchaefir{}, since this is shortly after the tragic \hs{fall of \Nexagglachel}. 

She also talks to others, who comment on the conflict between \Ishnaruchaefir{} and \Secherdamon. 

This is before \hs{\ps{\Secherdamon} rise to power}, but \Nzessuacrith{} or someone else\dash probably an \ophidian\dash predicts that the youngest brother is bound for greatness\dash a terrible kind of greatness. 
You can see it in his eyes, the bitterness, the avarice and the determination. 





\subsubsection{\Nzessuacrith{} flying over \Machai}
Maybe have a scene where \Nzessuacrith{} flies over the plains of \Machai{}. 

\lyricslimbonicart{Twilight Omen}{
  My soul had black wings and triumphant I did fly.\\
  I rode the storms and the midnight sky.\\
  I saw the thousand lights from cities underneath me,\\
  as I ventured deeper into the night,\\
  to that sacred place beyond the twilight zone.
}





\subsubsection{The fall of the Heart}
They talk about how most of the immortals are now dead, and of how the Heart was been weakened and is no longer strong now to bring them back to their glory days.
It cannot support such a population in its current state, with both factions pulling and tearing at the Heart. 









\subsection{Silenced}
Catrian, a Sentinel woman living somewhere near \Redce, sees a \bane{}. She is killed by the Cabal. 

During her flight, she submerges into \Nyx. She sees the \hr{Black stars of Nyx}{black stars}. 

Despite being a Sentinel, Catrian has never seen a \dragon. She has, however, seen some of the \draconian{} people, the \rachyth. 







\subsection{Wanderer in Darkness}
Have a scene where the Cabalists in the Pelidor region discuss their plans, and fear who might interfere. The company includes \Teshrial, \Achsah{} and Charcoal, who has been summoned. A few more unnamed Cabalists (perhaps named), a few lesser \banes{}. Maybe they are in communion with \Azraid{}, although he is not present in person. 

They convene in a dark hall in \Nyx. Compare to the scenes in the movie \cite{Movie:Blade} where the council of vampire elders convene. 

\lyricsbs{Limbonic Art}{Suicide Command}{
  In the deep pitch black Halls of Darkness,\\
  the cruel high council of Evil demands self-destruction.\\
  All aspects of love must be undone.\\
  Only then one can feel the emptiness\\
  as the cold heart reaches beyond.
}

\Teshrial{} relates that he has detected an enemy presence, one who might endanger their plan. 
\ta{One of the \KhothSell{} bloodline... kin of our progenitor, \Nexagglachel.}

\ta{Who might that be? \Nzessuacrith? (Another name or two.)}

\Teshrial: \ta{Possible. But I fear we deal here with an even greater power. Perhaps even one of the eldest generation. One of the \shaeeroths, and of the purest royal blood.}

%\ta{Surely not \Secherdamon?} one of the others laughs. (Don't use \ps{\Secherdamon} true name. Use a title. The \quo{Chaos Lord}, the \quo{Chaos Tyrant}, the \quo{Serpent Lord}, the \quo{Serpentine King}...)
\ta{Surely not the esteemed \quo{\hr{\Secherdamon}{Serpentine Lord}} in person?} one of the others laughs. \ta{Or whatever it is he calls himself these days.} (This refers to \Secherdamon.)

\Teshrial: \ta{No, that idea is hardly credible.}

\ta{But... a \shaeeroth... and of the blood of our progenitor. That leaves only...}

(Whispered:) \ta{You mean... the wanderer? The (insert title of \Ishnaruchaefir.)}

\ta{I think not. He has not been active for centuries.}

\Teshrial: \ta{Then it would appear he has returned.}

(Shivers:) \ta{The wanderer in darkness. The one who forsook his people after the \SecondShrouding{}...}

\ta{Quessanth \Ishnaruchaefir...}

Maybe \Ishnaruchaefir{} should have the title of \quo{pureblood}. Compare to the movie \cite{Movie:Blade}, where this title is given to vampires who were born as such, and not merely turned. 

\Achsah: \ta{Beware Quessanth \Ishnaruchaefir, my Lord. He is a terrible foe, not to be taken lightly.}

\Teshrial{} bitchslaps her. Not hard enough to cause serious pain\dash that is against the rules\dash but hard enough to humiliate her. \ta{Do not presume to teach me, \ashenblood.}

Pause. He gives her a condescending smile. \ta{Hm?}

\Achsah{} bows. 
\ta{Yes, my Lord.} 
She scowls at him behind his back.





\subsubsection{Snippet from Gardens of the Moon}
\lyricstitle{\SEGardensoftheMoon}{
  "But, clearly, Caladan Brood and the Tiste Andii weren't the only inhabitants of Moon's Spawn. An unseen lord remained in control of the fortress, bringing it here and sealing a pact with Pale's formidable wizards."
  
  "Tattersail cleared her throat. 'What do we know about the Lord of Moon's Spawn?'
  
  'Scant little, I'm afraid,' Tayschrenn said, his eyes veiled. 'A Tiste Andii, for certain. An archmage.'
  
  Hairlock leaned forward and deliberately spat at the floor in front of Tayschrenn. 'Tiste Andii, High Mage? I think we can be a little more specific than that, don't you?'
  
  'An archmage,' Tayschrenn repeated. 'Perhaps the Archmage of the Tiste Andii...
  
  ...Hairlock bared his teeth. 'The Tiste Andii are Mother Dark's first children. You've felt the tremors through the Warrens of Sorcery, Tayschrenn. So have I. Ask Dujek about the reports coming down from the North Campaign. Elder magic - Kurald Galain. The Lord of Moon's Spawn is the Master Archmage - you know his name as well as I do.'"
  
  "'Anomandaris.'
  
  Hairlock's eyes snapped open, found Tayschrenn with bright pleasure. 'Ahh,' he said, into the silence following Calot's single pronouncement. 'Of course. Three more High Mages? Only three?'
  
  Tattersail stared at Dujek's pale, still face. 'The poem,' she said quietly, 'I remember now.
  
  'Caladan Brood, the menhired one,
  
  winter-bearing, barrowed and sorrowless...'
  
  Calot picked up the next lines.
  
  '...in a tomb bereaved of words,
  
  and in his hands that have crushed anvils-'
  
  Tattersail continued, 
  
  'the hammer of his song - 
  
  he lives asleep, so give silent warning
  
  to all - wake him not.
  
  Wake him not.'
  
  Everyone in the compartment was staring at Tattersail now as her last words fell away. 'He's awake, it seems,' she said, her mouth dry. '"Anomandaris", the epic poem by Fisher Keltath.' 
  
  'The poem's not about Caladan Brood,' Dujek said, frowning. 
  
  'No,' she agreed. 'It's mostly about his companion.'
  
  Hairlock climbed slowly to his feet. He stepped close to Tayschrenn. ' Anomander Rake, Lord of the Tiste Andii, who are the souls of the Starless Night. Rake, the Mane of Chaos. That's who the Moon's Lord is, and you're pitting four High Mages and a single cadre against him.' 
  
  Tayschrenn's smooth face held the faintest sheen of sweat now. 'The Tiste Andii,' he said in an even voice, 'are not like us. To you they may seem unpredictable, but they aren't. Just different. They have no cause of their own. They simply move from one human drama to the next. Do you actually think Anomander Rake will stay and fight?'
  
  'Has Caladan Brood backed away?' Hairlock snapped.
  
  'He is not Tiste Andii, Hairlock. He's human - some say with Barghast blood, but none the less he shares nothing of Elder blood, or its ways.' 
  
  'You're counting on Rake betraying Pale's wizards - betraying the pact he made between them.'
  
  'The risk is not as overreaching as it may seem,' the High Mage said. 'Bellurdan has done some research in Genebaris, Sorceress. Some new scrolls of Gothos' Folly were discovered in a mountain fastness beyond Blackdog Forest. Among the writings are discussion of the Tiste Andii, and other peoples from the Elder Age. And remember, Moon's Spawn has withdrawn from a direct confrontation with the Empire before.'
  
  "A figure had appeared on the ledge before the portal, its arms upraised, long silver hair blowing from its head.
  
  Mane of Chaos. 
  Anomander Rake. 
  Lord of the black-skinned Tiste Andii, 
  who has looked down on a hundred thousand winters, 
  who has tasted the blood of dragons, 
  who leads the last of his kind, 
  seated in the Throne of Sorrow 
  and a kingdom tragic and fey\dash
  a kingdom with no land to call its own.
  
  Anomander Rake looked tiny against the backdrop of his edifice, almost insubstantial at this distance. The illusion was about to be shattered. She gasped as the aura of his power bloomed outward - too see it at such distance..."
}



 






\subsection{What Slithers Beneath}
\target{Ishnaruchaefir attacks Teshrial's creature}
\target{Ishna fights Teshrial's monster}
%Have a scene earlier on where \Ishnaruchaefir{} fights one of them and only barely prevails. Maybe this is why \Ishnaruchaefir{} knows about them. 
\hr{Ishnaruchaefir}{\Ishnaruchaefir} visits Malcur to challenge \hr{Teshrial's monsters}{\ps{\Teshrial} \ghobaleth}.





\subsubsection{Walking through the city}
He brings along his servant, \hr{Criseis}{\Criseis}. She is nervous and afraid and asks him if it is really wise to challenge the monster in combat when they don't know more about it.

\Ishnaruchaefir{} walks through the city in humanoid form first. He is well-disguised, as is \Criseis. But \hs{Rian} notices them. He thinks they look suspicious, so he shadows them. He witnesses much of the fight. (\hs{Rian} is sharp-minded, so he can see quite a bit of the Beyond.)

As they walk through the city, they can feel the \ghobaleth{} beneath them. 

\lyricsbalsagoth{
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  Yawning wide beneath me... \\
  the jaws of the worm...\\
  Hearken, the spell is woven... \\
  the call of the worm...
}

Perhaps Rian has also met the \hs{crazy old woman}, who can sense the \ghobal{} worm.

Rian notices that \Ishnaruchaefir{} looks old, somehow. 
He can't quite see how. 
He doesn't have flaking loose or discoloured scales, nor is he as gaunt as a typical old \scatha. 
But something about him seems... old. 





\subsubsection{At the dead garden}
\target{Ishnaruchaefir summons his glaive}
\Ishnaruchaefir{} goes to the \hs{dead garden}, which is one of the mystic centres of the city, and the place where the monsters dwell. There he summons his glaive, \Triestessakhin. He flexes his left hand, and Rian sees that it has sharp claws, very un-\scathaese. With his left claw, he tears open the back of his right hand. He swings the wounded right, splattering blood, then holds the hand aloft to allow the blood to flow down. 

The \draconian{} blood, replete with \ophidian{} and \xzaishannic{} blood alike, seethes and sizzles, as if burning through the Web of the Realms, like acid dissolving the very fabric of reality itself. 

As the blood seethes, \Ishnaruchaefir{} speaks words of power in the \Draconic{} tongue. The \Draconic{} spellwords should sound sibilant, hissing, snake-like. See the \hr{Spellwords}{section on spellwords}. 

The words translate roughly thus:

\draconicspell{
Come to me, o' glaive. \\
By the blood of the \ophidians, \\
by the blood of the \xzaishanns, \\
by the blood that is life I give thee form.\\
I summon thee! \Triestessakhin! Arise!}

\Criseis{} shudders, as she does every time she sees her lord spill his blood and wield the cruel glaive. 

Remember: Whenever \Ishnaruchaefir{} smiles, you can see his sharp fangs. A monstrous trait that shows that he is more than a mere \scatha. He also has a flexible tail (albeit not as flexible as that of a \hyperref[Naga-Scatha hybrids]{\naga-\scatha{} hybrid}).

Also remember that \ps{\Ishnaruchaefir} Chaos spells should \hr{Invoking Daemons}{invoke the names of \xss{} and other \daemons}. 







\subsubsection{Battle with the \ghobal}
\Ishnaruchaefir{} draws out one of the \ghobaleth, fights it, and only barely slays it. 

As the way to the \Nyx{} opens and the \ghobal{} emerges, everything shifts into \Nyx. Rian sees the \hr{Black stars of Nyx}{black stars} and despairs.

\Ishnaruchaefir{} had already guessed the identity of the \ghobal{} on his way through the city, but he is still surprised. \ta{So, you brought a \ghobal{} to \Miith{}. Impressive. I am sorry to spoil your fun...}

Remember that \Ishnaruchaefir{} should speak in an archaic fashion, using words like \quo{yea} and \quo{nay}.

Remember to describe \ps{\Ishnaruchaefir} glaive, how it moans aloud and weeps blood and tears from its blade. See section \ref{Ishnaruchaefir's glaive}. 

Describe how \Ishnaruchaefir{} and the \ghobal{} affect \emph{all} of the five senses: Sight, hearing, smell, taste, touch. The \ghobal{} is \hr{Banes are cold}{\quo{cold as death}}, like a \bane. 

Rian is at the dead garden and witnessed the battle. But the garden is swathed in \wildfog, which blocked his vision somewhat. The true battle takes place in the Beyond, where both combatants fight in their true form\dash\Ishnaruchaefir{} as a colossal \dragon, and the \ghobal{} as a worm hundreds of metres long. But they don't break through the Shroud, so to spectators within the Shroud they appear in their masked forms\dash\Ishnaruchaefir{} as a \scatha{} or \rachyth, the \ghobal{} as a dramatically smaller worm of only ten metres or so. Or maybe a writhing mass of worms. 

Still, when \Ishnaruchaefir{} is not thoroughly masked, hints of his true form shine through. Rian gets an impression of massive size, colossal wings and more. (Unlike on the walk through the city, where \Ishnaruchaefir{} was more masked.)

Also, when they talk, they do so in \Draconic{} Kingstongue, so Rian does not understand a word.

We see the battle from the points of view of \Criseis{} and Rian. \Criseis{} comments \ps{\Ishnaruchaefir} \xzaishannic{} blood and power, and the \ps{\ghobal} \Erebean{} \hyperref[Entropy]{Entropic} power. 

Maybe \Criseis{} comments on \hyperref[Ishnaruchaefir's rage]{her lord's rage}, expressing a vague fear that it will be unleashed to cause destruction.

Remember that throughout the scene, \Ishnaruchaefir{} is smiling, relaxed, unperturbed and fearless.

In the end, \Ishnaruchaefir{} lets himself be swallowed whole by the \ghobal, then cuts it open from within. 





\subsubsection[Ishnaruchaefir and Teshrial]{\Ishnaruchaefir{} and \Teshrial}
\Teshrial{} confronts him. 

Describe the contrast between \Ishnaruchaefir{} and \Teshrial. \Ishnaruchaefir{} is in the form of a black-scaled \scatha{} dressed in black armour and robe, interspersed with blood red, especially on his glaive. 
\Teshrial{} has black skin, but he is clad all in white, \hr{Teshrial's appearance}{as described in his section}
%and his hair is white, too. He carries a sceptre-like mace or morning star.

\Teshrial{} also might wear \hr{\Resphan{} crystals}{armour made of crystal}. 

Does \Teshrial{} \hr{Banes are cold}{radiate cold, like a \bane}?

As Rian sees \Teshrial, he is overwhelmed by this splendid, magnificent being who must surely be an angel... nay, a god. 

\tho{Before his eyes was a god! A living god in the flesh!}

\ps{\Teshrial} \hr{Teshrial is androgynous}{androgynous look} helps convey a superhuman impression. 

Surely the god must have come to vanquish this devil, this dark sorcerer. Rian wants to kneel down and worship the god, but his fear and awe of the two combatants leaves him frozen and huddling, unable to approach, unable to even flee; unable to do more than witness.

Then, as we watches more, he begins to doubt who is the god and who is the devil. 

\Ishna: \ta{\Teshrial. I am glad to see that your virtues still include hospitality.}

Remember to pay attention to what languages they are using! 

\Ishnaruchaefir{} would be using \Draconic{} and \Teshrial{} would speak the High Resphan tongue.

\Ishnaruchaefir{}, who is wounded, says something to the effect of: 
\ta{%
  Your creature is gone. Your defenses are broken. I will come for you soon enough.}

\Teshrial: 
\ta{%
  I would love to fight you, but I am afraid I have too many appointments for the time being.}

\Ishna: \ta{Spare me, \resphan. Look at me. I am weakened. Weakened enough that you would stand a chance of besting me in combat. But you are too cowardly to face me, and too cowardly to even confess it.}

This causes \Teshrial{} to attack. \Ishnaruchaefir{} fights him off. 

\Ishna: \ta{Very well. I underestimated your character, \Teshrial. But I do not wish to fight you. I do not fight battles I might lose unless for a good reason. Fare well, \resphan.}

\Criseis{} comments on the battle and \ps{\Teshrial} power. (\hyperref[Teshrial's history]{Who is \Teshrial?})





\subsubsection{Rian encounters \Ishna}
\target{Rian is inspired by Ishnaruchaefir}
%Rian sees \Ishnaruchaefir{} and his servant, \Criseis{}, walking through Malcur. He thinks they look suspicious, so he shadows them. He witnesses much of the fight. (Rian is sharp-minded, so he can see quite a bit of the Beyond. See section \ref{Rian}.)
At the end, \Ishnaruchaefir{} looks Rian in the eye. Perhaps he even addresses him. (If so, remember to pay attention to what language he uses!) Rian is left in awe, with a burning hope to meet this awesome character again. 

The encounter with \Ishnaruchaefir{} gives Rian the motivation he needs to give up his life of crime. He was instilled with a burning desire to become cool, to become a hero, like \Ishna. 

Near the end, they do meet again.





\subsubsection{Rian asks the crazy old woman}
\target{Crazy old woman warns Rian about worms})
After the fight, Rian goes to ask the \hs{crazy old woman} about it. She does some divination and can reveal \ps{\Ishnaruchaefir} name. She is also able to link the \ghobal{} to Malcur's mystic past.

And she babbles about worms.

\lyricsbalsagoth{
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  Can you not see the coils of the worm all about you?\\
  Can you not hear the writhing of the worm beneath you?\\
  Can you not scent the breath of the worm riding the wind?\\
  Can you not touch the skin of the worm in all that surrounds you?\\
  Can you not taste the ichors of the worm upon your tongue?\\
  Do dreams of the worm not haunt your slumber?
}





\subsubsection{Rian is traumatized}
Rian remembers the horrible black stars that hung in the heavens. 

\lyricsbs{Robert W. Chambers}{The Repairer of Reputations}{
  \ta{I... wept and laughed and trembled with a horror which at times assails me yet. 
  
  This is the thing that troubles me, for I cannot forget Carcosa where black stars hang in the heavens; where the shadows of men's thoughts lengthen in the afternoon, when the twin suns sink into the Lake of Hali; and my mind will bear forever the memory of the Pallid Mask.}
}

He was also scared shitless from seeing \Ishnaruchaefir{} fight. He has lost sanity points (to use the terminology of the RPG \cite{RPG:CallofCthulhu}). 





\subsubsection{\Psyrex{} and \Secherdamon{} see it}
\Psyrex{} and \Secherdamon{} notice the fight and comment it. 
They remark on the fact that it is a blatant breach of the \charade. 















\section{The Runger War}
\target{Runger war}
\subsection{Daggers and \Daemons}
We go to Malcur (capital city of Pelidor), where Duke \Icor{} is assassinated by the Sentinels. 
But it has to be well-concealed, so it's not obvious that it's the Sentinels that did it. 
It must look like it's just the Rungerans. 

At a ducal ball, an assassin sneaks up to the duke during the dance and knifes him. She has the backing of Sentinel agents. It's their magic that lets her get close to the duke. But she is brainwashed and thinks it's all thanks to her own cleverness and stealth and the aid of a few contacts. 

The Duke has heirs (sons and daughters), but they are all very young (the teen-aged crown princess was killed in a war against Beirod some years ago). 
So his widow, the Duchess \Tiroco, suddenly becomes regent of Pelidor. 
We follow her and the general \hs{Sethgal}, who must lead the nation against the Rungeran invasion. 

% \Tiroco{} is a young \sphyle, much younger than \Icor{}. 
% She's his second wife. 
% His first wife bore one daughter but failed to produce any more children. 
% She then died, possibly poisoned by her husband's evil family. 
% And \Icor{} married \Tiroco{}, who gave him two or three children before his death. 





\subsubsection{Intrigue in Malcur}
\Tiroco{} now plans, in accordance with Pelidorian tradition, to crown her and \ps{\Icor} eldest son, the six-year-old Roric, as the new duke, with \Tiroco{} ruling as regent until Roric comes of age. 

But she has enemies in Malcur. 
Among them is Liocai, \ps{\Icor} sister. 
She wants to succeed him as duchess and wants to get rid of \Tiroco{} and her children. Allied with Liocai is the Viscount Osphal of Turmalin, probably the most powerful Pelidorian lord after the duke. He intends to seize the throne together with Liocai, then marry her and secure the throne for his descendants. 

Other power factors in Malcur are the Redcor, the \Telcra{} Church and the Imetric emissaries. And \hs{Sethgal}, the general. 

And, of course, then there the Cabalists and Sentinels. The highest-ranking Cabalist in Malcur is Charcoal, whose mundane identity is Captain Archibald Curwen, a mage in the Pelidorian army. Among Charcoal's subordinates is Needle, \ps{\Tiroco} maidservant. 






\subsubsection{History of Malcur}
See section \ref{Malcur} for the history of Malcur. 

Liocai is one of the keepers of the ancient secrest of Malcur. In the beginning, she antagonizes \Tiroco, believing that whatever secret business she is up to can be no good. But later, \Tiroco{} convinces her that she is actually working to save Malcur, and Liocai agrees to help her, sharing her occult knowledge. 

It turns out that she knows a shocking amount of things. 
Things that even the Sentinels don't know. 
Her knowledge is leaked to \Psyrex, who makes use of it to help his master's scheme to bring in \Nithdornazsh{} (see section \ref{Nithdornazsh}). 

After beginning to learn of these things, \Tiroco{} has some cryptic dreams, where she sees images from Malcur's history.





\subsubsection{Charcoal, Constance and \Onatol}
After the murder, the assassin is instantly caught. %There are some clues laid out which trace him back to Runger, but it takes a few days to reach this conclusion, and by this time, Morgan's army is already crossing the border. 
Archibald Curwen (Charcoal) interrogates her. Her name is Constance of Kintair. After some questioning\dash Curwen does not elaborate, but the word \quo{torture} hangs in the air\dash she confessed to knifing the duke. Apparently she was bought by Morgan, the king of Runger. She does not know much, only that she was to kill the duke, and that she would be rewarded greatly. She speaks of marrying Matthias, Morgan's son, but it is unclear whether she was actually promised this. At any rate, she's been to Runger and seems to be in love with Prince Matthias. What's more interesting, she names an accomplice: A noble Pelidorian mage, whose name is \Ambrose{} \Anatoli{} or something like that. 

Her naming \Anatoli{} came as a surprise to Charcoal. He doesn't entirely belive it. He suspects something strange is going on, but he acknowledges the possibility that \Anatoli{} is a Sentinel. 

\Tiroco{} sentences Constance to death by hanging. (This is later mitigated to death by beheading, since she is, after all, noble-born.) She also orders that they arrest \Anatoli{}. 





\subsubsection{Charcoal kills \Onatol}
Curwen goes to grab \Anatoli{}. He is an old man and known to have a passion for science. It is revealed that he has had contacts in Runger, other mages doing research. There are also clues that he was hired by Morgan Runger to assist in the assassination in exchange for research funding and stuff. 

In truth, \Anatoli{} did have contacts in Runger. He kept them secret because of the well-known enmity between the two countries, but they were rather benign in nature. But the evidence of conspiracy with the king is fake, planted by the Sentinels to frame \Anatoli{} and draw attention away from the true plot. 

\Anatoli, driven mad by a Sentinel spell, resists arrest and fights back with his insidious Chaos magic. Remember to have him invoke aloud the sinister names of \daemons{} and wicked gods. 

He kills some soldiers, but after a short, bloody fight, Charcoal-tachi take him down. 

Remember that \ps{\Onatol} Chaos spells should \hr{Invoking Daemons}{invoke the names of \daemons}. 

After killing \Anatoli{}, Charcoal walks away musing. 
%(Charcoal is Curwen, of course, but that is not to be stated yet.) 





\subsubsection{Charcoal grabs Tantor's journal}
Charcoal grabs \hs{Tantor's journal}, which he found in \ps{\Onatol} room.





\subsubsection{Charcoal returns to Constance}
It's made known that Charcoal was present during the interrogation of Constance and took pleasure in raping the girl. 

In the end, Charcoal sneaks back to Constance's cell. She is to die, after all, but she is cute, so he wants to rape her some more first. 

%At some point, \Anatoli{} is killed. Maybe immediately, resisting arrest, or maybe he is arrested and then later tries to escape and has to be killed. This is due to a Sentinel fucking with his mind, inciting him to violence. They do this because they don't want him to testify and ruin their fake story (see below). 





\subsubsection{The haunted dungeon}
\target{Malcur dungeon haunted}
On his way to Constance's cell to rape her, Charcoal passes through the torture chambers of the dungeon. The torture chambers are a terrible hell hole, a madhouse where the Shroud is worn thin, serving as a passage to the horrible Realms Beyond. 

There is a reason why Charcoal has secured for himself the postition as master interrogator: 
The true nature of the torture chamber must be kept hidden. 
It is not necessarily much different from any other torture chamber, but it is still a hole in the Shroud, and the existence of such holes (and, indeed, the existence of the Shroud itself) must be kept from the un-initiated. 

Most of the people who work in the torture chambers are barely ever seen outside them. They are terrible degenerates, warped in body and mind by the horrors they have not only witnessed but been surrounded by for years. 

Perhaps one of the guards has lived in the dungeon all his life, a rape-child born of a prisoner. 
Compare to \cite{VictorHugo:HunchbackofNotreDame}.

As Charcoal passes through the dungeon, he sees through the open gaps into the Beyond. He fails to repress shivers at what he sees. Ghosts stare back at him with blind eyes full of despair. Some of the ghosts still bear chains, psychologically bound by the chains that bound them until their deaths. 
Some of them babble endlessly to themselves. 

He also meets \daemons{} that haunt and prey on the hapless ghosts. 









\subsection{Moro \Cornel}
\target{Moro feels Ishnaruchaefir and Teshrial}
Moro \Cornel{} feels the battle between \Ishnaruchaefir{} and \Teshrial{} in the dead garden. 
(She does not feel the \ghobal. It is too deeply Shrouded and concealed.) 

A bit later she goes to the garden to investigate. 
She cannot find anything.
\ta{My spiritual senses are too dull.} 

She touches the ground and concentrates as much as she can. 
For a brief moment she feels the presence of some gigantic creatures, crawling around her or under her. 
But only for a brief moment, and very indistinctly. 

\tho{It might be my imagination.
  It would not be the first time my paranoia and traumata have had me see things. 
  
  If only I were more sane...}








\subsection{War is Coming}
\target{Pelidor-Runger war}
The king of Runger plans to invade Pelidor after the assassination of Duke \Icor. 
%Flash to Dolmina, the capital of Runger. We follow some character in King Morgan's court who witnesses some of the events that transpire. 

%A Rissitic (Sentinel?) agent talks to the king and tells him that it is done; \Icor{} has been killed. 





\subsubsection{In Dormina}
Flash to Dolmina, the capital city of Runger. 
Insert a scene before \Icor{} dies: 

\hs{\Takestsha} agent talks to King Morgan and and tells him that everything is in motion; soon \Icor{} will be dead. 
The king is pleased and issues the order to mobilize the armies and march on the Pelidorian border.

Flash forward to after \Icor{} is dead. 

We follow some character in King Morgan's court. 
Perhaps a commander, perhaps a mage, perhaps even a Rissitic or Sentinel. 
In any case, someone close to the king. 
We follow them on their march and see them attack and conquer some towns near the border. 
The garrisons are slaughtered and we hear hints that the king and his mages have yet to unleash their most deadly weapon. 





\subsubsection{In Malcur}
\Tiroco{} and her court have received word that war is coming. 
\hs{Sethgal} is appointed Marshal and leads the armies into battle. 
\Cornel, Curwen, \Dornaer{} and many nobles are off to war, leaving Malcur somewhat depopulated. 

%Liocai and Viscount Osphal may also be with the army. 
Liocai is with the army, as are Osphal Turmalin's two daughters. 
Osphal himself, an aging widower, is too old to go off fighting, so he remains at the court. 

\Tiroco{}, not a trained warrior, remains in Malcur to rule, much to Liocai's chagrin. 
With her are \Vincerre{} (Camilienne being sent with the army), Norden and Bartholomy. 









\subsection{Beyond the Veil}
In Malcur they hold a funeral for \Icor. \Tiroco{} wants his spirit laid to rest so she can concentrate on moving on. 

We follow \Icor{} from the point of his death. He gets stabbed, then bleeds to death. At first he can still speak, but he quickly grows numb and can only lie there. He can still hear \Tiroco{} and feel her touch, but even that fades. 

Camilienne comes to heal him. He feels the \Sephiroth{} enter his body. He's fought wars and been healed by the \Sephiroth{} before, and it's always felt nice, but this time it's different. Death lifts the Shroud a little bit and lets us see some of the things we don't want to see. And now the dying \Icor{} vaguely sees the \Sephiroth{} as what they truly are: Horrors created by the \banes{} to enslave \humanity{} and enforce the Lie. He fears and despairs. 

After a while, the \Sephiroth{} dissipate. Camilienne proclaims him dead. He finds that he still has a bit of feeling for the living world. He can still feel \Tiroco{} a little bit. Which is bad, because he feels her pain and despair. 

Then he starts hearing the \daemons{} of the void. There are the occasional \daemons{} who have learned \Miithian{} languages and torment the dead to pass time. He is plagued by some of them. 

The \daemons{} go away and he floats around for a while in complete solitude, unable to perceive anything. He fears he is losing his mind, not wanting to spend eternity as a mad ghost. 






\subsubsection{\Icor{} sees vision of soul prison}
In the afterlife, \Icor{} sees a vision of a prison of souls: Thousands, perhaps millions of souls, chained and enslaved, screaming and weeping, bound within a horrible cage. 

This is actually the \Sephiroth{} that he sees. 

He sees souls of the dead being sucked into this Hell, into eternal suffering and torment. Some of them beg for help. A few are able to see him. They reach out to him, imploring him to save them. But he can't. Not only has he no idea of how he could help them; he is also paralyzed by fear. When one of the dead moans its pain and stretches its ghastly fingers toward him, he can only recoil in disgust, and feel guilt at his own cowardice, weakness and cruelty towards the tortured souls. 

Maybe he hears some dead souls talking. They are halfway or wholly mad and babble nonsensically. 






\subsubsection{\Psyrex{} approaches \Icor}
Why does he see it? 
Well, he is dead, so he is drifting towards it, until he is rescued by \Psyrex. 

\Psyrex{} comes to him in the guise of a child-like Cherub. 
 
\ps{\Icor} vision of the Realms is a bit clearer than normal, because he already had cause to suspect the \Sephiroth{} due to the events surrounding his death. 
And maybe \Psyrex{} helps him, showing him visions to scare him. 
(Of course, \ps{\Psyrex}{} interpretation of what \Icor{} sees is far from reality, and \Psyrex{} knows it.)

\Psyrex{} warns him that what he sees is \Itzach, where the souls of sinners go, and that \Icor{} must help him if he is to be considered among the righteous and avoid being thrown into \Itzach{} himself. 
\Icor{} doesn't quite believe \ps{\Psyrex}{} claims of holiness, but he sees no better choice. 







\subsection{Needle}
Charcoal goes to \hs{Needle}. Since Charcoal is going off to war, he gives her instructions to take over the local Cabal in his absence. 

Charcoal is certain that something fishy is going on in Malcur. He suspects Sentinel activity, mages preparing something of \quo{cataclysmic proportions}. He is also convinced that they know of the Cabalist presence in Malcur, since he has had agents killed and spells broken. 

He already has men out searching for them and wants Needle to take over the investigation. If they discover anything, they should destroy them, if possible. Show them that the Cabal means business. 

Even striking without really knowing what they're up against might be a good idea, because the Cabal is usually always careful and not happy to take chances, so if they come in with full force, it might convince their enemies that they know more than they do, and thus frighten them into being more reluctant, buying the Cabalists valuable time. Plus, if their enemies are afraid, they get stressed, and when stressed they are more liable to make mistakes that give them away. 

When done giving instructions, he fucks her. 









\subsection{For War and For Glory}
The Pelidorian army sets out from Malcur, marching towards the Rungeran border to fight. (This needs not be a chapter, perhaps.) 

Carzain has been outfitted: Hardened leather armour, a light breastplate and a metal helmet. Heavy, reinforced boots and tough leather gloves. Most of it black, his favourite colour. \tho{Goes with my hair,} he says.

\target{\Malcuric{} city gates}
They march through the \Malcuric{} city gates, which are enormous. Wide enough for an entire army to march through, almost in one broad line. 

Also, remember to tell us how big the Pelidorian army is. How many men?

And what about the Rungeran one?









\subsubsection{Portrayal of the armies}
Remember to describe the Pelidorian army as \hr{Glorious armies}{magnificent and glorious}. 

The Pelidorians use war elephants. 
So do the Rungerans. 
And maybe war rhinoceroses, too. 

The Rungeran army is also \hr{Glorious armies}{huge and epic}. 
They have war elephants and war rhinoceroses. 

Remember, the Pelidorians mustn't be portrayed as too good. 
The \hr{Rungeran temple magic}{Rungeran magic} is monstrous, but the magic wielded by the Pelidorian \ishrah{} is also bloody and grim.





\subsubsection{Rungeran Blunderbores}
The Rungerans have a number of \quo{ogres}. They look like \humans, but bigger, uglier and more monstrous. They have bestial faces with big-ass nasty teeth. Compare to the Ghouls in the game \cite{VideoGame:WarcraftIII} and the more monstrous Persians in the movie \cite{Movie:300}. 

Perhaps they are like the Blunderbores of the game \cite{VideoGame:DiabloII}: Giant-sized, wretched abominations, mentally warped and underdeveloped, and kept as slaves, beasts or worse. 

Some of them have had their arms amputated at the elbows, like the giants in a deleted scene in \cite{Movie:300}. This makes them unable to feed themselves in the wild should they flee, so they are forced to remain and live as slaves. 
When they march into battle, some of them have blades attached to their arms, like the monstrous executioner in \cite{Movie:300}.

Have the Pelidorians encountered these ogres before, or are they newly acquired exotic things imported from the \hs{Far Orient} or something?





\subsubsection{Pelidorian war \grulcans}
\target{Pelidorian war \grulcans}
The \hr{Pelidor symbol}{symbol of house Pelidor} is a \hs{\grulcan} bird. They tame these birds and use them as beasts of war. The bird also live in the wild in Pelidor and surrounding lands. 













\subsection{The Mystery of \EreshKal}
Charcoal reads Giles Tantor's journal. 

The whole thing might be written in some cipher code, but it's one Charcoal can easily decode. 

Just before Tantor reaches the lost temple, Charcoal is interrupted by a soldier who comes knocking on his tent flap. (For no specified reason. Curwen just has duties as an officer that require his attention.)







\subsection{Veils that Divide} 
\Icor{} comes back as a ghost. 
He finds his own funeral. 

He tries to communicate with \Tiroco, but fails.





\subsubsection{\Tiroco{} as regent}
\Tiroco{} and \Icor{} were married in an attempt to reconcile two branches of the Pelidor clan, the \Malcurians{} and the \Forkliners. 
Now that \Icor{} is dead, the clan fights over who should be the next duke. 
They can't decide and vote while there's a war going on, so they postpone the decision till after the war. 
This means that \Tiroco{} is stuck as regent until then. 

This is part of \ps{\Psyrex}{} plan. 
\Tiroco{} is weak and easy for him to manipulate, especially when he has \Icor{} as leverage. 







\subsection{A Dark Angel's Gift}
Needle is sitting in her room, setting her hair, putting on makeup and making herself pretty. She is happy that Charcoal is gone. She hates Charcoal, and she loathes being his sex slave. 

Charcoal is cruel and evil and does all he can to make the sex painful to her. In the beginning he took her often, because she was beautiful. She caught on and started deliberately making herself ugly, so he would be turned on by her and thus rape her less often. He may or may not know this. Once in a while he beat her as punishment for being ugly, but he did fuck her less often. Needle accepts the trade: She would choose his whip over his dick any day of the week. 

But now Charcoal is gone and she can be beautiful again. Like any girl, she much prefers being sexy. 

She hasn't become pregnant with him, for which she is very grateful. It is the magic, she knows. All that spellcasting \quo{sucks all the power and life out} of his sperm, leaving it ashen and dead. His cum tastes bitter and dead, too. The cum of a real man, while it may not exactly taste good, at least feels alive, energetic. 





\subsubsection{\Achsah{} seeks out Needle}
\hs{\Achsah} seeks out Needle and gives her new instructions. 

When Needle flinches, \Achsah{} assures her: 
\ta{No need to fear, girl. I am not going to rape you.} 
She pauses, then adds: 
\ta{I have higher standards than that.}

She gives Needle a gift: She teaches her a spell that lets her summon \Achsah{}, to communicate or to send reinforcements. 







\subsection{The Gods of \EreshKal}
Charcoal reads more in Tantor's journal. Tantor-tachi reach the temple of \Rungertemple. Inside they find tablets of arcane scribblings. 

The tables show fragments of the cosmic paths that connect \Miith{} and \Machai; the paths that were mapped out by \Tiamat{} and \ApepNesthra{} tens of thousands of years ago (see section \ref{Tiamat maps the way to Machai}). 

Maybe \Shilred-tachi find some of the same \hr{Ishnaruchaefir's fake mission}{in their cave}, and Carzain-tachi likewise in the Ghost Tower. 





\subsubsection{\Takestsha{} is a prodigy}
Tantor is impressed by how skilled \Takestsha{} is, considering her young age (she is supposed to look around 30). (This is perhaps a bit of a slip-up by \Nzessuacrith. She shouldn't be attracting attention like this.) 
Tantor explains it to himself by referring to \ps{\Takestsha} \quo{forbidden knowledge}. Charcoal buys this. 





\subsubsection{Charcoal is convinced that \Takestsha{} is not a Sentinel}
Charcoal reads Tantor's journal. 

Tantor has sex with \Takestsha. But he doesn't write it explicitly. He is ashamed of it, because he has a wife and is a faithful \Iquinian. But it shines through in his later words (he often dwells on \Takestsha, describing how beautiful, alluring and teasing she is). So Charcoal deduces it and laughs at Tantor. 

\target{\Takestsha{} on the run}
Tantor emphasizes how \Takestsha{} is on the run from her former masters/teachers, how they try to kill her because she knows too much, having discovered something forbidden. They are portrayed very much as Sentinels trying to uphold the \charade. 

Charcoal buys it. So he telepathically warns his fellow Cabalists that Runger is aided by a rogue non-Sentinel mage possessed of some terrible occult knowledge. 









\subsection{Captured}
\target{Rian's missing girlfriend}
Introduce Rian. He is a Malcurian boy of maybe 16-17, an orphan who used to be a thief. But at some point in his teens he helped a carpenter and his family. As thanks, the carpenter took him in as an apprentice, to help him get out of a life of crime and into a decent, honourable career. 

Now, Rian has a girlfriend, namely Neina the baker's daughter. They are engaged to be married in a year or so, but Rian is a horny youth and can hardly wait. We meet them an evening when he is walking her home for some reason. They are kissing in a corner, and he moves in under her blouse to grope her breasts, but she stops him. He relents and kisses her goodnight, and they part ways. 

She walks to her house, but she is intercepted by a thug working for the Sentinels. He knocks her out and kidnaps her, intending to use her as a sacrifice for the \Nithdornazsh{} ritual. 







\subsection{Carzain rejoins the army}
\target{Carzain rejoins the army}
Carzain \Shireyo{} has heard news of the war against Runger. 
He now comes to rejoin the army, and his old acquaintance Archibald Curwen. 

Carzain comes to rendezvous with the army in or near \Forklin. 

Vizicar is with him in his head and comments on the look of the city. 
He knew the early \Ortaicans{}, so he recognizes the design a little bit. 
But the \Ortaicans{} evolved a \emph{lot} in the centuries after Vizicar's time. 

Vizicar knows he is more than a \human, and he tells Carzain this. 
Vizicar wants to attain \kenosis{} and regain his body, power and memory. 
Then he wants to achieve \apotheosis{} and learn his true nature.
Then will he be a god. 

Carzain is not completely young and inexperienced in the Runger war. 
He has been to war before. 

The mutiny in Heropond happened several years earlier. 
Back then, \hr{Carzain joins the army}{Carzain joined the army} because he hoped it would help him find out what was happening to him, who he was and who Vizicar was. 

Several years later, Runger invaded Carzain's homeland. 
He figured he would fight them. 
So he rejoined the \ishrah{} and was reunited with his old acquaintance, Curwen. 

At the beginning of the Runger war, Carzain is already close to full \kenosis. 
Maybe he \emph{has} achieved perfect \kenosis. 
He is ready to grasp for \apotheosis{} now.

At the beginning of Carzain's part in \emph{\TwilightAngelRemember}, have several \emph{short} Vizicar scenes to clarify that he has attained \kenosis. 




\subsubsection{Carzain sees the Ghost Tower}
\target{Carzain passes near the Ghost Tower}
Carzain rides out to take a look at the Ghost Tower. Maybe he just goes out to explore, or maybe Curwen takes him (and his fellow mages?) out and shows it to him. 

Maybe he hears the \hr{Haskelek myth}{myths about the \Haskelek} here. Or maybe he doesn't hear it before \hr{Carzain returns to \Forklin}{he returns to \Forklin}.







\subsection{\Forklin}
Several days have passed since the Pelidorian army set out from Malcur. 

On their march north, the army passes through \Forklin. They camp there. 





\subsubsection{Curwen meets \Esmerel}
\target{Esmerel in Pelidor}
The Pelidorian army, led by \hs{Sethgal}, is marching out from Malcur. Soon after, they are joined by Redcor \Matron{} \Esmerel. 

\Esmerel{} is in Pelidor not to search for Scions, but to oversee and monitor the war. 
She is there to provide healing and \quo{spiritual guidance}, which in practice means she is a spy and a lobbyist trying to make people owe her a debt of gratitude. 
She intends to help heal the wounded. 
And maybe intervene and give more direct help in combat if it should be required. 

The Redcor do not trust Morgan Runger. 
He has long been unwilling to heed (read: obey) his Redcor advisors. 
They suspect him of using black magic and being disloyal toward the Iquinian faith. 
They are unhappy about this. 
They feel Morgan might need to be taught a lesson about disrespecting the Redcor. 

She meets Curwen and asks him questions. 
Curwen doesn't trust her, so he's evasive. 

\Esmerel{} might have \Racel{} with her as an assistant. 
This is because \Racel{} is Pelidorian.
It is pure coincidence that Carzain happens to know her. 





\subsubsection{The Pelidorian officers discuss strategy}
The Pelidorian army is now near the Rungeran border. 
The officers discuss strategy. 
Marshal \hs{Sethgal} is there, as are Curwen, \Sanyor{} and \Dornaer. 





\subsubsection{Carzain goes on a sortie}
The Pelidorian army sends out a small force to scout ahead and raid the Rungerans a bit. 

Curwen is going, and decides to take Carzain along. 
\hs{Delph} comes with them as a bodyguard. 

Also, remember to tell us how big the sortie is. How many men?







\section{The Cancerous City}







\subsection{Trinity of Pestilences}
\hs{Rian} is in the slums of Malcur, searching for \hr{Rian's missing girlfriend}{his missing girlfriend}. 

The slums are filled with death, poverty, destitution, despair, hunger, hopelessness. The poor, degenerate people are almost living dead. They live as pitiful scavengers. Some of them even eat \human{} and \scathaese{} flesh. 

They are useless, unloved parasites. As opposed to the nobility, who are useless but celebrated parasites. 

Is Rian pro- or anti-nobility? He is probably pro, inspired by idealistic stories of heroes and greatness, longing for an escape from the destitution that surrounds him. If so, the above quote about poverty vs. nobility should be one he recites from an old friend from his thieving days. 

There are many cults in the slums, including the \hs{Cult of the Worm}. Some cults are real, some are pure charlatans. 

Compare to Calcutta in \cite{PoppyZBrite:CalcuttaLordofNerves}. 

\target{Rian sees the \Morbus}
He sees the \hs{\Morbus} at work, how it transforms people into wretches, and eventually into the living dead. 





\subsubsection{Rian and the crazy old woman}
Rian goes around in the city asking his old thieving acquaintances. Among others, he talks to the \hs{crazy old woman} who lives near the \hs{dead garden}. 

The old woman tells him that the trees are getting restless, that something is going to happen. She warns him of \hr{Teshrial's creatures}{the worms}, just like \hr{Crazy old woman warns Rian about worms}{she did earlier}. 

\lyricsbalsagoth{
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  Can you not see the coils of the worm all about you?\\
  Can you not hear the writhing of the worm beneath you?\\
  Can you not scent the breath of the worm riding the wind?\\
  Can you not touch the skin of the worm in all that surrounds you?\\
  Can you not taste the ichors of the worm upon your tongue?\\
  Do dreams of the worm not haunt your slumber?
}

Not only that. The crazy old woman tells long, cryptic stories of the alleged nature of the universe. Compare to the legend told by Redmask in \cite[p.340]{StevenErikson:ReapersGale}, or Feather Witch's Tile castings in \cite{StevenErikson:MidnightTides}, or Fiddler's Deck reading in \cite{StevenErikson:TheBonehunters}.






\subsection{Where Angels Fear to Tread}
After the funeral \Tiroco{} is visited by \ps{\Icor} ghost, first in her dreams. 
\Icor{} mourns and complains that he is trapped in limbo and unable to go into the Light. He begs \Tiroco{} to help him by doing something in the crypt.

% (Is there a closed crypt or only an open cemetery?)





\subsubsection{\ps{\Icor} point of view}
\ps{\Icor} mind is hazy from being a ghost. 
He tends to forget \ps{\Psyrex}{} instructions, and even the mere fact that he's a ghost.

He has a hard time getting through to \Tiroco{} due to the Shroud. 
He tries to appear in shadows, in mirrors, behind curtains and stuff\dash places where people's Shrouded perception of reality is weakened, where they are more open to the possibility of strange things happening. 
But if he is behind a curtain and talking to her, and she pulls the curtain aside, then he \quo{vanishes} and she will see right through him\dash the Shroud separates them. 

He is frustrated by what he perceives as \Tiroco{} being stupid. 
He is gradually going mad. 

\lyricsbs{Hate Eternal}{Two Demons}{
  I am diversity. So weary of the angst, 
  so weary of what I have become.\\
  Through this dread I will retain 
  this penance that still haunts me.
  
  I am complexity. Within these walls that hold me, \\
  my past and my present collide.\\
  In this state I must sustain
  this morphing that becomes me.
}

But he also wants to \hs{stop the evil} that is festering in Malcur. 

It should be noted that \Icor{} sees the regular, Shrouded world and not the true world. 
This is due (in part) to a Shrouding spell cast on him by \LocarPsyrex. 





\subsubsection{\ps{\Tiroco} point of view}
In the beginning \Tiroco{} doesn't believe in it, thinking that it's just her sorrow and wishes that manifest in dreams. But the dreams become more insistent, and she begins to see \Icor{} even when awake (mostly at evening or otherwise in the dark, because the Shroud is more easily penetrable in darkness). 

She begins to believe that the visitations are real. She visits a priest of some sort, probably William Norden, to seek spriritual advice. Norden tells her that ghosts should not be listened to. For the most part, ghosts are not real, but illusions conjured by the \Qliphoth{} to trick people. And if the ghosts are real, they must be mad and twisted, and their pleas should not be heeded.

So \Tiroco{} tries to ignore the ghost, but \ps{\Icor} visitations become more frequent, and he begs and pleads, then blames her for betraying him. At last he guilts her into complying. 

The concrete things he wants her to do are quite complex and take a while to complete. She needs to consort with disagreeable people in the Malcurian underworld and do furtive, suspicious things. At the same time, \Icor{} tells her that she must not reveal anything to the churches. He says they won't understand and will try to stop her. What she must do is suspicious and dark in nature, consorting with powers normally considered forbidden. But, \Icor{} assures her, it's the only way to free him. If the church's dogmas are to be observed, he will be trapped in limbo forever. Already, he says, he is losing strength, and soon he will be unable to contact her, doomed to float forever in pain and solitude in the cold void. 

So \Tiroco{} gets to work, contacting people and acquiring components necessary for \ps{\Icor} \quo{exorcism} ritual. 

But she also wants to \hs{stop the evil} that is festering in Malcur. 





\subsubsection{Intrigue in Malcur}
Remember Liocai, \ps{\Tiroco} enemy. She is up to something. She discovers that \Tiroco{} has something fishy going on, so she sets out to find out what it is, and put a stop to it, if possible. 
(What is Liocai like? 
 Is she good or evil? 
 Does she have an ulterior motive, or does she just not like \Tiroco?)

And there is Moro \Cornel, the archmage. 
I need to use her for something. 
She is sneaky and sniffs stuff out. 

Maybe \Cornel{} goes undercover into the city to investigate. 
She might meet Rian and help him. 







% \subsection{\MageCadre{} intrigue}
% There is intrigue in the \Malcuric{} \magecadre. 
% 
% Lieutenant \Sanyor{}, a \scathaese{} Chaos mage, is Curwen's more-or-less trusted second-in-command. Unbeknownst to Curwen, \Sanyor{} is actually a \cuezcan{} agent. He might \emph{be} a \cuezcan{} in disguise himself, or he might just be a \scatha{} who works for them. At any rate, he knows that Curwen is Charcoal, and he works to undermine and mislead him. 
% 
% There is also \Hicorrim, another \scathaese{} Chaos sorcerer. Curwen doesn't like him and suspects him of being a Sentinel or otherwise a mole. \Sanyor{} knows this and actively (but subtly) works to frame \Hicorrim: Every time \Sanyor{} does something suspicious, he does what he can to make it look like it was actually \Hicorrim{} doing something strange. \Hicorrim{} doesn't realize this\dash he is a skilled mage, but a nerd, unskilled in social matters. Curwen believes that his eccentric, absent-minded pose is a ruse, but it's actually genuine. 
% 
% What exactly is \Sanyor{} up to? Well, spying on Curwen, for sure. But he must have some long-term sinister plan as well...





% \subsubsection{Size of the army}
% Also, remember to tell us how big the Pelidorian army is. How many men?












\subsection{The Terror of \EreshKal}
The sortie, that includes Carzain, pass by a Pelidorian village. It has been destroyed by the Rungerans' evil magic (as a test of their spells). They are horrified by the foul sorcery at work. 








\subsection{The \Qliphoth{} Lie Ever in Wait}
\Tiroco{} must move the guards around and divert the attention of the church and authorities. \Icor{} tells her that \quo{they would not understand}, that they, in ignorance, would sabotage their undertaking, dooming him. (Is it only \Icor{}, or are there more ghosts? I think he tells her that she is saving not only him, but many ghosts.) 

%Here's an idea: \Tiroco{} goes on a campaign against \quo{superstition}. She 
In order to do her undergound work, \Tiroco{} officially goes on a campaign against superstition. She approaches the church and convinces them to help her \quo{calm down} the population and suppress nasty rumours of ghosts, black magic and sinister crime. 
Fear is rampant in the country, after all, since the duke has just been murdered and the king of Runger has declared war. So the peasants and citizens need to be reassured, need to forget their fears. 
And this is handy, because if stories of supernatural activity are suppressed and dismissed as superstition, it makes it much easier for \Tiroco{} to do her furtive work. 

And then we hear the story from the perspective of some normal citizen who sees horrible, unnatural things happening, while the church and authorities tell him to forget it, that it's all delusions. This is \hs{Rian}, the ex-thief with the missing girlfriend, Neina. 

This is good for two reasons: 
First, it's a clever move by Tiroco, which helps give her some personality. Until now she's been a very tame character with no real skills, so she needs this. 
Second, it gives me the opportunity to write some horror parts featuring some \quo{common} people who can be genuinely horrified (as opposed to the mages and heroes who are otherwise my main characters, who are less easily frightened). 

What she is doing is a cruel, brutal oppression of her people. Needless to say, she does not respect modern \human{} rights in \emph{any} form. Like the War on Terror in RL. But see it from her point-of-view, where she justifies her crimes. Her love for \Icor{} is weighed against her obligation to her country. 





\subsubsection{She wants to stop the evil}
\Tiroco{} hopes to stop the mystic evil that is festering in Malcur. 
She hopes she is doing the right thing. 









\subsubsection{Needle notices \Tiroco}
Needle notices that \Tiroco{} is acting strange: 
Furtive, paranoid, jumpy, and keeping lots of secrets. 
Needle suspects that she is up to something. 





\subsubsection{Needle has sex}
Needle has sex with a subordinate Cabalist. 

I don't know if she uses him as a boy-toy or if she lets him dominate her. 

She moans: 
\ta{Oh! You are \emph{so} much better than Charcoal!}

Afterwards, she warns the man: 
\ta{Oh, and by the way. 
    If you tell anyone that I moaned about your being better than Charcoal, I will make sure you die a horrible death.}





\subsubsection{Rian is threatened by a thug}
Rian snoops around in the dark corners of the city, trying to sniff out clues about his girl, Neina. 
He sees something suspicious, 
which might be some of the Sentinel agents, out doing their shady work. 

Then he is jumped by a thief. The thief turns out to be an old \quo{friend}, so for old times' sake he does not kill Rian. He merely slaps him up and tells him to go home and stop snooping around. 









\subsection{The Emperor Inviolate}
The sortie encounters a small Rungeran force. They fight. 

Carzain fights and kills. 
But he is not as great a warrior as he fancies himself. 
So he gets clobbered and takes wounds. 

He calls out to Curwen-tachi for help. 
They save his ass. 

Then Vizicar awakens. 
It's due to a combination of factors: 

\begin{itemize}
  \item The pure rush of combat. 
  \item The anger and shame over being defeated in combat by such lowly grunts. 
  \item The wounds leave Carzain's own conscious mind weakened, making it easier for Vizicar to take over. 
\end{itemize}


% Recall that Carzain is a Scion, an incarnation of the \Malach{} Ramiel. 
% Occasionally, when he fights and kills, Ramiel awakens in him, and he hears the voice of \VizicarFull, the previous incarnation of Ramiel. (This is inspired by, and similar to, how Rand al'Thor in Wheel of Time hears the voice of Lews Therin Telamon. But where Lews Therin is mad, annoying and even dangerous, Vizicar is sane and a powerful ally.) 

% Anyway, Carzain fights and kills, and Vizicar comes along and takes over. 

Curwen immediately senses something fishy, probably a \vertexspike{}. 

This time there is a struggle between Carzain and Vizicar, as Carzain tries to get back in control of his own body. 

%After the battle, Carzain falls unconscious as Vizicar retreats. The prolonged, unaccustomed possession and the struggle between the two personas was too much for his consciousness to take. 

After the battle Curwen probes, prodding Carzain into telling him stuff. Carzain tells a little of what he knows, but it's not much. 

Carzain's body is in a bad shape. 
Vizicar is a harsh master and takes poor care of it. 
This is because Vizicar is only half-awake. 
He's still in a half-dreamy state, and his senses are weakened. 
He doesn't entirely register the pain, so he just pushes on. 
So after the fight Carzain is a useless wreck, barely conscious. 

Maybe Carzain asks the others: \ta{Did I save the da?} 

The others: 
\tho{Save the day? You crazy fuck, you nearly killed yourself, and maybe us, too.} 
\ta{Um, yeah. Sure. You saved the day.}

Delph is scared by Carzain's weirdness. Maybe insert an inner monologue with Delph about how Carzain is a crazy weirdo: 
\tho{Typically. 
     Finally I meet a guy who seems trustworthy, who might become a true friend, and turns out he is a madman. 
     Or possessed by \mdaemons{}, or whatever. 
     Huh. 
     That'll teach me to trust a sorcerer.}

During the fight, Carzan does something stupid and reckless. 
Perhaps he sees an enemy Vaimon and goes in to capture his sabre. 
Afterwards, Curwen bitchslaps him and scolds him: 
\ta{You crazy fuck, \Shireyo!
    What the fuck were you trying to do?
    You very nearly got yourself and the rest of us killed!}
He grabs Carzain by the collar. 
\ta{Let me tell you something, boy.
    Your insubordination stopped being charming a long time ago. 
    Now either you get in line or I'll have you beaten!}





\subsubsection{Vizicar dreams}
Have another scene that describes the battle from Vizicar's point of view. 





\subsubsection{Charcoal sends a message}
Charcoal/Curwen has discovered that Carzain seems to have hidden powers that only surface occasionally, during which times his personality seems to change, as if possessed. Curwen suspects that Carzain might be a Scion, so he informs his Cabalist contacts among the Redcor. The plan is that Carzain will be recruited into the Gandierre and used as a tool by the Cabalist faction within the Redcor, and eventually recruited as a full Cabalist. 

%So, the Redcor send someone to find him. This is \hr{Esmerel}{\Esmerel}. 
The Redcor relay the message to \Esmerel. 
They tell her they have received a tip from a confidential source that there's something fishy about \Shireyo. 








\subsection{The Thirsty Nether}
On his snooping through the city, Rian overhears some thieves (in Sentinel employ) talking about their wicked plan. 
Possibly \Psyrex{}, or at least some of his top-level henchmen. 
He sneaks into a suspicious building. 
Here, he is witness to a terrible ritual of dark magic, involving humanoid sacrifice. 
He sees into \Machai, terrible vistas of \daemonic{} landscapes and stuff. 

He is discovered, and the mages send thugs after him. 
He runs for his life. 
He has been given a warning, so he knows that this time they will surely kill him if they can catch him. 
He nearly gets caught and killed, but Moro \Cornel{} arrives to pull him out. 

He talks to her. She warns him that he shouldn't be snooping around in places where he might get killed. He tells that that he must, for the sake of his beloved. 

Rian fears the supernatural evil that is taking place in Malcur. 
He hopes someone will stop it. 





\subsubsection{Needle is approached by a spy}
Needle is approached by a spy of hers. He tells her that he and his fellows have discovered a lair of people who use chaos magic and seem to be up to something nasty. (This spy was at the same place that Rian was. Perhaps he actively sabotaged Rian's infiltration attempt, using him as a distraction, allowing himself to escape unseen. 

Needle begins to prepare a raid. 









\subsection{Dark Crypts of the Mind}
\subsubsection{Carzain dreams}
Now that Vizicar is closer to the surface, Carzain begins to \hr{Ramiel dreams}{share his visions and nightmares}. 

He is haunted by the tortured, hateful faces of shackled ghosts. They show him their world: Cold, cruel, dreadful. They hate him and desire to drag him down into their prison\dash groping for him with their clammy, hideous hands. 

He awakens full of terror, and also a tinge of guilt. He has a feeling that he is somehow responsible for their torment. 

He also has vague dreams of lost greatness\dash \hr{Visualizing a matrix}{unconsciously visualizing} the \hr{Mystraacht \matrix}{\Mystraacht{} \matrix}. Feelings of having been betrayed, having lost his power and his memory, upon which his enemies descended upon his weakened self like vultures, usurping his rightful place and honour and forcing him into flight and hiding. 
%, having his rightful place, power and honour usurped

When he wakes he thinks about the whole thing. 
Part of him is horrified at the madness that is consuming him. 
But another part is excited. 
Because the possession brings \emph{power}. 
And a feeling of being destined for greatness and glory. 
This is what he has always dreamt of. 

But he has doubts. 
Maybe these feelings are fake. 
Maybe the possessing \Archon{} is brainwashing him, all the while making him feel like it is the right thing to do. 
Maybe he is being mentally deceived. 

But it still feels good. 

He thinks of the legend of \hs{Lestor Delain}. 
He dealt with \qliphoth{} despite everyone's advice. 
It was dangerous. 
He became a dark and controversial figure, but also a hero who achieved great things. 





\subsubsection{\Tiroco{} talks to the crazy old woman}
\Tiroco, on a covert trip through the city, passes through the \hs{dead garden}, where is addressed by the \hs{crazy old woman}. The old woman is clingy and mad, desperately clutching \ps{\Tiroco} sleeve and babbling about worms, blood, death and the destruction of the city. 

\Tiroco{} herself is shaken, since she is already weak from the things she's witnessed, so her bodyguard has to shake off the old woman and drag a shocked \Tiroco{} away. But afterwards, \Tiroco{} finds herself seeing worms at every turn.

\lyricsbalsagoth{%
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  Can you not see the coils of the worm all about you?\\
  Can you not hear the writhing of the worm beneath you?\\
  Can you not scent the breath of the worm riding the wind?\\
  Can you not touch the skin of the worm in all that surrounds you?\\
  Can you not taste the ichors of the worm upon your tongue?\\
  Do dreams of the worm not haunt your slumber?
}

She tells stories of death, destruction and the end of the world.

\lyricslimbonicart{Legacy of Evil}{
  The night has a legacy of evil.\\
  Nocturnal dreamscapes.\\
  A wilderness of infinite disharmony\\
  in an isolated aspect eternally.\\
  A maze inside your brain\\
  leading into the insane\\
  abyss of fear, illusions and despair.
  
  Something ghastly is passing by.\\
  The full moon in the sky.\\
  See the coming hurricane of terror,\\
  ancient sadness and horror.\\
  A virulent syndrome of misanthropy,\\
  captured by the obscure mystery. 
}





\subsubsection{\Tiroco{} talks to Moro}
%What about Moro \Cornel? I don't think she has seen enough yet to truly act. But remember to have her in some scenes. 
Remember to have \Tiroco{} talk to Moro \Cornel{} a few times in the course of the book.

Moro has not yet seen enough to truly act. But remember to have her in some scenes. 

Moro hopes to \hr{stop the evil}{stop the mystic evil} that is festering in Malcur. 
She is investigating, trying to find out what is going on so she can stop it. 








\subsection{The Bleeding Wood}
\subsubsection{Sally rejoins the army}
Curwen's party, with Carzain in it, head back towards \Forklin. 

They find that the \Wylde{} has been (temporarily) devastated by the the Rissitics' magic, leaving the path wide open before them. They are horrified by a magic so powerful that even the terrible \Wylde{} recoils before it. 

Or... I don't know. Is the above overpowered? 

Anyway, the Rungerans are moving forward faster than they anticipated, and they must be in \Forklin{} to defend it, for it is a vital strategic point. 





\subsubsection{Carzain and Delph ogle women}
Carzain and Delph go to ogle women. Delph likes his women tall and thin (unlike himself, who is short and round). The taller and thinner, the better. He points out one. 

Carzain: \ta{Urgh. Hell no. She's ugly. She's got smaller breasts than you do, Delph.}

Both: \ta{LOL.}





\subsubsection{Carzain thinks more on his madness}
Part of him is horrified at the madness that is consuming him. 
But another part is excited. 
Because the possession brings \emph{power}. 
And a feeling of being destined for greatness and glory. 
This is what he has always dreamt of. 

But he has doubts. 
Maybe these feelings are fake. 
Maybe the possessing \Archon{} is brainwashing him, all the while making him feel like it is the right thing to do. 
Maybe he is being mentally deceived. 

But it still feels good. 

He thinks of the legend of \hs{Lestor Delain}. 
He dealt with \qliphoth{} despite everyone's advice. 
It was dangerous. 
He became a dark and controversial figure, but also a hero who achieved great things. 

Maybe move this to \quo{The Emperor Inviolate}. 





\subsubsection{Rian sees a raid}
\target{Rian sees a raid}
Rian sneaks back to a place near the one he was last time. 
He spies on some Sentinel-employed thieves and their evil talk. 

Then some Cabal agents arrive to crash the party. 
Needle is there, surrounded by bodyguards. 
And around her, more-or-less hidden in \Nyx, are \banerats{}. 
Rian is frozen in terror and just crouches still, watching the Cabal and Sentinel mages, warriors and creatures duke it out. 
He sees into \Nyx{} and other realms and is scared even more. 


When he finally runs away, he stumbles into \Nyx. 
He panics, but at last sits down and tries madly to convince himself that what he is seeing is not real, that he is hallucinating. 
And it works. 
His vision readjusts to the Shroud and he sees his old World again, and manages to stumble back into it. 

He goes away shaken to the core. 





\subsubsection{Rian meets a living building}
%Perhaps this happens gradually: 
Already early on, during the preparations for the great summoning of \Nithd{}, some people have begun degenerating into mutants, or living buildings. 

Rian discovers a building that has living humanoids magically merged into the foundation. Compare this to Bootstrap Bill or Wyvern, who are becoming part of the \shipname{Flying Dutchman} in the movies \cite{Movie:PiratesoftheCaribbean:II} and \cite{Movie:PiratesoftheCaribbean:III}. 









\subsection{The Fragile Egg}





\subsubsection{\Tiroco{} is urged to hurry}
\Psyrex{} contacts \Tiroco. 
He warns her that her progress is too slow, that she must hurry up. 
He tells her that an evil force is threatening Malcur, and that she must help him. 
(He manages to avoid lying. The \quo{evil force} is actually his own party.) 
He says that the Pelidor clan must fulfill its purpose, which it has forgotten for over a hundred years. 





\subsubsection{\Tiroco{} and Liocai}
%\target{Tiroco learns to trust Liocai}
\Tiroco{} is antagonized by Liocai, but eventually they talk about it, sort out their differences and work together (see section \ref{Tiroco learns to trust Liocai}).





\subsubsection{\Tiroco{} and Liocai have premonitions}
\target{Dreams of Malcur being transformed}
\Tiroco{} and Liocai are both spiritually and mystically bound to Malcur. They begin to feel that something is deeply wrong with their city. 

Each of them has dreams in which she \emph{is} the city and feels its pain as it/she is slowly transformed into a half-living, half-undead abomination. They can feel poison and rot in their bodies, but they are too blinded and weakened to fight with their humongous city-limbs.

\Tiroco{} feels trapped between Scylla and Charybdis: \Nithdornazsh{} and the \ghobaleth. 

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  By the Onyx Sceptre of my forefathers,\\
  the air is churning\\
  with auguries of dethronement,\\
  impending doom thus prophesized.
  
  In a dream I was bade ride \\
  the argent-eyed unicorn to the Ring of Stones.\\
  There a torrent of viscid slime assailed me\\
  as pipes and horns sang the clarion of my dissolution.
  
  And the usurpation of my ancient azure throne. \\
  Assassins stalk the nighted halls of my palace.\\
  Poisoned blades and chalices surround me.\\
  I thirsted for a balm, but my thirst \\
  was slaked by an envenomed draught.
  
  My sword-arm shackled by tendrils of sloth,\\
  enthralled by the chasmed gloom.\\
  Borne upon wings of labyrinthine dread,\\
  I awaken.
}

\lyricsbs{Marduk}{Perish in Flames}{
  Closer, come closer till nothing breathes.\\
  Come closer, and come without warning.\\
  The prophet's throat, ash and coal.\\
  Blind, but with a thousand seeking arms.\\
  Ash and coal.\\
  Can you outrun the mouths of Hell?
}





\subsubsection{\Tiroco{} slowly goes mad}
\target{Tiroco goes mad}
In the first $\fracs 2 3$ of the story, \Tiroco{} becomes more and more isolated, paranoid, distressed and downright mad. 

She sees visions of horrible things happening to her city, being devoured by giant worms or \hr{Dreams of Malcur being transformed}{transformed into an undead abomination}. 

She is frightened, but she doesn't know whom to turn to. 
She dares not go to \Psyrex{} nor \Icor, because she doesn't trust \Psyrex, and she fears that \Icor{} will be forced to report to \Psyrex{} anything he tells her. 
At first, she confides in Needle and her bodyguard, but slowly she loses faith in them, too. 
Needle is evil, of course, and occasionally that shines through. 
And her bodyguard is just not intelligent enough to understand it all. 
Maybe she is even superstitious and starts looking at \Tiroco{} the wrong way, so \Tiroco{} has to shut up to avoid alienating her friend.

As a result, she has become isolated and is starved and desperate for humanoid contact. 

This does not get better until she \hr{Tiroco learns to trust Liocai}{begins to trust Liocai}. 





\subsubsection{She cannot find rest in sleep}
\Tiroco{} cannot even find peace in sleep. 
She lies sleepless or has nightmares. 

\lyricslimbonicart{Towards the Oblivion of Dreams}{
  Like a nomad in the subconscious realms of the beyond.\\
  The night is old, yet I still seek peace. \\
  Restless drifting the dark corridors \\
  in the unknown chambers of the mind.
  
  Where is the door to the light of dreams? 
  
  Total isolation. \\
  Land of desolation. \\
  Dreamless sleeping. \\
  Darkness reaping.
}

She dreams of Malcur, its mystic past and its dark fate. 

\lyricslimbonicart{Towards the Oblivion of Dreams}{
  Sculptures in stone, \\
  dark protectors of sacred ground. \\
  Only the pure may enter \\
  into the twilight zone.
}





\subsubsection{She has Needle whipped}
Once, the mad \Tiroco{} had Needle whipped for some minor infraction. 
It is a symptom of how mad she is. 
It makes Needle hate her. 

Afterwards, \Tiroco{} regrets it. 
She wants to apologize to Needle, but etiquette forbids it. 
\Tiroco{} is pained. 





\subsubsection{\Tiroco{} seeks out Moro}
\Tiroco{} is frightened, so she seeks out Moro \Cornel{} to ask her advice. 

In the beginning, they work together, but also they cheat each other and work behind each others' backs. But gradually, \Tiroco{}, being afraid and alone and needing someone to turn to, tries to confide in Moro. But Moro is too shrewd and sees through \Tiroco. She realizes that \Tiroco{} is hiding something, and starts digging. 

Perhaps Moro fast-talks \Tiroco{} into letting Moro do a divination spell on her, to learn more about her visions/hallucinations. \Tiroco{} is \hr{Tiroco goes mad}{desperate in her isolation}, so in her distress she accepts Moro's offer without thinking.

\Tiroco{} realizes that Moro is onto her, so she claps shut like an oyster and storms out of the divination session. After that she tries to avoid Moro and freeze her out. This, of course, makes Moro even more convinced that something is wrong, and makes her work harder to find out. 

\Tiroco{} curses herself for her stupidity every time she dodges Moro or the like.

%Moro has talked to \Tiroco{} and has come to suspect that something strange is going on. 

%I need to have more scenes with Moro and \Tiroco{} talking. 

Moro has gotten suspicious and is now covertly stalking \Tiroco.





\subsubsection{They wants to stop the evil}
They both hope to \hr{stop the evil}{stop the mystic evil} that is festering in Malcur. 












\section{Spectre of the Fray}













\subsection{\Nithdornazsh{} peeks out}
Have scenes where \Nithdornazsh{} peeks out of the Shroud. 
Various mortals (possibly Rian) see glimpses of living (or undead) buildings made of flesh and metal. 
Walls suddenly transform into bleeding, oozing flesh for a short instant. 
Preferably in hidden places\dash dark alleys, the slums, behind boards.

Rian sees this more than once. 









\subsection{Imetrians join the war}
Telcastora Ilcas and some other Imetrians approach \Tiroco. 
They offer their military aid. 

The Imetrians have many soldiers spread out over the country, to protect their temples and their pilgrims. 
200 men at least, and several of them veterans. 
They are allowed this due to some agreements made with the Pelidorian dukes. 

They offer their aid. 
But in return they want more privileges for their religion in Pelidor. 
Their aim is clear: They want to proselytize. 

\Tiroco{} and her advisors acquiesce, albeit reluctantly. 
\Tiroco{} wants them, but she fears it is against her \quo{crusade}, and therefore it will look suspicious if she just invites them in. 
Fortunately, Liocai and others come to the rescue and vouch for the Imetrians. 
The Vaimons argue. 
Eventually, an agreement is made. 
Only minimal concessions are given. 





\subsubsection{Ilcas and Moro}
Before the Imetrians take off, Ilcas approaches \Tiroco. 
He tells her he wants to talk to an \Ishrah{} mage and asks her if there is one she trusts. 

\Tiroco{} hesitates due to her own falling-out with Moro. 
But she collects himself and reminds herself that Moro is good. 
So she directs Ilcas to Moro. 

Ilcas approaches Moro. 
He tells her about the visions Razor has been having. 
He warns her about the evil in the city. 
He and Razor give all the details they can. 
Moro thanks him. 
But she is suspicious: Why do this? 
Ilcas is not required to by their agreement. 

But Ilcas is a hero. 
Since Razor is sure this alien force is \quo{evil}, Ilcas-tachi feel it is their duty as good Imetrians to inform the people who are allies of their people. 

Moro learns some useful stuff. 





\subsubsection{Imetrians ride away and talk}
When it is settled, the Imetrians ride from Malcur towards \Forklin. 
They ride \relcs. 
You can't ride \nycans{} over long distances (they \hr{Nycan endurance}{lack the endurance}), and \mulgrons{} are too slow. 

Only minimal concessions were given. 

The Imetrians did not drive so hard a bargain. 
They know it will be bad for them if Pelidor falls to Runger. 
Runger has never let many Imetrians in. 
The Imetrians don't like Runger. 
To top it off, the Imetrians have long suspected Runger of having covert dealings with Durcac, albeit without proof. 

Ilcas talks to his mage-priest companion about this. 
They discuss the fact that Runger is possibly in league with Durcac. 

\begin{prose}
  Ilcas: 
  \ta{Should we not have told the duchess about our fears?}
  
  Mage: 
  \ta{No. Our intelligence is our own. 
    Dessali teaches that knowledge is precious.
    We cannot just give it out for free.}
\end{prose}

Ilcas is still not convinced. 
If it were up to him he would have told them. 
But at least he told them about his fears regarding the evil in Malcur. 
He tells the mage about that. 
The mage is not happy that Ilcas blurted it out. 
Ilcas defends himself saying that it was not Imetric intelligence but his discovery. 
Razor's discovery, actually. 
So the knowledge was Razor's property to dispense as he saw fit, and Razor saw fit to tell the Pelidorian mage. 










\subsection{Vizicar}
Vizicar fights to gain control of his own body. 

\lyricsbs{Marduk}{Voices From Avignon}{
  Speak through me. Speak through me.\\
  The sin must be washed away with blood.\\
  Dream through me. \\
  Called to a new life through death.\\
  Called to a new life through death.\\
  But what shall you reach for when all colours fall?\\
  Overwhelmed with maledictions. \\
  Feel the rays of redemption of a brand new Sun.
  
  Choking. Asphyxia. \\
  Inhale the Darkness, lungs filled up. \\
  Asphyxia. Asphyxia. \\
  But who shall you reach for when all colours fall?\\
  Long-drawn moans and piercing cries \\
  blend with prayers and litanies. \\
  Faces bone dry. Condemned as the river everybody drank of. \\
  Inhale! Inhale!
}

\ta{I will win the power and glory I deserve. 
  Not just as Vaimon Emperor, but higher yet. 
  I am a Scion. 
  I am a \Malach. 
  I will achieve the \apotheosis{} and become one with \Iquin{} and \Itzach.
  That is my purpose as a Scion. 
  
  But first I must gain control of my own body. 
  Right now I live out an ignominious existence as a ghost in a boy's head. 
  I am nothing...}

This makes him remember his nightmare of being nothing. 
He drifts away. 

He philosophizes. 

\lyricsbs{Emperor}{Sworn}{
  Four eyes as two in one.\\
  The forward circular view that never ends.\\
  An orbital voyage throughout the endless sphere of all,\\
  where time is lost and everything transcends.
  
  A graceful presence at stolen time
  
  As ghosts to the world.\\
  Ghosts to the world.
  
  For ice, outside, are we apart.\\
  As cold and eerie mist to the hand.\\
  Ever floating on its course\\
  towards the heights of shadowland.\\
  
  Thus appear the truly sworn.
  
  To be seen.\\
  To be feared.\\
  Yet, not to be reached.
}





\subsubsection{Lost in the labyrinth}
He is trapped in the labyrinths of \itzach{}, lost and searching for those precious and ephemeral windows through which he can peer out through Carzain's eyes and affect the world through Carzain's body. 

\lyricsbs{Emperor}{Ensorcelled By Khaos}{
  In an endless maze begotten,\\
  to dead ends led by fools.\\
  I sought a plague for those\\
  who smiled at walls in humble fear.\\
  
  Yet, belligerent ways came to an end.\\
  No war could ease my hunger.\\
  By craving death I was to darkness reborn.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine.
  
  No peace for me. No peace I seek.\\
  My quest goes far beyond.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine.
  
  I hail the greatest fall.\\
  Dark is the spirit of my token.\\
  Dark is my call.
  
  Still craving, still torn.\\
  Hear me, master of this realm\\
  to which I was reborn.
  
  \ta{Bearer of my stigma. Thou art of me.\\
  Yet, claim no gift, but guidance.\\
  For I am the giver of temptation.\\
  Thou art the executor of Thy rewards.}
  
  Dark is the spirit of my token.\\
  Dark is my call.
  
  The cosmic forces driving me,\\
  more noble, more free.
  
  Take me.

  Love and hate and all in between,\\
  I greet them all in ecstasy.\\
  Venus, seduce me.\\
  Mars, possess me.\\
  Tear my soul from sanity.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine and I am thine.
}









\subsection{Carzain in \Forklin}
\target{Carzain returns to \Forklin}
\target{Carzain sees the \Morbus{} in Forklin}
Carzain reaches \Forklin. 

When Carzain rides into \Forklin, have him comment on how the \Ortaican-built city looks very different from Vaimon-built ones. 
\hr{Vaimon Middle-East}{Vaimon things look Middle-Eastern}. 

He strides into the city and demands to be taken to Archibald Curwen, his old acquaintance. 
He \hr{Carzain rejoins the army}{rejoins the \ishrah}. 

In the scene where Curwen meets Carzain, have a scene from Curwen's point-of-view where he envies Carzain his thick, blair hair. 
Curwen has mixed feelings about \hr{Curwen's appearance}{his own gray hair}. 

It has been ten years since they last saw each other. 
Carzain is \hr{Carzain's power}{more powerful than Curwen now}, and Curwen knows it. 

Carzain brings valuable reconnaisance. 
The Pelidorians have scouted, of course, but they have not sent out any skilled mages (they have few of them to spare), so Carzain brings them things they don't know. 

When Curwen hears Carzain's story, he is very interested. 
It fits what he has been reading in Tantor's diary. 

Armed with Carzain's information, Curwen convinces Sethgal that it is best to stay holed up in \Forklin{} and meet the Rungerans there. 
See, Carzain's findings further confirms Curwen's suspicion that the Rungerans want \Forklin{} for mystic reasons. 

Carzain later walks around in the city. He sees the \hs{\Morbus} at work, and how it transforms people into half-dead and later undead abominations. 

He talks to people and hears \hr{Haskelek myth}{myths about the Ghost Tower and the \Haskelek}. 
(Or perhaps he already heard that myth when \hr{Carzain passes near the Ghost Tower}{he passed near the Tower earlier}.)

Remember that the \ishrah{} mages wear plate armour. 





\subsubsection{Vixal Pelidor}
Vixal Pelidor is the countess of \Forklin. 
She is the highest-ranking member of the \Forkliner{} Pelidors. 
Like the duke, the count or countess is elected. 
She rules for life. 





\subsubsection{Delph and \Tsekkect{} talk}
Delph and \Tsekkect{} talk. 

\begin{prose}
  Delph: \ta{Have you noticed that Carzain is acting weirder and weirder?}
  
  \Tsekkect: 
  \ta{Yeah. He's probably going mad. Mages tend to do that, you know.}
  
  Delph: \ta{Yeah, I guess. Pity, though. He was a cool guy.}
\end{prose}





\subsubsection{Ilcas and Sethgal}
Telcastora Ilcas and his companions arrive. 
Sethgal is happy to greet them. 

\begin{prose}
  Sethgal: 
  \ta{I knew we could rely on you.}
  
  \tho{That's actually not true. 
    I thought we couldn't. 
    I \hr{Sethgal curses Imetrians}{cursed the Imetrians earlier} for being faithless allies.
    But they proved me wrong.} 
\end{prose}





\subsubsection{Carzain meets Telcastora Ilcas again}
Carzain meets Telcastora Ilcas again. 

The Imetrians send a few elite soldiers and mages to support them and attempt to find out more. Telcastora Ilcas leads them. 
Curiet Serpentin is also there. Originally, Curiet was just a civilian Imetrian working in Forklin. 
Later he gets drafted to be some Imetric mage's assistant, or perhaps his interpreter. 

Carzain notices that Ilcas is being addressed as \quo{\Retaxis{} Northstar}. 

\begin{prose}
  Carzain: 
  \ta{\quo{\Retaxis}? 
    Is that title new? I seem to remember you had another one last time.}
  
  Ilcas: 
  \ta{%
    Yes. 
    I have been promoted since last we met.} 
  He smiles. 
  \ta{%
    Salacar be praised, I now hold the same rank as my wife. 
    It is just an honourary rank, mind you. 
    I do not command troops as a \Retaxis{} normally would. 
    I requested this reward because I was sick being outranked by my wife.}
\end{prose}

A bit later Carzain introduces Ilcas to Delph and \Tsekkect. 
They are wary of him and think to themselves that there is something strange about them. 
Ilcas immediately picks up on this: 
\begin{prose}
  \ta{%
    Yes, there \emph{is} something strange about me.
    I am a \nycaneer. 
    And yes, I \emph{can} read your thoughts.}
\end{prose}

Ilcas also meets Curwen. 
Ilcas frowns when he sees \hs{Curwen's pistol}. 
It is \hr{Rissitic economy}{Rissitic-made}, and Ilcas does not like Rissitics. 
His \hr{Ilcas becomes \Retaxis}{last major mission}, which gained him the rank of \Retaxis, had to do with opposing the Rissitics. 





\subsubsection{Razor is more wary of Carzain}
Since their last meeting, Carzain has grown darker. 
Vizicar has awakened again and is now closer to the surface. 
Therefore, more of his dark, wicked \sathariah{} nature shines through. 

Razor notices this immediately, and he is now more wary of Carzain than before. 
Does Razor hide this, or does he openly display his unease? 
He probably hides it. 
Razor is a sneaky bastard. 





\subsubsection{\Meccaran{} conscripts}
The Pelidorian army have drafted some local tribes of \meccara{} that live in eastern Pelidor. 
They are mostly independent, but nominally they owe allegiance to the duke. 
They are employed as guerillas, since they know the terrain. 

The various tribes each speak their own languages, and only few understand \Velcadian{} or \Tepharin. 
They are ill-integrated and have little love for the duke or duchess or whatever. 
They have their own languages and cultures and customs and do not feel like a part of Pelidor. 





\subsubsection{Carzain dreams}
Carzain has vague dreams of lost greatness\dash {unconsciously visualizing} the {\Mystraacht{} \matrix}. 
Feelings of having been betrayed, having lost his power and his memory, upon which his enemies descended upon his weakened self like vultures, usurping his rightful place and honour and forcing him into flight and hiding. 





\subsubsection{Curwen looks at the Ghost Tower}
When they return to \Forklin, Curwen sees the Ghost Tower. 
He thinks about it.

Later \hr{Charcoal guesses Ghost Tower plan}{he will realize its importance}. 











\subsection{Moro's research}






\subsubsection{Astrology}
After having failed to extract much information from \Tiroco, Moro tries to do the best she can with the descriptions \Tiroco{} provided her before storming out. 
So she tries to \hr{Astrology}{read the stars} for \Tiroco, to see if that gains her any insight. 

\hs{Moro has doubts about her astrology}. 
It is hard to read anything about a single person. 
It is somewhat easier to read about an entire city. 
She knows there is something wrong with Malcur as a whole. 
She has some descriptions and clues. 
She tries to use these and read the stars about them. 

It doesn't entirely work. 
So she contacts \Nasshikerr{} instead. 





\subsubsection{\Nasshikerr}
\target{Moro and \Nasshikerr}
Moro \Cornel{} wanted to find out more. 
She could not puzzle out what was going on. 
So she called on her patron god, \hs{\Nasshikerr}, whom \hr{Moro serves \Nasshikerr}{she served}.
He appeared in his guise of an chameleon.  
She asked him for advice and knowledge. 

\Nasshikerr{} was a vain god who saw no reason to help Moro any more than necessary, so she had to plead and beg and bargain. 
Eventually \Nasshikerr{} agreed. 
He could not tell her what was happening right now, but she should call him again later, and he would have something to tell her. 
And he warned her that she had better have a humanoid sacrifice ready next time; her credit was all but spent. 

\Nasshikerr{} does not admit that he doesn't know. 
He gives evasive answers and promises to return. 
But Moro sees through him. 
\tho{Stupid, arrogant god. 
  Just admit that you don't know.}

Afterwards, \Nasshikerr{} sits and wonders. 
Should he inform \Secherdamon? 
Nah. 
He is no close ally of \ps{\Secherdamon}. 
He will play his own game. 

\Nasshikerr{} is surprised at how much Moro knows, though. 
Given how traumatized she is, she should not be able to see this much. 
The Shroud must be \hs{unravelling}. 

\Nasshikerr{} resolves to read the stars some more. 
He is an expert astrologer. 

Remember to read the section about \hs{\Nasshikerr} before writing the chapter!

And remember that \Nasshikerr{} needs to be in the glossary. 
List his race as \quo{\Taortha}. 











\subsection{\ps{\Tiroco} visons get worse}
After the interrupted divination ritual with Moro \Cornel, \Tiroco{} suffers from an \quo{unfinished gestalt}, and her mind is left in a vulnerable state, unnaturally divorced from the Shroud. 

Her visions start to get really horrible and bloody at this point. She gains the ability to see into the future. (Of course, seeing the true future is impossible no matter what, and her \quo{ability} is exceptionally unreliable.)

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  The land awash with spilled blood \\
  and viscera torn forth from the sundered dead.\\
  Gorge the Earth with flesh darkened by the claw and fang of war,\\
  rent open to the ravenous maws of worms.
}

\Tiroco{} is traumatized.

She starts to realize that her visions are related to \Icor{} and \Psyrex.

Later it will turn out that it is the nocturnal visitations by \Icor, enabled by \Psyrex, that has slowly opened her mind to the Beyond. 
Made her see through the Shroud a little bit. 
Her encounter with \Uswa{} left her with a lot of images in her mind. 
Dwelling on those memories, her subconscious mind was able to see, in the Beyond, the \emph{true} images that inspired \ps{\Uswa} speech. 
Those images now appear in her dreams. 







\subsection{Rian seeks out \Tiroco}
Rian tries to tell the city guards about the incidents, but they throw him out. He goes to the church, and they call him a heretical madman. 

Eventually he resolves to go directly to the duchess. 

So he sneaks into \ps{\Tiroco} castle, corners her and talks to her about it. 
She realizes that this must not get out, and so, while it pains her to betray a subject, she does what she must: She calls the guards and tells them to throw Rian in prison and not listen to a word the madman says. 

At some point, Needle shows up. Rian freaks out, saying that it's her, that she is one of the evil sorcerers causing the whole thing. Everyone laughs, and the soldiers slap him silly. 

Needle begins to suspect that \Tiroco{} knows more than she lets on, so she begins spying on her mistress. 





\subsubsection{Rian haunted}
Rian, shocked by what he has witnessed, begins to see more and more through the Shroud. 
He is haunted by monsters from the Beyond. 

Moro picks up on this. 
It is one of the reasons she decides to take him under her wing. 
He is more sensitive than she and can see some things that she cannot. 

\citeauthorbook{RobertEHoward:WhichWillScarcelyBeUnderstood%
}{%
  Robert E. Howard%
}{%
  Which Will Scarcely Be Understood%
}{
  Oh, little singers, what know you of those \\
  ungodly, slimy shapes that glide and crawl\\
  out of reckoned gulfs when midnights fall\\
  to haunt a poet's slumbering, and close\\
  against his eyes thrust up their hissing head,\\
  and mock him with their eyes so serpent-red?
  
  Conceived and bred in blackened pits of Hell,\\
  the poems come that set the stars on fire;\\
  Born of black maggots writhing in a skull \\
  men call a poet's skull\dash an iron bell \\
  filled up wh burning mist and golden mire.
}









\subsection{Moro or \Tiroco{} dreams of ruins of \Nithd}
Moro \Cornel{} meditates, performs spells and takes drugs. She dreams herself back to the ruins of \Nithd{}. Have a nice description of the death, the decrepitude, the ancient-ness and the monstrous immensity of it all. 

Or perhaps it's not Moro, but \Tiroco{} or Liocai. 

%Maybe they work together, but also cheat each other. Moro has talked to \Tiroco{} and has come to suspect that something strange is going on. 

%I need to have more scenes with Moro and \Tiroco{} talking. 

Moro suspects that the duchess has ulterior motives for keeping Rian imprisoned and wanting to kill him. She decides that she can no longer trust \Tiroco, so she springs Rian from the dungeon and enlists his aid in her research. 

Remember that Rian needs to put his carpentry skills to use! 

\lyricsbs{Marduk}{Everything Bleeds}{
  Jeanne d'Arc, Jeanne d'Arc,\\
  your mothers are many, everything bleeds.\\
  Nor have they heard the Netherworld move its lips.\\
  You haven't heard a word, you haven't heard a word.\\
  It's the emptiness, everything is from within.\\
  Afraid to die you are.\\
  Don't receive the sword, don't receive the sword.\\
  Everything bleeds, the branches bleed\\
  between your cold mouths.\\
  They will throw your ashes over the Seine.\\
  Ashes over the Seine.\\
  Like a funeral veil.\\
  Ashes over the Seine.
  
  It's the emptiness, everything is from within.\\
  Afraid to die you are.\\
  Don't believe, don't believe.\\
  The saints are dead people, no pointed crowns.\\
  They will throw your ashes over the Seine.\\
  Like a funeral veil.\\
  Like a funeral veil.
  
  Everything bleeds, everything bleeds.\\
  Untie your dress, everything bleeds.\\
  And open up your protected room\\
  with two fingers. Everything bleeds.
}





\subsubsection{The horror of \Nithdornazsh}
She sees the \hs{Blood-Red Vaults of \Nithdornazsh} and is horrified. She is almost mentally pulled in, but she manages to steer away. 

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  This red charnel pit of primal horror, \\
  howling black ecstasies to the void.\\
  Ancient and divine, older than the hidden Icosahedron, \\
  now rebirthed beyond the chaosphere.\\
  Rise... rise and destroy!\\
  Hatred, carnage, slaughter, havoc, chaos, murder!\\
  I am become the devourer of all life!
}









\subsection{Rungerans besiege \Forklin}
The Rungeran army besieges \Forklin. 
Carzain marvels at the \hr{Glorious armies}{size and splendour of the army}. 

The Rungerans have \mezolisks. 
These are actually imported from Durcac. 
But they are not badly conspicuous. 
Runger has been known to use \mezolisks{} before. 
The Rissitics have just helped them beef up the number of them. 

Vizicar stirs half-awake within him and mumbles: 
\vizicar{%
  Bah. This is nothing. 
  I have seen armies twenty times the size of this. 
  Thirty times! 
  I have commanded such armies. 
  I have vanquished such armies...}

\lyricsbalsagoth{The Obsidian Crown Unbound}{
  And so the mighty and resplendent armies of the Imperium assembled before the towering cyclopean walls of ancient Gul-Kothoth.\\
  It was some time before the billowing dust cloud raised by the massed arrival of the vast imperial host settled, ultimately dissipating as the shadows of dusk descended.\\
  With nightfall, the imperial army's countless torches, braziers and cookfires illuminated the dark plain before the fortress like a coruscating sea, painting the stygian heavens the colour of flame.
}





\subsubsection{Charcoal-tachi realize their goal}
\target{Charcoal guesses Ghost Tower plan}
Charcoal and other Cabalists \quo{realize} that the Sentinels are after the Ghost Tower. 
After all, \hr{From Ghost Tower to Nyx}{the Tower is a portal to \Nyx}, and it stands to reason that the Sentinels would like to gain control of such a back door into \Nyx. 

\begin{prose}
  Charcoal:
  \tho{%
    Mages wielding great power.
    What are they after?
    What are all men with power after?
    More power. 
    Magical power.
    The Ghost Tower!}
\end{prose}

This prompts Curwen to convince the Pelidorians that they must hold \Forklin{} at all costs. 









\subsection{Moro springs Rian from prison}
Rian is thrown in the dungeon and sentenced to death. 

Before he is to be hung, however, Moro \Cornel{} sneaks in and frees him. 

He tells her that Needle is one of the bad guys. 
She is intrigued by what he has discovered and agrees to let him work with her. 

Remember that Rian needs to put his carpentry skills to use! 





\subsubsection{Rian has become scarred}
Remember that Rian has become scarred and terrified by what he has seen. 
He is harder and more bitter. 







\subsection{Carzain fights to defend \Forklin}
Carzain fights the Rungeran forces at \Forklin. 

Remember to describe both armies as \hr{Glorious armies}{magnificent and glorious}.

Vizicar awakens in him, but it feels different this time. Carzain's mind has absorbed some of Vizicar, and he retains control of himself. 

Sort of. Because his dark, \draconic{} blood awakens, and the death-ravening black fury fills him. He fights with reckless abandon and a savage laugh on his lips, with the ferocity of a \dragon{}. 

When I am to write a major battle-scene, I should remember to re-read \bandsong{Bal-Sagoth}{To Dethrone the Witch-Queen of Mytos K'Unn (The Legend of the Battle of Blackhelm Vale)}. 

After a battle, he again falls unconscious. This time, however, he is safe when it happens. 

He dreams. For the first time, he is conscious during the vision and able to talk to Vizicar, who tells him about himself. 

\lyricsbalsagoth{The Obsidian Crown Unbound}{
  At length, the dawn approached tentatively, and with the first signs of the newborn sun etching its promise upon the skies, the martial preparations commenced in earnest.\\
  A brief perfunctory exchange between the Imperial Herald and the fortification's Watch Commander held no surprises, and the Emperor's banner was duly driven into the seared earth before Gul-Kothoth with a chilling finality.\\
  Vast siege engines and powerful ballistae were hauled inexorably into position, alongside a battery of katapelte and petrobolos.\\
  The one hundred thousand strong Imperial Frontier Army, having planted their regimented blazons into the arid soil, waited with a disciplined patience born of never having met defeat in pitched battle or siege, the dreaded Imperial War-Leopards straining noisily against their iron-link leashes to the rear of the cohorts of conscripts and auxiliaries.\\
  The pitiless Iron Phalanx and their Lord Militant Commander had assumed position at the head of the army's Alpha Wing, polished swords, spears and poll-axes reflecting the glow from the myriad torches and braziers which still burned about the Imperial Host.\\
  And behind them were drawn of the legendary Legion of the Ebon Tiger, Pride of the Emperor, the infantry and cavalry famed throughout the Great Northern Continent, personal regiment of the feared general Baalthus Vane.\\
  True to their martial reputation, the six thousand strong Legion were inscrutable in their jet black armour, their sable banner billowing in the chill breeze which skittered over the plain.\\
  And finally, astride his azure-shaffroned warhorse and surrounded by his elite guard, the silvern-armoured Emperor Koord himself studied the precipitous gates with a disdainful scruntiny.\\
  At the Emperor's right hand was the renowned Swordmaster of Kyrman'ku, an eastern bladesman of preternatural skill and the most revered and expensive mercenary in the Imperium.\\
  At his left, the infamous Ogre-Mage of the Black Lake brooded silently, swathed in a stygian cloak and fuliginous cowl and exuding an aura of implacable malevolence, which unnerved even the bravest of the Imperial troops.\\
  The Emperor had deemed the services of these two nefarious renegades pivotal to the execution of the Final Campaign, for they alone had knowledge of the mysterious arcane rite known as The Words Which Unfetter.\\
  And, behind their titanic time-worn palisades, the defenders of Gul-Kothoth beheld this awesome force ranged against them and shuddered, not with fear, but with an awful and night-cold anticipation.
}

The \ishrah{} mages are equipped with plate armour. 
They are valuable and must not die. 





\subsubsection{Prayers}
Both sides have priests leading them in \hs{prayers against disease}. 





\subsubsection{Size of the army}
Also, remember to tell us how big the Pelidorian army is. And the Rungeran army. How many men?





\subsubsection{Imetrians fight}
A small army of about 200 Imetrians fight at \Forklin. 
Describe how skilled, disciplined and fearless they are, with their Imetric gods giving them courage and strength. 

They are supernaturally strong and effective.
As one of their priests says: 

\begin{prose}
  Priest: 
  \ta{We fight an important battle, brethren.
    There are few of us, but the power of our gods will run through us all the stronger for it.}
\end{prose}

And it is true. 
You can see their heathen gods are with them. 

We don't see this from the Imetrians' POV. 
After all, the Imetrians are just a minor player in the story so far. 
They should not get a big, dramatic role until I have had the time to develop them into something cooler, more badass, more background-rich, more well-rounded. 

We see it from Sethgal's POV. 
He is one of the only people present who speaks some Imetric. 
He overhears someone (Ilcas or an Imetric priest) giving the soldiers a peptalk. 

\begin{prose}
  Imetric priest: 
  \ta{If we die on this day, we shall live again!}
  
  Sethgal: 
  \tho{I know the Imetrians believe that they reincarnate when they die.
    I wonder if that is true.
    It is certainly not true for us Iquinians. 
    We die and go into the Light.
    But for them... who can say?}
\end{prose}

The Imetrians scare Sethgal. 
They fight with great zeal, \hr{Imetrian coldness}{but their fervour is... cold}. 
Calculating. 
Reptillian. 

(Maybe make a footnote about how the warm-blooded \scathae{} do not see themselves as \quo{reptiles}. At the very least, mention this in the glossary.)

Compare them to Haldir's Elves at Helm's Deep in the movie \cite{Movie:LordoftheRings:II} (not present in the book \cite{JRRTolkien:LordoftheRings:II}). 

Remember to read about \hs{Telcastora Ilcas} and the \nycans{} before writing this. 





\subsubsection{Sethgal and Ilcas}
After the battle, have a scene where Sethgal and Ilcas talk about leadership and strategy and experience. 

Ilcas is a good, inspiring leader because of his faith. 
He believes in his cause with great fervour, and this inspires people to follow him.
But he is no great strategist or leader. 
So he can make people follow him, but would not know where to lead them. 

Sethgal is the other way around. 
He is highly skilled as a general, but he does not have quite the same charisma, the same passion. 
His men admire and respect him, but they do not \emph{love} him. 
This is one of his weaknesses. 

Perhaps, Sethgal reflects, this is one of the reasons why he was not elected \rayuth{}. 

Also, remember to display \hs{Ilcas' racism}. 
He accidentally mentions that he and his men are of superior breeding than the Pelidorians. 
Then, when Sethgal is offended, he tries to back down and mitigate what he said. 





\subsubsection{Siege cannons}
The Rungerans use cannons in the siege. 





\subsubsection{Vizicar awakens again}
Somewhere along the way, Carzain-tachi get into a fight. Vizicar awakens. This time, after the battle Carzain falls unconscious. He dreams and meets Vizicar. 

He sees before his eyes a man who looks to be perhaps his father's age. 
But still strangely similar to himself. 
His complexion is much lighter, though. 
His long hair is blonde rather than black, and he wears a matching moustache. 

Carzain: \ta{Who are you?}

Vizicar: 
\vizicar{%
  Who am I? How can you not know who I am? I am \VizicarDurasRespina! The Emperor!}

Carzain: 
\tho{%
  \quo{Emperor}... is he the reason why that word has been popping up in my head?} 
(Maybe he doesn't think this until after he awakens from the dream-conversation.)

Carzain: \ta{Why are you in my head?}

Vizicar: \vizicar{Why are you in \emph{my} head?}

Carzain: \ta{I was here first.}

Vizicar: 
\vizicar{%
  Unless... oh, \qliphoth... unless I... oh, by \iquin{} and \nieur. I must be dead.

  Yes, I remember now. Those vile worms killed me. \quo{Disease}, they called it. Hah!}

Carzain: 
\tho{%
  Fuck. Not only is there a madman in my head, but now the madman is talking to himself!}

Carzain wonders what the deal is. 
How does this fit with the theory that it was the Midnight \Qliphoth{} that took control of him? 

Later, Vizicar apologizes Carzain for putting him through Hell by his own recklessness, by ignoring the \hr{Itzach pain}{pain of \itzach}. 
Vizicar admits that he has been crazy and has fucked their body up. 





\subsubsection{\Esmerel{} learns Carzain's identity}
When does \Esmerel{} discover that Carzain is the Scion? 
Probably somewhere near here. 

She tells Carzain: 
\ta{Dude, you're a Scion!}

By this time Vizicar is pretty awake, so Carzain already knows this. 
But he fakes ignorance and goes: 
\ta{Really? Golly, how interesting. 
  Take me with you and teach me more, o wise Redcor.}

But in reality Carzain and Vizicar know much more than they let on. 
They plan to use the Redcor; learn all they can from them but not get bound to them. 

Make it clear (perhaps from \ps{\Esmerel} POV) that \hs{\Esmerel{} is a nerd}. 









\subsection{Carzain reads about Scions}
Carzain is always researching what he is, always looking for more knowledge of Scions. 
He hopes it will lead him to \apotheosis. 

So he goes into a library in \Forklin{} and looks around. 
There isn't a big public library, but there are churches, and they have books. 
He goes into a church, introduces himself as an \ishrah{} mage and pulls a \trope{BavarianFireDrill}{Bavarian Fire Drill}.
He knows he has to use the same body language, frame control and social engineering skills that he masters when picking up women.
It works.
He gets his hands on the writings.

He also finds references to \hr{Vizicar's notes}{Vizicar's notes about \Malachim}, but can find no fragments of the notes themselves. 

He also finds references to \hr{Iolivine's notes}{\ps{\Iolivine} notes}. 
He has heard before that these notes are of exceptionally high quality, but he had been unable to find any copies of them. 
\hr{Redcor bogarted Iolivine's notes}{The Redcor are bogarting the notes}. 
This is one of the reasons he wants to go to \Redce. 

Among other things, he finds references to \Belzir. 
He already knows she was a Scion, allegedly an incarnation of an \quo{evil} \malach, and that she caused the \HundredScourges{} with her wicked \malach{} powers. 









\subsection{Morgan Runger sees what he has done}
We follow Morgan Runger. He has made an alliance with the Rissitics. Originally, he was thrilled at the prospect of rising to power as an ally of Durcac, but of late he has come to doubt, for two reasons. One, he fears that \Nechsain{} will subjugate him as a vassal rather than a true ally. Two, and perhaps more importantly, he beginst to ponder the ethical consequences of his actions. 

He oversees \Takestsha{} and her fellow sorcerers as they invoke the terrible spells gleaned from the tablets recovered from \Rungertemple, and he witnesses firsthand the horrible destruction they cause. 

He imagines that the \sephiroth{} are weeping, mourning his fall from grace.

\lyricslimbonicart{Beneath the Burial Surface}{
  The sky is darkening, soon the night befall.\\
  Righteously angels are weeping for my soul.\\
  All childhood dreams are soon to be lost,\\
  all innocence to be shattered.
  
  I am the fallen from grace.
  
  My face is a river.\\
  See my eyes as they drown in black.\\
  My sacred doom and nemesis\\
  beneath the burial surface\\
  To the final act of the immortal sin\\
  I am lead by funeral winds.
}

He sees the terrible wickedness of the \EreshKali{} magic.

\lyricslimbonicart{Darkzone Martyrium}{
  Black energies in the twilight space\\
  come shivering through the shallow haze.\\
  Into darkness so impure divine.\\
  A bloodshed emotion to evil wine.
}





\subsubsection{The evil magic}
\target{Rungeran temple magic}
The \Rungertemple{} magic might be defiler magic (as in \emph{Dungeons and Dragons: Dark Sun}), sucking life out of the world and leaving it gray, dusty and dead. Alternately, it might be bestial, destructive and chaotic magic, apalling in its sheer hate, ferocity and inhumanity. 

The magic involves the conjuration and binding of terrible \daemons{} from \Chaos. These should be as horrible, inhuman and Cthulhu-like as possible. The \daemons{} are the source of their power; they're the ones wreaking the destruction. 

It is hinted that the \daemons{} are not really bound; they are just playing along for their own unfathomable reasons, and may decide to turn on the mages any time. Have at least one scene where the sorcery suddenly backlashes on one of the mages and he dies a horrible death, his flesh boiled and burnt and his soul consumed by the \daemon{} he unleashed. 

Make it clear that the foolish \humans{} are playing with powers far beyond their understanding. 

It is very hard, taxing and traumatic work for the mages. The sorcerers, being ill-informed and ill-educated in the use of this great power, are twisted by it. Their bodies become warped and misshapen, and they go more and more mad. Compare to Hannan Mosag and his K'risnan in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}.

\lyricsbs{Monolith Deathcult}{
    1917 - Spring Offensive (Dulce Et Decorum Est)
}{
  Creeping like a snake from a can, \\
  the slithering stench of yellow death.\\
  Chemical flame of decay\\
  burning skin and intestine.\\
  Regurgitating the bloody guts.\\
  Spewing last life from a wretched soul.
}






\subsubsection{Morgan angsts}
Morgan grieves and is plagued with guilt and doubt? Should he continue along this path? But what else can he do? 

\target{Morgan has sex with Takestsha}
He has sex with \Takestsha{} (he has few compuctions against cheating on his wife, who is at home in Runger). \Takestsha{} comforts him and assures him that he is doing the right thing. 

Morgan has converted to the Rissitic faith, but he keeps it secret from people for the time being. He still catches himself praying to the \Sephiroth{} out of habit. 





\subsubsection{Morgan's history}
Morgan has a history. His father, Uther Runger, had something to do with High King \LastHighKing{} and the fall of \hs{\GreatBelkade}. 

Later (after \emph{\RungerWarBook}), Morgan will turn against the Rissitics and attempt to right what he has wronged. 










\subsection{Rian sees vision of soul prison}
Rian asks Moro \Cornel{} for magical help in finding Neina. Moro fears that Neina is dead and cannot bring herself to show the boy his girlfriend's horrible fate, so she refuses at first. But Rian pleads and begs, and at last Moro relents. 

So she uses her necromantic magic to search for Neina. She warns him first that this spell is not highly reliable and might not show anything useful. 

How does the spell work? What kind of divination? Astrology? Aquamancy? Pyromancy? 

After looking for her in the Shroud and the \Wylde{} (which can be frightening enough) to no avail, Moro expands her search to the soul prison of the \Sephiroth{}. Rian is horrified by what he sees; souls chained, tortured and crying out in pain. 

Rian somehow recognizes the feeling of the \Sephiroth. See, he is a very religious young man. A kind priest and a lot of religious discipline were highly instrumental in bringing him out of his life of crime and converting him into a respectable citizen. Bottom line, Rian prays a lot and knows the Light and the \Sephiroth{} well. So he recognizes their feeling in the soul prison. He is horrified. He tries rationalizing it away, but a lingering dread remains and will return to haunt him throughout the story. (Maybe at the end he dies and goes to the wicked \Sephiroth?) 

However, all is not bleak. He and Moro were unable to find Neina in the soul prison, and that is good news. But where is she then? Rian assumes that means she is alive, and is relieved. Moro is less optimistic, and though she tries to hide it from him, he picks up on her unease and is in turn made uneasy. 

He walks away with twin feelings of fear: \tho{What was that Hell I witnessed? And what was that feeling? No, it cannot be... No, I will not think on it!}

\tho{Neina. Be alive. Don't be dead. Please be alive. Please, \Sephiroth, let her be alive.}

\tho{The \Sephiroth... oh, Light...}





\subsubsection{Moro's motivation}
Moro knows that something is seriously wrong in Malcur, and she believes that the Rian/Neina case may be a lead. 
She intends to follow this lead and hopefully find some information on what is going on. 

She helps him search the Realms for Neina, but she is afraid she might lose herself in the process. 

\lyricslimbonicart{A Void of Lifeless Dreams}{
  I close my eyes and transcend.\\
  beyond the light to a dark world without end.\\
  The spirit escapes the temple of flesh,\\
  as seductive winds of madness\\
  absorbing me into the cryogenic system.
  
  A void of lifeless dreams.
  
  Enter a galactic domain,\\
  frozen in time and space.\\
  A new infinity of serenity.\\
  Interstellar voyage.\\
  The spirit escapes the temple of flesh\\
  into the sphere of mystified gloom.\\
  A cosmic funeral of memories. 
  
  Sarcophagus panorama.
  
  A mania to explore the enigma.\\
  Isolated celestial corpse.\\
  Astral embryonic life form.\\
  Invocation of the dormant realms.
}





\subsubsection{Moro tells Rian her true name}
At first, Moro keeps her identity secret from Rian and gives a false name. 
But Rian is trusting and tells her everything. 
This makes her feel guilty for deceiving him. 
It rips up old scars of trust and betrayal. 

Eventually she decides to come clean and tell Rian her true name and identity. 









\subsection{Carzain dreams of \ophidian{} eyes}
Carzain dreams of \ophidian{} eyes. When he wakes he wonders who the \ophidians{} are and how he knows of them. How does he know the name? How did it come to him?

Maybe move this to the next book. 

\lyricsbs{Bal-Sagoth}{
  A Black Moon Broods Over Lemuria
}{
  As a black Moon broods over Lemuria,\\
  ebon witchfire enshrouds the gleaming citadels.\\
  sinistrous shadows rise from the vaults of the dreaming elder gods.\\
  \Ophidian{} eyes glimmer through the icy whispering Moon-mist...
}

\lyricsbs{Bal-Sagoth}{
  Enthroned in the Temple of the Serpent Kings
}{
  Storm-borne bride of winter's fire,\\
  serpent-witch of the whispering fens.\\
  Veils of scarlet and sable,\\
  blood spilled in the vault of night,\\
  Frost-garlanded, the mind-binding \\
  glimmer of tear-filled ophidian eyes.\\
  The gleam of winter Moonlight upon black waters.\\
  Nighted spells of the enchantress.
}

\lyricsbs{Bal-Sagoth}{
  Shadows 'Neath the Black Pyramid
}{
  I hearken to the grisly murmur of nameless fiends,\\
  black jaws drooling blasphemy.\\
  Beyond the witch-song, darkly sweet,\\
  The wyrm-horn sounds cross Dagon's mere.\\
  Shadow-gate (portal to the Black Pyramid) yawns wide, beckoning...\\
  Spells scrawled in blood and frosty rime.\\
  Squamous god encoils the onyx shrine.\\
  (By the bleeding stone) I am enraptured by \ophidian{} eyes.
}









\subsection{Various people pick up on the \Sephiroth}
Gradually throughout the story, more than one person gradually comes to suspect the \Sephiroth{} and unravel the truth about them. Rian is obviously one. \Tiroco{} or Liocai may be another. 

At the end, strong hints will have been thrown that the \Sephiroth{} are not what they are made out to be. We still don't know much, tho, other than the fact that they are connected with the soul prison. 

Remember to have loads of prayers and religious references, where the \Sephiroth{} are described as good, indeed, as the source of all good. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  DeathspellOmega
}{
  The Shrine of Mad Laughter
}{
  The idea of God is pale next to that of perdition, \\
  but of this I could have no inkling in advance.
}







\subsection{\Tiroco{} and Liocai team up}
\target{Tiroco learns to trust Liocai}
During much of the book, \Tiroco{} is antagonized by Liocai. But eventually they are brought together. 

Why? Something must happen to them. They go through something traumatic together. Perhaps even something coming out of the Beyond to chase them. And they are forced to help each other in order to survive.

The two \sphyles{} talk about it, and \Tiroco{} spills the beans, telling her about \Psyrex{} and his warnings. Liocai understands (or believes she understands) the part about House Pelidor fulfilling its ancient purpose, so she confides in \Tiroco, telling her about the secrets of Malcur. 

It turns out she knows quite a lot. Some secrets that even Sentinels do not know. She helps speed things up. Which is necessary, because Needle is sneaky, and she is on to them.





\subsubsection{Liocai gets killed}
Liocai gets killed by Needle and her Cabalists. 

\Tiroco{} is aggrieved and frightened, but she has managed to learn something from Liocai. 
Perhaps enough to make a difference. 
She knows where to research, and she begins uncovering the city's dark secrets. 

\lyricslimbonicart{Towards the Oblivion of Dreams}{
  With the underworld's \\
  subconscious darkness I am allied. \\
  Deeper aspects, forces of nature,\\
  mind can now see the unseen. \\
  Ancient land hidden from man. \\
  An esoteric dream in the desert sand. \\
  Shimmering sparks in the darkness, \\
  as death overtakes the soul. \\
  Loose the body, and earthly conscience. \\
  The freedom of the spirit must be total.
}









\subsection{Rian has bad dreams}
After the traumatic divination experience, Rian has nightmares of the \Sephirah{} soul prison.

Alternatively, it might be Carzain dreaming of the \Malach{} soul prison. 

Quotes from \cite[Dread]{CliveBarker:BooksofBlood:II} (about a guy who, as a boy, suddenly becomes deaf and suffers from fits of tinnitus): 

\lyricsbs{Clive Barker}{Dread (Books of Blood II)}{
  One moment his life had been real, full of shouts and laughter. The next he was cut off from it, and the external world became an aquarium, full of gaping fish with grotesque smiles.
  
  His eyes would jerk open. His body would be wet with sweat. His mind would be filled with the most raucous din, which he was locked in with, beyond hope of reprieve. Nothing could silence his head, and nothing, it seemed, could bring the world, the speaking, laughing, crying world back to him. 
  
  He was alone.
  
  That was the beginning, middle and end of the dread. He was absolutely alone with his cacophony. Locked in this house, in this room, in this body, in this head, a prisoner of deaf, blind flesh.
}

See also section \ref{The dark universe}. 









\subsection{\Nasshikerr{} returns to Moro}
\hs{\Nasshikerr} returns to Moro. 
He has found out some stuff about what is going on in Malcur. 
He tells her about how it all comes together. 

Moro goes into action. 
She joins up with \Tiroco, to a limited extent. 
They do all they can to \hs{stop the evil}. 

They find out when the evil ritual will take place, and do all in their power to stop it. 





\subsubsection{\ps{\Nasshikerr} POV}
\Nasshikerr{} does not think any real harm will come from telling Moro about \ps{\Secherdamon} plan. 
He is a rival of \Secherdamon. 

Many Cabalists and especially Sentinels are more interested in their internal power squabbles than the \hs{Feud} itself. 
They do not expect the balance of power in the Feud to change within polynomial time... at least not change asymptotically. 
Millennia of pointless squabbling and minor balance-of-power fluctuations have made them complacent. 
They do not suspect that the end is near. 
Few are as keen-sighted as \Secherdamon{} or \Azraid, and few suspect the scope or nature of their \trope{XanatosGambit}{Xanatos Gambits}. 

Besides, \Nasshikerr{} does not actually believe that Moro will be able to accomplish anything real. 
She is up against the formidable \hr{Psyrex}{\LocarPsyrex}, after all. 
But \Nasshikerr{} feels it could be interesting to see her try. 
(But remember to not make \Nasshikerr{} too evil.) 

Moreover, \Nasshikerr{} hopes Moro will be able to figure out \ps{\Secherdamon} plan. 
He wants to know more about what \Secherdamon{} is up to in Malcur. 
He cannot figure it out on his own. 
He makes Moro promise to report her findings to him. 

\Nasshikerr{} kind of likes Moro, even though he is rough with her. 
She is a bit short-sighted, and her traumata make her narrow-minded and blind, but she does her best, and he respects her for it. 





\subsubsection{Moro sacrifices to {\Nasshikerr}}
Moro must sometimes sacrifice humanoids to \Nasshikerr. 
She is ashamed of it. 
She hides it from Rian, since she remembers how horrified Rian was after he had seen the Sentinels sacrificing humanoids. 

Whenever she must, she takes some thieves or other lowlife scum that no one will miss. 

\begin{prose}
  \tho{Thieves and scum. That could have been Rian, before I knew him.}
  The thought made Moro shudder.  
\end{prose}









\subsection{Malcur is going mad}
The city of Malcur is gradually going mad, as a result of the Sentinel ritual gaining strength. 

Mages can see energy seeping, bleeding out of holes in the Shroud, like cosmic blood. 

The people are affected by this chaos, too. They go mad and irrational. Violent riots become more and more frequent, resulting in lynches, arson, gang wars and bloody murder for no reason at all. 

Chaos is unleashing people's natural, inherent viciousness and bestial savagery. Have some \trope{RapeTheDog}{Rape the Dog} moments where the people of Malcur show what kind of scum they really are at heart. Then the reader will feel less sorry for them when they are massacred. 

Maybe, at the end, have a scene where a bunch of guys are lynching an innocent victim. Then some supernatural horror comes along and the bullies all die a gruesome death, while the victim is lucky and slinks away. 
















\section{The Immortals}







\subsection{The immortals and their background}
Remember, in chapters featuring the immortals, to have references to their history and relationships. 
And flashbacks, and dream sequences.

The above chapter with \Achsah{} is a good example of where I might do this. 

Does \Achsah{} or \Teshrial{} share a back story with \Ishnaruchaefir? That might be cool. 

Compare to the many flashbacks and cryptic back story references in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}. 









\subsection{\Achsah}
\subsubsection{\Achsah{} and \Teshrial}
Remember to read about \hs{\Achsah} and \hs{\Teshrial} before writing this! 

Have one or more scenes with \Achsah{} and \Teshrial. She is subordinate to him in rank, so she humbly knees before her master. But inside \hyperref[Achsah hates Teshrial]{she despises him}. 

Maybe she tells him about new developments with \Tiroco, which she's heard from Needle. 

\target{Brains will triumph over brawn}
We see \Teshrial{} training with various weapons. 
He is an \hr{Weapon master \Teshrial}{expert weapons master} with both melee weapons, firearms and magical devices. 
Therefore he wants to test his mettle against the infamous \Ishnaruchaefir. 
He wants to prove that technique triumphs over brute force (\hr{Brawn triumphs over brains}{unlike} last time). 
Some \resphain{} doubt this. 
He points out that he has fought \dragons{} before (perhaps even killed some), and he has fought the \Baelzerach{} and their \daemons. 
One of them thinks back to the time after \ps{\Teshrial} first battle with \Ishnaruchaefir. 
\Teshrial{} had been so badly wounded that he had had to drain 50 \humans{} dry of blood and consume all their lifeforce to heal himself and grow his wings and legs back.  

He remembers the humiliation of that day as if it were yesterday. 
It fires his pride. 

He thinks about {\ps{\Ishnaruchaefir} rematch offer}. 

\Teshrial{} admits to himself (if not to her) that he was overconfident and careless when fighting \Ishnaruchaefir{}. 
He promises himself to be better prepared next time. 
When he thinks back to the fight, he can see how reckless and stupid it was. 
What chance did he think he stood against the Destroyer? 
But he rationalizes it away, telling himself that he didn't go in to win. 
Rather (allegedly), the fight was a sort of reconnaisance. 
He did it to test \Ishnaruchaefir, see how he fought, so that he could better figure out how to counter it. 
It was just warm-up to make him better prepared for the real fight that is to come. 

\Achsah{} is somewhat disturbed to hear him talk of \quo{next time}. 
She would have thought that one battle against the terrible \Ishnaruchaefir{} must be enough. 
She is worried by the obsession her lord has developed. 

When \Teshrial{} mocks \ps{\Achsah} birth, she thinks to herself: 
\tho{%
  I was born like \Thanatzil, our founder. 
  In blood. 
  The same blood of life which, in other parts of our lives, we hail as something great and sacred.}
  
If \Thanatzil{} is mentioned, then remember to add him to the Dramatis Personae. 

Remember to read the sections about \hs{\Teshrial} and \hs{\Achsah} before writing the chapter!





\subsubsection{\Achsah{} has sex}
Have at least one scene with \hr{Achsah's sexuality}{\Achsah{} having sex} in \Nyx, probably with \human{} slaves. 





\subsubsection{\Achsah{} thinks about Needle}
Needle is very handy. 
The Sentinels know about Charcoal, but they don't know about her. 
She is all close to \Tiroco{} and can spy on her and have her shadowed, and the Sentinels don't know it. 

\Achsah{} kind of likes Needle. 
She loves her for her imperfections. 
\Achsah{} herself is imperfect, too, being \bezed-born. 




\subsubsection{\Achsah{} in Malcur}
Remember to have more scenes with \Achsah{} in Malcur. 

She has doubts about Needle's competence, so she takes action more directly. 

Remember to portray her as cool. 








\subsection{\ps{\Teshrial} farm}
\target{\ps{\Teshrial} farm}
Remember to read about \hs{\Teshrial} before writing this! 

\Teshrial{} breeds \humans. 
Not just slave \humans, no. 
Top quality \humans{}, for the \hs{Communion}. 
He breeds them for beauty, health, obedience and good taste. 

\tho{%
  Most \resphain{} don't understand \humans.
  To them, a \human{} is just an automaton that serves their needs.
  They do not understand all the care and hard work that does into breeding them. 
  
  \Humans{} must be bred with love.}

And \Teshrial{} loves his \humans. 

We have a scene where he visits a farm (breeding village) of his where he breeds them. 
He inspects the newborn and gives them his blessing. 
He touches them with the tips of his wings to bless them, caressing them with his soft feathers. 

He looks at a young girl of around 15. 
Touches her. 
She giggles and squirms when he tickles her with his feathers. 
But she is brave enough to meet his gaze. 

\ta{%
  Look at you. 
  How fine you are. 
  How perfect. 
  As beautiful as a \resvil.}

Maybe the girl is Evith. 
Almost ripe. 

\ta{%
  Very soon, my beautiful one. Very soon.}

But he thinks to himself: 
\tho{%
  Sigh.
  If only it \emph{were} a \resphan{} child.}
There are very few \resphain{} being born these days. 
\Teshrial{} has barely ever seen a \resphan{} child. 
He has only heard stories of the golden age (\hr{Shroud harms fertility}{before the Shroud}) when his people were numerous and fertile. 
It has something to do with the Shroud, he knows. 
He does not understand the details of \dweomer{} theory. 
It has not been his specialty. 

\tho{%
  What I would not give \hr{\Teshrial{} wants children}{to have a son or daughter of my own}. 
  Not a \bezed. 
  Not a surrogate.
  A pureblood.}





\subsubsection{Flying to the farm}
\Teshrial{} flies to the farm. 
Mention that \hs{\resphain{} enjoy flying}. 

\begin{prose}
\Teshrial: 
\tho{Maybe mortals would appreciate walking more if only nobles had legs.

  Brr. 
  What a grotesque and repulsive idea. 
  Legless \humans{} crawling around.
  Poor things.}
\end{prose}






\subsubsection{Punishing lovers}
There are two young \humans{} who have broken the rules. 
They have become lovers and had sex, and the girl has gotten pregnant. 
This is a crime, because they should only breed as they are ordered. 
It is a sin, for a \ps{\human} flesh and sex is a sacred thing (\resphan{} property) not to be thus profaned. 
They must be punished. 

\Teshrial: 
\ta{%
  Know this: 
  You have caused me great sorrow. 
  Your womb and your seed are sacred treasures, but you have violated and defiled yourselves by your act of fornication.
  I would that this sin could be forgiven and washed awau, for I grieve to see my beloved children punished. 
  But some sins cannot be washed away. 
  You must die, and your flesh shall feed the beasts, for you have been tainted and can no longer achieve the blessing of the Communion.}









\subsection{\ps{\Teshrial} banquet}
\Teshrial{} holds a small banquet and invites some \ketheran{} acquaintances. 
Among them is \Firaxel, a \resvil{} whom he has the hots for and wants to score. 
She is high status, capable and beautiful. 
A real catch. 
\Teshrial{} wants to lose his \quo{\hr{\ps{\Teshrial} virginity}{pureblood virginity}}. 

Read about \hs{\Teshrial} and \hs{\Firaxel} before writing this chapter!

For the party, \Teshrial{} has dyed his white hair with a single stripe of magenta, fitting the pink of his eyes. 
He also wears a magenta sash. 

Another guest is \hs{\Dezruth} of \Mystraacht. 
(Remember to describe \hr{Dezruth's appearance}{his appearance}.) 
He comes bringing two naked girl-slaves with him (\hr{Resphan slave livery}{\Mystraacht{} slaves often go naked}). 
This provokes some of the \CiriathSepher{} present. 
\Dezruth{} himself thinks he is being very modest and respectful of his host's culture by bringing only two slaves, where he would have liked to bring more. 
The girls kneel by his side most of the time, only occasionally doing something active to service him. 
\Dezruth{} mostly relies on the local slaves when he needs to be serviced. 
His own slaves are mostly there to show his status. 

He woos \Firaxel. 
She teases him. 
(\Resviel{} are expert teasers.)
But she is a bit impressed and aroused when she hears the story of how he stood his ground alone against the dreaded \Ishnaruchaefir{} and had the courage to challenge him. 
And even to fight to the death! 
(\Ishnaruchaefir{} has a reputation for destroying souls, so the fact that \Teshrial{} has survived with his soul intact is considered an accomplishment.
The \hs{Shroud prevents soul destruction}, but \Ishnaruchaefir{} is strong enough that he \emph{could} have eaten \ps{\Teshrial} soul if he \emph{really} wanted to.
\Menessiaraid{} later warns him about this.)

\Teshrial{} sees her breasts heavy ever so slightly in arousal. 
He knows he has won a small victory and is one step closer to his goal. 

He tells about his ambition to defeat \hr{Ishnaruchaefir}{\Ishnaruchaefir}. 
He hopes that it will win him status in the \ps{\resviel}{} eyes, especially \Firaxel. 
He thinks about \hr{\ps{\Teshrial} family}{his father and mother and their great deeds}. 

\tho{I deserve \resvil{} pussy. 
  I have earned it. But I will earn it even more.}

He and \Firaxel{} softly caress each other with the tips of their feathers. 

\Teshrial{} mentally comments to himself how un-beautiful \Achsah{} is compared to \Firaxel. 
(Contrast this to how beautiful \Achsah{} appears to Needle.) 

At the end of the party, she kisses him on the lips. 
That is another victory for \Teshrial, but no guarantee yet. 
She gives him one of her feathers as a gift. 
This is arrogant of her, and he worries that he has lost value by supplicating and treasuring it. 





\subsubsection{Friendly duel}
Before the banquet, \Teshrial{} has a friendly sword duel with a \resphan{} friend. 
\Teshrial{} takes some wounds, but he wins. 
He kills his partner. 

The other guy comes back to life, but he misses dinner. 
\Teshrial-tachi joke about that. 





\subsubsection{Communion}
Remember to read about \hs{\resphan} culture and \hr{\naor}{\naorim{} (food slaves)} before writing this!

We follow a \hs{\naor} girl, {Evith}. 
She is to be eaten, and she \hr{Voluntary drain}{offers herself gladly}. 
Her religion tells her that she will become one with her gods and achieve eternal bliss when she is eaten. 
They will eat more than one \human{} that day (four in all or so), but she is the delicacy of the evening, bred specifically by \Teshrial{} and some of the best he has to offer. 
And she knows it. 
She is top quality and very proud of being able to serve in this manner. 
This is the culmination of her life, the moment she has looked forward to as long as she can remember. 

She is a \naor. 
Of all the \humans{} that served the \resphain, there were perhaps those who held higher ranks than the \naorim, but none were more sacred. 

She is giddy and excited, but also scared. 
Her heart is pounding, hammering, as she prepares to go in. 
This is the most exciting evening of her life. 

Her two closest girlfriends are with her. 
They kiss her cheek, hug her and wish her the best of luck. 

They are under the stern but kind supervision of Master Dumah, the \hs{carver}. 
He reminds the two other girls that they will all be reunited soon. 
Because they are both beautiful and lovely girls and he is sure they will be chosen soon, too. 

Her handlers calm her down and reassure her. 

\begin{prose}
  \ta{It will be fine, Evith. 
    After all, you do not have to \emph{do} anything. 
    Just submit. 
    Fear not.
    You are in good hands. 
    The executioner is skilled and will take the best care of you.
    Now go.}

  She thanks them. 
  Hugs them. 
  Says goodbye. 
\end{prose}

When the moment of the \hs{Communion} comes, Evith approaches the \resphain{}. 
She is clad in skimpy clothes: 
A bikini and a short skirt. 
She is happy and proud to wear \hr{Resphan slave livery}{clothes that identify her as \ps{\Teshrial} property}. 

First she has to present herself to her eaters. 
She catwalks in.
Then she greets each \resphan{}, one by one. 
She kneels down in front of each and kisses their feathers and hands. 

Then, after having kissed all of them, she walks away, kneels before all of them and (stammering and nervous) recites her \hs{epitaph}:

\begin{prose}
  Evith:
  \ta{%
    It is my pleasure and my rivilege to be allowed to Commune with you, my Divine Lord \Ketheran. 
    I humbly beg you to accept me as I surrender every part of me to you, in the most sincere hope that it will please you.}
\end{prose}

Then she prostrates herself, kisses the floor and remains down, waiting. 
These seconds are the longest of her life. 
\Teshrial{} rises and goes over to her. 
He bids her rise. 

She rises. 
He lifts her up and kisses her on the lips. 
It is a tradition: 
The farewell kiss. 
It is given by a \resphan{} whom the \naor{} knows and loves and trusts and is comfortable with. 
The Communion must be pleasurable even for the \naor, remember. 

Evith's owner is proud of her. 

\begin{prose}
  \Teshrial:
  \ta{Dear, sweet, brave Evith.
    We find you worthy of the communion.
    Most worthy.
    You have done very well.
    We accept everything you offer. 
    Rest assured that everything about you pleases us, beautiful child.}
\end{prose}

He also praises her epitaph. 
It was simple and traditional, but beautiful and heartfelt. 

Evith is happy. 

Evith then strips naked (by taking off the special ceremonial robe), kneels down on a special block. 
Then another servant kills her with a \hr{Gelveir}{\gelveir}. 
She dies happy, knowing that her masters love her and that she has served them well. 

\Firaxel{} is offered some of the most important parts of Evith. 
This is a chivalrous custom. 
A \resvil{} must always be kept as healthy as possible, because it makes her more fertile. 

Evith thinks back to the night before (her last night alive). 
She had sex with \Teshrial. 
It is customary for the one chosen for Communion to sometimes be honoured with this special boon on her or his last night. 
It was Evith's first and only sex ever. 
She was nervous and afraid. 

\begin{prose}
  \Teshrial: 
  \ta{What ails you, child? Confide in me. I bid you.}
  
  Evith: 
  \ta{I am sorry, my divine lord \ketheran. 
    But... I don't know what to do.
    I do not have the expertise of a [professional courtesan].}
  
  \Teshrial: 
  \ta{Sweet Evith, you are no [professional courtesan], 
    nor would anyone ask you to be.
    The courtesans are to be honoured, but you are something special.
    You are a flower that will bloom only once, and there is a precious magic in that that no professional can duplicate.}
\end{prose}

She remembers the gentle touch of his silken soft feathers. 





\subsubsection{\ps{\Teshrial} quest}
\target{\ps{\Teshrial} quest}
\target{\ps{\Menessiaraid} advice}
\Teshrial{} tells the others about the quest he has undertaken to bring down the mighty \Ishnaruchaefir. 
He knows it is risky and dangerous, but he wants to take risks and be bold. 
The \resviel{} love a hero. 
And he notices how \ps{\Firaxel} eyes light up when he tells about it, subtly implying his own daring. 

At first, he simply talks big about vanquishing \Ishnaruchaefir, but has yet to formulate any real plan for how to do so. 

At the party is \hs{\Menessiaraid}, a friend of \Teshrial{} who wants him the best of success in his wooing of \Firaxel. 
He recommends that \Teshrial{} study the myths. 

There are people who believe that \emph{\WanderersInDarkness} holds the key to slaying the mighty \dragonlord. 
But not much research has been done. 
It is not really worth it. 
The have \resphain{} very rarely been given the opportunity to confront the elusive \Ishnaruchaefir{} on anything but his own terms\dash if at all. 

But \Teshrial{} now has such a chance. 
When they fought, \Ishnaruchaefir{} {offered to accept \ps{\Teshrial} challenge to a rematch} should he issue it. 

Given that he has this extraordinary chance, \ps{\Teshrial} friends encourage him to do research, prepare himself and lay traps that fully utilize \ps{\Teshrial} strengths and \ps{\Ishnaruchaefir} weaknesses. 
\quo{Solve his \hs{Aenigma}}, so to speak. 

A few have believed to have found the answer and then gone off to fight \Ishnaruchaefir{}. 
None returned to tell the tale. 
\Menessiaraid{} knows of one such would-be hero who challenged \Ishnaruchaefir{} and fell: 
\hs{\Lothagiel}. 
\Menessiaraid{} recommends that \Teshrial{} seek out \Nemuragh, who was a close friend or family member of \Lothagiel. 
\Teshrial{} later \hr{\Teshrial{} seeks out widow}{does}. 





\subsubsection{\ps{\Teshrial} motivation}
Make it clear that \ps{\Teshrial} motivation is not purely selfish. 
He wants to win glory for himself, but he also wants to do heroic things because he genuinely thinks they are right. 
He wants to destroy \Ishnaruchaefir{} not just out of a personal vendetta, but because he is an evil menace\dash so evil and insane that even his own people, even his brother and daughter, revile him as anathema. 
So evil that he was even \hr{Ishnaruchaefir and the Sentinels}{cast out of the Sentinels} (or so \Teshrial{} believes). 
And \Teshrial{} wants to avenge the many victims (warriors and civilians, mortal and immortal alike) whom the wicked Exile has slain over the millennia. 

He wants to have children, not just for his own vanity and legacy's sake, but because his race needs children. 
He genuinely thinks he has good genes, and it is his duty to carry them on. 





\subsubsection{Called back by \Achsah}
While out on his farm, \Teshrial{} receives word from \Achsah{} (who is a \hs{High Telepath}) that \Ishnaruchaefir{} has appeared in Malcur. 
He hurries back home. 









\subsection{\ps{\Ishnaruchaefir} Aenigma}
\subsubsection{\Teshrial{} reads portents of \Ishna}
Have lots of astrology involved when \Teshrial{} researches the Aenigma. 

Fearing \Ishnaruchaefir, \Teshrial{} reads the stars in an attempt to understand the weave of the \matrices. 
He finds \ps{\Ishnaruchaefir} star\dash the \hs{Exile}\dash shining bright, which is a sign that \Ishnaruchaefir{} is once more active as a \vertex, after having been mostly dormant for hundreds of years (unlike \Secherdamon, who is always plotting). 

\target{\Teshrial{} does not know that \Ishnaruchaefir{} knows}
\Teshrial{} is confident that \Ishnaruchaefir{} does not suspect the true extent of the \ghobal{} plot. 
After all, \Ishnaruchaefir{} said: 
\ta{%
  \hr{\Ishnaruchaefir{} fakes ignorance about \ghobaleth}{%
    What a shame that your scheme is now ruined.}}
(Actually \Ishnaruchaefir{} lied. 
 He knew full well that there were more \ghobaleth.)

\Achsah{} also fears the return of the mystic immortal. 
She never knows if \Ishnaruchaefir{} is a direct enemy, a third-party hindrance, or even a temporary ally. 
She doesn't understand him. 

\target{Achsah and Teshrial worry about Secherdamon and Ishnaruchaefir}
\Achsah{} and \Teshrial{} also worry about \Secherdamon.
They know they both have business in Malcur, so they suspect a connection. 
Even though the two are known to be archfoes, this coincidence is conspicuous. 
But they study the constellations, and the Exile is nowhere near any of \ps{\Secherdamon} \matrices, so they cannot be in league with one another. 
The two are presumably just both drawn toward Malcur because it is a \nexus. 





\subsubsection{\Nemuragh}
\target{\Teshrial{} seeks out widow}
\Menessiaraid{} \hr{\ps{\Menessiaraid} advice}{once recommended} that \Teshrial{} seek out \Nemuragh, who was a close friend and gay lover of \Lothagiel, a would-be hero who challenged \Ishnaruchaefir{} and fell. 

\target{\Teshrial{} gets notes}
\Teshrial{} seeks out \Nemuragh. 
\Nemuragh{} tells him of his friend's quest and his findings. 
After some negotiation, he lets \Teshrial{} have \ps{\Lothagiel} notes. 
This gives him a lot of insight into the Aenigma. 

Read about \hs{\Lothagiel}!

\ps{\Lothagiel} notes are not complete. 
There are fragments missing, presumably destroyed. 
Besides, they were written for himself to understand, not for outsiders. 
They were not compiled into an easily readable form. 
So \Teshrial{} has to piece it together and try to make out what \Lothagiel{} was thinking. 

\Nemuragh{} tells him that \Lothagiel{} was studying \emph{\WanderersInDarkness}. 
\Teshrial{} later brings this up with \Menessiaraid. 

\begin{prose}
  \Teshrial{} wants to scoff. 
  \tho{Poetry? 
    You want me to prepare for battle by reading poems?}
  It seems ridiculous to him. 
  
  But \Menessiaraid{} likes the idea.
  
  \Teshrial: 
  \ta{Please explain.} 
  
  \ta{\emph{\WanderersInDarkness} is powerful.
    It is widely believed that it holds the answers to many important questions within its riddles and symbols.}
  
  \WanderersInDarkness is an epic poem, Teshrial knows.
  It deals with Ishnaruchaefir and his brothers, among other things. 
  Written after the Incursion by \Melcryth, some mad \dragon.
  Or so it was believed.
  The poem is in Draconic, but the name \quo{\Melcryth} appears to be a pseudonym, and no one knows who hid behind it. 
  
  \Teshrial{} is inclined to disbelieve. 
  But he knows \Menessiaraid{} is not stupid.
  \Menessiaraid{}'s area of study is religion and mythology.
  He has helped shape the dogma and world-view of more than one puppet religion in the Shrouded Realms.
  He knows mythology is serious business.
  So he might have a point.
  
  \Menessiaraid:
  \ta{There are many who study it.
    Not just mystics and philosophers, but also magic scholars.
    And Matrix theorists. 
    The poem is difficult to understand, but its study has yielded some remarkable insights over the centuries.
    You should not discard it.
    Nor other pieces of myth and poetry like it.}
  
  \Teshrial: 
  \ta{Hm. 
    I am sceptical, but I know you know what you are talking about.
    Very well.
    I will do as you say and look into the myths.}
\end{prose}

After his initial defeat, \Teshrial{} has developed an obsession with \Ishnaruchaefir{} (just as \Ishnaruchaefir{} wanted him to) and now studies the records about him. 
He reads them on \hs{graph-glass}. 

He reads \hs{\Urizeth} annotated \emph{\hs{\WanderersInDarkness}}. 

There are many different versions and fragments of the epic. 
Some of them are considered apocryphal by many. 
\Teshrial{} reads them anyway. 
They are artistically successful and evocative, so \Teshrial, fancying himself an artist, likes them and believes there must be some truth in them. 






\subsubsection{\Urizeth}
\Teshrial{} does not figure out all this on his own. 
He seeks out \Urizeth{} and talks to her in person. 
He asks for her help in interpreting the Achilles' heel and the Nadir. 
She provides much help. 
He shows her \ps{\Lothagiel} notes. 
She did not previously know of it, so she is very fascinated and interested. 
\Teshrial{} learns much. 

\Urizeth{} asks to keep copies of \ps{\Lothagiel} notes and study them some more. 
She tells \Teshrial{} to come back later, and she will discuss her findings with him. 






\subsubsection{\Ishnaruchaefir{} hears of it}
Have a scene in the \hs{Mirage Asylum} with \Criseis{} and \Ishnaruchaefir. 

\begin{prose}
  \Criseis:
  \ta{Be careful with this \Teshrial, Master \Quessanth. 
    He is clever and resourceful. 
    Do you remember \Lothagiel? 
    I have learned from my Sentinel contacts that 
    \Teshrial{} has procured \ps{\Lothagiel} notes and is researching you. 
    Moreover, he is studying \emph{\WanderersInDarkness}, and even consulting an expert on the poem.
    A certain \Urizeth{} of \TiphredSerah.}
  
  \Ishnaruchaefir{} (smiling diabolically): 
  \ta{Is he now? 
    I will have to do something about that.
    \Urizeth, you say...?}
\end{prose}






\subsubsection{\Urizeth{} dies}
\Ishnaruchaefir{} catches word that \Teshrial{} is researching him. 
\Criseis{} tells him. 
She has heard from some of her Sentinel contacts. 

\Ishnaruchaefir{} is happy. 
This is exactly what he wants \Teshrial{} to do. 
But he wants to fake that he fears this research. 

So \Ishnaruchaefir{} seeks out \Urizeth{} while she is out in a Shrouded Realm, visiting a demesne. 
He sneaks up on her as close as he can while avoiding detection (which is not very close). 
Then he charges. 
She immediately senses a huge-ass \vertex{} coming straight at her, so she tries to flee. 
But she is unprepared. 
Besides, she is no athlete and hence no fast flyer. 

He catches her. 
He blasts her with an attack spell. 
It does not kill her, but it shreds her wings, grounding her. 
Now she cannot escape. 

\begin{prose}
  \Urizeth: 
  \ta{You... \Ishnaruchaefir!}

  \Ishnaruchaefir: 
  \ta{\Urizeth.
    It has come to my attention that you are... researching me.
    I must interpret this as a challenge. 
    And I am not pleased.
    I fear I must make an example.
    To you and all your kind.}
\end{prose}

Then he kills her. 
She defends herself, but she knows she has no chance. 

When she dies, he makes a mock attempt at destroying her soul. 
She fights back, using all the \TiphredSerah{} stealth and cleverness at her disposal. 
She succeeds, and her soul survives and eludes his grasp.
He lets her think she outsmarted him, but in reality he wanted her to do it. 
Maybe he might have been able to destroy her, but he let her go. 
(He admits, though, that she was good. Slippery like an eel. He is not sure he could have destroyed her. Maybe he tells this to \Secherdamon{} or \Nzessuacrith{} or \Menessiaraid{} or \Criseis.) 
He wants her to go back to \Teshrial{} and redouble her efforts to help him. 

And above all, \Ishnaruchaefir{} wants the \resphain{} to think he fears them and their research. 
He wants them to think they are on the right track and redouble their efforts to divine his weaknesses from \emph{\WanderersInDarkness}. 

This is a gamble from his side. 
He knows there is a chance they will discover some true weaknesses, but he is willing to take that chance. 
He thinks it more likely that they will discover red herrings and thus play into his hands. 





\subsubsection{\Teshrial{} hears of it}
When \Teshrial{} returns to \ps{\Urizeth} place to discuss their research, he is dismayed when another \resphan{} there tells him that \Urizeth{} has been killed. 
She has not yet regained consciousness, so her fellows only know that she is dead but not destroyed. 
They do not know who did it. 

\Teshrial{} walks away dismayed. 
He has a good idea of who might have killed \Urizeth{}. 






\subsubsection{\Urizeth{} comes back}
\Urizeth{} is thoroughly killed, so it takes several days for her to come back. 
Six days or so after her death, she sends word to \Teshrial{} and asks her to come see her. 
He does. 

When he sees her, she is in terrible shape. 
She looks like a mummy; a shrivelled, mutilated husk of a \resvil. 
She can talk and move her arms, but her legs and wings are not yet fully regrown, so she is confined to a wheelchair for the time being. 
\Teshrial{} is grossed out, but he fully sympathizes. 
He remember how badly shape he himself was in after \Ishnaruchaefir{} had killed him. 

\Urizeth{} tells him the story of how she was killed, and the warnings and threats \Ishnaruchaefir{} gave her. 
But \Urizeth{} refuses to give in to his threats. 
She also refuses to wait for her body to recover. 
She wants revenge on the evil \dragon. 
She wants to get back to work as soon as possible, so she can help \Teshrial{} devise a way to rid the world of this cruel monster for good. 






\subsubsection{They discover weaknesses}
With the help of \Urizeth{} and other wise, elder immortals (perhaps even non-\resphain, such as \quiljaaran), \Teshrial{} manages to figure out \ps{\Ishnaruchaefir} weaknesses. 
He studies records of \Ishnaruchaefir{} in battle and maps \hr{Ishnaruchaefir's fake weakness}{the weaknesses he displays}. 

But in truth, the weaknesses are all fake. 
They are lies that \Ishnaruchaefir{} himself planted for this exact reason: 
To fool his enemies, lure them out and destroy them. 
It wasn't in the original \emph{\hs{\WanderersInDarkness}}, so he has planted some edited and unfaithful copies with his own fake myths in them.
(Some bits he wrote himself, others he had his close allies compose.) 

\lyricsbs{William Blake}{%
  The Four Zoas (Night the Second, 24:10-24:4)
}{
  \begin{tabular}{cl}
    FZ2-23.11; E313 & 
    First he beheld the body of Man pale, cold, the horrors of death 
    \\
    FZ2-23.12; E313 & 
    Beneath his feet shot thro' him as he stood in the Human Brain 
    \\
    FZ2-23.13; E313 & 
    And all its golden porches grew pale with his sickening light 
    \\
    FZ2-23.14; E313 & 
    No more Exulting for he saw Eternal Death beneath 
    \\
    FZ2-23.15; E313 & 
    Pale he beheld futurity; pale he beheld the Abyss 
    \\
    FZ2-23.16; E313 & 
    Where Enion blind \& age bent wept in direful hunger craving 
    \\
    FZ2-23.17; E313 & 
    All rav'ning like the hungry worm, \& like the silent grave 
    \\
    &
    \\
    
      
    FZ2-24.1;   E314 & 
    Mighty was the draught of Voidness to draw Existence in 
    \\
    
      
    FZ2-24.2;   E314 & 
    Terrific Urizen strode above, in fear \& pale dismay 
    \\
    FZ2-24.3;   E314 & 
    He saw the indefinite space beneath \& his soul shrunk with horror 
    \\
    FZ2-24.4;   E314 & 
    His feet upon the verge of Non Existence; his voice went forth   
  \end{tabular}
}





\subsubsection{Nadir}
From \ps{\Lothagiel} notes, \Teshrial{} learns a very interesting observation: 
Apparently \hr{\ps{\Ishnaruchaefir} Nadir}{\Ishnaruchaefir{} has a period of Nadir} at more-or-less regular intervals. 

From regular \matrix{} theory it is unsurprising that this would happen. 
\Ishnaruchaefir, after all, is a big-ass \vertex, and the wielder of a powerful \hs{weaving artifact} to boot. 
But apparently no one had mapped the Nadir cycle before. 
\Lothagiel{} managed this. 
He researched some passages of \emph{\WanderersInDarkness} (which, as it turns out, were authentic, not planted) and picked up some hints. 
He studied \matrix{} theory, interpreted the symbols and kennings and connected the dots. 

According to \emph{\WanderersInDarkness}, the Nadir occurs \quo{when the \hs{Exile} is engulfed by the briny waters}. 
This is an astrological sign. 
\emph{\WanderersInDarkness} also reveals that he is at his weakest in the middle of the period, and there are further astrological signs to mark when this happens. 
\Teshrial{} and \Lothagiel{} have no means of verifying this last part, so they have to take the poet's word for it. 

Do not mention any exact numbers regarding the period. 
Just \quo{a number of years}. 
I don't want to paint myself into a corner.

Then he formulated a hypothesis and went about gathering empirical data from \quo{sightings} of \Ishnaruchaefir. 
These were few and far in between, of course, but still, with seven thousand years of history to draw from, he was able to dig up enough sightings for a pattern to emerge. 
And \Lothagiel{} was happy, for the observations supported his hypothesis: 
There were few to no sightings in the periods where \Ishnaruchaefir{} was supposed to be in Nadir. 
And when once in a while he was forced into combat, he seemed uncharacteristically reluctant, weak and prone to fleeing\dash and he did not wield his glaive. 

\ta{And without \Rystessakhin. 
  It\dash or should I say \emph{she}\dash is otherwise perhaps his most powerful weapon.}








\subsubsection{\ps{\Teshrial} research}
\Teshrial{} also learns that \Ishnaruchaefir{} is inquisitive and willing to take silly chances or be chivalrous for the sake of his curiosity. 
\Teshrial{} figures this out from some \emph{\WanderersInDarkness} passages and from conversations with other \resphain{}\dash and perhaps other creatures, too, such as \quiljaaran. 
He wants to take advantage of this. 
He figures it can buy him time to pull off some of his gambits and traps. 





\subsubsection{\Teshrial{} and \Menessiaraid}
\Teshrial{} hangs out with \Menessiaraid{} again. 
They discuss the plan. 

\begin{prose}
  \Teshrial: 
  \ta{That \scatha{} that \Ishnaruchaefir{} keeps around.
    What is her name?
    \Criseis.
    What about her?
    Might one go through her to get to him?}
  
  \Menessiaraid: 
  \ta{It has been attempted before, I believe, but it ended badly.
    I don't know the details, I'm afraid.}
\end{prose}





\subsubsection{The Achilles' heel}
\target{Ishnaruchaefir's weakness}
There is a myth that \Ishnaruchaefir{} can only be killed under certain conditions. 
He has an Achilles' heel. 

But it is difficult for \Teshrial{} to exploit the Achilles' heel using the skills, weapons and techniques at his disposal as a regular \resphan. 

So \Menessiaraid{} advises him to seek out the \quo{research department}. 
Who knows? 
They might have an \hr{\ps{\Teshrial} experimental weapon}{experimental weapon} for him...

Maybe it is not \Menessiaraid{} but \Azraid{} \hr{\Teshrial{} talks to \Azraid}{who suggests this}. 









\subsection{\Vizsherioch}
\target{Vizsherioch and Nithdornazsh}
\index{Dagger, the}%
The summoning of \Nithdornazsh{} is part of \ps{\Secherdamon} plan to bring \hs{\Vizsherioch} into Ascendancy. 
\Nithdornazsh{} is to become \ps{\Vizsherioch} citadel, a \nexus{} from which he can grow strong and spread his tendrils (politically and metaphysically) into the Realm of the Shroud. 

Previously, \Secherdamon{} had kept \Vizsherioch{} sequestered and hidden. 
He is his only son and the fruit of thousands of years of hard work, so \Secherdamon{} is very protective and does not want to lose him. 

Have scenes with the two in their citadel:
\begin{prose}
  \Vizsherioch: 
  \ta{Father, is your plan complete yet? 
    I long to get out of this citadel.}
  
  \Secherdamon: 
  \ta{Soon, my son.
    Remember, only the best is good enough for thee.}
\end{prose}

This is a vital step in the forging of the \hs{Dagger}. 
When the \Nithdornazsh{} project is complete, \Vizsherioch{} is more Dagger-y than ever. 








\subsection[Locar Psyrex]{\LocarPsyrex}
\subsubsection[Nzessuacrith visits Psyrex]{\Nzessuacrith{} visits \Psyrex}
Remember to have scenes where \Nzessuacrith{} visits \Psyrex{} at his Dark Crescent throne. 

Remove any direct references to the Malcur \nexus. 
Just refer to \quo{the \nexus{} in Pelidor}. 
We don't want to tell the reader that \Forklin{} is a decoy. 





\subsubsection{\Nzessuacrith{} thinks back to \Jirad{} Tantor}
\Nzessuacrith{} had a number of reasons for fucking \Jirad{} Tantor in her guise as \Takestsha: 

\begin{enumerate}
  \item 
    Boredom. 
    He's not a good lover, but it's better than twiddling her thumbs. 
    Remember, \dragons{} have no sexual taboos. 
  \item 
    It ties him closer to her, and she wants to have the Rungeran \ishrah{} tied to her. 
  \item
    She felt sorry for him after his son died. 
    Given her own bad relationship with her father (\Ishnaruchaefir), she has a weakness for such parent-child relationships, so seeing his grief toucher her heart, and she wanted to make it up to him. 
  \item
    The \quo{leaked diary} plot was actually not formulated at this point. 
    It was only later (or perhaps during the act) that \Nzessuacrith{} came up with the idea to kill two flies with one swat and use his diary to leak the information they wanted leaked to the Pelidorians. 
\end{enumerate}





\subsubsection[Psyrex fears Ishnaruchaefir]{\Psyrex{} fears \Ishna}
Have a scene from \ps{\Psyrex}{} point of view, where he fears \Ishna. He uses divination and discerns signs that \Ishnaruchaefir{} is active as a \vertex, and also near him. He frets, afraid of what the enigmatic immortal might do.

Remove any direct references to the Malcur \nexus. 
Just refer to \quo{the \nexus{} in Pelidor}. 
We don't want to tell the reader that \Forklin{} is a decoy. 





\subsubsection[Psyrex misleads Needle]{\Psyrex{} misleads Needle}
\Psyrex{} knows Needle's identity. At times he makes sure to feed her misinformation and lead her astray. 

\Psyrex{} has a double agent who repeats the things that Needle moans in bed. 









\subsection{\Criseis{} in Malcur}
\Criseis{} goes to Malcur to see how things are going. 
She alights on the roof of a high tower and gazes out over the city. 
She can clearly feel that something metaphysical is afoot. 





\subsubsection{Talks to a thug}
\Criseis{} espies a thug who smells like one aligned with the Sentinels. 
She catches him and forces him to tell her what he knows, using compulsion magic. 
Then she Shrouds the dude to make him forget. 





\subsubsection{Visits \Uswa}
\Criseis{} goes to the \hs{dead garden} and talks to \hs{\Uswa}. 
She recognizes that, though mad, \Uswa{} knows more than most people credit her for. 

First we see \Uswa{} alone. 
She is mumbling. 
She communes with \quo{things in the ground} and \quo{things in the air}. 
She knows that there is more than one \quo{tribe} of \quo{things} vying for dominance. 
She can see the chains leading down into the deep, and the spiritual chains that tie people to \Nyx{} and the Cabal \Matrix. 

Then \Criseis{} comes. 
\Uswa{} tells her stuff. 

\Uswa{} sees through \ps{\Criseis} mortal guise and sees that she is really immortal. 





\subsubsection{Meets \Teshrial}
\Teshrial{} meets \Criseis. 

She responds to him in the \Resphan{} tongue. 

He tells her he accepts {\ps{\Ishnaruchaefir} rematch offer}. 
He \quo{makes an appointment}. 

\Criseis{} is afraid. 
From the date \Teshrial{} requests, she can deduce that he has figured out \hs{\ps{\Ishnaruchaefir} Nadir}. 
But she doesn't know that this is part of \ps{\Ishnaruchaefir} \trope{XanatosRoulette}{Xanatos Roulette}, so she begins to really fear \Teshrial, for her master's sake. 

And, come to think of it, also for her own sake.
She can tell that he means her ill. 

\begin{prose}
  \Criseis: 
  \ta{I see the way you are looking at me, Lord \Teshrial. 
    Are you planning to use me as leverage to get to my master?
    I think you will regret it if you do. 
    So far Master \Quessanth{} has maintained a certain diplomatic code of conduct. 
    A certain mutual respect. 
    This will cease the instant you try to harm me.
    And I do not think that is what you want, my lord.}
  
  \Teshrial: 
  \ta{Are you threatening me, \scatha.}
  
  \Criseis: 
  \ta{%
    [The story of \hr{\ps{\Criseis} siblings}{her sister and brother}.] 
    And this is not a myth, Lord \Teshrial. 
    If you doubt me, I suggest you look up the incident in the \CiriathSepher{} archives.}
\end{prose}

\Teshrial{} threatens her, physically.

\begin{prose}
  \Teshrial: 
  \ta{Are you afraid, \Criseis?}
  
  \Criseis:
  \ta{Yes. But \emph{you} should be more afraid, Lord \Teshrial.
    I hear you breed \humans.
    How would you like to have a village of them suddenly consumed in a fireball?
    That is the least of what my master might do to you if you harm me.
    Please know that this is not my threat. 
    I would not condone the slaughter of defenseless \humans, but I cannot answer for my master's anger.}
\end{prose}

\Teshrial{} knows about \ps{\Ishnaruchaefir} rages and terrorism, so he wasn't going to harm her. 
But her tale still chills him a bit. 
He thinks of how horribly evil the Destroyer is, that he would be so cruel as to let cute, defenseless \humans{} suffer for his wrath. 
This makes \Teshrial{} hate him.
He must die. 

\begin{prose}
  \Teshrial: 
  \tho{Such a monster. He must be destroyed.}
\end{prose}


As \Teshrial{} discovers, \Ishnaruchaefir{} \hr{Ishnaruchaefir's code of honour}{does have a certain code of honour, but can go berserk if prompted}. 





\subsubsection[Meets Psyrex]{Meets \Psyrex}
She goes to the Dark Crescent and meets \LocarPsyrex. 
They call each other \quo{cousin}. 

Remove any direct references to the Malcur \nexus. 
Just refer to \quo{the \nexus{} in Pelidor}. 
We don't want to tell the reader that \Forklin{} is a decoy. 









\subsection{\Achsah{} goes to \Forklin}
\target{\Achsah{} suspects that Malcur is a decoy}
\Achsah{} is attempting to unravel what \Ishnaruchaefir{} and \Secherdamon{} are up to. 
Insert some musing about the terrible dark lord \Secherdamon, and the mystic immortal \Ishna, whose motives no-one knows, but whose badass-ness is universally feared. 

Late in the story, \Achsah{} becomes convinced that there is something wrong with the whole Malcur deal. 
It is too obvious. 
The Sentinels are leaving too many clues out in the open. 
She has been a Sentinel and opposed \Secherdamon{} for thousands of years. 
She knows that being this overt is not his style. 
He is smarter and more stealthy than this. 

She becomes convinced that there is something deeper going on. 
She suspects that Malcur is a decoy. 

This is deliberate. 
\Secherdamon{} has made his Malcur ploy so obvious as to convince everyone that it must be a decoy. 
He draws all eyes to him and assures them that there is nothing to see. 
That way, when \Nzessuacrith{} attacks \Forklin, everyone will assume that \Forklin{} is the real deal and rush off to there to try and stop him. 
This will leave Malcur wide open. 

So she goes to \Forklin{}, where \hr{\Achsah{} meets \Ishnaruchaefir}{she meets \Ishnaruchaefir}. 








\subsection{\Teshrial{} talks to \Azraid}
\target{\Teshrial{} talks to \Azraid}
Have a scene where \Teshrial{} talks to \hs{\Azraid}. 
He remarks on how \hr{\ps{\Azraid}{} appearance}{\Azraid{} is much shorter than he}, but looks taller because of his great presence. 

Remember to read about \hs{\Azraid} before writing this. 

\Azraid{} is very interested in the \vertexspike{}. 
He asks \Teshrial{} for details. 
\Teshrial{} regretfully informs him that he knows little. 
It is \ps{\Achsah} table. 
\Azraid{} \hr{\Azraid{} learns of spike}{later learns more}. 

\Teshrial{} talks about his plan to slay \Ishnaruchaefir. 
He has several trump cards:
\begin{itemize}
  \item The Shroud.
  \item Astrology. 
  \item \Ghobaleth.
  \item The Achilles' heel. 
\end{itemize}

\Azraid{} is sceptical about \ps{\Teshrial} plan to challenge \Ishnaruchaefir.
\Azraid{} has encountered and fought \Ishnaruchaefir{} and knows \Teshrial{} is clearly no match for the \dragon. 
\Teshrial{} assures him he has a plan. 
He will lay a clever ambush, use his \ghobaleth{} and employ the secrets of the prophecies to attack all of \ps{\Ishnaruchaefir} weaknesses. 
\Azraid{} is still doubtful, but the idea has potential. 
He gives \Teshrial{} his blessing to continue. 

\begin{prose}
  \Teshrial: \ta{I will lay a trap with my \ghobaleth.}
  
  \Azraid: 
  \ta{But \Ishnaruchaefir{} has already killed one of your \ghobaleth.}
  
  \Teshrial: 
  \ta{Yes, my High Lord \Sathariah, but he believes that was the end of it.
    He does not suspect the true extent of my \ghobal{} plot.
    And even if he does, the one he slew was a runt. 
    I have much bigger ones.
    And he knows naught of the cunning trap I have laid.
    I will utilize his Achilles' heel, as described in the prophecies.}
  
  \Azraid: 
  \ta{Prophecies. 
    You do not believe in such superstition, do you?}
  
  \Teshrial: 
  \ta{No, my High Lord \Sathariah, not literally, of course.
    But myths are often truth shrouded in poetry.}
  
  \Azraid: 
  \ta{True.
    \emph{\hs{\WanderersInDarkness}} has proven itself full of remarkable insight in the past, hidden in symbolism. 
    So you may be right. 
    But I hope you are interpreting this correctly, \Teshrial. 
  
    Besides... 
    \Ishnaruchaefir{} is known to take reckless chances.
    You just might fool him. 
    Very well. 
    You have my blessing. 
    
    However, as well prepared as you are, I still fear that it may not be enough. 
    I have an idea...}
\end{prose}

\Azraid{} is not sure he believes in the Achilles' heel. 
(This is foreshadowing of the fact that the heel is fake, so that does not seem like an \trope{AssPull}{Ass Pull}.) 

\begin{prose}
  \Azraid: 
  \ta{%
    Can it really be true, that \ps{\Ishnaruchaefir} greatest weakness was just under our noses all this time?
    It seems to good to be true.}
\end{prose}


\Teshrial{} comments (inside his head) on the fact that \hr{\ps{\Azraid}{} appearance}{\Azraid{} has wrinkles}. 
And his monstrous hand, which he always keeps hidden\dash with good reason, as \Teshrial{} knows. 
Have subtle references to the evil hand in all \Azraid{} chapters. 

\Azraid{} asks whether \Ishnaruchaefir{} might be in league with \Secherdamon. 
But \Teshrial{} assures him he is not. 
\hr{Achsah and Teshrial worry about Secherdamon and Ishnaruchaefir}{He and \Achsah{} have previously examined this}. 





\subsubsection{Experimental weapon}
\target{\ps{\Teshrial} experimental weapon}
\Azraid{} explains about some of the experiments that his scientists are working on. 
There is a mutation spell in their arsenal. 
\Teshrial{} is hesitant. 
But also excited.
\Azraid{} is good at marketing the thing. 
\Teshrial{} will bring extra glory to himself if he does his people this further service and field-tests their secret weapon. 

\Teshrial{} agrees to take this weapon (but only as a last-resort backup plan). 
\Azraid{} tells him to go to some Cabal scientists and get it from them. 

He does. 
There is a \banelord{} among them. 
Remember to make the \banelord{} use very archaic language. 

They give him this horrible parasite that crawls onto his body. 
When he activates it, it will burrow into his body and transform him into a monster. 

This tool is laboratory-tested but not field-tested... and only tested at a part of its potential strength, not at full power. 
They fear that the full-powered version will have unhealthy side-effects. 

\Teshrial{} sees the mutation process demonstrated (offscreen) and shudders. 

He takes the weapon, but makes no guarantees. 
He intends to hold it back as a last-resort back-up weapon, 
He fears it and will not use it unless he has to. 

The weapon is part of the \hs{\neoresphan} project. 





\subsubsection{\NeoResphan{} treatment}
The below is an optional spin on the whole \quo{experimental weapon} deal. 

\Teshrial{} is not only handed a device. 
He also undergoes some alchemical and magical treatment that is meant to transform and strengthen his body. 
It works. 
When the day of the duel arrives his body has been strengthened, so he is more powerful than normal even in his \resphan{} form. 

But there are side effects. 
He gets attacks of pain and dizziness. 
Sometimes he wakes up at night with nausea. 
One day after a meal, where he had been drinking lots of blood, he finds himself bleeding afterwards when he's alone. 
The blood he has ingested is seeping out of him. 

I am not sure about the above. 
It might be too cheesy. 
Remember, I am going for \quo{heroic} side effects, not \quo{villainous} ones. 

He is afraid. 
But he bears the pain and fear. 
For his quest's sake. 
For \Firaxel. 





\subsubsection{\Achsah{} fears the experimental spell}
\Teshrial{} mentions to \Achsah{} the possibility of using this experimental spell. 
\Achsah{} is frightened by the consequences of that. 
She does not like \Teshrial, but this mad sacrifice on his part is still frightening to her. 

\Achsah{} understands \ps{\Teshrial} motivation. 
He wants children. 
\Achsah{} can never have children. 
She wishes she could at least have the vain hope of once being a mother. 
So she tries to wish the best of success for him, at least. 







\subsection{\ps{\Teshrial} trap}





\subsubsection{\Teshrial{} sees \Ishnaruchaefir{} as the worst threat}
Have a scene with \Teshrial{} where he contemplates potential threats to Malcur. 
He sees \Ishnaruchaefir{} as the worst threat, because you never know what that meddling rogue immortal might do. 
\Secherdamon{} is less of a threat, because there is no way he would enter combat personally (it's a trauma he has from back when his brother was killed by \resphain). 
But he fears \Ishnaruchaefir{} and takes precautions for his return. 





\subsubsection{Looks at his \humans}
\Teshrial{} looks at some of home of his home-bred \humans. 
He caresses a beautiful youth with his feathers. 
\Teshrial{} loves his \humans{} and will not let the evil \Ishnaruchaefir{} harm them. 
He was shocked to learn that \Ishnaruchaefir{} would be so cruel as to let cute, defenseless \humans{} suffer for his wrath. 
This makes \Teshrial{} hate him.
He must die. 





\subsubsection{\Teshrial{} inspects his secret weapon}
\Teshrial{} inspects his secret weapon: 
The \ghobaleth{} hiding beneath Malcur. 
See section \ref{Teshrial's creatures}. 

\Teshrial{} is overconfident. After \ps{\Ishnaruchaefir} initial attack on Malcur (see section \ref{Ishnaruchaefir attacks Teshrial's creature}), \Teshrial{} was left with the impression that \Ishnaruchaefir{} believes that there was only one \ghobal{}, and that the way to Malcur is now open. But \Teshrial{} has several more, and he believes that \Ishnaruchaefir{} doesn't know about them. 

\Teshrial{} is confident in their ability to defend the city. Maybe he knows that \Ishnaruchaefir{} knows that he has one of the \ghobaleth{}, but he thinks the rest are hidden. But \Ishnaruchaefir{} sees through him. He knows that \Teshrial{} must have several more \ghobaleth{}. 

Perhaps he needs to perform an occult ritual to unchain the \ghobaleth{}. 
%Perhaps he must needs invoke powers greater than he\dash\resphan{} kings, or the \banelords, or even \Voidbringer.
He needs to invoke greater powers: 
His people's ancient pacts with the \banelords{} and their unholy might.

\lyricsbalsagoth{
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  I stand now at the anvil,\\
  adamantine hammer in my hand.\\
  In thunder-song the steel I smite,\\
  a clarion heard throughout this land.
  
  Ablaze upon the Altar of Stone,\\
  the Sigil of An-rayuth, the summoning.\\
  Folk of the Mist, Dwellers in Shadow,\\
  the thrice-blessed wand of the Wood-Gods is beckoning.
  
  At the aeon-swathed Shrine of the Oak I kneel.\\
  O' Oracle of the Great Forest, hear me this night...
}

Maybe this chapter should be called \quo{The Conqueror Worm}. 
Or some other chapter.

\lyricsbalsagoth{
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  Swaying serpents ring my oak-hewn throne,\\
  Night and Shadow are my hunting dogs.\\
  Ravenous, they howl to be unshackled,\\
  that their maws may be glutted \\
  (with the blood of my foes).
}





\subsubsection{He talks to \Achsah}
\Teshrial{} also talks to \Achsah{}. He sexually harasses her a bit, but he can't force her to sex. There are some privileges to being a \resvil.









\subsection{\Ishnaruchaefir{} goes to \Forklin}
\Ishnaruchaefir{} goes to \Forklin{} to see how things are going. 
He alights on the roof of a high tower and gazes out over the city. 
He can clearly feel that something metaphysical is afoot. 

He looks at the \hs{Ghost Tower} and comments that it is \hr{Ghost Tower history}{definitely \resphan-built}. 
Despite what the common folk may think. 

He cocks an ear and can hear speech. 
But he does not understand it. 

\begin{prose}
  \Ishnaruchaefir: 
  \tho{Maybe I should have taken the time to learn \Velcadian...}
\end{prose}






\subsubsection{Meets \Achsah}
\target{\Achsah{} meets \Ishnaruchaefir}
He meets \Achsah{} in the city. 
She is here because she \hr{\Achsah{} suspects that Malcur is a decoy}{suspects that Malcur is a decoy}. 
When \Ishnaruchaefir{} approaches the city, \Achsah{} \hr{Detecting \vertices}{can feel him from miles away}. 
It feels like a humongous 200 ton \hs{\brukath} stomping through the city. 
He has not only his own \vertex{} power, but also that of \Rystessakhin{} sending out tremours. 

\begin{prose}
  \Ishnaruchaefir: 
  \ta{Why are you here? Not to challenge me. You are wiser than that.}
  
  \Achsah:
  \ta{True. I bring a message from Lord \Teshrial. He wants to meet you.}
\end{prose}

\Achsah{} described \Teshrial{} in a way to make him seem madly overconfident. 
This is what he intends. 
He hopes to provoke \Ishnaruchaefir{} and goad him into coming to fight him, to \quo{teach him a lesson}. 

\Achsah{} lets slip that \Teshrial{} intends to use the astrological situation as a weapon against \Ishnaruchaefir. 
This is part of \ps{\Teshrial} plan: 
Leak information about one of the traps. 
That way \Ishnaruchaefir{} will be overconfident and not suspect the other traps. 

Make it clear how arrogant, dominant and strong \QuessanthIshnaruchaefir{} is. 
He all but commands \Achsah{} around. 
She realizes that if he gave her an order, she would likely obey him. 
She doesn't like that thought. 
She lived during the Incursion, after all. 
Or the \secondbanewar, as the Sentinels call it. 
She remembers his atrocities. 

She once encountered him on the battlefield. 
She saw his visage, ablaze with fierce chaotic sorcery and hatred toward her kind. 
She felt his presence, radiating a silent promise of death and vengeance. 
And she had not stood her ground. 
She had not even let him come near her. 
She had fled from his path in panic. 
The rest of the battlefield had seemed like a sanctuary, then. 

\begin{prose}
  \tho{I had no courage to face him. 
    But \Teshrial... he stood his ground. 
    He met the Destroyer in single combat, and he fought to the death.
    \Teshrial{} is brave, I must give him that. 
    Much braver than I.} 
\end{prose}



She should loathe \Ishnaruchaefir. 
And she does. 
But here, with him, it is hard not to be captivated by the force of his personality. 
Such will. 
Such power. 
Such glory. 

There is raging bloodlust and savagery in him, she knows. 
But at other times, such as this, there is 

He is an outcast, despised and condemned by his own people, feared and reviled by all. 
Yet he stands proud like a king. 
Every bit the \dragonking{} that his brother \Nexagglachel{} was. 
She feel some kind of kinship with him in that moment. 
She is also an Exile of sorts herself, being \ashenblooded. 

\begin{prose}
  \tho{If only I had his strength.
    His disdain.
    His pride.} 
\end{prose}







\subsubsection{Visits \Psyrex}
Then he goes to see \Psyrex. 
% Maybe have a scene where \Ishnaruchaefir{} approaches \Psyrex{} in Malcur. 
Like the scenes in \cite{StevenErikson:GardensoftheMoon} where Anomander Rake visits Baruk in Darujhistan. 

Remove any direct references to the Malcur \nexus. 
Just refer to \quo{the \nexus{} in Pelidor}. 
We don't want to tell the reader that \Forklin{} is a decoy. 

\Psyrex{} is not happy that \Ishnaruchaefir{} can simply barge in, bypassing his guards and spells. 

\begin{prose}
  \Ishnaruchaefir: 
  \ta{So. I see you are attempting to resurrect \Nithdornazsh.}
  
  \Psyrex: 
  \ta{Yes. Do not try to stop us!}
  
  \Ishnaruchaefir: 
  \ta{I would not dream of it. Are you aware of the \ghobaleth?}
  
  \Psyrex: 
  \ta{Of course. Here is how we plan to deal with them...}
\end{prose}


\Psyrex{} tells how the resurrection of \Nithdornazsh{} is a \quo{pivotal step, a decisive battle in the eternal war. One step on the long ladder of bringing the \matrix{} of our kind to ascendancy}.  

\Psyrex{} berates \Ishnaruchaefir{} for being too obvious and attracting unwanted attention. 
He feels somewhat weird yelling at an immortal who is close being the equal of his Exalted Lord, \Secherdamon. 
But \Psyrex{} is proud and knows his worth, so he sees himself as almost \ps{\Ishnaruchaefir} equal. 
So he dares treat him like one. 
Still, he calls him \quo{\Ishnaruchaefir} and not \quo{Exile}. 
\Psyrex{} is not confident enough to refuse him his name. 

Make it clear how arrogant, dominant and strong \QuessanthIshnaruchaefir{} is. 
\Psyrex{} is proud to have stood his ground. 
\Ishnaruchaefir{} tried to pry his plan out of him.
\Psyrex{} resisted, but \ps{\Ishnaruchaefir} frame was super-strong, and he was forced to give up much.
But he did not reveal as much as he could have done. 
He has not totally lost, and he takes pride in that. 
Few can stand against such force of personality, and \Psyrex, for all his skill and wisdom, is only a \scatha. 
He rarely admits that, but in this hour, in a room with the dreaded Exile, he feels the truth of it.
Immortal though he may be, he is only a \scatha. 

Compare \Ishnaruchaefir{} to Lord Asriel in \cite{PhillipPullman:NorthernLights} when he twists Iofur Raknisson around his little finger. 





\subsubsection{The Blood-Red Vaults of \Nithdornazsh}
\target{Blood-Red Vaults of \Nithdornazsh}
Perhaps they look at the underworld beneath Malcur. 
Like the \hr{Malcur dungeon haunted}{haunted dungeons beneath \CastlePelidor}, the underworld is a place where the Shroud is thin. 
It is a gateway to the Blood-Red Vaults of \Nithdornazsh. 

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  Ancient and divine, older than the hidden Icosahedron, \\
  now rebirthed beyond the chaosphere.\\
  Rise... rise and destroy!
  
  Hatred, carnage, slaughter, havoc, chaos, murder!\\
  I am become the devourer of all life!
  
  Phobos, Deimos! \\
  The moons' rays liquefied in these blood red pyramids.\\
  In the shrines of abomination, black tongues rapt with blasphemy.\\
  Chaosphere, watchtowers, genesis, Cydonia...\\
  The Abyss yawns wide!\\
  Spirit of the carrion-thronged battlefield, open wide thy gate!
  
  Unruly evil!\\
  Colossal shapes etched against the moons, \\
  supine obeisance 'fore the mound,\\
  Accursed fiends, hail the Slitherer, \\
  abhorrent jaws drooling lunacy.
}









\subsection{\Teshrial{} meets \Ishnaruchaefir}
\Teshrial{} somehow meets \Ishnaruchaefir{} in person. 
They exchange some taunts. 
\Teshrial{} tells \Ishnaruchaefir{} the date when he wants his rematch. 
It is at the center of \ps{\Ishnaruchaefir} Nadir. 

\Ishnaruchaefir{} fakes suicidal bravado (i.e., fakes that he is trying to fake that he is not afraid, ultimately to make \Teshrial{} think he \emph{is} afraid).
He laughs.

\begin{prose}
  \Ishnaruchaefir: 
  \ta{I see you have done your research. 
    You and that scribbler, \Urizeth.
    But very well.
    I will not renege on my word... not today, at least. 
    You are smaller than I, so it is only fair to grant you this concession.
    My legend attributes to me many flaws, but cowardice is not one of them.}
  
  \Teshrial:
  \ta{Actually, it is.}
  
  \Ishnaruchaefir:
  \ta{Hm. Yes, now that you mention it, it actually is.
    But be that as it may.
    I accept your challenge, \resphan.}
\end{prose}

\Ishnaruchaefir{} makes \Teshrial{} think that he (\Ishnaruchaefir) thinks that \Teshrial{} knows only about the Nadir and not the Achilles' Heel. 
He fakes being afraid that \Teshrial{} might discover the Heel, but still cocky and confident that \Teshrial{} probably won't find the Heel. 

















\section{The Fall of Pelidor}





\subsection{Extreme multiprogramming}
When I get to the climactic scenes, there is a technique I need to remember to use: 
\emph{Change POV often}. 
It is employed in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}, and to great and terrific effect. 
It prolongs the tension and draws attention to the bigness and epicness of the whole thing. 

All these things should happen more-or-less in parallel:
\begin{itemize}
  \item The fall of \Forklin. 
  \item The duel between \Teshrial{} and \Ishnaruchaefir. 
  \item Moro and Rian's underground work in Malcur. 
  \item \Takestsha-tachi's spellcasting in \Forklin. 
  \item \Psyrex-tachi's spellcasting in Malcur. 
  \item Moro's assassination of Needle. 
  \item Rian's rescuing Neina.  
  \item The battle for the Ghost Tower. 
\end{itemize}









\subsection{\Ishnaruchaefir{} contacts \Secherdamon}
\target{Ishnaruchaefir tells Secherdamon of the Ghobaleth}
\Ishnaruchaefir{} contacts \Secherdamon{} and tells him about what he is doing. 

Or maybe not \Secherdamon.
Maybe only \LocarPsyrex. 
Maybe he and \Secherdamon{} are not on speaking terms, so \Psyrex{} has to mediate. 

He tells \Psyrex{} of the \hr{Teshrial's creatures}{\ghobaleth}. 
They are a greater threat than \Psyrex{} realized, and can seriously fuck up his plans. 

\Psyrex{} curses at him for not having told him this before.

\Ishnaruchaefir{} bargains. 
He is willing to help \Psyrex, but he wants something in return. 
(I don't know what yet.) 
\Ishnaruchaefir{} will lead \Teshrial{} and his \ghobaleth{} away from the city. 
He has planted an obsession in \ps{\Teshrial} mind and manipulated him with his false myths, so he believes \Teshrial{} will be obsessed enough to leave his precious city semi-unguarded and rush off to face \Ishnaruchaefir. 
But due to the nature of the myths, on which \Teshrial{} relies, this must be done at a strategically exact point in time. 

\Psyrex{} listens while \Ishnaruchaefir{} describes his plan. 
(Offscreen, of course. 
 \trope{UnspokenPlanGuarantee}{Unspoken Plan Guarantee} and all that.)
Then:
\begin{prose}
  \Psyrex: \ta{This is madness!} 
  
  \Ishnaruchaefir: 
  \ta{
    My last gambit\dash the one for which I am now infamous\dash was also madness. 
    I will do this.
    I will do this favour to my race.
    To \Nexagglachel.
    Yes, even to \Secherdamon.
    And when I do, you will stand ready.}
\end{prose}

\Ishnaruchaefir{} cannot take on all of \ps{\Teshrial} \ghobaleth{} on his own. 
Therefore, the showdown must be planned to coincide with the ritual summoning \Nithdornazsh. 
This will confuse the \ghobaleth, and they will be forced to struggle against \Nithdornazsh, which will weaken them and slow them down. 

This means \Psyrex{} must speed up his plans. 

\Psyrex{} curses some more, then ultimately agrees, knowing that it is too late to do anything else. 
He passes on the message to \Nzessuacrith, telling her to hurry up and \quo{capture} the Ghost Tower already. 
He knows that \Achsah{} is resourceful and might salvage everything even if \Teshrial{} falls.
He fears her more than him, actually. 

This scene is inspired by the conversation between Ganoes Paran and Shadowthrone in the middle of \cite{StevenErikson:TheBonehunters}. 





\subsubsection{Nadir begins}
\hs{\ps{\Ishnaruchaefir} Nadir} is coming, and he feels its onset. 
He prepares for it. 
Sets \Rystessakhin{} in a special place where she can \quo{recharge}. 

Make clear that this is of vital importance for the Shroud and to protect \Miith{} from alien menaces (the \banes). 
This makes \Ishnaruchaefir{} dreadfully vulnerable, and \Criseis{} and the grandchildren know that he runs a terrible risk by going into battle at such a time. 

But to \Ishnaruchaefir, it is worth it. 
The resurrection of \Nithdornazsh{} would be a monumental victory for the Sentinels. 
He does not tell the people around him about his plan, of course. 

He leaves instructions with \Criseis{} and \Thiencaste-tachi about what to do if he dies. 
How to take care of \Rystessakhin{} and all that. 

\Criseis{} is very worried when she sees him put down \Rystessakhin. 
\hr{Nadirs get worse}{His Nadirs are getting worse} every time. 
Something must be profoundly wrong with the Shroud. 
She has tried to pry out of him what is wrong, but he is not talking much. 
When he puts down the glaive he stands tall and arrogant and does not let anything show. 
But \Criseis{} has served him for ten thousand years and knows him better than any other. 
She can detect all the little telltale signs: 
the way he hesitates for the briefest moment; the way he stands up a few millimetres taller afterwards when he no longer carries the glaive's burden. 
It all hints of a terrible, excuciating pain that would be unendurable to any lesser person... even a lesser \dragon. 

She feels his pain. 
It is unfair, she thinks, that he has to carry this terrible burden and danger, and get nothing but scorn in return from the world. 
And she fears for the future. 
\hr{Nadirs get worse}{The Nadirs are getting steadily worse}. 
What if some day the burden gets so heavy that even he can no longer shoulder it? 

Before his great duel, \Ishnaruchaefir{} draws some energy from \Rystessakhin \dash as much as he dares\dash and uses it to empower his \hs{ward runes}. 
(Remember to read about \hs{ward runes}.)

\Criseis{} warns him:

\begin{prose}
  \Criseis:
  \ta{\Teshrial{} is well-prepared this time. 
    He has studied your strengths and weaknesses.
    I believe he has studied \emph{\WanderersInDarkness}.}
  
  \Ishnaruchaefir:
  \ta{Has he now?}
  (Smug, mysterious smile.
  He knows \Teshrial{} has taken the bait and fallen for the story of his alleged Achilles' heel.)
  
  \Criseis:
  \ta{Do not do this, master!
    I beg you.
    It is obviously a trap.
    And you are at your weakest.
    You may fall!}
  
  \Ishnaruchaefir{} (looking wistful, contemplating the possibility that he might die):
  \ta{I might.
    But know this, \Criseis:
    This battle will be of pivotal importance.
    This I predict.
    A mighty storm is brewing on the Pelidorian horizon.
    This storm will herald a \thirdbanewar.
    And it is a battle I intend for my race to win.
    It is a risk, but I am willing to take it.
    For \Nexagglachel.
    For our people.
    Even... even for \Secherdamon, perhaps.}
\end{prose}





\subsubsection{\Secherdamon{} thinks}
\target{Secherdamon thinks Ishnaruchaefir will sacrifice himself}
Shortly before \ps{\Ishnaruchaefir} duel is scheduled, have a scene with \Secherdamon. 
He ponders his brother's involvement, and what \Ishnaruchaefir{} intends. 
Then he realizes what is about to happen. 

\begin{prose}
  \Secherdamon;
  \tho{Fuck.
    \Ishnaruchaefir{} is going into battle.
    Now.
    Right in the middle of his deep Nadir.
    (\Secherdamon{} knows about the Nadir\dash superficially, at least.)
    
    And he is walking straight into \ps{\Teshrial} trap!
    Surely he must realize this. 
    What is he doing?
    He might actually be in danger!
    
    Why is he doing this?
    And he is helping me.
    Why?
    
    Does he intend, at last, to sacrifice his life to pay for his crimes?
    That cannot be.}
\end{prose}

For a short moment, this line of thought makes \Secherdamon{} respect \Ishnaruchaefir{}. 
He thinks and visualizes \ps{\Ishnaruchaefir} name, something he has not done for many centuries. 












\subsection{\Forklin{} falls}
The war lasts about a year. Eventually, Runger escalates the war by bringing in more and more mages and supernatural aid. 
The Imetrians begin to suspect that Runger has allied with Durcac and gained the aid of Rissitic mages and troops (which is true). 
The Imetrians are not certain, but these suspicions sway them to finally send some aid to Pelidor. 





\subsubsection{Push comes to shove}
The Pelidorians are holed up in \Forklin. 
It is a strong city, and they believe they can hold off the Rungerans for long enough to hopefully summon allies from neighbouring kingdoms, or perhaps the Imetrium. 
As long as they can keep the Rungerans out, they have a chance. 

\Takestsha{} was also content to keep the siege up for a while. 
But then she receives news from \LocarPsyrex. 
He tells her that she will have to speed up her plans. 
She curses, but agrees. 
So instead of just waiting and holding the city besieged, she now forces Morgan to go all-out on the offensive and make every effort to take the city. 





\subsubsection{Rungeran reinforcements}
\Takestsha{} has lost a few mages, so she calls in some more \quo{recruits} to the \ishrah. 
These are actually Rissitic mages, disguised as rogues. 
Morgan knows this, but the rest of the \ishrah{} and army doesn't, although they may suspect. 

They have also brought on some companies of mercenaries, which are Rissitic soldiers or \Durcaci{} tribesmen in disguise. 
These mercenaries bring in big, frightening monsters: 
Stegosaurs or ankylosaurs or sauropods. 
And a few of the warriors are \cregorrs!
Those guys are fucking wicked. 

Ilcas observes the new recruits to the Rungeran army. 
No one knows the mages are new (and they don't cast Rissitic magic, so they are difficult to pinpoint as being odd-men-out). 
But scouts have seen the new mercenary bands arrive. 
They are also noticeably different from the rest. 
It is no secret that they are not native Rungerans. 
Ilcas suspects that they are \Durcaci{} tribesmen. 
And if they are \Durcaci, then it is likely that they are also Rissitic. 
And this fits nicely with the theory that the Rungerans are allied with the Rissitics. 
Ilcas goes to tell Sethgal about it. 
He also does his best to send a message to the Imetrium and inform them that there is almost definitely Rissitic involvement. 

This is true, of course. 
The tribesmen \emph{are} Rissitic, or at least Rissitic-allied. 
They were only brought to the battlefield at this late hour, because \Takestsha{} did not want everyone to know that Runger was in league with \Durcac{} too soon. 





\subsubsection{Carzain}
Near the end of the war, Carzain is stationed in \Forklin{}, a strategically important city in the northern Pelidor. There is a lengthy siege and the Rungerans bring in Rissitic reinforcements. 
The Imetrians send a few elite soldiers and mages to support them and attempt to find out more. Telcastora Ilcas leads them. Curiet Serpentin is also there. Originally, Curiet was just a civilian Imetrian working in Forklin. Later he gets drafted to be some Imetric mage's assistant, or perhaps his interpreter. 

Also, Redcor \Matron{} \Esmerel{} is there. \Esmerel{} suspects that a Scion has been incarnated and dwells in Pelidor. The Redcor have determined this via astrology or something. \Esmerel{} comes to investigate, together with \Racel{} and two Gandierre, \France{} \Perival{} and \Isacc{} \Chiran. \Racel{} is there because she is Pelidorian... I think. 
\Esmerel{} investigates and ultimately determines that Carzain is the Scion. 

They fight bravely, but ultimately the city falls.





\subsubsection{Carzain-tachi fight for survival}
After the fall of Forklin, Carzain ends up together with Telcastora Ilcas and a few other Imetrians, including Curiet. Carzain also has a few of his soldier buddies along. Then they meet up with \Esmerel{} and her Redcor. They slink around and try not to be killed by the Rungeran forces, but they are forced into a fight, and several of them are killed. Only Carzain, Ilcas, Curiet, \Esmerel{} and \Racel{} survive. They slink around some more and realize that \Forklin{} is lost. 





\subsubsection{Carzain and Delph discuss archetypes}
Carzain says to Delph: 
\ta{Y'know, this is almost like a scene from the legends.
  With the heroes standing in the rubble of the fallen city and swearing revenge and all.}

Delph:
\ta{I hope we're not in a legend, 'cause if we are, you're doomed.
  'Cause I'm the hero, and you're the hero's faithful companion. 
  And the companion always dies before the end.}

At the end, he is dying and thinks: 
\tho{I can't die.
  I'm not supposed to die.
  Damn you, Carzain. 
  You're the sidekick. 
  You were supposed to die, not me.}





\subsubsection{\Tsekkect{} runs away}
\Tsekkect{} is alone. 
Delph is dead, and she has been separated from Carzain-tachi. 
She thinks:
\tho{Fuck it. I've had it with these stupid nobles and their stupid war.
  I'm going back to my tribe.
  They'll take me back.
  They have to.
  They will.
  I hope.}

This is the last we ever see of her. 
I don't need her, I just want to avert the \trope{SortingAlgorithmOfMortality}{Sorting Algorithm of Mortality} by not killing the nonhuman companion. 





\subsubsection{Carzain-tachi encounters \vorcanths}
\target{\Vorcanths{} help Ramiel}
Have one very mysterious scene where Carzain dreams. 
His traumas and \hr{Ramiel's bound souls}{the bound souls that haunt him} take on physical shape and attack him. 
But \hr{Moon-Wolves help Ramiel in dreams}{white wolves appear and dispel them}, saving him. 
Only to disappear again, casting enigmatic glances at him. 
He senses that he knows them, and feels conflicting feelings of loss, guilt, joy and relief.

When Carzain first sees them, he compares them to wolves. But Vizicar says hyaenas. Carzain hasn't seen a hyaena, but he recognizes them from Vizicar's memories. (Vizicar is more well-travelled, since he is not only older, but also a king.)

Already in \emph{\TwilightAngelRemember}, Ramiel is receiving dreams about \vorcanths. 
It is a \hr{Carzain dreams of Moon-Wolves}{distress call from a \vorcanth{} in trouble}. 

Remember to read the section about \hs{\vorcanths} before writing the chapter!

Immediately after this scene with the \vorcanth{}, have a scene where some astrologer reads the stars and notices that Visha (associated with the \hs{\vorcanth{} \matrix}) is \hs{intersecting} with the Midnight Bat (the \hs{Mystraacht matrix}{\Mystraacht{} \matrix}). 
Or maybe this doesn't happen until later, where Ramiel is contacted by a badass \vorcanth{} leader. 

It is important to stress that it is the \vorcanths{} who take the initiative and help Ramiel out first. After that, \emph{he owes them}. 






\subsection{Needle summons \banes{} and \banerats}
\target{Needle summons \banes}
Needle needs to go on a raid against some Sentinel agents. 
She is only a minor mage, but she has been taught a spell that will invoke \Achsah{}, so she can send minions to her location. 





\subsubsection{She reports to \Achsah}
Some stuff happens. 

Needle is told to go into the crypt. 

\Achsah: \ta{Go into the crypt and summon \banes.}

Needle: \ta{Gasp! The ancient Vaimon crypt?}

\Achsah: 
\ta{%
  Tee-hee (very feminine laugh). I can share this secret with you: That crypt is older than the Vaimons.}

When Needle is down there\dash \emph{deep} down\dash she thinks about this, but it doesn't mean much to her. 
She knows nothing of architecture or ancient history. 





\subsubsection{She goes into the dark crypt}
She goes into the Vaimon-built crypt beneath \CastlePelidor. 
These are dark, disused and have an \quo{antediluvian} feel to them. 
It is a secret place built by Cabalists in the Vaimon Empire to serve as a gateway to \Nyx. 
Everwhere, she feels as if the eyes of wicked \Qliphoth{} are upon her. 
As if her audacious steps cause sleeping powers to stir in anger. 
She's afraid. 





\subsubsection{The \banes{} need \human{} hosts}
The \banes{} cannot come to \Miith{} directly, but need to possess a \human{} host. 
So Needle brings three prisoners with her to use. 
All of them total losers. 
They're probably dungeon inmates. 
She has contacts in the dungeon and can easily make some less important prisoners \quo{disappear} in the papers. 





\subsubsection{The summoning ritual}
The ritual is dark and mildly erotic. 
She must circumvent the \Sephiroth{} and invoke \Qliphoth{}, and even nameless powers. 

Is she naked? 
She might be, but only if I can come up with a good excuse for stripping her. 
Perhaps she was simply told that she should be naked because the \resphain{} like the sight of a \human{} prostrate, naked and begging\dash completely humiliated and submissive. 
Perhaps \Achsah{} sexually abuses her a bit. 

Needle is pretty afraid, for she has never had to deal with major issues like this alone before. 
Nor has she ever seen a \bane{} or \banerat{} up close. 
She has seen \resphain, but the more horrid creatures she has seen only from a distance. 
She has always shied away from them and averted her eyes, never having to deal with them directly. So she is frightened at having to take command of them. 

Needle mentions the Shroud. 
She doesn't really understand what the Shroud is. 
But is proud that she knows it exists. 





\subsubsection{She remembers how she first became a Cabalist}
Needle is reminded of the day when she first became a Cabalist, where she was first confronted with \itzach, \Nyx{} and the horrors that dwell there. 
She feels like she is re-living it. 

\lyricsdimmuborgir{Grotesquery Conceiled Within Measureless Magic}{
  For thy presence made pleasure of pain,\\
  and thy madness turned sanity into vain.\\
  Profoundly wicked owner of souls.\\
  The mysteries of thy creation beheld by ghouls.
  
  Diabolically disguised heavenly bodies,\\
  and its atrociously desired primordial elements.\\
  Plunging through the confused beart of sulphur.\\
  In all this darkness, how can a man see?
}

She originally thought that mages were specially gifted supermen with inborn magical powers beyond the ken of the common herd. 
She was wildly surprised and more than a little scared when Charcoal-tachi told her that \emph{she} herself could learn magic. 
According to Charcoal, all it took to cast magic was a worthwhile brain and the willingness to see beyond the lies with which the common folk surround themselves (code for the Shroud) and face the dark truths of the universe. 
And then grab this truth with both hands and coerce it to spit out what you want. 





\subsubsection{Read up on \banes}
Remember to read up on \banes{} in my notes before writing this chapter. 





\subsubsection{She is afraid of the \banes}
She manages to summon two or three \lesserbanes{} and maybe some \banerats. 
The \banerats{} are not so powerful and act mostly as scouts and bloodhounds. 
But the \banes{} are terrible. 
Needle is scared shitless at commanding them. 
(She notices that they wear splint-mail-like armour... maybe.)

The \banes{} approach her and seem very menacing. 
She can't control them. 
They come ever closer. 

They seem to be directing some mental attack her at her, which she can't defend herself against. 

Needle panics, thinking that they are coming to eat her. 
She freezes up, or falls to her knees. 
She begins crying and whimpering. 
She whines and begs: 
\ta{Stay back! Go away! Don't hurt me...}
She pleads with them to spare her life. 

\Achsah{} contacts her telepathically and slaps her up, telling her to get a hold of herself. 

Needle realizes that the \banes{} never intended to hurt her. 
They were simply menacing because that is how \banes{} appear to \humans: 
Hideous, cold, alien, evil. 

It turns out that the \banesz{} \quo{mental attack} was simply an attempt to communicate. 
They spoke to her in their telekinetic language and told her their names. 
\Bane{} names are not words but kinetic sensations. 
They are terribly frightening to unsuspecting mortals. 
\tho{So that's their way of speech, is it?}
To Needle it felt as if they were carving their names with daggers on her bare skin. 

Slowly she gets the hang of commanding them. 
But she is still afraid of them. 
Perhaps this gradually drives her mad. 

The three \banesz{} names are Quicksand, Undercurrent and Gallow. 
They look completely alike to her eyes, but their telepathic \quo{feel} is different. 

Seeing the \banes{} and fearing their terrible power makes Needle admire the \resphain{} even more, since they are mighty enough to control such fell, wicked beings. 
She comes to love them even more. 





\subsubsection{\Achsah{} laughs}
\Achsah{} has been observing. 
Now she sits back and laughs. 
There was no real need for Needle to be naked during the ritual. 
It was just a practical joke \Achsah{} pulled on her. 

She jokingly scolds herself for it. 
\tho{%
  That was unfair of me. 
  I shouldn't be doing that. 
  Playing tricks on poor, unsuspecting minions. 
  Naughty, wicked \Achsah.}





\subsubsection{What happens later}
The \banes{} kill many before they are finally overcome by \ps{\Psyrex}{} mages. 
Maybe Moro \Cornel{} slays one of them\dash after a difficult fight!





\subsubsection{Quotes}
\lyricslimbonicart{Moon in the Scorpio}{
  In an atmosphere supreme\\
  forces dwell in domancy.\\
  The essence of its spirit is evil,\\
  as a curse upon thy name.
  
  Midnight is the shepherd of mysterious powers\\
  and moving shadows in the corner of the eye.\\
  Moon's blazing intuition\\
  contains what death requires.
  
  Cleanse the doors of perception.\\
  See things appear in its true art.\\
  The cold hands of divinity\\
  will tear thy soul apart.
  
  Behold the sky above \\
  when the moon is in the Scorpio.\\
  A cold bleak light. 
}









\subsection{\Teshrial{} prepares to battle \Ishnaruchaefir}
\Teshrial{} suspects that \Ishnaruchaefir{} will soon return. He prepares himself to face him. \Achsah{} half-heartedly tries to dissuade him, and half-heartedly fears for him. 
(Not much, though. Theirs is hardly a Mele/Rio relationship...)

\Teshrial{} is laying a trap for \Ishnaruchaefir. 
He plans to meet him in a place parallel to Malcur, but farther away from the Shroud (perhaps through the \hs{dead garden} again). 
He has his \ghobaleth{} lying in wait and intends to call them out to ambush \Ishnaruchaefir{} while fighting him. 

\Teshrial{} has several trump cards:
\begin{itemize}
  \item The Shroud.
  \item Astrology. 
  \item \Ghobaleth.
  \item The Achilles' heel. 
\end{itemize}





\subsubsection{His brethren fear for him}
Make it clear \ps{\Teshrial} brethren fear for him and want him to succeed. 
\Menessiaraid, his close friend, comes to see him off. 

\Menessiaraid{} gives \Teshrial{} a gift: 
His own \senaan, \hs{\Ossiraith}. 
He knows \ps{\Teshrial} favourite weapon, \hs{\Turishah}, was destroyed. 
He entrusts his friend with \Ossiraith. 
\Teshrial{} is honoured and vows to put it to good use. 

In addition to \Ossiraith, \Teshrial{} carries into battle two \hr{Ghijed}{\ghijedeth}. 
Before going into battle he looks down at his pistols. 
He takes them with him just in case, but he does not expect so much from them. 
\Ishnaruchaefir{} will probably wear \hs{ward runes}, and as such will be protected against guns. 
Guns are not so great in single combat with \dragons{} overall.
They are good if you can outnumber or outmanoeuvre your enemy. 
But in a fight like this, \melee{} is the best way to go. 





\subsubsection{Stewardship of Malcur}
\target{Teshrial leaves Bezed in charge}
\Teshrial{} knows that Malcur is terribly important and that it would be bad if it fell into the Sentinels' hands. 
He must be careful and guard it against \Psyrex-tachi while he himself is off fighting. 
He knows the time of his duel is coming up, so he has contacted his superiors and requested to have more aid sent to him. 
Some more \resphain{} come to relieve him. 

When he feels that \Ishnaruchaefir{} is near, he takes off and leaves some low-ranking \resphain{} in charge of Malcur. 
At this point \Achsah{} is already in \Forklin. 

\Teshrial{} thinks he is manipulating \Ishnaruchaefir{} and forcing him to face him at the right astrological moment. 
But he is actually being strung along. 

\lyricslimbonicart{In Mourning Mystique}{
  Darkness!\\
  I seek the silence that you bring.
  
  Grant me thy sacred gifts,\\
  bestow my soul thy offerings.\\
  Let the ancient forces of nature rule.\\
  Take my blood as the sacrifice,\\
  a symbolic faithful bond of truth.\\
  I kneel in front of thy altar black.
  
  When you look into an abyss, the abyss also looks into you.
  
  Tonight I enter into obscure dreams.\\
  In darkness shelter, I am unseen.\\
  With the esoteric gifts I possess\\
  I bring damnation by enforcing death.\\
  In the beginning of the storm \\
  I'll come forth.
  
  An arrival into a twilight reverb\\
  as just a shadow of the former self.
  Sorrow is my name.\\
  My true essence is pain
  
  Hear the mourning of the mendacious\\
  from the empty halls and shafts\\
  of false blinding light.\\
  Prepare the last sacrifice (on the altar)\\
  in the temple of decay.
  
  Please spare me from the final agony of shame.
  
  I am evil from the moment of conception.
}





\subsubsection{\Achsah{} wishes him well}
As \Teshrial{} departs, he contacts \Achsah{} telepathically and briefs her. 
She expresses her fears and concern for him. 
I need to paint some measure of friendship between the two. 
She does not like him, but she does not want him to die a painful death, or mutate permanently into a monster. 
She asks him to be careful and wishes him luck. 
He thanks her. 

This is small measure of making-up for them. 
They have never liked one another.
Here at the last minute, they take steps toward each other. 
It should be a bit touching, and tragic in retrospect. 





\subsubsection{\Firaxel{} visits him}
\target{\ps{\Teshrial} date}
\Teshrial{} is visited by \Firaxel. 
He has specifically asked her to come see him off to his duel. 
He wants to see her one more time before he risks his life and soul. 
She is attracted to him and wants to see him, too. 
They have an intimate, romantic date. 

\hs{\Firaxel{} is a scientist}. 
He learns that she greatly admires people who do something to advance science, especially if they take great risks to do so. 

\begin{prose}
  \Firaxel: 
  \ta{Our race exists for a purpose: 
    To improve ourselves, to bring ourselves closer to perfection.
    And our best and finest tool in this quest is science.}
\end{prose}

\Teshrial{} wants to impress her. 
So he tells her of how he has spoken with cutting-edge researchers and is participating in the \neoresphan{} project and testing a dangerous experimental weapon. 
It is dangerous, but he does it. 
So he is fighting and risking his life not only to prove himself and for the war and rid the world of an evil menace and avenge all the victims of the wicked \Ishnaruchaefir, but also for science and the betterment of their people. 

This turns her on. 
He can see it. 
Her eyes glow with desire. 
Her breasts heave. 
She licks her lips with hunger. 

They \emph{almost} have sex. 
They certainly kiss and grope. 
She promises him sex (in unmistakable terms) when he returns triumphant. 
The best sex of his life. 
And he can believe it. 
\Resviel{} are great lovers. 

He walks away happy. 
His dreams are coming true. 
Seeing her has given him courage. 
Before he was unsure if he dared use the experimental weapon. 
He was planning on holding it back as a desperate last resort, and even so he was unsure if he would have the courage to use it. 
But now he knows how much \Firaxel{} will love him for it. 
Now he dares use it. 
For \ps{\Firaxel} sake he is willing to take that risk. 

Have some from \ps{\Firaxel} POV. 
\Firaxel{} has developed genuine feelings for him and is afraid for him. 
She admires him. 

\begin{prose}
  \tho{What a \resphan. 
    What a brave, noble, beautiful soul. 
  
    But my heart aches to see you go. 
    I fear to let you do this. 
    Silly warrior \resphan. 
    Why must you risk your life and your very soul? 
    Your bravery alone was enough to bring me into his bed. 
    I can't wait to have sex with you. 
    
    But what if you fail?
    What if you die? 
    I might never see you again. 
    This might be our last moment together.
    What then? 
    
    I want to have sex with you here and now.
    If only I could. 
    But I can't. 
    I have a duty. 
    I cannot give myself to anyone less than a true hero. 
    Otherwise I would be a slut.
    I have no choice but to wait.
    
    Damn all these rules.
    
    Come back safely to me.
    My brave, beautiful hero. 
    My sweet, beloved prince.}
\end{prose}






\subsubsection{He is nervous}
\Teshrial{} is nervous and afraid to enter his battle. 
After all, he is just a \ketheran{} facing a terrible \shaeeroth. 
But he thinks of \ps{\Firaxel} kiss. 
And her sexiness, her hot and lusty eyes, and her soft, whispered promises of erotic bliss to come. 
This gives him courage and strength. 
It is \trope{ThePowerOfLove}{The Power of Love}. 

There is also a little bit of unexpected \trope{ThePowerOfFriendship}{Power of Friendship} from \Achsah. 

Thinking of these bright things, \Teshrial{} takes heart. 
He rights himself and is now ready to face \Ishnaruchaefir. 









\subsection{\Forklin{} decoy}
The Cabalists suspect that the Sentinels (specifically, \Secherdamon) are trying to open some kind of portal some place in Pelidor, but they don't know exactly where. 

The Cabalists believe the ploy is to create a \emph{portal} or \emph{conduit} to \Nithdornazsh{} or something like that. 
They don't imagine that the Sentinels actually intend to \emph{resurrect} \Nithdornazsh{} and bring the entire city to \Azmith, straight into the deep Shroud. 

At first, the Cabalists suspect Malcur. 
But \ps{\Takestsha} desperate, rushed attack against \Forklin{} convinces them that the target is \Forklin{} and the Ghost Tower, and that Malcur was a decoy. 
\Secherdamon{} is known for very elaborate decoys like this. 
\Achsah, who has long \hr{\Achsah{} suspects that Malcur is a decoy}{suspected that Malcur was a decoy}, is the first to believe the \Forklin{} ruse. 

\Achsah, who is in \Forklin, looks at the \quo{\EreshKali} spells cast by \Takestsha-tachi. 
\Achsah{} wonders when she first observes the \EreshKali{} magic. 
It does not feel like anything she would expect them to have. 
It also does not feel like what she would expect ancient \meccara{} to have. 
It is new to her, and it makes her suspicious. 
But what it \emph{does} smell like is Rissitic magic. 
That makes her even more suspicious. 
(She has heard Charcoal's account of Tantor's diary, but Charcoal has never seen Rissitic magic, so he cannot draw the connection.) 

Then she realizes that those spells are actually meant to tear the Shroud and reach into the Beyond, where it can summon... stuff. 
And the Ghost Tower, which is in close promixity now that the Rungerans have breached \Forklin, acts as a catalyst. 
Those spells are tearing at the very fabric of the Shroud. 
Something fucking nasty is breaking through, or so \Achsah{} thinks. 
In reality the summoning spell at \Forklin{} is a smokescreen. 
It is meant to warp the Shroud and look big and impressive, but it doesn't actually \emph{do} anything. 
It's just meant to attract attention and convince everyone that the real stuff is happening in \Forklin, near the Ghost Tower. 





\subsubsection{The \EreshKali{} magic backfires}
\Nzessuacrith/\Takestsha{} has been forced to speed up her plan. 
This means she must push the Rungeran mages really hard. 
Push them to their limit and beyond it. 

The Cabalists pick up on this, and they use it. 
\Achsah-tachi lay a trap for \Takestsha{} that somehow, due to all the stress and strain, causes the \EreshKali{} spells to backfire on them. 
This kills much of the Rungeran \ishrah{} and badly wounds \Takestsha. 

By now \Forklin{} is pretty doomed, but now \Nzessuacrith{} is weakened enough for \Achsah{}, her fellow \resphain{} and their \hs{\umbrae} to have a fighting chance against her. 





\subsubsection{Charcoal strikes back}
\target{Charcoal at the Ghost Tower}
Throughout much of the story, Charcoal, supposedly the sneaky master Cabalist, is duped, manipulated and played for a fool by his enemies. Sentinels and other agents seem to run circles around him. 
He's been played for a \trope{XanatosSucker}{Xanatos Sucker} the whole book. 
But at the end he finally realizes what's going on around him and strikes back. 

Near the end\dash perhaps after having discovered one or more of the people who have been cheating him, such as \Sanyor\dash Charcoal shows what a formidable agent he truly is, when he devises a master plan involving the Ghost Tower, dispelling the Rissitics' \quo{lost temple} magic and striking a hard blow to their forces. This buys the Cabalists time to send in reinforcements, including \banes{} and perhaps \resphain, which forces \Nzessuacrith{} to breach the \charade{} and assume her \draconic{} form to fight them off. 

\lyricslimbonicart{Solace of the Shadows}{
  I set the stones for invoking ceremonies.\\
  In the twilight zones arise abstract galaxies.\\
  The magic eye unveils the blackened skies.\\
  A new horizon begins to each one that dies.
}

He is frightened by the magnitude of the powers he unleashes. 
But also thrilled, exhilarated.

\lyricslimbonicart{Solace of the Shadows}{
  The desolation makes me feel\\
  so dark, so cold, the silence.\\
  So dark, so cold, the emptiness.\\
  Solace of the shadows.
  
  Night surrounds and embraces me.\\
  Darkness holds the secrets of man's fears.\\
  It captures my heart as the purgatory sears.\\
  I cast now the spell, as I cross through raging flames,\\
  into darkness, cursing names.
}





\subsubsection{\Achsah{} calls for help}
\target{\Achsah{} calls for help}
\Achsah{} smells a \ps{\dragon}{} presence. 

This was not \ps{\Nzessuacrith}{} intention. 
She is a master of stealth. 
But \Secherdamon{} needs to alert \Achsah{} of her presence, so he lays a trap for \Nzessuacrith{} forcing her to reveal a bit of herself, and \Achsah{} picks up on it. 

Now \Achsah{} is really frightened. 
She realizes that she can't handle \Nzessuacrith{} on her own. 
Moreover, if a \dragon{} is here, then it must be \trope{SeriousBusiness}{Serious Business}. 
And it is well known that \Nzessuacrith{} works for \Secherdamon, so \Achsah{} is convinced that she is the spearhead of his plan. 

She also becomes convinced that this attack has been deliberately timed to coincide with \ps{\Teshrial} duel, so everyone's eyes would be fixed on Malcur. 
So \Secherdamon{} must have learned of the duel and is using it as a smokescreen. 
No one in the Cabal imagines that \Ishnaruchaefir{} is \emph{actively} and directly helping \Secherdamon, because he hasn't been doing that for millennia now. 

So \Achsah{} needs help. 
She contacts \Teshrial{} in Malcur and requisitions reinforcements. 
He sends some more of his \resphain{} to her, leaving only a few to guard Malcur. 
The \resphain{} whom \Teshrial{} \hr{Teshrial leaves Bezed in charge}{left in charge of Malcur} now leave Malcur to help \Achsah. 

They \hr{\ps{\Achsah} rank}{stand below \Achsah{} in rank} and must obey her commands. 
This galls them, for some of them are purebloods. 

Only one \resphan{} now remains in Malcur: \Paerzim. 
\hr{Psyrex kills Paerzim}{That ends badly}. 





\subsubsection{\Achsah{} fetches \umbrae}
\target{Achsah fetches Umbrae}
When \Achsah{} has realized \Takestsha{} is a \dragon{} (and perhaps even the mighty \Nzessuacrith), she reckons she still has a few hours of time before the shit hits the fan. 

So she calls on Charcoal (who is in \Forklin) and gives him responsiblity for keeping control of \Forklin{} for some hours until reinforcements arrive from Malcur. 

\Achsah{} then quickly submerges and goes to \Nyx{} to fetch one or more \umbrae. 
She believes she and her companions will need them if they are to confront the \dragon\dash especially if it really is \Nzessuacrith, as she fears. 

She has asked \Teshrial{} to send \emph{one} \resphan{} directly to \Forklin{} (to relieve poor Charcoal) and send the others to \Nyx{} to rendezvous with her there. 

Remember to have a cool, dark, evocative, mystic scene where they summon the \umbrae{} from the endless dark deep. 

\Achsah{} is in awe and fear when the \umbra{} shows up. 
She is old enough to remember the days in \Merkyrah{} when \hr{Merkyrans fear Umbrae}{the \resphain{} lived in fear of the \umbra}. 
She remembers the terror and awe she felt when \hr{Rebels awestruck by tame Umbrae}{she first saw the rebel leaders riding \umbrae}, back when she was just a rank-and-file rebel acolyte. 

Nowadays she has ridden an \umbra{} countless times. 
But she still remembers the fear of them and knows to be careful. 
Many younger \resphain{} do not know this, she reflects. 
They are overconfident around \umbrae.
They do not show the terrible monsters the respect they deserve. 
They have not lived back in the days when, at any moment, an \umbra{} might swoop in from the dark sky or the dark deep and kill and eat a half-dozen \resphain. 
(Remember, \resphain{} were weaker back then.)









\subsection{Carzain heads to \Redce}
\Esmerel{} wants to flee back to \Redce{} and tries to persuade Carzain to come with her, tempting him with romises of glory and greatness if he allies himself with the Redcor. 
Also, \Esmerel{} promises him that they can help him master his \hs{\Kenosis}. 
He wants this, since in his current state he is an unstable madman and a danger to everyone. 
Also, he hopes if he allies with the Redcor, he can get his hands on \hr{Iolivine's notes}{\ps{\Iolivine} notes on Scions}, which \hr{Redcor bogarted Iolivine's notes}{the Redcor are bogarting}. 

Ilcas agrees to accompany them, because the Imetrians and Redcor want to temporarily join forces to drive back the Rissitics. Carzain agrees, partly influenced by Ilcas' decision. Curiet tags along because he is lost in the chaos of the sacking of \Forklin{} and clings to Telcastora Ilcas. 

I need to stress the fact that Carzain does not agree to serve the Redcor. He is somehow tricked and coerced into coming with them, and thus can claim to be a prisoner of sorts in the Topaz \Chateau. 

How exactly does this work?

They slip out of \Forklin{} amid the chaos and make their way north to \Redce{}. 
But their way goes past the Ghost Tower, so Carzain becomes involved in the events there. 

Remember that the Redcor should refer a lot to their scripture and their historical heroes, such as Silqua and Rebecca Redcor. 





\subsubsection{Carzain espies Morgan Runger}
On the battlefield, Carzain espies \hs{Morgan Runger} in the distance. 

\vizicar{%
  Feh. Kings who are not mages themselves are mere upstarts. Such a coward. He commands his sorcerers to work their dire magics, but dares not do it himself.}

Vizicar is quite the pro-mage nazi. 







\subsubsection{Carzain sees reapers on the battlefield}
\target{Carzain sees reapers near Forklin}
After the battle of \Forklin, Carzain sees some \quo{reapers} on the battlefield. They are \hs{Worm Cult reapers}, as well as \hr{Crows and ravens}{crow- or raven-like men}. 

They appear as unclear ghosts. They might be an apparition created in his mind from the fog, smoke, animal and corpses. He is in doubt: \tho{Am I seeing things?}

They pick up some dead. Carzain seems to see corpses\dash or their souls\dash rise to wander, limp or crawl away into the Beyond. 

Perhaps the Worm Cult reapers fight the Ravens. 





\subsubsection{Carzain and Vizicar talk}
Carzain and Vizicar talk. 
Vizicar theorizes that it was he who \hr{Vizicar drives Carzain to war}{subconsciously imparted to Carzain a craving to fight and seek glory}, thus causing him to go off to war. 





\subsubsection{Carzain-tachi encounter a \bane}
Carzain-tachi encounter a \bane. 
Ilcas Northstar holds up an Imetric holy symbol and recites a prayer/\hs{orison} to ward off evil and keep it at bay. 
It seems to work for a moment, but then the \bane{} advances again. 





\subsubsection{Ilcas kills prisoners}
There is a scene where Telcastora Ilcas, together with some Redcor, have taken some enemies prisoner. 
These are Pelidorian soldiers who have deserted and turned into bandits. 

Ilcas is about to kill them. 

\begin{prose}
  \Racel/\Esmerel: 
  \ta{No! Stop. If you kill them, you are no better a man that they.}
  
  Ilcas: 
  \ta{What are you talking about? Fuck that!} 
  He kills the men. 
  \ta{Of course I am better than they. 
    They were not only brigand scum, they were also traitors. 
    They were paid and armed by their kingdom and entrusted to protect their people from enemies. 
    They betrayed that trust and turned against their own people. 
    They were the worst kind of filth. 
    I am doing the world a favour.}
\end{prose}

Ilcas truly hates these men's guts. 
Traitors and malfeasants are pieces of shit. 

\begin{prose}
  \Esmerel: More whining. 
  
  Ilcas: 
  \ta{We are not under the jurisdiction of Redcor law!} 
  
  \Esmerel: 
  \ta{Nor are we under Imetric law!}
  
  Ilcas: 
  \ta{Look around you. 
    Pelidor has fallen. 
    This place is \Wylde{}. 
    We are under no law. 
    When protected by no law it falls upon each of us to act on our morality as best we can. 
    I did exactly that.}
\end{prose}

Carzain stands next to Ilcas and admires the manliness. 

Maybe Ilcas concludes with something like this: 

\begin{prose}
  Ilcas: 
  \ta{%
    Maybe we \scathae{} have a more rational outlook on death and killing than you \humans{} do. 
    I don't know.}
\end{prose}

Perhaps the last part is said in private to Carzain out of earshot of the Redcor. 

Ilcas notices that during the killing, Carzain stood by and looked on with a bloodthirsty grin. 
This disturbs Ilcas. 
He had good reasons for killing them, but he did not \emph{enjoy} it. 
And now that he thinks about it, Carzain has been overfond of killing for a long time. 
He was also too proud for his own good when he told of the mercenaries he had killed in Heropond last year. 
Ilcas fears Carzain is turning into a bloodthirsty maniac. 





\subsubsection{Ilcas wants to feed his sword}
In truth, Ilcas killed the prisoners not just for the sake of punishment, but also to feed his sword. 
\Telderain{} hungers for blood and soul energy (although it does not eat entire souls; it just leaves them somewhat drained), otherwise it goes crazy and tries to drive Ilcas crazy, too.  

But he doesn't tell this to the Redcor. 
He doesn't want them to know that he wields a black magic sword filled with blood-drinking \daemons. 





\subsubsection{Later Ilcas lets a hostage die}
Later, Ilcas lets a hostage die. 
Perhaps a child, or an egg. 
He knows that sacrificing the hostage to kill the villain is preferable to letting the villain get away. 
But some of the dumbass Redcor, such as \Racel, are unwilling to see that. 





\subsubsection{Ilcas cares for his \nycans}
At some point, Ilcas Northstar endangers the rest of his companions for the sake of one of the \nycans. 

Some of the Redcor are butthurt about this.

\begin{prose}
\Esmerel: 
\ta{%
  You would endanger all of our lives for the sake of an \emph{animal}?}

Ilcas: 
\ta{\Matron, maybe I owe it to you to make our position clear. 
  Let me give you a run-down of my loyalties, in descending order of priority. 
  One: the Imetrium. 
  Two: the Telcastora clan.
  Three: my wife and children.
  Four: the \nycans.
  Five: you people.}
He looks at Curiet and jokingly adds.
\ta{Six: Serpentin.}

Curiet:
\ta{What? Why I am at the bottom?
  All of them are Vaimons! They can defend themselves. 
  I am a defenseless civilian!}

Ilcas looks at him.
\ta{Point taken. 
  Correction. 
  Five: Serpentin. 
  Six: you Vaimons.}
\end{prose}









\subsection{Needle dies}





\subsubsection{Needle finds the Sentinel lair}
Needle and her servants succeed in locating the Sentinel lair in Malcur. She begins to make preparations to storm them. 

Needle is growing ecstatic and hysterical, with the new dark powers at her command and the terrible \banes{} that follow her.

\lyricslimbonicart{Darkzone Martyrium}{
  I perish in my own desire.\\
  I burn within lusting hate.\\
  Destructively the minds inspire\\
  the soul to terminate.
  
  I ride the ancient overture\\
  as life is torn astray.\\
  I glance the illusive spectrum\\
  and all light that fades away.
  
  Black energies in the twilight space\\
  come shivering through the shallow haze.\\
  Into darkness so impure divine.\\
  A bloodshed emotion to evil wine.
}





\subsubsection[Psyrex-tachi invoke the ritual]{\Psyrex-tachi invoke the ritual}
\target{Psyrex-tachi invoke the ritual}
\Psyrex-tachi begin the sorcerous ritual that will summon and resurrect \Nithdornazsh. 

\Psyrex, the mad sorcerer, leads the ritual. 
Several other mages support him, and loads of servants stand by to perform menial tasks, such as procuring living prisoners to be sacrificed. 

They invoke mystic, forbidden names. 

\lyricsbs{Bal-Sagoth}{
  As the Vortex Illumines the Crystalline Walls of Kor-Avul-Thaa
}{
  By Klatrymadon and Zuranthus,\\
  such ancient secrets we discovered \\
  within these sinistrous, worm-worn pages,\\
  Etched with darksome glyphs and sigils, \\
  bound with fearsome spells, \\
  An eldritch tide of stygian sorceries \\
  unfettered by the forbidden Tome of Shadows...
  
  Now thunderous cataclysm befalls the gleaming Kor-Avul-Thaa \\
  (The mystic gate stands open!) \\
  The Xytaxehedron held to the stars... \\
  the incantation uttered with eager tongues... 
}

\ps{\Ishnaruchaefir} is one of the names. 

\lyricsbalsagoth{Invocations Beyond the Outer-World Night}{
  Invocations and ideograms (dreams of the Xytaxehedron?),\\
  Conjuration of the inner world's (tenebrous) denizens,\\
  And their star-spanning progenitors, \\
  spawned beyond the outer-world night.
}

They invoke Chaos. 

\lyricsbs{Arcane Wisdom}{Symphonia Chaos}{
  Chaos, ruler of Time. \\
  Chaos, infinity is Thine. \\
  Shadowy inner essence, \\
  cosmic tapestry and sparkling \\
  spheres of a circular reason. \\
  Chaos, ruler of Time. \\
  Chaos, infinity is Thine. 
}

\lyricsbs{Emperor}{Moon Over Kara-Shehr}{
  Our time is upon us. \\
  Master! Appear! \\
  Over the nocturnal sky \\
  from the mountains of black we ride. \\
  Fly! 
  
  All thy servants fly \\
  though the serpent's darkened sky. \\
  Hears the opponent cry, \\
  ravaged by his terror. 
  
  Master! We ride with the storm \\
  in his name, the sire, wolves' king.\\ 
  Enter the power coursing \\
  through veins of the night. 
  
  Who gathers winds, summons thunder, \\
  summons rain, summons might?
}

Describe how \pdaemons{} fly screaming through the sky and blood boils up through the ground. 

\lyricsbs{Bal-Sagoth}{
  Dreaming of Atlantean Spires
}{
  The sky is black with Chaos-fiends,\\
  spellcraft rides the witch-storm's wings.\\
  Beneath the vaults of time-lost tombs\\
  sorcerers summon the shadow-kings.\\
  The Topaz Throne is beckoning,\\
  the jewelled sword awaits my grasp.\\
  The dreaming gods now grimly brood\\
  in the silence of Atlantean Spires.
}

Also, describe the mages' awe and fear as they invoke the names of gods, and then see those gods actually appear!

\lyricsbs{Bal-Sagoth}{
  As the Vortex Illumines the Crystalline Walls of Kor-Avul-Thaa
}{
  What long-shackled powers of the elder dark have our conjurings loosed?
  
  By Klatrymadon and Zuranthus, \\
  the vortex blackens the stars above,\\
  A vast plague of amorphous horrors \\
  descends to rend with fang and talon,\\
  (As with torrents of blood the crystalline walls run red?)\\
  And in the glooming chambers of our shadowed sanctum, \\
  we wait, half-mad with terror,\\
  To reap the slaughterous harvest which we have sown...
  
  [The Chronicler of the Cataclysm:]\\
  And beyond the vortex, the churning black waters of the void did disgorge the Dwellers in Eternal Shadow. \\
  And upon a horde of winged horrors, brandishing swords of ebon flame, they rode out from the Gate... \\
  And a terrible silence fell upon Kor-Avul-Thaa...
  
  [The Echoes of the Oracle:]\\
  The sky rent asunder, \\
  black winged devils surge forth from the void...\\
  A maelstrom of crimson fire burns above us... \\
  what carnage has thou wrought?
  
  By Klatrymadon and Zuranthus, \\
  in Kor-Avul-Thaa, darkness reigns eternal...\\
  Nevermore shall the city glimmer, \\
  for now the crystalline walls gleam black...\\
  Ever black...
}





\subsubsection{Rian and \Cornel{} kill Needle}
\target{Needle dies}
Near the end of the story, Needle has managed to sniff out that \Tiroco{} is working for the Sentinels, and she is tracking her moves. 
Needle has her Cabalists poised to break in and interrupt the Sentinel ritual\dash which would FUBAR \ps{\Secherdamon} plans. 

\Psyrex{} suspects the raid and is trying hard to pin it down, but failing. 
Needle is not stupid. 

But Rian and \Cornel{} are onto Needle. 
Before Needle can launch her final raid, they strike against her. 
\Cornel{} keeps her (few) defenders (mortal or supernatural?) at bay. 
Rian distracts Needle and her companions by throwing knives at them (he has acquired skill in knife-throwing in his thieving days). 
Then Moro goes in and kills Needle. 

Remember that Rian needs to put his carpentry skills to use! 





\subsubsection{Needle calls to \Achsah{} for help}
Before she falls, Needle contacts \Achsah{} and begs for help. 
But \Achsah{} is at the Ghost Tower with more important matters to attend to\dash or so she thinks. 





\subsubsection{Rian is going mad}
Rian is slowly being driven mad by the things he has witnessed. 

\lyricslimbonicart{The Yawning Abyss of Madness}{
  Behind the sealed door to imagination \\
  I sense the voices of devastation. \\
  Dementia praecox. 
  
  A cascade of dark emotions. \\
  An ominous silence imprisons me\\
  with disfigured landscapes.
}





\subsubsection{They sneak up on Needle}
Rian and Moro sneak into the place where Needle is. 
They are afraid of the dark powers around them\dash the \banes{} worst of all. 
They feel the darkness and evil surrounding them, like a palpable force. 

\lyricslimbonicart{A Demonoid Virtue}{
  The night has predatorial eyes,\\
  drifting in a plae of disguise.\\
  Beneath the spelling moon\\
  the spirit rises out of darkness.\\
  The spirit rises...
  
  Voices call for my soul.
}





\subsubsection{Why do you do this?}
Before Needle dies, Rian asks her: 
\ta{Why do you do this?}

Needle: 
\ta{For survival. 
  For the future of my people. 
  \emph{Our} people, damn you! 
  For \human kind's survival!}

Just before she dies, Needle's last thoughts are: 
\tho{Great \resphain.
  \Achsah.
  \Teshrial.
  Etc.
  Forgive me for failing you. 
  But I have loved you and served you with all my being.
  Truly I have. 
  
  I have no regrets.
  
  No.
  That's not true. 
  There is something I regret.
  I regret...}

And then she dies. 
We never get to hear what she regrets. 





\subsubsection{A \bane{} hunts them}
One of \hr{Needle summons \banes}{the three \banes{} that Needle summoned} comes after Moro and Rian. It is too powerful for them to kill, but Moro has enough magic to be able to hold it at bay and give them time to escape. 

Moro uses the spell \word{\hs{khestni}}. 
It hurts the \bane, but does not kill it. 

Whenever Moro draws deep of her terrible magic, she fears that perverse powers might gain control of her. 

\lyricslimbonicart{A Demonoid Virtue}{
  Voices call for my soul.
  
  The cunning serpents kiss I taste.\\
  Baptised beside the ancient takes of\\
  fire, fire burning higher.\\
  Unite with me in dark desires.\\
  I perish in bliss of cruelty.\\
  Tormented souls will never rest in peace.
}

But time and time again she must risk it\dash such as when fending off the \bane. 

\lyricslimbonicart{A Demonoid Virtue}{
  In the flames an omen blaze,\\
  enforcing throught the cosmic haze.\\
  To cross the line and dare to glance,\\
  and enter cold void where death romances\\
  in mysteries.
}

After some time, it stops pursuing and goes after more important targets. Moro is relieved, because she was at her limit and could not hold it off much longer. 









\subsection[Psyrex wins]{\Psyrex{} wins}





\subsubsection{\Paerzim{} killed by \Psyrex}
\target{Psyrex kills Paerzim}
After \hr{\Achsah{} calls for help}{\Achsah{} has summoned everyone to \Forklin}, only one measly \resphan{}, \Paerzim, remains in Malcur. 
Needle is \ps{\Paerzim} second-in-command. 

\Paerzim{} is competent enough to give \Psyrex{} trouble. 

But then Needle is killed by Moro and Rian. 
This means \Paerzim{} has to take an active role in everything and divert his attention around. 
This is just what \Psyrex{} needs. 
He is now able to outmanoeuvre \Paerzim{} and kill him. 

Now the Cabal in Malcur is all but destroyed, and the way for \Psyrex-tachi is opened. 
\Achsah-tachi are busy in \Forklin. 
\Teshrial{} is busy with his duel. 
None of them are in a position to come back and stop \Psyrex. 
He can freely complete his summoning ritual. 
\Nithdornazsh{} will rise. 





\subsubsection{The Cabal are thwarted}
With Needle dead, the Cabal raid is thrown into disarray. 
\Psyrex{} finds their trail and figures out their moves. 
When the Cabalists finally get their act together, \Psyrex{} has his men and magic prepared for them. 
The Cabalists fight bravely and sneakily, but \Psyrex{} just manages to stitch together enough makeshift defenses to fend them off. 

\Achsah, who might be able to put a stop to the Sentinels' dastardly plan, is up near the Ghost Tower. \ps{\Secherdamon} clever plan is working. 

Just before all Hell breaks loose\dash literally!\dash\Psyrex{} appears before Rian and Moro. He congratulates them for their hard work and their success, and thanks them for the help. If not for them, he says, Needle-tachi would have taken him by surprise, he and his companions would have been slain and their gambit would have crumbled. 

%Do Rian and Moro die? I think Rian at least dies. Moro is cool enough that she might escape, but she might also die. If she dies, I might want to portray her as a bitchy Aes Sedai who bullies Rian, so the reader is not sad to see her die. 

%I need to portray Rian as semi-cool but not so cool that the audience will be outraged when I kill him. And I need to be very sure that \Psyrex{} is portrayed as kickass, so people will like it when he wins. 





\subsubsection{\Tiroco{} feels the end is near}
\Tiroco{} feels the end is near. 

\lyricsbs{Marduk}{Cold Mouth Prayer}{
  Quickened lumps of Earth,\\
  A feast for fowls and greedy worms.\\
  Count your sins, the Snakes within.\\
  An eyeless leap into the Bosom of Decay.\\
  Cold Mouth prayer.\\
  Cold Mouth prayer.
  
  A flash, a minute, a winter's dust.\\
  A choir of fingers sings of putrefaction.\\
  Cold Mouth Prayer. Cold Mouth Prayer.\\
  A smile left to rot in the Sun of Despair.
}









\subsection{Rian finds Neina}
\subsubsection{Rian and Moro explore the catacombs}
Rian and Moro \Cornel{} explore the dismal catacombs beneath Malcur. 
They encounter monstrous creatures that infest the crypt. 
(These creatures do not necessarily serve anyone. They can just be degenerate mutants who have taken up residence in the old crypt.) 
They fight some of them and flee from more. 

They find hints of cults worshipping forbidden powers. And hints of the crypts' dark origins. Moro understands these, while Rian struggles to understand Moro. 

Moro should swear and curse by the forbidden names of the \xss.

\lyricsbalsagoth{The Obsidian Crown Unbound}{
  [The Sorcerer:]\\
  By Klatrymadon and Zuranthus!\\
  They come!
}

At the end of their search \hs{they find Neina}.




\subsubsection{Rian finds Neina and escapes}
\target{they find Neina}
%At the last minute, however, they manage to escape. 
Rian finds Neina and they run away together. 

The sight of the two together, their love and happiness at being finally reunited, reaches Moro's heart, and she is both touched and envious. It softens her a little bit, and she gains a bit of hope for the future and the world.





\subsubsection{Neina's story}
\target{Neina's story}
Neina was supposed to have been killed a while ago. But some of the Sentinel-hired thugs screwed up, and she was left to rot in a dungeon for many weeks. 

A few times she was dragged to a ritual to be sacrificed, but then not sacrificed anyway and returned to the dungeon. 
\ps{\Psyrex}{} thugs are not the most organized people in the world. 

When Rian comes to rescue her, she is half-mad and hysterical, babbling about monsters and black magic. She is quite useless. 





\subsubsection{Rian and Moro almost eaten by living house}
\target{Rian and Neina are separated from Moro}
Rian, Neina and Moro huddle inside a house. Then suddenly the Shroud opens up and the house reveals itself as a monstrous living entity. It makes a grab for them with its claws or tentacles, intending to devour them. 

Compare to a scene in the anime \cite[episode 1]{Anime:IczerOne}, where a house comes alive.

They escape, but in the chaos, Rian and Neina get separated from Moro. Now the young lovers are in deep shit, because it was Moro's skill and sorcery that was keeping them alive.

Rian develops a nasty case of claustrophobia after being almost eaten by a living house, having seen the walls literally close in around him and turn into monstrous mouths. 















\section{\Nithdornazsh{} Rising}







\subsection{Battle for the Ghost Tower}
The Sentinels and Cabal battle for control of the Ghost Tower. 

Note that \hr{Immortals inside the Shroud}{the Shroud suppresses the immortals' powers}. 
I need to deal with that somehow. 

Remember to read about \hs{\dragons}, \hs{\resphain} and \hs{\umbrae} before writing this! 





\subsubsection{\Nzessuacrith{} in \draconic{} form}
\Nzessuacrith{} has finally been forced to leave the body of \Takestsha{} and assume her true, \draconic{} form and enter the fray. 

\Nzessuacrith{} wears \hs{ward runes}. 
(Remember to read about \hs{ward runes}.)

Before entering combat, \Nzessuacrith{} casts a spell that makes her natural weapons poisonous. 

Read about \hs{\Nzessuacrith}, \hs{\Achsah}, \hs{\dragons}, \hs{\resphain} and \hs{\umbrae} before writing this section. 
And read some RPG books for inspiration on spells and weapons and magical items they might use. 

\Nzessuacrith{} is surprised that she is able to take \draconic{} form so deep in the Shroud. 
She speculates that it might be due to the destabilizing influence of \Nithdornazsh{} and/or the Ghost Tower and the \EreshKali{} magic, all of which might locally and temporarily weaken the Shroud. 
But is she not quite convinced by this explanation. 
She fears the Shroud is \hs{unravelling}. 

\begin{prose}
  \tho{The barriers between the Realms are breakdown down.
    The great cosmic Seals are leaking.
    Like water seeping through holes in a rotted dam.
    What happens if\dash when\dash the river breaks through?
    A \thirdbanewar? 
    Can \Miith{} survive a \thirdbanewar?
    
    And what is causing it?
    Is it the weakening of the Heart?
    The conflict of the \matrices?
    What?}
\end{prose}

Have some mortals who are stricken with terror and awe at the sight of the \dragon{}. 
Perhaps Carzain and his party. 
They have heard \hs{myths} of \dragons, but their true power and majesty is downplayed in the Iquinian myths. 
The sight of an actual \dragon{} blows away all the myths and faerie tales. 

Delph dies in this final, climactic battle. 
But his rat lives.

Carzain sees the \hs{\umbrae} that \Achsah-tachi summon. 
He likens them to bats, but \hr{Umbra like bat}{different}. 
They also \hr{Umbra sounds}{hear the \umbrae{} howl}. 






\subsubsection{\Achsah{} meets the challenge}
The sight of \ps{\Nzessuacrith}{} unmasked has drawn \Achsah{} $100\%$ from Malcur to the Ghost Tower. 
Charcoal's plan\dash aided by Carzain\dash has bought the Sentinels enough time to call in reinforcements and ultimately fight off the Sentinels. 

We see \Achsah{} at the Tower. 
Perhaps she is riding a terrible but splendid monstrous steed.

\lyricsbalsagoth{When Rides the Scion of the Storms}{
  I see him... \\
  grim and noble astride his great winged steed, \\
  gleaming spear crackling in his grasp, \\
  beckoning me onwards to the next life... \\
  to ever more slaughter and carnage... \\
  Yes, adour and brooding spirit he is, \\
  and in his burning eyes I see \\
  a great secret which I must discover,\\ 
  a powerful mystery I alone must solve.
}

Does she actually wield a spear?

\Achsah{} mocks \Nzessuacrith{}: 
\ta{I had expected more. I had feared I would be facing Quessanth \Ishnaruchaefir.} 

\Nzessuacrith{} mocks \Achsah{} in turn: 
\ta{I had expected a \ketheran. 
Not some pathetic half-\human{} scum. 
Without the stolen \draconic{} blood you \resphain{} are worthless. 
You, \Achsah, are nothing but a swarthy \human{} with delusions of grandeur.} 

\Achsah: \ta{A \human, am I? We will see about that.}

They fight. 
Then, a bit later: 

\Achsah: 
\ta{If you did your research, \Nzessuacrith, you would know that I am of \Merkyrah, and as such not not half \human{} but half \nephil.} 

\Nzessuacrith: 
\ta{Hah! 
Feebly trying to defend the last shreds of your dignity? 
Very well, I take back my last insult. 
You, \Achsah{}, are nothing but a pathetic, swarthy \nephil{} with delusions of grandeur.} 

Notice that \Nzessuacrith{} is proven right. 
\Achsah{} is soundly beaten and only prevails when Ramiel, a \sathariah, shows up to help her. 





\subsubsection{They battle}
Enter a great battle between \Nzessuacrith{} and \Achsah. 
This battle is long, hard, bloody, brutal and dirty. 

\Achsah{} draws up her full power, which is considerable. 
What she lacks of inborn gifts she makes up for in age and experience. 

\lyricslimbonicart{Beyond the Candles Burning}{
  I am a dark star rising on the raveous bleaky sky,\\
  a black diamond slunning so deep within the night.\\
  Maliciously I dwell in a bluish shaded beam\\
  with a stonecold heart into the core of my being.
}

Perhaps they fight in humanoid form first before going into their monstrous forms. 

\Achsah{} summons a bat- or Balrog-like monster to ride. 
This might or might not be an \hs{\umbra}. 
Compare to the monster that Durza summons in the movie \cite{Movie:Eragon} (not present in the book \cite{ChristopherPaolini:Eragon}). 

Describe the awesome forces of magic unleashed.

\lyricsbalsagoth{The Obsidian Crown Unbound}{
  And even as this transpired, the Emperor's Prime Sorcerer, emissary of the Imperial Court and master of those arts which speak to man in narcotic dreams from the darkest and most silent places, summoned forth that black potency which lay entwined in stygian tendrils within his mind... an ireful power born of they who writhed upon the shores of Pangaea before man's progenitors ever erected their lofty spires to the restless skies.\\
  And yet Vyrgothia's Master Wizard, unrivalled Arch-Mage and adept of that lost Eastern order who journey beyond the boundaries of time and space upon those nebulous wings born of the sacred Azure Lotus, rose to meet this power which lapped at the periphery of his mind like a midnight tide, and stood firm against its insistent siren call.\\
  And upon that arid field of war, the sentinels of light and shadow spoke to each other in tongues dormant since the Third Moon fell burning from the heavens, and not sweet were the words they uttered.
}

\Nzessuacrith{} is weakened, but still a badass motherfucker. 
She kills more than one \resphan{} (but not permanently). 

\Nzessuacrith{} does \emph{not} use the spell \word{\hs{khestni}}. 
She has nastier weapons at her disposal. 

\Nzessuacrith{} uses magic to enhance all of her moves. 
She growls words to power to punctuate every attack or parade. 
Unlike \Ishnaruchaefir. 





\subsubsection{An \umbra{} escapes}
An \umbra{} escapes from the battlefield after its handler is killed. 
\Achsah{} reflects that it will probably go into the \Wylde{} and live off whatever mortals it can catch. 

There it will live out the rest of its days. 

The rest of its days... how much is that? 
Are \umbrae{} immortal? 
\Achsah{} does not know. 

And do they reproduce in the \Wylde{}?
How do they reproduce? 
Do they reproduce at all? 
\Achsah{} does not know. 

The \banelords{} probably know, she reflects. 
But she has never been in a position to ask a \banelord{} a question. 
And she would not dare even if she could. 
She is not too proud to admit that the \banelords{} make her shit herself with fear. 
She remembered feeling their evil presence during the Incursion. 
And the presence of the dreaded \Voidbringer. 
The fear has not decreased in her memory, even after all these millennia. 
She still remembers it vividly. 

That is another thing the young \resphain{} do not understand. 
They do not fear the \banes{} as they should. 
The mortals have the right idea here, she thinks. 
Many mortals see their gods as terribly frightening, alien powers around which one must tread very carefully.

\begin{prose}
  \tho{We \resphain{} could learn from that.
    We like to think of ourselves as being on top of that ladder of power.
    But we are not.
    There are things out there far older, far darker and far more powerful than we.}
\end{prose}





\subsubsection{Ramiel adds his power to the ritual}
\target{Ramiel scares Nzessuacrith}
\Nzessuacrith{} could defeat the \resphan, but \hyperref[Charcoal at the Ghost Tower]{Charcoal's spell antagonizes her}, and ultimately she loses and must retreat.

Now, Charcoal's magic alone would not be sufficient to make any difference, since \Nzessuacrith{} is a powerful \dragon. But Carzain/Vizicar is there. The \nieur{} ritual that Charcoal unleashes somehow causes the \sathariah{} within Carzain to stir and awaken a little bit. Acting instinctively, Ramiel adds his power to the ritual. 

Perhaps Ramiel senses that \Nzessuacrith{} is family. She is, after all, kin to \Nexagglachel, the sire of the \satharioth. 

Now, Ramiel doesn't have much power available. 
He is still in deep sleep. 
But he makes his \emph{presence} known. 
\Nzessuacrith{} feels the smell of a \sathariah, and it distracts and alarms her. 
She had not counted on the innocuous Scion being a \sathariah. 
It throws her off balance for a moment, and this is enough for \Achsah-tachi to wound her and drive her off. 





\subsubsection{Conclusion}
At the end of the day, the Tower is in Cabalist hands. 

The battle has wrought destruction of Godzilla-like proportions to the surrounding countryside. The Tower itself is untouched, because it is built with the technology of the ancients. \Forklin{} is laid in ruins, except for the castle and certain walls and towers, who are superhuman. 

\Nzessuacrith{} (\hr{\Nzessuacrith{} likes beauty}{who likes beautiful things}) mourns the devastation wrought on the beautiful \Forklin. 

Now \Achsah{} and \Nzessuacrith{} know who Carzain is\dash to an extent, at least.
\Achsah{} is $100\%$ sure the \vertex{} is a \sathariah{} aligned with the \hs{Midnight Bat}. 
Which means it must be a Scion. 
Which means there are only two possibilities. 
She reports this to \Azraid, who \hr{\Azraid{} learns of spike}{muses about it}. 

\Nzessuacrith{} and \Ishnaruchaefir{} are less certain about this. 
They have not studied the \vertex{} (or the theory of \malachim) as much as \Achsah{} has. 

Some of the Cabalists muse over how they underestimated Charcoal. They believed to have him figured out, but he still managed to thwart their plans. 

But in Malcur...









\subsection{\Teshrial{} and \Ishnaruchaefir}
\target{Ishnaruchaefir kills Teshrial}
\Ishnaruchaefir{} has taken \ps{\Teshrial} \quo{bait}. 
He arrives in the dead garden in answer to the challenge. 

\Teshrial{} has several trump cards:
\begin{itemize}
  \item The Shroud.
  \item Astrology. 
  \item \Ghobaleth.
  \item The Achilles' heel. 
\end{itemize}
    
Remember that \Teshrial{} walks the \hs{Path of Ice}. 

\Ishnaruchaefir{} uses the spell \word{\hs{khestni}} once during the fight. 
It hurts \Teshrial, but does not kill him. 

\Ishnaruchaefir{} wears \hs{ward runes}. 
(Remember to read about \hs{ward runes}.)

Remember to read about \hs{\dragons}, \hs{\resphain}, \hs{\Teshrial} and \hr{Ishnaruchaefir}{\Ishnaruchaefir} before writing this!





\subsubsection{\Menessiaraid{} looks on}
\Teshrial{} brings one spectator to the fight: 
His good friend \Menessiaraid. 

He only brings one spectator. 
Otherwise he fears \Ishnaruchaefir, suspecting an ambush, would refuse to fight. 
On the other hand, they both knew they could not fight in private. 
Rumours of this fight have been going all over the place among the dynasties. 
They would need to have \emph{someone} there to witness it. 

So \Menessiaraid{} is there alone, and he does not fight. 
He is a skilled telepath, and his head is crowded full of powerful \resphain{} who want to see the fight through his eyes. 

This means there are fewer \resphain{} left to keep an eye on \Forklin{} and Malcur. 
Which is exactly what \Ishnaruchaefir{} and \Secherdamon{} want. 





\subsubsection{\ps{\Teshrial} perspective}
The battle should be seen from \ps{\Teshrial} perspective. 
He tries every means at his disposal to defeat \Ishnaruchaefir, and more than once he thinks he has succeeded, but \Ishnaruchaefir{} keeps getting back up. 
Describe \ps{\Teshrial} anguish when he dies. 





\subsubsection{They fight in humanoid form}
\Ishnaruchaefir{} arrives. 
He does not carry his glaive, \Rystessakhin, but only a pair of \skekrathuins. 

They meet in a fairly tightly Shrouded layer of the Realm. 
They are forced to fight wearing \quo{\hs{Masks}}. 
This means that \Teshrial{} has something of an upper hand. 
He is \hr{Immortals inside the Shroud}{not as weakened as \Ishnaruchaefir{} is by the Shroud}. 

First they fight in humanoid form. 
\Teshrial{} challenges \Ishnaruchaefir{} to come down and face him in humanoid form. 
\Ishnaruchaefir{} accepts. 

\Teshrial{} is comparatively young and inexperienced. 
He has never seen \Ishnaruchaefir{} in combat before and underestimates him. 
He mocks \Ishnaruchaefir, calling him a decayed, outdated relic of the far past. 
He believes he can outmanoeuvre the old, bitter, set-in-his-ways \shaeeroth.
He underestimates him. 
Otherwise, \Teshrial{} would have realized how fucked he was, and would have fled. 

Even so, the battle is non-trivial, even for \Ishnaruchaefir. 

They duke it out. 
\Teshrial{} loses. 

At the beginning of the fight \Ishnaruchaefir{} is cool and calm. 
He keeps up this \facade{} as long as he is fighting in humanoid form. 
But when he reverts to \draconian{} form to battle the \ghobaleth{}, and later Mutant-\Teshrial, he lets loose all his \draconian{} fury and lets his hatred against the \resphain{} guide him. 

\Ishnaruchaefir{} does not use so much magic. 
His physical prowess in humanoid form is enough to defeat \Teshrial{}. 
His body is wicked-psycho-tough and durable on its own. 
It is part of his tactic to rely on physical strength as long as possible, thus conserving his magical reserves for when he really needs them. 
He doesn't go all-out magic until mutant-\Teshrial{} shows up. 





\subsubsection{\Ghobaleth}
\Teshrial{} is losing. 
So he pulls out one of his trump cards: 
He summons his \ghobaleth. 

\Ishnaruchaefir{} fights them. 
\Teshrial{} stands back and supports them with spells. 

Have a description of the monsters that swarm out to attack \Ishna. 

\lyricsbs{Bal-Sagoth}{
  As the Vortex Illumines the Crystalline Walls of Kor-Avul-Thaa
}{
  The sky rent asunder. \\
  Black-winged devils surge forth from the void.\\
  A maelstrom of crimson fire burns above us.\\
  What carnage hast thou wrought?
  
  And beyond the Vortex, the churning black waters of the Void did disgorge the Dwellers in Eternal Shadow.\\ 
  And upon a horde of winged horrors, brandishing swords of ebon flame, they rode out from the gate. \\
  And a terible silence fell upon Kor-Avul-Thaa.
}

\Teshrial{} has been fooled into believing that his \ghobaleth{} are a secret trap which \Ishnaruchaefir{} doesn't suspect. 
He keeps them hidden and only summons them in the last minute when he really needs them. 
But unbeknownst to him, \Ishnaruchaefir{} has predicted this move. 
And the fight has been planned so it coincides with \Psyrex-tachi's summoning of \Nithdornazsh. 
This means that the \ghobaleth{} are disoriented and weakened and slow to answer \ps{\Teshrial} call. 
This gives \Ishnaruchaefir{} plenty of time to prepare for them and pick them off one by one when they arrive. 
They cannot lie in wait and ambush him as \Teshrial{} wanted them to. 

\Ishnaruchaefir{} assumes his true, \draconian{} form to fight them. 
Insert an epic description of the mighty \dragon{} here, a la \bandsong{Bal-Sagoth}{Black Dragons Soar Above the Mountain of Shadows}. 

\Teshrial{}, desperately intent on vanquishing \Ishnaruchaefir{}, summons reinforcements, bleeding the city dry of Cabal monsters. 
This is what \Ishnaruchaefir{} wants, because it leaves Malcur vulnerable to \ps{\Psyrex}{} spell. 

When \Ishnaruchaefir{} fights, he has bound \daemons{} that whirl around his body and act as armour and weapons. 
They are black, gray, white, purple and blood red. 
Compare to the battle between Fulgrim and Ferrus Manus in \authorbook{Graham McNeill}{Fulgrim}. 





\subsubsection{\Teshrial{} mutates}
The \ghobaleth{} are vanquished. 

\Teshrial{} now uses his last resort: With an experimental spell he absorbs his servant monsters into himself and merges with them, thus mutating into a colossal monster. The spell is dangerous and quite likely irreversible\dash it might drive him mad, prevent him from changing back and dooming him to spend the rest of his life as an insane abomination. 

We see \Teshrial{} from the inside. He knows the danger and fears it, but he is consumed by his eagerness to slay the mythical \Ishnaruchaefir{} and prove his worth, so he can advance in the hierarchy of the \ketherain. 

The mutation thing is the only one of \ps{\Teshrial} traps which \Ishnaruchaefir{} failed to anticipate. 
It startles him and throws him off balance for a moment. 

\Teshrial{} suggets that they drop their \quo{\hr{Masks}{masquerade}}. 
This surprises \Ishnaruchaefir{}. 
It is rare for a \resphan{} to be the first to suggest to \quo{drop the masquerade}. 

The mutation takes time. 
But \Ishnaruchaefir{} does not take advantage of this. 
He politely stands back and gives \Teshrial{} time and room to transform. 
He is curious and wants to see this new weapon in action and test its mettle against his own. 
Knowledge is power, and he is willing to take even foolish chances to gain knowledge. 
He knows that if he has underestimated \Teshrial, he may well perish. 
But he chances it. 

\Teshrial{} mutates. 
He resembles Spawn from \cite{ToddMcFarlane:Spawn}, or a Xenomorph from \cite{Movie:Alien}, or the woman on the cover of \cite{HourofPenance:TheVileConception}, or Venom from \cite{StanLeeSteveDitko:SpiderMan}. 

\lyricslimbonicart{Beyond the Candles Burning}{
  I am a dark star rising on the raveous bleaky sky,\\
  a black diamond slunning so deep within the night.
  Maliciously I dwell in a bluish shaded beam\\
  with a stonecold heart into the core of my being.
  
  Beyond the candles burning, beyond all minds eye.\\
  A vast emperic enigma awaits me as I die.\\
  In a graceful dance obscene, in a ring of fire,\\
  I obtain my majesty as flames caressing higher.
  
  Release my spirit, unleash my soul.\\
  From the darkest dungeon, oblivion calls.\\
  In the phallic halls of ancient forlorn\\
  a cold sanctuary in doom is born.
}

\lyricslimbonicart{Solace of the Shadows}{
  I require the solace of the shadows,\\
  so the night can be redeemed.\\
  As the winds of darkness whispers my name,\\
  a kiss of death I receive.
  Nocturnal enchanter, to thine art I yield.\\
  Within the candlelight a rapture is now revealed.
}

In his \neoresphan{} form, \Teshrial{} gains \hs{increased vampire powers}. 
(\hr{Resphan vampirism}{\Resphain{} are vampiric}, remember.) 
He can now drain \ps{\Ishnaruchaefir} life force even from a distance. 
\Ishnaruchaefir{} realizes this and becomes more careful. 
He figures out that \Teshrial{} now also stands a better chance of absorbing his soul if he should win. 

\Ishnaruchaefir{} realizes that \Teshrial{} \quo{knows} about his Achilles' heel. 
So he pretends to fear this and makes certain to guard the Achilles' heel, to goad \Teshrial{} on. 

\Teshrial{} fights bravely and savagely. 
A battle of Godzilla-like proportions ensues. 
Perhaps \ps{\Teshrial} mutated form resembles the monster Orga from the movie \cite{Movie:Godzilla2000}. 

\target{Ishnaruchaefir impaled by spines}
\Ishnaruchaefir{} has his body impaled by two or three huge spear-like spines. 
One of his hearts is impaled, but \hyperref[Dragons have three hearts]{\dragons{} have three hearts}, so he can bear it. 

He can fight on fine despite the pain. 
But he doesn't play stoic. 
He growls and pants with pain of his many wounds. 
\Teshrial{} thinks he is finished, so he gets overconfident. 
He steps closer to finish off \Ishnaruchaefir{} and consume his soul to gain his power (he knows he can, with his increased vampire powers). 

\tho{%
  This will make me as great as a \sathariah. 
  Nay, greater!
  With this power I will be greater than even \Azraid!
  All glory will be mine!
  All \resviel{} will be mine!}

But this was what \Ishnaruchaefir{} wanted him to do. 
He is not dead, and now he leaps up and kills \Teshrial. 





\subsubsection{\Teshrial{} dies}
As \Teshrial{} dies, just before eating his soul \Ishnaruchaefir{} whispers in his ear: 
\ta{It was all a lie. Those myths were something I planted.}

Have a sad scene from \ps{\Teshrial} POV as he dies. 
He thinks of his beloved, of \hr{\ps{\Teshrial} date}{the amazing sex she promised him} and of the life they could have had together. 

Then \Ishnaruchaefir{} heads off to Malcur.









\subsection{\Nithdornazsh{} rises}
\target{Nith'dornazsh rises}
With Needle killed and with \Achsah{} and all other high-up Cabalists fighting for the Ghost Tower, there is no one to stop \Psyrex{} and his Malcurian Sentinels.
They successfully invoke their ritual. \Nithdornazsh{} rises into the world of \Miith{}, tearing the Shroud apart around it, and the city with it. \Secherdamon{} comes to claim his prize. 

The city is made of living flesh and metal. It gorges itself on the bodies of the inhabitants of Malcur, adding their flesh to its own monstrous body. Perhaps some modicum of their consciousness remains, leaving them to bleed and moan while imprisoned as part of the city walls. 

In fact, \Nithdornazsh{} is dead, and it is resurrected by absorbing the flesh and souls of the people of Malcur. It is born of Malcur and devours its own mother. Remember to have lots of horror about this. Perhaps witnessed by Moro \Cornel, who escapes at the end. 

During the resurrection ceremony, the people of Malcur are seized by a madness. The more susceptible among them become insane mutants who run amok, hunting down other people and eating their flesh. 

A witch-storm rips the sky. \Pdaemons{} and \dragon-spawn fly on the winds, raining down terror from above. 

Have a scene with some normal \Malcuric{} citizen or citizens. Possibly Rian. He runs through the city, literally seeing Hell erupt around him. The stones and the very earth become alive underneath him, coming up to swallow him. 

Hordes of warriors and \pdaemons{} swarm out of thin air\dash out of the Beyond, which is no longer Beyond, but right here! They rampage through the city, slaughtering and enslaving the people. 

\lyricsdimmuborgir{Architecture of a Genocidal Nature}{
  Emerged from the depths of the Earth, gasps.\\
  It rages against mankind, to annihilate the Earth and worse.\\
  It spills the blood like rain. The beauty of Death it represents.
}





\subsubsection{\Malcuric{} bullies die}
Have a scene with some \Malcuric{} thugs mugging a poor guy and being mean to animals. Then the \daemons{} come and give them a horrible, painful death, absorbing their souls into even more torment. 

The victim and animal run away and survive. 

Compare to the anime \cite[episode 6]{Anime:TokyoMajin} and \cite{Anime:ElfenLied}. 





\subsubsection{Comparison with Carcosa}
The following scenes from \cite{RPG:CallofCthulhu:GreatOldOnes}, a supplement to the RPG \cite{RPG:CallofCthulhu}, may give an idea of the atmosphere I want to evoke. 

\lyricstitle{\emph{The Great Old Ones} p.70-72}{
  [The prisoner of Carcosa] is free to do anything while awaiting rescue or madness in dark Carcosa. The alienness of this city of towering black buildings costs 1/1D10 SAN per day. 
  Fill the prisoner's time in the city with odd occurences:
  
  \begin{itemize}
    \item 
      a keening voice wailing a lonely dirge, the source of which can never be found;
    \item 
      intermittent wingbeats of great unseen things in the thick clouds overhead; 
    \item 
      a slithering wave of fog which tirelessly pursues the prisoner through the damp empty streets;
    \item 
      occasional footsteps or whispering voices in the streets of the abandoned city;
    \item 
      a glimpse of a shadowy figure down the street, where no one can be found;
    \item 
      nigthmarish splashing in the waters of the lake;
    \item 
      noises whose sources elude vision because of the thich fog;
    \item 
      a glowing Yellow Sign in the waters of the lake. 
  \end{itemize}
  
  [...]
  
  As the cultists chant the ritual, thick waves of fog roll in from the lake, then the lake itself swells and grows larger, and the water takes on an oily sheen. 
  The ground gently quakes and stretches. 
  Suddenly the investigators find themselves standing on the outskirts of an alien city, at the edge of a lake much larger than the one they had been observing. 
  The swamp has vanished. 
  The night sky is dull white, and in it black stars shine in unfamiliar patterns. 
}





\subsubsection{\Secherdamon{} rejoices}
\Secherdamon{} rejoices at the fruition of his grand plan. 

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  This red charnel pit of primal horror, \\
  howling black ecstasies to the void.
  Ancient and divine, older than the hidden Icosahedron, \\
  now rebirthed beyond the chaosphere.\\
  Rise... rise and destroy!
  
  Hatred, carnage, slaughter, havoc, chaos, murder!\\
  I am become the devourer of all life!
  
  Phobos, Deimos! \\
  The moons' rays liquefied in these blood red pyramids.\\
  In the shrines of abomination, black tongues rapt with blasphemy.\\
  Chaosphere, watchtowers, genesis, Cydonia...\\
  The Abyss yawns wide!\\
  Spirit of the carrion-thronged battlefield, open wide thy gate!
}

Monstrous \daemons{} who worship \Secherdamon{} appear and attack.

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  Unruly evil!\\
  Colossal shapes etched against the moons, \\
  supine obeisance 'fore the mound. \\
  Accursed fiends hail the Slitherer, \\
  abhorrent jaws drooling lunacy.
}

\Secherdamon{} himself manifests as a ghost-like avatar. 

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  The Abyss yawns wide... Claws sharpened on the dead.\\
  The Abyss yawns wide... Ensanguined fangs agleam.
  
  Great shadow, awaken and eclipse the suns of a thousand worlds...\\
  Slumbering 'neath these crimson vaults, \\
  behold the majesty of the Outer Darkness!\\
  Praise the Z'xulth!
}

% \Psyrex{} rejoices at the fall of the Iquinians, and of \hr{Urban's grudge}{hated Malcur}.

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  Fell Worm of the Black Galaxy, \\
  awaken and descend without pity upon the Tellurian sphere!\\
  Destroy the flaccid priests of the newborn usurper faiths.\\
  Sweep away the thralls of the cruciform stave!\\
  Crush the lackeys of the corrupted hexagram!\\
  Devour the slaves of the eastern crescent!\\
  Crush them, grind them, slay them all!\\
  Plague-blessed, flay them alive!
  
  Now, behold in terror what waits beneath the crimson vaults of Cydonia...
}







\subsubsection{\ps{\Urban}{} revenge}
\target{Urban's revenge}
\Urban{} strides through the blood-flowing streets, laughing like a madman. 

Now, at last, he celebrates his long-awaited revenge against the proud, shining white city. (See section \ref{Urban's grudge}.)

Have some flashbacks from \ps{\Urban}{} traumatic past. How old he is? Centuries. From before \hs{\GreatBelkade}. 

Some of \ps{\Urban}{} subordinate mages are horrified at what they have done, horrified at seeing their master walk laughing through the blood-red, flesh-filled streets. Some of them he intimidates or inspires back into the fold. Perhaps some of them are beyond his reach, so he kills them and lets \Nithdornazsh{} consume them. 

Have some young mage in \ps{\Urban}{} \ishrah{} who fears all this cosmic evil and repents. He thinks about the legends of \Ishnaruchaefir{} and \Secherdamon. Have some cryptic references to the mysterious immortal \Ishna. 

\lyricsbs{Bal-Sagoth}{
  As the Vortex Illumines the Crystalline Walls of Kor-Avul-Thaa
}{
  By Klatrymadon and Zuranthus,\\
  in Kor-Avul-Thaa darkness reigns eternal.\\
  Nevermore shall the city glimmer.\\
  For now the crystalline walls gleam black.\\
  Ever black.
  
  And so it was that the bedazzling and splendid Kor-Avul-Thaa did become
  the City of Shadows, a sinister fortress of elder fiends and fearsome beasts, unleashed by the meddlings of mortals aspiring to dark thresholds of forbidden knowledge and arcane power, a nightmare city shunned and feared by all. 
  And not since the sinking of Atlantis was the fall of a realm so sorely
  lamented...
}







\subsection[Psyrex thanks Tiroco]{\Psyrex{} thanks \Tiroco}
\target{Secherdamon lets Tiroco and Icor choose their fate}
\Psyrex{} approaches \Tiroco{}. He thanks her for her help and gives her an offer to serve her. Knowing that he is a Hellish enemy of the Light who betrayed her and her entire city, she refuses and curses him. He expected as much. Still feeling that he owes her a favour, he lets her choose her fate. She has proven herself skillful enough that he cannot simply let her go, so if she will not join him, she must die. %He explains that he has shown mercy to capable enemies in the past and always lived to regret it. 

He remarks that: \ta{Were I \Ishnaruchaefir, I might fall prey to sentimentality and spare you. But I am wiser than that. Show mercy to a capable enemy and you will live to regret it.}

But since she did it all for \ps{\Icor} sake, she deserves at least to be with him. So he grants her a choice: He can kill her and release \ps{\Icor} soul, letting them go into the Light as they wish. Or he can destroy them permanently, so that they will know peace. He advises them that the Light is not what they believe it to be, and that he would recommend annihilation rather than a return to slavery. 

%But she does not want to listen to him and chooses the Light. He is somewhat sad to oblige her. 
\Tiroco{} does not want to listen and chooses the Light. But \Icor{} objects. He has done some thinking and come to the conclusion that the \Sephiroth{} are not as good as people think. So he votes for annihilation. After a while, \Tiroco{} consents. 

Have a sad yet somewhat happy scene where the two drift off into oblivion in each other's arms. 

Then \Psyrex{} seats himself on his throne, surveying his new conquest. He muses that the \charade{} is broken. It is also interesting that \Ishnaruchaefir{} has returned to the \secretwar. 

Afterwards, \Psyrex{} comments to \Secherdamon{} (or \Nzessuacrith, or another) that it was difficult to save them. 
The \sephiroth{} had a strong grip on them. 
Moreover, the \quo{river} of \Iquin{} has grown stronger in recent years. 
Wilder, more raging. 
As if it is breaking out of control. 
(The Shroud is \hs{unravelling}.) 

\Psyrex{} fears the \sephiroth{} and \iquin{} and Iquinianism. 
Perhaps it should just be explained and made to seem as if he dislikes the Iquinian religion and does not want to give it any more souls and thus more power. 
Just keep it as a subtle undertone that he really believes an afterlife in \iquin{} would be painful for them\dash a fate he would not wish upon them, honourable folk as they are. 
(After all, I don't want the reader to know that \Iquin{} is evil just yet.)





\subsubsection{Why do you do this?}
Before she dies, \Tiroco{} asks \Psyrex: \ta{Why do you do this?}

\Psyrex: \ta{For survival. For the future of my people. And your people as well, \scatha. For our kind's survival, against the \humans{} and their creators.}

\Tiroco{} wonders who the \humansz{} \quo{creators} might be. Then she dies. 







\subsection{\Ishnaruchaefir{} returns to Malcur}
\subsubsection{Saves Rian and Neina}
Rian and Neina \hyperref[Rian and Neina are separated from Moro]{have gotten separated from Moro}. They flee and huddle together in the collapsing, mutating city. 

Then \Ishnaruchaefir{} arrives in Malcur to bear witness to the rise of \Nithdornazsh. Rian sees him, and their eyes meet. Rian sees something that he recognizes in those eyes, although he isn't sure what. He notices that the \dragon{} has huge, bleeding wounds that go all the way through his body (after being \hyperref[Ishnaruchaefir impaled by spines]{impaled on huge spines}). 

\Ishnaruchaefir{} descends, lands near Rian and assumes humanoid form. Rian recognizes him: It is the mighty warrior-mage who \hyperref[Rian is inspired by Ishnaruchaefir]{once inspired him to become a better man}. \Ishnaruchaefir{} is aware of this to some extent, and is glad to see that Rian has indeed become a better man. 

\Ishnaruchaefir{} is wise and can read much of Rian's story in his eyes. He sees immediately that the young man has fought bravely to save his beloved. This touches him, for he wishes he \hyperref[Ishnaruchaefir slays his beloved]{could have done same}. He also feels some kind of responsiblity for them, since he was part of the plan that destroyed their city. So, in a \trope{PetTheDog}{Pet the Dog} moment, he decides to save Rian and Neina. 

Some \daemons{} or evil warriors approach. \Ishnaruchaefir{} sends them packing with a single word. He then saves Rian and Neina, sending them through a portal out of the city and into an area that should be semi-safe. 

He sees that Neina is \hr{Neina's story}{badly traumatized}. So he casts a spell on her, erasing much of her memory of the last months. This has the side effect of making her permanently dumber than before. \Ishnaruchaefir{} warns Rian that he has done this, and that many memories have been lost other than those of her captivity (this kind of magic is inaccurate and risky, and it is not \ps{\Ishnaruchaefir} specialty). 

After the spell, Neina is not quite sure who Rian is, but some part of her remembers him and the love she had for him. He is hopeful and trusts that he can nurture her back to health. 

They thank \Ishnaruchaefir{} of all their hearts. Then they go through, hand in hand. 
We see them kissing and embracing, and it is implied that, despite whatever hardships cruel \Miith{} will throw at them, they will live happily every after. 





\subsubsection{Meets \Nzessuacrith}
He meets \Nzessuacrith{} in Malcur. 
She has just returned from the Ghost Tower, where she was hurt in combat and scared off by a wave of \sathariah{} power. 

She is in a bad shape after her fight. 
She has big, open, bleeding wounds. 
Her silvery scales are blackened and dirty. 
Many of her \hs{ward runes} are depleted. 
She is so wounded that she dares not go into the Shroud. 
Its constricting influence would cut off the flow of life-giving \xsic{} energy that is currently sustaining her, leaving her with a masked body too weak to cope with the bleeding wounds. 
That might (temporarily) kill her. 

\Nzessuacrith: 
\ta{The only power at their disposal that can match ours. 
    Stolen from us as it is.} 

But she is ashamed of the fact that a little \sathariah{} smell was enough to scare her so and force her to flee. 
She does not openly admit it to \Ishnaruchaefir, and only to \Secherdamon{} after treading water for a while. 

They do not \hr{Dragon violence}{snap and lash out at each other}, as a friendly pair of \dragons{} would. 
They just stare coldly. 
They don't like each other. 

\Ishnaruchaefir{} is intrigued by the \sathariah{} part. 
He flies out to the Ghost Tower general area to investigate. 
He is wiser than she and can see \matrices{} and \vertices{} more clearly. 
He tracks down Carzain to say hello. 

Maybe \Ishnaruchaefir{} is the one who tells \Nzessuacrith{} about \ps{\Secherdamon} true plan, and how she was just a diversion. 

In this scene, \Nzessuacrith{} for the first time calls \Ishnaruchaefir{} \quo{father}. 

\Nzessuacrith{} and \Secherdamon{} call \Ishnaruchaefir{} \quo{Exile}. 
They refuse to afford him the honour of pronouncing his name. 

It is mentioned that the whole thing is a major breach of the \charade. 





\subsubsection{He meets Carzain}
While Carzain-tachi are making their way through the \Wylde{}, \Ishnaruchaefir{} appears. 

Maybe he secretly sends monsters to attack them, then to come in and rescue them. 

He talks to them.

Remember that \Ishnaruchaefir{} does not speak \Velcadian. 
He does, however, speak Imetric and Vaimon. 

\Ishnaruchaefir{} is known and infamous to the Redcor. 
\Esmerel{} recognizes him and scorns him as a evil sorcerer. 
Northstar recognizes his name, but is uncertain as to whether he is good or evil. 

(Why? 
What is \ps{\Ishnaruchaefir} back-story? 
Who knows him? 
Who likes him? 
Who hates him? 
Who fears him?)

% \Ishnaruchaefir{} then somehow leads them back to the Ghost Tower. 
% He recognizes that Carzain is the \vertex{} they are all looking for, and since he is on the Pelidorians' side, \Ishnaruchaefir{} figures that Carzain will stir up some ruckus at the Ghost Tower, disturbing \Nzessuaz{} mission and forcing her to bring out the big guns. 
% Which will attract more attention to her, drawing it away from Malcur. 
% (\Ishnaruchaefir{} wants to help \Secherdamon{} resurrect \Nithdornazsh, and will happily sacrifice the Ghost Tower to that end.)

Carzain: 
\ta{Who are you? 
    Whose side are you on? 
    Are you good or evil?}

\Ishnaruchaefir{}: 
\ta{I... simply am what I am.}

Carzain: (Thinks about it for a moment.) 
\ta{What a stupid answer. 
    What a feeble way of dodging the question!}

\Ishnaruchaefir: \ta{Hm. True.} Smiles. 
\ta{Very well. 
    The truth: 
    I do not know. 
    I fear you will have to judge for yourself.} 

See, this was a test. 
\Ishnaruchaefir{} \hr{Ishnaruchaefir's inanities}{sometimes does this}; spouting inanities to see if the other guy accepts them as profound wisdom or recognizes them as inane and calls him out on it. 

\Ishnaruchaefir{} tells Carzain: 
\ta{I predict that you and I shall meet again. 
    Perhaps as allies, but more likely as enemies. 
    The world is cruel, do you not agree?}

After Carzain-tachi depart, \Criseis{} asks him: 
\ta{Why did you not kill him, my Lord, knowing what he is?}

\ta{What excitement would there be left in life if I were to slay all my enemies when they be still small?}

\Ishnaruchaefir{} thinks to himself: 
\tho{%
  He has the \sathariah{} smell. 
  I ought to deeply hate him. 
  And I do.
  
  Maybe \Criseis{} is right. 
  Maybe I should kill him. 
  But what the Hell?
  If I kill him now, there will just be another Scion in a couple of centuries. 
  Might as well let him grow up and deal with him now.} 







\subsection{Epilogue}
\subsubsection{Carzain}
Carzain and his party finally set out for \Redce. 





\subsubsection{Charcoal is rewarded}
\target{\Achsah{} rewards Charcoal}
Charcoal is rewarded by \Achsah{} for \hyperref[Charcoal at the Ghost Tower]{helping to guard the valuable Ghost Tower}.

%If it's \Achsah, then perhaps she rewards him by giving him the best sex he has ever had.
Perhaps \Achsah{} rewards him by giving him the best sex he has ever had.

Inside, Charcoal is thinking: 
\tho{I'm glad she doesn't mention the things I fucked up in Malcur. 
  But, after all, I wasn't present. I can wipe the blame off on Needle\dash and \Achsah{} herself, and even \Teshrial.}





\subsubsection{\Achsah{} curses the \dragons}
\Achsah, on her throne in \Nyx, curses at the audacity of the \dragons. The resurrection of a \Machaic{} fortress on \Miith{} has never been attempted before and is a blatant breach of the \charade. 

She is also baffled by \ps{\Ishnaruchaefir} ingenuity. She had thought that the mystic warrior remained mostly aloof from the \secretwar{} and had not thought that he would interfere so directly, much less to the aid of his brother. And least of all did she expect him to see through the plan with the \ghobaleth{} beneath Malcur. 

\ta{Damn \Secherdamon, that cheat. And damn \Ishna, that anarchist.}

Still, she is grateful that \Ishnaruchaefir{} has killed \Teshrial, whom she hated. 





\subsubsection{Some people wonder about the \quo{survival}}
Some people, both \human{} and \scathaese{}, speculate on the things they were told about how the feuding factions are allegedly fighting for: 
\quo{Survival. 
  The survival of our race. The \emph{purpose} of our race. We are waging the war that we were \emph{born} to wage.} 





\subsubsection{\Azraid{} muses}
\target{\Azraid{} muses on Exile and Pyre}
\Azraid{} sits and muses about \Ishnaruchaefir{} and his involvement. 
\Azraid{} is the \apex{} of his \matrix, so he detected it immediately when \Teshrial{} was destroyed. 
But he doesn't know the details of the fight. 

He thinks about \Ishnaruchaefir{} helping \Secherdamon. 
\hr{Exile intersecting with Pyre}{The Exile did not intersect with the Pyre}. 
And yet, it still did. 
In intent and effect, if not in the formal, metaphysical sense. 

Remember to have subtle references to \ps{\Azraid} evil hand in all \Azraid{} chapters. 

\begin{prose}
  \tho{But it is the thought that counts. 
    Let that be a lesson for all astrologers.
    The Star-Maps of the Cosmos can reveal much, but it cannot tell us all things that are worth knowing.}
\end{prose}

\target{\Azraid{} learns of spike}
He also thinks about the \vertexspike{}. 
\Achsah{} is $100\%$ sure the \vertex{} is a \sathariah{} aligned with the \hs{Midnight Bat}. 
Which means it must be a Scion. 
Which means there are only two possibilities. 

\Azraid{} is very interested. 
He wants Ramiel back. 
\Azraid{} himself \hr{\Azraid{} dies}{is preparing to die}, so he wants to set up an heir to take over leadership of the \resphan{} race when he is gone. 
Ramiel is a good candidate. 

So \Azraid{} \hr{\Azraid{} protects Carzain}{assumes the role of Ramiel's \quo{guardian angel}}, subtly pulling threads and protecting him from harm while he grows towards his \apotheosis. 
(This is necessary. Many forces conspire to kill Ramiel's Scion.)

\Azraid{} is distressed about the resurrection of \Nithdornazsh, but only in a detached, relaxed way, 
It is an annoyance that will make his work more difficult in the future. 






\subsubsection{\Secherdamon{} and \Nzessuacrith}
\Secherdamon{} and \Nzessuacrith{} talk. 
She mopes over being defeated. 
He had previously promised to come to her assistance if she needed it, so she berates him for not coming. 
He explains that he did indeed come to her assistance, for his actions in Malcur accomplished more than the capture of the Ghost Tower could possibly do. 
He thanks her for her help, for it was the failure of her initial, more covert plan which forced her to go in with full force. 
This in turn drew all Cabal eyes to her, which allowed him to carry out his plan. 
All of which he had planned in advance. 

He apologizes for having used her. 
\Secherdamon{} and \Nzessuacrith, of all people, understand very well the pain of being betrayed by their own family. 
They are close allies and should be able to trust each other. 
They are more sensitive and considerate than the irreverent \Ishnaruchaefir. 

It is mentioned that the whole thing is a major breach of the \charade. 

\Secherdamon{} muses about \ps{\Ishnaruchaefir} unpredictability. 
He also reveals that \Ishnaruchaefir{} is his brother. 
He is greatly disappointed that \Ishnaruchaefir{} did not die. 
\Secherdamon{} \hr{Secherdamon thinks Ishnaruchaefir will sacrifice himself}{had hoped \Ishnaruchaefir{} would sacrifice himself}. 

The book closes with \Secherdamon{} musing:
\tho{The Unspoken Covenant is broken. 
  Open war is upon us. 
  Perhaps even a \thirdbanewar.
  Yes. 
  The final war is upon us.
  And it has only just begun...}















\section{Changes}










\subsection{The Dreaming Predator}
\begin{changes}
  \begin{comment}\paragraph{Prologue}\end{comment}
  \changesitem{Prologue}
    
    Mention that the slain \dragons{} and \resphain{} have had not just their bodies destroyed but their immortal souls as well. 
    
    \Secherdamon{} whips his tail in anger. 
    
  \begin{comment}\paragraph{The Mutiny}\end{comment}
  \changesitem{The Mutiny}
    \hr{Mutiny chapter}{Moved to the Carzain Prequel}. 
    
  \begin{comment}\paragraph{Ilcas Northstar}\end{comment}
  \changesitem{Ilcas Northstar}
    \hr{Ilcas Northstar chapter}{Moved to the Carzain Prequel}. 
  
  \begin{comment}\paragraph{Wanderer in Darkness}\end{comment}
  \changesitem{Wanderer in Darkness} 
    Move the Evith scene from \quo{\ps{\Teshrial} Banquet} to this chapter. 
    Maybe make the party longer. 
    
    It takes place at \ps{\Teshrial} place, not \ps{\Ganethed}. 
    
    Have more atmosphere: 
    \begin{enumerate}
      \item 
        Outside the windows the thunderstorms rage in the deep beneath the spires. 
      \item 
        One of the \resphain looks out out of the window and sees a shape moving in the distance. 
        Possibly an \umbra. 
        He shudders to think of the horror of the creature. 
        A monstrosity older than the \resphain, and more wicked. 
        He dimly feels the beat of black wings from moonless gulfs. 
      \item 
        The room is lit by \hs{\glowmoss} lamps. 
        The glowmoss gives off a nice, dim, blue light. 
        Not like the harsh, yellow glare of the Sun that was visible outside \Nyx. 
        \Teshrial{} has never gotten used to that. 
        He is of \CiriathSepher{} and appreciates the light, but even so, the Sun is awfully bright. 
    \end{enumerate}
  
    \Teshrial, \Ganethed{} and Selguin should be better friends. 
    \Teshrial{} looks down on \Ganethed{} a bit (because he is just a snob), but the two are still friends. 
    
    Portray \Teshrial{} as less of a villain and more of a man who genuinely wants to protect his people's precious works from an evil enemy. 
    But still a bit of an overconfident, self-absorbed snob. 
    
    Have some more \hs{astrology}. 
    
%     \Achsah{} tells them that, according to her astrology, it is likely that the \vertex{} that \spiked{} is aligned with the \hs{Midnight Bat} \matrix. 
%     If this is true, and if it is also true that it is a Scion, then there are still several possibilities. 
%     It might be \Shiaraid{} stirring. 
%     She was killed, after all, but not destroyed. 
%     (Add her to the Dramatis Personae if she is mentioned. 
%     Set her race to \quo{\malach}.)
    
    Remove references to Carzain's \vertexspike. 
    
    After a lot of offscreen talk, the party is interrupted when \Achsah{} (who is a \hs{High Telepath}) feels a strange, giant \vertex{} moving in Malcur. 
    She is the first \resphan{} to feel it because she is the only \hs{High Telepath} attuned and closely aligned with the Malcuric \Nexus. 
    She sends her mind out to investigate and finds out that it is \Ishnaruchaefir. 
    
    Cannibalize the \quo{\VertexSpike} scene with \ChyrieEsmerel! 
    
    Revise the references to \hr{Ishnaruchaefir's titles}{\ps{\Ishnaruchaefir} titles}. 
    
    Make sure to use the right name for \emph{\WanderersInDarkness}. 
    
    \Ishnaruchaefir{} is feared as the wicked \hs{Destroyer} who sundered the world. 
    He killed millions, including many of his own race. 
    Everyone dreads him. 
    But \Teshrial{} is brave and dares challenge him and test his mettle. 
    
    After all, it is no secret that the Cabal claim Malcur as theirs and have vested interests there. 
    
    The others try to discourage \Teshrial.
    They think it is too dangerous. 
    But \Ishnaruchaefir{} is a dangerous invader, and \Teshrial{} will not stand idly by while he invades their territory and endangers their plans. 
    He will go out and challenge the invader. 
    He will defends the interests of \CiriathSepher, the Cabal and the \resphan{} people. 
    
    \Teshrial{} will meet him deep in the Shroud. 
    There he \hr{Immortals inside the Shroud}{cannot use his full \draconic{} power}, let alone his \xsic{} power. 
    Besides (\Teshrial{} thinks to himself), it is \hr{Shroud prevents soul destruction}{nearly impossible to destroy a soul from within the Shroud}. 
    So what is the worst thing that could happen?  
    
    Have \Teshrial{} gaze at the stars and interpret them while he's standing around on the causeway (just before slapping \Achsah). 
    He looks at the \hs{Exile} and wonders. 
    
    Show \Teshrial{} hefting the \senaan{} \hs{\Turishah}. 
  
  \begin{comment}\paragraph{What Slithers Beneath}\end{comment}
  \changesitem{What Slithers Beneath} 
    \Criseis{} should call \Ishnaruchaefir{} \hs{Master \Quessanth}. 
    
    \Ishnaruchaefir{} says \quo{yea} and \quo{nay}. 
    
    \Criseis{} \hr{Criseis' senses}{has sharper senses} than \hr{Ishnaruchaefir's senses}{her master does.}
    \begin{prose}
      \Ishnaruchaefir: 
      \ta{There is a boy following us.}
      
      \Criseis:
      \ta{I know.}
      \tho{I noticed him before you did.}
    \end{prose}

    \Criseis{} wonders why Rian can see them. 
    Granted, \Ishnaruchaefir{} is a mammoth \vertex, so massive than even Shrouded mortals can detect him by the sheer reverberations he sends out. 
    But he is prepared and has cast some serious spells to mask himself. 
    Mortals shouldn't be able to see him. 
    
    \begin{prose}
    \tho{Who is this boy? Is he someone special?
      Is he a mage or a \vertex{} himself?
      Is he someone in disguise?
      No, I can't believe that.
      I am certain he is just a regular boy.
      
      Something is rotten in the state of the Shroud.}
    \end{prose}
    
    \Criseis{} feels the \ghobaleth{} underneath Malcur:
    \begin{prose}
      \tho{Damn you, Master \Quessanth. 
        You knew how badly this would affect me.
        You know my senses are sharper than yours, so I feel things like this worse. 
        You could have warned me.}
    \end{prose}
      
    But then she regrets cursing him. 
    After all, he carries heavy burdens and is on an important mission. 
    He has more important considerations than her feelings. 
    Besides, she knows he would never let anything bad happen to her. 
    But still...
    
    There is a \hr{Wylde border}{\Wylde{} border} around the dead garden. 
    It is, after all, a small patch of \wylde{} in the middle of Malcur.
    
    Fix the name: 
    \Rystessakhin{} $\to$ \AeocrithRystessakhin. 
    Fix the Glossary, too! 
    
    Have \Criseis{} mention that she and \Ishnaruchaefir{} are \hr{Mask}{Masked}. 
    \Ishnaruchaefir{} drops his Mask as he moves deep into the Shroud to battle the \ghobal, then dons it again when he returns. 
    
    \Teshrial-tachi are about to arrive. 
    \Criseis{} notices them first and warns her master. 
    \Ishnaruchaefir{} smells the air with his tongue. 
    He feels it too.
    
    \Teshrial{} is the son of \Zereth. 
    Also fix the Dramatis Personae! 
    And the Glossary! 
    
    \Criseis{} notes that \Teshrial{} has an aristocratic-sounding tenor voice. 
    
    \target{\Ishnaruchaefir{} fakes ignorance about \ghobaleth}
    \Ishnaruchaefir{} says something like: 
    \ta{What a shame that your scheme is now ruined.}
    This is to fool \Teshrial{} into thinking \Ishnaruchaefir{} doesn't suspect the full extent of the \ghobal{} plan. 
    \hr{\Teshrial{} does not know that \Ishnaruchaefir{} knows}{\Teshrial{} takes the bait}. 
    
    Remember that \Teshrial{} walks the \hs{Path of Ice}. 
    
    \Teshrial{} wields a long-barrelled pistol of shining gray metal and a handle that looks like ivory. 
    It fires 50 cm long glowing harpoon-like needles that seem to explode and splinter like glass when they impale something, or when they are parried. 
    It is called a \quo{fezrot} or something. 
    He has his \senaan, \Turishah, strapped to his back. 
    When he needs it he releases it from its straps with a simple telekinetic command. 
    
    \Teshrial{} should not be too overconfident. 
    He knows he is in over his head and does not really expect to win. 
    
    \target{Brawn triumphs over brains}
    \Teshrial{} wields his \hr{Senaan}{\senaan}, \hr{Weapon master \Teshrial}{expertly}. 
    He parries one of \ps{\Ishnaruchaefir} attacks, or tries to. 
    His speed, reactions and technique are all flawless. 
    But he fails to take into account the sheer overwhelming brute force that \Ishnaruchaefir{} brings to bear. 
    Later he \hr{Brains will triumph over brawn}{thinks back to this}. 
    
    \Ishnaruchaefir{} uses the spell \word{\hs{khestni}}. 
    It hurts \Teshrial, but does not kill him. 
    
    After \Teshrial{} dies, his body dissolves as if in acid. 
    This is the Shroud-weaving, destructive power of \Rystessakhin... the reality-warping power of a \xs-empowered Fulcrum.  
    
    Later, \Achsah{} carries on \ps{\Ishnaruchaefir} message. 
    But she wishes \Teshrial{} would decline the offer. 
    
    When \Criseis{} insists they let Rian live, \Ishnaruchaefir{} goes:
    \ta{Sigh. [Smile.] 
      I fear one day your sentimentality will be the death of us, \Criseis.
      But very well.
      Now come.}
    
    \Criseis{} is worried that Rian can see them. 
    He should not be able to. 
    Granted, it was a shallow Mask that \Ishnaruchaefir{} was wearing. 
    It is very like him to be so reckless. 
    But it wasn't \emph{that} shallow. 
    The Shroud must be \hs{unravelling}. 
    (She has seen clues of this before. 
     The Shroud is frayed with holes these days.
     She also knows that her master's burdens are getting heavier, and his Nadirs are getting worse.)
    
    In the \Psyrex{} scene, remove any direct references to the Malcur \nexus. 
    Just refer to \quo{the \nexus{} in Pelidor}. 
    We don't want to tell the reader that \Forklin{} is a decoy. 
\end{changes}









\subsection{The Runger War}
\begin{changes}
  \begin{comment}\paragraph{Daggers and \Daemons}\end{comment}
  \changesitem{Daggers and \Daemons}
    People should not just smalltalk. 
    They should be discussing the \hr{Rissitics and Runger}{Rissitic invasion of \Scyrum/Sumian} and what it means for all \Galessan. 
    Make it clear that the Redcor Church is supporting the \Scyrics/Sumianese, and the Imetrium may throw its weight in as well. 
    Everyone is very disturbed by the Rissitic invasion. 
    
    The Rissitics are feared. 
    Have references to the dreaded, mighty warlord \Narkiza, who is more than a \scatha. 
    An immortal warrior mage. 
    Almost a demigod. 
    An \hs{\Ashenoch}. 
    Most of them do not know the word \quo{\Ashenoch}, but maybe one does. 
    \Sethgal, maybe. 
    
    \Tiroco{} shudders:
    \begin{prose}
      \Tiroco: 
      \ta{%
        I am glad I'm only \rinyuth{} and do not have to deal with all that. 
        Rissitics and their sorcery... it sounds frightfully dangerous.}
    \end{prose}

    
    Have references to the war with Beirod several years before, in which Carzain fought. 
    It is now long over. 
    (If Carzain's introduction is removed entirely, this is no longer important.)
    
    \Onatol{} has books and scrolls lying around. 
    And a star-map on the wall (annotated with plenty of occult data useful in calculating and interpreting the \matrices). 
    And some sigils representing various \sephiroth{} and \qliphoth. 
    And some herbs and drugs and incences used for meditation. 
    
    Remember the \hr{Itzach pain}{pain of \itzach} when Curwen casts magic. 
    
  \begin{comment}
  \paragraph{War is Coming}
  \end{comment}
  \changesitem{War is Coming}
    There is mention of the \hr{Rissitics and Runger}{Rissitic invasion of \Scyrum/Sumian}. 
    People worry about all these wars. 
    The old \sphyle{} muses: 
    \ta{I guess it's the season for war...}
  
  \begin{comment}\paragraph{Beyond the Veil}\end{comment}
  \changesitem{Beyond the Veil}
    Revise the funeral rites. 
    Think up a better funeral tradition. 
    See \href{http://limyaael.livejournal.com/179073.html}{Limyaael's death rant} for ideas. 
    
  \begin{comment}
  \paragraph{For War and For Glory}
  \end{comment}
  \changesitem{For War and For Glory}
    Make this chapter seen from \ps{\Sethgal} perspective instead. 
    
    Remember that he is a knight. 
  
  \begin{comment}\paragraph{The Mystery of \EreshKal}\end{comment}
  \changesitem{The Mystery of \EreshKal}
    Look at \href{http://limyaael.livejournal.com/167123.html}{Limyaael's \quo{Sounds of the Jungle} rant} for ideas and advice on the forest scenes. 
    
    Curwen quickly figures out that \hs{\Jirad{} Tantor} must be a kinsman of the \scarv{} of Tantor. 
    \hs{Most mages are nobles}, after all.
    
    There is a \hr{Wylde border}{\Wylde{} border} around Gedrock, which Tantor passes by. 
    
    Tantor needs to be more racist. 
    When he hears there are \meccara{} in \EreshKal, he scoffs. 
    \Meccara{} are \quo{lower humanoids}, clearly less intelligent and civilized and worthwhile than \humans{} and \scathae. 
    He does not expect much of them, and he certainly does not fear them. 
    
    Charcoal does not call him out on this. 
    Charcoal is a racist himself. 
  
  \begin{comment}\paragraph{A Dark Angel's Gift}\end{comment}
  \changesitem{A Dark Angel's Gift}
    Maybe Needle is not offered command over \banes. 
    Maybe that doesn't happen until much later. 
  
  \begin{comment}\paragraph{The Gods of \EreshKal}\end{comment}
  \changesitem{The Gods of \EreshKal}
    As soon as Tantor steps inside the entrance to \EreshKal{} he imagines he feels the dust and darkness of uncounted millenia. 
    He believes the building is extremely old. 
    From before the \Human{} Age. 
    Older than Cordos Vaimon. 
    
    It is well-known that the \meccara{} are a younger race than \humans. 
    But Tantor believes that these \EreshKali{} are the caretakers of a tradition of sinister, forbidden wisdom far older than they themselves. 
    A legacy that reaches back to the races and empires that reigned immemorial aeons ago and were forgotten before the first \humans{} set foot on \Miith. 
    
    \EreshKal{} is the ruins of what was originally a \quiljaaran{} city. 
    Tantor refers to the \hr{Myths of vanquished monsters}{myths of Iquinian heroes vanquishing inhuman Elder Races and monsters}. 
    He sees \EreshKal{} as a leftover from the mythical \hs{Age of Gods}. 
    He daydreams of the ancient wars when \humans{} vanquished the serpent men. 
    
    Charcoal laughs at Tantor. 
    He knows that the \quo{Age of Gods} is still going on and that the Elder Races are very much alive and kicking. 
  
    Describe the sounds and smells inside the \EreshKali{} temple. 
    The smell is musky and very old. 
    
    Tantor needs to be more racist. 
    Emphasize how \quo{filthy} and \quo{degenerate} the \EreshKali{} are, even by \meccaran{} standards\dash and that is saying a lot, because even a regular \meccaran{} is pretty dirty and stupid and ugly and inferior. 
    Tantor describes how his people win because they are of superior races. 
    (Some of his men are \scathae. 
     They are, of course, not as good as \humans, but still clearly better than \meccara.
     \Scathae{} are \quo{higher humanoids}, although not the highest there is.)
    
    Also write in the Glossary about \quo{lower} and \quo{higher} humanoids. 
    
    When \Mycah{} dies, Tantor thinks it is the ancient curse, cast upon this loathsome place by wicked pre-\human{} gods, that has caused it. 
    The old gods are bitter to have been displaced and hate the \humans{} that have since swarmed all over the world that was once theirs. 
    So they want revenge. 
    Encroaching on their territory can only end badly, Tantor muses. 
    
    Tantor finds some writing in the temple that he cannot read. 
    The symbols certainly look nothing like Vaimon nor \Ortaican{} script. 
    They are reminiscent of Rissitic glyphs, but Tantor is pretty sure that is not it, either. 
    He has reproduced some of them in the diary. 
    Charcoal cannot read them, either. 
    
    Charcoal wonders. 
    Can it really be true that there lay such a treasure trove of magical wealth hidden in Runger, right under everyone's noses, where any moderately-armed warband could just waltz in and claim it? 
    If so, how did \Takestsha{} learn of it, and why did no one else learn of it before her\dash especially if it really is as old as Tantor guesses? 
    It seems incredible. 
    The Cabal and/or Sentinels ought to have sniffed out this treasure and looted it long ago. 
    Something does not add up here... 
  
  \begin{comment}\paragraph{\Forklin}\end{comment}
  \changesitem{\Forklin} 
    \begin{itemize}
      \item 
        Get rid of \Racel. 
        
      \item 
        Sethgal talks to \Esmerel. 
        He broods. 
        He is worried. 
        
        \begin{prose}
          Sethgal: 
          \ta{%
            I thought Clan Redcor had no resources to support our war, with the Rissitic invasion taking up all your time?}
          
          \Esmerel: 
          \ta{That is true. 
            We are not here to fight your war for you.
            We will give assistance where we can, but we will not fight on the battlefield.}
          
          Sethgal: 
          \ta{Then why are you here?}
          
          \Esmerel: \ta{Redcor business is for Redcor to know.}
          
          Sethgal: 
          \target{Sethgal curses Imetrians}
          \tho{Arrogant bitch. You come here to mooch off us, but won't help.
            And damn those Rissitics. 
            It will be hard to get help from \emph{any} of our allies, with the Rissitic invasion stealing all the attention.
            
            The Imetrians are the same.
            We let them build their churches and preach their religion in our country, even though it's heretical to us, but are they coming to help us?
            I certainly don't see them here with us.}
        \end{prose}
        
        Sethgal learns, however, that the Redcor are worried about the spiritual direction Runger is headed. 
        There is concern that Morgan Runger has abandoned the principles of the Iquinian faith. 
        The Redcor will keep an eye on him, and they may choose to intervene in this war yet. 
        
      \item 
        Consider getting rid of all the scenes in \Forklin{} except the one where Carzain \quo{volunteers} for the sally. 
        This scene should be told from Curwen's POV. 
        
      \item 
        The scene in the forest where a \ranger{} explains how maps work (and don't work) in the \wylde{} should be rewritten. 
        It is good to have, so it should probably be moved somewhere else. 
    \end{itemize}
  
  \begin{comment}\paragraph{Trinity of Pestilences}\end{comment}
  \changesitem{Trinity of Pestilences} 
    Change title to \quo{Trinity of Plagues}. 
    
    In all the Rian chapters, whenever it is appropriate, have references to the \hr{Myths of vanquished monsters}{myths of Iquinian heroes vanquishing inhuman Elder Races and monsters}. 
\end{changes}









\subsection{The Cancerous City}
\begin{changes}
  \begin{comment}
  \paragraph{The Terror of \EreshKal}
  \end{comment}
  \changesitem{The Terror of \EreshKal}
    Rewrite the chapter so it is only Carzain.
    
    He still zones out at this touch of dark magic, but he keeps better control of himself than he did in the old version. 
  
    There is a \hr{Wylde border}{\Wylde{} border} around the dead garden. 
  
  \begin{comment}
  \paragraph{The Emperor Inviolate}
  \end{comment}
  \changesitem{The Emperor Inviolate}
    Rewrite the chapter so it is only Carzain.
    
    Vizicar is very interested in this magic that the Rungerans are using and wants to learn more about it. 
    He considers joining the Rungeran army for a moment. 
    But only for a moment. 
    Carzain's feelings sweep it away. 
    Carzain is no great patriot, but he will not be party to such a betrayal as it would be to join the army that is invading his homeland. 
    Especially after the atrocities they have committed.
    No, that would be too immortal.
    They resolve to go join the Pelidorian \ishrah{} and warn the Pelidorians of this new magic. 
    
    Again, Vizicar ignores the \hr{Itzach pain}{pain of \Itzach}, and Carzain gets burnt and wounded as a result. 
    
    Remember the \hr{Itzach pain}{pain of \itzach} when Curwen casts magic. 
    
    Remember to have references to the \hs{\shechinah}. 
    
    Maybe Vizicar holds back his power and magic. 
    He does not want to arouse suspicion and get caught. 
    
    \Takestsha{} does not detect the \vertex. 
    Or, if she does, it is something new to her. 
    She has not felt Carzain before. 
  
  \begin{comment}
  \paragraph{The Thirsty Nether}
  \end{comment}
  \changesitem{The Thirsty Nether}
    Needle knows she is a poor reader. 
    But she doesn't understand that it's because she learned it as an adult. 
    She thinks it's because she is lowborn, and that nobles simply have talent for reading and other fine arts by virtue of being nobles. 
    (Maybe ask on a forum how to best represent this.)
  
  
  \begin{comment}
  \paragraph{The Bleeding Wood}
  \end{comment}
  \changesitem[The Bleeding Wood]{\hr{Rian sees a raid}{The Bleeding Wood}}
    \begin{itemize}
      \item Mention that \hs{Needle hates the Black Plague}. 
      \item Rian should not see quite so much. 
        He knows that there is black magic and wickedness and conflict, but he doesn't know who is who. 
        He sees Needle, but doesn't know which side she is on, so he just categorizes her as \quo{evil}.
        (This ends with him and Moro killing Needle... maybe.)
        
        Rian just sees Needle-tachi near the building, armed and menacing. 
        Then a \grimrat{} startles him and chases him. 
        He sees no more. 
        He does not see the raid at all, so he does not know there are two different factions fighting each other. 
        He just knows there are evil mages and monsters. 
      \item 
        There is a \grimrat{} that crawls up a beam and runs across a crossbeam to leap down on its victim. 
      \item 
        Skip the entire battle and go straight to the aftermath with Needle contemplating. 
      \item 
        Needle is horrified after seeing the \grimrats{} tear people to shreds. 
        \ta{But it had to be done.}
        
        She is also squeamish about killing the plaguers. 
        But she must. 
        She has to remind herself that thugs such as these deserve no mercy. 
        She thinks back to the beginning of her family's tragedy, where her brother was killed by someone who might very well have been a plaguer. 
        A \scatha{} dressed in black, with a hood. 
        
        \tho{Yes. It was a plaguer. It must have been. I hate them.}
        She clings to this hate. 
        It makes her job easier. 
      \item 
        Afterwards, \Psyrex{} sits on his throne and muses. 
        \begin{prose}
          \ta{I have lost one of my mages. 
            I will probably have to import a new mage to Malcur.
            
            Sad business. 
            Still, they did their job. 
            The plan is still on schedule.}
        \end{prose}
    \end{itemize}
\end{changes}









\subsection{Characters}
\begin{changes}
  \begin{comment}\paragraph{Archibald Curwen}\end{comment}
  \changesitem{Archibald Curwen} 
    Rewrite Archibald Curwen. 
    He is boring because he is not emotionally involved in anything that goes on. 
    He is unlikable because he is grumpy and brutish. 
    Make him more dastardly, more sardonic. 
    Make him bitter in a sarcastic way rather than a grumpy way. 
    He should smile more. 
    He should say \quo{\Mister{} \Shireyo}. 
    
    He shouldn't be so fat. 
    Change \quo{lose that belly of yours} to \quo{lose some weight}. 
  
  \begin{comment}
  \paragraph{Carzain}
  \end{comment}
  \changesitem{Carzain} 
    Rewrite the Carzain story thread. 
    Make Carzain more mysterious. 
    
    Kill a lot of the waking scenes with Carzain, Delph and \Tsekkect. 
    In fact, kill most of the thread. 
    The Carzain/Vizicar story thread should be a teaser for things to come.
    It should not be the main story. 
    
    Move most of the scenes to a prequel detailing Carzain's travels and his path to \kenosis. 
    
    Carzain is not completely young and inexperienced in the Runger war. 
    He has been to war before. 
    
    The mutiny in Heropond happened several years earlier. 
    Back then, \hr{Carzain joins the army}{Carzain joined the army} because he hoped it would help him find out what was happening to him, who he was and who Vizicar was. 
    
    In the intermittent years, Carzain has travelled the land as an adventurer, working his way towards \kenosis. 
    He has often worked as a mercenary or a bounty hunter, killing monsters for rewards from nobles and wealthy citizens. 
    Sometimes even helping those in need, if he feels like it. 
    
    Several years later, Carzain heard the rumour that Runger was invading his homeland. 
    He discusses this with the voice in his head, and they decide to join the war. 
    
    In all chapters where Carzain uses magic, remember to describe \hr{Itzach pain}{the pain and horror of \Itzach}, in graphic detail. 
    And with blood! 
    
    Carzain is in eastern Pelidor when he hears the news. 
    He decides to go do some scouting/reconnaisance before riding to the army. 
    So he heads further east and sniffs out the Rungeran army. 
    He finds a destroyed village and smells evil magic there. 
    
    Then he goes into the forest, finds the army camp and spies on \Takestsha. 
    \emph{Maybe} she discovers him. 
    If so, he gets to show his badassitude as he fights his way out of it. 
    
    In these early Carzain chapters, have some references to the \hr{Myths of vanquished monsters}{myths of Iquinian heroes vanquishing inhuman Elder Races and monsters}. 
    Carzain gets \quo{Elder} feelings from the \EreshKali{} magic, just like Tantor did. 
    Carzain and Vizicar are unsure of those myths and have a feeling that the Elder Races still live, and that humanoids do not dominate the world as much as they think they do. 
    
    Then he goes to \Forklin. 
    He strides into the city and demands to be taken to Archibald Curwen, his old acquaintance. 
    He \hr{Carzain rejoins the army}{rejoins the \ishrah}. 
    
    When Carzain rides into \Forklin, have him comment on how the \Ortaican-built city looks very different from Vaimon-built ones. 
    \hr{Vaimon Middle-East}{Vaimon things look Middle-Eastern}. 
    
    He also brings valuable reconnaisance. 
    The Pelidorians have scouted, of course, but they have not sent out any skilled mages (they have few of them to spare), so Carzain brings them things they don't know. 
    
    Armed with Carzain's information, Curwen convinces Sethgal that it is best to stay holed up in \Forklin{} and meet the Rungerans there. 
    See, Carzain's findings further confirms Curwen's suspicion that the Rungerans want \Forklin{} for mystic reasons. 
    
    In the scene where Curwen meets Carzain, have a scene from Curwen's point-of-view where he envies Carzain his thick, blair hair. 
    Curwen has mixed feelings about \hr{Curwen's appearance}{his own gray hair}. 
  
  \begin{comment}\paragraph{Moro \Cornel}\end{comment}
  \changesitem{Moro \Cornel} 
    Have more scenes with Moro \Cornel.
    \begin{itemize}
      \item 
        Including \hr{Moro feels Ishnaruchaefir and Teshrial}{one in the dead garden in the beginning}. 
      \item 
        And the scene with \hs{Moro and \Nasshikerr}. 
    \end{itemize}
  
  \begin{comment}\paragraph{Rian}\end{comment}
  \changesitem{Rian} 
    Rewrite Rian.
    Make him more detective-like.
    Right now he depends too much on blind luck. 
    
    And compress the whole Rian story thread. 
    It is unrealistic for Neina to be held captive and alive for so long. 
  
  \begin{comment}\paragraph{Telcastora Ilcas}\end{comment}
  \changesitem{Telcastora Ilcas} 
    Have more focus on Ilcas Northstar and the Imetrians. 
    Show Ilcas and how he is sent to Pelidor because the Imetrians fear Rissitic involvement. 
    (And have a better explanation of why the Imetrians and Rissitics are such rivals.)
  
  \begin{comment}\paragraph{\ChyrieEsmerel}\end{comment}
  \changesitem{\ChyrieEsmerel} 
    \Esmerel{} is in Pelidor \hr{Esmerel in Pelidor}{not to search for Scions, but to oversee and monitor the war}. 
\end{changes}









\subsection{General}
\begin{enumerate}
  \item 
    Update the pronunciation guide!
    Fix the pronunciation of Imetric and Resphan/Vaimon words. 
    Read the \hs{Languages} appendix first. 
    
  \item 
    Fix \hs{noble titles}. 
    Update the glossary with them. 
  
  \item  
    Draw a map of Pelidor/Runger/\Scyrum. 
    And one of Malcur. 
  
  \item 
    Have more descriptions. 
    Describe not only looks, but also sounds and smells. 
    Describe: 
    \begin{itemize}
      \item \ps{\Tiroco} room. 
      \item Needle's room. 
      \item The temple of \EreshKal. 
      \item Sethgal's command tent. 
      \item The Pelidorian army camp. 
      \item The Rungeran army camp. 
    \end{itemize}
  
  \item 
    Rewrite the \Archon-summoning scenes to show the \hr{Visualizing \Archons}{personalized feel of each \Archon}. 
  
  \item 
    Have and mention examples of \hr{Rissitic economy}{Rissitic export goods}. 
  
  \item 
    Go over the Dramatis Personae and add more titles to names. 
    Such as \quo{\Symeon{} Clerk}. 
  
  \item 
    The translation of \quo{Iquin} $\to$ \quo{Light} is cheesy. 
    Get rid of most of them and just write \quo{\Iquin}. 
  
  \item 
    Make a appendix about \matrices{} and \hs{astrology}, entitled \quo{Map of the Stars} or \quo{Pattern of the Cosmos} or \quo{Star-Maps of the Ancient Cosmographers} or somesuch. 
    Read some Bal-Sagoth for inspiration. 
    
    And draw an actual map of the stars and mystic constellations, \hr{\vertices{} in the sky}{with \vertices{} shown}. 
    
    Remember to read the sections about \hr{\matrix}{\matrices} and \hs{astrology} before doing this. 
    
    Remember that \nexi{} such as Malcur and \Nithdornazsh{} should also be represented in the Star-Maps. 
    
    Compare to the Deck of Dragons in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}. 
  
  \item 
    Add the names of all \xss{} used to the glossary. 
    \Ishnaruchaefir{} invokes some in \quo{What Slithers Beneath}. 
    
  \item 
    Read the \hs{Languages} appendix and fix all names and words so they don't contain illegal phonemes. 
  
  \item 
    There are way too many of those dreams/visions of doom in Malcur.
    Get rid of some of them. 
  
  \item 
    Get rid of elephants, rhinoceroi, dogs, wolves and lions. 
    \Miith{} is \hs{\saurian-dominated}. 
  
    A \belwan{} is not a mammal but a small, hornless ceratopsian. 
    
  \item 
    Have references to the \quo{\hs{Ages of the World}} early on, and in the Glossary. 
  
  \item 
    Maybe the entire first \quo{Part} should be a Prologue \quo{Part}. 
  
  \item 
    Add a \hr{Vaimon Middle-East}{Middle-Eastern style to the Vaimons}. 
\end{enumerate}









\subsection{\TeX nicalities}
\begin{enumerate}
  \item
    Sort the index properly! 
    
    Find out how to do \quo{see also} in the index. 
  \item   
    Fix the counter-related problem with years! 
    And make a command that checks whether a number is defined.
  \item 
    Make a macro that capitalizes a word. 
    See \authorbook{Donald Knuth}{The \TeX book} example 20.19 p.217. 
  \item 
    Reduce line spacing in Dramatis Personae and Pronunciation. 
  \item 
    Typeset the index in a smaller font.
  \item 
    Typeset the table of contents in a smaller font and in two columns. 
  \item 
    Add \texttt{$\backslash$gref} commands for \emph{all} Glossary items (incl. people), at relevant places in the text. 
    Replace all \texttt{$\backslash$hr} and \texttt{$\backslash$hs} with these. 
  \item 
    Make a global switch that determines whether a \texttt{$\backslash$gref} should act as a \texttt{$\backslash$hr} or a \texttt{$\backslash$maybehr}. 
\end{enumerate}









\subsection{Limyaael-inspired ideas}
\begin{enumerate}
  \item
    Maybe \Esmerel{} doesn't recognize the signs of a Scion immediately. 
    Maybe she has to go research a lot of writings and signs first (in the big-ass library at the \TopazChateau). 
    Then, later, when she is sure that it was a Scion she saw, she tells the Conclave and receives their blessing to go off and search for it. 
  
  \item 
    Have references to poems, religious dogma, history records and whatnot. 
    See \emph{Limyaael}'s \href{http://limyaael.livejournal.com/357919.html}{Non-linear narrative rant}.
\end{enumerate}









\subsection{Koit's ideas}
\begin{enumerate}
  \item 
    Make Carzain stronger\dash but keep up a threat that he might crumble under the power. 
    \begin{itemize}
      \item 
        \quo{%
          Why I didn't like Carzain? No one is that overconfident in his nonexistant abilities... At least, that's how I saw him.}
    \end{itemize}
  \item Trim the scene with Tiroco and her egg. 
  \item Give \hs{Sethgal} more of a personality. 
  \item Write foreword and reading guide
  \item Fix \quo{Involate} $\to$ \quo{Inviolate}. 
  \item 
    Tiroco: 
    \quo{%
      She seems to be emotionally disabled from her current paragraphs. The behaviour seems inhuman (and she's not human). A typical human would likely do everything he or she could to spend more time with someone who has left (Icor), but she tries to flee from him when she sees him. Perhaps it's right, but it would deserve a bit of mention why it's soo. religious taboo set by Light? Ghosts are perhaps of dark? then I could understand her}
  \item 
    Make sure it is \quo{Charcoal} and not \quo{Curwen} who reads the diaries. 
  \item Give some indication that Curwen recognizes Takestsha. 
  \item Make Curwen's secret identity more secret. 
  \item Add more references to history and historic figures. 
  \item Have some Pelidor-Runger skirmishes before the main battle. 
  \item 
    \quo{have you devised any specific military tactics either side is well known of or feared for?}
  \item 
    It looks like \Ishnaruchaefir{} finds \Triestessakhin{} in the garden. It shouldn't. Fix it. 
  \item Maybe Iasper Bartholin's title shouldn't be \quo{Mister}. 
  \item Draw a map of Malcur. 
  \item 
    page 11, paragraph 5: 
    \ta{The captain may be,} said Carzain, 
    \ta{but has less savoury characters among his men.}
  \item 
    page 11, last paragraph: \quo{even alien and uneartly minerals} I would think that 'unearthly' and 'alien' have quite the same connotation, especially when there's no spacetravel (or if you don't mean that the minerals are from some other dimension)
  \item 
    page 11, last: 
    \quo{It was a journey of many days from \Redglen{} to Martinum}.  Shouldn't it be the opposite\dash they are coming from Martinum
  \item 
    page 12, third: 
    \quo{They were five days' travel out of Martinum and still ten days from Redglen,} 
    
    really, a travel of 15 days on foot and with a cart is rather quick and means a shor distance.
  \item 
    p. 13, fourth: \quo{warring kingdoms and baronies}, You mention a 'baronry' while you'll be dealing with a 'duke' for the most of the come time forward... 
  \item 
    p. 16, third: \quo{At the last minute} seriously, the guy's been running at him for *ages*
  \item 
    p. 16: the mace is above Carzain's head, if the mace falls, the head is below it.
  \item 
    p. 185 - how many moons? two? then it's 'larger' instead of 'largest' at paragraph 2 ending
  \item 
    Carzain: If you mention that he just came back from a trip to a faraway land, it's illogical that he *never* again brigns it up. 
  \item 
    The beginning of Northstar was really weird, I don't know anyone *That* arrogant (Show those Qliphoth who's boss). 
\end{enumerate}























\chapter{\TheKenosis}
\section{Overview}
There are three main plot threads in this book. 
Each of them takes place in the dwelling place of one of the three fragments of the \Haskelek{} and deals with the people fighting the \Haskelek. 

\begin{enumerate}
  \item 
    Carzain goes to \Redce{}, trains there, and ultimately goes to fight the \Haskelek{} in \Redce.
  \item
    Lica and Sir James fight the \Haskelek{} in their country.
  \item
    Sentinels and Cabalists battle for control of the Ghost Tower. 
    Ultimately the Sentinels, led by \Nzessuacrith{} and aided by the \Haskelek{} fragment, succeed in driving away the Cabalists, led by \Achsah. 
\end{enumerate}









\subsection{Carzain in \Redce}
Vizicar, at this point, has regained most of his memories from his life as Vizicar. 
He knows he is a Scion, an incarnation of a \malach. 
He knows he is a superhuman badass. 
He is not \human, but something bigger and better. 
Now he wants to break his feeble \human{} shell and reawaken his true potential. 

Early on, he is joined by Shereid. 
She learns that he is a Scion. 
She joins him and supports him, like Mele supporting Rio in \cite{Tokusatsu:Gekiranger}. 
Together they do some research. 
They want to find out how to achieve his \Apotheosis{} and become the Twilight Angel he was meant to be. 
To do this they must work together with the Redcor. 

In the meantime, they discover that something abnormal is afoot in \Redce.
Something evil. 
Or is it? 

The Redcor want Carzain/Vizicar's help to fight this evil. 
(They mostly ignore and discount Shereid.) 
He is reluctant to ally himself with them too closely, but he would like to work with them to learn more. 
So he lets them think he is obeying their orders, all the while manipulating them. 
When he wants to, Carzain can look like a stupid, brash, impulsive boy who is easy to manipulate into doing stuff. 
But Vizicar, who lies and lurks in the back of Carzain's head, is much shrewder and often outsmarts the Redcor. 
(Be careful not to make the Redcor too stupid, though.)









\subsection{Sentinels}
Meanwhile, \Narkiza-tachi are advancing north. 
They have conquered some stuff. 
They want to control more land. 
They need some strategic locations in southeastern \Velcad{} in order to resurrect \Belzir. 

See, the Sentinels have been communing with \Belzir. 
They want her back. 
She has grown to hate the Cabalists.
If she returns, she will want to take revenge on them. 
But they also know that she is a \Mystraacht{} patriot. 
So maybe, if she returns, she will be able to go to \Mystraacht{} and conquer it. 
This will leave a third of the Cabal's strength under the command of a maverick with a giant grudge against the rest of the Cabal. 
The Sentinels want this. 
So they are supporting \ps{\Belzir} \quo{Royalist Faction}, who work to see her restored. 

But, but, but. 
The Sentinels must not be seen as actively supporting \Belzir.
That would be bad. 
Instead, the Sentinels act as if they know nothing of the Royalists and are just pursuing their own gambits.
Then, by sheer chance, they \quo{unwittingly} end up accidentally helping the Royalists achieve their goal. 
The Sentinels obstruct the Cabalists and Redcor who were trying to obstruct the Royalists, and so the Sentinels \quo{unwittingly} end up accidentally helping the Royalists achieve their goal. 

(Oh, yes. 
\ps{\Secherdamon} \trope{XanatosGambit}{Xanatos Gambits} can be complicated.) 

The Sentinels now have \Nithdornazsh{} set up. 
So far, so good. 
This will allow \ps{\Vizsherioch} to spread his \vertex{} influence and become the \hs{Dagger}. 

Meanwhile, the Royalists are abroad. 
They have to solve some Aenigmata in order to free their queen. 
The Sentinels covertly help them do it. 

The Rissitic invasion also drains Cabal and Redcor resources away from \Redce, where a vital piece of \Belzir{} lies. 
This means that when the \Redcean{} Royalist infiltrators strike, there are few Vaimons to oppose them, and mostly weak ones. 
(Obviously this casts no suspicion on the Sentinels. 
 They have plenty of good reasons for wanting more land in \Velcad.
 No one would suspect them of secretly supporting an obscure cult serving a rogue \resphan.) 





\subsection{Royalists}
The Royalists do not have a fixed plan. 
In order to bring \Belzir{} back they need the blood (or, more generally, lifeforce) of a \resphan. 
This is not so easy to come by. 
\Shiaraid{} \hr{Shiaraid unpopular}{does not have many immortal allies}. 
So \quo{lots} of Royalists are out in the world, questing, seeking for a source of high-quality immortal blood or lifeforce. 

One group has the mummy of a powerful \quiljaaran{} king, unearthed from an ancient tomb. 
They think this mummy might contain some magic that will help them, so they are bringing it to their headquarters. 

Then Ramiel appears.
In Pelidor he \hr{Ramiel scares Nzessuacrith}{semi-unconsciously unleashes his \sathariah{} power} and scares \Nzessuacrith. 
\Shiaraid{} immediately detects and recognizes him. 
She knows Ramiel better than any other and can recognize his \vertex{} signature in a moment. 

This is a godsend for \Shiaraid. 
For centuries she has been searching for a way to come back to life. 
Now her old lover is suddenly reborn. 
This is an opportunity she cannot afford to waste. 
She must secure his alliance. 
She then sends some Royalists hunting for Ramiel (including Shereid). 

In addition to Ramiel's help, \Shiaraid{} also needs a strong link to the Midnight Bat \matrix. 
This is where \hr{Sentinels help Shiaraid with Ghost Tower}{the Sentinels can help}. 





\subsection{Shereid}
\hs{Shereid} is the first Royalist to find Ramiel. 

She wants to \quo{recruit} him and make him ally himself with \Belzir{} and the Royalists.
But Shereid cannot reveal her identity too soon. 
If Carzain were to refuse her offer, she would be in danger. 

She and Carzain initiate a subtle dance of evasion. 
He (Vizicar) quickly picks up on the fact that she knows something she is not saying; that she is more than she appears. 
He tries to ferret it out of her. 
But she is a skilled deceiver herself. 
She does not want to tell him before she is sure he is on her side. 

So she tries her best to turn him against the Redcor and get him to like the idea of a Geican revolution, and personal power and glory and sex. 
She talks about how bad the Redcor are and how great it would be to be free of them, to see how he reacts. 
He tentatively agrees, but he is also wary of her and does not tell her too much. 
It is a delicate game of mutual distrust. 

At last she lets slip to him the possibility that \Belzir{} is still sort of alive. 
This makes Vizicar very interested. 
He very much wants to meet this other Scion and exchange knowledge with her. 
He has read some claims that she achieved \apotheosis. 
This idea gives him a boner. 

But he still does not trust Shereid. 
Carzain and Vizicar have an internal dialogue about how they will not let her control them. 
I should also have plenty of scenes where he criticizes her\dash to her face, to others or inside his head. 
This is meant to fool the reader into thinking that he does \emph{not} want to go along with Shereid's ideas. 

But in fact he does. 
He likes Shereid. 
Much better than the Redcor. 
So, in the end, he betrays the Redcor (including \Racel) and goes with Shereid to Geica. 







\subsection{Underground cult in \Redce}
In \Redce{} there is an underground cult of hopeful, gullible youths who worship dark powers and hope for some kind of reward or insight. 
It is very much an ecstasy cult, with sex-orgies. 
The young people get their sexual urges satisfied, and more so, with drugs and dark magic. 
Maybe the dark powers feed on their sex. 

Have sexy priestesses and erotic rituals, including live sacrifice. 
The sacrifices may be unwilling captives, or willing, or mind-controlled. 
It works best, I suppose, if it's sexy girls who willingly let themselves be killed in a sexual ritual of pleasure and pain. 

The sexy priestesses have power, but they ultimately crawl at the feet of the master of the cult. 
The master is a badass gangster, like Lex from the movie \cite{Movie:GargoylesRevenge}. 

\lyricslimbonicart{Twilight Omen}{
  I salute thee, baptizer of my soul.\\
  Dear pagan master, let thy universe unfold.\\
  Show me the sign of the midnight sky.\\
  I will forever follow until dawn's early light.\\
  From the ashes a fire shall be woken.\\
  From the shadows words shall be spoken.\\
  A star constellation, \\
  a burning circle of serpent eyes.\\
  Esoteric mysteries of unknown life.
}

The Cabal actually know about the cult. 
At first, they allowed it to exist.
Back then, it was clear that the cultists were not Sentinels.
The Cabalists did extensive research and found \emph{no} links from the cultists to any Sentinel-aligned \matrices. 
In fact, the cult's magic was not even real, just smoke and mirrors. 

Moreover, the cult serves a useful purpose as an outlet for the people's evil nature. 
The Cabal knows that people have evil lusts. 
The Redcor try their best to suppress those lusts. 
For some people, the internal pressure becomes unbearable and they must have an outlet. 
From the Cabalists point of view, this underground cult is as good an outlet as any. 
So they let the cult exist, but keep it under surveillance. 

(Note that only the Cabal know about the cult. The Redcor know nothing.) 

For a while this went fine for the Cabal. 
But then, unbeknownst to them, \ps{\Shiaraid} Royalists found out about the cult. 
In deepest secrecy, she had her people infiltrate the cult. 
Now she has quite a lot of influence in the cult. 
She does not rule the cult, but she has enough power to use the cult for her purposes, as long as she is crafty. 
She can run her own business in the shadows, and whenever her people are discovered she can frame the cult and have it take the heat for it. 
The cult is not so well-organized, so the cult leaders and the Cabal spies do not have an overview of everything the cult members do. 
\Shiaraid{} herself encouraged this infighting and chaos and division, because she knew that chaos and outlawry would be the perfect milieu in which for her to work her shady schemes. 

The Redcor have no idea that \Shiaraid{} is back. 
To their minds, she is an ancient enemy they defeated millennia ago, and (despite what they may say to frighten children and outsiders) they do not suspect she will come back to haunt them any time soon. 

Under the cover of a \quo{harmless} ecstasy cult, \Shiaraid{} has sent her spies crawling all over the place under the \TopazChateau{}. 
She knew the Redcor had a piece of her soul prison in their keeping. 
Now, after decades of spying and searching, she knows where it is. 
But she cannot get at it. 
She does not have any contacts in the \Chateau{} that are sufficiently high-placed or sufficiently powerful. 

Hence, it is extremely fortunate for her that Carzain is now in \Redce. 
If she can get him converted to her cause, he could help her get her soul-jar thingy from the Redcor. 






\subsection{Ghost Tower}
\target{Sentinels help Shiaraid with Ghost Tower}
In addition to Ramiel's help, \Shiaraid{} also needs a strong link to the Midnight Bat \matrix, and through it the \Erebean{} \dweomer. 
Ramiel cannot provide this. 
His \kenosis{} weakens his link to the \matrix{} and \dweomer. 

But the Sentinels can. 
The \hs{Ghost Tower} is a link from \Azmith{} to \Nyx, remember. 
\Secherdamon-tachi plan to conquer the Tower, then \cooperate{} with \Shiaraid{} and Ramiel to cast a complex spell that will penetrate through the Tower into \Nyx{} and tap into the Midnight Bat and the \dweomer, then tap the energy and channel it through the Tower, through a complex \quo{series of tubes} devised by \Vizsherioch{} and built with assistance from the Royalist Faction, all the way from Pelidor through the Beyond and into Geica, where \ps{\Belzir} body is. 
This energy, combined with Ramiel's help, will let \Shiaraid{} rise from the dead. 

But there is a problem. 
This could be detected. 
If the Sentinels start siphoning energy from \Nyx, everyone will know. 
And the Sentinels still do not want it known that they are in bed with \Shiaraid. 
So they do something sneaky: 
They make it collide with another long-term plan of theirs, namely that of \hr{Vizsherioch becomes Shaeeroth}{raising \Vizsherioch{} to \shaeeroth{} status}. 
They will perform both \ps{\Vizsherioch} \shaeeroth{} ritual and \ps{\Shiaraid} resurrection ritual at the same time. 
Most of the energy will be consumed by \Vizsherioch, but some of it will be siphoned away and used by \Shiaraid. 
That way, if this is discovered at all, it will look as if some clever Royalists infiltrated the Sentinels and installed a \quo{back door}, stealing some of the Sentinels' energy and siphoning it away to use for their own nefarious purposes. 
No one will ever know. 

Of course, in order for the Sentinels to accomplish any of this, they must first capture the Ghost Tower. 
This is not easy, for the \resphain{} have turned it into a bastion and are fighting to defend it. 






\subsection{Telcastora Ilcas}
\target{Ilcas suspects}
The Imetrium is taking an active interest in \Velcad. 
They are ancient rivals of the Rissitics and do not want the Rissitics to conquer and gain too much power (be it secular or metaphysical power). 

Telcastora Ilcas escorts Carzain-tachi to \Redce. 
Then he turns back to southern \Velcad. 
There he works with other Imetrians and allies to oppose the Rissitic plan. 

He has to deal with the sinister \nagae{} that are the allies of the Imetrium. 
Gradually, he discovers more about the Imetrium's involvement with \nagae{} and other wicked powers. 
He becomes slowly disillusioned with his religion. 
He is learning \hr{The truth about the Imetrium}{the truth about the Imetrium}, and it is a darker truth than he would have liked. 

Gradually he turns away from his commanders, and even his gods. 
But only a little bit. 
He has served the Imetric gods all his life. 
He remains true to the ideals he has always upheld. 
But he becomes more critical and distrustful. 

From the Imetrians' point of view, Ilcas serves an important purpose in this battle. 
His sword, \Telderain, is a powerful \vertex{} in the Imetric \matrix. 
So when they find out he has gone prancing off to \Redce, they quickly send for him and fetch him back to southern \Velcad{} where he is needed to form part of the metaphysical bulwark against \ps{\Secherdamon} Sentinels. 

(Note that the Imetrians are not necessarily opposing \emph{all} Sentinels. But they are certainly opposing \Secherdamon.) 

In the process, Ilcas will encounter \Narkiza. 
They find out they have a lot in common. 
But they are destined to be enemies. 









\subsection{\Mystraacht}
Some of the \Mystraacht{} have learned that Ramiel is alive. 
They want to kill him, \hr{Mystraacht rival goes after Ramiel}{so they hunt him}. 
But \hr{Azraid protects Ramiel}{\Azraid{} protects Ramiel}, as does \Cishiel{}. 

\Cishiel{} should not discover that Ramiel lives until late in the story. 
She and \Dasteron{} need to be introduced before that point. 

In fact, maybe \Cishiel{} should be postponed to the next book. 









\subsection{Rissitics}
We follow \Narkiza{} and his Rissitic army, who are fighting their way through southern \Velcad{} in a campaign of conquest. 
Their attack is partially meant as a diversion, drawing Redcor and Cabal attention away from more important matters such as \Nithdornazsh{} and the Royalist Faction's resurrection project. 

But the invasion also serves a useful purpose. 
\Secherdamon{} knows (or suspects) that the final breaking of the Shroud is near. 
He knows \iquin{} has a Hell of a lot of power. 
He wants to try to break that power. 
To this end, he wants to destroy the Redcor. 
He hopes to enlist the help of \ps{\Shiaraid} Royalists. 

The plan is that the Rissitics will move in to attack some Iquinian key strongholds and nations. 
If these fall, it will cause Iquinianism to falter on an \Azmith-wide scale. 

The Redcor know this, so they will set in as many resources as they can to fight off the Rissitics. 
This does not merely mean sending in a bunch of Vaimons. 
It also means calling in favours, pulling strings, drawing deep of the Redcor credit coffers and bullying allied rulers into banding together and fighting the Rissitic menace and defending the Iquinian world.

Meanwhile, the Royalists will resurrect \Shiaraid. 
This will be done in some place relatively close to \Redce. 
\Shiaraid{} will harbour a great hatred against the Redcor and will want to take revenge on them. 
With her \sathariah{} powers, her loyal Royalists and her covert Sentinel backing, she should be able to wreak a lot of havoc on the Redcor, which would seriously harm the Iquinian church. 
(And, with luck, this will not implicate the Sentinels at all and thus not expose \ps{\Secherdamon} long-term plan.)

If the Iquinian church can be destabilized, it will harm the global Shroud of Civilization that the church exerts over \Azmith. 
This will allow \Secherdamon{} to use gain more power in \Azmith{} and use the Realm to complete the forging of his Dagger. 





\subsubsection{\Secherdamon{} and Ramiel}
\Secherdamon{} does not know that Ramiel is back. 
And \Shiaraid{} does not tell him, even though they do communicate every once in a while. 
She keeps Ramiel a secret from \Secherdamon.

\Secherdamon{} discovers the secret near the end of the book, though. 
When someone helps \Shiaraid{} rescue her stuff from \Redce, Ramiel releases some powerful energy. 
\Secherdamon{} has been paying attention to what \Shiaraid{} is up to\dash she is his ally, but he trusts her only as far as he throw her\dash and this sudden burst of new energy interests him. 

\Secherdamon{} sees clear signs of activity in the Midnight Bat \matrix, and he hears some rumours. 
He puts two and two together and deduces that she has an ally who is a \resphan{} in disguise\dash perhaps a Scion. 

\Secherdamon{} or \Vizsherioch{} then talks to \Shiaraid. 
She is mentally unstable and has a hard time concealing her feelings, so \Secherdamon{} begins to suspect that her old lover, Ramiel, is back. 

At last the cat comes out of the bag. 
Ramiel kills \Shiaraid{} during her would-be resurrection. 
He can no longer hide his existence. 

(At this point, Ramiel knows who he is. 
 Maybe he has even taken contact with \Cishiel{}. 
 But maybe not) 

\Secherdamon{} is nonplussed and \hr{Secherdamon wants to off Ramiel}{wants to off Ramiel}. 


















\section{Carzain in \Redce}









\subsection{Carzain-tachi go to \Redce}
\target{Carzain goes to Redce}
Carzain-tachi go to \Redce. 

\hyperref[Curiet]{Curiet} has become the \hyperref[Curiet becomes rat-keeper]{rat-keeper}.

\target{Curiet's colour vision}
Curiet is a fop who cares very much about his clothes. Remember to have a scene where he talks about some \hr{Scathaese colour vision}{colour nuances that only \scathae{} can tell apart}.





\subsubsection{They meet Shereid}
They meet Shereid. 

Carzain notices her green eyes. 
He wishes he had green eyes. 









\subsection{Alliance with the Redcor}
\target{Carzain with Redcor}
%After the war, Carzain is discovered by the Redcor, who recognize what he is (a Scion) and attempt to sway him to their cause. The Redcor are matriarchal and \squo{sisterhood-like}. They are arrogant and manipulative, like the Aes Sedai and the Bene Gesserit. The Redcor are condescending and treat Carzain like a servant or an ignorant child. 

At length, Carzain reaches \Redce{} and joins up with the Redcor. His mother is Redcor-born, and her name, \Deracille, is a Redcor name of the lesser nobility, so Carzain, grudgingly acquiescing to using his mother's last name, is accepted. He is trained as a Gandierre by Lacquasse, whom he comes to like and respect. %I don't know if he actually joins the Redcor and becomes a Gandierre, or whether he merely fights beside them. 

He quickly learns to distrust the Redcor and not submit to them too easily. When his training as a Gandierre apprentice is complete, he is released from his bonds as an apprentice, and it is assumed and expected that he will take his vows as a Gandierre. But Carzain surprises them all by refusing to join the Gandierre. He has studied the Redcor laws and found a loophole, saying once free of apprenticeship, he has no more duties to the Redcor. However, he graciously offers to remain as their ally. The Redcor are less than happy about this, but they have to accept. 

%So he fights as a hero on the Redcor's side, chiefly against the Rissitics, but also against \Banes. 
%Somehow, they get him to join them, and he fights as a hero on their side. Their chief enemies are the Rissitics, who are trying to conquer \Velcad{}. He also fights various lords, \dragons{}, demons and things (Banes?). 
%Possibly he also fights the Quaerin.\footnote{The Quaerin are a Vaimon clan. They live in the Far North and are evil. Compare to the Seanchan in WOT.}. 

%During the whole thing, he is telepathically visited by powers attempting to convince him to join them. These include Rissit Nechsain, Bel'zhir the Dark Queen, and possibly others. 






\subsubsection{Carzain as an unwilling ally}
Carzain is unwilling, but somehow circumstances force him to work with the Redcor. He struggles to maintain the frame of an independent ally, while they try to turn him into a servant who should rightfully obey. 

I need to make up a good reason for this. Perhaps I can use a story similar to that found in the anime \cite{Anime:Dragonaut}, where Kamishina Jin is pulled into the Dragonaut organization without understanding what is going on. 










\subsection{\Redcean{} climate}
Remember what the \hr{Redce climate}{\Redcean{} climate} is like. 
This will influence the story. 









\subsection{\Esmerel{} has won a victory}
When \Esmerel{} brings Carzain back with her to \Redce{} and can prove that he is a Scion, it is a professional victory over some of her rival scholars.
Many of her colleagues refused to believe her theory that the \spike{} was a Scion. 
There were many other reasonable explanations, after all. 
But \Esmerel{} was a bigger Scion expert than any other, and she was certain her theory was correct. 
Now she has proven it. 

Carzain and Vizicar are not happy to be paraded as her trophy. 









\subsection{Carzain was wrong about \Esmerel}
Carzain sees \Esmerel{} in a new dress: Much lower cut, showing off a bit of cleavage. 

He tells her: 
\ta{\Matron{} \Esmerel, I was wrong about you. 
I understand now that underneath your gruff, arrogant and bitchy exterior, you are actually a real woman... with a pair of very nice boobs.}









\subsection{Carzain gains an enemy}
Carzain is placed as a subordinate to a Redcor. She bullies and humiliates him, treating him like a stupid child. He tells her: \ta{You have gained an enemy. You have me outnumbered today, but know this: One day I will kill you.} 









\subsection{Carzain sees the \Morbus{} in \Redce}
\target{Carzain sees the \Morbus{} in Redce}
Carzain walks around in \Redce. He ventures into the slums, where he sees the \hs{\Morbus} at work.







\subsection{Look at the zwongas on that one}
Carzain is in \Redce{} with a friend. 
A girl with very large boobs walks by. 

The friend exclaims: \tho{Look at the zwongas on that one!}

\target{zwonga}
\target{zwongas}
A \quo{zwonga} is actually an oriental fruit, a soft thingy like a very large plum. 
It is also slang for a woman's breasts, because a zwonga feels kind of like a breast. 









\subsection{I have zwongas}
Carzain is at a ball in \Redce. 
A serving girl comes up to him. 

Girl: 
\ta{Good day, sir. 
I have zwongas. 
Very nice. 
Would you like to try one?}

Carzain spewed and, for the next many moments, could only stare at the girl\dash and her zwongas\dash with a dumbfounded grin. 
He later learned that the girl was selling zwongas, which were actually a kind of fruit. 









\subsection{Carzain rescues ungrateful Redcor}
Carzain rescues a Redcor. 
She is a bitch from moment one, trying to order him around. 

Carzain: 
\ta{I haven't rescued you yet. 
If I were in your position, I wouldn't be mouthing off.}








\subsubsection{Carzain watches his language}
Later, she orders him: \ta{Watch your language, boy!}

Carzain: \ta{Fuck you. You can suck my big, sweaty cock until you choke on my cum and die.}







\subsection{Carzain practices archery}
From time to time in \Redce, Carzain practices archery in his spare time. 
He is a sucky archer, rarely ever hitting the target. 

It's a habit he inherited from Vizicar. 
In Vizicar's time they had guns, so archery was a sport, a harmless hobby. 
Vizicar was a sucky archer, too. 







\subsection{Carzain is lazy}
The Redcor try to get Carzain to practice dilligently, but he is lazy and would rather be a \boheme. 

But, from time to time, Carzain has flashes of mastery. This is typically when Vizicar (or an even older incarnation) awakens to help him, or take control. This frustrates the Redcor. 

It also serves as a subversion of the oft-seen \trope{AnAesop}{Aesop} that you must train and practice all the time to achieve greatness: Carzain pulls greatness out of his ass. (But not all the time. That would make him an annoying \trope{MartyStu}{Marty Stu}. Just once in a while.)









\subsection{Someone disbelieves Carzain's talk of monsters}
Carzain talks about monsters. Someone, a Redcor, immediately laughs. \ta{Surely you are imagining things.} Compare to episode 2 of the anime \cite{Anime:Gilgamesh}.

Vizicar immediately sees through the guy. 
\vizicar{%
  Too fast a reaction. He is trying too hard to conceal what he knows, to avoid suspicion. We need to keep an eye on him, Carzain.}









\subsection{Telcastora Ilcas faces off with a Trickster Mentor}
There is an old Redcor woman who tries to play the \trope{TricksterMentor}{Trickster Mentor} and be all hysterical and demanding. She tries to get people to jump through hoops for her before she'll help them. 

Telcastora Ilcas calls her out on it. 
\ta{Listen to me. 
  We are not supplicants begging a favour of you. 
  We come to you as equal allies and call upon you to do your \emph{duty}. 
  No more, no less. 
  And now you wish to hold the future of the world hostage to your own petty desires, your perversions? 
  Kindly explain to me, then, what makes you any whit better than the Rissitics? 
  What makes you any less of an enemy of the world?}

Carzain is impressed by Ilcas' ballsy-ness. 









\subsection{Ilcas comments on worms}
Some people eat food with Durcaci spice. 
They talk about the rumour that \hr{Spice and worms}{the spice is produced by giant sandworms}. 
They ask Ilcas about it, since he has travelled in Durcac. 

He says he \emph{thinks} it is true. 
But he has never seen these worms. 









\subsection{Carzain and Vizicar work together}
Carzain and Vizicar gradually learn each others' strengths and weaknesses and how to best combine them. 

\hs{Carzain is a better lover than Vizicar}. 

Vizicar's practiced diplomacy combined with Carzain's irreverent daring make them a great detective and manipulator, akin to Vlad Taltos from \authorseries{Steven Brust}{Dragaera}. 
(Vizicar on his own is a bit too constricted by principles and etiquette after having spent his whole life at court. Carzain teaches him to loosen up and be more open-minded and undaunted.)







\subsection{Vizicar surprised by map}
At one point Carzain looks at a map. 
Vizicar is in his head, reading along. 

\begin{prose}
  Vizicar: 
  \vizicar{Damn. This looks nothing like the maps I know.}
  
  Carzain: 
  \ta{Huh? Oh, right. Makes sense. 
    You lived before the \Darkfall, after all.}
  
  Vizicar: 
  \vizicar{The what?}
  
  Carzain summarizes what he knows of the \Darkfall. 
  
  Vizicar: 
  \vizicar{Interesting.} 
  
  Vizicar is especially intrigued by this \hr{Belzir}{\Belzir} character. 
\end{prose}







\subsection{Carzain hates the Redcor}
The Redcor are bitches. Carzain puts up with it for a while, but gradually, their arrogance makes him grow to hate them. 

The Redcor know that the Rissitics are up to something. Gradually it turns out that they mean to resurrect a \daemonic{} demigod, a \Haskelek{}. 
%See section \ref{Haskelek story} for details. 
%The \Haskelek{} is an old ally of the Sentinels and a terribly evil \daemon. It was brought to \Miith{} once about 1000 years ago (after Vizicar's reign but before \Belzir's) where it conquered and controlled a kingdom in central \Velcad{}, current day Pelidor and surroundings. But after a prolonged war, the \Haskelek{} was defeated by the Vaimons. 

%Unable to destroy it, the Vaimons imprisoned the \Haskelek{} in his temple, located in the middle of a huge, wild forest south or southeast of Pelidor. There it lay dormant, but its evil seeped out and corrupted the beasts and people in the surrounding area. The forests around its temple became dark, twisted and hostile (even more so than the regular \Miithian{} nature, which can be harsh enough) and the humanoid tribes to become degenerate savages who now worship the \Haskelek, or the memory of it. 

%There might be some planar stuff going on here, with the temple residing in another plane of reality. I should give this more thought. 

%Somehow the Rissitics reach the \Haskelekz{} temple and awaken it. It has grown stronger in the meantime by feeding off the prayers and sacrifices of his primitive worshippers, and is now almost as strong as before its death, but it needs powerful help to break free of its prison. The Rissitics free it. 

%The Redcor now oppose the \Haskelek{} and attempt to destroy it. It comes to a climactic battle, where they weaken \Haskelek{}, forcing it to retreat to its temple to recuperate. Redcor forces, including Carzain\dash and possibly Curwen\dash pursue him there, intending to reactivate the old spell seals and reseal the \Haskelek{} in its old prison\dash or something like that. 





\subsection{The Redcor leaders are incompetent}
The Redcor fight against the Rissitcs and Sentinels and the \Haskelek. But some of their leaders are incompetent fools. So, at times, Telcastora Ilcas or Carzain/Vizicar have to take command and lead their forces to victory. (In case of Carzain/Vizicar, it's more of Vizicar, since he is better versed in the art of war and commanding armies). 

Compare to Jarod Shadowsong in Richard Knaak's \emph{The Sundering}. When he leads the warriors into battle, compare to the king of Hyperborea in \bandsong{Bal-Sagoth}{The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire}. 







\subsection{Carzain runs from battle}
Carzain and some Redcor are in trouble, threatened by enemies. 

A \gandierre: \ta{We must fight! Honour demands no less!}

Carzain: \ta{I have a better idea: Run like Hell!}

Telcastora Ilcas: \ta{I must agree with \Shireyo. I have my own honour, but it does not require me to let myself die if I can do more good alive.}

Perhaps this is another instance of Ilcas inspiring Carzain to value his life above that of others\dash which, by utilitarian reasoning, is perfectly justified. 







\subsection{Carzain fails at etiquette}
Carzain gets owned regularly in \Redce{} because he does not know Redcor etiquette, or because he refuses to acknowledge it. 

He bitches and disses the hypocrisy of the Redcor rules and taboos. Perhaps he discusses it with Vizicar. Perhaps with Curiet Serpentin. 







\subsection{Carzain discusses philosphy with Shereid}
Carzain discusses \hs{Redcor philosophy} and \hs{Geican philosophy} with Shereid. 








\subsection{Carzain is fencing, no Vizicar}
Carzain is in a sword-fight. He tries to \quo{summon} Vizicar, who is a superior swordsman, and get him to come out and take control. But Vizicar is submerged in dormancy at that moment. 

Carzain is not a good enough swordsman to win on his own, so he flees. The Redcor are nonplussed by his cowardice. 










\subsection{Vizicar takes crazy chances}
Vizicar takes over their shared body and takes some crazy chances that nearly kills them both. 

\begin{prose}
  Carzain: \ta{You crazy fuck, are you trying to kill us?}
  
  Vizicar: 
  \ta{Well, I've already died once. 
    I got better. 
    That puts things into perspective, you know.}
\end{prose}










\subsection{Carzain shows off his game}
\target{Carzain shows off his game}
Carzain wants to prove to Vizicar that \hr{Carzain is a better lover than Vizicar}{he is a better pick-up artist}. 

He walks up to a hot girl. 
Makes eye contact. 
Comes close. 
Kisses her and grabs her breast under her clothes. 
Then he goes, without a word. 
Later that night, she seeks him out. 
They have sex. 

Compare to Satan from the movie \cite{Movie:EndofDays}.

Vizicar is improved. 
\vizicar{Wow. I could not have done that.}









\subsection{Curiet saves everyone by drinking Witchbane}
\target{Curiet drinks Witchbane}
At one point, Carzain or some other mage is just about to be poisoned with \hs{Witchbane}. 
But Curiet drinks the Witchbane instead. 
And a huge dosis, too. 
He suffers brain damage and becomes permanently deranged and retarded. 
A heroic but horrible end. 









\subsection{Carzain sacrifices himself by fleeing}
Carzain has the choice of rescuing someone\dash\Racel?\dash at great risk to himself, or flee and save himself. Inspired by Telcastora Ilcas's utilitarianism, he chooses the latter. 

\Racel{} survives and later confronts him: \ta{What did you think you were doing? Why did you not come and rescue me? You knew I was in danger! Have you no honour? As a man, it is your Light-given duty to risk your life to save a woman! Or are you no man at all? Are you truly so selfish, so cowardly, so petty?}

Carzain slaps her up. \ta{Listen to me, you cunt. \emph{I} am the Scion! \emph{I} am the one whom you Redcor rely on to save you. I am the most important person on this expedition. Without me, there is no mission. \emph{I am the mission}. Without me, all that you have fought to accomplish will be for nothing. It follows that my life is worth more than any of yours. My foremost duty, then, is to remain alive, that I may fulfill the mission.

Nay, it is you who are selfish. It is you who are petty. It is you, you Redcor fuck, who don't know the meaning of sacrifice. I would love to save your pretty little ass\dash and with it, it would seem, my honour and manhood\dash but I know my duty. For that, I am willing to sacrifice my honour among the Redcor if need be. 

That is one of the many things that separate us: You are a fool, a blind fool, trapped in dogma and hypocrisy. Whereas I am wise enough to know right from wrong without such stupid principles. That is why I am better than you!}







\subsection{Carzain reveals his friend's secret}
Carzain has a Redcor friend who confides a secret to him. He makes Carzain solemnly swear that he will not reveal the secret to anyone. 

Later Carzain suspects that something fishy is going on, and tries to solve it. He works together with some allies\dash possibly Shereid and Curiet. In order to solve this mystery\dash and save humanoid lives and potentially avert disaster\dash he deems it necessary to reveal the friend's secret. 

This is one of the first of Carzain's many broken promises.







\subsection{Carzain's \human{} enemy}
Carzain is standing and hating some enemy, possibly a Redcor. 

A friend of his defends the enemy, saying: \ta{When you look closer at her, she's really very \human{}. Look, she has all these nice qualities and does all these sympathetic, \human{} things...}

Carzain: \ta{So? How does that excuse her crimes? In fact, it makes it worse. If she was a piece of shit all the time, then she might have the excuse of stupidity or a bad upbringing or whatnot. But her \quo{\humanity} only shows that she can be worthwhile if she chooses. Alas, she chooses to be a stupid bitch.}







\subsection{Carzain learns to control his souls}
Carzain slowly learns to control the dead souls bound to him, and to channel them as a weapon. (See section \ref{Bound souls as a weapon}.)

Carzain unleashes this power by accident one or more times in the latter half of this story, in a fit of extreme anger, anguish or other emotion. He is horrified by what he has done, as is Vizicar. 

Describe the victim's fear and horror. Inspired by Clive Barker's \emph{Jacqueline Ess: Her Will and Testament}. 

Afterwards, Carzain is like: \tho{What the fuck? That was no \Qliphah, and it sure as fuck wasn't a \Sephirah!}







\subsection{Carzain disgruntled}
After their victory, some of the Redcor are praised for their great worth, but Carzain is neglected and gets no praise, only reprimands. This causes him to resolve to turn on the Redcor. Shereid urges him on in that direction. Ultimately, while out in the wilderness somewhere\dash perhaps on a mission\dash Carzain betrays his \Redcean{} companions and kills at least one Redcor, then flees to Geica with Shereid. 

%The Redcor are bitches. Carzain puts up with it for a while, but eventually, their arrogance has bred such hatred in him that he turns on them. So, while on a mission, he betrays his companions and kills them, including one or more Redcor. 

%that he willingly turns to evil. In his experience, those that call themselves \squo{good} are no better. So, while on a mission, he betrays his companions and kills them, including one or more Redcor. 

%He goes to Geica and learns to channel Nieur like the Geican mages do. When he returns, he is far more powerful than before. 















\section{Carzain and his Dreams}









\subsection{Ramiel's \Kenosis}
Ramiel has undergone the \hs{\Kenosis} and become a Scion. 
But the \Kenosis{} is imperfect and has split his personality and memories into Carzain and Vizicar. 

Vizicar tells Carzain that before they can hope for \hs{\Apotheosis} and regain their true power, they must first master and perfect the \Kenosis. 
They must become one. 









\subsection{Dreaming of \Cuezcan{} Spires}
\target{Dreaming of Cuezcan Spires}
Carzain/Ramiel has amnesia and does not remember his past as a \resphan{} lord. But he remembers scattered pieces and fragments. His memory loss pains him, and he makes it his great quest to discover who he is. 

Carzain falls sick. During this time, he has fevered dreams and visions where hidden presences whisper to him about his purpose, his quest, his destiny of greatness. 

He sees visions of terrible creatures, macabre gods and ancient, ruined cities. 

Later, we have another scene where Carzain/Ramiel broods. He searches his mind for clues about his past and identity. He takes poisonous drugs and uses dangerous magic and meditation to take himself into trance.

\lyricsbs{Bal-Sagoth}{A Black Moon Broods Over Lemuria}{
  Slumbering upon the throne of Moon-caressed ice\\
  I have supped deep the draught of white vapours.\\
  Shimmering upon the gleaming garlanded marble,\\
  a single strand of glimmering gossamer.\\
  In brooding and sombre visions I hear cries. \\
  Enthralling cries 'neath this frost-Moon rising.\\
  The whisperer in crystals speaks in dreams,\\
  of silken shadows and the softest breath of dark enchantment,\\
  of ancient cyclopean temples, raising jewelled spires to the stars.\\
  There is witchcraft in the moon,\\
  and a brooding silence reigns over the woods.\\
  My storm-forged sword,\\
  ensorcelled by eon-veiled incantations.\\
  Dark wizards' spells entwine me in ravening shackles,\\
  and black roses draw my blood with thorns as sharp as serpent's tooth. \\
  I fall into the rapturous embrace of sloe-eyed witches, \\
  the Moon gleaming upon their ivory bosoms,\\
  and descend into the still, icy waters of the lakes.\\
  Beyond the veil of the north-winds\\
  I await the emissaries of the tyrant.\\
  The wind whispering across the everlasting snows.\\
  My slumber is light as a wolf's...
}






\subsubsection{Ramiel's dark secrets}
Ramiel has dark secrets and dark dreams. See section \ref{Ramiel dreams}.





\subsubsection{He dreams of \Nyx}
In his dark dreams he sees \Nyx. 

\lyricslimbonicart{Deathtrip to a Mirage Asylum}{
  To the abyss' morbid enigmas.
  
  Far beyond the earthly grave,\\
  the soul betakes to drift astray.\\
  Infinite horizons of pale grey skies.\\
  A still born heart within there lies.
}

He somehow understands and remembers that even though \Nyx{} is scary and horrid, it was once his home, and thus remains his home. 

\lyricslimbonicart{Deathtrip to a Mirage Asylum}{
  The sanctuary that once was lost\\
  is streaming endlessly in holocaust.\\
  The astral corpse is still pulsating,\\
  in a mirage asylum awaiting.
}









\subsection{Carzain gets lost in strange Realms}
Maybe have a scene where Carzain somehow stumbles into another Realm and is led astray. 

He encounters creatures that are sworn to serve his kind, but have been alone and abandoned for centuries or more. Perhaps they are incorporeal, but he imagines them in humanoid form. And because of his power over them, they assume the form the thinks up for them.

Perhaps this is where he finds \Belzir, and she finds him.







\subsection{\Belzir{} contacts Carzain in dreams}
Carzain is visited in his dreams by a mysterious woman. In his dreams, they have sex. The wraith-woman tempts him with promises of power, glory and revenge upon the Redcor. It turns out that the woman is \Belzir, the last Empress of the ancient Vaimon Empire and called the Dark Prophet of Nieur by some. She wants him to join her and her servitors, who are working to resurrect her. 

She also approaches Vizicar\dash maybe both at the same time, maybe one at a time. 

She urges them to join her, tempting them with promises of power, glory, sex... and, best of all, knowledge. 
She knows he is a Scion, amnesiac and questing to master the \hs{\Kenosis} and eventually the \hs{\Apotheosis}. 
She tells him that she is a Scion herself, the only Scion ever to have attained the \hs{\Apotheosis}. 
This gives Carzain and (especially) Vizicar a boner. 
Vizicar very much wants to go to her. 
He does not know of her and has not been indoctrinated to hate her (since he lived before she did), and he doesn't like the Redcor, so he roots for her. 
Carzain is a bit more sceptical, with his heroic ideals and all. 

\Belzir{} tells him of how she was a rebel against the Vaimons and their oppressive religion. 
This impresses Vizicar. 
He wanted to do the same, but never had the will to actually do something about it. 
He admires her a bit. 

Carzain is stuck by the \hr{Belzir's sorrow}{immense sorrow and pain} she radiates. 
He notices the lines of tears under her eyes.

He is also attracted and enraptured by her emerald green eyes. 
He can feel the Geican eagle in her. 

When Carzain/Ramiel first encounters \Belzir, he is struck by her commanding, seductive being. 
It fills him with conflicting emotions: 
\begin{itemize}
  \item Sexual lust for her. 
  \item Intimidation; an inclination to submit and obey her. 
  \item A masochistic lust to let her sexually dominate him. 
  \item Shame at his own weakness and unmanliness. 
  \item Anger at her for making him feel shame. 
  \item Desire to punish her. 
  \item Lust to sexually dominate her. 
  \item Excitement at this challenge. 
  \item Respect for her strength, sexiness, seductiveness and boldness for making him feel all of the above. 
\end{itemize}

Later and gradually, he comes to realize this: 
\begin{prose}
\tho{I want to rule, to dominate her.
  Any opposite feelings I may experience are alien, unnatural things she plants in me through her manipulation and wiles, and which I have to combat with the power of my true self. 
  
  But \emph{she} has both: 
  She wants to submit to me, and she wants to enslave me.
  Perhaps both at the same time. 
  
  The last part is a scary thought. 
  Underneath the surface, who is really dominating whom? 
  If one of us pulls the other by a chain, who truly leads and who follows? 
  I am simple, but she is complex. 
  Damnably complex. 
  And that makes her even more dangerous. 
  I must not let down my guard with her.}
\end{prose}







\subsubsection{Sex with \Belzir}
Remember that \Belzir{} is herself a Scion, and she knows a lot about the \Malachim. She uses this knowledge to drop hints to Carzain/Vizicar and lead them on.

The sex scenes with Carzain and \Belzir{} should be Bal-Sagoth-esque: 

\lyricsbs{Bal-Sagoth}{
  Enthroned in the Temple of the Serpent Kings
}{
  Ruby-lipped and midnight-tressed, \\
  eyes as black as raven's wing.\\
  Flesh so pale as dawn-frost gleaming,\\
  nighted spells of the enchantress.
}

Or \Duana-esque (in the following, replace \quo{he} with \quo{she}):

\lyricsduana{nightsong}{Night Song}{
  at night he slips through my window \\
  cool air caressing me like a lover's moist tongue 
  
  I shiver new awakening \\
  moaning a rhapsody of vowels \\
  and consonants like crosses in a row \\
  his lips of bittersweet agony \\
  bruising tender flesh \\
  as I lay impaled by lust \\
  and hear the sound of my heart beating \\
  druming blood through my viens 
  
  his love is wild like wolf-song \\
  howling at the pregnant moon \\
  his voice is smooth as liquid velvet \\
  as he sings his soothing lullaby \\
  hush hush hush my pretty pretty one 
  
  until the dawn bleeds from darkness \\
  tangerine rays grazing my cooling flesh \\
  and he flees like the shadow of a dream \\
  leaving silence in his wake
}

\lyricsbalsagoth{The Hammer of the Emperor}{
  [She Came Bearing Dark Portents (The Foreshadowing):]\\
  Fever-dreams, dark omens and auguries. Prophecy!\\
  Why, when I meet your narcotic sloe-eyed gaze, \\
  does the image of a viper nestling in a bed of blossoms fill my mind's eye?\\
  Why, when you come to me by the pale light of a waning moon, \\
  do I glimpse the sheen of ophidian scales through the veils of sable?\\
  Why, when you enrapture me with your envenomed kisses, \\
  does the flicker of a serpent's tongue score my flesh?\\
  Enthralled by the vitreous lustre of your rubicund lips, \\
  your snow-pale skin musky with the intoxicating scent of night... \\
  but such wicket thorns beneath this rose.\\
  Come witch, fly to me!\\
}

Gradually through the book, his sex with \Belzir{} helps him remember fragments of his past life. 

\lyricslimbonicart{Symphony in Moonlight and Nightmares}{
  This night belongs to us,\\
  my dear princess of death.\\
  We have a destiny together\\
  as we meet in hungry caress.
  
  A deadly kiss under moonlit sky,\\
  as I stare into thy dark and hollow eyes.\\
  You take me down where cold silence dwells.\\
  Unconscious darkness realms of demise.
  
  You are born at my grace to serve only me.
  
  Blood paint on the wall is the ancient dream I recall.\\
  Predictions in rainstorm as tears dark red cascaded.\\
  In cryptic depths of imprisoned rage where I succumbed to temptation,\\
  in the laughter of cruel gods, demonic wrath and devastation.
  
  A monstrous enemy demands to be set free.\\
  Frigid evil games. Black art and blasphemy.\\
  Prophecies in blood.\\
  A deadly kiss unto darkened bliss.
  
  We have a gift of shining\\
  by knowing the history\\
  behind obscure mysteries.
  
  The mysterious source of true art and experience.
}





\subsubsection{From \ps{\Belzir}{} perspective}
We see one of the scenes from \ps{\Belzir}{} point of view. 

\lyricsbs{Emperor}{The Ancient Queen}{
  Dark rivers run though me.\\
  Darkness follows everwhere. \\
  Kingdoms falling again and again.
}

In a dreaming state, she flies to him. 

\lyricsduana{thedreaming}{The Dreaming}{
  Midnight wakes beneath a mystic moon \\
  as ominous mists waltz dewy down \\
  the nocturnal dance of mothwings beating \\
  soft staccatos and whispered wind \\
  the spirit of a shape transforming \\
  like a ghost of velvet shadows \\
  through a lattice silently creeping \\
  into a window open to the night \\
  steals between the gauzy drapes \\
  to find the sleeper \\
  lost in slumber \\
  dreaming, dreaming, dreaming. 
  
  She watches as his soul lies hid \\
  slack-jawed and lashes fluttering \\
  lost in the nebulous expanse of dreams \\
  the rise and fall of his shallow breathing \\
  she sighs sweet syllables in his ear \\
  from bloody lips smiling deeply \\
  whispers caress his naked skin \\
  moonpale gooseflesh shivering \\
  his mouth opens to her poisoned kiss \\
  his breath captured as he is waking \\
  eyes open wide to the terrible sight \\
  dreams to night terrors transforming \\
  she drinks his spirit red like wine \\
  as his voice is \\
  screaming, screaming, screaming.
}





\subsubsection{Geican principles}
Carzain believes it's a Geican thing to accept your sexuality and revel in it. 
\hyperref[Carzain is disappointed in Geica]{He is disappointed} when he gets to Geica...





\subsubsection{Shereid}
Carzain hangs out with \hyperref[Shereid]{Shereid}, a Vaimon woman of Clan Geican. She is secretly a follower of \Belzir. She and Carzain end up having a sexual relationship.  





\subsubsection{He is scared when he learns \ps{\Belzir}{} identity}
When Carzain first learns \ps{\Belzir}{} true identity he is scared. 
But she convinces him that she is really good, and merely the victim of evil propaganda and lies. 
At this point Carzain doesn't like the Redcor, so he is willing to believe much. 





\subsubsection{\Belzir{} and Vizicar exchange memories}
\Belzir{} and Vizicar exchange memories of life, death and afterlife as \malachim. 

\lyricsbs{Emperor}{The Tongue of Fire}{
  the soul is never silent\\
  but wordless, held imprisoned in a cursed tomb\\
  wherein reflections never fade, never die\\
  slowly maddened by the emptiness
  
  left to perish in the ever-dark coil\\
  yet, always alert it its slumber\\
  scorn by the drops of light\\
  piercing through the surface\\
  and it screams
}

They both long to regain their true and rightful power.

\lyricsbs{Emperor}{The Tongue of Fire}{
  teach me the tongue of fire\\
  so that I may set the world ablaze\\
  for it is cold\\
  and this blindness can no longer give me shelter\\
  teach me the tongue of fire\\
  so that I may cry out loud my wrath\\
  and my passion\\
  or else my coil will blister and decay
}









\subsection{Carzain has evil daydreams}
Carzain's nightmares escalate. He begins to suffer from daymares as well: Daydreams that pop up every now and then, where he sees into the Beyond or into his own imagination. He sees people's true faces, or they are horribly distorted. He sees monsters from the Beyond, or the ghosts that are bound to him, or spectres from his imagination. 

A horrific theme is the blurring of the border between reality and fiction. Or rather, Carzain gradually realizes how blurred the border has always been. Some of the visions he sees in his daydreams are lies, his half-mad subconscious mind twisting the Shroud further to fit its own fears. But some of the visions he sees are truths, with his terrified mind momentarily breaking through the Shroud and gazing into Reality. 

See, when a mind is under great stress, afflicted with powerful, stressful emotions, it may be able to draw upon reserves of primal strength that are otherwise latent and sealed away from the dumb, Shrouded mind. This may sometimes enable the person to penetrate the Shroud. Although sometimes, the stressed mind may be in an exceptionally vulnerable state, and the experience of seeing into true Reality might be extra traumatic. 

In Carzain's case, he is not immediately traumatized. Vizicar helps a lot here, since he has had to live with this for a longer time and knows more of how to deal with it. But Carzain begins to doubt both the reality around him, and his own sanity. And Vizicar's. Because we more and more learn how demented Vizicar is. 

\lyricsbs{Arcane Wisdom}{Symphonia Chaos}{
  Ghastly ghostly presences.  \\
  Insanity takes its place, \\
  while an effigy fades astray \\
  and memories still withstand. 
}









\subsection{Carzain is repulsed, but also attracted}
At first, when Carzain learns of the horrors that fill the universe, he is repulsed. He is swayed by the Redcor's talk of the Light and all that is good, and almost renounces the \quo{black} Geican magic with which he is brought up. 

Vizicar objects to Carzain's idealism, and Carzain lashes back by repressing Vizicar and shutting him out. Compare to Rand in \emph{Wheel of Time} or Gollum in \emph{Lord of the Rings}, who represses his evil side. 

But the longer he stays among the Redcor, the more he is disgusted by them, their hypocrisy and arrogance. When his faith in the Light falters, Vizicar creeps back and whispers in his ear. 

Gradually through the book, Carzain becomes disillusioned and bitter, and more and more fascinated by the dark powers of \nieur{} and other forbidden things. Having to fight against the Redcor's moral principles, he develops a distaste for all morals and comes to enjoy breaking rules and reveling in his power, obeying only his own will and whim. 

This is gradual, tho. Whenever Carzain discovers a new power of his or Vizicar's, he is repulsed and horrified at first, and only later comes to like it. These powers become guilty pleasures to him: They are useful, and he likes the intoxicating rush they give, but he also tries to deny it\dash on the outside, to keep it secret, but also on the inside, because he wants to maintain his own illusion of himself as a principled and righteous hero. 

At the end of this book, of course, he completely abandons and betrays the Redcor and goes to side with Geica. 









\subsection{\Belzir{} awakens}
\Belzir{} slowly awakens. 
She is still groggy and half-delirious from her long slumber... and only halfway sane. 
The first times she came to Carzain and had sex with him, she was in a hazy dream, too. 
She doesn't quite understand what is going on herself. 

In dreams, she teaches Carzain secrets. 
She speaks in riddles, because she thinks in riddles. 
It's all still dreamlike and cryptic to her. 
Besides, she's half mad from her millennia in limbo. 

\lyricslimbonicart{Deathtrip to a Mirage Asylum}{
  In limbonic life I've slept,\\
  dreamt that cryptic seals me kept\\
  sheltered from all visual sight\\
  'cause shadows chased every sign of light.
  
  Awakened from an ancient slumber,\\
  recalled to act of strife.\\
  My spirit old and body cold\\
  remain in dark demise.\\
  Immortality beloved am I to dying,\\
  and the whispering of secrets to my soul.\\
  I am born to sing this sorrow.\\
  Evil has no rest in me.
}

She still suffers and has horrible dreams from her time in limbo. 

\lyricslimbonicart{Deathtrip to a Mirage Asylum}{
  The invisible addiction of darkness, emptiness.\\
  And the ghastly silence devours.
  
  Deathtrip to a mirage asylum.
}

\lyricslimbonicart{The Dark Paranormal Calling}{
  The black funeral uniform gives me powers. \\
  I'm catching without warning the dark paranormal calling.\\
  A putrefied shadow that in purgatory dwells,\\
  imprisoned by the cold anxious pits of Hell.
}

She is a \hr{Disembodied souls}{disembodied soul} and hence weak. 
She wants a body back. 
To do this she has to break some spells. 









\subsection{Something inside Carzain mourns his loss}
Something inside Carzain/Vizicar mourns his loss. Perhaps this is a servant or servants (\humans? \resphain?) who willingly let themselves be killed and have their souls bound to him, to serve him as ghosts. But he lost his ability to hear them.

\lyricsbalsagoth{%
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  Can you not remember? \\
  Have you forgotten the magic?\\
  Sing to us your spells once more, \\
  and the ancient forest shall dance to your words...
}









\subsection{Carzain dreams of his destiny of greatness}
Carzain dreams of the greatness for which he believes himself destined, namely as Overlord of \Mystraacht{} (although he doesn't understand that yet). 
These dreams are more optimistic, but still dark. 

\lyricsdimmuborgir{Reptile}{
  Black uneartly void. Creatures crawling.\\
  Forbidden, forgotten, fairly underrated.\\
  Bastards in the shape of angels holding my hands,\\
  passing me what is left of the wine.
}

\lyricsbs{Marduk}{Infernal Eternal}{
  As I looked into the mirror, \\
  and saw the creation which was fading, \\
  I sailed the darkened waters of my soul \\
  on the ship of flaming hate\\
  towards the land of the damned.
  
  The cold winds of the darkness blow strongly.\\
  The cemetery glows in the dark.\\
  A thousand times, thousand voices \\
  are screaming in pain from beyond.
  
  A number of faceless shapes \\
  march forth from the darkness within.\\
  Life is slowly passing away, poisoned by guilt and sin.
  
  Embraced in Black I lie,\\
  only waiting to die. 
  
  The greatest of life's events,\\
  and I begin my journey\\
  as hands of greater characters unveil the world.\\
  Plunging through space and time, my prison has now been slain.
  
  The reaper purifies my soul.
  
  Perdition and death. \\
  I was in ages so dark and far away,\\
  and I will always be.
}

\lyricsbs{Emperor}{Cosmic Keys to my Creations and Times}{
  All these landscapes are timeless, \\
  and this is all just a part of cosmos, \\
  (but) all is mine and past and future is yet to discover... \\
  Much have been discovered, but tomorrow \\
  I will realise I existed before myself.
  
  I will realise planets ages old, \\
  created by a ruler with a crown of dragon claws, \\
  arrived with a stargate... \\
  a king among the wolves in the night... \\
  An observer of the stars.
}









\subsection{Dreams of his father}
Carzain/Vizicar dreams of his true father, \hs{\Zachirah}, who urges him on: 
\ta{\hr{Ramiel can do better}{You can do better!}} 

When he wakens, Carzain talks to Vizicar. 
They discuss who this \quo{father} figure might be.  









\subsection{SM sex with \Belzir}
In dreams, \Belzir/\Shiaraid{} plays her sex-games with Carzain/Vizicar/Ramiel. 
She is a \hr{\ps{\Shiaraid} sexuality}{sado-masochist}. 

She hopes to achieve one of two things: 
Either coerce Ramiel into submission or provoke him so much that his rage and pride will awaken some of his inner power and let him dominate her. 
Either way, she wins. 

Ramiel has his pride and refuses to submit, because he \hr{Ramiel is nothing}{fears being nothing}. 
He fights with all he has in him. 

She presses him to his limit. 
Her attempts at domination are not merely physical, but also psychological and social. 
She convinces him that he is indebted to her and that he has to serve her and submit to her if he is to keep in her good graces, so she will continue to graciously help him. 
She hints that if he is disobedient or incompetent or otherwise displeases her, she will punish him and make his life miserable (not just physically, but socially). 

At last he explodes in a mighty roar. 
The Shroud is broken, and for a moment she sees him in his true \resphan{} form, black-skinned and winged. 
But only for a moment. 
His \hs{\kenosis} once again takes over, and he lapses back into \human{} form. 
But some memories remain. 
She has brought him a great leap closer to \hs{\apotheosis}. 
He has \trope{TookALevelInBadass}{Gained a Level in Badass}. 

Up until this point, \Belzir{} has been quite arrogant and always teased and baited Carzain. 
But now he is Ramiel, and just as strong as she. 
She is exhilarated. 

\begin{prose}
  \Belzir: 
  \ta{You have long said that you would make me pay for my insolence.
    Come and take your revenge then, if you have the strength and the courage for it. 
    Punish me... my lord Ramiel!}
\end{prose}

He does. (In dreams.)

Compare with the sex scenes in \authorseries{Jacqueline Carey}{Kushiel's Legacy} with \Phedre{} and Melisande, or with \Phedre{} and Severio Stregazza. 

\lyricsauthorbookpage{Jacqueline Carey}{Kushiel's Chosen}{100}{
  [Severio Stregazza:] \\
  \quo{You... will... acknowledge... my... sovereignty!}
}





\subsubsection{\Belzir{} thinks}
Afterwards, Belzir thinks to herself: 

\begin{prose}
  \Belzir:
  \tho{He is good. And evil. I can use him. 
    Yes, he and I will go on to a fruitful and delightful partnership. 
    In bed, and out of it.
    And as for the \quo{acknowledge my sovereignty}, well... we will see about that.}
\end{prose}

But later, she has doubts. 
She does not remember everything of her former lives, but she knows there is something \quo{wrong} with her. 
She is \hr{self-destructive \Shiaraid}{self-destructive}. 
It worries her. 

She cannot recall the details, but she remembers one name: 
\Nexagglachel. 
He has cursed her somehow. 
She knows her lusts are dangerous to her. 
\tho{It is madness. But it feels so sweet...}











\subsection{Vizicar remembers the \angels}
Vizicar remembers the time of the Vaimon Empire, when everyone thought that the \Sephiroth{} and the \angels{} were good and all-powerful, and that evil in the world would soon be defeated. See section \ref{Vaimon Empire naivete}.

Later, he is very much shocked to learn that the \resphain{} are evil.







\subsection{Carzain encounters \vorcanths{} again}
Carzain has bad dreams, perhaps even manifesting in the real world. 
And \hr{Moon-Wolves help Ramiel in dreams}{the \vorcanths{} come to help him}. 

The \vorcanths{} actually need his help. 
He owes them favours for their having helped him in the past (distant and \hr{\Vorcanths{} help Ramiel}{near} past alike), so they are \emph{demanding} that he come and help them. 









\subsection{\Belzir{} tempts Carzain}
\Belzir{} tempts Carzain to delve deeper into the darkness. 
This is after he has become embittered with the Redcor. 

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  Return with me, beyond the stars.\\
  Rule with me a thousand worlds.
}

\lyricslimbonicart{Path of Ice}{
  Journey into your darkened secrets.\\
  Feel the burning flame inside.\\
  Admit the ecstacy of the extreme.\\
  Just close the eyes and enjoy the override.\\
  When we adrift through the sensual streams\\
  the enchanted pains are so divine.
  
  There are thorns everywhere,\\
  but along the path of ice rose bloom above.\\
  Blood is the rose of mysterious unions,\\
  the symbol of potency.\\
  A taste of erotic sins of lust.\\
  The entrance of immortality.
  
  There are such sights to see,\\
  Adventures and pleasures to feel.
}

\lyricsdimmuborgir{The Maelstrom Mephisto}{
  Dwell in depths of the darker self, at any shore of infinity,\\
  and watch the relentless paint the soil black.\\
  What is being formed echoes throughout eternity,\\
  as the painter chooses color no more.
}

She teaches him some magic. 

\lyricslimbonicart{Path of Ice}{
  The dormant seeds of suffering.\\
  The art of mortal flesh that bleed.\\
  Indulged in desire, the forbidden soul empire.
  
  Path of ice.\\
  The entrance to immortality.
}

He sees glimpses of his past as a mighty \resphan{} warlord, and glimpses of a possible future as a great sorcerer-king with \Belzir{} by his side. 

This also foreshadows the fact that he \emph{is} on a path to greatness. The book ends with Carzain contemplating his path from now on. He is becoming a character like Rio from \JuukenSentaiGekiranger, obsessed with the pursuit of power and greatness.

\lyricslimbonicart{Path of Ice}{
  Cold winds pierce through me\\
  as my dark star unfolds.\\
  I ascend the throne of fantasies\\
  where the beautiful abyss recalls.
}

She tells of how the \quo{pious} Vaimons betrayed her, even though she fought for freedom and enlightenment. 
Therefore she wants him to reject the Redcor, their religion and all conventional morality. 
(The Sun is a symbol of the Redcor and the Iquinian church.) 

\lyricsbs{Monolith Deathcult}{Den Ensomme Nordens Dronning}{
  Curse the Sun and all that's holy. \\
  Turn back. I dwell around. \\
  Come to me as a shadow. \\
  Engrave the Sun and the Blackest Moon shadow. 
}





\subsubsection{She tells him of the \Feud}
\Belzir{} tells Carzain a few secrets about the \feud{} and the master races. 

\Belzir: 
\ta{Mages are so obviously superior to the common people. 
Why, then, do they not rule the world? 
Why have there been no great sorcerer-kings since me, do you think? 

I will tell you: 
\emph{They} fear ones such as us. 
Whenever a mage starts climbing to power, they stab him in the back and take him down. 
}

Carzain: \ta{\quo{They}?}

\Belzir: (Dodges the question.) 






\subsubsection{Carzain sees \Belzir{} as a kindred spirit}
Carzain instinctively recognizes that \Belzir{} is a kindred spirit of sorts. 
This is vague memories from their time as \resphain, where they were both \Mystraacht, close friends and sometime lovers. 

He lets her seduce him and allies with her. 

\lyricsdimmuborgir{United in Unhallowed Grace}{
  We embrace the madness gathered as one.\\
  Mourning dead passion... she comes to me.\\
  A fate awaits us in the night.\\
  In the ruins of creation we will unite.
  
  I am smitten by forbidden fruit.\\
  Possessed by moments of dark splendour.\\
  To walk the nightmare terrains forever.\\
  The enigma lies broken.
}

\lyricsbs{Emperor}{The Ancient Queen}{
  Crawl to thee over again. \\
  The Ancient Queen, the darkest woman.\\
  Stepping through her shadow. \\
  She who sees the soul. \\
  Black is her blood. \\
  Keeper of the fury. 
  
  Stepping through her shadow. \\
  Do you see her soul?\\
  Black is her blood. \\
  Keeper of the fury. 
  
  Dark under the shadow. \\
  Thy destiny lies with her. \\
  The Ancient Queen, \\
  ruler of the domain. \\
  Keeper of the fury. \\
  In shadow... shadow.
}

It also brings back memories of the time when \hr{\Zachirah{} seduces Ramiel}{\Zachirah{} tempted Ramiel into joining \Mystraacht}. 
This is what \Belzir{} is planning. 
She remembers their time in \Mystraacht{} together (if not perfectly then at least partially), and she knows how powerful and effective those memories are. 















\section{Immortals and the \Feud}









\subsection{\Azraid{} protects Ramiel}
\target{\Azraid{} protects Carzain}
\target{Azraid protects Ramiel}
Ever since \hr{\Azraid{} learns of spike}{\Azraid{} learned the details of the \vertexspike{}}, he has taken on the role of Ramiel's \quo{guardian angel}, subtly pulling threads and protecting him from harm while he grows towards his \apotheosis. 

This is necessary. 
Many forces conspire to kill Ramiel's Scion.







\subsection{Cabalists hold out in the Ghost Tower}
The \hs{Ghost Tower} is the Cabalists' bastion in Pelidor after they lost Malcur. They use it as a staging area to mount offensives. Due to \hyperref[Charcoal at the Ghost Tower]{Charcoal's clever spell}, later improved and strengthened by \Achsah, the Tower is easily defensible. 

\Achsah{} and Charcoal hold out in the Tower, command their Cabalist minions, and maybe \hr{\Achsah{} rewards Charcoal}{have sex}.





\subsubsection{\Achsah{} is inherited by a new mistress}
After \ps{\Teshrial} death, \ps{\Achsah} allegiance passes to another \resvil, a \Mystraacht{}, to whom \Teshrial{} was indebted. 

\Mystraacht: 
\ta{%
  You belong to me now.}

The \resphan{} tongue has many words for \quo{belong to} and \quo{have/possess/own}. 
She used one of the more respectful ones, but her tone and body language practically scream: 
\hypota{You are my slave.} 

\Achsah: 
\tho{%
  These \Mystraacht{} have no etiquette. 
  I miss \Teshrial{} already.}

Even so, it's not so bad, because the \Mystraacht{} are less snobbish and don't look down on her so much for her blood. 
They respect her more for her strength and skill. 









\subsection{Charcoal leaves the Ghost Tower}
To begin with, Charcoal is in the Ghost Tower with \Achsah. He helps her fight off the Sentinels, and she rewards him with sex. 

But eventually \Achsah{} sends him away on some mission. 









\subsection{Cabalists oppose the \Haskelek{} fragment in \Redce}
\Redcean{} Cabalists fight against a fragment of the \Haskelek. 
It is difficult, because they have to be covert and work indirectly under the nose of the nosy Redcor. 









\subsection{\Mystraacht{} rival goes after Ramiel}
\target{Mystraacht rival goes after Ramiel}
A \resphan{} of \Mystraacht, allied with a faction that hates Ramiel and does not want him to return, is pulling strings in \Redce. 
Trying to oppose Carzain and get him killed. 

This guy is approached by \Azraid, who asks him to stop. 
\Azraid{} \hr{\Azraid{} protects Carzain}{has his own plans for Ramiel} and does not want this guy to interfere. 

\Azraid{} is very polite, but in a sinister way, with an undertone of threat. 

\begin{prose}
  \Azraid:
  \ta{%
    You are not under my command, of course, so I cannot force you to do anything.
    But I can \emph{request} that you desist and cease interfering with Ramiel.
    I hope you can be persuaded to acquiesce to my request. 
    Otherwise I should be... saddened. 
    
    And by desist, I mean desist completely.
    Do not try to pull any strings.
    Do not interfere with him at all.
    
    Please consider my proposal.}
\end{prose}

After this, \Azraid{} figures that his veiled threats are probably not quite enough. 
So he contacts \Cishiel. 
Tells her about the affair. 
She is very interested. 

He sits back and is happy.
He knows \Cishiel{} will help keep Ramiel safe from meddling \Mystraacht{} busibodies. 
\Azraid{} was not confident he could keep them all away. 
But \Cishiel{} is very skilled. 
She has had to become sly and cunning just to survive. 
She has quite some insight into \Mystraacht, and she knows very well who Ramiel's enemies are. 
The two can work together and supply each other with information, which should be enough to keep Ramiel alive and guide him to a path where he can regain his memories and power. 










\subsection{\Vizsherioch{} and \Secherdamon}
Have scenes with \Vizsherioch{} and \Secherdamon{} at home, and show their relationship. 
Perhaps \Vizsherioch{} recommends that his father send him out, after his other minions have failed. This is the first time we see \Vizsherioch. 







\subsection{\Humans{} are special}
Some high-up Cabalist or Sentinel is talking to a \human.

\ta{The old days are gone, and so are the old master races. They may not know it, but their time is up. They had their time and now they are decline. 

Oh, they may still be strong, they may still have raw power. But they are locked in place. They are slaves to their own game, unable to break from it. 

But you \humans... you are special. You are unique. You alone possess true freedom of will. And it is this special \human{} quality that, in the end, will decide this war. All the power of the elder races is nothing compared to the gift that is \emph{\humanity}. This is the age of men, and the future lies in \human{} hands.}

Afterwards, he walks away, thinking to himself. \tho{By the \Voidbringer, that was disgusting. I almost feel dirty for spinning such an outrageous lie. I can hardly believe that he bought it. Heh. But that is \humans{} for you, is it not? So easily manipulated, so easily tricked into believing anything you tell them.}

\tho{Hah. \quo{True freedom} indeed. \quo{The gift of \humanity}. Hah.}

\tho{Foolish worms.}









\subsection{A \Haskelek{} fragment possesses a mortal host}
A mortal \scatha{} or \human{} is possessed and used as a host body by one of the fragments of the \Haskelek. 
This might be \hs{Lica}.

The fragment is only half-awake, so the mortal carries it around for a long while. 

The victim is slowly driven mad by the presence of the \Haskelek{} inside her. 
It is alien and terrifying. 
She tries to interpret and put into words those alien thoughts, emotions, images and visions that the \haskelek{} sends into her mind. 
The only recognizable emotion that comes close is... hate. 

In the end, the fragment breaks out of her, and her body explodes. 
Compare to the people possessed by Nyak in \authorbook{Stephen Marley}{Spirit Mirror}. 

\lyricslimbonicart{From the Shades of Hatred}{
  A thousand years time dimension \\
  in subconscious incarceration. \\
  My hatred to man, has transformed me \\
  into a habitation for demons. \\
  A devil incarnation. \\
  In the forgotten past, ages ago, \\
  beast became my alter ego.
  
  The god in me, infernal black divinity.\\
  After years of agony and pain \\
  hatred is all that remains.
}









\subsection{\Dzasselid{} explores the Beyond and gains knowledge}
\Dzasselid-tachi are on a mission. He needs more knowledge. 

Have a scene where he casts divination spells, explores the Beyond and gains some kind of enlightenment. See section \ref{The dark universe}.

\lyricslimbonicart{Dynasty of Death}{
  I'm launching into the abysmal universe.\\
  Disembodied I enter the cosmic cataclysm.
  
  I discover stairways to celestial dreamscapes\\
  A dark unknown conjunction within an immoral dimension.
}

Remember that the Rissitic \humans{} are dark-skinned. 
They should remark that \Velcadian{} \humans{} are much paler. 









\subsection{Someone finds a desecrated corpse}
Someone, investigating the strange happenings that have occurred lately in \Redce, finds a corpse that has been killed and desecrated by the underground cult. It is mutilated, perhaps with the skin torn off, and bears clear signs of sexual abuse (perhaps covered in sperm after bukkake). 

Maybe something a la Clive Barker's \emph{The Midnight Meat Train} (from \emph{Books of Blood I}). 









\subsection{\Narkiza{} fights and Belgrim almost dies}
\hr{Narkiza}{\Narkiza} fights in a great battle. \hs{Belgrim} takes grievous wounds and almost dies. But with massive, heroic effort, Belgrim rises again, roars its defiance and fury, then charges and causes immense destruction. He collapses again. 

\Narkiza{} fights off the enemies to keep Belgrim safe. He is not skilled enough to heal him, but he has enough spells to send Belgrim into a deep, ensorcelled sleep, stabilizing his wounds until they can find mages and have him healed. 

Belgrim lives.









\subsection{Raising the \Haskelek}
\target{Raising the Haskelek}
The Sentinels begin raising the \Haskelek. 

There are three parts, called the Hand, the Eye and the Heart. 

The strongest part is the Heart. It is imprisoned in a forgotten temple deep in Heropond forest. It's in the southern part of Heropond, where the forest is thickest. It is the hate, madness and evil of the \Haskelek{} Heart that has corrupted Heropond and made it a dark, haunted place of monsters and diabolist savages. (There might be some planar stuff going on here, with the temple residing in another plane of reality. I should give this more thought.) 

The Hand is in Sumian, buried in a secret, shunned tomb. 

The Eye is in northern Pelidor, near \Forklin. It lies in an enchanted tower which exists in \Nyx{} but can be glimpsed from the physical world. It is called the Ghost Tower, and the locals fear to come within sight of it. 

%Somehow the Rissitics reach the \Haskelekz{} temple and awaken it. 
The \Haskelek{} has grown stronger in the meantime by feeding off the prayers and sacrifices of his primitive worshippers, and each part is now stronger than after its initial defeat at the Vaimons' hands. But still, each part is not strong enough to break its prison, and so they need pwoerful help to escape. In come the Rissitics, who attempt to free it. 
%and is now almost as strong as before its death, but it needs powerful help to break free of its prison. The Rissitics free it. 

The Eye is the first part to be released. Soon after the Rungeran forces conquer \Forklin, the Rissitic mages move in and begin the spells to awaken the Eye. It takes humanoid form\dash a humanoid is sacrificed to it, and it occupies his/her body. 

The Hand is the second part to be released. It happens near the end of the first book. After a long quest, Sir James and Lica fail and are killed. The Sentinels successfully awaken the Hand. They use its power to scour the area of opposition, securing a strong foothold in Sumian. Then the Hand goes to Pelidor to join the Eye. 

Now Carzain and the Redcor come in to stop them. A lot of stuff happens. 

%The Heart is released, but eventually the resurrection process is stopped and the \Haskelek{} returned to sleep. This is not necessarily the end of the \Haskelek{}, but it will take a lot more work to awaken it again. I don't know how this goes on exactly. Perhaps they destroy some artifact that was vital to the process. 

Eventually the Heart is released, but before the three parts can be united as one again, Carzain and the Redcor storm in and attack. They succeed in breaking up the ritual, weakening (some of) the \Haskelek{} parts and forcing them to retreat.
%The Redcor now oppose the \Haskelek{} and attempt to destroy it. It comes to a climactic battle, where they weaken \Haskelek{}, forcing it to retreat to its temple to recuperate. Redcor forces, including Carzain\dash and possibly Curwen\dash pursue him there, intending to reactivate the old spell seals and reseal the \Haskelek{} in its old prison\dash or something like that. 

Ultimately, Redcor forces, including Carzain\dash and possibly Curwen\dash destroy the physical bodies of the Eye and Hand, possibly the Heart, too. This breaks them up.

See, each part is still bound to its tomb, but is able to project its power into a possessed body and thus walk abroad. But if that body is slain, the \Haskelek{} part is sent back to its prison, and a new ritual must be performed to release it again. After the defeat of the Hand and Eye, the Redcor (with Cabal aid) storm the Ghost Tower and/or the Hand's tomb and besiege them, thus preventing the three parts from easily uniting again. The book ends in a victory for the Redcor, but one that leaves Carzain bitter and resentful (see section \ref{Carzain with Redcor}). 















\subsection{\Daggerrain{} knows it all}
Have occasional references to \hs{\Daggerrain}, hinting at his status as \trope{TheChessmaster}{Chessmaster}. He pulls all the strings and knows everything. The reader should be kept guessing as to how much of the story was actually orchestrated by \Daggerrain. 

Have Cabalists going: \ta{Yes, \Daggerrain{} predicted that this would happen...}

An interesting twist might be to have \Secherdamon{} acting as a counter-Chessmaster, at times eaving pulling \trope{XanatosGambit}{Xanatos Gamits} on \Daggerrain.

Compare him to the Crippled God from \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}. 









\subsection{\Cishiel{} and \Dasteron}
\hs{\Cishiel} is allied with \hs{\Dasteron}. 
He wants to be Overlord of \Mystraacht, and she wants to help him. 
They are already lovers and have had plenty of sex. 
Often in public. 
That is \hr{\Mystraacht{} sexuality}{a \Mystraacht{} thing}. 





\subsubsection{Submissive \Cishiel}
The two devise a ploy to gain publicity: 
\Cishiel{} will sexually submit to \Dasteron{} in public. 
This will garner tons of attention and make them both look interesting and cool. 
It will make \Dasteron{} more alpha-male-ish and give him a little bit of \Zachirah-image. 

He invites her to a party at his place, or she invites him. 
As soon as they meet, she kneels down without a word and sucks his dick. 
She swallows, licks it clean, then stays on her knees. 
He grabs her hair and violently pulls her head back. 
She is in pain as she says: 
\quo{Thank you, Lord \Dasteron.}

He remains quiet. 
Throws her down to the floor and walks away. 
She remains on the floor for some seconds. 
Then she rises and meekly follows him. 

Then, at dinner, they both act like it didn't happen;
as if it were the most natural thing in the world. 
(Of course, they also have sex that night.)

Another possibility is to have \Cishiel{} act like a willing slave for \Dasteron. 
During dinner she kneels by his side. 
He caresses her hair and head, at times violently. 
When he is angered (by something else), he grips her hair and yanks her roughly. 
She moans and whimpers in a sexy way. 

Slave-girl \Cishiel{} is dressed in a skimpy bikini. 
Not naked as \hr{Resphan slave livery}{a \Mystraacht{} slave would normally be}, but close enough to naked to invoke associations of slavery. 
And a tight necklace reminiscent of a slave's collar. 
\Dasteron{} tried to make her wear an actual slave collar, but \Cishiel{} drew the line there. 
She was willing to endure much humiliation, but not that much. 

Everyone else knows that it was planned and constructed to make him look cool and give him publicity. 
But it still works. 
\ps{\Dasteron} rivals cannot help but be affected, even though they know it is a ploy. 
And \Dasteron{} knew they would. 

\Cishiel{} is, of course, richly compensated in favours. 
And it also reflects on her standing. 
She gains a certain naughty, erotic allure: 
\ta{Imagine the daring, that she would do such a thing!}
\hs{\Resphain{} are possessive}, and \Mystraacht{} perhaps more than any.
Now, whenever a \resphan{} sees her he thinks \quo{submissive sex slave} inside his head, and he gets obsessed and must have her. 
This gives her a great deal of power and political influence, and she knows how to use it. 

She muses over it. 
She has broken the rules of sexual conduct. 
In \CiriathSepher{} such an act would leave her branded as a slut with no self-respect. 
But in \Mystraacht{} it has the opposite effect. 
\Mystraacht{} is founded on a spirit of rebellion and anarchy; they hunger for sensations and turmoil. 
Breaking the rules is admired. 
She has been naughty and broken the oppressive \CiriathSepher{} morality, and the \Mystraacht{} love her for it. 





\subsubsection{\Cishiel{} hears rumours about Ramiel}
\Cishiel{} hears rumours that Ramiel is returning. 
She gets excited and goes looking for him. 

\Dasteron{} learns of it. 
It drives a wedge between him and \Cishiel. 
But they still have sex, and they still cooperate. 
It adds some spice, some challenge, some excitement to their relationship. 
They are \resphain{} of \Mystraacht, after all. 
They thrive on conflict. 

They end up enjoying this game, where they both try to extract information and favours from one another. 
They are now rivals. 
They manipulate and distrust but respect each other. 
And they have exciting, dangerous rival sex. 





\subsubsection{\Dasteron{} rapes \Cishiel}
Later, \Dasteron{} suspects \Cishiel{} of having done stuff to harm him behind his back. 
(She knows Ramiel is back. He does not know yet.) 

So \Dasteron{} comes and threatens \Cishiel. 
But she is clever. 
She manipulates him and re-frames his threats as a sex game. 
It ends with him mock-raping her and her mock-pleading for mercy. 

After he is done raping her and has dressed again and is about to leave, he turns around. 
She is still naked and lying on the bed. 
He gives her a long and intense stare. 
He makes her feel even more naked than she is. 
She wants to wrap her wings around her naked body in protection, but she does not want to show such a surrender to him, so she just lies there and lets him stare. 

Without words he tells her: 
\begin{prose}
  \Dasteron: 
  \ta{You tricked me today, \Cishiel. 
    But I will get you. 
    Mark my \quo{words}.}
\end{prose}










\subsection{\Dasteron{} becomes Overlord}
\target{Dasteron becomes Overlord}
\Dasteron{} made himself Overlord by gathering enough support to beat down those who disagreed. 
This had taken more than a thousand years of concentrated work. 

\target{Dasteron cannot become Apex}
But \ps{\Dasteron} power and skill is chiefly political, not metaphysical. 
He lacks the \vertex{} strength required to make himself \apex{} of the \Mystraacht{} \matrix. 

At the point when he becomes Overlord, \Cishiel{} has learned of Ramiel's return and is working behind \ps{\Dasteron} back to support her father. 









\subsection{\Vizsherioch{} becomes a \shaeeroth}
\target{Vizsherioch becomes Shaeeroth}
\Vizsherioch{} becomes a \shaeeroth.
This is the culmination of the whole \Nithdornazsh{} gambit. 
\Nithdornazsh{} was a stepping stone for \Vizsherioch, to enable him to contact the \xss{} and harness the power that would make him a \shaeeroth.

No one anticipated this. 
Most people have forgotten that \shaeeroth{} could be created, since \hr{No more Shaeeroth created}{no more had been created} in the last thousands of years. 
Plus, most people do not know \Vizsherioch{} even exists. 

The kind of invocation needed to become a \shaeeroth{} is different from most of the invocations that summon forth monsters or other stuff to do the mage's bidding. 
Therefore, when \Vizsherioch-tachi prepared and performed the deed, it was not seen as such an apocalyptic thing, so the Cabal did not really move out in force against them. 
They did not understand the magnitude of what was happening, because it was so atypical, and it looked relatively benevolent (or, at worst, self-destructive). 















\section{Ramiel's Defection}
Ramiel betrays the Redcor and defects to the Royalist Faction. 







\subsection{Carzain sacrifices \Racel} 
Somehow Carzain and the Redcor, fighting against the evil Royalist cultists, set up a gambit where Carzain poses as a turncoat who wants to join \Belzir. 

He tells the Redcor of his plan. 
\Belzir{} has long tired to seduce him, and he has let himself be seduced to an extent, but he has always defied her in the end. 
(We have seen this.) 
But now, he says, he thinks he can fool her. 
And here is how... 

The reader must not know his entire plan. 
Then the genre-savvy reader will know it will fail. 
\trope{UnspokenPlanGuarantee}{Unspoken Plan Guarantee}, remember. 

He sneaks in in order to infiltrate the Royalists so the Redcor can stop them. 
He now has his hands on \hr{Belzir}{\Belzir} soul-jar, which the Redcor had been keeping secret and hidden from everyone. 
He has persuaded them to give it to him because he says he can destroy \Belzir{} with it. 

\Racel{} is with him, for some reason. 

The Royalists do a \trope{ShootYourMate}{Shoot Your Mate}: 
They tell Carzain that if he is with them, he should kill \Racel. 

Carzain walks towards \Racel. 
She is nervous, but knows he would never kill her.
He moves closer.
She becomes afraid.
\tho{What is he planning?}

He kills her by chopping her head off. 

See, Carzain had been playing the Redcor for fools. 
He wanted to get in on their gambits and know as much of their insider knowledge as he could. 
But now he thinks he has learned as much from them as they are willing to let him, so he seeks greener pastures. 
He betrays them and joins \Belzir. 
He knows she can be of tremendous help to him.
He gives her the soul-jar, and she is now almost ready to return to life. 







\subsection{Carzain flees to Geica} 
Carzain flees to Geica, together with Shereid and possibly a few others. (Curiet? Maybe even Ilcas?) They meet up with other members of the Royalist Faction (the followers of the Dark Queen), including Senator Hayad. From here, the next step is to conquer Geica from within. (Geica has a democracy; they mean to seize it by a coup.) 

\emph{New idea:} 
At this point, Carzain is not evil, albeit disillusioned. 
Shereid convinces him that there are forces in Geica that are better than the Redcor. 
She introduces him to Hayad and some others, who make a good impression on him. 
It takes a while before he learns that the one behind it all is \Belzir. 
He balks at this, because he has always been told that \Belzir{} is evil, but they all argue that she was less evil than the stories say, that the Redcor and other wicked folks deliberately blackened her reputation\dash and that it was in fact their rebellion that caused the empire's fall, not \Belzir's just retaliation. 
After a while, Carzain accepts this. 
After all, he hates the Redcor and is willing to believe much bad about them. 
He also balks when he learns that they mean to conquer Geica by a coup, but after spending some time among the Geicans, he is convinced that they are little better than the Redcor. 







\subsection{Carzain allies himself with \Belzir} 
Carzain allies himself with the Dark Queen, and she sends demons to aid him. 
She wants him to help resurrect her, that she may return to \Miith{}. 
To this end, she gives him a magical orb. 
Carzain agrees, but plots against her. 

Carzain joins \Belzir's armies. 
He is equipped with the sabre and the \hs{Archon Ward} that belonged to her son Zacrias (the most powerful of \Belzir's many children, who succeeded her as Lord of Clan Geica after her death). 
He also gets two antique \hr{Vaimon guns}{Vaimon pistols} (magical and powerful). 

\Belzir{} also summons a Peryton (a hind, whom Carzain names Venom) to serve him. 

\lyricsbs{Emperor}{Witches' Sabbath}{
  Shifting shadows guide my way in the autumn. \\
  From this fell alliance eternal night shall arise. \\
  Hear the scream of the wolves calling again. \\
  Legions are wreaking destruction upon the fortress.
}















\section{Carzain in Geica}
\subsection{Geica is corrupt}
\target{Carzain is disappointed in Geica}
Carzain has been filled with stories of how glorious Geica is. He has heard and read stories of the splendid, enlightened Geica as it looked during the time of the \hs{Vaimon Empire}. He sees it as a proud, enlightened, freedom-loving and free-thinking culture where all men are equal and free to achieve their goals and live for their ideals, and also a Mecca of learning and wisdom. 

But he is sorely disappointed. The real Geica is corrupt, a cesspool of hypocrisy, bureaucracy and greed. I need to underline the avarice, pettiness and treacherousness of the Geicans. 

Have a named guild of politicians, lawyers and the like (\quo{\DJOF'ers}\footnote{\quo{\DJOF} is Danish for \quo{Danske Juristers og \O konomers Forbund} (or something like that), the \quo{Danish Lawyers' and Economists' Association}.}), who are made the scapegoats and blamed for the corruption of Geica, by virtue (or vice) of the materialistic world view they spread. 

Compare to the Letherii culture in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}, and especially Chancellor Triban Gnol and Invigilator Karos Invictad. 

Perhaps the Geicans own no slaves, only life-long indentured serfs. Compare to the Indebted in Lether. 

This is a part of Carzain's process of disillusionment with all that is good. 

According to \Belzir, it has been going downhill ever since her death. She represented the pinnacle of Geican civilization, but history has posthumously vilified her. Her son \hs{Zacrias}, who succeeded her, did his best to carry on her legacy. His successors were less dilligent and less faithful. 

Perhaps Geica's decay is a result of being vilified, demonized and hated by the rest of the world, especially the \hs{Redcor}, who blamed the Geicans for \Belzir{} and the \hs{\Darkfall}. 

Compare to House Harkonnen in \authorbook{Brian Herbert \& Kevin J. Anderson}{The Battle of Corrin}, who descended into evil after being abandoned by Vorian Atreides. 

After all this corruption and hypocrisy, \ps{\Belzir}{} bloody and violent coup almost seems an improvement. The \hs{Royalist Faction} have ideals of \quo{awakening to life the true Geican soul and legacy} and overthrow the corruption and decadence that has festered like a disease, a vermin infestation, in the absence of the true Geican spirit and way of life. They fight for the true Geica and seek to awaken the people. 

Compare them to Bruthen Trana and his Tiste Edur in \MalazanReapersGale. 





\subsubsection{True ruler is not good}
\ps{\Belzir} brutal coup is intended as a subversion of the \cliche{} of \quo{rightful ruler returns to the throne and all is good}. 





\subsubsection{Limyaael's ideas}
See \href{http://limyaael.insanejournal.com/205202.html}{Limyaael's rant on political systems} for inspiration and ideas on how to flesh out the Geican political system. 

See also \href{http://limyaael.insanejournal.com/205202.html}{Limyaael's rant on \quo{council scenes}} for inspiration regarding political intrigue and debates. 







\subsection{Royalists}
In Geica there is a \quo{Royalist Faction} who support \Belzir{} and want to restore her to life and throne. 
They love their queen and fight fiercely for her. 

Vizicar has similar feelings. 
He believes \Belzir{} is the key to his own goals. 
Besides, his feelings remember their old love for her. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  Through the marshland\\
  And through the rain and mud\\
  Now listen\\
  I march to youm my sleeping beauty\\
  I alone\\
  I cut myself on the moonlight beams\\
  Hordes of wolves follow behind me\\
  I alone\\
  I'm all alone\\
  My face brightens in the flash of the lightning
  
  Through the morning mist\\
  And through the frozen land\\
  I feel your presence\\
  I march to you, my sleeping beauty\\
  You alone\\
  I cut myself on the moonlight beams\\
  So that you can drink from my chest\\
  You alone\\
  The wind gripping my hair\\
  My teeth are grinding\\
  As we meet in the flash of the lightning\\
  It's like a dream
}







\subsection{Vizicar picks up an instrument}
In Geica, Vizicar sees a flute or something lying around. He picks it up. \ta{I can play that.}

He pipes some notes. It sounds horrible. He puts it down. \ta{I didn't say I could play it \emph{well}.}









\subsection{Carzain is drawn by the moon}
Carzain feels somehow that the moons are a key to unlocking the secrets of his past.

\lyricslimbonicart{Enthralled by the Shrine of Silence}{
  Restless days and sleepless nights.\\
  Drawn in the direction of the moon.\\
  Infernal magnet to mysterious destiny,\\
  beyond the grave of doom.
}









\subsection{Carzain goes on a quest to find a \vorcanth}
\target{Carzain dreams of Moon-Wolves}
Carzain is sought out in dreams by the \vorcanths. 

When he finally meets the \vorcanths, he also meets some of their \hs{\aryoth} companions. 
But it is the \vorcanths{} who lead, not the \aryothim. 

\lyricsbalsagoth{Of Carnage and a Gathering of the Wolves}{
  [VOICE OF THE NIGHT:]\\
  Who are you, wanderer?
  
  [WANDERING SPIRIT:]\\
  I can't remember...
  
  [VOICE OF THE NIGHT:]\\
  The wolves are gathering,\\
  the stars are shifting...\\
  come, join us in the hunt.
  
  [VOICE OF THE NIGHT:]\\
  Who are you, wanderer?
  
  [WANDERING SPIRIT:]\\
  I have the scent...
  
  [VOICE OF THE NIGHT:]\\
  Gaze into the mists...\\
  feel the earth thawing beneath your feet.\\
  Come, bring down the prey.
}

Turns out there is a wounded \vorcanth{} who cries out for his help. 
He goes on a quest to find and save it. 
See section \ref{Moon-Wolves help Ramiel in dreams}. 

They guide him, employing occult astrology and \hyperref[Moon-Wolves and the Moon]{their mystic connection to the moon Visha}.

\lyricsbalsagoth{Of Carnage and a Gathering of the Wolves}{
  [THE SYLVAN ORACLE:]\\
  The wolves are gathering.\\
  The stars are shifting.\\
  This spectre at the feast.\\
  This nectar of the vine.
}

They guide him towards his true identity. He begins to understand his true nature: A terrible creature, cruel yet glorious.

\lyricsbalsagoth{Of Carnage and a Gathering of the Wolves}{
  [VOICE OF THE NIGHT:]\\
  Look at the power you possess...\\
  See the might which you wield!\\
  You know who you are, do you not?
  
  [WANDERING SPIRIT:]\\
  Yes, I am the scythe in the field at summer,\\
  I am the thunder that awakens the earth,\\
  I am that which gives the night air its chill.
  
  [VOICE OF THE NIGHT:]\\
  Who are you, wanderer?
  
  [WANDERING SPIRIT:]\\
  I am far beyond the ken of men...\\
  my gaze shall make the night tremble!
}

The \vorcanths{} \hyperref[Moon-Wolves dislike Dragons]{do not like \dragons}, their ancient rivals. They see Ramiel as their saviour.

\lyricsbalsagoth{Of Carnage and a Gathering of the Wolves}{
  He is the scourge, the thanatos, \\
  the cleansing fire, the purifying storm...\\
  he is the cataclysm given corporeal form!
}

Later, he remembers that he is on a mission of genocide against the \dragons{} and their spawn.

\lyricsbalsagoth{Of Carnage and a Gathering of the Wolves}{
  [VOICE OF THE NIGHT:]\\
  Who are you, my son?
  
  [WANDERING SPIRIT:]\\
  Father... I am annihilation incarnate!
}







\subsection{Someone admits to rationalizing}
Someone, possibly \Ishna, tells about his own history. He portrays himself as the hero and most everyone else as misguided or corrupt. At some point, he confesses that he is subconsciously rationalizing and shining up the story to fit his own desired interpretation. 







\subsection{Fake rebellion is beaten down}
The Geican power holders have caught the scent of the Royalist Faction rebellion. 

So the Royalists stage a fake coup. They are discovered because of information they themselves leaked, and are beaten down. Some of their \quo{leaders} are caught and killed. Apparently the faction is destroyed. The intention is to make the enemy lower their guard, so they can resume their plotting and be more effective for it. 

Compare to the plot of \FLuneNoireVol{5-6}. 

Hayad fights against the rebellion and thus proves himself \quo{loyal} to the government (although, of course, this is just a cover). 

Carzain is unsuspecting and only barely survives thanks to Vizicar's cleverness. \Belzir{} then tells him that it was a test of him somehow. 

Carzain is bitter over having been deceived and almost killed. 

Only Hayad apologizes to Carzain for using him. 







\subsection{Carzain becomes really badass}
During the course of this book, Vizicar awakens some more, and he and Carzain learn to better control their powers. They become more badass, in power and attitude alike. 

He begins to be more of a Dark Knight. Perhaps, at times, his eyes glow with some spectral colour. 





\subsubsection{He remembers more of Ramiel}
He gradually remembers more and more of his life as Ramiel.

\lyricslimbonicart{Behind the Darkened Walls of Sleep}{
  Behind the darkened walls of sleep, \\
  as body rest and mind goes deep. \\
  A door opens in my heart. \\
  A dark euphoria.
  
  The soul is longing to escape \\
  the tyranny of the body. \\
  Dark winds now embrace \\
  the spiritual entity.
}

He remembers the wars he fought with the legions of \Mystraacht. 

\lyricsbs{Arcane Wisdom}{Maelstroms of Majestic Night}{
  Torrents of blasphemous fire enrage forth, \\
  thus allowing my soul to devour \\
  feeblish souls with sickening power, \\
  as the ancient warcrafts proudly descend from the North. 
  
  Oh the blood of my foes and fiends. \\
  How I beheld thy corpses, \\
  raptur'd by virulent winds. 
}









\subsection{Carzain drinks \ps{\Belzir}{} blood}
Carzain drinks \ps{\Belzir}{} blood during sex. 
It is \hr{Resphan cannibalism}{the greatest rush he's ever tasted}. 
It also brings back a little bit of \resphan{} memories, since it's \sathariah{} \Malach{} blood he's drinking. 

Compare to the movie \cite{Movie:QueenoftheDamned}. 







\subsection{Carzain goes into battle}
Carzain is about to go into battle. He dons his armour. 

Vizicar complains. 
\vizicar{This is primitive.} 
Vizicar is used to wearing an \hs{Archon Ward}, a magical super-armour so expensive that pretty much only the Vaimon Emperors could afford it. 















\section{War Against the Redcor}
\subsection{Carzain has become Ramiel}
During the course of the Geican coup, \hs{Carzain} regains almost all of \hs{Vizicar}'s memories, and much of \hs{Tydesmos}'. 

By the time of the beginning of this book, Carzain and Vizicar have merged enough to be one person, with access to all of their shared memories (or all that they remember of them). (Although they still have their internal dialogue from time to time.)

He now uses the name Ramiel. 

He has become a badass dark lord who wears black armour and robes. With swords and magic he kills anyone who stands in his way. At times his eyes glow red or some other evil colour. 

They ally with \hr{Psyrex}{\ps{\Psyrex}} cult and wage war against the Redcor. 

Compare to Wismerhill from \FLuneNoire. It is interesting that Geica's colours are green and black, like those of the Black Moon.

So the man who puts himself in command of the Geican army is far more than Carzain \Shireyo. He has all the life-long experience of a Vaimon Emperor and an archmage at his disposal. 
Vizicar is a much better general than \Belzir, but she is a far more skilled mage. 

Carzain is sort of like Rio from \emph{\JuukenSentaiGekiranger}. His obsession is not only to become stronger, but also to learn his true identity. 





\subsubsection{Archon Ward and other equipment}
\Belzir{} finally provides an \hs{Archon Ward} for Ramiel. Vizicar is happy. Ramiel also gets a black cape and robe, enforced with metal, to serve as backup armour. Now, at last, he looks like a true Vaimon dark knight. 

At Vizicar's command they also produce for Ramiel an imperial coronet. It is enchanted and socketed with magical jewels. Perhaps these jewels were previously acquired on a quest.







\subsection{\Belzir{} controls Geica}
\Belzir{} now controls Geica. She and her associates use a mix of sincerity, propaganda and Shroud-weaving magic to make the people adore them as liberators. 









\subsection{\ps{\Belzir}{} resurrection nears}
\Belzir{} is looking forward to her impending resurrection. 

\lyricslimbonicart{As the Bell of Immolation Calls}{
  In a timeless departure from the flesh,\\
  Drifting the cold ether streams of death.\\
  By the altar of sacrifice, as I call upon the night\\
  to take and give me life beyond the shores of light.
  
  I glorify the hour of blackness\\
  as the bell of immolation calls.
  
  A black heart will adorn\\
  the wings when I'm reborn.\\
  Engraved on my memory\\
  is whom hatred made me.\\
  The ravages of time.\\
  Battles on in my mind.\\
  There are still wounds that bleed\\
  deep in the soul of mine.
}

She is happy to leave behind the horrible limbo.

\lyricslimbonicart{As the Bell of Immolation Calls}{
  A life among the dead and sorrowful,\\
  the endless voids where spirits are mournful.\\
  From the pale of agonising light \\
  I cross the bridge to crystal night,\\
  as the bell of immolation calls.
}







\subsection{Carzain disgruntled again} 
It turns out that Ramiel and \Belzir{} were manipulated by \Secherdamon{} and \Psyrex. 

Ramiel grows to hate \Belzir{} and desires to usurp her, because she is an insane bitch. He also grows to hate the Sentinels for trying to manipulate him. 

He resents Shereid when he learns that she was part of the plan. He punishes her and means to kill her, but she pleads for her life. She claims that she loves him above all else and swears to serve as his devoted slave. So he lets her live. 

Ramiel's betrayal should be kept secret from the reader until the very end, but subtle hints should be dropped here and there, as he plots, schemes and prepares. The reader should understand that Ramiel is \quo{up to something}, but kept guessing as to what.









\subsection{Overlordship of \Mystraacht}
Ramiel and \Shiaraid{} both covet the throne of the \hs{Overlord} of \Mystraacht. 

\Shiaraid{} is the daughter of \hs{\Zachirah} and feels that she is the rightful heir and should be Overlord, with Ramiel as her Prince Consort. 
She accidentally lets a suggestion of this slip. 
Ramiel picks up on it. 

He is not happy. 
He wants to rule, over \Mystraacht{} as well as over her. 
\emph{Especially} over her. 

Later she offers him the position of Overlord, with herself as his Consort. 
But by that time he has gotten paranoid and fears her ambition. 
He suspects she will cheat him and try to manipulate him so she can rule behind the throne with him as a marionette. 
She has done it before. 
She is good at exercising power even when she seems submissive. 
He does not trust her. 

\Shiaraid{} feels it is OK to submit to him but still exercise power. 
In her mind, it would be a great arrangement. 
Ramiel has his pride and she has her submissive side, so she is perfectly willing to let him have the fancy title, with her as his nominal inferior. 
But she still sees herself as his equal in worth, so she wants an equal share of the power. 
So in a sense her sado-masochistic way of thinking is more sane and healthy, since she can accept a equal relationship where she is sometimes dominant and sometimes subservient. 

Ramiel does not want to share. 
He has his (almost hysterical) \hr{Ramiel is nothing}{fear of being nothing} and cannot stomach the thought of submitting to anyone. 
He must dominate all the time. 

\hs{\NexagglachelsCurse} plays them against each other and makes them suspect and plot against each other. 
They argue and fight and lash out in anger, with words or actual violence. 





\subsubsection{\Belzir{} is a bitch}
I need to make sure that \Belzir, under the influence of the Curse, acts like a real bitch at times. 
She may silently regret it afterwards. 
But she is bad enough that the reader understands Ramiel's growing hate and sympathizes with him (to some extent) when he betrays her. 









\subsection{\Belzir{} cries out \ps{\Aryal} name}
While having sex with Ramiel, \Belzir{} moans the name of \Aryal. 
Ramiel says nothing, but he is not happy. 
He knows that \Aryal{} was and is the greatest love of her life, and that he will always rank below her.
He does not like the reminder that he stands below someone else in some respect. 
It triggers his trauma about \hr{Ramiel is nothing}{being nothing}. 
It makes him jealous and resentful. 

It also makes him mistrust \Shiaraid. 
He fears she is more loyal to \Aryal{} than she is to him. 

Then he finds out the story of what happened to \Aryal. 
\Shiaraid{} \hr{Silqua dies}{betrayed and killed her}. 
If she would do that to her true love, what would she not do to him? 
The second-rate usurper who \quo{thinks he can take \ps{\Aryal} place in \ps{\Shiaraid} heart}? 

He resolves that he can't trust her and begins to plot against her. 

\Shiaraid{} also thinks about it. 
She knows Ramiel dislikes \Aryal, thinking of her as a coward and a weakling. 
This makes \Shiaraid{} resent Ramiel. 








\subsection{Shereid in distress}
Shereid slowly goes mad. Partially out of her obsessive love for Carzain/Ramiel, but even more so because she learns the cruel truth of \ps{\humanity} history. 

She keeps herself halfway sane by clinging to Ramiel and her love for him. 
They have incredible sex. Ramiel's love confirms to her that her life has a purpose. As long as she can be with him, she can live with the fact that her entire race is created to be the slaves of monstrous aliens. 

Compare her to Mele, with her love for Rio, from \emph{\JuukenSentaiGekiranger}. Come to think of it, Ramiel is also quite like Rio. 









\subsection{Carzain doubts his evil, and finally embraces it}
Throughout the book, Carzain is plagued by the memories of his evil life as Ramiel. At first he is horrified, repelled by what he finds inside him. But in the end, he embraces that legacy as his true self.

\lyricslimbonicart{Sources to Agonies}{
  Through the mirror of the soul\\
  I'm staring deep within\\
  To see what dwell behind the wall,\\
  The beauty of pale skin.
  
  The aura that surrounds me\\
  is not of noble kind.\\
  The blackness of the heart\\
  is all that's left to find.
  
  A dark river runs silent through my life\\
  like a floating nemesis.\\
  A dark shadow of what that used to be\\
  drifts now in lifeless misery.
  
  Live only to witness what I've become.\\
  Midnight is my shallow home.\\
  Soon to enter the last deed of mine.\\
  I'm forced to follow the streaming bloodline.
  
  When the wine of life is shed\\
  and dark cosmic space consumes\\
  I bring the memories back from the dead.\\
  Sources to agonies, a devouring monsoon.
}









\subsection{\Belzir{} is resurrected}
\Belzir{} is resurrected and has her body back. 
Perhaps she even gets a \resvil{} body. 

But part of her soul is imprisoned and sealed somewhere in \Redce. So they ally with \hr{Psyrex}{\ps{\Psyrex}} cult and conquer \Redce. 

Then they perform a magical ritual to heal \Belzir{} and return her true power to her.
Perhaps this ritual is also meant to restore her memories and her full \Malach{} power. 
But in the end, Carzain betrays \Belzir{} and kills her during the ritual. 

\lyricsbs{Cradle of Filth}{Cruelty Brought Thee Orchids}{
  Maleficent in dusky rose.\\
  Gathered satin lapped Her breasts\\
  like blood upon the snow.\\
  A tourniquet of Topaz\\
  glistened at Her throat.\\
  Awakening, pulled from the tomb,\\
  Her spirit, freed, eclipsed the Moon\\
  that She outshone as a fallen star.\\
  a regal ornament from a far flung nebular.
}







\subsection{\Vizsherioch{} is strengthened}
Have an arcane ritual where \Vizsherioch{} is given more power. 

Compare to \FLuneNoireVol{9}, where Wismerhill becomes the Prince of Negation. 

\lyricsflnv{9}{
  Haazeel Thorn: 
  \ta{%
    Life was truly torn from you, but I have replaced it with something better. In your veins now flows Negation.}
}







\subsection{\Redce{} falls}
Under the onslaught of the \hs{Geican} and \hs{Dark Crescent} armies, \hr{Redce}{\Redce} finally falls. 

In the end, Ramiel has to fight a boss monster: 
\Matriarch{} \hs{\Dominice}, a really badass Redcor mage. 
%, who is a Scion of the \Malach{} \hs{\Ariel}. She is older and more experienced that he, and knows more of her true nature and power. She might not be a \sathariah, but he cannot wield his full \sathariah{} power yet. 
She is far older and more experienced than he, and while a mere \human, she knows a lot about him and knows spells that can counter his \resphan{} powers. 

%She actually defeats Ramiel. But he is not quite dead. She becomes overconfident, and he rises to strike her down. Compare to Wismerhill from \FLuneNoireVol{10-11}. 
Ramiel knowingly holds back and lets \Dominice{} defeat him and \emph{almost} kill him. 
%\Dominice{} defeats Ramiel, almost killing him. 
He contacts \Belzir{} and requests that she use her power to keep him alive. 
She cannot afford to refuse. 

Meanwhile, \Dominice{} has become overconfident. 
He rises to strike her down. 
He kills her, then eats her and absorbs her power. 

Have a bloody scene where he tears out her heart, brain and liver and eat them. 

% He insisted on facing her alone because he wanted to eat her alone. 
% This gives him the strength he needs to face \Belzir{} and betray her. 
% Also, he has forced \Belzir{} to deplete her strength to heal him. A dangerous \trope{XanatosGambit}{Xanatos Gambit}, but Ramiel has always been reckless. 
This was a part of Ramiel's plan: 
He let himself be wounded, thus forcing \Belzir{} to pour her power into him and depleting her own strength to heal him. 
Now \Belzir{} is weakened, while he, having eaten \Dominice, is strong.
A dangerous \trope{XanatosGambit}{Xanatos Gambit}, but Ramiel has always been reckless. 












\subsection{The Resurrection} 
\target{\Shiaraid{} dies}
Ramiel makes Shereid his willing sex slave, and together they plot to usurp the Dark Queen. 
Ramiel is bitter at \Belzir{} for treating him badly. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Ecstasy Arise%
}{
  I've learned to cry and crawl away\\
  But at the closing of our circle you will pay\\
  I see the hope vanish in your eyes\\
  I feel the ecstasy in me arise
}

\Belzir's resurrection is a ritual performed by many mages. 

She must be reborn through a \human{} body. 
So a young, healthy, beautiful Royalist woman (named Shadira or somesuch) willingly sacrifices her body and soul to her beloved queen. 

Carzain and Shereid plan to interrupt the ritual and drain \Belzir's power. 
In order to do this, they must have their own agents participating in the ritual in the key spots. 
So they begin to subvert other members of the Royalist Faction to their cause. 
When the war progresses and the day of the resurrection nears, they take measures to assassinate the mages that have remained loyal to \Belzir, so that they may control the ritual. 

At the end of the story, there is a big ceremony to resurrect the Queen, in which Carzain must channel her power through the orb. 
But he betrays her by smashing the orb, thus keeper her power for himself. 

After this, Carzain sets himself up as Emperor. 
But unbeknownst to him, \Belzir{} is not destroyed. 
After the betrayal, she contacts a group of Royalists in Geica, who (hidden from Carzain) were prepared to take over the ritual if anything should go wrong. 
They succeed, and she is resurrected. Some of the Royalists side with Carzain. 

Hayad and his children are among the Royalists who side with \Belzir. However, after a while Hayad notices that \Belzir{} is becoming dangerously insane. 
One night, she tortures and kills a lover who fails to satisfy her sexually. 
Hayad, fearing that he is next in line, flees to join Carzain. 





\subsubsection{\Shiaraid{} dies}
So Carzain and \Belzir{} clash and fight.
And in the end he is victorious. 
He not only kills her, but also \hr{soul-eating}{consumes her soul}. 

She fights back. 
It is a hard battle. 
Ramiel is in danger, so he has to draw really fucking deep of the power within his \carcer. 
He digs deep into his inner darkness in order to unleash as much as he possibly can of his wicked \sathariah{} power. 
He forces the souls within his \carcer{} to submit and serve him. 
This is tough, because there are immortals in there. 
Even \dragons. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Shadow Self%
}{
  Blood on a legion of nameless shores, I beseech you!\\
  Skill of a thousand nameless whores, I invoke you!\\
  Holding the light away\\
  Twisting in my mind
  
  Love of a legion of begging slaves, I exalt you!\\
  Screams of a thousand burning souls, I unleash you!\\
  Holding the light away\\
  Twisting in my mind\\
  Into the shadow's waking eyes
  
  Power of a legion of nameless lords, I command you!\\
  Locks of a thousand nameless doors, I unlock you!\\
  Lash of the six soul-taking strokes, I will feed you!\\
  Twisting in my mind\\
  Into the shadow's waking eyes
  
  \quo{Spiritus Pervertus Nymph}\\
  \quo{Spiritus Pervertus Femme}\\
  Twisting in my mind
  
  I know he steals, my body is haunted\\
  Wicked voice in my spirit has control\\
  Blinded by the beauty of my darkness\\
  Makes me fly, takes me higher
  
  I invoke thee, blackened lord.\\
  Night begins to crawl the skies\\
  Kneel before your master, shadow self\\
  Taste the pain caressed by chains
}

But in the end, \Shiaraid/\Belzir{} submits and lets him kill her, like \hr{Silqua dies}{\Aryal{} once let \Shiaraid{} kill her}. 
For a number of reasons:
\begin{enumerate}
  \item 
    \Shiaraid{} feels guilty over having killed and eaten her (submissive) lover, \Eryal, so she feels she deserves to have her new (dominant) lover do the same to her. 
  \item 
    \NexagglachelsCurse{} makes her self-destructive and suicidal and emo. 
  \item 
    She is very sad because \Mystraacht{} is in turmoil and has been tearing itself apart from the inside for thousands of years. 
    \Mystraacht{} is her father's legacy, so she is strongly attached to it and wants it to live and be strong. 
    She has almost motherly feelings towards her dynasty and will sacrifice herself for it.
    When she lets Ramiel absorb her power and unify it with his own, \Mystraacht{} will be one step closer to uniting and restoring its former glory. 
    
    After all, \ps{\Zachirah} great strength as a leader derived partially from the fact that \hr{slave \resviel}{his \resviel{} submitted to him}. 
    That made him the ultimate alpha male, respected and envied by all. 
    \Shiaraid{} hopes that if she submits to Ramiel and lets him eat her, it will make him (in some small way) a new \Zachirah. 
\end{enumerate}

She feels she deserves to die for her wicked \sathariah{} lusts.

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  DeathspellOmega
}{
  Diabolus Absconditus
}{
  He only will grasp me aright \\
  whose heart holds a wound that is an incurable wound,\\
  Who never, for anything, in any way, would be cured of it...\\
  And what man, if so wounded, \\
  would ever be willing to \quo{die} of any other hurt?
}

In the end, she is a little bit happy. 
Now she can be sort of reunited with \hr{Shiaraid and the ghost of Eryal}{the ghost of \Eryal}. 
Previously, \Eryal{} had been locked away in \ps{\Shiaraid} \carcer. 
Now they will both be absorbed into Ramiel's \carcer. 
This is as close as they can come to a reunion. 

She tells herself that by sacrificing herself she has atoned for her crimes against the world, against \Eryal, and even against Ramiel. 
She has done what she thinks \Eryal{} would have wished. 

\begin{prose}
  \Shiaraid:
  \tho{Ramiel is saner than I.
    In all my life I did nothing but harm with my tremendous powers, but now, in Ramiel's hand, my powers can perhaps do some good.}
\end{prose}

She is also happy to be free of the burden of her \carcer, and all the loathsome undead souls haunting her. 
Now it is up to Ramiel to carry that burden. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  When struck I rise\\
  I'm finally free\\
  Mark the bitter tear descending\\
  No more heavy burden\\
  And this is my eternal music
}


Her last words to Ramiel are: 
\begin{prose}
  \ta{%
    Promise me you will reunite \Mystraacht{} and make it strong and mighty again!
    You now have me inside you, and with me the last remnants of \ps{\Zachirah} bloodline.
    That makes you his true heir. 
    And our last \sathariah.
    
    You are the only one!
    \ps{\Mystraacht} future rests on your shoulders, Ramiel.
    \ps{\Zachirah}, \ps{\Nathrach} and mine. 
    We all live on in you now. 
    You are all of us. 
    You carry our hopes, dreams and legacy. 
    You are the soul and heart of \Mystraacht!}
\end{prose}



%Hayad joins Carzain. But it turns out that he is not strong enough to maintain the Empire he attempted to conquer, and it falls to pieces.





\subsubsection{\ps{\Shiaraid} tragedy} 
\hs{\ps{\Shiaraid} tragedy} is \NexagglachelsCurse, which forces her to destroy herself and those she loves. 
For she genuinely loves Ramiel. 

When she finally perishes, it is \ps{\Nexagglachel} revenge. 
She imagines she hears him laughing inside her head, mocking him as she once mocked him in his captivity. 
She hates him, but still some part of her recognizes the justice in it. 





\subsubsection{Ramiel is sad}
\target{Ramiel blames both sides for the tragedy}
Ramiel is victorious, but his victory is bittersweet. 
He is somewhat sad. 
He loved \Shiaraid, and now he has betrayed her. 
He repents. 
He knows it was the Curse that turned them against one another. 

He tries to tell himself it is justice, because \Delphine{} \hr{Silqua dies}{did the same to her beloved \Aryal}, and \Shiaraid{} also \hr{\Shiaraid{} betrays \Zachirah}{turned her back on \Zachirah}.
But he cannot convince himself. 

The affair leaves him bitter and disillusioned, and he becomes more evil and brutal. 

He also speculates that maybe it is just and natural for him to kill and eat her. 
After all, it is inherent in the nature and purpose of the \resphain{} to be \hr{\Shiaraid{} betrays \Zachirah}{parasitic and consume one another}. 
But that doesn't make it any better. 
He concludes that both sides in the \hs{Feud} are to blame for this tragedy: 
The \banelords{} for having bred the \resphain{} into the destructive things they are, and \Nexagglachel{} and his \dragons{} for having twisted them further. 
He grows to hate both sides more. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Section X%
}{
  Blood on my fingers\\
  Night in my soul\\
  Your breath I will hear no more\\
  I'm slowly growing cold\\
  Your eyes are open\\
  Dead to the light\\
  I hear my soul cry\\
  On the wings of death I ride
}

Eating \Shiaraid{} strikes Ramiel as a hard blow, not just psychologically, but also physically and metaphysically. 
She is a humongous soul: 
\Sathariah{} and \malach, carrying behind a huge \carcer{} of her own. 
It is difficult to gulp her down. 
Her \carcer-souls attack him and haunt him. 
He has to struggle to subdue them. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Section X%
}{
  Hunting the shadows\\
  Knowing they are one\\
  Whispering voices\\
  They stalk me through the dark\\
  My eyes are open\\
  Black, all is black\\
  I am desperately cold\\
  And upon my knees I crawl
}






\subsection{Ramiel is closer to regaining himself}
Ramiel's betraying \Belzir{} and draining her power\dash perhaps even eating her flesh\dash is a key step towards regaining his full power. Remember, \hr{Resphan power and hunger}{a powerful \resphan{} needs to eat}. 

By absorbing her, he is able to \quo{inherit} some of her knowledge. 
He also absorbs her \hr{Fragments of \Nexagglachel}{\Nexagglachel{} fragment}, making him \hr{Ramiel is overpowered}{\uber-powerful}. 

\lyricslimbonicart{As the Bell of Immolation Calls}{
  A black heart will adorn\\
  the wings when I'm reborn.\\
  Engraved on my memory\\
  is whom hatred made me.\\
  The ravages of time.\\
  Battles on in my mind.\\
  There are still wounds that bleed\\
  deep in the soul of mine.
  
  I behold the beginnings of sorrow\\
  and predict the omens of cruelty.\\
  In the plague's shadow I follow,\\
  as tormenting winds sweeps\\
  through the cathedral halls,\\
  as the bell of immolation calls.
  
  In embers of infernal greed,\\
  feeding the fires unholy.\\
  Apocalypse was born\\
  when hell brainstormed through me.
}

















\section{Random ideas}









\subsection{Things to remember}
Remember that the books should not be too \human-centered. 
Have more focus on the \scathaese{} societies. 
This book should have lots of focus on the Rissitics and Imetrians. 
Perhaps even with Carzain as a mere subplot. 









\subsection{The \xzaishanns{} and the deepest Chaos}
Remember to have references to the \xzaishanns{} and the deepest recesses of Chaos, from which the \dragons{} draw their power. 

Compare to the First Warren of Starvald Demelain in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}.

Have references to \quo{the blood of the \xzaishanns} and \quo{the power of the \xzaishanns} and \quo{the legacy of the \xzaishanns}. 









\subsection{Malcur becomes a myth}
After the fall of Malcur, the city rapidly becomes a myth. Some months later, people have almost forgotten it. 
The talk is that the city has been eaten by the \Wylde{}, but people are forgetting when it existed\dash it's already categorized as \quo{the far past}. 

Soon, people look at you as if you're mad or a liar if you claim to have been there, or even be from the city. 
This is self-enforcing: 
It makes people question their own memories, repress their memories of having been there, until their minds make up a fake past to cover the fact that they're \Malcurian. 









\subsection{A sexy girl}
In this book or in one of the next, maybe I should have as a main character a sexy girl who regularly gets owned, dominated, humiliated and sexually harassed by other characters, villains and heroes alike. 





\subsubsection{Erotic scene with girl being killed}
Have an erotic scene with a girl being stripped naked and killed. As in the movie \emph{House of the Dead}. 










\subsection{Sentinels battle to the death}
Have a scene where Sentinels (\rachyth?), servitors of \Secherdamon{} or \Vizsherioch, fight to the death in ritual combat. This is a ceremonial contest, where the winner will be granted great power and status. 

Inspired by one of the early episodes of the tokusatsu series \emph{Go Go Sentai Boukenger}, where \Ryuuoun{} has some of his \Jaryuu{} Tribe battle to the death for the honour of being selected and transformed into a \Daijakuryuu, a powerful monster.







\subsection{Expedition to the lost \Dragonland}
Have a short excursion to \Dragonland, the lost realm of \dragons. Perhaps \Nzessuacrith{} or another major \draconian{} character. 







\subsection{Betrayal}
I need to have a character who seems good and nice and dandy, helping out the heroes. But in the end, he betrays them, and it turns out he was evil all along. 

Compare to the priest Father Soren from the movie \cite{Movie:GargoylesRevenge}. 
At the end it becomes apparent that he was actively working to help the gargoyles awaken. 







\subsection{Someone is betrayed and imprisoned}
Someone is betrayed and taken prisoner. By whom? The Redcor? Or the Rissitics?

And who? Perhaps Carzain, but perhaps rather someone else. I have enough Carzain material already. 

Anyway, the prisoner awakens some kind of inner power, perhaps one that had previously lain dormant and hidden. He/she strikes back and causes great destruction. 

Compare to the scene in \authorseries{Robert Jordan}{Wheel of Time} where Rand al'Thor is taken prisoner and stuffed in a chest by the Aes Sedai. Or a scene in volume 2 of \FLuneNoire{} where Wismerhill is captured by a wizard who wants to drink his blood. 







\subsection{A \succubus{} shows people illusions}
\index{\succubus}%
A \hs{\succubus}-like monster, or group of monsters or villains, lurk in the Topaz \Chateau{} in \Redce{} and lures people in, to devour or to capture for later use.







\subsection{\Dzasselid-tachi fight for good}
\Dzasselid{} and \Narkiza{} and the rest still fight for \Nechsain, but they try as best they can to bend it in a good direction, to work for a kind of \quo{Rissitism with a \human{} face}.

Compare to lots of good guys in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}, and maybe \authorseries{Michael Moorcock}{Elric of \Melnibone}, where Elric serves Arioch but tries to subvert him. 







\subsection{Ilcas and \Narkiza}
Telcastora Ilcas and \Narkiza{} meet. 
They criticize each other's countries and religions. 

\begin{prose}
  \Narkiza: 
  \ta{Yous sword drinks blood. (Subtext: That is evil.)}
  
  Ilcas: 
  \ta{I am a warrior. 
    I kill my enemies. But I have never killed an innocent.}
  
  \Narkiza: 
  \ta{Innocent how?}
  
  Ilcas: 
  \ta{Give it up. 
    You are trying to get me to doubt my religion and my cause. 
    That is \emph{not} going to happen.}
\end{prose}








\subsection{Someone is overly philosophical}
Some dude is being overly philosophical and sees symbolism everywhere. A wiser character (\hs{Criseis}{\Criseis}?) calls how down on it. 

\Criseis: \ta{Dude, knock it off. Understand this: The world is not full of symbols. The world is not full of meaning. The vast majority of what goes on in the world is due to chaos, chance, meaninglessness. I have lived twenty thousand years. I know this.}

Lamer: \ta{But I am \emph{giving} it meaning, here in my head!}

\Criseis: \ta{Then let it stay inside your head. And know that the world is infinitely larger than your head, and it cares nothing for how you \quo{interpret} it, how you \quo{give it meaning}.}







\subsection{Cool conversations with \Ishnaruchaefir}
\subsubsection{Immortality}
Someone comments that immortality must suck. 

\hyperref[Ishnaruchaefir]{\Ishna}, or \hyperref[Criseis]{\Criseis}, or another immortal: 
\ta{Hell no! If immortality sucked I would have killed myself long ago. Immortality owns ass!}

Subvert the trope \trope{WhoWantsToLiveForever}{Who Wants to Live Forever}.





\subsubsection{Peace with my past}
\Ishnaruchaefir: \ta{I have long since made peace with my past.}

\Criseis: \tho{You lie, my lord. You have never made peace. I see it, deep in your eyes. You merely hide it well and have developed skill at ignoring insults.}





\subsubsection{Fallibility}
\Ishnaruchaefir: \ta{Acknowledge my own fallibility? Ha. I think not. Perhaps in another ten thousand years.}







\subsection{A villain disses the younger races}
A Cabalist or Sentinel is accused of being evil. He does a long rant (perhaps a \trope{HannibalLecture}{Hannibal Lecture}) about how the younger races have not only inherited all of the elder races' evil, but also made it worse through stupidity. 

The elder races were and are cruel, true, but theirs is a cultured cruelty, evil with a purpose, intelligent malice. The evil of the younger races, on the other hand, is petty, vicious and, above all, senseless. Where they act there is more waste, more chaos, more senseless destruction and suffering. 

He recites many examples of how \humans{}, \scathae{} and \meccara{} are capable of horrible crimes, completely on their own initiative. This includes all kinds of people: The downtrodden Shroud slaves, the nobles who are still Shroud slaves, the enlightened who fight in the \secretwar, and those few who try to subvert the \secretwar. All of them commit terrible crimes, for what they believe is right, or for no reason at all.







\subsection{Social interaction sucks}
Someone, perhaps Carzain, or even \Ishna, complains about social interaction and all of the hypocrisy which is a necessary part of it. It stems from Carzain's being tired of running political games in Geica.







\subsection{Someone discusses sorcerer-kings}
Have some high-up villain comment on the subject of \hr{Sorcerer-kings}{sorcerer-kings}, and why there are not more of them. 







\subsection{\Ishnaruchaefir{} berates a whiner}
\Ishnaruchaefir{} is talking to someone who whines. He berates him: 
\ta{Get over it. 
  I have suffered more than you ever will. 
  For ten thousand years. 
  So do not come whining to me.}






\subsection{\Banes{} were not the first invaders}
Someone remarks that the \banes{} were not the first aliens to invade \Miith. 
There have been others. 
The \xss{} were one such invading force. 
They \emph{won} and ruled \Miith{} for millions of years. 
But then they grew sleepy...







\subsection{\Ishnaruchaefir{} fights during Nadir}
At some point in the series, I need to have a big, climactic event coincide with \hs{\ps{\Ishnaruchaefir} Nadir}. 
He is weak, but forced to fight anyway, and not through a \XanatosGambit{} of his own this time (unlike that time with \Teshrial). 

This new Nadir is much worse than the previous one (during \booktitle{\TwilightAngelRemember}). 
The \hs{Nadirs get worse}, remember.








\subsection{A \bane{} talks about viruses}
A \bane, perhaps even \Daggerrain: 
\daggerrain{%
  There exist diseases that spread (like viruses). 
  (\Daggerrain{} knows what a virus is, but the listener would not know, so he has to explain.) 
  You \humans{} are the same in the way you spread all over the world, destroying and enslaving the land around you. And yes, we \banes, too, are the same, only on a \cosmic{} scale.}

Or... maybe the \banes{} are not the virus. Maybe everything else, such as the \dragons, is the virus, and the \banes{} are the cosmic antibody, created to scour the infestation of life from the universe. See section \ref{Banes as an antibody}. 







\subsection{\Vizsherioch}
\subsubsection{\Rathyon{} and \Vizsherioch}
\hs{\Rathyon} meets \hs{\Vizsherioch}. 

\Vizsherioch: \ta{Greetings, nephew.}

\Rathyon: \ta{\quo{Nephew}? Who are you?}

\Vizsherioch: 
\ta{You do not know me? 
  I am \Vizsherioch, son of \Secherdamon.
  I am the \xss{} given flesh!}

\Rathyon: \ta{\quo{\Vizsherioch}? That does not sound like much.}

\Vizsherioch: 
\ta{[Smile.]
  I need to litany of names. \Vizsherioch.
  Speak my name. 
  Hear it.
  Perceive its Aenigma.
  And you will understand.}





\subsubsection{\Ishnaruchaefir{} and \Vizsherioch}
\Ishnaruchaefir{} meets \Vizsherioch{} for the first time. 

\Ishnaruchaefir: 
\ta{Aaah. 
  So \emph{you} are the new \vertex{} I sensed in \ps{\Secherdamon} constellation.}







\subsection{Immortals curse the Shroud}
Some immortals curse the Shroud. 
It makes them stupid and forgetful and \hr{Shroud represses technology}{represses technology}. 






















\chapter{\RamielsAwakeningBook}
\section{Concepts}
\subsection{Ramiel and Hayad}
After Ramiel betrayed \Belzir, Hayad remained his friend. 

But Hayad is Sentinel-allied, and Ramiel goes to join the Cabal. 
How does that work? 

I guess Hayad will die at some point, so Ramiel won't be forced to turn on his friend. 







\subsubsection{The \Bane{} Invasion}
%After defeating \Belzir{}, Carzain fights some Rissitics and some \banes{} sent by Rissit. But eventually, it becomes apparent that the \banes{} have their own agenda. 

After this, Carzain discovers that he and \Belzir{} have been manipulated by the Sentinels. He becomes angry and leaves them. 

Perhaps he travels the world for a while now, fighting for whatever cause catches his fancy. Kind of like Elric of \Melnibone{} in his mercenary years. 

Somehow, he meets the \banes. Perhaps he is taken prisoner by them. They show him how all morality is a lie, how everything in the world revolves around the struggle between \dragons{} and \banes. They convince him that, as a \Malach, he is created by the \banes{} and destined for greatness as a hero on their side. 

At this point, Carzain has encountered several different civilizations and their different moralities, and has found them all lacking --- totalitarian, intolerant and contradictory. He has also read snippets of the Book of Nom, strengthening his growing suspicion that good is futile. He is near to concluding that everyone is a hypocrite, that all morals are false and that the only truth is power. 
After being shown the brutal truth by the \banes, he becomes completely disillusioned and turns to evil completely. (Perhaps it is his already high degree of disillusionment at this point that lets him keep his sanity when confronted with the truth.) 
%Carzain, completely disillusioned, abandons all his former morals and turns to evil completely. 
He abandons the name Carzain \Shireyo{} and becomes Ramiel (his \Malach{} name). 

Later, he learns that the Redcor, or at least some of them, are on the Cabal's side, and that he will have to work with them. He balks until he is reassured that he will not be put under them but beside or above them. 

%The Cabal betrays \Belzir{}, and it turns out that they actually serve the \banes. 

%Late on in the story, Carzain and a party of other heroes go on a quest to destroy some \banes. It comes to a big boss fight, but in the end, one of the heroes betrays the party and turns on them. Carzain dies. %, and the \banes conquer \Velcad{}. 

%The \banes{} conquer \Velcad{}. The Imetrians and Rissitics team up with Irokas to oppose them. I don't know what happens after that. (A nice evil ending might be to have \Tiamat{} awaken and destroy \banes{} and \dragons{} alike...) 





\subsubsection{Ramiel's companions}
Maybe Ramiel has a female companion. 
Compare to Mele from \emph{\JuukenSentaiGekiranger}, with Ramiel (of course) being Rio. 

Perhaps he gathers \vorcanths{} and other creatures around him and forms his own \Rinjuuken. 









\subsection{Ramiel's enemies}
\target{Secherdamon wants to off Ramiel}
Ramiel had managed to keep his existence secret from the Sentinels for a while, but no longer. 
After he killed \Shiaraid, he could no longer hide. 

\Secherdamon{} is not happy about this new development. 
He liked \Shiaraid{} because she was so mad. 
She was dangerous to him, true, but he suspected she would be just as dangerous to the Cabal. 
But Ramiel is another matter. 
\Secherdamon{} does not know how \malach-hood and the Curse have affected Ramiel, but he remembers Ramiel as a formidable and competent adversary. 

So \Secherdamon{} decides he wants to off Ramiel. 
Throughout this book, therefore, Ramiel is hounded by Sentinels and Cabalists alike. 

Fortunately, Ramiel has allies: 
\Cishiel, \Azraid{} and the \vorcanths. 





\subsubsection{\Azraid{} helps Ramiel}
\Azraid{} \hr{\Azraid{} protects Carzain}{has his own plans for Ramiel}, so he protects him. 
He also subtly guides Ramiel on his quest and pokes him in the direction of the things he might need to regain his power. 

In this way, \Azraid{} acts as a \trope{StealthMentor}{Stealth Mentor} to Ramiel. 

When Ramiel finally learns of \ps{\Azraid} involvement, he is amused and slightly grateful, but not surprised. 
That is the kind of thing \Azraid{} has always done. 








\subsection{\Sithiyacaan}
Introduce \hs{\Sithiyacaan}, the last \hs{\Kezeradi} lord. 







\subsection{The \Feud}
\target{Resphain are winning the Feud}
From the \Shrouding{} and up until this time, the \feud{} had been pretty much a war of attrition. 
And the \resphain{} were winning. 
Their numbers were dwindling, true, but the \dragons{} were dwindling faster. 
Besides, those \resphain{} who survived were the strongest, \hr{Resphain grow stronger}{and they kept growing stronger}. 







\subsection{To break or preserve the Shroud}
\target{To break or preserve the Shroud}
The \dragons{} originally created the Shroud. They did not care for progress. The \resphain{} \emph{do} care for progress, so they want to get rid of the Shroud. But they are afraid that it will give their \draconic{} foes access to more \xsic{} power, so they will not unravel the Shroud before their \matrix{} has control. 

Both \Daggerrain{} and \Secherdamon{} plan to sunder the Shroud and bring in their forces to lay waste to \Miith{} (see section \ref{Daggerrain's master plan}). For both parties, this is \hr{Summoning the \xss: A deadly balance}{a delicate balance}.

Our \quo{heroes}... wait, who are our heroes? \Narkiza{} and \Dzasselid? Moro \Cornel? \Cuezcans? Imetrians? \Ophidians? Remnants of the Redcor and Geicans?

Anyway, our heroes initially want to destroy the Shroud and free the people of \Miith{} from its cruel oppression and their imprisonment as witless slaves and defenseless victims, easy prey for all the horrors that lurk in the universe.

But towards the end, it becomes apparent that unravelling the Shroud is not a good idea. It will enable \Daggerrain{} or \Secherdamon{} or both to carry out their plan, and whoever wins that struggle in the end, the consequences for \Miith{}'s inhabitants will be cataclysmic. So the heroes realize that, hateful as it may be, if they wish to protect \Miith{} they will have to fight to preserve the Shroud.

\target{Ishnaruchaefir fights to preserve the Shroud}
\Ishnaruchaefir{} helps them, but only in secret at first. Later he openly declares his opposition to \Secherdamon{} and overtly fights against him. Perhaps he becomes a leader of sorts for the opposition, like Elric in Michael Moorcock's \emph{Stormbringer}.

\Ishnaruchaefir: 
\ta{%
  A balance has reigned over the \Matrices{} of the \Feud{} for thousands of years, but it is slipping. 
  The \banes{} are gaining strength. 
  I cannot have that. 
  There are times when I have held a stalemate preferable to any end to the war. 
  But if any side is to win ascendancy, I want it to be my own people.}

The whole picture of alliances is very chaotic at this point, with factions splintering and turning on each other at the drop of a hat.

Remember to have some sad philosophy about how tragic it is that while the Shroud is a wicked abomination that keeps people down as ignorant slaves and hapless victims of the world around them, the same Shroud is still the world's best defense against all-out invasion and another apocalypse. 
The heroes have to fight to keep the world as a prison. 





\subsubsection{Mortals fight against \iquin}
Some mortals have learned the evil purpose behind \iquin. 
They fight to stop it. 

Describe \hr{How it feels to learn Iquin is evil}{how it feels to learn that your religion is really evil}. 









\subsection{The final purpose of the \Sephiroth}
The \hyperref[Sephiroth]{\Sephiroth} have \hr{Final purpose of the \sephiroth}{a grand purpose}. 
It ties in with the \hs{Morbus} and the \hr{Purpose of \humanity}{purpose of \humanity}. 







\subsection{\Kezerad}
But the \hs{\Kezeradi} are a danger to the \Sephirah{} project. They could potentially break the project, because they still have a \hyperref[Kezeradi telepathy]{deep connection to the \Sephiroth}.

By the end, some \Kezeradi{} have become main characters. Or at least one, namely \hs{\Sithiyacaan}, the last \Kezeradi{} prince. He and his followers work together with \Ishna\dash to some degree at least, although \Ishnaruchaefir{} was never exactly a friend of \Kezerad. 

The Cabal knows that the \Kezeradi{} have the power to fuck up their plan, so they do everything they can to hunt down the survivors.





\subsubsection{An undercover \Kezeradi}
A long-running \resphan, perhaps \Achsah, turns out to be an undercover \Kezeradi. Perhaps she is half \Kezeradi{} and openly condemned her heritage while secretly sympathizing with her people.









\subsection{Epidemies ravage \Azmith}
Epidemies ravage all of \Azmith, now that the \Iquin/\hs{\Morbus} plan is nearing its culmination. 
Entire countries are depopulated and collapse. 















\section{Ramiel's Search}





\subsection{\Vorcanths{} are mad at Ramiel}
The \hs{\vorcanths}, previously Ramiel's allies, had grown mad at him. 
They liked \Shiaraid{} and were nonplussed that Ramiel had backstabbed and killed her. 
They demanded he make it up to them and do them some favours before they would help him again. 





\subsection{Ramiel searches moons for answers}
Ramiel searches the moons, hoping to find answers and peace from his inner Chaos (and \hs{\NexagglachelsCurse}). 
Especially \hs{Visha}, the moon associated with the \hs\vorcanths. 

\lyricslimbonicart{Enthralled by the Shrine of Silence}{
  Cold jewel Moon, I found shelter in your shade \\
  as wind and time took me astray. \\
  I'm floating down the river of forgotten names \\
  into a dark and calm water that devours my flame.\\
  There I find rest and glorious peace, \\
  a sanctuary of eternal bliss.
}

\lyricslimbonicart{Seven Doors of Death}{
  Restless days and sleepless nights.\\
  Drawn in the direction of the moon.\\
  Infernal magnet to mysterious destiny,\\
  beyond the grave of doom.
}

He wants to be rid of his frail \human{} body and return to his true form. 

\lyricsbs{Hate Eternal}{I, Monarch}{
  In this being, in flesh, there can be no absolution.\\
  Therefore I must shed my skin, in a world so fabled, so false.\\
  
  In this shell, in flesh, there can be no solitude.\\
  I will not live in this facade, in a world of contradiction.\\
  
  I, Monarch, master of what shall be.\\
  I, Monarch, captor of what I seek.\\
  I, Monarch, victor of all battles.\\
  I, Monarch, sovereign of this domain.
}









\subsection{Ramiel sees through \Iquin}
Ramiel realizes the true nature of \iquin. 
He is himself a \carcer, and his growing self-understanding allows him to understand \iquin{} as well, and see it for the carcer it is. 

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  DeathspellOmega
}{
  Mass Grave Aesthetics
}{
  The dimension of ethereal totalitarianism discloses itself \\
  And takes possession of the quintessential human soul \\
  Like a nail hammered through most tender flesh \\
  Aeons separate the one \\
  whose eyes have seen through the night of the spirit \\
  The king, the Lord of hosts, draped in terrifying magnificence \\
  From the gleaming clot of trembling vermin
  
  This is you, nourishing \\
  the grand Mass Grave Aesthetics!
}









\subsection{Psychics see portents of the end of the world}
Gradually, as \ps{\Daggerrain}{} master plan unfolds (including the spread of the \hs{\Morbus}), psychics (people who can see through the Shroud) all over \Miith{} see portents of the end of the world: 
Death and emptiness, \hr{\Morbus}{disease} and horror, Entropy and torturous decay. 









\subsection{Ramiel and \Ishnaruchaefir}
Ramiel meets \Ishnaruchaefir. 

\begin{prose}
  \Ishnaruchaefir:
  \ta{Ramiel. I hear you destroyed \Shiaraid.}
  (He studies Ramiel's reaction.)
  \ta{You loved her.}
  
  \Ishnaruchaefir{} fingers his glaive.
  He also destroyed his beloved once, remember. 
  A wordless \quo{\trope{NotSoDifferent}{Not So Different}}-conversation passes between them. 
  They go their separate ways with a newfound respect and mutual understanding. 
\end{prose}









\subsection{Ramiel meets \Cishiel}
\target{Ramiel meets \Cishiel}
Ramiel is re-united with his long-lost daughter, \hs{\Cishiel}. 
At first he does not recognize her. 
She was a young girl when he last saw her.
Now she has grown into a mature and very powerful \resvil. 

She has searched for him. 
She wants him back and will support his bid for the throne. 
But she also resents him for abandoning her to fend for herself back when she was a defenseless little girl. 

\target{Ramiel regains guns}
She gives him back \hr{Ramiel's guns}{\Strith{} and \Currah}, the two pistols he once used to wield. 









\subsection{Ramiel sails north}
Ramiel sails north, seeking a lost \Mystraacht{}/\ophidian{} temple. 

\lyricsbs{Bal-Sagoth}{%
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  For how long have we travelled?\\
  The memory grows dim, lost in the cruel, searing storm-winds.\\
  With the blessings of the Elders we began our journey, \\
  beyond the great veil of shadowed glaciers.\\
  They spoke of a prophecy foretold, an ancient and glorious legacy.\\
  A quest for the realm of legendry, \\
  lost to Man since before even the star-lords descended.
}

He gazes out over the vast, black sea and the darkened, stormy sky, dimly lit by a faint, mystic, spectral luminescence, from the clouds or the northern lights. 

Compare to \bandsong{Bal-Sagoth}{Journey to the Isle of Mists (Over the Sunless Depths of Night-Dark Seas)}. 

\lyricsbalsagoth{Invocations Beyond the Outer-World Night}{
  Seeking answers to the cryptic riddles of the universe,\\
  Secrets of the blackest, most impenetrable deeps of the umbra,\\
  Wreathed in frozen shadow and ice-bound peril,\\
  Subterrene halls of horripilated wonderment...
  
  Tatsumaki Maru voyage north, ever north!\\
  Cleave a path through the massing Arctic ice!\\
  Agleam with all the colours of the aurora,\\
  Far beyond Ny Alesund lies our goal.
  
  Wreathed in frozen shadow and ice-bound peril.\\
  Agleam with all the colours of the aurora.\\
  The portal to the tenebrous cryptic core \\
  of this world's subterrene inner sanctums.\\
  Quaere verum... \\
  Sic itur ad astra!
  
  Invocations and ideograms (dreams of the Xytaxehedron?),\\
  Conjuration of the inner world's (tenebrous) denizens,\\
  And their star-spanning progenitors, \\
  spawned beyond the outer-world night.
}

He feels deep inside him that he is nearing enlightenment. 

\lyricslimbonicart{Beneath the Burial Surface}{
  Water from a thousand tears floats in streams.\\
  The feeling from a thousand years flow over me.\\
  As I once again return to the cemetery gate\\
  I hear the dismal call from the hollow grave.
}






\subsection{I know you are in there somewhere}
In a fight or the like, someone tells Ramiel this: 

\begin{prose}
  Someone: 
  \ta{Carzain! I know you are in there somewhere!}
  
  Ramiel: 
  \ta{%
    Oh, no. You have gotten it mixed up. See, it was never Carzain who was \quo{in there}. Back in the day, Carzain was up-front, and I, Ramiel, was \quo{in there} within him.
  
    You cannot break through to the \quo{real me}. 
    I \emph{am} the real me.
    I am as real as I can get.}
\end{prose}







\subsection{A \resvil{} who loves and hates Ramiel}
Ramiel has an admirer and enemy. A \resvil{} who is in love with him to the point of obsession, but also hates him for his evil and his (in her eyes) betrayal of her people. Is she \Mystraacht{} or from another clan?

Perhaps I can merge her with Shereid. 

Have some scenes from her perspective, where she is disgusted with her own obsession. 

In the end, he probably kills her. Perhaps she willingly lets him kill her: Stripping naked for him, kneeling down to first suck his dick, and then letting him run his blade through her breast. 

Compare her to Titus Pettifer from Clive Barker's \emph{Jacqueline Ess: Her Will and Testament} (\emph{Books of Blood II} p.81-84). Or the relationship between Elric and Stormbringer in Michael Moorcock's \emph{Elric of \Melnibone} series\dash and maybe the scenes where Elric slays Zarozinia and Moonglum. 















\section{At the Temple}
\subsection{Ramiel reaches the temple}
\target{Ramiel's awakening at the temple}
\target{Ramiel's awakening in the temple}
Ramiel reaches the temple, far to the north. 





\subsubsection{First impressions of the temple}
It is a \Mystraacht{} citadel, but built in \ophidian{} style, since \Mystraacht{} has conspired with the \ophidians. It is not only a temple, but a cosmic gzateway to the Throne of the \Mystraacht{} Overlord, ensorcelled by \resphan{} and \ophidian{} power alike. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Swathed in Moon-frosts, in icy winds our blazon flying.\\
  Iron gleaming 'neath the stars, black skies ablaze with astral fire.\\
  White wolves (like silent spirits) haunt us, ever northwards.\\
  The ice-gem leads us, glimmering.\\
  Powerful spells entwine the shrine of legendry,\\
  mighty gates of frozen splendour looming.\\
  When the moon and stars shine as one upon the snows, \\
  the ancient ice-gate opens, the prophecy is fulfilled!
}

\lyricslimbonicart{Lycanthropic Tales}{
  As the storm looms over the frozen landscape:\\
  A call from the beginning of time,\\
  out of darkness through the mist.
  
  Requiem in blood and fire.\\
  Symbols of occult desire.\\
  Through the cosmic vortex,\\
  the gate to unknown darkness.\\
  An esoteric voyage to eminent discovery.\\
  I am the deathlike shadow,\\
  architect of black mysteries.
}





\subsubsection{They fight their way in}
He and his companions fight their way to the temple, past its terrible guardians. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Towering, ice-encrusted forms lumber forth from the freezing mist,\\
  their eyes shimmering with a fiendish, eldritch malevolance...\\
  Our steel is raised against their weapons of gleaming crystal.\\
  And the virgin snow is rendered crimson by bloodshed 
  in a searing storm of slaughter.\\
  Wounded, dying, my flesh rent by weapons no human ever forged or wielded, \\
  I am beckoned forward by a strange, alluring force \\
  from beyond the veil of swirling mists...
}





\subsubsection{They explore it}
He explores the mystic temple. 

\lyricslimbonicart{Infernal Phantom Kingdom}{
  After years of dormancy\\
  in a cosmic mausoleum,\\
  arcane cemetery.\\
  The soil is cursed and sour.\\
  A rotten landscape draped in horror.\\
  Evil has a way of returning.\\
  You can not hide from hell's eye.\\
  It is always burning;\\
  a way of returning.
}

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Shadows, images form \\
  in the glittering rune-carved walls of this glacial chamber,\\
  aecrets frozen within the timeless vaults of eternity.\\
  The throne of the time-lost ice realm, \\
  entwined in the mantle of such searing star-born power.\\
  This frozen, aeon-cloaked seat of immortal majesty,\\
  of an empire forged long before the vast seas rose in devouring fury!
}





\subsubsection{Insight comes}
Here he regains some of his memory. He remembers his life as a \resphan{} lord. He recalls the march of the \Mystraacht{} \hr{Glorious armies}{armies}, the incounterable legions that once forced the world to its knees. Back in those days, the \banes{} were weakened and mostly absent after their great defeat in the \secondbanewar{}, so the \resphain{} were left to their own designs, and they fought among one another. \Mystraacht{} was the most powerful clan, but they were betrayed, their Overlord assassinated, and they sank into the mire of civil war. (See section \ref{Mystraacht betrayed}.)

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  What shimmering swords raised in combat \\
  once sang with the glorious clamour of steel on steel?\\
  What splendid banners, billowing in the icy gales, \\
  once heralded the march of these invincible silver-clad legions \\
  to the blood-swathed embrace of epic battle?\\
  The glory of untold thousands of years past... \\
  this ethereal legacy of mighty Ultima Thule.\\
  The frozen eyes of immortal kings watch me... such a dark splendour!
}

Perhaps Ramiel reads the story of his people on the walls, like in H.P. Lovecraft's \emph{At the Mountains of Madness}. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  These ancient carvings in a time-veiled tongue,\\ 
  etched into the primeval ice countless aeons ago, \\
  now bathed in diaphonous incandescence \\
  by this storm of lucent stellar power, \\
  their mindsearing meaning at last becomes known to me.\\
  Their cosmic secrets unfold.
}





\subsubsection{Ramiel remembers his past}
Ramiel remembers the bloody wars he fought against other \resphain{} and against \dragons{} and \ophidians. 

He remembers fragments of \Ishna. The two have a history together. They are enemies, but respecting enemies. Almost like friendly rivals. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  And then, enlightenment comes, gleaming down upon my consciousness as the bright moon gazes down upon this auroral vista... From my mind is lifted an obscuring veil, a veil induced by sorcerous arts, and I realize I have been merely a vassal of another's twisted will, a pawn in a game which is entwined in treachery and malign aspirations to thresholds of great power. 
  
  Such a traitorous web has been spun! The elders of my kingdom bow in obeisance to the vile priests of Xothan'kur, and it is their diseased machinations which have urged me here, to the very heart of the far-fabled ice realm... for they seek to usurp the power of the Conjunction, stealing the vast energies of the Ice-Veiled throne and absorbing them into their own leprous, undead bodies, perpetuating the adoration of their abhorrent liege for countless ages, liberating his vile will and enslaving the realms of the world...
}

He invokes \banes, \xss{} and cosmic gods. 

\lyricsbs{Hate Eternal}{Beyond Redemption}{
  Awaken from below I call thee,\\
  thy master pure in darkness,\\
  the one of hate before thy paths\\
  were chose to be forsaken.\\
  From depths of time in portals,\\
  through empty eyes of light,\\
  I searched the texts for knowledge.\\
  Now I bleed the sacrifice.
  
  I am of purest power. \\
  Strengths of a thousand souls.\\
  I hear the voices of\\
  the oldest ones burning within.\\
  Reveal the truth unto me, \\
  for I'll command the worthy.\\
  March through the ruins of diminished tribes.
}

He swears to retake the throne and reclaim power. 

\lyricsbs{Hate Eternal}{Beyond Redemption}{
  I summon winds of fire.\\
  I summon winds of disease.\\
  I summon torture upon\\
  all my rivals who shall bleed.\\
  Confronting all before me\\
  to tempt what I have in store.\\
  Don't tempt my fury for\\
  the flames shall burn eternally.
}







\subsection{\Azraid{} begins stockpiling \Erebean{} power}
\target{Azraid stockpiles Erebean power}
\Azraid{} sees portents (mystic or mundane?) that the \banes{} are reeling and about to be defeated. So he begins stockpiling \Erebean{} power, draining it away from \Erebos{} and the \banelords{} and hoarding it for himself. This is effective, because \Daggerrain{} is not expecting \Azraid{} to betray him. \Azraid{} has always been one of the most loyal \resphain. 

Remember to have subtle references to \ps{\Azraid} evil hand in all \Azraid{} chapters. 







\subsection{Ramiel is still bound}
Even after his enlightenment at the \Mystraacht{} temple, Ramiel is still bound. He is not entirely free of the Shroud, still trapped in a \human{} body, and without access to his full \sathariah{} power. He has a lot of power now, but he does not completely understand it. 

And not only that: He is under the effect of spells that chain his mind. He has enemies who want to manipulate him, use his power as a weapon of their own. They don't want him to awaken completely. Ultimately, they want to use him in their plan, where he is to expend all his power and be destroyed himself. Perhaps they plan to directly usurp his power, absorbing it for themselves and destroying him...

No! Better idea: They want to create a new kind of \Sephirah, a more powerful one, but under their control. They want to transform Ramiel into one such. In order for that to work, he must be awake and have access to his full \sathariah{} power... but he must awaken while under their control, so that immediately upon his awakening, they can chain and spellbind him and transform him into their new \Sephirah. 

Perhaps this is connected to the destruction of the original \Sephiroth. Perhaps Ramiel is to become the first of a new generation of \Sephiroth{} that will take over once the current ones have served their purpose. 

At any rate, Ramiel learns too much at the temple. Or, rather, he has learned too much before he came to the temple, so he is able to piece together more of the big picture than they expected him to. He suspects their scheme and takes active measures to undermine them, lay traps for them, infiltrate their ranks, so that in the end, he will be stabbing \emph{them} in the back. 







\subsection{Ramiel's enemies}
Ramiel has \hr{Ramiel's enemies}{enemies among the \resphain}. 
Have a Scabandari Bloodeye-like character. 







\subsection{Ramiel is broken down and rebuilt}
\target{Ramiel's final awakening}
He has regained much of his memory, but he is still trapped in the Shroud and must break free and be reconciled with his true self before he can regain his true \resphan{} form and his \sathariah{} power. 

He undergoes several mental torture. I don't know if this is voluntary or if he's trapped and imprisoned. Anyway, his Shrouded personality must be torn apart and broken down before his true self can re-emerge. 

\Cishiel{} and \Gilchad{} help him. 

Ramiel does not like \Gilchad. 
He is an obnoxious, condescending snob. 
He thinks he is smarter than everyone else and does not give Ramiel the respect he thinks he deserves. 





\subsubsection{Voyage into inner worlds}
Perhaps the awakening process should be presented as a dream-quest, a journey into imaginary worlds that exist/are formed within his mind. 

Compare to Elric's journey beyond the Shadow-Gate in \cite{MichaelMoorcock:ElricofMelnibone}. 





\subsubsection{Facing his fears}
He is confronted with all his fears, sorrows, regrets, shame and pain. He must face, learn and accept the entirety of the brutal truth of his people's cruel nature and monstrous origins, the nature of \humans{} as a slave race, and his own history as a cruel conqueror and betrayer. 

Compare with the \emph{thetalos} cave in \authorbook{Jacqueline Carey}{Kushiel's Chosen} or Chia's caves in \authorbook{Stephen Marley}{Shadow Sisters}. 

Before he begins he promises himself that he will win. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  I smell the gasoline\\
  I smell the fire\\
  I'll make it all so clear\\
  This is my mentor
}

\citebandsong{BeyondTwilight:LurkingFantasia}{Beyond Twilight}{Rage}{
  Trying to face my sanity. \\
  But I'm too afraid to confront with it. \\
  Reaching out. \\
  For what I do not know.\\
  There's no way to explain this Hell I'm in. \\
  Can you? Can you? 
  
  No source of power to take from and wake \\
  from this nightmarish lunacy \\
  Is there a meaning or is this \\
  just a test of destiny? \\
  Creating these monsters for self purposed riches \\
  and glory in the end \\
  Thousands of victims with fresh schizophrenia \\
  isn't out here to pretend.
}

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Godless and Wicked%
}{
  Parts of my memory have been erased.\\
  You've destroyed my files\\
  Oh but I'm getting nearer\\
  It's all getting clearer 
  
  Look for a passage way\\
  Wait for the judgement day\\
  The truth will be told\\
  And my dreams unfold \\
  I'll find a way 
  
  I'm half alive here\\
  But I have no fear\\
  Cause I'll find the light yeah 
  
  Time to changes\\
  Everything re-arranges
  
  I'm getting ready\\
  At the break of dawn \\
  The fight is on 
  
  Godless and wicked\\
  Creepy and cold
}

With all his might he clings to the good memories of grandeur. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Send yourself to get back night\\
  I see women crawl\\
  It's dusty and mid in mind\\
  This is my intention
}

He wants to prove that he is the boss. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  I've seen me set the light\\
  This is the mentor\\
  I met cold on this ride\\
  This is the centre
}

But dangers lurk within his mind. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Don't let it fall\\
  You're not you, you're me\\
  Don't let it get a taste of your blood\\
  Yeah you're feeling small\\
  Don't look at me, don't look at me\\
  You're dancing with the Devil in my hall
}

He almost wanders lost in the dark corridors of his mind. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Now am I lost? Deep in my soul. \\
  There will be no forever.\\
  Through time I'm tossed. A wish without hope. \\
  Into the never.\\
  As time stands still, my spirit grows cold.\\
  I fall into darkness, as black as my soul.

  Now am I lost?\\
  Without hope into the never\\
  Deep in my soul
}

He holds tight. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Crawl for your master\\
  You know I'm in control
}

The whole process takes a long time. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Smell the gasoline\\
  I light the fire inside\\
  Smell the gasoline\\
  I sway all through the night
}

Finally, slowly he awakens. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Ecstasy Arise%
}{
  From dark waters I rise\\
  My once trembling shell conceals a God
  
  Power surging through the void I soar\\
  Intoxicating visions whispering more\\
  In my radiance every color seems to fade
  
  I speak only in thought\\
  Life is not forever nothing is forever\\
  In dark waters I find\\
  Beauty beyond oceans of time
  
  In my radiance every color will soon fade away\\
  In the emptiness I will no longer stay
}





\subsubsection{Triumphant}
His traumas, his emotions and all his personality as Carzain, Vizicar and others is broken down. He is reconciled with his true nature as a \sathariah{} and his \malach{} power of binding souls. (See section \ref{Ramiel binding souls}.) He embraces the enslaved souls and uses them and their power. He becomes the true Ramiel. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  And so, enrob'd by tendrils of starfire and the raiments of lunar mist, the immortal liege whose sceptred empire is eternity sits enthroned and brooding over his dark realm once more.
  
  Swathed in moon-frosts, in icy winds our blazon flying. \\
  When the moon and stars shine as one upon the snows, \\
  the ice-gate opens, the prophecy is fulfilled!
}

He tears asunder his \human{} guise and strides forth from the Shroud into true Reality, resplendent in all of his \sathariah{} glory. 

He summons his faithful servants, which are wolf-like creatures. See section \ref{Ramiel's wolves}. 





\subsubsection{Stronger than before}
\target{Ramiel is wiser from walking the earth}
When he awakens, Ramiel is stronger than ever before. 
Partially because he has spent thousands of years \trope{WalkingTheEarth}{Walking the Earth} as a Scion, which has given him a broad selection of useful experience. 

He is wiser now. 
This helps him deal with and come to terms with his many mental problems and gain some semblance of sanity. 





\subsubsection{Kills \Gilchad}
\Gilchad{} was responsible for guiding him through the torture process. 
When Ramiel finally awakens and emerges, he tells him: 
\ta{I owe you thanks for helping me regain my memory. 
  But I can tell by looking at you that you enjoyed the process. 
  So, with that in mind, I also owe you \emph{this}...} 

And then Ramiel kills \Gilchad. 
And eats him. 

He had wanted to do this for a while, but he needed him. 
Now, for the first time ever in his life, Ramiel has full control over his \Malach{} powers and the associated \carcer. 
This means that he can eat (weak) souls far more easily than any normal \resphan{} or \dragon. 

He also wants to exercise and test that power. 
That is part of the reason for killing \Gilchad. 















\section{Return to \Mystraacht}
\target{Ramiel returns to Mystraacht}
Ramiel returns to \Mystraacht. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  He is the prince of darkness\\
  Returning home to take his kingdom
}





\subsection{Ramiel must get rid of \Dasteron}
Ramiel must get rid of \Dasteron. 

Ramiel learns that \hr{Dasteron cannot become Apex}{\Dasteron{} lacks the \vertex{} strength to ascend to the position of \apex{} of the \Mystraacht{} \matrix}. 
This is no good. 
It is one of the reasons why Ramiel knows he has to dethrone \Dasteron. 
He might be a good leader for a while, but if he cannot become \apex{}, his reign is stillborn and without true prospect. 

Ramiel has learned from his travels, and from the insight he has gathered over his many lifetimes, that something big is coming. 
Some cataclysmic metaphysical event. 
And the \Mystraacht{} \matrix{} has to be strong to deal with it. 
Therefore, a true \apex{} is needed. 
Ramiel feels this \apex{} should be him. 





\subsection{\Mystraacht{} has degenerated}
In Ramiel's absence, \Mystraacht{} has degenerated into a crowd of decadent barbarians striving for maximal evil and perversity for its own sake, and out of some misguided ideological idea that this is their true nature and the purpose of \Mystraacht. 

Compare to the Dark Eldar of \emph{Warhammer 40,000}.

Ramiel: 
\tho{%
  We of \Mystraacht{} boast of our independence and free thinking.
  But we are just as bound by tradition as the \KiriathSepher.
  We go with the flow just as much as they do.
  Just look at how I followed \Zachirah.}

Ramiel intends to bring order and restore the true \Mystraacht. 
Bring them back on track and introduce meaning in all the madness. 

Ramiel: 
\ta{%
  I am \ps{\Zachirah}{} only son. 
  I alone am heir to his legacy and his designs. 
  I alone comprehend the scope of his original vision. 
  I alone understand \ps{\Mystraacht}{} true purpose.}
\tho{%
  And I alone understand the flaws in my father's vision and know how to correct them.}

The \Mystraacht{} do a lot of eating and binding souls. 
This is the source of \hs{Ramiel's bound souls}. 

\lyricstitle{Warhammer 40,000: Codex Dark Eldar}{
  As the Dark Eldar died, the air was filled with escaping souls. 
  A roiling mass of blackness hovered on the edge of vision, the screams of spirits in eternal torment sounded on the edge of hearing.
  
  ...
  
  The ebbing and flowing of released souls slithered around the Dracon, drawn to her blood and fear. 
  She could feel their wispy tendrils sliding over her, probing gently into her mind. 
  She felt like screaming, but she gritted her teeth and was silent. 
  
  ...
  
  The Dark Eldar Lord's eyes glazed over, as he took a long, deep breath. 
  Khirareq felt the spirits around her drifting away, pulled towards the gulf inside the Lord's own soul. 
  The Lord's body twitched spasmodically as he absorbed the freed life essence of his followers. 
  As the spirits of the dead were consumed, Akhara'Keth's spasms increased and a thin dribble of saliva trickled from the corner of his slack lips. 
  With a shuddering sigh, the Lord finished and slumped back in the chair. 
  When he sat forward once more his eyes burned more brightly, his skin was less wrinkled, his hair darker with more lustre. 
  
  ...
  
  She stared straight back at the Lord, looking deep into the ancient pits of evil that were his eyes. 
  
  ...
  
  \ta{%
    You need to rule?
    What do you know of needs 
    You are young, the Thirst has a shallow hold on you. 
    I will tell you of need; a deep, unfaltering emptiness that grows larger and more demanding with every passing of the night. 
    You have heard tales of how I consume a hundred souls a day. 
    That number is but the morsel to whet my appetite. 
    A hundred times that number die every day to quench my desire, my need.
    Spirits unnumbered are distilled in agony and torture to the peak of exquisite taste to fill the chasm of my soul. 
    Do not confuse needs with ambitions.}
}









\subsection{Ramiel is overpowered}
\target{Ramiel is overpowered}
Now that he has regained his full \sathariah{} power, Ramiel is pretty \uber. 
See, he has eaten \Belzir, who was also a \sathariah. 
So now he has double \sathariah{} power. 
He has two \hr{Fragments of \Nexagglachel}{fragments of \Nexagglachel}. 

This has never happened before, so people he encounters do not know what it entails or how to account for it. 
So they underestimate him. 

But it is not pure blessing. 
In addition to her power, Ramiel has also inherited \hs{\ps{\Shiaraid} curse} of self-destructive madness. 
In him it does not take the form of sexual masochism. 
That is too far from his true personality. 
In him it takes instead the form of recklessness and a willingness to take insane chances. 
This is merely an extrapolation of a trait he already had. 
It also makes him more sadistic and disdainful, thus inviting others to bring about his downfall. 

It takes a while for him to realize this. 
He fears it. 
He knows he is turning evil and mad. 
He fights it. 
But he never manages to entirely rid himself of it. 
\hs{\NexagglachelsCurse lives on}.









\subsection{Ramiel confronts \Dasteron}
There is an upstart, \hs{\Dasteron}, who is the closest thing \Mystraacht{} has to a leader these days and thus counts as having usurped Ramiel's place. 

\Dasteron{} is taller than Ramiel, and very powerful. 
(You have to be powerful as fuck to aspire to lead \Mystraacht.)

He mocks Ramiel: 
\ta{%
  I believe you will find that things have changed in your absence, Lord Ramiel.}

Ramiel:
\ta{%
  You will find that things are about to change again following my return.}

\Dasteron{}: 
\ta{%
  You have been out of the game for thousands of years, Lord Ramiel.
  You drifted around down there playing \human, 
  while I was devouring souls and waxing strong. 
  I have even devoured \dragons.
  \Dragons, Lord Ramiel!
  Times have overtaken you.
  I am your superior now.}

Ramiel: 
\ta{%
  Then I challenge you.
  I invoke my right of Trial by Combat.}

Remember to compare Ramiel's and \ps{\Dasteron} \hr{Dasteron's appearance}{appearance}. 





\subsubsection{Motivation}
Ramiel knows he has to prove his own worth by defeating \Dasteron. 
He must impress the \Mystraacht{} so they will accept him as their Overlord. 
He has to entertain in order to lay a foundation for his future reign. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Panem et Circenses}{
  Awake, O' serpent of my heart. It is time.\\
  The sun stands high, and unfaithful crowds await thee.\\
  Redemption in their eyes and stone at hand.\\
  The arena hungers for your venom.\\
  Let the games begin.
  
  Bring in the lions. Bring in the beasts.\\
  It is time to confront the masses with their fears.\\
  A sober moment. A shred of truth.\\ 
  To gaze into an honest mirror. \\
  A disturbance of their sleep.
  
  Violent teeth and claws, untamed and fierce, \\
  reaches far and cut deep into the empty eye.\\
  It is time to let the bitter venom flow\\
  through this embodiment of emptiness.
  
  And the blood shall run free like words.\\
  And the bones shall form stairs to the future.
  
  Now, unfaithful spectator. Are you satisfied?\\
  Did you come close enough to feel the lion's breath?\\
  On day soon your shall be the sacrifice.\\
  A nameless grave of the past.
  
  Protagonist!\\
  Your time is now.
}





\subsubsection{Combat}
\target{\Dasteron{} dies}
\target{Dasteron stronger than Ramiel}
\Dasteron{} is more skilled than Ramiel. 
\hr{\ps{\Dasteron} skill}{Much more skilled}. 
He has faced down \satharioth{} before and knows how to turn an opponent's strength against him. 
Besides, \hr{\ps{\Dasteron} smithing}{he is a great weaponsmith} and armed with the sword \hs{\Scaleron} and many other powerful magical items. 

\ps{\Scaleron} design was inspired by \hs{\Ascaril}, Ramiel's mother's sword. 
\Dasteron{} tells Ramiel this. 

Ramiel is taken unawares when \Dasteron{} displays just \emph{how} skilled he is at all three \hs{Paths}; not only \hr{Path of Light}{Light}, but \hr{Path of Ice}{Ice} and \hr{Path of Darkness}{Darkness} as well. 
This nearly overpowers Ramiel. 
The two combatants are sort of evenly matched at the Path of Light, but \Dasteron{} is far better than Ramiel at Darkness and Ice. 

One reason why \Dasteron{} is stronger than Ramiel is that he has \hr{Dasteron's upbringing}{lived his entire life as a \Mystraacht{} warrior}.  
Ramiel spent his formative years in the wussy and semi-pacifist and effeminate \Merkyrah{}, and then spend thousands of years \trope{WalkingTheEarth}{Walking the Earth} as a Scion.  

Ramiel is \hr{Ramiel is overpowered}{\uber, because he has eaten \Belzir}. 
But even so, he is hard pressed. 
He is not confident he can win. 
So he \emph{cheats}. 

The fight is to the death, but \emph{not} to destruction. 
But after Ramiel wins he breaks the rules and eats his fallen foe's soul, destroying him. 
Dark Eldar style. 

\ta{Stop him!} people around him cry. 
This was not part of the deal.
But no one is brave enough to challenge the \sathariah{} who has just splattered their leader and is now eating his soul and radiating fucking wicked-sick \sathariah{} power in all directions. 

Ramiel: 
\ta{%
  I am Overlord now. That was the prize. I can do whatever I want. That is my right. Will anyone deny me?}

Someone dares call him out on the dishonourable methods he used, both before, during and after the fight: 
\ta{You cheated!}

Ramiel:
\ta{Have you become like the \KiriathSepher{} in my absence?
  Have you become fops and cowards, slaves of etiquette?
  Ruthlessness has always been the \Mystraacht{} credo. 
  I saw my chances, so I took them. 
  Just as I saw my throne and now seize it.}





\subsubsection{Claims \Scaleron}
After slaying \Dasteron, Ramiel claims the sword \Scaleron. 
From that point he wears and uses the sword. 
It is his way of paying tribute to \Dasteron. 
He was, after all, a great and brave man and a worthy opponent. 
A true warrior of \Mystraacht. 

\Scaleron{} is a more than worthy replacement for Ramiel's old weapon, \Ascaril. 









\subsection{Ramiel claims the throne}
Ramiel lays claim to the throne of \Mystraacht. 
At this time he is not only the son of the first and greatest Overlord, but also the last surviving \sathariah{} in \Mystraacht{} (\Shiaraid{}, whom he killed, was the penultimate one). 
So, try as they might, no one can can really deny that he is the best candidate for the throne. 

Critic: \ta{What gives you the right to claim Overlordship?}
Ramiel: \ta{I am Ramiel.} 
He could list off titles, lineage and accomplishments: One of the original discoverers, \sathariah, co-founder of \Mystraacht, sole heir of the last Overlord, and a mega-badass dude. 
But he needs say no more. 
Critic: \ta{I believe you will find, Lord Ramiel, that things have changed in your absence.} 
Ramiel: \ta{And I believe you will find, [Critic's name], that things are about to change again.} 

Perhaps he challenges his rivals by invoking his right of \hr{Mystraacht trial by combat}{trial by combat}, as is a \Mystraacht{} tradition.

\emph{\RamielsAwakeningBook} ends with Ramiel proclaiming his dominion and claiming his ancestral throne, cementing his position as the unchallenged Overlord of \Mystraacht. 

\lyricsbs{Emperor}{Moon Over Kara-Shehr}{
  Master! We ride with the storm \\
  in his name, the sire, wolves' king. \\
  Enter the power coursing \\
  through veins of the night.
  
  Power ripples through me. \\
  Armageddon's thunder will bring others to my side. \\
  The throne is mine. \\
  A blackened storm of evil. 
  
  Master! We ride with the storm to take \\
  revenge in the sky upon the one \\
  who cast thee from his side.
}

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Such power! I am the Chosen. \\
  The secrets of the earth and the stars are unlocked before me.\\
  I am destined to reign forever... \\
  to reign from the Ice-Veiled Throne of Ultima Thule!
}

At the end (or perhaps at the beginning of the next book), Ramiel is contacted by \Daggerrain. 

\daggerrain{Ramiel. 
  Thou hast united \Mystraacht. 
  That is good. 
  But forget not whom thou servest.}















\section{Sentinel story thread}










\subsection{\Vizsherioch{} versus \Ishnaruchaefir}
\Vizsherioch{} is strong, powerful enough to challenge even \Ishnaruchaefir. Despite his young age. 





\subsubsection{\Vizsherioch{} becomes the Dagger}
\target{Vizsherioch becomes the Dagger}
\index{Dagger, the}%
\Vizsherioch{} finally becomes the \hs{Dagger} and takes his rightful place in the \matrix. 
His confrontation with \Ishnaruchaefir{} (and his \hs{Fulcrum}, \Rystessakhin) was important in this process. 











\subsection{\Secherdamon{} communicates with Tiamat}
\target{Rissit communicates with Tiamat}
\Secherdamon, seeking power and guidance in his war against the \banes, contacts the \firstgendragons. He feels the presence of \Tiamat. She appears as a great mass of swirling Chaos, almost too amorphous to be a person. She seems almost mindless. Compare her to Azathoth from H.P. Lovecraft's stories, such as \emph{The Dream-Quest of Unknown Kadath}.

Of course, \Tiamat{} is not mindless. But she has absorbed so much Chaos power and \xzaishannic{} essence that she has become more like \xzaishann{} than a \dragon. Her mind is so Chaotic as to be completely alien and unknowable, even to \Secherdamon, who is otherwise one of the wisest among the \shaeeroths{} in the arts of Chaos, one of those who knows the most and has done the most research. (For instance, he\dash along with subordinates\dash created the Rissitic magic theory of the Three Worlds.)





\subsubsection{\Secherdamon{} visits \Dathka}
\Secherdamon{} visits the fallen city of \hs{\Dathka}. 

\lyricsbs{Emperor}{Ye Entrancemperium}{
  Drawn towards these lands again.
  Seeking death and sacred soil.
  I ride the longing winds of my blackened soul,
  growing stronger once I enter my empire beyond.
  
  Emperium!
  Behold my coming.
  
  The fullmoon rise above me,
  enlightening my realm in a silvery glow.
  Yet the shadows crawl beneath my storming sky,
  guarding treasures from forbidden light.
}

He remembers \hr{\ps{\Secherdamon} rise to power}{the time when he became a god}. 

\lyricsbs{Emperor}{Ye Entrancemperium}{
  I still remember,\\
  though ages ago it seems,\\
  the first time I entered the gates,\\
  the revelation of ritual death\\
  by which I became divine.\\
  Sacrifice of the life I had\\
  among the flesh of the light.
  
  And now I enter again.\\
  Even stronger, yet amazed by what I see.\\
  In ecstasy I mock the world.
  
  Suddenly I memorize,\\
  asking what I left behind.\\
  Nothing.
  
  Can I ever comprehend?\\
  Will my longing ever end?\\
  Never.
}





\subsubsection{\Secherdamon{} seeks out \KhothSell}
\Secherdamon{} also hopes to invoke \KhothSell{} and obtain her power of death to wield it against the \sephiroth{} and the \Morbus. 

\lyricsbs{Exmortem}{Death deceiver}{
  Ancient image of death.\\
  The deepest depts of horror.\\
  A diabolic master plan.\\
  Not to succumb to the damned.
  
  Mummified in slumber.\\
  Awaiting to appear.\\
  Death deceiver.\\
  Exmortem.
}







\subsection{\Ishnaruchaefir{} seeks power}
\target{Ishnaruchaefir seeks out cosmic gods}
\Ishnaruchaefir{} fears \ps{\Secherdamon} plotting. 
He plans to go up against his brother, but he is not powerful enough. 
He needs more knowledge and power. 





\subsubsection{Navel gazing}
He gazes into himself, and into his glaive, \Triestessakhin. 

\lyricsdimmuborgir{The Insight and the Catharsis}{
  Oh, dreadful angel of mine.\\
  Enrich me with the vastness of your being.
  
  Rigid father, teach me to comprehend.\\
  I'll commit myself to understand.\\
  To be the faithful and the instrument,\\
  so that the ones with blindfold can see what I have seen.
}





\subsubsection{\KhothSell}
He seeks out \KhothSell, his \quo{mother}. 
She tells him stuff. 

\lyricsdimmuborgir{The Insight and the Catharsis}{
  What more do you need of proof?\\
  Human hands conforming clooven hooves.\\
  For I know the secrets and lies behind all truths.\\
  Knowlege is power and the power is mine.\\
  It's all mine.
}





\subsubsection{Cosmic gods}
He seeks out some \hyperref[Cosmic gods]{cosmic gods}, hoping to gain the power and knowledge he needs to thwart his brother. 

Their dark halls are splendid and overwhelming, but also dangerous, filled with mighty guardians that strike even the legendary \Ishnaruchaefir{} with terror. 

\lyricsbalsagoth{Invocations Beyond the Outer-World Night}{
  These stygian pitch-black vaults are filled with batrachian devils,\\
  Dire crystalline watch-dogs of the chasmed deeps,\\
  (For the gleaming jewels of truth are not without their protection...)\\
  Vril-gorged adamantine fiends of the threshold,\\
  Spawn of the ersatz interior sun.
}

The cosmic gods turn him away. 

\lyricsbalsagoth{
  The Hound of Chaos Transcends the Nebulous Palisades of Z'xulth
}{
  [THEY-WHO-LURK-AND-BREED-IN-LIMBO:]\\
  Silence, godling! \\
  The fact that you stand before us is testimony to your mettle, 
  but your ambitions shall yet outreach your abilities. 
  
  We have long watched thee and your struggles with amusement, Zurra, 
  Sire of Angsaar. But this audience is now at an end. The path you 
  must traverse lies before you, and you must follow it to its 
  ultimate destination.
}

But \Ishnaruchaefir{} is sneaky, and he manages to surprise and outmanoeuvre them, if only for a moment. He successfully gleans enough of their secret knowledge to achieve what he needs. And so, \Ishnaruchaefir{} confronts some of the mightiest creatures in the cosmos, entities who could crush him underfoot with no effort at all, and he \emph{still} comes out looking like a total stud. \trope{Badass}{Badass}.  







\subsection{\Ishnaruchaefir{} laughs}
At some point, \Ishnaruchaefir{} experiences something funny. 
He laughs with sincere mirth for several seconds. 
\Criseis{} (who is with him) laughs along. 
Seeing him enjoying himself is intoxicating. 
She becomes ecstatic and blissfully happy. 
Her entire world lights up, and everything seems good and bright. 

While it lasts. 

Then he gets over it, and his usual brooding, grim, sardonic state-of-mind takes over. 
Suddenly \ps{\Criseis} world again turns dark and brutal and full of war and pain.
She understands that his mirth made him forget his gruesome burden and all his traumata and hate against the world for a brief moment. 
And his feelings rub off on her, who is closer to him than any other. 
And she is more impressionable and vulnerable than he, so it rocks her world more strongly. 





\subsection{Sentinels seeks out \voyagers}
Some Sentinels, perhaps \Ishnaruchaefir, seek out the \hr{Voyagers today}{surviving \voyagers} to gain knowledge useful against the \banes. 








\subsection{\Ishnaruchaefir{} begins to realize what he must do}
\target{Ishnaruchaefir begins to realize what he must do}
\Ishnaruchaefir{} slowly begins to realize \hr{Ishnaruchaefir realizes what he must do}{what he must do} to overcome his own mental blocks and reach the Gnosis he so desperately needs. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  A distant cry arose\\
  from the fathomless well that is my soul.\\
  I can not hear the words,\\
  so I throw my heart in like a coin\\
  and wish that it would sink forever.
}

He realizes that \hr{Mirage Asylum symbolism}{he is hiding}. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  A purpose, a sacrifice,\\
  or merely temptation?\\
  Is my solitude anything but a perversion\\
  of my vanity?
}

He defends/rationalizes his actions to himself. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  I never cared for this weak inclination,\\
  this paranoid tendency to flock.\\
  And in between all the noise, all the guilt,\\
  a silence would carry my spirit away\\
  from diminishing obsessions.\\
  Away from fools and poisonous flies.\\
}

But deep down he knows his rationalizations do not cut it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  The birth of a dreamer.
}









\subsection{\Ishnaruchaefir{} takes a crazy risk too much}
\QuessanthIshnaruchaefir{} is known to be reckless and take crazy risks. 
In this book, he takes one crazy risk too many. 
It goes wrong. 
He fucks up and accidentally leaves a back door open so the \resphain{} can sneak into his Mirage Asylum. 







\subsection{Mirage Asylum destroyed}
\target{Mirage Asylum destroyed}
At some point \ps{\Ishnaruchaefir} \hs{Mirage Asylum} is breached, invaded by \resphain{} and \banes, overrun and destroyed. 

\Ishnaruchaefir{} now has no safe hiding place. 
He cannot just skulk and let things happen. 
He is forced to take a more active role in the Feud. 
And he does. 
Oh, boy, does he. 
With a vengeance. 
The \resphain{} soon regret provoking him. 

Maybe this is part of \ps{\Azraid} \trope{XanatosGambit}{Xanatos Gambit}. 

The Asylum was protected by the Shroud. 
It was only because the Shroud was \hs{unravelling} that it was possible for the \resphain{} to breach it. 

Make sure to have plenty of story leading up to this, making it plausible that the Asylum could be breached now but not just at any point in the last seven thousand years. 

This is an omen of things to come. 
Soon, the whole world will lose its Mirage Asylum, the Shroud itself. 

Compare to where Chia loses her Black Dragon Valley in \authorbook{Stephen Marley}{Shadow Sisters}. 







\subsection{\Ishnaruchaefir{} confronts \Secherdamon}
\Ishnaruchaefir{} confronts \Secherdamon.

Perhaps, in the distant past, \Ishnaruchaefir{} warred against \Nexagglachel{} in an attempt to bring the \dragons{} together. 
They discuss this.

\begin{prose}
  \Ishnaruchaefir: 
  \ta{That is something you never grasped.}
  
  \Secherdamon: 
  \ta{You think you know so much about me. 
      Yes, I know and understand perfectly, as I always have. 
      But your mission is misaimed (forfejlet?). 
  
      You are so arrogant. 
      You do not understand what I have become; indeed, you never understood what I was. 
      You have power, yes, and you may best me in combat, but in the world I wield power beyond your wildest dreams.%
  }
  
  \Ishnaruchaefir: 
  \ta{Unlike you, I have no wildest dreams...}
  
  \Secherdamon: 
  \ta{... and that, brother, is your failing. 
      It is why you have become a relic of the past. 
      The future is mine! 
      I am the future!
  
      Heh. 
      Perhaps I ought to thank you and \Nexagglachel. 
      If not for his death, I might still live in his shadow. 
      The events of those days are what have me the push to rise above what I was. 
      And today I am by far the greatest of us three.%
  }
  
  ...
  
  \Secherdamon: 
  \ta{%
    The Gnosis which \hr{Ishnaruchaefir refuses to tell Secherdamon Gnosis}{thou stole from me}...
    I have \hr{Secherdamon gains Gnosis}{reclaimed it} by mine own craft.
    I am ready.
    My plan will come to fruition, and thy hideous work will be undone!}
\end{prose}

They fight a great duel. 
It is savage, murderous business, but cathartic. 
They slash and rip one another apart and let loose all the aggression and hate that they have pent up for one another and left to brood and fester for thousands of years. 

For once, \Ishnaruchaefir{} talks about feelings and motives. 
And he defends his actions, something he has always refused to do. 
He shouts in anger, which helps, because it is what \dragons{} do when they are being candid. 
This open anger is cathartic and brings them closer to each other (even though, between \resphain{} or \humans{} or \scathae, such anger could easily work the other way and drive them further apart). 

They learn to understand each other better, through the words and curses they speak, and through the deeper truths their bodies tell, with claws, weapons and magic. 
They understand each other's Aenigmata. 

They come a step closer to resolving the endless feud between the two brothers. 
They learn to respect each other. 

At the end, \Secherdamon{} admits that he is closer to forgiving \ps{\Ishnaruchaefir} crimes against them all. 
This is hard to say. 
Equally hard, \Ishnaruchaefir{} \emph{accepts} this step towards reconciliation. 
Previously he has responded to the idea of forgiveness with nothing but scorn. 
But this time he accepts and respects it (but wordlessly, not explicitly). 

This makes \Secherdamon{} more ready for his final mission. 
\hr{\ps{\Secherdamon} sacrifice}{His sacrifice}. 

% They fight. 
% Ultimately, \Ishnaruchaefir{} slays \Secherdamon.









\subsection{\Secherdamon{} dies}
\target{\Secherdamon{} dies}
\target{Secherdamon dies}
\Secherdamon{} has two possible deaths: 





\subsubsection{Version 1: \Vizsherioch{} kills him}
Somehow, \Secherdamon{} get into combat and is mortally wounded. \Vizsherioch{} comes to him. 
\Secherdamon{} asks his son to save him, but \Vizsherioch{} instead kills him. 

First, \Vizsherioch{} holds a monologue: 
\ta{Yes, father. 
  You created me to be loyal to you. But more importantly, you created me to be loyal to our quest, our legacy.

  You created me from your own essence. I am part of you, and you are part of me. In the long run, this is a weakness. You must understand this. You made me well, but you have held too much back.
  
  You are fallen. To save you would be... inefficient.
  
  I will strike you down, father, and subsume your essence into me. I will absorb your \xzaishannic{} blood, and in doing so I will become greater than any of us.
  
  I will become the ultimate \draecchonosh. I will become the ultimate heir to the \firstgendragons... and to the \xzaishanns. I will become... \emph{perfect}. And I swear to you this, father: I will filfull our destiny. I will scour \Miith{} of the \Erebean{} infestation and restore the glory of the \draconian{} race.}

\Secherdamon{} understands his son's vision, so he is happy when he dies. 

After this, \Vizsherioch{} becomes the ultimate god. 

He remembers the \quo{his} past as a \xzaishann{}.

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  I was spawned deep beneath the Pre-Cambrian sea, \\
  the scion of a far distant sun...\\
  I have traversed the endless stars, \\
  and journeyed to a myriad galaxies...\\
  The dimensional gates of the multiverse are mine to voyage effortlessly beyond,\\
  cosmic infinity is naught to one such as I... \\
  I am as one with celestial eternity...\\
  Clad in gleaming pentlandite armour, \\
  on a whim I may reshape entire worlds,\\
  or extinguish the blazing light of a sun... \\
  and I remain forever enchanted by sylphs...
}

He has memories of the \xzaishanns{} beyond anything \Secherdamon{} and even the \firstgendragons{} had achieved, and he also carries within him the stolen essence of the \banelords. 

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  Wielding this Power Cosmic,\\
  the Omniverse is mine to conquer.\\
  I am a god.
  
  Arcane power lances forth from my fingertips,\\
  life withers before my baleful gaze.
}

He remembers the whole civilizations that the \xzaishanns{} once destroyed.

Have some evil flashbacks with the \xzaishanns{} destroying civilizations. 

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  The proud citadels of great antediluvian empires\\
  have been razed to the ground by my zircon blade.
  
  Riding the screaming crest of fettered ions,\\
  I shall bring my crystalline Chaos where order reigns.
}

He looks down at his father's corpse. 
\ta{I'm sorry, father, but I was not telling the whole truth. 
  I am not driven by our legacy or quest, but by the Will to Power.} 
Compare with Friedrich Nietzsche's philosophy.





\subsubsection{Version 2: Heroic sacrifice}
\target{\ps{\Secherdamon} sacrifice}
\ps{\Secherdamon} death is a heroic sacrifice for his people. 
It has cosmos-spanning metaphysical ramifications and ripples. 

Compare to Anomander Rake's sacrifice in \cite{StevenErikson:TolltheHounds}. 















\section{Random scenes}









\subsection{The power of love}
A \human{} talks to a \resphan{} about how love is the greatest, most important thing in the world. 

\Resphan: \ta{Ah, yes. \quo{Love}. Insertion of dick into cunt, a splash of liquid, followed by cuddling. Believe me, I know what love is. I and my fellows were the ones that created it. We designed your people, programmed your obsession with sex and sexual bonding. Because that it what we need you for. Your \human{} \quo{love} is a pawn on our game, and your idolization of it is a keystone to our \hyperref[Daggerrain's master plan]{Master Plan}.}









\subsection{The master races did not infiltrate}
A Cabalist or Sentinel talks to a mortal about how his people supposedly infiltrated the kingdoms of mortals.

Big guy: 
\ta{%
  Ha! We never \quo{infiltrated} your world. We \emph{created} it! Your civilization is and was ever our tool. We never conquered you or couped you out. You were created, born and bred as our slaves.}









\subsection{\Criseis{} apologizes for \Ishnaruchaefir}
\Ishnaruchaefir{} has hurt some people. 
\Criseis{} comes in secret and of her own initiative to apologize and ask forgiveness on her master's behalf. 
\hs{\Ishnaruchaefir{} never apologizes}. 















\chapter{\ThirdBanewarBook}
\target{\thirdbanewar}
This book details what would later be retroactively called \thirdbanewar, the final showdown with the \banes. 















\section{Overview}









\subsection{The Unravelling brings chaos}
The \hs{Unravelling brings chaos}. 
The world is slowly going mad. 
It will get much worse...





\subsubsection{Ghosts escape}
Now, as the \hs{\sephirah{} plan} is approaching fruition, the \carcer{} of \Iquin{} is filled to the bursting. 
Due to the \hs{unravelling}, \Iquin{} has grown unstable and leaking. 
Ghosts seep out and escape into the world, in droves. 

Compare to the ghosts and the Spectres in \cite{PhillipPullman:HisDarkMaterials}. 









\subsection{\Voidbringer{} must be stopped}
The \dragons{} and other \bane-opponents know that if the Cabal manage to open the portal to \Erebos{} as wide as they did in the \secondbanewar, they will be able to let in millions of \bane{} warriors. 
There is no way in fucking Hell the \Miithian s will be able to deal with that many.
They are fewer and weaker than they were last time. 
So they must stop the portal. 















\section{The \Matrices{} Battle}









\subsection{\ps{\Daggerrain}{} master plan}
\hr{Daggerrain's master plan}{\ps{\Daggerrain}{} master plan}, planned and orchestrated throughout twenty thousand years, is unfolding. 

\Secherdamon{} and \Ishnaruchaefir{} oppose him. Ramiel ostensibly serves the \banes, but is actually planning yet another betrayal.

\Daggerrain{} intends to sunder the wall to \Erebos{} and allow the \Voidbringer{} unrestricted access to \Miith{}. 

But \hr{\ps{\Daggerrain}{} blind spot}{he has a blind spot}...

\Secherdamon, on the other hand, wants to open the gate to Chaos and awaken \Tiamat{} and the \firstgendragons. He has communicated with \KhothSell{} or another one of them. She agrees to help him, but only if he can open the way and make it easy for them to help him. (See section \ref{Rissit communicates with Tiamat}.)

But \Iurzmacul{} plots against his fellow \firstgendragons{}. He does not want to see \Tiamat{} and the others return and devastate \Miith{}. Maybe he tells \Ishnaruchaefir{} and guides him. Maybe \Ishnaruchaefir{} is the son of \Iurzmacul.





\subsubsection{\Dragons{} fear \Voidbringer}
The \dragons{} know that if \Voidbringer{} gains access to \Miith, they will not stand a chance against the feared \baneking. 
If that happens their only recourse will be to follow \ps{\Vizsherioch} lead and appeal to the \xss. 

\Vizsherioch{} will not accept \Ishnaruchaefir{} as an ally. 
He would prefer to kill him. 

\Vizsherioch{} \emph{wants} to see the \banes{} succeed and \Voidbringer{} brought into the world, because then all of \Miith{} will be forced to turn to him as their only saviour. 
He cannot summon the \xss{} alone, but with enough \dragons{} and \quiljaaran{} and other immortals on his side, he can pull it off. 

He relishes the thought of a war between the \xss{} and the \banelords. 
He is willing to risk the destruction of all of \Miith. 
He kind of thinks like a \xss, remember. 
Plus \hr{Immortal \Vizsherioch}{he is more immortal than most}. 









\subsection{Ramiel solidifies his power}
I should let a few years pass between the end of the last book and the beginning of (the serious part of) this one. 
Ramiel needs some time to consolidate his rule as Overlord. 
Not everyone swoons and falls down to worship at his feet. 

And even after some years, he still has rivals and has trouble controlling the dynasty. 









\subsection{\Vizsherioch{} seeks out \daemons}
\Vizsherioch{} seeks out some great and mighty \daemons{} who once served the \xzaishanns{} but have lain dormant for thousands if not millions of years. 

He demands that they serve him. They laugh and reject him, for they have been approached by \dragons{} before. But \Vizsherioch{} is more \xzaishann{} than any \dragon{} ever before. When the \daemons{} realize that, they are impressed and overwhelmed. They agree to serve him. 

He also seeks out \hyperref[Cosmic gods]{cosmic gods}\dash the same ones that \hyperref[Ishnaruchaefir seeks out cosmic gods]{\Ishnaruchaefir{} sought out}. But they turn him down. He claims that he is a \xzaishann{} reincarnated, and they laugh.

\lyricsbalsagoth{
  The Hound of Chaos Transcends the Nebulous Palisades of Z'xulth
}{
  The Outer Darkness has cast me from its cavernous maw! 
  So be it... the final pieces of this great macrocosmic puzzle shall soon fall into place. 
  It has been millennia since I last visited my beloved brother, Zuranthus... 
  and this reunion shall most certainly be steeped in ire! 
  
  The annals of eternity shall soon be illumined by the glorious radiance of my deeds, and the searing fire of my long denied vengeance! Woe unto my dogged nemesis and all those who dare aspire to thwart me... for my final ascendence is nigh!
}







\subsection{\Ishnaruchaefir{} invokes dark gods}
\Ishnaruchaefir{} is forced to invoke various dark gods to seek their power and aid. Some of the same forces that \Secherdamon{} originally invoked to gain power (see section \ref{Rissit invokes dark gods}). 

Perhaps these powers originally helped effect the \hs{\SecondShrouding}, and now \Ishnaruchaefir{} needs their power to defend the Shroud (see section \ref{To break or preserve the Shroud}).









\subsection{\Iquinian{} Church preaches}
The \Iquinian{} Church preaches extra hard. 
The advent of \Lithrim{} is nigh, and the Cabalists want to be sure all the myriad Iquinians are kept under tight control. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  DeathspellOmega
}{
  A Chore for the Lost
}{
  Every human being not going to the extreme limit \\
  is the servant or the enemy of man \\
  and the accomplice of a nameless obscenity.
}







\subsection{Ramiel accepts \NexagglachelsCurse}
Ramiel is seduced by the blood of \Nexagglachel{} in his veins. 
He is swayed by the \dragonlordz{} voice and ultimately agrees to betray the \banelords, in return for peace of mind from the \hr{Madness of \NexagglachelsCurse}{madness and dementia that the curse brings}.

\lyricslimbonicart{The Yawning Abyss of Madness}{
  The winds that carry this esoteric call\\
  emerges from the dungeons underneath my soul. \\
  As I cross the bridge to that darkness, \\
  my eyes are filled with so much death.
}







\subsection{\Ishnaruchaefir{} hears \Nexagglachel{} would be proud}
\target{Ishnaruchaefir hears Nexagglachel would be proud}
\Ishnaruchaefir{} meets some \sathariah. 
Possibly Ramiel or \Azraid. 
(Maybe when \hr{Azraid conspires with Ishnaruchaefir}{\Azraid{} conspires with \Ishnaruchaefir}.) 

\begin{prose}
  The \sathariah: 
  \ta{I have a piece of your brother inside of me, you know. 
    I know something of his thoughts. 
    And you know what? 
    I think if \Nexagglachel{} knew what you had done, he would be pleased.}
\end{prose}

The above is not well-meant. 
The \sathariah{} hates \Nexagglachel, because \Nexagglachel{} hates him and drives him mad and ruins his life. 
But it is sincere. 

\Ishnaruchaefir{} takes it as a confirmation that he is on the right track. 
This makes him incredibly relieved. 
He has spent millennia brooding over whether he is \hr{Ishnaruchaefir's stewardship}{carrying on \ps{\Nexagglachel} legacy} properly. 
When \Criseis{} next sees him, he is happier than she has seen him in thousands of years. 
He does not show it, but she, who knows him better than any other, can detect it in his smell and his aethereal threads. 
The pall of darkness that always hangs over him has lifted a little. 










\subsection{Ramiel allies with \Baelzerach}
In secret, Ramiel contacts the \Baelzerach{} and forges a hidden alliance between them and \Mystraacht. They will not openly fight side by side, but they will strike at the same enemies and covertly work to achieve the same goals. 

This is especially sneaky because no one expects it. \Mystraacht{} and \Baelzerach{} are traditionally enemies, having fought many and very bloody wars. 









\subsection{The \banes{} bring a spaceship to \Miith}
The \banelords{} succeed at bringing a titanic and ancient \hr{Bane technology}{\voyager{} spaceship} from \Erebos/\Nyx{} to \Miith{}. 
It will take all of the \psp{\dragons}{} \xsic{} power to destroy it.

Other people see signs of its approach.

\lyricslimbonicart{Nebulous Dawn}{
  Dark atmospheric winds\\
  are striking towards Earth.\\
  Nihilistic cosmic force.\\
  Asteroid curse.
}

The ship arrives. 
It is a massively powerful juggernaut and wreaks tremendous destruction. 

\lyricslimbonicart{Nebulous Dawn}{
  A blazing phenomenon\\
  launching through the skies.\\
  A deadly impact, tempest chaos.\\
  Utterly devoid of life.
  
  Fountains of fire rise from the lava chambers.\\
  Columns of smoke darken the sky\\
  and cover the landscape in ashes.\\
  Storms with the anatomy of disaster.\\
  Immense swirling winds.
}









\subsection{\Erebos{} \Matrix{} Ascendant}
The \bane{} \matrix{} is strong and has almost taken over the world. 
Its corrupting, destructive influence can be felt all over \Miith{}. 
The \hs{\Morbus} is but one of its manifestations. 

\lyricslimbonicart{Nebulous Dawn}{
  An epic eclipse of the Sun.\\
  A rebirth of desolation.\\
  When the cold silence reigns,\\
  darkness sweeps the face of Earth\\
  with infesting freezing torments.\\
  Across the desert wastelands.\\
  Cataclysmic events.
}









\subsection{\Rystessakhin{} is damaged}
\Ishnaruchaefir{} is in battle, wielding his \hs{glaive}. 
Suddenly it goes wrong, and the unthinkable happens: 
The glaive becomes damaged. 
One of the little blades snaps off. 

\Ishnaruchaefir{} is terrified. 
He knew the Shroud was \hs{unravelling} and it was becoming harder for \Rystessakhin{} to keep it in place. 
\hr{\ps{\Ishnaruchaefir} Nadir}{His own Nadirs} had been growing steadily worse as a result. 
But had never imagined that it would come to this. 

He immediately unsummons the glaive. 
Then he spends all his available energy on fighting his way free and escaping from the fight. 

He realizes that something is catastrophically wrong. 
The Shroud is under attack, and the pressure on poor \Rystessakhin{} has become so great that even her physical form is chipping and falling apart. 
The status quo is crumbling, and he cannot hope to maintain it any longer. 
He needs to change his strategy.
Something drastic must be done. 








\subsection{\Azraid{} conspires with \Ishnaruchaefir}
\target{Azraid conspires with Ishnaruchaefir}
\Azraid{} conspires with \Ishnaruchaefir. 

They have talked before and have a relationship as friendly rivals. 
They are both philosophers who feel somewhat estranged from their races, so they have a certain mutual understanding. 

Now \Azraid{}, for the first time \emph{ever}, comes clean and reveals (part of) his master plan to \Ishnaruchaefir. 
\Ishnaruchaefir{} is the best person he can trust with his plan. 

\Azraid{} also needs Ramiel, but he cannot trust him.
Ramiel is too volatile, too unreliable. 
\Ishnaruchaefir{} \hr{Ishnaruchaefir's impulsiveness}{has spent all his impulsiveness long ago}, so \Azraid{} knows he is dependable.

\Ishnaruchaefir{} agrees to cooperate with his old enemy. 

Perhaps it is here \Azraid{} \hr{Ishnaruchaefir hears Nexagglachel would be proud}{tells \Ishnaruchaefir{} that \Nexagglachel{} would be proud}. 








\subsection{\Ishnaruchaefir{} realizes what he must do}
\target{Ishnaruchaefir realizes what he must do}
\Ishnaruchaefir{} realizes that if he is to truly make a difference in this war, he will need more power.
(He \hr{Ishnaruchaefir begins to realize what he must do}{began to realize this earlier}.)
He will need true Gnosis of his own Aenigma. 
To do this he has to look deep inside himself and come to terms with himself. 
This means he must overcome a ton of traumata, which have festered inside him ever since he \hr{Ishnaruchaefir slays his beloved}{killed \Rystessakhin} and \hr{Ishnaruchaefir goes into the void}{fled into the void}. 

He must make peace with the memory of \Rystessakhin{}. 
He must save himself before he can hope to save the world. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  As deep cuts of truth.\\
  As a fire that closes the wound.\\
  So is my redemption.
  
  Beyond repentance.\\
  This is the ordeal of fire.
}

It will be hard, expensive and bloody, for both him and the world. 
But it will be worth it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  Come suffering, Apocalypse.\\
  Release the fires of Hell.\\
  I call upon destruction and despair.\\
  Not for vengeance, not for power.\\
  Beneath the ashes I walk.
}

At last he takes a deep breath and prepares to do it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  Behold, an angel of vengeance.\\
  A lion. A sword of fire. \\
  Alas, the burden of my heart\\
  is violence undone\\
  Pain unfulfilled.\\
  Silence.
}

Finally he does it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  When I finally cut \\
  deep into the flesh of guilt,\\
  the un-naked body of shame\\
  and the veins of repentance open wide,\\
  sending rivers of blood into my mouth.
  
  The pain is still mine.
}








\subsection{\Harbeth{} dies}
\target{\Harbeth{} dies}
\Harbeth{} dies for some reason. 

Maybe \Zereth{} also dies. 
Most of the \hs{\CiriathSepher{} heirs die}. 















\section{Climactic Battle}
Near the end there is a great, climactic battle between the \bane/\resphan{} forces and some \quo{good guys}. 
There are very few \dragons{} (perhaps only \Ishnaruchaefir{} and his companions), because most \dragons{} support \ps{\Secherdamon} gambit, hoping to utilize the \banesz{} Shroud-weaving spell to bring the \firstgendragons{} into the world and have them vanquish the \Voidbringer{} and his legions.







\subsection{\HothNrul}
\target{Hoth-Nrul summoned}
\Vizsherioch{} and his cohorts manage to bring a mighty ally to \Miith: 
\hs{\HothNrul}, a \xsic{} godling. 
\HothNrul{} is intended to spearhead the coming \xs{} invasion of \Miith. 

Later, \Ishnaruchaefir-tachi communicate with \HothNrul{} and convince the alien god that it is in its interest to attack \Daggerrain.
So \HothNrul{} seeks out the \banelord. 

\HothNrul{} has difficulty attacking \Daggerrain, for he is well-hidden-away. 
But it manages to do some damage. 
When \Daggerrain{} is distracted by the \xs{}, \Azraid{} and Ramiel strike and fuck up \Daggerrain. 

\HothNrul{} \hr{Hoth-Nrul left behind}{ends up the same place where \Daggerrain{} is}. 







\subsection{\Ishnaruchaefir{} leads \dragons}

\Ishnaruchaefir{} does not believe in this gambit. He has no faith in \Tiamat{} and her brethren and does not think they will come to help. So he works to persuade the \dragons{} to fight, to fly with him against \ps{\Daggerrain}{} legions. 

At the last moment, he succeeds. Have a massively epic scene where \Ishnaruchaefir{} flies at the head of a flight of a hundred \dragons, flanked by hundreds of \rachyths, \drakes{} and \pdaemons, to engage the \bane{} armies and seize victory.

Compare to: 

\begin{itemize}
  \item 
    \bandsong{Bal-Sagoth}{Black Dragons Soar Above the Mountain of Shadows}. 
  \item 
    The scenes in \authorseries{Richard Knaak}{War of the Ancients} where everyone holds their breath for the \dragons{} to come to their aid, and where they finally do come and save the day.
  \item 
    The scenes in \authorbook{Graham McNeill}{Fulgrim} p.472, where the Alpha Legion, Word Bearer, Night Lords and Iron Warriors come to the \quo{rescue}. 
\end{itemize}







\subsection{The advent of \Lithrim}
\target{Lithrim arises}
\Lithrim{} finally arises. 

Mankind is very Shrouded, \naive{} and stupid. 
Not quite as well-meaning and {innocent} as the \scathae, but not all that far from them.
That is why it is so effective when their inner \Erebean{} darkness is finally released in the culmination of the \Morbus{} plan. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Sola Fide
}{
  Some rejoice of the children's innocence and smiles\\
  Others of their shameful defloration \\
  by the ministers of Christ, swollen by arrogance and lust\\
  Jesus spoke words of wisdom: \quo{Let the children come to me}\\
  What's more enthralling indeed \\
  than ruining through them the genesis of life itself?\\
  Dive deep into the blue eyes of the newborn \\
  and thou shalt get a glance of heaven\\
  When this dive reveals despair, \\
  hideous ruins of the glory of Hell\\
  The serving sons of disobedience proclaim \\
  Vengeance belongeth unto Him...
}

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Innocence sacrificed and heaven denied\\
  Iniquity divine\dash no repentance\dash over mankind\\
  Mind-raped, self-devoured, empty god-eyed\\
  Transgression coercive, Redemption never to be found

  Under the altar of cannibalism\\
  Man hast (thou) confessed the spiritual schism\\
  And without pride mourned the loss of freedom,\\
  Our blessed Lord have condemned you to martyrdom
  
  Let everything that hath breath praise the Lord, \\
  praise ye the Lord.
}

It is the culmination of that which began with \ps{\Thanatzil} noble sacrifice. 

\citebandsong{DeathspellOmega:Kenose}{%
  DeathspellOmega
}{
  \Kenose
}{
  The advent of Plerosis is the destiny of Man \\
  and shall shatter up to the Heavens,\\
  A savage aperture to the High Mass of the Comforter
}

It is cataclysmic and destructive. 
It unleashes all the wicked, destructive Entropy that, as it turns out, were the building blocks of Man all along. 

\citebandsong{DeathspellOmega:Kenose}{%
  DeathspellOmega
}{
  \Kenose
}{
  Instigating manifold quadrants of industrialized death,\\
  An avid Moloch, never satiated, an endless Feast,\\
  Following the principle of reversibility of merits,\\ 
  shattering up the Word\\
  As Pillars of grayish Soulfire spurt out to a bereaved firmament
}

Man instinctively welcomes the advent of \Lithrim.

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  DeathspellOmega
}{
  Diabolus Absconditus
}{
  The unreservedly open spirit, \\
  open to death, to torment, to joy,\\
  The open spirit, open and dying,\\
  Suffering and dying and happy, \\
  stands in a certain veiled light:\\
  That light is divine.\\
  And the cry that breaks from a twisted \\
  mouth may perhaps twist him who utters it,\\
  But what he speaks is an immense alleluia, \\
  flung into endless silence, and lost there.
}

But it is also scary. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  DeathspellOmega
}{
  Diabolus Absconditus
}{
  From very high above a kind of stillness \\
  swept down upon me and froze me\\
  It was as though I were borne aloft \\
  in a flight of headless and unbodied angels\\
  Shaped from the broad swooping of wings, \\
  but it was simpler than that\\
  I became unhappy and felt painfully forsaken, \\
  as one is when in the presence of God
}

Some \humans{} fight against it. 

\citebandsong{BeyondTwilight:TheEdge}{Beyond Twilight}{Salem}{
  Entombed by the will of the night.\\
  All your thoughts deflowered.\\
  Waived all of your beliefs\\
  in this midnight hour. \\
  Search your past, try and make it back.\\
  All your strength overpowered.\\
  Unknown forces run you through \\
  in the shadow of the black tower.
  
  The witches of Salem hold your fate. 
  
  Relief obtained in sacred mass.\\
  All your sins forgiven. \\
  The ultimate sign of witchery.\\
  The total lack of sanity.
}

\Humans{} lose their individual identity. 

\citebandsong{DeathspellOmega:Kenose}{%
  DeathspellOmega
}{
  \Kenose
}{
  And the victim, blind to the radiating Light of Truth, \\
  stuttering, repeats:\\
  Lamma Sabacthani?\\
  Lamma Sabacthani?\\
  Lamma Sabacthani?
  
  Consummatum est.
}

Mankind becomes a god: \Lithrim. 

\citebandsong{DeathspellOmega:Kenose}{%
  DeathspellOmega
}{
  \Kenose
}{
  I am the son of Man, \\
  and this in erring reason's spite, is my pride...\\
  War, be enthroned, a form of divine retribution!\\
  Execution, be sacred, agent of divine Providence!
  
  The stillness of Contemplation \\
  is allowed in billions of woeful cries,\\
  So astonishingly simultaneous and in unison,\\
  Each and every second, \\
  They defuse each other in such a perfect manner,\\
  Equaling the most inscrutable of all silences\\
  Doctrine of Mystical Substitution, Mystical Body, \\
  Sanctorum Communionem,\\
  Celebrate the Sin of one reflecting, \\
  tectonic forces alike, upon the multitude
  
  The purest of all Holocausts shall be perpetrated\\
  By a loving hand, never knowing if it provided felicity\\
  Or the vilest of everlasting torments\\
  No man can see Me and live!
}

When the \humans{} become the fell, abhorrent \Lithrim, they (or the smarter of them) at last realize the purpose of their otherwise empty and wretched lives. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  DeathspellOmega
}{
  Diabolus Absconditus
}{
  The act whereby being\dash existence\dash is bestowed upon us\\
  Is an unbearable surpassing of being,\\
  An act no less unbearable than that of dying.\\
  And since, in death, being is taken away from us \\
  at the same time it is given us,\\
  We must seek for it in the feeling of dying,\\
  In those unbearable moments \\
  when it seems to us that we are dying\\
  Because the existence in us,\\
  During these interludes,\\
  Exists through nothing but a sustaining and ruinous excess,\\
  When the fullness of horror and that of joy coincide.
  
  As I waited for annihilation, all that subsisted in me\\
  Seemed to me to be the dross over which man's life tarries...
}

But they lose their \humanity{} in the process. 

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  DeathspellOmega
}{
  Mass Grave Aesthetics
}{
  The black Idol fills the veil of flesh with noxious smoke, \\
  Depicting primal human experiences indifferently, \\
  Contemptuous of moral concerns, dehumanized \\
  The howling of wolves and the destructive sword \\
  are portions of Eternity, \\
  Too great for the eyes of merely a man
}

But they gain new insight as they leave their \human{} forms:

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  DeathspellOmega
}{
  Mass Grave Aesthetics
}{
  Violence exists I the moment \\
  when the eye turns upwards into the head, \\
  When inversion is complete and total \\
  The darkness of the upturned eye is not the absence of light \\
  But the process of seeing being taken to its limit \\
  That thorough derangement of the senses, \\
  Way beyond the deceptive conflict between darkness and light \\
  Opens perceptions to the tyranny of the Chekhinah
}

\Lithrim{} is a slave under the \banelordsz{} command. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  DeathspellOmega
}{
  Diabolus Absconditus
}{
  I can utter no word, O my God, \\
  unless I be permitted by Thee\\
  And can move in no direction \\
  until I obtain Thy sanction\\
  It is Thou, O my God, \\
  who hast called me into being through the power\\
  Of Thy might, and has endued me \\
  with Thy grace to manifest Thy Cause
}

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  DeathspellOmega
}{
  Bread of Bitterness
}{
  From a supplication without response, \\
  the essence of man, his ground giving way, \\
  comes illumination by a sun of great evil \\
  that sets aflame the inner core \\
  and enthrones suffocation and the intolerable without respite \\
  as the joyful reward for a million aborted truths.
  
  This silence that among all man has charged with sacred horror, \\
  it becomes sovereign, in repugnant nativity, \\
  and detaches itself from the bonds \\
  which paralyse a vertiginous movement towards the void.
  
  Breathless ecstatic experience,\\
  it opens the horizon a bit more,\\
  this wound of God;\\
  it is the assassination of the abyss of possibilities, \\
  the depths of being left to holy vultures. 
}






\subsection{The portal opens}
\Lithrim{} opens the way for the \Voidbringer. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Perfect Dark%
}{
  Hold the candle\\
  Pass the flame\\
  We're all in this together \\
  Cosmic winds are gathering\\
  Coming your way\\
  Telling you you are only a fragment\\
  A fragment of time 
  
  And it's perfect dark\\
  It's perfect dark here\\
  Hear the angels screaming
}





\subsubsection{People feel the \Voidbringer}
As the Cabal plot nears fruition and they are opening the gate to \Erebos, \Miithian s can feel the presence of the \Voidbringer: 
An ever hungry, ever consuming emptiness, completely inhuman. 
The older immortals remember it from the \secondbanewar. 





\subsubsection{\Banes{} slip through}
Many \lesserbanes{} slip through into \Miith. 
Not in the same millions that got through in the \secondbanewar, but still quite a lot. 
But not so many that the combined \dragons{} and \resphain{} cannot deal with them... hopefully. 

















\section{Ramiel the Betrayer}
\target{Ramiel betrays Voidbringer}
\target{Ramiel betrays Banes}









\subsection{Summary}
\hs{Ramiel} has decided that he will no longer serve the \banelords. 

\lyricsbs{Dream Theater}{In the Presence of Enemies}{\obeylines%
  My soul grows weaker.\\
  He knows and he waits.\\
  He watches over me,\\
  standing at the infernal gates.\\
  In the hour of darkness,\\
  the moment I feared has passed,\\
  the moment I lost my faith.\\
  Promising salvation.\\
  My soul is my own now.\\
  I do not fight for you,\\
  Dark Master!
}

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Hellfire%
}{
  Before me now I see a dying planet.\\
  Captured souls with microchips implanted.\\
  When warning came you stayed the same.\\
  When warning came you stayed the same.\\
  I am crumbling over the obstacles.\\
  Nothing left to entertain. \\
  The smell of burning corpses. \\
  A new world domain.
  
  Before me now I see a future\\
  A future black\\
  Oh come and save me\\
  I'm under soul attack
  
  I will break out from this madness\\
  There is nothing here but sadness\\
  I'm burning in the hellfire\\
  There must be a way\\
  Waiting for the day\\
  
  Hellfire burns higher\\
  Higher, higher. \\
  Only blood remains\\
  There is nothing more to gain \\
  Take me.
}

He now plans to betray the \banes. 
He intends to siphon energy from the \Voidbringer, thus empowering himself enough to overpower \Daggerrain{} and slay or banish him. 
It is a mad scheme, but Ramiel has always been one for mad schemes. It stems from his sublime arrogance and megalomania (see section \ref{Ramiel's megalomania}). 

It is a good plan, but \Daggerrain{} is too clever. 
The \banelord{} has always known that Ramiel was a loose cannon and could not be trusted, so he had taken precautions. 
When Ramiel finally betrayed the \banes, they were ready for him. 

So Ramiel's plan fails...

... or would fail, if not for the intervention of \Azraid. 
\Azraid{} had always played the loyal Cabalist, faithful servant of the \banelords, but \hr{\Azraid{} hates \banes}{in secret he has always hated them} and \hr{\Azraid{} plots against \banes}{plotted against them}. 
He anticipated Ramiel's betrayal and planned for it. 
So when Ramiel fails, \hr{\Azraid{} helps Ramiel betray \banes}{\Azraid{} steps in and helps him}. 

\ps{\Azraid} gambit cannot succeed without Ramiel's help. 
But he cannot tell Ramiel about it before the very last minute, because he doesn't trust Ramiel's ability to keep the secret. 
(It is \emph{hard} to keep secrets from \Daggerrain.) 
It is thus something of a \trope{XanatosRoulette}{Xanatos Roulette}. 

So, in the end, it turns out that \Azraid{} was \hs{\ps{\Daggerrain}{} blind spot}. 





\subsubsection{The Ark}
\target{Ark}
\index{Ark}
The plan (a collaborative effort between \Azraid{} and \Ishnaruchaefir) is to use the wild threads of the collapsing Shroud to \quo{cut} free a chunk of \Miith{}, forming a pocket Realm. 
They then hope to be able to close the way behind them, setting up a makeshift barrier by piecing together fragments of the shattered \CrystalSphere{} and Shroud.

They will then have formed a new mini-Realm, a micro-\Miith{} torn loose. 
This will be their Ark. 
A small population of \Miithian s should be able to escape in this Realm. 
The makeshift barrier will keep the \banes{} out for a short while, while the masterminds use their magic to twist the fabric of space around them propel the Ark away through the universe, to a place where the \banes{} cannot easily find them. 

It will be fucked-up difficult, but \Azraid{} is ready. 
He has spent millennia preparing for this day, and he is prepared to sacrifice his life to see it through. 
And he has \ps{\Ishnaruchaefir} awesome Gnosis helping him. 

In the end, \Ishnaruchaefir{} and Ramiel end up on the Ark, while \Azraid{} destroys himself in the process. 

Perhaps the Ark is not a chunk of planet, but a spaceship. 
Perhaps a commandeered \bane/\resphan{} ship. 
If so, it is huge. 
A colony ship. 
A world-ship. 





\subsubsection{It all takes place in the \matrix{} world}
Note that all of this takes place in the world of the \matrices. 
The three may not physically meet at all. 
They simply pull at cosmic strings using their \vertex{} abilities. 
Any any \quo{portals} are not physical portals, but a ubiquitous thinning of the Shroud allowing passage into \Erebos{} or somewhere else. 





\subsubsection{Why they wait so long}
One might think \Azraid{} could have betrayed the \banes{} long ago. 
But that would not have worked. 
He was not confident he could have done enough damage before he was caught, eliminated and replaced. 

No, this is a unique opportunity. 
\ps{\Azraid} betrayal has to happen \emph{after} the advent of \Lithrim. 
See, they need to rely on the Shroud-wide chaos and fluctuations that \Lithrim{} creates, and use them to set the Ark free. 









\subsection{Ramiel drains the \ps{\Voidbringer}{} power}
Ramiel tries to betray the \Voidbringer. 
This is similar to how Astronema betrays Dark Specter and drains his power in \emph{Power Rangers in Space}. 
%It stems from Ramiel's sublime arrogance and megalomania (see section \ref{Ramiel's megalomania}). 

He absorbs some of the \ps{\Voidbringer}{} power. 





\subsubsection{How it feels}
He feels himself swimming adrift in an endless, bleak ocean of dark, Entropic power, feels how it almost devours him and his sanity.

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{
  The ravening black worms of madness 
  are devouring the shredded remnants of sanity 
  as I return to my slumbering steel-clad body... \\
  but as the dream-veil lifts, I feel my limbs transform, 
  flesh becoming cold stone... \\
  enshrouded by a dark mantle of obsidian. \\
  And the laughter of the Guardians echoes, 
  carries upon the winds of this spectral eve.
}

Actually, he began doing this much earlier, but it takes a while before \Daggerrain{} \quo{discovers} his treachery. 





\subsection{Ramiel fails}
\target{Ramiel as Xanatos Sucker}
\Daggerrain{} is too clever for Ramiel. 
He had anticipated Ramiel's betrayal and easily stops him. 
He is about to kill and destroy Ramiel... 

Before his death, Ramiel's life flashes before his eyes. 
He realizes that \Daggerrain{} must have anticipated his every move and planned accordingly. 
He has been playing straight into \ps{\Daggerrain}{} hands the whole time. 

He truly \hr{Ramiel is nothing}{is nothing}... 
or so he fears. 

Compare a \hr{\Azraid{} as Xanatos Sucker}{similar scene with \Azraid{} much earlier}. 
Also compare to the scene in \emph{\JuukenSentaiGekiranger} episode 46 (or so) where Rio discovers that his entire life has been masterminded by Long. 

We see inside Ramiel's head as he struggles against \Daggerrain{} and almost dies. 

\lyricsbs{Hate Eternal}{Path to the Eternal Gods}{
  On this journey into death, \\
  I am beside myself in tremendous bliss,\\
  For this allegiance has been made. \\
  Shall my sins be absolved, \\
  washed away by the blood of the sacred lambs? \\ 
  Yet I am not amongst the flock.
  
  The remnants of my life now become my vast illusions,\\
  whilst exiled from your grace. 
  
  With fortitude, with courage, 
  I face all my fears, \\
  on my path to the eternal gods. \\
  With my wrath, with my disdain, 
  I face all my fears, \\
  on my path to the eternal gods.\\
  As I cross over into my final place, 
  I face all my fears, \\
  on my path to the eternal gods.\\
  As I bear trials in my final resting place, 
  I face all my fears, 
  on my path to the eternal gods.\\
}





\subsection{\Azraid{} helps Ramiel}
\target{\Azraid{} helps Ramiel betray \banes}
At the last moment, before \Daggerrain{} would have destroyed Ramiel, \Azraid{} steps in and backstabs \Daggerrain. 

Ramiel realizes that he had been overreacting before, overestimating \ps{\Daggerrain}{} omniscience and underestimating his own capability. 
Some parts of his plan actually \emph{were} successful, not covered by the \ps{\banelord}{} \trope{XanatosGambit}{Xanatos Gambit}. 
He regains some faith in himself. 

Together, the two \satharioth{} push \Daggerrain{} back. 
% It closes behind him. 
Ramiel now manages to hold \Daggerrain{} occupied while \Azraid{} works his magic and tears the \hs{Ark} loose. 





\subsubsection{Ramiel and \Azraid{} as kindred spirits}
\Azraid{} criticizes Ramiel for being too overt and honest (\hr{Mystraacht philosophy}{and would be expected of a \Mystraacht}), making him predictable. 
In contrast to \Azraid{} himself, who has managed to creep under even \ps{\Daggerrain}{} radar for twenty thousand years. 

But he is also sympathetic, because he recognizes that Ramiel's situation is like a mirror of his own. 
Back when \Daggerrain{} manipulated the young \Azraid{} into betraying and murdering his brother \Damiarch, he was similarly shocked and disillusioned. 
He shares this with Ramiel. 
This is a rare \trope{PetTheDog}{Pet the Dog} moment for \Azraid. 

A new understanding and empathy suddenly exists between the two \resphan{} lords. 
They are now kindred spirits. 
After this battle they part, not as friends, nor allies, but with a deeper mutual respect than previously. 

\begin{prose}
  Ramiel: 
  \ta{\Azraid. Were you among those who betrayed \Zachirah{} and me?}

  \Azraid: 
  \ta{LOL. Ramiel. 
    I have deceived the \banelords{} for thousands of years. 
    I have deceived everyone. 
    Among all the \resphain, there is no greater fraud than I.
    If I were to answer \quo{no}, would you believe me?
    I would not believe me.}
\end{prose}






\subsubsection{Ramiel imagines hearing \ps{\Daggerrain}{} voice}
Ramiel jokingly imagines hearing \ps{\Daggerrain}{} voice in his head: 
\daggerrain{A minor setback. 
I have planned for this contingency. 
It will take us another 3651 years to get out plan back on schedule...} 
(The number 3651 is a random one that Ramiel pulls out of his ass, but it sounds like something \Daggerrain{} might say.)








\subsection{\Azraid{} dies... maybe}
\target{\Azraid{} dies}
Maybe \Azraid{} dies. 
He sacrifices himself in order to violently disrupt the \Erebean{} \matrix{}, thus causing it to implode and collapse faster than \Daggerrain{} can restore it to order. 

\ps{\Azraid} death leaves \CiriathSepher{}, its hierarchy and \matrix, in chaos. 
(\hr{\CiriathSepher{} heirs die}{Not much is left} of the \hs{\CiriathSepher{} order of succession} at this time.)
It is now up to Ramiel to pick up the pieces and lead the \resphan{} race, if they are to have a chance of surviving. 

Compare to Anomander Rake's sacrifice in \cite{StevenErikson:TolltheHounds}. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Surrender\\
  Lost in the dark\\
  Without angels to guide me 
  
  Hands of death reaching out for me\\
  I'm longing to rest\\
  I see myself move in need of power
}

He knows the \banes{} better than any other. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  I've looked straight into the eyes of demons rising\\
  So close.\\
  I've had one foot on the other side\\
  For so long. \\
  I've seen evil so evil that all living died\\
  The devil is near.\\
}

He wants to stop the \iquin{} plan. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  You may fool the people, but you can't fool me\\
  No more, not anymore. 
  
  And all the souls turned black\\
  There is no way back
}

He dies. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Stranded with the darkness\\
  It's so cold in here \\
  I feel the rush within me
}

He hopes that \Miith{} (or a fragment of it) now has a future. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Time will mend\\
  Ease the sorrow\\
  Take my hand\\
  There's no tomorrow
}











\subsection{\Daggerrain{} falls}
\target{Daggerrain falls}
\target{\Daggerrain{} falls}
\Daggerrain{} has fallen. 
And the worst part is that the link between \Erebos{} and \Nyx{} fell with him. 
\hr{Daggerrain is the gate}{\Daggerrain{} \emph{was} the link}. Without him, the way is closed permanently. 
Now, the only way for the \banes{} to return from \Erebos{} would be to send spaceships, like they did the first time around. 
That might take millennia, because \Erebos{} and \Miith{} are very distant from each other. 





\subsubsection{\HothNrul{} left behind}
\target{Hoth-Nrul left behind}
\HothNrul{} ends up the same place where \Daggerrain{} is. 
No one knows what becomes of it. 
Perhaps it gets destroyed by \Daggerrain{} and his fellow \banelords... if it is even possible to destroy a \xs, which is not known. 
Or perhaps it returns to the \xs{} homeworld. 

Or perhaps it wins. 
It is very difficult to get a clear idea of the balance of power between so \uber-powerful beings as \xss{} and great \banelords. 

The survivors of the war are not sure \HothNrul{} will not return to wreak more havoc on them. 
But they hope not. 















\section{The Fall of the Shroud}
\subsection{\ps{\Ishnaruchaefir} glaive is destroyed}
\target{Ishnaruchaefir's glaive is destroyed}
\target{Glaive is destroyed}
Throughout most of the story, \hr{Ishnaruchaefir fights to preserve the Shroud}{\Ishnaruchaefir{} has fought to preserve the Shroud}. But at the end, he lets himself persuade to assist in unravelling the Shroud. \Triestessakhin{} is the one who persuades him. 

Ultimately, \hr{Ishnaruchaefir's glaive}{\ps{\Ishnaruchaefir} glaive} is destroyed, its Shroud-weaving effect (as a \hs{weaving artifact}) is broken, and the soul of \Triestessakhin{} is released. 
\hr{Glaive must be destroyed}{This had to happen}. 

She is quite insane after these many thousand years inside the sword, but he manages to lead a conversation with her. She is bitter and tries to make him repent. 

\Ishna: 
\ta{%
  I mourn what I have done, and at times I even regret. But I would not change it, and given the chance, I would do the same again.}

Compare to the scene with Lord Soth and his wife at the end of \emph{Spectre of the Black Rose} by James Lowder and Voronica-Whitney Robinson. 



% \subsection{Daggerrain's epilogue}
% In the end, the \banes{} are defeated and the way to \Erebos{} is sealed shut once more. 
% 
% In the very last chapter, \Daggerrain{} holds a monologue, telling his subordinates to get to work. Having planned for this contingency, he has a new plan to reclaim \Miith{}, another four thousand years from now. As he says: \daggerrain{I have waited thirty thousand years. Another four thousand is nothing to me.}







\subsection{\Vizsherioch{} falls asleep}
\target{Vizsherioch falls asleep}
\Vizsherioch{} \hr{Vizsherioch's XS blood}{has too much \xsic{} blood} and is susceptible to the \hs{\xsic{} slumber}. He uses his \bane{} blood to draw upon \Erebean{} power to negate this effect. 

But when \hs{\Daggerrain{} falls}, his connection to \Erebos{} fails and he falls prey to the \xsic{} slumber. 







\subsection{\Miith{} is once again in \Miithian{} hands}
\hyperref[Daggerrain falls]{\Daggerrain{} is gone}. So now the supreme leaders of the \resphain{} are Ramiel and \hs\Azraid. There are still \banelords, but they cannot replenish their number, so they will eventually be hunted down and destroyed. 

Similarly, \Vizsherioch{} falls prey to the \xzaishannic{} slumber. The lords of \dragonkind{} are \Ishnaruchaefir{} and some other \uber-dragons. 

The \Erebean{} and \Machaic{} overlords are gone, and only their descendants remain. The future of \Miith{} now once again belongs to \Miithian{} powers. 









\subsection{The Shroud is torn}
In the process of this whole thing, the Shroud has been ripped and torn and now lies greatly weakened. A climax of this was the \hr{Glaive is destroyed}{breaking of the glaive \Triestessakhin}. 

The \charade{} is breaking apart and the old world order is crumbled. 

The \hs{Unravelling brings chaos}. 
The world will descend into chaos and anarchy. 

\lyricstitle{\cite{HPLovecraft:CallofCthulhu}}{
  The most merciful thing in the world, I think, is the inability of the human mind to correlate all its contents. We live on a placid island of ignorance in the midst of black seas of infinity, and it was not meant that we should voyage far. The sciences, each straining in its own direction, have hitherto harmed us little; but some day the piecing together of dissociated knowledge will open up such terrifying vistas of reality, and of our frightful position therein, that we shall either go mad from the revelation or flee from the deadly light into the peace and safety of a new dark age.
  
  [...]
  
  That cult would never die till the stars came right again, and the secret priests would take great Cthulhu from His tomb to revive His subjects and resume His rule of earth. The time would be easy to know, for then mankind would have become as the Great Old Ones; free and wild and beyond good and evil, with laws and morals thrown aside and all men shouting and killing and revelling in joy. Then the liberated Old Ones would teach them new ways to shout and kill and revel and enjoy themselves, and all the earth would flame with a holocaust of ecstasy and freedom.
}

A new world order will establish itself, although it may take centuries. 

\index{technology}
\Ishnaruchaefir{} predicts that the Shroud will mostly unravel and fade away. With the loss of the Shroud, \hs{technology} will again accelerate. 

A suggestion for an epitaph: 

\lyrics{
  The \charade{} is broken. \\
  The Shroud is sundered. \\
  Now, let the arms race begin.
}

Knowledge will escalate, and so will war. 
In a way, this is \hr{Ishnaruchaefir sees three futures}{\ps{\Ishnaruchaefir} nightmare} come true. 

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there... 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}





\subsubsection{The Space Age begins}
Both races will now venture into space, looking for new \dweomers{} to consume to feed the dying Heart. 




\subsubsection{The \banes{} still exist}
Make it clear that the \banes{} have only been banished, not destroyed. 
\Daggerrain{} still lives. 
He will be back. 
\Miith{} has gained a reprieve. 
Maybe a thousand years. 
Maybe less.
However long or short it takes, the \banes{} \emph{will} return. 

So all this talk about \quo{evolution towards perfection}, which obsesses both sides in the Feud, is more relevant than ever, if Mith is to prepare itself and be ready to face the \ps{\Voidbringer} attack a \emph{fourth} time. 






\subsubsection{A respite for the Heart}
\target{Respite for the Heart}
The Heart of \Miith{} is finally freed from \hr{Heart weakened}{the scourge of the \sephiroth{} and the \Morbus}. 
The millions upon millions of imprisoned souls finally die and are released back into the Heart. 
This lets the Heart regain some of the stolen lifeforce and thus grow in strength. 

But this is just a temporary respite. 
The menace of the \banes{} is gone, but the remaining two master races (\dragons{} and \resphain) still battle for control of the Heart. 
The two races \emph{cannot} coexist\dash their \matrices{} are inherently incompatible and inimical, ripping and tearing into the Heart\dash and the Heart will continue to be drained and weakened until this war comes to an end. 

So the war for the Heart escalates again (as per the \quo{arms race} above). 
After all, this is what the Heart is: 
Life and death, beauty and ugliness, love and cruelty. 
Nature. 

\Miith{} is a cruel world. 





\subsubsection{Ramiel and \Ishnaruchaefir}
Ramiel and \Ishnaruchaefir{} are on the Ark and chatting. 

\begin{prose}
  \Ishnaruchaefir:
  \ta{Perhaps the \banelords{} will find us again.
    Perhaps not.
    Perhaps there will one day be peace between our two peoples.
    Perhaps one of our races will become extinct\dash or both.
    Perhaps we will somehow find the means to wage war for all eternity.
    Who knows?}
  
  Ramiel:
  \ta{%
    We \resphain{} have always held that science is one of our greatest weapons and assets.
    We know\dash or believe\dash that we are set in the world to rise above our nature.
    I will take command of the \resphain{} here, and I will see to it that we rise to our fullest potential.
    I am Overlord now...}
  
  \Ishnaruchaefir:
  \ta{Overlord of what?
    I doubt any traces of the old world order have survived the exodus of the Ark.
    I doubt that \Mystraacht{} even exists anymore.}
  
  Ramiel:
  \ta{I have seized a throne by force before and I can do it again.
    And know this: 
    My goal is to secure the future of \Mystraacht.
    No one else's. 
    Maybe this road will end in peace.
    But if I must destroy your people\dash or any other\dash so that mine may live, then so be it.}
  
  \Ishnaruchaefir:
  \ta{Heh. So be it.}
\end{prose}

Remember that after the exodus of the Ark, \Mystraacht{} does not really exist anymore. 
So Ramiel is no longer Overlord. 
But:

\begin{prose}
  Ramiel:
  \ta{I have seized a throne by force before and I can do it again.}
\end{prose}







\subsubsection{\Ishnaruchaefir{} looks forward}
The very last scene of the book is with \Ishnaruchaefir{}.
He looks forward the chaos and war that is to come. 
No longer will he hide and huddle in some Asylum. 
He will fight. 
It will be... exciting. 

Remember: \emph{End on a dark note!}









\subsection{The cost of the \thirdbanewar}
The \thirdbanewar{} is the most costly and most apocalyptic of the three \banewars. 
It did not kill as many people in absolute numbers as the first two had done, but it killed a larger percentage of the population. 
The population is smaller at this time, remember. 

\Daggerrain{} is now gone, but \Miith{} has paid a terrible price. 
Ahead wait centuries of chaos, blood and war. 














\section{The Future}
After a thousand years or two, a new interstellar civilization centered on \Miith{} will be established, and a \quo{science fantasy} aera will begin. Compare to \emph{Warhammer 40.000} and \bandalbum{Bal-Sagoth}{The Power Cosmic}. 









\subsection{\Resphan/\dragon{} hybrids}
Perhaps some day in the far future, someone will begin experimenting and trying to create a race of \resphan/\dragon{} hybrids. 
These will try to conquer the races and destroy those who will not join them. 
This is seen as evil, but the intent is good: 
Only a hybrid race can stop the war and let the Heart of \Miith{} live on in peace. 























\chapter{Random Ideas}












\section{\Shilred{} Story Arc}
\subsection{Rissitic invasion}
Some time after the Rungerans cross the Pelidorian border, Rissitic fleets sail north to besiege and conquer cities in \Scyrum. 
%march north from Gaznor into Beirod. They besiege and conquer Beirodi cities. 

%Or... wait... is it Beirod they attack? Or is it \Scyrum? \Scyrum{} might make more sense. 

For the Rissitics, controlling more land in \Velcad{} is nice, but the chief purpose of this attack is to draw the Redcor away. See, in intra-\Velcadian{} wars the Redcor traditionally take little part, acting mostly as negotiators and healers. But in case of a major attack on an Iquinian kingdom by a heathen invader, the Redcor typically offer more direct aid, participating in battles with their magic. So when the Rissitics invade, the Redcor are forced to send Vaimons from the entire region to help oppose them. 
This makes the invasion harder, but it has the nice bonus feature that it leaves Malcur drained of Redcor, making it easier for the Sentinels to operate there. 

We follow Narkiza on his march north through \Scyrum. 

%Is Geldashad with him, or is he off on a mission of his own?

%What about \Shilred? 

Remember to describe the Rissitic army as \hr{Glorious armies}{magnificent and glorious}.







\subsection{\Shilred-tachi get lost in \Nyx}
\Shilred{}, \Dzasselid{} and \KarsaOrlong{} (see \ref{Karsa Orlong}) take part in the initial attack on a port city in southern \Scyrum. Maybe they are together with Mestos and Semphai. Anyway, during the battle they become separated from the main army and nearly get killed by \banes. %Maybe they even flee out of the mortal Realm and stumble into \Nyx. 

Maybe \Dzasselid{} deliberately takes them into \Nyx. Perhaps he has a back-story as a double agent for the Cabal, and thus knows his way around in \Nyx. Or something like that. He needs some skeletons in his closet, remember?

At any rate, they end up in \Nyx{} and get surrounded by \banes{} or other monsters. 






\subsubsection{\Ishnaruchaefir{} approaches}
Just when \Shilred-tachi are about to be killed, \Ishnaruchaefir{} appears. He appears in humanoid form. Using magic (incl. the spell \quo{\kingstongue{khestni}}) and his mighty glaive (see section \ref{Ishnaruchaefir's glaive}), he slays the monsters and saves them. The monsters should be huge, monstrous and menacing, like in the anime \emph{Devil May Cry}. 

Given that they owe him their lives, he claims them as his own. Perhaps one of the \RNinjas{} knows who he is and convinces the others to be respectful. Somehow or other, \Ishnaruchaefir{} beats it into their heads that he is a high-ranking ally of \Hriist{} and that they should obey him. 

Maybe \Ishnaruchaefir{} first approaches \Narkiza{}, gives a little help and asks to borrow some of his men. 






\subsubsection{\ps{\Ishnaruchaefir} mission}
\target{Ishnaruchaefir recruits Shilred-tachi}
\Ishnaruchaefir{} sends them on a private, secret mission. He wants them to find a cave somewhere in western \Velcad{}, where they must do fulfill some as-of-yet unspecified task for him. 

\Ishnaruchaefir{} tells them that he cannot go off searching for the cave himself, as he would be detected and attract Cabal attention (and Sentinel attention, for that matter). But he teaches them an invocation that will summon him, to use when they reach the cave or are in dire need of his help. 

\hyperref[Ishnaruchaefir's fake mission]{The above is actually a lie.}







\subsection{\Shilred-tachi go into the \Wylde}
On their mission for \Ishna, \Shilred-tachi must go into the \Wylde{}. \Ishnaruchaefir{} throws them into some place which has a tenuous link to \Nyx. Perhaps a cave system that was once inhabited, or a ruined castle. It must be something sort of urban area, since \Nyx{} is city-like. 

From there, they go out into the \Wylde{}. They fight their way through monster-infested jungles. 

Maybe they encounter a native tribe. Maybe they help them, like how Karsa Orlong helps the Anibar in \emph{The Bonehunters}. Maybe they just coerce them into accepting them. Maybe they hire native guides, who later die. 

They are chased through the \Wylde{} by savage monsters, maybe zombies or lycanthropes. Monstrous almost-humanoids, at any rate. Occasionally they are harassed by the Cabal. 







\subsection{\Shilred-tachi find a ruined city}
\Shilred-tachi find a ruined city out in the wild, with broken walls, toppled towers, defaced monuments and statues and the like. It is decrepit, dead, moss-grown and spooky. 

Compare to the cemetery in the movie \cite{Movie:HouseoftheDead}. 

Remember to have some references: 
\ta{%
  There are many places of power in the world, places of convergence. Especially out in the \Wylde{}. After all, the \Wylde{} is far vaster than the settled world.}

Remember to have them fight monsters. Have a scene where \Dzasselid{} kicks the butts of loads of monsters. 







\subsection{\Shilred-tachi find a laboratory}
\Shilred-tachi fight past monsters and end up in the laboratory of some necromancer or witch-doctor. It is filled with mutilated corpses and deformed creatures\dash living, dead or undead. Like in the movie \cite{Movie:HouseoftheDead}. 







\subsection{\Shilred-tachi crawl around underground}
\Shilred-tachi find themselves underground in a system of dark, creepy, monster-infested caves. Like in the movie \cite{Movie:HouseoftheDead}. 








\subsection{\Shilred{}-tachi see great monsters in the distance}
%Remember \Shilred{} and her party. They need to do something intelligent. 
\Shilred-tachi, travelling in the \Wylde{}, see some colossal creatures far off in the distance. They need to be at some special place or in special circumstances, being able to see into the Beyond, in order to be able to see them. 

Maybe they see the creatures on a background of \Nyx{} or \Machai{}, or maybe just the great mountains and forests of the Beast Realm (these are larger than the ones that can be seen from within the Shroud). 

Perhaps the creatures are \dragons{} and \banes{} fighting. 

Perhaps, in the end, they see \Ishnaruchaefir{} vs \Teshrial-tachi this way. 

Remember to drop hints along the way about how powerful and terrible \Ishnaruchaefir{} is. Perhaps when they see these monsters, they reflect about \Ishnaruchaefir{} and his awesome power. 







\subsection{\Narkiza{} on the move}
%Early on, we follow \Filshed{} and her party as they invade Fendor. 

We follow \Narkiza{}, first in the port city in \Scyrum, and later as his army pushes north into \Velcad{}. His invasion is one of several \quo{prongs} in the Sentinel scheme.

In \emph{\RungerWarBook}, only little time is devoted to \Narkiza{} and the other Rissitics. They will be given much more screen time in \emph{\CarzainWithRedcorBook}. 
%in the scheme to awaken the \Haskelek, 

%\Filshed{}, maybe together with the two \Gisshorn, are sent as a second \quo{prong} on covert missions to revive parts of the \Haskelek. 

%A third \quo{prong} are the Rissitics that are with Morgan Runger. 

%There might be a fourth \quo{prong}, consisting of some non-Rissitic Sentinels. They might include \Cryocas{} and her lover, Nisgzarchiev. Or maybe Vlad Racul. 










\subsection{\Shilred-tachi reach the cave}
\target{Shilred-tachi reach the cave}
\Shilred-tachi finally reach their destination. 





\subsubsection{They see fantastic and terrible things}
They near the cave and travel through fantastic, alien Realms (perhaps parts of \hs{\Machai}). Compare to \authorbook{Clark Ashton Smith}{The Door to Saturn}. 

They even see glimpses of the \xss. 
\Shilred{}, \hr{\Shilred{} is a nerd}{being something of a nerd}, is amazed by what she sees. And horrified.

\lyricslimbonicart{When Mind and Flesh Depart}{
  I'm captured by the sound of the tempest winds, \\
  and my demonvoice that dwells within.\\
  The ground I walk is sour.\\
  A spectrum shines so genuine.\\
  While the earthquake starts to devour,\\
  I behold the shrine in the ruin.
}

She sees horrors and is disillusioned. 

\lyricslimbonicart{When Mind and Flesh Depart}{
  The human way of life, \\
  an inferior state of mind.
  The third stone from the Sun\\
  had become a stillborn illusion.
  
  I'm under siege of anger and fury.\\
  There is no values, no faith or glory.\\
  Antagonising mortal flesh.\\
  Life on Earth I do oppress\\
  with infernal bleedings of bitterness.
}






\subsubsection{\Teshrial{} moves out}
\Teshrial{} fails in his attempts to guess \ps{\Ishnaruchaefir} thoughts. 
When \Shilred-tachi ostensibly reach their destination\dash the main entrance to the cave\dash they are attacked by \ps{\Teshrial} monsters and must call on \Ishnaruchaefir. 
He appears in humanoid form to fight the monsters. 
\Teshrial{} is now convinced that \Ishnaruchaefir{} means business, so he rushes to his location in person, leading a group of mighty \banes{} and monsters. 





\subsubsection{Epic description of \Ishnaruchaefir{} as a \dragon}
\Ishnaruchaefir{} assumes his true, \draconian{} form. Insert an epic description of the mighty \dragon{} here, a la \bandsong{Bal-Sagoth}{Black Dragons Soar Above the Mountain of Shadows}. 

This is the first time we are shown a \dragon. 
Describe the mortals' awe at the sight. 
\Dzasselid{} might have seen one before, but \Shilred{} sure hasn't. 
She has heard \hs{myths} of \dragons{}, but reality surpasses the myths. 





\subsubsection{\Dzasselid-tachi are sent to the real cave}
\Ishnaruchaefir{} draws out all the Cabal monsters in the area. 

In the meantime, \Criseis{} sees to it that \Dzasselid-tachi are sent to the \emph{real} cave he is after\dash which is now mostly unguarded. 

They encounter some creatures that try to block their way. 
\Criseis{} zaps them.

\lyricsbalsagoth{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire - Part II: The Dark Liege of Chaos is Unleashed at the Ensorcelled Shrine of A'zura-Kai
}{
  [THE KING:]\\
  By the darkling powers of the Shadow-Sword, \\
  I call forth the fury of the storm\\
  to rend the massed legions of Chaos!
  
  [ALTARUS:]\\
  And at the sound of his baleful Words of Power, \\
  the sky split wide in fury, \\
  and searing tendrils of ruinous lightning \\
  lanced inexorably forth from the heavens \\
  to rake and reave the massed hordes of Chaos...
}

They find the creatures they are looking for and set them free. Thus \Ishnaruchaefir{} has tricked \Teshrial{}, and his circuitous plan has succeeded. The freed monsters now rush to Malcur to assist in the summoning of \Nithdornazsh. 

See \hyperref[Ishnaruchaefir kills Teshrial]{here} for the end of the fight.

%\Teshrial{} tries to flee to Malcur, but \Ishnaruchaefir{} keeps him, and eventually kills him. 





\subsubsection{\Shilred{} is left behind near the cave}
\Shilred{} accidentally gets separated from the rest and stays behind near the cave. 
She gets to see the fight between \Ishnaruchaefir{} and \Teshrial{} in all its gory glory. 















\section{Sir James story arc}
Sir James is a \human{} Iquinian knight living somewhere in \Velcad{}. 
It might be in the east, if I want him connected to the king-thing and Vlad Racul, or it might be in the west (Ontephar or \Scyrum) if I want him connected to Telcastora Ilcas. 
I think it's going to be in the east. 

There is also Sir Lawrence, another knight. 
Perhaps Sir James' companion. 

And Prince Alistair, who later becomes King Alistair. 
I think. 

And Vlad Racul, a mysterious sorcerer who is actually the \dragon{} Candrazor (a high-ranking Sentinel) in disguise. 

Sir James discovers a Rissitic plot somewhere. 
The Rissitics work on resurrecting a part of the \Haskelek{} \daemon. 
He goes to the Redcor for help. They set out to thwart the Rissitics. 
It turns into a big quest with all sorts of stuff going on. 
There's an evil Rissitic mastermind (who?) who keeps outsmarting them, but somehow the reader is assured that good will prevail. 
And then, in the end, I assfuck the reader by having the Rissitics win, and Sir James and his party of heroes are killed. 




\subsection{The beginning}
Sir James, as a knight and minor lord of sorts, is approached by the girl Lica, a commoner who's had visions, seen suspicous things. 
His advisors scoff at the girl's fanciful tales and persuade him to dismiss her, but he does so with doubts. 
Later stuff happens to him that convinces him she was right, so he seeks her out and brings her back. 

James or his companion asks Lica: 
\ta{How old are you, girl?}

\ta{I am sixteen, my lord.}

Later, James comments to his companion: 
\ta{She is pretty, though.}

The companion laughs. 
\ta{She is sixteen, James. 
  Even my warty cackling crone of a great-grandmother was pretty when she was sixteen.}

%Turns out that Lica has seen a \bane. The \banes{} are working on some big thing, so they are getting bolder and more careless. (It's for the same reason that Catrian saw a \bane{} earlier.) Or maybe she hasn't seen an actual \bane, but merely a Cabalist working magic. Or maybe some \Nyxian{} monster. 
Turns out that Lica has seen either a Sentinel mage or some \daemon. 
And it's a good thing that Sir James starts to believe her, because it turns out the Sentinels is after her. Assassins come for her and he has to protect her. They flee back to the castle or whatever, and the authorities (Redcor church?) finally believe that something is up. 

Lica is gifted in seeing into the worlds beyond. Since her childhood she has had trouble accepting the illusion that everyone else believes in. She always wanted to see through the lie, doubt what she was told. This has continued to the current day (she is now 16 or so) and lets her see many things that others can't, but it also makes her strange (she is unmarried and unbetrothed, and her parents worry) and affects her sanity. 

Alarmed by Lica's vision, the Redcor send a delegation to investigate. Lica is brought along as a guide of sorts, and Sir James goes as her protector. 









\subsection{Lica sees strange visions}
Lica sees grim and horrid visions. 
She hates this \quo{gift}. 

\lyricslimbonicart{The Supreme Sacrifice}{
  Thought are tyrants that always return\\
  to rape and torment the heart.\\
  As darkness sweeps the face of Earth,\\
  I enter the chambers of bleeding art.
}









\subsection{Lica sees the \Morbus}
Lica sees the \hs{\Morbus} at work. 
She has dreams of its evil consequences. 

She sees visions of \Nyx{} and mistakes them for visions of the future. 
She is scared shitless. 

\lyricsduana{thisistheend}{This is the End}{
  I dream of a host cockroaches \\
  crawling, swarming over charred flesh \\
  up bitter blackend walls \\
  in sewer pipes now purgd \\
  the cries of many amplifd \\
  then swallowd by silence \\
  echoes of a lost world \\
  of a foul smoke that lingers like stale breath \\
  of steel/glass/concrete fusion-statues \\
  rising high in a pale and infinite twilight \\
  shining beacons like bleachd bones 
  
  I see field upon field upon field \\
  of bloatd-cattle-corpses bleeding intestines \\
  staring with sightless opaque eyes \\
  of waves drowning mountains \\
  and the earth's flesh torn with angry fissures \\
  of molten-spewing-spittle \\
  and hot lashing tongues \\
  of a planet roaring/quaking/quivering \\
  with unbound vergence 
  
  shivers erupt through space and time \\
  and images flashing faster faster... \\
  until finally all is annihilated 
  
  like a vacuum space sucks the debris \\
  into a black empty hole \\
  and I fall down into the void \\
  this is the end
}









\subsection{Lica suffers}
Lica feels like she is losing her innocence and being corrupted from the inside by the terrible truths she sees.

\lyricslimbonicart{Beneath the Burial Surface}{
  The sky is darkening, soon the night befall.\\
  Righteously angels are weeping for my soul.\\
  All childhood dreams are soon to be lost,\\
  all innocence to be shattered.
  
  I am the fallen from grace.
  
  My face is a river.\\
  See my eyes as they drown in black.
  My sacred doom and nemesis\\
  beneath the burial surface\\
  To the final act of the immortal sin\\
  I am lead by funeral winds.
}









\subsection{Lica can curse people}
Lica discovers at a young age that she can curse people. 
When people are mean to her or refuse to believe her, she can stare at them and hate them and wish them ill\dash and sometimes it happens.
This is a manifestation of her (albeit weak) \vertex{} powers. 




































 

 

 
\end{garbage}