
\begin{comment}
\part{The Book Series of \Miith}
\end{comment}
\begin{comment}
\include{SentinelsMain}
\include{Utilities/UsePackages}
\input{Commands}
\input{Hyphenation}
\include{Story/DominatorsofMith}
\include{Story/ArchonsofMith}
\include{Story/SentinelsofMith}
\end{comment}



\part{Dominators of \Miith}















\chapter{\FirstbanewarBook}
Tells the story of the \ophidians, the origin of the \draecchonosh{}, the coming of the \banes{} and the \firstbanewar. 















\section{Pre-History}
\subsection{The time of the ancient gods}
In ancient times there were three peoples that dominated \Miith{}: The \krakens, the \xss{} and the \voyagers. 

Only the \krakens{} were native to \Miith{}. 
Billions of years ago they ruled the Realm. 
Then they became tired and went dormant. 

Then the \voyagers{} came from space in their spaceships. 
They created life in their \quo{Genesis Pits}. 
They created the primordial slime from which all \Miithian{} life descends. Compre to Ubbo-Sathla, the shoggoth \quo{mother mass} from the Cthulhu Mythos. 

Perhaps the \voyagers{} created \emph{blood}, the vessel for the power of the \hr{Heart}{Heart of \Miith} and the foundation of all \Miithian{} life. 

\target{Voyagers create the Heart}
The \voyagers{} created the Heart from some Chaos power. 
They shaped \Miith{} into something that looked like modern-day \Miith{}. 

Perhaps they also created the Sun, which is a manifestations of the heart. 
But I doubt that. 

But when the \voyagers{} shaped all their life-stuff, they unwittingly tapped into a sinister force; the energy of some dark god of life and death. 
Perhaps a \kraken, perhaps a \xs{} (\hr{Kyaethem Chrei Az}{\KyaethemChreiAz}?). 
This entity infested their \dweomers{} and their Ubbo-Sathla. 
The \voyagers{} did not discover this until very late. 
From there they could only hope to contain the taint, not cleanse it. 
Later their creations rebelled against them. 

Then the \xss{} invaded and, after waging war for millions of years, they wiped out the \voyagers{}, who had previously dominated \Miith{}. 

\lyricsbs{Vital Remains}{Icons of Evil}{
  Defame the names of all your dead gods.\\
  Vomit upon the path of salvation.\\
  Watch the creator succumb to extinction.\\
  The hunter now the hunted,\\
  you become the prey for us all.
}

Later, the \xss{} and \krakens{} waged wars. 

Then the \xss{} went dormant. 

Billions of years later, this life that the \voyagers{} had created would become the \ophidians. 
But they also created some horrid abominations. 
Something like the shoggoths from \authorbook{H.P. Lovecraft}{At the Mountains of Madness}. 
Maybe these are the \hs{Bladed People}. 

Maybe I should have some gruesome \trope{BodyHorror}{Body Horror} scenes with this primordial slime or blood. 





\subsubsection{\Xzaishanns{} left behind ruins}
\target{XS ruins}
The \xss{} left behind some ruins and stuff from the age when they ruled \Miith{}. 

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  I built temples, statues and pyramids \\
  as monuments of my endless might.\\
  Colossal knowledge lays hidden in tablets and shrines, \\
  protected by spells and incantations.
}





\subsection{Poetic version}
\subsubsection{The \voyagers{} and the \krakens}
Once there were the \voyagers, a race of mighty beings (gods, if one wills) who travelled across the Universe, seeding worlds they found with life. In primordial time, billions of years ago, they came to \Miith{}, desiring to make the world theirs, a breeding ground for their creations. 

But \Miith{} was not barren. Before the \voyagers{} came, \Miith{} had her own children, her own indigenous life, and the greatest of them were the \krakens, the native overlords of \Miith{}. Terrible creatures they were, and immortal. And they were jealous and cared not for invaders, but craved \Miith{} as their birthright, and when the \voyagers{} sought to conquer their world, they fought. Few were the \krakens{}, numbering scarcely a dozen against the thousands of \voyagers{}, great and mighty in their own right. Yet in their wrath, the \krakens{} proved more than a match for the invaders, and in every conflict they would prevail. With valour and fury the \voyagers{} would fight, and with despair, for the \krakens{} were immortal and wielded the primal power of \Miith{} herself. Their leader and mother, the great \Kraken{} Queen, was the mightiest of all the children of \Miith{}, and none could stand before her when she rose in fury. 

But the \krakens{} were indolent, and they would often sleep, their entire race, for aeons at a time - millions, even hundreds of millions of years. And so, whenever the \krakens{} slept, the \voyagers{} would invade \Miith{}, to populate the planet with myriad life forms of their devise. And every time, after an aeon, the \krakens{} would awake to vanquish the \voyagers{}, scour the world of their creatures and repopulate it with their own spawn. But inevitably, the \krakens{} would once more go dormant, and the \voyagers{} would return to begin their work anew. 

For the \voyagers{} seek ever to perfect life, and \Miith{} is precious to them, for \Miith{} is an anvil on which to forge and shape their creations, their works of art. And a most excellent anvil is Mother \Miith{}, for it is her nature to take what is given to her and break it down and hammer it into a new shape, greater and mightier than before. The \voyagers{} have travelled the universe for billions of years, and they have known many planets. Many worlds are hostile, wastelands of death that will destroy life and cause it to decline and decay. Other worlds are indifferent, possessed of no powerful energy, positive or negative. They will allow life to exist, but they will not support it. On such worlds, life will persist, but it will stagnate and remain humble and never know greatness. Not so Mother \Miith{}. She is possessed of a soul, and she is strong and fierce and indomitable. A loving mother is \Miith{}, but also cruel. The weak among her children she will destroy, and they shall have no legacy and know only oblivion. But the strong among her children she will cherish and glorify. Forged in fire and tempered in blood they shall rise, growing ever stronger, and they shall know greatness. For \Miith{} is a crucible of life, and her like is seldom found in the universe, and the \voyagers{} knew to cherish her. 





\subsubsection{\Moroch{} and the \nagae}
So the history of \Miith{} is divided into such cycles of creation and destruction in the cosmic struggle between these factions, the native \krakens{} and the alien \voyagers{}. 

Our story begins in one such cycle. The \voyagers{} had filled \Miith{} up with their creations, but they were fled, for the stars moved, and they knew that the \krakens{} would soon awaken. And one of the \krakens{} did awaken; in this day and age he is called \Moroch{}. What is his aim we cannot know, but when he awoke he began not to destroy, but to create. From the sea he took primitive beings, creatures of the \voyagers{}, and reshaped them in his own design. He gave them strength of body and mind, and bestowed upon them the power of thought, and he made them his servitors. 

The years passed, a million years and more, and still the \Kraken{} Queen and her brethren slumbered, and even \Moroch{} grew sleepy and fell dormant. But his spawn lived, and they grew and prospered, and they recalled their sire and offered him prayer and tribute. Hybrid children they were, born from the womb of the \psp{\voyagers} creation but fathered by a \kraken{} lord. Lowly they were, yet in this age they were the lords of \Miith{}, and their built their cities in the deep oceans across the globe, and they were the \nagae{}. 















\section{The \Ophidian{} Civilization}
\target{Ophidian humanoids}
Hundreds of millions of years after the \voyagers{} had left \Miith{}, the \ophidians{} evolved. 
They were snake-like humanoids, not much bigger than \humans{} or \scathae. 









\subsection{Evolution}
The \ophidians{} \hr{Ophidians evolved}{evolved from reptiles} who were making the transition from \quo{cold-blooded} to \quo{warm-blooded}. 

They evolved intelligence and telepathic abilities. 









\subsection{Origin of the \nagae}
In the very early beginning, the \ophidians{} and \nagae{} were one species. 
But eventually they grew apart. 

The \ophidians{} were reptiles, descended from amphibians who in turn had evolved from fish. 
One branch of the proto-\ophidians{} took to the sea. 
The ones who returned to the sea eventually degenerated into atavistic, fish-like forms. 
They came to resemble eels more than snakes. 
The sea-dwelling ones took up the worship of the \Krakens{} and became the \nagae{}.  

They thrived, and even survived the coming \firstbanewar{} relatively unscathed. 
But they stayed in the seas, and their technology remained comparatively low. 









\subsection{Early culture}
\target{Early Ophidian culture}
They developed culture and civilization early on, many millions of years before \Tiamat. 
But they had the infinite patience of reptiles, so they lived very slowly, and hence their culture also developed extremely slowly. 
Also, they were not very social creatures to begin with, with made things even slower. 

This also meant that they did not fuck up the ecosystem around them. 
Every new invention for the \ophidians{} might take many thousands of years, giving surrounding species time to adapt and not just be wiped away. 

The \ophidians{} were physically and metally powerful, so they did not develop tools at first. 
On the contrary, their comfortable and slow lives gave them plenty of time to lie around and think. 
With their telepathy they could lie and think and at the same time communicate with their brethren across great distances. 
So they developed philosophy and science. 

They had the natural ability to control their own metabolism. 
From their they gradually learned all sorts of other mental body control (psychometabolism). 
They developed psionics. 
Eventually they also delved into sorcery. 

The \ophidians{} learned to utilize their \hs{torpor}. 
From this they would eventually discover the secret of immortality. 

% Slowly (over millions of years) they developed science and technology. 










\subsection{Great civilization}
\target{Ophidian golden age}
\target{Ophidian civilization}
\target{Ophidians and Nagae were one species}
\index{technology!\ophidian}
The \ophidians{} built a civilization which was great, mighty, proud, enlightened and technologically advanced. 
Albeit perhaps cruel. 

Back then the \ophidians{} were so powerful as to almost rival the \voyagers, or even the \xss. 
Certainly as powerful as, say, Elder Things or the Great Race from the Cthulhu Mythos. 

This was millions of years ago, before they waged a giga-war that destroyed the \ophidian{} humanoids and left their culture in darkness. 
Their civilization lasted for millions of years. 
The \ophidians{} lived very slowly, due in part to their \hs{torpor}. 

Or perhaps they lived all the way up to the \firstbanewar{} and the forging of the \hr{Crystal Sphere}{\CrystalSphere}. 



\lyricsbalsagoth{Invocations Beyond the Outer-World Night}{
  ... and their star-spanning progenitors, \\
  spawned beyond the outer-world night.
}



\lyricstitle{\emph{Call of Cthulhu} RPG p.118}{
  [The Serpent People] built black basalt cities and fought wars, all in the Permian aera or before. 
  They were great sorcerers and scientists, and devoted much energy to calling forth dreadful \daemons{} and brewing potent poisons.
}





\subsubsection{Association with snakes}
Despite the name, and despite looking somewhat like snakes with legs, the \ophidians{} were not snakes, nor even closely related to snakes. 
But their culture idolized snakes. 
Snakes were seen as epitomizing virtues of patience, stealth and contemplative wisdom. 

Compare to how \humans{} in RL idolize lions for courage and owls for wisdom, even though this may be unfounded superstition. 

At any rate, snakes played a large role in \ophidian{} culture, and much of their aesthetics was patterned after a serpentine motif. 
Hence they conveyed a snake-like impression to other creatures, and hence the name \quo{\ophidian} survived. 
(They had other names for themselves, of course.)





\subsubsection{Breeding work}
\target{Ophidians breed}
They had several entire races as their servants and slaves. 
And they controlled \daemons{}, whom they commanded to build their great cities. 

They learned bio-technology and biomancy. 
They started manipulating other races, breeding and tweaking them. 
They created their own servitor races and animals. 

That was the reason why, later on, there existed so many animal species on \Miith{} that could be domesticated: 
The \ophidians{} had been breeding them, millions of years before. 

Among other things, they helped shape the \hr{Nephil}{\nephilim} and \hr{Nycan}{\nycans}. 

Perhaps they created shoggoth-like monsters (the \bladedpeople?) who rebelled against them?





\subsubsection{Telepathy and speech}
\target{Ophidian telepathy}
Originally the \ophidians{} communicated using telepathy. 
This was how they evolved. 
They used sound and their voices only for artistic purposes, not for regular communication. 

\target{Ophidians discover spellwords}
But at some point, \ophidian{} sorcerers (\hs{Sethicus}?) discovered a system of spellwords that used the voice to work sorcery. 
(This would later evolve into the \hr{True Draconic}{True \Draconic} tongue.) 
With this discovery, speech suddenly became more valuable. 
The \ophidians{} began to develop a spoken language. 





\subsubsection{\Ophidian{} philosophy}
The old \ophidians{} were \hr{Ophidian philosophy}{atheistic and rational}. 















\section{The \FirstBanewar}
\subsection{Origin of the \banes}
\target{Banes are created}
Meanwhile, the \hr{Banes}{\banes} were created on the planet \hr{Erebos}{\Erebos} by the \hr{Voyager}{\voyagers}. 
After being thwarted by the \krakens{}, the \voyagers{} left \Miith{} to attempt to create their perfect creatures elsewhere. 

They found \Erebos{}, a thoroughly hostile and cruel world, and decided to do their experimentation here. Surely a creature strong enough to survive here was a good candidate for their \quo{perfect} race. 

\target{Banes destroy Voyagers}
But the \banes{} became twisted and destructive, and they turned against their creators, ultimately destroying the \voyagers. 

Then they waged wars of genocide and eradicated several entire \hr{Erebos}{races that existed on \Erebos}, and perhaps other worlds. They won in the end by being the coldest, most ruthless and most efficient, almost machine-like. 

They have cruelly exploited their homeworld until \Erebos{} is now a dying husk, almost all its life energy drained away. The \banes{} know that they cannot evolve further while still tied to \Erebos\dash indeed, \Erebos{} and the \banes{} it are doomed to decay and extinction. So the \banes{} are searching for a new planet to leech from, so that they may survive and grow in power. (See also section \ref{Fighting for survival}.)





\subsubsection{Created by a cosmic god or force}
\target{Cosmic god creating the Banes}
\target{Cosmic god creates Banes}
\target{Evil Cosmic God creates Banes}
Perhaps the \banes{} were twisted by some wicked \hr{Cosmic gods}{cosmic god}, who, out of spite against the \voyagers, desired to destroy the \psp{\voyagers} civilization and corrupt their beloved children, in whom the \voyagers{} had invested all of their love and creativity, into a nightmarish scourge to ravage the universe, destroying all in their path and leaving only Entropy behind. 

\target{Evil force corrupts the Banes}
Or... perhaps it wasn't the conscious actions of an actual god, but rather the influence of an impersonal cosmic force of corruption, entropy and parasitism. 
A force of betrayal, of devouring one's own creator or parent. 

As such, the \banes{} are a physical manifestation of a cosmic force of destruction. 

The latter is a more evil vision, since you can't just place the blame on an evil god. 
Rather, it is the entire universe itself which is inherently evil and destructive. 

But this force might still be named and referred to as a god. 
It just needs to be revealed at some point that it is really an inherent, impersonal aspect of the universe.

\target{Banes as an antibody}
In this vision, the \banekings{} are physical manifestations of this force of Entropy, leading their people on a crusade against Creation, as a cosmic disease... or cosmic antibodies, fighting against the infestatation that is life.

Compare them to the Zerg Overmind from the game \cite{VideoGame:Starcraft}. 

\lyricsbalsagoth{The Sixth Adulation of His Chthonic Majesty}{
  I now know that there is something inestimably evil at large throughout the cosmos.\\
  It is a ravenous and pitiless storm which rages across the universe, permeating the very fabric of creation, existing simultaneously in all dimensions, wholly unconstrained by linear time.\\
  This force is the black, quasi-sentient mana which sustains such ageless revenants of the Z'xulth as the dread Dwellers in Eternal Shadow and the unspeakable They-Who-Lurk-And-Breed-In-Limbo.\\
  When beings whose essences are intrinsically malefic choose to embrace this darksome energy source, the resultant sinister symbiosis can be sublimely diabolical, as evidenced by the black blight that was the infamous pseudo-human sorcerer Lord Angsaar!
}









\subsection{The \bane{} invasion}
\target{Banes come to Miith}
\target{First Banewar}
\target{FBW}
\target{Banes come to Miith in spaceships}
\index{\firstbanewar}
And so it came to be that a \baneking{} (whom the \dragons{} would later came to call the \quo{\Voidbringer}) succeeded in opening a great dimensional portal from \Erebos{} to \Miith{}. 
Through it he sent forth millions of his \bane{} warriors to conquer and claim the new world in his name. 

The \banes{} came to \Miith{} flying in vast spaceships. They \hr{Why the Banes want Miith}{had their reasons for wanting \Miith}. 
They had flown all the way from \Erebos{}, a journey of hundreds or thousands of years. 

The people of \Miith{} were taken unaware when, on the Eve of the Black Gate, a massive rent opened in the sky and myriads of fiendish \bane{} warriors surged forth to conquer and destroy. 
Millions of \bane{} warriors and beasts, and hundreds of \banelords, all led by Daggerrain himself, invaded and attacked the \draconic{} kingdoms. 
Many millions perished in the initial assault and whole continents were laid waste before the \ophidians{} were able to muster their forces in defense. 
The Eve of the Black Gate marked the beginning of the \Banewar, the most terrible and devastating war that \Miith{} has seen since the \Kraken{} Queen last returned to her sleep. 

\index{technology!\bane}
The \banes{} fought against the \ophidians{} in what became known as the \firstbanewar. 
They invaded with millions of \bane{} warriors and terrible magic. 
An important edge they had over the \Miithian{}s was their \hr{Bane technology}{higher technology}.









\subsection{Sethicus}
\hs{Sethicus} was one of the leaders of the \ophidians{} during the war. 
He was controversial because he used \xs{}-based sorcery (\hr{Ophidians and XS}{which the \ophidian{} establishment frowned upon}), but now the other \ophidians{} realized they would need every weapon at their disposal to defeat the \bane{} invaders. 

During the war, Sethicus-tachi unleashed more \daemons{} and more \xzaishannic{} power than ever before. This nearly tore the planet apart, and might even have killed the Heart itself. 

Perhaps the \banes{} feared that. The \banes{} might be more keenly aware of the Heart of \Miith{}, since their entire quest revolves around it. The \ophidians, on the other hand, had dwelt on \Miith{} for millions of years, and the Heart has always been there, so they might not have paid much attention to the peril their magic posed. 

\lyricstitle{\SETolltheHounds{} p.107}{
  ... in the north sky something terrible was happening. 
  Lurid slashes like a rainbow gone mad, spreading in waves that devoured darkness. 
  Was it pain that strangled the very air? 
  Was it something else burgeoning to life, shattering the universe itself?
  
  ... he could see the city, the roofs like the gears of countless mechanisms, gears that could lock with the sky itself, with all creations. 
  Such was Kharkanas, First Born of all citites. 
  But the sky had cyhanged. 
  The perfect machine of existence was broken\dash\emph{see the sky!}
  
  The city trembles, the roofs now ragged-edged.
  A wind had begun to howl, the voice of the multihued light-storm as it lashed out, flared with thunderous fire. 
}

Maybe move some or all of \ps{\Kserasshana} \quo{awakening} to Sethicus. 









\subsection{\Dragons{} are created}
The \ophidians{} realized that their bodies were not strong enough for this war. 
So, using their advanced gene-technology and psychometabolism and Sethicus's \xsic{} sorcery, they designed a race of \ophidian{} super-warriors. 
A number of \ophidian{} warriors volunteered to be transformed into these new superbeings. 

To create these creatures, the \ophidians{} took inspiration (and at times actual genes) from various fierce creatures, including \nycans, \corgoroth{} and \vreiiden{} (many of which had themselves originally been designed and shaped by \ophidians). 
And they infused them with all the \xsic{} ferocity they could conjure up. 

When the experiments where at last successful, the result was huge, flying monsters: 
\Dragons. 
They did not yet possess the full \xsic{} sorcerous power of the \dzraicchenosses. 
It was only later they \hr{Dragons unlock XS potential}{learned to channel the true \xsic{} power inside them}.
Still, they were formidable warriors. 

Sethicus oversaw their creation, but he did not undergo the metamorphosis himself. 

As it turned out, the \dragons{} were able to breed true as a race unto themselves. 





\subsubsection{\Cregorrs{} are created}
\target{Origin of Cregorr}
The \dragons{} were full-fledged \ophidians, altered for war. 
But the \ophidians{} also wanted servitor warriors. 
So at approximately the same time they worked to create a race of warrior servants. 
This became the \cregorrs.  









\subsection{The \CrystalSphere}
\target{Crystal Sphere}
\index{\CrystalSphere}
The \ophidians{} received help and knowledge from the \xss{}. 
Using this magic they were able to forge a mystic seal between the worlds, severing the connection to \Erebos{} and preventing the \banes{} from drawing power from their homeworld and its \dweomer. 

Sethicus-tachi built a vast \CrystalSphere, a cosmic shell of \quo{ice} encasing all of Mith and its Heart. 
Thus they captured the \banelords, who were caught and frozen in the ice. 

The \CrystalSphere{} was a whole mini-Realm of ice in its own right. 
The \banelords{} became trapped there. 

With the \banesz{} leaders and power source gone, they were weak, and the remaining legions of \bane{} warriors were easily slaughtered. 

Maybe this seal works as a huge-ass cosmic \hr{Storm beacon}{storm beacon}. 

The \xs{} \hr{Naath-Kur-Ramalech}{\NaathKurRamalech} was very important in building the \CrystalSphere. 

\Daggerrain{} would later draw on the \CrystalSphere{} to weave the \hr{Shroud of Girigor}{Shroud of \Girigor}. 
So \hr{Shroud and Crystal Sphere}{the Shroud is tied to the ice}. 

Compare to the devils in the manga \cite{NagaiGo:Devilman}, who are also frozen in ice. 





\subsubsection{No spaceships}
\target{Crystal Sphere isolates Miith}
One might think that even though the \CrystalSphere{} prevented the \banelords{} from going to \Miith{} by dimensional means, they should be able to fly there in spaceships. 

But no. 
The \CrystalSphere{} also kept spaceships out. 
It acted like a huge-ass \hs{storm beacon}. 
In fact, the sorcery wrought through \NaathKurRamalech{} completely enclosed \Miith{} and made it inaccessible from the outside. 
It constricted and strangled \Miith{}. 
It was one of the causes of the \hr{Heart weakened}{weakening of the Heart}. 
The Shroud made it worse, of course. 

It would be possible to attack the Sphere from the outside with magical weapons. 
But that would be very risky. 
Such an attack might easily damage or even destroy the Heart of \Miith. 
No, the Sphere had to be unravelled from the inside. 
















\section{The Fall of the \Ophidians}
\target{Fall of the Ophidians}
\index{technology!\ophidian}
Even though the \ophidians{} were victorious in the \firstbanewar{}, it  heralded the downfall of their civilization. 

The war and the destructive forces (magical and non-magical) unleashed by both sides caused not one but multiple ecological catastrophes. 
This cataclysm heralded a mass extinction wiping out a ton of species. 

\target{Ophidians lose telepathy}
It struck the \ophidians{} themselves hard. 
A backlash by the \banelords{} bathed the planet in destructive radiation. 
This radiation was bad enough for regular animal and plant life, but it was worst for the \ophidians, who were highly telepathically sensitive. 
The radiation attacked their highly-developed minds and resulted in permanent and debilitating brain damage. 
They suffered from amnesia and insanity\dash apathy or irrational aggression. 
The brain damage also harmed their intelligence and burned out much of their telepathic and psionic abilities. 

Only a few survived. 
And with the loss of telepathy, their civilization quickly broke down, for all their technology was built to be operated telepathically. 
The vast majority of \ophidians{} died in the war and its long aftermath. 
With their newfound insanity they used what was left of their science and magic to wage war on each other, until their race was all but extinct. 

The \ophidians{} (not counting \dragons) became divided into two groups. 
One group developed hyper-aggression, the other group developed hyper-apathy. 
In time, all the hyper-aggressive ones killed each other and died out, leaving only the apathetic ones. 
The latter evolved into \quiljaaran. 
They had not the will nor energy to maintain or rebuild their civilization, so it continued to decline. 
The \ophidian{} culture fell into barbarism, a process that took over a thousand years. 













\section{New World Order}
The survivors had forgotten much of their old culture.
They had no technology and barely any magic. 
They had only legends. 

The technology used to be very high, but after the war they forgot their civilization and science, and how to control their slave races and \daemons. 
Compare to the Azghouls from the RPG \emph{Kult}, who were once the slaves of \humans. 

Two branches of \ophidians{} survived: 

\begin{enumerate}
  \item 
    The genetically enhanced super-warriors, who became \dragons.
    
    The \quiljaaran{} saw them as freaks and did not trust them. 
    They, in turn, saw the \quiljaaran{} as inferior weaklings and cowards. 
    So they fought rather than working together. 
    
    The \dragons{} were strong, but few in number. 
    So they did not rise to dominate the world... yet. 
  \item 
    Some regular \ophidian{} civilians, who eventually became \quiljaaran. 
\end{enumerate}









\subsection{\QuilJaaran}
The \quiljaaran{} kept on dwelling in the desolate and crumbling \ophidian{} cities. 
Each \quiljaar{} was usually able to keep a few dozen servants or slaves (mostly \loculs, sometimes \cregorrs{} and \nephilim). 
But this still meant that they ended up with dozens to hundreds of people living in \hr{Ophidian architecture}{Cyclopean} ruined cities that were built to house tens of thousands if not millions. 

The \nephilim{} were less friendly towards their \quiljaaran{} masters than the reptillian races. 
They would often run away or commit mutiny. 
Few \nephilim{} wanted to live near a \quiljaar. 









\subsection{\Cregorr{} barbarians}
\target{Cregorr did not dominate}
The \cregorrs{} \hr{Origin of Cregorr}{had been created at this point}. 
After the \firstbanewar{} and the collapse of the \ophidian{} civilization, the \cregorrs{} escaped into the \wylde. 

But they did not become a dominant race. 
They were \emph{too} aggressive and disorganized. 
They failed to develop much civilization on their own. 
They remained barbarians. 

Some \cregorrs{} ended up serving the \quiljaaran. 
But not so many. 
The \quiljaaran{} did not like the warlike \cregorrs. 
They made them feel uncomfortable. 

Many \cregorrs{} \hr{Cregorr worship XS}{worshipped the \xss}.









\subsection{Millennia pass}
Many thousands of years passed from the \firstbanewar{} to the rise of the \aryothim. 
\Dragons and \quiljaaran{} were immortal, so \quo{many tens of thousands of years} was only a few generations for them. 
Many were alive whose grandparents or even parents had lived during the \banewar. 
Also, they had long memories, which was one reason why it took their civilization so long to decline. 

But decline it did.
The \quiljaaran{} were too apathetic to rebuild their empire, and the \dragons were not much better.
It was not until they became \dzraicchenosses{} that the \dragons (as a people) finally lost their apathy and regained their zest for life and their lust for combat, adventure and power. 
The \quiljaaran{} had a lust for knowledge and philosophy, but \hr{QJ not inventive}{they were not inventive}. 
















\section[The Aryoth Invasion]{The \Aryoth{} Invasion}
\target{Aryothim kill QJ}
The \aryothim{} showed up. 





\subsection{Origin}
\target{Aryothim enslaved by sorcery}
The \aryothim{} might have been artifically created, possibly by \ophidians{} who wanted to transform those silly \nephilim{} into more useful servants, for use in their internal wars. 
It backfired, and the \aryothim{} destroyed their masters.

In the process, \hr{Aryothim hate sorcery}{the \aryothim{} developed a hatred of sorcery}, which was what their makers had used to enslave them and mistreat so many of their people. 

It might also not have been \dragons. 
It might have been \hr{Voyager}{\voyagers}. 
After all, a few \voyagers survived on \Miith{}. 









\subsection{Rampage}
They hated the \quo{loathsome serpent men}. 
So they waged war against the \quiljaaran{} and their servitors and slaughtered many. 
They invaded the \quiljaaran{} cities, killed the \quiljaaran{} and their servitors and laid waste to the cities. 

Later the \aryothim{} would invent legends of how they had fought a valiant crusade to rid the world of the wicked reptillian menace. 
The \quiljaaran, on the other hand, considered themselves the victims of murder and vandalism at the hands of bloodthirsty barbarians. 

\target{Nephilim kill Locul}
The \loculs{} were especially hard hit. 
They were \hr{Locul weak}{weak and fearful fighters}, so they died in the droves at the hands of the rampaging racist \nephilim. 
Moreover, they were \hr{Locul friendly}{friendly and trusting}, which made it even easier for the ungrateful \nephilim{} to betray, enslave and kill them. 

To the \nephilim, the \loculs{} were loathsome reptillian creeps, but \hr{QJ miss Locul}{the \quiljaaran{} missed them when they were gone}. 

Compare to the way the Mabden kill off the Vadhagh and Nhadragh in \cite{MichaelMoorcock:Corum}. 
And the way barbarians slaughter the \quo{Peaceful Ones} in \cite{TadWilliams:MemorySorrowandThorn}. 









\subsection[Aryoth seamanship]{\Aryoth{} seamanship}
\target{Aryoth seamanship}
\target{QJ seamanship}
One advantage the \aryothim{} had over the \quiljaaran{} was that they were great sailors. 

The \quiljaaran{} had a taboo against challenging their long-lost kin the \nagae{}, who had long held dominion over the seas by default. 
So the \quiljaaran{} kept to the land, even though with their technology they could have made themselves a sea power had they tried. 
\hr{QJ apathy}{\QuilJaaran{} were ever apathetic}. 

The \aryothim{} had no such scruples, so they sailed out and explored. 
They quickly gained built great sea-spanning empires. 
The \nagae{} resented this and opposed the \aryothim. 
\Naga-\aryoth{} wars were fought. 
The \aryothim{} suffered losses in these wars, but these losses were outweighed by the gains of seafaring. 

The \aryothim{} gained naval superiority, which remained unbroken until the \dzraicchenosses{} came and kicked their asses. 









\subsection{Conquest}
The \aryothim conquered the world and dominated much of it for thousands of years.
At first they were stone-age barbarians.
Over the millennia they developed a high-tech civilization.

The \aryoth civilization ended up \hr{Aryothim hate sorcery}{steering clear of alienist sorcery} and focusing on \hr{Aryoth magic}{psionics/animism} and \hr{Aryoth inventors}{natural science}. 

They reached a 20th century level of technology.















\section{\Saphyrae}
\target{Saphyrae}
\index{\Saphyrae}
\Saphyrae{} was the greatest and mightiest \quiljaaran{} empire ever. 
It rose after the \firstbanewar. 
The \Saphyraeans{} considered themselves the heirs of the \ophidian{} empire, which was \trope{ShroudedInMyth}{Shrouded in Myth} and legend already back then. 

\Saphyrae{} was the only \quiljaaran{} empire which the \aryothim{} could never really threaten. 
Although that did not stop them from trying. 
The \aryothim{} waged many wars against \Saphyrae, but they never achieved much. 

But though \Saphyrae{} held its ground, they did not expand. 
The \quiljaaran{} were already then a people in decline. 
One reason was that they were apathetic, \hr{QJ apathy}{as \quiljaaran{} were ever wont to be}. 

\Saphyrae{} only fell when the \dzraicchenosses{} conquered the world. 
For that reason, the time between the \firstbanewar{} and the Draconian Supremacy is sometimes called the \Saphyraean{} Age. 













\section{Draconian Ascendancy}
\target{Draconian Ascendancy}
The \quo{Draconian Ascendancy} was the event when the \dzraicchenosses{} conquered \Miith. 
It heralded the beginning of the Age of Draconian Supremacy. 









\subsection{The rise of the \draecchonosh}
\target{Origin of Dragons}
% Some thousands of years after the cataclysmic war between the \ophidians{} and the \hr{XS}{\xzaishann}, some \ophidian{} lords came to crave more power. 
Millions of years passed. 
Then \Tiamat{} was born. 





\subsubsection{The \ophidians{} were pressed}
\Tiamat{} saw the \dragons{} as a \quo{fallen} people, after millions of decline from the golden age of the \hr{Ophidian civilization}{\ophidian{} civilization}. 

\target{The struggle for Dominion over Miith}
The \ophidians had been displaced as the Dominators of \Miith{}.%
\footnote{%
  Perhaps this is what the title of the series should refer to: 
  The struggle for Dominion over \Miith{}.%
} 
The \dragons{} and \quiljaaran were retreating before the advance of the \aryothim.
They lived in half-empty ruined cities\dash a painful testament to the heights from which they had fallen, the greatness which they had lost. 
They were being pushed back hard. 
Some even feared their races would become extinct. 

\Tyarith felt the \quiljaaran were doing nothing to prevent it, so the task must fall to her people. 
\Tiamat{} wanted to resurrect the \ophidian golden age. 

Compare to \bandsong{Demilich}{The Planet that once used to Absorb Flesh in order to Achieve Divinity and Immortality (Suffocated to the Flesh that it Desired)}. 






\subsubsection{Inspired by the \cregorrs}
\Kserasshana-tachi noticed the \cregorr{} cults that were \hr{Cregorr worship XS}{worshipping the \xss}. 
This gave \Kserasshana{} an idea.
It inspired her further work. 






\subsubsection{Discovering the \xss}
\target{Tiamat maps the way to Machai}
\target{Star-Maps of the Ancient Cosmographers}
Their leader was \Tiamat. 
Her chief accomplice was her lover \ApepNesthra. 
They discovered the \xss{} from the \hr{XS ruins}{ancient ruins they left behind}. 
Together they charted the cosmic paths leading to \Machai, the \xzaishannic{} homeworld that had been lost after the fall of the \ophidians. 
(These are some of the same paths that Chaos sorcerers use today.)

She and \ApepNesthra{} explore the cosmos, looking for illumination and arcane knowledge. 

\lyricslimbonicart{Dynasty of Death}{
  I'm launching into the abysmal universe.\\
  Disembodied I enter the cosmic cataclysm.
  
  I discover stairways to celestial dreamscapes\\
  A dark unknown conjunction within an immoral dimension.
  
  Through dark tunnels in levitation, \\
  black cosmic space in manifestation.\\
  I escape the earthly pandemonium\\
  into a vast nocturnal sanctum.\\
  A nemesis for all evil I confess.\\
  My soul bleeds by all the forces I possess\\
  A benediction of unholy wrath and sorrow.\\
  My heart is buried in dark catacombs of horror.
}

They learn learn the grim truths and secrets of the universe. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  They
  were the words of a great thaumaturgist who had seemingly discovered a
  repository of aeons-old lore detailing the sidereal web of the cosmos, with
  arcane diagrams pinpointing certain astral portals and places of empyreal
  potency, a sort of pangalactic ley-line chart, if you will. 

  [The Thaumaturgist:]\\
  The Great Eye of the Universe opens! \\
  Through this astral art the secrets of the cosmos are mine to know... \\
  for the stars are my dominion!
}

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Everything you have been taugh about the nature of Creation is a lie. \\
  This is a voyage in search of the truth. \\
  It will not be a pleasant journey.
  
  I have discovered a terrifying universal axiom which cannot be denied.
}

They learn of the origin of their people, and all life.

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Betwixt the hammer and the anvil are forged the stars... \\
  On the wings of the ersatz ones... \\
  through the fathomless abyss.
}

They feared this discovery, and the madness that the \xss{} might bring. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Like a blackened and baleful sun shall I gaze down \\
  from beyond the cumuli and the firmament upon you. \\
  I alone must bear the burden of this fiend-wrested lore.
  
  New stars without number burn in the heavens, \\
  but the shadow of oblivion falls ever closer.
}

She discovers a wealth of cosmic knowledge, comparable to the Sith library in the game \emph{Knights of the Old Republic II: The Sith Lords}. Also comparable to the tale of the Empyreal Lexicon by Bal-Sagoth. 

\lyricsbalsagoth{Return to Hatheg-Kla}{
  Some would call it epiphany, others would deem it the final descent into madness... whatever the case, the last vestiges of those tenuous palisades which had previously, and blessedly, safeguarded my reason and prevented my mind from accepting the full and staggering magnitude of the naked truth then crumbled, fading into nothingness like the dissolution of a night-mist.\\
  At length, one oppressively miasmic night, with such malefically portentous lore preying pitilessly upon my sanity, I began to descend through a myriad veils of sombre and swirling shades, finally surrendering my grip on wakefulness.\\
  And on that fitful, fateful eve, the last of the dreams came...\\
  A waking dream?\\
  I dare not speculate.}





\subsubsection{The keys to insight}
In order to summon the \xss{} and invoke their power, \Tiamat-tachi discover that they must find a number of \quo{keys}. 
After a while of searching they finally realize that the \quo{keys} are not physical objects but insights. 

They are told that some of the keys must be captured from their rival races. 
They only manage to do this when they realize that what they are supposed to steal/conquer is knowledge, not artifacts. 

\lyricsbalsagoth{Return to Hatheg-Kla}{
  A terrible sound filled my ears... \\
  an insidious resonance which sent waves of excruciating pain coursing through my mind... \\
  a sound which inexorably coalesced into a recognizable but entirely inhuman voice, a voice which slowly, inevitably, formed approximations of words which I could discern...
  
  [The Crystalline Oracle:]\\
  Hearken, o' manling of the Tellurian orb... the Circle closes.\\
  Perpare to embrace the agony of enlightenment.\\
  Know you of the Six Cataclysms?
  
  [The Aspirant:]\\
  I do. Six times has the world perished and been reborn!
  
  [The Crystalline Oracle:]\\
  You have discovered the true meaning of the six coruscating rings of arcane power?
  
  [The Aspirant:]\\
  Praise Klatrymadon and Zuranthus! The Six Keys!
  
  [The Crystalline Oracle:]\\
  Know you of the blackened orb which burned bright o'er ancient Lemuria?\\
  Know you of the sidereal flame which engulfed the high seat of power in Ultima Thule?\\
  Know you of that martial sorcery woven in the pitiless throng of epic battle?\\
  Know you of the astral power permeating the multiverse and the might of the cosmic codex?\\
  Know you of the rise and fall of glorious Atlantis?\\
  Know you the blasphemies contained within the Chthonic Chronicles?
  
  [The Aspirant:]\\
  I know all this, and more!
  
  [The Crystalline Oracle:]\\
  Have you, o' hybrid child of the cosmos, gazed into the Great Eye of the Universe?
  
  [The Aspirant:]\\
  I have.
  
  [The Crystalline Oracle:]\\
  And what did you see there, young Xerxes?
  
  [The Aspirant:]\\
  I saw oblivion and damnation.\\
  I saw truth, and enlightenment.\\
  I saw the closure of the Great Circle Without End.\\
  I saw the Sixth Great Cataclysm.\\
  I saw the alpha and the omega, \\
  I saw the beginning... and I saw the end.\\
  The end of all there is!
}





\subsubsection{Summoning the \xzaishanns}
\target{Origin of Draecchonosh}
\target{Tiamat contacts XS}
\Tiamat, together with her accomplices, contacted the lords of the \xzaishanns{} and learn to channel their power. 
They even absorbed some of the \ps{\xzaishanns} souls into themselves, transforming themselves into the mighty \draecchonosh. 

Have a scene where \Tiamat{} and \ApepN{} summons the \xzaishannic{} power, similar to \bandsong{Bal-Sagoth}{Summoning the Guardians of the Astral Gate.}

\lyricsbs{Hate Eternal}{Catacombs}{
  Rise up from the ancient tombs. \\
  Grant us all your infinite wisdom. \\
  Endure as you rise from the catacombs. 
}

\lyricsbs{Hate Eternal}{The Creed of Chaotic Divinity}{
  Awakened by this ancient creed. \\
  Evoked, the ancestry of thee.\\
  Forsaken for centuries of times. \\
  Exiled, all of their kind. \\
  Foretold, the inheriting of the Earth.\\
  Forewarned of this predestined rebirth. \\
  Engaged, the rising from below.\\
  Fear, all mortals, for what they shall bestow.
  
  Conjure all, so that they may sustain\\
  their race, of what they must retain.\\
  Spew forth incantations in vain. \\
  Invocate all that they try to negate.\\
  Enchant all of their wonderful splendour. \\
  Recant all of the texts that are sacred. \\
  Recreate all that has been begotten. \\
  Revive all that has been forgotten. 
}

\lyricsbalsagoth{The Empyreal Lexicon}{
  The key word of Transcendence!\\
  The key word of Transference!\\
  I shall liberate the rightful owners of the Lexicon...\\
  the true rulers of the cosmos!
  
  X'atham-ry'aa! Tha'zai-tonn!\\
  Darker than a score of hells... \\
  wherein astral horrors sublime dwell,\\
  Macrocosmic realms aflame... \\
  Prey of fiends that have no name!\\
  Bow to the gods that have no name!}

The \xss{} are powers of evil whom the \ophidians{} used to fear. 

\lyricsbs{Vital Remains}{Icons of Evil}{
  Confront me now, defiler of human desire.\\
  Voracious hordes await the hour of ascension.\\
  Unravel their delusion,\\
  their translucent divinity.
}

When \Tiamat-tachi first invoke the \xzaishannic{} power, it goes wrong and the \xzaishanns{} wreak immense destruction. It takes some time for \Tiamat-tachi to learn to control and channel their power. 

\lyricsbalsagoth{The Voyagers Beneath the Mare Imbrium}{
  Fools! The Darklight Portal has grown strong.\\
  Only one moon remains in orbit.\\
  The mewling ape-spawned humans have discovered the icosahedron and the Lexicon's call can once again be heard throughout the stars, beckoning my ireful brethren to return to the slaughterous embrace of the fray!\\
  We have won! The orb azure is ours... ours to enslave!}





\subsubsection{The guide appears}
A guiding god appears to \Tiamat-tachi: 
A \xs{} or a \hs{cosmic god}. 
He gifts them with knowledge and makes them worship the \xss{} and \Chaos. 
Compare him to Nyarlathotep from \HPLovecraft's stories. 

\lyricsbalsagoth{The Chronicle of Shadows}{
  [The Imperator of the Night \\
  (Hearken to the Attestation of the Sinistrous):]\\
  For it is the iniquity of man which compels him to these tenebrous gates,\\
  seeking opiate dreams and the alluring embrace of oblivion...
  
  Such adoration bestowed upon me beneath the cryptic moon!
  
  (Behold the true purity of that which lurks concealed beneath the mantle of 
  shadow, and let the deluded, debauched sybarites flee in terror from that 
  darkness which they profess to embrace!) 
  
  Beyond the spheres of light and darkness, \\
  beneath distant pallid stars, \\
  I bring the iridescent glimmer of forbidden truth, \\
  seared in the crucible of blasphemy! 
  
  For amorphous they come, steeped in the fetor of ten thousand years, \\
  Abhorrent colossi spawned from the sinistrous cosmic spheres.
  
  And upon their tongues, vile secrets so terrible sweet madness is a redolent balm!
  
  Rejoice and revel in the triumph of the Dark. 
  
  I shall glut the maw of that ineffable nameless evil which lurks forever in the soul of man, for so it is written in the Chronicle of Shadows...
}

\Xserasshana{} receives the \hr{True Draconic}{True \Draconic} tongue from the \xss. 

\lyricsauthorbookpage{Anton Szandor LaVey}{The Satanic Bible}{29}{
  Each verse is an inferno, each word is a tongue of fire.
  The flames of Hell burn fierce... and purify! 
}





\subsubsection{\Tiamat-tachi worship the \xzaishanns}
\Tiamat-tachi admire and worship the \xzaishanns{}. 

\lyricsbs{Exmortem}{Sovereignty}{
  Admiring the triumphant demonthrone, \\
  sealed with the knowledge of time.\\
  Magic runes are carved here.\\
  Will you ever find the key?\\
  The bound demon in the earth\\
  is waiting to be released.
  
  He has travelled beyond the worlds.\\
  He has danced with death.\\
  Now he controls it all.\\
  With strength he suffered.
}





\subsubsection{They unlock true potential}
\target{Dragons unlock XS potential}
The \dragons{} were finally able to unlock and access the true potential of the well of \xsic{} power that resided inside them. 
They were \hr{Origin of Dragons}{stuffed full of \xsic{} power when they were created}, remember? 





\subsubsection{They become \draecchonosh}
The first generation of \draecchonosh{}, who came to be known as the \firstgendragons{}, directly absorbed \xzaishann{} essence. The second generation, the \shaeeroths{}, received it channeled from them, and later generations inherited it naturally.

After this, the \dragons{} enslaved legions of \daemons{} that previously served the \xzaishanns. They turn their gaze on \Miith{}, bent on conquest.

\lyricsbalsagoth{The Voyagers Beneath the Mare Imbrium}{
  My power is absolute... greater even than that of Angsaar himself!\\
  I shall crush the Tellurian sphere,\\
  and the flaccid lickspittles who strive in vain to safeguard it!\\
  Yes... The dreaming is over!\\
  Now, let the vengeance begin!}

This newfound power corrupted them into chaotic, \daemonic{} beings. Twisted by the \xzaishannic{} souls within them, they almost became \xzaishanns{} in \ophidian{} form. 





\subsubsection{Later someone discovers it}
Later in the series, I should have a story arc where someone discovers the truth of \Tiamat-tachi and their research. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  ... a fantastic and somewhat 
  horrifying dream in which I traversed a great black cyclopean cityscape,
  its towering stygian walls inscribed with some form of outlandish glyphs which
  seemed to writhe squamously and alter their shape even as I gazed at them.
  \\
  A sibilant whispering which seemed at once familiar and yet intrusively alien
  compelled me to walk to the edge of a particularly sinister looking edifice
  and peer out over its precipitous perimeter. 
  \\
  When I did so, I beheld this
  world of ours, recognizing vaguely the apparent shapes of the five continents,
  yet the entire vista seemed so distant that the whole appeared in its entirety
  no larger than a sphere which I could fit snugly into the palm of my hand.
  \\
  When I turned again to behold the looming obelisks, I found I could then
  easily read the previously untranslatable ciphers in the black stone. 
  \\
  They
  were the words of a great thaumaturgist who had seemingly discovered a
  repository of aeons-old lore detailing the sidereal web of the cosmos, with
  arcane diagrams pinpointing certain astral portals and places of empyreal
  potency, a sort of pangalactic ley-line chart, if you will. 
  \\
  Indeed, these
  Star-Maps of the Ancient Cosmographers seemed to take a not insignificant 
  toll on the author's sanity, as evidenced by the tone of his inscriptions, which
  seem to suggest that in discovering this Pandora's Box of dark elucidation,
  his fate was to be inexorably dogged by some nameless and implacable gloom
}









\subsection[Tyarith Kserasshana as a Dark Messiah]{\Tiamat{} as a Dark Messiah}
\Tiamat{} is a \trope{DarkMessiah}{Dark Messiah} kind of character. 
At first she wanted to bring enlightenment to her people. 
But the awful knowledge she discovered and absorbed drove her mad and caused her ideals to became twisted. 

She became traumatized and warped and gave in to perversity. 
She embraced and rejoiced in the most cruel, inhuman and destructive aspects of the \xss{} and their power. 

Compare to Horus from \emph{Warhammer 40,000}.

But despite her corruption (or perhaps because of it), she won and became queen of the \dragons. 
And in the \firstbanewar{} she was their first and greatest hope. 





\subsubsection{\Tiamat{} hears voices in her head}
Perhaps \Tiamat{} hears voices in her head, voices who are actually various figments of her mind and imagination. 
They question her principles and tempt her into perversity. 

Compare to the scenes in \authorbook{Graham McNeill}{False Gods} where Horus, in dreams, meets a phantom masquerading as his companion Sejanus. 





\subsubsection{\Tiamat{} worships the \xss}
\lyricsdimmuborgir{Relinquishment of Spirit and Flesh}{
  King of tempests and storms!\\
  Lord of innumerable figures and forms!\\
  Blessed with thy cold I am,\\
  as I upon the shoulders of mine\\
  bear the burden of Thine.
  
  Once I got touched by a fire from beyond,\\
  an invitation to darkness of which I could not resist.\\
  Caressed by the feathers of the fallen,\\
  I took the fate in my hand.
  
  Revealing Thy powers in visions and dreams.\\
  Invoking your magic at night.\\
  Honoured I am to mission Thy word.\\
  Within a creed is sworn of majestic might.\\
  An infernal allegiance in which I pay my share.\\
  An unholy awakening inside of which I intend to bear.
  
  Possesses by the true god of Earth I am.\\
  Possessed for eternity.
}

She becomes evil. 

\lyricsdimmuborgir{The Serpentine Offering}{
  My descent is the story of everyman.\\
  I am hatred, darkness and despair.
  
  Evoked and entertained through centuries.\\
  Wrathful and sullen. Dormant still.
  
  The ferocity pervades everywhere,\\
  waiting to be released at last.\\
  Hear my offering, ye bastard sons and daughters.\\
  Share my sacrifice.\\
  Share my sacrifice.
}

\lyricsdimmuborgir{For the World to Dictate our Death}{
  Let us sit by and watch \\
  Death and destruction's devotees revel. \\
  Let us sit back and witness \\
  innocent semen being poured...
  
  Into the arms of Armageddon. \\
  Let it pour, more and more. \\
  Pure fucking Armageddon. \\
  Let it pour, more and more.
}

\lyricsbs{Marduk}{Legion}{
  A new era will arise \\
  as I see the black angels of the abyss fly\\
  and the demons come storming in the silent cloudless sky\\
  with their burning eyes of ripping evil.
  
  I am given strength from a thousand sinners that dwell \\
  in the everlasting, burning, roaring depths of Hell. \\
  With the demons the possess my blackened heart and soul\\
  I shall strive for Satan's triumph and reach infernal goals.
  
  Children of darkness, raise your blood-filled cups \\
  to our father with horns.\\
  In eternity, we shall blaspheme the one \\
  who was tormented with thorns. 
  
  Feel the darkness growing when we draw near.\\
  My name is legion, for we are many in here.
  
  Heaven shall burn accompaigned by the angels' cries.\\
  We shall invert paradise.\\
  Death to peace!
}

She preaches to her followers of a \daemonic{} paradise. 

\lyricsdimmuborgir{Allehelgens D\o{}d i Helveds Rike}{
  Utspente vinger over M\o{}rkets dype svelg.\\
  Satt til verden for \aa{} meske seg med pest og d\o{}d.\\
  Fr\aa{}tsende i synd og hor.\\
  Overmakten fra p\o{}lens bastarder\\
  n\ae{}rer behag i syndens hierarki.\\
  Et evig liv i Paradis\\
  er fullkommenhet i Satans dynasti.
}

She seduces them to follow her. 

\lyricsdimmuborgir{Cataclysm Children}{
  Are you born from the abyss,\\
  and have you sought the creed \\
  that drape the shadows\\
  of your own thought?
  
  Is your heart mesmerized \\
  by the fire that burns forevermore?\\
  And do the secrets from the flames \\
  hold the mysteries over which you preside?
}

They have become forever corrupted by the \xss:

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Sola Fide
}{
  Verily I say unto you, \\
  there is none righteous enough to resist, no, not one...\\
  For your hands are defiled with blood, and your fingers with iniquity;\\
  Your lips have spoken lies, your tongue has muttered perversity.\\
  The heart of a lost angel is in the earth, \\
  the immaculate is abased... forevermore.
  
  Sola Fide. Sola Deo Infernali Gloria.
  
  Neither stormful convulsions \\
  nor an apex of light shall break the yoke\\
  For he that keepeth His commandments \\
  dwelleth in him, and He in him.\\
  And hereby we know that He abideth in us, \\
  by the Spirit which He hath given us
}





\subsubsection{Some \Draecchonosh{} become bitter}
Some \draecchonosh, after tying themselves to the \xss, become bitter and evil. 

\lyricsdimmuborgir{For All Tid}{
  Hver en t\aa{}re er frosset.\\
  V\aa{}r sjel er lenket.\\
  V\aa{}rt hat er blodig.
  
  All glede er svunnet.\\
  All latter er forstummet.\\
  Alt liv skal ende i d\o{}d.
  
  I et kalt og \o{}de landskap\\
  skal den sorte horde tre frem.\\
  V\aa{}r herre skal stige opp for all tid, \\
  reise sitt rike igjen.
  
  N\aa{} er tiden kommet.\\
  Ja, knus de godes ord.\\
  La oss for alltid bli herskere \\
  p\aa{} denne jord.
}





\subsubsection{Maybe she was just a queen}
Maybe \Kserasshana{} was not the one responsible for all of the above. 
Maybe she didn't \quo{found} the \dzraicchenoss{} people at all.
Maybe the invocation of the \xss{} happened before her time, or maybe she was just one among several such summoners (albeit more powerful and daring than most). 
Maybe she was just a queen, a great leader who managed to unite her people. 










\subsection{The nature of the \firstgendragons}
\target{Tiamat is XS}
Perhaps the \hr{Elder Dragons}{\firstgendragons} are not \dragons/\ophidians{} at all. Perhaps they are \xss. Perhaps the \draconian{} race was founded when they began to worship the \firstgendragons, who were \xss. 

This has a relation to the issue of \hr{Draconic immortality}{\draconic{} immortality} vs. \hr{Ophidian immortality}{\ophidian{} immortality}. 

The \dragons{} began to interpret and depict the \firstgendragons{} in \draconic{} form, as \uber-powered \dragons; the founders and sort-of progenitors of the race. (See the section about \hs{Tiamat's true form}.)

If this is so, then how can \hr{Ishnaruchaefir}\Ishnaruchaefir-tachi be the \quo{sons} of \hr{Khoth-Sell}{\KhothSell}? 









\subsection{Some see the \xss{} as evil}
Some \ophidians{} see the \xss{} as a terrible evil that must not be allowed into the world. 

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there... 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}









\subsection{The \Draecchonoshwar}
\target{Draecchonosh war}
Some of the other \ophidians{} were swayed by the \psp{\dzraicchenosses} power and glory and joined them, while others were repelled by their brutality and evil. 

\lyricsbalsagoth{The Empyreal Lexicon}{
  Stay thy hand and thy tongue, slave of the Outer Darkness...
  Surely you are not foolhardy enough to dare awaken the dire titans of Z'xulth!}

\target{Tiamat kills Hesod-Nerga}
The \firstgendragons{} waged war against their fellow \ophidians{}... and the world.

\HesodNerga{}, the great \ophidian{} hero, protested against his daughter's embracing this thoroughly evil power. Some of the \ophidians{} tried to \quo{save} \Tiamat, believing her brainwashed and possessed by the \xzaishanns{} against her will, and sought to exorcise the \daemons. They were dismayed to realize that \Tiamat{} was \trope{NotBrainwashed}{Not Brainwashed}. 
She responded by slaying her \HesodNerga. 

After this defeat, many \ophidians{} went into dormancy. \Tiamat{} conquered \Miith{} and reigned as its queen for tens of thousands of years, and the \dragons{} reigned with her as the lords of \Miith{}. 

Later, the term \quo\dragon, derived from \quo\draecchonosh, came to be used of all \ophidians, regardless of whether they possessed \xzaishannic{} blood or not. 

\lyricsbs{Exmortem}{Berzerker Legions}{
  Frigid storms and devastating raids.\\
  They are unconquerable.\\
  Frigid seas and devastating raids.\\
  Paramageddon.
  
  Runes imprinted in our skin.\\
  Northern magic surrounds us.\\
  Asa demons showing the way.\\
  Berzerker legions on all sides.
}

\lyricsbs{Monolith Deathcult}{Doomed To Slaughter}{
  The ancient gods are back on earth. \\
  We serve the book of blood.\\
  The blood of men will drench the fields in darkness.
}









\subsection{\Draconian{} Supremacy}
Previously, the \dragons{} had been too few to be a world superpower. 
They were strong, but they had little magic. 
As few as they were, they were no match for the \quiljaaran{} or the \aryothim, even though each \dragon{} was worth ten of them in combat. 
Now, with their new powers, the \dzraicchenosses{} were suddenly psycho-badass. 
They conquered{} \Miith{} and continued to dominate it for thousands of years. 
All the way up till the \secondbanewar. 





\subsubsection{\Aryoth conquered}
The \dragons waged brutal war on the \aryothim, almost eradicating them. 
In their hatred, the \dragons destroyed much of the \aryoth civilization, including much of their hated \hr{Aryoth inventors}{technology} that had so long been a threat to the Serpentine peoples.
They destroyed universities, libraries and all sorts of containers of this hateful \aryoth knowledge, to ensure that \dragons would once again reign supreme. 





\subsubsection{Technology}
The \dragons cared primarily about sorcery, since this was what had saved their people and returned them to the throne of \Miith. 
So that was what they researched and developed. 
They disdained natural science as a poor man's substitute for true power, so they discouraged research into that area. 

Besides, they did not want lesser races to be able to once again gain control and dominate over their betters. 
\Dragons had a great natural talent for sorcery. 
They had no such advantage in the area of natural science. 

So they suppressed many sciences, and the overall technology dropped in a lot of areas. 












\subsection{The \shaeeroths}
The first \shaeeroth{} were created some time around here. 

\target{Secherdamon does not become Shaeeroth}
\Nexagglachel{} and \Ishnaruchaefir{} became \shaeeroth{} early in their lives. 
\Secherdamon{} wanted to follow in their footsteps, but he knew he had not the courage nor the strength. 









\subsection{\Scathae{} are created}
\target{Origin of Scathae}
It is at this point that the \scathae{} were created. 
The \dragons{} wanted a servitor race to serve them. 
So they took some of their own \ophidian{} genes and mixed them with the genes of various \saurians{}, including \hr{Nycan}{\nycans}. 

The \scathae{} were bred from \hr{Locul}{\locul} stock. 
They were created with bits of the original \ophidian{} people, salvaged from mummies. 
And also with \cregorr{} genes. 

They performed many experiments. 
Most failed. 
But a few succeeded. 
These became the \scathae{}. 

\target{Cregorr came to serve Dragons}
The \dragons{} also tamed many of the \cregorrs{} and made them serve them. 

Both \scathae{} and \cregorrs{} had \xsic{} genes, which gave rise to the \hr{Scatha fury}{primal fury that lurked even in the peaceful \scathae}. 















\section{Draconian Supremacy waning}
\subsection{\Firstgendragons{} died}





\subsubsection{\Kserasshana{} and \Nexagglachel}
\target{Nexagglachel gets stewardship}
\index{stewardship}
Before her death, \Kserasshana{} talked to \Nexagglachel. 
He was her eldest and most skilled son. 

\begin{prose}
  \Kserasshana: 
  \ta{%
    After I and the other elders are gone, thou wilt be the greatest and best \dragon{} on \Miith.
    I charge thee with the stewardship of \Miith.
    Carry on our legacy.
    Lead our race, rule our world and keep it safe for our people.
    Your two brothers are also strong and have much potential.
    But you must lead them.}
\end{prose}






\subsubsection{The \firstgendragons{} died}
\target{Elder Dragons die}
\Tiamat{} eventually died in some war. 

But the heroic role they played in the war overshadowed their cruel tyranny. 
After the war their corpses came to be \hr{Elder Dragons worshipped}{worshipped as dead gods}, close to the \xss{} in status. 










\subsection{\Nexagglachel-tachi rise}
After the elder \dragons{} had all perished, it now fell to younger \dragons{} to lead their people (to the extent that the \draconic{} people is willing to be led). 
\Nexagglachel{} and his brothers were now the de facto top-of-the-pop. 

Without the \firstgendragons, the \dragons{} were weakened, but they still pulled through, under the capable leadership of \Nexagglachel{} and other great \dragonlords, and were able to strike back and exterminate the \banes{} that remained on \Miith. 









\subsection{\QuilJaaran{} supremacy}
\target{QJ supremacy}
The \quiljaaran{} were always rivals of the \dragons{} and \ophidians, but the sometimes allied. 

The \quiljaaran{} fought alongside the \dragons{} in the \firstbanewar. 
They suffered great losses in that war, but not quite as devastating losses as the \dragons{} (who lost almost all their elder leaders). 

So for a couple of thousand years after the \firstbanewar, the \quiljaaran{} were pretty dominant on the face of \Miith{}. 
They ruled several Realms. 

There were conflicts between \quiljaaran{} and \dragons{} in this time, but the \dragons{} were too few, too scattered to wage full-scale war, so they were most often forced to retreat before the expanding \quiljaaran. 

The \vorcanths{} and \nagae{} were also involved in these wars. 

Their domination lasted until \Nexagglachel{} was able to unite sufficiently many \dragons{} to challenge the \quiljaaran. 
\Nexagglachel{} intended to rebuild \ps{\TyarithXserasshana} empire. 

Maybe this \quo{\draconian{} revenge} \hr{Nexagglachel and Thanatzil}{coincided with \ps{\Thanatzil} time}.









\subsection{\Dragons{} disorganized}
\target{Dragons disorganized}
The \dragons{} were terribly disorganized after the \firstbanewar. 
\Nexagglachel{} made a heroic effort to unite them, and he achieved some success, but not as much as he had hoped for. 
The \dragons{} would continue that way all the way \hr{Second Banewar unites Dragons}{up till the \secondbanewar}. 

The \dragons{} were aloof and operated behind the scenes, letting the \quiljaaran{} and others dominate the picture. 









\subsection{Golden age of technology}
\target{Golden age of technology}
\index{technology}
The time between the \firstbanewar{} and the \secondbanewar{} was something of a golden age of technology. 
Many new things were invented in this period. 























\chapter{\AvatarofEntropy}
Tells the story of \Semiza, the origin of the \resphain, \Merkyrah, the \resphan{} rebellion, the creation of the \satharioth{} and the \secondbanewar. 





\begin{blurb}
  \Miith{} is a cruel world. 
  
  \Dragons{} rule the skies, and their legions of reptillian \cregorrs{} and \scathae{} sweep across the land. 
  The \nephilim{} have been banished from the fertile grasslands and forced to live in deserts, in caves and under the earth. 
  
  \Semiza, \nephilic{} king of \Girigor, desperate to find a way to save his people from the \psp{\dragons}{} depredations, turns to black magic. 
  An alien god appears in \ps{\Semiza}{} visions and offers him a chance to vindicate the \nephilim. 
  
  But the price will be a gruesome sacrifice...
\end{blurb}
















\section{The Big Picture}
\subsection{The \Bane{} Master Plan}
\subsubsection{The \banes{} in exile}
\target{Origin of Nyx}
The \banelords{} were not all destroyed. At the last moment, \Daggerrain-tachi seized hold of a corner of the Shroud of Realms that the \ophidians{} were weaving, twisting it into a pocket Realm, into which they fled. This Realm was a vestibule, a thin, almost unnoticeable corridor to \Erebos. They remained in this Realm for thousands and thousands of years, reshaping and expanding it into a shadow of \Erebos. It became \Nyx, the Twilight Realm. 





\subsubsection{\Daggerrain{} is the gate}
\target{Daggerrain is the gate}
\Daggerrain{} embodies the cosmic conduit between \Erebos{} and \Nyx. See, \Erebos{} is tens of thousands of light years from \Miith{}. The \banes{} \hr{Banes come to Miith in spaceships}{came to \Miith{} in spaceships}, but this took thousands of years. 

But \Daggerrain{} has solved the cosmic equations and cast the Realm-weaving spells that create a short-cut through the Realms directly to \Erebos, and as long as he is present in \Nyx, the connection persists.
Granted, the conduit is narrow after the formation of the \hr{Crystal Sphere}{\CrystalSphere}, but it's better than nothing. 

Were \Daggerrain{} to fall, the link would be broken, and \Nyx{} would be permanently severed from \Erebos. At the end of \SentinelsFinalBook, \hr{Daggerrain falls}{this is exactly what happens}. 





\subsubsection{\Bane{} magic on \Miith}
After the \firstbanewar, the \CrystalSphere{} was not entirely tight, so \Erebean{} energy could seep through in small amounts. Some mages discover that they can channel \bane{} power and use it to cast a kind of primitive \nieur{} magic. 

At first, the \dragons{} and others are terrified at the thought of the \banes{} returning, so they persecute and wipe out these mages. But nothing seems to come of it, so gradually, as the centuries pass, the \dragons{} glow lax and stop caring. 





\subsubsection{The \banesz{} plan}
We are now several thousand years after the \firstbanewar: The \banes{} are forgotten and no one fears their return any more, barely even the \dragons{} who actually fought them last time. 

\index{technology}
Note that \hr{Technology}{the technology is still low}, for a number of reasons. 

But this is all part of \ps{\Daggerrain}{} plan. See, \Daggerrain-tachi could not travel back into \Miith{}, but the Shroud was thin enough for them to gaze into \Miith{} and observe, so they had a reasonably good idea of what was going on there, and they could plan their return. He knows that he will have a hard time reconquering \Miith{} with the \dragons{} opposing him, but he has immortality and patience, so he waits some millennia, planning his return while lulling the \dragons{} into a false sense of security. 

When the time is right and the opportunity presents itself, \Daggerrain{} plans to contact some \Miithian{} mortals, bargain with them and convince them to help the \banelord{} bring his people to \Miith{}. 

\Daggerrain{} will not bring the \banes{} to \Miith{} immediately. Rather, he intends to \quo{crossbreed} his people with some native \Miithian{}s\dash possibly the \nephilim\dash to create a new super-race. This race will eventually become the \hr{Resphan}{\resphain}. 





\subsubsection{The Vortex}
The \banes{} try to open a dimensional gate called the \quo{Vortex}. 

The Vortex is actually not a mere portal but a deeper merging of the planes, a connection allowing a high degree of free movement from \Erebos{} to \Nyx{} and on to \Miith{}. 









\subsection{\Draconian{} Aspect}
\target{Nexagglachel and Thanatzil}
This book also has a \draconian{} aspect: 
While \Semiza-tachi are trying to bring \banes{} to \Miith{}, \Nexagglachel{} is fighting to unite the \dragons{} and reclaim \Miith{} for their race. 
The \dragons{} are \hr{Dragons disorganized}{terribly disorganized}, and \Nexagglachel{} hopes to change that. 
They are waging wars against one another and against their rival races, the \quiljaaran, \vorcanths{} and \nagae. 









\subsection{The other races}
Have plenty of \aryothim, \vorcanths{} and \quiljaaran{} in major roles in this book. 

Maybe even turn \Vexstrasshin{} from a \dragon{} into a \quiljaar. 









\subsection{When is it?}
When did this story take place? 
When did \Thanatzil{} live? 

It could be just few years after the \hs{Draconian Ascendancy}.
Or it could be thousands of years later. 















\section{\Girigor}
\target{Girigor}
Over thousands of years, various groups, independent of each other, discover this energy source. \Girigor, the \nephilic{} kingdom ruled by \hr{Semiza}{\Semiza} is one of them. 

In \Girigor\dash and among many other \nephilic{} peoples of that time\dash the written tongue was sacred and secret, known only to the priest-mage class and surrounded in much mysticism and ritual. It was closely tied to their magic. 

Back then, sorcerer-kings ruled. It was before the \feud{} came to dominate and manipulate everything, remember. (In the days of the \charade, \hr{Sorcerer-kings}{sorcerer-kings} are usually dethroned by the master races, who \hr{Master races seek to control magic}{try to control magic} and fear the threat that such a ruler might potentially pose.)

\Girigor{} is very misogynistic, \hr{Nephil misogyny}{as the \nephilim{} are wont}. 





\subsubsection{Language}
The language of \Girigor{} should resemble ancient Sumerian or Babylonian. 





\subsubsection{Magic}
\Semiza{} and the other mages had some magic skulls and bones that originally belonged to their sorcerous ancestors, or even dead gods. 
Even in death, these bones retained some magical power. 
They had been handed down for centuries. 
Some of the oldest and most powerful sorcerers' bones were still preserved. 

\ps{\Semiza} people created a \matrix{} from the souls of their great dead mages. 
But they had to deal with forbidden powers, including the \xss{} that dwelt beneath the earth. 

\citeauthorbook{RobertEHoward:RedNails}{Robert E. Howard}{Red Nails}{
  \quo{Madness and death lurk in it. 
    The wizard of Xotalanc understand its secret\dash they found it in the catacombs, where lie the bones of terrible kings who ruled in Xuchotl in the black centuries of the past. 
    To gaze upon its freezes the blood and withers the brain of a man who understands not its mystery.}
  
  \quo{In life it housed the awful brain of a king of magicians! 
    It holds still the life and fire of magic drawn from outer spaces!}
}





\subsubsection{Religion}
The gods of \Girigor{} were \hr{Aryoth}{\aryothim}. 
But these gods were slain by \dragons{} (or maybe \quiljaaran) in some great battle that destroyed \ps{\Girigor} civilization. 
After this great defeat, \ps{\Semiza} people were hunted down and killed by the legions of \cregorrs{} and \scathae. 

Remember to have flashbacks of this terrible battle.
\Semiza{} and others have nightmares about the evil day when their world was destroyed and all they loved was torn from them. 
They even had to watch their gods die. 

\lyricsbs{Iced Earth}{Setian Massacre}{{\obeylines
  Screaming in agony, cries fill the air \\
  Eyes once full of hope shedding tears of despair \\
  All that they've ever known is dead 
  
  Fire reigns from above, iron birds of dread \\
  All that they ever loved is dead \\
  All that they ever dreamt is dead 
  
  Temples are burning, streets soaked with blood \\
  Heed the prophecy, destiny is done \\
  All that they ever loved is dead \\
  All that they ever dreamt is dead 
  
  Yet there's a glint of hope \\
  If the chosen can survive \\
  In secret the ten thousand hide \\
  East in the mountains \\
  The chosen bide their time \\
  The Clouding, our strike on mankind 
}}

They are now a people forsaken, alone and unprotected, with no gods watching over them. 
Therefore many are prepared to embrace the \banes. 
But many subjects refuse to accept the fact that the gods are dead. 
They insist that \trope{HesJustHiding}{They Are Just Hiding} and keep praying to them. 
\Semiza{} and \Eshayzal{} despair over this display of stupidity and stubbornness. 
Meanwhile, some among the people resent their king for so readily abandoning the gods they have served for a thousand years (or whatever) and take up the first new religion that walks by. 





\subsubsection{Technology}
\index{technology!\Girigor}
The technology is low. 
Late Stone Age or early Bronze Age. 
They have mostly stone and bone tools. 

Comparable to early Egypt. 

The only metal weapons they have are those few they can buy or steal from the \scathae{} and \cregorrs. 

Also, they do not have the skills to tame \saurians{}, so they only have mammals domesticated. 
Including some hyaena- or \latinname{Hyaenodon}-like dogs they use in war. 





\subsubsection{Other \nephilic{} societies}
There had been many other \nephilic{} societies before \Girigor. 
Many of them were considerably greater, more powerful and more advanced than \Girigor. 
But whenever one would rise too high, the \scathae{} would come to wipe them out. 















\section{\Semiza{} and \Ilu}










\subsection{\Semiza}
\Semiza{} was the eldest son of the \nephil{} sorcerer-king of \Girigor. 
Later he would take the throne and become sorcerer-king himself. 





\subsubsection{Young \Semiza}
Early on we see him passing some kind of \quo{manhood test}, marking him as a full-fledged sorcerer and a worthy heir to the throne. 

At an early point, \Semiza{} meets some girl that he likes. 
Either right after his rite of manhood or some time after, he is betrothed to her. 

Some years pass. 
The Jocainites hear the tales of war, of some terrible invaders from the sea devouring entire kingdoms. 
The king and mages are concerned, but \Semiza{} is still young and untroubled. 

Then comes the day of \Semiza{}'s wedding. 
On this, supposedly the greatest day of the young prince's life, the \dragons{} invade Jocain. 
It becomes massacre and young \Semiza{} sees his bride and his entire family slaughtered before his eyes. 

\Semiza{} and a few survivors flee to a system of underground caverns. 
Somehow they manage to survive the \draconic{} army's onslaught. 
\Semiza{} assumes the mantle of king and leads his people in exile. 





\subsubsection{\Eshayzal}
\Eshayzal{} is \ps{\Semiza}{} trusted friend and advisor. 

\index{technology!\bane}
The two are great geniuses and will later be able to perform miraculous feats of science using the \hr{Bane technology}{knowledge supplied to them by the \banes}\dash knowledge which is in turn \hr{Voyager technology}{stolen from the \voyagers}.





\subsubsection{Adult \Semiza}
Now \Semiza{} was sorcerer-king.
He had many wives and concubines. 

He hates the \dragons{}. 
Now, the \dragons{} were tyrants and had always been preying on his people, but I think there should be something more personal in it. 
Perhaps \ps{\Semiza}{} most dearly beloved wife or concubine or son\dash or more than one\dash was/were killed by \dragons{} or their minions in one of their raids. 

Anyway, this makes him bitter.









\subsection{\Daggerrain{} contacts \Semiza}
Throughout the millennia, there had been many people\dash thousands, perhaps millions\dash whom \Daggerrain{} might contact and who might stand a chance of succeeding in bringing \banes{} to \Miith. 
But \Daggerrain{} was patient, so he waited until he found the perfect situtation. 

\Semiza{} was a scientific genius, as was his partner, \Eshayzal. 
And \Semiza{} was bitter at the \dragons{} and longing for revenge and a \quo{return to glory} for his people. 
And his rule coincided with some nasty wars among the \dragons. 

\Daggerrain{} chose him. 

The \dragons{} had forgotten the \nephil{} survivors and thought nothing of them. 
Hiding in his underground lair, Semiza nurtured his hatred and dreams of revenge against the \dragons{}. 

Somehow Semiza reached out into the Cosmos with his mind. 
Perhaps he was deliberately searching for allies; perhaps he was taking mind-expanding drugs. 
By whatever means, he contacted \Daggerrain. 
Or \Daggerrain{} contacted him. 

Daggerrain penetrated the \ps{\nephil} vulnerable mind and probed around in it. 
He took from the sorcerer-king's mind his language and his entire memory. 
Then he introduced himself to the \nephil{} king, offering him the power to take his revenge, destroy the \dragons{} and restore his kingdom, that he might rule forever as an immortal king. 
In return, \Semiza{} had to help \Daggerrain{} bring his people to \Miith{}. 

At this point, Semiza asked: \ta{Who are you?}

In response \Daggerrain{} sent a vision where Semiza found himself alone and naked amid an endless, featureless plain, with a cruel and unrelenting hail beating down upon him with its sharp shards of ice, like a rain of a million daggers. 
Semiza interpreted the \banelord{}'s name as \quo{Daggerrain}. 

If he was to help Semiza and his people, Daggerrain needed the \nephil{} sorcerer to bring him to \Miith{}. 
He instructed the \nephil{} in the spells to use, and \Semiza{} went to work procuring occult ingredients and sacrifices (mostly \scathae) and recruiting and training mages to assist in the spellwork. 
The preparations took perhaps several years, but at last they are ready to perform their summoning ritual. 







\subsubsection{\Semiza{} turns from his gods}
\Semiza{} feels that his people's gods have betrayed him, so he searches for new ones. 

He feels like a pawn, adrift in sea governed by vast powers beyond his ken. 
He feels impotent, and he rages. 
He wants to regain control of his own fate and that of his people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Let me embrace my fate which was adrift and hung. \\
  I will be again the apple of his eye. \\
  Take me from among the doomed Laodiceans \\
  whose defamation thrilled the seething skies.
}





\subsubsection{\Semiza{} feels the calling of dark powers}
At first, \Semiza{} vaguely feels the call of dark forces from the Beyond. 

\lyricslimbonicart{Moon in the Scorpio}{
  A mirror blank ocean above me decoy.\\
  Superior forces that heal or destroy.\\
  Take me astray into the moonlight above
  through twilight eyes as a spectre shadow.
  
  It is a time of great light\\
  and of great darkness.\\
  Can you feel the presence\\
  of its phenomenon?
  
  In an atmosphere supreme\\
  forces dwell in domancy.\\
  The essence of its spirit is evil,\\
  as a curse upon thy name.
  
  Midnight is the shepherd of mysterious powers\\
  and moving shadows in the corner of the eye.\\
  Moon's blazing intuition\\
  contains what death requires.
  
  Cleanse the doors of perception.\\
  See things appear in its true art.\\
  The cold hands of divinity\\
  will tear thy soul apart.
  
  Behold the sky above \\
  when the moon is in the Scorpio.\\
  A cold bleak light
}

\Daggerrain{} haunts him. 
He tells \Semiza{} that he is the only hope for \Semiza{} and his people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Night after night grim voices shriek \\
  in portentous horror dreams, \\
  even though his room was locked, \\
  but a Seraph comes unseen. 
  
  Night after night his skin was flogged. \\
  Damn those recurrent dreams. \\
  Desperately flogging for relief \\
  while murmuring blasphemies. 
  
  The bloodstained walls surround him, \\
  icons made of Calvary wounds. \\
  Dreams of riddance were shattered in sin, \\
  ill-fated to avert doom.
}

He learns more of these dark new powers. 

\lyricslimbonicart{The Supreme Sacrifice}{
  I stand within the flame,
  watch the wisdom be discovered.
  When life and death is the same,
  I am devoured.
  
  So many nights I have spent \\
  in thoughts not heaven sent.\\
  Blood of hatred poured down like rain \\
  for evil secretus insane.\\
  In silent gloom I kneeled obsessed,\\
  channeling the enigmatic darkness.\\
  My soul, the servant\\
  under the illusive wings of death.
  
  When I receive a black picture of the future,
  and schockwaves attack from a nihilistic universe.\\
  My body, the temple, a mausoleum in flesh\\
  under the illusive wings of death.
}

He is overwhelmed with awe. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  The man started to cry, hands held to the sky,\\ 
  and expected to be purified in flames. \\
  But the Angel smiled and took the Book \\
  and commanded his holy mandate.
}

He was looking for a way to seize control of his own destiny, and this is it. 
He jumps at the chance and devotes himself to serving the \banes.

\lyricslimbonicart{Behind the Darkened Walls of Sleep}{
  I open gates and close the others. 
  Behind me now there is no return. 
  I broke the sealed door to imagination. 
  The pulsating darkness now around me burn.
}





\subsubsection{The name \quo\bane{} is born}
\Semiza{} is overwhelmed by the power and glory of \Daggerrain{} and his people (and the \Voidbringer). He believes that these gods will be the salvation of his people and the bane of all their enemies, and so he names them the \quo{\banes}. 





\subsubsection{\Semiza{} introduces the \bane{} religion}
\target{Bane religion}
\Semiza{} preaches to his people of the new gods he has discovered. He promises that they will save his people. In exchange, they must worship and serve them. 

Perhaps at first \Semiza{} does not know that the \banes{} are an entire people. He might think it is just a single god (\Daggerrain), whom he names \quo{the \bane}. 





\subsubsection{\Daggerrain{} reveals his true nature}

At first, \Daggerrain{} comes in disguise. 
It is only later that he shows \Semiza{} his true face.

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  The Fallen Seraph lowered his radiant mask \\
  and showed the man the countenance of the fallen Morningstar.}

Semize is terrified. 
But there is no way back. 
\Semiza{} gives him the name \quo{\Daggerrain}. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  The man seemed stricken by a thousand bludgeons. \\
  Penetrating just-healed wounds as foreplay for the storm.
}









\subsection{\Semiza{} builds a stargate}
\target{Semiza's stargate}
\Semiza{}, working under the \psp{\banelords}{} guidance, builds a great temple that is to act as a stargate, a focus for the portal to \Erebos. 









\subsection{The \banemessiah}
\target{Bane Messiah}
%The plan is that the \nephilim{} must provide a 
The plan is to give birth to a \quo{\banemessiah}: A superbeing, born of a \nephilic{} mother but invested with the life force of the \banes{} and possessing the power to open a conduit to \Erebos{}. Through this conduit they will be able to draw more energy and spawn more people like the Messiah, thus founding a whole race of half-\bane{} demigods. 
When there are enough of them, they will be able to challenge the \dragons, overcome the \hr{Crystal Sphere}{\CrystalSphere} and grant \Daggerrain{} and his people unrestricted access to \Miith{}, whereupon they will march in like a conquering army, scouring the world of the \draconian{} tyrants. 

\target{Thanatzil is the gate}
So the Messiah \emph{is} the key and the gate, an incarnation of the \bane{} soul and legacy. If \hr{Thanatzil fails}{he dies, the portal collapses}.









\subsection{The Shroud of \Girigor}
\target{Shroud of Girigor}
\Daggerrain{} took some threads, components, techniques and ideas from the \hr{Crystal Sphere}{\CrystalSphere} and used them to weave a small Shroud around \Girigor, thus shielding \Semiza-tachi and the \resphan{} project from prying \draconian{} eyes. 

Later he went on to \hr{Shroud of Nyx}{weave a similar Shroud on \Nyx}, but that did not work out so swell.









\subsection{\Vexstrasshin{} suspects}
Most \dragons{} suspect nothing. 
When \ps{\Semiza}{} people start invoking \banes{}, no one believes it. so they are allowed to proceed. 

\target{Dragon war when Resphain appear}
Also, this coincides with a bloody war among the factions of \dragons{} (\Tiamat{} is dead, after all), so they are busy fighting each other and have little time left to investigate alleged \bane{} summoning. 
This war is, to some extent, masterminded by \Daggerrain, a part of his \trope{XanatosGambit}{Xanatos Gambit}. 

But at least one \dragon{} suspects that \ps{\Semiza} new religion and this whole \Thanatzil-business is \trope{SeriousBusiness}{Serious Business}, namely \hr{Vexstrasshin}{\Vexstrasshin}. 
Her fellow \dragons{} do not believe her (being caught up in their own wars), so she sneaks into \ps{\Semiza} city in disguise. 
Here she tries to discover what is up. 

When she discovers \Thanatzil, she tries to stop him. 
She fears him. 





\subsubsection{Cameos}
Have some cameos with the \dragons{}: 
\Nexagglachel, \Ishnaruchaefir, \Secherdamon, \Triestessakhin, perhaps \Nzessuacrith{} (she was very young). 
They were all very happy back then. 
\trope{ItGotWorse}{It Got Worse}. 









\subsection{\Ilu, the Sacred Mother}
First of all, the \banes{} need a mother for their Messiah. \Semiza{} chooses his most beautiful, most beloved young daughter who is still an unmarried virgin: \hr{Ilu}{\Ilu}. 

\Ilu{} has been raised to be very loyal and obedient to her father and king and to her people, so when she is chosen as the Sacred Mother, she could not refuse even if she were given the choice, which she isn't. She is honoured to be selected as the instrument of her new god's will. 

But there is a catch. Rather, two catches. 

\begin{enumerate}
  \item 
    The pregnancy and birth will be very hard and painful for her, so she must be strong and brave and endure much hardship for the sake of her god and her people.
  \item
    She \emph{must} be an untouched virgin. Otherwise it will all be much worse for her, and she may die.
\end{enumerate}

\Semiza{} is convinced and offers his beloved daughter as a sacrifice to the \banes. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  She is Thine, O take her quickly. \\
  Thou art her hope, O raise her high. \\
  Ever hoping, ever trusting, \\
  unto Thee I strive and cry.
}

He will make her a heroic martyr. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  But shall she be refined in Thine holy light? \\
  Her spirit will shine will thousand suns. \\
  Condone my doubt, but who am I? \\
  The haranguing priest of the newborn Herod king.
}

He just wants to save his people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Let them through thy boundless mercy \\
  from all evil be restored. \\
  Hearken to the voices pleading \\
  of Thy Church, O gracious Lord!
}

She has one purpose. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Born with the ability of begetting\\
  Only but One gift were she granted\\
  To excrete a new humanity unwanted\\
  Reluctantly she\dash woman\dash \\
  loves the god of a creation within
}





\subsubsection{\ps{\Ilu}{} sin}
\target{Ilu's sin}
The virginity requirement is a problem. See, \Ilu{} has \hr{Ilu's lover}{a lover}. They haven't had actual vaginal intercourse, so she is still a virgin. But they have done... \emph{stuff}. She has sucked his dick. Only once, but it is enough that she cannot call herself \quo{untouched}.

But she was not supposed to suck his dick, and she dares not confess to her father that she did it. So she lies and proclaims herself untouched. \Semiza{} and everyone else is happy, and they proceed with the process of impregnating her as the Sacred Mother. 

Or maybe she was never asked, because her father considered her virtue to be beyond question. 

\Ilu{} is scared shitless. She is afraid that because of her wicked promiscuity (as she sees it), the whole project is in danger and may fail, and her people may never be saved. She has lots of guilt over this, but she is too afraid to come clean. She has lied to her father and made it all worse for herself. 

She's done other sexual stuff, too, but only touched a man's dick this once. And it's the worst part. The penis plays a huge role in their old religion, rituals, symbolism and sexual mysticism. The vagina is also important, but doesn't have as big a role as the penis. They are a masculine, patriarchal people who worship the phallus as a symbol of strength, fertility, masculinity, life, initiative and all that is good. In sex, the man and his mighty dick conquers the woman and binds her as his slave and property. He plants his seed in her womb, thus claiming it as his domain, and by extension, the woman must serve and obey him. (Perhaps you can even legally steal another man's virgin daughter by raping her, based on this mysticism.)





\subsubsection{She wants to conquer her sin}
\target{Ilu wants to conquer her sin}
She decides that she has brought the problem upon herself and is responsible for dealing with it. So she resolves to fight as hard as she can for the sake of the god-child that will soon be growing inside her. She swears that she will fight her own sin and vanquish it, and that the god-child \emph{will} be born. 

\Ilu{} is religious and prays a lot. To the old gods of her people, and to \hr{Bane religion}{her father's new gods, the \banes}\dash the \quo{fathers} of her child.





\subsubsection{Earlier attempts and giving birth to \resphain}
\Ilu{} was not the first woman who tried to give birth to the \banemessiah. Several other women had tried and died horribly before. 

The real reason for this is that first experimental \resphan{} foeti were \emph{too} voracious, too greedy, too parasitic. In their hunger they drained too much life-force from their poor, suffering mothers. The mothers would die long before the children were ready to be born, and the children would die as well.

But this was covered up. The official story, as told by \Semiza{} and \Eshayzal, was that the women were weak of faith and will. They had failed their god and their people. This put great emotional stress on poor \Ilu, who feared that she, too, would not be good enough, and would ultimately fail and die. 

There was always only one prospecting Sacred Mother at a time. The \banelords{} invested all of their \resphan{} power into the one \banemessiah, and so could only incarnate one at a time. Whenever one would die, the \banes{} would quickly reclaim the power and recycle it. 

Whenever the Sacred Mother started bleeding, mutating and suffering badly, she would be secreted away deep in a temple and kept hidden until her inevitable and grisly death. Thus, no one knows how horribly they suffer and die. 

Thus, \Ilu{} is happy and full of hope. She believes that she has been chosen for something wonderful and will give birth to a beautiful saviour. \Semiza{} assures her that she is the right one and that it won't go wrong this time. 

Perhaps \Semiza{} had long known that \Ilu{} was a good candidate. But out of love for her he didn't select her at first, because he knew the danger. But \Daggerrain{} tells him that she has the best chance of succeeding\dash and even a chance of surviving (not a lie). So at last, \Semiza{} chooses her. And she does fare better than many, because of her strong will and idealism. 









\subsection{The seed is sown}
\target{Semiza designs Resphain}
\target{Origin of Resphain}
\Semiza{} and his sorcerers, under guidance from \Daggerrain{} and his \banelords, labour to prepare the arcane ritual that will impregnate \Ilu{} with the Messiah, the first \resphan. 

This must be done in secret, so that the \dragons{} do not suspect.

\hr{Entropy}{The \banes{} suffer from stagnation and cannot easily create new things}. So they needed the help of an ingenious mortal mind to engineer their new super-race.
So \Semiza{} ends up acting like the primary artist and designer behind the whole \resphan{} project. He understands \ps{\Daggerrain}{} vision of a super-creature with traits from \banes, \voyagers{} and \nephilim{} alike. The \banes{} can supply them with knowledge, but they must do the research themselves.

At \ps{\Semiza}{} side stands \hr{Eshayzal}{\Eshayzal}, his companion and advisor. Together they engineer the \resphan{} god-child. 

They worked hard for some time, and finally the research was complete. 
They were ready to perform a magical ritual and impregnate \Ilu{}. 




\subsubsection{Ritual prepared}
They began the impregnation ritual of poor \Ilu. 

\citebandsong{DeathspellOmega:Kenose}{%
  DeathspellOmega
}{
  \Kenose
}{
  Thou shalt bringeth the chalice of divine wrath \\
  and final consummation to thine lips, \\
  and drink with confidence...\\
  Tell me, sweet child, \\
  why are tears rolling from your eyes?
}




\subsubsection{Invocation of the \banes}
\Semiza-tachi invoke the \banes. 

\lyricsbs{Hate Eternal}{Catacombs}{
  Rise up from the ancient tombs. \\
  Grant us all your infinite wisdom. \\
  Endure as you rise from the catacombs. 
}

\lyricsbs{Hate Eternal}{The Creed of Chaotic Divinity}{
  Awakened by this ancient creed. \\
  Evoked, the ancestry of thee.\\
  Forsaken for centuries of times. \\
  Exiled, all of their kind. \\
  Foretold, the inheriting of the Earth.\\
  Forewarned of this predestined rebirth. \\
  Engaged, the rising from below.\\
  Fear, all mortals, for what they shall bestow.
  
  Conjure all, so that they may sustain\\
  their race, of what they must retain.\\
  Spew forth incantations in vain. \\
  Invocate all that they try to negate.\\
  Enchant all of their wonderful splendour. 
  Recant all of the texts that are sacred. \\
  Recreate all that has been begotten. \\
  Revive all that has been forgotten. 
}




\subsubsection{\Ilu{} impregnated}
\Ilu{} was knocked up. 
This happened in an aethereal, sexual dream sequence. 
She was half-raped, half-seduced by faceless, unclear, monstrous, almost-but-not-quite-\nephil-like monsters:

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Organic procreation, mind-intromission; there comes the salvation\\
  Pubescent vaginas obstructed with the redeemer's holy essence\\
  Humanity reduced to its supreme worthlessness;\\
  Children under His will, Ethic fulfilled
}

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Carnal Malefactor
}{
  There resides the fusion, there is the nucleus\\
  Angel prick and holy semen,\\
  And a woman genuflecting an aroused beast of burden alike\\
  Seduced by the father and seducing the son\\
  There resides the fusion, there is the nucleus\\
  A phallic communion that sanctifies interior wastelands
}









\subsection{\Ilu{} suffers}
\Ilu{} suffers horribly during her long pregnancy. 

How long is her pregnancy? The gestation period for \nephil{} women needs not be nine months like it is for \humans, and the gestation period of the \banemessiah{} needs not be the same as that of a \nephil{} child. 

It might be longer than nine months. And the sorcerers might need to perform many spells on her while she carries the child. And she would be required to work hard to aid them in their spellwork. (How?) 

\Ilu{} believes that it is \hr{Ilu's sin}{her own sin} that causes her to suffer. That and her weakness. She is intent on conquering her sin, so she fights hard, not only to combat her weakness, but also to hide it. She \emph{will} be strong. She \emph{will} serve her people well. She \emph{will} make her father proud. His faith in her shall not have been misguided. 

In truth, \ps{\Ilu}{} little blowjob had no effect at all (except psychologically). The \banes{} needed physical virginity for some reason. Why? Because there is some \hr{Heart}{Heart of \Miith} related power in her womb and sexual organs that they need to harvest, and that power is weakened when a girl loses her virginity. 

Anyway, the point is that all of \ps{\Ilu}{} suffering is not her fault. It is caused by the \banes{} and the \halfbane{} child growing inside her. 
As the mother of the \erebean{} abomination, she is cruelly abused. 
She is cruelly abused by the parasitic abomination growing inside her. It sucks out all of its own mother's life-force. She grows weaker and weaker and will eventually die in childbirth. 

%The \nephil{} women who had to give birth to the first \resphain{} are cruelly abused. They carried and delivered the children in gruesome pain and suffering, and the parasitic children sucked out all of the mother's lifeforce, killing her in childbirth. In fact, the first experimental \resphan{} foeti were \emph{too} voracious, killing their mothers long before they were ready to be born, and then died. As the mother carries the child, she suffers horribly as the gruesome thing sucks everything from them. 

Compare to the Mhybe from \cite{StevenErikson:MemoriesofIce}, except that all the suffering takes place \emph{before} the birth (whereupon she dies). Also compare to \bandsong{Hour of Penance}{Hideously Conceived}. 

She dreams of her wicked child and his evil \quo{father}. 
She is afraid. 

But it is important to note that Ilu is not against the whole thing. 
She laments the fact that she must suffer, but she tries to be strong because she knows it is the right thing to do. 
Her suffering will bring much good into the world. 

\Semiza{} and the others try to support her and be nice to her. 
She is their beloved and holy martyr, and they admire her for doing it. 
\Semiza{} tries to be a good and loving father, but his crazy religion somewhat estranges him from his people. 
Ilu laments this. 
She doesn't want her father to be alone and weird. 
So she is extra brave for his sake. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Night after night grim voices shriek \\
  in portentous horror dreams, \\
  even though his room was locked, \\
  but a Seraph comes unseen. 
  
  Night after night his skin was flogged. \\
  Damn those recurrent dreams. \\
  Desperately flogging for relief \\
  while murmuring blasphemies. 
  
  The bloodstained walls surround him, \\
  icons made of Calvary wounds. \\
  Dreams of riddance were shattered in sin, \\
  ill-fated to avert doom.
}

According to the theory, her suffering is partially caused by the \kenosis: 
The process by which the god (to whom she must give birth) is incarnated in the form of a feeble foetus. 
This process is difficult and painful, and it is \Ilu{} who must bear this pain. 

\citebandsong{DeathspellOmega:Kenose}{%
  DeathspellOmega
}{
  \Kenose
}{
  Obedience to the point of death,\\
  Falling down through increasing pressure\\
  Into the deathlike region\\
  Of ooze and slime and decay\\
  These are the fruits and symptoms \\
  of the abasement of the World,\\
  The assumption of humanity \\
  and the simultaneous occultation of Divinity
}





\subsubsection{Hentai nightmares}
\Ilu{} feels terrible guilt over having sucked dick. She has frequent nightmares of being forced to suck dick. She might be in a forest of penises, like monstrous trees or fungi or worms or snakes that slither around her and try to sneak into her mouth and other openings. Perhaps faceless men with penises (and no other recognizable \nephilic{} features) crowd and rape her.

Hentai!















\section{\Thanatzil{}, the \BaneMessiah}
\subsection{\Thanatzil{} is born}
At last, the \banemessiah{} is born. \Semiza{} gives him the name \hr{Thanatzil}{\Thanatzil}, which probably means something in their language. 

The story of \Thanatzil{} is very much inspired by the Christian myth of Jesus, and is intended, to some extent, to be a very dark, sick, twisted version of the Jesus myth. I need to have plenty of Jesus-like symbolism surrounding him.

\begin{itemize}
  \item 
    He is born of a virgin by immaculate conception.
  \item 
    \Nephilic{} kings come to greet him and pay homage to him at his birth. These are the kings of other tribes who have allied with \Semiza, swayed by his vision and his new religion. 
  \item
    He is an earthly/\Miithian{} incarnation of his gods, the \bane{} people, and born as a saviour to deliver the \nephilic{} people. 
  \item
    He \hr{Thanatzil must die}{must die and be resurrected} in order to save his people from hellish imprisonment. 
  \item 
    His birth is heralded in the heavens by a \hr{Black stars of Nyx}{black star} that shines through from \Nyx, or perhaps even \Erebos. It is a temporary portal through which flows power and a \bane{} soul from \Nyx{} into \ps{\Thanatzil}{} body. It is visible everywhere on \Miith{}, and some \dragons{} take note.
  \item
    \Nephilic{} kings came to visit and pay homage to the newborn \Thanatzil. These were allies of \Semiza{} who believed in his new religion and his vision of a future for their people. 
\end{itemize}





\subsubsection{\Thanatzil{} appears}
\ps{\Thanatzil}{} birth is terrible to behold. The infant is unlike any \nephil: Short and slim, black as midnight, and completely naked (where \nephilim{} are covered in hair, even from birth). He remains bald and hairless throughout his life. And he has feathered wings on his back. 


\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Carnal Malefactor
}{
  When a woman is knead by the claws of fowls attracted\\
  By seminal odours no longer hidden by dignity\\
  And purified by their beaks rummaging her swollen vagina\\
  When laments alter into praises \\
  despite holy duty and menacing perdition\\
  Seers can say that his birth does death subdue no more\\
  His birth does death subdue not, \\
  for my God proceeds of failed humility...\\
  O Master, the eastern pillar of your domination \\
  is the organic fallibility.
}

The Messiah comes into the world riding a river of blood, tearing apart the flesh of his screaming, dying mother. He utters no cry, but rises to his feet (impossible for any normal \nephilic{} newborn) and gazes at everyone with his cold, wicked eyes, gleaming with an unearthly incandescence. The sight of this un-\nephilic{}, naked, winged creature, black-skinned and covered in blood, seeing deep into everyone's soul with eyes revealing knowledge and intellect that should by right be beyond any infant, is chilling and morbid to behold, but also awesome. Most of the people are already blinded by their religion and its mind-controlling magic, so they see him only as a beautiful, magnificent, majestic saviour. 

(It is somewhat strange that he would rip his mother open, since he is smaller than a \nephilic{} child. But he does, because his birth and his very nature are so violent and cruel.)





\subsubsection{\Ilu{} dies}
\ps{\Ilu}{} body is only a bleeding ruin at this point, but she lives a few more moments. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Innocence sacrificed and heaven denied\\
  Iniquity divine\dash no repentance\dash over mankind\\
  Mind-raped, self-devoured, empty god-eyed\\
  Transgression coercive, Redemption never to be found

  Under the altar of cannibalism\\
  Man hast (thou) confessed the spiritual schism\\
  And without pride mourned the loss of freedom,\\
  Our blessed Lord have condemned you to martyrdom
  
  Let everything that hath breath praise the Lord, \\
  praise ye the Lord.
}

She sees her son and sees that he is alive and healthy. She feels the power and life force radiating out from him\dash power that he stole from her. He turns and meets her gaze. She recognizes the monstrously alien soul inside him, but he is still her son, her flesh and blood, so she loves him. He gives her a half-smile of gratitude. She is happy, knowing that she \hr{Ilu wants to conquer her sin}{conquered her sin in the end} and so fulfilled the quest she undertook. Her hard work, prayers and suffering have borne fruit and she has redeemed herself. She has served her father, her son, her kingdom and her gods. She is happy to die for this. And so she does, with a smile on her lips and her body torn to shreds. 

\lyricsbs{Monolith Deathcult}{Der Kriegmeister}{
  For the glory of Death and the crown of the horns.\\
  I murder like Manson when I cut out her womb.\\
  In the blood that she bled she lay drowned in her tomb.
  
  Suffocate, inhale death's breath. \\
  The crown of thorns tortures my head.\\
  Rape my wounds, my doomed bloodlet, \\
  receive my last caress.\\
  Demonclaws tore my skin, \\
  salicious women prove my sin.\\
  The seventh day had just begun, \\
  and soon your God will die.
}

\Ilu{} believes in the \banes{} and in \Thanatzil{} even with her dying breath. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  First Prayer
}{
  Lungs filled with embers and regurgitating boiling blood I say:\\
  Praise the Lord, praise,\\
  O servants of the Lord...\\
  We will sing a new song to thee,\\
  O God: a psaltery of thirteen Stations. \\
  May scoria bury Eden and blind the light of hope...
}





\subsubsection{Do more research}
I should do more research on Jesus, Horus, Mithras and other similar gods. 









\subsection{Rebels}
\target{Rebels against Semiza}
\target{Semiza's rebels}
Some of \ps{\Semiza}{} subjects are horrified by the evil of this new religion and the insanity of the king's plan. They begin to work against \Semiza. Their heroic deeds are essential in defeating the \banelords{} by \hr{Semiza fails}{interrupting \ps{\Thanatzil}{} resurrection}. 

Compare this to the rebellion in the \emph{Star Wars} movies.

They dislike the king's blasphemy against the old gods. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Shrovetide is violated by heathens. \\
  Nefarious splurges of sin. \\
  Persuasion is trembling with fever \\
  and became a mantra of occult tongues. \\
  Mankind enclasped Doom. \\
  He turned his back on God. \\
  Virtue became ultra-decadence. \\
  We are all libertines of the damned.
}





\subsubsection{A rebel Messiah}
Maybe the rebels have their own Messiah-figure, a representative of their old gods. 
Probably a woman. 
She founds the rebellion. 

She is secretly backed by \Vexstrasshin. 
Perhaps even possessed by her. 

Perhaps she is killed by \ps{\Semiza}{} people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  A Fidei Defensor arises, \\
  flogged and whipped from head to foot. \\
  The body cleansed by self-flagellation, \\
  supressed the lust of flesh and blood.
}









\subsection{The \resphan{} race}
%In the beginning, the entire \resphan{} power is 
\Thanatzil{} wields the power of the \banemessiah. But it is not his mission to save his people \emph{alone}. Rather, his purpose is to be the founder of a new race of \halfbane{} superbeings. 

\Semiza{} names them \resphain. 
This means \quo{superhuman} or something like that in their tongue. 





\subsection{\Resviel{} are designed}
\target{Origin of Resviel}
%\ps{\Semiza}{} sorcerers now collaborate with the \banelords{} and the fledgling \resphain{} to create a race of slaves: \Humans.
\Semiza-tachi realize that the process of having \nephilic{} women give birth to the \resphain{} is inefficient. 
The \nephilim{} are too weak. 

So \Semiza{} and the \banelords{} want to create a new race of female \resphain, to act as sex slaves and birth mothers for the \resphan{} race. 
They design the \resviel. 

The \resvil{} experiment succeeds beyond all expectations, and already in the design phase, when the first \resvil{} has yet to be born, it is clear that the \resviel{} are too good to use as sex slaves and mothers. 
This is part of the motivation for \hr{Origin of Humans}{creating \humans}.











\subsection{\ps{\Thanatzil}{} life}
\Thanatzil{} grows up. By the age of less than 10 he looks like a \human{} youth of maybe 18. 
(This is abnormal. \Resphain{} normally grow slower than \humans.) 
He is tall, almost as tall as a \nephilic{} man, but much slimmer. 

He has the \hr{Resphan vampirism}{vampiric appetites of a \resphan}. 
He eats the hearts of people sacrificed to him, to devour their souls. 
This may or may not be distasteful to him, but he does it. 
He probably doesn't enjoy it. He is the first \resphan, after all, and he sees clearly the horror writ on every (sane) face around him when he eats hearts or does other horrible things. 
(In later \resphan{} societies, every \resphan{} does it, so it is considered perfectly acceptable.)

He becomes sexually mature and has sex with \nephil{} women. 

For all his power, \Thanatzil{} is only a boy, and it is hard for him to bear the responsibility of the \banemessiah. 

He knows that he is a scion and representative of the \bane{} people, an incarnation of their legacy.

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  I have lived for millions of years. \\
  I am the day of yesterday. \\
  I know the day of tomorrow. \\
  The Alpha and Omega. \\
  I am eternal.
}

He is a guide and holy figure to his people. 

\lyricsxkcd{40}{
  In a dark and confusing world, \\
  you burn brightly. \\
  I never feel lost. 
}

He is distressed because he feels he has no power to control his own life. 

\citebandsong{BeyondTwilight:TheEdge}{Beyond Twilight}{Salem}{
  The darkness in the crystal expresses the inner fear.\\
  The light reveals the love she holds inside her. \\
  Reborn to lead a life controlled by the sorceress. \\
  She will know what she must do to come through. \\
  
  Her life on Earth lasted only for eight years.\\
  You can see she's frightened of the dark, \\
  but you'll never see her tears. 
  
  Nightmare in nowhere land.\\
  Exempting lying poetry. \\
  Missing the life she's owned.\\
  Slowly withering away.\\
  Too young to take a stand.\\ 
  There is no remedy. \\
  Her life being overthrown. \\
  Sunk in silent prayer. 
}




\subsubsection{Devoured souls}
He feels all the souls he has devoured, feels their pain, anguish and hate.

\lyricslimbonicart{A Venomous Kiss of Profane Grace}{
  The dead speaks to me\\
  from beyond the grave.\\
  That is why my conscience is.\\
  I`ve buried the dead alive.}

But he needs their power to fulfill his quest. 

\lyricslimbonicart{A Venomous Kiss of Profane Grace}{
  The blood of the child is pure now.\\
  In death it gives me life.\\
  The circle is complete.\\
  Begin another...
}





\subsubsection{He sees the evil that he represents}
\Thanatzil{} gazes into himself and sees the morbid evil of which he is the prophet, the messiah. 
He is horrified, but he keeps his faith and forces himself to repress doubts and fears. 

\lyricslimbonicart{Dynasty of Death}{
  Dungeon darkness in violent fire.\\
  Transfix the soul with Hell's desire.\\
  Where myriad's of lives are laid in ruins, \\
  dormant in the ashes of all terrestrial dreams.
  
  The dynasty of death.
}

He angsts over his evil. 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  A passion for my rage, with my sights of darkness.\\
  The atrocities at hand I must bare/bear. \\
  Entangled in a state so cold, so dormant. \\
  My sickened rageful state, my hateful lair. 
  
  Saturated in dejection. 
}

But he must. 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  Hardened by this reality. \\
  Sights of vengeance ever so clear. \\
  Compelled to rejuvenate this world of hate \\
  into a mass of chaos and fear. 
  
  Saturated in dejection. 
}

He eats souls and grows strong. 
This strength allows him to send his soul wandering through the Cosmos. 
He contacts cosmic gods and his \bane{} fathers. 
He gains wisdom.  

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  The sickening things that I witness. \\
  I derive distinct visions from\\
  the sickening throughts that they confess. \\
  Hatred at its purest form. 
}

He forces himself to accept it. 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  So compelled to what I've witnessed, \\
  mesmerizing, so enticing,\\
  I revel in their grief. \\
  I confess, my vision is my religion. 
}

He has a split personality of sorts, being part \nephil{} and part \bane. 

\lyricsbs{Hate Eternal}{Two Demons}{
  I am duality. A being so consumed with 
  the darkness inside of me.\\
  Through this pain I must endure 
  these beings that still haunt me.
  
  I am adversity. Within the sunder of 
  the essence of my very soul.\\
  In this rage I shall remain, 
  these creatures that become me. 
  
  Come forth and purge yourself for what you are.\\
  Reveal thyself and become what you will. 
  
  I am diversity. So weary of the angst, 
  so weary of what I have become. \\
  Through this dread I will retain, 
  this penance that still haunts me.
}

He is unsure whether what he is doing is right. 

\lyricsbs{Emperor}{Grey}{
  desperately I seize tomorrow, all out of my reach\\
  that is what I learned, this is what I teach\\
  corruption seems to flourish while promises decay\\
  where lights are dim and shades of black are grey
}

He had doubts. 
He was allegedly an incarnation of the mighty \bane-god, older and greater and mightier even than the \dragons. 
But often he did not feel like a god. 

\citebandsong{DeathspellOmega:Kenose}{%
  DeathspellOmega
}{
  \Kenose
}{
  And He is before all things, and in Him all things consist\\
  Triune God, morphed into a Being of apparent theanthropic nature\\
  Deprived of the Light of Splendor\\
  Dost thou still stand in undiminished Majesty\\
  After the exinanition of divine attributes\\
  The face of profound fire gone astray,\\
  Exhaling austerities in concealed, divine radiance?
}





\subsubsection{\Semiza-tachi convince \Thanatzil}
\Thanatzil{} has plenty of doubts and fears. 
\Semiza{} and his ilk do all they can to convince him that he is doing the right thing and must continue. 

\lyricsbs{Hate Eternal}{Servants of the Gods}{
  Heed not for our sins,\\
  for our sins hath no path of impurities.\\
  For it is I who will conquer \\
  this plane of existence.
  
  Heed not for our scrolls,\\
  for our text hath no path of deviation.\\
  For it is I who will transcend to \\
  this plane of existence.
}

At the same time, \Semiza{} is thinking about his own dream. 

\lyricsbs{Hate Eternal}{Servants of the Gods}{
  I shall exact my revenge, \\
  for I am the top of the hierarchy.\\
  Heir to a tradition of unification.\\
  For I am the mother and the father\\
  and the heart of our domain.\\
  I am the wiseman.\\
  I am a thing of evil.
}









\subsection{\Humans{} are designed}
\target{Origin of Humans}
\ps{\Semiza}{} sorcerers now collaborate with the \banelords{} to create a race of slaves: 
\Humans.

Note that first \humans{} were created \emph{before} the \resphain{} (bar \Thanatzil). 





\subsubsection{Purpose}
%The \human{} men are created because the \nephilim{} and \resphain{} don't want to work and want some slaves to do their dirty, menial work for them. 
The \human{} men are created to serve as a race of worker slaves, beneath the \resphain{} and more manageable than the somewhat savage \nephilim. 

The \human{} women are created to serve the \resphain{}\dash and, to a lesser extent, the \human{} men\dash as sex slaves and mothers. Originally, \hr{Origin of Resviel}{the \resviel{} were designed to fill this role}, but they proved useful for far more than that, and were promoted, so the \human{} women were designed to fill the vacancy.

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Born with the ability of begetting\\
  Only but One gift were she granted\\
  To excrete a new humanity unwanted\\
  Reluctantly she\dash woman\dash \\
  loves the god of a creation within
}





\subsubsection{How they were created}
The first \humans{} are created by letting \Thanatzil{} have sex with and impregnate some \nephilic{} women, after both mother and father have been annointed with special spells. 
So the \humans{} are half \nephil, half \resphan\dash in other words, three quarter \nephil{} and one quarter \bane. 





\subsubsection{The experiment fails}
\target{Humans fail}
The preliminary \human{} experiments are considered failures. 
The alpha-test \humans{} were supposed to have been killed, but after \hr{Thanatzil fails}{\Thanatzil{} was killed}, the \humans{} escaped into the wild and bred true. 
Later they would be rediscovered and adopted by the \resphain. 









\subsection{\Semiza{} names the \banes}
It was \Semiza{} who named the \banelords, including \Daggerrain, and it was he who coined the term \quo{\bane} for their race, since he envisioned them as the bane of his hated enemies, the \dragons. Not until a late time does he realize that they are the same creatures that fought the \dragons{} thousands of years ago. The \dragons{} have their own names for the \banes: The Alien Ones, the Sinister Ones, the Spawn of Darkness. 









\subsection{\Thanatzil{} is tempted by a \dragon}
At least one \dragon{} suspects that this whole \Thanatzil-business is \trope{SeriousBusiness}{Serious Business}. His/her fellow \dragons{} do not believe him, so he sneaks into \ps{\Semiza}{} city in disguise. Maybe even in the form of a serpent. 

He seeks out \Thanatzil{} in dreams and tries to tempt him to abandon his people. He doesn't quite understand what \Thanatzil{} is or what he wants. (Maybe the \bane{} power is masked so that the \dragons{} cannot recognize it. Or maybe this \dragon{} is not old enough to remember the \firstbanewar.) But he tempts the young \resphan{} with promises of power and things. 

\Thanatzil{} goes out into a desert or the like to confront the tempter. Here he finally banishes the \dragon. 

\Thanatzil: \ta{I know what thou art. Begone! Thou canst not tempt me, not canst thou thwart me.}

The \dragon{} then conspires with the \hr{Semiza's rebels}{rebels} to interrupt \hr{Thanatzil's resurrection}{\ps{\Thanatzil}{} resurrection}. 















\section{\Thanatzil{} and his Destiny}
\subsection{\Thanatzil{} must die}
\target{Thanatzil must die}
In the beginning, the entire \resphan{} power is incarnated in \Thanatzil. 
In order to spawn the \resphan{} people, \Thanatzil must:

\begin{enumerate}
%   \item 
%     Grow to adulthood, or at least \hr{Resphan sexual maturity}{sexual maturity}.
  \item
    Impregnate a number of women with his seed. 
    \subitem
      Are these women \nephilim{} or \humans{}? 
      Probably \nephilim, since it takes at least like 12-15 years to grow a \human{} woman old enough to bear children, and \Thanatzil{} is not meant to live that long.
    \subitem
      How many women? 
      Perhaps some magical number, like 12 or 21 or 40.
  \item 
    Undergo a dark and terrible ritual in which he will die and be resurrected. 
    \subitem
      His death will release the Messiah power within him. 
      It will fly free, reach out to the \bane{} souls incarcerated in the depths of \Nyx, free these souls and allow them to pass into \Miith{}, where they can merge with the souls of \nephilim{}\dash the sons and daughters of \Thanatzil \dash and incarnate as \resphain. 
      %power and distribute it among his his sons and daughters, allowing them to be born. 
    \subitem
      His resurrection is necessary, because \Thanatzil{} is an embodiment of the connection between \Miith{} and \Nyx{} (just like how \hr{Daggerrain is the gate}{\Daggerrain{} is the key to the pathway between \Nyx{} and \Erebos}). 
      If \Thanatzil{} dies permanently, then so does the contact with \Daggerrain. 
\end{enumerate}

The resemblance to Jesus should be obvious. 

All the mothers are impregnated in one day/night\dash spells are used to keep \ps{\Thanatzil}{} dick going all that time. 
The occult rituals involved in the spawning of the \resphain{} make sure to keep all the mothers synchronized, so that all the births will happen on the same day. 

\Thanatzil{} thinks of \Erebos: 

\lyricsbs{Emperor}{The Prophet}{
  \quo{%
    It is the place where blood and soil\\
    lie beyond the boundaries of the sun}
}

He thinks of his own role. 

\lyricsbs{Emperor}{The Prophet}{
  \quo{%
    and I am its prophet \\
    I cast the shadow\\
    I absorb the light}
  
  \quo{%
    I am the prophet\\
    I bear witness\\
    I absorb\\
    I cry}
    
  \quo{%
    As I die, I shall burst wide open\\
    As I die, I shall release the apocalypse\\
    My prophecy\\
    Thus, I hold on to faith\\
    Thus, I keep the hope\\
    That it will prosper \\
    and devour}
}





\subsubsection{Mothers of the \resphan}
\target{Mothers of the Resphain}
A number of \nephilic{} women are impregnated by the young \Thanatzil{} in the months up to the sacrifice ritual. 
They are meant to stay pregnant through the ritual. 
(If they were to give birth prematurely, the children would die.)
The ritual and \ps{\Thanatzil} sacrifice will release the \bane{} energy that will empower the infants growing in their wombs so that they may live and be born as healthy \resphain{} and \resviel. 

How many mothers are there? 
Quite a lot. 
Perhaps 100. 





\subsubsection{Some mothers are hidden}
Most of the mothers attended the sacrificial ritual. 
But a few of them were hidden away. 
This was a special security precaution by \Daggerrain. 
He knew that something might go wrong at the ritual and in that case he wanted to have a few mothers left as a backup plan. 

But \Vexstrasshin{} was clever and sniffed out these mothers and had them killed. 
The \nephilic{} rebels she coerced into killing the mothers were not happy about killing pregnant and defenseless women, but they did their duty. 









\subsection{\Thanatzil{} saves the outcasts}
\Thanatzil{} summons all sorts of sick people, madmen and outcasts to him. 
He promises them redemption by the \bane{} gods, offers to give their lives meaning. 

This \quo{meaning} is to be consumed so that their souls may feed the summoning ritual. 
The \quo{redemption} is that their useless lives will be over and their deaths will serve a useful purpose (so their deaths will be more valuable than their lives ever were). 

\Thanatzil{} does not want to do this, because it feels like betrayal and dishonesty. 
But \Semiza{} convinces him that he must. 
\Semiza{} tells him of the many sacrifices he has made himself. 
\ta{Yes, it will be a painful decision. 
    But it is the duty of a leader to suffer for his people. 
    You must do the right thing, \Thanatzil.}

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Pagan Messiah\dash the almighty fiend. \\
  Abode of the damned, defiled, unclean. 
  
  Spiritual holocaust. 
  
  Plead for forgiveness. \\
  You can't resist its temptation. }

The damned die. 

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Spiralling permanence. \\
  Merciless decadence. \\
  Unethical banishment. \\
  Fall before that which summons you.
  
  Imminent dormancy. \\
  Heinous atrocities.\\
  Demons that beckon me.\\
  That which to escape is to die. 
  
  Spiritual holocaust. 
}









\subsection{The Resurrection Day}
\target{Thanatzil's resurrection}
\target{Resphain lose contact with Banelords}
The great day draws near when \Thanatzil{} will die and rise again, and with his resurrection the \resphain{} will be born. 

%I need to make up a cool name for this day. 

All the \hr{Mothers of the Resphain}{\resphan{} mothers} are gathered, as are a lot of soldiers and priests. 
The mothers are to \quo{inherit} the energy he will release with his death. 

The ritual is prepared. 

\citebandsong{DeathspellOmega:Kenose}{%
  DeathspellOmega
}{
  \Kenose
}{
  Kenosis, O' theory of great peril!\\
  Blinded, sanguineous eyes and with a trembling hand,\\
  A frail androgynous being holds the perilous doctrinal balance,\\
  Robed in a maculated garment spattered with the sordid blood\\
  Of the Flagellation, of the lacerations and fierce wounds\\
  Carved by royal attributes, of the crimson spurts\\
  Dripping without end,\\
  As was celebrated the High Mass of the Comforter
  
  Kenosis, O' theory of great peril!\\
  Rob God of any attribute and fill the shattering universe\\
  With the pestilent scent of putrefaction \\
  and the glorious cloud of death,\\
  For steadfast, at any cost, He must be\\
  Solely the incarnate Word \\
  proclaimed by all the prophets and apostles\\
  Would have, in dying, an infinite value,\\
  Sufficient to atone, by His astonishing work,\\
  For the Sins of the world
}

The ritual commences. Compare it to the Babylonian myth of \quo{The Descent of Ishtar}. And the text \quo{Of the Sleep of Ishtar}, a fictional reinterpretation of aforementioned myth, found in \simonnecronomicon. 





\subsubsection{\Thanatzil{} dies}
\target{Thanatzil dies}
\Thanatzil{} prepares his sacrifice. 

\lyricsbs{Emperor}{The Majesty of the Night Sky}{
  Too long I have suffered the desert sands of time. \\
  But as I drown in darkness it will release the sign. \\
  My soul will leave this mortal coil of flesh and earthly life, \\
  to fly into the mist of night, into the nightside eclipse, \\
  and experience existence on the other side. 
  
  As a stone of scorching enthusiasm \\
  I refract the reflecting surface of this unfathomable sea. \\
  Growing circles of grief and pain slides across the land \\
  as an omen of the horror yet to come. 
  
  The strength of a thousand fire-breathing demons \\
  breed in my infernal, sinking soul. \\
  And as I reach the surface once again \\
  these powers are under my control. \\
  Now I am one with the night sky majesty.
}

\Thanatzil{} dies. 

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  The Abyss yawns wide... Claws sharpened on the dead.\\
  The Abyss yawns wide... Ensanguined fangs agleam.
  
  Great shadow, awaken and eclipse the suns of a thousand worlds...\\
  Slumbering 'neath these crimson vaults, \\
  behold the majesty of the Outer Darkness!\\
  Praise the Z'xulth!
  
  Fell Worm of the Black Galaxy, \\
  awaken and descend without pity upon the Tellurian sphere!\\
  Destroy the flaccid priests of the newborn usurper faiths.\\
  Sweep away the thralls of the cruciform stave!\\
  Crush the lackeys of the corrupted hexagram!\\
  Devour the slaves of the eastern crescent!\\
  Crush them, grind them, slay them all!\\
  Plague-blessed, flay them alive!
  
  Now, behold in terror what waits beneath the crimson vaults of Cydonia...}
  
\lyricslimbonicart{A Venomous Kiss of Profane Grace}{
  Silent screams of suffering.\\
  I stand in flames of torturing.\\
  Goddess of flesh hunger and desire,\\
  grant me wings of hellish fire.\\
  Know that all my creations spring\\
  from blood on the cross in blasphemy.\\
  I am death, the creator of sin.\\
  and of the pure I am the wind.}

\lyricslimbonicart{The Dark Paranormal Calling}{
  A serpent in my soul.
  
  In midnight's aura as a ghostly fire.\\
  The child prodigy of abysmal desire.\\
  As the deathlike silence pervades, \\
  the incubus now invades.\\
  Show yourself, unclean spirit. \\
  Tonight I give thy shadow life.\\
  Rise with me in darkest blessing.\\
  Thine demon force I feel possessing.\\
  A holotropic mind and spectral eyes divine.\\
  Through the shallow haze as the sky turns red\\
  I walk and dream among the dead.
}

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Spiralling permanence. \\
  Merciless decadence. \\
  Unethical banishment. \\
  Fall before that which summons you.
  
  Imminent dormancy. \\
  Heinous atrocities.\\
  Demons that beckon me.\\
  That which to escape is to die. 
  
  Spiritual holocaust. 
}

\lyricslimbonicart{A Cosmic Funeral of Memories}{
  The night belongs to the predator\\
  to the one who dares crossing the threshold,\\
  the axis of dreams and wonders and black miracles.\\
  I see my self in the mirror of your eyes:\\
  A dark star on the celestial beautiful midnight sky.\\
  Release the inner radiance of what you have become.\\
  Brighten the night with your sacrifice.
  
  I have returned to life to speak of clairvoyance.\\
  I am the voice from the grave land of memories.\\
  Life can be only an illusion, and death a temptation,\\
  a final destiny.
}





\subsubsection{Rebels strike}
But then disaster strikes. The \hr{Rebels against Semiza}{rebels} attack and interrupt the ritual. 

\Vexstrasshin{} hopes to kill all the mothers. 





\subsubsection{A rebel sacrifices himself}
The rebels are almost stopped. Then their \draconian{} ally speaks to them. She cannot enter the city herself\dash\Semiza{} and the \bane{} magic has blocked her out\dash so she must act through her \nephilic{} allies. 

One hero among the rebels sacrifices himself to allow the \dragon{} to possess his body and channel her magic through him. This is a dangerous, experimental process and will permanently destroy both his body and soul. 

\lyricsbalsagoth{
    The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire 
    - Part III: 
    Cry Havoc for Glory, and the Annihilation of the Titans of Chaos
}{
  [THE ECHOES OF THE IMMORTAL:]\\
  Hearken, noble King of Hyperborea.\\
  ...\\
  To utterly destroy the Dark Liege of Chaos, you must join your essence with mine... we must fuse our life-forces and become one so that my full power may be unleashed against Angsaar once more. \\
  But this final deed demands the most severe of tolls, o' noble monarch...\\
  To become as one with the immortal essence of the Shadow-Sword is to sacrifice forever your own mortality, and to forsake eternally the world of man. \\
  Are you prepared to pay this price, King of Hyperborea?
  
  [THE KING:]\\
  To preserve the sovereignty of my realm and safeguard my people from the 
  forces of darkness? Aye! For my kingship demands no less a commitment!\\
  So be it... let this final deed be done!
}

\Thanatzil{} still hangs around as a ghost with some power. The \bane{} power flows into him, and he becomes manic.

\lyricsbalsagoth{
    The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire 
    - Part III: 
    Cry Havoc for Glory, and the Annihilation of the Titans of Chaos
}{
[LORD ANGSAAR:]\\
  (No... my eternal nemesis, you will not thwart me! Abominations rise! 
  Destroy these mortals who vex me as the buzzing of gnats vexes a titan!
  Drag their impudent souls to the abyss!)
  
  [THE WARRIORS OF HYPERBOREA:]\\
  (Havoc is the cry! Come, fiends of the nether-void...\\
  face righteous pattern-welded death!)
  
  [LORD ANGSAAR:]\\
  Abominations rise! \\
  Souls to the abyss! 
  
  [THE WARRIORS OF HYPERBOREA:]\\
  Havoc is the cry! \\
  Pattern-welded death! 
  
  [LORD ANGSAAR:]\\
  (Praise Chaos! By the crystal heart of Mera I shall stand deified!)
  
  [THE WARRIORS OF HYPERBOREA:]\\
  (Glory eternal! For our King and sacred Hyperborea!)
}

\Thanatzil{} is consumed by hatred: 
All he wanted was to help his people. 
And they stab him in the back! 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  I now become my saving grace, \\
  exiling all this human waste.\\
  I deny your emotions, you perjurers. \\
  I deny your falsifications, you perjurers.
}

\Thanatzil{} grows more and more manic. 

\lyricsbalsagoth{
    The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire 
    - Part III: 
    Cry Havoc for Glory, and the Annihilation of the Titans of Chaos
}{
[ANGSAAR:]
  (The circle closes... you cannot resist the unparalleled might of Chaos 
  and the exquisite majesty of the Z'xulth! I shall unleash all the terrors of 
  the Outer Darkness against thee! Behold the true extent of my power...) 
  
  My flesh is a shrine wherein all demons dwell!
  
  Bae'an, Zurra, Uldorr, Neoloth. \\
  E'manh, Phaegus, Nyaszar, Merlech.
}





\subsubsection{Survivors sucked into \Nyx}
\target{Semiza fails}
\target{Thanatzil fails}
\Thanatzil{} never got resurrected, so he died permanently. 
And worse, since \hr{Thanatzil is the gate}{\Thanatzil{} was the gate}, this meant that the portal to \Nyx{} was closed and \Daggerrain{} was once again shut out. 

At the last minute, \Daggerrain{} realized what was happening. 
He acted swiftly, while there was still a tenuous conduit from \Erebos/\Nyx{} to \Tembrae{} (the conduit which \ps{\Thanatzil} death had opened). 
He seized some of the threads of the \hr{Shroud of Girigor}{Shroud of \Girigor} and used them to create a pocket of Realm-stuff.
He wrapped this pocket around the surviving mothers and soldiers as well as \Semiza{} and \Eshayzal. 
He tossed this pocket into \Nyx{}. 
With the Shrouding they were now invisible and hidden from \Vexstrasshin{} and her ilk. 

\Daggerrain{} also laid out a smokescreen in the form of a plausible-looking implosion that destroyed the temple and laid waste to much of the city. 
That way it looked as if everyone was dead and the plan thwarted. 





\subsubsection{\Vexstrasshin{} dies}
\target{Vexstrasshin dies}
\Vexstrasshin{} is killed by \ps{\Daggerrain} treachery, so she cannot go out and tell the tale of what happened here. 
During the death-and-resurrection ritual, while the portal is open, \Daggerrain{} reaches through with as much power as he can muster and attacks \Vexstrasshin. 
She is unprepared for the power of this attack. 
She fights back with all her might and wiles, but \Daggerrain{} is too powerful. 
He slays her and destroys her soul. 















\section{Aftermath}









\subsection{Rebels celebrate}
The \nephilic{} rebels were happy.
They had lost much: 
Several heroes, their mentor \Vexstrasshin{}, tons of innocent lives and much of their city. 

But the evil plan had been stopped. 
They had saved the world, they thought. 

And the destruction was not so bad. 
They had seen its like before at the hands of the \dragons. 
They knew how to cope with it and rebuild. 









\subsection{\Humans}
Plenty of \humans{} were born by this time. 
They were still children, and many died, but enough survived. 
\hr{Humans are fertile}{\Humans{} are fertile}, more so than the \nephilim, so they bred and multiplied quickly. 
They could interbreed with \nephilim, but the \human{} genes were dominant, so they spread even more quickly. 

The \dragons{} wondered a bit when they noticed this new race of pygmy \nephilim{} that appeared seemingly overnight. 
But they paid it little heed.









\subsection{Survivors in \Nyx}
Many of the mothers and soldiers died, but enough survived and were tossed into \Nyx. 
They found themselves stranded in a strange and inhospitable world. 
They had no idea how to get back to their own world, so they could only do their best to fend for themselves and survive in this new, frightening world of towering spires and bottomless abysses. 





\subsubsection{The Shroud of \Nyx}
\target{Shroud of Nyx}
\Daggerrain{} recycled threads and techniques from the \hr{Shroud of Girigor}{Shroud of \Girigor} and wove another Shroud around the part of \Nyx{} where the survivors had landed, thus shielding them from prying \draconian{} eyes. 
But \Daggerrain{} had little time to do this, since he was rapidly losing his conduit, so he could only manage a shoddy hack-job. 

The Shroud worked, but with side-effects: 
It harmed the mind, causing confusion and amnesia. 
So the poor surviving \nephilim{} could not remember all that had happened. 
That was one of the reasons why \Merkyrah{} ended up inventing \hr{Merkyran myths}{so many false myths}. 










\subsection{\Semiza}
\target{Semiza flung away}
\Semiza{} and a few of his cohorts remembered, but they were imprisoned, buried alive when his temple/palace collapsed around him. 

\Daggerrain{} realized that \Semiza{} could still be useful. 
So when the nascent \resphain{} were sucked away into \Nyx{}, \Daggerrain{} grabbed \Semiza, and, using the last of his hold on \Tembrae, flung him (and a pocket of the world around him) into \Nyx{} after them. 

Unfortunately \Daggerrain{} was quickly losing his conduit to \Tembrae, so his aim was poor. 
\Semiza{} ended up buried deep in a cellar in a building in \Nyx. 
(Remember, the endless city of \Nyx{} existed already then. 
 Remember also that \Nyx{} has no surface, only tall buildings.) 


At first \Semiza{} thought everything was lost and that he was going to die. 
He cursed and raged at everyone: 
The \dragons, the rebels, the \banes. 
But even when he was buried under tons and tons of stone, sand and earth, he did not die. 
He realized that he could still feel the faint, cold hand of \Daggerrain{}, channelling power into him and keeping him alive. 

\begin{prose}
  \tho{\ps{\Daggerrain} power is not broken.
    Our covenant still holds. 
    He promised me immortality. 
    He promised me that I would live to see the \dragons{} destroyed, and then I would rule. 
    He is staying true to his word. 
    I will not die.}
\end{prose}

Gradually he became aware of other feelings beside his pain. 
He could dimly feel the \resphain. 
He had a link to them since they were all his descendants. 
He could tell they still lived. 

At the very end of the book, \Semiza{} lay thinking: 
\begin{prose}
  \tho{We have lost much, but not everything. 
    Some of the seeds we have planted have taken root.
    Brave Ilu. 
    Brave \Thanatzil. 
    Your sacrifices were not in vain. 
    
    The \resphain{} live!}
\end{prose}


There he lay for thousands of years, unable to move but immortal, and descending further into madness. 
As \Daggerrain{} promised, he gained immortality (by sucking energy from the Heart through \Nyx, and maybe a bit from \Erebos). 
But he lies a thousand years under the earth, eating mud and worms. 

Perhaps \Eshayzal{} is also there, \hr{Eshayzal is a Lich}{as a \Lich}. 























\chapter{\MerkyrahBook}
This book takes place in \hr{Merkyrah}{\Merkyrah}. 















\section{The Truth}
A few \resphain{} discover the truth of their origin.









\subsection{Prologue: \Semiza}
The book opens with \Semiza, who is lying in the ground. 
Suffering, alone, decaying and unable to move. 
He sends out his mournful and patient call to the \resphain{} in their cities above him. 
His children. 
(After all, all \resphain{} descend from \Thanatzil, who is \ps{\Semiza}{} grandson.)

Compare to the titular \quo{call} in \authorbook{\HPLovecraft}{The Call of Cthulhu}. 









\subsection{Main conflicts}
There are a number of main conflicts in this book: 

\begin{enumerate}
  \item 
    The \hr{Umbra menace}{\umbra{} menace}, which was slowly killing the \resphain. 
    It was the greatest threat to their people, and governed much of their lives. 
    And \hr{Umbra menace growing}{it was growing}. 
  \item 
    The \Merkyran{} religion.
    For some it was happiness and peace and good. 
    But for others it was stagnation, oppression, asceticism, denial of all that was life. 
    Some said \emph{it} was slowly killing the \resphain.
    Some even said the religion was the reason why the \umbrae{} hunted them. 
  \item 
    Hunger. 
    The \hr{Merkyran hunters}{monsters that the \resphain{} hunt were becoming scarcer}. 
    This caused hunger and malnutrition. 
\end{enumerate}





\subsubsection{The Awakening}
\target{Awakening}
\index{Awakening}
The \resphan{} rebellion was also known as the Awakening.
The rebels believed they were Awakening from a dream, a daze, a stupour, and were now, for the first time, clear-sighted enough to understand their true nature. 










\subsection{Malcontents}
Many are discontent with life in \Merkyrah. 
They include \Kezrabal, \Gevural, \Zachirah{} and others. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Sola Fide
}{
  Where is the book of truth, or the inheritance that'd enlighten me?\\
  No voice shall answer to my probe and throbbing prayers...\\
  But certainty and madness write in ashen letters
}










\subsection{The Delving}
\target{Delving}
\index{\Delving}
\target{Resphan rebels}
After thousands of years, a few \resphain, led by \Damiarch, went on an exploring expedition. 
The motivating factors for the mission included: 

\begin{itemize}
  \item 
    Simple hunting. 
    The \resphain{} \hr{Merkyran hunters}{hunter monsters, and hunters were highly respected}. 
  \item 
    The \hr{Merkyrans fear Umbrae}{\umbra{} menace}, which was \hr{Umbra menace growing}{growing}. 
    They hoped to learn more about what the \umbrae{} were and how they could combat them. 
\end{itemize}

For astrological reasons, the \umbra{} threat was especially bad this particular year. 
\Damiarch-tachi found some traces, full of \Erebos-aligned energies, that smelled kind of like the \umbrae{} (who are also \Erebean). 
They suspected a clue, so they followed these trails to their source.
This brought them deep underground. 
As it turns out, these trails were created by \Semiza, who lay down in the earth and tried to attact some \resphain{} to him. 

This voyage would later come to be known as \emph{the \Delving}

The brave explorers (the \quo{\Delvers}) included: 

\begin{itemize}
  \item \Damiarch.
  \item \Gevural.
  \item \Zachirah.
  \item \Ramiel.
  \item \Shiaraid.
  \item 6-8 more. Maybe \Sithiyacaan.
\end{itemize}

Among them are several who would later become the dreaded \satharioth, including \Gevural{} (\Azraid{}) and Ramiel. 

\Gevural{} is one of the senior members, but the leader is his brother, \Damiarch. Ramiel and the rest are younger and look up to \Damiarch{} and \Gevural{} as great leaders. 

While exploring some underground ruins they discover a mystic, evil garden of twisted, distorted plants. 
Compare to the cover art of \bandalbum{Dimmu Borgir}{Godless Savage Garden}. 





\subsubsection{Some look for meaning}
Some of the explorers, already in the early stages of the Delving, were disillusioned and looked for a new meaning to it all. 
They felt their religion was sad and pointless. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Called by the Fire}{
  The sky is clouded and grey like a mirror.\\
  Dreams of celestial bliss buried deep.\\
  An invisible web of whispers\\
  spread out over dead-end streets.\\
  Silently blessing the virtue of sleep.
}

Some were sure the religion was a lie, and that there was something more out there to be found. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Called by the Fire}{
  Every day I grow more immune to social sedatives.\\
  Every day the web is more transparent.\\
  United in fear and the comfort of reason.\\
  Illusions that we are all peers.\\
  Walking the stairs I am ever more awake.
}

There was a darker truth out there. 
They could feel it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Called by the Fire}{
  The black cloud is beneath me,\\
  and I laugh.
}

They hated what they saw as the religion's hypocrisy and pettiness. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Citizen}{
  Citizen! Whence came your voice, your right to speak?\\
  Is there a purpose to your tongue and gnawing teeth?\\
  I ask thee; how deep and hollow is your mouth?\\
  What lie is too decayed for you to stomach?
  
  With humility and obedience\\
  you pride yourself.\\
  Evasive and lukewarm\\
  until the end.
}

Some just wanted to rebel, because they were sick of it all.

\citebandsong{DeathspellOmega:Kenose}{%
  DeathspellOmega
}{
  \Kenose
}{
  The fruit that is forbidden\\
  Holds the greatest potential for providing infinite knowledge\\
  Spiritual Incest and the defilement \\
  of the temple of the Holy Spirit\\
  Ritualized and Immanent...\\
  The pursuit of perversity, is it not but a mask\\
  On the search for meaning and knowledge?\\
  The purest of all Holocausts shall be perpetrated\\
  By a loving hand, never knowing if it provided felicity\\
  Or the vilest of everlasting torments\\
  No man can see Me and live!
}





\subsubsection{Ramiel and \Shiaraid}
Ramiel and \Shiaraid{} are the same age. 
They are close friends. 
They are major influences on each other's lives. 

Already at this time, Ramiel and \Shiaraid{} were secret lovers. 
\quo{Secret} from society at large, that is. 
Having sex out of sanctioned marriage was a taboo. 
But their fathers, who were both free thinkers (or, at least, pragmatists), knew about their affair and accepted it. 
\Zachirah{} even encouraged it.
\Nathrach{} remained mostly stoic. 

The two should have a \quo{secret} sex scene at the beginning of the book. 

At this point, they just had normal sex, no sadomasochism involved. 
It was not until after \Semiza{} that he \hr{Ramiel develops sadism}{developed his sadism} and she \hr{Shiaraid develops sadomasochism}{developed her sadomasochism}. 









\subsection{\ps{\Semiza}{} garden}
\subsubsection{The garden}
They find this suck, twisted, evil garden. 

\lyricsdimmuborgir{The Promised Future Aeons}{
  The faces you saw in the withering garden.\\
  I witnessed the flickering, made to look like stone.\\
  Quivering like little figures lost in broken flames.\\
  Never to forget again the names carved in horrid flesh.
}





\subsubsection{They find \Semiza}
\target{Explorers meet Semiza}
Following the trail they stumbled upon in the garden, they somehow found and awakened the imprisoned \hr{Semiza}{\Semiza}. 
He beckoned them to him. 

\Semiza{} had been able to listen to the \resphain{} telepathically, so he understood their tongue well enough to make himself understood. 

\lyricsbs{Vital Remains}{Sanctity In Blasphemous Ruin}{
  Welcome to my dwellings of unholiness. \\
  Upheld, the blackest dreams, oh, infernal bliss. \\
  Your tabernacles pleasured and continuance \\
  lies in the innocents existence. 
  
  Down through the bowels of unholiness. \\
  Upheld, the blackest deeds, oh, infernal bliss. \\
  I am he who is malevolence, \\
  raping the weary so diminished. \\
  Come, mighty Babalon, \\
  mother of Abominations. \\
  Grant me the flesh, grant me the fear, \\
  grant me sanctity of ruin. 
}

They communicated with \Semiza. 
They felt his wisdom and \hr{Madness}{madness} like a palpable force. 

He showed them visions and revelations. 
He told them that everything they believed was a lie. 

\lyricsdimmuborgir{Grotesquery Conceiled Within Measureless Magic}{
  Poor misguided fool...\\
  It is not God you are talking to.\\
  I am not impostrous, hiding behind perly walls.\\
  However, I am still yet to be found, known.\\
  I shall guide you on your midnight-ride as the sun fades black.\\
  And beyond your grotesque imagination,\\
  my name will be revealed... \\
  The blood of Christ can't heal your wounds.\
  Give me all of yours, and I'll give you mine...
}

Terrible images from his own time, of death, ruin and the fall of his kingdom. 
And memories of \Erebos{} and the \banes. 

\lyricslimbonicart{Seven Doors of Death}{
  Woe be unto him who ventures near.\\
  without knowledge.\\
  Ultra violent scenarios.\\
  Anguish crying.\\
  Images from the beyond.\\
  Nightmares never dying.
  
  Within the realm of desperation,\\
  seeking lexis of illumination.\\
  Psychological terror, permanent psychosis.\\
  A sculpture in the land of decay.\\
  Woe be unto him who opens\\
  the seven dreaded gateways.
  
  Asylum of neurotic minds.\\
  Devour all consciousness.\\
  Insanity is there to find.\\
  Dominion of darkness.
}

He tells them about their origins, how they were created by the dreadful \banes. 
He awakens their memories, repressed and buried deep down in their minds.

\lyricslimbonicart{Seven Doors of Death}{
  Walk and dream amongst the dead.\\
  Anger and pain resurrected.\\
  Necropolis manifestation.\\
  Supernatural obsession.\\
  Phantasmagorical state of mind.\\
  Trapped in another dimension of time.\\
  In a paradise lost.\\
  Endless horizon of wilderness and holocaust.
}

Now, the \resphain{} did have vague, mostly repressed memories of having once had connections to the \banes{} in their infant past. 
They did not know the \banesz{} identity, but they could recognize the feeling of them. 
(Do all \resphain{} have this memory through some kind of racial memory, or is it only the oldest generations that remember it?) 
Some of them tried to deny \ps{\Semiza}{} tale, but others could not deny that it not only rang true, but also suddenly made a lot of pieces of the puzzle of their repressed memory and past come together.

Perhaps they get their hands on \ps{\Semiza}{} \hr{Book of Erebos}{\BookofErebos}. 

They learn that they are created by the \banes{} to carry on their culture and soul, the very legacy of \Erebos. 
And they learn of the dark greatness that is rightly theirs. 

\lyricsbs{Vital Remains}{Societe des Luciferiens}{
  In the midst of Our black paradise \\
  shall undefiled wisdom rule. \\
  The rites of Christ are but rites of Death, \\
  now receive the truth.
}





\subsubsection{\Semiza{} shows them tailored visions}
\target{Semiza shows tailored visions}
Perhaps \Semiza{} reads each of their minds and shows each of them a personally tailored vision that is meant to shape their life. 
Remember, \Semiza{} is a genius. 

\begin{enumerate}
  \item 
    Ramiel was shown \hr{Ramiel is nothing}{his own insignificance}. 
  \item 
    \Shiaraid{} was taught \hr{Shiaraid develops sadomasochism}{that she was really a sadomasochist}. 
\end{enumerate}



\lyricsbs{Hate Eternal}{Behold Judas}{
  I bestow upon you my contempt, Master of the Arcane.\\
  I bestow upon you apathy, Master of the Labyrinth.\\
  I bestow upon you malice, Master of the Kingdom.\\
  I bestow upon you savagery, Master of the Revered Palace.
}









\subsection{Their reaction to the truth}
Some of them are dismayed by this and feel reinforced in their principles of sin, shame and atonement. 
After all, this confirms that their myths are true: 
They were created by evil and have evil in their blood, and they must strictly discipline themselves to suppress and overcome this. 

But others feel liberated: 
They have no sin within them. 
The darkness, the \quo{evil} they feel is their true nature and purpose. 
It is not something wrong and bad, something to reject and suppress. 
Rather, it is their true selves and should be embraced. 
They feel an immense freedom. 
Suddenly they need no longer feel guilt and shame; they can embrace their inner selves, for this is what they were created to be. 

Some of them grow to hate \Merkyrah. 

\lyricsbs{Hate Eternal}{Beyond Redemption}{
  In vein of sacred scriptures\\
  provide the sight and visions.\\
  The lusting of hypocrisy\\
  forever scars the soul.\\
  Cursed is the life once given.\\
  Your prayers obsolite.\\
  The termination of the myths\\
  you've led yourself to believe.
}









\subsection{The first schism}
Already out there on the expedition, a schism forms between two factions: 
Those who wish to embrace their newfound dark past and those who wish to fight against it. 
They argue a lot while they're out there, and more on the way back. 

Some of the \quo{dark siders} decide that they will reach no consensus, and that the \quo{light siders} are a threat to them. 
Reasonably enough; the light siders would likely report them to the church and have all the dark siders tortured and killed. 

So the dark siders, or at least some of them, conspire and kill the light siders. 
They disguise it as an accident. 

There are also some neutrals, or some wimpy dark siders, who were too afraid to take part in the murder. 
These are now forced to side with the other dark siders and help keep the secret, or they too will be tortured and killed by the authorities for letting it happen. 
(Remember, the \resphan{} church is not reasonable. 
It will punish people harshly at the drop of a hat, and assume suspects to be guilty until proven innocent.)

Perhaps some \quo{light siders} die of the shock, or kill themselves. 
Perhaps some wimpy neutrals lose the will to live and waste away. 
Unable to handle the truth. 









\subsection{They try to repress it}
The explorers try to repress this new knowledge of theirs, but it keeps coming back to them and will not leave them alone. 
Day and night it haunts them, and they dream and ponder it. 

\lyricsdimmuborgir{The Promised Future Aeons}{
  Burn the pictures, so unexpected in this strange deserted place.\\
  Once opened its secrets would become the world.\\
  Its attributes would continue to unfold forever.
  
  Through the fabric of the promised future aeons.\\
  I offer this suffering of my unwanted father...
  
  And the stars did wander,\\
  separated in the forbidden Universe. 
}

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Sola Fide
}{
  They burst my veins to pieces, these wan rats inside,\\
  with their jaws so contagious of a disease,\\
  as if it dropped like pus from the twelve wings of Sammael.\\
  The primeval light inside, gift of god and the holy spirit.\\
  It bleeds, so swollen by the bubo of this pest divine.\\
  The least traces of the consolation of Eden\\
  were consumed by this heinous blessing in ashes.
}

They try to carry on their lives as normal, but they can't. 
So they start their underground movement. 









\subsection{One comes to term with it}
One of the rebels battles with the revelations and tries to come to terms with it. 
It might be \Shiaraid, or \Sithiyacaan, or even \Damiarch. 
Let's assume for the nonce that it's \Shiaraid. 

She fears to give up \Merkyrah{} and the things she likes about it. 

\lyricsbs{Emperor}{With Strength I Burn}{
  Deep Green Dark Chaos.\\
  Blinded I run down these paths.\\
  By heart I know them.\\
  They lead to the soaring cliffs.\\
  Stout they stand above the water's edge,\\
  lifeless.
  
  And this is my foundation:\\
  Cold stone.\\
  Formed only by winds and time.\\
  How invulnerable,\\
  lifeless.
}

She wonders if \ps{\Semiza}{} revelations can really be true. 

\lyricsbs{Emperor}{With Strength I Burn}{
  For once I wish to see\\
  the entity behind the voice.\\
  The face of this seduction,\\
  the beauty of my pain.
  
  Am I blessed or am I cursed by thy presence?\\
  What is my crime, what is my deed?\\
  Is this life my redemption?\\
  Shall I repent or proceed?
}

She chooses side and pledges herself to the rebellion. 

\lyricsbs{Emperor}{With Strength I Burn}{
  I hate my flesh.\\
  Its dimension poisoned my soul with doubt.\\
  It made me question\\
  the essence of the \quo{I}.\\
  Slaves are those of this world\\
  given freedom to lay chains upon The Master.
  
  The wolf is no longer free.\\
  Release the chains and come for me.
}

She is fascinated by the opportunities this revolution offers. 

\lyricsbs{Emperor}{With Strength I Burn}{
  Grant me sight so I can see\\
  that which lies ahead of me.\\
  Cursed be my mortal eyes\\
  for dying in the realm of Death.
}

After the whole rebellion and conquest is concluded, she ponders whether it was worth the cost. 

\lyricsbs{Emperor}{With Strength I Burn}{
  I return to the soaring cliffs.\\
  They truly shine of strength.\\
  Even though I nothing learned.\\
  With strength I burn...
}









\subsection{They feel their new power}
The dark ones discover a tremendous power when they embrace \nieur. A destructive and creative force. They cannot fully channel and control it yet, but they can feel the immensity of it. 

\lyricsbalsagoth{The Awakening of the Stars}{
  With but a gesture of my incorporeal hand 
  I illumine the heart of a new-born sun,
  revelling as its searing stellar radiance engulfs my ersatz form.
  Gazing out across the limitless, stygian cosmos,
  I hear the whispered voice of destiny echoing within the solar winds...
  
  No small task, to awaken a universe from slumber.}

This feeling is further magnified \hr{Origin of Satharioth}{when they become \satharioth}. 

\lyricslimbonicart{A Cosmic Funeral of Memories}{
  The night belongs to the predator\\
  to the one who dares crossing the threshold,\\
  the axis of dreams and wonders and black miracles.\\
  I see my self in the mirror of your eyes:\\
  A dark star on the celestial beautiful midnight sky.\\
  Release the inner radiance of what you have become.\\
  Brighten the night with your sacrifice.
  
  I have returned to life to speak of clairvoyance.\\
  I am the voice from the grave land of memories.\\
  Life can be only an illusion, and death a temptation,\\
  a final destiny.
}

\lyricsbs{Arcane Wisdom}{Of Skyfire Burning Deep}{
  In dark waters shall we bathe \\
  yet again, as we`d done aeons ago. \\
  Wretched souls left grimly wandering \\
  like specters of a long-dead kingdom. \\
  And so great and mighty, the dismal sky \\
  whither we shall return to \\
  when the day arrives.
}

\lyricsbs{Aeternus}{Burning the Shroud}{
  Within you it lies since the rise of your time.\\
  You've feared it, ignored, but truth never lies.\\
  Its existence marked at the birth of time.\\
  The darkness inside.\\
  The shadows that dance in your soul.
  
  To deny is to fear.\\
  Embrace the darkness.\\
  Reveal in its power.\\
  Within it lies the harmonious truth.\\
  A voyage into the cave of shadows\\
  yields the jewels of knowledge and wisdom.
  
  Does not the night\\
  and the silver moon\\
  enchant your being?
  
  The caressing whisper of the night.\\
  No harm will come to those who are true of heart.\\
  Look to the sun and the brightness shall blind you.\\
  Stare into the black embrace,\\
  the sight deepened with wisdom.
  
  Free your consciousness.\\
  Accept the reality of darkness.\\
  It has never been a place of dread.\\
  Knowledge and wisdom\\
  is given to those who seek.
  Achieve the empowerment\\
  of endless mysterious nights.
}









\subsection{Ramiel, \Shiaraid{} and \Eryal}
From \Semiza, Ramiel had learned sadism and \Shiaraid{} had learned masochism. 
They quickly implemented this in practice in their sex life. 
They loved it. 
They found great pleasure in this \quo{sinful} behaviour. 

But \Shiaraid{} found out that she was not entirely content. 
She had both dominant and submissive lusts. 
She wanted to take turns being the dominant part. 
Ramiel would have none of that. 
Already he had developed an irrational fear of being \quo{nothing}. 
Being sexually submissive would confirm that fear. 
He would not let that happen. 
He would prove to himself that he was not nothing, that he was superior and not inferior. 
So he refused to submit to anyone, even the \resvil{} he loved. 

\Shiaraid{} was nonplussed. 
She tried to persuade or tempt him, but it became clear he would not budge. 
She was unhappy for a while, but then she realized that their new rebellious philosophy had no rules about monogamy. 
If she wanted a kind of sex that her lover was not providing, she was free to go elsewhere and get it. 

So \Shiaraid{} went out looking for a lover. 
She found \Eryal. 
They had known each other a little bit before and had been attracted to each other, but lesbianism was forbidden in \Merkyrah, so they had repressed their feelings. 
Now \Shiaraid{} sought out \Eryal{}.
She could tell that \Eryal{} had submissive tendencies. 
Her new realization of her own hidden lusts had also given her clearer sight when it came to reading other \resphain{} and \emph{their} repressed feelings and desires. 

\Eryal{} knew nothing of the rebellion and was a demure and faithful \Merkyran. 
But she was attracted to \Shiaraid, and \Shiaraid, having already partially embraced her dark nature, suddenly shone with a new aura of glory, beauty, promise and forbidden allure. 
\Shiaraid{} did her best to seduce \Eryal, and the young, inexperienced \Eryal{} could not resist her. 
They had sex. 
And their sex quickly become dark and naughty. 
\Eryal{} loved being dominated and gave in one hundred percent. 
Soon she was virtually \ps{\Shiaraid} slave, in the bedroom and out of it. 
She lived to serve and obey her mistress, and she loved her. 





\subsubsection{Ramiel's hypocrisy}
Ramiel picked up on the fact that \Shiaraid{} had an affair with \Eryal. 
He was not happy that \Shiaraid{} was having sex with other people.
Worse, he sensed that she had a \emph{better} relationship with \Eryal{} than with him. 
\Eryal{} submitted to \Shiaraid{} more whole-heartedly and sincerely than \Shiaraid{} ever submitted to Ramiel. 
He became jealous. 

So he called \Shiaraid{} out on it. 
She explained her reasoning as if it were the most natural thing in the world: 
They had rejected the \Merkyran{} religion and were free to have sex with whomever they chose. 
\ta{Is it not wonderful, Ramiel? I love it, this new freedom.}

Ramiel could not argue with that, but it did not sit well with him. 
He knew he was being a hypocrite, but he was not happy about having to share his \resvil{} with others. 
Like all \resphain, he had \hr{Resphain are possessive}{a genetic urge to own his \resvil}. 
He had grown up with the strict monogamous tradition of \Merkyrah. 
From childhood he had learned that it was his goal in life (like every other \resphan) to strive to possess a \resvil{} and make her his own. 

\Shiaraid{} had abandoned monogamy, so Ramiel did likewise. 
He went out and had sex with other \resviel. 
By the time this happened, he was a popular rebel leader and could attract a fair number of groupies. 
So he fucked them. 
And he was rough with them. 
Some of them he hurt really badly. 
He was a sexual sadist now, remember? 

But it did not make him happy. 
He still had sex with \Shiaraid, but he knew he had to share her with others, and that made him bitter. 
He wanted to own \Shiaraid. 
He began to hate \Eryal. 

\Shiaraid{} noticed that Ramiel was not hitting it off with \Eryal. 
She encouraged the two to have sex, hoping that it would bring them closer together. 
\Eryal, eager to please her mistress' every whim, went to Ramiel and offered herself to him. 
She submitted to him and let him dominate her to his heart's desire. 
He did. 
\emph{Brutally}.

\Eryal{} halfway regretted having agreed to do it. 
When \Shiaraid{} tortured her, it was always with an undertone of love. 
Not so with Ramiel. 
He \emph{genuinely} wanted her to suffer. 
And suffer she did. 
\Eryal{} begged and whimpered and cried and wept. 

And it did not help much.
Their relationship did not really improve. 





\subsubsection{\Eryal{} joins the rebellion}
\Eryal{} joined the rebellion. 
She was urged to do so by \Shiaraid. 

\Eryal{} was good and faithful and did not like the evil she saw in the rebels. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  As night turns into morning\\
  All the shadows disappear\\
  Although mine is still here
  
  As morning turns into night\\
  All the shadows reappear\\
  Although mine is not here?
}

But she knew she dearly loved \Shiaraid, and she dearly loved the sex she had. 
\Merkyrah{} would forbid their relationship. 
And if she refused to join, she and \Shiaraid{} would be torn apart on either sides of the war. 
She could not live with being parted from her mistress. 

Besides, (\Shiaraid{} argued,) there were several great and wise people on the rebels' side. 
Surely they could not be all wrong...

So, despite her misgivings, \Eryal{} gave herself to the rebellion. 

Be sure to depict how happy \Eryal{} was when \Shiaraid{} approved of her decision to join the rebels. 
She beamed under her beloved mistress' affection and compliments. 

\Eryal{} was introduced to \Semiza. 
She was scared of him. 

She joined, but she still feared it was madness. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  Raging madness, smiling sadness.\\
  Walk out and meet the Path of Darkness \\
  with your unwary naked feet.\\
  Beg for mercy.
}










\subsection{They lose \Semiza}
\target{Rebels lose Semiza}
Somehow they lose contact with \Semiza. 
Perhaps the \Merkyrans{} discover a sense of evil emanating from his twisted garden, and so they bomb the place and seal it up. 
Comparable to how the authorities bombard Innsmouth and Devil's Reef in \authorbook{\HPLovecraft}{The Shadow Over Innsmouth} and the game \emph{Call of Cthulhu: Dark Corners of the Earth}. 

So from here on they are on their own and without his guidance. 
They must discover their true selves by experimentation. 
They slowly begin to split into various ideological factions (later becoming the dynasties). 
Some believe that only through utter depravity will they discover/realize their true nature and destiny. 
Others believe that they must master their inner darkness/evil and bring it under control via some kind of morality (these become \KiriathSepher). 















\section{Darkness Festers}
\subsection{Underground cult}
The enlightened ones know that they cannot simply cry their newfound knowledge from the rooftops. They would be killed. But they can gather supporters from among the \hr{Early fallen Resphain}{fallen ones}. 

So they form an underground cult, a rebel organization, and begin gathering strength, politically and mystically, by doing research and learning to control their true power, unfiltered by the false Light. 

Some of the fallen ones are overjoyed. Suddenly they discover that they are not just weaklings after all; they were simply living out their true nature all along. They need no longer feel shame and self-hatred. And what's even better, they can use their darkness to overthrow the government, get revenge on the church that has hated and oppressed them for so long, and gain power, glory and eternal, sinful pleasure. Suddenly their bleak, failed existence has a purpose. 

The enlightened ones were mighty and capable \resphain{} already before they went on their expedition, and they are even mightier now that they have learned to channel their true power (to some limited extent). The fallen ones are wimps, so they embrace the enlightened ones as their saviours and bow down to worship at their feet. Ramiel suddenly finds himself with several \resviel{} (hot goth chicks) begging to be his sex slaves, pleading for the opportunity to give him pleasure\dash and then doing their utmost to please him. This is an awesome feeling for Ramiel, because \resphain{} lust very much after the \resviel, who are fewer in number and sexually picky. (They lust after \human{} women, too, but much more so after \resviel. The \resviel{} are far more attractive because they possess better genes and will produce \resphan{} offspring.)

\lyricsdimmuborgir{The Blazing Monoliths of Defiance}{
  Godless temples beckon,\\
  through gleaming scapes of horrid nightmare.\\
  Gathered between symbols and signs.\\
  A glow of new light is born out of the night.
}

They grow to hate \Merkyrah{} and feel are disgusted by its supposed marvels. 
Some succumb to nihilism and begin to hate everything. 

\lyricsbs{Arcane Wisdom}{Misanthropic Horror Magnified}{
  Senseless oblivious towers,\\
  monuments to absurdity.\\
  Oceans of ignorance.\\
  Humanity at its cruel best! 
  
  When all noble values are (shamelessly) inverted, \\
  and brainwashed minds endure.\\
  When animal essence is forgotten. \\
  Misanthropic horror... magnified.
  
  Decadence is all I see. \\
  Triviality lies before me. \\
  Nihilism\dash the only solution. \\
  Misanthropy\dash the final escapism. 
  
  Your world sinks to vomiting proportions. \\
  Visions of decay spring everywhere. \\
  Entire lost civilizations \\
  succumb to a \quo{worldly} oddity. 
  
  Woe and torment be behind me... \\
  the maze of such reality. 
}





\subsubsection{An army of misfits}
The rebels end up with a terrible army of misfits, madmen, malcontents, criminals, heretics and outcasts. 
The good leaders are not entirely happy about this. 
But the evil ones (\Zachirah, \Gevural) enjoy it and do their best to fully utilize and channel the evil potential. 

\lyricsbs{Monolith Deathcult}{Master of the Bryansk Forest}{
  Waffen-Sturm-Brigade RONA, \\
  filled up with criminal prison inmates, \\
  political prisoners, traitors and faggots \\
  to defend the newborn Republic of Lokot. \\
  Dissidents, criminals, thieves and violators, \\
  a murderous phenomenon behind enemy lines. \\
  Anti-Soviet, pro-German death squads \\
  ambushed in the woods of Bryansk.
  
  Partisan liers-in-wait, \\
  dressed in bloodstained White Army uniforms. \\
  Anti-Soviet, pro-German Werewolves \\
  assembled before the gates of Warsaw. \\
  Warsaw's Jews, Gypsies and retards, \\
  prepare yourself for death and horror. \\
  The Kaminski Brigade enters the perimeter \\
  and waits for the command to lay your city in ruins.
}

They wage a secret guerilla war. 

\lyricsbs{Hate Eternal}{The Obscure Terror}{
  We are your enemies, sworn to secrecy.\\
  Mentors of all that is profane.\\
  We are betrayers, devoid of your worth.\\
  We thrive in all that is stained.\\
  We poison all that is pure.\\
  We endanger all that be.
  
  Why hinder thou from escaping obscurity,\\
  thus dominating your race?\\
  You will not stop us, you can not stop us,\\
  for we shall never falter.\\
  We are extraordinary in our design.\\
  We flourish in your pain.\\
  In your blindness, your very blindness,\\
  we attack with ferocity.
  
  Strength through adversity.\\
  Death with nobility.\\
  Instruments of insurgency.\\
  We are the obscure terror.
}

\Kezrabal-tachi emphasize that angry misfits have an important part to play in the world, especially in the conflict that is to come. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Odium Nostrum
}{
  Odium\\
  Oh Merciless Hatred;\\
  Spare nothing, spare no one\\
  Oppressive heat, intense flavour\\
  From the pupil of the one-eyed mongrel \\
  to the distant depths of the macrocosm\\
  We are all waiting for the releasing hour
}





\subsubsection{Awakening their inner darkness}
The rebels perform occult rituals in an attempt to contact and awaken the true darkness within them. 

\lyricsbs{Vital Remains}{Scrolls of a Millenium Past}{
  Arose from the second triangle burning my soul. \\
  Gehenna is the place for burning, takes me away. \\
  Order of the golden dawn summoning Beelzebub. \\
  Give your eternal loyalty, demon of death and evil.
  
  I am (the) personification of cosmic force \\
  and (the) creator of all living things. \\
  Even the gods bow at my feet \\
  to lick the blood from my sword.
  
  Book of Revelations. I forsee the fallen angels \\
  rise to destroy the ministers of God. \\
  Strong as a lion in the Moon of the woods. \\
  (Great) beast come, gods fucking withdraw.
}

They discover great, mystic, Chaotic pleasure. 

\lyricsbs{Vital Remains}{Into Cold Darkness}{
  Sensual pleasures of non-resistant triumph.\\
  Spiritual tendencies deeply rooted in man's psyche.\\
  Ab-I-Hayat, waters of immortality,\\
  a sanctuary to mortuate your mind.
}









\subsection{\Sithiyacaan{} and his idealism}
\Sithiyacaan{} was one of the original \hr{Resphan rebels}{\resphan{} rebels}. He was idealistic, driven by a sincere dream to bring freedom and enlightenment to the \resphan{} people. He disliked the totalitarian and repressive \Merkyran{} church and wanted to give the people a better, happier alternative. He had scruples, but was seduced by the darkness and the leaders of the rebels (such as \hr{Gepheral}{\Gevural} and his brother). 

He believes that the \Merkyran{} religion will lead to a slow death of stagnation. 
He believes that one must first destroy in order to pave the way for new creation. 
He believes that breaking the rules is the way to creation, insight, happiness and a way out of slavery, stagnation, stupidity and prejudice.

He becomes a Zarathustra-like preacher. Compare to \authorbook{Friedrich Nietzsche}{Also Sprach Zarathustra}. 

Most people, \resphan{} and mortal alike, do not understand the rebels. They mock them and laugh at them. The rebels become more bitter, and even the more idealistic ones, like \Sithiyacaan, begin to accept that more extreme methods are needed. 









\subsection{The Glory of Darkness}
The \Merkyrans{} denied their \hr{Resphan vampirism}{vampiric nature}. This made them weak, declining as the years and generations passed. So at this point, thousands of years after the initial creation of the \resphain, they were mere shadows of themselves.

The rebels realized that they were the \quo{children of \nieur}, which in turn was born of Chaos and Darkness. 

As the rebels learn more of their true power, they start draining life again. First they drink a bit of blood. Some of them drink each other's blood during sex. This is hot and gives them pleasure, but it doesn't help, since they're just draining each other. Then they start draining the blood of others, and eating \human{} flesh. They get a taste for it, and their perverse tastes escalate into orgies. Eventually, they dare abduct and kill \resphain{}, drink their blood and eat their flesh. Even later, they learn to drain all a person's lifeforce and suck out and devour his soul. 

The more they do this\dash and other dark things\dash the more they revert to their true nature. And it shows. The darkness inside them seems to glow even stronger than light. They are respendent in their dark majesty and glory, and they awaken even more of their natural ability to command \humans{} (and, to a lesser extent, other creatures such as \nephilim). 

Their cult grows dramatically. Especially \humans{} flock to them, for even though the rebels are clearly evil, their charm and authority is so great that the feeble \humans{} (who are, after all, created with the chief purpose of being slaves of the \resphain, not question their morality) can't help but admire and worship them. They are the first \emph{true} \resphain{} that these \humans{} have met, and they are overwhelmed by the sheer awesomeness. 

The \hs{Voices of God} contacted the dark ones in visions and tried to stop them. 

\lyricsbalsagoth{The Empyreal Lexicon}{
  Such carnage wrought with your malevolent tongue, dark one...\\
  What unfathomable horrors dwell within the lightless corners of your cursed soul?\\
  Heed not the voice of the Lexicon... lest its whispers drive you mad!}





\subsubsection{\Kezrabal, the propaganda minister}
\target{Kezrabal becomes propaganda minister}
\index{propaganda minister}
One of the rebels, \Kezrabal, was the \quo{propaganda minister}. 
He wa the most talented demagogue of them and pulled lots of people in. 
He told them whatever they want to hear, whatever they \emph{needed} to hear, and was perfectly willing to tell outright lies if it was convenient. 

He preached of the glory of the rebellion. 

\lyricsbs{Exmortem}{The Revolutionary Soul}{
  We have made a weapon of hatred\\
  to slay the stagnant powers,\\
  to reach the land of utopia\\
  where creative chaos reigns.
  
  Now blasphemic bells\\
  are ringing in your head.\\
  Wicked demons on the ringside.\\
  The challenger has cut his chains.
  
  So cast yourself into the flames.\\
  Lick the powers of the burning planet.\\
  It is the reawakening\\
  of the revolutionary soul.
}

He preaches against \Merkyrah. 

\lyricsbs{Vital Remains}{Devoured Elysium}{
  Worship your God and pray unto him. \\
  For his love is masked by the stench of decay. \\
  Your death is what he needs, the blood of the righteous. \\
  We will celebrate, as you will go \\
  one by one, one by one, one by one... \\
  to meet your bastard maker.
}





\subsubsection{New people are lured in}
The rebellion lures in new people, folks who are disgruntled with the church. 

The more evil sub-fractions preach hate and revenge, whereas the more idealistic fractions preach truth and freedom. 
\Gevural{} was pretty brutal at first, but got much more refined when he became \Azraid. 

\lyricsdimmuborgir{Broderskapets Ring}{
  Kom, unge bror. \\
  Skjenk oss din rene ungdom.\\
  Legg ditt liv i v\aa{}re hender.\\
  Kjemp v\aa{}r krig med oss.
  
  La vare sorger form\o{}rke ditt sinn.\\
  La din sjel slites.\\
  F\o{}l natten som legger seg rundt deg.\\
  Glem all kj\ae{}rlighet.\\
  
  Ingen t\aa{}rer skal fylle dine netter.\\
  Tre inn i broderskapets ring.\\
  Ingen svakhet skal du finne i din sjel.\\
  Styrken skal vandre ved din side.\\
}

\lyricsdimmuborgir{N\aa{}r Sjelen Hentes Til Helvete}{
  F\o{}lg, f\o{}lg etter.\\
  Til Ondskapens hall vi drar.\\
  Der det vendte kors pryder ferden\\
  av M\o{}rkets Allmektighet.
  
  P\aa{} kristi flesk vi spytter.\\
  La det r\aa{}tne!\\
  Et symbol p\aa{} godhettens bortgang.\\
  Et skuespill der endes.
  
  Bring frem v\aa{}rt indre sinne.\\
  Vis veien for v\aa{}rt hat.\\
  Skjend guds sjeler til evig pine.\\
  I Ondskapens paradis er de dine.
}

\lyricsdimmuborgir{The Serpentine Offering}{
  Reconcile not with the fear of the snake,\\
  but embrace it as your own.\\
  Inject its venom into your veins,\\
  and replant the seed that gives growth.\\
  Still shrouded in mystery\\
  until you arise above perception.\\
  A veil of ignorance is in motion,\\
  continuing throughout generations.
}

\lyricsdimmuborgir{The Sacrilegious Scorn}{
  My word and world holds ground and is real.\\
  Your word is like floods of poisoned water,\\
  a language spoken with spit of different tongues.\\
  You can never corrupt me again.
  
  Time has come to step up\\
  and take back what you took from me.\\
  You can never corrupt me again.
}

They embrace the darkness, come what may, no matter the cost. 

\citebandsong{Ihsahn:angL}{Ihsahn}{Malediction}{
  And so you earn my contempt.\\
  My enmity. Malediction. \\
  Though my path be that of thorns,\\
  the way of my affliction\\
  is the way to myself.
  
  The devil will not let me go, \\
  though I do not mind.\\
  Through fiery lakes to where cold rivers flow,\\
  I honour the contract I signed.
}






\subsubsection{Initiation ritual}
New members worship and adore the cult. 

\lyricsdimmuborgir{Master of Disharmony}{
  Master of disharmony, welcome my tainted soul.\\
  Take me from the hordes of the living\\
  into the blessed darkness
  
  Master of disorder, take my impure flesh.\\
  Lead me unto the path of temptation.\\
  Save me from cowardness.
}

New members are initiated in a ritual where they die, get in contact with the \Erebean{} force of Entropy and are symbolically reborn as new, purer, better \resphain. 

\lyricsdimmuborgir{Master of Disharmony}{
  Master of death, take my pitiful life.\\
  I am enslaved.\\
  I shall never forget the pain.
  
  Master of sin, take my cursed heart.\\
  Bring me where I can find salvation.\\
  For I am the damned.\\
}

They swear undying loyalty to the cult. 

\lyricsdimmuborgir{Allehelgens D\o{}d i Helveds Rike}{
  \ae{}tlinger som sverger eden,\\
  med troskapsl\o{}fte om \aa{} ugj\o{}re freden\\
  \aa{} styrte himmelslavers velv\ae{}re\\
  og triumfere i kulde til Dyrets \ae{}re.
  
  Vredens beger renner over I forherdelse, \\
  fra oppr\o{}rdjevlers svovelvind, gl\o{}dende, \\
  fra regionen av Belial's barn,\\
  avlet hinsides harmens trossende tind. \\
  De siste tegn fra Kristi tapende engler\\
  brenner ub\o{}nnh\o{}rlig i ravnens ild.
}

\lyricsbs{Vital Remains}{At War With God}{
  Draped by the flames has now become your flesh. \\
  The purity of pain. Your yearning for pleasure.  \\
  Shedding the skin of lies. \\
  Rejoice in our impure desires. 
}

\lyricsbs{Vital Remains}{Societe des Luciferiens}{
  Beauty in purity, the darkness glows upon the flesh. \\
  Through this, the Black Flame of Satan, thou walketh in Hell. \\
  Thy senses are awakened to the joy of rebirth. \\
  The Gates are flung wide, and thy passage is heralded \\
  by the deathless cries of His guardian beasts. \\
  His searing brand shall be evermore \\
  emblazoned on thy consciousness.
  
  Its fiery meaning shall make thee free.
}





\subsubsection{Outcasts embrace the rebellion}
Especially outcasts\dash such as the \ashenblooded\dash embrace the rebellion. 
After they win, the \ashenblooded{} are still rewarded with nothing but scorn, however. 

\lyricsbs{Dreamsfear}{Ruins}{
  Up from these ruins we'll rise\\
  to conquer this world once again.\\
  Out of the dark underground,\\
  we'll break free from these chains we are in.
  
  You never thought we'd be back from the dead. \\
  Can you feel our breath on the back of your neck?\\
  You'll know it's true when we kick in your door.\\
  You'll know it's real when your head hits the floor.
  
  No mercy this night. \\
  We're out to destroy.\\
  From the ruins we rise.
}

They blame the church for all evils of the world. 

\lyricsbs{Dreamsfear}{Ruins}{
  Not forgiven and you'll never be forgotten.\\
  Can't forgive and then we won't forget.\\
  Can't believe we couldn't see it in your eyes.\\
  Can't believe we couldn't see through your lies.
  
  Here on this night we gather to fight.\\
  For vengeance we fight.\\
  Waited so long now our time is in sight.\\
  Revenge is in sight.
  
  You're hanging on in the eye of the storm.\\
  Only a matter of time till you fall.
}





\subsubsection{They prove that their religion is stronger}
Have some biblical scenes where the rebels prove that their religion and their magic is stronger than that of \Merkyrah. 
Compare to the scene in Exodus (Old Testament) where the Egyptian sorcerers turn their staves into snakes. 









\subsection{Learning how to command \umbrae}
\target{Resphain learn to command Umbrae}
The \Merkyrans{} had always lived \hr{Merkyrans fear Umbrae}{in fear of the dangerous \umbrae}. 
\Semiza{} taught the rebels how to ward off the \umbrae, or even command them. 
This became one of their greatest weapons in the war, physically as well as psychologically. 
Many took this conquest of their ancestral foes as meaning one of two things: 

\begin{enumerate}
  \item 
    The rebels had the right idea. 
    They knew how to combat the decline and depredations they had been suffering from. 
    Theirs was the way to power, glory and advancement for the \resphan{} people. 
  \item 
    The rebels were evil itself. 
\end{enumerate}

\target{Rebels awestruck by tame Umbrae}
The lower-ranking rebels were awestruck when they for the first time saw their masters come riding on on subdued \umbrae. 
(\Achsah{} was one of them, as \hr{Achsah fetches Umbrae}{she would later recall}.)









\subsection{Learning how to kill a \resphan}
Previously, no one knew how to kill a \resphan, so they would never die. 
The very oldest \resphain{} ever were still alive at this point. 

But the rebels learned how to permanently destroy a \resphan. 
Maybe \Semiza{} told them. 
They must kill the body, cook it with special spells, eat the victim's flesh, drink his blood and devour his soul. 

\target{Rebels learn soul-eating from Umbrae}
They learned this skill by studying the \hr{Umbra}{\umbrae} and sort of reverse-engineering the \ps{\umbrae} \hr{Umbrae eat souls}{soul-eating technique}. 
But they never learned to do it as easily and effectively as the \umbrae{}. 

This was a horrible, gruesome weapon, and the \Merkyrans{} were horrified when they learned of it. 









\subsection{The \resphan{} lords betray their own}
There are cases where the \resphan{} lords betray their own and eat them. 
The leaders eat their younger fans, adherents, groupies, worshippers\dash those who trusted and loved them. 

Compare to Akasha in the movie \emph{Queen of the Damned}. 









\subsection{Show the good side of \Merkyrah}
\Semiza{} and the rebels dissed \Merkyrah{} like no tomorrow. 
But we should still see some scenes demonstrating the good sides of \Merkyrah. 

Show people who were happy about their lives. 
Have some tree-hugging, diabetes-inducing sweetness and gay pacifism. 









\subsection{The rebellion is necessary}
\target{Merkyran rebellion is necessary}
The rebels know that the rebellion, no matter how brutal, is necessary. 
The \resphan{} people are not only far from their true potential, they are actively declining. 
If they continue the \Merkyran{} way, they will continue to degenerate until they are no more powerful than \humans. 
In the end their Entropic hunger will consume them and they will die. 
Being afflicted with \Bane{} \hs{Entropy}, the \hr{Resphan parasitism}{\resphain{} are parasitic} and must consume external power to survive. 

They must gain access to the \hr{Heart}{Heart of \Miith} and draw of its power. 
This is the only way to keep their people alive. 
But the \dragons{} and their ilk are hogging the Heart. 
In order to eat of the Heart's power, they must steal it from the \dragons. 
So war is the only option. 

The rebels cannot hope to stand against the \dragons{} alone. 
They can stand a chance only if the entire \resphan{} people stands united. 
They know that the \Merkyran{} church will never accept this truth, since their entire religion is knowingly and deliberately build up around the active denial of this very truth. 
Thus, a violent rebellion and coup is the only way. 

The more moral rebels (especially \Damiarch{} and \Sithiyacaan) are saddened by this, but they have a sacred duty to their people and must do what they must. 
Their entire race's survival and future is at stake. 
That is more important than anything, and worth any price, even genocide and tyranny. 

\lyricsbs{Hate Eternal}{The Victorious Reign}{
  The victorious reign!
  
  We are the glorious order, \\
  bound together by blood and by faith,\\
  successors to a tradition.\\
  Are we the vessels of death?
  
  We are your purification, \\
  united by purpose and will,\\
  affiliates of an allegiance. \\
  Are we the blasphemous creed?
  
  We are the infamous legion, \\
  a covenant of supposed heresy,\\
  conceivers of a hierarchy. \\
  Are we the disciples from Hell?
  
  Sworn to this alliance, we only speak of truths.\\
  Heretical in its shape. Is it profane?\\
  Devotees to the cause, sacrilegious in its form.\\
  Sworn to this alliance, we only honor him.\\
  Heretical in its shape. Is it profane?
}









\subsection[Zachirah founds Mystraacht]{\Zachirah{} founds \Mystraacht}
\target{Zachirah founds Mystraacht}
\hr{Zachirah}{\Zachirah} turned \hr{Zachirah goes mad}{evil and power-hungry and mad}. 
He was not entirely satisfied with \Damiarch{} and \ps{\Gevural} ideology, so he founded his own extremist sub-fraction: \Mystraacht. 

He also founded \hr{Mystraacht philosophy}{\ps{\Mystraacht}{} evil philosophy} (see that section). 

He preached hate and violence. 

\lyricsdimmuborgir{Progenies of the Great Apocalypse}{
  The battle raged on and on, \\
  fuelled by the venom of hatred for Man. \\
  Consistently, without the eyes to see, \\
  by those who revel in sewer equally.
  
  Are we not the undisputed prodigy of warfare, \\
  fearing all the mediocrity that they possess? \\
  Should we not hunt the bastards down with our might, \\
  reinforce and claim the throne that is rightfully ours?
  
  Consider the god we could be without the grace. \\
  Once and for all. \\
  Diminish the sub principle and leave it's toxic trace. \\
  Once and for all.
}

\lyricsdimmuborgir{Vredesbyrd}{
  Reis deg opp, la oss bestride den tanke fra v\aa{}r lend, \\
  og dyrk p\aa{} en forbannet jord en smertens \ae{}tt. \\
  For s\aa{} og tynge de barmhjertiges skj\o{}d, \\
  som har tiltro til den sjell\o{}ses br\o{}d.
}

He recruited new people to join his faction. 

\lyricsbs{Vital Remains}{I Am God}{
  Follow me now and walk the hounds of Hell \\
  and ride the whirlwinds of the night. \\
  Together we become an army out of Hell, \\
  to scourge the Earth, and melt the ice.
  
  I am one within myself. \\
  I am one with the night. \\
  Prevailing darkness, I rule this space. \\
  Call me God, remembering my face. \\
  I will rise divide and conquer. \\
  This world I live there is no other. \\
  Call to the points North, West, South, East. \\
  You summon me, I am the Beast!
}

They feel that this new truth they have discovered not only warrants but \emph{demands} a total break from tradition. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  DeathspellOmega
}{
  The Repellent Scars of Abandon and Election
}{
  The feeling of destroying the capacity for inward peace, \\
  an insane dance with the angels of innocence \\
  amidst thorns and in frenzy, \\
  the warmth of a divine blessing, \\
  a daringness which prevailed over any imaginable fear\\
  hovering on the brink of a voluntary act of contrition, \\
  but soon all pales besides the cry \\
  this shattering truth wrests from all fellow men, \\
  there is more to it than suffering and sounds of suffering, \\
  it is a process that only the extinction \\
  of a divine soul could terminate. 
  
  The eye can outstare neither the sun, nor death... \\
  if I sought God it was in delirium \\
  and in the delight of temptation.
}





\subsubsection{\Zachirah{} seduces Ramiel}
\target{Zachirah seduces Ramiel}
\Zachirah{} convinced Ramiel to join his fraction. 

\lyricsbs{Marduk}{Darkness It Shall Be}{
  I have dreamt the dreams about Satan's beautiful promises\\
  Of the dark arts, and the blackened powers I possess\\
  I have dreamt about worlds burning in millions of fires\\
  And the worthless christianity burning with them\\
  I and you are all that is dark of the world\\
  And so we shall greet the everlasting night with pride\\
  You and I bear the wisdom of a thousand geniuses\\
  And we are granted the right to lead the people to their ends
  
  I have dreamt about the deeds of the very past\\
  But none of them are as great as those to come\\
  I have dreamt about great days to come\\
  When I shall wear the black crown, and rule with Satanic might\\
  I and you are born of the same great blood\\
  And we are proud warriors in the great army of Satan\\
  You and I have got the world in our grasp\\
  The world at our knees, and the vision of destruction in our eyes
  
  A new age will come, and a new King will be crowned\\
  A new age will arrive.. In your own blood, you shall be drowned\\
  This new age of Satan, the new age of Hell\\
  This is what I have seen, and darkness it shall be
  
  I have dreamt the dreams that will come true.
}









\subsection{Rebels ally with tribes}
The rebels ally with some of the other \resphan{} tribes that were the traditional enemies of \Merkyrah. 
Compare to how Alexander Devon recruits the Heshette in \authorbook{Alan Campbell}{Scar Night}. 









\subsection{A rebel kills a faithful}
A rebel gets into a fight and kills a faithful. 
This is one of the sparks that ignite open war. 

The killer had been nurturing hate towards the church and the faithful for a long time, and finally snapped, craving release. 

\lyricsdimmuborgir{Da Den Kristne Satte Livet Til}{
  Min sjel den gl\o{}det og mitt sinn det lengtet\\
  etter \aa{} f\aa{} fatt i en kristen faen.\\
  I det kalde m\o{}rket jeg ventet med vinden.\\
  Det ulte som besatt av Fanden.
  
  Jeg ventet, \aa{}h, som jeg ventet.\\
  Tiden virket som evig.\\
  Men endelig fikk jeg \o{}ye p\aa{} stakkar'n.\\
  Jeg hevet min knyttede neve og skrek.
  
  Svake kristne! D\o{} i natt!\\
  Jeg skal flerre din sjel i to.\\
  Du skal f\o{}le makten jeg har f\aa{}tt av m\o{}rket.\\
  Din tid er omme, ogs\aa{} din tro!
  
  Be om n\aa{}de, du stakkars faen,\\
  og min latter skal atter runge\\
  h\o{}yt i nattens kulde\\
  der frosten fryser din siste t\aa{}re...
  
  Svake kristne! Du d\o{}de i natt!\\
  Med et kraftig hugg tok jeg din skalle.\\
  En blodig slakt som til syvende og sist\\
  hvis stemmer (vil) for alltid i D\o{}dsriket gjalle.
}









\subsection{Preparing for war}
\lyricsbs{Vital Remains}{At War With God}{
  Beneath my flesh flows the blood of wisdom. \\
  Within my heart, the hunger for conquest. \\
  This silent legion, birth of a new revelation. \\
  The day has come when God's land shall burn. \\
  Watching as your kingdom falls. At war with God.
}
















\section{The Mask Falls}
\subsection{Rebellion}
\target{Merkyran rebellion}
\target{Resphan rebellion}
It comes to open rebellion and war between the dark siders and the light siders. 

Since the \Merkyrans{} deny their vampiric nature, they are weak, easy prey for the rebels, who strike them down and devour their blood, flesh and their very souls. Remember to have some dark, grisly scenes where the rebels eat \resphan{} flesh. 

The dark ones announce their war by launching a grand attack on a \Merkyran{} city. They fall upon it like a terrible storm. 

Have some bloodbath scenes where \Merkyrans{} and their \human{} and \nephilic{} subjects are mowed down in droves. 

\lyricsbalsagoth{The Thirteen Cryptical Prophecies of Mu}{
  [THE CHIEF CULTIST OF ZURRA:]\\
  In the sweltering swathe of Zurra's sword! Kill, kill, kill! \\
  'Fore the matchless might of Zurra's wrath! Die!
  
  [THE HIGH PRIEST OF MU:]\\
  The storm comes.\\
  On the katabatic winds rides ravening doom.\\
  Yasa-mega... Yasa-giga... Yasa-tera!\\
  May Klatrymadon preserve us!
}

Perhaps there are some \nexus{} \trope{McGuffin}{McGuffins} in the city that the dark ones need. 

\lyricsbalsagoth{The Thirteen Cryptical Prophecies of Mu}{
  Become one with the shard, progeny of the Nexus...\\
  embrace its power... embrace the glory of immolation!
}

They fight with pride, considering themselves the true keepers of their race's legacy. 

\lyricsbs{Ancient Rites}{Victory or Valhalla (Last Man Standing)}{
  Stand strong with clenched fists. \\
  Withstand with all thy might. \\
  Stand strong with clenched fists \\
  until they are silenced right. 
  
  Let the glory shine on thee. \\
  Lift thy ancient legacy... into light! \\
  Lift thy legacy into light, \\
  so their spirits will shine on bright... \\
  shine bright!
}

The \Merkyrans{} fight back.

\lyricsbalsagoth{The Thirteen Cryptical Prophecies of Mu}{
  [THE PRIME VOYAGER:]\\
  Your folly ends here, Zurra!\\
  The Empyreal Lexicon has been made whole...\\
  and its power is lost to you forever!\\
  The foe has been cast back into the Outer Darkness,\\
  but your treachery must not go unpunished!\\
  Submit to our judgement or face eternity in the limbo of Z'xulth!
  
  [ZURRA:]\\
  I would sooner suffer damnation a thousand times than bend the knee to you! \\
  You and your sublimely arrogant ilk, who strode the primordial surface of Pangaea and watched with disdain as life evolved in the boiling oceans...\\
  You have won nothing! \\
  My power is born of Chaos...\\
  it sustains me and courses blackly through my ersatz veins!\\
  Now face the true potency of the power you seek to destroy, and behold in awe the true nature of the universe!}





\subsubsection{Demography of the war}
\index{technology!\Merkyrah}
There were \hr{Merkyran demography}{rather many \resphain{} at this time}, and \hr{Merkyran technology}{the technology was low}. 
This meant that armies of mortals little chance against \resphain. 
So the war was fought largely with armies of \resphain. 
They rode mythical beasts and monsters. 

Many great, beautiful and wonderful monuments are destroyed in the war. 
\Azraid{} and Ramiel promise the people that they will built new ones, and even grander and more marvelous. 
They do, but many of these then end up getting destroyed in the \secondbanewar{} and the \resphanwars. 

But even today the \resphain{} have much splendour and beauty. 

\lyricsbs{Vital Remains}{Into Cold Darkness}{
  Now hundreds of angels rebel against God. \\
  Winged and naked, riding black wolves.
}

\lyricsbs{Vital Remains}{Descent Into Hell}{
  Riding out the demon locust, war horses of Hell. \\
  Penetrating the blazing heat (where) wicked angels dwell. \\
  Cast to Earth, unleashing spells, devouring your souls. \\
  Christian doctrine of false belief. God is bound in Hell.\\ 
  Bow your heads to the supreme God, Lord of darkness. \\
  (Seduced nations denying Christ Satan leads the aggression.)
  
  Abbadon, leader of locust spawn, \\
  destroyer of all Christianity.
}









\subsection{Scrupulous rebels angst}
The more scrupulous of the rebels (\Damiarch{} and \Sithiyacaan) fear the evil that they have helped unleash. 
They angst over it. 

\lyricsbs{Exmortem}{Fix of Negativity}{
  My acid burnt eyes\\
  predicting the rise of evil. \\
  A quick fix of negativity, \\
  a lifetime in misery. \\
  Paranoia strikes hard. 
  
  With glass in my eyes, \\
  I see clearer now. \\
  Feel a touch of divine suffering. \\
  I am an angel with bloody hands.
}

\lyricsbs{Monolith Deathcult}{Wrath of the Ba'ath}{
  I saw their starved lips in the gloam. \\
  With horrid warning their still fuming mouths gaped wide. \\
  And I awoke, and found me here, \\
  the sole survivor writhing on the cold hill's side.
}









\subsection{\Azraid{} does a coup}
\target{Azraid coup}
The leader of the rebellion is \Damiarch. But \Gevural{} covets leadership for himself. 





\subsubsection{\Gevural{} has an inner struggle}
\Gevural{} has an inner struggle. 
He is torn between \quo{good} and \quo{evil} and doesn't know what is right. 

\lyricsdimmuborgir{Kings of the Carnival Creation}{
  In search for the guidelines to the gateways of sin, \\
  through mires of misanthropy with wrath in mind.\\
  Sophistication as cruelty and perfection as virulent truth.
  
  Confidently dawned, to pick the best of enemies.
  
  An abyss womb stretched wide open, exposed to retaliate.
}

\Daggerrain{} manipulates him, pulls him toward the darkness. 

\lyricsdimmuborgir{Kings of the Carnival Creation}{
  Glance into the blackness hidden beneath your surface,\\
  and enjoy the suffering, sanity drained in disrespect.\\
  With such bedevilled faith in good, subsequently trusting evil.\\
  Next step for mankind will be the last seasons in sin.
}

\Daggerrain{} tempts him with darkness and evil. 

\lyricsdimmuborgir{The Maelstrom Mephisto}{
  Dwell in depths of the darker self, at any shore of infinity,\\
  and watch the relentless paint the soil black.\\
  What is being formed echoes throughout eternity,\\
  as the painter chooses color no more.
}





\subsubsection{\Gevural{} becomes \Azraid}
\Gevural{} claims some great power and takes the name \Azraid{}. 
He gains his \hs{dead hand}.

\lyricslimbonicart{Pits of the Cold Beyond}{
  As the shadows of dark angels fall\\
  from the grace of light,\\
  I am carried in the arms of death\\
  into the night.}

He floats through mystic dimensions. 

\lyricslimbonicart{Pits of the Cold Beyond}{
  The universe unveils\\
  a glowing entrance to doom,\\
  next to the setting sun \\
  and the rising moon.}

All the death and destruction gives him power.

\lyricslimbonicart{Pits of the Cold Beyond}{
  Wine of life streams\\
  in faint nocturnal screams.
  
  As the rivers run red\\
  from the wrath of Armageddon,\\
  and the wine of life is shed\\
  into the pits of the cold beyond.
}

Long after his sinister experiment, \Gevural{} lies in a coma. 
The other \resphan{} lords believe him to be dead and are about to elect a successor to take over his rank.

\lyricslimbonicart{Pits of the Cold Beyond}{
  At the time when the sun emerges from the dark,\\
  in limbo a star shines and in silver it sparks.\\
  I search my soul as darkness burns.\\
  For a shadow it shall return\\
  from the pits of the cold beyond.
}

\lyricslimbonicart{Unleashed From Hell}{
  Back from the dead, across the axis of dreams.\\
  A malicious hunger. The bloodline still streams.\\
  I am a martyr of the dark side,\\
  a tyrant in soul and flesh.
}





\subsubsection{Contrast between \Damiarch{} and \Gevural}
\Damiarch{} is much more idealistic. 
He genuinely believes that he fights for the liberation and enlightenment of his people and for their glorious destiny. 
He fights for a Utopia, and \trope{UtopiaJustifiesTheMeans}{Utopia Justifies the Means}. 

In contrast, \Azraid{} is far more evil. 
He craves power for its own sake, and desires to rule in the name of Chaos and Darkness. 

\lyricsbalsagoth{Callisto Rising}{
  Break the sidereal seal, brother!\\
  Open the astral portal! Give me the Lexicon...\\
  give me that which is rightfully mine!\\
  Destroy the guardian-light... Kill!
  
  Unfetter yourself, brother Zuranthus...\\
  bestow upon me the shard which I seek...\\
  give me my godhead, or I shall condemn your flaccid essence\\
  to a dimension of unparalleled pain! Kill!
}





\subsubsection{\Azraid{} kills \Damiarch}
\target{Azraid kills Damiarch}
\Daggerrain{} wants rid of \Damiarch. 
\Damiarch{} is too moral, too scrupulous for the \ps{\banelord}{} purposes. 
He needs someone more flexible, someone who will not shy away from things that, in \ps{\Daggerrain}{} grand scheme, need doing. 
He sees \Gevural/\Azraid{} as a good candidate who would be willing to do all sorts of evil if goaded a bit. 

So \Daggerrain{} manipulates \Azraid{} into murdering \Damiarch{} and enthroning himself as the lord of the \resphain. 

\Azraid{} eats \Damiarch{} to gain his power. 

\lyricslimbonicart{The Black Hearts Nirvana}{
  Hallowed be the darkness that coronates my soul.\\
  Deep within its shelter I seek my highest goals.\\
  I shall release what is conquered \\
  from which that I now possess.\\
  All lifeforce is abandoned \\
  into the arms of death.
  
  Beyond the great dark adventures, \\
  in streams from the vast mysteries,\\
  limbonic spheres enclose me. \\
  My star is the death of memories.
}





\subsubsection{\Azraid{} begins to hate the \banes}
\target{Azraid as Xanatos Sucker}
But soon after the deed \Azraid{} realized what he had done, and how \Daggerrain{} had manipulated him. 

Compare a \hr{Ramiel as Xanatos Sucker}{similar scene with Ramiel later on}. 
Also compare to the scene in \emph{\JuukenSentaiGekiranger} episode 46 (or so) where Rio discovers that his entire life has been masterminded by Long. 

Later, during the bloody war against \Merkyrah{}, he would come to realize that the \banes{} really cared nothing for the \resphain{} except as tools to use and discard. 

Thus he begins to hate the \banes. 
He still obeys the \banelords{} on the surface and does everything he can to further their schemes, but in secret he is plotting to overthrow them. 
It will take him twenty thousand years, but eventually he will betray and usurp \Banelord{} \Daggerrain. 









\subsection{Destroy their faith}
The rebels learn that \Merkyrah{} is held together by a Shroud \hs{Mask}. 
In order to break the mask they must break the \Merkyran{} people's faith in their religion. 
Only then can they create a new world in their image. 

\lyricsbs{Vital Remains}{Icons of Evil}{
  Defame the names of all your dead gods.\\
  Vomit upon the path of salvation.\\

  Confront me now, defiler of human desire.\\
  Voracious hordes await the hour of ascension.\\
  Unravel their delusion,\\
  their translucent divinity.

  Burn down the churches... engulfed by hatred. \\
  Tear down the kingdom... incinerate his vision. \\
  Destroy their icons... pulled from their neck.\\
  The exodus of faith... their will we did break.\\
  Shattering the hope they once loved. 
}

They force themselves to surrender the last vestiges of faith. 

\lyricsbs{Vital Remains}{Infidel}{
  The infidel within me,  \\
  forever unbelieving. \\
  Purgate the stain of thy blessings. \\
  Obscure the light of Eden.
}

Some rebels are unsure and still think there are good things about \Merkyrah{} that are worth preserving. 
The mourn and angst over the fact that their inner goodness dies and is replaced by evil. 

\lyricsbs{Vital Remains}{Infidel}{
  Taint the vision of purity. Heaven ravaged. \\
  A revelation of impurity has awakened. \\
  Your inner being withers from a lifetime of devotion. \\
  Never to hear the endless cries of the faithful.
}









\subsection{Orgies}
The rebels hold great orgies of sex and violence. 
Compare to Bequa Kynska's \emph{Maraviglia} in \authorbook{Graham McNeill}{Fulgrim}. 

Some of the \KiriathSepher{} feel that this is too vulgar, too uncivilized, too evil. 
This is one of the reasons for the split between the dynasties. 









\subsection{The Murder of the Dawn}
\target{Murder of the Dawn}
The deciding climax in the rebellion was the day of the \quo{Murder of the Dawn}. 
This is an Invocation of \Erebean{} Darkness. 
The dark ones \quo{murdered the dawn} by shifting the entire capital city into \Nyx, where eternal twilight reigns. 
The city is built using the power of \hr{Old Good Iquin}{(an early variant of) \iquin}, which is ultimately a filtered form of \nieur, which is \Nyx-based.
It opens a weak conduit to \Erebos. 

The \nephilim{} can clearly see that the dark ones are evil, so very few \nephilim{} join them. 
(Unlike \humans, \nephilim{} are not bred to serve the \resphain.) 
They are slaughtered in retaliation, and their whole race is nearly exterminated. 
Today \nephilim{} are rare because of this genocide. 

Perhaps the Murder of the Dawn is the \hr{Nyx was killed}{\quo{killing} of \Nyx} which turns \Nyx{} into a parasite Realm. 

\lyricsbs{Hate Eternal}{Para Bellum}{
  May thy kingdom of the accused ones now rise.\
  Para Bellum! Para Bellum!\\
  March upon the gates of death,\\
  for those who walk among us must follow.
  
  Ira Deorum.
  
  We shall ravage the earth \\
  and destroy the ominous skies.\\
  Bring forth the end of days.\\
  Where the darkness of time \\
  shall once again consume us all.\\
  Come forth the end of time.
  
  May thy kingdom of the accursed ones now rise.\\
  Para Bellum! Para Bellum!\\
  March upon the gates of death, \\
  For those who walk among us must follow.
  
  May thy sovereign of the imperial ones now rise.\\
  Para Belllum! Para Bellum!.\\
  For we shall now conquer death,\\
  For those who walk among us are lords of war.
  
  We must darken and enlighten the world \\
  upon the mountainous shrine.\\
  Cometh forth the end of days.\\
  Hence the frenzy of brutality rules us all.\\
  Cometh forth the end of time.
}

\lyricsbs{Vital Remains}{At War With God}{
  The sun descends into the blackening horizon. \\
  We shall wait and chant until our hearts bleed hatred. \\
  Vision the bloodstream upon the one you adore. 
  
  Darken the light of the dying. \\
  Erase the thought of salvation. \\
  In Hell is where you are. \\
  The war has been upon you all.
}

\lyricsbs{Vital Remains}{Behold the Throne of Chaos}{
  The knell tolls, divine holocaust 
  by the grace of the Black Moon. \\
  The apocalyptic vision for all the world to bear \\
  witness to this, the opening of the wound. \\
  Your numinous kingdom now flows with... blood.
}

\lyricsbs{Vital Remains}{Societe des Luciferiens}{
  The ever-fading light, the light of redemption. \\
  We appear as ravens through the mist. 
  Night-fallen, all-devouring. \\
  Shrouds of blackness \\
  silently consume all that is pure. \\
  Obscure his words, brothers of the bloodwar, \\
  for we are unchained and almighty.
  
  Solemn, the lifeless angel of dawn. \\
  Silhouette, the fading symbol of life... \\
  disappears amongst the shadow of wolves.
  
  The celebrations of Christ become the worship of abhorrence, \\
  chant the paean of threnody \\
  for the council of virtue, a requiem sung for the all divine. \\
  Their lives are now exhausted \\
  as murdered day casts the sky in blood \\
  over the befallen city of... Man.
  
  In the midst of Our black paradise \\
  shall undefiled wisdom rule. \\
  The rites of Christ are but rites of Death, \\
  accept the absolute. 
  
  Vanish into the void of thy empty Heaven, \\
  for thou wert never, nor shalt thou ever be. \\
  Undefiled wisdom, its fiery meaning shall make thee free.
}

The \hs{black stars} become visible in the sky. 
The \Merkyrans{} \hr{Merkyran myths of black stars}{had feared this}, so they despair. 
Many become truly convinced now that the rebels speak the truth and that their old way of life truly is doomed. 

\lyricsbs{Marduk}{Blutrache}{
  Judgement Day edges toward evening.\\
  Every nation marches singing,\\
  every nation towards death.\\
  Let us rejoice in the light\\
  of this man-made Armageddon\\
  this man-made Hell.\\
  Hand in hand with angels of iron,\\
  angels of wrath.\\
  Panzer thunder, panzer death.\\
  Black twelve-armed holy Sun.\\
  Rise, rise, holy black Sun.
  
  The great cathedral of Man arise\\
  through doors flung wide.\\
  Every nation marches singing\\
  towards defeat and death.
  
  Every nation marches singing,\\
  every nation towards death.\\
  Let us rejoice in the light of\\
  this glaring mass cremation,\\
  this shining mass-death-light.\\
  Hand in hand with angels of iron,\\
  angels of wrath.\\
  Panzer chaos, panzer Hell.\\
  Black twelve-armed holy Sun.\\
  Rise, rise, holy Sun.
  
  Let us rejoice in the light of\\
  this solemn dance of death.
}









\subsection[The Merkyrans fight back]{The \Merkyrans{} fight back}
The \Merkyrans{} fight back, but their hope and faith are failing. 

\lyricsbs{Monolith Deathcult}{Seven Months of Suffering}{
  I turn my eyes to Dagon, our great god, \\
  flat on his divine face in the Temple of Oannis.
  
  I turn my eyes to Ba'al, our great god,\\
  Powerlessly staring at the horizon \\
  in the temple of Created Things.\\
  We feel no more glory about the battle of Aphek.\\
  What sacrifice is needed for victory?
  
  We burn... oh god we burn!\\
  We bow down in shame and whisper powerless words: \\
  \ta{Let not the ark of the God of Israel be with us,\\
      for his hand is hard on us and on Dagon our god.}\\
  Release us from the suffering.}

They fear this new evil that has befallen them. 

\lyricsbs{Monolith Deathcult}{Seven Months of Suffering}{
  This blasphemy will be avenged upon us.\\
  Our blood will colour the earth blood-red.\\
  And it will be licked away by the dog-gods.\\
  Darkness will be upon us for three horrible days.\\
  Pestilence and death creep over our land.\\
  Flocks of bugs will ruin our crops.\\
  Blistering flashes from the skies\\
  onslaught the enemies of Israel.
  
  We are the damned race, \\
  sursed by the wrath of Yahweh.\\
  Our millennial resurrection\\
  shall be smothered in blood.}

They despair when facing the rebels and their diabolical magic. 

\lyricsbs{Monolith Deathcult}{Seven Months of Suffering}{
  Those who speak in tongues of distemper\\
  purify us in black flames.\\
  The fire-spitting demon Azazel\\
  spreads his blackened wings.\\
  The earth is drenched in the blood of Goliath.\\
  Seven months of suffering.}

They keep praying desperately. 

\lyricsbs{Monolith Deathcult}{Seven Months of Suffering}{
  Lord Ba'al, creator of our fertile earth,\\
  majestic father and king of gods and men.\\
  Master of the mountains, ruler of the rainstorms,\\
  we bow down before thy splendour.
  Lord Ba'al-El, god of life and fertility!
  Intermit the continual combat with the god Mot.\\
  Show the leech of Yahweh thy might,\\
  and slay the Hebrews and their ravaging god.
  
  ... and [Yahweh] \quo{ravaged and smote} \\
  the Philistines of Ashdod and its territories \\
  \quo{with tumours} for seven horrible months.
}

\lyricsbs{Hate Eternal}{Thus Salvation}{
  Pray for salvation, pray for absolution.\\
  These are the days of great lamentation.\\
  So we may be again as one.\\
  We are cursed by this plague.\\
  We are cursed by this travesty.\\
  Yet we shall rise above the depravity of man.\\
  Thus salvation!
}

The rebels confront them with the truth. 

\lyricsbs{Hate Eternal}{Thus Salvation}{
  Reveal thyself, dare not to deceive me.\\
  See what I see through these eyes of flame.\\
  You must believe in thy ways.\\
  Divulge to me, confessor of all that is holy.
  
  Prepare thyself, for you know not what I am.\\
  See what I see through these eyes of flame.\\
  You must choose your path wisely.\\
  Inevitable your descent into black.
}





\subsubsection{Ramiel kills a champion}
There is a \Merkyran{} champion whom \Zachirah{} wants to kill. 

\lyricsbs{Vital Remains}{Behold the Throne of Chaos}{
  Antagonist, come forth and defy my bloodwar \\
  at the first light of dawn. \\
  Crowned lord beheaded before me, glimpse your God dethroned. \\
  Iconoclast, the glorification of darkness, all is gone. \\
  He is dead.
}

But Ramiel demands the honour of slaying him. 
\Zachirah{} acquiesces and gives Ramiel his blessing. 

\lyricsbs{Vital Remains}{Behold the Throne of Chaos}{
  Pureblood of iniquity, \\
  unfurl the wings of infamy. \\
  Seraph enthralled by desecration, \\
  our bloodwar towards completion. \\
  Purgate all thought on divination, \\
  the knell tolls on forever. \\
  Lightless, amid empyrean collapse, \\
  behold the Throne of Chaos. \\
  Lightless, amid empyrean ablaze, \\
  behold the Throne of Chaos. 
}

Ramiel prevails and rejoices, drunk on victory and enraptured by the destruction. 

\lyricsbs{Vital Remains}{Behold the Throne of Chaos}{
  Deify my imperious vehemence. \\
  Their kingdom burns in flames. \\
  The ashes of God I bequeath, \\
  beneath our feet, defiled.
}

\Zachirah{} gloats. 

\lyricsbs{Vital Remains}{Behold the Throne of Chaos}{
  They weep in the Sign of the Horns, \\
  glory to blasphemy of idols. \\
  Satanic Millenium, upheaval. \\
  Let the joyless be adorned with horns.
}









\subsection{Driven by hate}
\Damiarch{} was lots nicer about stuff. 
His ideals were enlightenment and fulfillment of his people's true potential. 
But \Azraid{} and \Zachirah{} preach hate and destruction. 

\lyricsdimmuborgir{Gud's Fortapelse\dash{}\AA{}penbaring Av Dommedag}{
  Hengitt er vi til M\o{}rkets keiser, \\
  den allmektiges kraft\\
  (som) f\o{}rer v\aa{}rt sinn i kamp\\
  mot godhet og l\o{}gn.
  
  Dog fiendens h\ae{}r er fattig, er den stor.\\
  Men vi skal ta dem alle og hente dem inn,\\
  en etter en.
  
  Det h\aa{}p de ser i Gud\\
  skal forsvinne i et hav av torner.
  
  Himmelen skal rakne, \\
  og en fandens torden skal buldre \aa{} brake.\\
  Hans krefter vil r\o{}yne, \\
  der M\o{}rkets front beseirer lystes pest.
  
  \O{}yne vil renne i sorg\\
  n\aa{}r de innser (at) deres Gud ikke lenger kan hjelpe.\\
  Det h\aa{}p de s\aa{} i Gud \\
  er svunnet og vekk for alltid.
}

\lyricsdimmuborgir{Avmaktslave}{
  Stanken fra den uransaklige vei,\\
  hvor forkynnelse og falsk forh\aa{}pning er \aa{}te,\\
  trenger igjennom som en bitterhetens gave\\
  og befrukter den menneskelige r\aa{}te.
  
  Retrett. Du har ei livets rett.\\
  Retrett. Du har ei livets rett.
  
  For ignoreres Dyret og idolets tegn\\
  vil straff omsider den skyldige bifalle.
}

\lyricsbs{Aeternus}{Slaying the Lambs}{
  Mother Earths men march.\\
  The power of Darkness\\
  glows in their blackened eyes.\\
  The lies of Christianity\\
  shall no longer be heard.\\
  Not ever again shall our world be branded\\
  by lies.
}





\subsubsection{They lose their innocence}
They are frenzied, obsessed with the need for destruction, and cannot stop even if they wanted to. 
Their vampiric nature has consumed them. 
This is the point where the \resphan{} people loses its \quo{innocence}. 
After this, there is no turning back. 
After all the atrocities they have committed against their own culture, the invasion of \Tembrae{} seems trivial. 

\lyricsdimmuborgir{In Death's Embrace}{
  By the light of the Moon\\
  and the beings of the night,\\
  a curse has been laid upon us: \\
  To seek and tear celestial gloss to pieces.
  
  By the power of Death\\
  and the shadow of the Reaper,\\
  a call has been brought upon us:\\
  To complete the infinite fall of Heaven.
}









\subsection{Angels and iconoclasm}
Maybe have some \uber-angels on the \Merkyran{} side. Perhaps these are the \hs{Voices of God} in physical form. 

They draw their power from some idols, statues, monuments, or even tablets of writing. Have a scene where a dark one, perhaps \Azraid{} or \Ramiel, or even \Sithiyacaan, destroys these icons one by one and watches as the angels weep and weaken. 

Perhaps the angels are not \uber{} at all, but powerless and forced to watch. 

Compare to a scene in \FLuneNoireVol{11} (I think). 

\lyricsbs{Monolith Deathcult}{1567 - Under The Bloodcampaign}{
  Yea, we pull down the images of the false church.\\
  We pillage the temples of the popery.\\
  Defacing the paintings and tapestries of ancient Rome.\\
  With a fierce contempt we destroy the symbols of the dishonest.
}

\Zachirah{} laughs as he destroys the \Merkyran{} faith. 

\lyricsbs{Monolith Deathcult}{Forest of Flesh}{
  Bow for me, pathetic mortals, your God is dead for ages,\\
  impaled like thousands of your despised people.\\
  Eyes gazing glassy and vacant at the bloodred sky.\\
  Violently condemned to see your dying God above.
}









\subsection[Merkyrah falls]{\Merkyrah{} falls}
\target{Rebels conquer Merkyrah}
Eventually the dark siders win and conquer the entire \resphan{} civilization. 

They rejoice in their evil. 

\lyricsdimmuborgir{Mourning Palace}{
  Whispering voices, summoning screams.\\
  Waiting for Satan to bless their sins.\\
  Blackhearted angels fallen from grace,\\
  oossessed by the search for utter darkness.
}

They mock the empire as it falls.

\lyricsdimmuborgir{Kings of the Carnival Creation}{
  Sense the withering eternity as it fades away.\\
  The ultimate graceless voyage of all times.\\
  Only death will be guarding your angels, silently.\\
  Cripples joining arms in clamour.\\
  Institutionalized for the rebirth, the herd will be hunted.
}

\lyricsbs{Aeternus}{Wrath of a Warlord}{
  Manipulation!\\
  Open your eyes and see your failure.\\
  The whirlwinds of my destiny.\\
  Blackened might.\\
  The eternity has no throne for you.
  
  You pretended to be a god.\\
  You carved lies into minds.\\
  Now the lies shall die with you.\\
  I will show you the face of a god.\\
  The wary lust for torture\\
  roars inside of me.
  
  Now you will die.\\
  The whirlwinds of your destiny.\\
  Feel the blade of fire\\
  as it cuts your mortal soul.
  
  Fragile souls yet blessed by eternity.\\
  Find strength in unity.\\
  There is none above and none beneath.\\
  You are the gods,\\
  the lords and queens of darkness\\
  and glorified immortality.
}

They revel in the darkness as they destroy the last remnants of \Merkyrah{}. 

\lyricsbalsagoth{The Thirteen Cryptical Prophecies of Mu}{
  Ah, the Alpha and the Omega.\\
  As all life was created from Chaos...\\
  so shall it be DESTROYED!!!
}

Especially the \Mystraacht{} rejoice in the evil they have wrought. 
They celebrate their infernal glory. 

\lyricsbs{Vital Remains}{Unleash Hell}{
  To the almighty of this godless land. \\
  For our brothers who bled upon the earth. \\
  For the warriors of the bloodwar who stand triumphant: \\
  The raised fist of domination, our final act of hate. \\
  Hail to us, to blasphemy!
}

\lyricsbs{Vital Remains}{Rush of Deliverance}{
  Choosing the one with the infernal horns. \\
  The one with black wings proudly soars \\
  across the path you've wandered upon. \\
  See your monuments of faith charred. \\
  In Satan we trust... Satan, Satan, Satan, Satan. 
}





\subsubsection{\Nyx{} becomes a dark ruin}
In the process of the war the beautiful cities of \Nyx{} are devastated and become a dark ruin. 

\lyricsbs{Vital Remains}{Scrolls of a Millenium Past}{
  Burning churches to the ground.\\
  Unearthly desolation, all is black.\\
  Bones stand tombless as their flesh.\\
  Crackling flames wither away.\\
  All remains covered by dust.\\
  Funeral piles, the war must go on.
}





\subsubsection{They must corrupt the people's faith}
Now the rebels must corrupt and break the people's faith in the \Merkyran{} religion. 

\lyricsbs{Vital Remains}{Scorned}{
  The balance of faith has been shifted. \\
  Consumed by the light, vehement for deliverance\\
  spreads the contamination within the righteous, \\
  leading them towards the abyss of blood and wickedness. 
}

\lyricsbs{Vital Remains}{Infidel}{
  Victory by vehemence. The conquered shall feel our steel. \\
  Implode the structures of religion.\\
  All faith in god collapses. \\
  Your shrine of gold has rusted away.
}

\lyricsbs{Vital Remains}{At War With God}{
  Insacred vision. The horrific truth revealed. \\
  For those who sought, impurity has taken.  \\
  No light shall shine for thee. The flock of mockery. \\
  At the end of all life. \\
  Never to praise the worm. Maggot of the holy. \\
  Scourge of all life. Ravager of the weak. \\
  Blood is no worth to those who shall reap. \\
  End their time of peace.\\
  End their fucking time of peace now. 

  The coming of eternal war. \\
  Prepare for the end of your divine image. \\
  Swarming the faithful. \\
  Crushing the unity of all that is holy. 
}

Some believers mourn. 

\lyricsbs{Vital Remains}{Infidel}{
  Bedarken the sight of Paradise. \\
  Mourn the thought of hope departing. \\
  To walk the path of the righteous slave, \\
  forever dragging the chains of torment.
}

Faith finally dies. 

\lyricsbs{Vital Remains}{Devoured Elysium}{
  The veil of lies is lifted from their blinded eyes. \\
  Ceaselessly devoured Elysium. \\
  Your truth was torn from the womb of Mary. \\
  The word of God slowly dies.
}

The \Merkyrans{} realize that their faith is a lie. 

\lyricsbs{Vital Remains}{Devoured Elysium}{
  As dusk reveals the remains of the kingdom, \\
  the structures of faith collapses before you. \\
  Use his name in vain again and again. \\
  My flesh and blood will never be yours.
}





\subsubsection{Soon they will summon the \banelords}
Soon the rebels would be able to summon the \banelords.
They looked forward to that. 


\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  DeathspellOmega
}{
  Odium Nostrum
}{
  Odium\\
  Oh Merciless Hatred;\\
  Burn the Me in me,\\
  And thus every cell of humanity.\\
  May the essence of impurity redeem my soul\\
  Unleashed hatred be my salvation and thy ghoul
  
  Worship, honour, glory, blessing,\\
  Odium, we offer unto Thee.\\
  Young and old, Thy praise expressing,\\
  In glad homage bend the knee.\\
  All demons in hell adore Thee;\\
  We would bow before Thy throne.\\
  As His angels serve before Thee,\\
  So on earth Thy will be done.\\
  Wherefore He also hath highly exalted it, \\
  and given it a name which is above every name:
  
  That at the name of Odium every knee should bow, \\
  of things in heaven, and thing in earth, and things under the earth;\\
  And that every tongue should confess that Odium is Lord, \\
  to the glory of Satan our Master.
}






















\chapter{\SecondbanewarBook}
% The story of the \secondbanewar, called the Incursion by the \resphain. 















\section{The \Resphain{} Prepare}
\subsection{The \Baelzerach{} schism}
Among the dark ones there was now a schism. They knew that they were spawned by \quo{Chaos and Darkness}. They disagreed over which parent was more important, Father Darkness or Mother Chaos. The majority voted for Darkness, but a minority held Chaos as the superior force. 

This faction became \Baelzerach. They split off from the other \resphain. 

Perhaps they followed a Satan-like god, or a super-powerful \resphan{} lord. And maybe his sexy daughter? Compare her to Lillith from \authorbook{\Francois{} Marcela Froideval}{666} (comic book series). 

The \Baelzerach{} did not fight against the \dragons{} in the \secondbanewar{}. Perhaps they even took the side of the \dragons{} (who were Chaos-aspected). Thus they became, and remained, far more friendly with \dragons{} than the rest of the \resphain. 

\Ishnaruchaefir{} would go on to have \hr{Ishnaruchaefir and Baelzerach}{dealings with \Baelzerach}. 

%\Baelzerach{} splits off from the other evil \resphan{} factions. 

The \Baelzerach{} begin to invoke Chaos: 

\lyricsbs{Marduk}{Accuser/Opposer}{
  Accuser! Accuser!\\
  Exhaustless fountain of poison divine!\\
  I ate of Death to cleanse my flesh of God,\\
  to make me thy entrance to the veins of the world.\\
  Now as we turn to seek thy face,\\
  pour down on us thy redeeming wrath.
  
  Opposer! Opposer!\\
  Core, marrow and essence of my Will!\\
  I renounce this flesh in the name of thy praise,\\
  to kindle the coals of Salvation's spring.\\
  I drank of hell to cleanse my soul of God,\\
  to reach the light in which thou dwellest.
}







\subsection{\KiriathSepher{} ascendant}
\target{Kiriath-Sepher founded}
The remaining \resphain{} form the kingdom of \KiriathSepher{} to replace fallen \Merkyrah{}. (The other \resphan{} kingdoms later branch off from here.)

The conquest of \Merkyrah{} and the rise of \KiriathSepher{} paves the way for the \resphan{} race's ascent out of ignominy and into the glory they feel they deserve. 

\lyricsbalsagoth{The Thirteen Cryptical Prophecies of Mu}{
[THE HIGH PRIEST OF MU:]\\
Ascent to ecliptic! Mu and Poseidonis!

[THE CHIEF CULTIST OF ZURRA:]\\
The Emperor commands... Uroboros to rise!
}

The regular \resphain{} are frightened by the new darkness. 
They turn to \Azraid-tachi for leadership and guidance. 

\lyricsbs{Monolith Deathcult}{Cathedral of Corpses}{
Beneath the shadow of thy throne \\
still may we dwell secure.\\
Suffering is thine arm alone \\
and our defense is sure.
}

\Azraid{} uses the \ashenblooded{} as artificial scapegoats. 
He wants to create a ranking system so the \resphain{} will feel good. 
Or something. 

\lyricsbs{Monolith Deathcult}{Cathedral of Corpses}{
My word commands your flesh to dust: \\
\quo{Return, ye sons of men!}\\
Immortals rose from earth at first \\
and my blood will live again.
}





\subsubsection{\KiriathSepher{} adopts \Merkyran{} traditions}
\target{Azraid adopts Merkyran imagery}
Under \ps{\Azraid}{} command, \KiriathSepher{} adopts much of \ps{\Merkyrah}{} imagery, aesthetics and perhaps even philosophy. 

\Azraid{} defends this, saying that the new empire must not reject everything that the people know, lest the people become unruly and difficult to control, and the empire grow inefficient.

Other \resphain{} object to \hr{Azraid's pragmatism}{\ps{\Azraid}{} pragmatism} and claim that he should be more true to the ideology of \quo{Darkness and Chaos}. This is one of the reasons why the \resphan{} clans split off from each other.

The other rebels also believe that they should reveal the entire truth to the people. But \Azraid{} wants to still keep many things hidden from the people and let many lies live on. The others protest, but acquiesce to \ps{\Azraid}{} plan. But it makes them bitter, and division is sown among the lords of \KiriathSepher. 









\subsection{They look forward to fighting \dragons}
The \resphain{} remember the \hr{Merkyran myths of Dragons}{\Merkyran{} myths of \dragons}. 
They are aching and excited to finally face these \dragons{} in combat. 
They want to take back what was once theirs. 

\lyricsbs{Aeternus}{Possessed by the Serpents Vengeance}{
  Your wrath coiled around the earth.\\
  Your venom courses it veins.\\
  Strike at their fear.\\
  Destroy their kingdoms\\
  with your poisonous rage.
}

\lyricsbs{Monolith Deathcult}{Demigod}{
  The great Persian serpent lies in wait.\\ 
  Let us face his army of immortals. \\
  We shall butcher those hunters of men's souls \\
  and crush their nimbus of immortality.
  
  A beast is approaching us. \\
  Its magnitude will blot out the Sun. \\
  We shall drink Persian blood \\
  and find our glory in the final arrow hail. 
  
  We blaspheme the tyrant.
  
  Under the banner of [\Mystraacht]. \\
  For the eternal glory of [\Nyx]. 
}









\subsection{They learn \Draconic}
The \resphain{} learn some of the \Draconic{} tongue from the \banelords{} (who have been monitoring \Miith{} for millennia), so that they can communicate and deal with their foes. 
They also study the \psp{\dragons}{} magic, weapons, physique, psychology and culture, so they are better equipped to fight them. 









\subsection{\Resphain{} come to \Tembrae{} in spaceships}
\target{Resphain come down in spaceships}
\index{technology!\bane}
\Merkyrah{} was not in \Tembrae{} but in \Nyx. 
The \resphain{} of newly-formed \KiriathSepher{} had to travel to \Tembrae{} in spaceships (\hr{Bane technology}{\voyager{} relics}). 

So they came to \Tembrae{}, descending from the sky in chariots of fire, like the gods they were. 
They conquered the primitive, savage \humans{} living there. 

Since then, \humans{} have had myths about how the gods (\resphain) came from the sky/stars in burning ships or chariots, to liberate them from the depredations of the wicked \dragons{} and their spawn.





\subsubsection{Population}
At this time, the total population of all \resphain{} was in the range of 100,000--200,000. 





\subsubsection{They marvel at the \Wylde}
\hr{Merkyrah is one huge city}{\Merkyrah{} was one huge city}, so the \resphain{} had never seen \Wylde{} nature before. 
They marvelled at the sight, but it also frightened them. 
Some of them became convinced that this new world was a savage, backward land that they must conquer and civilize. 

Yet others simply enjoyed the beauty and coolness. 

\lyricsdimmuborgir{Stien}{
  Her gandviks bergtroll trampet frem\\
  i ondt og stort et tussefolge.\\
  Hvor ferdafolk fant stor en visdom\\
  om landets skogsliv og m\oe rke sider,\\
  Her p\aa{} stien som bukter seg uendelig frem.\\
  Mellom berg hvor de vanskelig fremdeles\\
  kan \oe ynes i horisonten.
  
  Sa storslatt det m\aa{} ha v\ae rt\\
  og speide ut over alt dette\\
  og a vandre sa alene og fri.\\
  En hostkveld i en kald og lett t\aa ke,\\
  slik som mange for meg har opplevd\\
  og som mange for meg har verdsatt.
}

Nature was both frightening and compelling to them. 
They could sense the immense power and life force around them. 
See, \Nyx{} was \hr{Nyx is far from the Heart}{farther removed from the Heart of \Miith}, and therefore it could not be felt to the same extent. 
\hr{Nyx is a parasite Realm}{\Nyx{} lived by leeching off this life}, but here in \Tembrae{} it could be felt in its undiluted form. 

\lyricsdimmuborgir{Stormbl\aa{}st}{
  Glatt er runen p\aa{} det h\o{}ye fjell,\\
  gnidd vekk av regn og vind.\\
  Dragende kraft av ondskap lurer\\
  her ved trollheims muldne grind.\\
  Fortumlet av dette m\o{}rke byggverk,\\
  med r\o{}vet gull fra lyets pakt,\\
  brukt som spott til \aa{} senke deres murer.
  
  Vi grunder over dette riket,\\
  s\aa{} vakkert fylt med tidel\o{}s skumring.\\
  Som en stjerne i tomsindighetens juv,\\
  det bringer frem en nattlig mimring\\
  over tanker fra en vissen tid.
}

They want to conquer this new, beautiful Realm. 

\lyricsdimmuborgir{Stormbl\aa{}st}{
  Der sorg har beseiret alle gleder\\
  og bygd et land p\aa{} menneskets jord,\\
  fylt med isklad prakt og heder.
}







\subsubsection{The savage \humans}
\index{technology!\human}
The early \humans{} who escaped the fall of \ps{\Semiza}{} kingdom and fled into the wild formed their primitive tribes. They were barbarians, stone age level, or bronze age at best. \Humans{} are too stupid to create any non-trivial civilization on their own. They only gained more technology when the \resphain{} came and took control. If they had bronze age technology, then it was stolen from the \scathae. 

\lyricsbs{Monolith Deathcult}{Origin}{
  Risen from the seed of Enki\\
  with consent of the God-father Anu.\\
  We are the working race,\\
  created in the temples of SCH.RUPPAK.

  The Masters ride the midnight sky\\
  in their lucent chariots of thunder.\\
  Those who behold the radiant face of the Gods\\
  died eyeless, scorched and ablaze.
  
  And God-slaves we are,\\
  suffering in the mines of our Masters.\\
  We populate the fields of E.DIN,\\
  the base of the Gods from Nibiru-Pha\"eton.
}

The \humans{} did have \hs{myths} about \Thanatzil, \Semiza{} and the \resphain. 
They worshipped them as absent gods. 

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  I built temples, statues and pyramids \\
  as monuments of my endless might.\\
  Colossal knowledge lays hidden in tablets and shrines, \\
  protected by spells and incantations.
  
  Your history is not yours. \\
  I gave thee wisdom. \\
  I gave thee science \\
  and I delivered thee from bestiality.\\
  My name was carved in thousands of stones \\
  and diurnally murmured in deadly incantations.\\
  Atlantis was built when you amoebas crawled through filth. \\
  I am Holiness Divine, your Lord and Master, \\
  the Supreme God and Creator.
}

They have myths about a saviour god named \quo{Anatheal} or a variant thereof. 
This is a corruption of \hr{Thanatzil}{\Thanatzil}. 
According to myth, Anatheal came to them a thousand years ago to create an eternal paradise for \humans{} where they would live in bliss alongside his angels. 
But \humans{} were wicked and sinful, and they wasted Anatheal's precious sacrifice. 
Now they are condemned to live as filth, preyed upon by the \dragons{} and their spawn, until the day when Anatheal will return. 









\subsection{Hiding in \Nyx}
Perhaps the \resphain{} used \Nyx{} to hide their cities and lands from the \dragons{} while they built their empires. 









\subsection{They need the stargate}
The \resphain{} need \hr{Semiza's stargate}{\ps{\Semiza}{} stargate}. 
After \ps{\Thanatzil}{} fall, \hr{Semiza flung away}{\Semiza{} was flung far away} from the stargate. 
The \resphain{} must find, exhume and restore it. 

They must also find \Semiza{} again (since \hr{Rebels lose Semiza}{they lost him}). 

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  The sacred altars erected for the Sun-God \\
  point at the sky as a tremendous beacon. \\
  The Heavengate was sealed and buried forever. \\
  deep beneath the surface of the earth. 
  
  When the Portal is disinterred, \\
  and the Door to Heaven is unsealed again, \\
  then I shall return to restore my immense power.\\ 
  Thou shall be enslaved again.
}





\subsubsection{They find \Semiza}
They find \Semiza{} again. 
He tells them more about the \banes. 
Among other things, he tells them about the \hr{Bane telekinesis}{\banesz{} tactile language} and how that ties in with their names (like \quo{\hr{Daggerrain}{\Daggerrain}}). 









\subsection{\Resphan-\aryoth{} alliance}
\target{Resphan-Aryoth alliance}
The \aryothim{} and \vorcanths{} had often warred against the \dragons, and the \quiljaaran{} for that matter. 
Some \resphain{}, having caught wind of this, recognized the \aryothim{} and \vorcanths{} as potential allies and sent a delegation to find some of their great and respected elders. 
Ramiel and \Shiaraid{} were the leaders of this delegation. 

They managed to sway many of the \aryothim{}, who joined their war, but only few of the \vorcanths{}. 
Most \vorcanths{} elected to remain neutral. 

During the war there were several \aryoth{} kings and chieftains who fought and argued among each other over how they should act in the war, on which side they should fight and under which conditions. 
They were as diverse as any other race. 















\section{The \Sathariah{} Project}









\subsection{\Dragons{} wonder why the Heart is weak}
\target{Dragons wonder why the Heart is weak}
The \hr{Heart}{Heart of \Miith} began to \hr{Heart weakened}{weaken} as soon as the first \resphain{} were born, and it \hr{Merkyrah strained the Heart}{became worse as the \Merkyran{} population grew}. 
Gradually, the \dragons{} became less and less fertile, and fewer live children hatched. 
But the \banelords{} had hidden \hr{Merkyrah}{\Merkyrah} well, so the \dragons{} couldn't figure out what was causing it. 
For thousands of years they grieve and research and try to find out why their eggs die, but they can't find anything conclusive, only some vague astrological \hr{Matrix}{\matrix} mumbojumbo. 

Only when the \resphain{} reveal themselves do the \dragons{} piece together the true answer.   









\subsection{Awakening the \banelords}
%They create the \resphain. When they have enough \resphain, they blast open the doorway from \Nyx{} into \Miith{} and march forth, proudly announcing to the world the beginning of the \secondbanewar. 
%The \hr{Resphan rebellion}{rebellious \resphain} have conquered the \hr{Good Resphan Empire}{previously good \resphan{} empire}. 
The dark ones are victorious and now control the \resphan{} empire. 
%They now reopen the gate to \Nyx{} and summon \banes{} to their aid. 

In the beginning, they waged wars with \dragons{} and their ilk here and there, but nothing out of the ordinary. The \dragons{} knew that a new religion had risen to prominence among the \resphain, but paid it little heed. Very few \dragons{} suspected that the \quo\banes{} whom the \resphain{} now worshipped as their creations were the same as the ancient foe of \dragonkind. They simply believed that the \resphain{} had discovered some new magic and concocted a fictional mythology to surround it, as so many cultures had done before them. So they still wasted their strength on internal wars. They did not fear the \Nyx-aspected magic, for it had existed for thousands of years and never been a real threat to the \dragons. 

%They resume contact with the \banelords{} and summon \banes{} to their aid. When they have enough strength, they blast open the doorway from \Nyx{} into \Miith{} and march forth, proudly announcing to the world the beginning of the \secondbanewar. 
But at last the rebels succeed in penetrating the \hr{Crystal Sphere}{\CrystalSphere} and contacting \Daggerrain. They have high expectations of the \banes{}. 

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  The Abyss yawns wide... Claws sharpened on the dead.\\
  The Abyss yawns wide... Ensanguined fangs agleam.
  
  Great shadow, awaken and eclipse the suns of a thousand worlds...\\
  Slumbering 'neath these crimson vaults, \\
  behold the majesty of the Outer Darkness!\\
  Praise the Z'xulth!
  
  Fell Worm of the Black Galaxy, \\
  awaken and descend without pity upon the Tellurian sphere!\\
  Destroy the flaccid priests of the newborn usurper faiths.\\
  Sweep away the thralls of the cruciform stave!\\
  Crush the lackeys of the corrupted hexagram!\\
  Devour the slaves of the eastern crescent!\\
  Crush them, grind them, slay them all!\\
  Plague-blessed, flay them alive!
  
  Now, behold in terror what waits beneath the crimson vaults of Cydonia...
}

\lyricsbalsagoth{The Empyreal Lexicon}{
  Fear is the power... Terror is the key!\\
  X'atham-ry'aa... Tha'zai-tonn!\\
  I am replete with sovereign mastery!\\
  The portals to the Outer Darkness yawn wide once more!\\
  They-Who-Lurk-And-Breed-In-Limbo are free!}

The \banelords{} had been imprisoned in \Nyx{} for thousands of years, forcing to sit idly by while the \Merkyrans{} tapped their power and called it \quo{God}. 

\lyricsbalsagoth{The Voyagers Beneath the Mare Imbrium}{
  From a time beyond time, we come.\\
  We, who once crested the waves of the great astral sea...\\
  and who now must strive again for the domination of the stars...
  
  The great lunar seal is broken.\\
  We are free... free to rule!
  
  For more than ten times a thousand years\\
  have we slept beneath these cratered, lifeless stones...\\
  The Lexicon's crystalline core has at last been reactivated...\\
  We have heard the sighing of a thousand souls...\\
  now at last we shall hearken once more to the siren call of the cosmos.}

The \banelords themselves are unable to come through, but they can communicate with the \resphain{}, and they can send \lesserbanes{} to their aid. 

The \resphan{} lord gathered their strength, consolidated their sovereignty over their race, as well as the \humans{} and the few surviving \nephilim, now slaves. And they laid plans\dash against the \dragons, and against each other. They also received technology from \Erebos, and they did research to refine it and create new technology. 

\lyricsbs{Hate Eternal}{Catacombs}{
  Rise up from the ancient tombs. \\
  Grant us all your infinite wisdom. \\
  Endure as you rise from the catacombs. 
}

\lyricsbs{Hate Eternal}{The Creed of Chaotic Divinity}{
  Awakened by this ancient creed. \\
  Evoked, the ancestry of thee.\\
  Forsaken for centuries of times. \\
  Exiled, all of their kind. \\
  Foretold, the inheriting of the Earth.\\
  Forewarned of this predestined rebirth. \\
  Engaged, the rising from below.\\
  Fear, all mortals, for what they shall bestow.
  
  Conjure all, so that they may sustain\\
  their race, of what they must retain.\\
  Spew forth incantations in vain. \\
  Invocate all that they try to negate.\\
  Enchant all of their wonderful splendour. 
  Recant all of the texts that are sacred. \\
  Recreate all that has been begotten. \\
  Revive all that has been forgotten. 
}

\lyricsbs{Marduk}{The Black Tormentor of Satan}{
  When the dark clouds in the sky open,\\
  a thousand eyes burn in the night.\\
  A kneeling shape in a void of fire \\
  gazes out over this world.\\
  Within a blink of an eye\\
  a gruesome face looks down from the sky\\
  on this world where darkness soon will reign\\
  and the people shall meet their new King.\\
  That night will be the one\\
  that will open the gates to the realm beyond\\
  and the wings of funeral will take my soul\\
  and complete the eclipse of my heart.
}





\subsubsection{\Mystraacht{} are especially eager}
\Zachirah-tachi were especially eager to meet their \banelords. 

\lyricsbs{Emperor}{My Empire's Doom}{
  Once our lord has come again, \\
  all black hearts will celebrate \\
  the darksome fiend \\
  in the kingdom of sorrow. 
  
  Nocturnal fiends, \\
  the beings of the night and shadows \\
  calling forth the pure spirit \\
  of the night.
}









\subsection{The \Sathariah{} project}
The \resphain{} and their \bane{} masters lay sinister plans to gain more power. The \resphain{} already possess some measure of Chaotic power, but they crave more. To do this they needed \draconic{} blood. 

After much preparation\dash decades, perhaps\dash the \resphain{} are ready. They have concocted an elaborate plan to capture one of the \shaeeroths{}, slay him and used his blood and life-force to empower their new generation of \resphain\dash the \hr{Sathariah}{\satharioth}, who would go on to become the mightiest of them all. 

%So in an elaborate plan, the \banes{} captured the \dragonking{} \Nexagglachel{}, killed him and used his blood and life-force to empower their new generation of \resphain, who went on to become the mightiest of them all. Ramiel and \Shiaraid{} belong to this group. 
They set their eyes on \Ishnaruchaefir.







\subsection{\Ishnaruchaefir{} has premonitions}
Somehow, \Ishnaruchaefir{} has premonitions. 
Perhaps he uses divination magic. 
He sees visions of being betrayed, imprisoned, tortured and slowly killed. 
He sees his body and soul being cut into pieces and devoured by ravenous horrors (the would-be \satharioth). 
He sees himself impaled on a tree of thorns, his blood drained and his flesh peeled off in strips. (See section \ref{Nexagglachel in captivity}.) 
He sees visions of death, eternal war and the destruction of the world. 

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  By the Onyx Sceptre of my forefathers,\\
  the air is churning\\
  with auguries of dethronement,\\
  impending doom thus prophesized.
  
  In a dream I was bade ride the argent-eyed unicorn to the Ring of Stones.\\
  There a torrent of viscid slime assailed me\\
  as pipes and horns sang the clarion of my dissolution.
}

\lyricslimbonicart{Suicide Commando}{
  In the shadows of the world's ambitions \\
  I see life and death, in an enormous collision. \\
  Light destroys what dark creates. \\
  Forever floating, the dark rivers of the heart. \\
  Lifeless drifting, in an orbital decay. \\
  A vicious circle of extinction. \\
  The soul reaches the state: Oblivion.
}

\lyricsduana{thisistheend}{This is the End}{
  I see field upon field upon field \\
  of bloatd-cattle-corpses bleeding intestines \\
  staring with sightless opaque eyes \\
  of waves drowning mountains \\
  and the earth's flesh torn with angry fissures \\
  of molten-spewing-spittle \\
  and hot lashing tongues \\
  of a planet roaring/quaking/quivering \\
  with unbound vergence 
  
  shivers erupt through space and time \\
  and images flashing faster faster... \\
  until finally all is annihilated 
  
  like a vacuum space sucks the debris \\
  into a black empty hole \\
  and I fall down into the void \\
  this is the end
}

Also compare to the visions of Hell in the movies \emph{Hellraiser} and \emph{Event Horizon}. 

The reason why it is \Ishnaruchaefir{} and not \Secherdamon{} who sees these visions is twofold:

\begin{enumerate}
  \item 
    It is \Ishnaruchaefir{} who is the \ps{\resphain} intended target.  
    They have already began weaving subtle spells to entrap him. 
    These spells are not quite subtle enough, and he picks up on them. 
  \item 
    \Secherdamon{} was always very goal-oriented and focused his research on the \xss. 
    \Ishnaruchaefir{} was focused and had a wider range of interests. 
    He tended to gaze out into the universe rather than narrowly into the \psp{\dragons}{} past. 
    He cared about the cosmic gods and the more elusive mysteries of existence\dash mysteries that might have no solution at all, and might have no practical application even if solved. 
    (\Secherdamon{} ignored these questions for those reasons.)
    
    \Nexagglachel{} was not so much into sorcery. 
    He was more absorbed in earthly matters of politics. 
    
    This made \Ishnaruchaefir{} more sensitive to alien things than his brothers, so he could feel these dreams when the \resphain{} approached. 
\end{enumerate}








\subsection{\Ishnaruchaefir{} seeks the advice of elders}
\Ishnaruchaefir{} dreads this horrible fate. 
He seeks out wise elder \ophidians{} and \nagalords{} and asks for their advice. 



\subsubsection{Searching for the elders}
He goes to a dark, menacing place where these elders live. 
Perhaps this place is a \hr{Black pyramids}{\quo{black pyramid}}, as in \bandsong{Bal-Sagoth}{Shadows 'Neath the Black Pyramid}, or an ancient, cyclopean castle, as in \bandsong{Bal-Sagoth}{Into the Silent Chambers of the Sapphirean Throne (Sagas from the Antediluvian Scrolls)}.

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  The king was compelled to lead his forces to the shadow-haunted Mountains of the Dead, a grim and brooding place steeped in dark and ancient legendry. Alone he rode into the gaping maw of a huge cave hewn into the side of the tallest mountain co untless ages past by unknown hands.
}

\lyricslimbonicart{Lycanthropic Tales}{
  As the storm looms over the frozen landscape:\\
  A call from the beginning of time,\\
  out of darkness through the mist.
  
  Requiem in blood and fire.\\
  Symbols of occult desire.\\
  Through the cosmic vortex,\\
  the gate to unknown darkness.\\
  An esoteric voyage to eminent discovery.\\
  I am the deathlike shadow,\\
  architect of black mysteries.
}





\subsubsection{The elders' advice}
The elders are expert diviners and are able to show him more detailed visions of the future... a future full of darkness, blood, death and eternal war. 

\lyricstitle{Warhammer 40,000}{%
  In the grim darkness of the future, there is only war.
}

\lyricsbs{Bal-Sagoth}{%
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire%
}{%
  I shall seek the counsel of the sorcerer, \\
  keeper of the ancient scrolls of wisdom, \\
  and the Crystals of Power...
  
  My liege, great and regal king... \\
  the mists disclose their secrets...\\
  Drink deep of the potions of the apothecary, \\
  for upon thee now I bestow \\
  a shard of the mystic Crystal of Mera... \\ 
  sacred artefact of the Atlantean mages, \\
  won in battle by our legions.\\
  My liege, the Crystal of Mera shall unveil the truth \\
  lurking hidden in thy most fever-haunted dreams...
  
  The land awash with spilled blood, \\
  and viscera torn forth from the sundered dead... \\
  Gorge the earth with flesh darkened with the claw and fang of war... \\
  rent open the ravenous maws of worms...
  
  The Crystal illumines dark secrets, the truth is known... \\
  a dire and ancient threat is ranged against me.
}





\subsubsection{He is one of few who can stop it}
\Ishnaruchaefir{} is told that he is one of the few who have a realistic chance of changing this fate. 
This is due to a number of things: 

\begin{itemize}
  \item He is fucking badass.
  \item He is a powerful \vertex.
  \item He is at the centre of \ps{\Daggerrain}{} plan, since he is the \dragon{} whom they plan to use for their \sathariah{} project. 
\end{itemize}

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
I saw beyond and into the warp. I saw the powers that dwell there... 

There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 

I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
All is grim darkness and all is war. \\
Only you have the power to stop this future. \\
You must be strong, Warmaster. \\
Never forget that.
}






\subsubsection{\ps{\Criseis}{} point of view}
\Criseis{} camps outside and finally sees her lord return from the sinister dwelling of the ancients. 

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  For three full days and nights he did not emerge from the cave... until, at last, he rode forth from the eldritch mountain once more, a terrible knowledge shadowed in his icy eyes...
}

Have flashbacks about this! Possibly from \ps{\Criseis}{} point of view. And later have some conversations where one of the elders reveal to a third/fourth person what transpired. (Yeah, \emph{Malazan Book of the Fallen} style.)





\subsubsection{Origin of the glaive}
Perhaps \Ishnaruchaefir{} gains or forges \hr{Ishnaruchaefir's glaive}{his glaive} here.

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  ... and bearing in his gauntleted fist a huge black sword, a magnificent ebon blade which no human blacksmith ever forged. Fearsome sorcerous power crackled within the yard of black steel, dancing upon its searingly honed, glyph-scored blade... and its bejewelled, dragon-carved hilt did whisper arcane secrets to the king in a strange, elder tongue.
}









\subsection{The Fall of \Nexagglachel}





\subsubsection{Capturing \Nexagglachel}
\target{Fall of Nexagglachel}
\target{Death of Nexagglachel}
\target{Origin of Satharioth}
In an attempt to prevent this dreaful fate\dash for himself and for the world\dash\Ishna{} seeks out his brother \Nexagglachel{} for help. 

Perhaps \Nexagglachel{} has seen similar visions, but was afraid to seem weak or mad in front of his backstabbing fellow \dragons, so he kept it secret. Compare him to King Leoric in the \emph{Madness of the Black King} story arc in the game \emph{Diablo}. 

The brothers fight against the \banes. \Ishnaruchaefir{} fights hard, both for himself and his brother, but in the end he fails. He lives, but \Nexagglachel{} falls instead. The \banes{} and \resphain{} are happy, having succeeded beyond their expectations and captured the mightiest of the three brothers, instead of just the second mightiest. So they use his blood, and the \satharioth{} are born. See section \ref{Nexagglachel in captivity}.





\subsubsection{\Nexagglachel{} in captivity}
\target{Nexagglachel in captivity}
\Nexagglachel{} was captured by the \banes{}. 
There he was tortured physically, magically and psychologically. 
He was crucified and impaled on a giant tree of thorns, and his blood and power was drained from him.

But through it all, he never surrendered, or even faltered. His pride and dignity remained intact, and he was able to mock his captors throughout his captivity, untill they finally killed him and drained the last of his life force and soul to create the \satharioth. 

See, as a son of \KhothSell{} he is, in a sense, an incarnation of Death. He fears neither death nor pain, and actively enjoys physical pain. So he laughs every time the \resphain{} ram another spike through his body.





\subsubsection{They taunt him}
Some of the wannabe-\Satharioth{} taunt \Nexagglachel. 

\lyricsbs{Vital Remains}{Entwined by Vengeance}{
  Ageless and obscure. \\
  Feel the burning in my heart. \\
  My eyes have seen the truth. \\
  Now my hands will tear your fucking God apart. \\
  
  In the name of Satan, \\
  our hate consumes the heavens. \\
  Decimate the holy land, \\
  for pain is now your savior.
  
  In this season of monumental horror, \\
  we hunger for heavenly termination. \\
  Of blood and war. We shall devour.
}





\subsubsection{His cold eyes}
\target{Nexagglachel's hatred}
\Nexagglachel stared back at the \resphain with his \hr{Nexagglachel's appearance}{cold, black eyes}. 
Even when he roared in pain and anger, his eyes retained their unfazed coldness. 
Remember, he was a \dragon, and \dragons relished combat, conflict, violence and pain. 
He enjoyed the challenge, even though he was convinced he was doomed. 
He was planning his long-term revenge. 

He told them: 
\ta{With every attack you only strengthen me.
  Every attack feeds my hatred. 
  The hatred that will devour you and your kind from within.
  I will be your downfall, \satharioth.
  Forever you will feel my cold eyes.
  Forever you will feel my hate.
  I will be the cancer that eats away at your being, until the day your people is destroyed.}

His pride drove his captors mad. 
They tried everything to break him, but to no avail. 
He was unbreakable. 





\subsubsection{\Nexagglachel{} and \Azraid{} reach an understanding}
\Nexagglachel{} and \Azraid{} look into each other's eyes. 
They both see the same fear manifested: 
The fear that the \banes{} will win and end up devouring both of their races in their hunger. 
They want to avoid that. 
To that end, both are willing to make any sacrifice. 

They reach a silent, unspoken understanding. 
They will work together in utmost secrecy in a \XanatosGambit{} that will take many thousands of years. 
Together they will overthrow the \banes. 

Maybe \Damiarch{} still lives at this point, and \Nexagglachel{} inspires \Azraid{} to kill him. 
But probably not. 





\subsubsection{He breaks free}
\target{Ishnaruchaefir gains stewardship}
\index{stewardship}
Through his captivity, the \resphain{} made sure to keep \Nexagglachel{} blocked so that he cannot telepathically contact the outside world. 

At one point \Nexagglachel{} escaped. 
He broke free of their block and managed to contact \Ishnaruchaefir{} and warn him of the \ps{\resphain} plan, so they could be ready for what is to come. 

He told \Ishnaruchaefir{} that he would die. 
He passed on the mantle of the stewardship of \Miith{} to \Ishnaruchaefir. 
It would now fall to \Ishnaruchaefir{} to lead the \dragons{} and defend the planet against invaders. 

He told \Ishnaruchaefir{} of \hr{Nexagglachel gets stewardship}{the time when \TyarithXserasshana{} had given \emph{him} the stewardship}. 
Now he would pass it on to \Ishnaruchaefir. 

\Ishnaruchaefir{} expressed his doubt. 
He was not confident that he was up to the task. 
He had always been a loner, not a social sort, and least of all a leader of an entire people. 

But \Nexagglachel{} was certain he could: 
\begin{prose}
  \Ishnaruchaefir: 
  \ta{I cannot do this. 
    \Raemyth, I am not thou!
    I own not thy strength!}
  
  \Nexagglachel: 
  \ta{Yea, \Quessanth. 
    Thou art stronger than thou knowest.
    Strong enough to do what must be done.
    Thou art the best of us.
    \Irocas{} is skilled, but brittle. 
    He possesseth not thy solid foundation.
    Thou must take leadership.}
  
  \Ishnaruchaefir:
  \ta{Very well, \Raemyth.
    I will do what thou askest of me.
    I accept the mantle of stewardship. 
    I will find in me the strength to do what must be done.
    I will not fail thee, brother.}
\end{prose}

This ended up \hr{Ishnaruchaefir's stewardship}{shaping \ps{\Ishnaruchaefir} life}. 


\Nexagglachel{} knew he was going to die. 
He did not expect to be rescued. 
So he went along with it. 
He plotted his own \XanatosGambit. 
He would live on as a ghost in the \satharioth{} and bestow upon them a curse to bring them down. 

Soon after, he was killed and his soul recaptured (his body regrows in captivity). 

Compare to the scene with Tai-Lung's escape in the movie \emph{Kung-Fu Panda}. 

\Secherdamon{} is hurt and angry that \Nexagglachel{} would choose to trust \Ishnaruchaefir{} rather than him, even after \Ishnaruchaefir{} failed him and was responsible for getting \Nexagglachel{} captured in the first place. 
This makes \Secherdamon{} doubly grim and ambitious and determined to prove his worth. 









\subsection{The birth of the \Satharioth}
\subsubsection{Some \satharioth{} die}
\target{Satharioth die}
Originally there were many more than thirteen \satharioth. 
Maybe there were around 30. 
But they underestimated \Nexagglachel, and when they siphoned power from him, he seized control, lashed back and killed many of them. 
Some of them died immediately. 
Others caught a wasting disease from the ritual and died soon after, mostly in gruesome pain and madness. 

He knew he could not kill them all, so he endeavoured to kill those he hated most, and some of those who could be the greatest threats (including \hr{Kezrabal}{\Kezrabal}). 

He tried to get rid of \Azraid, but failed. 
But he let \Zachirah, Ramiel and \Sithiyacaan{} live because he foresaw that they might cause trouble and dissension among the \resphain. 





\subsubsection{\Satharioth{} are born}
The \satharioth{} are born. 
Compare to the front cover picture of \artisttitle{Exmortem}{Berzerker Legions}. 

Each of them now contains a \hr{Fragments of Nexagglachel}{fragment of \Nexagglachel}. 

\Zachirah-tachi (the \Mystraacht) are ecstatic. 

\lyricsbs{Hate Eternal}{Born by Fire}{
  Born by fire now force thy ways. I am the entity.\\
  I hold the chalice, the praise of demi-gods, my oath to thee.\\
  Behold majestic strengths amongst the chosen ones,\\
  to desecrate, dominate all enemies that dare to rise.
  
  Impending visions of prophecies await the dormancy.\\
  To seek our path, the path of righteousness, eternal bliss.\\
  Possess the rites of time, to thee of virgin blood.\\
  Now desecrate, dominate the ones that shall be left behind. 
  
  We are the coming of the scorned messiah, apocalyptic seeds.\\
  The loathing of your arrogance ordained.\\
  In absence of the souls in withered lies, defeating all that stand.\\
  Conceration of the frail's demise.
  
  You'll submit to our immortal ways\\
  to only realize that we command.\\
  The armies of the dark shall form in flame, destroying forgery.\\
  You cannot fool the eyes of the gods.
}

They drink \ps{\Nexagglachel}{} blood and are filled with expectation of great, bloody success to come. 

\lyricsbs{Marduk}{Holy Blood, Holy Grail}{
  Empire of blood arise.\\
  Vengeance be our holy blood.\\
  Our holy grail. Kill all the frail.\\
  Be our holy blood, our holy grail.
  
  Vengeance is mine, says the Lord.\\
  And I believe him. I believe him. 
}









\subsection{The \satharioth{} begin to feel the curse}
Soon after their inception, the \satharioth{} begin to feel \hr{Curse}{\NexagglachelsCurse}. 
They begin to wonder if this whole project was a good idea.

\lyricslimbonicart{The Yawning Abyss of Madness}{
  Again I drift the halls of wondering. \\
  The black castle of solitude. \\
  On the very edge of sanity \\
  in mental cryogenic interludes. \\
  I have slipped into the seventh, \\
  the seventh circle of Hell, \\
  in realms where deadly shadows \\
  infest every cell. 
  
  Internal ceremonies in ritual death. \\
  External bleedings for the demon of madness. \\
  Hide from the torture of the dazzling light. \\
  The demolition voice shall speak tonight. 
  
  While I'm staring down into the darkest pit, \\
  an ocean black as the night, \\
  so infinite deep and consuming, \\
  it swallows all life force with might. 
  
  Again I drift the halls of wondering, \\
  as I focus for the darkness to come. \\
  In anguish minds uplift the conquering \\
  to cross the line of death beyond.
  
  An abstract reality and bottomless insanity. \\
  To search for the powers to please\\
  the subconscious spirit of disease. \\
  Time found no remedy, \\
  cause winds of darkness was stealing me. 
  
  The yawning abyss of madness. \\
  A cryptic slaughter by hate. \\
  Darkness is the only survivor \\
  as evil dominion terminates. \\
  The yawning abyss of madness.
}















\section{Open War}
\subsection{The \secondbanewar}
\target{Second Banewar}
\target{Incursion}
\index{\secondbanewar}
\index{Incursion}
The dreaded \satharioth{} march forth, legions of \banes{} and monsters at their back, 
announcing to all of \Miith{} the beginning of the \secondbanewar.
Or \quo{the Incursion}, as the \resphain{} call it. 











\subsection{\Ishnaruchaefir{} and \Secherdamon}
\target{Early conflict between Ishnaruchaefir and Secherdamon}
Have lots of conflict between the two brothers. 
\Secherdamon{} blamed \Ishnaruchaefir{} for \ps{\Nexagglachel} death, and much more. 
They fought and hated each other. 

After \ps{\Nexagglachel} death, there was much dispute about who, if anyone, should inherit his place as leader of the \dragons{}. 

\index{stewardship}
\Ishnaruchaefir{} claimed that \Nexagglachel, in their last conversation, had named him his successor and passed on the mantle of stewardship to him. 
But they only had his word for it. 

\Ishnaruchaefir{} was a great and acknowledged warrior and hero already before the \secondbanewar, so he argued that he would make a better war leader. 
\Secherdamon{} was famous for his more peaceful achievements. 
He was a scientist and philosopher and artist.
A nerd, where his brother was a macho-man. 

\Secherdamon{} argued that he really was more skilled. 
\ps{\Ishnaruchaefir} accomplishments looked flashy, but they were all things of destruction. 
\Secherdamon{} was a \emph{creator}, and it took much more expertise to create than destroy. 
\Ishnaruchaefir{} countered, saying that creation was all fine and dandy in peace time, but this was war, and a destroyer was needed, 

\target{Ishnaruchaefir gains title of Destroyer}
Hence arose \ps{\Ishnaruchaefir} title of \hs{Destroyer}. 
It was used for him in the war: 
\begin{prose}
  \ta{Beware! Flee for your lives! Here comes the Destroyer!}
\end{prose}

Later, \Secherdamon{} would muse that people ought to call \emph{him} the \quo{Creator}, in contrast. 

In the end, \Ishnaruchaefir{} won and was accepted as \ps{\Nexagglachel} successor. 
Even though \Secherdamon, being more of a team player and less of a loner, might have made a better leader. 











\subsection{The first battle}
A \resphan{} army marches against a \draconic{} city for the very first time. 
A hapless \scatha{} stands guard and sees the terrible black horde approach. 
They come with ice and cold, clad in \hr{Resphan crystals}{black onyx and other crystal}. 

\lyricsdimmuborgir{Raabj\o{}rn Speiler Draugheims Skodde}{
  Langt... der borte i m\o{}rket.\\
  Gjennom tretopper der m\aa{}nelys driver.\\
  Langt... der borte i all t\aa{}ke.\\
  Inn gjennom min sjel den sorte angst river.
  
  P\aa{} de mosegrodde steiner de seg viser,\\
  n\aa{}r nattem\o{}rket har senket seg over.\\
  Ekkoene... fra deres grufulle jamring\\
  endel\o{}st... du kan h\o{}re.\\
  
  I horisonten langt vekk\\
  skimtes den sigende skodde.\\
  Horder av ild rider m\aa{}nelyset i flokk.\\
  Ved daggry de samles ved en bortgjemt odde.\\
}

The \resphain\dash especially the dark \Mystraacht\dash chant their evil war songs. 

\lyricsdimmuborgir{For All Tid}{
  Hver en t\aa{}re er frosset.\\
  V\aa{}r sjel er lenket.\\
  V\aa{}rt hat er blodig.
  
  All glede er svunnet.\\
  All latter er forstummet.\\
  Alt liv skal ende i d\o{}d.
  
  I et kalt og \o{}de landskap\\
  skal den sorte horde tre frem.\\
  V\aa{}r herre skal stige opp for all tid, \\
  reise sitt rike igjen.
  
  N\aa{} er tiden kommet.\\
  Ja, knus de godes ord.\\
  La oss for alltid bli herskere \\
  p\aa{} denne jord.
}

\lyricsbs{Vital Remains}{Entwined by Vengeance}{
  Breath the air of the dawning winds, \\
  awakening the process \\
  of unpure procreation. \\
  Born to this world to cause your destruction. 
  
  Listen to our legion, chanting thy name. \\
  Listen to our legion, chanting thy name. \\
  Listen to our legion, chanting thy name. \\
  Blasphemy reigns unchallenged. \\
  In the name of torment we reign supreme. 
}

\lyricsbs{Vital Remains}{Entwined by Vengeance}{
  Moon at dawn, high above the horizon. \\
  Wind is calm, sun is slowly rising. \\
  Clouds will form, hide the blazing star. \\
  Mighty winds bring the coming storm. 
  
  Gather, sons of the northern frost. \\
  Born of thorns, you are nocturnal ones. \\
  Moonlight ride, your chariot will glide \\
  through the sky into a blade of glory. 
  
  The climate's right, prepare to fight. \\
  Observe the light in the dark night. \\
  Onward we ride, nowhere to hide. \\
  You fear in side, let the battle begin. 
  
  Cast the souls into the blazing fire. \\
  Sacrifice, judgment of our desire. \\
  Battles end, victory won. \\
  Lord of Darkness, your work is done.
  
  Warriors of the night, \\
  come and rejoice, hear the harlots sing. \\
  Celebrate in triumph. \\
  Warriors of the night, \\
  come and rejoice, hail you noble king. \\
  Celebrate thy victory. 
  
  Rebelling souls born against God, \\
  armed and ready to dethrone the fool. \\
  Twilight has come, twilight of the gods. \\
  Dawn breaks the east, it's the morning of Majick.
  
  Destroy the light, don't fear the darkness. \\
  Spirits arise, hover the crimson sky. \\
  Destroy the light, don't fear the darkness. \\
  Conquer and fight, take over the holy kingdom.
}





\subsubsection{They come from the cold north}
The invaders come from the cold north. 

\lyricsbs{Exmortem}{Berzerker Legions}{
  Born through an ice ages blast.\\
  Demonic winter race.\\
  Anger is present in their empty eyes.\\
  Fires dominate the landscape.
  
  Frigid storms and devastating raids.\\
  They are unconquerable.\\
  Frigid seas and devastating raids.\\
  Paramageddon.
}









\subsection{The \Dragons{} unite}
\target{Second Banewar unites Dragons}
The \dragons{} had been \hr{Dragons disorganized}{terribly disorganized} ever since the \firstbanewar, despite \ps{\Nexagglachel} heroic efforts. 
But the appearance of a clear external menace\dash and one powerful enough to pose a genuine threat, exemplified by the killing of \Nexagglachel\dash finally roused them, and they managed to unite, at least for a time. 

\Ishnaruchaefir{} acted as a leader of sorts, but reluctantly. 
He was never socially skilled enough to lead the \dragons. 









\subsection{\Zachirah{} as the Dark Warlord}
\Zachirah{} commands the armies of the \resphain{}. 
He is the most skilled warlord of them, being the most brutal and aggressive of the \satharioth. 
He drives his armies on with bloodlust, hunger and hate. 

\lyricsdimmuborgir{Antikrist}{
  Stig opp p\aa{} min trone, bleke lik.\\
  Fall p\aa{} kne \ae{}rb\o{}diget foran mine f\o{}tter.\\
  Ta imot mitt kalde kyss p\aa{} din panne.\\
  Jeg har lagt veien som f\o{}rer til Helvete klar.
  
  L\o{}ft deres sverd til kamp, stolte menn.\\
  La massakeren begynne i dag.\\
  Hogg hodet av hver kristen\\
  og voldta deres kvinner og barn.
}

The \resphain{} have been driven to raging bloodthirst by the Chaos power within them. 

\lyricsdimmuborgir{Antikrist}{
  Hver natt skal du v\aa{}kne med ett skrik\\
  og kjenne blodet som brenner dypt i deg.\\
  Hver natt skal du rave som en sansel\o{}s i gaten\\
  og utslette hvert et tegn du ser til liv.
}

The voice of \Nexagglachel{} warns the \satharioth{} and \ketherain{} (if any) of \hr{Curse}{the curse}. 

\lyricsdimmuborgir{Antikrist}{
  H\o{}r min tale, menneskedyr.\\
  Mine ord er din fremtid.\\
  Jeg er Satans legemliggj\o{}relse.\\
  Jeg er din herre.
}

\lyricsbs{Aeternus}{Warlust}{
  I break the chains that holds the storm.\\
  I feel its pulse, it hammers the sky.
  
  Volcanic winds of blooded rage,\\
  mind tearing frost\\
  shall provide brutal death.\\
  Once again you shall feel\\
  the darkened realms.\\
  Warriors!
  
  By our will you will kneel.\\
  Beneath us you will always stand.\\
  Your poisoned soul belongs to me.
  
  Warlust.
  
  Remembrance.\\
  We know you know the pain.\\
  Intensified it shall become.
  
  Drenched the fields of war.\\
  Know what we possess.
}

They eat the flesh of their enemies. 

\lyricsbs{Monolith}{Deathcult}{
  I am the plague of the thousand burning cities.\\
  With lust I eat the flesh of my enemies.\\
  Slaying my enemies I delight in war.\\
  Their blood gives me strength to slay the forces of [\Tembrae].\\
  We ride our war horses out of the great steppes of [\Merkyrah].
}





\subsubsection{\Zachirah{} tempts Ramiel}
\Zachirah{} urges Ramiel to submit to evil as he has. 

\lyricsdimmuborgir{The Maelstrom Mephisto}{
  Ride the vortex winds with the beast inside.\\
  Cast down all memories from a past and future world.\\
  The cynic icons and the cryptic writings\\
  as a picturesque creation in force and spirit.
  Against their reason and will, it is time.\\
  Give darkness it's passion plea.
  
  The venomous tongue, \\
  the inevitable poison,\\
  paralyze the angels.\\
  Freeze the forgiven,\\
  baptize in fire,\\
  unleash the devil at heart.
  
  Unleash the Maelstrom Mephisto.
  
  So sinner, mourn well.\\
  Make all the swans suffer in Hell.\\
  The maelstrom of the Mephisto left the trace\\
  to revel and feast in undelivered grace.
}









\subsection{\Shiaraid{} and \Eryal}
\target{Shiaraid and Eryal driven apart}
\Shiaraid{} and \Eryal{} were lesbian lovers already back then. 
They had been for some time. 
Their relationship was sado-masochistic, with \Shiaraid{} dominant and \Eryal{} submissive. 
It used to be healthy and pleasant for both parts. 
\Shiaraid{} knew how far she could go and respected \Eryal{} even when she tortured her. 

But after she became a \sathariah, \ps{\Shiaraid} mind gradually became twisted by \hr{Curse}{\NexagglachelsCurse}. 
Her sado-masochism became a \hr{Self-destructive Shiaraid}{self-destructive madness}. 
She became abusive and downright evil to poor \Eryal. 
They loved each other, but \Shiaraid{} was going mad. 
The Curse broke both their hearts and drove them apart. 

\target{Shiaraid and Eryal break up}
It came to an ugly break between them. 
The ensuing heartbreak was one of the reasons why \Shiaraid{} and \Mystraacht{} later fell from grace, while \Eryal{} became one of the \hr{Founding of Kezerad}{founders of \Kezerad}. 









\subsection{Battle scenes}
Have a battle scene where a few \dragons{} mow down mortals by the thousands. Show how worthless and impotent humanoids are compared to \dragons.

\lyricsflnv{10}{
  The passage of the Golden \Dragons{} and the Emperor completely destroyed the knights. 
  In one stroke of lightning, Wismerhill had lost his best forces. 
  The high nobility of the Black Moon had been annihilated!
}

Have another battle scene, or the same, where \dragons{} fight against \banes{} and their monsters. There is slaughter inflicted on both sides, with only selected super-heroes being untouched. 

\lyricsflnv{10}{
  Only the Emperor's \Dragon{} seemed untouchable, and it even managed to hold its own against the Lords of Negation. 
  The Emperor was truly a terrifying opponent.
}









\subsection{\Ishnaruchaefir{} leads the \dragons{} to war}
\target{Ishnaruchaefir leads the Dragons to war}
\Ishnaruchaefir{} fights against the \resphan{} menace, leading his \draconic{} brethren and their massive armies into battle.

\lyricsbs{Bal-Sagoth}{The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire}{
  Hearken, the clarion is upon the winds, \\
  now the call to arms is upon us all. \\
  (Grim warriors, take up thy spears and hone thy gleaming swords. \\
  Archers, string thy bows, brave knights, saddle the steeds of war.) \\
  The glory of battle is nigh at last, \\
  our banner shall fly this day in victory!
  
  My warriors, a legacy shall this day be wrought by our blades,\\
  decreed by the gods, \\
  blessed by the blood of vanquished foes. \\
  Our destiny beckons...
}









\subsection[Aryothim abandon alliance]{\Aryothim{} abandon alliance}
The \aryothim{} (and the few \vorcanths{}) gradually found out that the \resphain{} were in league with the \banes, and that the \banes{} were genocidally evil. 
They were nonplussed, so they seceded from \hr{Resphan-Aryoth alliance}{their alliance with the \resphain}. 
They retreated to Visha and remained mostly neutral. 

But the \vorcanths{} were very loyal by nature, so even if they would no longer fight in the \ps{\resphain} war, the bonds of friendship they had tied with individual \resphain{} (including Ramiel and \Shiaraid) survived. 





\subsubsection[Aryothim went downhill]{\Aryothim{} went downhill}
It went ill for the \aryothim. 
They had suffered many losses in the war. 
After they seceded from the alliance it got no better. 
Now both sides in the \feud{} hated them. 

The different \aryoth{} tribes also hated one another. 
Some tribes hated the others for \quo{tricking} them into the alliance, and the others hated the first group for tricking them \emph{out} of the alliance. 

Their only support were the \vorcanths, and they didn't give any hard and fast promises. 









\subsection{The devastation wrought}
The war is horribly bitter and brutal and bloody, and by the end\dash many years later\dash both sides are decimated. 

\lyricsbs{Exmortem}{Funerary Sculpture}{
  Huge battle machines\\
  now funerary sculptures.\\
  Armoured divisions\\
  no longer a threat.
  
  Isolated war scenarios.\\
  Rusty iron deserts.\\
  Human remains\\
  in the sand and the wrecks.
  
  Unaffected of the grim disease\\
  I walk these fields of flesh piles.\\
  Desolated, lifeless.\\
  Slowly decaying.
  
  Huge battle machines\\
  now funerary sculptures.\\
  Armoured divisions\\
  now plague eaten filth.
}









\subsection{It looks hopeless}
The war was going badly for the \Miithian s. 
It looked hopeless. 
The \bane{} hordes were endless. 

Compare to the hordes of Chaos in \cite{RPG:Warhammer:HighElves} and other \emph{Warhammer} titles. 




\subsubsection{\Ishnaruchaefir{} is a poor leader}
At this point, \Ishnaruchaefir{} had been grudgingly accepted as \emph{de facto} \dragonlord{} and leader of the \dragons.
He did his best to lead because he felt he had to, but he was no great leader nor tactical genius. 

He was an able leader who won through by sheer willpower, courage, daring and brute force, but he also made some major strategic blunders. 
Moreover, he was already becoming alienated from his fellow \dragons{}, which made him more and more self-sufficient and unwilling to listen to advice, which made everything worse. 





\subsubsection{\Ishnaruchaefir{} takes drastic measures}
It came to be that his three sons all perished in battle in rapid succession. 
This hardened him. 
He decided drastic measures had to be taken. 
He wanted to call upon darker, forbidden powers. 
He decided to seek out \NerrhanKoss, the darkest, most horrible, most frightening of the \xss, and make a pact with him. 

His fellow \dragons{} were against this. 
They feared that the power of \NerrhanKoss{} was too dark, too evil, and that if they called upon him for aid it would corrupt and doom them and call down eternal tragedy upon their kind and all \Miith. 





\subsubsection{The glaive}
\target{Glaive origin}
\Ishnaruchaefir{} went on, heedless of their warnings. 
He was willing to pay any price. 
So went to a dark shrine of \hr{Nerrhan-Koss}{\NerrhanKoss} and made his pact. 

Here he gained his \hs{glaive}. 
It was a gift of sorts from \NerrhanKoss. 
\Ishnaruchaefir{} forged it himself (using magic), but \NerrhanKoss{} taught him how. 
Maybe \NerrhanKoss{} also provided the materials. 
So in a sense, the glaive was a gift from \NerrhanKoss. 

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  The king was compelled to lead his forces to the shadow-haunted Mountains of the Dead, a grim and brooding place steeped in dark and ancient legendry. Alone he rode into the gaping maw of a huge cave hewn into the side of the tallest mountain co untless ages past by unknown hands.
  
  For three full days and nights he did not emerge from the cave... until, at last, he rode forth from the eldritch mountain once more, a terrible knowledge shadowed in his icy eyes, and bearing in his gauntleted fist a huge black sword, a magnificent ebon blade which no human blacksmith ever forged. Fearsome sorcerous power crackled within the yard of black steel, dancing upon its searingly honed, glyph-scored blade... and its bejewelled, dragon-carved hilt did whisper arcane secrets to the king in a strange, elder tongue.
}

With the glaive and the gifts of dark \NerrhanKoss, \Ishnaruchaefir{} was suddenly so psycho-badass you would not believe it. 
\NerrhanKoss{} had taught him how to unlock and unleash even more \xsic{} \shaeeroth{} power, so \Ishnaruchaefir{} had \trope{TookALevelInBadass}{Gained a Level in Badass}. 

Compare to Aenarion in \cite{RPG:Warhammer:HighElves}, who becomes \uber-powerful after he draws the forbidden and evil Sword of Khaine. 

\citeauthorbook{RPG:Warhammer:HighElves}{Andy Chambers et al}{High Elves}{
  Aenarion returned to the fray and carried everything before him. 
  The power of the sword was so great that nothing could stand against him.
  It filled his enemies with terror and his own troops with unshakeable faith and unquenchable blood lust. 
  The followers of Aenarion became ever more brutal, cruel and merciless, lost in a dream of endless slaughter. 
  With each victory they became ever more heedless of their fate, they fought with no thought for their own lives, possessed by a desire to spill the blood of their enemies. 
  All the Elf warriors became heedless of danger and most heedless of them all was Aenarion. 
  
  Old longings, deeply buried in the Elf soul began to stir, and a darkness of the spirit descended on their armies. 
  There were those who fought for the joy of fighting and those who slew for the sake of slaying. 
  Aenarion carved himself out a new kingdom in northern Ulthuan, in the bleak land of Nagarythe, a place that mirrored his own dismal mood. 
  Many of the most savage Elf warriors were drawn here. 
  
  [...]
  
  The war reached its final stage, an unequal contest of might between the Elves and the innumerable legions of the four Chaos powers. 
  Touched by Asuryan and marked by Khaine, Aenarion was an all but invincible warriors, a child of darkness and light. 
  His blade lent him power beyond mortal reckoning; the eternal flame gave him the strength to use it. 
  In battle, Aenarion slew foes beyond reckoning. 
  His loyal mount Indraugnir was a match for any Daemon. 
  And yet there was only one Aenarion, and the number of his followers was finite. 
}








\subsubsection{\Ishnaruchaefir{} asks \xss}
\target{Ishnaruchaefir sacrifices to the XS}
\Ishnaruchaefir{} sought out the counsel of the \xss{} or cosmic gods. 
They wanted a price in blood before they would help him. 
He offered them his own blood as payment (saturated with \xsic{} power), but that was not enough. 

\target{Nathrach dies}
So he challenged the \sathariah{} \hr{Nathrach}{\Nathrach} to single combat. 
\Nathrach{} accepted. 
He fought bravely, but fell. 

\target{Ishnaruchaefir eats Nathrach}
\Ishnaruchaefir{} captured \ps{\Nathrach} soul and offered it as a sacrifice to the \xss. 
They accepted and helped him. 
They returned a fragment of \ps{\Nathrach} soul to \Ishnaruchaefir, allowing him to ingest it. 
This piece contained some of the \hr{Fragments of Nexagglachel}{\Nexagglachel{} fragment} inside \Nathrach. 
From eating this, \Ishnaruchaefir{} \hr{Ishnaruchaefir understands the curse}{inherited a certain intuitive understanding} of \hr{Curse}{\NexagglachelsCurse} and the psychology of the \satharioth. 





\subsubsection{\Resphain{} strike back}
With his newfound power, \Ishnaruchaefir{} pushed back the \resphain.
But they were not done. 
They devised counter-plans and again turned the tide of the war in their favour. 

So the \dragons{} had to take \emph{new} drastic measures. 
They began to plan the \hr{Shrouding}{\SecondShrouding}, which consisted of letting the \xss{} rape the foundations of the world. 














\section{The \SecondShrouding}
\target{Shrouding}
\subsection{The \SecondShrouding{} is prepared}
The \dragons{} come up with the \SecondShrouding{} as a means to banishing the \banelords{} from \Miith{} and ending the war.
%The \secondbanewar{} ends with the \SecondShrouding{}. 





\subsubsection{\Ishnaruchaefir{} advocates the Shrouding}
\target{Ishnaruchaefir and the Shrouding}
There is dissension among the \dragons{} about whether this Shrouding plot is a good idea. 

\Ishnaruchaefir{} was an advocate of the Shrouding plan. 
He had secretly negotiated with some \resphan{} lords who were planning to betray the \banes. 
That was why he was so fond of the Shrouding plan: 
He had invested a lot in it. 
(Arguably this was a case of the Down Funds Fallacy.)

(He would later go on to become one of the prime architects behind the \hs{Lie Sublime} and the \hr{Charade}{\charade}, too.) 





\subsubsection{The balance of the \matrices}
\target{Balance of the Matrices}
\Ishnaruchaefir{} still remembered his dreadful visions of a bloody future of eternal war. He conferred again with the wise elder \ophidians, \nagae{} and perhaps other creatures (such as the \hs{cosmic gods}). 
They tell him that the two \matrices{} are closely balanced, and that it is this unholy balance that keeps the war going, and will continue to do so. 
Tremendous \vertex{} power will be needed to shatter this balance, and this is not likely to happen for many thousands of years. 

This is a subversion of the trope \trope{BalanceBetweenGoodAndEvil}{Balance Between Good and Evil}.

And so, the way \Ishnaruchaefir{} saw it, if the war could not be won or stopped, then it could at least be contained, made milder. He believed in the \charade{} project, because he saw it as a means of creating a peaceful world. That way, the great war between \dragons{} and \banes{} would be contained, and they would have to resort to stealth, instead of rampaging freely and laying waste to the world. 





\subsubsection{Three futures}
\target{Ishnaruchaefir sees three futures}
\target{Ishnaruchaefir chooses eternal war}
A revision: 
\Ishnaruchaefir{} did not see only one future, but three: 
Chaos, Darkness or eternal war. 
The two first were too horrible to contemplate, so he chose the third. 

The above is not strictly correct. 
The gods did not see three futures. 
They saw a myriad number of futures. 
But in most of them, \Miith{} was dominated by one of three tendencies. 

The gods should \hr{XS speech}{speak weird}. 





\subsubsection{Weaving artifacts}
\target{Fulcrum}
\target{Fulcra}
\target{Weaving artifacts}
\target{weaving artifacts}
\target{weaving artifact}
\index{Fulcrum}
\index{weaving artifact}
In order to effect the Shrouding, the \dragons{} used powerful magical items in the weaving. 
These became known as the \quo{Fulcra}, or \quo{weaving artifacts}. 
One such was \ps{\Ishnaruchaefir} \hs{glaive}. 

These Fulcra are item-shaped \vertices{} that hold the Shroud in place. 

\lyricsbs{Bal-Sagoth}{
  And Lo, When the Imperium Marches Against Gul-Kothoth, Then Dark Sorceries Shall Enshroud the Citadel of the Obsidian Crown
}{
  Darkly bejewelled circlet of night,\\
  crown of the Elder King.\\
  Unfettered at last the Trinity of Might,\\
  the sceptre, the sword, and the ring.
}





\subsubsection{\Ishnaruchaefir{} needs \ps{\Secherdamon} Gnosis}
\target{Ishnaruchaefir steals Secherdamon's research}
\Ishnaruchaefir{} needed to contact \hr{Naath-Kur-Ramalech}{\NaathKurRamalech}, the most important of the \xss{} that partook in the forging of the \hr{Crystal Sphere}{\CrystalSphere}. 
In order to do that, he needed some more Gnosis about the \ps{\xss} Aenigmata. 

He knew that \hr{Secherdamon seeks Gnosis}{\Secherdamon{} had done lots of research in this field}, so he sought him out. 
After some persuasion (and emotional blackmail invoking \ps{\Nexagglachel} dying wishes), \Secherdamon{} agreed to \cooperate. 
So he put all his research at his brother's disposal. 

\Ishnaruchaefir{} stood on \ps{\Secherdamon} shoulders, and with a little help from the cosmic gods he achieved a flash of insight, granting him the Gnosis he needed. 
But he did not pass this knowledge on to \Secherdamon. 
At first \Ishnaruchaefir{} excused himself by saying that there was no time to teach \Secherdamon{} the very complex revelations he had seen.
\Secherdamon{} accepted this explanation, but expected \Ishnaruchaefir{} to tell him everything as soon as he was able. 

In truth, \Ishnaruchaefir{} was reluctant to tell \Secherdamon{} anything. 
He did not want to share the burden of \hr{Ishnaruchaefir's stewardship}{stewardship}, and he was already now getting paranoid.
Later, he would \hr{Ishnaruchaefir refuses to tell Secherdamon Gnosis}{outright refuse to tell \Secherdamon}. 





\subsubsection{\Ishnaruchaefir{} alienated}
\Ishnaruchaefir{} was bad at cooperating with his brethren. 
Numerous factors conspired to drive him apart from them: 
\begin{enumerate}
  \item 
    He felt guilt over having caused \ps{\Nexagglachel} death. 
    He should have died in his stead. 
  \item 
    \index{stewardship}
    He had \hr{Ishnaruchaefir gains stewardship}{promised \Nexagglachel{} to carry the burden of leadership}. 
    He was \hr{Ishnaruchaefir's stewardship}{unwilling to share that load}. 
  \item 
    Other \dragons{} accused him of being a coward and a weakling, having abandoned \Nexagglachel{} to his fate, leaving a far better \dragon{} to perish in his stead. 
    He failed to grab his obvious chances to save \Nexagglachel, they felt. 
    \Ishnaruchaefir{} partially agreed, but he refused to show any weakness and acknowledge any guilt. 
    This made the discussions turn nasty. 
  \item 
    There was a deepening chasm between him and \Secherdamon. 
    Both wanted to inherit \ps{\Nexagglachel} place. 
    They disagreed on how to lead their people, how to wage the war and how to carry on the legacies of \Nexagglachel{} and \Kserasshana. 
  \item 
    He argued with \Rystessakhin{}. 
    They had different plans to defeat the \resphain. 
    They were driven apart by their disagreements. 
\end{enumerate}

\Ishnaruchaefir{} became alienated from his \draconic{} brethren. 
He convinced himself that it was a futile effort to attempt to unite them behind him and make them see the wisdom of his actions. 
He could not trust his fellow \dragons. 
He was better off alone, walking his own path and trusting himself only, whatever others may think of him. 
So he took it upon himself to do as much as he could on his own. 
He did not rely on the input and expertise of others.
This meant that the \SecondShrouding{} ended up being much bloodier than it needed to be. 
It killed more \dragons{} and others and laid waste to more Realms than it needed. 
It was crude and rushed work. 
If they had all worked together, they could have found a cheaper, better, more effective solution. 
But that was not to be. 
Everyone's pride and other negative emotions prevented it. 
It was quite the tragedy. 

He decided to carry his burden alone and in silence. 
He had become disillusioned and now refused to \cooperate.
His fellow \dragons{} had become a burden and an obstacle. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Citizen}{
  I preach not for understanding.\\
  In you I have no faith.\\
  I spit at you my truth;\\
  that you are the burden of my heritage.
}

But in a way it was nothing new to him. 
It was in his nature to walk alone. 
He was used to trust himself and not depend on others. 

\citebandsong{Ihsahn:angL}{Ihsahn}{Monolith}{
  It was never\\
  the icy winds of the heights,\\
  but the coldness of the world\\
  that hardened my foundation.
  
  Whether your approach\\
  is that of praise or blasphemy,\\
  the construction of my being\\
  will remain the same.
}

He saw himself as called to a higher purpose, one that lesser beings (even other \dragons) could not understand. 

\citebandsong{Ihsahn:angL}{Ihsahn}{Monolith}{
  If my soaring presence\\
  threatens to break your neck,\\
  then so be it.\\
  You shall dread my name.
}

He accepted that others would not understand and love him.

\citebandsong{Ihsahn:angL}{Ihsahn}{Monolith}{
  There is a fundamental cleft\\
  between your world and mine.\\
  One of divine origin.
}

He felt the others were hypocrites who would never realize that he was right and they were wrong. 
(He would later revise this view a little bit, after realizing the depths of depravity to which he himself could sink.)

\citebandsong{Ihsahn:angL}{Ihsahn}{Monolith}{
  Were you to witness\\
  the nakedness of your own soul,\\
  it would still appear a tower of Babel.
  
  Is it such a crime to go apart and be alone?\\
  Your holy simplicity turns gold into stone.
}





\subsubsection{\Ishnaruchaefir{} kept Gnosis to himself}
\target{Ishnaruchaefir refuses to tell Secherdamon Gnosis}
After the \SecondShrouding{} was complete, \Secherdamon{} still felt \Ishnaruchaefir{} was obligated to teach him the Gnosis that he had achieved by using \ps{\Secherdamon} research. 
But \Ishnaruchaefir{} refused. 
He did not trust \Secherdamon. 
They had grown to dislike and distrust each other during the infighting in the war. 

\hr{Secherdamon becomes better when denied Gnosis}{\Secherdamon{} grew bitter}. 





\subsubsection{\Secherdamon{} takes over}
After \Ishnaruchaefir{} went his own ways, \Secherdamon{} tried to take over and fill the empty position of leader. 
He tried to pick up the pieces after \Ishnaruchaefir{} abandoned them and left them in chaos and ruins (at least, that was how \Secherdamon{} saw it). 

This was hard work. 
It was one of the reasons why he came to hate \Ishnaruchaefir. 









\subsection{\Satharioth{} betray the \banelords}
\target{Banishment of the Banelords}
\target{End of the Second Banewar}
\target{Satharioth betray Banes}
The war rages. 

At the time of the \secondbanewar, the \dragons{} were weakened by internal warfare, so the \resphain{} had the upper hand for a while. 

But they crumbled when the \satharioth{} decided to betray the \banes.
%In the end, everyone loses, but especially the \banes. They were secretly backstabbed by the \satharioth{}. 
\hr{Curse}{\NexagglachelsCurse} overcame them, and so, poisoned with hatred of their creators, they decided that they desired overlordship for themselves and were unwilling to defer to their \bane{} masters after all. 

So the \satharioth{} secretly supported the \SecondShrouding{}. 
They allowed the \dragons{} to perform their Shrouding spells and even did some of their own. 
They also supported the \dragons{} with knowledge gleaned from the \hr{Shroud of Nyx}{Shroud of \Nyx}, which \Daggerrain{} had woven at the \hr{Thanatzil dies}{fall of \Thanatzil}. 

\Azraid{} secretly masterminded this deceit, but he did it so masterfully that no one suspected him. 
All the people who knew were quickly killed and their souls destroyed. 

\lyricsbs{Monolith Deathcult}{Origin}{
  The Lord was the blessed name they carried,\\
  composed from the leeches of the Kosmos.
  
  The Gods must be slain,\\
  so [\resphan-]kind will be blessed with their wisdom.\\
  In the darkest depths of AB.ZU,\\
  with the vulpine Snake on our side,\\
  ruler of the underworld of E.DIN.\\
  We conspire against our Masters.\\
  After the dismantling of the alien Gods\\
  we become divine.
}

It remains unknown to what extent the \banes{} know of this treachery\dash certainly no \resphan{} dares bring it up with a \banelord. 









\subsection{\Ishnaruchaefir{} and \Rystessakhin}





\subsubsection{\Rystessakhin{} opposes \Ishnaruchaefir}
But \ps{\Ishnaruchaefir} true love, \Triestessakhin, mother of \Nzessuacrith{} and the \dragon{} closest to him in his life, railed against the plan. 
She saw the Lie Sublime, the perpetual and brutal oppression and the thousand-year-long underground war as a horrible dystopia and insisted that a better solution must be found to destroy the \banes. 
(Compare her to Latra Posae from \cite{RobertJordan:WorldofWOT}.) 
They debated and fought heatedly over this issue, and it drove them apart. 

\ps{\Ishnaruchaefir} vision of the Shrouding was bloody. 
Millions would have to die, and entire Realms might perish. 
\Rystessakhin{} did not like it. 
She felt nothing was worth the terrible cost that \Ishnaruchaefir{} proposed. 
She could not accept the idea of so callously throwing away millions and lives and devastating entire Realms. 
It would be a worse atrocity than the war itself. 

\Rystessakhin{} had a more peaceful, more tree-hugging plan. 
I don't know what exactly, but it should be something that sort of invokes \trope{ThePowerOfLove}{The Power of Love}. 
But without making her stupidly \trope{GenreBlind}{Genre Blind}. 
Anyway, the point is that \Ishnaruchaefir{} does not believe in her plan. 
He believes that only his own, more ruthless plan has a chance of success, because the world is like that. 
Ruthless. 

\ps{\Rystessakhin} plan \emph{could} work. 
He admitted that. 
But he didn't like the odds. 
Moreover, her plan involved her risking her own life and soul, becoming a \trope{BarrierMaiden}{Barrier Maiden} of sorts. 
\Ishnaruchaefir{} would not accept that. 
He did not want to risk losing her.
He would sacrifice everyone else on Mith before he saw that happen. 
He felt that his plan was safer, and therefore well worth the cost in blood. 

Another point of contention was that \ps{\Rystessakhin} plan put her in great personal danger. 
She was prepared to sacrifice her life and soul. 
\Ishnaruchaefir{} felt that \hr{Ishnaruchaefir's stewardship}{the salvation of \Miith{} was \emph{his} burden} and \emph{his alone}. 
He did not want \Rystessakhin{} to pay the price in his stead. 
If he let her do that, he would feel he had failed \Nexagglachel, her, himself and everyone. 
He wanted to bear the burden alone. 
His pride demanded no less. 
(But it was OK to let others die in the process. 
His principles were somewhat strange in that regard.)





\subsubsection{\Ishnaruchaefir{} slays \Rystessakhin}
\target{Ishna slays his beloved}
\target{Ishnaruchaefir slays his beloved}
Ultimately, \Rystessakhin{} somehow managed to stand in the way and block them, preventing \ps{\Ishnaruchaefir} faction from initiating the Shrouding. 
\Ishnaruchaefir{} confronted her and attempted one last time to reason with her. 
They failed to come to an agreement, and he had to admit\dash to himself, and to her\dash that he loved his vision more than he loved her. 
And so, at last, he slew her, striking her down with his glaive.

This scene needs to be heartbreaking. 
Compare to the scene in \cite{PhillipPullman:TheAmberSpyglass} where Lyra leaves Pantalaimon behind in order to travel to the realm of the dead. 

\begin{prose}
  \Ishnaruchaefir:
  \ta{Curse thee, \Aeocrith, stand aside!
    Or I swear by the \xss{} I shall strike thee down!}
  
  \Rystessakhin:
  \ta{
    Then strike me down, \Quessanth, for I will not let thee do this thing.}
\end{prose}

At this point, \Ishnaruchaefir{} had already forged his powerful glaive and intended to use it as a \hs{weaving artifact}. 

He did not intend to destroy nor eat \ps{\Aeocrith} soul. 
Nor did he mean to bind her in the glaive. 
He just meant to kill her temporarily. 
Even that was a pretty big thing between lovers (roughly equal to a mortal man brutally beating up or raping his wife). 
That was her own doing. 
She knew the glaive was his weaving artifact, the instrument of his plan.





\subsubsection{Moments of destruction}
As he slew her, she latched onto the glaive and poured her soul into it. 
She realized that she could not stop him, so she wanted to help him and share his burden. 
She intended to sacrifice herself and make herself a permanent Barrier Maiden and help him uphold the Shroud. 
He tried to stop her and carry on with his own plan. 
He did not want her to pay the price in his stead. 
He would rather see millions of innocents die. 

He fought to stop her. 
But she insisted. 

Countless innocents died all over the realms in those precious seconds where he struggled against her (she was, after all, sacrificing herself to save those people). 

And it got worse. 
\Ishnaruchaefir{} raged inside at the injustice of it. 
He realized \Rystessakhin{} would sacrifice her soul and so be lost to him, and try as he might he could not prevent it. 

\begin{prose}
  \tho{%
    Without \Nexagglachel{} I am the greatest, the mightiest, the bravest, the noblest of all the \dzraicchenosses.
    I deserve better than this!
    I have worked and fought so hard and sacrificed so much for the world and the \psp{\dragons}{} sake. 
    I have wrung dry and depleted my standing and reputation. 
    And now I must lose my beloved!
    This is wrong!}
\end{prose}

Rationally, he knew better than to appeal to any \quo{justice}. 
He did not believe in such silliness. 
But at that moment he did not care. 
All the burning hot power of the \xss{} was coursing through his veins, and they filled his heart with volatile passion. 
His emotions blinded him and carried him away and took control of him. 
Only for a brief moment, but it was a brutal, costly moment. 
In his fury he lashed out against the world.
Millions died across the Realms of \Miith{} in that moment to sate his anger. 

He released all his anger. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  Come suffering, Apocalypse.\\
  Release the fires of Hell.\\
  I call upon destruction and despair.\\
  Here the days of slumber end.\\
  I beckon the night \\
  to live and overcome the fear.
}

By now he knew he would be hated forever for his actions. 
And in that moment the world could go fuck itself for all he cared. 
So he might as well make it worse. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  Come sin, come shame.\\
  Congregation of contempt.\\
  I bid you welcome to the pyre.\\
  Will our objective truths \\
  withstand this affliction?\\
  I venture.\\
  Let it all come down.

  The deafeaning sound of trumpets roar\\
  in celebration of impending chaos.\\
  This is not terror, this is not war.\\
  Beyond repentance.\\
  This is the call of the abyss.
}

He released, and gave into, his inner evil. 
Part of it was his \xs-born destructive urges. 

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  DeathspellOmega
}{
  Mass Grave Aesthetics
}{
  Transcendence of thresholds occurs with violence \\
  And will for Vice is like the mind's dark radiance \\
  Which blinds and of which I'm dying \\
  Corruption is the spiritual cancer \\
  reigning in the depths of things \\
  And it fills until the last cell of my vivid being \\
  Dissolution and putrefaction, \\
  prevailing Aesthetic experience, \\
  The splendor of the obscene and inhuman; \\
  For what matters the death of a vague human beings \\
  If thereby the individual affirms himself?
}

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  DeathspellOmega
}{
  The Shrine of Mad Laughter
}{
  As if Death was dashed onto the death within, \\
  a violent thrust stealing the light of the eyes. \\
  A ray of darkness, a negation. \\
  The bread of bitterness \\
  that ignites neither devotion nor fervour.
  
  Resplendent nothingness! \\
  Make all things appear with clarity.\\
  Ruined in the flame of repudiation, \\
  in the flame of God!
}

He knew what he was doing was evil.

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  DeathspellOmega
}{
  The Shrine of Mad Laughter
}{
  Interwoven joy and confusion, 
  a stabbing confusion. \\
  Asphyxiation from within, yet I gained this certitude: \\
  Malediction, degradation, sown in me like seeds.\\
  Now I belonged to my flesh. \\
  I belonged to death.\\
  In harbouring a desire for the hideous, \\
  I was beckoning to death. 
  
  Insatiable combustion! Expand! \\
  This body is thy vessel of grace!
}

In these moments of destruction, a tremendous struggle and a tremendous character development took place inside \ps{\Ishnaruchaefir} head. 
He gained much insight into his own Aenigma. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  DeathspellOmega
}{
  The Repellent Scars of Abandon and Election
}{
  I was beyond withstanding my own ignominy. \\
  I invoked it and blessed it.\\
  I progressed ever further into vileness and degradation. \\
  Am I resurging, intact, out of infamy?
}

At last he realized that his struggling was pointless and only demeaned her noble sacrifice (by aggravating the destruction she fought to prevent), so he relented and let her do her thing. 
She poured all her soul into the glaive, where it would \hr{Rystessakhin's consciousness}{become crippled and never again regain consciousness}. 

\index{stewardship}
He was not happy about it. 
He felt like he had failed in \hr{Ishnaruchaefir's stewardship}{his task}.
\emph{He} should be the one carring \ps{\Miith} safety on his shoulders. 
Not she. 
Never her. 
It was wrong that she should suffer like this. 
(He didn't mind condemning many others to suffering, and was even willing to kill her, but \quo{that was different}. 
His motivations need not be entirely consistent.) 

But he never told this story to the world. 
They all thought he killed her and bound her soul against her will. 
For \Ishnaruchaefir, to admit the truth would be a declaration of failure for more than once reason:

\begin{enumerate}
  \item 
    He would be admitting he had failed in the task entrusted to him by \Nexagglachel, which he had previously been so obsessive about.
  \item 
    He would appear to have been too weak to bear the great sacrifice alone. 
    This would harm his \hr{Myths about Ishnaruchaefir}{mythical reputation} as an invincible superbeing. 
    He likes that reputation. 
    It makes people fear him. 
  \item 
    He would look like he was apologizing for his mistake and seeking forgiveness. 
\end{enumerate}

His pride allows him to do neither. 
Only \Criseis-tachi knew the truth. 
And he made them promise not to reveal the story to anyone. 
(By the time of the \thirdbanewar, the accepted story was so ingrained that if \Criseis-tachi had tried to spread the true story, no one would have believed them.)


Mourning what he had done, he resolved to honour her sacrifice. 
From that day he would keep the glaive safe and always carry it with him. 
He went on to use the glaive as his \hs{weaving artifact} as he and his fellows wove the \hr{Shrouding}{\SecondShrouding}. 

He remains to this day one of the pivotal \vertices{} keeping the Shroud in place.

But slaying his beloved was traumatic and became a turning point in his life. It distanced him further from Chaos, the \firstgendragons{} and his fellow \dragons.

\Ishnaruchaefir{} contemplates his betrayal. 

\lyricsbs{Vital Remains}{Scorned}{
  So be it. I am the enemy.\\
  So be it. I am the one you seek.\\
  So be it. I have no sympathy or empathy.\\
  It is done. My words and life bleed blasphemy.
}









\subsection{The \SecondShrouding}
The \SecondShrouding{} was complete. 





\subsubsection{The cost of the Shrouding}
The \SecondShrouding{} was an incredibly costly and bloody affair. 
Millions of souls had to perish so that their vital cores and energies could be consumed and used to feed the nascent Shroud. 
This sacrifice would destroy entire Realms, bleed them dry and lifeless. 
It was a cosmic violation that left Mother \Miith{} wounded and bleeding and suffering for millennia to come. 

These souls still exist, bound in the Shroud. 
They retain a minimum of consciousness, enough to weep and suffer. 

The weaving artifacts each bind a very powerful soul, thus acting as \vertices{} in the \matrix{} that is the Shroud. \ps{\Ishnaruchaefir} glaive, for instance, holds the soul of \Triestessakhin. 

The ones weaving the Shroud needed to siphon and sap the emotions of the people they sacrificed. 

\lyricslimbonicart{Deathtrip to a Mirage Asylum}{
  Cut the string, the chain to soil.\\
  Unleash the powers within death's coil.\\
  No darker emotion is there to find\\
  than the fading feeling of a dying kind.
  
  Deathtrip to a mirage asylum.
}





\subsubsection{Why was it worse than last time?}
Why was it so much worse than the forging of the \hr{Crystal Sphere}{\CrystalSphere}, also a humongous cosmic upheaval? 
Probably because the \banes{} were closer this time and had more of their tendrils firmly secured on \Miithian{} soil. 
And they were advancing rapidly. 
And they had learned from their mistakes from last time and would not be so easily outwitted again. 

The \dragons{} had to act swiftly and desperately. 
Besides, they were not nearly as unified as they were last time (under \Kserasshana). 
This also weakened them. 
In the end, \QuessanthIshnaruchaefir{} acted virtually alone, against the world. 
So his Shrouding could not help but be a messy hackjob. 





\subsubsection{Entire Realms destroyed}
The price of the \SecondShrouding{} was extremely bloody. 
Entire sub-Realms of \Miith{} were laid waste, sucked dry of life in order to feed the Shroud. 
Actually, the \SecondShrouding{} itself might have caused \emph{more} destruction than the entire \secondbanewar{} had caused (up till that time, that is).

The world is violently torn apart and laid waste by the terrible destruction. 

\lyricsbible{Revelations 8:7}{
  And there followed hail and fire with blood, \\
  and they were cast upon the earth.\\
  And the third part of trees was burnt up, \\
  and all the green grass was burnt up.\\
  And the name of the star is called Wormwood.\\
  And the third part of the waters became wormwood.\\
  And many men died of the waters,\\
  because they were made bitter.
}

Especially the \resphan{} cities in \Nyx{} are hit hard by this. 
They lose the flow of \bane{} power from \Erebos{} on which they had previously relied. 
Now the entire Realm of \Nyx{} must sustain itself by leeching off of the other \Miithian{} Realms. 
The vast, splendid cities of \Nyx{} (only recently cleaned up from the bloodshed of the \Merkyran{} war) crumble and become a dead necropolis. 

\lyricsbs{Monolith Deathcult}{Concrete Sarcophagus}{
  In this gargantuan tumour,\\
  the choice had already been made.
  
  A thousand tons of steel and cement\\
  dispersed like a cancerous cough.
  
  Attending their fall-out funeral, this monstrous colossus.\\
  Radiating cancer for generations to come.\\
  20,000 tonnes of steel and cement\\
  cover the tumourous spider.\\
  Awaiting her next victims.\\
  The Concrete Sarcophagus.
}

\lyricsbible{Revelations 8:7}{
  And the name of the star is called Wormwood.\\
  And the third part of the waters became wormwood.\\
  And many men died of the waters,
  because they were made bitter\\
}























\chapter{\ResphanWarsBook}
\section{The \Dragons}
\subsection{\Ishnaruchaefir{} and \Secherdamon{} split}
After the \hr{Fall of Nexagglachel}{fall of \Nexagglachel}, \Ishnaruchaefir{} and \Secherdamon{} had a falling out and went their separate ways. 

\Secherdamon{} was obsessed with Chaos, the \xzaishanns{} and the \firstgendragons. 

\Ishnaruchaefir, on the other hand, did research on the Darkness and the origin and nature of the \bane{} and \resphan{} peoples. He had lots of \hr{Ishnaruchaefir and Baelzerach}{dealings with the \Baelzerach} and learned much of the Darkness from them. 

This is one of the reasons why he became so dark. 

\lyricstitle{Zeratul from \cite{VideoGame:Starcraft}}{
  You speak of knowledge, Judicator. 
  You speak of experience. 
  I have journeyed through the darkness between the most distant stars. 
  I have beheld the births of Negative Suns and borne witness to the entropy of entire realities. 
  Unto my experience, Aldaris, all that you have built here on Aiur is but a fleeting dream. 
  A dream from which your precious Conclave will awaken, to find themselves drowned in a greater nightmare.
}





\subsubsection{\Ishnaruchaefir{} absent}
\Ishnaruchaefir{} left \Miith{} and took no part in the \resphanwars. 

As such, he \emph{does not appear} in this book, unless there are scenes taking place in the Mirage Asylum and other exotic places. 






\subsubsection{\Ishnaruchaefir{} resented for leaving}
Many \dragons, not only \Secherdamon, resented \Ishnaruchaefir{} for leaving and \quo{abandoning} his people.
They felt he should have stayed when his people needed him and taken on the role of leader in \ps{\Nexagglachel} stead. 
But \Ishnaruchaefir{} did not feel up to the task. 
And he needed time away from everyone after the \SecondShrouding, which was traumatic for him. 









\subsection{\ps{\Secherdamon} rise to power}
\target{Secherdamon's rise to power}
After the \hr{Death of Nexagglachel}{death of \Nexagglachel} and the great \secondbanewar, \HriistD{} burned with ambition, and with his determination, ruthlessness and cunning he quickly rose to power in the \draconic{} hierarchy (to the extend that a such existed).

After cursing \ps{\Ishnaruchaefir} treachery, \Secherdamon{} decided that the aftermath of the \secondbanewar{} was his great chance. 
He was happy that \Ishnaruchaefir{} had had the decency to run away. 
In \ps{\Secherdamon} mind, his self-important brother very much deserved to fall from grace, after trying to set himself up as \dragonlord. 

\citebandsong{Emperor:Prometheus}{Emperor}{He Who Sought the Fire}{
  Towards the heavens he did aspire.\\
  Now he shall burn who sought the fire.
}

\Secherdamon{} will not mourn. 
He will seize his chance. 
His time for greatness has come. 

\citebandsong{Emperor:Prometheus}{Emperor}{He Who Sought the Fire}{
  Some will mourn the ashes cold,\\
  while others behold the inferno unfold.
  
  Now he shall burn who sought the fire,\\
  to manifest another.
}


This left \Secherdamon{} as one of the mightiest \dragons{} around. 

I need to tell a detailed back story with \Secherdamon{} as the protagonist. 
He has flaws, but rises above them. 
We see the adversity he faces, and his determination and courage, and we love him. 
Compare him to Zurra from \bandalbum{Bal-Sagoth}{The Power Cosmic}, but sympathetic.

In order to claim the mystic power that he coveted, he needed  knowledge and artifacts. 
These he took by force and treachery, waging war and slaying his fellow \dragons{} and \ophidian{} to obtain what he needed.





\subsubsection{Motivation}
He finds his motivation and grows strong of will.

\lyricsbalsagoth{Arcana Antediluvia}{
And so it was written \\
that rage would carry him like a howling wind, \\
leaving only frozen corpses,\\
their bones rattling in hollow armour, \\
to tell their tale in his wake.
}

He wants to restore the \dragons{} to their rightful position of overlordship. 

\lyricsbs{Hate Eternal}{King of All Kings}{
  As I am I reclaim the throne of all creation. \\
  As I shall be annointed king. \\
  For thy strength I must sustain.\\
  For thy dominion I shall proclaim.
}





\subsubsection{Seeking allies}
He slew other \dragons, including those mightier than he, and somehow stole their \vertex{} power by necromancy. 
Compare this to the power of Boris Dragosani in \authorbook{Brian Lumley}{Necroscope}.

\target{Secherdamon sacrifices Dragons}
He did not \hr{soul-eating}{devour their souls}, because \hr{Dragons do not eat Dragons}{that would be taboo}. 
But he sacrificed their souls to the \xss. 
Perhaps the \xss{} then granted him their \vertex{} power. 

He also seeks out allies. He wants old and powerful \dragons{} and \ophidians{} to help him. One especially great and powerful one rejects him. They fight, and \Secherdamon{} loses. But later he returns and exacts his revenge. 

\lyricsbalsagoth{Callisto Rising}{
[ZURANTHUS:]\\
Do not seek to threaten me, wormcast.\\
My tenure here is preordained...\\
and I will suffer your arrogance no longer, little brother.\\
The power of the Lexicon is not destined\\
to be possessed by one such as you. Be gone!

[CONDEMNED SOULS OF THE BROTHERHOOD OF DARK ELUCIDATION:]\\
Bipolar nebula! A falling star! The gate yawns wide above eon-veiled Mu...

[ZURRA:]\\
V'aan-ayth'ultaa, No'maal-pha'guus...\\
Damn you, Zuranthus... You will pay dearly for this outrage,\\
I swear it by the blackened maw of the sacred Z'xulth!
}





\subsubsection{Stealing artifacts}
\target{Secherdamon steals weaving artifacts}
And he steals several \hs{weaving artifacts}, killing their original owners and usurping their power. 

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{The incantation of Xuk'ul is known to me, \\
the Orb of Summoning earned with bloodshed! \\
The crystalline key to the Outer Realms and the arcane rite to empower it are at last mine, seized at swordpoint from the citadel of the Black Templars.

And the central stone of the ancient ebon ring begins
to pulsate with a darksome energy...}









\subsection{\Secherdamon{} becomes a \shaeeroth}
\target{Secherdamon becomes Shaeeroth}
\Secherdamon{} finally had the strength and desperate determination to cross the boundary and become a full-fledged \shaeeroth{} (\hr{Secherdamon does not become Shaeeroth}{unlike before}). 





\subsubsection{Invocation of power}
\target{Rissit invokes dark gods}
\HriistD{} performs a dark, occult ritual, summoning the \firstgendragons{}, \xzaishanns{} and cosmic gods (see section \ref{Cosmic gods}), seeking to gain their wisdom and power. 

\lyricsbs{Bal-Sagoth}{As the Vortex Illumines the Crystalline Walls of Kor-Avul-Thaa}{By Klatrymadon and Zuranthus, \\
such ancient secrets we discovered\\
in these sinistrous, worm-worm pages.\\
Etched with darksome glyphs and sigils, \\
bound with fearsome spells. \\
An eldritch tide of stygian sorceries \\
unfettered by the forbidden Tome of Shadows...

Now thunderous cataclysm befalls the gleaming Kor-Avul-Thaa.\\
(The mystic gate stands open!) \\
The Xytaxehedron held to the stars... \\
the incantation uttered with eager tongues... 

(What long-shackled powers of the elder dark have our conjurings loosed?)

By Klatrymadon and Zuranthus, \\
the vortex blackens the stars above.\\
A vast plague of amorphous horrors \\
descends to rend with fang and talon.}





\subsubsection{Calling upon dark powers}
He calls upon the ancient \ophidian{} lords, who are primordial natural forces and dormant rulers of \Miith{}.

\lyricsbalsagoth{Into the Silent Chambers of the Sapphirean Throne (Sagas from the Antediluvian Scrolls)}{Winged dragon coiled in thrice,\\
bane of flame in shadowed ice.
Flooded by the bloated Moon,\\
awake o' worm and quit thy tomb!}

He invokes dark names.

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{Ka-kur-ra, I summon thee,\\
Zul'tekh Azor Vol-thoth.\\
Mighty Xuk'ul arise,\\
Kur'oc Gul-Kor, come forth.

I hold aloft the pulsing orb.\\
Astral spheres empower the mystic key.\\
Ring of elder stones entwined in prophecy,\\
the Rite of Invocation enthralls thine power.

Lucent beams lancing forth from gleaming Cepheid stars.\\
A creeping mist ensorcels my tongue...}





\subsubsection{Obtaining power}
He is granted power far greater and more sinister than ever before. 

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{Replete from drinking deep of darkness...}

He becomes almost a \quo{\Tiamat{} junior}. He summons hordes\dash or entire races\dash of \mdaemons{} to serve him.

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{Black shapes dancing 'twixt the stars.}





\subsubsection{Conquering his enemies}

He becomes powerful, so that even other \dragons{} fear him. He is spoken of in legends as a terrible force.

\lyricsbalsagoth{Arcana Antediluvia}{
His gaze is as fire, \\
his words are as spear-points, \\
his voice is as thunder, \\
his touch as the plague!
}

He seeks out his foes.

\lyricsbalsagoth{Arcana Antediluvia}{
And one night, there came a storm, \\
a storm with searing red winds.\\
Fire and steel rode within it, \\
and vengeance writ in thunder and blood.\\
}

He conquers and crushes his enemies, and it is at last his turn to laugh.

\lyricsbalsagoth{The Empyreal Lexicon}{
Kur'oc! Gul-Kor! \\
I have won... bow, yield, kneel! \\
Darken the sun... Narra, Gorra, Kaasha! \\
I arise... bow, yield, kneel! \\
Parhelion dies... Narra, Gorra, Kaasha! \\
I can taste the sweet ichors of omni potency upon my lips...\\
Let it begin! \\
X'atham-ry'aa j'aiigh! \\
Tha'zai-tonn nax'a-gorrha!
}

\lyricsbalsagoth{Callisto Rising}{
[ZURANTHUS:]\\
Stray not into my darksome embrace,\\
lest I grind my jaws on your soul.

[CONDEMNED SOULS OF THE BROTHERHOOD OF DARK ELUCIDATION:]\\
Spare us your wrath, great one, we beg thee.\\
Begot of the thunder... spellbinder. Callisto Rising!

[ZURANTHUS:]\\
Behold my godhood... and pray!
}





\subsubsection{Death and rebirth}
\target{Rissit's death and rebirth}
In order to fully absorb his new power, \HriistD{} must die and be reborn. He is a son of the god of Death, after all. 

This is necessary to unlock his true potential as a son of Death. \Ishnaruchaefir{} went through a similar thing (see section \ref{Ishnaruchaefir's death and rebirth}), but \HriistD{} was initially to scared to do it. 

This is kind of a darker, more evil version of the Babylonian myth of Ishtar's death and rebirth. 

Perhaps it is a theme that \Secherdamon{} was originally somewhat weak and cowardly, but later in life acquired the immense determination and ambition that let him become one of the mightiest creatures on \Miith{}. 





\subsubsection{Witnesses to the ritual}
\Nzessuacrith{} helps \Secherdamon{} from the beginning, being disappointed in her father for seeming cowardice and abandoning his people. She participates in his empowering ritual. 

Describe it in a flashback!

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{
  A great stillness binds the moon-cloaked mountaintop in glooming shackles... \\
  High above, the myriad stars gleam bright against the night sky,
  three more resplendently bedazzling than the others, their sidereal auras engulfing the stones... \\
  And the central stone of the ancient ebon ring begins to pulsate with a darksome energy... \\
  A thunderous maelstrom ablaze with writhing celestially spawned power then rends the stygian night... \\
  A vast shimmering aperture, a vortex of heliacal fire... the pathway to beyond beckons!\\
  The Astral Gate is open...\\
  The Guardians have awakened...
}

Someone important (not \Ishnaruchaefir, though) watches from a distance and discusses the situation with someone. 







\subsection{\Secherdamon{} goes to war}
\Secherdamon{} goes to war wielding his new terrible powers. 

\lyricsbs{Arcane Wisdom}{Maelstroms of Majestic Night}{
  Torrents of blasphemous fire enrage forth, \\
  thus allowing my soul to devour \\
  feeblish souls with sickening power, \\
  as the ancient warcrafts proudly descend from the North. 
  
  Dwelling in the depths of midnight horizons, \\
  endless realms of darkness. \\
  Benight'd by the Third Moon, \\
  through dismal soil, eternally I wander. 
  
  Such pure Nightly evocative magick...
  
  I have sworn on the whoracle of the damned\\ 
  to forever raise my fist to the sky. \\
  A thousand sorcerers I summon'd \\
  on my forest way to the hellish Kulthay.
  
  Oh the blood of my foes and fiends. \\
  How I beheld thy corpses, \\
  raptur'd by virulent winds. 
}














\section{The \resphanwars}
\target{Resphan Wars}
\target{Resphan wars}
After the \secondbanewar, \resphain{} and \dragons{} alike fought on with all the spite they could muster\dash against each other, and internally. For thousands of years. Both sides had lost great leaders in the war and were now divided, left in chaos. Their civilizations declined. 









\subsection{Dynasties wage war}
\target{Dynasties split}
After the \hr{Shrouding}{\Shrouding}, the \banelords{} were locked out again. 
They now had little power over \Miithian{} affairs. 
They could still communicate, but only with difficulty. 

The \banelords{} were gruesome \trope{CosmicHorror}{Cosmic Horrors}, and the \resphain{} feared them. 
They feared and loathed \emph{contact} with the horrible \banes{} more than they feared the punishment that would be their \emph{if} the \banes{} were to one day return in force. 
Many \resphain, believing the \banelords{} were gone for good, ignored them and blocked them out and refused to obey their commands (\hr{Resphan cannibalism}{patricidal bastards that they were}). 

(Only the \banelords{} were gone. 
\Lesserbanes{} continued to serve the \resphain, but the \resphain{} never allowed them to evolve into \banelords.) 

Only few \resphain, like \hr{Azraid}{\Azraid}, remained \quo{loyal} to the \banelords. 


With the \banes{} and their leadership gone, the central organization of the \resphan{} empire crumbled.
The \resphain{} splintered into several dynasties and began to war amongst themselves. 
It was a big free-for-all. 

At first there was \hs{Cabal}. 
\hr{Cabal formed}{That came later}. 
There was no \quo{Cabal bloc}, and all dynasties had shifting alliances and enmities. 





\subsubsection{\Kezerad}
\Kezerad{} was not particularly the \quo{odd man out}. 
They sometimes allied with the other dynasties. 

\target{Tiphred-Serah and Kezerad ally}
The \TiphredSerah{}, being \hr{Tiphred-Serah free-thinking}{the most free-thinking of the dynasties}, were the ones most liable to ally with \Kezerad. 





\subsubsection{\Mystraacht}
\target{Mystraacht dominance during Resphan Wars}
For a long time during the \resphanwars, \Mystraacht{} was the most powerful of the dynasties. 
They had the most capable warriors and generals, but they were also \hr{Mystraacht not diplomatic}{the least diplomatic}. 

They relied on military power alone and eventually got many enemies against them. 
This was one of the things that \hr{Mystraacht betrayed}{felled them in the end}. 









\subsection{The \satharioth{} try to break the curse but fail}
Time and time again the \satharioth{} try to break free of \hr{Curse}{\NexagglachelsCurse}, but fail. 

\lyricslimbonicart{The Yawning Abyss of Madness}{
Again I drift the halls of wondering. \\
The black castle of solitude. \\
On the very edge of sanity \\
in mental cryogenic interludes. \\
I have slipped into the seventh, \\
the seventh circle of Hell, \\
in realms where deadly shadows \\
infest every cell. 

Internal ceremonies in ritual death. \\
External bleedings for the demon of madness. \\
Hide from the torture of the dazzling light. \\
The demolition voice shall speak tonight. 

While I'm staring down into the darkest pit, \\
an ocean black as the night, \\
so infinite deep and consuming, \\
it swallows all life force with might. 

Again I drift the halls of wondering, \\
as I focus for the darkness to come. \\
In anguish minds uplift the conquering \\
to cross the line of death beyond.

An abstract reality and bottomless insanity. \\
To search for the powers to please\\
the subconscious spirit of disease. \\
Time found no remedy, \\
cause winds of darkness was stealing me. 

The yawning abyss of madness. \\
A cryptic slaughter by hate. \\
Darkness is the only survivor \\
as evil dominion terminates. \\
The yawning abyss of madness.
}









\subsection{Mortal armies come into fashion}
Originally, the master races did not send armies of mortals into battle. That was not cost-effective, since mortals were nigh-worthless when pitted against the master races.  

But after the cataclysmic \secondbanewar, the \dragons{} and \resphain{} had become critically decimated, and it would take them many millennia to recover their numbers. Their slave races were also decimated, but they could be replenished far faster. So suddenly it began to pay off to raise armies of mortals for war. 

In the beginning, these mortals were outfitted with terrible \hr{technology}{high-tech weapons} and magic, but this turned out to be too dangerous, so after the adoption of the \hr{Charade}{\charade}, this practice was abolished. 









\subsection{\Sathariah{} bloodlines dominate}
The \resphan{} people saw three horrible wars: The rebellion, the \secondbanewar{} and the \resphanwars. 
%Many, many \resphain{} were slaughtered in the rebellion
All this bloody fighting wiped out most of the number. Above it all, the \satharioth{} stood victorious, with their allies and blood-kin at their side. 

Their houses and bloodlines came to dominate the \resphan{} race, and today most \resphain{} have some \sathariah{} blood in them. This makes \hr{Curse}{\NexagglachelsCurse} all the more potent. 










\subsection[Mystraacht falls]{\Mystraacht{} falls}
\target{Mystraacht betrayed}
The \Mystraacht{} were the most adept among the clans at utilizing the power of \chaos{} and combining it with the \erebean{} power of the \banes. 
So they were the strongest, and none of the other \resphan{} kingdoms, nor even the \dragons, could stand against them. 
They might even have conquered the planet, were it not for treachery. 
For \hr{Zachirah}{\Zachirah}, the Overlord of \Mystraacht{}, was betrayed, by forces inside the clan as well as outside it, and he was assassinated. 





\subsubsection{\Shiaraid{} betrays \Zachirah}
\target{Shiaraid betrays Zachirah}
\hr{Shiaraid's tragedy}{\ps{\Shiaraid} tragedy} was \NexagglachelsCurse, which forced her to destroy herself and those she loved. 
One person she loved was her father, \Zachirah. 

Somehow the Curse turned them against one another. 
She did not mean to, but her destructive impulses made her betray him and be instrumental in his downfall. 





\subsubsection{\Zachirah{} dies}
\target{Zachirah dies}
When \Zachirah{} was finally killed, he ordered his \hr{Zachirah's slave Resviel}{slave \resviel} to give him their life force to sustain him. 
They did so willingly, sacrificing their souls in the process. 
(Life drain is \hr{Voluntary drain}{more effective if it's willing}.)
But to no avail; he still died. 

When \Zachirah{} realized he was doomed, he cast a desperate spell that destroyed his soul, causing it to explode. 
He would rather destroy himself than let his enemies consume his remains. 

His enemies were shocked. 
\ta{Only a madman would destroy his own soul,} they thought. 
But some of them sensed a trace of \ps{\Nexagglachel} savage essence in \ps{\Zachirah} eyes in his last moments. 
They speculate if \hr{Curse}{\NexagglachelsCurse} played a part. 

Several princes now fought for the legendary Throne of \Mystraacht, but none was able to prevail. The clan crumbled in internal struggles for power and was diminished. 





\subsubsection{Ramiel defeated at sea}
\target{Ramiel defeated at sea}
Ramiel had a traumatic defeat in a naval battle which spelled the end of his career and spurred him on to \hr{Malach project}{become a \Malach}. 
It also gave him \hr{Ramiel fears the sea}{a fear of the sea}. 

\target{Ascaril destroyed}
During this ill-fated battle, Ramiel's sword, \hr{Ascaril}{\Ascaril}, is shattered and destroyed. 

Ramiel is killed, but only temporarily. 









\subsection{The \Malach{} Project}
\target{Malach project}
The \Malach{} project started as a secret underground gathering of \resphain{} who were disgruntled with the dynasties. 
They had been dishonoured and felt betrayed. 
So they wanted to be \uber{} and show the others how great they were and how much glory they deserved, and thus claim their rightful places and power. 

The \banelords{} supported them. 
But \Azraid{} did not know about them until very late in the process. 
He considered that a great personal failure. 
He thought he knew everything. 
He would later rectify that by \hr{Captive Malach}{capturing a \malach} for research. 

They envisioned the \Malach{} project. 
It was supposed to be the successor to the \sathariah{} project and transform them into super-powered \uber-\resphain. 





\subsubsection{\Malach{} cannibalism}
\target{Cannibal Malachim}
\index{cannibalism!\Malachim}
Just as the \satharioth{} grew strong by consuming \Nexagglachel, 
the \malachim{} were to derive their power from stolen and subsumed \resphan{} souls. 
It had been known for a while that the \resphain{} were meant to devour others of their kind to survive and grow, but the \malach{} project aimed to take this to its utmost consequence. 
Each \malach{} was to become a walking \carcer, a deep well of souls, and of \emph{power}. 

To achieve this, they had to capture, kill and devour \emph{many} \resphain{}.
(They endeavoured to victimize their own enemies as much as they could.
Ramiel-tachi, after their fall-from-grace, had many such enemies.)
That is why the project had to be kept such a secret and operate underground.  
The dynasties would destroy them if they knew. 





\subsubsection{It went wrong}
But someone had gotten word of their plan and wanted to thwart it. 
Sentinels and Cabalists alike infiltrated their group and fucked up the spells and research. 
\hr{Curse}{\ps{\Nexagglachel}{} ghost} also played a part (some of the prospective \malachim{} were \satharioth). 

% The spells were very expensive and difficult to carry out. 
% So instead of doing just one test run they decided to risk it and make several \malachim{} at once. 
% One of the \satharioth{} stepped up and claimed that he/she was not afraid and wanted to be part of the first batch. 
% This made the others fight over the remaining places. 
% So in the end, it was the most powerful ones that went first. 
% (Some also feared that if the weaker ones were transformed into \uber-powerful \malachim, they might strike back at their previously-more-powerful brethren and betray them when they had the chance, before the \satharioth{} could go through the ritual and surpass them again.)
At first, it seemed to go well. 
When he first \malachim{} came out on the other side, they had new and enhanced powers. 
Their new powers were erratic and difficult to control, but they had no reason to assume that this was anything but an issue of practice and experience. 

So they carried on and created more \malachim. 
One of the \satharioth{} stepped up and claimed that he/she was not afraid and wanted to be part of the first batch. 
This made the others fight over the remaining places. 
So in the end, it was the most powerful ones that went first. 
(Some also feared that if the weaker ones were transformed into \uber-powerful \malachim, they might strike back at their previously-more-powerful brethren and betray them when they had the chance, before the \satharioth{} could go through the ritual and surpass them again.)

Some days later, it started going wrong. 
The \malachim{} began to suffer from side effects. 
They were prone to amnesia, manic behaviour and disease. 
Gradually, over a course of days, they wasted away mentally and physically, until they died. 

The rest knew that the dead \malachim{} were not destroyed, but their souls had grown faint and Shrouded and were difficult to track. 
Later the remaining next-of-kin discovered that the \malachim{} were being reborn with amnesia as \humans{} (later called \hs{Scions}). 

There were many more who wanted to become \malachim, but sinced it went so wrong, the spell was never repeated. 
They did more research and tried to fix the flaws, but they did not succeed, so they soon abandoned the project and returned to their dynasties, defeated. 





\subsubsection{\Cishiel{} wanted to join}
\target{Cishiel wanted to be a Malach}
\hr{Cishiel}{\Cishiel} wanted to join the \malach{} project and be part of the first generation. 
But Ramiel forbade it. 
She was still a young girl, and his only heir. 
He did not want to see her put in harm's way. 

She was bitter. 
But after it all went wrong she had to admit that he was right. 

In the days when the \malachim{} were going mad, it was horrible for the young \Cishiel{} to witness her father, the mighty Ramiel, wasting away and degenerating into a maddened wretch. 
She was now very grateful that he had forbidden her to partake. 





\subsubsection{They lose their memory}
The \malachim{} lose their memory and descend into amnesia and madness. 
They feel great pain, anguish, sorrow and hate over this betrayal.

\lyricslimbonicart{Purgatorial Agony}{
  Experimental malediction.\\
  Destructive minds.\\
  Seeking places no living can find.\\
  Awaiting darkness, transcending, venture into the night.
  
  I hide within places unknown.\\
  There was nothing else to do.\\
  With sorrow and hatred burning inside,\\
  the suffering was endless.\\
  Mementos undivine.\\
  The bleeding scenarios,\\
  The reservoirs of shame.\\
  Damned in misanthropic fires,\\
  the soul dwelt.
  
  The feelings for mankind were gone,\\
  and so were the values of life.\\
  There was only a final wish:\\
  Death before a living hell.
}

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  DeathspellOmega
}{
  A Chore for the Lost
}{
  An exhausted fall into disgrace, \\
  famished for peace, \\
  for a mere moment of respite in dying eternities, \\
  on the verge of being deprived of all humanity: \\
  Nonsense is the outcome of every possible sense, \\
  it is the start of transcendence, \\
  the dissolution that spreads without limits \\
  and the critical violation.
}














\section{Other races}
Remember that even though the period is often called \quo{the \resphanwars}, the \nagae, \aryothim{} and \vorcanths{} also played important roles. 























