\bookchapter{Beyond the Veil}

\begin{comment}
\subsection{Darkness}
\end{comment}

Darkness. All was darkness. 

And silence. 

And cold. 

\tho{What is this?} \Icor{} thought to himself. 
\tho{Where am I? Why is everything dark?} 

Slowly it came back to him. 
\tho{I was stabbed. 
  Poisoned. \Tiroco{} was there. 
  And the Redcor, Camilienne. 
  She tried to heal me. 
  The \Sephiroth{}... it was awful.
  
  She failed.
  
  Did I die? 
  Am I dead? 
  Is this the afterlife?
  
  \Tiroco...
  
  No, I can't be dead. 
  I passed out from the pain. 
  I'll be fine.}

He couldn't feel his body. He had no limbs. The pain of the poison was gone, replaced by a dull coldness. 

\tho{I am alive. 
  I passed out. 
  I am sleeping. 
  I'll live. 
  I'll see \Tiroco{} again. 
  I'll see my children again.}

Cold. 

Darkness. 

Nothingness.

\tho{But if I am sleeping, why am I not dreaming? 
  Why am I stranded in this... void?
  
  If this is a dream, then it's like no dream I've ever had.
  
  It is said that you can wake yourself from a dream by pinching your arm. 
  But I can't feel my arms!
  
  I am freezing.
  
  Oh, Light. I must be dead. 
  Am I dead?
  I can't be dead. 
  I can't. 
  
  Oh, Light. 
  I'm dead. 
  I'll never see \Tiroco{} again. 
  Roric. 
  Little Frico.
  And the egg. 
  We were so looking forward to seeing the egg hatch...
  
  I can't be dead.
  
  I don't want to be dead.
  
  I refuse to be dead!}

But even though he refused all he could, the darkness and cold did not go away. 

Endless nothingness. 

He could not see. 
Could not hear. 
Could feel nothing but the omnipresent cold. 

\tho{I am losing my mind.

  Is this the afterlife? 
  I can't be. 
  I am supposed to go into the Light.
  
  By the \Sephiroth, I am a faithful and pious Iquinian. 
  I am supposed to be embraced by the Light into eternal bliss. 
  That's what the church has always preached. 
  That's what I have always believed.
  
  Then why am I stranded here? 
  Why am I not going into the Light?
  
  The Light. 
  The \sephiroth. 
  I saw them. 
  I felt them. 
  They were supposed to save me. 
  They didn't. 
  
  And where are they now? 
  The \sephiroth{} are supposed to come for me when I die. 
  Why haven't they come for me?
  
  Am I doomed to spend eternity in this hellish void?
  
  Is this \Itzach?
  
  It can't be. 
  I am not wicked. 
  I am good. 
  I should go into the Light. 
  
  I don't want to stay here forever. 
  
  I won't. 
  
  I won't believe it!
  
  I just died, and they haven't buried me yet. 
  They haven't recited the prayers for me yet. 
  That must be the reason. 
  As soon as they perform my last rites I will go into the Light. 
  That must be it. 
  I am not damned. 
  I won't stay here forever. 
  I will go into the Light. 
  Soon.
  
  \Tiroco... hurry. I don't want to stay here.
  
  \Tiroco...}



