
\bookchapter{Screaming in the Dark}

% The Ring of Iryx:

% Grum asks Faeni why she is not wearing the gold ring.
% It is one he gave her a week ago or so, taken from some trader they robbed. 
% Dutifully she fished out the ring. 
% She did not like it.
% It is gold, but blotched and discoloured.
% The shapes carved on it do not form any recognizable pictures, but they suggest the loathsomely sinuous forms of eels or worms or some other slithering things. 
% There is something eerie about the small green stone, too. 
% Whenever she looks at it, she feels like it stares back, like the cold eye of some slimy fish.
% But she puts on the ring anyway.

% In the end, Carzain takes the ring from the woman's body. 
% In the village: 
% He looks at the ring now on his finger, the one he had taken from the bandit woman's body.
% The Ring of \Iryx.
% The ring has long been kept in the silent monastery of Sorn-Gul. 
% Some weeks ago Carzain heard that the monastery had been sacked by barbarians and their sorcerous artifacts stolen. 
% Immediately Carzain began to covet the fabled ring and made efforts to learn its whereabouts. 
% Carzain has spent some time trying to track it.
% Finally, not many days ago, he caught word that it had \travelled, through a number of owners, to Grum's gang of raiders. 
% He jumped at the chance to obtain the precious artifact, and rid the world of a gang of marauding scum in the process.
% And now finally the ring is his. 

\begin{comment}
  \section{Village}
\end{comment}
\placestamp{Village of \maybehs{Derwael}, \maybehs{Pelidor}}
\ta{Mother! Don't die!} cried Tur. 

\ta{T-Tur\prikker} his mother stammered, coughing up blood. 

\ta{No, don't speak,} said Tur's father, taking his wife's hand.
\ta{Just lie still. The healer will be here soon. You'll make it. I know you will.}
Tur and his father were trying to stop the bleeding wound in her chest, where the raider's sword had torn through her scales. 

\tho{\Itzach curse those damned \humans,} Tur thought. 

It was the third raid they had suffered. 
The bandits had killed ten people by now, and there was almost nothing of value left in the village of Derwael. 
Tur looked around and saw thatched roofs smoldering, booths overturned, shops smashed. 
From all around came the moaning and weeping of the dead and wounded and their kin\dash people like himself. 

\ta{What is wrong with those \human?} wailed a voice nearby.
\ta{How can they rob and kill decent, Light-fearing people who have never done them harm?
  Have they no heart?}

\ta{No,} said Tur, his voice full of hate. 
\ta{They do not.
  They are not civilized people with respect for life, like us \scathae.
  They are \humans.}
Tur had lived all his life in Derwael, but he knew all the stories and legends. 
For thousands of years in what was now called the \Human Age, wicked \VaimonClans had ruled as tyrants, conquering and oppressing the \scathae who had dwelt on \Miith long before the \humans came.
It was well known that \ClanZether was the only pious clan; all the other Vaimons were corrupt \human-supremacists. 
\tho{This is what \humans are like. 
  Fighting and killing and destroying is all they do.}

\ta{This isn't right.
  The \VaimonCaliphate is gone. 
  The \Human Age is past.
  They don't rule \Miith anymore!
  We \scathae shouldn't cower in fear of them any longer. 
  It's horribly wrong that they still prey on us.
  Are we not subjects of Pelidor?
  Is Pelidor not a \scathaese land?
  Is the \rayuth in \Malcur not a \scatha like us?
  Why, then, must we suffer the depredations of these \humans?}

Tur looked around. 
No one spoke. 
Everyone shared his outrage, but no one could give him the answer he sought. 

\ta{It is not right,} Tur repeated.
\ta{\Scathae are not defenseless.
  We are stronger than \humans. 
  If only we had proper weapons.
  With a gun and a sword and I would take on any \human.}
But the villagers were unarmed and unused to violence, where the raiders were armed and vicious. 

Something caught Tur's eye and he whirled about. 
Another \human! 
In his village! 
Walking down the steet towards him! 
Tur let loose a vicious growl and seized up his pitchfork. 
He may not have a sword or a gun, but he was not quite defenseless. 

The \human was perhaps in his thirties, six feet tall, clad in dark leathers and a long hooded cloak.
He had the upright pose of a \quo{Man of the Light}, but his skin was darker\dash although not nearly as dark as that of the black men from \Durcac. 
His face was beardless, framed by long black hair that fell to his shoulders. 
In his belt he carried a pistol, a dirk and a sabre\dash a Vaimon's weapon. 

\ta{Who are you?} said Tur, eyeing the dark-clad, dark-skinned man. 
\ta{Another one of you scum, come back to kill more innocent people?
  I'll get you!}

\ta{No, Tur, wait!} said old Erowol, stepping out from behind the \human.
\ta{This man is not our enemy.}

\ta{What are you talking about?} said Tur, not taking his eyes from the \human. 

\ta{He is not a bandit,} said Erowol.
\ta{He can help us.}

\ta{He's a \human! He's just like the rest of his kind!}


\ta{I am a Vaimon,} said the \human.
He had not drawn his sabre or pistol and merely watched Tur with cold eyes.
He pointed to Tur's mother, who had now fallen unconscious. 
\ta{That \sphyle is badly wounded. 
  She will die soon. 
  I can help her.}

\ta{Don't you come near her!}
Tur took a step forward and poked the air with his pitchfork. 

\ta{Calm down, Tur!} said Erowol. 
Old and frail though he might be, his voice still carried enough authority to make Tur instinctively obey. 
\ta{This man is here to help her, not harm her. Now make room.}

Impotently Tur stepped aside. 
His hands twitched on the fork as the \human sat down by his mother and fingered her wounds. 

\ta{What happened to her?} asked the Vaimon. 

Tur's father explained how his wife had taken up a gun and tried to fight off the villains. 
She was no trained shooter, so she missed with her single bullet. 
The bandits cut her down and stole the gun, then rode off on their \relcs, laughing the whole way. 

The Vaimon laid his hands on her and closed his eyes. 
\ta{\Ishiel,} he murmured, invoking the \sephirah and its healing power. 
Tur's mother twitched and gasped but did not awake, and Tur could see no change in the wounds. 
The Vaimon sat still for a few more moments, concentrating, before he rose. 
\ta{She will live,} he declared. 

In the meantime more people had gathered around them.
A score of \scathae surrounded the \human, all brandishing pitchforks, axes, clubs, sticks, long knives and even a bow. 
For many moments the tense silence stretched as the Vaimon regarded them with his cold, brown eyes, as if daring them to attack. 

\ta{Make way!} came a voice at last. 
The crowd parted to admit the speaker. 
It was Claedd, a middle-aged \sphyle and one of the most respected people of Derwael. 
She was the only villager to own a sword, a sturdy old weapon which she now held ready in her hand. 

Claedd met the \human's stare. 
\ta{Who are you?}

\ta{\CarzainShireyo. Vaimon of Clan Geican.}

Tur licked both his eyes at the mention of the name. 
He had heard of this man. 
He was a wandering adventurer, mercenary and assassin. 
A dark sorcerer. 
A villain who fought villains. 
A monster who fought monsters. 

\ta{Who are you?} asked \Shachar. 

\ta{My name is Claedd.}

\ta{You lead this village?}

\ta{When I have to,} said Claedd with a resigned grimace.
\ta{What do you want from us?}

\ta{Food, shelter and various supplies.}

\ta{Why should we give them to you?}

\ta{Well, the obvious answer would be \quo{money}. Apart from that, I can also help you,} said \Shachar with a glance in Tur's mother's direction. 

\ta{Why should we trust you, \human?} said a club-wielding \scatha. 
\ta{I've heard about you.
  You're a mercenary and an evil sorcerer. 
  And you're Geican!}
The Vaimon \ClanGeican was evil, Tur knew. 
It was the \vclan that had once produced \Belzir, the depraved and corrupt witch-queen whose sins had destroyed the ancient \VaimonCaliphate and devastated half of the world. 

\ta{Look what your kind did to us, \human!} the \scatha went on.
\ta{Look at the little child over there, crying over the body of her dead father.
  Can you bring him back to her?
  Huh?}

\Shachar glanced at the dead \dax in question. 
\ta{No. 
  I cannot.}
He looked up, gazing into empty space with a chilling half-smile.
\ta{Perhaps one day, when my powers have grown, I will be able to command life and death.
  As of yet, no, I cannot bring back the dead.}
He met Claedd's eyes, his visage now grim and serious.
\ta{But I can avenge them.
  In exchange for your aid, I will rid you of these bandits that plague you.}

\ta{You still have not argued why we should trust you,} said Claedd.
\ta{You are of their kind. 
  Why should you side with us?
  How do we know you are not out to trick us?}

\ta{Don't listen to anything he says,} said another \scatha.
\ta{His kind killed ten of our people!
  He'll just join them and come back to kill us.
  We should kill him now while he's alone and on foot.
  It's the only sensible thing to do.}

\Shachar stood tall and unafraid, barely acknowledging the speaker at all. 
He had still made no move to draw any of his weapons. 
Besides, they all knew the Vaimon's sabre and gun were the least of their worries.

\ta{I am not responsible for the actions of my \quo{kind},} said \Shachar. 
\ta{But nor have I any particular love of the \human race.
  It is no better than the \scatha race.
  These raiders are ample evidence of that. 
  I have decided to help you in this.
  Now tell me about them.}

Several villagers snarled and raised their weapons, offended by the commanding tone this stranger used toward their leader. 
But Claedd merely held \Shachar's gaze. 
Tur held his breath for a long moment. 

\ta{Hm,} said Claedd at length.
\ta{Very well. I will tell you.}
And she related everything she knew about the raiders. 
They had made their hideout somewhere in the jungle, presumably in the old ruined cemetery, a good hour's walk from the village. 
There were ten of them as far as the villagers could count. 
All were \human save two or three who were half-ogres; crossbreeds between \humans and the hulking, bestial \nephilim. 
These hybrids had the worst of both worlds: 
The size and strength of a \nephil and the sly, petty cruelty of a \human.
Their leader, Grum, was one such half-ogre. 
He was a huge man, nearly eight feet tall and as broad as a \muroc. 
There was a woman among them too; the villagers did not know her name, but it seemed she fought and killed as viciously as the nine men. 

All the raiders had guns and swords, and they rode \relcs. 
The villagers had almost no weapons and no \relcs. 
\Relcs, being fast-running \saurians, were favoured by soldiers, while poor farmers such as the people of Derwael were content with slower and sturdier beasts. 
This left the villagers hopelessly out\manoeuvred, unable to properly fight or pursue the raiders.

Tur thought it warped and wrong that \scathae should need a \human to save them from other \humans. 
Under sane conditions this would never happen. 
But Derwael was an isolated village, surrounded on all sides by a mass of jungles. 
It was an island in the \wylde. 
In name they belonged to the nation of Pelidor, but in practice they were on their own. 
The \rayuth and his court were far away and would not be coming to their rescue. 

\ta{Very well,} said \CarzainShireyo when Claedd had finished.
\ta{These miscreants are lower than beasts and deserve death. 
  I will kill them for you and return with proof. 
  You will owe me a better welcome then.}



\begin{comment}
  \section{Jungle}
\end{comment}
\placestamp{Ruined cemetery near Derwael, Pelidor}
\begin{comment}
  \subsection{Bandits haunted}
\end{comment}
The wind howled above, and the rustling of the swaying trees was like the whispering voices of sly goblins in the dark. 
The jungle was thick and impenetrable, wreathed in mystic \wildfog that hid the creatures of the shadows from sight. 
The ruined cemetery had once been a clearing, but the \wylde had closed in over the decades, and now the trees towered as much as a hundred feet above the camp, blocking out the sun and turning afternoon into gloomy night. 

The cemetery was an array of moss-grown tombstones and great crumbling blocks of masonry. 
Tall statues had once stood as silent sentinels watching over the tombs; now, broken and overgrown, they had the appearance of sickly amputees and lepers. 

As much as possible, Faeni kept her eyes on the bonfire and her companions. 
Whenever she looked upon the statues, the collapsed crypts or the mist-shrouded jungle beyond, she imagined menacing, hideous shapes slithering just beyond the circle of light. 

% Faeni shivered. 
% \tho{I hate this place,} she thought. 

But foreboding though the cemetery might be, at least it still had some \eidola intact. 
Back when the place had been inhabited, the enchanted \eidola had acted as boundaries of civilization, keeping the \wylde jungle at bay. 
After decades of neglect the \eidola had waned in potency, but they still offered some protection, providing a refuge from some of the worse horrors of the \wylde.
Unless they were to conquer the village of Derwael and settle there, this clearing was the safest place to make camp. 

\ta{Woman,} said Grum.
\ta{How do you like the necklace I gave you?}

\ta{Hmm\prikker}
Faeni idly fingered the necklace, a piece of booty from the last raid on the village. 
She was sorely disappointed. 
\tho{Grum probably thinks it's gold.
  Stupid bastard. 
  It's just polished brass.
  You're too dumb to know the difference. 
  Can't you even get me real gold?}

Grum frowned, annoyed by her silence. 
\ta{What?} he growled.

Faeni realized she had to do some acting, so she threw her small arms around the half-ogre's broad, bearded neck and kissed him on his huge lips.
\ta{Oh, thank you, Grum. It is beautiful.}

Grum grunted approvingly and began to run his big hands over her body.
\tho{Thank the \sephiroth. 
  He bought it.}
Faeni had no warm feelings for Grum, nor he for her, but she knew that she had to act the part of his willing hussy lest she be kicked out of the gang. 
Or worse, demoted to everyone's hussy. 
Kissing up to Grum's vanity was a cheap price to pay to retain her elevated status. 
Meanwhile, she did her best to manipulate him when she could. 
This was not easy, for dim-witted though the half-ogre might be, he had a frustrating tendency to simply not care what she said and thought. 

Suddenly there came a scream from the jungle.
Everyone gave a start; Faeni saw at least two of her companions jump to their feet and grab their weapons. 
What was that voice?
Who was it?
It might have been a \human. 
It sounded like a scream of pure horror, as if the man had been caught in the clutches of some gruesome, inhuman monster.

\ta{You think that was Rogg?} said one of the bandits. 
\ta{He went out to piss and hasn't come back.}

\ta{Bah,} snarled Grum with a have of his big, hairy hand.
\ta{It was just some animal.
  Rogg is dumb, but not that dumb.
  How hard can it be to piss?
  He can take care of himself.
  Now sit down.}
He grabbed Faeni and pulled her down on his lap

\tho{Grum is trying too hard.
  He is more worried than he lets on.}
She had felt his hands tense on her body when they heard the scream. 
\tho{Try as he might to hide it, he is just as afraid as the rest of us.}

Grum resumed his groping. 
Faeni responded mechanically with just barely enough rubbing and sighing to convince him she was enjoying it. 
Her mind was occupied elsewhere. 

\ta{Take it off,} Grum commanded. 

Obediently Faeni began to strip off her shirt. 
She despised Grum. 
He was not just a stupid brute, but an inhuman half-breed.
An animal. 
She hated him just like she hated most of these men. 
\tho{I am better than them. 
  I am smarter than any man here, and stronger than some.}
But she was not nearly as strong as a half-ogre.
Not strong enough to lead the gang. 
Besides, they would never accept a woman as their leader. 
So she had to accept a position as Grum's floosie and make do with whatever power she could scrounge for herself.
But it was not so bad. 
At least she was Grum's personal woman.
The gang leader had the sole right to her body, and he guarded her jealously from the lustful hands of the other gangsters. 

\ta{I don't like it,} said a thug.
\ta{Someone should go out and look for Rogg.}

Grum growled, and Faeni yelped as he squeezed her nipple hard.

\tho{Don't take it out on me, you dumb beast.}

\ta{Fine,} said Grum.
\ta{Then \emph{you} go and hold his dick while he pisses.}

Another thug, Ivar, rose to his feet.
\ta{I will go.} 

Ivar was the bravest of the gang. 
\tho{I'm glad it's not me.}
A shiver went through Faeni's body as she watched him slink off alone into the murky jungle. 
She tried to tell herself she was just freezing because she was stripped to the waist. 
She tried not to think about what slavering things might lurk in the shadows beyond the mystic fog. 

% In the beginning Faeni had hated stripping naked in front of the gang, and even worse, having Grum take her with all the men watching. 
% But since she had no choice, she might as well learn to enjoy it. 
% So instead of shrinking under the lustful eyes of the bandits she had learned to revel in them. 
% Her body was the thing the thugs desired most.
% She dangled it in front of their faces almost every day, but they would never have it.

Out of the corner of her eye Faeni could see Gawl, the youngest of the bandits. 
Though not a half-ogre, Gawl was a quite big and quite stupid young man. 
He sat shifting nervously, scratching his crotch and staring at her with hungry eyes. 
He always looked at her that way. 
As if he had never had a woman.
In fact, Faeni suspected he never had. 
She had come to enjoy taunting Gawl by parading her body before him. 
When Grum was looking the other way, Faeni winked at Gawl and kissed the air in his direction.
He goggled dumbly at her in response. 
She half expected drool to dribble down his chin. 

\emph{He is pathetic.}

Then came the voice of Ivar from the edge of the woods. 
\ta{Guys! Guys! Grum!} he shouted as he came running into the camp, a frenzied expression on his face. 

Grum sprang to his feet, unceremoniously dropping Faeni onto the ground. 
\ta{What's wrong with you? Where's Rogg?}

\ta{Dead,} said Ivar.
\ta{Killed by some monster, some\prikker thing!}
Ivar's face was pale, his eyes wild, his voice unnaturally shrill. 
The sight filled Faeni with fear. 

\tho{Ivar is the bravest of us.
  Nothing scares him. 
  
  What in \itzach's name could affect him like this?}

Suddenly the ruined cemetery seemed even less safe than before, for all its \eidola. 
The monolithic tombstones and silent, brooding statues took on an even more sinister aspect than before. 
It occurred to Faeni that this was a place of death where only the dead came. 
And the dead suffered not the living to pass through. 

\tho{This graveyard will be our graveyard. We're all going to die here.} 
% Such thoughts came to her. 

Grum drew his sword and his gun. 
Faeni huddled close to him for protection, but he brutally slapped her away. 
\ta{Get off me, woman!}

Then, from the darkness of the trees, an object was tossed into the middle of their camp. 
A small, roundish object. 
It fell near the fire and rolled. 
Faeni stared at it in puzzlement, then recoiled screaming as she realized what it was. 

With glazed eyes, Rogg's severed head stared back at her. 

\ta{What the hell happened?} Grum yelled at Ivar. 

\ta{I don't know. 
  I saw his headless body lying out there and saw a glimpse of some thing retreating from it.}

\ta{Speak the fuck up! What kind of \quo{thing}?}

\ta{%
  I don't know!
  Something horrid.
  Something unnatural.
  Something cold and dark and hateful and evil.
  A \qliphah.
  A thing of the Outer Darkness.}

\ta{Nonsense!} shouted Grum. 
\ta{You pussy! 
  It's just the \wylde making you see things. 
  You saw some animal in the dark and pissed yourself in fear, and now you're making up stories!}
Grum yelled louder and louder, as if to convince himself. 
Faeni could tell he did not believe his own words. 
They all knew Ivar had seen the \wylde and dead men many times before. 
He would not go telling ghost stories without good reason. 

The bandits had little time to discuss before the next horror assailed them. 
Now they heard the beating of great wings above them. 
Looking up, they saw an indistinct shape, black as the deepest night, blotting out the sky.
As it passed over the clearing it uttered a high-pitched shrill howl.
Where the scream earlier had been that of a man, this new shriek sounded nothing like any earthly creature. 
It was the cry of a pre-\human thing of the Elder Ages of unknown chaos and darkness, a nameless horror of the gulfs beyond the skies. 

With their nerves already fraught, none of the bandits dared stand before this hideous thing. 
In panic they ran for cover and lay cowering, waiting for the horror to pass them by. 

Faeni heard no more sounds from above. 

When she dared to look up, there was nothing to see. 
She rose to a crouch and looked around. 
Her companions had scattered. 
She could see a few of them near the fire.
Grum's large outline was easy to make out.
And she could see Ivar, who sat far from the fire but carried a torch. 
The rest were hidden in the gloom. 

She heard Grum's voice: 
\ta{Ivar! Get over here with that torch!}

Ivar rose from where he crouched and started toward Grum. 
But barely had he taken two steps before something\dash a dark blur\dash pounced on him. 
Ivar shouted and made to defend himself.
The torch went out. 
Ivar's yell turned to a scream, then to a gargle, then to silence. 
Faeni heard the thump of his body as it fell to the ground. 

Icy tendrils of dread gripped Faeni's limbs and held her still. 
\tho{That was not natural.}
Good torches did not just go out when dropped. 
Some dark force had snuffed it out, as if draining away the light to feed its own hunger.

\tho{This is no natural enemy.
  
  Some nameless thing is stalking us.}

Grum called to order. 
\ta{To me, men!
  Stop pissing yourselves and get back in line.
  We'll get this beast yet.} 

Grum moved closer to the fire, and several men rallied around him. 
Faeni wanted to join them, longed for the safety of the group, but she could not move, her body still frozen in the grip of fear. 

Then another shrill, inhuman howl ripped through the silence. 
A sound of pure malice, coming from directly above Grum and his group. 
On instinct, Faeni screamed, closed her eyes and lowered her head, huddling against the ground. 

She heard the bandits holler. 
There was a gunshot. 
Two gunshots. 
Then another hideous shriek. 
Different this time. 
Deeper, more wavering. 

\tho{Did they hit it? 
  Is the monster wounded?}

Faeni dared open her eyes and peek. 
She was just in time to see one of the bandits scream as an indistinct, shadowy blur whipped across his torse. 
A great bleeding wound sprang open on his chest and he fell to the ground, bleeding and yelling in pain. 
The others recoiled in horror from the body, leaving their fallen comrade gasping and cursing in his dying pains. 

Faeni squeezed her eyes shut, wishing she had never opened them. 
By now Faeni was trembling all over. 
She could barely think straight. 
\tho{%
  A monster is stalking us, and we're helpless against it.
  It's killed three men, and we've barely even caught a glimpse of it.
  What is it?
  How does it kill?
  How does it even look?
  How big is it?} 
She did not know.  
It could be huge. 
Like a \dragon.
Perhaps it \emph{was} a \dragon.
An incarnation of the hatred and evil of the Outer Darkness.
A thing of corruption and chaos, a destroyer of all that is pure.

Dimly she heard Grum shout in the distance. 
Another gunshot. 

The swoosh of great wings above. 

Then another \human scream, coming from barely two yards away. 

The feeling of warm, wet blood and gore splattering on her bare skin finally unfroze Faeni's limbs. 
And without a thought in her mind, she ran into the jungle. 



\begin{comment}
  \subsection{Grum dies}
\end{comment}
\new 
\ta{Come on!} shouted Grum.
\ta{We're not going to let this thing get away with killing our men!
  We can fight it!
  Men?}

Grum looked around. 
Listened. 
No answer. 
Only the whispering wind. 
He realized that all his men were either dead or fled. 
He was alone. 

Having discharged both his guns in vain, he could only yell and wave his sword. 
\ta{Come out! Come out, you beast!}
he hollered into the air.

And he was not feeling well. 
There was something wrong with him, he could tell.
He was weaker and slower and dumber than normal.
He felt dizzy, his limbs leaden. 

\tho{Is this some kind of spell?}

Then out of the corner of his eye, Grum saw a shape move. 
Not a flying thing in the sky.
A thing near the ground. 
In the gloom the shape was still dark, its outlines blurry. 
But it was coming at him. 

The assailant came within reach. 
Something lashed out from it. 
A metallic glint. 
Grum, reacting with a fighter's instincts, swiftly raised his sword. 
Blades clashed. 

Grum leapt a step back. 
Now, in the light of the bonfire, he got his first real look at his opponent.
It was not an amorphous horror. 
It was a man-shape, shorter than Grum, wielding a sabre. 
But he looked like no natural man. 
He was burning.
Black fire danced all over his body. 

The burning man attacked again, and again Grum parried. 
The half-ogre, being larger, instinctively wanted to take advantage of his greater reach and strength, so the next time the combatants closed, Grum punched with his off-hand. 
His opponent rolled, and the punch only glanced him.
Too late Grum realized his mistake as the black flames engulfed his bare hand. 
It burned, but not like regular fire.
It felt somehow hot and cold at the same time. 
It was a hideous, alien feeling. 
The dark fire was like the essence of raw, black, nameless evil, seeping into his body. 
Gasping with pain and dread, Grum wrenched himself away.

\tho{What is he? Is he man or monster?}

That was all Grum got to think, for his brief moment of shock left him open, and his foe struck. 
The burning man's sabre sliced into Grum's right arm, leaving a bleeding gash. 
Grum cried out and dropped his sword. 
Wasting no time, the burning man slashed again. 

Grum was hit. 

His neck burst. 

Blood fountained out. 

Pain filled him.

He gargled.

Tried to breathe but failed.

Fell to the ground. 

Grum's world went dark. 



\begin{comment}
  \subsection{Faeni raped}
\end{comment}
\new 
Faeni ran on through the jungle.
The gloom and her fear made her surroundings come to malignant life. 
Every hanging vine she touched felt like the slimy tentacle of some amorphous horror.
Every root that tripped her felt like the grasping claw of some ravenous beast.
Dimly over the noise of the forest she thought she could hear a monster's heavy footfalls and slavering breath behind her. 
Still she ran on, not daring to look back for fear of what what grisly shapes she might glimpse in the dark. 

Finally, after what seemed like a whole night, she could run no further and had to pause and rest. 

She stood and tried to still her panting breath so she could listen. 

\tho{Is it gone? Did I outrun it?}

For a moment she could hear nothing but the forest sounds. 

Then something jumped her. 
She screamed as a heavy body slammed her to the ground. 
It had caught her!
It was on her! 
She kicked and fought under its weight. 

There came a voice. 
\ta{Faeni, it's me!}

It took a while before she understood the words. 
It was a \human voice. 
A familiar voice. 

\tho{Gawl?}

Now she could recognize his round, stubbled face above her. 
He leered down at her with a broad, idiotic grin. 

Faeni realized she was still mostly naked. 
She tried to cover herself, but Gawl grabbed her arms and pinned them to the ground. 

\ta{Ow! 
  What are you doing? 
  Get off me!
  Let me go, you stupid idiot!}

\ta{Shut up!} said Gawl, releasing her arm just long enough to backhand her across the face. 

\ta{Ah!} she cried. 
\ta{What's wrong with you?
  Get off me!
  Moron! Loser! Pussy!}

\ta{You always call me names like that,}
said Gawl, his voice shaky and frantic. 
\ta{You always mock me and look down on me. 
  You think you're better than me, do you?
  Huh, slut?
  Just because you're Grum's whore?}

\ta{What are you talking about?} said Faeni.
She was growing more afraid by the moment, but still she kept up her \facade.
\ta{At least Grum is a man.
  You're not even a real man.
  You're just some big, dumb\prikker}

\ta{I said shut up!} yelled Gawl in what was almost a falsetto. 
He punched her hard in the stomach. 
All breath went out of her, leaving her coughing and gasping for air. 

Gawl was giggling hysterically now.
\ta{We're done for, you know that?
  You're dead.
  I'm dead.
  The monster is going to come for us and kill us.}

Faeni realized that Gawl was completely crazy. 
The encounter with the monster must have driven him out of his wits. 

\ta{But I don't want to die never having fucked a woman.}

Faeni screamed, writhed and resisted as much as she could, but she was already exhausted, and Gawl was larger, younger and stronger. 
She managed to get in a few kicks and scratches, but Gawl held her down and ripped the rest of her clothes away. 

\ta{Hee-hee-hee,} he giggled. 
\ta{This is going to be great!}
In the dark, Faeni could only barely discern his face, staring eyes and mindless grin. 

\tho{Oh, Silqua. 
  This can't be happening to me. 
  This can't be happening to me!
  Silqua, please, don't let this be happening to me!}

\ta{You think you're better than me, huh, bitch?
  Think I'm not good enough to have you?
  Well, I'll show you\prikker gaah!}
There was a gruesome splattering noise. 
Gawl cried out and choked. 
Blood erupted from his back.
His large body slumped and fell on her, punching all air out of her. 

He convulsed, then lay still. 

\tho{Merciful Silqua.
  He is dead.
  
  What killed him?
  
  The monster?}

With effort she pushed Gawl's heavy body off her and looked up. 
Squinting, she could see a silhouette above her. 
The silhouette of a man. 

\ta{Wh-who are you?} she managed. 

\ta{I am \CarzainShireyo,} said a baritone voice. 
A \human voice. 

Faeni was crawling on all fours, naked, unarmed and exhausted. 
She could not hope to fight or escape. 
She knew her last chance was to beg for her life.
\ta{You're \human! You saved me!} she blabbered.
\ta{Please don't kill me!
  Let me live! I'll do anything! Anything you want!}

\ta{Your gang is guilty of robbery and murder. 
  I have no reason to believe you are any better than the rest.
  I promised the villagers I would kill you all, and I intend to keep my word.}

The man stepped closer, sabre in hand.

\ta{No! No! I'll do anything!} Faeni pleaded. 

\ta{Look at it from the bright side. 
  I did not let him rape you.}

\Shachar ran his sabre through her breast.



\placestamp{Village of \maybehs{Derwael}, \maybehs{Pelidor}}
\begin{comment}
  \section{Return to the village}
\end{comment}
The villagers was bustling with activity again, people rushing to and fro and repairing the booths and roofs the raiders had ruined. 
They still mourned their dead, but it had lifted their spirits to learn that their tormentors had been wiped out. 
Their severed heads, which Carzain had brought back, now hung from poles as proof that the villages had nothing more to fear. 

\tho{That went well,} thought Carzain to himself.
\tho{Those thugs were easier to deal with than I had feared, despite their numbers.
  Is that no so, Vizicar?}

\vizicar{Yes,} said the voice in Carzain's head, the ghost of \VizicarDurasRespina.
\vizicar{But circumstances were in our \favour.
  You felt it.
  The \qliphoth are strong in that place.
  We were able to reach into the Beyond and perform feats that would normally be beyond us. And call forth fearsome things from the Beyond.}

\tho{If only for a moment,} Carzain commented. 

Those flying, shrieking things that Carzain had summoned had never truly been under his control. 
He had merely ripped a hole in the veils of reality and lured the mindless horrors into passing from the Beyond into the world for a brief swoop, before the natural barriers of the world cast them back into the elder darkness. 
Indeed, the hungry things might easily have turned on him, but he had judged it worth the gamble. 
\CarzainShireyo was nothing if not a risk-taker. 

Carzain had been surprised when one of the creatures was shot. 
He knew little about these alien monsters, so he could not say for certain whether they could be killed or even hurt by mortal weapons. 
If indeed they could be killed at all; for some of the terrible denizens of the Realms Beyond were immortal and ageless, older than the \human race by far if legends could be believed. 

Then the chattering of some townspeople caught his ear. 

\ta{Dreadful news, this talk of war,} said an older \sphyle.
\ta{I hope it will not touch us all the way up here.}

\ta{Who knows?} said another \sphyle.
\ta{The \rayuth might come collecting new taxes or even drafting our young ones as soldiers\prikker}

\ta{What is this war you speak of?} Carzain broke in. 
The two townspeople recoiled and fell silent as he approached, in fear of the mercenary sorcerer. 
\ta{Speak! What war?}

\ta{W-we heard it a few days ago,} stammered one of them.
\ta{Th-the king of Runger has invaded Pelidor.}

\ta{His army is marching west towards \Malcur,} said the other.

\ta{Is he now?} said Carzain.
\ta{Thank you.}
He turned away and walked on, pondering. 

\tho{An invasion? Of my homeland? Interesting.}

\vizicar{Indeed,} said Vizicar in his head. 
\vizicar{We will need to investigate\prikker}









