%\section{The Duke's Ball}
\bookchapter{Daggers and \Daemons}
%\section{The Veil of Death}

\begin{comment}
\subsection{The ball}
\end{comment}

% It's a big royal ball in Malcur. 
% Tiroco is talking to a flattering young lord while her husband the \rayuth is dancing. She sees him dancing with a young woman in a yellow dress. By chance she catches her husband's eye just as the yellow-clad woman sticks a dagger into him. 
% She sees his eye widen in pain and shock, and she looks down to see the dagger sticking from his chest. The yellow woman is slinking away. Tiroco screams and points, and everyone sees the dagger. Ladies scream and faint. The yellow-clad one screams, too, but it sounds fake to Tiroco's eye, and when she falls over, apparently fainted, Tiroco is not impressed. She orders the guards to seize her. 

% From a short way away, Charcoal (Archibald Curwen) hears the scream and moves in to investigate. We see his quick, deductive reasoning at work. He deduces that the dance was not close enough for any reasonable assassin to knife the king with no one noticing, and that magic must have been used. He uses his `second sight' to go into trance and see into the Beyond. And true, he detects the lingering scent that is the residue of a spell. He cannot be sure, but it smells likely that world-walking and lie-weaving magic was used. 
%\dateplace{Runger war}{21st}{\Atzirah}{Ducal palace, Malcur, Pelidor}
\stamp
  {\dateIcorDies}
  {\CastlePelidor, \hs{Malcur}, \hs{Pelidor}}

\begin{garbage}
\ta{And have I mentioned that you look positively stunning tonight, dear \rinyuth?} 

\Tiroco{} smiled and chuckled. 
\ta{%
  Really, Baron Graenell, should you not be saving your charms for the unmarried maidens?} 

\ta{Oh, fear not, my Lady. I have enough to spread around.} 

They laughed. Coming from a lesser man such a comment might seem a feeble brag, but she could not deny that Graenell spoke the truth. Too young to remember first-hand, she knew from the gossip that the Baron had been quite popular with the ladies at court in his youth, and now, recently widowed after more than a decade of marriage, he was evidently back in the courtship game with a vengeance. 

%He was handsome, and charming. And rich, and powerful. Yes, she could well imagine herself falling for the Baron, under different circumstances. But of course, she was married to the \rayuth, the most powerful lord in Pelidor. \Tiroco{} had cause to envy no \sphyle. 
He was handsome, and charming, yes. And rich, and powerful. But also rather old, and perhaps shallow in the end. Not that it mattered to her, of course. She was married to the \rayuth, the most powerful lord in Pelidor. \Tiroco{} had cause to envy no \sphyle. 

She looked out over the hall and caught sight of her husband dancing, regal-looking in his blue silks, white furs and golden jewelry. \Tepharin{} of descent, his scales were azure and the ridges on his snout and eyebrows were fine and sharp. A handsome \dax, he was. That, too. And good and caring, for her and their children. 
\tho{Yes, I envy no \sphyle.} 

\Rayuth[\Icor], along with many guests, amused themselves in the tacupien, an native Pelidorian dance. For the nonce the dance saw the \rayuth paired with a young woman, round of features, dark brown of hair and clad in a wide dress of yellow. He gave her his hand and she took it, curtsying as proscribed by the dance while smiling shyly at being this close to her sovereign. He pulled her in by the hand and suddenly felt somewhat cramped as the dance brought several pairs of dancers close together in a cluster. 

Stretching out his head for a breath of air, \Icor{} noticed his wife standing near the edge of the dance floor. 
\tho{She is beautiful,} he thought. He caught her eye and smiled. 

%\Icor{} met his wife's eye. She was beautiful. He smiled. 

Then grunted as he felt an intense, stabbing pain in his stomach. 

He looked down, found a dagger buried to the hilt in his belly. He looked up, met the eyes of the girl in yellow. He thought he saw a wicked smile on her face. She mouthed words, but he could not hear them. Then she turned and walked away through the crowd. 

\tho{I have been attacked. I have been stabbed! I have been assassinated!} He tried to cry out, but no sound came out. He wanted to run, but his legs did not obey. The pain spread into his limbs. 

From the raised part of the floor, \Tiroco{} saw her \rayuth's smile fade to a silent gasp, saw his playful eyes widen in shock and pain. His snout opened, his tongue spasmed, but no sound came out. \ta{What is going on?} she said aloud. 

\ta{Eh\prikker what?} said a distracted Graenell beside her. 

The dancers surrounding the \rayuth now gave way as the dance pulled them along. A yellow-clad \human{} seemed to move away with great speed, almost as if fleeing. \Tiroco{} craned her neck to see. A \sphyle{} with a wide-brimmed hat finally moved, giving the \rinyuth a clear view of her husband, who still stood gasping. She looked down to see the hilt of a dagger jutting out of his chest, saw blood seeping out to stain the white silk. 

\ta{Aaaaaaa!} she screamed, pointing her finger. 
\ta{%
  The \rayuth! \Rayuth[\Icor] has been attacked! Help him! For the \hs{Light}, someone help him!} 

The surrounding dancers now turned, saw the \rayuth reeling, saw the dagger and the stain of blood. Ladies shrieked and dropped to the floor or in the arms of their partners, fainting. Lords shouted in anger and bewilderment. People ran. Soon the whole dance floor was in panic. 

%Heads turned toward him. More screams. Ladies fainted. People ran. Shouting. Panic. 

\Icor{} registered all this through a haze of pain. 
\tho{A simple stab shouldn't cause this.} 
He had fought battles and taken wounds before. 
\tho{Poison. I have been poisoned.} 

His legs failed under him. So did his consciousness. \Icor{} slipped into a daze\prikker

\prikker and was jarred awake as his head crashed into the hard marble floor. 

With consciousness, the pain returned. It crept into his every finger, every toe, every scale. 
\tho{Take it away! Light, take it away!}

\Tiroco{} saw him fall. 
\tho{\Icor{} has been attacked. As the \rinyuth, I must command.} 
\ta{Guards!} she shouted at the top of her voice. 
\ta{%
  Get a healer here, fast! And block the doors! We have an assassin in here!} 
More shrieks at that pronouncement. 
\ta{Baron Graenell! Help me restore some order.} 

\ta{Yes, \rinyuth,} he said promptly, then turned and began barking orders. \ta{%
  Stop running, you fools! Guards, to me! You up there, keep your eyes on the dance floor! Don't let the assassin escape!}

Some yards away from the \rayuth she espied the yellow-clad woman with whom \Icor{} had been dancing. It appeared to \Tiroco{} that she was slinking away, but as the commotion around her grew, she turned to the \rayuth, seemingly noticing the knife for the first time. She shrieked once. Shrieked again. Then she fell into the arms of a nearby \dax, unconscious. 
\tho{Or is she?} 
To \Tiroco{} the display seemed fake, premeditated. 

She jumped forward. 
\ta{Sieze her! The woman in yellow, get her! She is the assassin!}

At first no one understood her command, but with repeated gesturing she managed to get the message across, and several nearby people moved in to grab the \human. But \Tiroco{} did not stay to attend the apprehension, instead rushing to her husband's side. 

%One swift-acting \sphyle{} had come to his aid, one whom \Tiroco{} recognized as \Risvet, the Baroness of Hemfork. She had removed the dagger and bound the wound tightly with a scarf, halting the blood loss. The \rinyuth knelt down beside him and took his hand in hers. 

Lying on the floor, it took \Icor{} a while to understand that a voice was calling out to him. 
\ta{My lord \rayuth!} 
He opened his eyes to see a middle-aged \sphyle{}, with sky blue scales and wearing a white-and-blue robe. Baroness \Risvet{} Hemfork. 
\ta{\Rayuth[\Icor], can you hear me? Hang on, \rayuth. Help is on the way.}

\ta{\Tiroco\prikker} he managed. 

\ta{Your wife is coming. Help is coming, my lord \rayuth.} Hemfork knelt beside him. \ta{Let us get rid of this.} New pain shot through his stomach as she removed the dagger. He cried out, however feebly. Hemfork quickly tied a scarf tightly around the wound. But the pain of the poison remained. 

He heard a familiar voice now. \ta{\Icor!} He saw \Tiroco{} on the floor beside him, felt her hands around his. 

\ta{T\prikker\Tiroco,} he stammered. 

\ta{%
  Yes, I am here. Don't worry, \Icor{}. You will be fine. The healer will be here any minute.}

Her image was blurred. Not only were his eyes full of tears from the pain, his senses were also growing dull from the effect of the venom.

\ta{I can't\prikker feel\prikker my body.} 
His voice was a hoarse rasp. 
\ta{I have been poisoned. I think\prikker I think I'm dying.}

\ta{No!} she cried, tears forming in eyes, too. 
\ta{\emph{No!} You will be fine! You will!}

\Risvet{} climbed to her feet beside \Tiroco. 
\ta{Where is that healer?} she shouted. 

\ta{\Tiroco\prikker} His voice was only a whisper now. 

\ta{\Icor{}! Hang on!} 

\ta{Make way!} came an imperious voice from above. \Icor{} discerned the form of a woman in a fiery red dress that matched her hair. 
\tho{\hs{Redcor}. The younger, thinner one. \Clarice{} \Camilienne.}

%Into view came \Clarice{} Camilienne, a thin woman in a fiery red dress that matched her hair. 
In \ps{\Tiroco}{} eyes, the Redcor \hr{Soror}{\soror} took her bloody time arranging her skirts before finally seating herself on the floor next to the fallen \rayuth. Finally she placed her long-fingered hands on his head and intoned: 
\ta{\hr{Ishiel}{\Ishiel}.} 

% Clarice comes to heal Icor. 
% She invokes Ishiel. 
% Ishiel comes and tries to heal Icor. 
% 
% Icor feels Ishiel.
% She talks to him, telling him it will all be OK. 
% It should be soothing. 
% It is soothing. 
% And nice. 
% He knows this feeling. 
% Everything will be all right. 
% 
% Except it won't. 
% The pain continues. 
% Ishiel is in him, but it doesn't help. 


\Icor{} felt the \Sephirah{} descend upon him, enter his mind and body. 
\Ishiel's virtue was Patience, and she came whispering soothing words of encouragement. 
\hypota{Forget your pain,} she seemed to say. 
\hypota{Endure. 
  Have faith, and you will see a release from pain in the end.
  Time will heal all pain.}

But \Icor{} could not relax. 
\tho{%
  Time is what I don't have, damn you! 
  I am poisoned! 
  I am going to die!
  What good is patience then?} 

% More Archons come. 
% They talk to him. 
% 
% Cushed tells him to fight and live. 
% Icor tries. 
% But it doesn't help.
% He gets frustrated with the Sephiroth. 
% They are not getting him anywhere. 
% It starts to feel bad. 
% Stifling. 
% Suffocating. 
% 
% Clarice calls Omariel and Teshiron. 
% More Iquinian energy. 
% More coaxing and soothing and commanding. 

\Camilienne{} now invoked \ta{\hr{Cushed}{\Cushed}}, the \Sephirah{} of Lawfulness, and \Icor{} felt a new force flow through him. 
\hypota{Obey me,} it commanded. 
\hypota{Forget your doubts. 
  Forget your fears. Forget your thoughts. Obey me.}

In \ps{\Icor}{} state, he felt the \ps{\sephirah} presence as oppressive, suffocating. 
\tho{Don't just tell me what to do! 
  Heal me, damn it!
  Save me! 
  That's what you're here for. 
  That's what you're meant to do!}

He wanted to shout this out loud, but his body did not respond, and the Redcor \soror{} kept trying. 
Through muddy ears he heard \ta{\hr{Omariel}{\Omariel}}, and later \ta{\hr{Teshiron}{\Teshiron}}. 
He felt the \Sephiroth{} envelop him in their promises and admonitions. 

But for all the their assurances, the pain of the poison continued. 
He could not feel his body anymore. 
He had no legs. 
No arms. 
No tail. 
No eyes. 
No ears. 
He felt nothing but the pain, perceived nothing but the whispers of the \Archons. 

% Icor gets more frustrated: 
% \quo{Save me, Sephiroth! That's what you're supposed to do!}
% 
% He gets angry. 
% They are not saving him. 
% They should be. 
% He has prayed to them all his life and obeyed their laws. 
% And they couldn't even save him from a measly poisoned dagger. 
% 
% Crappy Sephiroth. 
% Crappy religion. 

\tho{This is not working.
  I don't feel any better. 
  The \sephiroth{} are not helping. 
  They are not saving me. 
  They should be.} 
\Icor{} felt he had always been a loyal Iquinian. 
Faithfully he had prayed to the Light and the \Sephiroth. 
When in doubt, he had gone to them for guidance. 
Grieving, he had prayed to them for consolation. 
Rejoicing, he had praised them in thanks. 

\tho{And they can't even save me from a measly poisoned dagger. 
  
  Crappy religion.}

Only one thing kept him from total despair. 

\tho{\Tiroco.} 
He could no longer feel her hand on his, but he knew she was there. 
She was with him. 
Crying. 
\tho{\Tiroco. You are real. Your love is real.} 
He thought he heard her sob. 
\tho{Don't leave me, \Tiroco.} 

\tho{I don't want to die.}

The \Sephiroth{} slowly faded, and consciousness with them. 
\Tiroco{} faded. 
Even the pain faded. 

\tho{I don't want to die.}



\begin{comment}
\subsection{Into the Light}
\end{comment}

\new
\ps{\Icor}{} hand in hers, \Tiroco{} waited anxiously while the \soror{} did her work, channelling \Sephirah{} after \Sephirah{}, finally calling upon \Ishiel{} again. But no \Archon{} could dispel her frown, which only deepened. At last she released the \rayuth, shaking her head. 
\end{garbage}








\begin{comment}
\subsection{Icor dies}
\end{comment}
\new
The white-marbled, pillared hall was abuzz with activity as the ball guests poured in. 
Close and distant members of the ruling House Pelidor had come from all corners of the land to the \rayuth's ball, as had numerous nobles from other families under the \rayuth's rule. 

Laughter, smalltalk and jolly music filled the hall. 
\Rayuth[\Icor], the ruler of Pelidor, seemed to be in high spirits. 
His cousin, \rah[Sethgal] Pelidor, found it more difficult to relax. 
The recent news still plagued his thoughts. 
At heart, Sethgal was a \scatha of the battlefield and not of the ballroom, and he was more prone to brooding over matters of war and statecraft than to merriment. 
His attire reflected his demeanour. 
He wore a gilded light cuirass and a purple cape, both sporting the bronze-\coloured \grulcan-bird that was the emblem of Pelidor. 
The left-handed warrior wore a sword on his right hip and a pistol holster on his left; the latter empty, since guns were prohibited in the hall. 

\ta{\Rah[Sethgal],} said a voice. 
It was \rah[\Dornaer] Pelidor, his distant cousin from the city of \Forclin. 
She, too, was dressed in ceremonial half-armour and carried a sword and dagger. 
Her clothes were ultramarine blue, matching the \colour of her scales. 
\talk{What do you think of the news about the Rissitic incursion?}

\talk{I do not know what to think,} said Sethgal. 
They had recently received news that the Rissitic peoples of far southern \Durcac, united under the banner of a sinister warlord, had sailed north to attack cities in the kingdom of \Scyrum, neighbour to Pelidor. 
\talk{At present we know little of the Rissitics' strength. 
  We do not know if this is a border skirmish or an all-out invasion.}

There were more rumours than facts. 
The marauding hordes of \Durcac were often presented in tales as diabolical monsters, and many feared that all \Scyrum might fall. 
\Scyrum and Pelidor were not allies, but if \Scyrum did fall to the advancing Rissitics, it stood to reason that Pelidor might be next. 

\talk{I am not optimistic,} said \Dornaer. 
She fingered her golden hawk necklace, the holy symbol of the \sephirah \Izion. 
\talk{I wonder if our alliance with the Imetrium will be an asset or a liability.} 

A \human slave walked by carrying a tray with glasses of ruby-red wine.
Sethgal took one and sipped from it. 
\talk{Yes, I have wondered the same,} he said. 
The Imetrians were a powerful ally, but the alliance might also incur the Rissitics' wrath. 
\talk{There are Imetric representatives present tonight. 
  \Icor and I intend to speak to them soon and initiate negotiations.}

They were joined now by \rinyuth[\Tiroco], who was \Dornaer's sister and \Icor's wife.
\talk{I'm sorry, \Dornaer and \rah[Sethgal],} she said,
\talk{but I heard you talking about the Rissitics.
  Please tell me something. 
  I know the Rissitics are heathens who do pray to the \sephiroth or the One Light.
  But is it really true that their sorcerers burn people alive in giant ovens to feed their dark gods?}

\talk{I have not seen these ovens, \rinyuth[\Tiroco],} said Sethgal, 
\talk{nor have I heard it from a Rissitic mouth, but I do believe it is true.}

\talk{Allegedly the ovens consume both the body and the soul,} said \Dornaer.
\talk{What is more, the Rissitics consider it an honour to be burnt alive for their wicked gods.}

The horror story made \Tiroco lick her eyes repeatedly. 
\ta{Great Silqua,} she said, shuddering slightly.
\ta{I am glad I am only \rinyuth{} and do not have to deal with all that. 
  Rissitic hordes and their dark sorcery\prikker it sounds frightfully dangerous.}

Sethgal chuckled inside. 
He rather liked \Tiroco. 
She was by no means a warrior, and indeed Sethgal held a rather low opinion of her abilities, but she was a very sweet and good-natured \scatha. 

Now a fanfare rang out from a dozen trumpets, indicating that all the guests had arrived and the ball could begin. 
\Rayuth[\Icor] rose and stepped onto the dais before the throne. 
The ruler of Pelidor was un\armoured and wore instead fine velvet and silk of white and dark blue, offsetting the azure of his scales. 
He reared up, higher than a \scatha's natural, near-horizontal posture, and almost sat back on his tail, so as to be visible above the crowd.
He raised his hands. 
When the chattering fell silent, \Icor spoke: 

\talk{Family, friends, my lords and ladies!
  I thank you all for coming to my ball.
  This is a time for\dash}

\emph{Blam!} came a gunshot from above. 

Immediately shouting and screaming filled the hall. 

\Icor staggered on his dais. 
Blood welled from a wound in the side of his neck. 
He reeled, toppled and fell on his face. 

Sethgal, while scanning for the source of the gunshot, instinctively reached for his pistol. 
His hand found only an empty holster, but his eyes spotted a dark shape slinking out of the shadow of a statue on the balcony above. 

\talk{Up there!} he called, pointing. 
\talk{Behind that statue!
  Soldiers, get him!} 
Sethgal looked around for someone who could help. 
He found Lord Archibald Curwen, the \ishrah mage. 
\talk{Lord Curwen! Do something!}

Curwen was a Vaimon of \ClanTelcra and a member of the \ishrah, the cadre of mages. 
He was a heavily built, aging \human man with close-cut steel-gray hair and beard. 
He nodded briefly with a face that said:
\hypota{Send in the guards. I'll do what I can with my spells.}
Curwen then turned towards the balcony, and Sethgal, trusting in Curwen to know what to do, went to direct his soldiers. 
\talk{You\dash get up there! 
  You\dash guard the stairs! 
  You\dash take care of this crowd!}

Sethgal then turned back to his cousin who lay bleeding on the floor. 
\Tiroco knelt by him, sobbing and calling his name. 
A \human woman in a red dress\dash\ClariceCamilienne, a Vaimon of \ClanRedcor\dash sat on his other side and worked her healing magic on him, invoking the power of the \sephirah \Ishiel.
\Icor did not stir, and while \Camilienne remained stoic, Sethgal guessed from her body language that her spells were having little success. 

\talk{\Icor!} cried \Tiroco.
\talk{\Icor, my love! Don't die! Don't leave me!}

\Icor opened his mouth and spoke some low, garbled words that Sethgal could not hear. 

\talk{No!} said \Tiroco.
\talk{You will be fine.
  The \Soror \Camilienne is here.
  She will save you.
  You will live.
  You have to live!}

\Camilienne called upon other \sephiroth: 
\Zumrad, and \Nomariel, and even \Teshiron. 
All the while the pool of crimson at her feet only grew, and \Icor's movements grew weaker. 
The Redcor \cleric summoned \Ishiel again, but to no avail. 
At length, \Camilienne released the \rayuth and shook her head. 

\ta{What are you doing?} asked \Tiroco, her voice trembling. 
\ta{Surely there is more you can do? 
  More \sephiroth, more prayers\prikker try again!}

\ta{No,} said the \soror.

\ta{What do you mean \quo{no}?} she shrieked. 

\ta{The Light has taken him into its embrace,} said \Camilienne. 

\ta{No! No! He is not dead! He cannot be dead!} 
\Tiroco{} grabbed the Redcor's hands, forced them down to touch \ps{\Icor}{} head. 
\ta{Try again!}

\ta{Release me!} the Redcor commanded with such sternness that \Tiroco involuntarily obeyed. 
\Camilienne{} rose. 
\ta{\Rayuth[\Icor] has gone into the Light. All we can do now is pray for his soul.} 

\Tiroco{} dropped down to embrace the \rayuth's motionless form, sobbing louder now. 
\ta{\Icor{}! Come back to me! \Icor{}!}




\begin{comment}
\subsection{Curwen catches the assassin}
\end{comment}
\new
Archibald Curwen, Vaimon mage of \ClanTelcra and of the Pelidorian \ishrah, was past fifty years of age, but his eyes were still strong enough to catch a glimpse of the assassin on the balcony before he slunk out of sight. 

\thought{\Rayuth[\Icor] shot in broad daylight.
  Damn it.
  Can't I turn my back for a second without having some shit like this happen?}

Now Curwen had to hurry. 

\thought{I can't see you anymore, you little bastard, but I have a good idea of where you are.} 
  
With the ease of decades of practice, Curwen slipped into Vaimon semi-trance and sent his mind wandering into the \empyrean, the mental plane where dwelt the godlike \Archons\dash{}the \sephiroth and \qliphoth\dash from whom the Vaimons derived their arcane power. 
His consciousness floated through dimensions bright and sinister, amid snaking tendrils of spiritual energy. 
Swiftly he crossed the Yawning Abyss and entered the domain of \itzach, the Outer Darkness. 
He envisioned a vast, blackened plain, up from which thrust desolate towers of black stone, wherein dwelt the mighty \qliphoth, the \Archons of the Outer Darkness. 
He sought out the abode of one such \qliphah: 

\tho{\Kithvaz, Breaker of Wills, come forth.
  By the power of the Vaimon pacts I have sworn, by the legacy of \Zether Vaimon, I summon you.
  By the path forged by Cordos Vaimon and walked by Lestor \Delaen, through the gate opened by Holy Silqua, come to me!
  \Qliphah!
  Flow into my mind and body and lend me your strength.
  Breaker of Wills!
  \Kithvaz! Come!}

Immediately he felt the \qliphah's presence like ice in his brain, felt its dark energy like slime upon his skin. 
The power of the Outer Darkness was in him. 

All this had taken place in the span of three or four heartbeats. 

Curwen unleashed the force of \Kithvaz in a blast of spiritual energy towards the area on the balcony above where he had glimpsed the assassin. 
Since he did not know his target's exact location, he had to expend much energy to cover a large enough area, and this took its toll on his body and mind. 
A lance of pain stabbed into his left ribs, where an old war wound had never quite healed, and his stomach almost regurgitated the last mouthful of the burning wine he had swallowed. 
And, as if sensing Curwen's momentary weakness, the insidious voice of \Kithvaz slithered into his head, whispering barely intelligible words of seduction and madness. 

Curwen took this without flinching. 
Such was the price that any mage paid who dealt with the forces of \itzach, for the \qliphoth of the Outer Darkness were cruel allies, not as forgiving and honeyed as their counterparts, the \sephiroth of the One Light. 
Curwen had faced this every day of his life, and worse. 
He was prepared for it and refused to let it stun him for even an instant. 

More importantly, from the feedback he received through \Kithvaz he could tell that his spell had struck home. 
The Breaker of Wills had penetrated the fleeing assassin's mind. 
The \qliphah would stun its victim with pain, dread and confusion, buying Curwen valuable time. 

Quickly he reached out again into the black wasteland of \itzach and summoned another \qliphah:
\OmmonThul, the Cold Lurker. 
As the \qliphah's presence seeped into his mind he felt himself submerged in clammy muck, sucking down his feet, weighing down his limbs and crushing very air from his lungs. 
Curwen projected the \qliphah's numbing embrace away from himself and towards the unknown assassin. 
\OmmonThul's victim would be ensnared in an invisible mire of spiritual slime that rendered him slow and weak. 
Again pain lanced through Curwen's old wound, his blood froze to shards of ice in his veins, and wicked voices \clamoured inside his skull. 
Again he stood his ground. 

\thought{So far so good.
  Now I really need to see what I am doing.}

With the assassin now hopefully slowed down, Curwen had time to perform a more time-consuming invocation and summon the \qliphah \Dweryog. 
This \qliphah helped him expand his senses into the Realms Beyond so that he could, among other things, sense things though solid stone walls. 
Now at last he was able to discern the form of his quarry. 
It was a \scatha, awkwardly limping away. 

\thought{Hah. I got him.}
But to be on the safe side, Curwen called on \Kithvaz again and struck the assassin with a focused lash of pain and dread. 
With the sight provided by \Dweryog Curwen could see his victim convulse and stumble as the spell washed over him. 

\thought{This one has a weak mind,} Curwen could tell.
Spells such as these were hard to use against another mage or a powerful warrior, who would often possess enough willpower to resist or at least cope with the effect. 
This one was weak-willed\prikker or under the influence of something. 

Curwen looked around and saw frightened people milling about in confusion. 
Several soldiers had made it up the stairs and were running towards the assassin's position.
\thought{Good. They should be able to hold him, at least until I can get up there.}

Curwen drew his sword, which had the useful side-effect of making the crowd more willing to part around him.
He made for the stairs, roughly elbowing aside anyone who got in his way. 
Meanwhile, now that he finally had some moments to think, his mind was racing.

\thought{%
  What is going on here?
  Who is this guy?
  Why did he shoot \Icor?
  Who wants \Icor dead?
  It cannot be anyone in the Cabal.
  Or so I hope.
  Because if the Cabal wanted \Icor dead, I should know about it.
  No, it can't be one of ours.
  Who then?
  Sentinels?
  Rissitics?
  
  No. 
  Focus, Archibald, focus!
  Speculate later.
  First deal with this guy.}

When Curwen reached the balcony he was gasping for air. 
Running upstairs was painfully exhausting for a man of his age and girth, and he had already exterted himself with his spells. 
He arrived to see a half dozen soldiers surrounding a tailed figure in a grayish cloak and cowl.
The cloaked assassin fired a shot\dash evidently he had a spare gun\dash but in his dazed state he failed to hit anything. 
He discarded the pistol and drew a short sword. 
The soldiers pointed their own guns at him. 

\talk{Don't shoot, you lackwits! Take him alive!} shouted Curwen. 

With a manic look in his eyes the assassin jumped to his feet and charged, hissing and yelling all the while. 
He slashed wildly with his sword as the soldiers moved in to stop him. 
The soldiers fought back and gave him several shallow cuts, but he fought on with undiminished frenzy. 

\talk{Take him alive! We need him!} Curwed yelled. 

\thought{Fuck. 
  What's going on with this guy?
  How can he still be fighting like that?
  Is he on drugs?
  I've got to cast a spell and disable him.}

Curwen reached into the \empyrean again. 
Before his mind's eye he saw once more the Abyss, and beyond it the benighted, forbidding towers of the \qliphoth. 

Then it was as if a spiritual gust of wind seized hold of him. 

He lost sight of \itzach. 

He was falling into the Abyss, drawn down into its Stygian depths. 

All was pitch black. 

\thought{No!}

Curwen concentrated and pulled back. 
The blackness dissipated. 
His vision returned. 
He could see the white marble walls and pillars again. 

Winded and stressed, he had faltered for a moment, and faced with the unnatural horror of \itzach the fear within his own mind had taken hold of him. 
In more extreme cases, such slip-ups could kill a Vaimon, and even\dash some said\dash make him lose his immortal soul, consumed by the Nameless \Qliphoth that dwelt in the Yawning Abyss. 
As it was, it had been easy enough for Curwen to snap out of it, but he did black out for several moments, and when he regained control of himself, the damage was done. 

The assassin lay dying, bleeding from a score of cuts and stab wounds. 

\talk{Fools! I said take him alive!}
Curwen rushed forward, shoved the soldiers out of the way and grabbed the fallen assassin by the neck. 
It was a young \dax\dash a male \scatha\dash with drab, grayish-blue scales. 

\talk{I am a Vaimon,} said Curwen.
\talk{Tell me who hired you and I may save your life.}
This was a lie. 
Curwen was a poor healer and did not believe he had any chance of saving the \scatha, but he thought the bluff worth a try.
But the young \dax was in too great pain to speak. 
He whimpered once, coughed, and died. 

\thought{Fuck,} thought Curwen. 
Then he said it aloud: 
\talk{Fuck!}

He bent to examine the dead assasin. 
\thought{This place is supposed to be guarded.
  How could the bastard just sneak in and shoot the \rayuth?
  The people in charge should be too smart for that.
  \emph{I} should be too smart for that.}
  
He looked closer and noticed a strange effect of the \scatha's gray cloak. 
It was oddly glossy. 
It shimmered and reflected light. 
Curwen reached out with his mystic senses and examined the cloak. 
Now in his mind he could feel the presence of \daemonic essence in the fabric, like black and putrid slime. 
\thought{\Daemons.
  This cloak has been enchanted, and by a \rethyax mage.}

On the spot Curwen could not possibly interpret the spells woven into the cloth, but he guessed it was designed to somehow divert the eyes of onlookers and hide the wearer from view. 
\thought{I wish I had such a cloak myself. 
  Too bad it's been slashed like this.
  Where did the bastard get this? 
  Who made it?
  Wait\prikker I know! 
  \Onatol!}

\Ambrose \Onatol was another mage of the Pelidorian \ishrah; a \rethyax who worshipped the old \Ortaican gods and drew his power from the \daemons of the Realm of Chaos. 
Curwen could remember having heard hints that \Onatol had been working on spells to make a man invisible. 
And now that he thought about it, he was fairly sure \Onatol had \emph{not} been present at the ball, even though the whole \ishrah had been invited. 

\thought{Interesting.
  But who is this \dax?
  Whom is he working for?}

In the meantime more soldiers had arrived. 
\talk{Men!} said Curwen to them.
\talk{Who is this \dax? 
  Look at his face.
  Someone tell me who he is!}

\talk{Lord Curwen,} said a soldier, a young \sphyle\dash a female \scatha.
\talk{I've seen him before.
  That's\prikker I don't know his name, but he's a servant.
  He worked for that mage.
  The \rethyax\prikker \Onatol.}

\thought{I see. 
  We have a conspiracy on our hands.
  I'll have to catch \Onatol.}

Curwen rose and went downstairs to the dais before the throne. 
As he expected, \rah[Sethgal] had assumed command and was working to restore order. 
\Rinyuth[\Tiroco] lay sobbing over the body of \rayuth[\Icor], who now looked quite dead. 

\thought{Shit.
  Dead \rayuth.
  That's going to mean an interregnum while the nobles elect a new one.
  Interregna are rarely easy.
  And I'm sure we haven't seen the worst of it yet.
  Whoever ordered \Icor killed must be up to something more.
  I see difficult times ahead for Pelidor.}

The red-clad \soror, \Camilienne, stood nearby. 
Resentment glowed on her face as Curwen approached. 
She always disapproved of him, of course, and even more so now that the stench of \itzach was upon him, a reminder of what he was. 
\Camilienne was of \ClanRedcor, and according to the Redcor religion the \qliphoth were creatures of pure evil, and to invoke them was the blackest of sins. 
Curwen had no time for such childish morality. 
He knew that the the world was a vaster and darker place than the Redcor's narrow world-view allowed them to admit. 

\talk{\Rah[Sethgal],} said Curwen, acknowledging the \scatha's rank with a nod. 

\talk{Lord Curwen,} said Sethgal. 
\talk{What happened?}

Curwen summarized the capture of the assassin and the evidence implicating \Onatol. 
\talk{So, you see, I want to go after \Onatol immediately.
  If he has not already fled, he must be on his way out, so there's no time to waste.}

\talk{Very well, Lord Curwen,} said Sethgal. 
\talk{Go. Use whatever force is necessary.}

\begin{garbage}
Curwen tells Sethgal he suspects \Onatol and wants permission to go after him right now.
Sethgal says go. 
Curwen walks off, hoping that \Onatol is in his room. 

Maybe Curwen takes another mage with him into \Onatol's room. 
Maybe even \Cobrel. 

\Onatol is likewise under mind control magic. 
The spell does not control \Onatol's entire mind, it just makes him slightly crazy and aggressive, so that he fights and gets himself killed when the soldiers come to arrest him. 
At the end of the book, make sure to reveal that \Onatol was an innocent guy, framed as a part of a circuitous \trope{XanatosRoulette}{Xanatos Roulette} with the purpose of leaking Tantor's diary to Charcoal and making him think he had discovered a vital clue. 

\Onatol{} has books and scrolls lying around. 
And a star-map on the wall (annotated with plenty of occult data useful in calculating and interpreting the \matrices). 
And some sigils representing various \sephiroth{} and \qliphoth. 
And some herbs and drugs and incences used for meditation. 

Remember the \hr{Itzach pain}{pain of \itzach} when Curwen casts magic. 

Have plenty of \hr{Demihuman}{\demihuman} slaves in Pelidor and stuff. 
Read about \hr{Demihuman}{\demihumans}.

After \Onatol dies, have a scene where \LocarPsyrex contacts his local agent. 
The agent tells \Psyrex that everything went well. 
The agent then slinks away.
The agent is one of the sorcerers who will later be responsible for raising \Nithdornazsh.
\end{garbage}





\begin{comment}
\subsection{Charcoal}
\end{comment}
\begin{garbage}
\new
Charcoal was making advances to a very pretty maiden, whose name he had forgotten, when he heard the cry. 

\ta{Aaaaaaa! The \rayuth! \Rayuth[\Icor] has been attacked!} 

\tho{What the fuck?} was his first thought.

\ta{Oh, dear Light, what is that?} the girl began, but she was already forgotten, Charcoal running toward the \rinyuth' voice. 

Navigating through the crowd of panicking dancers was proving painfully slow and difficult. 
\tho{Not acceptable.} 
Invoking a \Qliphah{} or two, he felt his twilight shape grow, becoming more commanding, more menacing. 
The mindless crowd could not \emph{see} his twilight body, of course, but their animal minds perceived it, and they instinctively gave way, fleeing from his path. 
%shied away from him, opening a path through the mass of people. 

\tho{\Machai,} he cursed under his breath. \tho{Why does this shit always happen? Can't I turn my back for a second?} 

He heard the \rinyuth shout again. 
\ta{Sieze her! The woman in yellow, get her! She is the assassin!} 
\tho{Assassin? Fuck!} 

Finally pushing to the fore of the crowd, he saw the \rayuth on the floor, a dagger jutting out of his belly. 
\Risvet{} Hemfork was by his side and his wife was rushing for him. 
\tho{How did this happen?} 
His mind raced. 
%\tho{The tacupien is a close dance, but not close enough that you can just stick a dagger in your partner or neighbour unnoticed. No regular assassin could do that. Magic?} 
\tho{Hm. The tacupien is a close dance. Close enough that you can knife neighbour just like that? Perhaps. Unnoticed? Perhaps not.} 

\tho{Magic?}

Concentrating, Charcoal expanded his senses into the Realms Beyond. \tho{Let us see\prikker} His mind scanned the dimensions, until he discerned a faint smell. The lingering scent of sorcery. 
\ta{%
  Aha. Weaving spell. Chaotic in aspect. Someone has been tampering with the Shroud here, and it's not me.} 

%He focused his senses on the scent, but it was no use. It had already faded to almost nothing. \tho{Damn. I lost it.} 

He focused his senses on the scent, trying to track it back to the source. The trail led to his right. Craning his neck, he espied the originator, standing near the edge of the dance floor in a white-and-silver robe that accentuated the ultramarine of her scales. 

\tho{Crap. Just \Cornel{} and her illusion.} The archmage Moro \Cornel{} was an old \sphyle{}, her body gradually failing under the ravages of time. A fact which she, in her vanity, dilligently concealed under layered illusions, masquerading as a healthy \sphyle{} in her prime. 
\tho{Damn her and her filthy \hr{Rethyax}{\rethyactic} magic.} 

Charcoal sniffed the Realms again, but he could detect no magic save \ps{\Cornel}{} and his own. 
\tho{Fuck you, \Cornel. This brings me no further.} Again his mind spun. \tho{%
  What to make of this? Three possibilities. One: \Cornel{} is involved. Two: \Cornel is not involved, but her damned spell overshadows the assassin's magic. Three: \Cornel is not involved, and the assassin used no magic.} 

A high squeal snapped him out of his trance.
%Snapping out of the trance, he heard a squeal. 
To his left he saw a young woman in a yellow dress squirming in the grip of a pair of armed guards. 
\tho{%
  What is\prikker oh, right. \quo{The woman in yellow}. The assassin. Supposedly.} 
He studied her. 
\tho{She doesn't look dangerous.} 
He almost laughed. 
\tho{Which makes her doubly suspicious, of course.} 

He turned his attention once more on the fallen \rayuth, focusing his supernatural senses on him. 
\tho{%
  The wound's not terribly deep. 
  Nor terribly precise, if I am any judge\prikker which I am. 
  Probably poisoned. Assuming that magic was used, an attacker who has the resources to use magic sure as fuck ought to have the resources and the foresight to use poison.} 
He suppressed a grin. 
\tho{That's what I would do.} 

Entering the scene from his right was the Redcor emissary. 
\tho{What's her name? \Clarice{} something.} 
She knelt down with that characteristic Redcor grace that somehow made it look as though she was seated on a throne, not on the floor. Charcoal giggled inside. 
\tho{%
  One thing I have to give the Redcor. They master the art of keeping up appearances.}

As \Clarice{} called upon \iquin{} and channeled her \Sephiroth{} into the \rayuth's body, a thought occurred to him. 
\tho{Could it be the work of one of our own?} 
He glanced at the yellow-clad girl. 
\tho{%
  Is she one of us? She could be. But then I should know about it. 
  Unless\prikker unless it comes from the top.} 
He did not quite manage to suppress a pursing of his lips. 
\tho{%
  No, that can't be. 
  \Rayuth[\Icor] isn't so big a fish. 
  No, anything that goes on in Malcur goes through me. 
  Ergo, not Cabal. Then what?} 
He smiled inside. 
\tho{I will have to have a\prikker chat\prikker with that girl.}

He turned his attention back on the Redcor, who was reaching inside the wounded \rayuth with every \Sephirah{} she could think of. 
\tho{%
  She is not cheating, as far as I can see. Supporting the theory that\prikker}
%\prikker The Redcor is not cheating\prikker 

\ta{What do you mean \quo{no}?} demanded the \rinyuth in a hysterical voice. 

\ta{The Light has taken him into its embrace,} 
said the \soror{}. 
Charcoal might have laughed at the religious implications of that, if not for the import of the concrete message. 

\tho{%
  No more \rayuth? Fuck. This is bad. I don't know who's behind this, but it's not me. Which means it's bad. Who would want the \rayuth dead? Well, plenty of people.
  But who did it?
  Was magic involved or not?} 
He almost cursed aloud. 
\tho{%
  Eat shit and die, \Cornel! If not for you and your bloody vanity it would be easier to figure out. Now I don't know what's going on, and it bothers the shit out of me.}
%Charcoal preferred stupid people who were easily manipulated. Mindless commoners who could be made to believe anything with just a tiny flick of magic. Anyone who was as smart as he, or close to it, was a threat. 

He glanced back at the apprehended suspect. 
\tho{%
  I will definitely need to have a chat with that girl. 
  
  She is pretty\prikker}














\begin{comment}
\subsection{Archibald Curwen}
\end{comment}

%\section{\Ambrose{} \Onatol}
%\dateplace{Runger war}{22nd}{\Atzirah}{Throne room, ducal palace}
\stamp
  {\dateCurwenKillsOnatol}
  {Throne room, ducal palace, Malcur}
%
% \Tiroco{} is in the throne room together with:
% Roric, her eldest son and the new \rayuth, a boy of six.
% Frico, her daughter, a girl of three - or maybe she's not present. 
% \Dornaer{}, \ps{\Icor}{} brother and a supporter of \Tiroco{}. 
% Liocai, \ps{\Icor}{} sister, who's never liked \Tiroco{}.
% \Sethgal{}, a warrior who will be appointed the new Marshal of Pelidor. 
% Zacophine Vincerre, a Redcor \mater{} and emissary. 
% Clarice Camilienne, a Redcor \soror{} and emissary. 
% Iasper Bartholin, a royal administrator of sorts. For now let's give him the title of `\minister'. 
% William Norden, a Belkadian Vicar
% Moro \Cornel{}, archmage to the \rayuth. 
%
% Roric is made the new \rayuth. He's scared and insecure, while people are telling him to be brave. 
% Liocai is \skeptical of \Tiroco{}. She wants someone else put in charge. But \Dornaer{} says that there is nothing to discuss: The law states that if the \rayuth is under the age of sixteen, his closest adult relative must rule as regent. In this case \Tiroco{}. 
% Bartholin can tell them that the law does indeed support \Tiroco{}. 
% The Redcor are silent for a long while - communicating amongst themselves silently - but eventually support \Tiroco{}. 
% Liocai storms out. 
% \Sethgal{} is silent, voicing no opinion. 
% After a while, it's decided that \Tiroco{} is now regent of Pelidor. 
% \Icor{} was previously not only \rayuth but also marshal, supreme leader of the Pelidorian armies. Traditionally this office is held by the ruler, but \Tiroco{} is not a trained soldier. \Dornaer{} is considered, but ultimately \Sethgal{} is chosen. He is a great warrior and was a close friend of \rayuth \Icor{}. 
% Then Curwen comes in. 
\begin{comment}
\ta{You must be strong, Roric,} Liocai was saying. \ta{You are the \rayuth now. You must make your father proud. Do you understand?}

Roric nodded feebly. Sitting in the high seat with the heavy, golden ducal emblem around his neck, the six-year-old boy looked anything but brave. Closer to terrified. \Tiroco{} reached down to hold his hand. 

\ta{Don't pamper him!} Liocai snapped. \ta{He needs to grow up.}

\Tiroco{} suppressed a jump and almost retracted her hand, but stopped herself. \ps{\Icor}{} sister had always intimidated her, but with effort she managed to meet her gaze. \tho{It's not only Roric who must be strong. So must I. Even more so. Now that \Icor{} is gone.} 

She was about to speak when Liocai cut her off.

\ta{Which brings us to the next item of discussion. Who will rule Pelidor until Roric comes of age?}

\tho{Be strong, \Tiroco. Make \Icor{} proud.} \ta{I will.} 

Liocai snorted. \ta{I am sure you would, but I believe that someone\prikker}

\tho{Be strong, \Tiroco.} \ta{This is not an item of discussion,} \Tiroco{} cut in. \ta{The law is perfectly clear. If she sitting \rayuth is not of age, his closest relative will reign as regent. I am his mother. I will rule in my son's stead.} 

Liocai made to protest, but she was getting flustered. \Tiroco{} was emboldened. \ta{\Mr{} Bartholin, what does the law say?} 

\ta{My lady \rinyuth is correct,} said the old \dax{} in his slow voice. \Minister{} Iasper Bartholin was the court's chief administrator, responsible for managing mundane matters too minor to warrant the \rayuth's personal involvement. \ta{If a \rayuth is appointed below the age of sixteen, then a regent must reign in his stead until he can step into rule proper on his sixteenth birthday. The regent chosen must be the \rayuth's closest adult relative, if such exists. Closest of all are considered the \rayuth's father and mother. If none are to be found, the second-closest group are grandparents. After grandparents are considered the siblings of the \rayuth's parents\prikker}

\ta{Thank you, \Mr{} Bartholin,} \Tiroco{} broke in. 

But Liocai was not done. \ta{Laws can be changed. That is the privilege of rulers. It is what separates us from commoners\prikker}

\ta{Nonsense,} said \Dornaer{}, the younger brother of \Icor{} and Liocai. He moved closer to \Tiroco. \ta{I support you, \Tiroco.} 

\prikker
\end{comment}
A knock on the door. 

\ta{What?} snapped the \rinyuth. 

\ta{Mage-captain Curwen requests an audience, \rinyuth,} a servant announced. 
\ta{He says he brings news from the interrogation of the prisoner.} 

\ta{Send him in.}

% Curwen enters. He informs the \rinyuth that they have interrogated the prisoner. Her name is \Constance{} of \Kintaer{}. After some questioning - Curwen does not elaborate, but the word `torture' hangs in the air - she confessed to knifing the \rayuth. Apparently she was bought by Morgan, the king of Runger. She does not know much, only that she was to kill the \rayuth, and that she would be rewarded greatly. She speaks of marrying Matthias, Morgan's son, but it is unclear whether she was actually promised this. At any rate, she's been to Runger and seems to be in love with Prince Matthias. What's more interesting, she names an accomplice: A noble Pelidorian mage, whose name is \Onatol{} or something like that. 

The herald retreated, bowing. The door swung open to admit Captain Archibald Curwen, the commander of the Pelidorian \hr{Ishrah}{\ishrah}\dash the coven of mages\dash and who, when present, also acted as a ducal interrogator. 
He was an aging man, steel-gray hair and beard cut short. Tall and massive, he made and impressive figure in his blue-and-silver coat and long cape as he strode forward. 
He carried a sword and a pistol in his belt, but \Tiroco{} doubted that the mage would need either if forced to defend himself. 

Reaching the edge of the table, he bowed. 
\ta{\Rinyuth[\Tiroco].} 
He acknowledged the rest of the assembly with nods. 
\ta{Ladies. Gentlemen.} 
Turning back to the \rinyuth, he continued. 
\ta{%
  I have interrogated the prisoner, and I have news I you will want to know.}

%\ta{Who is the prisoner?} \Dornaer{} broke in.

%Curwen spared him a glance. \ta{She is \Constance{} of \Kintaer{}.} 

The prisoner, they all knew by now, had in the meantime been identified as \Constance{} \Kintaer{}, daughter of Earl \Theal{} \Kintaer{}. Her family had vehemently objected to her imprisonment and had been clamouring all night and morning to have her released. 

\ta{After some questioning}\dash Curwen's tone when he said \quo{questioning} left the word \quo{torture} hanging in the air\dash\ta{\Constance{} confessed her crime.} 

\ta{That bitch!} \Dornaer{} exclaimed. 

%\ta{Confessed,} asked \Vincerre, \ta{as in \quo{willing to confess anything}, or reliably?}
\ta{Confessed,} asked \Vincerre, 
\ta{as in \quo{willing to confess anything}?}

\ta{Reliably. I have every reason to assume that she speaks the truth.} 
Curwen maintained his characteristic sarcastic half-smile as he faced her, and his tone betrayed an annoyance well above his station, taking into account \ps{\Vincerre} status as a Redcor emissary. 

\ta{Moreover,} Curwen continued, forestalling further interruption, 
\ta{we discovered her motives. 
  \Constance{} was in the employ of King Morgan Runger.} 

This brought several gasps and much muttering from the assembled. 

\ta{Runger, that foul rat,} came \Dornaer{} again, and \Tiroco{} could only agree. She had met King Morgan only once or twice, but she had found him an altogether disagreeable sort. That he would order such a vile murder hardly surprised her. 

\ta{Captain Curwen,} asked \Vincerre, her voice not loud but firm enough to squelch the muttering. 
\ta{You say \quo{in his employ}. 
  How so? What did young \Constance{} hope to gain?}

%\ta{Moreover,} said Curwen in a voice loud enough to squelch the muttering, \ta{we}

\ta{A valid question,} said Curwen, acknowledging the \mater{} with a nod that was almost condescending. 
\ta{Our dear \ps{\Constance}{} explanation becomes somewhat less clear here}%
\dash%
\Tiroco{} repressed a shudder at the gleam in Curwen's eye when he said \quo{dear \Constance}, and she did not want to know what had transpired in the dungeon%
\dash%
\ta{but she spoke of marrying Prince Zacrias.} 
Zacrias was the younger of Morgan's two sons. A very handsome \human, or so \Tiroco{} was told. 
\ta{%
  I gather that our girl had fallen in love with the handsome prince and been led to believe that he would marry her if she succeeded in assassinating the \rayuth.}

%\ta{\quo{Led to believe}?} inquired Bartholin. 

\ta{So,} interjected the Viscountess Osphal Turmalin, 
\ta{her crime was committed for love. How romantic.} 
\Tiroco{} shot her a glare, but the Viscountess' expression remained as flat and unreadable as hertone of voice had been.

\ta{Interesting, yes,} said Curwen, almost overbearingly. 
\ta{%
  But what is more important is that little \Constance{} named an accomplice. Here in Malcur.}

Dramatic pause. 

More muttering, louder this time. 

\ta{Be silent, all of you!} \Tiroco{} had to shout to cut through the chatter. 
\ta{Continue, captain.} 
With effort, she ignored the glares that answered her command. 

Curwen gave a slight bow before continuing. 
\ta{According to our girl,}%
\dash again \Tiroco{} had to keep from shuddering\dash%
\ta{she received her instructions from \Ambrose{} \Onatol{}.}

\ta{\Onatol?} Moro \Cornel{} burst out. 
\ta{\Ambrose{} \Onatol{} a traitor? I can't believe it\prikker} 

\Onatol{} was a member of the mage \ishrah{}\dash a \rethyax, practitioner of the \Ortaican{} tradition of magic. 
He was a respected scholar, even though the church frowned upon the Chaos magic he practiced. 
He had always struck \Tiroco{} as a eccentric but harmless old \dax, mostly absorbed in his scientific pursuits. 
Whatever those might be. 
\Tiroco{} knew nothing of the art of magic. 

\ta{Why would he do that?} asked \Tiroco. 

\ta{I don't know, my lady \rinyuth,} said Curwen, 
\ta{%
  but with your permission, I would like to take \Onatol{} into immediate custody.}

\ta{Permission granted, captain. You may go.} 

Curwen gave her another bow, then turned and strode from the chamber. 
% A thought occurred to \Tiroco. 
% \tho{%
%   Curwen is contemptuous of almost everyone. Why is he polite to me? Is he really mocking me, and I am just too stupid to see it?}

\ta{Well, I daresay this changes things,} said Turmalin. 

\ta{It changes little until we know more,} \Mater{} \Vincerre{} countered. 
\ta{A confession under torture is little more than an accusation.} 
\Tiroco{} noticed several noses wrinking, several faces averted, at this first open mention of the ugly word \quo{torture}. 

\ta{I would have thought,} said Turmalin, 
\ta{that you would be among the first to condemn the sorcerer.}

\ta{Yes, I suppose you would.} The \ps{\mater} expression was blank, and all the more condescending for that. Turmalin answered with a scowl. 

For a moment no one spoke. 
\tho{The Redcor often have that effect,} \Tiroco{} mused. 

Bartholin cleared his throat. 
\ta{What do we do about \Miss{} \Constance?} 

Sudden anger welled in \Tiroco. 
\ta{Kill her.} 
As she thought of her husband's murderess, images returned to her. 
\tho{\Icor. 
  His face. His smile. His touch. Our lovemaking. All stolen from me.} 

\ta{I do not belive that that is your decision,} said Liocai. 
\ta{If I may remind you, you are not yet regent.}

\ta{%
  No new \rayuth has been crowned, so I am still \rinyuth, and in \ps{\Icor}{} absence I speak for him. Am I not right, \Mr{} Bartholin?}

\ta{%
  Um\prikker yes. The law states that if the \rayuth is absent or incapacitated, or\prikker}

\ta{Thank you, \minister. So.} There was hate in \ps{\Tiroco}{} voice now. \ta{The bitch dies.} \tho{\ps{\Icor}{} blood seeping out on the floor. The fear and pain in his eyes.} \ta{I want her to hang!}

\ta{But my lady \rinyuth,} the \hr{Frater}{\Frater} Norden began. 
\ta{%
  \Miss{} \Constance{} is noble-born. You cannot hang her. It would be a breach of all propriety. She must be accorded the honour of beheading\prikker}

\ta{Shut up!} 
At another time, \Tiroco{} might have been shocked or amused at this obsession with the manner of death, combined with a disregard for life and death itself, but in this moment she could think only of her \Icor{} and the woman that had robbed her of him. 
\tho{His glazed eyes. His body growing cold in my arms.} 
\ta{Shut up, all of you! She hangs!} 

\tho{I want her to die. A poor payment for my \Icor.}

\tho{\Icor\prikker}

% Tiroco sentences \Constance{} to death by hanging. (This is later mitigated to death by beheading, since she is, after all, noble-born.)

% After that, Charcoal walks away musing. (Charcoal is Curwen, of course, but that is not to be stated yet.) It's made known that he was present during the interrogation and took pleasure in raping the girl. 
% Her naming \Onatol{} came as a surprise to Charcoal. He doesn't entirely belive it. He suspects something strange is going on, but he acknowledges the possibility that \Onatol{} is a Sentinel. 
% In the end, Charcoal sneaks back to \ps{\Constance}{} cell. She is to die, after all, but she is cute, so he wants to rape her some more first. 
 
\end{garbage}








\begin{comment}
\subsection{\Ambrose{} \Onatol{}}
\end{comment}

\placestamp{\Ishrah{} Tower, Malcur}
%
\ta{You go in first,} Curwen instructed. 
\ta{And remember, we want him alive if at all possible.}

\ta{Yes, sir,} the lead guard replied. 
All four soldiers\dash \scathae{} all\dash saluted. 

\ta{Now!} said Curwen. 

The two soldiers in front threw themselves against the door to \Ambrose \Onatol's chambers, flung it open and stormed in. 

\ta{Light! What is this?} came a startled \scathaese voice from within.

The second pair of guards pushed their way inside, and Curwen moved to the doorframe. 
\ta{%
  \Ambrose{} \Onatol, I place you under arrest! 
  Do not resist!}

As Curwen had expected, \Onatol was seated at his table, surrounded by books, scrolls, herbs and occult star-maps. 
He was an old \dax{}, many of his sky blue scales dis\coloured and loose, and wore a plain brown robe. 
\ta{Wha\prikker Curwen? What is going on here?} 

\ta{I am taking you into custody, \Onatol. Do not resist.} 

As the guards moved in to grab the old mage, a strange look came over \Onatol. 
He rose, his eyes gleaming with some madness, and his voice was strained and rasping as he spoke. 
\ta{You will never take me alive!} 

\thought{Fuck,} thought Curwen.
\thought{Not good.
  That looks like the same kind of frenzy I saw before with the henchman.}

The guards moved closer, swords drawn.

\ta{\kingst{Zegaled \Daxian! Zegaled Shellagh!}} shouted \Onatol, calling upon the \Ortaican{} gods. 
\ta{\kingst{Vez'pherikh nakkruss ashfalech!}} 
His voice became deep and menacing, even unnatural, as he chanted the spellwords in the \Draconic{} tongue. 

The soldiers understood only that he was using \quo{black magic}, nothing more, but Curwen could see the \chaotic{} power surging through \ps{\Onatol}{} body, could discern the hazy forms of mindless \hr{Daemon}{\daemons} that came forth from the depths of Chaos to heed the sorcerer's command.  
He could hear their wordless whisperings, smell the sulphurous scent of their unearthly bodies. 
They were like clouds of dark smoke, vaguely like flying beasts with long tails, talons and what might be eyes, gleaming with inhuman viciousness. 

The Chaos mage gestured at the nearest guard, and Curwen saw ravenous \daemons{} close on the soldier, circle about him. Encountering a magical ward, which Curwen had cast on each soldier prior to storming the room, the \daemons{} hesitated a moment. 

Around the ward they circled, like sharks, faster and faster. 

To Curwen they seemed to scream with some infernal glee. 

They attacked. 

%The ward cracked, the sound audible to Curwen's trained ear as it shattered like glass. 
%The ward cracked, shattering like glass with a sound audible to Curwen's trained ear. 
The ward cracked. 
The sound was audible to Curwen's trained ear; like glass shattering. 

All this happened within a heartbeat. 

The soldier's face became contorted in pain. 
He tried to scream, but only a choked gasp came out. 
Veins ruptured in a dozen places all over his body. 
Scales cracked and popped loose. 
Blood sprayed in every direction. 
The young \dax{} fell to the floor, feebly trying to cover his wounds with his hands. 

\tho{Shit,} thought Curwen. 
\tho{%
  I'd hoped that with the wards the boys would last a bit longer than this.} 

The other soldiers made to back away in revulsion. 
\ta{Get him, damn you! Knock him down!} 
Curwen's authority overcame their horror, and they advanced again, but their hesitation\dash and Curwen's poor preparation\dash had gifted \Onatol{} with more time. 

\ta{\kingst{Vez'pherikh nakkruss ashfalech!}} \Onatol{} repeated the spell, pointing at the next guard. 
Curwen saw ghostly \daemons{} force their way into the world, saw them close on the hapless soldier. 
The ward burst, and so did the \ps{\sphyle} body, collapsing in a mess of blood and torn flesh. 

% \Kithvaz, a Qliphah.
But now Curwen was ready. 
\tho{%
  I'll get you down. 
  Your magic may be nasty, but it's slow.
  In a close fight like this, a \rethyax{} is no match for a Vaimon.}
\ta{\hr{Kithvaz}{\Kithvaz}!} he invoked out loud, sending the \Qliphah{} to strike at \ps{\Onatol}{} mind, hoping to knock him unconscious without too much brain damage. 
After all, they needed to know what he knew. 

%Immediately the soldier doubled over and fell to the floor. 
%He tried to scream, but managed little more than a choked gasp

With his mind's eye Curwen saw the \Qliphah{} penetrate the sorcerer's mind. 
But then \Onatol{} cast his head back and screamed. 
A terrible cry, replete with \chaotic{} power. 
And the \Qliphah{} shrivelled, dispersed, its manifestation dispelled. 

The Chaos mage fixed Curwen with eyes full of madness. 
\tho{A madness born of Chaos.} 
Curwen could see the \daemons{} behind those eyes, swarming in \ps{\Onatol}{} mind. 

\ta{You will not take me!} \Onatol hissed. 
Curwen saw the sorcerer's thoughts reach out, like tendrils stretching off into the vastness of the Realms, as \Onatol{} drew in the power of Chaos, silently calling the \daemons{} to attend to him as he opened his mouth to intone a spell. 

That malefic gaze would leave a lesser man frozen in place with fear. 
But Curwen was no stranger to Chaos, and with \ps{\Onatol}{} attention fixed on him he was quick to react. 
\ta{Kill him!} he shouted to the guards. 
\ta{Gut the fuck! Gut him!} 

A sudden glimmer of doubt flickered in \ps{\Onatol}{} mad eyes, and he began to turn his head. 

Then he grunted as the tip of a sword burst out through his belly. 

Too late he realized that the two surviving soldiers had reached him. 

Another sword broke through his scales and pierced his chest. 

But \Onatol kept his hideously gleaming eyes focused on Curwen. 
Impaled on two swords, he still found the strength to speak:
\talk{\kingst{Zegaled \Daxian\prikker}}

Curwen did not let him finish. 
\ta{\Bozchul!} he invoked. 
\Bozchul was one of the most insidious of the \qliphoth, belonging to the dreaded Circle of Midnight, and Curwen had to draw deep of the energy of \nieur{} to summon it. 
Now it wheeled forth from his hand to grab the old \scatha. 
Penetrating \Onatol{} as if with a myriad tentacles, it wormed into the core of his body to feed on his very life force. 
In a better condition the Chaos mage might have fended off the \Qliphah, but wounded as he was, he could only rattle as the terrible \Archon{} snuffed out his life. 
His body dried and shrivelled, as if aged many decades in a matter of seconds. 

The dark energy unleashed was of such magnitude that it broke through the Shroud, manifesting itself in the physical world as a smoke-like, foul-smelling substance seeping from \Onatol's body. 
The two guards, having learned to dread the old \ps{\dax} sorcery, recoiled from the cloud, one even leaving his weapon stuck in the mummy-like body. 

% that brought snuffed out life itself 
\ta{Don't run,} Curwen ordered. 
\ta{%
  This last magic was mine. 
  It's over. 
  He's dead.} 

\tho{Fuck,} he thought to himself. 
\tho{%
  Old \Onatol{} was learned, I knew that, but I didn't expect him to be able to handle himself in combat like he did. 
  Looks like the fucker cheated me all this time.} 
Curwen had hoped to take \Onatol alive, but the \rethyax proved more dangerous than he had hoped, and in the end Curwen had decided he could take no more chances and had to kill \Onatol before things got out of control. 

\tho{Two suspects killed resisting arrest.
  And I have no clues.
  What is going on here?}

He wheeled around and singled out one of the guards. 
\ta{You!} The \sphyle{} jumped. 
\ta{%
  Go call some servants to clean up the mess and start collecting evidence.} 
The \sphyle{} saluted, then strode\dash almost ran\dash from the chamber. 

\tho{%
  Damn you to \nieur, \Onatol, for dying and taking your secrets with you. 
  What were you hiding, old bastard?}

He began looking through \Onatol's stuff. 
One item looked particularly interesting. 
It was a brown book, fairly new, in between whose pages had been thrust a stack of letters. 
He flipped a few pages and found the book to be a diary or journal. 
What he saw made him quickly grab the book and letters and tuck them away under his coat. 

\tho{Interesting stuff. Very interesting.} 
From his many years in the Cabal, Curwen had developed an intuition for such things. 
\tho{I will need to study these when I have the time.
  And I don't think I will be showing this to the Pelidors.
  Not yet.} 





\begin{comment}
\subsection{The dungeon}
\end{comment}
\begin{garbage}

\placestamp{Later}
%
By virtue of his skills and his contacts, Charcoal was privy to many things, having witnessed both \Constance{} \ps{\Kintaer} interrogation and the attempted arrest of \Ambrose{} \Onatol. 
When the apprehension party had begun collecting clues from \ps{\Onatol}{} quarters, Charcoal had been quick and stealthy in grabbing a journal and a stack of letters that caught his eye, stealthily tucking them away before the investigators could get their hands on them. 

\tho{Interesting stuff, by the looks of them,} he mused as he strolled down the stairs from \ps{\Onatol}{} tower room. 
From his many years in the organization, Charcoal had developed an intuition for such things. 
\tho{I will need to study these when I have the time.} 

\tho{But first things first. 
The \rinyuth wants little \Constance{} killed. 
She's cute, but she's no use to me dead. 
That would be icky. 
I'll need to visit her again and see if I can't extract some more, ahem, \quo{information} from her, before they cut off her pretty head.} 

And so he descended into the dungeon. 

The dark stone walls were thick down here. 
Stained with blood in places and adorned with chains, hooks, iron maidens and all sorts of imaginative torture instruments. 
Long poles with barbs, scissors-like objects, evil-looking masks and other things. 

Some of the instruments were not at all useful, Charcoal knew, their only purpose to evoke an intimidating atmosphere. 
Some were even encarved with the forms of evil \daemons{} or gargoyles to inspire greater dread and apprehension. 

At times, ghastly sounds could be heard. 
Some of them were merely the cries of prisoners, but there were never many live prisoners at a time in the dungeon. 
The worst were the sounds from Beyond. 
For though the stone walls might be thick, the Shroud was precious thin in this place. 
Places of torture and horror, Charcoal knew, had a tendency to accumulate a certain \quo{residual madness}, which sometimes let you peer through the Shroud. 
And let you hear the wailing of the damned souls who had died here, and the slavering of the \daemons{} and \qliphoth{} that fed on such things. 

Shrugging off the haunting sounds and feelings, Charcoal made his way through narrow, oppressive, vermin-infested corridors to \ps{\Constance}{} cell, where the guard quickly opened the door upon his approach. 

Entering the cell, he found \Constance{} strapped naked to a table. 
Another guard\dash Nobb, a big, stupid man\dash was having his way with her. 
Judging from \ps{\Constance}{} lack of movement, he had been at it for a while. 

\ta{Move over, Nobb,} said Charcoal, reaching down to undo his belt. 
\ta{My turn.}
 
\end{garbage}







