\bookchapter{Needle}
\stamp
  {\dateCharcoalFucksNeedle}
  {Slave quarters, \CastlePelidor, Malcur}

The door to her room was flung open and a pair of boot stomped in. \Brittany{} spun around, ready to berate the intruder for not knocking. 
She might be a slave, but as the duchess' personal handmaiden she was owed respect from her fellow slaves. 
Her open mouth was quickly clamped shut as she recognized the newcomer. 

Charcoal slammed the door behind him. 
\Brittany{} immediately rose and curtsied. 
\ta{Master.}

Charcoal grabbed the lone chair in the room and seated himself. 
It creaked under his considerable weight. 
\ta{This chair is uncomfortable,} he complained. 

\ta{I'm sorry, master.} 
\tho{What do you expect? 
  This is a slave's quarters. 
  If you want a chair that can hold you, then lose that belly of yours.}

\ta{I may have to go away on some business, Needle. 
  In my absence I am leaving you in charge of the city.} 

\ta{Yes, master.} 

\ta{I have been detecting massive Sentinel activity lately. 
  I've sensed spells being cast, and I've lost several men. 
  Be very careful about them. 
  How's it going with infiltrating that thieves' guild?} 

\ta{I am making progress, master. 
  I have established a few contacts and am crawling up in the pecking order.} 

\ta{Good. 
  I'm in a hurry, so listen well...}

And \Brittany\dash Needle\dash listened as Charcoal explained what she would need to know:
How to contact his various agents in the city, 
how to identify prove her status as their Cabal mistress, 
what Sentinel signs to watch out for, 
what people and places to beware, 
and any and all further information that he was willing to divulge. 

\ta{If you manage to close in on the Sentinels' nest, then strike quickly. 
  Destroy them if you can. 
  Show them that the Cabal means business.
  Even if you haven't figured out what's going on, strike anyway. 
  Go at them with full force. 
  Fool them into thinking you know more than you do. 
  With luck, we can scare them into doing something stupid. 
  Or at least into acting more reluctant, thus buying our side valuable time.} 

He paused and looked at her with eyes narrowed. 
\ta{Are you up for this, Needle?
  Can I trust you with running our operations in the city by yourself?}

Needle repressed a sneer. 
Charcoal was her mentor and accomplice, and perhaps even her friend, but there were times when she almost hated him for his brusqueness and condescension. 

She held her head up and looked him in the eye. 
\ta{Master, I am \needlecircle{} for a reason. 
  I can do this.}

Charcoal studied her some more. 
His lips twitched, missing his pipe. 

\ta{Very well,} he said. 
\ta{Do not disappoint me.} 

\tho{Or you could have gone with \quo{good luck} or \quo{take care}.}
But that was not his style. 
At least, not nowadays. 
She and Charcoal had been closer in the past, but their relationship had since cooled. 

\tho{I will do this. 
  This is my chance to grow out of Charcoal's shadow and prove my worth as a Cabalist. 
  Perhaps I can even secure a promotion.
  
  Just you wait, Charcoal.  
  I'm advancing faster than you. 
  One day I'll outrank you.% 
%   Then I'll no longer answer to you.
}

\begin{comment}
Needle is annoyed by the doubt. 
But she also wants to prove herself. 
She doesn't dislike Charcoal. 
He is her mentor, and she owes him. 
But he is a jerk at times. 
She is tired of working under him. 
She longs to be promoted and be his equal, not his servant. 

So she holds her head up high - maybe too high, considering her status, and assures him she can do it. 
"I am nth circle, master. I can do this."

He studies her a bit more. 
"Very well. Do not disappoint me." 

\tho{Or you could have gone with "good luck" or "take care".}
She and Charcoal had been closer in the past, but their relationship had cooled. 

\tho{I will do this. 
  This is my chance to grow out of Charcoal's shadow and prove my worth as a Cabalist. 
  Perhaps I can even secure a promotion.}
\end{comment}









