\bookchapter{River of the Damned}

\begin{comment}
\subsection{Frozen}
\end{comment}

Darkness. 
All was darkness. 

He knew not how long he had been stranded here. 
He knew not if he was conscious or not. 
He knew not who he was. 
He knew not who he had been. 

He did not even know that he was losing his mind. 

Frozen. 
Lifeless. 
Dreaming. 

There was pain. 
But there was no mind to feel the pain. 
A desire to scream. 
But no mouth with which to scream. 
No voice. 
No breath. 
No life. 
Only the frozen pain. 

All was darkness. 
Emptiness. 
An emptiness so vast and consuming that all consciousness was swallowed and extinguished. 
There was no sanity. 
There was not madness. 
There was nothingness. 

Nothing. 



\new
Then... something. 

Movement. 
Feeling. 

Something. 

\tho{Something happens. 
Something exists.} 

With the return of the senses came, ever so slowly, the return of the self. 

\tho{I exist.

Who am I?
\Icor. 
Yes. 
That's it. 
I am \Icor. 
I am \Icor{} Pelidor. 
Duke \Icor{} Pelidor. 

Where am I?

I am dead.} 



\begin{comment}
\subsection{The River}
\end{comment}

% Slowly, the darkness was broken by an image. 
% A thing came into view. 
Slowly, his senses came back to him. 
An image came into view. 
Sounds could be heard. 

\tho{Voices? Words?}

The image gradually took shape. 
There was motion. 
There was energy. 
There was... life? 

\tho{A river?}

Yes. 
It was something like a river. 
A river of... something. 
Flowing amid an endless ocean of crushing darkness. 
The river was powerful. 
It foamed and roared. 
It flowed with...

\tho{People?}

He began to see things that reminded him of faces. 
Bodies. 
Limbs. 

\tho{A river of people?} 

\Scathae. 
\Meccara.
\Humans. 
Other things. 
They flowed with the stream. 
Writhing. 
Helpless. 
Their eyes were dead. 
Their limbs were cramped. 
Their legs and tails were withered. 
Their hands reached out. 
Claw-like. 
But feeble. 
Impotent. 

There was something around them, between them. 
Bars? 
Chains?

\tho{A cage?}

The people were shackled together and imprisoned behind bars. 
They could not escape from the river. 
They could only flow with the stream. 

\tho{The river is a cage.} 

He looked into those lifeless eyes and saw... death. 

\tho{These people are dead.
A river of the dead.} 

Their mouths were moving. 
He could hear them now. 
He understood few words, but he understood the tone. 
The dead were wailing. 
Moaning. 
Weeping. 
Begging. 
Mourning. 
Cursing. 
Babbling. 
Threatening. 
Beckoning. 

\tho{They are mad. 
Mindless. 
Senseless. 
A river of enslaved, crazed dead. 
Flowing on and on. 
Helpless.
Forever. 
Through the frozen void.} 

Their morbid wailing reached out to him. 
Their ghastly, dead voices tore into his mind, like nails hammered into his head. 
Their mad voices beckoning him. 
Calling him. 
Imploring him. 
Commanding him. 

\tele{Come to us.
Be one of us. 
Be one with us.
Share our death.
Share our fate. 
Share our suffering.} 

The river of souls roared louder. 
He realized that he was drifting closer to it. 
He was being drawn toward them. 

\tho{No!} 

He struggled. 
He tried to struggle. 
He tried to flail. 
But he had no arms. 
He had no legs. 
He had no tail. 
He could not stop himself. 

The river roared ever louder. 

The macabre voices wailed ever louder. 

\tho{No! 
Let me go!
I don't want to join you!
I don't want to be trapped in this prison of souls.
I don't want to flow forever in a river of the dead.}

It struck him. 
\tho{These people are the damned. 
The realm of the damned. 
This is \Itzach. 
It must be. 

Oh, \sephiroth. 
I am in \itzach!} 



\begin{comment}
\subsection{The Angel}
\end{comment}

\tele{Nay. Thou art not.} 

That was a new voice. 
Not deathlike. 
Beautiful. 
Pristine. 
Noble. 

A vision appeared before him. 
Bright. 
Shining. 
Blinding. 

It took many moments for \ps{\Icor} senses to adjust to the vision. 
It was... a \scathaese{} child. 
Androgynous, with pearly white scales. 
And great feathered wings on its back. 
It was almost translucent, glowing with with a brilliant white light that seemed to radiate from the core of its body. 

\tho{An angel. 
Who... are you?}

\tele{I am a messenger.} 

\tho{What is this? Where am I?} 

\tele{Thou art in the realm of the dead.} 
The angel gestured to the roaring, weeping river. 
\tele{What thou seest before thee is the realm of the damned, where souls are enslaved in torment.} 

\tho{\Itzach. 
But... why? 
Why am I here? 
Why am I in \itzach?}

\tele{Thou art not in \itzach. 
Not yet. 
But neither art you saved. 
Thou mayest yet fall into the river.}

\tho{But why? 
Have I sinned? 
Why am I not going into the Light?}

\tele{There is evil at work in the world, \Icor{} Pelidor. 
Evil forces that capture the souls of the wicked and the innocent alike. 
Thou hast felt the power of the river. 
It reacheth out and draweth souls unto itself.} 

The angel turned its piercing gaze on him. 
\tele{We fight these evil forces, but we are not all-powerful. 
We cannot save every soul. 
We need thine aid, \Icor{} Pelidor.}

\tho{Me? You need my help?} 

\tele{Yes. 
Do what we ask, \Icor{} Pelidor, and thou shalt know our aid in return. 
Thy soul can be saved. 
Thou wilt be able to go into the Light.} 

\Icor{} would have gulped, but he had no throat. 

\tho{What do you want me to do?} 

The angel told him. 









\begin{comment}
\subsection{\Psyrex}
\end{comment}
\begin{comment}
\stamp
  {\dateIcorMeetsPsyrex}
  {Dark Crescent throne}

With a smile, \LocarPsyrex{} released the spell that created the image of the childlike angel and let the illusion fade away. 

\tho{He swallowed every word. 
And why should he not? 
I told no lies.} 
\Psyrex{} enjoyed it when he could mislead people simply by twisting the truth, never telling an outright lie. 
It was a sport to him. 
He would lie whenever he needed to, of course, but millennia spent manipulating others had shaped him into a conoisseur, an artist. And every artist had his eccentric habits. 

\tho{Yes. \Icor{} Pelidor will serve my purpose well.}
\end{comment}










