\documentclass[a4paper,12pt,openany,oneside]{book}
\include{Utilities/UsePackages}
\input{Commands}
\bibliographystyle{plainnat}
\begin{document}
\chapter{Introduction}
I want to write one or more stories set in the Cthulhu Mythos, the shared universe developed by H. P. Lovecraft and others. 
These are some notes and ideas for those stories. 























\chapter{Ideas}















\section{Apep}
Apep is a Great Old One.
He is identical with the Ouroboros and Tiamat of Babylonian myth and the Mappo no Ryujin from \cite{RPG:CallofCthulhu:SecretsofJapan}. 

Apep is the parent of Yig, perhaps together with Shub-Niggurath.
He is the cruel god of destruction whom the serpent people fear.
One day he will lay waste to the world and prepare the way for the reign of the Great Old Ones.

Apep intends to open the gates to chaos and awaken/free the Great Old Ones. 
Some serpent people want to make this happen.
They have realized that it was a mistake for serpent people to try and coexist with humans. 
The humans must be wiped out. 

The Elder Things know that Apep is about to awaken.
They want to return to Earth and consume all life, like they planned the whole time.















\section{Black Lotus}
I should have black lotus dreams, like in Robert E. Howard's stories.















\section{Cryptozoology}
Refer to real-world cryptozoology. 
Cool cryptids include: 

\begin{itemize}
  \item The Mongolian death worm (olgoi-khorkhoi).
  \item The Mothman.
\end{itemize}
















\section{Cthulhu}
The Cthulhu cultists are like Gnostics. 
They long for the day where the false gods go away and the true gods return. 
See \cite{RobertMPrice:TheOldOnesPromiseofEternalLife}.















\section{Elder Things}
Like all other life on Earth, the Serpent People evolved from things engineered by the Elder Things. 
As such, they were paws for the Elder Things to harvest, just like they harvest the humans in \cite{TimCurran:Hive}. 
And they \emph{were} harvested, in the Triassic. 
This destroyed their civilization, but some Serpent Men survived. 

Since then the Serpent Men have craved revenge against the Elder Things. 
They know they are the underdogs in this conflict, so they have appealed to the Great Old Ones: 
Yig and Tsathoggua. 

Also, man-made global warming is really engineered by the Elder Things. 
They know the Great Old Ones will awaken soon and wage war against them.
They are tired of being frozen in the Antarctic. 

There have been many races thoughout Earth's history which the Elder Things have bred, manipulated and ultimately harvested.
This was why the humans were able to conquer the world and drive out the Serpent Men and other elder races at the beginning of the Thurian Age:
The Elder Things were destroying them and sowing new crops, namely mankind. 

The Serpent Men are an ancient race. 
They have survived several cataclysms and seen several races wiped out by the Elder Things, so they know what they are up against.
They are underdogs, but they have been preparing for hundreds of millions of years, so they are not defenseless. 









\subsection{Elder Gods}
The Elder Things are the same as the Elder Gods. 
They have a base on Betelgeuse. 

The Elder Things on Earth hope that if the shit hits the fan and the Great Old Ones break free of their prison, their long-lost brethren on Betelgeuse will come to Earth to save them.
The Things on Betelgeuse are more advanced and have not forgotten so much of their science as the ones on Earth have\ldots or at least, so the Terran Elder Things believe and hope. 

That is one of the reasons why the Elder Things on Earth want to harvest the humans quickly:
They need a new influx of energy if they are to contact their kin on Betelgeuse and convince them to come to their rescue.
And that has to happen soon, before the Great Old Ones awaken. 

It was the Elder Things who created the Elder sign: 
\quo{the five-pointed star carven of gray stone from ancient Mnar} 
(\cite[p.289]{AugustDerleth:TheTrailofCthulhu}).







\subsection{Mountains of Madness}
Beyond the mountains of madness in Antarctica there is an even taller mountain range. 
Here dwells an unnameable horror which even the Elder Things fear:
The colour out of space (as in \cite{TimCurran:Hive}), the Unknown God (as in \cite{RPG:CallofCthulhu:BeyondtheMountainsofMadness}), or something else. 
The thing may be connected to Yog-Sothoth, according to Paul Danforth on the last page of \cite{HPLovecraft:AttheMountainsofMadness}. 















\section{End of the World}
The end of the world is heralded by earthquakes and other natural catastrophes. 
Compare to \cite{RPG:CallofCthulhu:EndTime} and \cite{RobertBloch:StrangeEons}. 















\section{La Fin Absolue du Monde}
Refer to the fictional film \emph{La Fin Absolue du Monde}, found in \cite{Movie:CigaretteBurns}.















\section{Ghroth}
The planet Ghroth is a harbinger of the end times. 
It first appeared in our solar system in \cite{RamseyCampbell:TheTugging}, which takes place in the 1970s. 
 
Ghroth is still in the solar system. 
After all, the cycles of the universe take thousands or millions of years. 
Ghroth does not awaken the Great Old Ones immediately when it arrives. 
It takes a few decades. 

Ghroth moves in a very strange orbit. 
It does not seem to follow the normal laws of how celestial bodies move.
It gives astronomers gray hairs. 
Some astronomers become desperate and lose sanity points from attempting to understand it. 















\section{Gnophkehs}
Some say that the Gnophkehs (who destroyed Lomar) were reptilian and worshipped Azathoth.















\section{Hounds of Tindalos}
The Hounds of Tindalos are the Spawn of Noth-Yidik and the effluvium of K'thun.
They serve Azathoth. 
Their allies are Doels and satyrs (spawn of Shub-Niggurath).
See \cite{LinCarter:TheMadnessOutofTime}.















\section{Kadath and Leng}
According to \cite{DanielHarms:TheCthulhuMythosEncyclopedia}, Kadath was once a vast city of the Elder Gods that covered our entire planet at one time. 

Various sources place Kadath in Tibet/China, Antarctica and the Dreamlands. 
Make a decision about this.
Kadath might be in all of these places at once, a transcendent eternal city.
Compare to Tanelorn from \cite{MichaelMoorcock:ElricofMelnibone} and Metropolis from \cite{RPG:Kult}. 















\section{Kane}
I want to tie Karl Edward Wagner's Kane into the Cthulhu Mythos. 
In my reinterpretation, Kane was born in the early Thurian Age, created by a mad Great One (one of the gods of the dreamlands) who dreamed of shaping a race in his own image. 

Kane was one of the co-inventors of nuclear weapons. 

In the modern age, Kane and Klesst are two of humankind's mightiest sorcerers. 

In the end, Kane is killed by the violence he himself helped create. 







\subsection{Yahweh}
Yahweh was a Great One (one of the gods of the dreamlands) who dreamed of shaping a race in his own image. 
He created Kane. 
In response, Kane slew Yahweh.

Yahweh is identical to the human god Tirawa worshipped in \cite{HPLovecraft:TheCurseofYig} and \cite{HPLovecraft:TheMound}. 
The worshippers of Tirawa have never realized that their god is dead. 

His real name might be Der-huach.















\section{Mi-Go}
The Mi-Go secretly operate on Earth in the guise of \quo{Grays}. 
They occasionally work with the Serpent Men, but also fight against them.
The Mi-Go want to try to prevent the return of the Great Old Ones because they have important mining operations going on on Earth.















\section{Oriuagor}
I should incorporate \emph{Oriuagor\dash The One Who Waits} from \cite{PalleVibe:OriuagorsProfeti}. 















\section{Serpent Men}
My story should feature the serpent people.
They are cool. 

The serpent men of the second Valusia which were defeated by Kull the Atlantean were degenerate wimps. 
They worshipped the Great Serpent (Set/Yig), but they were touched by the taint of Tsathoggua. 
They were so feeble that humans could defeat them and drive them away. 
Without their superior science and sorcery, serpent people are not so formidable. 
They are physically strong enough, but they are long-lived and reproduce slowly, and they tend to be sluggish and slow, so after some thousand years the fast-breeding, numerous and aggressive humans were able to overwhelm them. 

But at that point the serpentine civilization was already decayed. 
They had forgotten their ancient knowledge. 
Later, long after Kull's time, some of the mightier serpent men awoke from their torpor. 
They remembered the knowledge that formed the greatness of their civilization.
They set out to reunite their fallen brethren and rebuild their empire, slowly, ever so slowly. 
This would take thousands of years, but with the infinite patience of immortal reptiles nothing was impossible. 

In some parts of the world, the serpent men taught science and magic to the humans.
The humans betrayed the serpents and killed them.
The serpents reproduced slower than humans, so the humans were able to overrun them. 

The serpent men want to reawaken the Great Old Ones so they will be reunited with their Father Yig. 









\subsection{Gods}
The serpent people served a number of gods, chiefly Yig.
Secondarily Tsathoggua and Apep.

The \quo{Nagas of ancient Mu} (obviously serpent men) worshipped Narayana, the Seven-Headed Serpent, according to \cite[p.108]{RichardTierney:ThroneofAchamoth}. 

Some serpent men worshipped Azathoth in a black tower somewhere in the Arabic desert maybe 500,000 years ago. 
Perhaps near the Nameless City. See \cite{JohnGlasby:TheNamelessTower}.









\subsection{Necromancy}
The Serpent People are great necromancers. 
As stated in \cite{RobertEHoward:TheShadowKingdom}, when a man is killed by the Serpents his ghost becomes their slave. 

They can also teach humans to achieve immortality by shedding their skin, as in the song \quo{Serpent-Headed Mask} on \cite{Nile:AmongsttheCatacombsofNephrenKa}.










\subsection{Reptilian conspiracy}
\label{Reptilian conspiracy}
The serpent people are really behind much of humanity's technology. 
Did you really think the feeble humans could have invented all those marvels of science on their own?
No.
They were given to them by the serpent men, but not as free gifts.
The serpent men have a plan.
All human civilization is a tool of theirs, an instrument of their revenge and the resurrection of the Great Serpent. 

The conspiracy theories of \cite{DavidIcke:TheBiggestSecret} and others, about a race of reptilian humanoids secretly controlling the world, are true.
The serpent men are those reptiles. 

David Icke believes the reptiles are extraterrestrials. 
In this he is wrong.
The serpent men are native to earth, although they can travel to other dimensions.
They were created by extraterrestrials, though. 
(All life was seeded by the elder things, and Yig is credited as the father of all snakes.)

The serpent people control humans via astral projection and possession.
The serpents' own bodies lie in suspended animation.
Humans with serpent blood (nephilim) are an ancient conspiracy.
See \cite{RPG:CallofCthulhu:SecretsofJapan}. 









\subsection{K'n-Yan, Yoth and N'kai}
Serpent people once dwelt in the red-littern cavern of Yoth. 
Here they engineered many servitor races. 
They worshipped Tsathoggua.
For this Yig cursed them.
They degenerated into quadrupeds.

The serpent people of Yoth claimed in their writings that black N'kai was devoid of life, but later people of K'n-yan found the formless spawn of Tsathoggua down there.
The serpent people knew of them, but feared them and would not acknowledge their existence. 

By the time humans moved into K'n-yan above Yoth, the surviving serpent men were gone, having been led away to Voormithadreth by Sss'haa. 
They left behind some denegerate reptile-human things that resembled \hs{Worms of the Earth}. 
These were the unfortunate that had succumbed to Yig's curse.









\subsection{Magic and technology}

The humans of K'n-yan could teleport and perform some kind of astral projection.
The fully avatistic serpent people must have \emph{at least} the same level of technology. 

The greatest and wisest serpent people possess at least the same level of enlightenment as Randolph Carter in \cite{HPLovecraft:ThroughtheGatesoftheSilverKey}. 









\subsection{Worms of the Earth}
\target{Worms of the Earth}
Yig can crossbreed humans and serpent people.
He does this to punish either side. 
That was how he created the Worms of the Earth: 
By mixing the unfaithful serpent men with humans\dash a great and terrible humiliation for the serpent people. 















\section{Other influences}
I should incorporate influences from the following:

\begin{itemize}
  \item 
    Conspiracy theories. 
    See the section about the \hr{Reptilian conspiracy}{reptilian conspiracy}.
  \item 
    Cryptozoology. 
  \item 
    New Age spiritualism.
  \item 
    Traditional mysticism, such as Gnosticism and Cabbalah.
  \item 
    Mainstream religions.
\end{itemize}























\chapter{Timeline}
According to \cite{HPLovecraft:OutoftheAeons}, Hyperborea and Mu existed at 200,000 BCE. 
This might have been the very early Thurian Age, or an age just before that.

Perhaps humanity originated on Mu. 

Mu fell before Atlantis rose to dominance. 
This is consistent with the notion that Mu flourished before the age of Kull and Atlantis became a great civilization \emph{after} Kull.
See \cite[p.95]{HenryKuttner:TheInvaders}, where Mu was attacked by the \quo{Dwellers in the Hidden World}, who were vanquished by Vorvadoss.

Humans and serpent people coexisted on Mu.
Mu perished in a \quo{Great Experiment}, and the suriving humans fled to Japan, according to \cite{RPG:CallofCthulhu:SecretsofJapan}.

In my version, humans settled K'n-yan about 200,000 BCE in the early Thurian Age.
They sealed the entrances after the fall of Atlantis and Lemuria, which occurred some time \emph{after} the life of Kull, 100,000 BCE.

Lomar fell around 26,000 years ago, according to \cite{HPLovecraft:Polaris}. 

Sarnath stood around 10,000 years ago, according to \cite{HPLovecraft:TheDoomthatCametoSarnath}. 























\bibliography{Mith.bib}


\end{document}
