
\documentclass
  [a4paper,
   12pt,
   %openany,
   oneside
  ]%
  {article}





%\usepackage{sectionbreak}
\usepackage[all]{nowidow}

\usepackage[english]{babel}
% \usepackage[
%   backend=biber,
%   style=alphabetic,
%   citestyle=authortitle
% ]{biblatex}
\usepackage[utf8]   {inputenc}
\usepackage[T1]     {fontenc}
%\usepackage         {charter}
\usepackage         {comment}
\usepackage         {cuted}
\usepackage         {etoolbox} 
\usepackage         {graphicx}
\usepackage[sc]     {mathpazo}
\usepackage[toc]    {multitoc}
\usepackage         {twoopt}
\usepackage         {xspace}
\usepackage[pdftex,colorlinks,linkcolor=blue,pdfstartview=FitH]{hyperref}

%\include{UsePackages}
\input{Commands}
\input{Hyphenation}

\newcommand{\sectionbreak}{\bigskip\noindent}
\newcommand{\drum}[1]{\textsf{#1}}




\title{Hold Until I Come}



\stuffinthepreamble



\begin{document}



    \maketitle
    \tableofcontents














% 
% \section*{Dramatis Personae}
% \begin{dramatispersonae}
%   \dramitemnoyear{Suthis Mephilex}{\scatha}{\female}, 
%     apprentice sorceress
%   \dramitemnoyear{Suthis Dristan}{\scatha}{\male}, 
%     apprentice sorcerer, Mephilex's cousin
%   \dramitemnoyear{Suthis Cruan}{\scatha}{\male}, 
%     master sorcerer, Mephilex's grandfather
%   \dramitemnoyear{Jaslar Thul}{\scatha}{\female}, 
%     sorceress
% \end{dramatispersonae}



\section{War}
``'Hold until I come'{}'', the captain read aloud from the telegram. ``'And protect the hierophant at all costs.' That is the message from Exalted Lord Iscrafel.'' 

Murmuring broke out among the soldiers and others: ``Great Insharrad!'' and ``Jach-dun preserve us!'' 

Filima Kepra did not understand what was going on in the world. 
All he knew was that rumours said the resphan kingdoms had gone to war against the suchian nations. 

Kepra looked out. From where he stood in the Cressax citadel courtyard he could not see only the walls. Those massive stone walls that looked impenetrable. 
But out there somewhere to the west was an enemy army bent on their destruction.

Why was there suddenly war? Why would the resphain attack? 
\emph{Then again, who understands the resphain? Who can understand the strange mind of a mammal?} 
The mammalian races\dash{}resphain and humans\dash{}were not like sane reptiles. The mammals did not know the two Divine Principles\dash{}Zotha and Asheen, the virtues of Greatness and Harmony\dash{}that guided the noble reptilian civilization. Nor did they know any of the Epitomes. A human could be \emph{taught} about the Principles and the Epitomes, sure, but they could never \emph{feel} it. They did not have Zotha and Asheen in their hearts, and so no Epitome of virtue could truly touch them. 

Still, Kepra knew, humans were not savage beasts. They had intelligence. Nor were they wholly evil. They could have morals and honour. At the best of times a human could be noble, almost like even a suchian. But Kepra did not understand them. 
\emph{Without the Holy Principles, what leads a human to good or evil?} 

And as for a resphan, who could tell? The greater mammalian race, far above humans, far greater and more terrifying. Capable of good, he supposed, but also of great evil. Who could tell what went on in the terrible mind of a resphan? As he mused, Kepra muttered a prayer to Jach-dun, the Epitome of defiance against foreign powers.

\emph{And now they are coming here.} 

Kepra’s tongue darted out nervously to lick his eye.

%If the foe did intend to wreak evil and destruction, it made sense for them to come here to Cressax Outpost. 

%Filima Kepra defends Cressax Outpost outside the city of Luth Gormat. Kepra is assigned here because he and his brood, the Filima, are citizens of Luth Gormat, under the rule of the Gormat brood. Cressax is an important site, containing both a zest refinery and one of the Sacred Pillars of the Great Concord that keeps the suchian race united. Surely the resphain do not intend to destroy or desecrate the Pillar? Surely not even a resphan is capable of such blasphemous evil? Kepra glances towards the Pillar. It is a marvel. Outwardly an obelisk of white and black stone, adorned with figures of Epitomes, heroes and serpents in gold and brass and iron. And inside it houses marvellous machinery devised by brilliant mages and engineers, consecrated to the Epitomes Kelesh, Suthalba and Tsor. It is this machinery, channelled through the splendid obelisk and many other Pillars like it, that uphold the Divine Concord and thus keep all reptilians connected to each other and to the virtuous Epitomes. It is the Concord that allows the Epitomes to guide all suchians and scathae to lead virtuous lives and contribute to the greatness and harmony of their civilization.

Cressax Outpost was an important site, housing not only a major zest refinery but more importantly one the Sacred Pillars of the Great Concord that kept the suchian race united. Surely the resphain could not intend to destroy or desecrate the Pillar? Surely not even a resphan was capable of such blasphemous evil? 

Kepra turned his head to look at the Pillar. It was a marvel. On the outside a monolithic obelisk of white and black stone, adorned with figures of Epitomes, heroes and serpents in gold and brass and iron. And inside it was full of marvellous machinery devised by brilliant mages and engineers, consecrated to the Epitomes of the Concord\dash{}noble Kelesh, wise Suthalba and mystic Tsor. It was this machinery, channelled through the splendid obelisk and many other Pillars like it, that upheld the Divine Concord and thus kept all reptilians connected to each other and to the Epitomes. It was the Concord that allowed the Epitomes to guide all suchians and scathae to lead virtuous lives and contribute to the greatness and harmony of their civilization.

\emph{Would the resphain seek to destroy this? Is that how deep their evil goes?}

Kepra could not even imagine what might happen if the Pillar were destroyed and the Concord damaged. Would all reptiles lose sight of the virtues of the Epitomes? Would they lose the Holy Principles, Zotha and Asheen, Greatness and Harmony? Would they turn on each other like mad beasts, bereft of all morals, all civilization, all bonds of kinship?

\emph{
    We must not let it come to that.%
%     We must hold until the Exalted Lord arrives.
     }



\section{Hierophant}
% The captain, Onocca Sabot, says: 
``We are in luck'', said the captain. ``The resphan force is small. They have only just over two thousand humans and no heavy siege engines. They outnumber us, but this citadel is strong. We can hold them. But I will not deceive you: It will not be easy. They have several resphain with them.'' 

A shudder went through the army at the thought of facing resphain. Kepra was no great warrior, but he would stand up to marauding humans with Zotha in his heart. 
%And with Druzcalacht, Epitome of valour. 
But resphain? 
\emph{How does one fight against such monsters?}
Kepra prayed silently that Druzcalacht, the Epitome of valour, would give them all strength.

The captain continued: ``But we stand not alone. We need only hold until the Dragonlord Iscrafel comes to our rescue. Stay true to the Epitomes and to your comrades and we will live. The Dragonlord will be here before nightfall.''

\emph{The Dragonlord! A dragon is coming to rescue us!} 

And not just any dragon, but Iscrafel! Belraphon Quessanth Iscrafel, the Juggernaut, the Last Mysteriarch's right hand and champion, the most renowned warrior-mage among all suchian nations and broods! 
Kepra had seen a dragon before, but only one of the less famous ones.
%- Semirex was her name. 
But Quessanth Iscrafel! The thought of getting to see Iscrafel and his army in battle made Kepra's heart soar with a tingle of Zotha\dash{}the Principle of Greatness, that drive towards achievement and nobility and pride that lived within every suchian.

\emph{And we will need him.} 
Kepra looked around. 
Cressax was a strong fortress, but they were unprepared for war and had only a skeleton garrison.
The defenders numbered a mere three hundred\dash{}most of them scathae, with about thirty suchians like Kepra and unit of a few dozen human spearmen.

He hoped their walls would hold. 

%Their force numbers maybe 200. Most are scathae. There are about 20 suchians like Kepra, mostly mages and founts plus the commanding captain. They also have 20-30 human spearmen.

Another suchian stepped forth next to the captain\dash{}their spiritual leader, the hierophant Aeocryth of Rystessakhin.
She was older than most of them; past a hundred at the very least, well into suchian middle age.
She looked exotic in her beautiful yellow robe adorned with stones and jewels. 
Where Kepra and most of the other suchians here had normal gray scales, Aeocryth’s faintly maroon-tinted scales marked her as a foreigner. 
Though she spoke perfect High Talaac, she was not ethnically Talaac like Kepra and his master, nor Saphyr like many of the others. 
Rystessakhin was a Felgian brood; hence her odd name, \emph{Aeocryth of Rystessakhin}. 
By Talaac or Saphyr tradition the name would be Rystessakhin Aeocryth. 

She was the one whom Lord Iscrafel told them to protect.

Aeocryth spoke: ``We must stand together. Trust in the man next to you, and be true to the Epitomes. Have Druzcalacht in your heart, and Jach-dun, and Insharrad!'' 
The hierophant intoned the holy names with great passion, and every reptile present felt it\dash{}felt the truth and the presence of the noble Epitomes in their bodies. 
Felt the Concord. 
Kepra smiled at the uplifting touch of Insharrad, called by some the Greatest Epitome and representing the pride and unity of the suchian race.

And yet underneath it all, Kepra seemed to detect in the hierophant a certain sadness.

The hierophant went off to say some words to the humans among the defenders. 
It made sense, Kepra supposed, that the humans would need special spiritual guidance, since they could not feel the reptilian Epitomes. But he had no idea what she said to them.

\emph{Those humans. No Asheen in them. No Zotha. How can you trust them?}

That reminded Kepra of something. 
When the captain had announced the order to protect her ``at all costs'', he thought he'd seen a flicker of a strange reaction from her. 
He thought she had winced or even cringed. 
What was that? 
Was it fear at the thought of getting killed by resphain? 
It must be.



\section{Founts}
``Take your positions!'' said a scatha lieutenant. 

Kepra double-checked that he had his dagger\dash{}for emergency self-defense. 
He attached his third drumstick to his tail, 
adjusted the position of his secondary drum,
and picked up his two main drumsticks.

Kepra was of the greater reptilian race, the suchians. 
But he took orders from the lieutenant, a scatha. 
This was just the way things were. 
The scathae were a lower race, but they could rise in the ranks according to their merits. 
Many scathae in the world ended up outranking one such as him.
Such was life.
Kepra’s brood, the Filima, were not of noble rank, and besides, Kepra knew he was young and inexperienced\dash{}just 33, barely a man by the standards of his people. 
And he was no officer or mage. 
Barely even a soldier. 
He was just a youth with a drum. 

He had once dreamed of being a mage, but that had proven too dangerous for one of his meagre talents. 
So now he served as a fount. Not the most glorious of professions, but a perfectly respectable and well-paid one.

He took his place at his giant bass drum, with a smaller drum behind him so he could also use his tail. 

He looked around to see his friends. 
The ones he knew best were of course his fellow founts in service to the ward-mage Tezoron Rarxan. 
They were all in place. Grecca with his smaller drums. Sorom and Contor with their horns. Sipel with her flutes. 
And there, robed in blue and silver and strapped into the ward machine, was master Tezoron. 
It was she whose work Kepra and his fellows would be supporting. And over there was the other ward-mage, Griph Parun, and her founts. He did not know them quite as well, but they had trained in concert together. 
They were supposed by several more musicians who were not founts.

\emph{We can do this.}

With the two ward-mages was the cleric Aeocryth of Rystessakhin, seated on a sacred altar-throne, a machine that connected her directly to the Pillar. 
Kepra's drums happened to get set up in a spot that put the cleric right in his line of sight. 
She carried no weapon. 
She was a mage, but not a warrior-mage. 
Her role was to be their spiritual guide, to keep Zotha and Asheen and the Epitomes alive in the heart of every reptile and thus keep their army together and their spirits high. 

He could understand why Lord Iscrafel had admonished them to protect her.

\emph{Iscrafel. I hope he will be here soon.} 

Kepra pictured the Exalted Dragonlord flying at the head of a splendid army to sweep away the resphain and their minions. He pictured the dragon flanked by flying Fireborne knights blasting resphain out of the sky; rows of shining cavalry following on the ground below mowing down droves of resphan-worshippers. 
What a glorious sight it would be! Again he felt Zotha swelling inside him at the thought, and Insharrad. 

A glorious sight. If they survived to see it.



\section{Mages}
``Enemy sighted!'' yelled a scout.

From his position Kepra could not see the enemy, only the immense wall. He could only hear the news as it was passed back from the battlements. 
The resphan army marched on the west gate. 

The so-called resphan army consisted almost entirely of humans\dash{}the lesser mammalian race. 
Apparently the Fireborne reported five resphain. That was already bad enough. Kepra did not even want to think about the idea of facing a genuine army of resphain. 

A mighty suchian warrior\dash{}like one of the Fireborne\dash{}might be a match for a resphan, but not a humble fount like Kepra. 

\emph{I hate resphain. If only someone would wipe them out.} Were they even of this world? Or were the rumours true that the resphain hailed from some other world, some vast corpse-city of crumbling towers and eternal night?

His reverie was broken by a gasp that rippled through the ranks of defenders. 
Mutters of ``Jach-dun!''. 
Kepra felt a foreign presence sweep over them.
In his mind it was like a shower of heavy rocks, pounding them and weighing them down. 
He peered out. 
Above the wall he glimpsed a pair of shapes hovered above the enemy army.
Like humans, but greater, with giant feathered wings on their backs. 
Clad in gleaming jeweled armour and wielding wicked bladed weapons. 
They soared like harbingers of death, evil coming off them in palpable waves. 
Their fell eyes seemed to through pierce him with harpoons of dread, and Kepra had to resist the urge to cower. 

\emph{What can they do? What dread sorcery might they wield?} 

He felt exposed. 
The walls could stop humans, but not flying resphain. 
He wished for shelter.
But of course the hierophant and mages and founts needed to be out in the open to oversee the defense. 
The last time Kepra had been on a battlefield they had at least had armoured carts and other shelter for the mages and founts. 
\emph{But of course, if we'd been that well-prepared for war we'd also have more men.}
%Of course, if they had been properly prepared for war they would also have more men.

\emph{I hope Lord Iscrafel and his army will be here soon.}

Then a surge of warmth welled up in him, sweeping away the dread like water sweeps away filth. 
``Be ready, brethren!'' said the cleric Aeocryth. 
Kepra felt her presence in the Concord, channelled through the mighty Pillar behind them. 
Like strong kind hands holding him up. 
Like the hands of the loving brood nurses that had raised him from egg to man.
``Remember Druzcalacht, valour! Remember Jach-dun, defiance! Remember Insharrad, unity of reptiliankind! Remember Asheen and Zotha!'' 

And Kepra felt them, flowing through him and giving him power. He stood up straight, as did every suchian and scatha in sight. 

\emph{Yes, holy one.}

\emph{Zotha. Greatness. Asheen. Harmony. With these in heart we stand up to evil. With these in heart we defy the resphain and destroy their minions!}

``Prepare for battle!'' the captain called.

A loud boom followed his call, the first blast from the defensive cannons. 

``Founts, get ready!'' said Tezoron Rarxan. 

%With his giant drum, Kepra is responsible for keeping the rhythm. Kepra begins beating his drum. 
Kepra began beating his drum. As bass drummer he was responsible for keeping the rhythm for everyone else.

\drum{One two three four five.} 

He had no spear or gun or armor. Just a drum. 
%He felt unprepared. defenseless. 
But he was just as important.
The others needed him. 
The founts were vital. 

\drum{One two three four five.}

A five-beat rhythm, as was traditional in suchian music. 

\drum{%
    One two three four five. One two three four \emph{tail}. One two three four \emph{tail}. One two-and-three four-and-five. One-and-two-and-three four-and-five. One-and-two \emph{tail} four-and-five. One-and-two \emph{tail} four-and-five.}

The other founts and musicians joined in. 
Soon Kepra began to feel the trance. 
He felt the connection to his brethren\dash{}his fellow founts and Master Tezoron. And the hierophant Aeocryth, their spiritual matriarch, soaring above and guiding them all. 
Now in trance, the founts could begin to share the strength of their minds and bodies with their master.

They played a well-known battle song. 
Those soldiers who could began to sing the words to the song. Some stomped their feet, some pounded their spears to the rhythm. Kepra felt them in the Concord. Though the soldiers and musicians were not trained founts and could not share their strength directly, they could still contribute to morale and help strengthen the Epitomes in everyone.

The hierophant gazed out over them all with a benevolent smile.

Master Tezoron Rarxan, now empowered by her loyal founts, began to chant spellwords in Mystic Talaac. 
Kepra could not understand much of the meaning. Mystic Talaac was difficult to understand; very different from High Talaac or his native dialect.
But he knew the gist of it. It was a spell of warding. 

Master Tezoron’s eyes rolled back. Her body shivered. She must be descending in her mind into the mystic Labyrinth. Kepra knew only hearsay about the dread Labyrinth; after all, he had failed the entrance exam to the academy of mages and had been told to train as a fount instead. 
As such, Kepra could only guess at the spectral horrors that his master must face on that benighted spiritual plane in order to work her sorcery. 

Master Griph, Tezoron's colleague, was likewise murmuring her spellwords. 
The glass tubes and spheres of the ward machines began to hum and shimmer. Soon the air above them crackled and sparkled as the defensive barrier materialized.

Vital energy flowed. 
Quickened by the music and the trance, power flowed through the founts' bodies and between them, through the wise hierophant, through the mages, through the machines. And into the shimmering barrier that would keep them alive. 
That was what founts did: They served as living wellsprings of energy for the mages.
Such was the wonder and beauty of suchian magic.

Meanwhile gunners and archers stood ready at the battlements, waiting for the foe to come within range. 
The loyal humans were in position with spears to fight off any attackers that might try to to scale the walls. 
The defensive cannons kept pounding away at the enemy. Kepra could see nothing, but he smiled with Zotha at the thought of cannonballs ripping resphan-worshippers to shreds.

%The humans on the defenders’ side stood ready on the walls with spears, to fight off any attackers that try to scale them. Spears are what humans are good at. With these small numbers it does not matter much, but Kepra knows that humans are very often used as spearmen or pikemen. Due to their upright stance you can pack many humans tight, forming a strong pike formation. Scathae and suchians are bad a pike formations because they take up a lot of space with their vertical bodies and tails. Scathae, with their quick, strong legs, make better skirmishers. 
%Kepra has once heard scatha skirmishers described as ``a poor man’s cavalry''. 

Kepra looked at the human spearmen. He hoped those humans would remain true to… whatever they had that they could be true to. 

\emph{Show your worth, humans. Show that your race is not all resphan-worshipping marauding scum.}



\section{Ward}
Enemy artillery barked in the distance.

And now the archers on the wall begin firing. The enemy must be close.

After several misses, the first enemy artillery shell shattered against the barrier, sending crackling ripples of lightning across it. Master Tezoron shuddered and hissed through clenched teeth as if struck. Through the Concord Kepra felt a dull thud of that pain, like a punch to the brain. 

\emph{Stand firm, master! Jach-dun!} Kepra prayed as he sent her his energy.

\drum{One two \emph{tail} four five. One-and-two \emph{tail} four \emph{tail}.}

He felt the current of energy flowing into Master Tezoron. She relaxed and breathed deep.

``Well done, noble founts!'' said Aeocryth. ``That could have killed us!'' 
Kepra felt a surge of courage at her words, like water to a thirsty throat. 

\emph{We can do this!}

And was he mistaken or had the cleric nodded and smiled directly at him just before, when he sent prayers to his master? 
Was she reading his mind?

At the battlements, gunfire was intensifying. A scatha cried out in pain. Kepra could not see. It could be an enemy hit or it could be the soldier’s own gun malfunctioning.

Kepra drummed on. 
\emph{Must keep the barrier strong.}
%The trance was strong. He clearly felt his connection to the barrier and how his body and mind were doing their part to uphold it.

\drum{One two-and-three four-and-five. One two-and-three four-and-five.}

More shells struck the barrier. It seethed and threw sparks. But the founts did their duty. The barrier held.



\section{Resphain}
\drum{One two-and-three four \emph{tail}. One-and-two \emph{tail} four-and-five.}\nopagebreak

Suddenly a swift jab of pain. A fellow fount cried out and stumbled for a moment. Out of the corner of his eye Kepra saw a great arrow clattering to the ground, stopped by the barrier.

Another stab of pain through the Concord. 
Another arrow dropped to the ground.

Then someone cried out: ``Resphan!''

The soldiers gasped. Kepra looked up while keeping his rhythm. A hideous winged form swept past, leaving a trace of foul evil like a stench in its wake. 

A black-armoured resphan, wielding a great bow carved with eldritch symbols. 

The resphan beat his wings and rose high into the air. Then he folded his wings and let himself drop. In free fall, the resphan notched an arrow and loosed. And another. The two arrows howled through the air like hungry daemons and punched into the barrier with a crackle. Once again the resphan spread his wings and veered off.

When the resphan dragged the bow through the air, the bow seemed to leave behind an inky smear of black murderous evil. 
The weapon must be consecrated to whatever dark nameless powers the resphain prayed to, ensorcelled to bring destruction and death.

``Kill the resphan! Shoot him down!'' cried the captain. Outside the edge of the barrier, archers and gunners let loose upon the flying resphan, but none managed to score a hit before he rose out of reach. 

The resphan soared, unable to draw back his bow while beating his wings. 
Then he dove again and loosed. This time one arrow punched through the barrier with a resounding crack. 
A spearman wailed, impaled on the arrow. Master Tezoron pounded her fist on something and growled in frustration. She hissed spellwords. 

Again Kepra felt the watchful presence of the hierophant, soothing their fears and keeping them standing.

The barrier held. One arrow had punched through, but the barrier held. 

The officers shouted orders. Outside more gunners fired on the resphan, but to little effect. The shots that did touch him either bounced off or took a feather or two at best.

``Another resphan!'' someone shouted. 

Kepra peeked and caught a glimpse of a resphan diving near the wall\dash{}this one slimmer, perhaps female\dash{}wielding great scimitar-like talons attached to her boots.
%a curved greatsword that shrieked as it swung. 
The resphan swooped and kicked. Her talon-sword shrieked as it punched straight through a scatha spearman. 
He fell to the ground without even a cry. 
To Kepra’s eyes it seemed as though the slain man shrivelled as he fell, as if that daemoniac blade destroyed his very soul and essence. There was an cold ripple in the Concord like a torrent of razor-sharp shards of deathly ice. 

Kepra dropped his drumstick in momentary shock. 

\emph{How can we fight foes like this? Where is Lord Iscrafel?}

``Hold your ground, men!'' said the leader.

Aeocryth echoed him: ``Don’t falter, noble founts! Asheen!''

And Kepra's drumstick was back in his hand. He barely remembered picking it up. 
He could have sworn the hierophant must have taken it from the ground and handed it to him. Such was her influence. 

\emph{She is incredible. She is almost a Mysteriarch.}

Aeocryth admonished the men: ``Remember Asheen! Stand with your fellows!''
And there, throbbing within all of them, was Asheen\dash{}the Divine Principle of Harmony, that drive that every suchian felt to aid, to give, to serve his fellows.
%Throbbing within all of them. 
%Kepra felt his fellows’ need. 

\emph{That's right. My fellows need me. We are all in this together. Asheen.}

Kepra picked up the rhythm.
%He picked up his drumstick. Picked up the rhythm. 

\drum{One two three four \emph{tail}. One two \emph{tail} four \emph{tail}.}

Kepra allowed himself a sigh of relief.
With a powerful cleric such as Aeocryth to lead them, the burden of duty was so light. 
It was almost effortless. 
Like floating in water, buoyed up by her gentle strength.

The other musicians likewise found their pace again. 
They reached out to each other’s presence and the hierophant’s guidance. 
%It gave them strength. 
The music swelled as Holy Asheen swelled in their hearts, and Zotha.

\emph{
    We can do this.
    Keep up the fight. Think of what might happen if we are overrun. If we fall, the Pillar will fall. The Holy Concord will be damaged. 
%     Think of the horrors that will befall the city of Luth Gormat without the Concord and with an army of marauding resphain at the door!
    Think of the horrors that will befall our homes and kinsmen without the Concord and with an army of marauding resphain at the door!%
} 
Kepra thought of his beloved clan, the Filima brood. His brothers and cousins. The wise brood elders. The kind nurses and caretakers. The hatchlings and eggs. 
\emph{Think of the eggs!}

\drum{One two-and-three-and-four \emph{tail}. One-and-two \emph{tail} four \emph{tail}.}

\emph{Please come soon, Lord Iscrafel!}

Emboldened by Asheen, scatha spearmen rushed the talon-bearing resphan woman and managed to drive her off the walls. 

Kepra looked around. Many defenders were wounded or slain\dash{}some felled by enemy shot, some cut down by the cruel resphain. 
The remnants of the loyal humans were holding their ground, to their credit. 
Even with several of their number fallen and without Asheen and Zotha they remained loyal. None had laid down arms and fled. 

\emph{Maybe humans are not that bad.}

\drum{One-and-two three-and-four \emph{tail}. One-and-two-and-three \emph{tail} five.}

The taloned resphan returned. This time she flew high over the wall and dove straight down in their midst. 
%She flies straight through the barrier\dash{}for it protects only against projectiles. 
The barrier only protected against missile weapons, so she passed right through it. 
She flew low over the defenders, shrugging off spear-jabs and kicking with her daemoniac blades. 
%Soldiers jabbed at her with their spears. 
Soldiers gasped as they fell to her talons.

The resphan swooped right past Kepra’s head to swing at Master Tezoron and the ward machine. 
Light flashed and sparks flew as she shattered some of the tubes. 

Tezoron fell to the ground. 

Kepra froze. He missed several beats. 

Aeocryth seized him in a spiritual iron fist: 
``Founts, focus! Falter and we die! Stand together and we live!'' 

Before Kepra could think, he felt the drumstick in his hand pounding on the drum again. 

He shook his head. 

\emph{Yes. Focus.} 

Aeocryth had picked him up again. He had his rhythm back. 

\emph{Bless you, holy one!} he quietly praised her.

\drum{One two-and-three four-and-five. One two-and-three four-and-five.}

\emph{We must hold. Think of the brood. Think of the little ones and the eggs!}

The female resphan came back for yet another pass. She swooped near, her daemoniac talon-swords leaving a kind inky shadows behind where they swung, like blackened wounds of death in the fabric of the world itself. 
A soldier fell, head severed. 

Kepra kept drumming. 

\emph{Jach-dun. Jach-dun! Asheen!}

\drum{One two three-and-four five. One two three-and-four-and-five.}



\section{Concord}
Out of the corner of his eye Kepra just barely saw a third resphan swooping right at him, swinging some bladed weapon. On reflex he threw himself on the ground moments before the resphan's weapon clove his giant drum. 

He looked up from the ground. 
The resphan had flown past and was out of sight for the moment. 
But his bass drum was damaged now.
Without his drum, what could he do? 
He looked around. So many defenders had fallen. Tezoron Rarxan was down\dash{}perhaps killed. He could not see the other ward mage. 

Where was the hierophant? 

There.
His subconscious mind pulled his eyes to her. 

She had risen from the altar-throne.

The taloned female resphan was coming straight at her! 

What was Kepra to do? 

A part of him wanted to run. But an unseen force kept him there, kept him focused.

\emph{Remember Asheen. Duty. Service. Loyalty.} 
He was not sure whether the inner voice was his own or the hierophant's.

\emph{Think of the eggs.} 

That was his own inner voice.

The resphan dipped down to strike at the hierophant. 
Aeocryth dropped to the ground as a brave suchian warrior armed with sword and shield leapt to her defense. 
Aeocryth's eyes followed the warrior as he sprang, as if she was controlling his body.
%Aeocryth's eyes followed the warrior as he sprang, almost as if she was controlling him like a puppet.

The resphan kicked from above. 
The suchian warded off one hit with his shield. 
The resphan kicked again. 
This time the suchian warrior just barely parried the talon with his own sword but still took the blunt force of the blow. 
He fell to one knee with a grunt. 

Kepra looked around. 

\emph{Do something!}

Was this his own voice?

\emph{What can I do?}

His eyes scanned.

There. A gun. 

The resphan landed. She unsheathed a sword and strode towards Aeocryth and her defender, now with three blades ready. The unarmed hierophant backed away, eyes fixed on her assailant. 

Kepra picked up the gun. 

The battered suchian swordsman staggered forward to meet the resphan. 
Aeocryth gritted her teeth. 
Although the man's strength was almost spent, his eyes shone bright and fierce.
He raised his shield with a defiant cry of ``Zotha!''

Kepra fumbled to check the gun. 

The resphan kicked the warrior's shield aside with one talon. 
He stumble down on one knee again. 
Aeocryth hissed and clenched her fist.
The warrior tried to raise the shield again but failed. 
He held up his sword. 

The gun was loaded.

A talon lashed out. Blades clashed again. The suchian’s sword fell from his hand. Another talon thrust. This time the blade rammed through his skull. 
The resphan pulled back her foot and he slumped, half of his head gone.

The old cleric let slip a wordless yelp of terror.

\emph{How can I fight a foe like that?} thought Kepra. \emph{We are all going to die!}

The resphan took a step. Aeocryth took a step back. Her eyes locked on Kepra.

\emph{No! We cannot give up. We must live! Asheen! Jach-dun! Zotha!}

The resphan had the hierophant in her reach now.
Kepra raised his gun. 
The resphan raised her sword, focused on Aeocryth. 

Aeocryth breathed out. 

Kepra let Asheen and Zotha flow through him. 

Aeocryth bit down.

Kepra fired. 

At this point-blank range the bullet tore through the resphan’s wing. 
Bloody feathers scattered. 
She let out a snarl of outrage. 
She turned to face him. 
Her eyes drilled through him and transfixed him with terror. 
Those eyes seem to suck out his soul, like vortex tunnels to some horrific world of eternal blackness and death. 

Dimly he began to hear a monotonous droning noise in the distance.

Kepra's legs carried him a step forward. 

%Kepra feels Aeocryth’s powerful presence. 
\emph{Keep true.} 

That was definitely not Kepra's own inner voice. 
That was Aeocryth. 
Through the Concord she held his soul in a mighty grip, pouring her resolve into him.

\emph{Yes. Thank you, holy one.}

He would not break.
He would not succumb to fear.

The resphan advanced on him. 

The distant noise intensified.

He bared his teeth.

\emph{%
    I am a suchian. I am of the greater reptilian race. My race is of equal standing to that thing's. This is not a god but a monster. I will not cower before a monster.}

There were no more shots in the gun. 

Flight was unthinkable.

He raised the gun and stood his ground. Ready to meet the resphan with his bayonet. 

\emph{I will die, but at least I die a brave suchian. For the holy one!} 

The resphan was upon him.

The distant noise droned louder as if coming nearer.

``Asheen! Zotha!'' he cried. He thrust with the bayonet.

The resphan raised a foot and kicked with her talon twice, lightning fast. 
The first strike ripped the gun from his hands. 
The second whacked him in his left side. He groaned and fell to the ground on all fours. 

His left flank, shoulder and thigh were aching. 

Bruised. Not cut. 

It must have been a clumsy hit, perhaps with the flat of the blade. 

A strangled grunt from Aeocryth.

A gunshot barked from behind him, cutting through the droning sound. 
Another bullet struck the resphan’s wings, tearing free feathers and blood. 
Kepra turns his head. 

\emph{Sipel!} His fellow fount Hesca Sipel. She had also found a gun and fired at the resphan.

Sipel had a trance-like look on her face.
Like the music trance, but not quite.
Her eyes gleamed with a deep clarify and purpose.

Sipel charged with her bayonet. 

Kepra's self-preservation instincts kicked in and he rolled away just as the resphan kicked in direction. 
The talon bit into his robe and scales, but he got to keep his organs intact.
The resphan flapped her wings and leapt past him\dash{}her wings still strong despite the wounds. 
She kicked with one foot, then the other.
%Kepra's directionKepra a savage kick and strides past. She swings her sword. 
% It cuts clean through Sipel’s unarmoured body and she falls to the ground, dead where she stands. 
The talons impaled poor Sipel, then ripped out through her back. 
She crumpled in a bloody heap.

Aeocryth wailed behind him. 
Not in fear, but in anguish.
Sorrow. 

Perhaps even guilt.

Was this the same feeling that made her cry out before? Kepra had mistaken it for fear. Was it actually compassion, grief for her slain defenders?

\emph{No time to ponder!}

The resphan landed. 

Meanwhile Kepra had found his feet. 

His gun was out of reach now. 

The resphan turned to face him. 

Aeocryth snapped a brief growl.
Kepra drew his dagger. 

The droning sound swelled.

The resphan bore down on him yet again.
%The resphan turns around. She faces Kepra. 
%Again he feels a clutch of dread. His bruise ached, remembering their last clash. 

Kepra was aware of clutch of dread.
But it was dull, blurred. He was removed from it, as if swimming in water. 
Around him was the Concord. 
It was thick and warm. 
His limbs moved with it. 

His legs were Asheen. 
His hand was Zotha. 
%He reached out to the Concord. Sipel was dead or almost dead, but the Concord was still there. 
%Asheen and Zotha were there. The hierophant was there. 

No fear. 
No hesitation.
Only purpose.

Asheen took a step, placing Kepra's body between the hierophant and the resphan.

The droning was now thunder.

Zotha raised Kepra's hand and dagger. 

The resphan took a step and flicked her sword, then kicked. The first hit bashed away his weapon. The second stabbed into his side. 
She withdrew her foot and
Kepra fell on his snout. 

Asheen clenched. Zotha pulled. But Kepra's muscles did not obey.
%He was too weak now.
His body had no strength left.
He lay on the ground.
Blood poured out.

At this moment there rushed in a completely new sensation in the Concord. 
A colossal presence intruded upon his mind.
Where Aeocryth's touch had been focused, this was omnipresent, engulfing him and all of them.

A tidal wave of fire and fury. 

A storm of pure burning rage.

A consuming maelstrom of Zotha.

In the physical world, a roar from above split the air. 
A machine voice booming with Epitomes of vengeance and hatred.

And in the next moment, blasts of cannons. 

The resphan gave a start and snapped around to look up at the sky behind Kepra. 
Kepra's jaw and skull shook as the earth beneath him buckled from the impact of great lead balls smashing into the ground. 

The resphan kicked off and took flight. 

In agony, Kepra looked up. 

A vast shape soared above, made of dull metal and black-scaled flesh and burning Zotha. 
The rotors in its great metal wings droned like hurricanes. 
Mighty guns embedded in its body belched fire and lead upon the resphain. 
A great crocodilian mouth roared dreadful spellwords in Mystic Talaac, causing each bullet fired to hammer home as if carried on wings of righteous hate. 

\emph{Iscrafel.} 

\emph{Exalted Lord Quessanth Iscrafel.} 

\emph{The Dragonlord is come.}

%Kepra’s blood poured onto the ground as he watched in a daze.
%as he watched awestruck.
% 
% The resphan is there, with two fellows. 
% They charge the dragon. 
% Iscrafel fires his guns and tears through one. 
% The resphan falls with an injured wing. 
% The other two falter, but they have only a moment before Iscrafel is upon them. 
% The dragon lashes out with an enormous blade embedded in his metallic arm. 
% An explosion of sparks erupt as the resphan’s armour and wards burst. 
% He falls to the ground in two pieces. 
% The other resphan turns tail and runs, but not fast enough. 
% In a barbaric move the Dragonlord seizes the resphan in his jaws. 
% The resphan has only a moment to struggle before Iscrafel impales him on his vast sword-like blade. 
% 
% He watched in a daze as the resphan and her two fellows charged the dragon. 

\section{Exalted}
Kepra’s blood pours onto the ground as he watches in a daze.

The resphan and her two fellows charge the dragon. 
Iscrafel fires his guns and tears through one. 
The other two falter.
%For one instant. 
A blink of an eye.
Then Iscrafel is upon them. 
The dragon lashes out with an enormous blade embedded in his metallic arm. 
% Iscrafel closes and lashes out with an enormous blade embedded in his metallic arm. 
An explosion of sparks erupt as a resphan’s armour and wards shatter before the Juggernaut’s fury. 
The resphan falls to the ground in two bleeding pieces. 
The other resphan turns tail and flees. 
Not fast enough. 
In a savage bestial move the Dragonlord seizes the resphan in his jaws, then impales it on his vast sword-like blade. 

Kepra’s vision blurs. 
The pain fades away, replaced by numbness.

\emph{We are saved. Lord Iscrafel is come.}

\emph{We have done it. We held out. We kept the hierophant safe.}

The roar of the dragon’s metal wings fades. 

\emph{I was able to protect her.}

\emph{I held true to the Epitomes.}

\emph{Asheen.}

\emph{Zotha.}

Kepra’s vision goes black. 

No pain. 

Just numbness. 

Darkness.

Nothingness.



%\section{Nothingness}
% {``\sc{Live.}''}
\sectionbreak
{\Large{``{LIVE.}''}}


\sectionbreak
One word booms through Kepra’s senseless emptiness. 

A one-word imperative.

Mystic Talaac.

A spellword.

Spoken in a loud, metallic baritone. 

%\sectionbreak
Pain returns. 

His head feels pounded with hammers. 

His body burns. 

His limbs spin and tingle. %, but they are too weak to move. 

His body and mind obey the command of the spellword. 

He lives.



\section{Life}
%Kepra's body burned in agony for what seemed like forever. 

After a time\dash{}he had no idea how long\dash{}Kepra opened his eyes. 
The weak evening light felt blinding. 

The first face he saw was the gentle Aeocryth. 

``You live!'' said Aeocryth with a beaming smile. 

Looming over them was a gigantic black-scaled and metallic form.

\emph{Iscrafel.}

% Iscrafel is clad only in his lesser body now\dash{}half machine and hugely massive, but still suchian-sized, unlike his Draconian greater body. 

% Black-scaled Iscrafel gives a toothy smile. 
%The Dragonlord gave a toothy smile.

Kepra still felt battered and dazed, but he could tell that his body was slowly recovering now. 
%He can tell he’s recovering. 
He struggled onto all fours. 

``Exalted Lord Iscrafel.'' Kepra croaked. ``Hierophant Aeocryth.''

``Rest, brave fount,'' said Aeocryth. ``What is your name?''

Kepra could not help noticing how the old cleric's hand was softly caressing Lord Iscrafel’s giant metal claw.

``Filima Kepra, holy one.'' 

Iscrafel bent down and touched Kepra's shoulder with a heavy bladed claw. 
He gave a toothy grin.
``You have my thanks, Filima,'' rumbled his metallic voice. ``My beloved Aeocryth would have died if not for you. You are a brave warrior.'' 

``I am no warrior, Exalted Lord. I am a drummer.''

Iscrafel laughed out loud. ``Hah! Excellent! Then you are a brave drummer, Filima!'' 

Kepra turned to Aeocryth. 
To him, she was as awesome as an Exalted One. 
%She had kept him from disgracing himself.
She had saved him from the abyss of terror. 
Multiple times he had almost broken, and every time she had been here.
She had taken his hand and pulled him from the clutch of fear, guided him back to Asheen and Zotha and shown him his purpose.
%Delivered him from disgrace and back to virtue. 
When he veered towards disgrace she led him to virtue.

Salvation.

%He would never forget that. 
Under her benevolent eye he felt safe from corruption, safe from sin. Safe as an egg.

``Did you heal me, holy one?''

``No. Lord Iscrafel did.'' She laughed softly. 
``For some reason this part never sticks to his reputation, but he is actually an excellent healer.''
%Well, as long as it’s something that doesn’t require complicated medicine. Anything that can be healed with brute force.'' 

Kepra rose onto two feet. He looked around. 
The bodies of defenders were strewn all around. 
Few had been as lucky as him. 
%lucky enough that they could be healed. 
In fact, few of anything remained alive. 

In the distance he thought he could hear the footsteps of the fleeing resphan army. 

``Where is your army, Exalted Lord?''

%``Army?'' 
Iscrafel raised an eyebrow\dash{}one of the fleshy parts of his face.

It dawned on Kepra. 

\emph{%
    There is no army. There never was. The order was not ``hold until we come''. It was ``hold until I come''.%
}

He pictured thousands of humans fleeing before the dragon.

Iscrafel grinned again, apparently guessing his thoughts. 
``You did well, Filima. You all did well. Many fell, but no one broke. Despite the resphain's sorcerous attempts to cow you, you held. With Zotha and Asheen in heart, you held. The battle of Cressax is won.''



\section{Zotha}
``I hate it, Quessanth,'' said Aeocryth. ``Having others die for me.''

Iscrafel heard her and said nothing. 

The two were alone on the battlements; the soldiers and founts were resting or tending the wounded.
Iscrafel was clad only in his lesser body now\dash{}half machine and hugely massive, but still suchian-sized, unlike his Draconian greater body. 

``And I hate puppeteering!'' she continued. 
``I had to forcibly \emph{drag} three suchians between me and that resphan. Two of them got killed. I killed them. We only barely saved the third. And feeling each of them die was worse than if I had just taken the blow myself!''

Iscrafel gazed out over the battlefield beyond the walls as he listened. 
%His metal claws idly scraped on the walls.
He remained silent. 

%``At times I wished I had never become a hierophant. 
``You should not have told them to protect me `at all costs'!''

He turned to look her in the eyes.
``Yes, I should. You are more important than all of them.''

``No, I am not!''

``Of course you are. Not just to me, but to suchian-kind.''

Now it was her turn to be silent. 

``We need you. Zotha needs you,'' said Iscrafel.

Aeocryth hesitated. She nodded slowly. ``Aye,'' she whispered. ``Zotha.''

``You did well. You kept them together. Even those humans. You are one of the best hierophants we have. Better than some Mysteriarchs.''

She sighed. 
``I will never be a Mysteriarch. At times I wished I had never even become a hierophant.'' 
She whirled on him. 
``And I will not let myself grow numb to death as you have, Quessanth!'' 

He smiled, more softly now. ``Good. Agreed. I will do the killing so that you may do the healing.''

She turned away. ``I wish it were that simple, Quessanth.''

``We always do, Aeocryth. We always do.''








\newpage
\appendix
\section{Pronunciation Guide}
% Pronunciation is given in both IPA (International Phonetic Alphabet) and my own makeshift phonetics. 
Some notes about my home-made phonetics: 
[CH] is like in German \pex{ach}. 
[KH] is like in German \pex{ich}. 
% [ZH] is like the \lett{SI} in English \pex{vision}. 
[DH] is as in English \pex{this}. 
[Ä] is as in \pex{cat}.
[EI] is as in \pex{say}.
[AI] is as in \pex{sigh}.    

\begin{pronunciationenvironment}{
%   \section{Wordlist}
}
  \pitem{Aeocryth}{}{EI-o-krith}
  \pitem{Asheen}{}{ä-SHEEN}
  \pitem{Belraphon}{}{BEL-ra-fon}
  \pitem{Cressax}{}{KRES-säks}
  \pitem{Druzcalacht}{}{DROOZ-kä-laacht}
  \pitem{Felgian}{}{FEL-gee-an}
  \pitem{Filima}{}{FIL-i-ma}
  \pitem{Kepra}{}{KEP-raa}
  \pitem{Insharrad}{}{in-SHAAR-raad}
  \pitem{Iscrafel}{}{IS-kra-fel}
  \pitem{Jach-dun}{}{jaach-DOON}
  \pitem{Kelesh}{}{ke-LESH}
  \pitem{resphain}{}{RES-fain}
  \pitem{resphan}{}{RES-fän}
  \pitem{Quessanth}{}{KWES-saanth}
  \pitem{Rystessakhin}{}{ris-TES-ä-kheen}
  \pitem{Saphyr}{}{sä-FEER}
  \pitem{scatha}{[''ska:Da] or [''ska:Ta]}{SKAA-dha or SKAA-tha}
  \pitem{scathae}{[''ska:DEI] or [''ska:TEI]}{SKAA-dhei or SKAA-thei}
  \pitem{Sipel}{}{si-PEL}
  \pitem{suchian}{}{SOO-kee-an}
  \pitem{Suthalba}{}{SOO-thäl-bä}
  \pitem{Talaac}{[tæla:k]}{tä-LAAK}
  \pitem{Tezoron}{}{TEZ-o-ron}
  \pitem{Zotha}{}{ZO-tha}
\end{pronunciationenvironment}









% \section{Glossary}
% \begin{gloss}
% 
% 
% 
% \begin{comment}
% \paragraph{Arcanum}
% \end{comment}
% \gitem[Arcana]{Arcanum}
% \target{Arcanum}
% Generic term for mystic secrets or teachings to be studied and internalized. 
% Curricula in magic are often organized as a series of Arcana.  
% 
% 
% 
% \begin{comment}
% \paragraph{\daemon}
% \end{comment}
% \gitem[\daemons]{\daemon}
% \target{Daemon}
% \target{Daemons}
% Incorporeal entities that dwell in the Beyond. 
% Believed to be mostly mindless. 
% 
% 
% 
% 
% \begin{comment}
% \paragraph{\human}
% \end{comment}
% \gitem{\human}
% \target{Human}
% A \maybehs{humanoid} race. 
% One of the most widespread humanoid races on \Miith{}, alongside the \scathae. 
% Founders and rulers of the \VaimonCaliphate. 
% 
% 
% 
% \begin{comment}
% \subsection{\iquin}
% \end{comment}
% \gitem{\iquin}
% \index{Light}
% \target{Iquin}
% \target{Light}
% The force of Light in \hs{Vaimon} metaphysics. 
% By the \hs{Iquinian Church} viewed as the source of all good and worshipped as a divine force. 
% 
% 
% 
% \begin{comment}
% \paragraph{\Iquinian Church}
% \end{comment}
% \gitem{\Iquinian Church}
% \target{Iquinian Church}
% \target{Iquinian}
% A Vaimon religion based around the worship of \hr{Iquin}{\Iquin}. 
% 
% 
% 
% \begin{comment}
% \paragraph{Isxae}
% \end{comment}
% \gitem{\Isxae}
% \target{Isxae}
% \Ortaican goddess of law and rulership.
% 
% 
% 
% \begin{comment}
% \subsection{\itzach}
% \end{comment}
% \gitem{\Itzach}
% \target{Itzach}
% The force of Darkness in \hs{Vaimon} metaphysics. 
% By the \hs{Iquinian Church} reviled as the source of all evil. 
% 
% 
% 
% \begin{comment}
% \paragraph{mosca}
% \end{comment}
% \gitem{mosca}
% \target{Mosca}
% A large lizard. 
% Eaten in some cultures as a delicacy.
% 
% 
% 
% \begin{comment}
% \paragraph{Kush}
% \end{comment}
% \gitem{Kush}
% \target{Kush}
% A pre-\scathaese civilization. 
% Its language\dash written in a unique sinuous script\dash is still used in some spells. 
% 
% 
% 
% \begin{comment}
% \paragraph{Nasshikerr}
% \end{comment}
% \gitem{\Nasshikerr}
% \target{Nasshikerr}
% \Ortaican goddess of shadows and the hidden.
% 
% 
% 
% \begin{comment}
% \paragraph{\Ortaica}
% \end{comment}
% \gitem{\Ortaica}
% \target{Ortaica}
% A great \hr{Scatha}{\scatha}-dominated realm that flourished after the fall of the \maybehr{Vaimon Caliphate}{\VaimonCaliphate}. 
% 
% 
% 
% % \begin{comment}
% % \paragraph[Baccon]{\baccon}
% % \end{comment}
% % \gitem[\baccons]{\baccon}
% % \index{\bacconate}
% % \target{Bacconate}
% % A ruling council in certain (predominantly \scathaese{}) cultures. 
% % Typically aristocratic in nature. 
% % A realm ruled by a \baccon{} is called a \bacconate{}. 
% 
% 
% 
% \begin{comment}
% \paragraph{\rethyax}
% \end{comment}
% \gitem[\rethyaxes]{\rethyax}
% \target{Rethyax}
% A \hr{Scatha}{\scatha}-dominated order of mages, founded by the \maybehr{Ortaica}{\Ortaicans}. 
% 
% 
% 
% \begin{comment}
% \paragraph{\scatha}
% \end{comment}
% \gitem[\scathae]{\scatha}
% \target{Scatha}
% A race of reptilian \maybehs{humanoids}. 
% A \scatha{} resembles a bipedal dinosaur with a long, rigid tail. 
% They walk on straight legs and with a horizontal spine like bipedal dinosaurs, not with a vertical spine like \humans.
% An average adult is 170-180 cm tall or long. 
% They have tough scaly skin and are omnivorous. 
% 
% The \scathae{} are one of the most widespread humanoid races on \Miith{}, alongside \hr{Human}{\humans}. 
% 
% 
% 
% \begin{comment}
% \paragraph{Talaac}
% \end{comment}
% \gitem{Talaac}
% \index{Talaac}
% \index{Mystic Talaac}
% \target{Talaac}
% A language spoken by \dragons and some humanoids. 
% Written in a cuneiform script. 
% The arcane variant of the language, called Mystic Talaac, is used in many spells. 
% 
% 
% 
% \begin{comment}
% \paragraph{Vaimon}
% \end{comment}
% \gitem{Vaimon}
% \index{Vaimon}
% \target{Vaimon}
% \target{Vaimons}
% A \hr{Human}{\human}-dominated order of \maybehs{mages}.
% Their magic theory is based around the two forces of \hr{Iquin}{\iquin} and \hr{Itzach}{\itzach}. 
% Many Vaimons follow the \hr{Iquinian Church}{Iquinian} religion.
% 
% 
% 
% \begin{comment}
% \paragraph{\VaimonCaliphate}
% \end{comment}
% \gitem{\VaimonCaliphate}
% \target{Vaimon Caliphate}
% \index{\VaimonCaliphate}
% A \human-dominated theocratic empire ruled by the \hs{Vaimons}. 
% It existed from the year \yic{Founding of the Vaimon Caliphate}, where it was founded by \maybehs{Cordos Vaimon}, and until the \maybehr{Hundred Scourges}{\HundredScourges} in the year 	\yic{Hundred Scourges} where it fell, during the reign of \maybehr{Belzir}{\Belzir}. 
% 
% 
% 
% \begin{comment}
% \paragraph{Yormis}
% \end{comment}
% \gitem{\Yormis}
% \index{\Yormis}
% An \Ortaican city. 
% After the fall of \Ortaica \Yormis resisted all attempts at conquest and became a sovereign city-state. 
% It has a reputation as a city of black sorcerers. 











%\printindex









% \end{gloss}
\end{document}
