
\documentclass
  [a4paper,
   12pt,
   %openany,
   oneside
  ]%
  {article}





\include{Utilities/UsePackages}
\input{Commands}
\input{Hyphenation}




\title{The Amorphous God}



\stuffinthepreamble



\begin{document}



  \stuffatthebeginning
  \setcounter{page}{1}















\section*{Dramatis Personae}
\begin{dramatispersonae}
  \dramitemnoyear{Suthis Mephilex}{\scatha}{\female}, 
    apprentice sorceress
  \dramitemnoyear{Suthis Dristan}{\scatha}{\male}, 
    apprentice sorcerer, Mephilex's cousin
  \dramitemnoyear{Suthis Cruan}{\scatha}{\male}, 
    master sorcerer, Mephilex's grandfather
  \dramitemnoyear{Jaslar Thul}{\scatha}{\female}, 
    sorceress
\end{dramatispersonae}















\section{The Birthright}
Ever since my cousin died screaming and insane, I had been afraid. 

I am Suthis Mephilex. 
All my life I have dwelt under the roofs of the castle-city of \Yormis, where we \scathae rule\dash we, the reptilian folk\dash and where the only \humans are servants.%
\index{\human}%
\index{\scatha}%
\index{\Yormis}
As a daughter of nobles I am used to walk the halls in pride, but in those days I crept along casting fearful glances over my shoulder, for it seemed to me that a spectral horror stalked the ancient stone halls and corridors of my home city. 

As the descendant of a long line of \rethyax sorcerers, I was expected to master the occult arts myself. 
In my eighteen years of study I had passed through the first six Dreaded Gateways and mastered the six Lower \Arcana. 
I knew the secret names and rites of the gods. 
I had learned to hear the the \daemons howl in the Beyond, and to command them.%
\index{\daemon}
Now, with my eighteenth birthday, my time had come to be initiated into the Innermost \Arcana of the Suthis clan, the secrets that were my birthright. 
%No longer a mere apprentice, I was to learn the secrets that were my birthright, the secrets that would make me a true sorceress. 
%No longer would I be a mere apprentice and suffer the scorn of my rivals. 
I would be a true \rethyax sorceress.

Yet my scales shivered when I thought of the day I was to descend into the crypts beneath \Yormis for my initiation.
I dreaded what I might find.
For I thought about my cousin, Suthis Dristan. 
He had been my closest childhood friend, a wonderful \scatha and an expert apprentice. 
He faced his own initiation a few months before. 
I remembered the day I bid him farewell as the clan elders led him down into the dark and ancient catacombs beneath the towers of Clan Suthis; those crypts that were rumoured to predate \Yormis by millennia and to hold a whole subterranean city built by pre-\scathaese hands. 

I embraced him and wished him luck. 

That is my last good memory of him. 

%Dristan was never himself again. 
Some minds are too fragile to contain the dark secrets of the cosmos, the Higher \Arcana.
The revelations broke him.  
When they carried him back on a litter he was a wretch; screaming and frothing; thrashing his limbs and tail. 
He babbled about \quo{the horrid flesh}, about being filled with \quo{filth} and \quo{corruption}.

\hypota{The shapeless thing. 
  The devourer.
  Deep down below.
  Inside.
  Inside us all\prikker}

I only caught glimpses of him before they shooed me away. 
% They shooed me away, fearing what the sight of him would do to me in my impressionable state. 
I was forbidden to know what had happened below. 
I could only speculate that Dristan's mind had wandered too far Beyond and encountered a hostile entity that invaded and broke his mind. 

Dristan died the next day. 
I will always remember the grief of that day. 
Grief became nausea, and I could barely keep my food down. 
I remember that my grandfather\dash Suthis Cruan, the clan leader\dash had the servants prepare a special delicacy for me\dash mosca flesh\dash and that I tried to vain to appreciate it. 

I had lost loved ones before.
My mother had fallen in war when I was young, and I had seen my aunt slain before my eyes in a duel with a \scatha of Clan Jaslar, our rivals.%
\index{\scatha}
Neither could compare with the horror of Dristan's madness. 
It also made me fear for myself, for Dristan had been every bit as strong-willed and talented as I. 
Would I die screaming as he had?

I did my best to control my apprehension as I went about my business. 
Dutifully I practiced my spells and meditations. 
I ate the food and drank the elixirs I was given. 
They served me mosca flesh several times. 
%(A mosca, I believe, is a fat crawling reptile.)
It was something the clan elders sometimes ate, and I remembered Dristan had also been served it before his initiation. 
Mosca flesh was supposedly a delicacy, and in time I came to appreciate the taste of it, but never the weird squirming feeling in my stomach that it gave me. 
%It felt wrong and unnatural inside me, as if it crawled inside my stomach like a living thing. 
%I tried to decline it, but 
My family told me it was made especially for me. 
%I realized there was a meaning to this, but 
I knew better than to ask or argue. 

The elixirs were worse. 
I was not told how they were supposed to help me in my coming ordeal, but they certainly did affect my mind. 
Every time I had drunk that pink-gray viscous goo I would toss and turn with nightmares. 
In my dreams I was immersed in horrid slime\dash not water nor blood, but the essence of corruption and death. 
I suffocated, I drowned, I was absorbed. 
I felt it gnawing at the edges of my soul.
% Several times, when the corruption was about to consume me forever, 
I awoke gagging and gasping for air, and long after I could feel the corruption clinging to me. 
%My insides would roil and I would shiver with horror. 

In those weeks my nerves and health alike hung in tatters, and my enemies noticed my weakness.
Chief among them was Jaslar Thul. 
Clan enemies since the time we were eggs, Thul and I had fought throughout our childhood and youth. 
More than once she had taken my friends and poisoned them against me with her slander. 
I had hated her with all my heart. 

After word got out that Dristan's initiation had killed him, I knew that Thul and her cohorts would use it against me. 
%In my state I had not the strength to rally my own social circle against her, so I avoided her whenever possible, but I could not wholly hide from them. 
I wince to recall one day when I came upon them in a dark hallway. 
I had gone to see one of my tutors, alone save for a \human slave, when they cornered me.\index{\human} 
Thul lashed out with all her spite, mocking me and our clan for Dristan's failure. 
Their taunts cut twice as deep because I could no longer lean on my cousin for support, and Thul knew it. 

% In my state I could not fight them, only cower. 
% My nerves must have snapped under the attack, 
As I cowered under their assault, too weary to fight back, a fit of nausea suddenly washed over me. 
The food in my belly rose up in my throat, like a poison my body wanted to expel. 
My head ached and I faltered, leaning on the wall for support\dash and I recoiled, yelping in dismay. 
For when I touched the wall I felt not dusty stone but swamp and clammy muck. 
I looked down at my hand and saw my scales covered in wet filth, cold as death. 
Panic seized hold of me and I screamed and ran, the laughter of Thul's sycophants ringing in my ears. 

When I paused to look at my hand I found it dry and clean.
To this day I still do not know if what I saw and felt was hallucination or morbid truth. 
I told no one about it. 
I knew better than to show such weakness to anyone but Dristan. 
But I dreaded to face my initiation in such a state, for I felt that my mind could snap and spiral into madness any day. 

And the day loomed ever closer. 















\section{The Spawn of \Dragons}
Finally the day of my initiation came. 

I stood before the great metal doors that led down into the sepulchral underworld.
Beside me stood my grandfather, a few other elders and a handful of bodyguards armed with muskets and swords.
All trusted Suthis clansmen in the jade-green colours of our clan. 



My grandfather, Suthis Cruan, touched the lock on the massive door with the enchanted key talisman he carried around his neck.
He spoke the spellwords in the \draconian tongue of Mystic Talaac to activate the key:%
\index{Talaac}
\index{Mystic Talaac}
\ta{\tongue{Hebal kur haye-zudomach.}}
The lock came apart and my grandfather swung open the door. 
An eerie draught howled up from below to meet us, freezing my scales with the deathly cold from the underworld. 
For a moment I imagined that the floor quaked beneath me, as if a colossal formless power was stirring in the depths. 

Suthis Cruan led the way.
We descended, down flights of stairs that stretched on forever, until at last we came to another door. 

\ta{%
  In here is where you will face your initiation, Mephilex,} said my grandfather.
\ta{% 
  Here you will learn three \Arcana of Clan Suthis:
  The \Arcanum of the Master, the \Arcanum of the Flesh and the \Arcanum of the Soul.
  Here, take this scroll.
  You will need the spells inscribed hereon.
  Keep it safe, and do not open it until it is time.}

I nodded and took the scroll. 

He unlocked and opened the second door.
I stepped through.

And I gaped and stared. 
Before me, lit by faintly glowing red gemstones embedded in the rock, stretched an immeasurably vast subterranean chamber. 
 
The stories of an underground city were true. 

There were pillars twenty feet wide and perhaps a hundred feet tall. 
There broken pedestals, rotted doors, crumbled passages, withered and faceless statues. 
I could see no living creatures but ourselves. 
A wind of death blew through the ruins. 

This was the corpse of a city. 

Remembering the rumours that the crypts existed long before the city above was built, I felt the oppressive weight of tens of thousands of years crushing me down. 
I almost felt the eyes of a thousand generations of the dead upon me.

They led me on through the city of the dead.
As we walked I could hear my grandfather and the others talking quietly. 
Politics.
Tension was high in these days between Clans Suthis and Jaslar. 
Either clan was ready to resort to assassination any day now. 

\ta{We need to get back soon and make our plans,} I heard one of my uncles say.

\ta{Yes,} said my grandfather. 
\ta{But right now our first priority is Mephilex.
  We will need her soon\prikker}

I almost flinched, feeling the pressure of his expectation.
Again I imagined the eyes of a million mummified ancestors staring down from their hidden niches in the walls above. 
I felt those stares drilling into me, judging me. 
% % I faltered. 
% % It took all my self-control to keep from running away.

As my eyes adjusted to the darkness, more than once I thought I saw distant furtive shapes slinking through the gloom.
They were like \scathae, with arms and legs and tails, and yet hideously different.%
\index{\scatha}
The stiffness of their legs and the snake-like fluidity of their tails filled me with loathing.
I looked away. 

\ta{%
  Fear them not, Mephilex,} said one of my cousins.
\ta{They will not harm you.}

\ta{Father\prikker} I croaked. 
% I drew myself up and asked: 
\ta{What is this place?}

\ta{This is the heart of \Yormis,} said my grandfather.
\index{\Yormis}
He spread wide his arms.
\ta{These pillars have stood for thousands of years before the city above was raised. 
  It is the true \Yormis. 
  The city of the Master.} 

% A hush of awe fell over our party at the mention of that name. 

\ta{The Master?} 

\ta{The Master is the lord of the underworld.
  He is the true ruler of \Yormis.}

And as we walked on, my grandfather told me about the Master. 
He told me of the antediluvian ages when the Master's people reigned.
For the Master was not a \scatha like us but the scion of an elder and superior reptilian race.%
\index{\scatha}
Long before the \humans founded their \VaimonCaliphate\dash indeed, before the \humans existed, before even the \scatha race existed, this city stood.%
\index{\human}%
\index{\VaimonCaliphate}
It was built by the founder race, called the \ophidians by some.
They were the spawn of \dragons and the progenitors of the \scathae.%
\index{\dragon}
For uncounted millennia they ruled \Miith, using their mighty arts to reshape mountains and seas and even life itself. 

Then came a terrible foe, an evil from the black void of the Beyond, bringing a tremendous war that destroyed their nations and empires of the master race.
Now they were few in number, their once glorious cities reduced to ruins like this.
They were driven underground, and for a million years the Master and his brethren have dwelt in darkness. 
But their power still lived on. 
Deep down in his terrible tomb the Master still lived.
And they all served him.
Not only Clan Suthis, but Jaslar, Vrael, Torshen, Kish and all the major clans of \Yormis.
Fight though we might in the city above, in secret we all owed our allegiance to the Master of \Yormis. 

I began to understand what I was seeing around me, and my awe deepened. 
In the stone blocks and arches I recognized the legacy of those mighty lords of the antediluvian world. 
I saw how the vastness of their works reflected the magnitude of the elder beings themselves. 
I felt the wing-beat of a million years of history in those twining reliefs of \dragons and serpents now faint on the columns.\index{\dragon}

I looked up at my grandfather.
\ta{And I\prikker?}

\ta{And you too, dear daughter, will serve the Master. 
  He waits for you in the deeper levels below. 
  Very soon you will meet him, and you will know the \Arcanum of the Master.}

\ta{Yes, grandfather.}

\ta{And then you will meet another, mightier than even he.
  A hidden one, older and greater than this world.
  But that is for later.}

We walked on in silence. 
I shuddered to think of the terrible might of the elder race. 
I felt small and weak in this immense necropolis that brooded over me, each stone whispering its tale of lost glory and decay and sleeping malice. 

I wanted to learn more. 

I wanted to see this Master. 









\section{The Natural Order}
We entered a domed temple with twisting, snaking pillars. 
Inside were seats and tables. 
% The building showed some signs of habitation by the living.
I guessed that this was a place where the servants of the Master came.

\ta{This is the temple of \UzulKaya. Here we will rest,} said my grandfather.\index{\UzulKaya}
The servants set out food and drinks on the table: 
More mosca flesh, and more of that viscous elixir. 

On the walls were inscriptions.
They appeared to be written in the occult tongue of Kush. 
I understood no Kush, but from books I recognized the sinuous script\dash wholly unlike regular \Ortaican letters or the cuneiform of Talaac.\index{Kush}\index{\Ortaican}\index{Talaac}

\ta{Before you meet the Master, I will tell you about one more thing,} said my grandfather.
\ta{About the \Arcanum of the Flesh.
  I know you have wondered why we have been feeding you mosca flesh.
  I will tell you.
  Clan Suthis has thrived because we let nothing go to waste. 
  Not our gold, not our knowledge, and not our people.
  I know you loved your cousin Dristan dearly. 
  Take comfort in this: He did not die in vain.}

\ta{What?} said I.

\ta{You will understand soon.
  You know that the Vaimon religion teaches that the soul is everything, and that the body is but a vain garment. 
%   Dirt and dust. 
  You also know that the Vaimon religion is false.\index{Vaimon}
  The \humans are wrong.%
  \index{\human}
  There is power in flesh and blood. 
  Power that endures beyond death, and which can be passed on.
  Thus all life feeds on death. 
%   All greatness is built on rape and destruction. 
  We are all vampires, parasites. 
  This is the natural order: 
  Beasts feed on plants, and humanoids feed on beasts.}

While he talked I saw another of our party labouring with a key talisman to unlock a great door on the wall opposite the entrance. 

My grandfather continued:
\ta{%
  The \human tribesmen of the jungles outside \Yormis believe that by eating the hearts of their enemies they gain their strength and courage.%
  \index{\Yormis}
  In this the savages are wiser than their learned Vaimon kinsmen.%
  \index{Vaimon}
  Their crude practices are based on a core of truth. 
  With the aid of higher arts the adept can wrest from the flesh its secrets and make its power his own.}

My stomach began to churn. 
I felt as if the food inside me was alive and crawling. 
I remembered Dristan's ravings about \quo{the horrid flesh}, and about being \quo{filled with corruption}. 

\ta{So\prikker grandfather\prikker are you saying that\prikker this mosca flesh\prikker?}

\ta{%
  Each one of us has his part to play, for the greater and purer the subject, the more potent its flesh. 
  The food becomes the body. 
  By consuming that which is strong and pure, the adept becomes himself strong and pure.
  We have learned to recognize such purity and select for it. 
  For the greatest nourishment is found in consuming the vitality of those which are like oneself. 
  By feeding on kin.} 

I sat motionless, held by tentacles of cold dread. 
I struggled against the revelation. 
\ta{But\prikker the mosca\prikker?}

\ta{Come, now, Mephilex. 
  You have already guessed the truth.
  The flesh you ate did not come from a mosca.}

\tho{No\prikker}

A new wave of nausea swept up in me.
I felt my body rebelling, wanting to expel the taint inside. 

\tho{No\prikker}

\ta{You have fed me\prikker \scatha flesh?}%
\index{\scatha}

\ta{Not just any \scatha. 
  Only those bred for strength and purity. 
  Some were always meant to serve as food for their betters.
  Others were meant for greater things, but were halted by unfortunate circumstances and ended up serving in the only way they could.}

% The blood froze to ice in my veins. 
\tho{This cannot be true.
  Tell me this is not true.}

My grandfather's voice became softer. 
\ta{Mephilex,} he said with sad compassion, 
\ta{I know you miss Dristan.
  He was a great \scatha and would have been a formidable sorcerer.
  We are all sad to have lost him.
  But Dristan did not live and die in vain.
  He is still part of our clan and bloodline.
  This way his soul and potential lives on\prikker}

Tears welled up in my eyes and bile in my throat.
Again I had to fight the urge to vomit. 
I thought I could feel Dristan's ghost oozing through my veins.
Whispering to me.

My grandfather rose and came over to me. 
He put his arm around my shoulders.
\ta{Dear Mephilex\prikker}

\ta{Is this what killed Dristan?} I said. 
\ta{This \Arcanum?}

\ta{No. 
  Dristan accepted the \Arcanum of the Flesh, and that of the Master.}
His voice became distant, melancholic.
\ta{It was the third \Arcanum that broke him.
  What he learned deeper down\prikker}

%He paused. 
\ta{I know this is frightening to you, Mephilex. 
  Understand that this is what Dristan would have wanted.
  Dristan was our prime scion, and now that mantle has passed to you.
%   His essence is yours now.
  He is still with you.
  I hope you will learn to take comfort in that.
  I know you relied on your cousin for support.
  He can still provide that, if you will let him.
  If only you\prikker}

The sound of a gunshot ripped through the air.

Suthis Cruan gasped. 
His eyes widened.
He grimaced in pain and shock. 

I screamed. 









\section{The Name}
Muskets sounded from all around. 
Our soldiers scrambled for cover and pulled out their weapons. 
\ta{It's the Jaslars!} one yelled.

I fled under the table. 

Suthis Cruan fell to the ground beside me, bleeding from wounds in his back and flanks where bullets had torn through his scales. 
Convulsing in the pains of death he found the strength to hold out his key talisman to me. 
He looked me in the eyes and croaked one last word:

\hypota{Flee.}

All hell had broken loose.
Assailants fired at us from the shadows behind the pillars and balconies. 
They must have snuck in under cover of sorcery.
I cowered under the table, hidden behind an overturned divan and my grandfather's body. 
The thought struck me that perhaps I survived only because my grandfather shielded me with his body. 
He had risen to comfort me, and that ended up saving my life.

Soon, as the combatants emptied their firearms, the sounds of gunfire ceased and 
instead I heard the rustle of swords.
% and the cries of the dead and wounded. 
Peeking out I saw only few green-clad Suthis warriors still standing. 
The purple-clad Jaslars were swarming them. 

I knew I could not sit and wait. 
My grandfather was right. 
I had to flee.

The fray lay between me and the main door. 
It was the only exit I knew. 
But then I noticed another door behind me. 
It was the one that my uncle had been unlocking while my grandfather had told his story. 
Now it stood ajar. 
I did not know where it led, but it was the best chance I had. 

I ran for the door. 

I heard a voice behind me shout:
\ta{There she is! Mephilex!}

The voice stuck me like needles. 
I recognized that hated voice anywhere.
It was Jaslar Thul.
A part of me wanted to turn around and charge her with my dagger, consequences be damned.
But I ran on.

As I reached the door I heard another voice yell: 
\ta{Thul! Go after her!} 
Then I dove through the opening and into a narrow and dimly lit corridor. 

From behind came the tramps of pursuing feet and Jaslar Thul's voice: 
\ta{Coward, Mephilex! Stand and fight!}

I knew I could not fight them. 
I was still an apprentice. 
My magic was weak, for I had made no pacts yet with any gods.
Thul, a year older, was a full-fledged mage. 
She alone could crush me in a fight, and she had armed soldiers with her. 
I could only flee.

So I ran down through the tunnel.

The tunnel was dimly lit by those red jewels. 
I know not how long or how far I ran. 
More than once I came to a fork and chose a random direction.
At one point I noticed writing on the tunnel ceiling above me. 
It was written not in regular ortaican script but in Talaac cuneiform.%
\index{Talaac}%
\index{\Ortaican}
I forgot the full text, but one mysterious word stuck in my mind: 
\quo{\emph{\Ubloth{}}}.

\emph{\Ubloth{}}? 
What a hideous word, I thought. 

A bitter smell wafted up from the corridor ahead.

Then I was struck by a sudden spell of weakness.
My stomach turned, my vision blurred and I had to lean on the tunnel wall to keep from collapsing.
I expected to find solid dry stone, but to my horror the wall gave way like mud! 
My hand sank in. 
I pulled my hand away and found it wet with sticky slime. 

I forced myself to keep running even though my head spun and my stomach hurt. 
For some reason the name \emph{\Ubloth} haunted my thoughts. 
A vague unnamed dread dripped from it.

\emph{DOOM.}
\emph{DOOM.}

I began to feel those tremours again.
As if some gargantuan creature were tossing in its sleep deep below.

\emph{DOOM.} 
\emph{DOOM.}

My head was being hammered by those reverberations from below. 
I knew I could not keep running for long, not in this state. 
My pursuers were gaining on me. 
I had to find somewhere to hide. 

The tunnel had widened, and in a niche in the wall I came upon a statue of a corpulent \scatha resting on a divan.%
\index{\scatha}
I crawled behind the statue and crouched down in a small space underneath its tail.
It was cramped and painful, but I am a small \scatha. 

I wove a quick spell of concealment about myself:
\ta{Merciful \Nasshikerr,} I intoned in the melodious spellwords of Mystic Talaac, 
\ta{stretch out thy hand and shield me from my enemies' eyes.}%
\index{\Nasshikerr}
I had no pact with \Nasshikerr, goddess of shadows and the hidden, so I could only hope my spell would have some effect. 

As the booming subsided I could hear my pursuers approach.

\ta{This place makes me sick,} said a voice.
\ta{Is it true that some giant horror stalks these deeps?}

The next voice was that of Jaslar Thul.
\ta{You are thinking of the stories of Clan Suthis's hidden god. 
  \Ubloth.} 

The sound of that name hammered against my head, and I had to clamp my mouth shut lest I cry out in pain.
\tho{Hidden god? Is that what \Ubloth is?}

\ta{It does not \quo{stalk},} said Thul
\ta{It will not come for us.
  We need not fear it.} 

\ta{If you say so, \Miss Thul.} 

While I lay waiting for them to be gone, I pondered their words.
The hidden god? 
Were they talking about the Master? 
No. 
My grandfather had said that the Jaslars also served the Master, and Thul had said \quo{Clan Suthis's hidden god}.
Was this some other entity?
What was it my grandfather had said? 
That there was another, a hidden one.

\tho{What is \Ubloth? Or who?}









\section{The Effluvium}
When I was sure they were gone I snuck out and hobbled the other way, my joints aching with cramps. 
I took a different turn and found a wooden door. 
I tried my grandfather's key talisman and the Talaac spell he had used: 
\ta{\tongue{Hebal kur haye-zudomach.}}
It worked. 
The door recognized me as a Suthis and opened for me. 

I found myself in a room full of cauldrons, vials, jars, scrolls and animal bones\dash evidently a mage's laboratory. 
There was a door at the far end, perhaps thirty feet away. 
I was about to through the room when a familiar smell caught my attention. 
It was the same bitter smell as those elixirs my family had made me drink, only much stronger.  

I looked around and recognized flasks of familiar pink-gray goo on a table.
Next to the table was a great vat full of thick gray slime, from which the smell arose. 
My curiosity pickled, I went to take a closer look.

The stuff in the vat looked similar to the elixirs, only more viscous.
On the table with the flasks lay an open book and many scattered sheets of paper. 
Some of the papers were again written in the mysterious Kush.%
\index{Kush}
The book\dash written in normal \Ortaican\dash showed a section with the heading \quo{\emph{Formula for Distilling Elixir of Purity}}.%
\index{\Ortaican}
The word \quo{purity} made me shiver as it brought to mind my grandfather's terrible words. 
Scanning the page I found a list of ingredients and instructions. 
It mentioned something called the \quo{effluvium of \Ubloth}, which I gathered must be the thick gray ooze in the vat. 

I tried to make sense of all this.
Was \Ubloth the hidden god that my grandfather had mentioned? 
What kind of god exudes slime like this? 
And worse yet: 
Had I been drinking it? 

\tho{Merciful gods, I have been drinking it!}

As I realized this, the vague eeriness of it all thickened into a much more intimate horror. 
The tub of ooze was suddenly a dark mirror into my own tainted body and soul.
I turned away but found no escape. 
Everywhere I looked I saw a new looming menace. 
Every flask and jar and bone was a blade that lay in wait to pierce my flesh with its venom. 

The words I had gleaned from the book flashed before my eyes:
\emph{%
  Purification\prikker 
  the distilled essence of \Ubloth\prikker 
  the \nexus transcends flesh, transcends bodies, transcends generations\prikker
  bound in flesh and spirit\prikker 
  the soul of \Ubloth\prikker}

\emph{\Ubloth.}

I had to get out. 
I fled out of the laboratory, back into the tunnel from which I came. 
I doubled over with nausea as I felt my stomach turning again.
Before, panic had driven the thought of Dristan from my mind. 
Now it returned. 
Now I could feel him boiling inside me again. 
I had eaten my cousin's flesh.
And I had drunk this \quo{effluvium}.
What had they done to me?
Why? 
Was this the awful secret of Clan Suthis?
The third \Arcanum?
The \Arcanum of the Soul?

\emph{\Ubloth.}

My vision blurred. 
In my mind I saw that tub of gray slime. 
No, no longer a tub. 
A lake. 
An ocean. 
An endless sea of slime that drowned the world. 
I was back in my nightmare from before, now more intense than ever. 
As I descended into that mass of rot and death and decay, I could discern its components.
I saw that it was composed of the souls of the dead. 
A throng of damned and tormented mindless souls. 
A mass of blind eyes and a multitude of mute and gaping, sucking mouths.

I remembered my grandfather's words: 
\hypota{The food becomes the body.}

And I remembered Dristan's ravings: 
\hypota{The shapeless thing. 
  The devourer.
  Deep down below.
  Inside.
  Inside us all\prikker}

Dristan continued: 
\tele{There is no escaping it.}
Now I did not know if I was hearing my memory or if Dristan's ghost was actually talking to me.
I had long lost track of what was vision and what was reality.

In my vision I sank deeper into the endless sea of slime. 
The mute souls groped at me, and all the while Dristan's voice droned on: 
\tele{There is no escaping the corruption.
  It becomes one with you. 
  It consumes you from within. 
  Once you drink its ichor, it owns your soul. 
  Its soul is yours.
  You are part of its \nexus.
  \Ubloth.
  The hidden god. 
  The god beyond all earthly gods.
  Older than the world.
  The heart of the underworld. 
  The soul of the Suthis clan.
  We are bound to its\prikker}

\ta{\MakeUppercase{Stop}!} I cried. 

The voice fell quiet. 

The vision faded. 
I was back in the tunnel. 

For a brief instant everything was quiet.

Then a very real voice shouted. 

\ta{There she is! Get her!}









\section{The Dweller Beneath}
Down one end of the tunnel I saw a pair of armed Jaslars coming towards me. 
I turned around to run and saw even more purple-clad soldiers in the distance. 

I was surrounded. 
I had only one chance. 
I ran back into the laboratory and ran to the door at the other end where I stammered the key incantation. 
The door opened. 
I did not know how to lock these doors again, so I just I ran through.

I was in another dark stone corridor that sloped downward. 
The walls were coated in sticky slime and reeked of rot. 
I thought I was hallucinating again until I heard a voice cry out in loathing from behind: 
\ta{Erch! What is this?
  This place is smeared with some kind of goo!}

The tunnel was cruder than the previous ones; less like a carven corridor and more like a natural hole. 
If it was made by humanoids, I thought, it must be a hundred thousand years old. 

I met a few forks, and each time I took the road that looked most difficult, hoping that my enemies would guess I had taken the easy road. 
After the frist bend there were no more red-glowing jewels. 
The rest of the runnel was dark. 
Gradually the tunnel narrowed, and after a while I could no longer stand with my legs straight.%
\footnote{\Scathae normally walk on straight legs and with a horizontal spine like bipedal dinosaurs, not with a vertical spine like \humans.} 
Soon I was crawling on my knees in pitch darkness through an inch-thick layer of goo. 

\tho{Where is this slime coming from?} I thought.
\tho{What is down here?}

Dristan began to whisper: 
\tele{The dweller beneath.
  Once you drink its ichor, it owns your soul. 
  Its soul is yours\prikker}

Using all the concentration skills that my meditation training had given me, I repressed the voice. 
I refused to think about it. 

\tho{Just move.}

\tho{Move.}

\tho{Move.}

At long last the tunnel widened again. 
I could see light ahead. 
I crawled on, hopeful, and emerged into a cavern. 
A giant cavern, the ceiling above me almost as high as in the underground city. 
A faint pale gray light shone somewhere ahead, and I could hear bubbling and splashing sounds as if from a seashore. 
I could not see the source of the light and sound for the great rocks that rose ahead, but the paths were clear to my left and right. 

My whole body hurt. 
I was covered in slime all over. 
My robe hang in tatters. 
I had bleeding wounds where some of my scales had been torn off. 
I needed to find a place to hide and rest, just for a while.
I stumbled on and found a cluster of large rocks with a hole in it.
I crept into this hole. 

From my hiding-place I could see the cavern roof above. 
The dead gray light cast eerie shapes on the roof as it pulsated in rhythm with the splashing water. 

The voice droned in my head again. 
I had no strength to repress it. 

\tele{%
  It is here. 
  The devourer.
  The god beyond gods.
  The heart of the underworld. 
  The fountain of corruption. 
  The soul of Clan Suthis.}

I wanted to repress the voice, but I no longer had the strength.

\tele{%
  It owns your soul.
  Its soul is yours. 
  You have drunk its effluvium. 
  You are one with it, as are we all.
  There is no escape from the corruption.}

\tho{I don't understand}, I wanted to scream. 
\tho{What is \Ubloth?
  What is the point of it all?}

\tele{Its soul is yours\prikker}

\tho{I don't understand that! 
  What does it mean?
  What is the third \Arcanum?} 

\tele{The \Arcanum is in your grasp, Mephilex. 
  Use the key. 
  Use the spell.
  Use the scroll.}

Now I remembered: 
The scroll! 
The scroll my grandfather have given me!
I checked under my robe, and true enough, I still had it. 
I pulled it out. 
Though torn and slime-smeared it was still legible in parts. 
It was in Mystic Talaac. 
I began to read. 

\begin{diary}%
%   I pledge my soul to thee, \Ubloth.
%   My lifeblood is in thee, and thine essence is in me. 
%   I am one with thee. 
%   My soul is thine in this life and the next. 
%   Cleave unto me, great one, and grant me thy power. 
%   Feed me with strength as I pledge myself to feed thee in turn. 
%   My body and soul are one with thine, for I am Suthis. 
%   As thou gave birth to me so shall I return to thee, and as I return to thee so shalt thou give birth to me again. 
%   In this cycle is our clan sworn to thee forever. 
%   This is our covenant.
%   This is the pact which I now swear. 
%   Receive my soul and give me thine!
%   \Ubloth!
  \prikker my soul to thee, \Ubloth.
  My lifeblood\prikker thine essence is in me. 
  \prikker in this life and the next. 
  Cleave unto me\prikker thy power. 
  Feed me with\prikker to feed thee in turn. 
  My body and soul\prikker in thy \nexus, for I am Suthis. 
  As thou gave birth to\prikker I return to thee\prikker give birth to me again. 
  In this cycle is our clan\prikker 
  \prikker our covenant.
  \prikker the pact which I now swear. 
  Receive my soul and give me thine!
  \Ubloth!%
\end{diary}

Every word I could decipher was another tentacle of black dread that wormed inside my heart. 
What madness was I entangled in?
What was this awful god.
Why did my family serve it? 
Why did they want me to pledge myself to it? 
What would happen if I did?

Then once again my thoughts were interrupted by a shouting voice. 

\ta{In here! She must be in here!}
The voice boomed in the chamber, clear even above the crashing water. 

The Jaslars had found me. 

Then a scream. 

\ta{Great gods! 
  Mighty \Isxae preserve me!%
  \index{Isxae}
  What in the world is that?}

\ta{Great gods,} repeated a second voice that made me cringe with hatred. 
Jaslar Thul.
\ta{I\prikker I don't believe it. 
  I knew it existed, but I had not thought\prikker this\prikker 
  Merciful \Isxae\prikker merciful \Nasshikerr\prikker}%
\index{\Isxae}
\index{\Nasshikerr}

\tho{What? 
  What are they seeing?}

\ta{We can't fight this!} screamed one.
\ta{Run for your lives! 
  Run!} 

Curiosity grabbed hold of me and pulled me up from my hiding place. 
Perhaps I was insane, for even though I knew it was death if they saw me, I had a perverse need to know what they were seeing. 
Slowly, cautiously I crawled out of my hole, up into the pulsating light. 
I crawled up on a rock and peered out towards the centre of the cavern.

My breath froze in my lungs. 

There it lay. 

I must struggle for words to describe it. 
Colossal. 
Unimaginably vast\dash filling the entire cavern and more. 
Amorphous. 
A seething and bubbling pit of pure vileness and filth. 
An ocean of horrid pulpy flesh, with vast pseudopods like waves forming, rising and crashing. 
Glowing with a dead gray luminescence, its surface showing glimpses of silently screaming faces. 

Its size could not be measured. 
The cavern was perhaps a hundred feet across, but this thing was greater. 
It seemed to me that the thing was not \emph{in} the cavern, not even \emph{in the world}\dash rather, I thought, the monstrosity was a world ocean, and the world I knew was an island floating on its surface.
It was not merely in the cavern below. 
It was in the rocks, in the earth. 
Its horror permeated everything, oozed into everything. 
Nothing was beyond its taint. 

The god beyond gods. 

The heart of corruption. 
The heart of Clan Suthis. 

\tho{No.
  It cannot be this\prikker this abomination.}

Insanity held me in a grip, and I found myself climbing higher, closer. 
The loathsome mass below called to me, and I must answer.
I hated it. 
I longed for it. 

\ta{There she is!
  There on the rock!}

I glanced down and saw Jaslar Thul pointing at me.

\ta{Get her!
  Pull yourselves together.
  The slime is not going to eat you.
  Just keep your distance from it.
  Now go!}

The Jaslar soldiers overcame their horror and crept towards my perch with swords in hand, having long since discharged their guns. 

I looked around. 
I was surrounded. 
There was no way out.

I was dead. 

\tele{There is a way out,} said the voice.
\tele{Do what you came here to do.
  Complete your initiation.
  Make your pact.}

\tho{With that thing? No!}
And yet I must. 
For I understood that whether I wanted it or not, I was already bound to it. 

\ta{I have you now, Suthis Mephilex,} said Thul.
\ta{This time you are going to die. 
  Cowering. Weak. Worthless!}

I found myself crawling forward.

\tho{But I don't know the spell. 
  The scroll is damaged\ldots}

\tele{I know the spell. 
  Let me help you, Mephilex. 
  You will triumph where I failed.}

I glanced back.
The Jaslars were less than twenty feet away. 

\tho{Yes.

  \Ubloth.

  I pledge myself to thee.}

I leapt from the rock. 









\section{The Last \Arcanum}
For a long moment I hung in the air. 

Time stood still. 

The flesh rippled underneath me as if in anticipation. 

I fell. 

I think even the Jaslars held their breath. 

The slime opened up to receive me and I plunged in.
It engulfed me and dragged me down into its murky depths.
I surrended myself to \Ubloth, and its fluids oozed through my mouth and nose, through my very scales and every pore in my body.
It crept inside me and filled me. 
The essence of \Ubloth coursed through my veins.
% Into my brain.
% Into my mind and soul.

I became one with it. 

And in a flash of insight I understood everything. 
Immortal \Ubloth, older than the first \dragon, is but the maggot spawn of a race of cosmic gods too dreadful to contemplate. 
Far removed from the petty wars and empires of humanoids, far above our pitiful lives, its horrid kind has infested the myriad realms of universe for millions of years. 
They are tumours upon the very fabric of the cosmos. 

I understood the symbiosis of Clan Suthis with \Ubloth. 
Every mage of the clan has sworn a pact with the loathsome god: to feed it with sacrifices of flesh and souls, and in return it feeds us with sorcerous power.  
We drink its effluvium and feed it our own blood. 
Thus we are bound to it forever, our flesh and souls soaked in its corruption. 
When we die our screaming souls are consumed by \Ubloth, and through its ghastly effluvium we return to life. 

% For eternities she floats through the amorphous god's crushing embrace.
% She drowns. 
% She dies.
% And she is reborn. 
% Her body is crushed and reshaped. 
% 
% She sees visions of the churning chaos at the planet's core where \Ubloth was spawned. 
% She floats in ultimate horror. 
% She lives lifetimes of agony, lifetimes of ecstasy. 
% Her sanity is slashed and torn. 

I realized that I have lived before. 
All the souls from which I am made are the souls of Suthis mages that have returned to \Ubloth.
It secreted their essence through its effluvium, which was distilled into potions that my mother drank, and thus they flowed into her unlaid egg and formed the new life that became Suthis Mephilex. 

Now I had returned to the embrace of \Ubloth. 
The circle was closed once more. 
I understood the \Arcanum of the Soul. 
I understood all. 

%After a million years 
I regained consciousness. 
I was rising, borne up by waves of putrid flesh.
I emerged into open air.
I found myself standing, the flesh of \Ubloth now as solid ground under my feet. 

The Jaslars still stood bewildered on the shores.

My voice boomed in the cavern:
\ta{Jaslar Thul! I am still here.} 

\ta{Wh-what hideous power is this?} said one of them.

\ta{Thul!} said another.
\ta{You said she was a weak mage!
  You did not tell us she had powers like this!}

Jaslar Thul did not speak. 
She just backed away.

I raised my arms. 
\tho{\Ubloth.
  I am thine.
  Let thy power flow through me.} 
And from \Ubloth's shore below there flew into the air a throng of shrieking blinded souls, forming tendrils of vaporous ectoplasma. 

Terror shone in Jaslar Thul's eyes. 
She could not turn away. 

The tendrils snaked through the air. 

Thul glanced around and found her cohorts likewise frozen in terror. 

The howling tendrils closed in. 

At the last moment Thul turned and ran. 

I clenched my fist. 

The tendrils closed around Thul. 

She screamed. 

The ghostly tentacles lifted her into the air. 

This broke the hold of terror on Thul's lackeys. 
They fled in blind panic. 
I flexed my hands.
More wailing tendrils snaked out and snatched them, clutched them between gaping faces and blindly groping hands. 

\ta{A weakling, am I, Jaslar?} I said.

I pulled her closer to me.
Closer to the surface of \Ubloth.

She squirmed. 
\ta{Not this\prikker let me live\prikker Suthis, please\prikker}

\ta{No.}

I flicked my hand.
The tentacles plunged Jaslar Thul and her sycophants screaming into the ocean of slime. 
Their souls would not return to their gods.
They would be absorbed by \Ubloth and join the silently wailing throng of the damned. 

I had triumphed. 

It was finished. 

%They say that I am a prodigy, and that only this allowed me to survive this twofold ordeal.
I need not tell you the details of how I found my way back to the surface, nor of how I was later brought before the Master and gave my allegiance to him. 

But I will tell you one more thing. 
I will tell you of that which\dash for me\dash stands as the crowning horror of my ordeal. 
I will tell you what sparked my flash of insight and made me understand the slavering inhuman evil of this loathsome shapeless thing which I am now forever pledged to serve, in this life and the next. 
It was this realization that shattered all peace of mind, perhaps forever. 
For when I plunged into the slime I saw before me one face stare back at me with vacant blinded eyes. 
Bereft of all sanity and reason it wailed silently its horror and despair.
It was Suthis Cruan, my grandfather. 









\newpage
\appendix
\section{Pronunciation}
% Pronunciation is given in both IPA (International Phonetic Alphabet) and my own makeshift phonetics. 
Some notes about my home-made phonetics: 
% [CH] is like in German \pex{ach}. 
% [KH] is like in German \pex{ich}. 
% [ZH] is like the \lett{SI} in English \pex{vision}. 
[DH] is as in English \pex{this}. 
[Ä] is as in \pex{cat}.
[EI] is as in \pex{say}.
[AI] is as in \pex{sigh}.    

\begin{pronunciationenvironment}{
%   \section{Wordlist}
}
  \pitem{\Arcana}{[ar"kEIn@] or [ark"a:n@]}{ar-KEI-na or ar-KAA-na}
  \pitem{\Arcanum}{[ar"kEIn@m] or [ark"a:n@m]}{ar-KEI-num or ar-KAA-num}
  \pitem{Cruan}{["kru:æn]}{KROO-an}
  \pitem{Dristan}{["drIstæn]}{DRIS-tan}
  \pitem{\Isxae}{["i:sksEI]}{EES-ksei}
  \pitem{Jaslar}{["dZæsla:r]}{JÄS-laar}
  \pitem{Kush}{["ku:S]}{KOOSH}
  \pitem{Mephilex}{["mEfIlEks]}{MEF-i-leks}
  \pitem{mosca}{["m6skæ]}{MOS-ka}
  \pitem{\Nasshikerr}{["næSikEr]}{NÄS-shi-keir}
  \pitem{\Ortaica}{[6r"taIkæ]}{or-TAI-ka}
  \pitem{\rethyax}{["rETjæks]}{RETH-yäks}
  \pitem{\scatha}{["ska:Da] or ["ska:Ta]}{SKAA-dha or SKAA-tha}
  \pitem{\scathae}{["ska:DEI] or ["ska:TEI]}{SKAA-dhei or SKAA-thei}
  \pitem{Suthis}{["su:TIs]}{SOO-this}
  \pitem{Talaac}{[tæla:k]}{ta-LAAK}
  \pitem{Thul}{["Tu:l]}{THOOL}
  \pitem{\Ubloth}{["ubl6T]}{OOB-loth}
  \pitem{Vaimon}{["vaIm6n]}{VAI-mon}
  \pitem{\Yormis}{["j6rmIs]}{YOR-mis}
\end{pronunciationenvironment}









\section{Glossary}
\begin{gloss}



\begin{comment}
\paragraph{Arcanum}
\end{comment}
\gitem[Arcana]{Arcanum}
\target{Arcanum}
Generic term for mystic secrets or teachings to be studied and internalized. 
Curricula in magic are often organized as a series of Arcana.  



\begin{comment}
\paragraph{\daemon}
\end{comment}
\gitem[\daemons]{\daemon}
\target{Daemon}
\target{Daemons}
Incorporeal entities that dwell in the Beyond. 
Believed to be mostly mindless. 




\begin{comment}
\paragraph{\human}
\end{comment}
\gitem{\human}
\target{Human}
A \maybehs{humanoid} race. 
One of the most widespread humanoid races on \Miith{}, alongside the \scathae. 
Founders and rulers of the \VaimonCaliphate. 



\begin{comment}
\subsection{\iquin}
\end{comment}
\gitem{\iquin}
\index{Light}
\target{Iquin}
\target{Light}
The force of Light in \hs{Vaimon} metaphysics. 
By the \hs{Iquinian Church} viewed as the source of all good and worshipped as a divine force. 



\begin{comment}
\paragraph{\Iquinian Church}
\end{comment}
\gitem{\Iquinian Church}
\target{Iquinian Church}
\target{Iquinian}
A Vaimon religion based around the worship of \hr{Iquin}{\Iquin}. 



\begin{comment}
\paragraph{Isxae}
\end{comment}
\gitem{\Isxae}
\target{Isxae}
\Ortaican goddess of law and rulership.



\begin{comment}
\subsection{\itzach}
\end{comment}
\gitem{\Itzach}
\target{Itzach}
The force of Darkness in \hs{Vaimon} metaphysics. 
By the \hs{Iquinian Church} reviled as the source of all evil. 



\begin{comment}
\paragraph{mosca}
\end{comment}
\gitem{mosca}
\target{Mosca}
A large lizard. 
Eaten in some cultures as a delicacy.



\begin{comment}
\paragraph{Kush}
\end{comment}
\gitem{Kush}
\target{Kush}
A pre-\scathaese civilization. 
Its language\dash written in a unique sinuous script\dash is still used in some spells. 



\begin{comment}
\paragraph{Nasshikerr}
\end{comment}
\gitem{\Nasshikerr}
\target{Nasshikerr}
\Ortaican goddess of shadows and the hidden.



\begin{comment}
\paragraph{\Ortaica}
\end{comment}
\gitem{\Ortaica}
\target{Ortaica}
A great \hr{Scatha}{\scatha}-dominated realm that flourished after the fall of the \maybehr{Vaimon Caliphate}{\VaimonCaliphate}. 



% \begin{comment}
% \paragraph[Baccon]{\baccon}
% \end{comment}
% \gitem[\baccons]{\baccon}
% \index{\bacconate}
% \target{Bacconate}
% A ruling council in certain (predominantly \scathaese{}) cultures. 
% Typically aristocratic in nature. 
% A realm ruled by a \baccon{} is called a \bacconate{}. 



\begin{comment}
\paragraph{\rethyax}
\end{comment}
\gitem[\rethyaxes]{\rethyax}
\target{Rethyax}
A \hr{Scatha}{\scatha}-dominated order of mages, founded by the \maybehr{Ortaica}{\Ortaicans}. 



\begin{comment}
\paragraph{\scatha}
\end{comment}
\gitem[\scathae]{\scatha}
\target{Scatha}
A race of reptilian \maybehs{humanoids}. 
A \scatha{} resembles a bipedal dinosaur with a long, rigid tail. 
They walk on straight legs and with a horizontal spine like bipedal dinosaurs, not with a vertical spine like \humans.
An average adult is 170-180 cm tall or long. 
They have tough scaly skin and are omnivorous. 

The \scathae{} are one of the most widespread humanoid races on \Miith{}, alongside \hr{Human}{\humans}. 



\begin{comment}
\paragraph{Talaac}
\end{comment}
\gitem{Talaac}
\index{Talaac}
\index{Mystic Talaac}
\target{Talaac}
A language spoken by \dragons and some humanoids. 
Written in a cuneiform script. 
The arcane variant of the language, called Mystic Talaac, is used in many spells. 



\begin{comment}
\paragraph{Vaimon}
\end{comment}
\gitem{Vaimon}
\index{Vaimon}
\target{Vaimon}
\target{Vaimons}
A \hr{Human}{\human}-dominated order of \maybehs{mages}.
Their magic theory is based around the two forces of \hr{Iquin}{\iquin} and \hr{Itzach}{\itzach}. 
Many Vaimons follow the \hr{Iquinian Church}{Iquinian} religion.



\begin{comment}
\paragraph{\VaimonCaliphate}
\end{comment}
\gitem{\VaimonCaliphate}
\target{Vaimon Caliphate}
\index{\VaimonCaliphate}
A \human-dominated theocratic empire ruled by the \hs{Vaimons}. 
It existed from the year \yic{Founding of the Vaimon Caliphate}, where it was founded by \maybehs{Cordos Vaimon}, and until the \maybehr{Hundred Scourges}{\HundredScourges} in the year 	\yic{Hundred Scourges} where it fell, during the reign of \maybehr{Belzir}{\Belzir}. 



\begin{comment}
\paragraph{Yormis}
\end{comment}
\gitem{\Yormis}
\index{\Yormis}
An \Ortaican city. 
After the fall of \Ortaica \Yormis resisted all attempts at conquest and became a sovereign city-state. 
It has a reputation as a city of black sorcerers. 











%\printindex









\end{gloss}
\end{document}
