\section{Timeline}



\bepo{Pre-History}
\eepo



\bepo{The Age of \Dragons{}}

\event{First Dragons}{First \Dragons{} born.}
\event{Founding of Nom}{
  Florocthakhsur, Lord of House Tindarex, declares herself Queen of the \Dragon{} Kingdom of Nom, taking the royal name Nacheldryss, meaning `vengeful'.} 
\event{Fall of Nom}{The Fall of Nom.} 
\eventl{Founding of Irokas}{
  Hekhdraxsis, Lord of House Irokas, declares herself Queen of the \Dragon{} Kingdom of Irokas, taking the royal name Tentocoth, `unequaled'.} 
\eepo



\bepo{The Days of the Empire}

\event{Faegos birth}{Faegos Vaimon is born.} 
\event{Belandos birth}{Belandos Vaimon II is born, the first son of Faegos Vaimon.} 
\event{Cordos Vaimon birth}{Cordos Vaimon born, the first child of Belandos Vaimon II.} 
\event{Faegos death}{King Faegos dies. Belandos Vaimon II crowned king.} 
\event{Silqua birth}{Silqua Delain born.} 
\event{Silqua wed}{Silqua weds Cordos Vaimon.} 
\event{Belandos death}{King Belandos II dies. Cordos Vaimon crowned king. He begins to conquer a bunch of stuff.} 
\event{Silqua death}{Silqua Delain Vaimon dies.} 
\event{IC}{Cordos Vaimon declares himself Emperor of the Vaimon Empire.} 
\event{Belzir birth}{\Belzir{} daughter of Cormin born.} 
\eventl{Darkfall}{The \Darkfall{} and the end of the Empire.} 
\eepo



\bepo{The Modern Age}

\event{Noreocchyrias birth}
{Birth of Xoldm of House of Irokas (later to be King Noreocchyrias).} 
\event{Founding of Imetrium}
{Imetrium is formed.} 
\event{Noreocchyrias crowned}
{Xoldm is crowned king and takes the name Noreocchyrias, `feared by his enemies'.} 
\event{Tentocoth birth}
{Birth of Frycad of House Irokas (later to be King Tentocoth).} 
\event{Founding of Belkade}
{Belkadian Empire formed.} 
\event{Tentocoth Vaccashyth}
{Frycad comes of age and takes the name Vaccashyth.} 
\event{Tentocoth Rhoahathnex}
{Vaccashyth takes the name Rhoahathnex.} 
\event{Tentocoth Ibrethnavish}
{Vaccashyth takes the name Ibrethnavish.} 
\event{\EreshKal{} flourished}{The civilization of \EreshKal{} flourish in modern-day Runger.}
\event{\EreshKal{} destroyed}{\EreshKal{} is destroyed after several neighbouring lords band together to wage war against them.}
\event{Fall of Belkade}
{Belkadian Empire collapses.} 
%\event{Noreocchyrias abdicates}{King Noreocchyrias abdicates. His son Vaccashyth is crowned king and takes the name Tentocoth.} 
\event{Noreocchyrias death}{King Noreocchyrias dies. His son Vaccashyth is crowned king and takes the name Tentocoth.} 
\event{Carzain birth}{Carzain is born on the 12th day of \Izion.} 
\eventl{Runger war}{King Morgan of Runger invades Pelidor in the beginning of \Atzirah.}
\eepo

