
\bookchapter{The Ghost Tower}





\begin{comment}
  \section{Carzain asks Curwen about Ghost Tower}
\end{comment}
Carzain and Curwen are together. 

Carzain finally remembers that he wanted to ask Curwen what the deal is with the Ghost Tower. 
So he does.
Curwen tells him some of what he knows, but not everything. 
Curwen tells him the Tower is indeed magical. 
He is aware of the illusion effect. 
The locals fear the magic, so they prefer to pretend the tower is not there, and they hate to be reminded that it exists.
He tells Carzain where to find it in the city. 

Carzain goes away to find the Ghost Tower. 
(Read about it.)
He finds it.
Now that he is close to it, he can see how awesome it really is. 
It is immensely ancient, and completely different from the rest of \Forclin in style. 
It is a \maybehr{Dark monuments}{dark monument}, possibly built by some Elder Race. 
It looks like a work of superior architecture that could only have been built by superior Elder Races.

He tries to enter, but cannot come in. 





\begin{comment}
  \section{Curwen thinks Rungerans want Ghost Tower}
\end{comment}
\new
Curwen stands behind and thinks about the Ghost Tower. 
It is comparable to the \quo{dead garden} in \Malcur. 

He looks at the Ghost Tower. 
You can see a blurry outline of it in the mist if you are clear-sighted and know where to look. 
But it is well-hidden in the Shroud. 

Then Curwen realizes something: 
The Tower has plenty of power in it, and it can act as a gateway to \Nyx. 
He and the Cabal speculate that Sentinels have a hand in the Rungeran invasion. 
He has been trying to figure out what their goal is.

Inspired by this, Curwen \quo{realizes} that the Sentinels are after the Ghost Tower. 
After all, \maybehr{From Ghost Tower to Nyx}{the Tower is a portal to \Nyx}, and it stands to reason that the Sentinels would like to gain control of such a back door into \Nyx. 

Remember to have more speculation from Curwen about how the Rungerans are likely being manipulated by Sentinels, and that the whole war therefore has a Sentinel goal. 

\begin{prose}
  Charcoal:
  \tho{%
    Mages wielding great power.
    What are they after?
    What are all men with power after?
    More power. 
    Magical power.
    The Ghost Tower!}
\end{prose}

This prompts Curwen to convince the Pelidorians that they must hold \Forklin{} at all costs. 









