
\bookchapter{Moro and Rian Interrogate a Thug}
\target{Rian and Moro interrogate a thug}
Read about: Moro, Rian, Black Plague, the Sentinel plan, \Malcur, \quo{\Malcur is going mad}.

Remember that \Malcur is an ancient city.
Much of it is built by very early Vaimons, thousands of years ago. 
Rian gets a feeling of immense age, but he does not know much. 

Moro knows that \Malcur is older than \Yormis and many other things. 
The small houses and huts are like weeds springing up and crawling around at the feet of the infinitely vaster, older and mightier castles, walls and towers that stand like majestic trees and mountains. 

In certain places, \Malcur looks almost alive, as if it is a creature or plant that has sprung from the earth and rock of its own power. 



\begin{comment}
  \section{Looking for a victim}
\end{comment}

Moro and Rian go out in the city.
They hope to find a Black Plague gangster whom they can capture and interrogate.
It takes several nights of trying before they find some. 

Remember that \Malcur is going mad. 

Rian and Moro are out in the city at night. 
Rian is lost in his own thoughts. 
He has become scarred and scared and disillusioned.
Moro is scary.
He trusts her because she helped him and is still helping him.
So he has agreed to work for her.
But he is still afraid of her. 

And he has dark thoughts, as described above. 

They see some gangsters.

Moro:
\ta{Look! Over there!}

Rian is absent-minded.

Moro slaps him: 
\ta{Pay attention! 
  You are supposed to be the young man with good eyes.}

Rian:
\ta{Sorry, \MissCornel.}

Moro:
\ta{Look at that one over there.}

Rian agrees that the \scatha looks suspicious. 



\begin{comment}
  \section{Capturing the victim}
\end{comment}

They somehow overpower the thug using magic. 
Moro does the work.
Rian cowers down and prays. 
He feels the dark forces, the \daemons she summons.
He is afraid. 

Maybe move a lot of lines from the \quo{Moro Sacrifices to \Nasshikerr} chapter to here.
Otherwise we end up with two rather similar and unnecessary scenes. 

After the thug is pacified, Rian begs Moro not to use such evil things. 

Moro is having none of that. 
She tells him: 
\ta{Do not try to push your religion on me. 
  I will use my magic whenever I need it, and that is that.}
She snarls at him, angrily.

Rian pulls away, intimidated.
Then he looks back at her. 
She looks at him sadly, as if she regrets her outburst of anger. 
Then she quickly turns away. 

Rian understands.
She does not want to be angry and grumpy like this.
She is bitter and does not trust anyone, but she is not a bad \scatha. 
Rian is sad, because he suspects Moro is sad. 
Of course she is.
Her soul is damned. 
She does business with \daemons and evil gods. 
He wishes she would stop.
But no one can be redeemed from one day to another. 
He will keep trying to make her see reason and repent her evil magic and turn to the One Light. 



\begin{comment}
  \section{Interrogating the victim}
\end{comment}

They drag the gangster into a nearby alley. 
The gangster is a \sphyle. 
They interrogate her. 
Moro uses some subtle magic to make the gangster talk. 

The gangster is easily scared when she sees magic.
She has mages in her own group and knows what horrible things they can do.
So she quickly gives in and talks. 

From the gangster they learn where the abductees are kept and where the Plague have their hideout.
At least one hideout. 
There are others, but this thug does not know where they are.
She is only a low-lewel grunt. 
She is not in on the secrets of how the organization operates. 

Moro interrogates her about the mages and what their plan is.
She knows nothing. 
She has been sent out to kidnap people once in a while. 
And she has been sent to procure money or assassinate people. 

Rian breaks in: 
\ta{Kidnap people? Did you kidnap Neina?}
He describes her.
The gangster says she cannot remember any single person.
Maybe she snagged her. 
She does not know. 

Moro pushes Rian away.
\ta{Let me handle this.}

She asks more questions about the sorcerers.
The gangster knows nothing. 
Not even their names. 
She only takes answers from her bosses, and the bosses confer with the sorcerers. 
She is too wise to try to ferret out what the sorcerers' plans are.
That can only end badly. 
But she has heard them talking about \quo{{the Change}}. 
She does not know what it is, but apparently it is some goal they are working towards. 
Some big magic they are planning. 

Moro asks about the snake-people.
The gangster has heard rumours about snake-people, but has never seen one and does not know anything useful. 



\begin{comment}
  \section{Killing the victim}
\end{comment}

Moro keeps going for a while, but they get nothing new.
Nothing worthwhile. 
In the end, Moro kills the gangster. 

Rian wants to storm in and rescue Neina now that they know where she is, or at least have a good idea where. 
Moro urges caution. 
Moro is not satisfied. 
The thug did not really know anything. 
They have learned an address and the descriptions of some people.
But they have not learned details nor overview of the Black Plague's plans. 

Moro is intrigued by this \quo{Change}.
But she feels she cannot act until she knows more. 
But they cannot just go on doing what they have been doing. 
It has taken them a lot of time to get just this far.
They do not have the time to keep doing it.

She decides she must do something else.
Something more effective.
She will call again on her patron god, \Nasshikerr. 
And this time she will pay the price he asks.
The grave situation demands no less. 

Remember that \Malcur is going mad. 
At the end of the chapter, something horrible happens.
The city turns against them.
Maybe they get chased by a crowd of mutants. 
Maybe a house comes alive. 
Maybe the ground is crawling with worms.
Maybe they see into the Beyond like Catrian did. 








