
\bookchapter{Moro asks \Nasshikerr}
Read about \maybehr{Moro}{Moro \Cornel} and \maybehr{Nasshikerr}{\Nasshikerr}. 

Read about \maybehr{Ortaica}{\Ortaican mysticism} and \maybehr{Rethyax magic}{\rethyactic magic}. 





\begin{comment}
  \section{Astrology}
\end{comment}
Moro is looking at stars. 
Navigating the constellations.
Trying to feel the ley lines.
Trying to find some trace of \Tiroco. 
Trying to divine the \ps{\rinyuth} fate. 

\tho{Speak to me, stars. Tell me the destiny that awaits \Tiroco Pelidor.

  Aw, crap.
  Whom am I fooling?
  This is getting me nowhere.}

She is trying to find out what is wrong with \Tiroco and how she can help her. 
But \Tiroco has not given her much to go by, since she stormed out last time. 
She is doing the best she can with the tools she has, but she is failing. 

And she has doubts about her astrology. 
Among other duties, Moro acts as court astrologer. 
But she has doubts about her ability. 
She is experienced and has drawn many horoscopes, but she is not sure if she believes in it. 

In her own experience, foretelling anything about a single person is very difficult. 
Individual mortals are too small and insignificant for the stars to care about them, so asking the stars about them does not gain much. 
She follows the textbook guidelines on how to make horoscopes, and she does the best she can to give people something meaningful, but secretly she suspects that she is a fraud. 

It is hard to read anything about a single person. 
It is somewhat easier to read about an entire city. 
She knows there is something wrong with \Malcur as a whole. 
She has some descriptions and clues. 
She has tried to use these and read the stars about them. 

But she has not been able to learn much. 





\begin{comment}
  \section{Moro calls on \Nasshikerr}
\end{comment}

\tho{Time to go in another direction.
  Time to ask a favour of \Nasshikerr.}

\Nasshikerr is the patron god with whom Moro has made deals.
He gives her sorcerous power and knowledge in exchange for her allegiance. 
Every \rethyax has to have one or more patron gods in order to be able to command \daemons.

She calls on \Nasshikerr. 
She performs an elaborate spell.
She grumbles that if \Nasshikerr valued her more highly, she would not have to go through so much trouble to contact him. 
But there we are. 

Moro has a sinister statue of \Nasshikerr which she uses to summon him.

When she prays to \Nasshikerr, she hears the beat of black leathern wings from moonless gulfs. 
The act of prayer itself peels back the Shroud a bit opens up vistas of the Beyond. 
Because when a mortal prays, he expects to be able to reach something beyond his everyday experience, so the expectations that feed the Shroud are weakened. 
The mind becomes more susceptible. 
It is an act of self-suggestion, self-hypnosis. 
Note that this works even if you do not receive an answer. 
(The above should be moved to a more central place in the main notes.)

Make \Nasshikerr more frightening, more awesome and loathsome.
Like Tsathoggua.
He has big, rolling chamaeleon eyes. 
Moro fears him.

\Nasshikerr appeared in his guise of an chameleon.  
She asked him for advice and knowledge. 
She knelt before his apparition. 

\Nasshikerr:
\ta{Why have you dared to contact me, mortal? Speak!}

Moro:
\ta{\Nasshikerr, great lord.
  It is I, Moro \Cornel, your most humble servant.
  I call upon you because I have great need of your wisdom, mighty \Nasshikerr.}

\Nasshikerr:
\ta{And why should I aid you?}

He was a vain god, she knew, and needed much coaxing. 

Moro:
Some more praise, ass-kissing. 

Eventually \Nasshikerr{} agrees to help. 

Moro:
\ta{%
  I have felt that some supernatural evil is afoot in the city of \Malcur, great \Nasshikerr.
  It haunts me, and it haunts my sovereign, \rinyuth[\Tiroco] Pelidor. 
  I want to fight this evil, but I have been unable to identify it, so I do not know how.
  I need your help, mighty one.
  Please help me find out how to save my city and my \rinyuth.}

% \Nasshikerr pauses for dramatic effect. 
% Then: 
% \ta{Very well, Moro \Cornel. 
%   I will share some of my wisdom with you.}
% 
% There was a new pause. 
% Less dramatic. 
% More awkward. 
% 
% \Nasshikerr:
% \ta{Contact me again in no less than a week, and bring me a sacrifice. 
%   Then I will return and tell you more.}
% 
% \tho{Right. Meaning you don't know and won't admit it.
% 
%   Hm. 
%   But at least he offers to try to find out.}
% 
% \Nasshikerr:
% \ta{And Moro?}
% 
% Moro:
% \ta{Yes, great \Nasshikerr?}
% 
% \Nasshikerr:
% \ta{Bring me a better sacrifice next time. 
%   A \emph{real} sacrifice. 
%   Your credit is all but spent.}
% 
% Moro:
% \ta{Yes, my master.}

\Nasshikerr tells her a little, but not much.
He says if she wants more help, she must give him a sacrifice of blood.

\Nasshikerr vanishes. 

Moro sits back and grumbles. 
She fears \Nasshikerr, but she is smart enough to suspect that he knows more than he is telling her. 
The gods always are. 

She resents the fact that he is like that (arrogant, superior, unwilling to \cooperate with a mere mortal), but that is how gods are.
She has gotten used to it. 
She should not say this openly.
It should be conveyed subtly.
The reader must \emph{not} be led to think of Moro and \Nasshikerr as being near-equals. 

Moro is not sure if she will sacrifice to him.
It is a terrible thing to do.
She would rather not.
She will first see if she cannot solve her problem by other means. 
Dealing with the gods is always risky and expensive business. 
She will rely on herself as much as she can. 
As she always has.
(Insert some self-pity here.)









\begin{comment}
  \section{\Nasshikerr broods}
\end{comment}
\new
In his homeworld, \Nasshikerr sits brooding. 
His \ophidian eyes stare out with their calculating inhuman stare. 
His reptillian body lies in torpor, cold and unmoving. 



The situation in \Malcur is interesting to him. 
He knew something was going on there, but previously he had given it little thought. 
Moro's plea had made him investigate some more. 

Turns out there is quite a lot going on there. 
Lots of work by both the Sentinels and the Cabal. 
He cannot easily deduce what, but \Secherdamon clearly has some big plan in the works there. 

Whatever \ps{\Secherdamon} plan might be, it is no doubt bad news for the people of \Malcur. 
Moro has sniffed that much. 
And she is now out to stop it. 

\Nasshikerr smiles inside to himself. 
Mortals rarely amount to much, but Moro \Cornel is a very capable mortal. 
With his help, and a good share of luck, she might manage to fuck up \ps{\Secherdamon} plan. 

If Moro is onto the fact that something is going on, then no doubt others are, too. 
In fact, \Nasshikerr{} is surprised at how much Moro knows, though. 
Given how traumatized she is, she should not be able to see this much. 
Strange. 
At times it feels like the Shroud is thinning. 
It also feels like holes are showing up more often that they once were. 
But he is probably just imagining it. 
The Shroud is woven tightly, and it is not about to go away. 

\Nasshikerr considers his options. 
What should he do now? 
\Nasshikerr was affiliated with the Sentinels. 
He had once been an ally of \Secherdamon. 
He could act on old loyalty and warn \Secherdamon and his Sentinels, so they can take precautions and not be caught unawares by meddlesome mortals slipping through their fingers. 

But why should he?
He is no longer a close ally of \Secherdamon. 
Certainly not a friend. 
He feels not much loyalty towards him. 
\Secherdamon has done plenty to alienate himself from \Nasshikerr and others like him. 

Nah. 
\Nasshikerr chooses to play his own game. 
He is bored, and wrecking the plans of other immortals can be good fun. 
It's not like anything will come of \ps{\Secherdamon} plottings, anyway. 
The \feud has been going on for thousands of years with no change in the status quo, and will probably continue to do so for thousands more. 
So why not just live in the moment and do what seems most interesting?

Yes, that is what \Nasshikerr will do. 
He will read the stars and see what he can discover. 
He knows more astrology than any mortal, after all. 
He will spy on \ps{\Secherdamon} plots and see what he can learn, then tell Moro. 
Perhaps she might make a difference. 
Perhaps enough to annoy \Secherdamon. 
That would be fun. 









