
\bookchapter{Moro and Rian Perform Divination}
Read about \maybehr{Moro}{Moro \Cornel} and \maybehs{Rian} and maybe \maybehr{Nasshikerr}{\Nasshikerr}. 

Read about the Shroud. 

Read about \maybehr{Ortaica}{\Ortaican mysticism} and \maybehr{Rethyax magic}{\rethyactic magic}. 

\begin{comment}
  \section{Telepathic search of the city}
\end{comment}
Moro's POV. 

Moro takes Rian with her to her chambers in the castle. 
He is deadly afraid, but she tells him to just be quiet and follow her.
Her magic will hide him from prying eyes. 

He breathes a sigh of relief when she closes the door behind them. 
Fortunately she has a way out of her chambers that is fairly short and sees little traffic. 
After all, Moro has her own dealings that she does not want the palace staff to know about. 

Now they are in her chambers. 
Rian looks around at her books, scrolls, star-maps and occult requisites. 
Then he pulls himself together. 

Rian:
\ta{\Mistress \Cornel.
  Is there anything we can do to find Neina?
  Cant you help?
  With your... your magic?}

Moro can tell he is not comfortable with it, but he is willing to do anything to get his girl back.
Even resort to magic. 

Moro knows that something is seriously wrong in \Malcur, and she believes that the Rian/Neina case may be a lead. 
She intends to follow this lead and hopefully find some information on what is going on. 
She helps him search the Realms for Neina, but she is afraid she might lose herself in the process. 

Moro:
\tho{Hm.
  He thinks his girl has been taken by the Black Plague.
  And we know the Black Plague has something to do with those mages.
  So it stands to reason that if we could track down the girl, it would give us vital clues towards finding the enemies we are looking for.
  
  But that's if she is alive.
  More likely she is dead already.
  Her soul fed to some voracious \daemons.
  I don't want to show the boy his lover's horrible fate.
  If she is dead, he is better off not knowing.
  In cases like this, ignorance is bliss.}

Rian:
Begs and pleads some more.

Moro:
\tho{But I can't hold him off forever.
  And I can't lie to him.
  I suppose we will have to risk it.}
  
\ta{Very well, Rian.
  I have some spells that may be able to locate your missing girlfriend.}

They perform a spell. 
Rian must think about Neina as hard as he can. 
Moro will connect with him telepathically and read from his mind what he knows about Neina. 
From this she will try to reconstruct a mental signature of Neina. 
Moro will then try to reach out telepathically and search for her mental signature. 
It is difficult.
She has to smoke a lot of weed to go into the right telepathic trance. 
And she casts some spells to keep them safe from attacks. 
She also has to make sure the door is very securely locked, so no one walks in on them while they are in trance. 

Rian has to smoke the weed too.
He coughs and spits. 
It is strong and ill-smelling and ill-tasting. 
She grumbles.
\tho{Hasn't this lowlife ever smoked before? What a wuss.}

Moro again warns Rian that this is a long shot and has no guarantee of working, even if she is alive and well and close to them. 

Eventually they start the spell. 
Scene ends.

Throughout the spell, have plenty of references to astrology and constellations and \vertices. 
Read about astrology and \vertices in my notes.

Go re-read the scene where Moro performs divination with \Tiroco.
Delete that scene. 
Cannibalize it and recycle parts of it in this chapter. 
Remember, I have too many \quo{visions of evil} in \Malcur already.




\begin{comment}
  \section{Moro searches the afterlife}
\end{comment}
\new
The spell is still going. 
Moro has now searched for a while. 
She has found nothing. 
Well, she has found a few things that might be her, but only faint traces.
Nothing she can depend on.
And nothing she was able to track. 

This person-finding is hard for Moro.
She almost wishes she were a Rissitic mage. 
She has heard they can do this sort of thing very well, with their magic of \quo{true names}. 

\tho{Nothing in the city.
  Damn!
  Damn!
  
  Maybe it is time to take a chance.}

She can expand her search and try to look in the Realms Beyond. 
With luck and skill, she might be able to look into the afterlife. 
Necromancy like this is risky business. 
It will be more dangerous.
Her soul will be less protected from harm or evil influence. 
It could go wrong. 

But she is deep in her look-beyond trance now.
If there is a time for it, that time is now. 

She tries. 




\begin{comment}
  \section{Rian sees \sephiroth}
\end{comment}
\new
Rian is connected to Moro. 
He has not felt much so far. 
There is not much to feel in the living world. 
But now she moves into the afterlife. 
It is more dangerous. 
His soul is less protected. 

Suddenly he starts seeing visions of horrible things. 
A prison of souls.
A river of the damned. 

\lyricslimbonicart{A Void of Lifeless Dreams}{
  I close my eyes and transcend.\\
  beyond the light to a dark world without end.\\
  The spirit escapes the temple of flesh,\\
  as seductive winds of madness\\
  absorbing me into the cryogenic system.
  
  A void of lifeless dreams.
  
  Enter a galactic domain,\\
  frozen in time and space.\\
  A new infinity of serenity.\\
  Interstellar voyage.\\
  The spirit escapes the temple of flesh\\
  into the sphere of mystified gloom.\\
  A cosmic funeral of memories. 
  
  Sarcophagus panorama.
  
  A mania to explore the enigma.\\
  Isolated celestial corpse.\\
  Astral embryonic life form.\\
  Invocation of the dormant realms.
}

He calls out to the \sephiroth to protect him.
As he thinks of the \sephiroth, he looks at the monsters around him, and a horrible thought dawns on him:
That these things \emph{are} the \sephiroth, or at least connected to them.
He recognizes them.
He has, after all, been to church and attended prayer together with real Vaimons who could invoke the \sephiroth, so he has felt the presence of the real \sephiroth.
Now he looks at these things and thinks of the \sephiroth and recognizes something that strikes a chord. 
He is scared shitless and recoils.
He awakens screaming, breaking the spell. 





\begin{comment}
  \section{The spell ends}
\end{comment}
\new
Moro realizes that Rian is reeling and trying to free himself from the vision, so she ends the spell and awakens herself and Rian. 

Rian awakens with a shriek. 
He shudders and hugs himself. 
To him, it was horrible. 

Rian:
\ta{What was that? I saw a horrible vision.
  A hell.}

Moro:
\ta{I was having no luck in the physical world, so I tried to look in the afterlife.
  The afterlife can be a scary place if you have not seen it before.}

Rian:
\ta{The afterlife?}
He has trouble absorbing it. 

Moro:
\ta{I found nothing.
  A few traces in the physical world. 
  Nothing in the afterlife.}

Have them discuss the afterlife a little bit.
Make clear that Moro does not actually know what happens in the afterlife.
She just knows that sometimes she can detect souls of the dead, and sometimes even communicate with them in a very primitive fashion.
The dead are not very coherent, though.
It is hard to get anything useful out of them.
And she only rarely succeeds at reaching a dead soul.
She does not really know what goes on. 

Alternatively, have her describe the afterlife in terms of her own \rethyax beliefs. 
(Read about the \Ortaican religion.)
Rian disbelieves her story and re-interprets it in his own Iquinian terms. 

Rian is worried. 
\ta{Does this mean... Neina is...?}

Moro:
\ta{It does not mean anything.
  She could be alive and sitting in the next room.
  Detecting an individual person is difficult.
  Besides, in a way this is good news.
  I found no traces of her in the realm of the dead, but a few traces in the world of the living.
  So from where we stand now, she is more likely alive than dead.}

Rian:
\ta{%
  Ooookay.
  That's good... I guess.}

Rian thinks about the ghastly things he witnessed. 
And the similarity he noticed. 
Those things were somehow similar to the \sephiroth.
What horrid blasphemy is that?
Those things must be evil imitations. 
Monsters that masquerade as \sephiroth.
They must be \qliphoth.
Evil twins of the \sephiroth.
That is the only sensible explanation.
Unless... no, that alternative is too horrible to consider. 
The idea that such mockeries of the beautiful \sephiroth exist is bad enough. 

Rian hugs himself for comfort. 
Rian has always considered himself a religious person. 
He knows he is not the most virtuous of men. 
He has sinned many times. 
His old life was not easy, and the temptation to sin was always there. 
In recent years, a kind priest and a lot of religious discipline were highly instrumental in bringing him out of his life of crime and converting him into a respectable citizen. 
He is very grateful to the Light for what he has, but worried that he might fall back. 
So he prays daily to \iquin.
He prays for forgiveness from his past sins, and he prays to be delivered from temptation so he can stay on the right path and not sin in the future. 

So this blasphemy, this affront against the purity and beauty of his religion, is deeply disturbing to him. 
He feels as if something deep inside him has been sullied. 
He tries rationalizing it away, but a lingering dread remains and will return to haunt him throughout the story. 

Rian:
\ta{So... what do we do now?}

Moro: 
\ta{I have some ideas. 
  But I must first think and plan.}

Rian sits and muses. 
\tho{%
  What was that Hell I witnessed? 
  And what was that feeling? 
  No, it cannot be... 
  No, I will not think on it!}

\tho{Neina. 
  Be alive. 
  Don't be dead. 
  Please be alive. 
  Please, \Sephiroth, let her be alive.}

\tho{The \Sephiroth... oh, Light...}









