
\bookchapter{Moro Springs Rian}
Read about \maybehr{Moro}{Moro \Cornel} and \maybehs{Rian}. 
Read about the Shroud. 

\begin{comment}
  \section{Rian feels sorry for himself}
\end{comment}
Rian sits in a dark, smelly prison cell. 
There are rats and bugs and lizards everywhere.
And it smells like shit. 
Literally. 
It's small, only three of his paces across. 
There is another prisoner in here\dash an older \dax\dash but he is dead. 
Newly dead, it seems. 
He smells bad, but not as bad as he could. 

He curses himself. 

\tho{%
  Why am I such an idiot? 
  Why did I think the \rinyuth would be any better than the rest of them?
  Just a stupid, narrow-minded noble who doesn't care about anyone other than herself. 
  Fucking nobles. 
  They're shit, all of them. 
  And the commoners, they're shit too. 
  Look at the guards. 
  And look how many people turn to crime and join evil gangs like the Black Plague. 
  
  Now those evil wizards are running loose. 
  \Malcur is going to Hell, and no one cares about it. 
  Am I the only sane man in the world?
  
  Neina. 
  I'm sorry. 
  I failed you. 
}

Rian has been charged with attacking the \rinyuth.
The guards told him that the penalty for that is death by hanging. 

\tho{Attacking the \rinyuth?
  That's crazy talk.
  I was trying to warn her.
  Why doesn't anybody get that?}

As Rian's hunt goes on, he becomes hungry and his health suffers.
His life is hard enough to begin with, and with his hunt for Neina costs him much valuable time and energy, leaving him hungry and tired. 
Now that he thinks back, this exhaustion is probably one of the reasons why he was so desperate and stupid and came up with such a stupid idea. 
Moreover, tiredness and hunger made him weak and slow.
If he had been in better shape he could have dodged those guards and would not have been thrown in jail.

And now that he is in jail, he is even worse off. 
Jail food is icky, and there is not much of it.

He starts to pray:
\tho{Great \sephiroth, have mercy on my soul. 
  Bla bla.}

Make Rian more religious.
Make sure he prays in every chapter and scene that he is in.
Make clear how grateful to the Light he is for how he has been freed from his life of crime and allowed to make a new, honest life for himself.
    
In all the Rian chapters, whenever it is appropriate, have references to the \maybehr{Myths of vanquished monsters}{myths of Iquinian heroes vanquishing inhuman Elder Races and monsters}. 
When he encounters something supernatural, he fears that the wicked Elder monsters will conquer the world. 
In jail, he fears that the wicked Elder monsters will conquer the world. 

It is very dark in the cell.
There is only a tiny window high above, and it is full of dirt, so barely any light can get through.
He can barely see anything. 

While he is in the cell he experiences more madness. 
He feels around and discovers that one corner gives way to soft, wet, oozing flesh. 
He gasps out load and crawls away. 
He backs over to a wall and lets himself tumble backward into the wall.
Only to find that the wall has turned to flesh behind him. 
He panics and flails around.
It feels like he is sinking into that wall of flesh.
As if the wall is sucking him in. 
He flees from it. 
Stumbles around. 
Falls. 
The floor ruptures under his hands and they sink deep into slimy, lukewarm flesh.
Ooze or blood wells up and soaks his hands and his clothes. 
He screams. 
The madness continues.
He imagines he hears voices from the walls. 
He imagines he sees fragments of faces on the walls.
Not full faces, just hideous, all-too-\human mouths that whisper blasphemy to him. 
He can only make out small parts of what they are saying, but the little he understands fills him with dread. 
He shouts and claps his hands over his ears to block them out.
He feels the slimy blood on his hands. 
Now that his hands touch his head, the slime seems to seep into his hears. 
He panics even more. 
Finally he collapses and loses consciousness.




\begin{comment}
  \section{Moro rescues Rian}
\end{comment}
He awakes when Moro comes into his cell and kicks him.
He is still sticky.
His clothes are half-wet with some disgusting substance. 

\tho{%
  What's this?
  Feeding time?
  Or are they coming to take me to the gallows already?
  I have no idea how long I've been here.}

% The door opens. 
% Light comes in. 
A single figure stands there. 
A \scatha. 
That's all he can make out. 
His eyes are busy adapting to the light. 

\ta{You,} says the figure in a low voice. 
A \ps{\sphyle} voice.
\ta{Come with me.}

\tho{This is it. 
  I'm going to die.
  They're going to hang me.}

\ta{Listen to me!
  This is all a mistake!
  I'm innocent!}

\ta{I know. Now be quiet.}

\ta{Please don't kill me! You have to beli... wait, what?}

\ta{%
  Keep your voice down!
  Do you want to alert all the guards?}
the \scatha hissed.
\ta{%
  I am not here to kill you.
  I am here to free you.}

\ta{What? Who are you?}

\ta{Do you want to live or not? Just be quiet and come with me.}

He can see a bit better now. 
It is an older \sphyle, dressed in a dark robe with a hood. 
Her face is in darkness. 
He notices she carries a pistol. 

\tho{Who is this person?
  Is it some kind of trap?
  
  Well, I don't have much to lose. 
  I suppose I'd better follow her.}

So he does. 
She leads her out through some dark corridors. 
Closes some doors behind them. 

They quickly flee from the cell. 
Now that light comes in from Moro's torch, the walls are solid stone again.
Rian tries to tell himself he was just hallucinating last night, but the goo is still on him. 
He goes away horrified. 
Moro is interested when she hears his story.
She does not know how much of it to believe. 





\begin{comment}
  \section{Moro and Rian talk}
\end{comment}
\new
Maybe switch to Moro's POV here.

Moro stops and closes a door. 
\ta{There. I think we are safe now.}

She takes off her hood. 

Rian gasps.
\ta{You're that \sphyle from that day! 
  You were there when those evil mages killed those people!}

\ta{Yes.}

\ta{Why did you save me?}

She hesitates. 
\ta{I need your help. And you need mine.}
She looks at him.
\ta{What is your name, boy?}

\ta{Rian.} 

\ta{You have been spying on the... \quo{evil mages}. Why?}

And Rian tells her of how they have kidnapped his girlfriend and he wants her back.
Besides, what they are doing is clearly evil, and he wants to stop them if he can. 

\ta{How much have you found out? Tell me what you know.}

Rian tells her all he has discovered. 
She is especially interested to hear his allegation that Needle is one of the bad guys. 
And that there are two factions of evil wizards fighting each other. 

Rian:
\ta{Now I've told you what I know. 
  You haven't even told me your name.}

Moro hesitates. 
Moro debates with herself. 
Should she give him a fake name? 
She would prefer to, so she could keep herself secret. 
But Rian is trusting and tells her everything. 
This makes her feel guilty for deceiving him. 
It rips up old scars of trust and betrayal. 

He looks at her with a hurt, accusing look.
\ta{I deserve to know at least that much.}

Eventually she decides to come clean and tell Rian her true name and identity. 
She sighs.
\ta{My name is Moro \Cornel.}

Rian:
\ta{Moro \Cornel? 
  The \ps{\rayuth} archmage? 
  No. 
  You can't be her. 
  She looks nothing like you.}

Moro:
\ta{I am an archmage.
  I can look however I please.}

This disturbs Rian. 
He fears magic. 
He does not want to work with an evil mage.
\ta{Listen to me, Rian. I am not evil. 
  I work for the \rinyuth.
  I want to stop this evil and save \Malcur.}

Rian is worried that the \rinyuth can't be trusted. 
Moro debates that a bit in her mind.
Moro suspects that the \rinyuth has ulterior motives for keeping Rian imprisoned and wanting to kill him. 
She decides that she can no longer trust \Tiroco.
That is one of the reasons she freed Rian. 

Rian:
\ta{What happens now? Won't the guards come hunting for me?}

Moro:
\ta{No. I will make you disappear in the paperwork.}

Rian:
\ta{\quo{Disappear} in the \quo{paperwork}? 
  What does that mean?
  Is this more of your magic?}

Moro:
\ta{No.}
\tho{%
  Sigh. 
  Mention papers and writing to these commoners and they immediately assume it's magic.}
\ta{I have contacts. I will take care of it.}

Rian:
\ta{So... now what?}

Moro:
\ta{We continue our investigation. 
  I have a plan.}



\begin{comment}
  \section{Moro's chambers}
\end{comment}
Moro also notices that Rian looks very hungry and malnourished and haggard and unhealthy and tired. 
So she feeds him.
He becomes very grateful and feels indebted to her.
Rarely if ever has he had such good food. 

Moro is very interested when Rian tells her of the tree-\sphyle. 

Moro and Rian exchange their stories. 
They have both seen glimpses of the \hr{QJ in Malcur}{\quiljaaran in \Malcur}, but denied it.
Now they know they both saw them. 
So they must be real. 
This is a relief, but also a horrible discovery.

For Rian, \quiljaaran are a remnant of the \hs{Age of Chaos}.
They are Elder monsters that should by all rights have been \hr{Myths of vanquished monsters}{wiped out by Cordos Vaimon}. 

For Moro, they are a cruel, painful reminder of the horrors that lurked beneath \Yormis. 
She has seen brief glimpses of them back in \Yormis, but only very brief.
She assumed they were just hallucinations that she saw because she was delirious and mentally unstable at the time.
Now she knows it was real.
It brings back memories of the loathsome amorphous god \Ubloth. 
(Have throwaway references to \hr{Mystic names}{mystic names and places}, like Shung.)

After Rian learns that the \serpentmen really do exist, he thinks back to them.
They scare him.
They remind him of the myths of how Cordos Vaimon and other great heroes vanquished the frightful monsters of the Age of Chaos. 
(Read about them!)
Rian now finds himself in the middle of such a tale, pitted against Elder monsters.
But he is no great hero.
He is nothing like Cordos Vaimon. 
Neither is Moro \Cornel.
How are they to do this terrible thing? 
Rian is afraid. 
He prays fervently to Silqua and the \sephiroth for guidance and protection. 
Suddenly, Rian feels as if mankind is really just a little, feeble, ignorant thing in a vast, cruel universe. 

\citeauthorbook[p.36]{RobertEHoward:TheShadowKingdom}{Robert E. Howard}{%
  The Shadow Kingdom%
}{
  Against a gray, ever-shifting background moved strange nightmare forms, fantasies of lunacy and fear; and man, the jest of the gods, the blind, wisdomless striver from dust to dust, following the long bloody trail of his destiny, knowing not why, bestial, blundering, like a great murderous child, yet feeling somewhere a spark of divine fire\ldots}

Moro confirms to Rian that there are legends of \serpentmen. 
But she does not tell him everything she knows. 
(Read more about Moro's relationship with \quiljaaran.)






\begin{comment}
  \section{Needle looks for Rian}
\end{comment}
\begin{garbage}
Needle comes into the dungeon with some of her goons. 
She intends to silence Rian before he can squeal on her. 
But she finds his cell empty. 
She gets mad and searches the dungeon. 

She finds nothing in the paperwork. 

Later she looks in the paperwork again and finds that Rian has allegedly been taken out and killed. 
This is Moro's addition. 
\end{garbage}










