
\bookchapter{Rungerans Besiege \Forklin}
\begin{comment}
  \section{The Rungerans come into view}
\end{comment}

Read about \Forclin. 

The Rungeran army besieges \Forklin. 
Sethgal or Curwen marvels at the \maybehr{Glorious armies}{size and splendour of the army}. 

There are about 20,000 Rungerans. 
Mostly \humans. 
The heavy infantry is made up of \scathae. 
The cavalry consists largely of the Rungeran nobility, which is \human-dominated. 
Conversely, the Pelidorian nobility and cavalry was \scatha-dominated, whereas most of the \humans are found in the light and medium infantry and among the gunners and archers. 

The main body of the cavalry is the 4000 \relcers. 
The hard core is 60 or so \murocs. 
They have no \grulcans, though. 
\Grulcans are mainly a \Galessan thing.

There are also some 200 \mezolisks. 
These are actually imported from Durcac. 
But they are not badly conspicuous. 
Runger has been known to use \mezolisks{} before. 
The Rissitics have just helped them beef up the number of them. 

Perhaps most gruesome of all, the Rungerans have perhaps 300 \nephil ogres. 
But they are hidden, so the Pelidorians can't see them yet. 

In contrast, the Pelidorian army is smaller, only about 12,000 men. 
They have mostly \scathae. 
Including 1500 \relcers.
And 40 \murocs. 
And a fearsome elite cavalry riding \grulcans.
600 of them. 
Sethgal wonders how the \grulcans will fare against the Rungeran \mezolisks. 

The Pelidorians also have 9,000 infantry, gunners and archers. 

There are also supposed to be some \meccaran irregulars. 
They are conscripted from a bunch of tribes that live in this area. 
They are only loosely tied to Pelidor, and indeed they are mostly barbarians. 
But they do owe some measure of fealty to the \rayuth, so after some cajoling and coercion, the diplomats managed to conscript a bunch of them into army service. 

The \meccarans have not arrived yet. 
Sethgal only knows he has sent out recruitment officers to their tribes to try to make them \honour their vows of fealty. 
He hopes the \meccarans will \honour their obligation and come, but he cannot be sure of them. 
(They will show up when it is crucial.)

The Rungerans also have a bunch of siege cannons.

Sethgal is most worried about the cannons. 
But when he mentions it to Curwen, Curwen tells him he is more worried about the \ishrah.
Curwen is not revealing his sources, but he has it on good authority that the Rungeran \ishrah has something decidedly nasty up their sleeves. 





\begin{comment}
  \section{Carzain and Vizicar}
\end{comment}
\new
Carzain stands next to them and looks out over the besieging army as it marches up and takes positions (out of cannon range, of course). 

\lyricsbalsagoth{The Obsidian Crown Unbound}{
  And so the mighty and resplendent armies of the Imperium assembled before the towering cyclopean walls of ancient Gul-Kothoth.\\
  It was some time before the billowing dust cloud raised by the massed arrival of the vast imperial host settled, ultimately dissipating as the shadows of dusk descended.\\
  With nightfall, the imperial army's countless torches, braziers and cookfires illuminated the dark plain before the fortress like a coruscating sea, painting the stygian heavens the \colour of flame.
}

Vizicar stirs half-awake within Carzain and mumbles: 
\vizicar{%
  Bah. This is nothing. 
  I have seen armies twenty times the size of this. 
  Thirty times! 
  I have commanded such armies. 
  I have vanquished such armies...}
  
Carzain scouts for the \ishrah. 
He sees something in the distance that looks like their quarters and points it out to Curwen. 
Carzain, with his young eyes, can see a person which might be a woman in a dress\dash the commanding woman, perhaps. 
Curwen, who is much older, can't see shit at that distance, so he can only take Carzain's word for it. 





