
\bookchapter{The Conqueror Worm}
Read about: 
\Teshrial, \Urizeth, \Nyx, \noggyaleth, \resphain. 

\Teshrial and \Urizeth go to \Malcur to plan and set up a trap for \Ishnaruchaefir. 



\begin{comment}
  \section{Urizeth worries about Teshrial}
\end{comment}

We start in \Nyx in \Urizeth's quarters.
\Teshrial and \Urizeth are sitting together and talking. 

\Teshrial has brought some of his homebred \humans as a gift for \Urizeth. 
She needs some quality food if she is to get better.
She is very hungry in her healing state. 
(This started as an empty gesture of courtesy from \Teshrial.
 But he realizes he actually cares for \Urizeth as a friend.
 He is genuinely happy to see her get better.)

But she is already looking better. 

\Urizeth:
\ta{Yes. Now you can almost look at me without wincing, eh, \Teshrial?
  Almost.}

\Teshrial:
\ta{Well... um...}
He is embarrassed. 
She speaks the truth, of course.
But he does not want to admit it, and she should know better than to bring it up.
She really has no manners.

\Urizeth:
\ta{Thank you for the gift.
  They look beautiful.}

\Teshrial{} looks at some of home of his home-bred \humans. 
He caresses a beautiful youth with his feathers. 
\Teshrial{} loves his \humans{} and will not let the evil \Ishnaruchaefir{} harm them. 
He was shocked to learn that \Ishnaruchaefir{} would be so cruel as to let cute, defenseless \humans{} suffer for his wrath. 
This makes \Teshrial{} hate him.
He must die. 

\Urizeth:
\ta{Now, \Teshrial.
  Our vendetta against the Destroyer is important, no doubt.
  But I fear that we are neglecting other important issues.
  We have our own work in \Malcur to worry about, after all.
  And \ps{\LocarPsyrex} Sentinels will most likely not stand idly by.}

\Teshrial:
\ta{Yes... yes, I know.}

\Teshrial contemplates the potential threats to \Malcur. 
He knows \Secherdamon and \Psyrex are a threat. 
But he has dealt with them before, and he has spoken much with and learned much from people who have dealt with them even more.
The \CiriathSepher Cabal libraries have thick books (graph-glass) with thousands of pages of strategy for dealing with \Secherdamon and \Psyrex, based on the dynasty's thousands of years of experience of fighting them.

\Secherdamon is dangerous, but he is \quo{the devil you know}. 
\Teshrial knows much about him, or at least feels like he knows much about him.
\Secherdamon is not mysterious and unknown.
\Teshrial sees him as something well-known. 
Therefore \Teshrial does not feel intimidated.
Besides, in \Malcur he is not even facing \Secherdamon in person, but only his lackey, \Psyrex. 
\Teshrial has a tendency to underestimate \Psyrex.
He does not respect \Psyrex.
\Psyrex is only a \scatha, after all. 

In his gut he feels confident that whatever \Psyrex can whip up, he can deal with it.
He and \Urizeth and \Ganethed and \Achsah and the rest of the \resphain working in Pelidor. 

\Urizeth seems to have read his mind, for she says:
\ta{We cannot discount \Psyrex, \Teshrial.
  He may be a \quo{mere} \scatha, but he is as experienced and as devious as any \resphan.
  We must not underestimate him.
  In my state I cannot take a very active role in our work in \Malcur.
  I hope you are not neglecting it as well.}

\Teshrial:
\ta{Yes.
  I mean no. 
  I know.
  You are right, of course. 
  \Psyrex is a threat.
  But we will manage. 
  Remember, you and I are not alone in this.
  We have the strength of our allies to draw on.
  We have \Ganethed and \Achsah and several others working on our side.
  We are not letting \ps{\Psyrex} Sentinels run unchecked.}

Here \Urizeth grows uncertain.
She is a nerd, and talking about personal and emotional things is difficult for her.
\ta{%
  I do not know, \Teshrial, but it seems to me that you are growing obsessed with the quest against \Ishnaruchaefir.
  It seems to me that...}
She pauses.
\ta{It seems like it is all you think about.}

\Teshrial:
\ta{Obsessed? 
  Me?
  By the Rose, no.
  No, I do not have an obsessive personality.
  Worry not, \Urizeth. 
  You need not fear for my sanity.}

\Urizeth:
\ta{Really? Very well. I am relieved to hear it.}
She does indeed seem relieved. 

\Teshrial:
\tho{Hm. Well, that was easy.
  I was completely talking out of my ass there.
  She did not notice.
  Huh.
  You know, \Urizeth, for a wise scholar you can be quite simple-minded.}

\Teshrial muses on. 
He feels that \Secherdamon is a problem he has covered. 
He sees \Ishnaruchaefir{} as the worst threat, because you never know what that meddling rogue immortal might do. 



\begin{comment}
  \section{Urizeth suggests trap}
\end{comment}

\Teshrial expresses doubt.
He has told \Urizeth before of the secret weapon he got from \Azraid.
But he does not think it is enough.
After all, it is not sufficient for them to simply kill \Ishnaruchaefir.
If they just let him revive, they have accomplished nothing. 

\Urizeth suggests they lay a trap in the Shroud and with the \noggyaleth.
Steal text from the chapter with \Azraid. 

\Teshrial is hesitant to use the \noggyaleth.
They are an important part of their plan for \Malcur. 
What if the ambush fails and \Ishnaruchaefir kills them? 

\Urizeth:
\ta{If the Destroyer kills the \noggyaleth, then we are completely screwed over anyway.
  Then you will die and most likely everything will come crumbling down.}

(This argument might not make so much sense.
 Write a better one.
 The essence is, they agree that risking the \noggyaleth in battle is acceptable.)



\begin{comment}
  \section{They inspect Nogg-yaleth}
\end{comment}

They inspect their \noggyaleth that hide beneath \Malcur. 

They use telepathy to inspect the \noggyaleth.
They feel the \noggyaleth through their \matrix.
The \noggyaleth are aligned with their constellation. 

\Teshrial \maybehr{Teshrial fears Noggyaleth}{is afraid of the \noggyaleth}. 

\Urizeth usually performs the spells to direct the \noggyaleth.
\Teshrial has steered clear of learning those spells. 
Ostensibly he thinks it is nerd business and unsuitable for a \resphan like him; a gentleman of the finest breeding and the finest culture, and a master of martial arts, that noblest and most beautiful and artistic of pursuits. 
He used to joke that dealing with slimy, icky things like \noggyaleth was not his style. 
But the truth is that he has always been afraid of \noggyaleth and unwilling to admit it. 

But if \Teshrial is to command them in battle, he will need to learn the spells himself. 
\Urizeth begins to teach him. 
He needs to invoke greater powers: 
His people's ancient pacts with the \banelords{} and their unholy might.

\lyricsbalsagoth{
  Enthroned in the Temple of the Serpent Kings
}{
  Hailing a black sun with ebon rays,\\
  Hailing a black moon as onyx agleam,\\
  The dark horn sounds 'cross the nighted vale,\\
  Shadows call in this bleak winter's dream.
}

\lyricsbalsagoth{
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  I stand now at the anvil,\\
  adamantine hammer in my hand.\\
  In thunder-song the steel I smite,\\
  a clarion heard throughout this land.
  
  Ablaze upon the Altar of Stone,\\
  the Sigil of An-rayuth, the summoning.\\
  Folk of the Mist, Dwellers in Shadow,\\
  the thrice-blessed wand of the Wood-Gods is beckoning.
  
  At the aeon-swathed Shrine of the Oak I kneel.\\
  O' Oracle of the Great Forest, hear me this night...
}

\lyricsbalsagoth{
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  Swaying serpents ring my oak-hewn throne,\\
  Night and Shadow are my hunting dogs.\\
  Ravenous, they howl to be unshackled,\\
  that their maws may be glutted \\
  (with the blood of my foes).
}





