\chapter{\AvatarofEntropy}
Tells the story of \Semiza, the origin of the \resphain, \Merkyrah, the \resphan{} rebellion, the creation of the \satharioth{} and the \secondbanewar. 





\begin{blurb}
  \Miith{} is a cruel world. 
  
  \Dragons{} rule the skies, and their legions of reptilian \cregorrs{} and \scathae{} sweep across the land. 
  The \nephilim{} have been banished from the fertile grasslands and forced to live in deserts, in caves and under the earth. 
  
  \Semiza, \nephilic{} king of \Numah, desperate to find a way to save his people from the \psp{\dragons}{} depredations, turns to black magic. 
  An alien god appears in \ps{\Semiza}{} visions and offers him a chance to vindicate the \nephilim. 
  
  But the price will be a gruesome sacrifice\prikker
\end{blurb}
















\section{The Big Picture}
\subsection{The \Bane{} Master Plan}
\subsubsection{The \banes{} in exile}
\target{Origin of Nyx}
The \banelords{} were not all destroyed. At the last moment, \Daggerrain-tachi seized hold of a corner of the Shroud of Realms that the \ophidians{} were weaving, twisting it into a pocket Realm, into which they fled. This Realm was a vestibule, a thin, almost unnoticeable corridor to \Erebos. They remained in this Realm for thousands and thousands of years, reshaping and expanding it into a shadow of \Erebos. It became \Nyx, the Twilight Realm. 





\subsubsection{\Daggerrain{} is the gate}
\target{Daggerrain is the gate}
\Daggerrain{} embodies the cosmic conduit between \Erebos{} and \Nyx. See, \Erebos{} is tens of thousands of light years from \Miith{}. The \banes{} \hr{Banes come to Miith in spaceships}{came to \Miith{} in spaceships}, but this took thousands of years. 

But \Daggerrain{} has solved the cosmic equations and cast the Realm-weaving spells that create a short-cut through the Realms directly to \Erebos, and as long as he is present in \Nyx, the connection persists.
Granted, the conduit is narrow after the formation of the \hr{Crystal Sphere}{\CrystalSphere}, but it's better than nothing. 

Were \Daggerrain{} to fall, the link would be broken, and \Nyx{} would be permanently severed from \Erebos. At the end of \SentinelsFinalBook, \hr{Daggerrain falls}{this is exactly what happens}. 





\subsubsection{\Bane{} magic on \Miith}
After the \firstbanewar, the \CrystalSphere{} was not entirely tight, so \Erebean{} energy could seep through in small amounts. Some mages discover that they can channel \bane{} power and use it to cast a kind of primitive \nieur{} magic. 

At first, the \dragons{} and others are terrified at the thought of the \banes{} returning, so they persecute and wipe out these mages. But nothing seems to come of it, so gradually, as the centuries pass, the \dragons{} glow lax and stop caring. 





\subsubsection{The \pps{\banes}{} plan}
We are now several thousand years after the \firstbanewar: The \banes{} are forgotten and no one fears their return any more, barely even the \dragons{} who actually fought them last time. 

\index{technology}
Note that \hr{Technology}{the technology is still low}, for a number of reasons. 

But this is all part of \ps{\Daggerrain}{} plan. See, \Daggerrain-tachi could not travel back into \Miith{}, but the Shroud was thin enough for them to gaze into \Miith{} and observe, so they had a reasonably good idea of what was going on there, and they could plan their return. He knows that he will have a hard time reconquering \Miith{} with the \dragons{} opposing him, but he has immortality and patience, so he waits some millennia, planning his return while lulling the \dragons{} into a false sense of security. 

When the time is right and the opportunity presents itself, \Daggerrain{} plans to contact some \Miithian{} mortals, bargain with them and convince them to help the \banelord{} bring his people to \Miith{}. 

\Daggerrain{} will not bring the \banes{} to \Miith{} immediately. Rather, he intends to \quo{crossbreed} his people with some native \Miithians\dash possibly the \nephilim\dash to create a new super-race. This race will eventually become the \hr{Resphan}{\resphain}. 





\subsubsection{The Vortex}
The \banes{} try to open a dimensional gate called the \quo{Vortex}. 

The Vortex is actually not a mere portal but a deeper merging of the planes, a connection allowing a high degree of free movement from \Erebos{} to \Nyx{} and on to \Miith{}. 









\subsection{\Draconian{} Aspect}
\target{Nexagglachel and Thanatzil}
This book also has a \draconian{} aspect: 
While \Semiza-tachi are trying to bring \banes{} to \Miith{}, \Nexagglachel{} is fighting to unite the \dragons{} and reclaim \Miith{} for their race. 
The \dragons{} are \hr{Dragons disorganized}{terribly disorganized}, and \Nexagglachel{} hopes to change that. 
They are waging wars against one another and against their rival races, the \quiljaaran, \vorcanths{} and \nagae. 





\subsubsection{\Draconic names for \banes}
\target{Draconic names for Banes}
The \dragons{} had their own names for the \banes: 
The Alien Ones, the Sinister Ones, the Spawn of Darkness. 









\subsection{The other races}
Have plenty of \aryothim, \vorcanths{} and \quiljaaran{} in major roles in this book. 

Maybe even turn \Vexstrasshin{} from a \dragon{} into a \quiljaar. 









\subsection{When is it?}
When did this story take place? 
When did \Thanatzil{} live? 

It could be just few years after the \hs{Draconian Ascendancy}.
Or it could be thousands of years later. 















\section{\Numah}
\target{Girigor}
\target{Numah}
\index{\Numah}
Over thousands of years, various groups, independent of each other, discover this energy source. \Numah, the \nephilic{} kingdom ruled by \hr{Semiza}{\Semiza} is one of them. 

In \Numah\dash and among many other \nephilic{} peoples of that time\dash the written tongue was sacred and secret, known only to the priest-mage class and surrounded in much mysticism and ritual. It was closely tied to their magic. 

Back then, sorcerer-kings ruled. 
It was before the \feud{} came to dominate and manipulate everything, remember. 
(In the days of the \charade, \hr{Sorcerer-kings}{sorcerer-kings} are usually dethroned by the master races, who \hr{Master races seek to control magic}{try to control magic} and fear the threat that such a ruler might potentially pose.)

\Numah{} is very misogynistic, \hr{Nephil misogyny}{as the \nephilim{} are wont}. 





\subsubsection{Language}
The language of \Numah{} should resemble ancient Sumerian or Babylonian. 





\subsubsection{Magic}
\target{Numah bones}
\Semiza{} and the other mages had some magic skulls and bones that originally belonged to their sorcerous ancestors, or even dead gods. 
Even in death, these bones retained some magical power. 
They had been handed down for centuries. 
Some of the oldest and most powerful sorcerers' bones were still preserved. 

\ps{\Semiza} people created a \matrix{} from the souls of their great dead mages. 
But they had to deal with forbidden powers, including the \xss{} that dwelt beneath the earth. 

\citeauthorbook{RobertEHoward:RedNails}{Robert E. Howard}{Red Nails}{
  \quo{Madness and death lurk in it. 
    The wizard of Xotalanc understand its secret\dash they found it in the catacombs, where lie the bones of terrible kings who ruled in Xuchotl in the black centuries of the past. 
    To gaze upon its freezes the blood and withers the brain of a man who understands not its mystery.}
  
  \quo{In life it housed the awful brain of a king of magicians! 
    It holds still the life and fire of magic drawn from outer spaces!}
}

The \nephil necromancer-kings at this time derived much knowledge and power from the dead.

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  I Whisper in the Ear of the Dead
}{
  I Dream of the Dead\\
  And Their Shades Showeth Me \\
  Visions Which No Living Man Can Know\\
  I Whisper in the Ear of the Dead\\
  And Mine is the UnWritten Knowledge\\
  That Lieth Under The Black Earth
}





\subsubsection{Mound of Hernon}
\Semiza's palace-temple lay on the top of the Mound of Hernon.

This is a reference to \cite{RHCharles:BookofEnoch}.

\citetitle[p.35]{RHCharles:BookofEnoch}{The Book of Enoch VI.6}{
  And they [the Grigori] were in all two hundred; who descended in the days of Jared on the summit of Mount Hernon, and they called it Mount Hernon, because they had sworn and bound themselves by mutual imprecations upon it.
}





\subsubsection{Politics and rulers}
\target{Aryoth-blooded rulers}
The rulers of \Numah, as well as many other \nephil kingdoms, were \nephilim with \aryoth blood. 

In this age, \hr{Aryothim as aloof gods}{the \aryothim would be rare and keep a low profile}. 
But the \dragons did not bother exterminating mortal \nephilim. 
So mortal \nephilim with strong \aryoth blood in their veins would take up the role as priest-kings and rule over their brethren, with only \hr{Aryothim as aloof gods}{limited support from their aloof \aryoth gods}. 





\subsubsection{Religion}
\target{Aryothim as aloof gods}
The gods of \Numah{} were \hr{Aryoth}{\aryothim}. 
The true \aryothim were few in number after having been \hr{Dragons destroy Aryothim}{hunted and decimated by the \dragons}.
So they hid and kept a low profile. 
They would support their mortal brethren to some limited extent, acting like aloof gods. 

But these gods were slain by \dragons{} (or maybe \quiljaaran) in some great battle that destroyed \ps{\Numah} civilization. 
After this great defeat, \ps{\Semiza} people were hunted down and killed by the legions of \cregorrs{} and \scathae. 

Remember to have flashbacks of this terrible battle.
\Semiza{} and others have nightmares about the evil day when their world was destroyed and all they loved was torn from them. 
They even had to watch their gods die. 

\lyricsbs{Iced Earth}{Setian Massacre}{{\obeylines
  Screaming in agony, cries fill the air \\
  Eyes once full of hope shedding tears of despair \\
  All that they've ever known is dead 
  
  Fire reigns from above, iron birds of dread \\
  All that they ever loved is dead \\
  All that they ever dreamt is dead 
  
  Temples are burning, streets soaked with blood \\
  Heed the prophecy, destiny is done \\
  All that they ever loved is dead \\
  All that they ever dreamt is dead 
  
  Yet there's a glint of hope \\
  If the chosen can survive \\
  In secret the ten thousand hide \\
  East in the mountains \\
  The chosen bide their time \\
  The Clouding, our strike on mankind 
}}

They are now a people forsaken, alone and unprotected, with no gods watching over them. 
Therefore many are prepared to embrace the \banes. 
But many subjects refuse to accept the fact that the gods are dead. 
They insist that \trope{HesJustHiding}{They Are Just Hiding} and keep praying to them. 
\Semiza{} and \Eshayzal{} despair over this display of stupidity and stubbornness. 
Meanwhile, some among the people resent their king for so readily abandoning the gods they have served for a thousand years (or whatever) and take up the first new religion that walks by. 





\subsubsection{Technology}
\index{technology!\Numah}
The technology is low. 
Late Stone Age or early Bronze Age. 
They have mostly stone and bone tools. 

Comparable to early Egypt. 

The only metal weapons they have are those few they can buy or steal from the \scathae{} and \cregorrs. 

Also, they do not have the skills to tame \saurians{}, so they only have mammals domesticated. 
Including some hyaena- or \latinname{Hyaenodon}-like dogs they use in war. 





\subsubsection{Other \nephilic{} societies}
There had been many other \nephilic{} societies before \Numah. 
Many of them were considerably greater, more powerful and more advanced than \Numah. 
But whenever one would rise too high, the \scathae{} would come to wipe them out. 

\index{Zibrid}
Other kingdoms that lay near \Numah in the same time period were Zibrid and Crimur. 















\section[Semiza and Ilu (\yds{Semiza birth})]{\Semiza{} and \Ilu (\yds{Semiza birth})}










\subsection[Semiza (\yds{Semiza birth})]{\Semiza (\yds{Semiza birth})}
\Semiza{} was the eldest son of the \nephil{} sorcerer-king of \Numah. 
Later he would take the throne and become sorcerer-king himself. 





\subsubsection{Young \Semiza}
Early on we see him passing some kind of \quo{manhood test}, marking him as a full-fledged sorcerer and a worthy heir to the throne. 

At an early point, \Semiza{} meets some girl that he likes. 
Either right after his rite of manhood or some time after, he is betrothed to her. 

Some years pass. 
The Jocainites hear the tales of war, of some terrible invaders from the sea devouring entire kingdoms. 
The king and mages are concerned, but \Semiza{} is still young and untroubled. 

Then comes the day of \Semiza{}'s wedding. 
On this, supposedly the greatest day of the young prince's life, the \dragons{} invade Jocain. 
It becomes massacre and young \Semiza{} sees his bride and his entire family slaughtered before his eyes. 

\Semiza{} and a few survivors flee to a system of underground caverns. 
Somehow they manage to survive the \draconic{} army's onslaught. 
\Semiza{} assumes the mantle of king and leads his people in exile. 





\subsubsection{\Eshayzal}
\Eshayzal{} is \ps{\Semiza}{} trusted friend and advisor. 

\index{technology!\bane}
The two are great geniuses and will later be able to perform miraculous feats of science using the \hr{Bane technology}{knowledge supplied to them by the \banes}\dash knowledge which is in turn \hr{Voyager technology}{stolen from the \voyagers}.





\subsubsection{Adult \Semiza}
Now \Semiza{} was sorcerer-king.
He had many wives and concubines. 

He hates the \dragons{}. 
Now, the \dragons{} were tyrants and had always been preying on his people, but I think there should be something more personal in it. 
Perhaps \ps{\Semiza}{} most dearly beloved wife or concubine or son\dash or more than one\dash was/were killed by \dragons{} or their minions in one of their raids. 

Anyway, this makes him bitter.









\subsection[{\Daggerrain contacts Semiza}]{\Daggerrain contacts \Semiza}
Throughout the millennia, there had been many people\dash thousands, perhaps millions\dash whom \Daggerrain{} might contact and who might stand a chance of succeeding in bringing \banes{} to \Miith. 
But \Daggerrain{} was patient, so he waited until he found the perfect situtation. 

\Semiza{} was a scientific genius, as was his partner, \Eshayzal. 
And \Semiza{} was bitter at the \dragons{} and longing for revenge and a \quo{return to glory} for his people. 
And his rule coincided with some nasty wars among the \dragons. 

\Daggerrain{} chose him. 

The \dragons{} had forgotten the \nephil{} survivors and thought nothing of them. 
Hiding in his underground lair, Semiza nurtured his hatred and dreams of revenge against the \dragons{}. 

Somehow Semiza reached out into the Cosmos with his mind. 
Perhaps he was deliberately searching for allies; perhaps he was taking mind-expanding drugs. 
By whatever means, he contacted \Daggerrain. 
Or \Daggerrain{} contacted him. 

Daggerrain penetrated the \ps{\nephil} vulnerable mind and probed around in it. 
He took from the sorcerer-king's mind his language and his entire memory. 
Then he introduced himself to the \nephil{} king, offering him the power to take his revenge, destroy the \dragons{} and restore his kingdom, that he might rule forever as an immortal king. 
In return, \Semiza{} had to help \Daggerrain{} bring his people to \Miith{}. 

At this point, Semiza asked: 
\ta{Who are you?}

In response \Daggerrain{} sent a vision where Semiza found himself alone and naked amid an endless, featureless plain, with a cruel and unrelenting hail beating down upon him with its sharp shards of ice, like a rain of a million daggers. 
Semiza interpreted the \banelord{}'s name as \quo{Daggerrain}. 

If he was to help Semiza and his people, Daggerrain needed the \nephil{} sorcerer to bring him to \Miith{}. 
He instructed the \nephil{} in the spells to use, and \Semiza{} went to work procuring occult ingredients and sacrifices (mostly \scathae) and recruiting and training mages to assist in the spellwork. 
The preparations took perhaps several years, but at last they are ready to perform their summoning ritual. 







\subsubsection{\Semiza{} turns from his gods}
\Semiza{} feels that his people's gods have betrayed him, so he searches for new ones. 

He feels like a pawn, adrift in sea governed by vast powers beyond his ken. 
He feels impotent, and he rages. 
He wants to regain control of his own fate and that of his people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Let me embrace my fate which was adrift and hung. \\
  I will be again the apple of his eye. \\
  Take me from among the doomed Laodiceans \\
  whose defamation thrilled the seething skies.
}





\subsubsection{\Semiza{} feels the calling of dark powers}
At first, \Semiza{} vaguely feels the call of dark forces from the Beyond. 

\lyricslimbonicart{Moon in the Scorpio}{
  A mirror blank ocean above me decoy.\\
  Superior forces that heal or destroy.\\
  Take me astray into the moonlight above
  through twilight eyes as a spectre shadow.
  
  It is a time of great light\\
  and of great darkness.\\
  Can you feel the presence\\
  of its phenomenon?
  
  In an atmosphere supreme\\
  forces dwell in domancy.\\
  The essence of its spirit is evil,\\
  as a curse upon thy name.
  
  Midnight is the shepherd of mysterious powers\\
  and moving shadows in the corner of the eye.\\
  Moon's blazing intuition\\
  contains what death requires.
  
  Cleanse the doors of perception.\\
  See things appear in its true art.\\
  The cold hands of divinity\\
  will tear thy soul apart.
  
  Behold the sky above \\
  when the moon is in the Scorpio.\\
  A cold bleak light
}

\Daggerrain{} haunts him. 
He tells \Semiza{} that he is the only hope for \Semiza{} and his people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Night after night grim voices shriek \\
  in portentous horror dreams, \\
  even though his room was locked, \\
  but a Seraph comes unseen. 
  
  Night after night his skin was flogged. \\
  Damn those recurrent dreams. \\
  Desperately flogging for relief \\
  while murmuring blasphemies. 
  
  The bloodstained walls surround him, \\
  icons made of Calvary wounds. \\
  Dreams of riddance were shattered in sin, \\
  ill-fated to avert doom.
}

He learns more of these dark new powers. 

\lyricslimbonicart{The Supreme Sacrifice}{
  I stand within the flame,
  watch the wisdom be discovered.
  When life and death is the same,
  I am devoured.
  
  So many nights I have spent \\
  in thoughts not heaven sent.\\
  Blood of hatred poured down like rain \\
  for evil secretus insane.\\
  In silent gloom I kneeled obsessed,\\
  channeling the enigmatic darkness.\\
  My soul, the servant\\
  under the illusive wings of death.
  
  When I receive a black picture of the future,
  and schockwaves attack from a nihilistic universe.\\
  My body, the temple, a mausoleum in flesh\\
  under the illusive wings of death.
}

He is overwhelmed with awe. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  The man started to cry, hands held to the sky,\\ 
  and expected to be purified in flames. \\
  But the Angel smiled and took the Book \\
  and commanded his holy mandate.
}

He was looking for a way to seize control of his own destiny, and this is it. 
He jumps at the chance and devotes himself to serving the \banes.

\lyricslimbonicart{Behind the Darkened Walls of Sleep}{
  I open gates and close the others. 
  Behind me now there is no return. 
  I broke the sealed door to imagination. 
  The pulsating darkness now around me burn.
}

\Semiza{} has a terrifying enlightenment scene, where \Daggerrain{} shows him the mysteries and wonders of \hr{The dark universe}{the dark universe}. 

He shares it with a select few subjects.





\subsubsection{The name \quo\bane{} is born}
\target{Semiza names Banes}
\Semiza{} is overwhelmed by the power and glory of \Daggerrain{} and his people (and the \Voidbringer). 
He believes that these gods will be the salvation of his people and the bane of all their enemies, and so he names them the \quo{\banes}. 

It was \Semiza{} who named the \banelords, including \Daggerrain, and it was he who coined the term \quo{\bane} for their race, since he envisioned them as the bane of his hated enemies, the \dragons. 
Not until a late time does he realize that they are the same creatures that fought the \dragons{} thousands of years ago. 

The \dragons originally had \hr{Draconic names for Banes}{other names for the \banes}. 





\subsubsection{\Semiza{} introduces the \bane{} religion}
\target{Bane religion}
\Semiza{} preaches to his people of the new gods he has discovered. He promises that they will save his people. In exchange, they must worship and serve them. 

Perhaps at first \Semiza{} does not know that the \banes{} are an entire people. He might think it is just a single god (\Daggerrain), whom he names \quo{the \bane}. 





\subsubsection{\Daggerrain{} reveals his true nature}

At first, \Daggerrain{} comes in disguise. 
It is only later that he shows \Semiza{} his true face.

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  The Fallen Seraph lowered his radiant mask \\
  and showed the man the countenance of the fallen Morningstar.}

Semize is terrified. 
But there is no way back. 
\Semiza{} gives him the name \quo{\Daggerrain}. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  The man seemed stricken by a thousand bludgeons. \\
  Penetrating just-healed wounds as foreplay for the storm.
}









\subsection[{Semiza builds a stargate}]{\Semiza builds a stargate}
\target{Semiza's stargate}
\Semiza{}, working under the \psp{\banelords}{} guidance, builds a great temple that is to act as a stargate, a focus for the portal to \Erebos. 









\subsection{The \banemessiah}
\target{Bane Messiah}
%The plan is that the \nephilim{} must provide a 
The plan is to give birth to a \quo{\banemessiah}: A superbeing, born of a \nephilic{} mother but invested with the life force of the \banes{} and possessing the power to open a conduit to \Erebos{}. Through this conduit they will be able to draw more energy and spawn more people like the Messiah, thus founding a whole race of half-\bane{} demigods. 
When there are enough of them, they will be able to challenge the \dragons, overcome the \hr{Crystal Sphere}{\CrystalSphere} and grant \Daggerrain{} and his people unrestricted access to \Miith{}, whereupon they will march in like a conquering army, scouring the world of the \draconian{} tyrants. 

\target{Thanatzil is the gate}
So the Messiah \emph{is} the key and the gate, an incarnation of the \bane{} soul and legacy. If \hr{Thanatzil fails}{he dies, the portal collapses}.









\subsection{The Shroud of \Numah}
\target{Shroud of Girigor}
\Daggerrain{} took some threads, components, techniques and ideas from the \hr{Crystal Sphere}{\CrystalSphere} and used them to weave a small Shroud around \Numah, thus shielding \Semiza-tachi and the \resphan{} project from prying \draconian{} eyes. 

Later he went on to \hr{Shroud of Nyx}{weave a similar Shroud on \Nyx}, but that did not work out so swell.









\subsection{\Vexstrasshin{} suspects}
Most \dragons{} suspect nothing. 
When \ps{\Semiza}{} people start invoking \banes{}, no one believes it. so they are allowed to proceed. 

\target{Dragon war when Resphain appear}
Also, this coincides with a bloody war among the factions of \dragons{} (\Tiamat{} is dead, after all), so they are busy fighting each other and have little time left to investigate alleged \bane{} summoning. 
This war is, to some extent, masterminded by \Daggerrain, a part of his \trope{XanatosGambit}{Xanatos Gambit}. 

But at least one \dragon{} suspects that \ps{\Semiza} new religion and this whole \Thanatzil-business is \trope{SeriousBusiness}{Serious Business}, namely \hr{Vexstrasshin}{\Vexstrasshin}. 
Her fellow \dragons{} do not believe her (being caught up in their own wars), so she sneaks into \ps{\Semiza} city in disguise. 
Here she tries to discover what is up. 

When she discovers \Thanatzil, she tries to stop him. 
She fears him. 





\subsubsection{Cameos}
Have some cameos with the \dragons{}: 
\Nexagglachel, \Ishnaruchaefir, \Secherdamon, \Triestessakhin, perhaps \Nzessuacrith{} (she was very young). 
They were all very happy back then. 
\trope{ItGotWorse}{It Got Worse}. 









\subsection{\Ilu, the Sacred Mother (\yds{Ilu birth})}
First of all, the \banes{} need a mother for their Messiah. \Semiza{} chooses his most beautiful, most beloved young daughter who is still an unmarried virgin: \hr{Ilu}{\Ilu}. 

\Ilu{} has been raised to be very loyal and obedient to her father and king and to her people, so when she is chosen as the Sacred Mother, she could not refuse even if she were given the choice, which she isn't. She is honoured to be selected as the instrument of her new god's will. 

But there is a catch. Rather, two catches. 

\begin{enumerate}
  \item 
    The pregnancy and birth will be very hard and painful for her, so she must be strong and brave and endure much hardship for the sake of her god and her people.
  \item
    She \emph{must} be an untouched virgin. Otherwise it will all be much worse for her, and she may die.
\end{enumerate}

\Semiza{} is convinced and offers his beloved daughter as a sacrifice to the \banes. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  She is Thine, O take her quickly. \\
  Thou art her hope, O raise her high. \\
  Ever hoping, ever trusting, \\
  unto Thee I strive and cry.
}

He will make her a heroic martyr. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  But shall she be refined in Thine holy light? \\
  Her spirit will shine will thousand suns. \\
  Condone my doubt, but who am I? \\
  The haranguing priest of the newborn Herod king.
}

He just wants to save his people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Let them through thy boundless mercy \\
  from all evil be restored. \\
  Hearken to the voices pleading \\
  of Thy Church, O gracious Lord!
}

She has one purpose. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Born with the ability of begetting\\
  Only but One gift were she granted\\
  To excrete a new humanity unwanted\\
  Reluctantly she\dash woman\dash \\
  loves the god of a creation within
}





\subsubsection{\ps{\Ilu}{} sin}
\target{Ilu's sin}
The virginity requirement is a problem. See, \Ilu{} has \hr{Ilu's lover}{a lover}. They haven't had actual vaginal intercourse, so she is still a virgin. But they have done\prikker \emph{stuff}. She has sucked his dick. Only once, but it is enough that she cannot call herself \quo{untouched}.

But she was not supposed to suck his dick, and she dares not confess to her father that she did it. So she lies and proclaims herself untouched. \Semiza{} and everyone else is happy, and they proceed with the process of impregnating her as the Sacred Mother. 

Or maybe she was never asked, because her father considered her virtue to be beyond question. 

\Ilu{} is scared shitless. She is afraid that because of her wicked promiscuity (as she sees it), the whole project is in danger and may fail, and her people may never be saved. She has lots of guilt over this, but she is too afraid to come clean. She has lied to her father and made it all worse for herself. 

She's done other sexual stuff, too, but only touched a man's dick this once. And it's the worst part. The penis plays a huge role in their old religion, rituals, symbolism and sexual mysticism. The vagina is also important, but doesn't have as big a role as the penis. They are a masculine, patriarchal people who worship the phallus as a symbol of strength, fertility, masculinity, life, initiative and all that is good. In sex, the man and his mighty dick conquers the woman and binds her as his slave and property. He plants his seed in her womb, thus claiming it as his domain, and by extension, the woman must serve and obey him. (Perhaps you can even legally steal another man's virgin daughter by raping her, based on this mysticism.)





\subsubsection{She wants to conquer her sin}
\target{Ilu wants to conquer her sin}
She decides that she has brought the problem upon herself and is responsible for dealing with it. So she resolves to fight as hard as she can for the sake of the god-child that will soon be growing inside her. She swears that she will fight her own sin and vanquish it, and that the god-child \emph{will} be born. 

\Ilu{} is religious and prays a lot. To the old gods of her people, and to \hr{Bane religion}{her father's new gods, the \banes}\dash the \quo{fathers} of her child.





\subsubsection{Earlier attempts and giving birth to \resphain}
\Ilu{} was not the first woman who tried to give birth to the \banemessiah. Several other women had tried and died horribly before. 

The real reason for this is that first experimental \resphan{} foeti were \emph{too} voracious, too greedy, too parasitic. In their hunger they drained too much life-force from their poor, suffering mothers. The mothers would die long before the children were ready to be born, and the children would die as well.

But this was covered up. The official story, as told by \Semiza{} and \Eshayzal, was that the women were weak of faith and will. They had failed their god and their people. This put great emotional stress on poor \Ilu, who feared that she, too, would not be good enough, and would ultimately fail and die. 

There was always only one prospecting Sacred Mother at a time. The \banelords{} invested all of their \resphan{} power into the one \banemessiah, and so could only incarnate one at a time. Whenever one would die, the \banes{} would quickly reclaim the power and recycle it. 

Whenever the Sacred Mother started bleeding, mutating and suffering badly, she would be secreted away deep in a temple and kept hidden until her inevitable and grisly death. Thus, no one knows how horribly they suffer and die. 

Thus, \Ilu{} is happy and full of hope. She believes that she has been chosen for something wonderful and will give birth to a beautiful saviour. \Semiza{} assures her that she is the right one and that it won't go wrong this time. 

Perhaps \Semiza{} had long known that \Ilu{} was a good candidate. But out of love for her he didn't select her at first, because he knew the danger. But \Daggerrain{} tells him that she has the best chance of succeeding\dash and even a chance of surviving (not a lie). So at last, \Semiza{} chooses her. And she does fare better than many, because of her strong will and idealism. 





\subsubsection{Old artifacts consumed}
\Semiza needed a lot of old \aryoth relics in order to create \Thanatzil and imbue him with all the power of the greatest ones that \nephil-kind has to offer.
He took some \hr{Numah bones}{old magical bones and skulls and mummies} and destroyed them in the process.
The priests of the old religion were not happy at all, and neither were the people.
It was hard for \Semiza.
He cursed them for being so backwards and ignorant and unwilling to change.
They could not see that their old religion had failed them and that they needed to look elsewhere.
\Semiza was sad that he was one of the only \nephilim who saw with an open mind.









\subsection{The seed is sown (\yds{Ilu pregnant})}
\target{Semiza designs Resphain}
\target{Origin of Resphain}
\Semiza{} and his sorcerers, under guidance from \Daggerrain{} and his \banelords, labour to prepare the arcane ritual that will impregnate \Ilu{} with the Messiah, the first \resphan. 

This must be done in secret, so that the \dragons{} do not suspect.

\hr{Entropy}{The \banes{} suffer from stagnation and cannot easily create new things}. So they needed the help of an ingenious mortal mind to engineer their new super-race.
So \Semiza{} ends up acting like the primary artist and designer behind the whole \resphan{} project. He understands \ps{\Daggerrain}{} vision of a super-creature with traits from \banes, \voyagers{} and \nephilim{} alike. The \banes{} can supply them with knowledge, but they must do the research themselves.

At \ps{\Semiza}{} side stands \hr{Eshayzal}{\Eshayzal}, his companion and advisor. Together they engineer the \resphan{} god-child. 

They worked hard for some time, and finally the research was complete. 
They were ready to perform a magical ritual and impregnate \Ilu{}. 




\subsubsection{Ritual prepared}
They began the impregnation ritual of poor \Ilu. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Thou shalt bringeth the chalice of divine wrath \\
  and final consummation to thine lips, \\
  and drink with confidence\prikker\\
  Tell me, sweet child, \\
  why are tears rolling from your eyes?
}




\subsubsection{Invocation of the \banes}
\Semiza-tachi invoke the \banes. 

\lyricsbs{Hate Eternal}{Catacombs}{
  Rise up from the ancient tombs. \\
  Grant us all your infinite wisdom. \\
  Endure as you rise from the catacombs. 
}

\lyricsbs{Hate Eternal}{The Creed of Chaotic Divinity}{
  Awakened by this ancient creed. \\
  Evoked, the ancestry of thee.\\
  Forsaken for centuries of times. \\
  Exiled, all of their kind. \\
  Foretold, the inheriting of the Earth.\\
  Forewarned of this predestined rebirth. \\
  Engaged, the rising from below.\\
  Fear, all mortals, for what they shall bestow.
  
  Conjure all, so that they may sustain\\
  their race, of what they must retain.\\
  Spew forth incantations in vain. \\
  Invocate all that they try to negate.\\
  Enchant all of their wonderful splendour. 
  Recant all of the texts that are sacred. \\
  Recreate all that has been begotten. \\
  Revive all that has been forgotten. 
}




\subsubsection{\Ilu{} impregnated}
\Ilu{} was knocked up. 
This happened in an aethereal, sexual dream sequence. 
She was half-raped, half-seduced by faceless, unclear, monstrous, almost-but-not-quite-\nephil-like monsters:

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Organic procreation, mind-intromission; there comes the salvation\\
  Pubescent vaginas obstructed with the redeemer's holy essence\\
  Humanity reduced to its supreme worthlessness;\\
  Children under His will, Ethic fulfilled
}

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Carnal Malefactor
}{
  There resides the fusion, there is the nucleus\\
  Angel prick and holy semen,\\
  And a woman genuflecting an aroused beast of burden alike\\
  Seduced by the father and seducing the son\\
  There resides the fusion, there is the nucleus\\
  A phallic communion that sanctifies interior wastelands
}









\subsection{\Ilu{} suffers}
\Ilu{} suffers horribly during her long pregnancy. 

How long is her pregnancy? The gestation period for \nephil{} women needs not be nine months like it is for \humans, and the gestation period of the \banemessiah{} needs not be the same as that of a \nephil{} child. 

It might be longer than nine months. And the sorcerers might need to perform many spells on her while she carries the child. And she would be required to work hard to aid them in their spellwork. (How?) 

\Ilu{} believes that it is \hr{Ilu's sin}{her own sin} that causes her to suffer. That and her weakness. She is intent on conquering her sin, so she fights hard, not only to combat her weakness, but also to hide it. She \emph{will} be strong. She \emph{will} serve her people well. She \emph{will} make her father proud. His faith in her shall not have been misguided. 

In truth, \ps{\Ilu}{} little blowjob had no effect at all (except psychologically). The \banes{} needed physical virginity for some reason. Why? Because there is some \hr{Heart}{Heart of \Miith} related power in her womb and sexual organs that they need to harvest, and that power is weakened when a girl loses her virginity. 

Anyway, the point is that all of \ps{\Ilu}{} suffering is not her fault. It is caused by the \banes{} and the \halfbane{} child growing inside her. 
As the mother of the \erebean{} abomination, she is cruelly abused. 
She is cruelly abused by the parasitic abomination growing inside her. It sucks out all of its own mother's life-force. She grows weaker and weaker and will eventually die in childbirth. 

%The \nephil{} women who had to give birth to the first \resphain{} are cruelly abused. They carried and delivered the children in gruesome pain and suffering, and the parasitic children sucked out all of the mother's lifeforce, killing her in childbirth. In fact, the first experimental \resphan{} foeti were \emph{too} voracious, killing their mothers long before they were ready to be born, and then died. As the mother carries the child, she suffers horribly as the gruesome thing sucks everything from them. 

Compare to the Mhybe from \cite{StevenErikson:MemoriesofIce}, except that all the suffering takes place \emph{before} the birth (whereupon she dies). Also compare to \bandsong{Hour of Penance}{Hideously Conceived}. 

She dreams of her wicked child and his evil \quo{father}. 
She is afraid. 

But it is important to note that Ilu is not against the whole thing. 
She laments the fact that she must suffer, but she tries to be strong because she knows it is the right thing to do. 
Her suffering will bring much good into the world. 

\Semiza{} and the others try to support her and be nice to her. 
She is their beloved and holy martyr, and they admire her for doing it. 
\Semiza{} tries to be a good and loving father, but his crazy religion somewhat estranges him from his people. 
Ilu laments this. 
She doesn't want her father to be alone and weird. 
So she is extra brave for his sake. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Night after night grim voices shriek \\
  in portentous horror dreams, \\
  even though his room was locked, \\
  but a Seraph comes unseen. 
  
  Night after night his skin was flogged. \\
  Damn those recurrent dreams. \\
  Desperately flogging for relief \\
  while murmuring blasphemies. 
  
  The bloodstained walls surround him, \\
  icons made of Calvary wounds. \\
  Dreams of riddance were shattered in sin, \\
  ill-fated to avert doom.
}

According to the theory, her suffering is partially caused by the \kenosis: 
The process by which the god (to whom she must give birth) is incarnated in the form of a feeble foetus. 
This process is difficult and painful, and it is \Ilu{} who must bear this pain. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Obedience to the point of death,\\
  Falling down through increasing pressure\\
  Into the deathlike region\\
  Of ooze and slime and decay\\
  These are the fruits and symptoms \\
  of the abasement of the World,\\
  The assumption of humanity \\
  and the simultaneous occultation of Divinity
}





\subsubsection{Hentai nightmares}
\Ilu{} feels terrible guilt over having sucked dick. She has frequent nightmares of being forced to suck dick. She might be in a forest of penises, like monstrous trees or fungi or worms or snakes that slither around her and try to sneak into her mouth and other openings. Perhaps faceless men with penises (and no other recognizable \nephilic{} features) crowd and rape her.

Hentai!















\section{\Thanatzil{}, the \BaneMessiah (\yds{Thanatzil birth})}
\subsection{\Thanatzil{} is born}
At last, the \banemessiah{} is born. \Semiza{} gives him the name \hr{Thanatzil}{\Thanatzil}, which probably means something in their language. 

The story of \Thanatzil{} is very much inspired by the Christian myth of Jesus, and is intended, to some extent, to be a very dark, sick, twisted version of the Jesus myth. I need to have plenty of Jesus-like symbolism surrounding him.

\begin{itemize}
  \item 
    He is born of a virgin by immaculate conception.
  \item 
    \Nephilic{} kings come to greet him and pay homage to him at his birth. These are the kings of other tribes who have allied with \Semiza, swayed by his vision and his new religion. 
  \item
    He is an earthly/\Miithian{} incarnation of his gods, the \bane{} people, and born as a saviour to deliver the \nephilic{} people. 
  \item
    He \hr{Thanatzil must die}{must die and be resurrected} in order to save his people from hellish imprisonment. 
  \item 
    His birth is heralded in the heavens by a \hr{Black stars of Nyx}{black star} that shines through from \Nyx, or perhaps even \Erebos. It is a temporary portal through which flows power and a \bane{} soul from \Nyx{} into \ps{\Thanatzil}{} body. It is visible everywhere on \Miith{}, and some \dragons{} take note.
  \item
    \Nephilic{} kings came to visit and pay homage to the newborn \Thanatzil. These were allies of \Semiza{} who believed in his new religion and his vision of a future for their people. 
\end{itemize}





\subsubsection{\Thanatzil{} appears}
\ps{\Thanatzil}{} birth is terrible to behold. The infant is unlike any \nephil: Short and slim, black as midnight, and completely naked (where \nephilim{} are covered in hair, even from birth). He remains bald and hairless throughout his life. And he has feathered wings on his back. 


\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Carnal Malefactor
}{
  When a woman is knead by the claws of fowls attracted\\
  By seminal odours no longer hidden by dignity\\
  And purified by their beaks rummaging her swollen vagina\\
  When laments alter into praises \\
  despite holy duty and menacing perdition\\
  Seers can say that his birth does death subdue no more\\
  His birth does death subdue not, \\
  for my God proceeds of failed humility\prikker\\
  O Master, the eastern pillar of your domination \\
  is the organic fallibility.
}

The Messiah comes into the world riding a river of blood, tearing apart the flesh of his screaming, dying mother. He utters no cry, but rises to his feet (impossible for any normal \nephilic{} newborn) and gazes at everyone with his cold, wicked eyes, gleaming with an unearthly incandescence. The sight of this un-\nephilic{}, naked, winged creature, black-skinned and covered in blood, seeing deep into everyone's soul with eyes revealing knowledge and intellect that should by right be beyond any infant, is chilling and morbid to behold, but also awesome. Most of the people are already blinded by their religion and its mind-controlling magic, so they see him only as a beautiful, magnificent, majestic saviour. 

(It is somewhat strange that he would rip his mother open, since he is smaller than a \nephilic{} child. But he does, because his birth and his very nature are so violent and cruel.)





\subsubsection{\Ilu{} dies}
\ps{\Ilu}{} body is only a bleeding ruin at this point, but she lives a few more moments. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Innocence sacrificed and heaven denied\\
  Iniquity divine\dash no repentance\dash over mankind\\
  Mind-raped, self-devoured, empty god-eyed\\
  Transgression coercive, Redemption never to be found

  Under the altar of cannibalism\\
  Man hast (thou) confessed the spiritual schism\\
  And without pride mourned the loss of freedom,\\
  Our blessed Lord have condemned you to martyrdom
  
  Let everything that hath breath praise the Lord, \\
  praise ye the Lord.
}

She sees her son and sees that he is alive and healthy. She feels the power and life force radiating out from him\dash power that he stole from her. He turns and meets her gaze. She recognizes the monstrously alien soul inside him, but he is still her son, her flesh and blood, so she loves him. He gives her a half-smile of gratitude. She is happy, knowing that she \hr{Ilu wants to conquer her sin}{conquered her sin in the end} and so fulfilled the quest she undertook. Her hard work, prayers and suffering have borne fruit and she has redeemed herself. She has served her father, her son, her kingdom and her gods. She is happy to die for this. And so she does, with a smile on her lips and her body torn to shreds. 

\lyricsbs{Monolith Deathcult}{Der Kriegmeister}{
  For the glory of Death and the crown of the horns.\\
  I murder like Manson when I cut out her womb.\\
  In the blood that she bled she lay drowned in her tomb.
  
  Suffocate, inhale death's breath. \\
  The crown of thorns tortures my head.\\
  Rape my wounds, my doomed bloodlet, \\
  receive my last caress.\\
  Demonclaws tore my skin, \\
  salicious women prove my sin.\\
  The seventh day had just begun, \\
  and soon your God will die.
}

\Ilu{} believes in the \banes{} and in \Thanatzil{} even with her dying breath. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  First Prayer
}{
  Lungs filled with embers and regurgitating boiling blood I say:\\
  Praise the Lord, praise,\\
  O servants of the Lord\prikker\\
  We will sing a new song to thee,\\
  O God: a psaltery of thirteen Stations. \\
  May scoria bury Eden and blind the light of hope\prikker
}





\subsubsection{Do more research}
I should do more research on Jesus, Horus, Mithras and other similar gods. 









\subsection{Rebels}
\target{Rebels against Semiza}
\target{Semiza's rebels}
Some of \ps{\Semiza}{} subjects are horrified by the evil of this new religion and the insanity of the king's plan. They begin to work against \Semiza. Their heroic deeds are essential in defeating the \banelords{} by \hr{Semiza fails}{interrupting \ps{\Thanatzil}{} resurrection}. 

Compare this to the rebellion in the \emph{Star Wars} movies.

They dislike the king's blasphemy against the old gods. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Shrovetide is violated by heathens. \\
  Nefarious splurges of sin. \\
  Persuasion is trembling with fever \\
  and became a mantra of occult tongues. \\
  Mankind enclasped Doom. \\
  He turned his back on God. \\
  Virtue became ultra-decadence. \\
  We are all libertines of the damned.
}





\subsubsection{A rebel Messiah}
Maybe the rebels have their own Messiah-figure, a representative of their old gods. 
Probably a woman. 
She founds the rebellion. 

She is secretly backed by \Vexstrasshin. 
Perhaps even possessed by her. 

Perhaps she is killed by \ps{\Semiza}{} people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  A Fidei Defensor arises, \\
  flogged and whipped from head to foot. \\
  The body cleansed by self-flagellation, \\
  supressed the lust of flesh and blood.
}









\subsection{The \resphan{} race}
%In the beginning, the entire \resphan{} power is 
\Thanatzil{} wields the power of the \banemessiah. But it is not his mission to save his people \emph{alone}. Rather, his purpose is to be the founder of a new race of \halfbane{} superbeings. 

\Semiza{} names them \resphain. 
This means \quo{superhuman} or something like that in their tongue. 





\subsection{\Resviel{} are designed}
\target{Origin of Resviel}
%\ps{\Semiza}{} sorcerers now collaborate with the \banelords{} and the fledgling \resphain{} to create a race of slaves: \Humans.
\Semiza-tachi realize that the process of having \nephilic{} women give birth to the \resphain{} is inefficient. 
The \nephilim{} are too weak. 

So \Semiza{} and the \banelords{} want to create a new race of female \resphain, to act as sex slaves and birth mothers for the \resphan{} race. 
They design the \resviel. 

The \resvil{} experiment succeeds beyond all expectations, and already in the design phase, when the first \resvil{} has yet to be born, it is clear that the \resviel{} are too good to use as sex slaves and mothers. 
This is part of the motivation for \hr{Origin of Humans}{creating \humans}.











\subsection{\ps{\Thanatzil}{} life}
\Thanatzil{} grew up. 
By the age of 20 he looked like a \human{} youth of the same age. 
(This was abnormal. \Resphain{} normally grew slower than \humans.) 
He was tall, almost as tall as a \nephilic{} man, but much slimmer. 

He has the \hr{Resphan vampirism}{vampiric appetites of a \resphan}. 
He eats the hearts of people sacrificed to him, to devour their souls. 
This may or may not be distasteful to him, but he does it. 
He probably doesn't enjoy it. He is the first \resphan, after all, and he sees clearly the horror writ on every (sane) face around him when he eats hearts or does other horrible things. 
(In later \resphan{} societies, every \resphan{} does it, so it is considered perfectly acceptable.)

For all his power, \Thanatzil{} is only a boy, and it is hard for him to bear the responsibility of the \banemessiah. 

He knows that he is a scion and representative of the \bane{} people, an incarnation of their legacy.

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  I have lived for millions of years. \\
  I am the day of yesterday. \\
  I know the day of tomorrow. \\
  The Alpha and Omega. \\
  I am eternal.
}

He is a guide and holy figure to his people. 

\lyricsxkcd{40}{
  In a dark and confusing world, \\
  you burn brightly. \\
  I never feel lost. 
}

He is distressed because he feels he has no power to control his own life. 

\citebandsong{BeyondTwilight:TheEdge}{Beyond Twilight}{Salem}{
  The darkness in the crystal expresses the inner fear.\\
  The light reveals the love she holds inside her. \\
  Reborn to lead a life controlled by the sorceress. \\
  She will know what she must do to come through. \\
  
  Her life on Earth lasted only for eight years.\\
  You can see she's frightened of the dark, \\
  but you'll never see her tears. 
  
  Nightmare in nowhere land.\\
  Exempting lying poetry. \\
  Missing the life she's owned.\\
  Slowly withering away.\\
  Too young to take a stand.\\ 
  There is no remedy. \\
  Her life being overthrown. \\
  Sunk in silent prayer. 
}




\subsubsection{Devoured souls}
He feels all the souls he has devoured, feels their pain, anguish and hate.

\lyricslimbonicart{A Venomous Kiss of Profane Grace}{
  The dead speaks to me\\
  from beyond the grave.\\
  That is why my conscience is.\\
  I`ve buried the dead alive.}

But he needs their power to fulfill his quest. 

\lyricslimbonicart{A Venomous Kiss of Profane Grace}{
  The blood of the child is pure now.\\
  In death it gives me life.\\
  The circle is complete.\\
  Begin another\prikker
}




\subsubsection{Sex}
\Thanatzil began having sex when he was 15.
He soon impregnated his first \nephil women.
Soon after that \hr{Origin of Humans}{the first \humans} were born.





\subsubsection{He sees the evil that he represents}
\Thanatzil{} gazes into himself and sees the morbid evil of which he is the prophet, the messiah. 
He is horrified, but he keeps his faith and forces himself to repress doubts and fears. 

\lyricslimbonicart{Dynasty of Death}{
  Dungeon darkness in violent fire.\\
  Transfix the soul with Hell's desire.\\
  Where myriad's of lives are laid in ruins, \\
  dormant in the ashes of all terrestrial dreams.
  
  The dynasty of death.
}

He angsts over his evil. 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  A passion for my rage, with my sights of darkness.\\
  The atrocities at hand I must bare/bear. \\
  Entangled in a state so cold, so dormant. \\
  My sickened rageful state, my hateful lair. 
  
  Saturated in dejection. 
}

But he must. 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  Hardened by this reality. \\
  Sights of vengeance ever so clear. \\
  Compelled to rejuvenate this world of hate \\
  into a mass of chaos and fear. 
  
  Saturated in dejection. 
}

He eats souls and grows strong. 
This strength allows him to send his soul wandering through the Cosmos. 
He contacts cosmic gods and his \bane{} fathers. 
He gains wisdom.  

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  The sickening things that I witness. \\
  I derive distinct visions from\\
  the sickening throughts that they confess. \\
  Hatred at its purest form. 
}

He forces himself to accept it. 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  So compelled to what I've witnessed, \\
  mesmerizing, so enticing,\\
  I revel in their grief. \\
  I confess, my vision is my religion. 
}

He has a split personality of sorts, being part \nephil{} and part \bane. 

\lyricsbs{Hate Eternal}{Two Demons}{
  I am duality. A being so consumed with 
  the darkness inside of me.\\
  Through this pain I must endure 
  these beings that still haunt me.
  
  I am adversity. Within the sunder of 
  the essence of my very soul.\\
  In this rage I shall remain, 
  these creatures that become me. 
  
  Come forth and purge yourself for what you are.\\
  Reveal thyself and become what you will. 
  
  I am diversity. So weary of the angst, 
  so weary of what I have become. \\
  Through this dread I will retain, 
  this penance that still haunts me.
}

He is unsure whether what he is doing is right. 

\lyricsbs{Emperor}{Grey}{
  desperately I seize tomorrow, all out of my reach\\
  that is what I learned, this is what I teach\\
  corruption seems to flourish while promises decay\\
  where lights are dim and shades of black are grey
}

He had doubts. 
He was allegedly an incarnation of the mighty \bane-god, older and greater and mightier even than the \dragons. 
But often he did not feel like a god. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  And He is before all things, and in Him all things consist\\
  Triune God, morphed into a Being of apparent theanthropic nature\\
  Deprived of the Light of Splendor\\
  Dost thou still stand in undiminished Majesty\\
  After the exinanition of divine attributes\\
  The face of profound fire gone astray,\\
  Exhaling austerities in concealed, divine radiance?
}

\Thanatzil could feel the pressure of the \banelords upon him, and it scared him.
He felt naked and vulnerable under their dread gaze.

\citebandsong{Nile:FestivalsofAtonement}{Nile}{
  Wrought
}{
  Nanna Father of the Zonei\\
  Eldest of the Wanderers\\
  A Shadow out of Time\\
  The Moon is calling Me\\
  The Breath of the Old Ones\\
  Whispers in my Ear\\
  With inhuman Impatience\\
  They Beckon to Me

  I call to the Moon and Sin\\
  I now possess the secrets of the Tides of Blood

  I have \traveled on the Spheres\\
  And the spheres do not protect Me\\
  I have Walked in the Pit\\
  And the Pit does not protect Me

  The Lords of the Wind rush about Me\\
  The Lords of the Earth crawl about my Feet\\
  And are Angered\\
  A Wind has Risen \\
  The Dark Waters Stir
}





\subsubsection{\Semiza-tachi convince \Thanatzil}
\Thanatzil{} has plenty of doubts and fears. 
\Semiza{} and his ilk do all they can to convince him that he is doing the right thing and must continue. 

\lyricsbs{Hate Eternal}{Servants of the Gods}{
  Heed not for our sins,\\
  for our sins hath no path of impurities.\\
  For it is I who will conquer \\
  this plane of existence.
  
  Heed not for our scrolls,\\
  for our text hath no path of deviation.\\
  For it is I who will transcend to \\
  this plane of existence.
}

At the same time, \Semiza{} is thinking about his own dream. 

\lyricsbs{Hate Eternal}{Servants of the Gods}{
  I shall exact my revenge, \\
  for I am the top of the hierarchy.\\
  Heir to a tradition of unification.\\
  For I am the mother and the father\\
  and the heart of our domain.\\
  I am the wiseman.\\
  I am a thing of evil.
}









\subsection{\Humans{} are designed \yic{First Humans conceived}}
\target{Origin of Humans}
\ps{\Semiza}{} sorcerers now collaborate with the \banelords{} to create a race of slaves: 
\Humans.

Note that first \humans{} were created \emph{before} the \resphain{} (bar \Thanatzil). 





\subsubsection{Purpose}
%The \human{} men are created because the \nephilim{} and \resphain{} don't want to work and want some slaves to do their dirty, menial work for them. 
The \human{} men are created to serve as a race of worker slaves, beneath the \resphain{} and more manageable than the somewhat savage \nephilim. 

The \human{} women are created to serve the \resphain{}\dash and, to a lesser extent, the \human{} men\dash as sex slaves and mothers. Originally, \hr{Origin of Resviel}{the \resviel{} were designed to fill this role}, but they proved useful for far more than that, and were promoted, so the \human{} women were designed to fill the vacancy.

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Born with the ability of begetting\\
  Only but One gift were she granted\\
  To excrete a new humanity unwanted\\
  Reluctantly she\dash woman\dash \\
  loves the god of a creation within
}





\subsubsection{How they were created}
The first \humans{} are created by letting \Thanatzil{} have sex with and impregnate some \nephilic{} women, after both mother and father have been annointed with special spells. 
So the \humans{} are half \nephil, half \resphan\dash in other words, three quarter \nephil{} and one quarter \bane. 





\subsubsection{The experiment fails}
\target{Humans fail}
The preliminary \human{} experiments are considered failures. 
The alpha-test \humans{} were supposed to have been killed, but after \hr{Thanatzil fails}{\Thanatzil{} was killed}, the \humans{} escaped into the wild and bred true. 
Later they would be rediscovered and adopted by the \resphain. 





\subsubsection{\Demihumans}
The first \humans were diverse. 
There were several exotic \quo{\hr{Demihuman}{\demihuman}} strains that quickly died out. 

Also, remember that \humans quickly mixed with \nephilim. 
So the first \humans might very well have looked much less \quo{\human} than the later ones. 









\subsection{Madness}
\Semiza{} was going mad. 
Partly due to consorting with the wicked and scary \banes. 
Partly due to isolation and despair because his people were hesitant to embrace his new religion, even after all he had sacrificed for their sake. 
And partly out of concern for Ilu. 
He truly loved Ilu and was sad to see her suffer. 

\lyricsbs{Emperor}{Empty}{
  he is an empty shell\dash{}shell-shocked luciferian heart\\
  he is an empty shell\dash{}drained and sealed\\
  he is an empty shell\dash{}penetrating cold\\
  he is an empty shell\dash{}empty luciferian soul
  
  the constant struggle for a moment of quiet indulgence\\
  eventually stirred and quaked the earth so hard\\
  it swallowed him in a dark and heavy cloud\\
  slowly and gently starving him into insanity
  
  an inferno of ice\\
  with an ever burning \\
  bleeding heart
}

\Semiza{} knew well that he is going mad. 
But it was worth it to gain power, revenge and eternal glory.
So he kept at it.









\subsection{\Thanatzil{} is tempted by a \dragon}
At least one \dragon{} suspects that this whole \Thanatzil-business is \trope{SeriousBusiness}{Serious Business}. His/her fellow \dragons{} do not believe him, so he sneaks into \ps{\Semiza}{} city in disguise. Maybe even in the form of a serpent. 

He seeks out \Thanatzil{} in dreams and tries to tempt him to abandon his people. He doesn't quite understand what \Thanatzil{} is or what he wants. (Maybe the \bane{} power is masked so that the \dragons{} cannot recognize it. Or maybe this \dragon{} is not old enough to remember the \firstbanewar.) But he tempts the young \resphan{} with promises of power and things. 

\Thanatzil{} goes out into a desert or the like to confront the tempter. Here he finally banishes the \dragon. 

\Thanatzil: \ta{I know what thou art. Begone! Thou canst not tempt me, not canst thou thwart me.}

The \dragon{} then conspires with the \hr{Semiza's rebels}{rebels} to interrupt \hr{Thanatzil's resurrection}{\ps{\Thanatzil}{} resurrection}. 















\section{\Thanatzil{} and his Destiny (\yds{Thanatzil death})}
\subsection{\Thanatzil{} must die}
\target{Thanatzil must die}
In the beginning, the entire \resphan{} power is incarnated in \Thanatzil. 
In order to spawn the \resphan{} people, \Thanatzil must:

\begin{enumerate}
%   \item 
%     Grow to adulthood, or at least \hr{Resphan sexual maturity}{sexual maturity}.
  \item
    Impregnate a number of women with his seed. 
    \subitem
      Are these women \nephilim{} or \humans{}? 
      Probably \nephilim, since it takes at least like 12-15 years to grow a \human{} woman old enough to bear children, and \Thanatzil{} is not meant to live that long.
    \subitem
      How many women? 
      Perhaps some magical number, like 12 or 21 or 40.
  \item 
    Undergo a dark and terrible ritual in which he will die and be resurrected. 
    \subitem
      His death will release the Messiah power within him. 
      It will fly free, reach out to the \bane{} souls incarcerated in the depths of \Nyx, free these souls and allow them to pass into \Miith{}, where they can merge with the souls of \nephilim{}\dash the sons and daughters of \Thanatzil \dash and incarnate as \resphain. 
      %power and distribute it among his his sons and daughters, allowing them to be born. 
    \subitem
      His resurrection is necessary, because \Thanatzil{} is an embodiment of the connection between \Miith{} and \Nyx{} (just like how \hr{Daggerrain is the gate}{\Daggerrain{} is the key to the pathway between \Nyx{} and \Erebos}). 
      If \Thanatzil{} dies permanently, then so does the contact with \Daggerrain. 
\end{enumerate}

The resemblance to Jesus should be obvious. 

All the mothers are impregnated in one day/night\dash spells are used to keep \ps{\Thanatzil}{} dick going all that time. 
The occult rituals involved in the spawning of the \resphain{} make sure to keep all the mothers synchronized, so that all the births will happen on the same day. 

\Thanatzil{} thinks of \Erebos: 

\lyricsbs{Emperor}{The Prophet}{
  \quo{%
    It is the place where blood and soil\\
    lie beyond the boundaries of the sun}
}

He thinks of his own role. 

\lyricsbs{Emperor}{The Prophet}{
  \quo{%
    and I am its prophet \\
    I cast the shadow\\
    I absorb the light}
  
  \quo{%
    I am the prophet\\
    I bear witness\\
    I absorb\\
    I cry}
    
  \quo{%
    As I die, I shall burst wide open\\
    As I die, I shall release the apocalypse\\
    My prophecy\\
    Thus, I hold on to faith\\
    Thus, I keep the hope\\
    That it will prosper \\
    and devour}
}





\subsubsection{Mothers of the \resphan}
\target{Mothers of the Resphain}
A number of \nephilic{} women are impregnated by the young \Thanatzil{} in the months up to the sacrifice ritual. 
They are meant to stay pregnant through the ritual. 
(If they were to give birth prematurely, the children would die.)
The ritual and \ps{\Thanatzil} sacrifice will release the \bane{} energy that will empower the infants growing in their wombs so that they may live and be born as healthy \resphain{} and \resviel. 

How many mothers are there? 
Quite a lot. 
Perhaps 100. 





\subsubsection{Some mothers are hidden}
Most of the mothers attended the sacrificial ritual. 
But a few of them were hidden away. 
This was a special security precaution by \Daggerrain. 
He knew that something might go wrong at the ritual and in that case he wanted to have a few mothers left as a backup plan. 

But \Vexstrasshin{} was clever and sniffed out these mothers and had them killed. 
The \nephilic{} rebels she coerced into killing the mothers were not happy about killing pregnant and defenseless women, but they did their duty. 









\subsection{\Thanatzil{} saves the outcasts}
\Thanatzil{} summons all sorts of sick people, madmen and outcasts to him. 
He promises them redemption by the \bane{} gods, offers to give their lives meaning. 

This \quo{meaning} is to be consumed so that their souls may feed the summoning ritual. 
The \quo{redemption} is that their useless lives will be over and their deaths will serve a useful purpose (so their deaths will be more valuable than their lives ever were). 

\Thanatzil{} does not want to do this, because it feels like betrayal and dishonesty. 
But \Semiza{} convinces him that he must. 
\Semiza{} tells him of the many sacrifices he has made himself. 
\ta{Yes, it will be a painful decision. 
    But it is the duty of a leader to suffer for his people. 
    You must do the right thing, \Thanatzil.}

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Pagan Messiah\dash the almighty fiend. \\
  Abode of the damned, defiled, unclean. 
  
  Spiritual holocaust. 
  
  Plead for forgiveness. \\
  You can't resist its temptation. }

The damned die. 

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Spiralling permanence. \\
  Merciless decadence. \\
  Unethical banishment. \\
  Fall before that which summons you.
  
  Imminent dormancy. \\
  Heinous atrocities.\\
  Demons that beckon me.\\
  That which to escape is to die. 
  
  Spiritual holocaust. 
}









\subsection{The Resurrection Day}
\target{Thanatzil's resurrection}
\target{Resphain lose contact with Banelords}
The great day draws near when \Thanatzil{} will die and rise again, and with his resurrection the \resphain{} will be born. 

%I need to make up a cool name for this day. 

All the \hr{Mothers of the Resphain}{\resphan{} mothers} are gathered, as are a lot of soldiers and priests. 
The mothers are to \quo{inherit} the energy he will release with his death. 

The ritual is prepared. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Kenosis, O' theory of great peril!\\
  Blinded, sanguineous eyes and with a trembling hand,\\
  A frail androgynous being holds the perilous doctrinal balance,\\
  Robed in a maculated garment spattered with the sordid blood\\
  Of the Flagellation, of the lacerations and fierce wounds\\
  Carved by royal attributes, of the crimson spurts\\
  Dripping without end,\\
  As was celebrated the High Mass of the Comforter
  
  Kenosis, O' theory of great peril!\\
  Rob God of any attribute and fill the shattering universe\\
  With the pestilent scent of putrefaction \\
  and the glorious cloud of death,\\
  For steadfast, at any cost, He must be\\
  Solely the incarnate Word \\
  proclaimed by all the prophets and apostles\\
  Would have, in dying, an infinite value,\\
  Sufficient to atone, by His astonishing work,\\
  For the Sins of the world
}

The ritual commences. Compare it to the Babylonian myth of \quo{The Descent of Ishtar}. And the text \quo{Of the Sleep of Ishtar}, a fictional reinterpretation of aforementioned myth, found in \simonnecronomicon. 





\subsubsection{\Thanatzil{} dies}
\target{Thanatzil dies}
\Thanatzil{} prepares his sacrifice. 

\lyricsbs{Emperor}{The Majesty of the Night Sky}{
  Too long I have suffered the desert sands of time. \\
  But as I drown in darkness it will release the sign. \\
  My soul will leave this mortal coil of flesh and earthly life, \\
  to fly into the mist of night, into the nightside eclipse, \\
  and experience existence on the other side. 
  
  As a stone of scorching enthusiasm \\
  I refract the reflecting surface of this unfathomable sea. \\
  Growing circles of grief and pain slides across the land \\
  as an omen of the horror yet to come. 
  
  The strength of a thousand fire-breathing demons \\
  breed in my infernal, sinking soul. \\
  And as I reach the surface once again \\
  these powers are under my control. \\
  Now I am one with the night sky majesty.
}

\Thanatzil{} dies. 

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  The Abyss yawns wide\prikker Claws sharpened on the dead.\\
  The Abyss yawns wide\prikker Ensanguined fangs agleam.
  
  Great shadow, awaken and eclipse the suns of a thousand worlds\prikker\\
  Slumbering 'neath these crimson vaults, \\
  behold the majesty of the Outer Darkness!\\
  Praise the Z'xulth!
  
  Fell Worm of the Black Galaxy, \\
  awaken and descend without pity upon the Tellurian sphere!\\
  Destroy the flaccid priests of the newborn usurper faiths.\\
  Sweep away the thralls of the cruciform stave!\\
  Crush the lackeys of the corrupted hexagram!\\
  Devour the slaves of the eastern crescent!\\
  Crush them, grind them, slay them all!\\
  Plague-blessed, flay them alive!
  
  Now, behold in terror what waits beneath the crimson vaults of Cydonia\prikker}
  
\lyricslimbonicart{A Venomous Kiss of Profane Grace}{
  Silent screams of suffering.\\
  I stand in flames of torturing.\\
  Goddess of flesh hunger and desire,\\
  grant me wings of hellish fire.\\
  Know that all my creations spring\\
  from blood on the cross in blasphemy.\\
  I am death, the creator of sin.\\
  and of the pure I am the wind.}

\lyricslimbonicart{The Dark Paranormal Calling}{
  A serpent in my soul.
  
  In midnight's aura as a ghostly fire.\\
  The child prodigy of abysmal desire.\\
  As the deathlike silence pervades, \\
  the incubus now invades.\\
  Show yourself, unclean spirit. \\
  Tonight I give thy shadow life.\\
  Rise with me in darkest blessing.\\
  Thine demon force I feel possessing.\\
  A holotropic mind and spectral eyes divine.\\
  Through the shallow haze as the sky turns red\\
  I walk and dream among the dead.
}

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Spiralling permanence. \\
  Merciless decadence. \\
  Unethical banishment. \\
  Fall before that which summons you.
  
  Imminent dormancy. \\
  Heinous atrocities.\\
  Demons that beckon me.\\
  That which to escape is to die. 
  
  Spiritual holocaust. 
}

\lyricslimbonicart{A Cosmic Funeral of Memories}{
  The night belongs to the predator\\
  to the one who dares crossing the threshold,\\
  the axis of dreams and wonders and black miracles.\\
  I see my self in the mirror of your eyes:\\
  A dark star on the celestial beautiful midnight sky.\\
  Release the inner radiance of what you have become.\\
  Brighten the night with your sacrifice.
  
  I have returned to life to speak of clairvoyance.\\
  I am the voice from the grave land of memories.\\
  Life can be only an illusion, and death a temptation,\\
  a final destiny.
}





\subsubsection{Rebels strike}
But then disaster strikes. The \hr{Rebels against Semiza}{rebels} attack and interrupt the ritual. 

\Vexstrasshin{} hopes to kill all the mothers. 





\subsubsection{A rebel sacrifices himself}
The rebels are almost stopped. Then their \draconian{} ally speaks to them. She cannot enter the city herself\dash\Semiza{} and the \bane{} magic has blocked her out\dash so she must act through her \nephilic{} allies. 

One hero among the rebels sacrifices himself to allow the \dragon{} to possess his body and channel her magic through him. This is a dangerous, experimental process and will permanently destroy both his body and soul. 

\lyricsbalsagoth{
    The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire 
    - Part III: 
    Cry Havoc for Glory, and the Annihilation of the Titans of Chaos
}{
  [THE ECHOES OF THE IMMORTAL:]\\
  Hearken, noble King of Hyperborea.\\
  \prikker\\
  To utterly destroy the Dark Liege of Chaos, you must join your essence with mine\prikker we must fuse our life-forces and become one so that my full power may be unleashed against Angsaar once more. \\
  But this final deed demands the most severe of tolls, o' noble monarch\prikker\\
  To become as one with the immortal essence of the Shadow-Sword is to sacrifice forever your own mortality, and to forsake eternally the world of man. \\
  Are you prepared to pay this price, King of Hyperborea?
  
  [THE KING:]\\
  To preserve the sovereignty of my realm and safeguard my people from the 
  forces of darkness? Aye! For my kingship demands no less a commitment!\\
  So be it\prikker let this final deed be done!
}

\Thanatzil{} still hangs around as a ghost with some power. The \bane{} power flows into him, and he becomes manic.

\lyricsbalsagoth{
    The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire 
    - Part III: 
    Cry Havoc for Glory, and the Annihilation of the Titans of Chaos
}{
[LORD ANGSAAR:]\\
  (No\prikker my eternal nemesis, you will not thwart me! Abominations rise! 
  Destroy these mortals who vex me as the buzzing of gnats vexes a titan!
  Drag their impudent souls to the abyss!)
  
  [THE WARRIORS OF HYPERBOREA:]\\
  (Havoc is the cry! Come, fiends of the nether-void\prikker\\
  face righteous pattern-welded death!)
  
  [LORD ANGSAAR:]\\
  Abominations rise! \\
  Souls to the abyss! 
  
  [THE WARRIORS OF HYPERBOREA:]\\
  Havoc is the cry! \\
  Pattern-welded death! 
  
  [LORD ANGSAAR:]\\
  (Praise Chaos! By the crystal heart of Mera I shall stand deified!)
  
  [THE WARRIORS OF HYPERBOREA:]\\
  (Glory eternal! For our King and sacred Hyperborea!)
}

\Thanatzil{} is consumed by hatred: 
All he wanted was to help his people. 
And they stab him in the back! 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  I now become my saving grace, \\
  exiling all this human waste.\\
  I deny your emotions, you perjurers. \\
  I deny your falsifications, you perjurers.
}

\Thanatzil{} grows more and more manic. 

\lyricsbalsagoth{
    The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire 
    - Part III: 
    Cry Havoc for Glory, and the Annihilation of the Titans of Chaos
}{
[ANGSAAR:]
  (The circle closes\prikker you cannot resist the unparalleled might of Chaos 
  and the exquisite majesty of the Z'xulth! I shall unleash all the terrors of 
  the Outer Darkness against thee! Behold the true extent of my power\prikker) 
  
  My flesh is a shrine wherein all demons dwell!
  
  Bae'an, Zurra, Uldorr, Neoloth. \\
  E'manh, Phaegus, Nyaszar, Merlech.
}





\subsubsection{Survivors sucked into \Nyx}
\target{Semiza fails}
\target{Thanatzil fails}
\Thanatzil{} never got resurrected, so he died permanently. 
And worse, since \hr{Thanatzil is the gate}{\Thanatzil{} was the gate}, this meant that the portal to \Nyx{} was closed and \Daggerrain{} was once again shut out. 

At the last minute, \Daggerrain{} realized what was happening. 
He acted swiftly, while there was still a tenuous conduit from \Erebos/\Nyx{} to \Tembrae{} (the conduit which \ps{\Thanatzil} death had opened). 
He seized some of the threads of the \hr{Shroud of Girigor}{Shroud of \Numah} and used them to create a pocket of Realm-stuff.
He wrapped this pocket around the surviving mothers and soldiers as well as \Semiza{} and \Eshayzal. 
He tossed this pocket into \Nyx{}. 
With the Shrouding they were now invisible and hidden from \Vexstrasshin{} and her ilk. 

\Daggerrain{} also laid out a smokescreen in the form of a plausible-looking implosion that destroyed the temple and laid waste to much of the city. 
That way it looked as if everyone was dead and the plan thwarted. 





\subsubsection{\Vexstrasshin{} dies}
\target{Vexstrasshin dies}
\Vexstrasshin{} is killed by \ps{\Daggerrain} treachery, so she cannot go out and tell the tale of what happened here. 
During the death-and-resurrection ritual, while the portal is open, \Daggerrain{} reaches through with as much power as he can muster and attacks \Vexstrasshin. 
She is unprepared for the power of this attack. 
She fights back with all her might and wiles, but \Daggerrain{} is too powerful. 
He slays her and destroys her soul. 















\section{Aftermath}









\subsection{\Morza}
\target{Morza rescues survivors}
\hr{Morza}{\Morza} was a \nephil soldier in \Numah.

He was one of the soldiers charged with protecting the mothers of the \resphain.
When disaster struck and \Thanatzil failed, he took command and led the mothers and the other survivors to safety.

He led them to a promised land in \Nyx.

They found some passages in their traditional religious scripture, combined with \Semiza's new bane religion, which foretold that this would happen.
He became their chieftain.
For thousands of years after his death, \Morza would be revered as a great hero.
Compare him to Moses and other leaders from the Hebrew Bible.

\Morza was no great champion or hero. 
He was a regular soldier, a \quo{little guy} who stood up and did what he had to when there was no one else to do it. 









\subsection{Rebels celebrate}
The \nephilic{} rebels were happy.
They had lost much: 
Several heroes, their mentor \Vexstrasshin{}, tons of innocent lives and much of their city. 

But the evil plan had been stopped. 
They had saved the world, they thought. 

And the destruction was not so bad. 
They had seen its like before at the hands of the \dragons. 
They knew how to cope with it and rebuild. 









\subsection{\Humans}
Plenty of \humans{} were born by this time. 
They were still children, and many died, but enough survived. 
\hr{Humans are fertile}{\Humans{} are fertile}, more so than the \nephilim, so they bred and multiplied quickly. 
They could interbreed with \nephilim, but the \human{} genes were dominant, so they spread even more quickly. 

The \dragons{} wondered a bit when they noticed this new race of pygmy \nephilim{} that appeared seemingly overnight. 
But they paid it little heed.





\subsubsection{\Morza saves some \humans}
\Morza saved several \human children. 
(The oldest \humans were as much as six years old at this time.)





\subsubsection{\Scathae and \humans hate each other}
\target{Scathae and Humans hate each other at first}
When the first \scatha meets a \human: 
Show the \scatha's revulsion at the sight of this ghastly, grotesque, naked\prikker thing. 
Compare the \human to a naked mole rat. 

\Scathae tended to see mammals as disease-ridden vermin in the first place, and this naked mammal that stood upright and tried to mimic (\quo{ape}) the \scathaese form was horrid to behold. 
Besides, the \scatha could feel the Cosmic Horror of the \pps{\banes} influence on the \human. 

It would take centuries for the two races to become fully accustomed to each other and not feel this Cosmic Horror revulsion anymore. 

See also the section about \hr{Anti-Scatha racism}{anti-\scatha racism}. 





\subsubsection{\Human trees in \Tembrae}
\target{Human trees}
In the Realms of \Tembrae, some \human tribes worshipped hideous alien powers.
Unbeknownst to the \dragons, these powers were really the \banes.

Using loathsome magic, these \humans transformed some of their own into horrid trees. 
These trees were abominations that lived on life force. 
They were telepathic. 
Their true purpose was to prepare a way from \Nyx to \Tembrae. 
At the time of the Incursion, the \human trees had grown powerful, their roots ran deep, and the way was ready to be opened. 

Some \dragons (\hr{Ishnaruchaefir wanted to destroy Humans}{including \Ishnaruchaefir}) wanted to destroy the \humans for their abominable religious practices. 









\subsection{Survivors in \Nyx}
Many of the mothers and soldiers died, but enough survived and were tossed into \Nyx. 
They found themselves stranded in a strange and inhospitable world. 
They had no idea how to get back to their own world, so they could only do their best to fend for themselves and survive in this new, frightening world of towering spires and bottomless abysses. 





\subsubsection{The Shroud of \Nyx}
\target{Shroud of Nyx}
\Daggerrain{} recycled threads and techniques from the \hr{Shroud of Girigor}{Shroud of \Numah} and wove another Shroud around the part of \Nyx{} where the survivors had landed, thus shielding them from prying \draconian{} eyes. 
But \Daggerrain{} had little time to do this, since he was rapidly losing his conduit, so he could only manage a shoddy hack-job. 

The Shroud worked, but with side-effects: 
It harmed the mind, causing confusion and amnesia. 
So the poor surviving \nephilim{} could not remember all that had happened. 
That was one of the reasons why \Merkyrah{} ended up inventing \hr{Merkyran myths}{so many false myths}. 










\subsection[Semiza]{\Semiza}
\target{Semiza flung away}
\target{Semiza entombed}





\subsubsection{Flees into crypt}
\Semiza{} and some of his cohorts (including \Eshayzal) survived and remembered, but they were imprisoned, buried alive when his temple/palace collapsed around him. 

\Daggerrain{} realized that \Semiza{} could still be useful. 
So when the nascent \resphain{} were sucked away into \Nyx{}, \Daggerrain{} made sure to keep a protective hand over \Semiza so he would not die but escape safely. 

When everything collapsed, \Semiza fled with some servants. 
He found the entrance to the underground crypts and ran inside before he was crushed.
From here, he made his way to the burial chambers where the mummies of his ancestors were kept. 

At this time, \Semiza was an old man. 
He hoped to live forever as \Daggerrain promised him, but some doubt and some belief in his ancestral religion remained in him. 
So he had made his servants prepare a tomb for him just in case. 





\subsubsection{Realizes all is not lost}
At first \Semiza{} thought everything was lost and that he was going to die. 
He cursed and raged at everyone: 
The \dragons, the rebels, the \banes. 
But when the catastrophe was over, \Daggerrain contacted him.
He told \Semiza that all was not lost. 
He instructed \Semiza to have himself entombed. 
\Semiza still had a part to play in \ps{Daggerrain} master plan, but he would have to wait, perhaps centuries or millennia. 

\Semiza despaired at this suggestion, but he knew there was nothing to be done, so he instructed his servants to entomb him. 

\begin{prose}
  \tho{\ps{\Daggerrain} power is not broken.
    Our covenant still holds. 
    He promised me immortality. 
    He promised me that I would live to see the \dragons{} destroyed, and then I would rule. 
    He is staying true to his word. 
    I will not die.}
\end{prose}

Gradually he became aware of other feelings. 
He could dimly feel the \resphain. 
He had a link to them since they were all his descendants. 
He could tell they still lived. 





\subsubsection{Thinks of the future}
At the very end of the book, \Semiza{} lay thinking: 
\begin{prose}
  \tho{We have lost much, but not everything. 
    Some of the seeds we have planted have taken root.
    Brave Ilu. 
    Brave \Thanatzil. 
    Your sacrifices were not in vain. 
    
    The \resphain{} live!}
\end{prose}


There he lay for millennia while his body wasted away.
Unable to move but immortal, and descending further into madness. 
He could still feel the faint, cold hand of \Daggerrain{}, channelling power into him and keeping him alive. 
As \Daggerrain{} promised, he gained immortality (by sucking energy from the Heart through \Nyx, and maybe a bit from \Erebos). 
But he lay a thousand years under the earth, eating mud and worms. 





\subsubsection{Helped the \resphain}
\target{Semiza helps fugitives establish themselves in Nyx}
\Semiza still retained his mental powers.
As a necromancer, he had great skill and experience in the art of sending his mind out to wander the spirit worlds.
So he was able to maintain some limited contact with \Daggerrain and with the \resphain.

In the beginning, \Semiza was able to help the fugitive \nephilim and the fledgling \resphain and \humans using his magic.
He helped them get established in the hostile world of \Nyx. 
But after some decades, \Semiza exhausted his reserves of energy.
He had no way to replenish his energy.
So he had to go dormant.

His descendants were on their own now.
But he had given them a start. 





\subsubsection{Freedom}
\Semiza remained in his tomb for over a thousand years, until \hr{Explorers meet Semiza}{\Damiarch-tachi found his now-undead remains} and freed him.























