\chapter{\SathariahBook}
% The story of the \secondbanewar, called the Incursion by the \resphain. 















\section{The \Resphain Prepare}
\subsection{The \Baelzerach schism}
Among the dark ones there was now a schism. They knew that they were spawned by \quo{Chaos and Darkness}. They disagreed over which parent was more important, Father Darkness or Mother Chaos. The majority voted for Darkness, but a minority held Chaos as the superior force. 

This faction became \Baelzerach. They split off from the other \resphain. 

Perhaps they followed a Satan-like god, or a super-powerful \resphan{} lord. And maybe his sexy daughter? Compare her to Lillith from \authorbook{\Francois{} Marcela Froideval}{666} (comic book series). 

The \Baelzerach{} did not fight against the \dragons{} in the \secondbanewar{}. Perhaps they even took the side of the \dragons{} (who were Chaos-aspected). Thus they became, and remained, far more friendly with \dragons{} than the rest of the \resphain. 

\Ishnaruchaefir{} would go on to have \hr{Ishnaruchaefir and Baelzerach}{dealings with \Baelzerach}. 

%\Baelzerach{} splits off from the other evil \resphan{} factions. 

The \Baelzerach{} begin to invoke Chaos: 

\lyricsbs{Marduk}{Accuser/Opposer}{
  Accuser! Accuser!\\
  Exhaustless fountain of poison divine!\\
  I ate of Death to cleanse my flesh of God,\\
  to make me thy entrance to the veins of the world.\\
  Now as we turn to seek thy face,\\
  pour down on us thy redeeming wrath.
  
  Opposer! Opposer!\\
  Core, marrow and essence of my Will!\\
  I renounce this flesh in the name of thy praise,\\
  to kindle the coals of Salvation's spring.\\
  I drank of hell to cleanse my soul of God,\\
  to reach the light in which thou dwellest.
}







\subsection{\CiriathSepher ascendant}
\target{Kiriath-Sepher founded}
The remaining \resphain{} form the kingdom of \CiriathSepher{} to replace fallen \Merkyrah{}. (The other \resphan{} kingdoms later branch off from here.)

The conquest of \Merkyrah{} and the rise of \CiriathSepher{} paves the way for the \resphan{} race's ascent out of ignominy and into the glory they feel they deserve. 

\lyricsbalsagoth{The Thirteen Cryptical Prophecies of Mu}{
  [THE HIGH PRIEST OF MU:]\\
  Ascent to ecliptic! Mu and Poseidonis!
  
  [THE CHIEF CULTIST OF ZURRA:]\\
  The Emperor commands\ldots{} Uroboros to rise!
}

The regular \resphain{} are frightened by the new darkness. 
They turn to \Morcariel-tachi for leadership and guidance. 

\lyricsbs{Monolith Deathcult}{Cathedral of Corpses}{
  Beneath the shadow of thy throne \\
  still may we dwell secure.\\
  Suffering is thine arm alone \\
  and our defense is sure.
}

\Morcariel{} uses the \ashenblooded{} as artificial scapegoats. 
He wants to create a ranking system so the \resphain{} will feel good. 
Or something. 

\lyricsbs{Monolith Deathcult}{Cathedral of Corpses}{
  My word commands your flesh to dust: \\
  \quo{Return, ye sons of men!}\\
  Immortals rose from earth at first \\
  and my blood will live again.
}





\subsubsection{\CiriathSepher adopts \Merkyran traditions}
\target{Azraid adopts Merkyran imagery}
Under the command of \Morcariel and \Azraid, \CiriathSepher adopted much of \ps{\Merkyrah}{} imagery, aesthetics and perhaps even philosophy. 

\Azraid{} defends this, saying that the new empire must not reject everything that the people know, lest the people become unruly and difficult to control, and the empire grow inefficient.

Other \resphain{} object to \hr{Azraid's pragmatism}{\ps{\Azraid}{} pragmatism} and claim that he should be more true to the ideology of \quo{Darkness and Chaos}. 
This is one of the reasons why the \resphan dynasties \hr{Dynasties drift apart}{split off from each other}.

The other rebels also believe that they should reveal the entire truth to the people. But \Azraid{} wants to still keep many things hidden from the people and let many lies live on. The others protest, but acquiesce to \ps{\Azraid}{} plan. But it makes them bitter, and division is sown among the lords of \CiriathSepher. 









\subsection{\Bezedeth disappointed}
Many \bezedeth flocked to the rebellion because they were promised better conditions in the new world order. 
They became sorely disappointed after the rebellion. 
The rebel ideology could not bring them True Immortality, and their lot did not improve much.
They were not outcast, but they were still looked down on as inferior half-\resphain.









\subsection{They look forward to fighting \dragons}
The \resphain{} remember the \hr{Merkyran myths of Dragons}{\Merkyran{} myths of \dragons}. 
They are aching and excited to finally face these \dragons{} in combat. 
They want to take back what was once theirs. 

\lyricsbs{Aeternus}{Possessed by the Serpents Vengeance}{
  Your wrath coiled around the earth.\\
  Your venom courses it veins.\\
  Strike at their fear.\\
  Destroy their kingdoms\\
  with your poisonous rage.
}

\lyricsbs{Monolith Deathcult}{Demigod}{
  The great Persian serpent lies in wait.\\ 
  Let us face his army of immortals. \\
  We shall butcher those hunters of men's souls \\
  and crush their nimbus of immortality.
  
  A beast is approaching us. \\
  Its magnitude will blot out the Sun. \\
  We shall drink Persian blood \\
  and find our glory in the final arrow hail. 
  
  We blaspheme the tyrant.
  
  Under the banner of [\Mystraacht]. \\
  For the eternal glory of [\Nyx]. 
}









\subsection{Learning \Miithian languages}
\target{Resphain learn Miithian languages}
% The \resphain{} learn some of the \Draconic{} tongue from the \banelords{} (who have been monitoring \Miith{} for millennia), so that they can communicate and deal with their foes. 
% They also study the \psp{\dragons}{} magic, weapons, physique, psychology and culture, so they are better equipped to fight them. 

The \resphain did not learn the \draconic tongue before they began the Incursion. 
They learned it slowly afterwards, but only few ever learned it and none ever truly mastered it.
The \dragons were not interested in teaching it to them, but the \resphain learned quite a bit from some \quiljaaran whom they got persuaded or coerced into cooperating.

\hr{Resphain speak poor Draconic}{Only very few \resphain ever mastered the \Draconic tongue}. 

But the \resphain did make some effort to study the \psp{\dragons}{} magic, weapons, physique, psychology and culture, so they are better equipped to fight them. 










\subsection{\Resphain{} come to \Tembrae{} in spaceships}
\target{Resphain come down in spaceships}
\index{technology!\bane}
\Merkyrah{} was not in \Tembrae{} but in \Nyx. 
The \resphain{} of newly-formed \CiriathSepher{} had to travel to \Tembrae{} in spaceships (\hr{Bane technology}{\voyager{} relics}). 

So they came to \Tembrae{}, descending from the sky in chariots of fire, like the gods they were. 
They conquered the primitive, savage \humans{} living there. 

Since then, \humans{} have had myths about how the gods (\resphain) came from the sky/stars in burning ships or chariots, to liberate them from the depredations of the wicked \dragons{} and their spawn.





\subsubsection{Population}
At this time, the total population of all \resphain{} was in the range of 100,000--200,000. 





\subsubsection{They marvel at the \Wylde}
\hr{Merkyrah is one huge city}{\Merkyrah{} was one huge city}, so the \resphain{} had never seen \Wylde{} nature before. 
They marvelled at the sight, but it also frightened them. 
Some of them became convinced that this new world was a savage, backward land that they must conquer and civilize. 

Yet others simply enjoyed the beauty and coolness. 

\lyricsdimmuborgir{Stien}{
  Her gandviks bergtroll trampet frem\\
  i ondt og stort et tussefolge.\\
  Hvor ferdafolk fant stor en visdom\\
  om landets skogsliv og m\oe rke sider,\\
  Her p\aa{} stien som bukter seg uendelig frem.\\
  Mellom berg hvor de vanskelig fremdeles\\
  kan \oe ynes i horisonten.
  
  Sa storslatt det m\aa{} ha v\ae rt\\
  og speide ut over alt dette\\
  og a vandre sa alene og fri.\\
  En hostkveld i en kald og lett t\aa ke,\\
  slik som mange for meg har opplevd\\
  og som mange for meg har verdsatt.
}

Nature was both frightening and compelling to them. 
They could sense the immense power and life force around them. 
See, \Nyx{} was \hr{Nyx is far from the Heart}{farther removed from the Heart of \Miith}, and therefore it could not be felt to the same extent. 
\hr{Nyx is a parasite Realm}{\Nyx{} lived by leeching off this life}, but here in \Tembrae{} it could be felt in its undiluted form. 

\lyricsdimmuborgir{Stormbl\aa{}st}{
  Glatt er runen p\aa{} det h\o{}ye fjell,\\
  gnidd vekk av regn og vind.\\
  Dragende kraft av ondskap lurer\\
  her ved trollheims muldne grind.\\
  Fortumlet av dette m\o{}rke byggverk,\\
  med r\o{}vet gull fra lyets pakt,\\
  brukt som spott til \aa{} senke deres murer.
  
  Vi grunder over dette riket,\\
  s\aa{} vakkert fylt med tidel\o{}s skumring.\\
  Som en stjerne i tomsindighetens juv,\\
  det bringer frem en nattlig mimring\\
  over tanker fra en vissen tid.
}

They want to conquer this new, beautiful Realm. 

\lyricsdimmuborgir{Stormbl\aa{}st}{
  Der sorg har beseiret alle gleder\\
  og bygd et land p\aa{} menneskets jord,\\
  fylt med isklad prakt og heder.
}







\subsubsection{The savage \humans}
\index{technology!\human}
The early \humans{} who escaped the fall of \ps{\Semiza}{} kingdom and fled into the wild formed their primitive tribes. They were barbarians, stone age level, or bronze age at best. \Humans{} are too stupid to create any non-trivial civilization on their own. They only gained more technology when the \resphain{} came and took control. If they had bronze age technology, then it was stolen from the \scathae. 

\lyricsbs{Monolith Deathcult}{Origin}{
  Risen from the seed of Enki\\
  with consent of the God-father Anu.\\
  We are the working race,\\
  created in the temples of SCH.RUPPAK.

  The Masters ride the midnight sky\\
  in their lucent chariots of thunder.\\
  Those who behold the radiant face of the Gods\\
  died eyeless, scorched and ablaze.
  
  And God-slaves we are,\\
  suffering in the mines of our Masters.\\
  We populate the fields of E.DIN,\\
  the base of the Gods from Nibiru-Pha\"eton.
}

The \humans{} did have \hs{myths} about \Thanatzil, \Semiza{} and the \resphain. 
They worshipped them as absent gods. 

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  I built temples, statues and pyramids \\
  as monuments of my endless might.\\
  Colossal knowledge lays hidden in tablets and shrines, \\
  protected by spells and incantations.
  
  Your history is not yours. \\
  I gave thee wisdom. \\
  I gave thee science \\
  and I delivered thee from bestiality.\\
  My name was carved in thousands of stones \\
  and diurnally murmured in deadly incantations.\\
  Atlantis was built when you amoebas crawled through filth. \\
  I am Holiness Divine, your Lord and Master, \\
  the Supreme God and Creator.
}

They have myths about a saviour god named \quo{Anatheal} or a variant thereof. 
This is a corruption of \hr{Thanatzil}{\Thanatzil}. 
According to myth, Anatheal came to them a thousand years ago to create an eternal paradise for \humans{} where they would live in bliss alongside his angels. 
But \humans{} were wicked and sinful, and they wasted Anatheal's precious sacrifice. 
Now they are condemned to live as filth, preyed upon by the \dragons{} and their spawn, until the day when Anatheal will return. 









\subsection{Hiding in \Nyx}
Perhaps the \resphain{} used \Nyx{} to hide their cities and lands from the \dragons{} while they built their empires. 









\subsection{They need the stargate}
The \resphain{} need \hr{Semiza's stargate}{\ps{\Semiza}{} stargate}. 
After \ps{\Thanatzil}{} fall, \hr{Semiza flung away}{\Semiza{} was flung far away} from the stargate. 
The \resphain{} must find, exhume and restore it. 

They must also find \Semiza{} again (since \hr{Rebels lose Semiza}{they lost him}). 

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  The sacred altars erected for the Sun-God \\
  point at the sky as a tremendous beacon. \\
  The Heavengate was sealed and buried forever. \\
  deep beneath the surface of the earth. 
  
  When the Portal is disinterred, \\
  and the Door to Heaven is unsealed again, \\
  then I shall return to restore my immense power.\\ 
  Thou shall be enslaved again.
}





\subsubsection{They find \Semiza}
\target{Semiza becomes a Lich}
They found \Semiza{} again. 
He told them more about the \banes. 
Among other things, he told them about the \hr{Bane telekinesis}{\pps{\banes}{} tactile language} and how that tied in with their names (like \quo{\hr{Daggerrain}{\Daggerrain}}). 

The \resphain resurrected \Semiza as a \Lich.
It was traumatic for him, and also for some of them, for it involved some pretty wicked magic. 
\citebandsong{Nile:AmongstheCatacombsofNephrenKa}{Nile}{
  Opening of the Mouth
}{
  I split open your Eyes for you\\
  I open your mouth for you\\
  With the Adze of Iron\\
  Which split open the mouths of the Gods\\
  The Iron which issueth from Set

  With the Adze of Iron\\
  I did clean your Bones\\
  With Iron Hook and Chisel\\
  I did scrape your Flesh\\
  And separate your Bones for you

  Sebau Fiends work Evil on the Body

  Raise yourself Asari\\
  Receive your Head\\
  Collect your Bones\\
  Gather your limbs Together\\
  Throw off the Earth from your Flesh\\
  Khnemet-Ur cometh to Thee
}









\subsection{\Resphan-\aryoth{} alliance}
\target{Resphan-Aryoth alliance}
The \aryothim{} and \vorcanths{} had often warred against the \dragons, and the \quiljaaran{} for that matter. 
Some \resphain{}, having caught wind of this, recognized the \aryothim{} and \vorcanths{} as potential allies and sent a delegation to find some of their great and respected elders. 
Ramiel and \Shiaraid{} were the leaders of this delegation. 

They managed to sway many of the \aryothim{}, who joined their war, but only few of the \vorcanths{}. 
Most \vorcanths{} elected to remain neutral. 

During the war there were several \aryoth{} kings and chieftains who fought and argued among each other over how they should act in the war, on which side they should fight and under which conditions. 
They were as diverse as any other race. 















\section{The \Sathariah Project (\yds{Satharioth})}









\subsection{\Dragons wonder why the Heart is weak}
\target{Dragons wonder why the Heart is weak}
The \hr{Heart}{Heart of \Miith} began to \hr{Heart weakened}{weaken} as soon as the first \resphain{} were born, and it \hr{Merkyrah strained the Heart}{became worse as the \Merkyran{} population grew}. 
Gradually, the \dragons{} became less and less fertile, and fewer live children hatched. 
But the \banelords{} had hidden \hr{Merkyrah}{\Merkyrah} well, so the \dragons{} couldn't figure out what was causing it. 
For thousands of years they grieve and research and try to find out why their eggs die, but they can't find anything conclusive, only some vague astrological \hr{Matrix}{\matrix} mumbojumbo. 

Only when the \resphain{} reveal themselves do the \dragons{} piece together the true answer.   

The \dragons originally had \hr{Draconic names for Banes}{other names for the \banes}. 









\subsection{Awakening the \banelords}
%They create the \resphain. When they have enough \resphain, they blast open the doorway from \Nyx{} into \Miith{} and march forth, proudly announcing to the world the beginning of the \secondbanewar. 
%The \hr{Resphan rebellion}{rebellious \resphain} have conquered the \hr{Good Resphan Empire}{previously good \resphan{} empire}. 
The dark ones are victorious and now control the \resphan{} empire. 
%They now reopen the gate to \Nyx{} and summon \banes{} to their aid. 

In the beginning, they waged wars with \dragons{} and their ilk here and there, but nothing out of the ordinary. The \dragons{} knew that a new religion had risen to prominence among the \resphain, but paid it little heed. Very few \dragons{} suspected that the \quo\banes{} whom the \resphain{} now worshipped as their creations were the same as the ancient foe of \dragonkind. They simply believed that the \resphain{} had discovered some new magic and concocted a fictional mythology to surround it, as so many cultures had done before them. So they still wasted their strength on internal wars. They did not fear the \Nyx-aspected magic, for it had existed for thousands of years and never been a real threat to the \dragons. 

%They resume contact with the \banelords{} and summon \banes{} to their aid. When they have enough strength, they blast open the doorway from \Nyx{} into \Miith{} and march forth, proudly announcing to the world the beginning of the \secondbanewar. 
But at last the rebels succeed in penetrating the \hr{Crystal Sphere}{\CrystalSphere} and contacting \Daggerrain. They have high expectations of the \banes{}. 

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  The Abyss yawns wide\ldots{} Claws sharpened on the dead.\\
  The Abyss yawns wide\ldots{} Ensanguined fangs agleam.
  
  Great shadow, awaken and eclipse the suns of a thousand worlds\ldots{}\\
  Slumbering 'neath these crimson vaults, \\
  behold the majesty of the Outer Darkness!\\
  Praise the Z'xulth!
  
  Fell Worm of the Black Galaxy, \\
  awaken and descend without pity upon the Tellurian sphere!\\
  Destroy the flaccid priests of the newborn usurper faiths.\\
  Sweep away the thralls of the cruciform stave!\\
  Crush the lackeys of the corrupted hexagram!\\
  Devour the slaves of the eastern crescent!\\
  Crush them, grind them, slay them all!\\
  Plague-blessed, flay them alive!
  
  Now, behold in terror what waits beneath the crimson vaults of Cydonia\ldots{}
}

\lyricsbalsagoth{The Empyreal Lexicon}{
  Fear is the power\ldots{} Terror is the key!\\
  X'atham-ry'aa\ldots{} Tha'zai-tonn!\\
  I am replete with sovereign mastery!\\
  The portals to the Outer Darkness yawn wide once more!\\
  They-Who-Lurk-And-Breed-In-Limbo are free!}

The \banelords{} had been imprisoned in \Nyx{} for thousands of years, forcing to sit idly by while the \Merkyrans{} tapped their power and called it \quo{God}. 

\lyricsbalsagoth{The Voyagers Beneath the Mare Imbrium}{
  From a time beyond time, we come.\\
  We, who once crested the waves of the great astral sea\ldots{}\\
  and who now must strive again for the domination of the stars\ldots{}
  
  The great lunar seal is broken.\\
  We are free\ldots{} free to rule!
  
  For more than ten times a thousand years\\
  have we slept beneath these cratered, lifeless stones\ldots{}\\
  The Lexicon's crystalline core has at last been reactivated\ldots{}\\
  We have heard the sighing of a thousand souls\ldots{}\\
  now at last we shall hearken once more to the siren call of the cosmos.}

The \banelords themselves are unable to come through, but they can communicate with the \resphain{}, and they can send \lesserbanes{} to their aid. 

The \resphan{} lord gathered their strength, consolidated their sovereignty over their race, as well as the \humans{} and the few surviving \nephilim, now slaves. And they laid plans\dash against the \dragons, and against each other. They also received technology from \Erebos, and they did research to refine it and create new technology. 

\lyricsbs{Hate Eternal}{Catacombs}{
  Rise up from the ancient tombs. \\
  Grant us all your infinite wisdom. \\
  Endure as you rise from the catacombs. 
}

\lyricsbs{Hate Eternal}{The Creed of Chaotic Divinity}{
  Awakened by this ancient creed. \\
  Evoked, the ancestry of thee.\\
  Forsaken for centuries of times. \\
  Exiled, all of their kind. \\
  Foretold, the inheriting of the Earth.\\
  Forewarned of this predestined rebirth. \\
  Engaged, the rising from below.\\
  Fear, all mortals, for what they shall bestow.
  
  Conjure all, so that they may sustain\\
  their race, of what they must retain.\\
  Spew forth incantations in vain. \\
  Invocate all that they try to negate.\\
  Enchant all of their wonderful splendour. 
  Recant all of the texts that are sacred. \\
  Recreate all that has been begotten. \\
  Revive all that has been forgotten. 
}

\lyricsbs{Marduk}{The Black Tormentor of Satan}{
  When the dark clouds in the sky open,\\
  a thousand eyes burn in the night.\\
  A kneeling shape in a void of fire \\
  gazes out over this world.\\
  Within a blink of an eye\\
  a gruesome face looks down from the sky\\
  on this world where darkness soon will reign\\
  and the people shall meet their new King.\\
  That night will be the one\\
  that will open the gates to the realm beyond\\
  and the wings of funeral will take my soul\\
  and complete the eclipse of my heart.
}





\subsubsection{\Mystraacht{} are especially eager}
\Zachirah-tachi were especially eager to meet their \banelords. 

\lyricsbs{Emperor}{My Empire's Doom}{
  Once our lord has come again, \\
  all black hearts will celebrate \\
  the darksome fiend \\
  in the kingdom of sorrow. 
  
  Nocturnal fiends, \\
  the beings of the night and shadows \\
  calling forth the pure spirit \\
  of the night.
}









\subsection{The \Sathariah project}
The \resphain{} and their \bane{} masters lay sinister plans to gain more power. The \resphain{} already possess some measure of Chaotic power, but they crave more. To do this they needed \draconic{} blood. 

After much preparation\dash decades, perhaps\dash the \resphain{} are ready. They have concocted an elaborate plan to capture one of the \dragonlords{}, slay him and used his blood and life-force to empower their new generation of \resphain\dash the \hr{Sathariah}{\satharioth}, who would go on to become the mightiest of them all. 

%So in an elaborate plan, the \banes{} captured the \dragonking{} \Nexagglachel{}, killed him and used his blood and life-force to empower their new generation of \resphain, who went on to become the mightiest of them all. Ramiel and \Shiaraid{} belong to this group. 
They set their eyes on \Ishnaruchaefir.







\subsection{\Ishnaruchaefir has premonitions}
Somehow, \Ishnaruchaefir{} has premonitions. 
Perhaps he uses divination magic. 
He sees visions of being betrayed, imprisoned, tortured and slowly killed. 
He sees his body and soul being cut into pieces and devoured by ravenous horrors (the would-be \satharioth). 
He sees himself impaled on a tree of thorns, his blood drained and his flesh peeled off in strips. (See section \ref{Nexagglachel in captivity}.) 
He sees visions of death, eternal war and the destruction of the world. 

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  By the Onyx Sceptre of my forefathers,\\
  the air is churning\\
  with auguries of dethronement,\\
  impending doom thus prophesized.
  
  In a dream I was bade ride the argent-eyed unicorn to the Ring of Stones.\\
  There a torrent of viscid slime assailed me\\
  as pipes and horns sang the clarion of my dissolution.
}

\lyricslimbonicart{Suicide Commando}{
  In the shadows of the world's ambitions \\
  I see life and death, in an enormous collision. \\
  Light destroys what dark creates. \\
  Forever floating, the dark rivers of the heart. \\
  Lifeless drifting, in an orbital decay. \\
  A vicious circle of extinction. \\
  The soul reaches the state: Oblivion.
}

\lyricsduana{thisistheend}{This is the End}{
  I see field upon field upon field \\
  of bloatd-cattle-corpses bleeding intestines \\
  staring with sightless opaque eyes \\
  of waves drowning mountains \\
  and the earth's flesh torn with angry fissures \\
  of molten-spewing-spittle \\
  and hot lashing tongues \\
  of a planet roaring/quaking/quivering \\
  with unbound vergence 
  
  shivers erupt through space and time \\
  and images flashing faster faster\ldots{} \\
  until finally all is annihilated 
  
  like a vacuum space sucks the debris \\
  into a black empty hole \\
  and I fall down into the void \\
  this is the end
}

Also compare to the visions of Hell in the movies \emph{Hellraiser} and \emph{Event Horizon}. 

The reason why it is \Ishnaruchaefir{} and not \Secherdamon{} who sees these visions is twofold:

\begin{enumerate}
  \item 
    It is \Ishnaruchaefir{} who is the \ps{\resphain} intended target.  
    They have already began weaving subtle spells to entrap him. 
    These spells are not quite subtle enough, and he picks up on them. 
  \item 
    \Secherdamon{} was always very goal-oriented and focused his research on the \xss. 
    \Ishnaruchaefir{} was focused and had a wider range of interests. 
    He tended to gaze out into the universe rather than narrowly into the \psp{\dragons}{} past. 
    He cared about the cosmic gods and the more elusive mysteries of existence\dash mysteries that might have no solution at all, and might have no practical application even if solved. 
    (\Secherdamon{} ignored these questions for those reasons.)
    
    \Nexagglachel{} was not so much into sorcery. 
    He was more absorbed in earthly matters of politics. 
    
    This made \Ishnaruchaefir{} more sensitive to alien things than his brothers, so he could feel these dreams when the \resphain{} approached. 
\end{enumerate}








\subsection{\Ishnaruchaefir seeks the advice of elders}
\Ishnaruchaefir{} dreads this horrible fate. 
He seeks out wise elder \ophidians{} and \nagalords{} and asks for their advice. 



\subsubsection{Searching for the elders}
He goes to a dark, menacing place where these elders live. 
Perhaps this place is a \hr{Black pyramids}{\quo{black pyramid}}, as in \bandsong{Bal-Sagoth}{Shadows 'Neath the Black Pyramid}, or an ancient, cyclopean castle, as in \bandsong{Bal-Sagoth}{Into the Silent Chambers of the Sapphirean Throne (Sagas from the Antediluvian Scrolls)}.

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  The king was compelled to lead his forces to the shadow-haunted Mountains of the Dead, a grim and brooding place steeped in dark and ancient legendry. Alone he rode into the gaping maw of a huge cave hewn into the side of the tallest mountain co untless ages past by unknown hands.
}

\lyricslimbonicart{Lycanthropic Tales}{
  As the storm looms over the frozen landscape:\\
  A call from the beginning of time,\\
  out of darkness through the mist.
  
  Requiem in blood and fire.\\
  Symbols of occult desire.\\
  Through the cosmic vortex,\\
  the gate to unknown darkness.\\
  An esoteric voyage to eminent discovery.\\
  I am the deathlike shadow,\\
  architect of black mysteries.
}





\subsubsection{The elders' advice}
The elders are expert diviners and are able to show him more detailed visions of the future\ldots{} a future full of darkness, blood, death and eternal war. 

\lyricstitle{Warhammer 40,000}{%
  In the grim darkness of the future, there is only war.
}

\lyricsbs{Bal-Sagoth}{%
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire%
}{%
  I shall seek the counsel of the sorcerer, \\
  keeper of the ancient scrolls of wisdom, \\
  and the Crystals of Power\ldots{}
  
  My liege, great and regal king\ldots{} \\
  the mists disclose their secrets\ldots{}\\
  Drink deep of the potions of the apothecary, \\
  for upon thee now I bestow \\
  a shard of the mystic Crystal of Mera\ldots{} \\ 
  sacred artefact of the Atlantean mages, \\
  won in battle by our legions.\\
  My liege, the Crystal of Mera shall unveil the truth \\
  lurking hidden in thy most fever-haunted dreams\ldots{}
  
  The land awash with spilled blood, \\
  and viscera torn forth from the sundered dead\ldots{} \\
  Gorge the earth with flesh darkened with the claw and fang of war\ldots{} \\
  rent open the ravenous maws of worms\ldots{}
  
  The Crystal illumines dark secrets, the truth is known\ldots{} \\
  a dire and ancient threat is ranged against me.
}





\subsubsection{He is one of few who can stop it}
\Ishnaruchaefir{} is told that he is one of the few who have a realistic chance of changing this fate. 
This is due to a number of things: 

\begin{itemize}
  \item He is fucking badass.
  \item He is a powerful \vertex.
  \item He is at the centre of \ps{\Daggerrain}{} plan, since he is the \dragon{} whom they plan to use for their \sathariah{} project. 
\end{itemize}

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\ldots{} 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}






\subsubsection{\ps{\Criseis}{} point of view}
\Criseis{} camps outside and finally sees her lord return from the sinister dwelling of the ancients. 

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  For three full days and nights he did not emerge from the cave\ldots{} until, at last, he rode forth from the eldritch mountain once more, a terrible knowledge shadowed in his icy eyes\ldots{}
}

Have flashbacks about this! Possibly from \ps{\Criseis}{} point of view. And later have some conversations where one of the elders reveal to a third/fourth person what transpired. (Yeah, \emph{Malazan Book of the Fallen} style.)





\subsubsection{Origin of the glaive}
Perhaps \Ishnaruchaefir{} gains or forges \hr{Ishnaruchaefir's glaive}{his glaive} here.

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  \ldots{} and bearing in his gauntleted fist a huge black sword, a magnificent ebon blade which no human blacksmith ever forged. Fearsome sorcerous power crackled within the yard of black steel, dancing upon its searingly honed, glyph-scored blade\ldots{} and its bejewelled, dragon-carved hilt did whisper arcane secrets to the king in a strange, elder tongue.
}









\subsection{The Fall of \Nexagglachel}





\subsubsection{Capturing \Nexagglachel}
\target{Fall of Nexagglachel}
\target{Death of Nexagglachel}
\target{Origin of Satharioth}
In an attempt to prevent this dreaful fate\dash for himself and for the world\dash \Ishnaruchaefir{} seeks out his brother \Nexagglachel{} for help. 

Perhaps \Nexagglachel{} has seen similar visions, but was afraid to seem weak or mad in front of his backstabbing fellow \dragons, so he kept it secret. 
Compare him to King Leoric in the \emph{Madness of the Black King} story arc in the game \emph{Diablo}. 

The brothers fight against the \banes. 
\Ishnaruchaefir{} fights hard, both for himself and his brother, but in the end he fails. 
He lives, but \Nexagglachel{} falls instead. 
The \banes{} and \resphain{} are happy, having succeeded beyond their expectations and captured the mightiest of the three brothers, instead of just the second mightiest. 
So they use his blood, and the \satharioth{} are born. 
See section \ref{Nexagglachel in captivity}.

\Nexagglachel killed many \resphain before he was killed and captured.
When he revived, he was surprised to see that several of the killed \resphain had also revived.
They possessed \hs{True Immortality}.
He realized this was a foe to be reckoned with.






\subsubsection{\Nexagglachel{} in captivity}
\target{Nexagglachel in captivity}
\Nexagglachel{} was captured by the \banes{}. 
There he was tortured physically, magically and psychologically. 
He was crucified and impaled on a giant tree of thorns, and his blood and power was drained from him.

But through it all, he never surrendered, or even faltered. His pride and dignity remained intact, and he was able to mock his captors throughout his captivity, untill they finally killed him and drained the last of his life force and soul to create the \satharioth. 

See, as a son of \KhothSell{} he is, in a sense, an incarnation of Death. He fears neither death nor pain, and actively enjoys physical pain. So he laughs every time the \resphain{} ram another spike through his body.

After \Nexagglachel was taken prisoner:
\Nexagglachel learned the \resphan tongue by telepathically attacking a \resphan.
This was a sneak attack that took his captors completely by surprise.
\Nexagglachel was able to kill, destroy and devour his victim before the \resphain could stop him.
He learned much from the \resphan's mind.
He took from him many secrets about their origins, their plans, their technology and magic and their language.

\Nexagglachel did much to sow the seeds of doubt, fear, discord and rivalry among his \resphan captors, even when alive.
He would goad them on and manipulate them.
When they tried to interrogate him he would give them \trope{HannibalLecture}{Hannibal Lectures} instead.
He helped shape \Azraid into the very critical \resphan he later became.
And he shaped \Sithiyacaan into a rebel leader.
And \Shiaraid into a dangerous maverick.





\subsubsection{They taunt him}
Some of the wannabe-\Satharioth{} taunt \Nexagglachel. 

\lyricsbs{Vital Remains}{Entwined by Vengeance}{
  Ageless and obscure. \\
  Feel the burning in my heart. \\
  My eyes have seen the truth. \\
  Now my hands will tear your fucking God apart. \\
  
  In the name of Satan, \\
  our hate consumes the heavens. \\
  Decimate the holy land, \\
  for pain is now your savior.
  
  In this season of monumental horror, \\
  we hunger for heavenly termination. \\
  Of blood and war. We shall devour.
}





\subsubsection{His cold eyes}
\target{Nexagglachel's hatred}
\Nexagglachel stared back at the \resphain with his \hr{Nexagglachel's appearance}{cold, black eyes}. 
Even when he roared in pain and anger, his eyes retained their unfazed coldness. 
Remember, he was a \dragon, and \dragons relished combat, conflict, violence and pain. 
He enjoyed the challenge, even though he was convinced he was doomed. 
He was planning his long-term revenge. 

He told them: 
\ta{With every attack you only strengthen me.
  Every attack feeds my hatred. 
  The hatred that will devour you and your kind from within.
  I will be your downfall, \satharioth.
  Forever you will feel my cold eyes.
  Forever you will feel my hate.
  I will be the cancer that eats away at your being, until the day your people is destroyed.}

His pride drove his captors mad. 
They tried everything to break him, but to no avail. 
He was unbreakable. 





\subsubsection{\Nexagglachel and \Azraid reach an understanding}
\Nexagglachel{} and \Azraid{} look into each other's eyes. 
They both see the same fear manifested: 
The fear that the \banes{} will win and end up devouring both of their races in their hunger. 
They want to avoid that. 
To that end, both are willing to make any sacrifice. 

They reach a silent, unspoken understanding. 
They will work together in utmost secrecy in a \XanatosGambit{} that will take many thousands of years. 
Together they will overthrow the \banes. 

Maybe \Damiarch{} still lives at this point, and \Nexagglachel{} inspires \Azraid{} to kill him. 
But probably not. 





\subsubsection{\Nexagglachel contacts \Ishnaruchaefir}
\target{Ishnaruchaefir gains stewardship}
\index{stewardship}
Through his captivity, the \resphain{} made sure to keep \Nexagglachel{} blocked so that he cannot telepathically contact the outside world. 

At one point \Nexagglachel{} escaped. 
He broke free of their block and managed to contact \Ishnaruchaefir{} and warn him of the \ps{\resphain} plan, so they could be ready for what is to come. 

He told \Ishnaruchaefir{} that he would die. 
He passed on the mantle of the stewardship of \Miith{} to \Ishnaruchaefir. 
It would now fall to \Ishnaruchaefir{} to lead the \dragons{} and defend the planet against invaders. 

He told \Ishnaruchaefir{} of \hr{Nexagglachel gets stewardship}{the time when \TyarithXserasshana{} had given \emph{him} the stewardship}. 
Now he would pass it on to \Ishnaruchaefir. 

\Ishnaruchaefir{} expressed his doubt. 
He was not confident that he was up to the task. 
He had always been a loner, not a social sort, and least of all a leader of an entire people. 

But \Nexagglachel{} was certain he could: 
\begin{prose}
  \Ishnaruchaefir: 
  \ta{I cannot do this. 
    \Raemyth, I am not thou!
    I own not thy strength!}
  
  \Nexagglachel: 
  \ta{Yea, \Quessanth. 
    Thou art stronger than thou knowest.
    Strong enough to do what must be done.
    Thou art the best of us.
    \Irocas{} is skilled, but brittle. 
    He possesseth not thy solid foundation.
    Thou must take leadership.}
  
  \Ishnaruchaefir:
  \ta{Very well, \Raemyth.
    I will do what thou askest of me.
    I accept the mantle of stewardship. 
    I will find in me the strength to do what must be done.
    I will not fail thee, brother.}
\end{prose}

This ended up \hr{Ishnaruchaefir's stewardship}{shaping \ps{\Ishnaruchaefir} life}. 

\target{Ishnaruchaefir learns Azraid is on the level}
\Nexagglachel also told \Ishnaruchaefir of the various \resphan lords; which ones to beware. 
\Ishnaruchaefir learned that \Azraid was one of the better of them. 
He could be made to see reason. 
Later the two \hr{Ishnaruchaefir and Azraid develop empathy}{would develop an understanding}.

\Nexagglachel{} knew he was going to die. 
He did not expect to be rescued. 
So he went along with it. 
He plotted his own \XanatosGambit. 
He would live on as a ghost in the \satharioth{} and bestow upon them a curse to bring them down. 

Soon after, he was killed and his soul recaptured (his body regrows in captivity). 

Compare to the scene with Tai-Lung's escape in the movie \emph{Kung-Fu Panda}. 

\Secherdamon{} is hurt and angry that \Nexagglachel{} would choose to trust \Ishnaruchaefir{} rather than him, even after \Ishnaruchaefir{} failed him and was responsible for getting \Nexagglachel{} captured in the first place. 
This makes \Secherdamon{} doubly grim and ambitious and determined to prove his worth. 





\subsubsection{\Ishnaruchaefir tries to rescue \Nexagglachel}
This is an alternative to the above.

\Ishnaruchaefir seeks out his brother in the world of dreams.
He attacks the \resphain on this mental plane. 
\Ishnaruchaefir slays the \resphan \Nathrach.

\Ishnaruchaefir almost manages to save \Nexagglachel, but \Nexagglachel lets himself die.
\Ishnaruchaefir thinks he has failed and blames himself for ten thousand years.
Only when \hr{Ishnaruchaefir hears Nexagglachel would be proud}{Ramiel unwittingly lets something slip} does \Nexagglachel realize the truth. 









\subsection{The birth of the \Satharioth}
The birth of the \satharioth is the great dramatic climax of the book.





\subsubsection{Some \satharioth{} die}
\target{Satharioth die}
\target{Nathrach dies}
There were many who took part in the ritual and tried to become \satharioth. 
Maybe there were around 30. 
But they underestimated \Nexagglachel, and when they siphoned power from him, he seized control and lashed back.
He managed to destroy some of the would-be \satharioth.
He let them drain some of his essence, but also sent a portion of his will and malevolence into their bodies.
(A larger portion than into the others, that is.)
This way he was able to destroy them from within, causing them to tear themselves apart in pain, frenzy and madness.

He knew he could not kill them all, so he endeavoured to kill those he hated most, and some of those who could be the greatest threats (including ). 

The ones slain include:
\begin{enumerate}
  \item \hr{Nathrach}{\Nathrach}
  \item \hr{Tezrabal}{\Tezrabal}
\end{enumerate}


He tried hard to kill \Morcariel, but failed. 
But he let \Azraid, \Zachirah, Ramiel and \Sithiyacaan{} live because he foresaw that they might cause trouble and dissension among the \resphain. 

\citebandsong{Nile:AnnihilationoftheWicked}{Nile}{
  Cast Down the Heretic
}{
  Horus Repulseth Thy Crocodile.\\
  Sut Defileth Thy Tomb.\\
  Nephthys Hacketh Thee in Pieces.\\
  The Sons of Horus Speareth Thee.\\
  The Gods Repulse Thee.\\
  The Flame of Their Fire is Against Thee.\\
  Cursed Art Thou, Impaled Thou Art, Flayed Art Thou.\\
  Heretic, Thou Art Cast Down.

  Blows are Rained upon Thee.\\
  Dismemberment and Slaughter are on Thee.\\
  Thy Crocodile is Trampled under Foot.\\
  Thy Soul is Wrenched from its Shade.\\
  Thy Name is Erased. Thy Spells are Impotent.\\
  Nevermore Shalt Thou Emerge from Thy Den.\\
  Thy City Armana Lays in Ruin.\\
  Damned Art Thy Accursed Soul and Shadow.\\
  Die O One, which Art Consumed.\\
  Thy Name is Buried in Oblivion.\\
  Silence Covereth Thee and Thy False One.\\
  Down upon Thy Belly.\\
  Be Drowned, Be Drowned, Be Vomited Upon.

  Khnemu Draggeth Thy Spawn to the Block of Slaughter.\\
  Sick Shalt Thou be at the Mention of Thine Own Name.\\
  Sekhmet Teareth Out Thy Bowels and Casteth Them into Flames.\\
  She Filleth Thine Orifices with Fire.\\
  Uadjit Shutteth Thee in the Pits of Burning.\\
  Nevermore Shall You Breathe or Procreate.\\
  Neither Thy House or Tomb Exist.\\
  Thou Shalt Drive Thy Teeth into Thine Own Body.\\
  Heretic, Thou Art Cast Down.\\
  Overthrown, Ended, Hacked in Pieces, Slaughtered, Butchered.\\
  Ra Hath Made Thoth to Slay Thee Utterly.
}





\subsubsection{\Satharioth{} are born}
The \satharioth{} are born. 
Compare to the front cover picture of \artisttitle{Exmortem}{Berzerker Legions}. 

Each of them now contains a \hr{Fragments of Nexagglachel}{fragment of \Nexagglachel}. 

\Zachirah-tachi (the \Mystraacht) are ecstatic. 

\lyricsbs{Hate Eternal}{Born by Fire}{
  Born by fire now force thy ways. I am the entity.\\
  I hold the chalice, the praise of demi-gods, my oath to thee.\\
  Behold majestic strengths amongst the chosen ones,\\
  to desecrate, dominate all enemies that dare to rise.
  
  Impending visions of prophecies await the dormancy.\\
  To seek our path, the path of righteousness, eternal bliss.\\
  Possess the rites of time, to thee of virgin blood.\\
  Now desecrate, dominate the ones that shall be left behind. 
  
  We are the coming of the scorned messiah, apocalyptic seeds.\\
  The loathing of your arrogance ordained.\\
  In absence of the souls in withered lies, defeating all that stand.\\
  Conceration of the frail's demise.
  
  You'll submit to our immortal ways\\
  to only realize that we command.\\
  The armies of the dark shall form in flame, destroying forgery.\\
  You cannot fool the eyes of the gods.
}

They drink \ps{\Nexagglachel}{} blood and are filled with expectation of great, bloody success to come. 

\lyricsbs{Marduk}{Holy Blood, Holy Grail}{
  Empire of blood arise.\\
  Vengeance be our holy blood.\\
  Our holy grail. Kill all the frail.\\
  Be our holy blood, our holy grail.
  
  Vengeance is mine, says the Lord.\\
  And I believe him. I believe him. 
}





\subsubsection{\Nexagglachel lived on}
\target{Nexagglachel lives on in Satharioth}
After \Nexagglachel's death, his soul lived on in fragments inside the \satharioth.
The \resphain never understood this phenomenon. 
They never understood that \draconian immortality was something greater and more profound than their own immortality.
They did not understand the idea that a soul could be destroyed and devoured and yet live on and retain consciousness. 
The \resphain had no Gnosis of the Aenigmata that \KhothSell had taught to her followers.

See also the section on \hr{Draconic immortality}{\draconic immortality}. 









\subsection{The \satharioth begin to feel the curse}
Soon after their inception, the \satharioth{} begin to feel \hr{Curse}{\NexagglachelsCurse}. 
They begin to wonder if this whole project was a good idea.

\lyricslimbonicart{The Yawning Abyss of Madness}{
  Again I drift the halls of wondering. \\
  The black castle of solitude. \\
  On the very edge of sanity \\
  in mental cryogenic interludes. \\
  I have slipped into the seventh, \\
  the seventh circle of Hell, \\
  in realms where deadly shadows \\
  infest every cell. 
  
  Internal ceremonies in ritual death. \\
  External bleedings for the demon of madness. \\
  Hide from the torture of the dazzling light. \\
  The demolition voice shall speak tonight. 
  
  While I'm staring down into the darkest pit, \\
  an ocean black as the night, \\
  so infinite deep and consuming, \\
  it swallows all life force with might. 
  
  Again I drift the halls of wondering, \\
  as I focus for the darkness to come. \\
  In anguish minds uplift the conquering \\
  to cross the line of death beyond.
  
  An abstract reality and bottomless insanity. \\
  To search for the powers to please\\
  the subconscious spirit of disease. \\
  Time found no remedy, \\
  cause winds of darkness was stealing me. 
  
  The yawning abyss of madness. \\
  A cryptic slaughter by hate. \\
  Darkness is the only survivor \\
  as evil dominion terminates. \\
  The yawning abyss of madness.
}















\chapter{\SecondbanewarBook}
% The story of the \secondbanewar, called the Incursion by the \resphain. 















\section{Open War}









\subsection{The \secondbanewar}
\target{Second Banewar}
\target{Incursion}
\index{\secondbanewar}
\index{Incursion}
The dreaded \satharioth{} march forth, legions of \banes{} and monsters at their back, 
announcing to all of \Miith{} the beginning of the \secondbanewar.
Or \quo{the Incursion}, as the \resphain{} call it. 









\subsection{Technology}
\hr{SBW technology}{Technology was fairly high}.











\subsection{\Ishnaruchaefir{} and \Secherdamon}
\target{Early conflict between Ishnaruchaefir and Secherdamon}
Have lots of conflict between the two brothers. 
\Secherdamon{} blamed \Ishnaruchaefir{} for \ps{\Nexagglachel} death, and much more. 
They fought and hated each other. 

After \ps{\Nexagglachel} death, there was much dispute about who, if anyone, should inherit his place as leader of the \dragons{}. 

\index{stewardship}
\Ishnaruchaefir{} claimed that \Nexagglachel, in their last conversation, had named him his successor and passed on the mantle of stewardship to him. 
But they only had his word for it. 

\Ishnaruchaefir{} was a great and acknowledged warrior and hero already before the \secondbanewar, so he argued that he would make a better war leader. 
\Secherdamon{} was famous for his more peaceful achievements. 
He was a scientist and philosopher and artist.
A nerd, where his brother was a macho-man. 

\Secherdamon{} argued that he really was more skilled. 
\ps{\Ishnaruchaefir} accomplishments looked flashy, but they were all things of destruction. 
\Secherdamon{} was a \emph{creator}, and it took much more expertise to create than destroy. 
\Ishnaruchaefir{} countered, saying that creation was all fine and dandy in peace time, but this was war, and a destroyer was needed, 

\target{Ishnaruchaefir gains title of Destroyer}
Hence arose \ps{\Ishnaruchaefir} title of \hs{Destroyer}. 
It was used for him in the war: 
\begin{prose}
  \ta{Beware! Flee for your lives! Here comes the Destroyer!}
\end{prose}

Later, \Secherdamon{} would muse that people ought to call \emph{him} the \quo{Creator}, in contrast. 

In the end, \Ishnaruchaefir{} won and was accepted as \ps{\Nexagglachel} successor. 
Even though \Secherdamon, being more of a team player and less of a loner, might have made a better leader. 











\subsection{Two attacks: One against the tree}
\target{Resphain attack tree}
The \resphain planned two simultaneous attacks: 
One against \Nexagglachel and one against the \dragons' world-tree. 
\hs{Saduraid} was the \resvil who got the honour of leading the attack against the tree.











\subsection{The first battle}
A \resphan{} army marches against a \draconic{} city for the very first time. 
A hapless \scatha{} stands guard and sees the terrible black horde approach. 
They come with ice and cold, clad in \hr{Resphan crystals}{black onyx and other crystal}. 

\lyricsdimmuborgir{Raabj\o{}rn Speiler Draugheims Skodde}{
  Langt\ldots{} der borte i m\o{}rket.\\
  Gjennom tretopper der m\aa{}nelys driver.\\
  Langt\ldots{} der borte i all t\aa{}ke.\\
  Inn gjennom min sjel den sorte angst river.
  
  P\aa{} de mosegrodde steiner de seg viser,\\
  n\aa{}r nattem\o{}rket har senket seg over.\\
  Ekkoene\ldots{} fra deres grufulle jamring\\
  endel\o{}st\ldots{} du kan h\o{}re.\\
  
  I horisonten langt vekk\\
  skimtes den sigende skodde.\\
  Horder av ild rider m\aa{}nelyset i flokk.\\
  Ved daggry de samles ved en bortgjemt odde.\\
}

The \resphain\dash especially the dark \Mystraacht\dash chant their evil war songs. 

\lyricsdimmuborgir{For All Tid}{
  Hver en t\aa{}re er frosset.\\
  V\aa{}r sjel er lenket.\\
  V\aa{}rt hat er blodig.
  
  All glede er svunnet.\\
  All latter er forstummet.\\
  Alt liv skal ende i d\o{}d.
  
  I et kalt og \o{}de landskap\\
  skal den sorte horde tre frem.\\
  V\aa{}r herre skal stige opp for all tid, \\
  reise sitt rike igjen.
  
  N\aa{} er tiden kommet.\\
  Ja, knus de godes ord.\\
  La oss for alltid bli herskere \\
  p\aa{} denne jord.
}

\lyricsbs{Vital Remains}{Entwined by Vengeance}{
  Breath the air of the dawning winds, \\
  awakening the process \\
  of unpure procreation. \\
  Born to this world to cause your destruction. 
  
  Listen to our legion, chanting thy name. \\
  Listen to our legion, chanting thy name. \\
  Listen to our legion, chanting thy name. \\
  Blasphemy reigns unchallenged. \\
  In the name of torment we reign supreme. 
}

\lyricsbs{Vital Remains}{Entwined by Vengeance}{
  Moon at dawn, high above the horizon. \\
  Wind is calm, sun is slowly rising. \\
  Clouds will form, hide the blazing star. \\
  Mighty winds bring the coming storm. 
  
  Gather, sons of the northern frost. \\
  Born of thorns, you are nocturnal ones. \\
  Moonlight ride, your chariot will glide \\
  through the sky into a blade of glory. 
  
  The climate's right, prepare to fight. \\
  Observe the light in the dark night. \\
  Onward we ride, nowhere to hide. \\
  You fear in side, let the battle begin. 
  
  Cast the souls into the blazing fire. \\
  Sacrifice, judgment of our desire. \\
  Battles end, victory won. \\
  Lord of Darkness, your work is done.
  
  Warriors of the night, \\
  come and rejoice, hear the harlots sing. \\
  Celebrate in triumph. \\
  Warriors of the night, \\
  come and rejoice, hail you noble king. \\
  Celebrate thy victory. 
  
  Rebelling souls born against God, \\
  armed and ready to dethrone the fool. \\
  Twilight has come, twilight of the gods. \\
  Dawn breaks the east, it's the morning of Majick.
  
  Destroy the light, don't fear the darkness. \\
  Spirits arise, hover the crimson sky. \\
  Destroy the light, don't fear the darkness. \\
  Conquer and fight, take over the holy kingdom.
}





\subsubsection{They come from the cold north}
The invaders come from the cold north. 

\lyricsbs{Exmortem}{Berzerker Legions}{
  Born through an ice ages blast.\\
  Demonic winter race.\\
  Anger is present in their empty eyes.\\
  Fires dominate the landscape.
  
  Frigid storms and devastating raids.\\
  They are unconquerable.\\
  Frigid seas and devastating raids.\\
  Paramageddon.
}









\subsection{The \Dragons{} unite}
\target{Second Banewar unites Dragons}
The \dragons{} had been \hr{Dragons disorganized}{terribly disorganized} ever since the \firstbanewar, despite \ps{\Nexagglachel} heroic efforts. 
But the appearance of a clear external menace\dash and one powerful enough to pose a genuine threat, exemplified by the killing of \Nexagglachel\dash finally roused them, and they managed to unite, at least for a time. 

\Ishnaruchaefir{} acted as a leader of sorts, but reluctantly. 
He was never socially skilled enough to lead the \dragons. 









\subsection{\Zachirah as the Dark Warlord}
\Zachirah{} commands the armies of the \resphain{}. 
He is the most skilled warlord of them, being the most brutal and aggressive of the \satharioth. 
He drives his armies on with bloodlust, hunger and hate. 

\lyricsdimmuborgir{Antikrist}{
  Stig opp p\aa{} min trone, bleke lik.\\
  Fall p\aa{} kne \ae{}rb\o{}diget foran mine f\o{}tter.\\
  Ta imot mitt kalde kyss p\aa{} din panne.\\
  Jeg har lagt veien som f\o{}rer til Helvete klar.
  
  L\o{}ft deres sverd til kamp, stolte menn.\\
  La massakeren begynne i dag.\\
  Hogg hodet av hver kristen\\
  og voldta deres kvinner og barn.
}

The \resphain{} have been driven to raging bloodthirst by the Chaos power within them. 

\lyricsdimmuborgir{Antikrist}{
  Hver natt skal du v\aa{}kne med ett skrik\\
  og kjenne blodet som brenner dypt i deg.\\
  Hver natt skal du rave som en sansel\o{}s i gaten\\
  og utslette hvert et tegn du ser til liv.
}

The voice of \Nexagglachel{} warns the \satharioth{} and \ketherain{} (if any) of \hr{Curse}{the curse}. 

\lyricsdimmuborgir{Antikrist}{
  H\o{}r min tale, menneskedyr.\\
  Mine ord er din fremtid.\\
  Jeg er Satans legemliggj\o{}relse.\\
  Jeg er din herre.
}

\lyricsbs{Aeternus}{Warlust}{
  I break the chains that holds the storm.\\
  I feel its pulse, it hammers the sky.
  
  Volcanic winds of blooded rage,\\
  mind tearing frost\\
  shall provide brutal death.\\
  Once again you shall feel\\
  the darkened realms.\\
  Warriors!
  
  By our will you will kneel.\\
  Beneath us you will always stand.\\
  Your poisoned soul belongs to me.
  
  Warlust.
  
  Remembrance.\\
  We know you know the pain.\\
  Intensified it shall become.
  
  Drenched the fields of war.\\
  Know what we possess.
}

They eat the flesh of their enemies. 

\lyricsbs{Monolith}{Deathcult}{
  I am the plague of the thousand burning cities.\\
  With lust I eat the flesh of my enemies.\\
  Slaying my enemies I delight in war.\\
  Their blood gives me strength to slay the forces of [\Tembrae].\\
  We ride our war horses out of the great steppes of [\Merkyrah].
}





\subsubsection{\Zachirah tempts Ramiel}
\Zachirah{} urges Ramiel to submit to evil as he has. 

\lyricsdimmuborgir{The Maelstrom Mephisto}{
  Ride the vortex winds with the beast inside.\\
  Cast down all memories from a past and future world.\\
  The cynic icons and the cryptic writings\\
  as a picturesque creation in force and spirit.
  Against their reason and will, it is time.\\
  Give darkness it's passion plea.
  
  The venomous tongue, \\
  the inevitable poison,\\
  paralyze the angels.\\
  Freeze the forgiven,\\
  baptize in fire,\\
  unleash the devil at heart.
  
  Unleash the Maelstrom Mephisto.
  
  So sinner, mourn well.\\
  Make all the swans suffer in Hell.\\
  The maelstrom of the Mephisto left the trace\\
  to revel and feast in undelivered grace.
}









\subsection{Thel}
\target{Thel}
\index{Thel}
Thel was the first city that the \resphain built in \Tembrae.
It was later destroyed.

Thel became a legend. 
Its ruins still existed thousands of years later.









\subsection[Shiaraid and Eryal]{\Shiaraid and \Eryal}
\target{Shiaraid and Eryal driven apart}
\Shiaraid{} and \Eryal{} were lesbian lovers already back then. 
They had been for some time. 
Their relationship was sado-masochistic, with \Shiaraid{} dominant and \Eryal{} submissive. 
It used to be healthy and pleasant for both parts. 
\Shiaraid{} knew how far she could go and respected \Eryal{} even when she tortured her. 

But after she became a \sathariah, \ps{\Shiaraid} mind gradually became twisted by \hr{Curse}{\NexagglachelsCurse}. 
Her sado-masochism became a \hr{Self-destructive Shiaraid}{self-destructive madness}. 
She became abusive and downright evil to poor \Eryal. 
They loved each other, but \Shiaraid{} was going mad. 
The Curse broke both their hearts and drove them apart. 

\target{Shiaraid and Eryal break up}
It came to an ugly break between them. 
The ensuing heartbreak was one of the reasons why \Shiaraid{} and \Mystraacht{} later fell from grace, while \Eryal{} became one of the \hr{Founding of Kezerad}{founders of \Kezerad}. 









\subsection{Dynasties drift apart}
\target{Dynasties drift apart}
In the beginning, \Azraid was the dark, mysterious necromancer-king, ruler of all, and \Zachirah was his bloodhound. 
It did not last.
\Zachirah grew disgruntled with \Azraid's leadership. 
He began to see \Azraid as a wuss and resented serving under him. 

Besides, \Zachirah remembered how \Azraid had himself usurped his brother's place.
\Zachirah decided it was his time to usurp \Azraid. 

\Zachirah's rebellion was a catalyst that triggered more rebellions.
The \resphain began to split apart into many factions (only much later stabilizing into the famous dynasties). 
\hr{Dynasties split}{The final split} did not happen until after the Shrouding, but there was much unrest and scheming and infighting already during the Incursion War. 
This infighting was one of the major reasons why the \resphain did not win the war: 
They lost their unity, which was one of their greatest assets against the chaotic \dragonlords. 









\subsection{Battle scenes}
Have a battle scene where a few \dragons{} mow down mortals by the thousands. 
Show how worthless and impotent humanoids are compared to \dragons.

\lyricsflnv{10}{
  The passage of the Golden \Dragons{} and the Emperor completely destroyed the knights. 
  In one stroke of lightning, Wismerhill had lost his best forces. 
  The high nobility of the Black Moon had been annihilated!
}

Have another battle scene, or the same, where \dragons{} fight against \banes{} and their monsters. There is slaughter inflicted on both sides, with only selected super-heroes being untouched. 

\lyricsflnv{10}{
  Only the Emperor's \Dragon{} seemed untouchable, and it even managed to hold its own against the Lords of Negation. 
  The Emperor was truly a terrifying opponent.
}









\subsection{World tree destroyed}
\target{Resphain destroy world tree}
\target{World tree}
In this age the \dragons had a \quo{world tree}. 
It was a humongous living machine that looked sort of like a giant tree or bush. 
It was an \trope{EldritchAbomination}{Eldritch Abomination}, a horror that fed on the blood, flesh and souls of living creatures. 
But in return, it fed the earth so farmers could grow stuff. 
It was a central keystone in the ecosystem of the world in those days. 
It sucked up the power of the Heart of \Miith and distributed it to the people through its roots which reached deep into the earth and thousands of kilometres out through the land. 

It was a horror, but it had been there for hundreds of years, so the people were used to it and worshipped it as a godlike thing, alongside the \dragons which were its masters. 
The people relied on the tree for their livelihoods. 

The \resphain saw none of this. 
When they saw the tree, they saw only a cancerous monstrosity that leeched energy from the planet and ate the flesh of its denizens. 
It was an abomination and just went to demonstrate how monstrous and evil the \dragons were. 
The \resphain would liberate \Miith from this blight and then destroy the wicked \dragons. 

So they attacked and destroyed the tree. 
Using \SitraAchra sorcery they infected the tree with a terrible blight. 
They infected the \dragons' entire network of magical plants and made them all rot away and die. 

This was a tragedy and a catastrophic blow for the \dragons and the denizens of \Tembrae.
Their ecosystem and economy suddenly collapsed overnight. 

Compare to the scene in the movie \cite{Movie:Avatar} where the \humans bomb the Na'vi Home Tree. 

\Rystessakhin mourned the loss of the tree. 

\citebandsong{BlindGuardian:NIME}{Blind Guardian}{Nightfall}{
  No sign of life did flicker.
  In floods of tears she cried:
  \ta{All hope's lost. It can't be undone.
    They're wasted and gone.}
}

\Rystessakhin remembered the fall of \Nexagglachel, the first tragedy of the Incursion. 

\citebandsong{BlindGuardian:NIME}{Blind Guardian}{Nightfall}{
  \ta{Monstrous it covered the shore
    Fearful into the unknown}
  Quietly it crept in new horror
  Insanity reigned
  And spilled the first blood
  When the old king was slain
}





\subsubsection{Technology set back}
\target{Incursion hurts Ophidian technology}
The destruction of the world-tree was a catastrophe for the \ophidian civilization.
It broke their infrastructure and made much of their technology inoperable. 
It was like the \hr{Ophidian technology set back after Sethicus}{setback that happened when they lost \Sethicus}. 





\subsubsection{\Sithiyacaan realizes it}
\Sithiyacaan realized that the tree was not pure evil, but a vital necessity for the \Tembraeans. 
This made him question his people's right to conquer. 
He realized that the \bane propaganda was false. 
The \resphain were not benevolent heroes fighting against the evil \dragons. 

Later he began to feel \NexagglachelsCurse. 
He feared it. 
He began to repent his people's evil. 

\citebandsong{BlindGuardian:NIME}{Blind Guardian}{Noldor (Dead Winter Reigns)}{
  (You) can't escape from my damnation,\\
  (nor) run away from isolation.
}









\subsection{\Ishnaruchaefir leads the \dragons{} to war}
\target{Ishnaruchaefir leads the Dragons to war}
\Ishnaruchaefir{} fights against the \resphan{} menace, leading his \draconic{} brethren and their massive armies into battle.

\lyricsbs{Bal-Sagoth}{The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire}{
  Hearken, the clarion is upon the winds, \\
  now the call to arms is upon us all. \\
  (Grim warriors, take up thy spears and hone thy gleaming swords. \\
  Archers, string thy bows, brave knights, saddle the steeds of war.) \\
  The glory of battle is nigh at last, \\
  our banner shall fly this day in victory!
  
  My warriors, a legacy shall this day be wrought by our blades,\\
  decreed by the gods, \\
  blessed by the blood of vanquished foes. \\
  Our destiny beckons\ldots{}
}





\subsubsection{\Ishnaruchaefir curses the \resphain}
\ta{Your race will perish.
  We will destroy you.
  They that fight will meet with slaughter at the hands of their betters.
  They that fight not will be trodden under foot, down to the very last mewling whelp.
  Your souls shall feed the hunger of the \xzaishanns in our veins.
  Your flesh will become carrion.
  And when victor and worm alike have slaked their thirst, your race will be not even a memory.
  Nothing.}









\subsection[Aryothim abandon alliance]{\Aryothim{} abandon alliance}
The \aryothim{} (and the few \vorcanths{}) gradually found out that the \resphain{} were in league with the \banes, and that the \banes{} were genocidally evil. 
They were nonplussed, so they seceded from \hr{Resphan-Aryoth alliance}{their alliance with the \resphain}. 
They retreated to Visha and remained mostly neutral. 

But the \vorcanths{} were very loyal by nature, so even if they would no longer fight in the \ps{\resphain} war, the bonds of friendship they had tied with individual \resphain{} (including Ramiel and \Shiaraid) survived. 





\subsubsection[Aryothim went downhill]{\Aryothim{} went downhill}
It went ill for the \aryothim. 
They had suffered many losses in the war. 
After they seceded from the alliance it got no better. 
Now both sides in the \feud{} hated them. 

The different \aryoth{} tribes also hated one another. 
Some tribes hated the others for \quo{tricking} them into the alliance, and the others hated the first group for tricking them \emph{out} of the alliance. 

Their only support were the \vorcanths, and they didn't give any hard and fast promises. 









\subsection{The devastation wrought}
The war is horribly bitter and brutal and bloody, and by the end\dash many years later\dash both sides are decimated. 

\lyricsbs{Exmortem}{Funerary Sculpture}{
  Huge battle machines\\
  now funerary sculptures.\\
  Armoured divisions\\
  no longer a threat.
  
  Isolated war scenarios.\\
  Rusty iron deserts.\\
  Human remains\\
  in the sand and the wrecks.
  
  Unaffected of the grim disease\\
  I walk these fields of flesh piles.\\
  Desolated, lifeless.\\
  Slowly decaying.
  
  Huge battle machines\\
  now funerary sculptures.\\
  Armoured divisions\\
  now plague eaten filth.
}





\subsubsection{Diseases}
When the \resphain invaded from \Nyx, they and their mortal armies brought with them many new, nasty diseases from \Nyx.
And they, in turn, encountered \Tembraean diseases foreign to them.
The immortals were too resilient to succumb to mere mortal diseases, but the mortal \Tembraeans and \Nyxians were not so lucky.
They died in droves.
\Tembrae was ravaged by deadly epidemies, further compounding the horror and carnage of the \secondbanewar.

But the \secondbanewar lasted more than 100 years, and it was fought chiefly with immortal armies.
The epidemies were a great problem for logistics since they killed a lot of servants and food sources, but they were not as great a problem as some other aspects of that time.
When the \secondbanewar was over, the epidemies had run their course and the survivors had developed resistance.









\subsection{It looks hopeless}
The war was going badly for the \Miithian s. 
It looked hopeless. 
The \bane{} hordes were endless. 

Compare to the hordes of Chaos in \cite{RPG:Warhammer:HighElves} and other \emph{Warhammer} titles. 




\subsubsection{\Ishnaruchaefir is a poor leader}
At this point, \Ishnaruchaefir{} had been grudgingly accepted as \emph{de facto} \dragonlord{} and leader of the \dragons.
He did his best to lead because he felt he had to, but he was no great leader nor tactical genius. 

He was an able leader who won through by sheer willpower, courage, daring and brute force, but he also made some major strategic blunders. 
Moreover, he was already becoming alienated from his fellow \dragons{}, which made him more and more self-sufficient and unwilling to listen to advice, which made everything worse. 





\subsubsection{\Ishnaruchaefir's sons die}
\target{Ishnaruchaefir's sons die}
\Ishnaruchaefir had three sons:
\hr{Tentocoth}{Tentocoth}, \hr{Thiencaste}{\Thiencaste} and \hr{Rathyon}{\Rathyon}. 
The three were close friends and great, brave warriors. 
In one of the first great battles against the \resphain the three brothers led the \draconian forces and fought from the frontline.

There was a great tragic battle.
Some very important monuments were destroyed, immense numbers of soldiers and civilians died, and the three heroic brothers perished. 

Compare to the battle in \cite{Movie:Avatar} where the Home Tree is destroyed. 





\subsubsection{\Ishnaruchaefir takes drastic measures}
The news of his sons' death hardened \Ishnaruchaefir. 
He decided drastic measures had to be taken. 
He wanted to call upon darker, forbidden powers. 
He decided to seek out \NerrhanKoss, the darkest, most horrible, most frightening of the \xss, and make a pact with him. 

His fellow \dragons{} were against this. 
They feared that the power of \NerrhanKoss{} was too dark, too evil, and that if they called upon him for aid it would corrupt and doom them and call down eternal tragedy upon their kind and all \Miith. 

\Ishnaruchaefir did not care.
He was willing to do whatever it took and pay any price. 
He cared not for his reputation.

\citebandsong{BlindGuardian:NIME}{Blind Guardian}{The Curse of F\"eanor}{
  Taken the long way. Dark realms I went through.\\
  I arrived. My vision's so clear. \\
  In anger and pain I left deep wounds behind. \\
  But I arrived.\\
  Truth might be changed by victory.

  I've heard the warning.\\
  Well, curse my name.\\
  I'll keep on laughing.\\
  No regret. No regret. 

  All hope is gone but I swear revenge. \\
  Hear my oath.\\
  I will take part in your damned fate.
}





\subsubsection{\Ishnaruchaefir gains the glaive}
\target{Glaive origin}
\Ishnaruchaefir{} went on, heedless of their warnings. 
He was willing to pay any price. 
So went to a dark shrine of \hr{Nerrhan-Koss}{\NerrhanKoss} and made his pact. 

Here he gained his \hs{glaive}. 
It was a gift of sorts from \NerrhanKoss. 
\Ishnaruchaefir{} forged it himself (using magic), but \NerrhanKoss{} taught him how. 
Maybe \NerrhanKoss{} also provided the materials. 
So in a sense, the glaive was a gift from \NerrhanKoss. 

\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  The king was compelled to lead his forces to the shadow-haunted Mountains of the Dead, a grim and brooding place steeped in dark and ancient legendry. Alone he rode into the gaping maw of a huge cave hewn into the side of the tallest mountain co untless ages past by unknown hands.
  
  For three full days and nights he did not emerge from the cave\ldots{} until, at last, he rode forth from the eldritch mountain once more, a terrible knowledge shadowed in his icy eyes, and bearing in his gauntleted fist a huge black sword, a magnificent ebon blade which no human blacksmith ever forged. Fearsome sorcerous power crackled within the yard of black steel, dancing upon its searingly honed, glyph-scored blade\ldots{} and its bejewelled, dragon-carved hilt did whisper arcane secrets to the king in a strange, elder tongue.
}





\subsubsection{\Ishnaruchaefir takes the name \Nierzshah}
\target{Ishnaruchaefir takes the name Nierzshah}
Armed with new Gnosis and power from the \xss, \Ishnaruchaefir took a new name:
\quo{\Nierzshah}, meaning \quo{Destroyer}.
At this point he had already been known by the title \quo{Destroyer} by \resphain and \dragons alike because of his fierceness in battle. 

It was a dark and terrible name, full of destructive power and ferocity and malice. 

\lyricstitle{Something}{%
  Now I am become Death, the Destroyer of Worlds.
}





\subsubsection{\Ishnaruchaefir became psycho-badass}
Armed with the glaive, the gifts of dark \NerrhanKoss and his new terrible name, \Ishnaruchaefir{} was suddenly so psycho-badass you would not believe it. 
\NerrhanKoss{} had taught him how to unlock and unleash even more \xsic{} power, so \Ishnaruchaefir{} had \trope{TookALevelInBadass}{Gained a Level in Badass}. 

Compare to Aenarion in \cite{RPG:Warhammer:HighElves}, who becomes \uber-powerful after he draws the forbidden and evil Sword of Khaine. 

\citeauthorbook{RPG:Warhammer:HighElves}{Andy Chambers et al}{High Elves}{
  Aenarion returned to the fray and carried everything before him. 
  The power of the sword was so great that nothing could stand against him.
  It filled his enemies with terror and his own troops with unshakeable faith and unquenchable blood lust. 
  The followers of Aenarion became ever more brutal, cruel and merciless, lost in a dream of endless slaughter. 
  With each victory they became ever more heedless of their fate, they fought with no thought for their own lives, possessed by a desire to spill the blood of their enemies. 
  All the Elf warriors became heedless of danger and most heedless of them all was Aenarion. 
  
  Old longings, deeply buried in the Elf soul began to stir, and a darkness of the spirit descended on their armies. 
  There were those who fought for the joy of fighting and those who slew for the sake of slaying. 
  Aenarion carved himself out a new kingdom in northern Ulthuan, in the bleak land of Nagarythe, a place that mirrored his own dismal mood. 
  Many of the most savage Elf warriors were drawn here. 
  
  [\ldots{}]
  
  The war reached its final stage, an unequal contest of might between the Elves and the innumerable legions of the four Chaos powers. 
  Touched by Asuryan and marked by Khaine, Aenarion was an all but invincible warriors, a child of darkness and light. 
  His blade lent him power beyond mortal reckoning; the eternal flame gave him the strength to use it. 
  In battle, Aenarion slew foes beyond reckoning. 
  His loyal mount Indraugnir was a match for any Daemon. 
  And yet there was only one Aenarion, and the number of his followers was finite. 
}








\subsubsection{\Ishnaruchaefir{} asks \xss}
\target{Ishnaruchaefir sacrifices to the XS}
\Ishnaruchaefir{} sought out the counsel of the \xss{} or cosmic gods. 
They wanted a price in blood before they would help him. 
He offered them his own blood as payment (saturated with \xsic{} power), but that was not enough. 

\target{Quelthah dies}
So he challenged the \sathariah{} \hr{Quelthah}{\Quelthah} to single combat. 
\Quelthah{} accepted. 
He fought bravely, but fell. 

\target{Ishnaruchaefir eats Quelthah}
\Ishnaruchaefir{} captured \ps{\Quelthah} soul and offered it as a sacrifice to the \xss. 
They accepted and helped him. 
They returned a fragment of \ps{\Quelthah} soul to \Ishnaruchaefir, allowing him to ingest it. 
This piece contained some of the \hr{Fragments of Nexagglachel}{\Nexagglachel{} fragment} inside \Quelthah. 
From eating this, \Ishnaruchaefir{} \hr{Ishnaruchaefir understands the curse}{inherited a certain intuitive understanding} of \hr{Curse}{\NexagglachelsCurse} and the psychology of the \satharioth. 





\subsubsection{\Ishnaruchaefir attacks \Nyx}
\target{Ishnaruchaefir devastates Nyx}
\Ishnaruchaefir led an incursion into \Nyx. 
As retribution for the \resphain's crimes, he and his brethren unleashed the destructive power of the \xss upon the \resphan homeworld. 
This slaughtered countless thousands of \resphain and millions of mortals and turned \Nyx into a blackened ruin. 
\Nyx would never recover from this blow. 





\subsubsection{\Resphain{} strike back}
With his newfound power, \Ishnaruchaefir{} pushed back the \resphain.
But they were not done. 
They devised counter-plans and again turned the tide of the war in their favour. 

So the \dragons{} had to take \emph{new} drastic measures. 
They began to plan the \hr{Shrouding}{\SecondShrouding}, which consisted of letting the \xss{} rape the foundations of the world. 









\subsection{\Ishnaruchaefir and \Azraid}
\target{Ishnaruchaefir and Azraid develop empathy}
\Ishnaruchaefir and \Azraid met a few times. 
They secretly developed a faint empathy of sorts.
\Ishnaruchaefir had heard from \Nexagglachel that \hr{Ishnaruchaefir learns Azraid is on the level}{\Azraid was on the level}. 

\Ishnaruchaefir had some suspicion that \Azraid had more up his sleeve than he let on, and that he had plans for \Miith different from those of the \banelords.
He suspected that \Azraid had a hand in the \Shrouding, although \Azraid did not allow himself to be seen. 

Later the two would \hr{Ishnaruchaefir and Azraid plot together, early in TBW}{begin to plot together in ernest}. 









\subsection{\Ishnaruchaefir asks \Zaz and \Urzaz}
\target{Zaz denies Ishnaruchaefir}
At some point (perhaps here, perhaps earlier or later), \Ishnaruchaefir appealed to the mysterious pair \hr{Zaz}{\Zaz and \Urzaz}. 
He asked them for aid. 

They denied him and punished him.
He was wounded and weakened by their attack.

Compare to \bandsong{Bal-Sagoth}{The Hound of Chaos Transcends the Barricades of Z'xulth}.














\section{The \SecondShrouding (\yds{Shrouding})}
\target{Shrouding}
\subsection{The \SecondShrouding{} is prepared}
The \dragons{} come up with the \SecondShrouding{} as a means to banishing the \banelords{} from \Miith{} and ending the war.
%The \secondbanewar{} ends with the \SecondShrouding{}. 





\subsubsection{\Ishnaruchaefir{} advocates the Shrouding}
\target{Ishnaruchaefir and the Shrouding}
There is dissension among the \dragons{} about whether this Shrouding plot is a good idea. 

\Ishnaruchaefir{} was an advocate of the Shrouding plan. 
He had secretly negotiated with some \resphan{} lords who were planning to betray the \banes. 
That was why he was so fond of the Shrouding plan: 
He had invested a lot in it. 
(Arguably this was a case of the Down Funds Fallacy.)

(He would later go on to become one of the prime architects behind the \hs{Lie Sublime} and the \hr{Charade}{\charade}, too.) 





\subsubsection{The balance of the \matrices}
\target{Balance of the Matrices}
\Ishnaruchaefir{} still remembered his dreadful visions of a bloody future of eternal war. He conferred again with the wise elder \ophidians, \nagae{} and perhaps other creatures (such as the \hs{cosmic gods}). 
They tell him that the two \matrices{} are closely balanced, and that it is this unholy balance that keeps the war going, and will continue to do so. 
Tremendous \vertex{} power will be needed to shatter this balance, and this is not likely to happen for many thousands of years. 

This is a subversion of the trope \trope{BalanceBetweenGoodAndEvil}{Balance Between Good and Evil}.

And so, the way \Ishnaruchaefir{} saw it, if the war could not be won or stopped, then it could at least be contained, made milder. He believed in the \charade{} project, because he saw it as a means of creating a peaceful world. That way, the great war between \dragons{} and \banes{} would be contained, and they would have to resort to stealth, instead of rampaging freely and laying waste to the world. 





\subsubsection{Three futures}
\target{Ishnaruchaefir sees three futures}
\target{Ishnaruchaefir chooses eternal war}
A revision: 
\Ishnaruchaefir{} did not see only one future, but three: 
Chaos, Darkness or eternal war. 
The two first were too horrible to contemplate, so he chose the third. 

The above is not strictly correct. 
The gods did not see three futures. 
They saw a myriad number of futures. 
But in most of them, \Miith{} was dominated by one of three tendencies. 

The gods should \hr{XS speech}{speak weird}. 





\subsubsection{Weaving artifacts}
\target{Fulcrum}
\target{Fulcra}
\target{Weaving artifacts}
\target{weaving artifacts}
\target{weaving artifact}
\index{Fulcrum}
\index{weaving artifact}
In order to effect the Shrouding, the \dragons{} used powerful magical items in the weaving. 
These became known as the \quo{Fulcra}, or \quo{weaving artifacts}. 
One such was \ps{\Ishnaruchaefir} \hs{glaive}. 

These Fulcra are item-shaped \vertices{} that hold the Shroud in place. 

\lyricsbs{Bal-Sagoth}{
  And Lo, When the Imperium Marches Against Gul-Kothoth, Then Dark Sorceries Shall Enshroud the Citadel of the Obsidian Crown
}{
  Darkly bejewelled circlet of night,\\
  crown of the Elder King.\\
  Unfettered at last the Trinity of Might,\\
  the sceptre, the sword, and the ring.
}





\subsubsection{\Ishnaruchaefir{} needs \ps{\Secherdamon} Gnosis}
\target{Ishnaruchaefir steals Secherdamon's research}
\Ishnaruchaefir{} needed to contact \hr{Naath-Kur-Ramalech}{\NaathKurRamalech}, the most important of the \xss{} that partook in the forging of the \hr{Crystal Sphere}{\CrystalSphere}. 
In order to do that, he needed some more Gnosis about the \ps{\xss} Aenigmata. 

He knew that \hr{Secherdamon seeks Gnosis}{\Secherdamon{} had done lots of research in this field}, so he sought him out. 
After some persuasion (and emotional blackmail invoking \ps{\Nexagglachel} dying wishes), \Secherdamon{} agreed to \cooperate. 
So he put all his research at his brother's disposal. 

\Ishnaruchaefir{} stood on \ps{\Secherdamon} shoulders, and with a little help from the cosmic gods he achieved a flash of insight, granting him the Gnosis he needed. 
But he did not pass this knowledge on to \Secherdamon. 
At first \Ishnaruchaefir{} excused himself by saying that there was no time to teach \Secherdamon{} the very complex revelations he had seen.
\Secherdamon{} accepted this explanation, but expected \Ishnaruchaefir{} to tell him everything as soon as he was able. 

In truth, \Ishnaruchaefir{} was reluctant to tell \Secherdamon{} anything. 
He did not want to share the burden of \hr{Ishnaruchaefir's stewardship}{stewardship}, and he was already now getting paranoid.
Later, he would \hr{Ishnaruchaefir refuses to tell Secherdamon Gnosis}{outright refuse to tell \Secherdamon}. 





\subsubsection{\Ishnaruchaefir{} alienated}
\Ishnaruchaefir{} was bad at cooperating with his brethren. 
Numerous factors conspired to drive him apart from them: 
\begin{enumerate}
  \item 
    He felt guilt over having caused \ps{\Nexagglachel} death. 
    He should have died in his stead. 
  \item 
    \index{stewardship}
    He had \hr{Ishnaruchaefir gains stewardship}{promised \Nexagglachel{} to carry the burden of leadership}. 
    He was \hr{Ishnaruchaefir's stewardship}{unwilling to share that load}. 
  \item 
    Other \dragons{} accused him of being a coward and a weakling, having abandoned \Nexagglachel{} to his fate, leaving a far better \dragon{} to perish in his stead. 
    He failed to grab his obvious chances to save \Nexagglachel, they felt. 
    \Ishnaruchaefir{} partially agreed, but he refused to show any weakness and acknowledge any guilt. 
    This made the discussions turn nasty. 
  \item 
    There was a deepening chasm between him and \Secherdamon. 
    Both wanted to inherit \ps{\Nexagglachel} place. 
    They disagreed on how to lead their people, how to wage the war and how to carry on the legacies of \Nexagglachel{} and \Kserasshana. 
  \item 
    He argued with \Rystessakhin{}. 
    They had different plans to defeat the \resphain. 
    They were driven apart by their disagreements. 
\end{enumerate}

\Ishnaruchaefir{} became alienated from his \draconic{} brethren. 
He convinced himself that it was a futile effort to attempt to unite them behind him and make them see the wisdom of his actions. 
He could not trust his fellow \dragons. 
He was better off alone, walking his own path and trusting himself only, whatever others may think of him. 
So he took it upon himself to do as much as he could on his own. 
He did not rely on the input and expertise of others.
This meant that the \SecondShrouding{} ended up being much bloodier than it needed to be. 
It killed more \dragons{} and others and laid waste to more Realms than it needed. 
It was crude and rushed work. 
If they had all worked together, they could have found a cheaper, better, more effective solution. 
But that was not to be. 
Everyone's pride and other negative emotions prevented it. 
It was quite the tragedy. 

He decided to carry his burden alone and in silence. 
He had become disillusioned and now refused to \cooperate.
His fellow \dragons{} had become a burden and an obstacle. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Citizen}{
  I preach not for understanding.\\
  In you I have no faith.\\
  I spit at you my truth;\\
  that you are the burden of my heritage.
}

But in a way it was nothing new to him. 
It was in his nature to walk alone. 
He was used to trust himself and not depend on others. 

\citebandsong{Ihsahn:angL}{Ihsahn}{Monolith}{
  It was never\\
  the icy winds of the heights,\\
  but the coldness of the world\\
  that hardened my foundation.
  
  Whether your approach\\
  is that of praise or blasphemy,\\
  the construction of my being\\
  will remain the same.
}

He saw himself as called to a higher purpose, one that lesser beings (even other \dragons) could not understand. 

\citebandsong{Ihsahn:angL}{Ihsahn}{Monolith}{
  If my soaring presence\\
  threatens to break your neck,\\
  then so be it.\\
  You shall dread my name.
}

He accepted that others would not understand and love him.

\citebandsong{Ihsahn:angL}{Ihsahn}{Monolith}{
  There is a fundamental cleft\\
  between your world and mine.\\
  One of divine origin.
}

He felt the others were hypocrites who would never realize that he was right and they were wrong. 
(He would later revise this view a little bit, after realizing the depths of depravity to which he himself could sink.)

\citebandsong{Ihsahn:angL}{Ihsahn}{Monolith}{
  Were you to witness\\
  the nakedness of your own soul,\\
  it would still appear a tower of Babel.
  
  Is it such a crime to go apart and be alone?\\
  Your holy simplicity turns gold into stone.
}





\subsubsection{\Ishnaruchaefir{} kept Gnosis to himself}
\target{Ishnaruchaefir refuses to tell Secherdamon Gnosis}
After the \SecondShrouding{} was complete, \Secherdamon{} still felt \Ishnaruchaefir{} was obligated to teach him the Gnosis that he had achieved by using \ps{\Secherdamon} research. 
But \Ishnaruchaefir{} refused. 
He did not trust \Secherdamon. 
They had grown to dislike and distrust each other during the infighting in the war. 

\hr{Secherdamon becomes better when denied Gnosis}{\Secherdamon{} grew bitter}. 





\subsubsection{\Secherdamon{} takes over}
After \Ishnaruchaefir{} went his own ways, \Secherdamon{} tried to take over and fill the empty position of leader. 
He tried to pick up the pieces after \Ishnaruchaefir{} abandoned them and left them in chaos and ruins (at least, that was how \Secherdamon{} saw it). 

This was hard work. 
It was one of the reasons why he came to hate \Ishnaruchaefir. 









\subsection{\Satharioth betray the \banelords}
\target{Banishment of the Banelords}
\target{End of the Second Banewar}
\target{Satharioth betray Banes}
The war rages. 

At the time of the \secondbanewar, the \dragons{} were weakened by internal warfare, so the \resphain{} had the upper hand for a while. 

But they crumbled when the \satharioth{} decided to betray the \banes.
%In the end, everyone loses, but especially the \banes. They were secretly backstabbed by the \satharioth{}. 
\hr{Curse}{\NexagglachelsCurse} overcame them, and so, poisoned with hatred of their creators, they decided that they desired overlordship for themselves and were unwilling to defer to their \bane{} masters after all. 

So the \satharioth{} secretly supported the \SecondShrouding{}. 
They allowed the \dragons{} to perform their Shrouding spells and even did some of their own. 
They also supported the \dragons{} with knowledge gleaned from the \hr{Shroud of Nyx}{Shroud of \Nyx}, which \Daggerrain{} had woven at the \hr{Thanatzil dies}{fall of \Thanatzil}. 

\Azraid{} secretly masterminded this deceit, but he did it so masterfully that no one suspected him. 
All the people who knew were quickly killed and their souls destroyed. 

The \satharioth also plotted against one another. 
\Netzachirah and Ramiel and \Azraid had come to hate \Morcariel, so they betrayed him and \hr{Morcariel dies}{let \Secherdamon destroy him}. 

\lyricsbs{Monolith Deathcult}{Origin}{
  The Lord was the blessed name they carried,\\
  composed from the leeches of the Kosmos.
  
  The Gods must be slain,\\
  so [\resphan-]kind will be blessed with their wisdom.\\
  In the darkest depths of AB.ZU,\\
  with the vulpine Snake on our side,\\
  ruler of the underworld of E.DIN.\\
  We conspire against our Masters.\\
  After the dismantling of the alien Gods\\
  we become divine.
}

It remains unknown to what extent the \banes{} know of this treachery\dash certainly no \resphan{} dares bring it up with a \banelord. 









\subsection{\Secherdamon defeats \Morcariel}
\target{Morcariel dies}
By treachery \Secherdamon out\manoeuvred \Morcariel and forced him to fight. 
\Morcariel (with his bodyguards) braced himself for what he thought would be a fair fight and a heroic last stand. 

\Secherdamon:
\talk{Nay, \Morcariel.
  This will not be a fair fight.
  I have tricked thee.}

\Secherdamon took \Morcariel captive. 
He enslaved his soul and tortured \Morcariel forever after, as punishment for his horrible crimes against \dragonkind. 









\subsection{\Ishnaruchaefir and \Rystessakhin}





\subsubsection{\Rystessakhin opposes \Ishnaruchaefir}
But \ps{\Ishnaruchaefir} true love, \hr{Rystessakhin}{\Triestessakhin}, mother of \hr{Nzessuacrith}{\Nzessuacrith} and the \dragon{} closest to him in his life, railed against the plan. 
She saw the Lie Sublime, the perpetual and brutal oppression and the thousand-year-long underground war as a horrible dystopia and insisted that a better solution must be found to destroy the \banes. 
(Compare her to Latra Posae from \cite{RobertJordan:WorldofWOT}.) 
They debated and fought heatedly over this issue, and it drove them apart. 

\ps{\Ishnaruchaefir} vision of the Shrouding was bloody. 
Millions would have to die, and entire Realms might perish. 
\Rystessakhin{} did not like it. 
She felt nothing was worth the terrible cost that \Ishnaruchaefir{} proposed. 
She could not accept the idea of so callously throwing away millions and lives and devastating entire Realms. 
It would be a worse atrocity than the war itself. 

\Rystessakhin{} had a more peaceful, more tree-hugging plan. 
I don't know what exactly, but it should be something that sort of invokes \trope{ThePowerOfLove}{The Power of Love}. 
But without making her stupidly \trope{GenreBlind}{Genre Blind}. 
Anyway, the point is that \Ishnaruchaefir{} does not believe in her plan. 
He believes that only his own, more ruthless plan has a chance of success, because the world is like that. 
Ruthless. 

\ps{\Rystessakhin} plan \emph{could} work. 
He admitted that. 
But he didn't like the odds. 
Moreover, her plan involved her risking her own life and soul, becoming a \trope{BarrierMaiden}{Barrier Maiden} of sorts. 
\Ishnaruchaefir{} would not accept that. 
He did not want to risk losing her.
He would sacrifice everyone else on Mith before he saw that happen. 
He felt that his plan was safer, and therefore well worth the cost in blood. 

Another point of contention was that \ps{\Rystessakhin} plan put her in great personal danger. 
She was prepared to sacrifice her life and soul. 
\Ishnaruchaefir{} felt that \hr{Ishnaruchaefir's stewardship}{the salvation of \Miith{} was \emph{his} burden} and \emph{his alone}. 
He did not want \Rystessakhin{} to pay the price in his stead. 
If he let her do that, he would feel he had failed \Nexagglachel, her, himself and everyone. 
He wanted to bear the burden alone. 
His pride demanded no less. 
(But it was OK to let others die in the process. 
His principles were somewhat strange in that regard.)





\subsubsection{\Ishnaruchaefir as Judas}
\Ishnaruchaefir was a sort of Judas-figure. 
Judas had to sacrifice his honour, his legacy and perhaps his soul (condemning himself to Hell) because he had to \quo{betray} Jesus so that Jesus could die and rise and save Mankind. 

Likewise, \Ishnaruchaefir had to sacrifice his reputation and commit horrible crimes in order to save \Dragonkind. 

\Iscrafel learned that in order to cast the mighty Shrouding spell and close the dimensional gates to \Erebos, he must anoint the glaive with \quo{blood}. 
He must slay a powerful one of his own kind with it\dash{}one of the \hs{Diamond}. 
He considered sacrificing himself, but he felt he could not.
He had \hr{Ishnaruchaefir's stewardship}{stewardship of the world}. 
He could not abandon that responsibility. 
He knew that the world would soon need him again\dash{}especially if he succeeded with his spell.
It would leave the world in ruins. 
He resolved that he would sacrifice himself if need be, but only as a last resort. 

In the end he used \Rystessakhin. 
It was a horrid sacrifice for him. 





\subsubsection{\Ishnaruchaefir{} slays \Rystessakhin}
\target{Ishna slays his beloved}
\target{Ishnaruchaefir slays his beloved}
\target{Ishnaruchaefir kills Rystessakhin}
Ultimately, \Rystessakhin{} somehow managed to stand in the way and block them, preventing \ps{\Ishnaruchaefir} faction from initiating the Shrouding. 
\Ishnaruchaefir{} confronted her and attempted one last time to reason with her. 
They failed to come to an agreement, and he had to admit\dash to himself, and to her\dash that he loved his vision more than he loved her. 

\Ishnaruchaefir needed a sacrifice to complete his spell. 
\Rystessakhin knew that, so she made sure to fuck his plan up.
There was no one else around, and time was running out. 
That was what \Rystessakhin meant when she said she would stop him with her life.
She was certain he would not kill her. 

She was wrong. 

\begin{prose}
  \Ishnaruchaefir: 
  \ta{Aeocrith.}
  
  \Rystessakhin: 
  \ta{Quessanth.}
  
  \Ishnaruchaefir: 
  \ta{Step aside, Aeocrith.}
  
  \Rystessakhin: 
  \ta{Nay. This hath gone too far. I will not let thee do this.}
  
  \Ishnaruchaefir: 
  \ta{Curse thee, Aeocrith. I must! Canst thou not see?}
  
  \Rystessakhin: 
  \ta{Aye, I see very clearly.
    That which thou hast planned is an abomination.
    An atrocity.}
  
  \Ishnaruchaefir: 
  \ta{It is the only way. Let me pass.}
  
  \Rystessakhin: 
  \ta{I will not let thee do this thing.
    Not now, not ever.
    Thou shalt not pass, lest thou go through me.}
  
  \Ishnaruchaefir: 
  \ta{Curse thee! I have to save us all!}
  
  \Rystessakhin: 
  \ta{Thou wouldst damn us all, Quessanth.
    I know what thou intendest.
    It is too vile to consider.}
  
  \Ishnaruchaefir: 
  \ta{It is the only solution left.}
  
  \Rystessakhin: 
  \ta{The price is too high!
    I will stop this madness, with my life if need be.
    Listen to reason, Quessanth!
    We fight the resphain because they are ravagers and destroyers of worlds.
    If we do this thing, we would be as wicked as they.
    Wilt thou have us become destroyers of worlds in their image, Quessanth?}
  
  \Ishnaruchaefir: 
  \ta{If it would save our people?
    Aye.
    I would.}
  
  \Rystessakhin: 
  \ta{Nay, Quessanth.
    I will not let our race pay this price.
    I will not let our race bear this burden.
    This crime.
    This evil!}
  
  \Ishnaruchaefir: 
  \ta{So be it.
    If, as thou sayest, our race must not bear this evil... then they shall not.
    I will bear it.}
\end{prose}


\Ishnaruchaefir was desperate.
He knew time was running out.
He had to act now.
\Rystessakhin's refusal to see reason was making him furious.
She had ruined all other options.

\Ishnaruchaefir could not fail. 
He had a duty to \Nexagglachel.
He had failed him once before (when \Nexagglachel got captured instead of him). 
He was willing to pay \emph{any} price in order to not fail \Nexagglachel again. 

Just before this, \Ishnaruchaefir had sworn an oath not to back down no matter what. 
No matter the cost to him or to anyone else. 

He could sacrifice himself, but no. 
He needed to be alive to maintain the spell and mop up afterwards. 
He had to stay alive. 
There were no other sacrifices available. 
There was only \Rystessakhin. 

And so, at last, he slew her, striking her down with his glaive.

This scene needs to be heartbreaking. 
Compare to the scene in \cite{PhillipPullman:TheAmberSpyglass} where Lyra leaves Pantalaimon behind in order to travel to the realm of the dead. 

The \dragons \hr{True Draconic signifies emotion}{spoke \TrueDraconic out of emotion}. 

\begin{prose}
  \Ishnaruchaefir:
  \ta{Curse thee, \Aeocrith, stand aside!
    Or I swear by the \xss{} I shall strike thee down!}
  
  \Rystessakhin:
  \ta{
    Then strike me down, \Quessanth, for I will not let thee do this thing.}
\end{prose}

At this point, \Ishnaruchaefir{} had already forged his powerful glaive and intended to use it as a \hs{weaving artifact}. 

He did not intend to destroy nor eat \ps{\Aeocrith} soul. 
Nor did he mean to bind her in the glaive. 
He just meant to kill her temporarily. 
Even that was a pretty big thing between lovers (roughly equal to a mortal man brutally beating up or raping his wife). 
That was her own doing. 
She knew the glaive was his weaving artifact, the instrument of his plan.





\subsubsection{Moments of destruction}
\target{Ishnaruchaefir destroys the world}
As he slew her, she latched onto the glaive and poured her soul into it. 
She realized that she could not stop him, so she wanted to help him and share his burden. 
She intended to sacrifice herself and make herself a permanent Barrier Maiden and help him uphold the Shroud. 
He tried to stop her and carry on with his own plan. 
He did not want her to pay the price in his stead. 
He would rather see millions of innocents die. 

He fought to stop her. 
But she insisted. 

Countless innocents died all over the realms in those precious seconds where he struggled against her (she was, after all, sacrificing herself to save those people). 

And it got worse. 
\Ishnaruchaefir{} raged inside at the injustice of it. 
He realized \Rystessakhin{} would sacrifice her soul and so be lost to him, and try as he might he could not prevent it. 

\begin{prose}
  \tho{%
    Without \Nexagglachel{} I am the greatest, the mightiest, the bravest, the noblest of all the \dzraicchenosses.
    I deserve better than this!
    I have worked and fought so hard and sacrificed so much for the world and the \psp{\dragons}{} sake. 
    I have wrung dry and depleted my standing and reputation. 
    And now I must lose my beloved!
    This is wrong!}
\end{prose}

Rationally, he knew better than to appeal to any \quo{justice}. 
He did not believe in such silliness. 
But at that moment he did not care. 
All the burning hot power of the \xss{} was coursing through his veins, and they filled his heart with volatile passion. 
His emotions blinded him and carried him away and took control of him. 
Only for a brief moment, but it was a brutal, costly moment. 
In his fury he lashed out against the world.
Millions died across the Realms of \Miith{} in that moment to sate his anger. 

He released all his anger. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  Come suffering, Apocalypse.\\
  Release the fires of Hell.\\
  I call upon destruction and despair.\\
  Here the days of slumber end.\\
  I beckon the night \\
  to live and overcome the fear.
}

By now he knew he would be hated forever for his actions. 
And in that moment the world could go fuck itself for all he cared. 
So he might as well make it worse. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  Come sin, come shame.\\
  Congregation of contempt.\\
  I bid you welcome to the pyre.\\
  Will our objective truths \\
  withstand this affliction?\\
  I venture.\\
  Let it all come down.

  The deafeaning sound of trumpets roar\\
  in celebration of impending chaos.\\
  This is not terror, this is not war.\\
  Beyond repentance.\\
  This is the call of the abyss.
}

He released, and gave into, his inner evil. 
Part of it was his \xs-born destructive urges. 

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega
}{
  Mass Grave Aesthetics
}{
  Transcendence of thresholds occurs with violence \\
  And will for Vice is like the mind's dark radiance \\
  Which blinds and of which I'm dying \\
  Corruption is the spiritual cancer \\
  reigning in the depths of things \\
  And it fills until the last cell of my vivid being \\
  Dissolution and putrefaction, \\
  prevailing Aesthetic experience, \\
  The splendor of the obscene and inhuman; \\
  For what matters the death of a vague human beings \\
  If thereby the individual affirms himself?
}

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  The Shrine of Mad Laughter
}{
  As if Death was dashed onto the death within, \\
  a violent thrust stealing the light of the eyes. \\
  A ray of darkness, a negation. \\
  The bread of bitterness \\
  that ignites neither devotion nor fervour.
  
  Resplendent nothingness! \\
  Make all things appear with clarity.\\
  Ruined in the flame of repudiation, \\
  in the flame of God!
}

He knew what he was doing was evil.

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  The Shrine of Mad Laughter
}{
  Interwoven joy and confusion, 
  a stabbing confusion. \\
  Asphyxiation from within, yet I gained this certitude: \\
  Malediction, degradation, sown in me like seeds.\\
  Now I belonged to my flesh. \\
  I belonged to death.\\
  In harbouring a desire for the hideous, \\
  I was beckoning to death. 
  
  Insatiable combustion! Expand! \\
  This body is thy vessel of grace!
}

In these moments of destruction, a tremendous struggle and a tremendous character development took place inside \ps{\Ishnaruchaefir} head. 
He gained much insight into his own Aenigma. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  The Repellent Scars of Abandon and Election
}{
  I was beyond withstanding my own ignominy. \\
  I invoked it and blessed it.\\
  I progressed ever further into vileness and degradation. \\
  Am I resurging, intact, out of infamy?
}

At last he realized that his struggling was pointless and only demeaned her noble sacrifice (by aggravating the destruction she fought to prevent), so he relented and let her do her thing. 
She poured all her soul into the glaive, where it would \hr{Rystessakhin's consciousness}{become crippled and never again regain consciousness}. 

\index{stewardship}
He was not happy about it. 
He felt like he had failed in \hr{Ishnaruchaefir's stewardship}{his task}.
\emph{He} should be the one carring \ps{\Miith} safety on his shoulders. 
Not she. 
Never her. 
It was wrong that she should suffer like this. 
(He didn't mind condemning many others to suffering, and was even willing to kill her, but \quo{that was different}. 
His motivations need not be entirely consistent.) 

But he never told this story to the world. 
They all thought he killed her and bound her soul against her will. 
For \Ishnaruchaefir, to admit the truth would be a declaration of failure for more than once reason:

\begin{enumerate}
  \item 
    He would be admitting he had failed in the task entrusted to him by \Nexagglachel, which he had previously been so obsessive about.
  \item 
    He would appear to have been too weak to bear the great sacrifice alone. 
    This would harm his \hr{Myths about Ishnaruchaefir}{mythical reputation} as an invincible superbeing. 
    He likes that reputation. 
    It makes people fear him. 
  \item 
    He would look like he was apologizing for his mistake and seeking forgiveness. 
\end{enumerate}

His pride allows him to do neither. 
Only \Criseis-tachi knew the truth. 
And he made them promise not to reveal the story to anyone. 
(By the time of the \thirdbanewar, the accepted story was so ingrained that if \Criseis-tachi had tried to spread the true story, no one would have believed them.)


Mourning what he had done, he resolved to honour her sacrifice. 
From that day he would keep the glaive safe and always carry it with him. 
He went on to use the glaive as his \hs{weaving artifact} as he and his fellows wove the \hr{Shrouding}{\SecondShrouding}. 

He remains to this day one of the pivotal \vertices{} keeping the Shroud in place.

But slaying his beloved was traumatic and became a turning point in his life. It distanced him further from Chaos, the \firstgendragons{} and his fellow \dragons.

\Ishnaruchaefir{} contemplates his betrayal. 

\lyricsbs{Vital Remains}{Scorned}{
  So be it. I am the enemy.\\
  So be it. I am the one you seek.\\
  So be it. I have no sympathy or empathy.\\
  It is done. My words and life bleed blasphemy.
}









\subsection{Now I am Become Death, the Destroyer of Worlds}
The \SecondShrouding{} was complete. 





\subsubsection{The cost of the Shrouding}
The \SecondShrouding{} was an incredibly costly and bloody affair. 
Millions of souls had to perish so that their vital cores and energies could be consumed and used to feed the nascent Shroud. 
This sacrifice would destroy entire Realms, bleed them dry and lifeless. 
It was a cosmic violation that left Mother \Miith{} wounded and bleeding and suffering for millennia to come. 

These souls still exist, bound in the Shroud. 
They retain a minimum of consciousness, enough to weep and suffer. 

Have scenes of madness and destruction like in \cite{HPLovecraft:TheCrawlingChaos}. 

The weaving artifacts each bind a very powerful soul, thus acting as \vertices{} in the \matrix{} that is the Shroud. \ps{\Ishnaruchaefir} glaive, for instance, holds the soul of \Triestessakhin. 

The ones weaving the Shroud needed to siphon and sap the emotions of the people they sacrificed. 

\lyricslimbonicart{Deathtrip to a Mirage Asylum}{
  Cut the string, the chain to soil.\\
  Unleash the powers within death's coil.\\
  No darker emotion is there to find\\
  than the fading feeling of a dying kind.
  
  Deathtrip to a mirage asylum.
}





\subsubsection{Why was it worse than last time?}
Why was it so much worse than the forging of the \hr{Crystal Sphere}{\CrystalSphere}, also a humongous cosmic upheaval? 
Probably because the \banes{} were closer this time and had more of their tendrils firmly secured on \Miithian{} soil. 
And they were advancing rapidly. 
And they had learned from their mistakes from last time and would not be so easily outwitted again. 

The \dragons{} had to act swiftly and desperately. 
Besides, they were not nearly as unified as they were last time (under \Kserasshana). 
This also weakened them. 
In the end, \QuessanthIshnaruchaefir{} acted virtually alone, against the world. 
So his Shrouding could not help but be a messy hackjob. 





\subsubsection{Entire Realms destroyed}
The price of the \SecondShrouding{} was extremely bloody. 
Entire sub-Realms of \Miith{} were laid waste, sucked dry of life in order to feed the Shroud. 
Actually, the \SecondShrouding{} itself might have caused \emph{more} destruction than the entire \secondbanewar{} had caused (up till that time, that is).

The world is violently torn apart and laid waste by the terrible destruction. 

\lyricsbible{Revelations 8:7}{
  And there followed hail and fire with blood, \\
  and they were cast upon the earth.\\
  And the third part of trees was burnt up, \\
  and all the green grass was burnt up.\\
  And the name of the star is called Wormwood.\\
  And the third part of the waters became wormwood.\\
  And many men died of the waters,\\
  because they were made bitter.
}

Especially the \resphan{} cities in \Nyx{} are hit hard by this. 
They lose the flow of \bane{} power from \Erebos{} on which they had previously relied. 
Now the entire Realm of \Nyx{} must sustain itself by leeching off of the other \Miithian{} Realms. 
The vast, splendid cities of \Nyx{} (only recently cleaned up from the bloodshed of the \Merkyran{} war) crumble and become a dead necropolis. 

\lyricsbs{Monolith Deathcult}{Concrete Sarcophagus}{
  In this gargantuan tumour,\\
  the choice had already been made.
  
  A thousand tons of steel and cement\\
  dispersed like a cancerous cough.
  
  Attending their fall-out funeral, this monstrous colossus.\\
  Radiating cancer for generations to come.\\
  20,000 tonnes of steel and cement\\
  cover the tumourous spider.\\
  Awaiting her next victims.\\
  The Concrete Sarcophagus.
}

\lyricsbible{Revelations 8:7}{
  And the name of the star is called Wormwood.\\
  And the third part of the waters became wormwood.\\
  And many men died of the waters,
  because they were made bitter\\
}





\subsubsection{It is temporary}
Someone (maybe \Ishnaruchaefir) remarks that a new age has begun.
An age of the Shroud. 
But he knows how destructive and constricting the Shroud is.
It will not last. 
It will push the world towards some climax, until finally all hell will break loose. 
The Shroud will one day be lifted again, and \Miith will be free\ldots{} or \Miith will be destroyed. 









\subsection{\Secherdamon curses his enemies}
After the \secondbanewar, \Secherdamon planned his revenge against the \resphain (and \Ishnaruchaefir, for that matter):

\citebandsong{Nile:FestivalsofAtonement}{Nile}{
  Black Hand of Set
}{
  Eaters of \human Flesh\\
  Hath eaten unlawful Flesh\\
  Upon our Brethren\\
  They have Feasted\\
  Seed of our Father\\
  We must now Avenge

  In secret conclave we Gather\\
  To rain Destruction \\
  on those Whom We have Cursed

  With vile Black Arts\\
  And Tempestuous Rage\\
  We vent our Wrath\\
  Red Blood stains my Hands and damns my Soul

  You will drink the Black Sperm of my Vengeance

  The Mighty Voices of my Vengeance\\
  Smash the Stillness of the Air\\
  And stand as Monoliths of Wrath\\
  Upon a plan of writhing Sepents

  I call upon the messengers of Doom\\
  To slash with Grim Delight this Victim I hath Chosen\\
  Feed upon his Brain Pulp, Rend his Throat\\
  Pierce his Lungs with the strings of Scorpions\\
  Oh Kali\\
  Oh Sekhmet\\
  Oh Dagon
}






















