\chapter{\MerkyrahBook}
This book takes place in \hr{Merkyrah}{\Merkyrah}. 













\section{\Resphain and \Ophidians}









\subsection{\Ophidians and \resphain meet}
\target{Ophidians meet Resphain}
The \ophidians \hr{Ophidians discover Nyx}{had discovered \Nyx} long before the \resphain were created.
But they had only explored a small part of \Nyx.
The place where the \resphain originated was far away from the regions colonized by \ophidians.
So at first they knew nothing of each other. 

After the \resphain arose, they quickly spread and began to build their civilization(s). 
After many centuries, \resphan explorers encountered \ophidians. 
Politics and dealings began between the two races. 
There were many small wars and skirmishes, and also peace and trade. 









\subsection{\Ophidian/\resphan coexistence}
The two races would coexist for thousands of years\dash fighting, trading, competing and cooperating. 
\Resphan colonies would be founded in the Realms of \Azmith. 
\Resphan allies and mercenaries would fight alongside \ophidians in \ophidian wars. 

The \ophidians were still somewhat xenophobic, so no great \resphan empires were allowed to flourish in \Azmith.
When a \resphan-dominated nation or other organization grew powerful enough to be a threat, the \ophidians would band together and destroy the \resphan upstarts lest they usurp the \ophidian homeworld. 
Eventually, many \resphain grew to resent the \ophidians for this oppression. 





\subsection{Guilds and armators}
\target{Armator}
\index{armator}
\index{guilds}
In the time before the \secondbanewar there were powerful guilds\dash essentially corporations. 
These ruled much of the world. 
They included weaponmakers, called \emph{armators}. 
















\section{The Truth (\yds{Delving})}
A few \resphain{} discover the truth of their origin.









\subsection[Prologue: Semiza]{Prologue: \Semiza}
The book opens with \Semiza, who is lying in the ground. 
Suffering, alone, decaying and unable to move. 
He sends out his mournful and patient call to the \resphain{} in their cities above him. 
His children. 
(After all, all \resphain{} descend from \Thanatzil, who is \ps{\Semiza}{} grandson.)

Compare to the titular \quo{call} in \authorbook{\HPLovecraft}{The Call of Cthulhu}. 









\subsection{Main conflicts}
There are a number of main conflicts in this book: 

\begin{enumerate}
  \item 
    The \hr{Umbra menace}{\umbra{} menace}, which was slowly killing the \resphain. 
    It was the greatest threat to their people, and governed much of their lives. 
    And \hr{Umbra menace growing}{it was growing}. 
  \item 
    The \Merkyran{} religion.
    For some it was happiness and peace and good. 
    But for others it was stagnation, oppression, asceticism, denial of all that was life. 
    Some said \emph{it} was slowly killing the \resphain.
    Some even said the religion was the reason why the \umbrae{} hunted them. 
  \item 
    Hunger. 
    The \hr{Merkyran hunters}{monsters that the \resphain{} hunt were becoming scarcer}. 
    This caused hunger and malnutrition. 
\end{enumerate}





\subsubsection{The Awakening}
\target{Awakening}
\index{Awakening}
The \resphan{} rebellion was also known as the Awakening.
The rebels believed they were Awakening from a dream, a daze, a stupour, and were now, for the first time, clear-sighted enough to understand their true nature. 










\subsection{Malcontents}
Many are discontent with life in \Merkyrah. 
They include \Kezrabal, \Gevural, \Zachirah{} and others. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Sola Fide
}{
  Where is the book of truth, or the inheritance that'd enlighten me?\\
  No voice shall answer to my probe and throbbing prayers\ldots{}\\
  But certainty and madness write in ashen letters
}










\subsection{The Delving}
\target{Delving}
\index{\Delving}
\target{Resphan rebels}
After thousands of years, a few \resphain, led by \Damiarch, went on an exploring expedition. 
The motivating factors for the mission included: 

\begin{itemize}
  \item 
    Simple hunting. 
    The \resphain{} \hr{Merkyran hunters}{hunter monsters, and hunters were highly respected}. 
  \item 
    The \hr{Merkyrans fear Umbrae}{\umbra{} menace}, which was \hr{Umbra menace growing}{growing}. 
    They hoped to learn more about what the \umbrae{} were and how they could combat them. 
\end{itemize}

For astrological reasons, the \umbra{} threat was especially bad this particular year. 
\Damiarch-tachi found some traces, full of \Erebos-aligned energies, that smelled kind of like the \umbrae{} (who are also \Erebean). 
They suspected a clue, so they followed these trails to their source.
This brought them deep underground. 
As it turns out, these trails were created by \Semiza, who lay down in the earth and tried to attact some \resphain{} to him. 

This voyage would later come to be known as \emph{the \Delving}

The brave explorers (the \quo{\Delvers}) included: 

\begin{itemize}
  \item \Damiarch.
  \item \Gevural.
  \item \Zachirah.
  \item \Ramiel.
  \item \Shiaraid.
  \item 6-8 more. Maybe \Sithiyacaan.
\end{itemize}

Among them are several who would later become the dreaded \satharioth, including \Gevural{} (\Azraid{}) and Ramiel. 

\Gevural{} is one of the senior members, but the leader is his brother, \Damiarch. Ramiel and the rest are younger and look up to \Damiarch{} and \Gevural{} as great leaders. 

While exploring some underground ruins they discover a mystic, evil garden of twisted, distorted plants. 
Compare to the cover art of \bandalbum{Dimmu Borgir}{Godless Savage Garden}. 

\Semiza's garden and tomb were located in the fallen and haunted tower of \Jazerubel in a region of darkness, monster-haunted and feared by all \resphain.
\Damiarch-tachi were very brave to venture there.
They believed they would have to brave this evil wasteland in order to solve the mystery of the \umbrae and enable their people to defend themselves from this menace.

\citebandsong{Nile:AnnihilationoftheWicked}{Nile}{
  Annihilation of the Wicked
}{
  The Dominion of Seker.\\
  Barren Desert of Eternal Night.\\
  Shunned by Ra.\\
  Behind the Gate Aha-Neteru.\\
  The Wastelands of Seker.\\
  Eldest Lord of Impenetrable Blackness.\\
  Death God of Memphis.\\
  He of the Darkness and Decay of the Tomb.\\
  He of Rosetau, the Mouth of the Passage to the Underworld.\\
  Closely Guarded by Terrible Serpents\\
  who Careth Not for His Own Cult of Worshippers.
}

There they find the tomb of \Semiza.

\citebandsong{Nile:AnnihilationoftheWicked}{Nile}{
  Annihilation of the Wicked
}{
  Seker, Ancient and Dead,\\
  Primeval Master of the World Below,\\
  Remaineth Unwitnessed, Unseen.\\
  Hidden in His Secret Chamber.\\
  His Primitive Graven Image like as a Hawk-headed Man.\\
  Shrouded and Swathed in Tomb Wrappings.\\
  Standing Between a Pair of Wings \\
  which Issue Forth from the Back of a Monstrous Serpent,\\
  Having Two Heads, Having Two Necks \\
  and Whose Tail Terminates in a \human Skull.
}





\subsubsection{Some look for meaning}
Some of the explorers, already in the early stages of the Delving, were disillusioned and looked for a new meaning to it all. 
They felt their religion was sad and pointless. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Called by the Fire}{
  The sky is clouded and grey like a mirror.\\
  Dreams of celestial bliss buried deep.\\
  An invisible web of whispers\\
  spread out over dead-end streets.\\
  Silently blessing the virtue of sleep.
}

Some were sure the religion was a lie, and that there was something more out there to be found. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Called by the Fire}{
  Every day I grow more immune to social sedatives.\\
  Every day the web is more transparent.\\
  United in fear and the comfort of reason.\\
  Illusions that we are all peers.\\
  Walking the stairs I am ever more awake.
}

There was a darker truth out there. 
They could feel it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Called by the Fire}{
  The black cloud is beneath me,\\
  and I laugh.
}

They hated what they saw as the religion's hypocrisy and pettiness. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Citizen}{
  Citizen! Whence came your voice, your right to speak?\\
  Is there a purpose to your tongue and gnawing teeth?\\
  I ask thee; how deep and hollow is your mouth?\\
  What lie is too decayed for you to stomach?
  
  With humility and obedience\\
  you pride yourself.\\
  Evasive and lukewarm\\
  until the end.
}

Some just wanted to rebel, because they were sick of it all.

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  The fruit that is forbidden\\
  Holds the greatest potential for providing infinite knowledge\\
  Spiritual Incest and the defilement \\
  of the temple of the Holy Spirit\\
  Ritualized and Immanent\ldots{}\\
  The pursuit of perversity, is it not but a mask\\
  On the search for meaning and knowledge?\\
  The purest of all Holocausts shall be perpetrated\\
  By a loving hand, never knowing if it provided felicity\\
  Or the vilest of everlasting torments\\
  No man can see Me and live!
}





\subsubsection{Ramiel and \Shiaraid}
Ramiel and \Shiaraid{} are the same age. 
They are close friends. 
They are major influences on each other's lives. 

Already at this time, Ramiel and \Shiaraid{} were secret lovers. 
\quo{Secret} from society at large, that is. 
Having sex out of sanctioned marriage was a taboo. 
But their fathers, who were both free thinkers (or, at least, pragmatists), knew about their affair and accepted it. 
\Zachirah{} even encouraged it.
\Nathrach{} remained mostly stoic. 

The two should have a \quo{secret} sex scene at the beginning of the book. 

At this point, they just had normal sex, no sadomasochism involved. 
It was not until after \Semiza{} that he \hr{Ramiel develops sadism}{developed his sadism} and she \hr{Shiaraid develops sadomasochism}{developed her sadomasochism}. 









\subsection[Semiza's garden]{\Semiza's garden}
\subsubsection{The garden}
They find this suck, twisted, evil garden. 

\lyricsdimmuborgir{The Promised Future Aeons}{
  The faces you saw in the withering garden.\\
  I witnessed the flickering, made to look like stone.\\
  Quivering like little figures lost in broken flames.\\
  Never to forget again the names carved in horrid flesh.
}





\subsubsection{They find \Semiza}
\target{Explorers meet Semiza}
Following the trail they stumbled upon in the garden, they somehow found the \hr{Semiza entombed}{tomb} of \hr{Semiza}{\Semiza}. 

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  Hall of Saurian Entombment
}{
  Through Subterranean Labyrinths of Catacombs\\
  We Hath Crawled To Gather in this Dimly Lit Hall Of Colossal Proportion\\
  Which Few Ever See\\
  Along Black Walls\\
  Rise Tier after Tier of Carven Painted Sacrophagi\\
  Each Standing in a Niche in the Stone\\
  The Mounted Tiers Rising Up To Be Lost in the Gloom Above\\
  Thousands of Carven Masks Stare Down Upon Us\\
  We Who are Rendered Futile and Insignificant\\
  By This Vast Array of the Dead
}



He beckoned them to him. 

\Semiza{} had been able to listen to the \resphain{} telepathically, so he understood their tongue well enough to make himself understood. 

\lyricsbs{Vital Remains}{Sanctity In Blasphemous Ruin}{
  Welcome to my dwellings of unholiness. \\
  Upheld, the blackest dreams, oh, infernal bliss. \\
  Your tabernacles pleasured and continuance \\
  lies in the innocents existence. 
  
  Down through the bowels of unholiness. \\
  Upheld, the blackest deeds, oh, infernal bliss. \\
  I am he who is malevolence, \\
  raping the weary so diminished. \\
  Come, mighty Babalon, \\
  mother of Abominations. \\
  Grant me the flesh, grant me the fear, \\
  grant me sanctity of ruin. 
}

They communicated with \Semiza. 
They felt his wisdom and \hr{Madness}{madness} like a palpable force. 

He showed them visions and revelations. 
He told them that everything they believed was a lie. 

\lyricsdimmuborgir{Grotesquery Conceiled Within Measureless Magic}{
  Poor misguided fool\ldots{}\\
  It is not God you are talking to.\\
  I am not impostrous, hiding behind perly walls.\\
  However, I am still yet to be found, known.\\
  I shall guide you on your midnight-ride as the sun fades black.\\
  And beyond your grotesque imagination,\\
  my name will be revealed\ldots{} \\
  The blood of Christ can't heal your wounds.\
  Give me all of yours, and I'll give you mine\ldots{}
}

Terrible images from his own time, of death, ruin and the fall of his kingdom. 
And memories of \Erebos{} and the \banes. 

\lyricslimbonicart{Seven Doors of Death}{
  Woe be unto him who ventures near.\\
  without knowledge.\\
  Ultra violent scenarios.\\
  Anguish crying.\\
  Images from the beyond.\\
  Nightmares never dying.
  
  Within the realm of desperation,\\
  seeking lexis of illumination.\\
  Psychological terror, permanent psychosis.\\
  A sculpture in the land of decay.\\
  Woe be unto him who opens\\
  the seven dreaded gateways.
  
  Asylum of neurotic minds.\\
  Devour all consciousness.\\
  Insanity is there to find.\\
  Dominion of darkness.
}

He tells them about their origins, how they were created by the dreadful \banes. 
He awakens their memories, repressed and buried deep down in their minds.

\lyricslimbonicart{Seven Doors of Death}{
  Walk and dream amongst the dead.\\
  Anger and pain resurrected.\\
  Necropolis manifestation.\\
  Supernatural obsession.\\
  Phantasmagorical state of mind.\\
  Trapped in another dimension of time.\\
  In a paradise lost.\\
  Endless horizon of wilderness and holocaust.
}

Now, the \resphain{} did have vague, mostly repressed memories of having once had connections to the \banes{} in their infant past. 
They did not know the \pps{\banes}{} identity, but they could recognize the feeling of them. 
(Do all \resphain{} have this memory through \hr{Resphan racial memory}{some kind of racial memory}, or is it only the oldest generations that remember it?) 
Some of them tried to deny \ps{\Semiza}{} tale, but others could not deny that it not only rang true, but also suddenly made a lot of pieces of the puzzle of their repressed memory and past come together.

Perhaps they get their hands on \ps{\Semiza}{} \hr{Book of Erebos}{\BookofErebos}. 

They learn that they are created by the \banes{} to carry on their culture and soul, the very legacy of \Erebos. 
And they learn of the dark greatness that is rightly theirs. 

\lyricsbs{Vital Remains}{Societe des Luciferiens}{
  In the midst of Our black paradise \\
  shall undefiled wisdom rule. \\
  The rites of Christ are but rites of Death, \\
  now receive the truth.
}





\subsubsection{\Semiza{} shows them tailored visions}
\target{Semiza shows tailored visions}
Perhaps \Semiza{} reads each of their minds and shows each of them a personally tailored vision that is meant to shape their life. 
Remember, \Semiza{} is a genius. 

\begin{enumerate}
  \item 
    Ramiel was shown \hr{Ramiel is nothing}{his own insignificance}. 
  \item 
    \Shiaraid{} was taught \hr{Shiaraid develops sadomasochism}{that she was really a sadomasochist}. 
\end{enumerate}



\lyricsbs{Hate Eternal}{Behold Judas}{
  I bestow upon you my contempt, Master of the Arcane.\\
  I bestow upon you apathy, Master of the Labyrinth.\\
  I bestow upon you malice, Master of the Kingdom.\\
  I bestow upon you savagery, Master of the Revered Palace.
}









\subsection{Their reaction to the truth}
Some of them are dismayed by this and feel reinforced in their principles of sin, shame and atonement. 
After all, this confirms that their myths are true: 
They were created by evil and have evil in their blood, and they must strictly discipline themselves to suppress and overcome this. 

But others feel liberated: 
They have no sin within them. 
The darkness, the \quo{evil} they feel is their true nature and purpose. 
It is not something wrong and bad, something to reject and suppress. 
Rather, it is their true selves and should be embraced. 
They feel an immense freedom. 
Suddenly they need no longer feel guilt and shame; they can embrace their inner selves, for this is what they were created to be. 

Some of them grow to hate \Merkyrah. 

\lyricsbs{Hate Eternal}{Beyond Redemption}{
  In vein of sacred scriptures\\
  provide the sight and visions.\\
  The lusting of hypocrisy\\
  forever scars the soul.\\
  Cursed is the life once given.\\
  Your prayers obsolite.\\
  The termination of the myths\\
  you've led yourself to believe.
}









\subsection{The first schism}
Already out there on the expedition, a schism forms between two factions: 
Those who wish to embrace their newfound dark past and those who wish to fight against it. 
They argue a lot while they're out there, and more on the way back. 

Some of the \quo{dark siders} decide that they will reach no consensus, and that the \quo{light siders} are a threat to them. 
Reasonably enough; the light siders would likely report them to the church and have all the dark siders tortured and killed. 

So the dark siders, or at least some of them, conspire and kill the light siders. 
They disguise it as an accident. 

There are also some neutrals, or some wimpy dark siders, who were too afraid to take part in the murder. 
These are now forced to side with the other dark siders and help keep the secret, or they too will be tortured and killed by the authorities for letting it happen. 
(Remember, the \resphan{} church is not reasonable. 
It will punish people harshly at the drop of a hat, and assume suspects to be guilty until proven innocent.)

Perhaps some \quo{light siders} die of the shock, or kill themselves. 
Perhaps some wimpy neutrals lose the will to live and waste away. 
Unable to handle the truth. 









\subsection{They try to repress it}
The explorers try to repress this new knowledge of theirs, but it keeps coming back to them and will not leave them alone. 
Day and night it haunts them, and they dream and ponder it. 

\lyricsdimmuborgir{The Promised Future Aeons}{
  Burn the pictures, so unexpected in this strange deserted place.\\
  Once opened its secrets would become the world.\\
  Its attributes would continue to unfold forever.
  
  Through the fabric of the promised future aeons.\\
  I offer this suffering of my unwanted father\ldots{}
  
  And the stars did wander,\\
  separated in the forbidden Universe. 
}

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Sola Fide
}{
  They burst my veins to pieces, these wan rats inside,\\
  with their jaws so contagious of a disease,\\
  as if it dropped like pus from the twelve wings of Sammael.\\
  The primeval light inside, gift of god and the holy spirit.\\
  It bleeds, so swollen by the bubo of this pest divine.\\
  The least traces of the consolation of Eden\\
  were consumed by this heinous blessing in ashes.
}

They try to carry on their lives as normal, but they can't. 
So they start their underground movement. 









\subsection{One comes to term with it}
One of the rebels battles with the revelations and tries to come to terms with it. 
It might be \Shiaraid, or \Sithiyacaan, or even \Damiarch. 
Let's assume for the nonce that it's \Shiaraid. 

She fears to give up \Merkyrah{} and the things she likes about it. 

\lyricsbs{Emperor}{With Strength I Burn}{
  Deep Green Dark Chaos.\\
  Blinded I run down these paths.\\
  By heart I know them.\\
  They lead to the soaring cliffs.\\
  Stout they stand above the water's edge,\\
  lifeless.
  
  And this is my foundation:\\
  Cold stone.\\
  Formed only by winds and time.\\
  How invulnerable,\\
  lifeless.
}

She wonders if \ps{\Semiza}{} revelations can really be true. 

\lyricsbs{Emperor}{With Strength I Burn}{
  For once I wish to see\\
  the entity behind the voice.\\
  The face of this seduction,\\
  the beauty of my pain.
  
  Am I blessed or am I cursed by thy presence?\\
  What is my crime, what is my deed?\\
  Is this life my redemption?\\
  Shall I repent or proceed?
}

She chooses side and pledges herself to the rebellion. 

\lyricsbs{Emperor}{With Strength I Burn}{
  I hate my flesh.\\
  Its dimension poisoned my soul with doubt.\\
  It made me question\\
  the essence of the \quo{I}.\\
  Slaves are those of this world\\
  given freedom to lay chains upon The Master.
  
  The wolf is no longer free.\\
  Release the chains and come for me.
}

She is fascinated by the opportunities this revolution offers. 

\lyricsbs{Emperor}{With Strength I Burn}{
  Grant me sight so I can see\\
  that which lies ahead of me.\\
  Cursed be my mortal eyes\\
  for dying in the realm of Death.
}

After the whole rebellion and conquest is concluded, she ponders whether it was worth the cost. 

\lyricsbs{Emperor}{With Strength I Burn}{
  I return to the soaring cliffs.\\
  They truly shine of strength.\\
  Even though I nothing learned.\\
  With strength I burn\ldots{}
}









\subsection{They feel their new power}
The dark ones discover a tremendous power when they embrace \nieur. A destructive and creative force. They cannot fully channel and control it yet, but they can feel the immensity of it. 

\lyricsbalsagoth{The Awakening of the Stars}{
  With but a gesture of my incorporeal hand 
  I illumine the heart of a new-born sun,
  revelling as its searing stellar radiance engulfs my ersatz form.
  Gazing out across the limitless, stygian cosmos,
  I hear the whispered voice of destiny echoing within the solar winds\ldots{}
  
  No small task, to awaken a universe from slumber.}

This feeling is further magnified \hr{Origin of Satharioth}{when they become \satharioth}. 

\lyricslimbonicart{A Cosmic Funeral of Memories}{
  The night belongs to the predator\\
  to the one who dares crossing the threshold,\\
  the axis of dreams and wonders and black miracles.\\
  I see my self in the mirror of your eyes:\\
  A dark star on the celestial beautiful midnight sky.\\
  Release the inner radiance of what you have become.\\
  Brighten the night with your sacrifice.
  
  I have returned to life to speak of clairvoyance.\\
  I am the voice from the grave land of memories.\\
  Life can be only an illusion, and death a temptation,\\
  a final destiny.
}

\lyricsbs{Arcane Wisdom}{Of Skyfire Burning Deep}{
  In dark waters shall we bathe \\
  yet again, as we`d done aeons ago. \\
  Wretched souls left grimly wandering \\
  like specters of a long-dead kingdom. \\
  And so great and mighty, the dismal sky \\
  whither we shall return to \\
  when the day arrives.
}

\lyricsbs{Aeternus}{Burning the Shroud}{
  Within you it lies since the rise of your time.\\
  You've feared it, ignored, but truth never lies.\\
  Its existence marked at the birth of time.\\
  The darkness inside.\\
  The shadows that dance in your soul.
  
  To deny is to fear.\\
  Embrace the darkness.\\
  Reveal in its power.\\
  Within it lies the harmonious truth.\\
  A voyage into the cave of shadows\\
  yields the jewels of knowledge and wisdom.
  
  Does not the night\\
  and the silver moon\\
  enchant your being?
  
  The caressing whisper of the night.\\
  No harm will come to those who are true of heart.\\
  Look to the sun and the brightness shall blind you.\\
  Stare into the black embrace,\\
  the sight deepened with wisdom.
  
  Free your consciousness.\\
  Accept the reality of darkness.\\
  It has never been a place of dread.\\
  Knowledge and wisdom\\
  is given to those who seek.
  Achieve the empowerment\\
  of endless mysterious nights.
}









\subsection[Ramiel, Shiaraid and Eryal]{Ramiel, \Shiaraid and \Eryal}
From \Semiza, Ramiel had learned sadism and \Shiaraid{} had learned masochism. 
They quickly implemented this in practice in their sex life. 
They loved it. 
They found great pleasure in this \quo{sinful} behaviour. 

But \Shiaraid{} found out that she was not entirely content. 
She had both dominant and submissive lusts. 
She wanted to take turns being the dominant part. 
Ramiel would have none of that. 
Already he had developed an irrational fear of being \quo{nothing}. 
Being sexually submissive would confirm that fear. 
He would not let that happen. 
He would prove to himself that he was not nothing, that he was superior and not inferior. 
So he refused to submit to anyone, even the \resvil{} he loved. 

\Shiaraid{} was nonplussed. 
She tried to persuade or tempt him, but it became clear he would not budge. 
She was unhappy for a while, but then she realized that their new rebellious philosophy had no rules about monogamy. 
If she wanted a kind of sex that her lover was not providing, she was free to go elsewhere and get it. 

So \Shiaraid{} went out looking for a lover. 
She found \Eryal. 
They had known each other a little bit before and had been attracted to each other, but lesbianism was forbidden in \Merkyrah, so they had repressed their feelings. 
Now \Shiaraid{} sought out \Eryal{}.
She could tell that \Eryal{} had submissive tendencies. 
Her new realization of her own hidden lusts had also given her clearer sight when it came to reading other \resphain{} and \emph{their} repressed feelings and desires. 

\Eryal{} knew nothing of the rebellion and was a demure and faithful \Merkyran. 
But she was attracted to \Shiaraid, and \Shiaraid, having already partially embraced her dark nature, suddenly shone with a new aura of glory, beauty, promise and forbidden allure. 
\Shiaraid{} did her best to seduce \Eryal, and the young, inexperienced \Eryal{} could not resist her. 
They had sex. 
And their sex quickly become dark and naughty. 
\Eryal{} loved being dominated and gave in one hundred percent. 
Soon she was virtually \ps{\Shiaraid} slave, in the bedroom and out of it. 
She lived to serve and obey her mistress, and she loved her. 





\subsubsection{Ramiel's hypocrisy}
Ramiel picked up on the fact that \Shiaraid{} had an affair with \Eryal. 
He was not happy that \Shiaraid{} was having sex with other people.
Worse, he sensed that she had a \emph{better} relationship with \Eryal{} than with him. 
\Eryal{} submitted to \Shiaraid{} more whole-heartedly and sincerely than \Shiaraid{} ever submitted to Ramiel. 
He became jealous. 

So he called \Shiaraid{} out on it. 
She explained her reasoning as if it were the most natural thing in the world: 
They had rejected the \Merkyran{} religion and were free to have sex with whomever they chose. 
\ta{Is it not wonderful, Ramiel? I love it, this new freedom.}

Ramiel could not argue with that, but it did not sit well with him. 
He knew he was being a hypocrite, but he was not happy about having to share his \resvil{} with others. 
Like all \resphain, he had \hr{Resphain are possessive}{a genetic urge to own his \resvil}. 
He had grown up with the strict monogamous tradition of \Merkyrah. 
From childhood he had learned that it was his goal in life (like every other \resphan) to strive to possess a \resvil{} and make her his own. 

\Shiaraid{} had abandoned monogamy, so Ramiel did likewise. 
He went out and had sex with other \resviel. 
By the time this happened, he was a popular rebel leader and could attract a fair number of groupies. 
So he fucked them. 
And he was rough with them. 
Some of them he hurt really badly. 
He was a sexual sadist now, remember? 

But it did not make him happy. 
He still had sex with \Shiaraid, but he knew he had to share her with others, and that made him bitter. 
He wanted to own \Shiaraid. 
He began to hate \Eryal. 

\Shiaraid{} noticed that Ramiel was not hitting it off with \Eryal. 
She encouraged the two to have sex, hoping that it would bring them closer together. 
\Eryal, eager to please her mistress' every whim, went to Ramiel and offered herself to him. 
She submitted to him and let him dominate her to his heart's desire. 
He did. 
\emph{Brutally}.

\Eryal{} halfway regretted having agreed to do it. 
When \Shiaraid{} tortured her, it was always with an undertone of love. 
Not so with Ramiel. 
He \emph{genuinely} wanted her to suffer. 
And suffer she did. 
\Eryal{} begged and whimpered and cried and wept. 

And it did not help much.
Their relationship did not really improve. 





\subsubsection{\Eryal{} joins the rebellion}
\Eryal{} joined the rebellion. 
She was urged to do so by \Shiaraid. 

\Eryal{} was good and faithful and did not like the evil she saw in the rebels. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  As night turns into morning\\
  All the shadows disappear\\
  Although mine is still here
  
  As morning turns into night\\
  All the shadows reappear\\
  Although mine is not here?
}

But she knew she dearly loved \Shiaraid, and she dearly loved the sex she had. 
\Merkyrah{} would forbid their relationship. 
And if she refused to join, she and \Shiaraid{} would be torn apart on either sides of the war. 
She could not live with being parted from her mistress. 

Besides, (\Shiaraid{} argued,) there were several great and wise people on the rebels' side. 
Surely they could not be all wrong\ldots{}

So, despite her misgivings, \Eryal{} gave herself to the rebellion. 

Be sure to depict how happy \Eryal{} was when \Shiaraid{} approved of her decision to join the rebels. 
She beamed under her beloved mistress' affection and compliments. 

\Eryal{} was introduced to \Semiza. 
She was scared of him. 

She joined, but she still feared it was madness. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  Raging madness, smiling sadness.\\
  Walk out and meet the Path of Darkness \\
  with your unwary naked feet.\\
  Beg for mercy.
}










\subsection[They lose Semiza]{They lose \Semiza}
\target{Rebels lose Semiza}
In the beginning, \Semiza fulfilled the role of an oracle. 
He told \Damiarch-tachi things about the vast, dark universe and their own origins and their place in it.

Later, the rebels somehow lost contact with \Semiza. 
Perhaps the \Merkyrans{} discover a sense of evil emanating from his twisted garden, and so they bomb the place and seal it up. 
Comparable to how the authorities bombard Innsmouth and Devil's Reef in \authorbook{\HPLovecraft}{The Shadow Over Innsmouth} and the game \emph{Call of Cthulhu: Dark Corners of the Earth}. 

So from here on they are on their own and without his guidance. 
They must discover their true selves by experimentation. 
They slowly begin to split into various ideological factions (later becoming the dynasties that would later \hr{Dynasties drift apart}{drift apart}). 
Some believe that only through utter depravity will they discover/realize their true nature and destiny. 
Others believe that they must master their inner darkness/evil and bring it under control via some kind of morality (these become \CiriathSepher). 















\section{Darkness Festers}
\subsection{Underground cult}
The enlightened ones know that they cannot simply cry their newfound knowledge from the rooftops. They would be killed. But they can gather supporters from among the \hr{Early fallen Resphain}{fallen ones}. 

So they form an underground cult, a rebel organization, and begin gathering strength, politically and mystically, by doing research and learning to control their true power, unfiltered by the false Light. 

Some of the fallen ones are overjoyed. Suddenly they discover that they are not just weaklings after all; they were simply living out their true nature all along. They need no longer feel shame and self-hatred. And what's even better, they can use their darkness to overthrow the government, get revenge on the church that has hated and oppressed them for so long, and gain power, glory and eternal, sinful pleasure. Suddenly their bleak, failed existence has a purpose. 

The enlightened ones were mighty and capable \resphain{} already before they went on their expedition, and they are even mightier now that they have learned to channel their true power (to some limited extent). The fallen ones are wimps, so they embrace the enlightened ones as their saviours and bow down to worship at their feet. Ramiel suddenly finds himself with several \resviel{} (hot goth chicks) begging to be his sex slaves, pleading for the opportunity to give him pleasure\dash and then doing their utmost to please him. This is an awesome feeling for Ramiel, because \resphain{} lust very much after the \resviel, who are fewer in number and sexually picky. (They lust after \human{} women, too, but much more so after \resviel. The \resviel{} are far more attractive because they possess better genes and will produce \resphan{} offspring.)

\lyricsdimmuborgir{The Blazing Monoliths of Defiance}{
  Godless temples beckon,\\
  through gleaming scapes of horrid nightmare.\\
  Gathered between symbols and signs.\\
  A glow of new light is born out of the night.
}

They grow to hate \Merkyrah{} and feel are disgusted by its supposed marvels. 
Some succumb to nihilism and begin to hate everything. 

\lyricsbs{Arcane Wisdom}{Misanthropic Horror Magnified}{
  Senseless oblivious towers,\\
  monuments to absurdity.\\
  Oceans of ignorance.\\
  Humanity at its cruel best! 
  
  When all noble values are (shamelessly) inverted, \\
  and brainwashed minds endure.\\
  When animal essence is forgotten. \\
  Misanthropic horror\ldots{} magnified.
  
  Decadence is all I see. \\
  Triviality lies before me. \\
  Nihilism\dash the only solution. \\
  Misanthropy\dash the final escapism. 
  
  Your world sinks to vomiting proportions. \\
  Visions of decay spring everywhere. \\
  Entire lost civilizations \\
  succumb to a \quo{worldly} oddity. 
  
  Woe and torment be behind me\ldots{} \\
  the maze of such reality. 
}





\subsubsection{Leaders}
The rebel leaders took titles for themselves. 
\begin{enumerate}
  \item \Netzachirah became their \hr{Resphan Warlord}{Warlord}.
  \item \Kezrabal became their \hs{First Orator}.
  \item \Damiarch became their \hs{Thearch}. 
\end{enumerate}






\subsubsection{A counter-cult existed}
Before the Delving there already existed one or more subcultures in \Merkyrah that rebelled against the system and the religion. 
They idolized everything that was opposite to the prevailing system. 

Compare to how some Satanists use the inverted cross as their symbol. 

\citeauthorbook[p.111]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  The malevolent octopoid shape, eldritch green and seething\ldots{} suggests a tower of devils ululating, thirsting, slaying and yammering.
  Dread Cthulhu who begins to Awaken, I leave you refreshed.
  The color of your embryonic shadow grants me foul nourishment.
  Sacrificial blood is the water of life. 
  A million tributes to Satan, Nyarlathotep, Shub-Niggurath, Hastur, Tsathoggua, Tsalal, and Satanis.}
  
The rebels easily assimilated these counter-cultists. 

It is worth mentioning that the \resphan rebels, for all their rebellion, still preached submission and obedience to the gods, unlike \Sethicus, who preached dominance and freedom and personal will and personal power. 

\citeauthorbook[p.113--114]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  I AM here, horned, slimy, gruesome and unholy Masters.
  The demons of the ancient chasm share my soul\dash viscous green and dripping from Cthulhu's tentacled mind.
  So incomprehensible is our Drowned Lord, so unclean His presence, so dark and contemplative is his manner. 
  
  One thousand gateways opening into the Great Singular Void. 
  
  As I see this universal model, I shall know its weakness and limitations.
  I AM stronger than this world.
  By the foul, corpulent stench of the Elder Things I travel through the astral dimensions.
  Passing by alien caverns, purple skies, and sunken cities I journey to the end of time\ldots{} before the universe was born.
  Where the Old Ones rule.
  Their crimson thrones like a gluttonous abbatoir.
  I kneel before the Fathers as They offer obsidian gestures. 
  
  \ldots 
  
  Give me aid, Powers of Darkness!
  I beseech you; grant me strength to annihilate this false paradigm.
  We are not the masters\ldots{} killing and reveling.
  In your loathsome name, I spread the wisdom as tentacles erupt from the forbidden subterranean doorways. 
}





\subsubsection{An army of misfits}
The rebels end up with a terrible army of misfits, madmen, malcontents, criminals, heretics and outcasts. 
The good leaders are not entirely happy about this. 
But the evil ones (\Zachirah, \Gevural) enjoy it and do their best to fully utilize and channel the evil potential. 

\lyricsbs{Monolith Deathcult}{Master of the Bryansk Forest}{
  Waffen-Sturm-Brigade RONA, \\
  filled up with criminal prison inmates, \\
  political prisoners, traitors and faggots \\
  to defend the newborn Republic of Lokot. \\
  Dissidents, criminals, thieves and violators, \\
  a murderous phenomenon behind enemy lines. \\
  Anti-Soviet, pro-German death squads \\
  ambushed in the woods of Bryansk.
  
  Partisan liers-in-wait, \\
  dressed in bloodstained White Army uniforms. \\
  Anti-Soviet, pro-German Werewolves \\
  assembled before the gates of Warsaw. \\
  Warsaw's Jews, Gypsies and retards, \\
  prepare yourself for death and horror. \\
  The Kaminski Brigade enters the perimeter \\
  and waits for the command to lay your city in ruins.
}

They wage a secret guerilla war. 

\lyricsbs{Hate Eternal}{The Obscure Terror}{
  We are your enemies, sworn to secrecy.\\
  Mentors of all that is profane.\\
  We are betrayers, devoid of your worth.\\
  We thrive in all that is stained.\\
  We poison all that is pure.\\
  We endanger all that be.
  
  Why hinder thou from escaping obscurity,\\
  thus dominating your race?\\
  You will not stop us, you can not stop us,\\
  for we shall never falter.\\
  We are extraordinary in our design.\\
  We flourish in your pain.\\
  In your blindness, your very blindness,\\
  we attack with ferocity.
  
  Strength through adversity.\\
  Death with nobility.\\
  Instruments of insurgency.\\
  We are the obscure terror.
}

\Kezrabal-tachi emphasize that angry misfits have an important part to play in the world, especially in the conflict that is to come. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Odium Nostrum
}{
  Odium\\
  Oh Merciless Hatred;\\
  Spare nothing, spare no one\\
  Oppressive heat, intense flavour\\
  From the pupil of the one-eyed mongrel \\
  to the distant depths of the macrocosm\\
  We are all waiting for the releasing hour
}





\subsubsection{Awakening their inner darkness}
The rebels perform occult rituals in an attempt to contact and awaken the true darkness within them. 

\lyricsbs{Vital Remains}{Scrolls of a Millenium Past}{
  Arose from the second triangle burning my soul. \\
  Gehenna is the place for burning, takes me away. \\
  Order of the golden dawn summoning Beelzebub. \\
  Give your eternal loyalty, demon of death and evil.
  
  I am (the) personification of cosmic force \\
  and (the) creator of all living things. \\
  Even the gods bow at my feet \\
  to lick the blood from my sword.
  
  Book of Revelations. I forsee the fallen angels \\
  rise to destroy the ministers of God. \\
  Strong as a lion in the Moon of the woods. \\
  (Great) beast come, gods fucking withdraw.
}

They discover great, mystic, Chaotic pleasure. 

\lyricsbs{Vital Remains}{Into Cold Darkness}{
  Sensual pleasures of non-resistant triumph.\\
  Spiritual tendencies deeply rooted in man's psyche.\\
  Ab-I-Hayat, waters of immortality,\\
  a sanctuary to mortuate your mind.
}





\subsubsection{Motivation}
The rebels were not merely evil.
They fought for what they believed to be the truth against corruption and lies and decay. 
They believed they could end the \hr{Umbra menace}{\umbra menace} and the \hr{Resphan tribes}{bloody war between the tribes} once and for all.

The rebels \hr{Rebels learn soul-eating from Umbrae}{discovered how to eat \resphan souls}. 
They realized this was a dark and terrible thing to do, but they did it anyway.
They did not know by then how addictive it was.
They would later learn that once a \resphan had eaten \resphan souls, there was no going back.









\subsection[Sithiyacan and his idealism]{\Sithiyacaan{} and his idealism}
\Sithiyacaan{} was one of the original \hr{Resphan rebels}{\resphan{} rebels}. He was idealistic, driven by a sincere dream to bring freedom and enlightenment to the \resphan{} people. He disliked the totalitarian and repressive \Merkyran{} church and wanted to give the people a better, happier alternative. He had scruples, but was seduced by the darkness and the leaders of the rebels (such as \hr{Gepheral}{\Gevural} and his brother). 

He believes that the \Merkyran{} religion will lead to a slow death of stagnation. 
He believes that one must first destroy in order to pave the way for new creation. 
He believes that breaking the rules is the way to creation, insight, happiness and a way out of slavery, stagnation, stupidity and prejudice.

He becomes a Zarathustra-like preacher. Compare to \authorbook{Friedrich Nietzsche}{Also Sprach Zarathustra}. 

Most people, \resphan{} and mortal alike, do not understand the rebels. They mock them and laugh at them. The rebels become more bitter, and even the more idealistic ones, like \Sithiyacaan, begin to accept that more extreme methods are needed. 









\subsection{The Glory of Darkness}
The \Merkyrans{} denied their \hr{Resphan vampirism}{vampiric nature}. This made them weak, declining as the years and generations passed. So at this point, thousands of years after the initial creation of the \resphain, they were mere shadows of themselves.

The rebels realized that they were the \quo{children of \nieur}, which in turn was born of Chaos and Darkness. 

As the rebels learn more of their true power, they start draining life again. First they drink a bit of blood. Some of them drink each other's blood during sex. This is hot and gives them pleasure, but it doesn't help, since they're just draining each other. Then they start draining the blood of others, and eating \human{} flesh. They get a taste for it, and their perverse tastes escalate into orgies. Eventually, they dare abduct and kill \resphain{}, drink their blood and eat their flesh. 
Even later, they \hr{Rebels learn soul-eating from Umbrae}{learn to drain all a person's lifeforce and suck out and devour his soul}. 

The more they do this\dash and other dark things\dash the more they revert to their true nature. And it shows. The darkness inside them seems to glow even stronger than light. They are respendent in their dark majesty and glory, and they awaken even more of their natural ability to command \humans{} (and, to a lesser extent, other creatures such as \nephilim). 

Their cult grows dramatically. Especially \humans{} flock to them, for even though the rebels are clearly evil, their charm and authority is so great that the feeble \humans{} (who are, after all, created with the chief purpose of being slaves of the \resphain, not question their morality) can't help but admire and worship them. They are the first \emph{true} \resphain{} that these \humans{} have met, and they are overwhelmed by the sheer awesomeness. 

The \hs{Voices of God} contacted the dark ones in visions and tried to stop them. 

\lyricsbalsagoth{The Empyreal Lexicon}{
  Such carnage wrought with your malevolent tongue, dark one\ldots{}\\
  What unfathomable horrors dwell within the lightless corners of your cursed soul?\\
  Heed not the voice of the Lexicon\ldots{} lest its whispers drive you mad!}

The \resphain learned that they were created by dark, formless, hideous gods in order to help them break free and eventually inherit their legacy.
This was a horrible realization.
New cultists who were admitted into the inner circle and told the inner mysteries often went through three stages of insight. 

\citeauthorbook[p.92--93]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  \ldots I have discovered three separate stages of AWakening. 
  Without knowing about these states, an initiate might very easily lose his way. 
  
  I have talked with Cultists who practiced self-remembering only to find themselves stripped bare, devoid of feeling or emotion.
  A vast emptiness consumed them, and they were left with sensations of cold, terrifying clarity.
  While disorienting, Cultists should not be alarmed after experiencing this first stage of Awakening 
  
  After this initial feeling of nothingness, comes a calm joyfulness.
  Entering this second state allows a Cultist to build energy, discipline, and understanding. 
  The second state comes after the Cultist has become familiar with the unconfortable and distressing first state of Awakening. 
  
  The third state of Awakening is the payoff, the most exciting part.
  This state of being utilizes directed, conscious force.
  The Cultist creates goals and then uses his Awakened consciousness to achieve them. 
  
  To recap: the first is nothingness, second is understanding, and the third is creating.
  
  These are the three states of Awakening.
  If you've only encountered the first state, then it's no wonder that it feels strange and possibly even horrible.
  Keep trying to consciously exist in the present moment and eventually you will reach the second stage.
  Finally, after months of training, the most rewarding state will unfold.
  Reality will obey you rather than the other way around.
}

They preach that the true religion shall come to rule. 

\citeauthorbook[p.100--101]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  One night, an unearthly squid will erupt from an emerald green trapezoid, and this shall be the symbol of Cthulhu's Cult. 
  Three tentacles will comprise the governing bodies: magic, religion, and philosophy.
  Thus a new age of darkness is born; an old age of darkness returns.
  Exalted are the beasts who understand what can never be seen!
  
  \ldots
  
  Black magic is the new law; ritual chambers shall become our courtroom.
  With such undreamt of power, the Cult of Cthulhu shall uphold the Will of the Ancient Ones because Their Will is congruent with mankind's evolution!
  And when They emerge from their shimmering, luminous rifts in time and space, our organization will be there to usher in the change. 
}





\subsubsection{\Kezrabal, the propaganda minister}
\target{Kezrabal becomes propaganda minister}
\index{propaganda minister}
One of the rebels, \Kezrabal, was the \quo{propaganda minister}. 
He wa the most talented demagogue of them and pulled lots of people in. 
He told them whatever they want to hear, whatever they \emph{needed} to hear, and was perfectly willing to tell outright lies if it was convenient. 

He preached of the glory of the rebellion. 

\lyricsbs{Exmortem}{The Revolutionary Soul}{
  We have made a weapon of hatred\\
  to slay the stagnant powers,\\
  to reach the land of utopia\\
  where creative chaos reigns.
  
  Now blasphemic bells\\
  are ringing in your head.\\
  Wicked demons on the ringside.\\
  The challenger has cut his chains.
  
  So cast yourself into the flames.\\
  Lick the powers of the burning planet.\\
  It is the reawakening\\
  of the revolutionary soul.
}

He preaches against \Merkyrah. 

\lyricsbs{Vital Remains}{Devoured Elysium}{
  Worship your God and pray unto him. \\
  For his love is masked by the stench of decay. \\
  Your death is what he needs, the blood of the righteous. \\
  We will celebrate, as you will go \\
  one by one, one by one, one by one\ldots{} \\
  to meet your bastard maker.
}





\subsubsection{New people are lured in}
The rebellion lures in new people, folks who are disgruntled with the church. 

The more evil sub-fractions preach hate and revenge, whereas the more idealistic fractions preach truth and freedom. 
\Gevural{} was pretty brutal at first, but got much more refined when he became \Azraid. 

\lyricsdimmuborgir{Broderskapets Ring}{
  Kom, unge bror. \\
  Skjenk oss din rene ungdom.\\
  Legg ditt liv i v\aa{}re hender.\\
  Kjemp v\aa{}r krig med oss.
  
  La vare sorger form\o{}rke ditt sinn.\\
  La din sjel slites.\\
  F\o{}l natten som legger seg rundt deg.\\
  Glem all kj\ae{}rlighet.\\
  
  Ingen t\aa{}rer skal fylle dine netter.\\
  Tre inn i broderskapets ring.\\
  Ingen svakhet skal du finne i din sjel.\\
  Styrken skal vandre ved din side.\\
}

\lyricsdimmuborgir{N\aa{}r Sjelen Hentes Til Helvete}{
  F\o{}lg, f\o{}lg etter.\\
  Til Ondskapens hall vi drar.\\
  Der det vendte kors pryder ferden\\
  av M\o{}rkets Allmektighet.
  
  P\aa{} kristi flesk vi spytter.\\
  La det r\aa{}tne!\\
  Et symbol p\aa{} godhettens bortgang.\\
  Et skuespill der endes.
  
  Bring frem v\aa{}rt indre sinne.\\
  Vis veien for v\aa{}rt hat.\\
  Skjend guds sjeler til evig pine.\\
  I Ondskapens paradis er de dine.
}

\lyricsdimmuborgir{The Serpentine Offering}{
  Reconcile not with the fear of the snake,\\
  but embrace it as your own.\\
  Inject its venom into your veins,\\
  and replant the seed that gives growth.\\
  Still shrouded in mystery\\
  until you arise above perception.\\
  A veil of ignorance is in motion,\\
  continuing throughout generations.
}

\lyricsdimmuborgir{The Sacrilegious Scorn}{
  My word and world holds ground and is real.\\
  Your word is like floods of poisoned water,\\
  a language spoken with spit of different tongues.\\
  You can never corrupt me again.
  
  Time has come to step up\\
  and take back what you took from me.\\
  You can never corrupt me again.
}

They embrace the darkness, come what may, no matter the cost. 

\citebandsong{Ihsahn:angL}{Ihsahn}{Malediction}{
  And so you earn my contempt.\\
  My enmity. Malediction. \\
  Though my path be that of thorns,\\
  the way of my affliction\\
  is the way to myself.
  
  The devil will not let me go, \\
  though I do not mind.\\
  Through fiery lakes to where cold rivers flow,\\
  I honour the contract I signed.
}






\subsubsection{Initiation ritual}
New members worship and adore the cult. 

\lyricsdimmuborgir{Master of Disharmony}{
  Master of disharmony, welcome my tainted soul.\\
  Take me from the hordes of the living\\
  into the blessed darkness
  
  Master of disorder, take my impure flesh.\\
  Lead me unto the path of temptation.\\
  Save me from cowardness.
}

New members are initiated in a ritual where they die, get in contact with the \Erebean{} force of Entropy and are symbolically reborn as new, purer, better \resphain. 

\lyricsdimmuborgir{Master of Disharmony}{
  Master of death, take my pitiful life.\\
  I am enslaved.\\
  I shall never forget the pain.
  
  Master of sin, take my cursed heart.\\
  Bring me where I can find salvation.\\
  For I am the damned.\\
}

They swear undying loyalty to the cult. 

\lyricsdimmuborgir{Allehelgens D\o{}d i Helveds Rike}{
  \ae{}tlinger som sverger eden,\\
  med troskapsl\o{}fte om \aa{} ugj\o{}re freden\\
  \aa{} styrte himmelslavers velv\ae{}re\\
  og triumfere i kulde til Dyrets \ae{}re.
  
  Vredens beger renner over I forherdelse, \\
  fra oppr\o{}rdjevlers svovelvind, gl\o{}dende, \\
  fra regionen av Belial's barn,\\
  avlet hinsides harmens trossende tind. \\
  De siste tegn fra Kristi tapende engler\\
  brenner ub\o{}nnh\o{}rlig i ravnens ild.
}

\lyricsbs{Vital Remains}{At War With God}{
  Draped by the flames has now become your flesh. \\
  The purity of pain. Your yearning for pleasure.  \\
  Shedding the skin of lies. \\
  Rejoice in our impure desires. 
}

\lyricsbs{Vital Remains}{Societe des Luciferiens}{
  Beauty in purity, the darkness glows upon the flesh. \\
  Through this, the Black Flame of Satan, thou walketh in Hell. \\
  Thy senses are awakened to the joy of rebirth. \\
  The Gates are flung wide, and thy passage is heralded \\
  by the deathless cries of His guardian beasts. \\
  His searing brand shall be evermore \\
  emblazoned on thy consciousness.
  
  Its fiery meaning shall make thee free.
}





\subsubsection{Outcasts embrace the rebellion}
Especially outcasts\dash such as the \ashenblooded\dash embrace the rebellion. 
After they win, the \ashenblooded{} are still rewarded with nothing but scorn, however. 

\lyricsbs{Dreamsfear}{Ruins}{
  Up from these ruins we'll rise\\
  to conquer this world once again.\\
  Out of the dark underground,\\
  we'll break free from these chains we are in.
  
  You never thought we'd be back from the dead. \\
  Can you feel our breath on the back of your neck?\\
  You'll know it's true when we kick in your door.\\
  You'll know it's real when your head hits the floor.
  
  No mercy this night. \\
  We're out to destroy.\\
  From the ruins we rise.
}

They blame the church for all evils of the world. 

\lyricsbs{Dreamsfear}{Ruins}{
  Not forgiven and you'll never be forgotten.\\
  Can't forgive and then we won't forget.\\
  Can't believe we couldn't see it in your eyes.\\
  Can't believe we couldn't see through your lies.
  
  Here on this night we gather to fight.\\
  For vengeance we fight.\\
  Waited so long now our time is in sight.\\
  Revenge is in sight.
  
  You're hanging on in the eye of the storm.\\
  Only a matter of time till you fall.
}

\target{Bezedeth rebel against Merkyrah}
In \Merkyrah, \bezedeth had \hr{Bezed status in Merkyrah}{low status and bad reputation}. 
According to their religion, they were forbidden the afterlife, being \hr{Ashenblood lesser immortality}{Lesser Immortals}. 
This made them very bitter, so when the rebels came and preached to them the \bezedeth were all too eager to rebel against \Merkyrah.

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  The Blessed Dead
}{
  Looked Down Upong With Scorn\\
  We Work the Fields of the Masters\\
  And Share Not the Bounty of the Black Earth

  Destitute Servile Cast Out\\
  Affording No Tomb\\
  We Shall Be Buried\\
  Unprepared in the Sand

  We Shall Never Be The Blessed Dead

  Scorned By Asar\\
  Condemned at the Weighing of the Heart\\
  We are Exiled from the Netherworld\\
  Serpents fall Upon us Dragging us Away\\
  Ammitt Who Teareth the Wicked to Pieces

  Pale Shades of the UnBlessed Dead\\
  None Shall Enter Without the Knowledge\\
  Of the Magickal Formulas\\
  Which is Given to Few to Possess

  Not for Us to Sekhet Aaru\\
  Our Souls Will be Cut to Pieces with Sharp Knives\\
  Tortured Devoured\\
  Consumed in Everlasting Flames

  We Shall Never Be The Blessed Dead
}





\subsubsection{They prove that their religion is stronger}
Have some biblical scenes where the rebels prove that their religion and their magic is stronger than that of \Merkyrah. 
Compare to the scene in Exodus (Old Testament) where the Egyptian sorcerers turn their staves into snakes. 









\subsection{Learning how to command \umbrae}
\target{Resphain learn to command Umbrae}
The \Merkyrans{} had always lived \hr{Merkyrans fear Umbrae}{in fear of the dangerous \umbrae}. 
\Semiza{} taught the rebels how to ward off the \umbrae, or even command them. 
This became one of their greatest weapons in the war, physically as well as psychologically. 
Many took this conquest of their ancestral foes as meaning one of two things: 

\begin{enumerate}
  \item 
    The rebels had the right idea. 
    They knew how to combat the decline and depredations they had been suffering from. 
    Theirs was the way to power, glory and advancement for the \resphan{} people. 
  \item 
    The rebels were evil itself. 
\end{enumerate}

\target{Rebels awestruck by tame Umbrae}
The lower-ranking rebels were awestruck when they for the first time saw their masters come riding on on subdued \umbrae. 
(\Achsah{} was one of them, as \hr{Achsah fetches Umbrae}{she would later recall}.)









\subsection{Learning how to kill a \resphan}
Previously, no one knew how to kill a \resphan, so they would never die. 
The very oldest \resphain{} ever were still alive at this point. 

But the rebels learned how to permanently destroy a \resphan. 
Maybe \Semiza{} told them. 
They must kill the body, cook it with special spells, eat the victim's flesh, drink his blood and devour his soul. 

\target{Rebels learn soul-eating}
\target{Rebels learn soul-eating from Umbrae}
They learned this skill by studying the \hr{Umbra}{\umbrae} and sort of reverse-engineering the \ps{\umbrae} \hr{Umbrae eat souls}{soul-eating technique}. 
But they never learned to do it as easily and effectively as the \umbrae{}. 

This was a horrible, gruesome weapon, and the \Merkyrans{} were horrified when they learned of it. 









\subsection{The \resphan{} lords betray their own}
There are cases where the \resphan{} lords betray their own and eat them. 
The leaders eat their younger fans, adherents, groupies, worshippers\dash those who trusted and loved them. 

Compare to Akasha in the movie \emph{Queen of the Damned}. 









\subsection{Show the good side of \Merkyrah}
\Semiza{} and the rebels dissed \Merkyrah{} like no tomorrow. 
But we should still see some scenes demonstrating the good sides of \Merkyrah. 

Show people who were happy about their lives. 
Have some tree-hugging, diabetes-inducing sweetness and gay pacifism. 









\subsection{The rebellion is necessary}
\target{Merkyran rebellion is necessary}
The rebels know that the rebellion, no matter how brutal, is necessary. 
The \resphan{} people are not only far from their true potential, they are actively declining. 
If they continue the \Merkyran{} way, they will continue to degenerate until they are no more powerful than \humans. 
In the end their Entropic hunger will consume them and they will die. 
Being afflicted with \Bane{} \hs{Entropy}, the \hr{Resphan parasitism}{\resphain{} are parasitic} and must consume external power to survive. 

They must gain access to the \hr{Heart}{Heart of \Miith} and draw of its power. 
This is the only way to keep their people alive. 
But the \dragons{} and their ilk are hogging the Heart. 
In order to eat of the Heart's power, they must steal it from the \dragons. 
So war is the only option. 

The rebels cannot hope to stand against the \dragons{} alone. 
They can stand a chance only if the entire \resphan{} people stands united. 
They know that the \Merkyran{} church will never accept this truth, since their entire religion is knowingly and deliberately build up around the active denial of this very truth. 
Thus, a violent rebellion and coup is the only way. 

The more moral rebels (especially \Damiarch{} and \Sithiyacaan) are saddened by this, but they have a sacred duty to their people and must do what they must. 
Their entire race's survival and future is at stake. 
That is more important than anything, and worth any price, even genocide and tyranny. 

\lyricsbs{Hate Eternal}{The Victorious Reign}{
  The victorious reign!
  
  We are the glorious order, \\
  bound together by blood and by faith,\\
  successors to a tradition.\\
  Are we the vessels of death?
  
  We are your purification, \\
  united by purpose and will,\\
  affiliates of an allegiance. \\
  Are we the blasphemous creed?
  
  We are the infamous legion, \\
  a covenant of supposed heresy,\\
  conceivers of a hierarchy. \\
  Are we the disciples from Hell?
  
  Sworn to this alliance, we only speak of truths.\\
  Heretical in its shape. Is it profane?\\
  Devotees to the cause, sacrilegious in its form.\\
  Sworn to this alliance, we only honor him.\\
  Heretical in its shape. Is it profane?
}









\subsection[Zachirah founds Mystraacht]{\Zachirah{} founds \Mystraacht}
\target{Zachirah founds Mystraacht}
\hr{Zachirah}{\Zachirah} turned \hr{Zachirah goes mad}{evil and power-hungry and mad}. 
He was not entirely satisfied with \Damiarch{} and \ps{\Gevural} ideology, so he founded his own extremist sub-fraction: \Mystraacht. 

He also founded \hr{Mystraacht philosophy}{\ps{\Mystraacht}{} evil philosophy} (see that section). 

He preached hate and violence. 

\lyricsdimmuborgir{Progenies of the Great Apocalypse}{
  The battle raged on and on, \\
  fuelled by the venom of hatred for Man. \\
  Consistently, without the eyes to see, \\
  by those who revel in sewer equally.
  
  Are we not the undisputed prodigy of warfare, \\
  fearing all the mediocrity that they possess? \\
  Should we not hunt the bastards down with our might, \\
  reinforce and claim the throne that is rightfully ours?
  
  Consider the god we could be without the grace. \\
  Once and for all. \\
  Diminish the sub principle and leave it's toxic trace. \\
  Once and for all.
}

\lyricsdimmuborgir{Vredesbyrd}{
  Reis deg opp, la oss bestride den tanke fra v\aa{}r lend, \\
  og dyrk p\aa{} en forbannet jord en smertens \ae{}tt. \\
  For s\aa{} og tynge de barmhjertiges skj\o{}d, \\
  som har tiltro til den sjell\o{}ses br\o{}d.
}

He recruited new people to join his faction. 

\lyricsbs{Vital Remains}{I Am God}{
  Follow me now and walk the hounds of Hell \\
  and ride the whirlwinds of the night. \\
  Together we become an army out of Hell, \\
  to scourge the Earth, and melt the ice.
  
  I am one within myself. \\
  I am one with the night. \\
  Prevailing darkness, I rule this space. \\
  Call me God, remembering my face. \\
  I will rise divide and conquer. \\
  This world I live there is no other. \\
  Call to the points North, West, South, East. \\
  You summon me, I am the Beast!
}

They feel that this new truth they have discovered not only warrants but \emph{demands} a total break from tradition. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  The Repellent Scars of Abandon and Election
}{
  The feeling of destroying the capacity for inward peace, \\
  an insane dance with the angels of innocence \\
  amidst thorns and in frenzy, \\
  the warmth of a divine blessing, \\
  a daringness which prevailed over any imaginable fear\\
  hovering on the brink of a voluntary act of contrition, \\
  but soon all pales besides the cry \\
  this shattering truth wrests from all fellow men, \\
  there is more to it than suffering and sounds of suffering, \\
  it is a process that only the extinction \\
  of a divine soul could terminate. 
  
  The eye can outstare neither the sun, nor death\ldots{} \\
  if I sought God it was in delirium \\
  and in the delight of temptation.
}





\subsubsection{\Zachirah{} seduces Ramiel}
\target{Zachirah seduces Ramiel}
\Zachirah{} convinced Ramiel to join his fraction. 

\lyricsbs{Marduk}{Darkness It Shall Be}{
  I have dreamt the dreams about Satan's beautiful promises\\
  Of the dark arts, and the blackened powers I possess\\
  I have dreamt about worlds burning in millions of fires\\
  And the worthless christianity burning with them\\
  I and you are all that is dark of the world\\
  And so we shall greet the everlasting night with pride\\
  You and I bear the wisdom of a thousand geniuses\\
  And we are granted the right to lead the people to their ends
  
  I have dreamt about the deeds of the very past\\
  But none of them are as great as those to come\\
  I have dreamt about great days to come\\
  When I shall wear the black crown, and rule with Satanic might\\
  I and you are born of the same great blood\\
  And we are proud warriors in the great army of Satan\\
  You and I have got the world in our grasp\\
  The world at our knees, and the vision of destruction in our eyes
  
  A new age will come, and a new King will be crowned\\
  A new age will arrive.. In your own blood, you shall be drowned\\
  This new age of Satan, the new age of Hell\\
  This is what I have seen, and darkness it shall be
  
  I have dreamt the dreams that will come true.
}









\subsection{Rebels ally with tribes}
The rebels allied with some of the other \resphan{} tribes that were the traditional enemies of \Merkyrah. 
\Zachirah \hr{Zachirah has tribe contacts}{had contacts among the tribes}, so he was central in establishing this alliance. 

Compare to how Alexander Devon recruits the Heshette in \authorbook{Alan Campbell}{Scar Night}. 

\citebandsong{Nile:BlackSeedsofVengeance}{Nile}{
  Black Seeds of Vengeance
}{
  Dismemberment and slaughter shall you perform on them\\
  The mighty Sekhmet will devour them\\
  The chain of Sut is around their neck, Horus hammereth them\\
  Nepthys hacketh them to bits, the eye of Ra eateth into their faces\\
  Their carcasses will be consumed in the desert\\
  The seed of Amu with perish utterly\\
  Their filth shall never breed among you again\\
  We shall blot out the remembrance of Amalek from under the sky.
}





\subsubsection{Alliance with freed prisoners}
At \Zachirah's initiative, the rebels freed some prisoners from the \hr{Merkyrah prison}{dungeons of \Merkyrah}, if these agreed to serve them and join the rebellion and help overthrow \Merkyrah. 









\subsection{A rebel kills a faithful}
A rebel gets into a fight and kills a faithful. 
This is one of the sparks that ignite open war. 

The killer had been nurturing hate towards the church and the faithful for a long time, and finally snapped, craving release. 

\lyricsdimmuborgir{Da Den Kristne Satte Livet Til}{
  Min sjel den gl\o{}det og mitt sinn det lengtet\\
  etter \aa{} f\aa{} fatt i en kristen faen.\\
  I det kalde m\o{}rket jeg ventet med vinden.\\
  Det ulte som besatt av Fanden.
  
  Jeg ventet, \aa{}h, som jeg ventet.\\
  Tiden virket som evig.\\
  Men endelig fikk jeg \o{}ye p\aa{} stakkar'n.\\
  Jeg hevet min knyttede neve og skrek.
  
  Svake kristne! D\o{} i natt!\\
  Jeg skal flerre din sjel i to.\\
  Du skal f\o{}le makten jeg har f\aa{}tt av m\o{}rket.\\
  Din tid er omme, ogs\aa{} din tro!
  
  Be om n\aa{}de, du stakkars faen,\\
  og min latter skal atter runge\\
  h\o{}yt i nattens kulde\\
  der frosten fryser din siste t\aa{}re\ldots{}
  
  Svake kristne! Du d\o{}de i natt!\\
  Med et kraftig hugg tok jeg din skalle.\\
  En blodig slakt som til syvende og sist\\
  hvis stemmer (vil) for alltid i D\o{}dsriket gjalle.
}









\subsection{Preparing for war}
\lyricsbs{Vital Remains}{At War With God}{
  Beneath my flesh flows the blood of wisdom. \\
  Within my heart, the hunger for conquest. \\
  This silent legion, birth of a new revelation. \\
  The day has come when God's land shall burn. \\
  Watching as your kingdom falls. At war with God.
}
















\section{The Mask Falls (\yds{Murder of the Dawn})}
\subsection{Rebellion}
\target{Merkyran rebellion}
\target{Resphan rebellion}
It comes to open rebellion and war between the dark siders and the light siders. 

Since the \Merkyrans{} deny their vampiric nature, they are weak, easy prey for the rebels, who strike them down and devour their blood, flesh and their very souls. Remember to have some dark, grisly scenes where the rebels eat \resphan{} flesh. 

The dark ones announce their war by launching a grand attack on a \Merkyran{} city. They fall upon it like a terrible storm. 

Have some bloodbath scenes where \Merkyrans{} and their \human{} and \nephilic{} subjects are mowed down in droves. 

\lyricsbalsagoth{The Thirteen Cryptical Prophecies of Mu}{
  [THE CHIEF CULTIST OF ZURRA:]\\
  In the sweltering swathe of Zurra's sword! Kill, kill, kill! \\
  'Fore the matchless might of Zurra's wrath! Die!
  
  [THE HIGH PRIEST OF MU:]\\
  The storm comes.\\
  On the katabatic winds rides ravening doom.\\
  Yasa-mega\ldots{} Yasa-giga\ldots{} Yasa-tera!\\
  May Klatrymadon preserve us!
}

Perhaps there are some \nexus{} \trope{McGuffin}{McGuffins} in the city that the dark ones need. 

\lyricsbalsagoth{The Thirteen Cryptical Prophecies of Mu}{
  Become one with the shard, progeny of the Nexus\ldots{}\\
  embrace its power\ldots{} embrace the glory of immolation!
}

They fight with pride, considering themselves the true keepers of their race's legacy. 

\lyricsbs{Ancient Rites}{Victory or Valhalla (Last Man Standing)}{
  Stand strong with clenched fists. \\
  Withstand with all thy might. \\
  Stand strong with clenched fists \\
  until they are silenced right. 
  
  Let the glory shine on thee. \\
  Lift thy ancient legacy\ldots{} into light! \\
  Lift thy legacy into light, \\
  so their spirits will shine on bright\ldots{} \\
  shine bright!
}

The \Merkyrans{} fight back.

\lyricsbalsagoth{The Thirteen Cryptical Prophecies of Mu}{
  [THE PRIME VOYAGER:]\\
  Your folly ends here, Zurra!\\
  The Empyreal Lexicon has been made whole\ldots{}\\
  and its power is lost to you forever!\\
  The foe has been cast back into the Outer Darkness,\\
  but your treachery must not go unpunished!\\
  Submit to our judgement or face eternity in the limbo of Z'xulth!
  
  [ZURRA:]\\
  I would sooner suffer damnation a thousand times than bend the knee to you! \\
  You and your sublimely arrogant ilk, who strode the primordial surface of Pangaea and watched with disdain as life evolved in the boiling oceans\ldots{}\\
  You have won nothing! \\
  My power is born of Chaos\ldots{}\\
  it sustains me and courses blackly through my ersatz veins!\\
  Now face the true potency of the power you seek to destroy, and behold in awe the true nature of the universe!}





\subsubsection{Demography of the war}
\index{technology!\Merkyrah}
There were \hr{Merkyran demography}{rather many \resphain{} at this time}, and \hr{Merkyran technology}{the technology was low}. 
This meant that armies of mortals little chance against \resphain. 
So the war was fought largely with armies of \resphain. 
They rode mythical beasts and monsters. 

Many great, beautiful and wonderful monuments are destroyed in the war. 
\Azraid{} and Ramiel promise the people that they will built new ones, and even grander and more marvelous. 
They do, but many of these then end up getting destroyed in the \secondbanewar{} and the \resphanwars. 

But even today the \resphain{} have much splendour and beauty. 

\lyricsbs{Vital Remains}{Into Cold Darkness}{
  Now hundreds of angels rebel against God. \\
  Winged and naked, riding black wolves.
}

\lyricsbs{Vital Remains}{Descent Into Hell}{
  Riding out the demon locust, war horses of Hell. \\
  Penetrating the blazing heat (where) wicked angels dwell. \\
  Cast to Earth, unleashing spells, devouring your souls. \\
  Christian doctrine of false belief. God is bound in Hell.\\ 
  Bow your heads to the supreme God, Lord of darkness. \\
  (Seduced nations denying Christ Satan leads the aggression.)
  
  Abbadon, leader of locust spawn, \\
  destroyer of all Christianity.
}









\subsection{Scrupulous rebels angst}
The more scrupulous of the rebels (\Damiarch{} and \Sithiyacaan) fear the evil that they have helped unleash. 
They angst over it. 

\lyricsbs{Exmortem}{Fix of Negativity}{
  My acid burnt eyes\\
  predicting the rise of evil. \\
  A quick fix of negativity, \\
  a lifetime in misery. \\
  Paranoia strikes hard. 
  
  With glass in my eyes, \\
  I see clearer now. \\
  Feel a touch of divine suffering. \\
  I am an angel with bloody hands.
}

\lyricsbs{Monolith Deathcult}{Wrath of the Ba'ath}{
  I saw their starved lips in the gloam. \\
  With horrid warning their still fuming mouths gaped wide. \\
  And I awoke, and found me here, \\
  the sole survivor writhing on the cold hill's side.
}









\subsection{\Gepheral becomes \Azraid}
\target{Azraid coup}





\subsubsection{\Gevural has an inner struggle}
\Gevural{} has an inner struggle. 
He is torn between \quo{good} and \quo{evil} and doesn't know what is right. 

\lyricsdimmuborgir{Kings of the Carnival Creation}{
  In search for the guidelines to the gateways of sin, \\
  through mires of misanthropy with wrath in mind.\\
  Sophistication as cruelty and perfection as virulent truth.
  
  Confidently dawned, to pick the best of enemies.
  
  An abyss womb stretched wide open, exposed to retaliate.
}

\Daggerrain{} manipulates him, pulls him toward the darkness. 

\lyricsdimmuborgir{Kings of the Carnival Creation}{
  Glance into the blackness hidden beneath your surface,\\
  and enjoy the suffering, sanity drained in disrespect.\\
  With such bedevilled faith in good, subsequently trusting evil.\\
  Next step for mankind will be the last seasons in sin.
}

\Daggerrain{} tempts him with darkness and evil. 

\lyricsdimmuborgir{The Maelstrom Mephisto}{
  Dwell in depths of the darker self, at any shore of infinity,\\
  and watch the relentless paint the soil black.\\
  What is being formed echoes throughout eternity,\\
  as the painter chooses color no more.
}





\subsubsection{\Gevural becomes \Azraid}
\Gevural{} claims some great power and takes the name \Azraid{}. 
He gains his \hs{dead hand}.

\lyricslimbonicart{Pits of the Cold Beyond}{
  As the shadows of dark angels fall\\
  from the grace of light,\\
  I am carried in the arms of death\\
  into the night.}

He floats through mystic dimensions. 

\lyricslimbonicart{Pits of the Cold Beyond}{
  The universe unveils\\
  a glowing entrance to doom,\\
  next to the setting sun \\
  and the rising moon.}

All the death and destruction gives him power.

\lyricslimbonicart{Pits of the Cold Beyond}{
  Wine of life streams\\
  in faint nocturnal screams.
  
  As the rivers run red\\
  from the wrath of Armageddon,\\
  and the wine of life is shed\\
  into the pits of the cold beyond.
}

Long after his sinister experiment, \Gevural{} lies in a coma. 
The other \resphan{} lords believe him to be dead and are about to elect a successor to take over his rank.

\lyricslimbonicart{Pits of the Cold Beyond}{
  At the time when the sun emerges from the dark,\\
  in limbo a star shines and in silver it sparks.\\
  I search my soul as darkness burns.\\
  For a shadow it shall return\\
  from the pits of the cold beyond.
}

\lyricslimbonicart{Unleashed From Hell}{
  Back from the dead, across the axis of dreams.\\
  A malicious hunger. The bloodline still streams.\\
  I am a martyr of the dark side,\\
  a tyrant in soul and flesh.
}





\subsubsection{Chosen for his weakness}
\Daggerrain chose \Gepheral as his new agent and groomed him to be the High Lord of the \Resphain. 
\Daggerrain saw \Gepheral as a fairly weak and predictable \resphan whom he could easily dominate and manipulate. 
And true, at first, \Gepheral was fairly weak and predictable.
But after \Daggerrain invaded his mind, \Gepheral did not simply succumb. 
He experienced inner epiphanies and found great inner strength.
He realized that he did not wish to serve the \banes, and he was clever and strong enough to be able to conceal this from the \banes.





\subsubsection{\Azraid begins to hate the \banes}
\target{Azraid as Xanatos Sucker}
Through his transformation \Azraid gained new and terrible insight. 
He began to understand the \hs{dead universe}, which \Sethicus had also seen. 

\citebandsong{BlindGuardian:ANATO}{Blind Guardian}{The Soulforged}{
  And through the hour glass\\
  Everything's grey, everyone's pale\\
  Nor colour nor beauty will enlighten my heart\\
  The seat of life's empty and cold\\
  Cadaverous you all seem to me\\
  Stillborn but you're still alive\\
  You're still alive
}

With his new occult insight, \Azraid began to realize that he and the rest of the \resphain had been manipulated from the start by \Daggerrain. 

Compare a \hr{Ramiel as Xanatos Sucker}{similar scene with Ramiel later on}. 
Also compare to the scene in \emph{\JuukenSentaiGekiranger} episode 46 (or so) where Rio discovers that his entire life has been masterminded by Long. 

Later, during the bloody war against \Merkyrah{}, he would come to realize that the \banes{} really cared nothing for the \resphain{} except as tools to use and discard. 

Thus he begins to hate the \banes. 
He still obeys the \banelords{} on the surface and does everything he can to further their schemes, but in secret he is plotting to overthrow them. 
It will take him twenty thousand years, but eventually he will betray and usurp \Banelord{} \Daggerrain. 









\subsection{\Morcariel stages a coup}
\target{Morcariel coup}
The leader of the rebellion is \Damiarch. 
But \Morcariel covets leadership for himself. 





\subsubsection{Contrast between \Damiarch and \Morcariel}
\Damiarch was much more idealistic. 
He genuinely believed that he fought for the liberation and enlightenment of his people and for their glorious destiny. 
He fought for a Utopia, and \trope{UtopiaJustifiesTheMeans}{Utopia Justifies the Means}. 

In contrast, \Morcariel was far more evil. 
He craved power for its own sake, and desired to rule in the name of Chaos and Darkness. 

\lyricsbalsagoth{Callisto Rising}{
  Break the sidereal seal, brother!\\
  Open the astral portal! Give me the Lexicon\ldots{}\\
  give me that which is rightfully mine!\\
  Destroy the guardian-light\ldots{} Kill!
  
  Unfetter yourself, brother Zuranthus\ldots{}\\
  bestow upon me the shard which I seek\ldots{}\\
  give me my godhead, or I shall condemn your flaccid essence\\
  to a dimension of unparalleled pain! Kill!
}





\subsubsection{\Morcariel kills \Damiarch}
\target{Morcariel kills Damiarch}
\target{Morcariel betrays Damiarch}
\target{Azraid kills Damiarch}
\Daggerrain{} wants rid of \Damiarch. 
\Damiarch{} is too moral, too scrupulous for the \ps{\banelord}{} purposes. 
He needs someone more flexible, someone who will not shy away from things that, in \ps{\Daggerrain}{} grand scheme, need doing. 
He sees \Morcariel as a good candidate who would be willing to do all sorts of evil if goaded a bit. 

So \Daggerrain{} manipulates \Morcariel into murdering \Damiarch{} and enthroning himself as the lord of the \resphain. 

\Morcariel eats \Damiarch{} to gain his power. 

\lyricslimbonicart{The Black Hearts Nirvana}{
  Hallowed be the darkness that coronates my soul.\\
  Deep within its shelter I seek my highest goals.\\
  I shall release what is conquered \\
  from which that I now possess.\\
  All lifeforce is abandoned \\
  into the arms of death.
  
  Beyond the great dark adventures, \\
  in streams from the vast mysteries,\\
  limbonic spheres enclose me. \\
  My star is the death of memories.
}









\subsection{Destroy their faith}
The rebels learn that \Merkyrah{} is held together by a Shroud \hs{Mask}. 
In order to break the mask they must break the \Merkyran{} people's faith in their religion. 
Only then can they create a new world in their image. 

\lyricsbs{Vital Remains}{Icons of Evil}{
  Defame the names of all your dead gods.\\
  Vomit upon the path of salvation.\\

  Confront me now, defiler of human desire.\\
  Voracious hordes await the hour of ascension.\\
  Unravel their delusion,\\
  their translucent divinity.

  Burn down the churches\ldots{} engulfed by hatred. \\
  Tear down the kingdom\ldots{} incinerate his vision. \\
  Destroy their icons\ldots{} pulled from their neck.\\
  The exodus of faith\ldots{} their will we did break.\\
  Shattering the hope they once loved. 
}

They force themselves to surrender the last vestiges of faith. 

\lyricsbs{Vital Remains}{Infidel}{
  The infidel within me,  \\
  forever unbelieving. \\
  Purgate the stain of thy blessings. \\
  Obscure the light of Eden.
}

Some rebels are unsure and still think there are good things about \Merkyrah{} that are worth preserving. 
The mourn and angst over the fact that their inner goodness dies and is replaced by evil. 

\lyricsbs{Vital Remains}{Infidel}{
  Taint the vision of purity. Heaven ravaged. \\
  A revelation of impurity has awakened. \\
  Your inner being withers from a lifetime of devotion. \\
  Never to hear the endless cries of the faithful.
}









\subsection{Orgies}
The rebels hold great orgies of sex and violence. 
Compare to Bequa Kynska's \emph{Maraviglia} in \authorbook{Graham McNeill}{Fulgrim}. 

Some of the \CiriathSepher{} feel that this is too vulgar, too uncivilized, too evil. 
This is one of the reasons for the \hr{Dynasties drift apart}{split between the dynasties}. 









\subsection{The Murder of the Dawn}
\target{Murder of the Dawn}
The deciding climax in the rebellion was the day of the \quo{Murder of the Dawn}. 

There was a great theatre show in \Merkyrah.
It was an important tradition, and every important \resphan was there to attend. 
This was where the rebels struck. 
Compare to \cite{EdgarAllanPoe:TheConquerorWorm} and Simtal's F\^ete in \cite{StevenErikson:GardensoftheMoon}.

This is an Invocation of \Erebean{} Darkness. 
The dark ones \quo{murdered the dawn} by shifting the entire realm of \Nyx closer to \Erebos, where eternal darkness reigned. 
The city is built using the power of \hr{Old Good Iquin}{\Esheram}, which is ultimately a filtered form of \nieur, which is \Nyx-based.

The invocation opens a weak conduit to \Erebos, allowing the \resphain to draw more raw power from the \banes.
This was necessary for \Daggerrain's masterplan at this point in time.

It also had another useful consequence: 
When \Nyx was shifted closer to \Erebos it was removed further from the senses of the \dragons in \Tembrae. 
This made it more difficult for the \dragons to sense what was going on in \Nyx, making it easier for the \resphain to rearm in secret and prepare for an invasion.

Perhaps the Murder of the Dawn is the \hr{Nyx was killed}{\quo{killing} of \Nyx} which turns \Nyx{} into a parasite Realm. 





\subsubsection{Imagery}
\lyricsbs{Hate Eternal}{Para Bellum}{
  May thy kingdom of the accused ones now rise.\
  Para Bellum! Para Bellum!\\
  March upon the gates of death,\\
  for those who walk among us must follow.
  
  Ira Deorum.
  
  We shall ravage the earth \\
  and destroy the ominous skies.\\
  Bring forth the end of days.\\
  Where the darkness of time \\
  shall once again consume us all.\\
  Come forth the end of time.
  
  May thy kingdom of the accursed ones now rise.\\
  Para Bellum! Para Bellum!\\
  March upon the gates of death, \\
  For those who walk among us must follow.
  
  May thy sovereign of the imperial ones now rise.\\
  Para Belllum! Para Bellum!.\\
  For we shall now conquer death,\\
  For those who walk among us are lords of war.
  
  We must darken and enlighten the world \\
  upon the mountainous shrine.\\
  Cometh forth the end of days.\\
  Hence the frenzy of brutality rules us all.\\
  Cometh forth the end of time.
}

\lyricsbs{Vital Remains}{At War With God}{
  The sun descends into the blackening horizon. \\
  We shall wait and chant until our hearts bleed hatred. \\
  Vision the bloodstream upon the one you adore. 
  
  Darken the light of the dying. \\
  Erase the thought of salvation. \\
  In Hell is where you are. \\
  The war has been upon you all.
}

\lyricsbs{Vital Remains}{Behold the Throne of Chaos}{
  The knell tolls, divine holocaust 
  by the grace of the Black Moon. \\
  The apocalyptic vision for all the world to bear \\
  witness to this, the opening of the wound. \\
  Your numinous kingdom now flows with\ldots{} blood.
}

\lyricsbs{Vital Remains}{Societe des Luciferiens}{
  The ever-fading light, the light of redemption. \\
  We appear as ravens through the mist. 
  Night-fallen, all-devouring. \\
  Shrouds of blackness \\
  silently consume all that is pure. \\
  Obscure his words, brothers of the bloodwar, \\
  for we are unchained and almighty.
  
  Solemn, the lifeless angel of dawn. \\
  Silhouette, the fading symbol of life\ldots{} \\
  disappears amongst the shadow of wolves.
  
  The celebrations of Christ become the worship of abhorrence, \\
  chant the paean of threnody \\
  for the council of virtue, a requiem sung for the all divine. \\
  Their lives are now exhausted \\
  as murdered day casts the sky in blood \\
  over the befallen city of\ldots{} Man.
  
  In the midst of Our black paradise \\
  shall undefiled wisdom rule. \\
  The rites of Christ are but rites of Death, \\
  accept the absolute. 
  
  Vanish into the void of thy empty Heaven, \\
  for thou wert never, nor shalt thou ever be. \\
  Undefiled wisdom, its fiery meaning shall make thee free.
}

The \hs{black stars} become visible in the sky. 
The \Merkyrans{} \hr{Merkyran myths of black stars}{had feared this}, so they despair. 
Many become truly convinced now that the rebels speak the truth and that their old way of life truly is doomed. 

\lyricsbs{Marduk}{Blutrache}{
  Judgement Day edges toward evening.\\
  Every nation marches singing,\\
  every nation towards death.\\
  Let us rejoice in the light\\
  of this man-made Armageddon\\
  this man-made Hell.\\
  Hand in hand with angels of iron,\\
  angels of wrath.\\
  Panzer thunder, panzer death.\\
  Black twelve-armed holy Sun.\\
  Rise, rise, holy black Sun.
  
  The great cathedral of Man arise\\
  through doors flung wide.\\
  Every nation marches singing\\
  towards defeat and death.
  
  Every nation marches singing,\\
  every nation towards death.\\
  Let us rejoice in the light of\\
  this glaring mass cremation,\\
  this shining mass-death-light.\\
  Hand in hand with angels of iron,\\
  angels of wrath.\\
  Panzer chaos, panzer Hell.\\
  Black twelve-armed holy Sun.\\
  Rise, rise, holy Sun.
  
  Let us rejoice in the light of\\
  this solemn dance of death.
}









\subsection[The Merkyrans fight back]{The \Merkyrans{} fight back}
The \Merkyrans{} fight back, but their hope and faith are failing. 

\lyricsbs{Monolith Deathcult}{Seven Months of Suffering}{
  I turn my eyes to Dagon, our great god, \\
  flat on his divine face in the Temple of Oannis.
  
  I turn my eyes to Ba'al, our great god,\\
  Powerlessly staring at the horizon \\
  in the temple of Created Things.\\
  We feel no more glory about the battle of Aphek.\\
  What sacrifice is needed for victory?
  
  We burn\ldots{} oh god we burn!\\
  We bow down in shame and whisper powerless words: \\
  \ta{Let not the ark of the God of Israel be with us,\\
      for his hand is hard on us and on Dagon our god.}\\
  Release us from the suffering.}

They fear this new evil that has befallen them. 

\lyricsbs{Monolith Deathcult}{Seven Months of Suffering}{
  This blasphemy will be avenged upon us.\\
  Our blood will colour the earth blood-red.\\
  And it will be licked away by the dog-gods.\\
  Darkness will be upon us for three horrible days.\\
  Pestilence and death creep over our land.\\
  Flocks of bugs will ruin our crops.\\
  Blistering flashes from the skies\\
  onslaught the enemies of Israel.
  
  We are the damned race, \\
  sursed by the wrath of Yahweh.\\
  Our millennial resurrection\\
  shall be smothered in blood.}

They despair when facing the rebels and their diabolical magic. 

\lyricsbs{Monolith Deathcult}{Seven Months of Suffering}{
  Those who speak in tongues of distemper\\
  purify us in black flames.\\
  The fire-spitting demon Azazel\\
  spreads his blackened wings.\\
  The earth is drenched in the blood of Goliath.\\
  Seven months of suffering.}

They keep praying desperately. 

\lyricsbs{Monolith Deathcult}{Seven Months of Suffering}{
  Lord Ba'al, creator of our fertile earth,\\
  majestic father and king of gods and men.\\
  Master of the mountains, ruler of the rainstorms,\\
  we bow down before thy splendour.
  Lord Ba'al-El, god of life and fertility!
  Intermit the continual combat with the god Mot.\\
  Show the leech of Yahweh thy might,\\
  and slay the Hebrews and their ravaging god.
  
  \ldots{} and [Yahweh] \quo{ravaged and smote} \\
  the Philistines of Ashdod and its territories \\
  \quo{with tumours} for seven horrible months.
}

\lyricsbs{Hate Eternal}{Thus Salvation}{
  Pray for salvation, pray for absolution.\\
  These are the days of great lamentation.\\
  So we may be again as one.\\
  We are cursed by this plague.\\
  We are cursed by this travesty.\\
  Yet we shall rise above the depravity of man.\\
  Thus salvation!
}

The rebels confront them with the truth. 

\lyricsbs{Hate Eternal}{Thus Salvation}{
  Reveal thyself, dare not to deceive me.\\
  See what I see through these eyes of flame.\\
  You must believe in thy ways.\\
  Divulge to me, confessor of all that is holy.
  
  Prepare thyself, for you know not what I am.\\
  See what I see through these eyes of flame.\\
  You must choose your path wisely.\\
  Inevitable your descent into black.
}





\subsubsection{\Nephilim fight against rebels}
The \nephilim{} can clearly see that the dark ones are evil, so very few \nephilim{} join them. 
(Unlike \humans, \nephilim{} are not bred to serve the \resphain.) 
They are slaughtered in retaliation, and their whole race is nearly exterminated. 
Today \nephilim{} are rare because of this genocide. 





\subsubsection{\Merkyran magic fails}
\Merkyrah had a plethora of false myths and spells meant to protect against evil and invoke God.
The rebels preached that all this was a lie. 
They, on the other hand, had real magic with real power.

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  Kheftiu Asar Butchiu
}{
  The Fire Which Is in the Serpent Khetti\\
  Shall Come Forth\\
  And Blaze Against The Enemies of Osiris\\
  Whosoever Knoweth How to Use\\
  These Words of Power\\
  Against the Serpent Shall Be As One\\
  Who Doth Not Enter Upon His Fiery Path
}




\subsubsection{Ramiel kills a champion}
There is a \Merkyran{} champion whom \Zachirah{} wants to kill. 

\lyricsbs{Vital Remains}{Behold the Throne of Chaos}{
  Antagonist, come forth and defy my bloodwar \\
  at the first light of dawn. \\
  Crowned lord beheaded before me, glimpse your God dethroned. \\
  Iconoclast, the glorification of darkness, all is gone. \\
  He is dead.
}

But Ramiel demands the honour of slaying him. 
\Zachirah{} acquiesces and gives Ramiel his blessing. 

\lyricsbs{Vital Remains}{Behold the Throne of Chaos}{
  Pureblood of iniquity, \\
  unfurl the wings of infamy. \\
  Seraph enthralled by desecration, \\
  our bloodwar towards completion. \\
  Purgate all thought on divination, \\
  the knell tolls on forever. \\
  Lightless, amid empyrean collapse, \\
  behold the Throne of Chaos. \\
  Lightless, amid empyrean ablaze, \\
  behold the Throne of Chaos. 
}

Ramiel prevails and rejoices, drunk on victory and enraptured by the destruction. 

\lyricsbs{Vital Remains}{Behold the Throne of Chaos}{
  Deify my imperious vehemence. \\
  Their kingdom burns in flames. \\
  The ashes of God I bequeath, \\
  beneath our feet, defiled.
}

\Zachirah{} gloats. 

\lyricsbs{Vital Remains}{Behold the Throne of Chaos}{
  They weep in the Sign of the Horns, \\
  glory to blasphemy of idols. \\
  Satanic Millenium, upheaval. \\
  Let the joyless be adorned with horns.
}









\subsection{Driven by hate}
\Damiarch{} was lots nicer about stuff. 
His ideals were enlightenment and fulfillment of his people's true potential. 
But \Morcariel{} and \Zachirah{} preach hate and destruction. 

\lyricsdimmuborgir{Gud's Fortapelse\dash{}\AA{}penbaring Av Dommedag}{
  Hengitt er vi til M\o{}rkets keiser, \\
  den allmektiges kraft\\
  (som) f\o{}rer v\aa{}rt sinn i kamp\\
  mot godhet og l\o{}gn.
  
  Dog fiendens h\ae{}r er fattig, er den stor.\\
  Men vi skal ta dem alle og hente dem inn,\\
  en etter en.
  
  Det h\aa{}p de ser i Gud\\
  skal forsvinne i et hav av torner.
  
  Himmelen skal rakne, \\
  og en fandens torden skal buldre \aa{} brake.\\
  Hans krefter vil r\o{}yne, \\
  der M\o{}rkets front beseirer lystes pest.
  
  \O{}yne vil renne i sorg\\
  n\aa{}r de innser (at) deres Gud ikke lenger kan hjelpe.\\
  Det h\aa{}p de s\aa{} i Gud \\
  er svunnet og vekk for alltid.
}

\lyricsdimmuborgir{Avmaktslave}{
  Stanken fra den uransaklige vei,\\
  hvor forkynnelse og falsk forh\aa{}pning er \aa{}te,\\
  trenger igjennom som en bitterhetens gave\\
  og befrukter den menneskelige r\aa{}te.
  
  Retrett. Du har ei livets rett.\\
  Retrett. Du har ei livets rett.
  
  For ignoreres Dyret og idolets tegn\\
  vil straff omsider den skyldige bifalle.
}

\lyricsbs{Aeternus}{Slaying the Lambs}{
  Mother Earths men march.\\
  The power of Darkness\\
  glows in their blackened eyes.\\
  The lies of Christianity\\
  shall no longer be heard.\\
  Not ever again shall our world be branded\\
  by lies.
}





\subsubsection{They lose their innocence}
They are frenzied, obsessed with the need for destruction, and cannot stop even if they wanted to. 
Their vampiric nature has consumed them. 
This is the point where the \resphan{} people loses its \quo{innocence}. 
After this, there is no turning back. 
After all the atrocities they have committed against their own culture, the invasion of \Tembrae{} seems trivial. 

\lyricsdimmuborgir{In Death's Embrace}{
  By the light of the Moon\\
  and the beings of the night,\\
  a curse has been laid upon us: \\
  To seek and tear celestial gloss to pieces.
  
  By the power of Death\\
  and the shadow of the Reaper,\\
  a call has been brought upon us:\\
  To complete the infinite fall of Heaven.
}









\subsection{\Hoshiabalon writings exposed}
\target{Rebels expose Berugiel}
The rebels learned the truth behind the \hr{Hoshiabalon}{\Hoshiabalon letters}. 
They discovered the true and complete meaning/translation of the letters, including the parts that were spawned from \hr{Berugiel}{\Berugiel}'s subconscious mind and which he tried to hold back and hide. 

The rebels published the translation to everyone. 
People did not want to believe, but deep inside people knew that the rebels were telling the truth.
Their words rang true. 
It created doubt and despair among their enemies. 
(The rebels needed this because they were vastly outnumbered by their enemies.)

A few of the rebels, including \Azraid, worked on the translation in secret. 
The publication came as a surprise and a shock to most of the other rebels. 









\subsection{Angels and iconoclasm}
Maybe have some \uber-angels on the \Merkyran{} side. Perhaps these are the \hs{Voices of God} in physical form. 

They draw their power from some idols, statues, monuments, or even tablets of writing. Have a scene where a dark one, perhaps \Morcariel{} or \Ramiel, or even \Sithiyacaan, destroys these icons one by one and watches as the angels weep and weaken. 

Perhaps the angels are not \uber{} at all, but powerless and forced to watch. 

Compare to a scene in \FLuneNoireVol{11} (I think). 

\lyricsbs{Monolith Deathcult}{1567 - Under The Bloodcampaign}{
  Yea, we pull down the images of the false church.\\
  We pillage the temples of the popery.\\
  Defacing the paintings and tapestries of ancient Rome.\\
  With a fierce contempt we destroy the symbols of the dishonest.
}

\Zachirah{} laughs as he destroys the \Merkyran{} faith. 

\lyricsbs{Monolith Deathcult}{Forest of Flesh}{
  Bow for me, pathetic mortals, your God is dead for ages,\\
  impaled like thousands of your despised people.\\
  Eyes gazing glassy and vacant at the bloodred sky.\\
  Violently condemned to see your dying God above.
}









\subsection[Merkyrah falls]{\Merkyrah{} falls}
\target{Rebels conquer Merkyrah}
Eventually the dark siders win and conquer the entire \resphan{} civilization. 

They rejoice in their evil. 

\lyricsdimmuborgir{Mourning Palace}{
  Whispering voices, summoning screams.\\
  Waiting for Satan to bless their sins.\\
  Blackhearted angels fallen from grace,\\
  oossessed by the search for utter darkness.
}

They mock the empire as it falls.

\lyricsdimmuborgir{Kings of the Carnival Creation}{
  Sense the withering eternity as it fades away.\\
  The ultimate graceless voyage of all times.\\
  Only death will be guarding your angels, silently.\\
  Cripples joining arms in clamour.\\
  Institutionalized for the rebirth, the herd will be hunted.
}

\lyricsbs{Aeternus}{Wrath of a Warlord}{
  Manipulation!\\
  Open your eyes and see your failure.\\
  The whirlwinds of my destiny.\\
  Blackened might.\\
  The eternity has no throne for you.
  
  You pretended to be a god.\\
  You carved lies into minds.\\
  Now the lies shall die with you.\\
  I will show you the face of a god.\\
  The wary lust for torture\\
  roars inside of me.
  
  Now you will die.\\
  The whirlwinds of your destiny.\\
  Feel the blade of fire\\
  as it cuts your mortal soul.
  
  Fragile souls yet blessed by eternity.\\
  Find strength in unity.\\
  There is none above and none beneath.\\
  You are the gods,\\
  the lords and queens of darkness\\
  and glorified immortality.
}

They revel in the darkness as they destroy the last remnants of \Merkyrah{}. 

\lyricsbalsagoth{The Thirteen Cryptical Prophecies of Mu}{
  Ah, the Alpha and the Omega.\\
  As all life was created from Chaos\ldots{}\\
  so shall it be DESTROYED!!!
}

Especially the \Mystraacht{} rejoice in the evil they have wrought. 
They celebrate their infernal glory. 

\lyricsbs{Vital Remains}{Unleash Hell}{
  To the almighty of this godless land. \\
  For our brothers who bled upon the earth. \\
  For the warriors of the bloodwar who stand triumphant: \\
  The raised fist of domination, our final act of hate. \\
  Hail to us, to blasphemy!
}

\lyricsbs{Vital Remains}{Rush of Deliverance}{
  Choosing the one with the infernal horns. \\
  The one with black wings proudly soars \\
  across the path you've wandered upon. \\
  See your monuments of faith charred. \\
  In Satan we trust\ldots{} Satan, Satan, Satan, Satan. 
}





\subsubsection{\Nyx becomes a dark ruin}
\target{Resphain devastate Nyx}
In the process of the war the beautiful cities of \Nyx{} were devastated and became a dark ruin. 
It would \hr{Nyx rebuilt}{later be rebuilt}. 

\lyricsbs{Vital Remains}{Scrolls of a Millenium Past}{
  Burning churches to the ground.\\
  Unearthly desolation, all is black.\\
  Bones stand tombless as their flesh.\\
  Crackling flames wither away.\\
  All remains covered by dust.\\
  Funeral piles, the war must go on.
}





\subsubsection{They must corrupt the people's faith}
Now the rebels must corrupt and break the people's faith in the \Merkyran{} religion. 

\lyricsbs{Vital Remains}{Scorned}{
  The balance of faith has been shifted. \\
  Consumed by the light, vehement for deliverance\\
  spreads the contamination within the righteous, \\
  leading them towards the abyss of blood and wickedness. 
}

\lyricsbs{Vital Remains}{Infidel}{
  Victory by vehemence. The conquered shall feel our steel. \\
  Implode the structures of religion.\\
  All faith in god collapses. \\
  Your shrine of gold has rusted away.
}

\lyricsbs{Vital Remains}{At War With God}{
  Insacred vision. The horrific truth revealed. \\
  For those who sought, impurity has taken.  \\
  No light shall shine for thee. The flock of mockery. \\
  At the end of all life. \\
  Never to praise the worm. Maggot of the holy. \\
  Scourge of all life. Ravager of the weak. \\
  Blood is no worth to those who shall reap. \\
  End their time of peace.\\
  End their fucking time of peace now. 

  The coming of eternal war. \\
  Prepare for the end of your divine image. \\
  Swarming the faithful. \\
  Crushing the unity of all that is holy. 
}

Some believers mourn. 

\lyricsbs{Vital Remains}{Infidel}{
  Bedarken the sight of Paradise. \\
  Mourn the thought of hope departing. \\
  To walk the path of the righteous slave, \\
  forever dragging the chains of torment.
}

Faith finally dies. 

\lyricsbs{Vital Remains}{Devoured Elysium}{
  The veil of lies is lifted from their blinded eyes. \\
  Ceaselessly devoured Elysium. \\
  Your truth was torn from the womb of Mary. \\
  The word of God slowly dies.
}

The \Merkyrans{} realize that their faith is a lie. 

\lyricsbs{Vital Remains}{Devoured Elysium}{
  As dusk reveals the remains of the kingdom, \\
  the structures of faith collapses before you. \\
  Use his name in vain again and again. \\
  My flesh and blood will never be yours.
}





\subsubsection{\Morcariel reigned}
\target{Morcariel reigns}
\Morcariel reigned as High Lord of the new \resphan nation of \CiriathSepher, but he did not reign unchallenged. 
There were others, such as \Netzachirah and \Sithiyacaan, who disagreed with him and were influential enough to rival him. 

\Azraid was more ambiguous. 
He mostly supported \Morcariel, but \Azraid sort of represented \quo{evil with a \human face}.





\subsubsection{Soon they will summon the \banelords}
Soon the rebels would be able to summon the \banelords.
They looked forward to that. 


\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Odium Nostrum
}{
  Odium\\
  Oh Merciless Hatred;\\
  Burn the Me in me,\\
  And thus every cell of humanity.\\
  May the essence of impurity redeem my soul\\
  Unleashed hatred be my salvation and thy ghoul
  
  Worship, honour, glory, blessing,\\
  Odium, we offer unto Thee.\\
  Young and old, Thy praise expressing,\\
  In glad homage bend the knee.\\
  All demons in hell adore Thee;\\
  We would bow before Thy throne.\\
  As His angels serve before Thee,\\
  So on earth Thy will be done.\\
  Wherefore He also hath highly exalted it, \\
  and given it a name which is above every name:
  
  That at the name of Odium every knee should bow, \\
  of things in heaven, and thing in earth, and things under the earth;\\
  And that every tongue should confess that Odium is Lord, \\
  to the glory of Satan our Master.
}





\subsubsection{Consolidation}
\target{Nyx rebuilt}
\Nyx was laid waste. 
More than hald of all \bezedeth and two thirds of all mortals perished. 
But the surviving pureblood \resphain were now stronger than ever, having gorged themselves on the flesh and souls of the fallen. 
They were sated, healthy and fertile, ready to rebuild. 

\Morcariel-tachi could now begin to build up a strong, sustainable, grim and brutal empire. 
They went to work replenishing their populations (of \resphain and mortals alike) and consolidating their power. 
They needed an army vast enough to invade and conquer an entire planet. 
\Morcariel needed to consolidate his position as High Lord. 

So far only \Merkyrah had fallen to the rebels. 
Vast though the empire was, it covered only a small part of \Nyx. 
There were many nations and tribes yet to conquer.

With the aid of the \banelords, \CiriathSepher conquered their rivals and created peace in \Nyx.
Soon no one dared defy the High Lord. 
Some lords outside \Merkyrah willingly allied themselves with the nascent empire of \CiriathSepher and were made princes. 
(\hr{Harbeth}{\Harbeth} was one.)
They conquered or reconquered many uninhabited towers and extended their domain further down into the deep, driving the monsters before them. 
The \resphan-inhabited \Nyx grew larger than ever before.
(See the section about \hr{Resphan demographics}{\resphan demographics}.)

They rebuilt \Nyx into something beautiful, if grim and martial. 
It would remain beautiful until \hr{Ishnaruchaefir devastates Nyx}{\Ishnaruchaefir attacked and devastated it}. 

It would be hundreds of years before they were ready to attack \Tembrae. 























