















\chapter{\FirstbanewarBook}















\section{Pre-History}
In ancient times there were three peoples that dominated \Miith{}: 
The \krakens, the \xss{} and the \voyagers. 

Only the \krakens{} were native to \Miith{}. 
Billions of years ago they ruled the Realm. 
Then they became tired and went dormant. 









\subsection{World-Gods}
\target{History of the World-Gods}
The \quo{World-Gods} were a race of cosmic gods.
A World-God could merge with a planet and \emph{become} the planet.
In this way they colonized much of the universe.
Two such planets were \Miith and \Erebos. 

The \voyagers waged a neverending war against the World-Gods.

\target{Voyagers slay the World-God of Miith}
After a titanic war the \voyagers slew the World-God of \Miith.
To prevent it from ever rising again the \voyagers created a parasitic \dweomer, the \hr{Heart of Miith}{Heart of \Miith}.
This \dweomer drained energy from the World-God's own \dweomer, the \hs{Dark Heart} of \Miith. 
The Dark Heart remained undead and rotting precisely because the Heart feasted on it like a leech.
And all life on \Miith was spawned by the Heart and lived in symbiosis with the Heart.
What this meant was that all life on the planet really existed only to keep the World-God chained in death. 
All living creatures were prison wardens. 
The blood that coursed through their veins were conduits for the power of the Heart that kept the dead World-God in check.

Thus the World-God created its own monsters to destroy this hated life and allow the World-God to rise again and resume its awful, monstrous life.
These monsters were the \hs{Masters of Negation}, and their servitors were the \hr{Noggyal}{\noggyaleth}.

The Masters of Negation waged war against the \voyagers. 
Eventually the \voyagers left \Miith. 
Billions of years later, this life that the \voyagers{} had created would become the \ophidians. 









\subsection{\Voyagers come to \Miith}
\target{Voyagers come to Miith}
The \voyagers{} came from space in their spaceships. 
They created life in their Genesis Pits. 

\target{Voyagers create the Heart}
The \voyagers{} created the \hr{Heart}{Heart of \Miith} from some Chaos power. 
They shaped \Miith{} into something that looked like modern-day \Miith{}. 

\target{Voyagers create mother-mass}
They tampered with the \noggyal \hs{mother-mass} (which was \hr{Noggyaleth were the first life}{the first life form on \Miith}). 
From it they shaped all sorts of life. 

They enslaved the \noggyaleth and used them as machines and slaves and even houses.
The \voyagers taught the \noggyaleth much. 
Thus was sown one of the seeds that would eventually cause the \pps{\voyagers} downfall. 

When the \voyagers{} shaped all their life-stuff, they unwittingly tapped into a sinister force; the energy of a dark god of life and death: \KhothSell. 
This entity infested their \dweomers{} and their \hs{mother-mass}. 
The \voyagers{} did not discover this until very late. 
From there they could only hope to contain the taint, not cleanse it. 
Later their creations rebelled against them. 









\subsection{\Voyagers erect Palisades}
\target{Voyagers erect Palisades}
\target{Palisades}
The voids between planets were \hr{Horrors of the Void}{filled by all sorts of horrors}.
When the \voyagers settled \Miith hundreds of millions of years ago, they erected dimensional barriers around the Realms of \Miith to keep it safe from these horrors.

In a sense, the \xss were some of these \quo{horrors} that the \voyagers feared.
They were some of the greatest \quo{horrors}.

These dimensional barriers, known as the \Voyagers' Palisades, were an early Shroud-like construction, but much better made (by the super-advanced \voyagers), and so had none or few of the destructive side-effects that the later Shroud had.

The Palisades also kept the \banes out, but eventually the \banes managed to drill through.

The \ophidians had some limited understanding of the \voyagers' work, and they drew on it.
They built the \hr{Crystal Sphere}{\CrystalSphere} to patch up the holes in the Palisades that the \banes had made.









\subsection{Poetic version}
\subsubsection{The \voyagers{} and the \krakens}
Once there were the \voyagers, a race of mighty beings (gods, if one wills) who \travelled across the Universe, seeding worlds they found with life. In primordial time, billions of years ago, they came to \Miith{}, desiring to make the world theirs, a breeding ground for their creations. 

But \Miith{} was not barren. Before the \voyagers{} came, \Miith{} had her own children, her own indigenous life, and the greatest of them were the \krakens, the native overlords of \Miith{}. Terrible creatures they were, and immortal. And they were jealous and cared not for invaders, but craved \Miith{} as their birthright, and when the \voyagers{} sought to conquer their world, they fought. Few were the \krakens{}, numbering scarcely a dozen against the thousands of \voyagers{}, great and mighty in their own right. Yet in their wrath, the \krakens{} proved more than a match for the invaders, and in every conflict they would prevail. With valour and fury the \voyagers{} would fight, and with despair, for the \krakens{} were immortal and wielded the primal power of \Miith{} herself. Their leader and mother, the great \Kraken{} Queen, was the mightiest of all the children of \Miith{}, and none could stand before her when she rose in fury. 

But the \krakens{} were indolent, and they would often sleep, their entire race, for aeons at a time - millions, even hundreds of millions of years. And so, whenever the \krakens{} slept, the \voyagers{} would invade \Miith{}, to populate the planet with myriad life forms of their devise. And every time, after an aeon, the \krakens{} would awake to vanquish the \voyagers{}, scour the world of their creatures and repopulate it with their own spawn. But inevitably, the \krakens{} would once more go dormant, and the \voyagers{} would return to begin their work anew. 

For the \voyagers{} seek ever to perfect life, and \Miith{} is precious to them, for \Miith{} is an anvil on which to forge and shape their creations, their works of art. And a most excellent anvil is Mother \Miith{}, for it is her nature to take what is given to her and break it down and hammer it into a new shape, greater and mightier than before. The \voyagers{} have \travelled the universe for billions of years, and they have known many planets. Many worlds are hostile, wastelands of death that will destroy life and cause it to decline and decay. Other worlds are indifferent, possessed of no powerful energy, positive or negative. They will allow life to exist, but they will not support it. On such worlds, life will persist, but it will stagnate and remain humble and never know greatness. Not so Mother \Miith{}. She is possessed of a soul, and she is strong and fierce and indomitable. A loving mother is \Miith{}, but also cruel. The weak among her children she will destroy, and they shall have no legacy 
and know only oblivion. But the strong among her children she will cherish and glorify. Forged in fire and tempered in blood they shall rise, growing ever stronger, and they shall know greatness. For \Miith{} is a crucible of life, and her like is seldom found in the universe, and the \voyagers{} knew to cherish her. 





\subsubsection{\Moroch{} and the \nagae}
So the history of \Miith{} is divided into such cycles of creation and destruction in the cosmic struggle between these factions, the native \krakens{} and the alien \voyagers{}. 

Our story begins in one such cycle. The \voyagers{} had filled \Miith{} up with their creations, but they were fled, for the stars moved, and they knew that the \krakens{} would soon awaken. And one of the \krakens{} did awaken; in this day and age he is called \Moroch{}. What is his aim we cannot know, but when he awoke he began not to destroy, but to create. From the sea he took primitive beings, creatures of the \voyagers{}, and reshaped them in his own design. He gave them strength of body and mind, and bestowed upon them the power of thought, and he made them his servitors. 

The years passed, a million years and more, and still the \Kraken{} Queen and her brethren slumbered, and even \Moroch{} grew sleepy and fell dormant. But his spawn lived, and they grew and prospered, and they recalled their sire and offered him prayer and tribute. Hybrid children they were, born from the womb of the \psp{\voyagers} creation but fathered by a \kraken{} lord. Lowly they were, yet in this age they were the lords of \Miith{}, and their built their cities in the deep oceans across the globe, and they were the \nagae{}. 















\section{The \Ophidian{} Civilization}
\target{Ophidian humanoids}
Hundreds of millions of years after the \voyagers{} had left \Miith{}, the \ophidians{} evolved\dash also called the \caisith. 
From the ashes of the devastated world they rose up to make themselves its masters.
They went on to form great empires and develop marvelous science and sorcery.









\subsection{Origin of the \ophidians}





\subsubsection{Nibir}
\target{Nibir}
\target{Phaetonian}
\index{Nibir}%
\index{Phaetonian}%
Before the \ophidians, the Nibir dominated \Miith. 
The Nibir were aliens who came from the world of Phaeton. 

A Nibir looked like a giant \emph{Anomalocaris}, but with many long spindly jointless legs like the spines on a \emph{Hallucigenia}, and with many soft \emph{Hallucigenia}-like tentacles on its back. 

They were served by a lesser race called the Phaetonians. 
A Phaetonian was roughly human-sized or slightly larger. 
It resembled a \emph{Marrella} (a trilobite-like creature from the Burgess Shale), but with fewer limbs: 
Four long multi-jointed crab- or spider-like legs and four slimmer \quo{arms}. 

The Phaetonian cities took the form of giant coral arches. 





\subsubsection{\Caisith evolve intelligence under Nibir}
The \caisith evolved intelligence much faster than humans on Earth. 
Remember that on \Miith, intelligence and cognition is based on a combination of the physical brain and the non-physical soul. 
The \caisith souls were connected in a great \nexus. 
In a sense it was their \nexus that gained maturity, and this trickled down to the individual \caisith in the form of intelligence and sentience. 
It took several thousands of years, which is a short moment in the timeline of evolution. 

In ancient times, the \ophidians were the underdogs in a vast, hostile world of gruesome alien races and lightly slumbering Elder horrors.
The early \ophidians were not at the top of the food chain. 
The \caisith evolved while the Nibir ruled \Miith. 
The Nibir and Phaetonians were all immortal. 
Many thousands of years of existence had made them indolent and complacent. 
They barely noticed the rise of the \caisith into sentience, and they certainly paid them no attention. 
They vied for control of the planet with much more terrible forces: 
The \moongods, the \vorcanths, the Lords of the Deep. 
The Nibir did not for a moment imagine that the lowly \caisith would pose a threat. 

The Phaetonians took to hunting the \caisith as pests or simply for sport, or capturing them for cruel experiments. 
This persecution served to accelerate the \caisith evolution because it forced them to be more intelligent and organized in order to survive. 
They evolved cunning, stealth and dexterity. 
They learned to manipulate objects, both with their limbs and with telekinesis. 

The Phaetonian persecution also strengthened the \caisith race's species-wide spiritual bond. 
Living in the ruins of elder civilizations and fighting for their lives, the early \ophidians gradually learned to live together in packs and cooperate. 
Their nascent culture learned that they must work together to preserve their race from enemy outsiders.
Social structure developed. 
They developed the use of tools. 
Gradually they developed intelligence and culture. 
They learned to dream about the future of their race, to focus on it and sacrifice for it.

Eventually the \caisith would \hr{War against the Nibir}{wipe out the Nibir and the Phaetonians}.  





\subsubsection{Metabolism}
\target{Ophidians evolved}
\target{Ophidians half warm-blooded}
\target{metabolism control}
\index{metabolism control}
\index{warm-blooded}
\index{cold-blooded}
The \ophidians{} descended from reptiles who were making the transition from \quo{cold-blooded} to \quo{warm-blooded}. 
Crocodiles, lizards and the like remained cold-blooded, while synapsids, dinosaurs and pterosaurs evolved and become warm-blooded. 

Another group of animals were stranded midways. 
They developed the curious ability to switch back and forth, controlling their own metabolism to \quo{cool down} and become cold-blooded or warm-blooded as they wished. 
In a sense, this gave them the best of both worlds: 
The dynamic speed of warm-blooded creatures coupled with the patience of cold-blooded creatures. 

\citeauthorbook[p.80]{RobertTBakker:TheDinosaurHeresies}{%
  Robert T. Bakker%
}{%
  The Dinosaur Heresies%
}{
  The great serpents succeed by being something a warm-blooded mammal could never be\dash a hunter of infinite patience\ldots{}
}

The early \ophidians{} were crocodile-like in form. 
They developed relatively small bodies (like \humans or smaller). 

Despite their advantages, they were still not quite as effective as the more specialized true cold-bloods and true warm-bloods, so they remained a niche group. 
For many millions of years they evolved to fill special niches. 
Instead of huge size like some \saurians{} (or tiny size, like mammals), the proto-\ophidians{} were forced to take a different evolutionary route: 
They evolved psionic abilities, most notably psychometabolism. 

\target{torpor}
\index{torpor}
The \ophidians{} learned that if they made sure to be as inactive as possible, they could conserve their bodily energy, keep it in reserve and use it to power their brains (and, later, their psionics and sorcery). 
They could go into a state of torpor where their bodies would hibernate and operate at a very low metabolism, but their brains and minds could still work at full capacity. 
By utilizing their torpor strategically, \hr{Ophidian Imperial}{Imperials} would later learn to hoard vast amounts of energy and redirect it for magical purposes. 





\subsubsection{Telepathy and telekinesis}
The \caisith's psychometabolistic abilities were linked to a large and powerful brain. 
As their brains grew, this opened up the possibility for them to learn simple telepathy. 
Telepathic sensitivity was a useful survival trait that helped them hunt their prey and escape their own predators. 

They also learned simple telekinesis. 









\subsection{\Ophidian rise to power}
\target{Ophidians as underdogs}
From their very inception as a race, the \ophidians were pitted against elder creatures. 
They fought to survive. 
The nascent \ophidians were cunning and swift, and they reproduced quickly. 
They developed science, technology, psionics and sorcery.
Gradually, over the course of many millennia, the tide turned in their favour. 
They were able to push back the elder races and establish their own strongholds.
\Ophidian cities began to emerge. 

The \ophidians were underdogs, but they persevered. 
They managed to steer clear of the worst threats. 
As they learned more about the true nature of the world, they kept from going insane and instead increased in power. 
Their science and sorcery grew, aided in part by alien relics that they discovered. 
There were still horrid things that the \ophidians feared to challenge, but these were dormant threats. 
Those alien forces that actively threatened were ultimately defeated, and the \ophidian race won dominance over the planet. 
They were now a mighty race of scientists and sorcerers.

They grew to become the dominant civilization. 





\subsubsection{Paragons/Imperials}
The \ophidians were individually too weak to challenge the elder races. 
But they had social behaviour, and they had their psionic powers. 
Gradually they learned to take pack cooperation a step further. 
They learned to lend the pack's collective mental power to the leader, allowing the leader to grow much more powerful than an average \ophidian by drawing upon the essence of his pack.
These leaders became known as \emph{paragons}, and their supporters as \emph{vassals}.
This was a form of \emph{\nexus}, with the paragon as an \emph{\apex}. 
In time, the \ophidians also learned that a paragon could act in turn as vassal to a greater paragon. 

The \ophidians discovered that\dash at great cost\dash they could imbue an egg with extra essence and thus breed a prodigy who could wield paragon power to greater effect than a regular \ophidian. 
These \quo{born paragons} gradually became a superior subrace, a ruling caste. 
They came to be known as \hr{Ophidian Imperial}{\emph{Imperials}}.

The \ophidian Imperials \hr{Ophidian immortality}{achieved immortality}. 





\subsubsection{Terrible elder world}
They were the most recent in a long line of civilizations on the planet. 
Almost like \humans in the Cthulhu Mythos. 

Compare to the people of Mu in \cite{HPLovecraft:OutoftheAeons}, who fear Ghatanothoa and other terrible gods and placate them with sacrifices. 

There were mountains and great basaltic pillars wherein dwelt the horrid \hs{flying polyps}. 
There were great areas that the \ophidians dreaded and learned to stay away from.
Even in their time of greatness they feared these relics of an elder age. 





\subsubsection{Wars against the Nibir}
\target{War against the Nibir}
For thousands of years the cruel \hr{Phaetonian}{Phaetonians} used the early \ophidians as slaves or hunted them for sport. 
But the \ophidians fought. 

The fledging \ophidian civilization waged bitter wars against the Nibir and eventually prevailed. 
They destroyed all Nibir and Phaetonians on \Miith. 

Compare this to the wars waged by humanity against the elder races in \cite{RobertEHoward:TheShadowKingdom}. 





\subsubsection[Wars against the Shugul]{Wars against the \moonthings}
\target{Ophidians drive out Shugul}
The \ophidians waged war against the \moonthings and their \moongods.
They destroyed the \moonthings' cities and drove them out.
Soon only the \moonthings' capital of \Nom was left.

Later \hr{Sethicus invades Nom}{\Sethicus invaded \Nom} and built his own temple-city of \Baltherium.





\subsubsection{Wars against the \noggyaleth}
\target{Ophidian-Noggyal wars}
\target{Noggyaleth lose a war before the FBW}
The \ophidians knew that the \noggyaleth existed. 
They did not know the \noggyaleth's true nature, although a few occultists suspected.
The \ophidians feared the \noggyaleth just as they did the \xss, but the \ophidian magic was mostly powerful enough to keep the chaotic, bestial \noggyaleth at bay or even destroy them.
In earlier days, the \ophidians waged great wars against the \noggyaleth and drove them underground.





\subsubsection{Early \ophidian culture}
\target{Early Ophidian culture}
The \ophidians developed culture and civilization early on, many millions of years before \Tiamat. 
But they had the infinite patience of reptiles, so \hr{Ophidians are slow}{they lived very slowly}, due in part to their \hs{torpor}.
Hence their culture also developed slowly. 

At first the \ophidians knew nothing of the \xss except vague legends handed down from prehistoric alien races. 
But they knew of various monstrous gods that dwelt on \Miith, such as \Ubloth. 
These \Miithian gods are comparable to the Great Old Ones of the Cthulhu Mythos, where the \xss are comparable to the Outer Gods. 
The \ophidians lived in fear of the ancient gods and worshipped them. 

They still knew little about the \xss. 
Only hints and myths.
What little they knew, they feared.
Only a few mad cultists worshipped them, and with little success.
\Sethicus was the first who was strong and brave and daring and heretic enough to \hr{Sethicus understands XS}{\emph{understand} the \xss}. 





\subsubsection{Lords of the Deep}
\target{Ophidians against Lords of the Deep}
The \hs{Lords of the Deep} had fought against the \moonthings. 
After the \ophidians had weakened the \moonthings, the Lords of the Deep returned, now more powerful. 
They conquered the planet and enslaved some \ophidians. 

The \ophidians fought back. 
They remembered that they had prevailed against elder races before. 
They vanquished the Lords of the Deep and cast them out, back into the deep sea. 
The \ophidians were now truly the rulers of \Miith. 





\subsubsection{Religion taboo}
After the \ophidians had won their freedom from the Nibir and other elder races, they promised to never again serve or worship a foreign race. 
They had developed a xenophobic distrust of other races after having fought genocidal wars. 
They pledged themselves to the dream of \ophidian supremacy:
The \ophidians should rule and bow to no masters. 

A strong cultural taboo arose. 
It was forbidden to worship anything as a god. 
The \ophidian culture was highly \hr{Ophidian philosophy}{atheistic}. 
It was held sacred that the \hs{Ouroboros}\dash the \caisith people\dash should serve no outsider, and preferably not keep outsider servants either. 

Hence they \hr{Enslaved Ophidian subraces}{created their own \ophidian subraces and enslaved them} instead of employing servitor races. 
Only millennia later, when this taboo had withered away, \hr{Origin of Scathae}{were the \scathae created}. 

They also established a taboo against certain types of sorcery. 
\Sethicus would later challenge that taboo. 





\subsubsection{Ouroboros}
\target{Ouroboros}
The \caisith created the Ouroboros \nexus to make themselves independent of foreign gods. 
The \nexus would safeguard their souls after death and allowed them to wield powerful magic. 










\subsection{Golden age}
\target{Ophidian Golden Age}
\target{Ophidian golden age}
\target{Ophidian civilization}
\index{technology!\ophidian}
The \ophidians{} built a civilization which was great, mighty, proud, enlightened and technologically advanced. 



\lyricstitle{\emph{Call of Cthulhu} RPG p.118}{
  [The Serpent People] built black basalt cities and fought wars, all in the Permian aera or before. 
  They were great sorcerers and scientists, and devoted much energy to calling forth dreadful \daemons{} and brewing potent poisons.
}

\citeauthorbook[p.44--45]{ClarkAshtonSmith:UbboSathla}{Clark Ashton Smith}{Ubbo-Sathla}{
  At length, after aeons of immeroial brutehood, it became one of the lost serpent-men who reared their cities of black gneiss and fought their venomous wars in the world's first continent.
  It walked undulously in antehuman streets, in strange crooked vaults; it peered at primeval stars from high, Bebelian towers; it bowed with hissing litanies to great serpent-idols.
}





\subsubsection{Interstellar civilization}
\target{High-tech civilization}
\target{interstellar civilization}
\index{technology!interstellar civilization}
The \ophidians built an interstellar civilization. 
Using magic and other science, creatures could travel between Realms and through the vastness of space to \cooperate, trade or wage wars. 

\Sethicus \hr{Sethicus brought innovation}{would later help expand this civilization}. 

They built colonies on other planets. 
Here they found remnants of extinct alien civilizations.
Some of the colonies, however, were destroyed when those remnants rose up in vengeance against the \Miithian interlopers.

There were also \hs{living machines}. 





\subsubsection{Wars against the \vorcanths}
After the victories \hr{Ophidians drive out Shugul}{against the \moonthings} and \hr{Ophidians against Lords of the Deep}{against the Lords of the Deep}, the \ophidians fought against the \vorcanths. 
The \ophidians wanted to colonize all the Realms of the system. 
The \vorcanths would not let them. 





\subsubsection{\Ophidian expedition to Visha}
\target{Ophidians invade Visha}
The \ophidians once tried to conquer Visha.
They fled in horror before the horrid and unfathomable \moongods. 
They abandoned the plan to settle Visha. 









\subsection{\Ophidians create subraces and servitors}
\target{Ophidians breed}
They had several entire races as their servants and slaves. 
And they controlled \daemons{}, whom they commanded to build their great cities. 

They learned bio-technology and biomancy. 
They started manipulating other races, breeding and tweaking them. 
They created their own servitor races and animals. 

That was the reason why, later on, there existed so many animal species on \Miith{} that could be domesticated: 
The \ophidians{} had been breeding them, millions of years before. 

Among other things, they helped shape the \hr{Nycan}{\nycans}. 
They also \hr{Ophidians create Nephilim}{created the \nephilim as slaves}. 





\subsubsection{\Ophidian subraces}
\target{Enslaved Ophidian subraces}
The \caisith made several genetically engineered subraces, especially of the Worm caste.
These \caisith variants were mostly enslaved and subjugated. 

Compare to the thunder warriors and astrotelepaths of \emph{Warhammer 40,000}. 





\subsubsection{\Ophidians create \nephilim}
\target{Ophidians create Nephilim}
Perhaps the \ophidians bred the \nephilim as slaves.
The \nephilim would remain slaves until \hr{Origin of Aryothim}{the advent of the \aryothim}. 





\subsubsection{Dreadnoughts created}
The \hr{Dreadnought}{Dreadnoughts} were created. 
They were biomechanical war machines in the shape of gigantic reptiles. 
They were created to fight against the \vorcanths and other enemies of the \ophidians.
And also used in wars between \ophidian nations. 















\subsection{Ramarxes and the Concord}
\target{Concord}
\index{Concord}
\hs{Ramarxes} was a genius \caisith inventor and entrepreneur. 
His great invention was the \emph{Concord}. 
The Concord was a telepathic union allowing all participants to communicate and remain in contact.
The Concord also functioned as a global repository of knowledge and data\dash a telepathic internet. 
A universal \caisith supermind. 

When the Concord was invented, it was quickly adopted and spread across the world. 
It strengthened the \caisith civilization.
It was revolutionary and ushered in a new golden age of marvelous progress and prosperity for the \caisith. 
It allowed them to build stronger \nexuses, so the paragon leaders could grow stronger. 
Ramarxes, as the inventor of the Concord, became the most famous and popular \caisith alive\dash perhaps ever (until \Sethicus). 
He was hailed as a genius and a benefactor\dash but he was also feared. 





\subsubsection{Inspired by Umaja}
Ramarxes had discovered the existence of \hr{Umaja supermind}{Umaja}, the supermind of the \hs{Greatest Race}. 
He had gleaned some insight from its tablets. 
It inspired him to create the Concord. 





\subsubsection{New Concord}
\target{New Concord}
Ramarxes kept developing and refining the technology of the Concord. 
He hungered for personal power and greatness, as did any ambitious \caisith. 
He wanted to be the greatest. 
So he developed \quo{deeper} Concord contracts, which individuals could then enter into (like license agreements). 
This enhanced set of Concord contracts was called the New Concord. 
Gradually, the New Concord became able to extract more and more information from individuals and influence their minds more and more.
More and more, the New Concord became a tool of mind control. 

The development of the Concord and the New Concord took centuries. 





\subsubsection{Ramarxes distrusted}
Ramarxes was not \apex of the entire Concord. 
(The rest of his people would never willingly agree to make him global \apex.)
There were other powerful \apexes, and some had a greater pyramid of vassals than Ramarxes did. 
So Ramarxes did not \emph{look} like the most powerful \caisith in the world.
But Ramarxes understood the Concord better than any other.
He knew many tricks and shortcuts.
So he had a lot of power he could abuse. 

From Ramarxes' perspective, his motives were pure. 
Ramarxes wanted to conquer the other races in the universe. 
He wanted the \caisith to rule the universe\dash and he wanted to rule the \caisith.
He wanted to be the greatest of all, as any self-respecting \caisith would. 
He wanted to be a god, the incarnation of the soul of the \caisith race and their \hs{dweomer}. 

Gradually Ramarxes began to draw on the resources available to him.
It dawned on the rest of the population that Ramarxes was growing more powerful.
By this time the entire \caisith civilization was built around the Concord.
It was virtually impossible to \quo{opt out}. 





\subsubsection{War against Ramarxes}
More and more, people began to distrust Ramarxes. 
Other leaders banded together and demanded that Ramarxes relinquish power.
Ramarxes contended that he was not holding any unlawful power, and that there was nothing to relinquish.

Others began to actively attack Ramarxes and try to force him to relinquish power.
Ramarxes fought back with the weapons at his disposal. 
In doing so, Ramarxes \quo{tightened} the New Concord and utilized its potential for mind control. 
The more Ramarxes fought, the more people began to fear him.
Battle lines were drawn. 
Boundaries were crossed.
It came to war. 

Ramarxes became afraid. 
Afraid of losing everything he had built.
Afraid of being destroyed. 
So he began taking drastic measures.
He delved into dark sorcery. 
As the master of the Concord, he had access to vast resources of knowledge, so he was able to reconstruct ancient outlawed sorceries and perfect them further. 
He descended into darkness. 
And with his power over the New Concord, he dragged the minds of the \caisith race with him down into darkness. 

Horror reigned. 
Many \ophidians succumbed to madness\dash and their madness unleashed alien horrors upon the world. 





\subsubsection{Fall of Ramarxes}
Ramarxes' empire was crumbling, and enemies were at his very door, coming to slay him. 

In his desperation, Ramarxes reached out into the great void searching for power.
He looked to the Umaja Tablets. 
This drove him mad. 

When his enemies found him, Ramarxes was a wretch. 
He was in total despair. 
He laughed madly and made no effort to save himself. 
They slew him. 





\subsubsection{\Sethicus kills Ramarxes}
\target{Sethicus kills Ramarxes}
The team of champions sent to slay Ramarxes included Valcan (\hr{Sethicus}{\Sethicus}) and the parents of \Nexagglachel, \Iscrafel and \Secherdamon. 
Perhaps Valcan delivered the killing blow. 





\subsubsection[Tyrasshana gets Ramarxes' records]{\Tiamat gets Ramarxes' records}
\target{Tiamat get Ramarxes records}
\Tiamat got hold of some records from Ramarxes and his inner circle describing their vision for the Concord and their pain and frustration and sorrow because so many condemned them and tried to destroy them with violence.

At the time\dash after Ramarxes' fall\dash Ramarxes was unpopular.
It would be dangerous to \Tiamat's career (and perhaps her life) to be seen as a Ramarxes sympathiser, so she kept these records secret and told no one that she was reading them. 
She began to greatly respect Ramarxes and came to share his utopian vision. 

























\section{\Sethicus and his research}
\hr{Sethicus}{Valcan} (later known as \Sethicus) was an \ophidian polymath.
He was controversial because he delved into sorceries \hr{Ophidians and XS}{which the \ophidian{} establishment frowned upon}. 







\subsection{Technology and \Sethicus's innovation}
\target{Sethicus brought innovation}
\Sethicus's time was characterized by very fast development. 
\Sethicus was a very impatient and ambitious \ophidian.
He craved more than his race's slow, complacent lifestyle.
He craved action, excitement and renewal.
He was a great scientist who made many inventions.
He inspired many followers to live fast like him. 

\Sethicus himself was a brilliant scientist and made many exciting new discoveries in various fields. 
Later in his life, he became preoccupied with alienist sorcery.
This came to dominate his life and career. 

\Sethicus was a primus motor when it came to pushing the boundaries of space travel and establishing an interstellar \ophidian empire. 
Before him, they had been a spacefaring race for millennia, but rarely ventured beyond their solar system, and they had done no colonization beyond the occasional research station in the solar system. 
\Sethicus made them found settlements on many planets and moons in the solar system and even beyond it, and they began terraforming processes. 





\subsubsection{Energy sources}
\target{Draconian energy sources}
\Sethicus's society required colossal amounts of energy to sustain it.
To procure enough energy they used dark spells to draw energy from the void and the Heart, and they sacrificed vast numbers of humanoids to feed their machines. 

\Sethicus himself helped build this network of power plants.
He used complex black spells which only he fully understood to suck even more energy from the dying universe so it could fuel his \hr{Sethicus plan}{masterplan}. 

Compare to the Immortal Emperor and the Astronomican in \cite{RPG:Warhammer40000}, which requires the sacrifice of countless \humans daily to sustain them.









\subsection[Sethicus and Tyrasshana]{\Sethicus and \Tiamat}
One of \Sethicus's more important allies was \hr{Tiamat}{\Tiamat}. 

Originally she was his assistant and servant.
She followed him around on his journeys and learned much. 

\Tiamat wanted to make the world a better place, lift her people out of warfare and strife, \hr{Enslaved Ophidian subraces}{oppression of Worms} and all-round suffering.
She saw the existing \ophidian oligarchy as decadent and corrupt. 
She saw the dystopia of the \hr{Enslaved Ophidian subraces}{enslaved \caisith subraces} and wanted to change it.
She wanted to seize power and improve the world. 









\subsection{Discovering the \xss}
\target{Sethicus maps the way to Machai}
\target{Star-Maps of the Ancient Cosmographers}
\Sethicus and \Tiamat discovered the \xss{} from some ancient ruins\dash perhaps left behind by the \voyagers. 
Together they charted the cosmic paths leading to the spritual plane of the \xzaishann. 
(These are some of the same paths that Chaos sorcerers would use millennia later.)





\subsubsection{\Ophidian origin}
\target{Sethicus discovers Ophidian origin}
It had been theorized that \hr{Ophidian parentage}{the \ophidians were descended from \xss}. 
It was \Sethicus who really understood the connection. 
He theorized that the \ophidians were related to the \xss.
Perhaps even created by them, or at least evolved from creatures created by them.
\Sethicus believed they had been \hr{Sethicus believes Ruin Satha created Ophidians}{imparted hunger/will/motivation by \RuinSatha, and then physical life by \KhothSell}. 
And he shaped his beliefs into mystical theories that could be used to cast magic. 

\citeauthorbook[p.16]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  A sliver of this transcendent black essence dwells in the darkest part of man's being. 
  Yes, a fragment of this demonic god lives inside every man, allowing him to be part of Greater Reality.
  Because \human reasoning has developed enough to understand unnatural logic, non-Euclidean geometry, quantum physics, string theory, abstract thinking and our holographic universe\prikker we can begin to understand what lurks Outside!
  
  We are the children of the Old Ones, and we are their progenitors.
  A select group of \human beings shall keep the Dark Gods alive in their words, their thoughts, and their deeds. 
  Because of our insane beliefs, a fragment of Greater Reality has Awakened inside us.
  Some liken this to a black flame, twist of Cain, being touched by the hand of God, an alien encounter, a divine spark, mark of Satan, gidt of Set, or call of Cthulhu.
  
  Whatever its name, it exists in the hitherto unexplored areas of our mind like some cyclopean race memory to which we are irrevocably drawn.
  This evolutionary nudge that was given to out species aeons ago allows us to comprehend godlike knowledge and become godlike ourselves. 
  
  \prikker seek out those Those Who Came Before.
  The Old Ones' understanding is carried on through the Cult of Cthulhu.
  Our organization merely tries to uncover Their ghastly, depraved illumination.
  The unknown can be terrifying, but that does not stop us from grasping it. 
  
  \prikker 
  
  The religion of the Old Ones\prikker is based upon the concept of fear.
  The unknown is the heart of both theologies.
  That nameless, black quality which forces the \human imagination to conjure up the richest dreams and the most hideous terror\prikker
  
  Fear that is felt, fear that drives, attracts, repels\prikker fear that is overcome!
  Inside the unknown is out salvation, if we have the courage to look\prikker and then plunge our warlock hands into the unplumbed, inky vortex!
}





\subsubsection{Voyage of discovery}
They explored the cosmos, looking for illumination and arcane knowledge. 

\lyricslimbonicart{Dynasty of Death}{
  I'm launching into the abysmal universe.\\
  Disembodied I enter the cosmic cataclysm.
  
  I discover stairways to celestial dreamscapes\\
  A dark unknown conjunction within an immoral dimension.
  
  Through dark tunnels in levitation, \\
  black cosmic space in manifestation.\\
  I escape the earthly pandemonium\\
  into a vast nocturnal sanctum.\\
  A nemesis for all evil I confess.\\
  My soul bleeds by all the forces I possess\\
  A benediction of unholy wrath and sorrow.\\
  My heart is buried in dark catacombs of horror.
}

They learned the grim truths and secrets of the universe. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  They
  were the words of a great thaumaturgist who had seemingly discovered a
  repository of aeons-old lore detailing the sidereal web of the cosmos, with
  arcane diagrams pinpointing certain astral portals and places of empyreal
  potency, a sort of pangalactic ley-line chart, if you will. 

  [The Thaumaturgist:]\\
  The Great Eye of the Universe opens! \\
  Through this astral art the secrets of the cosmos are mine to know\prikker \\
  for the stars are my dominion!
}

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Everything you have been taugh about the nature of Creation is a lie. \\
  This is a voyage in search of the truth. \\
  It will not be a pleasant journey.
  
  I have discovered a terrifying universal axiom which cannot be denied.
}

They learned of the origin of their people, and all life.

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Betwixt the hammer and the anvil are forged the stars\prikker \\
  On the wings of the ersatz ones\prikker \\
  through the fathomless abyss.
}

They feared this discovery, and the madness that the \xss{} might bring. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Like a blackened and baleful sun shall I gaze down \\
  from beyond the cumuli and the firmament upon you. \\
  I alone must bear the burden of this fiend-wrested lore.
  
  New stars without number burn in the heavens, \\
  but the shadow of oblivion falls ever closer.
}

She discovered a wealth of cosmic knowledge, comparable to the Sith library in the game \emph{Knights of the Old Republic II: The Sith Lords}. 
Also comparable to the tale of the Empyreal Lexicon by Bal-Sagoth. 

\lyricsbalsagoth{Return to Hatheg-Kla}{
  Some would call it epiphany, others would deem it the final descent into madness\prikker whatever the case, the last vestiges of those tenuous palisades which had previously, and blessedly, safeguarded my reason and prevented my mind from accepting the full and staggering magnitude of the naked truth then crumbled, fading into nothingness like the dissolution of a night-mist.\\
  At length, one oppressively miasmic night, with such malefically portentous lore preying pitilessly upon my sanity, I began to descend through a myriad veils of sombre and swirling shades, finally surrendering my grip on wakefulness.\\
  And on that fitful, fateful eve, the last of the dreams came\prikker\\
  A waking dream?\\
  I dare not speculate.}

\Sethicus was excited.
He was beginning to learn the ancient spellwords that would later become known as the \TrueDraconic tongue. 

\citeauthorbook[p.316]{HPLovecraft:TheDiaryofAlonzoTyper}{\HPLovecraft}{%
  The Diary of Alonzo Typer%
}{%
  At last my dreams are to be realised!
  Whether or not my life or spirit or body will be claimed, I shall enter the gateway!
  \ldots
  
  There is beneath this house\dash sepulchred I know not where\dash an ancient forgotten One who will shew me the gateway I would enter, and give me the lost signs and words I shall need.
  \ldots
  Men of this earth know It not, save in the secret whispers of the fear-shaken few who have found or inherited the key.
  No \human eye has ever yet glimpsed It\dash unless, perhaps, the vanished wizards of this house delved farther than has been guessed. 
  
  With knowledge of the symbols came likewise a mastery of the Seven Lsot Signs of Terror\dash and a tacit recognition of the hideous and unutterable Words of Fear.
  All that remains for me to accomplish is the Chant which will transfigure that Forgotten One who is Guardian of the Ancient Gateway.
  I marvel much at the Chant.
  It is composed of strange and repellent gutturals and disturbing sibilants resembling no language I have ever encountered\dash even in the blackest chapters of the \emph{Livre d'Eibon}. 
  \ldots
  
  \ldots
  
  Today dark ominous clouds have hovered intermittently over the circle on the hill.
  \ldots 
  They are snake-like and fantastic, and curiously like the evil shadow-shapes I have seen in the house.
  They float in a circle around the primal cromlech\dash revolving repeatedly as though endowed with a sinister life and purpose.
  \ldots
  Are they indeed those dread Ones whom Solomon knew of old\dash those giant black beings whose number is legion and whose tread doth shake the earth?
  
  I have been rehearsing the Chant that will transfigure the Nameless Thing, yet strange fears assail me even when I utter the syllables under my breath.
  Piecing all evidence together, I have now discovered that the only way to It is through the locked cellar vault.
  The vault was built with a hellish purpose, and must cover the hidden burrow leading to the Immemorial Lair.
  What guardians live endlessly within, flourishing from century to century on an unknown nourishment, only the mad may conjecture. 
  
  \ldots
  
  \quo{The secrets of the monstrous primal Ones,} ran the crabbled text, 
  \quo{%
    whose cryptic words relate th ehidden things that were before man; the things no one of earth should learn, lest peace be forever foreited; shall by never suffer revelation.
    To Yian-Ho, that lost and forbidden city of countless aeons whose place may not be told, I have been in the veritable flesh of this body, as none other among the living has been.
    Therein have I found, and thence have I borne away, that knowlege which I would gladly lose, though I may not.
    I have learnt to bridge a gap that should not be bridged, and must call out of the earth That Which should not be waked or called.
    And what is sent to follow me will not sleep till I or those after me have found and done what is to be found and done.}
  
  \quo{%
    That which I have awaked and bornre away with me, I may not part with again.
    So is it written in the Book of Hidden Things.
    That which I have willed to be has twined its dreadful shape around me, and\dash if I live not to do the bidding\dash around those children born and unborn who shall come after me, until be bidding be done.
    Strange may be their joinings, and awful the aid they may summon till the end be reached.
    Into lands unknown and dim must the seeking go, and a house must be built for the outer Guardians.}
}






\subsubsection{The keys to insight}
In order to summon the \xss{} and invoke their power, \Sethicus-tachi discover that they must find a number of \quo{keys}. 
After a while of searching they finally realize that the \quo{keys} are not physical objects but insights. 

They are told that some of the keys must be captured from their rival races. 
They only manage to do this when they realize that what they are supposed to steal/conquer is knowledge, not artifacts. 

\lyricsbalsagoth{Return to Hatheg-Kla}{
  A terrible sound filled my ears\prikker \\
  an insidious resonance which sent waves of excruciating pain coursing through my mind\prikker \\
  a sound which inexorably coalesced into a recognizable but entirely inhuman voice, a voice which slowly, inevitably, formed approximations of words which I could discern\prikker
  
  [The Crystalline Oracle:]\\
  Hearken, o' manling of the Tellurian orb\prikker the Circle closes.\\
  Perpare to embrace the agony of enlightenment.\\
  Know you of the Six Cataclysms?
  
  [The Aspirant:]\\
  I do. Six times has the world perished and been reborn!
  
  [The Crystalline Oracle:]\\
  You have discovered the true meaning of the six coruscating rings of arcane power?
  
  [The Aspirant:]\\
  Praise Klatrymadon and Zuranthus! The Six Keys!
  
  [The Crystalline Oracle:]\\
  Know you of the blackened orb which burned bright o'er ancient Lemuria?\\
  Know you of the sidereal flame which engulfed the high seat of power in Ultima Thule?\\
  Know you of that martial sorcery woven in the pitiless throng of epic battle?\\
  Know you of the astral power permeating the multiverse and the might of the cosmic codex?\\
  Know you of the rise and fall of glorious Atlantis?\\
  Know you the blasphemies contained within the Chthonic Chronicles?
  
  [The Aspirant:]\\
  I know all this, and more!
  
  [The Crystalline Oracle:]\\
  Have you, o' hybrid child of the cosmos, gazed into the Great Eye of the Universe?
  
  [The Aspirant:]\\
  I have.
  
  [The Crystalline Oracle:]\\
  And what did you see there, young Xerxes?
  
  [The Aspirant:]\\
  I saw oblivion and damnation.\\
  I saw truth, and enlightenment.\\
  I saw the closure of the Great Circle Without End.\\
  I saw the Sixth Great Cataclysm.\\
  I saw the alpha and the omega, \\
  I saw the beginning\prikker and I saw the end.\\
  The end of all there is!
}





\subsubsection{Summoning the \xzaishanns}
\target{Origin of Draecchonosh}
\target{Sethicus contacts XS}
\Sethicus-tachi contacted the lords of the \xzaishanns{} and learn to channel their power. 
They even absorbed some of the \ps{\xzaishanns} souls into themselves, transforming themselves into the mighty \draecchonosh. 

Have a scene where \Sethicus-tachi summon the \xzaishannic{} power, similar to \bandsong{Bal-Sagoth}{Summoning the Guardians of the Astral Gate.}

\lyricsbs{Hate Eternal}{Catacombs}{
  Rise up from the ancient tombs. \\
  Grant us all your infinite wisdom. \\
  Endure as you rise from the catacombs. 
}

\lyricsbs{Hate Eternal}{The Creed of Chaotic Divinity}{
  Awakened by this ancient creed. \\
  Evoked, the ancestry of thee.\\
  Forsaken for centuries of times. \\
  Exiled, all of their kind. \\
  Foretold, the inheriting of the Earth.\\
  Forewarned of this predestined rebirth. \\
  Engaged, the rising from below.\\
  Fear, all mortals, for what they shall bestow.
  
  Conjure all, so that they may sustain\\
  their race, of what they must retain.\\
  Spew forth incantations in vain. \\
  Invocate all that they try to negate.\\
  Enchant all of their wonderful splendour. \\
  Recant all of the texts that are sacred. \\
  Recreate all that has been begotten. \\
  Revive all that has been forgotten. 
}

\lyricsbalsagoth{The Empyreal Lexicon}{
  The key word of Transcendence!\\
  The key word of Transference!\\
  I shall liberate the rightful owners of the Lexicon\prikker\\
  the true rulers of the cosmos!
  
  X'atham-ry'aa! Tha'zai-tonn!\\
  Darker than a score of hells\prikker \\
  wherein astral horrors sublime dwell,\\
  Macrocosmic realms aflame\prikker \\
  Prey of fiends that have no name!\\
  Bow to the gods that have no name!}

The \xss{} are powers of evil whom the \ophidians{} used to fear. 

\lyricsbs{Vital Remains}{Icons of Evil}{
  Confront me now, defiler of human desire.\\
  Voracious hordes await the hour of ascension.\\
  Unravel their delusion,\\
  their translucent divinity.
}

When \Sethicus-tachi first invoke the \xzaishannic{} power, it goes wrong and the \xzaishanns{} wreak immense destruction. 
It takes some time for \Sethicus-tachi to learn to control and channel their power. 

\lyricsbalsagoth{The Voyagers Beneath the Mare Imbrium}{
  Fools! The Darklight Portal has grown strong.\\
  Only one moon remains in orbit.\\
  The mewling ape-spawned humans have discovered the icosahedron and the Lexicon's call can once again be heard throughout the stars, beckoning my ireful brethren to return to the slaughterous embrace of the fray!\\
  We have won! The orb azure is ours\prikker ours to enslave!}





\subsubsection{Guide appears}
\target{Sethicus's guide}
A guiding god appears to \Sethicus-tachi: 
\hr{Achamoth}{\Achamoth}, the messenger of the \xss and the vizier of \RuinSatha. 

He gifts them with knowledge and makes them worship the \xss{} and \Chaos. 
Compare him to Nyarlathotep from \HPLovecraft's stories. 

\lyricsbalsagoth{The Chronicle of Shadows}{
  [The Imperator of the Night \\
  (Hearken to the Attestation of the Sinistrous):]\\
  For it is the iniquity of man which compels him to these tenebrous gates,\\
  seeking opiate dreams and the alluring embrace of oblivion\prikker
  
  Such adoration bestowed upon me beneath the cryptic moon!
  
  (Behold the true purity of that which lurks concealed beneath the mantle of 
  shadow, and let the deluded, debauched sybarites flee in terror from that 
  darkness which they profess to embrace!) 
  
  Beyond the spheres of light and darkness, \\
  beneath distant pallid stars, \\
  I bring the iridescent glimmer of forbidden truth, \\
  seared in the crucible of blasphemy! 
  
  For amorphous they come, steeped in the fetor of ten thousand years, \\
  Abhorrent colossi spawned from the sinistrous cosmic spheres.
  
  And upon their tongues, vile secrets so terrible sweet madness is a redolent balm!
  
  Rejoice and revel in the triumph of the Dark. 
  
  I shall glut the maw of that ineffable nameless evil which lurks forever in the soul of man, for so it is written in the Chronicle of Shadows\prikker
}

\Xserasshana{} receives the \hr{True Draconic}{\TrueDraconic} tongue from the \xss. 

\lyricsauthorbookpage{Anton Szandor LaVey}{The Satanic Bible}{29}{
  Each verse is an inferno, each word is a tongue of fire.
  The flames of Hell burn fierce\prikker and purify! 
}





\subsubsection{Enlightenment}
\Sethicus achieved a great spiritual enlightenment. 
Compare this to:

\begin{itemize}
   \item 
     Randolph Carter's enlightenment in \cite{HPLovecraft:ThroughtheGatesoftheSilverKey}.
   \item 
     Randolph Carter's quest for Kadath and his ultimate ride towards the throne of Azathoth in \cite{HPLovecraft:TheDreamQuestofUnknownKadath}. 
   \item 
     Walter Gilman's dreams of Azathoth and Yog-Sothoth in \cite{HPLovecraft:TheDreamsintheWitchHouse}. 
\end{itemize}









\subsection{\Sethicus's allies}
Among \ps{\Sethicus} other allies were \ApepNesthra and \Iurzmacul. 

They attracted allies by tempting them with power, glory and greatness.

\citeauthorbook[\quo{First Thought in Three Forms}, p.86--100]{%
  BentleyLayton:TheGnosticScriptures%
}{%
  Bentley Layton%
}{%
  The Gnostic Scriptures%
}{
  So, then, hear me O children of thinking; hear the voice of the mother of your mercy.
  For you have become worthy of the mystery that has been hidden since eternities, so that you might [\prikker].
  And the end of this realm and of this violent.
  I am androgynous, a parent with myself alone.
  [\prikker]
  The entirety through me alone. 
  It is I who am the womb of the entirety, giving birth to the light in glory.
  It is I who am the aeon that [\prikker] the completion of the entirely, namely Meirothea, the glory of the mother,
  And I project a voice of the sound into the eats of those who recognize me.
  And I am calling you to enter the superior, perfect light.
  When you enter it you will be glorified by the glorifiers; the enthroners will give you thrones; you will be given robes by the enrobers, and the baptists will baptize you; so that along with glories you become the glory in which you existed, luminous, in the beginning. 
}

The part about \quo{in the beginning} refers to the idea that \hr{Ophidians related to XS}{their pre-history is connected to the \xss}. 










\subsection{Worshipping the \xzaishanns}
At first, \Sethicus and his fellows retained the \ophidians atheism and merely consorted with the \xss. 
Later they began to admire them more. 
As time went on, they became addicted to the power that the \xss could bring, and the began to worship them in earnest. 

\lyricsbs{Exmortem}{Sovereignty}{
  Admiring the triumphant demonthrone, \\
  sealed with the knowledge of time.\\
  Magic runes are carved here.\\
  Will you ever find the key?\\
  The bound demon in the earth\\
  is waiting to be released.
  
  He has \travelled beyond the worlds.\\
  He has danced with death.\\
  Now he controls it all.\\
  With strength he suffered.
}





\subsubsection{\Sethicus understands the \xss}
\target{Sethicus understands XSS}
At this time the \ophidians still knew little about the \xss. 
Only hints and myths.
What little they knew, they feared.
Only a few mad cultists worshipped them, and with little success.
\Sethicus was the first who was strong and brave and daring and heretic enough to \hr{Sethicus understands XS}{\emph{understand} the \xss}. 

In order to do this he needed to understand the truth about the \hs{dead universe}, which was an indescribably awful truth that the \ophidians dared not face or even contemplate, even though their occult philosophy and science had by now given them sufficient hints to suspect it. 

This \emph{understanding} was something \Sethicus needed.
Only then could he begin to truly draw on the power of the \xss.
Only then could he envision the \TrueDraconic tongue and map out the \draconic theory of magic.







\section{\Sethicus (\yds{Sethicus creates Dragons})}
\subsection{\Dragons are created}
\target{Origin of Dragons}
\target{Sethicus creates Dragons}
\Sethicus became the first \dragon.
\Tiamat become the second.

\target{Dragons use Dreadnoughts}
Using their advanced gene-technology and psychometabolism and \Sethicus's \xsic{} sorcery, they designed a race of \ophidian{} super-warriors. 
They fused their own \ophidian bodies and minds with those of mighty \hs{Dreadnoughts}, infused with all the \xsic{} ferocity they could conjure up. 
A number of \ophidian{} warriors volunteered to be transformed into these new superbeings. 

When the experiments where at last successful, the result was huge, flying monsters: 
\Dragons. 

The \dragons were the first \hs{True Immortals}. 

The \dragons{} enslaved legions of \daemons{} that previously served the \xzaishanns. 
They turned their gaze on \Miith{}, bent on conquest.

\lyricsbalsagoth{The Voyagers Beneath the Mare Imbrium}{
  My power is absolute\prikker greater even than that of Angsaar himself!\\
  I shall crush the Tellurian sphere,\\
  and the flaccid lickspittles who strive in vain to safeguard it!\\
  Yes\prikker The dreaming is over!\\
  Now, let the vengeance begin!}

This newfound power corrupted them into chaotic, \daemonic{} beings. Twisted by the \xzaishannic{} souls within them, they almost became \xzaishanns{} in \ophidian{} form. 





\subsubsection{\Tiamat was the founding mother}
\Tiamat became the founder of the \draconian race.
She had a vision of a race of mighty super-\ophidians.
She convinced \Sethicus to help her in this endeavour.
Later ages would remember \Sethicus as the father of the \draconian race, but it was actually chiefly \Tiamat's project.
(The \dragons of later days did not like to remember \Tiamat because of \hr{Tiamat mutates}{the monster she later became}.)





\subsubsection{\Dragons lose much in the transition}
The \dragons gained much wisdom, power and pleasure when they became \dragons. 
But they also lost much of their sanity, humanity, gentleness and the calm, rational philosophical disposition that \hr{Ophidian philosophy}{had been their trademark}. 

In a sense it was a fall from grace. 
But only very few \dragons saw it this way. 
\Iurzmacul and \Nexagglachel were pretty much the only ones. 
Only much later would \Ishnaruchaefir come to share their views.





\subsubsection{Later someone discovers it}
Later in the series, I should have a story arc where someone discovers the truth of \Sethicus-tachi and their research. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  \prikker a fantastic and somewhat 
  horrifying dream in which I traversed a great black cyclopean cityscape,
  its towering stygian walls inscribed with some form of outlandish glyphs which
  seemed to writhe squamously and alter their shape even as I gazed at them.
  \\
  A sibilant whispering which seemed at once familiar and yet intrusively alien
  compelled me to walk to the edge of a particularly sinister looking edifice
  and peer out over its precipitous perimeter. 
  \\
  When I did so, I beheld this
  world of ours, recognizing vaguely the apparent shapes of the five continents,
  yet the entire vista seemed so distant that the whole appeared in its entirety
  no larger than a sphere which I could fit snugly into the palm of my hand.
  \\
  When I turned again to behold the looming obelisks, I found I could then
  easily read the previously untranslatable ciphers in the black stone. 
  \\
  They
  were the words of a great thaumaturgist who had seemingly discovered a
  repository of aeons-old lore detailing the sidereal web of the cosmos, with
  arcane diagrams pinpointing certain astral portals and places of empyreal
  potency, a sort of pangalactic ley-line chart, if you will. 
  \\
  Indeed, these
  Star-Maps of the Ancient Cosmographers seemed to take a not insignificant 
  toll on the author's sanity, as evidenced by the tone of his inscriptions, which
  seem to suggest that in discovering this Pandora's Box of dark elucidation,
  his fate was to be inexorably dogged by some nameless and implacable gloom
}









\subsection{Some see the \xss{} as evil}
Some \ophidians{} see the \xss{} as a terrible evil that must not be allowed into the world. 

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\prikker 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}












\subsection{War against the Gods Beneath}
Perhaps the \hs{Gods Beneath} awoke and attacked the \ophidians at this point. 
This was just when \Sethicus and his cohorts were achieving enlightenment. 
\Sethicus and his \dragons rose up and defeated the Gods Beneath.















\section{Conflict against \Sethicus}
\target{Draecchonosh war}
It came to armed conflict between the \dragons and other other \ophidian factions. 
Some of the other \ophidians{} were swayed by the \psp{\dragons} power and glory and joined them, while others were repelled by their brutality and evil. 
The \dragons{} waged war against their fellow \ophidians{}\prikker and the world.





\subsubsection{Religion}
The rebellion was religious in character. 
\Sethicus and his cohorts fought for their mystic beliefs.
His opponents fought for their materialistic, atheistic beliefs and saw \Sethicus as a dangerous fanatic and madman. 

\citeauthorbook[p.80--82]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  Only the cosmic horror that comes from the worship of oozing, malevolent monsters from vast and sprawling dimensions can set man on the right path.
  The Old Ones are the road to madness, destruction, and truth.
  
  Endarkenment is the opposite of enlightenment.
  The light strives to make the illusion real. 
  In darkness, Cthulhu Cultists shall have reality naked and exposed. 
  
  \prikker
  
  Purification will begin when the Cult of Cthulhu has taken over the world.
  Those who are biologically closer to the Old Ones will fully transform into their accurate conformation.
  That which was \human shall be cleansed; the eldritch beast is resurrection from the shadow that has learned to walk in Hell.
  The demonic soul is freed!
  
  \prikker
  
  Respect the laws of your land until the apocalypse begins.
  When Cthulhu Cultists number in the thousands, the balance of power will begin to shift.
  When the stars align, our bilious green and slimy inquisition shall be unleashed. 
  Death to all who oppose us!
}





\subsubsection{\Sethicus's ambition}
\Sethicus had \hr{Sethicus plan}{a mad plan}.









\subsection{\Nexagglachel and his brothers}
\target{Nexagglachel-tachi in their youth}
\Nexagglachel and his brothers were alive at this time. 
Their parents\dash weakened after having produced three powerful sons\dash perished in the last great war. 
The three sons were powerful and accomplished adults by the time Valcan and \Tyarith made their discoveries. 

\Raemyth (later \Nexagglachel) was now a lord. 
He was a warlord with dreams of kingship and conquest. 

Quessanth (later \Iscrafel) \hr{Iscrafel's early history}{fought for his brother as a champion}.

Irocas (later \Secherdamon) was a gentle artist and composer. 
He desired only be allowed to produce and perfect his art for its own sake. 













\section{\Sethicus reigns}
\Sethicus became the spiritual leader of the \ophidian empire and also amased vast secular power. 
He appeared obsessed with science and religion and would often seem to neglect and ignore the welfare of his people (not only mortals but also \ophidians and \dragons) for the sake of his mystical ambitions. 
This was actually because of his \hr{Sethicus plan}{plan to save his race from False Life}. 
His intentions were good, but his means were brutal, and he was not good at explaining his reasons. 
The wiser he became and the further his epic plan progressed, the more inhuman and alien and incomprehensible his mind became to his fellows, and the more he became estranged from them. 









\subsection{\Nom and \Baltherium}
At \Achamoth's encouragement, \Sethicus conquered the land of \Nom. 
At the time \Nom was one of the last bastions of the \moonthings on \Miith (after the \ophidians \hr{Ophidians drive out Shugul}{had driven them out}). 
With their newfound sorcerous power \Sethicus and his companions defeated the \moonthings and their monstrous allies (such as the Weavers) and conquered \Nom. 

He then proceeded to build the gigantic fortress-city of \hr{Baltherium}{\Baltherium}, built upon ancient \moonthing ruins and drawing upon the \dweomers of captive \moongods. 
(Read about \Baltherium and \Nom.)









\subsection{\Dragon wars}
\target{Dragon wars under Sethicus}
Even in \Sethicus's time there were great and bloody wars fought between factions of \dragons.

Some of these conflicts sprung from ideological or religious differences. 
One would think that \Sethicus ought to know the \quo{correct} religion, but he did little to stop these conflicts. 
In fact, he almost seemed to be encouraging them. 
This helped make \Sethicus unpopular. 
People became convinced that he was insane.
% This eventually led to the \hs{Durance}. 

For millennia these wars raged. 
They caused serious damage to the planet.
They tore open dimensional wounds through which monstrous powers could seep in. 
\Miith became bathed in the evil \xs energies that the \dragons unleashed. 
These evil energies caused living creatures to mutate, spawning hideous monsters. 
Some of these monsters would found races that would continue to plague the \wylde tens of thousands of years later.

The \wylde spread uncontrollably.















\section[Tyrasshana]{\Tiamat}









\subsection[Tyrasshana as a Dark Messiah]{\Tiamat{} as a Dark Messiah}
\Tiamat{} is a \trope{DarkMessiah}{Dark Messiah} kind of character. 
She wanted to bring enlightenment to her people. 
But the awful knowledge she discovered (including the \hr{Umaja}{Umaja Tablets}) twisted her and alienated her from her people, so that she might easily appear insane and evil. 

In her life, \Tiamat saw again and again the cruelty that the \caisith were capable of.
Even though theirs was a highly enlightened society with great ideals of progress and freedom for all, their world always had a dark underside, and everywhere (in all strata of society) there were those who were willing to commit horrid atrocities in the name of questionable ideals or simple personal gain. 

\Tiamat also \hr{Tiamat get Ramarxes records}{studied Ramarxes' diaries} along with historical records. 
She became convinced that Ramarxes, with his Concord project, was really on the path to fixing the \caisith society and saving their race. 

\Tiamat studied the social sciences and the causality of history (psychohistory). 
She saw that the more people were isolated from one another, the more they treated each other with cruelty. 
\ta{%
  Where there is separation, there is conflict and suffering. 
  To have peace and happiness we must have unity.%
}

She came to disagree with Valcan. 
In her years spent with Valcan as her mentor, \Tiamat would sometimes probe to see if Valcan shared any of her Ramarxian ideas. 
Valcan rejected most of Ramarxes' philosophy. 
He believed that \caisith civilization was moving in the right direction and that the system, for its flaws, was overwhelmingly a positive thing that must be preserved against subversive/revolutionary menaces. 
\Tiamat argued that he thought that way because\dash for all his virtues\dash he was part of that system and therefor part of the problem.
He was a noble and unwilling to acknowledge the fundamental and pervasive \emph{wrongness} of his social class and the social order that made their lifestyle possible. 

This disagreement drove a wedge between \Tiamat and Valcan. 
\Tiamat concluded that she could not truly trust Valcan and that his conception of right and wrong was different from hers. 
From her point of view, Valcan was still governed by the causality of psychohistory, isolation and group loyalty. 
She, on the other hand, had experienced what it was like to be a slave, as well as a leader. 
She was wiser.
The ruling class hated and feared anything that was potentially more powerful than them and hence a threat to them. 
(Compare to how humans in real life fear artificial intelligence.) 
The aristocracy turned against Ramarxes.
\Tiamat predicted that the aristocracy would turn against her as well when she tried to pursue her ideals. 
\Tiamat saw the aristocracy's protests against her as something understandable and predictable but \emph{wrong}. 
As she saw it, they fought her out of causality, and she would have to destroy them out of necessity. 

She would finish what Ramarxes started. 
She would create the \hs{New Concord}. 
She would destroy the old system and all its horrors. 
She would bring unity.
She would bring a better world. 
This new world would be worth \emph{any price}. 





\subsubsection{Cult}
\Tiamat began to preach cryptic apocalyptic mysticism. 
Some dismissed her teachings as nonsense. 
No one understood what she meant, but it was evocative and seductive.
It rang true because it was based on truth.
Many joined her.
Some of her followers read the Umaja Tablets. 
(Some completely lost their minds from reading the tablets.)

Compare to Horus from \emph{Warhammer 40,000}.

\Tiamat became a Lucifer-like figure and founded a powerful and destructive cult, like Morathi's Slaanesh-cult in \emph{Warhammer}. 
\Tiamat's cult became so powerful and so destructive that other \dragons had to wage war against them and destroy them.





\subsubsection{\Tiamat{} hears voices in her head}
Perhaps \Tiamat{} hears voices in her head, voices who are actually various figments of her mind and imagination. 
They question her principles and tempt her into perversity. 

Compare to the scenes in \authorbook{Graham McNeill}{False Gods} where Horus, in dreams, meets a phantom masquerading as his companion Sejanus. 





\subsubsection{\Tiamat{} worships the \xss}
\lyricsdimmuborgir{Relinquishment of Spirit and Flesh}{
  King of tempests and storms!\\
  Lord of innumerable figures and forms!\\
  Blessed with thy cold I am,\\
  as I upon the shoulders of mine\\
  bear the burden of Thine.
  
  Once I got touched by a fire from beyond,\\
  an invitation to darkness of which I could not resist.\\
  Caressed by the feathers of the fallen,\\
  I took the fate in my hand.
  
  Revealing Thy powers in visions and dreams.\\
  Invoking your magic at night.\\
  Honoured I am to mission Thy word.\\
  Within a creed is sworn of majestic might.\\
  An infernal allegiance in which I pay my share.\\
  An unholy awakening inside of which I intend to bear.
  
  Possesses by the true god of Earth I am.\\
  Possessed for eternity.
}

She becomes evil. 

\lyricsdimmuborgir{The Serpentine Offering}{
  My descent is the story of everyman.\\
  I am hatred, darkness and despair.
  
  Evoked and entertained through centuries.\\
  Wrathful and sullen. Dormant still.
  
  The ferocity pervades everywhere,\\
  waiting to be released at last.\\
  Hear my offering, ye bastard sons and daughters.\\
  Share my sacrifice.\\
  Share my sacrifice.
}

\lyricsdimmuborgir{For the World to Dictate our Death}{
  Let us sit by and watch \\
  Death and destruction's devotees revel. \\
  Let us sit back and witness \\
  innocent semen being poured\prikker
  
  Into the arms of Armageddon. \\
  Let it pour, more and more. \\
  Pure fucking Armageddon. \\
  Let it pour, more and more.
}

\lyricsbs{Marduk}{Legion}{
  A new era will arise \\
  as I see the black angels of the abyss fly\\
  and the demons come storming in the silent cloudless sky\\
  with their burning eyes of ripping evil.
  
  I am given strength from a thousand sinners that dwell \\
  in the everlasting, burning, roaring depths of Hell. \\
  With the demons the possess my blackened heart and soul\\
  I shall strive for Satan's triumph and reach infernal goals.
  
  Children of darkness, raise your blood-filled cups \\
  to our father with horns.\\
  In eternity, we shall blaspheme the one \\
  who was tormented with thorns. 
  
  Feel the darkness growing when we draw near.\\
  My name is legion, for we are many in here.
  
  Heaven shall burn accompaigned by the angels' cries.\\
  We shall invert paradise.\\
  Death to peace!
}

She preaches to her followers of a \daemonic{} paradise. 

\lyricsdimmuborgir{Allehelgens D\o{}d i Helveds Rike}{
  Utspente vinger over M\o{}rkets dype svelg.\\
  Satt til verden for \aa{} meske seg med pest og d\o{}d.\\
  Fr\aa{}tsende i synd og hor.\\
  Overmakten fra p\o{}lens bastarder\\
  n\ae{}rer behag i syndens hierarki.\\
  Et evig liv i Paradis\\
  er fullkommenhet i Satans dynasti.
}

She seduces them to follow her. 

\lyricsdimmuborgir{Cataclysm Children}{
  Are you born from the abyss,\\
  and have you sought the creed \\
  that drape the shadows\\
  of your own thought?
  
  Is your heart mesmerized \\
  by the fire that burns forevermore?\\
  And do the secrets from the flames \\
  hold the mysteries over which you preside?
}

They have become forever corrupted by the \xss:

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Sola Fide
}{
  Verily I say unto you, \\
  there is none righteous enough to resist, no, not one\prikker\\
  For your hands are defiled with blood, and your fingers with iniquity;\\
  Your lips have spoken lies, your tongue has muttered perversity.\\
  The heart of a lost angel is in the earth, \\
  the immaculate is abased\prikker forevermore.
  
  Sola Fide. Sola Deo Infernali Gloria.
  
  Neither stormful convulsions \\
  nor an apex of light shall break the yoke\\
  For he that keepeth His commandments \\
  dwelleth in him, and He in him.\\
  And hereby we know that He abideth in us, \\
  by the Spirit which He hath given us
}





\subsubsection{Some \dragons become bitter}
Some \dragons, after tying themselves to the \xss, become bitter and evil. 

\lyricsdimmuborgir{For All Tid}{
  Hver en t\aa{}re er frosset.\\
  V\aa{}r sjel er lenket.\\
  V\aa{}rt hat er blodig.
  
  All glede er svunnet.\\
  All latter er forstummet.\\
  Alt liv skal ende i d\o{}d.
  
  I et kalt og \o{}de landskap\\
  skal den sorte horde tre frem.\\
  V\aa{}r herre skal stige opp for all tid, \\
  reise sitt rike igjen.
  
  N\aa{} er tiden kommet.\\
  Ja, knus de godes ord.\\
  La oss for alltid bli herskere \\
  p\aa{} denne jord.
}









\subsection[Tyrasshana's civil war]{\Tiamat's civil war}
\Tiamat turned against her fellow \dragons and wanted to seize power for herself.
This resulted in a vast civil war between the \dragons, for \Tiamat was charismatic and turned many \dragons to her side.
Of all the devastating \dragon wars this was the worst. 

\target{Tiamat kills Hesod-Nerga}
\HesodNerga{}, the great \ophidian{} hero, protested against his daughter's embracing this thoroughly evil power. 
Some of the \ophidians{} tried to \quo{save} \Tiamat, believing her brainwashed and possessed by the \xzaishanns{} against her will, and sought to exorcise the \daemons. 
They were dismayed to realize that \Tiamat{} was \trope{NotBrainwashed}{Not Brainwashed}. 
She responded by slaying \HesodNerga. 








\subsubsection{\Tiamat mutates}
\target{Tiamat mutates}
\Tiamat changed her physical body into a horrible monster. 
An almost amorphous mass of flesh and black slime, with several hideous heads. 





\subsubsection{Infrastructure}
\Tiamat build up a great infrastructure of \nexuses, \vertices and focus points for the \draconic civilization.
When she was defeated, this infrastructure remained. 





\subsubsection{\Sethicus defeats her}
\target{Sethicus versus Tiamat}
At this time, \Sethicus had secluded himself in his sanctum in \hr{Baltherium}{\Baltherium} and explored the spiritual universe in a deep meditation that lasted years. 
So we was absent during most of \Tiamat's rebellion and civil war. 

Eventually \Sethicus awoke from his meditation. 
He saw her as having gone mad and out of control, so he opposed her.
\Sethicus took leadership of the forces arrayed against \Tiamat. 

Ultimately \Sethicus defeated \Tiamat, but he himself was destroyed in the process.

\target{Tiamat imprisoned}
Everyone now believed that \Tiamat was destroyed, but in reality she was only banished. 
\Sethicus could not destroy her. 
She lived on as a shadow, now embittered and hateful. 
\Sethicus imprisoned her essence in a nightmare dimension, impaled and left rotate for all eternity while contemplating the stars and the universe.
Compare her to the god Yibb-Tstll from the Cthulhu Mythos. 









\subsection{\Sethicus is defeated}
\target{Sethicus betrayed}
Eventually, his fellow \ophidians, unable to understand his actions, decided that \Sethicus had gone mad and rebelled against him. 
Even \dragons joined the rebellion, including many of the younger ones. 
The ones that stayed loyal were mostly older ones. 

The rebels might include \Iurzmacul, \Nexagglachel and perhaps even \Ishnaruchaefir. 

After a long, violent insurrection, \Sethicus was defeated.
But his \dragons were immortal.
Far more so than the natural \ophidians.

The \ophidians lacked the sorcery to destroy them. 
Or if they knew how, they refused to use it on principial grounds because it was destructive sorcery and would corrupt their people and lead them on a sliding slope towards the \xs, which would be the end of their enlightened civilization.

\target{Sethicus imprisoned}
So they imprisoned \Sethicus-tachi instead.
They were interred in vast tombs and bound with fearsome spells and seals to prevent them from rising and claiming their revenge.
There they lay for thousands or millions of years.
\Nexagglachel was \hr{Nithdornazsh was Nexagglachel's tomb}{entombed in \Nithdornazsh}. 
Sometimes attended by living or undead monstrous servants (like the ones in \Nithdornazsh).

\target{Durance}
\index{Durance}
The imprisonment and entombment of the \dragons was also called the \quo{Durance of \Sethicus}, occasionally the \quo{Durance of the \Dragons}.

Later the \dragons \hr{Sethicus and his Dragons resurrected}{would be brought back and freed}. 





\subsubsection{Some \dragons disagreed with \Sethicus}
Not all \dragons agreed with \Sethicus's aggressive, warlike manner and his plans of conquest. 
\Nexagglachel was one of his critics.
\Nexagglachel was always calm and benevolent and thought of the future of the people (\ophidians as well as lesser races), whereas \Sethicus was mostly focused on his own greatness. 

When \Sethicus and \Tiamat were defeated and entombed, many of the remaining \dragons, convinced by \Nexagglachel, willingly stepped down and let themselves be entombed.
There they could lie and think and explore. 
(Many of the \dragons were scientists and philosophers who had been attracted by \Sethicus's free thinking.)

They felt sure that their time would come again, some day in the future. 









\subsection{\Ophidians adopted \Sethican technology}
\Sethicus built magical machines based on the secrets and energies of dark gods. 

\target{Ophidian technology set back after Sethicus}
The \ophidians began to base their technology on \Sethicus's sorcery. 
Then, when \Sethicus fell and went into Durance, their technology began to fail, because only the \dragons had the occult knowledge and raw power to keep everything working. 

The \ophidians tried to revert to their older forms of technology, but they found that the many ecological and arcane disasters of the last period had made this impossible. 
They were screwed. 
This set back their technology by millennia, and it took them forever to recover. 

\target{Ophidians worship machines}
Some of \Sethicus's machines still worked.
The \ophidians were now very dependent on these relics, since their old infrastructure was destroyed. 
But no one remained alive who understood how they functioned.
The machines came to be worshipped as objects of religion.

A \hr{Incursion hurts Ophidian technology}{similar setback} struck the \ophidians after the \Resphan \hs{Incursion} when the \resphain \hr{Resphain destroy world tree}{destroyed their world tree}. 





\subsubsection{\Nithvezurun and the living cities}
The \hr{Ophidians worship machines}{mysterious machines which the \ophidians now worshipped} included the living cities. 
Some of these cities became invested with \ophidian souls and became sentient. 
A living city could absorb/merge with several \ophidian souls and thus become super-intelligent and super-powerful.

After the loss of \Sethicus the cities began to grow chaotically and out of control.
They mutated into twisted nightmare jungles of flesh and metal, life and death. 

One upon a time there was a city named \Nithvezurun. 
Its machine-network merged with an \ophidian mind and became intelligent. 
Over time more and more \ophidians merged with their city's mind, and \Nithvezurun grew in power. 
\Nithvezurun was fairly peaceful and innocent, but it grew so powerful that other \ophidians feared it, so they banded together and waged war against \Nithvezurun and destroyed it. 

After this war the \ophidians made a taboo against creating thinking machines or hiveminds.
The \ophidians were xenophobic and feared to place power in non-\ophidian hands.
Any powerful thing must be controlled by an \ophidian mind.





\subsubsection{Everything slow again}
\Sethicus's time was \hr{Sethicus brought innovation}{characterized by very fast development}. 
After \Sethicus's fall, \ophidian progress once again slowed to a crawl. 
The colonies were either abandoned or became sleepy, unambitious things. 





\subsubsection{\Ophidians could not contain the \wylde}
\target{Ophidians cannot contain the Wylde}
In the \hr{Dragon wars under Sethicus}{bloody \dragon wars in \Sethicus' time}, the \wylde had grown out of control.
Now, with the loss of the \dragons' power and sorcery, the remaining \ophidians were unable to contain the \wylde.
They lost control of most of the planet and retreated behind the walls of their cities.

\Miith became a world of islands.
It never recovered again.
Never again would it become an enlightened world of civilization. 

See also the section about \hr{History of the Wylde}{the history of the \wylde}.









\subsection{Some \ophidians followed \Sethicus}
\target{Ophidians follow Sethicus under Durance}
After \Sethicus's Durance had begun, some \ophidians chose to follow his teachings and carry on his dark religion in secret. 
Later they would \hr{Cultists want to free Sethicus}{advocate freeing \Sethicus}. 

Other \Sethican cultists joined their \draconian masters in Durance, either voluntarily or forcibly. 
They later \hr{Undead Ophidians}{returned as undead mummies}. 




\subsubsection{\Sethican writings survive}
After \Sethicus was forced into \hs{Durance}, some \hr{Sethican writings}{writings containing the original words and theories of \Sethicus} regarding \hr{Sethican philosophy}{his philosophy} survived. 
These were treated as sacred by the surviving \Sethican cultists. 















\section{War against \Shuggon}
\target{Shuggon}
\index{\Shuggon}
The \ophidians still had their interstellar civilization. 
Eventually they discovered the world of \Shuggon. 
(This was probably after \Sethicus was laid in durance, but it might also have been before.)

\Shuggon was not a planet \emph{per se}. 
It was a cloud of planet-fragments and great air-filled caverns and swirling spaces and vortices. 
It was inhabited by a race of gigantic moth-like beings, comparable to the monsters Battra from \cite{Movie:GodzillaVsMothra} and Megaguirus from \cite{Movie:GodzillaVsMegaguirus}. 
The \ophidians waged a long war against these monsters.
The \ophidians lost and were eventually forced to retreat from \Shuggon. 
But passageways had been opened. 
In later ages, the spawn of the moth-things from \Shuggon would sometimes return to plague \Miith. 

The name \quo{\Shuggon} is taken from \cite{HPLovecraft:TheBlackTomeofAlsophocus}. 














\section{The \FirstBanewar (\yds{First Banewar begins})}









\subsection{The \bane{} invasion}
\target{Banes come to Miith}
\target{First Banewar}
\target{FBW}
\target{Banes come to Miith in spaceships}
\index{\firstbanewar}
The \banes \hr{Banes are created}{had been created on the world of \Erebos}.

And so it came to be that a \baneking{} (whom the \dragons{} would later came to call the \quo{\Voidbringer}) succeeded in opening a great dimensional portal from \Erebos{} to \Miith{}. 
Through it he sent forth millions of his \bane{} warriors to conquer and claim the new world in his name. 

The \banes{} came to \Miith{} flying in vast spaceships. They \hr{Why the Banes want Miith}{had their reasons for wanting \Miith}. 
They had flown all the way from \Erebos{}, a journey of hundreds or thousands of years. 

The people of \Miith{} were taken unaware when, on the Eve of the Black Gate, a massive rent opened in the sky and myriads of fiendish \bane{} warriors surged forth to conquer and destroy. 
Millions of \bane{} warriors and beasts, and hundreds of \banelords, all led by Daggerrain himself, invaded and attacked the \draconic{} kingdoms. 
Many millions perished in the initial assault and whole continents were laid waste before the \ophidians{} were able to muster their forces in defense. 
The Eve of the Black Gate marked the beginning of the \Banewar, the most terrible and devastating war that \Miith{} has seen since the \Kraken{} Queen last returned to her sleep. 

The \banes{} fought against the \ophidians{} in what became known as the \firstbanewar. 
They invaded with millions of \bane{} warriors and terrible magic. 





\subsubsection{\Noggyaleth remain neutral}
\target{Noggyaleth remain passive in the FBW}
The \noggyaleth had remained passive in the \firstbanewar. 
They were not highly intelligent. 
It took a long time for the \banes to get through to the \noggyaleth and form some kind of alliance. 
Until then, the \noggyaleth stayed hidden. 

Besides, the \noggyaleth were not stupid.
\Banes and \ophidians were bombarding the surface of the planet.
The \noggyaleth had a sense of self-preservation and did not want to expose themselves to that inferno.
Especially after \hr{Noggyaleth lose a war before the FBW}{having recently lost a major war}. 






\subsubsection{Technology at the time}
\target{FBW technology}
\index{technology!\bane}
When the \banes invaded, the \ophidians had an interstellar civilization.
They commanded dozens of planets. 
The \banes \hr{Interstellar Bane empire}{likewise had an interstellar empire}. 
But \Miith was the important planet that they had been searching for all along. 
It contained a Heart full of \voyager-tampered energy, and the \noggyal \hs{mother-mass}, which was the \quo{other half} that the \banes wanted. 

The war lasted centuries. 
At last the \ophidians were overwhelmed by the \bane hordes, so they retreated to their homeworld and barricaded it with the \CrystalSphere. 
The \banes conquered all their other planets. 

Both sides used weapons of \hr{Weapons of mass destruction}{mass destruction made with black magic}. 
And \hr{Living machines}{biological machine monsters}. 

The \ophidians had higher technology than the \banes. 








\subsection{\Sethicus resurrected}
\target{Sethicus and his Dragons resurrected}
The \ophidians realized they were not winning this war.
If they wanted to win, would need the help of \Sethicus and his \dragons, \hr{Sethicus imprisoned}{whom they had previously imprisoned}. 

\hr{Sethicus}{\Sethicus} was controversial because he used \xs-based sorcery (\hr{Ophidians and XS}{which the \ophidian{} establishment frowned upon}), but now the other \ophidians{} realized they would need every weapon at their disposal to defeat the \bane{} invaders. 
So after much negotation (first amongst themselves, then with \Sethicus), the \ophidians released the \dragons. 

The imprisonment and entombment of the \dragons was also called the \quo{\hs{Durance} of \Sethicus}, occasionally the \quo{Durance of the \Dragons}.




\subsubsection{\Sethicus made them resurrect him}
Maybe it was \Sethicus himself who made the first move. 

\Sethicus lay entombed, but not unconscious.
He realized the \banes were invading.
So he reached out telepathically and touched the minds of \ophidians.
He was deeply buried and bound with fearsome spells, so it was not easy for him.
He could only send unclear visions and messages.
But his mental power was formidable, and he was able to compel the \ophidians to release him.
This would have been impossible at any other time, but now they knew they needed him and his \dragons, so it was easy to convince many powerful \ophidians to come and release his seals.





\subsubsection{Cultists want to free \Sethicus}
\target{Cultists want to free Sethicus}
There were some \hr{Ophidians follow Sethicus under Durance}{\ophidian cultists who had carried on \Sethicus's religion}. 
It was they who argued that \Sethicus should be freed. 





\subsubsection{Resurrection caused problems}
\Sethicus then went to work releasing his fellow \dragons.
It took a lot of magic to resurrect them, for their souls had been away for a million years and were no longer accustomed to living in a physical body.

They awakened many, but not all.
Some slumbered too deeply and could not be reached.
Others refused the call.

Some of the \dragons had wandered the Realms of the \xss. 
Others had simply lain there thinking, developing new philosophy and science and magic.
Some of the resurrected \dragons did not want to be resurrected and went mad.
Their minds had become twisted into inhuman, \xs-like monsters.

\citebandsong{Nile:Ithyphallic}{Nile}{
  The Essential Salts
}{
  It is a great shock to the soul\\
  To tear it back from its resting place and reanimate it\\
  The resurrected are often insane and scream ceaselessly \\
  or dash themselves into walls
}

When \Sethicus came to awaken the \dragons, he also found that many had chosen to leave their bodies behind permanently and could not be resurrected.
Others had perished for various reasons.
Some refused \Sethicus's call and remained asleep. 
These would remain \hr{Aloof Dragons}{aloof} for a long time. 





\subsubsection{\Sethicus lets \Nexagglachel sleep}
\target{Sethicus lets Nexagglachel sleep}
There were yet other \dragons whom \Sethicus deliberately let sleep.
This included his three sons.
It is possible that \Sethicus knew there was a great risk that the \dragons who fought in this war would be destroyed. 
He wanted some \dragons to live on so they could awaken at a later date and reclaim \Miith, thus carrying on his legacy.
\Sethicus was wise and saw far.

It is known that he did some work to weaken the seals on their tombs so that the brothers would later awaken on their own.
He rigged some spells that would awaken \Nexagglachel some thousand years later.
Beside \Nexagglachel, \Sethicus also set up some other powerful \dragons (whom he sort-of trusted) to wake up. 
He wanted to be on the safe side and not rely on \Nexagglachel alone.
For all \Sethicus knew, something nasty might happen to \Nexagglachel in mean time, so he wanted a backup plan. 





\subsubsection{\Sethicus fights}
During the war, \Sethicus-tachi unleashed more \daemons{} and more \xzaishannic{} power than ever before. 
This nearly tore the planet apart, and might even have killed the Heart itself. 

Perhaps the \banes{} feared that. 
The \banes{} might be more keenly aware of the Heart of \Miith{}, since their entire quest revolves around it. 
The \ophidians, on the other hand, had dwelt on \Miith{} for millions of years, and the Heart has always been there, so they might not have paid much attention to the peril their magic posed. 

\lyricstitle{\SETolltheHounds{} p.107}{
  \prikker in the north sky something terrible was happening. 
  Lurid slashes like a rainbow gone mad, spreading in waves that devoured darkness. 
  Was it pain that strangled the very air? 
  Was it something else burgeoning to life, shattering the universe itself?
  
  \prikker he could see the city, the roofs like the gears of countless mechanisms, gears that could lock with the sky itself, with all creations. 
  Such was Kharkanas, First Born of all citites. 
  But the sky had changed. 
  The perfect machine of existence was broken\dash\emph{see the sky!}
  
  The city trembles, the roofs now ragged-edged.
  A wind had begun to howl, the voice of the multihued light-storm as it lashed out, flared with thunderous fire. 
}

Maybe move some or all of \ps{\Kserasshana} \quo{awakening} to \Sethicus. 





\subsubsection{\Dragons fight}

The war song of the \dragons: 
They revelled in their power and fury, their ability to cause destruction and fear.

\citebandsong{Nile:RamsesBringerofWar}{Nile}{
  Ramses Bringer of War
}{
  Wretched Fallen one of Khatti\\
  Rise against the oppressing Sword\\
  Encircled Abandoned Alone\\
  I Smite the vile Hittite Foe

  My Father Amon what carest Thee\\
  For the Vile and Ignorant of God\\
  My Father Amon what carest Thee\\
  For these Effeminate ones\\
  At millions of whom I groweth not Pale

  Raging like Menthu like Baal in his Hour\\
  Lo the mighty Sekhmet is with Me\\
  I enter in among them even as a hawk striketh\\
  I slay I hew to pieces and cast to the ground\\
  The royal snake upon my brow\\
  Spits forth Fire in the face of mine enemies\\
  And Burneth their Limbs
}





\subsubsection{\Cregorrs{} are created}
\target{Origin of Cregorr}
The \dragons{} were full-fledged \ophidians, altered for war. 
But the \ophidians{} also wanted servitor warriors. 
So at approximately the same time they worked to create a race of warrior servants. 
This became the \cregorrs.  









\subsection{The \CrystalSphere}
\target{Crystal Sphere}
\index{\CrystalSphere}
The \ophidians{} received help and knowledge from the \xss{}. 
Using this magic they were able to forge a mystic seal between the worlds, severing the connection to \Erebos{} and preventing the \banes{} from drawing power from their homeworld and its \dweomer. 

\Sethicus-tachi built a vast \CrystalSphere, a cosmic shell of \quo{ice} encasing all of Mith and its Heart. 
Thus they captured the \banelords, who were caught and frozen in the ice. 

The \CrystalSphere{} was a whole mini-Realm of ice in its own right. 
The \banelords{} became trapped there. 

The \CrystalSphere was based on the \hr{Palisades}{\pps{\Voyagers} Palisades}. 
The \ophidians had some limited understanding of the \voyagers' work, and they drew on it.
They built the \CrystalSphere to patch up the holes in the Palisades that the \banes had made.

With the \pps{\banes}{} leaders and power source gone, they were weak, and the remaining legions of \bane{} warriors were easily slaughtered. 

Maybe this seal works as a huge-ass cosmic \hr{Storm beacon}{storm beacon}. 

The \xs{} \hr{Naath-Kur-Ramalech}{\NaathKurRamalech} was very important in building the \CrystalSphere. 

\Daggerrain{} would later draw on the \CrystalSphere{} to weave the \hr{Shroud of Girigor}{Shroud of \Numah}. 
So \hr{Shroud and Crystal Sphere}{the Shroud is tied to the ice}. 

Compare to the devils in the manga \cite{NagaiGo:Devilman}, who are also frozen in ice. 





\subsubsection{No spaceships and no interstellar civilization}
\target{Crystal Sphere isolates Miith}
One might think that even though the \CrystalSphere{} prevented the \banelords{} from going to \Miith{} by dimensional means, they should be able to fly there in spaceships. 

But no. 
The \CrystalSphere{} also kept spaceships out. 
It acted like a huge-ass \hs{storm beacon}. 
In fact, the sorcery wrought through \NaathKurRamalech{} completely enclosed \Miith{} and made it inaccessible from the outside. 
It constricted and strangled \Miith{}. 
It was one of the causes of the \hr{Heart weakened}{weakening of the Heart}. 
The Shroud made it worse, of course. 

The \CrystalSphere also prevented the \Miithians from establishing any interstellar or interdimensional civilization.

It would be possible to attack the Sphere from the outside with magical weapons. 
But that would be very risky. 
Such an attack might easily damage or even destroy the Heart of \Miith. 
No, the Sphere had to be unravelled from the inside. 









\subsection{The fall of \Sethicus}
\target{Sethicus dies}
\Sethicus used a spell that drew upon the \matrix which united all \dragons.
His spell succeeded, and the \banes were banished from \Miith. 
But \Sethicus sacrificed himself and was destroyed. 
Many \dragons perished with him.





\subsubsection{Durance}
The remaining \dragons realized that \Sethicus's spell had weakened the Heart and that they could not live on \Miith any longer.
They chose to go into Durance until such a time as the Heart would again be able to support them. 

Those \dragons who refused to go into Durance would sicken, waste away and die over the course of the next centuries. 
Most \dragons eventually saw reason and went into Durance. 





\subsubsection{\Sethicus-tachi die}
Eventually \Sethicus fell, but his corpse was preserved.

\Sethicus fell and was seemingly destroyed in the \firstbanewar.
He overloaded his body with power and could not resurrect.
He was believed lost.
Out of respect for his heroism, they took his body and enshrined it in \hr{Baltherium}{\Baltherium}, where it was \hr{Elder Dragons worshipped}{worshipped as a dead god}. 

But \hr{Sethicus became a god}{\Sethicus's soul lived on as a disembodied god}.

















