\chapter{\ResphanWarsBook}
\section{The \Dragons}
\subsection{\Ishnaruchaefir{} and \Secherdamon{} split}
After the \hr{Fall of Nexagglachel}{fall of \Nexagglachel}, \Ishnaruchaefir{} and \Secherdamon{} had a falling out and went their separate ways. 

\Secherdamon{} was obsessed with Chaos, the \xzaishanns{} and the \firstgendragons. 

\Ishnaruchaefir, on the other hand, did research on the Darkness and the origin and nature of the \bane{} and \resphan{} peoples. He had lots of \hr{Ishnaruchaefir and Baelzerach}{dealings with the \Baelzerach} and learned much of the Darkness from them. 

This is one of the reasons why he became so dark. 

\lyricstitle{Zeratul from \cite{VideoGame:Starcraft}}{
  You speak of knowledge, Judicator. 
  You speak of experience. 
  I have journeyed through the darkness between the most distant stars. 
  I have beheld the births of Negative Suns and borne witness to the entropy of entire realities. 
  Unto my experience, Aldaris, all that you have built here on Aiur is but a fleeting dream. 
  A dream from which your precious Conclave will awaken, to find themselves drowned in a greater nightmare.
}





\subsubsection{\Ishnaruchaefir{} absent}
\Ishnaruchaefir{} left \Miith{} and took no part in the \resphanwars. 

As such, he \emph{does not appear} in this book, unless there are scenes taking place in the Mirage Asylum and other exotic places. 






\subsubsection{\Ishnaruchaefir{} resented for leaving}
Many \dragons, not only \Secherdamon, resented \Ishnaruchaefir{} for leaving and \quo{abandoning} his people.
They felt he should have stayed when his people needed him and taken on the role of leader in \ps{\Nexagglachel} stead. 
But \Ishnaruchaefir{} did not feel up to the task. 
And he needed time away from everyone after the \SecondShrouding, which was traumatic for him. 









\subsection{\ps{\Secherdamon} rise to power}
\target{Secherdamon's rise to power}
After the \hr{Death of Nexagglachel}{death of \Nexagglachel} and the great \secondbanewar, \HriistD{} burned with ambition, and with his determination, ruthlessness and cunning he quickly rose to power in the \draconic{} hierarchy (to the extend that a such existed).

After cursing \ps{\Ishnaruchaefir} treachery, \Secherdamon{} decided that the aftermath of the \secondbanewar{} was his great chance. 
He was happy that \Ishnaruchaefir{} had had the decency to run away. 
In \ps{\Secherdamon} mind, his self-important brother very much deserved to fall from grace, after trying to set himself up as \dragonlord. 

\citebandsong{Emperor:Prometheus}{Emperor}{He Who Sought the Fire}{
  Towards the heavens he did aspire.\\
  Now he shall burn who sought the fire.
}

\Secherdamon{} will not mourn. 
He will seize his chance. 
His time for greatness has come. 

\citebandsong{Emperor:Prometheus}{Emperor}{He Who Sought the Fire}{
  Some will mourn the ashes cold,\\
  while others behold the inferno unfold.
  
  Now he shall burn who sought the fire,\\
  to manifest another.
}


This left \Secherdamon{} as one of the mightiest \dragons{} around. 

I need to tell a detailed back story with \Secherdamon{} as the protagonist. 
He has flaws, but rises above them. 
We see the adversity he faces, and his determination and courage, and we love him. 
Compare him to Zurra from \bandalbum{Bal-Sagoth}{The Power Cosmic}, but sympathetic.

In order to claim the mystic power that he coveted, he needed  knowledge and artifacts. 
These he took by force and treachery, waging war and slaying his fellow \dragons{} and \ophidian{} to obtain what he needed.





\subsubsection{Motivation}
He finds his motivation and grows strong of will.

\lyricsbalsagoth{Arcana Antediluvia}{
And so it was written \\
that rage would carry him like a howling wind, \\
leaving only frozen corpses,\\
their bones rattling in hollow armour, \\
to tell their tale in his wake.
}

He wants to restore the \dragons{} to their rightful position of overlordship. 

\lyricsbs{Hate Eternal}{King of All Kings}{
  As I am I reclaim the throne of all creation. \\
  As I shall be annointed king. \\
  For thy strength I must sustain.\\
  For thy dominion I shall proclaim.
}





\subsubsection{Seeking allies}
He slew other \dragons, including those mightier than he, and somehow stole their \vertex{} power by necromancy. 
Compare this to the power of Boris Dragosani in \authorbook{Brian Lumley}{Necroscope}.

\target{Secherdamon sacrifices Dragons}
He did not \hr{soul-eating}{devour their souls}, because \hr{Dragons do not eat Dragons}{that would be taboo}. 
But he sacrificed their souls to the \xss. 
Perhaps the \xss{} then granted him their \vertex{} power. 

He also seeks out allies. He wants old and powerful \dragons{} and \ophidians{} to help him. One especially great and powerful one rejects him. They fight, and \Secherdamon{} loses. But later he returns and exacts his revenge. 

\lyricsbalsagoth{Callisto Rising}{
  [ZURANTHUS:]\\
  Do not seek to threaten me, wormcast.\\
  My tenure here is preordained\ldots{}\\
  and I will suffer your arrogance no longer, little brother.\\
  The power of the Lexicon is not destined\\
  to be possessed by one such as you. Be gone!
  
  [CONDEMNED SOULS OF THE BROTHERHOOD OF DARK ELUCIDATION:]\\
  Bipolar nebula! A falling star! The gate yawns wide above eon-veiled Mu\ldots{}
  
  [ZURRA:]\\
  V'aan-ayth'ultaa, No'maal-pha'guus\ldots{}\\
  Damn you, Zuranthus\ldots{} You will pay dearly for this outrage,\\
  I swear it by the blackened maw of the sacred Z'xulth!
}





\subsubsection{Stealing artifacts}
\target{Secherdamon steals weaving artifacts}
And he steals several \hs{weaving artifacts}, killing their original owners and usurping their power. 

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{
  The incantation of Xuk'ul is known to me, \\
  the Orb of Summoning earned with bloodshed! \\
  The crystalline key to the Outer Realms and the arcane rite to empower it are at last mine, seized at swordpoint from the citadel of the Black Templars.
  
  And the central stone of the ancient ebon ring begins
  to pulsate with a darksome energy\ldots{}
}





\subsubsection{Invocation of power}
\target{Rissit invokes dark gods}
\HriistD{} performs a dark, occult ritual, summoning the \firstgendragons{}, \xzaishanns{} and cosmic gods (see section \ref{Cosmic gods}), seeking to gain their wisdom and power. 

\lyricsbs{Bal-Sagoth}{
  As the Vortex Illumines the Crystalline Walls of Kor-Avul-Thaa
}{
  By Klatrymadon and Zuranthus, \\
  such ancient secrets we discovered\\
  in these sinistrous, worm-worm pages.\\
  Etched with darksome glyphs and sigils, \\
  bound with fearsome spells. \\
  An eldritch tide of stygian sorceries \\
  unfettered by the forbidden Tome of Shadows\ldots{}
  
  Now thunderous cataclysm befalls the gleaming Kor-Avul-Thaa.\\
  (The mystic gate stands open!) \\
  The Xytaxehedron held to the stars\ldots{} \\
  the incantation uttered with eager tongues\ldots{} 
  
  (What long-shackled powers of the elder dark have our conjurings loosed?)
  
  By Klatrymadon and Zuranthus, \\
  the vortex blackens the stars above.\\
  A vast plague of amorphous horrors \\
  descends to rend with fang and talon.
}





\subsubsection{Calling upon dark powers}
He calls upon the ancient \ophidian{} lords, who are primordial natural forces and dormant rulers of \Miith{}.

\lyricsbalsagoth{
  Into the Silent Chambers of the Sapphirean Throne (Sagas from the Antediluvian Scrolls)
}{
  Winged dragon coiled in thrice,\\
  bane of flame in shadowed ice.
  Flooded by the bloated Moon,\\
  awake o' worm and quit thy tomb!
}

He invokes dark names.

\lyricsbs{Bal-Sagoth}{
  Summoning the Guardians of the Astral Gate
}{
  Ka-kur-ra, I summon thee,\\
  Zul'tekh Azor Vol-thoth.\\
  Mighty Xuk'ul arise,\\
  Kur'oc Gul-Kor, come forth.
  
  I hold aloft the pulsing orb.\\
  Astral spheres empower the mystic key.\\
  Ring of elder stones entwined in prophecy,\\
  the Rite of Invocation enthralls thine power.
  
  Lucent beams lancing forth from gleaming Cepheid stars.\\
  A creeping mist ensorcels my tongue\ldots{}
}





\subsubsection{Obtaining power}
He is granted power far greater and more sinister than ever before. 

\lyricsbs{Bal-Sagoth}{
  Summoning the Guardians of the Astral Gate
}{
  Replete from drinking deep of darkness\ldots{}
}

He becomes almost a \quo{\Tiamat{} junior}. He summons hordes\dash or entire races\dash of \mdaemons{} to serve him.

\lyricsbs{Bal-Sagoth}{
  Summoning the Guardians of the Astral Gate
}{
  Black shapes dancing 'twixt the stars.
}





\subsubsection{Conquering his enemies}

He becomes powerful, so that even other \dragons{} fear him. He is spoken of in legends as a terrible force.

\lyricsbalsagoth{Arcana Antediluvia}{
  His gaze is as fire, \\
  his words are as spear-points, \\
  his voice is as thunder, \\
  his touch as the plague!
}

He seeks out his foes.

\lyricsbalsagoth{Arcana Antediluvia}{
  And one night, there came a storm, \\
  a storm with searing red winds.\\
  Fire and steel rode within it, \\
  and vengeance writ in thunder and blood.\\
}

He called down curses and spells of destruction upon his enemies.
See the section on \hr{Magic visuals}{magic visuals}, especially \hr{Curses of destruction visuals}{curses of destruction}.


He conquers and crushes his enemies, and it is at last his turn to laugh.

\lyricsbalsagoth{The Empyreal Lexicon}{
  Kur'oc! Gul-Kor! \\
  I have won\ldots{} bow, yield, kneel! \\
  Darken the sun\ldots{} Narra, Gorra, Kaasha! \\
  I arise\ldots{} bow, yield, kneel! \\
  Parhelion dies\ldots{} Narra, Gorra, Kaasha! \\
  I can taste the sweet ichors of omni potency upon my lips\ldots{}\\
  Let it begin! \\
  X'atham-ry'aa j'aiigh! \\
  Tha'zai-tonn nax'a-gorrha!
}

\lyricsbalsagoth{Callisto Rising}{
  [ZURANTHUS:]\\
  Stray not into my darksome embrace,\\
  lest I grind my jaws on your soul.
  
  [CONDEMNED SOULS OF THE BROTHERHOOD OF DARK ELUCIDATION:]\\
  Spare us your wrath, great one, we beg thee.\\
  Begot of the thunder\ldots{} spellbinder. Callisto Rising!
  
  [ZURANTHUS:]\\
  Behold my godhood\ldots{} and pray!
}




\subsubsection{Sacrificing them for more power}
\Secherdamon rose to power in a way that \hr{Narkiza's rise to power}{would later be mirrored by \Narkiza}.
Not by eating his enemies directly, but by sacrificing them to the \xss and being granted power in return.
This amounted to the same thing, allowing him to dodge draconic taboos.
\Secherdamon remembered this similarity when he sponsored \Narkiza.

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  Unas, Slayer of the Gods
}{
  Unas Hath Ingested Their Spirits\\
  Hath Feasted On Their Immortality\\
  He Hath Consumed their Shadows\\
  Unas The Slayer of the Gods\\

  Unas The Sekhem Great\\
  The Sekhem of the Sekhemu\\
  Unas The Ashem Great\\
  The Ashem of the Ashemu\\
  Behold Orion\\
  Unas Riseth
}





\subsubsection{Death and rebirth}
\target{Rissit's death and rebirth}
In order to fully absorb his new power, \HriistD{} must die and be reborn. 
He is a son of the god of Death, after all. 

This is necessary to unlock his true potential as a son of Death. \Ishnaruchaefir{} went through a similar thing (see section \ref{Ishnaruchaefir's death and rebirth}), but \HriistD{} was initially to scared to do it. 

This is kind of a darker, more evil version of the Babylonian myth of Ishtar's death and rebirth. 

Perhaps it is a theme that \Secherdamon{} was originally somewhat weak and cowardly, but later in life acquired the immense determination and ambition that let him become one of the mightiest creatures on \Miith{}. 





\subsubsection{Witnesses to the ritual}
\Nzessuacrith{} helps \Secherdamon{} from the beginning, being disappointed in her father for seeming cowardice and abandoning his people. She participates in his empowering ritual. 

Describe it in a flashback!

\lyricsbs{Bal-Sagoth}{
  Summoning the Guardians of the Astral Gate
}{
  A great stillness binds the moon-cloaked mountaintop in glooming shackles\ldots{} \\
  High above, the myriad stars gleam bright against the night sky,
  three more resplendently bedazzling than the others, their sidereal auras engulfing the stones\ldots{} \\
  And the central stone of the ancient ebon ring begins to pulsate with a darksome energy\ldots{} \\
  A thunderous maelstrom ablaze with writhing celestially spawned power then rends the stygian night\ldots{} \\
  A vast shimmering aperture, a vortex of heliacal fire\ldots{} the pathway to beyond beckons!\\
  The Astral Gate is open\ldots{}\\
  The Guardians have awakened\ldots{}
}

Someone important (not \Ishnaruchaefir, though) watches from a distance and discusses the situation with someone. 







\subsection{\Secherdamon{} goes to war}
\Secherdamon{} goes to war wielding his new terrible powers. 

\lyricsbs{Arcane Wisdom}{Maelstroms of Majestic Night}{
  Torrents of blasphemous fire enrage forth, \\
  thus allowing my soul to devour \\
  feeblish souls with sickening power, \\
  as the ancient warcrafts proudly descend from the North. 
  
  Dwelling in the depths of midnight horizons, \\
  endless realms of darkness. \\
  Benight'd by the Third Moon, \\
  through dismal soil, eternally I wander. 
  
  Such pure Nightly evocative magick\ldots{}
  
  I have sworn on the whoracle of the damned\\ 
  to forever raise my fist to the sky. \\
  A thousand sorcerers I summon'd \\
  on my forest way to the hellish Kulthay.
  
  Oh the blood of my foes and fiends. \\
  How I beheld thy corpses, \\
  raptur'd by virulent winds. 
}














\section{The \resphanwars}
\target{Resphan Wars}
\target{Resphan wars}
After the \secondbanewar, \resphain{} and \dragons{} alike fought on with all the spite they could muster\dash against each other, and internally. For thousands of years. Both sides had lost great leaders in the war and were now divided, left in chaos. Their civilizations declined. 









\subsection{Dynasties wage war}
\target{Dynasties split}
After the \hr{Shrouding}{\Shrouding}, the \banelords{} were locked out again. 
They now had little power over \Miithian{} affairs. 
They could still communicate, but only with difficulty. 

The \banelords{} were gruesome \trope{CosmicHorror}{Cosmic Horrors}, and the \resphain{} feared them. 
They feared and loathed \emph{contact} with the horrible \banes{} more than they feared the punishment that would be their \emph{if} the \banes{} were to one day return in force. 
Many \resphain, believing the \banelords{} were gone for good, ignored them and blocked them out and refused to obey their commands (\hr{Resphan cannibalism}{patricidal bastards that they were}). 

(Only the \banelords{} were gone. 
\Lesserbanes{} continued to serve the \resphain, but the \resphain{} never allowed them to evolve into \banelords.) 

Only few \resphain, like \hr{Azraid}{\Azraid}, remained \quo{loyal} to the \banelords. 

With the \banes{} and their leadership gone, the central organization of the \resphan{} empire crumbled.
The \resphain{} splintered into several dynasties and began to war amongst themselves. 
It was a big free-for-all. 

At first there was \hs{Cabal}. 
\hr{Cabal formed}{That came later}. 
There was no \quo{Cabal bloc}, and all dynasties had shifting alliances and enmities. 





\subsubsection{\Kezerad}
\Kezerad was not particularly the \quo{odd man out}. 
They sometimes allied with the other dynasties. 

\target{Tiphred-Serah and Kezerad ally}
The \TiphredSerah{}, being \hr{Tiphred-Serah free-thinking}{the most free-thinking of the dynasties}, were the ones most liable to ally with \Kezerad. 





\subsubsection{\Mystraacht}
\target{Mystraacht dominance during Resphan Wars}
For a long time during the \resphanwars, \Mystraacht{} was the most powerful of the dynasties. 
They had the most capable warriors and generals, but they were also \hr{Mystraacht not diplomatic}{the least diplomatic}. 

They relied on military power alone and eventually got many enemies against them. 
This was one of the things that \hr{Mystraacht betrayed}{felled them in the end}. 





\subsubsection{\TiphredSerah}
\target{TiphredSerah in the Resphan Wars}
In the beginning, the \TiphredSerah were doing good in the wars.
They were pragmatic and always ready to ally with whomever convenience dictated.
They rode the winds of fortune and were sneaky and opportunistic. 

But in the end this tactic backfired.
Eventually no one trusted the \TiphredSerah.
No one would ally with them for fear of being betrayed soon after. 
Everyone began to hate \TiphredSerah.

They lost some wars and lost many members.
After this, the kept a low profile. 
From now on, \TiphredSerah was one of the smallest dynasties. 
They would never recover. 









\subsection{The \satharioth{} try to break the curse but fail}
Time and time again the \satharioth{} try to break free of \hr{Curse}{\NexagglachelsCurse}, but fail. 

\lyricslimbonicart{The Yawning Abyss of Madness}{
Again I drift the halls of wondering. \\
The black castle of solitude. \\
On the very edge of sanity \\
in mental cryogenic interludes. \\
I have slipped into the seventh, \\
the seventh circle of Hell, \\
in realms where deadly shadows \\
infest every cell. 

Internal ceremonies in ritual death. \\
External bleedings for the demon of madness. \\
Hide from the torture of the dazzling light. \\
The demolition voice shall speak tonight. 

While I'm staring down into the darkest pit, \\
an ocean black as the night, \\
so infinite deep and consuming, \\
it swallows all life force with might. 

Again I drift the halls of wondering, \\
as I focus for the darkness to come. \\
In anguish minds uplift the conquering \\
to cross the line of death beyond.

An abstract reality and bottomless insanity. \\
To search for the powers to please\\
the subconscious spirit of disease. \\
Time found no remedy, \\
cause winds of darkness was stealing me. 

The yawning abyss of madness. \\
A cryptic slaughter by hate. \\
Darkness is the only survivor \\
as evil dominion terminates. \\
The yawning abyss of madness.
}









\subsection{Mortal armies come into fashion}
Originally, the master races did not send armies of mortals into battle. That was not cost-effective, since mortals were nigh-worthless when pitted against the master races.  

But after the cataclysmic \secondbanewar, the \dragons{} and \resphain{} had become critically decimated, and it would take them many millennia to recover their numbers. Their slave races were also decimated, but they could be replenished far faster. So suddenly it began to pay off to raise armies of mortals for war. 

In the beginning, these mortals were outfitted with terrible \hr{technology}{high-tech weapons} and magic, but this turned out to be too dangerous, so after the adoption of the \hr{Charade}{\charade}, this practice was abolished. 









\subsection{\Sathariah{} bloodlines dominate}
The \resphan{} people saw three horrible wars: The rebellion, the \secondbanewar{} and the \resphanwars. 
%Many, many \resphain{} were slaughtered in the rebellion
All this bloody fighting wiped out most of the number. Above it all, the \satharioth{} stood victorious, with their allies and blood-kin at their side. 

Their houses and bloodlines came to dominate the \resphan{} race, and today most \resphain{} have some \sathariah{} blood in them. This makes \hr{Curse}{\NexagglachelsCurse} all the more potent. 










\subsection[Mystraacht falls]{\Mystraacht{} falls (\yds{Zachirah death})}
\target{Mystraacht betrayed}
The \Mystraacht{} were the most adept among the dynasties at utilizing the power of \chaos{} and combining it with the \erebean{} power of the \banes. 
So they were the strongest, and none of the other \resphan{} kingdoms, nor even the \dragons, could stand against them. 
They might even have conquered the planet, were it not for treachery. 
For \hr{Zachirah}{\Zachirah}, the Overlord of \Mystraacht{}, was betrayed, by forces inside the dynasty as well as outside it, and he was assassinated. 





\subsubsection{\Shiaraid{} betrays \Zachirah}
\target{Shiaraid betrays Zachirah}
\hr{Shiaraid's tragedy}{\ps{\Shiaraid} tragedy} was \NexagglachelsCurse, which forced her to destroy herself and those she loved. 
One person she loved was her father, \Zachirah. 

Somehow the Curse turned them against one another. 
She did not mean to, but her destructive impulses made her betray him and be instrumental in his downfall. 





\subsubsection{\Zachirah{} dies}
\target{Zachirah dies}
When \Zachirah{} was finally killed, he ordered his \hr{Zachirah's slave Resviel}{slave \resviel} to give him their life force to sustain him. 
They did so willingly, sacrificing their souls in the process. 
(Life drain is \hr{Voluntary drain}{more effective if it's willing}.)
But to no avail; he still died. 

When \Zachirah{} realized he was doomed, he cast a desperate spell that destroyed his soul, causing it to explode. 
He would rather destroy himself than let his enemies consume his remains. 

His enemies were shocked. 
\ta{Only a madman would destroy his own soul,} they thought. 
But some of them sensed a trace of \ps{\Nexagglachel} savage essence in \ps{\Zachirah} eyes in his last moments. 
They speculate if \hr{Curse}{\NexagglachelsCurse} played a part. 

Several princes now fought for the legendary Throne of \Mystraacht, but none was able to prevail. The dynasty crumbled in internal struggles for power and was diminished. 





\subsubsection{Ramiel defeated at sea}
\target{Ramiel defeated at sea}
Ramiel had a traumatic defeat in a naval battle which spelled the end of his career and spurred him on to \hr{Malach project}{become a \Malach}. 
It also gave him \hr{Ramiel fears the sea}{a fear of the sea}. 

\target{Ascaril destroyed}
During this ill-fated battle, Ramiel's sword, \hr{Ascaril}{\Ascaril}, is shattered and destroyed. 

Ramiel is killed, but only temporarily. 









\subsection{The \Malach{} Project (\yds{Malach fiasco})}
\target{Malach project}
The \Malach{} project started as a secret underground gathering of \resphain{} who were disgruntled with the dynasties. 
They had been dishonoured and felt betrayed. 
So they wanted to be \uber{} and show the others how great they were and how much glory they deserved, and thus claim their rightful places and power. 

The \banelords{} supported them. 

They envisioned the \Malach{} project. 
It was supposed to be the successor to the \sathariah{} project and transform them into super-powered \uber-\resphain. 





\subsubsection{\Azraid}
\target{Azraid masterminds Malachim}
Unbeknownst to all, \Azraid was monitoring the \malach project from the very beginning. 
He did not mastermind it, but he did influence it, and he had a good idea of what they were doing. 
For him, \hr{Azraid turns Malachim into Neo}{this research was a precursor} to his own \hr{Neo-Resphan}{\neoresphan} project. 

Later \Azraid \hr{Captive Malach}{captured a \malach} for research. 

Even later, he managed to \hr{Ramiel becomes Neo}{turn the awakened Ramiel into a \neoresphan}. 




\subsubsection{\Malach{} cannibalism}
\target{Cannibal Malachim}
\index{cannibalism!\Malachim}
Just as the \satharioth{} grew strong by consuming \Nexagglachel, 
the \malachim{} were to derive their power from stolen and subsumed \resphan{} souls. 
It had been known for a while that the \resphain{} were meant to devour others of their kind to survive and grow, but the \malach{} project aimed to take this to its utmost consequence. 
Each \malach{} was to become a walking \carcer, a deep well of souls, and of \emph{power}. 

To achieve this, they had to capture, kill and devour \emph{many} \resphain{}.
(They endeavoured to victimize their own enemies as much as they could.
Ramiel-tachi, after their fall-from-grace, had many such enemies.)
That is why the project had to be kept such a secret and operate underground.  
The dynasties would destroy them if they knew. 

They called down curses and spells of destruction upon their enemies and ate them.
See the section on \hr{Magic visuals}{magic visuals}, especially \hr{Curses of destruction visuals}{curses of destruction}.

The \malachim became powerful by eating their fellow \resphain.
In this they remained true to the spirit and purpose of the \resphan race. 
More so than their enemies, they boasted.

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  Unas, Slayer of the Gods
}{
  Unas Hath Taken Possession of the Hearts of the Gods\\
  Unas Feedeth on their Entrails\\
  He Hath gorged on their Unuttered Sacred Words\\
  He Hath Assimilated the Wisdom of the Gods\\
  His Existence is Everlasting

  Behold The Souls of the Gods are in Unas\\
  Their Spirits are In Unas\\
  The Flame of Unas in Their Bones\\
  Their Shadows are With their Forms
  
  Unas is Rising\\
  Hidden, Hidden
}



\subsubsection{It went wrong}
But someone had gotten word of their plan and wanted to thwart it. 
Sentinels and Cabalists alike infiltrated their group and fucked up the spells and research. 
\hr{Curse}{\ps{\Nexagglachel}{} ghost} also played a part (some of the prospective \malachim{} were \satharioth). 

% The spells were very expensive and difficult to carry out. 
% So instead of doing just one test run they decided to risk it and make several \malachim{} at once. 
% One of the \satharioth{} stepped up and claimed that he/she was not afraid and wanted to be part of the first batch. 
% This made the others fight over the remaining places. 
% So in the end, it was the most powerful ones that went first. 
% (Some also feared that if the weaker ones were transformed into \uber-powerful \malachim, they might strike back at their previously-more-powerful brethren and betray them when they had the chance, before the \satharioth{} could go through the ritual and surpass them again.)
At first, it seemed to go well. 
When he first \malachim{} came out on the other side, they had new and enhanced powers. 
Their new powers were erratic and difficult to control, but they had no reason to assume that this was anything but an issue of practice and experience. 

So they carried on and created more \malachim. 
One of the \satharioth{} stepped up and claimed that he/she was not afraid and wanted to be part of the first batch. 
This made the others fight over the remaining places. 
So in the end, it was the most powerful ones that went first. 
(Some also feared that if the weaker ones were transformed into \uber-powerful \malachim, they might strike back at their previously-more-powerful brethren and betray them when they had the chance, before the \satharioth{} could go through the ritual and surpass them again.)

Some days later, it started going wrong. 
The \malachim{} began to suffer from side effects. 
They were prone to amnesia, manic behaviour and disease. 
Gradually, over a course of days, they wasted away mentally and physically, until they died. 

The rest knew that the dead \malachim{} were not destroyed, but their souls had grown faint and Shrouded and were difficult to track. 
Later the remaining next-of-kin discovered that the \malachim{} were being reborn with amnesia as \humans{} (later called \hs{Scions}). 

There were many more who wanted to become \malachim, but sinced it went so wrong, the spell was never repeated. 
They did more research and tried to fix the flaws, but they did not succeed, so they soon abandoned the project and returned to their dynasties, defeated. 





\subsubsection{\Cishiel{} wanted to join}
\target{Cishiel wanted to be a Malach}
\hr{Cishiel}{\Cishiel} wanted to join the \malach{} project and be part of the first generation. 
But Ramiel forbade it. 
She was still a young girl, and his only heir. 
He did not want to see her put in harm's way. 

She was bitter. 
But after it all went wrong she had to admit that he was right. 

In the days when the \malachim{} were going mad, it was horrible for the young \Cishiel{} to witness her father, the mighty Ramiel, wasting away and degenerating into a maddened wretch. 
She was now very grateful that he had forbidden her to partake. 





\subsubsection{They lose their memory}
The \malachim{} lose their memory and descend into amnesia and madness. 
They feel great pain, anguish, sorrow and hate over this betrayal.

\lyricslimbonicart{Purgatorial Agony}{
  Experimental malediction.\\
  Destructive minds.\\
  Seeking places no living can find.\\
  Awaiting darkness, transcending, venture into the night.
  
  I hide within places unknown.\\
  There was nothing else to do.\\
  With sorrow and hatred burning inside,\\
  the suffering was endless.\\
  Mementos undivine.\\
  The bleeding scenarios,\\
  The reservoirs of shame.\\
  Damned in misanthropic fires,\\
  the soul dwelt.
  
  The feelings for mankind were gone,\\
  and so were the values of life.\\
  There was only a final wish:\\
  Death before a living hell.
}

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  A Chore for the Lost
}{
  An exhausted fall into disgrace, \\
  famished for peace, \\
  for a mere moment of respite in dying eternities, \\
  on the verge of being deprived of all humanity: \\
  Nonsense is the outcome of every possible sense, \\
  it is the start of transcendence, \\
  the dissolution that spreads without limits \\
  and the critical violation.
}














\section{Other races}
Remember that even though the period is often called \quo{the \resphanwars}, the \nagae, \aryothim{} and \vorcanths{} also played important roles. 























