\target{Third Banewar}
\target{TBW}
This book details what would later be retroactively called \thirdbanewar, the final showdown with the \banes. 















\section{Overview}









\subsection{The Unravelling brings chaos}
\target{Eschaton: ThirdBanewarBook}
The \hs{Unravelling brings chaos}. 
The world is slowly going mad. 
It will get much worse\prikker

See also the general section about the \hs{Eschaton}. 





\subsubsection{Ghosts escape}
Now, as the \hr{Sephirah plan}{\sephirah{} plan} is approaching fruition, the \carcer{} of \Iquin{} is filled to the bursting. 
Due to the \hs{unravelling}, \Iquin{} has grown unstable and leaking. 
Ghosts seep out and escape into the world, in droves. 

Compare to the ghosts and the Spectres in \cite{PhillipPullman:HisDarkMaterials}. 









\subsection{The world goes mad}
\target{The world goes mad}
Have a longer story where the world goes mad. 
More people discover the truth about \iquin, but by then it is too late, and their souls are too deeply bound to \iquin to break free. 

They also discover that there are even older and more malevolent things in the world than \iquin.
Things perhaps even more inimical to them.
So that even if \iquin is a parasitic soul prison, it is perhaps better than the alternative. 

The end of the world is heralded by earthquakes and floods and other natural catastrophes. 

Compare to the movie \cite{Movie:IntheMouthofMadness}, and \cite{RobertBloch:StrangeEons} and \cite{RPG:CallofCthulhu:EndTime}. 

Have scenes of chaos as in \cite{TimCurran:TheSpawning}.

See also the general section about the \hs{Eschaton} and the section about \hr{Eschaton: RamielsAwakeningBook}{the cataclysmic events} that happen at this time. 

\citeauthorbook[\quo{First Thought in Three Forms}, p.86--100]{%
  BentleyLayton:TheGnosticScriptures%
}{%
  Bentley Layton%
}{%
  The Gnostic Scriptures%
}{
  Now, when the great authorities knew that the time for fulfillment had come\dash as when labor pains are felt by a lying-in woman\dash and that it was near the door, and that just so, destruction had drawn night, all the elements together shook.
  And the foundations of Hades and the ceilings of chaos moved.
  A great fire broke out in their midsts.
  And the rocky cliffs and the earth moved as a reef is moved by the wind. 
}

Seek inspiration in the Book of Revelation in the \emph{Bible} and other religious eschatology. 

\lyricsbs{Slayer}{Raining Blood}{Raining blood from a lacerated sky.\\
  Bleeding its horror.\\
  Creating my structure.\\
  Now I shall reign in blood!
}

\lyricstitle{\cite{HPLovecraft:TheCallofCthulhu}}{
  The most merciful thing in the world, I think, is the inability of the human mind to correlate all its contents. We live on a placid island of ignorance in the midst of black seas of infinity, and it was not meant that we should voyage far. The sciences, each straining in its own direction, have hitherto harmed us little; but some day the piecing together of dissociated knowledge will open up such terrifying vistas of reality, and of our frightful position therein, that we shall either go mad from the revelation or flee from the deadly light into the peace and safety of a new dark age.
  
  [\prikker]
  
  That cult would never die till the stars came right again, and the secret priests would take great Cthulhu from His tomb to revive His subjects and resume His rule of earth. The time would be easy to know, for then mankind would have become as the Great Old Ones; free and wild and beyond good and evil, with laws and morals thrown aside and all men shouting and killing and revelling in joy. Then the liberated Old Ones would teach them new ways to shout and kill and revel and enjoy themselves, and all the earth would flame with a holocaust of ecstasy and freedom.
}

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\prikker 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}





\subsubsection{Storm in the afterlife}
At this time there is such a furious storm of chaos raging just outside \Miith's walls that it is shaking even the afterlife. 
All cultures are losing mortal souls at an alarming rate.
And even immortal souls are in danger of being swallowed up by the consuming emptiness outside, where hungry and mindless gods gnaw and rage and howl. 
Compare them to the dancers around Azathoth's throne in \cite{HPLovecraft:TheDreamQuestofUnknownKadath}.

The Shroud has created an unnatural pressure inside the walls of \Miith. 
Now that it is all about to come apart, the blind powers of the outer spaces are back with a vengeance. 
Immortality is no longer certain. 
The immortals suddenly know new kinds of fear. 









\subsection{\Voidbringer must be stopped}
The \dragons{} and other \bane-opponents know that if the Cabal manage to open the portal to \Erebos{} as wide as they did in the \secondbanewar, they will be able to let in millions of \bane{} warriors. 
There is no way in fucking Hell the \Miithians will be able to deal with that many.
They are fewer and weaker than they were last time. 
So they must stop the portal. 








\subsection{Aloof \dragons must be roused}
There were some \hr{Aloof Dragons}{aloof \dragons} who took no part in the \feud.

The aloof ones did not care that \hr{No new Dragons are born}{almost no new \dragons were born} since the \hr{Heart weakened}{weakening of the Heart} began.
The aloof ones were powerful and immortal and had the luxury to wait a few thousands or even tens of thousands of years between procreating. Many of them were over 20,000 years old and saw the war with the \resphain as a temporary nuisance. 

\Ishnaruchaefir and \Secherdamon were similarly old and would likely have thought the same, but the war came horribly close to them when some of their close family members (Nexagglachel and \Ishnaruchaefir's three sons) were destroyed by the \resphain.
Now, in the \thirdbanewar, \Secherdamon or \Ishnaruchaefir had to convince the aloof ones that the war was more than a nuisance and that its conclusion would have great repercussions for all \dragons, even the ones who had fled to \Machai.
Eventually some of the aloof ones became convinced. 
Not all, but enough.

The conclusion of the war WAS important.
The aloof ones could hide in \Machai, but they could not really get away. 
They were still bound by the Heart and would suffer its fate.
Either that, or they would have to evolve, abandoning their Draconic nature entirely and becoming something different.
\Ishnaruchaefir and \Secherdamon knew this might be an option\dash{}to flee to \Machai and abandon \dragonkind\dash{}but it was not a palatable one. 
They both wanted the Draconian race to survive.
\Secherdamon wanted to win the war and was willing to enlist the \xs, with all the associated costs.
\Ishnaruchaefir did not like that idea.
So he looked outward into the universe for other ideas.









\subsection{Ramiel is mad}
Ramiel tries to hide it, but \hr{Ramiel is mad after awakening}{his sanity has suffered badly}. 









\subsection{Clean \humans}
There are some \humans who are \quo{\hr{Clean Humans}{clean}}, in the sense that they have no blood of the \quo{\hs{Men of Light}} and thus do not carry \Lithrim inside them. 
These \humans still have \bane and \resphan blood, but no \Lithrim.
This means that they are unaffected by the \hs{Second Advent}. 

Some of these \humans are among the heroes. 
They help the immortal heroes.
They accomplish some minor things and manage to make a difference. 
Then they die at the end.
But they die a heroic death. 

















\section{The \Matrices Battle}









\subsection{\ps{\Daggerrain} master plan}
\hr{Daggerrain's master plan}{\ps{\Daggerrain}{} master plan}, planned and orchestrated throughout twenty thousand years, is unfolding. 

\Secherdamon{} and \Ishnaruchaefir{} oppose him. Ramiel ostensibly serves the \banes, but is actually planning yet another betrayal.

\Daggerrain{} intends to sunder the wall to \Erebos{} and allow the \Voidbringer{} unrestricted access to \Miith{}. 

But \hr{Daggerrain's blind spot}{he has a blind spot}\prikker

\Secherdamon, on the other hand, wants to open the gate to Chaos and awaken \Tiamat{} and the \firstgendragons. He has communicated with \KhothSell{} or another one of them. She agrees to help him, but only if he can open the way and make it easy for them to help him. (See section \ref{Rissit communicates with Tiamat}.)

But \Iurzmacul{} plots against his fellow \firstgendragons{}. He does not want to see \Tiamat{} and the others return and devastate \Miith{}. Maybe he tells \Ishnaruchaefir{} and guides him. Maybe \Ishnaruchaefir{} is the son of \Iurzmacul.





\subsubsection{\Dragons fear \Voidbringer}
The \dragons{} know that if \Voidbringer{} gains access to \Miith, they will not stand a chance against the feared \baneking. 
If that happens their only recourse will be to follow \ps{\Vizsherioch} lead and appeal to the \xss. 

\Vizsherioch{} will not accept \Ishnaruchaefir{} as an ally. 
He would prefer to kill him. 

\Vizsherioch{} \emph{wants} to see the \banes{} succeed and \Voidbringer{} brought into the world, because then all of \Miith{} will be forced to turn to him as their only saviour. 
He cannot summon the \xss{} alone, but with enough \dragons{} and \quiljaaran{} and other immortals on his side, he can pull it off. 

He relishes the thought of a war between the \xss{} and the \banelords. 
He is willing to risk the destruction of all of \Miith. 
He kind of thinks like a \xss, remember. 
Plus \hr{Immortal Vizsherioch}{he is more immortal than most}. 









\subsection{Ramiel solidifies his power}
I should let a few years pass between the end of the last book and the beginning of (the serious part of) this one. 
Ramiel needs some time to consolidate his rule as Overlord. 
Not everyone swoons and falls down to worship at his feet. 

And even after some years, he still has rivals and has trouble controlling the dynasty. 

\target{Dasteron's cousins oppose Ramiel}
Among his most vehement foes are \hr{Dasteron's cousins}{\ps{\Dasteron} cousins}, \Sargamel and \Themirod. 

\target{Ramiel uses macho rhetoric as Overlord}
Ramiel uses traditional \Mystraacht \hr{Mystraacht philosophy}{macho rhetoric}. 
But he is actually \hr{Ramiel is critical of Mystraacht ideology}{critical of the \Mystraacht ideology}. 

After his return to Overlordship, Ramiel broods over the doings of the \resphan race.
He is disgusted by their stupidity and hypocrisy. 
The \Mystraacht curse the \CiriathSepher for being shallow and dishonest, but the new, wiser Ramiel can now see that the \Mystraacht are no better themselves, with all their shallow machismo and their hollow talk of \honour and bravery and whatnot.

He thinks: 
\tho{There are times when I wish the \banelords would just come and devour everything. Or whatever it is they plan to do.}

Even among the highest tiers of the \resphain who serve them, there is no one who really knows what the \banelords intend to do.
No \resphan understands the mind of a \bane.









\subsection{\Dragons summon \xss}
\Secherdamon-tachi want to awaken the \xss and summon them to \Miith to fight against the \bane menace. 
Maybe this is mostly intended to slow down the \banes. 
The \dragons know they cannot rely on the \xss as allies.
The \xss might decide it is not worth the effort and pull out of \Miith.
But if the \dragons can at least get the \xss to hold off the \banes, they have a chance. 

The \banes have a thousand-year master plan.
The \xss have little interest in \Miith.
They are likely to give up and go home. 
They will not commit many resources to \Miith. 
It is unlikely that they will save it in the long run, but they may save it in the short run. 





\subsubsection{\Vizsherioch seeks out \daemons}
\Vizsherioch{} seeks out some great and mighty \daemons{} who once served the \xzaishanns{} but have lain dormant for thousands if not millions of years. 

He demands that they serve him. They laugh and reject him, for they have been approached by \dragons{} before. But \Vizsherioch{} is more \xzaishann{} than any \dragon{} ever before. When the \daemons{} realize that, they are impressed and overwhelmed. They agree to serve him. 

He also seeks out \hr{Cosmic gods}{cosmic gods}\dash the same ones that \hr{Ishnaruchaefir seeks out cosmic gods}{\Ishnaruchaefir{} sought out}. But they turn him down. He claims that he is a \xzaishann{} reincarnated, and they laugh.

\lyricsbalsagoth{
  The Hound of Chaos Transcends the Nebulous Palisades of Z'xulth
}{
  The Outer Darkness has cast me from its cavernous maw! 
  So be it\prikker the final pieces of this great macrocosmic puzzle shall soon fall into place. 
  It has been millennia since I last visited my beloved brother, Zuranthus\prikker 
  and this reunion shall most certainly be steeped in ire! 
  
  The annals of eternity shall soon be illumined by the glorious radiance of my deeds, and the searing fire of my long denied vengeance! Woe unto my dogged nemesis and all those who dare aspire to thwart me\prikker for my final ascendence is nigh!
}







\subsection{\Ishnaruchaefir invokes dark gods}
\Ishnaruchaefir{} is forced to invoke various dark gods to seek their power and aid. Some of the same forces that \Secherdamon{} originally invoked to gain power (see section \ref{Rissit invokes dark gods}). 

Perhaps these powers originally helped effect the \hr{Shrouding}{\SecondShrouding}, and now \Ishnaruchaefir{} needs their power to defend the Shroud (see section \ref{To break or preserve the Shroud}).

In the end, a few Elder \Dragons manage to awaken (now that the Shroud is broken) and come to \Ishnaruchaefir's aid.









\subsection{\Iquinian Church preaches}
The \Iquinian Church preaches extra hard. 
The advent of \Lithrim{} is nigh, and the Cabalists want to be sure all the myriad Iquinians are kept under tight control. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  A Chore for the Lost
}{
  Every human being not going to the extreme limit \\
  is the servant or the enemy of man \\
  and the accomplice of a nameless obscenity.
}







\subsection{Ramiel accepts \NexagglachelsCurse}
Ramiel is seduced by the blood of \Nexagglachel{} in his veins. 
He is swayed by the \ps{\dragonlord} voice and ultimately agrees to betray the \banelords, in return for peace of mind from the \hr{Madness of the Curse}{madness and dementia that the curse brings}.

\lyricslimbonicart{The Yawning Abyss of Madness}{
  The winds that carry this esoteric call\\
  emerges from the dungeons underneath my soul. \\
  As I cross the bridge to that darkness, \\
  my eyes are filled with so much death.
}







\subsection{\Ishnaruchaefir hears \Nexagglachel would be proud}
\target{Ishnaruchaefir hears Nexagglachel would be proud}
\Ishnaruchaefir{} meets some \sathariah. 
Possibly Ramiel or \Azraid. 
(Maybe when \hr{Ishnaruchaefir and Azraid plot together, late in TBW}{\Azraid{} conspires with \Ishnaruchaefir}.) 

\begin{prose}
  The \sathariah: 
  \ta{I have a piece of your brother inside of me, you know. 
    I know something of his thoughts. 
    And you know what? 
    I think if \Nexagglachel{} knew what you had done, he would be pleased.}
\end{prose}

The above is not well-meant. 
The \sathariah{} hates \Nexagglachel, because \Nexagglachel{} hates him and drives him mad and ruins his life. 
But it is sincere. 

\Ishnaruchaefir{} takes it as a confirmation that he is on the right track. 
This makes him incredibly relieved. 
He has spent millennia brooding over whether he is \hr{Ishnaruchaefir's stewardship}{carrying on \ps{\Nexagglachel} legacy} properly. 
When \Criseis{} next sees him, he is happier than she has seen him in thousands of years. 
He does not show it, but she, who knows him better than any other, can detect it in his smell and his aethereal threads. 
The pall of darkness that always hangs over him has lifted a little. 










\subsection{Ramiel allies with \Baelzerach}
In secret, Ramiel contacts the \Baelzerach{} and forges a hidden alliance between them and \Mystraacht. They will not openly fight side by side, but they will strike at the same enemies and covertly work to achieve the same goals. 

This is especially sneaky because no one expects it. \Mystraacht{} and \Baelzerach{} are traditionally enemies, having fought many and very bloody wars. 









\subsection{The \banes bring a spaceship to \Miith}
The \banelords{} succeed at bringing a titanic and ancient \hr{Bane technology}{\voyager{} spaceship} from \Erebos/\Nyx{} to \Miith{}. 
It will take all of the \psp{\dragons}{} \xsic{} power to destroy it.

Other people see signs of its approach.

\lyricslimbonicart{Nebulous Dawn}{
  Dark atmospheric winds\\
  are striking towards Earth.\\
  Nihilistic cosmic force.\\
  Asteroid curse.
}

The ship arrives. 
It is a massively powerful juggernaut and wreaks tremendous destruction. 

\lyricslimbonicart{Nebulous Dawn}{
  A blazing phenomenon\\
  launching through the skies.\\
  A deadly impact, tempest chaos.\\
  Utterly devoid of life.
  
  Fountains of fire rise from the lava chambers.\\
  Columns of smoke darken the sky\\
  and cover the landscape in ashes.\\
  Storms with the anatomy of disaster.\\
  Immense swirling winds.
}









\subsection{\Erebos \Matrix Ascendant}
The \bane{} \matrix{} is strong and has almost taken over the world. 
Its corrupting, destructive influence can be felt all over \Miith{}. 
The \hr{Morbus}{\Morbus} is but one of its manifestations. 

\lyricslimbonicart{Nebulous Dawn}{
  An epic eclipse of the Sun.\\
  A rebirth of desolation.\\
  When the cold silence reigns,\\
  darkness sweeps the face of Earth\\
  with infesting freezing torments.\\
  Across the desert wastelands.\\
  Cataclysmic events.
}









\subsection{\Rystessakhin is damaged}
\Ishnaruchaefir{} is in battle, wielding his \hs{glaive}. 
Suddenly it goes wrong, and the unthinkable happens: 
The glaive becomes damaged. 
One of the little blades snaps off. 

\Ishnaruchaefir{} is terrified. 
He knew the Shroud was \hs{unravelling} and it was becoming harder for \Rystessakhin{} to keep it in place. 
\hr{Ishnaruchaefir's Nadir}{His own Nadirs} had been growing steadily worse as a result. 
But had never imagined that it would come to this. 

He immediately unsummons the glaive. 
Then he spends all his available energy on fighting his way free and escaping from the fight. 

He realizes that something is catastrophically wrong. 
The Shroud is under attack, and the pressure on poor \Rystessakhin{} has become so great that even her physical form is chipping and falling apart. 
The status quo is crumbling, and he cannot hope to maintain it any longer. 
He needs to change his strategy.
Something drastic must be done. 








\subsection{\Azraid conspires with \Ishnaruchaefir}
\target{Ishnaruchaefir and Azraid plot together, late in TBW}
\Azraid{} conspires with \Ishnaruchaefir. 

They have \hr{Ishnaruchaefir and Azraid develop empathy}{talked before} and have a relationship as friendly rivals. 
They have even \hr{Ishnaruchaefir and Azraid plot together, early in TBW}{plotted together before}. 
They are both philosophers who feel somewhat estranged from their races, so they have a certain mutual understanding. 

Gradually and ever so subtly through \quo{Sentinels of \Miith} \Ishnaruchaefir becomes convinced that Azraid is on the level, and he also begins to suspect the general nature of Azraid's plan. 
So when Azraid finally approaches \Ishnaruchaefir and asks for his cooperation in a secret venture, \Ishnaruchaefir has a bit of a \quo{what took you so long?} attitude, and the whole interaction has a \quo{I know you know I know you know\prikker} frame.
The two have each formulated ideas that can be combined into a useful whole.

Now \Azraid{}, for the first time \emph{ever}, comes clean and reveals (part of) his master plan to \Ishnaruchaefir. 
\Ishnaruchaefir{} is the best person he can trust with his plan. 

\Azraid{} also needs Ramiel, but he cannot trust him.
Ramiel is too volatile, too unreliable. 
\Ishnaruchaefir{} \hr{Ishnaruchaefir's impulsiveness}{has spent all his impulsiveness long ago}, so \Azraid{} knows he is dependable.

\Ishnaruchaefir{} agrees to cooperate with his old enemy. 

Perhaps it is here \Azraid{} \hr{Ishnaruchaefir hears Nexagglachel would be proud}{tells \Ishnaruchaefir{} that \Nexagglachel{} would be proud}. 








\subsection{\Harbeth dies}
\target{Harbeth dies}
\Harbeth dies for some reason. 

Maybe \Zereth also dies. 
Most of the \hr{CS heirs die}{\CiriathSepher{} heirs die}. 








\subsection{\Ishnaruchaefir sacrifices \Criseis}
Near the end, \Ishnaruchaefir sacrifices \Criseis and commits other cruel but necessary acts. 
Make it horrifying but awesome. 
He calls upon the \xss and other terrible dark gods and prepares to sacrifice the entire world, as he once did in the \hs{Shrouding}. 

Compare to Bayaz in \cite{JoeAbercrombie:LastArgumentofKings} where he sacrifices Yulwei and breaks the First Law. 















\section{\Ishnaruchaefir's quest}
\Ishnaruchaefir has lost his Mirage Asylum. 
He realizes that if he is to truly make a difference in this war, he will need more power.
(He \hr{Ishnaruchaefir begins to realize what he must do}{began to realize this earlier}.)
He decides that he has to go on a pilgrimage to the ancient \draconian land of \Dragonland and the dreaded citadel of \hr{Baltherium}{\Baltherium}. 

Compare the whole quest to Randolph Carter's search for Kadath in \cite{HPLovecraft:TheDreamQuestofUnknownKadath}. 

Read about \hr{Nom}{\Nom} and \hr{Baltherium}{\Baltherium}.









\subsection{\Matrix}
Fortunately \Ishnaruchaefir has prepared for this. 
He has sought out allies and recruited heroes for his cause, both mortal and immortal. 
He now drafts some of these heroes.
He needs them to accompany him and serve as \vertices, for he will need a full \hr{Draconian Matrices}{\draconian \matrix} if he is to accomplish his task. 

His \matrix includes \hr{Criseis}{\Criseis} and \hs{Telcastora Ilcas}.
It was also supposed to include \hr{Najarod}{\Najarod}, but he was suddenly killed, and his youngest lover \hr{Shiin}{\Shiin} took his place. 

\Criseis was not originally supposed to come.
She begged \Ishnaruchaefir to take her along, and he relented.
But she was not a part of the \matrix.
Then something went wrong, and another \matrix member died.
\Criseis now had to take the last position, as much as \Ishnaruchaefir hated to see her take the risk. 









\subsection{Culmination}
At the end, \Ishnaruchaefir has to fight his way through the horrors of the \hs{dead universe}. 

\citeauthorbook[p.482--483]{HPLovecraft:TheDreamQuestofUnknownKadath}{\HPLovecraft}{%
  The Dream-Quest of Unknown Kadath%
}{%
  And Randolph Carter, gasping and dizzy on his hideous Shantak, shot screamingly into space toward the cold blue glare of boreal Vega; looking but once behind him at the clustered and chaotic turrets of the onyx nightmare wherein still glowed the lone lurid light of that window above the air and the clouds of earth's dreamland. Great polypous horrors slid darkly past, and unseen bat wings beat multitudinous around him, but still he clung to the unwholesome mane of that loathly and hippocephalic scaled bird. The stars danced mockingly, almost shifting now and then to form pale signs of doom that one might wonder one had not seen and feared before; and ever the winds of nether howled of vague blackness and loneliness beyond the cosmos.
  
  Then through the glittering vault ahead there fell a hush of portent, and all the winds and horrors slunk away as night things slink away before the dawn. Trembling in waves that golden wisps of nebula made weirdly visible, there rose a timid hint of far-off melody, droning in faint chords that our own universe of stars knows not. And as that music grew, the Shantak raised its ears and plunged ahead, and Carter likewise bent to catch each lovely strain. It was a song, but not the song of any voice. Night and the spheres sang it, and it was old when space and Nyarlathotep and the Other Gods were born.
  
  Faster flew the Shantak, and lower bent the rider, drunk with the marvel of strange gulfs, and whirling in the crystal coils of outer magic. Then came too late the warning of the evil one, the sardonic caution of the daemon legate who had bidden the seeker beware the madness of that song. Only to taunt had Nyarlathotep marked out the way to safety and the marvellous sunset city; only to mock had that black messenger revealed the secret of these truant gods whose steps he could so easily lead back at will. For madness and the void's wild vengeance are Nyarlathotep's only gifts to the presumptuous; and frantick though the rider strove to turn his disgusting steed, that leering, tittering Shantak coursed on impetuous and relentless, flapping its great slippery wings in malignant joy and headed for those unhallowed pits whither no dreams reach; that last amorphous blight of nether-most confusion where bubbles and blasphemes at infinity's centre the mindless daemon-sultan Azathoth, whose name no lips dare speak aloud.
  
  Unswerving and obedient to the foul legate's orders, that hellish bird plunged onward through shoals of shapeless lurkers and caperers in darkness, and vacuous herds of drifting entities that pawed and groped and groped and pawed; the nameless larvae of the Other Gods, that are like them blind and without mind, and possessed of singular hungers and thirsts
  Onward unswerving and relentless, and tittering hilariously to watch the chuckling and hysterics into which the risen song of night and the spheres had turned, that eldritch scaly monster bore its helpless rider; hurtling and shooting, cleaving the uttermost rim and spanning the outermost abysses; leaving behind the stars and the realms of matter, and darting meteor-like through stark formlessness toward those inconceivable, unlighted chambers beyond time wherein Azathoth gnaws shapeless and ravenous amidst the muffled, maddening beat of vile drums and the thin, monotonous whine of accursed flutes.
}







\subsection{\Ishnaruchaefir realizes what he must do}
\target{Ishnaruchaefir realizes what he must do}
At the end, in order to break free (like Randolph Carter on his way to Azathoth's throne) \Ishnaruchaefir will need true Gnosis of his own Aenigma. 
To do this he has to look deep inside himself and come to terms with himself. 
Face his inner demons. 
This means he must overcome a ton of traumata, which have festered inside him ever since he \hr{Ishnaruchaefir slays his beloved}{killed \Rystessakhin} and \hr{Ishnaruchaefir goes into the void}{fled into the void}. 

He must make peace with the memory of \Rystessakhin{}. 
Only then can he call upon all his strength. 
He must save himself before he can hope to save the world. 

\Achamoth fights against \Ishnaruchaefir and seems to want to stop him (like Nyarlathotep in \cite{HPLovecraft:TheDreamQuestofUnknownKadath}).
But in the end \Ishnaruchaefir suspects that he has been played for a \trope{XanatosSucker}{Xanatos Sucker} and that \Achamoth was really guiding him through the necessary struggle as a \trope{TricksterMentor}{Trickster Mentor}. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  As deep cuts of truth.\\
  As a fire that closes the wound.\\
  So is my redemption.
  
  Beyond repentance.\\
  This is the ordeal of fire.
}

It will be hard, expensive and bloody, for both him and the world. 
But it will be worth it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  Come suffering, Apocalypse.\\
  Release the fires of Hell.\\
  I call upon destruction and despair.\\
  Not for vengeance, not for power.\\
  Beneath the ashes I walk.
}

At last he takes a deep breath and prepares to do it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  Behold, an angel of vengeance.\\
  A lion. A sword of fire. \\
  Alas, the burden of my heart\\
  is violence undone\\
  Pain unfulfilled.\\
  Silence.
}

Finally he does it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  When I finally cut \\
  deep into the flesh of guilt,\\
  the un-naked body of shame\\
  and the veins of repentance open wide,\\
  sending rivers of blood into my mouth.
  
  The pain is still mine.
}

\citeauthorbook[p.484--485]{HPLovecraft:TheDreamQuestofUnknownKadath}{\HPLovecraft}{%
  The Dream-Quest of Unknown Kadath%
}{%
  Turn\dash turn\dash blackness on every side, but Randolph Carter could turn.
  
  Thick though the rushing nightmare that clutched his senses, Randolph Carter could turn and move. He could move, and if he chose he could leap off the evil Shantak that bore him hurtlingly doomward at the orders of Nyarlathotep. He could leap off and dare those depths of night that yawned interminably down, those depths of fear whose terrors yet could not exceed the nameless doom that lurked waiting at chaos' core. He could turn and move and leap\dash{}he could\dash{}he would\dash{}he would\dash{}he would.
  
  Off that vast hippocephalic abomination leaped the doomed and desperate dreamer, and down through endless voids of sentient blackness he fell. Aeons reeled, universes died and were born again, stars became nebulae and nebulae became stars, and still Randolph Carter fell through those endless voids of sentient blackness.
  
  Then in the slow creeping course of eternity the utmost cycle of the cosmos churned itself into another futile completion, and all things became again as they were unreckoned kalpas before. Matter and light were born anew as space once had known them; and comets, suns and worlds sprang flaming into life, though nothing survived to tell that they had been and gone, been and gone, always and always, back to no first beginning.
  
  And there was a firmament again, and a wind, and a glare of purple light in the eyes of the falling dreamer. There were gods and presences and wills; beauty and evil, and the shrieking of noxious night robbed of its prey. For through the unknown ultimate cycle had lived a thought and a vision of a dreamer's boyhood, and now there were remade a waking world and an old cherished city to body and to justify these things. Out of the void S'ngac the violet gas had pointed the way, and archaic Nodens was bellowing his guidance from unhinted deeps.
  
  Stars swelled to dawns, and dawns burst into fountains of gold, carmine, and purple, and still the dreamer fell. Cries rent the aether as ribbons of light beat back the fiends from outside. And hoary Nodens raised a howl of triumph when Nyarlathotep, close on his quarry, stopped baffled by a glare that seared his formless hunting-horrors to grey dust. Randolph Carter had indeed descended at last the wide marmoreal flights to his marvellous city, for he was come again to the fair New England world that had wrought him.
}













\section{Climactic Battle}
Near the end there is a great, climactic battle between the \bane/\resphan{} forces and some \quo{good guys}. 
There are very few \dragons{} (perhaps only \Ishnaruchaefir{} and his companions), because most \dragons{} support \ps{\Secherdamon} gambit, hoping to utilize the \pps{\banes}{} Shroud-weaving spell to bring the \firstgendragons{} into the world and have them vanquish the \Voidbringer{} and his legions.







\subsection{Rage, Rage Against the Dying of the Light}
One of the sections or chapters of this book should be called \quo{Rage, Rage Against the Dying of the Light}.
It is a reference to the poem \quo{Do not go gentle into that good night} by Dylan Thomas.







\subsection{\HothNrul}
\target{Hoth-Nrul summoned}
\Vizsherioch{} and his cohorts manage to bring a mighty ally to \Miith: 
\hr{Hoth-Nrul}{\HothNrul}, a \xsic{} godling. 
\HothNrul{} is intended to spearhead the coming \xs{} invasion of \Miith. 

Later, \Ishnaruchaefir-tachi communicate with \HothNrul{} and convince the alien god that it is in its interest to attack \Daggerrain.
So \HothNrul{} seeks out the \banelord. 

\HothNrul{} has difficulty attacking \Daggerrain, for he is well-hidden-away. 
But it manages to do some damage. 
When \Daggerrain{} is distracted by the \xs{}, \Azraid{} and Ramiel strike and fuck up \Daggerrain. 







\subsection{\Ishnaruchaefir leads \dragons}
\target{Ishnaruchaefir leads Dragons to war in TBW}
\Ishnaruchaefir{} does not believe in this gambit. He has no faith in \Tiamat{} and her brethren and does not think they will come to help. 
So he works to persuade the \dragons{} (including some \hr{Aloof Dragons}{aloof ones}) to fight, to fly with him against \ps{\Daggerrain}{} legions. 

At the last moment, he succeeds. 
Have a massively epic scene where \Ishnaruchaefir{} flies at the head of a massive flight of a \dragons, flanked by hundreds of \rachyths, \drakes{} and \pdaemons, to engage the \bane{} armies and seize victory.
They are awesome to behold as they return to \Miith in full force. 
Dozens of Elder \Dragons. 

Compare to: 

\begin{itemize}
  \item 
    \bandsong{Bal-Sagoth}{Black Dragons Soar Above the Mountain of Shadows}. 
  \item 
    The scenes in \authorseries{Richard Knaak}{War of the Ancients} where everyone holds their breath for the \dragons{} to come to their aid, and where they finally do come and save the day.
  \item 
    The scenes in \authorbook{Graham McNeill}{Fulgrim} p.472, where the Alpha Legion, Word Bearers, Night Lords and Iron Warriors come to the \quo{rescue}. 
\end{itemize}

\citeauthorbook[p.344]{ClarkAshtonSmith:TheDarkEidolon}{Clark Ashton Smith}{%
  The Dark Eidolon%
}{
  Yea, the undying worms of fire and darkness have come forth like an army at thy summons\prikker
}







\subsection{The Advent of \Lithrim}
\target{Lithrim arises}
\target{Second Advent}
\target{Second Advent of Lithrim}
\Lithrim{} finally arises. 

Mankind is very Shrouded, \naive{} and stupid. 
Not quite as well-meaning and {innocent} as the \scathae, but not all that far from them.
That is why it is so effective when their inner \Erebean{} darkness is finally released in the culmination of the \Morbus{} plan. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Sola Fide
}{
  Some rejoice of the children's innocence and smiles\\
  Others of their shameful defloration \\
  by the ministers of Christ, swollen by arrogance and lust\\
  Jesus spoke words of wisdom: \quo{Let the children come to me}\\
  What's more enthralling indeed \\
  than ruining through them the genesis of life itself?\\
  Dive deep into the blue eyes of the newborn \\
  and thou shalt get a glance of heaven\\
  When this dive reveals despair, \\
  hideous ruins of the glory of Hell\\
  The serving sons of disobedience proclaim \\
  Vengeance belongeth unto Him\prikker
}

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Innocence sacrificed and heaven denied\\
  Iniquity divine\dash no repentance\dash over mankind\\
  Mind-raped, self-devoured, empty god-eyed\\
  Transgression coercive, Redemption never to be found

  Under the altar of cannibalism\\
  Man hast (thou) confessed the spiritual schism\\
  And without pride mourned the loss of freedom,\\
  Our blessed Lord have condemned you to martyrdom
  
  Let everything that hath breath praise the Lord, \\
  praise ye the Lord.
}

It is the culmination of that which began with \ps{\Thanatzil} noble sacrifice. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  The advent of Plerosis is the destiny of Man \\
  and shall shatter up to the Heavens,\\
  A savage aperture to the High Mass of the Comforter
}

It is cataclysmic and destructive. 
It unleashes all the wicked, destructive Entropy that, as it turns out, were the building blocks of Man all along. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Instigating manifold quadrants of industrialized death,\\
  An avid Moloch, never satiated, an endless Feast,\\
  Following the principle of reversibility of merits,\\ 
  shattering up the Word\\
  As Pillars of grayish Soulfire spurt out to a bereaved firmament
}

Man instinctively welcomes the advent of \Lithrim.

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  The unreservedly open spirit, \\
  open to death, to torment, to joy,\\
  The open spirit, open and dying,\\
  Suffering and dying and happy, \\
  stands in a certain veiled light:\\
  That light is divine.\\
  And the cry that breaks from a twisted \\
  mouth may perhaps twist him who utters it,\\
  But what he speaks is an immense alleluia, \\
  flung into endless silence, and lost there.
}

But it is also scary. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  From very high above a kind of stillness \\
  swept down upon me and froze me\\
  It was as though I were borne aloft \\
  in a flight of headless and unbodied angels\\
  Shaped from the broad swooping of wings, \\
  but it was simpler than that\\
  I became unhappy and felt painfully forsaken, \\
  as one is when in the presence of God
}

Some \humans{} fight against it. 

\citebandsong{BeyondTwilight:TheEdge}{Beyond Twilight}{Salem}{
  Entombed by the will of the night.\\
  All your thoughts deflowered.\\
  Waived all of your beliefs\\
  in this midnight hour. \\
  Search your past, try and make it back.\\
  All your strength overpowered.\\
  Unknown forces run you through \\
  in the shadow of the black tower.
  
  The witches of Salem hold your fate. 
  
  Relief obtained in sacred mass.\\
  All your sins forgiven. \\
  The ultimate sign of witchery.\\
  The total lack of sanity.
}

\Humans{} lose their individual identity. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  And the victim, blind to the radiating Light of Truth, \\
  stuttering, repeats:\\
  Lamma Sabacthani?\\
  Lamma Sabacthani?\\
  Lamma Sabacthani?
  
  Consummatum est.
}

Mankind becomes a god: \Lithrim. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  I am the son of Man, \\
  and this in erring reason's spite, is my pride\prikker\\
  War, be enthroned, a form of divine retribution!\\
  Execution, be sacred, agent of divine Providence!
  
  The stillness of Contemplation \\
  is allowed in billions of woeful cries,\\
  So astonishingly simultaneous and in unison,\\
  Each and every second, \\
  They defuse each other in such a perfect manner,\\
  Equaling the most inscrutable of all silences\\
  Doctrine of Mystical Substitution, Mystical Body, \\
  Sanctorum Communionem,\\
  Celebrate the Sin of one reflecting, \\
  tectonic forces alike, upon the multitude
  
  The purest of all Holocausts shall be perpetrated\\
  By a loving hand, never knowing if it provided felicity\\
  Or the vilest of everlasting torments\\
  No man can see Me and live!
}

When the \humans{} become the fell, abhorrent \Lithrim, they (or the smarter of them) at last realize the purpose of their otherwise empty and wretched lives. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  The act whereby being\dash existence\dash is bestowed upon us\\
  Is an unbearable surpassing of being,\\
  An act no less unbearable than that of dying.\\
  And since, in death, being is taken away from us \\
  at the same time it is given us,\\
  We must seek for it in the feeling of dying,\\
  In those unbearable moments \\
  when it seems to us that we are dying\\
  Because the existence in us,\\
  During these interludes,\\
  Exists through nothing but a sustaining and ruinous excess,\\
  When the fullness of horror and that of joy coincide.
  
  As I waited for annihilation, all that subsisted in me\\
  Seemed to me to be the dross over which man's life tarries\prikker
}

But they lose their \humanity{} in the process. 

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega%
}{
  Mass Grave Aesthetics
}{
  The black Idol fills the veil of flesh with noxious smoke, \\
  Depicting primal human experiences indifferently, \\
  Contemptuous of moral concerns, dehumanized \\
  The howling of wolves and the destructive sword \\
  are portions of Eternity, \\
  Too great for the eyes of merely a man
}

\citebandsong{BlindGuardian:FTB}{%
  Blind Guardian%
}{
  Hall of the King
}{
  You're the birth and you're the end.\\
  You've been hurt but you're not dead.\\
  Discovering you is what should never be.\\
  Poisoned are our souls and dark our hearts.\\
  Ruins we have left to rule the world.\\
  Destructive are our minds. It's much too late.\\
}

But they gain new insight as they leave their \human{} forms:

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega%
}{
  Mass Grave Aesthetics%
}{
  Violence exists I the moment \\
  when the eye turns upwards into the head, \\
  When inversion is complete and total \\
  The darkness of the upturned eye is not the absence of light \\
  But the process of seeing being taken to its limit \\
  That thorough derangement of the senses, \\
  Way beyond the deceptive conflict between darkness and light \\
  Opens perceptions to the tyranny of the Chekhinah
}

\Lithrim{} is a slave under the \psp{\banelords}{} command. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  I can utter no word, O my God, \\
  unless I be permitted by Thee\\
  And can move in no direction \\
  until I obtain Thy sanction\\
  It is Thou, O my God, \\
  who hast called me into being through the power\\
  Of Thy might, and has endued me \\
  with Thy grace to manifest Thy Cause
}

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  Bread of Bitterness
}{
  From a supplication without response, \\
  the essence of man, his ground giving way, \\
  comes illumination by a sun of great evil \\
  that sets aflame the inner core \\
  and enthrones suffocation and the intolerable without respite \\
  as the joyful reward for a million aborted truths.
  
  This silence that among all man has charged with sacred horror, \\
  it becomes sovereign, in repugnant nativity, \\
  and detaches itself from the bonds \\
  which paralyse a vertiginous movement towards the void.
  
  Breathless ecstatic experience,\\
  it opens the horizon a bit more,\\
  this wound of God;\\
  it is the assassination of the abyss of possibilities, \\
  the depths of being left to holy vultures. 
}





\subsubsection{Sentinels realize \Lithrim}
The Sentinels finally realize what \Lithrim is.
(Do not reveal this until the \humans have already coalesced into \Lithrim.)

\begin{prose}
  \ta{\Lithrim, the hideous that feeds on the souls of the \humans.}
  
  \ta{No. 
    It is worse than that.
    \Lithrim does not feed on the \humans.
    \Lithrim \emph{is} the \humans!
    Picture it.
    Every \human every born into the \iquinian faith, for thousands of years, has been gathered for this purpose.
    Each \human soul is puny, of course, but they number in the hundreds of millions, if not billions.
    All coalesced together to form a nightmare god of colossal power!}
\end{prose}





\subsubsection{\Lithrim awakens the \resphain's latent madness}
When \Lithrim awakens, the madness latent in the \resphain also awakens. 
Even in places where they believe themselves safe the \resphain are seized by madness and begin to fight and kill each other.
They almost ruin everything. 










\subsection{The portal opens}
\Lithrim{} opens the way for the \Voidbringer. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Perfect Dark%
}{
  Hold the candle\\
  Pass the flame\\
  We're all in this together \\
  Cosmic winds are gathering\\
  Coming your way\\
  Telling you you are only a fragment\\
  A fragment of time 
  
  And it's perfect dark\\
  It's perfect dark here\\
  Hear the angels screaming
}





\subsubsection{People feel the \Voidbringer}
As the Cabal plot nears fruition and they are opening the gate to \Erebos, \Miithians can feel the presence of the \Voidbringer: 
An ever hungry, ever consuming emptiness, completely inhuman. 
The older immortals remember it from the \secondbanewar. 





\subsubsection{\Banes{} slip through}
Many \lesserbanes{} slip through into \Miith. 
Not in the same millions that got through in the \secondbanewar, but still quite a lot. 
But not so many that the combined \dragons{} and \resphain{} cannot deal with them\prikker hopefully. 

















\section{Ramiel the Betrayer}
\target{Ramiel betrays Voidbringer}
\target{Ramiel betrays Banes}









\subsection{Summary}
\hs{Ramiel} has decided that he will no longer serve the \banelords. 

\lyricsbs{Dream Theater}{In the Presence of Enemies}{\obeylines%
  My soul grows weaker.\\
  He knows and he waits.\\
  He watches over me,\\
  standing at the infernal gates.\\
  In the hour of darkness,\\
  the moment I feared has passed,\\
  the moment I lost my faith.\\
  Promising salvation.\\
  My soul is my own now.\\
  I do not fight for you,\\
  Dark Master!
}

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Hellfire%
}{
  Before me now I see a dying planet.\\
  Captured souls with microchips implanted.\\
  When warning came you stayed the same.\\
  When warning came you stayed the same.\\
  I am crumbling over the obstacles.\\
  Nothing left to entertain. \\
  The smell of burning corpses. \\
  A new world domain.
  
  Before me now I see a future\\
  A future black\\
  Oh come and save me\\
  I'm under soul attack
  
  I will break out from this madness\\
  There is nothing here but sadness\\
  I'm burning in the hellfire\\
  There must be a way\\
  Waiting for the day\\
  
  Hellfire burns higher\\
  Higher, higher. \\
  Only blood remains\\
  There is nothing more to gain \\
  Take me.
}

He now plans to betray the \banes. 
He intends to siphon energy from the \Voidbringer, thus empowering himself enough to overpower \Daggerrain{} and slay or banish him. 
It is a mad scheme, but Ramiel has always been one for mad schemes. It stems from his sublime arrogance and megalomania (see section \ref{Ramiel's megalomania}). 

It is a good plan, but \Daggerrain{} is too clever. 
The \banelord{} has always known that Ramiel was a loose cannon and could not be trusted, so he had taken precautions. 
When Ramiel finally betrayed the \banes, they were ready for him. 

So Ramiel's plan fails\prikker

\prikker or would fail, if not for the intervention of \Azraid. 
\Azraid{} had always played the loyal Cabalist, faithful servant of the \banelords, but \hr{Azraid hates Banes}{in secret he has always hated them} and \hr{Azraid plots against Banes}{plotted against them}. 
He anticipated Ramiel's betrayal and planned for it. 
So when Ramiel fails, \hr{Azraid helps Ramiel betray Banes}{\Azraid{} steps in and helps him}. 

\ps{\Azraid} gambit cannot succeed without Ramiel's help. 
But he cannot tell Ramiel about it before the very last minute, because he doesn't trust Ramiel's ability to keep the secret. 
(It is \emph{hard} to keep secrets from \Daggerrain.) 
It is thus something of a \trope{XanatosRoulette}{Xanatos Roulette}. 

So, in the end, it turns out that \Azraid{} was \hr{Daggerrain's blind spot}{\ps{\Daggerrain}{} blind spot}. 





\subsubsection{The Ark}
\target{Ark}
\index{Ark}
\Azraid{} and \Ishnaruchaefir plan to use an ancient artifact to destroy \Daggerrain: the Ark. 
The Ark is based on the ruins of the \hr{Sethicus tomb}{tomb of \Sethicus}, which lies in the Realm of \hr{Neevrai}{\Neevrai}. 

It will be difficult, but \Azraid{} is ready. 
He has spent millennia preparing for this day, and he is prepared to sacrifice his life to see it through. 
And he has \ps{\Ishnaruchaefir} awesome Gnosis helping him. 

In the end \Azraid{} destroys himself.  

The Ark was actually an unfinished relic created by \Sethicus. 
It was a part of \hr{Sethicus plan}{his masterplan} to escape \Miith before \hr{Sethican eschatology}{it was destroyed}. 
As was to be expected of an element of \Sethicus's plan, the Ark required a tremendous sacrifice of blood and life and Heart-power to launch it, and more sacrifice still to sustain it on its journey. 





\subsubsection{It all takes place in the \matrix{} world}
Note that all of this takes place in the world of the \matrices. 
The three may not physically meet at all. 
They simply pull at cosmic strings using their \vertex{} abilities. 
Any any \quo{portals} are not physical portals, but a ubiquitous thinning of the Shroud allowing passage into \Erebos{} or somewhere else. 





\subsubsection{Why they wait so long}
One might think \Azraid{} could have betrayed the \banes{} long ago. 
But that would not have worked. 
He was not confident he could have done enough damage before he was caught, eliminated and replaced. 

No, this is a unique opportunity. 
\ps{\Azraid} betrayal has to happen \emph{after} the advent of \Lithrim. 
They need to rely on the Shroud-wide chaos and fluctuations that \Lithrim{} creates.





\subsubsection{Ark fueled by dead \ophidians}
The Ark is a big-ass \hs{living machine}. 

The Ark is built from \Sethicus's old tomb. 
\Sethicus was buried with many other \ophidians and perhaps even \dragons.
Many of them still lie there, dead but dreaming. 
These can be used as fuel to power the Ark and keep it alive. 
When the dead learn about this plan, they are nonplussed. 
They see it as betrayal and fight back. 
They would rather see everyone perish with them than be betrayed and sacrificed for someone else's gain. 

The undead cannot move, but they still have arcane power. 
\Ishnaruchaefir has to expend more of his already badly strained power to overcome the dead and force them to become fuel. 
This is also psychologically hard for him: 
It is another horrible betrayal of his own people, even violating the \dragons' important \hr{Dragons do not eat Dragons}{cannibalism taboo}. 
It is another gruesome scar on his soul. 
But it must be done, and \Ishnaruchaefir knows he is the only one hard enough to do it. 

This should be a climactic thing, another \quo{everything almost going awry at the last minute} twist at the end of the last book. 









\subsection{Ramiel drains the \ps{\Voidbringer}{} power}
Ramiel tries to betray the \Voidbringer. 
This is similar to how Astronema betrays Dark Specter and drains his power in \emph{Power Rangers in Space}. 

He absorbs some of the \ps{\Voidbringer}{} power. 





\subsubsection{How it feels}
He feels himself swimming adrift in an endless, bleak ocean of dark, Entropic power, feels how it almost devours him and his sanity.

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{
  The ravening black worms of madness 
  are devouring the shredded remnants of sanity 
  as I return to my slumbering steel-clad body\prikker \\
  but as the dream-veil lifts, I feel my limbs transform, 
  flesh becoming cold stone\prikker \\
  enshrouded by a dark mantle of obsidian. \\
  And the laughter of the Guardians echoes, 
  carries upon the winds of this spectral eve.
}

Actually, he began doing this much earlier, but it takes a while before \Daggerrain{} \quo{discovers} his treachery. 

Ramiel plans to use his \carcer against the \Voidbringer.

\citebandsong{BlindGuardian:IFTOS}{Blind Guardian}{%
  The Script for My Requiem (demo version)%
}{
  Battle rages higher and higher. \\
  Akron starts to feel my hate. \\
  There's no escaping for the dark souls \\
  I can't control anymore, anymore. \\
  What started in the underworld, \\
  it should be finished here and now. 
  
  I know his tricks, black magic power. \\
  But now it's time for him to say goodbye. \\
  There's only one thing left, the dawn shall arrive. \\
  We've got to get it past, fear the dark side. \\
  Turn off his light. \\
  Turn off his light.
}





\subsection{Ramiel fails}
\target{Ramiel as Xanatos Sucker}
\Daggerrain{} is too clever for Ramiel. 
He had anticipated Ramiel's betrayal and easily stops him. 
He is about to kill and destroy Ramiel\prikker 

Before his death, Ramiel's life flashes before his eyes. 
He realizes that \Daggerrain{} must have anticipated his every move and planned accordingly. 
He has been playing straight into \ps{\Daggerrain}{} hands the whole time. 

He truly \hr{Ramiel is nothing}{is nothing}\prikker 
or so he fears. 

Compare a \hr{Azraid as Xanatos Sucker}{similar scene with \Azraid{} much earlier}. 
Also compare to the scene in \emph{\JuukenSentaiGekiranger} episode 46 (or so) where Rio discovers that his entire life has been masterminded by Long. 

We see inside Ramiel's head as he struggles against \Daggerrain{} and almost dies. 

\lyricsbs{Hate Eternal}{Path to the Eternal Gods}{
  On this journey into death, \\
  I am beside myself in tremendous bliss,\\
  For this allegiance has been made. \\
  Shall my sins be absolved, \\
  washed away by the blood of the sacred lambs? \\ 
  Yet I am not amongst the flock.
  
  The remnants of my life now become my vast illusions,\\
  whilst exiled from your grace. 
  
  With fortitude, with courage, 
  I face all my fears, \\
  on my path to the eternal gods. \\
  With my wrath, with my disdain, 
  I face all my fears, \\
  on my path to the eternal gods.\\
  As I cross over into my final place, 
  I face all my fears, \\
  on my path to the eternal gods.\\
  As I bear trials in my final resting place, 
  I face all my fears, 
  on my path to the eternal gods.\\
}





\subsection{\Azraid helps Ramiel}
\target{Azraid helps Ramiel betray Banes}
At the last moment, before \Daggerrain{} would have destroyed Ramiel, \Azraid{} steps in and backstabs \Daggerrain. 

Ramiel realizes that he had been overreacting before, overestimating \ps{\Daggerrain}{} omniscience and underestimating his own capability. 
Some parts of his plan actually \emph{were} successful, not covered by the \ps{\banelord}{} \trope{XanatosGambit}{Xanatos Gambit}. 
He regains some faith in himself. 

Together, the two \satharioth{} push \Daggerrain{} back. 





\subsubsection{Ramiel and \Azraid{} as kindred spirits}
\Azraid{} criticizes Ramiel for being too overt and honest (\hr{Mystraacht philosophy}{and would be expected of a \Mystraacht}), making him predictable. 
In contrast to \Azraid{} himself, who has managed to creep under even \ps{\Daggerrain}{} radar for twenty thousand years. 

But he is also sympathetic, because he recognizes that Ramiel's situation is like a mirror of his own. 
Back when \Daggerrain{} manipulated the young \Azraid{} into betraying and murdering his brother \Damiarch, he was similarly shocked and disillusioned. 
He shares this with Ramiel. 
This is a rare \trope{PetTheDog}{Pet the Dog} moment for \Azraid. 

A new understanding and empathy suddenly exists between the two \resphan{} lords. 
They are now kindred spirits. 
After this battle they part, not as friends, nor allies, but with a deeper mutual respect than previously. 

\begin{prose}
  Ramiel: 
  \ta{\Azraid. Were you among those who betrayed \Zachirah{} and me?}

  \Azraid: 
  \ta{LOL. Ramiel. 
    I have deceived the \banelords{} for thousands of years. 
    I have deceived everyone. 
    Among all the \resphain, there is no greater fraud than I.
    If I were to answer \quo{no}, would you believe me?
    I would not believe me.}
\end{prose}






\subsubsection{Ramiel imagines hearing \ps{\Daggerrain}{} voice}
Ramiel jokingly imagines hearing \ps{\Daggerrain}{} voice in his head: 
\daggerrain{A minor setback. 
I have planned for this contingency. 
It will take us another 3651 years to get out plan back on schedule\prikker} 
(The number 3651 is a random one that Ramiel pulls out of his ass, but it sounds like something \Daggerrain{} might say.)








\subsection{\Azraid dies\prikker maybe}
\target{Azraid dies}
Maybe \Azraid{} dies. 
He sacrifices himself in order to violently disrupt the \Erebean{} \matrix{}, thus causing it to implode and collapse faster than \Daggerrain{} can restore it to order. 

\ps{\Azraid} death leaves \CiriathSepher{}, its hierarchy and \matrix, in chaos. 
(\hr{CS heirs die}{Not much is left} of the \hr{CS order of succession}{\CiriathSepher{} order of succession} at this time.)
It is now up to Ramiel to pick up the pieces and lead the \resphan{} race, if they are to have a chance of surviving. 

Compare to Anomander Rake's sacrifice in \cite{StevenErikson:TolltheHounds}. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Surrender\\
  Lost in the dark\\
  Without angels to guide me 
  
  Hands of death reaching out for me\\
  I'm longing to rest\\
  I see myself move in need of power
}

He knows the \banes{} better than any other. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  I've looked straight into the eyes of demons rising\\
  So close.\\
  I've had one foot on the other side\\
  For so long. \\
  I've seen evil so evil that all living died\\
  The devil is near.\\
}

He wants to stop the \iquin{} plan. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  You may fool the people, but you can't fool me\\
  No more, not anymore. 
  
  And all the souls turned black\\
  There is no way back
}

He dies. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Stranded with the darkness\\
  It's so cold in here \\
  I feel the rush within me
}

He hopes that \Miith{} (or a fragment of it) now has a future. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Time will mend\\
  Ease the sorrow\\
  Take my hand\\
  There's no tomorrow
}











\subsection{\Daggerrain falls}
\target{Daggerrain falls}
\Daggerrain{} has fallen. 
And the worst part is that the link between \Erebos{} and \Nyx{} fell with him. 
\hr{Daggerrain is the gate}{\Daggerrain{} \emph{was} the link}. Without him, the way is closed permanently. 
Now, the only way for the \banes{} to return from \Erebos{} would be to send spaceships, like they did the first time around. 
That might take millennia, because \Erebos{} and \Miith{} are very distant from each other. 















\section{The Fall of the Shroud}
\subsection{\ps{\Ishnaruchaefir} glaive is destroyed}
\target{Ishnaruchaefir's glaive is destroyed}
\target{Glaive is destroyed}
Throughout most of the story, \hr{Ishnaruchaefir fights to preserve the Shroud}{\Ishnaruchaefir{} has fought to preserve the Shroud}. But at the end, he lets himself persuade to assist in unravelling the Shroud. \Triestessakhin{} is the one who persuades him. 

Ultimately, \hr{Ishnaruchaefir's glaive}{\ps{\Ishnaruchaefir} glaive} is destroyed, its Shroud-weaving effect (as a \hs{weaving artifact}) is broken, and the soul of \Triestessakhin{} is released. 
\hr{Glaive must be destroyed}{This had to happen}. 

She is quite insane after these many thousand years inside the sword, but he manages to lead a conversation with her. She is bitter and tries to make him repent. 

\Ishnaruchaefir: 
\ta{%
  I mourn what I have done, and at times I even regret. 
  But I would not change it, and given the chance, I would do the same again.}

Compare to the scene with Lord Soth and his wife at the end of \emph{Spectre of the Black Rose} by James Lowder and Voronica-Whitney Robinson. 









\subsection{The Shroud is torn}
In the process of this whole thing, the Shroud has been ripped and torn and now lies greatly weakened. A climax of this was the \hr{Glaive is destroyed}{breaking of the glaive \Triestessakhin}. 

The \charade{} is breaking apart and the old world order is crumbled. 

The \hs{Unravelling brings chaos}. 
The world will descend into chaos and anarchy. 

\lyricstitle{\cite{HPLovecraft:TheCallofCthulhu}}{
  The most merciful thing in the world, I think, is the inability of the human mind to correlate all its contents. We live on a placid island of ignorance in the midst of black seas of infinity, and it was not meant that we should voyage far. The sciences, each straining in its own direction, have hitherto harmed us little; but some day the piecing together of dissociated knowledge will open up such terrifying vistas of reality, and of our frightful position therein, that we shall either go mad from the revelation or flee from the deadly light into the peace and safety of a new dark age.
  
  [\prikker]
  
  That cult would never die till the stars came right again, and the secret priests would take great Cthulhu from His tomb to revive His subjects and resume His rule of earth. The time would be easy to know, for then mankind would have become as the Great Old Ones; free and wild and beyond good and evil, with laws and morals thrown aside and all men shouting and killing and revelling in joy. Then the liberated Old Ones would teach them new ways to shout and kill and revel and enjoy themselves, and all the earth would flame with a holocaust of ecstasy and freedom.
}

In a way, this is \hr{Ishnaruchaefir sees three futures}{\ps{\Ishnaruchaefir} nightmare} come true. 

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\prikker 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}















\section[The Return of Tyrasshana]{The Return of \Tiamat}
\target{Ungod}
\index{Ungod}
In secret, \Tiamat was behind the \resphain. 
She was the Ungod of the Outer Darkness.
Her goal was to absorb all intelligent life on \Miith and unite them all in one great Concord. 
She found the \banes and conquered them and made them her slaves, part of her Concord hivemind. 
That was one of the reasons why the \banes were so horrid: 
They were not individuals. 
They were, in a sense, soulless\dash but also part of something greater and terrifying. 

\Tiamat masterminded the fall of Semiza and the rise of the \resphain.
She made Semiza corrupt the \resphain to her service. 
She made them invade \Miith and wage war against the \ophidian races. 

\Tiamat wanted to grow strong and escape from her awful prison. 
The advent of \Lithrim finally freed her. 
She was now free. 
Ramiel, \Azeraid and \Iscrafel managed to destroy \Daggerrain and the \bane hordes, but they could not stop the Mother. 
\Tiamat was now awake, and she would devour the world. 

(\Daggerrain was a servant of the \hr{Voidbringer}, the cosmic god of the \banes. 
The Voidbringer is separate from the Ungod, although they are often conflated by the ignorant.)

But all was not completely bleak. 
\Tiamat's merger with the \banes made her more stagnant and decaying and destructive than she might otherwise have been.
The heroes had destroyed this, the worst part of her. 
And in their own quests they had grown strong.
They now represented a mighty and virtuous force of positive change. 
\Tiamat absorbed them, and in doing so she absorbed their virtue and strenght and made it part of her.
So they would live on in her, and their deeds and legacy would help steer the great Mother. 
Now \Tiamat would devour everything on the planet and then move on to conquer the universe. 

And the Mother spread her wings. 





















