
\part{Sentinels of \Miith}























\chapter{The Amorphous God}
\target{Mephilex' initiation story}
\index{Innermost \Arcana, The}
This short story tells the back-story of \hs{Suthis Mephilex}. 















\section{Summary}









\subsection{Mephilex must learn \arcana}
At the beginning of this story (or another story), Mephilex was young and ignorant.
She was 26 years old. 
As per the traditions of the \Yormissian \rethyaxes she had spent her first thirteen years learning basic skills such as literacy, mathematics and meditation, and her next thirteen years mastering the first six \hr{Arcana}{\arcana} and their spells. 
Now she was ready to learn the True \Arcana that lay beyond the basic \arcana. 
She was ready to descend further through the \hs{Dreaded Gateways}. 
She must also learn the secrets of her family and what went on in the hidden lodge halls in cellars beneath \Yormis. 

She must learn the three \hr{Suthis Innermost Arcana}{Innermost \Arcana of the Suthis clan}.

The story should start like \cite{RobertBloch:TheSecretintheTomb}, with the reader learning that Mephilex was a descendant of a line of sorcerers.






\subsubsection{Mephilex remembers Dristan}
\target{Suthis Dristan dies}
Mephilex had an older cousin, \hs{Suthis Dristan}. 
He was also a \rethyax and had had to learn these same revelations that Mephilex now faced. 

Dristan proved not strong enough.
The revelations drove him insane, so insane that he died of fright.
Mephilex remembered well the time of her cousin's death.
She had been close to him, and the loss of him struck her hard.
Especially because she knew she must one day go through the same trials.
It made her sick to think about it.
She remembered how all food and drink seemed to taste sickly for weeks after Dristan's death. 
That was how bad she felt.

Shortly after Dristan's death Mephilex had been given a special dish, allegedly made from the flesh of a mosca. 
She later remembered that every time she had had mosca, at night she would have strange nightmares. 
She would see \Ubloth.
There would be horrid slime everywhere. 
Sometimes she would be immersed in the slime.
Sometimes it was as if the slime was inside her, pumping through her veins.
It was as if she drowned in the slime, was absorbed by it, became one with the slime. 
It was in her and she was in it. 

\citeauthorbook[p.45]{HenryKuttner:TheBlackKiss}{%
  Henry Kuttner%
}{%
  The Black Kiss%
}{%
  And in that kiss strangeness flooded him.
  He felt a shock and a tingling go through him, and then a sthrill of sudden ecstasy, and swift on its heels came horror.
  Black loathsome foulnees seemed to wash his brain, indescribable but fearfully real, making him shudder with nausea.
  It was as though unutterable evil were pouring into his body, his mind, his very soul, through the blasphemous kiss on his lips.
  He felt loathsome, contaminated.
  He fell back.
  He sprang to his feet. 
}





\subsubsection{Mephilex meditates}
The evening before her initiation, Mephilex sat and meditated. 
She felt a colossal formless power stirring, like a humongous living thing far down in the deep. 
She woke, and it was as if she could physically feel the stone tower quake underneath her, as if shaken by some thing moving far beneath.
She imagined she could hear a spectral groaning from underground.
But she convinced herself that she was just imagining it. 

Later in the story she would feel these reverberations again. 
But every time, when she looked around, it was as if only she could feel it. 

The reason was that her family had been feeding her the slime of \Ubloth for weeks, and they had been feeding her blood to \Ubloth, so the two were already forming a metaphysical bond. 









\subsection{The secret of the \ophidians}
Mephilex's father, \hs{Suthis Cruan}, was her mentor and guide.
He, together with other \rethyaxes, took her down into the deep. 
She saw the marvellous and sinister underground city. 

They took no guards with them, but as they descended further down Mephilex could see furtive shapes creeping in the darkness around them.
They were \hr{Suthis monster slaves}{the clan's monstrous half-\scathaese slaves}. 
She was afraid, but Cruan told her not to worry.
They were not enemies.
The creatures were here to protect and escort them.
She would soon see them up close.
Mephilex did not look forward to that.
The creatures were awful.
Hideously \scatha-like, and yet alien.
Monstrous.
Misshapen. 

It was very dark down here. 









\subsection{The Master}
\target{Mephilex is supposed to meet the Master}
Her father told her that she was to meet the \quo{Master}, the mysterious non-\scathaese lord that ruled the underworld of \Yormis.
This Master was really \hr{Ishtacca}{\Ishtacca}, the eldest \ophidian lord. 

Cruan (or another wise \scatha) told her that the Master and his people had dwelt in darkness for a million years and learned to live without light. 
That was why the city was so dark.

Make it clear that the Master was \emph{not} \Ubloth. 

Mephilex was shocked and repulsed by the sight of the half-\scathaese guard-slaves.
She was also scared by the \ophidian sarcophagi.

The Master was just about to possess a slave body (\hr{Ophidian possession}{as \ophidians did}) so he could talk to her.
Then the enemies attacked. 
They killed the slave body, dispelling the Master. 










\subsection{The secret of cannibalism}
Mephilex learned another horrifying secret: 
Her cousin \hr{Suthis Dristan}{Dristan} had not \hr{Suthis Dristan dies}{died on his own}, but had been killed by his family. 
Worse, they cut up Dristan's body, cooked it and fed it to Mephilex. 
Over the course of several weeks they made her eat all his flesh and drink his blood and fluids. 
That way his body did not go to waste. 
He was full of invaluable genetic material which must be preserved for the good of the bloodline.
He had been their prime scion, but now he had failed, and now Mephilex was their greatest hope.
They prepared his body with powerful spells and made her eat him so that she would inherit the power and purity in his veins. 
They even bound his very soul in his flesh and made her ingest it. 
That way he would live on through her. 

Mephilex was horrified to learn this. 
But later she accepted it.
She began to feel the closeness of Dristan's soul.
She could feel him inside her head, whispering to her.
At first this horrified her, but she learned to accept it.
She realized that she had not lost her beloved cousin.
He was still with her.
It was up to her to triumph where he had failed.
Her family expected it of her.
Dristan expected it of her.
She came to look to Dristan's ghost as a source of strength. 
She took comfort in it, and in the dark marvels of her clan. 

Compare to the main character in \cite{HPLovecraft:TheShadowOverInnsmouth}, who in the end learns to love and embrace his Deep One legacy.









\subsection{The secret of \Ubloth}
Mephilex was now ready for the third \arcanum: 
That \hr{Suthis and Ubloth}{the Suthises worshipped \Ubloth}, and that \hr{Suthis souls and Ubloth}{their souls were bound to \Ubloth}. 

Mephilex had not yet made a pact with any god. 
Her family forbade it. 
So her magic was still weak and immature.
She would soon learn why:
She was to enter into a pact with \Ubloth, her ancestral patron god. 









\subsection{Enemies attack}
But the Suthises had enemies. 
Mephilex herself had a mortal enemy in a rival clan. 
These enemies knew about the subterranean city, for there were other clans than Suthis that served the \ophidian \liches.  
Now, while Mephilex was being guided through her \arcana, the enemies attacked.
They wanted to assassinate Cruan and Mephilex while they were preoccupied and off their guard. 
And they wanted to do it down here in the deep where no one would ever know (for the existence of the underworld city was a secret from the public). 

The enemies attacked.
They killed several.









\subsection{Mephilex flees into the tunnels}
Mephilex was separated from her father and their guards and forced to flee for her life into the dark tunnels below. 
She had only heard half of the story and knew only bits and pieces about \Ubloth, not nearly enough to piece together the awful truth. 
But now, running blind through the black corridors, she stumbled on hidden altars, statues, inscriptions, laboratories and notebooks.
And on one occasion she lay hidden in a corner and listened to her enemies as they walked by her.
And she found evidence that her family sacrificed flesh and souls to \Ubloth. 

She also began to hear the voice of Dristan in her head. 
At first she fled from him and tried to shut him out.
But she realized that he was helping her, and she slowly accepted him as an ally. 
He helped her realize the truth. 

She had a scroll containing the spell she was to use to make the pact with \Ubloth.
Her father had given it to her along with strict orders not to open it until the right time came. 

From all these clues she slowly pieced together the truth.
She realized that her family served some hidden god named \Ubloth that had its shrine in the deeps. 
She realized that she had to make a pact with this god in order to gain her full power. 





\subsubsection{Mephilex encounters horrors}
Mephilex encountered horrors. 
She met awful undead slaves that went about their silent business.
They did not harm her and indeed completely ignored her, but she was still deathly afraid of them. 
She also saw living buildings, and she saw undead monsters and undead buildings that used to be alive. 









\subsection{Into \Ubloth's chamber}
Then she was chased into the deepest central chamber (or cavern).
Here she laid eyes upon the seething, bubbling pit of pure vileness and filth that was \Ubloth. 
She remembered Dristan's cries when he went mad.
He raved about \quo{the amorphous god}. 
She realized that this abomination was \Ubloth. 
This was the god that she was destined to serve. 
A hideous thing of slime that was fed with the flesh and souls of mortals. 
She screamed and cried. 

Her enemies came after her.
Self-preservation took over, and she fought to defend herself.
She managed to hide in a place where her enemies could not easily come at her.
This gained her a respite.
But she realized that she had to act fast. 
She could not fight her enemies.
She was too weak.
She was not yet a full \rethyax.
She realized what she must do: 
She must make her pact with \Ubloth, here and now.

She realized that she had been drinking the effluvium of \Ubloth for weeks, and \Ubloth had been drinking her blood. 
She was already inexorably bound to the loathsome god, whether she liked it or not.
She felt that she had no choice. 
She must bond with \Ubloth.

Fortunately she had the scroll.
She opened it and began the spell. 
She finished the spell and felt \Ubloth's filth seep into her mind. 
And she felt all the souls contained within \Ubloth; those who had given themselves to it, and those whom it had consumed. 

Mephilex had realized the nature of her clan's \hr{Suthis and Ubloth}{horrid symbiosis with \Ubloth}.
She knew she had been eating humanoid flesh and imbibing their souls, and that \Ubloth had been fed her blood, and that she had then been fed \Ubloth's effluvium. 
Finally Mephilex gave herself up to \Ubloth. 
She stepped or leapt into the pool.
She surrendered herself and let \Ubloth flow around her and into her and feed.
In return \Ubloth filled her with sorcerous power. 

Now filled with the power of \Ubloth, Mephilex immediately used it to cast a spell.
She drew energy directly from \Ubloth's body and blasted the minds of her assailants.
She then watched in horror as \Ubloth itself rose up to snatch and engulf her foes and drag them down into its slimy maw to devour their bodies and souls.
She shivered to think that it was she who brought this ghastly fate upon them.
And she shivered to think of the slavering inhuman evil of this loathsome shapeless thing which she is now forever pledged to serve, in this life and the next. 









\subsection{Aftermath}
Afterwards, Mephilex thought back to what happened. 
We hear that she later met the \quo{\hr{Mephilex is supposed to meet the Master}{Master}} and learned to love and worship him. 
Where \Ubloth was abhorrent, the Master was beautiful and splendid and terrible. 
He was not harmed when his host body was slain, for the Master was immortal.
He was the mightiest being in \Yormis save \Ubloth alone, for he is the messenger of \Ubloth and the eternal overlord of \Yormis. 
Praise the Master's name!















\section{Changes}
\begin{changes}
    
  \begin{comment}
  \paragraph{Mikkel Kjær Jensen}
  \end{comment}
  \changesitem{Mikkel Kjær Jensen}
    1. Det er mig ikke helt klart hvordan personerne i din historie ser i
    den underjordiske by. Ja, der bliver nævnt fakler nu og da, men de
    syntes at være der allerede da personerne ankommer og i det første
    tilfælde bliver det ikke nævnt at de bliver tændt, og i den andet
    tilfælde kan det ikke være sket.

    Taler vi her om de klassiske evigt-brændende Hollywood Torches (som
    har brændt siden nogen var der sidste), eller er der tale om andet?

    Hovedpersonen kan i hvert fald ikke se i mørke, ellers giver følgende
    sætning ikke mening:
    "There were few torches, so soon I was crawling on my knees in
    pitch darkness through an inch-thick layer of goo."

    2. Nær slutningen af "The Natural Order" har du et "Blam!". Jeg syntes
    at dette er en øjenbæ, som sagtens kunne fjernes, så "The sound of a
    gunshot ripped through the air." står alene. Jeg syntes det ville give
    et bedre overblik.

    3. “Yuck! This tunnel is full of goo, and it stinks!”
    Denne sætning, i starten af sektion 6, er fuld af Narm. I forhold til
    den sindstilstand som hovedpersonen har, og som bliver vidregivet til
    os. Hvis du ikke kan/vil fjerne sætningen, så overvej i det mindste at
    fjerne den sidste del "...and it stinks", det vil gøre det meget
    bedre, og mindre ufrivilligt komisk.

    Ellers syntes jeg den er fin, godt gået.
    
  \begin{comment}
  \paragraph{Worldbuilding}
  \end{comment}
  \changesitem{Worldbuilding}
    Mephilex should tell us what spells she is studying. 
    In her nightmare she passes some well-known milestones (see the section about \hr{Rethyax meditation}{\rethyax meditation}). 
    Then she is lost. 
    \Ubloth pulls her off her path and into its own clutches. 
    Later, when Mephilex throws herself into \Ubloth's embrace, she also passes through well-known stages of supernatural consciousness (albeit now on a more intuitive level, less analytical and controlled). 
  
    Mephilex mentions that the foundations were built by Suthis Ondra, her ancestor.
    (Add Suthis Ondra to the glossary.)
  
    Mention that the subterranean city is as old as Su-Gelba and Ibthek.
    Perhaps even so old that it was built while mythical \Aamon still stood (where now only the forbidding Tower of \Aamon stands).
    
    The underground temple where Cruan tells Mephilex about the \Arcanum of the Flesh is called the Shrine of the \hr{Uzul-Kaya}{\UzulKaya}.
    
    Make the reference to the war with the \banes more obscure, more vague.
    Just a hint. 
    
    Shorten the trip through the dead city. 
    
    When Mephilex prays to \Nasshikerr, she should not be speaking an easily understandable prayer.
    She recites the \hs{Lesser Shkormi Formula} in the name of the goddess \Nasshikerr who slithers unseen in the shadows.
    
    In the laboratory Mephilex finds a magical symbol that reminds her of the enigmatic and powerful Symbol of \Aamon.
    Some of the spells she sees are written in the language of \hs{Kush}.
    Mephilex knows no Kush, but she recognizes the curved sinuous script. 
    They are very different from the sharp angular \Draconic runes.
\end{changes}
























\chapter{The Master}
\target{Moro and Sperra story}
\target{Mephilex rises to power}
\index{Amorphous God, The}
The novel or novella tells the background story of \hr{Moro}{\MoroCobrel}.

\MoroCobrel and \TulionSperra were young mages in \hr{Yormis}{\Yormis}. 
They were lesbian lovers, with \Sperra as the dominant of the two. 















\section{Intrigue in \Yormis}
During Moro's time in \Yormis there was a big plot brewing.
Some factions fought against one another using ancient magic.
The Sentinels knew nothing of this whole thing and did not learn about it until it was over.
Sentinel resources were spread thin at this time, and they could not keep an eye on everyone.

A rebel faction, which included many \Ubloth cultists, had discovered the \hr{Mummies in Yormis}{crypt full of mummies} and wanted to resurrect them and thus gain an army of undead warriors and conquer the world. 

Another group, which included \hs{Suthis Mephilex}, wanted to stop them. 

\hr{Uldraan Kerross}{\UldraanKerross} was the most politically powerful mage in \Yormis at the time. 
He was horribly evil (read about him). 









\subsection{The Master}
The true ruler of \Yormis was the \ophidian lord \hr{Ishtacca}{\Ishtacca}, called the \quo{Master}. 
The story revolves around him.
Moro and Sperra heard tales of this mysterious and menacing \quo{Master}. 
They gradually discovered who the Master and his people were, and what they were doing in the dungeons below \Yormis.
They learned about the \ophidian quest for immortality.









\subsection{Suthis Mephilex}
A younger, up-and-coming mage of fine breeding and great talent was \hr{Suthis Mephilex}{Suthis Mephilex}. 




\subsubsection{Rise to power}
She wanted to oust \Uldraan and seize power for herself. 
But \Uldraan was still very powerful.
So Mephilex deftly manipulated various people into helping her defeat \Uldraan. 















\section{Sperra and Moro investigate}
\target{Moro and Sperra investigate Mephilex}
\Sperra and Moro suspected that Mephilex was up to something sinister.
They investigated. 










\subsection{Fighting or helping Mephilex}
They wanted to stop Mephilex's evil, but in reality they were being manipulated by Mephilex into helping her defeat her rival, \UldraanKerross. 

Moro started out inadvertently helping the rebels without knowing what they were up to.
Soon she switched sides. 
She helped Mephilex stop the rebels. 
Then Mephilex gained a lot of evil power and became one of the leaders of \Yormis. 

Moro was not quite happy about this. 
She did not trust Mephilex.
Moro feared Mephilex was evil.
She did not want her in power.
But she inadvertently helped Mephilex gain power.
Moro felt a bit guilty about this. 
She also feared she had done more harm than good in her attempts to save \Yormis.

Mephilex now planned to do the same thing as the rebel faction had planned to do.
Only somewhat different. 
She hoped to extract power from the mummies. 









\subsection{In the underground}
Sperra and Moro explored the dark caves underneath Mount \hr{Shrun}{\Shrun} near \Yormis.
They found the \hr{City beneath Yormis}{ruined underground \ophidian city}. 

Here they faced great danger and uncovered untold horrors. 
They saw glimpses of \hr{Degenerate Ophidians}{creeping degenerate \ophidians} and their servitors and monsters, but they were never sure exactly what they saw. 
There were also degenerate \scathae and \humans down there, \hr{Suthis cannibalism}{which were used a food} by the Suthis clan.  

They encountered undead in the underworld: 
\hr{Undead Ophidians}{\Ophidian mummies} and their zombie-like servitors.

They experienced ancestral dread.
Read about \hs{ancestral memory}.





\subsubsection{\Ubloth}
They found the great cavern-temple where lay the loathsome amorphous god \Ubloth. 
They saw the monstrous freaks that had been mutated by \hr{Effluvium of Ubloth}{\Ubloth's corrupting effluvium}.
In a climax of crowning horror they stumbled into the great hall and lay eyes upon \Ubloth itself.









\section{Sperra dies}
\target{Tulion Sperra dies}
\TulionSperra should be the main character and hero of this story.
More than once she risked her life and sanity to save Moro. 
In the end, \Sperra was killed and devoured by the god \Ubloth.
(This should come as a surprise for the reader.)

Moro many many mistakes and was clearly to blame for \Sperra's death.
Moro never forgave herself for this, and remained unhappy and guilt-wracked for the rest of her life. 
The only thing Moro could console herself with was that she had helped remove a gruesome tyrant and replace him with a somewhat milder tyrant. 
Moro only hoped that Suthis Mephilex's long-term evil plans would not prove her an even greater threat than \Uldraan was. 

After this incident, Moro left \Yormis. 
She had seen too many horrible things in the dungeons beneath. 
She wanted to get away from it all.
The whole city reminded her of horror and evil. 
She could not bear it anymore. 

Compare to the entombed saurians in \cite{Nile:InTheirDarkenesShrines}. 



























\chapter{\CarzainPrequelBook}
This book tells Carzain's back story, before he joined the Runger War. 
It details Carzain's travels, Vizicar's awakening and their joint path to \kenosis. 















\section{Overview}















\section{The Mutiny}
\target{Mutiny}
\target{Mutiny chapter}
Carzain and Nishain were betrayed by mercenaries in Heropond Forest. 
Vizicar awakened (for the first time in Carzain's life) and fought, killing the mutineers. 









\subsection{Old description}
Carzain goes to Martinum with his father. Then back.

It is only autumn as they travel through Heropond, but in the \Wylde it feels almost like winter: Hoarfrost lies on the ground, and cold mist fills the air.

The younger trees hate them and want the intruders out of their forest. Carzain finds an older tree that is indifferent, cold, uncaring\dash it knows that the humanoids will die soon enough anyway. 

(To what extent can Carzain read the thoughts of trees? Much of it is probably just guessing based on vague emotional impressions.)

He also sees the \hr{Moons}{moons} in the forest. They look spectral and spooky. Have some Bal-Sagoth-esque imagery about them.






\subsubsection{Carzain dreams of being nothing}
On the way back to \hr{Redglen}{\Redglen}, Carzain dreams \hr{Ramiel is nothing}{his recurrent nightmare of being nothing}. 

He sees visions of humongous gods: 
\Human-like, \dragons, amoebae with pseudopods\prikker





\subsubsection{Betrayed by mercenaries}
On the way back to \hr{Redglen}{\Redglen}, their hired guards mutiny against them. Carzain fights back using magic and suddenly feels a strange ecstasy, a possession. He fights with power he did not know he had and slays the thugs. He is puzzled by the possession experience. 

The magic should be more bloody. I should show how the skin blackens and seethes, let people scream their agony while they boil and burn. They get cramps and spasms and perform a sickly, morbid \quo{dance} before they die from being zapped. 

Maybe fire magic should cause the victim to burn up \emph{from the inside}, instead of just tossing fireballs. Or perhaps tossing fireballs is the beginner's tactic: Easier and cheaper, but less powerful and less accurate. Causing your victim to combust from within is harder, but much more deadly and accurate. It uses the victim's own life force as fuel, burning him to ashes. 

Describe how blisters boil and burst. 





\subsubsection{The Redcor discover the \vertexspike}
A Redcor \matron\dash\Esmerel?\dash is sitting in the Topaz \Chateau, performing divination though \index{aquamancy}. Insert some Bal-Sagoth imagery here. 

\lyricsbs{Bal-Sagoth}{A Black Moon Broods Over Lemuria}{
  And in the dark ethereal mists of winter dreams,\\
  the ebon waters of enlightenment gleam 'neath the Black Moon,\\
  and the Valley of Silent Paths beckons\prikker
}

She discovers the \vertexspike{} that is caused by Vizicar's brief awakening, and realizes something has happened. I am not sure how much the Redcor know about \vertices, but she definitely knows something is up. She goes into research, and eventually they determine that very likely a Scion has awakened. 

\Esmerel{} goes off to wander the lands of \Velcad{} in search of the Scion. A year or so later she finds him, in the midst of the Pelidor-Runger war\prikker






\subsection{Changes}
The mercenaries have guns (pistols or muskets).

Maybe I should edit the date. 

Carzain and Nishain have not been to the Imetrium, merely some big port city in southern \Scyrum. 
They do not know so much Imetric. 
Nishain only knows a few rudiments, and Carzain none at all. 

When Vizicar fights, he ignores the \hr{Itzach pain}{pain that \Itzach{} brings}. 
\Itzach{} Vaimons have ways of using power economically, thus minimizing the pain and risk. 
Vizicar does not care about this. 
He is groggy and sleepy and his senses are dulled, so he thinks he is completely fresh and healthy and has plenty of bodily energy to spare. 
He does not want to be careful and conservative. 
He wants to be flamboyant and teach these damned peasants a lesson. 

After all, he is \VaimonCaliph. 
He is used to being one of the most powerful and skilled Vaimons in the \caliphate, and a Scion to boot. 
He does not stop to consider that he is out-of-touch with his body, or that his new body is weaker and less trained than his old one. 

Remember to have references to the \hr{Shechinah}{\shechinah}. 

After the battle, Carzain has nasty open wounds caused by drawing too much \qliphah{} power. 
He uses these heroic wounds to score Mirai. 
Then he gets healed by Imetric healers. 

The chapters with \ChyrieEsmerel{} and \LocarPsyrex{} do not happen at all. 
Get rid of them. 
At this point in time, no one knows about the \vertex. 
If they did, that would just cause all sorts of trouble and plot holes. 















\section{Ilcas Northstar}
\target{Ilcas Northstar chapter}
\target{Ilcas introduction}
Carzain and Nishain met Ilcas Northstar in \Bryndwin. 









\subsection{Old description}
Carzain and Nishain go back out of Heropond forest to the town of \Bryndwin.

\Bryndwin has its share of monuments (see section \ref{Monuments}): Poles with flags and lamps on them, carved images of gods, heroes and creatures, meant to scare the \Wylde and intruders away.

They encounter \hs{Telcastora Ilcas}, his two \nycans, Razor and Countess, and a bunch of other Imetrians. 

Remember to describe \hs{Telcastora Ilcas's appearance}.

They see a big \hr{Mulgron}{\mulgron}. Carzain is impressed by how the \mulgron is even bigger than an elephant. 

Remember to \hr{Nycans are frightening}{describe the \nycans as frightening and alien}.

Carzain reaches out his hand and tries to touch Razor's snout. Razor's eyes narrow slighty, and he retracts the hand. 

The two Vaimons hitch a ride back to \Redglen with Telcastora Ilcas and his Imetrians. Carzain befriends Ilcas and his \nycans, Razor and Countess. 

They part ways somewhere in Pelidor. 

Carzain has a wound from his battle with the thugs, but he suppresses the pain, as he doesn't want to show weakness in front on Telcastora Ilcas. I should try to portray him as somewhat over-proud and silly. 

During the trip back, he is treated by an Imetric healer-surgeon. But he retains the scars: One in his leg, one in the side of his stomach. 
The surgeon's treatment is more bloody than the Iquinian healing he is used to, but it is at least as effective. The Imetrians have a scientific approach to medicine, whereas the Redcor repress real science in favour of traditional mysticism. 
This makes Carzain doubt the value of Vaimon tradition.









\subsection{Changes}
Write about Carzain's meditation. 

Replace \quo{resonance} by \quo{\shechinah}.
Add \quo{\shechinah} to the glossary. 

\Bryndwin has a \hr{Wylde border}{\Wylde border} with charms and totem poles. 

Carzain introduces himself to Ilcas: 
\ta{I am \VizicarDurasRespina.} 

Ilcas carries a gun. 

When negotiating with the priest: 
Carzain has no interest in theology, but he is skilled at faking interest, if he does say so himself. 
It is a skill he has honed when picking up women. 

On their first day on the caravan, Carzain talks to Ilcas. 
Ilcas tells stories of his heroic and violent deeds, and of his heroic and violent sword. 
He especially tells of how he has fought against the Imetrium's arch-nemeses, the Rissitics. 
\hr{Rissitics and Runger}{This is important. The Rissitics are important to the story.} 
Make sure to paint the Rissitics as threatening and imposing foes.
Tell of how they wear animal masks and have warrior orders named Order of the \hr{Order of the Crocodile}{Crocodile} and Jackal and Scorpion and \hr{Order of the Hippopotamus}{Hippopotamus} and so on. 

These associations of war makes Carzain see visions of his past, but still very vague, little more than regular daydreams. 

Then Carzain asks to hold the sword. 
Ilcas refuses. 
But he shows him the sword and swings it around a bit himself. 
And tells him about it. 

Carzain scores Mirai faster (already on the first night) and more solidly. 
I need to show the reader how cool he is. 
He pulls off a pick-up comparable to the way Tony Stark scores the reporter girl in the movie \cite{Movie:IronMan}: 
\ta{I'd be willing to lose a few hours of sleep with you.}
She is impressed already after their very first meeting. 

Have more Vizicar in the sex scene with Mirai. 
And after it. 
He talks to Carzain in his head. 
Perhaps from Vizicar's POV. 

The night after sex, he lies awake thinking wildly about what in all of \Iquin and \Itzach is happening to him. 
When he falls asleep, he meets Vizicar in dreams. 

\target{Vizicar drives Carzain to war}
After this night, Vizicar drifts away. 
Carzain feels lost. 
Like something is missing inside him. 
Some important clue in some important mystery. 
Some part of himself. 
He feels like half a man. 

Carzain goes off to war hoping to find Vizicar again.  
He seeks out battle in the hope of provoking more Vizicar action in his head, so he can figure out who Vizicar is and what the deal is. 
Maybe Vizicar subconsciously imparts in him a desire to fight and seek glory. 
















\section{Visions and dreams}
Carzain had visions and dreams. 
As did Vizicar. 

They met in dreams and talked to one another, but neither understood what was going on. 
Both thought the other man was a figment of their own imagination. 

The dreams were triggered by combat and war, or the expectation of it. 









\subsection{Vizicar's motivation}
Vizicar knew he is more than a \human, and he told Carzain this. 
Vizicar wanted to attain \kenosis and regain his body, power and memory. 
Then he wanted to achieve \apotheosis and learn his true nature.
Then he would be a god.












\section{Carzain in the War}
\target{Carzain joins the army}
Pelidor went to war against Beirod. 
A trivial border dispute, but bloody enough. 

At this point, Carzain knew there was something odd going on with him. 
Carzain joined the army because he hoped it would help him find out what was happening to him, who he was and who Vizicar was. 
He could hear Vizicar stirring in his head at the prospect of war and glory: 

\begin{prose}
  \tho{I thought so. 
    It is this sort of thing that brings you out.
    \quo{Vizicar}.
    Whoever you are.
    I will find out what the deal is with you.
    And how I can get rid of you.}
\end{prose}







\subsection{War is Coming}







\subsubsection{Carzain joins the army}
News of the impending war with Runger reaches \Redglen. 

Carzain's parents hate war. Perhaps they have even done stuff to get him to dodge the draft - without his knowledge. Any any rate, Carzain goes to the barracks and signs up. See, Carzain is bored as fuck. He's a big boy in a small town. He has a craving for greatness, fame and power - things he cannot possibly find in \Redglen. He wants to explore and wants something to happen. So he goes off to war. At this point, Carzain is maybe 22. 

In the Pelidorian army, Carzain is welcomed because of his magical knowledge. Pelidor has few mages, since neither the Imetrium nor the Iquinian church support them. He is assigned to serve under Captain Archibald Curwen, the commander of the \ishrah of the Pelidorian army.  
Carzain also learns a lot of combat technique. As he studies combat, he finds all sorts of things coming naturally to him, as if he already knows them but has just forgotten he knew. 

On the way to \Malcur, Carzain calls dibs on a horse\dash a gray stallion named Arrow\dash rather than a \relc. Later, having trouble riding the beast, he ponders his decision. Seeing some of the others getting easily ahead on their \relcs, he realizes that a horse is not necessarily better. It is just that horses are more Vaimon-like. In stories, Vaimons always ride horses, so when he pictures himself in his head as a great Vaimon hero, he sees himself astride a horse, not a \relc or other reptile. Carzain realizes that he is a status-fixated snob. 





\subsubsection{Carzain and the Goldsmiths}
He talks to the Goldsmith brothers. 
He talks of how he is destined for greatness. 
At this point he remembers \hr{Ramiel dreams of being nothing}{his recurring nightmare of being nothing}, and he tries desperately to convince himself that he is not nothing. 
He tells himself that he is big and important, because he fears that dream. 









\subsection[To Malcur]{To \Malcur}
Carzain \travelled to \Malcur to join the Pelidorian \ishrah.

On the way he met Adrian Testor. 

In \Malcur he met Archibald Curwen. 

Have plenty of Vizicar scenes early on, including before, during and after his signing-up to the army. 
(If \quo{The Mutiny} and \quo{Ilcas Northstar} are kept in \TwilightAngelRememberEmph, then include lots of Vizicar scenes there. Otherwise move them to the prequel story about Carzain.)

Vizicar (when he gained some \kenosis) liked the life of an adventurer. 
It was a refreshing change of pace from the court life he was used to, full of responsibility and chains. 
This was a new kind of freedom, and Vizicar loved it. 





\subsubsection[Carzain meets Delph and Tsekkect]{Carzain meets Delph and \Tsekkect}
\target{Carzain meets Delph}
Carzain meets \hs{Delph} and \hr{Tsekkect}{\Tsekkect}.

They are cheerful guys. 
They befriend Carzain and show him around the barracks, where, among other things, Delph utters his classic line: 
\ta{Life in the army is great. We get food, money, a shot at glory, and the best pussy that money can buy. Well\prikker the best pussy that \emph{our} money can buy, anyway.} 

To which Carzain replies: 
\ta{And all they ask in return is that we fight to the death.}






\subsubsection{Carzain's idealism}
At the beginning of the story, \hr{Carzain's idealism}{Carzain is quite idealistic}.





\subsubsection{Vizicar awakens a little bit}
At some time at the beginning of the war, before Carzain's first battle in the army, Vizicar surfaces a little bit. 









\subsection{To battle}
They go to battle the enemy. 





\subsubsection{Carzain and Delph practice with swords}
Carzain and Delph practice their swordsmanship. 

When the two duel, Carzain mostly loses. He knows some technique, taught to him by Sir Guy in \Redglen, and he is taller, which gives him a better reach. But the shorter and cruder Delph is faster and more agile, and he fights dirty. 

Carzain: \ta{You fight dirty, you know that?}

Delph: 
\ta{No, I just fight like a \meccaran. 
  That attitude of yours is just \human{} provincialism.}





\subsubsection{Carzain won't smoke}
Carzain hangs out with some soldiers. The others smoke some kind of strong drug, like hash or marijuana. 

\begin{prose}
  Soldier: \ta{Come on, \Shireyo, get over here and smoke.}
  
  Carzain: \ta{No, I don't touch that. It's filth.}
  
  Soldier: \ta{Why do you say that?}
  
  Carzain: 
    \tho{%
      Why \emph{do} I say that? 
      Because my father told me so, but I am not going to tell them that. Think, Carzain, think! 
      I can't lose face in front of these guys. 
      Say something witty.} 
    \ta{Something witty.} 
    \tho{Phew. Nicely salvaged, Carzain.}
\end{prose}





\subsubsection{Curwen and Carzain eat}
The officers of the Pelidorian army are eating a luxurious meal. This includes the \ishrah. 

Curwen: \ta{Ah, by \nieur, I love food.}

Carzain: \ta{Food is good, but I like sex better.}

Curwen: \ta{Meh. Most women cook better than they fuck.}

Both: \ta{LOL.}









\subsection{The \Caliph Inviolate}
The sortie encounters a small Rungeran force. They fight. 

Carzain fights and kills. 
But he is not as great a warrior as he fancies himself. 
So he gets clobbered and takes wounds. 

He calls out to Curwen-tachi for help. 
They save his ass. 

Then Vizicar awakens. 
It's due to a combination of factors: 

\begin{itemize}
  \item The pure rush of combat. 
  \item The anger and shame over being defeated in combat by such lowly grunts. 
  \item The wounds leave Carzain's own conscious mind weakened, making it easier for Vizicar to take over. 
\end{itemize}


% Recall that Carzain is a Scion, an incarnation of the \Malach{} Ramiel. 
% Occasionally, when he fights and kills, Ramiel awakens in him, and he hears the voice of \VizicarFull, the previous incarnation of Ramiel. (This is inspired by, and similar to, how Rand al'Thor in Wheel of Time hears the voice of Lews Therin Telamon. But where Lews Therin is mad, annoying and even dangerous, Vizicar is sane and a powerful ally.) 

% Anyway, Carzain fights and kills, and Vizicar comes along and takes over. 

Curwen immediately senses something fishy, probably a \vertexspike{}. 

This time there is a struggle between Carzain and Vizicar, as Carzain tries to get back in control of his own body. 

%After the battle, Carzain falls unconscious as Vizicar retreats. The prolonged, unaccustomed possession and the struggle between the two personas was too much for his consciousness to take. 

After the battle Curwen probes, prodding Carzain into telling him stuff. Carzain tells a little of what he knows, but it's not much. 

Carzain's body is in a bad shape. 
Vizicar is a harsh master and takes poor care of it. 
This is because Vizicar is only half-awake. 
He's still in a half-dreamy state, and his senses are weakened. 
He doesn't entirely register the pain, so he just pushes on. 
So after the fight Carzain is a useless wreck, barely conscious. 

Maybe Carzain asks the others: \ta{Did I save the da?} 

The others: 
\tho{Save the day? You crazy fuck, you nearly killed yourself, and maybe us, too.} 
\ta{Um, yeah. Sure. You saved the day.}

Delph is scared by Carzain's weirdness. Maybe insert an inner monologue with Delph about how Carzain is a crazy weirdo: 
\tho{Typically. 
     Finally I meet a guy who seems trustworthy, who might become a true friend, and turns out he is a madman. 
     Or possessed by \mdaemons{}, or whatever. 
     Huh. 
     That'll teach me to trust a sorcerer.}

During the fight, Carzan does something stupid and reckless. 
Perhaps he sees an enemy Vaimon and goes in to capture his sabre. 
Afterwards, Curwen bitchslaps him and scolds him: 
\ta{You crazy fuck, \Shireyo!
    What the fuck were you trying to do?
    You very nearly got yourself and the rest of us killed!}
He grabs Carzain by the collar. 
\ta{Let me tell you something, boy.
    Your insubordination stopped being charming a long time ago. 
    Now either you get in line or I'll have you beaten!}





\subsubsection{Vizicar dreams}
Have another scene that describes the battle from Vizicar's point of view. 










\subsection{Dark Crypts of the Mind}
Now that Vizicar is closer to the surface, Carzain begins to \hr{Ramiel dreams}{share his visions and nightmares}. 

He is haunted by the tortured, hateful faces of shackled ghosts. They show him their world: Cold, cruel, dreadful. They hate him and desire to drag him down into their prison\dash groping for him with their clammy, hideous hands. 

He awakens full of terror, and also a tinge of guilt. He has a feeling that he is somehow responsible for their torment. 

He also has vague dreams of lost greatness\dash \hr{Visualizing a matrix}{unconsciously visualizing} the \hr{Mystraacht Matrix}{\Mystraacht{} \matrix}. Feelings of having been betrayed, having lost his power and his memory, upon which his enemies descended upon his weakened self like vultures, usurping his rightful place and \honour and forcing him into flight and hiding. 
%, having his rightful place, power and \honour usurped

When he wakes he thinks about the whole thing. 
Part of him is horrified at the madness that is consuming him. 
But another part is excited. 
Because the possession brings \emph{power}. 
And a feeling of being destined for greatness and glory. 
This is what he has always dreamt of. 

But he has doubts. 
Maybe these feelings are fake. 
Maybe the possessing \Archon{} is brainwashing him, all the while making him feel like it is the right thing to do. 
Maybe he is being mentally deceived. 

But it still feels good. 

He thinks of the legend of \hr{Lestor}{Lestor \Delaen}. 
He dealt with \qliphoth{} despite everyone's advice. 
It was dangerous. 
He became a dark and controversial figure, but also a hero who achieved great things. 





\subsubsection{Carzain thinks more on his madness}
Part of him is horrified at the madness that is consuming him. 
But another part is excited. 
Because the possession brings \emph{power}. 
And a feeling of being destined for greatness and glory. 
This is what he has always dreamt of. 

But he has doubts. 
Maybe these feelings are fake. 
Maybe the possessing \Archon{} is brainwashing him, all the while making him feel like it is the right thing to do. 
Maybe he is being mentally deceived. 

But it still feels good. 

He thinks of the legend of \hr{Lestor}{Lestor \Delaen}. 
He dealt with \qliphoth{} despite everyone's advice. 
It was dangerous. 
He became a dark and controversial figure, but also a hero who achieved great things. 

Maybe move this to \quo{The \Caliph Inviolate}. 





\subsection{Vizicar}
Vizicar fights to gain control of his own body. 

\lyricsbs{Marduk}{Voices From Avignon}{
  Speak through me. Speak through me.\\
  The sin must be washed away with blood.\\
  Dream through me. \\
  Called to a new life through death.\\
  Called to a new life through death.\\
  But what shall you reach for when all \colours fall?\\
  Overwhelmed with maledictions. \\
  Feel the rays of redemption of a brand new Sun.
  
  Choking. Asphyxia. \\
  Inhale the Darkness, lungs filled up. \\
  Asphyxia. Asphyxia. \\
  But who shall you reach for when all \colours fall?\\
  Long-drawn moans and piercing cries \\
  blend with prayers and litanies. \\
  Faces bone dry. Condemned as the river everybody drank of. \\
  Inhale! Inhale!
}

\ta{I will win the power and glory I deserve. 
  Not just as \VaimonCaliph, but higher yet. 
  I am a Scion. 
  I am a \Malach. 
  I will achieve the \apotheosis{} and become one with \Iquin{} and \Itzach.
  That is my purpose as a Scion. 
  
  But first I must gain control of my own body. 
  Right now I live out an ignominious existence as a ghost in a boy's head. 
  I am nothing\prikker}

This makes him remember his nightmare of being nothing. 
He drifts away. 

He philosophizes. 

\lyricsbs{Emperor}{Sworn}{
  Four eyes as two in one.\\
  The forward circular view that never ends.\\
  An orbital voyage throughout the endless sphere of all,\\
  where time is lost and everything transcends.
  
  A graceful presence at stolen time
  
  As ghosts to the world.\\
  Ghosts to the world.
  
  For ice, outside, are we apart.\\
  As cold and eerie mist to the hand.\\
  Ever floating on its course\\
  towards the heights of shadowland.\\
  
  Thus appear the truly sworn.
  
  To be seen.\\
  To be feared.\\
  Yet, not to be reached.
}





\subsubsection{Lost in the labyrinth}
He is trapped in the labyrinths of \itzach{}, lost and searching for those precious and ephemeral windows through which he can peer out through Carzain's eyes and affect the world through Carzain's body. 

\lyricsbs{Emperor}{Ensorcelled By Khaos}{
  In an endless maze begotten,\\
  to dead ends led by fools.\\
  I sought a plague for those\\
  who smiled at walls in humble fear.\\
  
  Yet, belligerent ways came to an end.\\
  No war could ease my hunger.\\
  By craving death I was to darkness reborn.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine.
  
  No peace for me. No peace I seek.\\
  My quest goes far beyond.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine.
  
  I hail the greatest fall.\\
  Dark is the spirit of my token.\\
  Dark is my call.
  
  Still craving, still torn.\\
  Hear me, master of this realm\\
  to which I was reborn.
  
  \ta{Bearer of my stigma. Thou art of me.\\
  Yet, claim no gift, but guidance.\\
  For I am the giver of temptation.\\
  Thou art the executor of Thy rewards.}
  
  Dark is the spirit of my token.\\
  Dark is my call.
  
  The cosmic forces driving me,\\
  more noble, more free.
  
  Take me.

  Love and hate and all in between,\\
  I greet them all in ecstasy.\\
  Venus, seduce me.\\
  Mars, possess me.\\
  Tear my soul from sanity.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine and I am thine.
}









\subsection{Reads about Scions and Vizicar}
Maybe Carzain overhears someone (\Esmerel{} and \Racel{}?) talking about Scions. 
Maybe he is half-unconscious and they are standing over him, talking about him, trying to decide his future. 

He asks someone about the story of the Scions. 
Who? 
Perhaps \Racel, but more likely some other mage in the \ishrah. 
Perhaps \Sanyor. 

Anyway, he is told the story of the Scions. Or a version of it. Remember to have many false details, which can be brought into question later. 

Later, he goes into a library in \Forklin{} and reads about \VizicarDurasRespina. 
There isn't a big public library, but there are churches, and they have books. 
He goes into a church, introduces himself as an \ishrah{} mage and pulls a \trope{BavarianFireDrill}{Bavarian Fire Drill}.
He knows he has to use the same body language, frame control and social engineering skills that he masters when picking up women.
It works.
He gets his hands on the writings.

He also finds references to \hr{Vizicar's notes}{Vizicar's notes about \Malachim}, but can find no fragments of the notes themselves. 

He also finds references to \hr{Iolivine's notes}{\ps{\Iolivine} notes}. 
He has heard before that these notes are of exceptionally high quality, but he had been unable to find any copies of them. 
\hr{Redcor bogarted Iolivine's notes}{The Redcor are bogarting the notes}. 
This is one of the reasons he wants to go to \Redce. 

Among other things, he learns that \Belzir{} was an incarnation of an \quo{evil} \malach, and that she caused the \HundredScourges{} with her wicked \malach{} powers. 

More importantly, he learns that he is not mad. 
There are no \qliphoth{} controlling him. 
Instead, he is a Scion! 
He is an \uber-dude! 

He is happy. 









\subsubsection{Carzain reads about Scions}
Carzain is always researching what he is, always looking for more knowledge of Scions. 
He hopes it will lead him to \apotheosis. 

So he goes into a library in \Forclin{} and looks around. 
There isn't a big public library, but there are churches, and they have books. 
He goes into a church, introduces himself as an \ishrah{} mage and pulls a \trope{BavarianFireDrill}{Bavarian Fire Drill}.
He knows he has to use the same body language, frame control and social engineering skills that he masters when picking up women.
It works.
He gets his hands on the writings.

He also finds references to \hr{Vizicar's notes}{Vizicar's notes about \Malachim}, but can find no fragments of the notes themselves. 

He also finds references to \hr{Iolivine's notes}{\ps{\Iolivine} notes}. 
He has heard before that these notes are of exceptionally high quality, but he had been unable to find any copies of them. 
\hr{Redcor bogarted Iolivine's notes}{The Redcor are bogarting the notes}. 
This is one of the reasons he wants to go to \Redce. 

Among other things, he finds references to \Belzir. 
He already knows she was a Scion, allegedly an incarnation of an \quo{evil} \malach, and that she caused the \HundredScourges with her wicked \malach powers. 









\subsection{Why are you in my head?}
Somewhere along the way, Carzain-tachi get into a fight. Vizicar awakens. This time, after the battle Carzain falls unconscious. He dreams and meets Vizicar. 

He sees before his eyes a man who looks to be perhaps his father's age. 
But still strangely similar to himself. 
His complexion is much lighter, though. 
His long hair is blonde rather than black, and he wears a matching moustache. 

Carzain: \ta{Who are you?}

Vizicar: 
\vizicar{%
  Who am I? How can you not know who I am? I am \VizicarDurasRespina! The \caliph!}

Carzain: 
\tho{%
  \quo{\Caliph}\prikker is he the reason why that word has been popping up in my head?} 
(Maybe he doesn't think this until after he awakens from the dream-conversation.)

Carzain: \ta{Why are you in my head?}

Vizicar: \vizicar{Why are you in \emph{my} head?}

Carzain: \ta{I was here first.}

Vizicar: 
\vizicar{%
  Unless\prikker oh, \qliphoth\prikker unless I\prikker oh, by \iquin{} and \nieur. I must be dead.

  Yes, I remember now. Those vile worms killed me. \quo{Disease}, they called it. Hah!}

Carzain: 
\tho{%
  Fuck. 
  Not only is there a madman in my head, but now the madman is talking to himself!}

Carzain wonders what the deal is. 
How does this fit with the theory that it was the Midnight \Qliphoth{} that took control of him? 

Later, Vizicar apologizes to Carzain for putting him through Hell by his own recklessness, by ignoring the \hr{Itzach pain}{pain of \itzach}. 
Vizicar admits that he has been crazy and has fucked their body up. 









\subsection{Changes}
\begin{changes}
    
  \begin{comment}
  \paragraph{War is Coming}
  \end{comment}
  \changesitem{War is Coming}
    Remember to have references to the \hr{Shechinah}{\shechinah} in Nishain's speculations. 
    
    Rewrite the \quo{I want to fight} section from the officer's POV. 
    
    Mention Carzain's age (\quo{a young man, around 25\prikker}). 
    
    Make sure the soldiers notice that Carzain is a bit swarthy (being half Geican). 
    
    This might be the place where Carzain introduces himself:
    \ta{I am \VizicarDurasRespina. No! Wait\prikker I am Carzain \Shireyo\prikker}

  \begin{comment}
  \paragraph{To \Malcur}
  \end{comment}
  \changesitem{To \Malcur}
    Rewrite the scene where Curwen and Carzain meet, so it is from Curwen's POV. 
    
    Curwen should be smoking his pipe. 
    
    Mention Carzain's age (\quo{a young man, around 25\prikker}). 
    
    This might be the place where Carzain introduces himself:
    \ta{I am \VizicarDurasRespina. No! Wait\prikker I am Carzain \Shireyo\prikker}
  
  \begin{comment}\paragraph{\Forklin}\end{comment}
  \changesitem{\Forklin} 
    Get rid of \Racel. 
    
    Carzain is \hr{Carzain PUA}{a great PUA}. 
    He \emph{does} score in \Forklin.  
  
  \begin{comment}
  \paragraph{The \Caliph Inviolate}
  \end{comment}
  \changesitem{The \Caliph Inviolate}
    Again, Vizicar ignores the \hr{Itzach pain}{pain of \Itzach}, and Carzain gets burnt and wounded as a result. 
    
    Remember the \hr{Itzach pain}{pain of \itzach} when Curwen casts magic. 
    
    Remember to have references to the \hr{Shechinah}{\shechinah}. 
    
    Curwen needs to tell the reader that the \ishrah{} mages are equipped with plate \armour. 
    They just do not wear it when \travelling, nor on stealth missions like this. 
    But when the battle comes, he misses it. 
    
    Maybe Vizicar holds back his power and magic. 
    He does not want to arouse suspicion and get caught. 
  
  \begin{comment}\paragraph{\Tsekkect{} and Delph}\end{comment}
  \changesitem{\Tsekkect{} and Delph} 
    Make sure people like \Tsekkect{} and Delph have inner lives of their own and don't spend all their time gaping at Carzain. 
\end{changes}
















\section{Mercenary}
After this short war ended, Carzain left the army and became a mercenary and adventurer.
























\chapter[Twilight Angel, Remember]{\TwilightAngelRemember}
\target{Twilight Angel, Remember}
\input{Story/Sentinels01Notes} 

























\chapter{\TheKenosis}
\input{Story/Sentinels02Notes}























\chapter{\RamielsAwakeningBook}
\input{Story/Sentinels03Notes}















\chapter{\ThirdBanewarBook}
\target{Third Banewar}
\target{TBW}
This book details what would later be retroactively called \thirdbanewar, the final showdown with the \banes. 















\section{Overview}









\subsection{The Unravelling brings chaos}
\target{Eschaton: ThirdBanewarBook}
The \hs{Unravelling brings chaos}. 
The world is slowly going mad. 
It will get much worse\prikker

See also the general section about the \hs{Eschaton}. 





\subsubsection{Ghosts escape}
Now, as the \hr{Sephirah plan}{\sephirah{} plan} is approaching fruition, the \carcer{} of \Iquin{} is filled to the bursting. 
Due to the \hs{unravelling}, \Iquin{} has grown unstable and leaking. 
Ghosts seep out and escape into the world, in droves. 

Compare to the ghosts and the Spectres in \cite{PhillipPullman:HisDarkMaterials}. 









\subsection{The world goes mad}
\target{The world goes mad}
Have a longer story where the world goes mad. 
More people discover the truth about \iquin, but by then it is too late, and their souls are too deeply bound to \iquin to break free. 

They also discover that there are even older and more malevolent things in the world than \iquin.
Things perhaps even more inimical to them.
So that even if \iquin is a parasitic soul prison, it is perhaps better than the alternative. 

The end of the world is heralded by earthquakes and floods and other natural catastrophes. 

Compare to the movie \cite{Movie:IntheMouthofMadness}, and \cite{RobertBloch:StrangeEons} and \cite{RPG:CallofCthulhu:EndTime}. 

Have scenes of chaos as in \cite{TimCurran:TheSpawning}.

See also the general section about the \hs{Eschaton} and the section about \hr{Eschaton: RamielsAwakeningBook}{the cataclysmic events} that happen at this time. 

\citeauthorbook[\quo{First Thought in Three Forms}, p.86--100]{%
  BentleyLayton:TheGnosticScriptures%
}{%
  Bentley Layton%
}{%
  The Gnostic Scriptures%
}{
  Now, when the great authorities knew that the time for fulfillment had come\dash as when labor pains are felt by a lying-in woman\dash and that it was near the door, and that just so, destruction had drawn night, all the elements together shook.
  And the foundations of Hades and the ceilings of chaos moved.
  A great fire broke out in their midsts.
  And the rocky cliffs and the earth moved as a reef is moved by the wind. 
}

Seek inspiration in the Book of Revelation in the \emph{Bible} and other religious eschatology. 

\lyricsbs{Slayer}{Raining Blood}{Raining blood from a lacerated sky.\\
  Bleeding its horror.\\
  Creating my structure.\\
  Now I shall reign in blood!
}

\lyricstitle{\cite{HPLovecraft:TheCallofCthulhu}}{
  The most merciful thing in the world, I think, is the inability of the human mind to correlate all its contents. We live on a placid island of ignorance in the midst of black seas of infinity, and it was not meant that we should voyage far. The sciences, each straining in its own direction, have hitherto harmed us little; but some day the piecing together of dissociated knowledge will open up such terrifying vistas of reality, and of our frightful position therein, that we shall either go mad from the revelation or flee from the deadly light into the peace and safety of a new dark age.
  
  [\prikker]
  
  That cult would never die till the stars came right again, and the secret priests would take great Cthulhu from His tomb to revive His subjects and resume His rule of earth. The time would be easy to know, for then mankind would have become as the Great Old Ones; free and wild and beyond good and evil, with laws and morals thrown aside and all men shouting and killing and revelling in joy. Then the liberated Old Ones would teach them new ways to shout and kill and revel and enjoy themselves, and all the earth would flame with a holocaust of ecstasy and freedom.
}

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\prikker 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}





\subsubsection{Storm in the afterlife}
At this time there is such a furious storm of chaos raging just outside \Miith's walls that it is shaking even the afterlife. 
All cultures are losing mortal souls at an alarming rate.
And even immortal souls are in danger of being swallowed up by the consuming emptiness outside, where hungry and mindless gods gnaw and rage and howl. 
Compare them to the dancers around Azathoth's throne in \cite{HPLovecraft:TheDreamQuestofUnknownKadath}.

The Shroud has created an unnatural pressure inside the walls of \Miith. 
Now that it is all about to come apart, the blind powers of the outer spaces are back with a vengeance. 
Immortality is no longer certain. 
The immortals suddenly know new kinds of fear. 









\subsection{\Voidbringer must be stopped}
The \dragons{} and other \bane-opponents know that if the Cabal manage to open the portal to \Erebos{} as wide as they did in the \secondbanewar, they will be able to let in millions of \bane{} warriors. 
There is no way in fucking Hell the \Miithians will be able to deal with that many.
They are fewer and weaker than they were last time. 
So they must stop the portal. 








\subsection{Aloof \dragons must be roused}
There were some \hr{Aloof Dragons}{aloof \dragons} who took no part in the \feud.

The aloof ones did not care that \hr{No new Dragons are born}{almost no new \dragons were born} since the \hr{Heart weakened}{weakening of the Heart} began.
The aloof ones were powerful and immortal and had the luxury to wait a few thousands or even tens of thousands of years between procreating. Many of them were over 20,000 years old and saw the war with the \resphain as a temporary nuisance. 

\Ishnaruchaefir and \Secherdamon were similarly old and would likely have thought the same, but the war came horribly close to them when some of their close family members (Nexagglachel and \Ishnaruchaefir's three sons) were destroyed by the \resphain.
Now, in the \thirdbanewar, \Secherdamon or \Ishnaruchaefir had to convince the aloof ones that the war was more than a nuisance and that its conclusion would have great repercussions for all \dragons, even the ones who had fled to \Machai.
Eventually some of the aloof ones became convinced. 
Not all, but enough.

The conclusion of the war WAS important.
The aloof ones could hide in \Machai, but they could not really get away. 
They were still bound by the Heart and would suffer its fate.
Either that, or they would have to evolve, abandoning their Draconic nature entirely and becoming something different.
\Ishnaruchaefir and \Secherdamon knew this might be an option\dash{}to flee to \Machai and abandon \dragonkind\dash{}but it was not a palatable one. 
They both wanted the Draconian race to survive.
\Secherdamon wanted to win the war and was willing to enlist the \xs, with all the associated costs.
\Ishnaruchaefir did not like that idea.
So he looked outward into the universe for other ideas.









\subsection{Ramiel is mad}
Ramiel tries to hide it, but \hr{Ramiel is mad after awakening}{his sanity has suffered badly}. 









\subsection{Clean \humans}
There are some \humans who are \quo{\hr{Clean Humans}{clean}}, in the sense that they have no blood of the \quo{\hs{Men of Light}} and thus do not carry \Lithrim inside them. 
These \humans still have \bane and \resphan blood, but no \Lithrim.
This means that they are unaffected by the \hs{Second Advent}. 

Some of these \humans are among the heroes. 
They help the immortal heroes.
They accomplish some minor things and manage to make a difference. 
Then they die at the end.
But they die a heroic death, having helped ensure that the Ark could escape. 









\subsection{\Neevrai}
Much of this book takes place in \hr{Neevrai}{\Neevrai}. 
This is where the \hs{Ark} is. 

















\section{The \Matrices Battle}









\subsection{\ps{\Daggerrain} master plan}
\hr{Daggerrain's master plan}{\ps{\Daggerrain}{} master plan}, planned and orchestrated throughout twenty thousand years, is unfolding. 

\Secherdamon{} and \Ishnaruchaefir{} oppose him. Ramiel ostensibly serves the \banes, but is actually planning yet another betrayal.

\Daggerrain{} intends to sunder the wall to \Erebos{} and allow the \Voidbringer{} unrestricted access to \Miith{}. 

But \hr{Daggerrain's blind spot}{he has a blind spot}\prikker

\Secherdamon, on the other hand, wants to open the gate to Chaos and awaken \Tiamat{} and the \firstgendragons. He has communicated with \KhothSell{} or another one of them. She agrees to help him, but only if he can open the way and make it easy for them to help him. (See section \ref{Rissit communicates with Tiamat}.)

But \Iurzmacul{} plots against his fellow \firstgendragons{}. He does not want to see \Tiamat{} and the others return and devastate \Miith{}. Maybe he tells \Ishnaruchaefir{} and guides him. Maybe \Ishnaruchaefir{} is the son of \Iurzmacul.





\subsubsection{\Dragons fear \Voidbringer}
The \dragons{} know that if \Voidbringer{} gains access to \Miith, they will not stand a chance against the feared \baneking. 
If that happens their only recourse will be to follow \ps{\Vizsherioch} lead and appeal to the \xss. 

\Vizsherioch{} will not accept \Ishnaruchaefir{} as an ally. 
He would prefer to kill him. 

\Vizsherioch{} \emph{wants} to see the \banes{} succeed and \Voidbringer{} brought into the world, because then all of \Miith{} will be forced to turn to him as their only saviour. 
He cannot summon the \xss{} alone, but with enough \dragons{} and \quiljaaran{} and other immortals on his side, he can pull it off. 

He relishes the thought of a war between the \xss{} and the \banelords. 
He is willing to risk the destruction of all of \Miith. 
He kind of thinks like a \xss, remember. 
Plus \hr{Immortal Vizsherioch}{he is more immortal than most}. 









\subsection{Ramiel solidifies his power}
I should let a few years pass between the end of the last book and the beginning of (the serious part of) this one. 
Ramiel needs some time to consolidate his rule as Overlord. 
Not everyone swoons and falls down to worship at his feet. 

And even after some years, he still has rivals and has trouble controlling the dynasty. 

\target{Dasteron's cousins oppose Ramiel}
Among his most vehement foes are \hr{Dasteron's cousins}{\ps{\Dasteron} cousins}, \Sargamel and \Themirod. 

\target{Ramiel uses macho rhetoric as Overlord}
Ramiel uses traditional \Mystraacht \hr{Mystraacht philosophy}{macho rhetoric}. 
But he is actually \hr{Ramiel is critical of Mystraacht ideology}{critical of the \Mystraacht ideology}. 

After his return to Overlordship, Ramiel broods over the doings of the \resphan race.
He is disgusted by their stupidity and hypocrisy. 
The \Mystraacht curse the \CiriathSepher for being shallow and dishonest, but the new, wiser Ramiel can now see that the \Mystraacht are no better themselves, with all their shallow machismo and their hollow talk of \honour and bravery and whatnot.

He thinks: 
\tho{There are times when I wish the \banelords would just come and devour everything. Or whatever it is they plan to do.}

Even among the highest tiers of the \resphain who serve them, there is no one who really knows what the \banelords intend to do.
No \resphan understands the mind of a \bane.









\subsection{\Dragons summon \xss}
\Secherdamon-tachi want to awaken the \xss and summon them to \Miith to fight against the \bane menace. 
Maybe this is mostly intended to slow down the \banes. 
The \dragons know they cannot rely on the \xss as allies.
The \xss might decide it is not worth the effort and pull out of \Miith.
But if the \dragons can at least get the \xss to hold off the \banes, they have a chance. 

The \banes have a thousand-year master plan.
The \xss have little interest in \Miith.
They are likely to give up and go home. 
They will not commit many resources to \Miith. 
It is unlikely that they will save it in the long run, but they may save it in the short run. 





\subsubsection{\Vizsherioch seeks out \daemons}
\Vizsherioch{} seeks out some great and mighty \daemons{} who once served the \xzaishanns{} but have lain dormant for thousands if not millions of years. 

He demands that they serve him. They laugh and reject him, for they have been approached by \dragons{} before. But \Vizsherioch{} is more \xzaishann{} than any \dragon{} ever before. When the \daemons{} realize that, they are impressed and overwhelmed. They agree to serve him. 

He also seeks out \hr{Cosmic gods}{cosmic gods}\dash the same ones that \hr{Ishnaruchaefir seeks out cosmic gods}{\Ishnaruchaefir{} sought out}. But they turn him down. He claims that he is a \xzaishann{} reincarnated, and they laugh.

\lyricsbalsagoth{
  The Hound of Chaos Transcends the Nebulous Palisades of Z'xulth
}{
  The Outer Darkness has cast me from its cavernous maw! 
  So be it\prikker the final pieces of this great macrocosmic puzzle shall soon fall into place. 
  It has been millennia since I last visited my beloved brother, Zuranthus\prikker 
  and this reunion shall most certainly be steeped in ire! 
  
  The annals of eternity shall soon be illumined by the glorious radiance of my deeds, and the searing fire of my long denied vengeance! Woe unto my dogged nemesis and all those who dare aspire to thwart me\prikker for my final ascendence is nigh!
}







\subsection{\Ishnaruchaefir invokes dark gods}
\Ishnaruchaefir{} is forced to invoke various dark gods to seek their power and aid. Some of the same forces that \Secherdamon{} originally invoked to gain power (see section \ref{Rissit invokes dark gods}). 

Perhaps these powers originally helped effect the \hr{Shrouding}{\SecondShrouding}, and now \Ishnaruchaefir{} needs their power to defend the Shroud (see section \ref{To break or preserve the Shroud}).

In the end, a few Elder \Dragons manage to awaken (now that the Shroud is broken) and come to \Ishnaruchaefir's aid.









\subsection{\Iquinian Church preaches}
The \Iquinian Church preaches extra hard. 
The advent of \Lithrim{} is nigh, and the Cabalists want to be sure all the myriad Iquinians are kept under tight control. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  A Chore for the Lost
}{
  Every human being not going to the extreme limit \\
  is the servant or the enemy of man \\
  and the accomplice of a nameless obscenity.
}







\subsection{Ramiel accepts \NexagglachelsCurse}
Ramiel is seduced by the blood of \Nexagglachel{} in his veins. 
He is swayed by the \ps{\dragonlord} voice and ultimately agrees to betray the \banelords, in return for peace of mind from the \hr{Madness of the Curse}{madness and dementia that the curse brings}.

\lyricslimbonicart{The Yawning Abyss of Madness}{
  The winds that carry this esoteric call\\
  emerges from the dungeons underneath my soul. \\
  As I cross the bridge to that darkness, \\
  my eyes are filled with so much death.
}







\subsection{\Ishnaruchaefir hears \Nexagglachel would be proud}
\target{Ishnaruchaefir hears Nexagglachel would be proud}
\Ishnaruchaefir{} meets some \sathariah. 
Possibly Ramiel or \Azraid. 
(Maybe when \hr{Ishnaruchaefir and Azraid plot together, late in TBW}{\Azraid{} conspires with \Ishnaruchaefir}.) 

\begin{prose}
  The \sathariah: 
  \ta{I have a piece of your brother inside of me, you know. 
    I know something of his thoughts. 
    And you know what? 
    I think if \Nexagglachel{} knew what you had done, he would be pleased.}
\end{prose}

The above is not well-meant. 
The \sathariah{} hates \Nexagglachel, because \Nexagglachel{} hates him and drives him mad and ruins his life. 
But it is sincere. 

\Ishnaruchaefir{} takes it as a confirmation that he is on the right track. 
This makes him incredibly relieved. 
He has spent millennia brooding over whether he is \hr{Ishnaruchaefir's stewardship}{carrying on \ps{\Nexagglachel} legacy} properly. 
When \Criseis{} next sees him, he is happier than she has seen him in thousands of years. 
He does not show it, but she, who knows him better than any other, can detect it in his smell and his aethereal threads. 
The pall of darkness that always hangs over him has lifted a little. 










\subsection{Ramiel allies with \Baelzerach}
In secret, Ramiel contacts the \Baelzerach{} and forges a hidden alliance between them and \Mystraacht. They will not openly fight side by side, but they will strike at the same enemies and covertly work to achieve the same goals. 

This is especially sneaky because no one expects it. \Mystraacht{} and \Baelzerach{} are traditionally enemies, having fought many and very bloody wars. 









\subsection{The \banes bring a spaceship to \Miith}
The \banelords{} succeed at bringing a titanic and ancient \hr{Bane technology}{\voyager{} spaceship} from \Erebos/\Nyx{} to \Miith{}. 
It will take all of the \psp{\dragons}{} \xsic{} power to destroy it.

Other people see signs of its approach.

\lyricslimbonicart{Nebulous Dawn}{
  Dark atmospheric winds\\
  are striking towards Earth.\\
  Nihilistic cosmic force.\\
  Asteroid curse.
}

The ship arrives. 
It is a massively powerful juggernaut and wreaks tremendous destruction. 

\lyricslimbonicart{Nebulous Dawn}{
  A blazing phenomenon\\
  launching through the skies.\\
  A deadly impact, tempest chaos.\\
  Utterly devoid of life.
  
  Fountains of fire rise from the lava chambers.\\
  Columns of smoke darken the sky\\
  and cover the landscape in ashes.\\
  Storms with the anatomy of disaster.\\
  Immense swirling winds.
}









\subsection{\Erebos \Matrix Ascendant}
The \bane{} \matrix{} is strong and has almost taken over the world. 
Its corrupting, destructive influence can be felt all over \Miith{}. 
The \hr{Morbus}{\Morbus} is but one of its manifestations. 

\lyricslimbonicart{Nebulous Dawn}{
  An epic eclipse of the Sun.\\
  A rebirth of desolation.\\
  When the cold silence reigns,\\
  darkness sweeps the face of Earth\\
  with infesting freezing torments.\\
  Across the desert wastelands.\\
  Cataclysmic events.
}









\subsection{\Rystessakhin is damaged}
\Ishnaruchaefir{} is in battle, wielding his \hs{glaive}. 
Suddenly it goes wrong, and the unthinkable happens: 
The glaive becomes damaged. 
One of the little blades snaps off. 

\Ishnaruchaefir{} is terrified. 
He knew the Shroud was \hs{unravelling} and it was becoming harder for \Rystessakhin{} to keep it in place. 
\hr{Ishnaruchaefir's Nadir}{His own Nadirs} had been growing steadily worse as a result. 
But had never imagined that it would come to this. 

He immediately unsummons the glaive. 
Then he spends all his available energy on fighting his way free and escaping from the fight. 

He realizes that something is catastrophically wrong. 
The Shroud is under attack, and the pressure on poor \Rystessakhin{} has become so great that even her physical form is chipping and falling apart. 
The status quo is crumbling, and he cannot hope to maintain it any longer. 
He needs to change his strategy.
Something drastic must be done. 








\subsection{\Azraid conspires with \Ishnaruchaefir}
\target{Ishnaruchaefir and Azraid plot together, late in TBW}
\Azraid{} conspires with \Ishnaruchaefir. 

They have \hr{Ishnaruchaefir and Azraid develop empathy}{talked before} and have a relationship as friendly rivals. 
They have even \hr{Ishnaruchaefir and Azraid plot together, early in TBW}{plotted together before}. 
They are both philosophers who feel somewhat estranged from their races, so they have a certain mutual understanding. 

Gradually and ever so subtly through \quo{Sentinels of \Miith} \Ishnaruchaefir becomes convinced that Azraid is on the level, and he also begins to suspect the general nature of Azraid's plan. 
So when Azraid finally approaches \Ishnaruchaefir and asks for his cooperation in a secret venture, \Ishnaruchaefir has a bit of a \quo{what took you so long?} attitude, and the whole interaction has a \quo{I know you know I know you know\prikker} frame.
The two have each formulated ideas that can be combined into a useful whole.

Now \Azraid{}, for the first time \emph{ever}, comes clean and reveals (part of) his master plan to \Ishnaruchaefir. 
\Ishnaruchaefir{} is the best person he can trust with his plan. 

\Azraid{} also needs Ramiel, but he cannot trust him.
Ramiel is too volatile, too unreliable. 
\Ishnaruchaefir{} \hr{Ishnaruchaefir's impulsiveness}{has spent all his impulsiveness long ago}, so \Azraid{} knows he is dependable.

\Ishnaruchaefir{} agrees to cooperate with his old enemy. 

Perhaps it is here \Azraid{} \hr{Ishnaruchaefir hears Nexagglachel would be proud}{tells \Ishnaruchaefir{} that \Nexagglachel{} would be proud}. 








\subsection{\Harbeth dies}
\target{Harbeth dies}
\Harbeth dies for some reason. 

Maybe \Zereth also dies. 
Most of the \hr{CS heirs die}{\CiriathSepher{} heirs die}. 








\subsection{\Ishnaruchaefir sacrifices \Criseis}
Near the end, \Ishnaruchaefir sacrifices \Criseis and commits other cruel but necessary acts. 
Make it horrifying but awesome. 
He calls upon the \xss and other terrible dark gods and prepares to sacrifice the entire world, as he once did in the \hs{Shrouding}. 

Compare to Bayaz in \cite{JoeAbercrombie:LastArgumentofKings} where he sacrifices Yulwei and breaks the First Law. 















\section{\Ishnaruchaefir's quest}
\Ishnaruchaefir has lost his Mirage Asylum. 
He realizes that if he is to truly make a difference in this war, he will need more power.
(He \hr{Ishnaruchaefir begins to realize what he must do}{began to realize this earlier}.)
He decides that he has to go on a pilgrimage to the ancient \draconian land of \Dragonland and the dreaded citadel of \hr{Baltherium}{\Baltherium}. 

Compare the whole quest to Randolph Carter's search for Kadath in \cite{HPLovecraft:TheDreamQuestofUnknownKadath}. 

Read about \hr{Nom}{\Nom} and \hr{Baltherium}{\Baltherium}.









\subsection{\Matrix}
Fortunately \Ishnaruchaefir has prepared for this. 
He has sought out allies and recruited heroes for his cause, both mortal and immortal. 
He now drafts some of these heroes.
He needs them to accompany him and serve as \vertices, for he will need a full \hr{Draconian Matrices}{\draconian \matrix} if he is to accomplish his task. 

His \matrix includes \hr{Criseis}{\Criseis} and \hs{Telcastora Ilcas}.
It was also supposed to include \hr{Najarod}{\Najarod}, but he was suddenly killed, and his youngest lover \hr{Shiin}{\Shiin} took his place. 

\Criseis was not originally supposed to come.
She begged \Ishnaruchaefir to take her along, and he relented.
But she was not a part of the \matrix.
Then something went wrong, and another \matrix member died.
\Criseis now had to take the last position, as much as \Ishnaruchaefir hated to see her take the risk. 









\subsection{Culmination}
At the end, \Ishnaruchaefir has to fight his way through the horrors of the \hs{dead universe}. 

\citeauthorbook[p.482--483]{HPLovecraft:TheDreamQuestofUnknownKadath}{\HPLovecraft}{%
  The Dream-Quest of Unknown Kadath%
}{%
  And Randolph Carter, gasping and dizzy on his hideous Shantak, shot screamingly into space toward the cold blue glare of boreal Vega; looking but once behind him at the clustered and chaotic turrets of the onyx nightmare wherein still glowed the lone lurid light of that window above the air and the clouds of earth's dreamland. Great polypous horrors slid darkly past, and unseen bat wings beat multitudinous around him, but still he clung to the unwholesome mane of that loathly and hippocephalic scaled bird. The stars danced mockingly, almost shifting now and then to form pale signs of doom that one might wonder one had not seen and feared before; and ever the winds of nether howled of vague blackness and loneliness beyond the cosmos.
  
  Then through the glittering vault ahead there fell a hush of portent, and all the winds and horrors slunk away as night things slink away before the dawn. Trembling in waves that golden wisps of nebula made weirdly visible, there rose a timid hint of far-off melody, droning in faint chords that our own universe of stars knows not. And as that music grew, the Shantak raised its ears and plunged ahead, and Carter likewise bent to catch each lovely strain. It was a song, but not the song of any voice. Night and the spheres sang it, and it was old when space and Nyarlathotep and the Other Gods were born.
  
  Faster flew the Shantak, and lower bent the rider, drunk with the marvel of strange gulfs, and whirling in the crystal coils of outer magic. Then came too late the warning of the evil one, the sardonic caution of the daemon legate who had bidden the seeker beware the madness of that song. Only to taunt had Nyarlathotep marked out the way to safety and the marvellous sunset city; only to mock had that black messenger revealed the secret of these truant gods whose steps he could so easily lead back at will. For madness and the void's wild vengeance are Nyarlathotep's only gifts to the presumptuous; and frantick though the rider strove to turn his disgusting steed, that leering, tittering Shantak coursed on impetuous and relentless, flapping its great slippery wings in malignant joy and headed for those unhallowed pits whither no dreams reach; that last amorphous blight of nether-most confusion where bubbles and blasphemes at infinity's centre the mindless daemon-sultan Azathoth, whose name no lips dare speak aloud.
  
  Unswerving and obedient to the foul legate's orders, that hellish bird plunged onward through shoals of shapeless lurkers and caperers in darkness, and vacuous herds of drifting entities that pawed and groped and groped and pawed; the nameless larvae of the Other Gods, that are like them blind and without mind, and possessed of singular hungers and thirsts
  Onward unswerving and relentless, and tittering hilariously to watch the chuckling and hysterics into which the risen song of night and the spheres had turned, that eldritch scaly monster bore its helpless rider; hurtling and shooting, cleaving the uttermost rim and spanning the outermost abysses; leaving behind the stars and the realms of matter, and darting meteor-like through stark formlessness toward those inconceivable, unlighted chambers beyond time wherein Azathoth gnaws shapeless and ravenous amidst the muffled, maddening beat of vile drums and the thin, monotonous whine of accursed flutes.
}







\subsection{\Ishnaruchaefir realizes what he must do}
\target{Ishnaruchaefir realizes what he must do}
At the end, in order to break free (like Randolph Carter on his way to Azathoth's throne) \Ishnaruchaefir will need true Gnosis of his own Aenigma. 
To do this he has to look deep inside himself and come to terms with himself. 
Face his inner demons. 
This means he must overcome a ton of traumata, which have festered inside him ever since he \hr{Ishnaruchaefir slays his beloved}{killed \Rystessakhin} and \hr{Ishnaruchaefir goes into the void}{fled into the void}. 

He must make peace with the memory of \Rystessakhin{}. 
Only then can he call upon all his strength. 
He must save himself before he can hope to save the world. 

\Achamoth fights against \Ishnaruchaefir and seems to want to stop him (like Nyarlathotep in \cite{HPLovecraft:TheDreamQuestofUnknownKadath}).
But in the end \Ishnaruchaefir suspects that he has been played for a \trope{XanatosSucker}{Xanatos Sucker} and that \Achamoth was really guiding him through the necessary struggle as a \trope{TricksterMentor}{Trickster Mentor}. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  As deep cuts of truth.\\
  As a fire that closes the wound.\\
  So is my redemption.
  
  Beyond repentance.\\
  This is the ordeal of fire.
}

It will be hard, expensive and bloody, for both him and the world. 
But it will be worth it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  Come suffering, Apocalypse.\\
  Release the fires of Hell.\\
  I call upon destruction and despair.\\
  Not for vengeance, not for power.\\
  Beneath the ashes I walk.
}

At last he takes a deep breath and prepares to do it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  Behold, an angel of vengeance.\\
  A lion. A sword of fire. \\
  Alas, the burden of my heart\\
  is violence undone\\
  Pain unfulfilled.\\
  Silence.
}

Finally he does it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  When I finally cut \\
  deep into the flesh of guilt,\\
  the un-naked body of shame\\
  and the veins of repentance open wide,\\
  sending rivers of blood into my mouth.
  
  The pain is still mine.
}

\citeauthorbook[p.484--485]{HPLovecraft:TheDreamQuestofUnknownKadath}{\HPLovecraft}{%
  The Dream-Quest of Unknown Kadath%
}{%
  Turn\dash turn\dash blackness on every side, but Randolph Carter could turn.
  
  Thick though the rushing nightmare that clutched his senses, Randolph Carter could turn and move. He could move, and if he chose he could leap off the evil Shantak that bore him hurtlingly doomward at the orders of Nyarlathotep. He could leap off and dare those depths of night that yawned interminably down, those depths of fear whose terrors yet could not exceed the nameless doom that lurked waiting at chaos' core. He could turn and move and leap\dash{}he could\dash{}he would\dash{}he would\dash{}he would.
  
  Off that vast hippocephalic abomination leaped the doomed and desperate dreamer, and down through endless voids of sentient blackness he fell. Aeons reeled, universes died and were born again, stars became nebulae and nebulae became stars, and still Randolph Carter fell through those endless voids of sentient blackness.
  
  Then in the slow creeping course of eternity the utmost cycle of the cosmos churned itself into another futile completion, and all things became again as they were unreckoned kalpas before. Matter and light were born anew as space once had known them; and comets, suns and worlds sprang flaming into life, though nothing survived to tell that they had been and gone, been and gone, always and always, back to no first beginning.
  
  And there was a firmament again, and a wind, and a glare of purple light in the eyes of the falling dreamer. There were gods and presences and wills; beauty and evil, and the shrieking of noxious night robbed of its prey. For through the unknown ultimate cycle had lived a thought and a vision of a dreamer's boyhood, and now there were remade a waking world and an old cherished city to body and to justify these things. Out of the void S'ngac the violet gas had pointed the way, and archaic Nodens was bellowing his guidance from unhinted deeps.
  
  Stars swelled to dawns, and dawns burst into fountains of gold, carmine, and purple, and still the dreamer fell. Cries rent the aether as ribbons of light beat back the fiends from outside. And hoary Nodens raised a howl of triumph when Nyarlathotep, close on his quarry, stopped baffled by a glare that seared his formless hunting-horrors to grey dust. Randolph Carter had indeed descended at last the wide marmoreal flights to his marvellous city, for he was come again to the fair New England world that had wrought him.
}













\section{Climactic Battle}
Near the end there is a great, climactic battle between the \bane/\resphan{} forces and some \quo{good guys}. 
There are very few \dragons{} (perhaps only \Ishnaruchaefir{} and his companions), because most \dragons{} support \ps{\Secherdamon} gambit, hoping to utilize the \pps{\banes}{} Shroud-weaving spell to bring the \firstgendragons{} into the world and have them vanquish the \Voidbringer{} and his legions.







\subsection{Rage, Rage Against the Dying of the Light}
One of the sections or chapters of this book should be called \quo{Rage, Rage Against the Dying of the Light}.
It is a reference to the poem \quo{Do not go gentle into that good night} by Dylan Thomas.







\subsection{\HothNrul}
\target{Hoth-Nrul summoned}
\Vizsherioch{} and his cohorts manage to bring a mighty ally to \Miith: 
\hr{Hoth-Nrul}{\HothNrul}, a \xsic{} godling. 
\HothNrul{} is intended to spearhead the coming \xs{} invasion of \Miith. 

Later, \Ishnaruchaefir-tachi communicate with \HothNrul{} and convince the alien god that it is in its interest to attack \Daggerrain.
So \HothNrul{} seeks out the \banelord. 

\HothNrul{} has difficulty attacking \Daggerrain, for he is well-hidden-away. 
But it manages to do some damage. 
When \Daggerrain{} is distracted by the \xs{}, \Azraid{} and Ramiel strike and fuck up \Daggerrain. 

\HothNrul{} \hr{Hoth-Nrul left behind}{ends up the same place where \Daggerrain{} is}. 







\subsection{\Ishnaruchaefir leads \dragons}
\target{Ishnaruchaefir leads Dragons to war in TBW}
\Ishnaruchaefir{} does not believe in this gambit. He has no faith in \Tiamat{} and her brethren and does not think they will come to help. 
So he works to persuade the \dragons{} (including some \hr{Aloof Dragons}{aloof ones}) to fight, to fly with him against \ps{\Daggerrain}{} legions. 

At the last moment, he succeeds. 
Have a massively epic scene where \Ishnaruchaefir{} flies at the head of a massive flight of a \dragons, flanked by hundreds of \rachyths, \drakes{} and \pdaemons, to engage the \bane{} armies and seize victory.
They are awesome to behold as they return to \Miith in full force. 
Dozens of Elder \Dragons. 

Compare to: 

\begin{itemize}
  \item 
    \bandsong{Bal-Sagoth}{Black Dragons Soar Above the Mountain of Shadows}. 
  \item 
    The scenes in \authorseries{Richard Knaak}{War of the Ancients} where everyone holds their breath for the \dragons{} to come to their aid, and where they finally do come and save the day.
  \item 
    The scenes in \authorbook{Graham McNeill}{Fulgrim} p.472, where the Alpha Legion, Word Bearers, Night Lords and Iron Warriors come to the \quo{rescue}. 
\end{itemize}

\citeauthorbook[p.344]{ClarkAshtonSmith:TheDarkEidolon}{Clark Ashton Smith}{%
  The Dark Eidolon%
}{
  Yea, the undying worms of fire and darkness have come forth like an army at thy summons\prikker
}







\subsection{The Advent of \Lithrim}
\target{Lithrim arises}
\target{Second Advent}
\target{Second Advent of Lithrim}
\Lithrim{} finally arises. 

Mankind is very Shrouded, \naive{} and stupid. 
Not quite as well-meaning and {innocent} as the \scathae, but not all that far from them.
That is why it is so effective when their inner \Erebean{} darkness is finally released in the culmination of the \Morbus{} plan. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Sola Fide
}{
  Some rejoice of the children's innocence and smiles\\
  Others of their shameful defloration \\
  by the ministers of Christ, swollen by arrogance and lust\\
  Jesus spoke words of wisdom: \quo{Let the children come to me}\\
  What's more enthralling indeed \\
  than ruining through them the genesis of life itself?\\
  Dive deep into the blue eyes of the newborn \\
  and thou shalt get a glance of heaven\\
  When this dive reveals despair, \\
  hideous ruins of the glory of Hell\\
  The serving sons of disobedience proclaim \\
  Vengeance belongeth unto Him\prikker
}

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Innocence sacrificed and heaven denied\\
  Iniquity divine\dash no repentance\dash over mankind\\
  Mind-raped, self-devoured, empty god-eyed\\
  Transgression coercive, Redemption never to be found

  Under the altar of cannibalism\\
  Man hast (thou) confessed the spiritual schism\\
  And without pride mourned the loss of freedom,\\
  Our blessed Lord have condemned you to martyrdom
  
  Let everything that hath breath praise the Lord, \\
  praise ye the Lord.
}

It is the culmination of that which began with \ps{\Thanatzil} noble sacrifice. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  The advent of Plerosis is the destiny of Man \\
  and shall shatter up to the Heavens,\\
  A savage aperture to the High Mass of the Comforter
}

It is cataclysmic and destructive. 
It unleashes all the wicked, destructive Entropy that, as it turns out, were the building blocks of Man all along. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Instigating manifold quadrants of industrialized death,\\
  An avid Moloch, never satiated, an endless Feast,\\
  Following the principle of reversibility of merits,\\ 
  shattering up the Word\\
  As Pillars of grayish Soulfire spurt out to a bereaved firmament
}

Man instinctively welcomes the advent of \Lithrim.

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  The unreservedly open spirit, \\
  open to death, to torment, to joy,\\
  The open spirit, open and dying,\\
  Suffering and dying and happy, \\
  stands in a certain veiled light:\\
  That light is divine.\\
  And the cry that breaks from a twisted \\
  mouth may perhaps twist him who utters it,\\
  But what he speaks is an immense alleluia, \\
  flung into endless silence, and lost there.
}

But it is also scary. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  From very high above a kind of stillness \\
  swept down upon me and froze me\\
  It was as though I were borne aloft \\
  in a flight of headless and unbodied angels\\
  Shaped from the broad swooping of wings, \\
  but it was simpler than that\\
  I became unhappy and felt painfully forsaken, \\
  as one is when in the presence of God
}

Some \humans{} fight against it. 

\citebandsong{BeyondTwilight:TheEdge}{Beyond Twilight}{Salem}{
  Entombed by the will of the night.\\
  All your thoughts deflowered.\\
  Waived all of your beliefs\\
  in this midnight hour. \\
  Search your past, try and make it back.\\
  All your strength overpowered.\\
  Unknown forces run you through \\
  in the shadow of the black tower.
  
  The witches of Salem hold your fate. 
  
  Relief obtained in sacred mass.\\
  All your sins forgiven. \\
  The ultimate sign of witchery.\\
  The total lack of sanity.
}

\Humans{} lose their individual identity. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  And the victim, blind to the radiating Light of Truth, \\
  stuttering, repeats:\\
  Lamma Sabacthani?\\
  Lamma Sabacthani?\\
  Lamma Sabacthani?
  
  Consummatum est.
}

Mankind becomes a god: \Lithrim. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  I am the son of Man, \\
  and this in erring reason's spite, is my pride\prikker\\
  War, be enthroned, a form of divine retribution!\\
  Execution, be sacred, agent of divine Providence!
  
  The stillness of Contemplation \\
  is allowed in billions of woeful cries,\\
  So astonishingly simultaneous and in unison,\\
  Each and every second, \\
  They defuse each other in such a perfect manner,\\
  Equaling the most inscrutable of all silences\\
  Doctrine of Mystical Substitution, Mystical Body, \\
  Sanctorum Communionem,\\
  Celebrate the Sin of one reflecting, \\
  tectonic forces alike, upon the multitude
  
  The purest of all Holocausts shall be perpetrated\\
  By a loving hand, never knowing if it provided felicity\\
  Or the vilest of everlasting torments\\
  No man can see Me and live!
}

When the \humans{} become the fell, abhorrent \Lithrim, they (or the smarter of them) at last realize the purpose of their otherwise empty and wretched lives. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  The act whereby being\dash existence\dash is bestowed upon us\\
  Is an unbearable surpassing of being,\\
  An act no less unbearable than that of dying.\\
  And since, in death, being is taken away from us \\
  at the same time it is given us,\\
  We must seek for it in the feeling of dying,\\
  In those unbearable moments \\
  when it seems to us that we are dying\\
  Because the existence in us,\\
  During these interludes,\\
  Exists through nothing but a sustaining and ruinous excess,\\
  When the fullness of horror and that of joy coincide.
  
  As I waited for annihilation, all that subsisted in me\\
  Seemed to me to be the dross over which man's life tarries\prikker
}

But they lose their \humanity{} in the process. 

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega%
}{
  Mass Grave Aesthetics
}{
  The black Idol fills the veil of flesh with noxious smoke, \\
  Depicting primal human experiences indifferently, \\
  Contemptuous of moral concerns, dehumanized \\
  The howling of wolves and the destructive sword \\
  are portions of Eternity, \\
  Too great for the eyes of merely a man
}

\citebandsong{BlindGuardian:FTB}{%
  Blind Guardian%
}{
  Hall of the King
}{
  You're the birth and you're the end.\\
  You've been hurt but you're not dead.\\
  Discovering you is what should never be.\\
  Poisoned are our souls and dark our hearts.\\
  Ruins we have left to rule the world.\\
  Destructive are our minds. It's much too late.\\
}

But they gain new insight as they leave their \human{} forms:

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega%
}{
  Mass Grave Aesthetics%
}{
  Violence exists I the moment \\
  when the eye turns upwards into the head, \\
  When inversion is complete and total \\
  The darkness of the upturned eye is not the absence of light \\
  But the process of seeing being taken to its limit \\
  That thorough derangement of the senses, \\
  Way beyond the deceptive conflict between darkness and light \\
  Opens perceptions to the tyranny of the Chekhinah
}

\Lithrim{} is a slave under the \psp{\banelords}{} command. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  I can utter no word, O my God, \\
  unless I be permitted by Thee\\
  And can move in no direction \\
  until I obtain Thy sanction\\
  It is Thou, O my God, \\
  who hast called me into being through the power\\
  Of Thy might, and has endued me \\
  with Thy grace to manifest Thy Cause
}

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  Bread of Bitterness
}{
  From a supplication without response, \\
  the essence of man, his ground giving way, \\
  comes illumination by a sun of great evil \\
  that sets aflame the inner core \\
  and enthrones suffocation and the intolerable without respite \\
  as the joyful reward for a million aborted truths.
  
  This silence that among all man has charged with sacred horror, \\
  it becomes sovereign, in repugnant nativity, \\
  and detaches itself from the bonds \\
  which paralyse a vertiginous movement towards the void.
  
  Breathless ecstatic experience,\\
  it opens the horizon a bit more,\\
  this wound of God;\\
  it is the assassination of the abyss of possibilities, \\
  the depths of being left to holy vultures. 
}





\subsubsection{Sentinels realize \Lithrim}
The Sentinels finally realize what \Lithrim is.
(Do not reveal this until the \humans have already coalesced into \Lithrim.)

\begin{prose}
  \ta{\Lithrim, the hideous that feeds on the souls of the \humans.}
  
  \ta{No. 
    It is worse than that.
    \Lithrim does not feed on the \humans.
    \Lithrim \emph{is} the \humans!
    Picture it.
    Every \human every born into the \iquinian faith, for thousands of years, has been gathered for this purpose.
    Each \human soul is puny, of course, but they number in the hundreds of millions, if not billions.
    All coalesced together to form a nightmare god of colossal power!}
\end{prose}





\subsubsection{\Lithrim awakens the \resphain's latent madness}
When \Lithrim awakens, the madness latent in the \resphain also awakens. 
Even in the \hs{Ark}, where they believe themselves safe, the \resphain are seized by madness and begin to fight and kill each other.
They almost ruin everything. 










\subsection{The portal opens}
\Lithrim{} opens the way for the \Voidbringer. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Perfect Dark%
}{
  Hold the candle\\
  Pass the flame\\
  We're all in this together \\
  Cosmic winds are gathering\\
  Coming your way\\
  Telling you you are only a fragment\\
  A fragment of time 
  
  And it's perfect dark\\
  It's perfect dark here\\
  Hear the angels screaming
}





\subsubsection{People feel the \Voidbringer}
As the Cabal plot nears fruition and they are opening the gate to \Erebos, \Miithians can feel the presence of the \Voidbringer: 
An ever hungry, ever consuming emptiness, completely inhuman. 
The older immortals remember it from the \secondbanewar. 





\subsubsection{\Banes{} slip through}
Many \lesserbanes{} slip through into \Miith. 
Not in the same millions that got through in the \secondbanewar, but still quite a lot. 
But not so many that the combined \dragons{} and \resphain{} cannot deal with them\prikker hopefully. 

















\section{Ramiel the Betrayer}
\target{Ramiel betrays Voidbringer}
\target{Ramiel betrays Banes}









\subsection{Summary}
\hs{Ramiel} has decided that he will no longer serve the \banelords. 

\lyricsbs{Dream Theater}{In the Presence of Enemies}{\obeylines%
  My soul grows weaker.\\
  He knows and he waits.\\
  He watches over me,\\
  standing at the infernal gates.\\
  In the hour of darkness,\\
  the moment I feared has passed,\\
  the moment I lost my faith.\\
  Promising salvation.\\
  My soul is my own now.\\
  I do not fight for you,\\
  Dark Master!
}

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Hellfire%
}{
  Before me now I see a dying planet.\\
  Captured souls with microchips implanted.\\
  When warning came you stayed the same.\\
  When warning came you stayed the same.\\
  I am crumbling over the obstacles.\\
  Nothing left to entertain. \\
  The smell of burning corpses. \\
  A new world domain.
  
  Before me now I see a future\\
  A future black\\
  Oh come and save me\\
  I'm under soul attack
  
  I will break out from this madness\\
  There is nothing here but sadness\\
  I'm burning in the hellfire\\
  There must be a way\\
  Waiting for the day\\
  
  Hellfire burns higher\\
  Higher, higher. \\
  Only blood remains\\
  There is nothing more to gain \\
  Take me.
}

He now plans to betray the \banes. 
He intends to siphon energy from the \Voidbringer, thus empowering himself enough to overpower \Daggerrain{} and slay or banish him. 
It is a mad scheme, but Ramiel has always been one for mad schemes. It stems from his sublime arrogance and megalomania (see section \ref{Ramiel's megalomania}). 

It is a good plan, but \Daggerrain{} is too clever. 
The \banelord{} has always known that Ramiel was a loose cannon and could not be trusted, so he had taken precautions. 
When Ramiel finally betrayed the \banes, they were ready for him. 

So Ramiel's plan fails\prikker

\prikker or would fail, if not for the intervention of \Azraid. 
\Azraid{} had always played the loyal Cabalist, faithful servant of the \banelords, but \hr{Azraid hates Banes}{in secret he has always hated them} and \hr{Azraid plots against Banes}{plotted against them}. 
He anticipated Ramiel's betrayal and planned for it. 
So when Ramiel fails, \hr{Azraid helps Ramiel betray Banes}{\Azraid{} steps in and helps him}. 

\ps{\Azraid} gambit cannot succeed without Ramiel's help. 
But he cannot tell Ramiel about it before the very last minute, because he doesn't trust Ramiel's ability to keep the secret. 
(It is \emph{hard} to keep secrets from \Daggerrain.) 
It is thus something of a \trope{XanatosRoulette}{Xanatos Roulette}. 

So, in the end, it turns out that \Azraid{} was \hr{Daggerrain's blind spot}{\ps{\Daggerrain}{} blind spot}. 





\subsubsection{The Ark}
\target{Ark}
\index{Ark}
The plan (a collaborative effort between \Azraid{} and \Ishnaruchaefir) is to use the wild threads of the collapsing Shroud to \quo{cut} free a chunk of \Miith{}, forming a pocket Realm. 
They then hope to be able to close the way behind them, setting up a makeshift barrier by piecing together fragments of the shattered \CrystalSphere{} and Shroud.

They will then have formed a new mini-Realm, a micro-\Miith{} torn loose. 
This will be their Ark. 
A small population of \Miithians should be able to escape in this Realm. 
The makeshift barrier will keep the \banes{} out for a short while, while the masterminds use their magic to twist the fabric of space around them propel the Ark away through the universe, to a place where the \banes{} cannot easily find them. 

The Ark is built from the ruins of the \hr{Sethicus tomb}{tomb of \Sethicus}, which lies in the Realm of \hr{Neevrai}{\Neevrai}. 

It will be difficult, but \Azraid{} is ready. 
He has spent millennia preparing for this day, and he is prepared to sacrifice his life to see it through. 
And he has \ps{\Ishnaruchaefir} awesome Gnosis helping him. 

In the end, \Ishnaruchaefir{} and Ramiel end up on the Ark, while \Azraid{} destroys himself in the process. 

Perhaps the Ark is not a chunk of planet, but a spaceship. 
Perhaps a commandeered \bane/\resphan{} ship. 
If so, it is huge. 
A colony ship. 
A world-ship. 

The Ark was actually an unfinished relic created by \Sethicus. 
It was a part of \hr{Sethicus plan}{his masterplan} to escape \Miith before \hr{Sethican eschatology}{it was destroyed}. 
As was to be expected of an element of \Sethicus's plan, the Ark required a tremendous sacrifice of blood and life and Heart-power to launch it, and more sacrifice still to sustain it on its journey. 

\target{Ark uses Tiamat's Heart}
The Ark became its own little world.
It had its own Dweomer, its own Heart, so that it could sustain itself and stay alive at least for a while.
This Heart was actually the herat of \Tiamat.

Compare to the movie \cite{Movie:Watchmen}. 





\subsubsection{It all takes place in the \matrix{} world}
Note that all of this takes place in the world of the \matrices. 
The three may not physically meet at all. 
They simply pull at cosmic strings using their \vertex{} abilities. 
Any any \quo{portals} are not physical portals, but a ubiquitous thinning of the Shroud allowing passage into \Erebos{} or somewhere else. 





\subsubsection{Why they wait so long}
One might think \Azraid{} could have betrayed the \banes{} long ago. 
But that would not have worked. 
He was not confident he could have done enough damage before he was caught, eliminated and replaced. 

No, this is a unique opportunity. 
\ps{\Azraid} betrayal has to happen \emph{after} the advent of \Lithrim. 
See, they need to rely on the Shroud-wide chaos and fluctuations that \Lithrim{} creates, and use them to set the Ark free. 





\subsubsection{Ark fueled by dead \ophidians}
The Ark is a big-ass \hs{living machine}. 

The Ark is built from \Sethicus's old tomb. 
\Sethicus was buried with many other \ophidians and perhaps even \dragons.
Many of them still lie there, dead but dreaming. 
These can be used as fuel to power the Ark and keep it alive. 
When the dead learn about this plan, they are nonplussed. 
They see it as betrayal and fight back. 
They would rather see everyone perish with them than be betrayed and sacrificed for someone else's gain. 

The undead cannot move, but they still have arcane power. 
\Ishnaruchaefir has to expend more of his already badly strained power to overcome the dead and force them to become fuel. 
This is also psychologically hard for him: 
It is another horrible betrayal of his own people, even violating the \dragons' important \hr{Dragons do not eat Dragons}{cannibalism taboo}. 
It is another gruesome scar on his soul. 
But it must be done, and \Ishnaruchaefir knows he is the only one hard enough to do it. 

This should be a climactic thing, another \quo{everything almost going awry at the last minute} twist at the end of the last book. 









\subsection{Ramiel drains the \ps{\Voidbringer}{} power}
Ramiel tries to betray the \Voidbringer. 
This is similar to how Astronema betrays Dark Specter and drains his power in \emph{Power Rangers in Space}. 
%It stems from Ramiel's sublime arrogance and megalomania (see section \ref{Ramiel's megalomania}). 

He absorbs some of the \ps{\Voidbringer}{} power. 





\subsubsection{How it feels}
He feels himself swimming adrift in an endless, bleak ocean of dark, Entropic power, feels how it almost devours him and his sanity.

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{
  The ravening black worms of madness 
  are devouring the shredded remnants of sanity 
  as I return to my slumbering steel-clad body\prikker \\
  but as the dream-veil lifts, I feel my limbs transform, 
  flesh becoming cold stone\prikker \\
  enshrouded by a dark mantle of obsidian. \\
  And the laughter of the Guardians echoes, 
  carries upon the winds of this spectral eve.
}

Actually, he began doing this much earlier, but it takes a while before \Daggerrain{} \quo{discovers} his treachery. 

Ramiel plans to use his \carcer against the \Voidbringer.

\citebandsong{BlindGuardian:IFTOS}{Blind Guardian}{%
  The Script for My Requiem (demo version)%
}{
  Battle rages higher and higher. \\
  Akron starts to feel my hate. \\
  There's no escaping for the dark souls \\
  I can't control anymore, anymore. \\
  What started in the underworld, \\
  it should be finished here and now. 
  
  I know his tricks, black magic power. \\
  But now it's time for him to say goodbye. \\
  There's only one thing left, the dawn shall arrive. \\
  We've got to get it past, fear the dark side. \\
  Turn off his light. \\
  Turn off his light.
}





\subsection{Ramiel fails}
\target{Ramiel as Xanatos Sucker}
\Daggerrain{} is too clever for Ramiel. 
He had anticipated Ramiel's betrayal and easily stops him. 
He is about to kill and destroy Ramiel\prikker 

Before his death, Ramiel's life flashes before his eyes. 
He realizes that \Daggerrain{} must have anticipated his every move and planned accordingly. 
He has been playing straight into \ps{\Daggerrain}{} hands the whole time. 

He truly \hr{Ramiel is nothing}{is nothing}\prikker 
or so he fears. 

Compare a \hr{Azraid as Xanatos Sucker}{similar scene with \Azraid{} much earlier}. 
Also compare to the scene in \emph{\JuukenSentaiGekiranger} episode 46 (or so) where Rio discovers that his entire life has been masterminded by Long. 

We see inside Ramiel's head as he struggles against \Daggerrain{} and almost dies. 

\lyricsbs{Hate Eternal}{Path to the Eternal Gods}{
  On this journey into death, \\
  I am beside myself in tremendous bliss,\\
  For this allegiance has been made. \\
  Shall my sins be absolved, \\
  washed away by the blood of the sacred lambs? \\ 
  Yet I am not amongst the flock.
  
  The remnants of my life now become my vast illusions,\\
  whilst exiled from your grace. 
  
  With fortitude, with courage, 
  I face all my fears, \\
  on my path to the eternal gods. \\
  With my wrath, with my disdain, 
  I face all my fears, \\
  on my path to the eternal gods.\\
  As I cross over into my final place, 
  I face all my fears, \\
  on my path to the eternal gods.\\
  As I bear trials in my final resting place, 
  I face all my fears, 
  on my path to the eternal gods.\\
}





\subsection{\Azraid helps Ramiel}
\target{Azraid helps Ramiel betray Banes}
At the last moment, before \Daggerrain{} would have destroyed Ramiel, \Azraid{} steps in and backstabs \Daggerrain. 

Ramiel realizes that he had been overreacting before, overestimating \ps{\Daggerrain}{} omniscience and underestimating his own capability. 
Some parts of his plan actually \emph{were} successful, not covered by the \ps{\banelord}{} \trope{XanatosGambit}{Xanatos Gambit}. 
He regains some faith in himself. 

Together, the two \satharioth{} push \Daggerrain{} back. 
% It closes behind him. 
Ramiel now manages to hold \Daggerrain{} occupied while \Azraid{} works his magic and tears the \hs{Ark} loose. 





\subsubsection{Ramiel and \Azraid{} as kindred spirits}
\Azraid{} criticizes Ramiel for being too overt and honest (\hr{Mystraacht philosophy}{and would be expected of a \Mystraacht}), making him predictable. 
In contrast to \Azraid{} himself, who has managed to creep under even \ps{\Daggerrain}{} radar for twenty thousand years. 

But he is also sympathetic, because he recognizes that Ramiel's situation is like a mirror of his own. 
Back when \Daggerrain{} manipulated the young \Azraid{} into betraying and murdering his brother \Damiarch, he was similarly shocked and disillusioned. 
He shares this with Ramiel. 
This is a rare \trope{PetTheDog}{Pet the Dog} moment for \Azraid. 

A new understanding and empathy suddenly exists between the two \resphan{} lords. 
They are now kindred spirits. 
After this battle they part, not as friends, nor allies, but with a deeper mutual respect than previously. 

\begin{prose}
  Ramiel: 
  \ta{\Azraid. Were you among those who betrayed \Zachirah{} and me?}

  \Azraid: 
  \ta{LOL. Ramiel. 
    I have deceived the \banelords{} for thousands of years. 
    I have deceived everyone. 
    Among all the \resphain, there is no greater fraud than I.
    If I were to answer \quo{no}, would you believe me?
    I would not believe me.}
\end{prose}






\subsubsection{Ramiel imagines hearing \ps{\Daggerrain}{} voice}
Ramiel jokingly imagines hearing \ps{\Daggerrain}{} voice in his head: 
\daggerrain{A minor setback. 
I have planned for this contingency. 
It will take us another 3651 years to get out plan back on schedule\prikker} 
(The number 3651 is a random one that Ramiel pulls out of his ass, but it sounds like something \Daggerrain{} might say.)








\subsection{\Azraid dies\prikker maybe}
\target{Azraid dies}
Maybe \Azraid{} dies. 
He sacrifices himself in order to violently disrupt the \Erebean{} \matrix{}, thus causing it to implode and collapse faster than \Daggerrain{} can restore it to order. 

\ps{\Azraid} death leaves \CiriathSepher{}, its hierarchy and \matrix, in chaos. 
(\hr{CS heirs die}{Not much is left} of the \hr{CS order of succession}{\CiriathSepher{} order of succession} at this time.)
It is now up to Ramiel to pick up the pieces and lead the \resphan{} race, if they are to have a chance of surviving. 

Compare to Anomander Rake's sacrifice in \cite{StevenErikson:TolltheHounds}. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Surrender\\
  Lost in the dark\\
  Without angels to guide me 
  
  Hands of death reaching out for me\\
  I'm longing to rest\\
  I see myself move in need of power
}

He knows the \banes{} better than any other. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  I've looked straight into the eyes of demons rising\\
  So close.\\
  I've had one foot on the other side\\
  For so long. \\
  I've seen evil so evil that all living died\\
  The devil is near.\\
}

He wants to stop the \iquin{} plan. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  You may fool the people, but you can't fool me\\
  No more, not anymore. 
  
  And all the souls turned black\\
  There is no way back
}

He dies. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Stranded with the darkness\\
  It's so cold in here \\
  I feel the rush within me
}

He hopes that \Miith{} (or a fragment of it) now has a future. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Time will mend\\
  Ease the sorrow\\
  Take my hand\\
  There's no tomorrow
}











\subsection{\Daggerrain falls}
\target{Daggerrain falls}
\Daggerrain{} has fallen. 
And the worst part is that the link between \Erebos{} and \Nyx{} fell with him. 
\hr{Daggerrain is the gate}{\Daggerrain{} \emph{was} the link}. Without him, the way is closed permanently. 
Now, the only way for the \banes{} to return from \Erebos{} would be to send spaceships, like they did the first time around. 
That might take millennia, because \Erebos{} and \Miith{} are very distant from each other. 





\subsubsection{\HothNrul{} left behind}
\target{Hoth-Nrul left behind}
\HothNrul{} ends up the same place where \Daggerrain{} is. 
No one knows what becomes of it. 
Perhaps it gets destroyed by \Daggerrain{} and his fellow \banelords\prikker if it is even possible to destroy a \xs, which is not known. 
Or perhaps it returns to the \xs{} homeworld. 

Or perhaps it wins. 
It is very difficult to get a clear idea of the balance of power between so \uber-powerful beings as \xss{} and great \banelords. 

The survivors of the war are not sure \HothNrul{} will not return to wreak more havoc on them. 
But they hope not. 















\section{The Fall of the Shroud}
\subsection{\ps{\Ishnaruchaefir} glaive is destroyed}
\target{Ishnaruchaefir's glaive is destroyed}
\target{Glaive is destroyed}
Throughout most of the story, \hr{Ishnaruchaefir fights to preserve the Shroud}{\Ishnaruchaefir{} has fought to preserve the Shroud}. But at the end, he lets himself persuade to assist in unravelling the Shroud. \Triestessakhin{} is the one who persuades him. 

Ultimately, \hr{Ishnaruchaefir's glaive}{\ps{\Ishnaruchaefir} glaive} is destroyed, its Shroud-weaving effect (as a \hs{weaving artifact}) is broken, and the soul of \Triestessakhin{} is released. 
\hr{Glaive must be destroyed}{This had to happen}. 

She is quite insane after these many thousand years inside the sword, but he manages to lead a conversation with her. She is bitter and tries to make him repent. 

\Ishnaruchaefir: 
\ta{%
  I mourn what I have done, and at times I even regret. 
  But I would not change it, and given the chance, I would do the same again.}

Compare to the scene with Lord Soth and his wife at the end of \emph{Spectre of the Black Rose} by James Lowder and Voronica-Whitney Robinson. 



% \subsection{Daggerrain's epilogue}
% In the end, the \banes{} are defeated and the way to \Erebos{} is sealed shut once more. 
% 
% In the very last chapter, \Daggerrain{} holds a monologue, telling his subordinates to get to work. Having planned for this contingency, he has a new plan to reclaim \Miith{}, another four thousand years from now. As he says: \daggerrain{I have waited thirty thousand years. Another four thousand is nothing to me.}







\subsection{\Vizsherioch falls asleep}
\target{Vizsherioch falls asleep}
\Vizsherioch{} \hr{Vizsherioch's XS blood}{has too much \xsic{} blood} and is susceptible to the \hr{XS slumber}{\xsic{} slumber}. He uses his \bane{} blood to draw upon \Erebean{} power to negate this effect. 

But when \hr{Daggerrain falls}{\Daggerrain{} falls}, his connection to \Erebos{} fails and he falls prey to the \xsic{} slumber. 







\subsection{\Miith is once again in \Miithian hands}
\hr{Daggerrain falls}{\Daggerrain{} is gone}. So now the supreme leaders of the \resphain{} are Ramiel and \hr{Azraid}{\Azraid}. There are still \banelords, but they cannot replenish their number, so they will eventually be hunted down and destroyed. 

Similarly, \Vizsherioch{} falls prey to the \xzaishannic{} slumber. The lords of \dragonkind{} are \Ishnaruchaefir{} and some other \uber-dragons. 

The \Erebean{} and \Machaic{} overlords are gone, and only their descendants remain. The future of \Miith{} now once again belongs to \Miithian{} powers. 









\subsection{The Shroud is torn}
In the process of this whole thing, the Shroud has been ripped and torn and now lies greatly weakened. A climax of this was the \hr{Glaive is destroyed}{breaking of the glaive \Triestessakhin}. 

The \charade{} is breaking apart and the old world order is crumbled. 

The \hs{Unravelling brings chaos}. 
The world will descend into chaos and anarchy. 

\lyricstitle{\cite{HPLovecraft:TheCallofCthulhu}}{
  The most merciful thing in the world, I think, is the inability of the human mind to correlate all its contents. We live on a placid island of ignorance in the midst of black seas of infinity, and it was not meant that we should voyage far. The sciences, each straining in its own direction, have hitherto harmed us little; but some day the piecing together of dissociated knowledge will open up such terrifying vistas of reality, and of our frightful position therein, that we shall either go mad from the revelation or flee from the deadly light into the peace and safety of a new dark age.
  
  [\prikker]
  
  That cult would never die till the stars came right again, and the secret priests would take great Cthulhu from His tomb to revive His subjects and resume His rule of earth. The time would be easy to know, for then mankind would have become as the Great Old Ones; free and wild and beyond good and evil, with laws and morals thrown aside and all men shouting and killing and revelling in joy. Then the liberated Old Ones would teach them new ways to shout and kill and revel and enjoy themselves, and all the earth would flame with a holocaust of ecstasy and freedom.
}

A new world order will establish itself, although it may take centuries. 

\index{technology}
\Ishnaruchaefir{} predicts that the Shroud will mostly unravel and fade away. With the loss of the Shroud, \hs{technology} will again accelerate. 

A suggestion for an epitaph: 

\lyrics{
  The \charade{} is broken. \\
  The Shroud is sundered. \\
  Now, let the arms race begin.
}

Knowledge will escalate, and so will war. 
In a way, this is \hr{Ishnaruchaefir sees three futures}{\ps{\Ishnaruchaefir} nightmare} come true. 

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\prikker 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}





\subsubsection{The Space Age begins}
Both races will now venture into space, looking for new \dweomers{} to consume to feed the dying Heart. 




\subsubsection{The \banes{} still exist}
Make it clear that the \banes{} have only been banished, not destroyed. 
\Daggerrain{} still lives. 
He will be back. 
\Miith{} has gained a reprieve. 
Maybe a thousand years. 
Maybe less.
However long or short it takes, the \banes{} \emph{will} return. 

So all this talk about \quo{evolution towards perfection}, which obsesses both sides in the Feud, is more relevant than ever, if Mith is to prepare itself and be ready to face the \ps{\Voidbringer} attack a \emph{fourth} time. 






\subsubsection{A respite for the Heart}
\target{Respite for the Heart}
The Heart of \Miith{} is finally freed from \hr{Heart weakened}{the scourge of the \sephiroth{} and the \Morbus}. 
The millions upon millions of imprisoned souls finally die and are released back into the Heart. 
This lets the Heart regain some of the stolen lifeforce and thus grow in strength. 

But this is just a temporary respite. 
The menace of the \banes{} is gone, but the remaining two master races (\dragons{} and \resphain) still battle for control of the Heart. 
The two races \emph{cannot} coexist\dash their \matrices{} are inherently incompatible and inimical, ripping and tearing into the Heart\dash and the Heart will continue to be drained and weakened until this war comes to an end. 

So the war for the Heart escalates again (as per the \quo{arms race} above). 
After all, this is what the Heart is: 
Life and death, beauty and ugliness, love and cruelty. 
Nature. 

\Miith{} is a cruel world. 





\subsubsection{Ramiel rules}
The old world order has crumbled. 
Ramiel is now the lord of the \resphain.

\citebandsong{Arcturus:AsperaHiemsSymfonia}{Arcturus}{
  Raudt og Svart
}{
  Deira dagar har m\o rkna\\
  Moder jord meld sitt fraafall\\
  Men sverdet har gaat vidare\\
  Til ein ny b\ae rar
  
  Me er einsomme menn\\
  Me b\ae r fenresulvens muspell\\
  Skoll skal sluka sola
  
  Me er djerve menn\\
  
  Sola svartner\\
  Der fjellvegg ramlar\\
  Naa gjestar sorgen\\
  Paa livets tre \\
  Yggdrasil
  
  For byleits bror farar\\
  Kva er det ikkje Kampfar klarer?
}





\subsubsection{Ramiel and \Ishnaruchaefir}
Ramiel and \Ishnaruchaefir{} are on the Ark and chatting. 

\begin{prose}
  \Ishnaruchaefir:
  \ta{Perhaps the \banelords{} will find us again.
    Perhaps not.
    Perhaps there will one day be peace between our two peoples.
    Perhaps one of our races will become extinct\dash or both.
    Perhaps we will somehow find the means to wage war for all eternity.
    Who knows?}
  
  Ramiel:
  \ta{%
    We \resphain{} have always held that science is one of our greatest weapons and assets.
    We know\dash or believe\dash that we are set in the world to rise above our nature.
    I will take command of the \resphain{} here, and I will see to it that we rise to our fullest potential.
    I am Overlord now\prikker}
  
  \Ishnaruchaefir:
  \ta{Overlord of what?
    I doubt any traces of the old world order have survived the exodus of the Ark.
    I doubt that \Mystraacht{} even exists anymore.}
  
  Ramiel:
  \ta{I have seized a throne by force before and I can do it again.
    And know this: 
    My goal is to secure the future of \Mystraacht.
    No one else's. 
    Maybe this road will end in peace.
    But if I must destroy your people\dash or any other\dash so that mine may live, then so be it.}
  
  \Ishnaruchaefir:
  \ta{Heh. So be it.}
\end{prose}

Remember that after the exodus of the Ark, \Mystraacht{} does not really exist anymore. 
So Ramiel is no longer Overlord. 
But:

\begin{prose}
  Ramiel:
  \ta{I have seized a throne by force before and I can do it again.}
\end{prose}







\subsubsection{\Ishnaruchaefir{} looks forward}
The very last scene of the book is with \Ishnaruchaefir{}.
He looks forward the chaos and war that is to come. 
No longer will he hide and huddle in some Asylum. 
He will fight. 
It will be\prikker exciting. 

Remember: \emph{End on a dark note!}









\subsection{The cost of the \thirdbanewar}
The \thirdbanewar{} is the most costly and most apocalyptic of the three \banewars. 
It did not kill as many people in absolute numbers as the first two had done, but it killed a larger percentage of the population. 
The population is smaller at this time, remember. 

\Daggerrain{} is now gone, but \Miith{} has paid a terrible price. 
Ahead wait centuries of chaos, blood and war. 














\section{The Future}
After a thousand years or two, a new interstellar civilization centered on \Miith{} will be established, and a \quo{science fantasy} aera will begin. Compare to \emph{Warhammer 40.000} and \bandalbum{Bal-Sagoth}{The Power Cosmic}. 









\subsection{\Resphan/\dragon hybrids}
Perhaps some day in the far future, someone will begin experimenting and trying to create a race of \resphan/\dragon{} hybrids. 
These will try to conquer the races and destroy those who will not join them. 
This is seen as evil, but the intent is good: 
Only a hybrid race can stop the war and let the Heart of \Miith{} live on in peace. 









\subsection{New cosmic empire}
In the far future, after the exodus from \Miith, the \dragons and \resphain ended up ruling each their vast interstellar empire spanning dozens or hundreds of planets. 
They became super-technological and super-magical civilizations close to rivalling the \voyagers in technology, but far surpassing them in aggression and greedy ambition. 
The \voyagers were a peaceful (if decadent) race of scientists and explorers. 
The exiled \Miithians were warriors and conquerors at their very core.

At this time, the \dragons and \resphain had found new \dweomers to sustain them, so they no longer had to fight each other for possession of the Heart of \Miith. 
But they were warriors by nature and instinct, so they still fought one another. 









\subsection{The return of \Tiamat}
\target{Tiamat returns}
\Tiamat returned to haunt the \dragons. 
She was \hr{Tiamat dweomer}{a \dweomer that fed through all \dragons in the universe}.
Though \hr{Tiamat imprisoned}{imprisoned}, \Tiamat was still a horrible parasite.
The \dragons had to struggle to be free of her.























\chapter{Random Ideas}












\section{\Shilred{} Story Arc}





\subsubsection[Ishnaruchaefir and his fake mission]{\Ishnaruchaefir{} and his fake mission}
\target{Ishnaruchaefir's fake mission}
\Ishnaruchaefir{} is clever. He knows about \hr{Teshrial's creatures}{the \noggyaleth{} in \Malcur}, or at least suspects them. So he \hr{Ishnaruchaefir attacks Teshrial's creature}{goes there to see for himself}. 

\Ishnaruchaefir initially believes \Secherdamon's plan takes place in \Malcur.
Then he falls for the \Forclin decoy when it is unveiled. 
He is impressed to learn that both were decoys. 

He has also seen through \ps{\Secherdamon} plan to resurrect \Nithdornazsh{} in \Malcur. 
He has more Sentinel contacts than most people realize, so he has spies telling him of \ps{\Secherdamon} plans. 
And he is an expert astrologer and \matrix-theorist, so he has picked up subtle clues concerning \Nithdornazsh{} and \Malcur. 

He knows that the \noggyaleth{} may put a stop to the plan. 
He wants to help his brother.
He does not fully approve of \ps{\Secherdamon} plan to resurrect \Nithdornazsh, but he helps out of respect for \hr{Nexagglachel}{\Nexagglachel}, since he still feels guilt and obligation towards him and his memory. 
\Nithd{} was \ps{\Nexagglachel}{} fortress, after all, so it can stand as a monument of sorts to the fallen \dragonking.

\target{Ishnaruchaefir's creatures}
So \Ishnaruchaefir{} plans to free some of his own servitors\dash\pdaemons, \dragons{} or otherwise\dash who are imprisoned in a cave or lost temple somewhere in the eastern \PelidorContinent. 

But he can't just go off and do that. He would be discovered and foiled by \hr{Teshrial}{\Teshrial}, the Cabalist in charge of the area around the cave. 

So \Ishnaruchaefir{} develops a circuitous plan: 
\hr{Ishnaruchaefir recruits Shilred-tachi}{He recruits \Shilred-tachi} and sends them off to fulfill an ill-defined quest for him, in the general area of the cave in question. He tells them to search for a cave or something like that. 

But whatever he alludes that he wants them to do is a lie. The purpose of their entire mission is to look suspicious. \Ishnaruchaefir{} shows up to help them just often enough that the sneaky Cabalists cannot help but notice, yet rarely enough that it still looks like he is trying to lay low. 

What he is actually looking for is another cave, where his servitors are imprisoned. 

The Cabalists in the area where \Shilred-tachi are going are led by \Teshrial{} (see section \ref{Teshrial}). We follow him in several chapters, where he fears \Ishnaruchaefir{} and tries to guess his plan. 






\subsection{Rissitic invasion}
Some time after the Rungerans cross the Pelidorian border, Rissitic fleets sail north to besiege and conquer cities in \Scyrum. 
%march north from Gaznor into Beirod. They besiege and conquer Beirodi cities. 

%Or\prikker wait\prikker is it Beirod they attack? Or is it \Scyrum? \Scyrum{} might make more sense. 

For the Rissitics, controlling more land in \Velcad{} is nice, but the chief purpose of this attack is to draw the Redcor away. See, in intra-\Velcadian{} wars the Redcor traditionally take little part, acting mostly as negotiators and healers. But in case of a major attack on an Iquinian kingdom by a heathen invader, the Redcor typically offer more direct aid, participating in battles with their magic. So when the Rissitics invade, the Redcor are forced to send Vaimons from the entire region to help oppose them. 
This makes the invasion harder, but it has the nice bonus feature that it leaves \Malcur drained of Redcor, making it easier for the Sentinels to operate there. 

We follow Narkiza on his march north through \Scyrum. 

%Is Geldashad with him, or is he off on a mission of his own?

%What about \Shilred? 

Remember to describe the Rissitic army as \hr{Glorious armies}{magnificent and glorious}.







\subsection{\Shilred-tachi get lost in \Nyx}
\Shilred{}, \Dzasselid{} and \KarsaOrlong{} (see \ref{Karsa Orlong}) take part in the initial attack on a port city in southern \Scyrum. Maybe they are together with Mestos and Semphai. Anyway, during the battle they become separated from the main army and nearly get killed by \banes. %Maybe they even flee out of the mortal Realm and stumble into \Nyx. 

Maybe \Dzasselid{} deliberately takes them into \Nyx. Perhaps he has a back-story as a double agent for the Cabal, and thus knows his way around in \Nyx. Or something like that. He needs some skeletons in his closet, remember?

At any rate, they end up in \Nyx{} and get surrounded by \banes{} or other monsters. 






\subsubsection{\Ishnaruchaefir{} approaches}
Just when \Shilred-tachi are about to be killed, \Ishnaruchaefir{} appears. He appears in humanoid form. Using magic (incl. the spell \quo{\kingstongue{khestni}}) and his mighty glaive (see section \ref{Ishnaruchaefir's glaive}), he slays the monsters and saves them. The monsters should be huge, monstrous and menacing, like in the anime \emph{Devil May Cry}. 

Given that they owe him their lives, he claims them as his own. Perhaps one of the \Gisshorns{} knows who he is and convinces the others to be respectful. Somehow or other, \Ishnaruchaefir{} beats it into their heads that he is a high-ranking ally of Rissit and that they should obey him. 

Maybe \Ishnaruchaefir{} first approaches \Narkiza{}, gives a little help and asks to borrow some of his men. 






\subsubsection{\ps{\Ishnaruchaefir} mission}
\target{Ishnaruchaefir recruits Shilred-tachi}
\Ishnaruchaefir{} sends them on a private, secret mission. He wants them to find a cave somewhere in western \Velcad{}, where they must do fulfill some as-of-yet unspecified task for him. 

\Ishnaruchaefir{} tells them that he cannot go off searching for the cave himself, as he would be detected and attract Cabal attention (and Sentinel attention, for that matter). But he teaches them an invocation that will summon him, to use when they reach the cave or are in dire need of his help. 

\hr{Ishnaruchaefir's fake mission}{The above is actually a lie.}







\subsection{\Shilred-tachi go into the \Wylde}
On their mission for \Ishnaruchaefir, \Shilred-tachi must go into the \Wylde{}. \Ishnaruchaefir{} throws them into some place which has a tenuous link to \Nyx. Perhaps a cave system that was once inhabited, or a ruined castle. It must be something sort of urban area, since \Nyx{} is city-like. 

From there, they go out into the \Wylde{}. They fight their way through monster-infested jungles. 

Maybe they encounter a native tribe. Maybe they help them, like how Karsa Orlong helps the Anibar in \emph{The Bonehunters}. Maybe they just coerce them into accepting them. Maybe they hire native guides, who later die. 

They are chased through the \Wylde{} by savage monsters, maybe zombies or lycanthropes. Monstrous almost-humanoids, at any rate. Occasionally they are harassed by the Cabal. 







\subsection{\Shilred-tachi find a ruined city}
\Shilred-tachi find a ruined city out in the wild, with broken walls, toppled towers, defaced monuments and statues and the like. It is decrepit, dead, moss-grown and spooky. 

Compare to the cemetery in the movie \cite{Movie:HouseoftheDead}. 

Remember to have some references: 
\ta{%
  There are many places of power in the world, places of convergence. Especially out in the \Wylde{}. After all, the \Wylde{} is far vaster than the settled world.}

Remember to have them fight monsters. Have a scene where \Dzasselid{} kicks the butts of loads of monsters. 







\subsection{\Shilred-tachi find a laboratory}
\Shilred-tachi fight past monsters and end up in the laboratory of some necromancer or witch-doctor. It is filled with mutilated corpses and deformed creatures\dash living, dead or undead. Like in the movie \cite{Movie:HouseoftheDead}. 







\subsection{\Shilred-tachi crawl around underground}
\Shilred-tachi find themselves underground in a system of dark, creepy, monster-infested caves. Like in the movie \cite{Movie:HouseoftheDead}. 








\subsection{\Shilred{}-tachi see great monsters in the distance}
%Remember \Shilred{} and her party. They need to do something intelligent. 
\Shilred-tachi, \travelling in the \Wylde{}, see some colossal creatures far off in the distance. They need to be at some special place or in special circumstances, being able to see into the Beyond, in order to be able to see them. 

Maybe they see the creatures on a background of \Nyx{} or \Machai{}, or maybe just the great mountains and forests of the Beast Realm (these are larger than the ones that can be seen from within the Shroud). 

Perhaps the creatures are \dragons{} and \banes{} fighting. 

Perhaps, in the end, they see \Ishnaruchaefir{} vs \Teshrial-tachi this way. 

Remember to drop hints along the way about how powerful and terrible \Ishnaruchaefir{} is. Perhaps when they see these monsters, they reflect about \Ishnaruchaefir{} and his awesome power. 







\subsection{\Narkiza{} on the move}
%Early on, we follow \Filshed{} and her party as they invade Fendor. 

We follow \Narkiza{}, first in the port city in \Scyrum, and later as his army pushes north into \Velcad{}. His invasion is one of several \quo{prongs} in the Sentinel scheme.

In \TwilightAngelRememberEmph, only little time is devoted to \Narkiza{} and the other Rissitics. They will be given much more screen time in \emph{\CarzainWithRedcorBook}. 
%in the scheme to awaken the \Haskelek, 

%\Filshed{}, maybe together with the two \Gisshorn, are sent as a second \quo{prong} on covert missions to revive parts of the \Haskelek. 

%A third \quo{prong} are the Rissitics that are with Morgan Runger. 

%There might be a fourth \quo{prong}, consisting of some non-Rissitic Sentinels. They might include \Cryocas{} and her lover, Nisgzarchiev. Or maybe Vlad Racul. 










\subsection{\Shilred-tachi reach the cave}
\target{Shilred-tachi reach the cave}
\Shilred-tachi finally reach their destination. 





\subsubsection{They see fantastic and terrible things}
They near the cave and travel through fantastic, alien Realms (perhaps parts of \hr{Machai}{\Machai}). Compare to \authorbook{Clark Ashton Smith}{The Door to Saturn}. 

They even see glimpses of the \xss. 
\Shilred{}, \hr{Shilred is a nerd}{being something of a nerd}, is amazed by what she sees. And horrified.

\lyricslimbonicart{When Mind and Flesh Depart}{
  I'm captured by the sound of the tempest winds, \\
  and my demonvoice that dwells within.\\
  The ground I walk is sour.\\
  A spectrum shines so genuine.\\
  While the earthquake starts to devour,\\
  I behold the shrine in the ruin.
}

She sees horrors and is disillusioned. 

\lyricslimbonicart{When Mind and Flesh Depart}{
  The human way of life, \\
  an inferior state of mind.
  The third stone from the Sun\\
  had become a stillborn illusion.
  
  I'm under siege of anger and fury.\\
  There is no values, no faith or glory.\\
  Antagonising mortal flesh.\\
  Life on Earth I do oppress\\
  with infernal bleedings of bitterness.
}






\subsubsection{\Teshrial{} moves out}
\Teshrial{} fails in his attempts to guess \ps{\Ishnaruchaefir} thoughts. 
When \Shilred-tachi ostensibly reach their destination\dash the main entrance to the cave\dash they are attacked by \ps{\Teshrial} monsters and must call on \Ishnaruchaefir. 
He appears in humanoid form to fight the monsters. 
\Teshrial{} is now convinced that \Ishnaruchaefir{} means business, so he rushes to his location in person, leading a group of mighty \banes{} and monsters. 





\subsubsection{Epic description of \Ishnaruchaefir{} as a \dragon}
\Ishnaruchaefir{} assumes his true, \draconian{} form. Insert an epic description of the mighty \dragon{} here, a la \bandsong{Bal-Sagoth}{Black Dragons Soar Above the Mountain of Shadows}. 

This is the first time we are shown a \dragon. 
Describe the mortals' awe at the sight. 
\Dzasselid{} might have seen one before, but \Shilred{} sure hasn't. 
She has heard \hs{myths} of \dragons{}, but reality surpasses the myths. 





\subsubsection{\Dzasselid-tachi are sent to the real cave}
\Ishnaruchaefir{} draws out all the Cabal monsters in the area. 

In the meantime, \Criseis{} sees to it that \Dzasselid-tachi are sent to the \emph{real} cave he is after\dash which is now mostly unguarded. 

They encounter some creatures that try to block their way. 
\Criseis{} zaps them.

\lyricsbalsagoth{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire - Part II: The Dark Liege of Chaos is Unleashed at the Ensorcelled Shrine of A'zura-Kai
}{
  [THE KING:]\\
  By the darkling powers of the Shadow-Sword, \\
  I call forth the fury of the storm\\
  to rend the massed legions of Chaos!
  
  [ALTARUS:]\\
  And at the sound of his baleful Words of Power, \\
  the sky split wide in fury, \\
  and searing tendrils of ruinous lightning \\
  lanced inexorably forth from the heavens \\
  to rake and reave the massed hordes of Chaos\prikker
}

They find the creatures they are looking for and set them free. Thus \Ishnaruchaefir{} has tricked \Teshrial{}, and his circuitous plan has succeeded. The freed monsters now rush to \Malcur to assist in the summoning of \Nithdornazsh. 

See \hr{Ishnaruchaefir kills Teshrial}{here} for the end of the fight.






\subsubsection{\Shilred{} is left behind near the cave}
\Shilred{} accidentally gets separated from the rest and stays behind near the cave. 
She gets to see the fight between \Ishnaruchaefir{} and \Teshrial{} in all its gory glory. 















\section{Sir James story arc}
Sir James is a \human{} Iquinian knight living somewhere in \Velcad{}. 
It might be in the east, if I want him connected to the king-thing and Vlad Racul, or it might be in the west (Ontephar or \Scyrum) if I want him connected to Telcastora Ilcas. 
I think it's going to be in the east. 

There is also Sir Lawrence, another knight. 
Perhaps Sir James' companion. 

And Prince Alistair, who later becomes King Alistair. 
I think. 

And Vlad Racul, a mysterious sorcerer who is actually the \dragon{} Candrazor (a high-ranking Sentinel) in disguise. 

Sir James discovers a Rissitic plot somewhere. 
The Rissitics work on resurrecting a part of the \Haskelek{} \daemon. 
He goes to the Redcor for help. They set out to thwart the Rissitics. 
It turns into a big quest with all sorts of stuff going on. 
There's an evil Rissitic mastermind (who?) who keeps outsmarting them, but somehow the reader is assured that good will prevail. 
And then, in the end, I assfuck the reader by having the Rissitics win, and Sir James and his party of heroes are killed. 




\subsection{The beginning}
Sir James, as a knight and minor lord of sorts, is approached by the girl Lica, a commoner who's had visions, seen suspicous things. 
His advisors scoff at the girl's fanciful tales and persuade him to dismiss her, but he does so with doubts. 
Later stuff happens to him that convinces him she was right, so he seeks her out and brings her back. 

James or his companion asks Lica: 
\ta{How old are you, girl?}

\ta{I am sixteen, my lord.}

Later, James comments to his companion: 
\ta{She is pretty, though.}

The companion laughs. 
\ta{She is sixteen, James. 
  Even my warty cackling crone of a great-grandmother was pretty when she was sixteen.}

%Turns out that Lica has seen a \bane. The \banes{} are working on some big thing, so they are getting bolder and more careless. (It's for the same reason that Catrian saw a \bane{} earlier.) Or maybe she hasn't seen an actual \bane, but merely a Cabalist working magic. Or maybe some \Nyxian{} monster. 
Turns out that Lica has seen either a Sentinel mage or some \daemon. 
And it's a good thing that Sir James starts to believe her, because it turns out the Sentinels is after her. Assassins come for her and he has to protect her. They flee back to the castle or whatever, and the authorities (Redcor church?) finally believe that something is up. 

Lica is gifted in seeing into the worlds beyond. Since her childhood she has had trouble accepting the illusion that everyone else believes in. She always wanted to see through the lie, doubt what she was told. This has continued to the current day (she is now 16 or so) and lets her see many things that others can't, but it also makes her strange (she is unmarried and unbetrothed, and her parents worry) and affects her sanity. 

Alarmed by Lica's vision, the Redcor send a delegation to investigate. Lica is brought along as a guide of sorts, and Sir James goes as her protector. 









\subsection{Lica sees strange visions}
Lica sees grim and horrid visions. 
She hates this \quo{gift}. 

\lyricslimbonicart{The Supreme Sacrifice}{
  Thought are tyrants that always return\\
  to rape and torment the heart.\\
  As darkness sweeps the face of Earth,\\
  I enter the chambers of bleeding art.
}









\subsection{Lica sees the \Morbus}
Lica sees the \hr{Morbus}{\Morbus} at work. 
She has dreams of its evil consequences. 

She sees visions of \Nyx{} and mistakes them for visions of the future. 
She is scared shitless. 

\lyricsduana{thisistheend}{This is the End}{
  I dream of a host cockroaches \\
  crawling, swarming over charred flesh \\
  up bitter blackend walls \\
  in sewer pipes now purgd \\
  the cries of many amplifd \\
  then swallowd by silence \\
  echoes of a lost world \\
  of a foul smoke that lingers like stale breath \\
  of steel/glass/concrete fusion-statues \\
  rising high in a pale and infinite twilight \\
  shining beacons like bleachd bones 
  
  I see field upon field upon field \\
  of bloatd-cattle-corpses bleeding intestines \\
  staring with sightless opaque eyes \\
  of waves drowning mountains \\
  and the earth's flesh torn with angry fissures \\
  of molten-spewing-spittle \\
  and hot lashing tongues \\
  of a planet roaring/quaking/quivering \\
  with unbound vergence 
  
  shivers erupt through space and time \\
  and images flashing faster faster\prikker \\
  until finally all is annihilated 
  
  like a vacuum space sucks the debris \\
  into a black empty hole \\
  and I fall down into the void \\
  this is the end
}









\subsection{Lica suffers}
Lica feels like she is losing her innocence and being corrupted from the inside by the terrible truths she sees.

\lyricslimbonicart{Beneath the Burial Surface}{
  The sky is darkening, soon the night befall.\\
  Righteously angels are weeping for my soul.\\
  All childhood dreams are soon to be lost,\\
  all innocence to be shattered.
  
  I am the fallen from grace.
  
  My face is a river.\\
  See my eyes as they drown in black.
  My sacred doom and nemesis\\
  beneath the burial surface\\
  To the final act of the immortal sin\\
  I am lead by funeral winds.
}









\subsection{Lica can curse people}
Lica discovers at a young age that she can curse people. 
When people are mean to her or refuse to believe her, she can stare at them and hate them and wish them ill\dash and sometimes it happens.
This is a manifestation of her (albeit weak) \vertex{} powers. 




































 

 
