














\section{\Sethicus and his research}
\Sethicus was an \ophidian polymath.
He was controversial because he delved into sorceries \hr{Ophidians and XS}{which the \ophidian{} establishment frowned upon}. 







\subsection{Technology and \Sethicus's innovation}
\target{Sethicus brought innovation}
When the \dragons were created, the \ophidians had only begun to build an \hs{interstellar civilization}. 
So the \dragons had only limited knowledge of the \ophidian super-technology.
The \dragons and \ophidians would both continue to develop their knowledge in the coming millennia, but in different directions. 

The \ophidians were generally \hr{Ophidians are slow}{long-lived, slow-living and slothful}, so they developed new ideas only slowly. 
Hence \hr{Early Ophidian culture}{their culture lasted for millions of years}.

\Sethicus's time was characterized by very fast development. 
\Sethicus was a very impatient and ambitious \ophidian.
He craved more than his race's slow, complacent lifestyle.
He craved action, excitement and renewal.
He was a great scientist who made many inventions.
He inspired many followers to live fast like him. 
In those decades and centuries, technology developed just as quickly as it might for a short-lived race.

\Sethicus himself was a brilliant scientist and made many exciting new discoveries in various fields. 
Later in his life, he became preoccupied with alienist sorcery.
This came to dominate his life and career. 

\Sethicus was a primus motor when it came to pushing the boundaries of space travel and establishing an interstellar \ophidian empire. 
Before him, they had been a spacefaring race for millennia, but rarely ventured beyond their solar system, and they had done no colonization beyond the occasional research station in the solar system. 
\Sethicus made them found settlements on many planets and moons in the solar system and even beyond it, and they began terraforming processes. 





\subsubsection{Energy sources}
\target{Draconian energy sources}
\Sethicus's society required colossal amounts of energy to sustain it.
To procure enough energy they used dark spells to draw energy from the void and the Heart, and they sacrificed vast numbers of humanoids to feed their machines. 

\Sethicus himself helped build this network of power plants.
He used complex black spells which only he fully understood to suck even more energy from the dying universe so it could fuel his \hr{Sethicus plan}{masterplan}. 

Compare to the Immortal Emperor and the Astronomican in \cite{RPG:Warhammer40000}, which requires the sacrifice of countless \humans daily to sustain them.









\subsection[Sethicus and Tyrasshana]{\Sethicus and \Tiamat}
One of \Sethicus's more important allies was \hr{Tiamat}{\Tiamat}. 

Originally she was his assistant and servant.
She followed him around on his journeys and learned much. 





\subsubsection[Tyrasshana's]{\Tiamat's motivation}
\Tiamat wanted to make the world a better place, lift her people out of warfare and strife, oppression of Worms and all-round suffering.
She saw the existing \ophidian oligarchy as decadent and corrupt. 
She saw the dystopia of the \hr{Enslaved Ophidian subraces}{enslaved \caisith subraces} and wanted to change it.
She wanted to seize power and achieve \quo{great things} (whatever that meant). 









\subsection{Discovering the \xss}
\target{Sethicus maps the way to Machai}
\target{Star-Maps of the Ancient Cosmographers}
\Sethicus-tachi discovered the \xss{} from some ancient ruins\dash perhaps left behind by the \voyagers. 
Together they charted the cosmic paths leading to \Machai, the \xzaishannic{} homeworld that had been lost after the fall of the \ophidians. 
(These are some of the same paths that Chaos sorcerers would use millennia later.)





\subsubsection{\Ophidian origin}
\target{Sethicus discovers Ophidian origin}
It had been theorized that \hr{Ophidian parentage}{the \ophidians were descended from \xss}. 
It was \Sethicus who really understood the connection. 
He theorized that the \ophidians were related to the \xss.
Perhaps even created by them, or at least evolved from creatures created by them.
\Sethicus believed they had been \hr{Sethicus believes Ruin Satha created Ophidians}{imparted hunger/will/motivation by \RuinSatha, and then physical life by \KhothSell}. 
And he shaped his beliefs into mystical theories that could be used to cast magic. 

\citeauthorbook[p.16]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  A sliver of this transcendent black essence dwells in the darkest part of man's being. 
  Yes, a fragment of this demonic god lives inside every man, allowing him to be part of Greater Reality.
  Because \human reasoning has developed enough to understand unnatural logic, non-Euclidean geometry, quantum physics, string theory, abstract thinking and our holographic universe\prikker we can begin to understand what lurks Outside!
  
  We are the children of the Old Ones, and we are their progenitors.
  A select group of \human beings shall keep the Dark Gods alive in their words, their thoughts, and their deeds. 
  Because of our insane beliefs, a fragment of Greater Reality has Awakened inside us.
  Some liken this to a black flame, twist of Cain, being touched by the hand of God, an alien encounter, a divine spark, mark of Satan, gidt of Set, or call of Cthulhu.
  
  Whatever its name, it exists in the hitherto unexplored areas of our mind like some cyclopean race memory to which we are irrevocably drawn.
  This evolutionary nudge that was given to out species aeons ago allows us to comprehend godlike knowledge and become godlike ourselves. 
  
  \prikker seek out those Those Who Came Before.
  The Old Ones' understanding is carried on through the Cult of Cthulhu.
  Our organization merely tries to uncover Their ghastly, depraved illumination.
  The unknown can be terrifying, but that does not stop us from grasping it. 
  
  \prikker 
  
  The religion of the Old Ones\prikker is based upon the concept of fear.
  The unknown is the heart of both theologies.
  That nameless, black quality which forces the \human imagination to conjure up the richest dreams and the most hideous terror\prikker
  
  Fear that is felt, fear that drives, attracts, repels\prikker fear that is overcome!
  Inside the unknown is out salvation, if we have the courage to look\prikker and then plunge our warlock hands into the unplumbed, inky vortex!
}





\subsubsection{Voyage of discovery}
They explored the cosmos, looking for illumination and arcane knowledge. 

\lyricslimbonicart{Dynasty of Death}{
  I'm launching into the abysmal universe.\\
  Disembodied I enter the cosmic cataclysm.
  
  I discover stairways to celestial dreamscapes\\
  A dark unknown conjunction within an immoral dimension.
  
  Through dark tunnels in levitation, \\
  black cosmic space in manifestation.\\
  I escape the earthly pandemonium\\
  into a vast nocturnal sanctum.\\
  A nemesis for all evil I confess.\\
  My soul bleeds by all the forces I possess\\
  A benediction of unholy wrath and sorrow.\\
  My heart is buried in dark catacombs of horror.
}

They learned the grim truths and secrets of the universe. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  They
  were the words of a great thaumaturgist who had seemingly discovered a
  repository of aeons-old lore detailing the sidereal web of the cosmos, with
  arcane diagrams pinpointing certain astral portals and places of empyreal
  potency, a sort of pangalactic ley-line chart, if you will. 

  [The Thaumaturgist:]\\
  The Great Eye of the Universe opens! \\
  Through this astral art the secrets of the cosmos are mine to know\prikker \\
  for the stars are my dominion!
}

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Everything you have been taugh about the nature of Creation is a lie. \\
  This is a voyage in search of the truth. \\
  It will not be a pleasant journey.
  
  I have discovered a terrifying universal axiom which cannot be denied.
}

They learned of the origin of their people, and all life.

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Betwixt the hammer and the anvil are forged the stars\prikker \\
  On the wings of the ersatz ones\prikker \\
  through the fathomless abyss.
}

They feared this discovery, and the madness that the \xss{} might bring. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Like a blackened and baleful sun shall I gaze down \\
  from beyond the cumuli and the firmament upon you. \\
  I alone must bear the burden of this fiend-wrested lore.
  
  New stars without number burn in the heavens, \\
  but the shadow of oblivion falls ever closer.
}

She discovered a wealth of cosmic knowledge, comparable to the Sith library in the game \emph{Knights of the Old Republic II: The Sith Lords}. 
Also comparable to the tale of the Empyreal Lexicon by Bal-Sagoth. 

\lyricsbalsagoth{Return to Hatheg-Kla}{
  Some would call it epiphany, others would deem it the final descent into madness\prikker whatever the case, the last vestiges of those tenuous palisades which had previously, and blessedly, safeguarded my reason and prevented my mind from accepting the full and staggering magnitude of the naked truth then crumbled, fading into nothingness like the dissolution of a night-mist.\\
  At length, one oppressively miasmic night, with such malefically portentous lore preying pitilessly upon my sanity, I began to descend through a myriad veils of sombre and swirling shades, finally surrendering my grip on wakefulness.\\
  And on that fitful, fateful eve, the last of the dreams came\prikker\\
  A waking dream?\\
  I dare not speculate.}

\Sethicus was excited.
He was beginning to learn the ancient spellwords that would later become known as the \TrueDraconic tongue. 

\citeauthorbook[p.316]{HPLovecraft:TheDiaryofAlonzoTyper}{\HPLovecraft}{%
  The Diary of Alonzo Typer%
}{%
  At last my dreams are to be realised!
  Whether or not my life or spirit or body will be claimed, I shall enter the gateway!
  \ldots
  
  There is beneath this house\dash sepulchred I know not where\dash an ancient forgotten One who will shew me the gateway I would enter, and give me the lost signs and words I shall need.
  \ldots
  Men of this earth know It not, save in the secret whispers of the fear-shaken few who have found or inherited the key.
  No \human eye has ever yet glimpsed It\dash unless, perhaps, the vanished wizards of this house delved farther than has been guessed. 
  
  With knowledge of the symbols came likewise a mastery of the Seven Lsot Signs of Terror\dash and a tacit recognition of the hideous and unutterable Words of Fear.
  All that remains for me to accomplish is the Chant which will transfigure that Forgotten One who is Guardian of the Ancient Gateway.
  I marvel much at the Chant.
  It is composed of strange and repellent gutturals and disturbing sibilants resembling no language I have ever encountered\dash even in the blackest chapters of the \emph{Livre d'Eibon}. 
  \ldots
  
  \ldots
  
  Today dark ominous clouds have hovered intermittently over the circle on the hill.
  \ldots 
  They are snake-like and fantastic, and curiously like the evil shadow-shapes I have seen in the house.
  They float in a circle around the primal cromlech\dash revolving repeatedly as though endowed with a sinister life and purpose.
  \ldots
  Are they indeed those dread Ones whom Solomon knew of old\dash those giant black beings whose number is legion and whose tread doth shake the earth?
  
  I have been rehearsing the Chant that will transfigure the Nameless Thing, yet strange fears assail me even when I utter the syllables under my breath.
  Piecing all evidence together, I have now discovered that the only way to It is through the locked cellar vault.
  The vault was built with a hellish purpose, and must cover the hidden burrow leading to the Immemorial Lair.
  What guardians live endlessly within, flourishing from century to century on an unknown nourishment, only the mad may conjecture. 
  
  \ldots
  
  \quo{The secrets of the monstrous primal Ones,} ran the crabbled text, 
  \quo{%
    whose cryptic words relate th ehidden things that were before man; the things no one of earth should learn, lest peace be forever foreited; shall by never suffer revelation.
    To Yian-Ho, that lost and forbidden city of countless aeons whose place may not be told, I have been in the veritable flesh of this body, as none other among the living has been.
    Therein have I found, and thence have I borne away, that knowlege which I would gladly lose, though I may not.
    I have learnt to bridge a gap that should not be bridged, and must call out of the earth That Which should not be waked or called.
    And what is sent to follow me will not sleep till I or those after me have found and done what is to be found and done.}
  
  \quo{%
    That which I have awaked and bornre away with me, I may not part with again.
    So is it written in the Book of Hidden Things.
    That which I have willed to be has twined its dreadful shape around me, and\dash if I live not to do the bidding\dash around those children born and unborn who shall come after me, until be bidding be done.
    Strange may be their joinings, and awful the aid they may summon till the end be reached.
    Into lands unknown and dim must the seeking go, and a house must be built for the outer Guardians.}
}






\subsubsection{\XzaiShanns slept}
At \Sethicus's time, the \xss had long been very deep in their sleep. 
As a consequence, the \Miithians had all but forgotten them. 
Many \ophidians did not believe they existed, and they did not believe that magic (in the form \Sethicus proposed) was even possible. 

But the \xss had begun to stir ever so slightly.
Thus \Sethicus was able to discover them and learn some of their secrets and make pacts with them so he could cast magic. 
\Sethicus became the founder of alienist magic.





\subsubsection{The keys to insight}
In order to summon the \xss{} and invoke their power, \Sethicus-tachi discover that they must find a number of \quo{keys}. 
After a while of searching they finally realize that the \quo{keys} are not physical objects but insights. 

They are told that some of the keys must be captured from their rival races. 
They only manage to do this when they realize that what they are supposed to steal/conquer is knowledge, not artifacts. 

\lyricsbalsagoth{Return to Hatheg-Kla}{
  A terrible sound filled my ears\prikker \\
  an insidious resonance which sent waves of excruciating pain coursing through my mind\prikker \\
  a sound which inexorably coalesced into a recognizable but entirely inhuman voice, a voice which slowly, inevitably, formed approximations of words which I could discern\prikker
  
  [The Crystalline Oracle:]\\
  Hearken, o' manling of the Tellurian orb\prikker the Circle closes.\\
  Perpare to embrace the agony of enlightenment.\\
  Know you of the Six Cataclysms?
  
  [The Aspirant:]\\
  I do. Six times has the world perished and been reborn!
  
  [The Crystalline Oracle:]\\
  You have discovered the true meaning of the six coruscating rings of arcane power?
  
  [The Aspirant:]\\
  Praise Klatrymadon and Zuranthus! The Six Keys!
  
  [The Crystalline Oracle:]\\
  Know you of the blackened orb which burned bright o'er ancient Lemuria?\\
  Know you of the sidereal flame which engulfed the high seat of power in Ultima Thule?\\
  Know you of that martial sorcery woven in the pitiless throng of epic battle?\\
  Know you of the astral power permeating the multiverse and the might of the cosmic codex?\\
  Know you of the rise and fall of glorious Atlantis?\\
  Know you the blasphemies contained within the Chthonic Chronicles?
  
  [The Aspirant:]\\
  I know all this, and more!
  
  [The Crystalline Oracle:]\\
  Have you, o' hybrid child of the cosmos, gazed into the Great Eye of the Universe?
  
  [The Aspirant:]\\
  I have.
  
  [The Crystalline Oracle:]\\
  And what did you see there, young Xerxes?
  
  [The Aspirant:]\\
  I saw oblivion and damnation.\\
  I saw truth, and enlightenment.\\
  I saw the closure of the Great Circle Without End.\\
  I saw the Sixth Great Cataclysm.\\
  I saw the alpha and the omega, \\
  I saw the beginning\prikker and I saw the end.\\
  The end of all there is!
}





\subsubsection{Summoning the \xzaishanns}
\target{Origin of Draecchonosh}
\target{Sethicus contacts XS}
\Sethicus-tachi contacted the lords of the \xzaishanns{} and learn to channel their power. 
They even absorbed some of the \ps{\xzaishanns} souls into themselves, transforming themselves into the mighty \draecchonosh. 

Have a scene where \Sethicus-tachi summon the \xzaishannic{} power, similar to \bandsong{Bal-Sagoth}{Summoning the Guardians of the Astral Gate.}

\lyricsbs{Hate Eternal}{Catacombs}{
  Rise up from the ancient tombs. \\
  Grant us all your infinite wisdom. \\
  Endure as you rise from the catacombs. 
}

\lyricsbs{Hate Eternal}{The Creed of Chaotic Divinity}{
  Awakened by this ancient creed. \\
  Evoked, the ancestry of thee.\\
  Forsaken for centuries of times. \\
  Exiled, all of their kind. \\
  Foretold, the inheriting of the Earth.\\
  Forewarned of this predestined rebirth. \\
  Engaged, the rising from below.\\
  Fear, all mortals, for what they shall bestow.
  
  Conjure all, so that they may sustain\\
  their race, of what they must retain.\\
  Spew forth incantations in vain. \\
  Invocate all that they try to negate.\\
  Enchant all of their wonderful splendour. \\
  Recant all of the texts that are sacred. \\
  Recreate all that has been begotten. \\
  Revive all that has been forgotten. 
}

\lyricsbalsagoth{The Empyreal Lexicon}{
  The key word of Transcendence!\\
  The key word of Transference!\\
  I shall liberate the rightful owners of the Lexicon\prikker\\
  the true rulers of the cosmos!
  
  X'atham-ry'aa! Tha'zai-tonn!\\
  Darker than a score of hells\prikker \\
  wherein astral horrors sublime dwell,\\
  Macrocosmic realms aflame\prikker \\
  Prey of fiends that have no name!\\
  Bow to the gods that have no name!}

The \xss{} are powers of evil whom the \ophidians{} used to fear. 

\lyricsbs{Vital Remains}{Icons of Evil}{
  Confront me now, defiler of human desire.\\
  Voracious hordes await the hour of ascension.\\
  Unravel their delusion,\\
  their translucent divinity.
}

When \Sethicus-tachi first invoke the \xzaishannic{} power, it goes wrong and the \xzaishanns{} wreak immense destruction. 
It takes some time for \Sethicus-tachi to learn to control and channel their power. 

\lyricsbalsagoth{The Voyagers Beneath the Mare Imbrium}{
  Fools! The Darklight Portal has grown strong.\\
  Only one moon remains in orbit.\\
  The mewling ape-spawned humans have discovered the icosahedron and the Lexicon's call can once again be heard throughout the stars, beckoning my ireful brethren to return to the slaughterous embrace of the fray!\\
  We have won! The orb azure is ours\prikker ours to enslave!}





\subsubsection{Guide appears}
\target{Sethicus's guide}
A guiding god appears to \Sethicus-tachi: 
\hr{Achamoth}{\Achamoth}, the messenger of the \xss and the vizier of \RuinSatha. 

He gifts them with knowledge and makes them worship the \xss{} and \Chaos. 
Compare him to Nyarlathotep from \HPLovecraft's stories. 

\lyricsbalsagoth{The Chronicle of Shadows}{
  [The Imperator of the Night \\
  (Hearken to the Attestation of the Sinistrous):]\\
  For it is the iniquity of man which compels him to these tenebrous gates,\\
  seeking opiate dreams and the alluring embrace of oblivion\prikker
  
  Such adoration bestowed upon me beneath the cryptic moon!
  
  (Behold the true purity of that which lurks concealed beneath the mantle of 
  shadow, and let the deluded, debauched sybarites flee in terror from that 
  darkness which they profess to embrace!) 
  
  Beyond the spheres of light and darkness, \\
  beneath distant pallid stars, \\
  I bring the iridescent glimmer of forbidden truth, \\
  seared in the crucible of blasphemy! 
  
  For amorphous they come, steeped in the fetor of ten thousand years, \\
  Abhorrent colossi spawned from the sinistrous cosmic spheres.
  
  And upon their tongues, vile secrets so terrible sweet madness is a redolent balm!
  
  Rejoice and revel in the triumph of the Dark. 
  
  I shall glut the maw of that ineffable nameless evil which lurks forever in the soul of man, for so it is written in the Chronicle of Shadows\prikker
}

\Xserasshana{} receives the \hr{True Draconic}{\TrueDraconic} tongue from the \xss. 

\lyricsauthorbookpage{Anton Szandor LaVey}{The Satanic Bible}{29}{
  Each verse is an inferno, each word is a tongue of fire.
  The flames of Hell burn fierce\prikker and purify! 
}





\subsubsection{Enlightenment}
\Sethicus achieved a great spiritual enlightenment. 
Compare this to:

\begin{itemize}
   \item 
     Randolph Carter's enlightenment in \cite{HPLovecraft:ThroughtheGatesoftheSilverKey}.
   \item 
     Randolph Carter's quest for Kadath and his ultimate ride towards the throne of Azathoth in \cite{HPLovecraft:TheDreamQuestofUnknownKadath}. 
   \item 
     Walter Gilman's dreams of Azathoth and Yog-Sothoth in \cite{HPLovecraft:TheDreamsintheWitchHouse}. 
\end{itemize}









\subsection{\Sethicus's allies}
Among \ps{\Sethicus} other allies were \ApepNesthra and \Iurzmacul. 

They attracted allies by tempting them with power, glory and greatness.

\citeauthorbook[\quo{First Thought in Three Forms}, p.86--100]{%
  BentleyLayton:TheGnosticScriptures%
}{%
  Bentley Layton%
}{%
  The Gnostic Scriptures%
}{
  So, then, hear me O children of thinking; hear the voice of the mother of your mercy.
  For you have become worthy of the mystery that has been hidden since eternities, so that you might [\prikker].
  And the end of this realm and of this violent.
  I am androgynous, a parent with myself alone.
  [\prikker]
  The entirety through me alone. 
  It is I who am the womb of the entirety, giving birth to the light in glory.
  It is I who am the aeon that [\prikker] the completion of the entirely, namely Meirothea, the glory of the mother,
  And I project a voice of the sound into the eats of those who recognize me.
  And I am calling you to enter the superior, perfect light.
  When you enter it you will be glorified by the glorifiers; the enthroners will give you thrones; you will be given robes by the enrobers, and the baptists will baptize you; so that along with glories you become the glory in which you existed, luminous, in the beginning. 
}

The part about \quo{in the beginning} refers to the idea that \hr{Ophidians related to XS}{their pre-history is connected to the \xss}. 










\subsection{Worshipping the \xzaishanns}
At first, \Sethicus and his fellows retained the \ophidians atheism and merely consorted with the \xss. 
Later they began to admire them more. 
As time went on, they became addicted to the power that the \xss could bring, and the began to worship them in earnest. 

\lyricsbs{Exmortem}{Sovereignty}{
  Admiring the triumphant demonthrone, \\
  sealed with the knowledge of time.\\
  Magic runes are carved here.\\
  Will you ever find the key?\\
  The bound demon in the earth\\
  is waiting to be released.
  
  He has \travelled beyond the worlds.\\
  He has danced with death.\\
  Now he controls it all.\\
  With strength he suffered.
}





\subsubsection{\XzaiShanns would soon rise}
\target{Sethicus believed XS would soon rise}
\Sethicus knew that the \xss were slightly more awake now than they had been for many ages.
In the beginning he interpreted this to mean that the \xss would soon arise and reconquer the world. 
Later he realized his error and revised his theories accordingly. 
It turned out the \xss were not at all about to rise. 





\subsubsection{\Sethicus understands the \xss}
\target{Sethicus understands XSS}
At this time the \ophidians still knew little about the \xss. 
Only hints and myths.
What little they knew, they feared.
Only a few mad cultists worshipped them, and with little success.
\Sethicus was the first who was strong and brave and daring and heretic enough to \hr{Sethicus understands XS}{\emph{understand} the \xss}. 

In order to do this he needed to understand the truth about the \hs{dead universe}, which was an indescribably awful truth that the \ophidians dared not face or even contemplate, even though their occult philosophy and science had by now given them sufficient hints to suspect it. 

This \emph{understanding} was something \Sethicus needed.
Only then could he begin to truly draw on the power of the \xss.
Only then could he envision the \TrueDraconic tongue and map out the \draconic theory of magic.







\section{\Sethicus (\yds{Sethicus creates Dragons})}
\subsection{\Dragons are created}
\target{Origin of Dragons}
\target{Sethicus creates Dragons}
\Sethicus became the first \dragon.
\Tiamat become the second.

\target{Dragons use Dreadnoughts}
Using their advanced gene-technology and psychometabolism and \Sethicus's \xsic{} sorcery, they designed a race of \ophidian{} super-warriors. 
They fused their own \ophidian bodies and minds with those of mighty \hs{Dreadnoughts}, infused with all the \xsic{} ferocity they could conjure up. 
A number of \ophidian{} warriors volunteered to be transformed into these new superbeings. 

When the experiments where at last successful, the result was huge, flying monsters: 
\Dragons. 

The \dragons were the first \hs{True Immortals}. 

The \dragons{} enslaved legions of \daemons{} that previously served the \xzaishanns. 
They turned their gaze on \Miith{}, bent on conquest.

\lyricsbalsagoth{The Voyagers Beneath the Mare Imbrium}{
  My power is absolute\prikker greater even than that of Angsaar himself!\\
  I shall crush the Tellurian sphere,\\
  and the flaccid lickspittles who strive in vain to safeguard it!\\
  Yes\prikker The dreaming is over!\\
  Now, let the vengeance begin!}

This newfound power corrupted them into chaotic, \daemonic{} beings. Twisted by the \xzaishannic{} souls within them, they almost became \xzaishanns{} in \ophidian{} form. 





\subsubsection{\Tiamat was the founding mother}
\Tiamat became the founder of the \draconian race.
She had a vision of a race of mighty super-\ophidians.
She convinced \Sethicus to help her in this endeavour.
Later ages would remember \Sethicus as the father of the \draconian race, but it was actually chiefly \Tiamat's project.
(The \dragons of later days did not like to remember \Tiamat because of \hr{Tiamat mutates}{the monster she later became}.)





\subsubsection{\Dragons lose much in the transition}
The \dragons gained much wisdom, power and pleasure when they became \dragons. 
But they also lost much of their sanity, humanity, gentleness and the calm, rational philosophical disposition that \hr{Ophidian philosophy}{had been their trademark}. 

In a sense it was a fall from grace. 
But only very few \dragons saw it this way. 
\Iurzmacul and \Nexagglachel were pretty much the only ones. 
Only much later would \Ishnaruchaefir come to share their views.





\subsubsection{Later someone discovers it}
Later in the series, I should have a story arc where someone discovers the truth of \Sethicus-tachi and their research. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  \prikker a fantastic and somewhat 
  horrifying dream in which I traversed a great black cyclopean cityscape,
  its towering stygian walls inscribed with some form of outlandish glyphs which
  seemed to writhe squamously and alter their shape even as I gazed at them.
  \\
  A sibilant whispering which seemed at once familiar and yet intrusively alien
  compelled me to walk to the edge of a particularly sinister looking edifice
  and peer out over its precipitous perimeter. 
  \\
  When I did so, I beheld this
  world of ours, recognizing vaguely the apparent shapes of the five continents,
  yet the entire vista seemed so distant that the whole appeared in its entirety
  no larger than a sphere which I could fit snugly into the palm of my hand.
  \\
  When I turned again to behold the looming obelisks, I found I could then
  easily read the previously untranslatable ciphers in the black stone. 
  \\
  They
  were the words of a great thaumaturgist who had seemingly discovered a
  repository of aeons-old lore detailing the sidereal web of the cosmos, with
  arcane diagrams pinpointing certain astral portals and places of empyreal
  potency, a sort of pangalactic ley-line chart, if you will. 
  \\
  Indeed, these
  Star-Maps of the Ancient Cosmographers seemed to take a not insignificant 
  toll on the author's sanity, as evidenced by the tone of his inscriptions, which
  seem to suggest that in discovering this Pandora's Box of dark elucidation,
  his fate was to be inexorably dogged by some nameless and implacable gloom
}









\subsection{Some see the \xss{} as evil}
Some \ophidians{} see the \xss{} as a terrible evil that must not be allowed into the world. 

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\prikker 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}












\subsection{War against the Gods Beneath}
Perhaps the \hs{Gods Beneath} awoke and attacked the \ophidians at this point. 
This was just when \Sethicus and his cohorts were achieving enlightenment. 
\Sethicus and his \dragons rose up and defeated the Gods Beneath.









\subsection{Rebellion}
\Sethicus and his \dragons rebelled against the other \ophidians. 

The war song of the \dragons: 
They revelled in their power and fury, their ability to cause destruction and fear.

\citebandsong{Nile:RamsesBringerofWar}{Nile}{
  Ramses Bringer of War
}{
  Wretched Fallen one of Khatti\\
  Rise against the oppressing Sword\\
  Encircled Abandoned Alone\\
  I Smite the vile Hittite Foe

  My Father Amon what carest Thee\\
  For the Vile and Ignorant of God\\
  My Father Amon what carest Thee\\
  For these Effeminate ones\\
  At millions of whom I groweth not Pale

  Raging like Menthu like Baal in his Hour\\
  Lo the mighty Sekhmet is with Me\\
  I enter in among them even as a hawk striketh\\
  I slay I hew to pieces and cast to the ground\\
  The royal snake upon my brow\\
  Spits forth Fire in the face of mine enemies\\
  And Burneth their Limbs
}

\Tiamat and \Sethicus both saw themselves as mighty conquerors:

\citebandsong{Nile:RamsesBringerofWar}{Nile}{
  Ramses Bringer of War
}{
  My Chariot Wheels trample the Fallen\\
  Cut to pieces before my Steeds\\
  And laying in their own Blood\\
  I Crush the Skulls of the Dying\\
  And Sever the hands of the Slain\\
  I Ramses\\
  Builder of Temples\\
  Usurper of Monuments \\
  Slayer of Hittites\\
  Bringer of War
}

\target{Draecchonosh war}
Some of the other \ophidians{} were swayed by the \psp{\dragons} power and glory and joined them, while others were repelled by their brutality and evil. 

\lyricsbalsagoth{The Empyreal Lexicon}{
  Stay thy hand and thy tongue, slave of the Outer Darkness\prikker
  Surely you are not foolhardy enough to dare awaken the dire titans of Z'xulth!}

\target{Tiamat kills Hesod-Nerga}
The \firstgendragons{} waged war against their fellow \ophidians{}\prikker and the world.

\HesodNerga{}, the great \ophidian{} hero, protested against his daughter's embracing this thoroughly evil power. 
Some of the \ophidians{} tried to \quo{save} \Tiamat, believing her brainwashed and possessed by the \xzaishanns{} against her will, and sought to exorcise the \daemons. 
They were dismayed to realize that \Tiamat{} was \trope{NotBrainwashed}{Not Brainwashed}. 
She responded by slaying her \HesodNerga. 

After this defeat, many \ophidians{} went into dormancy. 
\Tiamat{} conquered \Miith{} and reigned as its queen for tens of thousands of years, and the \dragons{} reigned with her as the lords of \Miith{}. 

Later, the term \quo\dragon, derived from \quo\draecchonosh, came to be used of all \ophidians, regardless of whether they possessed \xzaishannic{} blood or not. 

\lyricsbs{Exmortem}{Berzerker Legions}{
  Frigid storms and devastating raids.\\
  They are unconquerable.\\
  Frigid seas and devastating raids.\\
  Paramageddon.
  
  Runes imprinted in our skin.\\
  Northern magic surrounds us.\\
  Asa demons showing the way.\\
  Berzerker legions on all sides.
}

\lyricsbs{Monolith Deathcult}{Doomed To Slaughter}{
  The ancient gods are back on earth. \\
  We serve the book of blood.\\
  The blood of men will drench the fields in darkness.
}





\subsubsection{Religion}
The rebellion was religious in character. 
\Sethicus and his cohorts fought for their mystic beliefs.
His opponents fought for their materialistic, atheistic beliefs and saw \Sethicus as a dangerous fanatic and madman. 

\citeauthorbook[p.80--82]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  Only the cosmic horror that comes from the worship of oozing, malevolent monsters from vast and sprawling dimensions can set man on the right path.
  The Old Ones are the road to madness, destruction, and truth.
  
  Endarkenment is the opposite of enlightenment.
  The light strives to make the illusion real. 
  In darkness, Cthulhu Cultists shall have reality naked and exposed. 
  
  \prikker
  
  Purification will begin when the Cult of Cthulhu has taken over the world.
  Those who are biologically closer to the Old Ones will fully transform into their accurate conformation.
  That which was \human shall be cleansed; the eldritch beast is resurrection from the shadow that has learned to walk in Hell.
  The demonic soul is freed!
  
  \prikker
  
  Respect the laws of your land until the apocalypse begins.
  When Cthulhu Cultists number in the thousands, the balance of power will begin to shift.
  When the stars align, our bilious green and slimy inquisition shall be unleashed. 
  Death to all who oppose us!
}





\subsubsection{\Sethicus's ambition}
\Sethicus had \hr{Sethicus plan}{a mad plan}.









\subsection{\Nexagglachel and his brothers}
\Nexagglachel and his brothers were alive at this time. 
Their parents\dash weakened after having produced three powerful sons\dash perished in the last great war. 
The three sons were powerful and accomplished adults by the time Valcan and \Tyarith made their discoveries. 

\Raemyth (later \Nexagglachel) was now a lord. 
He was a warlord with dreams of kingship and conquest. 

Quessanth (later \Iscrafel) fought for his brother as a champion.
He was a martial artist and warrior-mage who hungered for glory and recognition. 

Irocas (later \Secherdamon) was a gentle artist and composer. 
He desired only be allowed to produce and perfect his art for its own sake. 













