\section{\Sethicus reigns}
\Sethicus became the spiritual leader of the \ophidian empire and also amased vast secular power. 
He appeared obsessed with science and religion and would often seem to neglect and ignore the welfare of his people (not only mortals but also \ophidians and \dragons) for the sake of his mystical ambitions. 
This was actually because of his \hr{Sethicus plan}{plan to save his race from False Life}. 
His intentions were good, but his means were brutal, and he was not good at explaining his reasons. 
The wiser he became and the further his epic plan progressed, the more inhuman and alien and incomprehensible his mind became to his fellows, and the more he became estranged from them. 









\subsection{\Nom and \Baltherium}
At \Achamoth's encouragement, \Sethicus conquered the land of \Nom. 
At the time \Nom was one of the last bastions of the \moonthings on \Miith (after the \ophidians \hr{Ophidians drive out Shugul}{had driven them out}). 
With their newfound sorcerous power \Sethicus and his companions defeated the \moonthings and their monstrous allies (such as the Weavers) and conquered \Nom. 

He then proceeded to build the gigantic fortress-city of \hr{Baltherium}{\Baltherium}, built upon ancient \moonthing ruins and drawing upon the \dweomers of captive \moongods. 
(Read about \Baltherium and \Nom.)









\subsection{\Dragon wars}
\target{Dragon wars under Sethicus}
Even in \Sethicus's time there were great and bloody wars fought between factions of \dragons.

Some of these conflicts sprung from ideological or religious differences. 
One would think that \Sethicus ought to know the \quo{correct} religion, but he did little to stop these conflicts. 
In fact, he almost seemed to be encouraging them. 
This helped make \Sethicus unpopular. 
People became convinced that he was insane.
% This eventually led to the \hs{Durance}. 

For millennia these wars raged. 
They caused serious damage to the planet.
They tore open dimensional wounds through which monstrous powers could seep in. 
\Miith became bathed in the evil \xs energies that the \dragons unleashed. 
These evil energies caused living creatures to mutate, spawning hideous monsters. 
Some of these monsters would found races that would continue to plague the \wylde tens of thousands of years later.

The \wylde spread uncontrollably.















\section[Tyrasshana]{\Tiamat}









\subsection[Tyrasshana as a Dark Messiah]{\Tiamat{} as a Dark Messiah}
\Tiamat{} is a \trope{DarkMessiah}{Dark Messiah} kind of character. 
She wanted to bring enlightenment to her people. 
But the awful knowledge she discovered (including the \hr{Umaja}{Umaja Tablets}) twisted her and alienated her from her people, so that she might easily appear insane and evil. 

In her life, \Tiamat saw again and again the cruelty that the \caisith were capable of.
Even though theirs was a highly enlightened society with great ideals of progress and freedom for all, their world always had a dark underside, and everywhere (in all strata of society) there were those who were willing to commit horrid atrocities in the name of questionable ideals or simple personal gain. 

\Tiamat also \hr{Tiamat get Ramarxes records}{studied Ramarxes' diaries} along with historical records. 
She became convinced that Ramarxes, with his Concord project, was really on the path to fixing the \caisith society and saving their race. 

\Tiamat studied the social sciences and the causality of history (psychohistory). 
She saw that the more people were isolated from one another, the more they treated each other with cruelty. 
\ta{%
  Where there is separation, there is conflict and suffering. 
  To have peace and happiness we must have unity.%
}

She came to disagree with Valcan. 
In her years spent with Valcan as her mentor, \Tiamat would sometimes probe to see if Valcan shared any of her Ramarxian ideas. 
Valcan rejected most of Ramarxes' philosophy. 
He believed that \caisith civilization was moving in the right direction and that the system, for its flaws, was overwhelmingly a positive thing that must be preserved against subversive/revolutionary menaces. 
\Tiamat argued that he thought that way because\dash for all his virtues\dash he was part of that system and therefor part of the problem.
He was a noble and unwilling to acknowledge the fundamental and pervasive \emph{wrongness} of his social class and the social order that made their lifestyle possible. 

This disagreement drove a wedge between \Tiamat and Valcan. 
\Tiamat concluded that she could not truly trust Valcan and that his conception of right and wrong was different from hers. 
From her point of view, Valcan was still governed by the causality of psychohistory, isolation and group loyalty. 
She, on the other hand, had experienced what it was like to be a slave, as well as a leader. 
She was wiser.
The ruling class hated and feared anything that was potentially more powerful than them and hence a threat to them. 
(Compare to how humans in real life fear artificial intelligence.) 
The aristocracy turned against Ramarxes.
\Tiamat predicted that the aristocracy would turn against her as well when she tried to pursue her ideals. 
\Tiamat saw the aristocracy's protests against her as something understandable and predictable but \emph{wrong}. 
As she saw it, they fought her out of causality, and she would have to destroy them out of necessity. 

She would finish what Ramarxes started. 
She would create the \hs{New Concord}. 
She would destroy the old system and all its horrors. 
She would bring unity.
She would bring a better world. 
This new world would be worth \emph{any price}. 





\subsubsection{Cult}
\Tiamat began to preach cryptic apocalyptic mysticism. 
Some dismissed her teachings as nonsense. 
No one understood what she meant, but it was evocative and seductive.
It rang true because it was based on truth.
Many joined her.
Some of her followers read the Umaja Tablets. 
(Some completely lost their minds from reading the tablets.)

Compare to Horus from \emph{Warhammer 40,000}.

\Tiamat became a Lucifer-like figure and founded a powerful and destructive cult, like Morathi's Slaanesh-cult in \emph{Warhammer}. 
\Tiamat's cult became so powerful and so destructive that other \dragons had to wage war against them and destroy them.





\subsubsection{\Tiamat{} hears voices in her head}
Perhaps \Tiamat{} hears voices in her head, voices who are actually various figments of her mind and imagination. 
They question her principles and tempt her into perversity. 

Compare to the scenes in \authorbook{Graham McNeill}{False Gods} where Horus, in dreams, meets a phantom masquerading as his companion Sejanus. 





\subsubsection{\Tiamat{} worships the \xss}
\lyricsdimmuborgir{Relinquishment of Spirit and Flesh}{
  King of tempests and storms!\\
  Lord of innumerable figures and forms!\\
  Blessed with thy cold I am,\\
  as I upon the shoulders of mine\\
  bear the burden of Thine.
  
  Once I got touched by a fire from beyond,\\
  an invitation to darkness of which I could not resist.\\
  Caressed by the feathers of the fallen,\\
  I took the fate in my hand.
  
  Revealing Thy powers in visions and dreams.\\
  Invoking your magic at night.\\
  Honoured I am to mission Thy word.\\
  Within a creed is sworn of majestic might.\\
  An infernal allegiance in which I pay my share.\\
  An unholy awakening inside of which I intend to bear.
  
  Possesses by the true god of Earth I am.\\
  Possessed for eternity.
}

She becomes evil. 

\lyricsdimmuborgir{The Serpentine Offering}{
  My descent is the story of everyman.\\
  I am hatred, darkness and despair.
  
  Evoked and entertained through centuries.\\
  Wrathful and sullen. Dormant still.
  
  The ferocity pervades everywhere,\\
  waiting to be released at last.\\
  Hear my offering, ye bastard sons and daughters.\\
  Share my sacrifice.\\
  Share my sacrifice.
}

\lyricsdimmuborgir{For the World to Dictate our Death}{
  Let us sit by and watch \\
  Death and destruction's devotees revel. \\
  Let us sit back and witness \\
  innocent semen being poured\prikker
  
  Into the arms of Armageddon. \\
  Let it pour, more and more. \\
  Pure fucking Armageddon. \\
  Let it pour, more and more.
}

\lyricsbs{Marduk}{Legion}{
  A new era will arise \\
  as I see the black angels of the abyss fly\\
  and the demons come storming in the silent cloudless sky\\
  with their burning eyes of ripping evil.
  
  I am given strength from a thousand sinners that dwell \\
  in the everlasting, burning, roaring depths of Hell. \\
  With the demons the possess my blackened heart and soul\\
  I shall strive for Satan's triumph and reach infernal goals.
  
  Children of darkness, raise your blood-filled cups \\
  to our father with horns.\\
  In eternity, we shall blaspheme the one \\
  who was tormented with thorns. 
  
  Feel the darkness growing when we draw near.\\
  My name is legion, for we are many in here.
  
  Heaven shall burn accompaigned by the angels' cries.\\
  We shall invert paradise.\\
  Death to peace!
}

She preaches to her followers of a \daemonic{} paradise. 

\lyricsdimmuborgir{Allehelgens D\o{}d i Helveds Rike}{
  Utspente vinger over M\o{}rkets dype svelg.\\
  Satt til verden for \aa{} meske seg med pest og d\o{}d.\\
  Fr\aa{}tsende i synd og hor.\\
  Overmakten fra p\o{}lens bastarder\\
  n\ae{}rer behag i syndens hierarki.\\
  Et evig liv i Paradis\\
  er fullkommenhet i Satans dynasti.
}

She seduces them to follow her. 

\lyricsdimmuborgir{Cataclysm Children}{
  Are you born from the abyss,\\
  and have you sought the creed \\
  that drape the shadows\\
  of your own thought?
  
  Is your heart mesmerized \\
  by the fire that burns forevermore?\\
  And do the secrets from the flames \\
  hold the mysteries over which you preside?
}

They have become forever corrupted by the \xss:

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Sola Fide
}{
  Verily I say unto you, \\
  there is none righteous enough to resist, no, not one\prikker\\
  For your hands are defiled with blood, and your fingers with iniquity;\\
  Your lips have spoken lies, your tongue has muttered perversity.\\
  The heart of a lost angel is in the earth, \\
  the immaculate is abased\prikker forevermore.
  
  Sola Fide. Sola Deo Infernali Gloria.
  
  Neither stormful convulsions \\
  nor an apex of light shall break the yoke\\
  For he that keepeth His commandments \\
  dwelleth in him, and He in him.\\
  And hereby we know that He abideth in us, \\
  by the Spirit which He hath given us
}





\subsubsection{Some \dragons become bitter}
Some \dragons, after tying themselves to the \xss, become bitter and evil. 

\lyricsdimmuborgir{For All Tid}{
  Hver en t\aa{}re er frosset.\\
  V\aa{}r sjel er lenket.\\
  V\aa{}rt hat er blodig.
  
  All glede er svunnet.\\
  All latter er forstummet.\\
  Alt liv skal ende i d\o{}d.
  
  I et kalt og \o{}de landskap\\
  skal den sorte horde tre frem.\\
  V\aa{}r herre skal stige opp for all tid, \\
  reise sitt rike igjen.
  
  N\aa{} er tiden kommet.\\
  Ja, knus de godes ord.\\
  La oss for alltid bli herskere \\
  p\aa{} denne jord.
}









\subsection[Tyrasshana's civil war]{\Tiamat's civil war}
\Tiamat turned against her fellow \dragons and wanted to seize power for herself.
This resulted in a vast civil war between the \dragons, for \Tiamat was charismatic and turned many \dragons to her side.
Of all the devastating \dragon wars this was the worst. 






\subsubsection{\Tiamat mutates}
\target{Tiamat mutates}
\Tiamat changed her physical body into a horrible monster. 
An almost amorphous mass of flesh and black slime, with several hideous heads. 





\subsubsection{Infrastructure}
\Tiamat build up a great infrastructure of \nexuses, \vertices and focus points for the \draconic civilization.
When she was defeated, this infrastructure remained. 





\subsubsection{\Sethicus defeats her}
\target{Sethicus versus Tiamat}
At this time, \Sethicus had secluded himself in his sanctum in \hr{Baltherium}{\Baltherium} and explored the spiritual universe in a deep meditation that lasted years. 
So we was absent during most of \Tiamat's rebellion and civil war. 

Eventually \Sethicus awoke from his meditation. 
He saw her as having gone mad and out of control, so he opposed her.
\Sethicus took leadership of the forces arrayed against \Tiamat. 

Ultimately \Sethicus defeated \Tiamat, but he himself was destroyed in the process.

\target{Tiamat imprisoned}
Everyone now believed that \Tiamat was destroyed, but in reality she was only banished. 
\Sethicus could not destroy her. 
She lived on as a shadow, now embittered and hateful. 
\Sethicus imprisoned her essence in a nightmare dimension, impaled and left rotate for all eternity while contemplating the stars and the universe.
Compare her to the god Yibb-Tstll from the Cthulhu Mythos. 









\subsection{\Sethicus is defeated}
\target{Sethicus betrayed}
Eventually, his fellow \ophidians, unable to understand his actions, decided that \Sethicus had gone mad and rebelled against him. 
Even \dragons joined the rebellion, including many of the younger ones. 
The ones that stayed loyal were mostly older ones. 

The rebels might include \Iurzmacul, \Nexagglachel and perhaps even \Ishnaruchaefir. 

After a long, violent insurrection, \Sethicus was defeated.
But his \dragons were immortal.
Far more so than the natural \ophidians.

The \ophidians lacked the sorcery to destroy them. 
Or if they knew how, they refused to use it on principial grounds because it was destructive sorcery and would corrupt their people and lead them on a sliding slope towards the \xs, which would be the end of their enlightened civilization.

\target{Sethicus imprisoned}
So they imprisoned \Sethicus-tachi instead.
They were interred in vast tombs and bound with fearsome spells and seals to prevent them from rising and claiming their revenge.
There they lay for thousands or millions of years.
\Nexagglachel was \hr{Nithdornazsh was Nexagglachel's tomb}{entombed in \Nithdornazsh}. 
Sometimes attended by living or undead monstrous servants (like the ones in \Nithdornazsh).

\target{Durance}
\index{Durance}
The imprisonment and entombment of the \dragons was also called the \quo{Durance of \Sethicus}, occasionally the \quo{Durance of the \Dragons}.

Later the \dragons \hr{Sethicus and his Dragons resurrected}{would be brought back and freed}. 





\subsubsection{Some \dragons disagreed with \Sethicus}
Not all \dragons agreed with \Sethicus's aggressive, warlike manner and his plans of conquest. 
\Nexagglachel was one of his critics.
\Nexagglachel was always calm and benevolent and thought of the future of the people (\ophidians as well as lesser races), whereas \Sethicus was mostly focused on his own greatness. 

When \Sethicus and \Tiamat were defeated and entombed, many of the remaining \dragons, convinced by \Nexagglachel, willingly stepped down and let themselves be entombed.
There they could lie and think and explore. 
(Many of the \dragons were scientists and philosophers who had been attracted by \Sethicus's free thinking.)

They felt sure that their time would come again, some day in the future. 









\subsection{\Ophidians adopted \Sethican technology}
\Sethicus built magical machines based on the secrets and energies of dark gods. 

\target{Ophidian technology set back after Sethicus}
The \ophidians began to base their technology on \Sethicus's sorcery. 
Then, when \Sethicus fell and went into Durance, their technology began to fail, because only the \dragons had the occult knowledge and raw power to keep everything working. 

The \ophidians tried to revert to their older forms of technology, but they found that the many ecological and arcane disasters of the last period had made this impossible. 
They were screwed. 
This set back their technology by millennia, and it took them forever to recover. 

\target{Ophidians worship machines}
Some of \Sethicus's machines still worked.
The \ophidians were now very dependent on these relics, since their old infrastructure was destroyed. 
But no one remained alive who understood how they functioned.
The machines came to be worshipped as objects of religion.

A \hr{Incursion hurts Ophidian technology}{similar setback} struck the \ophidians after the \Resphan \hs{Incursion} when the \resphain \hr{Resphain destroy world tree}{destroyed their world tree}. 





\subsubsection{\Nithvezurun and the living cities}
The \hr{Ophidians worship machines}{mysterious machines which the \ophidians now worshipped} included the living cities. 
Some of these cities became invested with \ophidian souls and became sentient. 
A living city could absorb/merge with several \ophidian souls and thus become super-intelligent and super-powerful.

After the loss of \Sethicus the cities began to grow chaotically and out of control.
They mutated into twisted nightmare jungles of flesh and metal, life and death. 

One upon a time there was a city named \Nithvezurun. 
Its machine-network merged with an \ophidian mind and became intelligent. 
Over time more and more \ophidians merged with their city's mind, and \Nithvezurun grew in power. 
\Nithvezurun was fairly peaceful and innocent, but it grew so powerful that other \ophidians feared it, so they banded together and waged war against \Nithvezurun and destroyed it. 

After this war the \ophidians made a taboo against creating thinking machines or hiveminds.
The \ophidians were xenophobic and feared to place power in non-\ophidian hands.
Any powerful thing must be controlled by an \ophidian mind.





\subsubsection{Everything slow again}
\Sethicus's time was \hr{Sethicus brought innovation}{characterized by very fast development}. 
After \Sethicus's fall, \ophidian progress once again slowed to a crawl. 
The colonies were either abandoned or became sleepy, unambitious things. 





\subsubsection{\Ophidians could not contain the \wylde}
\target{Ophidians cannot contain the Wylde}
In the \hr{Dragon wars under Sethicus}{bloody \dragon wars in \Sethicus' time}, the \wylde had grown out of control.
Now, with the loss of the \dragons' power and sorcery, the remaining \ophidians were unable to contain the \wylde.
They lost control of most of the planet and retreated behind the walls of their cities.

\Miith became a world of islands.
It never recovered again.
Never again would it become an enlightened world of civilization. 

See also the section about \hr{History of the Wylde}{the history of the \wylde}.









\subsection{Some \ophidians followed \Sethicus}
\target{Ophidians follow Sethicus under Durance}
After \Sethicus's Durance had begun, some \ophidians chose to follow his teachings and carry on his dark religion in secret. 
Later they would \hr{Cultists want to free Sethicus}{advocate freeing \Sethicus}. 

Other \Sethican cultists joined their \draconian masters in Durance, either voluntarily or forcibly. 
They later \hr{Undead Ophidians}{returned as undead mummies}. 




\subsubsection{\Sethican writings survive}
After \Sethicus was forced into \hs{Durance}, some \hr{Sethican writings}{writings containing the original words and theories of \Sethicus} regarding \hr{Sethican philosophy}{his philosophy} survived. 
These were treated as sacred by the surviving \Sethican cultists. 















\section{War against \Shuggon}
\target{Shuggon}
\index{\Shuggon}
The \ophidians still had their interstellar civilization. 
Eventually they discovered the world of \Shuggon. 
(This was probably after \Sethicus was laid in durance, but it might also have been before.)

\Shuggon was not a planet \emph{per se}. 
It was a cloud of planet-fragments and great air-filled caverns and swirling spaces and vortices. 
It was inhabited by a race of gigantic moth-like beings, comparable to the monsters Battra from \cite{Movie:GodzillaVsMothra} and Megaguirus from \cite{Movie:GodzillaVsMegaguirus}. 
The \ophidians waged a long war against these monsters.
The \ophidians lost and were eventually forced to retreat from \Shuggon. 
But passageways had been opened. 
In later ages, the spawn of the moth-things from \Shuggon would sometimes return to plague \Miith. 

The name \quo{\Shuggon} is taken from \cite{HPLovecraft:TheBlackTomeofAlsophocus}. 














\section{The \FirstBanewar (\yds{First Banewar begins})}









\subsection{The \bane{} invasion}
\target{Banes come to Miith}
\target{First Banewar}
\target{FBW}
\target{Banes come to Miith in spaceships}
\index{\firstbanewar}
The \banes \hr{Banes are created}{had been created on the world of \Erebos}.

And so it came to be that a \baneking{} (whom the \dragons{} would later came to call the \quo{\Voidbringer}) succeeded in opening a great dimensional portal from \Erebos{} to \Miith{}. 
Through it he sent forth millions of his \bane{} warriors to conquer and claim the new world in his name. 

The \banes{} came to \Miith{} flying in vast spaceships. They \hr{Why the Banes want Miith}{had their reasons for wanting \Miith}. 
They had flown all the way from \Erebos{}, a journey of hundreds or thousands of years. 

The people of \Miith{} were taken unaware when, on the Eve of the Black Gate, a massive rent opened in the sky and myriads of fiendish \bane{} warriors surged forth to conquer and destroy. 
Millions of \bane{} warriors and beasts, and hundreds of \banelords, all led by Daggerrain himself, invaded and attacked the \draconic{} kingdoms. 
Many millions perished in the initial assault and whole continents were laid waste before the \ophidians{} were able to muster their forces in defense. 
The Eve of the Black Gate marked the beginning of the \Banewar, the most terrible and devastating war that \Miith{} has seen since the \Kraken{} Queen last returned to her sleep. 

The \banes{} fought against the \ophidians{} in what became known as the \firstbanewar. 
They invaded with millions of \bane{} warriors and terrible magic. 





\subsubsection{\Noggyaleth remain neutral}
\target{Noggyaleth remain passive in the FBW}
The \noggyaleth had remained passive in the \firstbanewar. 
They were not highly intelligent. 
It took a long time for the \banes to get through to the \noggyaleth and form some kind of alliance. 
Until then, the \noggyaleth stayed hidden. 

Besides, the \noggyaleth were not stupid.
\Banes and \ophidians were bombarding the surface of the planet.
The \noggyaleth had a sense of self-preservation and did not want to expose themselves to that inferno.
Especially after \hr{Noggyaleth lose a war before the FBW}{having recently lost a major war}. 






\subsubsection{Technology at the time}
\target{FBW technology}
\index{technology!\bane}
When the \banes invaded, the \ophidians had an interstellar civilization.
They commanded dozens of planets. 
The \banes \hr{Interstellar Bane empire}{likewise had an interstellar empire}. 
But \Miith was the important planet that they had been searching for all along. 
It contained a Heart full of \voyager-tampered energy, and the \noggyal \hs{mother-mass}, which was the \quo{other half} that the \banes wanted. 

The war lasted centuries. 
At last the \ophidians were overwhelmed by the \bane hordes, so they retreated to their homeworld and barricaded it with the \CrystalSphere. 
The \banes conquered all their other planets. 

Both sides used weapons of \hr{Weapons of mass destruction}{mass destruction made with black magic}. 
And \hr{Living machines}{biological machine monsters}. 

The \ophidians had higher technology than the \banes. 








\subsection{\Sethicus resurrected}
\target{Sethicus and his Dragons resurrected}
The \ophidians realized they were not winning this war.
If they wanted to win, would need the help of \Sethicus and his \dragons, \hr{Sethicus imprisoned}{whom they had previously imprisoned}. 

\hr{Sethicus}{\Sethicus} was controversial because he used \xs-based sorcery (\hr{Ophidians and XS}{which the \ophidian{} establishment frowned upon}), but now the other \ophidians{} realized they would need every weapon at their disposal to defeat the \bane{} invaders. 
So after much negotation (first amongst themselves, then with \Sethicus), the \ophidians released the \dragons. 

The imprisonment and entombment of the \dragons was also called the \quo{\hs{Durance} of \Sethicus}, occasionally the \quo{Durance of the \Dragons}.




\subsubsection{\Sethicus made them resurrect him}
Maybe it was \Sethicus himself who made the first move. 

\Sethicus lay entombed, but not unconscious.
He realized the \banes were invading.
So he reached out telepathically and touched the minds of \ophidians.
He was deeply buried and bound with fearsome spells, so it was not easy for him.
He could only send unclear visions and messages.
But his mental power was formidable, and he was able to compel the \ophidians to release him.
This would have been impossible at any other time, but now they knew they needed him and his \dragons, so it was easy to convince many powerful \ophidians to come and release his seals.





\subsubsection{Cultists want to free \Sethicus}
\target{Cultists want to free Sethicus}
There were some \hr{Ophidians follow Sethicus under Durance}{\ophidian cultists who had carried on \Sethicus's religion}. 
It was they who argued that \Sethicus should be freed. 





\subsubsection{Resurrection caused problems}
\Sethicus then went to work releasing his fellow \dragons.
It took a lot of magic to resurrect them, for their souls had been away for a million years and were no longer accustomed to living in a physical body.

They awakened many, but not all.
Some slumbered too deeply and could not be reached.
Others refused the call.

Some of the \dragons had wandered the Realms of the \xss. 
Others had simply lain there thinking, developing new philosophy and science and magic.
Some of the resurrected \dragons did not want to be resurrected and went mad.
Their minds had become twisted into inhuman, \xs-like monsters.

\citebandsong{Nile:Ithyphallic}{Nile}{
  The Essential Salts
}{
  It is a great shock to the soul\\
  To tear it back from its resting place and reanimate it\\
  The resurrected are often insane and scream ceaselessly \\
  or dash themselves into walls
}

When \Sethicus came to awaken the \dragons, he also found that many had chosen to leave their bodies behind permanently and could not be resurrected.
Others had perished for various reasons.
Some refused \Sethicus's call and remained asleep. 
These would remain \hr{Aloof Dragons}{aloof} for a long time. 





\subsubsection{\Sethicus lets \Nexagglachel sleep}
\target{Sethicus lets Nexagglachel sleep}
There were yet other \dragons whom \Sethicus deliberately let sleep.
This included his three sons.
It is possible that \Sethicus knew there was a great risk that the \dragons who fought in this war would be destroyed. 
He wanted some \dragons to live on so they could awaken at a later date and reclaim \Miith, thus carrying on his legacy.
\Sethicus was wise and saw far.

It is known that he did some work to weaken the seals on their tombs so that the brothers would later awaken on their own.
He rigged some spells that would awaken \Nexagglachel some thousand years later.
Beside \Nexagglachel, \Sethicus also set up some other powerful \dragons (whom he sort-of trusted) to wake up. 
He wanted to be on the safe side and not rely on \Nexagglachel alone.
For all \Sethicus knew, something nasty might happen to \Nexagglachel in mean time, so he wanted a backup plan. 





\subsubsection{\Sethicus fights}
During the war, \Sethicus-tachi unleashed more \daemons{} and more \xzaishannic{} power than ever before. 
This nearly tore the planet apart, and might even have killed the Heart itself. 

Perhaps the \banes{} feared that. 
The \banes{} might be more keenly aware of the Heart of \Miith{}, since their entire quest revolves around it. 
The \ophidians, on the other hand, had dwelt on \Miith{} for millions of years, and the Heart has always been there, so they might not have paid much attention to the peril their magic posed. 

\lyricstitle{\SETolltheHounds{} p.107}{
  \prikker in the north sky something terrible was happening. 
  Lurid slashes like a rainbow gone mad, spreading in waves that devoured darkness. 
  Was it pain that strangled the very air? 
  Was it something else burgeoning to life, shattering the universe itself?
  
  \prikker he could see the city, the roofs like the gears of countless mechanisms, gears that could lock with the sky itself, with all creations. 
  Such was Kharkanas, First Born of all citites. 
  But the sky had changed. 
  The perfect machine of existence was broken\dash\emph{see the sky!}
  
  The city trembles, the roofs now ragged-edged.
  A wind had begun to howl, the voice of the multihued light-storm as it lashed out, flared with thunderous fire. 
}

Maybe move some or all of \ps{\Kserasshana} \quo{awakening} to \Sethicus. 





\subsubsection{\Dragons fight}

The war song of the \dragons: 
They revelled in their power and fury, their ability to cause destruction and fear.

\citebandsong{Nile:RamsesBringerofWar}{Nile}{
  Ramses Bringer of War
}{
  Wretched Fallen one of Khatti\\
  Rise against the oppressing Sword\\
  Encircled Abandoned Alone\\
  I Smite the vile Hittite Foe

  My Father Amon what carest Thee\\
  For the Vile and Ignorant of God\\
  My Father Amon what carest Thee\\
  For these Effeminate ones\\
  At millions of whom I groweth not Pale

  Raging like Menthu like Baal in his Hour\\
  Lo the mighty Sekhmet is with Me\\
  I enter in among them even as a hawk striketh\\
  I slay I hew to pieces and cast to the ground\\
  The royal snake upon my brow\\
  Spits forth Fire in the face of mine enemies\\
  And Burneth their Limbs
}





\subsubsection{\Cregorrs{} are created}
\target{Origin of Cregorr}
The \dragons{} were full-fledged \ophidians, altered for war. 
But the \ophidians{} also wanted servitor warriors. 
So at approximately the same time they worked to create a race of warrior servants. 
This became the \cregorrs.  









\subsection{The \CrystalSphere}
\target{Crystal Sphere}
\index{\CrystalSphere}
The \ophidians{} received help and knowledge from the \xss{}. 
Using this magic they were able to forge a mystic seal between the worlds, severing the connection to \Erebos{} and preventing the \banes{} from drawing power from their homeworld and its \dweomer. 

\Sethicus-tachi built a vast \CrystalSphere, a cosmic shell of \quo{ice} encasing all of Mith and its Heart. 
Thus they captured the \banelords, who were caught and frozen in the ice. 

The \CrystalSphere{} was a whole mini-Realm of ice in its own right. 
The \banelords{} became trapped there. 

The \CrystalSphere was based on the \hr{Palisades}{\pps{\Voyagers} Palisades}. 
The \ophidians had some limited understanding of the \voyagers' work, and they drew on it.
They built the \CrystalSphere to patch up the holes in the Palisades that the \banes had made.

With the \pps{\banes}{} leaders and power source gone, they were weak, and the remaining legions of \bane{} warriors were easily slaughtered. 

Maybe this seal works as a huge-ass cosmic \hr{Storm beacon}{storm beacon}. 

The \xs{} \hr{Naath-Kur-Ramalech}{\NaathKurRamalech} was very important in building the \CrystalSphere. 

\Daggerrain{} would later draw on the \CrystalSphere{} to weave the \hr{Shroud of Girigor}{Shroud of \Numah}. 
So \hr{Shroud and Crystal Sphere}{the Shroud is tied to the ice}. 

Compare to the devils in the manga \cite{NagaiGo:Devilman}, who are also frozen in ice. 





\subsubsection{No spaceships and no interstellar civilization}
\target{Crystal Sphere isolates Miith}
One might think that even though the \CrystalSphere{} prevented the \banelords{} from going to \Miith{} by dimensional means, they should be able to fly there in spaceships. 

But no. 
The \CrystalSphere{} also kept spaceships out. 
It acted like a huge-ass \hs{storm beacon}. 
In fact, the sorcery wrought through \NaathKurRamalech{} completely enclosed \Miith{} and made it inaccessible from the outside. 
It constricted and strangled \Miith{}. 
It was one of the causes of the \hr{Heart weakened}{weakening of the Heart}. 
The Shroud made it worse, of course. 

The \CrystalSphere also prevented the \Miithians from establishing any interstellar or interdimensional civilization.

It would be possible to attack the Sphere from the outside with magical weapons. 
But that would be very risky. 
Such an attack might easily damage or even destroy the Heart of \Miith. 
No, the Sphere had to be unravelled from the inside. 









\subsection{The fall of \Sethicus}
\target{Sethicus dies}
\Sethicus used a spell that drew upon the \matrix which united all \dragons.
His spell succeeded, and the \banes were banished from \Miith. 
But \Sethicus sacrificed himself and was destroyed. 
Many \dragons perished with him.





\subsubsection{Durance}
The remaining \dragons realized that \Sethicus's spell had weakened the Heart and that they could not live on \Miith any longer.
They chose to go into Durance until such a time as the Heart would again be able to support them. 

Those \dragons who refused to go into Durance would sicken, waste away and die over the course of the next centuries. 
Most \dragons eventually saw reason and went into Durance. 





\subsubsection{\Sethicus-tachi die}
Eventually \Sethicus fell, but his corpse was preserved.

\Sethicus fell and was seemingly destroyed in the \firstbanewar.
He overloaded his body with power and could not resurrect.
He was believed lost.
Out of respect for his heroism, they took his body and enshrined it in \hr{Baltherium}{\Baltherium}, where it was \hr{Elder Dragons worshipped}{worshipped as a dead god}. 

But \hr{Sethicus became a god}{\Sethicus's soul lived on as a disembodied god}.

















