\bookchapter{A Dark Angel's Gift}
\stamp
  {\dateAchsahAndNeedle}
  {Slave quarters, \CastlePelidor, \hs{Malcur}}



\begin{comment}
\section{Needle makes herself pretty} 
\end{comment}

\ps{\Piacet}{} eyes watered as she brushed her lashes in front of the mirror. 
The sap of the pettic tree, which she used to colour her eyes, had an unpleasant odour, but perfumes would soon drown that out. 

Her make-up routine was \ps{\Piacet}{} favourite part of the day. 
Needle loved being pretty. 
She knew she was not exceptionally beautiful, nor had she been when she was in her prime. 
But she did her best. 
Being able to turn men's heads was a pleasant side effect, but the most important thing was that it made her feel a little bit like the young, innocent girl she had once been, many years ago. 
It brought her a measure of inner peace and confidence. 

She needed that. 
She still longed for her childhood. 
She had been a free person back then, however poor. 
But when her mother and father sickened and died, they left the family indebted, and \Piacet{} and her sister Belya were taken and sold into slavery to pay it off. 
They had ended up in a brothel. 

It had been Charcoal who had rescued her from the brothel. 
He pulled some strings to have her sold to the palace, and at the same time introduced her into the Cabal. 

Charcoal had been irrestible back then, fifteen years ago. 
Full of power. 
Full of wealth. 
Full of charm. 
Full of mystery. 
And younger and slimmer, too. 
She had been his willing lover, then, and loving it. 
That had not lasted. 
Gradually his interest had waned, and their relationship grown more distant. 

Among her mentors had also been Charcoal's fellow \ishrah{} mage Borg Zelab. 
Needle, whose family had been servants for as long as any could remember, was uneducated, but \Mr{} Zelab had taught her to read and the basics of magic, before his death of old age two years ago. 
He was terribly old\dash he must have been a hundred years old, she thought\dash and, for a powerful Cabalist mage, strangely timid. 
During her lessons, she could clearly see in his gaze that he lusted after her, but never once had he made advances to her. 
\tho{Probably couldn't get it up and standing,} she had assumed. 



% But those golden days did not last. 
% Gradually, Charcoal's interest waned, and he came to care only for her body. 
% He no longer bothered to arouse and seduce her. 
% Sex with him became a chore rather than a pleasure. 
% \Piacet{} began to resent her Cabal master. 
% 
% \tho{%
%   Just you wait, Charcoal.  
%   I'm advancing faster than you. 
%   One day I'll outrank you. 
%   Then I'll no longer answer to you.
%   Neither in the Cabal nor in bed.} 



\begin{comment}
\section{\Achsah{} appears} 
\end{comment}

Suddenly, Needle froze. 

A shudder went through her, as if a cold draught filled the room. 
There was a low sound, like bubbling or seething. 
And a smell, of dust and howling winds and desolate expanses. 

A tear in the Shroud. 

A surfacing. 

Needle turned to see an unnatural shadow filling a corner of the room. 
And the shadow was not merely dark. 
It was \emph{deep}. 
Through it she could peer into an endless space, a veiled, mystic, unknowable world hinted at in the murkiness. 

And from that twilight rent, a figure emerged. 
%A figure so beautiful it made her eyes hurt. 

The figure wore an elaborate dress: wide skirts black and dotted with silvery pinpricks that gleamed like stars in the night sky; 
bodice striped in white and black like a tiger; 
long sleeves gray and sparkling silver; 
shoulders bare, along with the top of the chest and some cleavage. 

\tho{A \hr{Resvil}{\resvil}!} 

Even though the newcomer was not winged like the greatest of her race, she was still a \resvil, and Needle knew that only the deepest, humblest submission would be suffered. 

She flung herself to the floor, face prostrate against the planks. 
\ta{My lady \resvil.} 
A shiver of excitement ran down her spine. 
\tho{A \resvil{} is in my room. 
     A goddess is gracing me with her presence.}

The \resvil{} hovered near the humble chair for a few heartbeats. 
Needle imagined she felt distaste emanating from the divine being. 
Then the dark angel dismissed the thing and chose instead the softer bed. 
Slowly she sat, taking her time arranging her skirts. 

\ta{Needle.} 
Her voice was silken soft, replete with all the grace of a goddess, and tinted with a slight hint of... \tho{playfulness?}

\ta{Yes, my lady \resvil?} Needle replied, her nose still pressed against the floorboards. 

\ta{Look at me.} 

Needle raised her head, but kept her knees, hands and elbows on her floor. 
The \resvil{} sat with crossed legs staring down upon her. 
For the first time she got a proper look at the visitor's face: 
gray rather than black, but still uneathly beautiful, with a slim, pointed chin and large, slanted eyes that shone silvery white. 
Her lips were dark but glittering, like a night sky full of stars. 
In her raven-black hair she had small flowers made of a bluish-silvery metal, and a pure gold necklace, the only vividly coloured part of her attire, adorned her neck and breast. 

\tho{Truly a goddess.} 

Needle had only rarely been so blessed to gaze upon the \resphain{} in the flesh, but this one she had seen before, and she could not imagine that she might ever forget the face of such a superhuman being. 

\tho{\hr{Achsah}{\Achsah}. Of the \achsahcircle{} circle.}

She trembled with emotion. 
Awe. 
Terror. 
Love. 
She almost averted her eyes, but the goddess had commanded that she look, and she dared not disobey.  
So she lay there, prostrated in worship. 

\tho{%
  This is whom I serve. 
  Not surly old men like Charcoal. 
  Not \humans{}.
  Gods. 
  Superior and beautiful.} 
It made her forget all her worries. 
\tho{%
  Who could ask for more than to be allowed to serve these magnificent gods?}



\begin{comment}
\section{\Achsah{} gives orders} 
\end{comment}

\ta{Sit up,} the goddess commanded. 

Needle lifted her torso from the ground, but kept her hands on the floor. \tho{Mustn't get ahead of myself.} 

\ta{You are in command of Malcur in Charcoal's absence, hm?}

\ta{Y-y-yes, my lady \resvil.}

\ta{%
  No need to shake, girl. 
  I am not here to molest you.} 
\Achsah{} put up a slight frown as she ran her eyes up and down Needle's kneeling form. 

It was all Needle could do not to crumble under that scrutiny. 
She imagined \Achsah{} pointing out her every flaw. 
\hypota{Ugly, imperfect mortal.
  Fingers too bony. 
  Breasts too pointed. 
  Nose and chin too long and narrow. 
  Hair too stringy.}

Needle wanted to curl up and hide herself. 
\tho{Forgive me, great goddess. 
  Forgive me my imperfections. 
  
  Next to you I am nothing. 
  I know that.}

Then \Achsah{} smiled. 
It was a slight smile, but warm. 

\tho{She smiles! 
  She is satisfied with me. 
  She loves me, unworthy as I am.
  My goddess loves me!}
The thought filled Needle's body with warmth. 
\tho{%
  What a wonderful smile.
  So beautiful. 
  So divine.}
She found that she loved \Achsah{} more with every moment. 
\tho{The \resphain{} are the only ones who truly love me.
  And I love them. 
  That is why I serve them.}

\ta{%
  Now listen,} said \Achsah. 
\ta{%
  I have noticed intensified Sentinel activity lately. 
  Moreover, I have detected \hr{Psyrex}{\ps{\LocarPsyrex}} presence. 
  Physically. 
  In the city.} 

\tho{\LocarPsyrex}. 
The lord of the \hs{Dark Crescent}. 
A terrible Sentinel sorcerer; a \scatha{}, but said to have \hr{Daemon}{\daemonic} blood in his veins. 
So powerful that even the godlike \resphain{} were wary of him. 

\ta{Here? Now, my lady \resvil?}

\ta{%
  No. Only a few brief moments. 
  But enough to be cause for concern. 
  I believe that Charcoal may have underestimated the danger, 
  and thus left you ill equipped to deal with it.
  As such, you will need... this.} 
\Achsah{} produced a scroll from somewhere in her wide skirts. 
\ta{%
  This scroll details an \hs{orison} that will let you contact me and, if necessary, summon aid from \hr{Nyx}{\Nyx}.} 

\ta{Aid, my lady \resvil?}

\ta{\hr{Bane}{\Banes}.} 

\tho{\Banes.} 
Needle openly shuddered at the thought, unable to help herself. 
\Banes{} were horrors from the Realm of Darkness. 
She had seen them only a few times, and every time they had filled her with dread and loathing. 
She remembered one occasion where Charcoal had summoned a \bane{} to their aid in combat. 
It had killed with ruthless efficiency and an utter inhuman coldness. \tho{Awful to behold.} 

\ta{My lady \resvil... you will place me in charge of these \banes?} 

\ta{Yes.} The goddess smiled with cold amusement. 
\ta{Unless you are not up to the task...?} 

\ta{Oh, no, my lady \resvil. I am up to it.} 
She did not want to show cowardice or ineptitude in front of \Achsah. 
She wanted nothing more than to please the her, to make the \resvil{} proud of her. 
Besides, \Achsah{} was Charcoal's superior. 
If Needle wanted to advance and rise above him, it was \Achsah{} she needed to impress.
\ta{I thank you, my lady \resvil, for entrusting me with this honour.} 
She bowed low, face to the floor. 

\ta{%
  Good. 
  Redouble your efforts to find the Sentinels' lair.
  Do not fail us.} 

\ta{By your command, my lady \resvil.} 
She bowed again.  
\tho{I will not fail.
  I must not. 
  \Achsah{} loves me. 
  I must earn that love.}



\begin{comment}
\section{\Achsah{} leaves} 
\end{comment}

The \resvil{} rose, invoking a \hr{Qliphah}{\qliphah} that Needle did not recognize. 
The corner of the room shimmered, again somehow cast in unnatural shadows. 
Peering into that twilight, Needle could perceive glimpses of another world: 
Immense towers, causeways, bridges and decaying ruins. 
And \Achsah{} passed through the darkness and into that hidden world. 

Rarely gifted with a view of mystic \Nyx, the world of the \resphain, Needle stared after her. 
The dark angel took to the air from a dusty gangbridge, floating free in the dark emptiness upheld by unseen \qliphoth, soaring off into the distance until she faded from view. 

Needle, still on her hands and knees, crept closer to that edge and dared to peek down into the deeps. 
A vast, lightless abyss stretched off into infinity before her, the massive spires going on forever until they vanished in the pitch blackness beneath. 

So endless and consuming was that void, it made her mentally recoil from the sight. 
Abruptly the vision vanished, blocked out by her subconscious mind. 
The Shroud snapped back into place. 
Now only the gray stones and moldy wooden boards greeted her. 

Needle was again alone in her room, in the world. 

Even so, she remained on the floor for the next long while, digesting all she had seen and heard. 

\tho{%
  A marvelous angel. \Achsah. 
  
  An evil sorcerer. \Psyrex.
  
  A neverending twilight. \Nyx.
  
  An ancient horror. The \banes. 
  
  Now under my command...}





