\bookchapter{Captured}
\begin{comment}
\section{Rian and Neina}
\end{comment}
\stamp
  {\dateNeinaCaptured}
  {An alley in the Workers' Quarter, Malcur}

% Rian used to be a thief, but at some point in his teens he helped a carpenter and his family. 
% As thanks, the carpenter took Rian in as an apprentice, to help him get out of a life of crime and into a decent, honourable career.
% 
% Now Rian has a girlfriend, namely Neina the baker’s daughter. 
% They are engaged to be married in a year or so, but Rian is a horny youth and can hardly wait. 
% 
% We meet them an evening when he has managed to catch her alone outside for some reason. 
% Her parents have noticed them together, but because they are nice guys they choose to allow it, for a moment, at least. 
% They are kissing in a corner, and Rian moves in under her blouse to grope her breasts, but she stops him. 
% He relents and kisses her goodnight, and they part ways.
% She walks to her house, but she is intercepted by a thug working for the Sentinels. 
% He knocks her out and kidnaps her, intending to use her as a sacrifice for the \Nithdornazsh{} ritual.
% 
Neina pulled back from the kiss. 
\ta{We shouldn't be doing this.}

\ta{You're right. We shouldn't,} Rian conceded with a mischievous smile. 
%She returned the smile, and he saw that he was on the right track.  
As soon as he saw her return the smile, he pulled her back in and kissed her again. 

\tho{No resistance. All riiight...} 

He put his hand on her stomach, deftly slipped it under her blouse (utilizing all the nimbleness of a former pickpocket), then let the hand slowly creep upwards while caressing her belly. 
She seemed to be enjoying his tongue in her mouth, too. 

\tho{Let's see how far I can push it...} 

He crept further up with his hand and let it cup her breast. 

That made Neina pull away again and push his hand down. 

\tho{Crap. That was one step too far.}

\ta{I should get home. Before someone sees us,} she said. 

\ta{You're right.} 
He squeezed her hand, then released it. 
\ta{Go on.}

She turned and walked out of the alley. 
At the end she turned her head to smile briefly back at him, then vanished around the corner and made towards her home. 

\tho{Didn't get any further today. 
Oh, well. 
I'll get there.}

Rian waited in the alley a while, so as not to be seen together with her. 
\tho{Not that it matters. 
Neina's parents aren't that dull-witted. 
I think they have a good idea of what's going on.} 

But they chose to allow it. 
Rod Baker and his wife were good-hearted people. 
The fact that they had been willing to betrothe their daughter to Rian, whom they knew had once been a thief, was enough testament to that. 
They has been skeptical at first, but \Bryon{} Carpenter, Rian's master, was a friend of their family and had spoken well for him. 

Rian owed much to the carpenter and his wife. 
Having no son and heir, the old man had taken the boy in as an apprentice and convinced him to give up thieving for an honest life as a carpenter. 
And in these last eight months since then, his life had been so much better. 

% It had been a long string of events, all beginning that day last summer when he had seen the strange black-scaled sorcerer in the dead garden. 
% Rian still struggled to remember what exactly had happened there, but for some reason he felt as if the experience had somehow changed him, set him on a new path. 
% 
% \tho{I feel like I somehow owe you for all this, \Mr{} Sorcerer.} 
% 
% But no need to brood on that. 
He had an apprenticeship and a girlfriend. 
When they were married, they could do all the naughty things he dreamed of, and which he suspected she dreamed of as well. 
Preferably sooner than that, if he had his way. 

His future looked bright. 

\tho{Life is good.}







\begin{comment}
\section{Thug watching}
\end{comment}
\new
% A thug sits on a rooftop and surveys the streets, looking for prey. 
% He sees Neina: A girl of maybe sixteen or seventeen, plump, brunette, and wearing the yellow shawl signifying a betrothed but unmarried virgin. 
% "Sure, why not?" 
% He crawls down towards her. 
From his hiding place on a flat rooftop, the thug scanned the dark and narrow street. 

\tho{Can't seem to find anything good tonight... ooo! 
What have we here?}

He spotted a young \human{} girl coming out of an alley. 
She was maybe sixteen or seventeen, plump, brunette, and wearing the yellow shawl signifying a betrothed but unmarried virgin. 

\tho{Well, hello there. 
What's a lass like you doing out alone so late?} 

Inwardly chuckling to himself, the thug snuck to the edge of the roof, found a patch of shadow and silently dropped down. 

\tho{Come to daddy...}







\begin{comment}
\section{Neina captured}
\end{comment}
\new
Rian was a good boy, Neina reflected. 
But she was not about to let him have his way with her just yet. 
That would not do. 
She was not a slut, after all. 
Their kissing before had already been too wild for propriety. 
That should not have happened. 
But he had been so sweet and naughty and insistent. 
She had really had no choice in the matter. 
It had just... happened. 
Thinking of it made her smile. 

\tho{Finish your apprenticeship soon, Rian. 
  Then we can marry. 
  Then we can... teehee... you know.} 

She looked up at the sky. 
It was dark. 
The Sun had set some time ago. 

\tho{I've got to hurry home. 
  Mustn't make them worried...}

% Then she is grabbed by a thug, clubbed dizzy, gagged, bound and dragged into an alley. 

A scaly hand clamped over her mouth. 

\ta{Mmmmph!}

From behind her, the owner of the hand pulled her into a tight embrace and whispered into her ear: 
\ta{Be a good and quiet girl.} 
In his other hand, the \dax{} brandished a knife. 
\ta{Wouldn't want anyone to get hurt.} 

\ta{Mmmmm...} Her squeal sounded pitiful to her own ears. 

% The knife pressed into her throat, drawing blood. 
% \ta{I said shut up!} 
The \dax{} pressed her head hard against his shoulder and punched her hard in the stomach with the pommel of the knife. 
\ta{I said shut up!} 
He waved the knife in front of her face. 
\ta{I can kill you any moment I like.}

Terrified, Neina obeyed. 

\tho{Please don't rape me! 

  He's a \scatha. 
  
  \Scathae{} don't rape humans...
  
  Do they? 
  
  Please don't rape me!}

\ta{Haha. You'll do nicely,} the thug mumbled as he dragged her into an alley. 

\tho{What is he going to do to me?

  Help me. 
  
  Rian... Father... Mother... someone. 
  
  Save me.
  
  I'm scared.} 







\begin{comment}
\section{Rian and Rod Baker}
\end{comment}
\new
\placestamp{The Carpenters' home, Malcur}
% The next day, Rod Baker (Neina's big and burly father) barges into the carpenters' home and wants to beat the shit out of Rian. 
% He demands that Rian give back Neina, and accuses him of rape, abduction and all sorts of evil, threatening to hand him over to the guards. 
% Rian is like: "WTF? I didn't abduct her anywhere!"
% Rod:  "Then where is she, damn you!?"
% Rian: "What do you mean 'where is she'? Isn't she at home?" 
% Rod:  "NO! She's been gone ever since you fooled around with her last night! I never should have let you get near her!" 
% Rian: "You mean... Neina's gone?" 
% Rod:  "Yes! Neina is gone! WHERE IS SHE?"
% Rian: "Itzach! We've got to go find her!" 
% Rod:  "Where do you think you're going?" 
% Rian: "Off to look for Neina!" 
Rian, lying in his bed, was stirred half-awake by the crash of a door flung open. 

\ta{There you are!} a gruff voice shouted. 

Still groggy, Rian registered a fat hand grasping him by the neck. 

\ta{Where is she? What have you done with her, damn you?} 
The hand was shaking him violently. 

Gradually he came to his senses. 
\ta{\Mister{} Baker?} 

\ta{Spit it out!} Rod Baker commanded. 
\ta{Where is Neina?} 

Rian blinked. 
It was still dark outside. 
\ta{What?} 

A fist connected with his jaw, sending him tumbling from his bed onto the floor. 
Neina's father was a bull of a man, and he packed a strong punch. 

\ta{Don't play dumb with me, you lowlife! 
  You've abducted my daughter! 
  Where have you taken her?} 

\ta{What? 
  I didn't take her anywhere!} 

The fat baker picked him up by the scruff of his neck and began shaking him again. 
\ta{Stop lying to me!}

A sleepy \Bryon{} Carpenter came into the room now and tried to soothe the furious baker. 
Rod shoved him aside. 

Rod pulled Rian close so that his big, brown beard scratched Rian's face. 
\ta{I know you were with her last night! 
  Now where is she?} 

Rian still understood nothing. 
\ta{What do you mean\dash ow!\dash what do you mean \quo{where is she}? 
  Isn't she at home?} 

\ta{No! 
  This is all your fault, you filth! 
  I never should have let you near her. 
  Once a crook, always a crook. 
  I should have known!} 

\ta{You mean... Neina's gone?} 

\ta{\shout{Yes}, damn you! 
  I swear, if I find out you've touched my daughter's virtue I'm going to...} 

\ta{\Itzach!} 
At last the import of the situation dawned on Rian. 
He jumped to his feet. 
\ta{We've got to go find her!} 

\ta{What do you mean \quo{go find her}? 
  Just tell me where she is!} 

Rian shrugged free of his grip. 
\ta{\Mister{} Baker, this is important! 
If Neina has been kidnapped, then we need to go look for her.}
Now it was Rian's turn to grab the baker. 
\ta{Where did you last see her?} 

Rod Baker was dumbfounded for a moment. 
\ta{Uh... last night. In the alley. With \shout{you}!} 

\ta{Oh, no. 
  There are all sorts of people out there. 
  Robbers and rapists and worse...} 

Becoming aware of the edge of genuine panic in Rian's voice, the baker seemed to finally understand. 
\ta{You... you don't know where she is?} 

\ta{No! That's what I've been trying to tell you!} 

\ta{Then... what?} 

\ta{She must have been kidnapped by bandits!} 
Rian was running around in his room, dressing and gathering up his gear. 
\ta{We've got to go find her!} 

\ta{Uh... yes...} 
The burly baker stood confused and disappointed as his anger slowly fizzled out. 

\ta{I'm off!} said Rian, already running out into the street, leaving the baker sizzling behind. 
\ta{I'll find her! I promise!} 

\tho{Neina. 
  Where are you? 
  
  I shouldn't have dragged you out in the alleys at night. 
  I shouldn't have left you alone. 
  It's my fault. 
  
  No! Mustn't dwell on that. Must focus on finding her. 
  
  I'll save you, Neina.}








