\bookchapter{\ps{\Teshrial} Farm}





Make sure to make the atmosphere in this chapter as dark as possible. 
Teshrial-tachi drink human blood from chalices, and eat Human and Scatha flesh. 
They have huge, deformed ogre servants and monsters. 
And there is dark sorcery all over the place. 









\begin{comment}
\subsection{Flying}
\end{comment}

Teshrial flies to Ruishagh, his estate. 
He flies above forests, meadows and fields. 
Through Realms. 
He has come from Nyx into a Shrouded Realm. 

Much of the way he has flown over \Wylde{}, but now he is nearing Ruishagh and there are signs of civilization. 
He sees human workers below, on foot or in carts. 
He flies above them. 

Many mortals, he reflects, dislike walking on their own and prefer to ride on beasts or in carriages. 
Walking - relying on your own body - is seen as plebeian. 
Teshrial could not disagree more. 
There exist flying monsters he could be riding on instead, but he would not dream of doing that even if it were practical. 
He loves flying. 
His wings are proof that he is a pureblood Resphan, and he revels in it. 
Feeling the wing beneath his wings reminds him of this and fills him with joy and confidence. 

\tho{Maybe mortals would appreciate walking more if only nobles had legs.

  Brr. 
  What a grotesque and repulsive idea. 
  Legless \humans{} crawling around.
  Poor things.}

Ruishagh is now in sight. 
He swoops down towards the landing balcony. 










\begin{comment}
\subsection{Blessing}
\end{comment}
\new
Teshrial is at Ruishagh. 
He has been welcomed by the top staff. 
Now he goes around inspecting the humans. 
They all come out and peek, happy to get a chance to see their god - maybe even touch him. 
He touches several of them and gives them his blessing. 
He loves his humans. 

\tho{%
  Most \resphain{} don't understand \humans.
  To them, a \human{} is just an automaton that serves their needs.
  They do not understand all the care and hard work that does into breeding them. 
  
  \Humans{} must be bred with love.}

And \Teshrial{} loves his \humans. 
And it is not just slave \humans{} he is breeding, oh no. 
Top quality \humans{}, for the {Communion}. 
He breeds them for beauty, health, obedience and good taste. 

There are new children that have been born since he was last here. 
He inspects the newborn and gives them his blessing. 
He touches them with the tips of his wings to bless them, caressing them with his soft feathers. 

He looks at a young girl of around 15. 
Touches her. 
She giggles and squirms when he tickles her with his feathers. 
But she is brave enough to meet his gaze. 

\ta{%
  Look at you. 
  How fine you are. 
  How perfect. 
  As beautiful as a \resvil.}

\ta{Almost ripe for the Communion. 
  Very soon, my beautiful one. Very soon.}

But he thinks to himself: 
\tho{%
  Sigh.
  If only it \emph{were} a \resphan{} child.}
There are very few \resphain{} being born these days. 
\Teshrial{} has barely ever seen a \resphan{} child. 
He has only heard stories of the golden age ({before the Shroud}) when his people were numerous and fertile. 
It has something to do with the Shroud, he knows. 
He does not understand the details of \dweomer{} theory. 
It has not been his specialty. 

\tho{%
  What I would not give {to have a son or daughter of my own}. 
  Not a \bezed. 
  Not a surrogate.
  A pureblood.}






\begin{comment}
\subsection{Punishment}
\end{comment}
\new
There are two young \humans{} who have broken the rules. 
They have become lovers and had sex, and the girl has gotten pregnant. 
This is a crime, because they should only breed as they are ordered. 
It is a sin, for a \ps{\human} flesh and sex is a sacred thing (\resphan{} property) not to be thus profaned. 
They must be punished. 

\Teshrial: 
\ta{%
  Know this: 
  You have caused me great sorrow. 
  Your womb and your seed are sacred treasures, but you have violated and defiled yourselves by your act of fornication.
  I would that this sin could be forgiven and washed awau, for I grieve to see my beloved children punished. 
  But some sins cannot be washed away. 
  You must die, and your flesh shall feed the beasts, for you have been tainted and can no longer achieve the blessing of the Communion.}









