\bookchapter{For War and for Glory}
\stamp
  {\dateTheArmySetsOut}
  {Malcur city gates}
%
%
%
\begin{comment}
\section{\Sethgal}
\end{comment}
\ta{\prikker and I need not tell you,} bellowed \rah[Sethgal] Pelidor, 
\ta{that this affront shall not go unanswered! Pelidor will not suffer the depredations of Runger!}  

Marshal \Sethgal was resplendent in his silver-and-bronze-shining breastplate, billowing azure cape and rainbow-plumed helmet, and with his lance raised high aloft, from which waved the banner of House Pelidor: 
A \grulcan{}-bird in bronze against an azure sky. 
He stood high above the ground in the howdah of a massive and wicked-looking \muroc; a great, horned, four-legged \saurian.
Behind him, as if following in his footsteps, were arrayed the colossal statues of Malcur's legendary heroes; ten or twenty times life-sized and with swords, maces and spears raised high in salute. 

\ta{Warriors of Pelidor! 
  We march forth this day, and soon King Morgan shall cower at the sound of our footsteps! Hail, proud warriors of Pelidor!}

\ta{\emph{Hail!}} the army replied as one. 

\ta{For the \rayuth and the \rinyuth!}

\ta{\emph{For the \rayuth and the \rinyuth!}} the army echoed. 

\ta{For the One Light!}

\ta{\emph{For the One Light!}}

\ta{For Pelidor!}

\ta{\emph{For Pelidor!}}

\ta{We march! For war and for glory!} 

The Marshal waved a cue, and drummers and trumpeters thundered their rhythms and fanfares. 
The \Malcuric{} city gates, so wide that thirty men could march through them abreast, slowly swung open.
And the army marched; thousands of \scathae and \humans arrayed in neat rows, helms and weapons glinting in the morning sun. 
There were cavalry and knights mounted on \relcs, swift-running green \saurians. 
There were \murocs, twice as tall as a \relc and perhaps ten times as massive; their heads and flanks beset with great blades and their backs outfitted with howdahs carrying a whole squad of archers and lancers. 
And there were \grulcans: great birds with bloodlust in their eyes; up to thrice as tall as a \scatha, plumed in brown and orange like bronze; flightless, but powerful runners, with beaks and talons as long and sharp as swords. 
This was Sethgal's natural element, and he took delight in this display of martial power. 

He allowed himself to slump forward in his seat into a natural \scathaese resting position. 
The coming long march would be the closest thing to rest that he had had in a long time. 
His last many days had been filled with hectic work. 
Soon after \Icor's murder, Archibald Curwen had presented tentative evidence suggesting that the assassin and the traitor \Onatol had been in the pay of King Morgan of the neighbouring kingdom of Runger.
And by amazing coincidence, not many days later news had come from eastern Pelidor that Morgan Runger had crossed the border with what sounded like a full-scale invasion force. 

\thought{That devious rat, Runger.}
Sethgal had met the \human King Morgan once or twice in his life and found him to be a vile character: 
Vicious, dis\honourable and greedy, like so many \humans. 
It would be very like him to order the assassination of a rival monarch. 

Pelidor, being an elective monarchy, had been thrown into a complicated interregnum with several factions within the ruling House vying for the throne. 
Even in the face of a potentially catastrophic war, the small step of electing a Marshal\dash a temporary supreme commander of the armies\dash had seemed an insurmountable task. 
It had taken days of hard negotiations, shady deals and bullying, but eventually Sethgal's faction had managed to gather enough support, and Sethgal was now Marshal. 

His words\dash\emph{for war and for glory}\dash were no lie.
The coming war meant everything for Sethgal's career. 
If fortune \favoured him, he might ascend the \rayuth's throne on his return.
If not, he might have to fight to the death to ensure that there would still be a Pelidor for anyone to rule. 

\thought{I hope we have enough.}
With him he had around six thousand troops, and they would be joined by at least three thousand more before they reached the battlefield. 
But it might not be enough. 
Runger was a larger kingdom than Pelidor, and Morgan Runger had obviously planned this war for some time, so it stood to reason he would send as many men as he possibly could. 
House Pelidor had sent word to all its major allies, including the mighty Imetrium, and asked for aid, but so far they had received no answer. 

The Rungeran invasion had come only shortly after the Rissitic hordes had landed in \Scyrum, south of Pelidor. 
This might be a coincidence, but Sethgal feared the worst. 
He suspected that the coming conflict was a thing greater than Pelidor and Runger, driven by greater forces than the greed of a petty \human king. 

\thought{We will need the help of our allies.

  I hope the Imetrians will come.}





\begin{garbage}
\begin{comment}
\section{Carzain marvels}
\end{comment}

Carzain marvelled at the splendour of it all. The \Malcuric{} city gates, so wide that thirty men could and did march through them abreast. The heroic statues, ten times life-sized if not twenty; swords, maces and spears raised high in salute. The army itself: thousands of \scathae{} and \humans{} arrayed in neat rows, helms and weapons glinting in the morning sun; an awesome display of martial power. 

According to Captain Curwen, the army was just over six thousand strong and would be joined by almost another two thousand before reaching the front. 

The core of the army were the mighty Tigers, the professional elite warriors. They wore gray and white fur cloaks bearing the white tiger, symbol of the ancient king Uther who had founded the order. 

Of the six thousand warriors, fifteen hundred were cavalry. 
In addition to the \relcs, the were also gray elephants, twice as tall as a \relc{} and five times as massive at the very least; their heads and flanks beset with great blades and their backs outfitted with howdahs carrying a whole squad of archers and lancers. 
And there were \grulcans: great birds with bloodlust in their eyes; up to twice as tall as a man, plumed in brown and orange like bronze; flightless, but powerful runners, with beaks and talons as long as swords, and looking just as sharp. 

Speaking of swords, Carzain was not entirely happy about the broadsword that now hung at his side. He had requested a sabre\dash as wielded by the Vaimon heroes of old\dash but Captain Curwen had advised against it. 

\ta{The sabres we have here are shit,} Curwen had said 
\ta{A sabre is a good weapon, but \emph{only} if made with superior craftmanship. 
  \emph{Vaimon} craftmanship. 
  The ones we have here are hackwork. 
  They'll break at the drop of a hat. 
  You're better off with a sturdy broadsword.} 
The great man had slapped him on the back and laughed. 
\ta{Hah! Who knows, \Shireyo? 
  Maybe you'll gut a Rungeran mage and capture his sabre as a trophy, eh?} 

\tho{I will have to be sure to do that.} 

And the young Vaimon could not complain about the rest of the \ishrah{} uniform with which he had been outfitted: 
A light metal breastplate, chain mail reaching down to his knees and elbows, and studded leather for the rest. 
A handsomely crafted skullcap protecting as much of his valuable head as could be afforded without obscuring his vision, which, as a mage, he would need. 
%and sprouting a single yellow feather to signal his special status. 
His chest as well as the front of the helm were emblazoned with the \grulcan{} of House Pelidor. Yellow epaulets covered his shoulders, and a single yellow feather sprouted from the helm, signalling his \ishrah{} status. 

% As it turned out, the entire \ishrah{} and their escort rode \relcs. 
% Curwen had explained that one avoided mixing horses and \relcs{} in the same unit, unless for a good reason. 
% The entire \ishrah{} and their escort were mounted on \relcs. 
% Carzain had kept the dark one he had been issued in \Redglen, Arrow. 
On the ride from \Redglen{} they had had to ride two or three soldiers on a single \relc. 
Now, as a full-fledged \ishrah{} member he had been issued his own personal \relc, as had every one of the mages and their escort. 
His was a dark green male named Arrow; large and strong, but rather mean-tempered. 
At least, so it seemed to Carzain, who was by no means an expert rider. 

He had asked the captain why the mages rode \relcs{} and not the faster \mikshas. 
Curwen had explained that \relcs{} were more reliable. 
\Mikshas{}\dash fast-running bipedal \saurians\dash were skittish and difficult to handle. 
Only a very skilled rider could keep a \miksha{} steady on a battlefield. 

And Carzain had to admit that he was having enough trouble with Arrow already. 
Riding the beast was a struggle. 
And to top it all off, it was prone to biting. 
It had snapped at him more than once, and while he had so far managed to escape any serious bite wounds, his hands did bear some scratches. 
\tho{But hey, I've got my own \relc. And that's not bad.} 

He looked out over the army again. 
Saw the thousands of helms and spearpoints, the mighty formations of men. 
Saw the banners billowing in the wind. 
There was the \grulcan{} of House Pelidor. 
There were three parallel black spears against an orange background, the symbol of House Turmalin. 
And there were the standards of many other Pelidorian nobles: 
A black boar; 
a bow with three arrows notched; 
a crescent moon encircled by four pterans. 

\vizicar{%
  And they all follow me. 
  The Emperor.} 

Carzain blinked. 

\tho{%
  What?
  Did I think that?
  
  It's that \quo{Emperor} thing again\prikker}

Moreover, there had been a feeling that Carzain could not quite shake off. 
It had only been for a moment, but it brought back unpleasant memories. 
Of the night in \hs{Heropond} a year ago, when he lost control of himself. 

\tho{%
  Oh, crap. 
  Not again. 
  I thought I was over that. 
  What did I do this time? 
  I was nowhere near a \qliphah! 
  Get out of my mind, damned voice!
  
  What is happening to me? 
  And what does this \quo{Emperor} mean? 
  
  Am I going mad?}

\begin{comment}
\section{Delph and \Tsekkect}
\end{comment}

\ta{They say he's the best,} said the \meccaran{} soldier to Carzain's right, jarring him out of his navel-gazing. 
\ta{Marshal Sethgal, I mean. 
    One of the finest commanders in all \PelidorContinent.}

\ta{He certainly looks the part, doesn't he?} 
Carzain replied, admiring again the hero leading them. 

\ta{He's of House Pelidor, you know. 
    A cousin of the fallen \rayuth. 
    Who knows, maybe they'll make him \rayuth after we win this war.} 

The \meccaran{} was a female, green-skinned, four-and-a-half feet tall. 
She eyed the Vaimon. 
Then her frog-like face burst open in a wide, toothy grin. 
\ta{So, don't be a stranger. What's your name?}

\ta{Carzain \Shireyo. Newly joined the \ishrah.}

\ta{Ooo, mage, huh? Yeah, goes with the uniform.} 
    The short \meccaran{} was mumbling while holding and gnawing a piece of ham. 
\ta{So you're one of those fancy-asses me and the boys will be bodyguarding?} 
Choice of words notwithstanding, her ham-stained smile was still welcoming. 

\ta{Fancy-ass. That's me,} Carzain agreed. 
\ta{But now you're being a stranger yourself. Who are you?}

\ta{Oh, right. Where are my manners?} 
She took the ham in her left and extended a greasy hand with webbed fingers. 
\ta{I'm \Tsekkect{}. How are you doing?}

\ta{\Tsekkect{}.} Carzain shook the hand. 
Then wiped it off on his trousers. 
\tho{Manners. Huh. If you say so.} 
%\ta{\Tsekkect{}\prikker what kind of strange name is that?}
\ta{\Tsekkect{}\prikker is that some weird \meccaran{} language?}

\ta{Yeah. \Thbatswa{}.} 

\ta{Say what? \quo{Spatspa}?} 

\ta{\Thbatswa{}.}

% \Tsekkect{} threw up her hands. 
% \ta{Why does everyone say that? 
% \Tsekkect{} is a perfectly normal \Tepharin{} name.}
% 
% % \tho{\Tepharin. Yeah, he kind of looks it.} 
% % \Tsekkect{}, who appeared to be of Carzain's age, was short, five foot and a half at most. His blonde hair was cut short, if irregularly, and his stubble of beard was the same colour. 
% \ta{\Tepharin? I didn't know there were \Tepharin{} \meccara.} 
% 
% \ta{There aren't. I just have a \Tepharin{} name, all right?}
% 
% The \human{} soldier on \ps{\Tsekkect}{} other side butted in. 
% %\ta{Hey, buddy. You got a problem with \Tepharites?} 
% \ta{Yeah, \Tepharin{} people are the best, too.} 
% 
% Carzain raised an eyebrow. \ta{Really?} 
% 
% \ta{You bet. Just look at me. Prime example.} 

The \human{} soldier on \ps{\Tsekkect}{} other side laughed out loud. 
\ta{%
  Give it up, buddy. 
  You'll never learn to pronounce it. 
  I've tried many times and never gotten close.}

% Carzain looked. 
The man, who appeared to be of Carzain's age, was not much taller than the \meccaran, five foot and a half at most. 
His blonde hair was cut short, if irregularly, and his stubble of beard was the same colour. 
\ta{Hi. I'm \Delph{}.} 

\ta{\Delph?} 
Carzain turned the name over in his mouth. 
\ta{Sounds \Tepharin.}

\ta{%
  Damn right. 
  \Tepharin{} is great.}
Delph smiled. 
His teeth, Carzain saw, were stained black from chewing tobacco. 

\ta{It is?}

\ta{%
  \Qliphoth, yes. 
  Much better language than \Velcadian.}

\ta{%
  Really? 
  All right, say something in \Tepharin.}

\ta{%
  I'm not your trained monkey. 
  I don't do tricks on command.}

\ta{%
  Hahaha. 
  Playing hard to get, are we?}

\ta{%
  Always. 
  Well, granted, I might give you an easier time if you had bigger jugs.}

Carzain lowered his voice, conspiratorily. 
\ta{You mean like Archibald Curwen?}

\Delph{} and \Tsekkect{} both laughed, \Tsekkect{} almost spewing a mouthful of ham. 
\ta{Oh, \sephiroth,} chuckled \Delph{}. 
\ta{Yes, like that, except on a slim chick's body.} 

\ta{So anyway, you new to the army?} \Tsekkect{} asked. 

\ta{Yes, just enlisted this \Razilah.}

\ta{Razi\prikker yeah, whatever,} \Tsekkect{} mumbled. 
The uneducated folk seldom used the formal names of the months, if they knew them at all. 
\ta{%
  I joined the army a year and a half ago. 
  I fought for House Turmalin against some raiders from Beirod in the south, and river pirates near Besuld. 
  Kicked their asses.} 
She flashed another ham-stained grin. 
\ta{%
  Then I got hit and took a nasty wound in my arm. 
  Infected, too. 
  And the surgeon was like: 
  \subta{%
    Oh, well, you're a \meccaran, so we'll just lop off the arm, shall we?}
  And I was like: \subta{What!?}
  And they were like: \subta{CHOP!}}
To illustrate, she used her free right hand to chop at her left arm above the elbow. 
\ta{%
  And I was like: \subta{Ow}!
  And they were like: \subta{Off you go!}}
She spat. 
\ta{My good left arm, too.} 
Carzain remembered that most \meccara{} were left-handed. 
\ta{%
  Had to spend half a year as a useless cripple, waiting for it to grow back. 
  And that wasn't easy, let me tell you! 
  You got any idea how hard it is to be a crippled \meccaran? 
  Huh? 
  You \humans{} and \scathae{} have it easy. 
  Lose an arm and all of a sudden everyone's like: 
  \subta{%
    Aw, poor you. 
    I feel so sorry for you. 
    Here's some free money.}
  Try that as a \meccaran{} and they're like: 
  \subta{%
    Piss off! 
    Go regrow that arm and get back to work!}} 

\ta{So you did?} 

\ta{So I did. And now I'm back in action.} 
She flexed her new left arm to demonstrate. 

\ta{So, I can rely on you guys and girls to guard my back?}

\ta{%
  Any time, bro. 
  In some weeks' time we'll be kicking Rungeran ass by the assload.} 

\Delph{} took the word as \Tsekkect{} paused to tear off another chunk of ham. 
\ta{%
  You'll like it here in the army, \Shireyo. 
  Glory, fighting, plenty of food, and pussy. 
  Well, at least for us guys with dicks. 
  Don't know about you, \Tsekkect{}. 
  I don't quite understand the way your people fuck. 
  But we \humans, we get the best pussy that money can buy.} 
He laughed.
\ta{Well, the best pussy that my kind of money can buy, anyway.}

\ta{Heh.} 
Carzain pondered that for a second. 
\ta{And all they ask in return is that we fight to the death.}

\ta{%
  Details, details. 
  Food and pussy come first. 
  Then we'll see about the dying.}

And so they rode on. 
\tho{%
  For food, pussy and dying. 
  For war. 
  For glory.}







\begin{comment}
\section{\Esmerel}
\end{comment}
\new
\placestamp{Elsewhere in Pelidor}

A jolt of electric force went through \Chyrie{} \ps{\Esmerel} body. 
The talisman she carried around her neck was vibrating, almost humming with energy. 
% The talisman that she had enchanted to trace the spiking \vertex{} was emitting signals. 
She stiffened. 

\tho{The \vertex! It is back!}

The talisman was a specialized tracking device she had enchanted to trace the spiking \vertex. 
Attuned to the \vertex, it would react whenever it detected activity. 
\Esmerel{} otherwise had to go deep into meditation to detect the spikes herself, and could not possibly keep a lookout for them all hours of the day.
The talisman could not actively investigate the source of the \vertex{} activity, of course, but it could determine a very rough direction and distance. 

\Isacc{} \Chiran, her \gandierre{} companion, turned to her. 
\ta{\Matron? Is anything the matter?} 

\ta{Possibly. 
    I have caught the scent of our quarry.} 

\ta{Excellent. Do we have a heading, \matron?} asked \Chiran. 

\ta{Yes. Follow me.}
 
\end{garbage}










