\bookchapter{Trinity of Pestilences}
\stamp
  {\dateRianLooksForNeina}
  {Malcur slums}

\begin{comment}
\subsection{Nothing}
\end{comment}

% Rian has spent the last two days non-stop trekking around the city looking for traces of Neina. 
% They have reported the incident to the city guards, of course, but they simply nod and sit on their asses. 
% After all, the bakers are just ordinary people, not rich or powerful enough for the guards to care one whit about.
Nothing. 

After two straight days non-stop trekking around the city looking for traces of Neina, Rian had found nothing. 
His only noteworthy achievement so far was convincing the bakers that he was not the culprit. 

They had reported the disappearance to the city guards of course. 
\tho{But they just nod and sit on their asses. 
The bakers are just ordinary folk, after all. 
Not rich or powerful enough for the guards to care one whit about.}

% At first, Rian asked only respectably people and tried to stay in respectable areas. After having rejected his thieving life he has developed a fear of sorts of the criminal milieu, and he tries very hard to steer clear of it. 
%% This is partly because that milieu disgusts him now, 
%% and partly because he doesn't want to run into his former enemies, and perhaps worse yet, his former friends. 
% But after two fruitless days he has realized that he'll have to go into the criminal milieu. 
%% For one, it is likely that the culprit(s) will be someone connected to the gangs and thieves' guilds, and thus he stands a better chance of tracking them down if he goes here to inquire and look for clues. 
%% For two, he will be better off if he can enlist the aid of some old friends and acquaintances from the slums. 
%% For three, as much as he hates to admit it, this is an area he knows well and understands, so he is better able to sneak around and make inquiries here than in the nicer neighbourhoods. 

At first, Rian had endeavoured to stay in respectable areas of the city and inquire only with respectable people, steering clear of the slums he once called home. 
But after two days of fruitless searching he was starting to realize that he would have to venture into the criminal milieu. 
For one, he would be better off if he could enlist the aid of some old friends and acquaintances from the slums, people experienced with such things. 
For two, it was likely that whoever had kidnapped Neina would be someone connected to the gangs and thieves' guilds, and thus he would stand a better chance of tracking them down if he went into the slums to ask questions and look for clues. 
And for three, as much as Rian hated to admit it, the slums was a place he knew well and understood, having lived the first sixteen years of his life there, so he would be better able to sneak around and make inquiries here than in the nicer, more posh neighbourhoods. 

But even with all those arguments, he was still loath to go there. 
The thought of delving back to his roots filled him with revulsion. 
It might have been his home once, but now he wanted nothing more than to stay away. 

\tho{I've worked so hard to distance myself from it. 
To rise above my thieving past.} 
He preferred to think of his history as an ugly memory, nothing more. 
\tho{I have a new life now. A better life. A real life.}

% But Rod Baker's accusations of \quo{once a crook, always a crook} were a painful reminder. 
% % Somewhere inside he had a nagging fear that the baker had been right. 
% % \tho{What if I fall back? 
% % What if I...}
% He didn't want to think of himself as a crook, but maybe he was. 
He also feared whom he might run into. 
Old enemies, or, perhaps even worse, old friends. 
\emph{Former} friends. 

% So he's finally ventured into the slums. 
% It's been months since he's last been here, and the decay is horrifying.
% "Was it always this bad? It can't possibly have been. And the smell. How could I ever have endured this?" 
% And the visible ugliness is just as nauseating as the stench. Decrepitude, famine and despair lies thick like a fog, suffusing everything. The low, irregular wooden hovels look rotten and liable to collapse any moment, held together only by the swarms of cockroaches and worms. The people all seemed wretched existences. 
% Half-naked children run around. Their shrieking voices seemed to Rian somehow twisted and evil, as if they unceasingly plotted torment on other children and whatever animals they could catch. 
% "Is this my neighbourhood? Have I been away so long?"
But beating about the bush was not going to solve anything, he had to remind himself, and so he had finally resolved to venture into the slums. 



\begin{comment}
\subsection{Decrepitude}
\end{comment}

It had been many months since he had last been there. 
The decay was horrifying to behold. 

\tho{Was it always this bad? 
It can't possibly have been. 
And the smell. 
How could I ever have endured this?} 

%And while the smell might be bad, 
Bad as the smell might me, 
the visible ugliness was just as nauseating. 
Decrepitude, famine and despair lay thick like a fog, suffusing everything. 
The low, irregular wooden hovels looked rotten and liable to collapse any moment, as if held together only by the swarms of cockroaches and worms. 

The people all seemed wretched existences, disenfranchised and hopeless. 
Half-naked children ran around, 
their shrieking voices seeming to Rian somehow twisted and evil, as if they were constantly plotting torment against other children and whatever animals they could catch. 

\tho{Is this really my neighbourhood? 
Have I been away so long?} 

% And then there's the Disease. 
% The Human Plague, as some call it, since it only affects Humans. 
% By the dudes who invented it, it's called the Morbus. 
% It's been spreading these last many years, infecting more and more people each year. It is not very deadly, and an infected person can live on for decades. But it's horrible. It makes the body rot alive, degenerating into an crawling less-than-human thing. The senses suffer, too - the eyes frequently become water-filled and dead, staring into nothing. 
% But worse yet, the mind suffers. The disease brings insanity, a rapid descent into abhorrent dementia. The sufferer loses the faculties of speech and thought and becomes a crazed, bestial wretch. 
And then there was the Disease. 

It had no proper name that anyone in the slums knew. 
Some called it the \Human{} Plague, since it affected only \humans. 
But to most, the name that had caught on was simply \quo{the Disease}. 
It had been spreading these last many years, infecting more people each year. 
It was usually not deadly, and the infected often lived on for decades. 
But it was horrible. 
It made the body rot alive, made the afflicted degenerate into a crawling less-than-human thing. 
The senses suffered, too\dash the eyes became water-filled and dead, staring into nothing. 

But worst of all, the Disease caused atrophy of the mind and brought insanity.
%, a rapid descent into abhorrent dementia. 
The sufferer gradually lost the faculties of speech and thought and became a crazed, bestial wretch. 
It was gruesome to witness. 
Rian counted himself lucky that he had never lost a close friend to the Disease. 

\tho{Useless, unloved parasites,} he thought sadly. 
\tho{Unlike the nobles, who are useless but highly celebrated parasites.} 
The last part was something an old and bitter friend had used to say. 

Rian did not wholly believe that. 
He liked to think that the nobles were somehow, well, noble. 
The idea that the high classes were morally superior, that their wealth and power were somehow deserved, made it easier to accept. 
It made it all seem less unfair. 



\begin{comment}
\subsection{Dennick}
\end{comment}

% Rian seeks out Dennick, an older friend who has been sort of a father-figure to him. 
At any rate, Rian had a goal in mind. 
He needed to see Dennick. 

Dennick was the one person in the slums he trusted most. 
Throughout Rian's childhood, the fifteen years older Dennick had been a mentor, a big brother, even a father to him. 
He was a thief and a gangster, but an honest gangster. 
He was the greatest man Rian knew. 
\tho{%
  Sure, there are people in the nice neighbourhoods who are just as honest. 
  But it's easy for them. 
  They live in a nice neighbourhood. 
  Dennick has lived his life surrounded by crime and brutality, and still managed to live as a good man. 
  That makes him great.} 
Some of his former friends would resent him for turning his back on them, he well realized, but not Dennick. 
Dennick would understand. 
Dennick would always be his friend. 

He made his way through the crumbling streets and mouldering shacks, dodging the Diseased wretches lying or crawling in the streets. 
He kept glancing nervously over his shoulder and around corners, always prepared to duck out of sight if he spotted someone he didn't want to meet. 
In the nice parts of the city this sort of skittishness would instantly mark him as a suspicious character, and would likely get the city guards called down on him. 
But here, paranoia was an everyday thing. 
Here, people knew that the world really was out to get them. 

% He finds Dennick's home and is relieved to see that it looks mostly like he remembers it. 
% Or maybe he's getting used to the look of the slums. Looking around him, he notices that it all starts to look less horrible and more familiar. 
% "Am I reverting to being a slum-dweller? Iquin, I hope not." 
At last he reached Dennick's home. 
He was relived to find that it looked like he remembered it. 
He knocked on the door. 

\tho{Be in. 
Light, let him be in.} 
He knocked again. 

% He knocks. After a while, Dennick opens. 
After a while, the door opened a few inches. 
A familiar face peered out from the opening: 
A \human{} man (naturally; \human{} gangs did \emph{not} mix with \scatha{} gangs) in his early thirties, with curly dark brown hair and a short beard but no moustache. 

\ta{Rian?} 

\ta{Hello, Dennick.}

\ta{Rian! You're back!} 

\ta{Well... sort of. 
Can I come in?} 

% He is impatient to get in. 
% He doesn't want anyone to see him. 
% Dennick invites him in.
\ta{Of course.}
Dennick opened the door. 

Rian slunk in and quickly shut the door behind him. 
He didn't want to spend any more time in the streets, in full view, than he had to. 
Who knew whom he might run into? 

He looked around. 
The inside of the house was like he remembered it, too. 
A well-kept place by slum standards: 
Solid roof, few holes in the walls, no clearly visible vermin. 
On the floor stood a table and several chairs and stools, only moderately rickety. 

\ta{I hear you've gone all legitimate,} said Dennick. 

\ta{Well... yes...} 

\ta{Sit down. 
I have some decent beer.} 
He produced a bottle. 
\ta{So, what brings you here?} 



\begin{comment}
\subsection{The Black Plague}
\end{comment}

Rian summed up his story and Neina's disappearance. 

\ta{I see,} said Dennick. 
\ta{You've been struck by the Nappers.} 

\ta{Nappers?} 

\ta{Kidnappers. 
That's what we call them around here.} 

\ta{You mean you know who they are?} 

\ta{No, nobody knows who the Nappers are. 
But round these parts everybody knows they exist.} 

And Rian listened as Dennick told the tale of what turned out to be a whole chain of abduction or disappearance incidents lately. 
Dennick\dash who was well-known in these parts\dash could name at least six people before Neina who had vanished in the last year's time, and he had heard of many more. 
All the victims were children or young adults, of all races and sexes. 
Dennick was best informed about the slums, but he had heard enough to be certain that the disappearances were not confined to the poor quarters. 
Merchants, citizens and even nobles had gone missing. 

No one knew who was behind it, but rumours abounded: 
Slavers, cannibals, \daemon-worshipping cults, vampires. 
\ta{Some even talk of monsters eating people whole,} Dennick explained. 
\ta{But I've heard more than one witness describe seeing the victims being knocked out and dragged away by humanoid thugs. 
So I'm discounting that last one.
No, humanoids are behind this.} 

\ta{So... Neina is still alive?} 

\ta{I didn't say that. 
I only know that some victims have been seen knocked out and dragged away alive.} 

\ta{So she is alive! She must be!} 

Dennick paused, then smiled. 
\ta{Yes. She must be.} 
It was a blatant lie to make him feel better, but Rian appreciated it. 

\ta{So, do we have any leads?} 

\ta{Well...} Dennick looked around nervously, then leaned in. 
\ta{I know nothing definite, but there are some tenuous scraps of evidence linking them to the Black Plague.} 

\tho{Shit. Black Plague. Not good.} 
The Black Plague was one of the most powerful, and arguably one of the most evil, of the thieves' guilds in Malcur. 
All the guilds and gangs had wicked-sounding names like that. 
\tho{Not good.} 
The Plague were nasty. 
You did not want to mess with them. 

Dennick read his expression. 
\ta{Yes, I know. Not good.} 

Rian looked him in the eye. 
\ta{I'm going to save her.}

\ta{You're wh...?}
Dennick half-choked. 
Then swallowed. 
\ta{Rian. You're going to get...} 

Rian fixed him with eyes full of defiance. 
Full of determination. 

\ta{You know,} Dennick began, \ta{she's prob... 
I mean, maybe you should... 
I mean...}

Rian held his gaze. 

Dennick sighed. 
\ta{Yes, I suppose you're going to go do it.} 
He took a deep breath, sighed again. 

\ta{All right. I'll tell you all I know. 
Now, you do \emph{not} have this from me...} 









\begin{comment}
\section{Rian in the garden}
\end{comment}
\stamp{%
  \dateRianAndTheCrazyOldWoman}{%
  Dead garden, \hs{Malcur}%
}

\begin{comment}
\subsection{Navel-gazing}
\end{comment}

% Rian is thinking about how much he's accomplished. 
% He's gazing at his shoes, kicking stones, lost in his thoughts. 
% Contemplating his navel. 
Rian looked down at his shoes as he walked. 
Kicking stones around. 
Lost in his thoughts. 

\tho{%
  What have I accomplished?
  Not much. 
  I wish I were clever and resourceful, like \hs{Grith Ecallivan}, the ancient Vaimon hero.}
Ecallivan was renowned for his resourcefulness, always able to figure out how to get in, get what he wanted and get out. 
The record of Ecallivan's life was one long adventure: 
Finding rare treasures, outwitting evil warlords and sorcerers and rescuing fair maidens. 

\tho{%
  I may not be a Grith Ecallivan. 
  I'm just Rian. 
  I haven't accomplished anything. Yet. 
  But I will.}

He was heading back to the dead garden, which he had not visited for some time. 
Even though he knew it to be somehow perverse and impious, he had often felt fascinated by and drawn toward the garden. 
Sometimes it gave him peace of mind. 
It was disturbing, but also pleasant. 
Like a ghost story, but real. 

As a young boy Rian had been was one of the few kids who dared venture into the garden, and the other kids had envied him his bravery. 
Thus, the garden was a sign of pride and confidence for him. 
It brought back memories of feeling brave and capable. 
Whenever the world would stump him, when he would fail at something, he would go to the garden to regain a feeling that there were some things he \emph{could} do. 
That he was not a failure. 
He needed that. 
Especially now. 

He did not need to look up from the ground to know he had reached the garden. 
He didn't know the hovels and ruins around it by sight\dash and indeed, they seemed to inexplicably change all the time\dash but he recognized the unmistakable smell of the place. 
It smelled of many things: 
Dust, dry leaves, sour ground. 
Above all, it smelled \emph{old}. 
\tho{The garden must be the oldest part of Malcur.}
Rian did know if this was true. 
He knew little of history, apart from the colourful tales of great heroes. 
But he felt that it must be. 
Nothing could be older than this smell, this feeling. 
There was an atmosphere of some strange... \emph{force}... as if something larger than life dwelt here. 

The \hs{Iquinian Church} said that that \quo{something} was evil. 
Rian had talked to some of the monks and nuns that would sometimes go into the slums to preach the truth of the \hs{Light} and offer charity to the poor. 
He had always liked those monks and nuns. 
They were points of light in the bleak everyday in the slums. 
But it made him sad when they condemned the dead garden. 
According to them, the powers that lurked there were wicked \hr{Qliphah}{\qliphoth} that twisted and perverted men's souls. 

\tho{%
  Maybe it's true. 
  Maybe the garden is evil.
  Maybe it corrupts men. 
  
  Maybe it has corrupted me. 
  Maybe that is why I am wicked. 
  
  I have sinned. 
  As much as I try to tell myself I've changed, I'm still a sinner. 
  A thief. 
  A lowlife. 
  Wicked. 
  Criminal. 
  Sinful. 
  
  Why am I so bad?
  Is it the garden's fault?
  Has it corrupted me?
  
  I shouldn't be going here for strength. 
  The monks and priests wouldn't like that if they knew. 
  They'd say I should pray to the Light instead.
  And I do. 
  I pray every day. 
  Many times every day.
  I pray that Neina is alive. 
  I pray I'll find her. 
  I pray we'll be happy together.
  
  But the \hr{Sephirah}{\sephiroth} haven't brougth her back to me. 
  The guards and the church haven't found her, either.
  I'm afraid I'll have to find her myself.
  She's only got me. 
  I can't let her down.}

And so he had come here, hoping for some guidance, or at least a boost of confidence. 
But today his gloomy mood coloured his perception of his surroundings. 
It made the whole place look even more dark and sinister than usual. 
Oppressive, even. 
Haunted. 
The crooked trees seemed to bend as if writhing in pain. 
A deep pain of the soul. 

He saw the deep shadows behind the trees. 
The were deformed like the trees themselves. 
He looked deep into those shadows and was almost sure he saw shapes in there. 
\Qliphoth. 
The evil \qliphoth{} the monks had warned him about. 
He imagined he saw them there, crouching, hiding in the dark corners of the world. 
Skin black as coal, black as their hearts. 
Horns on their heads. 
Claws on their hands. 
Hooves on their feet. 
Long teeth in their mouths. 
Mouths contorted in evil smiles. 

There were also ghosts in the garden, he knew. 
He had seen them. 
Heard their lamentations. 
They could be dangerous, too. 
They usually only came out at night, but one could never be sure. 

\tho{Maybe coming here to cheer me up wasn't the best idea.}

But now he was here. 
He plodded aimlessly around for a while. 
Sniffing the air. 
Looking at the shadows. 
He had no real purpose in mind. 
Did not know what he was looking for. 

\begin{comment}
\subsection{The old woman}
\end{comment}

Then he noticed a voice. 
A familiar voice. 
He smiled slightly and followed it to its source. 

And there, in a clearing amid the black and gray trees, squatted a familiar figure. 
Short and bent, skin brown and splotchy. 
The crazy old \hr{Meccaran}{\meccaran}. 
\Uswa. 

She sat hunched, pawing at the dirt with her hands and crooning softly to herself in her characteristic throaty wheeze. 
\Meccaran{} voices always had a certain chattering, squeaking quality to \human{} ears, but old age and heavy drinking had given \ps{\Uswa}{} voice an added gargle that made her difficult to understand. 
She was also half-deaf and half-mad, and her tendency to mumble to herself did not help matters. 

\Uswa{} was terribly old. 
Rian did not know what she had been like in her youth. 
She was one of those people he could not imagine ever having been young. 
As long as Rian could remember, she had always been very old. 
He did not know exactly how old. 
Even though he knew \meccara{} did not live as long as \humans{} or \scathae{} did, he could not help but imagine her as being at least a hundred years old. 

These days she eked out a living as a beggar and sometime fortune-teller. 
Once in a while richer people, especially young ones, would come into the slums looking for thrills. 
They amused themselves by looking at people worse off than themselves. 
It made them appreciate their wealth more, Rian supposed. 
They would go around in their fancy clothes, accompanied by armed bodyguards, and point their fingers at the squalour and misfortune. 
No one liked them. 
But they were good business, sometimes, if one had something to offer them. 
At times the sightseers would pay old \Uswa{} a few coins to tell their fortune. 
She would give them some bleak and cryptic rant about how all things decayed and all people were blind puppets and the world was a ghastly theatre and whatnot. 
Her patrons would listen for a short while, then dismiss her chilling predictions and just laugh at her ramblings. 
They saw it all as a grotesque joke. 

Rian found her predictions more scary than funny. 
He did not know how often they actually came true, because he rarely understood exactly what was supposed to happen. 
But the tone of her foretellings always chilled him. 

But today he had to talk to her. 
She might have important clues. 
She might know something.
Might be able to point him in Neina's direction. 

He approached her. 
The smell of some cheap and foul liquor assailed him. 
\Uswa{} was quite the drunk. 
Some people said it was her horrible visions that had driven her to drinking, and that the horror combined with the booze had driven her out of her wits. 
Others said it was the ghosts. 
Listening to their wicked talk was known to bring corruption and madness. 

He sat down next to her. 
\ta{Hello, \Uswa.}

\begin{comment}
\subsection{Her prophecy}
\end{comment}
She paid him no attention. 
\ta{%
  The trees are restless,} she mumbled. 
\ta{% 
  It will happen. 
  It will happen soon. 
  Tremours underground. 
  Tremours. 
  I feel them through my feet.} 
Her long legs twitched. 
\ta{%
  They are crawling. 
  Down there. 
  In the deep.} 
A shudder went though her body. 

Rian could not help but shudder, too. 
Her rants were spooky. 

\ta{%
  Always crawling. 
  Always burrowing. 
  In the deep. 
  In the darkness, where no one can see them. 
  But I can feel them.} 
She drew patterns in the dirt with her fingers, as if tracing the movement of burrowing worms. 
\ta{%
  Slithering. 
  Gnawing. 
  Gnawing on my feet. 
  Gnawing on my body. 
  My body!}
She gripped Rian's arms and feebly shook him.
\ta{%
  My body! 
  They are eating my body!}

\tho{%
  Eating her body? 
  Is she sick, maybe?}
He could not tell if she was really sick or just hallucinating. 
But she looked distressed, so he felt he had to try to comfort her. 
\ta{%
  \Uswa, take it easy. 
  No one is eating your body. 
  There's no one here but you and me.}

\ta{%
  But they are here! 
  I know they are! 
  I can feel them,} 
she insisted weakly. 

\ta{There is no one here but us,}
he assured her. 
\ta{%
  See? It's just me, Rian. 
  You know me. 
  Right?}

\ta{Rian...} 
She put her hands on his face and felt him, apparently not trusting her eyes and ears. 
\ta{Yes. Rian...}

Poor old \Uswa{} was almost deaf, and there was also something wrong with her eyes. 
Or... as far as Rian knew she could see well enough, physically. 
But often she would stare away into nothingness, not seeing people around her. 
Not seeing the real world. 
It was as if she could turn her eyes to somehow look into other worlds that normal people could not see. 
Perhaps, he thought, it was this gift\dash or curse\dash that was the source of her uncanny knowledge. 
And her madness. 

He looked at her. 
She did not look any sicker than usual. 
Granted, she was not exactly healthy looking, but what would one expect?
She was old and drunk and mad. 
He did not think he could solve that. 
But if he could calm her down, then maybe she could help him with \emph{his} problem. 
\ta{%
  \Uswa, I need your help.}

\ta{%
  Help. 
  Yes. 
  I need help. 
  They are eating me!
  See how I bleed!
  I need help!}

\ta{%
  No, \Uswa! 
  No one is eating you!
  You're not bleeding. 
  You're fine.}
He took her hand and showed it to her. 
\ta{%
  See? No blood.}

\ta{No blood,} she repeated stupidly. 
\ta{No blood.}

\ta{%
  Yes, no blood. 
  You're fine. 
  Healthy as a... uh... frog. 
  Look, \Uswa, I need your help.}

Her eyes cleared and she seemed to return to the present. 
Rian told her his story, of how Neina had gone missing and he had run around in the city like a madman trying to find clues about her disappearance. 
\ta{%
  You sometimes see things others can't. 
  Can you help me? 
  Can you help me find her?}

\ta{%
  If they have taken her, then there is no return. 
  They come for us all. 
  We will be consumed. 
  We will be gnawed and sucked dry. 
  Already I bleed.
  The pain... the pain!}
She grabbed her right leg and held it close to her chest. 
She clutched it right, as if to keep it from bleeding. 
\ta{%
  There is no escape from the darkness. 
  The worms. 
  Can you not hear them? 
  Listen!}
She gave him a sharp, intense look. 
\ta{%
  Listen!}

He stood silently. 
Listening. 

\ta{I can't hear anything...}

\ta{%
  It's here. 
  Under us.
  Around me. 
  In me. 
  Eating me alive!
  It is in my head! 
  In my head!}
She grabbed her head and rocked back and forth.

\ta{%
  \Uswa, there's nothing eating you. 
  You're just imagining it. 
  But what about Neina? 
  Can you see her?}

\ta{%
  She is lost!
  You are lost!
  I am lost!
  There is only death. 
  Decay.} 
She took her right foot in her hand and held it out to him.
\ta{%
  Look! 
  My feet are rotting!
  The ground is rotten.
  Infested. 
  Sick. 
  The city is sick.
  There is a cancer eating away at Malcur.
  At the world!}
% \end{comment}

\begin{comment}
\subsection{Rian gives up}
\end{comment}

Rian gave up. 
He sighed loudly and stood up. 
\ta{Goodbye, \Uswa.}

He walked away. 

\tho{%
  She's having one of her bad days. 
  I'll get no sense out of her.}

Part of him felt that he should be worrying about \ps{\Uswa}{} prophecy, or whatever it was. 
But he could not take it all in, and he really could not be bothered. 

\tho{\Uswa{} being sick.} 
If she had stuck to that he might have been able to cope with it. 
He could have tried to help her, procure some medicine or find a monk or something. 

Then it became a whole city that was allegedly sick. 
He could not relate to that. 
First of all, it made no sense to him. 
How could a city be sick? 
And even if it had made sense, he could not imagine what he could do about it. 

And then it became the whole world being sick. 
That was just... no, he just could not cope with that. 
He could do nothing but dismiss it as a mad drunk's ravings. 

\tho{%
  She's talking nonsense. 
  Like so often before. 
  That's all there is to it.}

Rian held on to that thought, because it meant he could also dismiss the rest of what \Uswa{} had said. 

\tho{%
  Neina is not lost. 
  I'll get her back.}










