\bookchapter{Veils that Divide}

\begin{comment}
\section{The Funeral}
\end{comment}

Darkness. 
All was darkness. 

He knew nothing. 
Remembered nothing. 
Felt nothing. 
Then, slowly, ever so slowly, he was given senses. 
Sounds came to him. 
Colours. 
Smells. 
Feeling. 
He drifted mindlessly and watched as a world took form around him. 

There was light. 
Yellow light from above. 

\tho{The Sun?}

White light from around him. 

\tho{Walls. White walls.} 

Sounds. 
Voices. 
Words. 

\tho{Where am I?
    Who am I?}

He remembered. 

\tho{I am \Icor{} Pelidor. 
    I was dead. 
    I am dead. 
    I was given a task by the angel. 
    Sent back to the world.} 

He was now awake enough to recognize his surroundings. 

\tho{Malcur. 
    The \Iquinian{} church.
    There are people here. 
    Priests. 
    Servants. 
    Soldiers.} 
%
% One caught his eye. 
%
% \tho{There is \Tiroco! 
%      And our children!}
% 
% He was about to rush over to her when he noticed the big mound. 
%
\tho{And a big mound. 
     What is that?}

The priest was speaking. 
He recognized words from the \iquinian{} death mass. 

\tho{A funeral?} 
He looked at the mound. 
\tho{Oh, \sephiroth. 
    This is \emph{my} funeral!}

His body lay atop a great pyre. 
Iquinian custom dictated that the bodies of the dead be burned. 
That way it could not be used for evil purposes by necromancers and \daemons, and the soul would be free to go into the Light. 

\tho{Go into the Light. 
     Heh. 
     Yes. 
     That is working out well.}

As was to be expected, many of House Pelidor were gathered at the funeral. 
\tho{There is \Tiroco! 
     And our children!} 

All other thoughts vanished, and he rushed forward to meet her. 
\tho{\Tiroco!} 
He came to a halt only few feet from her. 
\tho{\Tiroco. 
     It's me, \Icor. 
     I'm here!}

No reaction. 

\tho{\Tiroco? 
     Why won't you answer?
     Why won't you look at me?}

He reached out to touch her. 
His hand slid off her... and dissolved! 
Dismayed, he pulled back. 
He looked down at his hands. 
They looked strange. 
Alien. 
Abnormal. 
\tho{These aren't my hands.
     Are these my hands?
     They can't be my hands.
     Can they?}

He did not understand. 
He could not put into words what was wrong, but somehow the shape, the texture, the colour... they were all wrong. 
The wrongness fled when he tried to focus on it. 
One hand looked almost normal when he inspected it, but the other hand would seem to warp at the edges of his vision. 
It had too many fingers. 
No, it had too few. 
It bent at weird angles. 
It twisted around to meet itself in a circle. 

He reached out for her again. 
His hand almost touched her... and failed to touch. 
It did not meet resistance. 
Neither did it pass through her. 
It simply... slid off, vanishing into some impossible angle. 

\tho{\Tiroco!
     Help me!
     Something is wrong with me!
     \Tiroco!}

No reaction. 

He addressed his six-year-old son. 
\tho{Roric. 
     It's Father. 
     You know me, don't you?}

No reaction. 

He turned to his daughter, who, being only three years old, was being carried by a servant. 

\tho{Frico? 
     Little Frico?}

She turned away with a hoarse whimper. 

It dawned on him. 
\tho{I am dead.
     I am a ghost. 
     They can't see me.}

He looked down at his hands again. 
\tho{Why are they like this?}
This form, subtly wrong, subtly warped in some manner that defied his ability to describe. 
This was not how he had imagined a ghost would look. 
He had figured ghosts might be pale, corpselike. 
Perhaps misty, or shadowy, or transparent. 
But not this. 
Never this. 

\tho{They can't see or hear me. 
     I can't reach them.}

\begin{comment}
\section{The Pelidor schism}
\end{comment}

Defeated, he looked around. 
% There he saw \Dornaer, \ps{\Tiroco}{} warrior sister, guarding her like a hawk. 
% And others of her family. 
\Tiroco{} and the children were surrounded by her own family, who guarded her like hawks. 

He recognized the pattern immediately. 
\tho{Split into the two branches. 
     \Forkliners{} on this side, \Malcurians{} on the other side.}
\Icor, who had considered himself a fair and rational ruler, felt a pang of guilt over that fact that, in all his self-pity, he had not spared one moment of thought for the political consequences of his death. 
Now he did not know whether to laugh or cry. 
\tho{I am dead for a moment and they all start fighting.} 

House Pelidor, with all its offshoots put together, owned a sizable portion of the land; enough to consolidate their rule of the duchy. 
But there was infighting in the clan. 
Over the generations these differences had split the family into two rival branches: 
A western branch, the most powerful one, centered in Malcur and an eastern branch, only slightly less powerful, centered in \Forklin, the second greatest city in the duchy. 

\Icor{} himself was a \Malcurian{}. 
\Tiroco{} was a \Forkliner, and their marriage had been an attempt to reconcile the two fractions. 
It had worked well, \Icor{} thought, and quelled much of the hostilities between them. 
He had expected to rule until a natural death, after which, hopefully, one of their children\dash a descendant of both bloodlines\dash could be chosen as the new duke and thus tie them all together. 
But those hopes, he realized now, had been dashed by his untimely death. 
His children were all less than ten years old, and Pelidor needed a real duke. 
\Tiroco{} would not be chosen, either. 
% There was no possibility of that. 
% She was no ruler. 
% % She had been a compromise candidate from the start. 
% \ps{\Icor}{} family had been in favour of her for that exact reason: 
% She was weak. 
% The \Malcurians{} had wanted a spouse who would not unduly influence \quo{their} reigning duke. 
% No, \Tiroco{} would never be chosen as reigning duchess. 
Some other candidate would take the throne. 
The balance of power would shift. 
Very likely the conflict between the branches would escalate. 
His and \ps{\Tiroco}{} union had been arranged only after long and hard negotatiations between the rival Pelidor lords, and it would not be easy to establish another. 
\tho{Please elect someone good. 
     Don't let Pelidor descend into chaos and infighting.}

\Icor{} drifted around among the funeral guests. 
He was picking up snippets of conversation from the Pelidors. 
\tho{What is this? Something about a war?} 

The world around him was ghostly and unreal. 
Voices would rise and fade. 
Scenes would become blurred and misty. 
At times he would suddenly find himself in a new place, several yards from where he thought he was. 
\tho{Being a ghost is difficult. 
     I don't understand any of this.
     I hate being dead. 
     I want to be alive again. 
     Not this.}

% With the bits and pieces he was able to overhear he gradually pieced  together some of the puzzle. 
% \tho{We are at war with Runger. 
%      For some reason. 
%      \Sethgal{} is leading the army north-east to meet them. 
%      Probably many days have passed since I died. 
%      No new duke yet, though. 
%      Which means that \Tiroco{} is stuck as regent.} 
% When a reigning duke or duchess died, it was customary that his widow preside as regent until the House chose a new duke. 
% \tho{Poor \Tiroco. 
%      You wouldn't want this.} 

He looked at \Tiroco{} again. 
Their marriage had been political, but they had learned to love one another after all. 
\tho{Poor \Tiroco. 
     All alone in the chaos of interregnum and war. 
     She is crying. 
     But trying to be strong. 
     Oh, \Tiroco...}
She lifted her head, swept her eyes over the place. 
They reached the place where he stood, in the shadows under the pyre. 

Their gazes met. 

She licked both eyes and goggled.
%Her eyes widened. 

Her mouth opened. 
%She opened her mouth. 

\tho{She can see me!}
He took a step forward, reaching out with his hand. 
\tho{\Tiroco!}

She averted her face, covered her eyes with her hands and began to sob. 

He stopped. 
\tho{She doesn't want to see me.
     She's afraid of me. 
     
     Of course she is. 
     I am a ghost. 
     I am haunting her. 
     Who would want to be haunted?}

\ps{\Icor}{} mind was hazy and confused already simply from being a ghost. 
Now, his grief made him completely forget the angel and his task. 
%In his grief (and his already ), \Icor{} forgot
\tho{What have I become?
     My beloved wife can't stand the sight of me. 
     I'm a monster. 
     An abomination. 
     An unwanted, hateful thing. 
     I brought all this upon \Tiroco{} and the rest by dying, and now I'm back to haunt and scare them. 
     What am I doing?}

With those thoughts, \Icor{} faded away and lost consciousness. 

% Icor angsts over the fact that he is now an unwanted, hateful abomination. 
% So bad that even his beloved can't stand the sight of him. 
% Maybe this grief causes him to lose focus, and he fades into the darkness again. 

\begin{comment}
\section{\Tiroco{}}
\end{comment}

\stamp{\dateIcorBuried}
      {Iquinian Church, Malcur}
% Then insert a scene with \Tiroco{} where she angsts over the responsibility, and feels bad that she is now seeing ghosts and fretting over them where she should be strong for her people and her children. 
\tho{Get a grip of yourself, \Tiroco!} she told herself. 
\tho{Not only do I dream of \Icor{} being alive at night, now I also see hallucinations of him in broad daylight. 

     Face it. 
     \Icor{} is not coming back. 
     He has gone into the Light.

     Come on, \Tiroco. 
     You have got to be strong. 
     Your children need you. 
     Your clan needs you. 
     Your country needs you. 
     I must be strong.

% There was no possibility of that. 
% She was no ruler. 
% % She had been a compromise candidate from the start. 
% \ps{\Icor}{} family had been in favour of her for that exact reason: 
% She was weak. 
% The \Malcurians{} had wanted a spouse who would not unduly influence \quo{their} reigning duke. 
% No, \Tiroco{} would never be chosen as reigning duchess. 

     But I am not. 
     I am weak. 
     Much too weak. 
     Everyone knows that. 
     I was never meant to rule anything, I understood that. 
     I am no ruler. 
     That was why the \Malcurians{} had \Icor{} marry me instead of someone else, someone better. 
     They didn't want a strong \Forkliner{} exerting unduly influence over \quo{their} duke. 
     They wanted a weak little girl who would not get in their way. 
     
     And I fulfilled that role. %, damn it. 
     I was \ps{\Icor}{} wife, as simpering and useless as a \human{} woman. 
     And I did not complain. 
     I did not crave power. 
     I loved him. 
     }

Then everthing had gone wrong. 
\Icor{} was murdered. 
When a reigning duke or duchess died, it was customary that his widow preside as regent until the House chose a new duke. 
Meawhile, the Pelidor clan was thrown into a chaotic interregnum, fighting over the choice of the new ruler. 
And then Runger had invaded. 
\Sethgal{} had marched towards the border, leading the army to face them. 
With half of the nobles forced to go off to war, the clan was in no condition to elect a duke any time soon. 
So \Tiroco{} had to remain regent. 

\tho{%
  I didn't want to be regent. 
  They don't want me to, either. 
  None of them want me. 
  I am no good as a ruler, and everyone knows it. 
  But I ended up ruling anyway. 
  Now I must do my best. 
  I must be strong. 
  I must make my family proud of me. 
  
  I cannot keep seeing ghosts and wishing the real world away. 
  \Icor{} is gone. 
  I know I am not much of a replacement, but I will have to do. 
  
  I will have to do. 
}









