\bookchapter{Where Angels Fear to Tread}
\begin{comment}
\subsection{\Tiroco{} in the corridor}
\end{comment}
\stamp
  {\dateIcorHauntsTiroco}
  {A corridor, \CastlePelidor}

\tho{Great \Sephiroth, I'm tired.}

\Tiroco{} slumped. 
It had been a long day. 
As the acting regent she had many duties: 
There were taxes to administer, expenses to cover, laws and edicts to sign, soldiers to be drafted and routed around. 
And she had to judge in courts of law. 
She had spent much of this day listening to all sorts of people's complaints, allegations and pleas. 
All the while trying to figure out who was right and who was wrong. 

\tho{%
  Did I judge rightly? 
  Was that man really guilty of adultery, or did his wife just hate him? 
  Should I have convicted him?
  
  Had that \sphyle{} really stolen her neighbour's property?
  Or whose property was it really? 
  Should I have let her go? 
  
  I don't know. 
  
  I once thought I knew what was right and wrong. 
  I thought as long as I was noble and educated and went to church, I would know good from evil when I saw it. 
  But I don't. 
  I don't know anything. 
  
  Light, I'm tired. 
  I can't think anymore. 
}

She had felt she needed some time alone, so she had dismissed what servants she had around and chosen to walk back to her chambers alone. 

Caught up feeling sorry for herself, \Tiroco{} paid little attention to her surroundings. 
But when she passed a man-high mirror in the wall she thought she noticed some strange shadow in the corner of her eye. 

She turned. 

There, in the mirror, was \Icor!

She looked around and behind her, but he was nowhere to be found. 

Only in the mirror. 

\Tiroco{} backed away a step. 

It was \Icor. 
Yet he did not look like himself. 
He looked like a cadaver. 
He was emaciated, and his outline was frayed. 
Scales pale gray and falling out. 
Mouth gaping. 
Eyes bulging and staring, like those of a fish. 
They were unnaturally dry, those eyes, as if they had never been licked, and they goggled at her in a way that made them look about to pop out of their sockets. 

\Tiroco{} shook her head and, involuntarily, mumbled in a low whine. 
She took another step back.

The apparition reached out a hand towards her. 
Fingers grasping, groping the air. 
Dry eyes pleading. 
Mouth moving. 

She took a third step. 

An inarticulate croaking noise came from the ghost's throat. 
\hypotalk{Ti...ro...co...} she thought she heard him say. 

She turned away. 

She ran. 

\tho{\Icor...}

She sobbed aloud as she ran to her room. 



\tho{%
  No!
  This isn't happening. 
  This isn't real.}

But the words sounded hollow. 
She was not convinced. 
She did not know what to think. 
Nor was it the first time this had happened. 
It had began at \ps{\Icor}{} funeral, but since then she had more than once imagined seeing glimpses and images of him. 

\tho{%
  Something is wrong with me. 
  I'm seeing \qliphoth.}
The images always appeared in hidden places: in shadows, behind mirrors, in ponds, behind curtains or bushes. 
Dark places where dark things might lurk. 
\tho{%
  It's the power of darkness and the unknown. 
  The power of fear. 
  It is evil. 
  The priests warn us about this. 
  The \qliphoth{} are all around us and work to tempt us and lead us astray. 
  They must be kept away by unwavering faith in the Light.
  
  That thing is not \Icor. 
  A ghost is a thing of evil. 
  I must not let it into my heart.}

Slaves came into view at the end of the hallway. 
Ingrained protocol made \Tiroco{} slow down. 
Nobles did not run. 
Least of all in front of slaves. 

She continued at a fast walk, trying not to sob. 

\tho{ 
  Unwavering faith.
   
  But my faith wavers.
  
  Something is wrong with me. 
  Am I not a good Iquinian? 
  Am I bad? 
  Is that why I am seeing these things?
  Oh, I wish I were smarter. 
  Then I would know what to do. 
  I wish I were stronger of faith. 
  Then this wouldn't happen to me. 
  I'm supposed to follow the Light. 
  But how?
  I can't see the Light.
  I only see \ps{\Icor}{} ghost everywhere.}



\begin{comment}
\subsection{\Tiroco{} in her room}
\end{comment}

% She has now reached her room. 
% She slows down and forces herself to catch her breath before entering. 

Lost in thought, she found herself before the door to her chambers before she knew it. 
Again protocol seized control of her mind, and she forced herself to stop and catch her breath before entering. 
\tho{%
  Mustn't let the slaves see me flustered and despairing. 
  Must keep up appearances. 
  A ruler must always show strength. 
  If a ruler shows despair it will spread, and soon the whole country will despair.}

% So she tries to keep her head up high as she enters. 
% Two slaves immediately jump to their feet. 
% A third one\dash the one specifically assigned to keeping \ps{\Tiroco}{} egg warm\dash remains seated, as is her job, but bows as low as she is able from her position. 
% The slaves are \Piacet, Weyra and Duen. 
% Weyra and Duen are \sphyles. 
% \Piacet{} is a woman. 
% Weyra, the egg-keeper, is the oldest one of them. 
She took care to arrange her dress nicely, and when she entered she kept her head up high. 

Two of her chambermaid slaves, Duen and \Piacet, immediately jumped to their feet and bowed low. 
The third slave, Weyra, was specifically tasked with keeping \ps{\Tiroco}{} egg warm, so she remained seated and bowed as good as she could manage. 

\Tiroco{} took off her shawl and handed it to \Piacet, then sat down on the divan and slumped. 
\tho{%
  It's all right. 
  I'm allowed to slump. 
  I'm tired. 
  I can show being tired. 
  That's not improper.}

\ta{Weyra. Give me the egg.}

Weyra got up\dash slowly; she was an old \sphyle\dash and gently picked up the egg and presented it to its mother. 





% \Tiroco{} waves Weyra away and hugs the egg. 
% When she holds it close she can feel the baby squirming inside. 
\Tiroco{} hugged the egg tight and stroked it. 
She could feel it vibrate as the little one squirmed inside. 
When she put her ear to the shell she thought she could hear it rummage about. 

\tho{%
  I wish I were back in my egg. 
  It is a scary world out here, little one. 
  But don't you fear. 
  Mother will protect you.
  
  Yes.
  Mother will protect you. 
  I must be strong. 
  For the egg's sake.
  And for Roric and Frico.
  I owe them that.
  I can take care of my children. 
  That, at least, I can do.}





% She summons her servants (including \Piacet) and tries to have a good time with them. 
% They gossip and girl-chat and laugh like a lady and her slaves are supposed to. 
% 
% \Piacet{} seems very nice and loving and friendly. 
% \Tiroco{} likes her. 
% But secretly \Piacet{} hates her. 
Soon Duen began to chatter. 
She was the youngest of the three chambermaids and the most lively. 
\Piacet{} and Weyra joined in, and gradually the mood lightened. 

\Tiroco{} slowly loosened up. 
They gossipped and girl-chatted like a lady and her chambermaids were expected to do, and for a while \Tiroco{} managed to forget her worries. 
They talked about dresses, makeup, eggs and children, and even \daxes. 
This left \Piacet{} somewhat out in the cold, being the only \human{} present, but she took it well. 

\tho{%
  \Piacet{} is so sweet. 
  Always nice and loving and understanding. 
  I like her.}





% But then she glances over at the curtain. 
% It's a very thin-woven and translucent curtain. 
% And then she sees \Icor{} behind the curtain. 
% He stands there looking ghostly and scary and reaches out for her with his clammy hand. 

Weyra told a racy joke, and all four quacked with laughter\dash or, \Piacet{} squealed while the three \sphyles{} quacked. 
\Tiroco{} idly laid back her head and glanced over at the closed balcony curtain. 

\tho{What's that?}

There was a figure behind the translucent curtain. 

For a heartbeat she suspected a burglar or assassin, and almost cried out. 
But the next heartbeat, as she looked closer, it dawned on her:

\tho{\Icor!}

It was the apparition again. 
Ghostly and cadaverous and reaching out for her with his clammy hand. 





% \Tiroco{} yelps out loud. 
% The slaves all jump. 
% \Tiroco{} feels foolish for embarrassing herself in front of her slaves. 
% Especially given her earlier considerations that a ruler must never display despair lest it infect her subjects. 
% 
% She sends a slave over to pull the curtain aside. 
% \Icor{} promptly vanishes. 
% After all, he cannot appear in broad daylight. 
% 
% The slaves claim they saw nothing. 
% But \Tiroco{} thinks \Piacet{} saw it. 
% \Piacet{} is slightly more verticious than the rest and a bit better able to see stuff in the beyond.
% But she denies it. 
This time \Tiroco{} did cry out. 

The slaves all jumped. 
\ta{What is it, my Lady?} asked Duen. 

\ta{There... behind the curtain...} \Tiroco{} pointed. 

\ta{What? I don't see anything,} said Duen. 

\Tiroco{} noticed \ps{\Piacet}{} eyes narrowing as she studied the curtain. 
\Piacet{} said nothing. 

Weyra rose and went over to pull the curtain aside. 
Nothing there. 

\ta{What did you see, my Lady?} asked \Piacet. 

\ta{Didn't you see it?} said \Tiroco. 

\Piacet{} shook her head. 
\ta{No, my Lady. Nothing.}

The other two said the same. 

\Tiroco{} eyed \Piacet{} some more. 
\tho{%
  Was there something strange in her eyes?
  Did she see it, but won't admit it?
  
  No. 
  Shame on me. 
  It's wrong of me to distrust her. 
  I am the one seeing ghosts. 
  Who am I to judge others for being sane? 
  \Piacet{} is a good and devoted slave. 
  She loves me.
  She wouldn't lie.
  
  I must pull myself together. 
  I can't do this alone. 
  I must have faith in the people around me. 
  My slaves are wonderful. 
  They love me and only wish me and my family the best.}

Looking at it from this perspective, \Tiroco{} felt stupid for having yelled, not only embarrassing herself but also scaring the slaves who were her friends. 

\tho{%
  Yes. 
  My slaves are wonderful.
  They want nothing more than for me to be happy. 
  I have no right to let that go to waste by despairing.}

\ta{You're right. It was probably nothing. I am just seeing things.}
She forced herself to laugh. 
The others laughed as well, and gradually it began to feel less forced. 

They went back to chatting, joking and telling stories. 
Eventually \Tiroco{} managed to block out thoughts of the ghost and enjoy herself. 

When at last she fell asleep\dash the slaves sleeping in the room with her, as was custom\dash she was hugging the egg tight and thinking idly happy thoughts about the hatchling and its future. 



% Then she tries to have fun. 
% They giggle and talk and stuff. 
% Eventually she goes to sleep.
% The slaves are still in her room. 
% It is customary to sleep with slaves in the room. 
% 
% She falls asleep hugging the egg tight. 







\begin{comment}
\subsection{\Piacet{} mocks her mistress}
\end{comment}
\new
% POV: \Piacet/Needle. 
\Piacet\dash Needle, as she preferred to call herself\dash was still awake. 
She sat on a chair and looked down on the sleeping duchess and her egg. 

\tho{%
  You disgust me, \Tiroco. 
  You lord it over us and think you're better than us. 
  But look at you. 
  You are worthless. 
  Pampered and incompetent. 
  You can't do anything but cry. 
  And then you expect us to comfort you and do everything in our power to make you feel better. 
  
  What about us slaves? 
  Where are you when one of us is suffering? 
  Who is there for us? 
  No one! 
  
  The law says that it is the owner's duty to protect her slaves and keep them free from harm. 
  You can't even do that. 
  
  You think you have it hard. 
  Bah.}
Needle thought back to her childhood. 
She had been a free woman, once. 
But her family had been poor and indebted. 
When a disease claimed her mother and father, she had been claimed as a slave to repay the debt. 
\tho{%
  I have faced hardships you cannot imagine. 
  I was a nobody when I started, and the world conspired brought me even lower. 
  But I weathered it. 
  I have worked for everything I have. 
  I have suffered for it. 
  I \emph{deserve} everything I have, and more. 
  
  You had power and greatness thrown into your lap, and what do you do?
  You whine and complain and cry and shy away from it. 
  
  I am better than you. 
  Why is it, then, that you rule and I must serve? 
  What god or \sephirah{} made you duchess and me slave?
  
  I deserve to be much more than you. 
  I \emph{will} be. 
  I \emph{am} more than you. 
  By day I am \Piacet, the duchess' simpering slave. 
  But by night I am Needle, Cabalist of the \needlecircle{} circle.
  I will shape my own destiny. 
  
  You will never last, \Tiroco. 
  Your time of greatness is already over. 
  You and all the rest of you so-called nobles. 
  You will see. 
  When the \resphain{} return, your kind will be swept away. 
  
  How I long for that day.}





% At first, she was particularly disgusted when \Tiroco{} saw \Icor{} behind the curtain. 
% But then she looked closer, and she thought she saw it, too. 
% She wonders if there really \emph{is} something going on in the Beyond. 
% After all, \Achsah{} herself told her that the Sentinels are brewing something. 
She thought back to that time when \Tiroco{} yelped up about something she imagined she saw behind the curtain. 
At first she had been disgusted by the duchess' hysteria. 
But then, looking closer, she had thought she saw something, too. 
Needle did not know much about the Realms Beyond, but she knew that they existed, and that, of course, was more than most people did. 
She was not sure, but she thought she detected the fleeting presence of some entity from the Beyond. 

\tho{%
  Was there really something?
  After all, \Achsah{} herself told me that the Sentinels are brewing something. 
  Is there something sneaking around in the Beyond?
  And does \Tiroco{} know about it?}

% She looks down at the sleeping \Tiroco. 
% Comptemptuously. 
Again she looked down at the sleeping countess and sneered. 
\tho{%
  What's with you?
  Are you just a wimp who jumps at shadows? 
  Or is there something going on with you?
  
  And how much do you know?
  
  I will have to keep my eyes peeled.}







\begin{comment}
\subsection{\Icor{} angsts}
\end{comment}
\new
\Icor{} was there, and yet not there. 
He could see \Tiroco{} and the egg, almost clearly. 
Beyond that, everything became unclear. 
If he concentrated he could recognize the three slaves and a few features of the room, but only barely. 
It was all hazy, as if seen through murky water. 

\Tiroco{} and the children were the only things that mattered to him. 
\tho{%
  Maybe that's why.
  They are the only things that are real to me...
  
  But I am not real to them. 
  \Tiroco{} sees me. 
  I know she does. 
  I can see it in her eyes. 
  But she fears me. 
  She flees from me. 
  
  What have I become, that even my wife loathes me? 
  Why must I be this hateful thing?
  And \Tiroco... why do you not love me any more?
  Why have even you turned from me? 
  
  No! 
  Thinking like this brings me nowhere!}
He wanted to slap himself, or clench his hands, or lick his eyes. 
Or even just take a deep breath. 
But he could not. 
He had no hands. 
No lungs. 
He could only think: 
\tho{%
  Pull yourself together, \Icor. 
  I must not blame \Tiroco. 
  She is innocent of all this. 
  I must persevere. 
  Remember what the angel told me. 
  
  What \emph{did} the angel tell me? 
  It said something about what I had to do. 
  Something about what I \emph{could} do.}
He had to strain his mind to remember the angel's words. 

\tho{%
  Why can't I remember?
  Is it because I am a ghost?
  Are ghosts forgetful? 
  
  Do ghosts go insane?
  Do ghosts become evil?
  Is that why people fear them?
  
  No! 
  No more angst!
  Focus!}

He concentrated on the angel and its words. 
Gradually they came back to him. 
The angel had told him that it was doing all it could to help him, but its powers were not unlimited. 

\tho{Why not? Aren't they supposed to be?}

Then he remembered the rest. 
\tho{%
%   There is some great evil afoot in Malcur. 
%   The angel wants to stop the evil. 
  That's it. 
  The angel needs my help. 
  And \ps{\Tiroco}.
  That's why it contacted me. 
  That's why I must contact her.}

He also remembered what the angel had told him about how to appear to the living. 
He could not appear in broad daylight, for they would not see him. 
They would block him out and refuse to see what was before their eyes. 
He must show himself in corners, in shadows, behind curtains, in mirrors. 
Places where their vision was less sharp, where the world was less certain. 
And he had tried. 
He had called out to \Tiroco{} from the mirror, and from the balcony. 
She had seen him. 
But she had fled. 





% Then he appears in her sleep. 
% This works. 
% 
% Maybe the angel shows up to help him, having decided that he's too ineffectual on his own. 
% 
% \Tiroco{} is dreaming of \Icor{} still being alive. 
% This allows \Icor, with \Psyrexz{} help, to sneak into the dream and talk to her. 
% 
% Or wait. 
% Maybe she is just asleep, and therefore her mind accepts the possibility that she \emph{might} just be dreaming of him, and therefore he is able to sneak into her mind. 
% He remembers that the angel advises him to do this. 
% But first he hovers over her sleeping form and admires her beauty. 
% He tries to caress her and wipe away the tears, but he can't. 
% He tries to hug the egg, but he can't. 
\tho{%
  I don't know what to do. 
  \Tiroco... will I ever get through to you?
  Or are you lost to me forever?}
  
He hovered over her sleeping form. 
\tho{She is beautiful.} 
There were marks of tears on her cheek. 
She had been crying. 
He reached out to caress her, but he could not. 
His hand slid off into space, unable to touch her. 

\tho{So close, and yet so far.}

He looked at the egg. 
So perfect. 
So round. 
So strong and safe and protective. 
So full of life and promise and future. 
He tried to touch it, and again he failed. 
His hands almost reached the egg, but they could not find it. 
He could not reach the place where the egg should be. 
His hands kept finding the wrong places. 
They should touch, but they did not. 
Instead they grasped at empty air. 

\tho{My egg...}







\begin{comment}
\subsection{\Icor{} in \ps{\Tiroco}{} dream}
\end{comment}
\telepathy{She sleepeth.}

What was that?

It was the voice of the angel.
In his head. 

\tho{Angel?}

\telepathy{%
  She sleepeth. 
  Her thoughts are open and unguarded. 
  Thou wilt will be able to slip into her dreams and make her see thee.}

\tho{%
  But how?
  What am I supposed to do?}

\telepathy{%
  Concentrate. 
  Will thyself into her mind. 
  I will guide thee.}

\Icor{} did as he was told. 
He concentrated as hard as he could. 
\tho{\Tiroco. Let me in. Please. Let me in.}
% He concentrates really hard and wills himself into her mind. 
% Perhaps \Psyrexz{} spells help him. 

He felt the presence of the angel around him, felt its benevolent magic aiding him. 

And the world changed. 

First there was colourless mist and nothingness. 
Then things formed. 
Green things. 
Yellow things. 
Blue things. 
White things. 
Grass. 
Flowers. 
Trees. 
Castle walls. 
Towers. 
People and animals in the background. 

\tho{Where am I?}

It did not look like \CastlePelidor. 
But it \emph{felt} like \CastlePelidor. 
It \emph{smelled} like one of the castle gardens. 
And those walls and towers... the shapes and patterns were inaccurate, but the outlines were right. 
The overall colours were right. 
\tho{What is this place?}

\telepathy{%
  I have brought thee into her dream. 
  Now she can see and hear thee. 
  Go to her.}

\tho{%
  I get it. 
  This is a respresentation of the castle as it appears in \ps{\Tiroco}{} dream. 
  Inaccurate, crudely reconstructed from memory. 
  But clearly \CastlePelidor.}

A child ran by in across the grass. 
It was his daughter! 

\ta{Frico!} he called. 

Frico did not seem to hear. 

\tho{Am I still a ghost?}

He followed her. 
After a while she sat down and looked up. 
Not at him. 
Merely up. 
She looked strange. 
There was something about her face, her body, her movements. 
She looked happy, but somewhat unreal. 

\tho{Why is she here? And why is she so strange?}

\ta{Mother!} Frico yelled all of a sudden. 
She leapt up and ran past him. 

He turned. 
Then he saw \Tiroco. 
She sat on a bench amid high flowers. 
Roric was with her. 
In her arms she held the egg. 

\ta{\Tiroco!} 

She looked up. 
A blissful smile was on her lips. 
\ta{\Icor,} she said softly. 

\ta{\Tiroco, my love!} 
He ran to her, pulled her up and embraced her tight. 
He took her hands in his and held on to them. 
\ta{\Tiroco. You can see me...}
He licked her eye, and she licked his. 
They held each other for a long moment. 

\Icor{} looked down and found Roric. 
He laid his hand on his son's head. 
\ta{My son.}

Roric did not respond. 
\Icor{} noticed that the boy had the same strange look on his face that his sister did. 
And now that she thought about it, the egg looked strange, too. 
It all did. 

All but her. 
All but \Tiroco. 
She alone felt real. 

\tho{%
  Of course. 
  This is her dream. 
  Only she is real here. 
  All the rest are figments of her imagination. 
  This isn't really Roric and Frico and the egg, just as it isn't really the castle. 
  It's just \ps{\Tiroco}{} memory of them.
  
  But I am here, too. 
  I am real.}

\ta{%
  \Tiroco. 
  You must listen to me.}

\ta{%
  Mmmm...} she hummed. 
\ta{%
  What is it, my dear?}

He took a deep breath.
\ta{%
  \Tiroco, this is a dream.}

She looked at him bemused. 
\ta{What?}

\ta{%
  You are dreaming, \Tiroco. 
  You must remember. 
  Remember, \Tiroco!}

Confusion. 
\ta{Remember? Remember what?}
She looked into his eyes. 
Then looked away. 
Stared into space. 
Then looked him in the eye again. 

Then licked her eyes. 
\ta{No... no...}
Horrid realization spread across hear face. 

\ta{Yes, my love. I am afraid so,} he told her.

\ta{%
  But... but... you are dead. 
  How can you be dead when you are here with me?}

\ta{%
  I \emph{am} dead, \Tiroco. 
  But an angel sent me back!}

\ta{%
  This is a dream.
  It's not real.}
Tears formed in her eyes. 
\ta{%
  You're not back. 
  You can't be back. 
  It's just a dream. 
  It's all fake.}

\ta{%
  No! 
  \Tiroco, listen to me. 
  It's true, this is a dream. 
  But I am \emph{real}!
  I am not something you dreamt. 
  I have come back as a ghost to visit you in your dream. 
  It is really me.}

\ta{%
  No.} 
She looked down and shook her head. 
\ta{%
  I want you to say this. 
  I want to hear that everything is all right. 
  But I know it's not true.
  I keep seeing your ghost everywhere.
  I am losing my mind.}

He grabbed her by the shoulders. 
\ta{%
  You are \emph{not} losing your mind!
  Look at me!
  Look!}
He took Roric and lifted him up. 
\ta{%
  And look at him. 
  This is not Roric. 
  The real Roric lives in the real world. 
  This is just your dream of him.}
He put the boy down and seized Frico.
\ta{%
  And look at her. 
  This is also a dream. 
  This isn't the real Frico.
  Our children live, \Tiroco. 
  They are not ghosts. 
  They are regular dreams. 
  But look at them!
  Then look at me!
  I am different!
  I am real!
  I have come back to you from the realm of the dead.}
He was guessing. 
He could not see himself in a mirror, so he did not know if he looked any different from the children. 
But he ought to, since he was real and they were dreams. 
He hoped he did. 
He hoped she could see it. 

\Tiroco{} tried to wipe her eyes clean as she took in all of this. 
She looked deep into the children's eyes, and into \ps{\Icor}. 
\ta{%
  It's true... you look different.
  Is it really you, \Icor?}

\ta{Yes, my love. It is I.}

\ta{Oh, \Icor!}
She hugged him tight and licked his eyes, his snout, his lips. 
\ta{You've come back to me. You're not dead anymore!}

\Icor{} remained quiet. 
For a very long moment he simply held her. 
At length, he took a deep breath and pulled back. 
\ta{%
  No, \Tiroco. 
  I am still dead.
  I have not come back to life.}

\ta{What?} she said. 
He could see in her eyes how she refused to believe. 
\ta{But you must be. You're here. With me.}

\ta{%
  Listen. 
  I will tell you what happened.
  I was dead. 
  For a while I was in the afterlife. 
  I thought I would go into the Light, but I did not. 
  Then an angel came to me. 
  An angel, \Tiroco!
  
  It told me that there is some great evil afoot in Malcur. 
  Some dark force infesting the city, casting a wicked shadow over all.
  This evil was what killed me, and it is preventing me from going into the Light. 
  The angel opposes this evil, but the evil power is strong. 
  The evil has been growing for a long time, and it has grown strong. 
  That is why the angel is weakened. 
  \Itzach{} holds sway over the city. 
  Our beautiful city.
  
  That is why it helped me and sent me back to you as a ghost.
  The Light needs our help. 
  \emph{Your} help, \Tiroco. 
  You must help combat this evil that infests out city.}

\ta{%
  Me? 
  Combat a great evil?}
She laughed. 
There was pain in it. 
\ta{%
  You're making fun. 
  Don't mock me. Please.
  I can't fight anyone. 
  I can't do anything.
  I can barely protect my own children.}
Her voice became high-pitched, trembling, hysterical.
\ta{%
  I can't do anything!
  I can't fight anyone!
  And you speak of some great evil that gives pause to an \emph{angel}?
  What could I possibly do against such a thing?}

She sobbed. 
When she spoke again it was in a low voice.
\ta{%
  Please. 
  Come back to me, \Icor. 
  I can't do it alone.
  It's not fair.
  I don't want to rule.
  I never wanted to rule anything. 
  I'm not cut out to be regent.
  It's not fair!}

Part of him wanted to shout at her. 
\tho{%
  I died! 
  I endured torment in the realm of the dead and was sent back as a  undead thing. 
  And even then, you didn't acknowledge me! 
  You turned away from me in disgust!
  And you tell \emph{me} it's not fair?}
He opened his mouth to tell her this, but the distress painted on her face stopped him. 
One of the things he had had to learn as a duke was how to be strong for your people even when you did not feel strong. 
\tho{%
  I can do this. I must. We must both play our parts.
  I must be there for her, support her where I can.}

So he took her in his arms and held her close again. 
He kissed her eyes, caressed her lips and nose. 
\ta{%
  You're right. 
  It's not fair. 
  I know you didn't want this, \Tiroco.
  You shouldn't have to go through this. 
  No one should. 
  But I am here with you now.
  I can't come back to life, but I can still be here with you.
  I can't be at your side during the day, but I will come back tomorrow night.
  You won't have to be alone.}
  
He was promising more than he was sure he could keep, but he had to say something. 
\tho{%
  Please, Light. 
  Please, angel.
  Let it be possible.
  Let me visit her again.
  She needs me.
  And I need her.
  I am going out of my mind here in the afterlife. 
  I need her.}
  
\ta{%
  I promise I will give you all the support I can.
  But you must do this. 
  You must help me.}

She looked him in the eyes again.
Nodded. 
\ta{%
  I will. 
  I can do it.}

He smiled. 
\ta{I love you, \Tiroco.}
And then he told her what the angel had told him; what she must do to serve the cause of the Light and stem the tide of Darkness. 





% He looks down at his hands and body. 
% Maybe he notices that he looks more real, more fleshy, more alive here. 
% Maybe it's because she believes he is alive that it shapes the Shroud around him and makes him look and feel alive. 

% He then explains what she has to do in order to Stop The Evil. 
% The angel has told him that there is a great evil afoot in Malcur. 
% It seeks to corrupt the city and destroy their country. 
% It is an enemy of the Light and all that is good. 
% The angel wants to stop it, but it cannot fight it directly. 
% It needs to appeal to pious mortals for help. 

% \ta{%
%   We have a sacred duty here, \Tiroco. 
%   We must do all we can to serve the Light.
%   Here is what the angel told me...}









