
\chapter{Nature of the Universe}
\section{\Dweomers}
\target{Dweomer}
\target{dweomer}
\Dweomers{} are not physical objects but abstract sources of power\dash lifeforce and magical energy. 
They are disembodied forces that exist in the Web of Realms; distributed systems spread out on myriad threads. 








\subsection{\Dweomer{} filters}
\target{Dweomer filters}
\target{front-end}
There exist small \dweomers{} that are dependent on a mother \dweomer. 
Compare to how small streams branch off from a large river, which in turns branches off from the ocean. 
These small \dweomers{} can act as filters, \quo{front-ends} for a stronger but less user-friendly \dweomer. 
A good example is \iquin, which is a filter on \itzach, itself a front-end for the \hr{Heart}{Heart of \Miith}. 









\subsection{The Sun}
\target{Sun}
\index{Sun, the}
The Sun is a \dweomer{} connected to the \hr{Heart}{Heart of \Miith}. 
%It may be \hr{\voyagers{} create the Sun}{created by the \voyagers}.

The \banes{} want to conquer and control the Sun. 

\lyricsdimmuborgir{Vinder Fra En Ensom Grav}{
  Se der i fjellbrisens indre,\\
  hvor dets liv har s\oe{}kt ly for en sol\\
  som omsider vil m\oe{}rkne med den evige natt\\
  og hindre en verden i (\aa{}) blomstre og gro.
}









\subsection{The Heart of \Miith}
\target{Heart of Miith}
\target{Heart of Mith}
\target{Heart}
\index{Heart of \Miith{}, the}
\index{\Miith{}!Heart of \Miith{}, the}
The \quo{Heart of \Miith} is a \dweomer{} which many factions seek to access and control. 
It is, in a sense, the source of all life and power on \Miith{}. 
It is the centre of the Shroud, and whoever controls the Heart has the power to reshape the Shroud. 

The name \quo{\Miith} belongs to the Heart. 
It ought to have a longer name in \draconic, of which \quo{\Miith} is a contraction. 

Also, remember to name the Realms that are part of \Miith{}. 

\Erebos{} is \emph{not} a part of \Miith{}, but \Nyx{} is. 
\hr{Machai}{\Machai} might or might not be. 

The Heart of \Miith{} is connected with the \hs{Sun}. The Sun is the most obvious conduit for the Heart's life-giving power\dash but not the only one, nor the strongest. 

Perhaps the Heart was \hr{Voyagers create the Heart}{created by the \voyagers}. 









\subsubsection{Poetry about evolution}
Such is the history of \Miith{}, a crucible of life, a fierce and bright flame amid the darkness of the Cosmos. Whatever is given to her, she will smelt down and reforge into something greater. 

The void gave her lowly chemicals, and she gave birth to the \krakens{}, immortal and terrible. 

The \voyagers{} gave her fish and reptiles and mammals, and she made them into \caderyns, \nycans{}, \cortios{}, whales and elephants, creatures wild and strong. 

\Moroch{} took the fish-reptiles from the sea and created \nagae{}. \Miith{} took the \nagae{} and turned them into \dragons{}, majestic and proud. 

The \banes{} took the monkeys from the trees and created \humans{}. \Miith{} took the \humans{} and turned them into Vaimons, noble and arcane. 

Only time will tell what further wonders and horrors will spring from the womb of Mother \Miith{}, for time stands never still, and in her great forge, the fires burn ever hot\ldots{} 





\subsubsection{Fixed total power of the Heart}
Perhaps there is a certain fixed upper bound to him much power can be drawn from the Heart at one time. 

The \ophidian{} peoples are the prime consumers of this power. But since the \hr{Origin of Satharioth}{coming of the \satharioth}, the \resphain{} have been digging into it as well. The \dragons{} are bitter about this, because this steals some of the power that should be theirs. 

This is the real reason for the \hr{Feud}{\feud}: The two species fight for control of the power of the Heart. Both need it to keep their species alive and evolving. But they need the complete Heart. As long as it is divided, it is not strong enough. Therefore, they must fight until one side is annihilated. 

\Tiamat-tachi managed to expand the total power pool by drawing more \xsic{} power. But they also hogged a lot of it for themselves. 





\subsubsection{Mass extinctions}
Some of the great wars (like the two \Banewars) have tampered with the Heart and caused mass death among plants and smaller animals, because they were cut off from the Heart's life. 
This has caused more than one ecological catastrophe that laid waste to the planet. 





\subsubsection{Strong after the \firstbanewar}
\target{Heart after First Banewar}
After the \firstbanewar, \Miith{} was depopulated, but the Heart was still in a good shape. 
So there was energy enough to spawn many tens of thousands of \resphain. 
But near the end of \ps{\hr{Merkyrah}{\Merkyrah}} time, the \hr{Merkyrah strained the Heart}{Heart was getting over-strained}. 





\subsubsection{Weakening and dying after the \secondbanewar}
\target{Heart weakened}
At the time of the \thirdbanewar, the Heart was weakening and dying. 

This had multiple causes.

\begin{enumerate}
  \item 
    \hr{Immortality is an abomination}{Immortal souls steal power}. 
    The mere existence of the immortal and \hs{soul-eating} \resphain{} (and, to a lesser extent, \dragons) is an atrocity against the Heart and drains its power. 
    
  \item 
    The \draconic{} and \resphan{} \hr{Matrix}{\matrices} are fundamentally opposed, and their metaphysical struggle tears the Heart in two. 
    
  \item 
    The \hr{Crystal Sphere}{\CrystalSphere} kept \Miith{} \hr{Crystal Sphere isolates Miith}{hermetically sealed and isolated}. 
    This was constricting and strangling. 
    
  \item 
    \target{Shroud harms fertility}
    The \hs{Shroud} constricts and suffocates the Heart, making it hard for it to beat and flow and live. 
    
  \item 
    \hr{Iquin}{\Iquin} makes everything worse by gobbling up souls and hoarding them. 
\end{enumerate}

The \Miithians had fucked their homeworld over several times, and all the harm was cumulative. 
The Heart could not take much more. 

There were much bigger populations back in the days of \hr{Tembrae}{\Tembrae} (especially the immortal populations, but also the mortal ones). 
Nowadays the Heart is weaker and cannot sustain as many living creatures. 

\lyricslimbonicart{Last Rite for the Silent Darkstar}{
  Feel the heartbeat of the earth,\\
  as you're on the threshold to death or birth.\\
  Minds are tormenting, head is gone wild.\\
  Release yourself from what you can't abide.\\
  A star will also die \\
  on the beautiful moonlit sky.\\
  As the life is ended,\\
  the Goddess mother weeps her child.
}

The \banelords{} are not so concerned. 
True, the Heart is faltering. 
But it doesn't take much to stir up an ecosystem and make it unpleasant to live in. 
The \banes{} know that even though it seems like all of \Miith{} is drying up and dying and will be a dead wasteland within a thousand years, there is actually plenty of juice left in the Heart. 
If \Miith{} were to die of starvation, it would be a very long and slow death that could take millions of years. 
Civilizations and species are easy to wipe out; Realms are hard to kill. 
The \banelords{} know that there will be plenty of Heart power left for the \hr{Voidbringer}{\Voidbringer} to gobble up when he comes to devour the Heart (which he is supposed to do at the culmination of the \hr{Sephirah plan}{\sephirah{} plan}). 

Compare this to the game \cite{VideoGame:FinalFantasyVII}, where the evil corporation Shinra is draining the Lifestream dry by extracting all the \emph{Mak\=o}. 

\lyricstitle{
  \href
    {http://finalfantasy.wikia.com/wiki/Final_Fantasy_VII}
    {Final Fantasy Wiki: Final Fantasy VII}
}{
  Shinra [\ldots{}] profits from the use of machines known as \quo{Mako Reactors}. These reactors siphon a special type of energy\dash called \quo{Mako}\dash out of the Planet and convert it into electricity. One of the by-products of the extraction and refinement of Mako energy is materia, a concentrated form of Mako which allows the owner to use its magical properties. [\ldots{}]
  
  In actuality, Mako energy is drawn from the Lifestream, a flow of life-force beneath the surface of the Planet. All life originates from the Lifestream, and returns to it upon death. In short, the Lifestream is the sum of all the life that has ever and will ever walk upon the Planet. The process of extracting Mako energy literally drains the life of the Planet in order to generate electricity. This can be seen quite clearly in the Shinra's capital city of Midgar, where the eight Mako Reactors have sucked out so much of the Planet's life-force that the area is covered in perpetual darkness and no plants can grow.
}









\subsection{The Dark Heart of \Miith}
\target{Dark Heart}
\index{Dark Heart of \Miith}
The Dark Heart of \Miith was the \dweomer of the \hs{World-God} of \Miith. 
It was left chained and rotting when \hr{Voyagers slay the World-God of Miith}{the \voyagers slew the World-God}. 
The \hr{Heart of Mith}{Heart of \Miith} was a parasite that lived by draining the energy of the Dark Heart. 













\section{\Iquin and the \Sephiroth}
\target{Iquin}
\Iquin{} is a \hr{Dweomer}{\dweomer} that drawn power both from \Erebos{} and from the Heart of \Miith{}. 

It is the force of \quo{Light} in \hs{Vaimon} metaphyics. By the \hs{Iquinian Church} viewed as the source of all good and worshipped as a divine force. Its manifestations are the \hr{Sephiroth}{\Sephiroth}. 

In a sense, \iquin{} is a \emph{face}: 
A humanoid, benevolent-looking mask strapped on to hide the true underlying darkness, which is as faceless and inhuman as a \bane. 








\subsection{History}
\subsubsection{\Esheram}
When \hr{Origin of Resphain}{the \resphain{} were first spawned}, \itzach{} was developed and improved by \hr{Semiza}{\Semiza} and the early \resphain{} (who were \hr{Entropy}{more creative than the \banes}). 

Then \hr{Resphain lose contact with Banelords}{disaster struck} and the \resphain{} lost not only the contact with \Semiza{} and the \banelords, they also lost their memory. 
They founded \hr{Merkyrah}{a good empire}, and they were noble and good. 

So they shaped their own \dweomer, \hr{Esheram}{\Esheram}, which they \hr{Good Resphain and God}{personified as a god}. 

After the \hr{Resphan rebellion}{\resphan{} rebellion}, \Esheram collapsed.
The \resphain embraced \itzach. 





\subsubsection{\Kezeradi{} incarnation of \iquin}
\target{Kezeradi Iquin}
When \Kezerad{} was formed, the \Kezeradi{} took up \iquin{} again. 
But they improved and refined it by incorporating technology gleaned from the \ophidians{} and the \hr{Ophidian power source}{natural \Miithian{} power source they used}. 

This new \iquin{} was designed by genius scientists such as \hr{Eryal}{\Eryal}. 
\hr{Sithiyacaan}{\Sithiyacaan} helped by providing brute-force backup.  

\hr{Daggerrain}{\Daggerrain} saw this \dweomer{} and realized it could be useful to him. 
Eventually \hr{Fall of Kezerad}{\Kezerad{} was destroyed} and their \iquin{} became twisted by the \sephiroth{} into the \iquin{} that the Vaimons would later use. 





\subsubsection{Creation of the \sephiroth}
The sixteen \Sephiroth{} were originally created from the souls of sixteen rebellious \resphan{} lords, each merged with the soul of a sacrificed \banelord. 

These \resphain{} were the lords of the rebellious \Kezeradi. After the rebels' defeat, the \banes{} (or \bane-allied \resphain) decided that using their leaders as \Sephiroth{} would not only be an effective and useful tool, but also a suitable punishment: They would live on to see the virtues they fought for corrupted and perverted, and their own power would be used to achieve it. 

A theme throughout the series is that some of the characters gradually discover the nature of the \sephiroth. 
Some work actively to destroy the \sephiroth, thus freeing the souls of the captive \Kezeradi{} lords. 





\subsubsection{Religious beliefs}
For Iquinian religious/mystical beliefs about the \sephiroth, see the section on the \hs{Iquinian Church}. 









\subsection{How it feels}
For \humans{}, \iquin{} is the ultimate: 
Highest, deepest, brightest, darkest.
Most beautiful, most terrible. 
Most alluring, most abhorrent. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  God is nothing if He is not, in every sense, the surpassing God;\\
  In the sense of common everyday being, in the sense of dread,\\
  Horror and impurity, and, finally, in the sense of nothing\ldots{}
}





\subsubsection{How it feels to die}
Dying and going into the light feels like this:

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  Close your eyes, fall into deep\\
  Within this place where secrets hide\\
  The perfect heart, it's behind closed doors\\
  I don't want it to hide\\
  SOS. Help me, I'm falling\\
  into the perfect heart\\
  The perfect heart
}

When a \human{} meets \iquin, he sees a brief, vague glimpse of mankind's true nature, origin and purpose. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  Whispering thoughts of ages untold\\
  Think of what it tells you\\
  Lost tales of ages past\\
  The whispering winds are roaming fast\\
  Oh so fast
}





\subsubsection{How it feels to learn the truth}
\target{How it feels to learn Iquin is evil}
When someone discovers the truth about how \iquin{} is evil, describe the disappointment and disillusioning they feel to discover that they have been betrayed and misled.
That the religion which they followed and obeyed all their lives, that which they thought to be the source of all good, turns out to be evil; a parasitic bloodthirsty abomination, a \trope{CosmicHorror}{Cosmic Horror}. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Perfect Dark%
}{
  Follow the philosopher\\
  Is he God or Lucifer?\\
  It's written in the sky\\
  A prophecy for you and I 
  
  Electrical insects\\
  With nowhere to go 
  
  Asking the question why\\
  Religion might just be a lie\\
  Believer, take your fix\\
  Crawl up on your crucifix 
  
  I've found the answer\\
  I have the key\\
  Experience reality\\
  And the world will see \\
  That it's perfect dark\\
  It's perfect dark here\\
  In the Devil's hall of fame 
  
  Before me now I see a dying planet\\
  Captured souls with microchips implanted\\
  And it's perfect dark\\
  In the Devil's hall of fame \\
  There must be a way\\
  I'm waiting, waiting for the day\\
  Hellfire. Hellfire. \\
  Higher. Higher. \\
  Only blood remains\\
  There is nothing more to gain
}





\subsubsection{How it looks}
\target{Iquin through the Shroud}
When \iquinian people were viewed by someone who could see through the Shroud, they sometimes appeared faceless (like \banes) and bound with great chains that trailed away into nothingness. 

The purpose of \iquin was to tie people together. 
When an \iquinian saw through the Shroud he would sometimes see his dead family and friends as ghosts, tied to him by chains. 








\subsection{Parasitism}
\target{Parasitic Archons}
The \Archons{} are parasites. 
The \sephiroth{} \hr{Life drain}{drain life force} from worshippers, collecting it as a kind of \quo{tax}. 
Some of that force they allow Vaimon mages to channel. 
So Vaimon magic is powered by other people's stolen life force. 

Similarly, the reason why Vaimons \hr{Vaimon healing}{have such powerful healing magic} to offer is that they unwittingly feast on stolen lifeforce. 

This has global effects. 
In times where Vaimons expend great amounts of magical energy, this toll must be collected from the populace. 
This results in epidemies. 
People will fall sick with leprosy, limbs rotting and falling off. 









\subsection{The \Iquin plan}
\target{Sephirah plan}
\target{Iquin plan}
The \sephiroth{} were envisioned after the \hr{Cabal}{Cabalists} were disappointed in \humans. 
The \human{} race \hr{Humans are a failed slave race}{was a failure to begin with}, and the Cabal's many attempts to refine and improve them had met with little success even after thousands of years. 

So they devised a new and better way to use the \pps{\humans} soul power. 
They designed the \sephiroth{} to \hr{Sephirah soul prison}{act as a \carcer} that would suck up \human{} souls, and also bind living \humans{} to it. 
This would enable the Cabal to use the collective willpower of all the \humans{} as a \vertex. 
Granted, each \human{} will is pathetic, but bundle enough of them together and you have a formidable \vertex. 

\Iquin{} is thus a giant machine using living and dead humanoids as its nuts, bolts and cogs. 
It gives the \human{} race a purpose, a use, a meaning to their otherwise pointless, worthless existence. 

\Iquin{} was designed with \humans{} in mind, but it turned out to be simple to generalize it to work on \scathae{} and other humanoids as well. 
This was a bonus effect. 





\subsubsection{The \Resphan{} Purpose}
Apart from the planned climactic finale with \hr{Lithrim}{\Lithrim}, the \iquin{} plan also tied into the \hr{Resphan purpose}{\resphan{} \quo{purpose}}. 
It helped their race grow stronger and stronger, towards perfection. 





\subsubsection{\Noggyal connection}
\target{Iquin and Noggyaleth}
The \iquin plan was connected to the \hr{Noggyal burrowing}{burrowing of the \noggyaleth}.





\subsubsection{The \Morbus is the next step}
The \hr{Morbus}{\Morbus} is the next phase of the masterplan of which the \sephiroth{} are a part. 
In a sense, the \Morbus{} is the next \quo{generation}: 
A faster, even more efficient version of \iquin, a new and improved way to harvest \humans{}. 

It is still experimental, though. 





\subsubsection{Final purpose}
\target{Final purpose of the Sephiroth}
The {\Sephiroth} have a grand purpose. Like every other aspect of the Cabal's moves orchestrated by \hr{Daggerrain}{\Daggerrain}, the \sephirah{} project has all been in preparation for the final climax and the opening of the gate to \hr{Erebos}{\Erebos}. 

\Daggerrain{} is planning a great final ritual in which all of the combined Shroud-weaving energy contained within the \Sephiroth{} will be unleashed in a cosmic explosion of \vertex{} power that will tear the Shroud asunder and fling wide the dimensional gateway to \Erebos.

I need to build up to this throughout the entire series. Cabalists drop hints here and there, while the Sentinels suspect and attempt to piece together the puzzle.

Compare this legion of bound dead to Hood's army in \cite{StevenErikson:TolltheHounds}. 

\lyricsbs{Emperor}{Night of the Graveless Souls}{
  When night comes creeping in, \\
  dark restless shades arise. \\
  Graveless souls are gathering. \\
  Seem to ignite the flame. 
  
  Creeping shadows roam the night, \\
  as a merciless rain is closing upon.\\
  Demons coming to sever the Sun. \\
  Empty eyes come to life. 
  
  Darkness reigns in the Cosmos. \\
  Forces of the Devil's lair. \\
  Innocent or brave, \\
  they appear to rape your world. 
  
  Children of the evil and demonic\\
  curse his love again. \\
  Graveless souls awake, \\
  seem to ignite the flame. 
  
  When night comes creeping in, \\
  dark restless shades arise. \\
  Prepare to crawl and run. \\
  The Black is here tonight.\\
}






\subsubsection{\Carcer}
\target{Sephirah soul prison}
\index{\carcer!\iquin}
%The \sephiroth{} are a soul prison. 
\Iquin{} is a \carcer{}. 

\lyricslimbonicart{Grace By Torments}{
  Underneath the ice of winter\\
  there is a stream so powerful.\\
  A dark river that will swallow your soul.
  
  As it twists into form,\\
  you dwell in a cold dark void.\\
  Frozen and lifeless dreaming,\\
  deep down in the darkness screaming.
  
  When pain comes to power,\\
  all the sorrows of the heart\\
  leading your soul astray\\
  to a realm of agony.
  
  All you have left is death's desire for you.
  
  A black hole.\\
  Well of souls.\\
  Icy breath.\\
  Stone cold death.\\
  Darkness calls\\
  as Heaven falls to Earth.
}

\lyricslimbonicart{Seven Doors of Death}{
  Asylum of neurotic minds.\\
  Devour all consciousness.\\
  Insanity is there to find.\\
  Dominion of darkness.
}

\lyricsdimmuborgir{Mourning Palace}{
  Daylight has finally reached its end,\\
  as evenfall strikes into the sky.\\
  Far away in the dark glimpsing moonlight,\\
  sickening souls cry out in pain.
  
  Hear the cries from the Mourning Palace.\\
  Feel the gloom of restless spirits.\\
  Hear the screams from the Mouring Palace.\\
  Feel the doom of haunting chants.
  
  Eternal is their lives in misery.\\
  Eternal is their lives in grief.\\
  Abandoned in a void of nothingness.\\
  A chain of anger, a fetter of despair.
  
  In this garden of depraved beings,\\
  this unsacred place of helpless ones,\\
  Satan blessed the creatures,\\
  enswathed them in endless night.
}

\Iquin{} turns \humans{} into hapless slaves from birth. 
They have no control over their lives and exist only to be used. 

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Born aware, yet destined not to be.\\
  To an entity of pain you serve.\\
  Take from the light, nourishment through spite.\\
  Depleting human decree. \\
  Chronic infection through a sickening will, \\
  the many that stain this Earth.\\
  It doesn't matter who must suffer\\
  when the sickness claims rebirth. 
}

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  The Shrine of Mad Laughter
}{
  A sensation of everlasting rot and those frantic wails.\\
  No, it is not a fall into the abyss.\\
  The defiance of descent, a coronation beyond liberty and slavery.\\
  The cry of woe and deliverance exudes a flame, \\
  evasive as sound and ether.\\
  An instant of collusion with death, without hope nor prospect.
}









\subsection{\Sephiroth}
\target{Sephirah}
\target{Sephiroth}
The \Sephiroth{} are the \Archons{} of Iquin.
 They can be invoked to cast magic. 
There are sixteen of them. 
The \Sephiroth{} are associated with four \quo{\hs{elements}}. 
Each \Sephirah{} also personifies a virtue that is considered sacred to the \hs{Iquinian Church}. 

What is not taught in Iquinian theology is that these virtues are actually meant not to benefit the people but to control them. 
They are tools designed by the \banes{} to enslave the \humans{} and use them in their war against the \dragons. 

The \Sephiroth{} are not \vertices{} individually, because they are half-mindless slaves, lacking the force of personality to become true \vertices. 
Rather, \iquin{} as a whole is one immense \vertex{}. 

Each \Sephirah{} is associated with a \quo{virtue}. 
These virtures are actually evil and used to control men. 

\lyricsbs{Exmortem}{Fix of Negativity}{
  The world is swept in a curtain \\
  from the rottenness of Man. \\
  Fixing decadent values. \\
  Miserable mortals, open your eyes. 
}

\target{elements}
\target{pillars}
The \Sephiroth{} are divided into four \quo{elements} or \quo{pillars}. 
These are four integral components of the mind, and, in a sense, of the universe as a whole. 
The elements are things that can be hyped up in propaganda as being virtues, the source of all good, but can also easily be subverted and twisted into a source of evil. 

The pillars were originally the four \hr{Kezeradi beacons}{\beacons} of \Kezerad. 

The pillars are: 

\begin{description}
  \item[Passion:] 
    The deep, heartfelt belief in a cause and the burning desire to fight for it. 
  \item[Eye/Vision:] 
    The Eye lets you perceive and interpret the world: In a \quo{true}/\quo{good} way, or as a veil of lies, seeing only what you want to see (or what your masters want you to see).
  \item[Voice:] 
    The Voice that lets you communicate with your fellow beings, to offer wisdom and comfort, or to condemn and spread hate and lies. 
  \item[Tears:] 
    Tears of joy, or tears that release sorrow and help you deal with it. Or tears that confirm your sorrow and only serve to pull you deeper into a mire of suffering. 
\end{description}

Another schema might be that of four basic emotions:

\begin{description}
  \item{Anger:} Defense, expansion.
  \item{Fear/pain:} Self-preservation.
  \item{Hunger:} Self-improvement.
  \item{Lust:} Procreation. This one can be sublimated into an urge to create other things than progeny, such as art, or an empire.
\end{description}








% Each Sephirah has: A name, a classical element, a power, a virtue and an explanation. 
\newcommand{\sephitem}[5]{#1 (#2) & #3 & #4 & #5 \\\hline}

\newenvironment{sephirahlist}[1]{%
  \begingroup
  \scriptsize
  \begin{figure}
  \caption{\Sephiroth{} of #1}
  \begin{tabular}{|c|p{4cm}|c|p{6cm}|}
  \hline
  \textbf{Name} & \textbf{Power} & \textbf{Virtue} & \textbf{Description} 
  \\
  \hline
  \hline
}{%
  \end{tabular}
  \end{figure}
  \endgroup
}





\begin{comment}
\subsubsection{\Mor, the Eye}
\end{comment}
\begin{sephirahlist}{Eye}
\sephitem
  {\Cushed}
  {\male}
  {Used to shape, move and Sculpt earthen objects.}
  {Lawfulness}
  {Helps the rulers keep people in check. }
\sephitem
  {\Omariel}
  {\female}
  {Cures pain (but does not heal wounds).}
  {Acceptance}
  {Makes people accept hardship and oppression.}
\sephitem
  {\Yemared}
  {\female}
  {Cause paralysis.}
  {Tradition}
  {Prevent rebellion and keeps the social order stable and static.}
\sephitem
  {\Yeziel}
  {\male}
  {The Coronet: Protects against magical attacks.}
  {Chastity/Purity}
  {Sex is a dangerous thing, because it may open people's eyes to the \hs{Beyond}. Also, it makes them harder to control. Also, \human{} sexuality is something the \banes{} very much want to harness and control, so they need \Yeziel{} to keep people's sexuality in check. }
\end{sephirahlist}




\begin{comment}
\subsubsection{\Shiram, the Passion}
\end{comment}
\begin{sephirahlist}{Passion}
\sephitem
  {\Barion}
  {\male}
  {The Shield: Protects against melee attacks.}
  {Courage}
  {Encourages the people to fight against the enemies of the Church.}
\sephitem
  {\Hoshied}
  {\male}
  {The Battlement: Protects against targeted ranged attacks.}
  {Loyalty}
  {Keeps people under control and discourages them from asking questions.}
\sephitem
  {\Razilah}
  {\male}
  {Create lightning.}
  {Righteousness}
  {Opposes any kind of heresy, blasphemy and unorthodoxy; crusades against the heathens.}
\sephitem
  {\Teshiron}
  {\female}
  {The Rampart: Protects against area-of-effect attacks.}
  {Faith}
  {Keeps people loyal to the Church and not asking unwanted questions.}
\end{sephirahlist}





\begin{comment}
\subsubsection{\Urisol, the Tear}
\end{comment}
\begin{sephirahlist}{Tear}
\sephitem
  {\Feazirah}
  {\female}
  {The gentle wind.}
  {Humility}
  {Keeps people pacified and keep them from complaining.}
\sephitem
  {\Gamishiel}
  {\female}
  {}
  {Sacrifice}
  {Make people work hard for their masters and not expect any rewards. (Her month is only 20 days long.)}
\sephitem
  {\Hapheron}
  {\male}
  {}
  {Solidarity}
  {Hate of outsiders. Turns the Iquinians, and all \humans, into a united front against their enemies.}
\sephitem
  {\Ishiel}
  {\female}
  {Healing}
  {Patience}
  {Makes people accept hardship and oppression.}
\end{sephirahlist}





\begin{comment}
\subsubsection{\Zumir, the Voice}
\end{comment}
\begin{sephirahlist}{Voice}
\sephitem
  {\Atzirah}
  {\male}
  {The carrying wind. Used for lifting objects or flying.}
  {\Honour}
  {Keeps people inside the system for fear of dishonour while encouraging them to strive to please their masters and the Church.}
\sephitem
  {\Izion}
  {\male}
  {Creates blasts of fire. Perhaps the \Sephirah{} most commonly used in combat. }
  {Justice}
  {Destroys the wicked: Sinners, and the enemies of the church.}
\sephitem
  {\Keshirah}
  {\female}
  {The powerful wind. Used to create controlled gusts of wind. }
  {Dilligence}
  {Makes people work hard for their masters.}
\sephitem
  {\Thimared}
  {\female}
  {Limited mind control.}
  {Obedience}
  {Turn people into humble slaves. Keeps the masses from rebelling and rulers from sympathizing.}
\end{sephirahlist}







\subsection{The \Morbus: The next phase}
\target{Morbus}
\target{Disease}
A long-running theme: 
There is a ghastly, leprosy-like disease spreading like an epidemic through slums all over \Azmith, transforming people into the living dead. Or maybe into \hr{Lictors}{Lictor-like people}. 

The \Morbus{} strikes the hopeless, the disenfranchised, the weak-willed. It is a manifestation of the newest stage/phase of the \hr{Sephirah plan}{\sephirah{} plan}, and of the \hr{Return of the Banelords}{return of the \banelords}. 

In some parts of \Azmith, the \Morbus was simply called \quo{the Disease}. 
Rian \hr{Rian sees the Morbus}{sees it in \Malcur}, and Carzain \hr{Carzain sees the Morbus in Forklin}{sees it in \Forklin} and \hr{Carzain sees the Morbus in Redce}{later in \Redce}. 

Compare to Calcutta in \authorbook{\PZBrite}{Calcutta, Lord of Nerves}. And also \authorseries{Paolo Eleuteri Serpieri}{Morbus Gravis}. 

The \Morbus{} is strongest in the city slums, because these provide an easier link to the cities of \Nyx, and through them, \Erebos. Compare to the RPG \emph{Kult}, where slums are gateways to Metropolis, the eternal city\dash a morbid, decaying ruin. 

The \hs{Cult of the Worm} seek to utilize the \Morbus{} and twist it for their own purposes. 

\lyricsdimmuborgir{Blessings upon the Throne of Tyranny}{
  Infected by invalid behaviour,\\
  while capturing the stench of divine putrefaction.\\
  Confess to slavery for the world saviour.\\
  Give praise and inhale the corruption.
  
  The Enfeebled provides the fool.\\
  The Disabled provides the tool.\\
  The Apathetic demands the affection\\
  to those suffering from their own satisfaction.
}

\lyricsdimmuborgir{Architecture of a Genocidal Nature}{
  Devouring their flesh with a razorblade smile.\\
  Genes would still blindly carry on smouldering ember of Hell.\\
  Limned with gold leaf, the scarlet brush\\
  that sweeps all traces of time, place and pattern.
}

\lyricsbs{Exmortem}{Fix of Negativity}{
  We live in the noise and the dirt, the real life angst, \\
  filth and desperation, a portal of misery. \\
  The ultimate demonic playground.
  
  The world is swept in a curtain \\
  from the rottenness of Man. \\
  Fixing decadent values. \\
  Miserable mortals, open your eyes. 
}

The \Morbus{} feeds on \human{} emotions (\hs{Chaos} lifeforce, from the Heart of \Miith{}). It draws strength from \human{} evil and suffering. 

\lyricsdimmuborgir{Puritania}{
  I am war, I am pain.\\
  I am all you've ever slain.\\
  I am tears in your eyes.\\
  I am grief, I am lies.
}

\lyricsdimmuborgir{Eradication Instincts Defined}{
  Human depravity is at our disposal \\
  as the perfect tool to destroy mankind, \\
  the worst kind of them all. \\
  Modern times' ignorance, the world disease.\\
  Appeal to death of every man.
  
  A living hate smoldering abyss,\\
  nurtured through centuries with quietly exercised wrath, \\
  seeks the easiest way to the feed the engine, \\
  praising the final bloodbath.\\
}

\lyricsbs{Exmortem}{Human Rape Symphony}{
  I'm free floating cyanide, \\
  infesting the corpus collectivus. \\
  Admiring the obscure human rape symphony. 
  
  Ripened by their own corruption. \\
  Drown in your own shitty lives. \\
  Promoter of decadence. \\
  Distributor of pestilence.
  
  The pathetic stupidity of mankind. \\
  Humanity crawling on its knees. \\
  Corrupt and parasitic elements. \\
  All idylls must end!
}

\lyricsbs{Monolith Deathcult}{
    1917 - Spring Offensive (Dulce Et Decorum Est)}{
  The mindrape of the spectacle of dehumanization.\\
  Viral god wields his festering scythe of gangrene.\\
  By endless flashes of mortar or the cadaveric stench.\\
  Ghostly faces peer through the veil of celluloid.
}





\subsubsection{The plan}
The disease is called the \Morbus. 
It is a plan envisioned by \Daggerrain{} as a means to harvest \human{} souls and lifeforce and harness them as a \vertex. 
It is a further development of the \sephiroth: 
A faster, meaner, uglier version of \iquin. 

The \Morbus{} is meant to practically exterminate the \human{} race, engulf them, suck them dry and leave them \hr{Life drain}{drained} and empty of all their life and \vertex{} willpower. 
Then use them as a big \vertex{} under \ps{\Daggerrain}{} control. 

\lyricsdimmuborgir{Puritania}{
  Let chaos entwine on defenseless soil.\\
  Remove errors of man and sweep all the weakening kind.
  
  Bygone are tolerance and presence of grace.\\
  Scavengers are set out to cleanse the human filth parade.
}

The \banelords{} realize that having the \humans{} live and then die (and be absorbed into \iquin) is a waste. 
They might as well kill them, or turn them into semi-undead. 
Enter the \Morbus. 

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Upheaving desire, heinous in its wake.\\
  Abandonment of life, this baneful mistake. \\
  Sickness now unfolds in you. To death you beseech.
}

The \Morbus{} is a prelude to a planned global epidemy of madness and mind-wrought destruction that is intended to sunder the Shroud and the barriers between \Miith{} and \Erebos. 

\lyricsbs{Vital Remains}{Born to Rape the World}{
  Untouched by grace. Fallen are the messengers. \\
  Hymns of the profane unheard by the pious. \\
  Revere the inverted hypocrite\\
  as we breed to the sound of the hammering nail.
  
  Befoul the teachings of divinity. 
  
  Words shall unveil the silent truth,\\
  like razors through the flesh of the divine,\\
  severing the artery from God.\\
  Abandoned and devoured by the larvae of those who abhor. \\
  Distant lull deep in the subconscious.\\
  Unstoppable urge, uncontrolled, now coming to the surface.\\
  Their eyes are blind, but the dead shall always see\\
  the coming entity.
  
  All will witness as the undeniable truth unfolds. \\
  For they now know the truth that Heaven is no more. 
}

They mean to bring madness, suffering and ecstasy and force people's minds out of their comfort zones. 
Over the course of \booktitle{\SentinelsofMith}. 







\subsubsection{The afflicted}
When you look at the leper-like people afflicted by the \Morbus, they radiate all the world's emptiness, cruelty, lifelessness and neverending cold darkness. 

When you look into their eyes, the darkness and emptiness goes on forever with no bottom. Like abysses\dash portals to the true Abyss that is the endless universe. 





\subsubsection{Superstition}
Some of the afflicted turn to superstition. 
They believe that the \Morbus{} is a divine punishment, and that they must pray and believe extra hard in order to atone. 
Of course, this only makes matters worse (or better, from the Cabalists' POV). 

\lyricsbs{Hate Eternal}{Whom Gods May Destroy}{
  Afflicted by this scourge, \\
  the great plague that shall befall upon us,\\
  we are of disease, of destiny.\\
  We must become one with our gods, \\
  whose massive fury shall scorch this Earth,\\
  for we are all destined to oblivion.
}







\subsection{\Lithrim: The purpose of Man}
\target{Purpose of Humanity}
\target{Lithrim}
\index{\CrystalSphere}%
\index{\Lithrim}%
\Iquin{} and the \Morbus{} were stages in the plan, but what it all revolved around was \emph{\humanity{} itself}. 
The \human{} race was created not just to be slaves and breeders. 
They were made to form one huge species-wide \matrix{} that, when the time was right, would break open the Shroud and shatter the \CrystalSphere. 

\Humanity{} had a hidden \matrix{} that connected and empowered them all. 
This \matrix{}, feeding off the Heart of \Miith{} and drawing some power from \Erebos, gave the \humans{} their lifeforce, virility, fertility and zest for life. 
It also gave them their antisocial, destructive and self-destructive petty impulses (which \scathae{} did not have to quite the same degree).

\Humans{} were separated in individual bodies, but they had the potential to become one big god, \Lithrim: 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Everything, except God, \\
  has in itself some measure of privation.\\
  Thus all individuals may be graded \\
  according to the degree to which they are infected \\
  with mere potentiality.
}

\Lithrim was mostly an insubstantial, spiritual being; a \matrix. 
But it also had a physical manifestation (or more than one) as a gigantic, pale, fleshy thing. 
Amorphous, yet still somehow loathsomely \human. 
Perhaps with bits of \human faces and limbs sticking out, and huge \human or quasi-\human looking faces forming at random on its surface. 

The \Lithrim was an \hs{Atrocity} of the \SitraAchras, one of the \banes' superweapons. 





\subsubsection{First Advent of \Lithrim}
\Lithrim was a \bane god of destruction. 
It appeared for the first time during the \hr{Cuezcan Apocalypse}{\CuezcanApocalypse}. 
This time \Lithrim was defeated, and the \dragons believed it was gone for good. 
But it was not. 

Read about this in \hr{First Advent of Lithrim}{the relevant section}. 





\subsubsection{Clean \humans}
\target{Clean Humans}
The essence of \Lithrim was carried inside \humans.
It began when the \hs{Men of Light} were \hr{Men of Light created}{created}. 
They then spread their genes all over the place. 
Soon almost all \humans carried the gene that connected them to the \Lithrim \matrix.

Not all, though. 
There were some \humans who were \quo{\hr{Clean Humans}{clean}}, in the sense that they had no blood of the {\hs{Men of Light}} and thus did not carry \Lithrim inside them. 





\subsubsection{Second Advent of \Lithrim}
In the end, in the \thirdbanewar, all \humans{} were forcibly merged into one huge mindless superbeing:
\Lithrim, the manifestation of all \humanity{} combined. 
 
Then the plan failed and \humanity{} died out. 
At the end of the \thirdbanewar, there might have been a few straggler \humans{} still alive, but the \matrix{} that empowered their race was destroyed, so the survivors would most likely waste away\ldots{} or devolve into inhuman vermin. 

Compare to the anime \cite{Anime:NeonGenesisEvangelion}, where Ikari \Gendou's \quo{Human Instrumentality Project} aims to dissolve the AT Fields that keep \human{} beings apart as separate beings with individual bodies and minds, so as to merge all of \humanity{} into one Angel-like creature. 

The \Lithrim was a special \hs{Atrocity}. 
It was a conduit to Erebos, but it was also tied to \Miith, and therefore it could exist and manifest on \Miith and thus form the gateway to Erebos.

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  \Hetoimasia
}{
  For man is the key and man is the device\\
  And out of his ranks shall arise the saviour \\
  draped in the blood of the unborn
  
  But mankind was the prism to the quintessence of corruption\\
  Contemplate and say, what is earth, \\
  else than a frenetic psalmody for His venue?\\
  What joy and glory shouts he who bears the mark of the Beast\\
  Consumed and eaten have been the abundant abortions of mankind, \\
  but now, none of them, humans, shall remain \\
  but what birds could not carry off in their claws!
}





\subsubsection{How it feels}
This strange nature as pieces of a divided god was one of the reasons why \humans{} often felt emo and out of place. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Man, lost somewhere between the restrictive force\\
  Of Cain and the expansive force of Abel,\\
  Falls from his median position between Angel and Beast\\
  Each time he ceases to desire a being superior to himself\\
  Adam's descent into materiality,\\
  May it be questioned\ldots{}\\
  The separating line between the Saved and the Damned,\\
  May it be questioned\ldots{}
}

Instinctively, deep down, \humans{} had a vague feeling of their true nature, bond and purpose. 
They feared it. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  If there is nothing that surpasses \\
  our powers and our understanding,\\
  If we do not acknowledge something greater than ourselves,\\
  Greater than we are despite ourselves,\\
  Something which at all costs must not be,\\
  Then we do not reach the insensate moment \\
  towards which we strive with all that is in our power \\
  and which at the same time\\
  We exert with all our power to stave off
}

Occasionally they would catch a glimpse of \Lithrim through their \hr{Human racial memory}{racial memory}.
All \humans had an instinctive memory of a colossal god that came to dissolve the sinful world of matter, to sunder all chains and lead all \human souls to the eternal and infinite city of the One Light, a city of shining towers that touched the sky. 
(The last part was obviously an image of \Nyx.)
This was \Lithrim, the god who opened, \emph{was}, the way to \Erebos.
All \humans instinctively knew that their souls were entwined with this god, the Greatest One.

\citeauthorbook[p.327]{WilliamJones:DepthofDarkness}{William Jones}{%
  Depth of Darkness
}{
  Jason stumbled backward, a numbing blackness swagglign his mind, obscuring the world.
  In a void, he drifted, replaying memories that were not his\dash that were not \human.
  An infinite abyss convulsed before him, squirming and twisting, uniting into a vile scene reaching back to an unfathomable time, where alien creatures created and destroyed life, using and discarding it with cold indifference. 
}

\citeauthorbook[p.143--144]{TimCurran:Hive}{Tim Curran}{Hive} {%
  \talk{I'm not me anymore, Jimmy, \emph{I'm one of them}!
    One of them spreading my wings and swimming and diving through those pink honeycombs and knowing what they think like they know what I think\ldots{} we\ldots{} we're going to\ldots{} \emph{yes!}
    That's the plan, isn't it? 
    That's always, always, always been the plan\ldots}
    
  \ldots
  
  \talk{%
    We're rising now\ldots{} the hie is rising now\ldots{} through the water and ice into the green glowing sky\ldots{} thousands of us into the sky on buzzing wings, thousands and thousands of wings.
    We are the hive and the hive is us.
    We are the swarm, the ancient swarm that fills theskies\ldots}
  
  \ldots{}
  
  \talk{\ldots{} we all dream toether through the long, black night that goes on and on and on\ldots{} nothingness\ldots{} emptiness\ldots{} only the long, empty blackness\ldots}
  
  \ldots
  
  \talk{Dead\ldots dead\ldots nothing. 
    But the hive, the hive can seed it\ldots}
  
  Lind's eyes were now black and soulless and malevolent, fileld with a dire alien malignancy.
  They were black and oily, yet shining brightly like tensor lamps.
  They found Hayes and held him.
  And those eyes, those bleeding alien cancers, they did not just look through him, they looked straight into the center of his being, his soul, coldly appraising what they found there and contemplating how it could be crushed and contained and converted into something else.
  Something not human, something barren and blank, something that was part of the hive.
  
  Hayes screamed\ldots feeling \emph{them}, those ancient minds coming at him like a million yellowjacket wasps in a wind tunnel, punching through him and melting away his soul and individuality, making him part of the greater whole, the swarm, the swarm-mind.
}

\citeauthorbook[p.161]{TimCurran:Hive}{Tim Curran}{Hive}{%
  These man at the outpost had drilled into a chasm, yes, but it hadn't been just any chasm, but maybe a burial chamber of the Old Ones.
  And opening it had been like cutting the scab off some primordial, invidious wound.
  And the pus that leaked out was infection and evil, a wasting pestilence in the form of alien memories and undead essences, a decayed intelligence that was stil lvirulent after all those uncounted eons, a spiritual contamination that took their minds one by one by one.
  Making them something less than \human, something ageless and undying, a cosmic horror. 
}





\subsubsection{Mythology}
\Lithrim was the truth behind the \hr{Iquinian eschatology}{Iquinian beliefs about an Apocalypse}. 





\subsubsection{Secrecy}
\target{Lithrim was secret}
\Lithrim was a secret. 
Its true purpose was known only to the inner circles. 
The name was known to many Cabalists, but most thought \Lithrim was just a metaphor or abstraction. 
Most did not suspect so cataclysmic a result. 
















\section{\Itzach and the \Qliphoth}
\target{Itzach}
\Itzach, the \quo{Outer Darkness}, was a \hr{Dweomer}{\dweomer} created by the \hr{Banes}{\banes} as a \hs{front-end} for the power from \Erebos. 
\Itzach was raw \bane power, whereas \iquin was filtered \bane power. 

\Itzach was the \dweomer which the \resphain themselves used. 
But they did not want mortals using \itzach, because \itzach was volatile. 
They could control the mortals much better through \iquin. 
So in \hs{Vaimon} metaphysics \itzach was reviled as the source of all evil. 

% Originally, the \banes{} relied on magic that drew its power from \Erebos{}. 
% But when \Miith{} and \Nyx{} was sealed off from \Erebos{} at the end of the First \Banewar, the \banes{} lost the source of the magical power and were left crippled, and the \dragons{} and their minions were easily able to slaughter the millions of \banes{} still on \Miith{}. 
% Daggerrain and some other \banelords{} survived and were able to hide. 
% Deprived of their magic, they had to develop a new magic theory. 
% So they came up with \itzach{} theory, which is some principles from old \bane{} magic theory combined with some Chaos theory. 
% So \itzach{} is a chaotic force, and the \Kliffoth{} are more or less the same as the \hr{Daemon}{\daemons} which Chaos magicians invoke. 

But the \banes{} wanted a better tool to control their \humans{}. The problem was that if you taught \itzach{} magic to \humans{}, it tended to reinforce their chaotic nature and make them difficult to control. But without magic at all, the \humans{} were wimps. 
And so they created \hr{Iquin}{\Iquin}. 








\subsection{List of \Qliphoth}
\target{Qliphoth}
\target{Qliphah}
The manifestations of \itzach were the \hr{Qliphah}{\Qliphoth}. 
Each \qliphah was actually a \banelord. 

\target{Circle of Noon}
\target{Noon Circle}
\index{Noon Circle}
\index{Circle (in Vaimon mysticism)}
At least 100 \qliphoth{} are known and named. 
They are categorized into a number of \quo{Circles}. 
(Following this system, the \hr{Sephiroth}{\Sephiroth} are sometimes considered the Circle of Noon.) 

The darkest circles are feared as bringers of madness.

\lyricsbs{Aleister Crowley}{%
  Liber Aleph vel XCI 
  (Chapter 92: 
   De Aquila Sumienda/On Consuming the Eagle)
}{
  \ldots{} then is thy Danger fearful and imminent, for it is the Edge of the Abyss of Choronzon, where are the lonley Towers of the Black Brothers.
}





\begin{subgloss}
  \begin{comment}
  \paragraph{Circle of Dusk}
  \end{comment}
  \gitem{Circle of Dusk}
  \target{Circle of Dusk}
  \target{Dusk Circle}
  \index{Dusk Circle}
  The most harmless ones. 
  
  \begin{sephlist}
    \seph{\Dweryog}
    \target{Dweryog}
    \index{\Dweryog}
    Used to see things. 
    
    \seph{\Gavron}
    \target{Gavron}
    \index{\Gavron}
    Can cut through small things. 
    Some people use him as a shaving razor. 
    
    \seph{\KorRashad}
    \target{Kor-Rashad}
    \index{\KorRashad}
    The guide through the \empyrean{}. 
    \KorRashad{} represents, and is an extension of, the individual's \emph{will}. 
    He is depicted as a \mulgron: 
    Massive, immovable and unstoppable. 
    
    He is inspired by Ra-Hoor-Khuit, an entity that appears in Aleister Crowley's Thelema. 
    
    \seph{\OmmonThul}
    \target{Ommon-Thul}
    \index{\OmmonThul}
    The Cold Lurker. 
    Could stun, slow and paralyze victims. 
    
    \seph{Thaid}
    \target{Thaid}
    \index{Thaid}
    A guardian \qliphah. 
    He is represented as a snake: 
    Part phallus, part residue of ancient \ophidian{} mythology. 
    
    \seph{Thuin}
    \target{Thuin}
    \index{Thuin}
    A guardian \qliphah. 
    She is represented as an arch: 
    Part vagina, part heaven, part doorway. 
   
  \end{sephlist}




  \begin{comment}
  \paragraph{Circle of Twilight}
  \end{comment}
  \gitem{Circle of Twilight}
  \target{Circle of Twilight}
  \target{Twilight Circle}
  \index{Twilight Circle}
  The more dangerous ones. 
  This was the largest circle. 
  
  \begin{sephlist}
    \seph{\Djerzad}
    \target{Djerzad}
    \index{\Djerzad}
    A \Qliphah{} that causes bones to break. 
    
    \seph{\Iphicoss}
    \target{Iphicoss}
    \index{\Iphicoss}
    The \Kliffah{} of the Treacherous Gale, creates strong gusts of wind. 
    
    \seph{\Kithvaz}
    \target{Kithvaz}
    \index{\Kithvaz}
    The Breaker of Wills. 
    A \qliphah{} that attacks the mind. 
    
    \seph{\Shurreem}
    \target{Shurreem}
    \index{\Shurreem}
    A \qliphah that can surround the Vaimon in an aura of transparent black \quo{fire}. 
    The black flames were painful to touch unless you were accustomed to them. 
    They felt a bit like regular fire, but more mental, as if the fire was inside you and burning away at your very mind. 
    But they caused no real harm apart from the psychological shock effect. 
    
    \Shurreem was mostly useful for intimidation purposes. 
    It made the Vaimon look wicked and sorcerous. 
    
    The \qliphah was not very widely known. 
    This made it more effective as a bluff. 
  \end{sephlist}




  \begin{comment}
  \paragraph{Circle of Midnight}
  \end{comment}
  \gitem{Circle of Midnight}
  \target{Circle of Midnight}
  \target{Midnight Circle}
  \index{Midnight Circle}
  The most powerful and dangerous of all. 
  
  Includes the following: 
  
  \begin{sephlist}
    \seph{\Bozchul}
    \index{\Bozchul}
    \target{Bozchul}
    A \qliphah{} who brings death. 
    
    \seph{\Horvaleth}
    \index{\Horvaleth}
    \target{Horvaleth}
    The \Kliffah{} of the Cruel Winter. 
    Can create blasts of cold air and shards of ice. 
    
    \seph{\Nyxachel}
    \index{\Nyxachel}
    \target{Nyxachel}
    A \Kliffah{} of lightning. 
  \end{sephlist}




  \begin{comment}
  \paragraph{Others}
  \end{comment}
    Additional names, of whom no more details are known, include \Abbath, \Iachadion, \Iomelech, \Micozalra, \Oronigath, \Ozorugai, \Shabolan and \Zobbath. 
\end{subgloss}





\subsubsection{Nebulae/Pits}
\target{Nebula}
\target{nebula}
\target{Nebulae}
\target{nebulae}
\target{Pit}
\target{pit}
\target{Pits}
\target{pits}
The \qliphoth could also be divided into a number of \quo{nebulae} or \quo{pits}. 
These were analogous to the \quo{elements} into which the \sephiroth were divided. 
The nebulae were orthogonal to the circles. 

Perhaps mortals used the circle schema and the \resphain themselves (who felt less threatened by the \qliphoth) used the nebula schema.

I can name the nebulae after the \qliphoth I already have: 
The Cold Lurker, the Cruel Winter, the Treacherous Gale. 

The nebulae/pits should be compared to Winds of Magic from \cite{RPG:Warhammer}. 
For example, see how the dark wind Shyish corrupts the mage Nevin Kantor in \cite{StevenSavile:Dominion}.









\subsection{Realm}
According to Iquinian mythology, \Itzach{} is also the Realm of the Damned, where the souls of the wicked go after death. 

The Realm of \Itzach{} is a labyrinthine dungeon of endless dark corridors, where the weeping and morbid cries of the damned echo and resound forever. 

Compare to Iril, the Maze-Hell of \authorseries{Alan Campbell}{Deepgate Codex}. 








\subsection{Origin of \Itzach}
\target{Origin of Qliphoth}
Originally, when \hr{Origin of Nyx}{\Nyx{} was created},
the \banes{} created \itzach{} as an imitation of their native \erebean{} power. \Nieur{} is based in \Nyx{} and draws its power from that dimension. It doesn't draw power from \Erebos, it just utilizes the same technology. 

But \itzach{} isn't pure \Erebean{} style magic. 
It also incorporates some \hr{Chaos}{\Chaos}\ldots{}

The \qliphoth were created to serve who conduits to \Erebos{} through which magical energy could be channelled. 









\subsection{Religious beliefs}
For Iquinian religious/mystical beliefs about the \qliphoth, see the section on the \hs{Iquinian Church}. 













\section{Maintaining the Mask of Civilization}
\target{Maintaining the Mask of Civilization}
\target{Maintaining the Shroud of Civilization}
\target{Mask of Civilization}
\target{Shroud of Civilization}
%This section shouldn't be called \quo{maintaining the \quo{Shroud} of civilization}. I need to think of a better word to describe a sub-pattern of the Shroud created by local people's thoughts and beliefs. 

%Maybe \quo{frame}, as in psychology and The Game theory? 

A people's collective belief in the king's power and splendour create a a \hs{Mask}, a mental frame, a collective \vertex, which maintains the civilization's Shroud. 
This frame strengthens the citizens and allows them to work together more effeciently, and it also keeps away the \Wylde{}. 
The people's strong belief that their settlement is separate from the \Wylde{} actually pushes back the \Wylde{}.

In a sense, the Shroud is like money: 
A collective illusion. 









\subsection{Monuments}
\target{Monuments}
All successful civilizations build great monuments: Huge castles, temples, statues, pillars, obelisks and ornaments. These are particularly effective because of the Shroud: They send a message of power, glory and greatness. They create a frame which strengthens the subjects (mentally, in their resolve, and thus also physically) and intimidates enemies. 

%Furthermore, they keep the \Wylde{} at bay. The people's collective belief in the king's power and splendour strengthen the frame of civilization, and thus the civilization's Shroud. Almost like a \vertex. A collective \vertex. This should have a name! Anyway, this power keeps away the \Wylde{}.
This also serves to keep away the \Wylde{}.

The \hs{Cabal} and \hs{Sentinels} both use these monuments to keep people locked in the Shroud.

Monuments and idols that are cherished and worshipped will gradually acquire the power of \nexi. They are invested with mental power siphoned from the adoration and faith of their worshippers.

In order to overthrow/usurp a ruler or dynasty, a powerful weapon is iconoclasm, the destruction or desecration of monuments. Alternatively, you can steal the monuments and usurp them for yourself. 

If you destroy or desecrate the monuments, it is important to build and/or consecrate new ones of your own. Otherwise, you invite \hs{Chaos} and the \Wylde{}. People will degenerate into anarchy, order and civilization will crumble, and eventually barbarism will take over, and the city will sink into the \Wylde{}.

I need to remember to have these monuments in all cities and towns (some grand, some more lowly).

When people worship, admire or love something\dash an icon, a place or a living being\dash they invest not only mental energy but also a small part of their soul in the thing. This makes them yearn back to the thing, and they will keep coming back. An addiction is born.





\subsubsection{Monuments keeping the dead around}
\target{Monuments keeping the dead imprisoned}
By building a monument to the dead and venerate them, it is sometimes possible to keep the dead soul around as an incorporeal ghost, retaining some measure of consciousness and communication ability. 

\index{\carcer!monument}
Sometimes the dead soul wants this. Other times it is imprisoned against its will, often by hapless relatives who think they are doing the right thing by honouring their dead.
The monument thus becomes a small \carcer.

Sometimes the dead soul can take possession of its mummy or some kind of effigy, thus becoming \hr{Undead}{undead}.

\hr{Silqua as a ghost}{Silqua gets stuck after her death} as a powerless ghost. She suffers.







\subsection{Roads through the \Wylde}
\target{Roads through the Wild}
Roads, paths and passes through the \Wylde{} are maintained through the Shroud. If they fall into disuse, they become longer, narrower, more crooked, more sinister, as the chaotic forces of the \Wylde{} work to reclaim the territory. 

If roads are regularly used, protected and maintained, they will become nicer, shorter and more direct. In the best of cases, you can stand in one city, look out at the road leading to a neighbouring city beyond the \Wylde{}, and actually \emph{see} the other city in the distance, at the end of a broad, straight road. The legends say that all cities were like this during the time of the \hr{Vaimon Caliphate}{\VaimonCaliphate} (not true), and it was still like this in a few cases in \hr{Great Velcad}{\theBelkadianEmpire}. 

On a well-kept road, the \Wylde{} is less terrifying. It is still \Wylde{}, but it's farther away, and try as it might to extend into the road, it has much less power to do so. The mind will pick up on this, and so the \Wylde{} will seem less threatening. Also, the order and niceness of the road is contagious, so the closest edge of the \Wylde{} may grow slightly more \quo{tame}\dash brighter, cleaner and with no \wildfog{}, no peering eyes and no scary noises. 





\subsubsection{Road-keepers}
\target{road-keepers}
Every self-respecting kingdom had road-keepers hired to maintain every road. 
They were soldiers or tough woodsmen or \rangers.
Their duties includes:
\begin{itemize}
  \item 
    Patrolling the roads and making sure the \eidola were in place and that the \wylde was not creeping in.
  \item 
    Repairing whatever problems they could.
  \item 
    Alerting the nobles and/or the church if there were any problems they could not solve. 
\end{itemize}

Road-keepers often acted as guides, scouts and messengers as well. 










\subsection{\Wylde{} border}
\target{Wylde border}
\target{Eidolon}
It was well known that monsters and wickedness lurked in the \wylde, so people would erect wards and totem poles and statues and stuff at the border between \wylde{} and settlement, in order to ward off evil and keep the border well-defined. 

To keep the \wylde at bay, people used \eidola. 
And \eidolon was a magical totem blessed and enchanted to protect civilization and keep away the \wylde and its denizens. 
Every religion had its way of creating \eidola. 
Have them in every \wylde scene. 

\citeauthorbook[p.84]{RobertEHoward:KullUntitledDraft}{Robert E. Howard}{%
  Untitled Draft%
}{
  \ta{Nay. 
    Grondar ends here.
    Here is the end of the world; beyond is magic and the unknown.
    Here is the boundary of the world; there begins the realm of horror and mysticism.}
  
  \ldots 
  
  \ta{Remember, they who ride beyond the sun-rise, return not!
    For of all the thousands who have crosses the Stagus, not one was returned.
    Three hundred years have passed since first I saw the light, king of Valusia.
    I ferried the army of King Gaar the Conqueror when he rode into World's End wit hall his mighty hosts.
    Seven days they were passing over yet no man of them came back.
    Aye, the sound of battle, the clash of swords clanged out over the waste lands for a long while from sun to sun, but when the moon shone all was silence.
    Mark this, Kull, no man has ever returned from beyond the Stagus.
    Nameless horrors lurk in yonder lands and terrible are the ghastly shapes of doom I glimpse beyond the river in the vagueness of dusk and the grey of early dawn.
    Mark ye, Kull.}
}





\subsubsection{Sacrifices}
\target{Wylde totem sacrifice}
Every culture used blood sacrifice to keep its \wylde totems active. 
People would slave all day in hellish forges to make or repair the totems, and then the priests or mages would sanctify the totems with blood sacrifice.

Most religions used humanoid sacrifice.
A few, like the \iquinians, \hr{Iquinian animal sacrifice}{used only animal sacrifice}.















\section{Realms}
\target{Realm}
\target{Realms}
\index{Realm}
Remember to have a lot of stuff about the Web of the Realms. 
All the various Realms, their true names, their history, the barriers and pathways between them. 









\subsection{The Beyond}
\target{Beyond}
\index{Beyond}
There really exist more than three spatial dimensions. 
The different Realms exist beside each other and (potentially) intersecting each other. 
But regular creatures can't see all the dimensions at once. 
Neither mortals nor immortals can, but immortals find it easier to learn to compensate. 
With skill and magic, it is possible to \quo{turn your senses around} and so see some other dimensions than usual. 
The Realms Beyond are accessed through those other dimensions that people cannot normally see. 









\subsection{Bodies and souls}
See the section on \hr{extended soul}{extended souls}. 









\subsection{Realms within \Miith}
Many Realms are contained within \Miith{}. 
\hr{Azmith}{\Azmith} is but one of them. 
\Nyx{} and \Machai{} are other such mini-Realms, although further removed from the Heart. 

%\subsection{Large world}
The point of this is that world is large. 
There are other battlefields in the \hr{Feud}{\feud}{} than \Azmith, which despite the name is \emph{not} \quo{all of \Miith}. 

Have references to this when some immortals are absent from the action. 









\subsection{Storm beacons}
\target{Storm beacon}
\target{storm beacon}
\index{storm beacon}
Storm beacons are a kind of magical constructs or spells. 
They are cast on an area and stay there. 
They create a \quo{storm} that ravages the Realms, making it dangerous and difficult to travel through the Beyond in that area. 

But the trick is that the Shroud blocks these magical storms, so the Shrouded world remains mostly unaffected. 
So people can move about in the Shrouded world like normal, but much magic (including \hs{submerging} and summoning) is suppressed. 









\subsection{Summary of the Realms}
\target{Immortal Realms}
\target{Shrouded Realms}
\target{Shrouded Realm}
\target{Chthonic Realms}
\target{Chthonic Realm}
\target{Aquatic Realms}
\target{Aquatic Realm}
\target{Telluric Realm}
\target{Telluric Realms}
\index{Immortal Realms}
\index{Shrouded Realms}
At the time of the \thirdbanewar, \Miith contained a lot of Realms. 
The \Miithian{} Realms were informally divided into two classes: 

\begin{description}
  \item[The Immortal Realms] 
    were the ones where the immortals preferred to live. 
    
    There were at least six Immortal Realms of \Miith. 
    They were: 
    \hr{Nyx}{\Nyx}, \hs{Visha}, \hr{Dun}{\Dun} and three parts of \hr{Machai}{\Machai}.
    
    It was well-known in mythology and legend that the planets and moons were worlds with their own inhabitants. 
    
  \item[The Shrouded Realms \textnormal{aka} Telluric Realms]
    are more deeply Shrouded, hence the name. 
    But the Immortal Realms are also Shrouded, just not so much. 
    \hr{Azmith}{\Azmith} is one such Realm, and \hr{Azmith is important}{the most important one of them}. 
    
    The Telluric Realms were all on dry land. 
    There are 8-10 Shrouded Realms in all. 
  
  \item[The Chthonic Realms] 
    were underground Realms. 
    This class included \hr{Kai-Leng}{\KaiLeng}. 
    There were 3-6 of them. 
    
    These Realms might have been Shrouded or Immortal. 
    Perhaps there were some of each. 
    Perhaps they were neither. 
    Maybe the Shroud did not have the same kind of hold underground. 
  
    The underground Realms were thinly populated, and most immortals attributed to them less importance than they should.
    Only the wise \dragons and the \banelords and a few \resphain understood the significance of the underground, Chthonic Realms.

  \item[The Aquatic Realms \textnormal{or} Pelagic Realms] 
    were \hr{Deep Realm}{Realms of the Deep} and of \hr{Sea}{the sea}. 
    There were 6-8 of them. 
    
    These Realms might have been Shrouded or Immortal. 
    Perhaps there were some of each. 
    Perhaps they were neither. 
    Maybe the Shroud did not have the same kind of hold under water.
\end{description}

The Shrouded Realms are much smaller and narrower than the Immortal Realms, because of the Shroud. 
When one moves \quo{sideways} through the Shroud in a Shrouded Realm, one \hr{submerging}{gradually submerges into an Immortal Realm}. 
These Immortal Realms are full of monsters. 











\subsection{\NaathKurRamalech: He who is the Key and the Gate}
\hr{Naath-Kur-Ramalech}{\NaathKurRamalech} is a \hr{XS}{\xs} who \emph{is} the dimensional barriers around \Miith{}. 
















\section{The Shroud}
\target{Shrouded}
\target{Shroud}
\index{Shroud}
\target{Lie Sublime}
\citetitle[Lords of Cthul]{Misc:Monsterpocalypse}{Monsterpocalypse}{
  Beyond the veil of our own universe exist myriad dimensions teeming with unknown threats. 
  For eons, practitioners of the occult have dared to peel back that fragile layer that separates our world from a vast realm of darkness to glimpse the ancient powers that lurk within. 
  From time to time, those horrors have slipped through the void.
}

A major theme is that of the Shroud and the Lie Sublime. 

The Shroud is a phenomenon that not only makes the Realms less penetrable and more difficult to traverse, but also a mental illness of a sort, a collective delusion that has crept into the minds of all creatures of the known Realms, hiding the true nature of the Realms. Within the Shroud, creatures can only see a narrow sliver of their own Realm; they cannot see nor move into the deeper layers of their Realm nor into other Realms, except in special places, following \emph{threads} in the Shroud, or at special occasions where there occurs a temporary \emph{tear} in the Shroud. (The latter is what happens to Catrian in \TwilightAngelRememberEmph in the chapter \quo{Silenced}.)
For that matter, even the immortals had to travel along certain safe pathways between the Realms, lest they fall prey to the \hr{Horrors of the Void}{horrors of the void}. 

Occasionally, we see evidence of the Beyond, but our brain explains it away and we make up lies and illusions to cover it up. 
Those few who do see into the Beyond and acknowledge what they find are branded as madmen and heretics. 
Young children have not yet fully developed such illusions, so they see the real world somewhat clearer (although they don't always understand what they see). That is one of the reasons children often claim to see monsters and faeries\dash they really do. 

But this is cultural. A culture who believe certain things about the Beyond will see things that way. They will see certain snippets of the Beyond that fit their beliefs. Some cultures deliberately encourage a knowingly false view of the world to further their own ends. Through magic and religious rituals, they glimpse the Beyond, but often they see only the small, controlled parts of the Cosmos that their shadowy overlords wish them to see. 

At any rate, sometimes the barriers between the worlds break down and people can see or move into another world. This might happen in situations of stress/shock or through the use of meditation, magic or mind-affecting drugs. The wisest and mighties of mages know of the planes and can see into them. 







\subsection{History}





\subsubsection{Before the Shrouding}
Before the Shrouding, everyone knew much more about the Realms. Even the unlearned understood more and could see more of the true reality of the universe. But the Shrouding sent ripples through the fabric of the entire universe, leaving the inhabitants scarred in body and soul. 

The weak minds lost their memory, or lost the ability to understand their memories of the richer world they had lost, and so felt the need to repress their memory and make up false \hs{myths} about the nature of the world. 

Only the strongest minds remembered and still understood the nature of the universe. Even the \vertices, such as \Ishnaruchaefir, were profoundly shocked by the traumatic vehemence of the Shrouding. 





\subsubsection{The Shrouding}
\index{Shrouding}
The \Shrouding{} actually depended on more than one previous Shrouding-like spell: 

\begin{enumerate}
  \item The \hr{Crystal Sphere}{\CrystalSphere}, forged by \Tiamat-tachi.
  \item The \hr{Shroud of Girigor}{Shroud of \Girigor}, woven by \Daggerrain. 
  \item The \hr{Shroud of Nyx}{Shroud of \Nyx}, also woven by \Daggerrain. 
\end{enumerate}

The \hr{Shrouding}{\SecondShrouding} itself marked the end of the \secondbanewar. 

Make it clear that the Shroud was a patch. 
It was a hasty emergency solution to patch up the cracks in the much more well-designed \CrystalSphere. 
Everyone knowledgeable, including \Ishnaruchaefir, knew that the Shroud was only a temporary measure and could never last. 
Sooner or later it would collapse.
Everyone had better be ready when that happened. 








\subsubsection{The Unspoken Covenant}
\target{Charade}
In addition to the metaphysical effect of the \SecondShrouding{}, there was also the code of the \charade. By unspoken mutual consent, the \dragons{} and \banes{} agreed that from now on, their great war would be fought not in public but in secret, hidden from the eyes of mortals. 

\target{Unspoken Covenant}
This agreement is also called the Unspoken Covenant. 

\target{Founding of the Sentinels}
\target{Founding of the Cabal}
The organizations of the Cabal and the Sentinels of \Miith{} were founded at this time.

With the \charade, the master races intend to rule by fear, guilt, manipulation and psychological terror. Compare to the Demiurge from the RPG \emph{Kult} and the portrayal of Christianity and other religions in \DIBiggestSecret. 

\lyricsdimmuborgir{Heavenly Perverse}{
  For this is your empire. \\
  This is your intrigue. \\
  Here you own them all. \\
  Here you seal the deed. 
  
  Contaminated from the spree of self salvation, \\
  to keep the fever flowing in the veins. \\
  Prominently manipulating Heaven and Hell. \\
  Does your sophistically discreet interlude \\
  maintain stories not to be revealed?\\
  In your search for redemption, \\
  greed and lies become the saviour. \\
  Through the lecherous eyes disgust withstands. \\
  For are not these the windows to your soul?
}

The Shroud and the Unspoken Covenant were great tools for keeping mortals enslaved. 
Both sides of the \Feud benefited from this.
Mortals turned out to be more useful than the immortals had initially thought.
Back in the day when there were many immortals, they relied on brute force.
In the \hs{Age of the Shroud}, the immortals relied on stealth, cunning, science and long-term planning to gain Ascendancy or their \matrices.

\citebandsong{Nile:AnnihilationoftheWicked}{Nile}{
  Sss'Haa Set Yoth
}{
  And thus they keep us Ever Subjugated, Hopeless, Fearful\\
  And despairing in the Deep Hidden Abysses of our Souls.\\
  Helpless, Unable to Escape the Unending Quiet Desperation.\\
  We have Been Broken down\\
  Conditioned to Accept Unconscious Slavery.
}



\subsubsection{The Shroud and the \CrystalSphere}
\target{Shroud and Crystal Sphere}
\index{\CrystalSphere}%
The Shroud was ultimately based on the \CrystalSphere, the \psp{\banelords}{} prison created by \TyarithXserasshana. 
So to destroy the \CrystalSphere{} one had to destroy the Shroud. 

\target{thawing}
And indeed, as the Shroud began to \hr{unravelling}{unravel}, the \CrystalSphere{} also began to thaw. 
The \hr{Return of the Banelords}{\banelords{} could walk on Mith again}. 





\subsubsection{The Unravelling}
\target{Unravelling}
\target{unravelling}
In \SentinelsofMithEmph, the Shroud was beginning to unravel. 
Officially, it was because the Shroud drew its energy from the Heart of \Miith{}, and \hr{Heart weakened}{in its weakened, faltering state}, the Heart could not sustain such a complex construction. 

But that was what the \banelords{} wanted everyone to believe. 
In truth, the far more important reason was their \hr{Sephirah plan}{\sephirah{} plan}, which was wearing the Shroud thin. 
Another reason was \ps{\Secherdamon} \quo{\hr{Rissitic creativity}{Shroud-drilling}}. 

It was an omen of things to come. 

Things were slipping through the Shroud. 
People would see things they would not have been able to see in previous centuries. 
And monsters, storms, madness, disease and space-warping phenomena would leak in from the Beyond. 

Compare to the vast flowing streams of Dust which Mary Malone discovers in the world of the \emph{mulefa} in \cite{PhillipPullman:TheAmberSpyglass}. 





\subsubsection{It will be horrible}
\target{Unravelling brings chaos}
The \hs{unravelling}, and the ultimate breakdown of the Shroud, will be horrible and will plunge the world into chaos. 

\lyricstitle{\cite{HPLovecraft:TheCallofCthulhu}}{
  The most merciful thing in the world, I think, is the inability of the human mind to correlate all its contents. We live on a placid island of ignorance in the midst of black seas of infinity, and it was not meant that we should voyage far. The sciences, each straining in its own direction, have hitherto harmed us little; but some day the piecing together of dissociated knowledge will open up such terrifying vistas of reality, and of our frightful position therein, that we shall either go mad from the revelation or flee from the deadly light into the peace and safety of a new dark age.
  
  [\ldots{}]
  
  That cult would never die till the stars came right again, and the secret priests would take great Cthulhu from His tomb to revive His subjects and resume His rule of earth. The time would be easy to know, for then mankind would have become as the Great Old Ones; free and wild and beyond good and evil, with laws and morals thrown aside and all men shouting and killing and revelling in joy. Then the liberated Old Ones would teach them new ways to shout and kill and revel and enjoy themselves, and all the earth would flame with a holocaust of ecstasy and freedom.
}








\subsection{Living under the Shroud}
\subsubsection{Class differences}
It is a global tendency that the rich, the nobles, people of the upper classes in general, are stronger and more intelligent, healthy and beautiful than the people of the lower classes.

This is caused by the Shroud: It is perceived as the natural order of the world that the rulers are all-round superior to the subjects. The poor are expected to be weak, stupid and sickly, and so they become. The prophecy is self-fulfilling.

Remember to have references to this in the story.

\lyricsdimmuborgir{Heavenly Perverse}{
  Devoted to your own opiate \\
  in escapades from discontentment. \\
  Are you shutting off from the outside world \\
  to reflect on your mind shallow gutter?
  
  For this is your empire. \\
  This is your intrigue. \\
  Here you own them all. \\
  Here you seal the deed. 
  
  Contaminated from the spree of self salvation, \\
  to keep the fever flowing in the veins. \\
  Prominently manipulating Heaven and Hell. \\
  Does your sophistically discreet interlude \\
  maintain stories not to be revealed?\\
  In your search for redemption, \\
  greed and lies become the saviour. \\
  Through the lecherous eyes disgust withstands. \\
  For are not these the windows to your soul?
}

\lyricsbs{Exmortem}{Fix of Negativity}{
  The world is swept in a curtain \\
  from the rottenness of Man. \\
  Fixing decadent values. \\
  Miserable mortals, open your eyes. 
}









\subsubsection{Immortals inside the Shroud}
\target{Immortals inside the Shroud}
Immortals are weakened when they venture inside the Shroud. 
\Dragons{} cannot assume their true form, \resphain{} cannot fly and magic is weakened. 

The \hs{dead garden} in \Malcur is OK; the Shroud is weak there.
The crypts under \Malcur, where Needle summons her \banes, is also OK. 
But \Forklin{} (where \Nzessuacrith{} and \Achsah{} duke it out) is another matter. 

The \dragons{} have pulled the shortest straw here. 
They are greatly weakened by the Shroud, since they must assume feeble humanoid forms (and in addition to the loss of powers, they are often less skilled at fighting in such a form, to boot). 
The \resphain{} are not so weakened. 
A powerful \resphan{} might even have a fighting chance against a \dragon{} deep in the Shroud.  









\subsubsection{Keeping people ignorant}
\target{Destroying information}
\index{repression of technology!information repression}
An important part of the \charade{} is keeping the general populace as ignorant as possible. They mustn't know of the war that goes on behind the scenes, and the best way to keep them from knowing that is by keeping them from knowing \emph{anything} that they don't need to know. 

To this end, the master races tend to encourage the destruction of libraries and other culture products, to repress knowledge and expression. The \hs{Iquinian Church} is used for this purpose, among other things.

Somewhat like George Orwell's \emph{1984}\ldots{} maybe. Or \emph{Fahrenheit 451}. 









\subsubsection{Maintaining the Mask of Civilization}
See section \ref{Maintaining the Mask of Civilization}







\subsubsection{People don't believe in things}
\target{People don't believe in things}
Most people don't believe in \dragons{} or \banes{} or other monsters. Some know that \resphain{} and \rachyth{} exist, and some know the \hs{myths} that they are descended from \dragons{} and \banes, but they don't believe those myths. 

Have lots of references to this: 
Someone knows, and tries to warn people around her, but they disbelieve and mock her for her \quo{superstition}. 
Preferably, these people should then die. 

\target{People do not believe in Dragons}
Even the \rethyaxes doubted whether \dragons really existed.
They had not been seen since the \hr{Human Age}{\Human Age} began.
Perhaps the Vaimons had destroyed them all, or perhaps they had never existed.
Perhaps the Vaimons had made the \dragons up in order to make the accounts of their own deeds seem more impressive.

The Shroud blinded people not only to other dimensions, but also to what happened right before their eyes.
Mortals genuinely \emph{could not see} the unnatural unless they looked really hard. 
It was well-known that the supernatural existed only in the \wylde\dash unless a sorcerer called it forth.
That was one of the reasons why mages and magic were so frightening:
They made people believe in the supernatural, and thus opened their eyes so they could see a glimpse of the horrors that lurked in their everyday world. 
People suspected in their minds that this horror they saw was the truth, the real world underlying the illusion, but they repressed the idea and blamed the magic. 
Thus magic was feared and reviled. 





\subsubsection{People forget things}
After having been involved in something supernatural, ordinary people tend to quickly forget the incident. Their minds block it out and rationalize it away. 

Entangled in the Shroud, people are unwilling to accept any version of reality that differs from what they believe to know, so if their memories disagree with their preconceived beliefs, then those memories must be repressed, and new ones must be fabricated.

Remember to have references to this: Carzain (or whoever) rescues people from supernatural monsters, and then they forget it and seem to recall him only helping them with something trivial\dash or being wholly unwanted. 

Carzain becomes frustrated by this more than once. Perhaps he even kills the ungrateful fool.







\subsubsection{Technology repressed}
The \hs{Shroud represses technology}. 







\subsubsection{The world needs a hero}
People are stupid, blind sheep who long for a shepherd to follow. Any shepherd. Or just a sheep dog. 

A leader, a hero, someone who can paint a semblance of meaning upon the cold, cruel, meaningless universe. As per the trope \trope{DyingLikeAnimals}{Dying Like Animals}.







\subsubsection{Light and Darkness}
\target{Light and darkness}
Many people see the Sun/light as good things, because it shows a clear world, unlike the dark, unknown, frightening night.

Others (wiser) see the light as evil, because it makes everything black-and-white, hiding all the subtle nuances of the true world, thus confirming the Shroud and the \hr{Lie Sublime}{Lie Sublime}.







\subsubsection{Time}
For regular people, time is a soft, malleable concept. People remember up to one lifetime \emph{at best}. Everything before that is just \quo{the past}. 

Maybe I should have some hints that time is semi-meaningless and vague. 

However, all of this is purely psychological. It is not true. The \emph{real} time is hard and linear. It is the Shroud, the \Sephiroth{} and people's own stupidity that prevent people from seeing it clearly. 









\subsection{Breaking through the Shroud}
Breaking through the Shroud, even for a brief moment, is a shocking, traumatic experience that leads to madness and suffering.

\lyricslimbonicart{A Cosmic Funeral of Memories}{
  I watch the dying Sun\\
  as it fades into the horizon of crimson fire.\\
  The paranormal darkness is now descending.\\
  Invasion of my mind, heart and soul.\\
  As reality shatters around me,\\
  I feel the changing, the metamorphosis.
}

\citeauthorbook[p.250]{HPLovecraft:TheBlackTomeofAlsophocus}{%
  H. P. Lovecraft%
}{%
  The Black Tome of Alsophocus%
}{%
  For he who passes the gateways always wins a shadow, and never agains can he be alone.
  I had evoked\dash and the book was indeed all I had suspected.
  That night I passed the gateway to a vortex of twisted time and vision, and when morning found me in the attic room I saw in the walls and shelves and fittings that which I had never seen before. 
  
  Nor could I ever after see the world as I had known it.
  Mixed with the present scene was always a little of the past and a little of the future, and every once-familiar object loomed alien in the new perspective brought by my widened sight.
  From then on I walked in a fantasic dream of unknown and half-known shapes; and which each new gateway crossed, the less plainly could I recognize the things of the narrow sphere to which I had so long been bound.
  What I saw about me, none else saw; and I grew doubly silent and aloof lest I be thought mad.
}

\lyricstitle{Draft excerpt from the chapter \quo{What Slithers Beneath}}{
  Twisting in pain, Rian gazed up at the sky. Here a new horror assailed his already sorely tested eyes. 
  It should by right be noon, 
  %the sky had grown dark as midnight from horizon to horizon. 
  but as he looked up the Sun was nowhere in sight, and from horizon to horizon the sky had faded to a dusty coal gray. 
  And most awful of all were the stars that burned black in that deathly gray sky. Indeed, darker than black. Deeper than any darkness that should exist. They were like holes in the firmament; holes through which the direst, foulest of evils could seep, down from the endless, lightless chasms of nothingness that brood beyond the edge of the world; beyond everything, where all life and light end, where sanity ceases to have any meaning, where only inhuman chaos reigns; stretching on in all directions, forever. Of all this Rian saw a fleeting glimpse in those black stars that hung in the ghastly heavens, and it made him croak feebly his despair and huddle against the ground. 
}

\citeauthorbook[p.388]{KarlEdwardWagner:AtFirstJustGhostly}{%
  Karl Edward Wagner%
}{%
  At First Just Ghostly%
}{%
  The Queen's Larder was a blackened ruin, as were all of the buildings in sight, save for the Church of St. George the Martyr across the way.
  The sky was a sodium-flame yellow and outlined an endless horizon of blackened heaps of fused stone and glass.
  There was no clear evidence of sun or moon through the glowing haze. 
  Occasional and distant shapes seemed to sail on black wings across the dead skies; otherwise there was no sign of life.
  No sign of any sort of life whatsoever. 
}

\citeauthorbook[p.279]{HPLovecraft:He}{
  \HPLovecraft%
}{%
  He%
}{%
  For full three seconds I could glimpse that pandemoniac sight, and in those seconds I saw a vista which will ever afterward torment me in dreams. I saw the heavens verminous with strange flying things, and beneath them a hellish black city of giant stone terraces with impious pyramids flung savagely to the moon, and devil-lights burning from unnumbered windows. And swarming loathsomely on aerial galleries I saw the yellow, squint-eyed people of that city, robed horribly in orange and red, and dancing insanely to the pounding of fevered kettle-drums, the clatter of obscene crotala, and the maniacal moaning of muted horns whose ceaseless dirges rose and fell undulantly like the wave of an unhallowed ocean of bitumen.

  I saw this vista, I say, and heard as with the mind's ear the blasphemous domdaniel of cacophony which companioned it. It was the shrieking fulfilment of all the horror which that corpse-city had ever stirred in my soul, and forgetting every injunction to silence I screamed and screamed and screamed as my nerves gave way and the walls quivered about me.
}

\citeauthorbook[p.40--43]{ClarkAshtonSmith:TheHuntersfromBeyond}{Clark Ashton Smith}{%
  The Hunters from Beyond%
}{%
  \ta{%
    For a moment, the studio wasn't there at all\dash only a long, ray, oozing plain, beneath skies where the fumes of hell were writing like a million ghostly and distorted dragons.
    Marta was sinking into that ooze, and the Things were all about her, gathering in fresh hundred from every side, fighting each other for place, sinking with her like bloated, misshapen fen-creatures into their native slime.}

  \ldots

  Like one who confronts the Gorgon, I was frozen by her wide and sightless gaze. 
  Then behind her, where stood an array of carven Satans and lamias, the room seemed to recede, the walls and floors dissolving in a seething, unfathomable gulf, amid whose pestilential vapors the statues were mingled in momentary and loathsome ambiguity with the ravening faces, the hunger-contorted forms that swirled toward us from their ultr-dimensional limbo like a devil-laden hurricane from Malebolge.
  Outlined against that boiling measureless cauldron of malignant storm, Marta stood like an image of glacial death and silence in the arms of Cyprian.
  Then, once more, after a little, the abhorrent vision faded, leaving only the diabolic statuary.
}




\subsubsection{Chains}
\target{chains}
People who look through the \hs{Shroud} sometimes see other people as bound by chains that trail off into nothingness. 
This is the mind recognizing on a subtle level that people are bound and enslaved. 
The mind tries to translate this into familiar concepts, and this often takes the form of a vision of chains. 

These chains are a representation of people's binding to a \hr{Matrix}{\matrix}. 

Immortals who know the Shroud see these bindings all the time. 
They typically visualize them not as crude chains but as fine, silken threads connecting people to the vast universe of \matrices{} around them. 
Where Shrouded mortals see only slavery and horror, the immortals see meaning and purpose. 
Therefore the bindings look nicer to them. 





\subsubsection{Creatures in disguise}
Creatures (such as \ophidians and \banes) would sometimes disguise themselves as mortals and enter the world of the Shroud.
To augment their shapeshifting they would wear cloaks and cowls and hoods.
This made it easier to trick onlookers and so slip through the Shroud. 
A clever onlooker could sometimes see through their disguise and discern hints of their monstrous nature.

\citeauthorbook{ThomasLigotti:TheSectoftheIdiot}{Thomas Ligotti}{The Sect of the Idiot}{
  The creatures' movements suggested various hideous analogies. 
  The spinning legs of spiders.
  The greedy rubbing of a fly's feelers.
  The rippling of a lizard's tongue.
  The twitching of its tail.
}





\subsubsection{Dreams}
\target{dreams}
\target{dreaming}
When asleep, people are less bound by the Shroud. 
Their minds can wander more freely.
That is why people saw such strange visions in their dreams. 

This was why \LocarPsyrex \hr{Tiroco contacted in dreams}{contacted \Tiroco Pelidor in dreams}. 

It was \hr{Encountering Dragons in dreams}{possible to encounter} the \hr{Aloof Dragons}{sleeping \dragons} when {dreaming}.





\subsubsection{Freedom}
For a strong person, it can be very liberating to finally break through the Shroud. 

\citebandsong{BlindGuardian:IFTOS}{Blind Guardian}{I'm Alive}{
  Caught in an old cage\\
  The system failed\\
  Built up on lies\\
  Now I see that I'm alone\\
  In asylum's cage I'm left alone
  
  I'm alive my friend\\
  I can feel the shadows everywhere\\
  I'm alive\\
  I left the shadows far behind me\\
  Another one is waiting in the dark
}





\subsubsection{Horrors Beyond}
See the section about the \hr{Horrors of the Void}{horrors of the void}. 





\subsubsection{\Iquin}
See the section about \hr{Iquin through the Shroud}{\iquin as seen through the Shroud}. 





\subsubsection{Madness}
People who see through the Shroud, but are too ignorant, weak or stupid to understand or control it, acquire traumas and go mad. (Note that \hr{Madness}{madness} can at times be a good thing.)





\subsubsection{\Nyx}
One might see visions of the endless city of \Nyx. 

\citeauthorbook[p.181--182]{RobertEHoward:TheHouseintheOaks}{%
  Robert E. Howard and August Derleth%
}{%
  The House in the Oaks%
}{%
  Presently it lightened.
  Yet the moon and the moonlight did not return.
  Rather, some strange hallucinatory effects began to make show.
  Though  I could not say that I had memorized the loandscae outside the house, I was at least familiar enough with Old Dutchtown and its general area to realize that the disturbing facets of countryside I now saw in that dim, iridescent glow were not natural to New England.
  Indeed, they were not. 
  And once again lines of Geoffrey's pressed through\dash
  
  Tread not where stony deserts hold\\
  Lost secrets of an alien land,\\
  And gaunt against the sunset's gold\\
  Colossal nightmare towers stand.
  
  For I saw great towers, I caught glimpses of tall spires, shifting and vanishing before my eyes as I looked from that house as from some vortex in space across eons of time, shifting and vanishing in great clouds of blowing sand\dash and then, most terrifying of all, there was at last something more.
  
  [\prikker]
  
  I saw those great \quo{blinking, moving things} in that wierd landscape beyond the windows of that accursed house in the oaks\dash great, vague shapes that loomed through the blowing sand, I heard their shrieks and cries riding that wind from outer space\dash and, most horrible of all, I saw too the outlines of that colossal face with its eyes\dash eyes that flamed as with living fire\dash fixed upon me as certainly as I stared past the bars of the window into that alien world\dash saw it clearly and unmistakably, and knew it for what Geoffrey saw, before I fled that house in the early hours of the morning.
}





\subsubsection{Slums and torture chambers}
In the most horrible of places, in slums, torture chambers, prisons and asylums, the Shroud is worn thin and you can more often perceive the \hr{Horrors of the Void}{horrors that lurk} in the \hs{Beyond}. 

Remember to have plenty of horrors that lurk in the Beyond! 

See, the Shroud is woven to a large extent by the beliefs of people. And beliefs are based in passion, emotion. But as with every force, if emotion becomes too strong a force it becomes destructive. So very strong feelings, such as fear and pain, can wear through the Shroud. 

This \quo{thinning} most strongly affects those people already \quo{vulnerable} and liable to break the Shroud, such as madmen. But it also extends to other people in the area or in near those people. 

The \hs{dead garden} in \Malcur is a mild version of one such place, inhabited by an old, mad woman.  









\subsection{Masks}
\target{Mask}
\target{Masks}
The Shroud enforces a number of collective beliefs about how the world looks. 
These individual beliefs (fragments or manifestations of the Shroud) are called Masks. 
They are similar to the psychological concept of \quo{frames} in seduction theory. 

An example is the \hs{Mask of Civilization}. 

\quo{Mask} can also mean a Shroud around a person or place to hide its true form and/or nature. 
All immortals must wrap themselves in Masks when \travelling inside the Shroud. 
These Masks can be stronger or weaker. 









\subsection{The Realm of the Veins}
\target{Veins}
\index{Veins, the}
At the very densest part of the Shroud, the \quo{core}, \quo{closest} to the Heart, there lies a Realm called the Veins (ie., the Veins of the Heart). 
It is made of metallic corridors. 
People who wander in there are Shrouded beyond recognition and transformed into metal statues or robots. 

A \resphan{} once ventured in there. 
He lost his mind and locked himself into a \human{} body. 
After a \human{} lifetime his body died and his maddened soul wasted away. 









\subsection{Spiralling Realms}
When \hr{The world goes mad}{\Miith plunges into chaos in the \thirdbanewar}, it sometimes happens that a Shrouded Realm closes itself off. 
Just like the town of Kur\=ozu-Cho in \cite{ItoJunji:Uzumaki}. 

Even immortals can suddenly find themselves trapped in a Shrouded Realm that shrinks smaller and smaller.
At the same time the Realm becomes more and more Shrouded, so that the immortal loses his powers, degenerates into a mortal and finally suffocates and dies.
A gruesome, senseless, incomprehensible death.









\subsection{Conspiracy against the Human Race}
\target{Conspiracy against the Human Race}
The Shroud affects intelligent beings more than unintelligent beings. 
It is, in a sense, the curse of sentience. 

To some extent, the Shroud can be said to represent the alienation that thinking beings feel. 
Compare to \cite{ThomasLigotti:TheConspiracyAgainsttheHumanRace}. 















\section{Souls}
\index{souls}
All living creatures have a soul. The soul is actually their true \quo{body}, stretching beyond the physical body and into the Beyond. Thanks to the Shroud, the souls are deeply bound to their physical bodies, which are really shallow shadows of the actual souls, existing in the Realm of the Shroud. 

Souls are mortal: They can be created and destroyed. When \Miithian{} creatures reproduce, they invest some of their own life force and also tap into the creative power of the Heart of \Miith{} in order to create a new soul for their offspring. 

Sex taps into the power of the Heart of \Miith{}! Remember this. This is a useful theme. 

For the more powerful races, creating new souls is more difficult, requiring more power than the Heart can easily provide. So procreating is a complex, supernatural process, and the parents must permanently invest some of their own life force in the child. Such children are typically immortal or very long-lived. 

In contrast, regular creatures can be created cheaply, and they usually die soon after. The natural cycle of things is that when a creature dies, its soul lingers for a while but then gets absorbed by the Heart, its essence recycled to produce more life in the future. 

But civilizations have fucked this up. With all of their religion and magic, they try to make their souls immortal. This means that a lot of life energy which the Heart needs gets locked up in all these immortal souls, who may be bound in the \Sephiroth{} or whatever. So by virtue of their culture and religion, humanoids suck the life of of \Miith{}. 









\subsection{Bodies and souls}
\target{extended soul}
All creatures really extend beyond the physical plane. 
Their physical body is only a small part of their existence. 
Their complete being (often called the \quo{soul}) extends into the Realms Beyond, even into \hs{Chaos}. 


Most creatures are unaware of their true self and therefore cannot consciously use it to affect other planes beyond the physical.%
\footnote{%
  Except to a small, subconscious degree. 
  Empathy is actually the act of reaching out through the Beyond and sensing others' souls, and \quo{frame control} (the act of affecting other people's thoughts simply by acting a certain way\dash used in leadership and seduction) is reaching out and poking people.} 

The art of learning to control your true self and use it to perceive and affect the world is \emph{\hs{magic}}. 





\subsubsection{Disembodied souls}
\target{Disembodied souls}
\index{soul!disembodied}
A disembodied soul can be warded off, blocked, driven away or imprisoned. 
This is easy if the soul is weak, but hard if the soul is powerful. 

But a disembodied soul cannot be destroyed or eaten. 
At least not by any means known to \Miithians. 

On the other hand, a soul cannot do shit without a body. 
It can barely retain consciousness. 
It may be able to communicate and use some feeble magic. 
But not much. 

A disembodied soul is not worth much.
A disembodied soul cannot think and exists only in a barely-conscious, dreamlike state.
In order to be fully conscious and interact with the world, a soul needs to be housed in a \quo{brain} of some sort. And a brain needs to be supported by a body.
Furthermore, in order to cast magic, you need a body to channel the magical energy.

In many stories, ghosts (for example) are insubstantial. They can walk through walls but cannot affect physical objects.
In my world, disembodied souls are even more limited than that.
It partially derives from a question I have pondered from time to time: What is the relationship between the soul and the brain?
This has turned out to be a non-trivial question to answer. 
See, I want souls to have the opportunity to reincarnate into a new body after death. This new body may be genetically unrelated to the previous body.
But I also want a creature's intelligence and other mental traits to be affected by genetics.
This means that a living creature's psyche cannot depend on the soul entirely, but must also depend on the brain (which is part of the body). 
So I have decided that a soul cannot maintain consciousness without a brain of some kind.

The \dragons, with their superior immortality, were able to maintain consciousness even though their bodies were dead or destroyed. 
\Sethicus and \Tiamat did this after their deaths.
\Resphain could not do that. 
Only \Shiaraid achieved it (during Carzain's lifetime). 
It was a monumental achievement for her, only possible because she was a \sathariah \malach with a \carcer.









\subsection{\Carcers}
\target{Carcer}
\index{\carcer}
A \carcer{} is a soul prison. 
In it, souls can be stored to use as an energy source. 
Such souls can be molded into a powerful \vertex, or perhaps even a micro-\dweomer. 









\subsection{Death}
\target{Death}
\index{death}
Have some stuff about death. Remember to think about how death works in the \Miith{} universe. 

See also the section on \hs{Undead}. 

The \hr{Sephiroth}{\Sephiroth} are initimately tied to death. 

The \hs{Cult of the Worm} worship death. Worms are their symbols.

\target{Crows and ravens}
Crows and ravens (associated with death by virtue of the scavenger nature) are associated with the \hs{Cabal} and the \resphain. See the section about \hr{Harbeth}{\Harbeth}. 

Mortals do not step out of their body unscathed when they die. They are closely tied to their bodies and lose much of their power when they die. This is partly natural, partly caused by the \hs{Shroud}. 

\lyricstitle{\authorbook{Stephen Marley}{Mortal Mask} p.133}{
  \ta{What's copulation? 
    A brief, meaningless touching of flesh. 
    A birth is nothing more than an admission of death. 
    Mortals must give birth because all mortals must die, yet their race must continue. 
    Immortals have no need of birth. 
    Mortals should wear death masks when they make what they like to call love.}
}





\subsubsection{Afterlife}
\citeauthorbook[p.138]{RobertEHoward:QueenoftheBlackCoast}{Robert E. Howard}{%
  Queen of the Black Coast
}{%
  First there was the blackness of an utter void, with the cold winds of cosmic space blowing through it. Then shapes, vague, monstrous and evanescent, rolled in dim panorama through the expanse of nothingness, as if the darkness were taking material form. The winds blew and a vortex formed, a whirling pyramid of roaring blackness. From it grew Shape and Dimension; then suddenly, like clouds dispersing, the darkness rolled away on either hand and a huge city of dark green stone rose on the bank of a wide river, flowing through an illimitable plain. Through this city moved beings of alien configuration.
}









\subsection{Decrepity}
\target{Decrepity}
\target{decrepity}
\index{decrepity}
\index{soul!decrepity}
Most immortals were able to heal all kinds of wounds to their bodies. 
Almost. 
But some wounds could not be healed. 
Sometimes an especially traumatic injury would leave a psychological scar. 
This spiritual scar would show up in the body.
As long as the inner wound remained, the body would continue to show the wound. 
On the external level, the wound could sometimes be healed \emph{temporarily}\dash or at least concealed.
But only temporarily.
The body would always tend to decay back to the state of the soul within. 
Such a spiritual wound is called a \emph{decrepity}. 









\subsection{Immortality}
\target{Immortality}
\target{immortality}
\target{immortal}
\index{immortality}
\index{soul!immortal}





\subsubsection{Degrees of immortality}
\target{True immortal}
\target{True Immortals}
\target{True Immortality}
\target{lesser immortals}
\target{Lesser immortality}
\target{Lesser Immortality}
Some creatures are \quo{immortal}. 
There are two degrees of \quo{immortality}

\begin{description}
  \item[Lesser Immortality:] 
    These creatures never die of \quo{natural causes} and are very hard to kill manually, but they can die of violence. 
  \item[True Immortality:]
    In addition to the powers above, true immortals don't actually die even when they are killed. 
\end{description}

The last part warrants more explanation. 
A true immortal's body can be killed, but the body is only a small part of his being (as with all beings). 
The soul lives on, and it retains all its memories and most of its power (although physical death may leave the soul knocked temporarily unconscious). 
The soul can use a bit of magic, and it can communicate, and with time it can resurrect the body. 

If the body is destroyed the immortal needs external help to regrow a new body. 
He needs to have either a \hs{life-seed} or an ally who can grow him a new body.

\target{Resurrection help}
If the dead immortal has no life-seeds, his allies have to use magic to resurrect him.
They have to sacrifice part of their own bodies to create a life-seed for their dead comrade. 
Allies can also sacrifice their body and energy to help a dead comrade revive from his own life-seed. 

If the old body has been captured, the true immortal can voluntarily refuse to revive the body and grow a new one instead (provided he has the means).

A true immortal soul can still be \hr{soul destruction}{destroyed} or \hr{soul-eating}{eaten}. 

\quo{True immortality} was invented by \TyarithXserasshana, based on some \xsic{} technology. 
The \banelords{} spied on this technique and copied it when designing their \resphain, so the \resphain{} also possess it. 
But \quiljaaran, \vorcanths{} and \aryothim{} only have \quo{lesser immortality} and can be killed. 

No one is quite sure how immortal \banes{} are\ldots{}





\subsubsection{Kinds of immortality}
\target{Kinds of immortality}
The different kinds of immortality include: 
\begin{itemize}
  \item \hr{Ophidian immortality}{\Ophidian immortality}. 
  \item \hr{Draconic immortality}{\Draconic immortality}. 
  \item \hr{Resphan immortality}{\Resphan immortality}. 
  \item \hr{Malach immortality}{\Malach immortality}. 
  \item \hr{Naga immortality}{\Naga immortality}. 
\end{itemize}








\subsubsection{Immortals don't succumb to emotions}
Unlike mortals, the master races do not easily succumb to emotions such as pain and fear. 
Rather, it motivates them further, makes them stronger (albeit perhaps more irrational). 





\subsubsection{Immortality is an abomination}
\target{Immortality is an abomination}
The natural way of things is that souls are formed by the \hr{Heart}{Heart of \Miith} and incarnated in a body, live for a while and then die and return to the Heart. 
But the master races have broken this law of nature by making themselves immortal. 
Each \dragon{} and \resphan{} refuses to die and instead lingers on forever (or tries to), hogging some vital life force that the Heart needs and wants. 
Thus, power is permanently stolen from the heart, and the biosphere's cycle of life is impoverished. 

It gets worse: 
Immortal creatures cannot die of natural causes, but they can be killed by applying enough destructive magic. 
But this kind of death does not release the soul back into the Heart, it \emph{annihilates} it. 
Its fragment energies are scattered to the cosmic winds and cannot be reclaimed by the Heart. 
And so, some of the planet's heartblood is permanently stolen and lost. 

As long as the creature lives, it is still tied to the Heart, and so part of the biosphere. 
It both takes energy from the Heart and gives some back, in the cycle of life. 
But when the creature is destroyed, the Heart feels the pain of the permanent loss of soul power. 

Now, this isn't as bad as it sounds. 
While the master races have some heavy-ass souls, their populations are also pretty low. 
New \dragons{} and \resphain{} are born and die quite rarely. 
It was a major problem during the \secondbanewar{} and the \resphanwars, where the master races were being killed in droves. 
This actually causes planetwide devastation and created deserts and wastelands that have never recovered and perhaps never will. 
But otherwise, the master races rarely die, and so it's not so big a deal. 
The Heart can cope with it. 

But it gets worse. 
The \banelords{} conquered \iquin{} and turned it into a prison of souls. 
Suddenly, all mortals under the mantle of the Iquinian religion were granted immortality (albeit immortality as a powerless ghost in a nightmarish prison). 
The problem with this is, of course, that mortals (as the term suggests) die all the time, and are born all the time. 
Now we have a huge \quo{net} sucking up a ton of newborn souls and hoarding more and more of them as time goes by. 
This is disastrous for the Heart. 
It is slowly being sucked dry, more and more of its vital lifeblood being locked away by the \sephiroth. 
And recently the \hr{Morbus}{\Morbus} has come along and sped up the process, making things even worse. 

So, immortality for immortals is not so bad. 
They breed slowly \emph{because} they are immortal, and the Heart can cope with it. 
They are made for it. 
But immortality for mortals is \emph{bad news}. 
There are just too many of them.
They breed like rats and ruin everything. 

It is starting to show: 
\Miith{} is growing less lively by the year. 
Greater expanses of the \Wylde{} are decaying into dead wastelands. 
And it's harder to procreate. 
More and more children are stillborn, or misshapen wretches that die soon after birth. 
This is especially bad for the master races themselves, since they have a hard enough time procreating as it is. 

The hideous \sephiroth{} are gradually killing the Heart of \Miith{}. 
It is a vital part of the \psp{\banelords}{} evil plan. 
The next stage of this plan is already in motion: 
The \hr{Morbus}{\Morbus}. 





\subsubsection{Life-seeds}
\target{Life-seed}
\target{life-seed}
\target{life-seeds}
\index{life-seed}
A life-seed is a magical item that a true immortal can use to regrow a new body when is old body is destroyed. 
The immortal has to create the life-seed in advance from a part of his own body.
He must permanently sacrifice some life energy to create it, and the life-seed must be fed or \quo{charged} regularly.
This is expensive and limits the number of life-seeds it is practical for any one person to have. 

Creating a \resphan life-seed requires the sacrifice of a living \human (or \resphan). 
A \nephil will not do. 
The \human must be kept alive but mindless. 

Life-seeds can be detected using magic.

When invading a \resphan hold, the attackers would typically kill all the \resphain (or take them prisoner to eat them), capture all \resviel (to enslave as \yurideth) and destroy all life-seeds they could find.
Sometimes they would also kill the \humans.





\subsubsection{Sustenance for immortals}
\target{Immortal voracity}
All immortals were voracious carnivores, if not soul-devourers. 
They needed the energy of other living creatures to maintain their own lives. 





\subsubsection{How it ends}
The \hr{Daggerrain falls}{fall of \Daggerrain} finally puts a stop to the \ps{\banes}{} evil plans and causes the \sephiroth{} and the \Morbus{} to fail. 
Then \hr{Respite for the Heart}{the Heart can recover somewhat}. 









\subsection{Reincarnation}
\target{Reincarnation}
The Imetrium and Rissitics, and other religions, taught that the souls of the faithful dead would be reincarnated and return to the world, and that the best of them would be gathered unto the gods and given some blessed position.
The last part was true (although the \quo{blessed position} might be no more than a mindless niche in some \matrix).

The first part was also true, although perhaps not in the way people imagined it. 
The gods could shepherd souls and make sure they got recycled in the correct places, by means of prayers and spells cast on the dying (to catch the soul and store it in the \matrix) and on the conceiving, pregnant and newborn (to make sure a suitable soul would be injected into the mother and merge with the child). 
But this process was error-prone. 
Souls, however pious, might wander off and get lost, or get eaten by aethereal predators in the Beyond.
And souls are difficult to maintain in a disembodied state.
Great and powerful and skilled souls might be able to maintain themselves and even keep some measure of consciousness and power while disembodied.
But regular mortal souls lost consciousness and entered a dreamy state.
Here the souls became malleable and fluid.
They would break apart and merge into one another; lose soul-matter to the void and absorb new soul-matter from the void.
So an incarnated soul might not be an exact copy of any dead soul, but could be a mix of fragments of many souls.
Still, close enough.










\subsection{To destroy or eat a soul}
\target{soul destruction}
\target{soul-eating}
\index{soul!destroying}
\index{soul!eating}
Souls as usually semi-immortal. 
But they can be permanently destroyed. 
This is difficult. 

To destroy a soul, you must cast some spells on the body while it remains alive.
Then kill the body in a special, magical way. 
Then quickly cast some more spells to to capture the soul, and cast some more spells to destroy it. 
This is difficult, not only because the spells are difficult to learn and cast, but also because it has to be done in advance, while the victim still lives. 
The victim will probably notice and realize that he is in danger, and so fight extra hard or try to escape. 
It is not possible to capture a soul if the body dies before you are prepared for it. 
Then it escapes into the Beyond, at which point it is very difficult to track and capture. 
Typically, this means the soul-destroying business has to be planned and prepared in advance. 

Of course, it is harder when the victim is more powerful. 
If the killer is much more powerful than the victim it is pretty easy, but if they are equal in power it takes a lot of preparation and skill\ldots{} and trickery, because if the victim suspects he will take countermeasures. 

Even more insidiously, is is possible to not merely destroy a soul but \emph{consume} it. 
This is the most extreme form of \hr{Life drain}{life force drain}. 
It is even harder, trickier and more time-consuming than simply destroying and dissipating a soul. 

Destroying souls contributes to the \hr{Heart weakened}{weakening of the Heart of \Miith}. 

Some creatures (such as the \hr{Resphan}{\resphain}) \emph{live} by draining souls. 

\citeauthorbook[p.25]{RobertEHoward:ThePhoenixontheSword}{Robert E. Howard}{%
  The Phoenix on the Sword%
}{
  Over his mangled arm it glared fiendishly into the king's eyes, in which there began to be mirrored a likeness of the horror which stared from the dead eyes of Ascalante. Conan felt his soul shrivel and begin to be drawn out of his body, to drown in the yellow wells of cosmic horror which glimmered spectrally in the formless chaos that was growing about him and engulfing all life and sanity. Those eyes grew and became gigantic, and in them the Cimmerian glimpsed the reality of all the abysmal and blasphemous horrors that lurk in the outer darkness of formless voids and nighted gulfs. He opened his bloody lips to shriek his hate and loathing, but only a dry rattle burst from his throat.
}





\subsubsection{Shroud prevents soul destruction}
\target{Shroud prevents soul destruction}
It is very hard to eat or destroy a soul from deep within the Shroud. 
See, the Shroud allows physical bodies to interact, but it places harsh restrictions on how souls may interact with each other. 
This weakens many of the powers that strong souls otherwise possess (ie., magic), but it also protects them from being eaten. 
It can still be done, though. 
It is just very difficult. 

Examples: 
\hr{Silqua dies}{\Eryal{} allowed herself to be eaten}. 
\hr{Shiaraid dies}{So did \Shiaraid}. 
 

























