
\chapter{The Feud}
In almost all \Miithian{} cultures, stories and myths are told about two secret organizations that exist in the shadows and wage an eternal war for dominion over the planet\dash{}the Cabal and the Sentinels of \Miith{}. They are said to have existed for many thousands of years, if not forever, and the Sentinels are associated with \dragons{} while the Cabal is said to be connected with the mysterious \banes{}, but other than that, little is known about them. Some say that the Sentinels are good, nobly defending \Miith{} against the predations of the evil Cabal, whereas others claim that it is in fact the Sentinels who are evil, and yet others assert that both orders are uncaring manipulators that prey on the hapless people of \Miith{}. 

It is said that the conflict between these obscure forces has shaped the entire history of \Miith{} and that all major heroes, leaders and rulers though time have been manipulated by one (or both) of the orders\dash{}and many are the men and women in history who have been publicly accused, even convicted, of being Cabalists or Sentinels. Both organizations are said to be of otherworldly origin and to work though dark sorcery and \daemonic{} allies. 

But few and far in between are the actual, visible indications of their existence, and indeed, today many people believe that the dark orders are but myth and superstition. Most \Velcadians{} comfortably believe that all \dragons{}, or as near all as makes no difference, dwell in remote, legendary Irokas, and that the wicked \banes{} have vanished from \Miith{} many thousand years ago, if indeed they ever existed at all. Even major kingdoms and organizations know of little evidence that the twin orders exist, and so they are for the most part relegated to the realm of legends. 

Few know even fragments of the truth, and fewer still know the whole truth, but the Sentinels and the Cabal are very real and have existed for nearly ten thousand years, and their importance in \Miithian{} history, even today, can scarcely be overestimated. 















\section{The Cabal}
\target{The Cabal}
\target{Cabal}
\index{Cabal, the}
\index{Cabal, the!Cabalist}
The Cabal is an underground organization that secretly serves the \resphain{} and the \banes. Its members are called Cabalists.

There are thousands of actual Cabalists scattered across \Miith{}, but tens of thousands more unknowingly serve the purposes of the Cabal, and millions more are being subtly manipulated by the Cabalists. Even within the Cabal, most who call themselves Cabalists know very little of their actual purpose, for the Cabal's \emph{modus operandi} is secrecy above all else. 

The supreme leader of the Cabal on \Miith{} is the \banelord{} Daggerrain, who ultimately serves the \baneking{} called \Voidbringer. The majority of Cabalists are \human{}, but they also count \scathae{} and \meccara{} among their ranks, and more than once in history has a renegade \dragon{} turned to the Cabal. 

%The Cabal is an underground order that run by and serving the \banes{} and their loyal \resphain.

The Cabalists are arranged in a strict hierarchy. They can and do backstab each other, but will do so only after careful planning and conspiration. Diplomacy and social relations are very important when one means to advance.

In contrast, the Sentinels are far more chaotic and violent. Their structure is more anarchistic, more overtly based on bullying and intimidation. Brute force and violence means more, and open combat between rivals is more common.









\subsection{Activities}





\subsubsection{Encouraging heroes}
The Cabal actively encourages would-be heroes to go out and do heroic deeds. See section \ref{Cabal encourages heroes}. 





\subsubsection{Fake resistance within the Cabal}
For new Cabalists, there is a period of \quo{trial membership}, which can last for several years. 

Also, to weed out potential traitors, there exists a fake \quo{resistance} within the Cabal. They allegedly work against the Cabal and try to foil its evil plans and do good instead. But in reality, the resistance is a hoax. It is controlled by the Cabal and used to lure out and identify potential dissidents within the Cabal, who might consider joining or forming an actual resistance. They are introduced to the fake resistance as a test, and if they join, or just neglect to inform their superiors, they are usually judged unreliable and killed off. 

Compare to the fake resistance in \authorbook{George Orwell}{1984}.





\subsubsection{The Missionarium}
The Missionarium is the division of the Cabal charged with controlling people's thoughts, beliefs, morals and emotions. They manipulate religions and the like. 

Compare to the Bene Gesserit Missionaria Protectiva from \authorbook{Frank Herbert}{Dune}. 









\subsection{Organization}





\subsubsection{Circles}
\target{Cabalist circles}
The hierarchy of the Cabal is arranged in \quo{circles}. The innermost circles are the highest ranks. 

The first circle counts as members only the very highest ranking \resphain{} and the \banelords. All \satharioth{} are of the first circle. 

Almost everyone in the first seven circles are \resphain{} or \banes. Almost all \resphain{} belong to the first nine circles. 





\subsubsection{Not everyone is a member}
The Cabal was the part of the \resphain{} alliance that took care of \bane/\resphan{} affairs in the \hs{Shrouded Realms}, as per the scriptures of the \hs{Unspoken Covenant}. 

Not all \resphain{} were members of the Cabal. 
Many restricted their attention to affairs in the \hs{Immortal Realms}: 
Direct war, science, politics, art, education (i.e., passing on the fruits of science and experience). 





\subsubsection{Ordo ab Chao}
According to \DIBiggestSecret, the Freemason Society (who are, allegedly, run by the reptilian Babylonian Brotherhood) have as their motto \quo{Ordo ab Chao}, \quo{Order from Chaos}.

Maybe the Cabal should have a similar motto. 









\subsection{Religion and eschatology}
The mortal Cabalists had religious beliefs about the \resphain. 

The Cabalists did not see themselves as evil.
They were revolutionaries who used harsh means to achieve a noble higher goal. 

The Cabalists agreed with the \rethyaxes on one thing: 
Illumination was only for the select few, the worthy. 
Not for the masses. 
(See the section on \hr{Arcanum}{\arcana}.)





\subsubsection{Eschatology}
\target{Cabal eschatology}
The Cabalists believed in, and waited for, the \hr{Second Advent of Lithrim}{Second Advent of \Lithrim}. 
They believed the great transcendent god \Lithrim would descend to \Miith together with the \resphain.
Then the righteous (Cabalists) would inherit \Miith and the wicked would be punished, either destroyed or condemned to serve as slaves. 
The Cabalists looked forward to this.
It would be the time of great salvation for them. 

See also the sections on \hs{Iquinian theology} and \hs{Iquinian mythology}, and see \hs{Needle's motivation}. 

Compare to the Christian myth of the apocalypse. 
Also compare it to the apocalypse of the Cthulhu Mythos, where some cultists believe the Great Old Ones will reward them for their faith and destroy all unbelievers. 

\citeauthorbook[p.124]{BrianLumley:TheSecondWish}{Brian Lumley}{The Second Wish}{
  Now Julia sobbed and threw herself once more into Harry's arms, clinging to him as he gazed in astonishment and revulsion at the monstrous carvings.
  The central theme of these was an octopod creature of vast proportions\dash winged, tentacled, and \dragon{}like, and yet with a vaguely anthropomorphic outline\dash and around it danced all the demons of hell.
  Worse than this main horror itself, however, was what its attendant minions were doing to the tiny but undeniably \human figures which also littered the walls.
  And there, too, as if directing the nightmare activities of a group of these small, horned horrors, was a girl\dash with a leering dog-toad abortion that cavorted gleefully about her feet!
}





\subsubsection{\Humans and \scathae}
The Cabalists believed that only \humans could enter the divine realm. 
\Scathae were doomed to be slaves in the divine realm, since they were not part of \Lithrim. 





\subsubsection{Iquinianism}
They believed Iquinianism was a twisted, corrupted version of their true beliefs. 
In this they were partially correct.
The rejected the Iquinian idea that the divine realm was some faraway spiritual thing. 
They believed that the divine realm would come on \Miith in a real, physical, literal sense. 





\subsubsection{\Lithrim}
The Cabalists believed in \Lithrim and waited for its Second Advent. 
\Lithrim was an androgynous entity.
It was not merely a god.
It was the eternal, immortal, cosmic soul of the \human race.
The god above all gods. 





\subsubsection{Purpose}
Some Cabalists knew about the great \quo{\hr{Resphan purpose}{purpose}} of the \resphain, namely to evolve towards perfection. 

A few of the innermost Cabalists knew about the deeper, more hidden purpose: 
The \hs{Unification} of the \baneking \Voidbringer and the \noggyal \hs{mother-mass}.
Or at least they knew the name \quo{Unification}. 
Only the very top level, such as \Azraid, knew what it meant.
Even Ramiel did not learn this until late. 









\subsection{Lictor-like people}
\target{Lictors}
\target{Lictor}
Some people who serve the \banes{} decay and shrivel, coming to resemble living corpses, dead and rotting for many years. Or pale, bloated maggots. Or sickly lepers. 

Compare to the hearse-driving man in \authorbook{\RWChambers}{The Yellow Sign}, or the Lictors in the RPG \emph{Kult}, or the priests in the movie \emph{300}.

Their voices are hoarse and inarticulate, almost bestial.

Note that they only look like this in their true, un-\hs{Shrouded} forms. The Shroud makes them look like healthy, normal \humans.

These Lictor-like people are thoroughly loathsome and repulsive. 

Maybe they degenerate because they are weak of mind and \hr{The cost of magic}{cannot bear the pure energy of \itzach} that they channel.





\subsubsection{Charcoal hates them}
\hs{Charcoal} has to deal with the Lictor-men. He hates them and is disgusted by them. But some of them are of as high a rank as he. 

He thinks to himself: \tho{\Qliphoth, I'm glad I haven't degenerated into one of them. I'm not weak like those people.}















\section{Chaos and Entropy}
\target{Chaos}
\index{Chaos}
\index{Entropy}
Chaos is a basic force in the universe. 
It is one of the driving forces of all life, and perhaps all existence. 
Chaos creates movement, emotions, conflict\ldots{} life. 
And death. 

\Machai{} is sometimes called the \quo{Realm of Chaos}, and it is assumed that Chaos somehow originates from there. 
That is a misconception. 
Chaos permeates all Realms, all planes of existence. 
The forces of \Machai{} merely embody, in a more overt and visible manner, a kind of \quo{Chaos} that is psychologically easily recognizable as such, and so the Realm is considered especially Chaotic. 

\lyricsbs{Arcane Wisdom}{Symphonia Chaos}{
  Chaos, ruler of Time. \\
  Chaos, infinity is Thine. \\
  Shadowy inner essence, \\
  cosmic tapestry and sparkling \\
  spheres of a circular reason. \\
  Chaos, ruler of Time. \\
  Chaos, infinity is Thine. 
}

\hs{Entropy} is another such force. 
Entropy creates stagnation, death and decay. 
In a sense, Entropy is opposed to Chaos, since Chaos \quo{promotes} life and Entropy \quo{promotes} death. 
But all life must end in death, and all movement must eventually grind to a halt, and all complex structures must eventually collapse. 
As such, Entropy can be seen as the \quo{brother} of Chaos; its necessary consequence and counterpart; its \quo{child}, if you will. 















\section{The \Feud}
\target{Feud}
The \feud{} is conflict that is at the heart of the entire story: 
The eternal war between the \dragons, natives of \Miith{}, and the \banes, alien invaders. 

Since the adoption of the \hr{Charade}{\charade}, the \feud{} has not been fought in the open, but in secret, behind the scenes. It is waged today by the two secret organizations the Cabal and the Sentinels of \Miith{}. 

\lyricslimbonicart{Suicide Commando}{
  In the shadows of the world's ambitions \\
  I see life and death, in an enormous collision. \\
  Light destroys what dark creates. \\
  Forever floating, the dark rivers of the heart. \\
  Lifeless drifting, in an orbital decay. \\
  A vicious circle of extinction. \\
  The soul reaches the state: Oblivion.
}





\subsubsection{Darkest magic wins}
\target{Darkest magic wins}
There is a tendency that in war, whichever side is willing to break more moral rules and use darker magic than the other side, wins. 
This is a bit of a theme. 






\subsubsection{Fighting for survival}
\target{Fighting for survival}
There are many, on both sides of the \hr{Feud}{\feud}, who are not evil but simply fight for the future and survival of their people. The two peoples cannot coexist, and so the only option is to wage a war of genocide. 

They are bound by Entropy and must constantly fight on, destroy and devour, lest their hunger consume them from within. 
This is especially true of the \resphain, due to their \hr{Resphan parasitism}{parasitic nature}. 

Also, \hr{Races love war}{they actively enjoy war and conflict}, which only makes it worse.

\lyricsbs{Marduk}{Scorched Earth}{
  We must win to save us from the plague's grasping jaws.\\
  No enemy can bring forth our death.
}

\lyricsdimmuborgir{In Death's Embrace}{
  Without the wit or will to end this journey,\\
  we continue \travelling towards our faith,\\
  harvesting helpless Christian spirits,\\
  raping the sanctity of saints.
  
  For with the sign of the pentagram,\\
  hellfire rage is for us to come,\\
  as we shall wander the Pit,\\
  unhallowed by the Infernal One.\\
  We are forever captured\\
  by the embrace of Death.
}

\lyricsdimmuborgir{Progenies of the Great Apocalypse}{
  The battle raged on and on, \\
  fuelled by the venom of hatred for Man. \\
  Consistently, without the eyes to see, \\
  by those who revel in sewer equally.
  
  Are we not the undisputed prodigy of warfare, \\
  fearing all the mediocrity that they possess? \\
  Should we not hunt the bastards down with our might, \\
  reinforce and claim the throne that is rightfully ours?
  
  Consider the god we could be without the grace. \\
  Once and for all. \\
  Diminish the sub principle and leave it's toxic trace. \\
  Once and for all.
}





\subsubsection{The \resphain{} were winning}
For a long while, it looked as though \hr{Resphain are winning the Feud}{the \resphain{} were slowly winning the \Feud}. 















\section{Heroes}
\target{Cabal encourages heroes}
At times, the Cabal, and perhaps also the Sentinels, work to actively encourage would-be heroes to show themselves, stand up and do their heroism.

The Cabalists want to see that potential heroes, or \vertices, or people who can see through the Shroud, are discovered early on. If left to their own devices, such people might pose a threat, but if discovered while young and weak, they can either be killed off or brought into the fold. This is one of the ways they recruit new members. 















\section{Sentinels of \Miith}
\target{Sentinels}
\target{Sentinels of Miith}
\index{Sentinels of \Miith}
The Sentinels of \Miith{} are an organization founded by \dragons{}. Its purpose is to oppose the Cabal and thwart its advances. Its members are called Watchers and consider themselves the defenders of \Miith\dash{}true, native \Miithians protecting the planet from an alien menace who seek to invade the planet and destroy or enslave her people. In truth, however, much of the Sentinels' work is geared not towards opposing the \banes{}, but towards furthering the cause of \draconic{} dominance on \Miith{}. 









\subsection{Summoning the \xss: A deadly balance}
\target{Summoning the XS: A deadly balance}
The Sentinels, led by \Secherdamon{} and \Vizsherioch, among others, seek to awaken the \xss, but only partially. Enough to draw upon the \ps{\xss}{} power and use it to vanquish the \banes. But they don't want them to awaken so much that they will take control and subjugate or wipe out their \draconic{} spawn. 

To this end, the Sentinels \hr{To break or preserve the Shroud}{work to weaken the Shroud}. 

\target{Dragons want to usurp the XS}
In the best of worlds, the Sentinels hope to \quo{revive} the \xss{} by usurping them\dash transforming themselves into new \xss. \Vizsherioch{} comes closer to this than anyone else.

This is a delicate balance. Some, such as \Ishnaruchaefir, believe that the Sentinels will fail, and therefore \hr{Ishnaruchaefir fights to preserve the Shroud}{strive to preserve the Shroud}.









\subsection{Fractions among the Sentinels}
There were various fractions among the \dragons. 
The \dragons disagreed and fought against each other.

The Sentinels had a dark council who worked to ensuer the \quo{Imperial Court of \Draconian{} Sovereignty}. 
This title is taken from \DIBiggestSecret{} p.44.









\subsection{New Sentinels are initiated}
New Sentinels are initiated into the order. 

\lyricsbs{Arcane Wisdom}{
  A Winter Solstice\dash Hymn to the Fallen
}{
  Gathered to find the Ancient Spirit. \\
  United to \honour the Elderly Ones. 
  
  On the top of this misty white mountain. \\
  Aye\ldots{} our bones are now freezing cold. \\
  Let the ice burn our souls \\
  and the flames\ldots{} freeze our hearts. 
  
  For the Pagan circle of Fire must now be alit.
  
  Once men of great deeds did gather. \\
  Protected were they by ancestral deities. \\
  And now we welcome the arctic season \\
  in our souls that since long turned to ice, 
  and praise them in sheer rapture. \\
  A majestic winterspell \\
  under these cloudy angst-driven skies.
}









\subsection{The Cult of the Worm}
\target{Cult of the Worm}
\index{Cult of the Worm}
The Cult of the Worm is a cult that worships a form of \hr{Khoth-Sell}{\KhothSell}, the \firstgendragon{} goddess of Death. 
The cult is underground but not exactly secret. 
Everyone knows it exists. 
Governments, the \hs{Iquinian Church} and the \hs{Cabal} try to suppress it because it is subversive. 

Worshippers of the cult at times sacrifice their own limbs and organs, mutilating themselves for \quo{salvation}. 
This is probably misguided, since \KhothSell{} is a \xs. 

The cult knows about the \hr{Morbus}{\Morbus} and seek to twist and use it for their own purposes. 

\lyricsbs{Marduk}{Imago Mortis}{
  Today king, tomorrow worms and cold in mouth.\\
  A reach for purity, through decay, through black soil excrements.\\
  None shall stand before the Lord of the Death-Winged Dart.
}

The Cult of the Worm worshipped worms and decay as a manifestation of \KhothSell or other dark gods of death and decay.


\citebandsong{Nile:Ithyphallic}{Nile}{
  Eat of the Dead
}{
  The highest fulfillment of man\\
  Is to become food for the crawling things\\
  That burrow and slither in human flesh\\
  Unceasing in mindless hunger\\
  Remorseless undefiled by reason\\
  The worms of the tomb they are pure

  Their purity elevates them\\
  Above the putrefying pride of our race

  The destiny of man is\\
  Merely to be\\
  The nourishment of the worm\\
  Yet their excrement bestows higher wisdom

  From decay arises new life\\
  Fill myself with that which rots\\
  And I shall be reborn

  By writhing upon my belly like a mindless worm\\
  I shall rise up in awareness of truth\\
  I gnaw upon my own decaying flesh\\
  And my mind is forever purged\\
  Of the corruption of faith
}





\subsubsection{Reapers}
\target{Worm Cult reapers}
The priests of the cult function as \quo{reapers}. They haunt battlefields, slums, \hr{Asylums}{asylums} and other places where people die or suffer, and offer solace and salvation in exchange for loyalty and worship. Thus they prey on and recruit from the ranks of the dead and dying. The dying are easy to enlist. The dead less so, because they are harder to communicate with and less able to think clearly\dash but then, enlistment needs not necessarily be voluntary. Dead souls can be bound and enslaved.

Carzain \hr{Carzain sees reapers near Forklin}{sees some of these} after the battle at \Forklin.

If they must fight, the reapers kill with disease. Like the Silver Brethren from Stephen Marley's books \emph{Spirit Mirror} and \emph{Mortal Mask}. 









\subsection{The Dark Crescent}
\target{Dark Crescent}
\index{Dark Crescent}
A an \Azmith-spanning underground order or cult led by \LocarPsyrex. 

It is less covert than the Cabal or Sentinels. 
Most people know the order exists. 
The order is widespread and has much power in certain parts of \Velcad{}, despite the best efforts of the \hs{Iquinian Church} to suppress it. 
The cult is capable of raising a quite impressive army when it needs to (but its enemies do not know this, only suspect). 

It was an underground religious organization of mages and barbarians and stuff.
Many minor \rethyaxes and petty mages were secretly part of the Crescent.
Many heathen tribes in \Velcad were affiliated with the Crescent.

Compare it to the organization of the Black Moon in \FLuneNoire, led by Haazeel Thorn. 

Is the Dark Crescent connected to the actual \hr{Moons}{moons} of \Miith{}? 





\subsubsection{The physical Dark Crescent}
The Dark Crescent is actually a physical thing. It is a flying ship shaped somewhat like a crescent moon. \hr{Psyrex's throne}{\ps{\Psyrex}{} throne} is located on it. 

Perhaps it is shaped like an ashen claw, giving rise to the name of the Dark Crescent knights. 

Sometimes the Dark Crescent can be seen in the sky. But only with difficulty, since it is black. 





\subsubsection{Corruption}
Like the rest of \ps{\Secherdamon} minions, the Dark Crescent was \hr{Secherdamon plagued with corruption}{plagued by corruption and infighting}. 





\subsubsection{Dark knights}
\target{Dark Crescent Knights}
Have some sinister knights of the Dark Crescent. Like \hr{Dark knights of Mystraacht}{the dark knights of Mystraacht}. 

Compare to the Lords of Negation in \FLuneNoire. Maybe give them a similar title. 

Maybe they are the \quo{Ashenclaw knights}. 

Maybe they ride \hr{Vreiid}{\Vreiiden}.

Maybe there are undead knights who ride undead \vreiiden.

Maybe they resemble Revenants from the game \emph{Warcraft III}. 







































\chapter{Atmosphere}















\section{A dark, sinister world}
\target{The dark universe}
\target{dark universe}
I need to create the impression of a dark, mystic, cruel and savage world. In this regard I am very much inspired by the band Bal-Sagoth, especially their first two albums, \emph{A Black Moon Broods Over Lemuria} and \emph{Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule}. 

I want to create a Bal-Sagoth-esque atmosphere. How do I do that? 

Plenty of landscape descriptions: 
Mist-shrouded heaths, dark and impenetrable forests, cyclopean and towering cities and citadels. 

Hints of a mystic past: 
Old, lost temples and castles. 
Forgotten gods dreaming in the void beyond the world. 

Dreams, visions and hallucinations. 

In war, mages darken the sky with witch-storms. 

Things sunken beneath the sea.

Have a green, aethereal, algae-overgrown-looking building with tall spires. Like the one scene in episode 8 of the anime \emph{Trinity Blood}. 

Also, the concept of \quo{innocence} sucks. Innocence is a lie that weaklings and cowards cling to because they are too weak and afraid to face the true world. Classical symptom of being mired deep in the Shroud. 









\subsection{Ancestral memory}
\target{Ancestral memory}
\target{ancestral memory}
\target{Racial memory}
\target{racial memory}
It was sometimes possible for a person to recall dim memories of the time before his birth. 
Souls absorbed some measure of memory from other souls around them, and a reincarnated soul might retain some dim memory of past lives. 

In horror scenes, I sometimes want to focus on the primal dread that pounds in the back of the skull, caused by the stirring awake of aeons-old ancestral memory.
People remembered vague impressions of prehistoric wars against inhuman terrors, and how their ancestors hid and huddled and trembled in fear of the gruesome elder horrors that stalked the night, bringing with them the vile stench of the Great Outside. 









\subsection{Armies}
Have scenes where an army becomes strong and evil and demonic and filled with bloodlust after gruesome sacrifices of blood.
They chant evil songs and brandish blood-dripping weapons when they march into battle.









\subsection{Carrion worms}
Have a species of carrion worms or vultures, who feed on the suffering and destruction caused by the eternal \hr{Feud}{\feud}. 

Maybe these are intelligent, or maybe they have a cult worshipping them. These will want to sunder the Shroud and the \charade{} in order to escalate the war and create more destruction on which to feed. 







\subsection{The cold darkness of the infinite universe}
Have multiple scenes where a character sees glimpes of the beyond and is terrified but awestruck at the vistas of the cold darkness of the infinite universe, its horrors, mysteries and wonders. 

Compare to \bandsong{Bal-Sagoth}{As the Vortex Illumines the Crystalline Walls of Kor-Avul-Thaa} and \bandsong{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}. 

These visions are terrifying, but also fascinating and compelling. They can instill ambition, or they can crush your will to live. (In \hr{Moro Cornel}{Moro \ps{\Cornel}} case, they sort of did both.)

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{
  Such searingly terrible stellar majesty\ldots{} \\
  my sanity is lashed like a vessel on a storm-wracked sea. \\
  What price this invocation? \\
  Shall the singing stars claim my very mind?
  
  To countless worlds we travel, \\
  riding the endless black seas 'twixt the stars\ldots{} \\
  the ebon oceans of infinity\ldots{} \\
  flying through a thousand suns, then watching their light fade, as if it were but a flickering candleflame snuffed by the wind. As beings of pure energy we become one with the vastness, transcending the ethereal walls of time, spanning at once this celestial eternity, and yet existing as no more than a mote of dust within the vista of its endlessness\ldots{} \\
  Journeying beyond\ldots{} 
  
  The threshold looms, \\
  the star-way between dimensions stretches before me\ldots{} \\
  The Gate To That Which Lies Beyond yawns wide\ldots{} 
}

They might also see stars, planets and civilizations born and die, like lowly fireflies. But pretty\ldots{}

\lyricstitle{Zeratul from \cite{VideoGame:Starcraft}}{
  I have journeyed through the darkness between the most distant stars. I have beheld the births of negative suns and borne witness to the entropy of entire realities.
}

And, of course, you see hints of the dreadful, loathsome, awe-inspiring creatures that dwell in the far reaches of the Beyond. 
\hs{Cosmic gods}, some of which are \quo{evil}. 

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{
  Unspeakable forces gibber and pulsate in the Outer Darkness\ldots{} \\
  Elder horrors dwell here, things which were ancient and revelled in sublime galactic malevolence when even Xuk'ul was naught but a bloated cosmic maggot, writhing and suckling at the breast of its amorphous mother\ldots{} \\
  They-Who-Lurk-And-Breed-In-Limbo\ldots{} \\
  the squamous sovereigns of the elder void!
  
  Primal terror drags my essence \\
  screaming back from the threshold. \\
  The ichor of pestilent tongues clings to me, \\
  tendrils probing, the ire of fiends!
  
  The ravening black worms of madness are devouring the shredded remnants of sanity as I return to my slumbering steel-clad body\ldots{}
}







\subsection{The mind, the body, and sex}
Our minds and bodies are so close and so familiar to us, and yet so labyrinthine and unknowable. 
Perhaps, when you dig deep, they as dark and gruesome and terrible to explore as the cold, alien universe that surrounds us. 







\subsection{Horror and beauty}
The Beyond, the master races, \daemons{} and black magic are all dreadful, hideous and loathsome at first sight. 
This is an effect of the Shroud. 
But when you learn more of the true nature of the universe, you begin to see and appreciate the beauty and splendour of these mighty, exalted entities. 

The \resphain, and perhaps especially the \resviel, inspire in \humans{} an urge to kneel, grovel and worship at their feet. 
Compare to Queen Azshara in the \emph{Warcraft: War of the Ancients} books by Richard Knaak. 









\subsection{Nightmarish society}
The mortal world should be more nightmarish. 
The people toil endlessly in great forges in order to keep the \wylde at bay and preserve the
cities. 
The upper classes live in luxury while the lower classes suffer in endless toil to keep civilization alive. 
Meanwhile the leaders make it all worse by waging wars.

Compare to the world of \emph{Warhammer 40,000}. 








\subsection{Religion}
\target{Religion is dark}
The various gods of Azmith were usually seen by their followers as vast, powerful and frightening, but still mostly benevolent.
But most of them were really horrible elder entities. 
At best, they are \dragons, which is pretty terrifying already.
At worst, they are \xss (like \hr{XS Taorthae}{some \taorthae}) or abominations like the \sephiroth. 

It was gruesome for the people to realize the dark, sinister, occult nature of their gods.
It made some people realize how little they really knew, how powerful the occult unknown was and how much they were the slaves of the powers of primordial darkness.

A few Vaimons and other sorcerers suspected the truth, having learned much about the dark universe through their sorcerous practices.
These people generally kept their suspicions to themselves.
They were having a hard enough time adjusting to it themselves, and they knew most people would not believe them, or even burn them as heretics. 
Besides, it was a terrifying truth that people were better off not knowing at all.
It is better not to speculate, for down that road lies heresy, horror, corruption, evil and madness.
Ignorance is bliss.







\subsection{Survival of the fittest}
The world is a merciless crucible. 
The weak are broken down, succumbing to fear, apathy and stupidity, hammered down into a life of suffering and slavery. 

Only the strong of will are able to face the challenges of life, learn from them, emerge stronger, and thus rise above their original station in life. 
These are the people who have the potential to become \vertices. 

Note that \quo{potential} is not about inborn talent. 
It is all about making the right choices. 
Physical strength, intelligence, a talent for magic\dash all those things people are born with in various amounts. 
But all of them can be developed through sheer will, by \emph{choice}. 
It is about facing fear, accepting challenges, and embracing your inner ferocity. 

It is not about loving your neighbour. 
Altruistic motives can sometimes bring you a long way, but a selfish lust for power and ultimate pleasure can be just as effective, if not more. 
The key is \emph{ambition}. And \emph{perseverance}. 

That is what makes a man. 

That is what makes a hero. 

That is what makes a \vertex. 

(See also the section on how \hr{Races love war}{some races derive pleasure from war and conflict}.)















\section{Blurb}
\begin{blurb}
There are greater, darker and cooler things in the universe than mankind.
This is their story.

\Miith is a cruel world. 

\Miith{} is a world of islands\ldots{}

dark and mystical\ldots{}

swathed in moon-fogs\ldots{}

Fevered dreams of gleaming black onyx spires and forgotten, brooding gods. 

Vast and dark is the world, yet the people huddle in their towns and cities and close their eyes, comprehending nothing of the cruel universe that surrounds them. 
\end{blurb}















\section{Buildings and ruins}









\subsection{Dark ancient cities}
\target{Dark ancient cities}
\target{dark ancient cities}
\Draconian and \bane buildings alike violated the laws of three-dimensional geometry.
They extended into the dark, hidden dimensions of the Beyond. 
Alien dimensions that no one wanted to contemplate. 

The shapes of their walls, towers, statues and ornaments stretched out into the Beyond in a way that was not only physically painful for the eye to follow, but also horrible because it drew attention to hidden things that no mortal wanted to consider. 

See also:
\begin{enumerate}
  \item \hr{Draconic architecture}{\Draconic architecture}.
  \item \hr{QJ architecture}{\QuilJaaran architecture}.
  \item \hr{Resphan architecture}{\Resphan architecture}.
  \item \hr{Nyx}{\Nyx} and \hr{Erebos}{\Erebos}.
\end{enumerate}

Ancient immortal cities reached out into the Beyond. 
They were built in a time before the Shroud, when the barriers between the Realms were much more permeable. 
Their streets and corridors and towers were built so they criscrossed the Realms. 
This was why \hr{Nithdornazsh is a useful gateway}{\Nithdornazsh was so useful as a gateway} between \Machai and \Azmith. 





\subsubsection{Beauty}
\target{Beauty of dark ancient cities}
The dark cities were not only horrible, but also magnificent. 

\citetitle[p.41--42]{RHCharles:BookofEnoch}{The Book of Enoch XIV.9--19}{
  And I went in till I drew nigh to a large house which was built of crystals: and the walls of the house were like a tesselated floor made of crystals, and its groundwork was of crystal.\\
  Its ceiling was like the path of the stars and the lightnings, and between them were fiery cherubim, and their heaven was clear as water.
  A flaming fire surrounded the walls, and its portals blazed with fire.\\
  And I entered into that house, and it was hot as fire and cold as ice: there were no delights of life therein: fear covered me, and trembling gat hold upon me.\\
  And as I quaked and trembled, I fell upon my face.
  And I beheld a vision,\\
  And lo! there was a second house, greater than the former, and the entire portal stood open before me, and it was built of flames of fire.\\
  And in every respect it so excelled in splendour and magnificence and extent that I cannot describe to you its splendour and its extent.\\
  And its floor was of fire, and abive it were lightnings and the path of the stars, and its ceiling also was flaming fire.\\
  And I looked and saw therein a lofty throne; its appearance was as crystal, and the wheels thereof as the shining sun, and there was the vision of cherubim.\\
  And from underneath the throne came streams of flaming fire so that I could not look thereon.
}





\subsubsection{Dark things from the depths}
Sometimes one could see or imagine dark things rising up from the depths. 

\citeauthorbook[p.133--141]{JohnGlasby:TheOldOne}{John Glasby}{The Old One}{
  \ldots{} we caught a fragmentary glimpse of something which rose from those benighted depths, clawing up from the unseen floor. [\ldots{}]
  
  To me, they held ineffable suggestions of a blasphemous structure and architecture utterly unlike anything I had ever seen. 
  [\ldots{}] the searchlight beam only touched their topmost regions.
  But even this was enough to show the sheer alienness of their general outlines.
  Had they been mere conical towers, it would not have offended our sense of perspective to such a degree. 
  But there were bulbous appendages and truncated cones which intermeshed in angles bearing no relation to Euclidean geometry and I felt my eyes twist horribly as I tried vainly to take in everything I saw. 
  
  [\ldots{}] 
  I could not help feeling there was something evil about those nightmarishly misshapen spires and pinnacles with their bizarre curves and planes; yet it was not an evil associated with Earth but rather with the endless gulfs of space and time, with dimensions other than those we know. 
  
  The majority were smashed and broken with harsh, gaping orifices showing blackly against the sickly grey.
  What beings had once moved within these structres it was impossible to visualize. 
  Certainly no hand of man had erected them and carved their cruel, hideous contours.
  [\ldots{}]
  The obscure quality of menace in their weird symbolism made me shudder and long for the sanity and safety of the ship.
  
  [\ldots{}]
  
  [I watched] for he first indication of the vast grey-stone city.
  And then I saw them for the second time, rising out of the slime of the ocean floor, clawing upward for hundreds of feet; row upon seemingly endless row of fantastically symmetrical columns, the nearer ones blindingly clear in the harsh actinic light, with countless others stretching away into the black immensity. 
  
  [\ldots{}]
  
  The effect of that monstrous labyrinth which stretched away from us into inconceivable distrances was indescribable for it was apparent at once that whatever stood on this undersea plateau had never been fashioned by nature, even in her wildest and most capricious moments. 
  And it was equally obvious that whatever hands had erected these edifices had been far from \human. 
  
  [\ldots{}]
  
  I dreamed of the long-dead city under the sea.
  But before my dreaming gaze it now stood unbroken and untarnished by time on dry land and there was no sign of the ocean.
  On an incredibly ancient plateau, wreathed in clouds of steam and noxious vapours, the Cyclopean buildings streched away in all directions as far as the eye could see and high into the lowering clouds where the topmost spires were lost to sight.
  There was something terribly un\human about the geometry of its massive grey-stone walls, and the mind-wrenching alienness of its angles and intermeshing structures went against all reaon, all known laws of mathematics, logic and architecture.
  I knew, by some weird instinct, I was seeing it as it had been perhaps several millions of years ago when it had been newly built by that race from the stars. 
  
  [\ldots{}] now I saw the inhabitants, those hideous and, if the \emph{Book of K'yog} was to be believed\dash{}artificially\dash{}created abominations that had built it!
  I saw them as vague shapes ion the vast avenues and squares, saw them clinging limpet-like to the sides of the buildings or oozing jelly-like from the grotesque apertures and doorways.
  What insane blasphemy had bred those \emph{things} I could not conceive, but the mere sight of them woke me, yelling incoherently, from my dream. 
}






\subsection{Gargoyles}
\target{Gargoyles}
\index{gargoyles}
Gargoyles are awesome. 
I should have them. 

Maybe have some in \Malcur, some statues that are believed to be dead stone, but suddenly come alive. Perhaps in the crypts beneath, letting Rian and Moro encounter them. 

Are they Sentinel- or Cabal-created?

The \hr{Ortaican gargoyles}{\Ortaicans had gargoyles}. 









\subsection{Monuments}
\target{Dark monuments}
Have old, dark, foreboding statues and cemeteries.

When active, \hr{Monuments}{monuments} are important for \hr{Maintaining the Mask of Civilization}{maintaining the Mask of Civilization}. 

Have lots of old monuments built by Elder Races. 
Superior works of superior architecture that could only have been built by superior Elder Races.

Some of them are \hr{Atmosphere:Ruins}{ruined}. 










\subsection{Pyramids}
\target{pyramids}
\target{Dark pyramids}
\target{Black pyramids}
And have dark pyramids. 
Pyramids are cool. 
Perhaps with monsters or undead spirits slumbering entombed beneath them. 
And full of cryptic hieroglyphs. 

Old, creepy cemeteries, and morbid, Nazgul-like statues. 









\subsection{Ruins and fallen cities}
\target{Atmosphere:Ruins}
Remember to have lots of ancient civilizations and ruins of them. 

Have ancient, decayed, crumbling, ruined cities with great empty buildings, temples and monuments. 
People can go here to fight. 
Maybe these buildings lie in \hr{Nyx}{\Nyx}. 
Maybe they are the ruins of ancient \resphan{} cities, perhaps even \Merkyrah. 

See also: \hs{Fallen civilizations of undead}. 

Fallen cities included:
\begin{enumerate}
  \item \hr{Asaathur}{\Asaathur}.
  \item \hr{Baltherium}{\Baltherium}.
  \item \hr{Haamon}{\Haamon}.
  \item \hr{Ibthek}{Ibthek}.
  \item \hr{Su-Gelba}{Su-Gelba}.
  \item \hr{Sardathrion}{\Sardathrion}.
  \item \hs{Thel}.
\end{enumerate}


\lyricsbs{Exmortem}{Funerary Sculpture}{
  Huge battle machines\\
  now funerary sculptures.\\
  \Armoured divisions\\
  no longer a threat.
  
  Isolated war scenarios.\\
  Rusty iron deserts.\\
  Human remains\\
  in the sand and the wrecks.
  
  Unaffected of the grim disease\\
  I walk these fields of flesh piles.\\
  Desolated, lifeless.\\
  Slowly decaying.
  
  Huge battle machines\\
  now funerary sculptures.\\
  \Armoured divisions\\
  now plague eaten filth.
}

\lyricsbs{Exmortem}{Grand Dome of Destruction}{
Naked chambers so cold and grim.\\
  A last gasp for air.\\
  A smell of funerals to come.\\
  Icecold Ugliness.
  
  Here I saw the Lord of Death,\\
  and his eyes flashed with rage.
  
  Gruesome Icons. Demonic Tokens. \\
  Images of a defuct future.\\
  Funeral fests. Nocturnal Chill.\\
  A mirror of the underworld.
}

\citebandsong{Nile:BlackSeedsofVengeance}{Nile}{
  To Dream of Ur
}{
  Desolate and Forsaken \\
  Eerily Moaning Dark Winds\\
  Murmur Incantations\\
  Dusk Calls Forth Shadows

  Spirits of the Glorious Dead \\
  Lingering, Bound to this Place\\
  They Whisper of Untold Sagas, of Long Dead Cities\\
  the Seven Shining Cities Sacred to the Aphkhallu

  Of Ages Past when the World was Young\\
  When Babylon was Blessed of Marduk\\
  and the Sound of her Armies was the Blare of Ominous War Horns\\
  and the Clash of Immortal Cymbals\\
  of Bronze Gates Arrayed in Splendour\\
  and Magnificent Walls of Sunbaked Brick \\
  Of Temples of Marble and Bloodstained Altars

  Long Before the Jeweled Throne of Ur\\
  Fell Silent and Turned to Dust\\
  Beneath the Endless Shifting Sands\\
  and the Inevitable Vengeance of the Elements
}















\section{Cannibalism}
\target{Cannibalism}
\target{cannibalism}
A theme is cannibalism: 
All life feeds upon death. 
In order to grow and achieve greatness one must devour others. 
Others like oneself. 

The ones like yourself are your closest allies and also your closest rivals. 
(Memetic and genetic theory might agree with me on this.) 

This means that you have to sacrifice something. 
In order to become more than a mortal and escape the ignominious fate of normal mortals you have to sacrifice your humanity and become something unhuman, an \Ubermensch. 
Something at once greater (mightier, wiser) and lower (cruel, brutal, bestial) than a normal \human. 















\section{Epic feel}
Remember that while \Miith{} is a dark, horrible and cruel world, it is also epic, glorious and filled with splendid wonders. 









\subsection{Ancient history}
Be sure to have lots of references to ancient history, and the wars of old. 
Let the immortals talk about it. 
Compare to Drusas Achamian's dreams in \authorbook{R. Scott Bakker}{Prince of Nothing}. 







\subsection{Armies}
\target{Glorious armies}
Whenever there's a war or an army, remember to portray it in an epic manner, emphasizing the splendour and glory of the soldiers, and of war as a whole. Describe the vast size of the forces, the shining, deadly steel, their mighty war machines, their billowing banners and awesome fanfares.

This is also a way to combine darkness and epicness. 

Compare to \bandsong{Bal-Sagoth}{And Lo, When the Imperium Marches Against Gul-Kothoth, Then Dark Sorceries Shall Enshroud the Citadel of the Obsidian Crown}. 

\citeauthorbook[p.69]{RobertEHoward:KullUntitledDraft}{Robert E. Howard}{%
  Untitled Draft%
}{
  The cavalcade moved forward at an easy trot.
  The people of Valusia gazed curiously from their windows and doorways and the throngs on the streets turned as the clatter of silver hoofs resounded through the babble and chatter of trading and commerce. 
  The steeds flung their caparisoned manes; the bronze armor of the warriors glinted in the sun, the pennons on the long lances streamed backward.
}









\subsection{Mystic names and places}
\target{Mystic names}
I should spam throwaway references to mystic places and names all over the place, like Shung in this passage:

\citeauthorbook[p.254--255]{HPLovecraft:TheBlackTomeofAlsophocus}{H. P. Lovecraft}{%
  The Black Tome of Alsophocus%
}{%
  I \travelled faster than thought, past unlit planets and vistas of unknown realms which swirled and shifted across immensurable distances; the stars flashed by so rapidly that they appeared as gossamer-fine threads of brightness interlaced across the universe, minute shooting stars of brilliance shining against black aether that was darker than the fabled depths of Shung.
}

And dark, mystic, violent background events, like in \bandsong{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}.









\subsection{Very large castles and cities}
Cities and castles should be huge. Such as the {\Malcuric city gates}.

The ancient citadels are near-impregnable. They are as good as indestructible and can only be captured by a lengthy siege or by treachery.















\section{Eschaton}
\target{Eschaton}
A major theme of the whole series is that of the world ending. 
Through the books of \SentinelsofMithEmph, this must be developed. 

As the \thirdbanewar progressed and the Shroud continued to \hr{Unravelling}{unravel}, the world went more and more mad. 

See also the section about how the \hs{Unravelling brings chaos}. 

Several years passed in all.
The world went more and more to Hell. 
Conditions became worse and worse.
Horror and madness reigned.
Chaos engulfed the kingdoms of mortals. 

Compare to \cite{RPG:CallofCthulhu:EndTime}. 

Examples of this:
\begin{itemize}
  \item 
    In \RamielsAwakeningBook, \hr{Eschaton: RamielsAwakeningBook}{it was getting pretty bad}. 
  \item 
    In \ThirdBanewarBook, \hr{Eschaton: ThirdBanewarBook}{all Hell was about to fully break loose} and \hr{The world goes mad}{the world was going mad}. 
\end{itemize}
















\section{Mystery: Hint, don't show}
\target{Hints}
Make sure the \Miith series stays mysterious even as it goes on and more is revealed about the world. 
I should only slowly and gradually reveal more about the \Archons, \Taorthae, \arcana, \Primordials, \xss, \banes, \Lithrim, \neoresphain, cosmic gods, \Sethicus and the myth of the \hs{dead universe}. 

Drop hints all over the place about the background histories of \dragons, \resphain and \banes. 
Archibald Curwen and Moro \Cobrel, among others, knew fragments of myths that hinted at the truth. 

I want to show rather than tell, and hint rather than show. 
The dark world and the great supernatural menaces should be mysterious, hazy, seen only in glimpses.













\section{Quotes}
This is a collection of quotes from music, literature and other things that might be cool and serve as inspiration.









\subsection{Bal-Sagoth}
\subsubsection{A Black Moon Broods Over Lemuria}
\lyricsbs{Bal-Sagoth}{Dreaming of Atlantean Spires}{The Topaz Throne is beckoning, the jewelled sword awaits my grasp\ldots{}}

\lyricsbs{Bal-Sagoth}{Spellcraft and Moonfire Beyond the Citadel of Frosts}{
  Black stone stummoning the eternal power of the winter Moon\ldots{}
  
  Sorcery opens fiend-haunted pathways before me\ldots{}
  
  Dark spellcraft summons the Black Gate before me\ldots{}
  
  Icy waters whispering.\\
  Tower of Silence hides the shadow-key.\\
  Ember-trees haunt my fevered dreams.\\
  Moon-Bride, sing thine dark enchantment.
  
  Elder shadows writhing before the silvern gate of eternal winter.\\
  Dark shapes entwine the mist-veiled cromlech.\\
  Dynig torchlight gleams on silent black waters.\\
  Fen-wolves sing to the gibbous Moon\ldots{}
}

\lyricsbs{Bal-Sagoth}{A Black Moon Broods Over Lemuria}{
  As a black Moon broods over Lemuria,\\
  ebon witchfire enshrouds the gleaming citadels,\\
  Sinistrous shadows rise from the vaults of the dreaming elder gods.\\
  Ophidian eyes glimmer through the icy whispering Moon-mist\ldots{}
  
  Winter Moonlight gleams through crooked boughs.\\
  {The icy caress of night entwines the eon-veiled Obsidian Tower}.\\
  The whisperings of ancient tongues are borne upon the winds.
  Dark time-lost spells hold the key \\
  to the frost-veiled Gate of the Black Moon\ldots{}
}

\lyricsbs{Bal-Sagoth}{Enthroned in the Temple of the Serpent Kings}{
  Deep within the glacial, ice-veiled temple,\\
  ancient enchantments summon the shades \\
  of the dreaming Serpent Kings,\\
  and the Ophidian Throne once again draws power \\
  from the Moon-shrouded crystal.
  
  Storm-borne bride of winter's fire, \\
  serpent-witch of the whispering fens.
  
  Frost-garlanded, the mind-binding \\
  \emph{glimmer of tear-filled Ophidian eyes}.
  
  The wyrm-horn sounds 'cross Dagon's mere\ldots{}
}

\lyricsbs{Bal-Sagoth}{Shadows 'Neath the Black Pyramid}{
  I am enraptured by Ophidian eyes.
  
  In the vaults of the dreaming gods, \\
  shackled to the slime-smeared bleeding stone\ldots{}
}

\lyricsbalsagoth{Witch-Storm}{
  The skyqueen of the dead rides forth,\\
  black storm-borne steeds, immortal blood.\\
  Hark to the striking of the winds, \\
  the moon burns black as slaughter reigns.\\
  Witch-Storm!
}

\lyricsbs{Bal-Sagoth}{%
  Into the Silent Chambers of the Sapphirean Throne 
  (Sagas from the Antediluvian Scrolls)%
}{
  Grim-eyed legions wait brooding\\
  'neath the banner of the Serpent King.
  
  The Atlantean sword beckons me,\\
  and I descend from Moon-shrouded skies \\
  into the Tower of the Black Serpent.
  
  And lo, I hear the beat of black leathern wings from Moonless gulfs. \\
  Dark spirits wander the silent halls of the Sapphirean Throne.\\
  And in dreams I see the ocean rise to devour the gleaming spires\\
  as the shades of immortals guide me to the Valley of Silent Paths\ldots{}
  
  The Topaz Throne of Kings is crack'd,\\
  aeon-veiled, enrob'd in black.
  
  Black wings above the land of dreams\ldots{}
  
  The ivory worm now sleeps entombed.
}





\subsubsection{Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule}
\lyricsbs{Bal-Sagoth}{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire
}{
  I see a land far to the north\ldots{} \\
  a vast empire of dark endless moors and snow-crowned mountains\ldots{} \\
  a land of brooding citadels and warrior-kings who hail to grim gods.
}





\subsubsection{The Chthonic Chronicles}
\lyricsbalsagoth{The Fallen Kingdoms of the Abyssal Plain}{
  We know of the hidden and silent places, the places which reside in between the veils of reality, the places which mankind was never meant to see.\\
  All this we know\ldots{} we who survive, we who are descended from those First Ones, and who give thanks to the gods-who-are-not-gods, for our creation, our genesis, for the breath of life that was forced into our progenitors during the early epochs of this cratered globe.\\
  Hearken, children of the Ersatz gods, sons and daughters of the New Earth, for here is truth\ldots{}
}









\subsection{Warhammer 40,000}
\lyricsauthorbookpage{Ben Counter}{Galaxy in Flames}{114-118}{
  \ldots{} a vision of broken steppes spread out before Loken, expanses of desolation and plains of rusted machinery like skeletons of extinct monsters. 
  A hive city on the distant horizon split open like a flower, and from its broken, burning portals rose a mighty tower of brass that punctures the pollution-heavy clouds. 
  
  The sky above was burning and the laughter of Dark Gods boomed from the heavens. 
  
  \ldots{}
  
  He wrenched his mind away from the dying world, and suddenly he was soaring through the galaxy, tumbling between the stars. 
  He saw them destroyed, bleeding glowing plumes of stellar matter into the void. 
  A baleful mass of red stars glowered above him, staring like a great and terrible eye of flame. 
  An endless tide of titanic monsters and vast space fleets vomited from that eye, drowning the universe in a tide of blood. 
  A sea of burning flames spat and leapt from the blood, consuming all in its path, leaving black, barren wasteland in its wake. 
  
  \ldots{}
  
  \emph{You are seeing the galaxy die.}
  
  \ldots{}
  
  Loken could see it where the flames burned through, the endless churning mass of the warp at the heart of everything and the eyes of dark forces seething with malevolence. 
  \ldots{}
  Bloated monsters, their bodies heaving with maggots and filth, devoured dead stars as a brass-clad giant bellowed an endless war cry from its throne of skulls and soulless magicians sacrificed billions in a silver city built of lies. 
  
  \ldots{}
  
  Sindermann had been right. 
  Loken was hearing the music of the spheres, and it was a terrible sound that spoke of corruption, blood and the death of the universe. 
}







\lyricsauthorbookpage{Ben Counter}{Galaxy in Flames}{211}{
  Images tumbles through his brain, dark and monstrous, and he fought to hold onto his sanity as visions of pure evil assailed him. 
  
  Death, like a black seething mantle, hung over everything.
  
  Tendrils of darkness wound through the air, destroying whatever they touched. 
  He screamed as he saw the flesh sloughing from Mersadie's bones, looking down at his hands to see them rotting away before his eyes. 
  His skin peeled back, the bones maggot-white. 
}







\lyricsauthorbookpage{James Swallow}{The Flight of the Eisenstein}{262-265}{
  She screamed and flailed at him, beating her hands on his chest plate. 
  He could see now where her hands were bloody with self-inflicted scratch marks. 
  \ta{Eyes and blood,} she wailed. 
  \ta{But inside the pestilence!}
  
  \ldots{}
  
  \ta{Unclean, unclean! \ldots{} 
  I have seen it! Inside the eyes!} 
  She tore wildly at her face, ripping the skin and drawing blood. 
  \ta{You see it too!}
  
  \ldots{}
  
  The adjutant\ldots{} pressed into him and raked bloody fingers over his torso. 
  \ta{You see!} she gasped. 
  \ta{Soon the end comes! All will wither!}
  
  \ldots{} The woman's upturned face became paper, aged and crumbling. 
  She slid away from him\ldots{} turning into rags of meat and dead flesh, ash and then nothing. 
  
  \ldots{}
  
  The resplendent marble-white of their \armour bled away to become dis\coloured by a feeble, sickly green, the shade of new death. 
  The ceramite warped and became rippled, merging with their flesh until it stained and throbbed. 
  Parasites and bloated organs pulsed within, and in some places wounds opened like new mouths, red-lipped with tongues of distended bowel and duct. 
  
  \ldots{} The malformed shapes of his warriors crowded in, words falling from their cracked, lisping maws. 
  \ldots{} 
  Beyond the men he saw a ghostly form towering above them, too tall to fit into the cramped corridor yet there before him, beckoning with skeletal claws. 
  
  \ta{Mortarion?} he asked. 
  
  The twisted image of his primarch nodded, the figure's blackened hood dipping in sluggish acknowledgement. 
  What Garro could see of his primarch's \armour was no longer shining with steel and brass, but dis\coloured and corroded like old copper, wound with soiled bandages and soiled with rust. 
  The Death Lord was no more and in his place stood a creature of pure corruption. 
  
  \ta{Come, Nathaniel.} 
  The voice was a whisper of wind through dead trees, a breath from a sepulchre. 
  \ta{Soon we will all know the embrace of the Lord of Decay.} 
  
  \tho{The end comes.} 
  The words tolled in his mind like a bell, and Garro looked down at his hands. 
  His gauntlets were powder, flesh was sloughing off his fingers, bones emerging and turning into blackened twigs. 
  \ta{No!} he forced the denial from his throat. 
  \ta{This will not be!} 
}









\subsection{Others}
\citeauthorbook[p.12]{DarrellSchweizer:TheIdolinHisHand}{Darrell Schweizer}{%
  The Idol in His Hand%
}{
  It was because Prophet stood on the deck at night talking to the darkness, and the darkness \emph{answered back}; and sometimes he would climb to the top of the mast on moonless nights and all of us \emph{knew} there was something up there with him, darker than the blackness of the night, impossible to make out except when it blotted out the stars with what might have been great wings. 
}





\subsubsection{Ancient Rites}
\lyricsbs{Ancient Rites}{Dim Carcosa}{
  Black stars shine on the ancient fortified town.\\
  The sun invisible or since long down?\\
  Over the dismal landscape\ldots{}\\
  Above Carcosa
  
  No sound, only the wind sighed.\\
  Behind mysterious moons, strange towers hide.\\
  But even more distant is\ldots{}\\
  Lost Carcosa.
  
  Tales that the Hades will sing,\\
  vague stories of a yellow king,\\
  must die untold in\ldots{}\\
  Strange Carcosa.
  
  Mysteries hidden by lake Hali's nebulous depths.\\
  A presence of bizarre beauty and dread\\\
  remains unrevealed\ldots{}\\
  In Carcosa.
  
  Above the desert high,\\
  twin suns circle the sky.\\
  Nevertheless dim still\ldots{}\\
  Is Carcosa.
  
  My voice turns weak, lost is my mind.\\
  I see, but I am blind.\\
  And no sign of life in\ldots{}\\
  Dim Carcosa.
}





\subsubsection{Clive Barker}
\lyricsbs{Clive Barker}{The Son of Celluloid (Books of Blood II p.24)}{
  \ldots{} the illusion of life created from a perfect sequence of little deaths.
}

(In Barker's story, this is a reference to movies. It can also describe comics or tapestries, which are more common in Carzain's time than movies\ldots{})





\subsubsection{\RWCTKIY}
\lyricstitle{Cassilda's song in \emph{The King in Yellow}, 
act 1 scene 2}{
  Along the shore the cloud waves break.\\
  The twin suns sink beneath the \hr{Lake in Malcur}{Lake}.\\
  The shadow lengthens\\
  in Carcosa.
  
  Strange is the night where \hr{Black stars of Nyx}{black stars} rise\\
  and strange \hr{Moons}{moons} circle through the skies.\\
  But stranger still is \\
  Lost Carcosa.
  
  Songs that the Hyades shall sing,\\
  where flap the tatters of the King,\\
  must die unheard in \\
  Dim Carcosa.
  
  Song of my soul, my voice is dead.\\
  Die though, unsung, as tears unshed\\
  shall dry and die in\\
  Lost Carcosa.
}





\subsubsection{Slayer}
\lyricsbs{Slayer}{Raining Blood}{Raining blood from a lacerated sky.\\
  Bleeding its horror.\\
  Creating my structure.\\
  Now I shall reign in blood!
}







































\chapter{Technology}















\section{Technology: By field}









\subsection{\Armour and wards}
\target{Armour and wards}
On the higher levels of technology and/or power, wards and force fields become more effective than \armour. 

High-tech and magical \armour (including \hs{ward runes} and \hs{Archon Wards}) are most effective against magic and ranged weapons. 
It is easier to protect oneself against such attacks. 
Immortals tend to be less well-protected against \melee{} attacks.
In \melee, the attacker has more direct control over his attack and the techniques and force he puts into it, so it is easier to circumvent or penetrate a static defense (such as \armour or spells). 

Among mortals, \armour was \hr{Armour in the TBW}{still in use even up to the \thirdbanewar}. 

The \resphain sometimes wore \hr{Glass armour}{\armour made of glass or crystal}. 





\subsubsection{Ward runes}
\target{ward runes}
\index{ward rune}
Ward runes are worn especially by \dragons. 
They are enchanted runes, carved on their scales or on charms and talismans, containing protective spells that act as \armour. 
In combat, they light up (or darken) with Chaotic energy and release \hr{Daemon}{\daemons} that protect against attacks/magic or heal wounds. 

The ward runes are magical \hr{True Draconic}{\TrueDraconic} \hr{Draconic runes}{runes}. 
They are often written on \hs{graph-glass}. 
The glass can represent the runes more accurately and reliably, and channel power through them more effectively, than a simple carved surface. 

Ward runes must be empowered by pouring energy into them. 
When empowered, the runes will leak and gradually lose power. 
When they are empty they have to be charged again. 
You cannot just accumulate energy in them and make them arbitrarily strong. 
Of course, they deplete faster if they see combat. 

Ward runes are \hr{Armour and wards}{most effective against magic and ranged weapons}. 

Ward runes are very mystical, dark and occult. 
\XzaiShann-themed. 
Each ward rune is empowered by a specific, named \xs. 

\citeauthorbook[p.19]{RPG:Warhammer:DarkElves}{Gav Thorpe et al}{%
  Dark Elves%
}{
  Shaped into the leering face of an Ice Daemon, the Shield of Ghrond is imbued with the power of the north wind which robs attacks of their force. 
}

Some \xs ward runes work by fucking with the attacker's mind, projecting frightening visions of the \xs.

\citeauthorbook{RPG:Warhammer:HighElves}{Andy Chambers}{%
  High Elves%
}{
  The Stone of Midnight exudes an impenetrable mist of darkness, and anyone trying to strike at the possessor will be confronted by his worst nightmares, vion of his own death and failure of all the works of his life.
}









\subsection{Computers}
There were no computers in this universe.
The laws of physics prevented them.
It was simply not possible to build those extremely small transistors upon which 20th and 21st century computers were based.









\subsection{Domestic animals}





\subsubsection{Beasts of war}
\target{Beasts of war}
\target{beasts of war}
A lot of animals were used as beasts of war, including \hr{Corgorah}{\corgoroth}, \hr{Grulcan}{\grulcans}, \hr{Lotha}{\lothae}, \hr{Muroc}{\murocs}, \hr{Nycan}{\nycans} \hr{Relc}{\relcs} and more. 









\subsection{Living machines}
\target{Living machines}
\target{living machines}
\target{living machine}
The \ophidians and \voyagers and other high-tech civilizations often used machines of flesh instead of metal and plastic. 
In some ways, super-enhanced flesh was superior to metal.

Metal was a transitory thing. 
It was useful at certain tech levels, but at levels significantly above the 20th century it became obsolete. 
There were limits to how strong and durable metal items could become and still be practical. 
Flesh enhanced with bio-science and sorcery and psionics was more powerful. 

\begin{itemize}
  \item Flesh was more flexible.
  \item Flesh could more easily be made to regenerate itself. 
  \item Flesh could wax stronger through training and exercise.
    Metal would only weaken from use and require repair. 
  \item Creatures of flesh could eat and replenish themselves. 
    Machines had to be built.
  \item Flesh is more horrible than metal. 
\end{itemize}

See the section on \hr{Weapons of mass destruction}{weapons of mass destruction} for some visuals. 

The \noggyaleth, in a sense, were such machines, \hr{Voyagers train Noggyaleth}{trained by the \voyagers} as they were. 

The \dragons \hr{Dragon living technology}{used living technology a lot} (as \hr{Resphan dead technology}{opposed to the \resphain}). 
The \hr{Dragons are living machines}{\dragons themselves were also living machines}, in a sense.

Living machines should be dark and gruesome, \trope{CosmicHorror}{Cosmic Horror}. 

Some living machines were \emph{kaij\=u}; giant monsters in the vein of Godzilla. 





\subsubsection{Symbiotes}
\target{Symbiotes}
\target{Symbiote}
The \dragons and \ophidians used symbiotes. 
These were living things that could be attached (temporarily or permanently) to the body and serve as tools. 
They were living machines. 





\subsubsection{Undead machines}
\target{undead machines}
The \draconic{} necropolises were protected and maintained by undead machines: 
Shambling, creaking hulks of rusty steel and desiccated flesh. 

\lyricsauthorbookpage{Alan Campbell}{Iron Angel}{394}{
  Machines with human skin and faces crowded among the gears and chains?
}









\subsection{Mage-smiths}
\target{Mage-smith}
\target{Mage-smiths}
\target{mage-smith}
\target{mage-smiths}
\index{mage-smith}
In all ages and cultures there were mage-smiths. 
They could make very powerful \armour that protected even against muskets.
So those who could afford it still wore plate \armour.
But lower grades of \armour were uncommon.

Mage-smiths were especially valued when it came to making melee weapons and \armour. 
They were less useful in making \hs{guns}. 
A mage-smith could pour much magic into a sword and it would make a huge difference.
Guns were easier to mass-produce, and handcrafting did not make so great a difference.
Still, some powerful guns were handcrafted.





\subsubsection{Magical items}
See the section on \hr{Magical items}{magical items}. 









\subsubsection{Magic is advanced technology}
Magic \emph{is} advanced technology. 
The more advanced a civilization got, the more it began to rely on magic. 
Cultures such as the \ophidians went through TL7 before they mastered basic magic.
After that point, magic and bio-magic gradually displaced metal tools.
So an extremely high-tech civilization might \emph{look} primitive because it did not have metal and plastic everywhere. 

The mortal civilizations of the Age of the Shroud were anomalies:
They had inherited a limited knowledge of the arcane, so they could cast magic, but they knew nothing of the many stages of technology that lay in between.










\subsection{Resources}





\subsubsection{Fuels}
Two possibilities:

\begin{enumerate}
  \item 
    The \ophidian civilization used up a lot of the planet's fossil fuels. 
    The \quiljaaran and \aryoth civilizations \hr{Aryothim used up fossil fuels}{used up most of the rest}.
    By the \Human Age, there was almost no fossil fuels left.
    This made it hard to develop any industry. 
    So the mortals didn't. 
  \item 
    There were no fossil fuels or the like on \Miith at all. 
    This meant that technology could not progress into the industrial stage unless it was accompanied by sufficiently advanced magic. 
    There was no way to make machines run except by dark, horrible sorcery and the sacrifice of living beings. 
    Life was the essential fuel. 
    
    Maybe fossil fuels existed, but it took magic to release the energy.
    The use of fossil fuels is basically burning the bodies of (formerly) living creatures. 
    
    The \hs{Rissitic ovens} were an example of the above. 
\end{enumerate}





\subsubsection{Wood}
\target{Wood is precious}
In the Shrouded Realms, wood was a fairly precious resource. 
Cutting down trees was dangerous business, for in the \wylde dwelt dangerous monsters. 










\subsection{Shroud represses technology}
\target{Shroud represses technology}
\index{repression of technology!Shroud}
The \hs{Shroud} makes it worse. 
It makes everyone stupid and narrow-minded and less capable of devising new ideas and inventions.
It affects even the master races. 

Worse yet, the Shroud can cause immortals to \emph{forget} things they once knew. 
So in some areas the technology actually \emph{dropped} after the \secondbanewar, even among immortals. 

Mortals are even more severly affected. 
They are many in number and reproduce quickly, but the Shroud makes everyone so god-damned stupid that inventive geniuses are \emph{very} far in between. 
And many of their ideas get squashed by their Shrouded neighbours who are unwilling to accept new things. 

The Rissitics \hr{Rissitic research loophole}{have a loophole}.









\subsection{Technology that looks like magic}
Have lots of technology that looks like magic. 
Such as \hs{graph-glass}.
Compare to the Cthulhu Mythos. 









\subsection{Weapons}
\target{Weapons}
\target{weapons}
\index{weapons}





\subsubsection{Energy claws}
\target{Energy claws}
\target{energy claws}
\index{energy claws}
There existed martial spells that let a warrior-mage create great claws of shimmering black energy around his arms. 
This was an \ophidian technique, employed by a few \rethyaxes. 





\subsubsection{Guns}
\target{Guns}
\target{guns}
Guns had the side effect that the noise (and maybe smell too) scared animals. 
\hr{Relcs are skittish}{\Relcs were skittish}.
So \hr{Lothae are skittish}{were \lothae}.
\Murocs \hr{Murocs are steady}{were rock-steady}.  

Cannons were big, heavy, scary things.
They were often ornate, shaped like fierce animals. 





\subsubsection{Ranged \melee attacks}
\target{Ranged melee attacks}
There existed combat techniques that let the fighter make a ranged attack with a \melee weapon. 
For example, a warrior might slash with a sword and launch a wave of destructive energy from the blade. 

For this reason, immortal fighters tended to use \melee weapons more than ranged weapons, and immortal martial arts (such as the \hr{Resphan martial arts}{\resphan \quo{Paths}}) focused on techniques with \melee weapons.
Ranged weapons were important too, but \melee weapons were often more effective overall.
A \melee weapon like a swords was versatile; you could shoot with it and also use it to defend yourself in close combat. 

A huge weapon like a \senaan could fire lancing blasts of lightning-like energy. 

Compare to the powered attacks in \cite{VideoGame:FinalFantasyVII}, \cite{Anime:FinalFantasyVII:LastOrder} and \cite{Anime:FinalFantasyVII:AdventChildren}. 





\subsubsection{Superstition}
\target{Gun fiends}
There was superstition surrounding guns. 
Commoners did not really understand how they worked. 
Superstition said that there lived little fiends inside the guns that made them fire (or misfire).
Soldiers would pray to those fiends to placate them. 















\section{Technology: By Realm}
Some Shrouded Realms had higher or lower technology than others.














\section{Technology: By time period}
\target{Technology}
\target{technology}
\index{repression of technology}
Technology advanced slowly on \Miith{}, and it was often deliberately set back or repressed (\hr{Shroud represses technology}{by the Shroud} or \hr{Dragons repress technology}{by the \dragons} or otherwise). 







\subsubsection{Weapons of mass destruction}
\target{Weapons of mass destruction}
In the \Ophidian Age, there were weapons of mass destruction made with black magic. 
Such as an \quo{Azathoth Bomb} (see below). 
The \ophidians used them. 

There were also \hs{living machines}. 


\citeauthorbook[p.201]{BruceSterling:TheUnthinkable}{Bruce Sterling}{The Unthinkable}{
  \ta{And what of the Unthinkable, eh? 
    What price have you paid for \emph{that} business?}
  
  [\ldots{}] 
  \ta{We bear any burden in the defense of freedom.}
  
  [\ldots{}]
  \ta{%
    To deliberately contact an utterly alien entity from the abyss between universes\ldots an ultrademonic demigod whose very geometry is, as it were, an affront to sanity\ldots that Creature of nameless eons and inconceivable dimensions [\ldots]
    That hideous Radiance that bubbles and blasphemes at the cneter of all infinity.}
  
  \ta{You're being sentimental. 
    [\ldots]
    We must recall the historical circumstances in which the decision was made to develop the Azathoth Bomb.
    Giant Japanese Majins and Gojiras crashing through Asia.
    Vast squadrons of Nazi juggernauts blitzkrieging Europe\ldots and theur undersea leviathans, pretying on shipping\ldots}
  
  [\ldots]
  \ta{Yes, I witnessed one\ldots feeding.
    At the base in San Diego.}
  Doughty could recall it with an awful clarity\dash the great finned navy monster, the barnacled pockets in its vast ribbed belly holding a slumbering cargo of hideous batwinged gaunts.
  On order from Washington, the minor demons would waken, slash their way free of the monster's belly, launch, and fly to their appointed targets with pitiless accuracy and the speed of a tempest.
  In their ralongs, they clutched triple-sealed spells that could open, for a few hideous microseconds, the portal between universes.
  And for an instant, the Radiance of Azathoth would gush through. 
  And whatever that \colour touched\dash wherever its unthinkable beam contacted earthly substace\dash the Earth would blister and bubble in cosmic torment.
  The very dust of the explosion would carry an unearthly taint.
}

\citeauthorbook{}{Charles Stross}{A Colder War}{
  \ta{%
    Saddam Hussein al-Takriti spent years trying to get his hands on elder technology. 
    It looks like he finally succeeded in stabilising the gate into Sothoth. 
    Whole villages disappeared, Marsh Arabs, wiped out in the swamps of Eastern Iraq. 
    Reports of yellow rain, people's skin melting right off their bones.}
}









\subsection{\Saphyrae and Draconian Supremacy}
Before the rise of the \resphain, there existed several intelligent races, but many of them were individually powerful, thus not having developed strong cultures, and/or very long-lived, thus slow to produce new ideas. For this reason, technological advances were slow. 

Still, the time between the \firstbanewar{} and the \secondbanewar{} was something of a \hr{Golden age of technology}{golden age of technology}. 

The \banes{} brought some \hr{Bane technology}{technology with them from \Erebos}, most of which was pirated from the \voyagers{}.









\subsection{The Incursion}
The \resphain{} were quite creative and made many innovative pieces of technology. Gradually, however, they succumbed to \hr{Entropy}{\bane{} stagnation} and their own immortality, and their scientific advances slowed. Still, they are in possession of many scientific marvels. 

\target{SBW technology}
At the time of the \secondbanewar, technology on \Miith was high on both sides. 
\Miithians and \resphain each had some weapons that the other side lacked, making the first battles full of nasty surprises for both sides. 

The \hr{Cuezcan}{\cuezcans} were also advanced and boasted many high technology items and inventions. 
But they were destroyed and left in ruins. 





\subsubsection{Graph-glass}
\target{Graph-glass}
\target{graph-glass}
\index{graph-glass}
Graph-glass was a \resphan{} invention. 
It was a flat piece of glass that could display text. 

Graph-glass was not inherently magical, but the \resphain used magic to manufacture it.
It was \quo{wrought with complex and subtle spells}, as \Teshrial reflected in \TwilightAngelRememberEmph.





\subsubsection{Machines}
\index{technology!machines}
The \dragons{} and \banes/\resphain{} each have their machines and their primitive industry. 

Remember that the Cabal and Sentinels have at their disposal far higher technology than the mortal \Miithians. 
Part of the \charade{} is keeping the level of technology low, so people don't come to know too much and begin to suspect.

\Draconic{} machines are cyborgs, living hulks of metal and flesh. 
Some of them are called \colossi. They are hot, chaotic, almost savage things. 

Cabal machines are dead, articial, mechanical things of metal, stone and glass. They are cold, hard and exude an aura of unyielding, cruel hardness. 

The \resphain, among other things, had a kind of machine that copied \hs{graph-glass}. 

At the time of the \thirdbanewar{} no one was close to inventing computers, though. 









\subsection{Immortals in the {Age of the Shroud}}
The immortals had a printing press, both for paper and \hs{graph-glass}.
They also had industry, which they used to produce many of their weapons, including most guns. 
(But some of them were \hr{Mage-smith}{handcrafted by mage-smiths}.)

The immortals made sure that their industry stayed in the Immortal Realms and did not trickle down into the Shrouded Realms.
They had to consider the Unspoken Covenant.





\subsubsection{Cameras}
There were no cameras on \Miith. 
They could not be built like on Earth because of the different way \Miithian physics worked. 
An eye picked up images from many dimensions and the brain sorted out most of it (because of the Shroud and other things), so that the mind saw only a few of them. 
A photograph would be a mishmash of all those images from all those dimensions. 
Without a bigger context, the eye would be unable to make sense of the images on a photograph, so it would just be unrecognizable static. 

The immortals had high enough technology that they might reasonably be expected to create cameras, but they never did. 
The \ophidians, though, could make holograms using magic. 
These holograms extended out into all dimensions and were just like physical objects. 











\subsection{The Vaimon Age}
\target{Technology repressed in the Vaimon Age}
\index{repression of technology!Vaimon Age}
In \Azmith after the \hr{Cuezcan Apocalypse}{\CuezcanApocalypse}, the \hr{Shrouding}{\SecondShrouding} and the introduction of the \charade, technological advances were brutally repressed among the slave races. 
This repression was partly done intentionally by the master races, partly \hr{Shroud represses technology}{enforced by the Shroud itself}.
Only the master races were allowed to do serious research, and they were few in number and slow to reproduce, so very little progress has been done since then. 
Still, the master races know many technological marvels and will occasionally utilize them. 





\subsubsection{Railroads}
\target{Vaimon railroads}
The Vaimons built railroads. 
These did not have automotive-driven trains on them, but they did have big wagon trains drawn by huge dinosaurs.





\subsubsection{Weapons}
\hr{Vaimon guns}{The Vaimons made guns}. 
Most of them were ordinary, but some were magical and super-powerful. 
Later, \hr{Magical Vaimon guns survive}{only the most powerful ones survived}. 









\subsection{The \Thirdbanewar}
\target{TBW technology}
In \Azmith at the time of the \hr{TBW}{\thirdbanewar}, many high-tech items were old artifacts. 
The master races had \emph{forgotten} how to make them, due to so many dying and \hr{Shroud represses technology}{the Shroud making the survivors stupid}. 
But the technology was still fairly high. 

The \hr{Vaimon technology taboo}{Vaimons had a taboo against technology}. 
Technology still marched on, but slowly.
Much technology had been lost. 
Technology was being deliberately repressed by the immortals. 





\subsubsection{\Armour}
\target{Armour in the TBW}
Among mortals, \armour was still in use even up to the \thirdbanewar. 
There were guns, true, but sturdy metal \armour still offered good protection. 

\hr{Mage-smiths}{Mage-smiths could make powerful \armour} that protected against even musket fire. 
So those who could afford it still wore plate \armour.
But lower grades of \armour were uncommon.





\subsubsection{Languages}
\target{Languages in the Scatha Age}
In \Velcad, the \hs{Vaimon language} was used as a \emph{lingua franca} among the learned. 
There were many vernaculars, including \hr{Pelidorian language}{Pelidorian} and \hr{Rungeran language}{Rungeran}. 





\subsubsection{Railroads}
\target{TBW railroads}
There were railroads, \hr{Vaimon railroads}{as in the Vaimon Age}. 

These did not have automotive-driven trains on them, but they did have big wagon trains drawn by huge dinosaurs.

In the days of the \thirdbanewar, the trains were ancient colossi. 
The technology to build them had been lost. 
They were revered as relics and seen with superstitious awe. 
They were intimidating infernal machines. 
Legends said that once the trains had been able to move on their own (without animals to pull them), powered by the fire of \daemons. 

The technology to maintain the railroads themselves was not lost, thankfully. 
They were still being maintained. 

The trains were ornate, carved in the likeness of fierce animals like \saurians or hippopotami or crocodiles or \dragons. 





\subsubsection{Urbanization}
\target{Urbanization}
\target{urbanization}
\index{urbanization}
Most countries in \Azmith in the \Scatha Age had an urbanization of maybe 20\%. 
This number is taken from \cite{DerekKeene:FeedingMedievalEuropeanCities}, which claims that 1300s England had 20\% urbanization. 





\subsubsection{Weapons}
\target{TBW weapon ranges}
\index{guns}
\index{technology!guns|see{guns}}
At the time of the \thirdbanewar, mortals in the Shrouded Realms had lower technology than in the \VaimonCaliphate. 
They still had the technology to make guns, though. 
Just somewhat less powerful. 

There were muskets and pistols. 
(Full-fledged muskets.) 
Each gun held only a single shot, though. 
And pistols were inaccurate. 

Near the \thirdbanewar, many quality guns were \hr{Rissitic economy}{Rissitic-made}. 

\target{Magical Vaimon guns survive}
History told of \hr{Vaimon guns}{the \uber-powerful guns that existed in the Vaimons' time}. 
At the time the secrets of their making had been lost, and only a few remained. 
The remaining old guns were mostly \uber-powerful magical guns. 
This led some people to think that all older guns were \uber-powerful and magical. 
This was not the case. 
Most Vaimon guns were ordinary. 
It's just that the ordinary guns had all perished, and only the \uber{} ones had stood the test of time. 

Have plenty of nasty weapons, such as stuff that fires shrapnel.
And some equivalent of scythed chariots, mounted on big dinosaurs. 
One advantage of higher technology is that I can wreak more havoc and make battles more bloody. 

See also the general section on \hs{weapons}. 



\begin{gloss}
  \gitem{arquebus}
    The arquebus was a primitive gun. 
    \cite{GarrettsBridges} claims that 
    \quo{%
      [the] early arquebus fired only about 100 yards and often would not pierce traditional armor.}
    
    Other sources claim the arquebus had the same range as a crossbow, and a faster rate of fire.
  
  \gitem{cannon}
    Cannons had a range of up to maybe 300--400 m.
    A high-powered super-cannon, such as \hr{Rungeran super-cannon}{the one used by Morgan Runger's \ishrah}, might reach 600 m when supported with spells. 
  
  \gitem{crossbow}
    \cite{GarrettsBridges} claims that crossbows \quo{had an effective range of about 250 yards}. 
  
  \gitem{trebuchet}
    According to Wikipedia, a 1400s trebuchet might have a range of about 300 m.
\end{gloss}







































\chapter{Miscellaneous}















\section{Ages of the World}
\target{Ages of the World}
\target{Age of Gods}









\subsection{Immortal view}
The immortals dealt with a number of \quo{ages}, including:

\target{Age of the Shroud}
\begin{itemize}
  \item The age of the \Ophidian Civilization.
  \item The \hr{Saphyrae}{\Saphyraean} age.
  \item The age of \hr{Draconian Supremacy}{\Draconian Supremacy}.
  \item The age of the \hr{Resphan wars}{\resphanwars}.
  \item The age of the \hs{Shroud}. 
\end{itemize}










\subsection{Mortal view}
Among mortal scholars, the history of \Miith{} is sometimes semi-formally divided into a number of \quo{ages}: 

\begin{description}
  \item[The Age of Gods aka Age of Chaos:]
    \target{Age of Chaos} 
    Everything before the advent of the \VaimonCaliphate. 
    Allegedly, \hr{Myths of vanquished monsters}{\Miith{} was ruled by Elder Races and inhuman monsters}.
  
  \item[The \Human Age:]
    \target{Human Age}
    Called the \quo{Vaimon Age} by \human{} scholars and the \quo{\Human{} Age} by nonhumans. 
    This age began with the founding of the \VaimonCaliphate by Cordos Vaimon and ended with the \Darkfall. 
  
  \item[The \Scatha Age:]
    \target{Scatha Age}
    Everything after the \Human{} Age, according to some \scathaese{} scholars living in the period. 
    Named so because most of the major empires in this period were \scatha-dominated:
    \Ortaica, \Durcac, the Imetrium, \Tepharae{}, \Velcad. 
    
    Others prefer to subdivide it into some more, shorter ages:
    
    \begin{description}
      \item[The \Ortaican Age.]
      \item[The \Tepharin Age.]
      \item[The \Velcadian Age.]
    \end{description}
    
    Whatever you preferred to call it, it was true that at this point the age of \human{} dominion was over. 
    \Redce, Geica and a few other strongholds were the last bastions of the \human-dominated world. 
    
    But \humanity{} still had an important part to play: 
    The Advent of \hr{Lithrim}{\Lithrim}. 
\end{description}

Even in the \Human Age and the \Scatha Age, the ancient elder peoples still rule \Miith:

\citebandsong{Nile:AnnihilationoftheWicked}{Nile}{
  Sss'Haa Set Yoth
}{
  Lurking Among Us Hidden in Obscurity,\\
  Descended from the Dawn of the Ages,\\
  The Children of Yig And Set, Serpent Volk.\\
  Whose Civilaztions were Ancient, Long Dead And Forgotten\\
  Before The Eldest Pyramids were Built.\\
  Man Was Not the First to Walk Upright Upon the Earth.

  Cruel, Pitiless, of a Cunning Mind.\\
  Unwilling to Relinguish Dominion of the Earth.\\
  They Are Cold, Knowing No Remorse.\\
  They hath Made UnWitted Slaves of a Blinded Humanity.
}
















\section{Domestic animals}
\target{Domestic animals}
Many cultures domesticated animals and monsters and used them as mounts, beasts of burden and in war. 

\paragraph{Cultures}
\begin{description}
  \item[\hs{Imetrium}:] 
    Used \hr{Nycan}{\nycans} and \hr{Nycaneer}{\nycaneers}, as well as \hr{Imetric monsters}{various monsters, especially sea monsters}. 
    
  \item[\hs{Rissitics}:] 
    \hr{Rissitic monsters}{Used all sorts of monsters} and dinosaurs, including \lothae, \mezolisks and \corgoroth.
    
  \item[\hs{Vaimons}:]
    Used mostly herbivorous dinosaurs, such as \hs{sauropods} and hadrosaurs and pachycephalosaurs. 
\end{description}

\paragraph{Animals}
\begin{description}
 \item[\hr{Relc}{\Relcs}:] 
    Mostly military animals.
    Armies had them, but few civilians. 
    Civilians would use other and slower animals.
\end{description}


















\section{\Draconian Calendar}
\index{\Draconian{} Calendar}
The calendar used by \dragons. 
The \quo{first year of \Draconian{} Supremacy} (1 \DS) was the year where \Tiamat{} awakened the \xss. 

Year \yic{VC} is equal to year \yds{VC}. 















\section{Forbidden books}
Have some forbidden books and the like. Compare to the sizable library of fictional books in the Cthulhu Mythos (by H.P. Lovecraft and others), of which the most well-known is the Necronomicon. 

Some of them are written in blood.









\subsection[The Bath Shem Torradj]{The \BathShemTorradjErebossha}
\target{Book of Erebos}
\target{Bath Shem}
The \BathShemTorradjErebossha{} is 
%There is a \BookofErebos, 
a book (or something) written by \hr{Semiza}{\Semiza}, containing all the dark secrets of \hr{Erebos}{\Erebos}. It details the gruesome history of the \hr{Bane}{\bane} people, how \hr{Banes are created}{they were created} (possibly by \hr{Evil Cosmic God creates Banes}{an evil cosmic god}), how they conquered \Erebos{} and wiped out all other civilizations on the planet, and eventually even \hr{Banes destroy Voyagers}{destroyed their own creators}, the \hr{Voyagers}\voyagers.
% the \banes{} and the origin of \resphain{} and \humans. 

It goes on to describe how the \banes{} ravaged their way across the universe, finally coming to \Miith{}, and how they enlisted \Semiza{} and his sorcerers and created the \resphain{} as their successors and the \humans{} as their slaves. 

It is comparable to the Empyreal Lexicon from \bandalbum{Bal-Sagoth}{The Power Cosmic}.

\lyricsbalsagoth{The Empyreal Lexicon}{
  Behold the cosmic codex! The tome of the astral abyss!
  
  Such diabolical evil\ldots{}\\
  sublime macrocosmic malevolence!
  
  Such carnage wrought with your malevolent tongue, dark one\ldots{}\\
  What unfathomable horrors dwell within the lightless corners of your cursed soul?\\
  Heed not the voice of the Lexicon\ldots{} lest its whispers drive you mad!
}

\Semiza{} also describes the \psp{\banelords}{} thousand-year-long plans that were laid, and their many weapons to control \humanity.
There are things which one, as a \human, can recognize when reading them. It is frightening reading, because it reveals a lot of things that a \human{} would not want to know. No one wants to be told that he is created as a slave of a race of cruel aliens. 









\subsection{The Star-Maps of the Ancient Cosmographers}
The \hr{Star-Maps of the Ancient Cosmographers}{ancient cosmic maps created by \Tiamat{} and \ApepNesthra}. Compare to \bandsong{Bal-Sagoth}{Star-Maps of the Ancient Cosmographers}. 

\lyricsbalsagoth{Six Score and Ten Oblations to a Malefic Avatar}{
  Lore dating from time immemorial; lore surviving in the records of long extinct civilizations, be it inscribed upon parchment now crumbled to dust, etched into the sand-whipped, glyph-scored stone of hoary temples, or committed to verbal traditions long since ingrained into some collective tribal memory.\\
  This is no globally common myth cycle, no collection of universally allegorical folk tales; it is all cold, pitiless truth!
  
  What titanic demi-gods once strode the boiling surface of the young earth, treading the shattered surface of mighty Pangaea beneath their ersatz feet?\\
  What fearsome entities were already inestimably ancient when mankind himself was naught but a collection of mindless random atoms, a viscous puddle of gelid protoplasm teeming with the raw materials of life, transient cells of primordial slime, all naught but malleable and tractable clay to be worked at by unimaginable sculptors, immortal star-spanning fiends!\\
  What inhuman eyes even now watch the inconsequential toilings of man from afar?\\
  The answers to these questions of denied primacy and direful cosmogony were too repulsively horrific to contemplate, and yet\ldots{}\\
  I knew the truth!\\
  And more terrifying still\ldots{}\\
  The Z'xulth and their villainous agents of depravity even now walk among us!
}









\subsection{The Umaja Tablets}









\subsection{Wanderers in Darkness}
\target{Poem}
\target{Wanderers in Darkness}
There exists a dark, cryptic poem, entitled \emph{\hr{Wanderers in Darkness}{\WanderersInDarkness}}. 
It is filled with cosmic dread and beauty\ldots{} and wicked truth. 

Alternate titles:
\begin{itemize}
  \item 'Neath the Black Stars. 
  \item 'Neath the Cruel Stars. 
  \item Wanderers of the Formless Land (like \bandsong{Blind Guardian}{Punishment Divine}). 
  \item Shapeless Paths. 
  \item The Nocturnal \hs{Aenigmata}. 
  \item The Black Stars' Aenigmata. 
\end{itemize}





\subsubsection{Contents}
It is originally written in \hr{True Draconic}{\TrueDraconic} with \hr{Draconic runes}{runes}. 
There is much Gnosis contained in those runes and words. 

It is really about the three sons of \hr{Khoth-Sell}{\KhothSell}. 

In some sense it is the ultimate art. But it is \emph{too} deep, too wise, too transcendent. It is gruesome and horrifying for mortals, and even for immortals.

Remember that \Nexagglachel, one of the three brothers, lives on in the \satharioth. Thus, the poem is also about them, and they are \quo{bound} by it. 

It is partially about \Nexagglachel{} and \hr{Curse}{his \quo{ghost} that still haunts the \satharioth} and wanders in their inner darkness.

All sorts of characters appear in the poem. They have titles that hide their true identities, which are known only to the wise. These identities include \Ishnaruchaefir, \Secherdamon{} and more. 

A mystic star appears: Kya'hsim. 
Compare to the Hyades mentioned in \RWCTKIY. 

It has many references to the mourning \hr{Nymph}{\nymphs}. 





\subsubsection{History}
\WanderersInDarknessEmph was written in the early centuries after the \secondbanewar and the \Shrouding. 

The poem was attributed to \quo{\hr{Melcryth}{\Melcryth}}, which was probably a pseudonym (compare to \quo{Homer}). 
There existed several different, conflicting versions. 

It was translated into the \resphan tongue by \hr{Essenai}{\Essenai}. 





\subsubsection{\Ishnaruchaefir}

\Ishnaruchaefir{} feared the poem, because it revealed a deep, sinister truth about him, his nature and his likely destiny. 
Something which he was fleeing from and did not want to acknowledge. 

The poem contained insights that could potentially imperil \Ishnaruchaefir by revealing his weaknesses. 
So \Ishnaruchaefir tried to sabotage the poem. 
At first he tried to destroy or suppress the poem, but this failed and he had to give up. 
He did, though, manage to eradicate some of the fragments that he feared. 
Then he took up another strategy. 
He planted some fake, apocryphal fragments, so there would be several versions contradicting each other, thus muddying the big picture and undermining the credibility and deeper value of the poem. 





\subsubsection{Inspiration}
Compare to \RWCTKIY.

\lyricsbs{Robert W. Chambers}{The Repairer of Reputations}{
  \ta{%
    I\ldots{} wept and laughed and trembled with a horror which at times assails me yet. 
    
    This is the thing that troubles me, for I cannot forget Carcosa where black stars hang in the heavens; where the shadows of men's thoughts lengthen in the afternoon, when the twin suns sink into the Lake of Hali; and my mind will bear forever the memory of the Pallid Mask. 
    
    I pray God will curse the writer, as the writer has cursed the world with this beautiful, stupendous creation, terrible in its simplicity, irresistible in its truth\ldots{} 
    
    \ldots{} all felt that human nature could not bear the strain, not thrive on words in which the essence of purest poison lurked.}
}

Compare to the Deck of Dragons and the Tiles of the Cedance in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}. 
 














\section{Glossary}









\subsection{Creatures}









\begin{gloss}







\begin{comment}
\paragraph{\drake}
\end{comment}
\gitem{\drake}
\index{\drake}
\target{Drake}
A group of reptile-like animals. 
They are half warm-blooded and half cold-blooded. 

Species include \hr{Ophidians}{\ophidians}, \hr{Dragon}{\dragons}, \hr{QJ}{\quiljaaran} and \hr{Mezolisk}{\mezolisks}. 

Related to, but considered distinct from, \hr{pteran}{pterans}, \hr{saurian}{\saurians{}} and reptiles. 

\meta{%
  Dinosaurs. }









\begin{comment}
\paragraph{pteran}
\end{comment}
\gitem{pteran}
\index{pteran}
\target{Pteran}
\target{pteran}
Flying reptile-like creatures related to \hr{saurian}{\saurians{}}. 
Species include the \ravcor{} and the \quilrai. 

\meta{%
  Compare to pterosaurs like \latinname{Pteranodon}.}







\begin{comment}
\paragraph{\saurian}
\end{comment}
\gitem{\saurian}
\index{\saurian}
\target{Saurian}
\target{saurian}
Any of a diverse group of reptile-like animals. 
Many species are large. 
Species include the \hr{Nycan}{\nycan}, \hr{Relc}{\relc}, \hr{Corgorah}{\corgorah}, \hr{Mulgron}{\mulgron} and \hr{Tondra}{\tondra}. 
Related to \hr{pteran}{pterans} and \hr{Drake}{\drakes}. 

\meta{%
  Dinosaurs. }















\end{gloss}










\subsection{Miscellaneous}









% \section{Other stuff}
\begin{gloss}
  
  
  
  \begin{comment}
  \subsubsection{A-G}
  \end{comment}
  
  
  
  \begin{comment}
  \paragraph{Becallios}
  \end{comment}
  \gitem[Becallioi]{Becallios}
  Imetric term for \quo{devil}. Used as an exclamation, it is a strong curse and not to be used in finer company. 
  
  
  
  \begin{comment}
  \paragraph{\dai}
  \end{comment}
  \gitem{\dai-}
  In Imetric, \quo{\dai-} can be prefixed to a name, title or pronoun to form a polite vocative. (\quo{\Dai-} is capitalized if prefixed to an already capitalized word, such as a name, but otherwise not.)
  
  
  %\gitem{Dorlinum breed}
  %Dorlinum \nycans{} are those bred in the Imetric city of Dorlinum. Especially renowned are the Dorlinum Secca, who are some of the largest and strongest \nycans{} known. 
  
  
  
  
  \begin{comment}
  \paragraph{gness}
  \end{comment}
  \gitem[gnesses]{gness}
  \index{gness}
  \target{gness}
  \target{gnesses}
  Rissitic slang for the \scathaese{} hemipenis. A male \scatha{} does not have a \human{}-like penis but two small hemipenes. 
  
  
  
  
  
  
  
  
  
  \begin{comment}
  \paragraph{god}
  \end{comment}
  \gitem{god}
  \index{god}
  \target{god}
  \target{gods}
  Generic term for \hs{immortal} beings of great power. 
  Examples include the \hs{Imetric} and \hs{Rissitic} gods. 
  
  
  
  \begin{comment}
  \subsubsection{H-N}
  \end{comment}
  
  
  
  
  
  
  
  \begin{comment}
  \paragraph{invocation}
  \end{comment}
  \gitem{invocation}
  \index{invocation}
  \target{invocation}
  \target{invocations}
  A spell that calls upon one or more entities and attempts to compel said entities to do the mage's bidding. 
  Invocations are more difficult to learn than \hs{orisons}, but more powerful. 
  
  
  
  
  
  
  \begin{comment}
  \paragraph{\ishrah}
  \end{comment}
  \gitem[\ishroth]{\ishrah}
  \target{Ishrah}
  \index{\ishrah{} (plural \ishroth)}
  A group of mages working together. 
  
  
  
%   \gitem{Mictzan breed}
%   The Mictzan is a sub-breed of the Destran race of \nycans{}. It is named for a Clictuan \scatha{} who founded the breed. 
  
  
  
  \begin{comment}
  \paragraph{\MotherTiamat}
  \end{comment}
  \gitem{\MotherTiamat}
  \Narkiza's flagship, named after the \Dragon{} Mother of myth. She is 40 metres long, carved in the likeness of a many-headed \dragon{} and armed with ten ballistae. 
  
  
  
  \begin{comment}
  \paragraph{nicca}
  \end{comment}
  \gitem{nicca}
  The hips on a \scatha{}. The Niccas are considered a sexual body part, important in determining attractiveness, and many cultures dictate that they must be covered in public. 
  
  
  
  \begin{comment}
  \paragraph{North Star}
  \end{comment}
  \gitem{North Star}
  \target{North Star}
  A star lying close to \Miith{}'s rotational axis in the northern direction. 
  It is a white star of spectral class A and one of the brighter stars of the northern sky. Often considered by astrologers to have important occult qualities. 
  The Northstar clan, in addition to their Imetric religion, venerate the North Star. 
  Called \word{Telcastora} in the \hr{Ortaican language}{\Ortaican language}. 
  (Note that since \Miith{} is not Earth, the North Star is \emph{not} the same as Polaris, which is Earth's north star at the moment.)
  \also{Northstar clan}
  
  
  
  \begin{comment}
  \subsubsection{O-U}
  \end{comment}
  
  
  
  
  
  
  
  \begin{comment}
  \paragraph{orison}
  \end{comment}
  \gitem{orison}
  \index{orison}
  \target{orison}
  \target{orisons}
  A simple spell. 
  Consists of calling upon one or more entities and making a petition. 
  Orisons are far easier to learn and cast than \hs{invocations}, but not nearly as powerful or flexible. 
  
  
  
  \begin{comment}
  \paragraph{\raebar}
  \end{comment}
  \gitem[\raebari]{\raebar}
  \target{Raebar}
  \index{\raebar}
  A member of a \baccon. 
  
  
  
  
  
  
  
  \begin{comment}
  \paragraph{Real Life}
  \end{comment}
  \gitem{Real Life}
  \index{RL}
  \quo{Real Life}, abbreviated RL, refers to the real world, as opposed to \Miith{}. I use the term when comparing \Miithian{} phenomena to those of the real world. 
  
  
  
  
  
  
  
  \begin{comment}
  \paragraph{shade pearl}
  \end{comment}
  \gitem{shade pearl}
  A pearl harvested from a rare oyster in the Far Orient, dark gray in \colour and around 2 cm in diameter. They are useful as an ingredient in a spell that creates a \quo{shroud} which conceals magic cast inside it from outside detection. 
  
  
  
  
  
  
  
  \begin{comment}
  \paragraph{sorcerer}
  \end{comment}
  \gitem{sorcerer/sorceress}
  A practitioner of \quo{sorcery}. 
  \also{sorcery}
  
  
  
  
  
  \begin{comment}
  \paragraph{sorcery}
  \end{comment}
  \gitem{sorcery}
  \target{sorcery}
  \index{sorcery}
  A word for magic. 
  Has multiple possible meanings: 
  
  \begin{enumerate}
    \item 
      Used by laymen for magic that is considered \quo{dark} or \quo{forbidden}. 
    \item 
      Used by the \hs{Iquinian Church} as a disparaging term for non-Iquinian magic. 
    \item 
      Used by the few scholars who know what \hs{psionics} are to refer to magic that involves the summoning of otherworldly entities, as opposed to pure psionics. 
      Sorcery is potentially more powerful, but also far more dangerous and risky. 
  \end{enumerate}
  
  
  
  
  
  
  
  \begin{comment}
  \paragraph{tacupien}
  \end{comment}
  \gitem{tacupien}
  A Pelidorian dance.
  
  
  
  
  
  
  
  \begin{comment}
  \subsubsection{V-Z}
  \end{comment}
  
  
  
  
\end{gloss}
















\section{Myths}
\target{Myths}
\target{myths}
Many people all over \Miith{} have myths about their history and pre-history. Some of these myths are close to the truth, others are very far from it.









\subsection{Cautionary tales}
The \Iquinian church had longer, elaborate myths telling about the things that man did not know, and admonishing man that he ought not to know and should not try to find out.
Compare to \cite[\quo{Yonath the Prophet}]{LordDunsany:TheGodsofPegana}.









\subsection{Creatures beneath the earth}
There are myths of \hr{Myths of creatures beneath the earth}{creatures beneath the earth} whose power and movement affect the surface world. 









\subsection{\Dragons}
Mortals had \hr{Myths about Dragons}{myths about \dragons}. 









\subsection{Forgotten a lot}
People remember certain things, but there are also tons of things they don't remember. 
Such as the \banes, the \resphain, the \dragons{} and the \xss{} (most people have never heard the name \quo{\xs}). 

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  My name has sunk into oblivion. \\
  Thou art blinded by false gods \\
  with a ludicrous past of two millennia.
}









\subsection{The \Feud}
In almost all \Miithian{} cultures, stories and myths are told about two secret organizations that exist in the shadows and wage an eternal war for dominion over the planet\dash{}the \hs{Cabal} and the \hr{Sentinels}{Sentinels of \Miith}. 
They are said to have existed for many thousands of years, if not forever, and the Sentinels are associated with \dragons{} while the Cabal is said to be connected with the mysterious \banes{}, but other than that, little is known about them. Some say that the Sentinels are good, nobly defending \Miith{} against the predations of the evil Cabal, whereas others claim that it is in fact the Sentinels who are evil, and yet others assert that both orders are uncaring manipulators that prey on the hapless people of \Miith{}. 

It is said that the conflict between these obscure forces has shaped the entire history of \Miith{} and that all major heroes, leaders and rulers though time have been manipulated by one (or both) of the orders\dash{}and many are the men and women in history who have been publicly accused, even convicted, of being Cabalists or Sentinels. Both organizations are said to be of otherworldly origin and to work though dark sorcery and \daemonic{} allies. 

But few and far in between are the actual, visible indications of their existence, and indeed, today many people believe that the dark orders are but myth and superstition. Most \Velcadians{} comfortably believe that all \dragons{}, or as near all as makes no difference, dwell in remote, legendary Irokas, and that the wicked \banes{} have vanished from \Miith{} many thousand years ago, if indeed they ever existed at all. Even major kingdoms and organizations know of little evidence that the twin orders exist, and so they are for the most part relegated to the realm of legends. 

Few know even fragments of the truth, and fewer still know the whole truth, but the Sentinels and the Cabal are very real and have existed for nearly ten thousand years, and their importance in \Miithian{} history, even today, can scarcely be overestimated. 









\subsection{Gods that came from the stars}
Many \humans{} have myths of gods that came from the stars long ago. This refers to the \resphain{}, who \hr{Resphain come down in spaceships}{descended in spaceships from \Merkyrah}.

\lyricsbalsagoth{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  They spoke of a prophecy foretold, \\
  an ancient and glorious legacy.\\
  A quest for the realm of legendry\\
  lost to Man since before even the Star-Lords descended.
}









\subsection{\Humans vanquishing monsters}
There were \hr{Myths of vanquished monsters}{myths about how great \human{}  heroes fought against and vanquished the evil pre-\human{} monsters that had dominated \Miith{} in the ages past}. 









\subsection{\Isphet the Destroyer}
\index{\Isphet}
\hr{Isphet}{\Isphet was an evil figure in \Iquinian mythology}, loosely based on \QuessanthIshnaruchaefir. 











\subsection[Merkyrah]{\Merkyrah}
Some \humans{} have myths about \Merkyrah, where they lived and walked side-by-side with gods and angels. And some unclear, conflicting, dark stories about something evil that crept in and poisoned their paradise. 

The Iquinians \hr{Iquinian myths of Merkyrah}{had such myths}.









\subsection{Merfolk}
There were \hr{Myths about Nagae}{myths about merfolk}.
They were really \nagae.








\subsection{Monsters}
Have myths of monsters and mythological creatures that are twisted versions of the master races and other beings. 

People very rarely see these creatures directly, and few live to tell the tale. Most people see only vague signs that the creatures exist, and so the stories twist and mutate with each re-telling. They end up as fantastic tales whom no one believes, no matter how true. The \hs{Shroud} helps this effect along by making people stupid and more closed-minded. 

\hr{Malcur}{\Malcur}, for instance, might have myths of worms, based on the \hr{Teshrial's creatures}{\ghobaleth{} beneath the city}. 





\subsubsection{Vampires}
As an example, there are myths of vampires that drink people's blood and transform people into new vampires. These are based on sightings of \hr{Resphan vampirism}{blood-drinking \resphain}. 

Of course, in truth, \resphain{} cannot transform people into new \resphain{} by drinking their blood. 

A \resphan: \ta{It is \human{} folly and vanity to believe that you could ever become like us.}









\subsection{Mother \Miith turned away}
There is a myth that Mother \Miith{} once saw that her children waged wars and destroyed, betrayed and devoured one another. 
She was angered and saddened, so she turned her back to them and closed her Heart.
That is why the world today is going downhill: 
It is deprived of the love of Mother \Miith{}. 

This is a corruption of the true story of the \hr{Heart weakened}{weakening of the Heart of \Miith}. 

Compare to the turning away of Mother Dark in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}. 
And the story of Ayen's closing the gates of Paradise in \authorseries{Alan Campbell}{Deepgate Codex}. 









\subsection{People don't believe in things}
See the section \quo{\hs{People don't believe in things}}. 









\subsection{Sky falling down}
There is a myth about how the sky once fell down upon \Miith{}. It refers either to the \secondbanewar{} or to the \CuezcanApocalypse. 

Probably the \secondbanewar. This separates the \quo{age of myths} from the \quo{age of legends}. The \CuezcanApocalypse{} separates the \quo{age of legends} from historical time. 

\lyricsbalsagoth{In Search of the Lost Cities of Antarctica}{
  [The Testament of the Winds:]\\
  Before the Third Moon fell from orbit, before the\\
  Nine Continents were formed from Pangaea's shattered surface\ldots{} 

  On the day before the Third Moon's fall from the darkened sky, \\
  on the day before the Cataclysm the stars align.
}









\subsection{Wars among the gods}
Many people have myths of wars fought between different factions of gods. This may refer to the \banewars, the \resphanwars{}, the \Merkyran{} war or even the \hr{Feud}{\feud}. 















\section{Psychology}









\subsection{Differences from real life}
\target{Races love war}
Make clear that \Miithian psychology differs from RL psychology.
In RL it is often asserted that all true happiness derives from \quo{love}, and that all other desires are hollow and unfulfilling in the end.
This may or may not be true in RL, but it is not true on \Miith.
\Resphain and \dragons alike derive genuine pleasure from conflict, from living out \quo{negative} emotions such as anger, hate and pride.

That is one reason why there has been so much war:
Peace is not happy for these warrior races.

In a sense, this means the \resphain and \dragons were inherently \quo{insane}, since they naturally tended towards behaviour that was destructive for them in the end.
They also had an unfortunate tendency to idolize and be attracted to such destructive, \quo{insane} behaviour.
That was one reason why the \hr{Sathariah social status}{\satharioth were so popular} despite their derangement (at times very obvious, as with \Zachirah). 

Ramiel, for one, \hr{Ramiel scored as Sathariah}{attracted more \resviel} because of his inner demons and darkness and insanity.

See also the section on how \hr{Resphain love conflict}{the \resphain enjoyed conflict}. 









\subsection{Inventiveness}
\target{Inventiveness}
\quo{Inventiveness} is not an intrinsic quality of intelligent minds. 
Many races lack it, such as the \hr{QJ not inventive}{\quiljaaran} and \hr{Entropy}{\banes}. 








\subsection{Madness and insight}
\target{Madness}
In some cases, madness is the key to insight. Of course, if you are weak\dash or worse, stupid\dash madness is likely to crush you, and you will never recover. But if you are strong, or more importantly, clever, \quo{madness} can be a good thing.

Remember: To be \quo{mad} simply means that your way of thinking is sufficiently aberrant that you cannot function in society. Madness is the breakdown of conventional reasoning. But recall that within the Realm of the Shroud, conventional reasoning is wrong! 

As such, the madness caused by extreme stress, despair and shock can awaken some of the primal mind within you, the pure animal mind, still (mostly) untainted by the \hs{Lie Sublime}. This can allow you to see through the Shroud and into true reality, and thus attain insight that would be otherwise hidden. 

\lyricsbalsagoth{The Dreamer in the Catacombs of Ur}{
  \ldots{} a tragic shell of the man I once knew, a man beset by imagined terrors and ever wary of the immemorial horrors which he claimed lurked at the periphery of humanity's perceptions.
}





\subsubsection{Madness and power}
Madness can be the key to mystic power. The glimpses into the Beyond that madness can grant you may reveal secrets of power. This can be instinctive, animal power such as that employed by berserkers (see section \ref{Berserkers}), or it can be sophisticated arcane power. In order to use the latter, you need to either be a mage already, or be extremely intelligent and quick to grasp new things. 

Moro \Cornel{} (see section \ref{Moro Cornel}) is an example of a character who found power through madness. 

\lyricslimbonicart{A Cosmic Funeral of Memories}{
  The night belongs to the predator\\
  to the one who dares crossing the threshold,\\
  the axis of dreams and wonders and black miracles.\\
  I see my self in the mirror of your eyes:\\
  A dark star on the celestial beautiful midnight sky.\\
  Release the inner radiance of what you have become.\\
  Brighten the night with your sacrifice.
  
  I have returned to life to speak of clairvoyance.\\
  I am the voice from the grave land of memories.\\
  Life can be only an illusion, and death a temptation,\\
  a final destiny.
}

\lyricsbs{Aeternus}{Burning the Shroud}{
  Within you it lies since the rise of your time.\\
  You've feared it, ignored, but truth never lies.\\
  Its existence marked at the birth of time.\\
  The darkness inside.\\
  The shadows that dance in your soul.
  
  To deny is to fear.\\
  Embrace the darkness.\\
  Reveal in its power.\\
  Within it lies the harmonious truth.\\
  A voyage into the cave of shadows\\
  yields the jewels of knowledge and wisdom.
  
  Does not the night\\
  and the silver moon\\
  enchant your being?
  
  The caressing whisper of the night.\\
  No harm will come to those who are true of heart.\\
  Look to the sun and the brightness shall blind you.\\
  Stare into the black embrace,\\
  the sight deepened with wisdom.
  
  Free your consciousness.\\
  Accept the reality of darkness.\\
  It has never been a place of dread.\\
  Knowledge and wisdom\\
  is given to those who seek.
  Achieve the empowerment\\
  of endless mysterious nights.
}







\subsubsection{The price of madness}
\target{The price of madness}
The power and/or insight granted by madness sometimes comes at a price. Your humanoid body is a thing of the Shroud, remember. So if you embrace madness and the Beyond, your mind will become twisted out of its Shrouded form, and your body will follow suit. 

This is traumatic in itself, so it will tend to inspire further shock, despair and madness. Which will cause your body and mind to become further twisted. 

If the power or frame you have embraced is one of the \Wylde{}, you will find your body degenerating into a more bestial form. If you are attuned to a specific kind of animal or monster, your body is likely to mutate into a form resembling this beast. Berserkers and \rangers{} are prone to this. 

Compare to Declan from Clive Barker's \emph{Rawhead Rex} (\emph{Books of Blood III}), who ends up worshipping the monstrous Rawhead as a deranged madman.





\subsubsection{Asylums}
\target{Asylums}
Have some nasty asylums where the Shroud is worn thin. These are gateways to the Beyond, where all sorts of horrors can slip through. 

Compare to the \emph{Kult} RPG, and the trope \trope{BedlamHouse}{Bedlam House}. 









\subsection{Passion}
\Dragons, \resphain, \cuezcans{} and, to some degree, \nephilim, draw much of their strength from their passions, their emotions. They are strong, assertive and ruling through and by virtue of their passions. 

But the slave races (\scathae{} and \humans) are enslaved, numbed and imprisoned as crippled weaklings in the Shroud, precisely \emph{because} of their emotions. Feelings of fear, devotion, loyalty, pride and even love, all these are things that weave the Shroud, keep it in place, and keep people imprisoned there.

Such is the deviousness of the master races: They have taken the source of their own greatest strength and perverted it, turned it into their slaves' greatest weakness. By harnessing people's emotions, they turn their own nature against them and keep them subjugated. 















\section{Slavery}
\target{slave}
Many nations have slaves. Pelidor and Runger are among them, as is Belek. 
\Redce{} and the Imetrium are perhaps the only major kingdoms that outlaw slavery. 

The \Velcadian{} church approves of slavery, because there is a natural hierarchy in the world, which people should just accept. Remember, humility and servitude are important \hs{Iquinian} virtues. 

The Redcor oppose nominal slavery, but as it turns out, the Redcor world view places pretty much everyone else as a rightful slave of the Redcor. They see themselves as the natural ruling caste because of their superior insight and virtue, and as a result, everyone should bow down to them, revere them as demigods and obey their least whim. At least, this is the impression that Carzain gets of them. Which makes him hate their guts. 

The Imetrians have \hr{Imetric slavery}{enforced labour for criminals}, which is practically slavery. 

Geica has a system where \hr{Geican slavery}{deeply indebted people end up as practically slaves}. 















\section{Sterilization}
\target{Sterilization}
There exists a Chaos spell that can permanently sterilize a \human{} woman. 
It works by attaching a \hr{Daemon}{\daemon} to the woman's womb. 
Whenever she gets pregnant, the \daemon{} will kill and devour the child, feeding on its lifeforce. 
This is horrible\dash the mother feels her baby's pain as it dies. 

There is also a \qliphah{} that can achieve the same result, but nicer and without the pain. 
(%
  Maybe the child still feels the pain. 
  It's just \hr{Dweomer filters}{filtered away} though the \Itzach{} Shroud so the mother doesn't realize it.%
) 

All this works only on \humans{}. 
Other races require different spells. 























\section{Story ideas}
\subsection{Names}
Some cool names that I might use:

\begin{description}
  \item[From the Hebrew Bible:]
    \ 
    \begin{itemize}
      \item Athraim (from the Bible, Numbers 21:1).
      \item Azariah/Azariel. 
      \item Bethsaida.
      \item Cushan-Rishathaim (from the Bible, Judges 3:8).
      \item Ishbaal (from the Bible; 2 Samuel 2:8)
      \item Issachar (from the Bible; son of Jacob and Leah).
      \item Mahalath (from the Bible; daughter of Ishmael and wife of Esau). 
      \item Shadrach. 
      \item Shephatiah (from the Bible; 2 Samuel 3:4)
    \end{itemize}
    
  \item[Others:]
    \ 
    \begin{itemize}
      \item Capharnaum.
      \item Corozain.
      \item 
        Dante.
        With his two sons: Dexter and Sinister.
      \item 
        Urax: 
        A cruel warrior god. 
        Compare him to the Egyptian Unas, as featured in the song \bandsong{Nile}{Unas, the Slayer of the Gods}. 
    \end{itemize}
\end{description}











\subsection{Attacking a city to draw out your enemies}
Someone attacks a city in an attempt to force their enemies to come out of hiding and face them. 

Perhaps in connection with \Malcur in \TwilightAngelRememberEmph. But maybe not. 









\subsection{Body-snatcher}
Maybe have a creature that slowly steals a person's soul and causes his body to rot and decay, as the creature steals his form and identity. 

Inspired by the monster from Clive Barker's \emph{Human Remains} (from the \emph{Books of Blood III}). 









\subsection{Collector of souls}
Have a character who goes around seeking out sorrowing lost souls, people who have nothing left to live for and only suffer. He kills them, then absorbs and binds their souls. He taps their sorrow, tears and pain. 

\ta{They were suffering anyway, but in this way, their suffering has a purpose. That is my gift to them.}









\subsection{Colour vision}

\target{Curiet's colour vision}
Curiet is a fop who cares very much about his clothes. Remember to have a scene where he talks about some \hr{Scathaese colour vision}{\colour nuances that only \scathae{} can tell apart}.









\subsection{Crying for your lost loved ones}
Have scenes where people cry for their killed loved ones. 

Be cruel! Be evil! Be cynical! Be grim! Be necr0! Be simultaneously grim and necr0 if at all possible. 









\subsection{Ghostly scene with a monster}
Have a scene where suddenly everything turns quiet, misty, ghost-like. And then a monster appears from out of the Beyond. 

Like in the anime \emph{Devil May Cry}, episode 2. 









\subsection{Girl is unable to kill}
Have a scene where Guy tells Girl: \ta{Kill me!}

Girl: \ta{No! I can't!}

Guy: \ta{You must! It's our only chance!}

Girl: \ta{No!}

In the end, she doesn't. As a consequence, they both die a horrible death. 

This is a subversion of the scene in episode 18 of the anime \cite{Anime:TrinityBlood}, where Esther refuses to kill Ion.









\subsection{Killed and dismembered victims are left to be found}
A villain kills his enemy's family and friends and leaves their mutilated, tortured corpses where his enemy will find them. Psychological terror, to fuck with the enemy's brain. 

The victim ends up going half-mad and seeing into the Beyond, in the style of the \emph{Kult} RPG. 









\subsection{Lying oracle}
Maybe have a lying oracle, hired by the Cabal or Sentinels to lead people astray, or onto the paths that their masterminds desire. 









\subsection{Mutilation}
Have a scene where a monster kills and mutilates people, leaving behind horribly mangled corpses. Perhaps hung on stakes or hooks from the ceiling, or burned, or with their skin peeled off. Blood, rivers of blood.









\subsection{Possession}
Something with monsters that possess people and take over their bodies would be cool. Weak people can be possessed easily, but strong people can fight back, being controlled only imperfectly and with difficult. Compare to the story of \quo{The Madness of the Black King} in \emph{Diablo}. 









\subsection{Regrettable sacrifice}
Someone badass, possibly \hr{Ishnaruchaefir}{\Ishnaruchaefir}, wants to sacrifice an annocent for some purpose. Someone objects. 

\Ishnaruchaefir: 
\ta{Regrettable, yes. 
  But necessary. 
  Very well. 
  Let us divide the workload between us. 
  I will do the deed, and you can regret it. 
  How does that sound?}





\subsubsection{\Resvil{} vore sex}
Have an erotic vore scene where a \resvil{} has passionate sex with a food slave, all the while gradually devouring him/her. 
Perhaps even feeding bits and pieces of him/her to her other sex slaves, as a special boon to those who have served her well. 

See section \ref{Resphan food slaves}. 

Compare with the \emph{Morbus Gravis} comics.




















