\bookchapter{Ilcas Northstar}

\begin{comment}
\section{Pre-\Bryndwin}
\end{comment}
\begin{comment}
\subsection{Meditation}
\end{comment}
\stamp{\dateDayAfterMutiny}
  {\hs{Heropond Forest} \\
   Early morning}


% It's early morning. 
% Carzain is doing his daily resonance meditation. 
% He does it to attune himself to the \Archons{} so he can invoke them. 
% \quo{Gain their trust}, some people call it. 
% Others, \quo{prayer}. 

Carzain sat down and was about to commence his daily \hs{resonance} meditation, to attune himself to the \sephiroth{} and \qliphoth. 
It was his first resonance meditation after the possession incident. 
And now he hesitated. 

\tho{%
  Is this a good idea? 
  Can I do this?
  My \Archon-summoning didn't work out so well the last time. 
  I lost control. 
  I opened myself up to the Midnight Circle. 
  I did not consciously let them in, but I approached them. 
  I bared myself to them. 
  Only for a moment, but it was enough. 
  They slipped into my mind and took control of me. 
  
  Yes. 
  That must have been what happened.}

He was afraid to open up to the \qliphoth{}, for fear that the same thing would happen again. 
That he would lose control. 

\tho{Get a grip of yourself, Carzain!} he scolded.
\tho{%
  The purpose of the resonance is to gain power over the \Archons{}. 
  If you don't properly bind them to your will, the risk is all the greater that they break control when you try to invoke them. 
  So the literature warns.}

That was the Geican teaching. 
The \Iquinian{} clans taught that the \sephiroth{} were gods to be worshipped and the \qliphoth{} devils to be shunned. 
But Clan Geican taught that both were simply forces to be channelled and employed. 
Religious preconceptions aside, the Geicans simply observed that is was the Vaimon who commanded the \Archon, not the other way around. 

\tho{%
  Worship. 
  Fear. 
  Religious nonsense. 
  Who needs it? 
  No. 
  The Vaimon must exercise his will and master the \Archons, compel them to his bidding. 
  Not let them dominate him. 
  A competent Vaimon knows which \Archons{} and feats are within his ability and which are beyond him, and he knows to keep his mind free of the influence of dangerous \Archons.} 

\tho{%
  Yes. 
  Lack of self-discipline. 
  That was what caused it. 
  It must have been.
  More resonance is the key, not less.
  I must hone my will.} 

He chuckled. 
\tho{%
  Show those \qliphoth{} who's boss. 
  So it won't happen again.

  And stay away from the Midnight Circle.}

\begin{comment}
He begins his meditation. 
First he invokes \KorRashad{}. 
He makes the \qliphah{} a part of his mind. 
Thus protected, he ventures forth into the \empyrean. 

He invokes some \sephiroth. 
Some of the central ones that guide you through the \empyrean. 
Then he calls on the \qliphoth{} Thuin and Thaid. 
And he goes on to commune with all the \Archons{} he knows and needs to resonate with. 
\end{comment}










\begin{comment}
\subsection{Back to civilization}
\end{comment}
\stamp{\dateIlcasNorthstarIntroduction}
  {\hs{Heropond Forest}, near \hr{Bryndwin}{\Bryndwin}}

\ta{We are here!} Nishain pointed. 
\ta{You can make out the watch towers there behind the hill. See?}

And true enough, as they left behind the gloom of the thickest forest and entered the sparser forest edge, Carzain could see the wooden watch towers of \Bryndwin{}. As one ventured from \hr{Scyrum}{\Scyrum} into Heropond, \Bryndwin{} was the last major town before the land declined into \hr{Wild}{\Wylde}, with only scattered, half-savage villages and tribes. 

Carzain, having spent much time the last few days studying the maps, contemplating how to escape in case of a mutiny, had a good idea of their position and believed that they could reach \Bryndwin{} in less than two days, so after he and his father had recovered mentally from the attack, he had motioned that they turn back into \Scyrum{} and head for \Bryndwin{}. The way back had been longer than he had expected, but only slightly. 
\hs{Leglan's Pass} might be in decline, but it was not yet fully reclaimed into the \Wylde{}. Out there, it was said, chaos ruled; paths never stayed the same for long, as the land itself seemed to twist and warp, defying mortal reason. Carzain didn't know if he believed that... 
\tho{%
  but these past days I have experienced things firsthand that I wouldn't have thought possible. And I am supposed to be educated in the mystic aspects of the World.}

\tho{At any rate, good thing we're out of that Hell's kitchen.}

The \hr{Belwan}{\belwan} had been scared witless after the battle and it had taken them some time to calm it again. 
Fortunate that the animal had been securely tied to a tree; 
otherwise it would have bolted and they might never have seen it again. 
But they had, after all, been prepared for trouble\dash{}why else hire guards?\dash{}and so the \belwan{} had had to be tied well to keep it from running away at the sound of trouble. 

Carzain was pondering the weird possession the other day, making little progress in understanding what had happened. Suddenly it struck him: 
\tho{%
  That voice in my head... 
  it did not speak \maybehr{Velcadian language}{\Velcadian}. 
  It spoke \maybehr{Vaimon language}{Vaimon}. 
  \maybehs{Archaic Vaimon}, at that! 
  It is a wonder I understood it at all.} 
He frowned. 
\tho{%
  Some possessing entity speaking Archaic Vaimon... is this a clue vital to solving the puzzle, I wonder?} 

His musing was interrupted when his father spoke. 
\ta{Well,} said Nishain, 
\ta{%
  if we are re-entering civilization, I suppose we had better look presentable. I will need to groom myself and change into some cleaner clothes.} 

\ta{Yes,} said Carzain. He felt his cheeks. 
\ta{Hm. I need to shave. I must look like a bearded savage.} 
This last part was a joke. Carzain had no particular prejudice against beards. But it was Geican custom to choose a particular style of appearance for oneself and then dilligently maintain it. This symbolized the freedom to choose one's own destiny, a central tenet of Geican philosophy. Nishain followed this principle: He wore a bushy black moustache but kept his chin smooth, and his curly black hair fell to just below the ears. His son, only half-Geican, had adopted this custom of his father's people: He kept his face clean-shaven and let his wavy black hair fall to his shoulders. But these past few days, worry and stress had caused him to neglect shaving. 

He procured a mirror from their bags, then reached into \hr{Itzach}{\Nieur} and invoked: 
\ta{\hr{Gavron}{\Gavron}.} 
\Gavron{} was a \hr{Circle of Dusk}{Dusk} \hr{Qliphah}{\Kliffah} that Nishain had discovered and whose power was used to cut things in half. This discovery had been his chief contribution to the academia in his youth as a Vaimon scholar in Geica. The \Kliffah{} was not very powerful and could not cut through large objects\dash{}or only with difficulty\dash{}but the cuts were fine and could be made with great precision. \Gavron{} was difficult to control, but with enough practice it could be used for highly delicate tasks. Carzain had taken up the habit of invoking \Gavron{} to shave every morning, not so much for the convenience of not needing a razor, but more for the exercise in concentration and precision with magic. It was delicate and difficult work, and when he first began doing it he had frequently needed to have his mother patch him up after having cut himself, but he had kept on, to his mother's chagrin, and after a few years had mastered it. 

As Carzain shaved, he could sense the presence of the \Kliffah{}. He could not \emph{see} it, of course\dash{}although it was said that the greatest of Vaimons could physically see the Archons\dash{}but he envisioned \Gavron{} as a small black imp that cut with its sharp claws and teeth. The work required care and strength of will, for the chaotic imp was savage and murderous, as if enraged at being coerced into the mage's service, and as such it must be held fast in check, lest it lash out and slash its would-be master. It was also a slow process, much slower than shaving normally with a razor. The magic of the \Archons{} was an art, not a quick convenience; so he had read in more than one book on magic. 

When he finished shaving and combing his long hair, he decided to put on some of his favourite clothes: A jacket with matching trousers, black and with a white tiger embroidered on each part. It had been a gift from Joyce Magenta, a former lover of his. Joyce was one of the richest women he had bedded, the wife of Giles Magenta, a master tailor and a wealthy merchant. Carzain wanted to look his best today. 
He had ventured into the \Wylde{}, fought his first battle and won, and was now returning to civilization, and he felt that this special occasion warranted some ceremony.

He turned about to study the forest behind them. It looked even darker, thicker and more menacing than it had before, as if bitter at having let them escape. Beyond the first line of trees, the land was shrouded in \wildfog{}, seemingly impenetrable and mystical.

Carzain tried to repress a shudder but failed. Then he turned to face the town again, smiling to himself. \Bryndwin{} was no city, and no one would be awaiting his triumphant return, but Carzain, having had his first taste of glory, intended to march through the wooden gates like a conqueror. 



\begin{comment}
\section{\Bryndwin}
\end{comment}
\begin{comment}
\subsection{The Imetric caravan}
\end{comment}

\new
\ta{Father, look! All those wagons...} Having passed the gates, they could now see the market square in \Bryndwin{}. There, a surprising sight awaited them. 
%There they saw a column of large wagons. 

Nishain's eyes widened. \ta{It is an \hr{Imetrium}{Imetric} caravan!} In the middle of the market square, they could see a column of large wagons, clearly identifiable as Imetric by the flags hanging from several of them: A four-spoked star, white and edged with blue, within a larger circle of black against a white background. The people of the Imetrium were not known for their subtlety and tended to display their symbol wherever they went. 

Carzain counted ten or twelve wagons and more than a score of Imetrians around them. All the soldiers wore the Imetric star on their garb, as did several of the civilians. He looked around in the square and saw several more Imetrians scattered about doing business. Most of them were \hr{Scatha}{\scathae}, but there were also \humans{} among them. %, and even the occasional Meccaran. 

%But the most unusual aspect of the caravan was not the people but the animals. 
Some of the carts were pulled by \hr{Belwan}{\belwans} or \hr{Relc}{\relcs}\dash a thirteen-foot-long, green, quadrupedal, herbivorous \saurian{} with an elaborate antler-like crest on its head. 
Yet others were pulled by a \hr{Mulgron}{\mulgron}, a fearsome beast from the south that the Imetrians had domesticated. Carzain had seen a few of them in Martinum, but it was still an awesome sight. 
It was a huge beast, thirty feet long, covered in strong, black scales. It stood on four thick legs and had a short tail, but the fiercest part of the beast was its head. Counting the armoured frill covering its neck, the head alone was almost ten feet long. Two massive horns jutted forth from its forehead, a third horn from the nose and two horn-like spikes protruded from the sides of the head. 
%It was a \mulgron, a fearsome beast from the south that the Imetrians had domesticated. Carzain had seen a few of them in Martinum, but it was still an awesome sight. 
%The \Bryndwiners{}\dash{}none of whom had seen such a creature before, Carzain thought\dash{}chose to steer well clear of the giant monster. 

And the \mulgron{} was not the only exotic animal the Imetrians had brought along. 
Accompanying the soldiers were also several \hr{Nycan}{\nycans}. 
They were bipedal reptiles with long, stiff tails and two huge, wicked claws on each foot, as well as wicked-looking teeth and foreclaws. 
They were covered in feathers, red or orange striped with black. 
The smallest looked around ten feet long, and there were bigger ones. 
The \Bryndwiners{} steered clear of those as well. 

\tho{Exciting,} thought Carzain. 
\ta{Let us find out what they are doing here.} 

They drove the wagon up to the caravan and jumped down. 
% Carzain quickly regretted jumping instead of . 
Carzain instantly wished he had climbed carefully down instead. 
Pain lanced up through his wounded leg. 
% Carzain regretted that as soon as he landed on his wounded leg. 
%Carzain winced from the pain of his wounds. 
% He winced and bit back a yelp of pain. 
% \tho{I should have climbed down, not jumped like this.} 
He winced and tried to bite back a cry, which came out as a muffled yelp instead. 

\ta{I'm all right,} he insisted. 

\ta{Let us ask those two,} said Nishain, pointing to two Imetric soldiers, a \hr{Dax}{\dax} and a \hr{Sphyle}{\sphyle}\dash a male and a female \scatha. 
They approached them. 
Carzain tried not to limp. 

\ta{\tongue{Seadri is convaire, \hr{Dai}{\dai}rengoi}} said Nishain to the soldiers. 
He knew only some basic \maybehr{Imetric language}{Imetric}, and Carzain less still. 
\quo{\tongue{Seadri is convaire}} was an Imetric phrase for \quo{excuse me}. 
Or something to that effect. 
Not precisely \quo{excuse me}; the phrase had some theological meaning which Carzain did not quite understand. 
\quo{\quo\tongue{\Dai{}rengoi}} meant \quo{my dear soldiers} or something to that effect. 

\ta{\tongue{Velcar\'ino... questira?}} 
\tho{I understood that! \quo{Do you speak \Velcadian{}?}} 

The \scathae{} looked up lazily. 
The \dax{}\dash the male\dash shook his head. 
The \sphyle\dash the female\dash looked around, then pointed them in the direction of a nearby Imetrian woman. 

%\ta{\tongue{Leptassin},} said Nishain, meaning `thank you'. 
Nishain thanked them, and the Vaimons moved on. 

They approached the woman. 
Nishain repeated his question to her in Imetric: \ta{\tongue{Seadri is convaire, \dai{}figre. Velcar\'ino questira?}} 
\quo{\tongue{\Dai{}figre}} meant \quo{my good woman} or something, Carzain thought. 

The woman turned to face them. She was young, dark of hair and dressed in white and black, and might be pretty if not for the hawklike nose, characteristic of many Imetric \humans. 
\ta{Yes, I speak \Velcadian,} she responded\dash but with a noticeable accent. 
She raised her right hand, palm forward, an Imetric gesture of greeting. 
\ta{I am Equin Mirai.}

Nishain did likewise. 
\ta{Justice upon you, \Dai{}Equin,} he said, now in \Velcadian{}. 
It was a formal Imetric greeting, invoking \quo{Justice}\dash{}capitalized\dash{}an important principle in Imetric theology, Carzain knew. 
\ta{I am Nishain \Shireyo, and this is my son, Carzain \Shireyo.} 

\ta{Justice upon you, \Dai{}\Shireyo. How can I help you?}

\ta{Can you tell us, \Dai{}Equin, what is purpose of this caravan?} 
%Carzain reflected that would likely have been more polite to call her `\Dai{}Equin' rather than `\Dai{}Mirai'. 

\ta{%
  Certainly, \Dai{}\Shireyo{}. 
  This caravan is part of our efforts to spread the Imetric faith. 
  We are transporting personnel and supplies to Imetric churches across \Velcad{}.}

\ta{%
  I see. 
  And where are you heading, might I enquire?}

Mirai paused. 
\ta{%
Yes, I suppose you might. 
  Given that it is a proselytizing mission it can hardly count as a military secret, so I am sure the {\IlcasStartRank} will forgive me for revealing it.} 
She laughed. 
\ta{%
  From here we head north to Icconos, then west into Pelidor, Beirod and Runger. 
  I myself am bound for Manburg in Runger, so I cannot recall where exactly the rest of the caravan will be heading after that.}

\ta{I see. How long do you plan to stay here in \Bryndwin{}?}

\ta{%
  I do not know... I believe we will depart in a day or so... but I do not know. 
  If you need to know more, you might want to speak to the \IlcasStartRank{}.}

\ta{Who?} said Carzain?

\ta{\IlcasStartRank{} Telcastora Ilcas.} 
Mirai looked around, then pointed. 
\ta{%
  There, the \dax{} with the great sword. 
  That is Northstar, the commander of the guards.}

\ta{Thank you, \Dai{}Equin,} said Nishain. \ta{Perhaps we will.} He bowed. 

\ta{My pleasure,} she replied. 
\ta{Farewell to you, \Dai{}\Shireyo.}

Nishain turned away. 

Carzain met Mirai's eyes, then made a bow of his own\dash{}smaller than his father's, almost mocking\dash{}while overtly letting his eyes run up and down her body. 
He paused at her breasts and gave a slight twitch of his mouth and eye, as if to say: 
\tho{Hmm. A bit small, but they will do.} 
He looked her in the eyes again. 
\ta{Farewell to you, Mirai.} 
% His use of her first name with no title was a deliberate tease. 
\tho{%
  The Imetrians have their family names first and personal names last, right? 
  So this should be the rudest form. 
  I hope.}
In Carzain's experience, formality and politeness was not the way into a girl's bed. 

%Carzain gave a smaller bow, accompanied by a seductive smile and a wink. \ta{Farewell to you, Mirai.} His omission of honorifics was deliberate teasing. 

%This unexpected move confused Mirai. She blushed slightly and was at a loss for words as Carzain turned away. 

Mirai's eyes widened slightly. 
Her mouth made as if to move, but she said nothing as Carzain turned away. He frowned at himself. It was less of a reaction than he had expected. He smiled ironically to himself. 
\tho{%
  Perhaps my skills have suffered after having spent so many days with nothing but a bunch of sweaty, hairy men for company. A girl of her average looks should be blushing and fidgeting, not merely staring.} 
He turned it over in his mind. 
\tho{%
  But after all, she is Imetrian. My impression is that they are more difficult to fluster than Iquinians. Less afraid of themselves. Slightly less.} 
After a moment he reflected: 
\tho{%
  Or maybe she is not average-looking at all. Many Imetrians have that nose, after all, so perhaps she is a beauty among her own people.} 
He smiled again. 
\tho{%
  Even so, I must remember to keep my skill honed. Otherwise, the beautiful girls of \Miith{} would suffer, and we cannot have that.}

%She turned away, blushing and fidgeting. Carzain smiled to himself. \tho{I still have the touch. After having spent several days with nothing but a bunch of sweaty, hairy men for company, I must remember to keep my skills honed.} 



\begin{comment}
\subsection{What to do?}
\end{comment}
\new
\ta{I am skeptical about trying Heropond again,} said Carzain. 

\ta{Yes, I agree}, said his father. 
\ta{%
  Besides, I think it unlikely that we would be able to hire suitable guards here in \Bryndwin{}.}

\ta{So... you are thinking...?}

Nishain nodded. 
\ta{Yes. The Imetrians. They might be persuaded to bring us along.}

\ta{Will they? It seems that their business is decidedly Imetric.}

\ta{%
  They might not, but we should make the attempt. It is the perfect opportunity, meeting them here as we did, and we would be fools to pass it up.} 

\ta{Yes, I suppose you are right...} 
Carzain mumbled, beginning to nod, but he knew that the decision was made. His father was not tyrannical, but he was a natural leader, and he tended to make his own decisions rather than confer and debate. This assertiveness he had passed on to his son, but even so, when the two were together, Carzain was accustomed to following his father's leadership. 

%Nishain rose. Carzain drained his ale cup and tossed a few coins on the bar. They left the tavern and returned to the town square. 
Nishain rose. Carzan drained his ale cup, returned it to the sack on the wagon and rose to follow his father. 

\ta{%
  So, we are looking for the commander that Mirai mentioned... what was his name... Northstar?}

\begin{comment}
\subsubsection{Northstar}
\end{comment}

\ta{Yes,} said Nishain, scanning the square. He pointed. 
\ta{That must be him, over there by the \nycans.} 
Carzain looked in the direction he indicated and mumbled agreement, recognizing the male \scatha{} with the large sword strapped to his back. 
He was \Tassian{} in appearance with cobalt blue scales. 
He had pronounced ridges above both eyes, but the left one was chipped; evidently a scar from a past battle. 

They approached him, circling uncertainly around the \nycans. 
Nishain, sticking his head in, managed to catch the Imetrian's gaze and spoke: 
\ta{%
  \tongue{%
    Seadri is convaire. \Dai{}vel sei... \IlcasStartRank{} Telcastora?%
  %\footnote{Northstar's name is actually \emph{Telcastora}, which is the name of the North Star in Imetric. But where speech is represented in English, I have translated Telcastora into \quo{Northstar}. Where Imetric speech is represented verbatim, I have kept \quo{Telcastora}.}?}}%
  }
}

The \dax{} smiled. 
Carzain noticed that he had a scar on his lips, just on the right side. 
\ta{%
  Yes, I am \IlcSR{} Telcastora Ilcas. 
  And I speak \Velcadian{}, if you would prefer that.}
His tongue darted out to lick his eye. 
\tho{%
  That tongue looked kind of strange. 
  But I could be wrong.
  I only got a moment's glimpse of it.}

Nishain bowed his head and raised his hand. 
\ta{%
  Justice to you, \Dai{}\IlcSR{} Telcastora. 
  I am Nishain \Shireyo, and this is my son.} 

Carzain raised his hand likewise. 
\ta{Justice to you. I am Carzain \Shireyo.} %, but did not speak. 

Northstar reciprocated the gesture. 
\ta{%
  Justice come to you, \Dai{}\Shireyo.
  You may call me \quo{Ilcas Northstar}, if you prefer. 
  That would be the \Velcadian{} translation of my name.}
Carzain imagined he detected a half-amused subtext saying, \hypota{and please do; your Imetric is awful}. 



\begin{comment}
\subsubsection{Nycans}
\end{comment}

\ta{I was told... wah!} 
Nishain began, but cut off when all of a sudden a feathered snout poked forth to his right, almost touching his face. 
He and Carzain took a step back from the huge \nycan{} that was smelling them. 
The reptile bared its teeth. 

Northstar laughed and gave the \nycan{} a sharp look. 
It closed its mouth. 
\ta{%
  Let me introduce to you my companions. 
  This is Countess, of the Dorlinum breed of the Secca race.} 
Countess took a step forward, sniffing. Northstar, frowning, studied them both for a moment, and it seemed to Carzain that something passed between the \scatha{} and the \nycan. 

Countess inclined her head. 
\ta{She will do you no harm,} said Northstar. 
He flicked the \nycan{} another look, as if to say: 
\hypota{Did you hear that? You will do them no harm.} 

There was a short pause as Northstar and Countess held each other's eyes, before Northstar spoke again: 
\ta{You may touch her if you wish.} 

Carzain raised a cautious hand and touched her snout. 
She poked him and made a rustling noise that might be a purr:
\ta{Rrrrrrhhhh!}

\ta{Haha,} said Northstar. 
\ta{Countess also wishes justice upon you, \Mr{} Carzain.} 

Still cautious, Carzain stroked the \ps{\nycan}{} snout while studying her. 
He had seen \nycans{} before, but never touched one. 
The feathers were soft, almost like the fur of a dog or other mammal. 
Countess was huge, probably close to twenty feet long and heavily muscled, looking stronger than a \relc. 
Her feathers were flaming orange with stripes of black. 
The oversized claws on her feet were a full foot long. 

He became aware of a set of eyes upon him. 
He turned and saw, at the \IlcSR{}'s right shoulder, another, smaller \nycan. 
\ta{And this,} Northstar said, 
\ta{is Razor. He is of the Mictzan breed of the Destran race.} 
The lineages of the \nycans{} meant nothing to the two \humans, but Northstar apparently felt that the \nycans, lacking surnames and military ranks, still deserved some formal introduction. 

Razor stood still, watching Carzain, but making no move to approach him. 
He was not sniffing like Countess had done, merely watching. 
Meeting Razor's eyes, Carzain was both impressed and disturbed by the intensity of the \ps{\nycan}{} gaze. % and the intelligence hinted at in those gray eyes. 
He recalled that \nycans{} were said to be telepathic, and indeed, it seemed to him that Razor gazed not merely at his body, but into his soul. 
Those gray eyes hinted at an intelligence that, Carzain felt, should be beyond any animal. 
He grew more than a little disconcerted, but he did not look away, doing his best to match the \ps{\nycan}{} stare. 

Razor took a step forward and stretched his neck, almost touching Carzain. 
\tho{Don't flinch,} Carzain tried to tell himself. 
\tho{Don't back away.} 
Caught in that hypnotic stare, he was not sure whether or not he succeeded. 

Finally, Razor snorted slightly. 
He blinked and nodded, breaking eye contact. 
Carzain took this as a sign of acceptance. 
\tho{Be pro-active,} he remembered from his teachings. 
He lifted his hand to touch the \ps{\nycan}{} head. 
%He raised a flat hand. 

Razor opened his mouth and let out an almost inaudible hiss. 
Carzain's hand froze in midair. 

Razor touched his nose against Carzain's fingers for a brief moment. 
Then he took a step back and nodded. 


%After a while, Razor relented. He blinked, then moved forward to touch Carzain's hand with his snout. He remained silent, however. 

%\ta{Impressive,} 
\ta{Razor accepts you, \Mr{} Carzain,} said Northstar. 
% {He does not usually warm to strangers this quickly.}

Razor moved to study Nishain, who had come around to touching Countess' snout. Countess purred again, then turned to meet the eyes of her fellow \nycan, giving him a seemlingly significant look. 
Razor held her eyes for a moment, then turned back to study Nishain with those deep eyes of his. 

Nishain tried to return the look. 

Many moments passed. 
Eventually, Razor blinked and nodded again. 

\begin{comment}
\subsubsection{Passage}
\end{comment}

\ta{Razor accepts you both,} said Northstar. 
\ta{That means I accept you, too. 
I have learned that Razor is a better judge of character than I am. 
%Not bad. 
%He is otherwise slow to warm to strangers. 
But we were interrupted. 
You were about to say something, \Mr{} \Shireyo?} 

\ta{Um... yes,} said Nishain. 
\ta{I understand that you command this expedition.} 

\ta{Yes, I command the soldiers, at least.}

\ta{I was also told that you will be going to Pelidor.}

\ta{Yes.}

\ta{My son and I need to travel to Pelidor. As such, we are interested in buying passage on your caravan.} After a small pause, he added: \ta{If that is possible.}

\ta{Hm.} The \IlcSR{} grunted, then paused in thought. 
He licked his eye again. 
This time, Carzain got a better look at his tongue. 
It was slightly forked at the end. 
Apparently a cut that had never quite healed. 
Probably the same cut that gave him the scar in his lips. 
\ta{%
  Well... this is a religious expedition, not a commercial one. But what is your business?}

\ta{%
  We have been on a trading excursion to Martinum and are returning to our home in \Redglen{} in Pelidor. At first we thought to cross Heropond forest, but we... thought better of it, so we came here to \Bryndwin{}. And here it was that we encountered your caravan, and we figured that we would be safer in the company of Imetric soldiers than with a bunch of random hired mercenaries.} 

\ta{I see. And what cargo do you bring?}

\ta{%
  The two of us and a wagon. That is it over there, with the brown \belwan.}

\ta{%
  Very well. Normally I would be skeptical, but Razor seems to trust you, and his judgement of people has rarely failed me. I will have to confer with my fellows. Follow me.}

\ta{Uh... we are reluctant to leave the wagon unwatched,} said Carzain. 

\ta{Hm, yes,} said Northstar. He looked at Countess. His face twitched, and he nodded towards the wagon. The \nycan{} lumbered off towards it. 
\ta{%
  Countess will watch your wagon and allow no one to remove anything from it. Now, if you would follow me...} 

Carzain was amazed by how much the Imetrian could communicate to the \nycans{} with but a grimace. 
\tho{%
  \Nycans{} are marvelous creatures. And this Ilcas Northstar is an interesting personality.} 

\begin{comment}
\subsubsection{Ulphon Nestor}
\end{comment}

Northstar led them into an inn, where they found an old \dax{} in a fine-looking robe, black and white with the star of the Imetrium on his chest. 
\ta{%
  \Mr{} \Shireyo{}, this is the \hr{Ispan}{\Ispan} Ulphon Nestor. 
  \Dai{}\Ispan, this is Nishain \Shireyo{} and Carzain \Shireyo.} 

Ulphon raised his hand in greeting, but his face wore a reserved expression. 
\ta{Justice come to you.} 

\ta{Justice come to you, \Dai{}\Ispan{},} said Nishain. 
He and his son raised their hands. 

Northstar addressed the priest in Imetric, presumably explaining their situation. 
The \Ispan{} eyed the two Vaimons suspiciously. 
After having exchanged some words with the \IlcSR{}, he addressed them in \Velcadian{}: 
\ta{Pray tell, \Dai{}\Shireyo{}, what religion do you believe in?} 

%\ta{How do we know that you are not thieves}
 
\ta{None,} said Nishain. 
\ta{%
  I am born in Geica, and my son is half-Geicanese. 
  By Geican tradition we pray to no gods.}

Ulphon frowned, so Carzain interjected. 
\ta{But I for one am interested in learning about the Imetrium.}

Ulphon's expression changed to a half-smile. 
\ta{So you wish to learn about our gods, and about justice?}

Carzain was only moderately interested in theology, but it was plain that here was an opening with the priest. 
So he said: 
\ta{%
  Of course. 
  Who does not want to know right and wrong?}

\ta{Hm.} 
Ulphon gave a satisfied smile, but then frowned again. 
\ta{%
  That is all very well, but how do we know that you are not thieves or spies?} 

\ta{We bring along a wagon loaded with expensive goods,} said Nishain. 
\ta{%
  If we intended to steal from you and then run, we would have to leave our wares behind. 
  Hardly profitable.}

\ta{As for the spying,} Carzain added, remembering Mirai's words from earlier, 
\ta{%
  I thought this was a proselytizing mission where you \emph{wanted} people to listen to you. 
  I was not aware you were carrying military secrets.}

Northstar said something in Imetric. 
The \Ispan{} replied with what sounded like a complaint. 
Northstar said some words in a harder voice. 
They discussed a while back and forth. Finally, Ulphon turned back to them and said: 
\ta{%
  Very well. You and \IlcSR{} Northstar have convinced me.} 
Northstar gave a smile at that, one which seemed rude, but Ulphon did not notice. 
\ta{%
  We will allow you passage for the price of thirty Imetric \hs{ducatae}. 
  Or twenty-two \hr{Velcadian sun}{\Velcadian{} suns}.}

Nishain assumed the stance of a shrewd merchant. 
\ta{I will give you fiteen suns.} 

Ulphon arched an eyebrow. 
\ta{%
  Actually, that was not an invitation to haggle. 
  If you will recall, we do not actually \emph{need} your business. 
  Twenty-two golden suns it is, and you will need to bring your own supplies.}

Nishain gave a small laugh. 
\ta{Heh. Very well. Agreed.}

Nothstar smiled. 
\ta{Welcome aboard, \Mr{} \Shireyo{}.}







\begin{comment}
\subsection{Razor broods}
\end{comment}

\new
Razor watched Ilcas emerge from the house again with the two \humans{} in tow. 

\tho{Interesting.} 

When he told Ilcas that he trusted these \humans, he had not been telling the whole truth. 
True, he did not believe the \humans{} were likely to betray them any time soon. 
But that didn't mean he truly trusted them. 

There was something dark in them. 

The older, moustached one definitely had the smell and feel of the ones called Vaimons. 
But while Razor did not like that smell, it was nothing new to him. 
That was not what worried him. 

The younger one had the Vaimon smell, too, but there was more to it. 
There was something about him; deeper, more sinister. 
It made Razor uneasy, yet at the same time curious. 

That was the real reason. 
He had accepted the \humans{} not because he particularly liked them, but out of curiosity. 
He wanted to be close to them, to learn more. 
To solve the mystery. 







\begin{comment}
\section{Post-\Bryndwin}
\end{comment}
\begin{comment}
\subsection{Sex with Mirai}
\end{comment}

%\begin{comment}
%\new
\stamp{\dateCarzainFucksMirai}{In a forest north of \Bryndwin}

Mirai heaved a deep sigh of pleasure, then slumped down against him, gasping. 
\ta{Gods!} she exclaimed when she had caught her breath. 
\ta{\DaiShireyo{}, that was incredible!} 
She resumed her panting, resting her head on his chest. 

Carzain smiled smugly. 
\ta{Yes. But, after all, no less than you would expect from your Emperor.}

\ta{Mmm...} Mirai began, then paused and turned her head to look up at him with questioning eyes. 
\ta{Emperor?}

Carzain's thoughts raced. 
\tho{\quo{Emperor}? Where did that come from? What on \Miith{} made me say that?} 
But he kept his composure. 
\ta{Why, the Emperor of love, of course.}

She studied him for a moment, then giggled. 
\ta{Of course.} 
She snuggled closer to him. 
\tho{Nicely salvaged, Carzain,} he thought. 

Yet as he lay there he continued to ponder. 
\tho{Why did I say that? \quo{Emperor}? What does that mean?} 

Now that he thought of it, he had felt weird while making love to her. 
He had not had time to give it any thought while it happened, for Mirai was an exceptional lover. 
\tho{Are all Imetric girls like this? 
  I should make it a habit to court them.} 

But he was digressing. 
He had been \quo{lost} in passion before, but this was different. 
Towards the end, his body had almost been moving on its own, and he had been using techniques he had never known before. 
And as he brought Mirai to her final climax, he had felt a peculiar energy in him. 
Like that of \Itzach. 

\tho{%
  No. 
  I am just imagining things. 
  I am paranoid from that incident when I lost control. 
  Now I am seeing \qliphoth{} everywhere.
  It was nothing.
  Just good sex. 
  Nothing occult about it.}

% In fact, the feeling was not entirely strange to him. 
% Attempting to separate the possession from the mounting orgasm filling his body at the same time, he recalled a sensation similar to what he had experienced a few days ago when he fought the thugs in Heropond. 
% \ta{What is happening to me? Do I have a \Qliphah{} in my head that is taking over my body?}

Eventually he stirred, gently pushing the girl off him. 
\ta{We should get back. After all\dash} mischief in his eyes 
\ta{\dash we would not want anyone to suspect.} 
\tho{%
  Also, it's dangerous out here in the forest in the middle of the night, but that's a detail...}

They got dressed and made their way back to the wagons. As they reached the edge of the clearing\dash the campfires visible though the trees\dash he pulled Mirai close and kissed her. At length pulling his lips away, he held her eyes, placed his index finger on her lips and winked. With a conspiratory smile he directed her with a pointed finger towards an opening in the trees a dozen yards to their right, then gave her hand a final squeeze and turned away, going left to enter the clearing via another opening a score yards in the other direction. So as not to be seen together. Glancing back over his shoulder, he caught her gaze once more, and she winked and her raised left hand to kiss the knuckle of the index finger before vanishing between the trees. \tho{I wonder what that gesture means. I will have to remember to ask Northstar.}

Entering the camp he espied Northstar with Countess and Razor near the head of the wagon train but somewhat apart from the rest. The \IlcSR{} looked up as he approached. 

\ta{You were right, Northstar. Like a charm.}

Northstar nodded. \ta{So, how was she?}

\ta{Not bad. Not bad.} Carzain nodded, his expression indifferent. Then he rolled eyes at himself. 
\ta{Pff. Whom am I trying to fool. Seriously, she was good! She displayed techniques I had heard about but never actually encountered. Where do Imetrian girls learn all this?} 

\ta{Haha. Well...}

\ta{Do your people spend your entire youth having sex? 
  Practicing your moves?}

\ta{Haha. No. Maybe. I don't know...} 
% We Imetrians do own decency. We do not belive in sexual anarchy like the Rissitics do\dash or the Geicans, perhaps. I am not so familiar with Geican culture. But despite that, we do not share all the unreasonable sexual taboos that the Iquinians have. We practice a... \quo{golden middle road}, some might say. Now, I do not know Equin Mirai, but she is a comely young woman\dash if I am any judge\dash and from my impression of her disposition, I would not be surprised to learn that her sexual experience was extensive. And I know that there exist... \quo{techniques}, as you say, that in certain milieus are passed around and practiced.} Carzain shot him a questioning glance, which Northstar answered with a secretive, almost teasing one. \ta{I have no more than the most superficial experience with this sort of thing. I only know it exists.}

\ta{%
  I ought to do some more extensive research into this field. And by \quo{research} I mean fuck more Imetrian girls.}

%(... some more stuff about Mirai in bed...)

When they had first set out from \Bryndwin, Carzain, taking Mirai's provocatively unimpressed stance as a challenge, had accepted and resolved to seduce her. But his initial advances had met little success, her foreign Imetric ways confusing him, and so he had gone into research. At first he had questioned Ulphon Nestor, following up on his proclamation of alleged interest in Imetric culture, but he had quickly found that not only did the clergyman have a frustrating tendency to drift away from the subject of courtship and towards that of theology, he was also a frightfully dreary lecturer. 

And so Carzain had turned to \IlcSR{} Northstar instead. Which had been a good choice. Northstar, it turned out, was a \quo{\nycaneer}. As he explained it, \nycaneers{} were \scathae{} with an inborn talent for telepathy and a particular affinity with \nycans. This was interesting enough in itself, but most significantly from Carzain's viewpoint, the \ps{\IlcSR} telepathic ability had granted him a good understanding of people's thoughts and behaviour. Amused by the young Vaimon's quest and impressed by his determination, the he had agreed to advise him regarding matters of Imetric custom and tradition, providing him with what hints he could to aid him in his mission of courtship. 

% \ta{So, tell me...} said Carzain, changing the subject. \ta{Explain again how the whole fake secrecy deal works.}
% 
% Northstar chuckled. \ta{Well, I believe it is a consequence of...} He paused for words. \ta{See, despite what I said before about a \quo{golden middle road}, the truth is that 
% %the Imetric theology's teachings 
% %regarding sexual morals are notoriously unclear. 
% the Imetric view of sexual morals is notoriously unclear. 
% Promiscuity is traditionally considered taboo, but no such prohibitions are actually given in the \Imetriad{}.
% 
% I believe this has caused us to develop a strange, perhaps hypocritical mentality: Sex is at once both permitted and forbidden. I don't know... perhaps we have some instinctive need to establish sexual taboos. Or perhaps eroticism itself thrives on the... allure of the forbidden. I don't know. But whatever the reason, we seem to have created a half-imaginary prohibition against wanton sex.}
% 
% \ta{How so?}
% 
% \ta{Well...} again Northstar had to pause to put his thoughts into words. \ta{In a way, promiscuity\dash meaning sex outside of marriage or otherwise challenging tradition\dash in a way, it is forbidden, so that if one practices it, it must be kept hidden and secret from everyone. But on the other hand, the actual consequences of discovery are minimal. There is no punishment by law, no social stigma. No cruel expulsion, like Iquinian societies practice.
% 
% The result is a game of false secrecy, of conspiracy against a fictitious menace. It is a strange thing, and I admit I never truly understood it. I was never a great player of the game, back in the day.} He regarded the \human. \ta{Nonetheless, you seem to have absorbed it readily enough, \Shireyo.}
% 
% Carzain shrugged. \ta{I've learned that seduction doesn't need to make sense. I suppose the Imetric game of hiding is no stranger than the games we play in Pelidor.}
% 
% Northstar's reply to that was a shrug and a \ta{hm}. 

% \ta{So, tell me another thing,} said Carzain. 
% \ta{Why do you call yourself \quo{Northstar}? 
%   What does that mean?}

Carzain yawned. 
\ta{Well, it has been a busy night. I should crawl into my sheets.} 

\ta{Yes. We break up tomorrow an hour past dawn or so.}

Making a few more farewell noises, Carzain headed for his sleeping place near the fire to settle in. Thoughts passed through his head as he dozed off.

\tho{A busy night. But productive. I should do this again.} 
%Thoughts such as these passed through his head as he dozed off. 

\tho{Mm... fuck more Imetric girls...} 

\tho{\quo{Emperor}...}

%\Nycans, he learned, were highly intelligent creatures, communicating among themselves using telepathy, and they tended to see the \nycaneers{} as kindred spirits, almost-\nycans\dash and the \nycaneers, instinctively, felt a similar bond to the \nycans. It was not merely the skill of communication, Northstar had explained, for mages could learn telepathy in the universities of the Imetrium, but those who were not born \nycaneers{} never developed the same affinity with \nycans, no matter their telepathic skill. They could learn to communicate well enough with the creatures, but the \nycans{} did not accept them as kin. 

%No, the \nycaneers{} were born with \quo{the heart of a \nycan}, as some might phrase it. Indeed, Northstar could relate, a few \nycaneers{} were so \nycan{} in disposition that they abandoned their \scathaese{} kin to join a pack of wild \nycans. These wild ones seldom lasted long, for physically no \scatha{} was a match for a \nycan. 

%Fascinating as all this might be, it had the\dash from Carzain's point of view\dash very convenient consequence that Northstar's telepathic ability had granted a good insight in people's thoughts and behaviour. Amused by the young Vaimon's quest and impressed by his determination, the he had agreed to advise him regarding matters of Imetric custom and tradition. 



\begin{comment}
\new
Nishain and Carzain sell some stuff that they salvaged from the mercs, and then a day or two later, they set off. 

\new
On the journey, Carzain talks to Ilcas. 

He also gets to study the Imetrians. There were eighteen soldiers and about thirty civilians. The soldiers were mostly \scathae{} and only a few \humans. Some of the \scathae{} were \sphyles, but the \human{} soldiers were all men. Women as warriors were not unheard of in the Imetrium, Carzain knew, but still rare. Among \scathae, on the other hand, males and females were evenly matched in physique and thus evenly represented in the army. Among the civilians there were more \humans, perhaps half of them, and several were women. Seven, to be exact. 

\end{comment}

%\end{comment}



\begin{comment}
\subsection{Back in \Redglen}
\end{comment}

% \begin{comment}
\stamp
  {\dateCarzainBackInRedglen}
  {\Redglen, Malcur}

\ta{%
  Are you sure it was a good idea to bring the \nycans{} into town, \Mr{} Northstar?} asked Nishain, eyeing the two giant \saurians{}. 

\ta{Well,} said Northstar, 
\ta{this is a proselytizing expedition.
  So I figured anything that draws attention might potentially help us.}

\ta{But is it even legal?}

\ta{I confess we might be stretching our non-aggression pact somewhat.
  Our countries are strictly not allies.
  But would you argue with a twenty-foot \saurian{}?}

\ta{Point taken,} said Nishain. 

They certainly drew attention in the streets of \Redglen. 
People would run for cover, then cower behind cover and gape in awe at the fierce-looking creatures. 

Carzain poked Northstar's side. 
\ta{Haha, look, there's my boy,} he whispered, indicating a pretty, young woman with a boy in tow, a toddler of two or three years with black hair. 

\ta{Your boy?} asked Ilcas. 

%Leopold laughed knowingly as Carzain responded: 
\ta{That's \Theal, Ethwar the Wood Carver's boy
  The wood carver is a fat and dreary and eccentric man, but his wife is a cute, little thing. 
  I was shagging her for a while, a conspicuous nine months before little \Theal{} was born. 
  Add his voluminous black hair and handsome features and put two and two together.} 
He gave a smug, self-satisfied smile. 
Northstar could not help but chuckle. 









\new
\ta{Well, thank you for the ride, \Mr{} Northstar,} said Nishain. 
\ta{Won't you stop by our home for some refreshments, at least?} 

\ta{All right. 
    Can I bring the \nycans?} Northstar asked with a smile. 

Nishain and Carzain exchanged glances. 
\ta{Sure, why not?} laughed Nishain. 
\ta{I am sure my wife will love them.} 

\ta{Yeah, what's not to love?} said Carzain. 

So they steered their cart towards their house, 
Ilcas and the \nycans{} following on foot. 

% Ilcas follows them to their house. 
% \Roanne{} comes out. 
Soon they reached their home. 
It was a two-storey wooden house. 
Above the door was written, in Vaimon script: 

\begin{quote}
\begin{center}
{\bf 
Vaimons \\
\Shireyo{} and \Deracille{}
}
\end{center}
\end{quote}

They climbed down from the cart. 
Carzain had learned not to jump with his wounded leg. 
It was feeling much better now, though. 
On the trip they had gotten an Imetric chirurgeon to treat it. 
For Carzain, who knew only Vaimon healing, it had been a fascinating experience for Carzain, albeit not exactly pleasant. 
Where Vaimon healing consisted mostly of visualizing mystic threads and praying to the \sephiroth, Imetric chirurgy was a much more gritty, hands-on affair involving knives, salves and all sorts of tools. 
And nasty amounts of blood. 
And pain. 

Carzain had been healed countless times by his mother after getting into a fight or otherwise hurting himself. 
This felt totally different. 
When the \sephirah{} \Ishiel{} healed there was no pain, only a dreamlike numbness. 
It could be nauseating, or even terrifying; a feeling of being cut loose from your body, like a dead man, or a ghost. 

When the Imetric healer sawed away at him there was just good old-fashioned pain. 
It felt more natural, less unsettling, but certainly not more merciful. 
Carzain's efforts to keep from crying out had met with mixed success, to say the least. 

The chirurgeon had explained that his work was founded not only on spells, but also on an extensive understanding of anatomy, chemistry and medicine. 
\hypota{True science}, he had said. 
Carzain was not fully happy about the unspoken suggestion that the Vaimon tradition was based on religious mumbo-jumbo rather than science, but he was also intrigued by these new perspectives. 
He could not deny that the Imetric method was just as effective as the Vaimon way. 
The leg still smarted, but not so badly. 

% \tho{Heh. 
%      But who who have thought that \quo{true science} was so messy?} 

No sooner than they had climbed down, the door sprang open. 
A woman came out. 
She was in her forties, rather tall, red-haired, wearing a brown woolen dress. 
It was \Roanne{} \Deracille, Carzain's mother. 

\ta{Nishain! 
    Carzain!} she cried out as she rushing to meet them. 
\ta{Oh, \sephiroth. 
    You were gone so long. 
    I was worried about you!}

Nishain embraced and kissed his wife. 
\ta{Yes. 
    Sorry about taking so long. 
    There were... complications.}

\ta{And Carzain, my boy!} she said, turning to Carzain and embracing him. 
Then she pulled back, holding him at arm's length and studying him.
\ta{By \Iquin, Carzain!
    You are hurt!}

\ta{No, I'm not.} 

\ta{Yes, you are! 
    You are wincing!} 

\ta{No, I'm not!} he insisted while trying to repress a wince. 
\tho{Oh, no. 
     Don't fuss about me, Mother. 
     Not in front of Northstar. 
     And the \nycans.} 
He knew of nothing more emasculating than being pampered by his mother. 

\ta{Nonsense. 
    I have twenty years' experience of seeing through the macho \facade s you and your father put up. 
    There's no fooling me, boy. 
    I know enough to recognize when you're wounded.
    Now let me see that...}
She reached for his wounded leg. 

\ta{Mother, not out here in the street!} 
said Carzain, trying to fend her off with his hands. 
% \end{comment}
\ta{I'm fine! 
    It's just a scar, nothing more!}

\ta{Come, now, \Roanne{},} said Nishain, gently pulling her off him. 
\ta{Here, meet our escort.} 

The large \scatha{} stepped up. 
\ta{Justice upon you, \Mrs{} \Deracille. 
    I am \IlcasStartRank{} Ilcas Northstar of the Imetrium.}

\ta{Oh... how do you, \Mr{} Northstar. 
    Please, do come in.}
She stuck her head in the door and called for their slave: 
\ta{Denuis! 
    A guest!}
The \Shireyo s were not rich, but they were sufficiently well-off to own one slave. 
% \ta{Please, \Mr{} Northstar, come in,} she repeated, waving her arms around. 

\ta{And, Mother,} said Carzain. 
\ta{Meet the \nycans: 
    Countess and Razor.} 

\ta{Ooo! Light!} 
\Roanne{} shied away, startled as the huge Countess reached out with her nose. 

Carzain reached out to stroke Countess' soft feathers. 
He liked Countess. 
Despite the menacing impression she gave, she could be very friendly. 

He had a harder time with Razor, the smaller male. 
Where Countess was full of purrs, hisses and yelps, Razor was always silent. 
Brooding. 
Observing. 
\tho{%
  Ilcas said Razor \quo{accepted} me. 
  But those looks the creature keeps sending me don't look accepting to me. 
  It's like he sees too much. 
  Knows too much.}

And there was the way he moved. 
Countess was huge and massive and moved almost like a \relc. 
Heavy. 
Solid. 
Sturdy. 
Easy to see. 
\tho{%
  You know where you have her.
  You can even hear her footfalls, if you listen for it.}
Not so Razor. 
His movements, his entire aspect was... too soft. 
Stealthy. 
Graceful, but in a creepy way. 
Silent. 
Sneaking. 
Slinking. 
Stalking. 

Carzain looked over his shoulder and noticed Razor staring at him again, with those penetrating reptillian eyes that appeared to gaze into his soul. 
\tho{%
  There! He's doing it again! 
  \quo{A better judge of character than I}, Ilcas called him. 
  No kidding. 
  He is eerie. 
  I can't get used to him. 
  
  Damn you, you creepy lizard. 
  What are you hiding?}







\begin{comment}
\subsection{Razor broods some more}
\end{comment}

\new
% And Razor broods over Carzain and his mystery. 
% He comments that Ilcas has taken a liking to the Shireyos. All because he, Razor, was intrigued and wanted to 
Razor kept his distance and watched Ilcas and the \humans. 
He noted that Ilcas had evidently taken a liking to the \Shireyo s. 
After Razor had vouched for them, Ilcas had almost uncritically taken them into his confidence. 

\tho{
  Maybe I should not have done that. 
  I hope nothing bad will come of it. 
  The father seems trustworthy enough, but I have my misgivings about the son. 
  Ilcas relies on my judgement too much. 
  He trusts me too blindly. 
  He should not do that. 
  I should try to let him know that. 
}

He turned his piercing gaze on Carzain again. 
Razor had not been able to learn much. 
There was some strange darkness in the \human. 
At normal times it lay hidden, faintly distinguishable to Razor's sharp senses as a vague undercurrent of \quo{wrong-ness}. 
Only once in a while did it rise to the surface, manifesting as... a slightly stronger undercurrent of wrong-ness. 
Razor could not make sense of it. 
He was at a loss for words and images to even describe it properly. 
It was like nothing he had ever encountered before, and he cursed his own ignorance. 

\tho{I wish I was learned,}
he thought ruefully. 
\tho{Like a \scatha.} 
He acknowledged that the \scathae{} had certain inherent advantages over \nycans. 
Above all, he envied them writing. 
Razor had tried to learn to read like a \scatha, but he had never grasped it. 
He understood the basic idea that those painted symbols in some way encapsulated knowledge, allowed it to be transferred from one person to another. 
Like telepathy. 
Slower, but somehow with greater range and scope. 
The markings allowed the reader to share the knowledge of strangers from far away, and even ancestors from the past. 

Yet he had never been able to learn it. 
Spoken language was difficult enough for the telepathic \nycan{} to wrap his head around. 
Writing was still beyond him, and it pained him. 

\tho{
  If only I could read, I could absorb all the knowledge in the world.
  Then, surely, I would understand the nature of this \human. 
  I would know the source of the strange darkness in him. 
  I would know what to do.}
% He turned back to Carzain.

\tho{
  Damn you, you creepy \human. 
  What are you hiding?}







