% \bookchapter{Deep in the Halls of Twilight}
\bookchapter{Wanderer in Darkness}
\begin{comment}
  \section{Wanderer in Darkness}
\end{comment}

\begin{comment}
  \subsection{Things to remember}
\end{comment}
\begin{garbage}
Read about \maybehr{Resphan}{\resphain}, \maybehr{Dragon}{\dragons}, \maybehr{Nyx}{\Nyx} and the \maybehr{Malcur venture}{\Malcur venture}.
Read about \maybehr{Resphan equipment}{\resphan equipment}. 
And \maybehs{dark ancient cities}. 

Have references to the fact that \maybehr{Heart weakened}{the Heart is weakening} (and read the section). 
Perhaps in conjuction with magic or birth or the Shroud. 

Have throwaway references to \maybehr{Mystic names}{mystic names and places}, like Shung. 
And dark, mystic, violent background events, like in \bandsong{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}.

It takes place at \ps{\Teshrial} place, not \ps{\Ganethed}. 

Remember that the \humans should be various exotic \demihuman varieties.

Remember \maybehr{Resphan size}{how large \resphain are}. 
Remember to have plenty of \maybehr{Resphan wing body language}{wing body language} from the \resphain. 
Remember that \CiriathSepher dress in bright \colours. 
Remember that they practice the \quo{Dance} of etiquette.

Remember that the \maybehr{Horrors of the Void}{voids between the Realms are fucking dangerous}.
 
\end{garbage}

\begin{comment}
  \subsection{Teshrial at the window}
\end{comment}
\stamp
  {\dateIshnaruchaefirIntroduced}
  {\Teshrial's citadel, \maybehr{Nyx}{\Nyx}}
\index{\CiriathSepher}
\index{\Nyx}

Lightning flashed, and loud thunder rolled far below as the storm raged in the deep beneath \Nyx. 
Under a sky nearly pitch black, the only natural light was the ghastly, spectral glow of the raging thunderstorms hundreds of \metres below, in the bottomless abysses of \Ullor. 

\Teshrial stood on a balcony near the top of one such spire and looked out over the city of \Nyx; an infinity of black and gray spires of stone, metal and glass.  
It seemed to go on forever, as far as the eye could see and beyond, in all directions\dash even above and below, for there were spires that towered more than a thousand \metres above his level. 

From the windows of the inhabited spires, bright many-\coloured lights shone like tiny pinpricks in the vast darkness. 
But most of the towers were empty and dead. 
They stood like a vast plain of withered cadavers. 
\Nyx was a macabre ruin, a necropolis kept alive only by a small cadre of immortals who refuse to die. 
Had \Nyx once been active and teeming with life, \Teshrial wondered?
Or had it always been a decaying ruin like this? 
\Teshrial had never dared to find out. 
He was of \CiriathSepher, and no \CiriathSepher with any sense of decency cared to delve deep in the ancient records.
There was nothing wholesome to find there, he knew. 

To chase these morbid thoughts from his mind, \Teshrial turned his eyes to the small plaque of graph-glass in his hands. 
It was a \resphan invention; a piece of glass, wrought with complex and subtle spells, that could be activated to display images. 
From its crystalline surface now shone the portrait of the beautiful \Firaxel. 
The graphician had captured her well, \Teshrial thought.  
Her flawless onyx skin. 
Her white hair, dyed with three stripes of azure. 
Her lips, dyed matching azure. 
Her eyes, deep ultramarine from birth. 
He touched the picture, running a finger down the edge of her hair.

\tho{\Firaxel. 
  Every \resphan's desire.
  Do you even remember my name?}

% Lightning flashed again. 
% There was a grinding, groaning sound as great rocks fell loose from one of the crumbling towers and tumbled into the deep. 

% \tho{Such contrast.
%   \Firaxel fair and serene against the grim violence of the great \Nyxian abyss.}

An impression of movement in the corner of his eye caught his attention. 
Turning his head, \Teshrial thought he caught a glimpse of a titanic shape soaring through the gloom far out in the distance. 
A shape with immense black wings. 

\tho{An \umbra?}

The thought of one of those ancient abominations of the formless darkness, dreaded even by the \resphain, made \Teshrial grip the graph-glass portrait tighter in his hands. 
For an instant he imagined he felt the wind of its great wings on his skin. 
He almost felt an urge to wrap his own feathered wings around him for warmth. 

But \Teshrial composed himself.
He was a \resphan of \CiriathSepher. 
He was a \ketheran, a noble. 
He would not let himself be frightened by an unidentified shadow thousands of \metres away. 

% \tho{Oh, well.
%   Time to go back inside.}

He turned from the dark window and stepped away from the balcony, into a brightly lit hall. 
Here the walls themselves were coated with living \glowmoss, harvested at great risk in the thunderous abyss below and valued for its soothing bluish light. 
Almost as bright as the \quo{daylight}  that was found in some Realms, although, of course, never in \Nyx. 

\tho{I must get back to the others. 
  It is time for our Communion. 
  
  Young Evith should be ready by now.}



\begin{comment}
  \subsection{Evith}
\end{comment}
\new
\tho{Oh, great Silver Starlight Rose!
  This is it.
  This is the big day.}

Evith's heart hammered in her chest. 
Just thinking about it made her dizzy. 
This was the most exciting evening of her life. 
The day of her Communion. 
All her life had been building up to this day, and now it had finally come. 

Jirin and Luria would not stop hugging her and kissing her and chattering to her.
\ta{Oh, Evith, I can't believe this is really happening!
  You're finally going to go through the Communion.
  The Communion!}

Evith was glad to have them. 
Jirin and Luria were her best and closest friends. 
All three were beautiful young girls of fifteen. 
And all were \naorim. 
Of all the \humans that served the \resphain, there were perhaps those who held higher ranks than the \naorim, but none were more sacred. 

\ta{Evith, you look so beautiful in that ceremonial robe,} the girls blabbered.
\ta{I'm sure the \resphain will love you from the moment they see you.
  I wish it were me wearing it\prikker}

\ta{Hush, now, girls,} said the firm but kind voice of their caretaker, \Mistress Duma. 
The girls fell silent, obediently.
Duma was a \naor herself, but instead of undergoing the Communion she had been given the even greater \honour of giving birth to \naor children. 
Now she was a large, matronly woman. 
All \naorim were well-fed, and Duma had grown quite fat in her old age. 
She now bore her great bulk with pride as a testament to her long service and the children she had born. 

\ta{Turn around, child, and let me look at you,} said Duma to Evith. 

Evith obeyed.
She looked at herself in the full-length mirror. 
It was true.
She was beautiful. 
The servants had applied makeup all over her body. 
The black-and-white stripes of her skin had been painted up so they looked sharper and clearer than ever. 
The ceremonial \quo{robe} consisted of a bikini, a short skirt and a cape, leaving her arms, legs and midriff bare. 
Duma had selected a bright red robe for Evith, to offset the black-and-white of her skin. 
% Her arms, midriff and legs were bare. 
Small symbols adorned her clothes around the edges. 
Evith bore them with pride and joy, for although she could not read, she knew the letters identified her as the property of her Divine Lord, the \ketheran \Teshrial. 

\tho{%
%   I am beautiful. 
  I have never been so pretty before.}

\ta{I cannot believe how beatiful I look. Thank you, \Mistress Duma.}

\ta{Oh, Evith,} cried Luria, kissing Evith and crushing her tight. 
\ta{Take good care of yourself. I am going to miss you so much.}

Duma slapped Luria hard on her buttocks with her wooden cane.
Then she slapped Jirin, too, for good measure. 
\ta{Be quiet. And let go of her.}
The girls cast down their eyes, humbled. 

\ta{Now behave yourselves, girls,} she admonished.
\ta{Remember, this is not the end. 
  You will see Evith again soon.}
Duma's expression softened.
\ta{You are both lovely \naorim.
  I am sure you will be chosen soon, too.}
Luria and Jirin beamed at this praise, hugged each other and giggled. 

Evith noticed that she was crying. 
She was sad to be parted from her friends, even if only for a while.

\Mistress Duma embraced Evith and let the girl vanish in her huge bosom. 
\ta{There, don't cry, Evith.}
She stroked her head gently. 
\ta{It will be fine, child. 
  After all, you do not have to \emph{do} anything. 
  Just submit. 
  Don't be afraid.}
She held Evith at arm's length and looked her in the eyes.
\ta{You are in good hands. 
  The carver is skilled and will take the best care of you.}

Evith dried her eyes. 
\ta{Y-yes. Thank you, \Mistress Duma.}
She then hugged her two best friends one last time and said goodbye. 

Duma smiled again. 
\ta{You will do fine. 
  Now in with you, child.
  Make us all proud.}

Evith took a deep breath and went in. 

\tho{My Communion awaits.
  The sacred Rite of \Thanatzil.} 
She felt unworthy. 
\Thanatzil was the great founder of the \resphain.
She was just a puny \human.
\tho{%
  But I will do my best.
  Oh, Silver Starlight Rose,} she prayed.
\tho{Please embrace me, and give me strength.}

She entered the great council hall, shining with bright \glowmoss. 
The \resphain all turned in their great, throne-like chairs to look at her. 
Her body tingled with awe at the sight of them. 
Never before had she stood alone before so many \resphain. 

\emph{They are the true gods, of whom we \humans are but flawed reflections.}

In the host's seat she recognized her master, the \ketheran \Teshrial. 
The others she recognized from the pictures and descriptions she had been given. 
This was an important part, and she had spent much time rehearsing it. 
As the first step of the Communion, she had to present herself to her \resphan masters. 
She must make no missteps.
The order and all the forms must be correct. 

She glanced back at the door where she came in.
Luria and Jirin were there, waving her on. 
They were embracing each other tight. 
She could tell they were almost as nervous as she was.
Next time it might be them. 

She must approach the \resphain in the correct order.
The first criterion was birth: 
The highborn \ketherain first, then \thelyadeth, then the \bezed half-bloods. 
The second criterion was sex: 
\Resviel first, then \resphain. 
The third criterion was Cabal rank. 

\Teshrial was the only \ketheran present, but as the host, he came last. 
So the first one to approach was the \thelyad \resvil, \Urizeth. 
She was easily recognizable as the only winged female present. 
She was skinny and petite by the standards of her kind, but still much taller than the mortal Evith.

Evith approached the chair where \Urizeth sat.
Her legs trembled under her, but she managed to kneel almost smoothly.
\Urizeth reached out her wings to her. 
Evith bowed and kissed the feather on the tip of each wing. 
\Urizeth acknowledged her with a small, aloof smile. 

Evith's heart soared. 
\tho{I did it right! She is pleased.}

She rose to her feet and repeated the greeting ritual with every \resphan and \resvil in the correct order. 
Last of all the host, \Teshrial. 
As she kissed the shining white feathers of his left wing, he softly caressed her face with the tip of his other wing. 
She dared glance up and found his face beaming down at her, full of divine love. 
It made her feel warm inside. 

\tho{My Divine Lord loves me. I am doing well.}

\Teshrial gently waved her away.
She climbed to her feet, backed away and took her place on the podium next to the carver.
The carver nodded for her to proceed. 

\tho{I have almost made it. 
  Only a little left to do.}

It was time for her epitaph, which she had prepared and rehearsed. 
Whenever a \naor \human was chosen for Communion, it was customary to have him to compose a very short speech expressing his personal feelings. 

Evith swallowed.
Took a deep breath.

\ta{%
  My Divine Lords \Ketheran, \Thelyadeth, \Resphain,} she began.
\ta{% 
  My name is Evith. 
  It is my pleasure and my privilege to be allowed to Commune with you. 
  I beg you to accept me as I surrender myself to you, in the most sincere hope that it will please you.}

Evith the prostrated herself, face down to the floor.
She remained down, waiting. 
The hearbeats seemed to stretch into hours. 

\tho{Will they accept it?
  Will they like my epitaph?
  No, they won't.
  It's silly and boring and ordinary. 
  Why could I not come up with something better?}

Then she heard \Teshrial's soft, aristocratic tenor: 
\ta{Rise, Evith.}

She rose. 
\Teshrial came over to stand before her, within arm's reach, white wings spread wide. 
He towered over her, at least twice her height, and his wingspan even vaster. 
Stunned by his awesome presence, Evith could only stand and bathe in the radiance of her god. 

\Teshrial reached down and seized her with his hands around her torso, under her breasts. 
Gently he lifted her up till her face was on a level with his own. 
Her heart stood still as she hovered in his arms. 
Ever so softly he kissed her on the lips.
And for a brief instant, Evith felt as if she were already one with the Silver Starlight Rose, swimming in the love of her gods. 

\Teshrial set her down and seated himself again.
\ta{Dear, sweet Evith.
  We find you worthy of the communion.
  Most worthy.
  And it was a fine epitaph you gave. 
  Simple and heartfelt.
  You have done very well.
  Everything about you pleases us, beautiful child.}
% He sat back down and motioned for her to proceed to the final step. 
The other \resphain smiled kindly to her and nodded their assent. 

Evith was still in a daze. 
She stared at her master in stupid bliss. 
Not before the carver gently poked her did she snap out of it. 

\tho{This is it. 
  Only one more thing for me to do.}

She took another breath. 
Then she reached behind her head and found the string that held her garment together.
She pulled it, and her clothes fell off, neatly, as they were designed to do. 
A nearby servant, with practiced ease, quickly scooped up the fragments and retreated. 

\tho{Everything is right,} she reminded herself.
\tho{I need not fear to stand naked before the \resphain.
  My masters love me.
  I have served them well.}

Evith knelt down again and lowered her head. 
She prayed silently. 

\tho{Wise and mighty \Thanatzil.
  You, who were the first angel against chaos. 
  You, who once stood alone as a flame against the vast tides of ancient evil. 
  I submit and offer myself as you once did. 
  I surrender my unworthy self to your grace. 
  Please have mercy upon me and accept me into your embrace.}

She held her breath for what seemed like an age. 

Then she heard the carver move above her. 

She felt his knife cut into her neck. 

\tho{Merciful \Thanatzil. I am coming to you.}

There was a sharp pain. 
Then all feeling faded. 

Blood gushed from her severed neck.
Evith died a happy girl.



\begin{comment}
  \subsection{Cabal matters}
\end{comment}
\new
\ta{That was a splendid Communion,} said \Ganethed, wiping his lips. 
\ta{Tasty, nourishing, pretty and well-behaved.
  You have some quality \naorim, Lord \Teshrial.}

\ta{Thank you, Lord \Ganethed.}
\Teshrial lowered his wings slightly to acknowledge the compliment.
\ta{I breed them myself, you know.
  But let us get down to business. 
  Lady \Urizeth?}

\ta{Mwhat?} said \Urizeth, distracted, still chewing on a piece of Evith's flesh. 
\ta{Um. Yes.}

\Teshrial wanted to roll his eyes at her, but repressed it. 
\Urizeth was \CiriathSepher by name and birth, but not by manners. 
She really had no understanding of propriety. 
She was an occultist; weird and probably half mad, and with the tainted scent of eldritch powers about her. 
Just being in the same tower as her made \Teshrial's skin crawl. 
They could not expect sane behaviour from one like her, he thought. 

\Urizeth began to explain about the progress of their plans for the city of \Malcur. 
The state of the \vertices and \matrices and \nexus points. 

\ta{%
  As you may remember, we have learned that our Sentinel opponents are under the command of \LocarPsyrex.
  Our Cabalists are working to infiltrate them and learn their plans.
  In the meantime, I have tried to read their \matrix\prikker}

\Teshrial's attention drifted away.
In his mind he visualized the \maybehs{Silver Starlight Rose}, the constellation representing the \KiriathSepher{} \matrix: 
A vast, complex, mathematically structured network of interconnected constellations and \vertices{}, from which extended myriad aethereal threads, spreading out into the Realms like a puppeteer's strings. 
The \vertex{} that was \Teshrial{} himself formed a corner point of a core constellation, connected to all the other \vertices{} by infinitely fine threads. 
The constellation revolved around the dense \matrix{} nucleus, which was opaque even to him, wreathed as it was in the mystic darkness of fearful \Erebos. 
Only one feature shone through: 
The clear light of \maybehr{Azraid}{\Azraid}, High Lord of \CiriathSepher{} and \apex{} of the {Silver Starlight Rose}. 
And \ps{\Teshrial} kinsman. 

\Teshrial realized he had been dozing off. 
He tried to focus on what \Urizeth was saying, but her occult talk repulsed and disgusted him.
He did not understand it all, nor did he want to. 

\ta{On the \quo{deeper} level, so to speak, our schemes are proceeding on schedule,} \Urizeth was explaining. 
\ta{%
  The \noggyaleth are close to the surface\dash although, of course, not \emph{too} close.
  None of us are born yesterday.}
She giggled, presumably at some private joke that no one else got. 
\Teshrial shifted uncomfortably at the mention of the loathsome \noggyaleth. 
The creatures followed the \resphain's commands, but \Teshrial still feared them and had no wish to be near them. 



\begin{comment}
  \subsection{Achsah detects Ishnaruchaefir}
\end{comment}
% \new
% After a lot of offscreen talk, the party is interrupted when \Achsah{} (who is a \maybehs{High Telepath}) feels a strange, giant \vertex{} moving in \Malcur. 
% She is the first \resphan{} to feel it because she is the only \maybehs{High Telepath} attuned and closely aligned with the \Malcuric \Nexus. 
% She sends her mind out to investigate and finds out that it is \Ishnaruchaefir. 

\ta{My lords!} the \bezed \Achsah suddenly blurted out. 

\ta{What?} said \Teshrial.
He sent the gray-skinned half-blood an annoyed stare. 
\tho{Really. She should know better than to interrupt a pureblood.
  Even if it is a freakish pureblood talking occult nonsense.}

\ta{I am detecting a mammoth \vertex intruding into the Shroud near \Malcur.
  Approaching the \nexus point.}

\Achsah had concentration painted all over her face.
Her aethereal senses were strained. 
She was reaching out far beyond \Nyx, in the city of Malcur in the Shrouded Realm of \Azmith. 
\Teshrial was impressed that she could do it at all. 
\Malcur was far from here.
But then, \Achsah was a High Telepath. 
This was her specialty. 
It was one of the reasons she was assigned to this project. 
She could sense things that most \resphain could not. 
Besides, \Teshrial reminded himself, \Achsah was presumably not doing this unaided. 
She was surely telepathically attuned to measuring apparatuses in the Shrouded Realms that helped her pick up things signals this. 

\ta{A strange \vertex in \Malcur?} said \Urizeth.

\ta{\quo{Mammoth}?} said \Ganethed. 
\ta{How mammoth?}

\ta{\Ophidian in nature,} said \Achsah.
\ta{\Draconian. 
  Yes. 
  \Draconian. 
  I smell \xsic power.}

\Teshrial gave an involuntary flap of his wings. 
\ta{By the Rose! Are you telling us there is a \dragon in \Malcur?} he said, incredulously. 

\ta{Yes, my Lord \Ketheran.
  And not only that, 
  It is worse. 
  Much worse.
  I can feel it more clearly now.
  I believe it is a \shaeeroth.}

\tho{\Shaeeroth?}

The \shaeeroths were the eldest and greatest of the \dragons; beings of immense power. 
There were no more than half a dozen of them in the world\dash awake, at least. 

\index{Serpentine Lord}%
\ta{Surely you are mistaken, \Achsah,} said \Ganethed.
\ta{A \shaeeroth?
  Who should that be?
  Surely not the esteemed \quo{\maybehs{Serpentine Lord}} himself?} 
\Ganethed{} laughed. 
\ta{Or whatever he calls himself these days. 
  He would not deign to take matters into his own hands.}

\ta{Hm. No, that seems unlikely, does it not?} \Teshrial{} agreed. 

\ta{No, not him.
  Not \Secherdamon,} said \Achsah. 
She frowned, concentrating. 
\ta{This signature is unlike any I have seen since\prikker}
Her face twitched, as if she were struggling against some realization. 
\ta{It cannot be\prikker}

\ta{What?}

\Achsah looks up. 
Her face was now solemn, her voice almost shaky. 
\ta{The Destroyer.}

Mutters went through the hall.

\ta{The Destroyer\prikker}

\ta{The Exile\prikker}

\ta{The Wanderer in Darkness\prikker}

\ta{But he has not been active for centuries,} protested \Ganethed.
\ta{Millennia!}

\ta{The Destroyer.} 
It was Lelmach who had spoken, a \maybehr{Bezed}{\bezed} in \Ganethed's service. 
\ta{The one who forsook his people after the \maybehr{Shrouding}{\SecondShrouding}\prikker} 

There was a moment of silence. 

\index{\QuessanthIshnaruchaefir}%
\Urizeth was the first to dare break the silence and speak his name. 
\ta{\maybehr{Ishnaruchaefir}{\QuessanthIshnaruchaefir}.}

\index{Shroud}%
It was as if a cold wind swept through the hall at the mention of the dreaded name. 
{\Ganethed} silently mouthed the words, still not daring to speak them aloud. 
Lelmach was intently studying the gobelins carved on the table, as if hoping that the problem would melt away into the Shroud if only they ignored it strongly enough. 

\ta{A great power indeed,} \Urizeth conceded, still in hushed tones. 
\ta{%
  The Destroyer is that most dangerous of things: 
  A rogue \vertex. 
  Aligned with no \matrix, but mighty enough to move and shake the constellations, and the Web of Realms itself. 
  No pattern for us to predict, no discernible strategy for us to analyze\prikker just a wild \vertex{} wreaking havoc.}

\ta{As far as I can tell,} said \Achsah,
\ta{the Destroyer is deep in the Shroud, and working to dig even deeper.
  He is trying to break through into the Shrouded Realm of \Azmith itself, and into \Malcur.}

\ta{Can he even do that?} said \Ganethed.
\ta{Surely he is too massive a \vertex to tread the Shrouded Realms.}

\ta{Normally I would say so too, my lord \thelyad,} said \Achsah. 
\ta{I know of no instances since the Shrouding where the Destroyer has set his foot in the Shrouded Realms, or even tried.
  Normally I would not think it possible\prikker}

\ta{It is because of the unravelling,} said \Urizeth. 

\ta{The unravelling?} said Lelmach.
\ta{But, lady \thelyad, I thought that was just a myth?}

\ta{Pah,} \Urizeth spat.
\ta{It is no myth.
  It is a scientific theory, a belief held by many respectable occultists.}

\tho{Respectable occultist? Huh. There is a contradiction in terms.}

\ta{The Shroud is slowly weakening,} \Urizeth was explaining.
\ta{We have been seeing evidence of this for decades, even centuries\prikker}

\Teshrial took his face in his hand to hide a grimace. 
\tho{There she goes again, blabbering about her occult theories when we should be focusing on the task at hand.}

The \dragons were the ancestral foes of the \resphan race. 
A terrible menace; a remnant of an older, crueler age of bloody chaos and darkness, before the \resphain came to \Miith with the light of their civilization. 

And no \dragon was more feared than the legendary Wanderer in Darkness, \QuessanthIshnaruchaefir. 
A monster so evil that even his own vile race scorned him and cast him out. 
In the war of the Incursion, it had been \Ishnaruchaefir who had sundered the world, a cataclysmic crime that killed thousands of \resphain and innumerable millions if not billions of mortals, and even many of \Ishnaruchaefir's own race. 
Ever since that black day, \Ishnaruchaefir had been known as the Destroyer and the Exile, feared and reviled by all. 
Driven from the dwelling places of \dragonkind, the Exile had taken refuge in his citadel, the Mirage Asylum. 
It was said to be an insane nightmare fortress floating in the chaos of the blackened voids beyond the Realms of \Miith. 
But no one knew for certain, for the Mirage Asylum was hidden and secret, and in thousands of years none had penetrated it.

\ta{My lords,} said \Teshrial. 
\ta{This theoretical discussion is fascinating, no doubt, but this is hardly the time for it.
  The Destroyer has come out of hiding and is headed for \quo{our} city.
  It is no secret that the Cabal claim \Malcur as ours and have vested interests there. 
  We cannot afford to assume this is a coincidence.}

\ta{You are right,} said \Ganethed.
\ta{We must assume the Destroyer means to interfere with our plans.
  Our venture in \Malcur is vital to the future of \CiriathSepher.
  \Ishnaruchaefir must not be allowed to stop the \noggyaleth.}

\ta{But how?} protested Lelmach.
\ta{The Destroyer is a \shaeeroth.
  A \draconian god.
  How can we stop him?
  We must call for aid.
  Surely there are many \resphain who would be willing to help fight him off\prikker}

\ta{There is no time for that,} said \Achsah.
\ta{Certainly, with a \resphan army we could likely fight off \Ishnaruchaefir.
  But he might be able to destroy everything we have worked for in \Malcur before they arrive.
  Think of the negotiations necessary for such an alliance.
  No, we will have to think of something on our own.}



\begin{comment}
  \subsection{Teshrial volunteers}
\end{comment}
\Teshrial reached into his pocket and procured the piece of graph-glass. 
He fingered the crystal screen to activate it, and \Firaxel's portrait once again materialized. 

\tho{Watch me now, \Firaxel.}

He rose to his feet and spoke in a low voice. 
\ta{We must fight him.} 

Voices rose in protest against this proposal.
\ta{But we cannot!}
\ta{He is a \shaeeroth!}
\ta{It will be suicide!}
\ta{Surely we can do something more intelligent than get ourselves killed.}
\ta{Who will go?}
\ta{Who can fight the Destroyer?}

\Teshrial, who was the tallest of the \resphain in the room, drew himself up to his full height. 
There was no wavering or hesitation in his voice now. 
\ta{I will go.}
He looked into the eyes of his companions, one by one. 
\ta{We are \resphain of the Cabal.
  We are sworn to battle the \dragons. 
  Will you fulfill your oaths by by huddling here?
  I will not. 
  The honourable course is clear. 
  I am \CiriathSepher.
  I know my duty and commitment. 
  I have faced and even killed \dragons before.
  I will go to \Malcur.
  I will challenge the invader.}

The others began to murmur again, but \Teshrial cut them off. 
\ta{If I cannot defeat him, at least I can hold him off.}
He turned to the occultist.
\ta{Lady \Urizeth.
  Cover our tracks. 
  Retract the \noggyaleth.
  Mask our \matrix.
  Do whatever you have to do to conceal our works from the Destroyer's prying eyes.
  I will buy you the time.}

\Urizeth was stricken speechless. 
She could only nod slowly. 

\ta{I will face him in \Azmith.
  He will be unable to assume his true form or bring his full \draconic power to bear.
  And even the Destroyer cannot destroy my soul from within the Shroud.
  I will not cower in fear of him.}
He spread wide his shining white wings. 
\ta{Do I stand alone?}

Emotions warred on \Ganethed's face.
Finally he rose and opened his bright yellow wings.
He could not match \Teshrial in height or wingspan, but he was more heavily muscled and cut a fierce figure with his thick blond mane and beard. 
\ta{No, Lord \Teshrial.
  What you say is true.
  Battles are not won without taking risks.
  I will stand with you.}

Very slowly, \Achsah arose. 
A wingless, black-haired \resvil, she looked tiny and dark between the two shining purebloods. 
\ta{I too will come with you, my Lord \Ketheran.
  Perhaps I can be of some assistance.
  I have encountered the Destroyer on the battlefield before.}
  
\Teshrial raised a questioning eyebrow. 
\tho{You have?}

\ta{Long ago,} \Achsah explained in response to his unspoken question.
\ta{In the Incursion.}

\Teshrial frowned. 
He knew \Achsah was by far the oldest \resphan present, but to openly advertise her seniority was a breach of all propriety. 
\Achsah was a mere \bezed and thus not a true \CiriathSepher, but nevertheless she should possess better tact than this. 

\tho{She will not be of much use in combat.
  But one must admire her courage.}
As a \bezed, \Achsah was not nearly as strong as a pureblood, and she risked more than just her flesh. 

\ta{Servants!} said \Teshrial.
\ta{Bring me my armour and weapons.}
He met \Ganethed's blood-red eyes and \Achsah's dark eyes.
\ta{Very well, comrades.
  Let us go and challenge this \draconian god.}



\begin{garbage}
\begin{comment}
  \subsection{The causeways}
\end{comment}
\new
Soon after, they have gathered their equipment. 
They now stand on a causeway outside the citadel.

\Teshrial{} gazes at the stars.
He looks at the \maybehs{Exile} and wonders. 
He tries to interpret them, but he is no great astrologer. 

He then reached out through the Web and submerged to a different layer of \Nyx. 
The hundred-\metres-high mirrored walls of the council chamber faded, and he stepped onto a long, massive bridge suspended in the void. 
Beneath, the tall towers continued down into the deep, seemingly without end, until they were swallowed by a dark, misty haze. 
Above, between the metal spires rising hundreds or thousands of \metres into the sky like clawed and spindly fingers, many-\coloured stars and nebulae were visible. 
%, for this was a shallow layer, close enough to \Azmith{} for its skies to shine through. 
But dominating the heavens were the ebon stars of \Erebos: 
%, shining with a deeper blackness than even the empty voids 'twixt the galaxies. 
%They were 
Central \nexus{} points in the Cabal \Matrix, spiritual conduits to that Stygian world of which \Nyx{} was sired, shining with a deeper blackness than the sky itself. 

\Teshrial{} took a moment to admire the view. 
And to scan the sky for the representation of the \vertex{} called the Exile. 
The creature he sought. 
\tho{Where are you, \Ishnaruchaefir? 
  Which constellations are you intersecting with?}

\Teshrial{} hefts his \senaan, \maybehr{Turishah}{\Turishah}. 
The others are behind them. 

This will be risky, he knows. 
But he will not back away. 

\Teshrial{} spread wide his wings and leapt from the causeway. 
 
\end{garbage}









\begin{garbage}
\begin{comment}
  \section{In the Deep Halls of Darkness}
\end{comment}


\begin{comment}
  \subsection{Ganethed's citadel}
\end{comment}

\stamp
  {\dateIshnaruchaefirIntroduced}
  {A council chamber in a \maybehr{CS}{\KiriathSepher} citadel, \maybehr{Nyx}{\Nyx}}
\index{\CiriathSepher}
\index{\Nyx}

\index{\Teshrial}%
The wine in \ps{\Teshrial} glass was dark red and thick-flowing. 
\tho{Almost like blood. 
  If somewhat more bland in taste. 
  I should have brought my own.} 

\Teshrial{} drained the glass, made of translucent rosy crystal, and held it out to have it refilled. 
The slave holding the decanter was a young man. 
Very slim and pretty. 
\tho{%
  I would rather have a taste of that boy.
  He is pretty.
  Almost as pretty as one of my own \humans. 

  But I suppose drinking from the \quo{bottle} would be uncivilized of me.}

Bored, he let his eyes wander, gazing out over the walls. 
They were perhaps a hundred \metres high and covered in shining mirrors. 
Wherever he gazed, his and his companions' reflections looked back at him. 
% made of solid dark iron but covered in shining white enamel. 
% Deep grooves ran from floor to ceiling, their edges looking, from a distance, as sharp as swords. 
The hall was brightly lit by huge golden chandeliers, each one holding more than a hundred candles. 
They hung from the ceiling, but no higher than ten \metres above the floor. 
Above them there was no illumination. 
The reflective mirror walls did their best to light up the entire hall, but in the end the light faltered and failed, and the walls simply vanished in the gloom overhead. 

\tho{%
  A reminder, perhaps, that all light is ephemeral and ultimately does not hold a candle to the primordial darkness. 
  Or something. 
  
  Haha. 
  Hold a candle. 
  Good one.}

At intervals, distant balconies, ledges and catwalks were dimly visible, but the ceiling was shrouded in pitch darkness. 
Only with his arcane senses could \Teshrial{} perceive the strange mosaic carved into that unseen dome above. 
He could not quite interpret the motif, but he recognized those weird, twisted shapes of uneathly geometry as a veiled metaphor expressing the cosmic \maybehr{Matrix}{\matrices} and their \maybehs{constellations}. 
The \matrices, those mystic star-maps that depicted the forces of the universe and their balance of power. 
\tho{%
  So, a dimly lit mosaic showing a weird picture of an obscure metaphor for an occult representation of a metaphysical abstraction of political reality. 
  Aaargh. 
  Now I remember why I chose \emph{not} to pursue the visual arts.
  Or \matrix{} theory, for that matter.}
% veiled metaphors for fearful, cosmic themes pertaining to his people's dark ancestry, and to the world of \Erebos{} and its terrible overlords. 

\index{\resphan}%
Disturbed by these sinister hints, he retracted his aethereal senses from the mystic mosaic and returned his attention to the council table, where, counting himself, seven \maybehr{Resphan}{\resphain} were gathered, waited upon by numerous \maybehr{Human}{\human} slaves. 

On the wide floor in the centre of the hall, a dozen slaves were performing some elaborate dance. Of sorts. They were naked, as were all the slaves in the chamber, and for some reason, the dance entailed an awful lot of genital contact, of body parts inserted into other body parts. 

\ta{%
  You really have no taste, do you know that, Lord \Ganethed? Having all your slaves wading around naked for no reason, and fornicating on the floor like that. You lack understanding of the subtlety of the finer arts.} 

\index{\Ganethed}%
\Ganethed{}, his host, chuckled and rocked in his chair. 
\ta{%
  Always the art critic, aren't you, Lord \Teshrial? But in your obsession with the \quo{finer} arts there is much that you fail to appreciate. There is beauty in many things\prikker direct and indirect expression alike.}

\ta{Such as a man fiercely jabbing his penis into another man's armpit?} asked \Teshrial, eyeing the dance with half-amused, half-bored disbelief. 
\ta{%
  Yes, I could not agree more: There are things which I profoundly fail to appreciate.}

\ta{Hah. You \emph{are} a snob, \Teshrial.}

\ta{Yes. And you almost make that sound like a flaw.}

\Ganethed{} laughed, brushing through his ear-long mane of golden hair with a hand. 
% \tho{%
%   Also, you should give that gesture a rest, \Ganethed. 
%   It looks ridiculous on you. Unlike me.} 
% As if to illustrate his point, \Teshrial{} ran a single finger through his long, bright white locks. 

\tho{%
  You are a barbarian, my dear \Ganethed. 
  Not sophisticated enough to be a \KiriathSepher. 
  Perhaps you should have been born into \maybehr{Mystraacht}{\Mystraacht} instead. 
  
  I must admit, though, that your shirt with the black-and-white tiger-stripes is rather stylish\prikker} 

\index{Selguin}%
Lady Selguin chose to break the stretching silence. 
\ta{%
  This discussion of penises and armpits is deeply fascinating, my Lords. But before we adjourn this council, I believe we might want to touch the small detail of our \matrixx, and of the \Malcuric{} \nexus?}

\index{\ghobal}%
\Teshrial{} stretched his white wings out wide for a brief moment. 
That was slightly rude, of course. 
But then, so was Selguin's snappy remark. 
\ta{Everything is proceeding according to plan,} he said, folding his wings back down to let them hang relaxed from his shoulders. 
\ta{The \maybehr{Ghobal}{\ghobaleth} are close to the surface.}
A few of his fellow \resphain{} cast him worried glances at that.
\ta{No, not \emph{too} close, of course. 
  I have it under control.}

\tho{I was not born yesterday.} 

\tho{But near enough,} their gazes seemed to imply. 
\Teshrial{} was very much aware of the fact that he was the youngest \resphan{} in the room. 
Such things were not spoken aloud, but they were thought. 

\index{Sentinels of Mith}%
\ta{\maybehs{Sentinels}?} inquired \Ganethed. 

\ta{Yes,} \Teshrial{} replied simply. 

\ta{\quo{Yes}?}

\index{\ketheran}
\index{\thelyad}
\ta{Yes, there are Sentinels there.} 
\tho{What kind of answer were you expecting? Stupid \maybehs{plainblood}.} 
\Teshrial{} felt slightly ashamed at thinking that, but it was true. 
\Ganethed{} was of the the \teshrialcircle{} circle\dash the same rank as \Teshrial{} and Selguin
He was also a competent associate and a pleasant acquaintance. 
Almost a friend. 
But \Teshrial{} could never forget that fact that he was, by birth, a mere \maybehr{Thelyad}{\thelyad}. 
% \Ganethed{} was of the the \teshrialcircle{} circle\dash the same rank as \Teshrial{} and Selguin\dash so he could not very well call him \quo{plainblood} to his face. 
% But that was what he was. 
% A mere \thelyad. 
Unlike \Teshrial{} and Selguin, who were of the superior \maybehr{Ketheran}{\ketheran} bloodlines. 

\Ganethed{} would not let himself dismiss. \ta{And?} 

\index{Cabal}%
\index{\LocarPsyrex}%
\Teshrial{} almost wanted to sigh or roll his eyes, but repressed it. 
\ta{%
  \emph{And} they are under the supervision of \maybehr{Psyrex}{\LocarPsyrex}. 
  \emph{And} I am dealing with them. 
  \emph{And} in this regard I have confidence in my \maybehs{Cabalists}.} 

Selguin fixed her eyes upon \Teshrial. 
They were sharp as blades, those eyes, and shining silvery like her hair. 

\tho{True \KiriathSepher{} eyes. 
  True \ketheran{} eyes.}

\ta{And the\prikker imbalance?} she asked. 
\ta{There were signs connecting the spike to your territory. 
  Have you made any discoveries?}

\tho{Yes, that pesky disturbance in the Web.} 
Ever since that \maybehr{Vertex}{\vertex} spike that had come out of nowhere last year, there had been an imbalance in the Cabal \Matrices. 
A rogue \vertex{}, yet part of the pattern. 
Moving in the shadows behind the scenes. 
And it was pulling their carefully orchestrated \matrix{} askew. 

\tho{Unknown players in the Web of the Realms. Always vexing business.}

\Teshrial{} signalled his subordinate to speak. 
\ta{\Achsah?}

\ta{My Lord \Thelyad, my Lady and Lord \Ketherain\prikker} \Achsah{} began. 

\index{\Azraid}%
\index{Silver Starlight Rose}%
As she spoke, \Teshrial, already familiar with her account, allowed himself to zone out. 
In his mind he visualized the \maybehs{Silver Starlight Rose}, the constellation representing the \KiriathSepher{} \matrix: 
A vast, complex, mathematically structured network of interconnected constellations and \vertices{}, from which extended myriad aethereal threads, spreading out into the Realms like a puppeteer's strings. 
The \vertex{} that was \Teshrial{} himself formed a corner point of a core constellation, connected to all the other \vertices{} by infinitely fine threads. 
The constellation revolved around the dense \matrix{} nucleus, which was opaque even to him, wreathed as it was in the mystic darkness of fearful \Erebos. 
Only one feature shone through: 
The clear light of \maybehr{Azraid}{\Azraid}, High Lord of \CiriathSepher{} and \apex{} of the {Silver Starlight Rose}. 
And \ps{\Teshrial} kinsman. 

\index{\PelidorContinent}%
\index{\Scyrum}%
\ta{I have researched the matter of the \vertex{} spike,} 
\Achsah{} was explaining, 
\ta{%
  and I have found strong evidence linking the incident to the \maybehr{Pelidor Continent}{\PelidorContinent} area. Perhaps \maybehr{Scyrum}{\Scyrum}, or\prikker}

\index{Pelidor}%
\ta{\prikker or perhaps \maybehs{Pelidor}?} \Ganethed{} interrupted. 

\Achsah{} bowed toward him. 
\ta{Yes, my Lord. Perhaps Pelidor. 
  I have read the stars, but I am still doing the calculations. 
  I expect to be able to further narrow it down in the near future.}

\ta{And have you determined its nature?} demanded Selguin. 

\index{Midnight Bat}%
\index{\Shiaraid}%
\ta{As for its alignment, my Lady \Ketheran, 
  I have reason to believe it is linked to the \maybehs{Midnight Bat} \matrix. 
  As for its nature, it is too early to tell. 
  It could be part of an intrigue between the dynasties. 
  Of which I would know nothing.} 
\Achsah, of course, being of impure birth, would not be privy to the scheming of the great dynasties. 
\ta{%
  It could be the birth or awakening of a Scion, in which case there are multiple possibilities. 
  It might be \Shiaraid{} stirring. 
  She was, after all, defeated but never destroyed. 
  Or it could be a ploy by the Sentinels, or some other power.}

\tho{%
  Some other power. 
  Yes. 
  Always more rivals to fret over.}

\ta{Really, at this point it could be anything,}
\Achsah{} began again. 
\ta{But there is another thing we have discovered. 
  My Lord?}
She paused to let him take the word. 

\begin{comment}
\subsection{Wanderer in Darkness}
\end{comment}

\ta{Oh, yes,} said \Teshrial. 
\ta{%
  It may interest you to know that I have, most recently, detected the activity of an alien \vertex{} stirring the threads of the \Malcuric{} \nexus.}

This captured the attention of all the \resphain{} at the table. 
\Teshrial{} let the dramatic silence drag for a few seconds before continuing. 

\index{\xzaishann}%
\index{\dzraicchenoss}%
\ta{Not the same as the one \Achsah{} talked about. 
  Another. 
  This one is \draecchonosh, for certain.} 
He had used the formal word for \quo{\dragon} in the \psp{\dragons} own tongue. 
\ta{I smell \xzaishannic{} power. 
  One of the \ps{\TyarithXserasshana} bloodline, kin of our progenitor.}

\index{\Nzessuacrith}%
\index{Vaccashyth}%
\index{\Dasvedshiracht}%
\ta{So, who might it be?} ventured Selguin. 
\ta{\maybehr{Nzessuacrith}{\Nzessuacrith}? Vaccashyth? \Dasvedshiracht?} 

\index{\shaeeroth}%
\ta{Possible. 
  But from what I can discern of the stars, I fear that we have to do with an even greater power. 
  One of their elder lords. 
  A \shaeeroth, and of the purest royal blood.}

\index{Serpentine Lord}%
\ta{Surely not the esteemed \quo{\maybehs{Serpentine Lord}} himself?} 
\Ganethed{} laughed. 
\ta{Or whatever he calls himself these days. 
  He would not deign to take matters into his own hands.}

\ta{No, that seems unlikely, does it not?} \Teshrial{} agreed. 

\index{Lelmach}%
\index{\bezed}%
\ta{But\prikker a \secondgendragon\prikker and of the blood of the progenitor\prikker} 
It was Lelmach who had spoken, a \lelmachcircle{} circle \maybehr{Bezed}{\bezed} in Selguin's service. 
\ta{That leaves only\prikker}

\index{Exile}%
\index{Wanderer in Darkness}%
\ta{You mean\prikker the Exile? The Wanderer in Darkness?} 
Selguin's voice was a whisper.

\ta{I think not,} said \Ganethed. 
\ta{He has not been active for centuries.}

\ta{Then it would appear he has returned,} said \Teshrial. 

This gave pause to even the boastful \Ganethed. 
\ta{The Exile\prikker}

\index{Destroyer}%
\index{\SecondShrouding}%
\ta{The Destroyer,} 
Selguin breathed. 
\ta{The one who forsook his people after the \maybehr{Shrouding}{\SecondShrouding}\prikker} 

There was a moment of silence. 

\index{\QuessanthIshnaruchaefir}%
\Achsah{} was the first to dare speak his name. 
\ta{\maybehr{Ishnaruchaefir}{\QuessanthIshnaruchaefir}.}

\index{Shroud}%
It was as if a cold wind swept through the hall at the mention of the dreaded name. 
\ps{\Ganethed}{} silently mouthed the name, still not comfortable with speaking it aloud. 
\Teshrial{} noticed one or two of the lower-ranking \resphain{} intently studying the gobelins carved on the table, as if wishing that the problem would melt away into the Shroud if only they ignored it strongly enough. 

\ta{An greater power indeed,} Selguin conceded, still in hushed tones. 
The feathers behind her shoulders twitched. 
\ta{%
  The Destroyer is that most dangerous of things: 
  A rogue \vertex. 
  Aligned with no \matrix, but mighty enough to move and shake the  constellations, and the Web itself. 
  No pattern for us to predict, no discernible strategy for us to analyze\prikker just a wild \vertex{} wreaking havoc.}

\ta{In accordance with Chaos,} \Ganethed{} pointed out. 
\ta{A principle which we, as a people, nominally strive to embody.}

\ta{I beg to differ, Lord \Ganethed,} said \Teshrial. 
\ta{Chaos alone is no virtue. 
  As you well know, it must be tempered. 
  And that is precisely what \matrices{} are for. 
  That is what elevates us above our foe\prikker}

\ta{My Lords \Resphain. 
  I believe we have pressing matters we ought to discuss instead of basking in the glory of the \resphan{} civilization?} 
Selguin's voice was slow and patient, almost condescending. 
\ta{Such as that of the Destroyer.} 

\ta{Oh, yes,} said \Teshrial. 
\ta{What do you wish to discuss, my Lady? 
  Do you offer to come with me and help fight him off?} 

Selguin stuttered an un-ladylike noise that was half cough, half laugh. 
\ta{Fight him off? No, I think not.}

\ta{Lord \Ganethed?}

\ta{Haha. Perhaps the next time, Lord \Teshrial.}

\ta{As I thought. 
  Well, in that case I fear I must take my leave of you, my Lords.} 
\Teshrial{} rose, signalling for \Achsah{} to do likewise. 
\ta{This was a fine discussion. We should do it again soon.} 

\ta{Eh?} exclaimed a surprised \Ganethed.

\ta{%
  I intend to go to Malcur and see if I can track down this \shaeeroth{} lord.}

\ta{You intend to do \emph{what}?}

\ta{%
  I want to see for myself if the Destroyer is as fearsome as his reputation. 
  Test his mettle.}

\ta{You are going to challenge \QuessanthIshnaruchaefir?} said an incredulous Selguin. 
\ta{Well, I wish you the best of luck, Lord \Teshrial.}

\ta{Thank you, my Lady,} said \Teshrial{}. 

\begin{comment}
\subsection{The causeways}
\end{comment}

He then reached out through the Web and submerged to a different layer of \Nyx. 
The hundred-\metres-high mirrored walls of the council chamber faded, and he stepped onto a long, massive bridge suspended in the void. 
Beneath, the tall towers continued down into the deep, seemingly without end, until they were swallowed by a dark, misty haze. 
Above, between the metal spires rising hundreds or thousands of \metres into the sky like clawed and spindly fingers, many-\coloured stars and nebulae were visible. 
%, for this was a shallow layer, close enough to \Azmith{} for its skies to shine through. 
But dominating the heavens were the ebon stars of \Erebos: 
%, shining with a deeper blackness than even the empty voids 'twixt the galaxies. 
%They were 
Central \nexus{} points in the Cabal \Matrix, spiritual conduits to that Stygian world of which \Nyx{} was sired, shining with a deeper blackness than the sky itself. 

\Teshrial{} took a moment to admire the view. 
And to scan the sky for the representation of the \vertex{} called the Exile. 
The creature he sought. 
\tho{Where are you, \Ishnaruchaefir? 
  Which constellations are you intersecting with?}

\ta{My Lord \Ketheran?} came \ps{\Achsah}{} voice behind him. 

\ta{What?} he said, not turning. 

\ta{Do you truly intend to face the Destroyer in combat?}

\ta{Yes.} 
\tho{Why do they all think I am crazy?
  I will not be fighting him on his premises, of course. 
  I am not stupid. 
  I will be going deep into the Shroud.
  My soul will be well protected, and his powers will be weakened.  
  What is the worst thing that can happen?
  
  Huh. 
  I guess not all \resphain{} can be equal in courage.}

\ta{%
  Be careful, my Lord \Ketheran. \Ishnaruchaefir{} is a terrible foe. 
  His status is legendary for a reason. 
  You should not underestimate him. 
  I have encountered him a few times\prikker}

\Teshrial{} repressed the urge to sneer. 
\Achsah{} came dangerously close to the \fauxpas{} of openly advertising her age. 
It was almost painful to listen to. 
She seemed to relish subtly reminding him of how she was older and more experienced than he. 
As if it somehow cancelled out her inferior birth. 

\ta{\Achsah, come here.} She stepped closer. 

\index{\resvil}
He gazed down at the shorter \resvil. 
Far down. 
\Resphain{} were always taller than \resviel, and \Teshrial{} taller than most. 
And lacking wings, \ps{\Achsah}{} looked tiny. 
Stocky, though. 
She was heavier of build than \Teshrial, owing to her \nephilic{} blood. 

He put a finger under her chin and turned her face up. 

\tho{%
  Not beautiful. Crude by \resvil{} standards. 
  I have bred \humans{} that are prettier than she.}

He slapped her across the face. 

Not hard enough to cause actual pain, of course. 
That would be a breach of priopriety. 
%She stood beneath him in rank, but not near far enough that he could corporeally punish her. 
She was \achsahcircle{} circle, after all. 
Not nearly far enough below him that he could corporeally punish her; 
not on a whim, at least.

Just hard enough to be humiliating. 

\ta{Do not presume to educate me, \ashenblood,} he admonished. 

She scowled up at him, silent. 
He raised a questioning eyebrow. 

\ta{Yes, my Lord \Ketheran,} she mumbled. 

He turned away. 
\tho{Good.} 
It was a crude thing to do, slapping her.
But necessary. 
Everyone in the Cabal had to know and remember their place. 
\tho{Especially the low-born.
  Really, with all the millennia she silently boasts of having seen, she should have learned that much.}

\tho{And as for the infamous \shaeeroth, this mystic Exile\prikker 
     well, we will see about that.}

\Teshrial{} spread wide his wings and leapt from the causeway. 
 
\end{garbage}









