
\bookchapter{What Slithers Beneath}

\begin{comment}
\section{New Version}
\end{comment}

\stamp
  {\dateIshnaruchaefirSlaysAGhobal}
  {Southern merchants' quarter, Malcur, Pelidor}
  


\begin{comment}
  \subsection{Rian sees them}
\end{comment}
\new
\tho{Almost there\prikker}

\index{Rian}
Deftly concealed by his body, Rian's knife closed in on the strap holding the purse. The fat merchant was still unsuspecting. After all, the market was crowded at this time of day, and the young boy had picked his best cloak, so as not to stand out too much here among the upper tiers of the citizenry. 

Rian rarely ventured into the merchants' quarter, or any other of the wealthier parts of Malcur. Granted, there were great rewards to be reaped by a skilled thief, but the danger was accordingly higher. In the slums, people were left to police themselves; steal from a man who looked slower and less agile than yourself and you were usually safe. Here in the merchants' quarter they had city guards, and there was the very real risk of getting caught. For a lowlife like him, stealing from a higher citizen might lose him a hand, or even earn him the gallows. So, even though the pickings could be gold rather than copper, few thieves thought it worth the risk.

\hypota{What'll it be, Rian?} the gang leader had asked him. 
\hypota{You gonna be a real man? Or are you just a pussy?} 

\hypota{All the rest of us have done it, you know,} the thieves had prodded. 

\hypota{You're gonna have to prove yourself.}

Long story short, Rian had been dared into sneaking into the merchants' quarter, east of the slums where he lived, and bring back a trophy. 

\tho{%
  Almost there\prikker
  
  Mustn't shake\prikker
  
  Mustn't be nervous\prikker
  
  Ow!}

All of a sudden Rian was pushed from behind, and had to hurry and retract his hand, so as not to cut open the fat man's gut. He quickly concealed the knife under his cloak as he was borne forward by a wave of people. Rian turned and craned his neck, expecting to see riders cutting through the crowd, but found none. 

\tho{What made the crowd part? A nobleman, perhaps? Or soldiers? On foot?} 

Rian, who was no tall boy,  
could see nothing through the massed people. Curious now, he ducked and began elbowing his way to the front. This drew curses and the odd blow from the people he pushed through, but no more than the lowlife was used to. 

%Finally he reached the crowd frontline. 
What he found as he reached the crowd frontline was less than he expected.
A single \sphyle{}\dash a female \scatha{}\dash alone and on foot.
She looked rather old, but strong and healthy for her age. 
Her scales were bright red. 

\tho{Why did the crowd part for her?
  Who is she?
  
  Must be a foreigner, with that \colour.}

The \sphyle moved quickly, and the crowd resumed its natural rhythm behind her. 
Rian felt compelled to follow her and get a better look. 

Slipping through the masses of people, he found the red \sphyle continuing along in her little empty \quo{bubble} in the crowd. 
As Rian thought this, something dawned on him: 

\tho{Why is no one else reacting?} 

People moved out of the \traveler's way, but their faces and movements showed no fear nor deference. 
Their faces showed nothing out of the ordinary. 
They scuttled aside for no apparent reason, without ever noticing it. 
Rian studied the people around him, but found no one else who seemed to have taken note of anything.

\tho{What is going on here? Has everyone been struck blind and stupid?}

He studied the red-scaled \sphyle closer. 
Her garb was certainly not \Malcuric, but looked like what a wealthy \travelling merchant might wear. Brown and orange \colours mostly. Leather as well as silk and other expensive materials. 
She carried a long, curved dagger in her belt, made from some metal darker than iron, almost black. 
It was adorned with \dragons{} and serpents crawling up and down the hilt and sheath. 
Such ornate weapons were often unwieldy and nigh-unusable for other than ceremonial purposes. But in this case, the ornamentation somehow made the blade look \emph{more} dangerous. 
Studying it, Rian felt a nagging apprehension that the carved serpents were watching him with their cold, reptilian eyes, poised to strike. 
% Disconcerted, he had to look away from the weapon. 

The more details he noticed, the more Rian began to feel there was some kind of unnatural \emph{presence} about her. 
He did not like it. 
It felt \emph{evil}. 
It was not a thing of the One Light.
Something else. 
Something darker.
He imagined he sensed some great cosmic power, a fragment of some vast evil older than the \human race. 
A thing of the Outer Darkness. 
A thing of the chaos that was before the coming of Cordos Vaimon and Silqua. 
A cold, merciless, alien thing that cared nothing for the lives and concerns of humanoids. 

Part of Rian wanted to turn away and forget about it.
Forget the mysterious \scatha existed. 
Forget all about cosmic evils and get on with his Light-fearing life. 
But curiosity compelled him to stay and watch.

He cursed his curiosity.
It was a sinful thing, he knew.
Scripture said that a man should not seek out the Outer Darkness, but turn away from it. 
He should seek only goodness, pursue only the virtues of the One Light and shun all things of the Darkness. 
He knew that.
But in spite of all that, he could not look away. 
The images of pre-\human horrors stirred up in him a morbid fascination.
He had to know what was going on. 

\tho{Great \sephiroth, merciful Silqua, forgive me.
  Forgive my weakness.}

He followed her. 



\begin{comment}
  \subsection{Criseis walks through the city}
\end{comment}
\new
\Criseis passed statues of angels, monsters and \scathaese and \human heroes. 
\Malcur was a fairly old city by mortal standards, and the art of many different epochs was represented here. 
There were \human-looking angels from the time of the \VaimonCaliphate, \dragons and serpents from the age of \Ortaica, and \scathaese-looking angels from the more recent age of \Tepharae.

\Criseis was not comfortable walking through the city.
If she had her way she would have chosen a more covert approach. 
She felt awfully naked and vulnerable with her dark master's presence trailing behind her like this. 
She knew that her master's reverberations could be felt from worlds away. 
She feared it was only a matter of time before she would be accosted by the \resphain or their monsters.
Her scales twitched at the prospect. 

Absent-mindedly she fingered a spot on her left chest. 
Under her shirt she could feel the ward rune symbiote wriggling under her touch. 
She looked down at her wrist, where she had a weapon symbiote embedded. 
She doubted her weapons would be of much use against a \resphan, even a \bezed. 
\Criseis was a powerful sorceress, but still just a \scatha.
But if it came to blows, she hoped the ward runes would at least protect her from a few blows and buy her time to flee. 

She did not even fully understand why she was here. 
Her master, \QuessanthIshnaruchaefir, had not told her his plan. 
She could not help him break through the Shroud, nor fight the \resphain and their minions. 
She felt insignificant. 
She could only hope her dark god would protect her. 

She looked back through the crowd and caught a glimpse of a short, red-haired \human.
\tho{That boy is still following me.
  Why is he following me?
  Why can he even notice me?
  I should be better masked than this.
  Granted, Master \Quessanth is crying out his arrival from the metaphysical rooftops, but Shrouded mortals should not be noticing it.
  Not yet.
  
  Who is this boy? Is he someone special?
  Is he a mage or a \vertex{} himself?
  Is he someone in disguise?
  No, I cannot believe that.
  I am certain he is just a regular boy.
  
  This should not happen. 
  
  It would not have happened a few hundred years ago. 
  
  Something is rotten in the state of the Shroud these days.}



\begin{comment}
  \subsection{Rian follows Criseis}
\end{comment}
\new
Rian followed the red-scaled \sphyle down the road to the bad part of inner Malcur. 
As they walked, the scenery gradually changed, the tall, bright and shiny homes of the highborn and the wealthy being replaced by weird, twisted edifices. Many of these buildings were still tall and ornate, evidently once having been glorious like their counterparts nearer the castle, but now strangely decayed, as if abandoned for a generation or more. 
Some \emph{were} genuinely empty, but many were still inhabited, and yet still had this decayed look. 
And it seemed to Rian like more than mere disrepair. Their frames were somehow warped, disfigured, as if by the deliberate actions of some malign haunting spirit. It made them look almost like crooked trees rather than humanoid-built houses. 

Because of the eerie, misshapen buildings, this part of the city was shunned by the upper tiers of society and had thus degenerated into a lower middle class area. Still finer folk than slummers like Rian, but noticeably beneath the standard of neighbouring quarters. 

\tho{She is heading for the dead garden. She must be,} Rian decided. 
\tho{It makes sense. The garden is mysterious. This \sphyle is mysterious.}

As they continued, west-southwest away from the rich quarters, the houses shrank and the standard of living dropped. And as they neared the dead garden, the uncanny decrepitude intensified; buildings seeming to grow more deformed with every street they passed. Finally, the habitation ended, the last rows of houses long empty and crumbling. 

Before them lay the most sinister, mystical part of Malcur. 

It had no name, but was simply called \quo{the dead garden}. 
When it was referred to at all; for many people seemed unwilling to acknowledge that it existed. 
And glancing at it, it was not difficult to imagine why. 

The many trees and bushes in the garden were all twisted and misshapen. They seemed withered and dead, or at least dying; \coloured black, pallid white or sickly yellow. Dead, yet somehow very alive, for subtle evidence hinted that the trees not only grew, but also moved; creeping and writhing at the edges of one's vision. 
The place was ever twisting and writhing with chaos, and paths never looked quite the same twice. 
The garden was a small patch of \wylde in the middle of the city. 
A piece of savage and untamed nature. 

Rian took out the small talisman which he always carried around his neck. 
It was a crude tin figure of Silqua, blessed by a priest to ward against the horrors of the \wylde. 

\tho{Merciful Silqua, protect me from evil.}

The garden was scary and unsettling; Rian was not above admitting that to himself (although admitting it to the world was another matter). 
But at the same time, the place had an allure of the forbidden, the fantastic, the grotesque. 
An allure that drew Rian in. 
% As a newborn, these sixteen years ago, he had been found in a ruined house not all too far south of the garden, and had always imagined some connection to the morbid orchard. Many times he had fantasized about his origin: Born in the centre of the dead garden, the son of a mystic and powerful witch who had then sped off on some dark adventure. Idle daydreaming, of course, but as an orphan, it was the best he had. 

\tho{Fair Silqua, forgive me.}
This fascination was another sin, he knew. 
The kindly monks had told him to stay away from this place, and he wanted to, but still he found himself returning here time and time again. 
The garden gave him a sense of thrill, of adventure. 
In here he could feel a little bit like an exploring hero. 
He could play at being Cordos Vaimon, conquering the monstrous hordes of the \wylde and paving the way for \human civilization. 
This was a fantasy he had not mentioned aloud to the priests. 
Fancying himself as Cordos Vaimon was blasphemy. 

\tho{Fair Silqua, forgive me.}







\begin{comment}
  \subsection{Criseis in the dead garden}
\end{comment}
\new
\Criseis smelled the air with her tongue. 

\tho{This is the place.
  The \quo{dead garden}. 
  
  The Shroud is thin here.}

\tho{Master \Quessanth, I have arrived.}

\ishna{Excellent,} came the dreadful voice of her master inside her head. 
\ishna{Stand back,} he commanded. 

\Criseis did not have to be told that.
She quickly retreated to one of the ruined hovels near the edge of the {garden}. 

\tho{It is beginning.}

She could feel \Ishnaruchaefir's presence draw nearer, begin to expand. 
He had been hovering near the surface for a long time, but now he was finally breaking through the Shroud in earnest.
He was summoning the energies of the \xss for this great display of power. 
The threads of the Web of Realms began to hum and tremble violently, and from the twisting void she could hear the shrieking of a thousand \daemons as they came whirling to answer \Ishnaruchaefir's call. 

She heard the disembodied voice of her master, far removed from the frequencies of earthly sound, intoning words of power in the ancient \TrueDraconic tongue:

\draconicspell{
  Hearken, o' dreamer of the benighted realms: \\
  \quad
    \KyaethemChreiAz!\\
  Black mother, bringer of death and rebirth: \\
  \quad
    \KhothSell!\\
  Thou who hast neither beginning nor end; \\
  thou who art the gate and the spheres: \\
  \quad
    \NaathKurRamalech!}

A chilling wave of dread washed over \Criseis{} as her master invoked the sinister names of the \xzaishanns, those dreadful alien gods above gods, from whom \Ishnaruchaefir{} and his people derived so much of their power. 
He spoke arcane words that echoed the ancient covenants forged a million years ago by \Sethicus, the great father of \dragons. 

The air reverberated with the sorcerous power of those words. 
And the gods answered. 
She felt the essence of the \xss seeping down from their homes amid the howling stars, down through vast reaches of space. 
\KyaethemChreiAz. 
\KhothSell.
\NaathKurRamalech. 

\tho{He is coming.}



\begin{comment}
  \subsection{Rian sees vortex}
\end{comment}
\new
Rian saw the \sphyle retreat from the garden and crouch down in a collapsed hut. 
He followed at some distance and hid himself in another hut. 

There was something not right about the way the \sphyle moved. 
There was a sinuous softness to her steps. 
And her tail was strangely snaky, whipping back and forth like that of a cat. 
Not like the rigid tail of any normal \scatha. 
Rian could swear she looked different now than she had at first; that she had somehow gradually mutated. 
\tho{I must be imagining it. Right?}

She stopped up and lifted her nose to smell the air. 
Her tongue darted out. 
And it was no \scathaese{} tongue! 
A normal \ps{\scatha} tongue looked like that of a {\human}. 
This one's was long and slim and forked, and she tasted the air with it as would a snake!
The sight filled Rian with cold fear. 
He was right!
There was something unnatural and evil about this \scatha. 

Now he began to feel a change in the air. 
It felt charged with energy, like in a thunderstorm.
He thought he could hear a distant buzzing or droning noise\dash or, rather, feel it, like a vibration against his skin. 

\tho{What is happening here? 
  What evil sorcery is this?}

Straining his ears, he seemed to hear the echoes of a distant voice. 
It was an inhuman voice, impossibly deep; growling, thundering, as if resounding from the throat of an immensely large creature. 
The words, while alien and incomprehensible to him, nonetheless carried an undertone of dark portent that chilled him to the core. 

Now Rian thought he could hear a faint howling, echoing from far off. 

\tho{%
  Things. 
  Terrible things. 
  Blind and savage. 
  Raging. 
  Beyond the dim.}

Then there was a great flash of light from the centre of the garden. 
Rian had to look away and was half-blinded for many moments. 

Beneath him, it was as if the ground vibrated. 
\tho{An earthquake!} was his first thought. 
But then he realized that the ground under him was actually not moving. 
The quaking he felt was within his mind. 
It was as if his brain writhed, convulsed, struggling to break free of its prison inside his skull. 
He imagined the air around him growing thick, dense. 
Like water. 
Fathoms and fathoms of water. 
Weighing down upon him. 
Grinding him flat. 
Squeezing his insides out of him. 

When his sight returned, he dared peek in the direction from which the flash had come. 
What he saw there took his breath away.

\tho{Great \sephiroth preserve me\prikker}
        


\begin{comment}
  \subsection{Resphain travel}
\end{comment}
\placestamp{En route from \Nyx to \Malcur}
The great metal chariot hurled through the void in a blazing fireball. 
In the chariot, \Teshrial and his companions were safe from the blind, howling \daimonia and other horrors of the twisting chaos. 
As long as they followed the traditional passageways, carved and maintained by powerful spells. 
Outside the glass, the void swirled and shrieked and thundered, like an ocean of fire; black, purple, red, white, and other \colours for which \Teshrial had no name. 

\ta{I am still not sure how we are to fight the Destroyer,} said \Ganethed. 
\ta{\Achsah. 
  You said you had fought him before.
  What can you tell us about him?}

\Achsah looked down.
\ta{Well, my lord \thelyad, I did not so much \quo{fight} him.
  I only saw the Destroyer from a distance across the battlefield. 
  He fell upon us like a black storm of chaos and fury, wreaking havoc and and cutting a bloody swathe through the \resphan ranks.}

\ta{And what did you do?} asked \Ganethed.

\ta{This was in the Incursion, when he earned the title of \quo{Destroyer}.
  And rightly so. 
  None of our people could stand before him, my lord \thelyad.
  We \bezedeth least of all.
  So when the Destroyer came my way\prikker I fled.
  I did not dare come close enough to get any better impression of him, much less fight him.}

\ta{Hm,} said \Teshrial. 
If she were a pureblood he would have berated her for her cowardice, but since she was a \bezed he gave her the pass for now. 
\ta{But this was in the Incursion, before the Shroud.
  Things will be different here.}
\tho{I hope.}
\ta{In this age, here in a Shrouded Realm, we will stand much stronger.
  Moreover, remember, our aim is not to kill the Destroyer, but merely to push him back into the void.}

\ta{Or, failing that, just slow him down,} added \Ganethed. 

\ta{Yes,} said \Teshrial.
\ta{We can do this.
  We must.}



\begin{comment}
  \subsection{Rian sees Resphain}
\end{comment}
\placestamp{Dead garden, \Malcur}
Rian stood frozen still, gaping in horror and awe at the sight before him. 
The centre of the dead garden was gone, replaced by a huge vortex of energy, like a great hole in the ground, burning and seething with waves of black fire. 
And it was growing. 
Expanding. 
Devouring the fabric of the world to feed itself.

And he had a premonition of something even worse.
For he sensed that down there, in the depths of that writhing abyss of fire, there lay in wait\prikker something. 
Something vast. 
Something hideous. 
Something that had no place in this world, nor any sane, wholesome world. 
A monstrous creature that roared and wrestled, longing to be free of its prison in the outer chaos and to tread the lands of men under its monstrous feet. 

\tho{Great \sephiroth save me.
  It is the end of the world.}

He was reminded of the myths of \dragons; terrible creatures of evil that had ruled the world long ago, in the Age of Chaos when the One Light had refused to shine on \Miith. 
They had been vanquished and cast out of the world centuries ago by Cordos Vaimon and the brave order of Vaimons which he founded. 
The \dragons were now no longer found on \Miith, but according to scripture their evil still threatened the world. 
They were the spawn of Chaos, the kin of loathsome alien gods and the wielders of the blackest sorcery ever conceived. 
Their king was \Isphet, the Scourge, the Destroyer, the Lord of the Outer Darkness, eternal foe of the \sephiroth. 
Once, in pre-historic times, \Isphet had all but destroyed the world, and for this crime the \sephiroth had banished him to the void from whence he came. 

Rian felt sure that this abomination was a thing of \Isphet. 
A horror of the Outer Darkness. 
An enemy of the world. 
He began to recite the names of the sixteen \sephiroth:
\tho{\Atzirah, \Razilah, \Keshirah, \Feazirah\prikker}

Then there came another bright light. 
Rian looked to his right.
Once again he gaped as, out of the mist beyond, three figures appeared. 
They were like \humans{}\dash two men and a woman\dash but\prikker \emph{greater}. 
In all ways, greater. 

The one in front, a male, was immensely tall, twice as tall as Rian or more. 
His skin was obsidian black, his flawless face beardless and youthful, his hair flowing long and shining white. 
And, most incredible of all, huge white-feathered wings sprouted from his back. 
Everything about him shone with perfection and androgynous beauty. 
His black-skinned hands had long nails lacquered pearly white. 
Every one of his ten fingers was decorated with a jeweled ring. 
He was dressed in an immaculate robe, white like his hair and wings and adorned with silver and diamonds. 
Over the robe he wore a suit of \armour made of transparent, faceted crystal that glinted in the sun. 
The upper edges of his wings were covered by a slim shin of silvery metal that seemed to taper to a sharp, sword-like blade. 
In his hands he held a sword; silvery, single-edged and curved, and so immensely long it was almost a polearm. 

The second male was slightly shorter but heavier. 
His skin was also black. 
His hair, beard and wings were golden, and he was dressed in white and orange. 
He, too, wore crystal \armour and blades on his wings and carried a sword longer than he was tall. 

The third, the female, was shorter, but still overtopping Rian by what must be more than a foot. 
Her skin was ashen gray, her hair raven black, and she wore a dress fit for any queen or princess, striped and patterned in glinting gray, black and silver, and overlaid with plates of clear crystal. 
Her jewelry, too, was of silver, and a sabre hung scabbarded at her side. 
The woman's beauty was such that the young man was very near ashamed that that he had once though mortal women attractive. 
Unlike the men, she had no wings, and she did not radiate the same power as her companions, but her face and eyes seemed to hold the wisdom of countless ages. 

Rian he was struck dumb. He could but cower and stare. 
Surely these resplendent beings must be angels! 
\tho{%
  Such magnificence. Such might. 
  No, not angels. 
  Gods!
  Before my eyes\prikker three gods in the flesh!}
The \human{} would have fallen flat on his face in worship of these superhuman avatars, had he had the courage to move at all.

The gods approached the vortex, expressions of disgust and determination on their faces.

\tho{I see now!
  They are angels from the One Light, come to vanquish the world-devouring monster.
  My prayers were heard.
  Praised be the \sephiroth!
  We are saved!}



\begin{comment}
  \subsection{Teshrial battles Ishnaruchaefir}
\end{comment}
\new
\Teshrial had felt a great rend in the Shroud as soon as he stepped down from the chariot, but even so, he was still taken aback by the sight of the vast maelstrom. 
\tho{Great Rose. This will not be easy.}
He began to understand why \Achsah had feared to face the \draconian god in the Incursion. 

He recognized this place. 
It was an outcropping of \wylde in the middle of the city, a bulge of energy caused by the \Malcuric \nexus point. 
\tho{It stands to reason that \Ishnaruchaefir would choose this place. 
  The Shroud is thinner here. 
  We are still in the Shrouded Realm, but if \Ishnaruchaefir is to break through the Shroud, he stands a better chance of drilling a hole here than in any other place in \Malcur.} 

\ta{Look, my lords,} said \Achsah.
\ta{That \scatha skulking around there by the edges of the garden.
  It is \Criseis, a servant of the Destroyer.}

\ta{Leave her be,} said \Teshrial. 
\ta{We have no time to worry about a \scatha. 
  We have more pressing concerns.
  Look. 
  He is close to the surface.}

\ta{Yes,} said \Achsah.
\ta{He is about to break through.
  We have to act swiftly.
  But I do not understand how he can do this. 
  Penetrating the Shroud is not a matter of brute force. 
  I am certain that a thousand years ago this would not have been possible.
  It is as the lady \Urizeth says\prikker
}

% \Teshrial did not want to think about what that entails.
% What would happen if the Shroud were truly unravelling?
% Would all the nameless crawling horrors of the Beyond be able to slink inside, into \Nyx and the Shrouded Realms?
% \tho{No! 
%   I will not think about it.
%   Focus on the battle at hand.}

\ta{Be that as it may,} \Ganethed interrupted. 
\ta{With the Destroyer this close, we cannot stop him with Shroud-weaving spells alone.
  Some of us will have to attack and force him to relinquish his grip.
  Then maybe the rest of us can patch up the hole and force him back down.}

\Teshrial said nothing. 
He stood facing that vortex of chaos-spawned power.
Stood listening to the howling of the blind \daemons from Beyond. 
And as menacing undercurrents beneath it all, he could feel the essence emanating from the dreaded \xss, those cosmic gods of chaos from the most distant stars. 

He took a deep breath. 
Tightened his grip on his \senaan sword, \Turishah. 

\ta{I will go. Cover me.}

Without another word he leapt into the air. 
He spread his wings wide and soared over the maelstrom. 
On the ground below, \Ganethed and \Achsah began their spells to keep the hole from expanding and prevent \Ishnaruchaefir from breaking through any further. 

\ta{\QuessanthIshnaruchaefir!} \Teshrial called, raising \Turishah above his head in bold defiance.
\ta{I know you are down there. Can you hear me?
  I am \Teshrial of \CiriathSepher, \ketheran of the bloodline of \Azraid.
  I will not let you enter \Azmith.
  I will fight you!}

To punctuate his words, \Teshrial swung the \senaan \Turishah in a great arc. 
He focused his willpower and channelled it through the sword as a crescent-shaped wave of shining energy. 
The bolt sped down and faded into the gloom of the dimensional gateway. 
And yet\dash a burst of light!
His bolt had struck true. 

In response, several thin streaks of pale, ghostly energy burst forth from the abyss and converged on \Teshrial. 
\tho{Wraithworms!}
They were mindless \daemons in the shape of translucent skeletal snakes, a favoured attack spell of the \dragons and their ilk. 
Swift as lightning \Teshrial spun, striking with his \senaan and the bladed braces on his wings, called \kilghain. 
He managed to parry and dispel several of the wraithworms, and the last one shattered against his spell-forged crystal \armour as it struck. 

\Teshrial took heart. 
\tho{I am not defenseless against this god.
  Even if I cannot destroy him, I can put up a fight.}
But he would need all of his mastery of the martial arts. 
So he focused his powers again and swung \Turishah, sending yet more crescents of shimmering force down to bombard his foe. 

Then there came a voice from the abyss. 
A deep, growling, thundering voice, as if the earth itself were groaning. 

\ishna{Thou art a fool to stand before me, \resphan.
  Knowest thou not that I am the Destroyer of Worlds, the eternal bane of thy kind?}
  
He spoke in \TrueDraconic, and every word seethed with the taint of the \xss.
\Teshrial understood the \CommonDraconic tongue only poorly, and knew even less of \TrueDraconic, so he had to strain his ears to understand. 
He did not catch the exact words, but the message was clear enough. 

\ta{I do not fear you, Exile!} \Teshrial cried.
\ta{I have fought \dragons before and prevailed. 
  You have been hiding in your Asylum like a coward these last thousands of years.
  If no one else will face you, then I will.
  Come out and fight me!}

\ishna{I am come to claim this city as mine own.}

\ta{And I am here to stop you!}

% \ishna{Feel, then, the wrath of the fire of \RuinSatha, lord of the \xss.
%   Feel thou the fire which consumeth the veils of the world.
%   Feel thou the fire which maketh and unmaketh the worlds!}
% \Ishnaruchaefir's \TrueDraconic words were not mere poetry; they were spellwords, and they conjured up a storm of green, ghostly flames that erupted from the deep like a volcano. 
\Teshrial could dimly hear growled spellwords from below. 
They conjured up a storm of sickly green, spectral flames that erupted from the deep like a volcano. 
He had to use all his agility and skill to evade and ward off this massive attack, and even so the chaotic fires singed his feathers and struck ominous cracks in his glass \armour.

\tho{Whoa! That was close. A blast like that might have killed me.}

Then he heard the telepathic voice of \Achsah in his head. 
\tele{My lord \ketheran.
  I have heard from lady \Urizeth.
  She is almost done.
  We need only hold him back for a little while longer.
  But it is difficult.
  Despite our efforts, he is steadily gaining ground.}

\tho{Very well,} thought \Teshrial.
\tho{I must take more drastic measures, then.
  I cannot strike properly from up here.
  I am merely firing blindly.
  At this rate, I am an annoyance rather than an opponent.
  For good reasons he cannot come to me, so I must take the battle to him.}
He looked down into the swirling depths of the vortex and the black gulfs of space he sensed beyond. 
\tho{It will be dangerous. 
  I may die here. 
  But much must be risked in war.}

\Teshrial drew on the energy of the Silver Starlight Rose and wrapped himself in powerful protective spells. 
Then he closed his wings about him and dove into the maelstrom. 

Soon he was surrounded on all sides by torrents of dark fire and the shrieking of mindless horrors, but still he flew on, down and further down. 
This was a chaotic Realm, different from what \Teshrial knew. 
Barrages of nonsensical, seemingly random impressions assailed his eyes and ears. 
But he concentrated, and through the swirling waves he began to see images. 

\tho{He is down here.
  I can feel it.
  The Destroyer in the flesh.}

\Teshrial saw confusing glimpses of reptilian forms amid a twisting, formless chaos.
He caught an impression of huge coils of scaly flesh; of enormous black wings; of many burning yellow eyes; of many hungry, tooth-filled mouths. 

\tho{Is this the \dragonlord's true form?}

\Ishnaruchaefir's voice thundered again, ear-splittingly loud at this range.  
\ishna{Thou worm. I will not be thwarted by the likes of thine.}

\ta{I do not fear you, Exile!}
With this battle cry \Teshrial lunged for the nearest scaly coil he could find. 
He raised his sword and put all his strength into a great arcing slash. 
\Turishah shore through scales and flesh. 
\Draconic blood erupted seething in a great, dark, rancid cloud of filth. 

% \ishna{I will not be thwarted by the likes of thine.}
The Destroyer struck back. 
This time \Teshrial could physically feel the mists of \xsic energy drawing nearer and thickening.  
% as the Exile spoke the words of power: 
% \ishna{By \KhothSell, mother-goddess of death and birth, she who giveth life and taketh it, who striketh like unto the snake and the scorpion\prikker
%   perish, thou worm!}
% 
He felt a tidal wave of negative energy engulf him. 
\tho{I will not fall! I will fight till my last breath!}
He swung \Turishah, channelling all his might through the blade in an effort to dispel the attack. 
He sliced through the wave of corruption with all his art, all his power, all his will. 

And the dark force abated. 

But only for a second. 
% Then he once again heard the Destroyer:
% \ishna{%
%   By the art of \Sethicus, by the power of \KhothSell, and by all of the million \daemons: 
%   Perish, worm!}
Then the Destroyer renewed his attack. 
The tide of corruption swept over \Teshrial with full force again. 
Again he raised \Turishah, parting the waves with his sword like the prow of a ship. 
But he did not have the same strength as before, and the power of the \xs \KhothSell was limitless. 
With horror \Teshrial watched as \Turishah first bent and then \emph{shattered} in his hands. 
Too late he raised his \kilghan-covered wings to fend off the attack.
The \xs showered him with hailstones of pure Death, and under that unholy onslaught his beautiful wings crumbled, rotted away and fell off in tatters, as if suffering a millennium of decay in an instant. 
\Teshrial's crystal breastplate cracked and splintered. 
Pain and dread lanced through his mind, almost drowning out all thoughts and senses.
His flesh blistered and burst. 
His bones snapped. 

\tho{You will pay for this, \Ishnaruchaefir\prikker}
Such was his last thought. 



\begin{comment}
  \subsection{Criseis feels}
\end{comment}
\new
As soon as she saw the \resphain engage her master with their spells, \Criseis began to carry out her orders.
She reached out with her aethereal senses, like tendrils into the Beyond. 
Searching. Probing. 

\tho{Let us see. What do you hide, \Malcur?}

\Criseis had sharper senses than any \scatha, and sharper than many an immortal; and she had the help of an advanced detector symbiote, a centipede-like living thing that crawled on her head and amplified her senses. 
These senses were one of the chief reasons that \Ishnaruchaefir employed her on missions like this. 
And they did not fail her. 
Soon she detected an alien, unnatural presence. 
\tho{Something lurks beneath this city.} 
It was hidden well behind the ever-present Shroud, but she thought she could smell the rank breath of monstrous things pervading the air, feel the reverberations of immense shapes slithering in the Beyond. 

\tho{The underworld of \Malcur hides some crawling horror. 
  But what?}
\Criseis had a suspicion, but she wanted to be certain. 
So she probed deeper. 
Down into the Stygian, subterranean depths where the physical and metaphysical laws of the surface world dissolved and the borders to the Beyond became fluid and permeable. 
Down here the Shrouded Realm of \Azmith gave way to \Nyx and to the crypt-like abysses of benighted \Erebos, the Realm of Darkness. 
She peered into those vast corridors, and there, in a revelation of horror, she saw the \emph{thing}. 
Vast and amorphous it shambled towards her, its dark, slimy bulk quivering hideously as it moved. 
Of colossal proportions it was; wormlike and gaping with a hundred hungry mouths; and the charnel stench of cosmic decay followed in its wake. 
There it burrowed in the ever-blackened tunnels beneath the earth, gnawing at the fabric of the Web. 
She could almost feel the clammy, oozing skin of the behemoth abomination, coiled about her, smothering her with its massive bulk. 

With a dismayed sob \Criseis retracted her senses from the underworld. 
Frantically she grasped the detector symbiote and tore it off, severing the traumatic vision. 

For a long time she stood shaking from the shock, seeing little of what was happening around her. 
She barely noticed the bleeding wound on her face where she had ripped the symbiote up with its roots; nor did she notice the poor, mindless symbiote that lay curled up and dying on the ground where she had tossed it. 

\tho{So that is what slithers beneath\prikker}



\begin{comment}
  \subsection{\Resphan aftermath}
\end{comment}
\new
\Achsah was panting with effort. 
The Destroyer was immensely strong. 
She and \Ganethed had to strain themselves to the utmost just to slow him down. 
They tried their best to keep him down and close the Shroud, but the hole just kept growing and growing. 

\tho{What are you doing, \Teshrial? We need you.}

Then suddenly some object came flying up from the maelstrom.
\Achsah instinctively flinched away, fearing a bombardment of spells from the Destroyer. 
But this object was not a \daemon or a fireball or anything. 
It was\prikker a glop of slime. 

\tho{
  No, wait.
  That is not slime.
  It is a body. 
  A \resphan body?
  
  Oh, great \SitraAchras\prikker 
  
  \Teshrial?}

She looked over at \Ganethed and saw the same dismayed expression mirrored on his face. 
He even lowered his wings in shock. 

They heard a booming voice from the deep. 

\ishna{\Resphain! 
  Carry this message to your fallen comrade, \Teshrial.
  When he returneth to life, tell him this:
  Thy display of bravery hath left me impressed.
  If thou darest face me once more, then send unto me a new challenge, and I will humour thy request.}

Then, all of a sudden, the pressure on the gate fell away. 
The vortex calmed and began to shrink. 
The Destroyer's presence was withdrawing.
The hole in the Shroud was closing up. 

\tho{He\prikker fled?
  But why?
  Certainly it was not we who stopped him\prikker}

Soon the dead garden was silent. 
The great hole in the ground was gone, replaced once more by the familiar wizened trees and shrubs. 
It was as if nothing out of the ordinary had happened.
The Shroud had reaffirmed itself. 
Absently, \Achsah noted that the \scatha was also gone. 

She and \Ganethed walked over to the body. 
\tho{Poor \Teshrial.}
Nothing was left of him but a pile of molten flesh, covered in viscous and foul-smelling slime.

\tho{And look. 
  His beautiful \senaan, \Turishah, has been shattered. 
  He will be sad about that when he revives. 
  He loved that sword.} 

In silence they scooped up their companion's remains, loaded them onto the chariot and departed, back to \Nyx. 

\ta{Well,} said \Achsah, breaking the awkward silence. 
\ta{The good news is that \Urizeth succeeded.
  I heard from her before\prikker before \Teshrial was killed. 
  She believes she managed to hide our plans before \Ishnaruchaefir came close enough to detect or touch anything.
  Our secrets have not been compromised.}

\Ganethed's wings lifted slightly. 
\ta{That is good.
  That was what we came for. 
  So we succeeded after all. 
  \Teshrial's pains were not in vain. 
  We have won a battle against the Destroyer.}

\ta{Have we, my lord \thelyad?} said \Achsah. 
\ta{I do not think so.
  This was not a battle against the Destroyer.
  What we faced was only the merest sliver of him that peered through the Shroud.
  Moreover, \Teshrial fell, who was the strongest of us.
  That should tell us something about what we are up against.
  And did we truly win?
  I doubt it.
  We did not push back the Destroyer.
  He retreated of his own free will.
  Was it because he failed to find what he came looking for?
  Perhaps.
  But I suspect he has deeper motives.
  We have not seen the last of \QuessanthIshnaruchaefir.}



\begin{comment}
  \subsection{Rian aftermath}
\end{comment}
\new
Rian had watched the whole battle in stunned horror. 
The white shining angel descended into the mouth of the Outer Darkness to drive back \Isphet's monsters\prikker and he was killed!
How could this happen? 
Was the evil in the world so great that even angels fell before it?

Then the evil gate closed. 
Did the angel sacrifice himself to close it?
Rian did not understand. 
It was too vast, too cosmic, too horrible for him. 

Most of all he wanted to forget all this had happened. 

He walked away on shaking legs.




\begin{comment}
  \subsection{\Criseis aftermath}
\end{comment}
\placestamp{En route from \Malcur to the \maybehs{Mirage Asylum}}
Great wings and menacing shadows whirled past \Criseis. 
Slavering jaws snapped at her as she floated through the raging void.
She averted her eyes from the sight, still uneasy despite the protection afforded by her master's spells. 
\Ishnaruchaefir did not take the smooth road along a mapped and safe route as most would have done.
Scorning the beaten path, the Exile forced his way through the very heart of the chaotic void in proud defiance. 

Fortunately, her master, seeing her shocked state, had enough compassion to carry \Criseis and not force her to transport herself. 
So she lay and tried to relax, nervously fingering her sore, still-bleeding wound where she had ripped off the detector symbiote.

Finally \Ishnaruchaefir spoke. 
\ishna{Tell me, \Criseis. 
  What did you see?}

She described the awful vision to him. 

\ishna{Well done, \Criseis. 
  This is interesting\prikker}









\begin{garbage}

\begin{comment}
\section{Old Version}
\end{comment}

\begin{comment}
\subsection{Rian}
\end{comment}

\stamp
  {\dateIshnaruchaefirSlaysAGhobal}
  {Southern merchants' quarter, Malcur, Pelidor}
%
\tho{Almost there\prikker}

\index{Rian}
Deftly concealed by his body, Rian's knife closed in on the strap holding the purse. The fat merchant was still unsuspecting. After all, the market was crowded at this time of day, and the young boy had picked his best cloak, so as not to stand out too much here among the upper tiers of the citizenry. 

Rian rarely ventured into the merchants' quarter, or any other of the wealthier parts of Malcur. Granted, there were great rewards to be reaped by a skilled thief, but the danger was accordingly higher. In the slums, people were left to police themselves; steal from a man who looked slower and less agile than yourself and you were usually safe. Here in the merchants' quarter they had city guards, and there was the very real risk of getting caught. For a lowlife like him, stealing from a higher citizen might lose him a hand, or even earn him the gallows. So, even though the pickings could be gold rather than copper, few thieves thought it worth the risk.

\hypota{What'll it be, Rian?} Badrick had asked him. 
\hypota{You gonna be a real man? Or are you just a pussy?} 
The gang leader was really named Patrick, but everyone agreed that was too \quo{nice} a name for a rugged thug, so to everyone that mattered, he was Badrick. 

\hypota{All the rest of us have done it, you know,} Evar had prodded. 

\hypota{You're gonna have to prove yourself,} Badrick had warned. 

Long story short, Rian had been dared into sneaking into the merchants' quarter, east of the slums where he lived, and bring back a trophy. 

\tho{%
  Almost there\prikker
  
  Mustn't shake\prikker
  
  Mustn't be nervous\prikker
  
  Ow!}

All of a sudden Rian was pushed from behind, and had to hurry and retract his hand, so as not to cut open the fat man's gut. He quickly concealed the knife under his cloak as he was borne forward by a wave of people. Rian turned and craned his neck, expecting to see riders cutting through the crowd, but found none. 

\tho{What made the crowd part? A nobleman, perhaps? Or soldiers? On foot?} 

Being a boy of no more than average height, Rian 
could see nothing through the massed people. Curious now, he ducked and began elbowing his way to the front. This drew curses and the odd blow from the people he pushed through, but no more than the lowlife was used to. 

%Finally he reached the crowd frontline. 
What he found as he reached the crowd frontline was both more and less than he expected. Two \scathae, a tall \dax{} in the lead and a smaller \sphyle{} following. %, both unremarkable at first. 
At first sight both seemed unremarkable. 

\tho{Why did the crowd part for these two?}

%As he studied them closer
%Then, as he studied them closer, it suddenly struck him: 
Then it struck him: 
\tho{That is a strange-looking \dax.} His scales were pure black, glossy like some kind of precious stone. Rian had never seen a black \scatha{} before. Blue, red, occasionally green, but never black. 
\tho{How could I not notice this straight away?} 

As he studied the pair closer, new details seemed to appear out of nowhere. The \dax{} was very tall, seven feet at least. His garb was all black with occasional lines of silver and blood red. Dressed in a long cape over what appeared to be metal \armour, he looked the part of a warrior, but he bore no weapon that Rian could see. 
The two ridges on his head were strangely elongated, almost like a pair of slim, backwards-curling horns. 

%As Rian stood and stared, 
Then, slowly, calmly, not breaking his stride, the black-scaled \dax{} turned his head slightly and, with a slight smile on his lips, fixed Rian with his gaze. It was only a glimpse out of the corner of his right eye, 
but it so startled the young thief
%but Rian was so startled 
that he immediately, instinctively ducked out of sight and back into the crowd. 

Rian silently cursed himself. 
\tho{Dumbass! Dumbass! Dumbass!} Acting guilty was the worst thing a thief could do, anyone knew that. When a passer-by noticed you, you acted like nothing was out of place. The best way to invite suspicion was by \emph{being suspicious}. 

%But the look in that eye had been more than the boy could take in. It spoke volumes about\prikker something\prikker abnormal. Inhuman. Larger than life. Unnatural. Wisdom, terrible power\prikker and somehow, splendour. 
%and awe-inspiring majesty. 
%And the eyes themselves glinted red, as if a mystic fire burned behind them.  \tho{Who is he? \emph{What} is he?} 
But that stare had been more than the boy could take in. 
The eye glinted yellow. 
Not just the a regular yellow eye\dash uncommon but not unheard of. 
No, this eye shone. It \emph{burned}. 
As if a mystic fire burned behind it. 

And the \emph{look} in that eye! It had spoken volumes of cryptic meaning. Of something\prikker abnormal. Inhuman. Larger than life. 

Unnatural. 

Wisdom, terrible power\prikker and somehow, splendour. 

\tho{Who is he? \emph{What} is he?} 

Meanwhile, the crowd was resuming its natural rhythm, and Rian, curiosity aroused further now, had to hurry to catch up with the pair. \tho{Screw the pickpocketing. This I can't afford to miss.}

He found the onyx-scaled \dax{} and his companion continuing along in their little bubble in the crowd. As Rian formulated that thought, something dawned on him: 

\tho{Why is no one else reacting?} 

People moved out of the \travelers' way, but their faces and movement showed no fear nor deference. Their faces showed nothing out of the ordinary. And stranger still, no one seemed to cast a glace at the great black-\armoured warrior. They scuttled aside for no apparent reason, without ever noticing it. Rian studied the people around him, but found no one apart from himself who had taken note of anything extraordinary.

\tho{What is going on here? Has everyone been struck blind and stupid?}

The enigmatic pair \traveled north, seemingly heading for the Palace. \tho{I'm going to follow them. Maybe that'll lead me to some clue as to what's going on\prikker}









\begin{comment}
\subsection{\Criseis{} is anxious}
\end{comment}

\new
\index{\Criseis}%
\index{\Ishnaruchaefir}%
\index{\QuessanthIshnaruchaefir}%
\ta{Master \Quessanth,} said \Criseis, 
\ta{are you certain this is a good idea?}

\ta{Nay,} \QuessanthIshnaruchaefir{} conceded with a smile, as if it was nothing. 

\Criseis{} sulked. 
\tho{I hate it when he does that.} 

\ta{There is a boy following us,} \Ishnaruchaefir{} commented. 

\Criseis{} had an urge to turn around, but she repressed it. 
She knew better than that. 
Always better to allow the spy or assassin to get overconfident. 
\ta{Dangerous?}

\ta{I think not,} her master chuckled. 
\ta{What is it you fear, \Criseis?}

\ta{You, master. You and your recklessness.}

\ta{%
  You fret too much, \Criseis. 
  Nothing will go wrong. 
  Probably.}

%\tho{And you fret too little.} But there was no point in saying it aloud. 
\Criseis{} saw no point in answering. 
They had had this discussion before. 
Many times. 
It never changed anything. 

So she scuttled along nervously. 
\tho{%
  Are we there yet? 
  I hate these hiking trips he takes. 
  And in broad daylight, too\prikker}









\begin{comment}
\subsection{To the dead garden}
\end{comment}

\new
\tho{They're heading for the dead garden,} Rian realized. \tho{They must be. What are they after?}

The mysterious pair became yet more mysterious by the moment. The dark one's tail was strangely snaky, whipping back and forth like that of a cat. Certainly nothing like the mostly rigid tail of any normal \scatha. His snout was slender in the middle but widened slightly at the end, unlike the blunted triangle forms of ordinary \scathaese{} snouts. The ridges above his eyes were unnaturally elongated, tapering backwards almost like horns. And that glow in his eyes. Baleful, and yet fascinating. Rian half-imagined the black-scaled one to be some mighty \dragon{} or \daemon{} out of legend. 

\tho{A \dragon. Who's assumed \scathaese{} form to take a stroll through Malcur.} 
He laughed inside at the absurdity of that. 
Besides, there were no more \dragons{}, not in this day and age. 
If they ever existed at all. 

The \sphyle\dash evidently an attendant of the black one's\dash was much less outlandish. At least she was shaped like a normal \scatha. Her scales were of a bright red, almost fiery. Her garb was certainly not \Malcuric, but looked like what a wealthy \travelling merchant might wear. Red, brown and orange \colours. Leather as well as silk and other expensive materials. And in contrast to the unarmed but \armoured warrior, the \sphyle{} carried a long, curved dagger in her belt, made from some metal darker than iron, almost black. 
It was adorned with \dragons{} and serpents crawling up and down the hilt and sheath. Such weapons were often unwieldy and nigh-unusable for other than ceremonial purposes. But in this case, the ornamentation somehow made the blade look \emph{more} dangerous. %, as was often the case with such weapons. 
%Ornate, but not so excessively as to turn it into an unwieldy, ceremonial piece. \Dragons{} and serpents crawled up and down the  
%Overall, while the female lacked the menacing aura of her \armoured companion, 
%From this one, Rian 
Studying it, Rian felt a nagging apprehension that the encarved serpents were watching him through their cold, reptilian eyes, poised to strike. Disconcerted, he had to look away from the weapon. 

Indeed, while she may lack the powerful, menacing aura of her \armoured companion, the \sphyle{} was still one whom Rian would not dare steal from, however heavy her purse might be. 

Their path had led near to the centre of the city. The colossal \CastlePelidor{}\dash home of the \rayuth, ruler of Malcur and of all Pelidor\dash was visible even from the slums, looming forebodingly in the distance as a reminder of all that separated the lowlives from their highborn lords. But here, it towered over everything. Even though it was still distant and would take a long walk to reach\dash Rian guessed a thousand paces or more\dash, already its white marble walls seemed to span almost the entire horizon. Immense towers rose up to touch the sky, their brass-coated roofs gleaming like small suns. 
Friezes and statues adorned the walls, of \armoured knights, angels, beasts and dreadful monsters; some of them huge, many times taller than a man. 
Rian found himself in the line of sight of a giant angel of marble\dash androgynous, winged, brandishing aloft a flaming sword, as if to strike with righteous anger down upon the thief's sinful head. He hurried on, eager to put some buildings between him and the avenging stone angel. 

\tho{Burning eyes, \Dragons, carved snakes, and now angels. I'm letting superstition drive me nuts.} So he tried to tell himself. 









% \new
% \ta{My lord, why the detour?}
% 
% \ta{For the scenery, \Criseis. It is a nice castle. And it has taken the toll of the millennia quite well.} 









They moved on, turning west from the castle down the road to the bad part of inner Malcur. \tho{To the dead garden.} As they walked, the scenery gradually changed, the tall, bright and shiny homes of the highborn and the wealthy being replaced by weird, twisted edifices. Many of these buildings were still tall and ornate, evidently once glorious like their counterparts nearer to the castle, but now strangely decayed, as if abandoned for a generation or more. Some were genuinely empty, but many were still inhabited, and yet still had this decayed look. 
And it seemed, at least to Rian, like more than mere disrepair. Their frames were somehow warped, disfigured, as if by the deliberate actions of some malign haunting spirit. It made them look almost like crooked trees rather than humanoid-built houses. 

Because of the eerie, misshapen buildings, this part of the city was shunned by the upper tiers of society, and had thus degenerated into a lower middle class area. Still finer folk than slummers like Rian, but noticeably beneath the standard of neighbouring quarters. 

\tho{They must be headed for the dead garden,} Rian decided. \tho{It makes sense. The garden is mysterious. These \scathae{} are mysterious.}

As they continued, west-southwest away from the castle and the noble quarter, the houses shrank and the standard of living dropped. And as they neared the dead garden, the uncanny decrepitude intensified; buildings seeming to grow more deformed with every street they passed. Finally, the habitation ended, the last rows of houses long empty and crumbling. 

Before them lay the most sinister, mystical part of Malcur. 

It had no name, but was simply called \quo{the dead garden}. When it was referred to at all. Many people seemed unwilling to acknowledge, or even believe in, its existence. And glancing at it, it was not difficult to imagine why. 

The many trees and bushes in the garden were all twisted and misshapen. They seemed withered and dead, or at least dying; \coloured black, pallid white or sickly yellow. Dead, yet somehow very alive, for subtle evidence hinted that the trees not only grew, but also moved; creeping and writhing at the edges of one's vision. 

The garden was scary and unsettling; Rian was not above admitting that to himself (although admitting it to the world was another matter). But at the same time, the place had an allure of the forbidden, the fantastic, the grotesque, an allure that drew Rian in. As a newborn, these sixteen years ago, he had been found in a ruined house not all too far south of the garden, and had always imagined some connection to the morbid orchard. Many times he had fantasized about his origin: Born in the centre of the dead garden, the son of a mystic and powerful witch who had then sped off on some dark adventure. Idle daydreaming, of course, but as an orphan, it was the best he had. 

The two \scathae{} walked to the first line of trees, and Rian followed from some distance, crouching behind a collapsed hovel. 
\tho{Pointless. They've seen me already. They know I'm here.} 
Nonetheless, they were menacing-looking types, and he was not about to step forward and challenge them. 

They spoke together now. 
Rian strained his ears to hear, but the words he caught were in no language he could recognize. 
\tho{What are they saying now?}










\begin{comment}
\subsection{Black magic}
\end{comment}

\begin{comment}
\subsubsection{\Criseis}
\end{comment}
\new
\ta{Master, what was that detour for?}

\ta{For the scenery, \Criseis. It is a nice castle. And it has taken the toll of the millennia quite well.} 

\Criseis{} had not found herself able to fully appreciate the architecture. The longer she spent in Malcur, the stronger the alien presence crept into her mind. 
\tho{Something lurks beneath this city.} 
It was hidden well behind the ever-present Shroud, but she thought she could feel the reverberations of immense shapes slithering in the Beyond\dash burrowing in ever-benighted tunnels 'neath the earth, gnawing at the fabric of the Web. She could smell the rank breath of monstrous things pervading the air, and when she reached out with her senses, she thought she could almost feel the clammy skin of some behemoth abomination, coiled about her, smothering her with its massive bulk. 
\tho{But what? What do you hide, Malcur?}







\begin{comment}
\subsubsection{Rian}
\end{comment}
\new
From his hiding place, not comprehending a word, Rian saw the tall \dax{} lift his nose to smell the air. 
His tongue darted out. 
And it was no \scathaese{} tongue! 
A normal \ps{\scatha} tongue looked like a \ps{\human}. 
This one's tongue was long and slim and forked, and he tasted the air with it as would a snake!

The black one straightened and flexed the finger of his left hand. 
Rian squinted, then gaped. 
Those were not \scathaese{} fingers, either! Each of them sported a long claw! 
And when he looked closer, the black one's smile revealed not \scathaese{} teeth (which were no sharper than \psp{\humans}), but fangs.
Again, like a snake! 


%He understood that something was about to happen.
%\tho{This}
The \scatha{} held his right hand in a fist before his chest, touched it with his left, and Rian watched as he raked his sharp claws along the back of his own hand, drawing blood. There was a seething sound, and smoke seemed to rise from the wound\prikker as if the black one's blood was boiling in his veins. He shook the wounded hand and the unearthly blood was freed upon the air, sizzling and bubbling, and then held the hand high in the air for the blood to drip down. 







\begin{comment}
\subsubsection{\Criseis}
\end{comment}
\new
\index{\xzaishann}%
\index{\shaeeroth}%
With her supernaturally clear sight, \Criseis{} could see how her lord's spilled blood ate like acid through the weave of the Realms. 
\tho{%
  The blood of a \secondgendragon. 
  Replete with the power of the \xzaishanns. 
  The power of \Chaos. 
  The power that makes and unmakes the worlds. 
  The blood that is life and death. 
  \emph{All} life. 
  And, perhaps, all death.}

\QuessanthIshnaruchaefir{} then spoke spellwords in the potent and ancient \maybehr{True Draconic}{\TrueDraconic} tongue. Those arcane words of power never translated well into mortal tongues, but the meaning of the incantation was approximately this: 

\index{\Rystessakhin}
\index{\AeocrithRystessakhin}
\index{\ophidian}
\index{glaive}
\draconicspell{%
  Come to me, o' glaive. \\
  By the blood of the \ophidian{} people, \\
  by the blood of the \xzaishanns, \\
  by the blood that is life I give thee form.\\
  I summon thee! \AeocrithRystessakhin! Arise!}

As his speech veered into the \TrueDraconic{} tongue, his voice changed, becoming unnaturally deep; growling, thundering, as if resounding from the throat of a far vaster creature. 
As if emerging from his true form. 

The air reverberated with the sorcerous power of those words. 
And the seething, hissing blood that spilled from his hand began to coalesce and solidify. 
% Rian squinted again, watching as it took the shape of\prikker \tho{of what?} Some oblong object. \tho{A branch? A rod? An\prikker axe?} Nay, not an axe, but clearly a weapon. 
Gradually it took the shape of an oblong object. 
First it resembled a rough branch. 
Then a rod. 
Then an axe. 
Then finally a scythe-like polearm, half again as long as \Ishnaruchaefir{} in his \scathaese{} form was tall, and crooked, and with not one edge but several wicked blades, pointing both forward and back, making the head almost half as wide from end to end as the shaft was long. 
A scimitar-like spike jutted upward from the top, making the weapon look like a monstrous cross between a halberd and a scythe; another such blade protruded from the back end. 

The flowing blood dried and hardened, taking on the texture of metal. 
The shaft was dull black, but the blades appeared to shimmer between several \colours, and it was as if each \colour embodied a shade of emotion. 
Glossy onyx black was a deep sadness, abandonment, solitude\prikker emptiness. 
Blood red was pain, agony like nails through the heart. 
And a fierce, fiery yellow that was a great, superhuman passion, terrible and cruel in its searing intensity. 
A passion for what might be hunger, or hate, or love. 

Sinister power flowed in waves from the scythe. 
It was the glaive \AeocrithRystessakhin, \ps{\Ishnaruchaefir}{} dreadful weapon. 
\tho{%
  And the mark of his crime. 
  The source of much of his strength\prikker and perhaps, much of his weakness.
  
  \Rystessakhin. 
  Summoned and given form by his own blood.
  Symbolic of the cruel and bloody sacrifice it once took to forge that fell weapon. 
  Although it was not \emph{your} blood that was spilled that day, was it, Master \Quessanth? 
  
  But then, in an indirect way, it was.}
And \Criseis{} shuddered to recall that terrible day, when \QuessanthIshnaruchaefir{} had made his dreadful, irrevocable choice. 

The black sorcerer lifted the glaive to his lips, so close he could have kissed it, and whispered soft words, in a \scathaese{} voice again. \ta{I have need of you again, my love. There is work for us\prikker}

\tho{Oh, no. Now he is talking to it.} 
\Criseis{} fidgeted. 
In her experience, whenever her master started talking to the glaive, it meant something nasty was about to happen. 
% Then again, he rarely summoned the artifact in the first place unless he meant for something nasty to happen. 







\begin{comment}
\subsubsection{Rian}
\end{comment}
\new
At first, the hapless thief could but stare in awe and terror at the astounding conjuration. But while the black one stood mumbling to himself for a long moment, the Rian's wits gradually returned. 

\tho{A sorcerer! He is a sorcerer!} 

It all made sense now, including the way the \scathae{} had been able to wander all over the city with no one noticing them. He had heard that wizards could do that. 
\tho{An illusion. Or whatever it's called.} 
Rian felt proud of himself for being, it would seem, the only one in the city to see through the illusion. 
\tho{Not so all-powerful, now, are you?} he almost wanted to say. 

But a quick glance at the sinister weapon made him eat those words again, even before he could speak them. 

He peered closer. 

\tho{Is that something\prikker dripping from the blade? 
  Is it blood? Or\prikker tears?} 
The first guess was morbid, but the second was eerier still. Again Rian had to shudder. 







\begin{comment}
\subsubsection{\Criseis}
\end{comment}
\new
\Ishnaruchaefir{} was concentrating now, slightly bent forward, left hand flat above the ground and the other against a crooked tree, and \Criseis{} could perceive his feelings stretching out like tendrils into the Beyond. Searching. Probing. 

\ta{Where are you?} he mumbled. \ta{I know you are here\prikker} 

His physical fingers twitching slightly. 

His tendrils groped on. 

Then paused. 

He froze. 

Smiled. 

\ta{I have you now.}

% At length, \QuessanthIshnaruchaefir{} broke from his reverie. Again he laid one hand on a branch and concentrated, his aethereal senses searching the Beyond. 
% 
% But only for a moment. 

He raised the hand and quietly signalled to his servant with two clawed fingers. 

\tho{He has his prey,} \Criseis{} could tell. She retreated as instructed, away from the trees and into the shelter of a half-ruined house. 

\Ishnaruchaefir{} raised the glaive above his head. 
He spoke, and again his voice become impossibly deep and menacing as he intoned {\TrueDraconic} words of power:

\draconicspell{
  Hearken, o' dreamer of the benighted realms: \\
  \quad
    \KyaethemChreiAz!\\
  Black mother, bringer of death and rebirth: \\
  \quad
    \KhothSell!\\
  Thou who hast neither beginning nor end; \\
  thou who art the key, the gate and the spheres: \\
  \quad
    \NaathKurRamalech!}

A chilling wave of dread washed over \Criseis{} as her master invoked the forbidden names of the \xzaishanns, 
those dreadful alien gods from whom \Ishnaruchaefir{} and his people derived so much power. 
He spoke arcane words that echoed the ancient covenants forged by \Tiamat, she who discovered the \xzaishanns{} these many thousands of years ago. 







\begin{comment}
\subsubsection{Rian}
\end{comment}
\new
These ancient names and titles were so dire, so unwholesome that Rian, who understood nothing of the words, was nonetheless chilled to the core by the dark portent he sensed in them. 

Rian thought he could hear a faint howling, echoing from far off. 
\tho{%
  Things. 
  Terrible things. 
  Blind and savage. 
  Raging. 
  Beyond the dim.}

Then the sorcerer swung the polearm down, ramming the sharp back-end of the shaft into the ground. 

Rian felt the world shake around him. \tho{An earthquake!} was his first thought. But then he realized that the ground under him was actually not moving. The quaking he felt was within his mind. It was as if his brain writhed, convulsed, struggling to break free of its prison inside his skull. He imagined the air around him growing thick, dense. Like water. Fathoms and fathoms of water. Weighing down upon him. Grinding him flat. Squeezing his insides out of him. 

Twisting in pain, Rian gazed up at the sky. Here a new horror assailed his already sorely tested eyes. 
It should by right be noon, 
%the sky had grown dark as midnight from horizon to horizon. 
but as he looked up the Sun was nowhere in sight, and from horizon to horizon the sky had faded to a dusty coal gray. 
And most awful of all were the stars that burned black in that deathly gray sky. Indeed, darker than black. Deeper than any darkness that should exist. They were like holes in the firmament; holes through which the direst, foulest of evils could seep, down from the endless, lightless chasms of nothingness that brood beyond the edge of the world; beyond everything, where all life and light end, where sanity ceases to have any meaning, where only inhuman chaos reigns; stretching on in all directions, forever. Of all this Rian saw a fleeting glimpse in those black stars that hung in the ghastly heavens, and it made him croak feebly his despair and huddle against the ground. 









\begin{comment}
\subsection{The \ghobal}
\end{comment}

\begin{comment}
\subsubsection{\Criseis}
\end{comment}
\new
\Criseis{} had finally caught sight of the boy whom her master had mentioned earlier. 
\tho{It must be the same one.} 
His awe and curiousity had overpowered his caution, making him careless and easy to spot. 
\tho{Poor boy.} 
She could see his terror, see how the Reality unfolding before his eyes was smothering his Shrouded mind. 
\tho{Go back into the Shroud with you.} 
She gestured at the \human{} and quietly incanted a spell of her own. 







\begin{comment}
\subsubsection{Rian}
\end{comment}
\new
Rian's vision blurred. His eyes swam and he saw nothing. 
He collapsed, then sat up with a jolt, as if violently awakened from sleep. 

\tho{%
  What happened?
  
  Where am I?
  
  Ruined hovels\prikker 
  
  The dead garden. 
  
  What am I doing here?}

The world was still hazy, unclear. A smoky fog seemed to rise from the gnarled trees. And at the edge of the garden\prikker \tho{A \scatha\prikker dressed in black\prikker with a scythe-like weapon\prikker}

The sight of the sorcerer and his glaive stirred his memory. 

\tho{That \dax\prikker is someone special. I followed him\prikker} 

But that was all that came to him. 

He felt dizzy, had to struggle to retain consciousness. \tho{Stay awake, Rian. This is important\prikker I think.}

%He saw a smoky fog rise from the gnarled trees. 
He saw the dark warrior step forward, into the dense fog. 
And in there, deep within the morbid garden, obscured by layers of mist, there lay in wait\prikker something. Something vast. Something hideous. Something that had no place in this world, nor any sane, wholesome world. 

And he knew that the black mage marched to face it. 







\begin{comment}
\subsubsection{\Ishnaruchaefir}
\end{comment}
\new
\QuessanthIshnaruchaefir{} felt the tremours in the Web of the Realms. He had drawn the creature out, and it had come. He strained his arcane vision, gazing into the Beyond. 

It was near. 

\ta{Come out, vermin. Come out.}

The tremours intensified, even carrying over into the Shrouded world, and the ground of the dead garden in Malcur began to quake in earnest. 

\ta{Time to go meet it. We cannot bring this city down around our ears, after all.} 

And \Ishnaruchaefir{} drew upon his connection with the \xzaishanns{}, and he submerged through the layers of the Realms. Further away from Malcur and into the Beyond. 

\index{\Nyx}
And from out of the Stygian, subterranean depths of \Nyx, the Twilight Realm, his foe crawled forth. 
Of behemoth proportions it was, and it brought the charnel stench of cosmic death and decay. 
Wormlike, pallid gray in \colour, and gaping with a myriad hungry mouths, it slithered up to meet him. 

\index{\ghobal}%
\ta{As I suspected. A \ghobal. They have brought a \ghobal{} to Malcur. Impressive.}

The beast towered before him, easily a dozen times as long as his humanoid form. 
\ta{And we cannot have that, now, can we?} 
And so, calling yet again upon the \xzaishannic{} power in his blood, \Ishnaruchaefir{} cast off his mask and assumed his true form. 









\begin{comment}
\subsection{Battle beyond the Shroud}
\end{comment}

\begin{comment}
\subsubsection{Rian}
\end{comment}
\new
%The crushing, drowning sensation had passed, and Rian felt like he was thinking clearly again. Yet the scene before his eyes still seemed more like a hazy dream than reality. 
Rian was not sure if he was awake or dreaming. 
\tho{I hope I am dreaming.} 
Some veil like dark smoke obscured the garden, hiding the black one from view. %, giving him only vague glimpses of the black one. 

Then there came a monstrous sound. 

Roaring. 

Shrieking. 

Groaning. 

Rattling. 

From not one throat, but many. If, indeed, things capable of making such sounds had anything as familiar as throats. 

It came from deep beneath the earth. It came from all around him. It came from inside his head. But above all else, it came from the darkened garden. From the centre of the opaque haze. 

He heard a voice, then. Deep, growling, inhuman. But definitely a voice, speaking powerful words in an alien tongue. 
%It spoke 
\tho{The voice of the sorcerer.} Rian could not remember how he knew this, but he though that un-\scathaese{} voice was somehow that of the dark-scaled sorcerer. 

And a faint, distant howling, barely audible above the monstrous roaring. \tho{Or did I imagine it?}

There! Within the cloud, a flash. The glinting of metal. 

\tho{The scythe\prikker} 

The groaning noises intensified. 

The battle had begun. 

%And there! A glipse of what he thought was the black one
Terrible sounds of combat could be heard. 
The swish of steel through the air. 
The grinding of huge jaws. 
The clash of massive bodies. 
Grunts of pain. 
And terrible words in no \human{} tongue. 

And through the fog, through the blur that veiled everything, he saw glimpses. Flashes of light\prikker \tho{Lightning? Fire?} 
The writhing of towering things\prikker \tho{A worm? Worms?}
And black scales. Immense dark wings. Claws. Teeth. Horns. Blades. 
The splattering of alien blood. 

Rian did not know how long the battle went on. It could have been heartbeats, or a whole afternoon. \tho{Or a whole night, if I am dreaming.} 

Then suddenly, a high shriek ripped through his ears like a knife. 

The shriek became a rattle. 

The thrashing of a huge body, or bodies.

Seething, like boiling water. 

Thumping. 

Then silence. 

A long moment passed. 

\tho{%
  Is the battle over? 
  
  Who won?}

The silence stretched. Again he had to struggle to stay awake. The world swam before his eyes. \tho{Must not doze off. Must not.}

Then, movement. 

Rian tried to focus his blurred eyes. At the edge of the garden, something. Something was emerging. 

Black. With a great bladed weapon. 

\tho{The sorcerer. He prevailed.}







\begin{comment}
\subsubsection{\Criseis}
\end{comment}
\new
\Criseis{} saw her master soaked in the ichors of the thing. Brown, gray, ochre slime sticking to him. The battle had been awesome to behold, but he had slain the \ghobal. 

\tho{\Ghobal. 
     Horrid thing. 
     My lord has not faced such a foe in many centuries.}

\ta{Well, \Criseis. I believe this concludes our\prikker} 

He paused. 
They both felt it. 

And a presence transcended the boundary of \Nyx, surfaced into Malcur. 



\begin{comment}
\subsection{A god in the flesh}
\end{comment}

\begin{comment}
\subsubsection{Rian}
\end{comment}
\new
Rian saw clearly as the two figures appeared. 
They were like \humans{}\dash a man and a woman\dash but\prikker \emph{greater}. In all ways, greater. 

The one in front, the male, was immensely tall, overtopping even the great \scatha{} by a whole foot. 
His skin was obsidian black, his flawless face beardless and youthful, his hair flowing long and shining white. 
And, most incredible of all, huge white-feathered wings sprouted from his back, spread wide and spanning twice his height.
%to a massive span of twice his height.
% each being's height\dash his pure white, hers gray and tipped with black.

\index{pistol}
Having materialized high up in the air, he now descended with gentle flaps of his wings. 
He was dressed in an immaculate robe, white like his hair and wings and adorned with silver and diamonds. 
His black-skinned hands had long nails lacquered pearly white. 
Every one of his ten fingers was decorated with a jeweled ring. 
In his hand he held a long-barrelled pistol of shining gray metal with a handle of what looked to be ivory. 
A very long object was slung across his back\dash possibly a staff or polearm. 
The upper edges of his wings were covered by a slim shin of silvery metal that seemed to taper to a sharp, sword-like blade. 

She was wingless, but hovered in the air nonetheless. 
%The woman was 
Shorter than the male, her skin ashen gray skin and hair raven black,
she wore a dress fit for any queen or princess, striped and patterned in glinting gray, black and silver. Her jewelry, too, was of silver, and a sabre hung scabbarded at her side. 

Rian he was struck dumb. He could but cower and stare. 
Surely these resplendent beings must be angels! 
The woman's beauty was such that the young man was very near ashamed that that he had once though mortal women attractive. 
But the male was even more glorious in his radiant, androgynous perfection. 
\tho{%
  Such magnificence. Such might. 
  %And such beauty, beyond any man or woman.
  No, not an angel. A god!
  %\prikker nay, gods! \tho{
  Before my eyes\prikker a god in the flesh!}
The \human{} would have fallen flat on his face in worship of these superhuman avatars, had he the courage to move at all.

The god softly alighted, the goddess close behind him, as with shining silvery he eyes regarded the scythe-wielding sorcerer, stained now with putrid slime. 
\tho{I see now! The god has come to vanquish this warlock and his black magic.} 

Rian strained his memory. 
\tho{What was the \ps{\scatha} misdeed? What had he been up to?} 
But he could not remember. He had followed the sorcerer and his companion through the city to the dead garden, and\prikker something had happened. The sorcerer had worked his forbidden magic. That must be it. And now the god had come to punish this blasphemy. 









\begin{comment}
\subsection{\Teshrial}
\end{comment}

\begin{comment}
\subsubsection{\Criseis}
\end{comment}
\new
% \begin{comment}
\index{\resphan}%
The white-clad male \resphan{} spoke then, in the tongue of his kind. 
\ta{%
  Lord \QuessanthIshnaruchaefir.
  So, it was indeed you. I thought I had divined your presence.}

\ta{Foolish of you, then, to accost me,} \Ishnaruchaefir{} replied in his own language. 
%\ta{But will you not introduce yourself?}
\ta{Who are you?}

\index{\Teshrial}
\index{\CiriathSepher}
\ta{%
  I am \Teshrial{} of \KiriathSepher.}
He waggled his fingers at his companion. 

\ta{%
  Lord \Ketheran{} \Teshrial,} she proclaimed, 
\ta{%
  is the son of \Tuerdal, hero of the \Kezeradi{} War, and of \Zereth, in turn the daughter of \Azraid, the High Lord \Sathariah{} of \KiriathSepher.} 

\Teshrial{} himself, of course, was too \quo{modest} to brag about his own titles, and thus had to have his subordinate introduce him. 

\Ishnaruchaefir{} bared his ophidian fangs in a smile. 
\ta{%
  One of a young generation. 
  So, a whelp of a whelp of a leech, is it? 
  A leech who is, in turn, the spawn of cosmic vermin. 
  I am sure you are honoured to make my acquaintance. 
  \Ketheran.} 
The last word dripped contempt. 

\tho{%
  \Teshrial. 
  \Azraid. 
  Only those two names were noteworthy. 
  \KiriathSepher{} goes with his garment, and \ketheran{} goes with the smell. 
  The smell of the blood\prikker
  
  Of a young generation he may be, but of a high rank. 
  The jewelry around his neck identify him as one of the \teshrialcircle{} circle.%
}

\Ishnaruchaefir{} shifted his gaze to the woman, with a raised eyebrow. 

\index{\Achsah}
\index{Ishiin}
\index{\Merkyrah}
\index{\resvil}
\ta{I am \Achsah,} the \resvil{} spoke. 
\ta{Of Ishiin in \Merkyrah.}

\index{Murder of the Dawn}
\index{\bezed}
\index{\ashenblood}
\Criseis{} licked both her eyes at this, not bothering to suppress the reflex. 
\tho{%
  \Merkyrah{}? 
  The very first empire of the \resphain? 
  An elder, then. 
  An ancient. 
  She must still remember the Murder of the Dawn. 
  Very likely she fought in it. 
  But she is of inferior birth, and thus subordinate rank\dash \achsahcircle{} circle, if I am reading those jewels right. 
  Making her subservient to the \ketheran{}, though he must be millennia her junior.
  
  Gray skin. 
  No wings. 
  She is \bezed. 
  \quo{\Ashenblood}, they call them.
  Ah, yes. It shows in her eyes.
  The subjugation. 
  The humiliation.}

\Teshrial{} cringed slightly and rolled his eyes. 
\ta{You must forgive my subordinate her coarse tongue.}

\tho{%
  What? Oh. Of course. 
  She almost broke the age taboo by letting slip that she is from \Merkyrah. 
  Heh. 
  \Resphan{} etiquette is not a thing to be trifled with. 
}

\Teshrial{} now met \ps{\Ishnaruchaefir}{} gaze. 
\ta{%
  I have heard much about you, \QuessanthIshnaruchaefir. 
  Stories attribute much to you.%
}

\ta{Hm. So you came to put me to the test?}

\Teshrial{} put up a frown. 
\ta{It saddens me that you have slain my creature.}

This caused even \Ishnaruchaefir{} to lick his right eye. 
\ta{%
  Your creature, \Teshrial? 
  You summoned the \ghobal? 
  Hm. 
  I am impressed.} 
The fire in \ps{\Ishnaruchaefir}{} eyes seemed to cool as he studied \Teshrial{} with that impaling analytical stare of his. 
As if seeing into his soul. 
Exhuming and laying bare all the \ps{\resphan} fears and weaknesses. 
\ta{%
  What a shame that your scheme is now ruined. 
  You have my sincerest condolences for senseless waste of your hard work.%
}

\ta{I am sure I do.}

Without warning, \Teshrial{} aimed his pistol and fired. 
Beams of searing light lanced forth in rapid bursts. 
\Ishnaruchaefir{} was struck and fell back, raising his glaive to ward off further attacks. 

% \Teshrial{} leapt into the air, gesturing with his free right hand and mumbling some words. 
% But \Ishnaruchaefir{} was faster. 
% The sorcerer growled a single word:

\Criseis{} took cover. 
She knew better than to be in the line of fire when her lord joined combat. 
She noticed \Achsah{} backing off too, making no move to aid her lord. 

\Ishnaruchaefir{} prepared a spell, gesturing with his free right hand and mumbling some words. 
But \Teshrial{} was faster. 
He spread his wings and leapt into the air, firing more bursts of energy from his pistol. 
\Ishnaruchaefir{} took several hits and stumbled back a step, his concentration seemingly disrupted. 

He raised his glaive and intoned spellwords. 
Chaotic energy began to course through the glaive, like red lightning running up and down the shaft. 
Again \Teshrial{} fired, and a harpoon of shimmering energy jabbed into \ps{\Ishnaruchaefir}{} side. 
Again \Ishnaruchaefir{} grunted, and again his spell fizzled. 

\Teshrial, more confident now, charged forward. 

\Ishnaruchaefir{} raised a hand and growled a single quick spellword:
\ta{\kingstongue{\Guthnyad!}}

\Criseis{} glimpsed an incorporeal \daemon{} as it sprang from the air near her master, speeding through the air at the \resphan. 
A shapeless blur of some unearthly \colour. 
\tho{A \daemonic{} \colour, found nowhere in the World of the Shroud.}

\Teshrial{} grunted in pain as the lightning-quick \daemon{} tore into him. 
% , splintering bones all over the right side of his body. 
% He tumbled to the ground. 
% Blood gushed from his flank, arm and shattered wing. 
He tumbled to the ground. 
Blood splattered from his right flank. 

\tho{That should ground him. 
  He will have a hard time flying with those wounds.
  It's hard enough to fly in the first place, here in the Shroud.}

\begin{comment}
  Ishnaruchaefir charges. 
  Teshrial hops to his feet, dances out of the way and deflects the attack with a strong blow of his wing. 
  
  Teshrial leaps back and has time to fire his pistol a few times. 
  Ishnaruchaefir has to fend off the attack, which slows him down. 
  This gives Teshrial time to back off further, dump the gun and draw his senaan. 
  
  Ishnaruchaefir charges again. 
  Again Teshrial dodges and parries with his wing. 
  This time, before Ishnaruchaefir can attack again, Teshrial is lightning-quick and swings the senaan and hits Ishnaruchaefir. 
  
  Teshrial casts a spell. 
  A blow of entropy strikes Ishnaruchaefir's body. 
  His Xzai-Shann energy rejects the entropy, but it is costly for his body. 
  A great wound springs open and blood fountains. 
  
  But by now Ishnaruchaefir is close enough that Teshrial can't dance out of melee range. 
  So Ishnaruchaefir draws on his stamina, ignores the painful wound and presses the attack. 
  He swings the glaive directly down on Teshrial. 
  
  Teshrial brings up his senaan in a parade that is technically perfect. 
  It should deflect the glaive and place Ishnaruchaefir in an awkward position afterwards, whereas Teshrial himself would stand in an ideal position to strike. 
  
  But Teshrial has failed to take into account the sheer brute strength of the Dragonlord's attack. 
  His parade should stop any normal attack\prikker but Rystessakhin just shears straight through. 
  Teshrial's prized senaan, Turishah, just BREAKS in his hands!
  
  The glaive tears through Teshrial's right side, arm and wing. 
  He recovers from the shock and casts a spell. 
  Another bleeding wound erupts from Ishnaruchaefir's body. 
  But Ishnaruchaefir ignores the wound and strikes again. 
  Cutting through Teshrial. 
  
  Teshrial slumps back, limp. 
  His head is cloven, split down the middle. 
  He is dead. 
  
  Ishnaruchaefir addresses \Achsah. 
\end{comment}

\ta{%
  You cannot defeat me, whelp,} said \Ishnaruchaefir.  
\ta{Not now. 
  Not in ten thousand years.}
He cast a glance up to the sky. 
\ta{No matter how the planets stand.}
With those words he charged, hefting his glaive. 

The downed \Teshrial{}, despite his injuries, quickly scrambled to his feet and leapt out of the way. 
\Ishnaruchaefir{} took a swing at the retreating \resphan, but the blow became clumsy and \Teshrial{} easily blocked it with his unhurt left wing. 
Sparks flew as the glaive collided with his silvery wing-blade. 
\index{\kilghan}%
\index{vambrace}%
\emph{\maybehr{Kilghan}{\Kilghain}} they were called, those vambraces for the wings. 
\Resphan{} wings were not nearly as fragile as they looked at first glance, and the \resphain{} utilized them to their full effect in combat. 

\Ishnaruchaefir{} was less nimble and slower to turn, so \Teshrial{} had time to retreat several steps and fire his pistol again. 
Sparks flew from \ps{\Ishnaruchaefir}{} \armour as he was hit, and seething blood was freed upon the air. 

\index{\senaan}%
\Teshrial{} had evidently realized that he could not avoid \melee{} forever, for he now discarded his gun and unsheathed the long weapon slung across his back. 
It was a \senaan, a type of sword used by the \CiriathSepher. 
It was even longer than \ps{\Teshrial} was tall; so long it was almost a polearm. 
The ivory white handle was nearly three feet long and the silvery, curved, single-edged blade fully seven feet. 

%   Ishnaruchaefir charges again. 
%   Again Teshrial dodges and parries with his wing. 
%   This time, before Ishnaruchaefir can attack again, Teshrial is lightning-quick and swings the senaan and hits Ishnaruchaefir. 

\Ishnaruchaefir{} charged again, but again \Teshrial{} was too quick. 
Even grounded, the \resphan{} moved with all the grace of a ballroom dancer and nimbly deflected the blow with his \kilghan-shielded wing. 
Then he spun around and made a stabbing attack with his \senaan. 
The tip bit into \ps{\Ishnaruchaefir} shoulder. 
He snarled in pain and anger and twisted around, hoping to pull the weapon from \ps{\Teshrial} grip, but \Teshrial{} quickly retracted it. 

%   Teshrial casts a spell. 
%   A blow of entropy strikes Ishnaruchaefir's body. 
%   His Xzai-Shann energy rejects the entropy, but it is costly for his body. 
%   A great wound springs open and blood fountains. 

Having kept his distance, \Teshrial{} seized the change to cast an offensive spell. 
He unleashed a burst of entropic energy, which \Criseis{} visualized as a bolt of smoky darkness. 
A bleeding wound erupted on \ps{\Ishnaruchaefir} left thigh where it struck. 
The life-draining entropy might have reduced a lesser opponent to a withered, lifeless husk, and even her master's body, replete with chaotic \xsic{} energy, had to struggle to shrug it off. 

But he ignored the pain and advanced. 

With his \senaan, \Teshrial{} still had the longer reach, so he had time to strike once more. 
\Ishnaruchaefir{} raised his glaive to parry, but realized too late that the attack had been a feint. 
His glaive was slow to swung, and his misaimed parade left him wide open. \Teshrial{} darted in and stabbed his right shoulder. 
Again \Ishnaruchaefir{} growled, but he took the pain without flinching. 
Now he was close enough that \Teshrial{} could not dance out of \melee{} range. 

He raised \Rystessakhin{} above his head. 

\Teshrial{} braced himself. 
Feet spread, wings and \senaan{} held at the ready to receive the attack. 

\Ishnaruchaefir{} struck. 
A wide sweeping blow. 

\Teshrial{} brought up his \senaan. 
Lifted his left wing to support it. 

\Rystessakhin{} came down. 

\Criseis{} could see how \ps{\Teshrial} every movement virtually sparkled with skill and perfection. 
His parade was impeccable. 
It would deflect the attack and force his opponent into an awkward position, whereas \Teshrial{} himself would be left in an ideal position to strike. 

Except for one thing. 
\Criseis{} smiled when she noticed it. 

%   
%   Teshrial brings up his senaan in a parade that is technically perfect. 
%   It should deflect the glaive and place Ishnaruchaefir in an awkward position afterwards, whereas Teshrial himself would stand in an ideal position to strike. 
%   
%   But Teshrial has failed to take into account the sheer brute strength of the Dragonlord's attack. 
%   His parade should stop any normal attack\prikker but Rystessakhin just shears straight through. 
%   Teshrial's prized senaan, Turishah, just BREAKS in his hands!

\ps{\Teshrial} technique was flawless. 
Or, it would have been, against a lesser opponent. 
But he had not faced the Destroyer before. 
He had failed to anticipate the sheer brute force of the \ps{\dragonlord} attack. 
Instead of glancing harmlessly off the \senaan{} like it was supposed to, \Rystessakhin{} simply shore straight through. 
\ps{\Teshrial} eyes widened in horror as he realized what was happening\prikker the instant before his \senaan{} \emph{broke} in his hands. 

The glaive continued, mercilessly ripping through \kilghan{} and wing alike. 
\Teshrial{} stumbled back at the last moment, narrowly avoiding a cut that would have sliced open his chest. 

He stared in disbelief at his broken sword and the mangled stump that had been his left wing. 
But to his credit, \Teshrial{} composed himself. 
Stumbling back another step to buy time, he cast another spell, pouring as much energy into it as he could muster. 
Entropic power tore through \ps{\Ishnaruchaefir} body, causing blood to fountain from several new wounds. 

%   The glaive tears through Teshrial's right side, arm and wing. 
%   He recovers from the shock and casts a spell. 
%   Another bleeding wound erupts from Ishnaruchaefir's body. 
%   But Ishnaruchaefir ignores the wound and strikes again. 
%   Cutting through Teshrial. 

\Ishnaruchaefir{} was hurt, but he refused to let that slow him down. 
He advanced another step. 

\ta{Curse you, Exile!} 
\Teshrial{} spat in desperate anger as he shuffled away. 
\ta{By the \banelords, you will pay for this indignity!} 

\Ishnaruchaefir{} did not reply. 
He raised the glaive. 
Struck again. 

This time \Teshrial{} had no defenses. 
\Rystessakhin{} cut straight through him. 
He slumped back on the ground, limp. 
His head was cloven in two, split down the middle. 
His blood and brains spilled out onto the dirt. 

\Teshrial{} was dead. 

\Criseis{} shuddered. 
\tho{%
  \quo{By the \banelords.} 
  A hideous name. 
  One that normally even the \resphain{} fear to invoke.
}

\Ishnaruchaefir{} straightened. 

\ta{You! \Achsah!} he called, not turning towards the \resvil. 

\Achsah{} had backed further away during the duel. 
\ta{\Ishnaruchaefir,} she replied, cautiously. 

\ta{Deliver a message from me to your lord when he revives.
  Tell him I found him an interesting opponent.
  Tell him I may be inclined to grant him a rematch, should he request it.
  And tell him\prikker}
\Ishnaruchaefir{} smiled.
\ta{Tell him to be better prepared if he decides to challenge me again.}

\ta{Um\prikker yes. I will tell him.}
With that, \Achsah{} quickly made herself scarce. 
She folded the Shroud, submerged into \Nyx{} and faded from sight. 

\Ishnaruchaefir{} began to walk away. 
\ta{Come, \Criseis. Our work is done.}
Then he paused.
\ta{Oh, wait. Where is that boy?} 
He glanced over at the \human, who still huddled behind some ruins. 
\ta{I suppose we had better kill the witness.}
He began to move towards the boy. 

% \ta{%
%   I Shrouded him. He will remember little\prikker of the \ghobal, at least. But I fear the \resphainz{} appearance broke the spell.}

\Criseis{} quickly moved in to block his path.
\ta{No! Please, master. I have Shrouded him. He will remember little.}

For a moment \Ishnaruchaefir{} just looked at her with level eyes. 

\Criseis{} twitched under his stare. 
Even though she knew in her mind that he would never harm her, the thought of challenging her lord still filled her with irrational fear. 
It was with some effort that she forced herself to stand her ground.

After a long moment, he sighed. 
\ta{I fear one day your sentimentality will be the death of us, \Criseis.
  But very well. 
  I will indulge you. 
  This time.} 
% He turned away.
% \ta{Now come.}





\begin{comment}
\subsubsection{Rian}
\end{comment}
\new
Rian froze as the black one met his gaze. Those eyes, glinting with a deep inner fire, once again bored into his soul. Stricken with fear, he wanted to look away, but could not. Not until, after what seemed like a day and a night, the \scatha{} finally released him and moved on. Then he crept beneath the crumbled wooden wall, daring not to even peek. 

He waited there until the footsteps faded in the distance, and then quite some time, before he finally slunk out and made to leave the garden. Above, the sky was blue and the Sun had returned. 

\tho{Returned? What made me think that? Hm. I must be crazy.}

And no wonder. His world had been shaken. His thieving mission in the merchants' quarter was completely forgotten as he trudged on, trying to make sense of this day. 

First the dark mage. The black magic devil. Then the white-shining god and the gray goddess. 

\tho{The god challenged the devil\prikker and was struck down.}

This was not supposed to happen. In legends, gods and angels always triumphed against devils. This was all wrong. 

And yet\prikker that look in the dark one's eye\prikker it had spoken to him. 

He began to doubt. 

Who was really the god, and who was the devil? 

\tho{Who was the dark one? Someone great. Someone splendid.} 
He must be, to best the white-winged god. 

And to do\prikker something. 

\tho{What did he do?}
Rian could not shake the 
%And he had a 
nagging suspicion that there was more. Something which he ought to remember but could not. 

\tho{%
  Who was the dark one? 
  
  Someone magnificent. 
  
  Someone larger than life.
  
  A devil? 
  
  Or a god?
}









\begin{comment}
\subsection{\Nithdornazsh}
\end{comment}
\placestamp{Dark Crescent throne chamber}

% Psyrex sits in his throne chamber. 
% He sees through his Psychic Eyes. These are a kind of telepathic daemons allowing you to see (and use other senses) through them. He has sent several of them to Malcur where they patrol. 
% He inspects the great Nexus point and the various junctions, and is pleased with the progress his underlings are making. The spilled blood and bound souls are channelled along aethereal threads reaching down into Machai, down to Nith'dornazsh. 
% 
%   In the \Psyrex{} scene, remove any direct references to the \Malcur \nexus. 
%   Just refer to \quo{the \nexus{} in Pelidor}. 
%   We don't want to tell the reader that \Forclin{} is a decoy. 
% 
%   Read about \Psyrex, \dragons, technology and living machines. 
%   Have \Psyrex use living machines. 

\LocarPsyrex{}, archmage and lord of the Dark Crescent, reclined on his throne. 
Green, yellow and red incense smoke swirled all around him. 
In the glare of the flaming braziers along the alls, the wisps of smoke lit up like the aurora borealis, filling the chamber with a rainbow-\coloured mist. 

But \Psyrex{} saw none of that. 
Before his eyes he wore the enchanted crystalline goggles that allowed him to see, hear and feel through the Psychic Eyes he had stationed in Malcur. 
The Eyes were invisible telepathic \daemons{} he had summoned; difficult to control but invaluable for reconnaisance. 
They saw not only the world within the Shroud\dash the Malcur visible to mortal eyes\dash but also into the Realms Beyond, and indeed, into the very weave of the Web of Realms. 

He inspected the great Malcuric \nexus{}\dash a point of convergence in the Web, where a myriad threads met and intertwined. 
The \nexus{} throbbed like a beating heart, sending pulses of life-giving power into the vein-like threads. 
And he inspected the many smaller junction points that surrounded the \nexus, propagating its pulses and vibrations out through the threads\dash threads that governed the lives of all in the city and made up the fabric of the world itself. 

And the pulsing of that spiritual heart, and the \colour of the aethereal lifeblood that flowed in the veins of Malcur, were pleasing to him. 
For in those veins flowed the vital energy of hundreds of mortal souls. 
Souls slain in ritual sacrifice and now bound to the \Matrix{} of the Dark Crescent. 
His slaves in death. 
Those souls were channelled along threads from Malcur and deep into the Beyond. 
With one Psychic Eye \Psyrex{} followed the bound souls as they spiralled down into an aethereal abyss, down into the dark Realm of \Machai. 

% He gazes down there and sees the dread necropolis of Nith'dornazsh with its spires, bulbs and crevices, its walls of flesh, blood and metal. It is now dead and desolate, inhabited only by undead, lifeless machines (!). And he sees all the soul-empowered threads reaching down and latching onto Nith'dornazsh like spiritual chains, preparing to pull the city up from the abyss. 
Down to the necropolis of \Nithdornazsh. 

The sorcerer sent his Eye circling over the fallen city, marvelling at its crooked spires, its bulbs and crevices, its walls of flesh, blood and metal. 
It was colossal, greater than any mortal-built city. 
And it was alive. 
Or, rather, it had been alive once. 
Now it lay dead and desolate, its fleshy parts shrivelled, its dusty streets silent and empty, save for the immortal undead machines\dash shambling hulks of metal and desiccated flesh\dash that still guarded their ancient city, thousands of years after the last breathing inhabitant had expired. 

Down into that ghastly necropolis the threads extended, fastening themselves around spires, latching onto the very ground. 
Like spiritual chains preparing to pull the dead city up from its grave in the abyss. 

Then\prikker a tremour. 

A fierce power shook the myriad threads and chains. 

\tho{A \vertex.

Here in Malcur. 

Its reverberations amplified by the \nexus{} point.

Who? 

A \resphan? 

\Achsah? \Teshrial?} 

Quickly \Psyrex{} cast a spell through the goggles, connecting him to another Psychic Eye, one stationed near the \nexus. 
Here the force of the tremour almost overwhelmed him for an instant, like how the light of the Sun blinds the one who emerges from a dark cave. 

He recognized the presence immediately. 
The vibrations, the smell, the \colours unmistakable. 

\tho{This is no \resphan. 
It is he!} 

The cryptic Wanderer in Darkness.
A terrible elder immortal, greater than any \resphan.

\QuessanthIshnaruchaefir.

A rogue \vertex. 
So much greater a threat by virtue of his sheer unpredictability. 
You never know which side Ishnaruchaefir is on. 

\tho{His presence here could throw everything into chaos. 

Heh. Literally.} 

% Then he feels a fearsome force in the web. A great tremour shakes the myriad threads and chains. 
% A vertex. 
% Here in Malcur. 
% Its reverberations amplified by the Nexus point. 
% "It is he! The cryptic Wanderer in Darkness. A terrible elder immortal, greater than any Resphan." 
% A rogue vertex. So much greater a threat by virtue of his sheer unpredictability. 
% You never knew which side Ishnaruchaefir was on. 
% His presence here could throw everything into chaos. 
% Heh. Literally. 
% Psyrex quickly lets his psychic eyes home in on the Vertex' position. He finds him in the place the Malcurians call the dead garden. A place most tightly fettered and connected to the Nexus point. 

\Psyrex{} quickly had his eyes home in on the \ps{\vertex} position. 
He found him near the outskirts of the city, together with his companion, \Criseis. 
Walking. 

\tho{What is he doing?}

The Psychic Eye followed the immortal on his seemingly aimless frolic through the city, until at last he halted near the centre of the city, in the place the Malcurians called the dead garden. 

\tho{%
  A mystic place. 
  Tightly fettered and connected to the \nexus{} point.
  
  What is he doing now? 
  
  What is this new thing surfacing? 
  
  A \ghobal? 
  
  \Ishnaruchaefir{} knows about the \resphain{} and their \ghobaleth. 
  How does he know? 
  From where does he get his intelligence?
  
  Moreover, he actually manages to draw one of them out. 
  And challenge it. 
  Hah! Such astounding audacity.
} 

\Psyrex{} looked on with great interest as the immortal fought the monster, eventually dispatching it. 

\tho{%
  Taking on \ghobaleth{} in hand-to-hand combat. 
  Insanity. 
  Exactly the kind of insanity to be expected of \QuessanthIshnaruchaefir.
}

Then another \vertex{} tremour. 

Powerful, but more subtle. 

\tho{%
  \Resphan. 
  No, \resphain. 
  Two. 
  One of them with the smell of a \ketheran. 
  
  Ah, yes. 
  \Teshrial. 
  And \Achsah. 
  Interesting. 
  \Teshrial{} does not often show his face like this.
}

He urged his Eye to sneak closer, hoping to catch their words, but their conversation turned out disappointingly short and inane. 
A battle ensued, and \Psyrex{} had to laugh out loud as the \resphain{} were prompty sent packing. 

\ta{%
  Hahaha! 
  That is what you get from facing up to the \draecchonosh. 
  \Ketheran{} scum. 
  Haha.
}

% "What is this? A ghobal? Ishnaruchaefir knows about the ghobaleth. And he actually manages to draw one of them out. Hah. Such astounding audacity."
% He looks on with great interest as the immortal dispatches and destroys the monster. 
% Then another Vertex tremour. The Resphain show up. 
% "Interesting. Teshrial does not often show his face like this." 
% The Resphain are promptly sent packing, and Psyrex has to laugh out loud.
% "Perhaps now you understand, Ketheran scum, that the Draecchonash are not to be taken lightly. Hahahaha." 
% Ishnaruchaefir then departs. 
% Psyrex scratches his head. What was he after? Why pop in to slay a ghobal and then leave? What does he expect to achieve? 

\Ishnaruchaefir{} then departed the way he had come, leaving the Dark Crescent sorcerer scratching his head. 
\tho{%
  What was he after? 
  Why show up in the middle of Malcur, slay a \ghobal{} and then leave? 
  What does he hope to achieve?
}

His thoughts were interrupted by yet another presence, this time intruding not in the physical world but directly into his mind. 

A \vertex{} greater even that \Ishnaruchaefir. 
So vast that it blotted out everything else, filling up the whole world. 
Power bled from it in waves, its potency scathing like fire. 

A terrible voice resounded in his head. 
A voice brimming with majesty and \daemonic{} might. 

The voice of a god. 

The voice of \emph{his} god. 

\Secherdamon. 

\secherdamon{\LocarPsyrex.} 

The mighty sorcerer almost quavered under the onslaught of those {True \Draconic} words, every one seeming to shiver the Web of Realms with the weight of its inherent power. 

\ta{Exalted Lord \Secherdamon.}

\secherdamon{Thou hast felt it.}

\ta{%
  Yes. 
  The presence of\prikker} 
\Psyrex{} paused, hesitant to speak aloud the name of his lord's hated rival. 

\secherdamon{\QuessanthIshnaruchaefir.}

The god's feelings, awakened by the thought of \Ishnaruchaefir, flowed over the sorcerer like a tidal wave of pure chaotic fury. 
There was hatred there, and anger, and\prikker other things. 
\tho{Envy?}

\secherdamon{Knowest thou the implications of this?} 

\ta{%
  No, Exalted Lord, I do not. 
  I cannot guess his motives. 
  But this development worries me. 
  His presence might call down unwanted attention upon our affairs.
} 

\Secherdamon{} was silent for a long while. 
Then: 

\secherdamon{%
  Continue thy work, \LocarPsyrex. 
  Inform \Nzessuacrith. 
  And be watchful of the Cabal. 
  %Learn how they react to this. 
  Study their reaction. 
  
  If \Ishnaruchaefir{} returns\prikker 
  I shall take action.
} 

\Secherdamon{} withdrew from the sorcerer's mind, leaving him feeling drained and empty, deprived of his Exalted Lord's touch. 
He sat long in silence, pondering this situation. 

\tho{%
  \QuessanthIshnaruchaefir. 
  One of the greatest rogue \vertices{} in the known universe. 
  Casually strolling through a city built on top of a major \nexus{} point. 
  Challenging and destroying a \ghobal{} in single combat. 
  Then casually strolling out. 
  
  He knows that everyone worthwhile within hundreds of miles must have noticed. 
  Is he playing a mind trick on us? 
  
  How much does he know? 
  He knows of the \ghobaleth. 
  Or, at the very least, of the \ghobal. 
  
  Does he know of our plans in Malcur? 
  Does he know about \Nithdornazsh? 
  
  And what to do about it? 
  Is this a trick? 
  What is he expecting us to do? 
  Does he seek to aid us or thwart us? 
  
  Curse you, \Ishnaruchaefir. 
  
  \quo{Take action.}
  
  If anyone is capable of \quo{taking action} against \Ishnaruchaefir\prikker then it is \Secherdamon.
}
 
\end{garbage}