
\part{\DominatorsofMith}















\chapter{\FirstbanewarBook}
Tells the story of the \ophidians, the origin of the \draecchonosh{}, the coming of the \banes{} and the \firstbanewar. 















\section{Pre-History}
In ancient times there were three peoples that dominated \Miith{}: 
The \krakens, the \xss{} and the \voyagers. 

Only the \krakens{} were native to \Miith{}. 
Billions of years ago they ruled the Realm. 
Then they became tired and went dormant. 









\subsection{\Voyagers come to \Miith}
\target{Voyagers come to Miith}
The \voyagers{} came from space in their spaceships. 
They created life in their \quo{Genesis Pits}. 

\target{Voyagers create the Heart}
The \voyagers{} created the Heart from some Chaos power. 
They shaped \Miith{} into something that looked like modern-day \Miith{}. 

Perhaps they also created the Sun, which is a manifestations of the heart. 
But I doubt that. 

Perhaps the \voyagers{} created \emph{blood}, the vessel for the power of the \hr{Heart}{Heart of \Miith} and the foundation of all \Miithian{} life. 

\target{Voyagers create mother-mass}
They tampered with the \noggyal \hs{mother-mass} (which was \hr{Noggyaleth were the first life}{the first life form on \Miith}). 
From it they shaped all sorts of life. 

They enslaved the \noggyaleth and used them as machines and slaves and even houses.
The \voyagers taught the \noggyaleth much. 
Thus was sown one of the seeds that would eventually cause the \pps{\voyagers} downfall. 

When the \voyagers{} shaped all their life-stuff, they unwittingly tapped into a sinister force; the energy of some dark god of life and death. 
Perhaps a \kraken, perhaps a \xs{} (\hr{Kyaethem Chrei Az}{\KyaethemChreiAz}?). 
This entity infested their \dweomers{} and their \hs{mother-mass}. 
The \voyagers{} did not discover this until very late. 
From there they could only hope to contain the taint, not cleanse it. 
Later their creations rebelled against them. 





\subsubsection{\Voyagers defeated by \xzaishanns}
\target{Voyagers challenge XS}
The \xss{} invaded.
After waging war for millions of years, they wiped out the \voyagers{}, who had previously dominated \Miith{}. 
The cataclysmic climax of this war transformed \Miith into a Hell of lava, fire, chaos and death. 
It caused a mass extinction, exterminating most life on the planet.

\lyricsbs{Vital Remains}{Icons of Evil}{
  Defame the names of all your dead gods.\\
  Vomit upon the path of salvation.\\
  Watch the creator succumb to extinction.\\
  The hunter now the hunted,\\
  you become the prey for us all.
}

Later, the \xss{} and \krakens{} waged wars. 

Then the \xss{} went dormant. 

Billions of years later, this life that the \voyagers{} had created would become the \ophidians. 
But they also created some horrid abominations. 
Something like the shoggoths from \authorbook{H.P. Lovecraft}{At the Mountains of Madness}. 
Maybe these are the \hs{Bladed People}. 

Maybe I should have some gruesome \trope{BodyHorror}{Body Horror} scenes with this primordial slime or blood. 





\subsubsection{\XzaiShanns left behind ruins}
\target{XS ruins}
The \xss{} left behind some ruins and stuff from the age when they ruled \Miith{}. 

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  I built temples, statues and pyramids \\
  as monuments of my endless might.\\
  Colossal knowledge lays hidden in tablets and shrines, \\
  protected by spells and incantations.
}









\subsection{\Voyagers erect Palisades}
\target{Voyagers erect Palisades}
\target{Palisades}
The voids between planets were \hr{Horrors of the Void}{filled by all sorts of horrors}.
When the \voyagers settled \Miith hundreds of millions of years ago, they erected dimensional barriers around the Realms of \Miith to keep it safe from these horrors.

In a sense, the \xss were some of these \quo{horrors} that the \voyagers feared.
They were some of the greatest \quo{horrors}.

These dimensional barriers, known as the \Voyagers' Palisades, were an early Shroud-like construction, but much better made (by the super-advanced \voyagers), and so had none or few of the destructive side-effects that the later Shroud had.

The Palisades also kept the \banes out, but eventually the \banes managed to drill through.

The \ophidians had some limited understanding of the \voyagers' work, and they drew on it.
They built the \hr{Crystal Sphere}{\CrystalSphere} to patch up the holes in the Palisades that the \banes had made.









\subsection{Poetic version}
\subsubsection{The \voyagers{} and the \krakens}
Once there were the \voyagers, a race of mighty beings (gods, if one wills) who \travelled across the Universe, seeding worlds they found with life. In primordial time, billions of years ago, they came to \Miith{}, desiring to make the world theirs, a breeding ground for their creations. 

But \Miith{} was not barren. Before the \voyagers{} came, \Miith{} had her own children, her own indigenous life, and the greatest of them were the \krakens, the native overlords of \Miith{}. Terrible creatures they were, and immortal. And they were jealous and cared not for invaders, but craved \Miith{} as their birthright, and when the \voyagers{} sought to conquer their world, they fought. Few were the \krakens{}, numbering scarcely a dozen against the thousands of \voyagers{}, great and mighty in their own right. Yet in their wrath, the \krakens{} proved more than a match for the invaders, and in every conflict they would prevail. With valour and fury the \voyagers{} would fight, and with despair, for the \krakens{} were immortal and wielded the primal power of \Miith{} herself. Their leader and mother, the great \Kraken{} Queen, was the mightiest of all the children of \Miith{}, and none could stand before her when she rose in fury. 

But the \krakens{} were indolent, and they would often sleep, their entire race, for aeons at a time - millions, even hundreds of millions of years. And so, whenever the \krakens{} slept, the \voyagers{} would invade \Miith{}, to populate the planet with myriad life forms of their devise. And every time, after an aeon, the \krakens{} would awake to vanquish the \voyagers{}, scour the world of their creatures and repopulate it with their own spawn. But inevitably, the \krakens{} would once more go dormant, and the \voyagers{} would return to begin their work anew. 

For the \voyagers{} seek ever to perfect life, and \Miith{} is precious to them, for \Miith{} is an anvil on which to forge and shape their creations, their works of art. And a most excellent anvil is Mother \Miith{}, for it is her nature to take what is given to her and break it down and hammer it into a new shape, greater and mightier than before. The \voyagers{} have \travelled the universe for billions of years, and they have known many planets. Many worlds are hostile, wastelands of death that will destroy life and cause it to decline and decay. Other worlds are indifferent, possessed of no powerful energy, positive or negative. They will allow life to exist, but they will not support it. On such worlds, life will persist, but it will stagnate and remain humble and never know greatness. Not so Mother \Miith{}. She is possessed of a soul, and she is strong and fierce and indomitable. A loving mother is \Miith{}, but also cruel. The weak among her children she will destroy, and they shall have no legacy and know only oblivion. But the strong among her children she will cherish and glorify. Forged in fire and tempered in blood they shall rise, growing ever stronger, and they shall know greatness. For \Miith{} is a crucible of life, and her like is seldom found in the universe, and the \voyagers{} knew to cherish her. 





\subsubsection{\Moroch{} and the \nagae}
So the history of \Miith{} is divided into such cycles of creation and destruction in the cosmic struggle between these factions, the native \krakens{} and the alien \voyagers{}. 

Our story begins in one such cycle. The \voyagers{} had filled \Miith{} up with their creations, but they were fled, for the stars moved, and they knew that the \krakens{} would soon awaken. And one of the \krakens{} did awaken; in this day and age he is called \Moroch{}. What is his aim we cannot know, but when he awoke he began not to destroy, but to create. From the sea he took primitive beings, creatures of the \voyagers{}, and reshaped them in his own design. He gave them strength of body and mind, and bestowed upon them the power of thought, and he made them his servitors. 

The years passed, a million years and more, and still the \Kraken{} Queen and her brethren slumbered, and even \Moroch{} grew sleepy and fell dormant. But his spawn lived, and they grew and prospered, and they recalled their sire and offered him prayer and tribute. Hybrid children they were, born from the womb of the \psp{\voyagers} creation but fathered by a \kraken{} lord. Lowly they were, yet in this age they were the lords of \Miith{}, and their built their cities in the deep oceans across the globe, and they were the \nagae{}. 















\section{The \Ophidian{} Civilization}
\target{Ophidian humanoids}
Hundreds of millions of years after the \voyagers{} had left \Miith{}, the \ophidians{} evolved. 
From the ashes of the devastated world they rose up to make themselves its masters.
They were snake-like humanoids, not much bigger than \humans{} or \scathae. 
They went on to form great empires and develop marvelous science and sorcery.









\subsection{Evolution}
The \ophidians{} \hr{Ophidians evolved}{evolved from reptiles} who were making the transition from \quo{cold-blooded} to \quo{warm-blooded}. 

They evolved intelligence and telepathic abilities. 









\subsection{Origin of the \nagae}
In the very early beginning, the \ophidians{} and \nagae{} were one species. 
But eventually they grew apart. 

The \ophidians{} were reptiles, descended from amphibians who in turn had evolved from fish. 
One branch of the proto-\ophidians{} took to the sea. 
The ones who returned to the sea eventually degenerated into atavistic, fish-like forms. 
They came to resemble eels more than snakes. 
The sea-dwelling ones took up the worship of the \Krakens{} and became the \nagae{}.  

They thrived, and even survived the coming \firstbanewar{} relatively unscathed. 
But they stayed in the seas, and their technology remained comparatively low. 









\subsection{Early culture}
\target{Early Ophidian culture}
They developed culture and civilization early on, many millions of years before \Tiamat. 
But they had the infinite patience of reptiles, so \hr{Ophidians are slow}{they lived very slowly}, and hence their culture also developed extremely slowly. 
Also, they were not very social creatures to begin with, with made things even slower. 

This also meant that they did not fuck up the ecosystem around them. 
Every new invention for the \ophidians{} might take many thousands of years, giving surrounding species time to adapt and not just be wiped away. 

The \ophidians{} were physically and metally powerful, so they did not develop tools at first. 
On the contrary, their comfortable and slow lives gave them plenty of time to lie around and think. 
With their telepathy they could lie and think and at the same time communicate with their brethren across great distances. 
So they developed philosophy and science. 

They had the natural ability to control their own metabolism. 
From their they gradually learned all sorts of other mental body control (psychometabolism). 
They developed psionics. 
Eventually they also delved into sorcery. 

The \ophidians{} learned to utilize their \hs{torpor}. 
From this they would eventually discover the secret of immortality. 

% Slowly (over millions of years) they developed science and technology. 










\subsection{Great civilization}
\target{Ophidian golden age}
\target{Ophidian civilization}
\target{Ophidians and Nagae were one species}
\index{technology!\ophidian}
The \ophidians{} built a civilization which was great, mighty, proud, enlightened and technologically advanced. 
Albeit perhaps cruel. 

Back then the \ophidians{} were so powerful as to almost rival the \voyagers, or even the \xss. 
Certainly as powerful as, say, Elder Things or the Great Race from the Cthulhu Mythos. 

This was millions of years ago, before they waged a giga-war that destroyed the \ophidian{} humanoids and left their culture in darkness. 
Their civilization lasted for millions of years. 
The \ophidians{} lived very slowly, due in part to their \hs{torpor}. 

Or perhaps they lived all the way up to the \firstbanewar{} and the forging of the \hr{Crystal Sphere}{\CrystalSphere}. 



\lyricsbalsagoth{Invocations Beyond the Outer-World Night}{
  \ldots{} and their star-spanning progenitors, \\
  spawned beyond the outer-world night.
}



\lyricstitle{\emph{Call of Cthulhu} RPG p.118}{
  [The Serpent People] built black basalt cities and fought wars, all in the Permian aera or before. 
  They were great sorcerers and scientists, and devoted much energy to calling forth dreadful \daemons{} and brewing potent poisons.
}

\citeauthorbook[p.44--45]{ClarkAshtonSmith:UbboSathla}{Clark Ashton Smith}{Ubbo-Sathla}{
  At length, after aeons of immeroial brutehood, it became one of the lost serpent-men who reared their cities of black gneiss and fought their venomous wars in the world's first continent.
  It walked undulously in antehuman streets, in strange crooked vaults; it peered at primeval stars from high, Bebelian towers; it bowed with hissing litanies to great serpent-idols.
}





\subsubsection{Association with snakes}
\Ophidians were \hr{Ophidians and snakes}{traditionally associated with snakes}.





\subsubsection{Breeding work}
\target{Ophidians breed}
They had several entire races as their servants and slaves. 
And they controlled \daemons{}, whom they commanded to build their great cities. 

They learned bio-technology and biomancy. 
They started manipulating other races, breeding and tweaking them. 
They created their own servitor races and animals. 

That was the reason why, later on, there existed so many animal species on \Miith{} that could be domesticated: 
The \ophidians{} had been breeding them, millions of years before. 

Among other things, they helped shape the \hr{Nephil}{\nephilim} and \hr{Nycan}{\nycans}. 

Perhaps they created shoggoth-like monsters (the \bladedpeople?) who rebelled against them?





\subsubsection{Telepathy and speech}
Originally \hr{Ophidian telepathy}{the \ophidians{} were telepathic}. 
But \hr{Ophidians lose telepathy}{they lost it}. 





\subsubsection{\Ophidian{} philosophy}
The old \ophidians{} were \hr{Ophidian philosophy}{atheistic and rational}. 









\subsection{Wars against the \noggyaleth}
\target{Ophidian-Noggyal wars}
The \ophidians knew that the \noggyaleth existed. 
They did not know the \noggyaleth's true nature, although a few occultists suspected.
The \ophidians feared the \noggyaleth just as they did the \xss, but the \ophidian magic was mostly powerful enough to keep the chaotic, bestial \noggyaleth at bay or even destroy them.
In earlier days, the \ophidians waged great wars against the \noggyaleth and drove them underground.

\target{Noggyaleth lose a war before the FBW}
There was a great war between the \ophidians and the \noggyaleth shortly before the \firstbanewar.
The \ophidians won and the \noggyaleth were forced underground.














\section{\Sethicus (\yds{Sethicus creates Dragons})}
\Sethicus was an \ophidian.
He was controversial because he used \xs{}-based sorcery (\hr{Ophidians and XS}{which the \ophidian{} establishment frowned upon}).
He wanted to stage a coup against the existing \ophidian oligarchy, which he saw as decadent and ineffectual, something that was holding the \ophidian people back. 
He wanted to seize power and achieve \quo{great things} (whatever that meant). 

\Sethicus had imperial ambitions. 

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  Invocation to Seditious Heresy
}{
  And Here I Stand\\
  I who would be master of the Black Earth\\
  Have summoned you here secretly\\
  You who are faithful to me\\
  To share in the Black Kingdom that shall be\\
  Tonight we shall witness\\
  The breaking of the chains which Enslave us\\
  And the birth of a Dark Empire
}









\subsection{Technology and \Sethicus's innovation}
\target{Sethicus brought innovation}
When the \dragons were created, the \ophidians had only begun to build an \hs{interstellar civilization}. 
So the \dragons had only limited knowledge of the \ophidian super-technology.
The \dragons and \ophidians would both continue to develop their knowledge in the coming millennia, but in different directions. 

The \ophidians were generally \hr{Ophidians are slow}{long-lived, slow-living and slothful}, so they developed new ideas only slowly. 
Hence \hr{Early Ophidian culture}{their culture lasted for millions of years}.

\Sethicus's time was characterized by very fast development. 
\Sethicus was a very impatient and ambitious \ophidian.
He craved more than his race's slow, complacent lifestyle.
He craved action, excitement and renewal.
He was a great scientist who made many inventions.
He inspired many followers to live fast like him. 
In those decades and centuries, technology developed just as quickly as it might for a short-lived race.

\Sethicus himself was a brilliant scientist and made many exciting new discoveries in various fields. 
Alienist sorcery was his favourite subject and later came to dominate his life and career. 

\Sethicus was a primus motor when it came to pushing the boundaries of space travel and establishing an interstellar \ophidian empire. 
Before him, they had been a spacefaring race for millennia, but rarely ventured beyond their solar system, and they had done no colonization beyond the occasional research station in the solar system. 
\Sethicus made them found settlements on many planets and moons in the solar system and even beyond it, and they began terraforming processes. 





\subsubsection{Energy sources}
\target{Draconian energy sources}
\Sethicus's society required colossal amounts of energy to sustain it.
To procure enough energy they used dark spells to draw energy from the void and the Heart, and they sacrificed vast numbers of humanoids to feed their machines. 

\Sethicus himself helped build this network of power plants.
He used complex black spells which he alone fully understood to suck even more energy from the dying universe so it could fuel his \hr{Sethicus plan}{masterplan}. 

Compare to the Immortal Emperor and the Astronomican in \cite{RPG:Warhammer40000}, which requires the sacrifice of countless \humans daily to sustain them.









\subsection{\Sethicus's allies}
Among \ps{\Sethicus} allies were \Tiamat, \ApepNesthra and \Iurzmacul. 

\Tiamat was \Sethicus's lover. 

\Nexagglachel was the son of \Tiamat and \Sethicus, and thus the greatest of the three brothers.
\Ishnaruchaefir was the son of \Tiamat and \Iurzmacul.
\Secherdamon was the son of \Tiamat and \ApepNesthra.

They attracted allies by tempting them with power, glory and greatness.

\citeauthorbook[\quo{First Thought in Three Forms}, p.86--100]{%
  BentleyLayton:TheGnosticScriptures%
}{%
  Bentley Layton%
}{%
  The Gnostic Scriptures%
}{
  So, then, hear me O children of thinking; hear the voice of the mother of your mercy.
  For you have become worthy of the mystery that has been hidden since eternities, so that you might [\ldots{}].
  And the end of this realm and of this violent.
  I am androgynous, a parent with myself alone.
  [\ldots{}]
  The entirety through me alone. 
  It is I who am the womb of the entirety, giving birth to the light in glory.
  It is I who am the aeon that [\ldots{}] the completion of the entirely, namely Meirothea, the glory of the mother,
  And I project a voice of the sound into the eats of those who recognize me.
  And I am calling you to enter the superior, perfect light.
  When you enter it you will be glorified by the glorifiers; the enthroners will give you thrones; you will be given robes by the enrobers, and the baptists will baptize you; so that along with glories you become the glory in which you existed, luminous, in the beginning. 
}

The part about \quo{in the beginning} refers to the idea that \hr{Ophidians related to XS}{their pre-history is connected to the \xss}. 









\subsection{Discovering the \xss}
\target{Sethicus maps the way to Machai}
\target{Star-Maps of the Ancient Cosmographers}
\Sethicus-tachi discovered the \xss{} from the \hr{XS ruins}{ancient ruins they left behind}. 
Together they charted the cosmic paths leading to \Machai, the \xzaishannic{} homeworld that had been lost after the fall of the \ophidians. 
(These are some of the same paths that Chaos sorcerers would use millennia later.)





\subsubsection{\Ophidian origin}
\target{Sethicus discovers Ophidian origin}
It had been theorized that \hr{Ophidian parentage}{the \ophidians were descended from \xss}. 
It was \Sethicus who really understood the connection. 
He theorized that the \ophidians were related to the \xss.
Perhaps even created by them, or at least evolved from creatures created by them.
\Sethicus believed they had been \hr{Sethicus believes Ruin Satha created Ophidians}{imparted hunger/will/motivation by \RuinSatha, and then physical life by \KhothSell}. 
And he shaped his beliefs into mystical theories that could be used to cast magic. 

\citeauthorbook[p.16]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  A sliver of this transcendent black essence dwells in the darkest part of man's being. 
  Yes, a fragment of this demonic god lives inside every man, allowing him to be part of Greater Reality.
  Because \human reasoning has developed enough to understand unnatural logic, non-Euclidean geometry, quantum physics, string theory, abstract thinking and our holographic universe\ldots{} we can begin to understand what lurks Outside!
  
  We are the children of the Old Ones, and we are their progenitors.
  A select group of \human beings shall keep the Dark Gods alive in their words, their thoughts, and their deeds. 
  Because of our insane beliefs, a fragment of Greater Reality has Awakened inside us.
  Some liken this to a black flame, twist of Cain, being touched by the hand of God, an alien encounter, a divine spark, mark of Satan, gidt of Set, or call of Cthulhu.
  
  Whatever its name, it exists in the hitherto unexplored areas of our mind like some cyclopean race memory to which we are irrevocably drawn.
  This evolutionary nudge that was given to out species aeons ago allows us to comprehend godlike knowledge and become godlike ourselves. 
  
  \ldots{} seek out those Those Who Came Before.
  The Old Ones' understanding is carried on through the Cult of Cthulhu.
  Our organization merely tries to uncover Their ghastly, depraved illumination.
  The unknown can be terrifying, but that does not stop us from grasping it. 
  
  \ldots 
  
  The religion of the Old Ones\ldots{} is based upon the concept of fear.
  The unknown is the heart of both theologies.
  That nameless, black quality which forces the \human imagination to conjure up the richest dreams and the most hideous terror\ldots
  
  Fear that is felt, fear that drives, attracts, repels\ldots{} fear that is overcome!
  Inside the unknown is out salvation, if we have the courage to look\ldots{} and then plunge our warlock hands into the unplumbed, inky vortex!
}





\subsubsection{Voyage of discovery}
They explored the cosmos, looking for illumination and arcane knowledge. 

\lyricslimbonicart{Dynasty of Death}{
  I'm launching into the abysmal universe.\\
  Disembodied I enter the cosmic cataclysm.
  
  I discover stairways to celestial dreamscapes\\
  A dark unknown conjunction within an immoral dimension.
  
  Through dark tunnels in levitation, \\
  black cosmic space in manifestation.\\
  I escape the earthly pandemonium\\
  into a vast nocturnal sanctum.\\
  A nemesis for all evil I confess.\\
  My soul bleeds by all the forces I possess\\
  A benediction of unholy wrath and sorrow.\\
  My heart is buried in dark catacombs of horror.
}

They learned the grim truths and secrets of the universe. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  They
  were the words of a great thaumaturgist who had seemingly discovered a
  repository of aeons-old lore detailing the sidereal web of the cosmos, with
  arcane diagrams pinpointing certain astral portals and places of empyreal
  potency, a sort of pangalactic ley-line chart, if you will. 

  [The Thaumaturgist:]\\
  The Great Eye of the Universe opens! \\
  Through this astral art the secrets of the cosmos are mine to know\ldots{} \\
  for the stars are my dominion!
}

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Everything you have been taugh about the nature of Creation is a lie. \\
  This is a voyage in search of the truth. \\
  It will not be a pleasant journey.
  
  I have discovered a terrifying universal axiom which cannot be denied.
}

They learned of the origin of their people, and all life.

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Betwixt the hammer and the anvil are forged the stars\ldots{} \\
  On the wings of the ersatz ones\ldots{} \\
  through the fathomless abyss.
}

They feared this discovery, and the madness that the \xss{} might bring. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  Like a blackened and baleful sun shall I gaze down \\
  from beyond the cumuli and the firmament upon you. \\
  I alone must bear the burden of this fiend-wrested lore.
  
  New stars without number burn in the heavens, \\
  but the shadow of oblivion falls ever closer.
}

She discovered a wealth of cosmic knowledge, comparable to the Sith library in the game \emph{Knights of the Old Republic II: The Sith Lords}. 
Also comparable to the tale of the Empyreal Lexicon by Bal-Sagoth. 

\lyricsbalsagoth{Return to Hatheg-Kla}{
  Some would call it epiphany, others would deem it the final descent into madness\ldots{} whatever the case, the last vestiges of those tenuous palisades which had previously, and blessedly, safeguarded my reason and prevented my mind from accepting the full and staggering magnitude of the naked truth then crumbled, fading into nothingness like the dissolution of a night-mist.\\
  At length, one oppressively miasmic night, with such malefically portentous lore preying pitilessly upon my sanity, I began to descend through a myriad veils of sombre and swirling shades, finally surrendering my grip on wakefulness.\\
  And on that fitful, fateful eve, the last of the dreams came\ldots{}\\
  A waking dream?\\
  I dare not speculate.}






\subsubsection{\XzaiShanns slept}
At \Sethicus's time, the \xss had long been very deep in their sleep. 
As a consequence, the \Miithians had all but forgotten them. 
Many \ophidians did not believe they existed, and they did not believe that magic (in the form \Sethicus proposed) was even possible. 

But the \xss had begun to stir ever so slightly.
Thus \Sethicus was able to discover them and learn some of their secrets and make pacts with them so he could cast magic. 
\Sethicus became the founder of alienist magic.





\subsubsection{The keys to insight}
In order to summon the \xss{} and invoke their power, \Sethicus-tachi discover that they must find a number of \quo{keys}. 
After a while of searching they finally realize that the \quo{keys} are not physical objects but insights. 

They are told that some of the keys must be captured from their rival races. 
They only manage to do this when they realize that what they are supposed to steal/conquer is knowledge, not artifacts. 

\lyricsbalsagoth{Return to Hatheg-Kla}{
  A terrible sound filled my ears\ldots{} \\
  an insidious resonance which sent waves of excruciating pain coursing through my mind\ldots{} \\
  a sound which inexorably coalesced into a recognizable but entirely inhuman voice, a voice which slowly, inevitably, formed approximations of words which I could discern\ldots{}
  
  [The Crystalline Oracle:]\\
  Hearken, o' manling of the Tellurian orb\ldots{} the Circle closes.\\
  Perpare to embrace the agony of enlightenment.\\
  Know you of the Six Cataclysms?
  
  [The Aspirant:]\\
  I do. Six times has the world perished and been reborn!
  
  [The Crystalline Oracle:]\\
  You have discovered the true meaning of the six coruscating rings of arcane power?
  
  [The Aspirant:]\\
  Praise Klatrymadon and Zuranthus! The Six Keys!
  
  [The Crystalline Oracle:]\\
  Know you of the blackened orb which burned bright o'er ancient Lemuria?\\
  Know you of the sidereal flame which engulfed the high seat of power in Ultima Thule?\\
  Know you of that martial sorcery woven in the pitiless throng of epic battle?\\
  Know you of the astral power permeating the multiverse and the might of the cosmic codex?\\
  Know you of the rise and fall of glorious Atlantis?\\
  Know you the blasphemies contained within the Chthonic Chronicles?
  
  [The Aspirant:]\\
  I know all this, and more!
  
  [The Crystalline Oracle:]\\
  Have you, o' hybrid child of the cosmos, gazed into the Great Eye of the Universe?
  
  [The Aspirant:]\\
  I have.
  
  [The Crystalline Oracle:]\\
  And what did you see there, young Xerxes?
  
  [The Aspirant:]\\
  I saw oblivion and damnation.\\
  I saw truth, and enlightenment.\\
  I saw the closure of the Great Circle Without End.\\
  I saw the Sixth Great Cataclysm.\\
  I saw the alpha and the omega, \\
  I saw the beginning\ldots{} and I saw the end.\\
  The end of all there is!
}





\subsubsection{Summoning the \xzaishanns}
\target{Origin of Draecchonosh}
\target{Sethicus contacts XS}
\Sethicus-tachi contacted the lords of the \xzaishanns{} and learn to channel their power. 
They even absorbed some of the \ps{\xzaishanns} souls into themselves, transforming themselves into the mighty \draecchonosh. 

Have a scene where \Sethicus-tachi summon the \xzaishannic{} power, similar to \bandsong{Bal-Sagoth}{Summoning the Guardians of the Astral Gate.}

\lyricsbs{Hate Eternal}{Catacombs}{
  Rise up from the ancient tombs. \\
  Grant us all your infinite wisdom. \\
  Endure as you rise from the catacombs. 
}

\lyricsbs{Hate Eternal}{The Creed of Chaotic Divinity}{
  Awakened by this ancient creed. \\
  Evoked, the ancestry of thee.\\
  Forsaken for centuries of times. \\
  Exiled, all of their kind. \\
  Foretold, the inheriting of the Earth.\\
  Forewarned of this predestined rebirth. \\
  Engaged, the rising from below.\\
  Fear, all mortals, for what they shall bestow.
  
  Conjure all, so that they may sustain\\
  their race, of what they must retain.\\
  Spew forth incantations in vain. \\
  Invocate all that they try to negate.\\
  Enchant all of their wonderful splendour. \\
  Recant all of the texts that are sacred. \\
  Recreate all that has been begotten. \\
  Revive all that has been forgotten. 
}

\lyricsbalsagoth{The Empyreal Lexicon}{
  The key word of Transcendence!\\
  The key word of Transference!\\
  I shall liberate the rightful owners of the Lexicon\ldots{}\\
  the true rulers of the cosmos!
  
  X'atham-ry'aa! Tha'zai-tonn!\\
  Darker than a score of hells\ldots{} \\
  wherein astral horrors sublime dwell,\\
  Macrocosmic realms aflame\ldots{} \\
  Prey of fiends that have no name!\\
  Bow to the gods that have no name!}

The \xss{} are powers of evil whom the \ophidians{} used to fear. 

\lyricsbs{Vital Remains}{Icons of Evil}{
  Confront me now, defiler of human desire.\\
  Voracious hordes await the hour of ascension.\\
  Unravel their delusion,\\
  their translucent divinity.
}

When \Sethicus-tachi first invoke the \xzaishannic{} power, it goes wrong and the \xzaishanns{} wreak immense destruction. 
It takes some time for \Sethicus-tachi to learn to control and channel their power. 

\lyricsbalsagoth{The Voyagers Beneath the Mare Imbrium}{
  Fools! The Darklight Portal has grown strong.\\
  Only one moon remains in orbit.\\
  The mewling ape-spawned humans have discovered the icosahedron and the Lexicon's call can once again be heard throughout the stars, beckoning my ireful brethren to return to the slaughterous embrace of the fray!\\
  We have won! The orb azure is ours\ldots{} ours to enslave!}





\subsubsection{Guide appears}
A guiding god appears to \Sethicus-tachi: 
A \xs{} or a \hs{cosmic god}. 
He gifts them with knowledge and makes them worship the \xss{} and \Chaos. 
Compare him to Nyarlathotep from \HPLovecraft's stories. 

\lyricsbalsagoth{The Chronicle of Shadows}{
  [The Imperator of the Night \\
  (Hearken to the Attestation of the Sinistrous):]\\
  For it is the iniquity of man which compels him to these tenebrous gates,\\
  seeking opiate dreams and the alluring embrace of oblivion\ldots{}
  
  Such adoration bestowed upon me beneath the cryptic moon!
  
  (Behold the true purity of that which lurks concealed beneath the mantle of 
  shadow, and let the deluded, debauched sybarites flee in terror from that 
  darkness which they profess to embrace!) 
  
  Beyond the spheres of light and darkness, \\
  beneath distant pallid stars, \\
  I bring the iridescent glimmer of forbidden truth, \\
  seared in the crucible of blasphemy! 
  
  For amorphous they come, steeped in the fetor of ten thousand years, \\
  Abhorrent colossi spawned from the sinistrous cosmic spheres.
  
  And upon their tongues, vile secrets so terrible sweet madness is a redolent balm!
  
  Rejoice and revel in the triumph of the Dark. 
  
  I shall glut the maw of that ineffable nameless evil which lurks forever in the soul of man, for so it is written in the Chronicle of Shadows\ldots{}
}

\Xserasshana{} receives the \hr{True Draconic}{\TrueDraconic} tongue from the \xss. 

\lyricsauthorbookpage{Anton Szandor LaVey}{The Satanic Bible}{29}{
  Each verse is an inferno, each word is a tongue of fire.
  The flames of Hell burn fierce\ldots{} and purify! 
}









\subsection{Worshipping the \xzaishanns}
At first, \Sethicus and his fellows retained the \ophidians atheism and merely consorted with the \xss. 
Later they began to admire them more. 
As time went on, they became addicted to the power that the \xss could bring, and the began to worship them in earnest. 

\lyricsbs{Exmortem}{Sovereignty}{
  Admiring the triumphant demonthrone, \\
  sealed with the knowledge of time.\\
  Magic runes are carved here.\\
  Will you ever find the key?\\
  The bound demon in the earth\\
  is waiting to be released.
  
  He has \travelled beyond the worlds.\\
  He has danced with death.\\
  Now he controls it all.\\
  With strength he suffered.
}





\subsubsection{\XzaiShanns would soon rise}
\target{Sethicus believed XS would soon rise}
\Sethicus knew that the \xss were slightly more awake now than they had been for many ages.
In the beginning he interpreted this to mean that the \xss would soon arise and reconquer the world. 
Later he realized his error and revised his theories accordingly. 
It turned out the \xss were not at all about to rise. 









\subsection{\Dragons are created}
\target{Origin of Dragons}
\target{Sethicus creates Dragons}
\Sethicus became the first \dragon and the founder of the \draconian race.
He had a vision of a race of mighty super-\ophidians.

Using their advanced gene-technology and psychometabolism and \Sethicus's \xsic{} sorcery, they designed a race of \ophidian{} super-warriors. 
A number of \ophidian{} warriors volunteered to be transformed into these new superbeings. 

To create these creatures, the \ophidians{} took inspiration (and at times actual genes) from various fierce creatures, including \nycans, \corgoroth{} and \vreiiden{} (many of which had themselves originally been designed and shaped by \ophidians). 
And they infused them with all the \xsic{} ferocity they could conjure up. 

When the experiments where at last successful, the result was huge, flying monsters: 
\Dragons. 

As it turned out, the \dragons{} were able to breed true as a race unto themselves. 

The \dragons were the first \hs{True Immortals}. 

The \dragons{} enslaved legions of \daemons{} that previously served the \xzaishanns. 
They turned their gaze on \Miith{}, bent on conquest.

\lyricsbalsagoth{The Voyagers Beneath the Mare Imbrium}{
  My power is absolute\ldots{} greater even than that of Angsaar himself!\\
  I shall crush the Tellurian sphere,\\
  and the flaccid lickspittles who strive in vain to safeguard it!\\
  Yes\ldots{} The dreaming is over!\\
  Now, let the vengeance begin!}

This newfound power corrupted them into chaotic, \daemonic{} beings. Twisted by the \xzaishannic{} souls within them, they almost became \xzaishanns{} in \ophidian{} form. 





\subsubsection{Later someone discovers it}
Later in the series, I should have a story arc where someone discovers the truth of \Sethicus-tachi and their research. 

\lyricsbalsagoth{Star-Maps of the Ancient Cosmographers}{
  \ldots{} a fantastic and somewhat 
  horrifying dream in which I traversed a great black cyclopean cityscape,
  its towering stygian walls inscribed with some form of outlandish glyphs which
  seemed to writhe squamously and alter their shape even as I gazed at them.
  \\
  A sibilant whispering which seemed at once familiar and yet intrusively alien
  compelled me to walk to the edge of a particularly sinister looking edifice
  and peer out over its precipitous perimeter. 
  \\
  When I did so, I beheld this
  world of ours, recognizing vaguely the apparent shapes of the five continents,
  yet the entire vista seemed so distant that the whole appeared in its entirety
  no larger than a sphere which I could fit snugly into the palm of my hand.
  \\
  When I turned again to behold the looming obelisks, I found I could then
  easily read the previously untranslatable ciphers in the black stone. 
  \\
  They
  were the words of a great thaumaturgist who had seemingly discovered a
  repository of aeons-old lore detailing the sidereal web of the cosmos, with
  arcane diagrams pinpointing certain astral portals and places of empyreal
  potency, a sort of pangalactic ley-line chart, if you will. 
  \\
  Indeed, these
  Star-Maps of the Ancient Cosmographers seemed to take a not insignificant 
  toll on the author's sanity, as evidenced by the tone of his inscriptions, which
  seem to suggest that in discovering this Pandora's Box of dark elucidation,
  his fate was to be inexorably dogged by some nameless and implacable gloom
}









\subsection[Tyarith Kserasshana as a Dark Messiah]{\Tiamat{} as a Dark Messiah}
\Tiamat{} is a \trope{DarkMessiah}{Dark Messiah} kind of character. 
At first she wanted to bring enlightenment to her people. 
But the awful knowledge she discovered and absorbed drove her mad and caused her ideals to became twisted. 

She became traumatized and warped and gave in to perversity. 
She embraced and rejoiced in the most cruel, inhuman and destructive aspects of the \xss{} and their power. 

Compare to Horus from \emph{Warhammer 40,000}.

But despite her corruption (or perhaps because of it), she won and became queen of the \dragons. 
And in the \firstbanewar{} she was their first and greatest hope. 





\subsubsection{\Tiamat{} hears voices in her head}
Perhaps \Tiamat{} hears voices in her head, voices who are actually various figments of her mind and imagination. 
They question her principles and tempt her into perversity. 

Compare to the scenes in \authorbook{Graham McNeill}{False Gods} where Horus, in dreams, meets a phantom masquerading as his companion Sejanus. 





\subsubsection{\Tiamat{} worships the \xss}
\lyricsdimmuborgir{Relinquishment of Spirit and Flesh}{
  King of tempests and storms!\\
  Lord of innumerable figures and forms!\\
  Blessed with thy cold I am,\\
  as I upon the shoulders of mine\\
  bear the burden of Thine.
  
  Once I got touched by a fire from beyond,\\
  an invitation to darkness of which I could not resist.\\
  Caressed by the feathers of the fallen,\\
  I took the fate in my hand.
  
  Revealing Thy powers in visions and dreams.\\
  Invoking your magic at night.\\
  Honoured I am to mission Thy word.\\
  Within a creed is sworn of majestic might.\\
  An infernal allegiance in which I pay my share.\\
  An unholy awakening inside of which I intend to bear.
  
  Possesses by the true god of Earth I am.\\
  Possessed for eternity.
}

She becomes evil. 

\lyricsdimmuborgir{The Serpentine Offering}{
  My descent is the story of everyman.\\
  I am hatred, darkness and despair.
  
  Evoked and entertained through centuries.\\
  Wrathful and sullen. Dormant still.
  
  The ferocity pervades everywhere,\\
  waiting to be released at last.\\
  Hear my offering, ye bastard sons and daughters.\\
  Share my sacrifice.\\
  Share my sacrifice.
}

\lyricsdimmuborgir{For the World to Dictate our Death}{
  Let us sit by and watch \\
  Death and destruction's devotees revel. \\
  Let us sit back and witness \\
  innocent semen being poured\ldots{}
  
  Into the arms of Armageddon. \\
  Let it pour, more and more. \\
  Pure fucking Armageddon. \\
  Let it pour, more and more.
}

\lyricsbs{Marduk}{Legion}{
  A new era will arise \\
  as I see the black angels of the abyss fly\\
  and the demons come storming in the silent cloudless sky\\
  with their burning eyes of ripping evil.
  
  I am given strength from a thousand sinners that dwell \\
  in the everlasting, burning, roaring depths of Hell. \\
  With the demons the possess my blackened heart and soul\\
  I shall strive for Satan's triumph and reach infernal goals.
  
  Children of darkness, raise your blood-filled cups \\
  to our father with horns.\\
  In eternity, we shall blaspheme the one \\
  who was tormented with thorns. 
  
  Feel the darkness growing when we draw near.\\
  My name is legion, for we are many in here.
  
  Heaven shall burn accompaigned by the angels' cries.\\
  We shall invert paradise.\\
  Death to peace!
}

She preaches to her followers of a \daemonic{} paradise. 

\lyricsdimmuborgir{Allehelgens D\o{}d i Helveds Rike}{
  Utspente vinger over M\o{}rkets dype svelg.\\
  Satt til verden for \aa{} meske seg med pest og d\o{}d.\\
  Fr\aa{}tsende i synd og hor.\\
  Overmakten fra p\o{}lens bastarder\\
  n\ae{}rer behag i syndens hierarki.\\
  Et evig liv i Paradis\\
  er fullkommenhet i Satans dynasti.
}

She seduces them to follow her. 

\lyricsdimmuborgir{Cataclysm Children}{
  Are you born from the abyss,\\
  and have you sought the creed \\
  that drape the shadows\\
  of your own thought?
  
  Is your heart mesmerized \\
  by the fire that burns forevermore?\\
  And do the secrets from the flames \\
  hold the mysteries over which you preside?
}

They have become forever corrupted by the \xss:

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Sola Fide
}{
  Verily I say unto you, \\
  there is none righteous enough to resist, no, not one\ldots{}\\
  For your hands are defiled with blood, and your fingers with iniquity;\\
  Your lips have spoken lies, your tongue has muttered perversity.\\
  The heart of a lost angel is in the earth, \\
  the immaculate is abased\ldots{} forevermore.
  
  Sola Fide. Sola Deo Infernali Gloria.
  
  Neither stormful convulsions \\
  nor an apex of light shall break the yoke\\
  For he that keepeth His commandments \\
  dwelleth in him, and He in him.\\
  And hereby we know that He abideth in us, \\
  by the Spirit which He hath given us
}





\subsubsection{Some \Draecchonosh{} become bitter}
Some \draecchonosh, after tying themselves to the \xss, become bitter and evil. 

\lyricsdimmuborgir{For All Tid}{
  Hver en t\aa{}re er frosset.\\
  V\aa{}r sjel er lenket.\\
  V\aa{}rt hat er blodig.
  
  All glede er svunnet.\\
  All latter er forstummet.\\
  Alt liv skal ende i d\o{}d.
  
  I et kalt og \o{}de landskap\\
  skal den sorte horde tre frem.\\
  V\aa{}r herre skal stige opp for all tid, \\
  reise sitt rike igjen.
  
  N\aa{} er tiden kommet.\\
  Ja, knus de godes ord.\\
  La oss for alltid bli herskere \\
  p\aa{} denne jord.
}





\subsubsection{Maybe she was just a queen}
Maybe \Kserasshana{} was not the one responsible for all of the above. 
Maybe she didn't \quo{found} the \dzraicchenoss{} people at all.
Maybe the invocation of the \xss{} happened before her time, or maybe she was just one among several such summoners (albeit more powerful and daring than most). 
Maybe she was just a queen, a great leader who managed to unite her people. 





\subsubsection{\Dragons lose much in the transition}
The \dragons gained much wisdom, power and pleasure when they became \dragons. 
But they also lost much of their sanity, humanity, gentleness and the calm, rational philosophical disposition that \hr{Ophidian philosophy}{had been their trademark}. 

In a sense it was a fall from grace. 
But only very few \dragons saw it this way. 
\Iurzmacul and \Nexagglachel were pretty much the only ones. 
Only much later would \Ishnaruchaefir come to share their views.









\subsection{Some see the \xss{} as evil}
Some \ophidians{} see the \xss{} as a terrible evil that must not be allowed into the world. 

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\ldots{} 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}












\subsection{The \shaeeroths}
The first \shaeeroth{} were created some time around here. 

\target{Secherdamon does not become Shaeeroth}
\Nexagglachel{} and \Ishnaruchaefir{} became \shaeeroth{} early in their lives. 
\Secherdamon{} wanted to follow in their footsteps, but he knew he had not the courage nor the strength. 









\subsection{Rebellion}
\Sethicus and his \dragons rebelled against the other \ophidians. 

The war song of the \dragons: 
They revelled in their power and fury, their ability to cause destruction and fear.

\citebandsong{Nile:RamsesBringerofWar}{Nile}{
  Ramses Bringer of War
}{
  Wretched Fallen one of Khatti\\
  Rise against the oppressing Sword\\
  Encircled Abandoned Alone\\
  I Smite the vile Hittite Foe

  My Father Amon what carest Thee\\
  For the Vile and Ignorant of God\\
  My Father Amon what carest Thee\\
  For these Effeminate ones\\
  At millions of whom I groweth not Pale

  Raging like Menthu like Baal in his Hour\\
  Lo the mighty Sekhmet is with Me\\
  I enter in among them even as a hawk striketh\\
  I slay I hew to pieces and cast to the ground\\
  The royal snake upon my brow\\
  Spits forth Fire in the face of mine enemies\\
  And Burneth their Limbs
}

\Tiamat and \Sethicus both saw themselves as mighty conquerors:

\citebandsong{Nile:RamsesBringerofWar}{Nile}{
  Ramses Bringer of War
}{
  My Chariot Wheels trample the Fallen\\
  Cut to pieces before my Steeds\\
  And laying in their own Blood\\
  I Crush the Skulls of the Dying\\
  And Sever the hands of the Slain\\
  I Ramses\\
  Builder of Temples\\
  Usurper of Monuments \\
  Slayer of Hittites\\
  Bringer of War
}

\target{Draecchonosh war}
Some of the other \ophidians{} were swayed by the \psp{\dragons} power and glory and joined them, while others were repelled by their brutality and evil. 

\lyricsbalsagoth{The Empyreal Lexicon}{
  Stay thy hand and thy tongue, slave of the Outer Darkness\ldots{}
  Surely you are not foolhardy enough to dare awaken the dire titans of Z'xulth!}

\target{Tiamat kills Hesod-Nerga}
The \firstgendragons{} waged war against their fellow \ophidians{}\ldots{} and the world.

\HesodNerga{}, the great \ophidian{} hero, protested against his daughter's embracing this thoroughly evil power. 
Some of the \ophidians{} tried to \quo{save} \Tiamat, believing her brainwashed and possessed by the \xzaishanns{} against her will, and sought to exorcise the \daemons. 
They were dismayed to realize that \Tiamat{} was \trope{NotBrainwashed}{Not Brainwashed}. 
She responded by slaying her \HesodNerga. 

After this defeat, many \ophidians{} went into dormancy. 
\Tiamat{} conquered \Miith{} and reigned as its queen for tens of thousands of years, and the \dragons{} reigned with her as the lords of \Miith{}. 

Later, the term \quo\dragon, derived from \quo\draecchonosh, came to be used of all \ophidians, regardless of whether they possessed \xzaishannic{} blood or not. 

\lyricsbs{Exmortem}{Berzerker Legions}{
  Frigid storms and devastating raids.\\
  They are unconquerable.\\
  Frigid seas and devastating raids.\\
  Paramageddon.
  
  Runes imprinted in our skin.\\
  Northern magic surrounds us.\\
  Asa demons showing the way.\\
  Berzerker legions on all sides.
}

\lyricsbs{Monolith Deathcult}{Doomed To Slaughter}{
  The ancient gods are back on earth. \\
  We serve the book of blood.\\
  The blood of men will drench the fields in darkness.
}





\subsubsection{Religion}
The rebellion was religious in character. 
\Sethicus and his cohorts fought for their mystic beliefs.
His opponents fought for their materialistic, atheistic beliefs and saw \Sethicus as a dangerous fanatic and madman. 

\citeauthorbook[p.80--82]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  Only the cosmic horror that comes from the worship of oozing, malevolent monsters from vast and sprawling dimensions can set man on the right path.
  The Old Ones are the road to madness, destruction, and truth.
  
  Endarkenment is the opposite of enlightenment.
  The light strives to make the illusion real. 
  In darkness, Cthulhu Cultists shall have reality naked and exposed. 
  
  \ldots
  
  Purification will begin when the Cult of Cthulhu has taken over the world.
  Those who are biologically closer to the Old Ones will fully transform into their accurate conformation.
  That which was \human shall be cleansed; the eldritch beast is resurrection from the shadow that has learned to walk in Hell.
  The demonic soul is freed!
  
  \ldots{}
  
  Respect the laws of your land until the apocalypse begins.
  When Cthulhu Cultists number in the thousands, the balance of power will begin to shift.
  When the stars align, our bilious green and slimy inquisition shall be unleashed. 
  Death to all who oppose us!
}





\subsubsection{\Sethicus's ambition}
\Sethicus had \hr{Sethicus plan}{a mad plan}.









\subsection{\Sethicus reigns}
\Sethicus seized power and reigned as the ruler of the \ophidian empire. 
Perhaps this actually happened before he became a \dragon. 
He reigned for a long time, perhaps thousands of years. 

He was a cruel tyrant, obsessed with science and religion. 
He would often seem to neglect and ignore the welfare of his people (not only mortals but also \ophidians and \dragons) for the sake of his mystical ambitions. 
This was actually because of his \hr{Sethicus plan}{plan to save his race from False Life}. 
His intentions were good, but his means were brutal, and he was not good at explaining his reasons. 
The wiser he became and the further his epic plan progressed, the more inhuman and alien and incomprehensible his mind became to his fellows, and the more he became estranged from them. 





\subsubsection{\Sethicus is defeated}
\target{Sethicus betrayed}
Eventually, his fellow \ophidians, unable to understand his actions, decided that \Sethicus had gone mad and rebelled against him. 
Even \dragons joined the rebellion, including many of the younger ones. 
The ones that stayed loyal were mostly older ones. 

The rebels might include \Iurzmacul, \Nexagglachel and perhaps even \Ishnaruchaefir. 

After a long, violent insurrection, \Sethicus was defeated.
But his \dragons were immortal.
Far more so than the natural \ophidians.

The \ophidians lacked the sorcery to destroy them. 
Or if they knew how, they refused to use it on principial grounds because it was destructive sorcery and would corrupt their people and lead them on a sliding slope towards the \xs, which would be the end of their enlightened civilization.

\target{Sethicus imprisoned}
So they imprisoned \Sethicus-tachi instead.
They were interred in vast tombs and bound with fearsome spells and seals to prevent them from rising and claiming their revenge.
There they lay for thousands or millions of years.
\Nexagglachel was \hr{Nithdornazsh was Nexagglachel's tomb}{entombed in \Nithdornazsh}. 
Sometimes attended by living or undead monstrous servants (like the ones in \Nithdornazsh).

\target{Durance}
\index{Durance}
The imprisonment and entombment of the \dragons was also called the \quo{Durance of \Sethicus}, occasionally the \quo{Durance of the \Dragons}.

Later the \dragons \hr{Sethicus and his Dragons resurrected}{would be brought back and freed}. 





\subsubsection{Some \dragons disagreed with \Sethicus}
Not all \dragons agreed with \Sethicus's aggressive, warlike manner and his plans of conquest. 
\Nexagglachel was one of his critics.
\Nexagglachel was always calm and benevolent and thought of the future of the people (\ophidians as well as lesser races), whereas \Sethicus was mostly focused on his own greatness. 

When \Sethicus and \Tiamat were defeated and entombed, many of the remaining \dragons, convinced by \Nexagglachel, willingly stepped down and let themselves be entombed.
There they could lie and think and explore. 
(Many of the \dragons were scientists and philosophers who had been attracted by \Sethicus's free thinking.)

They felt sure that their time would come again, some day in the future. 





\subsubsection{Everything slow again}
\Sethicus's time was \hr{Sethicus brought innovation}{characterized by very fast development}. 
After \Sethicus's fall, \ophidian progress once again slowed to a crawl. 
The colonies were either abandoned or became sleepy, unambitious things. 









\subsection{Some \ophidians followed \Sethicus}
\target{Ophidians follow Sethicus under Durance}
After \Sethicus's Durance had begun, some \ophidians chose to follow his teachings and carry on his dark religion in secret. 
Later they would \hr{Cultists want to free Sethicus}{advocate freeing \Sethicus}. 

Other \Sethican cultists joined their \draconian masters in Durance, either voluntarily or forcibly. 




\subsubsection{\Sethican writings survive}
After \Sethicus was forced into \hs{Durance}, some \hr{Sethican writings}{writings containing the original words and theories of \Sethicus} regarding \hr{Sethican philosophy}{his philosophy} survived. 
These were treated as sacred by the surviving \Sethican cultists. 















\section{War against \Shuggon}
\target{Shuggon}
\index{\Shuggon}
The \ophidians still had their interstellar civilization. 
Eventually they discovered the world of \Shuggon. 
(This was probably after \Sethicus was laid in durance, but it might also have been before.)

\Shuggon was not a planet \emph{per se}. 
It was a cloud of planet-fragments and great air-filled caverns and swirling spaces and vortices. 
It was inhabited by a race of gigantic moth-like beings, comparable to the monsters Battra from \cite{Movie:GodzillaVsMothra} and Megaguirus from \cite{Movie:GodzillaVsMegaguirus}. 
The \ophidians waged a long war against these monsters.
The \ophidians lost and were eventually forced to retreat from \Shuggon. 
But passageways had been opened. 
In later ages, the spawn of the moth-things from \Shuggon would sometimes return to plague \Miith. 

The name \quo{\Shuggon} is taken from \cite{HPLovecraft:TheBlackTomeofAlsophocus}. 














\section{The \FirstBanewar (\yds{First Banewar begins})}









\subsection{The \bane{} invasion}
\target{Banes come to Miith}
\target{First Banewar}
\target{FBW}
\target{Banes come to Miith in spaceships}
\index{\firstbanewar}
The \banes \hr{Banes are created}{had been created on the world of \Erebos}.

And so it came to be that a \baneking{} (whom the \dragons{} would later came to call the \quo{\Voidbringer}) succeeded in opening a great dimensional portal from \Erebos{} to \Miith{}. 
Through it he sent forth millions of his \bane{} warriors to conquer and claim the new world in his name. 

The \banes{} came to \Miith{} flying in vast spaceships. They \hr{Why the Banes want Miith}{had their reasons for wanting \Miith}. 
They had flown all the way from \Erebos{}, a journey of hundreds or thousands of years. 

The people of \Miith{} were taken unaware when, on the Eve of the Black Gate, a massive rent opened in the sky and myriads of fiendish \bane{} warriors surged forth to conquer and destroy. 
Millions of \bane{} warriors and beasts, and hundreds of \banelords, all led by Daggerrain himself, invaded and attacked the \draconic{} kingdoms. 
Many millions perished in the initial assault and whole continents were laid waste before the \ophidians{} were able to muster their forces in defense. 
The Eve of the Black Gate marked the beginning of the \Banewar, the most terrible and devastating war that \Miith{} has seen since the \Kraken{} Queen last returned to her sleep. 

The \banes{} fought against the \ophidians{} in what became known as the \firstbanewar. 
They invaded with millions of \bane{} warriors and terrible magic. 





\subsubsection{\Noggyaleth remain neutral}
\target{Noggyaleth remain passive in the FBW}
The \noggyaleth had remained passive in the \firstbanewar. 
They were not highly intelligent. 
It took a long time for the \banes to get through to the \noggyaleth and form some kind of alliance. 
Until then, the \noggyaleth stayed hidden. 

Besides, the \noggyaleth were not stupid.
\Banes and \ophidians were bombarding the surface of the planet.
The \noggyaleth had a sense of self-preservation and did not want to expose themselves to that inferno.
Especially after \hr{Noggyaleth lose a war before the FBW}{having recently lost a major war}. 






\subsubsection{Technology at the time}
\target{FBW technology}
\index{technology!\bane}
When the \banes invaded, the \ophidians had an interstellar civilization.
They commanded dozens of planets. 
The \banes \hr{Interstellar Bane empire}{likewise had an interstellar empire}. 
But \Miith was the important planet that they had been searching for all along. 
It contained a Heart full of \voyager-tampered energy, and the \noggyal \hs{mother-mass}, which was the \quo{other half} that the \banes wanted. 

The war lasted centuries. 
At last the \ophidians were overwhelmed by the \bane hordes, so they retreated to their homeworld and barricaded it with the \CrystalSphere. 
The \banes conquered all their other planets. 

Both sides used weapons of \hr{Weapons of mass destruction}{mass destruction made with black magic}. 
And \hr{Living machines}{biological machine monsters}. 

The \ophidians had higher technology than the \banes. 








\subsection{\Sethicus resurrected}
\target{Sethicus and his Dragons resurrected}
The \ophidians realized they were not winning this war.
If they wanted to win, would need the help of \Sethicus and his \dragons, \hr{Sethicus imprisoned}{whom they had previously imprisoned}. 

\hr{Sethicus}{\Sethicus} was controversial because he used \xs-based sorcery (\hr{Ophidians and XS}{which the \ophidian{} establishment frowned upon}), but now the other \ophidians{} realized they would need every weapon at their disposal to defeat the \bane{} invaders. 
So after much negotation (first amongst themselves, then with \Sethicus), the \ophidians released the \dragons. 

The imprisonment and entombment of the \dragons was also called the \quo{\hs{Durance} of \Sethicus}, occasionally the \quo{Durance of the \Dragons}.




\subsubsection{\Sethicus made them resurrect him}
Maybe it was \Sethicus himself who made the first move. 

\Sethicus lay entombed, but not unconscious.
He realized the \banes were invading.
So he reached out telepathically and touched the minds of \ophidians.
He was deeply buried and bound with fearsome spells, so it was not easy for him.
He could only send unclear visions and messages.
But his mental power was formidable, and he was able to compel the \ophidians to release him.
This would have been impossible at any other time, but now they knew they needed him and his \dragons, so it was easy to convince many powerful \ophidians to come and release his seals.





\subsubsection{Cultists want to free \Sethicus}
\target{Cultists want to free Sethicus}
There were some \hr{Ophidians follow Sethicus under Durance}{\ophidian cultists who had carried on \Sethicus's religion}. 
It was they who argued that \Sethicus should be freed. 





\subsubsection{Resurrection caused problems}
\Sethicus then went to work releasing his fellow \dragons.
It took a lot of magic to resurrect them, for their souls had been away for a million years and were no longer accustomed to living in a physical body.

They awakened many, but not all.
Some slumbered too deeply and could not be reached.
Others refused the call.

Some of the \dragons had wandered the Realms of the \xss. 
Others had simply lain there thinking, developing new philosophy and science and magic.
Some of the resurrected \dragons did not want to be resurrected and went mad.
Their minds had become twisted into inhuman, \xs-like monsters.

\citebandsong{Nile:Ithyphallic}{Nile}{
  The Essential Salts
}{
  It is a great shock to the soul
  To tear it back from its resting place and reanimate it
  The resurrected are often insane and scream ceaselessly 
  or dash themselves into walls
}

When \Sethicus came to awaken the \dragons, he also found that many had chosen to leave their bodies behind permanently and could not be resurrected.
Others had perished for various reasons.
Some refused \Sethicus's call and remained asleep. 
These would remain \hr{Aloof Dragons}{aloof} for a long time. 





\subsubsection{\Sethicus lets \Nexagglachel sleep}
\target{Sethicus lets Nexagglachel sleep}
There were yet other \dragons whom \Sethicus deliberately let sleep.
This included his three sons.
It is possible that \Sethicus knew there was a great risk that the \dragons who fought in this war would be destroyed. 
He wanted some \dragons to live on so they could awaken at a later date and reclaim \Miith, thus carrying on his legacy.
\Sethicus was wise and saw far.

It is known that he did some work to weaken the seals on their tombs so that the brothers would later awaken on their own.
He rigged some spells that would awaken \Nexagglachel some thousand years later.
Beside \Nexagglachel, \Sethicus also set up some other powerful \dragons (whom he sort-of trusted) to wake up. 
He wanted to be on the safe side and not rely on \Nexagglachel alone.
For all \Sethicus knew, something nasty might happen to \Nexagglachel in mean time, so he wanted a backup plan. 





\subsubsection{\Sethicus fights}
During the war, \Sethicus-tachi unleashed more \daemons{} and more \xzaishannic{} power than ever before. 
This nearly tore the planet apart, and might even have killed the Heart itself. 

Perhaps the \banes{} feared that. 
The \banes{} might be more keenly aware of the Heart of \Miith{}, since their entire quest revolves around it. 
The \ophidians, on the other hand, had dwelt on \Miith{} for millions of years, and the Heart has always been there, so they might not have paid much attention to the peril their magic posed. 

\lyricstitle{\SETolltheHounds{} p.107}{
  \ldots{} in the north sky something terrible was happening. 
  Lurid slashes like a rainbow gone mad, spreading in waves that devoured darkness. 
  Was it pain that strangled the very air? 
  Was it something else burgeoning to life, shattering the universe itself?
  
  \ldots{} he could see the city, the roofs like the gears of countless mechanisms, gears that could lock with the sky itself, with all creations. 
  Such was Kharkanas, First Born of all citites. 
  But the sky had cyhanged. 
  The perfect machine of existence was broken\dash\emph{see the sky!}
  
  The city trembles, the roofs now ragged-edged.
  A wind had begun to howl, the voice of the multihued light-storm as it lashed out, flared with thunderous fire. 
}

Maybe move some or all of \ps{\Kserasshana} \quo{awakening} to \Sethicus. 





\subsubsection{\Dragons fight}

The war song of the \dragons: 
They revelled in their power and fury, their ability to cause destruction and fear.

\citebandsong{Nile:RamsesBringerofWar}{Nile}{
  Ramses Bringer of War
}{
  Wretched Fallen one of Khatti\\
  Rise against the oppressing Sword\\
  Encircled Abandoned Alone\\
  I Smite the vile Hittite Foe

  My Father Amon what carest Thee\\
  For the Vile and Ignorant of God\\
  My Father Amon what carest Thee\\
  For these Effeminate ones\\
  At millions of whom I groweth not Pale

  Raging like Menthu like Baal in his Hour\\
  Lo the mighty Sekhmet is with Me\\
  I enter in among them even as a hawk striketh\\
  I slay I hew to pieces and cast to the ground\\
  The royal snake upon my brow\\
  Spits forth Fire in the face of mine enemies\\
  And Burneth their Limbs
}





\subsubsection{\Cregorrs{} are created}
\target{Origin of Cregorr}
The \dragons{} were full-fledged \ophidians, altered for war. 
But the \ophidians{} also wanted servitor warriors. 
So at approximately the same time they worked to create a race of warrior servants. 
This became the \cregorrs.  









\subsection{The \CrystalSphere}
\target{Crystal Sphere}
\index{\CrystalSphere}
The \ophidians{} received help and knowledge from the \xss{}. 
Using this magic they were able to forge a mystic seal between the worlds, severing the connection to \Erebos{} and preventing the \banes{} from drawing power from their homeworld and its \dweomer. 

\Sethicus-tachi built a vast \CrystalSphere, a cosmic shell of \quo{ice} encasing all of Mith and its Heart. 
Thus they captured the \banelords, who were caught and frozen in the ice. 

The \CrystalSphere{} was a whole mini-Realm of ice in its own right. 
The \banelords{} became trapped there. 

The \CrystalSphere was based on the \hr{Palisades}{\pps{\Voyagers} Palisades}. 
The \ophidians had some limited understanding of the \voyagers' work, and they drew on it.
They built the \CrystalSphere to patch up the holes in the Palisades that the \banes had made.

With the \pps{\banes}{} leaders and power source gone, they were weak, and the remaining legions of \bane{} warriors were easily slaughtered. 

Maybe this seal works as a huge-ass cosmic \hr{Storm beacon}{storm beacon}. 

The \xs{} \hr{Naath-Kur-Ramalech}{\NaathKurRamalech} was very important in building the \CrystalSphere. 

\Daggerrain{} would later draw on the \CrystalSphere{} to weave the \hr{Shroud of Girigor}{Shroud of \Numah}. 
So \hr{Shroud and Crystal Sphere}{the Shroud is tied to the ice}. 

Compare to the devils in the manga \cite{NagaiGo:Devilman}, who are also frozen in ice. 





\subsubsection{No spaceships}
\target{Crystal Sphere isolates Miith}
One might think that even though the \CrystalSphere{} prevented the \banelords{} from going to \Miith{} by dimensional means, they should be able to fly there in spaceships. 

But no. 
The \CrystalSphere{} also kept spaceships out. 
It acted like a huge-ass \hs{storm beacon}. 
In fact, the sorcery wrought through \NaathKurRamalech{} completely enclosed \Miith{} and made it inaccessible from the outside. 
It constricted and strangled \Miith{}. 
It was one of the causes of the \hr{Heart weakened}{weakening of the Heart}. 
The Shroud made it worse, of course. 

It would be possible to attack the Sphere from the outside with magical weapons. 
But that would be very risky. 
Such an attack might easily damage or even destroy the Heart of \Miith. 
No, the Sphere had to be unravelled from the inside. 









\subsection{\Sethicus-tachi die}
\target{Sethicus dies}
Eventually \Sethicus fell, but his corpse was preserved.

\Sethicus fell and was seemingly destroyed in the \firstbanewar.
He overloaded his body with power and could not resurrect.
He was believed lost by all his followers.
Out of respect for his heroism, they took his body and enshrined it in \Dathka, where it was \hr{Elder Dragons worshipped}{worshipped as a dead god}. 

But \hr{Sethicus became a god}{\Sethicus's soul lived on as a disembodied god}.

All \dragons that were awake at this time perished or went back to dormancy or \hr{Aloof Dragons}{aloofness}. 





\subsubsection{\Tiamat might have survived}
\Tiamat likewise died and became a disembodied god. 

Or\ldots{} perhaps \Tiamat did not die in the \firstbanewar.
She awoke with \Nexagglachel. 
She had been driven mad and evil by a million years of imprisonment.
She conquered the world and reigned as a cruel tyrant.

Eventually \Nexagglachel decided she was too evil and rose up against her.
He converted many \dragons to his side, including his two brothers. 
They slew her. 

















\section{The Fall of the \Ophidians (\yds{First Banewar ends})}
\target{Fall of the Ophidians}
\index{technology!\ophidian}
Even though the \ophidians{} were victorious in the \firstbanewar{}, it  heralded the downfall of their civilization. 









\subsection{\Miith was nuked}
The war and the destructive forces (magical and non-magical) unleashed by both sides caused not one but multiple ecological catastrophes. 
This cataclysm heralded a mass extinction wiping out a ton of species. 

The \firstbanewar nuked the planet to smithereens. 
After the \banes had been banished, \Miith was bathed in fallout, both natural and supernatural. 
And ravaged by summoned monsters (many of whom still dwelt in the dark corners of \Miith millennia later). 





\subsubsection{Rampaging monsters}
After the \firstbanewar, the \ophidians lost control of many of their monsters. 
They ran amok and caused much havoc and destruction.
This was one of the many reasons why the \ophidian civilization declined and would not rise again for tens of thousands of years. 






\subsection{\Ophidian civilization collapsed}
\target{Ophidians lose telepathy}
It struck the \ophidians{} themselves hard. 
A backlash by the \banelords{} bathed the planet in destructive radiation. 
This radiation was bad enough for regular animal and plant life, but it was worst for the \ophidians, who were highly telepathically sensitive. 
The radiation attacked their highly-developed minds and resulted in permanent and debilitating brain damage. 
They suffered from amnesia and insanity\dash apathy or irrational aggression. 
The brain damage also harmed their intelligence and burned out much of their telepathic and psionic abilities. 

Only a few survived. 
And with the loss of telepathy, their civilization quickly broke down, for all their technology was built to be operated telepathically. 
The vast majority of \ophidians{} died in the war and its long aftermath. 
With their newfound insanity they used what was left of their science and magic to wage war on each other, until their race was all but extinct. 

The \banes' radiation also destroyed most of the \ophidians' computers, leaving their robots as immobile and useless hulks of metal and plastic and whatever.
Their civilization was very dependent on computers and robots, so this was another catastrophe for them.

The surviving \ophidians were few. 
They tried to rebuild their civilization, but they failed. 
Their empire declined over the next several thousand years until there was nothing left. 
To make it worse, they waged wars against each other, too. 
The great war had made the survivors more violent and xenophobic. 





\subsection{\Noggyaleth strike back}
\target{Noggyaleth suppress Ophidians}
After \hr{Noggyaleth remain passive in the FBW}{having been neutral in the \firstbanewar}, the \noggyaleth finally became convinced that it was in their interest to work with the \banes. 
They now attacked the remaining \ophidians. 
This was another factor that destroyed the \ophidian civilization. 

Since then and up till the \thirdbanewar, the \noggyaleth would hunt \ophidians.
Whenever the \ophidians tried to build greater cities and make any effort towards rebuilding their civilization, the \noggyaleth would attack. 
The \noggyaleth were insidious and cunning.
No matter how much the \ophidians tried to keep them out, they would worm their way in and find some way to fuck the \ophidians up:
\begin{itemize}
  \item Dig underneath the city and make it collapse.
  \item Destroy roads and disrupt logistics. 
  \item Poison water or food supplies.
  \item Dig tunnels and allow vermin to enter. 
  \item Generally make life hell. 
\end{itemize}








\subsection{\Ophidians divided}
The \ophidians{} (not counting \dragons) became divided into two groups. 
One group developed hyper-aggression, the other group developed hyper-apathy. 
In time, all the hyper-aggressive ones killed each other and died out, leaving only the apathetic ones. 
The latter evolved into \quiljaaran. 
They had not the will nor energy to maintain or rebuild their civilization, so it continued to decline. 
The \ophidian{} culture fell into barbarism, a process that took over a thousand years. 

Many \ophidians began to worship brutal \xs godlings that cared nothing for technology nor progress. 
Under the rule of these harsh gods, the \ophidians descended into barbarism.
They waged wars against one another and destroyed what little remained of their civilization and the planet's natural resources.

Compare to the Serpent People from the Cthulhu Mythos, who turned to the worship of Tsathoggua and were punished by their ancestral patron god Yig, causing them to degenerate. 

\target{Technology low after FBW}
In the next millennia, \Miith was populated by a lot of different barbaric, \xs-worshipping peoples. 
They would wage war a lot and destroy each other.
Technology remained low.
Until \hr{Origin of Aryothim}{the \aryothim came}.
Then \hr{Technology rises with Aryothim}{technology began to rise}. 









\subsection{\Ophidians tried to rebuild}
Throughout the ages, the \ophidians \hr{Noggyaleth plague Ophidians}{tried to rebuild their civilization, but always the \noggyaleth would ruin it}.










\section{New World Order}
The survivors had forgotten much of their old culture.
They had no technology and barely any magic. 
They had only legends. 

The technology used to be very high, but after the war they forgot their civilization and science, and how to control their slave races and \daemons. 
Compare to the Azghouls from the RPG \emph{Kult}, who were once the slaves of \humans. 

Two branches of \ophidians{} survived: 

\begin{enumerate}
  \item 
    The \dragons.
    
    The \quiljaaran{} saw them as freaks and did not trust them. 
    They, in turn, saw the \quiljaaran{} as inferior weaklings and cowards. 
    So they fought rather than working together. 
    
    The \dragons{} were strong, but few in number. 
    So they did not rise to dominate the world\ldots{} yet. 
  \item 
    Some regular \ophidian{} civilians, who eventually became \quiljaaran. 
\end{enumerate}









\subsection{\QuilJaaran}
The \quiljaaran{} kept on dwelling in the desolate and crumbling \ophidian{} cities. 
Each \quiljaar{} was usually able to keep a few dozen servants or slaves (mostly \loculs, sometimes \cregorrs{} and \nephilim). 
But this still meant that they ended up with dozens to hundreds of people living in \hr{Ophidian architecture}{Cyclopean} ruined cities that were built to house tens of thousands if not millions. 

The \ophidians/\quiljaaran had lost most of their culture and technology and been set back tens of thousands of years.
So they were now less powerful than before. 

The \nephilim{} were less friendly towards their \quiljaaran{} masters than the reptilian races. 
They would often run away or commit mutiny. 
Few \nephilim{} wanted to live near a \quiljaar. 









\subsection{\Cregorr{} barbarians}
\target{Cregorr did not dominate}
The \cregorrs{} \hr{Origin of Cregorr}{had been created at this point}. 
After the \firstbanewar{} and the collapse of the \ophidian{} civilization, the \cregorrs{} escaped into the \wylde. 

But they did not become a dominant race. 
They were \emph{too} aggressive and disorganized. 
They failed to develop much civilization on their own. 
They remained barbarians. 

Some \cregorrs{} ended up serving the \quiljaaran. 
But not so many. 
The \quiljaaran{} did not like the warlike \cregorrs. 
They made them feel uncomfortable. 

Many \cregorrs{} \hr{Cregorr worship XS}{worshipped the \xss}.









\subsection{Millennia pass}
Many thousands of years passed from the \firstbanewar{} to the rise of the \aryothim. 
\Dragons and \quiljaaran{} were immortal, so \quo{many tens of thousands of years} was only a few generations for them. 
Many were alive whose grandparents or even parents had lived during the \banewar. 
Also, they had long memories, which was one reason why it took their civilization so long to decline. 

But decline it did.
The \quiljaaran were too apathetic to rebuild their empire. 
The \quiljaaran had a lust for knowledge and philosophy, but \hr{QJ not inventive}{they were not inventive}. 









\subsection{\Dragonkings}
The surviving \ophidians idolized the \dragons who had fought and sacrificed themselves for their sake. 
They worshipped the \dragons and patterned themselves after them. 
The true stories about \Sethicus-tachi were twisted through the many millennia. 

Eventually a new aristocracy arose. 
They claimed descent from \Sethicus (plausible since \Sethicus was an \ophidian, but difficult to prove) and called themselves \quo{\dragonkings}. 

Many wars were fought between these \dragonkings. 









\subsection{\Saphyrae (\yds{Saphyrae dominates})}
\target{Saphyrae}
\index{\Saphyrae}
\Saphyrae{} was the greatest and mightiest \quiljaaran{} empire ever. 
It rose after the \firstbanewar. 
The \Saphyraeans{} considered themselves the heirs of the \ophidian{} empire, which was \trope{ShroudedInMyth}{Shrouded in Myth} and legend already back then. 

\Saphyrae{} was the only \quiljaaran{} empire which the \aryothim{} could never really threaten. 
Although that did not stop them from trying. 
The \aryothim{} waged many wars against \Saphyrae, but they never achieved much. 

But though \Saphyrae{} held its ground, they did not expand. 
The \quiljaaran{} were already then a people in decline. 
One reason was that they were apathetic, \hr{QJ apathy}{as \quiljaaran{} were ever wont to be}. 

\Saphyrae was the closest the \ophidians came to a new empire. 
It was a grand city.
But it was never completely thriving. 
The \noggyaleth besieged it from the shadows. 
So the \ophidians had little surplus to rebuild or innovate. 
Just keeping the city up and running was hard enough. 

The time between the \firstbanewar{} and the \hs{Draconian Supremacy} is sometimes called the \Saphyraean{} Age. 

When the \dragons awoke, they took control of \Saphyrae. 
\Nexagglachel set about rebuilding the \ophidian empire, and he was doing well. 
For two thousand years or so. 

\Saphyrae was destroyed in the \secondbanewar. 















\section{The \Aryoth Invasion (\yds{Aryoth invasion})}
\target{Aryothim kill QJ}
The \aryothim{} showed up. 





\subsection{Origin}
\target{Origin of Aryothim}
\target{Aryothim enslaved by sorcery}
The \aryothim{} were originally \nephilim{} who transformed themselves into immortal supermen using sorcery and genetic technology which they had originally learned from the \ophidians{} (\hr{Nephilim worship Ophidians}{whom they had worshipped and served}). 
The transformation process was inspired by the way some \ophidians{} had made themselves into \dzraicchenosses.

The process had something to do with the moon \hs{Visha}. 
In a certain sense, the \aryothim{} are children of Visha, like the \vorcanths. 


The \aryothim{} might have been artifically created, possibly by \ophidians{} who wanted to transform those silly \nephilim{} into more useful servants, for use in their internal wars. 
Some \quiljaaran created the \aryothim: A race of super-powered \nephilim blessed with \quiljaar-level intelligence.

It backfired, and the \aryothim{} destroyed their masters.

In the process, \hr{Aryothim hate sorcery}{the \aryothim{} developed a hatred of sorcery}, which was what their makers had used to enslave them and mistreat so many of their people. 

It might also not have been \dragons. 
It might have been \hr{Voyager}{\voyagers}. 
After all, a few \voyagers survived on \Miith{}. 









\subsection{\Aryoth technology}
\target{Technology rises with Aryothim}
Technology on \Miith \hr{Technology low after FBW}{had been low ever since the \firstbanewar}. 
Now, with the coming of the \aryothim, technology began to rise again. 

\target{Aryoth technology}
The \aryothim developed technology that, in some areas, was superior to that of the \quiljaaran. 
The \aryothim did not have nearly as powerful magic, but they had high-quality guns and stuff.
Perhaps they even had 20th century technology. 

See the section on \hr{Aryoth}{\aryothim} for more about their technology.





\subsubsection{\Aryoth seamanship}
\target{Aryoth seamanship}
\target{QJ seamanship}
One advantage the \aryothim{} had over the \quiljaaran{} was that they were great sailors. 

The \quiljaaran{} had a taboo against challenging their long-lost kin the \nagae{}, who had long held dominion over the seas by default. 
So the \quiljaaran{} kept to the land, even though with their technology they could have made themselves a sea power had they tried. 
\hr{QJ apathy}{\QuilJaaran{} were ever apathetic}. 

The \aryothim{} had no such scruples, so they sailed out and explored. 
They quickly gained built great sea-spanning empires. 
The \nagae{} resented this and opposed the \aryothim. 
\Naga-\aryoth{} wars were fought. 
The \aryothim{} suffered losses in these wars, but these losses were outweighed by the gains of seafaring. 

The \aryothim{} gained naval superiority, which remained unbroken until the \dragons came and kicked their asses. 





\subsubsection{Fuels}
\target{Aryothim used up fossil fuels}
The \aryothim developed technology that ran on fossil fuels. 

After they depleted all fossil fuels on the planet, they \hr{Aryothim used dark magic}{began relying on dark magic for their energy needs}. 
They broke \hr{Aryothim hate sorcery}{their old taboo against alienist sorcery}, which had lasted for many hundreds if not thousands of years and formed the core of all \hr{Aryoth religion}{their major religions}. 









\subsection{Rampage}
They hated the \quo{loathsome serpent men}. 
So they waged war against the \quiljaaran{} and their servitors and slaughtered many. 
They invaded the \quiljaaran{} cities, killed the \quiljaaran{} and their servitors and laid waste to the cities. 

Later the \aryothim{} would invent legends of how they had fought a valiant crusade to rid the world of the wicked reptilian menace. 
The \quiljaaran, on the other hand, considered themselves the victims of murder and vandalism at the hands of bloodthirsty barbarians. 

\target{Nephilim kill Locul}
The \loculs{} were especially hard hit. 
They were \hr{Locul weak}{weak and fearful fighters}, so they died in the droves at the hands of the rampaging racist \nephilim. 
Moreover, they were \hr{Locul friendly}{friendly and trusting}, which made it even easier for the ungrateful \nephilim{} to betray, enslave and kill them. 

To the \nephilim, the \loculs{} were loathsome reptilian creeps, but \hr{QJ miss Locul}{the \quiljaaran{} missed them when they were gone}. 

Compare to the way the Mabden kill off the Vadhagh and Nhadragh in \cite{MichaelMoorcock:Corum}. 
And the way barbarians slaughter the \quo{Peaceful Ones} in \cite{TadWilliams:MemorySorrowandThorn}. 





\subsubsection{Dark magic}
\target{Aryothim used dark magic}
The \aryothim used dark magic in their initial campaigns of genocide against the reptilian races.
They had to, since \hr{Aryothim used up fossil fuels}{they had no fossil fuels left}. 
They broke \hr{Aryothim hate sorcery}{their old taboo against alienist sorcery}, which had lasted for many hundreds if not thousands of years and formed the core of all \hr{Aryoth religion}{their major religions}. 

In fact, it is an ongoing theme on \Miith that in a war, \hr{Darkest magic wins}{the side that is willing to employ the darkest sorcery is usually the side that wins}. 

(The Vaimons' magic was disguised as something nice and good, but it was really even more insidious than \xs magic\dash{}more insidious than anyone had imagined, as it turns out in the end, with Lithrim.)

\Aryoth battle song:

\citebandsong{Nile:RamsesBringerofWar}{Nile}{
  Der Rache Krieg Lied Der Assyrische
}{
  Nergal, dread God of War and Plague\\
  Avenge the shades of our Fallen ones\\
  Blacken the sun with Fierce Winds\\
  Bring forth your Terrible Storms!\\
  Yea! Burn the flesh of our Enemies\\
  Gash their throats with Weapons of Iron\\
  Destroy Them utterly\\
  With Locusts and Disease
}




\subsubsection{Racism and Nazism}
Have plenty of Nazi-evoking race theory and racism surrounding the \aryothim. 
The similarity of \quo{\aryoth} and \quo{Aryan} is not coincidental. 

And consider the \hr{Resphan-Aryoth relationship}{relationship between \aryothim and \resphain}. 










\subsection{Conquest}
The \aryothim conquered the world and dominated much of it for thousands of years.
At first they were stone-age barbarians.
Over the millennia they developed a high-tech civilization.

The \aryoth civilization ended up \hr{Aryothim hate sorcery}{steering clear of alienist sorcery} and focusing on \hr{Aryoth magic}{psionics/animism} and \hr{Aryoth inventors}{natural science}. 

They reached a 20th century level of technology.





\subsubsection{Nuclear war}
The \aryothim and their \quiljaaran enemies developed nuclear weapons. 
They waged war. 
There was at least one nuclear holocaust in those days. 
After each major war, the \aryothim were quicker to get back on their feet than the slow-living \quiljaaran were, so they slowly gained the upper hand. 

Perhaps it was one such war of mass destruction that roused \Nexagglachel-tachi from their sleep. 
\Nexagglachel felt the catastrophic loss of life and decided he had to do something to fix it. 
So he spent the next century or more slowly picking the locks of his tomb, until finally he was able to rise from the dead and wake his brothers. 












\section{Draconian Ascendancy (\yds{Draconian Ascendancy})}
\target{Draconian Ascendancy}
\target{Draconian Supremacy}
The \quo{Draconian Ascendancy} was the event when the \dragons conquered \Miith. 
It heralded the beginning of the Age of Draconian Supremacy. 









\subsection{\Nexagglachel awakens}
\Nexagglachel still slept in durance, dead but dreaming.
\Sethicus \hr{Sethicus lets Nexagglachel sleep}{had let him sleep} but rigged him with spells so he would awaken millenia later. 
Finally \Nexagglachel awakened. 

When \Nexagglachel awoke, he immediately went out to awaken his two brothers.

When \Ishnaruchaefir was awakened by \Nexagglachel, he immediately went out to awaken \Rystessakhin. 





\subsubsection{The \dragons and their knowledge}
When the \dragons awoke, they had spent millennia pondering mysteries of science and magic. 
They had gained much insight into the occult, so their magic and mystic skills were immense. 
But they knew little of physical technology, because they had had no opportunity to experiment with building physical tools. 
So when they awoke, they could not just establish a new technological civilization. 
Furthermore, their skill was based on occult revelations and deep Gnosis which they could not easily teach to anyone else. 
So they remained monoliths of arcane power instead of building a new civilization. 

\Nexagglachel-tachi \hr{Nexagglachel could not rebuild Ophidian civilization}{tried to rebuild the \ophidian civilization but failed}. 





\subsubsection{The \ophidians were pressed}
\Nexagglachel saw that the \quiljaaran, the descendants of the \ophidians, were pressed. 
They were a \quo{fallen} people, after millions of decline from the golden age of the \hr{Ophidian civilization}{\ophidian{} civilization}. 

\target{The struggle for Dominion over Miith}
The \ophidians had been displaced as the Dominators of \Miith{}.%
\footnote{%
  Perhaps this is what the title of the series should refer to: 
  The struggle for Dominion over \Miith{}.%
} 
The \quiljaaran were retreating before the advance of the \aryothim.
They lived in half-empty ruined cities\dash a painful testament to the heights from which they had fallen, the greatness which they had lost. 
They were being pushed back hard. 
Some even feared their races would become extinct. 

Compare to \bandsong{Demilich}{The Planet that once used to Absorb Flesh in order to Achieve Divinity and Immortality (Suffocated to the Flesh that it Desired)}. 

\Nexagglachel decided that if the \ophidian golden age was to be restored, the task must fall to him and his \dragons. 

The \dragons thus set out to restore the world. 









\subsection{\Draconian Supremacy}
The \dragons were psycho-badass. 
They swept aside any \quiljaaran, \aryothim and \vorcanths that opposed them. 
They conquered \Miith and continued to dominate it for thousands of years. 
All the way up till the \secondbanewar. 





\subsubsection{\Aryothim conquered}
\target{Dragons destroy Aryothim}
The \dragons waged brutal war on the \aryothim, almost eradicating them. 
In their hatred, the \dragons destroyed much of the \aryoth civilization, including much of their hated \hr{Aryoth inventors}{technology} that had so long been a threat to the Serpentine peoples.
They destroyed universities, libraries and all sorts of containers of this hateful \aryoth knowledge, to ensure that \dragons would once again reign supreme. 

In the coming millennia, \hr{Aryothim as aloof gods}{\aryothim would be rare and keep a low profile}. 
So \hr{Aryoth-blooded rulers}{\aryoth-blooded \nephilim would rule in their stead}. 





\subsubsection{Golden age did not return}
\target{Nexagglachel could not rebuild Ophidian civilization}
The awakened \dragons could not rebuild the \ophidian civilization. 
\Nexagglachel tried his best, but it was hard. 
They were only a few individuals.
They had much scientific knowledge, but it was incomplete.
They remembered much of their science, but there was much technology that they could not replicate because they lacked the infrastructure necessary to produce it in any remotely efficient manner. 
Besides, they lacked the \hr{Draconian energy sources}{occult energy sources} which the \ophidian/\draconian civilization had used. 

The \ophidians would like to rebuild, too, but they had lost much knowledge over the many millennia, and besides, \hr{Noggyaleth suppress Ophidians}{they were being hounded by the \noggyaleth} whenever they tried to rebuild.

After \Nexagglachel died, only \Secherdamon retained the ambition to rebuild the \ophidian empire any time soon. 

The \dragons did make some progress, though. 
They introduced a lot of technology among their followers.





\subsubsection{Technology}
\target{Dragons repress technology}
\index{repression of technology!\dragons}
The \dragons repressed technology. 
For more than one reason:

\begin{enumerate}
  \item 
    \Nexagglachel saw the horrible destruction that high-tech weapons had caused.
    He decided that \humanoids were not intelligent enough to handle technology or powerful magic responsibly, so he repressed technology and kept it in the hands of the wise elite. 
    After his death, the remaining \dragons respected this aspect of his philosophy.
    It was part of the inspiration for the Unspoken Covenant. 

  \item 
    The \dragons cared primarily about sorcery, since this was what had saved their people and returned them to the throne of \Miith. 
    So that was what they researched and developed. 
    They disdained natural science as a poor man's substitute for true power, so they discouraged research into that area. 

  \item 
    The \dragons did not want lesser races to be able to gain control and dominate their betters. 
    \Dragons had a great natural talent for sorcery. 
    They had no such advantage in the area of natural science. 
\end{enumerate}

So they suppressed many sciences, and the overall technology dropped in a lot of areas. 









\subsection[Scathae are created (\yds{Scathae created})]{\Scathae are created (\yds{Scathae created})}
\target{Origin of Scathae}
It is at this point that the \scathae were created. 
The \dragons{} wanted a servitor race to serve them. 
So they took some of their own \ophidian genes and mixed them with the genes of various \saurians, including \hr{Nycan}{\nycans}. 

The \scathae were bred from \hr{Locul}{\locul} stock. 
They were created with bits of the original \ophidian people, salvaged from mummies. 
And also with \cregorr genes. 

They performed many experiments. 
Most failed. 
But a few succeeded. 
These became the \scathae{}. 

\target{Cregorr came to serve Dragons}
The \dragons{} also tamed many of the \cregorrs{} and made them serve them. 

Both \scathae{} and \cregorrs{} had \xsic{} genes, which gave rise to the \hr{Scatha fury}{primal fury that lurked even in the peaceful \scathae}. 

Different aspects of the \scathaese mind \hr{Primordials and the Scathaese mind}{were associated with different \xss}.














\section{Draconian Supremacy waning}
\subsection{\Firstgendragons{} died}





\subsubsection{\Kserasshana{} and \Nexagglachel}
\target{Nexagglachel gets stewardship}
\index{stewardship}
Before her death, \Kserasshana{} talked to \Nexagglachel. 
He was her eldest and most skilled son. 

\begin{prose}
  \Kserasshana: 
  \ta{%
    After I and the other elders are gone, thou wilt be the greatest and best \dragon{} on \Miith.
    I charge thee with the stewardship of \Miith.
    Carry on our legacy.
    Lead our race, rule our world and keep it safe for our people.
    Your two brothers are also strong and have much potential.
    But you must lead them.}
\end{prose}






\subsubsection{The \firstgendragons{} died}
\target{Elder Dragons die}
\Tiamat{} eventually died in some war. 

But the heroic role they played in the war overshadowed their cruel tyranny. 
After the war their corpses came to be \hr{Elder Dragons worshipped}{worshipped as dead gods}, close to the \xss{} in status. 










\subsection{\Nexagglachel-tachi rise}
After the elder \dragons{} had all perished, it now fell to younger \dragons{} to lead their people (to the extent that the \draconic{} people is willing to be led). 
\Nexagglachel{} and his brothers were now the de facto top-of-the-pop. 

Without the \firstgendragons, the \dragons{} were weakened, but they still pulled through, under the capable leadership of \Nexagglachel{} and other great \dragonlords, and were able to strike back and exterminate the \banes{} that remained on \Miith. 









\subsection{\QuilJaaran{} supremacy}
\target{QJ supremacy}
The \quiljaaran{} were always rivals of the \dragons{} and \ophidians, but the sometimes allied. 

The \quiljaaran{} fought alongside the \dragons{} in the \firstbanewar. 
They suffered great losses in that war, but not quite as devastating losses as the \dragons{} (who lost almost all their elder leaders). 

So for a couple of thousand years after the \firstbanewar, the \quiljaaran{} were pretty dominant on the face of \Miith{}. 
They ruled several Realms. 

There were conflicts between \quiljaaran{} and \dragons{} in this time, but the \dragons{} were too few, too scattered to wage full-scale war, so they were most often forced to retreat before the expanding \quiljaaran. 

The \vorcanths{} and \nagae{} were also involved in these wars. 

Their domination lasted until \Nexagglachel{} was able to unite sufficiently many \dragons{} to challenge the \quiljaaran. 
\Nexagglachel{} intended to rebuild \ps{\TyarithXserasshana} empire. 

Maybe this \quo{\draconian{} revenge} \hr{Nexagglachel and Thanatzil}{coincided with \ps{\Thanatzil} time}.









\subsection{\Dragons{} disorganized}
\target{Dragons disorganized}
The \dragons{} were terribly disorganized after the \firstbanewar. 
\Nexagglachel{} made a heroic effort to unite them, and he achieved some success, but not as much as he had hoped for. 
The \dragons{} would continue that way all the way \hr{Second Banewar unites Dragons}{up till the \secondbanewar}. 

The \dragons{} were aloof and operated behind the scenes, letting the \quiljaaran{} and others dominate the picture. 









\subsection{Golden age of technology}
\target{Golden age of technology}
\index{technology}
The time between the \firstbanewar{} and the \secondbanewar{} was something of a golden age of technology. 
Many new things were invented in this period. 























\chapter{\AvatarofEntropy}
Tells the story of \Semiza, the origin of the \resphain, \Merkyrah, the \resphan{} rebellion, the creation of the \satharioth{} and the \secondbanewar. 





\begin{blurb}
  \Miith{} is a cruel world. 
  
  \Dragons{} rule the skies, and their legions of reptilian \cregorrs{} and \scathae{} sweep across the land. 
  The \nephilim{} have been banished from the fertile grasslands and forced to live in deserts, in caves and under the earth. 
  
  \Semiza, \nephilic{} king of \Numah, desperate to find a way to save his people from the \psp{\dragons}{} depredations, turns to black magic. 
  An alien god appears in \ps{\Semiza}{} visions and offers him a chance to vindicate the \nephilim. 
  
  But the price will be a gruesome sacrifice\ldots{}
\end{blurb}
















\section{The Big Picture}
\subsection{The \Bane{} Master Plan}
\subsubsection{The \banes{} in exile}
\target{Origin of Nyx}
The \banelords{} were not all destroyed. At the last moment, \Daggerrain-tachi seized hold of a corner of the Shroud of Realms that the \ophidians{} were weaving, twisting it into a pocket Realm, into which they fled. This Realm was a vestibule, a thin, almost unnoticeable corridor to \Erebos. They remained in this Realm for thousands and thousands of years, reshaping and expanding it into a shadow of \Erebos. It became \Nyx, the Twilight Realm. 





\subsubsection{\Daggerrain{} is the gate}
\target{Daggerrain is the gate}
\Daggerrain{} embodies the cosmic conduit between \Erebos{} and \Nyx. See, \Erebos{} is tens of thousands of light years from \Miith{}. The \banes{} \hr{Banes come to Miith in spaceships}{came to \Miith{} in spaceships}, but this took thousands of years. 

But \Daggerrain{} has solved the cosmic equations and cast the Realm-weaving spells that create a short-cut through the Realms directly to \Erebos, and as long as he is present in \Nyx, the connection persists.
Granted, the conduit is narrow after the formation of the \hr{Crystal Sphere}{\CrystalSphere}, but it's better than nothing. 

Were \Daggerrain{} to fall, the link would be broken, and \Nyx{} would be permanently severed from \Erebos. At the end of \SentinelsFinalBook, \hr{Daggerrain falls}{this is exactly what happens}. 





\subsubsection{\Bane{} magic on \Miith}
After the \firstbanewar, the \CrystalSphere{} was not entirely tight, so \Erebean{} energy could seep through in small amounts. Some mages discover that they can channel \bane{} power and use it to cast a kind of primitive \nieur{} magic. 

At first, the \dragons{} and others are terrified at the thought of the \banes{} returning, so they persecute and wipe out these mages. But nothing seems to come of it, so gradually, as the centuries pass, the \dragons{} glow lax and stop caring. 





\subsubsection{The \pps{\banes}{} plan}
We are now several thousand years after the \firstbanewar: The \banes{} are forgotten and no one fears their return any more, barely even the \dragons{} who actually fought them last time. 

\index{technology}
Note that \hr{Technology}{the technology is still low}, for a number of reasons. 

But this is all part of \ps{\Daggerrain}{} plan. See, \Daggerrain-tachi could not travel back into \Miith{}, but the Shroud was thin enough for them to gaze into \Miith{} and observe, so they had a reasonably good idea of what was going on there, and they could plan their return. He knows that he will have a hard time reconquering \Miith{} with the \dragons{} opposing him, but he has immortality and patience, so he waits some millennia, planning his return while lulling the \dragons{} into a false sense of security. 

When the time is right and the opportunity presents itself, \Daggerrain{} plans to contact some \Miithian{} mortals, bargain with them and convince them to help the \banelord{} bring his people to \Miith{}. 

\Daggerrain{} will not bring the \banes{} to \Miith{} immediately. Rather, he intends to \quo{crossbreed} his people with some native \Miithians\dash possibly the \nephilim\dash to create a new super-race. This race will eventually become the \hr{Resphan}{\resphain}. 





\subsubsection{The Vortex}
The \banes{} try to open a dimensional gate called the \quo{Vortex}. 

The Vortex is actually not a mere portal but a deeper merging of the planes, a connection allowing a high degree of free movement from \Erebos{} to \Nyx{} and on to \Miith{}. 









\subsection{\Draconian{} Aspect}
\target{Nexagglachel and Thanatzil}
This book also has a \draconian{} aspect: 
While \Semiza-tachi are trying to bring \banes{} to \Miith{}, \Nexagglachel{} is fighting to unite the \dragons{} and reclaim \Miith{} for their race. 
The \dragons{} are \hr{Dragons disorganized}{terribly disorganized}, and \Nexagglachel{} hopes to change that. 
They are waging wars against one another and against their rival races, the \quiljaaran, \vorcanths{} and \nagae. 





\subsubsection{\Draconic names for \banes}
\target{Draconic names for Banes}
The \dragons{} had their own names for the \banes: 
The Alien Ones, the Sinister Ones, the Spawn of Darkness. 









\subsection{The other races}
Have plenty of \aryothim, \vorcanths{} and \quiljaaran{} in major roles in this book. 

Maybe even turn \Vexstrasshin{} from a \dragon{} into a \quiljaar. 









\subsection{When is it?}
When did this story take place? 
When did \Thanatzil{} live? 

It could be just few years after the \hs{Draconian Ascendancy}.
Or it could be thousands of years later. 















\section{\Numah}
\target{Girigor}
\target{Numah}
\index{\Numah}
Over thousands of years, various groups, independent of each other, discover this energy source. \Numah, the \nephilic{} kingdom ruled by \hr{Semiza}{\Semiza} is one of them. 

In \Numah\dash and among many other \nephilic{} peoples of that time\dash the written tongue was sacred and secret, known only to the priest-mage class and surrounded in much mysticism and ritual. It was closely tied to their magic. 

Back then, sorcerer-kings ruled. 
It was before the \feud{} came to dominate and manipulate everything, remember. 
(In the days of the \charade, \hr{Sorcerer-kings}{sorcerer-kings} are usually dethroned by the master races, who \hr{Master races seek to control magic}{try to control magic} and fear the threat that such a ruler might potentially pose.)

\Numah{} is very misogynistic, \hr{Nephil misogyny}{as the \nephilim{} are wont}. 





\subsubsection{Language}
The language of \Numah{} should resemble ancient Sumerian or Babylonian. 





\subsubsection{Magic}
\target{Numah bones}
\Semiza{} and the other mages had some magic skulls and bones that originally belonged to their sorcerous ancestors, or even dead gods. 
Even in death, these bones retained some magical power. 
They had been handed down for centuries. 
Some of the oldest and most powerful sorcerers' bones were still preserved. 

\ps{\Semiza} people created a \matrix{} from the souls of their great dead mages. 
But they had to deal with forbidden powers, including the \xss{} that dwelt beneath the earth. 

\citeauthorbook{RobertEHoward:RedNails}{Robert E. Howard}{Red Nails}{
  \quo{Madness and death lurk in it. 
    The wizard of Xotalanc understand its secret\dash they found it in the catacombs, where lie the bones of terrible kings who ruled in Xuchotl in the black centuries of the past. 
    To gaze upon its freezes the blood and withers the brain of a man who understands not its mystery.}
  
  \quo{In life it housed the awful brain of a king of magicians! 
    It holds still the life and fire of magic drawn from outer spaces!}
}

The \nephil necromancer-kings at this time derived much knowledge and power from the dead.

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  I Whisper in the Ear of the Dead
}{
  I Dream of the Dead\\
  And Their Shades Showeth Me \\
  Visions Which No Living Man Can Know\\
  I Whisper in the Ear of the Dead\\
  And Mine is the UnWritten Knowledge\\
  That Lieth Under The Black Earth
}





\subsubsection{Mound of Hernon}
\Semiza's palace-temple lay on the top of the Mound of Hernon.

This is a reference to \cite{RHCharles:BookofEnoch}.

\citetitle[p.35]{RHCharles:BookofEnoch}{The Book of Enoch VI.6}{
  And they [the Grigori] were in all two hundred; who descended in the days of Jared on the summit of Mount Hernon, and they called it Mount Hernon, because they had sworn and bound themselves by mutual imprecations upon it.
}





\subsubsection{Politics and rulers}
\target{Aryoth-blooded rulers}
The rulers of \Numah, as well as many other \nephil kingdoms, were \nephilim with \aryoth blood. 

In this age, \hr{Aryothim as aloof gods}{the \aryothim would be rare and keep a low profile}. 
But the \dragons did not bother exterminating mortal \nephilim. 
So mortal \nephilim with strong \aryoth blood in their veins would take up the role as priest-kings and rule over their brethren, with only \hr{Aryothim as aloof gods}{limited support from their aloof \aryoth gods}. 





\subsubsection{Religion}
\target{Aryothim as aloof gods}
The gods of \Numah{} were \hr{Aryoth}{\aryothim}. 
The true \aryothim were few in number after having been \hr{Dragons destroy Aryothim}{hunted and decimated by the \dragons}.
So they hid and kept a low profile. 
They would support their mortal brethren to some limited extent, acting like aloof gods. 

But these gods were slain by \dragons{} (or maybe \quiljaaran) in some great battle that destroyed \ps{\Numah} civilization. 
After this great defeat, \ps{\Semiza} people were hunted down and killed by the legions of \cregorrs{} and \scathae. 

Remember to have flashbacks of this terrible battle.
\Semiza{} and others have nightmares about the evil day when their world was destroyed and all they loved was torn from them. 
They even had to watch their gods die. 

\lyricsbs{Iced Earth}{Setian Massacre}{{\obeylines
  Screaming in agony, cries fill the air \\
  Eyes once full of hope shedding tears of despair \\
  All that they've ever known is dead 
  
  Fire reigns from above, iron birds of dread \\
  All that they ever loved is dead \\
  All that they ever dreamt is dead 
  
  Temples are burning, streets soaked with blood \\
  Heed the prophecy, destiny is done \\
  All that they ever loved is dead \\
  All that they ever dreamt is dead 
  
  Yet there's a glint of hope \\
  If the chosen can survive \\
  In secret the ten thousand hide \\
  East in the mountains \\
  The chosen bide their time \\
  The Clouding, our strike on mankind 
}}

They are now a people forsaken, alone and unprotected, with no gods watching over them. 
Therefore many are prepared to embrace the \banes. 
But many subjects refuse to accept the fact that the gods are dead. 
They insist that \trope{HesJustHiding}{They Are Just Hiding} and keep praying to them. 
\Semiza{} and \Eshayzal{} despair over this display of stupidity and stubbornness. 
Meanwhile, some among the people resent their king for so readily abandoning the gods they have served for a thousand years (or whatever) and take up the first new religion that walks by. 





\subsubsection{Technology}
\index{technology!\Numah}
The technology is low. 
Late Stone Age or early Bronze Age. 
They have mostly stone and bone tools. 

Comparable to early Egypt. 

The only metal weapons they have are those few they can buy or steal from the \scathae{} and \cregorrs. 

Also, they do not have the skills to tame \saurians{}, so they only have mammals domesticated. 
Including some hyaena- or \latinname{Hyaenodon}-like dogs they use in war. 





\subsubsection{Other \nephilic{} societies}
There had been many other \nephilic{} societies before \Numah. 
Many of them were considerably greater, more powerful and more advanced than \Numah. 
But whenever one would rise too high, the \scathae{} would come to wipe them out. 

\index{Zibrid}
Other kingdoms that lay near \Numah in the same time period were Zibrid and Crimur. 















\section[Semiza and Ilu (\yds{Semiza birth})]{\Semiza{} and \Ilu (\yds{Semiza birth})}










\subsection[Semiza (\yds{Semiza birth})]{\Semiza (\yds{Semiza birth})}
\Semiza{} was the eldest son of the \nephil{} sorcerer-king of \Numah. 
Later he would take the throne and become sorcerer-king himself. 





\subsubsection{Young \Semiza}
Early on we see him passing some kind of \quo{manhood test}, marking him as a full-fledged sorcerer and a worthy heir to the throne. 

At an early point, \Semiza{} meets some girl that he likes. 
Either right after his rite of manhood or some time after, he is betrothed to her. 

Some years pass. 
The Jocainites hear the tales of war, of some terrible invaders from the sea devouring entire kingdoms. 
The king and mages are concerned, but \Semiza{} is still young and untroubled. 

Then comes the day of \Semiza{}'s wedding. 
On this, supposedly the greatest day of the young prince's life, the \dragons{} invade Jocain. 
It becomes massacre and young \Semiza{} sees his bride and his entire family slaughtered before his eyes. 

\Semiza{} and a few survivors flee to a system of underground caverns. 
Somehow they manage to survive the \draconic{} army's onslaught. 
\Semiza{} assumes the mantle of king and leads his people in exile. 





\subsubsection{\Eshayzal}
\Eshayzal{} is \ps{\Semiza}{} trusted friend and advisor. 

\index{technology!\bane}
The two are great geniuses and will later be able to perform miraculous feats of science using the \hr{Bane technology}{knowledge supplied to them by the \banes}\dash knowledge which is in turn \hr{Voyager technology}{stolen from the \voyagers}.





\subsubsection{Adult \Semiza}
Now \Semiza{} was sorcerer-king.
He had many wives and concubines. 

He hates the \dragons{}. 
Now, the \dragons{} were tyrants and had always been preying on his people, but I think there should be something more personal in it. 
Perhaps \ps{\Semiza}{} most dearly beloved wife or concubine or son\dash or more than one\dash was/were killed by \dragons{} or their minions in one of their raids. 

Anyway, this makes him bitter.









\subsection[{\Daggerrain contacts Semiza}]{\Daggerrain contacts \Semiza}
Throughout the millennia, there had been many people\dash thousands, perhaps millions\dash whom \Daggerrain{} might contact and who might stand a chance of succeeding in bringing \banes{} to \Miith. 
But \Daggerrain{} was patient, so he waited until he found the perfect situtation. 

\Semiza{} was a scientific genius, as was his partner, \Eshayzal. 
And \Semiza{} was bitter at the \dragons{} and longing for revenge and a \quo{return to glory} for his people. 
And his rule coincided with some nasty wars among the \dragons. 

\Daggerrain{} chose him. 

The \dragons{} had forgotten the \nephil{} survivors and thought nothing of them. 
Hiding in his underground lair, Semiza nurtured his hatred and dreams of revenge against the \dragons{}. 

Somehow Semiza reached out into the Cosmos with his mind. 
Perhaps he was deliberately searching for allies; perhaps he was taking mind-expanding drugs. 
By whatever means, he contacted \Daggerrain. 
Or \Daggerrain{} contacted him. 

Daggerrain penetrated the \ps{\nephil} vulnerable mind and probed around in it. 
He took from the sorcerer-king's mind his language and his entire memory. 
Then he introduced himself to the \nephil{} king, offering him the power to take his revenge, destroy the \dragons{} and restore his kingdom, that he might rule forever as an immortal king. 
In return, \Semiza{} had to help \Daggerrain{} bring his people to \Miith{}. 

At this point, Semiza asked: 
\ta{Who are you?}

In response \Daggerrain{} sent a vision where Semiza found himself alone and naked amid an endless, featureless plain, with a cruel and unrelenting hail beating down upon him with its sharp shards of ice, like a rain of a million daggers. 
Semiza interpreted the \banelord{}'s name as \quo{Daggerrain}. 

If he was to help Semiza and his people, Daggerrain needed the \nephil{} sorcerer to bring him to \Miith{}. 
He instructed the \nephil{} in the spells to use, and \Semiza{} went to work procuring occult ingredients and sacrifices (mostly \scathae) and recruiting and training mages to assist in the spellwork. 
The preparations took perhaps several years, but at last they are ready to perform their summoning ritual. 







\subsubsection{\Semiza{} turns from his gods}
\Semiza{} feels that his people's gods have betrayed him, so he searches for new ones. 

He feels like a pawn, adrift in sea governed by vast powers beyond his ken. 
He feels impotent, and he rages. 
He wants to regain control of his own fate and that of his people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Let me embrace my fate which was adrift and hung. \\
  I will be again the apple of his eye. \\
  Take me from among the doomed Laodiceans \\
  whose defamation thrilled the seething skies.
}





\subsubsection{\Semiza{} feels the calling of dark powers}
At first, \Semiza{} vaguely feels the call of dark forces from the Beyond. 

\lyricslimbonicart{Moon in the Scorpio}{
  A mirror blank ocean above me decoy.\\
  Superior forces that heal or destroy.\\
  Take me astray into the moonlight above
  through twilight eyes as a spectre shadow.
  
  It is a time of great light\\
  and of great darkness.\\
  Can you feel the presence\\
  of its phenomenon?
  
  In an atmosphere supreme\\
  forces dwell in domancy.\\
  The essence of its spirit is evil,\\
  as a curse upon thy name.
  
  Midnight is the shepherd of mysterious powers\\
  and moving shadows in the corner of the eye.\\
  Moon's blazing intuition\\
  contains what death requires.
  
  Cleanse the doors of perception.\\
  See things appear in its true art.\\
  The cold hands of divinity\\
  will tear thy soul apart.
  
  Behold the sky above \\
  when the moon is in the Scorpio.\\
  A cold bleak light
}

\Daggerrain{} haunts him. 
He tells \Semiza{} that he is the only hope for \Semiza{} and his people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Night after night grim voices shriek \\
  in portentous horror dreams, \\
  even though his room was locked, \\
  but a Seraph comes unseen. 
  
  Night after night his skin was flogged. \\
  Damn those recurrent dreams. \\
  Desperately flogging for relief \\
  while murmuring blasphemies. 
  
  The bloodstained walls surround him, \\
  icons made of Calvary wounds. \\
  Dreams of riddance were shattered in sin, \\
  ill-fated to avert doom.
}

He learns more of these dark new powers. 

\lyricslimbonicart{The Supreme Sacrifice}{
  I stand within the flame,
  watch the wisdom be discovered.
  When life and death is the same,
  I am devoured.
  
  So many nights I have spent \\
  in thoughts not heaven sent.\\
  Blood of hatred poured down like rain \\
  for evil secretus insane.\\
  In silent gloom I kneeled obsessed,\\
  channeling the enigmatic darkness.\\
  My soul, the servant\\
  under the illusive wings of death.
  
  When I receive a black picture of the future,
  and schockwaves attack from a nihilistic universe.\\
  My body, the temple, a mausoleum in flesh\\
  under the illusive wings of death.
}

He is overwhelmed with awe. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  The man started to cry, hands held to the sky,\\ 
  and expected to be purified in flames. \\
  But the Angel smiled and took the Book \\
  and commanded his holy mandate.
}

He was looking for a way to seize control of his own destiny, and this is it. 
He jumps at the chance and devotes himself to serving the \banes.

\lyricslimbonicart{Behind the Darkened Walls of Sleep}{
  I open gates and close the others. 
  Behind me now there is no return. 
  I broke the sealed door to imagination. 
  The pulsating darkness now around me burn.
}

\Semiza{} has a terrifying enlightenment scene, where \Daggerrain{} shows him the mysteries and wonders of \hr{The dark universe}{the dark universe}. 

He shares it with a select few subjects.





\subsubsection{The name \quo\bane{} is born}
\target{Semiza names Banes}
\Semiza{} is overwhelmed by the power and glory of \Daggerrain{} and his people (and the \Voidbringer). 
He believes that these gods will be the salvation of his people and the bane of all their enemies, and so he names them the \quo{\banes}. 

It was \Semiza{} who named the \banelords, including \Daggerrain, and it was he who coined the term \quo{\bane} for their race, since he envisioned them as the bane of his hated enemies, the \dragons. 
Not until a late time does he realize that they are the same creatures that fought the \dragons{} thousands of years ago. 

The \dragons originally had \hr{Draconic names for Banes}{other names for the \banes}. 





\subsubsection{\Semiza{} introduces the \bane{} religion}
\target{Bane religion}
\Semiza{} preaches to his people of the new gods he has discovered. He promises that they will save his people. In exchange, they must worship and serve them. 

Perhaps at first \Semiza{} does not know that the \banes{} are an entire people. He might think it is just a single god (\Daggerrain), whom he names \quo{the \bane}. 





\subsubsection{\Daggerrain{} reveals his true nature}

At first, \Daggerrain{} comes in disguise. 
It is only later that he shows \Semiza{} his true face.

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  The Fallen Seraph lowered his radiant mask \\
  and showed the man the countenance of the fallen Morningstar.}

Semize is terrified. 
But there is no way back. 
\Semiza{} gives him the name \quo{\Daggerrain}. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  The man seemed stricken by a thousand bludgeons. \\
  Penetrating just-healed wounds as foreplay for the storm.
}









\subsection[{Semiza builds a stargate}]{\Semiza builds a stargate}
\target{Semiza's stargate}
\Semiza{}, working under the \psp{\banelords}{} guidance, builds a great temple that is to act as a stargate, a focus for the portal to \Erebos. 









\subsection{The \banemessiah}
\target{Bane Messiah}
%The plan is that the \nephilim{} must provide a 
The plan is to give birth to a \quo{\banemessiah}: A superbeing, born of a \nephilic{} mother but invested with the life force of the \banes{} and possessing the power to open a conduit to \Erebos{}. Through this conduit they will be able to draw more energy and spawn more people like the Messiah, thus founding a whole race of half-\bane{} demigods. 
When there are enough of them, they will be able to challenge the \dragons, overcome the \hr{Crystal Sphere}{\CrystalSphere} and grant \Daggerrain{} and his people unrestricted access to \Miith{}, whereupon they will march in like a conquering army, scouring the world of the \draconian{} tyrants. 

\target{Thanatzil is the gate}
So the Messiah \emph{is} the key and the gate, an incarnation of the \bane{} soul and legacy. If \hr{Thanatzil fails}{he dies, the portal collapses}.









\subsection{The Shroud of \Numah}
\target{Shroud of Girigor}
\Daggerrain{} took some threads, components, techniques and ideas from the \hr{Crystal Sphere}{\CrystalSphere} and used them to weave a small Shroud around \Numah, thus shielding \Semiza-tachi and the \resphan{} project from prying \draconian{} eyes. 

Later he went on to \hr{Shroud of Nyx}{weave a similar Shroud on \Nyx}, but that did not work out so swell.









\subsection{\Vexstrasshin{} suspects}
Most \dragons{} suspect nothing. 
When \ps{\Semiza}{} people start invoking \banes{}, no one believes it. so they are allowed to proceed. 

\target{Dragon war when Resphain appear}
Also, this coincides with a bloody war among the factions of \dragons{} (\Tiamat{} is dead, after all), so they are busy fighting each other and have little time left to investigate alleged \bane{} summoning. 
This war is, to some extent, masterminded by \Daggerrain, a part of his \trope{XanatosGambit}{Xanatos Gambit}. 

But at least one \dragon{} suspects that \ps{\Semiza} new religion and this whole \Thanatzil-business is \trope{SeriousBusiness}{Serious Business}, namely \hr{Vexstrasshin}{\Vexstrasshin}. 
Her fellow \dragons{} do not believe her (being caught up in their own wars), so she sneaks into \ps{\Semiza} city in disguise. 
Here she tries to discover what is up. 

When she discovers \Thanatzil, she tries to stop him. 
She fears him. 





\subsubsection{Cameos}
Have some cameos with the \dragons{}: 
\Nexagglachel, \Ishnaruchaefir, \Secherdamon, \Triestessakhin, perhaps \Nzessuacrith{} (she was very young). 
They were all very happy back then. 
\trope{ItGotWorse}{It Got Worse}. 









\subsection{\Ilu, the Sacred Mother (\yds{Ilu birth})}
First of all, the \banes{} need a mother for their Messiah. \Semiza{} chooses his most beautiful, most beloved young daughter who is still an unmarried virgin: \hr{Ilu}{\Ilu}. 

\Ilu{} has been raised to be very loyal and obedient to her father and king and to her people, so when she is chosen as the Sacred Mother, she could not refuse even if she were given the choice, which she isn't. She is honoured to be selected as the instrument of her new god's will. 

But there is a catch. Rather, two catches. 

\begin{enumerate}
  \item 
    The pregnancy and birth will be very hard and painful for her, so she must be strong and brave and endure much hardship for the sake of her god and her people.
  \item
    She \emph{must} be an untouched virgin. Otherwise it will all be much worse for her, and she may die.
\end{enumerate}

\Semiza{} is convinced and offers his beloved daughter as a sacrifice to the \banes. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  She is Thine, O take her quickly. \\
  Thou art her hope, O raise her high. \\
  Ever hoping, ever trusting, \\
  unto Thee I strive and cry.
}

He will make her a heroic martyr. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  But shall she be refined in Thine holy light? \\
  Her spirit will shine will thousand suns. \\
  Condone my doubt, but who am I? \\
  The haranguing priest of the newborn Herod king.
}

He just wants to save his people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Let them through thy boundless mercy \\
  from all evil be restored. \\
  Hearken to the voices pleading \\
  of Thy Church, O gracious Lord!
}

She has one purpose. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Born with the ability of begetting\\
  Only but One gift were she granted\\
  To excrete a new humanity unwanted\\
  Reluctantly she\dash woman\dash \\
  loves the god of a creation within
}





\subsubsection{\ps{\Ilu}{} sin}
\target{Ilu's sin}
The virginity requirement is a problem. See, \Ilu{} has \hr{Ilu's lover}{a lover}. They haven't had actual vaginal intercourse, so she is still a virgin. But they have done\ldots{} \emph{stuff}. She has sucked his dick. Only once, but it is enough that she cannot call herself \quo{untouched}.

But she was not supposed to suck his dick, and she dares not confess to her father that she did it. So she lies and proclaims herself untouched. \Semiza{} and everyone else is happy, and they proceed with the process of impregnating her as the Sacred Mother. 

Or maybe she was never asked, because her father considered her virtue to be beyond question. 

\Ilu{} is scared shitless. She is afraid that because of her wicked promiscuity (as she sees it), the whole project is in danger and may fail, and her people may never be saved. She has lots of guilt over this, but she is too afraid to come clean. She has lied to her father and made it all worse for herself. 

She's done other sexual stuff, too, but only touched a man's dick this once. And it's the worst part. The penis plays a huge role in their old religion, rituals, symbolism and sexual mysticism. The vagina is also important, but doesn't have as big a role as the penis. They are a masculine, patriarchal people who worship the phallus as a symbol of strength, fertility, masculinity, life, initiative and all that is good. In sex, the man and his mighty dick conquers the woman and binds her as his slave and property. He plants his seed in her womb, thus claiming it as his domain, and by extension, the woman must serve and obey him. (Perhaps you can even legally steal another man's virgin daughter by raping her, based on this mysticism.)





\subsubsection{She wants to conquer her sin}
\target{Ilu wants to conquer her sin}
She decides that she has brought the problem upon herself and is responsible for dealing with it. So she resolves to fight as hard as she can for the sake of the god-child that will soon be growing inside her. She swears that she will fight her own sin and vanquish it, and that the god-child \emph{will} be born. 

\Ilu{} is religious and prays a lot. To the old gods of her people, and to \hr{Bane religion}{her father's new gods, the \banes}\dash the \quo{fathers} of her child.





\subsubsection{Earlier attempts and giving birth to \resphain}
\Ilu{} was not the first woman who tried to give birth to the \banemessiah. Several other women had tried and died horribly before. 

The real reason for this is that first experimental \resphan{} foeti were \emph{too} voracious, too greedy, too parasitic. In their hunger they drained too much life-force from their poor, suffering mothers. The mothers would die long before the children were ready to be born, and the children would die as well.

But this was covered up. The official story, as told by \Semiza{} and \Eshayzal, was that the women were weak of faith and will. They had failed their god and their people. This put great emotional stress on poor \Ilu, who feared that she, too, would not be good enough, and would ultimately fail and die. 

There was always only one prospecting Sacred Mother at a time. The \banelords{} invested all of their \resphan{} power into the one \banemessiah, and so could only incarnate one at a time. Whenever one would die, the \banes{} would quickly reclaim the power and recycle it. 

Whenever the Sacred Mother started bleeding, mutating and suffering badly, she would be secreted away deep in a temple and kept hidden until her inevitable and grisly death. Thus, no one knows how horribly they suffer and die. 

Thus, \Ilu{} is happy and full of hope. She believes that she has been chosen for something wonderful and will give birth to a beautiful saviour. \Semiza{} assures her that she is the right one and that it won't go wrong this time. 

Perhaps \Semiza{} had long known that \Ilu{} was a good candidate. But out of love for her he didn't select her at first, because he knew the danger. But \Daggerrain{} tells him that she has the best chance of succeeding\dash and even a chance of surviving (not a lie). So at last, \Semiza{} chooses her. And she does fare better than many, because of her strong will and idealism. 





\subsubsection{Old artifacts consumed}
\Semiza needed a lot of old \aryoth relics in order to create \Thanatzil and imbue him with all the power of the greatest ones that \nephil-kind has to offer.
He took some \hr{Numah bones}{old magical bones and skulls and mummies} and destroyed them in the process.
The priests of the old religion were not happy at all, and neither were the people.
It was hard for \Semiza.
He cursed them for being so backwards and ignorant and unwilling to change.
They could not see that their old religion had failed them and that they needed to look elsewhere.
\Semiza was sad that he was one of the only \nephilim who saw with an open mind.









\subsection{The seed is sown (\yds{Ilu pregnant})}
\target{Semiza designs Resphain}
\target{Origin of Resphain}
\Semiza{} and his sorcerers, under guidance from \Daggerrain{} and his \banelords, labour to prepare the arcane ritual that will impregnate \Ilu{} with the Messiah, the first \resphan. 

This must be done in secret, so that the \dragons{} do not suspect.

\hr{Entropy}{The \banes{} suffer from stagnation and cannot easily create new things}. So they needed the help of an ingenious mortal mind to engineer their new super-race.
So \Semiza{} ends up acting like the primary artist and designer behind the whole \resphan{} project. He understands \ps{\Daggerrain}{} vision of a super-creature with traits from \banes, \voyagers{} and \nephilim{} alike. The \banes{} can supply them with knowledge, but they must do the research themselves.

At \ps{\Semiza}{} side stands \hr{Eshayzal}{\Eshayzal}, his companion and advisor. Together they engineer the \resphan{} god-child. 

They worked hard for some time, and finally the research was complete. 
They were ready to perform a magical ritual and impregnate \Ilu{}. 




\subsubsection{Ritual prepared}
They began the impregnation ritual of poor \Ilu. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Thou shalt bringeth the chalice of divine wrath \\
  and final consummation to thine lips, \\
  and drink with confidence\ldots{}\\
  Tell me, sweet child, \\
  why are tears rolling from your eyes?
}




\subsubsection{Invocation of the \banes}
\Semiza-tachi invoke the \banes. 

\lyricsbs{Hate Eternal}{Catacombs}{
  Rise up from the ancient tombs. \\
  Grant us all your infinite wisdom. \\
  Endure as you rise from the catacombs. 
}

\lyricsbs{Hate Eternal}{The Creed of Chaotic Divinity}{
  Awakened by this ancient creed. \\
  Evoked, the ancestry of thee.\\
  Forsaken for centuries of times. \\
  Exiled, all of their kind. \\
  Foretold, the inheriting of the Earth.\\
  Forewarned of this predestined rebirth. \\
  Engaged, the rising from below.\\
  Fear, all mortals, for what they shall bestow.
  
  Conjure all, so that they may sustain\\
  their race, of what they must retain.\\
  Spew forth incantations in vain. \\
  Invocate all that they try to negate.\\
  Enchant all of their wonderful splendour. 
  Recant all of the texts that are sacred. \\
  Recreate all that has been begotten. \\
  Revive all that has been forgotten. 
}




\subsubsection{\Ilu{} impregnated}
\Ilu{} was knocked up. 
This happened in an aethereal, sexual dream sequence. 
She was half-raped, half-seduced by faceless, unclear, monstrous, almost-but-not-quite-\nephil-like monsters:

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Organic procreation, mind-intromission; there comes the salvation\\
  Pubescent vaginas obstructed with the redeemer's holy essence\\
  Humanity reduced to its supreme worthlessness;\\
  Children under His will, Ethic fulfilled
}

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Carnal Malefactor
}{
  There resides the fusion, there is the nucleus\\
  Angel prick and holy semen,\\
  And a woman genuflecting an aroused beast of burden alike\\
  Seduced by the father and seducing the son\\
  There resides the fusion, there is the nucleus\\
  A phallic communion that sanctifies interior wastelands
}









\subsection{\Ilu{} suffers}
\Ilu{} suffers horribly during her long pregnancy. 

How long is her pregnancy? The gestation period for \nephil{} women needs not be nine months like it is for \humans, and the gestation period of the \banemessiah{} needs not be the same as that of a \nephil{} child. 

It might be longer than nine months. And the sorcerers might need to perform many spells on her while she carries the child. And she would be required to work hard to aid them in their spellwork. (How?) 

\Ilu{} believes that it is \hr{Ilu's sin}{her own sin} that causes her to suffer. That and her weakness. She is intent on conquering her sin, so she fights hard, not only to combat her weakness, but also to hide it. She \emph{will} be strong. She \emph{will} serve her people well. She \emph{will} make her father proud. His faith in her shall not have been misguided. 

In truth, \ps{\Ilu}{} little blowjob had no effect at all (except psychologically). The \banes{} needed physical virginity for some reason. Why? Because there is some \hr{Heart}{Heart of \Miith} related power in her womb and sexual organs that they need to harvest, and that power is weakened when a girl loses her virginity. 

Anyway, the point is that all of \ps{\Ilu}{} suffering is not her fault. It is caused by the \banes{} and the \halfbane{} child growing inside her. 
As the mother of the \erebean{} abomination, she is cruelly abused. 
She is cruelly abused by the parasitic abomination growing inside her. It sucks out all of its own mother's life-force. She grows weaker and weaker and will eventually die in childbirth. 

%The \nephil{} women who had to give birth to the first \resphain{} are cruelly abused. They carried and delivered the children in gruesome pain and suffering, and the parasitic children sucked out all of the mother's lifeforce, killing her in childbirth. In fact, the first experimental \resphan{} foeti were \emph{too} voracious, killing their mothers long before they were ready to be born, and then died. As the mother carries the child, she suffers horribly as the gruesome thing sucks everything from them. 

Compare to the Mhybe from \cite{StevenErikson:MemoriesofIce}, except that all the suffering takes place \emph{before} the birth (whereupon she dies). Also compare to \bandsong{Hour of Penance}{Hideously Conceived}. 

She dreams of her wicked child and his evil \quo{father}. 
She is afraid. 

But it is important to note that Ilu is not against the whole thing. 
She laments the fact that she must suffer, but she tries to be strong because she knows it is the right thing to do. 
Her suffering will bring much good into the world. 

\Semiza{} and the others try to support her and be nice to her. 
She is their beloved and holy martyr, and they admire her for doing it. 
\Semiza{} tries to be a good and loving father, but his crazy religion somewhat estranges him from his people. 
Ilu laments this. 
She doesn't want her father to be alone and weird. 
So she is extra brave for his sake. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Night after night grim voices shriek \\
  in portentous horror dreams, \\
  even though his room was locked, \\
  but a Seraph comes unseen. 
  
  Night after night his skin was flogged. \\
  Damn those recurrent dreams. \\
  Desperately flogging for relief \\
  while murmuring blasphemies. 
  
  The bloodstained walls surround him, \\
  icons made of Calvary wounds. \\
  Dreams of riddance were shattered in sin, \\
  ill-fated to avert doom.
}

According to the theory, her suffering is partially caused by the \kenosis: 
The process by which the god (to whom she must give birth) is incarnated in the form of a feeble foetus. 
This process is difficult and painful, and it is \Ilu{} who must bear this pain. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Obedience to the point of death,\\
  Falling down through increasing pressure\\
  Into the deathlike region\\
  Of ooze and slime and decay\\
  These are the fruits and symptoms \\
  of the abasement of the World,\\
  The assumption of humanity \\
  and the simultaneous occultation of Divinity
}





\subsubsection{Hentai nightmares}
\Ilu{} feels terrible guilt over having sucked dick. She has frequent nightmares of being forced to suck dick. She might be in a forest of penises, like monstrous trees or fungi or worms or snakes that slither around her and try to sneak into her mouth and other openings. Perhaps faceless men with penises (and no other recognizable \nephilic{} features) crowd and rape her.

Hentai!















\section{\Thanatzil{}, the \BaneMessiah (\yds{Thanatzil birth})}
\subsection{\Thanatzil{} is born}
At last, the \banemessiah{} is born. \Semiza{} gives him the name \hr{Thanatzil}{\Thanatzil}, which probably means something in their language. 

The story of \Thanatzil{} is very much inspired by the Christian myth of Jesus, and is intended, to some extent, to be a very dark, sick, twisted version of the Jesus myth. I need to have plenty of Jesus-like symbolism surrounding him.

\begin{itemize}
  \item 
    He is born of a virgin by immaculate conception.
  \item 
    \Nephilic{} kings come to greet him and pay homage to him at his birth. These are the kings of other tribes who have allied with \Semiza, swayed by his vision and his new religion. 
  \item
    He is an earthly/\Miithian{} incarnation of his gods, the \bane{} people, and born as a saviour to deliver the \nephilic{} people. 
  \item
    He \hr{Thanatzil must die}{must die and be resurrected} in order to save his people from hellish imprisonment. 
  \item 
    His birth is heralded in the heavens by a \hr{Black stars of Nyx}{black star} that shines through from \Nyx, or perhaps even \Erebos. It is a temporary portal through which flows power and a \bane{} soul from \Nyx{} into \ps{\Thanatzil}{} body. It is visible everywhere on \Miith{}, and some \dragons{} take note.
  \item
    \Nephilic{} kings came to visit and pay homage to the newborn \Thanatzil. These were allies of \Semiza{} who believed in his new religion and his vision of a future for their people. 
\end{itemize}





\subsubsection{\Thanatzil{} appears}
\ps{\Thanatzil}{} birth is terrible to behold. The infant is unlike any \nephil: Short and slim, black as midnight, and completely naked (where \nephilim{} are covered in hair, even from birth). He remains bald and hairless throughout his life. And he has feathered wings on his back. 


\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Carnal Malefactor
}{
  When a woman is knead by the claws of fowls attracted\\
  By seminal odours no longer hidden by dignity\\
  And purified by their beaks rummaging her swollen vagina\\
  When laments alter into praises \\
  despite holy duty and menacing perdition\\
  Seers can say that his birth does death subdue no more\\
  His birth does death subdue not, \\
  for my God proceeds of failed humility\ldots{}\\
  O Master, the eastern pillar of your domination \\
  is the organic fallibility.
}

The Messiah comes into the world riding a river of blood, tearing apart the flesh of his screaming, dying mother. He utters no cry, but rises to his feet (impossible for any normal \nephilic{} newborn) and gazes at everyone with his cold, wicked eyes, gleaming with an unearthly incandescence. The sight of this un-\nephilic{}, naked, winged creature, black-skinned and covered in blood, seeing deep into everyone's soul with eyes revealing knowledge and intellect that should by right be beyond any infant, is chilling and morbid to behold, but also awesome. Most of the people are already blinded by their religion and its mind-controlling magic, so they see him only as a beautiful, magnificent, majestic saviour. 

(It is somewhat strange that he would rip his mother open, since he is smaller than a \nephilic{} child. But he does, because his birth and his very nature are so violent and cruel.)





\subsubsection{\Ilu{} dies}
\ps{\Ilu}{} body is only a bleeding ruin at this point, but she lives a few more moments. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Innocence sacrificed and heaven denied\\
  Iniquity divine\dash no repentance\dash over mankind\\
  Mind-raped, self-devoured, empty god-eyed\\
  Transgression coercive, Redemption never to be found

  Under the altar of cannibalism\\
  Man hast (thou) confessed the spiritual schism\\
  And without pride mourned the loss of freedom,\\
  Our blessed Lord have condemned you to martyrdom
  
  Let everything that hath breath praise the Lord, \\
  praise ye the Lord.
}

She sees her son and sees that he is alive and healthy. She feels the power and life force radiating out from him\dash power that he stole from her. He turns and meets her gaze. She recognizes the monstrously alien soul inside him, but he is still her son, her flesh and blood, so she loves him. He gives her a half-smile of gratitude. She is happy, knowing that she \hr{Ilu wants to conquer her sin}{conquered her sin in the end} and so fulfilled the quest she undertook. Her hard work, prayers and suffering have borne fruit and she has redeemed herself. She has served her father, her son, her kingdom and her gods. She is happy to die for this. And so she does, with a smile on her lips and her body torn to shreds. 

\lyricsbs{Monolith Deathcult}{Der Kriegmeister}{
  For the glory of Death and the crown of the horns.\\
  I murder like Manson when I cut out her womb.\\
  In the blood that she bled she lay drowned in her tomb.
  
  Suffocate, inhale death's breath. \\
  The crown of thorns tortures my head.\\
  Rape my wounds, my doomed bloodlet, \\
  receive my last caress.\\
  Demonclaws tore my skin, \\
  salicious women prove my sin.\\
  The seventh day had just begun, \\
  and soon your God will die.
}

\Ilu{} believes in the \banes{} and in \Thanatzil{} even with her dying breath. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  First Prayer
}{
  Lungs filled with embers and regurgitating boiling blood I say:\\
  Praise the Lord, praise,\\
  O servants of the Lord\ldots{}\\
  We will sing a new song to thee,\\
  O God: a psaltery of thirteen Stations. \\
  May scoria bury Eden and blind the light of hope\ldots{}
}





\subsubsection{Do more research}
I should do more research on Jesus, Horus, Mithras and other similar gods. 









\subsection{Rebels}
\target{Rebels against Semiza}
\target{Semiza's rebels}
Some of \ps{\Semiza}{} subjects are horrified by the evil of this new religion and the insanity of the king's plan. They begin to work against \Semiza. Their heroic deeds are essential in defeating the \banelords{} by \hr{Semiza fails}{interrupting \ps{\Thanatzil}{} resurrection}. 

Compare this to the rebellion in the \emph{Star Wars} movies.

They dislike the king's blasphemy against the old gods. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  Shrovetide is violated by heathens. \\
  Nefarious splurges of sin. \\
  Persuasion is trembling with fever \\
  and became a mantra of occult tongues. \\
  Mankind enclasped Doom. \\
  He turned his back on God. \\
  Virtue became ultra-decadence. \\
  We are all libertines of the damned.
}





\subsubsection{A rebel Messiah}
Maybe the rebels have their own Messiah-figure, a representative of their old gods. 
Probably a woman. 
She founds the rebellion. 

She is secretly backed by \Vexstrasshin. 
Perhaps even possessed by her. 

Perhaps she is killed by \ps{\Semiza}{} people. 

\lyricsbs{Monolith Deathcult}{I Spew Thee Out of My Mouth}{
  A Fidei Defensor arises, \\
  flogged and whipped from head to foot. \\
  The body cleansed by self-flagellation, \\
  supressed the lust of flesh and blood.
}









\subsection{The \resphan{} race}
%In the beginning, the entire \resphan{} power is 
\Thanatzil{} wields the power of the \banemessiah. But it is not his mission to save his people \emph{alone}. Rather, his purpose is to be the founder of a new race of \halfbane{} superbeings. 

\Semiza{} names them \resphain. 
This means \quo{superhuman} or something like that in their tongue. 





\subsection{\Resviel{} are designed}
\target{Origin of Resviel}
%\ps{\Semiza}{} sorcerers now collaborate with the \banelords{} and the fledgling \resphain{} to create a race of slaves: \Humans.
\Semiza-tachi realize that the process of having \nephilic{} women give birth to the \resphain{} is inefficient. 
The \nephilim{} are too weak. 

So \Semiza{} and the \banelords{} want to create a new race of female \resphain, to act as sex slaves and birth mothers for the \resphan{} race. 
They design the \resviel. 

The \resvil{} experiment succeeds beyond all expectations, and already in the design phase, when the first \resvil{} has yet to be born, it is clear that the \resviel{} are too good to use as sex slaves and mothers. 
This is part of the motivation for \hr{Origin of Humans}{creating \humans}.











\subsection{\ps{\Thanatzil}{} life}
\Thanatzil{} grew up. 
By the age of 20 he looked like a \human{} youth of the same age. 
(This was abnormal. \Resphain{} normally grew slower than \humans.) 
He was tall, almost as tall as a \nephilic{} man, but much slimmer. 

He has the \hr{Resphan vampirism}{vampiric appetites of a \resphan}. 
He eats the hearts of people sacrificed to him, to devour their souls. 
This may or may not be distasteful to him, but he does it. 
He probably doesn't enjoy it. He is the first \resphan, after all, and he sees clearly the horror writ on every (sane) face around him when he eats hearts or does other horrible things. 
(In later \resphan{} societies, every \resphan{} does it, so it is considered perfectly acceptable.)

For all his power, \Thanatzil{} is only a boy, and it is hard for him to bear the responsibility of the \banemessiah. 

He knows that he is a scion and representative of the \bane{} people, an incarnation of their legacy.

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  I have lived for millions of years. \\
  I am the day of yesterday. \\
  I know the day of tomorrow. \\
  The Alpha and Omega. \\
  I am eternal.
}

He is a guide and holy figure to his people. 

\lyricsxkcd{40}{
  In a dark and confusing world, \\
  you burn brightly. \\
  I never feel lost. 
}

He is distressed because he feels he has no power to control his own life. 

\citebandsong{BeyondTwilight:TheEdge}{Beyond Twilight}{Salem}{
  The darkness in the crystal expresses the inner fear.\\
  The light reveals the love she holds inside her. \\
  Reborn to lead a life controlled by the sorceress. \\
  She will know what she must do to come through. \\
  
  Her life on Earth lasted only for eight years.\\
  You can see she's frightened of the dark, \\
  but you'll never see her tears. 
  
  Nightmare in nowhere land.\\
  Exempting lying poetry. \\
  Missing the life she's owned.\\
  Slowly withering away.\\
  Too young to take a stand.\\ 
  There is no remedy. \\
  Her life being overthrown. \\
  Sunk in silent prayer. 
}




\subsubsection{Devoured souls}
He feels all the souls he has devoured, feels their pain, anguish and hate.

\lyricslimbonicart{A Venomous Kiss of Profane Grace}{
  The dead speaks to me\\
  from beyond the grave.\\
  That is why my conscience is.\\
  I`ve buried the dead alive.}

But he needs their power to fulfill his quest. 

\lyricslimbonicart{A Venomous Kiss of Profane Grace}{
  The blood of the child is pure now.\\
  In death it gives me life.\\
  The circle is complete.\\
  Begin another\ldots{}
}




\subsubsection{Sex}
\Thanatzil began having sex when he was 15.
He soon impregnated his first \nephil women.
Soon after that \hr{Origin of Humans}{the first \humans} were born.





\subsubsection{He sees the evil that he represents}
\Thanatzil{} gazes into himself and sees the morbid evil of which he is the prophet, the messiah. 
He is horrified, but he keeps his faith and forces himself to repress doubts and fears. 

\lyricslimbonicart{Dynasty of Death}{
  Dungeon darkness in violent fire.\\
  Transfix the soul with Hell's desire.\\
  Where myriad's of lives are laid in ruins, \\
  dormant in the ashes of all terrestrial dreams.
  
  The dynasty of death.
}

He angsts over his evil. 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  A passion for my rage, with my sights of darkness.\\
  The atrocities at hand I must bare/bear. \\
  Entangled in a state so cold, so dormant. \\
  My sickened rageful state, my hateful lair. 
  
  Saturated in dejection. 
}

But he must. 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  Hardened by this reality. \\
  Sights of vengeance ever so clear. \\
  Compelled to rejuvenate this world of hate \\
  into a mass of chaos and fear. 
  
  Saturated in dejection. 
}

He eats souls and grows strong. 
This strength allows him to send his soul wandering through the Cosmos. 
He contacts cosmic gods and his \bane{} fathers. 
He gains wisdom.  

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  The sickening things that I witness. \\
  I derive distinct visions from\\
  the sickening throughts that they confess. \\
  Hatred at its purest form. 
}

He forces himself to accept it. 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  So compelled to what I've witnessed, \\
  mesmerizing, so enticing,\\
  I revel in their grief. \\
  I confess, my vision is my religion. 
}

He has a split personality of sorts, being part \nephil{} and part \bane. 

\lyricsbs{Hate Eternal}{Two Demons}{
  I am duality. A being so consumed with 
  the darkness inside of me.\\
  Through this pain I must endure 
  these beings that still haunt me.
  
  I am adversity. Within the sunder of 
  the essence of my very soul.\\
  In this rage I shall remain, 
  these creatures that become me. 
  
  Come forth and purge yourself for what you are.\\
  Reveal thyself and become what you will. 
  
  I am diversity. So weary of the angst, 
  so weary of what I have become. \\
  Through this dread I will retain, 
  this penance that still haunts me.
}

He is unsure whether what he is doing is right. 

\lyricsbs{Emperor}{Grey}{
  desperately I seize tomorrow, all out of my reach\\
  that is what I learned, this is what I teach\\
  corruption seems to flourish while promises decay\\
  where lights are dim and shades of black are grey
}

He had doubts. 
He was allegedly an incarnation of the mighty \bane-god, older and greater and mightier even than the \dragons. 
But often he did not feel like a god. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  And He is before all things, and in Him all things consist\\
  Triune God, morphed into a Being of apparent theanthropic nature\\
  Deprived of the Light of Splendor\\
  Dost thou still stand in undiminished Majesty\\
  After the exinanition of divine attributes\\
  The face of profound fire gone astray,\\
  Exhaling austerities in concealed, divine radiance?
}

\Thanatzil could feel the pressure of the \banelords upon him, and it scared him.
He felt naked and vulnerable under their dread gaze.

\citebandsong{Nile:FestivalsofAtonement}{Nile}{
  Wrought
}{
  Nanna Father of the Zonei\\
  Eldest of the Wanderers\\
  A Shadow out of Time\\
  The Moon is calling Me\\
  The Breath of the Old Ones\\
  Whispers in my Ear\\
  With inhuman Impatience\\
  They Beckon to Me

  I call to the Moon and Sin\\
  I now possess the secrets of the Tides of Blood

  I have \traveled on the Spheres\\
  And the spheres do not protect Me\\
  I have Walked in the Pit\\
  And the Pit does not protect Me

  The Lords of the Wind rush about Me\\
  The Lords of the Earth crawl about my Feet\\
  And are Angered\\
  A Wind has Risen \\
  The Dark Waters Stir
}





\subsubsection{\Semiza-tachi convince \Thanatzil}
\Thanatzil{} has plenty of doubts and fears. 
\Semiza{} and his ilk do all they can to convince him that he is doing the right thing and must continue. 

\lyricsbs{Hate Eternal}{Servants of the Gods}{
  Heed not for our sins,\\
  for our sins hath no path of impurities.\\
  For it is I who will conquer \\
  this plane of existence.
  
  Heed not for our scrolls,\\
  for our text hath no path of deviation.\\
  For it is I who will transcend to \\
  this plane of existence.
}

At the same time, \Semiza{} is thinking about his own dream. 

\lyricsbs{Hate Eternal}{Servants of the Gods}{
  I shall exact my revenge, \\
  for I am the top of the hierarchy.\\
  Heir to a tradition of unification.\\
  For I am the mother and the father\\
  and the heart of our domain.\\
  I am the wiseman.\\
  I am a thing of evil.
}









\subsection{\Humans{} are designed \yic{First Humans conceived}}
\target{Origin of Humans}
\ps{\Semiza}{} sorcerers now collaborate with the \banelords{} to create a race of slaves: 
\Humans.

Note that first \humans{} were created \emph{before} the \resphain{} (bar \Thanatzil). 





\subsubsection{Purpose}
%The \human{} men are created because the \nephilim{} and \resphain{} don't want to work and want some slaves to do their dirty, menial work for them. 
The \human{} men are created to serve as a race of worker slaves, beneath the \resphain{} and more manageable than the somewhat savage \nephilim. 

The \human{} women are created to serve the \resphain{}\dash and, to a lesser extent, the \human{} men\dash as sex slaves and mothers. Originally, \hr{Origin of Resviel}{the \resviel{} were designed to fill this role}, but they proved useful for far more than that, and were promoted, so the \human{} women were designed to fill the vacancy.

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Born with the ability of begetting\\
  Only but One gift were she granted\\
  To excrete a new humanity unwanted\\
  Reluctantly she\dash woman\dash \\
  loves the god of a creation within
}





\subsubsection{How they were created}
The first \humans{} are created by letting \Thanatzil{} have sex with and impregnate some \nephilic{} women, after both mother and father have been annointed with special spells. 
So the \humans{} are half \nephil, half \resphan\dash in other words, three quarter \nephil{} and one quarter \bane. 





\subsubsection{The experiment fails}
\target{Humans fail}
The preliminary \human{} experiments are considered failures. 
The alpha-test \humans{} were supposed to have been killed, but after \hr{Thanatzil fails}{\Thanatzil{} was killed}, the \humans{} escaped into the wild and bred true. 
Later they would be rediscovered and adopted by the \resphain. 





\subsubsection{\Demihumans}
The first \humans were diverse. 
There were several exotic \quo{\hr{Demihuman}{\demihuman}} strains that quickly died out. 

Also, remember that \humans quickly mixed with \nephilim. 
So the first \humans might very well have looked much less \quo{\human} than the later ones. 









\subsection{Madness}
\Semiza{} was going mad. 
Partly due to consorting with the wicked and scary \banes. 
Partly due to isolation and despair because his people were hesitant to embrace his new religion, even after all he had sacrificed for their sake. 
And partly out of concern for Ilu. 
He truly loved Ilu and was sad to see her suffer. 

\lyricsbs{Emperor}{Empty}{
  he is an empty shell\dash{}shell-shocked luciferian heart\\
  he is an empty shell\dash{}drained and sealed\\
  he is an empty shell\dash{}penetrating cold\\
  he is an empty shell\dash{}empty luciferian soul
  
  the constant struggle for a moment of quiet indulgence\\
  eventually stirred and quaked the earth so hard\\
  it swallowed him in a dark and heavy cloud\\
  slowly and gently starving him into insanity
  
  an inferno of ice\\
  with an ever burning \\
  bleeding heart
}

\Semiza{} knew well that he is going mad. 
But it was worth it to gain power, revenge and eternal glory.
So he kept at it.









\subsection{\Thanatzil{} is tempted by a \dragon}
At least one \dragon{} suspects that this whole \Thanatzil-business is \trope{SeriousBusiness}{Serious Business}. His/her fellow \dragons{} do not believe him, so he sneaks into \ps{\Semiza}{} city in disguise. Maybe even in the form of a serpent. 

He seeks out \Thanatzil{} in dreams and tries to tempt him to abandon his people. He doesn't quite understand what \Thanatzil{} is or what he wants. (Maybe the \bane{} power is masked so that the \dragons{} cannot recognize it. Or maybe this \dragon{} is not old enough to remember the \firstbanewar.) But he tempts the young \resphan{} with promises of power and things. 

\Thanatzil{} goes out into a desert or the like to confront the tempter. Here he finally banishes the \dragon. 

\Thanatzil: \ta{I know what thou art. Begone! Thou canst not tempt me, not canst thou thwart me.}

The \dragon{} then conspires with the \hr{Semiza's rebels}{rebels} to interrupt \hr{Thanatzil's resurrection}{\ps{\Thanatzil}{} resurrection}. 















\section{\Thanatzil{} and his Destiny (\yds{Thanatzil death})}
\subsection{\Thanatzil{} must die}
\target{Thanatzil must die}
In the beginning, the entire \resphan{} power is incarnated in \Thanatzil. 
In order to spawn the \resphan{} people, \Thanatzil must:

\begin{enumerate}
%   \item 
%     Grow to adulthood, or at least \hr{Resphan sexual maturity}{sexual maturity}.
  \item
    Impregnate a number of women with his seed. 
    \subitem
      Are these women \nephilim{} or \humans{}? 
      Probably \nephilim, since it takes at least like 12-15 years to grow a \human{} woman old enough to bear children, and \Thanatzil{} is not meant to live that long.
    \subitem
      How many women? 
      Perhaps some magical number, like 12 or 21 or 40.
  \item 
    Undergo a dark and terrible ritual in which he will die and be resurrected. 
    \subitem
      His death will release the Messiah power within him. 
      It will fly free, reach out to the \bane{} souls incarcerated in the depths of \Nyx, free these souls and allow them to pass into \Miith{}, where they can merge with the souls of \nephilim{}\dash the sons and daughters of \Thanatzil \dash and incarnate as \resphain. 
      %power and distribute it among his his sons and daughters, allowing them to be born. 
    \subitem
      His resurrection is necessary, because \Thanatzil{} is an embodiment of the connection between \Miith{} and \Nyx{} (just like how \hr{Daggerrain is the gate}{\Daggerrain{} is the key to the pathway between \Nyx{} and \Erebos}). 
      If \Thanatzil{} dies permanently, then so does the contact with \Daggerrain. 
\end{enumerate}

The resemblance to Jesus should be obvious. 

All the mothers are impregnated in one day/night\dash spells are used to keep \ps{\Thanatzil}{} dick going all that time. 
The occult rituals involved in the spawning of the \resphain{} make sure to keep all the mothers synchronized, so that all the births will happen on the same day. 

\Thanatzil{} thinks of \Erebos: 

\lyricsbs{Emperor}{The Prophet}{
  \quo{%
    It is the place where blood and soil\\
    lie beyond the boundaries of the sun}
}

He thinks of his own role. 

\lyricsbs{Emperor}{The Prophet}{
  \quo{%
    and I am its prophet \\
    I cast the shadow\\
    I absorb the light}
  
  \quo{%
    I am the prophet\\
    I bear witness\\
    I absorb\\
    I cry}
    
  \quo{%
    As I die, I shall burst wide open\\
    As I die, I shall release the apocalypse\\
    My prophecy\\
    Thus, I hold on to faith\\
    Thus, I keep the hope\\
    That it will prosper \\
    and devour}
}





\subsubsection{Mothers of the \resphan}
\target{Mothers of the Resphain}
A number of \nephilic{} women are impregnated by the young \Thanatzil{} in the months up to the sacrifice ritual. 
They are meant to stay pregnant through the ritual. 
(If they were to give birth prematurely, the children would die.)
The ritual and \ps{\Thanatzil} sacrifice will release the \bane{} energy that will empower the infants growing in their wombs so that they may live and be born as healthy \resphain{} and \resviel. 

How many mothers are there? 
Quite a lot. 
Perhaps 100. 





\subsubsection{Some mothers are hidden}
Most of the mothers attended the sacrificial ritual. 
But a few of them were hidden away. 
This was a special security precaution by \Daggerrain. 
He knew that something might go wrong at the ritual and in that case he wanted to have a few mothers left as a backup plan. 

But \Vexstrasshin{} was clever and sniffed out these mothers and had them killed. 
The \nephilic{} rebels she coerced into killing the mothers were not happy about killing pregnant and defenseless women, but they did their duty. 









\subsection{\Thanatzil{} saves the outcasts}
\Thanatzil{} summons all sorts of sick people, madmen and outcasts to him. 
He promises them redemption by the \bane{} gods, offers to give their lives meaning. 

This \quo{meaning} is to be consumed so that their souls may feed the summoning ritual. 
The \quo{redemption} is that their useless lives will be over and their deaths will serve a useful purpose (so their deaths will be more valuable than their lives ever were). 

\Thanatzil{} does not want to do this, because it feels like betrayal and dishonesty. 
But \Semiza{} convinces him that he must. 
\Semiza{} tells him of the many sacrifices he has made himself. 
\ta{Yes, it will be a painful decision. 
    But it is the duty of a leader to suffer for his people. 
    You must do the right thing, \Thanatzil.}

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Pagan Messiah\dash the almighty fiend. \\
  Abode of the damned, defiled, unclean. 
  
  Spiritual holocaust. 
  
  Plead for forgiveness. \\
  You can't resist its temptation. }

The damned die. 

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Spiralling permanence. \\
  Merciless decadence. \\
  Unethical banishment. \\
  Fall before that which summons you.
  
  Imminent dormancy. \\
  Heinous atrocities.\\
  Demons that beckon me.\\
  That which to escape is to die. 
  
  Spiritual holocaust. 
}









\subsection{The Resurrection Day}
\target{Thanatzil's resurrection}
\target{Resphain lose contact with Banelords}
The great day draws near when \Thanatzil{} will die and rise again, and with his resurrection the \resphain{} will be born. 

%I need to make up a cool name for this day. 

All the \hr{Mothers of the Resphain}{\resphan{} mothers} are gathered, as are a lot of soldiers and priests. 
The mothers are to \quo{inherit} the energy he will release with his death. 

The ritual is prepared. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Kenosis, O' theory of great peril!\\
  Blinded, sanguineous eyes and with a trembling hand,\\
  A frail androgynous being holds the perilous doctrinal balance,\\
  Robed in a maculated garment spattered with the sordid blood\\
  Of the Flagellation, of the lacerations and fierce wounds\\
  Carved by royal attributes, of the crimson spurts\\
  Dripping without end,\\
  As was celebrated the High Mass of the Comforter
  
  Kenosis, O' theory of great peril!\\
  Rob God of any attribute and fill the shattering universe\\
  With the pestilent scent of putrefaction \\
  and the glorious cloud of death,\\
  For steadfast, at any cost, He must be\\
  Solely the incarnate Word \\
  proclaimed by all the prophets and apostles\\
  Would have, in dying, an infinite value,\\
  Sufficient to atone, by His astonishing work,\\
  For the Sins of the world
}

The ritual commences. Compare it to the Babylonian myth of \quo{The Descent of Ishtar}. And the text \quo{Of the Sleep of Ishtar}, a fictional reinterpretation of aforementioned myth, found in \simonnecronomicon. 





\subsubsection{\Thanatzil{} dies}
\target{Thanatzil dies}
\Thanatzil{} prepares his sacrifice. 

\lyricsbs{Emperor}{The Majesty of the Night Sky}{
  Too long I have suffered the desert sands of time. \\
  But as I drown in darkness it will release the sign. \\
  My soul will leave this mortal coil of flesh and earthly life, \\
  to fly into the mist of night, into the nightside eclipse, \\
  and experience existence on the other side. 
  
  As a stone of scorching enthusiasm \\
  I refract the reflecting surface of this unfathomable sea. \\
  Growing circles of grief and pain slides across the land \\
  as an omen of the horror yet to come. 
  
  The strength of a thousand fire-breathing demons \\
  breed in my infernal, sinking soul. \\
  And as I reach the surface once again \\
  these powers are under my control. \\
  Now I am one with the night sky majesty.
}

\Thanatzil{} dies. 

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  The Abyss yawns wide\ldots{} Claws sharpened on the dead.\\
  The Abyss yawns wide\ldots{} Ensanguined fangs agleam.
  
  Great shadow, awaken and eclipse the suns of a thousand worlds\ldots{}\\
  Slumbering 'neath these crimson vaults, \\
  behold the majesty of the Outer Darkness!\\
  Praise the Z'xulth!
  
  Fell Worm of the Black Galaxy, \\
  awaken and descend without pity upon the Tellurian sphere!\\
  Destroy the flaccid priests of the newborn usurper faiths.\\
  Sweep away the thralls of the cruciform stave!\\
  Crush the lackeys of the corrupted hexagram!\\
  Devour the slaves of the eastern crescent!\\
  Crush them, grind them, slay them all!\\
  Plague-blessed, flay them alive!
  
  Now, behold in terror what waits beneath the crimson vaults of Cydonia\ldots{}}
  
\lyricslimbonicart{A Venomous Kiss of Profane Grace}{
  Silent screams of suffering.\\
  I stand in flames of torturing.\\
  Goddess of flesh hunger and desire,\\
  grant me wings of hellish fire.\\
  Know that all my creations spring\\
  from blood on the cross in blasphemy.\\
  I am death, the creator of sin.\\
  and of the pure I am the wind.}

\lyricslimbonicart{The Dark Paranormal Calling}{
  A serpent in my soul.
  
  In midnight's aura as a ghostly fire.\\
  The child prodigy of abysmal desire.\\
  As the deathlike silence pervades, \\
  the incubus now invades.\\
  Show yourself, unclean spirit. \\
  Tonight I give thy shadow life.\\
  Rise with me in darkest blessing.\\
  Thine demon force I feel possessing.\\
  A holotropic mind and spectral eyes divine.\\
  Through the shallow haze as the sky turns red\\
  I walk and dream among the dead.
}

\lyricsbs{Hate Eternal}{Spiritual Holocaust}{
  Spiralling permanence. \\
  Merciless decadence. \\
  Unethical banishment. \\
  Fall before that which summons you.
  
  Imminent dormancy. \\
  Heinous atrocities.\\
  Demons that beckon me.\\
  That which to escape is to die. 
  
  Spiritual holocaust. 
}

\lyricslimbonicart{A Cosmic Funeral of Memories}{
  The night belongs to the predator\\
  to the one who dares crossing the threshold,\\
  the axis of dreams and wonders and black miracles.\\
  I see my self in the mirror of your eyes:\\
  A dark star on the celestial beautiful midnight sky.\\
  Release the inner radiance of what you have become.\\
  Brighten the night with your sacrifice.
  
  I have returned to life to speak of clairvoyance.\\
  I am the voice from the grave land of memories.\\
  Life can be only an illusion, and death a temptation,\\
  a final destiny.
}





\subsubsection{Rebels strike}
But then disaster strikes. The \hr{Rebels against Semiza}{rebels} attack and interrupt the ritual. 

\Vexstrasshin{} hopes to kill all the mothers. 





\subsubsection{A rebel sacrifices himself}
The rebels are almost stopped. Then their \draconian{} ally speaks to them. She cannot enter the city herself\dash\Semiza{} and the \bane{} magic has blocked her out\dash so she must act through her \nephilic{} allies. 

One hero among the rebels sacrifices himself to allow the \dragon{} to possess his body and channel her magic through him. This is a dangerous, experimental process and will permanently destroy both his body and soul. 

\lyricsbalsagoth{
    The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire 
    - Part III: 
    Cry Havoc for Glory, and the Annihilation of the Titans of Chaos
}{
  [THE ECHOES OF THE IMMORTAL:]\\
  Hearken, noble King of Hyperborea.\\
  \ldots{}\\
  To utterly destroy the Dark Liege of Chaos, you must join your essence with mine\ldots{} we must fuse our life-forces and become one so that my full power may be unleashed against Angsaar once more. \\
  But this final deed demands the most severe of tolls, o' noble monarch\ldots{}\\
  To become as one with the immortal essence of the Shadow-Sword is to sacrifice forever your own mortality, and to forsake eternally the world of man. \\
  Are you prepared to pay this price, King of Hyperborea?
  
  [THE KING:]\\
  To preserve the sovereignty of my realm and safeguard my people from the 
  forces of darkness? Aye! For my kingship demands no less a commitment!\\
  So be it\ldots{} let this final deed be done!
}

\Thanatzil{} still hangs around as a ghost with some power. The \bane{} power flows into him, and he becomes manic.

\lyricsbalsagoth{
    The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire 
    - Part III: 
    Cry Havoc for Glory, and the Annihilation of the Titans of Chaos
}{
[LORD ANGSAAR:]\\
  (No\ldots{} my eternal nemesis, you will not thwart me! Abominations rise! 
  Destroy these mortals who vex me as the buzzing of gnats vexes a titan!
  Drag their impudent souls to the abyss!)
  
  [THE WARRIORS OF HYPERBOREA:]\\
  (Havoc is the cry! Come, fiends of the nether-void\ldots{}\\
  face righteous pattern-welded death!)
  
  [LORD ANGSAAR:]\\
  Abominations rise! \\
  Souls to the abyss! 
  
  [THE WARRIORS OF HYPERBOREA:]\\
  Havoc is the cry! \\
  Pattern-welded death! 
  
  [LORD ANGSAAR:]\\
  (Praise Chaos! By the crystal heart of Mera I shall stand deified!)
  
  [THE WARRIORS OF HYPERBOREA:]\\
  (Glory eternal! For our King and sacred Hyperborea!)
}

\Thanatzil{} is consumed by hatred: 
All he wanted was to help his people. 
And they stab him in the back! 

\lyricsbs{Hate Eternal}{Saturated in Dejection}{
  I now become my saving grace, \\
  exiling all this human waste.\\
  I deny your emotions, you perjurers. \\
  I deny your falsifications, you perjurers.
}

\Thanatzil{} grows more and more manic. 

\lyricsbalsagoth{
    The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire 
    - Part III: 
    Cry Havoc for Glory, and the Annihilation of the Titans of Chaos
}{
[ANGSAAR:]
  (The circle closes\ldots{} you cannot resist the unparalleled might of Chaos 
  and the exquisite majesty of the Z'xulth! I shall unleash all the terrors of 
  the Outer Darkness against thee! Behold the true extent of my power\ldots{}) 
  
  My flesh is a shrine wherein all demons dwell!
  
  Bae'an, Zurra, Uldorr, Neoloth. \\
  E'manh, Phaegus, Nyaszar, Merlech.
}





\subsubsection{Survivors sucked into \Nyx}
\target{Semiza fails}
\target{Thanatzil fails}
\Thanatzil{} never got resurrected, so he died permanently. 
And worse, since \hr{Thanatzil is the gate}{\Thanatzil{} was the gate}, this meant that the portal to \Nyx{} was closed and \Daggerrain{} was once again shut out. 

At the last minute, \Daggerrain{} realized what was happening. 
He acted swiftly, while there was still a tenuous conduit from \Erebos/\Nyx{} to \Tembrae{} (the conduit which \ps{\Thanatzil} death had opened). 
He seized some of the threads of the \hr{Shroud of Girigor}{Shroud of \Numah} and used them to create a pocket of Realm-stuff.
He wrapped this pocket around the surviving mothers and soldiers as well as \Semiza{} and \Eshayzal. 
He tossed this pocket into \Nyx{}. 
With the Shrouding they were now invisible and hidden from \Vexstrasshin{} and her ilk. 

\Daggerrain{} also laid out a smokescreen in the form of a plausible-looking implosion that destroyed the temple and laid waste to much of the city. 
That way it looked as if everyone was dead and the plan thwarted. 





\subsubsection{\Vexstrasshin{} dies}
\target{Vexstrasshin dies}
\Vexstrasshin{} is killed by \ps{\Daggerrain} treachery, so she cannot go out and tell the tale of what happened here. 
During the death-and-resurrection ritual, while the portal is open, \Daggerrain{} reaches through with as much power as he can muster and attacks \Vexstrasshin. 
She is unprepared for the power of this attack. 
She fights back with all her might and wiles, but \Daggerrain{} is too powerful. 
He slays her and destroys her soul. 















\section{Aftermath}









\subsection{\Morza}
\target{Morza rescues survivors}
\hr{Morza}{\Morza} was a \nephil soldier in \Numah.

He was one of the soldiers charged with protecting the mothers of the \resphain.
When disaster struck and \Thanatzil failed, he took command and led the mothers and the other survivors to safety.

He led them to a promised land in \Nyx.

They found some passages in their traditional religious scripture, combined with \Semiza's new bane religion, which foretold that this would happen.
He became their chieftain.
For thousands of years after his death, \Morza would be revered as a great hero.
Compare him to Moses and other leaders from the Hebrew Bible.

\Morza was no great champion or hero. 
He was a regular soldier, a \quo{little guy} who stood up and did what he had to when there was no one else to do it. 









\subsection{Rebels celebrate}
The \nephilic{} rebels were happy.
They had lost much: 
Several heroes, their mentor \Vexstrasshin{}, tons of innocent lives and much of their city. 

But the evil plan had been stopped. 
They had saved the world, they thought. 

And the destruction was not so bad. 
They had seen its like before at the hands of the \dragons. 
They knew how to cope with it and rebuild. 









\subsection{\Humans}
Plenty of \humans{} were born by this time. 
They were still children, and many died, but enough survived. 
\hr{Humans are fertile}{\Humans{} are fertile}, more so than the \nephilim, so they bred and multiplied quickly. 
They could interbreed with \nephilim, but the \human{} genes were dominant, so they spread even more quickly. 

The \dragons{} wondered a bit when they noticed this new race of pygmy \nephilim{} that appeared seemingly overnight. 
But they paid it little heed.





\subsubsection{\Morza saves some \humans}
\Morza saved several \human children. 
(The oldest \humans were as much as six years old at this time.)





\subsubsection{\Scathae and \humans hate each other}
\target{Scathae and Humans hate each other at first}
When the first \scatha meets a \human: 
Show the \scatha's revulsion at the sight of this ghastly, grotesque, naked\ldots{} thing. 
Compare the \human to a naked mole rat. 

\Scathae tended to see mammals as disease-ridden vermin in the first place, and this naked mammal that stood upright and tried to mimic (\quo{ape}) the \scathaese form was horrid to behold. 
Besides, the \scatha could feel the Cosmic Horror of the \pps{\banes} influence on the \human. 

It would take centuries for the two races to become fully accustomed to each other and not feel this Cosmic Horror revulsion anymore. 

See also the section about \hr{Anti-Scatha racism}{anti-\scatha racism}. 









\subsection{Survivors in \Nyx}
Many of the mothers and soldiers died, but enough survived and were tossed into \Nyx. 
They found themselves stranded in a strange and inhospitable world. 
They had no idea how to get back to their own world, so they could only do their best to fend for themselves and survive in this new, frightening world of towering spires and bottomless abysses. 





\subsubsection{The Shroud of \Nyx}
\target{Shroud of Nyx}
\Daggerrain{} recycled threads and techniques from the \hr{Shroud of Girigor}{Shroud of \Numah} and wove another Shroud around the part of \Nyx{} where the survivors had landed, thus shielding them from prying \draconian{} eyes. 
But \Daggerrain{} had little time to do this, since he was rapidly losing his conduit, so he could only manage a shoddy hack-job. 

The Shroud worked, but with side-effects: 
It harmed the mind, causing confusion and amnesia. 
So the poor surviving \nephilim{} could not remember all that had happened. 
That was one of the reasons why \Merkyrah{} ended up inventing \hr{Merkyran myths}{so many false myths}. 










\subsection[Semiza]{\Semiza}
\target{Semiza flung away}
\target{Semiza entombed}





\subsubsection{Flees into crypt}
\Semiza{} and some of his cohorts (including \Eshayzal) survived and remembered, but they were imprisoned, buried alive when his temple/palace collapsed around him. 

\Daggerrain{} realized that \Semiza{} could still be useful. 
So when the nascent \resphain{} were sucked away into \Nyx{}, \Daggerrain{} made sure to keep a protective hand over \Semiza so he would not die but escape safely. 

When everything collapsed, \Semiza fled with some servants. 
He found the entrance to the underground crypts and ran inside before he was crushed.
From here, he made his way to the burial chambers where the mummies of his ancestors were kept. 

At this time, \Semiza was an old man. 
He hoped to live forever as \Daggerrain promised him, but some doubt and some belief in his ancestral religion remained in him. 
So he had made his servants prepare a tomb for him just in case. 





\subsubsection{Realizes all is not lost}
At first \Semiza{} thought everything was lost and that he was going to die. 
He cursed and raged at everyone: 
The \dragons, the rebels, the \banes. 
But when the catastrophe was over, \Daggerrain contacted him.
He told \Semiza that all was not lost. 
He instructed \Semiza to have himself entombed. 
\Semiza still had a part to play in \ps{Daggerrain} master plan, but he would have to wait, perhaps centuries or millennia. 

\Semiza despaired at this suggestion, but he knew there was nothing to be done, so he instructed his servants to entomb him. 

\begin{prose}
  \tho{\ps{\Daggerrain} power is not broken.
    Our covenant still holds. 
    He promised me immortality. 
    He promised me that I would live to see the \dragons{} destroyed, and then I would rule. 
    He is staying true to his word. 
    I will not die.}
\end{prose}

Gradually he became aware of other feelings. 
He could dimly feel the \resphain. 
He had a link to them since they were all his descendants. 
He could tell they still lived. 





\subsubsection{Thinks of the future}
At the very end of the book, \Semiza{} lay thinking: 
\begin{prose}
  \tho{We have lost much, but not everything. 
    Some of the seeds we have planted have taken root.
    Brave Ilu. 
    Brave \Thanatzil. 
    Your sacrifices were not in vain. 
    
    The \resphain{} live!}
\end{prose}


There he lay for millennia while his body wasted away.
Unable to move but immortal, and descending further into madness. 
He could still feel the faint, cold hand of \Daggerrain{}, channelling power into him and keeping him alive. 
As \Daggerrain{} promised, he gained immortality (by sucking energy from the Heart through \Nyx, and maybe a bit from \Erebos). 
But he lay a thousand years under the earth, eating mud and worms. 





\subsubsection{Helped the \resphain}
\target{Semiza helps fugitives establish themselves in Nyx}
\Semiza still retained his mental powers.
As a necromancer, he had great skill and experience in the art of sending his mind out to wander the spirit worlds.
So he was able to maintain some limited contact with \Daggerrain and with the \resphain.

In the beginning, \Semiza was able to help the fugitive \nephilim and the fledgling \resphain and \humans using his magic.
He helped them get established in the hostile world of \Nyx. 
But after some decades, \Semiza exhausted his reserves of energy.
He had no way to replenish his energy.
So he had to go dormant.

His descendants were on their own now.
But he had given them a start. 





\subsubsection{Freedom}
\Semiza remained in his tomb for over a thousand years, until \hr{Explorers meet Semiza}{\Damiarch-tachi found his now-undead remains} and freed him.























