
\part{Sentinels of \Miith}























\chapter{\CarzainPrequelBook}
This book tells Carzain's back story, before he joined the Runger War. 
It details Carzain's travels, Vizicar's awakening and their joint path to \kenosis. 















\section{Overview}















\section{The Mutiny}
\target{Mutiny}
\target{Mutiny chapter}
Carzain and Nishain were betrayed by mercenaries in Heropond Forest. 
Vizicar awakened (for the first time in Carzain's life) and fought, killing the mutineers. 









\subsection{Old description}
Carzain goes to Martinum with his father. Then back.

It is only autumn as they travel through Heropond, but in the \Wylde it feels almost like winter: Hoarfrost lies on the ground, and cold mist fills the air.

The younger trees hate them and want the intruders out of their forest. Carzain finds an older tree that is indifferent, cold, uncaring\dash it knows that the humanoids will die soon enough anyway. 

(To what extent can Carzain read the thoughts of trees? Much of it is probably just guessing based on vague emotional impressions.)

He also sees the \hr{Moons}{moons} in the forest. They look spectral and spooky. Have some Bal-Sagoth-esque imagery about them.






\subsubsection{Carzain dreams of being nothing}
On the way back to \hr{Redglen}{\Redglen}, Carzain dreams \hr{Ramiel is nothing}{his recurrent nightmare of being nothing}. 

He sees visions of humongous gods: 
\Human-like, \dragons, amoebae with pseudopods\ldots{}





\subsubsection{Betrayed by mercenaries}
On the way back to \hr{Redglen}{\Redglen}, their hired guards mutiny against them. Carzain fights back using magic and suddenly feels a strange ecstasy, a possession. He fights with power he did not know he had and slays the thugs. He is puzzled by the possession experience. 

The magic should be more bloody. I should show how the skin blackens and seethes, let people scream their agony while they boil and burn. They get cramps and spasms and perform a sickly, morbid \quo{dance} before they die from being zapped. 

Maybe fire magic should cause the victim to burn up \emph{from the inside}, instead of just tossing fireballs. Or perhaps tossing fireballs is the beginner's tactic: Easier and cheaper, but less powerful and less accurate. Causing your victim to combust from within is harder, but much more deadly and accurate. It uses the victim's own life force as fuel, burning him to ashes. 

Describe how blisters boil and burst. 





\subsubsection{The Redcor discover the \vertexspike}
A Redcor \matron\dash\Esmerel?\dash is sitting in the Topaz \Chateau, performing divination though \index{aquamancy}. Insert some Bal-Sagoth imagery here. 

\lyricsbs{Bal-Sagoth}{A Black Moon Broods Over Lemuria}{
  And in the dark ethereal mists of winter dreams,\\
  the ebon waters of enlightenment gleam 'neath the Black Moon,\\
  and the Valley of Silent Paths beckons\ldots{}
}

She discovers the \vertexspike{} that is caused by Vizicar's brief awakening, and realizes something has happened. I am not sure how much the Redcor know about \vertices, but she definitely knows something is up. She goes into research, and eventually they determine that very likely a Scion has awakened. 

\Esmerel{} goes off to wander the lands of \Velcad{} in search of the Scion. A year or so later she finds him, in the midst of the Pelidor-Runger war\ldots{}






\subsection{Changes}
The mercenaries have guns (pistols or muskets).

Maybe I should edit the date. 

Carzain and Nishain have not been to the Imetrium, merely some big port city in southern \Scyrum. 
They do not know so much Imetric. 
Nishain only knows a few rudiments, and Carzain none at all. 

When Vizicar fights, he ignores the \hr{Itzach pain}{pain that \Itzach{} brings}. 
\Itzach{} Vaimons have ways of using power economically, thus minimizing the pain and risk. 
Vizicar does not care about this. 
He is groggy and sleepy and his senses are dulled, so he thinks he is completely fresh and healthy and has plenty of bodily energy to spare. 
He does not want to be careful and conservative. 
He wants to be flamboyant and teach these damned peasants a lesson. 

After all, he is \VaimonCaliph. 
He is used to being one of the most powerful and skilled Vaimons in the \caliphate, and a Scion to boot. 
He does not stop to consider that he is out-of-touch with his body, or that his new body is weaker and less trained than his old one. 

Remember to have references to the \hr{Shechinah}{\shechinah}. 

After the battle, Carzain has nasty open wounds caused by drawing too much \qliphah{} power. 
He uses these heroic wounds to score Mirai. 
Then he gets healed by Imetric healers. 

The chapters with \ChyrieEsmerel{} and \LocarPsyrex{} do not happen at all. 
Get rid of them. 
At this point in time, no one knows about the \vertex. 
If they did, that would just cause all sorts of trouble and plot holes. 















\section{Ilcas Northstar}
\target{Ilcas Northstar chapter}
\target{Ilcas introduction}
Carzain and Nishain met Ilcas Northstar in \Bryndwin. 









\subsection{Old description}
Carzain and Nishain go back out of Heropond forest to the town of \Bryndwin.

\Bryndwin has its share of monuments (see section \ref{Monuments}): Poles with flags and lamps on them, carved images of gods, heroes and creatures, meant to scare the \Wylde and intruders away.

They encounter \hs{Telcastora Ilcas}, his two \nycans, Razor and Countess, and a bunch of other Imetrians. 

Remember to describe \hs{Telcastora Ilcas's appearance}.

They see a big \hr{Mulgron}{\mulgron}. Carzain is impressed by how the \mulgron is even bigger than an elephant. 

Remember to \hr{Nycans are frightening}{describe the \nycans as frightening and alien}.

Carzain reaches out his hand and tries to touch Razor's snout. Razor's eyes narrow slighty, and he retracts the hand. 

The two Vaimons hitch a ride back to \Redglen with Telcastora Ilcas and his Imetrians. Carzain befriends Ilcas and his \nycans, Razor and Countess. 

They part ways somewhere in Pelidor. 

Carzain has a wound from his battle with the thugs, but he suppresses the pain, as he doesn't want to show weakness in front on Telcastora Ilcas. I should try to portray him as somewhat over-proud and silly. 

During the trip back, he is treated by an Imetric healer-surgeon. But he retains the scars: One in his leg, one in the side of his stomach. 
The surgeon's treatment is more bloody than the Iquinian healing he is used to, but it is at least as effective. The Imetrians have a scientific approach to medicine, whereas the Redcor repress real science in favour of traditional mysticism. 
This makes Carzain doubt the value of Vaimon tradition.









\subsection{Changes}
Write about Carzain's meditation. 

Replace \quo{resonance} by \quo{\shechinah}.
Add \quo{\shechinah} to the glossary. 

\Bryndwin has a \hr{Wylde border}{\Wylde border} with charms and totem poles. 

Carzain introduces himself to Ilcas: 
\ta{I am \VizicarDurasRespina.} 

Ilcas carries a gun. 

When negotiating with the priest: 
Carzain has no interest in theology, but he is skilled at faking interest, if he does say so himself. 
It is a skill he has honed when picking up women. 

On their first day on the caravan, Carzain talks to Ilcas. 
Ilcas tells stories of his heroic and violent deeds, and of his heroic and violent sword. 
He especially tells of how he has fought against the Imetrium's arch-nemeses, the Rissitics. 
\hr{Rissitics and Runger}{This is important. The Rissitics are important to the story.} 
Make sure to paint the Rissitics as threatening and imposing foes.
Tell of how they wear animal masks and have warrior orders named Order of the \hr{Order of the Crocodile}{Crocodile} and Jackal and Scorpion and \hr{Order of the Hippopotamus}{Hippopotamus} and so on. 

These associations of war makes Carzain see visions of his past, but still very vague, little more than regular daydreams. 

Then Carzain asks to hold the sword. 
Ilcas refuses. 
But he shows him the sword and swings it around a bit himself. 
And tells him about it. 

Carzain scores Mirai faster (already on the first night) and more solidly. 
I need to show the reader how cool he is. 
He pulls off a pick-up comparable to the way Tony Stark scores the reporter girl in the movie \cite{Movie:IronMan}: 
\ta{I'd be willing to lose a few hours of sleep with you.}
She is impressed already after their very first meeting. 

Have more Vizicar in the sex scene with Mirai. 
And after it. 
He talks to Carzain in his head. 
Perhaps from Vizicar's POV. 

The night after sex, he lies awake thinking wildly about what in all of \Iquin and \Itzach is happening to him. 
When he falls asleep, he meets Vizicar in dreams. 

\target{Vizicar drives Carzain to war}
After this night, Vizicar drifts away. 
Carzain feels lost. 
Like something is missing inside him. 
Some important clue in some important mystery. 
Some part of himself. 
He feels like half a man. 

Carzain goes off to war hoping to find Vizicar again.  
He seeks out battle in the hope of provoking more Vizicar action in his head, so he can figure out who Vizicar is and what the deal is. 
Maybe Vizicar subconsciously imparts in him a desire to fight and seek glory. 
















\section{Visions and dreams}
Carzain had visions and dreams. 
As did Vizicar. 

They met in dreams and talked to one another, but neither understood what was going on. 
Both thought the other man was a figment of their own imagination. 

The dreams were triggered by combat and war, or the expectation of it. 









\subsection{Vizicar's motivation}
Vizicar knew he is more than a \human, and he told Carzain this. 
Vizicar wanted to attain \kenosis and regain his body, power and memory. 
Then he wanted to achieve \apotheosis and learn his true nature.
Then he would be a god.












\section{Carzain in the War}
\target{Carzain joins the army}
Pelidor went to war against Beirod. 
A trivial border dispute, but bloody enough. 

At this point, Carzain knew there was something odd going on with him. 
Carzain joined the army because he hoped it would help him find out what was happening to him, who he was and who Vizicar was. 
He could hear Vizicar stirring in his head at the prospect of war and glory: 

\begin{prose}
  \tho{I thought so. 
    It is this sort of thing that brings you out.
    \quo{Vizicar}.
    Whoever you are.
    I will find out what the deal is with you.
    And how I can get rid of you.}
\end{prose}







\subsection{War is Coming}







\subsubsection{Carzain joins the army}
News of the impending war with Runger reaches \Redglen. 

Carzain's parents hate war. Perhaps they have even done stuff to get him to dodge the draft - without his knowledge. Any any rate, Carzain goes to the barracks and signs up. See, Carzain is bored as fuck. He's a big boy in a small town. He has a craving for greatness, fame and power - things he cannot possibly find in \Redglen. He wants to explore and wants something to happen. So he goes off to war. At this point, Carzain is maybe 22. 

In the Pelidorian army, Carzain is welcomed because of his magical knowledge. Pelidor has few mages, since neither the Imetrium nor the Iquinian church support them. He is assigned to serve under Captain Archibald Curwen, the commander of the \ishrah of the Pelidorian army.  
Carzain also learns a lot of combat technique. As he studies combat, he finds all sorts of things coming naturally to him, as if he already knows them but has just forgotten he knew. 

On the way to \Malcur, Carzain calls dibs on a horse\dash a gray stallion named Arrow\dash rather than a \relc. Later, having trouble riding the beast, he ponders his decision. Seeing some of the others getting easily ahead on their \relcs, he realizes that a horse is not necessarily better. It is just that horses are more Vaimon-like. In stories, Vaimons always ride horses, so when he pictures himself in his head as a great Vaimon hero, he sees himself astride a horse, not a \relc or other reptile. Carzain realizes that he is a status-fixated snob. 





\subsubsection{Carzain and the Goldsmiths}
He talks to the Goldsmith brothers. 
He talks of how he is destined for greatness. 
At this point he remembers \hr{Ramiel dreams of being nothing}{his recurring nightmare of being nothing}, and he tries desperately to convince himself that he is not nothing. 
He tells himself that he is big and important, because he fears that dream. 









\subsection[To Malcur]{To \Malcur}
Carzain \travelled to \Malcur to join the Pelidorian \ishrah.

On the way he met Adrian Testor. 

In \Malcur he met Archibald Curwen. 

Have plenty of Vizicar scenes early on, including before, during and after his signing-up to the army. 
(If \quo{The Mutiny} and \quo{Ilcas Northstar} are kept in \TwilightAngelRememberEmph, then include lots of Vizicar scenes there. Otherwise move them to the prequel story about Carzain.)

Vizicar (when he gained some \kenosis) liked the life of an adventurer. 
It was a refreshing change of pace from the court life he was used to, full of responsibility and chains. 
This was a new kind of freedom, and Vizicar loved it. 





\subsubsection[Carzain meets Delph and Tsekkect]{Carzain meets Delph and \Tsekkect}
\target{Carzain meets Delph}
Carzain meets \hs{Delph} and \hr{Tsekkect}{\Tsekkect}.

They are cheerful guys. 
They befriend Carzain and show him around the barracks, where, among other things, Delph utters his classic line: 
\ta{Life in the army is great. We get food, money, a shot at glory, and the best pussy that money can buy. Well\ldots{} the best pussy that \emph{our} money can buy, anyway.} 

To which Carzain replies: 
\ta{And all they ask in return is that we fight to the death.}






\subsubsection{Carzain's idealism}
At the beginning of the story, \hr{Carzain's idealism}{Carzain is quite idealistic}.





\subsubsection{Vizicar awakens a little bit}
At some time at the beginning of the war, before Carzain's first battle in the army, Vizicar surfaces a little bit. 









\subsection{To battle}
They go to battle the enemy. 





\subsubsection{Carzain and Delph practice with swords}
Carzain and Delph practice their swordsmanship. 

When the two duel, Carzain mostly loses. He knows some technique, taught to him by Sir Guy in \Redglen, and he is taller, which gives him a better reach. But the shorter and cruder Delph is faster and more agile, and he fights dirty. 

Carzain: \ta{You fight dirty, you know that?}

Delph: 
\ta{No, I just fight like a \meccaran. 
  That attitude of yours is just \human{} provincialism.}





\subsubsection{Carzain won't smoke}
Carzain hangs out with some soldiers. The others smoke some kind of strong drug, like hash or marijuana. 

\begin{prose}
  Soldier: \ta{Come on, \Shireyo, get over here and smoke.}
  
  Carzain: \ta{No, I don't touch that. It's filth.}
  
  Soldier: \ta{Why do you say that?}
  
  Carzain: 
    \tho{%
      Why \emph{do} I say that? 
      Because my father told me so, but I am not going to tell them that. Think, Carzain, think! 
      I can't lose face in front of these guys. 
      Say something witty.} 
    \ta{Something witty.} 
    \tho{Phew. Nicely salvaged, Carzain.}
\end{prose}





\subsubsection{Curwen and Carzain eat}
The officers of the Pelidorian army are eating a luxurious meal. This includes the \ishrah. 

Curwen: \ta{Ah, by \nieur, I love food.}

Carzain: \ta{Food is good, but I like sex better.}

Curwen: \ta{Meh. Most women cook better than they fuck.}

Both: \ta{LOL.}









\subsection{The \Caliph Inviolate}
The sortie encounters a small Rungeran force. They fight. 

Carzain fights and kills. 
But he is not as great a warrior as he fancies himself. 
So he gets clobbered and takes wounds. 

He calls out to Curwen-tachi for help. 
They save his ass. 

Then Vizicar awakens. 
It's due to a combination of factors: 

\begin{itemize}
  \item The pure rush of combat. 
  \item The anger and shame over being defeated in combat by such lowly grunts. 
  \item The wounds leave Carzain's own conscious mind weakened, making it easier for Vizicar to take over. 
\end{itemize}


% Recall that Carzain is a Scion, an incarnation of the \Malach{} Ramiel. 
% Occasionally, when he fights and kills, Ramiel awakens in him, and he hears the voice of \VizicarFull, the previous incarnation of Ramiel. (This is inspired by, and similar to, how Rand al'Thor in Wheel of Time hears the voice of Lews Therin Telamon. But where Lews Therin is mad, annoying and even dangerous, Vizicar is sane and a powerful ally.) 

% Anyway, Carzain fights and kills, and Vizicar comes along and takes over. 

Curwen immediately senses something fishy, probably a \vertexspike{}. 

This time there is a struggle between Carzain and Vizicar, as Carzain tries to get back in control of his own body. 

%After the battle, Carzain falls unconscious as Vizicar retreats. The prolonged, unaccustomed possession and the struggle between the two personas was too much for his consciousness to take. 

After the battle Curwen probes, prodding Carzain into telling him stuff. Carzain tells a little of what he knows, but it's not much. 

Carzain's body is in a bad shape. 
Vizicar is a harsh master and takes poor care of it. 
This is because Vizicar is only half-awake. 
He's still in a half-dreamy state, and his senses are weakened. 
He doesn't entirely register the pain, so he just pushes on. 
So after the fight Carzain is a useless wreck, barely conscious. 

Maybe Carzain asks the others: \ta{Did I save the da?} 

The others: 
\tho{Save the day? You crazy fuck, you nearly killed yourself, and maybe us, too.} 
\ta{Um, yeah. Sure. You saved the day.}

Delph is scared by Carzain's weirdness. Maybe insert an inner monologue with Delph about how Carzain is a crazy weirdo: 
\tho{Typically. 
     Finally I meet a guy who seems trustworthy, who might become a true friend, and turns out he is a madman. 
     Or possessed by \mdaemons{}, or whatever. 
     Huh. 
     That'll teach me to trust a sorcerer.}

During the fight, Carzan does something stupid and reckless. 
Perhaps he sees an enemy Vaimon and goes in to capture his sabre. 
Afterwards, Curwen bitchslaps him and scolds him: 
\ta{You crazy fuck, \Shireyo!
    What the fuck were you trying to do?
    You very nearly got yourself and the rest of us killed!}
He grabs Carzain by the collar. 
\ta{Let me tell you something, boy.
    Your insubordination stopped being charming a long time ago. 
    Now either you get in line or I'll have you beaten!}





\subsubsection{Vizicar dreams}
Have another scene that describes the battle from Vizicar's point of view. 










\subsection{Dark Crypts of the Mind}
Now that Vizicar is closer to the surface, Carzain begins to \hr{Ramiel dreams}{share his visions and nightmares}. 

He is haunted by the tortured, hateful faces of shackled ghosts. They show him their world: Cold, cruel, dreadful. They hate him and desire to drag him down into their prison\dash groping for him with their clammy, hideous hands. 

He awakens full of terror, and also a tinge of guilt. He has a feeling that he is somehow responsible for their torment. 

He also has vague dreams of lost greatness\dash \hr{Visualizing a matrix}{unconsciously visualizing} the \hr{Mystraacht Matrix}{\Mystraacht{} \matrix}. Feelings of having been betrayed, having lost his power and his memory, upon which his enemies descended upon his weakened self like vultures, usurping his rightful place and \honour and forcing him into flight and hiding. 
%, having his rightful place, power and \honour usurped

When he wakes he thinks about the whole thing. 
Part of him is horrified at the madness that is consuming him. 
But another part is excited. 
Because the possession brings \emph{power}. 
And a feeling of being destined for greatness and glory. 
This is what he has always dreamt of. 

But he has doubts. 
Maybe these feelings are fake. 
Maybe the possessing \Archon{} is brainwashing him, all the while making him feel like it is the right thing to do. 
Maybe he is being mentally deceived. 

But it still feels good. 

He thinks of the legend of \hr{Lestor}{Lestor \Delaen}. 
He dealt with \qliphoth{} despite everyone's advice. 
It was dangerous. 
He became a dark and controversial figure, but also a hero who achieved great things. 





\subsubsection{Carzain thinks more on his madness}
Part of him is horrified at the madness that is consuming him. 
But another part is excited. 
Because the possession brings \emph{power}. 
And a feeling of being destined for greatness and glory. 
This is what he has always dreamt of. 

But he has doubts. 
Maybe these feelings are fake. 
Maybe the possessing \Archon{} is brainwashing him, all the while making him feel like it is the right thing to do. 
Maybe he is being mentally deceived. 

But it still feels good. 

He thinks of the legend of \hr{Lestor}{Lestor \Delaen}. 
He dealt with \qliphoth{} despite everyone's advice. 
It was dangerous. 
He became a dark and controversial figure, but also a hero who achieved great things. 

Maybe move this to \quo{The \Caliph Inviolate}. 





\subsection{Vizicar}
Vizicar fights to gain control of his own body. 

\lyricsbs{Marduk}{Voices From Avignon}{
  Speak through me. Speak through me.\\
  The sin must be washed away with blood.\\
  Dream through me. \\
  Called to a new life through death.\\
  Called to a new life through death.\\
  But what shall you reach for when all \colours fall?\\
  Overwhelmed with maledictions. \\
  Feel the rays of redemption of a brand new Sun.
  
  Choking. Asphyxia. \\
  Inhale the Darkness, lungs filled up. \\
  Asphyxia. Asphyxia. \\
  But who shall you reach for when all \colours fall?\\
  Long-drawn moans and piercing cries \\
  blend with prayers and litanies. \\
  Faces bone dry. Condemned as the river everybody drank of. \\
  Inhale! Inhale!
}

\ta{I will win the power and glory I deserve. 
  Not just as \VaimonCaliph, but higher yet. 
  I am a Scion. 
  I am a \Malach. 
  I will achieve the \apotheosis{} and become one with \Iquin{} and \Itzach.
  That is my purpose as a Scion. 
  
  But first I must gain control of my own body. 
  Right now I live out an ignominious existence as a ghost in a boy's head. 
  I am nothing\ldots{}}

This makes him remember his nightmare of being nothing. 
He drifts away. 

He philosophizes. 

\lyricsbs{Emperor}{Sworn}{
  Four eyes as two in one.\\
  The forward circular view that never ends.\\
  An orbital voyage throughout the endless sphere of all,\\
  where time is lost and everything transcends.
  
  A graceful presence at stolen time
  
  As ghosts to the world.\\
  Ghosts to the world.
  
  For ice, outside, are we apart.\\
  As cold and eerie mist to the hand.\\
  Ever floating on its course\\
  towards the heights of shadowland.\\
  
  Thus appear the truly sworn.
  
  To be seen.\\
  To be feared.\\
  Yet, not to be reached.
}





\subsubsection{Lost in the labyrinth}
He is trapped in the labyrinths of \itzach{}, lost and searching for those precious and ephemeral windows through which he can peer out through Carzain's eyes and affect the world through Carzain's body. 

\lyricsbs{Emperor}{Ensorcelled By Khaos}{
  In an endless maze begotten,\\
  to dead ends led by fools.\\
  I sought a plague for those\\
  who smiled at walls in humble fear.\\
  
  Yet, belligerent ways came to an end.\\
  No war could ease my hunger.\\
  By craving death I was to darkness reborn.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine.
  
  No peace for me. No peace I seek.\\
  My quest goes far beyond.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine.
  
  I hail the greatest fall.\\
  Dark is the spirit of my token.\\
  Dark is my call.
  
  Still craving, still torn.\\
  Hear me, master of this realm\\
  to which I was reborn.
  
  \ta{Bearer of my stigma. Thou art of me.\\
  Yet, claim no gift, but guidance.\\
  For I am the giver of temptation.\\
  Thou art the executor of Thy rewards.}
  
  Dark is the spirit of my token.\\
  Dark is my call.
  
  The cosmic forces driving me,\\
  more noble, more free.
  
  Take me.

  Love and hate and all in between,\\
  I greet them all in ecstasy.\\
  Venus, seduce me.\\
  Mars, possess me.\\
  Tear my soul from sanity.
  
  No sacrifice too great.\\
  Caught in another maze.\\
  Truly endless.\\
  Still this maze is mine and I am thine.
}









\subsection{Reads about Scions and Vizicar}
Maybe Carzain overhears someone (\Esmerel{} and \Racel{}?) talking about Scions. 
Maybe he is half-unconscious and they are standing over him, talking about him, trying to decide his future. 

He asks someone about the story of the Scions. 
Who? 
Perhaps \Racel, but more likely some other mage in the \ishrah. 
Perhaps \Sanyor. 

Anyway, he is told the story of the Scions. Or a version of it. Remember to have many false details, which can be brought into question later. 

Later, he goes into a library in \Forklin{} and reads about \VizicarDurasRespina. 
There isn't a big public library, but there are churches, and they have books. 
He goes into a church, introduces himself as an \ishrah{} mage and pulls a \trope{BavarianFireDrill}{Bavarian Fire Drill}.
He knows he has to use the same body language, frame control and social engineering skills that he masters when picking up women.
It works.
He gets his hands on the writings.

He also finds references to \hr{Vizicar's notes}{Vizicar's notes about \Malachim}, but can find no fragments of the notes themselves. 

He also finds references to \hr{Iolivine's notes}{\ps{\Iolivine} notes}. 
He has heard before that these notes are of exceptionally high quality, but he had been unable to find any copies of them. 
\hr{Redcor bogarted Iolivine's notes}{The Redcor are bogarting the notes}. 
This is one of the reasons he wants to go to \Redce. 

Among other things, he learns that \Belzir{} was an incarnation of an \quo{evil} \malach, and that she caused the \HundredScourges{} with her wicked \malach{} powers. 

More importantly, he learns that he is not mad. 
There are no \qliphoth{} controlling him. 
Instead, he is a Scion! 
He is an \uber-dude! 

He is happy. 









\subsubsection{Carzain reads about Scions}
Carzain is always researching what he is, always looking for more knowledge of Scions. 
He hopes it will lead him to \apotheosis. 

So he goes into a library in \Forclin{} and looks around. 
There isn't a big public library, but there are churches, and they have books. 
He goes into a church, introduces himself as an \ishrah{} mage and pulls a \trope{BavarianFireDrill}{Bavarian Fire Drill}.
He knows he has to use the same body language, frame control and social engineering skills that he masters when picking up women.
It works.
He gets his hands on the writings.

He also finds references to \hr{Vizicar's notes}{Vizicar's notes about \Malachim}, but can find no fragments of the notes themselves. 

He also finds references to \hr{Iolivine's notes}{\ps{\Iolivine} notes}. 
He has heard before that these notes are of exceptionally high quality, but he had been unable to find any copies of them. 
\hr{Redcor bogarted Iolivine's notes}{The Redcor are bogarting the notes}. 
This is one of the reasons he wants to go to \Redce. 

Among other things, he finds references to \Belzir. 
He already knows she was a Scion, allegedly an incarnation of an \quo{evil} \malach, and that she caused the \HundredScourges with her wicked \malach powers. 









\subsection{Why are you in my head?}
Somewhere along the way, Carzain-tachi get into a fight. Vizicar awakens. This time, after the battle Carzain falls unconscious. He dreams and meets Vizicar. 

He sees before his eyes a man who looks to be perhaps his father's age. 
But still strangely similar to himself. 
His complexion is much lighter, though. 
His long hair is blonde rather than black, and he wears a matching moustache. 

Carzain: \ta{Who are you?}

Vizicar: 
\vizicar{%
  Who am I? How can you not know who I am? I am \VizicarDurasRespina! The \caliph!}

Carzain: 
\tho{%
  \quo{\Caliph}\ldots{} is he the reason why that word has been popping up in my head?} 
(Maybe he doesn't think this until after he awakens from the dream-conversation.)

Carzain: \ta{Why are you in my head?}

Vizicar: \vizicar{Why are you in \emph{my} head?}

Carzain: \ta{I was here first.}

Vizicar: 
\vizicar{%
  Unless\ldots{} oh, \qliphoth\ldots{} unless I\ldots{} oh, by \iquin{} and \nieur. I must be dead.

  Yes, I remember now. Those vile worms killed me. \quo{Disease}, they called it. Hah!}

Carzain: 
\tho{%
  Fuck. 
  Not only is there a madman in my head, but now the madman is talking to himself!}

Carzain wonders what the deal is. 
How does this fit with the theory that it was the Midnight \Qliphoth{} that took control of him? 

Later, Vizicar apologizes Carzain for putting him through Hell by his own recklessness, by ignoring the \hr{Itzach pain}{pain of \itzach}. 
Vizicar admits that he has been crazy and has fucked their body up. 









\subsection{Changes}
\begin{changes}
    
  \begin{comment}
  \paragraph{War is Coming}
  \end{comment}
  \changesitem{War is Coming}
    Remember to have references to the \hr{Shechinah}{\shechinah} in Nishain's speculations. 
    
    Rewrite the \quo{I want to fight} section from the officer's POV. 
    
    Mention Carzain's age (\quo{a young man, around 25\ldots{}}). 
    
    Make sure the soldiers notice that Carzain is a bit swarthy (being half Geican). 
    
    This might be the place where Carzain introduces himself:
    \ta{I am \VizicarDurasRespina. No! Wait\ldots{} I am Carzain \Shireyo\ldots{}}

  \begin{comment}
  \paragraph{To \Malcur}
  \end{comment}
  \changesitem{To \Malcur}
    Rewrite the scene where Curwen and Carzain meet, so it is from Curwen's POV. 
    
    Curwen should be smoking his pipe. 
    
    Mention Carzain's age (\quo{a young man, around 25\ldots{}}). 
    
    This might be the place where Carzain introduces himself:
    \ta{I am \VizicarDurasRespina. No! Wait\ldots{} I am Carzain \Shireyo\ldots{}}
  
  \begin{comment}\paragraph{\Forklin}\end{comment}
  \changesitem{\Forklin} 
    Get rid of \Racel. 
    
    Carzain is \hr{Carzain PUA}{a great PUA}. 
    He \emph{does} score in \Forklin.  
  
  \begin{comment}
  \paragraph{The \Caliph Inviolate}
  \end{comment}
  \changesitem{The \Caliph Inviolate}
    Again, Vizicar ignores the \hr{Itzach pain}{pain of \Itzach}, and Carzain gets burnt and wounded as a result. 
    
    Remember the \hr{Itzach pain}{pain of \itzach} when Curwen casts magic. 
    
    Remember to have references to the \hr{Shechinah}{\shechinah}. 
    
    Curwen needs to tell the reader that the \ishrah{} mages are equipped with plate \armour. 
    They just do not wear it when \travelling, nor on stealth missions like this. 
    But when the battle comes, he misses it. 
    
    Maybe Vizicar holds back his power and magic. 
    He does not want to arouse suspicion and get caught. 
  
  \begin{comment}\paragraph{\Tsekkect{} and Delph}\end{comment}
  \changesitem{\Tsekkect{} and Delph} 
    Make sure people like \Tsekkect{} and Delph have inner lives of their own and don't spend all their time gaping at Carzain. 
\end{changes}
















\section{Mercenary}
After this short war ended, Carzain left the army and became a mercenary and adventurer.
























\chapter[Twilight Angel, Remember]{\TwilightAngelRemember}
\target{Twilight Angel, Remember}
\input{Story/Sentinels01Notes} 

























\chapter{\TheKenosis}
\input{Story/Sentinels02Notes}























\chapter{\RamielsAwakeningBook}















\section{Concepts}









\subsection{Ramiel and Hayad}
After Ramiel betrayed \Belzir, Hayad remained his friend. 

But Hayad is Sentinel-allied, and Ramiel goes to join the Cabal. 
How does that work? 

I guess Hayad will die at some point, so Ramiel won't be forced to turn on his friend. 







\subsubsection{The \Bane{} Invasion}
%After defeating \Belzir{}, Carzain fights some Rissitics and some \banes{} sent by Rissit. But eventually, it becomes apparent that the \banes{} have their own agenda. 

After this, Carzain discovers that he and \Belzir{} have been manipulated by the Sentinels. He becomes angry and leaves them. 

Perhaps he travels the world for a while now, fighting for whatever cause catches his fancy. Kind of like Elric of \Melnibone{} in his mercenary years. 

Somehow, he meets the \banes. Perhaps he is taken prisoner by them. They show him how all morality is a lie, how everything in the world revolves around the struggle between \dragons{} and \banes. They convince him that, as a \Malach, he is created by the \banes{} and destined for greatness as a hero on their side. 

At this point, Carzain has encountered several different civilizations and their different moralities, and has found them all lacking\dash{}totalitarian, intolerant and contradictory. He has also read snippets of the Book of Nom, strengthening his growing suspicion that good is futile. He is near to concluding that everyone is a hypocrite, that all morals are false and that the only truth is power. 
After being shown the brutal truth by the \banes, he becomes completely disillusioned and turns to evil completely. (Perhaps it is his already high degree of disillusionment at this point that lets him keep his sanity when confronted with the truth.) 
%Carzain, completely disillusioned, abandons all his former morals and turns to evil completely. 
He abandons the name Carzain \Shireyo{} and becomes Ramiel (his \Malach{} name). 

Later, he learns that the Redcor, or at least some of them, are on the Cabal's side, and that he will have to work with them. He balks until he is reassured that he will not be put under them but beside or above them. 

%The Cabal betrays \Belzir{}, and it turns out that they actually serve the \banes. 

%Late on in the story, Carzain and a party of other heroes go on a quest to destroy some \banes. It comes to a big boss fight, but in the end, one of the heroes betrays the party and turns on them. Carzain dies. %, and the \banes conquer \Velcad{}. 

%The \banes{} conquer \Velcad{}. The Imetrians and Rissitics team up with Irokas to oppose them. I don't know what happens after that. (A nice evil ending might be to have \Tiamat{} awaken and destroy \banes{} and \dragons{} alike\ldots{}) 





\subsubsection{Ramiel's companions}
Maybe Ramiel has a female companion. 
Compare to Mele from \emph{\JuukenSentaiGekiranger}, with Ramiel (of course) being Rio. 

Perhaps he gathers \vorcanths{} and other creatures around him and forms his own \Rinjuuken. 









\subsection{Ramiel's enemies}
\target{Secherdamon wants to off Ramiel}
Ramiel had managed to keep his existence secret from the Sentinels for a while, but no longer. 
After he killed \Shiaraid, he could no longer hide. 

\Secherdamon{} is not happy about this new development. 
He liked \Shiaraid{} because she was so mad. 
She was dangerous to him, true, but he suspected she would be just as dangerous to the Cabal. 
But Ramiel is another matter. 
\Secherdamon{} does not know how \malach-hood and the Curse have affected Ramiel, but he remembers Ramiel as a formidable and competent adversary. 

So \Secherdamon{} decides he wants to off Ramiel. 
Throughout this book, therefore, Ramiel is hounded by Sentinels and Cabalists alike. 

Fortunately, Ramiel has allies: 
\Cishiel, \Azraid{} and the \vorcanths. 





\subsubsection{\Azraid{} helps Ramiel}
\Azraid{} \hr{Azraid protects Carzain}{has his own plans for Ramiel}, so he protects him. 
He also subtly guides Ramiel on his quest and pokes him in the direction of the things he might need to regain his power. 

In this way, \Azraid{} acts as a \trope{StealthMentor}{Stealth Mentor} to Ramiel. 

When Ramiel finally learns of \ps{\Azraid} involvement, he is amused and slightly grateful, but not surprised. 
That is the kind of thing \Azraid{} has always done. 

Later it turns out that \Azraid wants Ramiel to become a \neoresphan (\hr{Ramiel becomes Neo}{which he does}).
From \Azraid's point of view, the whole \malach project \hr{Azraid turns Malachim into Neo}{ties in with his own \neoresphan project}. 





\subsubsection{Heroes chase Ramiel}
\target{Sithiyacaan goes north}
Throughout the book, the \quo{heroes} chase Ramiel all over the world, trying to stop him from achieving his mad goal of becoming a god. 
Compare to how Cloud-tachi chase Sephiroth in \cite{VideoGame:FinalFantasyVII}. 

Telcastora Ilcas is one of these heroes.
\Sithiyacaan is another. 
\Sithiyacaan is still a madman and has most of his powers locked away. 









\subsection{Ramiel goes mad}
Ramiel's sanity is suffering.
Things are happening to his body.
Unbeknownst to him, he is \hr{Ramiel becomes Neo}{slowly mutating into a \neoresphan}. 
He has nightmares and even daymares where he feels his body transforming into something loathsome and unnatural and inhuman. 
He sees into the Beyond, even moves into it, and sees glimpses of his expanded \neoresphan body.
It scares him. 
He fears what is happening to him. 
Part of him is horrified at the though of what will happen if he goes through with his mad plan to become a god. 
Maybe he should turn back and live a quiet life as a normal \human. 

But he goes on. 
He banishes any scruples and fears he has. 
He stubbornly and fanatically continues with his mad quest to become a god, even though his own body and mind beg him to stop. 

This is a part of \quo{\hs{Ramiel's tragedy}}. 
It is a hoax to make the reader think that Ramiel is damned by his own corruption and fanaticism and doomed to fail. 
I hope to surprise the reader when Ramiel conquers and actually becomes a god. 







\subsection{The \Feud}
\target{Resphain are winning the Feud}
From the \Shrouding{} and up until this time, the \feud{} had been pretty much a war of attrition. 
And the \resphain{} were winning. 
Their numbers were dwindling, true, but the \dragons{} were dwindling faster. 
Besides, those \resphain{} who survived were the strongest, \hr{Resphain grow stronger}{and they kept growing stronger}. 







\subsection{To break or preserve the Shroud}
\target{To break or preserve the Shroud}
The \dragons{} originally created the Shroud. They did not care for progress. The \resphain{} \emph{do} care for progress, so they want to get rid of the Shroud. But they are afraid that it will give their \draconic{} foes access to more \xsic{} power, so they will not unravel the Shroud before their \matrix{} has control. 

Both \Daggerrain{} and \Secherdamon{} plan to sunder the Shroud and bring in their forces to lay waste to \Miith{} (see section \ref{Daggerrain's master plan}). For both parties, this is \hr{Summoning the XS: A deadly balance}{a delicate balance}.

Our \quo{heroes}\ldots{} wait, who are our heroes? \Narkiza{} and \Dzasselid? Moro \Cornel? \Cuezcans? Imetrians? \Ophidians? Remnants of the Redcor and Geicans?

Anyway, our heroes initially want to destroy the Shroud and free the people of \Miith{} from its cruel oppression and their imprisonment as witless slaves and defenseless victims, easy prey for all the horrors that lurk in the universe.

But towards the end, it becomes apparent that unravelling the Shroud is not a good idea. It will enable \Daggerrain{} or \Secherdamon{} or both to carry out their plan, and whoever wins that struggle in the end, the consequences for \Miith{}'s inhabitants will be cataclysmic. So the heroes realize that, hateful as it may be, if they wish to protect \Miith{} they will have to fight to preserve the Shroud.

\target{Ishnaruchaefir fights to preserve the Shroud}
\Ishnaruchaefir{} helps them, but only in secret at first. Later he openly declares his opposition to \Secherdamon{} and overtly fights against him. Perhaps he becomes a leader of sorts for the opposition, like Elric in Michael Moorcock's \emph{Stormbringer}.

\Ishnaruchaefir: 
\ta{%
  A balance has reigned over the \Matrices{} of the \Feud{} for thousands of years, but it is slipping. 
  The \banes{} are gaining strength. 
  I cannot have that. 
  There are times when I have held a stalemate preferable to any end to the war. 
  But if any side is to win ascendancy, I want it to be my own people.}

The whole picture of alliances is very chaotic at this point, with factions splintering and turning on each other at the drop of a hat.

Remember to have some sad philosophy about how tragic it is that while the Shroud is a wicked abomination that keeps people down as ignorant slaves and hapless victims of the world around them, the same Shroud is still the world's best defense against all-out invasion and another apocalypse. 
The heroes have to fight to keep the world as a prison. 





\subsubsection{Mortals fight against \iquin}
Some mortals have learned the evil purpose behind \iquin. 
They fight to stop it. 

Describe \hr{How it feels to learn Iquin is evil}{how it feels to learn that your religion is really evil}. 









\subsection{The final purpose of the \Sephiroth}
The \hr{Sephiroth}{\Sephiroth} have \hr{Final purpose of the Sephiroth}{a grand purpose}. 
It ties in with the \hs{Morbus} and the \hr{Purpose of Humanity}{purpose of \humanity}. 







\subsection{\Kezerad}
But the \hr{Kezerad}{\Kezeradi} are a danger to the \Sephirah{} project. They could potentially break the project, because they still have a \hr{Kezeradi telepathy}{deep connection to the \Sephiroth}.

By the end, some \Kezeradi{} have become main characters. Or at least one, namely \hr{Sithiyacaan}{\Sithiyacaan}, the last \Kezeradi{} prince. He and his followers work together with \Ishnaruchaefir{}\dash to some degree at least, although \Ishnaruchaefir{} was never exactly a friend of \Kezerad. 

The Cabal knows that the \Kezeradi{} have the power to fuck up their plan, so they do everything they can to hunt down the survivors.





\subsubsection[Sithiyacan]{\Sithiyacaan}
Introduce \hr{Sithiyacaan}{\Sithiyacaan}, the last \hr{Kezerad}{\Kezeradi} lord. 





\subsubsection{An undercover \Kezeradi}
A long-running \resphan, perhaps \Achsah, turns out to be an undercover \Kezeradi. Perhaps she is half \Kezeradi{} and openly condemned her heritage while secretly sympathizing with her people.









\subsection{Epidemies ravage \Azmith}
Epidemies ravage all of \Azmith, now that the \Iquin/\hr{Morbus}{\Morbus} plan is nearing its culmination. 
Entire countries are depopulated and collapse. 

It is a consequence of the life-drain inflicted by \Iquin, and also a side effect of the growing influence of the \banelords and their Entropy.
Disease is a manifestation of Entropy.

\citebandsong{Nile:AmongstheCatacombsofNephrenKa}{Nile}{
  Pestilence and Iniquity:
}{
  Heralds of Pestilence\\
  Blackest Plague Rusheth through the Land\\
  Burning Evil Winds\\
  Carry Sickness\\
  Invoking the Bitter Venom of the Gods

  Loathsome Sickening Stench of the Defiled\\
  A Cesspool Breeding the Unclean\\
  Hordes of Locusts\\
  Fiends of the South Winds\\
  Cleanse the Earth from the Impure

  The Daemon That Siezeth the Body\\
  The Daemon that Rendeth the Body

  Ruthless and Profane\\
  Lord of all Fevers and Plagues\\
  Grinning Dark Angel of the four Wings\\
  Spawn of Eng\\
  Horned God with rotting Genitalia\\
  Pazuzu
}









\subsection{Cataclysmic events}
\target{Eschaton: RamielsAwakeningBook}
There should be some apocalyptic events before the last book of \SentinelsofMithEmph where much of \Azmith is devastated and the truth of the \xs, \Iquin and perhaps even the \banes is revealed to the mortal masses. 

Hordes of Chaos and/or Darkness invade \Azmith, like in the \emph{Warhammer} game. 

The surviving mortals suffer.
They know their world has been destroyed and they are now living in a Hell on Earth.

See also the general section about the \hs{Eschaton}. 

\citebandsong{Nile:FestivalsofAtonement}{Nile}{
  Extinct
}{
  Paradise Lost\\
  Dreaming of Extinction\\
  We wander through the Walls of Sacrifice\\
  Sick winds brush against my Skin

  Power of Extinction\\
  Growth Intelligence No More\\
  Mud Rot Skeletal Earth\\
  Drown thy spirit of Kings

  Society's walls break Down\\
  \Humans Pound Down\\
  Dig I must dig Out\\
  Surviving puts all tools in Place\\
  Only peace comes in Death

  As I sleep I dream of Death\\
  Only Peace comes in Death
}









\subsection{Armies of the undead}
The Sentinels manage to raise great armies of the undead. 
This is a continuation of what happened during \hr{Mephilex rises to power}{Suthis Mephilex's rise to power in \Yormis}. 
In this context, the servitors of \Thessulax struggle against those of \Secherdamon, for the two have different ideas of how to enact this \quo{zombie apocalypse}. 

The end result is that vast armies of undead\dash mortal and immortal alike, as well as beasts and monsters\dash march across the land.









\subsection{Looming confrontation between Ramiel and \Dasteron}
Throughout the book, the upcoming conflict between Ramiel and \Dasteron looms. 
It is a source of tension. 
Everyone knows it will happen and is waiting for it to erupt. 
Compare to the promised battle between Karsa Orlong and Rhulad in \cite{StevenErikson:ReapersGale}. 














\section{Ramiel's Search}





\subsection{\Vorcanths{} are mad at Ramiel}
The \hr{Vorcanth}{\vorcanths}, previously Ramiel's allies, had grown mad at him. 
They liked \Shiaraid{} and were nonplussed that Ramiel had backstabbed and killed her. 
They demanded he make it up to them and do them some favours before they would help him again. 





\subsection{Ramiel searches moons for answers}
Ramiel searches the moons, hoping to find answers and peace from his inner Chaos (and \hr{Curse}{\NexagglachelsCurse}). 
Especially \hs{Visha}, the moon associated with the \hr{Vorcanth}{\vorcanths}. 

\lyricslimbonicart{Enthralled by the Shrine of Silence}{
  Cold jewel Moon, I found shelter in your shade \\
  as wind and time took me astray. \\
  I'm floating down the river of forgotten names \\
  into a dark and calm water that devours my flame.\\
  There I find rest and glorious peace, \\
  a sanctuary of eternal bliss.
}

\lyricslimbonicart{Seven Doors of Death}{
  Restless days and sleepless nights.\\
  Drawn in the direction of the moon.\\
  Infernal magnet to mysterious destiny,\\
  beyond the grave of doom.
}

He wants to be rid of his frail \human{} body and return to his true form. 

\lyricsbs{Hate Eternal}{I, Monarch}{
  In this being, in flesh, there can be no absolution.\\
  Therefore I must shed my skin, in a world so fabled, so false.\\
  
  In this shell, in flesh, there can be no solitude.\\
  I will not live in this facade, in a world of contradiction.\\
  
  I, Monarch, master of what shall be.\\
  I, Monarch, captor of what I seek.\\
  I, Monarch, victor of all battles.\\
  I, Monarch, sovereign of this domain.
}









\subsection{Ramiel sees through \Iquin}
Ramiel realizes the true nature of \iquin. 
He is himself a \carcer, and his growing self-understanding allows him to understand \iquin{} as well, and see it for the carcer it is. 

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega
}{
  Mass Grave Aesthetics
}{
  The dimension of ethereal totalitarianism discloses itself \\
  And takes possession of the quintessential human soul \\
  Like a nail hammered through most tender flesh \\
  Aeons separate the one \\
  whose eyes have seen through the night of the spirit \\
  The king, the Lord of hosts, draped in terrifying magnificence \\
  From the gleaming clot of trembling vermin
  
  This is you, nourishing \\
  the grand Mass Grave Aesthetics!
}









\subsection{Psychics see portents of the end of the world}
Gradually, as \ps{\Daggerrain}{} master plan unfolds (including the spread of the \hr{Morbus}{\Morbus}), psychics (people who can see through the Shroud) all over \Miith{} see portents of the end of the world: 
Death and emptiness, \hr{Morbus}{disease} and horror, Entropy and torturous decay. 









\subsection{Ramiel and \Ishnaruchaefir}
Ramiel meets \Ishnaruchaefir. 

\begin{prose}
  \Ishnaruchaefir:
  \ta{Ramiel. I hear you destroyed \Shiaraid.}
  (He studies Ramiel's reaction.)
  \ta{You loved her.}
  
  \Ishnaruchaefir{} fingers his glaive.
  He also destroyed his beloved once, remember. 
  A wordless \quo{\trope{NotSoDifferent}{Not So Different}}-conversation passes between them. 
  They go their separate ways with a newfound respect and mutual understanding. 
\end{prose}









\subsection{Ramiel meets \Cishiel}
\target{Ramiel meets Cishiel in person}
Ramiel is re-united with his long-lost daughter, \hr{Cishiel}{\Cishiel}. 
At first he does not recognize her. 
She was a young girl when he last saw her.
Now she has grown into a mature and very powerful \resvil. 

She has searched for him. 
She wants him back and will support his bid for the throne. 
But she also resents him for abandoning her to fend for herself back when she was a defenseless little girl. 

\target{Ramiel regains guns}
She gives him back \hr{Ramiel's guns}{\Strith{} and \Currah}, the two pistols he once used to wield. 









\subsection{Ramiel journeys to \UltimaThule}
\target{Ramiel journeys to Thule}
Ramiel sails north. 
He journeys to \hr{Thule}{\UltimaThule} in the hope of regaining his memory and power. 

\UltimaThule is in a different Realm. 

His goal was a particular lost temple city in \UltimaThule that had once been a sorcerous bastion (of some race), but was now abandoned and ruined.
Perhaps this was even a \voyager citadel.

\lyricsbs{Bal-Sagoth}{%
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  For how long have we \travelled?\\
  The memory grows dim, lost in the cruel, searing storm-winds.\\
  With the blessings of the Elders we began our journey, \\
  beyond the great veil of shadowed glaciers.\\
  They spoke of a prophecy foretold, an ancient and glorious legacy.\\
  A quest for the realm of legendry, \\
  lost to Man since before even the star-lords descended.
}

He gazes out over the vast, black sea and the darkened, stormy sky, dimly lit by a faint, mystic, spectral luminescence, from the clouds or the northern lights. 

Compare to \bandsong{Bal-Sagoth}{Journey to the Isle of Mists (Over the Sunless Depths of Night-Dark Seas)}. 

\lyricsbalsagoth{Invocations Beyond the Outer-World Night}{
  Seeking answers to the cryptic riddles of the universe,\\
  Secrets of the blackest, most impenetrable deeps of the umbra,\\
  Wreathed in frozen shadow and ice-bound peril,\\
  Subterrene halls of horripilated wonderment\ldots{}
  
  Tatsumaki Maru voyage north, ever north!\\
  Cleave a path through the massing Arctic ice!\\
  Agleam with all the \colours of the aurora,\\
  Far beyond Ny Alesund lies our goal.
  
  Wreathed in frozen shadow and ice-bound peril.\\
  Agleam with all the \colours of the aurora.\\
  The portal to the tenebrous cryptic core \\
  of this world's subterrene inner sanctums.\\
  Quaere verum\ldots{} \\
  Sic itur ad astra!
  
  Invocations and ideograms (dreams of the Xytaxehedron?),\\
  Conjuration of the inner world's (tenebrous) denizens,\\
  And their star-spanning progenitors, \\
  spawned beyond the outer-world night.
}

He feels deep inside him that he is nearing enlightenment. 

\lyricslimbonicart{Beneath the Burial Surface}{
  Water from a thousand tears floats in streams.\\
  The feeling from a thousand years flow over me.\\
  As I once again return to the cemetery gate\\
  I hear the dismal call from the hollow grave.
}

They encounter vast, violent storms of ice and snow. 

\citeauthorbook[p.208--209]{TimCurran:Hive}{Tim Curran}{Hive}{
  Hayes could see it out there in that haunted blackness, the headlights clotted with snow thick as a fall of flower petals, thick as the dust blowing through the decayed corridors of a ghost town.
  It was more than just a Condition One storm with near-zero visibility and winds approaching a hundred miles an hour and snow falling by the bails, pushed into frozen crests and waves.
  No, this was bigger than that.
  This was every storm that had ever scraped across the Geomagnetic graveyard of that white, dead continent.
  Pacific typhoons and Atlantic hurricanes, Midwestern tornadoes and oceanic white squalls, tempests and blizzards and violent gales\ldots all of them converging there, bled dry of their force and suction and devastation, reborn at the South Pole in a screaming glacial white-out that was sculpting the rugged landscape in canopies of frost, leeching warmth, driving blood to freon, and pushing anything alive down into a polar tomb, a necropolis of black, cracking ice. 
  
  \ldots 
  
  But there were other things on the storm.
  
  Things funneling and raging in that vortex that you could only feel in your soul, things like pain and insanity and fear.
  Maybe wraiths and ghosts and all those demented minds lost in storms and whirlwinds, creeping things from beyond death or nameless evils that had never been born\ldots the gathered malignancies and earthbound toxins aof that which was \human and that which was not, writhing shadows blown from pole to pole since antiquity.
  Yes, all of that and more, the collected horrors of the race and the sheared veil of the grave, coming together at once, breathing in frost and exhaling blight, a deranged elemental sentience that howled and screeched and cackled in the shrill and broken voices of a million, a million-million lost and tormented souls. 
  
  Hayes was feeling them out there on that moaning storm-wind, enclosing the SnoCat in a frozen winding sheet.
  Death.
  Unseen, unspeakable, and unstoppable, filling its lungs with a savage whiteness and his head with a scratching black madness.
  He kept his eyes fixed on the windshield, what the headlights could show him: snow and wind and night, everything all wrapped and twined together, coming at them and drowning them in darkness.
  He kept blinking his eyes, telling himself he wasn't seeing death out there.
  Wasn't seeing spinning cloven skulls and the blowing ,rent shrouds of deathless cadavers flapping tlike high masts.
  Boiling storms of sightless eyes and ragged cornhusk figures flitting about.
  Couldn't hear them calling his name or scraping at the windows with white skeletal fingers. 
}






\subsection{I know you are in there somewhere}
In a fight or the like, someone tells Ramiel this: 

\begin{prose}
  Someone: 
  \ta{Carzain! I know you are in there somewhere!}
  
  Ramiel: 
  \ta{%
    Oh, no. You have gotten it mixed up. See, it was never Carzain who was \quo{in there}. Back in the day, Carzain was up-front, and I, Ramiel, was \quo{in there} within him.
  
    You cannot break through to the \quo{real me}. 
    I \emph{am} the real me.
    I am as real as I can get.}
\end{prose}







\subsection{A \resvil{} who loves and hates Ramiel}
Ramiel has an admirer and enemy. A \resvil{} who is in love with him to the point of obsession, but also hates him for his evil and his (in her eyes) betrayal of her people. Is she \Mystraacht{} or from another dynasty?

Perhaps I can merge her with Shereid. 

Have some scenes from her perspective, where she is disgusted with her own obsession. 

In the end, he probably kills her. Perhaps she willingly lets him kill her: Stripping naked for him, kneeling down to first suck his dick, and then letting him run his blade through her breast. 

Compare her to Titus Pettifer from Clive Barker's \emph{Jacqueline Ess: Her Will and Testament} (\emph{Books of Blood II} p.81-84). Or the relationship between Elric and Stormbringer in Michael Moorcock's \emph{Elric of \Melnibone} series\dash and maybe the scenes where Elric slays Zarozinia and Moonglum. 















\section{At the Temple}
\subsection{Ramiel reaches the temple}
\target{Ramiel's awakening at the temple}
\target{Ramiel's awakening in the temple}
\target{Ramiel's awakening}
Ramiel reaches the temple, far to the north. 





\subsubsection{First impressions of the temple}
It is a \Mystraacht{} citadel, but built in \ophidian{} style, since \Mystraacht{} has conspired with the \ophidians. 
It is not only a temple, but a cosmic gzateway to the Throne of the \Mystraacht{} Overlord, ensorcelled by \resphan{} and \ophidian{} power alike. 

It is frightening, slime-covered, alien. 
Compare to R'lyeh from \cite{HPLovecraft:TheCallofCthulhu} and other Cthulhu Mythos stories. 
Also compare to \cite[p.22--25]{TanakaHirofumi:TheSecretMemoiroftheMissionary}.

It is full of ancient alien machinery. 
Compare to the Krelran temple in Arellarti in \cite[p.49]{KarlEdwardWagner:Bloodstone}. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Swathed in Moon-frosts, in icy winds our blazon flying.\\
  Iron gleaming 'neath the stars, black skies ablaze with astral fire.\\
  White wolves (like silent spirits) haunt us, ever northwards.\\
  The ice-gem leads us, glimmering.\\
  Powerful spells entwine the shrine of legendry,\\
  mighty gates of frozen splendour looming.\\
  When the moon and stars shine as one upon the snows, \\
  the ancient ice-gate opens, the prophecy is fulfilled!
}

\lyricslimbonicart{Lycanthropic Tales}{
  As the storm looms over the frozen landscape:\\
  A call from the beginning of time,\\
  out of darkness through the mist.
  
  Requiem in blood and fire.\\
  Symbols of occult desire.\\
  Through the cosmic vortex,\\
  the gate to unknown darkness.\\
  An esoteric voyage to eminent discovery.\\
  I am the deathlike shadow,\\
  architect of black mysteries.
}





\subsubsection{They fight their way in}
He and his companions fight their way to the temple, past its terrible guardians. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Towering, ice-encrusted forms lumber forth from the freezing mist,\\
  their eyes shimmering with a fiendish, eldritch malevolance\ldots{}\\
  Our steel is raised against their weapons of gleaming crystal.\\
  And the virgin snow is rendered crimson by bloodshed 
  in a searing storm of slaughter.\\
  Wounded, dying, my flesh rent by weapons no human ever forged or wielded, \\
  I am beckoned forward by a strange, alluring force \\
  from beyond the veil of swirling mists\ldots{}
}





\subsubsection{They explore it}
He explores the mystic temple. 

\lyricslimbonicart{Infernal Phantom Kingdom}{
  After years of dormancy\\
  in a cosmic mausoleum,\\
  arcane cemetery.\\
  The soil is cursed and sour.\\
  A rotten landscape draped in horror.\\
  Evil has a way of returning.\\
  You can not hide from hell's eye.\\
  It is always burning;\\
  a way of returning.
}

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Shadows, images form \\
  in the glittering rune-carved walls of this glacial chamber,\\
  aecrets frozen within the timeless vaults of eternity.\\
  The throne of the time-lost ice realm, \\
  entwined in the mantle of such searing star-born power.\\
  This frozen, aeon-cloaked seat of immortal majesty,\\
  of an empire forged long before the vast seas rose in devouring fury!
}





\subsubsection{Insight comes}
Here he regains some of his memory. 
He remembers his life as a \resphan{} lord. 
He recalls the march of the \Mystraacht{} \hr{Glorious armies}{armies}, the incounterable legions that once forced the world to its knees. 
Back in those days, the \banes{} were weakened and mostly absent after their great defeat in the \secondbanewar{}, so the \resphain{} were left to their own designs, and they fought among one another. 
\Mystraacht{} was the most powerful dynasty, but they were betrayed, their Overlord assassinated, and they sank into the mire of civil war. 
(See section \ref{Mystraacht betrayed}.)

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  What shimmering swords raised in combat \\
  once sang with the glorious clamour of steel on steel?\\
  What splendid banners, billowing in the icy gales, \\
  once heralded the march of these invincible silver-clad legions \\
  to the blood-swathed embrace of epic battle?\\
  The glory of untold thousands of years past\ldots{} \\
  this ethereal legacy of mighty Ultima Thule.\\
  The frozen eyes of immortal kings watch me\ldots{} such a dark splendour!
}

Perhaps Ramiel reads the story of his people on the walls, like in H.P. Lovecraft's \emph{At the Mountains of Madness}. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  These ancient carvings in a time-veiled tongue,\\ 
  etched into the primeval ice countless aeons ago, \\
  now bathed in diaphonous incandescence \\
  by this storm of lucent stellar power, \\
  their mindsearing meaning at last becomes known to me.\\
  Their cosmic secrets unfold.
}





\subsubsection{Ramiel remembers his past}
Ramiel remembers the bloody wars he fought against other \resphain{} and against \dragons{} and \ophidians. 

He remembers fragments of \Ishnaruchaefir. 
The two have a history together. 
They are enemies, but respecting enemies. 
Almost like friendly rivals. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  And then, enlightenment comes, gleaming down upon my consciousness as the bright moon gazes down upon this auroral vista\ldots{} From my mind is lifted an obscuring veil, a veil induced by sorcerous arts, and I realize I have been merely a vassal of another's twisted will, a pawn in a game which is entwined in treachery and malign aspirations to thresholds of great power. 
  
  Such a traitorous web has been spun! The elders of my kingdom bow in obeisance to the vile priests of Xothan'kur, and it is their diseased machinations which have urged me here, to the very heart of the far-fabled ice realm\ldots{} for they seek to usurp the power of the Conjunction, stealing the vast energies of the Ice-Veiled throne and absorbing them into their own leprous, undead bodies, perpetuating the adoration of their abhorrent liege for countless ages, liberating his vile will and enslaving the realms of the world\ldots{}
}

He invokes \banes, \xss{} and cosmic gods. 

\lyricsbs{Hate Eternal}{Beyond Redemption}{
  Awaken from below I call thee,\\
  thy master pure in darkness,\\
  the one of hate before thy paths\\
  were chose to be forsaken.\\
  From depths of time in portals,\\
  through empty eyes of light,\\
  I searched the texts for knowledge.\\
  Now I bleed the sacrifice.
  
  I am of purest power. \\
  Strengths of a thousand souls.\\
  I hear the voices of\\
  the oldest ones burning within.\\
  Reveal the truth unto me, \\
  for I'll command the worthy.\\
  March through the ruins of diminished tribes.
}

He swears to retake the throne and reclaim power. 

\lyricsbs{Hate Eternal}{Beyond Redemption}{
  I summon winds of fire.\\
  I summon winds of disease.\\
  I summon torture upon\\
  all my rivals who shall bleed.\\
  Confronting all before me\\
  to tempt what I have in store.\\
  Don't tempt my fury for\\
  the flames shall burn eternally.
}







\subsection{\Azraid{} begins stockpiling \Erebean{} power}
\target{Azraid stockpiles Erebean power}
\Azraid{} sees portents (mystic or mundane?) that the \banes{} are reeling and about to be defeated. So he begins stockpiling \Erebean{} power, draining it away from \Erebos{} and the \banelords{} and hoarding it for himself. This is effective, because \Daggerrain{} is not expecting \Azraid{} to betray him. \Azraid{} has always been one of the most loyal \resphain. 

Remember to have subtle references to \ps{\Azraid} evil hand in all \Azraid{} chapters. 









\subsection{Ilcas dies}
\target{Ilcas dies}
\target{Sithiyacaan awakens}
Telcastora Ilcas charges heroically into battle and dies.

\citebandsong{BlindGuardian:NIME}{Blind Guardian}{Time Stands Still (at the Iron Hill)}{
  He gleams like a star and the sound of his horn's\\
  Like a raging storm\\
  Proudly the high lord challenges the doom\\
  Lord of slaves he cries

  Lord of all Noldor\\
  A star in the night and a bearer of hope\\
  He rides into his glorious battle alone\\
  Farewell to the valiant warlord
}

This is the catalyst that makes \Sithiyacaan awaken. 
But not in time to save Ilcas. 
\Sithiyacaan now realizes that he has to use his full powers to save the world. 

\citebandsong{BlindGuardian:NIME}{Blind Guardian}{Time Stands Still (at the Iron Hill)}{
  Finally I've found myself in these lands\\
  Horror and madness I've seen here\\
  For what I became a king of the lost?\\
  Barren and lifeless the land lies
}









\subsection{Ramiel is still bound}
Even after his enlightenment at the \Mystraacht{} temple, Ramiel is still bound. He is not entirely free of the Shroud, still trapped in a \human{} body, and without access to his full \sathariah{} power. He has a lot of power now, but he does not completely understand it. 

And not only that: He is under the effect of spells that chain his mind. He has enemies who want to manipulate him, use his power as a weapon of their own. They don't want him to awaken completely. Ultimately, they want to use him in their plan, where he is to expend all his power and be destroyed himself. Perhaps they plan to directly usurp his power, absorbing it for themselves and destroying him\ldots{}

No! Better idea: They want to create a new kind of \Sephirah, a more powerful one, but under their control. They want to transform Ramiel into one such. In order for that to work, he must be awake and have access to his full \sathariah{} power\ldots{} but he must awaken while under their control, so that immediately upon his awakening, they can chain and spellbind him and transform him into their new \Sephirah. 

Perhaps this is connected to the destruction of the original \Sephiroth. Perhaps Ramiel is to become the first of a new generation of \Sephiroth{} that will take over once the current ones have served their purpose. 

At any rate, Ramiel learns too much at the temple. Or, rather, he has learned too much before he came to the temple, so he is able to piece together more of the big picture than they expected him to. He suspects their scheme and takes active measures to undermine them, lay traps for them, infiltrate their ranks, so that in the end, he will be stabbing \emph{them} in the back. 







\subsection{Ramiel's enemies}
Ramiel has \hr{Ramiel's enemies}{enemies among the \resphain}. 
Have a Scabandari Bloodeye-like character. 







\subsection{Ramiel is broken down and rebuilt}
\target{Ramiel's final awakening}
He has regained much of his memory, but he is still trapped in the Shroud and must break free and be reconciled with his true self before he can regain his true \resphan{} form and his \sathariah{} power. 

He undergoes several mental torture. I don't know if this is voluntary or if he's trapped and imprisoned. Anyway, his Shrouded personality must be torn apart and broken down before his true self can re-emerge. 

\Cishiel{} and \Gilchad{} help him. 

Ramiel does not like \Gilchad. 
He is an obnoxious, condescending snob. 
He thinks he is smarter than everyone else and does not give Ramiel the respect he thinks he deserves. 

During the process of Apotheosis, Ramiel gradually comes to remember all the bits of cosmic knowledge he has gleaned over his many lives, the many Aenigmata whose Gnosis he has glimpsed. 
Back then he usually understood very little of it, but now, with the full knowledge of his many lives, he is able to see this knowledge from many exciting perspectives, and suddenly it all makes sense.
So immense amounts of horrid, sinister insight crash down upon his mind like a tidal wave.
With his multi-faceted experience he is able to understand much more than he otherwise would.
He attains Gnosis that no \resphan has ever held before him, save perhaps \Azraid.

And it is hard on him,
He screams in terror and anguish and has to fight a desperate and bloody battle against the many inner \daemons of his thoughts and fears to avoid losing his mind entirely.
His sanity is lashed like a vessel on a storm-wracked sea.
\hr{Ramiel is traumatized from awakening}{Afterwards he is traumatized and shaken}. 





\subsubsection{\Cishiel is worried}
\Cishiel is worried.
She fears her father has gone mad, and that his new power will make him even more mad and more dangerous.
But she knows it is too late to turn back.
She has cast in her lot with Ramiel and cannot hope to betray him, even if she would\ldots{} which she would not.
He is still her father and she loves him. 
He saved her from the horrible fate that befell him.
She knows that had he not forbidden her to become a \malach herself, she would have had to undergo the same torture and madness that Ramiel has endured - or she might have been destroyed long ago, or still trapped in the body of an amnesiac human.
No, she owes everything to Ramiel and still has more to repay him.

She feels more anguish for \Dasteron, her other ally, for she fears Ramiel will destroy him.
Ramiel looks terrible in his fury (when he \hr{Ramiel kills a Resphan after awakening}{eats a \resphan}), and \Cishiel fears no one will be able to stand against him, not even the formidable and resourceful \Dasteron.





\subsubsection{Voyage into inner worlds}
Perhaps the awakening process should be presented as a dream-quest, a journey into imaginary worlds that exist/are formed within his mind. 

Compare to Elric's journey beyond the Shadow-Gate in \cite{MichaelMoorcock:ElricofMelnibone}. 





\subsubsection{Facing his fears}
He is confronted with all his fears, sorrows, regrets, shame and pain. He must face, learn and accept the entirety of the brutal truth of his people's cruel nature and monstrous origins, the nature of \humans{} as a slave race, and his own history as a cruel conqueror and betrayer. 

Compare with the \emph{thetalos} cave in \authorbook{Jacqueline Carey}{Kushiel's Chosen} or Chia's caves in \authorbook{Stephen Marley}{Shadow Sisters}. 

Before he begins he promises himself that he will win. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  I smell the gasoline\\
  I smell the fire\\
  I'll make it all so clear\\
  This is my mentor
}

\citebandsong{BeyondTwilight:LurkingFantasia}{Beyond Twilight}{Rage}{
  Trying to face my sanity. \\
  But I'm too afraid to confront with it. \\
  Reaching out. \\
  For what I do not know.\\
  There's no way to explain this Hell I'm in. \\
  Can you? Can you? 
  
  No source of power to take from and wake \\
  from this nightmarish lunacy \\
  Is there a meaning or is this \\
  just a test of destiny? \\
  Creating these monsters for self purposed riches \\
  and glory in the end \\
  Thousands of victims with fresh schizophrenia \\
  isn't out here to pretend.
}

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Godless and Wicked%
}{
  Parts of my memory have been erased.\\
  You've destroyed my files\\
  Oh but I'm getting nearer\\
  It's all getting clearer 
  
  Look for a passage way\\
  Wait for the judgement day\\
  The truth will be told\\
  And my dreams unfold \\
  I'll find a way 
  
  I'm half alive here\\
  But I have no fear\\
  Cause I'll find the light yeah 
  
  Time to changes\\
  Everything re-arranges
  
  I'm getting ready\\
  At the break of dawn \\
  The fight is on 
  
  Godless and wicked\\
  Creepy and cold
}

With all his might he clings to the good memories of grandeur. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Send yourself to get back night\\
  I see women crawl\\
  It's dusty and mid in mind\\
  This is my intention
}

He wants to prove that he is the boss. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  I've seen me set the light\\
  This is the mentor\\
  I met cold on this ride\\
  This is the centre
}

But dangers lurk within his mind. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Don't let it fall\\
  You're not you, you're me\\
  Don't let it get a taste of your blood\\
  Yeah you're feeling small\\
  Don't look at me, don't look at me\\
  You're dancing with the Devil in my hall
}

He almost wanders lost in the dark corridors of his mind. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Now am I lost? Deep in my soul. \\
  There will be no forever.\\
  Through time I'm tossed. A wish without hope. \\
  Into the never.\\
  As time stands still, my spirit grows cold.\\
  I fall into darkness, as black as my soul.

  Now am I lost?\\
  Without hope into the never\\
  Deep in my soul
}

He holds tight. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Crawl for your master\\
  You know I'm in control
}

The whole process takes a long time. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  The Path of Darkness%
}{
  Smell the gasoline\\
  I light the fire inside\\
  Smell the gasoline\\
  I sway all through the night
}

Finally, slowly he awakens. 

\citebandsong{BeyondTwilight:SectionX}{Beyond Twilight}{%
  Ecstasy Arise%
}{
  From dark waters I rise\\
  My once trembling shell conceals a God
  
  Power surging through the void I soar\\
  Intoxicating visions whispering more\\
  In my radiance every \colour seems to fade
  
  I speak only in thought\\
  Life is not forever nothing is forever\\
  In dark waters I find\\
  Beauty beyond oceans of time
  
  In my radiance every \colour will soon fade away\\
  In the emptiness I will no longer stay
}

It is much like \hr{Shaeeroth ritual}{the process that turns a \dragon into a \shaeeroth}. 
Ramiel gains insight into many horrible truths concerning his people, the \banes, their \matrices and their purpose.
This is only possible because of the wisdom he has already attained, and it makes him even wiser and stronger, but also less sane, and it brings him a pain and a despair that will continue to haunt him.

\citebandsong{Nile:Ithyphallic}{Nile}{
  Language of the Shadows
}{
  Abandon hope\\
  And I shall become free\\
  And with freedom acquire emptiness

  With the mind cleansed and empty\\
  There is the void known as despair\\
  A gateway upon an emptiness endless and vast

  In despair the language of the shadows is intelligible\\
  In madness all sounds become articulate

  Terror and despair they guide me\\
  Into nightmares that follow one upon the other\\
  Like windblown grains of sand

  [solo: Dallas]

  I have become as the wastelands\\
  Of unending nothingness\\
  Now shall the night things\\
  Fill me with their whisperings\\
  And the shadows reveal their wisdom
}





\subsubsection{Fights his old victims}
Maybe Carzain has a dream where he faces all the people he has killed and/or betrayed. 
These are souls conjured from his \carcer.
He has to fight them all. 

Compare to \cite[p.85--86]{RobertEHoward:Ghor}, where Ghor faces all the people he has killed. 





\subsubsection{Regains his memory}
Ramiel regains all memories of all his lives. 
They come crashing back to him like a torrent. 

\target{Ramiel accepts Vizicar's death}
Among other things, he realizes that he has been deluding himself about \hr{Vizicar dies}{Vizicar's death}. 
There were no evil sea gods out to get him. 
It was just a regular accident. 





\subsubsection{Triumphant}
His traumas, his emotions and all his personality as Carzain, Vizicar and others is broken down. 
He is reconciled with his true nature as a \sathariah{} and his \malach{} \hr{Malachim bind souls}{power of binding souls} (and \hr{Ramiel binding souls}{his \carcer}).  
He embraces the enslaved souls and uses them and their power. 
He becomes the true Ramiel. 

He says to \Cishiel:
\ta{Bring me my sword and my guns.}
She swiftly obeys. 

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  And so, enrob'd by tendrils of starfire and the raiments of lunar mist, the immortal liege whose sceptred empire is eternity sits enthroned and brooding over his dark realm once more.
  
  Swathed in moon-frosts, in icy winds our blazon flying. \\
  When the moon and stars shine as one upon the snows, \\
  the ice-gate opens, the prophecy is fulfilled!
}

He tears asunder his \human{} guise and strides forth from the Shroud into true Reality, resplendent in all of his \sathariah{} glory. 

He summons his faithful servants, which are wolf-like creatures. See section \ref{Ramiel's wolves}. 





\subsubsection{Stronger than before}
When he awakens, \hr{Ramiel is wiser from walking the earth}{Ramiel is stronger and wiser than ever before}. 





\subsubsection{Becomes a \neoresphan}
\target{Ramiel becomes Neo}
Ramiel learns that in his long process of Apotheosis and awakening, he has not only returned to his old self. 
He has gradually metamorphosed (fully or partially) into a \neoresphan.
He is not only a beautiful and mighty \resphan. 
He is now a gruesome, slimy, loathsome, abhorrent, inhuman monster. 
This is a horrible truth. 
\Azraid has long been manipulating him, and now Ramiel's tranformation into a \neoresphan is complete. 

The temple has played a big part in this.
It was restored by \Azraid with new machines and spells designed to do exactly this:
Transform a \malach into a \neoresphan. 

This is \hr{Azraid turns Malachim into Neo}{what \Azraid planned all along}. 
Now Ramiel can be inducted into the \hr{Neo-Resphan conspiracy}{\neoresphan conspiracy}. 










\subsection{Kills a \resphan}
\target{Ramiel kills a Resphan after awakening}
Ramiel wants to test his new powers. 
As a full-fledged \malach he has \hr{Malachim binding souls}{enhanced soul-eating powers}. 
He tests it by attacking an eating a \resphan. 

Ramiel zaps his foe with dark lightning. 
Then shoots him with his pistols.
Then blasts him repeatedly with sorcery and lightning.
Gradually he tears his foe apart and, turning himself into a devouring, hungry vortex, sucks in the victim and devours him body and soul.
It is like witnessing a black hole and its accretion disc.





\subsubsection{Kills \Gilchad}
\target{Ramiel kills Gilchad}
Perhaps the first \resphan that Ramiel kills is \Gilchad. 

\Gilchad{} was responsible for guiding him through the torture process. 
When Ramiel finally awakens and emerges, he tells him: 
\ta{I owe you thanks for helping me regain my memory. 
  But I can tell by looking at you that you enjoyed the process. 
  So, with that in mind, I also owe you \emph{this}\ldots{}} 

And then Ramiel kills \Gilchad. 
And eats him. 

He had wanted to do this for a while, but he needed him. 
Now, for the first time ever in his life, Ramiel has full control over his \Malach{} powers and the associated \carcer. 
This means that he can eat (weak) souls far more easily than any normal \resphan{} or \dragon. 

He also wants to exercise and test that power. 
That is part of the reason for killing \Gilchad. 















\section[Return to Mystraacht]{Return to \Mystraacht}
\target{Ramiel returns to Mystraacht}
Ramiel returns to \Mystraacht. 

\citebandsong{BeyondTwilight:FortheLoveofArtandtheMaking%
}{%
  Beyond Twilight%
}{%
  For the Love of Art and the Making%
}{
  He is the prince of darkness\\
  Returning home to take his kingdom
}

Ramiel is now \hr{Ramiel is overpowered}{immensely powerful}.
When he comes back, others \hr{Ramiel is underestimated after Apotheosis}{underestimate his strength}. 





\subsection{Ramiel and \Dasteron}





\subsubsection{Ramiel hears of \Dasteron}
At first, Ramiel's motivation was just to get his powers and memory back. 

Now that he has achieved that, he spends many days doing research, learning everything about the state of the world from records and from \Cishiel's Cabalist contacts.
He covets power and greatness and feels it is his right by succession to become Overlord.

But not only that.
He also doubts \Dasteron's ability.
He returns to \Mystraacht and studies \Dasteron in person.





\subsubsection{Ramiel gets to know \Dasteron}
Ramiel goes to \Mystraacht and meets \Dasteron.
Ramiel hangs out for a while and learns how thing work nowadays.
He greets \Dasteron with respect (of sorts), but no subservience.
\Dasteron reciprocates. (Ramiel is, after all, a \sathariah, and thus in a sense \Dasteron's superior.)
Ramiel comes to \Mystraacht intent on hating \Dasteron, this pathetic usurper who thinks he can be Overlord.
But Ramiel finds, much to his chagrin, that \Dasteron is a good \resphan, a worthy leader and even a potential friend.
This complicates matters.





\subsubsection{Ramiel must dethrone \Dasteron}
Ramiel learns that \hr{Dasteron cannot become Apex}{\Dasteron{} lacks the \vertex{} strength to ascend to the position of \apex{} of the \Mystraacht{} \matrix}. 
This is no good. 
It is one of the reasons why Ramiel knows he has to dethrone \Dasteron. 
He might be a good leader for a while, but if he cannot become \apex{}, his reign is stillborn and without true prospect. 

Ramiel has learned from his travels, and from the insight he has gathered over his many lifetimes, that something big is coming. 
Some cataclysmic metaphysical event. 
And the \Mystraacht{} \matrix{} has to be strong to deal with it. 
Therefore, a true \apex{} is needed. 
Ramiel feels this \apex{} should be him. 

He becomes convinced that, while \Dasteron is a good leader, he is not good enough.
He is a skilled politician and fighter, but he does not have the cosmic insight or \vertex strenght that \Mystraacht needs.
He finds out that \Dasteron shies away from all the darker writings and fears dealing with the \banes.
\Dasteron tends to obey the \banes quickly and with great fear.
\Dasteron is fearless when it comes to his fellow \resphain, but Ramiel fears \Dasteron is not capable of managing \resphan affairs in a larger cosmos.

This makes up Ramiel's mind.
He must dethrone \Dasteron and take the throne himself.
Only he is strong enough to rule \Mystraacht. 

Conversely, \Dasteron finds that Ramiel acts hysterical and manic and irrational.
\Dasteron concludes that Ramiel is insane and unfit to rule. 





\subsubsection{Ramiel laments having to kill \Dasteron}
Ramiel grieves. 
He has come to see \Dasteron as almost a friend. 

Ramiel also knows that however good \Dasteron is, Ramiel has to dethrone him.
\Dasteron knows this as well.
Sooner or later, Ramiel will challenge him for the throne.
Here is the real tragedy:
Ramiel knows that if he loses their match, he will not submit to \Dasteron's rule.
He will challenge him again and again until he wins, for Ramiel must win.
He also comes to know \Dasteron well enough to know that \Dasteron will do the same if Ramiel wins.
They are both full of pride.
Each believes that he is the better leader, that only he is worthy and capable of leading \Mystraacht.
\Dasteron believes that Ramiel, for all his brute force, is too insane and unstable and dangerous to have as Overlord.
So they conflict is doomed to continue forever, until one of them perishes.
So Ramiel makes a very hard decision.
He will destroy and eat \Dasteron as soon as he wins (if he can, that is). 
This is tragic.
Ramiel will miss \Dasteron.
He is a great \resphan and a friend.
It will be a great loss for \Mystraacht and for the \resphan race, and for Ramiel, and for \Cishiel.
But it must be done.










\subsection[Mystraacht has degenerated]{\Mystraacht has degenerated}
In Ramiel's absence, \Mystraacht{} has degenerated into a crowd of decadent barbarians striving for maximal evil and perversity for its own sake, and out of some misguided ideological idea that this is their true nature and the purpose of \Mystraacht. 

Compare to the Dark Eldar of \emph{Warhammer 40,000}.

Ramiel: 
\tho{%
  We of \Mystraacht{} boast of our independence and free thinking.
  But we are just as bound by tradition as the \KiriathSepher.
  We go with the flow just as much as they do.
  Just look at how I followed \Zachirah.}

Ramiel intends to bring order and restore the true \Mystraacht. 
Bring them back on track and introduce meaning in all the madness. 

Ramiel: 
\ta{%
  I am \ps{\Zachirah}{} only son. 
  I alone am heir to his legacy and his designs. 
  I alone comprehend the scope of his original vision. 
  I alone understand \ps{\Mystraacht}{} true purpose.}
\tho{%
  And I alone understand the flaws in my father's vision and know how to correct them.}

The \Mystraacht{} do a lot of eating and binding souls. 
This is the source of \hs{Ramiel's bound souls}. 

\lyricstitle{Warhammer 40,000: Codex Dark Eldar}{
  As the Dark Eldar died, the air was filled with escaping souls. 
  A roiling mass of blackness hovered on the edge of vision, the screams of spirits in eternal torment sounded on the edge of hearing.
  
  \ldots{}
  
  The ebbing and flowing of released souls slithered around the Dracon, drawn to her blood and fear. 
  She could feel their wispy tendrils sliding over her, probing gently into her mind. 
  She felt like screaming, but she gritted her teeth and was silent. 
  
  \ldots{}
  
  The Dark Eldar Lord's eyes glazed over, as he took a long, deep breath. 
  Khirareq felt the spirits around her drifting away, pulled towards the gulf inside the Lord's own soul. 
  The Lord's body twitched spasmodically as he absorbed the freed life essence of his followers. 
  As the spirits of the dead were consumed, Akhara'Keth's spasms increased and a thin dribble of saliva trickled from the corner of his slack lips. 
  With a shuddering sigh, the Lord finished and slumped back in the chair. 
  When he sat forward once more his eyes burned more brightly, his skin was less wrinkled, his hair darker with more lustre. 
  
  \ldots{}
  
  She stared straight back at the Lord, looking deep into the ancient pits of evil that were his eyes. 
  
  \ldots{}
  
  \ta{%
    You need to rule?
    What do you know of needs 
    You are young, the Thirst has a shallow hold on you. 
    I will tell you of need; a deep, unfaltering emptiness that grows larger and more demanding with every passing of the night. 
    You have heard tales of how I consume a hundred souls a day. 
    That number is but the morsel to whet my appetite. 
    A hundred times that number die every day to quench my desire, my need.
    Spirits unnumbered are distilled in agony and torture to the peak of exquisite taste to fill the chasm of my soul. 
    Do not confuse needs with ambitions.}
}









\subsection{Ramiel confronts \Dasteron}
There is an upstart, \hr{Dasteron}{\Dasteron}, who is the closest thing \Mystraacht{} has to a leader these days and thus counts as having usurped Ramiel's place. 

\target{Ramiel uses macho rhetoric against Dasteron}
Ramiel uses traditional \Mystraacht \hr{Mystraacht philosophy}{macho rhetoric}. 
But he is actually \hr{Ramiel is critical of Mystraacht ideology}{critical of the \Mystraacht ideology}. 

\Dasteron{} is taller than Ramiel, and very powerful. 
(You have to be powerful as fuck to aspire to lead \Mystraacht.)

He mocks Ramiel: 
\ta{%
  I believe you will find that things have changed in your absence, Lord Ramiel.}

Ramiel:
\ta{%
  You will find that things are about to change again following my return.}

\Dasteron{}: 
\ta{%
  You have been out of the game for thousands of years, Lord Ramiel.
  You drifted around down there playing \human, 
  while I was devouring souls and waxing strong. 
  I have even devoured \dragons.
  \Dragons, Lord Ramiel!
  Times have overtaken you.
  I am your superior now.}

Ramiel: 
\ta{%
  Then I challenge you.
  I invoke my right of Trial by Combat.}

Remember to compare Ramiel's and \ps{\Dasteron} \hr{Dasteron's appearance}{appearance}. 

The battle itself, despite what they try to show the spectators, is a grim, sad affair.
There is no hate or anger, so there is no enjoyment.
It is just a grim and gritty fight to the bitter end.





\subsubsection{Motivation}
Ramiel knows he has to prove his own worth by defeating \Dasteron. 
He must impress the \Mystraacht{} so they will accept him as their Overlord. 
He has to entertain in order to lay a foundation for his future reign. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Panem et Circenses}{
  Awake, O' serpent of my heart. It is time.\\
  The sun stands high, and unfaithful crowds await thee.\\
  Redemption in their eyes and stone at hand.\\
  The arena hungers for your venom.\\
  Let the games begin.
  
  Bring in the lions. Bring in the beasts.\\
  It is time to confront the masses with their fears.\\
  A sober moment. A shred of truth.\\ 
  To gaze into an honest mirror. \\
  A disturbance of their sleep.
  
  Violent teeth and claws, untamed and fierce, \\
  reaches far and cut deep into the empty eye.\\
  It is time to let the bitter venom flow\\
  through this embodiment of emptiness.
  
  And the blood shall run free like words.\\
  And the bones shall form stairs to the future.
  
  Now, unfaithful spectator. Are you satisfied?\\
  Did you come close enough to feel the lion's breath?\\
  On day soon your shall be the sacrifice.\\
  A nameless grave of the past.
  
  Protagonist!\\
  Your time is now.
}





\subsubsection{Combat}
\target{Dasteron dies}
\target{Dasteron stronger than Ramiel}
\Dasteron{} is more skilled than Ramiel. 
\hr{Dasteron's skill}{Much more skilled}. 
He has faced down \satharioth{} before and knows how to turn an opponent's strength against him. 
Besides, \hr{Dasteron's smithing}{he is a great weaponsmith} and armed with the sword \hr{Scaleron}{\Scaleron} and many other powerful magical items. 

\ps{\Scaleron} design was inspired by \hr{Ascaril}{\Ascaril}, Ramiel's mother's sword. 
\Dasteron{} tells Ramiel this. 

Ramiel is taken unawares when \Dasteron{} displays just \emph{how} skilled he is at all three \hs{Paths}; not only \hr{Path of Light}{Light}, but \hr{Path of Ice}{Ice} and \hr{Path of Darkness}{Darkness} as well. 
This nearly overpowers Ramiel. 
The two combatants are sort of evenly matched at the Path of Light, but \Dasteron{} is far better than Ramiel at Darkness and Ice. 

One reason why \Dasteron{} is stronger than Ramiel is that he has \hr{Dasteron's upbringing}{lived his entire life as a \Mystraacht{} warrior}.  
Ramiel spent his formative years in the wussy and semi-pacifist and effeminate \Merkyrah{}, and then spend thousands of years \trope{WalkingTheEarth}{Walking the Earth} as a Scion.  

Ramiel is \hr{Ramiel is overpowered}{\uber, because he has eaten \Belzir}. 
But even so, he is hard pressed. 
He is not confident he can win. 
So he \emph{cheats}. 

The fight is to the death, but \emph{not} to destruction. 
But after Ramiel wins he breaks the rules and eats his fallen foe's soul, destroying him. 
Dark Eldar style. 

\ta{Stop him!} people around him cry. 
This was not part of the deal.
But no one is brave enough to challenge the \sathariah{} who has just splattered their leader and is now eating his soul and radiating fucking wicked-sick \sathariah{} power in all directions. 

Ramiel: 
\ta{%
  I am Overlord now. That was the prize. I can do whatever I want. That is my right. Will anyone deny me?}

Someone dares call him out on the dishonourable methods he used, both before, during and after the fight: 
\ta{You cheated!}

Ramiel:
\ta{Have you become like the \KiriathSepher{} in my absence?
  Have you become fops and cowards, slaves of etiquette?
  Ruthlessness has always been the \Mystraacht{} credo. 
  I saw my chances, so I took them. 
  Just as I saw my throne and now seize it.}





\subsubsection{Claims \Scaleron}
After slaying \Dasteron, Ramiel claims the sword \Scaleron. 
From that point he wears and uses the sword. 
It is his way of paying tribute to \Dasteron. 
He was, after all, a great and brave man and a worthy opponent. 
A true warrior of \Mystraacht. 

\Scaleron{} is a more than worthy replacement for Ramiel's old weapon, \Ascaril. 









\subsection{Ramiel claims the throne}
Ramiel lays claim to the throne of \Mystraacht. 
At this time he is not only the son of the first and greatest Overlord, but also the last surviving \sathariah{} in \Mystraacht{} (\Shiaraid{}, whom he killed, was the penultimate one). 
So, try as they might, no one can can really deny that he is the best candidate for the throne. 

\begin{prose}
Critic: 
\ta{What gives you the right to claim Overlordship?}

Ramiel: 
\ta{I am Ramiel.} 

(He could list off titles, lineage and accomplishments: 
One of the original discoverers of \Semiza, \sathariah, co-founder of \Mystraacht, sole heir of the last Overlord, and a mega-badass dude. 
But he needs say no more.) 

Critic: 
\ta{I believe you will find, Lord Ramiel, that things have changed in your absence.} 

Ramiel: 
\ta{And I believe you will find, [Critic's name], that things are about to change again.} 
\end{prose}

Perhaps he challenges his rivals by invoking his right of \hr{Mystraacht trial by combat}{trial by combat}, as is a \Mystraacht{} tradition.

\emph{\RamielsAwakeningBook} ends with Ramiel proclaiming his dominion and claiming his ancestral throne, cementing his position as the unchallenged Overlord of \Mystraacht. 

\lyricsbs{Emperor}{Moon Over Kara-Shehr}{
  Master! We ride with the storm \\
  in his name, the sire, wolves' king. \\
  Enter the power coursing \\
  through veins of the night.
  
  Power ripples through me. \\
  Armageddon's thunder will bring others to my side. \\
  The throne is mine. \\
  A blackened storm of evil. 
  
  Master! We ride with the storm to take \\
  revenge in the sky upon the one \\
  who cast thee from his side.
}

\lyricsbs{Bal-Sagoth}{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  Such power! I am the Chosen. \\
  The secrets of the earth and the stars are unlocked before me.\\
  I am destined to reign forever\ldots{} \\
  to reign from the Ice-Veiled Throne of Ultima Thule!
}



After Ramiel has regained his full \malach powers and become Overlord, he lets himself hail as the saviour and champion of the \resphan race. 
He has mastered his \carcer and the dark powers of the \banes.
He is the ideal of all \resphain who crave power and greatness and perfection.

The new \Thanatzil, even.

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  Churning the Maelstrom
}{
  Hail To He Who Is In The Duat, Who Is Strong\\
  Even Before The Servants of Serpents\\
  He Gathers The Power From Every Pit of Torment\\
  From They Who Hath Burnt in Flames\\
  From Words of Power Uttered By the Darkness Itself

  Hail To He in The Pit, Who Is Strong\\
  Even Before the Terrors of The Abyss\\
  Who Gathers The Power from the Wailing And Lamentations\\
  Of The Shades Chained Therein\\
  From He Who Createth Gods \\
  From The Silence Alone
}





\subsubsection{Ramiel is sad}
After having slain \Dasteron and claimed the throne, Ramiel is very serious and determined and weighed down with responsibility.
Not at all the reckless adventurer he was in his youth.

Compare to William Adama from \cite{TV:BattlestarGalactica}.





\subsubsection{Contacted by \Daggerrain}
At the end (or perhaps at the beginning of the next book), Ramiel is contacted by \Daggerrain. 

\daggerrain{Ramiel. 
  Thou hast united \Mystraacht. 
  That is good. 
  But forget not whom thou servest.}















\section{Sentinel story thread}










\subsection{\Vizsherioch{} versus \Ishnaruchaefir}
\Vizsherioch{} is strong, powerful enough to challenge even \Ishnaruchaefir. Despite his young age. 





\subsubsection{\Vizsherioch{} becomes the Dagger}
\target{Vizsherioch becomes the Dagger}
\index{Dagger, the}%
\Vizsherioch{} finally becomes the \hs{Dagger} and takes his rightful place in the \matrix. 
His confrontation with \Ishnaruchaefir{} (and his \hs{Fulcrum}, \Rystessakhin) was important in this process. 











\subsection{\Secherdamon{} communicates with Tiamat}
\target{Rissit communicates with Tiamat}
\Secherdamon, seeking power and guidance in his war against the \banes, contacts the \firstgendragons. He feels the presence of \Tiamat. She appears as a great mass of swirling Chaos, almost too amorphous to be a person. She seems almost mindless. Compare her to Azathoth from H.P. Lovecraft's stories, such as \emph{The Dream-Quest of Unknown Kadath}.

Of course, \Tiamat{} is not mindless. But she has absorbed so much Chaos power and \xzaishannic{} essence that she has become more like \xzaishann{} than a \dragon. Her mind is so Chaotic as to be completely alien and unknowable, even to \Secherdamon, who is otherwise one of the wisest among the \shaeeroths{} in the arts of Chaos, one of those who knows the most and has done the most research. (For instance, he\dash along with subordinates\dash created the Rissitic magic theory of the Three Worlds.)

\Secherdamon wants to bring the \xss back. 

\citeauthorbook[p.68]{VengerSatanis:CthulhuCult}{Venger Satanis}{Cthulhu Cult}{
  The Great Work has one end result: to bring the Old Ones back.
  Once They return to this reality, an apocalypse of bilious green fire will burn the foolish and the weak. 
  Blood spilt in ritual sacrifice shall consecrate the ground, opening the gateways.
  Temples built to \honour the Dark Gods shall alert the vigilant.
  Hideous visions shal refresh the dead imaginations of the faithful. 
  
  Some distant night shall see the unspeakable entities from Outside descend\ldots{} shall see Them break free, lowered into this world\ldots{} shall see Them destroy as they recreate their shuddersome paradise.
  Those among us who are strong, wise and diabolic shall enter the void and become like the Old Ones.
}





\subsubsection{\Secherdamon{} visits \Dathka}
\Secherdamon{} visits the fallen city of \hr{Dathka}{\Dathka}. 

\lyricsbs{Emperor}{Ye Entrancemperium}{
  Drawn towards these lands again.
  Seeking death and sacred soil.
  I ride the longing winds of my blackened soul,
  growing stronger once I enter my empire beyond.
  
  Emperium!
  Behold my coming.
  
  The fullmoon rise above me,
  enlightening my realm in a silvery glow.
  Yet the shadows crawl beneath my storming sky,
  guarding treasures from forbidden light.
}

He remembers \hr{Secherdamon's rise to power}{the time when he became a god}. 

\lyricsbs{Emperor}{Ye Entrancemperium}{
  I still remember,\\
  though ages ago it seems,\\
  the first time I entered the gates,\\
  the revelation of ritual death\\
  by which I became divine.\\
  Sacrifice of the life I had\\
  among the flesh of the light.
  
  And now I enter again.\\
  Even stronger, yet amazed by what I see.\\
  In ecstasy I mock the world.
  
  Suddenly I memorize,\\
  asking what I left behind.\\
  Nothing.
  
  Can I ever comprehend?\\
  Will my longing ever end?\\
  Never.
}





\subsubsection{\Secherdamon{} seeks out \KhothSell}
\Secherdamon{} also hopes to invoke \KhothSell{} and obtain her power of death to wield it against the \sephiroth{} and the \Morbus. 

\lyricsbs{Exmortem}{Death deceiver}{
  Ancient image of death.\\
  The deepest depts of horror.\\
  A diabolic master plan.\\
  Not to succumb to the damned.
  
  Mummified in slumber.\\
  Awaiting to appear.\\
  Death deceiver.\\
  Exmortem.
}







\subsection{\Ishnaruchaefir{} seeks power}
\target{Ishnaruchaefir seeks out cosmic gods}
\Ishnaruchaefir{} fears \ps{\Secherdamon} plotting. 
He plans to go up against his brother, but he is not powerful enough. 
He needs more knowledge and power. 

In order to build and release the \hs{Ark}, \Ishnaruchaefir requires the help of some \hr{Aloof Dragons}{aloof Elder \Dragons} that sleep dormant.

Maybe replace the gods in this scene with Elder \Dragons. 
Or maybe it is \Secherdamon who contacts them.

In the end, a few Elder \Dragons manage to awaken (now that the Shroud is broken) and come to \Ishnaruchaefir's aid.
Not many, though. 
Perhaps 4--6.
10 at the very most. 




\subsubsection{Navel gazing}
He gazes into himself, and into his glaive, \Triestessakhin. 

\lyricsdimmuborgir{The Insight and the Catharsis}{
  Oh, dreadful angel of mine.\\
  Enrich me with the vastness of your being.
  
  Rigid father, teach me to comprehend.\\
  I'll commit myself to understand.\\
  To be the faithful and the instrument,\\
  so that the ones with blindfold can see what I have seen.
}





\subsubsection{\KhothSell}
He seeks out \KhothSell, his \quo{mother}. 
She tells him stuff. 

\lyricsdimmuborgir{The Insight and the Catharsis}{
  What more do you need of proof?\\
  Human hands conforming clooven hooves.\\
  For I know the secrets and lies behind all truths.\\
  Knowlege is power and the power is mine.\\
  It's all mine.
}





\subsubsection{Cosmic gods}
He seeks out some \hr{Cosmic gods}{cosmic gods}, hoping to gain the power and knowledge he needs to thwart his brother. 

Their dark halls are splendid and overwhelming, but also dangerous, filled with mighty guardians that strike even the legendary \Ishnaruchaefir{} with terror. 

\lyricsbalsagoth{Invocations Beyond the Outer-World Night}{
  These stygian pitch-black vaults are filled with batrachian devils,\\
  Dire crystalline watch-dogs of the chasmed deeps,\\
  (For the gleaming jewels of truth are not without their protection\ldots{})\\
  Vril-gorged adamantine fiends of the threshold,\\
  Spawn of the ersatz interior sun.
}

The cosmic gods turn him away. 

\lyricsbalsagoth{
  The Hound of Chaos Transcends the Nebulous Palisades of Z'xulth
}{
  [THEY-WHO-LURK-AND-BREED-IN-LIMBO:]\\
  Silence, godling! \\
  The fact that you stand before us is testimony to your mettle, 
  but your ambitions shall yet outreach your abilities. 
  
  We have long watched thee and your struggles with amusement, Zurra, 
  Sire of Angsaar. But this audience is now at an end. The path you 
  must traverse lies before you, and you must follow it to its 
  ultimate destination.
}

But \Ishnaruchaefir{} is sneaky, and he manages to surprise and out\manoeuvre them, if only for a moment. He successfully gleans enough of their secret knowledge to achieve what he needs. And so, \Ishnaruchaefir{} confronts some of the mightiest creatures in the cosmos, entities who could crush him underfoot with no effort at all, and he \emph{still} comes out looking like a total stud. \trope{Badass}{Badass}.  







\subsection{\Ishnaruchaefir{} laughs}
At some point, \Ishnaruchaefir{} experiences something funny. 
He laughs with sincere mirth for several seconds. 
\Criseis{} (who is with him) laughs along. 
Seeing him enjoying himself is intoxicating. 
She becomes ecstatic and blissfully happy. 
Her entire world lights up, and everything seems good and bright. 

While it lasts. 

Then he gets over it, and his usual brooding, grim, sardonic state-of-mind takes over. 
Suddenly \ps{\Criseis} world again turns dark and brutal and full of war and pain.
She understands that his mirth made him forget his gruesome burden and all his traumata and hate against the world for a brief moment. 
And his feelings rub off on her, who is closer to him than any other. 
And she is more impressionable and vulnerable than he, so it rocks her world more strongly. 





\subsection{Sentinels seeks out \voyagers}
Some Sentinels, perhaps \Ishnaruchaefir, seek out the \hr{Voyagers today}{surviving \voyagers} to gain knowledge useful against the \banes. 








\subsection{\Ishnaruchaefir{} begins to realize what he must do}
\target{Ishnaruchaefir begins to realize what he must do}
\Ishnaruchaefir{} slowly begins to realize \hr{Ishnaruchaefir realizes what he must do}{what he must do} to overcome his own mental blocks and reach the Gnosis he so desperately needs. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  A distant cry arose\\
  from the fathomless well that is my soul.\\
  I can not hear the words,\\
  so I throw my heart in like a coin\\
  and wish that it would sink forever.
}

He realizes that \hr{Mirage Asylum symbolism}{he is hiding}. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  A purpose, a sacrifice,\\
  or merely temptation?\\
  Is my solitude anything but a perversion\\
  of my vanity?
}

He defends/rationalizes his actions to himself. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  I never cared for this weak inclination,\\
  this paranoid tendency to flock.\\
  And in between all the noise, all the guilt,\\
  a silence would carry my spirit away\\
  from diminishing obsessions.\\
  Away from fools and poisonous flies.\\
}

But deep down he knows his rationalizations do not cut it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  The birth of a dreamer.
}









\subsection{\Ishnaruchaefir{} takes a crazy risk too much}
\QuessanthIshnaruchaefir{} is known to be reckless and take crazy risks. 
In this book, he takes one crazy risk too many. 
It goes wrong. 
He fucks up and accidentally leaves a back door open so the \resphain{} can sneak into his Mirage Asylum. 







\subsection{Mirage Asylum destroyed}
\target{Mirage Asylum destroyed}
At some point \ps{\Ishnaruchaefir} \hs{Mirage Asylum} is breached, invaded by \resphain{} and \banes, overrun and destroyed.
 
It had been a living thing, but now it died. 
It bled and felt pain as it died. 
It was horrible for \Criseis to feel it die.
It was her home. 

\Ishnaruchaefir{} now has no safe hiding place. 
He cannot just skulk and let things happen. 
He is forced to take a more active role in the Feud. 
And he does. 
Oh, boy, does he. 
With a vengeance. 
The \resphain{} soon regret provoking him. 

Maybe this is part of \ps{\Azraid} \trope{XanatosGambit}{Xanatos Gambit}. 

The Asylum was protected by the Shroud. 
It was only because the Shroud was \hs{unravelling} that it was possible for the \resphain{} to breach it. 

Make sure to have plenty of story leading up to this, making it plausible that the Asylum could be breached now but not just at any point in the last seven thousand years. 

This is an omen of things to come. 
Soon, the whole world will lose its Mirage Asylum, the Shroud itself. 

Compare to where Chia loses her Black Dragon Valley in \authorbook{Stephen Marley}{Shadow Sisters}. 









\subsection{\Ishnaruchaefir resurrects and learns about \iquin}
A very heroic or very innocent mortal is tragically killed. 
\Criseis, who had formed ties to this person, is devastated. 
As an immortal, she has long experience telling \quo{good} deaths from \quo{bad} deaths, and this one is a bad one. 
She rages at the injustice of it.

Someone:
\ta{It is no use. We cannot rule over life and death.}

\Criseis:
\ta{You are right.
  You and I cannot rule over life and death.
  But I know who can.}

Have some references to \Sethicus's lore and his great mastery of the forces of the world, and to the sorcery and pacts of \KhothSell. 

\Criseis prays. 
\ta{Master \Quessanth.
  \Quessanth \Melechet \Nierzshah \Tzeorossh \Ishnaruchaefir.
  Rarely have I asked you for anything. 
  I beg you now, help me.}

\Ishnaruchaefir:
\ta{I cannot. His/her soul has already passed into the afterlife.
  I cannot reach inside \iquin.}

\Criseis (desperate, tearful):
\ta{You lie! I know you can. I have seen you defy forces as great as \iquin before.}
She yells and curses at her master and all but orders him to do this for her. 

\Ishnaruchaefir is impressed by \Criseis's passionate outburst.
\Dragons respect strength and aggression more than humility. 
\ta{Very well, \Criseis. 
  You speak the truth.
  I do owe you this boon.
  So be it.
  For you I will defy the \sephiroth.}

\Ishnaruchaefir reaches into \iquin.
It is hard work.
Very hard. 
He struggles. 
He breaks through layer upon layer of \iquin. 
Finally he finds the soul he is looking for and tears it free. 
In the process he learns much about \iquin. 

\Ishnaruchaefir is horrified.
He had known \iquin was a \dweomer powered by souls of the dead, but it is a bigger, more cosmic and more ambitious project than he had dreamed. 
He had thought \iquin existed primarily as a power source for the Vaimons. 
He realizes it has bigger potential than that.
It is much more integrated into the world and has roots that go deeper. 
It is \hr{Iquin and Noggyaleth}{connected with the burrowing of the \noggyaleth}.
He begins to guess the \Lithrim plan.









\subsection{\Ishnaruchaefir{} confronts \Secherdamon}
\Ishnaruchaefir{} confronts \Secherdamon.

Perhaps, in the distant past, \Ishnaruchaefir{} warred against \Nexagglachel{} in an attempt to bring the \dragons{} together. 
They discuss this.

\begin{prose}
  \Ishnaruchaefir: 
  \ta{That is something you never grasped.}
  
  \Secherdamon: 
  \ta{You think you know so much about me. 
      Yes, I know and understand perfectly, as I always have. 
      But your mission is misaimed (forfejlet?). 
  
      You are so arrogant. 
      You do not understand what I have become; indeed, you never understood what I was. 
      You have power, yes, and you may best me in combat, but in the world I wield power beyond your wildest dreams.%
  }
  
  \Ishnaruchaefir: 
  \ta{Unlike you, I have no wildest dreams\ldots{}}
  
  \Secherdamon: 
  \ta{\ldots{} and that, brother, is your failing. 
      It is why you have become a relic of the past. 
      The future is mine! 
      I am the future!
  
      Heh. 
      Perhaps I ought to thank you and \Nexagglachel. 
      If not for his death, I might still live in his shadow. 
      The events of those days are what have me the push to rise above what I was. 
      And today I am by far the greatest of us three.%
  }
  
  \ldots{}
  
  \Secherdamon: 
  \ta{%
    The Gnosis which \hr{Ishnaruchaefir refuses to tell Secherdamon Gnosis}{thou stole from me}\ldots{}
    I have \hr{Secherdamon gains Gnosis}{reclaimed it} by mine own craft.
    I am ready.
    My plan will come to fruition, and thy hideous work will be undone!}
\end{prose}

They fight a great duel. 
It is savage, murderous business, but cathartic. 
They slash and rip one another apart and let loose all the aggression and hate that they have pent up for one another and left to brood and fester for thousands of years. 

For once, \Ishnaruchaefir{} talks about feelings and motives. 
And he defends his actions, something he has always refused to do. 
He shouts in anger, which helps, because it is what \dragons{} do when they are being candid. 
This open anger is cathartic and brings them closer to each other (even though, between \resphain{} or \humans{} or \scathae, such anger could easily work the other way and drive them further apart). 

They learn to understand each other better, through the words and curses they speak, and through the deeper truths their bodies tell, with claws, weapons and magic. 
They understand each other's Aenigmata. 

They come a step closer to resolving the endless feud between the two brothers. 
They learn to respect each other. 

At the end, \Secherdamon{} admits that he is closer to forgiving \ps{\Ishnaruchaefir} crimes against them all. 
This is hard to say. 
Equally hard, \Ishnaruchaefir{} \emph{accepts} this step towards reconciliation. 
Previously he has responded to the idea of forgiveness with nothing but scorn. 
But this time he accepts and respects it (but wordlessly, not explicitly). 

This makes \Secherdamon{} more ready for his final mission. 
\hr{Secherdamon's sacrifice}{His sacrifice}. 

% They fight. 
% Ultimately, \Ishnaruchaefir{} slays \Secherdamon.









\subsection{\Secherdamon{} dies}
\target{Secherdamon dies}
\Secherdamon{} has two possible deaths: 





\subsubsection{Version 1: \Vizsherioch{} kills him}
Somehow, \Secherdamon{} get into combat and is mortally wounded. \Vizsherioch{} comes to him. 
\Secherdamon{} asks his son to save him, but \Vizsherioch{} instead kills him. 

First, \Vizsherioch{} holds a monologue: 
\ta{Yes, father. 
  You created me to be loyal to you. But more importantly, you created me to be loyal to our quest, our legacy.

  You created me from your own essence. I am part of you, and you are part of me. In the long run, this is a weakness. You must understand this. You made me well, but you have held too much back.
  
  You are fallen. To save you would be\ldots{} inefficient.
  
  I will strike you down, father, and subsume your essence into me. I will absorb your \xzaishannic{} blood, and in doing so I will become greater than any of us.
  
  I will become the ultimate \draecchonosh. I will become the ultimate heir to the \firstgendragons\ldots{} and to the \xzaishanns. I will become\ldots{} \emph{perfect}. And I swear to you this, father: I will filfull our destiny. I will scour \Miith{} of the \Erebean{} infestation and restore the glory of the \draconian{} race.}

\Secherdamon{} understands his son's vision, so he is happy when he dies. 

After this, \Vizsherioch{} becomes the ultimate god. 

He remembers the \quo{his} past as a \xzaishann{}.

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  I was spawned deep beneath the Pre-Cambrian sea, \\
  the scion of a far distant sun\ldots{}\\
  I have traversed the endless stars, \\
  and journeyed to a myriad galaxies\ldots{}\\
  The dimensional gates of the multiverse are mine to voyage effortlessly beyond,\\
  cosmic infinity is naught to one such as I\ldots{} \\
  I am as one with celestial eternity\ldots{}\\
  Clad in gleaming pentlandite \armour, \\
  on a whim I may reshape entire worlds,\\
  or extinguish the blazing light of a sun\ldots{} \\
  and I remain forever enchanted by sylphs\ldots{}
}

He has memories of the \xzaishanns{} beyond anything \Secherdamon{} and even the \firstgendragons{} had achieved, and he also carries within him the stolen essence of the \banelords. 

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  Wielding this Power Cosmic,\\
  the Omniverse is mine to conquer.\\
  I am a god.
  
  Arcane power lances forth from my fingertips,\\
  life withers before my baleful gaze.
}

He remembers the whole civilizations that the \xzaishanns{} once destroyed.

Have some evil flashbacks with the \xzaishanns{} destroying civilizations. 

\lyricsbalsagoth{Return to the Praesidium of Ys}{
  The proud citadels of great antediluvian empires\\
  have been razed to the ground by my zircon blade.
  
  Riding the screaming crest of fettered ions,\\
  I shall bring my crystalline Chaos where order reigns.
}

He looks down at his father's corpse. 
\ta{I'm sorry, father, but I was not telling the whole truth. 
  I am not driven by our legacy or quest, but by the Will to Power.} 
Compare with Friedrich Nietzsche's philosophy.





\subsubsection{Version 2: Heroic sacrifice}
\target{Secherdamon's sacrifice}
\ps{\Secherdamon} death is a heroic sacrifice for his people. 
It has cosmos-spanning metaphysical ramifications and ripples. 

Compare to Anomander Rake's sacrifice in \cite{StevenErikson:TolltheHounds}. 















\section{Random scenes}









\subsection{The power of love}
A \human{} talks to a \resphan{} about how love is the greatest, most important thing in the world. 

\Resphan: \ta{Ah, yes. \quo{Love}. Insertion of dick into cunt, a splash of liquid, followed by cuddling. Believe me, I know what love is. I and my fellows were the ones that created it. We designed your people, programmed your obsession with sex and sexual bonding. Because that it what we need you for. Your \human{} \quo{love} is a pawn on our game, and your idolization of it is a keystone to our \hr{Daggerrain's master plan}{Master Plan}.}









\subsection{The master races did not infiltrate}
A Cabalist or Sentinel talks to a mortal about how his people supposedly infiltrated the kingdoms of mortals.

Big guy: 
\ta{%
  Ha! We never \quo{infiltrated} your world. We \emph{created} it! Your civilization is and was ever our tool. We never conquered you or couped you out. You were created, born and bred as our slaves.}









\subsection{\Criseis{} apologizes for \Ishnaruchaefir}
\Ishnaruchaefir{} has hurt some people. 
\Criseis{} comes in secret and of her own initiative to apologize and ask forgiveness on her master's behalf. 
\hr{Ishnaruchaefir never apologizes}{\Ishnaruchaefir{} never apologizes}. 















\chapter{\ThirdBanewarBook}
\target{Third Banewar}
\target{TBW}
This book details what would later be retroactively called \thirdbanewar, the final showdown with the \banes. 















\section{Overview}









\subsection{The Unravelling brings chaos}
\target{Eschaton: ThirdBanewarBook}
The \hs{Unravelling brings chaos}. 
The world is slowly going mad. 
It will get much worse\ldots{}

See also the general section about the \hs{Eschaton}. 





\subsubsection{Ghosts escape}
Now, as the \hr{Sephirah plan}{\sephirah{} plan} is approaching fruition, the \carcer{} of \Iquin{} is filled to the bursting. 
Due to the \hs{unravelling}, \Iquin{} has grown unstable and leaking. 
Ghosts seep out and escape into the world, in droves. 

Compare to the ghosts and the Spectres in \cite{PhillipPullman:HisDarkMaterials}. 









\subsection{The world goes mad}
\target{The world goes mad}
Have a longer story where the world goes mad. 
More people discover the truth about \iquin, but by then it is too late, and their souls are too deeply bound to \iquin to break free. 

They also discover that there are even older and more malevolent things in the world than \iquin.
Things perhaps even more inimical to them.
So that even if \iquin is a parasitic soul prison, it is perhaps better than the alternative. 

Compare to the movie \cite{Movie:IntheMouthofMadness}. 

See also the general section about the \hs{Eschaton}. 

\citeauthorbook[\quo{First Thought in Three Forms}, p.86--100]{%
  BentleyLayton:TheGnosticScriptures%
}{%
  Bentley Layton%
}{%
  The Gnostic Scriptures%
}{
  Now, when the great authorities knew that the time for fulfillment had come\dash as when labor pains are felt by a lying-in woman\dash and that it was near the door, and that just so, destruction had drawn night, all the elements together shook.
  And the foundations of Hades and the ceilings of chaos moved.
  A great fire broke out in their midsts.
  And the rocky cliffs and the earth moved as a reef is moved by the wind. 
}

Seek inspiration in the Book of Revelation in the \emph{Bible} and other religious eschatology. 

\lyricsbs{Slayer}{Raining Blood}{Raining blood from a lacerated sky.\\
  Bleeding its horror.\\
  Creating my structure.\\
  Now I shall reign in blood!
}

\lyricstitle{\cite{HPLovecraft:TheCallofCthulhu}}{
  The most merciful thing in the world, I think, is the inability of the human mind to correlate all its contents. We live on a placid island of ignorance in the midst of black seas of infinity, and it was not meant that we should voyage far. The sciences, each straining in its own direction, have hitherto harmed us little; but some day the piecing together of dissociated knowledge will open up such terrifying vistas of reality, and of our frightful position therein, that we shall either go mad from the revelation or flee from the deadly light into the peace and safety of a new dark age.
  
  [\ldots{}]
  
  That cult would never die till the stars came right again, and the secret priests would take great Cthulhu from His tomb to revive His subjects and resume His rule of earth. The time would be easy to know, for then mankind would have become as the Great Old Ones; free and wild and beyond good and evil, with laws and morals thrown aside and all men shouting and killing and revelling in joy. Then the liberated Old Ones would teach them new ways to shout and kill and revel and enjoy themselves, and all the earth would flame with a holocaust of ecstasy and freedom.
}

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\ldots{} 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}







\subsection{\Voidbringer must be stopped}
The \dragons{} and other \bane-opponents know that if the Cabal manage to open the portal to \Erebos{} as wide as they did in the \secondbanewar, they will be able to let in millions of \bane{} warriors. 
There is no way in fucking Hell the \Miithians will be able to deal with that many.
They are fewer and weaker than they were last time. 
So they must stop the portal. 








\subsection{Aloof \dragons must be roused}
There were some \hr{Aloof Dragons}{aloof \dragons} who took no part in the \feud.

The aloof ones did not care that \hr{No new Dragons are born}{almost no new \dragons were born} since the \hr{Heart weakened}{weakening of the Heart} began.
The aloof ones were powerful and immortal and had the luxury to wait a few thousands or even tens of thousands of years between procreating. Many of them were over 20,000 years old and saw the war with the \resphain as a temporary nuisance. 

\Ishnaruchaefir and \Secherdamon were similarly old and would likely have thought the same, but the war came horribly close to them when some of their close family members (Nexagglachel and \Ishnaruchaefir's three sons) were destroyed by the \resphain.
Now, in the \thirdbanewar, \Secherdamon or \Ishnaruchaefir had to convince the aloof ones that the war was more than a nuisance and that its conclusion would have great repercussions for all \dragons, even the ones who had fled to \Machai.
Eventually some of the aloof ones became convinced. 
Not all, but enough.

The conclusion of the war WAS important.
The aloof ones could hide in \Machai, but they could not really get away. 
They were still bound by the Heart and would suffer its fate.
Either that, or they would have to evolve, abandoning their Draconic nature entirely and becoming something different.
\Ishnaruchaefir and \Secherdamon knew this might be an option\dash{}to flee to \Machai and abandon \dragonkind\dash{}but it was not a palatable one. 
They both wanted the Draconian race to survive.
\Secherdamon wanted to win the war and was willing to enlist the \xs, with all the associated costs.
\Ishnaruchaefir did not like that idea.
So he looked outward into the universe for other ideas.









\subsection{Ramiel is mad}
Ramiel tries to hide it, but \hr{Ramiel is mad after awakening}{his sanity has suffered badly}. 









\subsection{Clean \humans}
There are some \humans who are \quo{\hr{Clean Humans}{clean}}, in the sense that they have no blood of the \quo{\hs{Men of Light}} and thus do not carry \Lithrim inside them. 
These \humans still have \bane and \resphan blood, but no \Lithrim.
This means that they are unaffected by the \hs{Second Advent}. 

Some of these \humans are among the heroes. 
They help the immortal heroes.
They accomplish some minor things and manage to make a difference. 
Then they die at the end.
But they die a heroic death, having helped ensure that the Ark could escape. 









\subsection{\Neevrai}
Much of this book takes place in \hr{Neevrai}{\Neevrai}. 
This is where the \hs{Ark} is. 

















\section{The \Matrices Battle}









\subsection{\ps{\Daggerrain} master plan}
\hr{Daggerrain's master plan}{\ps{\Daggerrain}{} master plan}, planned and orchestrated throughout twenty thousand years, is unfolding. 

\Secherdamon{} and \Ishnaruchaefir{} oppose him. Ramiel ostensibly serves the \banes, but is actually planning yet another betrayal.

\Daggerrain{} intends to sunder the wall to \Erebos{} and allow the \Voidbringer{} unrestricted access to \Miith{}. 

But \hr{Daggerrain's blind spot}{he has a blind spot}\ldots{}

\Secherdamon, on the other hand, wants to open the gate to Chaos and awaken \Tiamat{} and the \firstgendragons. He has communicated with \KhothSell{} or another one of them. She agrees to help him, but only if he can open the way and make it easy for them to help him. (See section \ref{Rissit communicates with Tiamat}.)

But \Iurzmacul{} plots against his fellow \firstgendragons{}. He does not want to see \Tiamat{} and the others return and devastate \Miith{}. Maybe he tells \Ishnaruchaefir{} and guides him. Maybe \Ishnaruchaefir{} is the son of \Iurzmacul.





\subsubsection{\Dragons fear \Voidbringer}
The \dragons{} know that if \Voidbringer{} gains access to \Miith, they will not stand a chance against the feared \baneking. 
If that happens their only recourse will be to follow \ps{\Vizsherioch} lead and appeal to the \xss. 

\Vizsherioch{} will not accept \Ishnaruchaefir{} as an ally. 
He would prefer to kill him. 

\Vizsherioch{} \emph{wants} to see the \banes{} succeed and \Voidbringer{} brought into the world, because then all of \Miith{} will be forced to turn to him as their only saviour. 
He cannot summon the \xss{} alone, but with enough \dragons{} and \quiljaaran{} and other immortals on his side, he can pull it off. 

He relishes the thought of a war between the \xss{} and the \banelords. 
He is willing to risk the destruction of all of \Miith. 
He kind of thinks like a \xss, remember. 
Plus \hr{Immortal Vizsherioch}{he is more immortal than most}. 









\subsection{Ramiel solidifies his power}
I should let a few years pass between the end of the last book and the beginning of (the serious part of) this one. 
Ramiel needs some time to consolidate his rule as Overlord. 
Not everyone swoons and falls down to worship at his feet. 

And even after some years, he still has rivals and has trouble controlling the dynasty. 

\target{Dasteron's cousins oppose Ramiel}
Among his most vehement foes are \hr{Dasteron's cousins}{\ps{\Dasteron} cousins}, \Sargamel and \Themirod. 

\target{Ramiel uses macho rhetoric as Overlord}
Ramiel uses traditional \Mystraacht \hr{Mystraacht philosophy}{macho rhetoric}. 
But he is actually \hr{Ramiel is critical of Mystraacht ideology}{critical of the \Mystraacht ideology}. 

After his return to Overlordship, Ramiel broods over the doings of the \resphan race.
He is disgusted by their stupidity and hypocrisy. 
The \Mystraacht curse the \CiriathSepher for being shallow and dishonest, but the new, wiser Ramiel can now see that the \Mystraacht are no better themselves, with all their shallow machismo and their hollow talk of \honour and bravery and whatnot.

He thinks: 
\tho{There are times when I wish the \banelords would just come and devour everything. Or whatever it is they plan to do.}

Even among the highest tiers of the \resphain who serve them, there is no one who really knows what the \banelords intend to do.
No \resphan understands the mind of a \bane.









\subsection{\Dragons summon \xss}
\Secherdamon-tachi want to awaken the \xss and summon them to \Miith to fight against the \bane menace. 
Maybe this is mostly intended to slow down the \banes. 
The \dragons know they cannot rely on the \xss as allies.
The \xss might decide it is not worth the effort and pull out of \Miith.
But if the \dragons can at least get the \xss to hold off the \banes, they have a chance. 

The \banes have a thousand-year master plan.
The \xss have little interest in \Miith.
They are likely to give up and go home. 
They will not commit many resources to \Miith. 
It is unlikely that they will save it in the long run, but they may save it in the short run. 





\subsubsection{\Vizsherioch seeks out \daemons}
\Vizsherioch{} seeks out some great and mighty \daemons{} who once served the \xzaishanns{} but have lain dormant for thousands if not millions of years. 

He demands that they serve him. They laugh and reject him, for they have been approached by \dragons{} before. But \Vizsherioch{} is more \xzaishann{} than any \dragon{} ever before. When the \daemons{} realize that, they are impressed and overwhelmed. They agree to serve him. 

He also seeks out \hr{Cosmic gods}{cosmic gods}\dash the same ones that \hr{Ishnaruchaefir seeks out cosmic gods}{\Ishnaruchaefir{} sought out}. But they turn him down. He claims that he is a \xzaishann{} reincarnated, and they laugh.

\lyricsbalsagoth{
  The Hound of Chaos Transcends the Nebulous Palisades of Z'xulth
}{
  The Outer Darkness has cast me from its cavernous maw! 
  So be it\ldots{} the final pieces of this great macrocosmic puzzle shall soon fall into place. 
  It has been millennia since I last visited my beloved brother, Zuranthus\ldots{} 
  and this reunion shall most certainly be steeped in ire! 
  
  The annals of eternity shall soon be illumined by the glorious radiance of my deeds, and the searing fire of my long denied vengeance! Woe unto my dogged nemesis and all those who dare aspire to thwart me\ldots{} for my final ascendence is nigh!
}







\subsection{\Ishnaruchaefir invokes dark gods}
\Ishnaruchaefir{} is forced to invoke various dark gods to seek their power and aid. Some of the same forces that \Secherdamon{} originally invoked to gain power (see section \ref{Rissit invokes dark gods}). 

Perhaps these powers originally helped effect the \hr{Shrouding}{\SecondShrouding}, and now \Ishnaruchaefir{} needs their power to defend the Shroud (see section \ref{To break or preserve the Shroud}).

In the end, a few Elder \Dragons manage to awaken (now that the Shroud is broken) and come to \Ishnaruchaefir's aid.









\subsection{\Iquinian Church preaches}
The \Iquinian Church preaches extra hard. 
The advent of \Lithrim{} is nigh, and the Cabalists want to be sure all the myriad Iquinians are kept under tight control. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  A Chore for the Lost
}{
  Every human being not going to the extreme limit \\
  is the servant or the enemy of man \\
  and the accomplice of a nameless obscenity.
}







\subsection{Ramiel accepts \NexagglachelsCurse}
Ramiel is seduced by the blood of \Nexagglachel{} in his veins. 
He is swayed by the \ps{\dragonlord} voice and ultimately agrees to betray the \banelords, in return for peace of mind from the \hr{Madness of the Curse}{madness and dementia that the curse brings}.

\lyricslimbonicart{The Yawning Abyss of Madness}{
  The winds that carry this esoteric call\\
  emerges from the dungeons underneath my soul. \\
  As I cross the bridge to that darkness, \\
  my eyes are filled with so much death.
}







\subsection{\Ishnaruchaefir hears \Nexagglachel would be proud}
\target{Ishnaruchaefir hears Nexagglachel would be proud}
\Ishnaruchaefir{} meets some \sathariah. 
Possibly Ramiel or \Azraid. 
(Maybe when \hr{Ishnaruchaefir and Azraid plot together, late in TBW}{\Azraid{} conspires with \Ishnaruchaefir}.) 

\begin{prose}
  The \sathariah: 
  \ta{I have a piece of your brother inside of me, you know. 
    I know something of his thoughts. 
    And you know what? 
    I think if \Nexagglachel{} knew what you had done, he would be pleased.}
\end{prose}

The above is not well-meant. 
The \sathariah{} hates \Nexagglachel, because \Nexagglachel{} hates him and drives him mad and ruins his life. 
But it is sincere. 

\Ishnaruchaefir{} takes it as a confirmation that he is on the right track. 
This makes him incredibly relieved. 
He has spent millennia brooding over whether he is \hr{Ishnaruchaefir's stewardship}{carrying on \ps{\Nexagglachel} legacy} properly. 
When \Criseis{} next sees him, he is happier than she has seen him in thousands of years. 
He does not show it, but she, who knows him better than any other, can detect it in his smell and his aethereal threads. 
The pall of darkness that always hangs over him has lifted a little. 










\subsection{Ramiel allies with \Baelzerach}
In secret, Ramiel contacts the \Baelzerach{} and forges a hidden alliance between them and \Mystraacht. They will not openly fight side by side, but they will strike at the same enemies and covertly work to achieve the same goals. 

This is especially sneaky because no one expects it. \Mystraacht{} and \Baelzerach{} are traditionally enemies, having fought many and very bloody wars. 









\subsection{The \banes bring a spaceship to \Miith}
The \banelords{} succeed at bringing a titanic and ancient \hr{Bane technology}{\voyager{} spaceship} from \Erebos/\Nyx{} to \Miith{}. 
It will take all of the \psp{\dragons}{} \xsic{} power to destroy it.

Other people see signs of its approach.

\lyricslimbonicart{Nebulous Dawn}{
  Dark atmospheric winds\\
  are striking towards Earth.\\
  Nihilistic cosmic force.\\
  Asteroid curse.
}

The ship arrives. 
It is a massively powerful juggernaut and wreaks tremendous destruction. 

\lyricslimbonicart{Nebulous Dawn}{
  A blazing phenomenon\\
  launching through the skies.\\
  A deadly impact, tempest chaos.\\
  Utterly devoid of life.
  
  Fountains of fire rise from the lava chambers.\\
  Columns of smoke darken the sky\\
  and cover the landscape in ashes.\\
  Storms with the anatomy of disaster.\\
  Immense swirling winds.
}









\subsection{\Erebos \Matrix Ascendant}
The \bane{} \matrix{} is strong and has almost taken over the world. 
Its corrupting, destructive influence can be felt all over \Miith{}. 
The \hr{Morbus}{\Morbus} is but one of its manifestations. 

\lyricslimbonicart{Nebulous Dawn}{
  An epic eclipse of the Sun.\\
  A rebirth of desolation.\\
  When the cold silence reigns,\\
  darkness sweeps the face of Earth\\
  with infesting freezing torments.\\
  Across the desert wastelands.\\
  Cataclysmic events.
}









\subsection{\Rystessakhin is damaged}
\Ishnaruchaefir{} is in battle, wielding his \hs{glaive}. 
Suddenly it goes wrong, and the unthinkable happens: 
The glaive becomes damaged. 
One of the little blades snaps off. 

\Ishnaruchaefir{} is terrified. 
He knew the Shroud was \hs{unravelling} and it was becoming harder for \Rystessakhin{} to keep it in place. 
\hr{Ishnaruchaefir's Nadir}{His own Nadirs} had been growing steadily worse as a result. 
But had never imagined that it would come to this. 

He immediately unsummons the glaive. 
Then he spends all his available energy on fighting his way free and escaping from the fight. 

He realizes that something is catastrophically wrong. 
The Shroud is under attack, and the pressure on poor \Rystessakhin{} has become so great that even her physical form is chipping and falling apart. 
The status quo is crumbling, and he cannot hope to maintain it any longer. 
He needs to change his strategy.
Something drastic must be done. 








\subsection{\Azraid conspires with \Ishnaruchaefir}
\target{Ishnaruchaefir and Azraid plot together, late in TBW}
\Azraid{} conspires with \Ishnaruchaefir. 

They have \hr{Ishnaruchaefir and Azraid develop empathy}{talked before} and have a relationship as friendly rivals. 
They have even \hr{Ishnaruchaefir and Azraid plot together, early in TBW}{plotted together before}. 
They are both philosophers who feel somewhat estranged from their races, so they have a certain mutual understanding. 

Gradually and ever so subtly through \quo{Sentinels of \Miith} \Ishnaruchaefir becomes convinced that Azraid is on the level, and he also begins to suspect the general nature of Azraid's plan. 
So when Azraid finally approaches \Ishnaruchaefir and asks for his cooperation in a secret venture, \Ishnaruchaefir has a bit of a \quo{what took you so long?} attitude, and the whole interaction has a \quo{I know you know I know you know\ldots{}} frame.
The two have each formulated ideas that can be combined into a useful whole.

Now \Azraid{}, for the first time \emph{ever}, comes clean and reveals (part of) his master plan to \Ishnaruchaefir. 
\Ishnaruchaefir{} is the best person he can trust with his plan. 

\Azraid{} also needs Ramiel, but he cannot trust him.
Ramiel is too volatile, too unreliable. 
\Ishnaruchaefir{} \hr{Ishnaruchaefir's impulsiveness}{has spent all his impulsiveness long ago}, so \Azraid{} knows he is dependable.

\Ishnaruchaefir{} agrees to cooperate with his old enemy. 

Perhaps it is here \Azraid{} \hr{Ishnaruchaefir hears Nexagglachel would be proud}{tells \Ishnaruchaefir{} that \Nexagglachel{} would be proud}. 








\subsection{\Ishnaruchaefir realizes what he must do}
\target{Ishnaruchaefir realizes what he must do}
\Ishnaruchaefir{} realizes that if he is to truly make a difference in this war, he will need more power.
(He \hr{Ishnaruchaefir begins to realize what he must do}{began to realize this earlier}.)
He will need true Gnosis of his own Aenigma. 
To do this he has to look deep inside himself and come to terms with himself. 
This means he must overcome a ton of traumata, which have festered inside him ever since he \hr{Ishnaruchaefir slays his beloved}{killed \Rystessakhin} and \hr{Ishnaruchaefir goes into the void}{fled into the void}. 

He must make peace with the memory of \Rystessakhin{}. 
He must save himself before he can hope to save the world. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  As deep cuts of truth.\\
  As a fire that closes the wound.\\
  So is my redemption.
  
  Beyond repentance.\\
  This is the ordeal of fire.
}

It will be hard, expensive and bloody, for both him and the world. 
But it will be worth it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{Invocation}{
  Come suffering, Apocalypse.\\
  Release the fires of Hell.\\
  I call upon destruction and despair.\\
  Not for vengeance, not for power.\\
  Beneath the ashes I walk.
}

At last he takes a deep breath and prepares to do it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  Behold, an angel of vengeance.\\
  A lion. A sword of fire. \\
  Alas, the burden of my heart\\
  is violence undone\\
  Pain unfulfilled.\\
  Silence.
}

Finally he does it. 

\citebandsong{Ihsahn:TheAdversary}{Ihsahn}{The Pain Is Still Mine}{
  When I finally cut \\
  deep into the flesh of guilt,\\
  the un-naked body of shame\\
  and the veins of repentance open wide,\\
  sending rivers of blood into my mouth.
  
  The pain is still mine.
}








\subsection{\Harbeth dies}
\target{Harbeth dies}
\Harbeth dies for some reason. 

Maybe \Zereth also dies. 
Most of the \hr{CS heirs die}{\CiriathSepher{} heirs die}. 















\section{Climactic Battle}
Near the end there is a great, climactic battle between the \bane/\resphan{} forces and some \quo{good guys}. 
There are very few \dragons{} (perhaps only \Ishnaruchaefir{} and his companions), because most \dragons{} support \ps{\Secherdamon} gambit, hoping to utilize the \pps{\banes}{} Shroud-weaving spell to bring the \firstgendragons{} into the world and have them vanquish the \Voidbringer{} and his legions.







\subsection{\HothNrul}
\target{Hoth-Nrul summoned}
\Vizsherioch{} and his cohorts manage to bring a mighty ally to \Miith: 
\hr{Hoth-Nrul}{\HothNrul}, a \xsic{} godling. 
\HothNrul{} is intended to spearhead the coming \xs{} invasion of \Miith. 

Later, \Ishnaruchaefir-tachi communicate with \HothNrul{} and convince the alien god that it is in its interest to attack \Daggerrain.
So \HothNrul{} seeks out the \banelord. 

\HothNrul{} has difficulty attacking \Daggerrain, for he is well-hidden-away. 
But it manages to do some damage. 
When \Daggerrain{} is distracted by the \xs{}, \Azraid{} and Ramiel strike and fuck up \Daggerrain. 

\HothNrul{} \hr{Hoth-Nrul left behind}{ends up the same place where \Daggerrain{} is}. 







\subsection{\Ishnaruchaefir leads \dragons}
\target{Ishnaruchaefir leads Dragons to war in TBW}
\Ishnaruchaefir{} does not believe in this gambit. He has no faith in \Tiamat{} and her brethren and does not think they will come to help. 
So he works to persuade the \dragons{} (including some \hr{Aloof Dragons}{aloof ones}) to fight, to fly with him against \ps{\Daggerrain}{} legions. 

At the last moment, he succeeds. 
Have a massively epic scene where \Ishnaruchaefir{} flies at the head of a massive flight of a \dragons, flanked by hundreds of \rachyths, \drakes{} and \pdaemons, to engage the \bane{} armies and seize victory.
They are awesome to behold as they return to \Miith in full force. 
Dozens of Elder \Dragons, several of them \shaeeroth.

Compare to: 

\begin{itemize}
  \item 
    \bandsong{Bal-Sagoth}{Black Dragons Soar Above the Mountain of Shadows}. 
  \item 
    The scenes in \authorseries{Richard Knaak}{War of the Ancients} where everyone holds their breath for the \dragons{} to come to their aid, and where they finally do come and save the day.
  \item 
    The scenes in \authorbook{Graham McNeill}{Fulgrim} p.472, where the Alpha Legion, Word Bearer, Night Lords and Iron Warriors come to the \quo{rescue}. 
\end{itemize}

\citeauthorbook[p.344]{ClarkAshtonSmith:TheDarkEidolon}{Clark Ashton Smith}{%
  The Dark Eidolon%
}{
  Yea, the undying worms of fire and darkness have come forth like an army at thy summons\ldots
}







\subsection{The Advent of \Lithrim}
\target{Lithrim arises}
\target{Second Advent}
\target{Second Advent of Lithrim}
\Lithrim{} finally arises. 

Mankind is very Shrouded, \naive{} and stupid. 
Not quite as well-meaning and {innocent} as the \scathae, but not all that far from them.
That is why it is so effective when their inner \Erebean{} darkness is finally released in the culmination of the \Morbus{} plan. 

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Sola Fide
}{
  Some rejoice of the children's innocence and smiles\\
  Others of their shameful defloration \\
  by the ministers of Christ, swollen by arrogance and lust\\
  Jesus spoke words of wisdom: \quo{Let the children come to me}\\
  What's more enthralling indeed \\
  than ruining through them the genesis of life itself?\\
  Dive deep into the blue eyes of the newborn \\
  and thou shalt get a glance of heaven\\
  When this dive reveals despair, \\
  hideous ruins of the glory of Hell\\
  The serving sons of disobedience proclaim \\
  Vengeance belongeth unto Him\ldots{}
}

\citebandsong{DeathspellOmega:SiMonumentumRequiresCircumspice}{%
  Deathspell Omega
}{
  Jubilate Deo (O Be Joyful in the Lord)
}{
  Innocence sacrificed and heaven denied\\
  Iniquity divine\dash no repentance\dash over mankind\\
  Mind-raped, self-devoured, empty god-eyed\\
  Transgression coercive, Redemption never to be found

  Under the altar of cannibalism\\
  Man hast (thou) confessed the spiritual schism\\
  And without pride mourned the loss of freedom,\\
  Our blessed Lord have condemned you to martyrdom
  
  Let everything that hath breath praise the Lord, \\
  praise ye the Lord.
}

It is the culmination of that which began with \ps{\Thanatzil} noble sacrifice. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  The advent of Plerosis is the destiny of Man \\
  and shall shatter up to the Heavens,\\
  A savage aperture to the High Mass of the Comforter
}

It is cataclysmic and destructive. 
It unleashes all the wicked, destructive Entropy that, as it turns out, were the building blocks of Man all along. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  Instigating manifold quadrants of industrialized death,\\
  An avid Moloch, never satiated, an endless Feast,\\
  Following the principle of reversibility of merits,\\ 
  shattering up the Word\\
  As Pillars of grayish Soulfire spurt out to a bereaved firmament
}

Man instinctively welcomes the advent of \Lithrim.

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  The unreservedly open spirit, \\
  open to death, to torment, to joy,\\
  The open spirit, open and dying,\\
  Suffering and dying and happy, \\
  stands in a certain veiled light:\\
  That light is divine.\\
  And the cry that breaks from a twisted \\
  mouth may perhaps twist him who utters it,\\
  But what he speaks is an immense alleluia, \\
  flung into endless silence, and lost there.
}

But it is also scary. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  From very high above a kind of stillness \\
  swept down upon me and froze me\\
  It was as though I were borne aloft \\
  in a flight of headless and unbodied angels\\
  Shaped from the broad swooping of wings, \\
  but it was simpler than that\\
  I became unhappy and felt painfully forsaken, \\
  as one is when in the presence of God
}

Some \humans{} fight against it. 

\citebandsong{BeyondTwilight:TheEdge}{Beyond Twilight}{Salem}{
  Entombed by the will of the night.\\
  All your thoughts deflowered.\\
  Waived all of your beliefs\\
  in this midnight hour. \\
  Search your past, try and make it back.\\
  All your strength overpowered.\\
  Unknown forces run you through \\
  in the shadow of the black tower.
  
  The witches of Salem hold your fate. 
  
  Relief obtained in sacred mass.\\
  All your sins forgiven. \\
  The ultimate sign of witchery.\\
  The total lack of sanity.
}

\Humans{} lose their individual identity. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  And the victim, blind to the radiating Light of Truth, \\
  stuttering, repeats:\\
  Lamma Sabacthani?\\
  Lamma Sabacthani?\\
  Lamma Sabacthani?
  
  Consummatum est.
}

Mankind becomes a god: \Lithrim. 

\citebandsong{DeathspellOmega:Kenose}{%
  Deathspell Omega
}{
  \Kenose
}{
  I am the son of Man, \\
  and this in erring reason's spite, is my pride\ldots{}\\
  War, be enthroned, a form of divine retribution!\\
  Execution, be sacred, agent of divine Providence!
  
  The stillness of Contemplation \\
  is allowed in billions of woeful cries,\\
  So astonishingly simultaneous and in unison,\\
  Each and every second, \\
  They defuse each other in such a perfect manner,\\
  Equaling the most inscrutable of all silences\\
  Doctrine of Mystical Substitution, Mystical Body, \\
  Sanctorum Communionem,\\
  Celebrate the Sin of one reflecting, \\
  tectonic forces alike, upon the multitude
  
  The purest of all Holocausts shall be perpetrated\\
  By a loving hand, never knowing if it provided felicity\\
  Or the vilest of everlasting torments\\
  No man can see Me and live!
}

When the \humans{} become the fell, abhorrent \Lithrim, they (or the smarter of them) at last realize the purpose of their otherwise empty and wretched lives. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  The act whereby being\dash existence\dash is bestowed upon us\\
  Is an unbearable surpassing of being,\\
  An act no less unbearable than that of dying.\\
  And since, in death, being is taken away from us \\
  at the same time it is given us,\\
  We must seek for it in the feeling of dying,\\
  In those unbearable moments \\
  when it seems to us that we are dying\\
  Because the existence in us,\\
  During these interludes,\\
  Exists through nothing but a sustaining and ruinous excess,\\
  When the fullness of horror and that of joy coincide.
  
  As I waited for annihilation, all that subsisted in me\\
  Seemed to me to be the dross over which man's life tarries\ldots{}
}

But they lose their \humanity{} in the process. 

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega%
}{
  Mass Grave Aesthetics
}{
  The black Idol fills the veil of flesh with noxious smoke, \\
  Depicting primal human experiences indifferently, \\
  Contemptuous of moral concerns, dehumanized \\
  The howling of wolves and the destructive sword \\
  are portions of Eternity, \\
  Too great for the eyes of merely a man
}

\citebandsong{BlindGuardian:FTB}{%
  Blind Guardian%
}{
  Hall of the King
}{
  You're the birth and you're the end.\\
  You've been hurt but you're not dead.\\
  Discovering you is what should never be.\\
  Poisoned are our souls and dark our hearts.\\
  Ruins we have left to rule the world.\\
  Destructive are our minds. It's much too late.\\
}

But they gain new insight as they leave their \human{} forms:

\citebandsong{DeathspellOmega:FromtheEntrailstotheDirt}{%
  Deathspell Omega%
}{
  Mass Grave Aesthetics%
}{
  Violence exists I the moment \\
  when the eye turns upwards into the head, \\
  When inversion is complete and total \\
  The darkness of the upturned eye is not the absence of light \\
  But the process of seeing being taken to its limit \\
  That thorough derangement of the senses, \\
  Way beyond the deceptive conflict between darkness and light \\
  Opens perceptions to the tyranny of the Chekhinah
}

\Lithrim{} is a slave under the \psp{\banelords}{} command. 

\citebandsong{DeathspellOmega:CrushingtheHolyTrinity}{%
  Deathspell Omega
}{
  Diabolus Absconditus
}{
  I can utter no word, O my God, \\
  unless I be permitted by Thee\\
  And can move in no direction \\
  until I obtain Thy sanction\\
  It is Thou, O my God, \\
  who hast called me into being through the power\\
  Of Thy might, and has endued me \\
  with Thy grace to manifest Thy Cause
}

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  Bread of Bitterness
}{
  From a supplication without response, \\
  the essence of man, his ground giving way, \\
  comes illumination by a sun of great evil \\
  that sets aflame the inner core \\
  and enthrones suffocation and the intolerable without respite \\
  as the joyful reward for a million aborted truths.
  
  This silence that among all man has charged with sacred horror, \\
  it becomes sovereign, in repugnant nativity, \\
  and detaches itself from the bonds \\
  which paralyse a vertiginous movement towards the void.
  
  Breathless ecstatic experience,\\
  it opens the horizon a bit more,\\
  this wound of God;\\
  it is the assassination of the abyss of possibilities, \\
  the depths of being left to holy vultures. 
}





\subsubsection{Sentinels realize \Lithrim}
The Sentinels finally realize what \Lithrim is.
(Do not reveal this until the \humans have already coalesced into \Lithrim.)

\begin{prose}
  \ta{\Lithrim, the hideous that feeds on the souls of the \humans.}
  
  \ta{No. 
    It is worse than that.
    \Lithrim does not feed on the \humans.
    \Lithrim \emph{is} the \humans!
    Picture it.
    Every \human every born into the \iquinian faith, for thousands of years, has been gathered for this purpose.
    Each \human soul is puny, of course, but they number in the hundreds of millions, if not billions.
    All coalesced together to form a nightmare god of colossal power!}
\end{prose}










\subsection{The portal opens}
\Lithrim{} opens the way for the \Voidbringer. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Perfect Dark%
}{
  Hold the candle\\
  Pass the flame\\
  We're all in this together \\
  Cosmic winds are gathering\\
  Coming your way\\
  Telling you you are only a fragment\\
  A fragment of time 
  
  And it's perfect dark\\
  It's perfect dark here\\
  Hear the angels screaming
}





\subsubsection{People feel the \Voidbringer}
As the Cabal plot nears fruition and they are opening the gate to \Erebos, \Miithians can feel the presence of the \Voidbringer: 
An ever hungry, ever consuming emptiness, completely inhuman. 
The older immortals remember it from the \secondbanewar. 





\subsubsection{\Banes{} slip through}
Many \lesserbanes{} slip through into \Miith. 
Not in the same millions that got through in the \secondbanewar, but still quite a lot. 
But not so many that the combined \dragons{} and \resphain{} cannot deal with them\ldots{} hopefully. 

















\section{Ramiel the Betrayer}
\target{Ramiel betrays Voidbringer}
\target{Ramiel betrays Banes}









\subsection{Summary}
\hs{Ramiel} has decided that he will no longer serve the \banelords. 

\lyricsbs{Dream Theater}{In the Presence of Enemies}{\obeylines%
  My soul grows weaker.\\
  He knows and he waits.\\
  He watches over me,\\
  standing at the infernal gates.\\
  In the hour of darkness,\\
  the moment I feared has passed,\\
  the moment I lost my faith.\\
  Promising salvation.\\
  My soul is my own now.\\
  I do not fight for you,\\
  Dark Master!
}

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  Hellfire%
}{
  Before me now I see a dying planet.\\
  Captured souls with microchips implanted.\\
  When warning came you stayed the same.\\
  When warning came you stayed the same.\\
  I am crumbling over the obstacles.\\
  Nothing left to entertain. \\
  The smell of burning corpses. \\
  A new world domain.
  
  Before me now I see a future\\
  A future black\\
  Oh come and save me\\
  I'm under soul attack
  
  I will break out from this madness\\
  There is nothing here but sadness\\
  I'm burning in the hellfire\\
  There must be a way\\
  Waiting for the day\\
  
  Hellfire burns higher\\
  Higher, higher. \\
  Only blood remains\\
  There is nothing more to gain \\
  Take me.
}

He now plans to betray the \banes. 
He intends to siphon energy from the \Voidbringer, thus empowering himself enough to overpower \Daggerrain{} and slay or banish him. 
It is a mad scheme, but Ramiel has always been one for mad schemes. It stems from his sublime arrogance and megalomania (see section \ref{Ramiel's megalomania}). 

It is a good plan, but \Daggerrain{} is too clever. 
The \banelord{} has always known that Ramiel was a loose cannon and could not be trusted, so he had taken precautions. 
When Ramiel finally betrayed the \banes, they were ready for him. 

So Ramiel's plan fails\ldots{}

\ldots{} or would fail, if not for the intervention of \Azraid. 
\Azraid{} had always played the loyal Cabalist, faithful servant of the \banelords, but \hr{Azraid hates Banes}{in secret he has always hated them} and \hr{Azraid plots against Banes}{plotted against them}. 
He anticipated Ramiel's betrayal and planned for it. 
So when Ramiel fails, \hr{Azraid helps Ramiel betray Banes}{\Azraid{} steps in and helps him}. 

\ps{\Azraid} gambit cannot succeed without Ramiel's help. 
But he cannot tell Ramiel about it before the very last minute, because he doesn't trust Ramiel's ability to keep the secret. 
(It is \emph{hard} to keep secrets from \Daggerrain.) 
It is thus something of a \trope{XanatosRoulette}{Xanatos Roulette}. 

So, in the end, it turns out that \Azraid{} was \hr{Daggerrain's blind spot}{\ps{\Daggerrain}{} blind spot}. 





\subsubsection{The Ark}
\target{Ark}
\index{Ark}
The plan (a collaborative effort between \Azraid{} and \Ishnaruchaefir) is to use the wild threads of the collapsing Shroud to \quo{cut} free a chunk of \Miith{}, forming a pocket Realm. 
They then hope to be able to close the way behind them, setting up a makeshift barrier by piecing together fragments of the shattered \CrystalSphere{} and Shroud.

They will then have formed a new mini-Realm, a micro-\Miith{} torn loose. 
This will be their Ark. 
A small population of \Miithians should be able to escape in this Realm. 
The makeshift barrier will keep the \banes{} out for a short while, while the masterminds use their magic to twist the fabric of space around them propel the Ark away through the universe, to a place where the \banes{} cannot easily find them. 

The Ark is built from the ruins of the \hr{Sethicus tomb}{tomb of \Sethicus}, which lies in the Realm of \hr{Neevrai}{\Neevrai}. 

It will be fucked-up difficult, but \Azraid{} is ready. 
He has spent millennia preparing for this day, and he is prepared to sacrifice his life to see it through. 
And he has \ps{\Ishnaruchaefir} awesome Gnosis helping him. 

In the end, \Ishnaruchaefir{} and Ramiel end up on the Ark, while \Azraid{} destroys himself in the process. 

Perhaps the Ark is not a chunk of planet, but a spaceship. 
Perhaps a commandeered \bane/\resphan{} ship. 
If so, it is huge. 
A colony ship. 
A world-ship. 

The Ark was actually an unfinished relic created by \Sethicus. 
It was a part of \hr{Sethicus plan}{his masterplan} to escape \Miith before \hr{Sethican eschatology}{it was destroyed}. 
As was to be expected of an element of \Sethicus's plan, the Ark required a tremendous sacrifice of blood and life and Heart-power to launch it, and more sacrifice still to sustain it on its journey. 

Compare to the movie \cite{Movie:Watchmen}. 





\subsubsection{It all takes place in the \matrix{} world}
Note that all of this takes place in the world of the \matrices. 
The three may not physically meet at all. 
They simply pull at cosmic strings using their \vertex{} abilities. 
Any any \quo{portals} are not physical portals, but a ubiquitous thinning of the Shroud allowing passage into \Erebos{} or somewhere else. 





\subsubsection{Why they wait so long}
One might think \Azraid{} could have betrayed the \banes{} long ago. 
But that would not have worked. 
He was not confident he could have done enough damage before he was caught, eliminated and replaced. 

No, this is a unique opportunity. 
\ps{\Azraid} betrayal has to happen \emph{after} the advent of \Lithrim. 
See, they need to rely on the Shroud-wide chaos and fluctuations that \Lithrim{} creates, and use them to set the Ark free. 





\subsubsection{Ark fueled by dead \ophidians}
The Ark is a big-ass \hs{living machine}. 

The Ark is built from \Sethicus's old tomb. 
\Sethicus was buried with many other \ophidians and perhaps even \dragons.
Many of them still lie there, dead but dreaming. 
These can be used as fuel to power the Ark and keep it alive. 
When the dead learn about this plan, they are nonplussed. 
They see it as betrayal and fight back. 
They would rather see everyone perish with them than be betrayed and sacrificed for someone else's gain. 

The undead cannot move, but they still have arcane power. 
\Ishnaruchaefir has to expend more of his already badly strained power to overcome the dead and force them to become fuel. 
This is also psychologically hard for him: 
It is another horrible betrayal of his own people, even violating the \dragons' important \hr{Dragons do not eat Dragons}{cannibalism taboo}. 
It is another gruesome scar on his soul. 
But it must be done, and \Ishnaruchaefir knows he is the only one hard enough to do it. 

This should be a climactic thing, another \quo{everything almost going awry at the last minute} twist at the end of the last book. 









\subsection{Ramiel drains the \ps{\Voidbringer}{} power}
Ramiel tries to betray the \Voidbringer. 
This is similar to how Astronema betrays Dark Specter and drains his power in \emph{Power Rangers in Space}. 
%It stems from Ramiel's sublime arrogance and megalomania (see section \ref{Ramiel's megalomania}). 

He absorbs some of the \ps{\Voidbringer}{} power. 





\subsubsection{How it feels}
He feels himself swimming adrift in an endless, bleak ocean of dark, Entropic power, feels how it almost devours him and his sanity.

\lyricsbs{Bal-Sagoth}{Summoning the Guardians of the Astral Gate}{
  The ravening black worms of madness 
  are devouring the shredded remnants of sanity 
  as I return to my slumbering steel-clad body\ldots{} \\
  but as the dream-veil lifts, I feel my limbs transform, 
  flesh becoming cold stone\ldots{} \\
  enshrouded by a dark mantle of obsidian. \\
  And the laughter of the Guardians echoes, 
  carries upon the winds of this spectral eve.
}

Actually, he began doing this much earlier, but it takes a while before \Daggerrain{} \quo{discovers} his treachery. 

Ramiel plans to use his \carcer against the \Voidbringer.

\citebandsong{BlindGuardian:IFTOS}{Blind Guardian}{%
  The Script for My Requiem (demo version)%
}{
  Battle rages higher and higher. \\
  Akron starts to feel my hate. \\
  There's no escaping for the dark souls \\
  I can't control anymore, anymore. \\
  What started in the underworld, \\
  it should be finished here and now. 
  
  I know his tricks, black magic power. \\
  But now it's time for him to say goodbye. \\
  There's only one thing left, the dawn shall arrive. \\
  We've got to get it past, fear the dark side. \\
  Turn off his light. \\
  Turn off his light.
}





\subsection{Ramiel fails}
\target{Ramiel as Xanatos Sucker}
\Daggerrain{} is too clever for Ramiel. 
He had anticipated Ramiel's betrayal and easily stops him. 
He is about to kill and destroy Ramiel\ldots{} 

Before his death, Ramiel's life flashes before his eyes. 
He realizes that \Daggerrain{} must have anticipated his every move and planned accordingly. 
He has been playing straight into \ps{\Daggerrain}{} hands the whole time. 

He truly \hr{Ramiel is nothing}{is nothing}\ldots{} 
or so he fears. 

Compare a \hr{Azraid as Xanatos Sucker}{similar scene with \Azraid{} much earlier}. 
Also compare to the scene in \emph{\JuukenSentaiGekiranger} episode 46 (or so) where Rio discovers that his entire life has been masterminded by Long. 

We see inside Ramiel's head as he struggles against \Daggerrain{} and almost dies. 

\lyricsbs{Hate Eternal}{Path to the Eternal Gods}{
  On this journey into death, \\
  I am beside myself in tremendous bliss,\\
  For this allegiance has been made. \\
  Shall my sins be absolved, \\
  washed away by the blood of the sacred lambs? \\ 
  Yet I am not amongst the flock.
  
  The remnants of my life now become my vast illusions,\\
  whilst exiled from your grace. 
  
  With fortitude, with courage, 
  I face all my fears, \\
  on my path to the eternal gods. \\
  With my wrath, with my disdain, 
  I face all my fears, \\
  on my path to the eternal gods.\\
  As I cross over into my final place, 
  I face all my fears, \\
  on my path to the eternal gods.\\
  As I bear trials in my final resting place, 
  I face all my fears, 
  on my path to the eternal gods.\\
}





\subsection{\Azraid helps Ramiel}
\target{Azraid helps Ramiel betray Banes}
At the last moment, before \Daggerrain{} would have destroyed Ramiel, \Azraid{} steps in and backstabs \Daggerrain. 

Ramiel realizes that he had been overreacting before, overestimating \ps{\Daggerrain}{} omniscience and underestimating his own capability. 
Some parts of his plan actually \emph{were} successful, not covered by the \ps{\banelord}{} \trope{XanatosGambit}{Xanatos Gambit}. 
He regains some faith in himself. 

Together, the two \satharioth{} push \Daggerrain{} back. 
% It closes behind him. 
Ramiel now manages to hold \Daggerrain{} occupied while \Azraid{} works his magic and tears the \hs{Ark} loose. 





\subsubsection{Ramiel and \Azraid{} as kindred spirits}
\Azraid{} criticizes Ramiel for being too overt and honest (\hr{Mystraacht philosophy}{and would be expected of a \Mystraacht}), making him predictable. 
In contrast to \Azraid{} himself, who has managed to creep under even \ps{\Daggerrain}{} radar for twenty thousand years. 

But he is also sympathetic, because he recognizes that Ramiel's situation is like a mirror of his own. 
Back when \Daggerrain{} manipulated the young \Azraid{} into betraying and murdering his brother \Damiarch, he was similarly shocked and disillusioned. 
He shares this with Ramiel. 
This is a rare \trope{PetTheDog}{Pet the Dog} moment for \Azraid. 

A new understanding and empathy suddenly exists between the two \resphan{} lords. 
They are now kindred spirits. 
After this battle they part, not as friends, nor allies, but with a deeper mutual respect than previously. 

\begin{prose}
  Ramiel: 
  \ta{\Azraid. Were you among those who betrayed \Zachirah{} and me?}

  \Azraid: 
  \ta{LOL. Ramiel. 
    I have deceived the \banelords{} for thousands of years. 
    I have deceived everyone. 
    Among all the \resphain, there is no greater fraud than I.
    If I were to answer \quo{no}, would you believe me?
    I would not believe me.}
\end{prose}






\subsubsection{Ramiel imagines hearing \ps{\Daggerrain}{} voice}
Ramiel jokingly imagines hearing \ps{\Daggerrain}{} voice in his head: 
\daggerrain{A minor setback. 
I have planned for this contingency. 
It will take us another 3651 years to get out plan back on schedule\ldots{}} 
(The number 3651 is a random one that Ramiel pulls out of his ass, but it sounds like something \Daggerrain{} might say.)








\subsection{\Azraid dies\ldots{} maybe}
\target{Azraid dies}
Maybe \Azraid{} dies. 
He sacrifices himself in order to violently disrupt the \Erebean{} \matrix{}, thus causing it to implode and collapse faster than \Daggerrain{} can restore it to order. 

\ps{\Azraid} death leaves \CiriathSepher{}, its hierarchy and \matrix, in chaos. 
(\hr{CS heirs die}{Not much is left} of the \hr{CS order of succession}{\CiriathSepher{} order of succession} at this time.)
It is now up to Ramiel to pick up the pieces and lead the \resphan{} race, if they are to have a chance of surviving. 

Compare to Anomander Rake's sacrifice in \cite{StevenErikson:TolltheHounds}. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Surrender\\
  Lost in the dark\\
  Without angels to guide me 
  
  Hands of death reaching out for me\\
  I'm longing to rest\\
  I see myself move in need of power
}

He knows the \banes{} better than any other. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  I've looked straight into the eyes of demons rising\\
  So close.\\
  I've had one foot on the other side\\
  For so long. \\
  I've seen evil so evil that all living died\\
  The devil is near.\\
}

He wants to stop the \iquin{} plan. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  You may fool the people, but you can't fool me\\
  No more, not anymore. 
  
  And all the souls turned black\\
  There is no way back
}

He dies. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Stranded with the darkness\\
  It's so cold in here \\
  I feel the rush within me
}

He hopes that \Miith{} (or a fragment of it) now has a future. 

\citebandsong{BeyondTwilight:TheDevilsHallofFame}{Beyond Twilight}{%
  The Devil's Hall of Fame%
}{
  Time will mend\\
  Ease the sorrow\\
  Take my hand\\
  There's no tomorrow
}











\subsection{\Daggerrain falls}
\target{Daggerrain falls}
\Daggerrain{} has fallen. 
And the worst part is that the link between \Erebos{} and \Nyx{} fell with him. 
\hr{Daggerrain is the gate}{\Daggerrain{} \emph{was} the link}. Without him, the way is closed permanently. 
Now, the only way for the \banes{} to return from \Erebos{} would be to send spaceships, like they did the first time around. 
That might take millennia, because \Erebos{} and \Miith{} are very distant from each other. 





\subsubsection{\HothNrul{} left behind}
\target{Hoth-Nrul left behind}
\HothNrul{} ends up the same place where \Daggerrain{} is. 
No one knows what becomes of it. 
Perhaps it gets destroyed by \Daggerrain{} and his fellow \banelords\ldots{} if it is even possible to destroy a \xs, which is not known. 
Or perhaps it returns to the \xs{} homeworld. 

Or perhaps it wins. 
It is very difficult to get a clear idea of the balance of power between so \uber-powerful beings as \xss{} and great \banelords. 

The survivors of the war are not sure \HothNrul{} will not return to wreak more havoc on them. 
But they hope not. 















\section{The Fall of the Shroud}
\subsection{\ps{\Ishnaruchaefir} glaive is destroyed}
\target{Ishnaruchaefir's glaive is destroyed}
\target{Glaive is destroyed}
Throughout most of the story, \hr{Ishnaruchaefir fights to preserve the Shroud}{\Ishnaruchaefir{} has fought to preserve the Shroud}. But at the end, he lets himself persuade to assist in unravelling the Shroud. \Triestessakhin{} is the one who persuades him. 

Ultimately, \hr{Ishnaruchaefir's glaive}{\ps{\Ishnaruchaefir} glaive} is destroyed, its Shroud-weaving effect (as a \hs{weaving artifact}) is broken, and the soul of \Triestessakhin{} is released. 
\hr{Glaive must be destroyed}{This had to happen}. 

She is quite insane after these many thousand years inside the sword, but he manages to lead a conversation with her. She is bitter and tries to make him repent. 

\Ishnaruchaefir: 
\ta{%
  I mourn what I have done, and at times I even regret. 
  But I would not change it, and given the chance, I would do the same again.}

Compare to the scene with Lord Soth and his wife at the end of \emph{Spectre of the Black Rose} by James Lowder and Voronica-Whitney Robinson. 



% \subsection{Daggerrain's epilogue}
% In the end, the \banes{} are defeated and the way to \Erebos{} is sealed shut once more. 
% 
% In the very last chapter, \Daggerrain{} holds a monologue, telling his subordinates to get to work. Having planned for this contingency, he has a new plan to reclaim \Miith{}, another four thousand years from now. As he says: \daggerrain{I have waited thirty thousand years. Another four thousand is nothing to me.}







\subsection{\Vizsherioch falls asleep}
\target{Vizsherioch falls asleep}
\Vizsherioch{} \hr{Vizsherioch's XS blood}{has too much \xsic{} blood} and is susceptible to the \hr{XS slumber}{\xsic{} slumber}. He uses his \bane{} blood to draw upon \Erebean{} power to negate this effect. 

But when \hr{Daggerrain falls}{\Daggerrain{} falls}, his connection to \Erebos{} fails and he falls prey to the \xsic{} slumber. 







\subsection{\Miith is once again in \Miithian hands}
\hr{Daggerrain falls}{\Daggerrain{} is gone}. So now the supreme leaders of the \resphain{} are Ramiel and \hr{Azraid}{\Azraid}. There are still \banelords, but they cannot replenish their number, so they will eventually be hunted down and destroyed. 

Similarly, \Vizsherioch{} falls prey to the \xzaishannic{} slumber. The lords of \dragonkind{} are \Ishnaruchaefir{} and some other \uber-dragons. 

The \Erebean{} and \Machaic{} overlords are gone, and only their descendants remain. The future of \Miith{} now once again belongs to \Miithian{} powers. 









\subsection{The Shroud is torn}
In the process of this whole thing, the Shroud has been ripped and torn and now lies greatly weakened. A climax of this was the \hr{Glaive is destroyed}{breaking of the glaive \Triestessakhin}. 

The \charade{} is breaking apart and the old world order is crumbled. 

The \hs{Unravelling brings chaos}. 
The world will descend into chaos and anarchy. 

\lyricstitle{\cite{HPLovecraft:TheCallofCthulhu}}{
  The most merciful thing in the world, I think, is the inability of the human mind to correlate all its contents. We live on a placid island of ignorance in the midst of black seas of infinity, and it was not meant that we should voyage far. The sciences, each straining in its own direction, have hitherto harmed us little; but some day the piecing together of dissociated knowledge will open up such terrifying vistas of reality, and of our frightful position therein, that we shall either go mad from the revelation or flee from the deadly light into the peace and safety of a new dark age.
  
  [\ldots{}]
  
  That cult would never die till the stars came right again, and the secret priests would take great Cthulhu from His tomb to revive His subjects and resume His rule of earth. The time would be easy to know, for then mankind would have become as the Great Old Ones; free and wild and beyond good and evil, with laws and morals thrown aside and all men shouting and killing and revelling in joy. Then the liberated Old Ones would teach them new ways to shout and kill and revel and enjoy themselves, and all the earth would flame with a holocaust of ecstasy and freedom.
}

A new world order will establish itself, although it may take centuries. 

\index{technology}
\Ishnaruchaefir{} predicts that the Shroud will mostly unravel and fade away. With the loss of the Shroud, \hs{technology} will again accelerate. 

A suggestion for an epitaph: 

\lyrics{
  The \charade{} is broken. \\
  The Shroud is sundered. \\
  Now, let the arms race begin.
}

Knowledge will escalate, and so will war. 
In a way, this is \hr{Ishnaruchaefir sees three futures}{\ps{\Ishnaruchaefir} nightmare} come true. 

\lyricsauthorbookpage{Graham McNeill}{False Gods}{157}{
  I saw beyond and into the warp. I saw the powers that dwell there\ldots{} 
  
  There is great evil in the warp and I need you to know the truth of Chaos before the galaxy is condemned to the fate that awaits it. 
  
  I saw it, Warmaster, the galaxy as a wasteland, the Emperor dead and mankind in bondage to a nightmarish hell of bureaucracy and superstition. \\
  All is grim darkness and all is war. \\
  Only you have the power to stop this future. \\
  You must be strong, Warmaster. \\
  Never forget that.
}





\subsubsection{The Space Age begins}
Both races will now venture into space, looking for new \dweomers{} to consume to feed the dying Heart. 




\subsubsection{The \banes{} still exist}
Make it clear that the \banes{} have only been banished, not destroyed. 
\Daggerrain{} still lives. 
He will be back. 
\Miith{} has gained a reprieve. 
Maybe a thousand years. 
Maybe less.
However long or short it takes, the \banes{} \emph{will} return. 

So all this talk about \quo{evolution towards perfection}, which obsesses both sides in the Feud, is more relevant than ever, if Mith is to prepare itself and be ready to face the \ps{\Voidbringer} attack a \emph{fourth} time. 






\subsubsection{A respite for the Heart}
\target{Respite for the Heart}
The Heart of \Miith{} is finally freed from \hr{Heart weakened}{the scourge of the \sephiroth{} and the \Morbus}. 
The millions upon millions of imprisoned souls finally die and are released back into the Heart. 
This lets the Heart regain some of the stolen lifeforce and thus grow in strength. 

But this is just a temporary respite. 
The menace of the \banes{} is gone, but the remaining two master races (\dragons{} and \resphain) still battle for control of the Heart. 
The two races \emph{cannot} coexist\dash their \matrices{} are inherently incompatible and inimical, ripping and tearing into the Heart\dash and the Heart will continue to be drained and weakened until this war comes to an end. 

So the war for the Heart escalates again (as per the \quo{arms race} above). 
After all, this is what the Heart is: 
Life and death, beauty and ugliness, love and cruelty. 
Nature. 

\Miith{} is a cruel world. 





\subsubsection{Ramiel rules}
The old world order has crumbled. 
Ramiel is now the lord of the \resphain.

\citebandsong{Arcturus:AsperaHiemsSymfonia}{Arcturus}{
  Raudt og Svart
}{
  Deira dagar har m\o rkna\\
  Moder jord meld sitt fraafall\\
  Men sverdet har gaat vidare\\
  Til ein ny b\ae rar
  
  Me er einsomme menn\\
  Me b\ae r fenresulvens muspell\\
  Skoll skal sluka sola
  
  Me er djerve menn\\
  
  Sola svartner\\
  Der fjellvegg ramlar\\
  Naa gjestar sorgen\\
  Paa livets tre \\
  Yggdrasil
  
  For byleits bror farar\\
  Kva er det ikkje Kampfar klarer?
}





\subsubsection{Ramiel and \Ishnaruchaefir}
Ramiel and \Ishnaruchaefir{} are on the Ark and chatting. 

\begin{prose}
  \Ishnaruchaefir:
  \ta{Perhaps the \banelords{} will find us again.
    Perhaps not.
    Perhaps there will one day be peace between our two peoples.
    Perhaps one of our races will become extinct\dash or both.
    Perhaps we will somehow find the means to wage war for all eternity.
    Who knows?}
  
  Ramiel:
  \ta{%
    We \resphain{} have always held that science is one of our greatest weapons and assets.
    We know\dash or believe\dash that we are set in the world to rise above our nature.
    I will take command of the \resphain{} here, and I will see to it that we rise to our fullest potential.
    I am Overlord now\ldots{}}
  
  \Ishnaruchaefir:
  \ta{Overlord of what?
    I doubt any traces of the old world order have survived the exodus of the Ark.
    I doubt that \Mystraacht{} even exists anymore.}
  
  Ramiel:
  \ta{I have seized a throne by force before and I can do it again.
    And know this: 
    My goal is to secure the future of \Mystraacht.
    No one else's. 
    Maybe this road will end in peace.
    But if I must destroy your people\dash or any other\dash so that mine may live, then so be it.}
  
  \Ishnaruchaefir:
  \ta{Heh. So be it.}
\end{prose}

Remember that after the exodus of the Ark, \Mystraacht{} does not really exist anymore. 
So Ramiel is no longer Overlord. 
But:

\begin{prose}
  Ramiel:
  \ta{I have seized a throne by force before and I can do it again.}
\end{prose}







\subsubsection{\Ishnaruchaefir{} looks forward}
The very last scene of the book is with \Ishnaruchaefir{}.
He looks forward the chaos and war that is to come. 
No longer will he hide and huddle in some Asylum. 
He will fight. 
It will be\ldots{} exciting. 

Remember: \emph{End on a dark note!}









\subsection{The cost of the \thirdbanewar}
The \thirdbanewar{} is the most costly and most apocalyptic of the three \banewars. 
It did not kill as many people in absolute numbers as the first two had done, but it killed a larger percentage of the population. 
The population is smaller at this time, remember. 

\Daggerrain{} is now gone, but \Miith{} has paid a terrible price. 
Ahead wait centuries of chaos, blood and war. 














\section{The Future}
After a thousand years or two, a new interstellar civilization centered on \Miith{} will be established, and a \quo{science fantasy} aera will begin. Compare to \emph{Warhammer 40.000} and \bandalbum{Bal-Sagoth}{The Power Cosmic}. 









\subsection{\Resphan/\dragon hybrids}
Perhaps some day in the far future, someone will begin experimenting and trying to create a race of \resphan/\dragon{} hybrids. 
These will try to conquer the races and destroy those who will not join them. 
This is seen as evil, but the intent is good: 
Only a hybrid race can stop the war and let the Heart of \Miith{} live on in peace. 









\subsection{New cosmic empire}
In the far future, after the exodus from \Miith, the \dragons and \resphain ended up ruling each their vast interstellar empire spanning dozens or hundreds of planets. 
They became super-technological and super-magical civilizations close to rivalling the \voyagers in technology, but far surpassing them in aggression and greedy ambition. 
The \voyagers were a peaceful (if decadent) race of scientists and explorers. 
The exiled \Miithians were warriors and conquerors at their very core.

At this time, the \dragons and \resphain had found new \dweomers to sustain them, so they no longer had to fight each other for possession of the Heart of \Miith. 
But they were warriors by nature and instinct, so they still fought one another. 























\chapter{Random Ideas}












\section{\Shilred{} Story Arc}





\subsubsection[Ishnaruchaefir and his fake mission]{\Ishnaruchaefir{} and his fake mission}
\target{Ishnaruchaefir's fake mission}
\Ishnaruchaefir{} is clever. He knows about \hr{Teshrial's creatures}{the \noggyaleth{} in \Malcur}, or at least suspects them. So he \hr{Ishnaruchaefir attacks Teshrial's creature}{goes there to see for himself}. 

\Ishnaruchaefir initially believes \Secherdamon's plan takes place in \Malcur.
Then he falls for the \Forclin decoy when it is unveiled. 
He is impressed to learn that both were decoys. 

He has also seen through \ps{\Secherdamon} plan to resurrect \Nithdornazsh{} in \Malcur. 
He has more Sentinel contacts than most people realize, so he has spies telling him of \ps{\Secherdamon} plans. 
And he is an expert astrologer and \matrix-theorist, so he has picked up subtle clues concerning \Nithdornazsh{} and \Malcur. 

He knows that the \noggyaleth{} may put a stop to the plan. 
He wants to help his brother.
He does not fully approve of \ps{\Secherdamon} plan to resurrect \Nithdornazsh, but he helps out of respect for \hr{Nexagglachel}{\Nexagglachel}, since he still feels guilt and obligation towards him and his memory. 
\Nithd{} was \ps{\Nexagglachel}{} fortress, after all, so it can stand as a monument of sorts to the fallen \dragonking.

\target{Ishnaruchaefir's creatures}
So \Ishnaruchaefir{} plans to free some of his own servitors\dash\pdaemons, \dragons{} or otherwise\dash who are imprisoned in a cave or lost temple somewhere in the eastern \PelidorContinent. 

But he can't just go off and do that. He would be discovered and foiled by \hr{Teshrial}{\Teshrial}, the Cabalist in charge of the area around the cave. 

So \Ishnaruchaefir{} develops a circuitous plan: 
\hr{Ishnaruchaefir recruits Shilred-tachi}{He recruits \Shilred-tachi} and sends them off to fulfill an ill-defined quest for him, in the general area of the cave in question. He tells them to search for a cave or something like that. 

But whatever he alludes that he wants them to do is a lie. The purpose of their entire mission is to look suspicious. \Ishnaruchaefir{} shows up to help them just often enough that the sneaky Cabalists cannot help but notice, yet rarely enough that it still looks like he is trying to lay low. 

What he is actually looking for is another cave, where his servitors are imprisoned. 

The Cabalists in the area where \Shilred-tachi are going are led by \Teshrial{} (see section \ref{Teshrial}). We follow him in several chapters, where he fears \Ishnaruchaefir{} and tries to guess his plan. 






\subsection{Rissitic invasion}
Some time after the Rungerans cross the Pelidorian border, Rissitic fleets sail north to besiege and conquer cities in \Scyrum. 
%march north from Gaznor into Beirod. They besiege and conquer Beirodi cities. 

%Or\ldots{} wait\ldots{} is it Beirod they attack? Or is it \Scyrum? \Scyrum{} might make more sense. 

For the Rissitics, controlling more land in \Velcad{} is nice, but the chief purpose of this attack is to draw the Redcor away. See, in intra-\Velcadian{} wars the Redcor traditionally take little part, acting mostly as negotiators and healers. But in case of a major attack on an Iquinian kingdom by a heathen invader, the Redcor typically offer more direct aid, participating in battles with their magic. So when the Rissitics invade, the Redcor are forced to send Vaimons from the entire region to help oppose them. 
This makes the invasion harder, but it has the nice bonus feature that it leaves \Malcur drained of Redcor, making it easier for the Sentinels to operate there. 

We follow Narkiza on his march north through \Scyrum. 

%Is Geldashad with him, or is he off on a mission of his own?

%What about \Shilred? 

Remember to describe the Rissitic army as \hr{Glorious armies}{magnificent and glorious}.







\subsection{\Shilred-tachi get lost in \Nyx}
\Shilred{}, \Dzasselid{} and \KarsaOrlong{} (see \ref{Karsa Orlong}) take part in the initial attack on a port city in southern \Scyrum. Maybe they are together with Mestos and Semphai. Anyway, during the battle they become separated from the main army and nearly get killed by \banes. %Maybe they even flee out of the mortal Realm and stumble into \Nyx. 

Maybe \Dzasselid{} deliberately takes them into \Nyx. Perhaps he has a back-story as a double agent for the Cabal, and thus knows his way around in \Nyx. Or something like that. He needs some skeletons in his closet, remember?

At any rate, they end up in \Nyx{} and get surrounded by \banes{} or other monsters. 






\subsubsection{\Ishnaruchaefir{} approaches}
Just when \Shilred-tachi are about to be killed, \Ishnaruchaefir{} appears. He appears in humanoid form. Using magic (incl. the spell \quo{\kingstongue{khestni}}) and his mighty glaive (see section \ref{Ishnaruchaefir's glaive}), he slays the monsters and saves them. The monsters should be huge, monstrous and menacing, like in the anime \emph{Devil May Cry}. 

Given that they owe him their lives, he claims them as his own. Perhaps one of the \Gisshorns{} knows who he is and convinces the others to be respectful. Somehow or other, \Ishnaruchaefir{} beats it into their heads that he is a high-ranking ally of Rissit and that they should obey him. 

Maybe \Ishnaruchaefir{} first approaches \Narkiza{}, gives a little help and asks to borrow some of his men. 






\subsubsection{\ps{\Ishnaruchaefir} mission}
\target{Ishnaruchaefir recruits Shilred-tachi}
\Ishnaruchaefir{} sends them on a private, secret mission. He wants them to find a cave somewhere in western \Velcad{}, where they must do fulfill some as-of-yet unspecified task for him. 

\Ishnaruchaefir{} tells them that he cannot go off searching for the cave himself, as he would be detected and attract Cabal attention (and Sentinel attention, for that matter). But he teaches them an invocation that will summon him, to use when they reach the cave or are in dire need of his help. 

\hr{Ishnaruchaefir's fake mission}{The above is actually a lie.}







\subsection{\Shilred-tachi go into the \Wylde}
On their mission for \Ishnaruchaefir, \Shilred-tachi must go into the \Wylde{}. \Ishnaruchaefir{} throws them into some place which has a tenuous link to \Nyx. Perhaps a cave system that was once inhabited, or a ruined castle. It must be something sort of urban area, since \Nyx{} is city-like. 

From there, they go out into the \Wylde{}. They fight their way through monster-infested jungles. 

Maybe they encounter a native tribe. Maybe they help them, like how Karsa Orlong helps the Anibar in \emph{The Bonehunters}. Maybe they just coerce them into accepting them. Maybe they hire native guides, who later die. 

They are chased through the \Wylde{} by savage monsters, maybe zombies or lycanthropes. Monstrous almost-humanoids, at any rate. Occasionally they are harassed by the Cabal. 







\subsection{\Shilred-tachi find a ruined city}
\Shilred-tachi find a ruined city out in the wild, with broken walls, toppled towers, defaced monuments and statues and the like. It is decrepit, dead, moss-grown and spooky. 

Compare to the cemetery in the movie \cite{Movie:HouseoftheDead}. 

Remember to have some references: 
\ta{%
  There are many places of power in the world, places of convergence. Especially out in the \Wylde{}. After all, the \Wylde{} is far vaster than the settled world.}

Remember to have them fight monsters. Have a scene where \Dzasselid{} kicks the butts of loads of monsters. 







\subsection{\Shilred-tachi find a laboratory}
\Shilred-tachi fight past monsters and end up in the laboratory of some necromancer or witch-doctor. It is filled with mutilated corpses and deformed creatures\dash living, dead or undead. Like in the movie \cite{Movie:HouseoftheDead}. 







\subsection{\Shilred-tachi crawl around underground}
\Shilred-tachi find themselves underground in a system of dark, creepy, monster-infested caves. Like in the movie \cite{Movie:HouseoftheDead}. 








\subsection{\Shilred{}-tachi see great monsters in the distance}
%Remember \Shilred{} and her party. They need to do something intelligent. 
\Shilred-tachi, \travelling in the \Wylde{}, see some colossal creatures far off in the distance. They need to be at some special place or in special circumstances, being able to see into the Beyond, in order to be able to see them. 

Maybe they see the creatures on a background of \Nyx{} or \Machai{}, or maybe just the great mountains and forests of the Beast Realm (these are larger than the ones that can be seen from within the Shroud). 

Perhaps the creatures are \dragons{} and \banes{} fighting. 

Perhaps, in the end, they see \Ishnaruchaefir{} vs \Teshrial-tachi this way. 

Remember to drop hints along the way about how powerful and terrible \Ishnaruchaefir{} is. Perhaps when they see these monsters, they reflect about \Ishnaruchaefir{} and his awesome power. 







\subsection{\Narkiza{} on the move}
%Early on, we follow \Filshed{} and her party as they invade Fendor. 

We follow \Narkiza{}, first in the port city in \Scyrum, and later as his army pushes north into \Velcad{}. His invasion is one of several \quo{prongs} in the Sentinel scheme.

In \TwilightAngelRememberEmph, only little time is devoted to \Narkiza{} and the other Rissitics. They will be given much more screen time in \emph{\CarzainWithRedcorBook}. 
%in the scheme to awaken the \Haskelek, 

%\Filshed{}, maybe together with the two \Gisshorn, are sent as a second \quo{prong} on covert missions to revive parts of the \Haskelek. 

%A third \quo{prong} are the Rissitics that are with Morgan Runger. 

%There might be a fourth \quo{prong}, consisting of some non-Rissitic Sentinels. They might include \Cryocas{} and her lover, Nisgzarchiev. Or maybe Vlad Racul. 










\subsection{\Shilred-tachi reach the cave}
\target{Shilred-tachi reach the cave}
\Shilred-tachi finally reach their destination. 





\subsubsection{They see fantastic and terrible things}
They near the cave and travel through fantastic, alien Realms (perhaps parts of \hr{Machai}{\Machai}). Compare to \authorbook{Clark Ashton Smith}{The Door to Saturn}. 

They even see glimpses of the \xss. 
\Shilred{}, \hr{Shilred is a nerd}{being something of a nerd}, is amazed by what she sees. And horrified.

\lyricslimbonicart{When Mind and Flesh Depart}{
  I'm captured by the sound of the tempest winds, \\
  and my demonvoice that dwells within.\\
  The ground I walk is sour.\\
  A spectrum shines so genuine.\\
  While the earthquake starts to devour,\\
  I behold the shrine in the ruin.
}

She sees horrors and is disillusioned. 

\lyricslimbonicart{When Mind and Flesh Depart}{
  The human way of life, \\
  an inferior state of mind.
  The third stone from the Sun\\
  had become a stillborn illusion.
  
  I'm under siege of anger and fury.\\
  There is no values, no faith or glory.\\
  Antagonising mortal flesh.\\
  Life on Earth I do oppress\\
  with infernal bleedings of bitterness.
}






\subsubsection{\Teshrial{} moves out}
\Teshrial{} fails in his attempts to guess \ps{\Ishnaruchaefir} thoughts. 
When \Shilred-tachi ostensibly reach their destination\dash the main entrance to the cave\dash they are attacked by \ps{\Teshrial} monsters and must call on \Ishnaruchaefir. 
He appears in humanoid form to fight the monsters. 
\Teshrial{} is now convinced that \Ishnaruchaefir{} means business, so he rushes to his location in person, leading a group of mighty \banes{} and monsters. 





\subsubsection{Epic description of \Ishnaruchaefir{} as a \dragon}
\Ishnaruchaefir{} assumes his true, \draconian{} form. Insert an epic description of the mighty \dragon{} here, a la \bandsong{Bal-Sagoth}{Black Dragons Soar Above the Mountain of Shadows}. 

This is the first time we are shown a \dragon. 
Describe the mortals' awe at the sight. 
\Dzasselid{} might have seen one before, but \Shilred{} sure hasn't. 
She has heard \hs{myths} of \dragons{}, but reality surpasses the myths. 





\subsubsection{\Dzasselid-tachi are sent to the real cave}
\Ishnaruchaefir{} draws out all the Cabal monsters in the area. 

In the meantime, \Criseis{} sees to it that \Dzasselid-tachi are sent to the \emph{real} cave he is after\dash which is now mostly unguarded. 

They encounter some creatures that try to block their way. 
\Criseis{} zaps them.

\lyricsbalsagoth{
  The Splendour of a Thousand Swords Gleaming Beneath the Blazon of the Hyperborean Empire - Part II: The Dark Liege of Chaos is Unleashed at the Ensorcelled Shrine of A'zura-Kai
}{
  [THE KING:]\\
  By the darkling powers of the Shadow-Sword, \\
  I call forth the fury of the storm\\
  to rend the massed legions of Chaos!
  
  [ALTARUS:]\\
  And at the sound of his baleful Words of Power, \\
  the sky split wide in fury, \\
  and searing tendrils of ruinous lightning \\
  lanced inexorably forth from the heavens \\
  to rake and reave the massed hordes of Chaos\ldots{}
}

They find the creatures they are looking for and set them free. Thus \Ishnaruchaefir{} has tricked \Teshrial{}, and his circuitous plan has succeeded. The freed monsters now rush to \Malcur to assist in the summoning of \Nithdornazsh. 

See \hr{Ishnaruchaefir kills Teshrial}{here} for the end of the fight.






\subsubsection{\Shilred{} is left behind near the cave}
\Shilred{} accidentally gets separated from the rest and stays behind near the cave. 
She gets to see the fight between \Ishnaruchaefir{} and \Teshrial{} in all its gory glory. 















\section{Sir James story arc}
Sir James is a \human{} Iquinian knight living somewhere in \Velcad{}. 
It might be in the east, if I want him connected to the king-thing and Vlad Racul, or it might be in the west (Ontephar or \Scyrum) if I want him connected to Telcastora Ilcas. 
I think it's going to be in the east. 

There is also Sir Lawrence, another knight. 
Perhaps Sir James' companion. 

And Prince Alistair, who later becomes King Alistair. 
I think. 

And Vlad Racul, a mysterious sorcerer who is actually the \dragon{} Candrazor (a high-ranking Sentinel) in disguise. 

Sir James discovers a Rissitic plot somewhere. 
The Rissitics work on resurrecting a part of the \Haskelek{} \daemon. 
He goes to the Redcor for help. They set out to thwart the Rissitics. 
It turns into a big quest with all sorts of stuff going on. 
There's an evil Rissitic mastermind (who?) who keeps outsmarting them, but somehow the reader is assured that good will prevail. 
And then, in the end, I assfuck the reader by having the Rissitics win, and Sir James and his party of heroes are killed. 




\subsection{The beginning}
Sir James, as a knight and minor lord of sorts, is approached by the girl Lica, a commoner who's had visions, seen suspicous things. 
His advisors scoff at the girl's fanciful tales and persuade him to dismiss her, but he does so with doubts. 
Later stuff happens to him that convinces him she was right, so he seeks her out and brings her back. 

James or his companion asks Lica: 
\ta{How old are you, girl?}

\ta{I am sixteen, my lord.}

Later, James comments to his companion: 
\ta{She is pretty, though.}

The companion laughs. 
\ta{She is sixteen, James. 
  Even my warty cackling crone of a great-grandmother was pretty when she was sixteen.}

%Turns out that Lica has seen a \bane. The \banes{} are working on some big thing, so they are getting bolder and more careless. (It's for the same reason that Catrian saw a \bane{} earlier.) Or maybe she hasn't seen an actual \bane, but merely a Cabalist working magic. Or maybe some \Nyxian{} monster. 
Turns out that Lica has seen either a Sentinel mage or some \daemon. 
And it's a good thing that Sir James starts to believe her, because it turns out the Sentinels is after her. Assassins come for her and he has to protect her. They flee back to the castle or whatever, and the authorities (Redcor church?) finally believe that something is up. 

Lica is gifted in seeing into the worlds beyond. Since her childhood she has had trouble accepting the illusion that everyone else believes in. She always wanted to see through the lie, doubt what she was told. This has continued to the current day (she is now 16 or so) and lets her see many things that others can't, but it also makes her strange (she is unmarried and unbetrothed, and her parents worry) and affects her sanity. 

Alarmed by Lica's vision, the Redcor send a delegation to investigate. Lica is brought along as a guide of sorts, and Sir James goes as her protector. 









\subsection{Lica sees strange visions}
Lica sees grim and horrid visions. 
She hates this \quo{gift}. 

\lyricslimbonicart{The Supreme Sacrifice}{
  Thought are tyrants that always return\\
  to rape and torment the heart.\\
  As darkness sweeps the face of Earth,\\
  I enter the chambers of bleeding art.
}









\subsection{Lica sees the \Morbus}
Lica sees the \hr{Morbus}{\Morbus} at work. 
She has dreams of its evil consequences. 

She sees visions of \Nyx{} and mistakes them for visions of the future. 
She is scared shitless. 

\lyricsduana{thisistheend}{This is the End}{
  I dream of a host cockroaches \\
  crawling, swarming over charred flesh \\
  up bitter blackend walls \\
  in sewer pipes now purgd \\
  the cries of many amplifd \\
  then swallowd by silence \\
  echoes of a lost world \\
  of a foul smoke that lingers like stale breath \\
  of steel/glass/concrete fusion-statues \\
  rising high in a pale and infinite twilight \\
  shining beacons like bleachd bones 
  
  I see field upon field upon field \\
  of bloatd-cattle-corpses bleeding intestines \\
  staring with sightless opaque eyes \\
  of waves drowning mountains \\
  and the earth's flesh torn with angry fissures \\
  of molten-spewing-spittle \\
  and hot lashing tongues \\
  of a planet roaring/quaking/quivering \\
  with unbound vergence 
  
  shivers erupt through space and time \\
  and images flashing faster faster\ldots{} \\
  until finally all is annihilated 
  
  like a vacuum space sucks the debris \\
  into a black empty hole \\
  and I fall down into the void \\
  this is the end
}









\subsection{Lica suffers}
Lica feels like she is losing her innocence and being corrupted from the inside by the terrible truths she sees.

\lyricslimbonicart{Beneath the Burial Surface}{
  The sky is darkening, soon the night befall.\\
  Righteously angels are weeping for my soul.\\
  All childhood dreams are soon to be lost,\\
  all innocence to be shattered.
  
  I am the fallen from grace.
  
  My face is a river.\\
  See my eyes as they drown in black.
  My sacred doom and nemesis\\
  beneath the burial surface\\
  To the final act of the immortal sin\\
  I am lead by funeral winds.
}









\subsection{Lica can curse people}
Lica discovers at a young age that she can curse people. 
When people are mean to her or refuse to believe her, she can stare at them and hate them and wish them ill\dash and sometimes it happens.
This is a manifestation of her (albeit weak) \vertex{} powers. 




































 

 
