\bookchapter{AchsahDetectsNzessuacrith}
The Cabalists suspect that the Sentinels (specifically, \Secherdamon) are trying to open some kind of portal some place in Pelidor, but they don't know exactly where. 

The Cabalists believe the ploy is to create a \emph{portal} or \emph{conduit} to \Nithdornazsh{} or something like that. 
They don't imagine that the Sentinels actually intend to \emph{resurrect} \Nithdornazsh{} and bring the entire city to \Azmith, straight into the deep Shroud. 

At first, the Cabalists suspect \Malcur. 
But \ps{\Takestsha} desperate, rushed attack against \Forclin{} convinces them that the target is \Forclin{} and the Ghost Tower, and that \Malcur was a decoy. 
\Secherdamon{} is known for very elaborate decoys like this. 
\Achsah, who has long \hr{Achsah suspects that Malcur is a decoy}{suspected that \Malcur was a decoy}, is the first to believe the \Forclin{} ruse. 





\subsubsection{\Nzessuacrith shows her true \colours}
\Takestsha was badly shocked when \hr{Eresh-Kali magic backfires}{Curwen's counterspell struck} and caused her \quo{\EreshKali} master-spell to backfire. 
She had to suddenly use a lot of powerful magic just to keep alive. 
(Her \human body is much weaker than her \draconian body, and \hr{Ilcas injures Takestsha}{she was wounded by Telcastora Ilcas}.) 

In her haste, she accidentally lets her stealth slip.
Tremours of her true \vertex signature spill forth. 

\target{Takestsha bleeds power}
\Takestsha realizes her cover is blown. 
But she is also hurt. 
She is leaking arcane blood so badly that even Shrouded humanoids can see it.
She is trailing tendrils of power, and she bleeds blood that sizzles and burns and evaporates. 
Her own Rungeran soldiers flee screaming from her path.

\target{Takestsha retreats to heal}
\Takestsha has to retreat. 
She must take a little while to heal. 
But she promises that after some minutes of rest, she will back.
And this time she will hold nothing back.
The \resphain must surely know by now that she is here, so there is no point in playing any more games of deception.
As soon as she is fresh, she will break her humanoid guise and attack in her true form. 

\begin{prose}
  \Takestsha: 
  \ta{Mark my words. 
    I will not be thwarted by mere mortals.
    \Forclin will fall this day by my hand.
    Or my claw, if need be.}
\end{prose}






\subsubsection{\Achsah detects \Nzessuacrith}
\target{Achsah calls for help}
\Achsah detects it when \Nzessuacrith lets her stealth slip. 
She smells a \ps{\dragon}{} presence. 

It is a frightening \trope{CosmicHorror}{Cosmic Horror} revelation for \Achsah when she perceives and recognizes \Nzessuacrith.
\Nzessuacrith may not be a \shaeeroth, but she is great a great and terrible \dragon. 

Now \Achsah{} is really frightened. 
She realizes that she can't handle \Nzessuacrith{} on her own. 
Moreover, if a \dragon{} is here, then it must be \trope{SeriousBusiness}{Serious Business}. 
And it is well known that \Nzessuacrith{} works for \Secherdamon, so \Achsah{} is convinced that she is the spearhead of his plan. 

She also becomes convinced that this attack has been deliberately timed to coincide with \ps{\Teshrial} duel, so everyone's eyes would be fixed on \Malcur. 
So \Secherdamon{} must have learned of the duel and is using it as a smokescreen. 
No one in the Cabal imagines that \Ishnaruchaefir{} is \emph{actively} and directly helping \Secherdamon, because he hasn't been doing that for millennia now. 






\subsubsection{\Achsah calls for help}
\Achsah{} needs help. 
An average \dragon is \hr{Dragons vs Resphain in power}{a terrible opponent}, even \hr{Umbra power}{if you have \umbrae} on your side.
And \Nzessuacrith, while no \shaeeroth, is far more than an average \dragon. 
\Achsah will need \emph{many} reinforcements if she is to take down \Nzessuacrith. 
She contacts her fellow \resphain who are working on the \hr{Malcur venture}{\Malcur venture} and requisitions reinforcements. 

The other \resphain are not happy about that, because they would like to keep some in reserve for \Ishnaruchaefir.
But Achsah pleads her case, and \Teshrial agrees with her (because he \hr{Teshrial fears to break agreement with Ishnaruchaefir}{fears to break \Ishnaruchaefir's agreement}).
(This happens before \Teshrial's duel has started.)

So a dozen \resphain hurry to \Forclin to fight off \Nzessuacrith. 
This includes the \resphain{} whom \Teshrial{} \hr{Teshrial leaves Bezed in charge}{left in charge of \Malcur}. 
There are now only a few left to guard \Malcur. 

This is distressing and hurtful to the Cabal's plans because they had not planned for such an eventuality. 
Like \humans, \resphain can be shortsighted.
\Dragon attacks \emph{almost} never happen.
Therefore, many \resphain tend to assume \dragon attacks will \emph{never} happen, and hence they will not plan for them. 
\Nzessuacrith's appearance is a blatant breach of the Unspoken Covenant which none could have foreseen.

Also remember that the faction taking care of Pelidorian business is small. 
There are not many \resphain there, so they are not well-equipped to deal with such fierce \dragon attacks, from \shaeeroth and other elders.

Only one \resphan{} now remains to guard \Malcur: \Paerzim. 
\hr{Psyrex kills Paerzim}{That ends badly}. 





\subsubsection{\Achsah fetches \umbrae}
\target{Achsah fetches Umbrae}
When \Achsah{} has realized \Takestsha{} is a \dragon{} (and perhaps even the mighty \Nzessuacrith), she reckons she still has a few hours of time before the shit hits the fan. 

So she calls on Charcoal (who is in \Forclin) and gives him responsiblity for keeping control of \Forclin{} for some hours until reinforcements arrive from \Malcur. 

\Achsah{} then quickly submerges and goes to \Nyx{} to fetch one or more \umbrae. 
She believes she and her companions will need them if they are to confront the \dragon\dash especially if it really is \Nzessuacrith, as she fears. 

She has asked \Teshrial{} to send \emph{one} \resphan{} directly to \Forclin{} (to relieve poor Charcoal) and send the others to \Nyx{} to rendezvous with her there. 

Remember to have a cool, dark, evocative, mystic scene where they summon the \umbrae{} from the endless dark deep. 

\Achsah{} is in awe and fear when the \umbra{} shows up. 
She is old enough to remember the days in \Merkyrah{} when \hr{Merkyrans fear Umbrae}{the \resphain{} lived in fear of the \umbra}. 
She remembers the terror and awe she felt when \hr{Rebels awestruck by tame Umbrae}{she first saw the rebel leaders riding \umbrae}, back when she was just a rank-and-file rebel acolyte. 

Nowadays she has ridden an \umbra{} countless times. 
But she still remembers the fear of them and knows to be careful. 
Many younger \resphain{} do not know this, she reflects. 
They are overconfident around \umbrae.
They do not show the terrible monsters the respect they deserve. 
They have not lived back in the days when, at any moment, an \umbra{} might swoop in from the dark sky or the dark deep and kill and eat a half-dozen \resphain. 
(Remember, \resphain{} were weaker back then.)
