
\bookchapter{\Ishnaruchaefir Contacts \Secherdamon}
\begin{comment}
  \section{Psyrex and Ishnaruchaefir}
\end{comment}
\placestamp{Dark Crescent throne}
\begin{comment}
  \subsection{Psyrex feels Ishnaruchaefir}
\end{comment}

Read about \maybehs{Chaos magic}, and remember to invoke \Sethicus and \Tiamat. 

\Psyrex sits on his throne, monitoring affairs. 
Then he feels an intruding presence. 
It is the Exile. 
Not just walking around on \Azmith, either, but coming this way.

\Psyrex has to think quickly.
Is this a mental attack?
If it is, can he defend himself against it?

He hesitates precious seconds, and \Ishnaruchaefir breaks through several layers of defense.
The Dark Crescent inner sanctum is otherwise well-defended with many spells. 
\Ishnaruchaefir is almost through.

\tho{What do I do?
  I must defend myself.
  No, wait.
  He is almost through.
  And he is a \shaeeroth.
  I am nothing next to him.
  If he wants in, I am powerless to stop him, at least now that he has come this far. 
  If I try to push him out, I may just make it worse for myself.}

So \Psyrex sits tight and waits. 

\Psyrex is distressed at how easily \Ishnaruchaefir broke in. 

\Ishnaruchaefir is not physically there. 
But he is close.
He is projecting his presence into \Psyrex's mind. 
\Psyrex feels a mammoth presence.



\begin{comment}
  \subsection{Ishnaruchaefir talks to Psyrex}
\end{comment}

\Psyrex hears a voice in his head.
A \draconian voice full of menace and power. 

\Ishnaruchaefir:
\secherdamon{\LocarPsyrex.}

\Psyrex cautiously replies:
\ta{Exile.}

\Ishnaruchaefir tells him that he has come to know things that will interest \Psyrex and his lord. 

He tells \Psyrex something. 
The reader does not hear it. 
In truth, he tells \Psyrex that the Cabalists have \noggyaleth in \Malcur. 
\Psyrex is distressed.
He did not know. 
They can seriously fuck up his plans.

\Psyrex:
\ta{This is terrible news. 
  \ps{\XzaiShanns} curses upon the \resphain.
  I must find a way to deal with them\ldots}

\Ishnaruchaefir:
\secherdamon{I will deal with them.}

\Psyrex:
\ta{You will what?}

\Ishnaruchaefir:
\secherdamon{I have remained aloof from the \feud for too long.}

\Psyrex:
\ta{You come to offer us your help?}

\Ishnaruchaefir:
\secherdamon{Nay.
  I come to tell you what I intend to do.
  It will be up to you to adjust your plans so as to best benefit from my work.}

\Psyrex seethes. 
He tries to bargain.
It soon becomes clear that \Ishnaruchaefir will not budge an inch. 
So \Psyrex must accept the terms as given. 

\Psyrex:
\ta{What will you do?}

\Ishnaruchaefir explains to him. 
\Ishnaruchaefir will lead \Teshrial and his \noggyaleth away from the city. 
He has planted an obsession in \ps{\Teshrial} mind and manipulated him with his false myths, so he believes \Teshrial{} will be obsessed enough to leave his precious city semi-unguarded and rush off to face \Ishnaruchaefir. 
But due to the nature of the myths, on which \Teshrial{} relies, this must be done at a strategically exact point in time. 

\Psyrex{} listens while \Ishnaruchaefir{} describes his plan. 
(Offscreen, of course. 
 \trope{UnspokenPlanGuarantee}{Unspoken Plan Guarantee} and all that.)
Then:

\Psyrex: 
\ta{This is madness!} 

\Ishnaruchaefir: 
\ta{%
  My last gambit\dash the one for which I am now infamous\dash was also madness.
  It had quite some effect.}

\Psyrex: 
\ta{But to take them all on alone. 
  This is the very depth of your Nadir.
  Are you even sure you can?
  What if you fail?} 

\Ishnaruchaefir: 
\ta{%
  I will go through with this.
  I will do this favour to my race.
  To \Nexagglachel.
  Yes, even to \Secherdamon.
  And when I do, you will stand ready.}

With that, \Ishnaruchaefir severs the connection. 
\Psyrex is left alone, thinking. 

Remember to stress how dangerous this is for \Ishnaruchaefir.
\Psyrex knows about the Nadir. 
He knows \Ishnaruchaefir will be at his very weakest. 
Ostensibly he will only be fighting a single \resphan, but \Psyrex is too smart to underestimate the \resphain.
\Ishnaruchaefir will be going into a trap, and he knows it. 

\Ishnaruchaefir will take on all of \Teshrial's \noggyaleth.
He will take all the \resphain's attention upon himself. 
In the meantime, \Psyrex-tachi must work fast. 
They must invoke their ritual while \Teshrial is preoccupied. 

This means \Psyrex{} must speed up his plans. 

This scene is inspired by the conversation between Ganoes Paran and Shadowthrone in the middle of \cite{StevenErikson:TheBonehunters}. 

Later in the scene, \Secherdamon appears, in vision form if not in physical form. 
He curses the Exile, but ultimately agrees to his demands. 

Remove any direct references to the Malcur \nexus. 
Just refer to \quo{the \nexus{} in Pelidor}. 
We don't want to tell the reader that \Forclin{} is a decoy. 





\begin{comment}
  \section{\Takestsha}
\end{comment}
\placestamp{Rungeran army camp outside \Forclin}

\begin{comment}
  \subsection{Psyrex contacts Takestsha}
\end{comment}

\Takestsha's POV. 

\Takestsha is with the Rungeran army.
They are besieging \Forclin.
She receives a telepathic call from \Psyrex.
She must retreat a little bit from the fray first.
Then she can answer the phone.

\Psyrex calls her by her true name (the reader does not hear the name).
\tele{Or should I say \quo{\Takestsha}.}

\Takestsha:
\ta{\LocarPsyrex.}

\Psyrex:
\tele{Is the attack proceeding according to plan.}

\Takestsha:
\ta{It is not easy, but yes.}

\Psyrex:
\tele{I am glad to hear it.}
He hesitates.
She can tell he is unsure of himself.
\tele{Listen... we may need to adjust our plans.}

\tho{I do not like the sound of this.}
\ta{Adjust? What do you mean?}

\Psyrex:
\tele{I was recently contacted... by the Exile.}

\ta{What!?}

\Psyrex explain the situation to her. 
She is quite shaken.
She had not expected that \Ishnaruchaefir would help them.
But if he was ever to offer his aid, this would be how he would do it.
\emph{Egenraadigt}, asking no one's advice and doing whatever he damn well pleased. 
Charging ahead and leaving others to pick up the pieces of the destruction he causes.
Just like always. 

\Psyrex:
\tele{So, as you see, we will need to speed up our plans.
  I will ask you to make your move sooner.}

\Takestsha:
\ta{Have you conferred with \Secherdamon.}

\Psyrex:
\tele{Yes.
  The Exalted Lord agrees with my proposal.}

\Takestsha:
\ta{Hm.}

\Psyrex:
\tele{Can you manage it?}

\Takestsha:
\ta{I will have to strain myself, but I can do it.
  Very well, \Psyrex.
  I will do as you ask.}

\Psyrex:
\tele{Excellent. Thank you. Good luck to you.}
He says perhaps a few more noises, then severs the connection. 

\begin{comment}
  \subsection{Takestsha thinks about her task}
\end{comment}

\Takestsha is nonplussed.
She will have to hurry, and her mages are already overtaxed. 

Moreover, her opponents are not to be underestimated.
\Achsah is here in \Forclin. 
\Takestsha has detected her. 
\Takestsha, being a master of stealth, is also a master of detection. 
\Achsah may be just a \bezed, but she is a skilled opponent. 
\Takestsha respects her more than she does this upstart \Teshrial over in \Malcur. 
\Achsah is not easy to trick, and quite capable of holding her own in combat. 
Besides, if push comes to shove \Takestsha will certainly not be facing \Achsah alone. 
\Achsah is too smart for that.
She will call for assistance. 

She laughs silently to herself.
\tho{%
  \quo{If} push comes to shove.
  You mean \quo{when}.}
And it will be soon. 

She has agreed with \Secherdamon that she must not break the Unspoken Covenant unless it is absolutely necessary. 
Make up some good reason for this!

Now that circumstances have forced her hand, she does not think she can avoid it.
She will have to break the Covenant sooner or later.
And oh so very blatantly. 
But if it is up to her, it will be later. 
She has worked undercover for millennia.
She will hold her character for as long as she can, and only become overt and go out in the open when she has to. 

But it will be soon. 

\begin{comment}
  \subsection{Takestsha thinks about Ishnaruchaefir}
\end{comment}
She thinks about \Ishnaruchaefir again. 
She has trouble comprehending it. 
It is shocking. 

\tho{Fuck.
  The Exile is going into battle.
  Now.
  Right in the middle of his deep Nadir.
  And he is walking straight into \ps{\Teshrial} trap!
  Surely he must realize this. 
  What is he doing?
  He might actually be in danger.
  Can he even fight in his condition?
  
  Why is he doing this?
  And he is helping us.
  \Secherdamon, and me. 
  Why?
  
  He might be defeated.
  He might perish.}
The thought is incredible.

\tho{%
  The Exile might perish.
  
  Does he intend to sacrifice his life?
  Will he atone for his crimes at last?
  That cannot be.}

For a short moment, this line of thought makes her respect \Ishnaruchaefir{}. 
She thinks and visualizes \ps{\Ishnaruchaefir} name, something she has not done for many centuries. 









