
\bookchapter{\LocarPsyrex}
Read about \maybehs{Chaos magic}, and remember to invoke \Sethicus and \Tiamat. 
The magic is \xs-related. 
And read about \Nithdornazsh and dark ancient cities.

Read about \Psyrex, \dragons, technology and living machines. 
Have \Psyrex use living machines. 

\Psyrex is sitting on his throne. 
(Describe the throne.)  
\Takestsha contacts him.
He calls her by her cover name.
They joke a little bit about the name.
But make sure not to mention her true name. 

Maybe see it from \Takestsha's POV. 

\Takestsha asks \Psyrex about his progress. 
\Psyrex tells her that there have been some setbacks. 
The Cabalists are sneaky.
He does not know who leads them, now that Charcoal is gone from the city. 
But whoever is in charge must be someone capable. 
They have managed to screw up some of his operations and kill some of his important Sentinels. 
But it is not so bad. 
He has planned for some amount of Cabal interference and taken precautions. 
He is importing more manpower. 
He will be ready on time. 

Remove any direct references to the Malcur \nexus. 
Just refer to \quo{the \nexus{} in Pelidor}. 
We don't want to tell the reader that \Forclin{} is a decoy. 

\Psyrex{} tells how the resurrection of \Nithdornazsh{} is a \quo{pivotal step, a decisive battle in the eternal war. One step on the long ladder of bringing the \matrix{} of our kind to ascendancy}.  

\begin{prose}
  \Vizsherioch: 
  \ta{The beacons are in place? Show me.}
  
  \Psyrex shows her. 
  \Takestsha sees the slender aethereal tendrils, grown from the Pyre \matrix.
  They reach up from \Nithdornazsh to twist around the ley lines and converge upon the \nexus point in Pelidor, where they grab on and hold fast, holding the \nexus in a constricting iron grip. 
  He sees the \matrix subtly reaching out to fasten upon the souls of the mortals in the city. 
  Binding them.
  They will be part of the invocation, he thinks. 
  
  \Takestsha: 
  \ta{Aye, I see it.
    You have done well, \Psyrex.}
  He smiles to himself.
  \ta{%
    I am sure \Secherdamon's son longs to set foot in what is to be his new citadel. 
    And to exert his power in \Azmith; supposedly the most pivotal of the Shrouded Realms.}
  
  They think about that.
  Both \Takestsha and \Psyrex fear \Vizsherioch, the son of \Secherdamon.
  There is a certain air of madness about him. 
  \Psyrex agrees, \Vizsherioch probably longs to \quo{exert his power}
  
  \Takestsha becomes distant, reaching out with her aethereal senses.
  \ta{The constellations are falling into place.
    I can feel the tension in the Pyre. 
    The Dagger is taking shape.
    It will not be long now.
    \Vizsherioch's rising is near.}
  She becomes present again.
  \ta{%
    What of the \resphain?}
  
  \Psyrex:
  \ta{I have detected some \resphan activity in both Malcur and \Forclin.
    I still have every reason to believe they will swallow the bait.
    But of course, I am dependent on you and your part of the mission.}
  
  \Takestsha:
  \ta{I will not fail.}
  
  \Psyrex:
  \ta{Yes.
    It is not that which makes me uneasy, nor the \resphain.}
  \Psyrex pauses and hesitates. 
  
  \Takestsha: 
  \ta{You mean the Exile.}
  She speaks the name with scorn. 
  She becomes cold. 
  Her eyes probably become menacing, shining with cold \ophidian malice.
  Even \Psyrex is made uncomfortable by those eyes.
  
  The name \quo{\QuessanthIshnaruchaefir} hangs in the air, but no one speaks it. 
  
  \Psyrex:
  \ta{Yes. He has been uncharacteristically\ldots{} \emph{active} recently.
    In the Pelidor region.}
  
  \Vizsherioch:
  \ta{But he has not antagonized us?}
  
  \Psyrex:
  \ta{Not that I can determine. 
    And that worries me.
    So far he seems to have acted only against the \resphain, but I cannot guess his motives.
    The Exile cannot be trusted.}
    
  \Takestsha looks at \ps{\Psyrex} star-charts. 
  Concentrates to shift her vision. 
  Looks up, bypassing the roof, at the real stars. 
  Stares at the star representing the Exile. 
  It is nowhere near the Pyre. 
  Nor any other known \matrix. 
  She is made uneasy by the thought of the rogue \vertex. 
  A wanderer in darkness who can appear anywhere at any time. 
  
  \Takestsha:
  \ta{Hm.
    The Exile is in the Pelidor region.
    So it is possible he has caught wind of our doings.
    He must not be allowed to interfere.}
  
  \Psyrex:
  \ta{The \resphain feel likewise.
    Have you heard about this \resphan, \Teshrial, who talks about confronting the Exile?}
  
  \Takestsha:
  \ta{Yes. 
    Allegedly the Exile has promised to face him.}
  
  \Psyrex:
  \ta{I wonder what will come of this challenge. 
    Will the Exile really return to meet the \resphan?
    I do not think \Teshrial is a fool.
    He has a plan.
    But will it be enough?}
  
  \Takestsha:
  \ta{Heh. 
    I do not know which outcome to hope for.}
  
  \Psyrex:
  \ta{I will continue to monitor the situation.
    I will not let the Exile get the better of us.}
\end{prose}





Perhaps they look at the underworld beneath Malcur. 
Like the \maybehr{Malcur dungeon haunted}{haunted dungeons beneath \CastlePelidor}, the underworld is a place where the Shroud is thin. 
It is a gateway to the Blood-Red Vaults of \Nithdornazsh. 

\lyricsbalsagoth{Beneath the Crimson Vaults of Cydonia}{
  Ancient and divine, older than the hidden Icosahedron, \\
  now rebirthed beyond the chaosphere.\\
  Rise\ldots{} rise and destroy!
  
  Hatred, carnage, slaughter, havoc, chaos, murder!\\
  I am become the devourer of all life!
  
  Phobos, Deimos! \\
  The moons' rays liquefied in these blood red pyramids.\\
  In the shrines of abomination, black tongues rapt with blasphemy.\\
  Chaosphere, watchtowers, genesis, Cydonia\ldots{}\\
  The Abyss yawns wide!\\
  Spirit of the carrion-thronged battlefield, open wide thy gate!
  
  Unruly evil!\\
  Colossal shapes etched against the moons, \\
  supine obeisance 'fore the mound,\\
  Accursed fiends, hail the Slitherer, \\
  abhorrent jaws drooling lunacy.
}





