\bookchapter{\LocarPsyrex Wins}




\subsubsection[Psyrex-tachi invoke the ritual]{\Psyrex-tachi invoke the ritual}
\target{Psyrex-tachi invoke the ritual}
\Psyrex-tachi begin the sorcerous ritual that will summon and resurrect \Nithdornazsh. 

\Psyrex, the mad sorcerer, leads the ritual. 
Several other mages support him, and loads of servants stand by to perform menial tasks, such as procuring living prisoners to be sacrificed. 

\Psyrex rejoices. 

\citeauthorbook[p.137]{RobertEHoward:TheAltarandtheScorpion}{Robert E. Howard}{%
  The Altar and the Scorpion%
}{
  \ta{The real gods are dark and bloody!
    Remember my words when soon you lie on an ebon altar behind which broods a black shadow forever!
    Before you die you shall know the real gods, the powerful, the terrible gods, who came from forgotten worlds and lost realms of blackness.
    Who had their birth on frozen stars, and black suns brooding beyond the light of any stars!
    You shall know the brain shattering truth of that Unnamable One, to whose reality no earthly likeness may be given, but whose symbol is\dash the Black Shadow!}
    
    The girl ceased to cry, frozen, like the youth, into dazed silence.
    They sensed, behind these threats, a hideous and inhuman gulf of monstrous shadows.
}

They invoke mystic, forbidden names. 

\lyricsbs{Bal-Sagoth}{%
  As the Vortex Illumines the Crystalline Walls of Kor-Avul-Thaa%
}{
  By Klatrymadon and Zuranthus,\\
  such ancient secrets we discovered \\
  within these sinistrous, worm-worn pages,\\
  Etched with darksome glyphs and sigils, \\
  bound with fearsome spells, \\
  An eldritch tide of stygian sorceries \\
  unfettered by the forbidden Tome of Shadows\ldots{}
  
  Now thunderous cataclysm befalls the gleaming Kor-Avul-Thaa \\
  (The mystic gate stands open!) \\
  The Xytaxehedron held to the stars\ldots{} \\
  the incantation uttered with eager tongues\ldots{} 
}

\ps{\Ishnaruchaefir} is one of the names. 

\lyricsbalsagoth{Invocations Beyond the Outer-World Night}{
  Invocations and ideograms (dreams of the Xytaxehedron?),\\
  Conjuration of the inner world's (tenebrous) denizens,\\
  And their star-spanning progenitors, \\
  spawned beyond the outer-world night.
}

They invoke Chaos. 

\lyricsbs{Arcane Wisdom}{Symphonia Chaos}{
  Chaos, ruler of Time. \\
  Chaos, infinity is Thine. \\
  Shadowy inner essence, \\
  cosmic tapestry and sparkling \\
  spheres of a circular reason. \\
  Chaos, ruler of Time. \\
  Chaos, infinity is Thine. 
}

\lyricsbs{Emperor}{Moon Over Kara-Shehr}{
  Our time is upon us. \\
  Master! Appear! \\
  Over the nocturnal sky \\
  from the mountains of black we ride. \\
  Fly! 
  
  All thy servants fly \\
  though the serpent's darkened sky. \\
  Hears the opponent cry, \\
  ravaged by his terror. 
  
  Master! We ride with the storm \\
  in his name, the sire, wolves' king.\\ 
  Enter the power coursing \\
  through veins of the night. 
  
  Who gathers winds, summons thunder, \\
  summons rain, summons might?
}

Describe how \pdaemons{} fly screaming through the sky and blood boils up through the ground. 

\lyricsbs{Bal-Sagoth}{
  Dreaming of Atlantean Spires
}{
  The sky is black with Chaos-fiends,\\
  spellcraft rides the witch-storm's wings.\\
  Beneath the vaults of time-lost tombs\\
  sorcerers summon the shadow-kings.\\
  The Topaz Throne is beckoning,\\
  the jewelled sword awaits my grasp.\\
  The dreaming gods now grimly brood\\
  in the silence of Atlantean Spires.
}

Also, describe the mages' awe and fear as they invoke the names of gods, and then see those gods actually appear!

\lyricsbs{Bal-Sagoth}{
  As the Vortex Illumines the Crystalline Walls of Kor-Avul-Thaa
}{
  What long-shackled powers of the elder dark have our conjurings loosed?
  
  By Klatrymadon and Zuranthus, \\
  the vortex blackens the stars above,\\
  A vast plague of amorphous horrors \\
  descends to rend with fang and talon,\\
  (As with torrents of blood the crystalline walls run red?)\\
  And in the glooming chambers of our shadowed sanctum, \\
  we wait, half-mad with terror,\\
  To reap the slaughterous harvest which we have sown\ldots{}
  
  [The Chronicler of the Cataclysm:]\\
  And beyond the vortex, the churning black waters of the void did disgorge the Dwellers in Eternal Shadow. \\
  And upon a horde of winged horrors, brandishing swords of ebon flame, they rode out from the Gate\ldots{} \\
  And a terrible silence fell upon Kor-Avul-Thaa\ldots{}
  
  [The Echoes of the Oracle:]\\
  The sky rent asunder, \\
  black winged devils surge forth from the void\ldots{}\\
  A maelstrom of crimson fire burns above us\ldots{} \\
  what carnage has thou wrought?
  
  By Klatrymadon and Zuranthus, \\
  in Kor-Avul-Thaa, darkness reigns eternal\ldots{}\\
  Nevermore shall the city glimmer, \\
  for now the crystalline walls gleam black\ldots{}\\
  Ever black\ldots{}
}





\subsubsection{\Paerzim killed by \Psyrex}
\target{Psyrex kills Paerzim}
After \hr{Achsah calls for help}{\Achsah{} has summoned everyone to \Forclin}, only one measly \resphan{}, \Paerzim, remains in \Malcur. 
Needle is \ps{\Paerzim} second-in-command. 

\Paerzim{} is competent enough to give \Psyrex{} trouble. 

But then Needle is killed by Moro and Rian. 
This means \Paerzim{} has to take an active role in everything and divert his attention around. 
This is just what \Psyrex{} needs. 
He is now able to out\manoeuvre \Paerzim{} and kill him. 

Now the Cabal in \Malcur is all but destroyed, and the way for \Psyrex-tachi is opened. 
\Achsah-tachi are busy in \Forclin. 
\Teshrial{} is busy with his duel. 
None of them are in a position to come back and stop \Psyrex. 
He can freely complete his summoning ritual. 
\Nithdornazsh{} will rise. 





\subsubsection{The Cabal are thwarted}
With Needle dead, the Cabal raid is thrown into disarray. 
\Psyrex{} finds their trail and figures out their moves. 
When the Cabalists finally get their act together, \Psyrex{} has his men and magic prepared for them. 
The Cabalists fight bravely and sneakily, but \Psyrex{} just manages to stitch together enough makeshift defenses to fend them off. 

\Achsah, who might be able to put a stop to the Sentinels' dastardly plan, is up near the Ghost Tower. \ps{\Secherdamon} clever plan is working. 

Just before all Hell breaks loose\dash literally!\dash\Psyrex{} appears before Rian and Moro. He congratulates them for their hard work and their success, and thanks them for the help. If not for them, he says, Needle-tachi would have taken him by surprise, he and his companions would have been slain and their gambit would have crumbled. 

%Do Rian and Moro die? I think Rian at least dies. Moro is cool enough that she might escape, but she might also die. If she dies, I might want to portray her as a bitchy Aes Sedai who bullies Rian, so the reader is not sad to see her die. 

%I need to portray Rian as semi-cool but not so cool that the audience will be outraged when I kill him. And I need to be very sure that \Psyrex{} is portrayed as kickass, so people will like it when he wins. 





\subsubsection{\Tiroco{} feels the end is near}
\Tiroco{} feels the end is near. 

\lyricsbs{Marduk}{
  Cold Mouth Prayer
}{
  Quickened lumps of Earth,\\
  A feast for fowls and greedy worms.\\
  Count your sins, the Snakes within.\\
  An eyeless leap into the Bosom of Decay.\\
  Cold Mouth Prayer.\\
  Cold Mouth Prayer.
  
  A flash, a minute, a winter's dust.\\
  A choir of fingers sings of putrefaction.\\
  Cold Mouth Prayer. Cold Mouth Prayer.\\
  A smile left to rot in the Sun of Despair.
}
