
\bookchapter{Moro Sacrifices to Nasshikerr}
Read about \maybehr{Moro}{Moro \Cornel} and \maybehr{Nasshikerr}{\Nasshikerr}. 

Read about \maybehr{Ortaica}{\Ortaican mysticism} and \maybehr{Rethyax magic}{\rethyactic magic}. 

\paragraph{Idea:}
Do not show the sacrifice. 
Cut directly to the part where \Nasshikerr appears. 
Moro just tells him that she has given him a sacrifice of blood as he asked. 
He is satisfied.
She feels dirty and villanous for doing it.
It was the right thing to do, she tells herself.
A necessary evil, in order to combat a worse evil. 
But it still feels horrible to have done it.
Do not tell the reader exactly what she did.
Leave the reader to guess that she has sacrificed a humanoid. 

\begin{comment}
  \section{Moro searches}
\end{comment}



\begin{comment}
  \subsection{Looking for victims}
\end{comment}
\Nasshikerr told Moro to come back after a week, bringing a sacrifice. 

When the time is up, Moro goes out into the city.
She looks for a piece of humanoid scum. 
This is much easier than her last task.
When she was out with Rian, they specifically needed a Black Plague member. 
Now she just needs to find a piece of humanoid scum.
The gods known there is enough of that in \Malcur (as there is in every other part of the world, she assumes). 

Maybe move this entire part from here to the \quo{Moro and Rian Interrogate a Thug} chapter.
Otherwise we end up with two rather similar and unnecessary scenes. 

Remember that \Malcur is going mad. 
Crime is escalating. 
She has heard this from the \rinyuth's council. 
And her own observations confirm it.
Crime is running rampant. 
Why is this happening?
Is it despair over the war?
No, she does not think so. 
She has seen wars before. 
And so have most of the population.
War is nothing out of the ordinary. 
People should not be going crazy over it. 
Is it because of the dead \rayuth?
No, she does not think so.
\Icor was a well-liked ruler, but again, nothing out of the ordinary. 

What is wrong in \Malcur?
Is there a supernatural explanation?
After all, she knows there have been many supernatural happenings in \Malcur recently. 
Such as the tree-\sphyle whom Rian claimed to have met. 
This is why Moro is even investigating. 

Is it connected to \quo{the Change} which the gangster they captured mentioned?
What is \quo{the Change}?
She needs to find out.
And for that, she needs \Nasshikerr's help.



\begin{comment}
  \subsection{Finding victims}
\end{comment}

Fortunately, the upsurge of crime works in her favour in this regard. 
She finds two \human bandits mugging and beating up a defenseless \scatha.

\tho{Perfect.}

It is extra perfect because it is close to the path she needs to take to get back to her chambers. 

She stands some way away, hiding, and casts her spells.
First she casts a dozing spell. 
It is slow to cast and slow to take effect, so it is not useful in combat (unless you are more skilled at it than Moro is), but it is useful here.
It makes all three of them sleepy and dull.
After 30 seconds' time, the two bandits are having trouble standing up.
The victim, who was already badly beaten up, has apparently fallen unconscious.

\tho{How fortunate. One less spectator to worry about. He should be fine when he wakes up.}

She could use much more nasty magic on them if she really wanted, but she does not want to attract attention, so she uses only moderate magic. 

Then she moves in to attack. 
She casts some more spells to hurt, wound and cripple the two thugs.
She curses at them to their faces, tells them how evil they are, how they are \human filth, and how she will make them suffer for it.

\tho{I can only transport one. I have to get rid of the other. Should I kill him? I probably should. I don't want him spreading rumours about me.}
She casts another glance at the victim. Still unconscious.
\tho{But a quick, painless death is too nice for such a piece of shit.}

She interrogates her victims before she kills one.
She wants to know whether they are Plaguers and whether they may know something.
It turns out they are members of another gang which is known to oppose the Plaguers (and, as far as Moro knowns, is not involed in anything supernatural). 
She is disappointed.
She had hoped to find a Plaguer to interrogate.
She has long tried to find a Plaguer to interrogate, but taking bandits captive is difficult. 
They are sneaky bastards.
Since her suspicions began she has only managed to capture one Plaguer, and he was a low-level nobody who knew nothing. 

Also make it clear that she usually just sacrifices animals to \Nasshikerr. 
Only once in a while does he demand a \humanoid.


She batters them some more with her spells.
She picks one to keep for a sacrifice and decides to kill the other.
She takes the one to kill and severs all his legs and arms and lets him bleed to death.

She asks the other: \ta{Do you surrender?}

They are cowardly shits and scared shitless, so they do.
Now that he has surrendered, she can cast a weak mind control spell.
Now, with a homunculus possessing the surviving thug, she can (for a short period of time) manipulate him like a zombie and force him to move as she wills.
It is difficult work.
He moves slowly and awkwardly and bumps into things, and she has to maintain the spell.

Moro would have liked to be able to use her mind control magic at court, but she has rarely been able to.
Her mind control has its limits. 
It only works on weak minds. 
And it is very hard to conceal its effect from the victim. 
Usually, the victim will always know he is being manipulated. 
Besides, as with all magic, you have to conserve your energy lest other mages nearby detect the fact that you're casting magic. 



\begin{comment}
  \section{Moro's chambers}
\end{comment}
\new



\begin{comment}
  \subsection{Moro gloats}
\end{comment}
Another advantage of the chaos that is engulfing \Malcur is that it is easier to be covert. 
She can skulk through the streets, cowled and furtive, with a zombie-like man trailing behind her, and not even look very suspicious. 
No one has time to notice. 
In fact, people seem to be trying hard to deny the fact that it is happening. 
This makes it easier to operate, but it is also very worrying.
Why are people insane and denying it?
(Moro may have seen it before, though. She knows \Ubloth, remember.)

\tho{This is not a good thing.
  If my crimes are the least of people's worries, then we are in a sorry shape indeed.}

Finally she gets him back to her secret entrance and into the castle with her. 
She takes him into her secret chambers.
There she ties him up securely.
She uses more magic to break his legs and arms so he can't fight even if he should break free.

Through the deal she talks to him and tells him how much she hates him and how he will suffer for his evil.
He weeps and whimpers and grovels and begs for mercy.

She tells him: 
\ta{Did you show mercy to that \scatha earlier today when he begged? 
  No, I did not think so. Spare me your hypocrisy, you shit. You deserve a worse fate than this. Then again, I strictly do not know what will happen to your soul when my god \Nasshikerr comes to claim it. Maybe you will be destroyed entirely and sent to oblivion. Maybe you will be tortured forever in some hell. Maybe you will be enslaved and made to serve \Nasshikerr as some horrid lemure.}

(Lemures are things in mythology and metaphysics. Moro is not sure whether they exist and, if so, exactly what manner of things they are.)



\begin{comment}
  \subsection{Nasshikerr arrives}
\end{comment}

At last she calls upon \Nasshikerr and kills the prisoner.

\Nasshikerr then tells her what he knows.
He has found out some stuff about what is going on in \Malcur. 
He tells her about how it all comes together. 

He tells her about the Sentinel plan, and about the Cabal plan.
But he does not tell her who is who, or even the very fact that there are two organizations fighting each other. 
He is a mischievous god who wants to create chaos.
He is interested in seeing what Moro will do with her limited information, and how much of a difference she can make.

\Nasshikerr tells Moro that there are some evil people that are preparing some big, evil ritual of magic, and that it is connected to that which is destroying the city.
Moro naturally assumes that this means the evil ones are the ones destroying the city.
But \Nasshikerr does not tell them what the factions are or what their different plans are.
He tells them a bunch of details pertaining to the two plans, but gives them no overview of the big picture. 

He tells her that the evil ones are using ancient magic. 
Magic from before \humans, before even \scathae. 

Maybe Moro finds out when the evil ritual will take place.
She and Rian do all in their power to stop it. 









