\bookchapter{Moro and Rian Go to Sentinel Lair}
Read about the Shroud. 

Moro and Rian have gotten some tips from \Nasshikerr (chiefly) and from the thug Moro has interrogated (secondarily).
They know there are some evil people that are preparing some big, evil ritual of magic, and that it is connected to that which is destroying the city.
The captive thug tells them where the ritual will take place. 
\Nasshikerr has told them the time. 

Moro and Rian go through \Malcur and look for the place which \hr{Nasshikerr returns to Moro}{\Nasshikerr} and/or \hr{Rian and Moro interrogate a thug}{their captive thug} described to them. 
This is dangerous and traumatic for them, because \hr{Malcur is going mad}{\Malcur is going mad}. 

\begin{comment}
  \section{Rian doubts Moro and her god}
\end{comment}
Moro and Rian are out in the city. 
They mean to find the evil mages' lair and do what they can to stop their evil doings. 
And rescue Neina and the other prisoners.

Around them, they seem to see buildings and other things twist and writhe in the corners of their eyes. 
They can hear strange whispering, hissing (hvislende) noises.
They can smell strange scents. 

Moro brings along a map.
She has marked the location where the bad guys should be located, if their information is correct. 
She has received more knowledge from \Nasshikerr.
She tells Rian that her patron god has told her stuff. 

Rian is \skeptical. 
He does not trust Moro's evil gods. 
He asks her if she is sure they can trust him?
They should not put their faith in evil gods. 
They should pray to the One Light for guidance. 

Moro is having none of that.
Rian can pray for guidance all he wants, but she will use the powers at her disposal. 
Inside she is stung by his words.
\Nasshikerr is a cruel god, and she does not like having to sacrifice to him, but it must be done. 
She feels guilty, but she denies her guilt and will not show it. 

But Rian is not fooled. 
He has lived many years as a thief.
He has learned to be perceptive, to pick up the subtle signals people send out.
He can tell Moro feels bad about using her evil god.
He is a bit happy that she is seeing the light, but also sad because she suffers. 

He is also happy because he feels he is achieving something. 
He is proselytizing. 
He is helping to spread the word of the love of the One Light. 
Moro is a heathen; in fact, she is one of those considered the worst of heathens, the \rethyaxes. 
But he is having an effect on her.
There is hope that her soul can be saved. 
Moro is not evil. 
She ought to be saved. 
But she will have to earn it first, he knows.
She will have to renounce her evil religion and repent.

\begin{comment}
  \section{Revelation of the Beyond}
\end{comment}
They see some people up ahead. 
The people are mutated and twisted. 
They look strange and inhuman from a distance. 
Moro stops.
She has an idea of what is going on. 
Rian is curious.
He creeps closer. 

(Remember, it is night. Rian only sees indistinctly.)

Moro tells him to stop.
She warns him he does not want to look closer. 
But he disobeys her and slinks closer. 

When he gets close enough he can see that the people are horribly mutated. 
Compare to an early scene in \cite{Movie:IntheMouthofMadness}. 
One of the men (or women) turns towards him and laughs in a menacing, gargling, inhuman voice. 
He takes a threatening step forward. 
Rian is horrified.
He backs away. 
Looks around. 
All of the people are monsters.
Slavering and gibbering and laughing.
And thirsting for his blood. 
The monsters seem to be closing in.
They seem to be growing, opening wide their grasping mouths to swallow him whole. 
Rian backs further away.
He bumps into a wall... and seems to sink in.
The wall becomes soft, slimy flesh. 
He casts a glance at the wall and he could swear the wall is full of staring eyes and gaping mouths. 
He looks around at the other houses.
Their outlines seem to have warped into hungry, leering, ravening monsters, all lying in wait and eager to devour him. 
Rian shrieks. 

\begin{comment}
  \section{Moro scares off attackers}
\end{comment}
Moro takes action. 
She casts a spell. 
(Rian hears her speak spellwords.)
The spell creates a flash of light and heat and fire. 
It is not a very dangerous spell.
It is mostly for intimidation purposes. 
But it does evoke the fire of the \Primordials (actually \RuinSatha, although Moro does not know that name). 

In the brief flash of bright light, the Shroud is reaffirmed. 
The building is normal dry wood again. 
The people are regular \humans and \scathae.
They may be armed and evil villains intent on robbing them, but they are normal people. 

The muggers are scared off by the display of magic.
\ta{Holy fuck, it's a sorcerer! Let's get out of here.}

\begin{comment}
  \section{Moro comforts Rian}
\end{comment}
Rian is still scared shitless. 
He shakes.
Moro embraces him and holds him tight. 
At first very stiffly and uncomfortably.
She has thick mental blocks against intimacy.
But gradually her embrace becomes more affectionate. 
Her arms become softer.
Almost like a mother. 

Rian finds himself again. 
He comes to his senses. 
He asks what in \itzach that was. 

Moro tells him she is not sure what they saw.
It might have been real.
It might have been an illusion.
It might have been half of each. 

Moro reminds Rian that it is dark, and that his nerves are badly strained. 
His mind might just be playing him a trick. 
Or the \qliphoth.
Yes, that's it.
The \qliphoth might be trying to confuse him and scare him so that he will run away and forget his important task.

Rian points out that it can't all have been an illusion.
He still has slime on his shoulders and neck and head from when he bumped into the slimy building.
The building which is now solid, dry wood again. 

Moro slaps Rian up (but gently).
He must pull himself together and not give in to fear and psychological warfare.
That is just what the \qliphoth want. 
He must hang on.
They have an important task to do.
They must stop the evil. 

Rian:
\ta{Yes. You're right. Of course.
  And \MissCornel...
  Thanks.
  For saving me.
  And...}
She looks away uncomfortably.
She is embarrassed by her display of affection. 
Rian smiles. 
He realizes that to say any more would just embarrass them both further. 
But he is happy that he has broken through to her a little bit more. 

Moro:
\ta{We should get going.}





