\bookchapter{Needle Attacks Sentinels}








\begin{comment}
  \section{Needle thinks}
\end{comment}
Read about Needle. 

Needle is outside the Sentinel lair.
She and her many Cabalists are poised to attack. 

The trip here has been harrowing. 
\Malcur is going mad. 
Strange things are happening. 
The Sentinels' weird sorcery is affecting the city and everyone in it.
She personally lost two men to what appears to have been attacks by no one.
One man leaned against a house and vanished. 
Some nearby guys swear they saw the wall itself open up a big mouth and swallow him. 

Another guy suddenly went crazy. 
He became paranoid and attacked his fellow Cabalists, all the while raving and ranting madly.
Her own men were forced to kill him. 

She herself experienced one such \quo{attack} from the city. 
She stepped on what she thought was solid ground and suddenly found her one leg sinking into the earth, as if she had stepped into deep mud. 
Her fellow Cabalists had to come and pull her out. 
When they had pulled her up and examined the ground closer (with torches), it looked like solid ground again. 

It is all very eerie and scary. 
It is almost worse than the \banes. 
They are skulking along with her.
As their summoner, she has a certain empathic bond with them and knows where they are. 
They do not show themselves much, but they slink along in the shadows around her and her party of Cabalists. 
She does not understand how they move.
They seem to walk through walls and roofs at will. 
She does not know if they really can do that, if that is one of their superpowers, or if it just seems like it to her because her empathy is vague.

The empathy itself is bad enough. 
The \banes are horrible. 
Their minds are cold and alien and inhuman.
They have no recognizable emotions as far as she can tell, except for something which feels to her as a deep hunger. 
A hunger as if to consume other life.
All other life. 
Like a devouring emptiness.
As if the \banes are hollow shells and seek to fill themselves. 
She fears the \banes. 

She is half-mad with terror, but also with euphoria. 
Needle is growing ecstatic and hysterical, with the new dark powers at her command and the terrible \banes that follow her.
The \bane empathy is wearing down her sanity. 
She is slowly coming to accept the \banes, at the cost of her \humanity. 
She begins to share their hunger, as if she too is being consumed by a cold emptiness from inside that must devour in an attempt to fill itself. 

\lyricslimbonicart{Darkzone Martyrium}{
  I perish in my own desire.\\
  I burn within lusting hate.\\
  Destructively the minds inspire\\
  the soul to terminate.
  
  I ride the ancient overture\\
  as life is torn astray.\\
  I glance the illusive spectrum\\
  and all light that fades away.
  
  Black energies in the twilight space\\
  come shivering through the shallow haze.\\
  Into darkness so impure divine.\\
  A bloodshed emotion to evil wine.
}

Needle worries that she has tarried too long and that the Sentinels may have done too much damage already.
But then again, it might be best to strike now and take the Sentinels with their pants down while they are performing their great spell.
If she had attacked any earlier, she might have given herself away and the Sentinels could have escaped and regrouped and gone through with their spell anyway. 

Needle knows that she is rationalizing to herself. 
She should not worry so much about what she cannot change. 
She should just act.
She has her followers.
She has her \banes. 
She knows where the Sentinels are.
They are about to begin their great spell. 
The time to strike is now. 

They are outside the Sentinel building. 
They have been there the whole time.
All the above is just Needle thinking. 

Needle sounds the attack. 





\begin{comment}
  \section{Moro and Rian find Needle}
\end{comment}
\new
Moro and Rian are near the Sentinel lair. 
Rian's heart is pounding.
They have not been attacked since last time (where he was almost sucked into a slimy wall), but he has seen and heard and smelled many things that were scary and disquieting. 
He frantically recites familiar prayers to Silqua and the \sephiroth (or maybe just their names).
Over and over. 
Out loud or in his head.
It is an attempt to think happy thoughts and block out the horror and stay sane. 

They they hear loud noises.
Screams of fear and pain.
And noises of battle. 
Gunfire. 
Rustle of swords and daggers and clubs. 
Needle-tachi's attack has begun. 

They wonder who is fighting whom. 
Who are the sides?
The evil ones against someone, obviously, but who?
Good guys?
Other evil guys? 
Perhaps even the authorities?
Moro does not think it is the authorities. 
She makes sure to keep well-informed, so if there was a raid planned, she ought to know about it. 

Moro and Rian sneak closer. 
They see corpses that have been shot, stabbed or slashed. 

Moro sees one body that has been sliced to pieces, as if by many swift cuts by an incredibly sharp blade. 
She wonders who could have done such a deed. 
Is there some great expert swordsman on one of the sides?
Or is it done with some nasty spell that she does not know of?
Or, worse, by some nasty \emph{creature} that she does not know of?
(It is really a \bane that has done it.)

They sneak up to the house. 
They find some nice shadows to hide in. 
They peer inside, into a hallway. 
There is a great \melee going on.
It is impossible for them to tell who is on what side, or what the sides are. 

Moro looks into a corner.
She thinks she sees a dark blur speed by a man, and the man drops, savagely cut and slashed.
She could not see what the dark blur was.
It was too fast and too dark.
It is far away, and her view is poor, and it is dark, but she suspects it is the same thing that killed the guy outside. 
It is eerie.
She is afraid of it.
She does not want to cross its path. 





\begin{comment}
  \section{Banes wreak havoc}
\end{comment}
\new
The \banes wreak havoc on the Sentinel camp. 
They slaughter many Sentinels. 

It was an unforeseen development.
\Psyrex had not expected the Cabalists to loose \banes. 
And these \lesserbanes are small enough to be difficult to detect for a mage, but still deadly enough to be a great menace. 
\Psyrex fears he will have to go in himself and fight the \banes. 

\Psyrex decides to go down.
He does. 





\begin{comment}
  \section{Moro and Rian attack}
\end{comment}
\new
\begin{comment}
  \subsection{Looking around}
\end{comment}
They go around and try to find a better place where they can slip through.
The house is not just one big hall, but many rooms and hallways and corridors. 

They are afraid of the dark powers around them\dash the \banes{} worst of all. 
They feel the darkness and evil surrounding them, like a palpable force. 

\lyricslimbonicart{A Demonoid Virtue}{
  The night has predatorial eyes,\\
  drifting in a plae of disguise.\\
  Beneath the spelling moon\\
  the spirit rises out of darkness.\\
  The spirit rises\ldots{}
  
  Voices call for my soul.
}

Rian and Moro \Cornel{} explore the cellars beneath the Sentinel building.
They lead into a large set of dismal catacombs.  
They encounter monstrous creatures that infest the crypt. 
(These creatures do not necessarily serve anyone. They can just be degenerate mutants who have taken up residence in the old crypt.) 
They fight some of them and flee from more. 

They find hints of cults worshipping forbidden powers. And hints of the crypts' dark origins. Moro understands these, while Rian struggles to understand Moro. 

Moro should swear and curse by the forbidden names of the \xss.

\lyricsbalsagoth{The Obsidian Crown Unbound}{
  [The Sorcerer:]\\
  By Klatrymadon and Zuranthus!\\
  They come!
}

They sneak into a hallway.
A bandit jumps at them.
They do not know what side he is on, but Moro is prepared. 
She quickly casts a spell that causes him to double over in pain.
She tells Rian to help.
Rian attacks the man.
Rian carries a nice, good quality club/mace that Moro has procured for him from the palace \armoury.
Rian bashes the man with the club. 
Rian does not kill him.
He hesitates before stiking the killing blow. 
So Moro takes out her long dagger/dirk/kris and kills the bandit. 

They move on. 
They get into a bigger hall.
This is better lit. 
There are torches and braziers full of fire. 
Here there are some of the Sentinel sorcerers.
There are rows of attackers and defenders.
Behind them, they see the sorcerers. 

One of the sorcerers is not a normal \scatha.
He has the head of a monstrous snake.
It is one of the hideous \serpentmen. 
Both Moro and Rian are horrified.
They are so shocked they have to retreat back into the corridor from whence they came. 

% Two bandits follow them into the corridor and attack. 
% One of them fires a pistol, but luckily misses. 
% It is chaotic, bad firing conditions, and pistols are not very accurate. 
% And they are still in partial darkness. 
% 
% Moro and Rian have to retreat even more.
% It is darker and safer in the tunnel. 
% The two bandits follow. 
% Fortunately one bandit appears to be groggy and does not fight well.
% Rian beats him up with his club. 
% Moro takes on the other.
% He has just emptied his pistol, so he goes into \melee.
% Moro casts a spell of pain. 
% And another spell that causes open wounds.
% Then she kills him with her kris. 
% It is fairly cheap to cause wounds and pain and fear with magic.
% It is somewhat more expensive to kill with magic. 
% It is sometimes cheaper to kill using physical means. 
% She wants to preserve her strength for when she needs it. 

They decide to go another way. 

\begin{comment}
  \subsection{Meeting Needle}
\end{comment}
They go through the corridors and come into another fairly large room.
They are in an unseen corner. 
There is fighting here.

Rian sees Needle.

Rian:
\ta{Look!
  That is her!
  I saw her before.}

Moro recognizes her as \Piacet. 
They decide that she is an evil traitor and should be hated.
How dare she betray \Malcur and \rinyuth[\Tiroco] like this. 

They see Needle commanding her Cabalist troops. 
They decide that she is a leader. 
Then they see her chanting words in a strange language. 
And again they see the dark blur killing someone. 
They both see the blur. 

They figure that Needle apparently has access to magic. 
It looks like primitive magic to Moro, but primitive magic can be dangerous enough. 
Apparently she controls the killing blur. 

Needle is close to them and has not seen them. 
They figure that if they kill Needle, maybe they can cut off the head of this evil, and then the rest will fall. 
They acknowledge that they do not fully understand what is going on. 
But they have to do something.
They came here to stop dark magic. 
Needle is using dark magic.
Killing her seems like the right thing to do.

\begin{comment}
  \subsection{Killing Needle}
\end{comment}
So they kill her. 
Moro keeps Needle's defenders at bay. 
 (Only mortals are near. 
  There is a \bane, but it is quite some way away.
  And Needle does not think far enough to summon it to her aid right away.)
Rian distracts Needle and her companions by throwing knives at them. 
He has acquired skill in knife-throwing in his thieving days. 

This unexpected rear attack distracts Needle, and it distracts her Cabalists. 
The Sentinels are able to break through their defenses.
Suddenly all Needle's defenders have their hands full fighting the Sentinels that are attacking from the front.
They have no time to defend Needle, who is being ambushed from the rear. 

Then Moro goes in and kills Needle. 





\begin{comment}
  \subsection{Needle dies}
\end{comment}
\new 
Needle is dying. 
She tries to recite her orison to \Achsah and beg for her help.
But it is no use. 
She does not have the strength to cast the orison properly.
She is in too much pain to concentrate.
And \Achsah is far away and busy with her own stuff. 

Before Needle dies, Rian asks her: 
\ta{Why do you do this?}

Needle: 
\ta{For survival. 
  For the future of my people. 
  \emph{Our} people, damn you! 
  For \human kind's survival!}

Just before she dies, Needle's last thoughts are: 
\tho{Great \resphain.
  \Achsah.
  \Teshrial.
  Etc.
  Forgive me for failing you. 
  But I have loved you and served you with all my being.
  Truly I have. 
  
  I have no regrets.
  
  No.
  That's not true. 
  There is something I regret.
  I regret\ldots{}}

And then she dies. 
We never get to hear what she regrets. 

Needle is sad to die. 
She was not evil.
She was genuinely working for a better world. 
She believed in the \resphain.
She saw how evil the current world order was, and she was convinced a \resphan world order would be better. 

Remember that Rian now has a religious trauma and fears that there is something wrong with the \sephiroth. 
He tries rationalizing it away, but a lingering dread remains and will return to haunt him throughout the story. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  The Shrine of Mad Laughter
}{
  The idea of God is pale next to that of perdition, \\
  but of this I could have no inkling in advance.
}






\begin{comment}
  \section{Moro and Rian attacked by Bane}
\end{comment}
\new 
Then a \bane comes near. 
They run into a corridor. 
They meet some Sentinel thugs.
They run past the Sentinels.
The \bane kills the Sentinels.
Then Moro and Rian have to deal with the \bane. 

Or maybe have them see it some more at first glance.
They are terrified of this alien monster, so they run.
Only later does Moro muster up the courage to fight it. 

At first glance they only see it unclearly:
A bluish-black humanoid with no face.
Possibly with four arms (hard to tell). 

They see it quickly and viciously attack and dismember the two Sentinels.
Like a dark blur. 

The \bane moves through a light area under two torches, and they get to see it clearly. 
Moro and Rian are horrified. 
It is alien and monstrous, and yet hideously humanoid. 
Frighteningly familiar.
And faceless. 
Just a blank slate where a normal creature ought to have a face. 
Moro thinks quickly. 
It is a \bane. 
She has not seen a \bane before, but she has read about them.

It sights them and decides they are enemies.
It attacks. 

Moro casts a big spell in haste, roughly aimed at the \bane. 
It hits and causes damage and pain.
It gives pause to the \bane. 

Rian wants to cower down and tremble. 
Moro looks at him. 
She wants to do the same. 
She fears the \bane. 
But she cannot. 
She must not! 
She casts another spell to drive the \bane away for a moment and give her more breathing room. 

She has a duty to Rian, and to Neina, and to the rest of the prisoners, and to \Tiroco, and to all of \Malcur. 
And to all that is good and decent.
She cannot just sit here and cower.
She cannot run away.
She has been running away and hiding for too much of her life.
She must take action. 
She is one of the most powerful mages in Pelidor. 
If she cannot do this, no one can. 
She has paid a heavy moral price for her magical powers.
Now she owes it to the world to do some good with those powers. 

Rian might be able to sneak/fight his way into the dungeon and free Neina-tachi. 
But he will need cover. 
He can do nothing against the \bane. 
But she can. 
With all her magic, she can combat it. 
Moro summons up all her courage. 
She will. 

Moro kicks Rian hard and tells him to run for it.
\ta{Go! Free the prisoners!}

Rian wakes from his panic. 
He looks over at the \bane. 

Moro:
\ta{Don't look! I will deal with it! \shout{Just go}!}





\begin{comment}
  \section{Rian in the dungeon}
\end{comment}
\new
Rian flees, as Moro has told him to.
He is terrified at the thought of the \bane. 
It is a loathsome creature that ought not to exist. 

\hr{Rian is religious}{Make Rian more religious}.
Make sure he prays in every chapter and scene that he is in.
When he sees \Ishnaruchaefir, he prays for deliverance from this great evil.
He prays to be delivered from \Isphet's evil. 
He has lingering existential/religious dread from the day when he saw the dark sorcerer slay the shining god (even though he was Shrouded and does not remember it all). 

In all the Rian chapters, whenever it is appropriate, have references to the \hr{Myths of vanquished monsters}{myths of Iquinian heroes vanquishing inhuman Elder Races and monsters}. 
When he encounters something supernatural, he fears that the wicked Elder monsters will conquer the world. 

He prays a lot.
He prays for deliverance from the \bane. 
He prays to forget the \bane.
He prays that the \bane does not really exist. 
He intones Silqua's and the \sephiroth's names again and again, trying to convince himself that the world is ruled by good and that the \bane does not exist.  

Rian is slowly being driven mad by the things he has witnessed. 

\lyricslimbonicart{The Yawning Abyss of Madness}{
  Behind the sealed door to imagination \\
  I sense the voices of devastation. \\
  Dementia praecox. 
  
  A cascade of dark emotions. \\
  An ominous silence imprisons me\\
  with disfigured landscapes.
}

Remember that Rian now has a religious trauma and fears that there is something wrong with the \sephiroth. 
He tries rationalizing it away, but a lingering dread remains and will return to haunt him throughout the story. 

\citebandsong{DeathspellOmega:FasIteMaledictiinIgnemAeternum}{%
  Deathspell Omega
}{
  The Shrine of Mad Laughter
}{
  The idea of God is pale next to that of perdition, \\
  but of this I could have no inkling in advance.
}




\begin{comment}
  \section{Psyrex comes down}
\end{comment}
\new
\Psyrex has come down. 
He has just destroyed the second \bane. 
He notices that the \banes became easier to fight after a while. 
They suddenly got stupid, less \coordinated, more confused.
They even killed their own Cabalist allies on occasion. 

Evidently someone must have killed the summoner who was in charge of them.
After that, the \banes had to act on their own. 
\Banes are not stupid, but these ones probably know little of \Malcuric politics, so they might have a hard time figuring out whom they were supposed to kill and whom they were supposed to protect. 





\begin{comment}
  \section{Moro saved by Psyrex}
\end{comment}
\new
Moro fights the \bane. 
It is too powerful for her to kill, but Moro has enough magic to be able to hold it at bay and give them time to escape. 

Moro uses the spell \word{\hs{khestni}}. 
It hurts the \bane, but does not kill it. 
It is traumatic for Moro to cast. 
It almost hurts her more than the \bane. 

Whenever Moro draws deep of her terrible magic, she fears that perverse powers might gain control of her. 

\lyricslimbonicart{A Demonoid Virtue}{
  Voices call for my soul.
  
  The cunning serpents kiss I taste.\\
  Baptised beside the ancient takes of\\
  fire, fire burning higher.\\
  Unite with me in dark desires.\\
  I perish in bliss of cruelty.\\
  Tormented souls will never rest in peace.
}

But time and time again she must risk it\dash such as when fending off the \bane. 

\lyricslimbonicart{A Demonoid Virtue}{
  In the flames an omen blaze,\\
  enforcing throught the cosmic haze.\\
  To cross the line and dare to glance,\\
  and enter cold void where death romances\\
  in mysteries.
}

She cannot kill it, but she can keep it at bay and occupy its attention long enough for \Psyrex to deal with the other two \banes. 
She keeps it at bay and wounds it somewhat, but she cannot defeat it. 
Her strategy is to blast it with a spell and flee a little bit, then repeat. 
It is wearing her down.
She cannot hold it off forever. 

She is resigning herself to the idea that she will soon die.
Cut down by a monstrous alien. 
But at least she died for a good cause.
She hopes she has helped \Malcur.
And helped Rian.
She hopes she has done a good thing in her otherwise sucky life. 

\Psyrex comes down.
He tracks down the \banes and kills them one by one.
Finally he goes after the one that is chasing Moro.
He tracks it down.
It is just about to kill Moro, but she is bravely holding on and fighting it off.
It has gotten some hits in.
Moro is wounded.
She will not last long. 
She cannot defend herself much longer. 
She is too weak to attack and can only keep up an all-out defense, repelling the \bane a bit and shielding herself. 

Then \Psyrex comes and attacks the \bane. 
The \bane quickly realizes that \Psyrex is a much greater threat, so it ignores the crippled Moro and tries to attack \Psyrex. 
But \Psyrex is an awesome archmage and quickly kills it. 

Moro lies bleeding and exhausted. 
She looks up. 
She thanks \Psyrex for saving her. 
But she is also horrified to see him, for he is a \serpentman. 

\Psyrex says it is nothing. 
He should be more thankful to her for killing Needle. 
But if she will excuse him, he has to be going.
He goes away to begin his big spell. 
Moro is wounded. 
She begins using spells to heal herself. 
She knows she is too weak now to fight any more baddies. 
She has to figure out another way to do some good. 

She did not quite understand what the \serpentman said. 
But it troubles her.
A lot. 
She knows that she acted in haste when she killed Needle. 
Was it the wrong thing to do?
Has she killed the wrong person?

She curses herself.
Just when she thought she was doing good, it turns out she may have done more harm than good?
She really sucks. 
She hates herself. 

She gets to her feet.
All is not lost yet.
There is time to do something.
If she cannot solve the world's problems by killing people, then she must try something else. 





