\bookchapter{Needle Summons \Banes}
\stamp
  {\dateNeedleSummonsBanes}
  {Slave quarters, \CastlePelidor, Malcur}












Remember to read up on \banes{} and on Needle and \Achsah.
And the Cabal.



\begin{comment}
  \section{Needle contacts Achsah}
\end{comment}

Needle has received word from her Cabalist subordinates. 
They have found the location of the Sentinels' big lair. 

They received some help from their \resphan lords in finding it.
They know that the Sentinels are planning some big spell. 
Such a spell has magical energy leaking out all over the place. 
So the \resphain, with a little effort, were able to determine the approximate locations of the sorcerers, or at least narrow it down. 
They then told Needle to send out her Cabalists and pinpoint the Sentinel lair.
She did, and they did. 

Her spies have also done some listening and interrogation and found out the time of the big spell.
It is soon. 

Ever since receiving word, Needle has been planning a big raid on the Sentinels. 
But she fears she does not have enough manpower.
The Sentinels have mages, after all.
Usually the Cabalists in Malcur have had Charcoal, but he is gone now. 
They only have Needle.

Needle needs supernatural aid.
So she casts her orison to contact \Achsah. 

\Achsah is far away (in \Forclin).
She muses that she should have thought ahead and taught Needle a spell to contact some other \resphain, some that actually were in Malcur. 
But fortunately, she is a High Telepath. 
She tells Needle to explain herself.

Needle explains her situation and requests aid. 

\Achsah agrees.
Needle needs aid.

\Achsah: 
\ta{Go into the crypt and summon \SitraAchras. \Banes.}








\begin{comment}
  \section{Needle goes into the crypt}
\end{comment}
\new 
Needle goes into the crypt. 
It scares her. 
Needle has only seen the closest levels of that crypt, and they were eerie enough.
Now she has to go deeper. 

When \Achsah told her to go down here, Needle did not want to and asked if she had to.
\Achsah tells her that she cannot just send \banes anywhere.
The crypts are a magical place where the barriers between this world and the worlds of the \resphain and the \banes are thin. 
Down here it is possible to summon the \banes. 

She goes into the Vaimon-built crypt beneath \CastlePelidor. 
These are dark, disused and have an \quo{antediluvian} feel to them. 
It is a secret place built by Cabalists in the \VaimonCaliphate to serve as a gateway to \Nyx. 
Everwhere, she feels as if the eyes of wicked \Qliphoth{} are upon her. 
As if her audacious steps cause sleeping powers to stir in anger. 
She's afraid. 

The tunnels are very large, being \resphan-built. 
But they are smaller than \ophidian buildings would be.
(Read about {\resphan architecture}.)

\lyricslimbonicart{Towards the Oblivion of Dreams}{
  With the underworld's \\
  subconscious darkness I am allied. \\
  Deeper aspects, forces of nature,\\
  mind can now see the unseen. \\
  Ancient land hidden from man. \\
  An esoteric dream in the desert sand. \\
  Shimmering sparks in the darkness, \\
  as death overtakes the soul. \\
  Loose the body, and earthly conscience. \\
  The freedom of the spirit must be total.
}

She has taken some books with her containing the spells she will need.
\Achsah will guide her through it, but she will have to perform part of the ritual herself. 
She must first study the spells thoroughly.
Then, when she has memorized them, she is to contact \Achsah again. 

She spends what she estimates to be more than an hour studying the spells. 
At last she feels she is ready.



\begin{comment}
  \section{Hosts are brought in}
\end{comment}

Then she procures the hosts.
The \banes{} cannot come to \Miith{} directly, but need to possess a \human{} host. 
So Needle brings three prisoners with her to use. 
They are dungeon inmates, scum, worthless people whom no one will miss. 
She has had her fellow Cabalists take them from the dungeon and bring them into the crypt. 
The hosts are securely chained so they cannot escape. 

Then Needle tells her fellow Cabalists to leave.
She will perform the rest of the spell alone. 
(Or maybe they stay. If Needle is not naked, they might as well stay.)







\begin{comment}
  \section{Needle begins spell}
\end{comment}
Needle contacts \Achsah. 
She begins the spell, with \Achsah's guidance and power backing her. 

The ritual is dark and mildly erotic. 
She must circumvent the \Sephiroth{} and invoke \Qliphoth{}, and even nameless powers. 

Is she naked? 
She might be, but only if I can come up with a good excuse for stripping her. 
Perhaps she was simply told that she should be naked because the \resphain{} like the sight of a \human{} prostrate, naked and begging\dash completely humiliated and submissive. 
Perhaps \Achsah{} sexually abuses her a bit. 

Needle is pretty afraid, for she has never had to deal with major issues like this alone before. 
Nor has she ever seen a \bane. 
They are horrible creatures. 
She is frightened at having to take command of them. 

Needle mentions the Shroud. 
She doesn't really understand what the Shroud is. 
But is proud that she knows it exists. 

\lyricslimbonicart{Moon in the Scorpio}{
  In an atmosphere supreme\\
  forces dwell in domancy.\\
  The essence of its spirit is evil,\\
  as a curse upon thy name.
  
  Midnight is the shepherd of mysterious powers\\
  and moving shadows in the corner of the eye.\\
  Moon's blazing intuition\\
  contains what death requires.
  
  Cleanse the doors of perception.\\
  See things appear in its true art.\\
  The cold hands of divinity\\
  will tear thy soul apart.
  
  Behold the sky above \\
  when the moon is in the Scorpio.\\
  A cold bleak light. 
}






\begin{comment}
  \section{Needle thinks back}
\end{comment}

Needle is reminded of the day when she first became a Cabalist, where she was first confronted with \itzach, \Nyx{} and the horrors that dwell there. 
She feels like she is re-living it. 

\lyricsdimmuborgir{Grotesquery Conceiled Within Measureless Magic}{
  For thy presence made pleasure of pain,\\
  and thy madness turned sanity into vain.\\
  Profoundly wicked owner of souls.\\
  The mysteries of thy creation beheld by ghouls.
  
  Diabolically disguised heavenly bodies,\\
  and its atrociously desired primordial elements.\\
  Plunging through the confused beart of sulphur.\\
  In all this darkness, how can a man see?
}

She originally thought that mages were specially gifted supermen with inborn magical powers beyond the ken of the common herd. 
She was wildly surprised and more than a little scared when Charcoal-tachi told her that \emph{she} herself could learn magic. 
According to Charcoal, all it took to cast magic was a worthwhile brain and the willingness to see beyond the lies with which the common folk surround themselves (code for the Shroud) and face the dark truths of the universe. 
And then grab this truth with both hands and coerce it to spit out what you want. 







\begin{comment}
  \section{The Banes arrive}
\end{comment}

She manages to summon three \SitraAchra \quo{\stalkers} (\lesserbanes). 
The \banes{} are terrible. 
Needle is scared shitless at commanding them. 
(She notices that they wear splint-mail-like armour\ldots{} maybe.)

The \banes{} approach her and seem very menacing. 
She can't control them. 
They come ever closer. 

They seem to be directing some mental attack her at her, which she can't defend herself against. 

Needle panics, thinking that they are coming to eat her. 
She freezes up, or falls to her knees. 
She begins crying and whimpering. 
She whines and begs: 
\ta{Stay back! Go away! Don't hurt me\ldots{}}
She pleads with them to spare her life. 

\Achsah{} contacts her telepathically and slaps her up, telling her to get a hold of herself. 

Needle realizes that the \banes{} never intended to hurt her. 
They were simply menacing because that is how \banes{} appear to \humans: 
Hideous, cold, alien, evil. 

It turns out that the \pps{\banes}{} \quo{mental attack} was simply an attempt to communicate. 
They spoke to her in their telekinetic language and told her their names. 
\Bane{} names are not words but kinetic sensations. 
They are terribly frightening to unsuspecting mortals. 
\tho{So that's their way of speech, is it?}
To Needle it felt as if they were carving their names with daggers on her bare skin. 

Slowly she gets the hang of commanding them. 
But she is still afraid of them. 
Perhaps this gradually drives her mad. 

The three \pps{\banes}{} names are Quicksand, Undercurrent and Gallow. 
They look completely alike to her eyes, but their telepathic \quo{feel} is different. 

Seeing the \banes{} and fearing their terrible power makes Needle admire the \resphain{} even more, since they are mighty enough to control such fell, wicked beings. 
She comes to love them even more. 





\begin{comment}
  \section{Achsah laughs}
\end{comment}
\new
\Achsah has been observing. 
Now she sits back and laughs. 
There was no real need for Needle to be naked during the ritual. 
It was just a practical joke \Achsah{} pulled on her. 

She jokingly scolds herself for it. 
\tho{%
  That was unfair of me. 
  I shouldn't be doing that. 
  Playing tricks on poor, unsuspecting minions. 
  Naughty, wicked \Achsah.}





