\bookchapter{Rian finds Neina}





\subsubsection{Rian chooses to save the girl}
Rian has the opportunity to stave off \Malcur's fall for a little while and save many more lives, but that would seriously endanger Neina. 
Rian is a dumbass and chooses to \trope{AlwaysSaveTheGirl}{Always Save the Girl}. 
Moro berates him for it to his face, and later (after he has gone) curses him in retrospect for being selfish and choosing what was obviously the worse choice.




\subsubsection{Rian finds Neina and escapes}
\target{they find Neina}
In the chaos that ensues after the \banes wreak havoc in the Sentinel camp, Rian slips in and manages to find and rescue Neina.

Have a long, tension-filled scene where we hop back and forth between Neina and Rian. 
There is a thug, Blon, who wants to rape Neina.
He reaches into her cell and gropes her. 
She shies away and hates him and suffers. 
But he dares not rape her because the sorcerers forbid it. 

Later, when all hell is breaking loose, Blon decides he might as well go for it. 
So while the rest are running around confused, he goes to Neina. 
He gropes her and undresses her. 
She screams and fights.
She manages to kick him painfully in the nuts.
He retreats a bit to get over the pain. 
This gives her a short reprieve.
Then he comes back in and beats her savagely. 
He rips her clothes off.
She screams and cries. 
She is desperate. 
She does not want to believe that this is happening to her. 
At last, he penetrates her and completes his violation of her. 
She loses her virginity to an evil, ugly, foul-smelling crook whom she hates. 

All the while, we hop back and forth between Rian and Neina.
He runs around frantically looking for her. 
At last he reaches her.
She is being raped by Blon. 
Rian attacks.
Blon pulls out.
Rian kills him.
This is the first person Rian has ever killed. 
As Blon dies, sperm pours out of his dick onto the ground.
Neina has been raped, but they can take some small consolation in the fact that Blon did not come inside her. 

Rian has saved her, but at a terrible price. 
Everything else is going to hell around them. 
Moro wished he was with her.
Together they might have been able to save more people.
But no.
Rian had only eyes for Neina.
He insisted that he had to \trope{AlwaysSaveTheGirl}{Always Save the Girl}.
It was a horribly bad choice from a utilitarian point-of-view, and he did not even succeed. 
Karma by proxy! 

Neina, being a weak soul, \hr{Weak souls go mad in Malcur}{is affected by the Change}.
She may be half-mad. 
She comes somewhat to her senses when she gets out of Malcur, but she will never be quite sane again. 





%At the last minute, however, they manage to escape. 
Rian finds Neina and they run away together. 

The sight of the two together, their love and happiness at being finally reunited, reaches Moro's heart, and she is both touched and envious. It softens her a little bit, and she gains a bit of hope for the future and the world.





\subsubsection{Neina's story}
\target{Neina's story}
Neina was supposed to have been killed a while ago. But some of the Sentinel-hired thugs screwed up, and she was left to rot in a dungeon for many weeks. 

A few times she was dragged to a ritual to be sacrificed, but then not sacrificed anyway and returned to the dungeon. 
\ps{\Psyrex}{} thugs are not the most organized people in the world. 

When Rian comes to rescue her, she is half-mad and hysterical, babbling about monsters and black magic. She is quite useless. 





\subsubsection{Rian and Moro almost eaten by living house}
\target{Rian and Neina are separated from Moro}
Rian, Neina and Moro huddle inside a house. Then suddenly the Shroud opens up and the house reveals itself as a monstrous living entity. It makes a grab for them with its claws or tentacles, intending to devour them. 

Compare to a scene in the anime \cite[episode 1]{Anime:IczerOne}, where a house comes alive.

They escape, but in the chaos, Rian and Neina get separated from Moro. Now the young lovers are in deep shit, because it was Moro's skill and sorcery that was keeping them alive.

Rian develops a nasty case of claustrophobia after being almost eaten by a living house, having seen the walls literally close in around him and turn into monstrous mouths. 





\subsubsection{Maybe Rian dies}
\target{Maybe Rian dies}
Maybe I will \hr{Remove Tiroco story thread}{remove the \Tiroco story thread}. 
If so, I might kill Rian and Neina instead.

\begin{itemize}
  \item 
    Maybe Moro tries to convince Rian to help her do some real good and save as many people as they can.
    Rian instead runs off, frantically intent on saving Neina, whatever the cost to everyone else. 
    He is quickly killed as punishment for his stupidity.
    \quo{\trope{AlwaysSaveTheGirl}{Always Save the Girl}} is not a good idea on \Miith. 
    
  \item 
    Maybe Rian does find Neina.
    He rescues her while she is still a virgin.
    They run out. 
    Then they are killed. 
\end{itemize}

Maybe Rian is killed by a \bane before Moro's eyes. 
Moro gets traumatized. 
But at least she manages to do some good and save some other people. 

Maybe it is Moro who gets rescued by \Criseis in the end. 
