\bookchapter{\Teshrial Goes to Meet \Ishnaruchaefir}
The time of \Teshrial's duel with \Ishnaruchaefir is almost at hand.
\Teshrial goes off to the agreed place to meet \Ishnaruchaefir.
\Menessiaraid is with him. 





\subsubsection{Stewardship of Malcur}
\target{Teshrial leaves Bezed in charge}
\Teshrial{} knows that Malcur is terribly important and that it would be bad if it fell into the Sentinels' hands. 
He must be careful and guard it against \Psyrex-tachi while he himself is off fighting. 
He knows the time of his duel is coming up, so he has contacted his superiors and requested to have more aid sent to him. 
Some more \resphain{} come to relieve him. 

When he feels that \Ishnaruchaefir{} is near, he takes off and leaves some low-ranking \resphain{} in charge of Malcur. 
At this point \Achsah{} is already in \Forclin. 

\Teshrial{} thinks he is manipulating \Ishnaruchaefir{} and forcing him to face him at the right astrological moment. 
But he is actually being strung along. 

\lyricslimbonicart{In Mourning Mystique}{
  Darkness!\\
  I seek the silence that you bring.
  
  Grant me thy sacred gifts,\\
  bestow my soul thy offerings.\\
  Let the ancient forces of nature rule.\\
  Take my blood as the sacrifice,\\
  a symbolic faithful bond of truth.\\
  I kneel in front of thy altar black.
  
  When you look into an abyss, the abyss also looks into you.
  
  Tonight I enter into obscure dreams.\\
  In darkness shelter, I am unseen.\\
  With the esoteric gifts I possess\\
  I bring damnation by enforcing death.\\
  In the beginning of the storm \\
  I'll come forth.
  
  An arrival into a twilight reverb\\
  as just a shadow of the former self.
  Sorrow is my name.\\
  My true essence is pain
  
  Hear the mourning of the mendacious\\
  from the empty halls and shafts\\
  of false blinding light.\\
  Prepare the last sacrifice (on the altar)\\
  in the temple of decay.
  
  Please spare me from the final agony of shame.
  
  I am evil from the moment of conception.
}





\subsubsection{\Achsah wishes him well}
As \Teshrial{} departs, he contacts \Achsah{} telepathically and briefs her. 
She expresses her fears and concern for him. 
I need to paint some measure of friendship between the two. 
She does not like him, but she does not want him to die a painful death, or mutate permanently into a monster. 
She asks him to be careful and wishes him luck. 
He thanks her. 

This is small measure of making-up for them. 
They have never liked one another.
Here at the last minute, they take steps toward each other. 
It should be a bit touching, and tragic in retrospect. 





\subsubsection{\Teshrial sees how ugly \Nyx is}
In a scene late in the book, after \Teshrial has acquainted himself with the \noggyaleth, \neoresphain and \WanderersInDarknessEmph:
  
He flies above \Nyx.
He sees the \bane-built spires. 
Now that he gazes into the deep, he notices how twisted they are.
They look really scary and wicked.
He had always taken them for granted, but now that he has gazed deep on the dark mysteries of his people (and the even darker mysteries of the \banes), they scare him.
There is something evil about the way they twist and bulge.
They twist into alien dimensions (more alien that what he likes to consider). 
Like they are appendages of some vast monster that tries to crawl and claw its way up from the deep where it belongs. 
See also the sections on \maybehr{Nyx}{\Nyx}, \maybehr{Resphan architecture}{\resphan architecture} and \maybehs{dark ancient cities}. 





\subsubsection{He is nervous}
\Teshrial{} is nervous and afraid to enter his battle. 
After all, he is just a \ketheran{} facing a terrible \shaeeroth. 
But he thinks of \ps{\Firaxel} kiss. 
And her sexiness, her hot and lusty eyes, and her soft, whispered promises of erotic bliss to come. 
This gives him courage and strength. 
It is \trope{ThePowerOfLove}{The Power of Love}. 

There is also a little bit of unexpected \trope{ThePowerOfFriendship}{Power of Friendship} from \Achsah and \Urizeth. 

Thinking of these bright things, \Teshrial{} takes heart. 
He rights himself and is now ready to face \Ishnaruchaefir. 









