
\bookchapter{\Teshrial Prepares to Battle \Ishnaruchaefir}
\Teshrial{} suspects that \Ishnaruchaefir{} will soon return. 
He prepares himself to face him. 

\Teshrial{} is laying a trap for \Ishnaruchaefir. 
He plans to meet him in a place parallel to Malcur, but farther away from the Shroud (perhaps through the \maybehs{dead garden} again). 
He has his \noggyaleth{} lying in wait and intends to call them out to ambush \Ishnaruchaefir{} while fighting him. 

\Teshrial{} has several trump cards:
\begin{itemize}
  \item The Shroud.
  \item Astrology. 
  \item \Noggyaleth.
  \item The Achilles Heel. 
\end{itemize}





\subsubsection{\Teshrial refuses ambush}
\target{Teshrial fears to break agreement with Ishnaruchaefir}
The other \resphain tell \Teshrial that they should set a bigger ambush for \Ishnaruchaefir, have some more \resphain lie and wait and attack him. 
\Teshrial very firmly declines and explains his reasons.

\Ishnaruchaefir has promised to fight \Teshrial alone.
If \Teshrial breaks their agreement, \Ishnaruchaefir will refuse to fight and exact a terrible vengeance later. 
They now have a chance to exploit the Destroyer's code of honour. 
They would be fools to let that go to waste. 

Instead, several powerful \resphain give \Teshrial gifts of magical items for him to use in the battle, including a sword, pistols, armour, amulets and wing braces.





\subsubsection{\Achsah contacts \Teshrial}
\Achsah contacts \Teshrial. 
She tells him about the situation in \Forclin.
He only listens half-heartedly.
She can tell that he is obsessed with his upcoming duel. 

\Achsah fears for him. 
She tries to dissuade him. 
\Teshrial brushes her off and berates her for her cowardice.

Afterwards, \Teshrial is a bit ashamed. 
He should treat \Achsah better, he reflects. 
She is worried about him.
He should respect that.
He resolves that after the battle he will try to be nicer to his \bezed subordinates.
This is a part of \maybehr{Teshrial's unfinished business}{\Teshrial's unfinished business}. 




\subsubsection{His brethren fear for him}
Make it clear \ps{\Teshrial} brethren fear for him and want him to succeed. 
\Menessiaraid, his close friend, comes to see him off. 

\Menessiaraid{} gives \Teshrial{} a gift: 
His own \senaan, \maybehr{Ossiraith}{\Ossiraith}. 
He knows \ps{\Teshrial} favourite weapon, \maybehr{Turishah}{\Turishah}, was destroyed. 
He entrusts his friend with \Ossiraith. 
\Teshrial{} is honoured and vows to put it to good use. 

In addition to \Ossiraith, \Teshrial{} carries into battle two \maybehr{Ghijed}{\ghijedeth}. 
Before going into battle he looks down at his pistols. 
He takes them with him just in case, but he does not expect so much from them. 
\Ishnaruchaefir{} will probably wear \maybehs{ward runes}, and as such will be protected against guns. 
Guns are not so great in single combat with \dragons{} overall.
They are good if you can outnumber or outmanoeuvre your enemy. 
But in a fight like this, \melee{} is the best way to go. 

\Teshrial dresses for the battle so as to match \Ossiraith. 
Read about \maybehr{Ossiraith}{\Ossiraith} and dress \Teshrial in the same colour. 

\Urizeth also fears for him.
She is sad that she will be nowhere near him during the battle.
She feels a bit cowardly for it.
\Teshrial is also warming towards her.
This is part of his personal development and \maybehr{Teshrial's unfinished business}{his unfinished business}. 





\subsubsection{\Firaxel visits him}
\target{Teshrial's date}
\Teshrial{} is visited by \Firaxel. 
He has specifically asked her to come see him off to his duel. 
He wants to see her one more time before he risks his life and soul. 
She is attracted to him and wants to see him, too. 
They have an intimate, romantic date. 

\maybehr{Firaxel is a scientist}{\Firaxel{} is a scientist}. 
He learns that she greatly admires people who do something to advance science, especially if they take great risks to do so. 

\begin{prose}
  \Firaxel: 
  \ta{Our race exists for a purpose: 
    To improve ourselves, to bring ourselves closer to perfection.
    And our best and finest tool in this quest is science.}
\end{prose}

\Teshrial{} wants to impress her. 
So he tells her of how he has spoken with cutting-edge researchers and is participating in the \neoresphan{} project and testing a dangerous experimental weapon. 
It is dangerous, but he does it. 
So he is fighting and risking his life not only to prove himself and for the war and rid the world of an evil menace and avenge all the victims of the wicked \Ishnaruchaefir, but also for science and the betterment of their people. 

This turns her on. 
He can see it. 
Her eyes glow with desire. 
Her breasts heave. 
She licks her lips with hunger. 

They \emph{almost} have sex. 
They certainly kiss and grope. 
She promises him sex (in unmistakable terms) when he returns triumphant. 
The best sex of his life. 
And he can believe it. 
\Resviel{} are great lovers. 

He walks away happy. 
His dreams are coming true. 
Seeing her has given him courage. 
Before he was unsure if he dared use the experimental weapon. 
He was planning on holding it back as a desperate last resort, and even so he was unsure if he would have the courage to use it. 
But now he knows how much \Firaxel{} will love him for it. 
Now he dares use it. 
For \ps{\Firaxel} sake he is willing to take that risk. 

Have some from \ps{\Firaxel} POV. 
\Firaxel{} has developed genuine feelings for him and is afraid for him. 
She admires him. 

\begin{prose}
  \tho{What a \resphan. 
    What a brave, noble, beautiful soul. 
  
    But my heart aches to see you go. 
    I fear to let you do this. 
    Silly warrior \resphan. 
    Why must you risk your life and your very soul? 
    Your bravery alone was enough to bring me into his bed. 
    I can't wait to have sex with you. 
    
    But what if you fail?
    What if you die? 
    I might never see you again. 
    This might be our last moment together.
    What then? 
    
    I want to have sex with you here and now.
    If only I could. 
    But I can't. 
    I have a duty. 
    I cannot give myself to anyone less than a true hero. 
    Otherwise I would be a slut.
    I have no choice but to wait.
    
    Damn all these rules.
    
    Come back safely to me.
    My brave, beautiful hero. 
    My sweet, beloved prince.}
\end{prose}

\lyricslimbonicart{In Mourning Mystique}{
  Darkness!\\
  I seek the silence that you bring.
  
  Grant me thy sacred gifts,\\
  bestow my soul thy offerings.\\
  Let the ancient forces of nature rule.\\
  Take my blood as the sacrifice,\\
  a symbolic faithful bond of truth.\\
  I kneel in front of thy altar black.
  
  When you look into an abyss, the abyss also looks into you.
  
  Tonight I enter into obscure dreams.\\
  In darkness shelter, I am unseen.\\
  With the esoteric gifts I possess\\
  I bring damnation by enforcing death.\\
  In the beginning of the storm \\
  I'll come forth.
  
  An arrival into a twilight reverb\\
  as just a shadow of the former self.
  Sorrow is my name.\\
  My true essence is pain
  
  Hear the mourning of the mendacious\\
  from the empty halls and shafts\\
  of false blinding light.\\
  Prepare the last sacrifice (on the altar)\\
  in the temple of decay.
  
  Please spare me from the final agony of shame.
  
  I am evil from the moment of conception.
}






