\bookchapter{Prologue}

\begin{comment}
\chapter{The \Secondbanewar}
\end{comment}

%     Mention that the slain \dragons{} and \resphain{} have had not just their bodies destroyed but their immortal souls as well. 
%     
%     Not only \dragons lie dead, but also their \quiljaaran allies. 
% 
%     Make the \dragons darker, more demonic, more sinister.
%     Less sympathy and \trope{TheWoobie}{Woobie}-ness. 
%     More badass and \trope{CosmicHorror}{Cosmic Horror}.
%     Emphasize their coldness and alien-ness.
%     \Nzessuacrith gazes out over the world with cold \ophidian eyes.
% 
%     See also the section on \hs{dark ancient cities}. 
%    
%     \Nzessuacrith sees the wrecks of mighty cannons and vast war machines of metal and flesh. 
%     She herself bears grim wounds. 
%     She lost her right forearm in battle with a titanic \umbra; a soul-devouring monster from \Erebos, fully as large as she was.
%     Call her \quo{Cryocas}.
%     Cater to the dumb reader who cannot understand long names. 
%     And get rid of those dead \dragons. At least, do not name them.  
%     
%     Perhaps \Nzessuacrith sees some dead bodies that have revived and are slowly, painfully crawling/limping from the battlefield. 

\begin{comment}
\section{\Nzessuacrith}
\end{comment}
\stamp
  {\dateSecherdamonsVow}
  {Aftermath of the \Secondbanewar}

\ta{So much death.}

{\CryocasNzessuacrith} spoke her thoughts aloud, even though no one was there to hear her voice but the \hr{Daemons}{\daemons} that lurked behind the veils of the world. 
Soaring above the field of battle on her silvern wings, she surveyed the carnage around her. 
% So much death. 
% Wherever she looked, and however far, \Nzessuacrith{} saw only destruction and death. 
% 
%She flew over the battlefield. 
% High above the field of battle she flew. 
Fire still burned in the ruined cities and the wrecks of homes and machines. 
Columns of black smoke blocked out the sunlight, turning dawn into gloomy dusk. 
The smoke stung her many scars, some of which still bled. 
And strewn everywhere lay the corpses of her fallen \hr{Dragon}{\draconian} brethren. 

%     \Nzessuacrith{} smells the air with her tongue. 

There was Kelthasserai, with whom she had often gone hunting. 
Now he lay skewered, each of his two hearts pierced by a barbed \hr{Resphan}{\resphan} lance. 
In his death throes he had torn to shreds a score of \resphain{} and their beasts of war, and now their remains lay scattered around him as a bloody tomb ornament. 
And there was Skelcurmaggra, who had taught her many a thing of sorcery. 
Fire had reduced her wings to blackened stumps, and once grounded she had been cut down with halberds. 
Half of the poles and blades had shattered against her scales, but enough had struck true, and she had bled her life's blood unto the ashen ground. 
There lay the severed head of Izvathorn, who had been her lover for a summer. 
His eyes, once filled with a gleam so fickle and fierce, were now glazed and empty. 

The invaders had done the impossible. 
They had slain those who were immortal. 

% The \resphain{} had come from their world of perpetual darkness. 
% Swarming across the land in legions a hundred thousand strong they had made war upon \Nzessuacrithz{} people, the \dragons, and wrought destruction upon their world. 
% A hundred years they had fought, and for a hundred years the world of \Miith{} had known nothing but war. 

Thousands of her people had fallen; nay, tens of thousands. 
They were the mightiest and most splendid of all the creatures of \Miith{}. From the skies they had ruled the world, and none had dared challenge their supremacy. 
Now only few remained. 
Their kingdoms lay devastated. 

\tho{So much death and destruction.} 

% The \resphain{} had laid everything in ruins. 
Her people had fought back with all their ferocity, all their might, all their hatred. 
A hundred years they had fought, and for a hundred years the world of \Miith{} had known nothing but war. 
Each \dragon{} was worth ten \resphain{}, if not twenty, yet still they prevailed not. 
Now, after a century of war, both of their races were decimated. 

Mortal corpses also covered the field. 
There lay \hr{Scatha}{\scathae}, and \hr{Cregorr}{\cregorrs}, and some of those creatures that had fought for the \resphain. 
\hr{Human}{\Humans}. 
They resembled their \resphan{} masters, but smaller, paler and infinitely weaker. 
Pathetic things, those \humans. 
On a better day, \Cryocas{} might have pitied them. 
They had no place on a battlefield of immortals. 

% A sudden cloud of debris made her eyes itch, and she licked them to clear them. 
% Then, distracted, she found that she had to swerve to steer clear of a ruined tower that groaned as if it might collapse at any moment. 
% Her sudden turn brought a jab of pain from a wound in her right wing where she had been singed by lightning from a \resphan{} mage. 

% The pain became anger, as it would for any \dragon{}. 
% \tho{%
%   They will pay for this. 
%   \Miith{} is \emph{ours}!}

At the end of the war, terrible spells had been wrought. 
Cosmic forces had clashed. 
And the world had been reshaped. 
Vividly she recalled the dimensional gate to \hr{Erebos}{\Erebos}, that unholy laceration in the very flesh of the world that the \resphain{} had slashed open. 
Recalled the feeling when she stared with her mind's eye directly into that spiritual chasm, the grasping mouth of a ever-hungering, ever-consuming dark emptiness. 
Recalled how the winds from that bleak vortex had reached every corner of \Miith{}.
No matter where she had run, she had not been able to escape those cold spiritual winds, nor block out their whispered promises of eternal decay. 

That vortex had at last been sealed. 
But at what cost? 

Now the Shroud had fallen over \Miith{}. 
The world had become a prison. 
A hall of mirrors and illusions. 

Only death filled her eyes. 
And beyond the vision of her physical eyes there was only the cruel mists of nothingness. 
Once the minds of the wise had been free to wander the endless Realms. 
Now those Realms had been ripped asunder, severed from each other and from themselves. 
Now every thought touched a wound, and from each wound the Heart of \Miith{} bled with all the world's pain. 

The world had become a lie. 
A morbid lie draped over a truth even more morbid. 

To an immortal such as she, who had once held the universe at her fingertips, it was like having her eyes gouged out and her arms, legs and wings severed. 
Now she felt deaf and dumb. 
Cut off from the world. 

She had become an island. 

Isolated. 

Alone. 
% And now \Nzessuacrith{} was alone. 

\begin{comment}
\section{\Secherdamon}
\end{comment}

No... not wholly alone. 
There was another out here. 
Another like her, a mourner prowling the battlefield. 
Even though the numbing Shroud, she recognized the psychic and physical scent. 

\hr{Secherdamon}{\IrocasSecherdamon}. 

%     \Secherdamon{} whips his tail in anger. 
%     
%     Maybe clarify that \Secherdamon \hr{True Draconic signifies emotion}{speaks \TrueDraconic out of emotion}.

Spreading wide her vast silver-shining wings, \Cryocas{} rose into the air and soared high above the killing ground, until the fires and smoldering embers became but a thousand pinpricks of light underneath. 
She lifted her nose to the wind and found the direction of \ps{\Secherdamon}{} scent. 

She sought him out and found him circling a ruined, smoking tower. 
As she drew near she could feel the power radiating from him. 
\Secherdamon{} was of the \hr{Shae'eroth}{\shaeeroth}, the elder generation, and half again her size in both length and wingspan. 
Even now, though blackened by soot, his golden scales still gleamed like fire. 
But his whole aura had a new sheen to it. 
A new edge, hinting promises of anger and ferocity. 

He turned to her and transfixed her with his pearly white eyes. 

\ta{Betrayal,}
he whispered. 
\ta{We have been betrayed.} 
He turned his eyes away and gazed at the horizon. 
\ta{And now my brothers are lost to me.} 

\tho{Yes,} thought \Cryocas. 
\tho{\Secherdamon{} has lost much in this war.}

His eldest brother, \hr{Nexagglachel}{\Nexagglachel}, the greatest of them all, had fallen to the \ps{\resphain} treachery. 
They had consumed him and made of his legacy an abomination, an atrocity. 
His other brother, \hr{Ishnaruchaefir}{\QuessanthIshnaruchaefir}, was gone, having abandoned his race to their fate, just like he had abandoned \Nexagglachel{} to the \resphain. 

And now \IrocasSecherdamon{} was alone. 
And there was a new darkness in him, a darkness that shone through even the constricting Shroud. 
% Even constricted by the Shroud 
\Cryocas{} had only endured the scrutiny of those pearly eyes for a few heartbeats, but the gleam she had seen chilled her to the core. 
\Secherdamon{} had once been a carefree spirit, full of life. 
Now his eyes, his voice and his stance dripped with hatred, bled with bitterness, seethed with mania. 

\ta{\CryocasNzessuacrith,} said he, not turning to her. 
\ta{Be thou witness to this mine oath.}
And he raised his head to the sky and cried out words of power in the \maybehr{True Draconic}{True \Draconic} tongue: 

\ta{%
  Cursed be ye, \resphain, spawn of pestilence!
  By the \hr{XS}{\xzaishann} pantheon I swear this: 
  I will destroy you! 
  I shall wipe out your wretched kind, eradicate your vile disease and reclaim this world for my people!
  This I swear! 
  By the \xzaishannic{} blood that floweth in my veins, I, \IrocasSecherdamon, third-born son of \hr{Tiamat}{\Tiamat}, the mother and founder of the \hr{Dzraic'chenoss}{\draecchonosh} race, do lay this oath. 
  
  \RaemythKhivaashNexagglachel, my brother! 
  I shall exact payment for what they have done unto thee, for all they have taken from thee.
  I will avenge thee!
  
  And I shall take what I am owed. 
  I will conquer this world and make it mine own, 
  and I shall rule in the name of the \draconian{} race.}

He turned to the western horizon and raised a clawed hand, stained dark with blood and ash. 
\ta{And thou, \QuessanthIshnaruchaefir!}
He clenched his hand so that the claws drew blood. 
\ta{%
  Thou art my brother no more. 
  In the name of all our kind I renounce thee.}
Blood dripped from his paw, as if to seal a mystic pact. 
\ta{%
  A time of reckoning will come for thee, 
  and thy betrayal shall be answered.
  This I swear.}

And \Secherdamon{} spread wide his wings and roared, and the fury of the \xzaishanns{} was in his cry. 

\tho{And the world will hear.} 
\Cryocas{} felt that she knew this. 
\tho{%
  \Secherdamon, youngest son of \Tiamat, 
  has had ascendancy thrust upon him,
  and he has seized it. 
  When he cries, the world will hear.}










\begin{comment}
\section{\Ishnaruchaefir}
\end{comment}

\new
%     Rewrite the prologue with Ishnaruchaefir.
%     He bears a great and terrible evil, and he knows it.
%     He refuses to repent.
%     \ta{Even unto thee. Aye, even unto thee.}

Far away, soaring slowly above yet another wasteland,  \QuessanthIshnaruchaefir{} heard not his brother's curse. 
There was no need. 
He could guess \ps{\Secherdamon}{} thoughts well enough. 

\tho{%
  It is fulfilled. 
%   Was it right?
%   Was it justice?
%   We will never know. 
%   We will never know what might have been.
}

He reached out into the world with his feelings, and was thwarted. 
He grasped blindly and found only emptiness. 
Only a bleak wall of nothingness. 
The Shroud. 

\tho{%
  I have done what I came to do.
  A new world has dawned. 
  A colder world. 
  A world of blindness. 
  A world of deception. 

  They name me Destroyer, and Betrayer. 
  They will curse me for a thousand years. 
  Ten thousand. 
  Let them. 
  It is true. 
  I have shattered the world, laid waste to the Realms.}
He beheld the ashen wasteland that stretched before him. 
\tho{%
  I caused this. 
  \Miith{} bleeds from a million wounds, and the claw that cut her was mine. 
  But I will offer no penance and ask no forgiveness. 
  I have done what I set out to do. 
  If that makes me the Destroyer and the Betrayer, then so be it. 
  I will repent nothing. 
  
  \Secherdamon{}. 
  \Nzessuacrith{}. 
  You will see it as treason.
  So curse me. 
  Your pain is nothing. 
  My betrayal of you pales to naught next to my ultimate betrayal.}

He raised the great glaive that was strapped to his forearm. 
Gently he ran a claw down the length of one of its jagged blades of red metal. 
A droplet of scarlet blood dripped seething from the tip. 
Not his blood. 
Not drawn from his flesh, but wept from the blade itself. 

Seeing this, \ps{\Ishnaruchaefir}{} reptillian eyes clouded, and he felt a stabbing pain in his soul, like needles through his two hearts. 

\tho{%
  I carry it with me. 
  A testament to my sacrifice. 
  A testament to the price I have paid. 
  The price which the world has paid. 
  The price that remains yet to be paid.}

His thoughts returned to the matter of his brother, and of \Nzessuacrith. 
\tho{%
  The ties that I have severed will not mend. 
  The wounds that I have inflicted will not heal. 
  I ask not for acceptance. 
  This new world is not one of forgiveness. 
  Nor one of healing. 
  Nor one of love. 
  
  It is a cruel world. 
  A world of strife. 
  A world of predators and prey. 
  
  It is the world of the Lie Sublime.}










\begin{comment}
\section{Ramiel}
\end{comment}
\begin{comment}
\new
Ramiel surveys the destruction. 
He sees the dead \dragons{} and the dead \resphain. 

They have not won a war. 
All they have won is a foothold, and the price has been steep. 

Then he talks to \Azraid. 

He feels resentment against \Azraid. 
He resents his \KiriathSepher{} arrogance and gayness. 
This comes as a surprise to him. 
Until recently he respected \Azraid. 
Now he sees him as a stranger, a potential enemy. 

He realizes that they have paid a higher price than just the deaths of tens of thousands of \resphain. (The deaths of millions upon millions of mortals does not even enter his mind.) 
They have lost their coherence as a race. 
The venom of distrust has entered them. 
They know that there was treachery involved in the Shrouding; that some of their \resphan{} brethren have consorted with \Ishnaruchaefir{} and his ilk. 
They grow apart. 
Cracks appear. 
Kin turns against kin. 
He predicts that their people will soon come to bloody kinstrife. 
Again. 

Perhaps it is their destiny. 
Perhaps it is inherent in the nature they have now embraced. 

Perhaps the venom of distrust is a natural consequence of their actions. 
Their abandonment of \Merkyrah. 
Their heresy. 
Their descent into evil, as some would call it. 

Perhaps they have lost something. 
But so be it. 
He would not go back to \Merkyrah. 
\end{comment}















\begin{comment}
\chapter{Silenced}
\end{comment}

% \bookchapter{Silenced}
\stamp{\dateCatrianDies}{\hs{Bendaire}, \hr{Marcil}{\Marcil}}
%\datestamp{Carz}{21st}{\Hoshied}
%
\tho{%
  It had no face! 
  Great gods, the creature had no face! 
  Take it away! 
  Chaos preserve me, take the vision away from me!}

Catrian ran, trying to wipe from her memory the image of the horrible creature she had seen. Her dress and shoes were not made for running, but she pushed on. 
\tho{I must hurry. I must tell my masters. The enemy is here!} 

She felt a sudden blow. 

She was aware of the ground rushing up to meet her. 

\ta{Hey! Watch where you are going!} The voice was that of an angry man. 

She lay prone on the ground next to him. Still in shock, Catrian had been running in a haze and had not seen the man before colliding with him. 

Hastily she climbed to her feet and set off again. 
\ta{Crazy woman! And rude besides...} 
Catrian ran on, sparing the man neither word nor glance, barely even an ear. 

\tho{Gods, the horror!} 
She could not forget the vision of the thing. Many years now had she served her masters, and many and strange were the sights she had seen: Forbidden magic, rituals, weird creatures, even a \dragon{} on one occasion. She knew of the enemy, but she had never before actually seen one. 

Until today. 

It occurred to her that perhaps she had never truly believed that they existed. She \emph{knew} they existed, that they had walked on \Miith{} in the past and that she and the secret society worked to oppose them, that the brotherhood had been created to fight them if they should return, but never had she actually believed that they would return in her lifetime. And least of all had she expected to meet one. 

Until today. 

As she saw the man in the inn she had felt something strange about him, so she had fingered the rune-carved talisman she carried and whispered the spell-words to grant her the second sight. 
(Catrian was not a true mage; she only knew the \hs{orisons} to activate a few enchanted items.) 
And then she had seen the man's true form: A thin, hunched humanoid with bluish-black skin and four strange-looking fingers on each hand. But the most terrible aspect of the creature was its face, for it had none; its head was blank, smooth like an egg, the only distinguishing features a pair of ear-like appendages at the top. 

Seeing the creature stunned Catrian for several moments. She knew what is was: One of the sinister ones, the enemies of \Miith{}, whom she was sworn to combat. But her mind struggled against the revelation. And then the thing turned to her! Its blank, eyeless face did not move, but she could feel its malefic gaze upon her. She felt the thing reach out through the Beyond with its mystic tendrils. She turned and ran. 

She knew what she had to do. 
\tho{I must reach my masters. I must tell them of this.} 
She ran in a panic, headed for the house of \Mister{} Dorian, her superior in the brotherhood. She was not certain the thing was following her, but surely it must be. 

Meaning to cut through an alley, Catrian turned at a corner, then halted. In the alley before her stood a woman and several men, all staring directly at her. 
The woman was in her middle years, with the look of a Redcor: tall and blonde, and clad in a robe of brown and yellow. 
The men were all armed and mean-looking. 

The woman raised her hand in Catrian's direction and spoke something that she could not hear. The men made to advance on her.

Catrian knew immediately that these were not mere ruffians. 
\tho{I have been discovered! The sinister ones' lackeys have come for me.} 
She could not look away from the woman, whose eyes gave an impression of a cold... \emph{evil}. 
\tho{They have come for me. I am going to die.}

Then, as Catrian stood and watched in fear, the evil-eyed woman seemed to change shape before her eyes. 
Her skin faded to a bluish black, her posture became hunched and her face became a smooth mask, featureless safe for twin ear-like protrusions. 
\tho{Another one! Another one of the things... the enemy!} 
The creature reached out for her, and its mystic hands seemed to fill her entire field of vision. 

Catrian turned and ran from the alley. 

So great was her terror that for several moments she knew nothing save that she was fleeing. Then she realized that she did not recognize her surroundings. This confounded and frightened her, for she had lived in the city all her life and knew this area very well.
%, so that it should be impossible for her to lose her way.
Nonetheless, her surroundings were strange, alien. The ground was no longer brown dirt but gray dust. She looked up and saw that the entire world had changed around her. There were buildings, but the wooden planks looked unnaturally dry and desiccated, and stones looked porous, ready to crumble to dust. The street seemed more narrow, more cramped, and the taller buildings loomed menacingly, as if poised to crash down upon her and drag her down in the deep like the claws or teeth of some hungry, undead giant. 

Still running, not daring to slow down, she studied her surroundings. There to her left she recognized a house: Anton the baker's shop. It was discoloured and sickening to look at, but it had retained its familiar shape. And there to the right was the house of Morris Neil's son with its characteristic round windows. 
She realized that she must still somehow be in Bendaire. The houses and streets were the same as those she knew, but warped somehow. 

%Something caught Catrian's foot, and she nearly fell on her face. Looking down, she cried out loud in revulsion. She saw now that the ground was not uniform, gray dust as it had first seemed. 

There were people in the streets also, but they too were warped. On many, the skin was unnaturally pale, sickly, like that of corpses. She noticed that the people were in different stages of decay: Some still had colour and looked mostly alive, but others were deathly white and moved sluggishly, slumped over, like the walking dead. On some of the people she could see what looked like chains attached to their necks or arms, trailing off into nothingness. 

She looked up and saw that the sky had been twisted as well: Instead of blue it was a pale gray, and the Sun was not yellow but ghastly white, like the Pale Moon, and its rays were cold, sharp and cruel, mercilessly revealing and emphasizing all the ugliness and the stagnation and the decay of this nightmare world. 

She ran past a wagon in the street and was startled when a man walked out behind the wagon and almost bumped into her. The man recoiled and spoke something, but she could not hear him over her own scream. 

The man had no face! 

His skin was pale, almost white, unlike the black of the sinister ones, but his face was a blank egg like one of theirs! 

Still screaming, Catrian ran away from the man. Across the street she ran, almost colliding with an old woman. Catrian glanced at her and shrieked again. 

She too was faceless! 

On she ran. A beggar looked up at her from the gutter. He had no mouth! And there was a young girl in a red dress, but she had no eyes! As Catrian glanced at the people around her, she was dismayed to find that only a few had normal faces. Some lacked eyes, or ears, or a mouth, and some were entirely faceless.

%She glanced at the people in the street and was horrified to see another faceless one pass her by. And another! And more! In fact, only a few had normal faces. Some lacked eyes, or ears, or a mouth, and some were entirely faceless.
%Of the rest, not all were entirely faceless; some merely lacked eyes, or ears, or a mouth. 

Crying in desperation now, tears running down her face, Catrian ducked into an alley to escape the horrible throng of faceless people. Then she began to hear strange noises from behind her; croaking, gargling, yelping noises. She ran on through the dark alley, but the noises came closer, ever closer. 

Suddenly there appeared before her a figure. It was a woman clad in a black-and-blue dress. Her face was blank, and about her was an aura of malevolence, almost like shards of dark ice, a blizzard encircling her. It seemed to strike Catrian with physical force. She recoiled, turned about and made to run. 

But what she saw caused her to freeze in place. 

They were like huge rats, as large as dogs, and they walked or hopped on long, strong legs. Their skin was brown and their sparse fur was a dark yellow, like patches of mold on their bodies. They had long jaws filled with sharp teeth, and their great, bulging eyes were pale and dead. Six or seven in number, they were the creatures who had made the gargling noises she had heard. They had caught up to her. 

%They encircled her. 

All thought of informing her masters was gone. Catrian thought only of how to escape with her life. 
\ta{No,} she whimpered. 
\ta{No! Get away from me!} 

The largest of the rat-things crept closer. It opened its mouth and licked its lips with a tongue that was pinkish-gray, parched and dry. 

\ta{Get away!} She wept. 

The thing jumped. She screamed as the thing sunk its teeth into her belly. The pain was terrible, unnatural, as if the thing tore not at her flesh but at her soul. She fought feebly to fend it off with her arms, but then felt a jolt of pain from her shin, and another from her buttocks, and another from her shoulder. She fell to the ground as the entire pack of rat-beasts swarmed over her. 

Some yards away, the faceless woman watched motionless as Catrian, screaming and weeping, was ripped and torn asunder by the hideous rat-things.
% fell to the ground, the entire pack of rat-beasts swarming over her. 
Then she turned away and left the alley by a door into one of the shady houses. 

Her work was done. 

%Catrian died in pain, screaming and weeping, ripped and torn asunder by the hideous rat-things. 



\new
Gaston saw the woman run into the alley, wild-eyed and shouting. He knew her. 
\tho{Gerald the weaver's wife. What is her name?} 
She was middle-aged, brown-haired and wearing a green-and-brown dress of wool. 
\tho{She is the daughter of Morgan the carpenter. What is her name?} 
At first he intended to simply move on, to let others deal with the matter, but as the woman's screams grew even wilder in the distance, he felt that maybe he should investigate. 

\tho{Catrian, that's it. That is her name.}

He walked the way she had gone. 
\emph{Poor woman.} 
The weaver's wife had always been somewhat strange, Gaston thought, and now it seemed she had gone mad. 

Cautiously he approached the alley. It was the middle of the day, of course, but even so, dark alleys could be dangerous. Consorting with the mad had its perils, too. 

He turned around the corner and into the alley. At first he could see nothing, for the buildings were tall and cut off the sunlight. But as he walked a few yards into the alley he saw her. She was lying motionless on the ground. He approached her. 
\ta{\Mrs{} Catrian!} he called. 

No response. 

He walked up to her to take a closer look, then pulled back in shock from her face. It was contorted in a morbid grimace of pain and terror, glassy eyes staring blindly into space. She was dead. Gaston thought about touching her to be sure, but the idea of touching the dead, mad woman disgusted him. 
\emph{There is no need. She is dead, that is plain to see.} 

He examined her. There were no wounds that he could see. Her dress was unharmed and there was no blood. 
\emph{Probably died of madness,} he thought. 
Madness was sometimes fatal, he knew. He felt sorry for her. 
\emph{Strange to think that she was evil.} 
After all, it was well-known that only wicked people went mad. Madmen were those who had abandoned the Light, sold their souls to dark powers or simply turned away from the Light. Fools and sinners who vainly believed that they could live without the Light. For these sinners, eventually their wickedness caught up with them and they went insane, deprived of the blessing of the Light. It was known. 

He turned from the body. It was not his worry, after all. He would inform the guards or the church, and the matter would be dealt with. Gaston walked away. 

Not his worry. 
