
\bookchapter{\Achsah{} and \Teshrial}





Make sure to make the atmosphere in this chapter as dark as possible. 
Teshrial-tachi drink human blood from chalices, and eat Human and Scatha flesh. 
They have huge, deformed ogre servants and monsters. 
And there is dark sorcery all over the place. 

Make clear that \maybehr{Resphain love conflict}{\resphain love conflict}.
\Teshrial sort of likes having been killed. 
He enjoys hating \Ishnaruchaefir. 

When \Teshrial revives, make him genuinely distressed and fearful of this great evil.
\Teshrial should not just be angry and arrogant.
    
Mention that the \resphain \maybehr{Resphain resent Mirage Asylum}{resent how \Ishnaruchaefir hides in his Mirage Asylum}. 

Re-read the \quo{\Achsah and \Teshrial} section in the big notes document.







\begin{comment}
\subsection{Training}
\end{comment}

Remember to have plenty of \maybehr{Resphan wing body language}{wing body language} from the \resphain. 

\Teshrial{} has recently come back to life. 
It has taken him several months, after his body was disintegrated by \Rystessakhin. 
Now he is recuperating, training to get back to full strength. 

First we have \Teshrial{} in his citadel in \Nyx. 
He trains with weapons. 
He is sparring with \Menessiaraid. 
He flies and wields a senaan and a ghijed. 
He cuts, shoots and dodges. 
He goes through the forms and patterns that he has been taught. 
Fighting airborne requires lots of skill and discipline. 
Especially with a long senaan. 
You can easily lop off your own wings if you don't know what you are doing. 

But inside he scolds himself. 
He should not just be practicing forms. 
His technique was perfect last time, and it availed him nothing. 
He needs to do something new. 
He needs a plan. 
The training is not real training. 
It's more like off-stressing. 
He likes practicing forms. 
It clears his mind, lets him think. 

He misses Turishah, which he lost in the fight. 
Now he is fighting with a no-name spare blade. 
It is a sucky blade in comparison. 
He needs to get himself a new senaan. 
A powerful one. 
He will need it if he is to face the Destroyer again. 

\begin{comment}
\subsection{Worrying}
\end{comment}

Menessiaraid is worried. 
Teshrial seems tense and stressed. 
He asks him what is wrong. 
"Are you still depressed because you lost that fight? 
 Do you feel you've lost face as a Resphan weapon master?
 For fuck's sake, Teshrial.
 You were up against Quessanth motherfucking Ishnaruchaefir. 
 The Destroyer. 
 One of the most powerful Dragons alive. 
 He has barely ever been defeated, and certainly never in single combat by a Resphan. 
 Of course you couldn't defeat him. 
 Don't beat yourself up over it."

"Yes. I know. 
 But still.
 I made mistakes. 
 The fight showed me that my technique was not flawless. 
 I am not as good as I could be. 
 As I should be. 
 I need to become stronger."

Teshrial thinks back to the fight. 
It was humiliating.
And more than humiliating. 
He was not just defeated. 
He was killed. 
He has not been killed in over three hundred years. 
He has forgotten how painful it was. 
And to top it off, his body was completely destroyed, forcing him to regrow it from scratch. 
It took all the energy of two score Communia before he was back to full strength. 
Such a waste. 
It makes him angry to think about it. 
That should not have happened. 
Damn you, Destroyer. 

And damn me for having been so stupid and overconfident. 
Really, what was I thinking?

But he was wiser now. 
He would not make the same mistakes again. 

Teshrial, in contrast, is a Resphan weapon master. 
He has won championships in several disciplines of the martial arts; melee, firearms and magic alike. 
He is a scion of all the sophistication of Ciriath-Sepher. 
He will put this to use. 

After all, he had not really expected to win that initial fight. 
It had been... reconnaisance. 
Yes. 
That was what it was. 
He wanted to study Ishnaruchaefir, test him, see how he fought, so that he would be better prepared to face him for real. 
It was just warm-up. 
Besides, he was in no real danger at the time. 
He had made sure of that. 
True, the Destroyer IS a mortal danger, and there are many reports of his having slain Resphain in combat and permanently destroyed them. 
But Teshrial was deep in the Shroud. 
In such a place, soul-destroying magic is repressed and weakened. 
This means that while his body might die, his immortal soul would almost certainly escape. 
In such a place, he did not think there was any chance that even Ishnaruchaefir might destroy his soul. 

And it had been successful reconnaisance. 
He has learned much. 
For all his power and ferocity, the Destroyer is a barbarian, a wild beast. 
His only tactic was to charge mindlessly on, not even caring if he was hit. 
He had not understood this before, but now he did, and he could plan for it. 
He will show them all. 
He can do it. 
Brains will triumph over brawn. 
Technique will triumph over brute force. 
You will see, Destroyer. 
You will see. 

Then Achsah comes in. 
She walks in through a door. 
She cannot fly naturally, but she could use magic to do it. 
Still, for some reason, she always walks, rarely flies. 
Almost as if she celebrates the fact that she is an ashenblood. 

The thought is icky to Teshrial. 
He imagines what it would be like to be an ashenblood.
Immortal like a true Resphan, but with thin, mortal blood in his veins. 
Feeble, pale and un-beautiful (Danish: "uskøn"). 
And worst of all, four-limbed. 
Wingless. 
Cursed to walk on the dusty ground like a human. 
He shuddered at the thought. 

"Well, Menessiaraid, I need to go down and hear my subordinate's report."

"Fair enough. Then I will be about other business. Later, dude."

Teshrial lands and sits down, waiting for Achsah to approach. 
She does. 

Teshrial: "Well?"









\begin{comment}
\subsection{Achsah}
\end{comment}
\new
Achsah walks away, having given her report and discussed plans with Teshrial. 
She is worried. 
Teshrial is being inattentive. 
It's like he barely cares about \Malcur and the Ghobaleth anymore. 
Well, he does his job, but it feels like it has become a second priority to him. 
He tends to drift out of the conversation and stare into space. 

Muttering to himself. 
About the Destroyer.
About what he will do next time he faces him. 

"Next time". 
Achsah does not like the sound of that. 
It sounds dangerous. 
Reckless.
Like an obsession. 

After the duel, Achsah had dutifully passed on the Destroyer's message as she had promised. 
But she had not thought Teshrial would accept the challenge. 
She had thought he would be smart enough to know when he was out of his league. 
That one duel against the Destroyer would be enough for anyone. 

It had certainly been enough for her. 
She had encountered Ishnaruchaefir on the battlefield once, back during the Incursion. 
He had cut a swathe through their ranks, wreaking havoc and slaying Resphain left and right. 
She had not stood and fought. 
She had fled from his path before she got inside his range. 
And she had not looked back. 

She had been young and inexperienced back then. 
Weak. 
She was far more skilled now. 
But she thinks she still would do the same. 
When the Destroyer called her name after he had killed Teshrial, she had been afraid. 
She had nearly pissed herself. 
She was happy and grateful she let her go.
No, she was certainly not going to challenge Ishnaruchaefir. 
She had too much sense of self-preservation for that. 

Not so Teshrial. 
Oh, no. 
Teshrial accepted.
And it seemed these days he could not think about anything else. 
He was always training, always planning, always preparing for "next time". 

Teshrial looks at her.
He sees through her. 
"You do not believe me, do you?
 You think it is madness. 
 You think I will never be a match for Ishnaruchaefir. 
 Such a narrow-minded way of thinking. 
 We Resphain were made to rise above ourselves. 
 To strive towards perfection and achieve the impossible."

She still doesn't believe. 
She thinks he will fail. 
And she fears he will fail so spectacularly that Ishnaruchaefir will destroy his immortal soul. 

Bah.
It's no more than he deserves. 
For all his self-righteousness and arrogance and megalomania. 
Just look at him. 
Look at that smug face of his. 
Looking down on me. 
He is no doubt concocting an elaborate lecture about how she, a stupid ashenblood, would not understand the grand aspirations of true Resphain. 
How she could not possibly comprehend the great heights he was reaching for, because she stood so far beneath him. 

You don't know shit, Teshrial.
She tries not to look petulant. 
She almost wanted to shout up in his face. 
Stop treating me like something inferior. 
I was born like Thanatzil, our founder. 
In blood. 
The same blood of life which we otherwise hail as something great and sacred. 
But none of those vaunted "purebloods" respect that. 

Teshrial is scum. 
He deserves to fail. 
He deserves to be destroyed. 

"Hm. 
 Think what you will."
He turns away. 

No insult came. 
Hm. 
There, I went and got myself all fired up over nothing. 
Perhaps I am just assuming the worst about him. 
Perhaps I shouldn't. 

She almost feels bad about how she just now wished for Teshrial's destruction. 

She goes away worrying about him.
What if he fails?

Gah! 
Achsah. 
Stop worrying about Teshrial. 
You have more important things to consider. 
Like \Malcur. 
With Charcoal gone, that girl Needle is in charge. 

Needle is a good tool. 
Needle is very handy. 
The Sentinels know about Charcoal, but they don't know about her. 
She is all close to \Tiroco{} and can spy on her and have her shadowed, and the Sentinels don't know it. 

Achsah kind of likes Needle. 
She recognizes something of herself in Needle. 
The girl is... damaged. 
Imperfect. 
Just like Achsah herself is imperfect, being \bezed-born. 
She feels a certain kinship with the human. 
She promises herself to watch over Needle and make sure she comes to no harm. 









