
\bookchapter{Rian and \Tiroco}
\begin{comment}
  \section{Moro spies on \Tiroco}
\end{comment}

\Tiroco is out in the city, walking with only a few guards. 
Moro \Cornel is there, watching \Tiroco from a distance.
She suspects that there is something wrong with \Tiroco. 
So now she is spying on her own \rinyuth. 

Nothing much is happening today. 
\Tiroco is not even in disguise, after all. 
It is probably just a regular walk. 
Perhaps it was a waste of Moro's time. 
But you never know.
    
In all the Rian chapters, whenever it is appropriate, have references to the \maybehr{Myths of vanquished monsters}{myths of Iquinian heroes vanquishing inhuman Elder Races and monsters}. 

Make Rian more religious.
Make sure he prays in every chapter and scene that he is in.
Make clear how grateful to the Light he is for how he has been freed from his life of crime and allowed to make a new, honest life for himself.





\begin{comment}
  \section{Rian thinks}
\end{comment}
\new
Rian is unhappy.
He is at his wit's end. 
The one den of villains he had his eyes on has now been raided and abandoned. 
He has not been able to find out anything new. 

He talked to those guards a while back, but they chased him away and refused to listen to him.
Since then he has also tried to talk to some priests, but with no better results. 
They accuse him of \quo{fear-mongering} and of being a threat to the public peace and piety. 

What nonsense is that? 
He is trying to help everyone!
There are monsters and evil wizards in the city, killing people, and no one listens to him. 

He is despairing. 
He has tried everything he can think of, but he is getting nowhere. 

Besides, as Rian's hunt goes on, he becomes hungry and his health suffers.
His life is hard enough to begin with, and with his hunt for Neina costs him much valuable time and energy, leaving him hungry and tired. 

But then he heard the \rinyuth was out in the city today. 
And he got an idea. 

\tho{\Rinyuth[\Tiroco]!
  She is good. 
  She has always been a friend of the people.
  She used to distribute alms to the poor.
  If I could get to talk to her and warn her, I'm sure she would understand.
  But how do I do that?
  I'm nobody.
  I can't exactly request an audience with the \rinyuth.
  
  But I am an experienced thief. 
  And now an experienced spy as well.
  If there is anything I know, it's how to sneak up on people.
  I just need to get past her guards and talk to her.
  When she hears I have urgent news about the city, I'm sure she will hear me out.
  Yes.
  That's what I'll do.
  Get past the guards and talk to the \rinyuth.
  That's a plan.}
  
He notices that \Tiroco is with a man who leads a naked \sheomir slave girl on a leash.
Rian finds himself resenting and envying the \sheomir. 
She is a filthy \demihuman\dash look at that tail!
And yet she lives in a palace. 
Look how well-fed she looks, how fine her skin is. 
She has luxuries that he can only dream of. 
He is a true Man of the Light.
He has the blood of Vaimons in his veins.
And he is a free man, not a slave.
And yet this half-animal girl leads a better life than he does. 
It is unfair. 

It is those stupid \scathae's fault. 
Back in the days when the world was ruled by \humans, this injustice would not have happened, with half-animal slaves being elevated above free Men of Light. 
Back in the \VaimonCaliphate. 
Those were the days. 






\begin{comment}
  \section{Needle}
\end{comment}
\new 
Needle walks with \Tiroco. 
With \Tiroco is some \human big shot, some important minister or big merchant boss or noble. 
The \human is a somewhat fat, bearded man in his fifties.
He has a slave with him. 
It is a young \sheomir girl of less than eighteen. 
She is beautiful. 
She has a furry tail that marks her as less than a true \human, but she is still beautiful. 
For a brief second, Needle envies her for her beauty and youth.
Needle was never anywhere near this beautiful, even though she is a true woman and this other one is merely a \demihuman. 

Then Needle thinks again. 
The girl is virtually naked, clad only in a bikini. 
Her owner holds her on a leash by the neck. 
He parades his property like an animal. 
It is degrading. 

Besides, the girl is clearly a sex slave. 
Needle would not want to serve as a pleasure toy for this digusting old man. 
And as Needle looks closer, she becomes even more apalled. 
The young girl bears marks of whips on her body. 
And trails of tears on her face. 
Judging by the look of complete submission on the girl's face, Needle guesses that this slave is neither disobedient nor troublesome. 
Most likely, her owner whips her because he enjoys it. 
What a piece of shit. 

Needle herself is just as much a slave as the \sheomir girl. 
She certainly has no love for \Tiroco, but at least the \rinyuth lets her slaves walk clothed and unchained, and she only rarely has them punished. 
Needle would not want to serve this man. 

Sometimes \humans can be worse than \scathae. 
This is natural, she supposes.
\Scathae are little more than creeping lizards that have learned to walk on two legs. 
\Humans had true souls.
This enabled them to rise to much greater heights than the lizards, but also to sink deeper into evil. 





\begin{comment}
  \section{Rian talks to \Tiroco}
\end{comment}
\new 
There are a half dozen guards or so. 
This is not the slums, after all.
This is the nice part of the city. 
He had to sneak a lot just to get this far. 

\tho{Dear \sephiroth, let this work. 
  Please let this work.}

There is a mob around the \rinyuth, but Rian knows how to navigate mobs. 

When the \ps{\rinyuth} folks are at a strategically good location for him, he causes a bit of confusion in the mob by saying: \ta{Hey, look over there!}
Then he throws a few stones to divert the guards' attention. 
Then he slips through the mob and, using on some convenient props standing nearby, he leaps over the mob and down near the \rinyuth. 

Rian:
\ta{My lady \rinyuth[\Tiroco]!}

\Tiroco:
\ta{Eeek! What is this? Who is this man?}

Rian:
\ta{Please, my lady, listen to me!
  There is something evil going on in \Malcur.
  Please, you must believe me!
  There are evil wizards, working black magic and killing people!}

The guards are back in action. 
They try to grab Rian. 
He tries to dodge them. 
He notices \ps{\Tiroco} eyes are widening in shock.

\tho{She believes me! She understands the danger! I was right!}

So he keeps talking.

Rian:
\ta{%
  The guards won't believe me, but I swear to you, it's true!
  I saw it with my own eyes!
  Only you can save us, \rinyuth[\Tiroco]!}

\Tiroco:
\ta{No\prikker no\prikker no\prikker
  Take him away from away! Take him away!}

Rian:
\ta{My lady! You must believe me!
  There are evil wizards in your city!
  Right under everyone's noses!}

The guards have managed to grab Rian and hold him tight. 

\Tiroco:
\ta{Be quiet!
  Make him shut up! Make him shut up!}

A guard punches Rian hard in the stomach. 
He has to gasp for air. 

Then Rian notices Needle standing behind \Tiroco.
He gasps.
\tho{That's her! 
  That's the woman I saw back at that raid.
  She's one of them. 
  She's in league with some of those evil people.}

\Tiroco:
\ta{%
  He's a madman.
  A disturber of the peace.
  He's just talking nonsense.
  Don't anyone listen to him!
  Take him away! 
  Throw him in the dungeon! 
  I don't ever want to see him again!}

Rian:
\ta{What? Wait! No! Oof\prikker}
Rian trails off as he gets punched hard again. 

Guard: 
\ta{Shut up, lowlife.}
They drag him away.

\tho{What was that evil woman doing there?
  Is the \rinyuth in league with them? 
  No!
  That can't be.
  She can't be in league with the evil wizards that are corrupting her own city.
  That doesn't make sense.
  What is going on here?

  This isn't what was supposed to happen!
  Why won't anyone listen to me?}





\begin{comment}
  \section{Moro thinks}
\end{comment}
\new
Moro is there. 
She studies Rian.
But she has hidden her face behind a different illusion than last time he saw her, so he does not recognize her. 
But she recognizes him.
She can tell by looking at him that he has become unsettled and half-insane and sensitive. 
He has begun to see more and more through the Shroud. 
He is haunted by monsters from the Beyond. 

Moro picks up on this. 
It is one of the reasons she decides to take him under her wing. 
He is more sensitive than she and can see some things that she cannot. 

Besides, he has shown himself resourceful and sneaky and brave. 
She could use his help. 
And he is one of the few people who know and acknowledge that there is a problem and want to do something about it. 





\begin{comment}
  \section{Needle thinks}
\end{comment}
\new
Needle begins to suspect that \Tiroco{} knows more than she lets on, so she begins spying on her mistress. 

Needle has been there the whole time. 
She is disturbed by this guy who seems to know about her doings, and/or the doings of the Sentinels. 
Her minions told her there was a \human, possibly a boy like this, who was at the raid site and escaped. 
Who is he?
Is he a Sentinel? 
If so, why is he blabbering? 
Is he a coward who ran away from his own masters?
Is he a spy, a part of some elaborate ploy, maybe an attempt to smoke out the Cabalists?
Or is he just some nobody who has seen too much. 
At any rate, Needle resolves to get rid of him. 
She will send her people into the dungeon to get him killed as soon as possible. 

She also suspects \Tiroco. 
Her reaction to the boy's ramblings was suspicious. 
Maybe she suspects something. 
That is not good. 
Needle will need to spy on \Tiroco some more. 









