% \bookchapter{The Power of \EreshKal}
\bookchapter{The Cannonade}

% \begin{comment}
%   \section{Pelidorian sally}
% \end{comment}

\stamp
  {\datePelidorianSally}
  {Inside the \Forclin city wall}

\begin{comment}
  \subsection{Rungeran cannonade}
\end{comment}

Yet another cannonball crashed into the wall. 

\tho{This cannot go on,} thought Sethgal. 

The cannonade had gone on for a whole day now. 
Apparently the Rungeran army possessed one exceptionally powerful cannon, larger than the others and wrought with ancient sorcery. 
Augmented further by the Rungeran \ishrah's own spells, this gun could fire farther than any other cannon, and with great force, allowing them to bombard the walls from afar while the defenders were powerless to reach them. 
Morgan seemed to have only such monster-cannon\dash and Sethgal praised the One Light for that\dash but one was bad enough. 
The thing had already punched several small holes in the otherwise so powerful city wall, and Sethgal knew that sooner or later the barrage would bring down enough of the wall for the Rungeran forces to pour through. 

They had to take out that cannon. 

The Pelidorian \ishrah had tried to do something, but with no luck. 
Most offensive magic could never match the range of artillery to begin with, and Lord Curwen had explained to him that the Rungeran \ishrah were protecting themselves and their cannon with a powerful ward. 
At this range there was nothing the mages could do. 

A sally was now their best option. 
Luckily Sethgal was in possession of a large cavalry that, until now, had just been sitting on their rear ends and eating supplies. 
It was high time for them to do some good. 

% The Rungerans did not have nearly enough forces to encircle the entire city, so instead they had camped down in a crescent outside the northeastern wall. 
% They had tried to send scouts circling the rest of \Forclin, but Sethgal was having none of that, so he had sent out his fast cavalry in swift sallies to destroy these scouts. 
% The result was that the city's outskirts were still contested. 

Sethgal and his officers had planned a two-pronged attack. 
At nightfall a large force of heavy cavalry led by \rah[\Theal] \Kintaer would surge out and come up from the south-west to attack the Rungeran lines. 
This attack was a diversion. 
When this force had engaged the Rungerans, a smaller force led by \rah[\Dornaer] Pelidor would ride out from the northern gate to strike the Rungerans from the west. 
This second force was composed of Sethgal's strongest fast cavalry and would attempt to penetrate the Rungeran defenses and reach the core of their camp, with the twofold purpose of disabling Morgan's main cannon and killing his mages. 
% Meanwhile, an even smaller strike force containing two mages would sneak out under cover of night and hidden with 

Another thud sounded behind him.
Another cannonball had struck. 
Sethgal cursed, picturing the grinning, bearded face of Morgan Runger. 

\tho{By the \sephiroth, I will deny you, Morgan.
  You may have your weapons and your black magic, but the One Light is on our side.
  
  The days of \human overlordship over \Ezmith is gone, and they will not return.
  Pelidor will not fall.
  Not to the likes of you.}




\begin{comment}
  \subsection{Kintaer rides out}
\end{comment}
\placestamp{\Forclin city wall, near the eastern gate}
At last the preparations, prayers and blessings were complete, and at dusk Sethgal watched the larger strike force under \rah[\Theal] \Kintaer ride out through the eastern gate. 
Hundreds of \relcs, \grulcans and \murocs marched out in massive lines to face the enemy. 

The Rungerans wasted no time but immediately began turning their artillery towards the Pelidorian cavalry, hoping to take out some of the attackers before they could close in. 
Only the main cannon remained where it was and kept firing against the walls. 
Meanwhile the Rungeran cavalry and infantry formed ranks to protect their army's core.

A rain of gunfire met the Pelidorian cavalry as they rode.
It ripped through their ranks and felled several, but they rode on undeterred. 
Then the cannonballs began to fall. 
They cut swathes through the Pelidorians, smashing even the most heavily \armoured riders and beasts into bloody wrecks, but still the riders rode on. 

The gap closed. 

\Kintaer's spearhead was a hard core of \relc-mounted knights, resplendent in their full \armour. 
Even from the walls, Sethgal could see the One Light enshroud the knights as they called upon its strength before they charged. 
Wreathed in the power of \iquin and shining like a beacon in the dusk they smashed through the Rungeran lines.
Against such a massive charge of knights the infantry lines could not hope to stand.
The Rungerans were broken and crushed under the mounts' feet, and Sethgal imagined their terror when they realized that their corrupted nation was under attack by the very wrath of the One Light itself. 

The knights trampled many rows of enemies and felled uncounted Rungerans, but they could not go on forever.
Some knights fell to the enemy's pikes, for there were well-trained soldiers among the Rungeran infantry, and though many of their fellows fell, still their rear lines held. 
Soon enough the knights had used up their momentum and became bogged down by the massing infantry. 

\tho{Hold together, \Kintaer,} Sethgal prayed.
\tho{Keep the Rungerans occupied.}

By now the Pelidorian advance had been effectively halted.
Bullets still rained down on their centre, and worse, the Rungerans were moving around to encircle them. 

\tho{Do not let them, \Kintaer.
  Hold your flanks free.
  Sweep them away with your \murocs. 
  You must be able to disentangle your forces and retreat.
  We cannot afford to lose you.}

But \Kintaer's forces had done their part. 
They were holding down thousands of Rungeran soldiers and keeping them occupied. 
Meanwhile, the second phase of Sethgal's plan was in motion. 



\begin{comment}
  \subsection{Dornaer rides out}
\end{comment}
\placestamp{Northern gate, \Forclin}
Riding out of the northern gate, \Rah[\Dornaer] Pelidor still heard the clerics' words in her mind:
\hypota{%
  May the One Light shine bright upon you, and may \Isphet and the Outer Darkness shy away from you.}
Right now, though, she was hoping just as much for the protection of the darkness. 
She was taking her forces northeast so as to come down and strike the Rungerans from the northwest where their centre should be less defended. 

\tho{%
%   The outriders earlier have done a good job of clearing the area of their scouts.
  We must get as close to Morgan's flank as possible before they notice us.
  We cannot hide our hundreds of \armoured riders forever, but every yard we can move before they can deploy against us is one yard closer to our goal.}

Alas, they did not get quite as far as \Dornaer had hoped, for when they came close enough to see the Rungerans clearly, their infantry was already forming ranks and lowering their pikes. 

\tho{%
  So much for that. 
  Oh, well.
  We would have to fight sooner or later anyway.}

In the moonlit gloom \Dornaer could not see how many men Morgan had managed to deploy against her on such short notice.
She had to hope for the best. 

\Dornaer turned in her saddle. 
\ta{%
  Warriors!} she yelled.
\ta{%
  This is the moment we have been waiting for!
  Long enough have we hidden behind our walls.
  Now it is time to repay the scum of Runger for their crimes against our land and our people. 
  We ride for the sake of the noble and lamented \rayuth[\Icor]. 
  We ride for the sake of all those innocent people that have been killed by Morgan's hordes, all that have been raped, and all that have had their lives destroyed.
  In the name of the One Light, I call for vengeance and justice for all of Pelidor!
  Death to Morgan's dogs!
  Death to the dogs of Runger!
  Warriors of Pelidor\prikker attack!}

With that \Dornaer's force set into a charge. 

It was of utmost importance that \Dornaer's frontriders strike with enough force to break Morgan's first lines. 
For this purpose, the strike force had been composed of the fastest and strongest cavalry Pelidor had to offer. 

\Dornaer raised her weapon, and she and her fellows silently mouthed together the knight's traditional prayer: 
\tho{O' Iquin, thou One Light. 
  O' \Izion, \Barion and \Razilah, mighty \sephiroth.
  Preserve us that we may live. 
  Take us into your embrace if we fall. 
  And give us strength that we may smite the wicked.
  Hail \iquin.
  We are all one.}

As she prayed \Dornaer could fill the One Light filling her body. 
\ta{Hail \Iquin!} she cried aloud. 

\ta{\emph{We are all one!}} her knights answered in unison. 

Out of the corners of the eye-slits in her helm she could see her knights literally glowing with power of \iquin. 

\tho{The Light fills us and reminds us that we are all one.}

Ahead, few yards away now, she could see fear in the enemies' faces. 

\tho{As one we have no fear.} 

The Rungeran pikemen wavered for a moment. 

And as one the knights of Pelidor crashed into Morgan's lines. 
One moment of hesitation was all they needed. 
Like an unstoppable tidal wave they tore the infantry apart and trampled them underfoot. 
As soon as the first line was broken, the lines behind began to falter.
Fear spread through the ranks.
One man backed away, and his neighbour instinctively followed. 
No man wanted to be the next to die. 
And so the Rungerans' fear became their undoing as their lines fell apart and \Dornaer's cavalry rode down rank after rank of them. 

\tho{The One Light \favours us.
  Our plan is working.}

\ta{\Rah[\Dornaer]!} shouted the knight next to her.
\ta{Look!}
He pointed straight ahead.
\Dornaer looked up and saw great shapes looming before them.
Huge things, ten or twelve feet tall, dark and shaggy.

\tho{\Nephilim! 
  Ogres!
  Scores of them. 
  There is no way we can trample them.
  If we try to charge them they will break us.
  We have to avoid them.}

\ta{Veer left!} she yelled.
\ta{Everyone, veer left!
  Ogres ahead!}

\Dornaer turned sharply to the left. 
She hoped to skirt around the \nephilim and move further northeast and away from the fray where, according to plan, the Rungerans were massed to halt \Kintaer's forces. 
It was not easy to turn in mid-charge through enemy ranks on short notice, and several riders on her right came too close to the ogres and were pounded to a pulp by the half-\human giants. 
And now, seeing her forces break off their charge, the Rungerans finally began to advance. 

\ta{The ogres are closing!} she shouted to her men.
\ta{Move!}

The Rungeran infantry, already shaken, parted to let \Dornaer's riders through. 

\tho{Good.
  We have to put some distance between ourselves and those ogres.}

But as the infantry pulled back a new threat appeared. 
Ahead she could now hear the rumble of massive feet. 

\tho{Rungeran cavalry.
  Fucking \itzach.
  They have deployed their reserves against us.
  They must have anticipated this two-pronged attack and planned for it.}

Lines of armoured cavalry now gleamed in the moonlight ahead. 

\ta{Ready for battle, men! We will fight ourselves out of this yet!}

\tho{This will not be easy.
  We have fallen into a trap.
  
  We should have seen this coming. 

  Actually, we did.}





\begin{comment}
  \subsection{Carzain sneaks in}
\end{comment}
\placestamp{North of Rungeran army camp}
They had not been spotted yet, but Carzain \Shachar and his group knew they had to tread very carefully. 
Rungeran tents and campfires surrounded them on all sides and as far as the eye could see.
The Pelidorian soldiers were still skittish, but they had come to acknowledge the fact that the Rungerans genuinely seemed to not see them, cloaked as they were in spells cast by Carzain and Rubin \Sanyor. 
\Sanyor was this group's leader; a middle-aged \sphyle and a senior Vaimon of the \ishrah. 
With them were a score of elite archers, all on foot. 

They were slowly making their way south through the Rungeran camp. 
% They kept to the more empty areas. 
To their right, out west, Carzain could hear the din of battle where \Dornaer and \Kintaer fought against Morgan's forces. 
To their left were more baggage trains, camp followers and more infantry reserves. 

\vizicar{Those baggage trains are tempting,} said the voice of Vizicar. 
As a seasoned commander, Vizicar itched to sabotage the Rungeran supply lines, but they both knew that they could not. 
Their mission was much more important than that. 

\ta{Listen to that noise,} said Carzain. 
\ta{It sounds to me like \rah[\Dornaer]'s forces are in trouble.}

\ta{Most likely,} said \Sanyor.
\ta{Which just makes our mission all the more vital. 
  Come on. 
  We are close now.} 





\begin{comment}
  \subsection{\Takestsha strikes back}
\end{comment}
\placestamp{Centre of Rungeran army camp}
\Takestsha reclined on her soft-cushioned couch, having allowed herself and the \ishrah some rest. 
She lay back with her eyes closed, but through her supernatural senses she was monitoring the battle around her. 

\tho{So.
  A two-pronged sally attack, both aimed at the \ishrah's position.
  Well executed, but very predictable.} 
Even Morgan's mortal advisors had been able to predict this move. 
It had been a simple matter to take precautions and stop both prongs. 
So far, everything was proceeding according to plan. 

\tho{And now that we have them out in the open, I believe it is time to give them a taste of our true power.
  The formless brood of \KhothSell has feasted enough. 
  It is ready to be unleashed.} 

\Takestsha rose to her feet. 

\ta{\Ishrah! Attend me!} 





\begin{comment}
  \subsection{Carzain tricks a soldier}
\end{comment}
\placestamp{North of Rungeran army camp}
\ta{Look!} said Carzain, pointing. 
\ta{That is the \ishrah there up ahead.}

\Sanyor studied them, and Carzain could see that she was looking through the lense of the \sephiroth of \Mor\dash the Eye, one of the four pillars of \iquin. 

\ta{They are beginning something,} said \Sanyor. 
\ta{We must hurry!}

Then a gruff voice shouted some words in Rungeran. 
A soldier was coming their way and evidently tried to question them. 

\tho{Crap,} thought Carzain.
\tho{We've been spotted.} 

\Sanyor held up a hand, signaling: 
\hypota{I will handle this.}
She stepped forward and spoke some words in Rungeran in a loud, clear voice. 

The soldier said something, still suspicious but now hesitant. 

\Sanyor held her head high and gave a curt reply. 
Carzain did not understand Rungeran, but her body language told everyone that she was one whom this grunt had no right to question. 

\Sanyor waved the \human aside. 
He mumbled something, then obeyed and let them pass. 

\ta{Nice work, \Mistress \Sanyor,} said Carzain.
\ta{And without any magic.}

Then, suddenly, Carzain felt his stomach knot up. 
A wave of energy washed over him, and he imagined he could smell a trace of some putrid sourness. 
He met \Sanyor's eyes. 
She felt it too, and he knew she was thinking the same thing as he.

\tho{The \ishrah.} 





\begin{comment}
  \subsection{\Dornaer under fire}
\end{comment}
\placestamp{West of Rungeran army camp}
\Dornaer lashed out with her heavy mace and another Rungeran rider fell back with a mortal wound. 
The battle was raging all around her; \scathae and \humans and beasts fighting and dying.
She knew she and her men had to break out and retreat, but the Rungerans were harrying them and keeping them locked down. 

She noticed the warrior next to her about to be overwhelmed by two enemies. 
He had lost his shield and was hard pressed to just keep himself alive. 
She rushed to his rescue and bashed the nearest Rungeran's \relc with her mace, causing the \saurian to pull back in pain.
\Dornaer pressed forward and struck at the rider's arm, shattering bone. 
The \human cried out and dropped his weapon. 
Under these circumstances \Dornaer felt no compunctions against striking a defenseless enemy. 
She proceeded to pound the Rungeran's head with her mace until he slumped down in the saddle incapacitated. 

\Dornaer turned to see how her fellow knight had fared, but found him dead or dying, having been thrown from his saddle and trampled. 

\tho{Shit. Too late. Shit.

  I've got to get us out of here.}

\ta{You!} she yelled to the nearest knight behind her.
\ta{Take over the frontline!} 
She rode back behind the Pelidorian line, hoping to be able to rally her forces and lead them out. 

Then she began to hear a strange noise. 
A sort of whispering?
Whistling? 
Wailing? 
It seemed to come from above. 
\tho{\Pterans? Birds?}
\Dornaer looked up and saw wisps of cloudy mist flying by.
\tho{A storm brewing? Or some strange weather phenomenon?}

The sounds grew louder, becoming a chorus of shrieking voices above and around her, like a swarm of screaming things. 

\ta{Sorcery!} she heard someone shout. 

\ta{Run for your lives!} shouted another voice. 

Two more voices cried out\dash a \scatha's and a \relc's. 
No words, just strangled screams.
\Dornaer whipped her head around and just barely caught, through the gloom, a glimpse of one of her riders rearing up and toppling to the ground. 

Everything grew darker.
\Dornaer looked up to the sky, and what she saw struck her dumb and left her gaping. 





\begin{comment}
  \subsection{Sanyor sneaks off}
\end{comment}
\placestamp{Centre of Rungeran army camp}
Carzain could hear the howling of \daimonia in the distance, a cacophony of them. 
This was what they had feared. 
% Sethgal and the others had suspected the Rungerans might see their two-pronged attack coming, so they had prepared a third prong in the form of \Sanyor, Carzain and their archers. 
% Now it was up to them. 

\ta{It's begun,} said \Sanyor.
\ta{The mages are letting rip.
  We have to move \emph{now}, \MrShachar.
  I am going in.
  You will have to cover me.}

\ta{Right,} said Carzain. 

\Sanyor wrapped some \Archons around herself and ran off. 
Carzain turned to the men.
To their credit, they were all still calm. 

\ta{All right, men,} said Carzain.
\ta{You heard her.
  We have to create a diversion.
  Attack!}





\begin{comment}
  \subsection{\Dornaer under fire}
\end{comment}
\placestamp{West of Rungeran army camp}
\Dornaer looked up at the sky in dread. 
Above hovered a vast shape that eclipsed the moons and stars. 
She could barely see in this darkness, but what she could discern was the outline of a grotesque, shapeless horror with limbs and mouths beyond counting. 
An unnatural thing, unlike any creature that had any right to exist on \Miith. 
An alien monstrosity from beyond the night sky. 
A blasphemy against the One Light, howling its hunger and its hatred against all life. 

\tho{I cannot stand here and gape.
  I have soldiers who are dependent on me.}
With great effort \Dornaer tore her eyes away and found her voice again. 

\ta{Retreat!} she shouted. 
\ta{It's their \ishrah! 
  Everyone retreat! 
  Fall back to the city!} 





\begin{comment}
  \subsection{Carzain attacks}
\end{comment}
\placestamp{Centre of Rungeran army camp}
Chaos and panic reigned around Carzain and his soldiers. 
Under the cover of Carzain's \qliphoth, the Pelidorian archers were all but invisible to the naked eye, so the hapless Rungerans could only run, scream and die as Carzain's squad carved a path to the \ishrah. 

\tho{So far this is working good.
  I wish we could have done this from the beginning.}
But that was impossible. 
% A problem with magic was always to avoid detection.
A powerful cloaking spell might hide you from laymen's eyes\dash especially with the aid of natural cover, such as this darkness\dash but make the spell too strong and nearby enemy mages would be able to feel the magic and dispel it. 
Now, though, the Rungeran \ishrah's own spells worked in Carzain's \favour, for the sheer intensity of the doomsday weapon drowned out his subtle cloaking spells so he could turn up the power. 
% Still, a squad of noisy gunners would have ripped through Carzain's concealment spells and brought every enemy within a hundred yards down on them. 
% But the silent archers could remain hidden and wreak mayhem in the Rungeran base. 

Carzain looked up to the hill ahead where the \ishrah was encamped. 
% His main task was to act as a diversion for \Sanyor, but with luck he might get close enough to loose some arrows against the \ishrah. 
The hill was shimmering and seemed to quiver under the immense energies the mages were channelling. 
Carzain could just barely make out the commanding woman, wearing a gray-and-white dress this time.

Then, from hundreds of feet away, the woman turned her head and looked Carzain straight in the eye!

She raised her hand, and he could see her mouthing spellwords. 

\tho{Fuck. There goes our luck.}





\begin{comment}
  \subsection{\Takestsha dispels magic}
\end{comment}
\new
\Takestsha held the eye of the Pelidorian mage. 

\tho{So. 
  A third attack. 
  And a very clever one, at that.
  You Pelidorians have turned out to be less predictable than I thought. 
  
  I am impressed by your bravery, mortal. 
  But it ends here.}





\begin{comment}
  \subsection{Carzain is uncovered}
\end{comment}
\new
\hypota{There they are! Get them!}
Carzain heard shouting from the Rungeran soldiers all around, and while he did not know the language it was easy to guess the message. 

\tho{Crap.
  She found us.}

\vizicar{%
  And she dispelled all our cloaking spells with just a gesture,} said Vizicar with disbelief.
\vizicar{She is good.} 

\tho{And now we're fucked.}

Carzain drew his sabre. 
\ta{Our cover's been blown! Defend yourselves!}





\begin{comment}
  \subsection{\Dornaer dies}
\end{comment}
\placestamp{West of Rungeran army camp}
\Dornaer and all her riders turned around and made full speed towards \Forclin. 
They heeded not the Rungeran soldiers, for anything\dash even death by blade and bullet\dash would be better than the monstrous sorcery that assailed them. 
It was all around them now, a half-insubstantial mass filling the air. 
\Dornaer could not tell if it was a swarm of shrieking fiends or a single vast, amorphous god with a thousand limbs. 
All she could make out was a myriad grappling ghostly claws, a myriad mouths yowling and drooling and biting and holding and sucking. 
She swung her mace as she rode, trying to fend the things off, but her weapon seemed to pass right through their wraithlike forms. 
She could feel their touch on her skin now.
A hideous, unnatural pain racked her body and she cried out as she felt their teeth and tongues tear through her scales, rending and defiling and devouring. 

Before her there was light. 
Up ahead the moonlight still shone on the field. 
\ta{We're nearly out!} she shouts to her people. 
\ta{Go for the light!
  We're safe if we can get out of its shadow!}
She hoped it was true. 
It had to be true. 
Right now, fighting for her life was all that kept her mind from snapping under the horror of it all. 

A jolt slammed into her through her saddle. 
Her \relc bellowed in pain.
The animal must have been hit. 
It stumbled and toppled to the ground, taking her with it. 

\ta{\Rah[\Dornaer]!} one of her men called.

\ta{Don't stop!} she cried with what breath she had left.
\ta{Save yourselves! Go!}
Her last word barely came out.
It turned into a shrill, agonized scream as she felt the abomination's fingers grab hold and drill into her brain. 
Feebly she tried to crawl out of her saddle, but her strength was gone and her limbs would not obey. 

Before she died, the last thing \rah[\Dornaer] Pelidor saw in her mind was the formless demigod's face. 





\begin{comment}
  \subsection{Carzain fights for his life}
\end{comment}
\placestamp{Centre of Rungeran army camp}
Carzain unleashed a \qliphah, and another foe crumpled bleeding to the ground. 
The Rungerans were wary of him, for they had seen how easily he could kill, but they also realized that there was one of him and scores or hundreds of them, so they kept closing in. 

\tho{We're not going to last long against all of them.}

His archers had done their job well, but their weaknesses were starting to show. 
They excelled at stealth attacks, but they were not equipped for an all-out \melee like this. 
As soon as the Rungerans closed in they started dropping, and now there were few left. 

Carzain heard a cry of pain and glanced over his shoulder to see one more archer go down with bleeding wounds. 

\vizicar{That's it,} said Vizicar.
\vizicar{Discretion is the better part of valour.
  We have to escape.}

Vizicar invoked a new \qliphah and unleashed a quick and brutal mental attack. 
The Rungeran soldiers recoiled screaming as sensations of pain and terror overwhelmed their feeble minds. 
This spell would only last a few moments, but it would buy Carzain time to make his escape. 

\tho{With luck we can steal a \relc and get back to \Forclin.
  We did our part.
  Now it's up to you, \Sanyor.}





\begin{comment}
  \subsection{Sanyor's last spell}
\end{comment}
\new
Still wrapped in spells of cloaking, Rubin \Sanyor crept unseen through the Rungeran ranks. 
From behind she heard screams and shouts of battle.
The archers had begun dying. 
She prayed to Silqua for their brave souls and hoped that some of them would survive. 
They had done well. 
Only their support had allowed her to come this far. 

Now she could see Morgan's main cannon in all its hideous glory. 
It was a huge thing, more than twelve feet long, gray and golden and carved in the shape of a crocodile. 
It had stopped firing, and indeed it could not fire under these conditions, for around it the earth itself was quaking and pulsating, as if the hill had awoken to hideous life from the corrupting essence of the \ishrah's heinous spells. 

She was close enough that she could catch snippets of the \ishrah's incantations. 
Some of the words were Rissitic. 
\tho{So Morgan Runger is indeed in league with the Rissitics of \Durcac.}
Other words were in that much more ancient tongue which \Ortaican \rethyaxes used, and which was supposedly the tongue of \dragons. 
Rubin was learned and had a knack for languages, so she understood small bits of both languages. 
Amid the invocations she caught some ominous names: 
\emph{\KhothSell{}}. 
\emph{Mother \KhothSell{}}. 
And once, \emph{\NaathKurRamalech{}}. 
She did not recognize the names, but they struck a chord deep in her subconscious, resonating with the evil of a thousand worlds and a thousand ages. 
She glanced west to where the great dark cloud of \daemons was wreaking havoc among \Dornaer's troops, and it seemed to her as if all the destructive horror of the thing was contained in and emanated from those hideous, barbaric syllables. 

\tho{Such atrocities.
  Such evil.
  Morgan Runger and his vile \ishrah must be stopped.
  Alas, I cannot destroy the \ishrah and stop all their crimes alone.
  I am not strong enough for that.
  But at least I can do this small thing.}

She began weaving a spell around the cannon. 
It was difficult, for the spell was complex and she had to work quickly. 

Immediately she felt white-dressed woman's attention upon her. 
Her spells came down upon Rubin like a tidal wave, hammering against her wards. 
The pain forced Rubin to her knees, but she kept working on her spell. 
In a way she was relieved. 
The Rungeran \human had not guessed what she was trying to do\dash otherwise she would have bent her efforts towards countering Rubin's magic. 

Rubin could feel her wards shattering one by one. 
\tho{She will kill me.
  I am going to die soon.
  But I will not die in vain.}
She summoned up all the energy she had in her body and called the \sephiroth into her.
They filled her up so that she was just about to burst open from the strain. 
For a few moments of ecstatic agony she could almost feel her brain haemorrhaging as the \sephiroth's awesome presence ravaged her mortal mind that was much too small to contain them. 

In the moment that her final ward cracked, Rubin unleashed all her power upon the Rungeran cannon. 

\tho{There. 
  I hope that will be enough to break the thing. 
  At least for a while.}

Then the \daemons broke through and Rubin \Sanyor's head imploded. 






% \begin{comment}
%   \subsection{Carzain flees}
% \end{comment}
% \new
% Sensing a fierce contest of sorcery behind him, Carzain glanced back to the hill and just caught a glimpse of Rubin \Sanyor before she collapsed in a bloody heap. 
% He also noticed something emanating from the great cannon, audible to his mystic senses as a crackling or seething sound, a scent like smoke. 
% 
% \vizicar{She made it,} said Vizicar.
% \vizicar{I cannot tell at a glance what she did, but if we are lucky it will disable the cannon.
%   At least for a while.}
% 
% \tho{Well done, \Sanyor.}
% 
% He continued his flight. 
% In the distance up ahead, looming high above the walls of \Forclin and looking out over all the blood and death, stood the Ghost Tower. 





\begin{comment}
  \subsection{Curwen realizes they want the Ghost Tower}
\end{comment}
\placestamp{\Forclin city wall}
Archibald Curwen had stood on the wall and watched it all. 
He did not know what had become of \Sanyor and \Shachar's mission, but both \rah[\Dornaer]'s and \rah[\Theal] \Kintaer's forces had been beaten and were now fleeing back to the city in tatters. 
Morgan's tactics had been effective, but what had really torn the Pelidorians apart was the \ishrah's doomsday weapon.
It was everything Curwen had feared it would be. 
A behemoth \daemon\dash or swarm of \daemons\dash destroying all in its path. 

\tho{%
  So this is \Takestsha's secret weapon.
  Stolen from the vault of \EreshKal.
  Or is it?
  I can't believe that this is just a \meccaran artifact.
  Why would such primitive beings possess such power?
  Why would their civilization have degenerated so if they had such a weapon?
  No.
  I fear this is something more insidious.
  This is not a normal earthly affair.
  I see greater forces involved in this.
  I see immortal hands.
  Sentinel hands.}

He turned the evidence over in his head and tried to make sense of it. 
It looked as though the Sentinels were behind the Rungeran invasion.
\tho{But why?
  What do they want?
  What is their interest in Pelidor, or Runger for that matter?}

What was it that \Jirad Tantor had said?

\hypota{\Takestsha seeks a source of even more power.
  I think she believes she will find it in Pelidor.
  In the city of \Forclin.}

\tho{What could he have meant?

  Perhaps I should contact the lady \Achsah.
  I hate to give up on a riddle, but perhaps she knows more than I do. 
  I should be able to reach her through the Ghost Tower\prikker}

Curwen glanced back into the city and saw, through the mist, the blurred outline of the aeons-old \resphan spire, jutting up out of the ground like a pale bone out of some forgotten, pre-human epoch. 

Then something dawned on him. 

\tho{The Ghost Tower! 

  Of course. 
  \Takestsha is after a source of great sorcerous power in the city of \Forclin.
  What else but the Ghost Tower itself?
  It makes perfect sense.
  The tower is a gateway to the Beyond. 
  The Sentinels want to conquer the tower and use it as a staging area from which to launch attacks upon \Nyx itself. 
  That must be it. 
  And this \Takestsha must be a Sentinel agent. 

  I must tell \Achsah immediately.} 









