
\bookchapter{\Urizeth Dies}

Remember to have plenty of \maybehr{Resphan wing body language}{wing body language} from the \resphain. 

\Teshrial is flying to \Urizeth's citadel. 
He is happy about his collaboration with her. 
She has been able to answer many of his questions, and with \Lothagiel's notes she has told him she believes she is close to reproducing the calculations that will let her pinpoint the Nadir. 

She has explained the Nadir to him. 
He did not entirely understand it, but it was something about how \Ishnaruchaefir's \vertex is connected to the Shroud, so when the Shroud experiences turbulence, so will he. 

Allegedly the Shroud was growing unstable lately. 
Some astrologers thought it was going to hell and that something was going to go massively wrong with the Shroud in the near future unless the Cabal pulled their heads out of their asses and did something to repair the damage that had been done and make the whole thing stable again. 
Allegedly this \quo{instability} is the reason why such \quo{turbulence} has been more frequent in recent years. 
The Shroud was falling apart. 

\Teshrial does not believe in this theory. 
From what he has heard, there are plenty of reasonable explanations for the violent dimensional storms these last years without resorting to hysterical doomsday prophecies. 
He assumes \Urizeth (and other doomsaying astrologers like her) are just hungry for attention and political influence, and more than a little demented from their over-exposure to immoral occultist writings. 

No, \Teshrial decides. 
On that count \Urizeth is just being crazy. 
But he thinks she can be trusted when it comes to things that genuinely are her specialty. 
Speficially: 
Interpreting myths and evidence and finding a way to defeat the Destroyer. 

\Teshrial enjoys hating \Ishnaruchaefir.
It is just as strong a feeling as being in love.
He thinks about \Firaxel and acknowledges to himself that he is in love.
(Have him thinking more about \Firaxel throughout. Ever since the party where she favours him, he falls in love and grows obsessed with her.)
His love for \Firaxel and his hate for \Ishnaruchaefir are his twin motivations, both driving him in the same direction.
And he loves both feelings.
They both affirm that he is alive, that he is a true \resphan who fights against his people's enemies (hate) and for the future and greatness of his bloodline and their race (love, sex, procreation).


Now he is at her tower. 
He lands. 
Gets shown in by servants. 

He does not like the atmosphere of the place, or the nervous, subdued way the servants are skulking around. 
There is something wrong. 

A \resphan comes out (a friend of \Urizeth's) and greets him. 
\ta{Lord \Teshrial.}

\Teshrial: \ta{Who are you?}

\ta{I am \Urizeth's son.}

\Teshrial: 
\tho{Her son? 
  I did not even know she had a son. 
  Huh. 
  Makes me realize how little I know of her.
  She is so reclusive.
  She never talks about herself.
  And I have never thought to find out\prikker}

\Teshrial: \ta{How do you do. I am here to see Lady \Urizeth.}

\ta{Alas, Lord \Teshrial. \Urizeth cannot receive you today.}

\ta{But we had an appointment. What is the matter?}

\ta{\Urizeth is dead.}










