\section{Out of the Mouth of Madness}

% Rian and Neina have been separated from Moro \Cornel.
% A monster approaches them. They are cornered with no escape. Rian feebly draws his knife, but he knows there is no hope. But then, all of a sudden, a fatter human runs past. The monster turns from them to chase the fat man instead.  
% They are saved this time, but it cannot last. They huddle in fear, while the city literally goes to Hell around them. 
% Neina is mad and babbling. 
% Rian is slowly resigning himself to the fact that they will most likely die. 
% Then Rian sees a great black Dragon above. It fascinates him, and he cannot look away. He catches its eye and it turns around and lands near them.
% The Dragon transforms into a Scatha. Rian recognizes \Ishnaruchaefir{} from the dead garden. 
% Ishnaruchaefir: "Who are you?" 
% Rian: "You are the one from the garden!"
% Ishnaruchaefir: "Oh, yes. The boy. You have grown since last time. Stronger. Wiser. Less sane." 
% Ishnaruchaefir notices Neina. "Who is she? What is wrong with her?"
% Rian: "Neina. My... my fiancee. She was a prisoner of those... those cultists." 
% Ishnaruchaefir: "And you freed her? Not bad." 
% Rian: "What is happening here?" 
% Ishnaruchaefir: "You do not want to know." 
% Neina cries aloud. Rian tries to comfort her. Ishnaruchaefir can see the strain written in his face.
% Ishnaruchaefir: "I suppose I owe this much, seeing as how I am, in a sense, responsible for this... mess."
% He create a portal and shoos them through into the Beyond. He guides them a short way, and they emerge out amid some fields outside the city.
% Neina collapses again, shuddering and weeping. 
% Ishnaruchaefir: "She will not recover from this on her own. But I can try to wipe the imprisonment from her memory." Zap. "She will remember little of her ordeal now. But be warned: She will likely have forgotten other things, too. She will be dependent on you." 
% Rian: "Thank you... Lord Ishnaruchaefir." 
% Ishnaruchaefir smiles. "Stay away from the city. You are on your own now. Fare well." He turns and leaves.
% Neina sort of recovers. She is not as weepy and despairing as before. Rian is hopeful. "We will survive. We will marry and live happily ever after. This I swear."
% Ishnaruchaefir turns back to the city. "I condemn ten thousand mortals to a horrible death, and the save two. Ha. And thus I remain inscrutable, my motivations remain opaque, unknowable. Even to myself." He smiles ruefully. 
% Ishnaruchaefir: "Secherdamon! Where are thou? Show thyself!"
% Or perhaps he meets not Secherdamon, but Nzessuacrith. 

And so they huddled together under the makeshift lean-to formed by a collapsed shop front, while the city literally went to Hell around them. 
Neina kept weeping and babbling to herself, and Rian had to fight hard to keep himself from doing the same. 

Through an opening in the houses opposite them, Rian could glimpse the castle. 
As he watched, a huge statue of an angel, proudly raising his sceptre to the heavens, slowly cracked, toppled and fell to the ground, shattering into a thousand pieces. In its place there arose a horrid claw-like appendage, ten times a man's height, made of brown flesh, specked with black stone scales and stained with the red blood of slaughtered citizens. 

The fallen angel's head rolled on the ground, empty eyes staring into nothingness. Defeated. 

\tho{We're doomed. It's as they said. The Light has abandoned us. It really is the world going under. We're all going to die.} 

He studied the knife in his hands. 
\tho{I ought to end it myself. 

A clean cut of a dagger. 
Better than being eaten by monsters.}

There was a loud crash directly above them. 
Rian cried aloud in spite of himself, then crept deeper into the corner with Neina, shielding them both with his arms as best he could, while fragments of the roof tumbled down around their ears. 

\tho{We're all going to die. We're all going to die.}

The rain of rocks and bricks abated, and he dared to lift his head again. 
Through the smoke and the unnatural blur of the air above, he thought he could see something. 
Something new, not quite like the \daemons. 
\tho{As if I've seen it somewhere before.} 

It was a flying shape, huge and dark, circling above the falling city. 
Rian squinted, hoping for the mysterious form to come closer. 

A building near them cracked and groaned. 
He and Neina shrieked in unison and clung to each other as they waited for it to pass. 

As soon as he dared, Rian again looked up, trying to spot the flying thing. 

For a moment, the blurry mist cleared. 

It came into view. 

Rian gaped. 
He halfway rose to his feet. 
Dimly he registered a throbbing pain in his head as it bumped against the roof of the lean-to. 
But only dimly. 
His eyes were riveted to the flying creature above.

It was a \dragon. 

Twenty times as long as Rian was tall, perhaps, and soaring on massive wings spread as wide as it was long. 
Its scales were pure black like onyx, but its eyes burned like fire. 
Those eyes, those claws, those horns, those wings... every aspect of the great creature spoke of power. 
Ancient, terrifying, majestic, awesome \emph{power}. 

Rian could not take his eyes away from the overwhelming sight. 
\tho{Is this the angel of death come to judge us all?} 
All his life, he had never really believed that \dragons{} existed, but with everything he had witnessed this day he was past surprise or disbelief. 
He just stared into those flaming yellow eyes. 

And then something sparked in those eyes. 
Recognition. 

The creature had noticed him.

\tho{It's spotted me. I'm going to die.} 

The \dragon{} slowly turned towards him. 

\tho{Run! Run! Run!} 

But Rian could not run. 
The monster's burning eyes held him nailed to the spot, unable to move a muscle. 

It descended. 
% Rian had to protect his face from the cloud of debris stirred up by its vast wings. 

It touched down with one clawed foot. 
And the air around it shimmered. 
An unnatural mist sprang up, almost like fire, but of a strange colour\dash\tho{purple? black?}\dash half-obscuring the immense creature. 

And the \dragon{} changed shape. 
It shrank, retracting its great wings and neck. 

The mystic flaming mist dispersed, and there stood a humanoid. 
A \scatha, seven feet tall, with pure black scales, a strangely slim and elongated snout and a snaking tail, clad in black robes and plates of metal armour. 
He stood only three or four paces from Rian's position, eyeing him with... what might be detached curiosity. 
Rian could only guess, for those alien eyes were opaque to him. 

%\ta{Do I know you?}
\ta{Do I know you?} asked the \scatha{}\dash no, the \dragon. He spoke Belkadian, in a deep, calm voice. 

\ta{You... you are that one! The sorcerer from the dead garden!}

The black one's eyes narrowed slightly. 
Then his mouth twitched. 
\ta{Ah, yes. The boy who followed me.} 
His eyes seemed to run up and down the young thief.
\ta{You have grown since last time. Stronger. Wiser. Less sane.}

It took a while before Rian could respond to that one. \ta{Who are you?} he managed. 

\ta{I am Quessanth \Ishnaruchaefir.} 

They heard a roaring noise in the distance. 
Neina yelped and began to sob loudly. 
Rian hugged her tight, feebly trying to comfort her. 

\ta{Who is she? What is wrong with her?} asked \Ishnaruchaefir. 

\ta{My \fiancee. 
She's been held prisoner by... those evil people.} 
He looked up accusingly. 
\ta{Those people who caused all this!} 

\ta{And you rescued her? Hm. Not bad.}

\ta{What is happening here?} Rian almost screamed. 

\ta{You do not want to know.}

Rian scowled at that, but was forced to turn back to Neina as she cried out again. 

\Ishnaruchaefir{} studied them. 
\ta{Hm. I suppose I owe this much, seeing as how I am, in a sense, responsible for this... mess. 
Look at me.} 
%He half-raised his left hand and made subtle gestures with his un-\scathaese{} clawed fingers while speaking a few low words in an alien tongue. 

Rian obeyed. 
As he met that flaming gaze he was once again riveted to the ground. 
Unable to look away. 
Unable to think. 

In a haze, he heard the sorcerer speak low words in an alien tongue. 

The burning eyes seemed to grow, until he was aware of nothing but that stare. 
The world around him vanished. 
Nothing existed except those eyes. 
Nothing had ever existed except those eyes. 

Rian heard a ghastly, uneathly sound coming from nowhere. 
A ripping, creaking, oozing sound. 
As if someone was tearing a hole in the fabric of reality. 

One burning eye went out. 
Then the other. 
The world went dark. 

The world returned. 
The world beyond those eyes. 
\Ishnaruchaefir{} had licked his eyes, breaking the transfixing gaze. 

% He looked up and saw a blur of strange, unnatural colours swirling in the air next to them. 
Rian looked up and saw that the world had... changed. 

The buildings and roads in front of him, behind the sorcerer, were suddenly twisted out of form. 
They still looked as buildings that might plausibly exist in Malcur, but somehow deformed and wrong, as if viewed through a bulging, uneven mirror, or mirrored in a curved spoon. 
The colours were unnatural, too. 
Still similar to the normal colours of wood and stone, but speckled with hints or strange colours that should not be there. 
Greens? 
Purples?
Rian was not sure, for they seemed to swirl and shift in and out of existence as he beheld them. 

He turned his head and saw that on the other side the world looked almost normal. 
It was slightly blurred and unclear, as if he were very drunk, but still recognizable as the normal world. 
The real world. 
But as he shifted his gaze to his right, where the black mage stood waiting, the real world shifted and twisted into this... this other world. 
This wrong world. 
This unnatural world. 

\Ishnaruchaefir{} beckoned. 
\ta{Come, if you want to live.} 

\ta{Wh-wh-wh-what is that?} Rian squeaked. 
\tho{More black magic! More insanity!}

\ta{Come!} the \draconian{} mage repeated, his voice deeper and slightly guttural. 

And before Rian knew it, he found that he and Neina had both risen to their feet. 
The black mage turned and led them into the twisted world. 
Before Rian could stop and think twice, they were following him, their bodies seeming to move on their own. 

\Ishnaruchaefir{} led them on a path between the deformed houses. 
As the walked, the houses around them were replaced by ruins. 
The ruins became rocks. 
The rocks became trees. 
The trees became crops. 
All of them were warped and out of proportion, and stained with unearthly colours, fearful and loathsome to the eye. 
Not quite orange, nor green, nor gray, but something similar to all of them and yet wholly different. 
Unlike any colours he had seen. 
Unlike any colours that ought to exist. 

Unable to make sense of any of it, Rian kept his eyes straight ahead and pushed on, holding his girlfriend tight. 
And before he knew of it, they emerged into...

% 
% 
% He turned... and somehow walked through the swirl of colours and out of the world, into another, stranger world. 
% Still visible, but clearly no longer in the street in Malcur. 
% 
% Rian found himself rising to his feet, his body almost moving on its own. 
% More incredibly, Neina also rose, even without his having to drag her. 
% Before he could stop and think twice, they were following the black mage into the rainbow blur. 
% 
% The street faded from view behind them, and Rian and Neina found themselves stranded in what looked to be a tunnel, its sides made of shifting, luminescent... stuff. 
% And the colours were all wrong. 
% Not quite orange, nor green, nor gray, but something similar to all of them and yet wholly different. 
% Unlike any colours he had seen. 
% Unlike any colours that ought to exist. 
% 
% \ta{Come! Follow!} \Ishnaruchaefir{} called back as the two \humans{} slowed to a halt. 
% The sorcerer waited maybe twenty paces ahead, where, behind him, there shimmered something with green and yellow colours on the ground and blue colours in the sky. 
% \tho{Normal colours. 
% Real colours. 
% A window out of this alien place?} 
% 
% Rian kept his eyes straight ahead and pushed on, holding his girlfriend tight. 
% They reached the place where \Ishnaruchaefir{} awaited them... 
% and popped back into the real world. 

A field. 

Yellow crops. 
Green trees. 
Blue sky. 
% Free, open air; no constricting tunnel walls made of unnatural stuff. 

\tho{Normal colours. 
Real colours. 
The real world.} 

Rian looked around. 
The yellow field surrounded them, grasses rippling in the breeze. 
There were no signs of the warped world. 

\tho{Black magic.} 
He understood nothing, could only think of one label with which to explain it all. 
\tho{Black magic.} 

In the distance behind him he could see towers, walls, battlements. 
Statues of angels, warriors and kings. 
Licking flames, columns of smoke, clouds of dust and debris. 

\tho{Malcur.} 
The thief had never been this far from the city in his life. 
\tho{Is this what it looks like from the outside?}

Neina had dropped to her hands and knees and was babbling gibberish again. 
Rian held her and stroked her, murmuring words of consolation. 

\ta{She will not recover on her own,} came the voice of \Ishnaruchaefir. 
\ta{As things are, she will remain a babbling wreck for the rest of her life.} 

Rian turned to the \dragon. 
His tear-filled eyes said all that needed saying. 
\tho{I beg you. Can you help her?}

\ta{I can wipe the memory of the ordeal from her mind. 
It is neither safe nor certain, but it will be an improvement.}

Rian looked his beloved in the eyes. 
She did not look back, only stared into space. 
She was quiet for the nonce, but her lips still moved, mouthing silent nonsense. 
At intervals, a weak shudder would run through her. 

\tho{Not safe. Not certain. But an improvement.}

He turned back to the \draconian{} mage. 

Swallowed. Nodded. 
\tho{Please. Do it.}

\Ishnaruchaefir{} twirled the fingers of his right hand and spoke arcane words, his voice deep and guttural like it had been back at the dead garden when he cast his spells. 

The girl sighed and slumped down, elbows and face against the ground. 

\ta{Neina! Neina!} 
He gently turned her over. 

Her eyes were closed. 

Slowly they opened. 
She looked him in the eyes. 
\tho{She looked me in the eyes!} 
Her gaze was groggy, but there came a glimmer of recognition. 
She moved her lips to speak, but no sound came out.

\ta{Neina! Can you hear me?}

\ta{Ri... Rian...} 

\tho{She spoke my name!}

\ta{Neina! You're back!} 
He embraced her tight, never wanting to let go again. \ta{Neina. You're back.}

\ta{She will remember little of her imprisonment, nor of the city's fall,} said \Ishnaruchaefir{} behind them. 
\ta{But she will have forgotten other things, too. She will be dependent on you.}

Rian turned back to the \dragon. 
Again tears filled his eyes and his throat, but these were tears of joy.
\ta{Thank you. Thank you, Lord \Ishnaruchaefir.}

The sorcerer's mouth twisted in a slight smile. 
\ta{Stay away from the city. You are on your own now. Fare well.} 
With that, he turned away and leapt into the air, ten paces high or more. 
And transformed. 
Fire wreathed and entwined his body as it changed, growing to colossal size. 
His neck and tail stretched, becoming long a snaky. 
His billowing cloak spread wide to become vast wings. 
His robe and armour faded away, as if melting and merging into his great scales. 

And in a tremendous gust of wind, the terrible black \dragon{} beat his wings and flew off in the distance, returning to the ruins of crumbling Malcur. 

% vanished into the manycoloured hole, which promptly closed behind him. 

Rian and Neina were alone in the field. 

\tho{On our own.
Yes. 
We will survive. 
We will marry and live happily ever after. 
This I swear. 
By all the sixteen \sephiroth, I swear it.} 

\ta{Rian... where are we? Who was that \scatha? He was scary...} 

%She was cut off. 
He kissed her, cutting off her words. 
She did not understand, but she kissed him back. 

\tho{We are safe,} he thought. \tho{We will survive.}







\new
Quessanth \Ishnaruchaefir{} reverted to his true form and again took to the air above the fallen city of Malcur. 
\tho{No, no longer Malcur. \Nithdornazsh.}

\tho{Today I have condemned ten thousand mortals to a horrible death. 
And saved two. 
Hm. 
And thus I remain inscrutable, my motivations still unknowable and mysterious.} 

He smiled ruefully. 

\tho{A mystery. Even to myself.}




