
\part{The Realm of \Azmith}
\index{\Azmith}
\target{Azmith}
\Azmith{} is a Realm on \Miith{}, a fragment of the shattered realm of \Tembrae. 
The name \quo{\Azmith} also refers to the politically most important continent of the Realm. 

The continent consists of \hr{Velcad}{\Velcad}, the \hs{Northern Kingdoms}, \hs{Threll}, the \hs{Imetrium}, \hs{Uzur}, \hr{Durcac}{\Durcac}, the \hs{Near Orient} and the \hr{Serpentines}{\Serplands}. %Some scholars also consider Irokas a part of \Azmith{} while others do not. 

\quo{\Azmith} is \hs{Archaic Vaimon} for \quo{all the world} (containing the word \quo{\Miith}, meaning \quo{the world}). 

\target{Azmith is important}
\Azmith was the most important of the \hs{Shrouded Realms}. 
This was the place where \hs{Silqua} was incarnated, and therefore place where the \hr{Vaimon Caliphate}{\VaimonCaliphate} first took root. 
As a result, \iquin was more strongly rooted here than in any other Realm (although religions parallel to \hs{Iquinianism} \hr{Iquinianism exported}{were exported} to other Shrouded Realms). 

This might be the reason why so many Scions incarnated in \Azmith. 
They were drawn to it as a \quo{centre of mystical convergence}. 

And it is the reason why it was in \Azmith{} that \Secherdamon{} chose to resurrect \Nithdornazsh. 








































\chapter{The Birth of the \VaimonCaliphate}















\section{\Asaathur}
\target{Asaathur}
\index{\Asaathur}
\index{Eryx!Ring of Eryx}
\index{Eryx!labyrinth}
\Asaathur was a fallen \ophidian nation. 
It was said that \Asaathur had fallen into ruin because the high \hs{Mysteriarch} went mad from sitting and gazing into the \hs{Ring of Eryx}.
This ring had been found in the mysterious invisible labyrinth of Eryx.















\section{Calaan}
\target{Calaan}
\index{Calaan}
A \human nation that existed at the time of Cordos Vaimon. 
A rival of \Imrath. 
The Calaanites might have been nomads. 

\hs{Silqua} was a princess of {Calaan}.

The name is inspired by \quo{Canaan}, a land mentioned in the Bible.















\section{Ematheroc}
\target{Ematheroc}
\index{Ematheroc}
A nation that existed at the time of Cordos Vaimon. 
A rival of \Imrath. 

The name is inspired by \quo{Kadatheron}, a city that is mentioned in \cite{HPLovecraft:TheDoomThatCametoSarnath}. 















\section{\Imrath}
\target{Imrath}
\index{\Imrath}
The \human kingdom to which \hs{Silqua} and \hs{Cordos Vaimon} belonged. 

\target{Imrathi nomads}
\Imrath{} was a nomadic people, like the Mongols. 
They waged wars against their rivals of \hs{Calaan}, \hs{Ematheroc} and \hs{Tulya}. 















\section{Lom}
\target{Lom}
\index{Lom}
Lom was a lake that lay near the place where the \hr{Imrath}{\Imrathi} dwelt.

By the shores of the mist-shrouded and murky lake of Lom there dwelt a race of repellent, half-\human things with huge hairless heads and fishlike, stupidly staring eyes.
The Lom-men prayed to the strange and ugly gods of the lake, chief among whom was \hs{Mnoth}, whose ichthyic features were awful to recall. 









\subsection{History}





\subsubsection{Destroyed by Cordos Vaimon}
The \humans of \Imrath had long hated the Lom-men and feared their wicked sorcery, until at last prince \hs{Cordos Vaimon} led an army against the Lom-men and \hr{Cordos conquers Lom}{defeated them}.





\subsubsection{Still haunted}
\target{Mnoth haunts Lom}
After Cordos Vaimon wiped out the Lom-men, the lake was still haunted and feared.
Once in a while the god Mnoth would still visit the lake, entering through arcane secret tunnels through the Beyond known only to the \hs{Lords of the Deep}. 
















\section{Nemaag}
\target{Nemaag}
\index{Nemaag}
A \scathaese nation that existed at the time of Cordos Vaimon. 
A rival of \Imrath. 

Nemaag was the most feared of \Imrath's rivals. 
It was a mystic realm of sorcery and shadows. 
Here the \ophidians still held sway, and Nemaag was said to be ruled by a \dragon-king. 















\section{Su-Gelba}
\target{Su-Gelba}
\index{Su-Gelba}
Su-Gelba was an \ophidian city.
It survived long as a bastion of sorcerers, even into the age of the \VaimonCaliphate. 









\subsection{The Tower of \Haamon}
\target{Aamon}
\target{Haamon}
\target{Tower of Aamon}
\target{Tower of Haamon}
\index{Tower of \Haamon}
The Tower of \Haamon was a mystical site existing somewhere in the dimensions. 
In ancient times it was the central citadel of Su-Gelba from where its terrible lords reigned. 

After the downfall of Su-Gelba the tower wandered the dimensions. 
It was co-terminous with outer spheres where the cosmic winds howled. 

In the tower dwelt a council of three immortal \ophidian philosopher-guru-mystics, mysterious and terrible. 

On the tower walls was encarved the powerful Symbol of \Haamon, as well as powerful runes in the language of \hs{Kush}. 

The tower had a mythical status among the \rethyaxes.
They hoped to catch a glimpse of it in their dream-meditations.
They hoped to glean a little of the wisdom of the terrible dark philosophers that dwelt in the tower. 















\section{Tulya}
\target{Tulya}
\index{Tulya}
A \scathaese nation that existed at the time of Cordos Vaimon. 
A rival of \Imrath. 















\section{Yaru}
\target{Yaru}
\index{Yaru}
A \scathaese nation that existed at the time of Cordos Vaimon. 
A rival of \Imrath. 








































\chapter{The \Human Age}
















\section{\Masthenon}
\target{Masthenon}
\index{\Masthenon}
A \hs{Tassian} \scathaese{} people that flourished during the time of the \hr{Vaimon Caliphate}{\VaimonCaliphate}. 

A single person is a \quo{\Masthen}, plural \quo{\Masthenon}, adjective \quo{\Mastheno}. 
\quo{The \Masthenon} is also the name of their civilization as a whole. 

The \hr{Ortaica}{\Ortaicans} descend from the \Masthenon. 
The \hr{Shurco}{\Shurco} have some \Masthenon{} heritage in their blood and culture, but also other things. 















\section[Sarun]{\Sarun}
\target{Sarun}
\index{\Sarun}
The \Saruns were a race of \humans that wielded great power in Cordos Vaimon's time. 









\subsection{Culture}





\subsubsection{Mages}
\Saruns \hr{Sarun intelligence}{were intelligent}. 
They valued learning, so they had a tradition of educating many mages.
With their power and wealth, they could also afford to educate mages. 





\subsubsection{Religion}
\target{Sarun religion}
The \Saruns worshipped brutal \draconian gods.
The Vaimons hated them for this (and for their cruelty). 





\subsubsection{Sultanate}
\target{Sarun sultan}
The \Saruns were ruled by a sultan.









\subsection{History}





\subsubsection{Empire}
At the time of \hs{Cordos Vaimon} the \Saruns wielded great political power. 
They were cruel and decadent rulers and \hr{Sarun religion}{worshipped evil gods}, so they were hated. 





\subsubsection{Defeated by Vaimons}
The Vaimons waged war against them. 
Eventually the Vaimons won.
They destroyed the \Sarun empire and wiped out almost the entire \Sarun race.




\subsubsection{Survivors}
After the fall of their empire only few \Saruns survived. 
They lived in hiding. 
They still worshipped their brutal and decadent gods. 









\subsection{Physique}
\Saruns had very pale skin, elongated heads with high foreheads, and white or gray hair. 
Due to their pale skin they were sensitive to sunlight.









\subsection{Psychology}
\target{Sarun intelligence}
\Saruns were often highly intelligent. 
But they also had a tendency to become insane and sadistic.
Compare to House Targaryen in \cite{GeorgeRRMartin:ASongofIceandFire}. 















\section{\Shurco}
\target{Shurcarie}
\target{Shurco}
\index{\Shurco}
\index{\Shurcarie}
The \Shurcarie{} was a \scathaese{} \hr{Mekrii}{\Mekrii} \hr{Bacconate}{\bacconate} that existed during the time of the \hr{Vaimon Caliphate}{\VaimonCaliphate}, controlling much of \hr{Durcac Continent}{\DurcacContinent}. 
It was defeated in a series of wars by \VizicarDurasRespina{} and others and did not last after the \hr{Hundred Scourges}{\darkfall}. 

Their heritage was carried on by the \Ortaicans{} and others. 

Modern-day \hr{Durcac}{\Durcac} owes much of its cultural heritage to the \Shurco.









\subsection{Culture}





\subsubsection{Egyptian}
\Shurco culture should be compared to that of Ancient Egypt. 





\subsubsection{Mysteriarchs}
\target{Mysteriarch}
\target{Mysteriarchs}
\index{Mysteriarch}
The rulers of \Shurco were the dark and feared Mysteriarchs, a cabal of sorcerers with \ophidian blood. 
The greatest of them was called the Last Mysteriarch or the Ultimate Mysteriarch. 










\subsection{History}
The \Shurco{} were \Mekrii, but they also owed parts of their culture to the \hs{Tassian} \Masthenon, to whom they were also in part related. 















\section{\Tepharae}
\target{Tepharae}
A \hr{Bacconate}{\bacconate}, dominated by the \hr{Tepharite}{\Tepharite} people, that existed after the \hr{Hundred Scourges}{\darkfall}. 
It rose to prominence after the fall of \hr{Ortaica}{\Ortaica} but before the advent of \hr{Great Velcad}{\theBelkadianEmpire}. 
At the height of its power, it covered modern-day \hs{Pelidor}, \hs{Runger}, \hs{Ontephar}, \hr{Scyrum}{\Scyrum}, \hs{Beirod} and some more. 
The \Tepharin{} tongue is still spoken in parts of these countries. 

\Tepharae{} was \hs{Iquinian}. 
It was they who \hr{Telcra founded}{founded} the Vaimon \hr{Telcra}{\ClanTelcra}. 
\also{\hr{Tepharite}{\Tepharite}}









\subsection{Culture}
\subsubsection{Names: Western order}
\Ortaican{} traditionally have two names: 
A family/clan name and a personal name. 
The \emph{personal} name comes \emph{first}. 

This is like \Velcadian{} and Vaimon, but unlike \Ortaican{} and Imetric. 









\subsection{History}
\Tepharae (together with \hr{Telcra}{\ClanTelcra}) \hr{Tepharae succeeds Ortaica}{rose to prominence after the fall of \Ortaica}.















\section{Sturia}
\target{Sturia}
\index{Sturia}
Sturia was a land that existed during the time of the \VaimonCaliphate.
It was part of the \caliphate, but like many other lands it would sometimes try to secede or rebel and have to be beaten into submission.

\target{Sturiac}
\index{Sturiac}
The chief language spoken in Sturia was Sturiac. 









\subsection{Uruthar}
\target{Uruthar}
\index{Uruthar}
Before the mortal kingdom of Sturia rose, there lay in the same region the eldritch realm of Uruthar.
It was ruled by a group of \bezed \resphain, including \hr{Lethiarch}{\Lethiarch} and \hr{Osra}{\Osra}. 





\subsubsection{\Resphain outcasts}
\target{Uruthar Resphain cast out}
These \resphain originally dwelt with their brethren among the dynasties, but they grew dissatisfied with their subjugated position. 
They desired to rule as gods rather than serve as scorned half-breeds. 
They were also afraid of the sinister cosmic sorcery practised by the dynasties. 
They felt that their brethren had gone too far in their dealings with the horrible \SitraAchras.
\Lethiarch-tachi would have no part in this evil worship of soul-corrupting, world-devouring macrocosmic madness.
So they fled (or were cast out, however one chooses to see it). 





\subsubsection{Founding of Uruthar}
\target{Uruthar founded}
They set up shop in the Shrouded Realms and built an underground city for themselves.
Here the Shroud was weak, so they could dwell here in peace and still have access to their powers.
(It was easier for a \bezed than for a pureblood to live inside the Shroud.)
It was easy to coerce the nearby \humans to serve and worship them.
So the \resphan outcasts founded the horrid kingdom of Uruthar. 
There they reigned as gods and devoured the flesh and souls of their worshippers. 

Aesthetically, they were a kind of \hr{Resphan vampire lords}{vampire lords}. 





\subsubsection{Uruthar driven underground}
In the millennia before \hs{Cordos Vaimon}, Uruthar would wage war against the rival nations of \hs{Yaru} and \hs{Tulya} and \hr{Nemaag}. 
And the \resphain would clash with the \hs{Cabal}, who resented having rogue \resphain running around and causing trouble and undermining the Cabal's authority over the \resphan race. 

Eventually the brave \scathae of Yaru and Tulya conquered the vile \humans. 
And the \resphain of Uruthar fought against the \draconian gods of the \scathae, and they fought with treachery and rage and the dark sorceries of the unplumbed void, but they prevailed not.

\target{Totems against Uruthar}
In the end the gods and men of Uruthar were overpowered. 
They withdrew to their dark caves under the earth, and the serpentine gods of the reptile folk cast mighty spells and erected mighty totems that forced the \resphain to huddle underground forever, for they had not the strength left to sunder the mighty spells of the reptilian gods.





\subsubsection{Shunned deeper tunnels}
\target{Shunned tunnels in Uruthar}
The people of Uruthar had lived underground for thousands of years, nourishing their hate. 
But there were deeper tunnels where they dared not go. 
There were dark entrances to tunnels that appeared to lead down.
These entrances were blocked up with stone and metal and carved with warding symbols.
People walked in great circles around these blocked entrances, superstitiously afraid to come near them. 
These were entrances to the Realm of \hr{Thessulax}{\Thessulax}, the \Dragon of Death, the charnel Queen of the Underworld.





\subsubsection{The gods of Uruthar died}
\target{Gods of Uruthar died}
\target{gods of Uruthar died}
One by one the gods of Uruthar were slain.

\target{Osra dies}
Finally only two \resphain were alive:
\hr{Lethiarch}{\Lethiarch} and \hr{Osra}{\Osra}. 
They waged war against each other. 
\Osra was the more powerful, and eventually \Lethiarch was forced to submit and surrender. 
\Lethiarch had sex with \Osra in order to prove her submission to him. 
But she betrayed him and knifed him while they were having sex.
She slew him. 
Then \Lethiarch was the last \resphan in Uruthar. 









\subsection{The Hills of Uldor}
\target{Uldor}
\index{Uldor}
In the time of \VizicarDurasRespina, the kingdom of dark Uruthar was lost to the mists of legendry. 
Only the hills of Uldor remained, marking the site of the heart of fallen Uruthar.
(The name \quo{Uldor} was a derivative of \quo{Uruthar}.) 

These hills were ill-reputed and feared in the region around them. 
The forest-covered hills were home to tribes of abominable, degenerate, half-\human barbarians. 
They would attack wayfarers, and they would raid nearby villages and steal food and livestock and even kidnap people. 
It was said that they ate their captives and/or sacrificed them to their wicked gods.

These barbarians were descendants of the \humans of Uruthar. 
They were now sunk deep into savagery. 
Many hundreds dwelt in the hills and in the subterranean city beneath them, but they were a feeble shadow of the kingdom's former glory.





\subsubsection{The hillmen had supernatural powers}
The people dwelling nearby had tried to defend themselves, but the slinking savages seemed to have supernatural powers. 
They could disappear in the forest and reappear anywhere they wanted, and they even seemed able to walk through walls. 

This was because the degenerates had had their brains twisted from centuries of dwelling underground. 
They had lost much of their sanity and humanity and intelligence, but had gained some new powers. 
They could see through the Shroud now, which enabled them to take shortcuts. 
But they were insane and retarded and depraved.

Nobles had tried to send soldiers into the hills to wipe out the hillmen. 
The soldiers were wiped out with treachery and poison and sorcery and awful monsters. 







































\chapter[The Scatha Age]{The \Scatha Age}















\section{Andras}
\target{Andras}
\index{Andras}
A kingdom southwest of \hr{Velcad}{\Velcad}. 
It borders the \hs{Imetrium}, \hs{Threll}, \hs{Ontephar}, \hr{Scyrum}{\Scyrum} and the \hr{Risvael Sea}{\Risvaelsea}. 
The Threll Mountains mark its northern border with Threll and the rivers Bron and \hr{Pylor}{\Pylor} mark its eastern border with \Scyrum{}. 

Andras is ruled by King Tiberius Andras. 
The kingdom is allied with the Imetrium, and the Imetric religion thrives alongside \hs{Iquinianism}. 





\subsubsection{Demographics and languages}
Languages and ethnic groups included \hr{Samurin}{\Samurin}, \hs{Imetric} and the occasional pockets of \hr{Tepharite}{\Tepharites} and \hr{Ortic}{\Orticans}. 















\section{Beirod}
\index{Beirod}
\target{Beirod}
A kingdom in the southern \hr{Velcad}{\Velcad}. 
It borders \hs{Pelidor} to the northwest, \hs{Runger} to the northeast, \hr{Scyrum}{\Scyrum}{} to the west (marked by Heropond Forest), \hs{Gaznor} to the south, the \Risvaelsea{} to the southeast and the \hs{Lorn Sea} to the east.  





\subsubsection{Demographics and languages}
Languages and ethnic groups included \hr{Velcadian language}{\Velcadian} and \hr{Ortic}{\Ortic}. 















\section{Belek}
\index{Belek}
\target{Belek}
A kingdom in western \Velcad{}. 
Belek is also the name of the royal house of the land. 
Its most famous member was \hs{Uther the Tiger}. 

Borders \hs{Sumian} in the south and \hr{Thyrin}{\Thyrin} in the north. 









\subsection{Lendamere}
\target{Lendamere}
\index{Lendamere}
The capital city of Belek. 















\section{Clictua}
\target{Clictua}
\index{Clictua}
A \hr{Meccaran}{\meccaran}-dominated kingdom in northeastern \hs{Uzur}. 
One of the largest known kingdoms in Uzur. 
It borders the \hs{Imetrium} to the north and \hr{Durcac}{\Durcac} to the east. 





\subsubsection{Demographics and languages}
The Clictua language is meant to resemble Nahuatl. 















\section{Geshiba}
\target{Geshiba}
\index{Geshiba}
One of the \hs{Northern Kingdoms}. 
It borders \hs{Rosval} to the west and the \hr{Serpentine Sea}{\Serpsea} to the east. 















\section{Gonarod}
\target{Gonarod}
\index{Gonarod}
A nation in northeastern \Velcad{}. 
It borders the \hs{Gwendor Sea} to the west, \hr{Marcil}{\Marcil} to the north and the \hr{Serpentine Sea}{\Serpsea} to the east. 















\section{\GreatVelcad}
\target{Great Velcad}
\index{\GreatBelkade}
A great dominated empire that existed from \yic{Founding of Belkade} to \yic{Fall of Belkade}. 
At the height of its power, it covered all the lands that are now \Velcad{}. 
The founder of the Empire was \hs{Cuthran the Victorious}, who became its first High King. 
The rulers of the Empire were the High Kings of House \Velcad. 

The Empire had strong ties to \hr{Telcra}{\ClanTelcra} from the beginning. 
They also had some ties to the Redcor. 

In \yic{Fall of Belkade}, the Empire collapsed for some reason. 
This shouldn't be too many years before our story begins. Perhaps only 5-10 years before Carzain is born. 
\also{\Velcadian{} (language)}





\subsubsection{Demographics and languages}
The official language of the Empire was \Velcadian{}, still spoken in large parts of \Velcad{}. 










\subsection{History}
\subsubsection{The fall of \theBelkadianEmpire}
It is still unclear and mysterious what actually happened at High King \ps{\LastHighKing} court. 

Perhaps \LastHighKing{} or his court Vaimons found out about the \Charade{} and the underground war, and acted to foil the factions' plans. 

Perhaps \LastHighKing{} or one of his advisors was planted by the \cuezcans{}. If so, he is still alive (or maybe undead) and at large, working underground to oppose the warring factions. 

Moro \Cornel, the Pelidorian archmage, might be in league with the fallen High King\ldots{}

The \hr{Kezerad}{\Kezeradi} might have had a hand in the fall of the Empire.

It might have had to do with \hr{Semiza}{\Semiza}. 





\subsubsection{\Velcad{} today}
\Velcad{} should be divided into a small number of large kingdoms, each of which is subdivided into multiple duchies, baronies and whatnot. Pelidor is one of the latter. 

The kingdoms need to be bigger so we can have bigger armies and wars on a more epic scale. 










\subsection{Noble titles}
\target{noble titles}
\index{noble titles}
The noble titles used in \Velcad{} include:

\begin{gloss}
  \gitem{King} 
    Used by some sovereign rulers, but not all. 
  \gitemnoindex{\Rayuth{}} 
    Was a vassal lord's title in \GreatVelcad. 
    Comparable to a duke. 
    After the fall of \GreatVelcad, some now-sovereign rulers retained the title. 
  \gitemnoindex{\Rinyuth{}}
    The husband or wife of a regent \rayuth{}. 
  \gitemnoindex{\Scarv{}}
    Below a \rayuth{}. 
    Comparable to a count. 
  \gitemnoindex{\Rah{}} 
    Used for \hs{knights}. Equivalent of \quo{sir}. 
\end{gloss}

Some of these titles are suffixed to names: 
\Rayuth[\Icor] Pelidor, \rah[\Sethgal] Pelidor. 








\subsubsection{High King}
\target{High King}
\index{High King}
\quo{High King} was the title taken by the kings of \theBelkadianEmpire. 
The first High King was \hs{Cuthran the Victorious}. 
The High Kings belonged to House \Velcad. 

A High King's wife was called High Queen. The Empire never had a ruling High Queen.















\section{Hazid}
\target{Hazid}
\index{Hazid}
A nation in the Near Orient, near Geica. Ruled by a Sultan. 















\section{Kochu}
\target{Kochu}
\index{Kochu}
A \hr{Meccaran}{\meccaran} nation in northwestern \hs{Uzur}. 





\subsubsection{Demographics and languages}
The Kochu language is meant to resemble Japanese. 
















\section{\Marcil}
\index{\Marcil}
\target{Marcil}
A nation in northeastern \Velcad{}. 
It borders \hr{Redce}{\Redce} to the west, \hs{Rosval} to the north, \hs{Gonarod} to the south and the \hr{Serpentine Sea}{\Serpsea} to the east. 









\subsection{Bendaire}
\target{Bendaire}
\index{Bendaire}
A city in \Marcil. 
















\section{Ontephar}
\index{Ontephar}
\target{Ontephar}
A kingdom in southern \Velcad{}. 
It borders Pelidor to the south, Runger to the east and \hr{Scyrum}{\Scyrum}{} to the south-west. 
It is ruled by an Archduke. 
Ontephar was previously the heartland of \hr{Tepharae}{\Tepharae}. 

Its capital city is \Tephar. 





\subsubsection{Demographics and languages}
Languages include \Velcadian{}, \Tepharin{} and occasionally Imetric.















\section{Pelidor}
\target{Pelidor}
\index{Pelidor}
A duchy in the central \hr{Pelidor Continent}{\PelidorContinent}.



\lyricstitle{Draft excerpt from the chapter \quo{What Slithers Beneath}}{
  Their path had led near to the centre of the city. The colossal \CastlePelidor{}\dash home of the \rayuth, ruler of Malcur and of all Pelidor\dash was visible even from the slums, looming forebodingly in the distance as a reminder of all that separated the lowlives from their highborn lords. But here, it towered over everything. Even though it was still distant and would take a long walk to reach\dash Rian guessed a thousand paces or more\dash, already its white marble walls seemed to span almost the entire horizon. Immense towers rose up to touch the sky, their brass-coated roofs gleaming like small suns. 
  Friezes and statues adorned the walls, of armoured knights, angels, beasts and dreadful monsters; some of them huge, many times taller than a man. 
  Rian found himself in the line of sight of a giant angel of marble\dash androgynous, winged, brandishing aloft a flaming sword, as if to strike with righteous anger down upon the thief's sinful head. He hurried on, eager to put some buildings between him and the avenging stone angel. 
}





\subsection{Demographics and languages}
\target{Pelidorian demographics}
\target{Pelidorian language}
The main language spoken in Pelidor was Pelidorian. 
It was related to \Ortaican and \Tepharin. 

Almost the entire nobility was \scathaese. 
Most slaves (but not all) were \humans.

Before the \thirdbanewar Pelidor had a population of maybe 500,000 to 1,000,000 people. 
It had a standard \hs{urbanization} of about 20\%. 







\subsection{House Pelidor}
\target{House Pelidor}
\index{House Pelidor}
\index{Pelidor!House Pelidor}
House Pelidor, a \scathaese{} noble family of \Tepharin{} descent, are the current rulers of \Malcur and the nation of Pelidor. 
Their head carries the title of \quo{\rayuth}.

The Pelidors were once worshippers of a group of lost gods (the Dreaming Gods?), perhaps \Tepharin{} gods. 
They were keepers of the occult secrets of what lay hidden underneath \Malcur. 
Charged to ensure that what lay beneath would not be awakened. 

But when the \Velcadians{} invaded, most of the Pelidors were killed as dangerous heretics and heathens, and a child prince was made \rayuth, now a \Velcadian{} vassal. The country was forcibly converted to the Iquinian faith and the secrets of \Malcur were lost. Many records were destroyed because the people should not know that kind of heresy. 

\Tiroco{} is also of House Pelidor. She is \ps{\Icor} half-cousin. She knows nothing of her family's legacy. 

But the secrets are not all forgotten. A select few keepers among the Pelidors have been handing down oral remembrance\dash always behind the \rayuth's back\dash all the while doing research and trying to rediscover more. 

Liocai Pelidor, the sister of \rayuth[\Icor], is one such keeper. She knows a shocking amount of things. Things that even the Sentinels don't know. 
 
This might be a good place to tie in the story of the mysterious fall of \hr{Great Velcad}{\theBelkadianEmpire}. 









\subsubsection{Symbol: \Grulcan}
\target{Pelidor symbol}
The symbol of House Pelidor is a bronze-\\coloured \hr{Grulcan}{\grulcan} bird on a blue background. They also \hr{Pelidorian war Grulcans}{use \grulcans{} as beasts of war}. 









\subsection{House Turmalin}
The second-most powerful noble house in Pelidor, after House Pelidor. 
They control much of southern Pelidor. 

Their head is Viscountess Osphal Turmalin. 

Their symbol is three parallel black spears on an orange background. 









\subsection{Besuld}
\index{Besuld}
\index{Pelidor!Besuld}
A port city in southeastern Pelidor. 











\subsection{Dendrum}
\index{Pelidor!Dendrum}
\index{Dendrum}
\target{Dendrum}
A city in eastern Pelidor. 
Lies on the \hs{Ucarn}, approximately halfway between \hr{Forclin}{\Forclin} and \hs{Ucarnum}. 











\subsection{Equipment and creatures}






\subsubsection{\Grulcans}
\target{Pelidorian war Grulcans}
The \hr{Pelidor symbol}{symbol of house Pelidor} is a \hr{Grulcan}{\grulcan} bird. 
They tame these birds and use them as beasts of war. 
The bird also live in the \wylde in Pelidor and surrounding lands. 









\subsection{\Forclin}
\target{Forklin}
\target{Forclin}
\index{Forklin}
\index{Pelidor!Forklin}
A city in northern \hs{Pelidor}.
It was built by the \hr{Ortaican}{\Ortaicans}. 

In accordance with \hs{Pelidorian demographics} and standard \hs{urbanization}, \Forclin might have had a population of 12,000 to 20,000 before the war with Runger.

It was built on top of the ruins of an ancient \resphan{} fortress, of which the \hs{Ghost Tower} was the only surviving remnant. 

Describe the colossal walls and towers of \Forclin.
It was a majestic city, but dark and mystical. 
To the eyes of an Iquinian it was not as nice and clean as the Vaimon-built \Malcur. 
It was more martial and barbaric and sorcerous and intimidating. 

But it was much younger than \Malcur. 
Only the Ghost Tower was truly ancient. 

The gargoyles on the walls were magical.
Maybe they could spit fire or napalm or other nasty stuff. 
Some gargoyles crawled on the walls, others sat on top of them. 

\citeauthorbook[p.24]{RobertEHoward:TheShadowKingdom}{Robert E. Howard}{%
  The Shadow Kingdom%
}{
  The \colour and the gayety of the day had goven away to the eery stillness of night.
  The city's antiquity was more than ever apparent beneath the bent, silver moon. 
  The huge pillars of the mansions and palaces towered up into the stars.
  The broad stairways, silent and desrted, seemed to climb endlessly until they vanished in the shadowy darkness of the upper realms.
  Stars to the stars, thought Kull, his imaginative mind inspired by the weird grandeur of the scene. 
  
  Clang! clang! clang! sounded the silver hoofs on the broad, moon-flooded streets, but otherwise there was no sound.
  The age of the city, its incredible antiquity, was almost oppressive to the king; it was as if the great silent buildings laughed at him, noiselessly, with unguessable mockery.
  And what secrets did they hold? 
  
  \ta{You are young,} said the palaces and the temples and the shrines, 
  \ta{but we are old.
    The world was awild with youth when we were reared.
    You and your tribe shall pass, but we are invincible, indestructible.
    We towered above a strange world, ere Arlantis and Lemuria rose from the sea; we still shall reign when the green waters sigh for many a restless fathom above the spires of Lemuria and the hills of Atlantis and when the isles of the Western Men are the mountains of a strange land.
    
    How many kings have we watched ride down these streets before Kull of Atlantis was even a dream in the mind of Ka, bird of Creation? 
    Ride on, Kull of Atlantis; great shall follow you; greater came before you.
    They are dust; they are forgotten; we stand: we know; we are. 
    Ride, ride on, Kull of Atlantis; Kull the king, Kull the fool.}
  
  [\ldots]
  
  Glow, moon: you light a king's way.
  Gleam, stars; you are torches in the train of an emepror!
  And clang, silver shod-hoods; you herald that Kull rides through Valusia. 
}









\subsection{Ghost Tower}
\target{Ghost Tower}
\index{Ghost Tower}
\index{Pelidor!Ghost Tower}
A spooky tower in \hr{Forclin}{\Forclin} in \hs{Pelidor}

There are a bunch of ancient ruins near the Ghost Tower\dash parts of a larger complex, of which the tower is the only complete remnant. 






\subsubsection{\Haskelek{} myth}
\target{Haskelek myth}
There are myths about how there allegedly lies a terrible \daemon{} imprisoned somewhere in the Ghost Tower\dash a \hr{Haskelek}{\Haskelek}. 





\subsubsection{Haunted}
\index{\succubus}%
It is probably haunted by monsters. 
These monsters could only rarely get through the Shroud before, but it is getting easier now with the \hs{unravelling}. 
Every now and then they manage to slink out of the Beyond and eat some people from \Forclin. 
Or lure the people to them, \hr{Succubus}{\succubus} style. 





\subsubsection{History}
\target{Ghost Tower history}
Many people assume the Tower is Vaimon-built, since it is older than the \Ortaican{} buildings around it. 
After all, the Vaimon age was long and featured diverse building styles. 
But this is actually not true. 
The Tower and the ruins are \resphan-built.
The Tower was originially the central tower of a larger fortress complex, but the rest has since decayed. 
The Tower, being virtually indestructible, has remained, but is now empty and abandoned. 





\subsubsection{Invisibility}
The Tower is invisible from within \Forclin, because the people repress the fact that it exists. 
Their collective denial creates a Shroud that renders it invisible, even to outsiders. 

The Tower can be clearly seen from outside \Forclin, though. 
Out there the Shroud of Civilization does not hold the same sway. 

When you are up close to the Tower, it can be seen. 
It stretches up above, but after about 5-10 metres it gets shrouded in fog so that you can't see the top or estimate how tall it is. 
It is actually over 100 metres tall. 





\subsubsection{Mystic lake}
\target{Mystic lake near the Ghost Tower}
Maybe there is a mystical, magical lake near the Tower. 
There might be \hr{Mystic lake in Malcur}{a similar lake in \Malcur}.

Compare to Lake Hali in \RWCTKIY. 





\subsubsection{Portal to \Nyx}
\target{From Ghost Tower to Nyx}
The upper levels of the Tower submerge into \Nyx. 











\subsection{Gilwaed}
\index{Pelidor!Gilwaed}
\index{Gilwaed}
\target{Gilwaed}
A village in eastern Pelidor, north of the \hs{Ucarn}, somewhere between \hr{Forclin}{\Forclin} and \hs{Ucarnum}. 
The name is \Tepharin. 

Population: Approximately 100 \scathae. 











\subsection{Kenshaer}
\index{Pelidor!Kenshaer}
\index{Kenshaer}
\target{Kenshaer}
A \hr{Wild}{\Wylde} forest in eastern Pelidor, north of the \hs{Ucarn} between \Forclin{} and \hs{Dendrum}. 









\subsection[Malcur]{\Malcur}
\target{Malcur}
\index{\Malcur}
\index{Pelidor!\Malcur}
\Malcur was the capital city of Pelidor, ruled by House Pelidor from Castle Pelidor in the heart of \Malcur. 

\Malcur was an ancient city. 
\CastlePelidor was built by Vaimons, not long after Cordos's time.

And the catacombs beneath were are thousands of years older. 
They were disused and forgotten, and the Pelidors barely remembered that they existed. 





\subsubsection{Ancient history}
\target{Ancient history of Malcur}
\Malcur was originally a \hr{Wild}{\Wylde}{} stronghold, and the crypts date back to this time. Or maybe it was built on top of a \xzaishann{} tomb, containing powerful arcane glyphs and spells forming a part of the seal that separates \Machai{} (the \hr{Wild}{\Wylde}{} homeworld) from \Miith\dash the very spells that formed the first foundation of the Shroud. The magic of these seals can be tapped for other purposes and used to weave the Shroud, making \Malcur and its underground a potent \nexus{} point. 

Some terrible power lies entombed beneath \Malcur. After the \Darkfall, someone attempted to release this power, but it failed. House Pelidor took over the castle and have been its stewards ever since. 

\hr{Teshrial's creatures}{\ps{\Teshrial} terrible monsters} are connected to \Malcur's mystic past somehow.





\subsubsection{Black Plague}
\index{Black Plague}
\index{plaguer}
\target{Black Plague}
\target{plaguers}
A thieves' guild in \hr{Malcur}{\Malcur}. 
Rumoured to have dealings with sorcerers. 
Their members are sometimes nicknamed \quo{plaguers}. 





\subsubsection{Churches and mausolea}
\Malcur had a great \Telcra{} cathedral and a smaller Redcor church, each with a mausoleum attached. 
These mausolea were huge. 

There was also a smaller Imetric church. 





\subsubsection{Description of the scenery}
The great buildings of \Malcur, including the city walls, guard towers and the central \CastlePelidor, are built of shining white stone\dash think of a name for this fictional type of stone. 

It has plenty of \hr{Monuments}{monumental structures}. 
In many places it is adorned and embossed with pink quartz and black opals. And there are enormous statues, obelisks, gargoyles or \hr{Iquinian angels}{angels}, friezes on the walls, ornate cathedrals and towers, and a behemoth central castle.

Describe it so it sounds exotic, epic and Bal-Sagoth-like. Almost like Kor-Avul-Thaa (but not quite).

\Malcur is built utilizing a lot of \hr{Occult geometry}{occult geometry}. 





\subsubsection{Rich and poor quarters}
\target{Malcur rich and poor}
\Malcur has a rich quarter, the High City, and a poor quarter, the Low City. 

The High City is made of very tall houses, palaces and towers. There are bridges between the towers so that the rich need never tread on the filthy ground where the poor live. 

The Low City spans everything from comfortable craftsmen to the worst slums. \hs{Rian} lives here.

There was an inner city, encircled by walls, which was mostly safe from monsters, and an outer city outside the walls, with only walls and \eidola for protection.
The slums were, of course, outside.

The inner city was very densely populated and crowded, since everyone who could afford it wanted to live there.
So there were also slum-like places in there. 





\subsubsection{Recent history}
\Malcur has never fallen in war and never been taken in a siege. At least, not since the Vaimons destroyed the city and rebuilt it. When the \Velcadians{} invaded, the \rayuth of Pelidor surrendered peacefully after lengthy negotiations. 





\subsubsection{\Nexus{} status}
\Malcur is an important \nexus{}. This is why \hr{Teshrial's creatures}{\Teshrial{} has brought \ghobaleth{} to \Malcur}. 

Perhaps these \ghobaleth{} have been there for thousands of years, or have gradually dug their way to \Malcur from Erebos over the course of thousands of years. 

But apart from the \ghobaleth, there is also \hr{Wild}{\Wylde}{} darkness lurking beneath \Malcur. And perhaps degenerate creatures who live in caves underground and worship them. 

Maybe there dwell degenerate \troglodytes, digging tunnels under the crypts and worshipping their detestable gods, perhaps including \dragons.Or perhaps these are \nagae, living in undergound lakes and the like.





\subsubsection{Dead garden}
\target{Dead garden in Malcur}
\target{dead garden}
\index{\Malcur!dead garden}
Somewhere in the centre of \Malcur, near Castle Pelidor (but not too near), there lies a garden of crooked, dead trees. 
It is one of the mystic centres of the city, somehow connected with \Malcur's occult past. 

The twisted trees are black and gray, leafless and withered-looking. They look dead, but they are alive. They radiate some kind of malice, and people steer clear of them. Only this one strange old woman lives near them. 

In or near the garden there lives a \hs{crazy old woman}. 
She knows quite a lot about the Beyond and the supernatural, but is also quite \hr{Madness}{mad}.

The garden is inspired by the Azath house and cemetery in \cite{StevenErikson:MidnightTides}. 

The dead garden is a small patch of \wylde in the middle of the city, which everyone tries to forget about (because otherwise they would be living in fear of it all the time).

The garden is the core of the \nexus. It is here that one can most easily feel the \hr{Teshrial's creatures}{worms}. 

Despite their wicked look and feel, the trees are not necessarily evil, although they may tend to be inimical to humanoids. They possess some measure of natural power and wisdom. The crazy old woman can hear their thoughts (because she is mad and more free from the Shroud), and she relays their warnings to anyone who will listen (which is not many). The twisted trees may not love humanoids, but they fear the \ghobaleth{}, and they fear \Nithdornazsh.

The Shroud is thin in the garden. 
This allows the immortals to use their full powers there, \hr{Immortals inside the Shroud}{which would otherwise be impossible}.

\lyricsbalsagoth{
  In the Raven-Haunted Forests of Darkenhold, Where Shadows Reign and the Hues of Sunlight Never Dance
}{
  Can you not see the coils of the worm all about you?\\
  Can you not hear the writhing of the worm beneath you?\\
  Can you not scent the breath of the worm riding the wind?\\
  Can you not touch the skin of the worm in all that surrounds you?\\
  Can you not taste the ichors of the worm upon your tongue?\\
  Do dreams of the worm not haunt your slumber?
}

There is a \hr{Wylde border}{\Wylde{} border} around the dead garden. 
It is, after all, a small patch of \wylde{} in the middle of \Malcur.
    
The dead garden is twisting and crawling with chaos.
It is monstrous and haunted.
Being \wylde, the garden twists and mutates.
Paths are never the same.

When describing the garden, remember to see the section about the \hr{Wylde}{\wylde}, and especially the one on \hr{Travelling through the Wylde}{\travelling through the \wylde}. 

There was a great hole in the middle of the dead garden.
Simply called \quo{the hole}. 
Not capitalized. 
The dead garden and things in it did not have names. 

The hole appeared to be bottomless and just went on down in the darkness. 
It was a passage into the Beyond. 

In the foremath of the \thirdbanewar, \Ishnaruchaefir tried to use the hole as a passage into \Azmith. 

\citeauthorbook[p.196]{RobertEHoward:SwordsofthePurpleKingdom}{Robert E. Howard}{%
  Swords of the Purple Kingdom%
}{
  But as night fell and the shadows merged, Delcarted grew nervous.
  The night wind whispered grisly things through the branches and the broad palm leaves and the tall grasses and the stars seemed cold and far away.
  Legends and tales came back to her, and she fancied that above the throb of her pulsing heart, she could hear the rustle of unseen black wings, and the mutter of fiendish voices. 
  
  \ldots 
  
  She stole along a broken pave, and the whispering palm leaves brushed against her like ghostly fingers.
  About her lay a pulsation gulf of shadows, vibrant and alive with nameless evil.
  There was no sound.
}







\subsubsection{Mystic lake}
\target{Mystic lake in Malcur}
\target{Lake in Malcur}
Maybe there is a mystical, magical lake near the garden. Maybe it lies between the garden and \CastlePelidor. 
There might be \hr{Mystic lake near the Ghost Tower}{a similar lake near the Ghost Tower}.

Compare to Lake Hali in \RWCTKIY. 









\subsection{Politics}





\subsubsection{\Meccaran conscripts}
The Pelidorian army can draft some local tribes of \meccara{} that live in eastern Pelidor. 
They are mostly independent, but nominally they owe allegiance to the \rayuth. 
They are employed as guerillas, since they know the terrain. 

The various tribes each speak their own languages, and only few understand \Velcadian{} or \Tepharin. 
They are ill-integrated and have little love for the \rayuth or \rinyuth or whatever. 
They have their own languages and cultures and customs and do not feel like a part of Pelidor. 









\subsection{\Redglen}
\target{Redglen}
\index{\Redglen}
\index{Pelidor!\Redglen}
A town in eastern Pelidor, near \hs{Heropond Forest} and west of \hs{Torgin}. 
It is the hometown of \hr{Carzain}{Carzain \Shireyo} and his family. 









\subsection{Sulcanum}
\target{Sulcanum}
\index{Sulcanum}
\index{Pelidor!Sulcanum}
A city north of \Malcur. 
Ruled by the family of \hs{Sethgal Pelidor}. 









\subsection{Torgin}
\target{Torgin}
\index{Torgin}
\index{Pelidor!Torgin}
A city in southern Pelidor, east of \Redglen. 









\subsection{Ucarn}
\target{Ucarn}
\index{Ucarn}
A river in eastern \hs{Pelidor}. 
Runs from \hr{Forclin}{\Forclin} in the west out to the port city of \hs{Ucarnum} at its mouth in the east, where it meets the (much wider) \hs{Nerim}. 









\subsection{Ucarnum}
\target{Ucarnum}
\index{Ucarnum}
A city in eastern \hs{Pelidor}. 
Lies at the mouth of the river \hs{Ucarn} where it runs into the \hs{Nerim}. 















\section{Rosval}
\target{Rosval}
\index{Rosval}
One of the \hs{Northern Kingdoms}. 
It borders the \hs{Gwendor Sea} to the west, \hr{Redce}{\Redce} to the southwest, \hr{Marcil}{\Marcil} to the south, the \hr{Serpentine Sea}{\Serpsea} to the east and \hs{Geshiba} to the northeast. 















\section{Runger}
\target{Runger}
\index{Runger}
A kingdom in central \hr{Velcad}{\Velcad}. 
It borders \hs{Beirod} to the south, \hs{Pelidor} to the west (marked by the river \hs{Nerim}), the \hs{Gwendor Sea} to the north and the \hs{Lorn Sea} to the east. 

%It borders the Hirum Gulf to the northwest, Pelidor to the southwest and Beirod to the south. 

It is ruled by the kings of House Runger. 
The current ruler is \hr{Morgan Runger}{King Morgan I son of Uther I}. 
Morgan has two daughters but no sons, so the heir to the throne is Prince Matthias, the husband of Morgan's eldest daughter, Estelle. Recently, King Morgan has allied himself with the Rissitics and plots to conquer Pelidor and perhaps other nearby kingdoms as well. 

The banner of Runger is two brown wolverines chasing each other in a circle, against a tan background.









\subsection{Demographics and languages}
\target{Rungeran language}
The main language spoken in Runger was Rungeran. 
It was a \human language resembling English. 

Or maybe they spoke the \hr{Vidran language}{same language as in \Vidra}.









\subsection{Dormina}
\index{Dormina}
Capital city of Runger. 









\subsection{\EreshKal}
\target{Eresh-Kal}
\index{\EreshKal}
A \meccaran{} civilization that once existed in modern-day Runger. Allegedly, a lost \EreshKali{} temple lies hidden in \hs{Waythane Forest}.  









\subsection{Gedrock}
\target{Gedrock}
\index{Gedrock}
A village in Runger, near \hs{Waythane Forest}. 









\subsection{Manburg}
A city in Runger. 









\subsection{Waythane Forest}
\target{Waythane Forest}
\index{Waythane Forest}
\index{Runger!Waythane Forest}
A large forest in southern Runger. Allegedly hides the last temple of \hr{Eresh-Kal}{\EreshKal}. 















\section[Scyrum]{\Scyrum}
\target{Scyrum}
\index{\Scyrum}
A kingdom southeast of \Velcad{}. 
Borders the Imetrium to the south, near Martinum, and borders Pelidor to the north-east. 
Much of the eastern part of the kingdom is made up by the large Heropond Forest. 

The capital city is \hr{Pylandos}{\Pylandos}. 
Other cities include Icconos. 





\subsubsection{Demographics and languages}
Languages and ethnic groups include \Tepharin, \Samurin{} and \Ortic. 









\subsection{\Bryndwin}
\index{\Bryndwin}
\target{Bryndwin}
A village in eastern \Scyrum, near \hs{Heropond Forest}. 









\subsection[Pylandos]{\Pylandos}
\index{\Pylandos}
\target{Pylandos}
Capital city of \Scyrum. 















\section{Shamanistic cultures}
\target{Shamanistic magic}
\index{Shamanism}
Shamanism is a religion, or, more properly, a collective term for a class of religions, practiced primarily by the \meccaran{} tribes, but also in some communities of other creatures. %as well as some communities of Humans. A few communities of Scathae have adopted Shamanistic beliefs, and some Troglodytes practice religions similar to Shamanism. 

Shamanism exists in many diverse forms and is not in any way a centralized or even homogeneous religion. Some forms of Shamanism are very peaceful (or even pacifist) and resemble Animism\footnote{Needless to say, my usage of the terms \quo{Shamanism} and \quo{Animism} in a \Miithian{} context is meant to be similar to, but also different from, the RL religions of the same name. In RL, shamanism is perhaps more properly considered a form of animism than merely something similar.}, wheras others are very dark and sinister, employing \quo{black} magic and consorting with monstrous powers. 

Shamanism is based on the belief that the world is full of spirits, that all things have a soul. Shamanistic magic works by communing with and influencing these spirits. 

Beliefs include: 

All people, animals and things have a soul. These souls can be communed with, and done other stuff to\ldots{} 

%Shamanistic magic is a tradition used primarily by the \meccaran{} tribes, especially in Uzur, but also in the Middle Lands. It is often considered primitive and barbaric by other cultures, and it is true that most Shamans have little theoretical understanding of how their magic works. Still, the Shamans are not to be underestimated, for their magic can be very effective. 

%Some aspects of Shamanistic magic and religion: 

There are Shamans and Witch-Doctors. (The distinction is not always rigid.) A Shaman is a religious authority whose magic is seen as something holy. A Witch-Doctor is an alienist who deals with dark, occult powers. He is primarily a mage, and perhaps secondarily a priest. In many tribes, Witch-Doctors are feared and mistrusted (but they are usually still there, because their magic is potent). 









\subsection{Examples of cultures}
Shamanistic cultures include: 

\begin{itemize}
  \item \hs{Clictua}. 
  \item \hr{Goyden}{\Goyden}. 
  \item \hs{Kochu}. 
\end{itemize}









\subsection{Shamanistic magic}
Shamans usually cannot cast \quo{spells} in a regular sense. Their magic relies either on rituals or on herbs and drugs. Witch-Doctors can usually cast regular spells. 

Their rituals revolve around dance and music. Some spells can be performed by the Shaman alone, but most require many people. 

\Meccaran{} singing usually uses a chanting choir and a lead singer. The chanting is rhythmic but not melodic. It may be with understandable words, strange, magical words or just nonsense. A lead singer is typically a shaman. \Meccaran{} lead singing is high-pitched and screaming, often wild and ecstatic. This often sounds extremely chaotic and un-musical to outsiders. 

Typical rituals are war dances, hunting dances and exorcisms. 

In a hunting ritual, the people seek out the great spirit of the prey animal. In some interpretations, the shaman peacefully communes with the spirit and obtains permission to kill some of the animals (this is granted because it is the nature of prey animals to get eaten). In other interpretation, the shaman duels with the spirit and takes his \quo{permission} by force. 

In a war ritual, the people seek out the guiding spirit of their enemies and combat it. If successful, the enemy is weakened and the tribesmen get bonuses to fight them. 

They eat the bodies of their dead (under a magic ritual), so that their souls return to the tribe. 

They eat the bodies of their enemies (under a different ritual) to gain their strength. (Only the blood and important organs, especially the heart and brain, have occult properties. The rest of the body is just eaten for nourishment.) 

Living people may drink each other's blood in a ritual, or even eat each other's flesh\footnote{For a \meccaran, it is easy to remove a finger or so, since it will regenerate.}, creating an arcane blood bond between them. 

Warriors have a totem animal and draw power from it. 

They use drugs a lot, to help the soul wander and to access spiritual power. Warriors sometimes take drugs to go berserk. 









\subsection{Shamanistic spells}
%Some sample spells: 

Here is a list of sample Shamanistic spells. Note that since Shamanistic communities are a very heterogeneous group, any given Shaman or Witch-Doctor need not have access to all of the spells below. 

\spellsha{Control Weather}
Shamans can control the weather to a limited extent. Requires a tribal ritual. 

\spellsha{Curse of Despair}
Causes depression and despair in the victim. 

\spellsha{Curse of Sloth}
Makes the victim lazy. 

\spellsha{Curse of Disease}
Causes disease\ldots{} 















\section{Sumian}
\target{Sumian}
\index{Sumian}
A nation in eastern \hr{Velcad}{\Velcad}, east of the \hs{Lorn Sea} and west of the \hr{Serpentine Sea}{\Serpsea}. 
Borders \hs{Belek} in the north. 















\section[Thyrin]{\Thyrin}
\target{Thyrin}
\index{\Thyrin}
A nation in eastern \hr{Velcad}{\Velcad}, east of the \hs{Lorn Sea} and west of the \hr{Serpentine Sea}{\Serpsea}. 
Borders \hs{Belek} in the south. 















\section{\UltimaThule}
\target{Ultima Thule}
\target{Thule}
\index{\UltimaThule}

\UltimaThule was an Immortal Realm. 
It was cold and full of ice.
It was closer to the \CrystalSphere than most any other place in \Miith, and a particularly good place for the \banelords to exert their influence, and for \Miithians to contact them or to draw power from Erebos.
The \resphain feared and disliked the place (just as they feared the \banelords), so while they had bastions there, they did not like to spend time there. 

It was to \UltimaThule that \hr{Ramiel journeys to Thule}{Ramiel journeyed to regain his memory and power}. 

The nothern regions of \Azmith gradually transitioned to \UltimaThule.
The lands were full of monsters and cold magic.
The inhabitants (\human or \scatha) were fierce barbarians who prayed to dark gods. 
Not only the \banelords had influence, but also the \xs. 
The Shroud was thin in the north, because the land gradually transitioned to an Immortal Realm. 

\Gnomphilim dwelt here. 

The Realm was ruled by cold, sleeping Ice-Gods (who might be \xss or \dragons) and cruel, cold \hs{Vampire Lords} or \quo{Cold Wraiths}. 

There were also \quiljaaran that dwelt there. 

In \UltimaThule one could feel the cold winds of darkness from Erebos.
They spoke of desolation, despair and entropy.

\lyricsbalsagoth{
  Starfire Burning Upon the Ice-Veiled Throne of Ultima Thule
}{
  The grim Ice-Gods sleep in these frost-bound tombs,\\
  illumined by the caress of lunar fire\\
  and the kiss of star-gleam from the Stygian void.
}

\citebandsong{Arcturus:AsperaHiemsSymfonia}{Arcturus}{
  To Thou That Dwellest in the Night
}{
  Here is so desolate;\\
  Times, they are dark\\
  Words ceas'\\
  to end as echoes rolling afar\\
  Empathy asseth\\
  whilst thou drapest this world in black;\\
  The only \colour that can paint my soul
  
  Clad in the shades of night\\
  Thou reflectest the pure of heart
  
  Amidst all the grief this winter unfoldeth\\
  The thorn in my side\dash{}thou retainest\\
  Thy breeze maketh me shiver\\
  Maimeth me with its frozen malice
  
  Thou minglest with the dense night\\
  I hearken to the voice of thy winds\\
  They are the saddest of all sounds of thine\\
  Never will I take leave from thy haunt
  
  Hast thou ever desired me?\\
  I receive no answer, \\
  thou letst it pass in silence\ldots{}
}















\section{\Vidra}
\index{\Vidra}
\target{Vidra}
A kingdom in northern \Velcad{}. 
\hr{Great Velcad}{\GreatVelcad}, during its time, was ruled from \Vidra{} by the \hr{High King}{High Kings} of House \Velcad. 
House \Velcad{} still rule the kingdom of \Vidra, but they no longer use the title High King. 
\also{\hs{High King}, \hr{Great Velcad}{\GreatVelcad}}









\subsection{Demographics and languages}
\target{Vidran language}
The main language spoken in Vidran was Vidran. 
It was a \human language resembling English. 

Or maybe they spoke the \hr{Rungeran language}{same language as in Runger}.















\section{\Yormis}
\target{Yormis}
\index{\Yormis}
\Yormis was an \Ortaican city.
After the fall of \Ortaica and the rise of \Iquinian \Tepharae, \Yormis did not surrender and remained a bastion of \hr{Rethyax}{\rethyaxes} that maintained the \Ortaican religion.
It became known as a dark city of sorcerers, and there were many unwholesome rumours about them.









\subsection{Appearance}
There were some dark, scary catacombs underneath \Yormis.
These led to \KaiLeng where dwelt \Ubloth and \Thessulax. 

\citeauthorbook[p.225]{RobertEHoward:HouroftheDragon}{Robert E. Howard}{%
  Hour of the Dragon%
}{
  He followed his awful guide through blackness that loomed before and behind them and was filled with skulking shapes of horror and lunacy that cringed from the blinding glow of the Heart.
}









\subsection{Geography}
\Yormis lay in northern \Velcad, near Pelidor.

It lay near the mountain of \hr{Shrun}{\Shrun}.





\subsubsection{\Shrun}
\target{Shrun}
\index{\Shrun}
\Shrun was a mountain upon whose slopes \Yormis was built.
The founders built their city here for two reasons:
\begin{enumerate}
  \item 
    The mountain was full of valuable ore for them to mine.
  \item 
    It was a great defensive position. 
    The mountain was covered in dangerous \wylde infested with \hr{Werloc}{\werlocs}. 
    (The people of \Yormis greatly feared these \werlocs.)
\end{enumerate}


Under the mountain was a system of tunnels that led down into the underworld of \hr{Kai-Leng}{\KaiLeng}. 
Here dwelt the \xs godling \hr{Ubloth}{\Ubloth}.





\subsubsection{Well}
\target{Well in Yormis}
Near Mount \Shrun there lay a \quo{lake} or \quo{well} of viscous black slime. 
The slime was an emanation of the loathsome god \hr{Ubloth}{\Ubloth}. 
By touching the slime, drinking it or submerging into the well, one could commune with \Ubloth and learn its secret \arcana. 

\citeauthorbook[p.103]{RobertEHoward:TheScarletCitadel}{Robert E. Howard}{%
  The Scarlet Citadel%
}{
  \ta{%
    [Tsotha] did descend into a well he found, and came out with a strange expression which has not since left his eyes.
  
    I have seen that well, but I do not care to seek in it for wisdom. 
    I am a sorcerer, and older than men reckon, but I am human.}
}









\subsection{Culture}
\target{Cults in Yormis}
\Yormis was ruled by a bit of an anarchy of cults and mage-schools.
Some worshipped the \Ortaican gods.
Others worshipped darker powers, such as \Ubloth (\hr{Ubloth cult}{who had a cult there}).
A few knew that the \Ortaican gods were \xss.
The Dark Crescent had much power in \Yormis.









\subsection{Equipment}





\subsubsection{Mummies}
\target{Mummies in Yormis}
Beneath \Yormis were catacombs full of mummies. 
Most of them were mortal \scathae, dating from \Ortaican times or from the first \Yormis. 

A few of the mummies were ancient \hr{Ophidian mummies}{\ophidian mummies}.
Most of those were from the first \Yormis, but a few were true ancients who had lain in Durance for a million years. 
These Elders were donated by \Thessulax from her mummy-filled tomb. 

The mummies were \hr{Ophidian mummy worship}{worshipped} because they could still impart wisdom. 









\subsection{History}





\subsubsection{Age of Chaos}
In the \quo{\hs{Age of Chaos}}, \Yormis was the site of an \ophidian city, ruled by \hr{Thessulax}{\Thessulax} from her tomb-citadel in \KaiLeng.

This city was destroyed by Cordos Vaimon. 
With \hr{Early Vaimons overpowered}{their superpowers in those days}, the early Vaimons were a match even for \ophidians. 





\subsubsection{Vaimon Age}
In the days of the \VaimonCaliphate, there was no \Yormis. 
The land around \hr{Shrun}{\Shrun} was just \wylde. 
This was partially because of the \xss that dwelt beneath \Shrun, spreading their evil and corruption. 





\subsubsection{\Ortaican Age}
\index{Suthis Ondra}
\Yormis was re-founded some time after the \hr{Hundred Scourges}{\HundredScourges} as an \Ortaican city. 
It was built by \hs{Suthis Ondra}, one of the great founders of \Ortaica and a mighty \hr{Rethyax}{\rethyax}. 

\Thessulax and her Sentinels guided Suthis to the place. 
Here Suthis discovered the mystic things beneath Mount \Shrun:
The entrance to \KaiLeng, the \xs \Ubloth and the \hr{Well in Yormis}{black well}. 
So he chose to build his sorcerous fortress here. 
The \ophidians helped him do it. 





\subsubsection{Post-\Ortaican Age}
\target{Yormis remained a power factor}
After the \hr{Fall of Ortaica}{fall of \Ortaica}, \Yormis survived and remained a \rethyax-dominated power factor. 
The reasons for \Yormis's success were both \hr{Yormis economy}{economical} and \hr{Yormis military}{military}. 





\subsubsection{Underground}
\target{City beneath Yormis}
The ruins of the ancient \ophidian city still lay beneath \Yormis.
There were vast caverns full of houses and towers. 

The giant city could house millions, but in the time of \MoroCobrel it was almost entirely dead and deserted and lifeless.
But it still felt as if it lived on with a terrible, unnatural, inhuman unlife. 
Half-seen ghastly shapes slithered, and sinister corpse-like eyes stared out from the whispering shadows.
A few \ophidians still dwelt there.
It was a horrible charnel corpse of a city, haunted by the lingering malevolence of a thousand aeons. 

There were also degenerate \scathae and \humans down there, \hr{Suthis cannibalism}{which were used a food} by the Suthis clan. 










\subsection{Inhabitants}





\subsubsection{Notable citizens}
\begin{itemize}
  \item 
    \index{Suthis Ondra}%
    \hs{Suthis Ondra} was the founder of \Yormis. 
    
  \item 
    \hs{Suthis Mephilex} was the most powerful mage in \Yormis at the time of the \thirdbanewar. 
    
  \item 
    \hr{Moro Cornel}{Moro \Cornel} was raised and educated in \Yormis. 
\end{itemize}









\subsection{\Ophidians}
\target{QJ ride salamanders}
There were \hr{QJ in Yormis}{some \quiljaaran in \Yormis}.

The \quiljaaran under \Yormis rode on grotesque salamanders. 
Or maybe on \hr{Lindworm}{\lindworms}.
(\hr{QJ often ride}{\QuilJaaran often rode}.)
Moro \Cobrel had seen them do it. 





\subsubsection{Search for immortality}
\target{Ophidians in Yormis search for immortality}
The \ophidians of \Yormis were ruled by a small council of elders who had survived the Durance.
They were now \hr{Undead Ophidians}{undead mummies}.
Their bodies were weak and frail, and they searched for a way to become strong again.
They were working on an elixir of immortality, brewed from the \hr{Effluvium of Ubloth}{effluvium of \Ubloth}. 
But it was still imperfect.
So they used their \scathaese servitors as guinea pigs.
Many \scathae desired immortality and were eager to accept whatever risks it entailed.









\subsection{Politics}





\subsubsection{Economy}
\target{Yormis economy}
\Yormis lay near Mount \hr{Shrun}{\Shrun}.
They had access to lots of valuable metals and other minerals. 
They had many great mines where ore was extracted. 
These minerals were a great export.
This kept \Yormis's economy strong. 

This economical factor was one of the reasons why \hr{Yormis remained a power factor}{\Yormis remained a power factor} in the region even after the fall of \Ortaica. 





\subsubsection{Military}
\target{Yormis military}
Other kingdoms had tried to invade \Yormis many times. 
But they defended themselves using sorcery, monsters and the \wylde. 

\Yormis also built up a reputation as fearsome sorcerers.
This was useful, because it made many people too afraid to invade them. 

This military/reputation factor was one of the reasons why \hr{Yormis remained a power factor}{\Yormis remained a power factor} in the region even after the fall of \Ortaica. 









\subsection{Suthis clan}
\target{Suthis}
\index{Suthis}
The Suthis clan was a powerful \scathaese clan. 
It traced its descent from \hs{Suthis Ondra}, one of the founders of \Yormis.
The clan remained one of the most powerful factors in \Yormis.

Another notable scion of the clan was \hs{Suthis Mephilex}.





\subsubsection{\Arcana}
\target{Suthis Arcana}
\target{Suthis Innermost Arcana}
The \rethyaxes of the Suthis clan had their own secret \hr{Arcanum}{\arcana}.
These they called their \quo{Innermost \Arcana}. 
They included these facts:

\begin{itemize}
  \item 
    That the \ophidian \liches existed underneath \Yormis, and that they ruled the Suthis clan as mentors.
  \item 
    That the Suthis clan \hr{Suthis cannibalism}{ate \scatha flesh} in order to refine their bodies and their bloodline.
  \item 
    That the Suthis \rethyaxes \hr{Suthis and Ubloth}{drew their sorcerous power from the hideous god \Ubloth}, and that \hr{Suthis souls and Ubloth}{their souls and reincarnation were bound to \Ubloth}.
\end{itemize}





\subsubsection{Cannibalism}
\target{Suthis cannibalism}
The Suthis clan kept degenerate \scathae and \humans as slaves in secret pens in the underground beneath \Yormis. 
These slaves were bred to serve as food. 
It was a part of the Suthises' \hr{Suthis research}{research and quest}.





\subsubsection{Descent}
The Suthises had \ophidian blood in them.
They repeatedly interbred with the \ophidians.
Some of them even had \xsic blood in them, like the \dragons. 
Suthis Mephilex \hr{Mephilex has XS blood}{was one such}. 
It was a part of the Suthises' \hr{Suthis research}{research and quest}.





\subsubsection{Monstrous slaves}
\target{Suthis monster slaves}
The Suthises cohorts had raised up some horrid quasi-humanoid things to serve them.
These were once slave races of the \ophidians and had been entombed with their masters.
The Suthises had resurrected some of them (having been taught the necessary spells and formulae by the \ophidians), but imperfectly.
Many of the things they raised came back as misshapen monsters. 
They were still obedient slaves, but they were crippled and awful to look upon, and some howled in constant pain. 





\subsubsection{Oath}
Here is a traditional Suthis oath/invocation to \Ubloth.


\begin{diary}%
  I pledge my soul to thee, \Ubloth.
  My lifeblood is in thee, and thine essence is in me. 
  I am one with thee. 
  My soul is thine in this life and the next. 
  Cleave unto me, great one, and grant me thy power. 
  Feed me with strength as I pledge myself to feed thee in turn. 
  
  My body and soul are one with thine, for I am Suthis. 
  As thou gave birth to me so shall I return to thee, and as I return to thee so shalt thou give birth to me again. 
  In this cycle is our clan sworn to thee forever. 
  
  This is our covenant.
  This is the pact which I now swear. 
  Receive my soul and give me thine!
  \Ubloth!
\end{diary}





\subsubsection{Politics}
The Suthis clan knew about the \hr{City beneath Yormis}{\ophidian city beneath \Yormis}. 
They had dealings with the \ophidians and with \Thessulax, and even forbidden powers: 
\Ubloth and the \xss. 





\subsubsection{Research}
\target{Suthis research}
The Suthis clan were conducting arcane research, under the supervision of their \ophidian masters.
They aimed to revive the \ophidian race.
They wanted to create a new \ophidian race from \scathaese stock, and they wanted to secure immortality for \hr{Undead Ophidians}{the old \ophidians who were undead from the Durance}.

The children of the Suthises were test subjects, spawned with \ophidian and \draconic blood.
Suthis Mephilex was a \hr{Mephilex is an experiment}{particularly successful experiment}.





\subsubsection{\Ubloth}
\target{Suthis and Ubloth}
Some \rethyaxes in \Yormis worshipped \Ubloth.
They were able to draw much sorcerous power from the demigod, for \Ubloth dwelt near to them and was a fairly generous and unambitious god. 
So the \Ubloth cult had much power in the city. 
They did not serve \Ubloth's designs (the thing had few designs at all, and \hr{Ubloth's mind}{might even be mindless}) but their own.
They just sacrificed to \Ubloth. 

All \rethyaxes must have a pact with one or more gods in order to cast really powerful magic. 
The Suthises used \Ubloth.

\target{Suthis souls and Ubloth}
The Suthis pact also bound their souls to \Ubloth. 
When they died their souls would return to \Ubloth. 
It was then possible to distil a soul from \Ubloth's \hs{effluvium}. 
This effluvium was fed to pregnant \sphyles in order to reincarnate the souls.
This was all part of the Suthises' \hr{Suthis research}{research and quest}.
(Souls would not necessarily reincarnate in one piece. 
 They could easily fragment and recombine during reincarnation.)

The Suthises lived in a gruesome symbiosis with \Ubloth.
\Ubloth did not feed directly, but \emph{through} them.
The Suthises devoured the flesh of humanoids, preparing their meals with sorcery so as to gain their victims' souls (or at least some of their soul-energy).
\Ubloth would then drink the blood of the Suthises and thus gain nourishment and souls.
The Suthises became physically weakened and decrepit from being drained by \Ubloth, but in exchange they were allowed to drink \Ubloth's effluvium (or potions distilled from it), which gave them a link to the god through which they could channel its magical energy. 









\subsection{Other clans}
\target{Jaslar}
\target{Kish}
\target{Torshen}
\target{Vrael}
Clan Jaslar was a hereditary enemy of Clan \hs{Suthis}.

Other clans included Kish, Torshen and Vrael.























\chapter{The Imetrium}
\target{Imetrium}
\target{Imetric}
\index{Imetrium, the}









\section{Culture}





\subsection{Aesthetics}
The symbol of the Imetrium is a white, four-spoked star, edged with blue within a circle of black against a white background. 

Imetrians often dress in shades of blue and green, like the sea. 
With stripes of white or copper.









\subsection{Caste system}
\target{caste}
\target{Caste system}
\index{caste system}
\index{\Durcac!caste system}
\index{Rissitics!caste system}
The Rissitics are organized in a system of castes.
The castes are, in descending order of status:

\begin{enumerate}
  \item \Nyzlet, the priests, sorcerers and scientists.
  \item \Reken, the elite warriors and commanders. 
    Typically translated \quo{knights}. 
  \item \Bedhin, craftsmen.
  \item \Kyth, warriors. 
  \item \Hok, labourers and peasants.
\end{enumerate}

(%
  In earlier versions I had the \quo{Gzend}, a slave caste. 
  I have gotten rid of them. 
  The \hok{} are already serfs.%
)






\subsubsection{Purpose}
\target{Purpose of the caste system}
The purpose of the caste system was to curb the damaging side-effects of the Shroud-weakening that allowed the \hs{Rissitic creativity}. 
The tight, rigid caste system was intended to create a \hs{Mask of Civilization} and thus form a stable frame around the \quo{drilled hole into Chaos}. 
That way, the Chaos could be (hopefully) contained and controlled, and the Rissitics could gain some bird's-eye-view of it, so they could utilize its beneficial effects but minimize its damaging side-effects. 





\subsection{Clerical ranks}
\index{Imetrium!clerical ranks}
The titles used by the Imetric clergy are (in descending order): 

\target{Laccorin}
\target{Ispan}
\target{Telphan}
\target{Amra}
\begin{itemize}
  \item \Laccorin{} (similar to a cardinal).
  \item \Ispan.
  \item \Telphan. 
  \item \Amra{} (a regular priest).
\end{itemize}

A generic word for \quo{priest} is \Stracos, plural \Stracoi. 
% \also{The Imetrium}




\subsection{Crime slavery}
\target{Imetric slavery}
You cannot officially own slaves in the Imetrium. 
But criminals can be put to forced labour under slave-like conditions. 
Usually temporarily, but sometimes for life. 
(This is not passed on to their children, though.)





\subsection{Etiquette}
\target{Imetric etiquette}
The Imetrians have an etiquette rule that one should not talk openly about one's own weaknesses. 
That is considered feeble and pandering for sympathy. 
One should, of course, still be aware of one's limitations, and it is occasionally OK to tell others about theirs. 

On the other hand, it's OK to be proud and tell people of your own virtues and accomplishments. 
The Imetrians believe people should be proud of their accomplishments and discuss them openly, because it will inspire and motivate others to also achieve great things for the empire. 





\subsection{Language}
\index{Imetrium!Imetric language}
The language spoken in the Imetrium. 
Imetric is descended from \hs{Ortaican} and written using the \Ortaican{} alphabet. 

Imetric is intended to look similar to Greek and Latin, but pronounced similar to English. 





\subsection{Military ranks}
\index{Imetrium!military ranks}
The military ranks used by the Imetric army are (in descending order): 

\target{Deccor}
\target{Retaxis}
\target{Salican}
\target{Vexstra}
\target{Corphin}
\target{Inclan}
\begin{itemize}
  \item \Deccor{} (equivalent to a general). 
  \item \Retaxis{}. 
  \item \Salican{}. 
  \item \Vexstra{}. 
  \item \Corphin{}. 
  \item \Inclan{} (equivalent to a private). 
\end{itemize}



A generic word for \quo{soldier} is \Rengos, plural \Rengoi. 
% \also{The Imetrium}









\subsection{\Naga skin clothes}
\target{Imetric Naga skin clothes}
The Imetrians made clothes from \hr{Nagae shed skin}{shed \naga skins}, freely given. 
It was a great \honour to wear them. 

Outsiders sometimes disbelieved the stories that the clothes were made from the skin of mermen and mermaids. 
Others assumed that the Imetrians killed the merfolk for their skins. 
Both notions were offensive to the Imetrians. 









\subsection{Names: Asian order}
Imetrians traditionally have two names: 
A family/clan name and a personal name. 
The clan name comes \emph{first}. 
This is \Ortaican{} tradition. 









\subsection{Sexuality}
Here are some excerpts of \hs{Telcastora Ilcas} trying to explain the Imetric sexual philosophy to \hr{Carzain}{Carzain \Shireyo}. 


\begin{prose}
  Northstar nodded. \ta{So, how was she?}
  
  \ta{Not bad. Not bad.} Carzain nodded, his expression indifferent. Then he rolled eyes at himself. 
  \ta{Pff. Whom am I trying to fool. Seriously, she was good! She displayed techniques I had heard about but never actually encountered. Where do Imetrian girls learn all this?} 
  
  \ta{Haha. Well\ldots{}}
  
  \ta{Do your people spend your entire youth having sex? 
    Practicing your moves?}
  
  \ta{Haha. No. Maybe. I don't know\ldots{} 
    We Imetrians do own decency. We do not belive in sexual anarchy like the Rissitics do\dash or the Geicans, perhaps. I am not so familiar with Geican culture. But despite that, we do not share all the unreasonable sexual taboos that the Iquinians have. We practice a\ldots{} \quo{golden middle road}, some might say. Now, I do not know Equin Mirai, but she is a comely young woman\dash if I am any judge\dash and from my impression of her disposition, I would not be surprised to learn that her sexual experience was extensive. And I know that there exist\ldots{} \quo{techniques}, as you say, that in certain milieus are passed around and practiced.} 
  Carzain shot him a questioning glance, which Northstar answered with a secretive, almost teasing one. 
  \ta{%
    I have no more than the most superficial experience with this sort of thing. I only know it exists.}
  
  \ldots{}
  
  
  
  \ta{So, tell me\ldots{}} said Carzain, changing the subject. \ta{Explain again how the whole fake secrecy deal works.}
  
  Northstar chuckled. \ta{Well, I believe it is a consequence of\ldots{}} He paused for words. \ta{See, despite what I said before about a \quo{golden middle road}, the truth is that 
  %the Imetric theology's teachings 
  %regarding sexual morals are notoriously unclear. 
  the Imetric view of sexual morals is notoriously unclear. 
  Promiscuity is traditionally considered taboo, but no such prohibitions are actually given in the \Imetriad{}.
  
  I believe this has caused us to develop a strange, perhaps hypocritical mentality: Sex is at once both permitted and forbidden. I don't know\ldots{} perhaps we have some instinctive need to establish sexual taboos. Or perhaps eroticism itself thrives on the\ldots{} allure of the forbidden. I don't know. But whatever the reason, we seem to have created a half-imaginary prohibition against wanton sex.}
  
  \ta{How so?}
  
  \ta{Well\ldots{}} again Northstar had to pause to put his thoughts into words. \ta{In a way, promiscuity\dash meaning sex outside of marriage or otherwise challenging tradition\dash in a way, it is forbidden, so that if one practices it, it must be kept hidden and secret from everyone. But on the other hand, the actual consequences of discovery are minimal. There is no punishment by law, no social stigma. No cruel expulsion, like Iquinian societies practice.
  
  The result is a game of false secrecy, of conspiracy against a fictitious menace. It is a strange thing, and I admit I never truly understood it. I was never a great player of the game, back in the day.} He regarded the \human. \ta{Nonetheless, you seem to have absorbed it readily enough, \Shireyo.}
  
  Carzain shrugged. \ta{I've learned that seduction doesn't need to make sense. I suppose the Imetric game of hiding is no stranger than the games we play in Pelidor.}
  
  Northstar's reply to that was a shrug and a \ta{hm}. 
\end{prose}





\subsection{Technology}
\target{Imetric technology}
Imetric technolog and economy were not bad, but they were inferior to those of the Rissitics. 
One reason for this was that the Imetrians spent so much time and energy \quo{dancing around totem poles} and building monuments and worshipping their gods (building up their \hr{Imetric fanaticism}{fanaticism}).
This sapped time and energy which they could potentially have used to grow food and make weapons.





\subsection{Water}
\target{Imetrium and water}
The Imetrium is very much a water-based civilization. 

The Imetrium is an kingdom of islands. 

Their gods are water-based. 

The Imetrians have become great seafarers. 

They live off fishing to a large extent. 

\hr{Imetric water magic}{Much of their magic} and \hr{Imetric monsters}{many of their monsters} are water-based. 

This is partially because of their \hr{Imetrians and Nagae}{ties to the \nagae}. 

Imetrian sailors and sea-mages are so renowned that they are often hired as mercenaries by others\dash{}those who dare associate with such dangerous sorcerers and their terrible monsters, that is.








\section{Geography}





\subsection{Falcus Aira}
\index{Falcus Aira}
\target{Falcus Aira}
The capital city of the Imetrium, built at the northern coast of the \hs{Naemor Strait}. 





\subsection{Fendor}
\index{Fendor}
\target{Fendor}
An island in the \hr{Risvael Sea}{\Risvaelsea}. 
It is currently controlled by the Imetrium. It has two major towns: Fendacor in the east and \Cicora{} in the west.





\subsection{Martinum}
\index{Martinum}
A city in the Imetrium, built on both sides of the narrow \hs{Martinum Strait}. 
It is famous for the great Martinum Bridge, spanning the Strait and considered a marvel of architecture. 

Martinum was previously the capital of a kingdom by the same name. It is one of the largest, most prosperous and most strategically important cities of the Imetrium, militarily as well as economically. 

Martinum is ruled by a \hr{Laccorin}{\Laccorin}.
The current ruler is Vian Martin, a descendant of the old royal line of Martinum. 





\subsection{Martinum Strait}
\index{Martinum Strait}
\target{Martinum Strait}
The narrow strait that separates the \Samure{} Gulf (west) from the Risvael Sea (east). 





\subsection{Tugan}
\index{Tugan}
\target{Tugan}
A small island in the \Risvaelsea. It is currently controlled by the Imetrium. It has one major town, Pandex. 















\section{History}
\target{Imetrium founded}
The Imetrium appeared near the end of \ps{\Ortaica}{} reign. 
They \hr{Fall of Ortaica}{conflicted with the \Ortaicans}. 

This is one of the reasons why the Rissitics and Imetrians hate each other. 









\subsection[Nycaneer alliance]{\Nycaneer{} alliance}
\target{Imetric-Nycaneer alliance}
Before the Imetrium there existed some \nycaneer{} tribes in \Ortaica, who were allied with \nycans. 
During \ps{\Ortaica} time they were still pretty \Wylde{}. 

Some of these tribes allied with the the \Ortaicans, but they were never assimilated into the \Ortaican{} culture and never really became a part of the \bacconate; they remained external sometime allies. 

\hs{Eoncos}, a \nycan{} god, succeeded in tying all (or most of) the tribes together and allying them with the nascent Imetrium. 









\section{Magic and metaphysics}
\target{Imetric magic}
The Imetrians have their own magic theory. 

Imetric magic theory deals with the \quo{Aether}, a mystical plane where magic resides.
Or maybe they call it the \quo{Astral Plane}. 

Imetric magic, in effect, might resemble \hs{psionics} more than traditional magic. 
It has a lot of telekinesis, telepathy and clairsentience. 
It is meant to look less \quo{occult} and more, I dunno, more \quo{clean} and \quo{nice} and \quo{scientific} than most schools of magic. 

Imetric magic is very mystical and strange and occult. Chaotic in a way, but a cold way.
In contrast, Rissiic magic is logical and scientific and rational.
Rissitic magic can also be chaotic, but in a controlled way, even though it may be hot and fiery.
Rissitics learn to channel, control and utilize their emotions.
Imetric mages come off as in\human, robotic, alien, devoid of emotions.

\citeauthorbook[p.26]{RPG:Warhammer:HordesofChaos}{Gavin Thorpe et al}{
  Warhammer: Hordes of Chaos
}{
  Raising his staff high into the air, he roared at the night sky. 
  Dark lightning flickered at the corners of his midnight eyes as the heavens answered his call, deep, rumbling echoes sounding over the plains.
  The darkness gathered around him like a whispering cloak, shadows coiling out rom the surrounding gloom to hover behind him.
  The twisting blackness reached out with amorphous tendrils, their icy touch sucking the warmth from the warriors' bodies, and making the fire shrink out of existence.
  
  In darkness the Sorcerer spoke, his voice as though there were a dozen people speaking the same words from his throat.
}





\subsection{Mages}

High-ranking Imetric sorcerers and priests are often those with much \naga blood, for these are more highly trusted by the gods and the predominant Imetric intelligentsia.
As they grow in age, power and occult \quo{forbidden} knowledge, their minds twist and become un-\scathaese and more \naga-like. 
As they channel lots of magic, their bodies twist as well, as the \naga sorcery awakens their \naga blood and strengthens and brings out the \naga part of them. 
They mutate and come to resemble \nagae.
Those with enough \naga blood and enough skill and experience (and luck) eventuality become \nagae and go to join their gods in the sea.

The Imetric gods are highly aquatic! 
Make this clear!

The older mages are strangely mutated and look deformed.
They are highly honoured for this in Imetric society, but outlanders use this as proof that the Imetrians are monsters that worship evil things.

Imetrian mages not only feel inhuman, they also look it physically.
And they think inhuman. 
Their minds become \naga-like, and they lose their more \scathaese emotions.
Outsiders sometimes interpret this as \quo{insanity}, but it is really just a change of perspectives, the acquisition of a new mindset, new emotions, new motivations, new ways of thinking.





\subsection{Power}
\target{Imetric vs Rissitic magic}
Imetric magic was slightly weaker than Rissitic magic, but still pretty powerful. 
They \hr{Imetrians rely on magic}{relied on it a lot in war}. 





\subsection{Water}
\target{Imetric water magic}
Much Imetric magic is water-based. 
They are, after all, \hr{Imetrium and water}{a sea power}. 















\section{Military}





\subsection{Armies}
\target{Imetric armies}
\index{technology!Imetrium}
One of the Imetrium's strengths is their soldiers. 
The Rissitics may have higher technology and magic, and certain empires have fielded larger armies, but none have had soldiers more well-trained, disciplined and dedicated as the Imetrians. 

They are backed by their gods: 
\Sarokash gives them the faith to fight for what is right. 
Eoncos strengthens their bodies. 
Dessali strengthens their minds. 
And so on. 





\subsection{Differences from other kinds of armies}
\lyricstitle{Draft excerpt from the chapter \quo{The Cannonade}}{
  The \nycaneers are super-effective with their telepathy. 
  Sethgal and Carzain are surprised at this. 
  They have heard of \nycaneers, but they still think of telepathy as a thing for mages, not armies of soldiers. 
  And the \nycaneers use it to awesome effect. 

  An Imetric priest says: 

  \begin{prose}
    Priest: 
    \ta{We fight an important battle, brethren.
      There are few of us, but the power of our gods will run through us all the stronger for it.}
  \end{prose}

  And it is true. 
  You can see their heathen gods are with them. 

  We don't see this from the Imetrians' POV. 
  After all, the Imetrians are just a minor player in the story so far. 
  They should not get a big, dramatic role until I have had the time to develop them into something cooler, more badass, more background-rich, more well-rounded. 

  We see it from Sethgal's POV. 
  Or maybe \Dornaer. 
  He is one of the only people present who speaks some Imetric. 
  Sethgal is happy to have the Imetrians on his side in the coming siege.

  \begin{prose}
    Sethgal: 
    \ta{I knew we could rely on you.}
    
    \tho{That's actually not true. 
      I thought we couldn't. 
      I \maybehr{Sethgal curses Imetrians}{cursed the Imetrians earlier} for being faithless allies.
      But they proved me wrong.} 
  \end{prose}

  Sethgal overhears someone (Ilcas or an Imetric priest) giving the soldiers a peptalk. 

  \begin{prose}
    Imetric priest: 
    \ta{If we die on this day, we shall live again!}
    
    Sethgal: 
    \tho{I know the Imetrians believe that they reincarnate when they die.
      I wonder if that is true.
      It is certainly not true for us Iquinians. 
      We die and go into the Light.
      But for them\ldots{} who can say?}
  \end{prose}

  The Imetrians scare Sethgal. 
  They fight with great zeal, \maybehr{Imetrian coldness}{but their fervour is\ldots{} cold}. 
  Calculating. 
  Reptilian. 
  He is quite disturbed.

  (Maybe make a footnote about how the warm-blooded \scathae{} do not see themselves as \quo{reptiles}. At the very least, mention this in the glossary.)
}





\subsection{Icy \armour}
Have Imetric warriors clad in \armour made of what looks like transparent crystal, glass or ice. 
And matching weapons: 
Spears and swords of ice. 

Compare to the Stormriders in \authorbook{Ian Cameron Esslemont}{Night of Knives}. 





\subsection{Monsters}
\target{Imetric monsters}
The Imetrians employed a wide variety of beasts and monsters in war (\hr{Rissitic monsters}{just like the Rissitics}).

The Imetrians especially used sea monsters, which made them so powerful and dangerous in naval battles. 
They were, after all, \hr{Imetrium and water}{a sea power}. 

See also the section on \hr{Domestic animals}{domestic animals}. 





\subsection{Pros and cons}
\target{Imetric military pros and cons}
\target{Imetrians rely on magic}
The Imetrians relied a lot on magic in war. 
They had \hr{Imetric technology}{slightly lower technology} and \hr{Imetric vs Rissitic magic}{slightly weaker magic} than the Rissitics, but they made up for it with better trained and disciplined men, and superior morale.
The Imetric gods \hr{Imetric fanaticism}{really knew how to make their worshippers fanatic}. 





\subsection{Seafaring power}
The Imetrium is \hr{Imetrium and water}{a sea power}. 















\section{Mythology}
\target{Imetric mythology}









\subsection{\Ishnaruchaefir}
\Ishnaruchaefir \hr{Ishnaruchaefir and the Imetrium}{appeared in Imetric mythology}.















\section{Politics}
The Imetrium is traditionally hostile towards \hr{Durcac}{\Durcac}. 

They have sometimes allied with the \hr{Iquinian}{\Iquinian} Vaimons





\subsection{Ideology}
The Imetric system is a primitive communist plan economy. 
People are comparatively wealthy, well-fed, healthy and secure. 
But the system is also rather totalitarian, obsessed as they are with their \quo{justice}. 
There is much control and repression. 





\subsection{Reputation}
\target{Imetric reputation}
The Imetrians were feared for being dark and inhuman, \hr{Rissitic reputation}{like the Rissitics}.
But they were less menacing and aggressive than the Rissitics, and so the \Velcadians sometimes made deals and alliances with them for mutual protection against the Rissitics.
The Rissitics rarely tried to invade the Imetrium.





\subsection{Ties to the \nagae}
\target{Imetrians and Nagae}
The Imetrium is tied to the \nagae. 
Perhaps \Sarokash is actually a \nagalord{} in disguise. 

Also, Dessali is a \naiad, a water-dwelling \quo{spirit}. 

The Imetrians have prayers that invoke the \nagae. 

\lyricsbs{Monolith Deathcult}{Den Ensomme Nordens Dronning}{
  Eternal Father, strong to save, \\
  whose arm hath bound the restless wave, \\
  who biddest the mighty ocean deep \\
  its own appointed limits keep; \\
  oh, hear us when we cry to Thee, \\
  for those in peril on the sea!
}








\section{Religion}
The Imetric religion has some adherents in surrounding countries, especially \hs{Andras} and \hr{Scyrum}{\Scyrum}, and even some of eastern \hr{Velcad}{\Velcad}. 

The religion is polytheistic. 
The five major gods make up \quo{the Tribunal}, which governs the Imetric pantheon and nation. 
The Tribunal members are: 
  
\begin{gloss}
  \gitemlink[Sarokash]{\Sarokash} 
  \index{\Sarokash}
    God of justice, head of the pantheon.
  \gitemlink{Dessali} 
  \index{Dessali}
    Goddess of reason, science and knowledge. 
  \gitemlink[Nishi-Settias]{\NishiS}
  \index{\NishiS}
    Goddess of life and death. 
  \gitemlink{Eoncos}
  \index{Eoncos}
    God of strength, bravery and war. 
  \gitemlink[Hiothrex]{\Hiothrex}
  \index{\Hiothrex}
    God of vengeance. 
\end{gloss}

Other gods worshipped by the Imetrians include: 

\begin{gloss}
  \gitemlink{Maegon} 
  \index{Maegon}
  A sea god, actually a \nagalord. 
\end{gloss}





\subsection{Cold fanaticism}
\target{Imetric fanaticism}
The Imetric gods really knew how to make their worshippers fanatic. 
It was an \quo{Elder World} thing, learned from the \nagae. 

That was also why Imetrians spoke so highly of their \quo{justice}. 
It was because the gods had good publicity and marketing. 
It \hr{Imetric military pros and cons}{worked great for military purposes}. 
It was actually pretty sinister.

The Imetrians as a people were very fanatic and devoted. 
Frighteningly so. 
To outsiders they could come off as religious madmen. 
They could look quite ecstatic as they fought for what they believed in. 

\target{Imetrian coldness}
\target{Imetric coldness}
The Imetrians fought and worshipped with great zeal and fervour, but it was a fervour that was somehow\ldots{} cold. 
Calculating. 
Reptilian. 
\Ophidian. 

This was due to the fact that the Imetrians were affiliated with the cold \nagae{} and even had \naga{} blood in their veins. 
Their religious faith was always cold and sinister, not hot and passionate like that of the Iquinians, \Ortaicans{} and \Tepharites. 

The cold fervour was a manifestation of the \hr{Scatha fury}{primal fury that lurked in all \scathae}. 







\subsection{The \Imetriad}
\index{\Imetriad}
The \Imetriad{} is the holy scripture of the Imetrium, containing the core of their beliefs and morals. 









\subsection{Reincarnation}
The Rissitics believed in \hr{Reincarnation}{reincarnation}. 















\section{The truth about the Imetrium}
\target{The truth about the Imetrium}
The Imetrium is secretly backed by the \nagae. 

\Sarokash is a saviour-figure of a kind. 
Similar to the \human{} \quo{Messiah} that is mentioned in \cite{StevenErikson:TheBonehunters}, who might be Shadowthrone. 

\Sarokash is a \quo{promised child}, born to return his own people to glory and, in his creators' eyes, purge the world of evil. 
As such, he carries in him the souls of many of his forebears in him, and their many thousands of years worth of memories. 
He is an powerful \vertex, the \apex{} of a \cuezcan/\naga{} \matrixx. 

But all of it in secret. 
Although the Cabal and Sentinels might suspect.





\subsection{Ilcas suspects}
At some point in the story, \hs{Telcastora Ilcas} learns something disquieting and \hr{Ilcas suspects}{begins to suspect} that the Imetric gods are more than they seem to be. 









\section{Northstar clan}
\index{Northstar!Northstar clan}
The Northstars are a \scathaese{} clan. 
The Northstar name is famous and prestigious (known throughout the Imetrium and parts of southern \Velcad{} and northern \Durcac), and the clan has produced several renowned heroes. 
The Northstars trace their history at least 1000 years back. 
Today they are Imetrians, but they retain certain pagan traditions, of which the most well-known is the veneration of the \hs{North Star}. 

The Northstars have their own city, Telcarmium, in the western Imetrium somewhat east of Martinum, where many of them live. The vast majority of Northstars live in the Imetrium. 
They are a tightly knit family and maintain contact between all their members. 
There are a few people outside the Imetrium who bear the name Northstar but maintain no contact with the family. 
These are considered traitors or impostors by the clan. 
The official Northstar clan has about a thousand members. 

The name \quo{Northstar} is actually \word{Telcastora}, which is the name of the North Star in the \Ortaican{} tongue. 
Throughout my writings, however, Telcastora has been translated into English \quo{Northstar}. 

Well-known Northstars include Ilcas and Cassili the Condor. 
\also{North Star} 
























\chapter{\Ortaica}
\target{Ortaican}
\target{Ortaica}
\index{\Ortaica}
A great \hr{Scatha}{\scatha}-dominated \hr{Bacconate}{\bacconate} that flourished after the \hr{Hundred Scourges}{\HundredScourges}. 

The \Ortaican religion and the \hr{Rethyax}{\rethyax} mages continued to flourish up to the \thirdbanewar. 









\section{Culture}





\subsection{Architecture}
\target{Ortaican architecture}
\index{architecture!\Ortaican}
The \Ortaicans{} used \hs{occult geometry} in their architecture. 
But primitively.
They were not as skilled as their successors the \hs{Rissitics}. 





\subsection{Asian name order}
\Ortaican{} traditionally have two names: 
A family/clan name and a personal name. 
The clan name comes \emph{first}. 

The Imetrium has inherited this, but the \hr{Tepharite}{\Tepharites} did not. 




\subsection{\Baccons}
\target{Bacconate}
\target{Baccon}
\index{\bacconate}
\index{\baccon}
A \baccon was a ruling council of \rethyaxes in \Ortaica. 
Every \Ortaican province was ruled by a \baccon, and the entire \Ortaican empire was ruled by a supreme \baccon. 

An area ruled by a \baccon{} was called a \bacconate. 

After the fall of \Ortaica, the concept of \baccons and \bacconates survived. 
Up till the \thirdbanewar, many non-Iquinian nations were ruled by \rethyaxes.
It was only in the Iquinian lands that sorcerer-kings were prevented. 

Originally, a \baccon was a \quo{council of the wise}, and wise meant mages, \rethyaxes.
In some post-\Ortaican \bacconates, though, the concept was watered down and the \baccons degenerated to mere aristocratic juntas. 

A member of a \baccon{} was called a \hr{Raebar}{\raebar}.





\subsection{Gargoyles}
\target{Ortaican gargoyles}
\Ortaican buildings were often adorned with \hr{Gargoyles}{gargoyles}.
They looked hideous to \human eyes, less to to \scathaese eyes.
\Forclin was an example of this.





\subsection{Language}
The \Ortaican{} language is now dead, but several modern languages are descended from it and still written using \Ortaican{} alphabet. 

\Ortaican looks a little bit like Nahuatl (the language spoken by the Aztecs and related peoples), but only a little.





\subsection{Mesoamerican asthetics}
Aesthetically, \Ortaica is partially based on Mesoamerican cultures such as the Aztecs.
But not too much.









\section{History}
\subsection{Etymology}
The name \quo{\Ortaican} derives from \quo{Noratai ca}, meaning \quo{Norat's tribe}. 
Norat was an ancient chieftain of a \Mastheno{} tribe that would later adopt his name and become the \Ortaicans. 





\subsection{Rise to power}
The \Ortaicans{} originated from the south, in modern-day \Durcac. 
They are a \Tassian{} people, descended from the \Masthenon. 
Under the influence of \hs{Sseju} and many others, they became a big \bacconate. 

At the height of its power, \Ortaica{} covered all of southern \hr{Azmith}{\Azmith}, including the lands that are now {\Durcac}, the \hs{Imetrium}, southern \hr{Velcad}{\Velcad} and even \hs{Uzur} and \hs{Geica}. 
\Scathaese{} cultures today, especially the Imetrium, owe much of their culture to the Ortaicans. 

The Ortaicans, alongside their kin the \Shurcos, warred against the \hr{Vaimon Caliphate}{\VaimonCaliphate} and were beaten by \hr{Vizicar}{\VizicarDurasRespina}. 
After the \hr{Hundred Scourges}{\darkfall} the \Shurco{} were in decline, but the \Ortaicans{} were on the rise. 
Their empire kind of rose from the ashes of the \Shurco. 
They built a great \hr{Bacconate}{\bacconate} and dominated much of the world for a while. 

Hardened by their wars against the Vaimons, the Ortaicans were a tough warrior people. 
They had a heathen religion with their own pantheon of gods, the \hr{Taortha}{\Taorthae}.  





\subsection{\Ishicah{} enslaved}
\target{Ishicah enslaved}
At some point the \rethyaxes{} managed to capture a Scion while she was still young and weak. 
This Scion was \hr{Iolivine}{\Iolivine}, an incarnation of the \Malach{} \hr{Ishicah}{\Ishicah}. 

Maybe \Ishicah{} had awakened to some of her powers and tried to set herself up as a goddess. 
She failed and was taken captive by the \Ortaicans. 

They kept her imprisoned and enslaved, and for over 100 years they used her magical power to power their own sorcery. 
They fed her with living creatures to keep her alive and strong\dash even \resphain, when they could procure them. 

The \rethyaxes{} had Sentinel backing and knew about the \ps{\resphain}{} existence. 
\Ishicah{} was a \sathariah{}. 
The Sentinels loved the irony of putting her through some of the same torture and \hr{Life drain}{power drain} that \Nexagglachel{} had undergone. 
But \Ishicah{} was not as strong as he. 
She succumbed and begged and became their obedient slave for the rest of her existence. 

They forced her to \hr{Apotheosis}{\Apotheosis}, but still kept her imprisoned. 

\target{Ortaican Matrix}
This was particularly effective because \Ishicah{}, \hr{Malachim binding souls}{being a \sathariah{} \malach}, had a very powerful \carcer{} of souls bound to her. 
Her \carcer{} would be torn from her and used as the foundation of the nascent \Ortaican{} \matrix. 
This \matrix{} was the source of the \ps{\rethyaxes} power. 
It bound a lot of \daemons{} to the \Taorthae{} and thus allowed the \rethyaxes{} to cast magic. 
It would continue to empower the \rethyaxes{} up to the \hs{Unravelling}, if not further.

The \Ortaican{} \matrix{} would also form the basis for the later \hr{Rissitic Matrix}{Rissitic \matrix}. 





\subsection{Unpopular}
The \Ortaican{} \baccons{} became unpopular. 
Their magic was no more evil than that of the Vaimons, but they failed to win the population's hearts in the same way the Vaimons did, because the Vaimons had the brainwashing power of \Iquin. 

Their remembrance has since been further blackened by propaganda from the \hr{Iquinian}{\Iquinian} \hr{Tepharite}{\Tepharites}. 
They are now remembered as an evil empire, whereas the \VaimonCaliphate is idealized as a golden age. 





\subsection{The Absconding of the \Taorthae}
The \taorthae were busy fighting wars on other Realms and amongst themselves.
They had little time to keep track of what their mortal followers were doing. 

That did not help \Ortaica. 
They fought and argued and had no surplus time nor energy to keep a good overview of what was happening in \Ortaica. 
This means they were not fully aware of the earthly political turmoil at the time. 
On top of that, the gods were too preoccupied to advise their worshippers properly, so the mortals were left to their own designs. 

Without the direct leadership of their gods, \Ortaica became fractured and unstable. 
This made it easier for their enemies to destroy them. 

This period where the gods were aloof would be known as \quo{the Absconding of the \Taorthae}.
In fact, the Absconding preceded and caused the splintering of \Ortaica.
Post-\Ortaican \rethyactic scholars would interpret it as the other way around.
Scholars would also blow the Absconding out of proportion.
Myths arose that back in the \quo{golden age} of \Ortaica, the gods had walked the earth amongst their followers and fought the enemies of the Bacconate in person.
The Vaimons' records had plenty of stories of \daemons fighting for the \Ortaicans, so it was not too hard to believe that the gods had been there. 
And now they were gone. 

The \rethyaxes mourned this.
Some lost faith in the \rethyactic religion, and the remnants of \Ortaica were weakened further.
This allowed the Imetrians and the Iquinian Tepharins to take over.
In fact the Absconding was much more relaxed. 
The gods had never been very active in the first place.
They obeyed the \hs{Unspoken Covenant}, after all.





\subsection{Cabal intrigue}
It was, for a large part, Cabal intrigue and treachery that drove the \Ortaicans apart and destroyed their empire.





\subsection{Fall}
\target{Fall of Ortaica}
The \Ortaicans{} eventually became too evil. 
At last \Ishicah was somehow destroyed, which lost them some of their power. 
The \hr{Iquinian}{\Iquinian} \Tepharites{} rose up in rebellion against them, and \Ortaica{} was overthrown. 
They also had conflicts with the \hr{Imetrium founded}{fledgling Imetrium}, which hastened \ps{\Ortaica}{} downfall. 

It came to bloody infighting between the \Ortaican{} \raebari. 
One of them broke away from his fellows in bloody rebellion. 
Compare to the insurrectionist Malekith (who founded the Dark Elves) in \cite{RPG:Warhammer:DarkElves}. 





\subsection{Rissitics survived}
The Rissitics \hr{Rissitics were Ortaican}{were originally a \rethyactic{} sect inside \Ortaica}. 
After the fall of the \bacconate{} the Rissitics lived on and formed their own kingdom. 









\section{Mythology}
\target{Ortaican mythology}









\subsection{\Dragons}
The \Ortaicans worshipped a number of \dragons. 
In mythology, these \dragons were once the rulers of the world and upholders of the cosmic order. 
They were then killed or sacrificed their lives, but even in death they continued to uphold and maintain the world. 

\target{Ortaican blood sacrifice}
In order to keep doing this, the dead \dragon gods must be fed with sacrifices of blood. 
Ergo the \Ortaicans sacrificed animals and humanoids to their hungry dead gods. 

These dead \dragons included the fallen \Nechsains: 
\hr{Settras}{\Settras} (\Sethicus) and \hr{Mezzagrael}{\Mezzagrael} (\Nexagglachel). 

\target{Iquinian sacrifices too}
The Iquinians \hr{Iquinian criticism of Ortaica}{criticized \Ortaica} for their tradition of blood sacrifice. 
But the Iquinian religion {was just as bad}. 
Their \sephiroth were fed by the sacrifice of souls.
They just kept it secret. 
The \Ortaicans were at least honest about their hunger for blood. 

Compare them to the Immortal Emperor of Mankind in \cite{RPG:Warhammer40000} and to various mythological figures, including Osiris (Egyptian), Jesus (Christian), Inanna (Sumerian) and Quetzalcoatl (Aztec). 

See also the section about \hr{Myths about Dragons}{\dragons in art and mythology}. 









\subsection{History of the world}





\subsubsection{Nature of the world}
\Ortaican mysticism was more naturalistic than Iquinian (and closer to the truth). 
It taught that the world was a natural thing. 
It existed and ought to exist. 
It was the soul's own responsibility and choice to seek enlightenment and greatness. 
Every mortal soul (at least, every \scathaese soul) had \hr{Ortaican potential for greatness}{potential for greatness}, but only if they approached it with virtue.

See also the section about \hr{Ortaican myths about Iquin}{\Ortaican myths about \iquin}, which describes some important myths. 





\subsubsection{\Banes}
\target{Ortaican myths about Banes}
Originally, the world was ruled by the \Ortaican gods.
This included the standard pantheon of \Taorthae and some additional ones. 
The ruler of the gods, the first \Nechsain, was \hr{Settras}{\Settras} (whose real identity was \Sethicus). 

\target{Ortaican myths about Sethicus}
There existed a dark force of evil, hungry and greedy and hateful. 
This dark force was not native to \Miith but invaded it. 
There was a great war, and the righteous gods defeated the invaders. 
In the process, some great and mighty gods (\Settras and \Tiamat) sacrificed their lives.

The invaders were imprisoned. 
But one day they would return. 
Then the \hr{Ortaican eschatology}{Eschaton} would begin. 
(See that section.) 

These dark invaders were based on the \banes. 






\subsection{\Iquin}
\target{Ortaican myths about Iquin}
The \Ortaicans had their own myths about \Iquin and the \sephiroth.

The \hr{Ortaican myths about Banes}{dark invaders} were defeated but not destroyed. 
Now they sent down their agents in disguise. 
These wicked gods in disguise conspired to overthrow the rightful rulers of the world. 

The evil gods were sly, so they feigned friendship and deceived the other gods. 
They backstabbed some of the righteous gods, took them captive and burned them in a huge pyre. 
They cast their spells on the pyre so that it looked nice and beautiful. 
The righteous gods, unsuspecting, were impressed by the bright pyre and remained friendly to the new gods. 
But in secret, the evil gods kept backstabbing more gods to feed their pyre. 

Eventually, when the righteous gods discovered the evil ones' intention, it was too late. 
Too many had been sacrificed to the pyre.
The betrayers, who drew their power from the pyre, had become too powerful to stop.
So the good gods retreated and went into hiding.
But they swore that one day they would return and take their revenge and liberate the world from the evil conquerors. 

The pyre could burn forever, fuelled by the bodies and souls of gods. 
The pyre became \iquin. 
It was masked with deceitful spells so that it looked beautiful to divine and mortal eyes alike.
The new gods now called themselves \sephiroth. 
Mortals took to worshipping the \sephiroth and their \iquin, and gradually the mortals forgot that the world had ever been ruled by other gods. 

Rissitics claimed that \hr{Rissit is a saviour}{\HriistN} (being the brother of \hr{Mezzagrael}{\Mezzagrael}) was that promised saviour who came to free the world of the \iquinian tyranny. 





\subsubsection{The \HundredScourges}
\target{Ortaican myths about the Hundred Scourges}
According to \Ortaican myths, their gods brought down the wicked Vaimons and drove away their hideous \Archons. 
This was \hr{Taorthae manipulate Belzir}{partially based on history}. 

\Ortaican myth saw the \HundredScourges as just punishment upon \Miithians for worshipping the wicked \Archons and not opposing the wicked Vaimons.





\subsubsection{Eschaton}
\target{Ortaican eschatology}
The \Ortaicans had myths about a great Apocalypse, an Eschaton. 
Here the \hr{Ortaican myths about Banes}{dark forces} (\banes) that had once been defeated by \Sethicus-tachi would finally break the chains of their prison and arise again.
They would invade \Miith and the gods would have to fight them. 

The \taorthae were not all-powerful. 
(\hr{Omnipotence of Iquin}{Unlike in Vaimon mythology}, their was no doubt among the \rethyaxes about this fact.)
So if the \taorthae were to win this last war, they would need help.
Therefore, it was the duty of every \rethyax to do his utmost to help the gods. 
\emph{This} was the true purpose of the \Ortaican religion. 

This purpose was an \arcanum, however. 
The commoners did not know of it.
The masses were just told that the evil forces would break free and that the \taorthae would fight them and prevail.
The wicked would be punished. 

The \Ortaican myth would turn out to be quasi-true:
\hr{The world goes mad}{The Apocalypse really did happen}! 
Compare to \hr{Vaimon eschatology}{Vaimon eschatology}. 
See also the general section about the \hs{Eschaton}. 

\citeauthorbook[On the Origin of the World, p.178]{%
  MarvinWMeyer:TheNagHammadiLibraryinEnglish}{Marvin W. Meyer et al}{
  The Nag Hammadi Library in English
}{
  Before the consummation of the aeon, the whole place will be shaken by a great thunder.
  Then the rulers will lament, crying out on account of their death-
  The \hr{Iquinian angels}{angels} will mourn for their men, and the demons will weep for their times, and their men will mourn to <\ldots{} and> they will be disturbed.
  Its kings will be drunk from the flaming sword and they will make war against one another, so that the earth will be drunk from the blood which is poured out.
  And the seas will be troubled by that war.
  Then the sun will darken and the moon will lose its light.
  The stars of the heaven will disregard their course and a great thunder will come out pf a great power that is above all the powers of Chaos, the place where the firmament of woman is situated.
  When she has created the first work, she will take off her wise flame of insight.
  She will put on a senseless wrath.
  Then she will drive out the gods of Chaos whom she has created together with the First Father.
  She will cast them down to the abyss.
  They will be wiped out by their own injustice.
  For they will become like the mountains which blaze out fire, and they will gnaw at one another until they are destroyed by their First Father.
  When he destroys them, he will turn against himself and destroy himself until he ceases to be. 
  And their heavens will fall upon one another and their powers will burn.
  their aeons will also be overthrown.
  And the First Father's heaven will fall and it will split in two.
  Likewise the place of his joy, however, will fall down to the earth, and the earth will not be able to support them.
  They will fall down to the abyss, and the abyss will be overthrown.
  
  The light will cover the darkness, and it will wipe it out.
  It will become like one which had not come into being.
  And the work which the darkness followed will be dissolved.
  And the deficiency will be plucked out at its root and thrown down to the darkness.
  And the light will withdraw up to its root.
  And the glory of the unbegotten will appear, and it will fill all of the aeons, when the prophetic utterance and the report of those who are kinds are revealed and are fulfilled by those who are called perfect.
  Those who were not perfected in the unbegotten Father will receive their glories in their aeons and in the kingdoms of immortals.
  But they will not ever enter the kingless realm.
  
  For it is necessary that every one enter the place from whence he came.
  For each one by his deed and his knowledge will reveal his nature.
}









\subsection{\Ishnaruchaefir}
\target{Ishnaruchaefir in Ortaican mythology}
\Ishnaruchaefir was not mentioned at all in \Ortaican mythology.
This was deliberate from \Secherdamon's side. 
He wanted to completely deny \Ishnaruchaefir and not even deign to acknowledge his existence.
\Secherdamon wanted \Ishnaruchaefir to be a true Exile. 

\target{Ortaicans reject Isphet}
The \Ortaicans rejected the myth of \hr{Isphet}{\Isphet}, whom the Iquinians feared so much.
According to \rethyactic lore, \Isphet did not exist and was merely an Iquinian fiction, like the notion of \hr{Omnipotence of Iquin}{the omnipotent \iquin}. 
This was partially because \Secherdamon would not grant \Ishnaruchaefir the honour of a place in his mythology and preferred to deny his existence entirely. 









\subsection{\Mezzagrael}
\target{Mezzagrael}
\target{Ortaican myths about Nexagglachel}
In \Ortaican mythology, \Mezzagrael was one of the oldest and greatest of the \taorthae. 
In ancient times he had been the just and rightful ruler of \Miith. 
(Even the inner \arcana acknowledged \Mezzagrael as the ruler of \Miith.
 He was less powerful than the \Primordials, but his rule was blessed by them.
 He held the mandate of the \Primordials.)

In the \hr{Ortaican myths about Iquin}{myth about \iquin}, he was one of the gods whom the evil usurper gods captured and sacrificed to their pyre. 
When \Mezzagrael realized the evil ones' plan, he sacrificed his immortal life in order to send a light of hope into the future. 
In this way, \Mezzagrael granted salvation unto the faithful (\Ortaican or pre-\Ortaican) people.
He gave a promise that one day, they would be delivered from the evil ones. 

\Mezzagrael was a type like Osiris from Egyptian mythology. 

\Mezzagrael, as ruler of the world, held the title \Nechsain. 
He had inherited it from \Settras, his father. 

See also the section about \hr{Myths about Dragons}{\dragons in art and mythology}. 





\subsubsection{Rissitic view}
Rissitics claimed that \hr{Rissit is a saviour}{Rissit} (being the brother of \hr{Mezzagrael}{\Mezzagrael}) was that promised saviour who came to free the world of the \iquinian tyranny and inherit the title of \Nechsain. 





\subsubsection{Truth}
The myth of \Mezzagrael was based on the true story of \hr{Nexagglachel}{\Nexagglachel}. 

\target{Ortaicans use Nexagglachel's name}
Both \quo{\Mezzagrael} and \quo{\Nechsain} were derived from the name \quo{\Nexagglachel}. 
(\hr{Nexagglachel is a powerful name}{It was a powerful name}, and the Sentinels who founded the \Ortaican mythology wanted to milk the name for everything it was worth.)









\subsection{Sseju}
Sseju's legacy was twisted into something unrecognizable.





\subsubsection{Pseudepigraphic quotes}
\target{pseudepigraphic Sseju quotes}
\Ortaican scripture had many pseudepigraphic quotes attributed to Sseju that condemned Iquinianism.

{\VizicarDurasRespina} \hr{Vizicar doubts Sseju quotes}{doubted the veracity of these quotes}. 









\subsection{Tower of \Haamon}
The \hr{Tower of Aamon}{Tower of \Haamon} had an important place in \rethyax mysticism. 















\section{Philosophy and religion}
\target{Ortaican religion}









\subsection{\Arcana}
\target{Arcanum}
\target{Arcana}
\index{\arcanum}
A central dogma was that of the \arcana (singular \arcanum). 
There existed a great number of \arcana. 
An \arcanum was a piece of secret knowledge. 
Every \rethyax spell was part of an \arcanum.
Each god presided over one or more \arcana and could teach them to its followers. 

\Arcanum theory was a simplification of the Aenigma theory the \dragons used. 
Each \arcanum was a piece of well-known Gnosis.

The more \arcana a \rethyax knows, the more powerful he is. 

\citeauthorbook[\quo{True Kabbalah Inspiration}, p.123--125]{%
  AlanUnterman:TheKabbalisticTradition%
}{%
  Alan Unterman%
}{%
  The Kabbalistic Tradition%
}{
  He knew the Mysteries of Creation [\emph{Maaseh Bereshit}], the Mysteries of the Divine Chariot [\emph{Maaseh Merkabah}], the languages of birds, the conversation of palms, trees and herbs, \ldots the flaming embers of charcoal and the conversation of \hr{Iquinian angels}{angels}.
}





\subsubsection{Secrecy}
Enlightenment was only for the select few, not the masses.
The \arcana were secret for a reason.
Knowledge was very dangerous in the wrong hands. 
Only a strong soul could manage such knowledge. 
Glancing an \arcanum prematurely could lead to disaster for you or your surroundings. 

Only a \rethyax should even try to learn any \arcana.
Commoners should leave the esoteric mysteries to their betters.
Some \arcana were deeper than others and had prerequisite \arcana. 

The act of learning or glancing an \arcanum which one was not ready for was called \quo{stealing} the \arcanum. 

\Ortaican mythology was full of fables where someone stole an \arcanum that they were not ready for and came to a gruesome end as result. 
A commoner would go mad or be eaten by some \daemon or monster.
Or the gods would smite him for insolence. 

Even a \rethyax who tried to steal \arcana would come to disaster.
He would go mad, or call down some calamity when his magic went out of control.
Or his patron gods would punish him. 





\subsubsection{The Eight Dreaded Gateways}
\target{Dreaded Gateways}
The \rethyaxes had eight dreaded gateways.
Each gateway led to new enlightenment and opened the way to new \arcana and new magical power.
But there was a price to pay.
The initiate lost some of his humanity and attracted the cruel attention of sinister forces.

\citeauthorbook[p.415]{HPLovecraft:TheBook}{\HPLovecraft}{The Book}{
  For he who passes the gateways always wins a shadow, and never again can he be alone.
}





\subsubsection{The First \Arcanum}
\target{First Arcanum}
The First \Arcanum was the first \arcanum that any \rethyax was taught. 
It was the \rethyax code that laid down the basic rules:
\begin{itemize}
  \item How a \rethyax should interact with gods, commoners and other \rethyaxes.
  \item The basics (descriptive and moral) principles of magic.
  \item The rules for deference between \rethyaxes. 
  \item 
    The First \Arcanum also taught that \hr{Ortaican planes of existence}{the world was composed of a number of layers or planes}. 
\end{itemize}





\subsubsection{The Deeper \Arcana}
The deeper \arcana contained dark knowledge of the horrors of \Miith and Beyond. 

\citeauthorbook[p.248]{RobertEHoward:AWitchShallBeBorn}{Robert E. Howard}{%
  A Witch Shall Be Born%
}{
  \ta{But the life in me was stronger than the life in common folk, for it partakes of the essence of the forces that seethe in the black gulfs beyond mortal ken.}
  
  \ldots 
  
  \ta{He said I was but an earthly sprite, knowing naught of the deeper gulfs of cosmic sorcery.}
}





\subsubsection{Writing}
The \hr{Ortaican letters}{\Ortaican alphabet} were almost an \arcanum, but not quite. 

\Rethyaxes sometimes also used \hr{Draconic runes}{\draconic runes} for their spells.
The runes were an \arcanum. 

\citeauthorbook[\quo{Mysticism of the Talmud}, p.126]{%
  AlanUnterman:TheKabbalisticTradition%
}{%
  Alan Unterman%
}{%
  The Kabbalistic Tradition%
}{
  All the words of the Talmudic Torah are like firebrands, mysteries of the Torah which they hid from the eyes of simple people who are not fit to learn their secrets.
}








\subsection{Commandments}
\target{Ortaican religion has few laws}
The basis of \Ortaican morality was a set of \leges (singular \lex) or pillars. 
These were basic laws. 
A religious constitution of sorts.
\Ortaican dogma did not lay out much morality beyond the bare necessities.
For example, there was no general law against theft.
Instead, \Ortaican dogma merely dictated a social order.
It would be up to secular rulers to formulate fitting laws.
The Iquinians used this fact as \hr{Iquinian criticism of Ortaica}{an argument to show that \Ortaicanism was evil}.

Some basic rules and principles of the \Ortaican religion were:

\begin{itemize}
  \item 
    Only the strong and wise should try to be \rethyaxes.
    The \rethyaxes should be the leaders of society.
    Many non-Iquinian nations were ruled by \rethyaxes.
  \item 
    The strong and wise had a duty to protect the weak and ignorant.
    Not least, they had to be protected from themselves.
    This meant that the wise had to lead and create laws to keep the masses safe. 
    And prevent the masses from learning what they should not. 
  \item 
    The world was full of evil and horrors that hunger for the souls of mortals. 
    They would devour all the souls of the dead if they could and condemn them to everlasting suffering. 
    \Iquin was one such soul-devouring horror.
    (Have juicy myths about these horrors.)
    Mortals could not hope to defend themselves from such monstrosities.
    So they must serve the gods. 
    In return the gods would safeguard their souls from the horrors so that they could pass through the void unharmed. 
    The souls would then reincarnate to new life and be given a new chance to rise to greatness and enlightenment. 
  \item 
    Everyone had the potential for greatness in them, but not everyone should strive for greatness. 
    Some people's lot in life was to serve. 
    They should just live a virtuous life.
    If they did that, they would be reborn into a better life.
    Their chance would come soon enough if only they honoured the gods and their betters.
    One day, in another life, they might themselves become \rethyaxes. 
  \item 
    The masses should serve the \rethyaxes and the \rethyaxes should serve the gods.
    The gods, in turn, would grant power and knowledge to the \rethyaxes, and the \rethyaxes would protect the people and keep them safe. 
    A cosmic feudalism. 
  \item 
    No one should ever try to steal an \arcanum. 
    Instead, people should strive to be virtuous.
    Knowledge of \arcana did not make a soul better.
    Only virtue made a soul better. 
    Those who were worthy would be granted access to the \arcana in due time. 
\end{itemize}








\subsection{Gods and angels}
The \rethyax gods were divided into two categories: 
The \Primordials and the Younger Gods. 





\subsubsection{\Primordials}
\target{Primordial}
\target{Primordials}
\target{XS Taorthae}
The \Primordials were really \xss.
In \Ortaican mythology they were credited with the creation of the world and living creatures.
The \Primordials came from the stars and shaped the world into its current form. 
Except \Nelxurra, who never set foot on \Miith but stayed among the stars. 

They had since absconded and now slept and kept themselves aloof from the world. 
But they were still sources of great power. 
The \Primordials were alien and incomprehensible to mortals. 

There were four \Primordials.
(The \Ortaicans did not know of \hr{Satha}{\RuinSatha}.)
They were known to the \Ortaicans by variant names.
The \quo{true} names of the \Primordials (the names the \dragons used) were deep and secret \arcana.

The mortals did not know they were actually \xss. 
(Most \rethyaxes did not know what a \quo{\xs} was.)
But their descriptions in \Ortaican mythology were fairly close to their true natures. 
Although they were more anthropomorphized in their \Ortaican versions.
The descriptions were close enough that a \rethyax who knew of the \Primordials would recognize them when he encountered the \xss (and be shocked and horrified by the revelation). 

Each \Primordial was \hr{Primordials and the Scathaese mind}{associated with a part of the \scathaese body and psyche}. 

\citeauthorbook[p.137]{RobertEHoward:TheAltarandtheScorpion}{Robert E. Howard}{%
  The Altar and the Scorpion%
}{
  \ta{The real gods are dark and bloody!
    Remember my words when soon you lie on an ebon altar behind which broods a black shadow forever!
    Before you die you shall know the real gods, the powerful, the terrible gods, who came from forgotten worlds and lost realms of blackness.
    Who had their birth on frozen stars, and black suns brooding beyond the light of any stars!
    You shall know the brain shattering truth of that Unnamable One, to whose reality no earthly likeness may be given, but whose symbol is\dash the Black Shadow!}
    
    The girl ceased to cry, frozen, like the youth, into dazed silence.
    They sensed, behind these threats, a hideous and inhuman gulf of monstrous shadows.
}



\begin{gloss}
  \begin{comment}
  \subparagraph{\Costorul}
  \end{comment}
  \gitem{\Costorul (\hr{Khoth-Sell}{\KhothSell})} 
  \target{Costorul}
  \index{\Costorul}
  \index{\KhothSell}
  Goddess of life, death, rebirth and immortality. 
  
  Associated with the earth, the groin and sexuality. 
  
  
  
  \begin{comment}
  \subparagraph{\Kythraxas}
  \end{comment}
  \gitem{\Kythraxas (\hr{Kyaethem Chrei Az}{\KyaethemChreiAz})} 
  \target{Kythraxas}
  \index{\KyaethemChreiAz}
  \index{\Kythraxas}
  God of\ldots{} something. 
  
  Associated with \hr{Kyaethem Chrei Az associated with air or water}{the air and wind, or maybe with the sea}. 
  
  
  
  \begin{comment}
  \subparagraph{\Nelxurra}
  \end{comment}
  \gitem{\Nelxurra (\hr{Nerrhan-Koss}{\NerranKoss})} 
  \target{Nelxurra}
  \index{\Nelxurra}
  \index{\NerrhanKoss}
  God of the occult and the distant Realms. 
  
  Associated with the stars and the questing, contemplative, philosophical mind. 
  
  
  
  \begin{comment}
  \subparagraph{\Rammasul}
  \end{comment}
  \gitem{\Rammasul (\hr{Naath-Kur-Ramalech}{\NaathKurRamalech})} 
  \target{Rammasul}
  \index{\NerrhanKoss}
  \index{\Rammasul}
  God of\ldots{} something. 
  
  Associated with the firmament (sky), the cranium and the firm, righteous thinking mind. 
\end{gloss}



The existence of the \Primordials was an \arcanum known only to the \rethyaxes. 
The masses only knew of and prayed to the \Taorthae. 
The \rethyaxes believed that the \Primordials were so dark and so dangerous that no commoner should interact with them at all. 
No uninitiated mortal should desire to look upon the faces of the \Primordials or hear their voices, lest his very mind be blasted and destroyed by the sheer awesome power of the eldest gods. 
The \Primordials dwelt in the Elder Darkness far beyond the fields of mortals, for their visages were too great and terrible for the world to behold. 

\citebandsong{Nile:Ithyphallic}{Nile}{
  As He Creates So He Destroys
}{
  No living creature can look upon his face\\
  And endure its terrible heat and black radiance\\
  That is like the reverberating unseen rays of molten iron\\
  Which strike and burn the skin of those who would dare\\
  Gaze into the countenance of the idiot god
}




\subsubsection{\Taorthae}
\target{Taortha}
\target{Taorthae}
\target{gods of Ortaica}
\target{Ortaican gods}
The Younger Gods, the \Taorthae, were depicted in mythology as descendants of the \Primordials.
While the \Primordials slept, the \Taorthae had inherited rulership of \Miith.
The Younger Gods were more humanoid in aspect and easier to worship. 
It was they who were charged with the daily maintenance of the world and with protecting their worshippers from malevolent powers.
  
They were \hr{Sseju finds gods}{discovered, contacted or freed by Sseju}. 
Some of these gods were \dragons. 

Some of them were later killed by the \hr{Tepharite}{\Tepharites}. 
Others went into the background and into hiding. 
They still exist and are still worshipped by occasional heathens. 
The \rethyaxes{} still swear by and invoke them. 

Some of them are \hr{front-end}{front-ends} for the dead \hr{Elder Dragons}{\firstgendragons}. 

Maybe the name should be different. 
Tabortha? 
Tarbotha? 
Thwerta?
Dwertha? 
Toartha?

Maybe have both an original \Ortaican{} form (more Greek) and a newer \Tepharin{} form (more Celtic). 

Some of the \taorthae appeared in the form of \dragons. 
After the Absconding, \rethyactic theologians would discuss whether they actually were \dragons or whether they just took on their likenesses. 
Even the \rethyaxes \hr{People do not believe in Dragons}{doubted whether \dragons really existed}.

The \taorthae included: 

  
\begin{gloss}
  \begin{comment}
  \subparagraph{Daxian}
  \end{comment}
  \gitemlink{Daxian} 
  \index{Daxian}
  God of weather and the \Wylde{}. 



  \begin{comment}
  \subparagraph{Ishcatla}
  \end{comment}
  \gitem{Ishcatla}
  \index{Ishcatla}
  
  
  
  \begin{comment}
  \subparagraph{Isxae}
  \end{comment}
  \gitemlink{Isxae} 
  \index{Isxae}
  Goddess of law and rulership. 
  
  
  
  \begin{comment}
  \subparagraph{\Mezzagrael}
  \end{comment}
  \gitemlink[Mezzagrael]{\Mezzagrael}
  \index{\Mezzagrael}
  An ancient god. 
  He was the second \Nechsain (rightful ruler of \Miith), inheriting the title from \hr{Settras}{\Settras}. 
  He was \hr{Ortaican myths about Nexagglachel}{killed by traitor gods}.
  His real identity was \hr{Nexagglachel}{\Nexagglachel}.  
  
  
  
  \begin{comment}
  \subparagraph{\Nasshikerr}
  \end{comment}
  \gitemlink[Nasshikerr]{\Nasshikerr}
  \index{\Nasshikerr}
  God of shadows and the hidden. 
  Patron of spies, assassins and thieves. 
  
  
  
  \begin{comment}
  \subparagraph{Rissit}
  \end{comment}
  \gitemlink[Rissit]{Rissit}
  \index{Rissit}
  God of sorcery and science. 
  Also a \hr{Rissitic gods}{Rissitic god}.
  His real identity was \hr{Secherdamon}{\Secherdamon}. 
  
  
  
  \begin{comment}
  \subparagraph{\Settras}
  \end{comment}
  \gitemlink[Settras]{\Settras}
  \index{\Settras}
  \target{Settras}
  An ancient god. 
  He was the first \Nechsain (the ruler of \Miith).
  Sacrificed his life in the \hr{Ortaican myths about Sethicus}{first war against the dark forces}. 
  His real identity was \hr{Sethicus}{\Sethicus}. 
  
  The Rissitic name \quo{\hr{Sesstra}{\Narkiza}} was a variant of \quo{\Settras}. 



  \begin{comment}
  \subparagraph{Shellagh}
  \end{comment}
  \gitemlink{Shellagh}
  \index{Shellagh}
  God of the sea.  



  \begin{comment}
  \subparagraph{Sithra}
  \end{comment}
  \gitem{Sithra}
  \index{Sithra}



  \begin{comment}
  \subparagraph{\Thessulax}
  \end{comment}
  \gitemlink[Thessulax]{\Thessulax}
  \index{\Thessulax}
  Goddess of the earth, the underworld and the undead. 
  
  
  
  \begin{comment}
  \subparagraph{\Usherain}
  \end{comment}
  \gitemlink[Usherain]{\Usherain}
  \index{\Usherain}
  A goddess with a portfolio overlapping that of \hr{Nasshikerr}{\Nasshikerr}. 
  Also a \hr{Rissitic gods}{Rissitic god}.
  Her real identity was \hr{Nzessuacrith}{\Nzessuacrith}. 



\end{gloss}





\subsubsection{Appearance}
\target{Appearance of Ortaican gods}
The \Ortaican gods and angels took grotesque forms.
They could look like combinations of many creatures:
Humanoids, \nycans, \lothae, \murocs, \hr{Pteran}{\pterans} and more. 

Legends had it that the gods would sometimes walk among mortals. 
They would travel in disguise, for ordinary mortals were not ready to behold the true faces of the gods. 
The faces of the gods were \arcana. 









\subsection{Planes of existence}
\target{Ortaican planes of existence}
\Rethyax metaphysics taught that the world was composed of a number of layers or planes. 

This was inspired by \Sethicus's \hr{Sethican planes}{theory of planes}. 

Commoners could only perceive the most shallow layer, the Material Plane. 
\Daimonia dwelt in the deeper planes. 
\Rethyaxes learned how to feel and interact with the deeper planes. 
They needed the help of the gods to do so. 

The mere existence of the planes was a part of the \hr{First Arcanum}{First \Arcanum}.
You had to learn other \arcana in order to actually feel the planes. 

The \Primordials alone knew all the planes, and how many there were. 









\subsection{Potential for greatness}
\target{Ortaican potential for greatness}
Unlike Iquinians, \Ortaicans were expected to strive for greatness. 
Humility was a virtue, but it was not given nearly as great emphasis as it was in Iquinian theology. 
An \Ortaican was expected to know his own limitations.
He must strive for purity before attempting anything that was out of his league.
But he should always hope for more. 

\Ortaicanism was a self-development religion. 
This was ultimately rooted in \hr{Sethican philosophy}{\Sethican philosophy}.

The \rethyaxes took this to a higher leve. 
They sought to become closer to the gods and eventually become gods or demigods themselves.
This quest, however, was in itself a secret \arcanum.
The masses knew nothing of this ambition.

In the early days of \Ortaica, only \scathae were considered to have this potential for greatness. 
This had to due with the fact that \hr{Ortaican religion was Scatha supremacist}{\Ortaica was a \scatha supremacist culture} and tied in with the (semi-true) mystic doctrine of \hr{Primordials and the Scathaese mind}{the \Primordials dwelt in the \scathaese mind}. 









\subsection[The Scathaese mind]{The \scathaese mind}
\target{Primordials and the Scathaese mind}
According to \rethyax mysticism, \scathae were created by the \hr{Primordial}{\Primordials}.
The {\Primordials dwelt in the minds and bodies of \scathae}. 

Each \Primordial created a part of the body and and a part of the \scathaese psyche. 
Each was also associated with a part of the world. 
See the section about \hr{Primordial}{\Primordials} for more. 

In truth, \hr{Origin of Scathae}{\scathae were created by the \dragons} using bio-magic learned from the \xss.
The process of creating the \scathae was very much inspired by the way the \dragons had created themselves.
The \scathae were designed as \dragons in miniature.
As such, \scathae \hr{Scathae have potential for greatness}{genuinely did have more individual potential for greatness} than \hr{Humans suck}{\humans did}.

Parts of a \scatha's consciousness felt like different gods or monsters. 
This was one of the \quo{truths} behind the myths that the various gods created various parts of the \scathaese mind. 
\Rethyax magic employed these mind aspects. 
A \rethyax had to activate his inner snake/worm/whatever to cast spells. 

It was horrifying when people recognized what other dark things were connected to things inside their minds.
Including various grotesque \xss such as \Ubloth.














\section{Politics}









\subsection{Dark}
The \Ortaican culture and religion should be portrayed as dark and sinister and occult and scary. 
They did horrible things. 
For example, they had \hr{Ortaican blood sacrifice}{blood sacrifice}

But the \Ortaican religion was not necessarily evil.
The Iquinians \hr{Iquinian sacrifices too}{needed sacrifices too}, they just kept it hidden. 









\subsection{\Humans}
\target{Ortaican religion was Scatha supremacist}
The \rethyax religion was designed with \scathae in mind.
It was very anti-\human at first. 
The \hr{Primordials and the Scathaese mind}{\Primordials dwelt in the minds and bodies of \scathae}. 

Later, theologians made concessions and allowed that the \Primordials might also dwell in \humans.









\subsection{Vaimons and Iquinianism}
\target{Ortaican-Vaimon relationship}
The \Ortaican religion was formed in the days of the \VaimonCaliphate. 
As such, it was very much a reaction against the Vaimon faith, and many of its teachings were devoted to telling how bad Iquinianism was and how it should be opposed.

\target{Iquinian criticism of Ortaica}
The Iquinians used the fact that \hr{Ortaican religion has few laws}{the \Ortaican religion had few laws} as an argument to show that \Ortaicanism was evil.
The Iquinians themselves \hr{Iquinianism has many laws}{had many laws}.
They argued that there were huge amounts of obviously evil deeds that the religion did not forbid and thus tacitly allowed and thus encouraged.
(Notice the nice straw man argument.)

The \Ortaicans retorted that Iquinianism was totalitarian where \Ortaicanism left some room for free will and humanoid common sense. 

The Iquinians also criticized \Ortaica because the \Ortaicans \hr{Ortaican blood sacrifice}{practiced blood sacrifice}, even that of humanoids.
But the Iquinian religion \hr{Iquinian sacrifices too}{was just as bad}. 

The \rethyaxes and others believed that Iquinianism was dangerous.
It was an apocalyptic religion whose declared goal was the destruction of the world (in the form of the dogma of \hr{Tikkun}{\tikkun}).
It should be obvious to anyone that they were dangerous and should be fought.
The Vaimons commanded powerful magic. 
Who knew if the Vaimons might one day succeed in their crazy dreams to destroy the world?

The \Ortaicans had \hr{Ortaican myths about Iquin}{myths about how \iquin came to be} and how evil it was. 














\section{\Rethyaxes and magic}
\target{Rethyax}
The \Ortaicans{} founded their own order of Chaos sorcerers, the \rethyaxes. 
They were ruled by \rethyax{} sorcerer-kings. 

\target{Rethyax magic}
\target{Rethyactic magic}
\Rethyactic magic was a variant of \Draconic{} Chaos magic. 
It involved the summoning of \hr{Daemon}{\daemons}. 

It did \emph{not} have the concept of \hs{Aenigmata}. 

But it did have plenty of astrology. 
The \daemons{} were associated with planets, \hs{moons} and stars. 

The \hr{Ortaican gods}{\Ortaican{} gods} were also associated with celestial bodies. 









\subsection{Demography}
\target{Rethyax demography}
There are fewer \rethyaxes{} than Vaimons. 
This is partially because the you need to understand some deeper, darker mysticism in order to become a \rethyax, and go through \hr{Rethyax initiation}{harder, more mystic initiation tests}. 

Vaimons just go through the \Archons, which are pretty user-friendly in comparison to the Chaotic powers the \rethyaxes{} wield. 
This power is filtered through the \Ortaican{} gods and originates from the \xss{} (although many \rethyaxes{} do not know the last part). 









\subsection{How to cast it}





\subsubsection{Shemrod}
\Rethyaxes{} sometimes smoke shemrod leaf in order to be able to channel more magic. 
It puts them in a faint trance-like state similar to the Vaimons' \hr{Shechinah}{\shechinah}. 
It protects them against the physical pain and damage of the virulent Chaotic magic. 

But shemrod is pretty unhealthy on its own. 
An overdose can be lethal. 









\subsection{Initiation}
\target{Rethyax initiation}
A \rethyax{} has to go through a tough, dark, mystic initiation in order to gain his powers, open his body and soul as a vessel of Chaotic power and bind the \hr{Daemon}{\daemons} to his will. 

\citeauthorbook[p.16]{RPG:Warhammer:DarkElves}{Gav Thorpe et al}{%
  Warhammer: Dark Elves%
}{
  A Sorceress must walk the dark paths of the Realm of Chaos, the deep pits of the oceans, and the raging bowels of the fiery mountains in her quest for knowledge. 
  The channelling of the raw Winds of Chaos and the binding of these forces give the Sorceress her power. 
  The creatures of the Chaos Hells will bow to her will in the end. 
  Such power is vast but dangerous, and the aspirant to the Dark Convent of the Sorceresses must be courageous and strong. 
}









\subsection{Meditation}
\Rethyaxes meditated to contact their gods and gain power. 
When a \rethyax wanted information from his god, he also did a meditation like this. 

\citeauthorbook[p.107--111]{StephenSennitt:LiberKoth}{Stephen Sennitt}{Liber Koth}{
  The dark wheel shifts to the next Aeon and the Temple is in readiness for the next phase.
  
  You squat, cowled in black before the flame which reveals the sigil of Hastur.
  You send your consciousness through the portal into the blood-red freezing desert night; into the wasteland of ancient Hali, which once might have been a paradise, but is now as dry and yellow-black as a corpse, with the dripping blood suns that never fully rise and never fully set.
  
  Moving across this deathly scene is a black titan windstorm, curiously silent in its merciless frenzy.
  It is the beating wings, the fluttering eyelid, of Great Hastur, the voice of the Old Ones, the Cry of Silence, He who stalks the spaces between the stars.
  As the cyclone that is His being approaches, you are sucked into the vortex and taken into the Higher Dimensions of reality.
  Here, the howling silence speaks to you, the eyelid beats in rhythm to the pulsation of the stars, the abyss of space is charged with a terrible sneitnece; the Great God blows through you, and you crack open like a lightning-struck tree.
  
  \ldots
  
  The aeonic wheel reaches its nadir and there is a gigantic shifting in the Black AByss beyond the portal.
  
  The sigil of Cthulhu is illuminated by one pale candle.
  As the shifting and pulsing becomes increasingly violent you feel yourself pulled through the vortex of the portal into the outer darkness.
  For a time there is nothing, a resounding absence of awareness, until, like someone awakening from a long, long sleep, you find yourself in a hellish terrain of ink-black ichor; the deep slime and mud of an island raised from the ocean-bed. 
  
  You follow a turgid path of sorts between ghastly ruined stones and pillars which depict strange aquatic lifeforms, until you reach a Temple, its ruined entranceway allowing you access into its dark interior.
  Inside the stench of aeons long death assails the nostrils, and the cloying decay is suffocating\dash and yet something stirs and vague thought-patterns begin to formulate into a haunting invokatory refrain:
  \quo{\emph{That is not Dead which can Eternal lie; And with strange Aeons even Death may Die.}}
  
  The sibilant voice echoes in your mind as you wind your way further into the lair of darkness.
  Finally you come to a rough, stone door upon which is emblazoned the sigil of Cthulhu. 
  It writhes, strangely sentient, and trident-like.
  At the whim of Something in the dark, the door awkwardly slides open and you enter into a cavernous chamber, beautiful in its ferocious asymmetry, flistening in deepest jade ran through with jet-black veins of marble.
  And it the centre of this terrible majesty sits Great Cthulhu Himself, Priest of the Old Ones.
  The dimensional strain He pulls on your perceptions seem to distort and displace the Angles of Space and Time, each displacement causing a shift in your perception, a radical change in consciousness, so that every facet of Self is revealed and it is understood that in reality \quo{Death} does not \quo{Die}; that Self is Deathless and Eternal.
  This realisation is a multi-faceted Jewel in the mind which liberates you from the sleep of Aeons, awakening you to the full knowledge of past-present-future self-reality.
}









\subsection{Was more powerful once}
The \rethyaxes{} were more powerful in the past during the reign of \Ortaica. 
This is because their gods had more worshippers back then and therefore more power to share. 
It was also partially because of \hr{Ishicah}{\Ishicah}. 









\subsection{What it can do}
\index{energy claws}
A few \rethyaxes knew how to create \hs{energy claws}.
This was a rare and powerful spell.






















\chapter{The Rissitics}
\index{\Durcac}
\index{Durkhak}
\index{Rissitics}
\target{Durcac}
\target{Rissitic}
\target{Rissitics}
A collection of peoples south in \hr{Durcac Continent}{\DurcacContinent}, united by the Rissitic religion \hr{Rissitic tribes divided}{but not always much else}. 

The largest Rissitic nation was \Durcac. 

The whole area was also called the Rissitic Dominion or the Rissitic Empire, which was not always a fitting description.

The Rissitic peoples claimed a huge area as their territory, but \hr{Durcac desert}{some of it is desert} and sparsely populated. 















\section{Culture}









\subsection{Aesthetics}
Rissitics often dress in reds, yellows and browns. 
Tinged with black and gold.









\subsection{Architecture}
\target{Rissitic architecture}
\index{architecture!Rissitic}
The Rissitics utilize tons of \hs{occult geometry} in their architecture. 
Their magic is very advanced in this area. 
It is related to their \hs{glyph} magic, which is also occult-geometric. 





\subsubsection{Pyramids and ziggurats}
\target{Rissitic pyramids}
The Rissitics have some great pyramids. All Rissitics who die have their bodies interred in the pyramids, as dictated by their religion. 

In truth, these corpses are used in secret to amass vast legions of the \hr{Rissitic undead}{undead}. Like in \emph{Warhammer: Tomb Kings}. 









\subsection{Dagger sign}
\index{sign of the dagger}
\index{dagger sign}
The \quo{sign of the dagger} or the \quo{dagger sign} is a Rissitic gesture of greeting, the dagger sign consists of a flat hand held up before one's face with the thumb-edge of the hand near the nose and the fingers pointing up. The hand is then moved down to form a fist touching the center of the chest, fingers inward. 

The sign is an imitation of Rissit's symbol of a snake coiled around a dagger. 
% \also{\HriistN}






\subsection{Units of measurement}
\index{Rissitics!units of measurement}
The Rissitics have their own system of measurement units. 

\index{thumb (unit of measurement)}
\index{finger (unit of measurement)}
\index{stride (unit of measurement)}
A thumb is 3 cm. Three thumbs make a finger (9 cm), twelve fingers make a stride (108 cm).















\section{Demographics}

The \scathaese{} population of \Durcac is largely \hr{Mekrii}{\Mekrii}, descended from the \hr{Shurco}{\Shurco}. 

The area claimed by the Rissitics was home to a number of nomadic peoples, some of which were Rissitic in name only, or not at all. 















\section{Geography}





\subsection{Desert}
\target{Durcac desert}
Abroad, it was said that virtually all of \Durcac was covered by desert. 
This was actually not true, but mostly just hearsay and rumours, painting the Rissitics as inhuman monsters. 
In reality, only parts of eastern \Durcac were desert. 

Remember to have an explanation for this desert. 
\Durcac was devastated and defiled in some terrible war in ages past. 





\subsection{Gaznor}
\index{Gaznor}
\target{Gaznor}
A peninsula in southern \Velcad{}, controlled by the Rissitic Dominion. It borders Beirod to the North and the \Risvaelsea{} on all other sides. 

Languages spoken include Rissitic, \Velcadian{} and \Ortic. 















\section{History}





\subsection{Originally part of \Ortaica}
\target{Rissitics were Ortaican}
The Rissitics were originally a part of \Ortaica. 
They were a \rethyactic{} sect concerned with research and science. 
They worshipped \Secherdamon as their most important god. 

\target{Rissitics split from Ortaica}
Rissitism appeared after a religious/political schism among the \Taorthae. 
\Secherdamon, who had \hr{Secherdamon takes the name Nexagglachel}{taken the name \quo{\Nexagglachel}}, wanted more power among the \taorthae.
The other \taorthae did not want to give him more power. 
They fought, and eventually \Secherdamon's followers split off and formed their own religion. 
Note that there was no full-scale war between the Rissitics and the orthodox \Ortaicans. 
There was violence, but overall it was a relatively peaceful religious split. 

In \hs{Rissitic mythology} this schism became represented as a myth of a battle between the gods. 
Compare to the Egyptian myths about Set, Osiris and Horus, and how the various cults used the myths to demonize each other. 

\Nzessuacrith was one of those who opposed \Secherdamon in the schism.
Later, after \Ortaica had dissolved, \Secherdamon persuaded her to ally herself with him again. 









\subsection{Lived on after \Ortaica}
After the fall of the \bacconate{} the Rissitics lived on. 
\Secherdamon{} made the Rissitics his main venture. 
He invested his full support in them. 









\subsection{Merging with tribes}
\target{Rissitics merge with tribes}
At first they existed as an underground cult, or even fugitives, hiding from the dominant Iquinians and Imetrians. 
This went on for centuries. 

The surviving Rissitics, persecuted, fled south into \Durcac. 
Here they allied and mixed with some indigenous tribes from the south and east. 
(This was why their language was so far from \Ortaican.)

The Rissitics and the tribesmen learned much from each other, for some of the tribes were \xs{} worshippers and knew some occult Gnosis that the Rissitics did not know. 

Some of the tribes had \hr{Cregorr}{\cregorr} among their numbers. 

\Secherdamon{} and his Rissitics allied with several other gods, who were eventually all subordinated under \Secherdamon. 
Some of them were weaker and consented to serve him. 
Others had to be slain. 
Yet others were aloof minor \xss{} who cared nothing for their \quo{rank} in some \Miithian{} pantheon.





\subsection{Creativity}
\target{Rissitic creativity}
\target{Rissitic research loophole}
\index{technology!Rissitic}
The Rissitics were very creative. 
They had many scientists and made quite a lot of scientific discoveries and breakthroughs. 
They had more success devising new technology than most people on \Miith{} \hr{Shroud represses technology}{ever since the \SecondShrouding}. 

% \Secherdamon{} has discovered a special \quo{loophole} that allows his people to bypass the Shroud and invent new things. 
% I need to work on what this could be. 
\Secherdamon{} had his own plan to break out of the Shroud. 
It was built upon the \hr{Secherdamon gains Gnosis}{\xs{} Gnosis} that \Secherdamon{} discovered after millennia of searching. 
At the time of \booktitle{\hr{Twilight Angel, Remember}{\TwilightAngelRemember}}, it had met with some success. 
It was the reason why the Rissitics could be such free-thinkers. 
The \hr{Rissitic Matrix}{Rissitic \matrix} was working like a giant drill, gradually drilling a \quo{hole} through the Shroud and out into Chaos, thus letting the creative (and destructive) influence of Chaos into their people's minds, allowing them to think new, creative thoughts (or go mad). 

This \quo{drilling} was dangerous business, though. 
It destabilized the barriers between the Realms. 
At times, the barriers would spring open and dangerous things would leak in from the Beyond: 
Monsters, storms, madness, disease, catastrophes that warp the fabric of the world and cause people, buildings and places to become deformed. 
This sort of thing happened distressingly often in \Durcac. 

To curb this effect, the Sentinels \hr{Purpose of the caste system}{devised the Rissitic caste system}. 

On a more long-term scale, \ps{\Secherdamon} Shroud-drilling interacted with the Cabal's \hr{Sephirah plan}{\sephirah{} plan} in unpredictable and dangerous ways. 
This destabilized the entire Shroud, causing it to \hr{unravelling}{unravel} and become full of holes. 

\index{Dagger, the}%
The goal of this hole Shroud-drilling business was to create the \hs{Dagger}. 





\subsection{Divided}
\target{Rissitic tribes divided}
Before the coming of \hr{Narkiza}{\Narkiza}, the Rissitics were not a unified nation, but a loose collection of tribes.
\Durcac was the largest, most powerful Rissitic nation, but not the only one, and it controlled less than half of the Rissitic peoples.

They were united by the Rissitic religion, but Rissit/\Secherdamon was not the only Rissitic god, and he did not have complete control of them.
Other gods struggled against him, as did the \jinn. 
And Cabal intrigue was a constant threat. 

The Rissitic Dominion was supposed to be a unified empire, but due to \hr{Rissitic infighting}{corruption and infighting and other reasons}, it splintered.

In the last many decades before \SentinelsofMithEmph, \Secherdamon had been very much preoccupied with strengthening his \matrix, getting it into top shape before the coming \thirdbanewar.
And preparing \Vizsherioch to become the \hs{Dagger}. 
He had little time and energy left to devote to political stability, and he realized too late that the Rissitic tribes were badly fractured.
Getting them all back together was a very non-trivial task, even for a god. 

\Secherdamon realized the problem too late. 
He could not solve it in a top-down manner. 
He had to do some bottom-up work, too.
So he found \Narkiza. 

\hr{Narkiza unites tribes}{\Narkiza united the tribes}. 





\subsection{United by \Narkiza}
\target{Narkiza unites tribes}
\Narkiza was already an \Ashenoch and a recognized hero.
\Secherdamon spoke directly to \Narkiza and bade him conquer and unite all the Rissitic tribes. 
It was hard work, but \Narkiza did it.
\Secherdamon heaped many rewards on \Narkiza for it. 


It was \hr{Narkiza}{\Narkiza} who united the Rissitic peoples into a single kingdom and paved the way for \Secherdamon's planned invasion of \Velcad.
Everyone feared this super\human overlord who had subdued the fearsome Rissitics under his banner. 
He had to first convince everyone that Rissit and the other gods were with him.

He got a \hr{Narkiza's dark warlord reputation}{reputation as a dark warlord}. 

















\section{Language}
\index{\Durcac!language}
\index{Rissitics!Rissitic language}
The Rissitic peoples did not all speak the same tongue.
There was a whole family of Rissitic languages. 
\quo{High Rissitic} was spoken in \Durcac.
Some of the tribes spoke languages completely different from and unrelated to Rissitic.

High Rissitic was far from \Ortaican. 
It had some roots in \Ortaican, but was based more on the languages of the \hr{Rissitics merge with tribes}{indigenous \Durcaci tribes that assimilated the Rissitic cult}. 

Rissitic is harsh and guttural, meant to resemble Danish, Dutch and German. 
Some words are taken from Egyptian or Mesopotamian languages, however, since \hs{Rissitic mythology} is inspired by those of Egypt and Mesopotamia. 















\section{Magic}
\target{Rissitic magic}
\target{Rissitics!Rissitic magic}
The Rissitics practiced the magic theory of the \quo{Three Worlds}, which was developed by \RissitNechsain{} from millennia of research. 
It was based on \hr{Rethyax magic}{\rethyactic magic theory}, but very different from it.

The power they wield is great, and many of them, being mortal humanoids, are not up to the task. 
Their minds and bodies succumb to the pressure and begin to \hr{The cost of magic}{twist and warp under the influence of the Chaotic power} that they feebly try to master. 
They become scarred and misshapen, their bodies rotting inside. 
Compare to Hannan Mosag and his K'risnan in \cite{StevenEriksonIanCameronEsslemont:MalazanBookoftheFallen}. 
For this reason, mages wear full-body-covering robes and masks. 
At least the \Shessefkesad, and likely the \Dzeyrgvin{}, too. 

They work hard to preserve their sanity through prayer and mental exercises. 
Sometimes it fails in the long run. 

Some of the priests are offered the gift of undeath to preserve them, since a dead mummy does not mutate. 

The \hr{Ashenoch}{\Ashenoch} are resistant to physical mutation, since their bodies are superhumanly empowered. They may still go mad, tho. 

Rissitic magic (which is a further development on Chaos magic) uses long incantations, and also uses symbols extensively. 
Most spells require an occult \hs{glyph} to be drawn. 
Rissitic magic focuses more on elaborate but powerful arcane rituals rather than quick spells. 
Quick spells exist, but they are difficult and their casting consumes much energy from the caster's body. 
Quick spells are used especially by the \hr{Ashenoch}{\Ashenoch}, who have plenty of physical strength to draw upon. 
But most spells are cast as rituals taking rather a long time and requiring several mages, usually a lead mage and some assistants. 









\subsection{Glyphs}
\target{glyphs}
\target{glyph}
\index{glyph}
Glyphs are writing symbols used in Rissitic. 
Occult glyphs are used in much Rissitic magic. 
Glyphs often consist of pictures of animals, plants and objects as well as geometric shapes.

Most spells require an occult {glyph} to be drawn. 
Glyphs can be drawn in the air with your fingers, or (better) with a special stylus, or they can be drawn on a surface. 









\subsection{Glyph heads}
\index{glyph head}
A glyph head is the severed head of a creature, mummified and enscribed with occult glyphs. Glyph heads are used for storing spells or magical energy for later use. The creation of a glyph head requires the sacrifice of a living creature, and the soul of the head's former owner is bound in the process, used to seal the magical energy in the head. 

When the spells contained are released the \hr{soul destruction}{soul is permanently destroyed} and the head becomes useless (it cannot be enchanted to work as a glyph head again). 









\subsection{\Matrix}
\target{Rissitic Matrix}
\Secherdamon{} designed a special Rissitic \matrix, somewhat separate from the various \draconic{} matrices but still connected. 
It was ultimately based on the \hr{Ortaican Matrix}{\Ortaican{} \matrix}, which was built upon \ps{\hr{Ishicah}{\Ishicah}} \hr{Carcer}{\carcer}. 

The Rissitics improved this \matrix{} and bound new, cooler, more advanced constellations of \daemons{} to it. 

\Secherdamon's \matrix was very powerful and very ambitious.
He tried to build it up to be the vastest and mightiest \matrix ever.
This meant that the \matrix required much maintenance.
So he had enire pyramids and ziggurats and the like erected whose purpose was to channel magical energies and act as \nexi and keep the \matrix alive and stable.
These buildings required sacrifices and spells performed daily to maintain them and keep them running.
They would grow and hum and cracle with sorcerous energy at all times.

Compare to the College of Light, from \cite{RPG:Warhammer:TheEmpire}, whose purpose is to maintain the sorcerous Wind of Hysh.










\subsection{Name theory}
Rissitic magic uses, among other things, some \quo{true names} that, when known, can be used in spells (spoken or written) to give the caster power over the named subject. 

Each creature (and perhaps object?) has a Body-name, a Spirit-name and a Shadow-name. 

These names are most efficient against mortals. 
Mortals are generally \quo{simple} beings whose names are short and manageable. 
Immortals have true names, too, but these typically consist of very long and complex spells, or even rituals. 
Sometimes so complex that they are not worth the effort. 

No Rissitic mage has ever been able to use the true names of a \bane{} to any worthwhile effect. 
Attempting to use a \ps{\bane}{} name (or even learn it) tends to badly damage the caster's sanity. 

This name theory is based on Chaotic \hs{Aenigma} theory. 
It is an attempt at a feasible application of Aenigmatic name theory, which is very heavy and impractical in its raw form. 





\subsubsection{Cursing names}
The Rissitics use the practice of cursing people's magical names:

\citebandsong{Nile:InTheirDarkenesShrines}{Nile}{
  Execration Text
}{
  Mut The Dangerous Dead\\
  Trouble me No Longer\\
  I Inscribe Thy Name\\
  I Threaten Thee With The Second Death\\
  I Kill Thy Name\\
  And Thus I Kill Thee Again\\
  In The Afterlife

  Bau Terror of the Living\\
  Angry Spirits of the Condemned Dead\\
  I Write thy Name\\
  I Burn Thy Name In Flames\\
  I Kill Thy Name\\
  And Thus Thee Are Accursed\\
  Even Unto The Underworld

  Mut The Troublesome Dead\\
  Plague Me No Longer\\
  Thou Art Cursed\\
  Thy Name Is Crushed\\
  Thine Clay is Smashed And Broken\\
  Thy Vengeance Against The Living\\
  Shall Come to Naught
}





\subsubsection{New names}
\target{Rissitic new names}
\hr{Ashenoch}{\Ashenoch} and other \uber-dudes receive new names when they are initiated into their \uber-order. 
The new names and their \hs{glyphs} have mystic significance and are tied to their superpowers. 








\subsection{Oven juice}
\target{Oven juice}
\index{oven juice}
Among other uses, the \hs{ovens} have this property: 
From them can be distilled an energy-rich, spirits-like drink. 
The \nyzlet{} drink this. 
It helps them with their magic. 

But it is quite addictive. 
The more heavy magic you cast, the more you get addicted to the drink. 
Rissitic magic draws its energy both from the caster's body/mind and from the Rissitic \matrix. 

The mages die if deprived of their drink. 
The really old or just really addicted ones can die in as little as 24 hours. 









\subsection{Undead}
\target{Rissitic Liches}
\target{Xul-Gann}
\target{Rissitic undead}
\index{\XulGann}
The Rissitics had undead among their number, including many elder priests. 
They were immortal \hr{Lich}{\Liches}, called the \XulGann.  
This had great religious significance, and they were much revered. 

\hr{Psyrex}{\LocarPsyrex} was \hr{Psyrex' undeath}{one such \Lich}\ldots{} sort of. 

The \hr{Ashenoch}{\Ashenoch} were another type of Rissitic undead. 

All types stayed undead by drinking the blood of \hr{Secherdamon's Resphan slaves}{captive slave \resphain}. 

\citebandsong{Nile:BlackSeedsofVengeance}{Nile}{
  Chapter for Transforming into a Snake
}{
  I am a Long Lived Snake\\
  I Pass the Night and Am Reborn Every Day\\
  I am the Snake which is in the Limits of the Earth\\
  I Pass the Night and am Reborn, Renewed and Rejuvenated Every Day
}









\subsection{Texall Axioms}
\target{Texall Axioms}
The Texall Axioms are a series of magical laws, discovered and formulated by \hs{Texall}. 
They were a great breakthrough and became a central foundation stone in Rissitic magic theory. 















\section{Military}





\subsection{Monsters}
\target{Rissitic monsters}
The Rissitics employ a wide variety of beasts and monsters in war (\hr{Imetric monsters}{just like the Imetrians}).
Including \lothae, \mezolisks and \corgoroth. 

They used the \hr{Hippopotamus}{hippopotamus} in their imagery, but they did not domesticate them. 

See also the section on \hr{Domestic animals}{domestic animals}. 





\subsection{Value of life}
\target{Rissitics value their lives}
The Rissitic population was relatively small. 
This meant that in war, lives were precious to them because of their small numbers.
They used tactics, technology and sorcery to make up for it.















\section{Orders}
The Rissitics have a number of \quo{Orders} of warriors, mages and whatnot. 
Many orders are named after an animal. 
They often carry masks carved in the likeness of their animal. 





\subsection{\Ashenoch}
\target{Ashenoch}
\index{\Ashenoch{} (plural \Ashenoch)}
The \Ashenoch{} (plural \Ashenoch) were a Rissitic order of superhuman undead warrior-mages. 
The name was derived from a longer name meaning \quo{the Order of the Rusty-Red \Corgorah}. 

They received \hr{Rissitic new names}{new names} when they became \Ashenoch. 





\subsubsection{Initiation ritual}
\target{Ashenoch ritual}
The initiate is killed and reborn as an \Ashenoch. 
The process is similar to, and derived from, the \hr{Shaeeroth ritual}{process that turns an \ophidian} into a \dragon. 

\citebandsong{Nile:BlackSeedsofVengeance}{Nile}{
  The Black Flame
}{
  Open, For Me the Gates Shall Open\\
  Over the Fire of the Spirit, The Breath Drawn by the Gods. \\
  Arise Apophis Return, That I Might Return, \\
  Borne by the Flame Drawn by the Gods Who Clear the Way that I Might Pass.\\
  The Gods Which Sprang from the Drops of Blood \\
  which Dripped From the Phallus of Set\\
  That I might be Reborn\\
  For I am Khetti Satha Shemsu, Seneh Nekai\\
  And Will Become Set of a Million Years
  
  Akhu Amenti Hekau\\
  I shed My Burnt Skin and am Renewed
}





\subsubsection{Undeath}
The \Ashenoch were undead.
Like the several other types of \hs{Rissitic undead}, 









\subsection{Order of the Crocodile}
\target{Order of the Crocodile}
Slow-moving heavy cavalry. 
Especially useful as siege troops. 
(Because the crocodile lies in wait for its prey.)





\subsection{Order of the Hippopotamus}
\target{Order of the Hippopotamus}
Heavy shock troopers. 

The \hr{Hippopotamus}{hippopotamus} is the largest and most dangerous mammal in the world, as far as some people know.
Mention this when the Rissitic Hippopotami are mentioned.






\subsection{Order of the Jackal}
Perhaps have an Order of the Jackal, whose members wear jackal-like metal masks and \armour. Compare to the movies \emph{The Scorpion King} and \emph{Stargate}. 

\lyricsbs{Monolith Deathcult}{Deus Ex Machina}{
  For thy blasphemy thou shalt be punished \\
  The Systemlords bring thee thy avengers \\
  Your soul will be possessed and brutally mentally slaughtered \\
  Resistance shall be butchered by Jackal-headed iron warriors \\
  The demons nestled themselves in your bodies \\
  While you stare in the red gleaming eye of the serpent mask \\
  Falcon claws will slit your throat to pieces \\
  Thou shall be enslaved again
}















\section{Politics}




\subsubsection{Corruption}
\target{Rissitic infighting}
Like the rest of \ps{\Secherdamon} minions, the Dark Crescent was \hr{Secherdamon plagued with corruption}{plagued by corruption and infighting}. 

\Durcac, the Rissitic Dominion, is ruled by \HriistN, who is actually \HriistD{} in disguise. 
But \Durcac is infiltrated. 
Chiefly by agents of other Sentinel factions, but also by Cabalists. 

Have some backstabbing like among Sha'ik's army in \cite{StevenErikson:HouseofChains} or the Malazans in \cite{StevenErikson:TheBonehunters}. 

Remember that the Cabal is more numerous and better organized than the chaotic Sentinels. 





\subsection{Economy and trade}
\target{Rissitic economy}
\index{technology!Rissitic}
\Durcac was not merely a warrior nation. 
They were also a major power by virtue of trade. 
Their geographical position gave them access to exotic goods from the south and southeast. 
And their high technology let them produce many unique and valuable export goods. 

Among other things, many quality guns were Rissitic made. 

Have more examples of Rissitic-made things! 

\Durcac's soul was not very fertile, but they made up for it with technology and industry. 
The standard of living was relatively high. 
Even slaves were rather well off. 

There was lots of pollution, though. 





\subsubsection{Spice}
\target{Spice and worms}
\Durcac exports a pepper-like spice. 
Rumours have it that this spice is produced by some enormous giant worms that live in the \hr{Durcac desert}{desert}. 









\subsection{Ideology}
The Rissitic system is somewhat chaotic and anarchistic on a small scale. 
At least, it is not nearly as centrally controlled as the Imetrium (which is a primitive communist plan economy). 
The Rissitic commoners are poorer, less healthy and less secure than Imetrians, but they are also more \quo{free}, in the sense that the laws and, more importantly, customs are less restrictive. 
For example, sexual morals are liberal. 





\subsection{Reputation}
\target{Rissitic reputation}
Outsiders often saw the Rissitics as murderous and evil, led by a violent, cruel religion. 

\lyricsbs{Monolith Deathcult}{Desecration of the Black Stone}{
  They conspire in their caves in their envious world of emptiness,\\
  preparing for Jihad to obey their desert god.\\
  They murder for belief to deflower 70 virgins.\\
  These \quo{brave} Mudjahedeen brought Gaza in darkness.\\
  Their God is a worm baptised in the blood of the prophet.
}

Be sure to demonize the Rissitics. 
Rumour turned them into legions of demons from Hell, inhuman wielders of dark sorcery and evil.
The fact that their warlord \Narkiza was known to be an \Ashenoch, and that the Rissitics had always relied on magic and monsters, only made their image worse.
They were seen as the marauding Legions of Chaos.

The Rissitics were seen as demonic hordes of evil, feared by the \Velcadians.
They used dark sorcery liberally and all the time, making them seem inhuman and supernatural monsters.

\Durcac was a nightmare place where laughing evil sorcerers kidnapped beautiful virgins and cast them screaming into great \hs{ovens} of fire to be burned alive as food for the sorcerers' terrible gods. 

They were seen as \hr{Imetric reputation}{worse than the Imetrium}.

\lyricsbalsagoth{
  Behold, the Armies of War Descend Screaming From the Heavens
}{
  Behold, the armies of war descend screaming from the heavens!
}





\subsection{Threat of destruction}
Perhaps the Rissitics, at least the upper echelons, are desperate to conquer for fear of being devoured from the inside by the Chaotic power that they utilize. 

\lyricsbs{Marduk}{Scorched Earth}{%
  We must win to save us from the plague's grasping jaws\ldots{}}
















\section{Religion}
\target{Rissitic mythology}
\index{\Durcac!religion}
\index{Rissitics!religion}
The Rissitic religion, also called Rissitism, is based around the worship of the god \HriistN, also called Rissit. 
\quo{Rissitics} is also the term used by nonbelievers for adherents of the religion. 









\subsection{\Dragons}
\Dragons featured prominently in Rissitic myth. 

See also the section about \hr{Myths about Dragons}{\dragons in art and mythology}. 









\subsection{Funeral ovens}
\target{Rissitic ovens}
\target{ovens}
\index{ovens}
After death, Rissitics are cremated in large, special, enchanted ovens. 
These ovens are designed to melt bodies and souls and extract energy from them to feed the Rissitic \matrix. 

The ovens are made with advanced technology. 
They are more sophisticated and more effective as a means of extracting life energy than just a raw digestion system, or the \psp{\resphain} \hs{Communion}. 

It is a great \honour to be burnt in the ovens.

The oven-burning is more energy-effective if done \emph{before} death, so people are encouraged to commit themselves to the ovens when they grow old, sick or invalid. 
This is an extra-great \honour; giving one's life for \Nechsain. 
Many faithful Rissitics choose this as a good way to die. 

It is almost expected for the \nyzlet{} to do this. 
Their bodies and souls are especially energy-rich after a whole life casting magic and channelling the power of the Rissitic \matrix. 

Sacred animals are sometimes sacrificed in the ovens. 
Also, criminals and prisoners of war are given to the ovens as sacrifices. 
This is seen as an \honour for them. 
It is a merciful redemption, absolving them of their sins as infidels or sinners, and accepting them into the Rissitic afterlife. 









\subsection{Gods}
\target{Rissitic gods}
The Rissitics worshipped a number of gods. 


\begin{gloss}  
  \begin{comment}
  \subparagraph{Rissit}
  \end{comment}
  \gitemlink[Rissit]{Rissit}
  \index{Rissit}
  God of sorcery and science. 
  Also a \hr{Taortha}{\taortha}.
  His real identity is \hr{Secherdamon}{\Secherdamon}. 

  
  
  \begin{comment}
  \subparagraph{\Usherain}
  \end{comment}
  \gitemlink[Usherain]{\Usherain}
  \index{\Usherain}
  A goddess with a portfolio overlapping that of \hr{Nasshikerr}{\Nasshikerr}. 
  Also a \hr{Taortha}{\taortha}.
  Her real identity is \hr{Nzessuacrith}{\Nzessuacrith}. 



\end{gloss}









\subsection{\RissitNechsain}
\target{Rissit is a saviour}
In Rissitic mythology, \hr{Rissit Nechsain}{\RissitNechsain} was seen as a saviour figure. 

Rissit was the brother of \hr{Mezzagrael}{\Mezzagrael}, the great god and original rightful ruler of \Miith who had sacrificed himself to save the world.
The ghost of \Mezzagrael once came to Rissit and showed him a revelation.
\Mezzagrael appointed Rissit as his successor and heir and charged him with the task of overthrowing the false gods. 

Unto Rissit, \Mezzagrael bestowed all his power and kingship. 
In fact, the ghost of \Mezzagrael merged with Rissit and let itself absorb into him. 
Thus Rissit gained and earned the title \Nechsain, which had originally belonged to \Mezzagrael. 
In a sense, \Nechsain was not merely the brother and heir of \Mezzagrael but his reincarnation. 
As such, it was \Nechsain's duty and right to conquer the world and rule it as the new \Mezzagrael. 

At the time this myth was founded, \Secherdamon/Rissit \hr{Secherdamon takes the name Nexagglachel}{really did take the name of his brother}. 

This apotheosis of Rissit happened at the time when the \hr{Rissitics split from Ortaica}{Rissitics split from \Ortaica}. 
Unfortunately, according to Rissitic mythology, some of the other \taorthae in their blindness and stubbornness refused to acknowledge Rissit as \Nechsain.
Therefore the Rissitics had to split from \Ortaica and become rivals.

Where \Mezzagrael is comparable to Osiris from Egyptian mythology, Rissit is comparable to Horus, who is both the son and the reincarnation of Osiris. 



\citeauthorbook[\quo{First Thought in Three Forms}, p.86--100]{%
  BentleyLayton:TheGnosticScriptures%
}{%
  Bentley Layton%
}{%
  The Gnostic Scriptures%
}{
  But then for my part, I descended and got as far as chaos.\\
  And I dwelt with my own who were there, hidden within them, bestowing power and imparting image unto them.\\
  And down to the present [\ldots{}] those who [\ldots{}], i.e. the offspring of the light.\\
  It is I who am their parent. \\
  And I shall tell you a mystery that is ineffable and indescribable by any mouth.\\
  For you I loosed all the fetters and broke the bonds of the demons of Hades, bonds that were bound to my limbs and worked against them. \\
  And I threw down the high walls of the darkness,\\
  And I broke open the solid gates of the merciless and split their bolts.\\
  And the evil agency, who strikes you, who impedes you, the tyrant, the adversary, the ruler, the real enemy\dash as for all of these, I taught them about my own, the offspring of the light:\\
  So that they might become loosened from all these and rescued from all the fetters, and might enter the place where they had been in the beginning.\\
  It is I who am the first to have descended, for the sake of that part of me which remained, \\
  Namely, the spirit that exists within the soul and which has come to exist out of the water of lige and out of the baptism of the mysteries.\\
  I myself spoke with the rulers and with authorities, for I had descended deep into their language;\\
  And I uttered my mysteries to my own\dash a hidden mystery\dash \\
  And the fetters were loosened, as was eternal forgetfulness.\\
  And within them I bore fruit, namely, the thinking that concerns the unchangeable eternal realm (aeon) and my house and their parent.\\
  \ldots{}\\
  All who were in me shone bright.\\
  And for the ineffable lights within me I prepared an manner of appearance.\\
  Amen!
}





\subsubsection{\Belzir}
\target{Rissitic myths about Belzir}
In Rissitic mythology, Rissit took credit for having shaped \Belzir into the destroyer-of-the-\caliphate she ended up becoming.
There was \hr{Rissit helps set up Belzir}{some truth in this}. 










\subsection{Reincarnation}
The Rissitics believed in \hr{Reincarnation}{reincarnation}. 









\subsection{\Resphan slaves}
There were rumours about \hr{Secherdamon's Resphan slaves}{\Secherdamon's \resphan slaves}. 









\subsection{Sacred animals}
A number of animals are \quo{sacred} and have religious significance to the Rissitics. 
The most important of these are cobras, \hr{Mezolisk}{\mezolisks} and \hr{Corgorah}{\corgoroth}. 








































\input{World/Azmith/Vaimons}








































\chapter{Ethnic groups}















\section{\Goydens}
\target{Goyden}
\index{\Goyden{} (plural \Goydens)}
The \Goydens{} are a savage people living in the \Wylde{} in southern Pelidor and northern \hs{Beirod}. 
They are \humans, but some say they are half \human{} and half beast. 
They speak their own language and pray to their own gods. 
According to some rumours they can change between \human{} and animal form. 















\section{\Orticans}
\index{\Ortican}
\index{\Ortic{} (language)}
\target{Ortic}
A \scathaese{} ethnic group and language somewhat widespread in \hs{Beirod}, \hs{Gaznor} and southern \hs{Pelidor} and \hr{Scyrum}{\Scyrum}. 

The \Ortic{} language is descended from \hr{Ortaican language}{\Ortaican}.















\section{\Samur}
\target{Samurin}
\index{\Samur}
A predominantly \scathaese{} people that originate from the area on the northern bank of the \Samure{} Gulf but later spread eastward into what is now the northeastern Imetrium, Andras and western \hr{Scyrum}{\Scyrum}. 









\subsection{\Samurin{} language}
\index{\Samur!\Samurin{} (language)}
The \Samurin{} language is still spoken in parts of Andras and \hr{Scyrum}{\Scyrum}, but repressed in the Imetrium. 















\section{\Tepharites}
\index{\Tepharite}
\target{Tepharite}
The \Tepharites{} are a people living in southern \hr{Velcad}{\Velcad}. 
Originally they were purely \scathae{} (of mixed \hr{Tassian}{\Tassian} and \hr{Mekrii}{\Mekrii} descent), but they merged with some \human{} tribes, and eventually these came to be considered \Tepharites{} as well. 

Prior to the advent of \hr{Great Velcad}{\theBelkadianEmpire} they had their \hr{Bacconate}{\bacconate}, \hr{Tepharae}{\Tepharae}. 

The \Tepharin{} language (related to \hr{Ortaican language}{\Ortaican}) is still spoken many places in \hs{Ontephar}, \hs{Pelidor} and \hr{Scyrum}{\Scyrum}. 
\also{\Tepharae}







































\chapter{Places}















\section{\Velcad}
\target{Velcad}
\index{\Velcad}
A region located in the middle of \hr{Azmith}{\Azmith} and comprising a large number of independent kingdoms (and great expanses of \Wylde{}). 
It is not well-defined or well-delimited, but is usually considered to cover (at least) all lands where the \Velcadian{} tongue is spoken. 

%It includes, among other things, the nations of Belek, \Redce, Pelidor and Runger. 

\Velcad{} includes the nations of \hs{Andras}, \hs{Beirod}, \hs{Belek}, \hs{Ontephar}, \hs{Pelidor}, \hr{Redce}{\Redce}, \hs{Runger} and \hr{Scyrum}{\Scyrum}, among others. 









\subsection{Knights}
\target{Knight}
\target{knights}
\index{knight}
In \hr{Velcad}{\Velcad}, especially honoured warriors are given the status of knights. They are blessed by the \hr{Iquinian}{\Iquinian} Church and carry the \hr{noble titles}{title} \quo{\rah}. 
Examples include \hr{Sethgal}{\rah[Sethgal] Pelidor}. 

\target{hedge knight}
Most knights are noble-born, but commoners are sometimes knighted. The latter are called \quo{hedge knights}. 

\target{Knights have superpowers}
Iquinian knights have superpowers.
They are not Vaimons, but with the help of priests they can summon the \sephiroth and perform superhuman feats of martial arts.
They also look and feel imposing and regal and commanding and holy, because they have the blessing of the \sephiroth\dash{}that blessing is what makes them knights.









\subsection{The Tigers}
\target{Tiger}
\index{Tiger (warrior order)}
The Tigers were the elite, professional soldiers of \hr{Great Velcad}{\theBelkadianEmpire}, taking their name from \hs{Uther the Tiger}. 
After the downfall of the empire the Tigers are no longer centrally organized. 
Some owe their allegiance to various lords, while others are mercenaries. 

The Tigers contain both cavalry and infantry, including archers. 
Some of them are \hr{Knight}{knights}, annointed by the \hs{Iquinian} church. 

The Tigers have no mages. 
Instead, the mages affiliated with \hr{Great Velcad}{\theBelkadianEmpire} were the \hr{Telcra}{\Telcras}. 















\section{Bron}
\index{Bron}
A river in western \hr{Velcad}{\Velcad} that, for much of its length, marks the border between \hs{Andras} and \hr{Scyrum}{\Scyrum}{}. It runs from the Threll mountains into the \hr{Risvael Sea}{\Risvaelsea} and meets the river \hr{Pylor}{\Pylor}. 















\section{Far Orient}
\target{Far Orient}
\index{Far Orient}
\index{Orient!Far Orient}
The eastern part of the \hs{Orient}. 















\section{Gwendor Sea}
\index{Gwendor Sea}
\target{Gwendor Sea}
A sea in the northen \hr{Velcad}{\Velcad}. It encloses \hr{Vidra}{\Vidra} and borders \hs{Threll}, \hs{Ontephar}, \hs{Runger} and \hr{Redce}{\Redce}, among others. To the west it flows into and becomes the \hs{Thenglain Sea}. 















\section{Heropond Forest}
\target{Heropond Forest}
\index{Heropond Forest}
A large \Wylde{} forest in \hr{Pelidor Continent}{\PelidorContinent}. Marks the border between \hs{Pelidor} and \hr{Scyrum}{\Scyrum}. 









\subsection{Leglan's Pass}
\index{Leglan's Pass}
A path through the narrowest part of Heropond forest, near \hr{Bryndwin}{\Bryndwin} (on the \Scyric{} side) and \Redglen{} (on the Pelidorian side. 
It was formerly used as a trade route, but has fallen out of use in recent decades and grown more \hr{Wild}{\Wylde}. 















\section{Hirum Gulf}
\target{Hirum Gulf}
\index{Hirum Gulf}
A gulf north of \hr{Pelidor Continent}{\PelidorContinent}. 
It meets the \hs{Gwendor Sea} to the northeast, \hs{Runger} to the southeast, \hs{Pelidor} to the southwest and \hs{Ontephar} to the west. 
The river \hs{Nerim} runs south from the Hirum Gulf. 















\section{\Durcaccontinent}
\target{Durcac Continent}
\index{\Durcaccontinent}
A continent south of \hr{Velcad}{\Velcad}, southeast of the \hs{Imetrium}, northeast of \hs{Uzur} and west of the \hs{Orient}. 
Contains \hr{Durcac}{\Durcac}, among other things. 
















\section{Lorn Sea}
\index{Lorn Sea}
\target{Lorn Sea}
A narrow sea in eastern \hr{Velcad}{\Velcad}, marking the eastern borders of \hs{Runger} and \hs{Beirod} and the western borders of \hr{Thyrin}{\Thyrin}, \hs{Sumian} and \hs{Belek}. It meets the \hs{Gwendor Sea} to the north and the \hr{Risvael Sea}{\Risvaelsea} to the south. 
















\section{Naemor Strait}
\target{Naemor Strait}
\index{Naemor Strait}
A strait in the \hs{Imetrium}, separating the \hr{Samure Gulf}{\Samure{} Gulf} from the \hs{Thenglain Sea}. The Imetric city of \hs{Falcus Aira} is built at the Naemor Strait. 
















\section{Near Orient}
\target{Near Orient}
\index{Near Orient}
\index{Orient!Near Orient}
A collective term for the nearer part of the \hs{Orient}. 
Kingdoms in the Near Orient include \hs{Hazid}. 
















\section{Nerim} 
\index{Nerim}
\target{Nerim}
A fjord that runs south from the \hs{Hirum Gulf} and marks the border between \hs{Runger} and \hs{Pelidor}. 
















\section{Northern Kingdoms}
\target{Northern Kingdoms}
\index{Northern Kingdoms}
Generic term for the lands north of \hr{Velcad}{\Velcad} (many of which are not actually kingdoms). 
















\section{Orient}
\target{Orient}
\index{Orient}
The area southeast of \hr{Velcad}{\Velcad} (east of \hr{Durcac}{\Durcac} and south of the \hr{Serpentines}{\Serplands}). 
Informally split into the \hs{Near Orient} and the \hs{Far Orient}.  
















\section{\PelidorContinent}
\target{Pelidor Continent}
\index{\PelidorContinent}
A continent in central \hr{Azmith}{\Azmith}. Contains \hs{Pelidor}. 
















\section[Pylor]{\Pylor}
\target{Pylor}
\index{\Pylor}
A river. 
Marks the border between \hs{Andras} and \hr{Scyrum}{\Scyrum}.















\section{\Risvaelsea}
\target{Risvael Sea}
\index{\Risvaelsea}
A large sea in the centre of \hr{Azmith}{\Azmith} that marks the southern border of \hr{Velcad}{\Velcad}, the northern border of \hr{Durcac}{\Durcac} and the easter border of the \hs{Imetrium}. In it lie the two large isles of \hs{Fendor} and \hs{Tugan}. 















\section{\Samure{} Gulf}
\target{Samure Gulf}
\index{\Samure{} Gulf}
A gulf in the \hs{Imetrium}. It borders the \hs{Thenglain Sea} to the west at the \hs{Naemor Strait} near \hs{Falcus Aira} and the \hr{Risvael Sea}{\Risvaelsea} to the east at the \hs{Martinum Strait}. 















\section{The \Serplands}
\target{Serpentines}
\index{\Serplands}
Also called the \Serpadj{} kingdoms. Collective term for a number of kingdoms that lie between the \hr{Serpentine Sea}{\Serpsea} to the west and the \Dragonridge{} to the east. The \Serpadj{} kingdoms are diverse in culture. Some are effectively vassal states of Irokas. 















\section{\Serpsea}
\target{Serpentine Sea}
\index{\Serpsea}
A sea that marks the eastern border of \hr{Velcad}{\Velcad}. The \Serp{} is long in the north-south direction but narrow in the east-west direction, and it twists and bends like a snake, hence the name. East of the \Serp{} lie a number of kingdoms called the \hr{Serpentines}{\Serplands}. 
\also{\Serplands}

%\gitem{\Serpriver}
%A great sea that runs along the eastern border of \Velcad{}. In fact, the \Serpriver is often considered to be the easter border of \Velcad{} by definition. East of the \Serpriver lie a number of kingdoms called the \Serplands. 
%\also{\Serplands}















\section{Thenglain Sea}
\target{Thenglain Sea}
\index{Thenglain Sea}
A great sea that marks the western border of \hr{Azmith}{\Azmith}. 















\section{Threll}
\target{Threll}
\index{Threll}
A region east of \hr{Velcad}{\Velcad}, a devastated land haunted by monsters. The Threll Mountains mark the its southern border with the \hs{Imetrium} and \hs{Andras}. It borders \hs{Ontephar} to the east, the \hs{Gwendor Sea} to the north and the \hs{Thenglain Sea} to the west. 















\section{Uzur}
\target{Uzur}
\index{Uzur}
A region south of the \hs{Imetrium} and southwest of \hr{Velcad}{\Velcad}. 
Much of it is covered in \hr{Wild}{\Wylde} forests and swamps, but there are nations that thrive here. 
\Meccara{} are the dominant humanoids. 

Nations include \hs{Clictua} and \hs{Kochu}. 




































































 
