%\section{\Vertex{} Spike}
\stamp{\dateMutiny}{\TopazChateau, \Redce}
%\dateplace{Carz}{11th}{\Yeziel}{\TopazChateau, \Redce}
%
% At the time of Carzain's fight, when Vizicar awakens within him and takes control of his body, the Malach's awakening sends ripples through Iquin. Esmerel is a Redcor Matron who has studied the Malachim. She feels the ripple and knows that a Malach has awakened. She begins research to discover its location and identity. 

%\new
%A ripple went through Iquin, and \Esmerel{} stirred from her books. It was almost nothing, the slightest of fluctuations, indiscernible to even a skilled Vaimon, and only \Esmerelz{} decades-long dedication and attunement enabled her to feel it. 
%
%She sat up with a start. With haste she reached into Iquin and invoked her \Sephiroth. 
%
%\ta{What is it, Matron?} said Iselle. \Esmerel{} raised a hand, and her assistant fell silent. 
%
%%\ta{Silence, girl,} said \Esmerel. 
%
%Esmerel sends Iselle off to find some incence and some more Redcor to assist Esmerel in the ritual. They combine to form a circle, then meditatate. 
%
%\Esmerel{} is deep in her \Sephirah{}-meditation, sitting at a mystic pool of silvery water\dash the Waters of Enlightenment. She notices a ripple in the Web of the Realms and sends her mind probing to investigate. 
\tho{A flash of lightning!} 

Redcor \Matron{} \EsmerelFull{} started, almost broken out of her meditation. \tho{What was that?} 

\tho{A ripple in the pool. A massive discharge of energy.}

She strained her inner sight, gazing deeper into the silvery mirror before her\dash the Waters of Enlightenment, the window to hidden dimensions Beyond. The ripple faded quickly, but she had caught its scent. 

\tho{Come to me, \sephiroth,} she prayed. \tho{Guard me and guide me safely through the shadows.} And she felt them draw near, felt their familiar yet wondrous touch. Calming, like a mother's embrace. And splendid, like the sunrise. And breathtaking, like the view from the high towers of the \TopazChateau{} when she had first seen it as a young girl, many decades ago. Shielded in the protective embrace of the \sephiroth{} and with her senses amplified by the mystic mirror, she sent her mind questing through occult dimensions in pursuit of the anomalous power surge. 

Some among the Redcor disapproved of the Waters; some even saw the use of the pool as heresy, a pathway to corruption. 
%But \Esmerel{} knew better. The silvery Waters were a doorway to great wisdom, and after all, 
\Esmerel{} shared none of those fears. 
%After all, 
%she had the protection of the \sephiroth, so why should she fear the shimmering mirror and the visions it showed? 
% \emph{The true heretics,} she mused, 
% \emph{are they who doubt the omnipotence and omnibenevolence of the \sephiroth{}. A truly faithful believer needs have no fear of the mystic mirror and the visions it shows.}
\tho{In doubting the omnipotence and omnibenevolence of the \sephiroth{},} she mused, \tho{they, if any, are the true heretics. A genuine believer needs have no fear of the mystic mirror and the visions it shows.}

No, the Waters of Enlightenment were a gift, and a doorway to great wisdom. And what luck that she had been meditating by the shimmering lake at this very moment, so that the Waters had enabled her to sense the cosmic anomaly, fleeting as it was. \tho{Truly wise is the Light,} she reflected. 

%\tho{But I must waste no time.} 
%But she knew she must waste no time. 
%But she could afford to waste no more time on such speculation. 

Suddenly, darkness. 

She was ripped out of her pious thoughts. 

\tho{Darkness.

Darkness everywhere.}

\Esmerel{} found herself aimlessly adrift amid a huge, endless space. Stars dotted the heavens in all directions, tiny pinpricks against the devouring blackness of the firmament. 
%But however pious these thoughts, they made her lose track of the object of her search. Suddenly she found herself aimlessly adrift amid a huge, endless space. Stars dotted the heavens in all directions, tiny pinpricks against the devouring blackness of the firmament. 
%\Esmerel{} 
She 
shuddered inside, overwhelmed by the sheer vastness of the nighted void\dash cold darkness stretching off into infinity on all sides, 
%black gulfs yawning open like the jaws of some cosmic monster of unimaginable proportions, 
like some cosmic monster of unimaginable proportions, black gulfs like jaws yawning wide open as if to swallow her, to crush her tiny body and soul in its lightless belly. 

\tho{Pull yourself together, \Esmerel,} she scolded herself. \tho{You are above such superstition.} She had to remind herself that as vast as space might be, the Light was greater still. 
With effort, she wrested her astral senses away from the enchanting but terrible vistas of the void and sought instead the consoling touch of the \sephiroth. 

The soothing presence of the \Archons{} gave her renewed peace of mind, %, and she was again able to focus. 
but with the comfort came a silent admonition: \tho{Concentrate on the task at hand.} 

% She invokes \sephiroth{}, and they guide her as her mind sails through the occult dimensions. She floats in a sea of stars, with the blazing \hs{Sun} and the twin \hs{Moons} as her guides. The Light envelops her, yet even so she cannot help but shudder at the great blackness surrounding her\dash cold darkness stretching off into infinity on all sides. She was overwhelmed by the sheer vastness of the void, looming all around as if poised to crush her, and had to remind herself that the Light was greater still. With effort she wrested her astral senses away from those vistas and sought instead the comforting touch of the \sephiroth. 
% 
% The soothing touch of the \Archons{} gave her renewed peace of mind. %, and she was again able to focus. 
% But with the comfort came a silent admonition: \tho{Focus on the task at hand.} 

%\Esmerel{} concentrated on directing the swirling mists of the Waters of Enlightenment. Amplified by the power of the enchanted pool she sent her soul questing along the ley lines of the great Web of the Realms
\Esmerel{} let the blessed calm of the Light flow through her body, erasing her fears and allowing her to focus her senses, and with renewed clarity she reached out through the cosmic threads of the Web of the Realms. 

And she detected it. A slight shivering of a thread. 
%\tho{I will find the source of this }
Swiftly she followed, sending her mind speeding along the thread, the weave and flow of the cosmos swirling around her as she flew. 
%Swiftly, she sent her mind floating along the thread. 
%The weave and flow of the cosmos swirled around her as she sent her mind speeding along the thread. 
As she moved closer, the thread seemed to vibrate more violently, and mystic winds tore at the web around her. Subtle, undetectable to the senses of the common folk, and even most of the initiated. But to \Esmerel, connected to the Realms as she was through the Waters of Eternity, it was like a raging storm shaking the fabric of the Web. 

Finally, the source of the power surge came into her view: A massive \vertex{}, pulling at the cosmic threads, flailing them about like whips. To her eyes the \vertex{} was a burning conflux of raw power\dash shining white interwoven with blood red and pitch black, all spinning in chaotic confusion. 

\tho{A \vertex{} spike! And not just any \vertex, at that.} For \Esmerel{} recognized the pattern of those energies, the vibrations they emitted. 

\tho{A Scion! There can be no doubt. A Scion has awakened! 

An \Archon{} given flesh...}

In that moment, a rogue burst of energy pulsed from the fiery \vertex. A thread wildly, blindly lashed out, striking \Esmerelz{} astral form, sending gut-wrenching pain through her.

Fast losing consciousness from the stress, she felt the \sephiroth{} closing about her, carrying her back to the safety of her body. One thought went through her mind as she dozed away: \tho{I found it. I, \EsmerelFull, discovered the new Scion...}

Oblivion took her. 



