\chapter{Belkade}
\index{Belkade}
\label{Belkade}
\pronun{Belkade}{BEL-kejd} is a region comprising much of \KnownWorld{}. %a quarter of the Known World. 
This chapter will describe the nations, cultures and religions of this region. 

%the region of \pronun{Belkade}{BEL-kejd}. 



%\section{General}



%\sectionnn{\Redce}{Redce}{\Redce}
\section{\Redce}
\label{Redce}
\index{\Redce}

Located at the heart of Belkade, \Redce{} is the homeland of the Vaimon \introd{Clan Redcor}{Redcor} and the seat of power of the \introt{Iquinian Church}. \Redce{} is a theocratic state, and the entire organization of \Redce{} and Clan Redcor is based on the Iquinian religion. The Redcor are a matriarchal people, and their kingdom is ruled by a council of women, called the \introt{Conclave}. The Conclave gather around the Topaz Throne in the capital city of \Redce{}. 

\index{\Redcean}
Note that the Redcor are the ruling class of \Redce{}. A common citizen of \Redce{} is a \Redcean{} (plural \emph{\Redcean{}s}). A believer of the Iquinian religion is called an \emph{Iquinian}. 

The traditional colour of Clan Redcor is yellow. The symbol of \Redce{}, Clan Redcor and the Iquinian Church is a yellow Sun on a blue background. 

The Iquinian Church, also called the \introt{Church of Iquin} or the \introt{Church of the Light}, is based on Iquin-Nieur theory (see section \ref{Vaimon magic}), the idea that the universe is based on two primal forces: Iquin and Nieur, Light and Shadow. The Iquinians worship Iquin and believe that it is the primary, the first and most important of the two, representing all that is just and good. %The Redcor insist that Nieur should be translated `Shadow', because, according to their religion, Iquin existed before Nieur, and Nieur is a corruption of Iquin, something secondary that exists only at the mercy of the Light.\footnote{This is comparable to the role of the Devil in certain Christian interpretations: God and Satan are not equally matched adversaries. Rather, God is seen as all-powerful, and Satan, with all his evil, exists only because God, in all his good, allows him to. Supposedly, this somehow makes sense.} 
The Light is personified as a god, called the \intro{Spirit of the Light}. The Spirit is viewed as a supreme, perfect being, all-good and very powerful, perhaps even all-powerful. The Spirit of the Light is seen as something special because it is `not of this world' but something `transcendent'. The Church tends to look down on religions that worship `earthly gods' (such as the Imetrium), which are seen as inferior, false gods. 

The Iquinians see themselves and their church as the champions of good. They seem to combat and destroy evil wherever they encounter it. The Church of Iquin is widespread throughout most of Belkade. The Church do not rule directly outside \Redce{}, but the Redcor are skilled manipulators, pulling strings and directing events from behind the thrones. 

\subsection{\Redcean{} society}

\subsubsection{Knights: \Ryzin{} and Gandierre}\index{\Redce{}!Knightly orders}
\Redce{} and the Church of Iquin has two orders of knights: The \pronune{\Ryzin}{rhy-ZHIN}, for women, and the \pronune{Gandierre}{gaan-DJEH(RH)}, for men. Many such knights are Redcor, but not most. 

Traditionally, the \Ryzin{} (unlike other \Redcean{} women) cut their hair short and wear trousers rather than skirts. 

%\subsubsectionl{\Ryzin}{Ryzin}
%The \pronun{\Ryzin}{rhy-ZHIN} is the order of female knights in \Redce{} and the Church of Iquin. Most of them are Redcor, but they need not be. 

%\subsubsectionn{Gandierre}
%The Gandierre is the order of male knights in \Redce{} and the Church. 



\sectionn{Geica}
Geica, located in the southeastern corner of Belkade, is the homeland of \introd{Clan Geican}{Geican}. 

Unlike the Redcor, who are purely a Vaimon Clan, Clan Geican is known to accept non-Vaimons `converts', granting them status of full Clan members. Once achieved, Geican status lasts for life and is passed on to all children... or is it? 

The Geicans, ie., the members of Clan Geican, are the upper class of Geica. The regular citizens of Geica are called \introep{Geicanese}{gej-ka-NEEZ} (the term is singular, plural and adjective). About 60\% of the Geicans are Vaimons. 

The traditional colour of Clan Geican is green, and many Geicans wear green robes of some sort. The symbol of Geica and Clan Geican is an eagle in flight (a symbol of freedom), green on a black background. The throne of Geica is of Emerald. 

They are scientists and study all sciences, including magic. They are known to use Nieur and actively pursue the study of it. They are believed to dabble in all sorts of black and evil magic and to consort with evil powers. 

\subsection{Government}
Geica has a democracy and is governed by a Senate of 30 Senators. Only Geican clan members can vote. 

\subsection{Religion}
The Geican culture is atheistic. They reject the personification of Iquin and Nieur that the Redcor believe in. According to the Geicans, the Iquinian religion is a lie: The Spirit of the Light does not exist, Iquin (like Nieur) is just an impersonal, amoral force. All Iquinian `miracles' are regular magic and the Iquinian metaphysics is based on a magic theory that is flawed and contradictory. The Redcor world view is a supremely naive fairy tale that blatantly ignores and denies many elementary facts known to any serious scholar. The Geicans see the Redcor as cowards who close their eyes to the real world because they are afraid to face the dark and terrible truth. In turn, they view themselves as a superior and wiser people, true scientists who pursue the truth without fear. 

Natually, this belief is blasphemous to the Iquinians. To make matters worse, Clan Geican is known to have utilized black magic, and the Dark Prophet \Belzir{}, who caused the Darkfall, was a Geican. As a result, the Redcor believe that the Geicans are all malicious diabolists and alienists bent on conquering or destroying the world. (The Geicans themselves claim that the Redcor are intolerant bigots and prejudiced against them because of a select few genuine villains in Geican history. They are also quick to quote a record of Redcor atrocities in return.) 

%Geicans insist that Nieur should be translated `Darkness', rather than `Shadow', as the Redcor do. To them, Nieur is not a feeble reflection of Iquin, but a primal force, possibly even more primal than Iquin. 
%Some Geican scholars use the parable of the night sky: The natural state of the sky, they claim, is total darkness. The stars, try as they might, cannot eliminate the darkness. If you remove all the stars, the blackness will remain, but it is, of course, not possible to remove the darkness and have only the stars remain. 
% Geican scholars believe that Nieur is, at the very least, equal in status to Iquin. Some say that Nieur is 

%Clan Geican is not centrally organized. Geica is a small nation and many Geicans live abroad, if they can avoid Redcor persecution. Durcac and the Imetrium has many Geican inhabitants. If asked, any Geican will tell you that their clan is unorganized and that they owe no allegiance to the Emerald Throne in Geica. The Redcor suspect that this is a lie and that Geicans living abroad are secret agents and spies of some evil conspiracy. 



\sectionn{Clan \Yrzhell{}}
The \introp{\Yrzhell{}}{yrh-ZHEL} have lost their original homeland and their Onyx Throne. Both were destroyed in the Fourth Cataclysm. Now they are a disorganized and wandering people. 

The traditional colour of Clan \Yrzhell{} is black. 

The \Yrzhell{} are a nature-loving people who practice a druid-like Animist religion. They are generally peaceful, unlike the militaristic Redcor. They live in forests in small communities or stuff like that. 

\sectionn{Clan Quaerin}
Clan \introp{Quaerin}{kwe-REEN} live in the cold, mystic land of Zoitan far to the north. Almost no Quaerin are known to dwell in any other lands than Zoitan, and their dealings with the rest of the world are very limited, so little is known about them and their culture. They are ruled by an Immortal Czar who sits on the Diamond Throne. Their traditional colour is white. 



\input{World/VaimonMagic}
