\section{The Cabal and the Sentinels of Mith}
%An important part of all politics on Mith is 
%In virtually all Mithian politics, two shady organizations play an important part: The Watch and the Cabal. For many thousands of years, much of the history of Mith has been guided and shaped by the conflict between these secret orders, forever sworn to oppose each other. 

In almost all Mithian cultures, stories and myths are told about two secret organizations that exist in the shadows and wage an eternal war for dominion over the planet\dash{}the Cabal and the Sentinels of Mith. They are said to have existed for many thousands of years, if not forever, and the Sentinels are associated with \dragons{} while the Cabal is said to be connected with the mysterious \banes{}, but other than that, little is known about them. Some say that the Sentinels are good, nobly defending Mith against the predations of the evil Cabal, whereas others claim that it is in fact the Sentinels who are evil, and yet others assert that both orders are uncaring manipulators that prey on the hapless people of Mith. 

It is said that the conflict between these obscure forces has shaped the entire history of Mith and that all major heroes, leaders and rulers though time have been manipulated by one (or both) of the orders\dash{}and many are the men and women in history who have been publicly accused, even convicted, of being Cabalists or Sentinels. Both organizations are said to be of otherworldly origin and to work though dark sorcery and \daemonic{} allies. 

But few and far in between are the actual, visible indications of their existence, and indeed, today many people believe that the dark orders are but myth and superstition. Most Belkadians comfortably believe that all \dragons{}, or as near all as makes no difference, dwell in remote, legendary Irokas, and that the wicked \banes{} have vanished from Mith many thousand years ago, if indeed they ever existed at all. Even major kingdoms and organizations know of little evidence that the twin orders exist, and so they are for the most part relegated to the realm of legends. 

Few know even fragments of the truth, and fewer still know the whole truth, but the Sentinels and the Cabal are very real and have existed for nearly ten thousand years, and their importance in Mithian history, even today, can scarcely be overestimated. 

\subsectionthe{Cabal}
The \pronun{Cabal}{kä-BAAL} are indeed the servitors of the sinister \banes{} (see \ref{Bane}). A member of the Cabal is called a \introp{Cabalist}{KÄ-ba-list}. There are thousands of actual Cabalists scattered across Mith, but tens of thousands more unknowingly serve the purposes of the Cabal, and millions more are being subtly manipulated by the Cabalists. Even within the Cabal, most who call themselves Cabalists know very little of their actual purpose, for the Cabal's \emph{modus operandi} is secrecy above all else. 

The supreme leader of the Cabal on Mith is the \banelord{} Daggerrain, who ultimately serves the \baneking{} called \Voidbringer. The majority of Cabalists are \human{}, but they also count \scathae{} and \meccara{} among their ranks, and more than once in history has a renegade \dragon{} turned to the Cabal. 



\subsectionthe{Sentinels of Mith}\label{Sentinels}
The Sentinels of Mith are an organization founded by \dragons{}. Its purpose is to oppose the Cabal and thwart its advances. Its members are called Watchers and consider themselves the defenders of Mith\dash{}true, native Mithians protecting the planet from an alien menace who seek to invade the planet and destroy or enslave her people. In truth, however, much of the Sentinels' work is geared not towards opposing the \banes{}, but towards furthering the cause of \draconic{} dominance on Mith. 
