\bookchapter{Pretty Sally}

\begin{comment}
\subsection{Lighten up}
\end{comment}

\stamp
  {\dateCarzainVolunteers}
  {Pelidorian army camp\\Early morning}

\ta{Come on, fancy-ass, lighten up,}
\Tsekkect{} was telling him. 
\ta{What's there to pout about?
    The Sun is shining and we're marching off to get ourselves killed.
    It's gonna be great.}

\ta{Yes. 
    You know, \Tsekkect, 
    I wish you'd stop calling me \quo{fancy-ass} already.}

\ta{Yeah, you'd wish a lot of things, wouldn't you?} 
she said with her usual foot-wide toothy smile. 

\ta{True,} he had to agree. 
% The \meccaranz{} rudeness was somewhat annoying, but also somehow endearing. 
\ta{Tell me, do you \meccara{} all call each other names like that?}

\ta{Stop saying \quo{you \meccara} like we're all the same, damn you. 
    You \scathae{} and \humans{} think you're the only races in the world with cultures, and all other races are just big crowds of identical people. 
    We come in different fucking kinds, too! 
    For instance, we \Thbatswa{} don't mix with the Ptatchukk. 
    'Cause they smell bad and talk ugly. 
    Also, they steal.}

\tho{Whoa. Talk about going off on a tangent,} 
Carzain thought. 
\ta{My. 
    What an enlightening and insightful monologue. 
    I now repent my wicked prejudice.} 

\ta{Yeah, you should.} 
They both laughed out loud. 

Annoying as the \meccaranz{} rudeness might be, it was also refreshing. 
Carzain had been in a bit of a sulky mood ever since \Forklin. 
His efforts to find and seduce a woman in the city had failed. 
\tho{Another reminder that I'm fallible like any other man. 
     I always hate those.}

Just then, a messenger showed up. 
\ta{\Mister{} \Shireyo?} 

\ta{That's me,} said Carzain.

\ta{Captain Curwen wants you.} 





\begin{comment}
\subsection{Volunteered}
\end{comment}

\new
\placestamp{Archibald Curwen's tent}

\ta{Congratulations, \Shireyo,} 
said Curwen, sitting in his chair and puffing on his pipe. 

\ta{Thanks, Captain. What for?} 
said Carzain. 

\ta{You've just volunteered for a sally.} 
Curwen pointed at Carzain with the pipe's mouthpiece for emphasis. 

\ta{I have? 
    How gracious of me.} 

\ta{Yes. 
    I volunteered you.} 

\ta{How gracious of you, then, Captain. 
    So, who is this Sally? 
    She pretty?} 
Carzain asked with a grin. 

\ta{If you like the sight of dark Wild, 
    ravaged towns and possible fighting, 
    then yes, \quo{she} is quite hot.} 
Curwen's expression remained level. 
\tho{He's probably heard the joke before,} 
Carzain decided. 
\ta{I am leading the mission, and you're coming along,} Curwen continued.  
\ta{We're going to flank the Rungeran army and do some reconnaisance.}

\ta{Sounds like a job for scouts. 
    Or outriders, or whatever they're called. 
    Why us mages?}

\ta{Because we have to ascertain, if possible, 
    what magical weapons the Rungers wield.} 

\ta{All right. 
    Why me?}

\ta{Because I tell you to, you smart-mouthed bastard.} 
Curwen took out the pipe and coughed for some moments.
His breath was foul. 
\ta{Now shut up and go get ready. 
    We leave in an hour.}

\ta{Yes, Captain.}



\begin{comment}
\subsection{No straight lines}
\end{comment}

\new
\placestamp{Kenshaer Forest
            %\\
            %North of the main army's position
            \\
            Two hours later
}
% The sally is: Curwen, Carzain, Delph, \Tsekkect{}, two Rangers (\sphyles) and maybe four more soldiers. 
% Carzain requested to have \Tsekkect{} and Delph along. 
% The Rangers guide them along some hidden paths in the forest. 
% These two Rangers are locals and know these forests like the tips of their tongues.\footnote{\Scathaese{} idiom. A \scatha{} is presumed to know the tip of his tongue very well because he uses it to lick his eyes.} 
% They know all the shortcuts and, with their Ranger skills, can guide them through the Wild much faster than a whole army could travel. 
% 
% Sneaking through the Wild only works with small groups, not big armies. 
% The Ranger tries to explain it to Carzain, but he doesn't understand it. 
% She claims that it's not something that can be explained in regular language, because language is a thing of civilization, and civilization and its trappings are anathema to the Wild. 
% Carzain surmises that the Ranger doesn't really understand it herself and is just trying to hide it. 
Soon Carzain found himself deep in a shady, Wild forest. 
Apart from him the sally consisted of Archibald Curwen, Delph and \Tsekkect{} (included at Carzain's request), two guides and eight more soldiers. 

The guides, \sphyles{} both, were \quo{\rangers}; people skilled at journeying through the Wild. 
Such \rangers{} typically worked as pathfinders or hunters, and were often outcasts in regular society, allegedly due to being \quo{Wild} and \quo{bestial}, not truly civilized people. 
\tho{And no wonder,} Carzain thought. 
They were creepy. 
Especially one of them, Gwelthein. 
She was an older \sphyle, long and thin, with dark green scales. 
And there was something animalistic about her\dash her gait, her gaze, her speech, her fluid movements\dash as if she might at any moment drop down on all fours and start hissing and biting. 
Carzain was reminded of the boy Kreb, who had given off a similarly bestial vibe. 

The younger \ranger, Filcoi, seemed more like a normal \scatha. 
She was shorter and huskier than Gwelthein, leafy green in colour. 
She wore leathers and carried a short, heavy sword, two daggers (that he could see) and a wooden sling. 

\ta{I did not quite understand what the captain said about our mission,} 
Carzain said to her. 
\ta{Why are we in the forest?
    How does that help us?}

\ta{Because we need to take a short cut and outflank the Rungerans,}
Filcoi explained. 

\ta{Um... how is this a short cut? 
    According to the maps, the main road is practically a straight line. 
    Surely the way through the woods must be a detour?}

\ta{You should not put so much faith in the lines your maps. 
    They may work fine in settled lands and roads, but the Wild does not obey maps.}

\ta{Well, granted, 
    the maps may be inaccurate when it comes what goes on in the Wild. 
    But this must still be a detour compared to the straight road...}

\ta{No, I don't just mean the maps are inaccurate. 
    I mean what I said: 
    The Wild \emph{does not obey} maps. 
    There are paths out here that you can't even draw on a flat map.}

\ta{But, look. 
    In geometry you can prove that the shortest possible route between two points is a straight line.} 
Carzain drew lines and points in the air with his hands.
\ta{All right? 
    So you are saying you can find a route that is shorter than the shortest possible route?}

\ta{I'm no scholar. 
    I don't know what \quo{geometry} is. 
    But yes, I am saying that we can find a route shorter than the straight road. 
    At least, I hope we can.}

\tho{Sounds like total superstition to me,} 
Carzain almost said aloud. 
\tho{Still, it was Curwen who ordered this whole thing. 
     One would think he would know what he is doing. 
     This just doesn't make any sense...}

Filcoi smiled, noting the incomprehension on his face. 
She pointed with her thumb back the way they had come. 
\ta{Back there\dash the road, \Forklin, Malcur\dash%
    that's a world of straight lines and nice curves.}
Carzain smiled and almost giggled when she said \quo{nice curves}. 
\ta{Out here is the Wild. 
    The Wild is not made of straight lines. 
    Out here, paths are crooked and winding. 
    They go places you don't expect them to. 
    They lead you places you didn't know you were going. 
    Places you didn't even know were there.
    Your eyes can deceive you. 
    If you know your way around, you can cross great expanses of Wild in no time. 
    If not, you can walk in a straight line for days and get nowhere.}
She fixed him with her gaze. 
\ta{It's not that the maps are inaccurate.
    \emph{No map} can depict the Wild. 
    The Wild does not obey the laws of straight lines and flat surfaces that the civilized world does.} 

Carzain gulped. 
\ta{Really?}
\tho{Damn. 
     I had heard stories about how the Wild twists around you and how it drives you mad because nothing makes sense. 
     But I always thought they were just superstition.
     Creepy stuff. 
     
     No wonder people shun these \rangers.}

He studied the \ranger. 
\tho{Hm. I still don't quite buy it.}

\ta{You don't believe me, do you?}
asked Filcoi. 

\ta{Well...}

She laughed softly. 
\ta{You know, you mages always think you know more than you do. 
    I mean, sure, maybe you can zap people with lightning, or whatever it is you do, but do you know how the world really looks outside your towers and libraries?}

Carzain turned that around in his head. 
\tho{Actually, it takes a great deal of understanding 
     of how the unseen worlds work before you can zap anyone with lightning.} 
He smiled.
\tho{And moreover: 
     Overconfident? 
     Who, me?
     No way. 
     Among my many virtues, humility has always been the foremost.}

He studied the darkness of the wood again. 
\tho{Hm. I don't know. Could she be right?}

\ta{My point is, Mith is vaster and darker and more mysterious than most of us realize,} 
Filcoi concluded. 
Then she spurred her dark gray \relc{} on ahead, leaving him. 

\begin{comment}
\subsection{A fucked-up place}
\end{comment}

% The Rangers know this area better than the Rungerans do, so they should be able to outpace, outmaneuvre and outflank the Rungeran army. 
% Curwen wants to take a look at their trail and see what he can sniff up. 

Carzain looked around at the chaotic mass of branches and leaves surrounding them. 
\tho{No matter how I look at it, 
     this doesn't look like a shortcut to anything. 
     The way it looks to me, we are going nowhere, and slowly.}

\tho{I'll try Curwen again.
     He's an academic.
     He ought to speak my language.}
He sought out the captain. 

\ta{Captain,} said Carzain. 

\ta{What?} Curwen barked. 

\ta{Is it true that the \rangers{} can find a path 
    that's shorter than the geometrically shortest way possible?}

\ta{That's what we pay them for.
    And they didn't come cheap, either, so they had better.}

\ta{But how on Mith is that possible?
    Do they use some kind of magic?}

\ta{It works because the Wild is a fucked-up place. 
    What do I know?}

Carzain turned his face away so he could roll his eyes without Curwen seeing it. 
\tho{Because the Wild is a \quo{fucked-up place}. 
     How enlightening.} 

He looked up.
They were deeper into the forest now. 
Branches enveloped them, all but blotting out the Sun, like many-fingered hands reaching out to crush them. 
He shuddered. 
The cramped twilight and the rustle of arms brought back memories of the last time Carzain was marooned in the Wild with a bunch of soldiers. 
Back in Heropond with the mutineers. 

\vizicar{But I slew them.} 

\tho{What?
     What was that?
     \Qliphoth. 
     Please tell me that was just my memories of last time. 
     Please tell me I am not hearing voices in my head.
     Again.}

% Carzain is disturbed by the spookiness of the forest. 
% He remembers the last time he was deep in a spooky forest. 
% Maybe Vizicar remembers, too. 









