\documentclass[a4paper,10pt,openany,oneside]{article}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{makeidx}
%\usepackage{showidx}
\usepackage[pdftex,colorlinks]{hyperref}

\title{Sentinels of Mith\\Story Fragments}
\author{Claus Appel \\ 
E-mail: \href{mailto:spectrumdt@gmail.com}{spectrumdt@gmail.com}}

\makeindex
\frenchspacing
\pagestyle{headings}



\begin{document}



\input{CommandsMath}
\input{CommandsBeginEnd}
\input{CommandsLabelIndex}
\input{CommandsMith}



\maketitle



\section{Carzain and Lacquasse}
Some distance away on the battlefield, Carzain recognized Lacquasse, his old arms instructor among the Redcor. He sought her out. 

\talk{Lacquasse!} he cried. \talk{Lacquasse! Face me!} 

The Redcor Mistress-at-Arms struck down a Scathaese warrior with her fiery sabre, then turned and made her way toward him. 

\talk{Carzain, you wretched traitor!} she called. \talk{How could you betray us so? Have you no honour?} 

\talk{\Ryzin{} Lacquasse... Mistress-at-Arms.} Carzain smiled and made a mocking bow. \talk{Among the Redcor you were one of the select few whom I could respect. It pains me that we must now meet as enemies.} 

\talk{Pains you? This entire war is your doing!} 

\talk{It is the Conclave's doing!} he screamed, his voice full of rage. \talk{Clan Redcor brought this upon themselves! In all my time among the Redcor I was awarded naught but contempt. Yes, I stand as your enemy, but you have none to blame but your own people!} 

\talk{But how could you find it in yourself to serve \Belzir? Carzain, she is evil! She means to enslave all of Mith!} 

\talk{How are the Redcor different? Your Clan treat their own people as slaves. They see all people as their slaves! Who is evil here, if not the Redcor?} 

\talk{You... you are beyond redemption, Carzain!} Lacquasse's voice and face showed anger, but her hesitatation betrayer her, and in that second, Carzain recognized the guilt in her eyes. 

\talk{You know that I speak the truth, Lacquasse!} 

\talk{NO! It is you who are evil! Die, betrayer of the Light! Feazin!} And with those words, Lacquasse leapt towards him, the power of Feazin\footnote{Feazin, a \Sephirah{} of the wind.} propelling her forward, her sabre stretched out to impale him. 

Carzain was not idle. Invoking aloud \talk{\Izion!\footnote{\Izion, a \Sephirah{} of fire.}} he conjured a ball of fire and hurled it at her, while simultaneously and silently conjuring Feazin to leap high and out of her way. Lacquasse reacted quickly, nimbly swerving in midair to dogde the fireball (which flew into the fray to incinerate a random fighter), then turning to call upon \Izion{} and launch at him a missile of her own. Carzain called for the Kliffah Horvaleth\footnote{Horvaleth, a Kliffah of cold and ice.} to counter with a massive blast of ice, intended not only to strike his opponent, but also to counter her fireball. 

But Lacquasse was nimble. As his sight cleared, Carzain found she had swiftly dodged his attack and was flying straight towards him. Her tactic was clear: She knew that in a magical duel he would overwhelm her by sheer brute force, but in close combat her skill at arms was superior. Her goal was therefore to close to melee range quickly, whereas he sought to keep her at bay and bombard her with his magic. 

%Carzain fired a powerful wind at her to knock her out of course, followed by a barrage of icy missiles. But again she was too quick, managing to avoid his attacks and still close in on him. All this happened in a matter of few seconds, and Carzain still hanging in mid-air from his magically-assisted leap, cursed himself for not having taking the time to learn flight. With Lacquasse being an expert flier, far surpassed maneuverability 

Summoning Iphicoss\footnote{Iphicoss, the Kliffah of the treacherous gale.}, Carzain hurled a powerful wind at her to knock her off course, followed by a barrage of icy missiles powered by Horvaleth. But again she was too quick, managing to evade his onslaught and still close on him. Lacquasse's advantage was her skill at flight and her control of Feazin, which afforded her superior maneuverability, and Carzain, still hanging in mid-air from his magically-assisted leap (for all this had transpired in a matter of seconds), cursed himself for not having taking the time to master this \Sephirah{}. 

%channelling Air to disperse the fireball, then nimbly turned in mid-leap

Carzain decided he had to gamble. Keeping up his bombardment with bolts of ice, he waited until Lacquasse was almost within melee range. Then, digging deep into his reserves of power and summoning aloud \Izion, he fired a tremendous fireball in her face at point-blank range, then turned again to Iphicoss to strike with a mighty gust of wind, not at Lacquasse, but at himself, knocking himself out of her grasp and to the ground. His landing was rough, for he had neither the time nor the skill to maneuver, but he sprang to his feet and saw that his ploy had been effective. Lacquasse had been unable to deflect the fireball at such short range and was hit with full force. She was fallen to the ground, but regained her footing quickly, her magical shield having absorbed most of the damage. 

She was still perilously close, so Carzain leapt backwards while firing projectiles of ice at her. Lacquasse called for Feazin and took to the air again, avoiding his missiles and launching a fireball at him. He directed a stream of cold at the fireball to dispel it, but Lacquasse was lightning-quick, drawing again upon Feazin to weave a powerful gust of wind to throw his own frost-blast back at him. Carzain moved to dodge, but Lacquasse came again swiftly, channeling the power of the \Sephirah{} Curomon\footnote{Curomon, a \Sephirah{} of the Earth, is normally invoked to move and Sculpt earthen objects.} to hinder his movement while guiding her magical wind around. He reached out to dispel the attacks, but he was too slow and was struck not only by his own blast of frost, but also by Lacquasse's fireball. 

Carzain reeled from the hit, and again Lacquasse charged forward. She held fast Curomon, but he managed to break the \Sephirah{}'s hold barely in time to raise his sabre and defend himself. Again and again she struck, swift and deadly as the cobra, but he managed to keep her at bay. Eventually she missed, and immediately he sprang aside, Feazin-assisted. But alas, he had failed to discern her feint, and she came around to cut into his side. Crying out in pain, he managed to leap further back and deflect her next thrust. Lacquasse reached out with Brycorre\footnote{Brycorre, a \Sephirah{} of wind and storms.} and threw a gust of wind into his back, pushing him forward toward her. Carzain would have been impaled on her sabre, but managed, by virtue of his sheer magical strength, to seize hold of the \Sephirah{} and twist its force around, pushing him aside and out of her way. Lacquasse thrust with her sabre and struck a deep blow in his left arm. He grunted in pain, but at this point he was soo deeply into the battle-fury of Nieur that the pain caused him to instinctively lash out with Nyxachel\footnote{Nyxachel, the Kliffah of Nieur lightning}. Through the sabre in his right hand he fired a bolt of Nieur lightning and hit her with full force. Feeling the vileness of Nieur surge into her body, Lacquasse reeled in pain, and Carzain blasted her with another bolt from Nyxachel, then seized Feazin to leap backward, away from her. 

Lacquasse recovered and rose. \talk{Kliffoth take you and the Light forever scorn you, betrayer,} she hissed. \talk{I can slay you yet. Fall into the darkness and DIE! Feazin!} With those words she lunged forward again, the full force of the \Sephirah{} at her back. Carzain, having gained several metres of distance, fired icy arrows of Horvaleth at her. She swerved to the left, avoiding them, and Carzain fired additional missiles, slightly to the right of the position, in an apparently obvious attempt to force her to swerve futher left. Taking this for a feint, meant to drive her back to the right, she swung left, easily avoiding the missiles, but she had failed to see the feint within the feint. The instant she moved left, Carzain was already reaching deep into Iquin, conjuring both \Izion and Feazin to create a mighty fireball, propelled forward by a strong wind. She saw the fireball and dodged upwards, but Carzain called Feazin to push her back down into the missile's path, countering her skill and agility with brute force, only his immense strength allowing him to hold these powerful Sephiroth all at once. 

Lacquasse had no time to counter his spells or attempt another dodge, so she braced herself and flew straight through the fireball. She was still coming at him at full speed, but she was weakened by the hit. At this close range, Carzain lashed out with Nyxachel and tore straight through her magical shield. Lacquasse screamed, but she still had the strength to swing her sabre, penetrate his shield and cut a deep gash in his right leg. Enduring the pain of the wound, Carzain kept up the stream of Nieur lightning, and Lacquasse, in her weakened state, could do nothing but writhe on the ground. 

\talk{Lacquasse,} he said. \talk{Among the Redcor I held none in higher regard than you. It pains me to slay you.} 

She managed to spit. \talk{Bah! I still curse you, betrayer. Enjoy slavery under your new Queen!} 

\talk{Under my new Queen? Hah. I think not.} Carzain raised his sabre. \talk{Lacquasse daughter of \Brizen of Clan Redcor... return to the Light.} With that, he swung the sabre and severed her head in one clean stroke. 




\end{document}

