\bookchapter{Silenced}
\timestamp{\dateCatrianDies}
%\datestamp{Carz}{21st}{\Hoshied}
%
\tho{It had no face! Great gods, the creature had no face! Take it away! Chaos preserve me, take the vision away from me!}

Catrian ran, trying to wipe from her memory the image of the horrible creature she had seen. Her dress and shoes were not made for running, but she pushed on. \tho{I must hurry. I must tell my masters. The enemy is here!} 

She felt a sudden blow. 

She was aware of the ground rushing up to meet her. 

\ta{Hey! Watch where you are going!} The voice was that of an angry man. 

She lay prone on the ground next to him. Still in shock, Catrian had been running in a haze and had not seen the man before colliding with him. 

Hastily she climbed to her feet and set off again. \ta{Crazy woman! And rude besides...} Catrian ran on, sparing the man neither word nor glance, barely even an ear. 

\tho{Gods, the horror!} She could not forget the vision of the thing. Many years now had she served her masters, and many and strange were the sights she had seen: Forbidden magic, rituals, weird creatures, even a \dragon{} on one occasion. She knew of the enemy, but she had never before actually seen one. 

Until today. 

It occurred to her that perhaps she had never truly believed that they existed. She \emph{knew} they existed, that they had walked on Mith in the past and that she and the secret society worked to oppose them, that the brotherhood had been created to fight them if they should return, but never had she actually believed that they would return in her lifetime. And least of all had she expected to meet one. 

Until today. 

As she saw the man in the inn she had felt something strange about him, so she had fingered the rune-carved talisman she carried and whispered the spell-words to grant her the second sight. (Catrian was not a true mage; she only knew the spells to activate a few enchanted items.) 
% silently cast her spell of second sight. 
And then she had seen the man's true form: A seven-foot-tall humanoid with bluish-black skin and four strange-looking fingers on each hand. But the most terrible aspect of the creature was its face, for it had none; its head was blank, smooth like an egg, the only distinguishing features a pair of ear-like appendages at the top. 

Seeing the creature stunned Catrian for several moments. She knew what is was: One of the sinister ones, the enemies of Mith, whom she was sworn to combat. But her mind struggled against the revelation. And then the thing turned to her! Its blank, eyeless face did not move, but she could feel its malefic gaze upon her. She felt the thing reach out through the Beyond with its mystic tendrils. She turned and ran. 

She knew what she had to do. \tho{I must reach my masters. I must tell them of this.} She ran in a panic, headed for the house of Mister Dorian, her superior in the brotherhood. She was not certain the thing was following her, but surely it must be. 

Meaning to cut through an alley, Catrian turned at a corner, then halted. In the alley before her stood a woman and several men, all staring directly at her. 
The woman was in her middle years, with the look of a Redcor: tall and blonde, and clad in a robe of brown and yellow. 
The men were all armed and mean-looking. 

The woman raised her hand in Catrian's direction and spoke something that she could not hear. The men made to advance on her.

Catrian knew immediately that these were not mere ruffians. \tho{I have been discovered! The sinister ones' lackeys have come for me.} She could not look away from the woman, whose eyes gave an impression of a cold... \emph{evil}. \tho{They have come for me. I am going to die.}

Then, as Catrian stood and watched in fear, the evil-eyed woman seemed to change shape before her eyes. She grew, gaining more than a foot in height, her skin faded to black and her face to a smooth mask, featureless safe for twin ear-like protrusions. \tho{Another one! Another one of the creatures... the enemy!} The monster reached out for her, and its mystic hands seemed to fill her entire field of vision. 

Catrian turned and ran from the alley. 

So great was her terror that for several moments she knew nothing save that she was fleeing. Then she realized that she did not recognize her surroundings. This confounded and frightened her, for she had lived in the city all her life and knew this area very well.
%, so that it should be impossible for her to lose her way.
Nonetheless, her surroundings were strange, alien. The ground was no longer brown dirt but gray dust. She looked up and saw that the entire world had changed around her. There were buildings, but the wooden planks looked unnaturally dry and desiccated, and stones looked porous, ready to crumble to dust. The street seemed more narrow, more cramped, and the taller buildings loomed menacingly, as if poised to crash down upon her and drag her down in the deep like the claws or teeth of some hungry, undead giant. 

Still running, not daring to slow down, she studied her surroundings. There to her left she recognized a house: Anton the baker's shop. It was discoloured and sickening to look at, but it had retained its familiar shape. And there to the right was the house of Morris Neil's son with its characteristic round windows. 
She realized that she must still somehow be in Bendaire. The houses and streets were the same as those she knew, but warped somehow. 

%Something caught Catrian's foot, and she nearly fell on her face. Looking down, she cried out loud in revulsion. She saw now that the ground was not uniform, gray dust as it had first seemed. 

There were people in the streets also, but they too were warped. On many, the skin was unnaturally pale, sickly, like that of corpses. She noticed that the people were in different stages of decay: Some still had colour and looked mostly alive, but others were deathly white and moved sluggishly, slumped over, like the walking dead. On some of the people she could see what looked like chains attached to their necks or arms, trailing off into nothingness. 

She looked up and saw that the sky had been twisted as well: Instead of blue it was a pale gray, and the Sun was not yellow but ghastly white, like the Pale Moon, and its rays were cold, sharp and cruel, mercilessly revealing and emphasizing all the ugliness and the stagnation and the decay of this nightmare world. 

She ran past a wagon in the street and was startled when a man walked out behind the wagon and almost bumped into her. The man recoiled and spoke something, but she could not hear him over her own scream. 

The man had no face! 

His skin was pale, almost white, unlike the black of the sinister ones, but his face was a blank egg like one of theirs! 

Still screaming, Catrian ran away from the man. Across the street she ran, almost colliding with an old woman. Catrian glanced at her and shrieked again. 

She too was faceless! 

On she ran. A beggar looked up at her from the gutter. He had no mouth! And there was a young girl in a red dress, but she had no eyes! As Catrian glanced at the people around her, she was dismayed to find that only a few had normal faces. Some lacked eyes, or ears, or a mouth, and some were entirely faceless.

%She glanced at the people in the street and was horrified to see another faceless one pass her by. And another! And more! In fact, only a few had normal faces. Some lacked eyes, or ears, or a mouth, and some were entirely faceless.
%Of the rest, not all were entirely faceless; some merely lacked eyes, or ears, or a mouth. 

Crying in desperation now, tears running down her face, Catrian ducked into an alley to escape the horrible throng of faceless people. Then she began to hear strange noises from behind her; croaking, gargling, yelping noises. She ran on through the dark alley, but the noises came closer, ever closer. 

Suddenly there appeared before her a figure. It was a woman clad in a black-and-blue dress. Her face was blank, and about her was an aura of malevolence, almost like shards of dark ice, a blizzard encircling her. It seemed to strike Catrian with physical force. She recoiled, turned about and made to run. 

But what she saw caused her to freeze in place. 

They were like huge rats, as large as dogs, and they walked or hopped on long, strong legs. Their skin was brown and their sparse fur was a dark yellow, like patches of mold on their bodies. They had long jaws filled with sharp teeth, and their great, bulging eyes were pale and dead. Six or seven in number, they were the creatures who had made the gargling noises she had heard. They had caught up to her. 

%They encircled her. 

All thought of informing her masters was gone. Catrian thought only of how to escape with her life. \ta{No,} she whimpered. \ta{No! Get away from me!} 

The largest of the rat-things crept closer. It opened its mouth and licked its lips with a tongue that was pinkish-gray, parched and dry. 

\ta{Get away!} She wept. 

The thing jumped. She screamed as the thing sunk its teeth into her belly. The pain was terrible, unnatural, as if the thing tore not at her flesh but at her soul. She fought feebly to fend it off with her arms, but then felt a jolt of pain from her shin, and another from her buttocks, and another from her shoulder. She fell to the ground as the entire pack of rat-beasts swarmed over her. 

Some yards away, the faceless woman watched motionless as Catrian, screaming and weeping, was ripped and torn asunder by the hideous rat-things.
% fell to the ground, the entire pack of rat-beasts swarming over her. 
Then she turned away and left the alley by a door into one of the shady houses. 

Her work was done. 

%Catrian died in pain, screaming and weeping, ripped and torn asunder by the hideous rat-things. 



\new
Gaston saw the woman run into the alley, wild-eyed and shouting. He knew her. \tho{Gerald the weaver's wife. What is her name?} She was middle-aged, brown-haired and wearing a green-and-brown dress of wool. \tho{She is the daughter of Morgan the carpenter. What is her name?} At first he intended to simply move on, to let others deal with the matter, but as the woman's screams grew even wilder in the distance, he felt that maybe he should investigate. 

\tho{Catrian, that's it. That is her name.}

He walked the way she had gone. \emph{Poor woman.} The weaver's wife had always been somewhat strange, Gaston thought, and now it seemed she had gone mad. 

Cautiously he approached the alley. It was the middle of the day, of course, but even so, dark alleys could be dangerous. Consorting with the mad had its perils, too. 

He turned around the corner and into the alley. At first he could see nothing, for the buildings were tall and cut off the sunlight. But as he walked a few yards into the alley he saw her. She was lying motionless on the ground. He approached her. \ta{Mistress Catrian!} he called. 

No response. 

He walked up to her to take a closer look, then pulled back in shock from her face. It was contorted in a morbid grimace of pain and terror, glassy eyes staring blindly into space. She was dead. Gaston thought about touching her to be sure, but the idea of touching the dead, mad woman disgusted him. \emph{There is no need. She is dead, that is plain to see.} 

He examined her. There were no wounds that he could see. Her dress was unharmed and there was no blood. \emph{Probably died of madness,} he thought. Madness was sometimes fatal, he knew. He felt sorry for her. \emph{Strange to think that she was evil.} After all, it was well-known that only wicked people went mad. Madmen were those who had abandoned the Light, sold their souls to dark powers or simply turned away from the Light. Fools and sinners who vainly believed that they could live without the Light. For these sinners, eventually their wickedness caught up with them and they went insane, deprived of the blessing of the Light. It was known. 

He turned from the body. It was not his worry, after all. He would inform the guards or the church, and the matter would be dealt with. Gaston walked away. 

Not his worry. 
