\chapter{Cosmology}

\section{Chaos and Cosmos}

\begin{quote}
A fundamental axiom of classic Dessalic metaphysics is the idea that the Universe is driven by two fundamental forces, Chaos and Cosmos. Chaos is the force of disorder, conflict and destruction, whereas Cosmos is the force of order, harmony and creation. 

According to ancient, apocryphal legends of unknown origin, in the beginning there was only Chaos. From the random twisting of Chaos, Cosmos was born. According to these legends, the Cosmos, and the Universe we know, is a small bubble floating in an infinite ocean of Chaos. 

The source of these stories cannot be ascertained, but they cannot be litterally true, for our research indicates that the very concepts of time and space are Cosmic in nature and have no meaning or existence in a Universe of pure Chaos. Thus, any talk of a 'time before the Cosmos' or a 'place beyond the Cosmos' is nonsensical. 
\end{quote}

%The stories also tell of a titanic war, as the gods of Cosmos clashed with the monstrous beings of Chaos for control of the Universe. 

\section{Dimensions}
The Universe is divided into a number of parallel universes, or \emph{dimensions}. The dimensions are coexistent, and every geographical location in one dimension corresponds in some sense to an equivalent location in all neighbouring dimensions. Also, many natural and supernatural forces reach into and affect objects in other dimensions. 

\subsection{Gravity}
As an example, the force of gravity reaches into neighbouring dimensions in almost unchanged form. For this reason, large bodies such as stars and planets will almost always correspond between dimensions. So where the planet Myrrnoth lies in the Myrrnoth dimension, there lies a planet of identical mass in the dimension of Hell, following the same orbit around the Black Sun, which is the Hellish equivalent of the Myrrnoth Sun. 

\subsection{Proximity}
Some dimensions are easily reached, while others can only be reached using very powerful magic or under special circumstances. This is usually approximately reciprocal, so if it is easy to get from A to B, it is just as easy to get from B to A. 

If two dimensions are easily reachable from each other, they are considered 'close' or 'neighbours'. A dimension that cannot be easily reached is considered 'distant'. 

Of course, 'easy' is relative. Unless you are near a portal, it is not possible to travel between dimensions without the use of powerful magic (or, at higher TLs, science). 

\subsection{Material and Ethereal Planes}
There are many different dimensions in the universe. The most well-known and well-traveled dimension can be divided into material and ethereal planes. 

The Myrrnoth dimension is a material plane, as are Hell and Caelum. 
Do material planes have any identifying characteristics? 

As far as we know, it seems that every material plane has a corresponding ethereal plane. The ethereal plane corresponding to the Myrrnoth plane is called Limbo. 

\subsection{Cosmic and Chaotic Dimensions}
Each dimension maintains a certain balance between Cosmic and Chaotic forces. Some dimensions are more Chaotic, however, while others are more Cosmic. The dimensions seem to be arranged in a "chain", each dimension bordering onto a Chaotic neighbour and a Cosmic neighbour. 
