\chapter{Old overview}
\section{The First \Dragons}
The \leviathans{} live in the sea. 
\HesodN{} urges his fellows to explore beyond the sea. 
They do, bringing along hordes of Nagae. 

When they go ashore, \HesodN{} proclaims that he and his fellows are no longer merely \leviathans{}, but that this day sees the founding of a completely new race. He names their people in the True Tongue, calling them \draecchonosh{}. It is a word that does not translate easily into Nag or any other language, but even those not learned in the true tongue can readily hear, when \HesodN{} speaks it with passion, that it is a word that speaks promises of strength, power, beauty and dominion. 

On land, \HesodN{} and his fellow \leviathans{} encounter impressive and inspiring creatures, such as \nycans, \cregorr{} and \wyverns{}. \HesodN{} shows his fellows these creatures and proclaims that he and his people will draw on the strength and beauty of these creatures and so become greater than any \leviathan. 

In a process that takes many years, \HesodN{} and his people absorb and assimilate the power and being of many land-living creatures, gradually transforming their own bodies, taking the best of what nature has to offer in the shape of various animals, and adding that to their own bodies. 
%They draw on the power and being of these creatures to transform their own bodies, taking the best of what nature has to offer in the shape of various animals, and adding that to their own bodies. 
\TyarithXserasshana{} is the first to pattern herself after a \wyvern{} and grow wings. 
%\HesodN{} and his closest companions transform themselves into magnificent \dragons{}, showing off their greatness and power and inspiring their Naga followers. 
%When they have transformed enough, \HesodN{} proclaims that they are no longer \leviathans{} but \draecchonosh{} - \dragons. 

The nascent \draconic{} kingdom establishes several cities near the shore. It turns out that the Nagae are ill suited to life on dry land\dash many Nagae are killed by wandering monsters and beasts. They encounter Cortios, and the \dragons{}, impressed by the majesty of these monsters, start creating the \cregorr{} in their image, as a race of warriors and protectors. 

The \cregorr{} are a great success and quickly become a large, respected warrior caste. With the \cregorr{} armies the \dragons{} move inland, claiming more territory from the monsters, \nephilim{} and other creatures that may inhabit the land. 








\section{Prince Semiza}
We also follow Semiza part of the time. 
Semiza is the eldest son of the \nephil{} sorcerer-king of Jocain. 
Early on we see him passing some kind of \quo{manhood test}, marking him as a full-fledged sorcerer and a worthy heir to the throne. 

At an early point, Semiza meets some girl that he likes. 
Either right after his rite of manhood or some time after, he is betrothed to her. 

Some years pass. 
The Jocainites hear the tales of war, of some terrible invaders from the sea devouring entire kingdoms. 
The king and mages are concerned, but Semiza is still young and untroubled. 

Then comes the day of Semiza's wedding. 
On this, supposedly the greatest day of the young prince's life, the \dragons{} invade Jocain. 
It becomes massacre and young Semiza sees his bride and his entire family slaughtered before his eyes. 

Semiza and a few survivors flee to a system of underground caverns. 
Somehow they manage to survive the \draconic{} army's onslaught. 
Semiza assumes the mantle of king and leads his people in exile. 







\section{The \Dragon{}-\Leviathan{} War}
Meanwhile, tension develops between the \dragons{} and the \leviathans{} living in the sea. At this point, the early \scathae{} are developed. The \leviathans{} decide that they have \quo{stock} in \ps{\HesodN}{} terrestrial kingdom and demand tribute. Some \leviathans{} also believe that the \dragons{} and their creations are abominations that should be destroyed. \HesodN{} refuses to pay any tribute, and the \leviathans{} attack. 

The \dragons{} are outnumbered, but they have done experimentation and research and discovered new, more daring and dangerous forms of Chaos magic and \daemon{} summoning. Among the greatest of the \draconic{} sorcerers are \HesodN, \TyarithXserasshana{} and her consorts. Summoning forth \daemonic{} aid from the Beyond, they manage, after a hard struggle, to turn the tide of the war and vanquish the \leviathans{}, who slink back into the sea. 







\section{Semiza, king-in-exile}
Meanwhile, in this great civil war, the \nephil{} survivors have been forgotten. Hiding in his underground lair, Semiza nurtures his hatred and dreams of revenge against the \dragons{}. 

Somehow Semiza reaches out into the Cosmos with his mind. Perhaps he is deliberately searching for allies; perhaps he takes mind-expanding drugs. By whatever means, he contacts Daggerrain. See, the \baneking{} \Voidbringer, Daggerrain's master, had felt the cosmic ripples caused by the \dragons{}' spellwork. 
%Tiamat's spellbinding. 
So \Voidbringer{} ordered his servant Daggerrain to investigate. Daggerrain probed with his mind toward \Miith{}, and shortly after, he found a \Miithian{} mind that was open for him to contact: that of Semiza, the \nephil{} king-in-exile. 

Daggerrain penetrated the \ps{\nephil} vulnerable mind and probed around in it. He took from the sorcerer-king's mind his language and his entire memory. Then he introduced himself to the \nephil{} king, offering him the power to take his revenge, destroy the \dragons{} and restore his kingdom to rule forever. At this point, Semiza asks \ta{Who are you?}, and in response Daggerrain sends a vision where Semiza finds himself alone and naked amid an endless, featureless plain, with a cruel and unrelenting hail beating down upon him with its sharp shards of ice, like a rain of a million daggers. Semiza interprets the \banelord{}'s name as \quo{Daggerrain}. 

If he is to help Semiza and his people, Daggerrain needs the \nephil{} sorcerer to bring him to \Miith{}. He instructs the \nephil{} in the spells to use, and Semiza goes to work procuring occult ingredients and sacrifices (mostly \scathae) and recruiting and training mages to assist in the spellwork. The preparations take perhaps several years, but at last they are ready to perform their summoning ritual. 







\section{The \Banewar}
The gateway to \Erebos{} is opened and Daggerrain's legions swarm forth into \Miith{}: millions of \bane{} warriors and beasts, and hundreds of \banelords, all led by Daggerrain himself. They invade and attack the \draconic{} kingdoms. 

The \dragons{} are hard pressed. Then \TyarithXserasshana{} steps forth. She is the daughter of \HesodN{} and a daring and talented sorceress, having conducted much research into forbidden magic together with her two consorts, Urzmagond and \ApepNesthra. She promises that she will be able to summon forth aid to vanquish their foes, but to do that she will need more power. She asks that the \dragons{} lend her their strength, pour their energy into her body in an arcane ritual, that she might bind the \daemons{} of the Beyond to her will, to serve her people forever for the glory of all \Dragonkind. 

She has her supporters and detractors. As the war with the \leviathans{} continues, however, the \dragons{} continue to lose ground and support for her plan grows. Soon enough \dragons{} acquiesce to support her. She begins her ritual, assisted by Urzmagond and \ApepNesthra, draining strength from her fellow \dragons{} and taking it for herself. With her augmented power, \Xserasshana{} reaches deep into the Beyond and spellbinds multitudes of \daemons. Her bindings lay the foundations of Chaos magic. She discovers Kingstongue and uses it to command the \daemons, and her spells of binding enslave the \daemons{} to her spellwords, so that future sorcerers can call upon those same \daemons{} using \ps{\Xserasshana}{} words. 

With her newly developed magic, \Xserasshana{}, flanked by her consorts, lead the \draconic{} legions into battle. Her newfound power is tremendous, and after a long and bloody war, even the terrible \bane{} legions are ultimately driven back. With enormous effort, the \dragons{} manage to close the gate to \Erebos{}. This cuts the \banes{} off not only from reinforcements, but from the source of their magical power. After this climactic strike, the remaining \banes{}, while they still number in the hundreds of thousands, are rounded up and destroyed. Only Daggerrain and a small force survive, and they hide underground with Semiza and his \nephilim. 
\Xserasshana{} is hailed for this glorious victory. 

Now, I have to devise a good explanation for this, but somehow \Xserasshana{} has only \quo{borrowed} her power from the \dragons{}. They expect her to relinquish it again when the battle is won. I expect they have some way of forcing her to relinquish it\dash or at least think that they do. But \Xserasshana{} has deceived them: When they try to reclaim their power, she denies them and keeps it for herself. Instead, she lashes out with it and forces the \dragons{} to obey her, proclaiming herself the supreme god of the new world. When her father, \HesodN, confronts her, she slays him, claiming that the supreme god can have no father. 

\Xserasshana{} lets her closest lovers and progeny share in her great power, and they become the \Dominators. (I don't know yet if all the \Dominators{} are born and full-grown at this point, or if some come later.) 
Many \dragons{} rebel against \Xserasshana{}, but enough support her, and eventually she destroys the rebels and rules supreme. 

\Xserasshana{} has a third lover, Saphlethcurir. He opposes her gambit for power and fights against her. Ultimately she slays him. But I should make him a major character, so the reader cares when he dies. 







\section{\ps{\Xserasshana}{} reign}
\Xserasshana{} rules the kingdom of the \dragons{}. With her command of the Beyond this evolves into a trans-dimensional empire spanning not only \Miith{} but reaching into the dimensions of Chaos bordering it. 

This kingdom endures for a thousand years or two. 

But during all this time, the \banes{} still exist. Daggerrain and the surviving \banelords{} survive together with Semiza's \nephilim. They do research and experimentation, partly to reopen a gateway to \Erebos{}, and partly to create the heirs of the \banes{}, merging their own \erebean{} power with the changefulness of Chaos. 

(I need to think this through better, but the idea is that the \banes{} are very ordered, structured creatures. As such, they lack innovation and progress and are thus doomed to a slow decline, unable to renew themselves. \Voidbringer{} knew this, and he recognized \Miith{} as a source of Chaotic energy... or a gateway to Chaos, or something, closer to Chaos than \Erebos{} is. So they come to \Miith{} in order to harness the power of Chaos to create a future for their people.)

They try and fail many times, and many times they are nearly discovered, surviving only through trickery and \draconic{} overconfidence, and often sacrificing many \nephilim{} to cover up their retreat. 

The \banes{} also work on shaping the dimension of \Nyx{}. Its purpose is threefold: First, it is meant to be a new source of power for them, similar to the power of \Erebos{} that they know. Second, it is intended as a bridge to \Erebos{}. Third, it is a hiding place where the \dragons{} cannot easily detect them. 







\section{The \Resphain{} and the \Secondbanewar}
Eventually, after more than a thousand years, the \banes{}' experiments bear fruit and their hybrid creatures are born: The \resphain, bred from \nephilic{} stock, endowed with \erebean{} minds and infused with the life-giving energy of Chaos. 

The \resphain{} settle in \Nyx{} and in hidden places on \Miith{} and proceed to build an empire, with themselves as the aristocracy, the \nephilim{} as the common folk and the \banes{} as their sinister affiliates and masterminds. For another thousand years or so, the \banes{} and \resphain{} labour to open a conduit from \Nyx{} to \Erebos{}. 

At long last they succeed and the way to the sinister \baneworld{} stands open once more. Daggerrain contacts his king, and again legions of terrible \banes{} pour forth. Another terrible war ensues, the \secondbanewar. \Dragons{}, \cregorr{} and \scathae{} battle against \banes{}, \resphain{} and \nephilim. 

After years of bloody conflict, the \draconic{} side manage to send a heroic party on a suicide mission into \Erebos{}, their quest to somehow destabilize the gate from the other side. However, the \banes{} deliver a mighty counterstrike, and the \draconic{} \Dominators{} are crippled and sent into dormancy/exile from \Miith{}. Mortal \dragons{} now vie for control. Simultaneously, the \banes{} have again been mostly wiped out, bu the fertile \resphain{} thrive\dash decimated, but determined and able to rebuild. 







\section{The Age of Nom}
Mortal \dragons{} eventually found the \Dragon{} Kingdom of Nom. Initially the \dragons{} revile \Xserasshana{} and her cruel rule. But after a while they discover that even in their dormancy they can still draw some measure of power from the \Dominators. This turns into a religion. In order to justify this they invent glorious lies about the \Dominators{} and their race's history, in which \Xserasshana{} is the heroic liberator rather than the kinslaying usurper and tyrant. 

This is called the Age of Nom, but Nom does not reign supreme. In fact, much of the time the \Dragonking{} barely reigns at all. The \dragons{} fight each other as well as the \resphain{}. \Resphain{} also fight each other, for many of them turn from the \banes{}' rule. 







\section{The \Cuezcan{} war}
\target{Cuezca}
\index{\Cuezca}
After the end of the great \dragon-\resphan{} war, both sides are badly weakened, and the Veil is formed, leaving room for new cultures to blossom. After a thousand years or two, one civilization rises to greatness: \Cuezca. (I don't know what race the \cuezcans{} are. They might be renegade \resphain.) 

\Dragons{} and \banes{} alike recognize that \Cuezca{} is a power factor, so they both try to sway them to their cause. They woo the \cuezcans{} very directly, using all means. They also teach their magic and science to the \cuezcans{}. The result is a catastrophe: With their newly acquired power, the \cuezcans{} cause immense destruction, tearing great expanses of the Realms apart. \Cuezca{} is destroyed in the process. 

The \dragons{} and \banes{} realize that open war\dash especially open war using mortal pawns, armed with power they can't wield responsibly\dash is no good, and that if they continue this way, they will destroy the world, leaving nothing to rule. So by unspoken consent, they \quo{agree} that from now on, their war will be fought in the shadows, using unwitting pawns. 

The Cabal and the Sentinels of \Miith{} are formed and the Unspoken Covenant is adopted. The Covenant dictates that the Cabal and Sentinels strive to keep mortals ignorant of the true world that surrounds them. They must not know of the secret organizations' existence, the underground war, their own origins nor the nature of the Realms. Also, the progress of science (including magic) must be suppressed and kept in check, and the Cabal and Sentinels must not teach their arcane knowledge to outsiders. 















\section{Writing style}
An idea: The book will shift back and forth between two different styles. Half of it is in biblical/mythologial style, describing the origin of the \dragons{} as if a myth. The other half is in more normal style, more normally describing the events from the POV of lesser characters, such as Semiza and the Nagae. 



% \chapter{\FirstbanewarBook}
% \input{Novels/Exodus}
% \input{Novels/TiamatsWings}
