\section{Carzain's first kill - other version}
\talk{I remember the first time I killed a man, back in the war with Runger. My company and I were marching to the front when we were ambushed by Rungerian troops. One man leapt towards me, so I called \Sezyron{}\footnote{\Sezyron{} is a \Sephirah{} (\Kliffah{}?) of Air who creates bolts of lightning from the hands.} and charred him with a bolt of lightning. 

%His skin sizzled and bubbled... 

Feeling the \Kliffah{} coursing though me, and seeing his smoking corpse lying at my feet, I felt a strange sensation. It felt... natural... to me. As if I had been born to fight and kill. So I proceeded to slaughter another dozen men. Men and woman, \humans{} and \scathae{}, I struck them down with fire or lightning or with my sword.

%But I killed several others in that battle. \Humans{} and \scathae{}, men and women, I struck them down with fire or lightning or with my sword. 

Afterwards, it made me think. You know, we have all been raised to believe that war and killing is horrible and scarring, and that killing hurts the killer almost more than the \squo{killee}. At least, I was told all that and more. So I expected to feel something bad. I don't know... guilt, grief, horror... something. But I felt nothing. My only thought was: \subtalk{These were my enemies, so I killed them.}} 

Carzain laughed. \talk{Of course, I never told my parents that.}





\section{The Resurrection}
Carzain and his followers are in the Imperial Palace, before the Rainbow Throne. The Blood Orb stands in a metal pedestal before the Throne. 

%Among the leaders of the ritual is Shereid\footnote{[she-REJD]}, a Geican Priestess and very loyal to the Dark Queen. 

Carzain took up his place by the Orb and the eleven cultists

%\footnote{\Belzhir's cultists ought to have a name, ought they not? Something like Cultists or Acolytes. A bit more exotic. How about \squo{The Cabal}? Yes, that sounds good.} formed their circle around him. 

\telepathy{Good,} said the voice of \Belzhir{} in his head.

The ritual commenced. Shereid led the circle in chanting the obscure invocations. 



