\chapter{The World of Mith}

The Mith Universe is centered\footnote{Not \squo{centered} in any literal or metaphysical sense, merely in the sense that Mith is the main focus of my attention.} around (and named after) the planet \pronunlong{Mith}{MEETH}%{This footnote is a pronunciation guide. Footnotes such as this will appear throughout the book. I recommend that every time you see one, you flip to the section on Pronunciation (p. \pageref{pronunciation}) in order to decode it.}
. Mith is a planet mostly Earthlike, with Earthlike gravity, atmosphere and climate. It is inhabited by many intelligent species, civilizations and religions. 

Before you proceed any further, I would like to point out the existence of the pronunciation guide. It is found in appendix \ref{PronunIPA}. Remember to use it for all Mithian words so you get the pronunciation right. Don't just go about making up your own pronunciation, 'cause that's dumb and ugly. I've provided you with the correct answers, so go look them up. 



\section{Geography}
Mith is populated by \humans{}, \scathae{} (lizard-men), \meccara{} (frog-men), \dragons{} and other creatures. These form many different civilizations, kingdoms and tribes. There are many great cities, castles, temples and armies on the planet. 

But beyond the city walls, there is also much savage wilderness on Mith. A large part of the planet is uncivilized and population density is generally low compared to Earth. Mith is a harsh place, filled with dangers. Wild beasts are larger and wilder than on Earth\dash{}examples include mammoths, wyverns and various dinosaurs. There are many dark forests, caves and lakes inhabited (or said to be inhabited) by monstrous creatures, demons or evil spirits with little love for intruders. 

My portrayal of Mith focuses on the continent of \intro{\KnownWorld{}}, which is similar in size to Europe. \KnownWorld{} is centered around the region of Belkade, which is comprised of many kingdoms large and small. South of Belkade lies the Imetrium (south-west) and Durcac, the Rissitic Empire (straight south). North of Belkade lie a number of kingdoms and tribes, collectively called the Northern Kingdoms. Of these Northern Kingdoms, the mightiest is the homeland of Clan Quaerin. 

At the heart of Belkade lies \Redce, the homeland of the Vaimon Clan Redcor (see section \ref{Clan Redcor}). In the southeastern corner of Belkade lies Geica, the homeland of the Vaimon Clan Geican (see section \ref{Clan Geican}). 

Straight west of Belkade (between the Imetrium and the western of the Northern Kingdoms) lies Threll, a sinister, haunted land where few men dare go. West of that lies a great sea, the Western Ocean. 

North of the Northern Kingdoms lies a sea, the North Sea. 

South of the Imetrium and Durcac lies Uzur, a land of dense jungles whose natives are predominantly \meccaran and technologically primitive. South of Durcac and Uzur is a hostile stretch of jungles, swamps and deserts, marking the border to the Far South, a region that is largely unknown and unmapped. 

East and north-east of Belkade lies a tall mountain range, the \Dragonridge. This marks the border to Irokas, the kingdom of \dragons{}, sometimes called \Dragonland. Irokas is the easternmost of nations of \KnownWorld{}. East of Irokas lies Nom, a dark and terrible land, haunted by foul monsters and feared and shunned by even the \dragons{}. 

East of Durcac (south-east of Belkade) lies a desert which marks the border to the Near Orient. There is trade with the Near Orient in \KnownWorld{}, but little is known of the lands. East of the Near Orient lies the Far Orient, of which almost nothing is known. 

\subsection{Population}
Total population of intelligent creatures in \KnownWorld{} (excluding Irokas): About 25 million.\footnote{For comparison, RL Europe had an estimated population of 38.5 million in year 1000, and 73.5 million in year 1340. Source: \emph{The Internet Medieval Sourcebook}, \href{www.fordham.edu/halsall/source/pop-in-eur.html}{www.fordham.edu/halsall/source/pop-in-eur.html}.} 

\KnownWorld{} consists of: 

\begin{itemize}
  \item Belkade (total population 7 mio) 
  \item The Imetrium (2 mio) 
  \item Durcac (2 mio) 
  \item The Northern Kingdoms (3 mio) 
  \item Uzur (1 mio) 
  \item The Near Orient (2 million) 
  \item The Serpentines (3 million)
\end{itemize}

Beyond that: 

\begin{itemize}
  \item Irokas (20 million) 
  \item The Far Orient (unknown) 
  \item The Far South (unknown) 
\end{itemize}

Some communities (villages, towns or entire kingdoms) are monoracial, made up exclusively of \humans{}, \meccara{} or whatnot. Others are multiracial, with creatures of different races living side by side. All large civilizations are multiracial, but some smaller kingdoms are monoracial, and many villages and small towns are monoracial. 

\introe{Racism} is the irrational dislike of creatures of different races and species



\subsection{Planetary data}
Mith is an Earthlike planet. It has the same size, gravity, atmosphere and climates as Earth. It orbits a star (simply called the Sun by Mithians) similar to our Sun. A Mithian day is 24 hours and a Mithian year is 360 days. 

\subsectionn{Moons}
Mith has two moons: \Dun{} and Visha. The two moons move in the Mithian ecliptic. 

\subsubsectionnn{\Dun{}, the Gray Moon}{Dun}{\Dun{}}
\index{Gray Moon}
\label{Gray Moon}
\pronun{\Dun{}}{DOON}, called the Gray Moon, is the larger of the two, about the same size as Earth's Moon. It is closer to Mith than Earth's Moon is to Earth, so it appears larger in the sky. \Dun{} has a dark gray colour. It is generally considered benevolent. 

\Dun{} is large enough to cause a solar eclipse. It is too large to cause the \squo{ring} effect known from solar eclipses on Earth, however. \Dun{} is larger than the Sun in the sky, so during an eclipse, the Sun is completely swallowed. 

\Dun{} itself is eclipsed when it passes behind the shadow of Mith. This is called a \Dun{} eclipse.\index{\Dun{}!\Dun{} eclipse} 

\subsubsectionnn{Visha, the Pale Moon}{Visha}{Visha}
\index{Pale Moon}
\label{Pale Moon}
\pronun{Visha}{VEE-sha}, called the Pale Moon, is only half the diameter of \Dun{}. It is also farther away from Mith, so it looks much smaller in the sky. Visha is considered malevolent and a bringer of ill omens. 

Visha is not large enough to eclipse the Sun. It is much smaller, so when Visha moves in front of the Sun, it is visible as a dark hole in the Sun. This phenomenon is known as a \squo{Sunhole}\index{Sunhole}. 

Visha also sometimes casts a shadow on \Dun{}. This is called a \squo{\Dun{} hole}.\index{\Dun{}!\Dun{} hole}\index{Visha!\Dun{} hole} 

Visha itself is eclipsed when it passes behind the shadow of \Dun{} or Mith iself. This is called a Visha eclipse\index{Visha!Visha eclipse}. 



%\input{Characters}
\input{General/Cabal}
%\input{Magic}
\input{General/Rules}



