\chapter{Metaphysics}

In this chapter I will try to explain the metaphysical foundation of the Mith Universe, ie., the principles of how the supernatural elements (such as magic and gods) work. 

I must point out that the Mith Universe \emph{is} governed by natural laws. Some of these laws are chaotic and non-deterministic, but there are laws that can explain everything that goes on.\footnote{Of course, the explanations given in this book will not be sufficient to 'explain everything that goes on' in the world. And the actual scientific knowledge of the inhabitants of Mith, at TL3, is even more incomplete. But my point is that the principles are \emph{there}, in the Universe, and may be discovered by Mithian scientists.} Even supernatural phenomena such as magic have a perfectly reasonable explanation according to these laws (which, of course, differ from the natural laws in RL). As such, terms such as 'supernatural' are not really well-defined or meaningful. In this book, I will use the term loosely to describe things that intuitively seem 'supernatural' because they cannot happen in RL\footnote{According to conventional modern science, at least.}. 

\section{Chaos and Cosmos}

\begin{quote}
A fundamental axiom of classic Dessalic metaphysics is the idea that the Universe is driven by two fundamental forces, Chaos and Cosmos. Chaos is the force of disorder, conflict and destruction, whereas Cosmos is the force of order, harmony and creation. 

According to certain apocryphal legends of unknown origin, in the beginning there was only Chaos. From the random twisting of Chaos, Cosmos was born. According to these legends, the Cosmos, and the Universe we know, is a small bubble floating in an infinite ocean of Chaos. 

The source of these stories cannot be ascertained, but they cannot be litterally true, for our research indicates that the very concepts of time and space are Cosmic in nature and have no meaning or existence in a Universe of pure Chaos. Thus, any talk of a 'time before the Cosmos' or a 'place beyond the Cosmos' is nonsensical. 
\end{quote}




