
\bookchapter{\Psyrex and \Vizsherioch}
The summoning of \Nithdornazsh{} is part of \ps{\Secherdamon} plan to bring \maybehr{Vizsherioch}{\Vizsherioch} into Ascendancy. 
\Nithdornazsh{} is to become \ps{\Vizsherioch} citadel, a \nexus{} from which he can grow strong and spread his tendrils (politically and metaphysically) into the Realm of the Shroud. 
This is a vital step in the forging of the \maybehs{Dagger}. 
When the \Nithdornazsh{} project is complete, \Vizsherioch{} is more Dagger-y than ever. 

Previously, \Secherdamon{} had kept \Vizsherioch{} sequestered and hidden. 
He is his only son and the fruit of thousands of years of hard work, so \Secherdamon{} is very protective and does not want to lose him. 

\Vizsherioch approaches \LocarPsyrex.
\Vizsherioch appears as a \dax in his prime, with pearly white scales, wearing a loose robe of white, silver and gold. 

\Psyrex fears him. 
Where \Secherdamon is fiery bright, his son \Vizsherioch is dark and sinister. 
Not in \colour, but in feel. 
A vast darkness follows behind him and around him. 

\Psyrex fears to look into his eyes. 
\ps{\Secherdamon} eyes are terrible enough, but \Psyrex is used to them. 
There is passion, fervour and desire in the eyes of \Secherdamon, and anger and hate, too. 
But in \ps{\Vizsherioch} eyes there are hints of otherworldly madness. 

\Vizsherioch asks \Psyrex about his progress. 
\Psyrex tells him that there have been some setbacks. 
The Cabalists are sneaky.
He does not know who leads them, now that Charcoal is gone from the city. 
But whoever is in charge must be someone capable. 
They have managed to screw up some of his operations and kill some of his important Sentinels. 
But it is not so bad. 
He has planned for some amount of Cabal interference and taken precautions. 
He is importing more manpower. 
He will be ready on time. 

\Vizsherioch: 
\ta{The beacons are in place? Show me.}

\Psyrex shows him. 
\Vizsherioch sees the slender aethereal tendrils, grown from the Pyre \matrix.
They reach up from \Nithdornazsh to twist around the ley lines and converge upon the \nexus point in Pelidor, where they grab on and hold fast, holding the \nexus in a constricting iron grip. 
He sees the \matrix subtly reaching out to fasten upon the souls of the mortals in the city. 
Binding them.
They will be part of the invocation, he thinks. 

\Vizsherioch: 
\ta{Aye, I see it.
  You have done well, \Psyrex.}
He smiles to himself.
\ta{My father has confined me to our Realms for too long.
  I long to at last set foot in my new citadel.
  And to exert my power in \Azmith; supposedly the most pivotal of the Shrouded Realms.}

\Vizsherioch becomes distant.
\ta{The constellations are falling into place.
  I can feel the tension in the Pyre. 
  The Dagger is taking shape.
  Very soon now...}
He becomes present again.
\ta{%
  What of the \resphain?}

\Psyrex:
\ta{I have detected some \resphan activity in both \Malcur and \Forklin.
  I still have every reason to believe they will swallow the bait.
  But of course, it will depend on \Nzessuacrith and her task.}

\Vizsherioch:
\ta{She will not fail us.}

\Psyrex:
\ta{Yes.
  It is not \Nzessuacrith nor the \resphain that make me uneasy.}
\Psyrex pauses and hesitates. 

\Vizsherioch: 
\ta{You mean the Exile.}

\Psyrex:
\ta{Yes. He has been uncharacteristically... \emph{active} recently.
  In the Pelidor region.}

\Vizsherioch:
\ta{But he has not antagonized us?}

\Psyrex:
\ta{Not that I can determine. 
  And that worries me.
  So far he seems to have acted only against the \resphain, but I cannot guess his motives.
  The Exile cannot be trusted.}
\Psyrex looks at his star-charts. 
Concentrates to shift his vision, so he can bypass the roof and see the sky. 
He looks up at the real stars.
He speaks some spells of divination to read them.  
He stares at the star representing the Exile. 
It is nowhere near the Pyre, nor any other known \matrix. 

Metaphysically, that is.
Physically, the Exile is much too close. 
He is made uneasy by the thought of the rogue \vertex. 
\Ishnaruchaefir is a mystery. 
A wanderer in darkness who can appear anywhere at any time, and from whom no one is safe. 

\Vizsherioch:
\ta{\QuessanthIshnaruchaefir.}
\Psyrex is taken aback. 
He had never heard \Vizsherioch speak the Exile's name before. 
He thought \Vizsherioch shunned the name like his father did.

\Vizsherioch: 
\ta{Called Exile and Destroyer.}
To \Psyrex: 
\ta{You fear him.}

\Psyrex:
\ta{Yes, I fear him. 
  Any creature lesser than a \dragon has cause to fear the Exile.}
\tho{And many a \dragon should fear him, too.}

\Vizsherioch:
\ta{Hm.
  He is in the Pelidor region.
  So it is possible he has caught wind of our doings.
  He must not be allowed to interfere.}

\Psyrex:
\ta{The \resphain feel likewise.
  Have you heard, Lord \Vizsherioch, about this \resphan, \Teshrial, who talks about confronting the Exile?}

\Vizsherioch:
\ta{Yes. 
  Allegedly the Exile has promised to face him.}

\Psyrex:
\ta{I wonder what will come of this challenge. 
  Will the Exile really return to meet the \resphan?
  I do not think \Teshrial is a fool.
  He has a plan.
  But will it be enough?}

\Vizsherioch:
\ta{Interesting prospect, this duel.}
He becomes distant.
\ta{Perhaps I should seek out \Ishnaruchaefir.
  After all, I have never met my uncle face to face...}

\Psyrex tries to imagine such a confrontation.
Would it end in violence?
\Vizsherioch was powerful, but young. 
Would he be able to stand before \Ishnaruchaefir?

\Vizsherioch reads his thoughts.
\ta{Fear not, \Psyrex.
  I will not challenge the Exile to single combat.}
Distant.
\ta{No, that would be wise.
  Not at this time.
  Not at this time...}









