\chapter{Story ideas}
\section{Names}
Some cool names that I might use:

\begin{itemize}
  \item Bethsaida.
  \item Capharnaum.
  \item Corozain.
  \item Dante.
  \item Urax: A cruel warrior god. Compare him to the Egyptian Unas, as featured in the song \bandsong{Nile}{Unas, the Slayer of the Gods}. 
\end{itemize}















\section{Attacking a city to draw out your enemies}
Someone attacks a city in an attempt to force their enemies to come out of hiding and face them. 

Perhaps in connection with Malcur in \emph{\RungerWarBook}. But maybe not. 















\section{Body-snatcher}
Maybe have a creature that slowly steals a person's soul and causes his body to rot and decay, as the creature steals his form and identity. 

Inspired by the monster from Clive Barker's \emph{Human Remains} (from the \emph{Books of Blood III}). 















\section{Collector of souls}
Have a character who goes around seeking out sorrowing lost souls, people who have nothing left to live for and only suffer. He kills them, then absorbs and binds their souls. He taps their sorrow, tears and pain. 

\ta{They were suffering anyway, but in this way, their suffering has a purpose. That is my gift to them.}















\section{Crying for your lost loved ones}
Have scenes where people cry for their killed loved ones. 

Be cruel! Be evil! Be cynical! Be grim! Be necr0! Be simultaneously grim and necr0 if at all possible. 















\section{Ghostly scene with a monster}
Have a scene where suddenly everything turns quiet, misty, ghost-like. And then a monster appears from out of the Beyond. 

Like in the anime \emph{Devil May Cry}, episode 2. 















\section{Girl is unable to kill}
Have a scene where Guy tells Girl: \ta{Kill me!}

Girl: \ta{No! I can't!}

Guy: \ta{You must! It's our only chance!}

Girl: \ta{No!}

In the end, she doesn't. As a consequence, they both die a horrible death. 

This is a subversion of the scene in episode 18 of the anime \cite{Anime:TrinityBlood}, where Esther refuses to kill Ion.















\section{Killed and dismembered victims are left to be found}
A villain kills his enemy's family and friends and leaves their mutilated, tortured corpses where his enemy will find them. Psychological terror, to fuck with the enemy's brain. 

The victim ends up going half-mad and seeing into the Beyond, in the style of the \emph{Kult} RPG. 















\section{Lying oracle}
Maybe have a lying oracle, hired by the Cabal or Sentinels to lead people astray, or onto the paths that their masterminds desire. 















\section{Mutilation}
Have a scene where a monster kills and mutilates people, leaving behind horribly mangled corpses. Perhaps hung on stakes or hooks from the ceiling, or burned, or with their skin peeled off. Blood, rivers of blood.















\section{Regrettable sacrifice}
Someone badass, possibly \hr{Ishnaruchaefir}{\Ishnaruchaefir}, wants to sacrifice an annocent for some purpose. Someone objects. 

\Ishnaruchaefir: 
\ta{Regrettable, yes. 
  But necessary. Very well. Let us divide the workload between us. I will do the deed, and you can regret it. How does that sound?}















