\chapter{Game Stats}
\section{Creatures}
\subsection{\Meccaran}
\subsubsection{GURPS}
\bd
  \item[Attributes:] ST -1 (-10 points), DX +1 (+10 points), IQ -1 (-10 points). 
  \item[Physical traits:] Dependency (fresh water, daily; -15 points), Reduced hit points (-1 due to small size; -5 points), Regrowth (+40 points), Short lifespan (approximately 75\% of normal; -25 points). 
  
  Sharp teeth (cutting damage based on ST; 5 points). 
  \item[Mental traits:] %Dyslexia (mild
  %
  \Meccara{} have a mild dyslexia. If a character is illiterate, this is a zero-point feature (the character can still understand simple symbols). If the character is litterate, this is a 3 point disadvantage - the \meccaran{} is just a poor, slow reader. 
  \item[Racial skills:] Swimming (DX level; +1 point). 
  \item[Common traits:] Impulsiveness. 
  \item[Net cost:] -14 points. 
\ed



\subsection{\Nycaneer}
\subsubsection{GURPS}
Note: A \nycaneer{} is a \scatha{} or \rachyth. The traits below are \emph{in addition} to the normal \scatha{} or \rachyth{} racial package. 
\bd
  %\item[Attributes:] As normal. 
  \item[Physical traits:] Discriminatory smell (+15 points). 
  \item[Mental traits:] 
  \item[Racial skills:] 
  \item[Common traits:] 
  \item[Net cost:] 
\ed



\subsection{\Rachyth}
\subsubsection{GURPS}
The stats below are for a first-generation \rachyth, a true Half-\Dragon. \Rachyth{} of second or third generation should have only some of the traits below, falling somewhere between the first-generation \rachyth{} and a \scatha. 
\bd
  \item[Attributes:] Increased ST (+50 points), IQ +3 ( points), HT +4 ( points). 
  \item[Physical traits:] Damage resistance (6 levels due to tough scales; +30 points), Extra hit points (5 hit points; +40 points), Regrowth (only small extremities; +20 points). 
  
  Claws (+2 damage; 15 points), Tail (striker, crushing damage, range 1; +15 points), Sharp teeth (cutting damage based on ST; 5 points). 
  
  Some first-generation \rachyth{} can breathe fire or ice. Fire breath 
  \item[Mental traits:] 
  \item[Common traits:] 
  \item[Net cost:] 
\ed



\subsection{\Scatha}
\subsubsection{GURPS}
\bd
  \item[Attributes:] ST +2 (+20 points), DX -1 (-10 points). 
  \item[Physical traits:] Damage resistance (3 levels due to tough scales; +15 points), Reduced move (-1 point of speed; -5 points). 
  
  Tail (striker, crushing damage, attacks at -2 to DX, range 0; +3 points). 
  \item[Mental traits:] Sense of Duty (to community: tribe, nation, religion, whatever; -10 points), Weak will (1 level; -8 points). 
  \item[Features:] A \scatha{} does not stand erect. As such, he takes up two hexes in length. On the other hand, a \scatha{} can crouch down more easily than a \human. 
  \item[Common traits:] Fanaticism, Honesty, Intolerance. 
  \item[Net cost:] +5 points. 
\ed
