\section{Shamanistic Cultures}
\label{Shamanism}
\index{Shamanism}
Shamanism is a religion, or, more properly, a collective term for a class of religions, practiced primarily by the \meccaran{} tribes, but also in some communities of other creatures. %as well as some communities of Humans. A few communities of Scathae have adopted Shamanistic beliefs, and some Troglodytes practice religions similar to Shamanism. 

Shamanism exists in many diverse forms and is not in any way a centralized or even homogeneous religion. Some forms of Shamanism are very peaceful (or even pacifist) and resemble Animism\footnote{Needless to say, my usage of the terms `Shamanism' and `Animism' in a Mithian context is meant to be similar to, but also different from, the RL religions of the same name. In RL, shamanism is perhaps more properly considered a form of animism than merely something similar.}, wheras others are very dark and sinister, employing `black' magic and consorting with monstrous powers. 

Shamanism is based on the belief that the world is full of spirits, that all things have a soul. Shamanistic magic works by communing with and influencing these spirits. 

Beliefs include: 

All people, animals and things have a soul. These souls can be communed with, and done other stuff to... 

%Shamanistic magic is a tradition used primarily by the \meccaran{} tribes, especially in Uzur, but also in the Middle Lands. It is often considered primitive and barbaric by other cultures, and it is true that most Shamans have little theoretical understanding of how their magic works. Still, the Shamans are not to be underestimated, for their magic can be very effective. 

%Some aspects of Shamanistic magic and religion: 

There are Shamans and Witch-Doctors. (The distinction is not always rigid.) A Shaman is a religious authority whose magic is seen as something holy. A Witch-Doctor is an alienist who deals with dark, occult powers. He is primarily a mage, and perhaps secondarily a priest. In many tribes, Witch-Doctors are feared and mistrusted (but they are usually still there, because their magic is potent). 

\subsectionn{Shamanistic magic}
Shamans usually cannot cast `spells' in a regular sense. Their magic relies either on rituals or on herbs and drugs. Witch-Doctors can usually cast regular spells. 

Their rituals revolve around dance and music. Some spells can be performed by the Shaman alone, but most require many people. 

\Meccaran{} singing usually uses a chanting choir and a lead singer. The chanting is rhythmic but not melodic. It may be with understandable words, strange, magical words or just nonsense. A lead singer is typically a shaman. \Meccaran{} lead singing is high-pitched and screaming, often wild and ecstatic. This often sounds extremely chaotic and un-musical to outsiders. 

Typical rituals are war dances, hunting dances and exorcisms. 

In a hunting ritual, the people seek out the great spirit of the prey animal. In some interpretations, the shaman peacefully communes with the spirit and obtains permission to kill some of the animals (this is granted because it is the nature of prey animals to get eaten). In other interpretation, the shaman duels with the spirit and takes his `permission' by force. 

In a war ritual, the people seek out the guiding spirit of their enemies and combat it. If successful, the enemy is weakened and the tribesmen get bonuses to fight them. 

They eat the bodies of their dead (under a magic ritual), so that their souls return to the tribe. 

They eat the bodies of their enemies (under a different ritual) to gain their strength. (Only the blood and important organs, especially the heart and brain, have occult properties. The rest of the body is just eaten for nourishment.) 

Living people may drink each other's blood in a ritual, or even eat each other's flesh\footnote{For a \meccaran, it is easy to remove a finger or so, since it will regenerate.}, creating an arcane blood bond between them. 

Warriors have a totem animal and draw power from it. 

They use drugs a lot, to help the soul wander and to access spiritual power. Warriors sometimes take drugs to go berserk. 



\subsection{Shamanistic spells}
%Some sample spells: 

Here is a list of sample Shamanistic spells. Note that since Shamanistic communities are a very heterogeneous group, any given Shaman or Witch-Doctor need not have access to all of the spells below. 

\spellsha{Control Weather}
Shamans can control the weather to a limited extent. Requires a tribal ritual. 

\spellsha{Curse of Despair}
Causes depression and despair in the victim. 

\spellsha{Curse of Sloth}
Makes the victim lazy. 

\spellsha{Curse of Disease}
Causes disease... 



