\bookchapter{\Vertex{} Spike}
%\section{A Brief Awakening}
\tho{They are upon me!} 

Vizicar Duras Respina was certain of very little save that he was beset by enemies. \tho{Who are they? What are they?} He did not know. 

He was fleeing through the familiar halls of the Rainbow Palace in \Merodar, where he had dwelt almost all his life. But something was amiss. Where some of the rooms and corridors were as they should be, others were wrong, twisted, changed. Stairs appeared where none should be. Dead ends greeted him where he expected doors. Had he been full of faculty this would have given him pause, but now it was all he could do to keep focused on his flight. Far behind him\dash\tho{yet so near, much too near!}\dash he thought he could dimly hear the footsteps of his pursuers. Assassins, invaders, ghosts... he could not say, but they were after his life, and he dreaded them. 

He ran on.

He was running through the woods, the deepest, darkest centre of an ancient, Wild forest. Where he was he did not know, but he knew that somewhere ahead lay his home\dash if he could only make it. From the distance came the faint baying of hounds. \tho{The hunting-dogs! They are on my heels!} He knew he must elude the dogs at all costs, lest they tear him apart and feast on his flesh. 

The Wild resented his presence. Gnarled trees loomed above him, regarding him with hateful, unseen eyes. Roots sought to trip him. Sharp-edged nuts and acorns cut into his bare feet. Branches like scourges lashed and tore his naked body. Boughs and leaves converged above like massive hands, seeking to block out the Sun and leave him stumbling in total darkness. 

The howl of a hound pierced his ears. \tho{Closer than ever before!} 

He ran on. 

He was swimming in an ocean\dash but what surrounded him was not water, but a thick, viscous slime. He could not breathe. Far above he could see the faintest glimmer of light, and he knew that he must climb to the surface, must reach the Sun. 

In the depths beneath he perceived a horde of creatures\dash or a lone abomination of unfathomable vastness? He did not know; all he perceived was the image of hundreds of tentacles reaching for him. 

%Tendrils of what might be seaweed entangled him. 
Tendrils entangled him. Seaweed, perhaps, or the fingers of horrid monsters. 

He struggled with all his strength to break free, paddling with his arms and legs, seeking to crawl upward and escape the grasping tentacles that would draw him down to the lightless depths, food for putrid things that had no name. The liquid bore down on him with a terrible weight, like the dirty foot of some tremendous giant, crushing him. The sea itself hated him and desired to devour him. 

He swam on. 

He turned around a corner, past one of the many crystalline pillars of the palace. As he did, he felt a whish of the wind, as if a knife sliced the air just a hair's breadth behind him. Not daring to turn, he plunged down the corridor. 

Pictures and tapesties adorned the walls, and all followed him with malicious eyes, burning into him. \hypotalk{You are not worthy,} they seemed to say. \hypotalk{You have fallen from grace and are no longer worthy.} 

The hounds were nearly upon him. He dared not turn, but their barking was loud, frenzied, and he could smell their hot breath, feel their drool on his back. The trees were crowding around him, and he had to edge his way between them. As he did, the trees twitched, moved, closing in to squeeze him, like giant fingers crushing a bug. 

Tentacles brushed his legs. He squirmed, feebly pushing his way through the suffocating ooze. The weed ensnared him like a fisherman's net. He wanted to gasp for air, but found only the foetid slime.

If he could only reach his home... if he could only reach the surface... 

\hypota{Gaaaaah!}

A cry ripped the air.

Somehow, the sound filled him not with dread but with relief. For this was not the yowl of some nightmarish beast, not the shriek of a slavering thing from the deep. It was the yell of a man. A man terrified, but nonetheless, a man beset not by the horrors that lurked in the world beyond mortals' sight, but by the terrors of the known world where men lived and died. To Vizicar it served to affirm his identity, his grasp on reality. It was as if the walls became more solid, more like rock and crystal. The trees became more rigid, and the ooze felt slightly more like water. 

He turned another corner and found himself staring into a man-high mirror. It was clearly a mirror, yet the man he saw before him was a stranger. Younger and different of build, his hair dark rather than fair, and beardless. A stranger, yet as Vizicar studied him, he could not escape a sense of familiarity. There was something about the man's traits, his eyes, his posture...

The shout was abruptly cut short. 

Vizicar again heard the baying of the hounds behind him. He imagined that he felt the puff of air from an assassin's dagger plunging toward his back. On pure instinct he leapt forward. 

With massive effort, he snapped the seaweed pinning him down. He gave the probing tentacle a desperate kick and pushed himself up. 

A root caught his naked foot, and he stumbled. The drool of the hunting-dogs dripped onto his heel and thigh. He crashed into the jeweled mirror. The mirror became a muddy pool in the forest. He fell through it... through the image of the dark-haired man... and into him. 

Suddenly he was aware of a foe running for him. 
It was a faceless, veiled assassin, moving in complete silence, envenomed stiletto in his hands. 
It was a wolfhound, its jaws slavering, its eyes burning yellow in the nighted forest, its paws stained red with dried gore. 
It was a bearded man shouting and swinging a mace. 
It was a horror of the lightless deeps, a nameless tentacled thing dripping ichor. It stormed at him. It clawed at his throat. It enveloped him. 

Vizicar felt hot rage rising in him. Furious, he slashed with his sabre. He kicked and punched with his bare limbs. He invoked \Archons{} to blast asunder his enemy. 

\hypota{Izion!} he heard himself invoke\dash\tho{is that my voice?}\dash and he felt the \Sephirah's power flow into his body. 

\tho{Betraying scum! I will kill you!} 

He screamed. He shouted. He roared. He cried out his fury, his outrage. 

\tho{I will kill you!}

\hypota{Izion!} Fire surged from his outstreched hand. Fire erupted from his body. The wolf yowled as it burned. The amorphous thing sizzled and melted, turning to vapour. The man crumpled in an ashen heap. 

Exhilarated, Vizicar looked around to see many more foes encircling him. They were hunting-dogs... armed men... slimy horrors... all those things at once and more still.

Anger mounted within him, but where before it had been hot, now it became cold. \tho{All these... I must kill them.} 

He pushed past one more gnarled tree. The forest cleared before him. Light filled his eyes. With one final stroke of his feet he broke through the surface of the slimy ocean, to find the Sun shining bright and within his grasp. 

He was in a forest. But not the hateful, benighted wolf-haunted forest of his fevered dream. This was a natural forest, the trees mercifully mindless and unmoving. Enemies surrounded him. He saw still the fangs of hounds on their blurred faces. He perceived still the ichor dripping from their limbs. But he know\dash somehow, he knew\dash that these were men. Not monsters of the Beyond. Not the inner \daemons{} of his dreams. Men of flesh and blood.  

Cold was his rage, and dark, and cruel. He smiled to himself. \tho{Very well. I will slay them. Betrayers! I will slay them all!} As those thoughts went through his head he heard them echoed somewhere in his mind, as if repeated by some voice. A voice tinged with wonder, disbelief. 

A man near him shouted words, but he did not hear them. \tho{No time. Now we fight.} He lifted his hand and invoked a name. \ta{\Razilah!} With practiced familiary he reached into \iquin{}, and the \Sephirah{} responded. Its power filled him, and its essence, and its will. \tho{You have wronged me.} Of that much he felt sure, even if the nature of their crime eluded him. \Razilah's conviction burned like ice in his veins. \tho{For you I have no pity. Perish.}

Power rippled through him, though his mind and body, and the shining, crackling arrows of \Razilah{} burst from his hand. With his righteous fury the \Sephirah{} smote the wrongdoer, and he was cast to the ground, and he was destroyed. 

Vizicar gazed down at his hand. It felt weird. It looked weird. Ghostlike. He flexed it, and the fingers moved. He clenched it into a fist, felt the fingers against the palm. It felt familiar, but also alien. As if it was his body, yet somehow not. As if... as if his mind was locked in another man's body. 

\tho{Why am I here? How did I get here?} He found no answer. \tho{Who am I?} 

He remembered a name. \tho{Vizicar. I am Vizicar Duras Respina.} 

\tho{But who is that?}

He was given no more time to contemplate. His foes were milling about him. One spoke, a short, ugly goblin-creature: \ta{This is not what we bargained for!} The creature turned and made to lope away. 

Hate and anger returned. He smiled. \tho{No. Not what you bargained for.} Again he heard the strange echo, as if a stranger was whispering his words back to him. A stranger who was surprised to hear him speak. 

Pushing the voice away, he turned to the goblin-creature. His ghostly body obeyed. %It felt as if moving too slow, and at the same time too fast.
\tho{No more playing.} \ta{\Horvaleth!} He reached into \nieur{}, calling out for the ice queen, and she responded, and came to him. He felt the cold of her wicked caress on his skin, tasted her cruel kiss like frostbite on his lips. \tho{Lend me your malice, ice queen.} And she did. He felt her power run though him. He watched as his fingers became those of the \Qliphah\dash frozen, poignant, deadly. \Horvaleth's fingers tore through the fleeing creature, and it was destroyed. It fell to the ground, speared on blades of ice, blood gushing out. 

Vizicar turned. Only one foe remained. He faced the creature. \tho{You are the worst of them.} Somehow he knew that. \tho{And now you are mine.} As he stared into his enemy's eyes, the world began to dissolve around him. 

\tho{I will kill you.}

He was in his throne room in the palace. He was floating above the sea of filth. He was at the clearing in the spectral forest. 

\tho{I will defeat you.}

His body became that of a ghost. It became mist. Air. Nothing. 

\tho{I will destroy you.}

His foe was a hound. He was a masked assassin. An abomination of slime. Then a ghost. Then mist. Then nothing. 

\tho{I have won. I have vanquished you all.}

Vizicar smiled inside with pleasure. 

Then his consciousness faded away. 









%\section{\Vertex{} Spike}
\stamp{\dateMutiny}{\TopazChateau, \Redce}
%\dateplace{Carz}{11th}{\Yeziel}{\TopazChateau, \Redce}
%
% At the time of Carzain's fight, when Vizicar awakens within him and takes control of his body, the Malach's awakening sends ripples through Iquin. Esmerel is a Redcor Matron who has studied the Malachim. She feels the ripple and knows that a Malach has awakened. She begins research to discover its location and identity. 

%\new
%A ripple went through Iquin, and \Esmerel{} stirred from her books. It was almost nothing, the slightest of fluctuations, indiscernible to even a skilled Vaimon, and only \Esmerelz{} decades-long dedication and attunement enabled her to feel it. 
%
%She sat up with a start. With haste she reached into Iquin and invoked her \Sephiroth. 
%
%\ta{What is it, Matron?} said Iselle. \Esmerel{} raised a hand, and her assistant fell silent. 
%
%%\ta{Silence, girl,} said \Esmerel. 
%
%Esmerel sends Iselle off to find some incence and some more Redcor to assist Esmerel in the ritual. They combine to form a circle, then meditatate. 
%
%\Esmerel{} is deep in her \Sephirah{}-meditation, sitting at a mystic pool of silvery water\dash the Waters of Enlightenment. She notices a ripple in the Web of the Realms and sends her mind probing to investigate. 
\tho{A flash of lightning!} 

Redcor \Matron{} \EsmerelFull{} started, almost broken out of her meditation. \tho{What was that?} 

\tho{A ripple in the pool. A massive discharge of energy.}

She strained her inner sight, gazing deeper into the silvery mirror before her\dash the Waters of Enlightenment, the window to hidden dimensions Beyond. The ripple faded quickly, but she had caught its scent. 

\tho{Come to me, \sephiroth,} she prayed. \tho{Guard me and guide me safely through the shadows.} And she felt them draw near, felt their familiar yet wondrous touch. Calming, like a mother's embrace. And splendid, like the sunrise. And breathtaking, like the view from the high towers of the \TopazChateau{} when she had first seen it as a young girl, many decades ago. Shielded in the protective embrace of the \sephiroth{} and with her senses amplified by the mystic mirror, she sent her mind questing through occult dimensions in pursuit of the anomalous power surge. 

Some among the Redcor disapproved of the Waters; some even saw the use of the pool as heresy, a pathway to corruption. 
%But \Esmerel{} knew better. The silvery Waters were a doorway to great wisdom, and after all, 
\Esmerel{} shared none of those fears. 
%After all, 
%she had the protection of the \sephiroth, so why should she fear the shimmering mirror and the visions it showed? 
% \emph{The true heretics,} she mused, 
% \emph{are they who doubt the omnipotence and omnibenevolence of the \sephiroth{}. A truly faithful believer needs have no fear of the mystic mirror and the visions it shows.}
\tho{In doubting the omnipotence and omnibenevolence of the \sephiroth{},} she mused, \tho{they, if any, are the true heretics. A genuine believer needs have no fear of the mystic mirror and the visions it shows.}

No, the Waters of Enlightenment were a gift, and a doorway to great wisdom. And what luck that she had been meditating by the shimmering lake at this very moment, so that the Waters had enabled her to sense the cosmic anomaly, fleeting as it was. \tho{Truly wise is the Light,} she reflected. 

%\tho{But I must waste no time.} 
%But she knew she must waste no time. 
%But she could afford to waste no more time on such speculation. 

Suddenly, darkness. 

She was ripped out of her pious thoughts. 

\tho{Darkness.

Darkness everywhere.}

\Esmerel{} found herself aimlessly adrift amid a huge, endless space. Stars dotted the heavens in all directions, tiny pinpricks against the devouring blackness of the firmament. 
%But however pious these thoughts, they made her lose track of the object of her search. Suddenly she found herself aimlessly adrift amid a huge, endless space. Stars dotted the heavens in all directions, tiny pinpricks against the devouring blackness of the firmament. 
%\Esmerel{} 
She 
shuddered inside, overwhelmed by the sheer vastness of the nighted void\dash cold darkness stretching off into infinity on all sides, 
%black gulfs yawning open like the jaws of some cosmic monster of unimaginable proportions, 
like some cosmic monster of unimaginable proportions, black gulfs like jaws yawning wide open as if to swallow her, to crush her tiny body and soul in its lightless belly. 

\tho{Pull yourself together, \Esmerel,} she scolded herself. \tho{You are above such superstition.} She had to remind herself that as vast as space might be, the Light was greater still. 
With effort, she wrested her astral senses away from the enchanting but terrible vistas of the void and sought instead the consoling touch of the \sephiroth. 

The soothing presence of the \Archons{} gave her renewed peace of mind, %, and she was again able to focus. 
but with the comfort came a silent admonition: \tho{Concentrate on the task at hand.} 

% She invokes \sephiroth{}, and they guide her as her mind sails through the occult dimensions. She floats in a sea of stars, with the blazing \hs{Sun} and the twin \hs{Moons} as her guides. The Light envelops her, yet even so she cannot help but shudder at the great blackness surrounding her\dash cold darkness stretching off into infinity on all sides. She was overwhelmed by the sheer vastness of the void, looming all around as if poised to crush her, and had to remind herself that the Light was greater still. With effort she wrested her astral senses away from those vistas and sought instead the comforting touch of the \sephiroth. 
% 
% The soothing touch of the \Archons{} gave her renewed peace of mind. %, and she was again able to focus. 
% But with the comfort came a silent admonition: \tho{Focus on the task at hand.} 

%\Esmerel{} concentrated on directing the swirling mists of the Waters of Enlightenment. Amplified by the power of the enchanted pool she sent her soul questing along the ley lines of the great Web of the Realms
\Esmerel{} let the blessed calm of the Light flow through her body, erasing her fears and allowing her to focus her senses, and with renewed clarity she reached out through the cosmic threads of the Web of the Realms. 

And she detected it. A slight shivering of a thread. 
%\tho{I will find the source of this }
Swiftly she followed, sending her mind speeding along the thread, the weave and flow of the cosmos swirling around her as she flew. 
%Swiftly, she sent her mind floating along the thread. 
%The weave and flow of the cosmos swirled around her as she sent her mind speeding along the thread. 
As she moved closer, the thread seemed to vibrate more violently, and mystic winds tore at the web around her. Subtle, undetectable to the senses of the common folk, and even most of the initiated. But to \Esmerel, connected to the Realms as she was through the Waters of Eternity, it was like a raging storm shaking the fabric of the Web. 

Finally, the source of the power surge came into her view: A massive \vertex{}, pulling at the cosmic threads, flailing them about like whips. To her eyes the \vertex{} was a burning conflux of raw power\dash shining white interwoven with blood red and pitch black, all spinning in chaotic confusion. 

\tho{A \vertex{} spike! And not just any \vertex, at that.} For \Esmerel{} recognized the pattern of those energies, the vibrations they emitted. 

\tho{A Scion! There can be no doubt. A Scion has awakened! 

An \Archon{} given flesh...}

In that moment, a rogue burst of energy pulsed from the fiery \vertex. A thread wildly, blindly lashed out, striking \Esmerelz{} astral form, sending gut-wrenching pain through her.

Fast losing consciousness from the stress, she felt the \sephiroth{} closing about her, carrying her back to the safety of her body. One thought went through her mind as she dozed away: \tho{I found it. I, \EsmerelFull, discovered the new Scion...}

Oblivion took her. 



