%\begin{comment}
\bookchapter{To Malcur}

\begin{comment}
\subsection{Braddon Hill}
\end{comment}

\begin{comment}
\stamp
  {\dateCarzainGoesToMalcur}
  {Braddon Hill, near Malcur, Pelidor}
%
%\dateplace{Runger war}{7th}{\Razilah}{Braddon Hill, near Malcur, Pelidor}
%
\ta{There we are,} said the sergeant, a \human{} man, reining in as they reached the top of the hill. 
\ta{You can see Malcur there in the distance.}    

Braddon Hill marked a sharp contrast from the darkness and cramped feeling of the \Wylde{} woodlands behind them. 
They now looked out over a vast expanse of farmland. 
Almost as far as the eye could see, the land was covered in fields, yellow and rolling in the wind. 
They whole party took a few moments to rest and admire the view. 

The city rose in the distance. 
It was huge, probably ten times as large as \Redglen{}, on each side. 
Shining white and yellow walls reaching up to twenty yards in height, and towers twice as tall as that, capped with metallic roofs that shone like gold in the Sun. 
From the central castle and several towers billowed the standard of House Pelidor: 
A bronze \grulcan{} bird on a field of azure. 
The smaller banners of other nobles could also be seen. 

\ta{Whoa...} said one of the other recruits, a big smith whose name Carzain could not remember. 
\ta{It's so big. 
There must be a thousand thousand people there.}

\ta{Welcome to civilization,} laughed the sergeant. 

\ta{How long is the ride?} asked another recruit. 
%Adrian Testor, the cavalier. 

\ta{It's afternoon now, so we'll be there around sunset,} said the sergeant. 
\ta{Move out!} 
With that he kicked his mount into motion. 
The recruits followed suit. 
\end{comment}



\begin{comment}
\subsubsection{Arrow}
\end{comment}

\begin{comment}
Albeit some more ably than others. 

Carzain poked his \ps{\relc}{} sides. 
\ta{Move, Arrow. Move!} 
Arrow was a dark green male, large and strong, but rather mean-tempered. 
At least, so it seemed to Carzain, who was by no means an expert rider. 
\ta{Move, damn you!} 

The big smith deftly passed him on his own \relc. 
%, riding his green \relc\dash a bipedal lizard about as big as a \relc, and just as fast. 

Suddenly Arrow sprang into motion, startling him. A few days before such a move would have thrown Carzain from the saddle, but he had gradually learned to respond quickly to Arrow's willfullness, and he managed to hang on. 

Riding Arrow was something of a struggle. 
And to top it all off, the beast was prone to biting. 
It had snapped at him more than once, and while he had so far managed to escape any serious bite wounds, his hands did bear some scratches. 

% As they set out from \Redglen, a number of horses and \relcs{} had been temporarily provided by the army. 
% Carzain, in imitation of his Vaimon heroes from history, had been quick to secure a horse. 
% \tho{No Vaimon rides a \relc, however nice and friendly the animal may be.} Such had been his reasoning back then. 
% \tho{Maybe I should have taken that \relc{} after all.} 
%bore the scratches to prove it. %, but he had been warned and managed to escape anything more than scratches. 

%Riding Arrow was something of a struggle. Carzain had disliked the horse at first, but over the last few days he felt he had grown to understand the beast. Arrow seemed to display a pride and disdain that he recognized in himself.

%With some effort he caught up with the others. 
\end{comment}

\begin{comment}
\subsubsection{Adrian Testor}
\end{comment}

\begin{comment}

\ta{Still with us, \Shireyo?} Adrian laughed when Carzain caught up to the rest. 

\ta{Yeah. But the beast doesn't always want what I want.} 
%is causing me trouble.} 

\ta{Arrow is a real man, I can tell. And it'll take a real man to ride him. Beginning to question the size of your balls, \Shireyo?}

\ta{Shut up, Testor. I'm getting there. As for my balls, Arrow is doing what he can to squash them.}

They both laughed at that. 

%\ta{We can't all be born horsemen, can we, Testor?}

\ta{Machismo aside, we can't all be born riders, can we, Testor?}

\ta{No, I suppose we can't.} %was what Testor's mouth said, but his 
Testor's tone seemed to say: \hypota{Of course. Some of us are just born better than others.}

Carzain smiled to himself. Of an age with the Vaimon, Adrian Testor was the son of Isaac Testor, one of the richer merchants in \Redglen. 
Where Carzain and the rest of the party had had to take the temporarily mounts supplied by the army for the journey to Malcur, Adrian had brought his own \relc\dash Prince, a beautiful, emerald-green male\dash and he was a connoisseur of \relcs, having ridden since he first learned to walk. 
As a second son, he stood not to inherit his father's business, and so he had gone to join the ranks of the cavalry\dash aspiring to one day become a Tiger and a knight. 

He was merely a wealthy citizen, but from his pride and hauteur one would think him a noble. 
%Carzain had taken a liking to the man because of those exact traits, as well as his irreverent humour, all of which Carzain recognized from himself. 
And it was those exact traits that had made Carzain take a liking for the man. Those, and well as his irreverent humour, all of which Carzain recognized from himself.  

\ta{Well,} Adrian continued, \ta{as a witcher, you are going to need to be able to ride, \Shireyo. You could us the practice.} With that, he spurred his own \relc{} forward. \ta{Come on, you pussy! Race me!}

\ta{What did you call me?} Carzain laughed back. \ta{I'll get you for that, you fag!} And he urged Arrow onward in pursuit.
\end{comment}



%\end{comment}

\begin{comment}

\new
They look out over the farmlands surrounding Malcur, and the river (name it!). Then they ride down. Carzain rides Arrow, a gray stallion, a strong but ill-tempered beast prone to biting\dash Carzain has a scar on his left hand from a glancing bite. Despite their differences, Carzain grows somewhat fond of Arrow. (Maybe not immediately, but eventually.) 

Apart from the sergeant, the party consists of: 

\begin{itemize}
	\item Adrian, a rich young man from \Redglen{} who brings his own \relc{} and is to become a cavalier. 
	\item Randall, a middle-aged \dax{} herbal healer. 
	\item Rory, a \human{} bladesmith. 
	\item And maybe a \sphyle{} who brings her own \relc{} and keeps to herself, whom none of the guys get to know. Maybe I can then use her later. (But then again, maybe this is overkill.) 
\end{itemize} 

They arrive at the Malcur barracks around sundown. The sergeant directs them to a desk officer (title?). The desk officer tells them to find rooms in the dormitories and settle in, then report back to her at the next bell. 

Carzain goes into the dormitory. He settles down next to a dude (Delph, a \Tepharin{} name) who becomes his friend. On his other side he has Adrian, who also becomes his friend. (Does this make sense? Perhaps they ought to be sleeping with people from their own unit. Consider this.)

Reporting back, Carzain is directed to the Mages' Guild. He meets Archibald Curwen. Curwen introduces him to the other mages. There are two \scathese{} Chaos sorcerers and a fifth guy whose race and craft I have yet to determine. 

\end{comment}









\begin{comment}
\subsection{Malcur}
\end{comment}
\begin{comment}
\subsubsection{I am Vizicar}
\end{comment}

%\begin{comment}
%\section{To Malcur}
%\dateplace{Runger war}{30th}{\Atzirah}{Army barracks, Malcur}
\stamp
  {\dateCarzainGoesToMalcur}
  {Army barracks, \hs{Malcur}}
They entered through the barracks' wooden gates. 
The sergeant led them first to the stables, where they left their mounts, and then to a desk before a tent in the yard, behind which sat a \dax{}. 
A single bronze stripe adorned each of his shoulders\dash the insignia of a sergeant.% on his shoulders. 

\ta{Sergeant,} said the officer who had brought them.

The \dax{} looked up. 
\ta{Sergeant,} he replied.

\ta{Five recuits from the Torgin area. Take care of them.}

\ta{Right.}

The \human{} sergeant wheeled around and stalked away. 

\ta{Line up, boys,} the \scathaese{} sergeant commanded. 
\ta{One at a time.} 

The cavalier went first. 
\ta{I am Adrian Testor, son of Isaac Testor.} 
Whether the name was known here or not, it was clear from his tone and stance that his father was allegedly someone important. 
\ta{I am to join the cavalry.} 

\ta{Do you bring your own mount and equipment?} 

\ta{I do.} 
Adrian patted the sword at his side. It looked like a fine weapon. 

\ta{Good. 
    Cavalry quarters are that way. Talk to Lieutenant Hilcor. She'll tell you more.} 

\ta{And my \miksha{}?} 

\ta{Lieutenant Hilcor will tell you more. 
    That will be all, recruit.} 

\ta{Hm.} 
Adrian gave a curt salute, then made his way in the indicated direction. 

\ta{Next,} said the sergeant. 

Carzain approached. 
\ta{I am \VizicarDurasRespina.} 

\tho{What?}

\ta{No! 
    No. 
    I mean... 
    I am, uh, \CarzainDeracilleShireyo. 
    Yes.}
His voice fell to a murmur.
\ta{Carzain \Shireyo. 
    That's me.}

% \ta{A man of few words, are you?}

% \ta{Not necessarily. Your manner does not exactly invite smalltalk.} 

The sergeant looked at him through lazy eyes. 
\ta{Made up your mind?}

\ta{Yes. 
    \Shireyo{} it is.
    Vaimon mage. 
    Going to the \ishrah.}

A flat nod. 
\ta{\Ishrah, you say?
    Hm.} 
The sergeant's expression suggested that being mad and forgetting your own name was what he expected from those crazy mages. 
He raised his voice. 
\ta{Kreb!} 

A \human{} emerged from the tent behind him, a boy of maybe sixteen, with curly brown hair and deeply tanned skin. 
\ta{Sergeant?}

Not sparing the kid a glance, the sergeant indicated Carzain. 
\ta{%
  Recruit for the \ishrah\dash the mage coven. 
  Take him to see Captain Curwen.} 

\ta{Yes, sir. 
Come this way, please.} 

Carzain followed. 

\tho{%
  What did I just say? 
  \quo{Vizicar}, was that it?
  And some more. 
  What was the rest?
  I don't remember.
  
  \Qliphoth. 
  I must be dizzy from all the riding. 
  Damn \relc. 
  Bumping me along like that.
  Yes, that's it. 
  It's the riding. 
  It's the \ps{\relc}{} fault. 
  That must be it.
  
  \quo{Vizicar}? 
  Is that even a real name?}

\ta{Next,} he heard from the sergeant behind him. 

\ta{My name is Rory. I'm from \Redglen. I'm a bladesmith...} 
The words faded in the distance. 

%(They walk through the camp, passing tents and groups of recruits. It looks like the barracks in \Redglen, but much bigger.)
Kreb led Carzain through the camp, passing all sorts of tents and wooden buildings\dash dormitories, armouries, storehouses and whatnot. 
It resembled the barracks back in \Redglen, but much bigger and more organized.

\tho{\quo{Welcome to civilization}, indeed.} 

\ta{So, whom are we going to see?} Carzain asked. 

\ta{Huh?} said Kreb. 
\ta{Oh... Captain Archibald Curwen. 
Field commander of the \ishrah{} mages, sir.} 
The boy spoke in a strange accent. 

He also had a strange walk. 
Carzain couldn't quite describe it, but Kreb seemed to somehow lope, like a wolf or something. 

\ta{\quo{Kreb},} he asked after a while. 
\ta{What kind of name is that?}

\ta{\Goyden, sir.} 

\tho{\Goyden. Hm. That explains the accent. And his dark skin. Probably the strange walk, too.} 
The \Goydens{} were savages who lived in the \Wylde{} in southern Pelidor. 
They had their own strange language and were said to be bestial and primitive and pray to strange gods. 

He kept studying Kreb's gait. 
There was something unnatural about it. 
Some said that the \Goydens{} were only half \human{} and half beast. 
In some stories, they were attributed the ability to change between \human{} and animal form. 
Carzain was not sure he believed those tales, but he could venture a guess as to where those rumours came from, for the boy's walk definitely had an... \emph{inhuman} quality to it.%, and it was not hard to guess where those rumours had come from.



\begin{comment}
\subsubsection{Archibald Curwen}
\end{comment}

The boy led him across the yard to a squat stone tower near the edge of the barracks enclosure. 
Above a broad door was written: 

\begin{quote}
\begin{center}
{\bf 
  Academy of Arcane Arts\\
  Ducal \Ishrah{} of Pelidor
}
\end{center}
\end{quote}

\ta{That's the \ishrah{} quarters?} Carzain asked. 

\ta{Yes, sir. How did you know?} 

Carzain gave a secretive smile. 
\ta{We sorcerers know many things.} 
%\tho{And it's barely even a lie. Mages mage up a large portion of all literate people in the world. Perhaps even the majority, counting the churches.}
\tho{Or, rather, we literate people know many things. 
Although I suppose to this barbarian's mind there's not much difference between writing and sorcery.}

% Carzain meets Curwen. They see a hot girl pass by and immediately hit it off together.

Kreb, accepting this explanation, now led him near the door, where stood a large man, his shoulders displaying the silver triangle that indicated a captain. 

\ta{This is Captain Curwen, sir,} said the Goyden. 

\ta{Yes, I guessed. If this is all, just go back, Kreb. I'll introduce myself.} 

Kreb nodded\dash\tho{was that a measly bow or just a deep nod?}\dash then turned back the way they had come. 

Carzain studied Curwen as he approached. Old enough to be the young Vaimon's father, his short hair and beard were steel-gray and he wore a gray-and-black coat to match. A sword at his hip, a Vaimon sabre of classical design. 

And he was large. Of a height with Carzain at least, but of much greater bulk. Much of his girth was fat, Carzain judged, but enough was muscle, and he suspected that the much older man would be more than his match in a contest of strength. 

He was in conversation with a middle-aged \sphyle{} in a black-and-brown robe. %, who nodded at something then turned away as he approached. 
As he was approaching, she nodded at something, then turned away, providing Carzain with an opening. 

\ta{Captain Archibald Curwen!} he called. 

The old mage turned his head slowly. 
\ta{What?} he grunted in a loud, gruff basso. 

Carzain waited until he was close enough to not have to shout. 
\ta{I am Carzain \Shireyo. I am to join the \ishrah.} 

\ta{Are you, now?} He ran his eyes up and down the new recruit. 
\ta{You don't look like much.} He gave him a level, almost bored look.

\ta{Do I not?} said Carzain, mock innocence in his voice. 
\ta{%
  Then I must be having a bad day. But looks can be deceptive, you know.} 
Pause. 
\ta{Captain.}

\ta{Hruh,} Curwen barked. 
\ta{Smartass, are you?}

\ta{Yes, sir.} Carzain's smile remained innocent. 

Curwen held his gaze for a moment. 
\ta{%
  Hm. Ah, well, that's a good thing, I guess. Humility doesn't become a mage.} 

\ta{That's what I've told myself, also.}

\ta{Hm. Alright, kid... what was the name?}

\ta{\Shireyo, captain. Carzain \Shireyo.}

\ta{Right.}

\ta{Certainly not \quo{kid}.}

\ta{%
  We'll see about that. What can you do? What kind of magic? Who taught you? What experience do you have?}

\ta{%
  I am a Vaimon. Rogue, trained to use \iquin{} and \nieur{} alike. I was taught by my father, Nishain \Shireyo{} of Clan Geican, and my mother, \Roanne{} \Deracille, previously a \soror{} of Clan Redcor...}

As Carzain talked, he noticed the captain's eyes drift away. 
Carzain followed them and found them settled on a young girl walking by. 
Chestnut hair in a single braid, she wore a dark dress and was carrying a basket of bread. Or apples. Or whatever. Carzain's words trailed off as his gaze was drawn quickly away from the contents of the basket and towards her bosom. It was ample to begin with, and the tight bodice of her dress, combined with the way she held the basket, served to further emphasize her curvature. 

The girl, who was short, walked close by them, allowing them a clear, close-up view of her cleavage. 

\ta{Hmmm,} it came from Curwen. 

\ta{Yum,} Carzain mumbled. 

The two men's eyes met. 
A moment of silence. 
Then they both laughed out loud. 

\ta{If only she had been a foot closer, I could have grabbed her ass,} chuckled the captain. 

\ta{What are \Qliphoth{} for, captain?} 
A sly smile on Carzain's lips. 

Two yards or so behind him, the girl yelped, then scowled around. 
Carzain demonstratively averted his gaze to the sky, whistling a tune. 

Curwen roared with laughter and gave Carzain's shoulder a hard slap. 
\ta{Ah, I think you and I will work fine together, \Shireyo.} 

\ta{Ow.} Carzain rubbed his shoulder. 

The girl's eyes found Curwen. 
He gave her a toothy grin. 
She immediately turned and hurried on her way. 

\ta{Heheheh. Girls,} Curwen chuckled. 
\ta{Now... you were saying something?}

% Also, the Redcor Esmerel arrives. She is on the hunt for the Scion. 
% Maybe she meets with Charcoal. I don't know. 
% Yeah, I think she does. Either she or her assistant. And Charcoal keeps looking at her breasts, even commenting on them. 

%\end{comment}





