\bookchapter{Dark Crypts of the Mind}
% \bookchapter{The Writhing of the Worm}
\begin{comment}
\subsection{Tiroco and the Crazy Old Woman}
\end{comment}
\stamp
  {\dateTirocoAndTheCrazyOldWoman}
  {Southeastern \hs{Malcur}\\
   Evening}

\Tiroco{} did not like these seedy lower-class neighbourhoods. 
They scared her. 
Those cramped streets with buildings leaning out to loom overhead made her feel choked. 
She was very glad to have Sevac, her faithful bodyguard, with her. 
She was afraid robbers might jump them at any moment. 
She was told poor neighbourhoods were full of robbers. 
She had never seen a robber except in chains, and had never feared them before, but now, out here in the city in disguise, with only a single soldier to protect her, she felt vulnerable. 

She bore her own smallsword under her robe. 
Every noble-born \scatha{} was expected to learn to defend himself or herself. 
\Tiroco{} had never developed any real skill with the weapon, and its unfamiliar presence at her waist did little to console her. 

It was very dark, compared to the lit palace corridors she was used to. 
And it smelled bad, too. 
\tho{Is this how poor people live? Awful.} 

\tho{I have no idea where we are. 
  I have spent plenty of time looking at maps of Malcur.
  The maps always look nice. 
  Even the ugly parts of town.
  I had thought the real thing would look similarly nice.
  
  I am supposed to rule and protect this city. 
  Now I realize how little I actually know of it.
  
  I am supposed to go and meet some of these servants of Light. 
  Why do I have to come to them? 
  Why can't they visit me at court?
  Or at least a nice mansion in a respectable neighbourhood? 
  Why must they operate in such murky places?
  Of course, they must. 
  For secrecy.
  I just wish they didn't have to be \emph{this} secret.}

\ta{How far yet, Sevac?} she asked. 

\ta{I'm not sure, my lady,} said Sevac. 
\ta{I think we took a wrong turn somewhere.}

Sevac had worked as a city guard before being promoted and eventually ending up as \ps{\Tiroco}{} personal bodyguard, so she should have some familiarity with these neighbourhoods. 
\tho{%
  But it has been several years since Sevac was last on street duty. 
  I suppose she hasn't been anywhere near here in years.
  I should have thought of that. 
  I think of her as a \quo{guard} who knows about \quo{guard}-things. 
  But of course, she has her own limitations. 
  I should have considered that. 
  I should be more considerate. 
  I should not treat her as a generic soldier and expect her to just be able to do whatever things I need. 
  
  Is this what I do? 
  Do I see my servants as faceless, generic commoners that exist just to serve my needs? 
  I hope not.
  Do I?}

\ta{My lady,} said Sevac, interrupting \ps{\Tiroco}{} brooding. 
\ta{You should stay close to me. 
  I am not sure where we are, but I don't think it's safe here.}

They emerged from the narrow streets into a more open area with short huts and hovels. 
Many of them looked crumbling and abandoned. 
\tho{And no wonder. 
  Who would want to live here?
  Also, did it not suddenly get colder?
  There is an unpleasant draught here.}

\tho{Sevac. I don't like this place. Get us out.} 
She was about to say that out loud, but scolded herself and stayed quiet. 
\tho{Sevac is doing her best. I should not always complain.}

They wandered further. 
After a while they came to a clearing where there grew trees. 
Ugly trees. 
Crooked and leafless. 
Not green and brown, but gray and black. 

\tho{%
  \Iquin. 
  What is this ghastly place? 
  I didn't imagine we had such ugliness in Malcur.}

Even at a distance, those trees scared \Tiroco. 
They looked dead, but somehow they seemed to move and writhe. 
As if they wanted to reach out to grab a passer-by and eat her. 

Just thinking about it made \Tiroco{} imagine those deathlike twigs and branches coiled around her arms and legs, dragging her into its monstrous embrace. 
She hugged herself tight and leaned close to Sevac. 

\ta{Where are we, Sevac? What is this place called?}

\ta{%
  It has no name, my lady, but some call it the \quo{dead garden}. 
  They say evil \qliphoth{} dwell here. 
  Let us leave quickly. 
  At least now I know where we are.}

They skirted around the edges of the \quo{garden}, steering clear of the trees. 
The place smelled of death and unwholesome, unnatural things. 
And it was deathly quiet. 
Other than their footsteps, no sounds could be heard. 

\tho{No, wait. There is a sound. A voice?}
\Tiroco{} looked around and noticed a humanoid figure among the trees. 
A \meccaran{}. 
An old female \meccaran. 
Wandering around, apparently aimlessly. 
Muttering to herself. 
\Tiroco{} cast a glance at Sevac. 
She had also noticed the \meccaran. 

\ta{It is coming closer,} the \meccaran{} said. 
\ta{% 
  Closer. 
  Ever closer. 
  Dead flesh everywhere. 
  Everything is turning to flesh. 
  Corpse flesh. 
  Cold and dead.
  And the chains. 
  Always groaning... grinding... rattling...}

She saw the two \scathae{} and stared directly at them, as if accusing them. 
\ta{%
  We are all bound!
  Bound in huge chains and dragged on!
  Dragged down. 
  Into the abyss of fear. 
  The abyss of illusions and despair.}

\ta{Who is this?} asked \Tiroco. 

\ta{Just some local madwoman,} said Sevac. 
\ta{And drunk, too, as far as I can smell. Stay behind me, my lady.}
She placed herself between \Tiroco{} and the \meccaran. 

The \meccaran{} was staggering closer to them. 
\ta{%
  Illusions and reality. 
  Reality and dreams. 
  Dreams of death.
  The land of death!
  A wasteland of flesh.
  Decayed. 
  Putrid.
  And crawling with worms.
  The worms!
  Growing ever fatter. 
  Feeding on our flesh.
  And our souls.
  Our minds!} 

Suddenly the \meccaran{} collapsed to her knees. 
There she sat, holding her head in her hands and rocking back and forth.
\ta{%
  Eating my mind!
  My thoughts. 
  My feelings.
  My dreams.
  Yes. 
  They are in my dreams. 
  In the wilderness of nightmares. 
  In the maze. 
  In the dark crypts of the mind, where all ancient horrors lurk. 
  Things older and darker than we know.
  Always lurking. 
  In the corners of our eyes. 
  Whenever we look away. 
  Wherever we refuse to look. 
  Wherever we fear to look. 
  There they are.}

She looked up at them. 
Her eyes were hazy. 
\Tiroco{} could not tell if she actually saw them or if she just stared blindly into space. 

\ta{My dreams! They are in my dreams! The worms!}
She crawled closer. 
\ta{Can you not feel the writhing of the worm beneath you?
  Can you not see them all around you? 
  Hear them? 
  Smell them?
  Do you not dream of them every night?}

She reached up and tried to paw at \Tiroco{} with her short arms. 

\ta{Get off of us, you bum!} 
Sevac pushed the mad \meccaran{} away. 
\ta{Come on, my lady.} 
She shooed \Tiroco{} on, keeping a watchful eye on the babbling \meccaran. 

\Tiroco{} had a hard time making herself look away. 
Her eyes were drawn to the \meccaran. 

The \meccaran{} babbled on. 
\ta{%
  You do not see them. You are too blind. But you will! Mark my words!
  The worms are coming. 
  They are coming for us all. 
  You will feel them. 
  Burrowing beneath you. 
  Gnawing your feet.
  Eating your mind.
  They are in your mind. 
  In the maze. 
  We are all trapped in the maze with the worms. 
  Running.
  Running blind. 
  But trapped. 
  And doomed.
  And the chains! 
  The chains bind us all!
  Groaning. 
  Grinding.
  There is no escape.
  No escape from the maze of chains...}
The words trailed off as Sevac all but dragged \Tiroco{} away from the scene. 

\Tiroco{} walked on, oblivious to her surroundings, letting Sevac guide her. 
She could not shake the \ps{\meccaran} words from her mind. 
They haunted her. 
They rung \emph{true} in \ps{\Tiroco}{} ears, and it was a ring that made the cold creep in under her scales. 

\ta{My lady?}

\Tiroco{} noticed they had stopped. 
Sevac was looking her into the eyes, a worried expression on her face.

\ta{Are you well, my lady?}

\ta{Yes... No.}

\ta{You are not worried about the madwoman's ramblings, are you? 
  Pay her no mind, my lady.
  There are many such crackpots in the city.
  But with this new campaign you have declared, I am sure we will have that problem fixed soon.}

\ta{Yes. Fixed. Yes.}
She tried to smile. 
\ta{You are right, Sevac.}

\ta{Come, my lady. We are almost there.}

Sevac led her on. 
But her thoughts stayed on the old \meccaran. 
\tho{Maybe Sevac is right. Maybe she is just mad.
  But maybe she is right. 
  Maybe she is referring to the same evil that the angel talked about. 
  And if that much is accurate, how many more of her words might not be true as well?
  
  Oh, \sephiroth. 
  Worms. 
  Dead flesh. 
  Chains. 
  And mazes. 
  Crypts.
  
  I don't understand any of it, and that is why it frightens me so much. 
  I wish I knew more. 
  I wish I were a wise mage, like \mater{} \Vincerre{} or Moro \Cornel. 
  Maybe then I would be able to understand what I am up against.
  I don't know anything about this evil that I am supposed to combat.
  Is it worms? 
  Is it something with chains?
  A maze of chains? 
  What does that even mean?
  The \quo{wilderness of nightmares}. 
  The \quo{dark crypts of the mind}. 
  What did she mean?
  
  Oh, I wish I were smarter...}









\begin{comment}
\subsection{Tiroco and Moro}
\end{comment}
\stamp
  {\dateTirocoAndMoro}
  {\CastlePelidor, \hs{Malcur}}

\Tiroco{} walked alone in a hallway, thinking the events of the previous night. 

She had met and talked to some of the servants of Light she was supposed to be \cooperating{} with. 
It had been a confusing experience. 
Some of them\dash the leaders\dash looked civilized, perhaps even heroic. 
But many of the rest had been  unwholesome to look on. 
Scary, even. 
They looked nothing like what she imagined servants of Light should look. 
They looked like criminals. 
Lowlives. 
Scum of \Miith{}. 

\tho{But then, they must. That was what \Icor{} told me. 
  They must disguise themselves as criminals. 
  So the Dark ones do not catch their scent. 
  And they must make sure not to break character, in case spies might be watching. 
  That must be it. 
  They were dressed up and acting.
  
  I must not be so judgmental.
  I must trust them.
  They are working to save our beloved city, just like I am.}

She walked on, lost in her thoughts. 
Along the way she met Moro \Cornel. 
\Tiroco{} gave the archmage a polite nod. 
\Cornel{} returned the gesture. 
Then slowed down. 
\Cornel{} looked around, almost suspiciously. 
She approached \Tiroco. 

\ta{My lady duchess? You look unwell.} 

\ta{Oh... no. Thank you. But it is nothing.} 

\tho{She can tell I am lying. 
  I know she can. \Cornel{} is too smart for me to deceive.}

\Tiroco{} tried to dodge past \Cornel{} and continue on her way. 
But at the last moment, \Cornel{} reached out and laid a hand on her arm. 
\Tiroco{} was trapped. 
She could not shake the hand off and keep walking; that would be rude. 
She was forced to stop. 

\ta{Remember, duchess,} said \Cornel, 
\ta{I am here to advise you, to share what wisdom I have. 
  I know many things. 
  It is an offer you should not waste.}
She paused, as if unsure of whether to continue. 
As if forcing herself. 
\ta{You are not alone in this. You are not alone \emph{against} this.}

With that, \Cornel{} averted her eyes and walked on, leaving a bewildered \Tiroco{} to wonder what she had meant. 



\new
Moro \Cornel{} hurried away, too embarrassed to stay. 

\tho{%
  Gods, that was awkward. 
  \quo{I know many things}. 
  That sounded ridiculous. 
  But that is the sort of things wise mages say in stories.
  Oh, gods, listen to me.
  Trying to emulate a hero from a story.
  One would think I was too old for that.
  
  I don't know if I did anything right.
  Probably not. 
  I can be subtle as long as \quo{subtle} means slinking around in silence and in disguise. 
  But when \quo{subtle} means talking to people and gaining their trust, I am lost.} 
  
\tho{%
  \quo{You are not alone against this}.} 
That one had been a probe. 
A risk she felt she had to take.
\tho{%
  There is something evil going on in Malcur. 
  I know it, and I think \Tiroco{} knows it, too. 
  If I am right about her, then maybe it convince her I am an ally. 
  If I am wrong, it will just make me look like a crazy old mage.
  If I am even more wrong, it will make her suspect me and trust me even less. 
  I hope I haven't made it worse for myself. 
  
  I wish I knew what I was doing.}









\begin{garbage}

\begin{comment}
\subsection{Carzain}
\end{comment}
\begin{comment}
\subsubsection{Dreaming}
\end{comment}
\stamp
  {\dateCarzainDreamsInWaythane}
  {Waythane Forest}

% Now that Vizicar is closer to the surface, Carzain begins to {share his visions and nightmares}. 
% 
% He is haunted by the tortured, hateful faces of shackled ghosts. They show him their world: Cold, cruel, dreadful. They hate him and desire to drag him down into their prison\dash groping for him with their clammy, hideous hands. 

% He awakens full of terror, and also a tinge of guilt. He has a feeling that he is somehow responsible for their torment. 
% 
% He also has vague dreams of lost greatness\dash {unconsciously visualizing} the {\Mystraacht{} \matrix}. Feelings of having been betrayed, having lost his power and his memory, upon which his enemies descended upon his weakened self like vultures, usurping his rightful place and honour and forcing him into flight and hiding. 
\begin{dream}
There is cold. 
There is pain. 

There is the lashing wind. 
There is the piercing ice. 

There is the touch of their hands. 

They reach out to grasp and grope at him with their clammy hands. 
He fends them off. 
They keep coming. 
Thousands of them. 
Millions of them. 
The shackled dead. 
They are bound to him, and he to them. 
He flees from them, but they follow behind him. 
They are his shadow. 

They hang like flies in a spider's web. 
Empty husks. 
Carrion. 

Their eyes are empty, but still they stare. 
Full of hate. 
Full of pain. 
Full of blame. 
Dead. 
Cold. 

They rattle their chains. 
They croak in their feeble voices. 
They grasp at him with cold hands. 

They hang behind in droves, like a tattered cloak of souls. 

No... not a cloak. 
A web. 
A network. 
A constellation. 

A \matrix. 

His vision clears. 
He sees it now. 
A vast network of roads, paths, pillars, ladders, catwalks. 
He stands on a colossal column overlooking the complex. 
Beneath, millions of slaves crawl in formation. 
Men and women.
\Humans{}, \scathae{} and other things. 

Faceless. 
Blank. 
Void. 

Chained together in threads and lines. 
Chained to him. 
Like marionettes. 
Milling like ants. 

Deaf. 
Dumb. 
Blind. 
Mindless. 
Toiling. 

Their lives and deaths are the blood and breath of the complex. 
The \matrix. 
His \matrix. 
His mission. 
His purpose. 
His life. 
\end{dream}

\begin{comment}
\subsubsection{Awake}
\end{comment}
\new
% When he wakes he thinks about the whole thing. 
% Part of him is horrified at the madness that is consuming him. 
% But another part is excited. 
% Because the possession brings \emph{power}. 
% And a feeling of being destined for greatness and glory. 
% This is what he has always dreamt of. 
Carzain opened his eyes. 
\tho{Whoa. What was that?} 

He looked around. 
Still in Waythane Forest. 
With \Tsekkect{} and Delph and the others. 
\Relcs{} and all. 

His wounds still smarted. 
But the visions he had seen disturbed him more. 

\tho{Does it mean something? 
  It might not. 
  Dreams do not always mean anything. 
  But some do.
  And right now I am a madman possessed by \qliphoth.
  I don't think I can afford to just discount it. 
  The dream might be a clue. 
  It might tell me something. 
  
  But what?}

\tho{What were those people I saw? The ones with the grasping hands. 
  They were horrible.} 
Just thinking back to it made his skin crawl. 
He could still feel their cold, corpselike hands pawing at him. 
Still hear their choked moans and wheezes. 
Still see their empty eyes. 
Devoid of all thoughts and dreams and will. 

And they blamed him for it. 
Drilling into his soul with their dead eyes. 
Ripping his skin with their numb, blunt fingers. 
So weak. 
So powerless. 
So dreadful. 

\tho{Who are they? What are they to me?
  Are they \qliphoth? 
  No, that doesn't feel right. 
  Ghosts?}
He could not say how, but he had a feeling they were ghosts. 
\tho{And why do they come for me? 
  They have something against me. 
  They hate me. 
  Why do they hate me?
  
  Are they just evil ghosts who hate everyone simply because they are evil ghosts? 
  No. 
  I don't think that's the answer. 
  
  There is more to them.
  
  They were tied to me in some way. 
  Why was I tied to those ghosts?
  Was I trapped by them?
  Were they trapped by me?
  In me?
  Am I possessed by ghosts? 
  Is that it?
  Is there a horde of ghosts inside me, controlling me?}
It was a morbid idea. 
It sent shivers down his spine and made his skin itch. 
He scratched his arms, as if that would expel the ghosts. 
He wanted to spit them out. 
Cough them out. 
Vomit them out. 

\tho{Am I full of ghosts? 
  Is that what is wrong with me?
  If so, where do they come from?
  Why me? 
  They have some grudge against me. 
  I felt that. 
  I am pretty sure of that.
  Why?
  It was as if... as if they blamed me for killing them.
  Are they people I have killed?
  No.
  That can't be.
  That's nonsense. 
  There were millions of ghosts. 
  I haven't killed more than... I don't know, a score of people at most.
  And if the ghosts were angry at my killing them, why would they possess me and make me kill more people? 
  
  No. 
  This can't be right.
  I am not just \quo{possessed by angry ghosts}.
  That explanation does not make sense. 
  I am barking up the wrong tree. 
  
  Back there, in the fight, it didn't feel like angry ghosts. 
  It was this \quo{Emperor} feeling. 
  A feeling of power. 
  Pride. 
  Majesty.
  That's not what a bunch of clammy ghosts would feel like. 
  At least, it didn't feel anything like this dream. 
  There is more to it. 
  But where do the ghosts fit into the picture? 
  If ghosts they are...}

He thought back to the dream. 

\tho{What happened after the part with the groping ghosts?}

The next part was more unclear, more mysterious. 
He had to struggle to remember it. 

\tho{There were those people.
  Slaves. 
  Chained and toiling. 
  Are they the same as the ghosts? 
  They might be. 
  And they were... faceless. 
  Blank and without identity, somehow. 
  What does that mean?
  
  They were moving in lines. 
  As if orchestrated. 
  And I stood atop that pillar.
  Looking down on them.
  Controlling them?
  What does that mean?
  
  \Qliphoth. 
  I can't make sense of any of this. 
  If only I had spent less time learning how to just summon some flashy \Archons{} and kick butt, and more on understanding the deeper mysteries of how the occult worlds work, maybe I would know how to interpret these dreams. 
%   
%   I wish I knew how to interpret dreams. 
%   I realize now that I don't know enough of the deeper mysteries of metaphysics. 
%   All my studies have been focused on commanding some flashy \Archons{} so I could kick some butt.
%   There are things in the books that could help me understand all this. 
%   There must be. 
%   
%   I wish now I had spent more time on really understanding how the occult worlds work. 
%   Who would have thought I would ever need it?
  
  I'm a madman trying to solve the riddle of his own madness.
  I need help. 
  At this rate I'll get myself killed, along with the people around me.} 

Suddenly feelings welled up in him in protest. 
\tho{
  No!
  That is not true.
  Both of the times when I was possessed, I \emph{saved} myself and my companions. 
  It is not madness. 
  It is power. 
  It is not evil. 
  It is good.} 

\tho{
  Wait, what am I saying? 
  Do I really mean that? 
  
  Were those even my own thoughts? 
  Or were they the thoughts of the thing possessing me?
  They sounded like my own thoughts. 
  But then, what do I know? 
  I am, after all, going mad.
  
  No! 
  I am not going mad! 
  I can combat this. 
  That time on the hill with Curwen, I successfully forced down the possession. 
  I can learn to control it.
  Maybe it is just like an \Archon{} that I need to learn how to manage.
  
  Yes. 
  I will get this under control. 
  I don't need help. 
  I will master this, just like I have mastered so many other \Archons. 
  That is what a Vaimon does: 
  Confront the entities of the mystic worlds, challenge them and conquer them. 
  
  Look at \hs{Lestor Delain}. 
  He dabbled in dark magic when everyone warned him not to. 
  But he persevered, and he mastered them all. 
  Even the Midnight \Qliphoth. 
  And he became one of the great heroes who shaped the \hs{Vaimon Empire}. 
  
  The Darkness is to be feared, yes, but not fled from. 
  Conquering our fears is what makes us great. 
  
  Or something like that.}
 
\end{garbage}








