\bookchapter{The Emperor Inviolate}
\begin{comment}
\subsection{Curwen spies on Rungerans}
\end{comment}
\stamp
  {\dateSortieInCombat}
  {\hs{Kenshaer Forest}\\
   Late evening}
% \begin{comment}
Gwelthein raised her hand. 
\ta{Quiet. Listen.}

Curwen strained his ears. 
Forest sounds. 
Birds screeching. 
The \relcs{} huffing and shuffling. 
One soldier scratching his ass. 
Nothing of note. 
\ta{What?}

\ta{I can hear the Rungerans,} said Gwelthein. 
\ta{This way.}

And true enough, after a short while the rest of them\dash without sharp \ranger{} ears\dash could also hear the noise from the Rungeran army camp. 

\tho{Finally,} thought Curwen. 
They had been trying to stalk the Rungerans for days. 
A few times they had been able to shadow them, peering out from the edge of the forest, but they could not keep creeping along at the edge for fear of discovery, so they had to take more convoluted paths through the \Wylde{} and hope to find the Rungerans again. 

\tho{%
  I need to catch them with their pants down.
  I need to see this vaunted sorcery of theirs in action.
  In an ideal world I'd like to see them conquer a town like they did with Gilwaed back there.
  But I can't very well just camp down in a town and wait for the Rungerans to waltz by and wipe it out.
  
  So we're reduced to stalking and spying on them.
  But with luck, we can at least get a peek at their \ishrah.}

\tho{%
  I need to get close. 
  This'll be risky business, of course. 
  But I didn't get to the place I am today by not taking risks.}

\ta{Right,} he said. 
\ta{We're moving in for a peek.}
\tho{Hm. We're way too many to sneak up on them in force.}
\ta{%
  Filcoi, you're with me. 
  \Shireyo. 
  You too. 
  Gwelthein, you're in charge of the rest while I'm gone. 
  Let's go.}






% They advance and peek into the army camp. 
% They sneak up on foot (ten \relcs{} are not easy to sneak with). 
% Curwen can sniff out the mages, so they pick the edge closest to where the \ishrah{} is camped. 
% Which is hard, because the \ishrah{} is in the middle of the camp. 
% As they would be in any sensible army. 
% Curwen: 
% \tho{Crap. The Rungerans aren't idiots.}
% 
% But they are camping along a road, so the camp is oblong and not circular. 
% So they can pick a good spot. 

They dismounted\dash the \relcs{} were hard to conceal\dash and snuck through the dense foliage. 
As they got closer Curwen could feel vibrations. 
\tho{Jackpot. Their \ishrah{} is at it.}
He followed the scent of magical activity and led them to the edge closest to where the Rungeran \ishrah{} was camped. 

As they reached the edge of the wood and neared the great road the army camp came into view. 
It was a huge sprawled mass of tents, fires and massive beasts. 
At first glance Curwen estimated its size at about ten thousand soldiers. 
But then he looked to the sides. 
The camp continued along the road for as far as the eye could see in both directions. 

\tho{%
  Damn. 
  Ten thousand? 
  Yeah, right. 
  More like twice that.
  I hope this is all they've got.}

On an open plain the army camp would have been more circular, but here they were travelling on a road through dangerous \Wylde{}, so they were forced to set up a long camp along the road. 
This worked in Curwen's favour, for it made it easier to sneak in and get a look at the \ishrah. 
As in any sane army, Curwen reflected, the mages would be placed somewhere in the middle for maximum protection. 
But in a long, narrow camp like this, the \quo{middle} was still relatively close to the edge and could be spied on. 

The Rungeran mages were practicing their magic. 
At this close range they shone like a beacon to Curwen's senses. 
The Pelidorians found a good position on the top of a small rise and hunkered down to observe. 

He noticed six mages at least. 
Probably a few more. 
One woman went among the others as if instructing them. 
She had brown hair and wore a burgundy travelling dress. 
The woman held her head high and directed the other mages with commanding gestures. 
Her body language clearly marked her as the \ishrah{} leader. 

\tho{%
  Interesting. Who is this one?
  
  She's pretty. 
  Wouldn't mind getting me a piece of that ass.}

Apparently their spellwork was just getting started. 
The burgundy-clad woman had arranged the \ishrah{} into a concert. 
They had lined up in geometric formation, with the woman in the centre as the \apex. 
\tho{%
  Definitely a \rethyactic{} formation. 
  Hm. 
  Odd. 
  I would have taken most of them for Vaimons.}

The mages began intoning the \draconic{} words of power, and lines of mystic energy shimmered into existence between them, making the concert glow like a huge hieroglyph of eldritch light. 
A hieroglyph whose nodes and corners were people. 
Curwen was no \rethyax, but he could feel how their arcane symbols opened the mystic paths into the Beyond, and how their words of power reached out into Chaos, beckoning. 

And the \daemons{} gave answer. 

\tho{%
  And what \daemons! 
  Such fury. 
  Such savagery. 
  Such hideousness. 
  Such malevolence. 
  Such \emph{power}.
  
  There is no doubt. 
  These are the same forces that wiped out Gilwaed.}

% The mere trace of these \daemons{} at Gilwaed had been poignant enough, but it could not compare to the feeling of the experincing the conjuration at close range like this. 
At this close range, the conjuration was so potent that even the mindless layman might notice it, and any mage worth his salt would recognize a \daemonic{} presence of the direst kind. 
To Archibald Curwen, whose senses reached deeper into the Beyond than even most mages', it was immense. 
It felt like a dozen whirlwinds blowing in his face, a hundred mouths howling straight into his ear, a thousand thorny paws pressed against his skin. 
% It might have broken a lesser man, and it was enough to leave Curwen breathless. 

\tho{%
  Fuck. 
  Just... fuck.
  
  Pull yourself together. 
  This is it. 
  This is what I was hoping for. 
  Must pay attention. 
  Must learn all I can.}







\begin{comment}
\subsection{\Tsekkect{} and Delph}
\end{comment}
\new
Gwelthein had had the rest of the group dismount and care for the \relcs, who were exhausted after a long ride through rough woodland. 
\Tsekkect{} had removed her beast's saddle and watered and fed it. 
She was now sitting on top of it, grooming it with her feet. 
Being \meccaran{}, she always preferred to use her strong legs instead of her short arms if it was at all practical. 

Delph was next to her, stroking his \relc, who was lying on its side looking indolent. 

\ta{Hey, midget,} she calls out. 

\ta{%
  Don't you dare start calling me that! 
  Don't start following Curwen's examples.}

\ta{Haha. All right. Anyway, what's with Carzain?}

\ta{What's with him?}

\ta{%
  He's been all quiet and navel-gazing ever since the village? 
  He barely talks. 
  You have to smack his head to get him to respond when spoken to. 
  A when you told that joke about your penis, he didn't even chuckle.}
One of the other soldiers laughed in the background at the mere mention of the penis joke. 
\ta{That's not natural.}

\ta{Well, that village... ow!} 
Delph was interrupted when his \relc{} roughly poked him with its big foot. 
\ta{%
  Stupid animal. 
  Anyway, that village was pretty freakish.
  Weren't you creeped out?}

\ta{%
  Sure, but does that justify being moody and un-talkative for days on end?
  Given how he talks big, oughtn't he be, y'know, made of stronger stuff?}

\ta{%
  Yeah.
  I guess he ought.}
Delph paused to spit out a piece of tobacco.
\ta{%
  I don't know. 
  He's one of them mages, after all. 
  Mages are always weird.
  All those spirits and ghosts slowly make them crazy in the head, you know.}

\ta{Huh.}
\ps{\Tsekkect}{} \relc{} gave a deep croon as she massaged its head with her feet. 
\ta{Maybe you're right. Maybe he's just crazy in the head.}







\begin{comment}
\subsection{Carzain feels Vizicar}
\end{comment}
\new
% Carzain is there with Curwen. 
% He looks down at the Rungeran mages and see them cast their spells. 
% He likewise recognizes the feeling from Gilwaed. 
% He sees, hears and smells all sorts of evocative images. 
\tho{What a bitch.}

Carzain had taken an immediate and instinctive disliking to the brown-haired woman who apparently led the Rungeran \ishrah{}. 
He could not exactly justify why, but on some level he disliked women who took a commanding role. 

Now they were casting their spells, in their \rethyactic{} manner. 
Invoking names, uttering words of power. 
Summoning \chaotic{} powers and \daemons. 

And he sensed the \daemons{} that came up from the depths of Chaos to heed the sorcerers' call. 
It was similar to the feeling at Gilwaed. 
It stirred up memories. 
Feelings. 
Feelings of revulsion. 
Feelings of elation. 

\tho{Stop that! Cut it out!}
He did not want to deal with those emotions. 
Did not want to consider their import. 
Did not want to face the dilemma they presented. 

So he forced himself to concentrate on the present. 
Concentrate on the Rungerans. 
Their incantations. 
Their shifting formation. 
The forces they conjured. 
The \daemons. 
The \daemons{} that came up from Chaos. 
Howling. 
Slithering. 

As he focused, new images intruded on his mind. 
He almost heard the beat of black leathern wings from the benighted voids beyond. 
Heard the slavering of things hungry for the blood and souls of men. 
Heard the clicking of their teeth and claws. 
Almost felt the drool from their maws on his neck. 
Felt the tremendous winds of their passage. 

It brought back memories of his old nightmare. 

\tho{%
  Cast adrift in the void. 
  Immense gods thunder past me. 
  
  And I am nothing...}

\vizicar{%
  The foe threaten us with their sorcery. 
  We must take to arms. 
  To war, my Vaimon brethren!}

\tho{What was that?}

Images flashed before Carzain's eyes. 
Gone and forgotten was the world from just a moment before. 
He stood on a hill overlooking a vast army, armoured in white and golden colours, arrayed in formations and battle-lines. 
All were watching him. 

He raised his sabre. 
And at his signal, the army marched. 
At his command, tens of thousands of men marched into battle. 

No. 
Not men. 
Monsters. 
And angels. 
And \daemons. 
Hordes of darkness and light.  
Clad in white and black. 
Silver and gold. 
Purple and blood red. 
Millions and yet millions of them. 
Angels. 
\Dragons. 
Monsters. 

Armies met in a mighty clash. 
Fire and lightning cracked the sky. 
Thunders rolled. 
The earth quaked. 
The heavens blackened. 
The horizons burned. 
The rivers ran crimson. 

Darkness. 
Light. 
Fire. 
Blood. 
Death. 
War. 

\vizicar{%
  And I stand above it all.
  
  I am...
  
  I am...
  
  Who am I?}

The scenes blurred. 

\vizicar{Who am I?}

He struggled to remember. 

\tho{%
  Who am I?}

A name came to him. 

\tho{%
  I am Carzain! 
  \CarzainShireyo!}

\vizicar{No...}

Slowly it came back to him. 

\tho{%
  Yes, damn it!
  I am \CarzainDeracilleShireyo!
  
  I'm in the middle of my own battle. 
  I can't get caught up in crazy fancies now.
  Focus, Carzain. 
  Focus on the real world.}

\vizicar{%
  Real world... 
  
  Real world...}

Doubt filled him. 

\vizicar{%
  What is real?}

He wrestled against the doubt. 

\tho{This is real! I am real! Pelidor and Runger are real!}

The visions subsided. 
The battlefields faded. 
\Dragons{} and angels slipped away. 
Mythical monsters became mundane \mulgrons{} and elephants. 
Ancient warriors in silver and black became modern Rungerans in tan and brown. 
Millions became thousands. 
Mountains and valleys became a road and a forest. 

Carzain was back in the real world. 
On the hill. 
Outside the forest. 
Next to the road. 
Overlooking the Rungeran camp. 

\tho{%
  Phew.
  I made it.}

It took a few moments for the import of that to sink in. 

\tho{%
  I made it!
  I forced down the vision. 
  I'm not mad.
  There may be something wrong with me, but it doesn't own me. 
  I can control it. 
  I'm not a slave of these hallucinations. 
  
  I'm not nothing.}

His mind once again his own, he remembered the task at hand. 
He studied the Rungeran mages. 

They had broken formation. 
Two of them were down, crawling on their knees. 
Exhausted and sick. 
One of them vomited. 
The commanding woman had left them and was crossing the camp with long, determined strides. 

\tho{What happened? Did I miss something important?}

Captain Curwen poked his side. 

\ta{%
  We can't risk to hang around any longer,}
said Curwen.
\ta{%
  They'll see us.
  Move.}

And so they crawled down the hill and back into the woods. 

\tho{%
  Great scouting I did. 
  I hope Curwen doesn't find out I dozed through it...}







\begin{comment}
\subsection{\Takestsha{} notices \vertex{}}
\end{comment}
\new
% % \begin{comment}
% \Takestsha{} has been keeping an eye on the wandering \vertex{}. 
% Remember, stealth and subterfuge is her area of expertise, so she has had some success in tracking it. 
% Now Vizicar flares up. 
% She immediately detects it. 
% 
\Takestsha{} was busy instructing the Rungeran mages, rehearsing the spells recovered from \EreshKal. 
It was hard and taxing work for all, for the \EreshKali{} spells were difficult, and most of the mages were Vaimons with no \rethyactic{} training. 
\tho{%
  They cannot all possibly learn to master the spells in the short time we have. 
  I know that. 
  But a few of them can learn. 
  And the rest can learn to support us in concert.
  That should be enough. 
}

\ta{You! Keep your concentration!}
she snapped at one of them. 
The Vaimons would keep pronouncing the words of power wrong or fail to visualize the spells correctly. 
\tho{%
  Fools. Is this really what passes for mages in this day and age? I ought to...}

They were close to their limit, she knew. 
Some were about to collapse from the strain. 
\tho{%
  But I have to train them. They will have to develop more endurance than this if we are to wield these spells on the battlefield.}

Her chain of thought was interrupted as a surge of power washed over her. 
Nothing like the \EreshKali{} energies. 
No, a spike of power in the Web. 

She recognized it immediately. 

\tho{The \vertex. It is back.}

It faded as quickluy as it spiked, but this time \Takestsha{} was prepared and wasted no time. 
As soon as she feels it, she reacted quick as lightning, latching onto a cosmic thread and following it to the source of the disturbance. 

\tho{%
  And the carrier is... 
  right next to me. 
  
  Over... there. 
  At the edge of the forest.}

The spike was gone again, leaving her little wiser concerning the nature of the \vertex. 
She still could not say \emph{what} it was, but now she knew at least \emph{where} it was. 
\tho{%
  Just up there on the hill. 
  Hm. 
  There is a Vaimon scent emanating from the source. 
  No, wait. 
  Two Vaimon scents. 
  One from the source, and another from a location near it. 
  The \vertex{} source is the... weaker one. 
  Interesting.

  What is going on? 
  Who is the \vertex, and why is it here? 
  I will have to probe to find out. 
  I could use magic to sniff... but no, that might give too much away. 
  No, let us try something a little more subdued. 
  Let us try sending some men to poke at it.

  They might get slaughtered, of course. 
  The \vertex{} might be dangerous. 
  But it is worth the price. 
  I would not want the \vertex{} to suspect the extent of my knowledge. 
  
  But a little squad of soldiers should do nicely. 
  After all, they are snooping around just at the edges of our army camp. 
  It should hardly surprise them that someone might notice them and try to dispatch them. 
  If, on the other hand, I were to take precautions for dealing with the \vertex, I will alert them to my presence. 
  Then I risk them taking their own precautions.
  We cannot have that.}

\ta{\Miss{} \Takestsha?} said one of the \ishrah{} mages behind her, panting. 
\ta{I cannot...}

\ta{Figure it out yourself,} she said, waving him off. 
She was already striding away. 

% Then she went off to find some expendable grunts. 







\begin{comment}
\subsection{Curwen-tachi are attacked}
\end{comment}
\new
% \begin{comment}
\tho{%
  I've seen enough,} 
Curwen thought as they made their way back to their mounts. 
\tho{%
  Well, not really. 
  I still don't know as much as I would like to. 
  But I can't afford to tarry any longer. 
  I have to get back and warn the army. 
  After all, I do want my country to win this war. 
  Besides, for every moment we hang around here we risk discovery.}

They returned to the spot where they had left their \relcs{} and the rest of the group. 

\ta{We're going back to rendezvous with the army,} he declared. 
\ta{Seat up and move out!}

They climbed back in their saddles and made their way back west. 
Curwen left it to the \rangers{} to guide them. 
He rode in his own thoughts, pondering all he had learned. 
And all he had \emph{not} managed to learn... 

\emph{Blam!} 

A bullet flew past his ear. 

\emph{Blam! Blam! Blam!} 

And they were getting pelted with bullets from unseen gunmen between the trees. 

\ta{An ambush! Rungeran goons!} Curwen shouted. 
Frantically he lookeds around, trying to locate the attackers. 

He heard grunts and screams behind him. 
Judging from the sound, at least one of their soldiers and one \relc{} went down in the initial volley. 

Then soldiers sprang out of the bushes and at them. 
Clad in Rungeran finery: 
Brown and tan, a wolverine's head emblem showing. 
A few on \relc-back, most of them on foot. 
And many of them. 
A score, at least. 
The Pelidorians were only a dozen. 

\ta{Shit.}
He looked back and shouted: 
\ta{%
  \Shireyo!
  With me!}
\tho{This is it, kid. If you're worth shit, then prove it.}

He turned back to the attackers to find three Rungerans almost upon him. 
\ta{Back off! \Keshirah!} he invoked. 
The \ps{\sephirah} energy flowed from \Iquin{} into him and through him, manifesting itself as a powerful blast of wind. 
The three soldiers were halted and pushed back; one lost his footing and fell. 

\ta{\Djerzad!} he called out, and the \qliphah{} so named came to him. 
\Djerzad{} lashed out, and the three Rungerans screamed in pain as their bones snapped and broke. 

\tho{Need to cast a ward.}
Curwen had no wards around him like he would normally have on a battlefield. 
They were no good on a covert operation like this. 
Enemy mages could smell a ward from miles away. 
\tho{But by now the harm is done.}
Having bought himself time, Curwen now invoked a \sephirah: 
\ta{\Hoshied!} 
The \sephirah{}, titled the Battlement, came to him, and he wrapped his presence like a mystic shield around Curwen, protecting him from enemy bullets. 

\tho{There. That's better.}
Magical wards were no guarantee, of course. 
A well-aimed or lucky shot could still break through. 
But it certainly made him feel safer. 

\tho{I hope the kid is worth his salt.}
Curwen and the other senior mages had been instructing \Shireyo{} and the other newcomers in spellcasting tactics in battle. 
Now he must prove his worth. 
\tho{%
  Under better circumstances I would have had the boy join me in concert. 
  But this fight is too sudden and chaotic for that. 
  He's on his own.}









\begin{comment}
\subsection{Carzain fights}
\end{comment}
\new
Carzain did not need Curwen's warning to know what was going on. 
\tho{This is battle. This is what I have been training for.}

While he prepared to unleash his \Archons, the Pelidorian soldiers took up positions between him and the Rungeran \quo{goons}, as Curwen had called them. 
Protecting the mages as was their assigned duty. 

\ta{\Hoshied!} he heard Curwen invoke. 
\tho{%
  \Hoshied. Yes. That's it. 
  Got to summon a ward.}

He concentrated. 
Penetrated the barriers of the physical world. 
Reached into \Iquin{} with his mind. 
Let its energy flow into him. 
Let his own mind flow into \ps{\Iquin} energy. 
Searching for the \sephirah. 

\emph{Blam!}

A bullet whiffed by close to his head. 
\tho{Shit! That was close.}

The shot had broken his concentration and he had to start over. 
\Hoshied{} had always been a difficult \sephirah{} for him. 
Again he reached out into \Iquin, searching for \Hoshied's psychic signature. 

\ta{Where's that \ishrah{} support, damn you?} he heard Delph's voice grunt. 
His protectors were hard pressed, he saw. 
One was down with a big, nasty gunshot wound in his head. 
Another was struggling to manage a wounded and bleeding \relc. 

\tho{%
  Got to help them.
  Ward must wait.}

\ta{\hr{Izion}{\Izion}!} he cried. 
\Izion{} was a \sephirah{} Carzain knew well, and he came without delay. 
\Iquin-energy burned in his body and mind, and he released it. 

Several Rungerans burst into flame. 
Their shrieks were awful to listen to as they burned up from the inside. 
Flames licked their skin, causing it to blacken and peel off. 
Flames spilled from their eyes and mouths. 
They writhed in agony. 
It was a merciful thing when Delph and the others cut them down and they fell like smoldering heaps to the ground. 

\tho{That should buy us some time. Now I really have to cast that ward.}

\ta{\Shireyo!} Curwen yelled above the din. 
\ta{%
  No fire! 
  The dry wood'll catch! 
  You'll get us all burned!}

\ta{Got it!} he called back. 
\tho{Right, sure. Just let me cast my ward...}

\ta{Heads up, Carzain!} he heard \Tsekkect{} shout. 
He looked up to see that a goon had broken through their defensive lines and was coming at him with a spear. 

\ta{Whoa! Um...} 
Carzain stammered, trying to come up with a good attack \Archon{} that was not \Izion. 
\ta{Uh... \Keshirah!} 
The \sephirah{} burst from his hands as a blasting wind. 
Carzain had no good idea of how much force was needed, so he poured a massive amount of energy into the attack. 
The spearman was slammed into the ground. 
His skullcap came halfway loose, and his head struck a big stone. 
Blood seeped from under the skullcap. 
He did not move. 

Carzain took a quick look around. 
\tho{I'm clear for the moment.} 
Again he receded into the \hr{Empyrean}{\empyrean}. 
He found his \sephirah. 
\ta{\Hoshied!} he invoked, and he felt the \ps{\sephirah} presence almost solidify around him in a ward. 
\tho{There. Finally.}

\ta{\Shireyo!} a voice called. 
\ta{Could use some help here!} 
It was Gwelthein, encircled by several Rungeran spearmen. 

\tho{I'll be there in a moment,} Carzain thought. 
But it was easier said than done, for another goon had closed in on him. 
This one a \sphyle, mounted on a \relc. 
She wore chain mail and wielded a sword and shield. 
Her chest and shield was adorned with the white tiger's head that was the symbol of the \hs{Tiger} order. 
Only her shoulders showed the brown wolverine of Runger. 
Tiger warriors were Tigers first and members of a king's army second. 

He noticed her too late, and she had already manoeuvred in on his left side. 
\tho{Shit. I should have readied my shield.}
Carzain had a shield, but it was still strapped to the back of the saddle, leaving his left side vulnerable. 

She swung her sword. 
He twisted away, so instead of slashing through his left arm her blade only hit his metal shoulder guard. 
But she was strong, and the force of the blow sent numbing pain through his arm. 

\ta{\Keshirah!} he invoked, throwing a gust of wind in her face. 
She was yanked out of place and only narrowly held on to her saddle. 
Her \relc{} reacted to the change of weight and turned away from him. 

Free for a moment, Carzain turned to Gwelthein. 
Just in time to see her narrowly dashing away an enemy spear that would have gutted her otherwise. 
She pulled at her reins, and her war-trained \relc{} reared up and knocked down her foe, then trampled him underfoot. 

\tho{%
  Phew. 
  I was afraid we'd lose her in the time it took me to save my own hide.}

Then, under him, Arrow yelped in pain as a bullet thudded into his shoulder. 
The wounded \relc{} shook and bucked, and Carzain had to struggle just to stay in the saddle. 
\tho{%
  Shit. 
  What do I do now? 
  I haven't been taught how to handle a wounded \relc!
  Shit!}

\ta{\Shireyo!} he heard Curwen shout.
\ta{I need you over here!}

\ta{I'm trying!} he cried feebly.
\tho{%
  What do I do? 
  Can I use magic? 
  Can I heal it? 
  No, that won't do.
  I can't reach. 
  Besides, the shock of that might make him buck me off.
  
  I know! 
  I can use \Omariel, \Sephirah{} of Acceptance, to deaden the pain. 
  That might help.
  Hold still, big boy.}

\ta{\Omariel,} he invoked, projecting the \ps{\sephirah} soothing essence into Arrow's body and mind. 
At first Arrow bleated his distress, but soon \Omariel{} took hold of the \ps{\relc}{} simple mind, and his loud bleating softened to a croon. 
The \relc{} remained skittish and unruly, but at least Carzain had regained some modicum of control. 

And not a moment too soon. 
For the Tiger was back in the saddle, too, and renewed her attack. 
In the meantime, though, Arrow had turned around so that she came from his right side, enabling Carzain to defend himself with his sword. 

\tho{%
  All right. 
  A sword fight. 
  \emph{This} I have been doing since I was a kid.
  \emph{This} I know how to do!
  Let's hope I know how to do it from \relc-back, too...}

The fight was too close and too hectic for him to use magic, but he fought with all the swordsmanship that Sir Guy and his officers had taught him. 
Their blades clashed. 
The Rungeran lashed out. 
Carzain parried and forced her sword away. 

But she had her left side turned towards him, and where he had only his sword, she also had her shield. 
Which she now used to bash Carzain in the face. 
He staggered in his saddle and only barely managed to fend off her next stabbing blow. 

He was weakening. 
He knew that. 
With his \quo{no fire} rule Curwen had robbed Carzain of his favourite and most potent weapon.
He was unaccustomed to using \Keshirah{} in combat, and he had expended much more energy doing so than he would have liked. 
The shield bash had not helped, either, nor did the skittish \relc{} underneath him. 

They traded a few more blows. 
Then the Tiger paused for breath. 
\tho{An opening!}
Carzain seized the opportunity and immediately stuck. 

And fell right into her feint. 
She easily fended off his overconfident strike and swatted away his arm. 
His elbow and shoulder ached under the force of her blow. 

\tho{Fuck! I thought I knew what I was doing...}

He was now wide open and could not bring his sword back to parry in time.
The Rungeran struck. 
Carzain tried to dodge by backing away. 
This did not work out so well, since he was strapped in a saddle. 
He took a cut in his right side and was now hanging in an awkward position, halfway dangling from Arrow's side. 

\tho{Shit. I'm done for. Shit. Shit.}

The Rungeran raised her sword for a killing blow. 

And then her head exploded. 
Blood fountained from a dozen places on her face and neck. 
Scales tore free. 
An eye popped out of its socket. 
She slumped lifeless over the back of her \relc, her brains oozing out.  

\ta{Pull yourself the fuck together, \Shireyo!} he heard Curwen say as the captain reined in next to him. 
The residue of a gruesome \qliphah{} still emanated from Curwen in waves. 

% Carzain has taken wounds and is weakening. 
% He feels slightly dizzy from that shield bash to his head, and the bleeding cut in his side isn't helping, either. 

\tho{%
  Pull myself together.}
That was easier said than done. 
Carzain was feeling weak and dizzy. 
Blood loss, exhaustion and bruises were all taking their toll. 
\tho{%
  \Qliphoth. 
  Here I stand. 
  Me. 
  The great Vaimon. 
  Who only recently called himself \quo{the new \hs{Cordos Vaimon}}. 
  And I can't even hold my own against one lowly Rungeran grunt. 
  I can't even manage a \relc. 
  And least of all save my comrades-in-arms when they need it.
  
  I am losing. 
  I am being defeated. 
  This is not right.
  This should not be happening. 
  I am better than this.
  
  I am not nothing.}

And at the edges of his consciousness, Carzain felt a door open in his mind. 
Dimly he felt himself drifting into obscure darkness. 

He crossed the bridge. 









\begin{comment}
\subsection{\Takestsha{} watches fight}
\end{comment}
\new
% \begin{comment}
\Takestsha{} watched with great interest as the events of the combat were relayed to her by her \hs{Psychic Eye}. 

\tho{%
  Here are our two Vaimons. 
  The older and bearded one is clearly the greater threat. 
  For the moment.}
She chuckled slightly.
\tho{%
  The younger one is only barely keeping up. 
  But even so, he is the interesting one. 
  He is the source of the \vertex{} spike.}

\Takestsha{} had no intention to take part in the fighting. 
She was content to watch from a safe distance. 
For the moment she did not expect to kill or capture the \vertex. 
She merely hoped to see it in action. 

She did not yet know enough to be able to act decisively, and she did not want to give herself away prematurely. 
For this reason she postponed sending out the Psychic Eye until \emph{after} the two Vaimons had begun to fight back. 
If she were to send the Eyes immediately it would have aroused suspicion, but now that the Pelidorian mages have revealed themselves it is no surprise that the Rungeran \ishrah{} would use magic to scout on them. 

The Eye not only saw, but also heard, and she had managed to catch some names. 
\tho{%
  Curwen. \Shireyo. 
  
  Hm. 
  \quo{Curwen} I have heard before. 
  He is a ranking member of the Pelidorian \ishrah. 
  \quo{\Shireyo} is new to me. 
  So that is our little \ps{\vertex} name? 
  Interesting.}

She read his mental signature and committed it to memory, ensuring that she could track him down later. 
\tho{Would not want to lose him entirely in case he gets away today.}

Then she was struck blind. 

For a moment the Psychic Eye blacked out as waves of energy swept over it. 
The cosmic threads quaked. 
The fabric heaved. 

\tho{Now what is this?}









\begin{comment}
\subsection{Vizicar awakens}
\end{comment}
\new
Fighting. 
Swords. 
Soldiers. 
\Relcs. 
\Sephiroth. 
\Qliphoth. 
Blood. 
Death. 
Killing. 

\VizicarDurasRespina{} did not understand where he was, nor could he remember how he got here. 
But he had found himself in a forest, surrounded by foes. 
Fighting for his life. 

These enemies were nothing. 
Somehow he knew this. 
They were mere grunts. 
Not monsters. 
Not mages. 
Not even knights. 
Just commoners. 
Nothing next to him. 
Him, the Emperor. 

And yet somehow he was losing. 

Vizicar did not know how. 
It was all hazy. 
He could not remember from one moment to the next. 
It was as if we has moving through wild water. 
All was opaque, and he was cast about by forces beyond his control. 

A part of him told him that it was all just a dream. 
That he should just doze off and ignore it. 
Another part of him told him that it was all real, that his life was in danger. 

A thought appeared to him. 

\hypota{%
  I am losing. 
  I am being defeated. 
  This is not right.
  This should not be happening. 
  I am better than this.
  
  I am not nothing.}

He did not know where the thought came from. 
Was it his own? 
Was it someone else's? 
Whatever the source, the thought came with strong and vivid emotion. 
It stirred up his pride. 
It awakened his indignation. 

% By now Carzain is wounded and tires. 
% His mind's grip on the body is weakening. 
% This makes it easier for Vizicar to step in and fill that hole. 

\tho{%
  I will not suffer this indignation. 
  I am \VizicarDurasRespina, and I will not be defeated.}

He heard a gun fire. 
Out of the corner of his eye he saw a bullet heading straight for him. 
% The \sathariah{} in him dozes, but only lightly, since it has recently stirred. 
He was still dizzy, but the immediate danger caused an instict of self-preservation to flare up. 
Filling him with an urge to \emph{act}. 
As quick as thought and with expert ease he invoked \ta{\hr{Atzirah}{\Atzirah}}, swatting away the bullet with the \ps{\sephirah} power. 

Suddenly he was awake. 
Suddenly everything became clear. 
Suddenly he was ready. 

He found himself in a forest at dusk, seated on a \relc. 
Embroiled in a fight. 
Instinctively he knew who his enemies and friends are. 
The men arrayed against him were dressed in brown and tan colours; his allies wore yellow and blue and gray. 

He righted himself in the saddle. 
\tho{Hold still and obey me,} his knees and feet told the \relc. 
Immediately it obeyed. 

Next to him rode a large man with gray hair and beard. 
An ally. 
Vizicar spurred his \relc{} on and pushed past the man. 
Approaching the line of foes. 

The brown-clad enemies had been closing in for the kill, but now, seeing his advance, they hesitated. 
They cast fearful glances to each other. 
Some began to back away. 
They reacted to the change in his body language, Vizicar trained eye could tell. 
Their quarry, who had been cringing just moments before, now burned with confidence and menace, and it filled them with fear. 

\tho{%
  You did not know with whom you were dealing, did you?
  Poor fools. 
  Let me tell you:
  I am the Vaimon Emperor!}

He heard the fat, bearded man bark something from behind him. 
Vizicar did not hang onto the words, but the tone was clearly that of a reprimand. 
Vizicar glanced over his shoulder and gave the old man a sharp glare. 
The man's eyes widened in shock and he fell silent. 

\tho{Insolence. Who does he think he is?}

More bullets flew towards him. 
Many of them were deflected by the \Hoshied-ward around him.
\tho{%
  I do not remember casting this ward. 
  But I did a shoddy job.
  Too many shots are getting through it.}
But the wisdom and clarity of the \sephiroth{} were in his eyes and ears. 
Little could surprise him in this state. 
Those bullets that pierced the ward he waved away with \Atzirah{} and a flourishing gesture. 

The fury of the \qliphoth{} was in his blood as he rode into the fray, and he showed no mercy. 
He called upon \Izion{} and \hr{Razilah}{\Razilah} and other fierce \Archons{} and let his foes go under in a storm of fire and thunder and lightning. 

He could have gone with a subtler, more artful approach, he reflected. 
But no. 
They had fired his blood, awakened his wrath. 
No, only a blatant display of his power would be enough. 

\tho{%
  This rabble has dared to stand against their rightful Emperor in combat. 
  This will not do. 
  An example must be made. 
  The world must see that I am involate, and that to defy me is to call the wrath of all \Iquin{} and \Itzach{} down upon yourself.}

And so he let loose the righteous fury of his \sephiroth. 
He burned and slew and destroyed until the forest was a blinding inferno around him. 

\tho{%
  A crown of fire.
  As befitting a conqueror.}
He laughed, celebrating his victory. 

\tho{%
  Now perhaps they will learn. 
  The Emperor is inviolate. 
  None may challenge me and live.}

Triumph brought a certain peace of mind. 
And peace brought drowsiness. 
He felt himself lose consciousness and fade away into a dreamy sleep. 

Dimly he felt his body slacken. 







\begin{comment}
\subsection{Curwen pulls everyone out}
\end{comment}
% \begin{comment}
\new
\tho{What the fuck is the kid thinking?} thought Curwen. 

He could feel the heat on his face. 
Flames surrounded them on all sides. 
\ps{\Shireyo}{} rampage had wiped out the Rungerans, all right, but it had also set off a huge forest fire. 
He had not been able to keep up with all the \Archons{} \Shireyo{} had invoked, but somehow the fire was driven by a pack of voracious \qliphoth, and their hunger caused the flames to spread faster than any natural fire would. 

\tho{%
  Never mind that. Kick the boy's ass later. Got to save our ditto.}
\ta{Pelidorians! Retreat!} he called out to rally his men. 
He quickly scanned the area. 
\tho{%
  Which way is least dangerous? 
  I can't tell in this glare, but I'll guess and say... this one.}
He wheeled his\dash now highly skittish\dash \relc{} around and spurred it towards what might be an opening. 
\ta{This way! Follow me!}

Looking back, Curwen saw \Shireyo{} slumping in his saddle. 
Dizzy, or worse, unconscious. 
He yelled at him: 
\ta{%
  \Shireyo, move your ass! 
  We're getting the fuck out of here!
  Get in line!}

% Carzain falls unconscious. 
% His body is in a bad shape. 
% Vizicar is a rough master. 
% He is not fully present in his body and doesn't fully feel its pain. 
% So he can't think clearly and gets careless. 
% Carzain's body gets hurt and burnt and falls unconscious without registering what happens. 
% He passes out. 
% But he is still seated on his \relc. 
\Shireyo{} swayed slightly, but gave no indication of having heard the order. 

\tho{%
  Fuck.
  The kid's lost it. 
  \Qliphoth, I'm tempted to just leave him to die in his own mess. 
  But I can't do that. 
  I have a war to win, and my \ishrah{} needs all the guys I can muster.
  I can't lose him.
  
  But I'm not going in there. 
  Who's closest to him?}
Curwen looked around and found the \meccaran{} hanging back near \Shireyo. 
\Tsekkect{}. 
\ta{%
  You! 
  \Meccaran! 
  \Shireyo's down. 
  Grab his \relc{} and pull him out of there!}

\ta{Say what?} said the \meccaran. 
\ta{But the fire...}

\ta{\shout{Do it}!}

\Tsekkect{} hesitated. 
Then she pulled the reins on her \relc{} and forced it into the inferno. 
Both she and the \relc{} gasped in pain as the flames seared their skin. 
But she managed to grab the reins of \ps{\Shireyo}{} \relc. 
The beast reared up and shook. 
The \meccaran, who was small and light, was almost yanked from her saddle, but she held on with all her strength and kept her grip on both \relcs. 
She struggled with both of them, but finally managed to get them to run in the right direction. 

\tho{%
  Good. 
  Now we run like \Itzach{} itself is on our heels. 
  Because it is.}

And the battered remains of Curwen's squad fled from the witch-fire as fast as as their haggard steeds could carry them. 







\begin{comment}
\subsection{\Takestsha{} ponders \vertex}
\end{comment}
\new
\Takestsha{} pondered what she had learned. 
The \vertex{} had flared down again and was now running away. 

\tho{
  Should I pursue? 
  No. 
  Better not. 
  After all, who would be crazy enough to follow them through that inferno? 
  
  Besides, the \vertex{} was formidable. 
  Who knows what it might do if I harry it further?
  No, I will let them run.
  
  Now... with whom are we dealing, I wonder?
  
  The \vertex{} wielded Vaimon magic, plainly. 
  And massive amounts of it. 
  That suggests a \resphan{} origin. 
  And I recognize the pattern of that flare. 
  
  Yes. 
  We have to do with a Scion. 
  That is the most plausible explanation. 
  
  But which one?
  
  Too early to tell.} 

The battle had given her a good, long sniff at the \humans. 
They were dressed in Pelidorian army uniforms. 
Curwen she knew as a Pelidorian \ishrah{} member, and this \Shireyo{} is  evidently also one. 
It stood to reason that they would be heading west to join the main army. 
So they might meet on the battlefield again. 
\Takestsha{} looked forward to that. 

Morgan Runger had approached her from behind and was few steps away now. 
She had smelled and heard him approach from a mile off, of course. 
\ta{They were Pelidorian scouts,} she told him, not turning. 
\ta{We have chased them off. I say we let them run.}

\ta{Mhm. Someone will deal with it,} said the king. 
Untroubled. 
Morgan had seen the fire, as had everyone, but evidently it did not scare him. 
He was confident that his bolstered \ishrah{} could counter any sorcerous attack. 
Just as she wanted him to be. 

He came up close behind and wrapped his arms around her. 
Began to grope her body. 
\tho{%
  Heh. Delegating responsibility so you can have your pleasure? How very kingly.}
Morgan had grown quite shameless about their affair, despite the fact that, as a nominal \Iquinian, he was theoretically obliged to be faithful to his wife. 
But he was a king and could do whatever he wanted. 
Do \emph{whomever} he wanted. 
\tho{%
  And, as any man might, he wants to remind everyone how beautiful a woman he is fucking.}

% She doesn't mind, of course. 
% As a \dragon{} she has no sexual shame. 
\Takestsha{} reflected that perhaps she ought to fake some shame and modesty to make her guise as a \human{} woman more believable. 
But then again, she was playing the role of the mysterious and erotic sorceress, and part of her allure was her rejection of conventional morals. 

\tho{%
  Oh, yes. 
  I suppose I had better have sex with Morgan. 
  Have to keep my pet king compliant. 
  
  Tee-hee.
  The discovery of the Scion has made me in a good mood. 
  Who knows? 
  I might even enjoy it tonight.}
% \end{comment}







\begin{comment}
\subsection{Carzain awakens}
\end{comment}
\new
The first thing Carzain knew when he awakened was that his entire body ached. 
There was pain in his stomach, his right flank, his left shoulder, his hands and legs. 

He lay on a carpet in the forest. 
% He tried to turn his head, but sudden cramps in his neck made him think better of it. 
Looking around he could see several of his companions around him. 
They did not look too good. 

He tried to sit up. 
Much to the protest of his battered body, he managed to push himself upright. 
\Tsekkect{} and Delph came over to him. 

\ta{Carzain! You're awake!} said Delph. 
\ta{Ooo... careful.}

Looking down at himself, he noticed several burn marks on his clothes and a few minor burns on his skin. 
\ta{Ow... what happened?}
He looked at his friends. 
Delph seemed mostly unhurt, but \Tsekkect{} had ugly burns, much worse than his own. 
\ta{\Tsekkect! You're burnt all over! What happened to you?}

\ta{Yeah, you fucking owe me for this,} she says. 
She glared at him for an extended moment. 
Then made a rasping noise and blinked. 
\ta{%
  Crrah, but don't shit yourself. 
  It's nothing I can't regrow. 
  You can return the favour later.} 

\ta{%
  And you, Delph,} said Carzain.
\ta{%
  You're limping!}

\ta{%
  No, I'm not,} said Delph. 
He averted his eyes, ostensibly to spit out a piece of tobacco. 
\ta{It's nothing. I'm fine.} 

\tho{%
  Sure you are, Delph. 
  Heh. 
  Yeah. 
  Masculine pride. 
  We all have it.
  I would be keeping up the same \facade{} myself if I could. 
  But I'm afraid I blew it by passing out.}

\ta{%
  How about you?} \Tsekkect{} asked him. 
\ta{%
  I thought for a moment you were a goner.}

He remembered the battle now. 
The Rungerans that had jumped out from the trees. 
The gunshots. 
The spearmen. 
The Tiger. 

And then... what had happened then? 

\tho{%
  Then that thing happened. 
  I heard voices in my head\dash or I was talking to myself\dash and I lost control of myself. 
  Just like back in Heropond. 
  My body fought. 
  Unleashed \qliphoth{} and \sephiroth{}.
  Killed. 
  Killed all the Rungerans with fire and lightning.
  
  Fire! 
  Curwen had said no fire! 
  Is that why \Tsekkect{} is burned?}
He glanced at the other people gathered.
\tho{Is that why everyone is burned?}

He gestured at \ps{\Tsekkect}{} wounds. 
\ta{Did... did I cause this?} 

\ta{Well, it was you who torched the place, so, um... yes.}

\ta{And then you went down,} said Delph. 
\ta{What happened?} 

\ta{I...} 
He did not want to tell them how he was possessed and lost all control. 
He did not want to tell them that he had no idea what he was doing. 
\ta{I guess I passed out from the strain of my magic. And my wounds.}
\tho{%
  Come to think of it, wasn't I more badly hurt than this? I remember being stabbed in the side by that Tiger.}
He felt his side where the wound was. 
His clothes were all soaked in dried blood, and the area was very sore, but there was no bleeding, and his flesh felt whole. 
\tho{Did someone heal me?}

\ta{You sure did,} Delph was chattering. 
\ta{%
  And then in came \Tsekkect!
  \Qliphoth, Carzain, you should have seen her!}
Delph waved his arms around and nearly spat out his chewing tobacco.
\ta{%
  She jumped straight into the fire and pulled you out!
  She saved your skin, man.}

Carzain looked her in the eye. 
\ta{Really?}

\ta{As I said, you fucking owe me.}
Then she looked away and forced a laugh. 
\ta{%
  But hey, it's not like I did it for your big red cheeks' sake.
  Curwen practically tossed me in there.}

\tho{%
  \quo{Big red cheeks}? 
  What does that mean? 
  Huh. 
  Probably a \meccaran{} thing.}

A shadow fell over him. 
He looked up to see Archibald Curwen loom over him, smoking pipe in his hand. 
\ta{%
  So you're up, huh?} said Curwen.
\ta{%
  Can you stand?}

\ta{I don't know. Let's see,} said Carzain, trying to sound unaffected. 
He climbed halfway to his feet.

As soon as he could reach, Curwen grabbed Carzain's collar and pulled him the rest of the way up, then yelled into his face: 
\ta{%
  You crazy fuck, \Shireyo!} 
His mouth, now mere inches from Carzain's nose, reeked of that stuff he smoked. 
\ta{%
  What in \Itzach{} did you think you were doing?
  You nearly got all of us killed!}
All the shouting evidently disagreed with Curwen's throat, making him cough out loud, right into Carzain's face. 
\ta{%
  Didn't I fucking tell you? 
  No\dash fire!
  Forest\dash might\dash catch!}
He spoke these words very slowly, as if talking to a dimwit. 
\ta{%
  Which of the words didn't you understand?
  Let me tell you something, boy. 
  Your insubordination stopped being charming a \emph{long} time ago.
  Now either you get in line or I'll have your ass beaten!
  Got that?}

Carzain squirmed, trying to break Curwen's grip. 
But the captain was stronger, and Carzain was still groggy and weak. 
\ta{Yeah. Yeah, sure.}

\tho{%
  But I didn't do it. 
  I wasn't myself. 
  It wasn't my fault. 
  No, I'm not telling him that.
  I've lost enough face for today.
  I'm not going to plead my innocence and confess my madness to him.}

Curwen gave him another angry look, then let him drop. 
Carzain almost collapsed. 
Muscles and skin were aching all over his body. 

\ta{%
  You'll want to be careful with those wounds. I'm not sure how clean they are,} Curwen warned, no compassion in his voice. 
\ta{I did some healing, but I was in a foul mood at the time.}

Carzain collected himself, forced himself to stand up straight. 
\tho{%
  I'm not going to accept blame from him. 
  Fuck him.}
Thinking about it this way made it all easier. 
Earlier he had felt guilty about causing \Tsekkect{} and the others to get hurt, but Curwen's reprimand got his hackles up. 
Pride won over guilt. 
\tho{
  I don't owe Curwen any explanation.
  I don't have to answer to anyone. 
  Besides, it didn't feel wrong at the time. 
  It felt right. 
  Not just right... \emph{righteous}. 
  That can't be all wrong. 
  Yes, that's right.}
Anger and pride made the conclusion much simpler.  
\tho{
  I didn't do anything wrong. 
  I saved us.
  
  Or did I?}
  
He looked around. 
He noticed that everyone had wounds from the fight and the fire. 
And \quo{everyone} was not many. 
Several were missing. 
In fact, apart from himself, Curwen, \Tsekkect{} and Delph, there were only two more people. 
There was Gwelthein and one more soldier\dash a \sphyle, Egian. 
Gwelthein was going around tending the \pps{\relcs} wounds using herbs, bandages and soothing words and strokes. 
The beasts were roughed up just as badly as their riders were. 

\tho{Six people gone.}

He turned to Delph and \Tsekkect{}. 
\ta{The remaining six...?}

\ta{Dead,} said Delph. 

They told him what they knew of the fight. 
Supposedly, two were shot dead before the combat even begun. 
Two more were definitely killed in the fight, and two more were down and wounded when the fire began. 

He suspected the question was written on his face clearly enough: 
\tho{Did I kill them?} 

\ta{%
  No, no, no,} said Delph quickly. 
\ta{%
  They were goners. 
  They were down and stuffed full of bullets and cuts and shit.}

\ta{%
  Right.}
\tho{%
  Oh, thank the \sephiroth. 
  For a second I was afraid my madness killed them.}

\tho{%
  I was right.}
He looked at Curwen's back and his pride returned. 
\tho{%
  I didn't harm us. 
  I saved us.
  For all I know we would all have been killed if not for me. 
  I saved us all. 
  Some burns are well worth that.} 
\ta{%
  Sorry about those burns, \Tsekkect. 
  I'll see what I can do to heal them.
  As soon as I'm fresh enough to not mess it up.}

\ta{All right, girls,} said Curwen, 
\ta{%
%   Get up 
%   Now that we're all up we'd better get moving. 
  We have to get back to the army fast.
  So get on your feet and get moving!}

Gwelthein, the only surviving \ranger, came over. 
\ta{As for that healing,} she told Carzain,
\ta{%
  you should use your energy to patch up the \relcs{} first.
  I've done what I could with some herbs, but some of them are still not in the best of conditions. 
  We need to get moving, and fast. 
  It's dangerous to stay here. 
  We're weakened, and if even we've shaken off the Rungerans, there are \nycans{} out here.}

\ta{There are \shout{what}?} cried Delph.
\ta{\Nycans?}
He turned an accusing glare on Curwen. 
\ta{You never told us of no fucking \nycans!}

\ta{Then what are you hesitating for?} asked Curwen. 
\ta{Move!}

Carzain took Gwelthein's advice and did what he could to heal Arrow, who had taken more than a few wounds from the fight and the fire. 
\tho{Sorry about this, mate.}

As soon as everyone was able, they were on the march again, back towards \Forklin. 
Carzain, now weakened further from the healing, could do no more than cling to his saddle as he was jostled along. 
He thought back to the battle and his possession. 

\tho{
  Come to think of it, it didn't feel scary or unnatural at the time.
  It felt... what is the word I'm looking for?
  Exhilarating.
  Liberating.
  Righteous.
  True.}

First there had been the regular fight. 
Hectic. 
Painful. 
Fast. 
So damned fast. 
Enemies coming from all sides. 
Swords and bullets flying. 
Curwen barking orders. 
The \qliphoth{} and \sephiroth{} tugging at his mind. 

And then he had snapped. 
It was as if he had fallen off the saddle and seen his body ride on. 

One moment there was pain and stress, anger and fear. 
The next moment there was... peace. 
Truth. 
Focus. 
Confidence. 
Power. 

Wrath. 
But the wrath of the righteous. 
An avenging angel. 

It felt like an awakening. 
As if he had suddenly awakened to his true self and found that his true self was a dark, avenging angel. 
As if he was suddenly for the first time able to truly spread his wings and soar. 
For a brief moment he was able to unfold his true being. 
As if this was the purpose of his life. 
As if this was the true him. 

A twilight angel. 
An avenging angel. 

\tho{%
  And there was that name. 
  \VizicarDurasRespina. 
  I've heard it before. 
  What does it mean? 
  Is it a \qliphah{}? 
  No... it called itself \quo{Vaimon Emperor}. 
  Why? 
  Who is this Vizicar? 
  I must find out.%
}

There was some deep meaning to this, he felt. 
It had been as if he had suddenly remembered who he really was. 
But only for a moment. 
Then it was gone. 
Now he felt somehow... empty. 
He knew there was more to him; he had seen a glimpse of that \quo{more}. 
But now it was gone again, slipping from his grasp like a fleeting dream. 
Slippery like an eel. 
But real. 
Real. 

\tho{
  I'm not mad. 
  Something is happening to me, but it's not just my imagination. 
  It's real. 
  It's real. 

  What was it? 
  What was I, back then?
  What am I?
  Why am I like this?
  
  Now it is gone. 
  But for a moment, I knew. 
  For a short moment, I remembered. 
  The twilight angel in me... remembered.}







\begin{comment}
\subsection{\Tsekkect{} contemplates}
\end{comment}
\new
\ps{\Tsekkect}{} wounds pained her as they rode. 
Her own \relc{}, having fought on the frontline, had taken too many wounds, and they had had to kill it. 
She was now riding double with Delph, whose mount was still mostly healthy. 
Clinging to the back of a saddle was not exactly helping her condition. 

\tho{%
  Dumb \humans. 
  They think just because I can grow it back I don't feel any pain. 
  Dumb \humans. 
  You owe me, 'Zain. 
  You said you'd heal me. 
  So get your act together and do it.}

\Tsekkect{} thought back to the battle and Carzain's magic. 
It was damned frightening. 

\tho{%
  \hs{Bled} and \hs{Thudun} know I didn't want to go in there and pull him out. 
  Curwen bullied me in there. 
  I was scared half to death, the way he was blasting left and right with his crazy magic. 
  I wasn't made to go through fire like that. 
  As much as I hate to conform to the stereotypes of how a \meccaran{} acts, I do kind of wish I was in a nice wet swamp right now instead of here. 
   
  'Zain is a friend, sure, but not one I'd go to my death for.}

She had been spending a lot of time with Carzain recently, so she told herself she knew him well. 
But she had never seen him fight before. 
She had used to think of him as a likable guy, if somewhat prejudiced and self-important. 
\tho{
  But he is also a man who can make his enemies burn to ashes from the inside with a mere word. 
  He's a fucking scary man. 

  And what's worse is the apparent callousness. 
  The way he condemns his enemies to a horrible death by burning or something equally nasty, without even thinking twice about it. 
  
  Delph was right. 
  Carzain is crazy in the head. 
  
  He's not evil. 
  He did offer to heal me. 
  He does help his friends. 
  But damn. 
  I wouldn't like to be his enemy. 
  That would be scary. 

  I've killed people myself, of course. 
  So has Delph. 
  And many of my friends. 
  But that's different. 
  Those are clean deaths, with swords and knives and blowdarts. 
  And bleeding wounds. 
  And infections. 
  And screaming, and crying, and begging for mercy. 
  But that's not the point!} 

Seeing Carzain wreak destruction like that had shattered an illusion of hers. 
She could not quite think of him in the same relaxed manner anymore. 
She had never been friends with a mage before, so she has always seen them as creepy and scary people. 
Now she remembered why. 

\tho{%
  Sorcery is fucked up, damn it!
  And what if she snaps and goes crazy again? 
  What happens then?
  
  Maybe I should try and make some saner friends...}







\begin{comment}
\subsection{Curwen ponders \vertex}
\end{comment}
\new
\tho{What the fuck is going on with that boy?} Curwen asked himself as he rode. 

Part of him wanted to dismiss \Shireyo{} as just a brash and stupid kid who played with forces he did not understand and could not control. 
A dumb brat who just wanted to play with the big boys. 
A child who needed to get in line and learn to act like an adult. 
It would hardly be a first.

\tho{
  But that's not the whole truth. 
  There is more to it.}

There was that time when \Shireyo{} suddenly rode forward to meet the enemy. 
Curwen had shouted for him to get in line. 
And the kid had sent him that look. 
That look in his eyes! 
Such force. 
Such command. 
That was not the \Shireyo{} he knew.
\tho{
  Now, granted, \Shireyo{} is a cocky young man. 
  Full of macho pride. 
  And he has a problem with taking orders. 
  But I've many guys like that before. 
  Those weren't just the eyes of a cocky and macho young man who didn't want to take orders. 
  They were the eyes of one used to command fear and obedience. 
  They were the eyes of someone... greater.}

% He looked freakish. 
% His long black hair had almost stood on end, as if electrocuted. 
% Curwen has seen people zapped with lightning magic, and their hair sometimes does that. 
% But this is not quite the same. 
% It didn't just stand erect. 
% It waved about. 
\ps{\Shireyo} whole body language also changed. 
He sat up straighter in the saddle, as if he had suddenly learned how to \emph{really} fight from \relc-back. 
Curwen knew the kid had taken wounds in the fight, but at that moment he seemed to completely disregard them. 
He had held himself high like some conquering hero or Vaimon lord.
\tho{Which is probably what he fancies himself to be.}

The \quo{ignoring his wounds} strategy had not worked out well in the end; when they pulled \Shireyo{} out of the fire he had been badly roughed up. 
\tho{%
  But that can't have been pure overconfidence. 
  \Shireyo{} is not that stupid. 
  No, it was as if he genuinely didn't feel the damage. 
  As if he were in some kind of trance. 
  Detached from reality.
  Detached from his own body.}

% And to hammer the point home, there was the feeling. 
But those things were details. 
More importantly, there was the \emph{feeling}. 
The cosmic threads had been shaking wildly, and there was a surge of power from the Beyond. 
Curwen had been fighting for his own life, too, so he had not been able to give the phenomenon his full attention. 
\tho{%
  But I know a \vertex{} spike when it whacks me over the head with a mace.
  
  \Shireyo{} is hiding something. 
  I know it.}

\tho{%
  But how much does \Shireyo{} know?} 
Curwen, having worked as an interrogator, liked to tell himself he knew how to spot a liar. 
When he had looked into the boy's eyes before, it did not look like he knew the whole story and was hiding it. 

\tho{%
  Maybe the boy himself doesn't understand what's going on. 

  Hm. 
  How to proceed from here?
  
  I can't very well go up to him and go: 
  \subta{So, kid, is there anything you'd like to tell me?}
  If he understands it himself then he's going to keep tight. 
  And if he doesn't understand what's going on with him, then he's not going to come to me with his worries. 
  He's not the kind of man who talks openly about his own flaws and problems.
  That much is obvious.} 
Curwen chuckled ruefully.
\tho{%
  And I'm not the kind of man to whom people talk openly about their flaws and problems, either. 
  Not voluntarily, anyway. 
  
  I'll have to keep him around and just keep digging. 

  I'll threaten to throw the kid out of my \ishrah. 
  Yeah, that's what I'll do. 
  Maybe that'll get him to behave. 
  
  Throw him out of my \ishrah. 
  Yeah, right. 
  Like I'd do that.
  Let him think that. 
  But there's no way in \Itzach{} I am letting him out of my sight. 
  Not until I have figured him out.}
% \end{comment}










