\bookchapter{\Vertex{} Awakening}

\begin{comment}
\section{The Mutiny}
\end{comment}

\begin{comment}
\subsection{I don't trust them}
\end{comment}

\stamp
  {\dateMutiny}
  {\hs{Heropond Forest}, east of \hr{Bryndwin}{\Bryndwin}, \hr{Scyrum}{\Scyrum}}
%\dateplace{Carz}{11th}{\Yeziel}{Heropond Forest, east of Bryndwin, \Scyrum}
%\datetime{Carz}{11th}{\Yeziel}{Early afternoon}
%
\talk{Father,} said \hr{Carzain Shireyo}{Carzain}. 
\talk{I don't trust them.} 

\talk{What do you mean, son?} asked \hr{Nishain Shireyo}{Nishain}.

\talk{The mercenaries. They are up to something.}

\talk{Do you think they will betray us?} Nishain glanced at the mercenary captain. 
\talk{%
  No, I cannot think that. I have dealt with Captain Arturo before. He is an honourable man.} 

\talk{The captain may be,} said Carzain, 
\ta{%
  but has less savoury characters among his men. The one with the nose\dash{}do not look!} 
he hissed as his father started to turn his head. 
\ta{%
  That one\dash{}Fisher, I think\dash{}he is the worst. He is always casting strange looks at us, at the captain and at the cargo.}

\talk{%
  Even so, I cannot believe that they will mutiny. Captain Arturo would not let that happen.}

\talk{They are thugs, scum.} said Carzain. 
\ta{But I hope you are right, Father.}  

Carzain was not reassured. 

He and his father had travelled to the great, splendid city of \hs{Martinum} to buy supplies, components needed to work their magic. 
Many of these were exotic things that could not be found in \hs{Pelidor} or its neighbouring kingdoms: Rare gems and crystals, body parts of fantastic animals, even alien and uneartly minerals. 
It was a journey of many days from \hr{Redglen}{\Redglen} to Martinum, 
and they travelled on a narrow path through the \hr{Wild}{\Wylde}\dash savage, untamed lands infested with beasts and bandits\dash so they had needed to hire guards. 
The soldiers they had brought along on their way out from home to Martinum had been of a relatively wholesome sort, by mercenary standards, but the band they had found for the return journey were, in Carzain's eyes, much less trustworthy. 
It seemed to him that the soldiers, especially the one called Fisher, kept casting glances at the cargo, glances full of base greed. 
The sellsword\dash unlearned and uncouth\dash did not know what most of the things were, of course, but much of it looked exotic, and even the unsophisticated knew that \quo{exotic} meant \quo{expensive}. 

%Carzain and Nishain sat in a small wooden cart pulled by a \belwan\dash a 
He kept shifting uncomfortably in his seat on the wooden cart. 
Before him waddled the \hr{Belwan}{\belwan} pulling the cart: 
A seven-foot-long brown-furred mammal, burly like a bear, but with larger forelegs and a long, wide snout. 

They were five days' travel out of Martinum and still ten days from \Redglen{}, so if the mercenaries did indeed plan to betray and rob them, they would be far from civilization when it happened. 
\tho{Heh,} he mused. 
\tho{If a man is killed and robbed in the \Wylde{}, does it make a sound?}

\tho{I doubt it.}

He eyed Fisher. 
A thin man with a long, narrow nose, medium-length, stringy black hair, a short stubble of black beard and a hunched posture. 
He wore brigandine armour and carried 
a falchion and a curved dagger in his belt. 
\tho{He looks the typical thug,} thought Carzain, 
\tho{%
  ready to cut his neighbour's throat and rob him at the first opportunity. Truly the scum of \Miith{}.} 
Carzain scowled at the man, then caught himself and suppressed it. 
\tho{If they notice my suspicion, they'll kill me first.} 

And so, through the entire day, Carzain went and eyed the soldiers suspiciously while doing his best to hide it. 

There were six of them, some worse than others. 
There was the captain, Arturo, a middle-aged man of perhaps forty, with rather well-kept graying hair and a short gray beard. 
He wore chain mail and carried a long sword and a round, wooden shield. 
He walked straight and commanded his men with quite admirable dignity and authority. 
\tho{%
  Yes, Father is probably right. 
  Arturo is a good man. 
  Quite the opposite of Fisher.} 
Again he had to fight the urge to scowl at the ugly man. 
\tho{%
  You can tell their character by the looks in their eyes and the way they walk.} 
Carzain was confident of his ability to read people and not inclined to doubt his own conclusions. 

There was Roger, a balding man with a goatee wearing studded leather and carrying a wicked-looking spiked mace. 
\tho{His mouth has a vicious sneer to it. He is one of the bad ones.} 

And there was the boy, Gasper. 
He was the youngest of the bunch, younger than Carzain by at least a few years. 
He had cut his brown hair short, and judging by the looks of his cheeks, he was working very hard to grow a beard and look rugged. 
\tho{%
  An insecure kid eager to play with the big boys, eager to earn their respect and be a big, tough man. 
  Classic gang lackey.
  Just like some of the worms I know back home.} 

He surveyed the caravan. 
To his right he saw old Harold. He was the oldest of the guards, of Nishain's age at least, half-bald and with a long, gray beard. He wore studded leather and wielded a mace. He looked up at Carzain and smiled. \tho{%
  Harold is perhaps the only one of them who smiles. He is an honest man.} 

He looked around again. 
To this left he found the last one, Hopper. 
\tho{I don't know about her. I can't read her, she is a \hr{Meccaran}{\meccaran}.} 
Hopper was the only non-\hr{Human}{\human} of the band and the only female. She wore no armour but carried two javelins and several daggers. He studied her characteristic hopping gait. 
\tho{Hopper is probably not even her true name. I suppose she has some \hs{Clictua} name or whatnot, something the soldiers can't pronounce.} 
He could not divine her moral character, but he suspected the worst. 

%There were nine mercenaries in all, and Carzain did not know the names of the last three, nor their moral character\dash{}but he suspected the worst. 



\begin{comment}
\subsection{Evening}
\end{comment}

\new
Even so, the day passed without incident. 
\tho{Of course,} thought Carzain. 
\tho{They want to get us further into the wilderness before they strike.} 
Having left the \hr{Pylandos Road}{\Pylandos{} Road} to head west into Pelidor, they had to cross the \Wylde{} of eastern \Scyrum{}, into the great \hs{Heropond Forest}. 
The paths had been quite civilized in the beginning, still close to the \Pylandos{} Road and the villages near it, 
%but villages had gotten more rudimentary and ill-kept by the hour, and by now, almost halfway through the forest, it was almost pure wilderness. 
but after they left the last town, \hr{Bryndwin}{\Bryndwin}, behind them, the landscape degenerated into wilderness. 

They stuck to \hs{Leglan's Pass}, the only half-civilized path through this part of Heropond. It had been a thriving, well-traveled road back in the days of \hr{Great Velcad}{\theBelkadianEmpire}, or so he had heard, but in the decades following the fall of the \hs{High King} and the splintering of the empire into warring kingdoms and baronies, the Pass had fallen into disuse, and the \Wylde{} was fast reclaiming it, thus severing this bridge between \Scyrum{} and Pelidor. 

Heropond was not meant to be crossed. It did not \emph{want} to be crossed. Stories abounded of monsters and evil spirits in the forest, and %while they were certainly exaggerated\dash{}such things always were\dash{}
Carzain did not doubt that there was truth in them. No one crossed Heropond. It looked \Wylde{}. It sounded \Wylde{}. It \emph{smelled} \Wylde{}. \Wylder{} than most. The forest was undoubtedly one of the main reasons why there was seldom war between Pelidor and \Scyrum{}: Most of the border between the kingdoms was nigh-impassable, so they had little border terrain they could possibly fight over. 

\tho{%
  But that is the way of the world, isn't it? \Miith{} is a world of islands. Small pockets of civilization adrift in a vast sea of \Wylde{}, connected by thin, fragile roads and passes. Like a spider's web. We go about our business in our little cities and towns, averting our eyes from the dark, savage lands beyond the town walls, and say to ourselves: 
  \hypota{This is the world.} 
  People are fools.}

\tho{Fools, barring exceptional individuals such as myself, of course.} 

\ta{Heh,} he muttered aloud. 
\tho{%
  All right, that must be enough philosophy for today. 
Fools or not, we're stuck in the middle of what is practically \Wylde{} territory.}

Merchants and other travellers took the much longer way north of Heropond, through \hr{Pylandos}{\Pylandos}, or the even longer way south by sea, but Nishain and Carzain had estimated that the time saved would be worth the trek through the forest, especially since the sellswords were expensive and charged by the day. 
Perhaps that had been poor judgement. 

He eyed Fisher with distaste. 
Having found himself unable to keep from studying the mercenaries, Carzain had taken to looking down his nose at them, using (only half-feigned) arrogance to mask his suspicion and scorn. Fisher noticed his gaze and scowled back at him. Carzain answered with an impetuous pout. Fisher snorted, then turned his back. 

\tho{%
  Yes, thug, that's right. I am just an upper middle class boy, a pampered scholar who thinks he is better than you. Blind to the world beyond my books. Nothing to worry about.} 
He hoped the soldier bought it. 

%Another day passed and still no incident. Every morning and evening, Carzain sat and studied their maps.

%Another day passed and still no incident. 

That evening, as the guards sat around the fire, playing dice and laughing raucously, Carzain pulled his father aside again. 
\ta{Father, I still think something up. Fisher is looking meaner by the minute. We cannot trust them.} 

\ta{%
  Carzain, you judge people too quickly. 
  Certainly, Fisher is an unkempt sort, but mercenaries \emph{are} a rough bunch. 
  They all are, but that does not make them marauders and mutineers.}

Carzain grimaced but said nothing but a low \talk{Hrumph}. 
\tho{Judge people too quickly? Bah.}

Nishain smiled and put a hand on his shoulder. 
\ta{%
  Don't worry, son. I am sure we will be fine. 
  Now, let us get some rest, don't you think?}

%At some point, Carzain's suspicions are proven correct as the mercenaries rebel, killing their own captain and attempting to kill Carzain and Nishain and rob them. Fortunately, Carzain, suspecting foul play, is only feigning sleep. He leaps up and challenges them, preparing to defend himself with magic. He realizes that he is being overconfident and will most likely be killed, but he enters combat anyway. 



\begin{comment}
\subsection{Dreaming}
\end{comment}

\new
\begin{dream}
Darkness. 

Darkness on all sides. 

He lies adrift, floating aimlessly in a cold void stretching off into infinity. 

Feebly he flails his arms and legs, trying to propel himself. 

\tho{Did it work? 
Am I moving?} 

He cannot tell. 
The empty space just continues forever with no landmarks. 
No matter where he tries to go, it is all the same. 
The vast emptiness is crushing him. 
He can do nothing to fight it. 

He is a speck of dust. 

He is nothing. 

He begins to discern shapes. 
Humongous gods and monsters float around him, each many thousands of times taller than he. 
Some look humanoid. 
Some look like \dragons{} or other fantastic creatures. 
Others are huge, amorphous blobs of slime, with tentacles dripping ichor. 
Yet others are so alien that he has no description for them. 

The enormous gods do not even notice him. 
He is deathly afraid. 
One of them might crush him like a fly and not even notice it. 
And he cannot even flee or hide. 

He is a speck of dust. 

He is nothing. 
\end{dream}




\begin{comment}
\subsection{Awakening}
\end{comment}

\new
Carzain's eyes popped open. 

\tho{%
  Whoa. 
  \hr{Qliphah}{\Qliphoth}. 
  That nightmare again.
  Being nothing.} 

He looked around. 

\tho{%
  I'm alive. 
  I'm in the real world. 
  I am not nothing.
  I am \CarzainDeracilleShireyo. 
  \hs{Vaimon} mage. 
  I am not nothing.}

%He was about to turn over when the shout came.
He turned over and fell into a new, restless sleep. 



\begin{comment}
\subsection{Attack}
\end{comment}
\new
\begin{comment}
\subsubsection{Carzain fights}
\end{comment}
\talk{What's this? No! Help! \emph{Gaaaaah!}} 

Carzain's eyes popped open even before the man's shout was cut short, in time to notice the mercenary bent over him\dash{}Roger, the one with the goatee. Swiftly he lashed out with the dagger he had concealed in his hand. His attack was clumsy, but he managed to give the thug a gash across his face. Roger yelled out in pain and suprise and staggered enough for Carzain to roll out of his grasp and climb to his feet. 

%\talk{The kid's up!} yelled a nearby thug, a fat, bald man wearing brigandine armour and wielding a wicked-looking spiked mace. \talk{Get him!} He ran toward Carzain, who had to think quickly. 

\talk{The kid's up!} yelled Roger. 
\talk{Get him!} 
He ran toward Carzain, who had to think quickly. 

\tho{Fuck,} thought Carzain. 
\tho{%
  I'm being attacked. 
  This is a real fight.}

Carzain had fought his fair share of brawls, but never before had be faced an actual fight to the death. 
But many were the books and stories he had studied about famous Vaimon warriors in the past and their glorious battles, and many were the imaginary battles he had fought in his head, not least these past few days. 

\tho{%
  All right. 
  I can do this. 
  This is what I've been training for all my life. 
  This is my chance to be what I have always dreamed of: 
  A warrior Vaimon.}

Brawls with his childhood had taught him some small measure of combat reflexes, and it was not unheard of for the young mage to cheat and use magic in a fistfight. 
Quickly he receded into Vaimon trance. 
Into the \hr{Empyrean}{\empyrean}. 
In his mind he floated through spiritual dimensions, feeling threads of mystic energy enmesh him, feeling the sinister presences of \qliphoth{} encircling him. 
Reaching out through the Cosmos with his aethereal senses, he touched the flow of power that was \hr{Iquin}{\iquin}. 
The \hs{Light} flowed into him, seeming to fill his body and soul, and he was consumed with a feeling of elation. 
Like so often before when he had been channelling the \hr{Sephirah}{\Sephiroth}, he found himself wondering how he had survived these many hours without touching the Light. 
Part of him wanted to hold on to \iquin{} and never release it again. 

But even with the calm warmth of \iquin{} filling him, the shock of seeing a flesh-and-blood, mace-swinging attacker rush at him had caused him to hesitate precious moments, and the mercenary was almost upon him. 

At the last minute he composed himself. 
\tho{I can do this.} 
He extended his right arm, revealing a bracelet of shining, polished brass, encarved with Vaimon writing and adorned with the image of a burning hawk in flight\dash the symbol of the \Sephirah{} \hr{Izion}{\Izion}. 
Focusing his mental power through the bracelet and reaching into \iquin{}, he found the \Sephirah{} he sought. 

The mace was raised high in the air above his head. 
Carzain flinched away, eyes averted, half-expecting to feel his skull crack open as he invoked aloud the name: 
\talk{\Izion!} 

Power surged through him, the power of \Izion, born of the Light of \iquin{}, focused through his mind and amplified by the enchanted bracelet. 
It seemed to him as though the world was bathed in bright, white light. He felt the presence of \Izion{} in his mind and was seized by a feeling of anger... \emph{justified} anger. 
\Izion{} came to him. 
\Izion{} welled up in him. 
\Izion{} filled him. 

\tho{%
  I transcend the barricades of the mind. 
  \Izion{} is with me. 
  \Izion{} is in me, and I am in \Izion.
  I am one with \Izion.
  I am he and he is I.
  His power is mine, and my power is his.}

The bracelet gave off a flash of light. 

The \sephirah{} surfaced into the physical world, its manifestation almost visible to Carzain's spiritual eye, conjuring forth the image of a hawk made of pure fire, exploding from inside the brigand, spreading its burning wings out through his body. 

And Roger burst into flame. 
Fire licked his skin, not from without but from \emph{within}. 
Heat charred his inner organs. 
He screamed in terrible pain, stumbling to the ground and dropping his mace. 

Heartened by success, and by the righteous wrath of \Izion, Carzain pressed the attack. 
In his many mind-battles, he had fought expertly with a sabre and called upon a host of different \Sephiroth{} and \Qliphoth{} for terrible effect, but in the here and the now, in the heat of battle, it was all he could manage to maintain his hold on this one. 

\ta{\Izion!} 
He called upon the \Sephirah{} again, drawing deeper of his power this time, and once more tongues of flames, like the feathers of the burning hawk that was \Izion, erupted from Roger's now prone form. 
Skin blackened, flesh crumbled and turned to ash. 
The bandit's shriek became a rattle. 

\thought{Betraying scum,} thought Carzain. 
\tho{I will kill you!} 

\tho{But I will need more power.} 
He had expended much of his body's energy as was already feeling the exhaustion that came from prolonged spellcasting. 

With his mind's eye he gazed into the \empyrean. 
Deeper. 
Beyond \Iquin. 
Beyond its translucent walls of light. 
Into the dusty wastelands, the black chasms and the neverending empty space. 

Into \Itzach{}, the source of Darkness, abode of the \Qliphoth. 

\tho{%
  More power. 
  Yes.
  The \qliphoth...}

But \Izion{} was still in him, and the \sephirah{} tugged at his mind. 
\tho{%
  No! 
  No \qliphoth{}. 
  The Light is all I need. 
  I have the power of Justice.}

Among the Iquinians, \Izion{} personified the virtue of Justice, the Justice that strikes down the wicked. 
The \Sephirah{} was in Carzain's mind, and his presence flowed through Carzain's thoughts and his passions, strengthening his resolve. 

\tho{I wield the power of Justice! I will kill you!} 

\talk{\Izion!} he called, invoking not only the \Sephirah's raw power but also the Justice he stood for. 
% He hurled yet another fireball at the fallen bandit, who shrieked once and then became still. 
He called forth yet another explosion of fire from the fallen bandit. 
Roger shrieked once and went still. 
A smoking, foul-smelling heap of charred flesh and bones. 

Slumping now with weariness, Carzain stood and watched the smoldering corpse for what seemed like many moments. 
Thoughts raced through his head. 
\tho{%
  I have killed a man. I have fought my first battle, and I won. I killed him. I swore to myself that I would kill him, and I did.} 

Then his eyes widened with sudden realization. 
\talk{Father!} 
He turned and was relieved to see Nishain alive and stirring, but with a bandit\dash{}whose name Carzain did not know\dash{}chrouching near him wielding a \hr{Durcac}{\Durcaci} scimitar. 
\talk{No!} he cried.

The thug stared at him. 
Evidently he had been about to kill Nishain but had recoiled when Carzain began casting spells. 

\begin{comment}
\subsubsection{Vizicar awakens}
\end{comment}
Carzain looked about to see three thugs standing, all with weapons drawn, all glaring at him, their eyes showing both fear and anger. 
\tho{%
  I have won one battle, but more battles await. 
  All these men... 
  I must kill them... or they will kill me.}

\tho{%
  Oh, \Qliphoth. 
  What am I saying?
  I am exhausted already.
  And surrounded by enemies.
  I am doomed.}

As he thought this, a strange trance came over him. 
\vizicar{No,} he heard himself think. 
\vizicar{%
  I will win. 
  I must. 
  They must pay.} 

\tho{Were those my thoughts?} 
It felt like a strange voice in his head. 
His body was moving now, and he saw himself advance on the brigand standing near his father. 

\vizicar{%
  I will slay them. 
  Betrayers! 
  I will slay them all!} 

Nishain was awake now. 
\talk{What is this?} he cried. 
\talk{What is going on?} 
He looked around. 
\talk{Captain Arturo, where are you? Carzain? What are you doing?} 

This caused the bandit near him\dash{}
the boy, Gasper\dash{}to snap out of his shock, and he moved towards Nishain, scimitar raised. 

Seeing the blade swoop towards his father's head, Carzain found himself detachedly considering that perhaps he should be feeling fear. 
But in the grip of this strange ecstasy he found himself strangely calm, feeling first and foremost a cold anger and a rush of excitement in anticipation of the impending battle. 
% Gone was the exhaustion\dash{}indeed, he felt strong and hale as never before. 

\vizicar{More power. I crave more power.}

Time seemed to stand still in the real world while Carzain felt his aethereal limbs reach into the \empyrean. 
Out of his control and of their own volition, they stretched out beyond the safe confines of luminous \Iquin{}. 
Soaring above the gloomy and dusty wastelands where dwelt the lesser \qliphoth{} of the \hs{Circle of Dusk}. 
And further still. 
Down into deep chasms of blackness, the domain of the greater \qliphoth{} of the \hs{Circle of Twilight}. 
And further still, into the chaotic, daemoniac void beyond, where loomed, gaunt and battlemented, the towers of the \hs{Circle of Midnight}, the direst and most dreaded \Qliphoth{} of all. 

\tho{%
  No! 
  Not that. 
  I must not. 
  I must turn back. 
  The Midnight \Qliphoth{} are too dangerous. 
  They bring madness!}

\vizicar{Yes. Just what I need.}

His spiritual body stood on the edge of a vast abyss, its depths roiling with unknown Chaos. 
Before him, a spindly bridge. 
And beyond it, the toothed and clawed Towers of Midnight. 

\tho{No. No. I am not doing this.}

\vizicar{Yes, I am.}

He crossed the bridge. 

He drifted into the Darkness. 

He opened himself up to the \qliphoth. 
And they flowed into him. 
Ecstasy filled him. 
And power. 
Carzain had channelled \Itzach{} before, but never Midnight \Itzach. 
He was not prepared for this. 
It was power such as he had never felt before. 
It hammered in his veins. 
It tingled in his fingers. 
It pounded in his ears. 
It sizzled on his tongue. 
It flashed before his eyes. 
It crackled through his hair. 
It caressed his skin with clawed fingers. 

Lost in the spirital sensation, he had almost forgotten he had a physical body, but now he felt himself move. 
His arm lifted itself. 
His finger extended itself to point at the boy, Gasper. 

His lips moved. 
His throat hummed and vibrated. 

A sound formed. 
A name. 

\ta{\hr{Nyxachel}{\Nyxachel}!}

And the \Itzach{} energy in him condensed into a tangible presence. 
\tho{%
  \Nyxachel. 
  A \Qliphah{} of Midnigh. 
  I have never invoked it before. 
  I cannot control it.}

But it would seem he did. 
\Nyxachel{} flowed through his mind, through his body. 
Into his arm. 
Into his hand. 
There was a crack like thunder, and a lightning lanced from his outstreched hand in a blinding flash\dash blinding with light and with blackness at the same time. 
% Viewed from within the Vaimon trance, it almost took on the shape of a \ravcor, a black-and-white flying pteran, its body and wings made of crackling sparks of electricity. 
It struck the scimitar-wielding boy with tremendous force, and Gasper flew many yards before collapsing in a broken, charred, unmoving heap, 
his boiled flesh seething and bubbling. 

The mercenaries gasped, finally realizing what was happening. 
\talk{Black magic!} he heard one croak. 
\talk{This is not what we bargained for, Fisher!} 
The speaker was Hopper, who proceeded to turn her tail and run.  

\vizicar{No. Not what you bargained for,} Carzain heard the voice say. 
Cold, sardonic. 
His own voice? 
Or someone else's? 

While he pondered this, Carzain felt himself turn towards the \meccaran.

Again, uncontrollably, he reached into \Itzach. 
A voice that was his own called out: 
\ta{\hr{Horvaleth}{\Horvaleth}!} 
He felt a cold, malevolent presence sweep over him as he channeled the power of the \Kliffah{} of the Cruel Winter. 
The \Kliffah{} touched his mind, but the emotion it evoked was not a moral wrath, merely a cold malice. 
Cold and hard and sharp like ice. 
Malice became manifest, and he watched as shards of ice flew from both of his hands to impale the running \meccaran{} through her back. She fell to her face in a puddle of blood and dirt. 
%They fell to their faces, each in a puddle of blood and snow. 

\vizicar{I am victorious.}

\begin{comment}
\subsubsection{Showdown with Fisher}
\end{comment}
Carzain looked around and saw only one thug still standing: 
Fisher, crouching some yards away with his falchion clutched in both hands. 

\talk{Fisher. This was your work.} 

Carzain, by now half-accustomed to being a passenger in his own body, was surprised to realize that he could no longer feel the possessing entity, and that the words he had spoken were his own. 

\tho{Whoa. I'm back. I think.}

Fisher looked around, saw his comrades who had run and gotten slaughtered. 
He turned to Carzain. 
\ta{Black magic fiend! I'll cut you to pieces!} 
He charged, sword raised high. 

Carzain, still in the habit of relying on his body reacting on its own, was caught off guard. 
\tho{Crap! I really am back!}
He jumped aside, but his movement was sluggish, for with the departure of the possessing force his own fatigue had returned. 
Fisher, not easily out-manoeuvred, twisted his sword around so that it tore into the flesh of Carzain's right side and lower arm. 

Carzain ran a few steps before turning. 
A residue of \Izion{} was still in him, and the pain in his wound rekindled the \ps{\sephirah} to fight. 
Fisher attacked again, but Carzain swifty raised his good hand and, drawing deep of his near-depleted energy reserves, invoked his \Sephirah. 
\ta{\Izion! \Izion! \Izion!} 
Again and again he called the name, 
%and again and again projectiles of fire sprang from his hand. 
and again and again fire erupted before him. 
Beyond the glare of the flames, pained screams could be heard. 

Carzain laughed at his victory. 
Then suddenly pain lanced up his left leg. 
He screamed, stumbled and fell over backwards. 
%, then screamed as pain lanced up his left leg. 

He looked up into Fisher's face, now horribly singed. 
The mercenary, after being struck once or twice, had rolled aside, then, while Carzain stood half-blinded by the blaze, had seen his chance to creep forth and slash at the mage's leg. 

Carzain cursed his own overconfidence. 
\tho{%
  I should have called on \Barion{} to shield me from their weapons.
  But \Barion{} is difficult. 
  I have never fully mastered him.}
His power was all but spent and he was close to collapse, but \Izion{} was in his mind, and the \Sephirah{} would not let him relent in the face of the treacherous renegade. 
He managed to sit up and extend his hands, and with the \ps{\Archon} passion burning in him, he felt a rush of new energy flow into him from \iquin{}. 
When he spoke \ps{\Izion} name, it was almost as if the \Sephirah{} was calling out to \emph{him}, ordering him, forcing him to invoke the \ps{\sephirah} name.  
Fisher stood over him, little more than a foot away. 
\Iquin{} flared through Carzain, and he was almost certain he saw the flaming hawk sweep up to sear the thug with its sharp beak and talons. 
%, but he managed to sit up and extend his hands. \Izion{} was in his mind, and the \Sephirah{} was unwilling to let him relent in the face of the treacherous renegade. \Izion
% as he turned his hand to Fisher. \ta{\Izion!} he cried, launching a firebolt at point-blank range straight at the brigand's face. 
Fisher did not cry out, merely crumpled. 
\ta{Die, backstabbing lowlife! Die!} Carzain croaked out, his voice hoarse with exhaustion. 
But \Izion{} remained in him, and he shook all over with fury as power poured from \iquin{} out through his body, manifesting as devouring flames that continued to incinerate the body of the fallen renegade until nothing remained but fine ashes. 



\begin{comment}
\subsection{Aftermath}
\end{comment}

\ta{Carzain! Carzain!} 

Opening his eyes, he found himself lying on the ground, apparently having passed out for a moment. 
Nishain stood bent over him. 
\ta{Father! Are you hurt?} 

%He was still burning away at the corpse when he heard the voice behind him. 

%Startled, he spun around, but it was only Nishain. \ta{Father! Are you hurt?} 

\ta{No, I am well,} said Nishain. 
\ta{But you... you are wounded! We must have you treated.}

%Even with the withdrawal of the strange ecstasy, Carzain was still in the grip of the fury of battle. Finally snapping out of it, he began to truly feel his injuries. He grunted in pain, attempting to cover the cuts with his hands and shifting his weight away from the bad leg. 

It was only then thay Carzain began to truly feel his injuries. 
Lifting his head, he saw that the wound in his side was bleeding heavily. 
A few yards away he could see Fisher's ghastly, smoking remains. 
But his head was already spinning with pain and dizziness, and he had to let it drop again. 

%\ta{Come over here and sit,} said his father, lending him a shoulder and leading him to the wagon so he could sit down. 

\ta{Hold still, let me...} said his father. 
He touched Carzain's side, near the wound and invoked: 
\ta{\Bihirai.} 
Carzain felt how the \Sephirah{} reached out through his father, seeming to caress him with her fingers. 
%He opened himself up to the \Sephirah{} and felt a surge of fatigue as it consumed his bodily energy in its efforts to heal his wound. 
Gradually, the wound closed and the bleeding stopped, the pain subsiding somewhat, but the cut was still there. 

Nishain let out a sigh. 
\ta{This is as good as I can manage.} 
He slumped with weariness. 
Normally, \Ishiel{} would draw the energy needed for healing from both the patient and the healer, but Nishain could see that his son had no energy left to spare\dash{}let the \Sephirah{} attempt to feed off his reserves and she might well kill him\dash{}so he had had to supply all the energy himself. 

\ta{Give me that leg.} 
He took Carzain's wounded leg in his hands and invoked the \Sephirah{} again, slumping further with the effort. 
Again, the wound closed but could still be felt. 

\ta{I can do little more,} said Nishain. 
\ta{%
  I am not the healer that your mother is. 
  Let us get you over to the cart. Can you stand?} 

With some assistance, Carzain climbed to his feet, then hobbled to the cart and sat down. 

\ta{We have some herbs that will help. I will get them,} said his father. 

For a while neither spoke. 
Nishain searched through the wagon for the herbs and tools while Carzain sat nursing his wounds and pondering what had happened. 

Nishain came back. 
\ta{%
  I found the \hr{Jiliba}{\jiliba} berries and the \hr{Dvingen}{\dvingen} leaves. 
  I will prepare them.} 
He sighed. 
\ta{And some food, I suppose.} 
He looked at his son with concern and some measure of unease. 
\ta{You should get some rest, son.} 

And so Carzain rested while his father made a fire and prepared breakfast and medicine. 

The silence stretched, became embarrassing. 
Carzain was not comfortable discussing what had happened and his father was not comfortable asking. 
Nishain was purposefully ignoring the charred bodies scattered around the camp, evidently focusing intently on the simple task at hand as a means of coping with the shock of the attack. 

Finally, Nishain took the pot of cooked herbs from the fire. 
\ta{It should be ready now.} 
He poured some in a cup and handed it to Carzain. 
\ta{Here, \jiliba{} tea.} 

\ta{Thank you.} 
Carzain took the cup and drank. 
\Jiliba{} tea was known to help you recover from exhaustion. 

Nishain took forth some straps of cloth. 
\ta{Here, you should also get a poultice for the cuts.} 
He took the pot with the dissolved \dvingen{} leaves. 
\ta{This will sting a bit at first.} 

Carzain grunted as he let his father foment his wounds with the \dvingen{} mash and wrap them up. 
It hurt, but he was not about to let it show. 
He had his masculine pride. 

\ta{There, this should help it heal,} said Nishain. 

\ta{Yes. Thank you, Father.}

Nishain returned to the fire and started to prepare food, as an excuse for prolonging the otherwise awkward silence. 
After a while, he returned with with some roasted pork, lettuce and wine. 
They ate for a while in silence. 

%At length, Nishain came back with some roasted pork, lettuce and wine. 

%(Some more stuff. They eat for a while in silence.) 

In the meantime, Carzain looked around. 
Apart from the four mutineers he had killed, there were two more bodies; those of Arturo and the old Harold. 
%Those were Arturo, the old Harold and the last soldier, a young, beardless man. Carzain did not know his name, but he believed it was this man's cry that had awakened him. His throat had been slit, and as far as he could see, the same had been done to the two others. 

At length, Nishain sighed. 
\ta{You were right, son. I should not have disbelieved you earlier.} 

Carzain gave a non-committal \ta{Hmm}. 
\tho{%
  I guess it was guilt, as much as shock, that kept Father silent for so long,} he mused. 

Again, for a while no one spoke. 

\tho{I suppose I should help assuage it,} thought Carzain. 
\ta{But you were right about Arturo, Father,} he said. 
\ta{He is over there.} He pointed. 
\ta{They mutinied against him, slit his throat. 
    It seems I was right about Fisher being the leader.}

Nishain nodded. 

There was another pause, until finally Nishain dared to ask: 
\ta{Carzain... how did you... how did you...?} 

\tho{How did I kill those men, you mean.} 
Carzain hesitated before answering. 
He \emph{had} killed them. 
He had quickly come to terms with that fact, and had found that he felt no guilt or grief over it, but even so, he found that he was not comfortable discussing it with his father. 
\ta{I don't know,} he said, buying himself more time to think. 
\tho{Fool,} he thought to himself. 
\tho{Why do I suddenly feel abashed?} He snorted inwardly at himself. 
\tho{Like a religious sheep.} 
Carzain used to pride himself of being free from such sentiments of irrational shame. 
He and his father were close, and he had always been able to talk to his father about anything. 
Even sex, which many people balked at. 
In this, among other things, he favoured his Geican heritage. 

%But here he had found something that his mind feared to talk about. 
But here he had found a subject matter that gave pause to him. 
\tho{Perhaps I am no better than all those fools who feel shame at everything.} 
This caused him to frown. 
\tho{Pull yourself together, Carzain. Of course I am better than they.} 
\ta{Yes,} he said at last, 
\ta{I killed those men. I...}\dash{}again he stalled\dash{}%
\ta{I don't quite know how.} 

\ta{You... you fought with such... such \emph{power},} his Father began. \ta{%
  And those \Qliphoth{} you called... 
  \Nyxachel... and \Horvaleth... 
  I had no idea you could do that.} 

\tho{Neither did I,} Carzain wanted to say. But what he said was: 
\ta{%
  No... I didn't realize I had such power. I think... I think when I realized they had betrayed us and wanted to kill us, I was... I was seized by an immense anger, an... an immense \emph{hate}.} 
Carzain was somewhat relieved at this turn of the conversation. What he said was true, even if it was not the whole reason, but moreover, this was something he could talk about, something he knew. 
As something of an outsider in his home town, he had always had enemies. 
\tho{Everyone had enemies,} he had always figured. 
When he was a small child, there had been other children, stronger and bigger than he, who had picked on the \quo{strange} Vaimon boy. 
He had since grown up and learned how to defend himself\dash with magic if need be\dash but some enmities remained. 
There were still bullies who would attempt to molest him when given the chance. 
\tho{They still resent me because I am better than they.}

At least, that was his side of the story. 

Yes, Carzain knew of anger and hate against an enemy, and he knew how to talk about it. 

\ta{%
  I think the anger gave me strength. You know I have been in fights often enough before where I wanted to kill my opponent.} 
They had discussed this before, and Nishain had shown more sympathy for his son's violent urges than an Iquinian would. 
\ta{%
  This was the first time I was able to kill an enemy. I don't know... this passion might have enabled me to channel more power than otherwise. Especially in conjunction with \Izion{} and his virtue. It has happened before.} 
It was true; according to the literature, strong emotion could often enable a mage to perform feats otherwise beyond his ability. It might be the explanation. Still, Carzain had his doubts, as this did not seem to explain his feeling of being possessed. 

His father nodded. 
\ta{%
  Hmm... yes... that might be. 
  But those \Qliphoth! 
  They are of the Midnight Circle. 
  Terribly cruel and dangerous.
  Or so I have read. 
  I have never tried to channel their power.} 
\hypota{And neither should you,} was what Nishain was trying to say. 
But he appeared to be finding it hard to reprimand the man who had just ruthlessly slaughtered four armed soldiers. 
Instead he said: 
\ta{%
  Do we even have any books that describe how to invoke them? 
  Or how do you know of them?}

Carzain was hesitant to talk about it, but he saw that his father was intent on pressing the issue. 
\tho{%
  Pull yourself together, Carzain! I just killed six armed soldiers. I need not fear to talk to my own father.} 
He took a deep breath. 
\ta{I don't.} 

\ta{What?}

\ta{%
  I don't know how to invoke them. 
  Yes, I did, but I don't know how. 
  It just came to me. 
  It was the same with both of them.} 

Nishain gave him a wondering, incredulous look.

\ta{%
  I fought the first man on my own, calling upon \Izion. I killed him, and then I felt...}%
\dash{}again he hesitated and had to force himself to go on\dash{}%
\ta{%
  I felt this weird... \emph{ecstasy}. 
  As if some force had seized control of my body. 
  As if I was possessed by some entity. 
  Perhaps it was the Midnight \Qliphoth{} themselves.} 
He paused to drink deep of the wine. 
\ta{That was when I channelled them. I cannot tell you how.}


\ta{Possessed by an \Qliphah?}
Nishain gaped. 
\ta{\Itzach!} he cursed. 
\ta{Huh. Literally.} 
He hesitated before saying: 
\ta{Very well, I believe you. But damn...} 

\ta{%
  I don't know if that is what happened, but that is how it felt. 
  As if something was in control of me.} 
He smiled. 
\ta{%
  Except at the end. 
  The ecstasy vanished at the end, when there was only Fisher left. 
  I fought him myself.} 
He gestured at his wounds with a sarcastic grin. 
\ta{%
  And see what that got me. 
  Maybe I should have left it to the \qliphah, huh?} 

He gritted his teeth. 

\ta{%
  But I killed him. I killed him.}

Nishain did not reply to that, leaving Carzain to his thoughts. 

\tho{%
  As if something was in control of me.
  As if a \qliphah{} or something was using my body to fight.
  As if \emph{it} was invoking and channelling \emph{me}. 
  That is now how it is supposed to be.
  The Vaimon is supposed to be the master. 
  That is the Geican way. 
  
  But maybe this is what the Midnight Circle do.
  Perhaps that is why they are feared.
  
  It was scary.
  And weird. 
  In a sense, it saved the day. 
  But it also damned well nearly got me killed in the process.}







%\bookchapter{\Vertex{} Spike}
\begin{comment}
\section{Vizicar dreams}
\end{comment}

\new
%\section{A Brief Awakening}
\tho{They are upon me!} 

Vizicar Duras Respina was certain of very little save that he was beset by enemies. 
\tho{Who are they? What are they?} 
He did not know. 

He was fleeing through the familiar halls of the \hs{Rainbow Palace} in \hr{Merodar}{\Merodar}, where he had dwelt almost all his life. But something was amiss. Where some of the rooms and corridors were as they should be, others were wrong, twisted, changed. Stairs appeared where none should be. Dead ends greeted him where he expected doors. Had he been full of faculty this would have given him pause, but now it was all he could do to keep focused on his flight. Far behind him\dash\tho{yet so near, much too near!}\dash he thought he could dimly hear the footsteps of his pursuers. Assassins, invaders, ghosts... he could not say, but they were after his life, and he dreaded them. 

He ran on.

He was running through the woods, the deepest, darkest centre of an ancient, \Wylde{} forest. Where he was he did not know, but he knew that somewhere ahead lay his home\dash if he could only make it. From the distance came the faint baying of hounds. \tho{The hunting-dogs! They are on my heels!} He knew he must elude the dogs at all costs, lest they tear him apart and feast on his flesh. 

The \Wylde{} resented his presence. Gnarled trees loomed above him, regarding him with hateful, unseen eyes. Roots sought to trip him. Sharp-edged nuts and acorns cut into his bare feet. Branches like scourges lashed and tore his naked body. Boughs and leaves converged above like massive hands, seeking to block out the Sun and leave him stumbling in total darkness. 

The howl of a hound pierced his ears. 
\tho{Closer than ever before!} 

He ran on. 

He was swimming in an ocean\dash but what surrounded him was not water, but a thick, viscous slime. He could not breathe. Far above he could see the faintest glimmer of light, and he knew that he must climb to the surface, must reach the Sun. 

In the depths beneath he perceived a horde of creatures\dash or a lone abomination of unfathomable vastness? He did not know; all he perceived was the image of hundreds of tentacles reaching for him. 

%Tendrils of what might be seaweed entangled him. 
Tendrils entangled him. Seaweed, perhaps, or the fingers of horrid monsters. 

He struggled with all his strength to break free, paddling with his arms and legs, seeking to crawl upward and escape the grasping tentacles that would draw him down to the lightless depths, food for putrid things that had no name. The liquid bore down on him with a terrible weight, like the dirty foot of some tremendous giant, crushing him. The sea itself hated him and desired to devour him. 

He swam on. 

He turned around a corner, past one of the many crystalline pillars of the palace. As he did, he felt a whish of the wind, as if a knife sliced the air just a hair's breadth behind him. Not daring to turn, he plunged down the corridor. 

Pictures and tapesties adorned the walls, and all followed him with malicious eyes, burning into him. 
\hypotalk{You are not worthy,} they seemed to say. 
\hypotalk{You have fallen from grace and are no longer worthy.} 

The hounds were nearly upon him. He dared not turn, but their barking was loud, frenzied, and he could smell their hot breath, feel their drool on his back. The trees were crowding around him, and he had to edge his way between them. As he did, the trees twitched, moved, closing in to squeeze him, like giant fingers crushing a bug. 

Tentacles brushed his legs. He squirmed, feebly pushing his way through the suffocating ooze. The weed ensnared him like a fisherman's net. He wanted to gasp for air, but found only the foetid slime.

If he could only reach his home... if he could only reach the surface... 

\hypota{Gaaaaah!}

A cry ripped the air.

Somehow, the sound filled him not with dread but with relief. For this was not the yowl of some nightmarish beast, not the shriek of a slavering thing from the deep. It was the yell of a man. A man terrified, but nonetheless, a man beset not by the horrors that lurked in the world beyond mortals' sight, but by the terrors of the known world where men lived and died. To Vizicar it served to affirm his identity, his grasp on reality. It was as if the walls became more solid, more like rock and crystal. The trees became more rigid, and the ooze felt slightly more like water. 

He turned another corner and found himself staring into a man-high mirror. It was clearly a mirror, yet the man he saw before him was a stranger. Younger and different of build, his hair dark rather than fair, and beardless. A stranger, yet as Vizicar studied him, he could not escape a sense of familiarity. There was something about the man's traits, his eyes, his posture...

The shout was abruptly cut short. 

Vizicar again heard the baying of the hounds behind him. He imagined that he felt the puff of air from an assassin's dagger plunging toward his back. On pure instinct he leapt forward. 

With massive effort, he snapped the seaweed pinning him down. He gave the probing tentacle a desperate kick and pushed himself up. 

A root caught his naked foot, and he stumbled. The drool of the hunting-dogs dripped onto his heel and thigh. He crashed into the jeweled mirror. The mirror became a muddy pool in the forest. He fell through it... through the image of the dark-haired man... and into him. 

Suddenly he was aware of a foe running for him. 
It was a faceless, veiled assassin, moving in complete silence, envenomed stiletto in his hands. 
It was a wolfhound, its jaws slavering, its eyes burning yellow in the nighted forest, its paws stained red with dried gore. 
It was a bearded man shouting and swinging a mace. 
It was a horror of the lightless deeps, a nameless tentacled thing dripping ichor. It stormed at him. It clawed at his throat. It enveloped him. 

Vizicar felt hot rage rising in him. Furious, he slashed with his sabre. He kicked and punched with his bare limbs. He invoked \Archons{} to blast asunder his enemy. 

\hypota{Izion!} he heard himself invoke\dash\tho{is that my voice?}\dash and he felt the \Sephirah's power flow into his body. 

\tho{Betraying scum! I will kill you!} 

He screamed. He shouted. He roared. He cried out his fury, his outrage. 

\tho{I will kill you!}

\hypota{Izion!} Fire surged from his outstreched hand. Fire erupted from his body. The wolf yowled as it burned. The amorphous thing sizzled and melted, turning to vapour. The man crumpled in an ashen heap. 

Exhilarated, Vizicar looked around to see many more foes encircling him. They were hunting-dogs... armed men... slimy horrors... all those things at once and more still.

Anger mounted within him, but where before it had been hot, now it became cold. 
\tho{All these... I must kill them.} 

He pushed past one more gnarled tree. The forest cleared before him. Light filled his eyes. With one final stroke of his feet he broke through the surface of the slimy ocean, to find the Sun shining bright and within his grasp. 

He was in a forest. But not the hateful, benighted wolf-haunted forest of his fevered dream. This was a natural forest, the trees mercifully mindless and unmoving. Enemies surrounded him. He saw still the fangs of hounds on their blurred faces. He perceived still the ichor dripping from their limbs. But he know\dash somehow, he knew\dash that these were men. Not monsters of the Beyond. Not the inner \daemons{} of his dreams. Men of flesh and blood.  

Cold was his rage, and dark, and cruel. He smiled to himself. 
\tho{Very well. I will slay them. Betrayers! I will slay them all!} 
As those thoughts went through his head he heard them echoed somewhere in his mind, as if repeated by some voice. A voice tinged with wonder, disbelief. 

A man near him shouted words, but he did not hear them. 
\tho{%
  No time. Now we fight.
  
  More power. 
  I crave more power.} 

He descended through the \empyrean, down until he reached the Towers of Midnight. 
They loomed before him. 
Unknowable and yet familiar. 
Foreboding and yet reassuring. 
Terrifying and yet alluring. 

\tho{Yes. Just what I need.}

He made to cross the bridge to the Darkness... but something stopped him. 
A force within him held him back. 
A fear.

\hypota{No. No. I am not doing this,} it seemed to say. 

No time for weakness now. 
Vizicar shrugged it off. 
\tho{Yes, I am.}

He lifted his hand and invoked a name. 
\ta{\Nyxachel!} 
With practiced familiary he reached into \Itzach{}, and the \Qliphah{} responded. Its power filled him, and its essence, and its will. 
\tho{You have wronged me. For you I have no pity. Perish.}

Power rippled through him, though his mind and body, and the crackling arrows of \Nyxachel{} burst from his hand. With his hatred the \Qliphah{} smote the wrongdoer, and he was cast to the ground, and he was destroyed. 

Vizicar gazed down at his hand. It felt weird. It looked weird. Ghostlike. He flexed it, and the fingers moved. He clenched it into a fist, felt the fingers against the palm. It felt familiar, but also alien. As if it was his body, yet somehow not. As if... as if his mind was locked in another man's body. 

\tho{Why am I here? How did I get here?} He found no answer. 
\tho{Who am I?} 

He remembered a name. 
\tho{Vizicar. I am Vizicar Duras Respina.} 

\tho{But who is that?}

He was given no more time to contemplate. His foes were milling about him. One spoke, a short, ugly goblin-creature: 
\ta{This is not what we bargained for!} The creature turned and made to lope away. 

Hate and anger returned. He smiled. 
\tho{No. Not what you bargained for.} 
Again he heard the strange echo, as if a stranger was whispering his words back to him. A stranger who was surprised to hear him speak. 

Pushing the voice away, he turned to the goblin-creature. His ghostly body obeyed. %It felt as if moving too slow, and at the same time too fast.
\tho{No more playing.} 
\ta{\Horvaleth!} He reached into \nieur{}, calling out for the ice queen, and she responded, and came to him. He felt the cold of her wicked caress on his skin, tasted her cruel kiss like frostbite on his lips. \tho{Lend me your malice, ice queen.} And she did. He felt her power run though him. He watched as his fingers became those of the \Qliphah\dash frozen, poignant, deadly. \Horvaleth's fingers tore through the fleeing creature, and it was destroyed. It fell to the ground, speared on blades of ice, blood gushing out. 

Vizicar turned. Only one foe remained. He faced the creature. \tho{You are the worst of them.} Somehow he knew that. \tho{And now you are mine.} As he stared into his enemy's eyes, the world began to dissolve around him. 

\tho{I will kill you.}

He was in his throne room in the palace. He was floating above the sea of filth. He was at the clearing in the spectral forest. 

\tho{I will defeat you.}

His body became that of a ghost. It became mist. Air. Nothing. 

\tho{I will destroy you.}

His foe was a hound. He was a masked assassin. An abomination of slime. Then a ghost. Then mist. Then nothing. 

\tho{I am victorious. I have vanquished you all.}

Vizicar smiled inside with pleasure. 

His consciousness faded away. 









\begin{comment}
\section{\Esmerel}
\end{comment}

%\section{\Vertex{} Spike}
\stamp
  {\dateMutiny}
  {\hr{Topaz Chateau}{\TopazChateau}, \hr{Redce}{\Redce}}
%\dateplace{Carz}{11th}{\Yeziel}{\TopazChateau, \Redce}
%
% At the time of Carzain's fight, when Vizicar awakens within him and takes control of his body, the Malach's awakening sends ripples through Iquin. Esmerel is a Redcor Matron who has studied the Malachim. She feels the ripple and knows that a Malach has awakened. She begins research to discover its location and identity. 

%\new
%A ripple went through Iquin, and \Esmerel{} stirred from her books. It was almost nothing, the slightest of fluctuations, indiscernible to even a skilled Vaimon, and only \Esmerelz{} decades-long dedication and attunement enabled her to feel it. 
%
%She sat up with a start. With haste she reached into Iquin and invoked her \Sephiroth. 
%
%\ta{What is it, Matron?} said Iselle. \Esmerel{} raised a hand, and her assistant fell silent. 
%
%%\ta{Silence, girl,} said \Esmerel. 
%
%Esmerel sends Iselle off to find some incence and some more Redcor to assist Esmerel in the ritual. They combine to form a circle, then meditatate. 
%
%\Esmerel{} is deep in her \Sephirah{}-meditation, sitting at a mystic pool of silvery water\dash the Waters of Enlightenment. She notices a ripple in the Web of the Realms and sends her mind probing to investigate. 
\tho{A flash of lightning!} 

\hs{Redcor} \hr{Matron}{\Matron} \EsmerelFull{} started, almost broken out of her meditation. 
\tho{What was that?} 

\tho{A ripple in the pool. A massive discharge of energy.}

She strained her inner sight, gazing deeper into the silvery mirror before her\dash the Waters of Enlightenment, the window to hidden dimensions Beyond. The ripple faded quickly, but she had caught its scent. 

\tho{Come to me, \sephiroth,} she prayed. 
\tho{Guard me and guide me safely through the shadows.} 
And she felt them draw near, felt their familiar yet wondrous touch. Calming, like a mother's embrace. And splendid, like the sunrise. And breathtaking, like the view from the high towers of the \TopazChateau{} when she had first seen it as a young girl, many decades ago. Shielded in the protective embrace of the \sephiroth{} and with her senses amplified by the mystic mirror, she sent her mind questing through occult dimensions in pursuit of the anomalous power surge. 

Some among the Redcor disapproved of the Waters; some even saw the use of the pool as heresy, a pathway to corruption. 
%But \Esmerel{} knew better. The silvery Waters were a doorway to great wisdom, and after all, 
\Esmerel{} scoffed at those fears. 
%After all, 
%she had the protection of the \sephiroth, so why should she fear the shimmering mirror and the visions it showed? 
% \emph{The true heretics,} she mused, 
% \emph{are they who doubt the omnipotence and omnibenevolence of the \sephiroth{}. A truly faithful believer needs have no fear of the mystic mirror and the visions it shows.}
\tho{Superstition,} she mused. 
\tho{%
  In doubting the omnipotence and omnibenevolence of the \sephiroth{}, they, if any, are the true heretics. A genuine believer needs have no fear of the mystic mirror and the visions it shows.}

No, the Waters of Enlightenment were a gift, and a doorway to great wisdom. And what luck that she had been meditating by the shimmering lake at this very moment, so that the Waters had enabled her to sense the cosmic anomaly, fleeting as it was. 
\tho{Truly wise is the Light,} she reflected. 

%\tho{But I must waste no time.} 
%But she knew she must waste no time. 
%But she could afford to waste no more time on such speculation. 

Suddenly, darkness. 

She was ripped out of her pious thoughts. 

\tho{Darkness.

  Darkness everywhere.}

\Esmerel{} found herself aimlessly adrift amid a huge, endless space. Stars dotted the heavens in all directions, tiny pinpricks against the devouring blackness of the firmament. 
%But however pious these thoughts, they made her lose track of the object of her search. Suddenly she found herself aimlessly adrift amid a huge, endless space. Stars dotted the heavens in all directions, tiny pinpricks against the devouring blackness of the firmament. 
%\Esmerel{} 
She shuddered inside, overwhelmed by the sheer vastness of the nighted void\dash cold darkness stretching off into infinity on all sides, 
%black gulfs yawning open like the jaws of some cosmic monster of unimaginable proportions, 
like some cosmic monster of unimaginable proportions, black gulfs like jaws yawning wide open as if to swallow her, to crush her tiny body and soul in its lightless belly. 

\tho{Pull yourself together, \Esmerel,} she scolded herself. 
\tho{You are above such superstition.} 
She had to remind herself that as vast as space might be, the Light was greater still. 
With effort, she wrested her astral senses away from the enchanting but terrible vistas of the void and sought instead the consoling touch of the \sephiroth. 

The soothing presence of the \Archons{} gave her renewed peace of mind, 
but with the comfort came a silent admonition: 
\tho{Concentrate on the task at hand.} 

% She invokes \sephiroth{}, and they guide her as her mind sails through the occult dimensions. She floats in a sea of stars, with the blazing \hs{Sun} and the twin \hs{Moons} as her guides. The Light envelops her, yet even so she cannot help but shudder at the great blackness surrounding her\dash cold darkness stretching off into infinity on all sides. She was overwhelmed by the sheer vastness of the void, looming all around as if poised to crush her, and had to remind herself that the Light was greater still. With effort she wrested her astral senses away from those vistas and sought instead the comforting touch of the \sephiroth. 
% 
% The soothing touch of the \Archons{} gave her renewed peace of mind. %, and she was again able to focus. 
% But with the comfort came a silent admonition: \tho{Focus on the task at hand.} 

%\Esmerel{} concentrated on directing the swirling mists of the Waters of Enlightenment. Amplified by the power of the enchanted pool she sent her soul questing along the ley lines of the great Web of the Realms
\Esmerel{} let the blessed calm of the Light flow through her body, erasing her fears and allowing her to focus her senses, and with renewed clarity she reached out through the cosmic threads of the Web of the Realms. 

And she detected it. A slight shivering of a thread. 
%\tho{I will find the source of this }
Swiftly she followed, sending her mind speeding along the thread, the weave and flow of the cosmos swirling around her as she flew. 
%Swiftly, she sent her mind floating along the thread. 
%The weave and flow of the cosmos swirled around her as she sent her mind speeding along the thread. 
As she moved closer, the thread seemed to vibrate more violently, and mystic winds tore at the web around her. Subtle, undetectable to the senses of the common folk, and even most of the initiated. But to \Esmerel, connected to the Realms as she was through the Waters of Enlightenment, it was like a raging storm shaking the fabric of the Web. 

Finally, the source of the power surge came into her view: A massive \vertex{}, pulling at the cosmic threads, flailing them about like whips. To her eyes the \vertex{} was a burning conflux of raw power\dash shining white interwoven with blood red and pitch black, all spinning in chaotic confusion. 

\tho{A \vertex{} spike! And not just any \vertex, at that.} 
For \Esmerel{} recognized the pattern of those energies, the vibrations they emitted. 

\tho{%
  A Scion! There can be no doubt. A Scion has awakened! 
  
  An \Archon{} given flesh...}

In that moment, a rogue burst of energy pulsed from the fiery \vertex. 
A thread wildly, blindly lashed out, striking \ps{\Esmerel} astral form, sending gut-wrenching pain through her.

Fast losing consciousness from the stress, she felt the \sephiroth{} closing about her, carrying her back to the safety of her body. 
One thought went through her mind as she dozed away: 

\tho{I found it. I, \EsmerelFull, discovered the new Scion...}

Oblivion took her. 



