\bookchapter{The Terror of \EreshKal}
\stamp
  {\dateSortieFindsTown}
  {Kenshaer Forest, north of Gilwaed}

% \begin{garbage}
\begin{comment}
\chapter{Old version}
\end{comment}
\begin{comment}
\section{Gilwaed in ruins}
\end{comment}

% \begin{comment}
% The sortie, that includes Carzain, pass by a Pelidorian village. 
% It has been destroyed by the Rungerans' evil magic (as a test of their spells). 
% They are horriﬁed by the foul sorcery at work.
\ta{We should be there soon,} said Gwelthein from her position at the head of the column. 
\ta{%
  Gilwaed is just around the corner. 
  The rest of you should stay here. 
  I'll scout ahead and look for any Rungerans nearby.}

Carzain had noticed that the forest was thinning. 
Looking up at the sky he could now see the moons clearly. 
They lit up the thick fog, making it appear as if the mist was emanating from the moons. 
There they hung in the sky like a pair of shining eyes. 
Drab gray \Dun, the largest moon, and Visha, smaller but brighter\dash a sinister, spectral kind of brightness; pale white with a hint of corpselike blue. 

\tho{\Dun{} and Visha. The two eyes of some gigantic and deformed god.} 
That was how some myths explained the moons. 

Soon after Gwelthein returned. 
\ta{Coast looks clear. 
    Follow me.}

Curwen silently gestured for the rest to follow Gwelthein's lead. 
As they rode on, the trees cleared and a village came into view. 

Or rather, the remains of a village. 

% Huts are ripped apart. This doesn't look so strange to Carzain, but the Rangers can tell them that this doesn't look like the work of regular animals or artillery. 
Huts and houses had been smashed and ripped apart, seemingly by some great animal. 
Broken beams and pieces of thatching lay scattered around, many of them charred. 
The villagers lay scattered around, too. 
The bloody corpses of dozens of \scathae{}; smashed, ripped and charred like their homes. 
Children and adults alike. 

Everywhere they could see, nothing larger than a bettle or rat moved. 
The village of Gilwaed had been wiped out. 

\ta{Whoa...} said a soldier. 
Echoing what was also Carzain's first thought. 

\ta{Looks like the Rungerans beat us to it,} another soldier said drily. 

They explored the ruins, their mounts stepping over severed limbs, pieces of timber and pools of dried blood. 
% Villagers lie scattered around. 

\Tsekkect{} moved gingerly among the corpses while making strange gestures. 
She would cross her arms across her neck, holding each hand near the opposite ear (or so Carzain thought; \meccara{} had little in the way of visible ears), wiggle her fingers and speak some incomprehensible words in a gargling, croaking voice. 
Presumably a superstition meant to ward off evil. 

\ta{This is wrong,} said Gwelthein. 
\ta{The stench is all wrong. 
    There's the smell of ash and dried blood and beginning rot, but that's not all. 
    Underneath it there is a fouler smell. 
    Like... flesh devoured by acid, perhaps. 
    Bitter... heady.} 
She snorted and shook her head as if to clear the foulness from her nostrils. 
%     It is a bitter and heady smell. 
%     It makes the nostrils itch if you sniff close to the bodies. 
\ta{The stench speaks of unnatural evil. 
    Wickedness has been unleashed here.
    Sorcery.%
}

\ta{Well, we've certainly gotten behind their army,} Delph commented. 

Carzain did not reply. 
He was too caught up in the feelings the place evoked. 
\tho{These people did not die a normal death.}
To his Vaimon senses the whole village was shrouded in an aura of evil. 
The death lay so thick he could almost touch it. 
It reminded him of the feeling of the \qliphoth{} of the Midnight Circle, but more primal, more savage, more vicious. 
He imagined a million biting teeth, a million stabbing claws. 
%He was busy fighting the urge to puke. 
Part of him wanted to puke, as if that might somehow clear away the taint that he felt seeping in. 

Yet another part of him took a morbid delight in the sensation and desired nothing more than to embrace the destruction that surrounded him. 
It was hard to explain, but the lingering scent of sorcery in the air somehow spoke to something within him. 
Teased some dormant inner hunger. 
Stirred deeply buried memories. 

\tho{%
  This feels... good, somehow.
  And it shouldn't. 
  This isn't right. 
  This isn't some campfire ghost story. 
  This is real people, killed by gruesome magic. 
  I should not be enjoying this.
  What is wrong with me? 
}








\begin{comment}
\section{A thousand mouths}
\end{comment}
\new
% On the southeastern edge of town they find armed militia, most of which have been pierced by arrows or cut down by swords and spears. That's the nice part. Other places they find people who seem to have been cut open from the inside, or have strange wounds were blood seems to have burst out for no reason. 
On the southeastern edge of town they found the bodies of \scathae{} armed with spears, axes, swords and guns, some wearing helms and shields. 
Evidently local militia, Archibald Curwen saw. 
Most had been pierced with arrows or cut down by swords. 

Filcoi dismounted for a closer look. 
She poked one body. 
\ta{Look here, sir,} she said. 
\ta{This one's been nibbled by rats.} 

\ta{Meaning?} said Curwen. 

\ta{None of those back there have been touched. 
    Only bugs dare eat them. 
    The rats shy away.}

\ta{Hm,} said Curwen. 
\tho{%
  Makes sense. 
  These guys died a natural death. 
  Those others didn't.}



% The Rangers can relate that it all smells abnormal. There is the smell of blood, beginning decay and burnt buildings, but there is also an undercurrent of something sinister. Like... flesh devoured by acid, perhaps. It is a bitter and heady smell. It makes the nostrils itch if you sniff close to the bodies. 

% It makes them all nauseous. 
% 
% Carzain recognizes a smell reminiscent of that of certain \qliphoth. 

Curwen went back into the village. 
He picked one of the \quo{unnatural} dead, a middle-aged \sphyle. 
She had strange wounds that looked as if they had not been inflicted, but had burst open from the inside on their own. 
\tho{Internal bleedings. Could be \daemon-inflicted.}
He turned her over to get a look at her face. 
%Curwen turns over one of the suspicious dead and looks into his eyes. 
The eyes were unusually gray and colourless, as if darkened by an abnormal \quo{deadness}. 
Behind and around those dead eyes the face was contorted with an eerie dread. 
Curwen had killed enough people and seen enough people die to know that this was not the face of one who merely feared death. 
This was the horror of something far beyond the ken of mortals. 
This \scatha{} had been killed by a thing from the Beyond. 
Curwen, who through his work as a mage had much experience with the dark corners of the mind, imagined he could read the story of the \ps{\sphyle} last moments in those lines of fear: 
\hypota{%
  Monsters! 
  \Daemons! 
  Evil magic! 
  This can't be happening to me. 
  This isn't real.
  It's a bad dream. 
  A really bad dream. 
  Oh, Light, it's real!
  It's the end of the world!
  We're all going to die!%
}

\tho{But that doesn't tell us exactly what happened.}
He looked up and saw Filcoi nearby. 
\ta{How long have they been dead?} 

\ta{More than two days, sir,} said Filcoi. 
\ta{Perhaps even a week.
    But certainly not two weeks.}

\tho{%
  Up to a week. 
  Damn.} % Curwen thought. 
\tho{%
  I hadn't thought it'd be more than a day or two. 
%   With luck, the Rungeran army will be some way away by now. 
%   And with luck, their mages will not be straggling behind.
}
% 
% 
% 
% The Pelidorian army had been planning to march past \Forklin{} and reach another city, Dendrum, closer to the border in time to reinforce it and hopefully hold it. 
% (This should be moved to another chapter, before the sally sets out from \Forklin!)
% 
% But the Rungeran army was advancing faster than Curwen had anticipated, and hoped. 
Clearly \ps{\Dornaer} suspicions had been correct. 
The Rungeran army was advancing faster than \Sethgal{} had anticipated and hoped. 
\tho{%
  The Dendrum plan is no good. 
  At this rate they will reach it before we do. 
%   So we'll arrive to find a city besieged. 
%   Or taken.
  I'm not convinced Dendrum can withstand a siege without us. 
  And I'm even less convinced that the nobles in charge can.
  
  This is bad.
  I need to get this news back to the army, and fast.%
}
     
Curwen looked around. 
\tho{And then there's the way they died.}
He looked at the jumbles of sticks and piles of ash that had once been houses. 
Looked at the villagers that lay scattered, covered in blood, limbs cramped, eyes gray and dead. 
\tho{%
  That's also bad.
  Worse, actually. 
  I don't know exactly what this sorcery is, but it's wicked.
  Black as fuck, even by black magic standards. 
  The smell alone is telling enough. 
  And there are the eyes, and the contorted faces. 
  
  Let's see if we can find out more...
}

Curwen slipped into Vaimon trance and reached out into the Beyond, looking for the traces of whatever \qliphoth{} or \daemons{} might have done this. 
He examined the cosmic threads and found a lingering smell, a residue of sorcery. 
\tho{%
  We've got something.
  Smells ugly.} 
He followed the threads, trying to trace the scent back to its origin. 

\tho{%
  It's buried deep. 
  Far removed from the mortal world.
  Down in Chaos...}

Curwen took a deep breath, then plunged his mind in... and immediately recoiled. 
The sheer presence of that force that lurked at the end of those threads struck him like a physical blow, the chaotic potency of it searing like fire. 
The image that arose in his mind was that of a gigantic monster: 
a blind, crawling, amorphous thing the colour of blood mixed with ash, roaring its mindless bloodlust from a thousand mouths. 

\tho{%
  \ps{\Qliphoth} cunts! 
  This is bad. 
  This is fucking bad. 
  The Rungerans shouldn't have this. 
  No ordinary \ishrah{} should be having this shit. 
  This can only mean one thing...
  
  But I still need to know more. 
  I need to get closer to them. 
  Try if I can see them in action.%
}

He rose to his feet. 
\ta{%
  All right, boys. 
  We've seen enough. 
  Move out!
}
% \end{comment}









\begin{comment}
\section{Vizicar}
\end{comment}
\new
\begin{comment}
Carzain is spacing out. 
Curwen tells the others to go poke him. 
But Carzain doesn't hear. 
He hears Vizicar instead. 

Vizicar feels the \daemons. 
He feels the essence of Chaos. 
The ground, the air, the plants... everything is soaked in it. 
It is hideous, but also invigorating. 
It is a myriad feelings at once. 
Death and life, horror and joy. 
It spoke to something deep within him. 
It made him feel... alive. 
It awakened a hidden side of him. 
It was a revelation. 
It brought him one step closer to who he really was. 

\tho{Who am I?}
\end{comment}
Vizicar felt the \daemonic{} presence around him. 
He felt the essence of Chaos. 
The ground, the air, the plants... everything was soaked in it. 

It was hideous, but also invigorating. 
It was terrifying, but also intoxicating. 
It was a myriad feelings at once. 
Death and life, horror and joy. 
It spoke to something deep within him. 
It made him feel... alive. 
It awakened a hidden side of him. 
He felt it as a revelation, bringing him one step closer to who he really was. 

\tho{Who am I?}

That was the question. 
That was what he had to remember. 

\tho{Who am I really?}





\new
Curwen climbed onto his \relc{} and headed back toward the forest. 
\ta{Come on, boys. Move out!}

Then he noticed that \Shireyo{} was not following. 
He stood amid the bodies and ruins with his back turned and did not seem to have heard the command at all. 

\tho{%
  Fuck. What's he doing now? 
  Is he getting all squeamish over a little blood and black magic?}

\ta{\Shireyo! Move, damn it!}

No reaction. 

\tho{Oh, \Itzach. Pull yourself together, you pussy.}
\ta{You! Midget!} 
he yelled to the short \hr{Tepharin}{\Tepharin} soldier who was loitering near \Shireyo. 
\ta{Go and punch him.}
\tho{Maybe that'll knock him out of his reverie.}

The runt, whose name was something \Tepharin{} that Curwen couldn't be bothered to remember, went over and shoved \Shireyo. 
Albeit not as hard as Curwen would have liked. 
\ta{Hey, Carzain! You sleeping?} said the runt. 

\ta{Gwah...!} 
\Shireyo{} gave a start and stumbled two or three steps. 
He looked at the runt. 
Curwen could not see his face, but his body language looked dazzled, confused. 

\ta{You still with us?} asked the short man. 

\ta{Yeah... yeah. Sure.} \Shireyo{} mumbled. 

\ta{Damn you, \Shireyo!} yelled Curwen. 
\ta{Don't you fucking go daydreaming on me!
    Now move out!}

\ta{Yes, uh. Sorry, captain.}

\tho{%
  What a pussy. 
  Good thing I made sure to keep an eye on him before sending him to do anything important.}





\new
It had happened again. 
One minute Carzain had stood there taking in the feeling of the sorcerous residue that hung over Gilwaed. 
The next minute all sorts of images had flashed before his eyes: 
Dark voids where blind, shapeless horrors roamed shrieking. 
Lying dreaming in a sea of misty nothingness. 
Rainbow-coloured crystal castles. 
Armies tens of thousands strong, bearing standards that had been familiar but which he could now no longer recall. 
White, jewelled halls hundreds of yards across and pearly towers thousands of yards high. 
A cave of twisted vines and bulbs. 
Then the vast towers again, now blackened with ash and gore. 

And a voice had spoken. 
{\vizicar{Who am I?}} it had said. 
{\vizicar{Who am I really?}}

There had been an unwelcome feeling of exhilaration. 
A rush, as if a strong, cold wind was blowing through him. 

And there was the \dejavu. 
It had been there in \hs{Malcur}, too, the last time he had heard the voice in his head. 
Back then he had denied it. 
Refused to deal with it. 
Wishing it would go away on its own. 
But this time the feeling had been unmistakable. 
It was the same feeling as that day back in \hs{Heropond}. 

\tho{%
  \Iquin{} and \Itzach. 
  It's happening again. 
  What \emph{is} this?
  What is happening to me?
  I am going mad. 
  This can't go on.
  I can't handle this. 
  I need help. 
  
  But who? 
  
  Delph? \Tsekkect? 
  No. 
  They know nothing of magic. 
  They would not understand. 
  Delph would just tell me to go to a whore and forget my worries. 
  Or, failing that, masturbate like crazy. 
  I've tried the latter. 
  Didn't help. 
  
  Curwen? No. 
  He's expecting me to prove myself. 
  I can't come whining to him.
  That won't do.
  
  I could ask those \hs{Redcor} when we get back to the army. 
  But I don't know. 
  That \Esmerel{} woman is high-and-mighty enough to begin with. 
  I don't fancy crawling to her for help.
  
  Damn it.
  I am supposed to be a grown man. 
  But I wish my father or mother were here.
  Or that Imetrian, \hr{Ilcas}{Northstar}.
  Anyone.}

% As he walked towards his \relc, Carzain noticed a tightness in his trousers. 
% He looked down. 
% 
% \tho{%
%   Aw, crap. 
%   Now the smell of death and black magic is giving me a boner?
%   \Qliphoth. 
%   I really am going mad.}











\begin{comment}
\section{\Takestsha{}}
\end{comment}
\placestamp{%
  Rungeran army, east of Dendrum}
\begin{comment}
\Takestsha{} is sitting in a howdah on a great \mulgron. 
She is in the royal howdah that also carries the king. 
The rest of the \ishrah{} are on some other \mulgrons{} nearby. 

\Takestsha{} is sitting with the king. 
She knows he is having second thoughts about this alliance. 
She can read the horror in his eyes, the guilt over the gruesome, unnatural carnage their mages have wrought. 
\tho{This little king is not as strong as I hoped.}
She comforts him, convinces him that he is doing the right thing. 

She uses her sexuality. 
Morgan, of course, being king, can have any number of young and beautiful women he wants, but none of them have \Takestshaz{} power. 

Somehow she notices Archibald Curwen. Or maybe it's Carzain she notices because he does something stupid. 

Maybe Curwen-tachi are camping out in a new village, hoping the Rungerans will come by and destroy the village using their evil magic. 
Or maybe they are out in the \Wylde{} and she just notices them because that's how good she is. 

Or maybe Vizicar stirs awake for a moment, creating a \vertex{} spike that she picks up. 

In her most sexy voice, she tells the king she has discovered some troublemakers and needs to send soldiers out to whoop their butts. 
\end{comment}
\Takestsha{} reclined on her soft, padded seat atop the \mulgron{} howdah. 
She started to yawn, but moulded it into a breathy, feminine sigh. 

\tho{Must not break character.}

Through languid eyes she studied Morgan Runger, who sat on her right in a higher, more ornate seat. 
She did not like his expression: 
Frowing. 
Distant eyes. 
Beard-scratching. 
Even occasional mumbling. 
With her long experience of subtly manipulating others, \Takestsha{} needed but look at his face to read his thoughts almost word-for-word: 

\hypota{%
  What am I doing?
  \Daemons{} that feast on people's blood and souls... what is this evil I have unleashed?
  Is this right?
  Even for the sake of House Runger... can this be justified?}
  
He turned his eyes to the sky.

\tho{%
  Praying to the \quo{Light} for forgiveness?} she thought. 
\tho{%
  We cannot have that.}

She reached up and laid a slim hand on his knee.
\ta{What ails you, my king?} she purred. 

Morgan glanced down at her and forced a smile. 
\ta{Nothing, my dear.} 
He patted her hand. 
\ta{Nothing that needs worry you.}

\Takestsha{} responded with what she hoped was a sweet and innocent smile. 
\tho{%
  Hah. 
  Men. 
  Patronizing as usual. 
  He knows I am the most powerful member of this entire army, yet he still sees me as merely a woman.
  A frail and delicate thing that must be protected by strong men.
  Even more incredibly, he is pondering the consequences of \emph{my} work, and he still tries to shelter me from it. 
  As if I were a child who knew no better. 
  
  A child who knows no better. 
  Come to think of it, one might say that is how the \humans{} view all their women.}

She almost laughed inside at Morgan's foolishness. 
But that would be unfair to him, she reminded herself. 
After all, she had spent the better part of a year goading him into this. 
Morgan was as intelligent as any \human, and seducing him had not been altogether easy. 
As a king he had access to any number of beautiful women. 
But none of them had her special talents, and in the end, what \human{} could resist her wiles?

The king had resumed his brooding. 
Sitting there, hunched over, lost in thought and fingering his long, once-black but now graying beard, he looked like a very old man. 

\tho{%
  He is still at it. 
  Seems I will have to resort to stronger means.}

\Takestsha{} had made sure to have her seat placed immediately next to the king's for this exact reason. 
Now she inched to the edge of her chair and took his hand in both of hers. 
The gnarled hand looked very large in hers, for Morgan Runger was a tall man\dash or had been, in his prime\dash and her assumed form was petite, just like the men liked it. 

\ta{My great, noble king,} she crooned, almost whispered. 
She took one of his fingers in her mouth and gently sucked on it, all the while keeping eye contact. 
Lust and pride were two easy channels into a man's mind. 
\ta{Something troubles you. 
    Confide in me.}

Morgan sighed. 
\ta{%
  I am worried about this sorcery. 
  These \daemons.
  It all seems... evil.
  Dangerous.}

She kissed the tips of his five fingers, one by one. 
\ta{Fear not, my king. And have faith.}
She giggled. 
\ta{In me.}
Her eyes and smile hinted at other things that might happen \quo{in her} tonight. 
\tho{Let him chew on that.}

\ta{Faith...} he mumbled, while idly running his hand down her soft cheek. 
\ta{But the Light...}

\ta{%
  Remember, my king, your aim was to free yourself from the Redcor and their narrow-minded religion. 
  The ones preaching about the \quo{will} of the Light are power-hungry priests and Vaimons. 
  You must not be ensnared by their words and... intolerance.}
While she spoke, she guided his hand down along her neck and through her cleavage. 
\tho{%
  Remember, Morgan. 
  From sexual open-mindedness it is no great leap to religious open-mindedness.
  And from there it is no great leap to soul-devouring black magic.}
She giggled at her own unspoken joke and shyly averted her eyes. 
But she allowed his fingers to rest between her breasts. 
\tho{Must not appear too sexually aggressive. They pick up on that.}

\ta{Yes...} he said. 

\ta{After all, it is for the sake of House Runger,} she reminded him. 

\ta{Yes. You are right, my dear.} 
He stroked the inside of her cleavage with his thumb and smiled condescendingly. 

Again she giggled, but this time she pulled his hand away. 
\tho{%
  No more free gifts for you. 
  If you want more, be a good little king and do as I say.}

As she turned away, she noticed \Jirad{} Tantor ogling her from the howdah of another \mulgron. 

\tho{Oh, no. Not again.}

In retrospect, having sex with Tantor might have been a bad idea. 
It had seemed worthwhile at the time. 
First, the old mage's grief over his son's death had touched a soft spot in her. 
Second, it seemed a convenient way to help secure the \ishrahz{} loyalty to her. 
And third, while Tantor was certainly no great lover, sex was still more enjoyable than twiddling her thumbs. 
But since then Tantor had grown awfully needy. 
\tho{Maybe I should sleep with him just to shut him up.}

Then a jolt of energy went through her. 

She sat up. 

\tho{%
  What was that?
  
  A \vertex{} spike. 
  Nearby.}

She reached out and concentrated on tracing the signal. 

\tho{%
  Through some \Wylde{}. 
  But not far from the road. 
  North. 
  No. 
  East. 
  Northeast. 
  Near that village, Gilwaed. 
  
  And judging by the feel of it, it might be the same source as the one detected somewhere in Pelidor two years ago. 
  The one I was warned of. 
  
  It is gone now. 
  I cannot trace it. 
  
  But I will keep my eye on you, little \vertex. 
  Be certain of that.}
% \end{garbage}

\begin{comment}
\chapter{New version}
\end{comment}









