\bookchapter{The Bleeding Wood}

\begin{garbage}
\begin{comment}
\section{Carzain}
\end{comment}

\begin{comment}
\subsection{They meet the army}
\end{comment}

\stamp
  {\dateCarzainReturnsToForklin}
  {\hs{Ucarn Road}, east of \hr{Forklin}{\Forklin}}

\ta{Look!} said Egian. 
\ta{Banners! It's the main army! We've made it! We're back!} 

\Tsekkect{} craned her neck and looked at the horizon. 
Squinted. 
And there it was. 
On a faraway hill he could dimly see some things that might be banners. 
Something that might be light glinting off metal. 

\ta{Good,} grumbled Curwen. 
\ta{About damned time, too.} 

\ta{Not bad, huh?} said \Tsekkect{} to her friends. 
\ta{We're almost back to civilization.}

\ta{And thank the \sephiroth{} for that,} said Carzain, on his \relc{} next to him. 
\ta{I'm sick of the \Wylde{}. 
  I'm sick of this party. 
  I need to get myself some tail, and badly.}

\ta{You said it, bro,} said Delph.  
\ta{Mmm. I can already smell the nice whores.
  And it smells fishy\prikker} 






\begin{comment}
\subsection{They ogle women}
\end{comment}

\placestamp
  {Pelidorian army camp, east of \hr{Forklin}{\Forklin}}

\ta{Ah,} said Delph, patting his belly as they walked. 
\ta{It was good to finally get some real food.
  That stuff they fed us on the sally was an insult to any honest man's stomach.}

\ta{You're one to talk,} said \Tsekkect. 
\ta{At least those rations were made for your \emph{race}.
  You have any idea how inedible the stuff was for me?
  I'm a \meccaran; I need real meat.
  Not those bread and crackers and disgusting shit they fed us with.}

\ta{You said it, girl. Good to be back, eh?}

\ta{By \hs{Lweddish}, yes.} 
She rubbed her arms. 
\ta{My wounds are even starting to look decent again.}
\tho{Still hurts, though,} she thought. 
Carzain had did what he could to heal her wounds on the trip, but she was \meccaran{}, and he did not quite know how to deal with that, so he had managed only an imperfect treatment. 
\tho{Guess it's up to my own regeneration to patch up the rest.} 

\ta{You still owe me, though, 'Zain,} she said, poking his side with her foot. 

\ta{Yeah, yeah,} said Carzain. 
\ta{I'll pull you out of the next fire. 
  Shame you're not \human, though.
  Then I could repay you with sexual favours.}

\ta{Pfft. You wish.}

\ta{Yes. I do.}

\ta{And what makes you think I'd go for you even if you were a \meccaran?
  If you were I bet you'd have some really small\prikker}

\ta{All right, that's enough of that!} Delph interrupted. 
\ta{You guys are making me picture things I do \emph{not} want to picture.}

\ta{What was that, Delph?} 
\Tsekkect{} poked him. 
\ta{You want a description of a \meccaran{} sex orgy?}

\ta{No!}

\ta{Well, first you need a nice pond. 
  Then all the females get in the pond, and the males\prikker}

\ta{Knock it off, damn you!} Delph laughed. 
\ta{If it doesn't have breasts, I don't want to picture it naked.
  Ooo, speaking of which\prikker}
He turned his head to watch a passing woman. 
\ta{%
  Now \emph{that}, on the other hand, is what I \emph{do} want to picture naked.
  And boy, am I picturing\prikker}

\Tsekkect{} and Carzain followed Delph's eyes and studied the object of his picturing. 

\ta{Hm,} said Carzain.
\ta{Not bad. But nah. 
  Too tall and thin. 
  Too flat-chested.
  And the hair \colour reminds me too much of my mother.}

\ta{Interesting,} said Delph. 
\ta{Now I'm picturing your mother naked.}

\ta{Well, don't.} 
Carzain gave Delph a joking whap against the back of his head. 

\ta{Anyway,} said Delph, 
\ta{there's no such thing as \quo{too tall}.
  My dream girl has to be twice as tall as me.
  Hehe.
  I want to be able to go down on her without having to go down.}

\ta{Lweddish,} \Tsekkect{} cursed, laughing.
\ta{That gives me all sorts of weird images in my head.}
She remembered the last sexual orgy she had participated in. 
Interesting things had happened\prikker

\ta{And don't you dare tell me about them!} said Delph.
\ta{I'm still trying to get rid of the last batch of your \quo{images}.
  C'mon, guys! Off to the whore tents!}

\ta{I'm still not keen on the whore business,} said Carzain
\ta{%.
  But somewhere in that big army camp surely there's got to be an honest camp follower I can seduce.
  After all, we have additional heroic experience to draw on now.
  It's got to be possible.}

\ta{Yeah, go get 'em, boys,} said \Tsekkect. 
\ta{As for me, I heard the army has enlisted some more \meccara.
  I'm going to seek them out.} 

\tho{With luck, there'll be sex involved. 
  There probably will.}
 
\end{garbage}













\begin{comment}
\section{Needle and Rian}
\end{comment}

\stamp
  {\dateRianSeesRaid}
  {Southern slums, \hr{Malcur}{\Malcur}\\
   Evening}

\begin{comment}
\subsection{Needle}
\end{comment}
\new
% Needle arrives with her Cabalists. 
% They encircle the Sentinel hideout and sneak up on the Sentinels and their Black Plague lackeys. 
Needle peered out from behind a beam and studied the big, flat building. 
\tho{So this is the Sentinel hideout?}

\ta{Look,} said her lackey next to her. 
He pointed to a cowled \dax{} who stood just outside the building. 
\ta{There is one of their sorcerers.}

\ta{That one? Hm.}
\tho{Such luck.}
According to intelligence, there was another mage present here as well. 
\tho{With a bit more luck we should be able to kill both.
  And a bunch of their Black Plague minions as well.}

\tho{But to do that we will need the \grimrats.}
Needle took a deep breath, then began quietly reciting an \hs{orison} \Achsah{} had taught her to control the \grimrats.
All the while she made sure to stare intently at the mage. 

As she spoke the words she could feel her mind reach out to the \banerats. 
Could feel their disgusting, bestial minds touching hers. 
Could almost feel their clammy paws on her skin. 
It made her shudder. 
\tho{Stop that, Needle,} she scolded herself. 
\tho{Mustn't show weakness in front of the men.
  Get the job done.}
She mentally imprinted on the \banerats{} the identity of their primary target (the Sentinel sorcerer) and their secondary targets (the Black Plague bandits). 
At least, she hoped that was what she was doing. 
\tho{I hope I am doing this orison right.}

\ta{Are our men in position?} she asked. 

\ta{Yes, mistress,} said her lackey.
\ta{We have the bastards surrounded.}

\ta{Good.} 
Needle looked around. 
When she looked carefully she could make out a few of the men. 
They were armed with bows, not guns, since this attack was supposed to be stealthy. 
\ta{Commence the attack on my signal. 
  Do your best to take out the mage.}

Her assistant hesitated. 
\ta{But, mistress\prikker what if he strikes back at us with magic?}

\ta{Don't worry about it. 
  If you can't easily take the mages out, I have backup to deal with them.} 

From under her bodice she pulled out the small flute that \Achsah{} also gave her, to use to command the \hr{Grimrat}{\grimrats}. 
As far as Needle understood it, it produced some magical sounds that only the \grimrats{} could hear. 
The flute was much faster and easier to use than the complicated orison, but it could only convey very simple commands, such as \quo{attack!} or \quo{retreat!}. 

The thought of the \grimrats{} still scared her. 
She took another breath. 
Put the flute in her mouth. 
\tho{Here goes.}

She blew on the flute, piping the \quo{attack} signal. 

No sound that she could hear.
\tho{I can only hope this works.}

\ta{Now!} she said to her assistant. 
\ta{Signal the attack!}

\ta{Yes, mistress.}
The assistant gestured to the other groups of Cabal minions stationed around on rooftops and in alleys. 

\tho{It begins.}

\begin{comment}
\subsection{Rian sees raid begin}
\end{comment}
\new
% Rian sneaks back to a place near the one he was last time. 
% He spies on some Sentinel-employed thieves and their evil talk. 
\tho{Nothing seems to be happening today,} thought Rian. 
\tho{Maybe it was a mistake to come here again.
  Maybe it's not worth the risk. 
  But it's the best thing I can think of.}

He was afraid of the Black Plague hideout. 
He did not want to come back here. 
The black magic scared him. 
Witnessing the evil ritual had shaken his faith in the all-powerful, all-loving Light. 
But weakness of faith was a sin, he knew. 
So he had visited a church and prayed. 
A lot. 
For guidance, and for protection. 

He even gave a gift to the church: 
A small figure he had been carving for practice. 
Thinking of the figure made him smile. 
It was a woman in a dress, wooden and as long as his hand was wide. 
It was a good carving, he thought. 
He had tried to make it look like Neina. 
Originally he had wanted to give it to her. 
But first he needed to get Neina back. 
And to get her back he needed the Light's favour. 
\tho{%
  And while the Light's love comes to all who believe and obey, the Light's favour is only given to those who are willing to sacrifice something.
  Something important.}
So in the end he had decided to give the figure to the \sephiroth. 
It was not much, but it was a thing that meant something to him. 
He hoped they would be happy for the gift and see fit to bless him in return. 
\tho{%
  Light knows, I'll need their blessing if I'm to have any chance against the Black Plague and their evil magic.} 

So now he was here again. 
Scary as the place may be, it was his best lead. 
\tho{%
  The plaguers have my Neina.
  They must have. 
  If I spy on them enough, sooner or later they must lead me to her.}
He had been here a few more times since the day he witnessed the ritual.
He had not seen any magic since, but he also had not been as bold. 
He had been more careful and kept in the background, not venturing forth to peek into holes. 
He had caught sight of the sorceress a few times, though, and also a \dax{} who carried the title of \quo{sorcerer}.
% He almost got caught once, but he had been relatively lucky. 

He had found a hut nearby with an abandoned attic where he had been able to hide out. 
It was cramped, and he could not see much from in here, but he could hear pretty well, and it was relatively safe. 
There were some small peek-holes between the boards that allowed a minimum of visibility. 
\tho{Shoddy carpentry,} he could tell with his carpenter training. 

Voices could be heard in the street below. 
Rian dared to crawl our of his shelter and up on the roof for a better look. 
He could see the male sorcerer was out and looking around. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Note to self: If I introduce guns, then these guys should still be wielding bows. Bows are stealthier. Guns are noisy. Needle should mention this in the section above
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Then arrows came flying out of the blue. 

\emph{Zip! Zip!}

A plaguer took a hit in the shoulder and went down, possibly dead or dying. 
Another arrow almost struck the sorcerer. 

\ta{An attack!} someone shouted. 

The sorcerer quickly retreated into the Black Plague building, shouting orders left and right. 

Rian's self-preservation instincts took over. 
He pressed himself flat against the roof. 
\tho{Shit! A big fight!
  I've got to get out of here!
  Creep back down in the attic?
  No. 
  No good. 
  It's hard to escape from in there.
  If someone's seen me and comes in after me, I'm cornered.
  
  Who are the attackers?
  City guards? 
  I doubt it.
  I've never seen the guards do raids like this.
  Another thieves' guild? 
  More likely.
  Or another Plague fraction.
  Anywho, I'd best assume both sides are bad guys.
  Which means I don't want to get caught in the crossfire.
  
  How do I get out of here?
  
  I'll keep still here and hope they haven't seen me.
  At this point, running away would only incite them to chase me.}

So he lay still. 
He was close to the edge, so he could see a little bit from where he lay. 

A shape darted across the street and into the plaguer hideout. 

\tho{What was that?

  It was no humanoid. 
  An animal? 
  A dog? 
  It was about the right length, but a bit too thick.
  Dogs around here are thinner than that. 
  A trained attack dog? 
  Could be\prikker} 

Another shape ran past below. 

\tho{There was another!

  It looked weird. 
  Sort of\prikker shadowy.
  What is going on here?
  More evil magic?
  \Iquin{} protect me\prikker}

He looked around. 
Noticed a thug on a neighbouring roof. 
\tho{Oh, crap. That guy has seen me. Run.}

He pushed away at the roof and let himself roll down. 
Flopped onto the street. 
Then ran. 
Around him, people were fighting. 
Some lashed out at him, but he managed to slip through the confusion. 

He ran through some streets. 
Turned left at a corner. 
Looked around. 
\tho{Where am I now?
  I'm behind the big plaguer hideout.
  
  I shouldn't be here. 
  Run away!
  
  No. 
  I'm here to spy on them. 
  I don't know what's going on, but I have to find out. 
  That's what I'm here for.
  I owe it to Neina to not just run.} 

Violent noises could be heard from within: 
Shouts.
Screams.
Crackling of fire.
Clashing of weapons. 
A bit further along the wall was a window. 
\tho{There.}

He snuck up to the window. 
Peeked in. 

\begin{comment}
\subsection{Rian sees mages die}
\end{comment}

And saw a great big \melee. 
All sorts of figures fighting and killing each other. 
It looked like one big chaos to Rian. 
He could not tell the sides apart. 
\tho{Who's killing whom, and why?}

The two mages were there, both chanting spellwords and waving their styli. 

Near the far door stood a thin woman with dark brown hair and a small thing in her mouth.
\tho{A flute?} 
She stood back from the fighting; apparently some sort of leader. 

And then there were some \emph{things}. 
Small, dog-like. 
Brown and yellow in \colour. 
Running on four legs\prikker or so he thought. 
It was hard to get a good look at them as they hopped around, lightning-fast, slashing at people with their claws and teeth. 
\tho{Light. What are those? They must be the shapes I saw before.}

Some of the dog-things had gotten close to the plaguer sorceress. 
Some bandits stood around her, protecting her. 
She was frantically waving her arms and reciting occult words. 

A dog-thing leapt. 
A bandit went down. 

\ta{\foreign{\prikker nedus zodagnin\prikker ktheffruin!}} the sorceress shouted, swinging her stylus. 
There was a whooshing, ripping noise, like an invisible wave. 
One of the dog-things collapsed on the ground, writhing; evidently caught by a spell. 

Another of the beasts came from her flank. 
It leapt through an opening among her defenders. 
Straight at the sorceress' face. 
She turned to face it. 
It landed on her face, slashing and biting. 
She went down, shrieking. 

More dog-things jumped her. 
No. 
Not dogs.
More like rats. 
Huge, long-legged rats. 
There were at least five of them in all. 
Perhaps more. 

Blood sprayed. 
Intestines were ripped loose. 

The male sorcerer, seeing his colleague's grisly death, turned tail and ran, carrying a book and several scrolls under his arm. 
He ran for the big window where Rian was lurking. 

\tho{Crap!} 

Rian quickly retreated from the window. 
Ran back along the wall where he came from. 
Turned right around the first corner. 
Behind him he heard an \ta{oomph!}. 
Crouching behind the corner, turns to look. 

The sorcerer climbed to his feet after a clumsy fall. 
He ran. 
Vanished behind a corner. 

Monsters came out of the window. 
They chased after the sorcerer. 

\tho{\Sephiroth{} preserve me! What are those things?}

\begin{comment}
\subsection{Rian chased by \grimrat}
\end{comment}

An indistinct shadow moved in the left corner of his eye. 
Rian turned. 
From the other side of the building a thing came leaping. 
Rian reacted quickly and rolled out of its way. 
It landed next to him. 

It was one of the rat- or dog-things. 

For what seems like a long moment, he just stared at the it. 
It had a muscular body and a cone-shaped muzzle. 
Not four legs, but five: Three forelegs and two hindlegs. 
It had two eyes\prikker or did it?
They did not look like normal eyes. 
They were pale gray and bulged out. 
Wobbling. 
Writhing. 
Like short tentacles. 
As if those eyes wanted to reach out and \emph{feel} rather than see him. 

Its smell was repulsive. 
Dusty. 
Musky. 
Moldy. 

For a moment he lay paralyzed with the shock of the thing. 
But then his instincts took over again. 
He jumped to his feet and ran. 
The monster followed. 
He ran faster. 

\tho{\Sephiroth, help me now! 
  Oh, Silqua, there's an evil monster right on my heels!
  If there was ever a time I needed you help, that time is now!}
He glanced back. 
Saw the beast in hot pursuit. 

He passed some streets and corners. 
\tho{I don't know where I am. Got to find somewhere I can cut it off.}

He jumped up on a barrel. 
Onto a balcony. 
Saw an open door. 
Ran through it. 
Slammed it behind him. 
Grabbed the handle and pulled, holding the door shut. 

Something beat against the door. 
He heard the scratching of claws. 
Smelled the scent of mold. 
With his heart pounding, he hung on to the door handle. 
\tho{Must not let it get through! If that thing catches me I'm dead!}

Moments passed. 

He heard sniffing. 

More moments passed. 

The thing pawed at a board. 

\tho{Silqua, don't let the board be loose!}

Even more moments passed. 

Silence. 

\tho{What's it doing now?}

Then, finally, clacking claws moving away. 

\tho{It's given up. I hope.}
Rian breathed a deep sigh of relief. 
He dared relax a little bit, but still held on to the handle. 
He looked around. 

\begin{comment}
\subsection{Rian sees living building}
\end{comment}

% Already early on, during the preparations for the great summoning of \Nithd{}, some people have begun degenerating into mutants, or living buildings. 
% 
% Rian discovers a building that has living humanoids magically merged into the foundation. 
% Compare this to Bootstrap Bill or Wyvern, who are becoming part of the \shipname{Flying Dutchman} in the \emph{Pirates of the Caribbean movies}.

\tho{Where am I?

  Some random house. 
  
  Should I get out of here?

  No. 
  I'm on a spying mission, remember. 
  Now that I'm here, I might as well look around.}

Rian snooped around. 
Passed through another door. 
Then froze. 
There was a humanoid sitting by a wall. 

\tho{Crap!} 
He retreated back behind the door. 
Held his breath. 
Was silent. 

No sound. 
Nothing at all. 
\tho{Come to think of it, that figure looked weird.}
Curiosity got the better of him. 
He peeked. 

The figure was a \sphyle. 
It did look weird. 
The scales were dis\coloured and brown. 
Misshapen and gnarly, too. 
She did not move at all. 
\tho{Is she asleep?} 
He moved in for a closer look. 

\emph{Crack!}

Rian's foot broke through a rotten floorboard. 
He yelped and fell. 
His foot touched something soft. 
And wet. 

He landed on the floor right next to the sitting \sphyle. 
She did not react, despite the loud crack, yelp and thump. 
Rian looked at her. 
She still did not move. 
\tho{She smells nasty, too. 
  Is she dead?} 
He looked closer. 
\tho{No\prikker she breathes. 
  She's alive.
  Is she asleep?
  Or has she been smoking weed?}

She did not smell of weed. 
Rian had a good sense of smell, owing to his many nightly excursions in his thieving days, but he could not her smell the \sphyle{} at all. 
There was a strong smell of dank wood that drowned her out. 
And a bitter, metallic smell coming from the hole. 
  
\tho{At any rate, looks like I'm pretty safe.}

He pulled his foot out of the hole and looked down at it. 
It was covered in some dark red stuff. 
\tho{What's this goo?}
He touched it with a finger and smelled it. 
\tho{Blood? What in \Itzach\prikker?} 

He crawled over to the hole in the floor. 
Cockroaches and other vermin crept out of it. 
He looked down. 
\tho{What is that down there? 
  Looks like\prikker flesh?}

Traumatic memories flashed through his head. 
He shuddered to recall the black magic ritual. 
The \human{} sacrifices. 
The ghastly transformation of the house. 
The dead flesh. 
Pulsing with stolen blood. 

But he had to make sure. 
Slowly, he reached down into hole with his hand. 
Touched the inside, first with one finger. 
Then with two fingers. 
It was soft and moist. 
He felt with a palm. 
Pushed. 
\tho{Oh, \Iquin! It \emph{is} flesh! It's alive! And it bleeds! 
  That's what the metallic smell was. 
  Blood! 
  
  What madness is this?
  
  What \emph{evil} is this?}

Rian's indignation at the sight of this atrocity overcame his caution. 
\tho{This is wrong!}
He went over to the sleeping \sphyle. 
\ta{Hey, you! What's going on here?}
He grabbed her shoulders and shook her.

Or tried to. 
She was stuck. 
Stuck to the wall. 

\ta{Hey! You!} 
He grabbed her arm and pulled. 
It would not come free of the floor. 
It was as if rooted. 
He bent down and looked closer. 

\tho{By \hs{Silqua} and the \Sephiroth! 
  It \emph{is} rooted!}
Her arm had merged into the wood. 
They were somehow merging into each other. 
The wood was becoming fleshy, and her flesh was becoming woody! 
\tho{%
  That's why I couldn't recognize her smell. 
  She smells like wood! 
  Like half flesh and half wood!} 
In some places, he noticed, she had open wounds from which oozed some sticky thing that might be blood or sap. 
He did not want to touch it and find out. 

He backed away in horror. 
Stumbled. 
Made some noise. 
Almost fell. 

The \ps{\sphyle} eyes opened. 
They looked at him. 
Still lidded. 
Sleepy. 

\ta{Wh-wh-what are you? What's wrong with you?} he stammered. 

She opened her mouth. 
Tried to speak. 
Only a dry, rough gargle came out. 

Rian backed away, shaking his head, until his back was against the wall. 

The \sphyle{} moved her fingers. 
Her limbs twitched. 
As if trying to stand up. 
She could not. 

She opened her mouth again. 
More inarticulate gargling. 

Rian could stand no more. 
He darted for the door and ran into the night. 









