
\bookchapter{\Forklin}

\begin{comment}
  \subsection{Carzain rides to \Forclin}
\end{comment}
\stamp{\dateCarzainReturnsToForklin}
  {Heath east of \maybehr{Forclin}{\Forclin}, Pelidor}
Carzain \Shachar rode over heaths and plains where grazed herds of giant \saurians, each as heavy as a thousand men. 
Finally, as he crossed a hill, the walls of \Forclin came into view. 

It was Carzain's first visit to \Forclin. 
\Forklin was one of the largest and mightiest cities in Pelidor, rivalling Malcur in splendour. 
Indeed, before the rise of the unified duchy of Pelidor, \Forklin{} had been the capital of an independent city-state, a rival of Malcur. 
Where Malcur was dominated by bright colours\dash white, ochre, yellow and azure\dash the walls and towers of \Forklin were much darker, painted in black and twilight gray and sapphire blue. 
The city wall was ringed with battlements and adorned with murder holes and crawling gargoyles. 
The tower tops were jagged as if beset with horns or teeth. 
In all, \Forklin conveyed an impression of barbaric, martial might; so strong, cold and hard that it made regal Malcur look almost foppish in comparison. 

\vizicar{It is \Ortaican-built, this city,} said Vizicar.
\vizicar{I recognize the style. 
  But there are differences.
  The city is newer than my time.}
The city must date from the days of the \Ortaican \bacconate, which did not arise until after the fall of the \VaimonCaliphate, generations after Vizicar's reign. 

\vizicar{Some parts are later, Vaimon-built additions.
  Look at those minarets rising up in the northern end.
  Do you see how out-of-place they look?}

\tho{Not as out-of-place as that spindly tower there,} thought Carzain. 

Somewhere behind the eastern wall there arose a high, lone tower. 
Its stones were a paler gray than most of the rest, and it looked skewed and twisted. 
It was one of the taller towers in the city, but its slim top was obscured by mist, making it impossible to determine its exact height. 

Carzain studied the tower as he neared the city. 
It had an air of occult age about it, as if built by elder things from another world. 

\tho{Some sorcerer's abode, I would guess. 
  I must investigate later.}









\begin{comment}
  \subsection{Carzain meets Curwen}
\end{comment}
\placestamp{\Ishrah quarters, \Forclin}
There was a knock on Archibald Curwen's door. 

\ta{Lord Curwen?} said a voice outside. 

\ta{What?} barked Curwen. 

\ta{There is a \human outside demanding to see you, sir.
  Says his name is \CarzainShireyo.}

This made Curwen rise halfway from his chair.
\tho{\Shireyo? Here? Now? What could have brought him here? 
  I haven't seen him in, what, ten years?}
He rose and opened the door. 

\ta{Very well. Take me to him.}

The soldier led Curwen to the eastern gate, where he found a man astride a gray-green \relc surrounded by several soldiers. 
The man was in his mid-thirties, had long black hair and wore black and brown \travelling leathers. 
The man had changed much since Curwen last saw him, but Curwen immediately recognized Carzain \Shachar. 
\Shachar had fought in the army under Curwen's command many years ago, before he left to travel the land as a freelance mercenary and adventurer. 
When they last worked together, \Shachar had been a talented young man, but rash and even unstable. 
Curwen was interested to see what he had made of himself since then. 

\ta{Lord Curwen,} said the leader of the soldiers in an apologetic tone.
\ta{He insisted we let him in, said he knew you, sir.}

\ta{\Mr Curwen!} \Shachar called out. 
It was the sort of irreverence Curwen had come to expect from him, though he would not have accepted it from anyone but a noble or a fellow mage. 
\ta{How good of you to come and see me.} 

\Shachar sprang down from his \relc and approached, with an air of such confidence that the soldiers instinctively drew back to let him pass. 

Curwen went to meet him and grabbed his hand.
\ta{\MrShireyo. 
  It's been a while.
  I see you have grown.}

\ta{Heh.} 
\Shachar darted a glance at Curwen's sizable belly. 
\ta{No comments.} 

Curwen looked up and down \Shachar. 
He stood an inch shorter than Curwen and many pounds lighter, but he was not the slim reed of a youth he once was. 
Back then Curwen could easily have bent the younger man in half. 
Nowadays he doubted he could best \Shachar in physical combat if he tried. 
Curwen was not getting any younger. 

\Shachar's skin was dark enough that one might call him a \demihuman. 
His heritage might be less than wholesome, but he had proven himself worthy enough that Curwen\dash himself a purebred \trueman\dash would give him the benefit of the doubt in that regard.

% Carzain was still mostly clean-shaven, and also retained his long, thick mane of black hair. 
% Curwen envies him that. 
% He never minded when his own hair and beard started to go gray. 
% Gray suits him.
% But these last years his hair has been thinning, and Curwen is not happy about that. 

\ta{So, what brings you here?} said Curwen. 

\ta{I heard Morgan Runger was invading.}
\Shachar grinned.
\ta{%
  I had a lengthy debate with myself over which side to pick, but eventually I decided to go with my homeland.
  So I come to offer my aid to the Pelidorian \ishrah.}

\ta{So you're back under my command?}

\ta{Well\prikker we can negotiate the exact terms later. 
  But more importantly, I took the liberty of doing some reconnaisance.
  I have been able to spy on Runger's army, and I have learned things that will interest you.}

\tho{\Qliphoth!} thought Curwen.
\tho{This I need to hear.
  He might know something that can help me piece together the puzzle of Tantor's journal.}

\ta{Splendid, \MrShireyo.}
He grabbed \Shachar's shoulder and began pulling him back towards the \ishrah quarters.
\ta{Why don't you come inside and tell me about it?}





\begin{comment}
  \subsection{Carzain tells Curwen news}
\end{comment}
\placestamp{\Ishrah quarters, \Forclin}
\Shachar took a long gulp of one of Curwen's expensive wines and looked Curwen in the eye from across the supper table.

\ta{You do not seem as surprised by this news as I had expected, \Mr Curwen.}

\ta{I have my sources of intelligence,} said Curwen. 
\ta{But your information is quite useful nonetheless. 
  Well done, \Mr \Shachar.}

Curwen sat back and sucked on his pipe as he digested both the food and the information. 
\tho{So. 
  A beautiful woman in charge of Runger's \ishrah.
  And some destructive, non-Vaimon magic that lays waste to towns.
  Deeper, darker, more destructive than anything a regular \ishrah ought to possess, \Shachar said. 
  
  This confirms my fears.
  I now have good reason to believe that Tantor's account is true.
  Whatever the power of \EreshKal is, it is real. 
  And \Takestsha is real.} 
The thought of the woman made Curwen nervous. 
A woman who could walk in and take control of a king's \ishrah was a force not to be underestimated.

\ta{Moreover, the Rungerans have made better speed than we had hoped. 
  They have made it far west into Pelidor already. 
  I still don't know how powerful their magic is, but I have reason to suspect the worst.
  It'll be too dangerous to engage the Rungerans on the open field.
  We should stay in \Forclin and force them to lay siege.}

At length, Curwen rose from the table. 
\ta{Good work, \Mr \Shachar. 
  I need to go and present our combined findings to the Marshal's council.}

\ta{Very good,} said \Shachar. 
\ta{I plan to go and explore the city here.
  But first I need a good rest.
  Whom do I need to badger to get some quarters?}





\begin{comment}
  \subsection{War room}
\end{comment}

\placestamp
  {War room, Pelidorian army camp}

\ta{The Rungerans are advancing faster than we expected,} Curwen was explaining. 
\ta{At this rate they will surely reach Dendrum before we do.
  If they have not already.}

\ta{Then we will have to move faster,} said Sethgal Pelidor. 

\tho{I will not abandon Dendrum for no good reason,} thought Sethgal. 
It had been his plan from the beginning to reinforce the fortress city of Dendrum in eastern Pelidor and hold it against the Rungerans. 

\ta{We can't move fast enough,} said Curwen. 
\ta{Look here, \maybehs{Marshal}.}
He pointed to the map. 
\ta{They were \emph{here} five days ago. 
  We are \emph{here}.
  There is no way we can overtake them.}

\ta{I must agree with Lord Curwen,} said \Dornaer. 
\ta{%
  Given this information it must be clear that we cannot reach Dendrum before the Rungerans.
  We will have to rethink our strategy.}

\tho{Shit,} thought Sethgal. 
\tho{It is as the saying goes. 
  No plan survives the encounter with the enemy.
  And we have not even encountered the enemy yet.}
\ta{What would you recommend, then?
  Lord Curwen, what is your impression regarding the strength of the Rungeran army?
  How do you estimate our chances against them on an open battlefield?}

\ta{Our chances are not good, sir.
  Estimates suggest they may have as much as twice our number of men.
  And according to my newest intelligence, they command a type of obscure and powerful magic.}

\ta{I am reluctanct to yield eastern Pelidor,} said Sethgal. 

\ta{The Rungerans have not been reluctant to claim it,} said \Dornaer. 
\ta{I fear that choice has been taken out of our hands.
  We cannot simply march on them and rout them.}

\ta{I agree,} said Curwen.
\ta{If we are to face their superior numbers \emph{and} their unknown magic, we need to do so from a position of strength.}

\ta{That is true, assuming your intelligence holds.}
Sethgal studied the map. 
\ta{We will need a city in which to make our stand.} 

\ta{Our best choice is\prikker} Curwen began. 

\ta{\Forklin,} Sethgal interrupted him. 
\ta{Here where we are.}
\tho{I know. 
  Don't try to take over control of the discussion, Curwen.} 

\ta{Yes, sir,} said Curwen.
\ta{It is our best bet. 
  \Forklin{} is strong. 
  It can be fortified.}

% \ta{That may be,} said \Dornaer, 
% \ta{but I fear}

Sethgal still hesitated. 
\tho{I do not want to cede any part of the country. 
  I need to win this war, \Itzach{} damn it.
  My \rayuthship depends on it. 
  I need to prove my worth so the rest of the House has no choice but to make me \rayuth.
  Holing up in \Forklin{} and letting Morgan Runger occupy all eastern Pelidor is hardly heroic.}

And there was another reason for his reluctance, one he was less happy to admit to himself. 
\tho{I don't like Curwen.
  I don't want to dance to his tune.
  That damn mage is always trying to worm his way into the court. 
  Trying to run things behind the back of the House.
  I have noticed the way he uses the soldiers to do his own covert work when he thinks I'm not looking. 
  
  You may be the son of some obscure nobleman in Belek, but you are not part of Pelidorian nobility. 
  You should not be sticking your nose in politics that don't concern you. 
  You should stick to your magic and leave the government of Pelidor to the Pelidorians.
  
  I don't know what you are after. 
  I suppose you are just an ambitious man who wants to gobble up political power and influence.
  Or perhaps you are bitter and hungry because you tasted power growing up as a noble but could not inherit your father's throne.}
Curwen was, after all, a younger son, and Sethgal knew it was tradition in Belek for the eldest son to inherit the family title and estate. 
This practice seemed foolish to him. 
\tho{%
  Why not choose the most able person, like we do here in Pelidor? 
  
  Or, at least, like we ought to do. 
  If House Pelidor had truly selected the best person for the job, then I would be \rayuth now.
  Electing \Icor{} instead of me was a mistake. 
  I have to make the House see that.%
}

\tho{Are you like me, Curwen? 
  Longing for the recognition you feel you deserve?}
For a brief moment he felt a sort of kinship with the mage. 

\ta{Marshal Sethgal?} asked \Dornaer. 
\ta{What shall we do?}

Sethgal stood up. 
\ta{I must agree with Lord Curwen's proposition.
  With the intelligence we have, the best course of action is to stay and fortify \Forklin.
  Sirs, issue the orders.}

Thinking about Curwen's situation had opened Sethgal's eyes a bit. 
\tho{I must not let myself be governed by stupid indignation. 
  I must be rational and do the smart thing. 
  Do what is right for our country.
  Otherwise I am not worthy to be Marshal, much less \rayuth.
  
  I will win this war. 
  I will be \rayuth. 
  I must.
  Pelidor needs a strong ruler.
  
  Besides, someone must relieve poor \Tiroco\prikker}








\begin{comment}
  \subsection{Carzain sees Morbus but not Tower}
\end{comment}
\placestamp{Streets of \Forclin}
\vizicar{I wonder why we cannot see that tower from anywhere,} thought Vizicar. 
He and Carzain had wandered around in the city for a while now, peering over the rooftops and trying to catch a glimpse of the strange tower they had seen from outside the walls, but with no luck. 

\tho{We'll ask around,} thought Carzain. 
\tho{Surely the first person we meet can direct us to it.}

Carzain looked around. 
He noticed a beggar sitting by the edge of the street. 
An older \human woman\prikker or perhaps aged before her time. 
She was clearly very sick and looked awful. 
Her skin was blotched and discoloured; her right eye was forced closed by a huge, sickly blue blister. 
Carzain judged that the hag could probably not even walk. 
She was a revolting and pitiful sight. 

\tho{Whoa,} thought Carzain.
\tho{All right, let us try to ask the \emph{second} person we meet.} 
He tossed the beggar a coin and hurried away. 
For all he knew her sickness could be infectious. 

Her imagine stayed in his mind as a disturbing reminder. 
He had seen similar cases before. 
There was a hideous wasting sickness that seemed to strike \humans only. 
It had been unknown to Vizicar, but in this day and age it was widespread in all lands he had visited. 
And he could swear it was becoming more frequent each year. 







