\bookchapter{Dark Crypts of the Mind}
% \bookchapter{The Writhing of the Worm}
\begin{comment}
\subsection{Tiroco and the Crazy Old Woman}
\end{comment}
\stamp
  {\dateTirocoAndTheCrazyOldWoman}
  {Southeastern \hr{Malcur}{\Malcur}\\
   Evening}

\Tiroco{} did not like these seedy lower-class neighbourhoods. 
They scared her. 
Those cramped streets with buildings leaning out to loom overhead made her feel choked. 
She was very glad to have Sevac, her faithful bodyguard, with her. 
She was afraid robbers might jump them at any moment. 
She was told poor neighbourhoods were full of robbers. 
She had never seen a robber except in chains, and had never feared them before, but now, out here in the city in disguise, with only a single soldier to protect her, she felt vulnerable. 

She bore her own smallsword under her robe. 
Every noble-born \scatha{} was expected to learn to defend himself or herself. 
\Tiroco{} had never developed any real skill with the weapon, and its unfamiliar presence at her waist did little to console her. 

It was very dark, compared to the lit palace corridors she was used to. 
And it smelled bad, too. 
\tho{Is this how poor people live? Awful.} 

\tho{I have no idea where we are. 
  I have spent plenty of time looking at maps of \Malcur.
  The maps always look nice. 
  Even the ugly parts of town.
  I had thought the real thing would look similarly nice.
  
  I am supposed to rule and protect this city. 
  Now I realize how little I actually know of it.
  
  I am supposed to go and meet some of these servants of Light. 
  Why do I have to come to them? 
  Why can't they visit me at court?
  Or at least a nice mansion in a respectable neighbourhood? 
  Why must they operate in such murky places?
  Of course, they must. 
  For secrecy.
  I just wish they didn't have to be \emph{this} secret.}

\ta{How far yet, Sevac?} she asked. 

\ta{I'm not sure, my lady,} said Sevac. 
\ta{I think we took a wrong turn somewhere.}

Sevac had worked as a city guard before being promoted and eventually ending up as \ps{\Tiroco}{} personal bodyguard, so she should have some familiarity with these neighbourhoods. 
\tho{%
  But it has been several years since Sevac was last on street duty. 
  I suppose she hasn't been anywhere near here in years.
  I should have thought of that. 
  I think of her as a \quo{guard} who knows about \quo{guard}-things. 
  But of course, she has her own limitations. 
  I should have considered that. 
  I should be more considerate. 
  I should not treat her as a generic soldier and expect her to just be able to do whatever things I need. 
  
  Is this what I do? 
  Do I see my servants as faceless, generic commoners that exist just to serve my needs? 
  I hope not.
  Do I?}

\ta{My lady,} said Sevac, interrupting \ps{\Tiroco}{} brooding. 
\ta{You should stay close to me. 
  I am not sure where we are, but I don't think it's safe here.}

They emerged from the narrow streets into a more open area with short huts and hovels. 
Many of them looked crumbling and abandoned. 
\tho{And no wonder. 
  Who would want to live here?
  Also, did it not suddenly get colder?
  There is an unpleasant draught here.}

\tho{Sevac. I don't like this place. Get us out.} 
She was about to say that out loud, but scolded herself and stayed quiet. 
\tho{Sevac is doing her best. I should not always complain.}

They wandered further. 
After a while they came to a clearing where there grew trees. 
Ugly trees. 
Crooked and leafless. 
Not green and brown, but gray and black. 

\tho{%
  \Iquin. 
  What is this ghastly place? 
  I didn't imagine we had such ugliness in \Malcur.}

Even at a distance, those trees scared \Tiroco. 
They looked dead, but somehow they seemed to move and writhe. 
As if they wanted to reach out to grab a passer-by and eat her. 

Just thinking about it made \Tiroco{} imagine those deathlike twigs and branches coiled around her arms and legs, dragging her into its monstrous embrace. 
She hugged herself tight and leaned close to Sevac. 

\ta{Where are we, Sevac? What is this place called?}

\ta{%
  It has no name, my lady, but some call it the \quo{dead garden}. 
  They say evil \qliphoth{} dwell here. 
  Let us leave quickly. 
  At least now I know where we are.}

They skirted around the edges of the \quo{garden}, steering clear of the trees. 
The place smelled of death and unwholesome, unnatural things. 
And it was deathly quiet. 
Other than their footsteps, no sounds could be heard. 

\tho{No, wait. There is a sound. A voice?}
\Tiroco{} looked around and noticed a humanoid figure among the trees. 
A \meccaran{}. 
An old female \meccaran. 
Wandering around, apparently aimlessly. 
Muttering to herself. 
\Tiroco{} cast a glance at Sevac. 
She had also noticed the \meccaran. 

\ta{It is coming closer,} the \meccaran{} said. 
\ta{% 
  Closer. 
  Ever closer. 
  Dead flesh everywhere. 
  Everything is turning to flesh. 
  Corpse flesh. 
  Cold and dead.
  And the chains. 
  Always groaning\prikker grinding\prikker rattling\prikker}

She saw the two \scathae{} and stared directly at them, as if accusing them. 
\ta{%
  We are all bound!
  Bound in huge chains and dragged on!
  Dragged down. 
  Into the abyss of fear. 
  The abyss of illusions and despair.}

\ta{Who is this?} asked \Tiroco. 

\ta{Just some local madwoman,} said Sevac. 
\ta{And drunk, too, as far as I can smell. Stay behind me, my lady.}
She placed herself between \Tiroco{} and the \meccaran. 

The \meccaran{} was staggering closer to them. 
\ta{%
  Illusions and reality. 
  Reality and dreams. 
  Dreams of death.
  The land of death!
  A wasteland of flesh.
  Decayed. 
  Putrid.
  And crawling with worms.
  The worms!
  Growing ever fatter. 
  Feeding on our flesh.
  And our souls.
  Our minds!} 

Suddenly the \meccaran{} collapsed to her knees. 
There she sat, holding her head in her hands and rocking back and forth.
\ta{%
  Eating my mind!
  My thoughts. 
  My feelings.
  My dreams.
  Yes. 
  They are in my dreams. 
  In the wilderness of nightmares. 
  In the maze. 
  In the dark crypts of the mind, where all ancient horrors lurk. 
  Things older and darker than we know.
  Always lurking. 
  In the corners of our eyes. 
  Whenever we look away. 
  Wherever we refuse to look. 
  Wherever we fear to look. 
  There they are.}

She looked up at them. 
Her eyes were hazy. 
\Tiroco{} could not tell if she actually saw them or if she just stared blindly into space. 

\ta{My dreams! They are in my dreams! The worms!}
She crawled closer. 
\ta{Can you not feel the writhing of the worm beneath you?
  Can you not see them all around you? 
  Hear them? 
  Smell them?
  Do you not dream of them every night?}

She reached up and tried to paw at \Tiroco{} with her short arms. 

\ta{Get off of us, you bum!} 
Sevac pushed the mad \meccaran{} away. 
\ta{Come on, my lady.} 
She shooed \Tiroco{} on, keeping a watchful eye on the babbling \meccaran. 

\Tiroco{} had a hard time making herself look away. 
Her eyes were drawn to the \meccaran. 

The \meccaran{} babbled on. 
\ta{%
  You do not see them. You are too blind. But you will! Mark my words!
  The worms are coming. 
  They are coming for us all. 
  You will feel them. 
  Burrowing beneath you. 
  Gnawing your feet.
  Eating your mind.
  They are in your mind. 
  In the maze. 
  We are all trapped in the maze with the worms. 
  Running.
  Running blind. 
  But trapped. 
  And doomed.
  And the chains! 
  The chains bind us all!
  Groaning. 
  Grinding.
  There is no escape.
  No escape from the maze of chains\prikker}
The words trailed off as Sevac all but dragged \Tiroco{} away from the scene. 

\Tiroco{} walked on, oblivious to her surroundings, letting Sevac guide her. 
She could not shake the \ps{\meccaran} words from her mind. 
They haunted her. 
They rung \emph{true} in \ps{\Tiroco}{} ears, and it was a ring that made the cold creep in under her scales. 

\ta{My lady?}

\Tiroco{} noticed they had stopped. 
Sevac was looking her into the eyes, a worried expression on her face.

\ta{Are you well, my lady?}

\ta{Yes\prikker No.}

\ta{You are not worried about the madwoman's ramblings, are you? 
  Pay her no mind, my lady.
  There are many such crackpots in the city.
  But with this new campaign you have declared, I am sure we will have that problem fixed soon.}

\ta{Yes. Fixed. Yes.}
She tried to smile. 
\ta{You are right, Sevac.}

\ta{Come, my lady. We are almost there.}

Sevac led her on. 
But her thoughts stayed on the old \meccaran. 
\tho{Maybe Sevac is right. Maybe she is just mad.
  But maybe she is right. 
  Maybe she is referring to the same evil that the angel talked about. 
  And if that much is accurate, how many more of her words might not be true as well?
  
  Oh, \sephiroth. 
  Worms. 
  Dead flesh. 
  Chains. 
  And mazes. 
  Crypts.
  
  I don't understand any of it, and that is why it frightens me so much. 
  I wish I knew more. 
  I wish I were a wise mage, like \mater{} \Vincerre{} or Moro \Cornel. 
  Maybe then I would be able to understand what I am up against.
  I don't know anything about this evil that I am supposed to combat.
  Is it worms? 
  Is it something with chains?
  A maze of chains? 
  What does that even mean?
  The \quo{wilderness of nightmares}. 
  The \quo{dark crypts of the mind}. 
  What did she mean?
  
  Oh, I wish I were smarter\prikker}









\begin{comment}
\subsection{Tiroco and Moro}
\end{comment}
\stamp
  {\dateTirocoAndMoro}
  {\CastlePelidor, \hr{Malcur}{\Malcur}}

\Tiroco{} walked alone in a hallway, thinking the events of the previous night. 

She had met and talked to some of the servants of Light she was supposed to be \cooperating{} with. 
It had been a confusing experience. 
Some of them\dash the leaders\dash looked civilized, perhaps even heroic. 
But many of the rest had been unwholesome to look on. 
Scary, even. 
They looked nothing like what she imagined servants of Light should look. 
They looked like criminals. 
Lowlives. 
Scum of \Miith{}. 

\tho{But then, they must. That was what \Icor{} told me. 
  They must disguise themselves as criminals. 
  So the Dark ones do not catch their scent. 
  And they must make sure not to break character, in case spies might be watching. 
  That must be it. 
  They were dressed up and acting.
  
  I must not be so judgmental.
  I must trust them.
  They are working to save our beloved city, just like I am.}

She walked on, lost in her thoughts. 
Along the way she met Moro \Cornel. 
\Tiroco{} gave the archmage a polite nod. 
\Cornel{} returned the gesture. 
Then slowed down. 
\Cornel{} looked around, almost suspiciously. 
She approached \Tiroco. 

\ta{My lady \rinyuth? You look unwell.} 

\ta{Oh\prikker no. Thank you. But it is nothing.} 

\tho{She can tell I am lying. 
  I know she can. \Cornel{} is too smart for me to deceive.}

\Tiroco{} tried to dodge past \Cornel{} and continue on her way. 
But at the last moment, \Cornel{} reached out and laid a hand on her arm. 
\Tiroco{} was trapped. 
She could not shake the hand off and keep walking; that would be rude. 
She was forced to stop. 

\ta{Remember, \rinyuth,} said \Cornel, 
\ta{I am here to advise you, to share what wisdom I have. 
  I know many things. 
  It is an offer you should not waste.}
She paused, as if unsure of whether to continue. 
As if forcing herself. 
\ta{You are not alone in this. You are not alone \emph{against} this.}

With that, \Cornel{} averted her eyes and walked on, leaving a bewildered \Tiroco{} to wonder what she had meant. 



\new
Moro \Cornel{} hurried away, too embarrassed to stay. 

\tho{%
  Gods, that was awkward. 
  \quo{I know many things}. 
  That sounded ridiculous. 
  But that is the sort of things wise mages say in stories.
  Oh, gods, listen to me.
  Trying to emulate a hero from a story.
  One would think I was too old for that.
  
  I don't know if I did anything right.
  Probably not. 
  I can be subtle as long as \quo{subtle} means slinking around in silence and in disguise. 
  But when \quo{subtle} means talking to people and gaining their trust, I am lost.} 
  
\tho{%
  \quo{You are not alone against this}.} 
That one had been a probe. 
A risk she felt she had to take.
\tho{%
  There is something evil going on in \Malcur. 
  I know it, and I think \Tiroco{} knows it, too. 
  If I am right about her, then maybe it convince her I am an ally. 
  If I am wrong, it will just make me look like a crazy old mage.
  If I am even more wrong, it will make her suspect me and trust me even less. 
  I hope I haven't made it worse for myself. 
  
  I wish I knew what I was doing.}









