
\bookchapter{Beyond the Reach of Conscious Memory}
\begin{comment}
\subsection{Carzain spies on Rungerans}
\end{comment}
\stamp
  {\dateSortieInCombat}
  {\hs{Kenshaer Forest}\\
   Late evening}



\tho{Finally,} thought Carzain. 
He had been trying to stalk the Rungerans for days. 
A few times he had been able to shadow them, peering out from the edge of the jungle, but he could not keep creeping along at the edge for fear of discovery, so he had to take more convoluted paths through the \wylde and hope to find the Rungerans again. 
Now at last he could hear army camp noises coming from up ahead through the trees. 

\tho{Now, let us see if we can catch a glimpse of the \ishrah working their magic.}

\vizicar{It would be best to see them in action, of course,} said Vizicar.

\tho{Yes, but we cannot very well wait for them to attack another town, can we? 
  For several reasons.}

Carzain dismounted and snuck through the dense foliage. 
As he reached the edge of the wood and neared the great railroad, the army camp came into view. 
It was a huge sprawled mass of tents, fires, railroad carts and the and huge beasts that pulled them. 
South of the camp flowed the river Ucarn, along which the road had been built. 
The camp continued along the road for as far as the eye could see in both directions. 

\tho{Looks big. How many do think they are, Vizicar?}

Vizicar studied them through Carzain's eyes, with a warlord's trained gaze.
\vizicar{I estimate at least ten thousand. 
  Probably twice that.
  And prepared for a major siege. 
  Look at how many cannons they have.}

As Carzain ran his eyes over the many great cannons, images flashed before his inner eye. 
Memories from Vizicar's life, many centuries ago. 
Images of ancient cannons, metallic mouths shaped like monsters, arrayed in rows of a hundred and more, belching smoke and fire and a roar like the sound of the world going under.
Images of age-old stone walls and castles crumbling beneath cannonades, beneath the brutal rain of fire and metal and sorcery. 

\vizicar{%
  These cannons may not be as powerful as they were in my day,} said Vizicar, 
\vizicar{but they will be fearsome enough.}

\tho{Pelidor may have worse problems than that,} thought Carzain.
\tho{Let us find their \ishrah.}

On an open plain the army camp would have been more circular, but here they were \travelling on a railroad through dangerous \Wylde{}, so they were forced to set up a long camp along the road. 
This worked in Carzain's favour, for it made it easier to sneak in and get a look at the \ishrah. 
% As in any sane army, the mages would be placed somewhere in the middle for maximum protection. 
% But in a long, narrow camp like this, the \quo{middle} was still relatively close to the edge and could be spied on. 

Near the middle of the long camp, the Rungeran mages\dash six of them at least\dash were practicing their magic. 
At this close range they shone like a beacon to Carzain's senses. 
One woman with brown hair and a in burgundy \travelling dress went among the others as if instructing them. 
The woman held her head high and directed the other mages with commanding gestures. 
Her body language clearly marked her as the \ishrah leader. 

\tho{%
  Interesting. 
  Who is this one?}

Apparently their spellwork was just getting started. 
The burgundy-clad woman had arranged the \ishrah into a concert. 
They had lined up in geometric formation, with the woman in the centre as the \apex. 
\tho{%
  Definitely a \rethyactic{} formation. 
  Odd. 
  Most of them look like Vaimons.}

The mages began intoning the \draconic words of power, and lines of mystic energy shimmered into existence between them, making the concert glow like a huge hieroglyph of eldritch light. 
A hieroglyph whose nodes and corners were people. 
Carzain was no \rethyax, but he could feel how their arcane symbols opened the mystic paths into the Beyond, and how their words of power reached out into Chaos, beckoning. 

And the \daemons gave answer. 
At this close range, the conjuration was so potent that even the layman might notice it. 
To Carzain it was like a dozen whirlwinds blowing in his face, a hundred mouths howling straight into his ear, a thousand thorny paws pressed against his skin. 
% It might have broken a lesser man, and it was enough to leave Carzain breathless. 

\tho{%
  There is no doubt. 
  These are the same forces that wiped out Gilwaed.}

\vizicar{This is elder world sorcery,} said Vizicar. 

Images came unbidden to their minds, vague impressions and imaginations of ancient ages of darkness before the advent of mankind, a legend-shrouded world ruled by inhuman horrors of tremendous power and cruelty. 
For a moment, Carzain stood before a dark plain under the dim light of stars in unknown constellations and felt upon his skin the beat of vast dark wings from far above. 
Millennia flickered before him, in which mankind's hapless ancestors crept fearfully in the shadows of the misshapen towers of alien cities and fled terrified before nightmarish and ravening things. 

And he saw himself. 
A superhuman figure towering above it all. 
He breathed in the chaos and laughed. 
Beneath him marched a legion of a hundred thousand men. 

No. 
Not men. 
Monsters, and angels, and demons. 
Hordes of darkness and light.  
Clad in white and black, silver and gold, purple and blood red. 
Millions and yet millions of them. 
Angels. 
\Dragons. 
Monsters. 

Armies met in a mighty clash. 
Fire and lightning cracked the sky. 
Thunders rolled. 
The earth quaked. 
The heavens blackened. 
The horizons burned. 
The rivers ran crimson. 

Darkness. 
Light. 
Fire. 

Blood. 
Death. 
War. 

\vizicar{%
  And I stand above it all. I\prikker}

As suddenly as it had come, the scene faded away. 
The jungle and the Rungeran camp returned. 

\tho{What was that?}

\vizicar{Images. Associations evoked by the sensation of their spells.}

\tho{But were they hallucinations or memories? Or both?}

\vizicar{I do not know.
  Likely both. 
  Bits and pieces I recognized from my life and what other lives I remember.
  Other bits I have seen before in visions like this.
  The rest\prikker I do not know.}

Carzain considered that. 
Scenes from ancient lives, millennia older than the reach of conscious memory. 
It was not much, but it was a clue. 
Carzain and Vizicar had come a long way from the days when Carzain, as a young man, first began to hear strange voices in his head. 
They had both learned much, but their Kenosis was still imperfect. 
They had much to learn before Apotheosis was theirs. 
If it would ever be. 
If there was such a thing as Apotheosis for one such as they. 

Later, when Carzain and Vizicar were satisfied that they had learned enough and dared not linger any longer, they turned back into the \wylde and made their way west. 








