\bookchapter{The Fragile Egg}

\begin{comment}
\section{Tiroco dreams}
\end{comment}
\stamp{\dateTirocoDreamsofWorms}{
  \CastlePelidor, \hs{Malcur}}

\begin{dream}
\Tiroco{} is breaking apart. 
Her towers are groaning and crumbling. 
Her walls are tumbling. 
Her streets are convulsing. 
Her ground is turning to putrid swamp and mud. 
And from deep below she can feel her foundations being gnawed by worm-like things.
Huge, blind and bloated. 
Chewing on her feet. 
Peeling off her scales. 
Drilling into her head with their sucking mouths. 
Sucking. 
Sucking the marrow from her bones, the juices from her brain. 
Leaving her dry and empty. 

And there is the rot. 
A poison. 
A disease. 
Festering in her body. 
Making her warp and mutate. 
Turning her blood into mud. 
Her flesh into dirt. 
Her skin and scales into gray metal. 
The corruption is taking her. 
She is losing herself. 
She is becoming a half-living, half-dead thing. 

Two forces. 
A myriad forces. 
Tearing at her from opposite sides. 
Ripping her apart. 
Violating her. 
Consuming her. 
Transmuting her. 

It comes closer. 
Ever closer. 
From all sides. 
Blind. 
Mindless. 
Searching. 
Groping. 
Greedy. 
Lustful. 
Devouring. 

There is filth. 
There is stink. 
And there is numbness. 
She wants to flee, but she cannot move. 
She feels her limbs going limp. 
Held down by chains. 
Acrawl with worms. 
Crushed in the belly of the creature. 
Lost in the dark. 
Lost in a maze. 
A maze of walls. 
Walls of hard stone. 
Walls of cold iron. 
Walls of oozing flesh. 
Tunnels. 
Bowels. 
The bowels of a huge and hideous thing. 
She runs through the tunnels. 
She runs in circles. 
She cannot get out. 
There is no way out. 

Vast figures loom over her. 
\Scathae{}. 
\Humans. 
Angels. 
Heathen gods. 
The hoary guardians of Malcur. 
Staring down on her. 
Their stone eyes weep. 
Sorrow.
Disappointment. 
Disappointment in her. 

She has failed. 
\end{dream}

\begin{comment}
\section{Tiroco wakes}
\end{comment}
\new
\Tiroco{} jolted awake feeling as though all her scales were shaking. 

\tho{Oh, thank the Light.
  I'm alive.
  I'm not being eaten by worms or turned into some unnatural thing.}
She felt herself with her hands.
\tho{I'm still myself.
  Warm and fleshy and scaly and alive.}

She laid back down in her bed, thinking. 
\tho{In the dream I was not just myself.}
The impression was hazy, but she understood this much. 
\tho{I was me, but also something more.
  I was Malcur.
  It was not just my own pain I was feeling. 
  It was the pain of the city. 
  I felt how Malcur was\dash is\dash being ravaged by sinister forces. 

  Something with worms. 
  And chains. 
  And a maze. 
  And a belly. 
  A maze that was a belly. 
  It is as the mad \meccaran{} said. 
  I can feel it, just like she described. 
  Something is infesting the city. 
  Eating the city. 
  Eating me. 
  Oh, \Iquin.}

She hugged herself.
She recalled the feeling of worm mouths nibbling her toes. 
Vermin creeping in under her scales. 
Filth pulsing through her veins. 

It was not the first time she had had this dream. 
It had begun the day after she had heard the \ps{\meccaran} predictions. 
Since then it had returned each night. 
And it had gotten worse. 

\tho{%
  This is too much.
  I can't do this alone. 
  
  But I am alone. 
  I haven't heard from \Icor{} or the angel in many days. 
  
  I can't fight this battle on my own. 
  My mind can't stand it. 
  I'll go crazy. 
  
  I need help. 
  
  I can't turn to the slaves. 
  They won't understand. 
  They are just slaves. 
  
  I can't go to Sevac, either. 
  She wouldn't believe me if I told her. 
  I heard her that other day. 
  She believes it's all just superstition. 
  Maybe it is superstition. 
  Maybe it's just my imagination. 
  But it feels so real... 
  
  I can't go to the Vaimons. 
  They believe in the crusade. 
  They will lose all respect for me. 
  
  I can't go to my family. 
  They already look down on me for being an incompetent ruler. 
  They will just think I am buckling under the strain like the weakling I am. 
  They will scoff. 
  They will think I'm going crazy. 
  
  Maybe I \emph{am} going crazy. 
  
  Why is \Icor{} not coming to me?
  
  There is no one I can go to.}

Then she remembered the other day. 
The chance encounter in the hall. 
Moro \Cornel. 
\hypotalk{You are not alone in this,} she had said. 
\hypotalk{You are not alone \emph{against} this.} 

\tho{Maybe she could help me.
  She is a mage. 
  She is wise. 
  Maybe she will know and understand what is happening to me.
  
  But she is a \rethyax, a heathen. 
  She is strange. 
  And scary. 
  I can't go to her. 
  
  But she did offer to help me.
  She is the only one who has done that.
  
  Can I trust her? 
  She is a \rethyax. 
  Who knows what her kind might be up to?
  
  No!
  \Cornel{} has been loyal to House Pelidor longer than I have been alive.
  She has served Pelidor longer and better than I ever have.
  I have no right to distrust her.
  
  But can I afford to trust her?
  
  Do I have a choice? 
  
  I don't know...}







\begin{comment}
\section{Tiroco punishes Needle}
\end{comment}
\stamp{\dateTirocoAsksMoro}{
  \CastlePelidor, \hs{Malcur}}

\Tiroco{} was at her desk, surrounded by her slaves. 
She knew she was supposed to be working. 
She had edicts to write and papers to sign. 
But again and again she found herself staring away into space, unable to concentrate. 

\tho{Maybe I should go to \Cornel.
  But I don't dare.
  What if I let slip something about \Icor{} and the servants of Light?
  No, it's too risky.
  I have to handle this on my own...}

\ta{My lady duchess?} came the voice of \Piacet. 
\ta{You are dripping.}

\ta{What? Oh...}
\Tiroco{} looked down and saw that she had been dripping ink all over the place with her feather pen. 
There were ugly black stains on the table. 
\tho{Oh, dear. I must be more careful.}

The pen was now too dry to write. 
She dipped it again and went back to her writing. 
Or tried to. 

\tho{
  Why is \Icor{} not coming to me? 
  Has he gone into the Light and forgotten about me?
  It's unfair! 
  Why is all this happening to me?
  Damn the world for being so cruel.
  I didn't want any of this...}

\ta{My lady duchess,} \Piacet{} ventured again.
\ta{You're doing it again. Dripping...}

\ta{Mind your own damned business, slave!} \Tiroco{} snapped. 

\Piacet{} recoiled from the outburst. 
Hurt and shock showed on her face. 
On the surface. 
But hidden in those eyes \Tiroco{} could see resentment. 
Anger. 

\tho{You have no right to pout at me. 
  You have no right to blame me.
  You are my slave.
  You are here to serve me. 
  I am suffering. 
  You should be smart enough to realize that and not annoy me.}

\ta{Piacet,} she said, holding her chin high. 
\ta{I am thirsty. More tea.}

\Piacet{} gave a slight curtsy and began pouring the tea. 

Slowly. 
So damned slowly. 

When the cup was half full \Tiroco{} was out of patience. 
\ta{That's enough!} she snapped, taking the cup away. 
It bumped into the tea pot. 
\ps{\Piacet}{} hands fumbled. 
Tea splattered all over the table and the papers. 

\ta{Gaaa!
  Now look what you did, you stupid, clumsy \human!}
\Tiroco{} pushed herself upright with a sigh. 
\ta{Clean up this mess you made!}

\ps{\Piacet}{} eyes narrowed in an offended frown. 
She began wiping the table, mumbling all the while. 
\ta{None of this would have happened if you hadn't been so...} 

\ta{What? 
  Are you talking back to me?
  You insolent, ungrateful, little...
  That is \shout{it}!
  You will report immediately to the Head of Discipline and ask to be beaten for impertinence!
  Do you understand?}

\Piacet{} curtsied low. 
\ta{Yes, my lady duchess.}
\Tiroco{} could not see her face, but she could well imagine the scowl. 
\Piacet{} turned and quickly left the room. 

\tho{Stupid slave. 
  Why can't she have some sympathy?}

\Tiroco{} sat back down. 
Then she noticed the room was suddenly all quiet. 
The cozy chattering of the other slaves, which she had taken for granted before, had fallen deafeningly silent. 
She looked around. 
Scared faces stared back at her. 
No one dared meet her eyes. 

\tho{My slaves are afraid of me.

  Oh, Silqua.
  What have I done?
  I have sent poor \Piacet{} off to a beating. 
  For what? 
  For nothing. 
  For a little clumsiness. 
  For \emph{my} clumsiness!
  
  I have done a terrible wrong!}

She wanted to run to the door and call \Piacet{} back and forgive her. 
But she could not. 
Could not bring herself to do it. 
It went against the rules of master-slave propriety she had been imprinted with as a child. 
She could not. 
Could only sit and do nothing. 

She could not bear to have the slaves see her face, so she rose and went over to the window. 
Looked out over the city. 
Looked at nothing. 

\tho{Oh, \Piacet. 
  I want to forgive you. 
  Wait, what am I saying?
  \quo{Forgive} her? 
  But she has done nothing wrong!
  She is my sweet \Piacet{}, who loves me.
  It is I who have wronged her.
  It is she who must forgive me.}

\tho{And now my slaves are all afraid of me.
  What is wrong with me?
  This is not me.
  I am not like this.
  I am kind to my slaves. 
  That is why they love me so.
  I am not cruel and unfair like this. 
  
  Am I?}

She remembered the day in the \quo{dead garden}, when she had caught herself thinking of Sevac as an object for her convenience, not as a real person. 
% And Sevac was not even a slave, but a free \sphyle.
\tho{\Iquin.
  And Sevac is a free \sphyle, at that. 
  How much worse am I to the slaves? 
  Am I really so inconsiderate?
  So petty? 
  Am I so absorbed wallowing in my own misery that I take it out on my sweet, innocent slaves?
  Is that really who I am?
  
  No! 
  It can't be!
  
  It's the strain.
  The mission.
  The dreams. 
  They are driving me mad. 
  
  I was wrong. 
  I can't handle this on my own.
  I need help.
  I need help badly. 
  I need to trust someone. 
  
  My only choice is Moro \Cornel.}








\begin{comment}
\section{Needle fumes}
\end{comment}
\placestamp{Outside the office of the Head of Discipline}

Needle tried her best to keep her normal posture as she walked, but it was difficult. 
Her buttocks smarted. 
The Head of Discipline was nothing if not thorough. 

\tho{Damn you to \Itzach, \Tiroco.
  Selfish stuck-up bitch.
  And worthless. 
  You can't do even the most simple things. 
  Can't write your own name without messing up the place.
  \quo{Don't tell me where to drip my ink!}
  Easy for you to say. 
  It's not you who has to clean it up.
  
  But you never got that, did you, \Tiroco?
  You've never seen beyond your own snout. 
  You've always been living in an egg. 
  Blind to what goes on around you.
  Blind to the suffering of your people. 
  Always whiny and hysterical. 
  Throwing a crying fit over nothing. 
  
  You think you have it tough?
  Well, bitch, you're wrong!
  You had everything back when \Icor{} was alive, and that didn't stop your whining.
  And even without your oh-so-precious duke you're still better off than all the rest of us.
  You have three children. 
  You're good-looking, with new suitors lining up to fill the empty space in your bed.
  You have servants and slaves to wipe your ass. 
  You have money far up said ass.
  You have it all!
  
  I've never had a husband. 
  Most men available to me are ugly scum. 
  I've never had a man to care for me and protect me. 
  The closest thing I have is Charcoal. 
  Hah.
  I can never have children.
  I have no money. 
  I can't go where I want, do what I want. 
  Worst of all, I have to wait on you.
  
  And I'm well off. 
  Lots of people, even if they're free people in name, have it worse than I.
  They face starvation and robbery and disease every day.
  They see their friends and family dying around them every day.
  
  \Miith{} is Hell. 
  And nobles like you are only making it worse.
  
  No one is doing anything. 
  
  But I am.
  We of the Cabal are working for a better world.
  A world ruled not by petty and stupid so-called nobles, but by the truly noble. 
  The \emph{only} ones who are truly noble. 
  Truly wise. 
  Truly superior. 
  Truly worthy to rule.} 
She felt warm just thinking about them. 

\tho{Our beautiful gods. 
  The \resphain.
  
  And we, their faithful, will rule as their stewards. 
  Your time is soon over, \Tiroco.
  Our time will begin.
  A better time.
  A better world.}







\begin{comment}
\section{Tiroco and Moro}
\end{comment}
\begin{comment}
\subsection{Tiroco asks for help}
\end{comment}
\placestamp{\hr{Ishrah}{\Ishrah} tower}

\Tiroco{} stood outside the door to Moro \ps{\Cornel}{} quarters. 

\tho{Should I go in?
  Am I doing the right thing?
  
  Get a hold of yourself, \Tiroco. 
  I have been over this. 
  I am going in.} 

She knocked on the door. 

A pause. 
Some low mumbled words could be heard on the other side. 
Then: 
\ta{Yes?}

\Tiroco{} let herself in. 

\Cornel{}, dressed in a rather drab gray robe, rose from her table and gave a slight bow. 
\ta{My lady duchess. What can I do for you?}

\ta{Archmage \Cornel.} 
\Tiroco{} inclined her head in respect. 
\ta{I was thinking... about... well, I mean... How shall I say it?}
She hesitated. 

\Cornel{} looked intently at her. 
\Tiroco{} all but crumbled under that stare. 
It was as though for a short moment she looked inside \ps{\Cornel}{} soul. 
The depths she glimpsed scared her. 
There was bitterness. 
There was the pain of betrayal. 
There was anticipation. 
And she thought there was an unspoken admonition: 
\hypotalk{%
  Do not make my sympathy for you be wasted. 
  I have too little of it.}

\ta{Archmage \Cornel,} she began again. 
\ta{You told me to come to you if I needed help and advice.}

\Cornel{} smiled. 
Slightly. 
The gloom in her eyes lightened. 
Slightly. 
\ta{Yes, I did.
  Please, duchess, take a seat.}

\Tiroco{} did. 

\ps{\Cornel}{} eyes became intent again. 
\ta{So, what can I help you with?}

And \Tiroco{} told her the story. 
Not about \Icor{} and the angel, of course. 
But about the dead garden, and the mad \meccaran{} and her prophecy. 
And about the dreams. 





\begin{comment}
\subsection{Moro considers}
\end{comment}
\new 
Moro \Cornel{} poured some wine for the duchess and herself while listening to \ps{\Tiroco}{} story. 

\tho{%
  Is all this true? 
  First of all, is she being honest, or is she lying to me?
  Second, if she is being honest, are her visions real or just her imagination? 
  Third, if they are real, why is she seeing them?
  I have had no reason to believe \Tiroco{} has clairvoyant or precognitive abilities. 
  Why would she begin now?
  
  It might be nothing. 
  \Tiroco{} has always been easily upset. 
  But I do know that something is terribly wrong in Malcur. 
  I have done my own research. 
  And there are similarities. 
  Her account does remind me of some of the things I have found before.
  The worms, and the chains. 
  
  Curse me!
  If only it were I and not she who was having these visions.
  Then perhaps I could understand them and deal with them. 
  And she would be spared the horror of it. 
  She is fragile. 
  I am hardened. 
  I could take it. 
  
  If only my senses were not so damned dull.
  If only I were not so blind and deaf.
  
  Gods, look at me. 
  I am supposed to be the wise and seeing mage, but I see nothing.
  I am supposed to be aware of supernatural menaces so I can advise the duchess, yet she has to come and tell me what is right under my nose.
  And I am reduced to a glorified confessor. 
  \quo{I know many things.} 
  What a lie. 
  I don't know anything...
  
  Stop it, Moro!
  I can feel sorry for myself later.
  Right now I must focus.
  I have to understand this and deal with it.
  Pelidor needs me. 
  \Tiroco{} needs me.}

\Tiroco{}, it seemed, had reached the end of her account. 
Now she was prattering on, nervous. 
\ta{%
  You may think me crazy, Archmage \Cornel.
  Especially after I declared the new \quo{crusade}.
  I don't know.
  Maybe I am crazy.}

\ta{No, duchess.
  You are not crazy.}
\tho{I should reach out with a hand. 
  Comfort her.
  Or should I?
  Maybe I should not.
  I won't.}
Instead she kept talking: 
\ta{There is something evil afoot in Malcur.
  This I, too, have come to believe.}

\Tiroco{} looked at her with big eyes, as if at once gladdened and saddened to hear this. 
Moro did not know how to respond to those eyes. 
\tho{Oh, no. Emotions.
  I can't deal with emotions. 
  No emotions. 
  Just scientific facts and hypotheses.
  I can do that.}
So Moro put on her scholarly mask. 
Retreated behind a mask of science. 
That was something she knew how to do. 

\ta{I cannot tell you its exact nature yet.
  I am still conducting research on that point.}
\tho{If groping blindly counts as research, that is.}
\ta{But I am glad you have come to me, my lady.
  We can solve this together, you and I.
  We can fight this evil.
  We can save Malcur.}

\ta{Really?} 
\Tiroco{} sounded hopeful, but reluctant. 

\ta{So I hope.}

\tho{She's still doubtful. 
  I must persuade her.
  All right. 
  I can do this.
  Use my scholarly authority. 
  \quo{Proof by intimidation}. 
  
  Look into my eyes, \Tiroco. 
  Believe me. 
  The wise and scary mage knows best.
  Trust me.}

\ta{%
  My lady, I would like to perform some research on you. 
  With the aid of some spells, I believe I will be able to... extract... the visions from your mind. 
  This will allow me to experience them myself. 
  I hope to be able to trace them to their source, or at the very least analyze them. 
  This will give us both a much better understanding of the nature of the threat and how to combat it.} 
Moro forced a smile. 
\ta{Together.}






\begin{comment}
\subsection{Tiroco backs out}
\end{comment}
\new 
\tho{Yes,} thought \Tiroco. 
\tho{%
  I very much want to learn more about this evil. 
  I need to know what I am up against.
  
  \quo{Combat it together}. 
  I like the sound of that.
  
  But... why is she staring at me like that?}
She looked into \ps{\Cornel}{} eyes. 
There was something strange in that look, that face. 
\tho{Is she... nervous? 
  Why?
  Is she trying to manipulate me?}

A thought occurred to \Tiroco{} that forced her to stifle a loud gasp.
\tho{%
  What if \Cornel{} is one of the Dark ones trying to deceive me?
  What if she is trying to pry information out of me concerning the angel and the servants of Light? 
  What if, by going to her, I am playing straight into the Dark ones' hands?
  Oh, Silqua. 
  I am making a terrible mistake.
  I have to get out of here!}

\Tiroco{} rose. 
\ta{Archmage \Cornel. 
  I think... 
  I think I may have overreacted. 
  I think maybe there is no need for...}

She trailed off as she looked again into \ps{\Cornel}{} eyes and saw the disappointment painted in them. 
The sorrow. 
The hurt. 

\tho{%
  I have offended her. 
  
  Maybe I am being prejudiced.
  Maybe she really does want to help me.
  
  But no! I can't afford to risk it. 
  I have made a promise to \Icor.}

\ta{I'm sorry, Archmage \Cornel,} she stammered, backing away. 

\ta{Now, duchess \Tiroco...} \Cornel{} began. 

\ta{I have made a mistake. 
  I should not have bothered you.
  I... I have to go.
  I'm sorry.} 
She was still blabbering as she stumbled, almost ran out the door. 

\tho{%
  Silqua help me.
  I don't know if I just averted the biggest mistake of my life, or if I just made that mistake.
  \Icor. 
  Moro \Cornel.
  I feel I have let both of you down. 
  Forgive me...}





\begin{comment}
\subsection{Moro left pondering}
\end{comment}
\new 
Moro \Cornel{} did not try to call \Tiroco{} back. 
She did not think it would help. 
\tho{At this point it would just make her more suspicious.} 

She slumped in her chair.
\tho{%
  She does not trust me.
  Of course she doesn't.
  
  She says she wants my help, but she will not divulge any of her secrets to me.
  What a selfish leech. 
  
  No. 
  Not selfish. 
  Just afraid. 
  Afraid of me. 
  
  And why should she not be?
  I am scary. 
  
  Sigh. 
  Now I am doing it again.
  Lashing out at the world and feeling sorry for myself.
  I should get to work.
  We did not get so far, but I did obtain some valuable information from our conversation alone.
  Good thing I remembered to take notes of her description. 
  Now I must think on this.
  Do more research.
  
  And I must find out what \Tiroco{} is hiding. 
  It might contain vital clues.}



\begin{comment}
After this, \Tiroco{} tries to avoid Moro and freeze her out. 
This, of course, makes Moro even more convinced that something is wrong, and makes her work harder to find out. 

\Tiroco{} curses herself for her stupidity every time she dodges Moro or the like.

Moro has gotten suspicious and is now covertly stalking \Tiroco.
\end{comment}

