\bookchapter{The \Qliphoth{} Lie Ever in Wait}
\begin{comment}
\subsection{\Tiroco{} has been told what to do}
\end{comment}
\stamp
  {\dateTirocoUndergroundWork}
  {Throne chamber, \CastlePelidor, \hs{Malcur}}

\begin{comment}
\subsection{Council chamber}
\end{comment}

\ta{%
  ... and thus, with most of our soldiers gone off to war, and with additional taxes being raised to fund said war, the danger of peasant uprisings is very real. 
  The above taken into consideration I believe it is imminent that we discuss what precautions we can take...}

\Tiroco{} allowed her attention to drift away as Iasper Bartholin, the ducal treasurer, explained on and on about the state of the country, in his extremely monotonous and boring voice. 
In the past, when she had only attended these ducal council meetings out of duty and politeness, she had been lulled to sleep more than once by the old treasurer's blabbering. 

Today she could not afford to fall asleep. 
But she did not have the energy to worry much about the state of the treasury, either. 
She had more personal worries that occupied her. 

\tho{%
  No. 
  Not just personal worries. 
  They affect us all. 
  The lurking evil that \Icor{} told me about threatens not just \Icor{} and me, but everyone. 
  It wants to corrupt all of Malcur. 
  I did not fully understand what this \quo{corruption} means, but \Icor{} said the \hs{angel} had told him that it was a dire threat to our city and our entire duchy. 
  
  And the evil hungers for souls, and seeks to consume the souls of the dead. 
  That's why \Icor{} had become a ghost, he said. 
  The angel had to turn him into a ghost to save him from being devoured by the darkness. 
  Along with many other souls. 
  
  I cannot let that happen. 
  I have to do something.}

\Icor{} had relayed the angel's explanation of how Malcur was full of the agents of the Darkness, how they had infiltrated the guards, the bureaucracy, the army, the nobility, everything. 
\tho{Even the court.} 
She looked around her, studying the faces of the council while trying not to look suspicious. 
\tho{Even the \hr{Ishrah}{\ishrah}.}
Her eyes found Moro \Cornel, the \hr{Rethyax}{\rethyax} archmage. 
\tho{Even the Church.} 
Her eyes found \hr{Pater}{\Pater} \WimarNorden.  
And \Zacophine{} \Vincerre, the \hs{Redcor}. 

\tho{Anyone and everyone might be an enemy.}
That was why it was paramount that she reveal her knowledge to no one, lest the servants of Dark suspect and conspire to dispose of her as they had \Icor. 

But she was not alone, he had told her. 
There were good people in Malcur. 
Servants of the Light. 
People who had been touched by the angels and even now worked bravely to thwart the evil plan. 
But she could not simply approach them. 
The faithful ones would dearly wish to \cooperate{} openly with the just and rightful rulers, but doing so would render them visible and vulnerable, and the eyes, ears and knives of Darkness were everywhere. 
So, for fear of discovery, the ones of the Light had to work in utmost secrecy. 
Underground, in the guise of criminals. 
All to keep themselves safe. 
Safe and hidden from the very people they worked to protect. 

\tho{%
  Good people, noble people forced to hide as criminals. 
  It's not fair. 
  
  And where does that leave me? 
  I don't know who our allies are.
  I don't understand what the evil plan is. 
  I don't even understand what the \emph{good} plan is.
  And I am supposed to save us.} 

But she must. 
The angel had worked long and hard to contact her. 
Because she was an unlikely candidate, \Icor{} had explained. 
Because everyone believed she was incapable. 
\Tiroco{} could not rule.
She would be more of a liability than an asset to the ones of light, so they would never consider approaching her. 
Or so the Dark ones believed. 

\hypota{But I know better,} \Icor{} had said.
\hypota{%
  You can do it, \Tiroco. 
  I know you better than anyone, my love, and you are stronger than anyone realizes. 
  Even yourself. 
  You can do this. 
  They do you injustice when they discount you. 
  The servants of Dark, most unjust of all, will also discount you. 
  They will not see past the weakness in you. 
  Let that weakness be your strength, \Tiroco! 
  Remember the \hr{Sephirah}{\Sephiroth} of the Tear. 
  They teach that Humility and Patience are virtues. 
  And only by aspiring the virtues of the \hr{Sephiroth}{\Sephiroth} can we overcome the Darkness.}

\tho{%
  Virtues.
  Overcoming.
  \Sephiroth{}. 
  Light.
  Darkness.}
It all made \Tiroco{} feel very small. 
And smallness did not feel like a virtue, whatever the \sephirah{} \hr{Feazirah}{\Feazirah} might teach. 

\tho{%
  I am responsible for everything.
  Not just governing Pelidor until a new duke can be chosen.
  I have to fight the great evil.
  Save Malcur.
  Save \ps{\Icor} soul. 
  Save all our souls.
  And on top of that, I have to do it without anyone ever finding out.
  I did not imagine that fighting for justice would be so... unjust. 
  
  But I must. 
  I must protect the servants of Light and keep their operations secret. 
  Trust the angel, \Icor{} told me. 
  Trust the angel.
  It trusts me. 
  And so does \Icor. 
  I can do this. 
  
  And I have an idea.
  
  Oh, Light, be with me. 
  I hope this works.
  This is the first day of the month of \hr{Feazirah}{\Feazirah}. 
  Maybe she will help me. 
  Use my humility and weakness as strength, \Icor{} said.
  I can do it. 
  Dear \hr{Feazirah}{\Feazirah}, please be with me. 
  With your help, I can do it.
  
  Here goes.}

\ta{My lords,} she announced in a strong, firm voice. 
Or so she hoped. 

Everyone's attention swung towards her. 

\tho{I have prepared this speech. I can do it.}
She took a breath. 
\ta{%
  My lords. 
  We have spoken much of the war that threatens our land. 
  But no one has spoken of the matter which is equally grave. 
  The other war.}
  
\ta{What \quo{other war} are you talking about, my lady duchess?} asked \Vincerre. 

\ta{%
  I refer, esteemed \hr{Mater}{\mater}, to the war \emph{within}.
  The war of the spirit. 
  The war against corruption and sin, for the salvation of our souls.}

\Vincerre{} nodded. 
She did not look convinced, but as a representative of the Redcor Church she could hardly object against piety. 

\ta{These are trying times,} \Tiroco{} continued. 
\ta{%
  Scripture teaches us that in times of strife and worldly hardship, it is all-important that we not let strife into our hearts.
  We must not let the heart mirror the corruption of the world. 
  Rather, when the outer world is darkest, that is when the inner light must shine brightest of all. 
  \hr{Omariel}{\Omariel} teaches us to endure hardship. 
  \hr{Barion}{\Barion} teaches us to do so with our heads held high. 
  And \hr{Teshiron}{\Teshiron} teaches to face the evils of the world with faith unflagging. 
  
  But this is hard. 
  I know this first-hand. 
  I know how hardship can make the heart's courage falter and faith waver. 
  We mortals are feeble. 
  In times like this, we are prone to doubt, to forget the truth of the Light and succumb to superstition and idolatry. 
  
  When Duke \Icor{} was taken from us, I did not want to accept it. 
  I wanted to believe that he was still with me. 
  So badly that I convinced myself I saw his ghost in every shadow. 
  I convinced myself \Icor{} was still by my side. 
  I let my faith waver, and with it my sanity, and my rule. 
  I have been foolish. 
  I have been weak. 
  You all know this from observing me.}

She paused to observe the effect. 
Some offered sympathetic smiles (fake or genuine). 
Some averted their eyes, embarrassed. 
Some even nodded: \hypota{Yes, you have been weak and foolish.} 

But it had affected them. 
Baring her heart like this skirted the edges of propriety, and it caught them unawares. 
Opened them up, perhaps. 
\tho{Is this what \Icor{} meant by using my weakness as my strength?}
Then she realized something. 
\tho{\hr{Iquin}{\Iquin}! I've just manipulated them!}
The thought made her soft skin tingle, and she had to keep herself from shuddering. 

\ta{%
  I have been weak,} she continued. 
\ta{%
  But I have recognized the folly of it.
  Pining over ghosts and mirages will not bring \Icor{} back, only trivialize his memory. 
  I know that such thoughts are an evil, and they must be fought with piety. 
  And I do, as well as I am able. 
  Yet I must also think beyond myself. 
  Witnessing my own frailty makes me fear for the plight of my people. 
  If this is how these troubles can affect even one of noble blood, then I shudder to think how it must affect the common folk.}
This, at least, no one challenged. 
They acknowledged that, weak and foolish though she may be, she was still a noble, and nobles stood above commoners. 
Everyone knew that. 

\ta{%
  This is a hard time for our people. 
  The see their children, parents, brothers and sisters march off to war, perhaps never to return. 
  And as \Mister{} Bartholin has told us, taxes have been raised to painful levels.
  In times like this, it is a struggle to keep up the faith. 
  The \hr{Qliphoth}{\qliphoth} lie ever in wait, striving to lead good people astray from the path of the light.
  Among their weapons are superstition, paranoia and discontentment. 
  The \qliphoth{} will make our citizens despair and succumb to wild fancies, and imagine ghosts in bright daylight. 
  In every thief they will see a \hr{Daemon}{\daemon}; in every wizened beggar a black sorcerer; in every gathering a wicked cult. 
  
  These are evils that threaten our people's souls under the Light as well as the stability of our country.
  We know that ghosts and other kinds of devilry do exist among us, but we also know that our best weapon against them is our faith.
  We know that evil can only harm us if we succumb to it and let it into our hearts.
  For does not \Teshiron{} teach that corruption within will inevitably lead to corruption without?
  But corruption without can be fought and overcome though purity within. 
  And in these times, our country needs all the inner purity and morale we can muster.} 

\ta{A most inspiring speech, my lady duchess, and very true,} said \WimarNorden. 
\ta{But what would you have us do?}

\ta{Tell us, if you please, \pater...} 
She nodded respectfully to the two Redcor, \Vincerre{} and \Camilienne. 
\ta{%
  \Mater, \hr{Soror}{\soror}. 
  Which is more important: The land or our immortal souls?}

\ta{Our souls, of course,} said \Vincerre. 

\ta{Thank you, \mater.
  When \hs{Runger} threatened, we immediately mobilized an army to oppose them. 
  When sin and doubt now threaten our people, can we then permit ourselves to do any less?}

This made \Soror{} \Camilienne{} smile broadly. 

\Vincerre{} kept her face blank and merely nodded half an inch. 
\ta{Well said, my lady duchess,} she said. 

\Tiroco{} beamed at the praise of the otherwise stern Redcor. 
But then she remembered herself. 
\tho{%
  I am supposed to be manipulating \emph{them}. 
  Must not let them control my feelings.}

\ta{What I propose is this: 
  An internal crusade. 
  Against superstition and impiety. 
  Against dissension. 
  Against insanity. 
  Against despair. 
  Against fearmongers who would spread crazy ideas of evil conspiracies.
  \emph{For} truth.
  \emph{For} hope. 
  \emph{For} faith in the Light. 
  \emph{For} belief in justice.
  \emph{For} trust in the rightful rulers.
  
  We must spread the truth of the Light and be an inspiration to all. 
  And those who spread fear and madness must be stopped and made to see the error of their ways, lest their madness spread and infect our people.
  My lords, we must present our beleaguered people with an example, and remind them that however bleak the world may look, the \sephiroth{} are always in us and with us.
  If we would but believe.}

Now Norden could restrain himself no longer. 
He rose to his feet, clapping. 
\ta{Such truth! Such piety! Bravo, my lady \Tiroco! Bravo!}
Gradually the council followed suit. 
Some eagerly.
The Redcor slowly and dignified. 

The mage, Moro \Cornel, also rose, but slowly. 
Hesitatingly. 
She clapped feebly, as if distracted. 

\ta{%
  Are we all in agreement?} asked \Tiroco. 
Everyone shouted or nodded their assent. 

Again \Cornel{} seemed hesitant. 
\tho{%
  Is here something wrong? 
  Does she doubt me? 
  Does she see through me? 
  Oh, I wish I understood all those subtleties of court policy and could read people's thoughts. 
  What is she thinking?
  
  Should I call her out on it?
  Or not?
  I don't know.
  
  I will call her out.}

\ta{%
  \Mistress{} \Cornel?
  Do you not agree? 
  I would think that, as an academic, you would be the first to acknowledge the ills that come of ignorance and misconceptions.} 
\tho{Yes. That sounded good. That would not arouse suspicion.}

\ta{Oh... yes. Certainly, my lady. I support you.} 
\Cornel{} licked her eye. 
Her face twitched. 
It looked to \Tiroco{} somehow weird, unnatural. 
She had heard rumours that \ps{\Cornel}{} face was not her real face; that she disguised herself with illusions; that her true face was hideously ugly. 
She did not know if she believed those rumours. 

\tho{%
  Maybe I am just seeing things.
  Maybe I am just nervous from the strain. 
  
  More importantly, I did well.
  I succeeded.
  
  This was clever, if I may say so myself.
  If the Light ones are working under the guise of a criminal cult, then this will shift focus away from them. 
  It will discourage people and authorities from snooping on them, and help suppress rumours that might lead the Dark ones to them.
  
  I've done something. 
  \Icor{} will be proud of me.
  
  \Icor. 
  I hope you will return to me tonight. 
  
  I want to make love to you again.}



\begin{comment}

...

Remember to have her address Moro \Cornel! 

...

And this is handy, because if stories of supernatural activity are suppressed and dismissed as superstition, it makes it much easier for \Tiroco{} to do her furtive work. 

Everyone agrees, and they begin spreading these new edicts immediately. 

This is good because it's a clever move by Tiroco, which helps give her some personality. Until now she's been a very tame character with no real skills, so she needs this. 

What she is doing is a cruel, brutal oppression of her people. Needless to say, she does not respect modern \human{} rights in \emph{any} form. Like the War on Terror in RL. But see it from her point-of-view, where she justifies her crimes. Her love for \Icor{} is weighed against her obligation to her country. 
 
\end{comment}





\begin{comment}
\subsection{Moro suspects}
\end{comment}
\new
Moro \Cornel{} was mostly quiet as the council around her how to formulate the edicts of the new \quo{crusade}. 
She shifted uncomfortably in her chair, but quickly righted herself.

\tho{Stop that, Moro!} she scolded herself. 
\tho{You know better than to show your emotions like that.} 

She was not all confortable with \ps{\Tiroco}{} announcement. 
It sounded suspicious in her ears. 
\tho{%
  On one side, I am all in favour of trying to keep the common folk from dabbling in the supernatural.
  I have learned firsthand the horrors of that, and it is not something I would wish on anyone else. 
  But on the other hand, to deny and repress the painful truth is not healthy, either. 
  That, too, I have learned firsthand. 
  Moreover, my experience is that those who rail on against \quo{lies} and \quo{madness} and \quo{impiety} are usually frauds who want to cover their own tracks. 
  Or fanatics who want to impose their own beliefs on the world.
  Often both.} 
She glances around at the clerics and coin-counters present. 
\tho{%
  I guess they are all in that boat. So they don't even notice it.}

\tho{%
  And then there's \Tiroco. 
  Now, I cannot claim I have people skills, but I have spent many years hiding my inner self\dash from others and from myself\dash so I have an idea of how that looks like.
  And \Tiroco{} looks like it to me.
  Is she lying? 
  Is she hiding something?
  
  I have never known \Tiroco{} to be a religious fanatic. 
  However much the clerics clap their little hands, her epiphany seems dubious to me.
  
  Yes, she must be hiding something.
  
  Is there something wrong with her?}

She looked at \Tiroco. 
The scales around her eyes were all dry.
\tho{% 
  She has licked many tears away. 
  She has had to endure much grief and pressure.
  So of course something is wrong with her. }

% Despite being a powerful mage, Moro has not \emph{felt} the magical tremours that run through Malcur these days. 
% She is not very sensitive because she is hidden behind so much repression and denial. 
% However, she is sneaky in her everyday life, and she spies a lot, so she has picked up that there are strange goings-on. 
% She knows there are thieves guilds who are up to no good, and that it might be supernatural in nature. 
% She has seen thugs together with mages. 
% She knows something evil is going on. 
% She wants to Stop the Evil. 

Moro had liked the old \Tiroco... to the extent she was willing to admit she liked anyone. 
\Tiroco{} had always struck her as sweet and carefree, not as bitter and selfish and corrupt as most nobles. 
\tho{%
  Not as bitter as me.
  
  But I still suspect her.
  
  I should keep an eye on her.
  
  I have never really gotten close to her. 
  I guess am too bitter.
  But I should have.
  I will.
  Yes. 
  That I will do. 
  Get closer to \Tiroco. 
  Try to gain her trust. 
  That way, if she is up to something, maybe I can sniff it out.}

Moro smiled ruefully to herself.
\tho{%
  After all, I still feel some measure of guilt about doing nothing constructive the last time a kingdom crumbled around my ears...}

She formulated it as a joke. 
But it failed to fully cover up the even more rueful feelings that she tried not to admit to herself. 
The thoughts came into her head before she could repress them. 
\tho{%
  Perhaps, besides just gain her trust, I ought to give her \emph{my} trust. 
  \Tiroco{} is good. 
  She doesn't deserve to be alone. 
  She deserves a friend. 
  I am not much of a friend. 
  But I ought to try.}







\begin{comment}
\section{Rian is threatened by a thug}
\end{comment}
\stamp
  {\dateRianAndJorgen}
  {%
    \hs{Black Plague} territory, \hs{Malcur}
    \\
    Evening%
  }

\tho{%
  I'm done for!
  They'll find me!}
These thoughts ran through Rian's head as he pressed himself flat against a wall. 

It was late evening and the city was dark. 
And in a shady quarter like this, dark meant \emph{dark}. 
The buildings were not as tall and looming as in the richer quarters, but the streets made up for it by being narrower. 
Rian could see little more than vague silhouettes. 
He told himself that he was skilled at moving around at night, having done so plenty of times in his thieving days. 
But then he reminded himself that the Black Plague thugs were just as skilled, if not more. 

\tho{%
  Light.
  I hope coming here wasn't a big mistake.}

This was Black Plague territory. 
The \emph{bad} part of the city. 
Rian had been wanting to go here for many days\dash ever since he heard from Dennick that the Black Plague was involved\dash but he had kept postponing it.
He was afraid. 
The Plague was bad news. 
That was common knowledge to everyone in the slums: 
Do \emph{not} mess with the Plague. 

But he has to go here. 
It's the best lead he has. 
So after many days of dithering he has finally pulled himself together and ventured into the part of the city where the Black Plague have their hideouts. 

\ps{\Uswa}{} fortune-telling having failed him, he was back to relying on his own ingenuity. 
\tho{%
  By the \sephiroth{}. 
  I will save her.
  The Light will help me.}

He's not gone far, and already he's having second thoughts. 
He wishes he was far away from here. 
Back in the carpenters' home. 
Or even back in the slums. 
Anywhere but this dreadful place. 

\tho{%
  I'm history. 
  I'll be gutted any moment. 
  I just know it.}

But he forces himself to go on. 
He's come this far and he can't turn back now. 

\tho{There!} 

A sound. 

A dull thud somewhere behind him. 

\tho{%
  Oh, no. 
  Have they seen me?
  Have they heard me?}

He kept completely still and listened. 

Nothing.

Low voices from behind a wall. 
Inside a house. 
Nothing important. 

Some thumps and shouts that might be a brawl, a street or two away. 
Nothing important. 

A faint rustle of wind from above. 

Dripping. 

No creaking. 
No footsteps. 
No shuffling. 

Wait! 

Some crackling. 
Gnawing? 
Yes, it sounded like gnawing. 

\tho{%
  Must have been a big rat or something.
  The rats grow pretty big here.}
Rian allowed himself to relax. 

When he had convinced himself that there was no danger, he crept along. 
Up ahead he could hear what sounded like an inn or den. 
\tho{%
  There might be something there.
  I don't know what I'm looking for, but this might be a lead.} 
He followed the sound. 

As he drew closer, the sound became louder and clearer. 
He could make out shouts, laughter. 
Singing? 
\tho{Definitely an inn or the like.}

Then...

\tho{What was that?}

A noise behind him, like that of feet. 

He turned around... just in time to see a \human{} shape flying towards him. 

Rian raised his fists to defend himself. 
The attacker batted them away and swiped with a fist at his face.
Rian pulled back as fast as he could, but not quite fast enough. 
He felt blood seep out of his bruised nose and lip. 
The pain slowed him for a moment. 
Too long a moment. 
The attacker's knee rammed into his stomach, and he felt how all air was pushed out of his lungs and replaced with pain. 
He doubled over. 
Feebly he raised his hands, but he couldn't stop the hand that cuffed him brutally in the face. 

Rian went down. 

The attacker stepped on his right arm with all his weight. 
Rian cried out in pain and dropped his knife. 
\tho{%
  Knife! I had a knife! I forgot about the knife. I should have used it.}

\ta{Sneaking into our territory, are you?} came a man's voice from above him. 
The bigger man slapped him once. 
Twice. 
Three times. 
Four times. 
\ta{Let's see who you are, you little shit.}
He grabbed the dark scarf that Rian had wrapped around his face and pulled it away. 

\ta{Rian?}

Now Rian recognized the voice. 

\ta{J-Jorgen?}

He looked up. 
The attacker had removed his own hood, and now Rian recognized the face, too. 
That pointed jaw and the red hair and beard. 
It was Jorgen, an old acquaintance of his. 
He was some years older than Rian and a rough fellow, but he had been nice to Rian in periods, and even taught him a few things. 
% Such as how to throw a knife. 
Everything Rian knew about how to throw a knife, he owed to Jorgen. 

\ta{What in \Itzach{} are you doing here?} 
asked Jorgen, not relinquishing his grip. 

\ta{I... I...}

\ta{\shout{Talk}!}
Jorgen held his own knife inches above Rian's face.

\ta{I'm looking for Neina!} Rian stammered. 
\ta{My girlfriend!} 

Jorgen's eyes widened. 
Then narrowed. 
He looked away. 
His face hinted of what might be exasperation... or sadness. 

Rian decided to push his luck. 
\ta{Do you know where she is?} 
he pressed. 

\ta{%
  Listen to me, Rian.
  This is fucking no place for you to be snooping around. 
  You just thank the Light it was me who found you. 
  Any other would have killed you without a second thought.}
Jorgen sighed. 
\ta{%
  I'm going to let you go this time, for old times' sake. 
  But don't let me see you \shout{anywhere} near here again!
  Or anywhere near any other place where the Plague operates. 
  Mess with the Plague and we \emph{will} kill you. 
  Don't go trying to play the hero! 
  You get that?}

Rian remained silent. 

Jorgen grabbed Rian's shirt and shook him so his head banged against the dirt. 
\ta{\shout{You get that}?}

\ta{Yes!} Rian cried while feebling struggling under the bigger man's grip. 

Jorgen released him and rose. 
\ta{Get out of here.}

Rian ran. 









\begin{comment}
\section{Needle suspects}
\end{comment}
\placestamp
  {Slave quarters, \CastlePelidor, \hs{Malcur}}

Needle was sitting in her room. 
Briar, her fellow Cabalist, was reporting his progress and findings. 
She was trying to make sense of it and decide what to do about it. 

Earlier, Needle had caught sight of \Tiroco{} sneaking out of the palace at strange hours, in disguise and with only Sevac (her faithful bodyguard) for escort. 
Needless to say, Needle has smelled something fishy going on, and so had set Briar and his goons on \ps{\Tiroco}{} trail. 
They had found the duchess sneaking into shady parts of the city where the Black Plague had their hideouts. 

\ta{We couldn't penetrate any further,} Briar apologized. 
\ta{Too dangerous. Full of Black Plague people.} 

\tho{You should have tried, damn you,} she thought.
\tho{That's what you're here for.}

\tho{But now I'm being a bitch.}
She looked at him. 
He was a wiry man with a reddish beard, about the same age as her. 
His real name was Ornen, but she called him by his code name \quo{Briar}, as was Cabal custom. 
\tho{He is doing his best, as are we all.
  He knows what he is doing.}

\ta{A shame,} she said. 

\ta{I'll go out and see what more I can dig up.} 

\ta{Yes. Good.}

Briar left. 
She remained, thinking. 

\tho{\Tiroco{} has some shady dealings.}
Needle had heard of the duchess' new \quo{inner crusade}. 
It was not highly suspicious by itself, since \Tiroco{} was a pious \hs{Iquinian}. 
But when viewed in conjunction with her all-in-all strange behaviour these last weeks\dash furtive, paranoid, jumpy, quiet, talking to herself\dash and now her sneaking out at night, a distinctly suspect picture began to take form. 

\tho{%
  Something strange is happening around the duchess. 
  Perhaps she is not quite the airhead I've always taken her for. 
  
  There was also that episode in her bedroom some time back, where \Tiroco{} jumped at some shadow in the window. 
  I might have felt something there.
  I can't be sure, but I might. 
  
  There's something strange going on with that \sphyle. 
  I'll need to have her tailed again the text time she goes wandering off.
  
  And into the Black Plague quarters. 
  That's not good. 
  We have only few informers among them, and none realiable. 
  What's worse, we have good reason to believe they are infiltrated by the Sentinels. 
  
  It is as \Achsah{} said. 
  The Sentinels are up to something nasty. 
  
  And so is \Tiroco. 
  For all I know she is in league with them. 
  Damn her. 
  Damn those nobles. 
  Always corrupt and selfish. 
  It's their fault the world is like this. 
  
  It's up to people like me to do the \ps{\resphain} will and stop this evil. 
  And I will.
  
  I will not fail you, \Achsah.}









