\bookchapter{Tremours}
\begin{comment}
\section{Rian is threatened by a thug}
\end{comment}
\stamp
  {\dateRianAndJorgen}
  {%
    \hs{Black Plague} territory, \hs{Malcur}
    \\
    Evening%
  }

\tho{%
  I'm done for!
  They'll find me!}
These thoughts ran through Rian's head as he pressed himself flat against a wall. 

It was late evening and the city was dark. 
And in a shady quarter like this, dark meant \emph{dark}. 
The buildings were not as tall and looming as in the richer quarters, but the streets made up for it by being narrower. 
Rian could see little more than vague silhouettes. 
He told himself that he was skilled at moving around at night, having done so plenty of times in his thieving days. 
But then he reminded himself that the Black Plague thugs were just as skilled, if not more. 

\tho{%
  Light.
  I hope coming here wasn't a big mistake.}

This was Black Plague territory. 
The \emph{bad} part of the city. 
Rian had been wanting to go here for many days\dash ever since he heard from Dennick that the Black Plague was involved\dash but he had kept postponing it.
He was afraid. 
The Plague was bad news. 
That was common knowledge to everyone in the slums: 
Do \emph{not} mess with the Plague. 

But he has to go here. 
It's the best lead he has. 
So after many days of dithering he has finally pulled himself together and ventured into the part of the city where the Black Plague have their hideouts. 

\Uswaz{} fortune-telling having failed him, he was back to relying on his own ingenuity. 
\tho{%
  By the \sephiroth{}. 
  I will save her.
  The Light will help me.}

He's not gone far, and already he's having second thoughts. 
He wishes he was far away from here. 
Back in the carpenters' home. 
Or even back in the slums. 
Anywhere but this dreadful place. 

\tho{%
  I'm history. 
  I'll be gutted any moment. 
  I just know it.}

But he forces himself to go on. 
He's come this far and he can't turn back now. 

\tho{There!} 

A sound. 

A dull thud somewhere behind him. 

\tho{%
  Oh, no. 
  Have they seen me?
  Have they heard me?}

He kept completely still and listened. 

Nothing.

Low voices from behind a wall. 
Inside a house. 
Nothing important. 

Some thumps and shouts that might be a brawl, a street or two away. 
Nothing important. 

A faint rustle of wind from above. 

Dripping. 

No creaking. 
No footsteps. 
No shuffling. 

Wait! 

Some crackling. 
Gnawing? 
Yes, it sounded like gnawing. 

\tho{%
  Must have been a big rat or something.
  The rats grow pretty big here.}
Rian allowed himself to relax. 

When he had convinced himself that there was no danger, he crept along. 
Up ahead he could hear what sounded like an inn or den. 
\tho{%
  There might be something there.
  I don't know what I'm looking for, but this might be a lead.} 
He followed the sound. 

As he drew closer, the sound became louder and clearer. 
He could make out shouts, laughter. 
Singing? 
\tho{Definitely an inn or the like.}

Then...

\tho{What was that?}

A noise behind him, like that of feet. 

He turned around... just in time to see a \human{} shape flying towards him. 

Rian raised his fists to defend himself. 
The attacker batted them away and swiped with a fist at his face.
Rian pulled back as fast as he could, but not quite fast enough. 
He felt blood seep out of his bruised nose and lip. 
The pain slowed him for a moment. 
Too long a moment. 
The attacker's knee rammed into his stomach, and he felt how all air was pushed out of his lungs and replaced with pain. 
He doubled over. 
Feebly he raised his hands, but he couldn't stop the hand that cuffed him brutally in the face. 

Rian went down. 

The attacker stepped on his right arm with all his weight. 
Rian cried out in pain and dropped his knife. 
\tho{%
  Knife! I had a knife! I forgot about the knife. I should have used it.}

\ta{Sneaking into our territory, are you?} came a man's voice from above him. 
The bigger man slapped him once. 
Twice. 
Three times. 
Four times. 
\ta{Let's see who you are, you little shit.}
He grabbed the dark scarf that Rian had wrapped around his face and pulled it away. 

\ta{Rian?}

Now Rian recognized the voice. 

\ta{J-Jorgen?}

He looked up. 
The attacker had removed his own hood, and now Rian recognized the face, too. 
That pointed jaw and the red hair and beard. 
It was Jorgen, an old acquaintance of his. 
He was some years older than Rian and a rough fellow, but he had been nice to Rian in periods, and even taught him a few things. 
% Such as how to throw a knife. 
Everything Rian knew about how to throw a knife, he owed to Jorgen. 

\ta{What in \Itzach{} are you doing here?} 
asked Jorgen, not relinquishing his grip. 

\ta{I... I...}

\ta{\shout{Talk}!}
Jorgen held his own knife inches above Rian's face.

\ta{I'm looking for Neina!} Rian stammered. 
\ta{My girlfriend!} 

Jorgen's eyes widened. 
Then narrowed. 
He looked away. 
His face hinted of what might be exasperation... or sadness. 

Rian decided to push his luck. 
\ta{Do you know where she is?} 
he pressed. 

\ta{%
  Listen to me, Rian.
  This is fucking no place for you to be snooping around. 
  You just thank the Light it was me who found you. 
  Any other would have killed you without a second thought.}
Jorgen sighed. 
\ta{%
  I'm going to let you go this time, for old times' sake. 
  But don't let me see you \shout{anywhere} near here again!
  Or anywhere near any other place where the Plague operates. 
  Mess with the Plague and we \emph{will} kill you. 
  Don't go trying to play the hero! 
  You get that?}

Rian remained silent. 

Jorgen grabbed Rian's shirt and shook him so his head banged against the dirt. 
\ta{\shout{You get that}?}

\ta{Yes!} Rian cried while feebling struggling under the bigger man's grip. 

Jorgen released him and rose. 
\ta{Get out of here.}

Rian ran. 









\begin{comment}
\section{Needle suspects}
\end{comment}
\placestamp
  {Slave quarters, \CastlePelidor, \hs{Malcur}}
Needle lay naked under the sheet, watching Briar\dash her fellow \hs{Cabalist}\dash get dressed. 

\tho{%
  He is not so bad looking, actually. 
  Although a bit too hairy for my taste...}

\ta{Leaving so soon?} she cooed. 
She ran a finger down the side of her body, following all the curves that the sheet covered. 
In the process she \quo{accidentally} pulled the sheet down a little bit, revealing another inch or two of skin. 
It left her nipples \emph{almost} visible, but not quite. 

Briar hesitated for a moment. 
Then began pulling his trousers off again. 
\ta{Well, I might be able to make some time...}

\ta{No.}
She tucked her sheet back up. 
\ta{You have work to do.} 

His face fell slightly, disappointed, but said nothing more. 

\tho{%
  Men. 
  Stupid as always. 
  Briar is a competent Cabalist, but he never learns to recognize when I'm leading him on. 
  
  It's still funny to tease him, though.}

When he was fully dressed he moved towards the door. 

\ta{Oh, and by the way,} she purred as he reached for the handle. 
\ta{%
  If I were you I wouldn't tell anyone about how I moaned about your being better in bed than Charcoal.
  He'd probably kill you if he heard.}

Briar gave her a sly smile over his shoulder, then left. 

\tho{Charcoal is more likely to kill \emph{me},} she reflected. 
\tho{%
  But it wouldn't do to tell him that. I need Briar to be loyal to me.
  If I am to one day usurp Charcoal's place, I will need all the support from the Cabalists I can get.} 

\tho{Anyway, right now I have more important things to consider.} 

Briar's visit had not been all pleasure, but also business. 
He had been reporting his progress and findings. 
Earlier, Needle had caught sight of \Tiroco{} sneaking out of the palace at strange hours, in disguise and with only Sevac (her faithful bodyguard) for escort. 
Needless to say, Needle has smelled something fishy going on, and so had set Briar and his goons on \Tirocoz{} trail. 
They had found the duchess sneaking into shady parts of the city where the Black Plague had their hideouts. 
There Briar and his thugs had been unable to penetrate any further. 

\tho{Guess the bed isn't the only place where Briar can't penetrate far.}
Briar was an able lover, but not a great one. 
That was a lie that she used to keep him loyal to her. 
She herself had been used enough sexually to know that men loved nothing more than being praised for their sexual ability, and she had learned how to use it to her advantage. 

\tho{%
  But back to the point.
  \Tiroco{} has some shady dealings.}
Needle had heard of the duchess' new \quo{inner crusade}. 
It was not highly suspicious by itself, since \Tiroco{} was a pious \hs{Iquinian}. 
But when viewed in conjunction with her all-in-all strange behaviour these last weeks\dash furtive, paranoid, jumpy, quiet, talking to herself\dash and now her sneaking out at night, a distinctly suspect picture began to take form. 

\tho{%
  Something strange is happening around the duchess. 
  Perhaps she is not quite the airhead I've always taken her for. 
  
  There was also that episode in her bedroom some time back, where \Tiroco{} jumped at some shadow in the window. 
  I might have felt something there.
  I can't be sure, but I might. 
  
  There's something strange going on with that \sphyle. 
  I'll need to have her tailed again the text time she goes wandering off.
  
  And into the Black Plague quarters. 
  That's not good. 
  The Black Plague is not nearly as well-infiltrated as we of the Cabal would like. 
  And we have our suspicions regarding whom they \emph{are} infiltrated by...}









