
\bookchapter{The Terror of \EreshKal}
\stamp
  {\dateSortieFindsTown}
  {Kenshaer Forest, north of Gilwaed}

\begin{comment}
\section{Gilwaed in ruins}
\end{comment}

Long had Carzain \Shachar \travelled through the dark, humid jungle when at last the towering trees began to thin. 
Above him the moons now shone bright, like a pair of eyes in the sky. 
The thick fog reflected their light, as if it emanated from the moons. 
Drab gray \Dun was the larger moon.
Visha was smaller but brighter\dash a sinister, spectral kind of brightness; pale bluish white, like a corpse. 
\tho{\Dun{} and Visha. The two eyes of some gigantic and deformed god.} 
That was how some myths explained the moons. 

The news of the coming war had piqued Carzain's interest, so he had resolved to travel east towards the Rungeran border and reconnoitre. 
So far he had encountered little but more rumours. 
He intended to rest and resupply at the village of Gilwaed before venturing further east. 
If memory and instinct served him right, Gilwaed should be right nearby. 

And true enough, the trees soon cleared and gave way to a ring of \eidola, totems enchanted to keep the \wylde and its denizens at bay. 
Within the protective circle lay a village. 

Or rather, the remains of a village. 
Huts and houses had been smashed and ripped apart, as if by some great animal. 
Broken beams and pieces of thatching lay scattered around, many of them charred. 
The villagers lay scattered around, too. 
The bloody corpses of dozens of \scathae, children and adults alike; smashed, ripped and charred like their homes. 
Everywhere he could see, nothing larger than crows and rats moved. 
The village of Gilwaed had been wiped out. 

% \ta{Whoa\prikker} said a soldier. 
% Echoing what was also Carzain's first thought. 

% \ta{Looks like the Rungerans beat us to it,} another soldier said drily. 
% \tho{The Rungerans must already have been here.}
\tho{What happened here?
  Who did this?
  
  The Rungerans?
  Or something out of the \wylde?}

His \relc mount, Arrow, shied and hissed and would go no further, so Carzain tethered Arrow to a tree outside the village and continued on foot. 
He explored the ruins, stepping over severed limbs, pieces of timber and pools of dried blood. 
To his Vaimon senses the death lay so thick he could almost touch it. 
% A thing with a million biting teeth, a million stabbing claws. 

\tho{Sorcery did this,} he mused. 

\vizicar{Of course,} said the voice of \VizicarDurasRespina. 
\vizicar{But what sorcery? Let us take a closer look.}

Carzain walked to the southern end of the village, where it met the railroad.
Here he bent to examine one corpse, a middle-aged \sphyle. 
She had strange wounds that looked as if they had burst open from the inside on their own. 
% \tho{Internal bleedings. Could be \daemon-inflicted.}
He turned her over to get a look at her face. 
The eyes were unusually gray and \colour{}less, and the surrounding face was contorted with dread. 
This was not the face of one who feared merely death. 
This was the horror of something far beyond the ken of mortals. 
This \scatha had been killed by a force from the Beyond, something that destroyed life and sanity alike. 

\vizicar{How long have they been dead, I wonder?} said Vizicar. 

\tho{Two days, at least. 
  Pehaps a week.
  Not two weeks, though.}

\vizicar{A week.} 
Through Carzain's eyes, Vizicar looked down the railroad that ran west to \Forclin. 
\vizicar{Then, assuming the Rungerans did this, they must have gone far west by now. 
  Farther than we had thought.}

\tho{Yes. We should go and warn someone.}

\vizicar{Soon enough. 
  But we still need to learn more.}

On Vizicar's initiative, they slipped into a Vaimon's \shechinah trance and reached out into the Beyond, looking for traces of the cosmic forces that had been unleashed. 
Carzain examined the cosmic threads and found a lingering smell, a residue of sorcery. 
% He felt the \daemonic{} presence around him. 
% Felt the essence of Chaos. 
% The ground, the air, the plants\prikker everything was soaked in it. 
It reminded him of the feeling of the \qliphoth{} of the Midnight Circle, but more primal, more savage, more vicious. 
He followed the threads, trying to trace the scent back to its origin. 

\vizicar{%
  It is buried deep. 
  Far removed from the mortal world.
  Down in Chaos\prikker}

Carzain took a deep breath, then plunged his mind in\prikker and immediately recoiled. 
The sheer presence of that force that lurked at the end of those threads struck him like a physical blow.
The image that arose in his mind was that of a gigantic monster: 
a blind, crawling, amorphous thing the \colour of blood mixed with ash, roaring its mindless bloodlust from a thousand mouths. 

With effort, Carzain and Vizicar tore their senses away from the monstrous vision. 

\tho{Great \qliphoth! What was that thing?}

\vizicar{I do not know. 
  We must find out.}







\begin{comment}
\section{\Takestsha}
\end{comment}
\placestamp{%
  Rungeran army, east of Dendrum}

\Takestsha{} reclined on her soft, padded seat atop the \mulgron{} howdah. 
Through languid eyes she studied Morgan Runger, who sat on her right in a higher, more ornate seat. 
She did not like his expression: 
Frowing. 
Distant eyes. 
Beard-scratching. 
Even occasional mumbling. 
With her many centuries of experience of manipulating mortals, \Takestsha needed but look at his face to read his thoughts almost word-for-word: 

\hypota{%
  What am I doing?
  \Daemons{} that feast on the blood and souls of men\prikker what is this evil I have unleashed?
  Is this right?
  Even for the sake of House Runger\prikker can this be justified?}
  
Morgan turned his eyes to the sky.

\tho{%
  Praying to the \quo{Light} for forgiveness?} she thought. 
\tho{%
  We cannot have that.}

She reached up and laid a slim hand on his knee.
\ta{What ails you, my king?} she purred. 

Morgan glanced down at her and forced a smile. 
\ta{Nothing, my dear.} 
He patted her hand. 
\ta{Nothing that needs worry you.}

\Takestsha{} responded with what she hoped was a sweet and innocent smile. 
\tho{%
  Men. 
  Patronizing as usual. 
  He knows I am the most powerful member of this entire army, yet he still sees me as merely a woman.
  A frail and delicate thing that must be protected by strong men.
  He even tries to shelter me from the consequences of \emph{my own work}.}

She almost laughed inside at Morgan's foolishness. 
But that would be unfair to him, she reminded herself. 
After all, she had spent the better part of a year goading him into this, moulding him into a marionette to serve her purposes. 
% Morgan was as intelligent as any \human, and seducing him had not been altogether easy. 
% As a king he had access to any number of beautiful women. 
% But none of them had her special talents, and in the end, what \human could resist her wiles?

All in all, their last weapons test had been fairly successful. 
The occult forces unleashed had of course been completely out of proportion with that small village, but it had been necessary. 
She would not send her \ishrah against the Pelidorian army without field-testing their most powerful weapon. 
Even though the battle against the Pelidorians was itself only a field test for battles to come. 

Meanwhile the king had resumed his brooding. 
Sitting there, hunched over, lost in thought and fingering his long, once-black but now graying beard, he looked like a very old man. 

\tho{%
  He is still at it. 
  Seems I will have to resort to stronger means.}

\Takestsha{} had made sure to have her seat placed immediately next to the king's for this exact reason. 
Now she inched to the edge of her chair and took his hand in both of hers. 
The gnarled hand looked very large in hers, for Morgan Runger was a tall man\dash or had been, in his prime\dash and her assumed form was petite, like many men preferred. 

\ta{Noble king,} she crooned, almost whispered. 
She took one of his fingers in her mouth and gently sucked on it, all the while keeping eye contact. 
Lust and pride were two easy channels into a man's mind. 
\ta{Something troubles you. 
    Confide in me.}

Morgan sighed. 
\ta{%
  I am worried about this sorcery, \Takestsha. 
  These \daemons.
  It all seems\prikker evil.
  Dangerous.}

She kissed the tips of his five fingers, one by one. 
\ta{Fear not, King Morgan. And have faith.}
She giggled. 
\ta{In me.}
% Her eyes and smile hinted at other things that might happen \quo{in her} tonight. 
% \tho{Let him chew on that.}

\ta{Faith\prikker} he mumbled, while idly running his hand down her soft cheek. 
\ta{But the Light\prikker}

\ta{%
  Remember, your aim was to free yourself from the Redcor and their narrow-minded religion. 
  The ones preaching about the \quo{will} of the Light are power-hungry priests and Vaimons. 
  You must not be ensnared by their words and\prikker intolerance.}
While she spoke, she guided his hand down along her neck and through her cleavage. 
\tho{%
  Remember, Morgan. 
  From sexual open-mindedness it is no great leap to religious open-mindedness.
  And from there it is no great leap to soul-devouring black magic.}
She giggled at her own unspoken joke and shyly averted her eyes. 
\tho{Must not appear too sexually aggressive. They pick up on that.}
But she allowed his fingers to rest between her breasts. 

\ta{Yes\prikker} he said. 

\ta{After all, it is for the sake of House Runger,} she reminded him. 

\ta{Yes. You are right, my dear.} 
He stroked the inside of her cleavage with his thumb and smiled condescendingly. 

Again she giggled, but this time she pulled his hand away. 
\tho{%
  No more free gifts for you. 
  If you want more, be a good king and do as I say.}

% As she turned away, she noticed \Jirad{} Tantor ogling her from the howdah of another \mulgron. 
% 
% \tho{Oh, no. Not again.}
% 
% In retrospect, having sex with Tantor might have been a bad idea. 
% It had seemed worthwhile at the time. 
% First, the old mage's grief over his son's death had touched a soft spot in her. 
% Second, it seemed a convenient way to help secure the \ps{\ishrah} loyalty to her. 
% And third, while Tantor was certainly no great lover, sex was still more enjoyable than twiddling her thumbs. 
% But since then Tantor had grown awfully needy. 
% \tho{Maybe I should sleep with him just to shut him up.}
% 
% \new
% Have some better ending here!

% Then a jolt of energy went through her. 
% 
% She sat up. 
% 
% \tho{%
%   What was that?
%   
%   A \vertex{} spike. 
%   Nearby.}
% 
% She reached out and concentrated on tracing the signal. 
% 
% \tho{%
%   Through some \Wylde{}. 
%   But not far from the road. 
%   North. 
%   No. 
%   East. 
%   Northeast. 
%   Near that village, Gilwaed. 
%   
%   And judging by the feel of it, it might be the same source as the one detected somewhere in Pelidor two years ago. 
%   The one I was warned of. 
%   
%   It is gone now. 
%   I cannot trace it. 
%   
%   But I will keep my eye on you, little \vertex. 
%   Be certain of that.}









