
\bookchapter{\Teshrial Gets Notes}

Read about \maybehr{Teshrial}{\Teshrial} and \maybehr{Menessiaraid}{\Menessiaraid}.

At some point, \Menessiaraid expresses doubt about whether \Teshrial's \Malcur venture is really so great and important a thing as they like to believe. 

\Teshrial and \Menessiaraid are gay lovers. 
They kiss and have sex. 

Have references to \maybehr{Menessiaraid creates religions}{\Menessiaraid's work with religions}.
He tells \Teshrial about what he does, but not on \Azmith.
Make the reader be critical of religions. 


\begin{comment}
  \section{Teshrial sits with notes}
\end{comment}

Remember to have plenty of \maybehr{Resphan wing body language}{wing body language} from the \resphain. 

Make clear that \Teshrial is obsessed with \Firaxel and falling badly in love with her. 

Menessiaraid comes to visit Teshrial.
He finds him poring over a great pile of papers. 

Menessiaraid:
``What are you doing?''

Teshrial:
``Research.''

Menessiaraid:
``Ishnaruchaefir?''

Teshrial:
``Yes. I am onto something good here.''

Teshrial tells him of his progress.

\Teshrial has \Dezruth's advice. 
He researched the name ``Lothagiel''. 
He found out that there was indeed a Lothagiel, 1700 years ago, who made it his quest to slay Ishnaruchaefir but ultimately failed. 
Allegedly Lothagiel did a lot of research, but Teshrial could find nothing about his actual findings in the \CiriathSepher archives. 

Teshrial then tried to get access to the Mystraacht archives, hoping they would have more information about Lothagiel. 
But the Mystraacht archivists were not inclined to let him in or tell him anything. 

So Teshrial researched Lothagiel's next of kin. 
It turned out that probably his closest associate was a lover\dash Nemuragh, a Mystraacht Thelyad. 
He found out that Nemuragh still lived and managed to set up a meeting with him. 

Teshrial emphasized to Nemuragh his admiration for the brave and tragic hero Lothagiel. 
Nemuragh told him about Lothagiel's quest and findings. 
Lothagiel had indeed done a lot of research. 
He believed he was onto something. 
He had discovered what he believed to be some important weaknesses of Ishnaruchaefir's and was on the way to discovering some even more important ones. 
But somewhere along the way, before Lothagiel was ready to face Ishnaruchaefir, the Destroyer himself caught wind of the fact that he was being researched. 
The Destroyer did not take kindly to this, so he quickly sought out Lothagiel and killed and destroyed him while he was still unprepared. 

Even more interestingly, Nemuragh let slip that Lothagiel had left behind a lot of research notes. 
This piqued Teshrial's interest. 
So he turned up the charm. 
Nemuragh turned out to be rather weak-willed, easily swayed and seduced by a sexy Ketheran. 
Teshrial knows how to sweet-talk a Resvil, and sweet-talking a Resphan is easy compared to that. 

So one thing led to another, and \Teshrial and \Nemuragh ended up in bed together. 

\Menessiaraid: \ta{How was he?}

\Teshrial: \ta{Mmm, he was decent.}
\Teshrial strokes \Menessiaraid with a feather as if to say: 
\hypota{But not as good as you.}

After sex, it was a simple matter to convince Nemuragh to hand over Lothagiel's notes. 

This was a few days ago. 
Teshrial has been studying them intently ever since. 
It is interesting stuff, if frustrating. 
The notes are exactly that: Notes. 
They are fragmented, disjointed, ill-organized and clearly written for Lothagiel's personal use. 
So Teshrial has to piece together what Lothagiel knew and was trying to say. 
Still, there is much useful information in them, once deciphered. 

Menessiaraid: 
\ta{So, what does he say?}

Teshrial:
Well, Lothagiel studied a lot of astrology and Matrix theory. 
He had a hypothesis that Ishnaruchaefir goes through a period of weakness at regular intervals. 
A Nadir. 
Look, he has a look of Matrix-diagrams and star-charts. 
If Lothagiel's theories are correct, these equations should enable you to calculate when the Destroyer will be in his Nadir. 
Which, of course, would seem like the best time to attack him. 

Menessiaraid: 
Interesting. 
What does he base that on? 

Teshrial: 
There are some historical references, too. 
As far as I can determine, Lothagiel was trying to dig up evidence to verify his theory. 
See here. 
He has gathered a lot of data on sightings of the Destroyer.  

\Menessiaraid:
``Sightings? There cannot have been many of them. \Ishnaruchaefir has been reclusive ever since he became the Destroyer.''

Teshrial:
True, but Lothagiel has gone through millennia of records, so that still adds up to a fair number of sightings. 
Interestingly, the Destroyer was almost never sighted during the periods where, according to Lothagiel, he should be in his Nadir. 
Lothagiel interprets this as evidence that he is right. 

There is also one case that Lothagiel especially likes. 
It is the only recorded case where Ishnaruchaefir has gone into combat during his alleged Nadir. 
And it seems from the descriptions that he was uncharacteristically weak. 
Eventually he was beaten into fleeing from only a few \resphain. 

Menessiaraid: 
Fascinating. 
So, when will his next Nadir be? 

Teshrial:
I don't know. 
I do not understand the mathematics, and you know Matrix theory was never my strong point.
But I gather the Nadirs have become more frequent in time. 
In the beginning there were centuries between them, but nowadays there are only few years between them. 

Teshrial pages through the notes some more. 
``Grrr. All this damned paper. Could he not have written in on graph-glass like a civilized \resphan?
And I can't understand his mathematics, nor his astrology.
On top of it all, there is some cryptic poetry I don't understand.''

Menessiaraid:
``Where?''

Teshrial:
``Here. Look. Here is an excerpt from \WanderersInDarknessEmph.'' 

\WanderersInDarknessEmph is an epic poem. 
\Teshrial has not read any of it, but it is said to be full of disturing occult wisdom.
The lines read:



\begin{poetry}
  Then do the frosted waters rise in thirst to feast on worlds. 
  Then sinketh the Exile underneath with loud a rending cry. 
  Then gather thick the mists, then fadeth too the morbid moon
  upon yon labyrinthine space, and blood doth ashen flow. 
\end{poetry}



Teshrial:
``What is this supposed to mean?
  Lothagiel claims they prove his Nadir theory, but he does not explain himself, and I cannot understand what the lines mean. 
  The \quo{Exile} must refer to \ps{\Ishnaruchaefir} \vertex. 
  And there's a note here: 
  \quo{\Urizeth: waters = \bane \matrix}.
  What does that mean? 
  Who or what is \Urizeth?''

Menessiaraid:
``I think I know. \Urizeth is a \thelyad \resvil of \TiphredSerah, a student of literature and poetry\prikker and \matrix theory.  
  She is especially notable for being one of the few \resphain to have read the complete \WanderersInDarknessEmph.
  She has even written a treatise with analysis of the poem.''

\Teshrial:
\ta{%
  I did not know you were into that sort of thing, \Menessiaraid.}

It is an epic poem, Teshrial knows. 
Very long. 
Very occult and sinister. 
Written after the Incursion by \Melcryth, some mad \dragon.
Or so it was believed.
The poem is in Draconic, but the name \quo{\Melcryth} appears to be a pseudonym, and no one knows who hid behind it. 

\Menessiaraid:
\ta{%
  Oh, no. 
  I have not dared to read it myself.}
\WanderersInDarknessEmph is known to be very dark and wicked. 
Darker than Bane wisdom. 
Blasphemous. 
Full of chaos and evil. 
It is not something that you read in respectable Resphan circles. 
Few Resphain have read it. 
It is said there are Resphain who have lost their minds from trying to understand it. 
\ta{But I have an interest in poetry and mythology, so I like to keep myself informed.}

(Read about \maybehr{Resphain and forbidden books}{\quo{forbidden books} in \resphan culture}.)

Teshrial is \skeptical. 
But Menessiaraid is a connoisseur of poetry, and he is not stupid. 
\Menessiaraid{}'s area of study is religion and mythology.
He has helped shape the dogma and world-view of more than one puppet religion in the Shrouded Realms.
He knows mythology is serious business.
So he might have a point.
So if he says it, Teshrial will not discard it out of hand.

\Teshrial: 
\ta{Hm. \WanderersInDarknessEmph.
  Is it a lead worth pursuing, I wonder?}
  
Menessiaraid:
\ta{%
  It could be.
  I know there are some who believe that the poem is about the sons of \TyarithXserasshana\dash Ishnaruchaefir and his brothers. 
  That they are meant to be the Wanderers to whom the title refers.}

Teshrial:
``Really?'' 

Menessiaraid:
\ta{%
  \WanderersInDarknessEmph is said to be full of riddles and deep symbolism. 
  It is widely believed that it holds much powerful knowledge in its verses, if only one has the wit\dash and the daring\dash to read and interpret it.}

Teshrial:
\ta{Hm. 
  I am \sceptical, but I know you know what you are talking about.
  Very well.
  I will do as you say and look into the myths.}
The thought makes \Teshrial uneasy.
He looks at the notes again. 
Skims the various \emph{Wanderers} excerpts in \ps{\Lothagiel} notes.
They make him uneasy.
They make his feathers twitch. 
The words do seem to hint at some deep, dark truths. 
It is disturbing to look at. 
He is not comforted by the thought of having to read it in detail and actually try to understand it.
He confesses as much to Menessiaraid. 

Menessiaraid: 
\ta{%
  True. 
  Moreover, you are no poet nor astrologer, Teshrial.
  \WanderersInDarknessEmph has defied the scrutiny of many learned occultists. 
  If you seek to unravel its secrets, I think you should seek help from an expert.}

\Teshrial:
\ta{Good idea.
  Hm. 
  An expert.
  What about this \Urizeth?
  Does she still live?}

\Menessiaraid:
\ta{I think so, yes.}

\Teshrial: 
\ta{Then maybe I should try to ask her. 
  Lothagiel names her multiple times.
  He seems to have much faith in her interpretations.}

\Menessiaraid: 
\ta{She is \TiphredSerah, though.}

\Teshrial: 
\ta{I have \TiphredSerah contacts. I can call in some favours.}

\Menessiaraid: 
\ta{Good idea. You do that.
  A word of warning, though.
  I have heard \Urizeth is quite strange.}

\Teshrial:
\ta{(Mocking) Really? 
  A \TiphredSerah astrologer and poetry analyst? 
  Why would you think that?}









