\bookchapter{The Thirsty Nether}
\begin{comment}
\section{Rian and the Black Plague}
\end{comment}
\stamp
  {\dateRianSeesMagicRitual}
  {Southern slums, \hs{Malcur}}
\begin{comment}
\subsection{Dangerous ground}
\end{comment}

A board creaked underneath Rian. 

\tho{%
  Crap! Must be quiet.
  
  There're \hs{plaguers} around here. 
%   There's no room for mistakes this time. 
  If I get caught again, I'm done for.}

Jorgen's warning had scared Rian enough to make him stay away from the Black Plague territory... so far.  
But he could not just twiddle his thumbs. 
He had continued his investigations, snooping around the city and asking questions of all the people he could think of. 
And just yesterday, he had received a tip about Black Plague activity in an area in the southern slums, not so far from where he used to live. 
It might be a red herring like many other leads, but he knew he had to investigate. 

So here he was, sneaking along the rooftops. 
That was one lesson he had learned from his run-in with Jorgen: 
Stay off the streets if at all practical. 
It was slow going, especially in the dark, but it helped. 
He had passed several people, some of whom might be plaguers, but so far he believed he had managed to escape detection. 
% He would freeze at every sound, every glimpse of light. 
% Even every smell. 
% But he had penetrated further into their territory than last time. 
% Further than he had ever wanted to come. 

\tho{%
  If only I knew what I was looking for, it would be easier. 
  
  I'm just stumbling blind.
  Literally. 
  I can't see a thing in this darkness, and skulking around like this doesn't exactly give me a great overview of what's going on. 
  
  I must be crazy.}

Then he heard footsteps on the street behind and below him. 

\tho{Someone's coming!}

He lay down flat on the rooftop and listened. 

The footsteps came closer. 

\tho{More than one person. Probably \scathae.}

He could hear voices now. 
\tho{Yes, definitely \scathae.}

\ta{%
  Shame we didn't get to snag that \sphyle{} from before,} 
one of the \scathae{} was saying. 
\ta{%
  She was a nice little thing. 
  I wouldn't mind letting her do her thing on my gnesses.}

\tho{%
  \quo{Snag}? 
  Kidnappers? 
  Plaguers?}

\ta{%
  Dream on,} said the other one.
\ta{%
  You know how picky the sorcerers are.
  \quo{No tampering with the prisoners} and \quo{bla bla bla}.}

\tho{%
  Prisoners? 
  
  Prisoners! 
  This is a clue!
  Neina!}

The pair had now passed by him and thus presumably had their backs on him, so he dared inch closer. 
\tho{%
  But they're plaguers.} 
All the anxiety he had felt when last sneaking up on the plaguers came back to him. 
\tho{%
  Plaguers. Mean bastards. They'll kill me without a second thought.}

As he crept he was very conscious of every noise he made. 
Every breath sounded like a gale. 
Every crawling step like a thunderclap. 
% He kept so low he could smell the moist wooden boards under him. 

He reached the edge of the roof and peered down. 
There were indeed two \scathae, wearing dark coats with hoods. 

\ta{I tell you, this sorcery makes my piss cold,} said the one. 

\tho{Sorcery?}

\ta{What's the matter?} the other one taunted. 
\ta{Want your eggshell back?}

\ta{Shut up.}

\tho{%
  They must be plaguers.
  I've got to follow them. 
  But \Sephiroth{} help me.
  \quo{Sorcery}. 
  That's not good.
  But \quo{prisoners}.
  That's good. 
  \quo{No tampering with the prisoners}.
  That's also good.
  If any of these scum try to hurt Neina I'll kill them.
  I should kill them just for considering it.
  And for calling it \quo{tampering}.
  Damn them. 
  \Iquin{} damn them.}

The two bandits turned around a corner. 
He followed them as best he could, but it was hard tailing them from the rooftops. 
He had to sneak snowly to prevent the boards from creaking. 
\tho{%
  Grith Ecallivan could probably hop from root to roof, as silent as a cat. 
  I can't do that.
  But I'm still a good climber.
  I can do this.
  I'm small and nimble, and I've skulked around on roofs plenty of times.
  I know how to get around without making noise. 
  I can do this.} 

He had to slow down as he passed over some ramshackle buildings with half-rotten roofs. 
\ta{Damn. Some of these could collapse any day.}

The two thugs crossed a street. 
Rian snuck to the edge of the roof, hoping to leap over to the next one. 
He stood still and quiet, scouting with his eyes, ears and nose. 

He could see nothing auspicious.

\tho{%
  Coast looks clear.
  
  No, wait!
  
  A sound.
  
  Snoring.
  Muted shuffling.
  
  A smell. 
  Beer. 
  And something ugly. 
  Might be vomit.
  
  The sound's coming from... over there.} 

He squinted down into the street, and thought he perceived a humanoid form seated near a wall. 
\tho{%
  A drunk. 
  Asleep. 
  Maybe deeply. 
  But maybe not. 
  I can't chance jumping over right on top of him. 
  I'll have to take a detour.}

He crept left until he felt he was far enough away to not awaken the drunk, then jumped across. 
\tho{That wasn't completely silent. Still, none too shabby.}

\tho{All right. Now to catch up with those two.}

He hurried along the rooftop as fast as he dared.
\tho{Where are they?}

He looked down from the edge. 
Nothing. 

He held himself still and listened for their footsteps. 
Nothing. 

He ran ahead and peeked down some streets.
Nothing. 

\tho{%
  Crap. I've lost them.
  
  All right. 
  Focus, Rian.
  I've tailed people before. 
  A bit.
  I can sniff them out. 
  Trust my instincts.}

He remembered Dennick's words from one of his philosophical moments.
\hypota{%
  Y'know,} he had said.
\hypota{%
  It's a dog-eat-dog world, kid.
  There are three worlds in this world, and all three are dog-eat-dog. 
  There's civilization, in there, with the castle and the churches. 
  In there, it's intelligence and social graces that count. 
  That's what makes you great, what makes you a duke or king or mage or whatnot. 
  In there. 
  And then there's the \hr{Wild}{\Wylde}, out there beyond the walls.
  In the \Wylde{}, you gotta be fast, and you gotta have a sharp nose and a gut that can feel trouble. 
  You gotta have your animal instincts. 
  And then there's the slums, down here. 
  We're halfway between them. 
  We have houses and city walls, true, but walls alone do not civilization create.
  Our home is half city and half \Wylde{}. 
  That's why you'll need both skills to survive here: 
  A sharp wit and a gut instinct.}

Dennick had been smoking some pretty strong weed at that time, but what he had said made sense to Rian. 
\tho{%
  I've survived this far because of my mind and my instinct. 
  I have my street rat intuition. 
  I can think like a thief, feel like a thief. 
  Now I need that intuition. 
  Gotta think like the hunter.
  
  If I were them, where would I be?

  I would be... down this way.}

It was a guess, but it felt right. 
He skipped along the rooftops, keeping eyes and ears wide open. 
And true enough. 
Soon he could hear footsteps and voices. 
He snuck closer, as fast and quiet as he could, and listened. 

\tho{%
  Same steps. Same voices. It's them!
  I did it!
  I don't know if it was intuition or pure luck, but who cares? 
  I'm back on the trail.}

\begin{comment}
\subsection{Sentinel building}
\end{comment}

He managed to stay on their tail this time. 
They passed some streets and alleys, turned some corners, until finally they came to a suspicious-looking building. 
Large, and somewhat taller than most other single-storied buildings. 
\tho{%
  I don't like that building. 
  I don't like the smell of it. 
  There's something strange about it.}

The thugs approached a door in the side of the building. 
Guarding the door were two bigger thugs, a \hr{Dax}{\dax} and a man. 
The two \scathae{} he had followed exchanged some gruff words with the guards, then went in. 

\tho{%
  It must be a plaguer hideout.
  I need to get a closer look.
  
  I'll try to sneak inside.
  
  Wait, what am I saying?
  Sneak inside? 
  Am I crazy? 
  I'll get caught and killed. 
  No. 
  Inside is bad.
  Outside is good.}

He looked at the building again.
\tho{%
  It has a nice, flat roof. 
  If I can get on the roof, maybe I can spy on them and find out something. 
  That's good. 
  That's a plan. 
  Get on the roof and peek.
  
  How do I get on the roof?}

He tried to lean out, but lost his footing on a fragile plank and had to leap backwards to keep from tumbling down into the street. 

This made a nasty \hypota{thump-crackle} noise. 

\tho{%
  Crap! 
  The guards must have heard that!}
He dropped flat. 
Below he heard the guards talk and hustle around.
\tho{They heard me, all right.}

He lay still and tried not to breathe. 
Tried not to move a muscle. 
He could feel cold sweat running down his neck. 
His face was pressed against the planks, filling his nose and mouth with the smell and taste of wood. 

A very, very long moment passed.

He could hear one guard walking around, trying to get a better look up at the roof. 
\tho{Dear \sephiroth, don't let him see me. Please. Don't let him see me.}

\ta{Can you see anything?} the \dax{} called in a low voice. 

\ta{Nah, I can't see nothing,} Rian heard the big man say. 
\ta{Must've been a big rat. You know how big they grow around here.}

Rian heard the guard returning to his place by the door. 
He lay still a while longer until he was sure the danger has passed.
\tho{%
  They might be faking it. Maybe those words were for my ears, and they're really camping down there and waiting for me to get overconfident and make my move.
  
  But I can't stay here.
  I have to move.}

He crept to the edge and looked around. 
They did not seem to be lying in wait for him. 
\tho{OK. Looks like they bought it. Now to move on.}

There was some light in the plaguer building, so he could actually \emph{see} a bit this time. 
\tho{%
  I can't jump over. 
  The guards would hear me.
  I'll have to get down and find a spot to climb up.
  But the building is kind of tall. 
  It won't be easy to climb up on it.
  I'll need to find a good spot.}

He crawled around, skirting the building, making sure to steer clear of the guards and keeping an eye out for others. 

\tho{There! A barrel. It looks solid. I can use that.} 

He looked and listened around. 
Around the corner he could hear the two guards talking and joking. 
\tho{Coast looks clear.}

He climbed down, as quietly as he could, and snuck across the street to examine the barrel. 
\tho{%
  By the smell, there's been beer in it. 
  Now it's empty. That's not good. 
  I'd hoped it'd be full. That would make it more stable.
  But it'll still do.}
Carefully, he climbed up on the barrel, reached up, grabbed the edge and pulled himself up on the roof. 

\tho{Did anyone hear me? No, I think I'm safe.}

He examined the roof. 
\tho{There's light over there. Looks like a hole.}

He crawled over there. 
It was indeed a hole. 

\tho{%
  What's that smell coming out of it?
  Smells kind of like a... church. 
  Incence?}

The hole was small, about a hand's breadth at its widest point. 
He peered down. 

A room. 
With people in it. 
Moving around. 
Talking. 
Several armed thugs. 
Some prisoners. 
Gagged and tied to the ground. 

\tho{Prisoners! Neina!}

He could only see a tiny portion of the room at once, so he had to move his head around a lot to scan the room. 
\tho{%
  I see four prisoners. But no Neina. Where is she?}

One of the prisoners was a young \human{} girl. 
She was naked and restrained, and squirmed feebly while a big, ugly \human{} thug laughed and groped her. 

\ta{You!} came a \ps{\sphyle} voice. 
\ta{Knock that off!}

\ta{Yes, \Mistress,} said the thug and withdrew. 
\ta{Sorry.}

\tho{Who was that?} 

He moved around until he caught a glimpse of a a \sphyle{} in a fine carmine robe. 
\tho{That must be her.}
She wore several talismans\dash bones, teeth, metal symbols\dash and carried an ornate stylus made of what looked like bone. 
Clearly the most expensive-clad of the bunch, and evidently a leader. 

\tho{Is she one of the sorcerers they mentioned?}

She ordered the bandits around, having them set up burning braziers and securing the prisoners. 
\tho{Braziers. Incence. That was what I smelled.}
The \sphyle{} herself was busy drawing some strange symbols on the floor. 

\tho{%
  Light. Look at those symbols. She must be a sorceress.
  But what is she doing? And why the incence?
  What magic are they working? 
  What's going to happen here? 
  
  What's going to happen to the prisoners?}







\begin{comment}
\subsection{Moro Cornel observes}
\end{comment}
\new
From across the street, Moro \Cornel{} hid in a rotting hut and observed the Black Plague hideout. 
\tho{%
  The spell is set up. 
  It will begin soon. 
  I can feel it.
  
  I wonder who the boy is...}
She had seen the \human{} boy crawl up on the roof. 
Or, not exactly \quo{seen}. 
She was old, and her eyes were not the best. 
But she had all her mystic senses open, with all the spells she had dared cast for fear of being discovered, and she had detected him. 

\tho{%
  Who is that boy? 
  Judging by how he skulked around, not one of the Plague. 
  A third party? 
  Someone from a rival guild? 
  
  And what is he to me?
  Another enemy? 
  Or someone potentially useful?} 

Then she felt sorcerous vibrations coming from the house. 
The threads were stirring. 
She put the kid out of her mind for the time being and focused on important things. 

\tho{It is beginning.}







\begin{comment}
\subsection{Sacrifice}
\end{comment}
\new
The sorceress had begun chanting gruesome words in some wizards' language that Rian did not understand. 
She was reading from a book on a stand in the middle of the room. 
The three prisoners had been bound with nails hammered into the ground. 
Apparently at some strategically important locations, judging by the lines of those symbols inscribed in the floor. 
\tho{%
  That's what magic is like,} he recalled from stories.
\tho{%
  There's lines and squares and circles and stars and stuff.
  The magic is in the forms.
  And maybe in the colours. I don't know. 
  And in the words and the hand-waving and the stylus and things.}

Over each prisoner stood a bandit with a knife.
\tho{%
  I don't like the looks of that one bit. Poor people. I wish I could save them.}

The sorceress chanted on. 
\tho{Invoking the names of evil gods,} Rian guessed. 
And slowly he began to feel it. 
There was something in the air. 
It prickled his skin, in those places he couldn't reach. 
It howled and hissed in his ears, just at the edge of hearing. 
It stung his nose, like the faint trace of corruption in a piece of food that was going bad. 
\tho{%
  Oh, Silqua. 
  Magic. 
  There's magic in the air. 
  \Sephiroth{} help me. 
  I've wandered into a dark wizard's den!}

Now he could even see it. 
Shapeless flashes of light in strange, abnormal colours dashed through the air. 
The diagrams in the floor lit up, seemed to vibrate. 
As if seething. 
Coloured smoke began to fill the room. 

\tho{Mmmmmmmmmph!}

The naked girl from before screamed as loud as she could under her gag. 
Rian looked back to her.
The bandit sat crouching over her. 
In one hand he held a knife just over her head. 
With his other hand he fondled her small breast. 
\tho{That disgusting pig. \Itzach{} damn him.}

\ta{Now!} he heard the sorceress call. 

And the bandit swung the knife and slashed the girl's throat. 
She gargled weakly as her blood gushed out on the floor.

But the blood did not just spread in an even pool. 
It was sucked towards the magical lines. 
It spread along those lines, and only those lines. 
The lines turned red and began to glow and pulsate. 
\tho{%
  \Iquin! I don't believe it! The lines are drinking her blood! What evil is this?}

All of a sudden, the dying girl's body convulsed. 
It bloated out in all sorts of places. 
Within moments she became horribly deformed. 
Her face swelled, her mouth growing as broad as a \ps{\meccaran}. 
Then the skin broke and blood spurted out. 
It was as if the body exploded and at the same time collapsed in on itself. 
\tho{Like a tomato that bursts open when you squeeze it.}
She twisted and warped into a horrid, deformed husk. 
What remained of her skin faded and became parched and blotched as all blood\dash all life\dash was violently sucked out of her. 

Rian could not bear to see any more. 
He looked away. 
\tho{%
  Sweet Silqua!} 
He recited the names of all the \sephiroth:
\tho{% 
  \Atzirah, \Razilah, \Keshirah{}, \Feazirah. 
  \Barion{}, \Teshiron, \Izion, \Hapheron. 
  \Thimared, \Yemared, \Cushed, \Hoshied. 
  \Omariel, \Yeziel, \Ishiel{}, \Gamishiel! 
  
  This is awful! 
  Awful! 
  What they did to that poor girl... 
  Maybe they mean to do the same to Neina.
  Kill her and feed her to their evil magic!
  
  Maybe they already have...
  
  No! 
  No.
  No.
  No. 
  She's still alive. 
  Neina is alive. 
  She is. 
  
  I've got to get her out of there.}

Then a wave pulsed through him. 

It felt like nothing he knew. 
As if all his inner organs got squeezed and rearranged for a brief instant. 
As if the ground heaved, like a thin blanket with someone crawling underneath it. 
Nausea swelled up in his throat, and he had to fight an urge to throw up. 

\tho{%
  It's an earthquake!
  
  No... wait. 
  It's not. 
  The ground's not moving. 
  The roof's not shaking. 
  
  Was it all me?
  Was it all in my head?
  
  It's the evil magic. 
  It must be. 
  I can feel the evilness. 
  It's seeping into my body. 
  My head. 
  My soul! 
  \Sephiroth{} preserve me. 
  \Sephiroth{} preserve us all!}

His body was shaking. 
His bowels convulsed. 
His head throbbed. 
He closed his eyes and shook his head, trying to clear it. 

Then opened them and looked down through the hole again.

\tho{What in \Itzach{}...?}

The sorceress still stood in the middle, waving her stylus around and chanting those ugly words, a manic look on her face. 
And around her, the room had changed. 
The floor had changed. 
Before it had been dirt. 
Now it looked like... flesh? 
Dry flesh, like a sickened and desiccated corpse. 
Gray. 
Dusty. 
Dead. 

No. 
Not quite dead. 
A few places, faint lines of pink could be seen. 
Throbbing. 
Pulsating. 
\tho{%
  Veins? 
  Flowing with blood?
  What evil is this?}

And there was more. 
The view was unclear and sketchy somehow, but he thought he could perceive... chains? 
Huge metal chains trailing away. 
Up into nothingness. 
Or down into nothingness. 
As if connecting this world to some other, horrid world. 
Grinding. 
Groaning.
As if... pulling... something. 

\tho{%
  By \Iquin{} and \Itzach! 
  What is going on? 
  What are they doing?}

\begin{comment}
\subsection{Discovery and flight}
\end{comment}

Rian's mind could not cope with the alienness and the horror of it.
Nor could his body. 
His elbow slipped. 
He stumbled and hit his head and shoulder against the planks with a loud thump. 

\ta{Owww...}

One of the bandits looked up at the sound. 
Scanned the ceiling. 

Their eyes met. 

\tho{Oh no!}

\ta{A spy!} shouted the bandit. \ta{Up on the roof!}

Rian immediately ducked away. 
Below he heard the sorceress: 
\ta{What? Where? Find him! Kill him!}

\tho{%
  Light!
  I gotta get out of here!}
He scrambled across the roof. 
\tho{Gotta get away before she blasts me with her evil magic.} 

He reached the edge of the roof. 
\tho{%
  Hop to the next roof?
  No. 
  Running on rooftops would be too slow. 
  And dangerous, here in the dark.
  I could fall and break my neck.
  No, I can run faster on the ground.}

He took a short run and leapt down to the ground. 
Rolled when he landed. 
Jumped to his feet. 
And ran as fast as he could into an alley. 

\tho{They're onto me.}
He could hear the plaguers behind him. 

He ran into a new alley. 

\tho{They're still onto me.}

A bandit sprang out of nowhere in front of him. 
It gave Rian a shock, but he tried hard not to panic. 
\tho{I've been chased before. I can do this. Instinct.}
So he did not slow down. 
Instead he jumped into the air and gave the bandit a knee in the face. 

\tho{Suck it, plaguer scum.}

He leapt over a fence and into a new alley. 

\tho{%
  \Itzach. I'm history. I can't keep running. They know this place better than me. They'll catch me sooner or later.}

There was an open door down the alley. 
A figure in the door. 

\tho{%
  Crap! Another one!}

He was just about to turn around and look for another way.
But a feeling occurred to him. 
\tho{%
  Wait. 
  This one feels different.}
He could not \emph{see} any difference, but this figure somehow \emph{felt} different from the plaguers. 
Maybe it was the smell. 
He didn't know. 

The figure beckoned to him, and it seemed to him that it looked him in the eye. 
\tho{%
  Is it a friend?
  Another one like me who's up against the plaguers? 
  
  No! 
  What am I thinking? 
  I must be crazy!
  
  But all other escape routes are blocked. 
  I can hear the bandits closing in from behind.
  
  This is my best bet. 
  Trust my gut feeling. 
  I have no choice. 
  I'm going for it.}

He ran towards the figure. 
It stepped aside. 
He ran through the door. 
The figure closed it. 

\ta{This way,} she said. 
She. 
A \sphyle. 

She led him through another door. 
And another. 
And into an alley.
A street. 
Another alley. 
Into a house. 

She closed the door behind them. 

\ta{I think we lost them,} she sighed. 

There was a little light in this room, allowing him to get his first real look at her. 
She was old. 
And ugly. 
Her scales might once have been violet, but now they were faded to a mottled grayish colour. 
Many of them were peeling off. 
Her right eye drooped somehow. 
She was leaning on a table and panting. 
\tho{The exercise must have been damned hard for someone her age.}

\ta{Thanks. You saved me. Who are you?}

\ta{Who are you?} she snapped back. 

There was exhaustion in her voice. 
And a deeper weariness and bitterness in her eyes. 
But behind that there was... a kind of strength? 
A jagged, brittle kind of strength. 
It scared Rian. 
He dared not but answer truthfully. 
\ta{I'm Rian. The... uh... carpenter.}

\ta{Carpenter?} 
She licked her drooping eye. 
The motion looked icky. Rian repressed a disgusted grimace. 

She looked away.
Repressed a grimace of her own. 
\ta{What are you doing here?} she asked without looking at him. 

\ta{%
  I'm looking for my girlfriend! 
  The plaguers took her.
  Why are you here?
  Are you trying to oppose the plaguers, too?
  Did you see what they were doing there?
  Did you see the evil magic?
  It was awful! 
  They're up to something terrible!}

\ta{%
  You shouldn't be here.
  You shouldn't be messing with this.}

\ta{%
  But what they're doing is wrong! Evil! 
  They killed those people! And they'll kill Neina, too!
  Someone has to stop them. 
  We have to go to the guards!
  The church!
  The duchess!
  The Black Plague are up to something terrible, and they've got to be stopped!}

\ta{Listen, boy!} she hissed. 
\ta{%
  You are in far over your head. 
  You are not the one to stop those sorcerers. 
  You can't do anything. 
  You shouldn't even be here.
  You'll only get yourself killed.}

\ta{%
  But I have to! For Neina. If I don't save her, who will?
  You can help me!
  You have to help me!}

She turned away. 
\ta{I can't help anyone.} 

\ta{Yes, you can. You just helped me...}

\ta{\shout{No}!} 
She looked at him with eyes full of pain. 
Grief. 
Impotent anger. 
She turned away again. 
\ta{I can't help you. Go away.}

\ta{But...}

\ta{Go away.}

Rian stared at her back, trying to think of something to say. 
Nothing came to mind. 

He turned towards the door. 
Grabbed the handle. 

Then paused. 
Looked at her again. 

She hadn't moved. 

He sighed. 
Then left. 







\begin{comment}
\subsection{Moro Cornel grumbles}
\end{comment}
\new
Moro \Cornel{} stayed in the hut after the kid\dash Rian\dash had left.

\tho{%
  Stupid boy. 
  And \naive. 
  Blurting out your name and life story to a complete stranger. 
  You should not open yourself up to people like that.
  Nothing good will come of that. 
  You're from the slums, I could tell. 
  Life in the slums should have taught you that much.
  Nothing good comes of trusting people.
  I know.

  Why did I even save him? 
  I know better than that. 
  Don't go around trying to help people. 
  It never helps. 
  They only grow dependent on you, and then blame you when life finally catches them. 
  I am not out here to make friends. 
  I know better than that. 
  I work alone.} 

She left the building and headed back to her chambers in the \ishrah{} tower. 

\tho{%
  I work alone. 
  I \emph{am} alone. 
  That is who I am.} 








\begin{comment}
\section{Rian and the guards}
\end{comment}
\placestamp
  {Northwestern Citizens' Quarter, Malcur}

Rian ran through the streets. 
\tho{%
  Guards! Where can I find some city guards?
  \Iquin{} damn them.
  Back when I was stealing and didn't want them around, they were always there breathing down my neck, trying to catch me and throw me in jail. 
  Now that I need them, they're nowhere to be found.
  
  Wait! 
  What's that over there? 
  Torchlight.
  That must be a patrol.}

He followed the light. 
True enough, it was carried by two \scathaese{} city guards. 
He ran up to them and grabbed the arm of one. 

\ta{\Mr{} guard! You've got to come help me!}

\ta{%
  Whoa!
  Let go of me, runt!} 
The guard backed away, shaking him off. 
\ta{%
  What are talking on about?
  And what are you doing outside at this hour?}

\ta{%
  You've got to come. 
  It's the Black Plague. 
  And a sorceress. 
  They're out there working their evil magic.
  Drawing evil symbols and summoning monsters. 
  They killed a girl! 
  I barely escaped with my life!}

\ta{%
  Kid!} 
The guard lifted his hand as if to slap him. 
Rian shrank away on reflex.
\ta{%
  Stop blabbering. 
  Now, what are you on about?
  And this had better be good.}

\ta{%
  Right. 
  No blabbering.
  Right.}
Rian took a deep breath. 
Then told the whole story of the Black Plague hideout and the sorcerous ritual, leaving out only the details of his flight and the mysterious \sphyle. 
He had a feeling she would not want him to mention her. 

\ta{So you see,} Rian said, \ta{you have to go and stop them.}

The guard turned to his buddy.
\ta{What do you think?}

The other guard gave Rian a disapproving look. 
\ta{%
  I think we got us one of them fear-mongers we're supposed to look out for.}

\ta{Yeah, you're right.}
The first guard turned back to Rian. 
\ta{%
  They warned us about troublemakers like you.
  Get out of here!} 
He shoved Rian away. 
\ta{%
  And shut your trap.
  Stop spreading your stupid lies. 
  That's an order directly from the duchess. 
  And the church. 
  If we catch you telling fairytales again, we'll beat the crap out of you!
  Get that?
  Now beat it!}

Rian stood dumbfounded. 
\tho{%
  What? There's evil mages loose in the city killing people and they don't even want to hear it?}

\ta{Didn't you hear us?} the other guard growled. 
She hefted her mace. 
\ta{We don't want your rumours here. Now scram!}

Rian ran. 

\tho{%
  What was I thinking?
  Going to the city guards. 
  I must have been stoned out of my head.
  I should have known they wouldn't listen. 
  The guards are nothing but mean bullies. 
  They hate people from the slums. 
  \quo{Duchess's orders}. 
  Yeah, right. 
  They say they're fighting criminals and bad guys, but we all know they just beat up people for fun. 
  
  With thugs, at least you know where you have them. 
  But the guards... they're the worst kind of scum. 
  How could I have thought they would help?
  
  It's the last time I'm trusting them with anything.}









\begin{comment}
\section{Needle and her spy}
\end{comment}
\placestamp
  {Slave quarters, \CastlePelidor, Malcur}

In her hands Needle held the metal-wrapped scroll \Achsah{} had given her. 
She caressed it slowly, reverently. 
Like the precious treasure it was. 

\tho{%
  So. 
  My Cabalist underlings have located a Sentinel hideout in the southern slums. 
  They are going down. 
  
  But I can't take them on directly.}

She held up the scroll.
\tho{Looks like I will need this.}

She took the scroll out of its fine metal casing. 
Unrolled it. 
It was short, about two feet long, and only half of that length was filled with text. 
Vaimon letters in a very archaic-looking script. 

\tho{Time to put it to use. For the first time.}
She took a deep breath. 
\tho{Here we go.} 
She knelt down on the floor, lay the scroll in front of her, then bent down over it and began to recite the \hs{orison}. 

Needle was a poor reader, having learned to read as an adult, but she had spent many evenings studying the precious scroll, and by now she almost knew the text by heart. 
She did not understand all the words, but she recognized \ps{\Achsah}{} name, and those of several \qliphoth. 

She got through the entire spell. 

Then waited. 

Nothing. 

\tho{%
  Maybe I should repeat it.} 
Sometimes it was necessary to repeat a spell several times, she knew. 
Needle had been studying magic for many years, but she had been quite old when she began, and she had never been able to devote much time to her studies. 
She had little free time as a slave, and her magic had to be kept secret. 
So, to her chagrin, she had never amounted to more than a novice Vaimon. 

She started over and recited the whole thing again. 
This time she could feel the \qliphoth{} stirring, touching her mind with their mystic fingers. 

But still no reply. 

\tho{I must be patient.}

She started over a third time. 
She felt the \qliphoth{} drawing closer, felt some of their energy flow into her body. 
It was a stinging, simmering sensation. 
It dulled the senses, but at the same time seemed to somehow sharpen them. 
Almost like \dvingen{} root. 
She had chewed raw \dvingen{} root a couple of times. 
The root gave a euphoric numbness, combined with a\dash perhaps deceptive\dash feeling of one's senses being expanded. 
That was the closest thing she could think of to describe this feeling. 

\tho{Wait!}

There was something new. 
In her head. 
Not a \qliphah. 
A more tangible presence entering her mind. 
Massive. 
Overshadowing everything. 

A voice sounded. 

\tele{Needle.} 

\tho{%
  \ps{\Achsah}{} voice!
  So beautiful.}
The voice felt warm and cold at the same time. 
Imperious, like a queen. 
But also loving, like a mother. 

\ta{My lady \resvil,} she managed. 
\ta{I am your humble servant.}

\tele{You contacted me?}

Needle pictured the \ps{\resvil} perfect face. 
Her smooth, dusk-gray skin and curled locks of raven-black hair. 
Her eyes, silvery like the moon. 
Her lips, sparkling like the starry sky. 

\ta{%
  Y-yes, my lady \resvil. 
  I have good news. 
  I have located a Sentinel stronghold. 
  I hope to be able to raid it and strike them a hard blow.}

\tele{But?}

This was the part of the conversation Needle had feared. 
She did not want to show weakness and beg for her goddess's help. 
But she had to. 

\ta{%
  I am afraid to attack it, my lady \resvil.
  We lack manpower. 
  My reports tell me they have at least one sorcerer, possibly more.
  I can lead the attack, but I have only few men at my disposal, and fewer still who stand any chance against mages.}

\tele{So...}

Needle paused to collect herself.
\ta{%
  So I pray to you, my lady \resvil. 
  I humbly beg that you grant me aid to counter the Sentinel sorcerers, that I may serve your will.}

Silence. 

\tho{Should I say more? No. Better stay quiet.}

Finally \Achsah{} spoke again. 
\tele{%
  Sorcerers, you say? 
  Very well. 
  I will send you some aid.
  Yes. 
  I will gift you some of my \banerats.}

Needle bowed so her face touched the floor. 
\ta{%
  Thank you, my lady \resvil, for this honour. 
  I will not fail your trust.}
\tho{What on \Miith{} are \banerats?}

\tele{I hope not. Now listen carefully...}










