\chapter{Timeline}















\section{Pre-History}















\section{\Ophidian{} Age}
\begin{timeline}
  
  \timeitem{First Banewar}
  \Firstbanewar{} begins. 
 
\end{timeline}
















\section{\Saphyraean{} Age}
\begin{timeline}

  \timeitem{XS} 
  \Tiamat{} summons the \xzaishann. 
  
  \timeitem{Nexagglachel birth}
  \hr{Nexagglachel}{\Nexagglachel} born. 
  
  \timeitem{Ishnaruchaefir birth}
  \hr{Ishnaruchaefir}{\Ishnaruchaefir} born. 
 
\end{timeline}















\section{Age of \Draconian{} Supremacy}
\begin{timeline}
  
  \timeitem{Secherdamon birth}
  \hr{Secherdamon}{\Secherdamon} born. 
  
  \timeitem{Scathae created}
  First \hr{Scatha}{\scathae} created.  
  
  \timeitem{Thanatzil birth}
  \hr{Thanatzil}{\Thanatzil} born. 
  
  \timeitem{Merkyrah falls}
  The \hs{Murder of the Dawn}. 
  \Merkyrah{} falls. 
  
  \timeitem{Satharioth}
  \hr{Origin of Satharioth}{\Satharioth{} are born}. 
  
  \timeitem{Second Banewar ends}
  The \secondbanewar{} ends. 
 
\end{timeline}















\section{Age of Gods}
\begin{timeline}
  
  \timeitem{Cuezca rises}
  \Cuezca{} rises. 
  
  \timeitem{Cuezcan Apocalypse}
  The \hr{Cuezcan Apocalypse}{\CuezcanApocalypse}.
  
  \timeitem{Cordos Vaimon birth}
  \hs{Cordos Vaimon} born. 
  
  \timeitem{Silqua birth}
  \hr{Silqua}{Silqua \Delaen} born. 
  
  \timeitem{Silqua wed}
  Cordos Vaimon marries Silqua \Delaen. 
 
\end{timeline}















\section{\Human{} Age}
\begin{timeline}
  
  \timeitem{Founding of the Vaimon Caliphate}
  Cordos Vaimon founds the \VaimonCaliphate. 
  
  \timeitem{Grith Ecallivan birth}
  \hs{Grith Ecallivan} born. 
  
  \timeitem{Vizicar birth}
  \hr{Vizicar}{\VizicarDurasRespina} born. 
  
  \timeitem{Belzir birth}
  \hr{Belzir}{\Belzir} born. 
  
  \timeitem{Darkfall}
  The \hr{Hundred Scourges}{\Darkfall}. 
  The \VaimonCaliphate crumbles. 
 
\end{timeline}















\section[Scatha Age]{\Scatha{} Age}
\begin{timeline}
  
  \timeitem{Fall of Ortaica}
  \Ortaica{} falls. 
  
  \timeitem{Founding of Imetrium}
  The Imetrium founded. 
  
  \timeitem{Fall of Tepharae}
  \Tepharae{} falls. 
  
  \timeitem{Eresh-Kal flourished}
  \EreshKal{} flourishes. 
  
  \timeitem{Eresh-Kal destroyed}
  \EreshKal{} falls. 
  
  \timeitem{Cuthran the Victorious birth}
  \hs{Cuthran the Victorious} born. 
  
  \timeitem{Founding of Belkade}
  \GreatVelcad{} founded. 
  
  \timeitem{Fall of Belkade}
  \GreatVelcad{} falls. 
 
\end{timeline}















\section{The Time of the \Thirdbanewar}
\begin{timeline}
  
  \timeitem{Carzain birth}
  \hr{Carzain}{\CarzainDeracilleShireyo} born. 
  
  \timeitem{Runger war}
  King Morgan Runger declares war on Pelidor. 
\end{timeline}









































