
\chapter{Tropes}
\begin{flushleft}
\section{Tropes I hate}
\begin{description}
  \item[Author Filibuster] 
  \item[Balance Between Good And Evil:] 
    Subverted, see section \ref{Balance of the Matrices}.
  \item[Beauty Equals Goodness:] Subverted with the \resphain.
  \item[Can Not Spit It Out] 
  \item[The Chris Carter Effect] 
  \item[ContrivedStupidity] and all subtropes. 
  \item[Designated Antagonist] 
  \item[Did You Just Punch Out Cthulhu?]
  \item[Dumb Is Good]
  \item[Dungeon Master]
  \item[The Force:] Subverted with \iquin{} and the \sephiroth.
  \item[Hero Ball]
  \item[Humanity is Superior]
  \item[Humans Are Special:] 
    Brutally averted: 
    \hr{Humans are a failed slave race}{\humans{} are a failed slave race}. 
    But they play an important part in the \pps{\banelords} schemes. 
  \item[If You Kill Him You Will Be Just Like Him:] 
    Subverted by Ilcas Northstar. 
  \item[Infant Immortality]
    (although I do have Animal Immortality, to an extent)
  \item[Instant Messenger Pigeon] 
  \item[Just Eat Gilligan]
  \item[Just In Time]
  \item[The McCoy]
    (over-idealistic emotional moron who saves the world through stupidity and sheer luck)
  \item[Most Writers Are Human] 
  \item[Non-Mammal Mammaries]
  \item[No Pronunciation Guide]
  \item[Patrick Stewart Speech] 
  \item[Ping-Pong Naivete]
  \item[Plausible Deniability:] 
    Would make no sense in the setting, but even if it would, I would still hate it.
  \item[Poor Communication Kills] (except when justified)
  \item[Reptiles are Abhorrent:] 
    Averted with the \scathae, especially \hs{Ilcas Northstar}. 
  \item[The Scourge of God]
  \item[Straw Vulcan]
  \item[Trickster Mentor]
  \item[Villain Decay]
  \item[Wangst] (I have to look out for this one)
  \item[What Measure is a Non-Cute?]
  \item[What Measure is a Non-Human?] 
    I subvert it into \quo{What Measure is a Human?}. 
  \item[You Suck] 
\end{description}

\section{Tropes I embrace}
\begin{description}
  \item[Achilles Heel:] Subverted with \Ishnaruchaefir. 
  \item[Affably Evil:] Ramiel, maybe others.
  \item[A God Am I:] Ramiel, \HriistD. 
  \item[Alien Geometries:] 
    The \hs{Mirage Asylum}, and other things. 
  \item[Amnesiac Dissonance:] 
    Carzain/Vizicar when they discover the truth about Ramiel.
  \item[Ancient Conspiracy] 
  \item[The Antichrist:]
    \Thanatzil. 
  \item[The Aragorn:] Ilcas Northstar.
  \item[Ape Shall Never Kill Ape:] 
    The \dragons{} and their \hr{Dragons do not eat Dragons}{cannibalism taboo}. 
  \item[Asshole Victim:] 
    Grum's bandits in \TwilightAngelRememberEmph. 
  \item[Authority Equals Asskicking]  
  \item[Badass:] 
    Many characters. 
    Oh, so many. 
    I hope. 
  \item[Barrier Maiden:] \Triestessakhin 
  \item[Bedlam House:] \hs{Asylums} can be nasty. 
  \item[\Bishounen:] \Teshrial. 
  \item[Black and Gray Morality]
  \item[Body Horror:] 
    \Ilu{} and other \nephilim{} and \humans{} who give birth to \resphain.
  \item[Breast Plate:] 
    \hr{Belzir}{\Belzir} wears one of these underneath her \hs{Archon Ward}.
  \item[Broke Your Arm Punching Out Cthulhu:]
    When the \Miithian s tried to evict the \banes, it resulted in the \SecondShrouding{} that devastated \Miith{} and killed uncounted millions. 
  \item[Casanova:] Carzain and others. 
  \item[Cosmic Horror:] 
    \hs{Cosmic gods}, \hr{XS}{\xss}, \hr{Voidbringer}{\Voidbringer}, \banelords.
  \item[Crapsack World]
  \item[Dangerously Genre Savvy] 
  \item[Dark is Not Evil:] 
    \Ishnaruchaefir{} most egregiously.
  \item[Dark Messiah:] 
    Cordos Vaimon unwittingly embodies this, \Belzir{} may be a more insidious variant.
  \item[Dark World:] 
    \Nyx{}, and pretty much every Realm Beyond.
  \item[Death By Childbirth:] \hr{Ilu}{\Ilu}.
  \item[Deliberate Values Dissonance]
  \item[Demonic Invaders:]
    The \banes, and to a lesser extent the \xss. 
  \item[The Empath:] 
    Ilcas Northstar. Razor even more so. 
  \item[Enemy Within:] \hr{Curse}{\NexagglachelsCurse}. 
  \item[Everything is Better With Dinosaurs] 
  \item[Evil Hand:] \hr{Azraid}{\Azraid}. 
  \item[Evil is Cool] 
  \item[Evil is Sexy] 
  \item[Evil Prince:] \Azraid.
  \item[Evilutionary Biologist:] \Daggerrain.
  \item[Evil Versus Evil]
  \item[Extraordinarily Empowered Girl:] Silqua. 
  \item[Face Heel Turn:] Carzain. 
  \item[Fantasy Counterpart Culture:] 
    Durcac = Egypt, Imetrium = Rome/Communism, Redcor = Christianity, Geica = USA.
  \item[Flaw Exploitation:] 
    The Sentinels will need a lot of this to defeat \Daggerrain.
  \item[Functional Magic:] 
    Has elements of Theurgy, Rule Magic and Force Magic.
  \item[Galactic Conqueror:] \hr{Voidbringer}{\Voidbringer}.
  \item[God Is Evil:] \iquin{} and the \Sephiroth.
  \item[God Save Us From the Queen:] \Belzir, by some accounts. 
  \item[Go Mad From the Revelation:] 
    Rian, Neina. 
    Moro \Cornel{} to some extent. 
    Maybe \Tiroco{} Pelidor. 
  \item[\Gotterdammerung{}:] 
    The \banewars{} and \hs{Shrouding}. 
    
    The \thirdbanewar arguably counts as an inversion, where the gods all come back. 
    
  \item[Government Conspiracy] (to some extent)
  \item[Half-Human Hybrids:] 
    I need to think up a metaphysical justification for this. It won't come up in the story itself, of course, since this is just how the \Miith{} universe works, but I need a reason.
  \item[Happiness in Slavery:] The \ps{\resphain} \human{} slaves.
  \item[Heroic Sociopath] 
  \item[Heroic Willpower:] This is what \vertices{} are all about. 
  \item[Humans are Bastards] 
  \item[I Am Not Left-Handed:] \Ishnaruchaefir. 
  \item[ImprobableWeaponWielder:]
    \subitem Sinister Scythe: \Ishnaruchaefir{} with \Triestessakhin. 
  \item[Inherent in the System:] 
    \Dragons{} and \banes{} fight for the survival of their peoples, and the whole universe is built on conflict and chaos.
  \item[In the Blood:] \hr{Curse}{\NexagglachelsCurse}.
  \item[In the Mouth of Madness] 
  \item[Invisible to Normals]
  \item[Jerkass:] Mostly the Redcor. 
  \item[Karma Houdini:] Charcoal, \Nzessua, \HriistD, others. 
  \item[Kneel Before Zod:] 
    Ramiel: \ta{Crawl, vermin! Crawl before your master!}
  \item[Knight Templar:] The Redcor and the Imetrium, some \resphain.
  \item[Light is Not Good:] \Teshrial, the Iquinian Church. 
  \item[The Lifestream:] The Heart of \Miith{}.
  \item[Made of Iron:] \Ishnaruchaefir, others. 
  \item[Magnificent Bastard:] \Daggerrain, \Secherdamon, to an extent \Ishnaruchaefir.
  \item[The Masquerade]
  \item[Ninja Pirate Robot Zombie:] 
    The \resphain, who are elves, angels and vampires all wrapped up in one. 
    The \satharioth{} are even worse, since they have \dragon{} blood.
  \item[Noble Demon:] \Ishnaruchaefir. 
  \item[Not Brainwashed:] 
    \Tiamat, when she embraces the \xsic{} power. 
  \item[One Winged Angel:]
    \Teshrial{} in his mutant form. 
  \item[Papa Wolf:] 
    \ps{\Ishnaruchaefir} genocidal rage when his beloved servants are killed. 
  \item[Path of Inspiration:] 
    The Iquinian Church... well, most religions, in fact. 
  \item[Pet the Dog:] 
    \Secherdamon, when he \hyperref[Secherdamon lets Tiroco and Icor choose their fate]{lets \Tiroco{} and \Icor{} choose their fate}.
  \item[Precursors:] The \hr{Voyagers}{\voyagers}. 
  \item[Proud Warrior Race Guy:] The \Mystraacht{} dynasty. 
  \item[Pursued Protagonist:] Catrian. 
  \item[Rage Against the Heavens] 
  \item[\trope{SanityHasAdvantages}{Sanity Has Advantages}:] \Sithiyacaan. 
  \item[Revenge By Proxy:] 
    \Ishnaruchaefir, avenging the deaths of \hr{Criseis's siblings}{\ps{\Criseis} siblings}. 
  \item[Royally Screwed Up:]
    The \satharioth and their madness. 
  \item[Satan is Good:] 
    The \daemonic{} Sentinels are portrayed as better than the Cabal. 
  \item[Sexual Objectification:] Wherever I can pull it off. 
  \item[Shoot the Dog] 
  \item[Shoot the Hostage:] Maybe \hs{Shereid} should die this way...
  \item[Sliding Scale of Anti-Heroes:] 
    \Ishnaruchaefir{} is probably a Type IV. 
    \Secherdamon{} and \Azraid{} are perhaps Type V. 
    \Vizsherioch{} is pure evil. 
  \item[Sorting Algorithm of Evil:] 
    Through the course of \SentinelsofMithEmph, the reader encounters progressively stronger villains, at least on the Cabal side: 
    \Teshrial, \Azraid, \Daggerrain, \Voidbringer.
  \item[The Spartan Way:]
    \hr{Dasteron's upbringing}{\ps{\Dasteron} upbringing}. 
  \item[Starfish Aliens:] 
    \Voyagers, \banes{} to some extent.
  \item[Starfish Language:] 
    The \banes, whose language is tactile. 
  \item[The Starscream:] 
    Ramiel wants to usurp \Azraid{} as the highest of all \resphain. 
  \item[Sympathetic POV]
  \item[Time Abyss:] Many of the immortals. 
  \item[Tome of Eldritch Lore]
  \item[Took a Level in Badass:] 
    \subitem Carzain takes many such levels until finally turning into the true Ramiel. 
    \subitem Razor takes one after Ilcas Northstar dies.
  \item[Too Kinky to Torture:] \Nexagglachel.
  \item[\Ubermensch:] Ramiel and \Ishnaruchaefir.
  \item[Villain Protagonist:] Ramiel and \Ishnaruchaefir. 
  \item[Villainy Discretion Shot:] 
    \ps{\Ishnaruchaefir} terrorism and massacres against innocent civilians \hr{Criseis's siblings}{for the sake of a personal vendetta} is a good example, but not the only one. 
  \item[Vizzini Gambit:] 
    The way \Ishnaruchaefir{} sets up \Teshrial. 
    Maybe. 
    (Although it's not like \Teshrial{} had \emph{no} chance of winning.)
  \item[Walking the Earth:]
    After his awakening, Ramiel reflects that he has been Walking the Earth as a Scion, which has \hr{Ramiel is wiser from walking the earth}{made him wiser}. 
  \item[Weirdness Censor:] The Shroud.
  \item[What the Hell Hero:] Carzain. 
  \item[Word of God]
  \item[World Half Empty] 
  \item[Worthy Opponent:] \Narkiza. 
  \item[Xanatos Gambit:] \Daggerrain, \Secherdamon. 
  \item[Xanatos Sucker:] 
    Silqua (in \SilquaBookEmph), 
    Charcoal (in \TwilightAngelRememberEmph), 
    Ramiel (in \SentinelsFinalBookEmph). 
\end{description}

\section{Tropes to consider but beware}
\begin{description}
  \item[Anachronic Order]
  \item[Contrived Coincidence] 
  \item[Dolphins, Dolphins Everywhere:] 
    I should have some dolphins and other whales here and there.
  \item[Freudian Excuse:] 
    Can be used, but not too much. 
  \item[Human Shield:] Must be justified. 
  \item[Lowest Cosmic Denominator:] 
    For example, I might be forced to rename the \hr{Sephiroth}{\sephiroth}.
  \item[Marty Stu:] 
    Carzain runs the risk of turning into one of these. 
    \subitem Specifically, Jerkass Stu.
  \item[Medieval Stasis:] 
    I use it, but it must be justified. 
  \item[Mooks:] 
    \Banes. They are terrifying adversaries against mortals, but become mooks when pitted against \dragons{} or other high-powered immortals.
  \item[The Reveal:] 
    In \TwilightAngelRememberEmph I need to reveal \ps{\Secherdamon} gambit, \ps{\Ishnaruchaefir} gambit and the \hs{Ghost Tower ploy}. 
    But I must be careful not to get too Agatha Christie-like.
  \item[The Scrappy:] I fear Curiet might turn into one of these...
  \item[Slytherin House] 
  \item[What Is Evil?]
\end{description}




 
\end{flushleft}





