
\bookchapter{The \Caliph Inviolate}
\begin{comment}
\subsection{Curwen spies on Rungerans}
\end{comment}
\stamp
  {\dateSortieInCombat}
  {\hs{Kenshaer Forest}\\
   Late evening}


    
Read about \maybehs{Carzain}/\maybehs{Ramiel}. 
    
Remember that there are \maybehr{TBW railroads}{railroads}. 
The Rungerans travel by railroad towards \Forklin. 
In fact, read about \maybehs{technology}, especially railroads. 

Replace \quo{forest} with \quo{\maybehr{Jungle}{jungle}}. 
Or maybe Carzain rides not through the jungle but across the heath. 
Read about jungles and the \wylde. 

Read some Robert E. Howard before I write the scenes with Carzain and Tantor in the \wylde. 

\tho{Finally,} thought Carzain. 
Now he can hear army noises coming from up ahead through the trees. 
He had been trying to stalk the Rungerans for days. 
A few times they had been able to shadow them, peering out from the edge of the forest, but they could not keep creeping along at the edge for fear of discovery, so they had to take more convoluted paths through the \Wylde{} and hope to find the Rungerans again. 

\tho{%
  I need to catch them with their pants down.
  I need to see this vaunted sorcery of theirs in action.
  In an ideal world I'd like to see them conquer a town like they did with Gilwaed back there.
  But I can't very well just camp down in a town and wait for the Rungerans to waltz by and wipe it out.
  
  So we're reduced to stalking and spying on them.
  But with luck, we can at least get a peek at their \ishrah.}

\tho{%
  I need to get close. 
  This'll be risky business, of course. 
  But I didn't get to the place I am today by not taking risks.}

They dismounted\dash the \relcs{} were hard to conceal\dash and snuck through the dense foliage. 
As they got closer Curwen could feel vibrations. 
\tho{Jackpot. Their \ishrah{} is at it.}
He followed the scent of magical activity and led them to the edge closest to where the Rungeran \ishrah{} was camped. 

As they reached the edge of the wood and neared the great road the army camp came into view. 
It was a huge sprawled mass of tents, fires and massive beasts. 
At first glance Curwen estimated its size at about ten thousand soldiers. 
But then he looked to the sides. 
The camp continued along the road for as far as the eye could see in both directions. 

\tho{%
  Damn. 
  Ten thousand? 
  Yeah, right. 
  More like twice that.
  I hope this is all they've got.}

Carzain counts the Rungeran cannons. 
There are quite a lot. 

On an open plain the army camp would have been more circular, but here they were travelling on a road through dangerous \Wylde{}, so they were forced to set up a long camp along the road. 
This worked in Curwen's favour, for it made it easier to sneak in and get a look at the \ishrah. 
As in any sane army, Curwen reflected, the mages would be placed somewhere in the middle for maximum protection. 
But in a long, narrow camp like this, the \quo{middle} was still relatively close to the edge and could be spied on. 

The Rungeran mages were practicing their magic. 
At this close range they shone like a beacon to Curwen's senses. 
The Pelidorians found a good position on the top of a small rise and hunkered down to observe. 

He noticed six mages at least. 
Probably a few more. 
One woman went among the others as if instructing them. 
She had brown hair and wore a burgundy travelling dress. 
The woman held her head high and directed the other mages with commanding gestures. 
Her body language clearly marked her as the \ishrah{} leader. 

\tho{%
  Interesting. Who is this one?
  
  She's pretty. 
  Wouldn't mind getting me a piece of that ass.}

Apparently their spellwork was just getting started. 
The burgundy-clad woman had arranged the \ishrah{} into a concert. 
They had lined up in geometric formation, with the woman in the centre as the \apex. 
\tho{%
  Definitely a \rethyactic{} formation. 
  Hm. 
  Odd. 
  I would have taken most of them for Vaimons.}

The mages began intoning the \draconic{} words of power, and lines of mystic energy shimmered into existence between them, making the concert glow like a huge hieroglyph of eldritch light. 
A hieroglyph whose nodes and corners were people. 
Curwen was no \rethyax, but he could feel how their arcane symbols opened the mystic paths into the Beyond, and how their words of power reached out into Chaos, beckoning. 

And the \daemons{} gave answer. 

\tho{%
  And what \daemons! 
  Such fury. 
  Such savagery. 
  Such hideousness. 
  Such malevolence. 
  Such \emph{power}.
  
  There is no doubt. 
  These are the same forces that wiped out Gilwaed.}

% The mere trace of these \daemons{} at Gilwaed had been poignant enough, but it could not compare to the feeling of the experincing the conjuration at close range like this. 
At this close range, the conjuration was so potent that even the mindless layman might notice it, and any mage worth his salt would recognize a \daemonic{} presence of the direst kind. 
To Archibald Curwen, whose senses reached deeper into the Beyond than even most mages', it was immense. 
It felt like a dozen whirlwinds blowing in his face, a hundred mouths howling straight into his ear, a thousand thorny paws pressed against his skin. 
% It might have broken a lesser man, and it was enough to leave Curwen breathless. 

\tho{%
  Fuck. 
  Just... fuck.
  
  Pull yourself together. 
  This is it. 
  This is what I was hoping for. 
  Must pay attention. 
  Must learn all I can.}







\begin{comment}
\subsection{Carzain feels Vizicar}
\end{comment}
\new
% Carzain is there with Curwen. 
% He looks down at the Rungeran mages and see them cast their spells. 
% He likewise recognizes the feeling from Gilwaed. 
% He sees, hears and smells all sorts of evocative images. 
\tho{What a bitch.}

Carzain had taken an immediate and instinctive disliking to the brown-haired woman who apparently led the Rungeran \ishrah{}. 
He could not exactly justify why, but on some level he disliked women who took a commanding role. 

Now they were casting their spells, in their \rethyactic{} manner. 
Invoking names, uttering words of power. 
Summoning \chaotic{} powers and \daemons. 

And he sensed the \daemons{} that came up from the depths of Chaos to heed the sorcerers' call. 
It was similar to the feeling at Gilwaed. 
It stirred up memories. 
Feelings. 
Feelings of revulsion. 
Feelings of elation. 

\tho{Stop that! Cut it out!}
He did not want to deal with those emotions. 
Did not want to consider their import. 
Did not want to face the dilemma they presented. 

So he forced himself to concentrate on the present. 
Concentrate on the Rungerans. 
Their incantations. 
Their shifting formation. 
The forces they conjured. 
The \daemons. 
The \daemons{} that came up from Chaos. 
Howling. 
Slithering. 

As he focused, new images intruded on his mind. 
He almost heard the beat of black leathern wings from the benighted voids beyond. 
Heard the slavering of things hungry for the blood and souls of men. 
Heard the clicking of their teeth and claws. 
Almost felt the drool from their maws on his neck. 
Felt the tremendous winds of their passage. 

It brought back memories of his old nightmare. 

\tho{%
  Cast adrift in the void. 
  Immense gods thunder past me. 
  
  And I am nothing...}

\vizicar{%
  The foe threaten us with their sorcery. 
  We must take to arms. 
  To war, my Vaimon brethren!}

\tho{What was that?}

Images flashed before Carzain's eyes. 
Gone and forgotten was the world from just a moment before. 
He stood on a hill overlooking a vast army, \armoured in white and golden \colours, arrayed in formations and battle-lines. 
All were watching him. 

He raised his sabre. 
And at his signal, the army marched. 
At his command, tens of thousands of men marched into battle. 

No. 
Not men. 
Monsters. 
And angels. 
And \daemons. 
Hordes of darkness and light.  
Clad in white and black. 
Silver and gold. 
Purple and blood red. 
Millions and yet millions of them. 
Angels. 
\Dragons. 
Monsters. 

Armies met in a mighty clash. 
Fire and lightning cracked the sky. 
Thunders rolled. 
The earth quaked. 
The heavens blackened. 
The horizons burned. 
The rivers ran crimson. 

Darkness. 
Light. 
Fire. 
Blood. 
Death. 
War. 

\vizicar{%
  And I stand above it all.
  
  I am...
  
  I am...
  
  Who am I?}

The scenes blurred. 

\vizicar{Who am I?}

He struggled to remember. 

\tho{%
  Who am I?}

A name came to him. 

\tho{%
  I am Carzain! 
  \CarzainShireyo!}

\vizicar{No...}

Slowly it came back to him. 

\tho{%
  Yes, damn it!
  I am \CarzainDeracilleShireyo!
  
  I'm in the middle of my own battle. 
  I can't get caught up in crazy fancies now.
  Focus, Carzain. 
  Focus on the real world.}

\vizicar{%
  Real world... 
  
  Real world...}

Doubt filled him. 

\vizicar{%
  What is real?}

He wrestled against the doubt. 

\tho{This is real! I am real! Pelidor and Runger are real!}

The visions subsided. 
The battlefields faded. 
\Dragons{} and angels slipped away. 
Mythical monsters became mundane \mulgrons{} and elephants. 
Ancient warriors in silver and black became modern Rungerans in tan and brown. 
Millions became thousands. 
Mountains and valleys became a road and a forest. 

Carzain was back in the real world. 
On the hill. 
Outside the forest. 
Next to the road. 
Overlooking the Rungeran camp. 

\tho{%
  Phew.
  I made it.}

It took a few moments for the import of that to sink in. 

\tho{%
  I made it!
  I forced down the vision. 
  I'm not mad.
  There may be something wrong with me, but it doesn't own me. 
  I can control it. 
  I'm not a slave of these hallucinations. 
  
  I'm not nothing.}

His mind once again his own, he remembered the task at hand. 
He studied the Rungeran mages. 

They had broken formation. 
Two of them were down, crawling on their knees. 
Exhausted and sick. 
One of them vomited. 
The commanding woman had left them and was crossing the camp with long, determined strides. 

\tho{What happened? Did I miss something important?}

Captain Curwen poked his side. 

\ta{%
  We can't risk to hang around any longer,}
said Curwen.
\ta{%
  They'll see us.
  Move.}

And so they crawled down the hill and back into the woods. 

\tho{%
  Great scouting I did. 
  I hope Curwen doesn't find out I dozed through it...}







\begin{comment}
\subsection{\Takestsha{} notices \vertex{}}
\end{comment}
\new
% % \begin{comment}
% \Takestsha{} has been keeping an eye on the wandering \vertex{}. 
% Remember, stealth and subterfuge is her area of expertise, so she has had some success in tracking it. 
% Now Vizicar flares up. 
% She immediately detects it. 
% 
\Takestsha{} was busy instructing the Rungeran mages, rehearsing the spells recovered from \EreshKal. 
It was hard and taxing work for all, for the \EreshKali{} spells were difficult, and most of the mages were Vaimons with no \rethyactic{} training. 
\tho{%
  They cannot all possibly learn to master the spells in the short time we have. 
  I know that. 
  But a few of them can learn. 
  And the rest can learn to support us in concert.
  That should be enough. 
}

\ta{You! Keep your concentration!}
she snapped at one of them. 
The Vaimons would keep pronouncing the words of power wrong or fail to visualize the spells correctly. 
\tho{%
  Fools. Is this really what passes for mages in this day and age? I ought to...}

They were close to their limit, she knew. 
Some were about to collapse from the strain. 
\tho{%
  But I have to train them. They will have to develop more endurance than this if we are to wield these spells on the battlefield.}

...

Morgan Runger had approached her from behind and was few steps away now. 
She had smelled and heard him approach from a mile off, of course. 
\ta{They were Pelidorian scouts,} she told him, not turning. 
\ta{We have chased them off. I say we let them run.}

\ta{Mhm. Someone will deal with it,} said the king. 
Untroubled. 
Morgan had seen the fire, as had everyone, but evidently it did not scare him. 
He was confident that his bolstered \ishrah{} could counter any sorcerous attack. 
Just as she wanted him to be. 

He came up close behind and wrapped his arms around her. 
Began to grope her body. 
\tho{%
  Heh. Delegating responsibility so you can have your pleasure? How very kingly.}
Morgan had grown quite shameless about their affair, despite the fact that, as a nominal \Iquinian, he was theoretically obliged to be faithful to his wife. 
But he was a king and could do whatever he wanted. 
Do \emph{whomever} he wanted. 
\tho{%
  And, as any man might, he wants to remind everyone how beautiful a woman he is fucking.}

% She doesn't mind, of course. 
% As a \dragon{} she has no sexual shame. 
\Takestsha{} reflected that perhaps she ought to fake some shame and modesty to make her guise as a \human{} woman more believable. 
But then again, she was playing the role of the mysterious and erotic sorceress, and part of her allure was her rejection of conventional morals. 

\tho{%
  Oh, yes. 
  I suppose I had better have sex with Morgan. 
  Have to keep my pet king compliant. 
  
  Tee-hee.
  The discovery of the Scion has made me in a good mood. 
  Who knows? 
  I might even enjoy it tonight.}









