\section{Carzain and Gregory}
Nearby on the battlefield, Carzain caught a glimpse of a familiar face: Gregory, his old childhood enemy. With a grim expression on his face, Carzain made his way toward him.

Gregory, wielding a sword but having lost his shield, was pitted against a slim Rungerian spearman. He was holding his own well, but despite his attempts he could not manage to close on the spearman. Feinting a leap to the left, Gregory turned to rush bravely forward, his sword thrust out before him. But alas, the Rungerian was nimble and took a quick step back, giving him a moment to adjust his spear. He stood his ground to meet the Pelidorian's charge, and the spear took Gregory in the side of his stomach. The big man grunted as blood gushed from the wound and the Rungerian moved in for the kill. 

By this time, Carzain was but few yards from the combatants. \thought{I think not,} he thought, and crying \talk{\Izion{}!} he leapt into the fray, and fire did spring forth from his left hand. The spearman was dismayed by his onslaught and recoiled in shock, giving the mage time to blast him once more with \Izion{} and then cut down the wounded soldier with his sabre. 

Gregory spoke: \talk{Ladyboy! I mean... Carzain! You saved me.} 

Carzain turned to him with a warm smile, but in the next moment his face became stone. He approached his prone countryman, sabre clutched hard in his hand.

\talk{La... Carzain? What are you doing? Help me up!}

Carzain walked over to stand beside him, then spoke softly, for Gregory's ears only. \talk{Gregory, my dear friend. I am a man of my word. And I always said that I would kill you some day.}

Gregory's eyes widened in fear. \talk{You don't mean...? No, wait! WAIT!}

Carzain sighed. \talk{And you had to call me that name one more time.} He swung his sabre and severed Gregory's head with a single, clean stroke. Kneeling down to wipe his blade on Gregory's coat, he looked into his foe's empty eyes. And smiled. 

Rising, he became aware of a nearby Pelidorian eyeing him with distaste. He raised his voice: \talk{An act of mercy,} he lied. \talk{He was in pain.} He paused. \talk{He was my friend. Think not that this was easy.} \thought{More lies,} he thought, but he managed to give the soldier a pained and weary stare. The man accepted his words, for he ran off and was lost in the fighting. Carzain allowed himself to smile once more as he rushed back into the fray. 
