\section{Carzain and his first meeting with \Belzhir}
Carzain slept, and his body was undisturbed, but his mind was not. In his dream, he was adrift in a dark void, nothing but hazy emptiness in all directions, seeming to go on forever. 

For a time, there was nothing. In some ways it felt like an eternity, in some ways it felt like but an instant, for time is strange in the world of dreams. But after a while, he began to hear a sound breaking the bleak silence; a distant sound, like a voice. It was the merest whisper, distant and disembodied, and he could recognize no words. He had the feeling that someone - \emph{something}? - was searching for him. Presumably the source of the voice. Gradually, the voice came closer, and as it did, Carzain felt an alien presence intruding in his mind. 

The voice was louder now, clearer, and he thougth he could almost recognize the words. Then he saw it. Something, some creature, was approaching. It came out of the void, and Carzain knew immediately that it was the source of the voice, the creature that had been searching for him. At first it appeared as an dark, amorphous cloud far out in the distance, but slowly it coalesced and took on shape. Two bright yellow eyes appeared in the cloud, and Carzain knew that it seen him, had found what it had been looking for. It coalesced more quickly now, until at last it founds its true form. 

It was that of a woman. She stood, some distance from him (a dozen strides at least, it seemed), on nothing, in the middle of the void. She was a Vaimon for certain, with the features of Clan Geican, and she was incredibly beautiful. Her skin was pearly white and her hair was black as night, but her eyes shone fiery yellow. She was clad in a tight-fitting dark dress that emphasized the curvature of her perfect body. Her face was young, no older than his, but her unnatural eyes hinted at an immense age and dreadful wisdom. She was beautiful, but also terrible - as hot as fire, and as cold as the black spaces between the stars. 

She spoke, and for the first time, her voice - which came from her mouth but at the same time seemed to issue from the void itself - was perfectly clear. She spoke a single word. 

\telepathy{Carzain.} 

The word cut into his soul like a knife, and Carzain was struck with horror - horror of this wraith-woman, who must surely be a wicked god or demon from some dark, nether world. But he also felt desire - an overpowering lust for this woman, surely the most beautiful and erotic creature he had ever seen. Carzain gazed deep into the abyss and found it not only gazing into him, but beckoning him, calling his name. 

\telepathy{Carzain.} 

She spoke again, and suddenly, not seeming to move nor teleport, stood directly before him. She looked into his eyes and smiled, and her smile was wicked, malicious... but alluring, oh, so alluring. Carzain looked down at her (for she was taller than most Geican women, but still shorter than he), still torn with emotions of fear and desire. He looked down at her body, her smile, her fiery eyes... and he smiled. 

Sensing that he had made his choice, her smile widened as she lifted her hand and touched the hem of her dress. The dress fell off, melting away and dissolving into the darkness. She stood before him naked, her breasts heaving as she also panted with lust. 

\telepathy{Carzain.}  

For the third time she spoke his name, and then she reached up to kiss him. His lips touched hers, and he felt a surge of power flowing into him. This power was Nieur, he realized, and it was both pain and pleasure at once. She pulled closer to him, her soft breasts brushing against his skin (at this point he was naked as well, without having consciously undressed), and pushed him back, and he lay down, seemingly on nothing, floating free in the void. She mounted on top of him and breathed a sigh of pleasure and expectation as he penetrated into her. The flow of Nieur into him grew stronger, and he lost the last vestige of control and could do nothing but obey his passion - and hers, for the wraith-girl was anything but passive. 

Their bodies writhed in ecstasy, and Carzain felt the storm of Nieur inside him seemingly whip itself into a mounting fury. He looked up at the wraith-woman and saw bolts of lightning surging forth from her body, her dark hair flailing in all directions as if lashed by a storm. He reached up and roughly grasped her breasts, and she whined in delight as she dug her sharp fingernails into his flesh in \squo{retaliation}. 

Their passion rose to a climax, and Carzain felt an explosion of erotic power from inside him that seemed to shake even the void. The wraith-girl screamed in ecstasy. For what seemed an eternity and yet only an instant, Carzain was carried by waves of pleasure, but also pain, as if his soul was being torn apart by tremendous, primal forces. At last, the feeling faded, and with it the dream. The last thing he perceived was the disembodied voice of the woman whispering: 

\telepathy{Carzain... you are now mine.} 
