\section{The Exodus from the Deep}
It is said that once, many millions of years ago, a race of alien creatures came to Mith. Out of the sky they descended, riding in their shining chariots of iron and borne upon wings of fire, and they were the Voyagers, and they came to despoil Mith and claim her for their own. 

Unto the bosom Mith did they descend, and in her lands they came to dwell. In the valleys they dwelt, and in the hills, and in the mountains, and upon the seas they did sail. And the Voyagers founded kingdoms and built cities, and vast were their cities and castles, and their great towers of steel and glass did reach into the sky and aspired to touch the stars. 

And the alien ones did spawn their young, and filled up the world with their get, and they did breed slaves to serve them and their spawn. And so the beings of Mith were brought low, and they were enslaved to serve the Voyagers and their spawn, and all Mith lay under the yoke of foreign rule. 

But beneath the seas, beneath the howling winds and the crashing waves and miles upon miles of dark waters there dwelt the \krakens. In their shining halls far beneath the waves, their glorious halls where no mortal may ever tread, they lay in deep sleep. For aeons and aeons had they slept, for they were the true gods of Mith and had been for ever and ever, the oldest and greatest of all being that exist. 

And the \krakens{} did awaken, and they saw that the Voyagers from the stars had occupied the lands of Mith and made it their own, and they saw that they had made of the denizens of Mith their slaves and conquered all that lay before them. And the \krakens{} were angered, and they were enraged. 

And the \krakens{} rose forth from the sea and came to the land where dwelt the Voyagers, and they did battle with them. And there was war on Mith, and the valleys and the hills and the mountains were ablaze with war. The Voyagers fought agains the \krakens; in their chariots of iron borne upon wings of fire they fought, and their spawn fought, and their slaves. And the \krakens{} fought against the invaders; with their tremendous power and wisdom and magic they fought, and Mith was ravaged and lain waste. 
The skies were blackened and the land was set afire and the seas were filled with blood. 

The \krakens{} fought against the invaders, and the Voyagers fought against the \krakens{}, but they prevailed not. The \krakens{} triumphed and were victorious, and they destroyed the Voyagers and all that they had made. They lay waste to the cities of the alien ones, and their towers of steel and glass they razed to the ground, and they slew the brood of the Voyagers, and they slew those who had become their slaves. Every single one of the Voyagers they destroyed, and nowhere was one of the aliens to be found alive. 

Thus did the \krakens{} vanquish the alien Voyagers who had come to despoil Mith and claim her for their own, and Mith was made pure again. 

Seeing that their work was done, the \krakens{} were pleased, and they returned to their forbidden homes in the deepest, darkest oceans. To their shining halls far beneath the waves, their glorious halls where no mortal may ever tread, they returned, and in their sacred halls they lay down and slept. And for aeons and aeons they slept, and they sleep still, for they are the true gods of Mith, the oldest and greatest of all being that exist. Before all things they were, and when all things come to an end they shall be, for they are the greatest of all gods, and they are eternal. 

But \Moroch{} was the youngest of the \krakens{}, and he slept not, but ventured forth from his splendid halls. \Moroch{} came into the great ocean, and he said unto himself: \ta{To ensure that Mith is never again enslaved by an alien power I shall leave behind guardians to guard her. I shall create children, and they shall fill the seas, and they shall be the custodians of Mith.}

And so \Moroch{} made his children and set them in the sea, and he said unto them: \ta{Ye are my children, and the name of your race shall be called the \nagae. Ye shall dwell in the seas, and ye shall multiply, and ye shall rule the seas forever, and ye shall protect Mith forever. And ye shall remember the \krakens, and ye shall remember me, for I am \Moroch, your creator.}

And \Moroch{} returned to his marvelous halls in the deep and lay down together with his kin, and he slept. 

And the \nagae{} remembered his words, and they remembered the \krakens, and they remembered \Moroch, their creator. And they did multiply, and they dwelt in the seas and built marvelous cities of coral, and they were the custodians of Mith. And the greatest and wisest of the \nagae{} grew huge in size and tremendous in power, and they were the \leviathans. And the \leviathans{} were the rulers of the \nagae{}, the keepers of wisdom and the legacy of the \krakens{}. And always the \leviathans{} remembered \Moroch, and always the \nagae{} remembered \Moroch, and they worshipped him, and he was their greatest god. They remembered his legacy, and the \nagae{} were the custodians of Mith for a million years.

Now, in the sea whose name is called Nag there lieth the coral reef whose name is Gyth'lrao'sribish. Vast is Gyth'rao'srimish, and it goeth on for miles upon miles, and in Gyth'rao'srimish is built the city of Vash'hythrai. A marvel is Vash'hythlai, reaching from the darkened depths to the sunny shallow waters, and her homes are decorated with blossoms of a hundred thousand colours. 

In Vash'hythrai there dwelt of yore Kiba'zenwar. A \leviathan{} he was, great in wisdom and power, and few were they that were his peers. One night as he slept in his house in Vash'hythrai, built of shining many-coloured coral, he dreamt, and in his dreams he heard a voice. And the voice spake unto Kiba'zenwar, saying: \ta{Kiba'zenwar, Kiba'zenwar of the \leviathans, hearken unto me. Know that I am \Moroch, thy creator, thy god.} And Kiba'zenwar hearkened, and he knew that the voice spake true, and that it was \Moroch{} of the \kraken{}, creator of the \nagae{} and the \leviathans. 

The voice spake unto him, saying: \ta{Kiba'zenwar, I have chosen thee, for thou art great in wisdom and power, and thou wilt serve me well. Thou must speak unto thy people, and any and all who will follow thee, them shalt thou bring with thee. And thou shalt go forth from the sea and unto the dry land, and there thou shalt dwell, together with them who will follow thee. 

And thou shalt forge an empire. Into the valleys shalt thou go, and thy people shall go with thee and build there cities, and they shall dwell in the valleys. Into the hills shalt thou go, and thy people shall go with thee and build there kingdoms, and they shall dwell in the hills. Into the mountains shalt thou go, and thy people shall go with thee and build there castles, and they shall dwell in the mountains. 

Thus I charge thee: Thou shalt forge an empire, and thy people shall fill the earth, and thou shalt rule over the valleys and the hills and the mountains, and thou shalt be the king of the land and the sky, and thou and thy people shall be the guardians of the land.}

And Kiba'zenwar awoke and rose from his sleep and knew that \Moroch{} his creator had spoken unto him. And he called together his fellows and bade them assemble. And when he saw that they had hearkened and come unto him, Kiba'zenwar addressed addressed the assembly of his fellows and spake unto them, and said: \ta{Hear me, ye \leviathans{} and \nagae{}, for I, Kiba'zenwar, have heard the voice of \Moroch{} our creator. This very night, in my dreams, \Moroch{} hath spoken unto me, and this he said: 

\subta{Thou must speak unto thy people, and any and all who will follow thee, them shalt thou bring with thee. And thou shalt go forth from the sea and unto the dry land, and there thou shalt dwell, together with them who will follow thee. Thus I charge thee: Thou shalt forge an empire, and thy people shall fill the earth, and thou and thy people shall be the guardians of the land.} 

Thus spake \Moroch{} our god unto me, Kiba'zenwar, and I have hearkened unto him. Thusly, I shall go forth unto the land, and I shall carve out a kingdom, and whosoever will follow me shall partake in that kingdom, and we shall rule as the guardians of the land.}

Now Daath'kwilthveir heard his words, and she was a \leviathan, one of the few who were Kiba'zenwar's equals in power. Now she rose...

...

\ta{For ages and ages uncounted have we dwelt in the sea, and for ages have we mastered it. All manner of creatures that swim and crawl in the sea bow before us and know that we are their kings.

But it is not right that we should reign only beneath the sea. This I say to you: Of Mith's creatures we are the greatest, and we should be kings not only of the sea, but of the land, and of the sky. I say this: We, the \leviathans, should ascend from our kingdom beneath the waves. We should rise into the sky, and we should conquer the sky and make it our domain. And we should descend upon the land, and we should conquer the land and make it our domain. For we are the greatest of all Mith's children, and all Mith should belong to us, for such is our birthright. This I say to you. I, \HesodN{}, have spoken.} 