\section{The Death of Ilcas Northstar}
(Ilcas Northstar (section \ref{Ilcas Northstar}) and some others are trying to escape from some enemies. They are being pursued by Geldashad (see section \ref{Geldashad}). They are at some narrow mountain pass or something.) 

\talk{You go on ahead}, said Northstar. \talk{The \nycans{} and I will stay and hold him while you make your escape.} 

\talk{What?} said X\footnote{I don't know who X is. Some woman, perhaps stupid.}. \talk{But you cannot! Geldashad is an Aschenoch, he is much too powerful. You will die!} 

\talk{Most likely,} said Ilcas. \talk{In a war, soldiers die.} 

\talk{No!} cried X. \talk{There must be another way!} 

\talk{There is not!} Ilcas shouted. \talk{There is no time to argue over it. NOW GO!} 

(They go.) 

\paragraph{}
\noindent
(Geldashad reaches the pass and finds Ilcas there, together with Countess and Razor. Geldashad is armed with a short, bladed polearm.) 

Geldashad slowed down. \talk{Northstar.} 

Ilcas lifted \Telderain{}. \talk{Geldashad.} 

Geldashad raised his hands and spoke words of power: \talk{\tongue{Ushevad khorûn ne ti fedhychin!}} 

(At some point Geldashad should say: \ta{I will tear off your gnesses and feed them to you!})

(They fight. Ultimately, the \nycans{} are cast aside and Ilcas is on the defensive.) 

His opponents all down for an instant, Geldashad was able to cast yet another spell. His voice distorted in a deep, guttural grumble, he spoke the word: \talk{\tongue{K'chunjoth nerrzuîn bah zevîhael udh goshakht.}}\footnote{The words for the spell \squo{Shadow Fury}.} As he spoke, his fingers traced a Glyph encarved on an armor plate on his stomach, and the arcane energy flowed into the mystic symbol. With the spell, he reached down and summoned up the energy of primal fury from the sinister depths of his Shadow. As he looked up again, his face was contorted into a mask of animalistic rage. 

When the Ashenoch charged, a fierce snarl on his lips, Northstar had regained his footing and was able to parry the first strike, but the sheer power of the attack almost knocked Ilcas off his feet again. Geldashad struck again with his polearm, and again Northstar was able to deflect it, sparks showering from their blades as they collided. Ilcas summoned all the power of \Telderain{} and slashed, the blade biting deep into his opponent's right arm. The enraged Ashenoch roared and lashed out with his bare hand. Again Ilcas was thrown off balance by the ferocity of the attack, but Geldashad wasted no time, thrusting forward with the polearm he still held in his left hand. Ilcas was unable to bring his sword down in time to parry and gave a loud groan as the blade pierced his armour and sunk deep into his right side. 

Geldashad pulled out his weapon, tearing a deep wound in Ilcas' side as he did so, and raised it to strike again. Ilcas lashed out and cut a bloody gash across his opponent's chest, and Geldashad cried out in pain and anger, but Northstar's strength was already fading and the wound he managed to inflict was not deep. The Ashenoch brought his weapon down, and Northstar, realizing that he had not the strength to parry it, opted instead to strike back in retaliation. He thrusted upwards and sunk his sword into the Ashenoch's left leg, but at the same time Geldashad's polearm pierced his chest. 

As the blade tore through his body, a horrible thought crossed Ilcas' mind. \thought{\Telderain{}! When I die, the sword is lost! Gelderain will take it. By Creyga! I will go down in disgrace in the Northstar legacy as the one who lost the Flash of the Northstar to the Rissitics.} Another thought: \thought{Curse me for a fool! I do this not for my own legacy, not to please the Northstar family! I die for the greater glory of the Imetrium. But still... I caused \Telderain{} to be lost!} 

Blood was already clouding his vision, but looking behind the towering Ashenoch, his eyes suddenly lit up with a faint glimmer of hope. He sent out his thoughts... 

%\paragraph{}
Geldashad cried out at the pain in his leg, but he knew that the victory was his. \talk{Die, Northstar! DIE!} he screamed as he pulled out his weapon. It tore through the Imetrian's chest, shoulder and neck, and the blood gushed out. Northstar's body twitched and then lay still. A cruel smile spread across the Ashenoch's lips. 

Then he heard a blood-curdling sound from behind him, a tortured scream full of anguish and hate. He only had the time to turn halfway around as a pair of great claws tore into his already wounded right arm. With her other foot, Countess slashed at his chest, and he was barely able to lift his polearm to deflect her attack. Leaning on his polearm for support and enduring the pain as the blade cut into her foot, Countess bent down and bit at the \scathaz{} exposed face. He screamed again as her teeth tore his snout. But the Shadow Fury still empowered him, and with immense effort he lifted up his arms and threw the giant \nycan{} off him. Countess managed another swipe with her left foot at the \scathaz{} back. The attack did not penetrate his armor, but her weight was sufficient to throw him off balance. Ignoring the pain in her wounded foot, the \nycan{} changed again, leaping up to slash at him with both feet. Geldashad swung his polearm to defend himself, but again Countess' weight overwhelmed him and he was cast to the ground, her curved claws cutting into his stomach. 

Meanwhile, Razor had been cautiously circling them, searching for an opening. He fully shared Countess' grief and outrage at the death of their beloved \foreign{melda}, and had little fear of death, even though realizing that the \nycans{} stood little chance against the Rissitic warrior-mage. But he had understood Ilcas' last thoughts. And so, when Countess' charge pulled the Ashenoch away from Northstar's body, Razor darted forward. %Instead of attacking, he ran towards the body.

Countess, entangled in close combat with the Rissitic, looked up to see Razor running not to her aid, but towards Ilcas's body. There he stopped and leaned down, fingering the body, or something lying by it. She sent out her thoughts to him. \telepathy{Razor! Come and help me defeat him. Avenge our \foreign{melda}!} 

\telepathy{No,} said Razor. \telepathy{I cannot.} He turned away. \telepathy{I must fulfill Ilcas' wish.} He ran towards the pass, but slowed down to glance back at her. \telepathy{Farewell, Countess.} Then he ran, sprinting at full speed through the pass and down the corridor. 

Countess did not understand what her fellow \nycan{} had meant, but she was given little time to ponder it, for in her distraction, Geldashad saw his chance to voice another spell. \talk{\tongue{Nashgor hin drovezgadh âgh kekhtûn!}} he spoke in a hoarse rattle as he dug the bare fingers of his maimed right arm into the bloody wound on the \nycanz{} foot. Countess yelped in pain and horror as the mage reached out through the Shadow World and siphoned her life-force out of her and into himself. She raised her foot to slash at him, but this was a mistake, as it weakened the blocking grasp she held on Geldashad's polearm. With lightning quickness, strengthened by the Shadow energy he had stolen, the Ashenoch pulled out his left arm from under her and immediately thrust upward with supernatural strength. As the blade pierced the \nycanz{} feathers and skin and slid deep into her belly, the warrior-mage spoke again the words of his necromantic spell: \talk{\tongue{Nashgor hin drovezgadh ak kechtûn!}} Again Countess screamed as she felt her life energy being drained from her, and Geldashad, with his new-found strength, was able to throw her great bulk off him and rise to his feet. 

Driven by mounting feeling of rage and despair, Countess again hurled herself at the \scatha, but he had already drained too much of her energy and was able to easily fend her off and cut another wound in her side. Her feathers drenched in dark blood, she leapt up to claw at him with both feet, but he dodged aside and struck back. The rune-carved polearm hit with full force and tore through her neck. The \nycan{} barely stumbled, barely felt the pain nor the blood gushing out of her neck, so swiftly did the Ashenoch raise his weapon to strike again. He swung his terrible polearm in a great arc that sheared through feathers, flesh and bone alike, and Countess' severed head fell from her neck. 

Geldashad kicked Countess' great body with contempt. \talk{Fah! I did not come here to fight simple beasts.} He moved over to where lay the corpse of Ilcas Northstar. \talk{Hah. Your pet was almost a greater challenge than you, Northstar.} But as he inspected the body, his eyes widened in anger. \talk{What?! NO!} 

\paragraph{}
\noindent
(The others run. Razor catches up with them and hands them \Telderain{}. Obviously, Ilcas' last wish was for the \nycans{} to save the sword, the Northstar heirloom, that it might be brought to his daughters.\footnote{Traditionally, \Telderain{} must be wielded only by those of the Northstar family. Ilcas' daughters carry the Northstar name, whereas his sons carry the name of their mother (Raeco Mannica). Ilcas hoped very much that one of his daughters will be deemed worthy to carry \Telderain{}.}) 



