%\section{In the Deep Halls of Darkness}
\stamp
  {\dateIshnaruchaefirIntroduced}
  {A Cabal council chamber, \Nyx}

The wine was dark red and thick-flowing. \tho{Almost like blood. If somewhat more bland in taste. 

I should have brought my own.} 

\Teshrial{} drained the cup, made of translucent rosy crystal, and held it out to have it refilled. The slave holding the decanter was a young man. Very slim and pretty. \tho{I'd rather be drinking the boy's blood,} he reflected. \tho{But I suppose that would be uncivilized of me.}

On the wide floor in the centre of the hall, a dozen slaves were performing some elaborate dance. Of sorts. They were naked, as were all the slaves in the chamber, and for some reason, the dance entailed an awful lot of genital contact, of body parts inserted into other body parts. 

\ta{You really have no taste, do you know that, Lord \Ganethed? Having all your slaves wading around naked for no reason, and fornicating on the floor for no reason. You lack understanding of subtlety the finer arts.} 

\Ganethed{} chuckled. \ta{Always the art critic, are you, Lord \Teshrial? But in your obsession with the \quo{finer} arts there is much that you fail to appreciate. There is beauty in many things... direct and indirect expression alike.}

\ta{Such as a man fiercely stabbing his penis into another man's armpit?} asked \Teshrial, eyeing the dance with half-amused, half-bored disbelief. \ta{Yes, I could not agree more: There are things which I profoundly fail to appreciate.}

\Ganethed{} laughed, running a hand through his ear-long mane of golden hair. \tho{Also, you should give that gesture a rest, \Ganethed. It looks ridiculous on you. Unlike me.} As if to illustrate his point, he ran a single finger through his long, bright white locks. 

\ta{I must admit, though, that your shirt with the black-and-white tiger-stripes is rather stylish...} 

Lady Selguin chose to break the stretching silence. \ta{This discussion of penises and armpits is deeply fascinating, my Lords. But before we adjourn this council, I believe we might want to touch the small detail of our \matrixx, and of the \Malcuric{} \nexus?}

\ta{Everything is proceeding according to plan,} said \Teshrial. \ta{The \ghobaleth{} are close to the surface. No, not \emph{too} close, of course. I was not born yesterday.} \tho{But close enough,} their gazes seemed to imply. \Teshrial{} was the youngest \resphan{} in the room, and he well knew that some disrespected him for that. \tho{Envious of my merits.}

\ta{Sentinels?} asked \Ganethed. 

\ta{Yes,} \Teshrial{} replied simply. 

\ta{\quo{Yes}?}

\ta{Yes, there are Sentinels there.} \tho{What kind of answer were you expecting? Stupid plainblood.} \Ganethed{} was of the same rank as he, so he could not very well call him \quo{plainblood} to his face, but that was what he was. Whereas \Teshrial{} and Selguin were of \Ketheran{} bloodlines. 

\Ganethed{} would not be bitten off. \ta{And?} 

\Teshrial{} repressed a deep sigh, which would have been a breach of etiquette. \ta{They are under the supervision of \PsyrexFull. And I am dealing with them. In this regard I have confidence in my Cabalists.} He eyed the plainblood, daring him to pester him with more inane questions. 

Selguin fixed her eyes upon \Teshrial. They were sharp as blades, those eyes, and shining silvery like her hair. \tho{True \KiriathSepher{} eyes. True \ketheran{} eyes.}

%They shone like silver, those eyes, and they were sharp as blades. 
\ta{And the... imbalance?} she asked. \ta{There were signs connecting the spike to your territory. Have you made any discoveries?}

\tho{Yes, that pesky disturbance in the Web.} Ever since that \vertex{} spike that had come out of nowhere last year, there had been an imbalance in the Cabal \Matrix. A rogue \vertex{}, yet part of the pattern. And it was pulling their carefully orchestrated \matrix{} askew. \tho{Unknown players in the Web of the Realms. Always vexing business.}

\Teshrial{} signalled his subordinate to speak. \ta{\Achsah?}

\ta{My Lords. My Lady,} \Achsah{} began. \ta{I have researched the matter of the \vertex{} spike, and I have found strong evidence linking the incident to the \PelidorContinent{} area. Perhaps \Scyrum, or...}

\ta{... or perhaps Pelidor?} \Ganethed{} interrupted. 

\ta{Yes, my Lord. Perhaps Pelidor. I expect to be able to further narrow it down in the near future.}

\ta{And have you determined its nature?} demanded Selguin. 

\ta{It is too early to tell, my Lady. It could be part of an intrigue between the dynasties. Of which I would know nothing.} \Achsah, of course, being of impure birth, would not be privy to the scheming of the great dynasties. \ta{It could be the birth or awakening of a Scion. It could be a ploy by the Sentinels, or some other power.}

\tho{Some other power. Yes. Always more rivals to fret over. Perhaps a consequence of Chaos... and the Heart...}

\ta{But there is another thing,} \Achsah{} began again. \ta{My Lord?}

\ta{Oh, yes,} said \Teshrial. \ta{It may interest you to know that I have detected the activity of an alien \vertex{} stirring the threads of the \Malcuric{} \nexus.}

This got the attention of all the \resphain{} at the table. \Teshrial{} let the dramatic silence drag for a few seconds before continuing. 

\ta{One of the \draecchonosh, for certain. I smell \xsic{} power. One of the \KhothSell{} bloodline, kin of our progenitor.}

\ta{So, who might it be?} ventured Selguin. \ta{\Nzessuacrith? Vaccashyth? \Dasvedshiracht?} 

\ta{Possible. But I fear that we have to do with an even greater power. Perhaps even one of their Elder Lords. A \secondgendragon, and of the purest royal blood.}

\ta{Surely not the esteemed \quo{Serpentine Lord} himself?} \Ganethed{} laughed. \ta{Or whatever he calls himself these days.}

\ta{No, that seems unlikely, does it not?} \Teshrial{} agreed. 

\ta{But... a \secondgendragon... and of the blood of our progenitor.} 
It was Lelmach who had spoken, an \ashenblood{} in Selguin's service. 
\ta{That leaves only...}

\ta{You mean... the Wanderer in Darkness? The Heartslayer?} Selguin's voice was a whisper.

\ta{I think not,} said \Ganethed. \ta{He has not been active for centuries.}

\ta{Then it would appear he has returned,} said \Teshrial. 

This gave pause to even \Ganethed. \ta{The Wanderer in Darkness...}

\ta{The mystic immortal. The one who forsook his people after the \CuezcanApocalypse...} Selguin whispered. 

\Achsah{} was the first to dare speak his name. \ta{Quessanth \Ishnaruchaefir.}

\ta{An greater power indeed,} Selguin conceded. \ta{\Ishnaruchaefir{} is that most dangerous of things: A rogue \vertex. Aligned with no \matrix, but mighty enough to move and shake \matrices, and the Web itself. No pattern, no discernible strategy... just a wild \matrix{} wreaking havoc.}

\ta{In accordance with Chaos,} \Ganethed{} pointed out. \ta{A principle which we, as a people, nominally strive to embody.}

\ta{I beg to differ, Lord \Ganethed,} said \Teshrial. \ta{Chaos alone is no virtue. As you well know, it must be tempered. And that is precisely what \matrices{} are for. That is what elevates us above our foe...}

\ta{I believe we have more pressing matters to discuss instead of basking in the glory of the \resphan{} civilization?} Selguin's voice was slow and patient. Condescendingly so. \ta{Such as the matter of Quessanth \Ishnaruchaefir.} 

\ta{Oh, yes,} said \Teshrial. \ta{What do you wish to discuss, my Lady? Do you offer to come with me and help fight him off?} 

Selguin's reply was prompt. \ta{No.}

\ta{Lord \Ganethed?}

\ta{Haha. Perhaps the next time, Lord \Teshrial.}

\ta{As I thought. Well, that was a fine discussion, my Lords.} 
\Teshrial{} rose, signalling for \Achsah{} to do likewise. 
\ta{We should do it again soon.} 

\ta{What?} exclaimed a surprised \Ganethed.

\ta{As for the \secondgendragon{} lord, I will deal with him myself.}

\ta{No doubt you will.} Selguin sounded less than convinced. 

\tho{Feh. Doubt me all you want. You will see. Soon enough.
 
%\Teshrial{} had never truly intended to discuss the matter of the \shaeeroth. 

Me versus the \shaeeroth. Let them chew on that.}

The \resphan{} lord reached out through the Web and submerged to a different layer of \Nyx. The hundred-metres-high grooved iron walls of the council chamber faded, and he stepped onto a long, massive bridge suspended in the void. Beneath, the tall towers continued down into the deep, seemingly without end, until they were swallowed by a dark, misty haze. Above, many-coloured stars and nebulae were visible, for this was a shallow layer, close enough to Mith for its skies to shine through. But dominating the heavens were the black stars of \Erebos; the gateways to that Stygian world of which \Nyx{} was sired, shining with a deeper blackness than even the empty voids 'twixt the stars. 

\Teshrial{} took a moment to admire the view. 

\ta{My Lord \Ketheran?} came \Achsahz{} voice behind him. 

\ta{What?} he said, not turning. 

\ta{Do you intend to face Quessanth \Ishnaruchaefir{} in combat?}

\ta{Hm.} The \ketheran{} smirked but did not reply. 

\ta{Be careful, my Lord. \Ishnaruchaefir{} is a terrible foe. His status is legendary for a reason. You should not underestimate him. I have encountered him a few times...}

\tho{Pulling the seniority card on me, are you?} \Achsah{} seemed to relish subtly reminding him of her age and experience. As if it somehow cancelled out her inferior birth. 

\ta{\Achsah, come here.} She stepped closer. He looked down at the shorter \resvil. 

Then slapped her across the face. 

Not hard enough to cause actual pain, of course. That would be a breach of priopriety. She stood beneath him in rank, but not near far enough that he could corporeally punish her. Just hard enough to be humiliating. 

\ta{Do not presume to educate me, \ashenblood.} She scowled up at him, silent. He raised a questioning eyebrow. 

\ta{Yes, my Lord \Ketheran.}

He turned away. \tho{Good.} Everyone in the Cabal must know their place, of course. \tho{Especially the low-born.}

\tho{And as for the infamous \shaeeroth, this mystic immortal... well, we will see about that.}

\Teshrial{} spread wide his wings and leapt from the causeway. 







