%\section{\Nzessuacrith{} and \HriistD}
% \Nzessuacrith{} flies through \Machai. 
% She reaches the city of \Undreioth, wherein lies \HriistDz{} stronghold of \Orokhthegglain{}.
% \HriistD{} is \Hriist{} \Nechsain\dash it is his \draconic{} name, or one of his names. He is also her uncle, since \Ishnaruchaefir, \Nzessuacrithz{} father, is the brother of \HriistD. 
% She flies over walls, guard towers, foundries, spawning pits and more on her way toward the stronghold. 
% Before reaching the stronghold she feels hungry, so she grabs a \daemon{} from the street and eats it. It's a \nrekkloi, a crustacean-like thing with a fur-covered, vaguely humanoid torso. It bellows when snatched and lashes out with its clawed arms and legs, but she bites off its head, then gulps down the rest. 

A crash of thunder rent the sky. The gleam of fire and lightning reflected in her metallic scales as \Nzessua{} soared above the blasted plains of \Machai. 

She reached the city of \Undreioth{}, passing mass of guard towers, foundries, spawning pits and more on her way to the central castle, \Orokhthegglain. 
%Reaching the city of \Undreioth{} 

Halfway through the city, \Nzessua{} recalled that she was feeling slightly hungry. \tho{One should confront \HriistD{} only on a full stomach,} she mused to herself as she surveyed the scene below her. The first obvious choice that occured to her was a \nrekkloi{} \daemon{} that appeared to be doing no useful work. 

\Nzessua{} folded up her vast wings and dove. 

Screaming and shouting ensued. The myriad creatures below fled in panic as \Nzessuacrith{} approached. The \nrekkloi{} scuttled away on its six legs, but \nrekklois{} were never fast runners. 

Moments before crashing into the ground, \Nzessua{} spread wide her silver-shining wings, gliding gracefully forward. The four-metre-long \daemon{} was nothing next to her, and she easily snatched it with her forehands, her claws tearing through the hard carapace of its crustacean-like body. Her prey secured, she beat her wings to rise back into the air, throwing dozens of creatures to the ground and breaking quite a few roofs and windows. She felt her tail collide with something and vaguely registered a crashing sound behind her\dash likely a collapsing hut. 

The \nrekkloi{}, bellowing in pain and outrage, squirmed in her grasp and lashed out with its clawed arms. Annoyed, \Nzessua{} resolutely seized the creature's head in her jaws. A quick tug and the head came free, blood spraying from the neck-stump. The monster convulsed a few times, then fell limp. \Nzessua{} gulped down the rest of it in three bites. 

%\Orokhthegglain{} is a massive, terrifying edifice with halls hundreds of metres high and spires reaching thousands of metres in the air. Like a typical \Machai{} structure it is made of flesh, stone and metal. 
Her hunger sated, she proceeded towards \Orokhthegglain. The stronghold was a colossal edifice made of metal, stone and living flesh, jagged spires reaching literally thousands of metres in the air. 

She crossed the wall and the spires and headed for the central tower, a menacing building shaped to resemble a \draconic{} skull. The soldiers on the great balcony fled before her as she alighted on the stony floor. Recognizing her, they bowed from their refuge places in the far corners. 
% and went to stand and bow in the corners as she alighted on the central balcony. 

Ignoring them, she faced the wall. It was covered in a solid, metallic carapace. \Nzessuacrith{} intoned words of power in the \Draconic{} tongue, which translate poorly into \human{} languages, but the meaning was roughly this: 

\kingstongue{Hearken, \Orokhthegglain! I am Rizuss \Nzessuacrith{} Khthelgrain Curzsesxachiv of the Bloodline Morcaryn, and I bid thee: Open! Open wide thy gate for me that I might enter, for I am \Nzessuacrith{} of the Bloodline Morcaryn, and I command thee.}

And the living castle reacted to her spell. 
%The many-inches-thick metal plates slid aside to reveal a soft, fleshy wall. The flesh, metres trick, retracted as well, revealing a layer of stone on the inside. Finally the stone gave way, and a great, slime-dripping aperture yawned in the castle wall. The opening, as well as the corridor beyond, were huge, a hundred metres wide or more, easily enough for \Nzessua{} to fly, so she spread wide her shining wings and leapt through, leaving the hole to close behind her on its own.
The wall groaned. The many-inches-thick metal covering, previously a seemingly unbroken surface, split apart into scale-like plates. Gradually these plates crept aside, almost like scuttling crabs, to reveal a wall of soft, red flesh. A long wound-like rent appeared, dripping with blood and slime, and with a wet, ripping sound the fleshy wall opened wide. 
It became apparent that the wall was metres thick and coated on the inner side with a layer of rough stone. 
%Gradually, the many-inches-thick metal plates crept 
Cracking and hissing, spilling sand and pebbles onto the floor\dash also covered in living stone\dash the stone gave way, and a great, slime-dripping aperture yawned in the castle wall. 

\Nzessua{} spread wide her shining wings and leapt through\dash the opening, as well as the corridor beyond, were huge, a hundred metres wide or more, easily wide enough for her to fly. The tunnels were twisted and uneven, like the bowels of some monster of tremendous size. Which was, in a way, exactly what they were: A city-sized abomination with stone and metal for skin. 

% She flies over the wall and past the spires to alight on a battlement of the central tower. The \daemon{} guards retreat as she lands, then bow in the corner. 
% She intones words of power in Kingstongue, proclaiming her name and title and bidding the fortress wall to open for her. It does. 
% She makes her way through the castle towards the throne room. Several times more she has to recite spells and invoke her name to open the doors, and always the palace obeys. 

% At last she reaches the throne room. \HriistD{} is lying on his pedestal, surrounded by \daemonic{} and humanoid servants and a few \dragons. 

A few more times she had to stop and invoke her name to open the way, until at last she reached the throne throne room.
%She flew and walked on through the palace\dash a few more times having to stop and invoke her name to open the way for her\dash until at last she reached the throne throne room.
The final wall to the inner sanctum was, naturally, especially well-sealed, forcing her to not only intone a lengthy monologue of power words, but also wait for the master of the castle to admit her. 

The master of the castle kept her waiting. \tho{Still enjoying your power trip, \HriistD?} she chuckled inside her head. Probably a trick for impressing mortals, she reflected. For one such as herself, a few minutes of waiting %hardly caused any emotions. 
were hardly a cause to get excited.

At length, the metal-plated living wall cracked, and a bleeding doorway was torn open before her. 
%a doorway opened and she glided into the throne chamber, an immense hall a thousand metres across. 
She glided into the throne chamber, an immense hall a thousand metres across. 

% It was lit by great braziers, in which one could perceive the writhing, hapless souls of the bound creatures whose life-force was providing the flame. 
The hall was lit by great braziers, and as \Nzessua{} passed one of them, the hapless soul of one of the bound creatures within almost took on form and seemed to reach out for her. 
%, powered by bound souls. 
The wretch almost formed a recognizable face. Almost. The spell that bound their life force as fuel for the torch rendered the poor things all but mindless, but sometimes their broken minds retained some memories. 

\Nzessua{} ignored the tortured soul and flew to settle on her favoured pedestal, which the other attendants in the chamber had wisely kept empty. The exterior of the pedestal was hard rock, but the top, where the occupant would lie or sit, was soft, supple skin, warm to the touch. 

\ta{\Nzessuacrith,} came a voice from the edge of the chamber. 

She turned slowly. \ta{\HriistD.} 

The host lay on the throne pedestal, tallest and most ornate of all. 

% She has felt a vertex spike: The sudden appearance of a potent vertex in the Web of the Realms, which quickly disappeared again. This vertex is, of course, the \Malach{} Ramiel, who sort of awakens in Carzain as Vizicar. 
% She confronts \Cheross{} with this: What does he know about it?
% He says it's one of the Twilight Angels. 
% Not far from me, she says. 
% Indeed. 
% Send your guys to find him, she says. I don't want him interfering with my affairs. 
% Things are already in motion, he says. 
% Have you spoken of this with Ishnaruchaefir? 
% Not yet. But I am expecting him shortly. It is his time to come to me. 

%Images of a myriad worlds swirled around her as \Nzes{} broke the Shroud and 
%Storms of power raged around her, the gleam of fire and lightning reflected in her metallic scales as she soared above the blasted plains of \Machai. 

%The cyclopean spires of \Orokhthegglain{} loomed far above her as she 



