\section{Tiamat's wings}

Imnath'uri threw back her long neck and shrieked in pain as mystic power rippled through her body. 
But she faltered not, and though her body and mind did rail, urging her to release the magic and slink back into the water, she did not give in.
%But she quickly regained her composure, and, 
%repressing the urge to release the forces of magic she was weaving and slink back into the water. 
Imnath'uri kept her spells in check, and lifting her eyes again toward the stars she resumed her incantations. %, speaking words of power in the True Tongue. 

\ta{Nash kweg\rhh ash se'rom Ashfaleth, ram pur churdzad shor Ashfaleth khel...} Imnath'uri chanted the words of the True Tongue, and the \daemons{} of the night did hearken. Urnazregond could see them, swarming about her, flowing through her. Savage they were, like a school of ravenous piranha fish. With fury they ripped into Imnath'uri's body, as if they lusted to tear her to bloody shreds, and indeed blood stained the rock all around where she perched, and scales torn loose together with red lumps of flesh littered the ground at her feet. But Imnath'uri held the imps in a grip of iron, and they struck only where she bade them strike, tore only where she bade them tear. 

Beside him, Jeshrasab stared in silence, mesmerized by the marvel of what they witnessed. But while Urnazregond marveled also, his sense of wonder was tinged with fear. He turned to \HesodN. \ta{Great one, surely this is not right? See how they rip and bite into her body! We must interfere!}

\ta{Patience, young one. Wait and see.} \HesodNz{} eyes were fixed on Imnath'uri, not even flickering as he spoke; \HesodN{} the elder, who had once been Kiba'zenwar, and whom Urnazregond had not yet grown accustomed to call by his new name. 
He studied her as intently as did Jeshrasab, but his was not awe but appraisal... appraisal and approval. \ta{She has them in grip yet. I would see what she intends.}

Urnazregond turned again to Imnath'uri. She had already changed much, in imitation of \HesodN, her large and heavy body having elongated into a sleeker, more smooth form. Her tail, which had been high and flat and ending in a great vertical fin as on any Vlekkesh'sal, had become long and slim, tapering to a whiplike point. The long fin along her back had become a row of sharp spines, and her webbed hands had given way to delicate fingers. Her head had grown a long, narrow snout, and great horns had sprung forth and now curved back along her snaking neck. \tho{She is fair. Barely like unto a Vlekkesh'sal at all, but so beautiful.}

Now she dug her claws into the earth, her tail lashing the ground behind her, as tirelessly she chanted the words of power that bound the imps to her will. The ritual of reshaping had gone on for hours; it would not be long till sunrise. Their magic was of the True Tongue, the tongue of the stars, and so relied on the guidance of the stars, and as such they worked their spells more easily at night when the stars could be clearly seen. Urnazregond looked into her eyes and saw that they were empty, staring into space, into the Worlds Beyond\dash the worlds of the stars, and of the \daemons. 

\ta{Sheshem'bracul Tashrun Kal naero tzuerimachir, naero xirashassed, naero xerifoss...} She invoked the names of stars and \daemons, her spell slowly rosing to a terrible crescendo, and Urnazregond could hear the wailing of the imps, like the music of a choir infernal. 

\ta{She is almost done...} announced Kiba'zenwar\dash\HesodN. Beside them Jeshrasab mouthed words, but no sound came out. 

Now Imnath'uri rose on her hind legs, stretching her body and neck up as if reaching for the sky. She threw wide her forearms and screamed aloud, a scream that carried dreadful pain, but also sublime ecstasy. There was a cracking, ripping and splattering sound, and twin fountains of blood erupted from her back, near her shoulders. Urnazregond shouted in alarm and would have rushed to her side, had not \HesodN{} called out to him. 

\ta{Stay. Do not interfere,} the elder commanded. 

And so Urnazregond beheld in horror this last stage of his beloved's transformation\dash horror, but also awe. Stumps of flesh and bone now grew forth from the wounds in Imnath'uri's back, like a second pair of arms. They grew and grew, stretching longer than her arms and legs, and they split and grew many ways at once, branching off into several \quo{fingers} near the end. Still they grew until two limbs together spanned as wide as her entire length, if not wider still. And now skin appeared, connecting the spindly fingers to form two immense...

\ta{Wings...} Jeshrasab breathed. \ta{She is forming wings!} 

And all of them watched in amazement as blood and life flowed into Imnath'uri's new wings. At long last she fell silent, the \daemons{} slowly dispersing around her. 

The spell of metamorphosis was complete. 

Imnath'uri slowly opened her eyes to gaze upon her new form. In wonder she studied her new wings, flexing them and spreading them wide for the first time. Carefully testing all her limbs and joints, she crouched down, all muscles tensed. She set off, jumping many yards into the air. Then she threw wide her wings and gave a tremendous blow\dash and soared! Again she flapped her wings, lifting her body higher into the air. Delighted, she let rip a triumphant roar as she propelled herself yet further skywards. 

\ta{Magnificent,} said \HesodN, the two younger Vlekkesh'sala stunned into silence. 



But he saw that her eyes were empty, staring into space, into the Worlds Beyond, and he suspected that she would...

Draecchonosh
